### 2016-08-10 docs/Notes.tex
added new files to repo

  % JFM
%\NeedsTeXFormat{LaTeX2e}
%\documentclass {jfm}

% PHYSICS OF FLUIDS
%\documentclass[aip, pof, reprint]{revtex4-1} 
% the files aip4-1.rtx seems to be necessary
\documentclass[11pt]{article}

% PACKAGES, minimal set?
\usepackage{graphicx}
\usepackage{amsmath, amssymb, amsfonts}
%\usepackage[justification=RaggedRight]{caption}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% LATEX DEFINITIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Partial differentiation, standard fraction notation
\newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
\newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
\newcommand{\pdpd}[3]  { \frac{\partial^2 #1}{\partial #2 \partial #3 } }
\newcommand{\pppd}[2]  { \frac{\partial^3 #1}{{\partial #2}^3} }
% Differentiation
\newcommand{\pdi}[2] { {\partial_#2} #1 }
\newcommand{\td}[2] { \frac{d #1} { d #2 } }
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
% Vectors and operators
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\avg}[1] { \left\langle {#1} \right\rangle}
\newcommand{\dash} {\text{-}}
\newcommand{\conj}[1] {\overline{#1}}

% Stuff
\newcommand {\bu} {\bvec{u}}
\newcommand{\nhat}{\hat{\bvec{n}}}
\newcommand{\shat}{\hat{\bvec{s}}}
\newcommand{\Vn}{V_n}

\newcommand{\Rey}{ \text{Re} }
% Domains
\newcommand {\bdry} {\partial B}
\newcommand {\onBdry} {\text{on } \bdry }
\newcommand {\xfar} {\text{as } \abs{\bvec{x}} \to \infty }
\newcommand {\nfar} {\text{as } \, \ny / \dchar \to \infty }

\newcommand{\nn}{\mathbf{n}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{Brief notes on erosion}
\author{}
\maketitle

%\begin{abstract}
%\end{abstract}

\section{Governing equations}
The deformation, or rate-of-strain, tensor is given by
\begin{equation}
\bvec{E} = \frac{1}{2} \left( \grad \bu + \grad \bu^T \right)
\end{equation}
where $\bu = (u,v)$ is the velocity field. The stress tensor is given by
\begin{equation}
\bvec{\sigma} = -p \bvec{I} + 2 \mu \bvec{E} = -p \bvec{I} + \mu \left( \grad \bu + \grad \bu^T \right)
\end{equation}
The surface traction is given by
\begin{equation}
\bvec{f} = \bvec{\sigma} \cdot \nhat 	\qquad \onBdry
\end{equation}
where $\nhat$ is the (outward) unit normal and $\bdry$ is the solid
boundary. The shear stress $\tau$ is defined as the tangential
component of the traction, i.e.~
\begin{equation}
\tau = \bvec{f} \cdot \shat 
= \mu \left( \grad \bu + \grad \bu^T \right) \cdot \nhat \cdot \shat	\qquad \onBdry
\end{equation}
where $\shat$ is the unit tangent vector. It turns out that the shear
stress is simply given by the surface vorticity
\begin{equation}
\tau = \mu \left( u_y - v_x \right) \qquad \onBdry
\end{equation}
which can be shown by a direct calculation, using the no-slip boundary
conditions (which implies that $\pdi{u}{s} = \pdi{v}{s} = 0$ on
$\bdry$).  The interface velocity of the eroding body is linearly
proportional to the absolute shear stress
\begin{equation}
\Vn = -C \abs{\tau}
\end{equation}
where $C$ is a constant.

\section{Layer potentials}
The kernel of the Stokes double-layer potential is
\begin{equation}
  \frac{1}{\pi} \frac{\rr \otimes \nn}{\rho^{2}} 
  \frac{\rr \otimes \ssigma}{\rho^{2}} \rr.
\end{equation}

The deformation tensor is
\begin{align*}
  \bvec{E} &= \frac{1}{2} \left( \grad \bu + \grad \bu^T \right) \\
  &= \frac{1}{\pi} \frac{(\rr \cdot \nn)(\rr \cdot \ssigma)}{\rho^{4}}I 
   + \frac{1}{2\pi} \frac{(\rr \cdot \ssigma)}{\rho^{4}}
    (\rr \otimes \nn + \nn \otimes \rr) \\
  &+ \frac{1}{2\pi} \frac{(\rr \cdot \nn)}{\rho^{4}} 
    (\rr \otimes \ssigma + \ssigma \otimes \rr) 
   - \frac{4}{\pi}\frac{(\rr \cdot \nn)(\rr \cdot \ssigma)}{\rho^{6}}
    (\rr \otimes \rr).
\end{align*}

The shear stress $\tau$ is
\begin{align*}
  \tau &= \frac{1}{\pi}\frac{(\rr \cdot \ssigma)}{\rho^{4}}
      (\rr + (\nn \cdot \rr)\nn) \cdot \shat
   + \frac{1}{\pi}\frac{(\rr \cdot \nn)}{\rho^{4}}
      ((\ssigma \cdot \nn)\rr + (\rr \cdot \nn)\ssigma) \cdot \shat \\
  &- \frac{8}{\pi}\frac{(\rr \cdot \nn)(\rr \cdot \ssigma)}{\rho^{6}}
      (\rr \cdot \nn)(\rr \cdot \shat) \\
  &= \frac{1}{\pi}\frac{(\rr \cdot \ssigma)(\rr \cdot \shat)}{\rho^{4}}
   + \frac{1}{\pi}\frac{(\rr \cdot \nn)(\ssigma \cdot \nn)(\rr \cdot \shat)}{\rho^{4}} \\
  &+ \frac{1}{\pi}\frac{(\rr \cdot \nn)^{2}(\ssigma \cdot \shat)}{\rho^{4}}
   - \frac{8}{\pi}\frac{(\rr \cdot \nn)^{2}(\rr \cdot \ssigma)(\rr \cdot \shat)}{\rho^{6}}
\end{align*}

\end{document}

### 2016-08-10 code/gmres_routines.f

@@ -1,0 +1,2755 @@
+*DECK DGMRES
+      SUBROUTINE DGMRES (N, B, X, NELT, IA, JA, A, ISYM, MATVEC, MSOLVE,
+     +   ITOL, TOL, ITMAX, ITER, ERR, IERR, IUNIT, SB, SX, RGWK, LRGW,
+     +   IGWK, LIGW, RWORK, IWORK)
+C***BEGIN PROLOGUE  DGMRES
+C***PURPOSE  Preconditioned GMRES iterative sparse Ax=b solver.
+C            This routine uses the generalized minimum residual
+C            (GMRES) method with preconditioning to solve
+C            non-symmetric linear systems of the form: Ax = b.
+C***LIBRARY   SLATEC (SLAP)
+C***CATEGORY  D2A4, D2B4
+C***TYPE      DOUBLE PRECISION (SGMRES-S, DGMRES-D)
+C***KEYWORDS  GENERALIZED MINIMUM RESIDUAL, ITERATIVE PRECONDITION,
+C             NON-SYMMETRIC LINEAR SYSTEM, SLAP, SPARSE
+C***AUTHOR  Brown, Peter, (LLNL), pnbrown@llnl.gov
+C           Hindmarsh, Alan, (LLNL), alanh@llnl.gov
+C           Seager, Mark K., (LLNL), seager@llnl.gov
+C             Lawrence Livermore National Laboratory
+C             PO Box 808, L-60
+C             Livermore, CA 94550 (510) 423-3141
+C***DESCRIPTION
+C
+C *Usage:
+C      INTEGER   N, NELT, IA(NELT), JA(NELT), ISYM, ITOL, ITMAX
+C      INTEGER   ITER, IERR, IUNIT, LRGW, IGWK(LIGW), LIGW
+C      INTEGER   IWORK(USER DEFINED)
+C      DOUBLE PRECISION B(N), X(N), A(NELT), TOL, ERR, SB(N), SX(N)
+C      DOUBLE PRECISION RGWK(LRGW), RWORK(USER DEFINED)
+C      EXTERNAL  MATVEC, MSOLVE
+C
+C      CALL DGMRES(N, B, X, NELT, IA, JA, A, ISYM, MATVEC, MSOLVE,
+C     $     ITOL, TOL, ITMAX, ITER, ERR, IERR, IUNIT, SB, SX,
+C     $     RGWK, LRGW, IGWK, LIGW, RWORK, IWORK)
+C
+C *Arguments:
+C N      :IN       Integer.
[…]

### 2016-08-10 code/stokesDriver.f

@@ -1,0 +1,29 @@
+      program stokesDriver
+      implicit real*8 (a-h,o-z)
+
+      parameter (ninner = 256)
+
+      dimension x(ninner),y(ninner)
+      dimension shear_stress(ninner)
+
+
+      twopi = 8.d0*datan(1.d0)
+      dtheta = twopi/dble(ninner)
+      do k = 1,ninner
+        theta = dble(k-1)*dtheta
+        x(k) = 5.d-1*dcos(theta)
+        y(k) = 5.d-1*dsin(theta)
+c        rad = 2.d-1 + 8.d-2*dcos(5*theta)
+c        x(k) = rad*dcos(theta)
+c        y(k) = rad*dsin(theta)
+      enddo
+c     parameterize from left most point and proceed up the top of the
+c     curve, throught the back point, and back to the leading
+c     singularity point
+
+      call stokesSolver(ninner,x,y,shear_stress)
+c     pass in number of points and x and y coordinates and return the
+c     shear stress on the boundary
+
+      end
+

### 2016-08-10 code/stokesSolver.f

@@ -1,0 +1,1101 @@
+      subroutine stokesSolver(nninner,xx,yy,shear_stress)
+c     Input x and y coordinates and return the shear_stress on the
+c     boundary.  Outer wall is used to enclose the inner boundary so
+c     that Stokes paradox is avoided
+      implicit real*8 (a-h,o-z)
+
+      dimension xx(nninner),yy(nninner)
+c     x and y coordinates of obstacle
+
+      parameter (nmax = 2**15)
+c     max points on the boundary of the obstacle      
+      parameter (maxl = 400, liwork = 30)
+      parameter (lrwork = 10 + nmax*(maxl+6) + 
+     $     maxl*(maxl+3))
+c     maximum size of workspaces for GMRES
+
+      parameter(nx = 20,ny = 20)
+c     number of points in x and y direction where velocity will be
+c     computed
+
+      dimension x(nmax),y(nmax)
+      dimension px(nmax), py(nmax)
+c     x and y coordinates of the normal of the obstacle
+      dimension cur(nmax), speed(nmax)
+c     Jacobian and curvature of the geometry
+
+      dimension xouter(nmax),youter(nmax)
+c     x and y coordinates of confining wall
+      dimension px0(nmax), py0(nmax)
+c     x and y coordinates of the normal of the confining wall
+      dimension cur0(nmax), speed0(nmax)
+c     Jacobian and curvature of the confining wall
+
+      dimension gmwork(lrwork), igwork(liwork)
+c     workspaces for GMRES
+
+      dimension rhs(nmax)
+c     right hand side
+      dimension den(nmax)
+c     x and y coordinates of the density function
+      dimension E11(2*nninner),E12(2*nninner),E22(2*nninner)
+c     components of the deformation gradient on the obstacle
+      dimension shear_stress(nninner)
+c     shear stress on the obstacle
+
+      dimension xtar(nx,ny),ytar(nx,ny)
+      dimension utar(nx,ny),vtar(nx,ny)
+
+      common /geometry/ x,y,centerx,centery,px,py,cur,speed,ninner
+      common /wall/ xouter,youter,px0,py0,cur0,speed0,nouter
[…]

### 2016-08-14 docs/Notes.tex
updated tex notes with ideas about how to move the center of mass in the theta-L formulation

@@
-  % JFM
-%\NeedsTeXFormat{LaTeX2e}
-%\documentclass {jfm}
-
-% PHYSICS OF FLUIDS
-%\documentclass[aip, pof, reprint]{revtex4-1} 
-% the files aip4-1.rtx seems to be necessary
 \documentclass[11pt]{article}
 
-% PACKAGES, minimal set?
-\usepackage{graphicx}
-\usepackage{amsmath, amssymb, amsfonts}
+% PACKAGES
+\usepackage{graphicx, amsmath, amssymb, amsfonts, mathtools, mathrsfs, color}
+\usepackage{comment, enumerate, tabularx}
+\usepackage{natbib, hyperref, url}
 %\usepackage[justification=RaggedRight]{caption}
@@
 
-% Partial differentiation, standard fraction notation
+% Basic editing
+\newcommand{\tocite}{{\color{blue}(to cite)}}
+\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
+\newcommand{\np}{\newpage \noindent}
+% Derivatives
 \newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
 \newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
-\newcommand{\pdpd}[3]  { \frac{\partial^2 #1}{\partial #2 \partial #3 } }
-\newcommand{\pppd}[2]  { \frac{\partial^3 #1}{{\partial #2}^3} }
-% Differentiation
 \newcommand{\pdi}[2] { {\partial_#2} #1 }
@@
 \newcommand{\norm}[1]{\left\| #1 \right\|}
-\newcommand{\avg}[1] { \left\langle {#1} \right\rangle}
-\newcommand{\dash} {\text{-}}
-\newcommand{\conj}[1] {\overline{#1}}
-
-% Stuff
+\newcommand{\mean}[1]{\left< #1 \right>}
+% Specific variables
 \newcommand {\bu} {\bvec{u}}
@@
 \newcommand{\shat}{\hat{\bvec{s}}}
-\newcommand{\Vn}{V_n}
-
-\newcommand{\Rey}{ \text{Re} }
+\newcommand{\eps}{\varepsilon}
+\newcommand{\atau}{\abs{\tau}}
+\newcommand{\thh}{\hat{\theta}}
+\newcommand{\GG}{\mathcal{G}}
+\newcommand{\Dt}{\Delta t}
+\newcommand{\X}{\bvec{X}}
 % Domains
@@
 \newcommand {\xfar} {\text{as } \abs{\bvec{x}} \to \infty }
-\newcommand {\nfar} {\text{as } \, \ny / \dchar \to \infty }
-
-\newcommand{\nn}{\mathbf{n}}
-\newcommand{\rr}{\mathbf{r}}
-\newcommand{\ssigma}{\boldsymbol{\sigma}}
 
@@
 
-\section{Governing equations}
+\section{Shear stress and erosion law}
 The deformation, or rate-of-strain, tensor is given by
@@
 \end{equation}
-where $\nhat$ is the (outward) unit normal and $\bdry$ is the solid
-boundary. The shear stress $\tau$ is defined as the tangential
-component of the traction, i.e.~
+where $\nhat$ is the (outward) unit normal and $\bdry$ is the solid boundary. The shear stress $\tau$ is defined as the tangential component of the traction, i.e.~
 \begin{equation}
@@
 \end{equation}
-where $\shat$ is the unit tangent vector. It turns out that the shear
-stress is simply given by the surface vorticity
+where $\shat$ is the unit tangent vector. It turns out that the shear stress is simply given by the surface vorticity
 \begin{equation}
@@
 \end{equation}
-which can be shown by a direct calculation, using the no-slip boundary
-conditions (which implies that $\pdi{u}{s} = \pdi{v}{s} = 0$ on
-$\bdry$).  The interface velocity of the eroding body is linearly
-proportional to the absolute shear stress
+which can be shown by a direct calculation, using the no-slip boundary conditions (which implies that $\pdi{u}{s} = \pdi{v}{s} = 0$ on $\bdry$).
+The interface velocity of the eroding body is linearly proportional to the absolute shear stress
 \begin{equation}
-\Vn = -C \abs{\tau}
+V_n = -C \atau
 \end{equation}
@@
 
-\section{Layer potentials}
-The kernel of the Stokes double-layer potential is
+\section{Scaling law and interface smoothing}
+For Stokes flow, the shear stress scales like
 \begin{equation}
-  \frac{1}{\pi} \frac{\rr \otimes \nn}{\rho^{2}} 
-  \frac{\rr \otimes \ssigma}{\rho^{2}} \rr.
+\tau \sim \mu V/L
+\end{equation}
+where $V$ and $L$ are a characteristic velocity and length scale respectively.
+To evolve the interface in our numerical method, we will probably need to introduce some smoothing to mitigate high frequencies.
+A common approach is to introduce a small curvature term into the interface velocity, sometimes called the method of vanishing viscosity.
+The most basic implementation would be
+\begin{equation}
+V_n = - C \atau - \eps \kappa
+\end{equation}
+where $\eps$ is a small parameter and $\kappa$ is the surface curvature. However, we have two additional preferences
+\begin{enumerate}
+\item As the body changes size, we would like the influence of the curvature term relative to the shear stress to remain the same.
+\item We prefer the curvature term not to change the size of the body.
+\end{enumerate}
+Fortunately, the first requirement is already satisfied since both $\tau$ and $\kappa$ scale like $1/L$.
+To satisfy the second requirement, we replace $\kappa$ with this same quantity minus its mean.
+To allow for some generality, we allow the curvature term by to be scaled by a power of $L$, giving
+\begin{equation}
+V_n = - C \atau - \eps L^{\beta} \left(\kappa - \frac{2 \pi}{L} \right)
+\end{equation}
+Thus, for the present case of Stokes flow $\beta=0$, but for the previous case of high-Reynolds-number flow $\beta=1/2$.
+
+\section{Numerical interface evolution}
+
+To evolve the interface numerically, we use the $\theta$-$L$ method.
+Rather than re-derive the formulas, I will use the convention from Shelley 1994, with the curve parameterized in the CCW direction and the normal vector pointing {\em inward}.
+With this convention, the normal interface velocity is the negative of what it was previously, giving
+\begin{equation}
+V_n = C \atau + \eps L^{\beta} \left(\kappa - \frac{2 \pi}{L} \right)
+\end{equation}
+Recall that for Stokes flow, $\beta = 0$.
+
+Now, the interface $\X = (x,y)$ evolves according to
+\begin{equation}
+\pd{\bvec{X}}{t} = V_n \nhat + V_s \shat
+\end{equation}
+where $\nhat = (-y_s, x_s)$ is the inward pointing normal vector and $\shat = (x_s, y_s)$ is the tangential vector (running in the CCW direction).
+Here, we have introduced a tangential velocity $V_s$ that will be chosen to keep the curve in the equal-arclength parameterization.
+We will frequently use a normalized arclength $\alpha = s/L$, where $L$ is the total length of the curve.
+
+We introduce the tangent angle $\theta$, defined as
+\begin{equation}
+\tan \theta = y_s/x_s = y_\alpha / x_\alpha
+\end{equation}
+Remember the identity that $x_s^2 + y_s^2 = 1$ as this is very useful.
+The curvature is given by
+\begin{equation}
+\kappa = x_s y_{ss} - x_{ss} y_s = \pd{\theta}{s} = L^{-1} \pd{\theta}{\alpha}
+\end{equation}
+We are using the standard convention, where a convex shape, like a circle, has positive curvature. The normal velocity now can be written as
+\begin{equation}
+V_n = C \atau + \eps L^{\beta-1} \left(\pd{\theta}{\alpha} - 2 \pi \right)
 \end{equation}
 
-The deformation tensor is
-\begin{align*}
-  \bvec{E} &= \frac{1}{2} \left( \grad \bu + \grad \bu^T \right) \\
-  &= \frac{1}{\pi} \frac{(\rr \cdot \nn)(\rr \cdot \ssigma)}{\rho^{4}}I 
-   + \frac{1}{2\pi} \frac{(\rr \cdot \ssigma)}{\rho^{4}}
-    (\rr \otimes \nn + \nn \otimes \rr) \\
-  &+ \frac{1}{2\pi} \frac{(\rr \cdot \nn)}{\rho^{4}} 
-    (\rr \otimes \ssigma + \ssigma \otimes \rr) 
-   - \frac{4}{\pi}\frac{(\rr \cdot \nn)(\rr \cdot \ssigma)}{\rho^{6}}
-    (\rr \otimes \rr).
-\end{align*}
+We now discuss how to choose $V_s$ to remain in the equal-arclength frame of reference. We will use the term
+\begin{equation}
+\gamma = \pd{\theta}{\alpha} V_n
+\end{equation}
+Then the necessary tangential velocity is determined by
+\begin{equation}
+\td{V_s}{\alpha} = \gamma - \mean{\gamma}
+\end{equation}
+where $\mean{}$ indicates the mean value.
 
-The shear stress $\tau$ is
-\begin{align*}
-  \tau &= \frac{1}{\pi}\frac{(\rr \cdot \ssigma)}{\rho^{4}}
-      (\rr + (\nn \cdot \rr)\nn) \cdot \shat
-   + \frac{1}{\pi}\frac{(\rr \cdot \nn)}{\rho^{4}}
-      ((\ssigma \cdot \nn)\rr + (\rr \cdot \nn)\ssigma) \cdot \shat \\
-  &- \frac{8}{\pi}\frac{(\rr \cdot \nn)(\rr \cdot \ssigma)}{\rho^{6}}
-      (\rr \cdot \nn)(\rr \cdot \shat) \\
-  &= \frac{1}{\pi}\frac{(\rr \cdot \ssigma)(\rr \cdot \shat)}{\rho^{4}}
-   + \frac{1}{\pi}\frac{(\rr \cdot \nn)(\ssigma \cdot \nn)(\rr \cdot \shat)}{\rho^{4}} \\
-  &+ \frac{1}{\pi}\frac{(\rr \cdot \nn)^{2}(\ssigma \cdot \shat)}{\rho^{4}}
-   - \frac{8}{\pi}\frac{(\rr \cdot \nn)^{2}(\rr \cdot \ssigma)(\rr \cdot \shat)}{\rho^{6}}
-\end{align*}
+We now discuss how to evolve $\theta$ and $L$ forward in time according to the interface velocity given above. The resulting evolution equations are
+\begin{align}
+& \td{L}{t} = - \mean{\gamma} \\
+& \pd{\theta}{t} = L^{-1} \left( \pd{V_n}{\alpha} + \pd{\theta}{\alpha} V_s \right)
+\end{align}
+Then, using the above $V_n$, the equation for $\theta$ simplifies to
+\begin{equation}
+\pd{\theta}{t} = \eps L^{\beta-2} \ppd{\theta}{\alpha} + L^{-1} \left( C \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
+\end{equation}
+
+We now discuss the numerical methods used to solve the above evolution equations. For $L$, we use an explicit method
+\begin{equation}
+L^{(n+1)} = L^{(n)} + \frac{\Dt}{2} \left( 3 M^{(n)} - M^{(n-1)} \right)
+\end{equation}
+where
+\begin{equation}
+M = \td{L}{t} = -\mean{\gamma}
+\end{equation}
+For $\theta$, we use a spectral method, giving
+\begin{equation}
+\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{\beta-2} \thh_k = \hat{N}_k
+\end{equation}
+where the nonlinear terms are grouped together as
+\begin{equation}
+N = L^{-1} \left( C \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
+\end{equation}
+We evolve with the integrating-factor method. When recast in terms of Gaussian filters, this gives
+\begin{equation}
+\thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
++ \frac{\Dt}{2} \left( 3 \GG(N^{(n)}, \sigma_1) - \GG(N^{(n-1)}), \sigma_2 \right)
+\end{equation}
+where
+\begin{align}
+& \sigma_1 = 2 \pi \sqrt{\eps \Dt} \sqrt{(L^{n})^{\beta-2} + (L^{n+1})^{\beta-2} } 	\\
+& \sigma_2 = 2 \pi \sqrt{\eps \Dt} \sqrt{(L^{n-1})^{\beta-2} + 2 (L^{n})^{\beta-2} + (L^{n+1})^{\beta-2} }
+\end{align}
+
+\subsection{Center of mass motion}
+Consider the body's center of mass
+\begin{equation}
+(x_{cm}, y_{cm}) = \frac{1}{A} \iint (x, y) \, dA
+\end{equation}
+I did a calculation to determine the motion of the center of mass, given the interface velocity. The result that I get is
+\begin{equation}
+\td{}{t} (x_{cm}, y_{cm})  = -\frac{1}{A} \int (x(s), y(s)) V_n(s) \, ds
+\end{equation}
+I believe the sign is correct for $\nhat$ the inward pointing normal, so that $V_n$ is positive if the body is shrinking.
+
+To calculate the center of mass, I can use the divergence theorem
+\begin{equation}
+\iint \grad \cdot \bvec{F} \, dA = \int \bvec{F} \cdot \nhat \, ds
+\end{equation}
+Take $\bvec{F} = \frac{1}{2} (x^2, y^2)$, so that $\grad \cdot \bvec{F} = (x,y)$. Then
+\begin{equation}
+(x_{cm}, y_{cm} ) = \frac{1}{2 A} \int x^2 n_x + y^2 n_y \, ds
+\end{equation}
+To calculate the total area, $A$, I can use the divergence theorem again, to get
+\begin{equation}
+A = \int x n_x ds = \int y n_y ds
+\end{equation}
 

### 2016-08-14 julia/geometries.jl
Added the folder julia with the julia codes in it.

@@ -1,0 +1,48 @@
+# geometries.jl: Construct various geometries.
+
+# heaviside: The Heaviside function
+function heaviside(tt)
+   0.5 * (sign(tt) + 1)
+end
+
+#= trigeo: Construct a triangle geometry within the theta-L framework.
+nn: The number of points on the triangle.
+angle: The triangle's front opening angle in degrees.
+sigma: The amount of smoothing. 
+The triangle has the following properties:
+- It is up-down symmetric.
+- It's nose is at the origin.
+- It has a vetical extent of 2 units.
+- It is parameterized by t, i.e. (x(t), y(t)), for t in [0,1]
+- It is parameterized in the CCW direction. =#
+
+function trigeo(nn, angle, sigma)
+	#= Initially, the triangle is parameterized in CW direction, 
+	but that will be reversed at the end. =#
+	# Parameterize the triangle by t in [0,1] and use and offset t-grid.
+	dt = 1.0/nn
+	tt = collect(range(0.5*dt, dt, nn))
+	# alpha is the half opening angle of the triangle in radians.
+	alpha = 0.5 * angle*pi/180
+	# The length of the traingle's sloped face.
+	len1 = 1/sin(alpha)
+	# Total arclength is the sum of the 2 sloped faces and back vertical face.
+	stot = 2+2*len1
+	# The values of t where we change from one face to another.
+	t1 = len1 / stot
+	t2 = (2+len1) / stot
+	# The tangent angle theta as a function of t.
+	theta = 0.0*dt
+	theta = alpha 
+	theta += (-0.5*pi-alpha)*heaviside(tt-t1) 
+	theta += (-0.5*pi-alpha)*heaviside(tt-t2)
+
+	# Smooth the triangle.
+	theta = gaussfilter(theta + 2*pi*tt, sigma) - 2*pi*tt
+	# To parameterize in the CCW direction, reverse the vector and add pi.
+	theta = reverse(theta) + pi
+	# The point (0,xback) fixes the nose at the origin. 
+	xback = 1/tan(alpha)
+	return theta,stot,xback,tt
+end
+

### 2016-08-14 julia/spectral.jl

@@ -1,0 +1,73 @@
+# spectral.jl
+#= Collection of spectral routines 
+=#
+
+# fftnice: shifted fft.
+function fftnice(fx::Vector)
+	fh = fft(fx)
+	return fftshift(fh)
+end
+
+# ifftnice: shifted ifft.
+function ifftnice(fh::Vector)
+	fhsh = ifftshift(fh)
+	return ifft(fhsh)
+end
+
+# kvec: Construct the vector of k values.
+# In the even case, sets the highest mode to zero or not depending on hmode.
+function kvec(nn::Integer, hmode=0)
+	if iseven(nn)
+		nsm = div(nn,2)-1
+		return [hmode*(nsm+1); -nsm : nsm]
+	else
+		nsm = div(nn-1,2)
+		return -nsm : nsm
+	end
+end
+
+function imagtest(fx::Vector, thold::Float64=1e-10)
+	maxim = maxabs(imag(fx))
+	if maxim > thold
+		warn("imag part too big: ", maxim)
+	end
+	return
+end
+
+# specdiff: Compute the derivative of fx spectrally.
+# Default: assumes that the length of the interval is 1.0
+function specdiff(fx::Vector, intvlen::Float64=1.0)	
+	fh = fftnice(fx)
+	kv = kvec(length(fx), 0)
+	dfh = 2*pi*im * kv.*fh
+	df = ifftnice(dfh)
+	imagtest(df)
+	return real(df)/intvlen
+end
+
+# specint: Compute the antiderivative of fx spectrally.
+# Assumes that the input fx has mean-zero.
+# Forces the output Fx to have mean-zero.
+function specint(fx::Vector, intvlen::Float64=1.0)
+	fh = fftnice(fx)
+	kv = kvec(length(fx), 0)
+	Fh = fh./(2*pi*im*kv)
+	# This kills the zeroth mode and, if nn is even, also the highest mode.
+	Fh[kv.==0] = 0.0
+	Fx = ifftnice(Fh)
+	imagtest(Fx)
+	return real(Fx)*intvlen	
+end
+
+# gaussfilter: Apply a Gaussian filter of width sigma.
+function gaussfilter(fx::Vector, sigma::Float64)
+	fh = fftnice(fx)
+	kv = kvec(length(fx), 1)
+	fh .*= exp(-0.5*sigma^2 * abs(kv).^2)
+	fs = ifftnice(fh)
+	return real(fs)
+end
+
[…]

### 2016-08-14 julia/tests/mymod.f90

@@ -1,0 +1,16 @@
+module mymod 
+
+contains
+   function foo(xx)
+      real*8 :: foo, xx
+      foo = 2*xx
+   end function foo
+
+   subroutine add(xx,yy)
+      real*8, intent(in) :: xx(2)
+      real*8, intent(out) :: yy(2)
+      yy(1) = xx(1)+xx(2)
+      yy(2) = xx(1)*xx(2)
+   end subroutine add
+
+end module mymod

### 2016-08-14 julia/tests/zfort.jl

@@ -1,0 +1,11 @@
+# Test calling a Fortran code.
+workspace()
+
+aa = 1.8
+bb = ccall((:__mymod_MOD_foo, "libmymod.so"), 
+		Float64, (Ptr{Float64},), &aa)
+
+xx = [1.2, 0.4]
+yy = [0.0, 0.0]
+ccall((:__mymod_MOD_add, "libmymod.so"), 
+	Void, (Ptr{Float64}, Ptr{Float64}), xx, yy)

### 2016-08-14 julia/tests/zgaussfilter.jl

@@ -1,0 +1,27 @@
+# Test gaussfilter
+# workspace()
+# set_zero_subnormals(true)
+include("spectral.jl")
+using Winston
+
+function wrap(fx)
+	return [fx; fx; fx[1]]
+end
+
+function teststuff()
+	nn = 64
+	sigma = 0.2
+	# Calculated parameters
+	aa = -pi
+	bb = pi
+	dx = (bb-aa)/nn
+	xx = range(aa, dx, nn)
+	# Smooth a function
+	fx = abs(xx)
+	fs = gaussfilter(fx,sigma)
+	# Plot
+	xext = [xx; xx+(bb-aa); 2*bb-aa]
+	plot(xext, wrap(fx), "k.-", xext, wrap(fs), "b.-")
+end
+
+teststuff()

### 2016-08-14 julia/tests/zspecdiff.jl

@@ -1,0 +1,32 @@
+# Test specdiff() and specint()
+# workspace()
+include("spectral.jl")
+
+function teststuff()
+	nn = 4
+	aa = 0.0
+	bb = 2*pi
+	dx = (bb-aa)/nn
+	xx = range(aa, dx, nn)
+
+	# This function is resolved exactly for nn>=4.
+	a0,a1,a2,b1 = randn(4)
+	fx = 0.5*a0 + a1*cos(xx) + a2*cos(2*xx) + b1*sin(xx)
+	# Exact derivative.
+	dfex = -a1*sin(xx) -2*a2*sin(2*xx) + b1*cos(xx)
+	# Exact antiderivative, forgetting about a0 term.
+	Fxex = a1*sin(xx) + 0.5*a2*sin(2*xx) - b1*cos(xx)
+
+	# Numerical derivative using specdiff and adjusting for the interval size.
+	df = specdiff(fx, bb-aa)
+	# Numerical antiderivative using specint and adjusting for the interval size.
+	Fx = specint(fx, bb-aa)
+
+	# Print the errors.
+	errdf = maxabs(dfex-df)
+	errFx = maxabs(Fxex-Fx)
+	println("specdiff error = ", errdf)
+	println("specint error = ", errFx)
+end
+
+teststuff()

### 2016-08-14 julia/thetalen.jl

@@ -1,0 +1,126 @@
+# thetalen.jl: Collection of codes for theta-L boundary evolution.
+#=
+Variables
+ast (vector): The absolute value of the shear stress, computed by fluid solver.
+theta (vector): The tangent angle as it varies along the boundary.
+len (scalar): The length of the curve, L.
+alpha(vector): Normalized arclength, s/L
+
+Parameters
+dt: The time-step.
+epsilon: The constant for the smoothing, curvature-driven-flow component.
+beta: The power of L hitting the curvature-term in the V_n.
+
+Convention for tangential and normal vectors
+I use the same convention as Shelley 1994.
+I assume the curve is parameterized in the counter-clockwise (CCW) direction,
+and I use the inward pointing normal.
+
+Misc Notes
+synonums: advnance, increment, step, evolove
+=#
+
+#= advance_thetalen: Advance theta and len from time-step n=1 to n=2, 
+using some values from n=0. =#
+function advance_thetalen(ast::Vector{Float64}, theta1::Vector{Float64}, 
+		len0::Float64, len1::Float64, M0::Float64, N0::Vector{Float64}, 
+		dt::Float64, epsilon::Float64, beta::Real)
+
+	# Get the terms M and N at time n=1.
+	M1,N1 = getMN(ast,theta1,len1,epsilon,beta)
+	# Update len with explicit method.
+	len2 = len1 + 0.5*dt*(3*M1-M0)
+	if len2<0; error("The curve length is negative"); return; end
+	# Update theta with integrating-factor method.
+	theta2 = advance_theta(theta1,len0,len1,len2,N0,N1,dt,epsilon,beta)
+	return theta2, len1, len2, M1, N1
+end
+
+# getMN: Calculates the terms M=dL/dt and N.
+function getMN(ast::Vector{Float64}, theta::Vector{Float64}, len::Float64, 
+		epsilon::Float64, beta::Real)
+	# The derivative of theta wrt alpha.
+	alpha = getalpha(endof(theta))
+	dtheta = specdiff(theta - 2*pi*alpha) + 2*pi
+	# Calculate the normal velocity.
+	vnorm = ast + epsilon*len^(beta-1) * (dtheta - 2*pi)
+	# Get the tangential velocity and dL/dt.
+	vtang, dldt = tangvel(dtheta, vnorm)
[…]

### 2016-08-14 julia/zfort.jl

@@ -1,0 +1,21 @@
+# Test calling a Fortran code.
+# workspace()
+using Winston
+
+nn = 64
+rad = 0.05
+
+dth = 2*pi/nn
+theta = range(0, dth, nn)
+xx = rad*cos(theta)
+yy = rad*sin(theta)
+tau = zeros(nn)
+
+ccall((:stokessolver_, "libstokes.so"),
+        Void, (Ptr{Int}, Ptr{Float64}, Ptr{Float64}, Ptr{Float64}),
+        &nn, xx, yy, tau)
+
+tauex = sin(theta)/rad
+err = maximum(abs(tau-tauex))
+println(err)
+plot(theta,tau,".-k",theta,tauex,".-b")

### 2016-08-14 julia/ztriangle.jl

@@ -1,0 +1,67 @@
+# Test curvature-driven flow for an initial triangle.
+# workspace()
+include("spectral.jl")
+include("thetalen.jl")
+include("geometries.jl")
+using Winston
+
+# plotcurve
+function plotcurve(theta::Vector{Float64}, len::Float64, 
+		xback::Float64, x0::Vector{Float64}, y0::Vector{Float64}, cnt::Integer)
+	# Reconstruct the x,y coordinates of the curve.
+	xx,yy = getcurve(theta,len,xback)
+	p1 = plot(x0,y0,".-", xx,yy,".-")
+	xlim(-1.0,1.0); ylim(-1.0,1.0)
+	figname = string("../Figs/fig",string(cnt),".pdf")
+	savefig(p1, figname, width=500, height=500)
+end
+
+##### PARAMETERS #####
+# Triangle geometry parameters.
+nn = 128
+angle = 90
+sigma = 0.05
+# Evolution parameters.
+tfin = 2.0
+dt = 0.02
+epsilon = 0.1
+beta = 0
+######################
+
+# Get the initial triangular geometry.
+theta,len,xback,alpha = trigeo(nn, angle, sigma)
+x0,y0 = getcurve(theta,len,xback)
+# For pure curvature driven flow, make the stress term vanish.
+ast = 0.0*theta[:]
+
+# Initialize with RK2
+len0 = len
+# Get the time derivatives at t=0
+M0,N0 = getMN(ast,theta,len,epsilon,beta)
+th0dot = thetadot(theta,len,N0,epsilon,beta)
+# Take the first half step of RK2
+len05 = len0 + 0.5*dt*M0
+th05 = theta + 0.5*dt*th0dot
+# Get the time derivatives at t=0.5*dt
+M05,N05 = getMN(ast,th05,len05,epsilon,beta)
+th05dot = thetadot(th05,len05,N05,epsilon,beta)
+# Take the second half step of RK2
+len1 = len05 + 0.5*dt*M05
+theta1 = th05 + 0.5*dt*th05dot
+# Plot the result.
+cnt = 1
+plotcurve(theta1,len1,xback,x0,y0,cnt)
+
+# Enter while loop.
+tfin += 0.1*dt
+tm = dt
+while(tm < tfin)
+	# Advance theta and len in time
+	theta1,len0,len1,M0,N0 = advance_thetalen(ast,theta1,
[…]

### 2016-08-21 docs/Notes.tex
Added to latex notes. Discussed motion of a reference point for theta-L.

@@
 
-\subsection{Center of mass motion}
+\subsection{Motion of a reference point}
+
+\subsubsection{The center of mass}
 Consider the body's center of mass
@@
 
+\subsubsection{The surface-average coordinates}
+I believe this will be even simpler. Consider the average of the surface coordinates
+\begin{equation}
+(x_a, y_a) = \int (x(\alpha), y(\alpha)) \, d\alpha
+\end{equation}
+I believe that this point moves according to
+\begin{equation}
+\td{}{t} (x_a, y_a) = \int V_n \, (n_x, n_y) \, d\alpha
+\end{equation}
+
 \end{document}

### 2016-08-21 julia/basic.jl

@@ -1,0 +1,107 @@
+# basic.jl: Basic stuff.
+
+#################### Object data types ####################
+# ParamType includes the parameters dt, epsilon, and beta.
+type ParamType
+	dt::Float64; epsilon::Float64; beta::Real;
+end
+# ThetaLenType includes all of the data that for a curve.
+type ThetaLenType
+	theta::Vector{Float64}; len::Float64; xc::Float64; yc::Float64; 
+	atau::Vector{Float64}; mterm::Float64; nterm::Vector{Float64};
+	xx::Vector{Float64}; yy::Vector{Float64};
+end
+##################################################
+
+#################### Includes ####################
+using Winston
+include("spectral.jl")
+include("thetalen.jl")
+##################################################
+
+#################### Object functions ####################
+# Create a new ThetaLenType that has all zeros.
+function new_thlen()
+	return ThetaLenType([], 0., 0., 0., [], 0., [], [], [])
+end
+# Copy the relevant contents from thlen1 to thlen2.
+function copy_thlen!(thlen1::ThetaLenType, thlen2::ThetaLenType)
+	thlen2.theta = thlen1.theta
+	thlen2.len = thlen1.len
+	thlen2.xc = thlen1.xc
+	thlen2.yc = thlen1.yc
+	thlen2.atau = thlen1.atau
+	thlen2.mterm = thlen1.mterm
+	thlen2.nterm = thlen1.nterm
+	thlen2.xx = thlen1.xx
+	thlen2.yy = thlen1.yy
+	return
+end
+##################################################
+
+#################### Stokes functions ####################
+# All routines work for multiple bodies.
+# stokes: Julia wrapper to call the Fortran stokessolver
+function stokes(npts::Integer, nbods::Integer, xx::Vector{Float64}, yy::Vector{Float64})
+	ntot = npts*nbods
+	tau = zeros(Float64, ntot)
+	ccall((:stokessolver_, "libstokes.so"),
+		Void, (Ptr{Int}, Ptr{Int}, Ptr{Float64}, Ptr{Float64}, Ptr{Float64}), 
+		&npts, &nbods, xx, yy, tau)
+	return tau
+end
+# stokes!: Dispatch for vector of ThetaLenType; updates atau in each thlen.
+function stokes!(thlenv::Vector{ThetaLenType})
+	nbods = endof(thlenv)
+	npts = endof(thlenv[1].theta)
[…]

### 2016-08-21 julia/thetalen.jl

@@ -105,7 +105,7 @@ end
 
 #################### Starter routines ####################
 #= RKstarter: Explicit second-order Runge-Kutta to start the time stepping.
-It calculates mterm and nterm and saves them in thlen0. =#
+It also calculates mterm and nterm and saves them in thlen0. =#
 function RKstarter!(thlen0::ThetaLenType, params::ParamType)
 	# Extract the needed variables.
 	dt, epsilon, beta = params.dt, params.epsilon, params.beta

### 2016-08-28 docs/Notes.tex
Implimented the motion of the reference point, which I took to be the surface-mean coordinates. It appears to work. Now it will be possible to do multiple bodies.

@@
 \subsubsection{The surface-average coordinates}
-I believe this will be even simpler. Consider the average of the surface coordinates
+I believe this will be even simpler. Consider the surface-mean coordinates
 \begin{equation}
-(x_a, y_a) = \int (x(\alpha), y(\alpha)) \, d\alpha
+(x_{sm}, y_{sm}) = \int_0^1 (x(\alpha), y(\alpha)) \, d\alpha
 \end{equation}
-I believe that this point moves according to
-\begin{equation}
-\td{}{t} (x_a, y_a) = \int V_n \, (n_x, n_y) \, d\alpha
-\end{equation}
+These coordinates move according to
+\begin{align}
+& \td{}{t} x_{sm} = \int_0^1 V_n \, n_x + V_s \, s_x \, d\alpha \\
+& \td{}{t} y_{sm} = \int_0^1 V_n \, n_y + V_s \, s_y \, d\alpha
+\end{align}
+Given $\nhat = (-\sin \theta, \cos \theta)$ and $\shat = (\cos \theta, \sin \theta)$, these simplify to
+\begin{align}
+& \td{}{t} x_{sm} = \int_0^1 -V_n \sin \theta + V_s \cos \theta \, d\alpha \\
+& \td{}{t} y_{sm} = \int_0^1 V_n \cos \theta + V_s \sin \theta \, d\alpha
+\end{align}
+Note: Initially, I was unsure whether $\int_0^1 V_s \hat{s} d\alpha$ makes a non-zero contribution or not, but based on some tests, it seems that it does make a difference.
+The order of magnitude is the same as the first term involving $V_n$.
 

### 2016-08-28 julia/basic.jl

@@ -7,9 +7,10 @@ type ParamType
 end
 # ThetaLenType includes all of the data that for a curve.
 type ThetaLenType
-	theta::Vector{Float64}; len::Float64; xa::Float64; ya::Float64; 
-	atau::Vector{Float64}; mterm::Float64; nterm::Vector{Float64};
+	theta::Vector{Float64}; len::Float64; xsm::Float64; ysm::Float64;
 	xx::Vector{Float64}; yy::Vector{Float64};
+	atau::Vector{Float64}; mterm::Float64; nterm::Vector{Float64}; 
+	xsmdot::Float64; ysmdot::Float64;
 end
 ##################################################
 
@@ -22,19 +23,21 @@ include("thetalen.jl")
 #################### Object functions ####################
 # Create a new ThetaLenType that has all zeros.
 function new_thlen()
-	return ThetaLenType([], 0., 0., 0., [], 0., [], [], [])
+	return ThetaLenType([], 0., 0., 0., [], [], [], 0., [], 0., 0.)
 end
 # Copy the relevant contents from thlen1 to thlen2.
 function copy_thlen!(thlen1::ThetaLenType, thlen2::ThetaLenType)
 	thlen2.theta = thlen1.theta
 	thlen2.len = thlen1.len
-	thlen2.xa = thlen1.xa
-	thlen2.ya = thlen1.ya
+	thlen2.xsm = thlen1.xsm
+	thlen2.ysm = thlen1.ysm
+	thlen2.xx = thlen1.xx
+	thlen2.yy = thlen1.yy
 	thlen2.atau = thlen1.atau
 	thlen2.mterm = thlen1.mterm
 	thlen2.nterm = thlen1.nterm
-	thlen2.xx = thlen1.xx
-	thlen2.yy = thlen1.yy
+	thlen2.xsmdot = thlen1.xsmdot
+	thlen2.ysmdot = thlen1.ysmdot
 	return
 end
 ##################################################
@@ -87,7 +90,7 @@ function getalpha(npts::Integer)
 	return alpha
 end
 # circgeo: Creates a circle.
-function circgeo(npts::Integer, rad::Float64, xa::Float64=0.0, ya::Float64=0.0)
+function circgeo(npts::Integer, rad::Float64, xsm::Float64=0.0, ysm::Float64=0.0)
 	# Create a new ThetaLenType variable.
 	thlen = new_thlen()
[…]

### 2016-08-28 julia/thetalen.jl

@@ -34,10 +34,9 @@ function advance_thetalen!(thlen1::ThetaLenType, thlen0::ThetaLenType, params::P
 	thlen2.len = len2
 	# Update theta with a multistep, integrating-factor method.
 	advance_theta!(thlen2,thlen1,thlen0,params)
-
-	# TEMPORARY: keep xa and ya fixed.
-	thlen2.xa = thlen1.xa; thlen2.ya = thlen1.ya;
-	
+	# Update surface-mean coordinates with an explicit, multistep method.
+	thlen2.xsm = thlen1.xsm + 0.5*dt*(3*thlen1.xsmdot - thlen0.xsmdot)
+	thlen2.ysm = thlen1.ysm + 0.5*dt*(3*thlen1.ysmdot - thlen0.ysmdot)
 	# Now thlen1 becomes the new thlen0, and thlen2 becomes the new thlen1
 	copy_thlen!(thlen1,thlen0)
 	copy_thlen!(thlen2,thlen1)
@@ -81,14 +80,18 @@ function getmn(theta::Vector{Float64}, len::Float64, atau::Vector{Float64}, para
 	datau = specdiff(atau)
 	# The nonlinear term in the theta-evolution equation.
 	nterm = (datau + dtheta.*vtang)/len
-	# Return mterm and nterm.
-	return mterm, nterm
+	# Calculate the motion of the surface-mean points.
+	xsmdot = mean(-vnorm.*sin(theta) + vtang.*cos(theta))
+	ysmdot = mean( vnorm.*cos(theta) + vtang.*sin(theta))
+	# Return everything.
+	return mterm, nterm, xsmdot, ysmdot
 end
 #= getmn!: Dispatch for ThetaLenType input; saves mterm and nterm in thlen.
 Also returms mterm to be used locally.
 Note: thlen must already be loaded with the correct atau. =#
 function getmn!(thlen::ThetaLenType, params::ParamType)
-	thlen.mterm, thlen.nterm = getmn(thlen.theta, thlen.len, thlen.atau, params)
+	thlen.mterm, thlen.nterm, thlen.xsmdot, thlen.ysmdot = 
+		getmn(thlen.theta, thlen.len, thlen.atau, params)
 	return thlen.mterm
 end
 # tangvel: Compute the tangential velocity and mterm = dL/dt along the way.
@@ -123,18 +126,22 @@ function RKstarter!(thlen0::ThetaLenType, params::ParamType)
 	# Take the first half-step of RK2.
[…]

### 2016-08-28 julia/zerode.jl

@@ -4,14 +4,16 @@ function main()
 	##### PARAMETERS #####
 	# Geometry parameters.
 	npts = 256
-	xa = 0.2; ya = 0.1;
-	rad = 0.2								# For circle geometry.
+	xsm = 0.5; ysm = 0.4;
+	rad = 0.3								# For circle geometry.
 	nsides = 4; sigma = 0.1; sdlen = 0.2	# For polygon geometry.
 	# Evolution parameters.
 	tfin = 0.1
-	dt = 1e-3
+	dt = 2e-4
 	epsilon = 0.2
 	beta = 0
+	# Misc parameters.
+	axlim = 1.0
 	######################
 
 	# Make slight adjustment to ensure that tfin is obtained.
@@ -19,15 +21,15 @@ function main()
 	# Put the parameters in a single variable.
 	params = ParamType(dt,epsilon,beta)
 	# Create the initial geometry.
-	thlen00 = circgeo(npts,rad,xa,ya)
-	#thlen00 = polygongeo(npts, nsides,sigma,sdlen,xa,ya)
+	thlen00 = circgeo(npts,rad,xsm,ysm)
+	#thlen00 = polygongeo(npts, nsides,sigma,sdlen,xsm,ysm)
 	# Copy to thlen0, which will be modified in the multi-step method.
 	thlen0 = new_thlen()
 	copy_thlen!(thlen00,thlen0)
 	# Use RK2 as a starter.
 	thlen1 = RKstarter!(thlen0,params)
 	# Plot the result.
-	tm = dt; cnt = 1; plotcurve!(thlen1,thlen00,cnt)
+	tm = dt; cnt = 1; plotcurve!(thlen1,thlen00,cnt,axlim=axlim)
 	# Enter while loop.
 	while(tm < tfin)
 		# Compute the new stress and save it.
@@ -35,7 +37,7 @@ function main()
 		# Advance thlen forward in time using the multi-step method.
 		advance_thetalen!(thlen1,thlen0,params)
 		# Advance time & counter and plot the result.
-		tm += dt; cnt += 1; plotcurve!(thlen1,thlen00,cnt)
+		tm += dt; cnt += 1; plotcurve!(thlen1,thlen00,cnt,axlim=axlim)
 	end
 end
 

### 2016-10-13 julia/misc.jl
Writing main routine erosion()

@@ -52,11 +52,25 @@ end
 
 
 #################### Other routines ####################
+#= get_thlen: Given the x and y coordinates, calculate theta and len. =#
+function get_thlen(xx::Vector{Float64}, yy::Vector{Float64})
+	# The partial derivatives dx/dalpha and dy/dalpha.
+	dxda = specdiff(xx)
+	dyda = specdiff(yy)
+	# Calculate theta and len.
+	theta = atan2(dyda,dxda)
+	lvec = sqrt(dxda.^2+dyda.^2)
+	len = mean(lvec)
+	# Check that the input is nearly equally spaced in arclength.
+	relerr = maxabs(lvec-len)/len
+	if relerr>1.e-2; error("The coordinates are not equally spaced"); return; end 
+	return theta, len
+end
 #= getxy: Given theta and len, reconstruct the x and y coordinates of a body.
 xsm and ysm are the boundary-averaged values.
 While we're at it, we can also calculate the normal direcations. =#
 function getxy(theta::Vector{Float64}, len::Float64, xsm::Float64, ysm::Float64)
-	# The increments of dx and dy
+	# The partial derivatives dx/dalpha and dy/dalpha.
 	dx = len * (cos(theta) - mean(cos(theta)))
 	dy = len * (sin(theta) - mean(sin(theta)))
 	# Integrate to get the x,y coordinates; result will have mean zero.

### 2016-10-16 docs/Notes.tex
Writing main routine erosion()
Got main erosion() routine working. Now working on scaline eps and sigma

@@
 
-We introduce the tangent angle $\theta$, defined as
+We introduce the tangent angle $\theta$, defined by
+\begin{equation}
+(x_s, y_s) = (\cos \theta, \sin \theta)
+\end{equation}
+so that we have
 \begin{equation}
@@
 \begin{equation}
+\label{intfact}
 \thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
@@
 
+\subsection{How to scale smoothing parameters?}
+We have two smoothing parameters: $\eps$ and $\sigma$.
+How should they scale with the simulation resolution parameters?
+The most important resolution parameter is $N$, the total number of points on each body, but there is also $\Delta t$ and maybe some others.
+Figuring out $\sigma$ is the easier part: $\sigma$ is a lengthscale and should go like $1/N$.
+On the other hand, $\eps$ is a diffusivity in dimensions.
+I did a calculation and found that $\eps$ should scale like $2/(\pi^2 N^2)$.
+
+The calculation is based on looking at Eq.~(\ref{intfact}), where $\sigma_1 \sim 2 \pi \sqrt{\eps \Delta t}$.
+For the largest wavenumbers, $k_{max} \sim N/2$, we want the smoothing to beat the nonlinear term (so that overall, these modes decay).
+So we need $e^{-\pi^2 \eps \Delta t N^2 / 2} < 1 - C\Delta t$, which gives $\eps > 2C/(\pi^2 N^2)$, independent of $\Delta t$.
+If $C=1$, this gives roughly $\eps > 0.2/ N^2$.
 \end{document}

### 2016-10-16 julia/basic.jl

@@ -58,7 +58,6 @@ function stokes(npts::Integer, nbods::Integer, xx::Vector{Float64}, yy::Vector{F
 	utar = zeros(Float64, ntargs)
 	vtar = zeros(Float64, ntargs)
 	ptar = zeros(Float64, ntargs)
-	# NEW
 	ccall((:stokessolver_, "libstokes.so"),
 		Void, (Ptr{Int}, Ptr{Int}, Ptr{Int}, 
 		Ptr{Float64}, Ptr{Float64}, Ptr{Float64}, Ptr{Float64}, 
@@ -74,7 +73,7 @@ function stokes!(thlenv::Vector{ThetaLenType}, sigma::Float64,
 	nbods = endof(thlenv)
 	npts = endof(thlenv[1].theta)
 	ntot = nbods*npts
-	xv = zeros(Float64,ntot); yv = zeros(Float64,ntot)
+	xv,yv = [zeros(Float64,ntot) for ii=1:2]
 	# Put all of the xy values in a single vector.
 	for nn = 1:nbods
 		# Compute the xy coordinates if they are not already loaded in thlen.

### 2016-10-16 julia/main.jl

@@ -1,38 +1,21 @@
 # main.jl
 
-# erosion: The main routine to erode a group of bodies.
-function erosion(npts::Integer, nbods::Integer, 
-	dt::Float64, nsteps::Integer, 
-	xv::Vector{Float64}, yv::Vector{Float64}; 
+# erosion: The main routine to erode a group of bodies for input of Vector{ThetaLenType}.
+function erosion(npts::Integer, nbods::Integer, nsteps::Integer,
+	params::ParamType, thlenvec0::Vector{ThetaLenType}; 
 	axlims::Vector{Float64} = [1.,1.])
-	# Calculate the two smoothing parameters from dt.
-	epsilon = 5*dt^(2/3)
-	sigma = epsilon
- 	# Store the parameters in a single variable.
-	params = ParamType(dt,epsilon,sigma,0)
-	# Set up the target points to measure u, v, and pressure.
+
+	# TEMPORARY: Set up the target points to measure u, v, and pressure.
 	ntargs = 11
 	yend = 0.8
 	ytar = collect(linspace(-yend, yend, ntargs))
 	xtar = -2.8 * ones(Float64, ntargs)
-	# Given the x and y coordinates, calculate the theta-len values.
-	thlenvec0 = [new_thlen() for ii=1:nbods]
-	for nn = 1:nbods
-		n1 = npts*(nn-1)+1
-		n2 = npts*nn
-		xx,yy = xv[n1:n2],yv[n1:n2]
-		thlenvec0[nn].theta, thlenvec0[nn].len = get_thlen(xx,yy)
-		thlenvec0[nn].xsm, thlenvec0[nn].ysm = mean(xx),mean(yy)
-	end
 	# Initialize variables for u, v, and pressure at target points.
 	utar,vtar,ptar = [zeros(Float64,ntargs) for ii=1:3]
 	pavg = zeros(Float64,nsteps)
+
 	# Plot the initial geometries, t=0.
 	plotcurves!(thlenvec0,0; axlims=axlims)
-
-
-	#HERE
-
 	# Use RK2 as a starter.
 	thlenvec1 = RKstarter!(thlenvec0, params)
 	# Plot the result for t=dt.
@@ -40,7 +23,7 @@ function erosion(npts::Integer, nbods::Integer,
 	# Enter the time loop.
 	for cnt = 2:nsteps
 		# Compute the new stress and save it.
[…]

### 2016-10-16 julia/misc.jl

@@ -1,27 +1,6 @@
 # misc.jl
 
 #################### Converting between x,y and theta,len ####################
-#= get_thlen: Given the x and y coordinates, calculate theta and len. =#
-function get_thlen(xx::Vector{Float64}, yy::Vector{Float64})
-	# The partial derivatives dx/dalpha and dy/dalpha.
-	dxda = specdiff(xx)
-	dyda = specdiff(yy)
-	# Calculate theta and len.
-	theta = atan2(dyda,dxda)
-
-
-	# HERE
-	theta[theta .< theta[1]] += 2*pi
-
-
-
-	lvec = sqrt(dxda.^2+dyda.^2)
-	len = mean(lvec)
-	# Check that the input is nearly equally spaced in arclength.
-	relerr = maxabs(lvec-len)/len
-	if relerr>1.e-2; error("The coordinates are not equally spaced"); return; end 
-	return theta, len
-end
 #= getxy: Given theta and len, reconstruct the x and y coordinates of a body.
 xsm and ysm are the boundary-averaged values.
 While we're at it, we can also calculate the normal direcations. =#
@@ -51,6 +30,7 @@ function getnormals(theta::Vector{Float64})
 	ny = cos(theta)
 	return nx, ny 
 end
+
 #################### Plotting routines ####################
 # plotcurve: Plot multiple curves from the theta-len values.
 function plotcurves!(thlenvec::Vector{ThetaLenType}, cnt::Integer,
@@ -84,6 +64,7 @@ function plotpress(ytar::Vector{Float64}, ptar::Vector{Float64},
 	figname = string("../figs/press",string(cnt),".pdf")	
 	savefig(p1, figname, width=400, height=400)
 end
+
 #################### Geometry routines ####################
 # getalpha: Calculate the parameterization variable, alpha = s/L.
 function getalpha(npts::Integer)
@@ -133,3 +114,67 @@ function polygongeo(npts::Integer, nsides::Integer,
 	return thlen
 end
 ##################################################
+
+
+
+
+
+
+# makegeodata
+function makegeodata(filename::AbstractString, npts::Integer, nbods::Integer)
+	# Creat the data vector.
+	nparams = 2
[…]

### 2016-10-16 julia/main.jl
NM

@@ -1,9 +1,19 @@
 # main.jl
 
 # erosion: The main routine to erode a group of bodies for input of Vector{ThetaLenType}.
-function erosion(npts::Integer, nbods::Integer, nsteps::Integer,
-	params::ParamType, thlenvec0::Vector{ThetaLenType}; 
+function erosion(tfin::Float64, dt::Float64, thlenvec0::Vector{ThetaLenType}; 
 	axlims::Vector{Float64} = [1.,1.])
+
+	# Extract the basic parameters
+	npts = endof(thlenvec0[1].theta)
+	nbods = endof(thlenvec0)
+	nsteps = round(Int,tfin/dt)
+	# Calculate the smoothing parameters based on the spatial resolution.
+	epsilon = 10./npts
+	sigma = 15./npts
+	# Save the parameters in one variable.
+	params = ParamType(dt,epsilon,sigma,0)
+
 
 	# TEMPORARY: Set up the target points to measure u, v, and pressure.
 	ntargs = 11

### 2016-10-16 julia/misc.jl

@@ -113,15 +113,8 @@ function polygongeo(npts::Integer, nsides::Integer,
 	thlen.xsm = xsm; thlen.ysm = ysm
 	return thlen
 end
-##################################################
-
-
-
-
-
-
-# makegeodata
-function makegeodata(filename::AbstractString, npts::Integer, nbods::Integer)
+# make4circs: Makes up to four circles and stores the data in a file.
+function make4circs(filename::AbstractString, npts::Integer, nbods::Integer)
 	# Creat the data vector.
 	nparams = 2
 	vsize = npts + 3
@@ -151,7 +144,8 @@ function makegeodata(filename::AbstractString, npts::Integer, nbods::Integer)
 	return
 end
 
-# readgeodata:
+
+# readgeodata: Reads the geometry from a data file.
 function readgeodata(filename::AbstractString)
 	# Open the input data file.
 	infile = open(string(filename), "r")
@@ -176,5 +170,5 @@ function readgeodata(filename::AbstractString)
 		thlenvec[nn].xsm = invec[n2-1]
 		thlenvec[nn].ysm = invec[n2]
 	end
-	return thlenvec, npts, nbods
+	return thlenvec,npts
 end

### 2016-10-16 julia/zdrive.jl
NM

@@ -1,0 +1,14 @@
+# Driver
+include("basic.jl")
+
+function driver(tfin::Float64=1.)
+	# Extract the geometry from a data file.
+	thlenvec,npts = readgeodata("thlen.dat")
+	# Optional: set dt based on npts.
+	dt = 0.2/npts
+	# Call the main erosion routine.
+	erosion(tfin,dt,thlenvec; axlims=[1.,1.])
+end
+
+make4circs("thlen.dat",128,4)
+driver()

### 2016-10-16 julia/znbods.jl

@@ -1,65 +1,0 @@
-# Erode multiple bodies.
-include("basic.jl")
-function main()
-	##### PARAMETERS #####
-	# Geometry parameters.
-	npts = 256
-	xsm1, ysm1 = +0.0, +0.4
-	xsm2, ysm2 = -0.0, -0.4
-	xsm3, ysm3 = +0.4, +0.0
-	xsm4, ysm4 = -0.4, -0.0	
-	# For circle geometry
-	rad1, rad2, rad3, rad4 = 0.2, 0.2, 0.2, 0.2
-	# Evolution parameters.
-	dt = 2e-3
-	epsilon = 5*dt^(2/3)
-	sigma = epsilon
-	nsteps = 50
-	# Misc parameters.
-	beta = 0
-	axlims = [1.,1.]
-	# Target points
-	ntargs = 11
-	yend = 0.8
-	ytar = collect(linspace(-yend, yend, ntargs))
-	xtar = -2.8 * ones(Float64, ntargs)
-	######################
-
-	# Put the parameters in a single variable.
-	params = ParamType(dt,epsilon,sigma,beta)
-	# Initialize variables.
-	utar,vtar,ptar = [zeros(Float64,ntargs) for ii=1:3]
-	pavg = zeros(Float64,nsteps)
-	# Create the initial geometries.
-	thlen01 = circgeo(npts,rad1,xsm1,ysm1)
-	thlen02 = circgeo(npts,rad2,xsm2,ysm2)
-	thlen03 = circgeo(npts,rad3,xsm3,ysm3)
-	thlen04 = circgeo(npts,rad4,xsm4,ysm4)
-	# Create the vector of ThetaLenType values.
-	thlenvec0 = [thlen01, thlen02, thlen03, thlen04]
-	#thlenvec0 = [thlen01]
-	
-	# Plot the initial geometries, t=0.
-	plotcurves!(thlenvec0,0; axlims=axlims)	
-	# Use RK2 as a starter.
-	thlenvec1 = RKstarter!(thlenvec0, params)
-	# Plot the result for t=dt.
-	plotcurves!(thlenvec1,1; axlims=axlims)
-
-	# Enter the time loop.
-	for cnt = 2:nsteps
-		# Compute the new stress and save it.
-		utar,vtar,ptar = stokes!(thlenvec1,sigma,ntargs,xtar,ytar)
-		# Advance thlen forward in time using the multi-step method.
[…]

### 2016-12-28 code/stokesDriver.f
starting methods paper

@@ -2,7 +2,7 @@
       implicit real*8 (a-h,o-z)
 
 c      parameter (ninner = 512)
-      parameter (ninner = 2**13)
+      parameter (ninner = 64)
       parameter (nbodies = 1)
       parameter (maxtargets = 20000)
 
@@ -135,7 +135,7 @@ c      enddo
       smoothOrder = 8.d0
       dr = 1.d-2
 c      radius(1) = 0.d0
-      radius(1) = 5.d-1 - dr
+      radius(1) = 2.5d-1 - dr
       do i=1,1
         radius(1) = radius(1) + dr
 
@@ -144,8 +144,8 @@ c      radius(1) = 0.d0
             theta = dble(k-1)*dtheta
 c            var_rad = radius(j)*(1.d0 + 2.d-1*dcos(5*theta))
             var_rad = radius(j)
-            var_rad = var_rad*(dcos(theta)**smoothOrder + 
-     $          dsin(theta)**smoothOrder)**(-1.d0/smoothOrder)
+c            var_rad = var_rad*(dcos(theta)**smoothOrder + 
+c     $          dsin(theta)**smoothOrder)**(-1.d0/smoothOrder)
             x((j-1)*ninner+k) = centerx(j) + var_rad*
      $          (dcos(phi(j))*dcos(theta) + dsin(phi(j))*dsin(theta))
             y((j-1)*ninner+k) = centery(j) + var_rad*
@@ -155,8 +155,7 @@ c            y((j-1)*ninner+k) = var_rad*dsin(theta) + centery(j)
           enddo
         enddo
 
-
-        ifmm = 1
+        ifmm = 0
         call stokesSolver(ninner,nbodies,ntargets,ifmm,x,y,
      $        xtar,ytar,utar,vtar,press_tar,shear_stress)
 c       pass in number of points and x and y coordinates and return the

### 2016-12-28 code/stokesSolver.f

@@ -11,8 +11,8 @@ c     x and y coordinates of obstacle
 c     x and y coordinates of target locations where velocity and
 c     pressure need to be evaluted
 
-      parameter (nmax = 2**15)
-      parameter (maxbodies = 20)
+      parameter (nmax = 2**12)
+      parameter (maxbodies = 50)
 c     max points on the boundary of the obstacle      
       parameter (ntarmax = 20000)
       parameter (maxl = 3000, liwork = 30)
@@ -303,7 +303,7 @@ c     extra terms need for rotlet and stokeslet conditions
 
 c***********************************************************************
       subroutine solveBIE(ninner,nbodies,nouter,den,rhs,
-     $    rwork,lrwork,iwork,liwork,maxl,ifmm)
+     $    gmwork,lrwork,igwork,liwork,maxl,ifmm)
 c     Solve the boundary integral equation with GMRES
       implicit real*8 (a-h,o-z)
 
@@ -313,23 +313,30 @@ c     Solve the boundary integral equation with GMRES
       dimension rhs(2*nouter+2*ninner*nbodies+3*nbodies)
 c     leave room for stokeslets and rotlets at the end of den
 
-      dimension rwork(lrwork),iwork(liwork)
+      dimension gmwork(lrwork),igwork(liwork)
 c     gmres workspaces
+
+      dimension iwork(3)
+c     workspace integer array that'll be passed to preconditioner msolve
 
       itol = 0
       tol = 1.d-8
       isym = 0
-      iwork(1) = maxl
+      igwork(1) = maxl
       do i=2,liwork
-        iwork(i) = 0
+        igwork(i) = 0
       enddo
 c     paramters for DGMRES
 
-      iwork(4) = 0
+      igwork(4) = -1
 c     preconditioner flag
 
-      iwork(5) = -1
+      igwork(5) = -1
 c     restart flag
+
+      iwork(1) = ninner
+      iwork(2) = nbodies
+      iwork(3) = nouter
 
       do k = 1,2*nouter+2*ninner*nbodies+3*nbodies
         den(k) = rhs(k)
@@ -341,14 +348,14 @@ c     initial guess
         call DGMRES(2*nouter+2*ninner*nbodies+3*nbodies,rhs,den,
      $      nelt,ia,ja,a,isym,
      $      matvec_DLP_fmm,msolve_DLP,itol,tol,itmax,iter,err,
[…]

### 2016-12-28 tests/circle_packing.m

@@ -48,7 +48,7 @@ end
 
 
 
-N = 4096;
+N = 512;
 theta = (0:N-1)'*2*pi/N;
 clf; hold on
 for k = 1:numel(xc)

### 2017-02-03 docs/Notes.tex
NM
Working on notes
Wrote up some notes on stress related to vorticity and how to compute drag

@@
 \begin{equation}
+\label{stressdef}
 \tau = \bvec{f} \cdot \shat 
@@
 where $C$ is a constant.
+
+\subsection{The calculation to show stress is equal to vorticity}
+First, calculate use Eq.~(\ref{stressdef}) directly to get
+\begin{equation}
+\tau/\mu = (u_y+v_x) (n_2 s_1 + n_1 s_2 ) + 2 u_x n_1 s_1 + 2 v_y n_2 s_2
+\end{equation}
+Next, use $(n_1,n_2) = (-s_2,s_1)$ to get
+\begin{equation}
+\tau/\mu = (u_y+v_x) (s_1^2 - s_2^2) + 2s_1 s_2 (v_y - u_x)
+\end{equation}
+Then do a complete the square type step
+\begin{equation}
+\tau/\mu = (u_y - v_x) (s_1^2 + s_2^2) - 2 u_y s_2^2 + 2v_x s_1^2 + 2s_1 s_2 (v_y - u_x)
+\end{equation}
+Then regroup the last several terms as
+\begin{equation}
+-2 s_2 ( u_x s_1 + u_y s_2 )
+\end{equation}
+and
+\begin{equation}
+2 s_1 ( v_x s_1 + v_y s_2)
+\end{equation}
+Both of these terms are zero because $\pdi{u}{s} = 0$ and $\pdi{v}{s} = 0$, which shows that
+\begin{equation}
+\tau/\mu = u_y - v_x
+\end{equation}
+
+\vsp{1}
+Note: By a similar calculation, I think it is true that
+\begin{equation}
+\bvec{E} \cdot \nhat \cdot \nhat = 0
+\end{equation}
+so that $\bvec{f} \cdot \nhat = -p \nhat$. I confirmed this in the simple case of $x=s, y=n$.
+
+\subsection{Drag}
+The drag on a body is given by integrating the traction on the surface. If my above claim is true, this reduces to
+\begin{equation}
+\bvec{F}_D = \int_{\bdry} \bvec{f} \, dS = \int_{\bdry} -p \nhat + \tau \shat \, dS
+\end{equation}
 
@@
 
+\subsection{How to scale smoothing parameters?}
+We have two smoothing parameters: $\eps$ and $\sigma$.
+How should they scale with the simulation resolution parameters?
+The most important resolution parameter is $N$, the total number of points on each body, but there is also $\Delta t$ and maybe some others.
+Figuring out $\sigma$ is the easier part: $\sigma$ is a lengthscale and should go like $1/N$.
+On the other hand, $\eps$ is a diffusivity in dimensions.
+I did a calculation and found that $\eps$ should scale like $2/(\pi^2 N^2)$.
+
+The calculation is based on looking at Eq.~(\ref{intfact}), where $\sigma_1 \sim 2 \pi \sqrt{\eps \Delta t}$.
+For the largest wavenumbers, $k_{max} \sim N/2$, we want the smoothing to beat the nonlinear term (so that overall, these modes decay).
+So we need $e^{-\pi^2 \eps \Delta t N^2 / 2} < 1 - C\Delta t$, which gives $\eps > 2C/(\pi^2 N^2)$, independent of $\Delta t$.
+If $C=1$, this gives roughly $\eps > 0.2/ N^2$.
+However, this analysis did not take into account how the spectrum of the nonlinear term decays (or maybe it even grows???)
+
 \subsection{Motion of a reference point}
@@
 
-\subsection{How to scale smoothing parameters?}
-We have two smoothing parameters: $\eps$ and $\sigma$.
-How should they scale with the simulation resolution parameters?
-The most important resolution parameter is $N$, the total number of points on each body, but there is also $\Delta t$ and maybe some others.
-Figuring out $\sigma$ is the easier part: $\sigma$ is a lengthscale and should go like $1/N$.
-On the other hand, $\eps$ is a diffusivity in dimensions.
-I did a calculation and found that $\eps$ should scale like $2/(\pi^2 N^2)$.
-
-The calculation is based on looking at Eq.~(\ref{intfact}), where $\sigma_1 \sim 2 \pi \sqrt{\eps \Delta t}$.
-For the largest wavenumbers, $k_{max} \sim N/2$, we want the smoothing to beat the nonlinear term (so that overall, these modes decay).
-So we need $e^{-\pi^2 \eps \Delta t N^2 / 2} < 1 - C\Delta t$, which gives $\eps > 2C/(\pi^2 N^2)$, independent of $\Delta t$.
-If $C=1$, this gives roughly $\eps > 0.2/ N^2$.
 \end{document}

### 2017-03-14 docs/Notes.tex
Working on a benchmark for the interface evolution under some sort of curvature driven flow

@@
 \begin{equation}
+\label{thetaEvolve}
 \pd{\theta}{t} = \eps L^{\beta-2} \ppd{\theta}{\alpha} + L^{-1} \left( C \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
@@
 
-\subsection{Motion of a reference point}
-
-\subsubsection{The center of mass}
-Consider the body's center of mass
-\begin{equation}
-(x_{cm}, y_{cm}) = \frac{1}{A} \iint (x, y) \, dA
-\end{equation}
-I did a calculation to determine the motion of the center of mass, given the interface velocity. The result that I get is
-\begin{equation}
-\td{}{t} (x_{cm}, y_{cm})  = -\frac{1}{A} \int (x(s), y(s)) V_n(s) \, ds
-\end{equation}
-I believe the sign is correct for $\nhat$ the inward pointing normal, so that $V_n$ is positive if the body is shrinking.
-
-To calculate the center of mass, I can use the divergence theorem
-\begin{equation}
-\iint \grad \cdot \bvec{F} \, dA = \int \bvec{F} \cdot \nhat \, ds
-\end{equation}
-Take $\bvec{F} = \frac{1}{2} (x^2, y^2)$, so that $\grad \cdot \bvec{F} = (x,y)$. Then
-\begin{equation}
-(x_{cm}, y_{cm} ) = \frac{1}{2 A} \int x^2 n_x + y^2 n_y \, ds
-\end{equation}
-To calculate the total area, $A$, I can use the divergence theorem again, to get
-\begin{equation}
-A = \int x n_x ds = \int y n_y ds
-\end{equation}
-
-\subsubsection{The surface-average coordinates}
-I believe this will be even simpler. Consider the surface-mean coordinates
+\subsection{Tracking a reference point: the surface-averaged coordinates}
+To evolve the body, I need to track the motion of one reference point.
+The initial choice might be center of mass, but this turns out to be complicated.
+Instead, it is simpler to consider the surface-mean coordinates
 \begin{equation}
@@
 \end{align}
-Note: Initially, I was unsure whether $\int_0^1 V_s \hat{s} d\alpha$ makes a non-zero contribution or not, but based on some tests, it seems that it does make a difference.
+Note 1: Initially, I was unsure whether $\int_0^1 V_s \hat{s} d\alpha$ makes a non-zero contribution or not, but based on some tests, it seems that it does make a difference.
 The order of magnitude is the same as the first term involving $V_n$.
+\\
+Note 2: If I need to calculate the area, the divergence theorem gives
+\begin{equation}
+A = \int x n_x ds = \int y n_y ds
+\end{equation}
+
+%% CENTER OF MASS calculations... OBSELETE
+\begin{comment}
+\subsubsection{The center of mass}
+Consider the body's center of mass
+\begin{equation}
+(x_{cm}, y_{cm}) = \frac{1}{A} \iint (x, y) \, dA
+\end{equation}
+I did a calculation to determine the motion of the center of mass, given the interface velocity. The result that I get is
+\begin{equation}
+\td{}{t} (x_{cm}, y_{cm})  = -\frac{1}{A} \int (x(s), y(s)) V_n(s) \, ds
+\end{equation}
+I believe the sign is correct for $\nhat$ the inward pointing normal, so that $V_n$ is positive if the body is shrinking.
+To calculate the center of mass, I can use the divergence theorem
+\begin{equation}
+\iint \grad \cdot \bvec{F} \, dA = \int \bvec{F} \cdot \nhat \, ds
+\end{equation}
+Take $\bvec{F} = \frac{1}{2} (x^2, y^2)$, so that $\grad \cdot \bvec{F} = (x,y)$. Then
+\begin{equation}
+(x_{cm}, y_{cm} ) = \frac{1}{2 A} \int x^2 n_x + y^2 n_y \, ds
+\end{equation}
+To calculate the total area, $A$, I can use the divergence theorem again, to get
+\begin{equation}
+A = \int x n_x ds = \int y n_y ds
+\end{equation}
+\end{comment}
+% END CENTER OF MASS
+
+\subsection{Benchmark the interface evolution}
+It would be good to test the interface evolution, in particular verify that the curvature-driven-flow (CDF) is 2nd order accurate in time.
+Initially, I thought I would be able to get exact solutions for CDF, but it turns out that the PDE (\ref{thetaEvolve}) does not reduce to simply a diffusion equation, but instead still has nonlinear terms, thus making exact solutions impractical.
+I also tried to recast CDF in polar coordinates for star-shapes, but still the governing PDE is not simple enough to get exact solutions.
+Instead, I can do a completely numerical convergence test.
 

### 2017-03-14 julia/ztest_intevo.jl
Working on interface evolution test.

@@ -1,0 +1,42 @@
+# Test the curvature driven flow
+
+# Curvature-driven flow.
+function cdf(npts::Int, dt::Float64, epsilon::Float64,
+		tfin::Float64=0.1, len0::Float64=2*pi*0.2, lenevo::Int=0)
+	# Calculate parameters and initial shape.
+	nsteps = round(Int,tfin/dt)
+	params = ParamType(dt,epsilon,0.,0.,lenevo,0)
+	thlenvec0 = makeshape(npts,len0,a1)
+	# Start the simulation with RKstarter.
+	thlenvec1 = RKstarter!(thlenvec0,params,noatau)
+
+	# Continue the simulation with the multi-step method.
+	for nn = 2:nsteps
+		advance_thetalen!(thlenvec1,thlenvec0,params)
+	end
+	return thlenvec1
+end
+
+# Make the initial shape.
+function makeshape(npts::Int, len::Float64, a1::Float64, 
+		xsm::Float64=0., ysm::Float64=0.)
+	alpha = getalpha(npts)
+	# theta for a circle.
+	theta = 0.5*pi + 2*pi*alpha[:]
+	# Add a sin component.
+	theta += a1*sin(2*pi*alpha[:])
+	# Put the shape in a thlenvec.
+	thlen = new_thlen()
+	thlen.theta = theta
+	thlen.len = len
+	thlen.xsm = xsm
+	thlen.ysm = ysm
+	thlenvec = [thlen]
+	return thlenvec
+end
+
+# Function to pass into RKstarter without computing abs tau.
+function noatau(thlenv::Vector{ThetaLenType}, params::ParamType)
+	return
+end
+

### 2017-03-20 docs/Notes.tex
Working on interface evolution test.
Writing notes to scale curvature-driven flow differently. This is because for 2D Stokes flow, my tests show that the stress scales like 1/(L log L) instead of 1/L. This is probably because of 2D Stokes paradox type stuff.

@@
 \begin{equation}
+\label{Vn1}
 V_n = C \atau + \eps L^{\beta} \left(\kappa - \frac{2 \pi}{L} \right)
@@
 \begin{equation}
+\label{Vn2}
 V_n = C \atau + \eps L^{\beta-1} \left(\pd{\theta}{\alpha} - 2 \pi \right)
@@
 \end{align}
+
+\subsubsection{Different scaling of the stress}
+Some numerical tests reveal that the stress scales like $\tau \sim 1/(L \log L)$, instead of the naive $1/L$.
+This might because we are in a 2D bounded domain (Stokes paradox type stuff).
+So we need to modify the curvature driven flow to have the same scaling.
+To this end, modify Eq.~(\ref{Vn1}) to read
+\begin{equation}
+V_n = \atau + \eps f(L) \left(\kappa - \frac{2 \pi}{L} \right)
+\end{equation}
+where for 2D Stokes flow, we will have $f(L) = -1/\log L$. Carrying through this change, Eq.~(\ref{Vn2}) becomes
+\begin{equation}
+V_n = \atau + \eps L^{-1} f(L) \left(\pd{\theta}{\alpha} - 2 \pi \right)
+\end{equation}
+and Eq.~(\ref{thetaEvolve}) becomes
+\begin{equation}
+\pd{\theta}{t} = \eps L^{-2} f(L) \ppd{\theta}{\alpha} + L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
+\end{equation}
+Then to evolve $\theta$ spectrally, we use
+\begin{equation}
+\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{-2} f(L)  \thh_k = \hat{N}_k
+\end{equation}
 
@@
 I also tried to recast CDF in polar coordinates for star-shapes, but still the governing PDE is not simple enough to get exact solutions.
+Also, in the $\theta$-$L$ formulation I tried to determine the normal velocity to make the nonlinear terms vanish, but this does not appear possible either.
 Instead, I can do a completely numerical convergence test.

### 2017-03-22 julia/basic.jl
Removed all instances of the parameter beta. Instead I am using the function cdfscale to scale the curvature-driven flow how I like. For 2D Stokes flow, cdfscale should be -1/Log(L).

@@ -1,10 +1,9 @@
 # basic.jl: Basic routines such as datatypes and Stokes solvers.
 
 #################### Object data types ####################
-# ParamType includes the parameters dt, epsilon, and beta.
+# ParamType includes the parameters dt, epsilon, sigma, etc.
 type ParamType
-	dt::Float64; epsilon::Float64; sigma::Float64; 
-	beta::Real; ifmm::Int; fixarea::Int;
+	dt::Float64; epsilon::Float64; sigma::Float64; ifmm::Int; fixarea::Int;
 end
 # ThetaLenType includes all of the data that for a curve.
 type ThetaLenType

### 2017-03-22 julia/main.jl

@@ -77,7 +77,7 @@ function getparams()
 	sigma = sigfac/npts
 	dtoutexact = cntout*dt
 	# Save params and paramvec
-	params = ParamType(dt,epsilon,sigma,0,ifmm,fixarea)
+	params = ParamType(dt,epsilon,sigma,ifmm,fixarea)
 	paramvec = [paramvecin; dtoutexact; cntout; 0.]
 	return thlenvec0,params,paramvec,nsteps,cntout
 end

### 2017-03-22 julia/thetalen.jl

@@ -8,7 +8,6 @@ atau (vector): The absolute value of the shear stress, computed by fluid solver.
 Parameters
 dt: The time-step.
 epsilon: The constant for the smoothing, curvature-driven-flow component.
-beta: The power of L hitting the curvature-term in the V_n; should be zero for Stokes flow. 
 
 Convention for tangential and normal vectors
 I use the same convention as Shelley 1994. That is, I assume the curve 
@@ -30,7 +29,7 @@ This is a multi-step method and uses some values from n=0 too.
 Note: thlen1 must already be loaded with the correct atua, which is used in getmn!() =#
 function advance_thetalen!(thlen1::ThetaLenType, thlen0::ThetaLenType, params::ParamType)
 	# Extract the needed variables.
-	dt = params.dt; m0 = thlen0.mterm; len1 = thlen1.len
+	dt, m0, len1 = params.dt, thlen0.mterm, thlen1.len
 	# Calculate mterm and nterm at time n=1.
 	m1 = getmn!(thlen1,params)
 	# Update len with an explicit, multistep method.
@@ -52,17 +51,18 @@ end
 # advance_theta: Advance theta in time with the integrating-factor method.
 function advance_theta!(thlen2::ThetaLenType, thlen1::ThetaLenType, thlen0::ThetaLenType, params::ParamType)
 	# Extract the needed variables.
-	dt, epsilon, beta = params.dt, params.epsilon, params.beta
+	dt, epsilon = params.dt, params.epsilon
 	theta1, len1, n1 = thlen1.theta, thlen1.len, thlen1.nterm
 	len0, n0 = thlen0.len, thlen0.nterm
 	len2 = thlen2.len
 	alpha = getalpha(endof(theta1))
-	lpow = beta-2
+	# The function that enters the sigmas of the Guassian filter.
+	lenfun(len::Float64) = len^(-2)*cdfscale(len)
 	# The first value used in the Gaussian filter.
-	sig1 = sqrt( len1^lpow + len2^lpow )
+	sig1 = sqrt( lenfun(len1) + lenfun(len2) )
 	sig1 *= 2*pi*sqrt(epsilon*dt)
 	# The second value used in the Gaussian filter.
-	sig2 = sqrt( len0^lpow + 2*len1^lpow + len2^lpow )
[…]

### 2017-03-22 docs/Notes.tex
NM
Removed all instances of the parameter beta. Instead I am using the function cdfscale to scale the curvature-driven flow how I like. For 2D Stokes flow, cdfscale should be -1/Log(L).
writing notes on scaling the smoothing term

@@
 
-\subsubsection{Different scaling of the stress}
+\subsection{Different scaling of the stress}
 Some numerical tests reveal that the stress scales like $\tau \sim 1/(L \log L)$, instead of the naive $1/L$.
@@
 \end{equation}
+where the nonlinear terms are grouped together as
+\begin{equation}
+N = L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
+\end{equation}
+We evolve with the integrating-factor method. When recast in terms of Gaussian filters, this gives
+\begin{equation}
+\label{intfact}
+\thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
++ \frac{\Dt}{2} \left( 3 \GG(N^{(n)}, \sigma_1) - \GG(N^{(n-1)}), \sigma_2 \right)
+\end{equation}
+where
+\begin{align}
+& \sigma_1 = 2 \pi \sqrt{\eps \Dt} \sqrt{g(L^{n}) + g(L^{n+1}) } 	\\
+& \sigma_2 = 2 \pi \sqrt{\eps \Dt} \sqrt{g(L^{n-1}) + 2 g(L^{n}) + g(L^{n+1}) }
+\end{align}
+where $g(L) = L^{-2} f(L)$.
+%This will also modify the scaling law for area vs time!!!
+
+\vsp{2}
+{\bf  Alternative}: Perhaps I just want to calculate the mean of the shear stress directly and use it to scale the curvature driven flow. This idea gives
+\begin{equation}
+V_n = \atau + \eps \mean{\atau} \left(\kappa - \frac{2 \pi}{L} \right)
+\end{equation}
+which gives
+\begin{equation}
+V_n = \atau + \eps L^{-1} \mean{\atau} \left(\pd{\theta}{\alpha} - 2 \pi \right)
+\end{equation}
+Then we get
+\begin{equation}
+\pd{\theta}{t} = \eps L^{-2} \mean{\atau} \ppd{\theta}{\alpha} + L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
+\end{equation}
+Then to evolve $\theta$ spectrally, we use
+\begin{equation}
+\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{-2} \mean{\atau}  \thh_k = \hat{N}_k
+\end{equation}
+Then the Gaussian filter stuff becomes
+\begin{equation}
+\label{intfact}
+\thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
++ \frac{\Dt}{2} \left( 3 \GG(N^{(n)}, \sigma_1) - \GG(N^{(n-1)}), \sigma_2 \right)
+\end{equation}
+where
+\begin{align}
+& \sigma_1 = 2 \pi \sqrt{\eps \Dt} \sqrt{g^{n} + g^{n+1} } 	\\
+& \sigma_2 = 2 \pi \sqrt{\eps \Dt} \sqrt{g^{n-1} + 2 g^{n} + g^{n+1} }
+\end{align}
+where $g(t)= L^{-2} \mean{\atau}$ and $g^{(n)} = g(t^{(n)})$.
+BUT the problem with this is that I do not yet know $\mean{\atau}$ at time-step $n+1$, so I would have to change my time-stepping strategy which is a significant change to the code structure.
+Thus, I prefer the first method of using $L \log L$.
 

### 2017-06-05 docs/PhysicsPaper/StokesErosion.tex
Fixing the folder stucture and adding back files I accidentally deleted

% Journal of Computational Sciences
\documentclass[3p]{elsarticle}

% PACKAGES
\usepackage{graphicx, amsmath, amssymb, amsfonts, mathtools, mathrsfs, color}
\usepackage{comment, enumerate, tabularx, multirow}
\usepackage{natbib, hyperref, url}
\usepackage{algorithm, algpseudocode, pifont, longtable}
%\usepackage[justification=RaggedRight]{caption}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COMMANDS

% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
\newcommand{\HERE}[1]{ \vsp{#1} {\color{blue} HERE} }
\newcommand{\tofix}{\color{blue}}
\newcommand{\new}{}		% \color{green}
\newcommand{\newa}{}		% \color{red}
\newcommand{\newb}{}		% \color{blue}
% Basic math, derivatives
\newcommand{\td}[2]{\frac{d #1 }{d #2}}
\newcommand{\ttd}[2]{\frac{d^2 #1 }{{d #2}^2}}
\newcommand{\pd}[2]{ \frac{ \partial #1}{ \partial #2 } }
\newcommand{\ppd}[2]{ \frac{ \partial^2 #1}{ {\partial #2}^2 } }
% Basic math, vectors and other
\newcommand{\BigO}[1]{ \mathcal{O} \left(#1\right) }
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\grad}{\nabla} 
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\tavg}[1]{\langle #1 \rangle}
\newcommand{\norm}[1]{ \left\| #1 \right\| }
\newcommand{\ip}[1]{ \langle #1 \rangle }
% For real and imaginary, could use \Re or \Im, or \mathcal{R}, or \text{Re}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{Stokes Erosion}
\author{M. Nicholas J. Moore}
%\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, FL 32306, USA}
%\thanks{Email addresses for correspondence: moore@math.fsu.edu, nickmoore83@gmail.com}

\begin{abstract}
Abstract
\end{abstract}
\maketitle

Stuff \cite{MooreCPAM2017}

\bibliographystyle{plain}
\bibliography{refs}
\end{document}

### 2017-06-06 docs/methods/erosion_methods.tex
working on methods paper

\documentclass[preprint, 10pt]{elsarticle}

\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}}
\newcommand{\secref}[1]{\ref{#1}}

\input{preambles.tex}
\begin{document}

\title{Methods paper for erosion}

\author[Nick]{M.~Nicholas J.~Moore}
\author[Bryan]{Bryan D.~Quaife}
\address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\address[Bryan]{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}

\begin{abstract} 
We consider two dimensional eroding bodies in Stokes flow
\end{abstract}

\begin{keyword}
  Stokes flow \sep Erosion \sep Boundary integral method \sep
  Fluid-structure interaction \sep Fast multipole methods 
\end{keyword}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}

This is a methods paper
\begin{itemize}
  \item Boundary integral equation formulation
  \item How we compute the shear stress and pressure
  \item Multiple bodies
  \item Avoiding stokes paradox
  \item $\theta-L$ formulation
  \item Regularization
\end{itemize}

\cite{moo-ris-chi-zha-she2013}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation\label{s:formulation}} 
We consider multiple bodies being eroded by a two-dimensional Stokesian
fluid.  The Stokes paradox is circumvented by using a rounded-off
rectangle that encloses the eroding bodies.  Then, the flow is driven
by a boundary conditions, such as a Hagen-Poiseuille flow, on the
boundary of the outer geometry \todo[inline]{Need a figure here}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Erosion Model} 
\todo[inline]{Governing equations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary Integral Equation Formulation} 
The incompressible Stokes equations are
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Gamma.
\end{alignat*}
The viscosity $\mu$ sets the time scale, and we will assume that
$\mu=1$.  The double-layer potential 
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \rr \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:dlp}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
normal.  The double-layer potential can not capture velocity fields
corresponding to rigid body motions~\cite{pow-mir1987}.  A standard
method to complete the double-layer potential is to introduce a
Stokeslet and rotlet due to each interior body
\begin{align}
  S[\llambda_k,\cc_k] = \frac{1}{4\pi} \left(-\log \rho \II + 
    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_k
  \quad \text{and} \quad
  R[\xi_k,\cc_k] = \frac{\rr^\perp}{\rho^2}\xi_k,
  \label{eqn:stokeslet_rotlet}
\end{align}
where $\cc_k$ is a point in the interior of $\Omega_k$, $\rr = \xx -
\cc_k$, and $\rr^\perp = (r_2,-r_1)$.

Then, the solution of the Stokes equations with a Dirichlet boundary
condition $\ff$ can be written in terms of the completed double-layer
potential
\begin{align}
  \uu(\xx) = \DD[\eeta](\xx) + \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
              \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Omega,
  \label{eqn:completedDLP}
\end{align}
where the density function, Stokeslets, and rotlets satisfy the
second-kind integral equation
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
      \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Gamma, \\
  \llambda_k &= \frac{1}{2\pi}\int_{\Gamma_k} \eeta(\yy) \, ds_\yy, \\
  \xi_k &= \frac{1}{2\pi}\int_{\Gamma_k} \yy^\perp \cdot \eeta(\yy)
  \, ds_\yy.
  \label{eqn:completed_DLP}
\end{align}
Finally, because of the incompressibility constraint, the boundary
condition must satisfy 
\begin{align}
  \int_{\Gamma} \ff \cdot \nn \, ds_\yy = 0.
\end{align}
These results in a rank-one null space in
equation~\eqref{eqn:completed_DLP} which is removed by adding the rank
one modification $\NN_0[\eeta](\xx) = \int_{\Gamma_0} (\nn(\xx) \times
\nn(\yy))\nn(\yy) \, ds_\yy$, for $\xx \in \Gamma_0$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the Shear Stress, Pressure, and Drag} 
The governing equations~\eqref{eqn:} require the shear stress which is
defined on the boundary of each pore.  We are also interested in
computing the drag on each pore which requires the pressure.

The shear stress is given by
\begin{align}
  \tau = \left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss,
  \label{eqn:shearStress}
\end{align}
where $\ss$ is the unit tangent vector.  We note that for the Stokes
equations, because of the no-slip boundary condition on the pores, the
shear stress is identical to the surface vorticity $\tau = u_y - v_x$.
However, we use equation~\eqref{eqn:shearStress} to compute the shear
stress since the jump conditions resulting from the double-layer
potential are known~\cite{qua-bir2014a}.  In particular, we start by
first computing the deformation tensor $\ssigma = \frac{1}{2}(\nabla\uu
+ \nabla\uu^T)$ of the double-layer potential~\eqref{eqn:dlp} at $\xx
\in \Omega$
\begin{align*}
  \ssigma(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) \,ds_\yy,
\end{align*}
where the kernel $K$ is given by
\begin{align*}
  K(\xx,\yy) = \frac{1}{2\pi}\left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) +
    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
  \right).
\end{align*}
To compute the shear stress at boundary points $\xx_0 \in \bd\Omega$, we
require the jump in the shear stress as the target point approaches the
boundary.  The limiting value is given by
\begin{align}
  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}\sigma(\xx) =
  J[\eeta](\xx_0) + \ssigma(\xx_0) = 
  \frac{1}{2}\pderiv{\eeta}{\ss} \cdot \ss
  \left[ \begin{array}{cc}
    s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
  \end{array}\right] + \sigma(\xx_0), \quad \xx_0 \in \Gamma.
\end{align}
Finally, adding the deformation tensor due to the Stokeslets and rotlets
in equation~\eqref{eqn:stokeslet_rotlet}, the deformation tensor of the
complete double-layer potential formulation~\eqref{eqn:completedDLP} is
\begin{align}
  \ssigma(\xx_0) = \frac{\rr \cdot \llambda}{4\pi\rho^2} \left(
    \II - \frac{2}{\rho^2} \rr \otimes \rr \right) -
  \frac{\xi}{\rho^4} \left(\rr \otimes \rr^\perp + 
                           \rr^\perp \otimes \rr \right)
\end{align}
\todo[inline]{Put together the whole stress calculation correctly}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods\label{s:method}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature} 
There are several integrals that we need to compute including the
double-layer potential velocity field~\eqref{eqn:dlp}, the shear
stress~\eqref{}, and the pressure~\eqref{}.  By using carefully choosing
the quadrature rules, high-order solutions can be computed.  For all the
integrals, the trapezoid rule is used since it achieves spectral
accuracy for smooth periodic functions.  However, care must be taken
when the source point and target points coincide.

For the

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Stepping} 
We use a quasi-static formulation ....

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\theta-L$ Formulation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Artificial Diffusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Gaussian Filter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results\label{s:results}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendices}
\section{Error estimates for near-singular integration \label{A:AppendixA}} 
\end{appendices}

\bibliographystyle{plainnat} 
\bibliography{refs}
\biboptions{sort&compress}
\end{document}

### 2017-06-07 docs/methods/erosion_methods.tex
worked on methods paper

@@
 boundary of the outer geometry \todo[inline]{Need a figure here}
+\begin{subequations}
+\label{eqn:erosionModel}
+\begin{gather}
+eqn1 \label{eqn:eqn1} \\
+eqn2 \label{eqn:eqn2} \\
+eqn3 \label{eqn:eqn3}
+\end{gather}
+\end{subequations}
 
@@
     \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
-    \rr \, ds_\yy, \quad \xx \in \Omega,
+    \eeta \, ds_\yy, \quad \xx \in \Omega,
     \label{eqn:dlp}
@@
 where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
-normal.  The double-layer potential can not capture velocity fields
+normal, solves the incompressible Stokes equations for any sufficiently
+smooth density function $\eeta$.  However, the double-layer potential can not capture velocity fields
 corresponding to rigid body motions~\cite{pow-mir1987}.  A standard
@@
 where $\cc_k$ is a point in the interior of $\Omega_k$, $\rr = \xx -
-\cc_k$, and $\rr^\perp = (r_2,-r_1)$.
-
-Then, the solution of the Stokes equations with a Dirichlet boundary
-condition $\ff$ can be written in terms of the completed double-layer
-potential
+\cc_k$, and $\rr^\perp = (r_2,-r_1)$.  Then, the solution of the Stokes
+equations with a Dirichlet boundary condition $\ff$ can be written in
+terms of the completed double-layer potential
 \begin{align}
@@
 \end{align}
-These results in a rank-one null space in
-equation~\eqref{eqn:completed_DLP} which is removed by adding the rank
+This results in a rank-one null space of
+equation~\eqref{eqn:completed_DLP} which we remove by adding the rank
 one modification $\NN_0[\eeta](\xx) = \int_{\Gamma_0} (\nn(\xx) \times
@@
 \subsection{Computing the Shear Stress, Pressure, and Drag} 
-The governing equations~\eqref{eqn:} require the shear stress which is
-defined on the boundary of each pore.  We are also interested in
-computing the drag on each pore which requires the pressure.
-
-The shear stress is given by
+The governing equations~\eqref{eqn:erosionModel} require the shear
+stress which is defined on the boundary of each pore.  The shear stress
+is given by
 \begin{align}
@@
 stress since the jump conditions resulting from the double-layer
-potential are known~\cite{qua-bir2014a}.  In particular, we start by
-first computing the deformation tensor $\ssigma = \frac{1}{2}(\nabla\uu
-+ \nabla\uu^T)$ of the double-layer potential~\eqref{eqn:dlp} at $\xx
-\in \Omega$
+potential are known~\cite{qua-bir2014a}.  The velocity field of the
+completed double-layer potential involves three terms: the double-layer
+potential $\DD$, the Stokeslets $S$, and the rotlets $R$.  To compute
+the shear stress, we first compute the deformation tensor $\ssigma =
+\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of each of these terms
+individually.
+
+Considering the double-layer potential~\eqref{eqn:dlp} evaluated at $\xx
+\in \Omega$, the deformation tensor is
 \begin{align*}
-  \ssigma(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) \,ds_\yy,
+  \ssigma^\DD(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) \,ds_\yy,
 \end{align*}
@@
 \end{align*}
-To compute the shear stress at boundary points $\xx_0 \in \bd\Omega$, we
-require the jump in the shear stress as the target point approaches the
-boundary.  The limiting value is given by
+We are interested in the deformation tensor at boundary points $\xx_0
+\in \bd\Omega$, and this requires an expression for the jump in
+$\ssigma^\DD(\xx)$ as $\xx \rightarrow \xx_0 \in \Gamma$.  The limiting
+value is given by~\cite{qua-bir2014a}
 \begin{align}
-  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}\sigma(\xx) =
-  J[\eeta](\xx_0) + \ssigma(\xx_0) = 
+  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}\sigma_\DD(\xx) =
+  J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) = 
   \frac{1}{2}\pderiv{\eeta}{\ss} \cdot \ss
@@
     s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
-  \end{array}\right] + \sigma(\xx_0), \quad \xx_0 \in \Gamma.
+  \end{array}\right] + \ssigma^\DD(\xx_0), \quad \xx_0 \in \Gamma.
 \end{align}
-Finally, adding the deformation tensor due to the Stokeslets and rotlets
-in equation~\eqref{eqn:stokeslet_rotlet}, the deformation tensor of the
-complete double-layer potential formulation~\eqref{eqn:completedDLP} is
+
+The deformation tensor due to the Stokeslets and rotlets in
+equation~\eqref{eqn:stokeslet_rotlet} are
 \begin{align}
-  \ssigma(\xx_0) = \frac{\rr \cdot \llambda}{4\pi\rho^2} \left(
-    \II - \frac{2}{\rho^2} \rr \otimes \rr \right) -
-  \frac{\xi}{\rho^4} \left(\rr \otimes \rr^\perp + 
-                           \rr^\perp \otimes \rr \right)
+  \ssigma^S(\xx_0) &= \frac{\rr \cdot \llambda}{4\pi\rho^2} \left(
+    \II - \frac{2}{\rho^2} \rr \otimes \rr \right),  \\
+  \ssigma^R(\xx_0) &= -\frac{\xi}{\rho^4} \left(\rr \otimes \rr^\perp + 
+                           \rr^\perp \otimes \rr \right).
 \end{align}
-\todo[inline]{Put together the whole stress calculation correctly}
+Now that the deformation tensor of each component of the completed
+double-layer potential are computed, the shear stress at $\xx_0 \in
+\Gamma$ can be computed as
+\begin{align}
+  \tau = \left(J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) + 
+    \ssigma^S(\xx_0) + \ssigma^R(\xx_0)\right) \nn \cdot \ss.
+\end{align}
+
+To compute the pressure at $\xx_0 \in \Gamma$, we follow the same
+procedure used for the shear stress.  In particular, we compute the
+pressure due to each of the three terms that compose the completed
+double-layer potential.  They are given by
+\begin{align}
+  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
+  -\pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0),
+\end{align}
+where
+\begin{align}
+  p^\DD(\xx) = -\frac{1}{\pi}\int_{\Gamma} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
+    \nn \cdot \eeta \,ds_\yy.
+\end{align}
+The pressure due to the Stokeslets is
+\begin{align}
+  p^S(\xx_0) = \frac{\rr \cdot \eeta}{2\pi\rho^2},
+\end{align}
+and the velocity due to a rotlet is pressure-free.  Therefore, once the
+density function and Stokeslets are computed, the pressure at a point
+$\xx_0 \in \Gamma$ is
+\begin{align}
+  p(\xx_0) = -\pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0) + 
+              \frac{\rr \cdot \eeta}{2\pi\rho^2}.
+\end{align}
+
+Finally, with the pressure and shear stress, the drag on a single pore
+with boundary $\Gamma_k$ is
+\begin{align}
+  F_D = \int_{\Gamma_k} (-p \nn + \tau \ss)\,ds.
+\end{align}
 
@@
 \section{Numerical Methods\label{s:method}} 
+We discretize the second-kind integral equation~\eqref{} using a
+Nystr\"om method.  This results in a dense linear system which we solve
+with fast multipole accelerated GMRES.  Then, the shear stress,
+pressure, and drag must all be computed.  Finally, the pores must be
+eroded according to our erosion model~\eqref{}. \todo[inline]{Give
+section numbers here}
 
@@
 
-For the
+For the velocity field, the kernel of the integral operator
+\begin{align}
+  D(\xx,\yy) = \frac{\rr \cdot \nn}{\rho^2} 
+               \frac{\rr \otimes \rr}{\rho^2}
+\end{align}
+has a removable singularity when $\xx = \yy$.  In particular
+\begin{align}
+  \lim_{\substack{\yy \rightarrow \xx \\ \yy \in \Gamma}} D(\xx,\yy) = 
+  \frac{\kappa(\xx)}{2\pi}\ss \otimes \ss,
+\end{align}
+where $\kappa(\xx)$ is the curvature of $\Gamma$ at $\xx$.  By replacing
+the diagonal term
 

### 2017-06-08 docs/PhysicsPaper/StokesErosion.tex
Editing Physics paper a bit.
working on methods paper
Working on tex for PhysicsPaper

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 % COMMANDS
-
 % Basic editing
@@
 % For real and imaginary, could use \Re or \Im, or \mathcal{R}, or \text{Re}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% TITLE AUTHORS ABSTRACT
 \begin{document}
-\title{Stokes Erosion}
-\author{M. Nicholas J. Moore}
-%\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, FL 32306, USA}
-%\thanks{Email addresses for correspondence: moore@math.fsu.edu, nickmoore83@gmail.com}
-
+%\title{An eroding porous medium}
+\title{The development of anisotropy in an eroding porous medium}
+%
+\author[Nick]{M.~Nicholas J.~Moore}
+\author[Bryan]{Bryan D.~Quaife}
+\address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+\address[Bryan]{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
 \begin{abstract}
-Abstract
+We numerically simulate the erosion of a porous medium due to an internally flowing fluid.
+The solid constituents of the porous medium erode under the action of surface shear stress.
+As the particles shrink, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.
 \end{abstract}
 \maketitle
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 
-Stuff \cite{MooreCPAM2017}
+\section{Introduction}
+Stuff \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017} and other stuff \cite{Rycroft2016, Mitchell2016}.
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.5 \textwidth]{./Figs/shapes.pdf}
+\caption{
+Shapes.}
+\label{fig1}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 

### 2017-07-14 docs/methods/erosion_methods.tex
cleaned up fortran code and added a routine to compute the velocity and pressure at target points

@@
 eqn2 \label{eqn:eqn2} \\
-eqn3 \label{eqn:eqn3}
+\pderiv{\xx}{\nn} = -|\tau| \label{eqn:poreEvolution}
 \end{gather}
@@
     \eeta \, ds_\yy, \quad \xx \in \Omega,
-    \label{eqn:dlp}
+    \label{eqn:velocityDLP}
 \end{align}
@@
 second-kind integral equation
+\begin{subequations}
+\label{eqn:completed_DLP}
 \begin{align}
@@
       \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
-      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Gamma, \\
-  \llambda_k &= \frac{1}{2\pi}\int_{\Gamma_k} \eeta(\yy) \, ds_\yy, \\
+      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Gamma, 
+      \label{eqn:DLP}\\
+  \llambda_k &= \frac{1}{2\pi}\int_{\Gamma_k} \eeta(\yy) \, ds_\yy, 
+  \label{eqn:stokeslet} \\
   \xi_k &= \frac{1}{2\pi}\int_{\Gamma_k} \yy^\perp \cdot \eeta(\yy)
   \, ds_\yy.
-  \label{eqn:completed_DLP}
+  \label{eqn:rotlet}
 \end{align}
+\end{subequations}
 Finally, because of the incompressibility constraint, the boundary
@@
 
-Considering the double-layer potential~\eqref{eqn:dlp} evaluated at $\xx
-\in \Omega$, the deformation tensor is
+Considering the double-layer potential~\eqref{eqn:velocityDLP} evaluated
+at $\xx \in \Omega$, the deformation tensor is
+\begin{align}
+  \ssigma^\DD(\xx) = \int_{\bd\Omega} K_\ssigma(\xx,\yy) \eeta(\yy) \,ds_\yy,
+  \label{eqn:shearStressDLP}
+\end{align}
+where the kernel $K_\ssigma$ is given by
 \begin{align*}
-  \ssigma^\DD(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) \,ds_\yy,
-\end{align*}
-where the kernel $K$ is given by
-\begin{align*}
-  K(\xx,\yy) = \frac{1}{2\pi}\left(
+  K_\ssigma(\xx,\yy) = \frac{1}{2\pi}\left(
     2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
@@
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot \eeta \,ds_\yy.
+    \nn \cdot \eeta(\yy) \,ds_\yy.
 \end{align}
@@
 \begin{align}
-  p^S(\xx_0) = \frac{\rr \cdot \eeta}{2\pi\rho^2},
+  p^S(\xx_0) = \frac{\rr \cdot \llambda}{2\pi\rho^2},
+  \label{eqn:pressureDLP}
 \end{align}
@@
   p(\xx_0) = -\pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0) + 
-              \frac{\rr \cdot \eeta}{2\pi\rho^2}.
+              \frac{\rr \cdot \llambda}{2\pi\rho^2}.
 \end{align}
@@
 
+\todo[inline]{Describe convention for normal and tangent vectors}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Numerical Methods\label{s:method}} 
-We discretize the second-kind integral equation~\eqref{} using a
-Nystr\"om method.  This results in a dense linear system which we solve
-with fast multipole accelerated GMRES.  Then, the shear stress,
-pressure, and drag must all be computed.  Finally, the pores must be
-eroded according to our erosion model~\eqref{}. \todo[inline]{Give
-section numbers here}
+We discretize the second-kind integral equation~\eqref{eqn:DLP} using a
+Nystr\"om method.  The equations for the
+Stokeslets~\eqref{eqn:stokeslet} and rotlets~\eqref{eqn:rotlet} are
+approximated with the trapezoid rule.  By applying a quadrature method,
+this results in a dense linear system which we solve with fast multipole
+accelerated GMRES.  Because of the second-kind nature of the integral
+equation, the number of GMRES iterations is mesh independent (but not
+geometry independent), and the overall complexity of the Stokes solver
+is proportional to the cost of a single matrix-vector multiplication.
+The shear stress, pressure, and drag must also be computed using
+quadrature, and this can be interpreted as a post-processing step once
+the density function, Stokeslets, and rotlets are computed.  All the
+quadrature methods are described in Section~\ref{sec:quadrature}
+
+Once the shear stress is computed, it is used to update the shape of the
+pores according to the normal flow~\eqref{eqn:poreEvolution}.  To
+eliminate tangling and stretching of the mesh, we use a $\theta-L$
+formulation~\cite{hou-low-she1994} which is described in
+Section~\ref{sec:thetaL}.  In this section, we also describe our time
+stepping method and two regularization terms that are necessary to
+control the curvature of the pores and to maintain spectral accuracy in
+space.
+
+\todo[inline]{Describe the upcoming subsections better}
 
@@
 \subsection{Quadrature} 
+\label{sec:quadrature}
 There are several integrals that we need to compute including the
-double-layer potential velocity field~\eqref{eqn:dlp}, the shear
-stress~\eqref{}, and the pressure~\eqref{}.  By using carefully choosing
-the quadrature rules, high-order solutions can be computed.  For all the
+double-layer potential velocity field~\eqref{eqn:velocityDLP}, the shear
+stress~\eqref{eqn:shearStressDLP}, and the
+pressure~\eqref{eqn:pressureDLP}.  By using carefully choosing the
+quadrature rules, high-order solutions can be computed.  For all the
 integrals, the trapezoid rule is used since it achieves spectral
@@
 \end{align}
-where $\kappa(\xx)$ is the curvature of $\Gamma$ at $\xx$.  By replacing
-the diagonal term
+where $\kappa(\xx)$ is the curvature of $\Gamma$ at $\xx$.  By using
+this limiting term in when applying the trapezoid rule, spectral
+accuracy is achieved because of the smoothness and periodicity of the
+integrand~\cite{tre-wei2014}.
+
+For the shear stress and the pressure, we will use odd-even integration
+which achieves spectral accuracy if the integrand is no stronger than
+$\mathcal{O}(\rho^{-1})$.  Since both these integrands are too strong,
+the singularity must be weakened.  This can be done by adding a constant
+density function which has no effect on the shear stress and
+pressure~\cite{}.  In particular, the shear stress due to the
+double-layer potential is equivalent to
+\begin{align}
+  \ssigma^{\DD}(\xx_0) &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
+      \ssigma(\yy) \, ds_{\yy} \\ 
+      &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
+      (\ssigma(\yy) - \ssigma(\xx_0)) \, ds_{\yy}.
+\end{align}
+For the pressure, the double-layer potential is equivalent to
+\begin{align}
+  p^\DD(\xx) = -\frac{1}{\pi}\int_{\Gamma} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
+    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
+\end{align}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Time Stepping} 
-We use a quasi-static formulation ....
+\subsection{Fast Summation} 
+All the layer potentials are compatible with a fast summation such as
+the Fast Multipole Method (FMM).  The majority of the
 
@@
 \subsection{$\theta-L$ Formulation} 
+\label{sec:thetaL}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fast Summation}
+We use a quasi-static approximation so that the velocity field
+instantaneously changes with the changing geometry.  Therefore, we can
+alternate between the two main aspects of our simulation
+\begin{enumerate}
+  \item Given a geometry, compute the shear stress of along each of the
+  pores.
+  \item Given the shear stress, update the geometry according to the
+  erosion model.
+\end{enumerate}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Artificial Diffusion}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Gaussian Filter}
+\todo[inline]{Artificial Diffusion} 
+\todo[inline]{Gaussian Filter}
 

### 2017-07-14 fortran_code/stokesDriver.f

@@ -1,26 +1,34 @@
       program stokesDriver
       implicit real*8 (a-h,o-z)
 
-      parameter (ninner = 2048)
-c      parameter (ninner = 32)
-      parameter (nbodies = 1)
+c      parameter (ninner = 1024)
+      parameter (ninner = 128)
+      parameter (nbodies = 2)
       parameter (nouter = 2**12)
+      parameter (ntargets = 40)
+      parameter (maxbodies = 10)
 
-      dimension centerx(20),centery(20)
-      dimension radius(20),phi(20)
+      dimension centerx(maxbodies),centery(maxbodies)
+      dimension radius(maxbodies),phi(maxbodies)
       dimension x(ninner*nbodies),y(ninner*nbodies)
       dimension den(2*ninner*nbodies + 3*nbodies + 2*nouter)
       dimension shear_stress(ninner*nbodies)
       dimension pressure(ninner*nbodies)
       dimension drag(2*nbodies)
 
+      dimension xtar(ntargets*ntargets)
+      dimension ytar(ntargets*ntargets)
+      dimension utar(ntargets*ntargets)
+      dimension vtar(ntargets*ntargets)
+      dimension press_tar(ntargets*ntargets)
+
       twopi = 8.d0*datan(1.d0)
       dtheta = twopi/dble(ninner)
 
       centerx(1) = -0.0d0
       centery(1) = 0.0d0
-      centerx(2) = 0.5d0
-      centery(2) = -0.0d0
+      centerx(2) = 0.8d0
+      centery(2) = -0.1d0
       radius(1) = 2.d-1
       radius(2) = 2.d-1
       phi(1) = 0.d0
@@ -35,6 +43,25 @@ c      parameter (ninner = 32)
      $          (dcos(phi(j))*dcos(theta) + dsin(phi(j))*dsin(theta))
           y((j-1)*ninner+k) = centery(j) + 2.d0*var_rad*
      $          (-dsin(phi(j))*dcos(theta) + dcos(phi(j))*dsin(theta))
+        enddo
+      enddo
+
+
+      xmin = -1.d0
+      xmax = 2.d0
+      ymin = -5.d-1
+      ymax = 5.d-1
+      nx = ntargets
+      ny = ntargets
+      dx = (xmax - xmin)/dble(nx-1)
+      dy = (ymax - ymin)/dble(ny-1)
+
+      icount = 0
+      do j = 1,nx
+        do k = 1,ny 
[…]

### 2017-07-14 fortran_code/stokesSolver.f

@@ -1592,55 +1592,45 @@ c     OBSTACLES
 
 
 c***********************************************************************
-      subroutine computeShearStress(nninner,nnbodies,nnouter,xx,yy,den,
+      subroutine computeShearStress(ninner,nbodies,nouter,x,y,den,
      $    shear_stress)
 c     Input x and y coordinates and the density function on the
 c     boundary and return the shear stress on the inner walls.  
       implicit real*8 (a-h,o-z)
 
-      dimension xx(nninner*nnbodies),yy(nninner*nnbodies)
-c     x and y coordinates of obstacle
-
       parameter (nmax = 2**15)
       parameter (maxbodies = 10)
 c     max points on the boundary of the obstacle      
 
-      dimension x(nmax),y(nmax)
-      dimension centerx(maxbodies),centery(maxbodies)
-      dimension px(nmax),py(nmax)
+      dimension x(ninner*nbodies),y(ninner*nbodies)
+      dimension centerx(nbodies),centery(nbodies)
+      dimension px(ninner*nbodies),py(ninner*nbodies)
 c     x and y coordinates of the normal of the obstacle
-      dimension cur(nmax),speed(nmax)
+      dimension cur(ninner*nbodies),speed(ninner*nbodies)
 c     Jacobian and curvature of the geometry
 
-      dimension xouter(nmax),youter(nmax)
+      dimension xouter(nouter*nbodies),youter(nouter*nbodies)
 c     x and y coordinates of confining wall
-      dimension px0(nmax), py0(nmax)
+      dimension px0(nouter*nbodies), py0(nouter*nbodies)
 c     x and y coordinates of the normal of the confining wall
-      dimension cur0(nmax), speed0(nmax)
+      dimension cur0(nouter*nbodies), speed0(nouter*nbodies)
 c     Jacobian and curvature of the confining wall
 
-      dimension den(2*nninner*nnbodies + 3*nnbodies + 2*2**12)
+      dimension den(2*ninner*nbodies + 3*nbodies + 2*nouter)
 c     x and y coordinates of the density function
 
-      dimension E11(nninner*nnbodies)
-      dimension E12(nninner*nnbodies)
-      dimension E22(nninner*nnbodies)
+      dimension E11(ninner*nbodies)
+      dimension E12(ninner*nbodies)
+      dimension E22(ninner*nbodies)
 c     components of the deformation gradient on the obstacle
[…]

### 2017-07-14 docs/TexNotes/Notes.tex
Fixing the folder stucture and adding back files I accidentally deleted

--- 2017-03-22 docs/Notes.tex
@@
 \newcommand{\X}{\bvec{X}}
+\newcommand {\bq} {\bvec{q}}
 % Domains
@@
 
+\subsection{The vanishing rate of the area}
+The rate of area loss is given by
+\begin{equation}
+\dot{A} = -C \abs{\tau} L
+\end{equation}
+We then insert the scaling $\abs{\tau} \sim -1/(L \log L)$ and simplify to get
+\begin{equation}
+\dot{A} = C/\log{A}
+\end{equation}
+which we solve to get
+\begin{equation}
+A (1 - \log A) = C (t_f - t)
+\end{equation}
+In particular, I believe the signs are correct here.
+
 \subsection{How to scale smoothing parameters?}
@@
 
+\section{Permeability, conductivity, drag, resistance, and all of that}
+
+Darcy's law is
+\begin{equation}
+\bq = - \bvec{K} \grad \phi
+\end{equation}
+where $\bq$ is the specific discharge, $\phi = z + p/\gamma$ is the hydraulic head, and $\gamma = \rho g$.
+The rank-2 tensor $\bvec{K}$ is the {\em conductivity}, which is related to the {\em permeability} $\bvec{k}$ via $\bvec{K} = \bvec{k} \gamma/\mu$, where $\mu$ is the viscosity of the fluid.
+The units of conductivity are length-per-time (i.e.~velocity) and the units of permeability are length squared.
+Perhaps the most standard parameter to characterize the porous medium is the permeability, so lets focus on that. Let us also eliminate gravity from consideration to get
+\begin{equation}
+\bq = - \bvec{k} \grad p / \mu
+\end{equation}
+Consider first an isotropic medium with permeability $k$ (scalar).
+I propose that we decompose the permeability into the contribution from channel walls and from the embedded bodies $k = k_{c} + k_{b}$.
+Lets first figure out the contribution from the channel walls $k_c$.
+Consider flow in a channel of width $2w$ due to a pressure difference of $\Delta p$ occurring over a length $2 \ell$, so that the pressure gradient is $\grad p = -\Delta p/(2 \ell)$.
+If I did it correctly, the velocity is
+\begin{equation}
+u(z) = \frac{\Delta p}{4 \mu \ell} (w^2 - z^2)
+\end{equation}
+Then we can calculate the discharge as
+\begin{equation}
+q = \frac{1}{2w} \int_{-w}^{w} u(z) dz = \frac{\Delta p w^2}{6 \mu \ell} = - \frac{w^2}{3 \mu} \grad p
+\end{equation}
+so that the channel permeability is given by
+\begin{equation}
+k_c = w^2/3
+\end{equation}
+This result at least has the correct units (length squared).
+
 \end{document}

### 2017-07-16 docs/TexNotes/Notes.tex
Writing Latex notes on permeability, resistance, and how to remove the contribution from the walls

@@
 
-\section{Permeability, conductivity, drag, resistance, and all of that}
+\section{Permeability, conductivity, drag, resistance, and all that}
 
@@
 Consider first an isotropic medium with permeability $k$ (scalar).
-I propose that we decompose the permeability into the contribution from channel walls and from the embedded bodies $k = k_{c} + k_{b}$.
-Lets first figure out the contribution from the channel walls $k_c$.
-Consider flow in a channel of width $2w$ due to a pressure difference of $\Delta p$ occurring over a length $2 \ell$, so that the pressure gradient is $\grad p = -\Delta p/(2 \ell)$.
+As a warmup, consider flow in a channel of width $2w$ due to a pressure difference of $\Delta p$ occurring over a length $2 \ell$, so that the pressure gradient is $\grad p = -\Delta p/(2 \ell)$.
 If I did it correctly, the velocity is
@@
 \end{equation}
-so that the channel permeability is given by
+so that the permeability due to the channel walls is given by
 \begin{equation}
-k_c = w^2/3
+k_w = w^2/3
 \end{equation}
@@
 
+Next, consider measuring the permeability for flow through a matrix of bodies.
+To accomplish this, we should measure the pressure and velocity along two vertical lines, one at $x = x_0$ and another at $x = -x_0$, and average to get $p^+ = \left< p(x_0) \right>$, $p^- = \left<p(-x_0) \right>$ and the same for $q$.
+Then the measured value of the total permeability (setting $\mu = 1$), is
+\begin{equation}
+k_{tot} = \frac{x_0 (q^+ + q^-)}{p^- - p^+}
+\end{equation}
+Presumably, $q$ (the average along a vertical cross-section) should be the same everywhere, but we should check this.
+
+The `total' permeability above includes resistance from both the bodies and the channel walls, and so the value is artificially low (the true permeability of just the bodies will be a bit higher).
+In electrical circuits, the conductivity and resistivity are simply reciprocals of one another, so I presume the same holds for porous media flow, giving
+\begin{equation}
+\frac{1}{k_{tot}} = \frac{1}{k_w} + \frac{1}{k_b}
+\end{equation}
+ where $k_w = w^2/3$ is from the channel walls and $k_b$ is from the erodible bodies.
+Then, to compute the permeability from the bodies, we would remove the contribution from the walls.
+First, lets consider the resistances (the reciprocals of the permeabilities)
+\begin{equation}
+\frac{1}{k_b} = \frac{1}{k_{tot}} - \frac{1}{k_w} = \frac{k_w - k_{tot}}{k_w k_{tot}}
+\end{equation}
+which gives
+\begin{equation}
+k_b = \frac{k_w k_{tot}}{k_w - k_{tot}}
+\end{equation}
+
 \end{document}

### 2017-07-18 julia/basic.jl
Added ztest_channel.jl which just computes the flow in a 2D channel with no erodible bodies inside. This is useful to test my resistivity / permeability routines and I expect it could be useful for many other things in the future

@@ -175,7 +175,11 @@ end
 # getnvals: Calculate npts and nbods.
 function getnvals(thlenv::Vector{ThetaLenType})
 	nbods = endof(thlenv)
-	npts = endof(thlenv[1].theta)
+	if nbods ==0
+		npts = 0
+	else
+		npts = endof(thlenv[1].theta)
+	end
 	return npts,nbods
 end
 # Calculate n1 and n2 to divy up the separate bodies.

### 2017-07-18 julia/main.jl

@@ -159,7 +159,7 @@ end
 # resistivity: Compute the resistivity/permeability of the porous matrix.
 function resistivity(thlenden::ThLenDenType, nouter::Int, x0::Float64)
 	# Set up targets points on a y-grid for midpoint rule.
-	nypts = 5
+	nypts = 21
 	dy = 2./nypts
 	ylocs = collect(-1+0.5*dy: dy: 1-0.5*dy)
 	# Target points for plus/minus x0.
@@ -183,7 +183,9 @@ function resistivity(thlenden::ThLenDenType, nouter::Int, x0::Float64)
 	# Subtract the contribution from the walls.
 	rbods = rtot - 3.
 
-	println("At x0 = ",x0," the body resistivity is: ",rbods)
+	println("At x0 = ", x0, " the total resistivity is: ", signif(rtot,3))
+	println("At x0 = ", x0, " the body resistivity is: ", signif(rbods,3))
+
 
 	# Calculate the corresponding permeabilities.
 	#ktot = 1/rtot

### 2017-07-18 julia/ztest_channel.jl

@@ -1,0 +1,19 @@
+# Test
+include("main.jl")
+
+function test()
+	nouter = 1024
+	# ParamType(dt,eps,sigma,nouter,iffm,fixarea)
+	params = ParamType(0., 0., 0., nouter, 1, 0)
+	thlenden = ThLenDenType([],[],[])
+	compute_density!(thlenden,params)
+
+	#--------------------------------------#
+	# Compute the permeability
+	println()
+	r1 = resistivity(thlenden,nouter,1.2)
+	r2 = resistivity(thlenden,nouter,1.5)
+	r3 = resistivity(thlenden,nouter,1.8)
+end
+
+test()

### 2017-07-18 julia/main.jl
Trying to figure out the subtleties of restistivy of the buffer plus porous matrix regions.

@@ -104,9 +104,9 @@ function postprocess(foldername::AbstractString)
 		#--------------------------------------#
 		# Compute the permeability
 		println()
-		r1 = resistivity(thlenden,nouter,1.2)
-		r2 = resistivity(thlenden,nouter,1.5)
-		r3 = resistivity(thlenden,nouter,1.8)
+		rt1,rb1 = resistivity(thlenden,nouter,1.2)
+		rt2, rb2 = resistivity(thlenden,nouter,1.5)
+		rt3, rb3 = resistivity(thlenden,nouter,1.8)
 
 		#--------------------------------------#
 		# Compute the drag on each body.
@@ -159,7 +159,7 @@ end
 # resistivity: Compute the resistivity/permeability of the porous matrix.
 function resistivity(thlenden::ThLenDenType, nouter::Int, x0::Float64)
 	# Set up targets points on a y-grid for midpoint rule.
-	nypts = 21
+	nypts = 11
 	dy = 2./nypts
 	ylocs = collect(-1+0.5*dy: dy: 1-0.5*dy)
 	# Target points for plus/minus x0.
@@ -182,13 +182,8 @@ function resistivity(thlenden::ThLenDenType, nouter::Int, x0::Float64)
 	rtot = (pminus - pplus)/(2*x0*qavg)
 	# Subtract the contribution from the walls.
 	rbods = rtot - 3.
-
+	# For testing.
 	println("At x0 = ", x0, " the total resistivity is: ", signif(rtot,3))
 	println("At x0 = ", x0, " the body resistivity is: ", signif(rbods,3))
-
-
-	# Calculate the corresponding permeabilities.
-	#ktot = 1/rtot
-	#kbods = 1/rbods
-	return rbods
+	return rtot,rbods
 end

### 2017-07-18 julia/ztest_channel.jl

@@ -11,9 +11,9 @@ function test()
 	#--------------------------------------#
 	# Compute the permeability
 	println()
-	r1 = resistivity(thlenden,nouter,1.2)
-	r2 = resistivity(thlenden,nouter,1.5)
-	r3 = resistivity(thlenden,nouter,1.8)
+	rt1,rb1 = resistivity(thlenden,nouter,1.2)
+	rt2,rb3 = resistivity(thlenden,nouter,1.5)
+	rt2,rb3 = resistivity(thlenden,nouter,1.8)
 end
 
 test()

### 2017-07-18 docs/TexNotes/Notes.tex
Added ztest_channel.jl which just computes the flow in a 2D channel with no erodible bodies inside. This is useful to test my resistivity / permeability routines and I expect it could be useful for many other things in the future
Finished routines for resistivity

--- 2017-07-14 docs/TexNotes/Notes.tex
@@
 \end{equation}
-Consider first an isotropic medium with permeability $k$ (scalar).
-I propose that we decompose the permeability into the contribution from channel walls and from the embedded bodies $k = k_{c} + k_{b}$.
-Lets first figure out the contribution from the channel walls $k_c$.
-Consider flow in a channel of width $2w$ due to a pressure difference of $\Delta p$ occurring over a length $2 \ell$, so that the pressure gradient is $\grad p = -\Delta p/(2 \ell)$.
-If I did it correctly, the velocity is
+Consider first an isotropic medium with permeability $k$ (scalar). Overall, it is more straightforward to work with the resistivity $r = 1/k$.
+
+As a warmup, consider flow in a channel of width $2w$ due to uniform (negative) pressure gradient $p_x$ in the $x$-direction. The resulting velocity profile is
 \begin{equation}
-u(z) = \frac{\Delta p}{4 \mu \ell} (w^2 - z^2)
+u(z) = -\frac{p_x}{2 \mu} (w^2 - z^2)
 \end{equation}
@@
 \begin{equation}
-q = \frac{1}{2w} \int_{-w}^{w} u(z) dz = \frac{\Delta p w^2}{6 \mu \ell} = - \frac{w^2}{3 \mu} \grad p
+q = \frac{1}{2w} \int_{-w}^{w} u(z) dz = - \frac{ p_x w^2}{3 \mu} 
 \end{equation}
-so that the channel permeability is given by
+so that the permeability due to the channel walls is $k_w = w^2/3$ and the resistivity is $r_w = 3/w^2$.
+
+Next, consider the flow through a porous matrix (and set $\mu=1$ via nondimensionalization).
+Measure the pressure and velocity along two vertical lines, one at $x = x_0$ and another at $x = -x_0$, and average to get $p^+ = \left< p(x_0) \right>$, $p^- = \left<p(-x_0) \right>$ and the same for $q$.
+Then the {\em total} resistivity (that of the porous matrix and the channel walls together) is
 \begin{equation}
-k_c = w^2/3
+r_{tot} = \frac{p^- - p^+}{2 x_0 q_{avg}}
 \end{equation}
-This result at least has the correct units (length squared).
+This total resistivity reflects the resistivity from the porous matrix as well as the channel walls.
+There is a buffer region that lies outside the porous-matrix region ($x_0$ lies in the bugger region), and we would like to remove the contribution from this region.
+Lets regard the total resistivity as an area-integral of resistivity-density, so that we can write the total in terms of the areas of the regions
+\begin{equation}
+A_{t} r_{t} = A_{b} r_{b} + A_{m} r_{m}
+\end{equation}
+Here, the subscripts are as follows: $t$ stands for total, $b$ for buffer, and $m$ for matrix. Then we can solve for the resistivity in the matrix region
+\begin{equation}
+r_m = \frac{A_t r_t - A_b r_b}{A_m}
+\end{equation}
+In the buffer region, resistivity is only due to channel walls so that $r_b = 3$.
+The area of the included buffer region depends on $x_0$ via $A_b = 4(x_0 - 1)$.
+The area of the matrix region is always $A_m = 4$, and $A_t = A_b + A_m$.
+The resulting resistivity in the matrix, $r_m$, includes the contribution from the bodies as well as the channel walls.
+We can then subtract the contribution from the walls, to get $\tilde{r}_m$, the resistivity due to the bodies alone as
+\begin{equation}
+\tilde{r}_m = r_m - 3 \, .
+\end{equation}
+Putting everything together, the final formula is
+\begin{equation}
+\tilde{r}_m = x_0 (r_t - 3) \, .
+\end{equation}
+As convoluted as this calculation seems, it does appear to give convergent numerical results that are {\em independent of the choice of $x_0$} (to the expected order of accuracy).
 

### 2017-07-18 julia/main.jl

@@ -104,9 +104,9 @@ function postprocess(foldername::AbstractString)
 		#--------------------------------------#
 		# Compute the permeability
 		println()
-		rt1,rm1 = resistivity(thlenden, nouter, 1.5)
-		rt2,rm2 = resistivity(thlenden, nouter, 2.0)
-		rt3,rm3 = resistivity(thlenden, nouter, 2.5)
+		rt1,rb1 = resistivity(thlenden, nouter, 1.5)
+		rt2,rb2 = resistivity(thlenden, nouter, 2.0)
+		rt3,rb3 = resistivity(thlenden, nouter, 2.5)
 
 		#--------------------------------------#
 		# Compute the drag on each body.
@@ -180,14 +180,11 @@ function resistivity(thlenden::ThLenDenType, nouter::Int, x0::Float64)
 	assert(qreldiff < 1e-6)
 	# Calculate the total resistivity
 	rtot = (pminus - pplus)/(2*x0*qavg)
-	#= Estimate the resistivity of the porous matrix region by
-	an area-weighted average. =#
-	Amat = 4.
-	Abuf = 4*(x0-1)
-	Atot = Amat+Abuf
-	rbuf = 3.
-	rmat = (rtot*Atot - rbuf*Abuf)/Amat
-	# In the porous matrix region, subtract the contribution from the walls.
-	rmat = rmat - 3.
-	return rtot,rmat
+	# Calculate the resisitvity due only to the bodies.
+	rbods = x0*(rtot - 3)
+
+	# For testing.
+	println("At x0 = ", x0, " the total resistivity is: ", signif(rtot,3))
+	println("At x0 = ", x0, " the matrix resistivity is: ", signif(rbods,3))
+	return rtot,rbods
 end

### 2017-07-18 julia/ztest_channel.jl

@@ -11,9 +11,9 @@ function test()
 	#--------------------------------------#
 	# Compute the permeability
 	println()
-	rt1,rm1 = resistivity(thlenden,nouter,1.5)
-	rt2,rm3 = resistivity(thlenden,nouter,2.0)
-	rt2,rm3 = resistivity(thlenden,nouter,2.5)
+	rt1,rb1 = resistivity(thlenden,nouter,1.5)
+	rt2,rb3 = resistivity(thlenden,nouter,2.0)
+	rt2,rb3 = resistivity(thlenden,nouter,2.5)
 end
 
 test()

### 2017-07-18 julia/main.jl
NM

@@ -182,9 +182,8 @@ function resistivity(thlenden::ThLenDenType, nouter::Int, x0::Float64)
 	rtot = (pminus - pplus)/(2*x0*qavg)
 	# Calculate the resisitvity due only to the bodies.
 	rbods = x0*(rtot - 3)
-
 	# For testing.
-	println("At x0 = ", x0, " the total resistivity is: ", signif(rtot,3))
-	println("At x0 = ", x0, " the matrix resistivity is: ", signif(rbods,3))
+	#println("At x0 = ", x0, " the total resistivity is: ", signif(rtot,3))
+	#println("At x0 = ", x0, " the matrix resistivity is: ", signif(rbods,3))
 	return rtot,rbods
 end

### 2017-08-16 docs/methods/erosion_methods.tex
made a few small changes to the methods paper

@@
 density function which has no effect on the shear stress and
-pressure~\cite{}.  In particular, the shear stress due to the
+pressure~\cite{poz1992}.  In particular, the shear stress due to the
 double-layer potential is equivalent to
@@
 \subsection{Fast Summation} 
-All the layer potentials are compatible with a fast summation such as
-the Fast Multipole Method (FMM).  The majority of the
+The majority of the computational cost comes from evaluating the the
+double-layer potential $\mathcal{D}$ in equation~\eqref{eqn:DLP}.  This
+layer potential can be efficiently evaluated using a fast summation
+method such as the Fast Multipole Method
+(FMM)~\cite{gre-rok1987}\footnote{The FMM for the Stokes double-layer
+poetntial was supplied by Manas Rachh.}.  By using the
+FMM,~\eqref{eqn:completed_DLP} can be solved with $\mathcal{O}(N)$
+operations, where $N$ is the total number of discretization points.
+
+In our erosion model, the shear stress must be computed which requires
+evaulating the layer potential~\eqref{eqn:shearStressDLP}.  In our
+implementation, this calculation is done directly which requires
+$\mathcal{O}(N^2)$ operations.  This complexity could be reduced with
+the kernel-independent FMM~\cite{yin-bir-zor2004}.  However, since this
+calculation is only computed once per time step, unlike the velocity
+double-layer potential that must be evaluated at each GMRES iteration.
 

### 2017-08-16 fortran_code/stokesDriver.f

@@ -1,9 +1,9 @@
       program stokesDriver
       implicit real*8 (a-h,o-z)
 
-c      parameter (ninner = 1024)
+c      parameter (ninner = 4096)
       parameter (ninner = 128)
-      parameter (nbodies = 2)
+      parameter (nbodies = 1)
       parameter (nouter = 2**12)
       parameter (ntargets = 40)
       parameter (maxbodies = 10)
@@ -22,35 +22,46 @@ c      parameter (ninner = 1024)
       dimension vtar(ntargets*ntargets)
       dimension press_tar(ntargets*ntargets)
 
-      twopi = 8.d0*datan(1.d0)
+      pi = 4.d0*datan(1.d0)
+      twopi = 2.d0*pi
       dtheta = twopi/dble(ninner)
 
       centerx(1) = -0.0d0
       centery(1) = 0.0d0
-      centerx(2) = 0.8d0
+c      centerx(2) = 0.8d0
+      centerx(2) = 0.0d0
       centery(2) = -0.1d0
       radius(1) = 2.d-1
       radius(2) = 2.d-1
       phi(1) = 0.d0
       phi(2) = 0.d0
 
+      Nphi = 128
+      dphi = twopi/Nphi
+      open(unit=21,file='output/dragx.dat')
+      open(unit=22,file='output/dragy.dat')
+
+      do kk = 1,Nphi
+        phi(1) = dble(kk-1)*dphi
 
       do j = 1,nbodies
         do k = 1,ninner
           theta = dble(k-1)*dtheta
           var_rad = radius(j)
           x((j-1)*ninner+k) = centerx(j) + var_rad*
-     $          (dcos(phi(j))*dcos(theta) + dsin(phi(j))*dsin(theta))
-          y((j-1)*ninner+k) = centery(j) + 2.d0*var_rad*
-     $          (-dsin(phi(j))*dcos(theta) + dcos(phi(j))*dsin(theta))
+     $          (dcos(phi(j))*dcos(theta) + 
+     $           dsin(phi(j))*2.d0*dsin(theta))
+          y((j-1)*ninner+k) = centery(j) + var_rad*
+     $          (-dsin(phi(j))*dcos(theta) + 
+     $           dcos(phi(j))*2.d0*dsin(theta))
         enddo
       enddo
 
 
       xmin = -1.d0
-      xmax = 2.d0
-      ymin = -5.d-1
-      ymax = 5.d-1
+      xmax = 1.d0
+      ymin = -8.d-1
+      ymax = 8.d-1
[…]

### 2017-08-25 docs/methods/erosion_methods.tex
Worked a little on Methods tex file.

@@
   \item Avoiding stokes paradox
-  \item $\theta-L$ formulation
+  \item \thL formulation
   \item Regularization
@@
 This results in a rank-one null space of
-equation~\eqref{eqn:completed_DLP} which we remove by adding the rank
-one modification $\NN_0[\eeta](\xx) = \int_{\Gamma_0} (\nn(\xx) \times
+equation~\eqref{eqn:completed_DLP} which we remove by adding the 
+rank-one modification $\NN_0[\eeta](\xx) = \int_{\Gamma_0} (\nn(\xx) \times
 \nn(\yy))\nn(\yy) \, ds_\yy$, for $\xx \in \Gamma_0$.
@@
 pores according to the normal flow~\eqref{eqn:poreEvolution}.  To
-eliminate tangling and stretching of the mesh, we use a $\theta-L$
+eliminate tangling and stretching of the mesh, we use a \thL
 formulation~\cite{hou-low-she1994} which is described in
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{$\theta-L$ Formulation} 
+\subsection{\thL Formulation} 
 \label{sec:thetaL}
@@
 \end{enumerate}
+
+\vsp{2}
+To handle boundary evolution, we use the \thL    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems.
+Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).
+(BRYAN: Can we use these conventions throughout the paper?)
+
+In order to regularize boundary evolution, we modify Eq.~(\ref{eqn:poreEvolution}) to include a curvature-driven component (also corrected errors in this equation)
+\begin{equation}
+\pderiv{\xx}{t} = |\tau| \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
+\end{equation}
+The curvature term acts to smooth bodies that have high-frequency oscillations.
 

### 2017-08-26 docs/TexNotes/Notes.tex
Worked a little on Methods tex file.
Updated some things to reflect the log(W/L) issue. In particular, I updated my latex Notes.

@@
 \section{Scaling law and interface smoothing}
-For Stokes flow, the shear stress scales like
+For 3D Stokes flow, the shear stress scales like
 \begin{equation}
@@
 \subsection{Different scaling of the stress}
-Some numerical tests reveal that the stress scales like $\tau \sim 1/(L \log L)$, instead of the naive $1/L$.
-This might because we are in a 2D bounded domain (Stokes paradox type stuff).
+Some numerical tests reveal that for 2D Stokes flow the stress scales like $\tau \sim 1/(L \log L)$, instead of the naive $1/L$.
+This is because we are in a 2D bounded domain (Stokes paradox type stuff).
 So we need to modify the curvature driven flow to have the same scaling.
@@
 \end{equation}
-where for 2D Stokes flow, we will have $f(L) = -1/\log L$. Carrying through this change, Eq.~(\ref{Vn2}) becomes
+For 2D Stokes flow, we have 
+\begin{equation}
+f(L) = \frac{1}{\log (W/L)}
+\end{equation}
+where $W$ is the lengthscale of the 3rd dimension (e.g.
+the length of a long cylinder).
+The 2D approximation requires $W \gg L$, and in the code I chose $W = 2 \pi$.
+Carrying through this change, Eq.~(\ref{Vn2}) becomes
 \begin{equation}
@@
 where $g(L) = L^{-2} f(L)$.
-%This will also modify the scaling law for area vs time!!!
-
-\vsp{2}
-{\bf  Alternative}: Perhaps I just want to calculate the mean of the shear stress directly and use it to scale the curvature driven flow. This idea gives
-\begin{equation}
-V_n = \atau + \eps \mean{\atau} \left(\kappa - \frac{2 \pi}{L} \right)
-\end{equation}
-which gives
-\begin{equation}
-V_n = \atau + \eps L^{-1} \mean{\atau} \left(\pd{\theta}{\alpha} - 2 \pi \right)
-\end{equation}
-Then we get
-\begin{equation}
-\pd{\theta}{t} = \eps L^{-2} \mean{\atau} \ppd{\theta}{\alpha} + L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
-\end{equation}
-Then to evolve $\theta$ spectrally, we use
-\begin{equation}
-\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{-2} \mean{\atau}  \thh_k = \hat{N}_k
-\end{equation}
-Then the Gaussian filter stuff becomes
-\begin{equation}
-\label{intfact}
-\thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
-+ \frac{\Dt}{2} \left( 3 \GG(N^{(n)}, \sigma_1) - \GG(N^{(n-1)}), \sigma_2 \right)
-\end{equation}
-where
-\begin{align}
-& \sigma_1 = 2 \pi \sqrt{\eps \Dt} \sqrt{g^{n} + g^{n+1} } 	\\
-& \sigma_2 = 2 \pi \sqrt{\eps \Dt} \sqrt{g^{n-1} + 2 g^{n} + g^{n+1} }
-\end{align}
-where $g(t)= L^{-2} \mean{\atau}$ and $g^{(n)} = g(t^{(n)})$.
-BUT the problem with this is that I do not yet know $\mean{\atau}$ at time-step $n+1$, so I would have to change my time-stepping strategy which is a significant change to the code structure.
-Thus, I prefer the first method of using $L \log L$.
 
@@
 In particular, I believe the signs are correct here.
+BUT, I am not so sure of this calculation anymore, now that $W$ is included.
 

### 2017-08-26 julia/postprocess.jl

@@ -50,6 +50,7 @@ function postprocess(foldername::AbstractString)
 		targdata = [label; targets.xtar; targets.ytar; 
 			targets.utar; targets.vtar; targets.ptar]
 		writedata(targdata, targfile)
+		println("Finished step ", cnt, " of ", ntimes, ".")
 	end
 	return
 end
@@ -81,7 +82,10 @@ function resistivity(thlenden::ThLenDenType, nouter::Int, x0::Float64; rotation:
 	#= The discharge should be exactly the same at any location x.
 	So check that it is the same at x0 and -x0. =#
 	qreldiff = (qplus-qminus)/qavg
-	assert(qreldiff < 1e-6)
+	#assert(qreldiff < 1e-6)
+	if qreldiff > 1e-6
+		warn("The flux does not match at x0 and -x0: qreldiff = ", qreldiff)
+	end
 	# Calculate the total resistivity
 	rtot = (pminus - pplus)/(2*x0*qavg)
 	# Calculate the resisitvity due only to the bodies.

### 2017-08-28 docs/methods/erosion_methods.tex
changed pores to bodies in methods paper

@@
 eqn2 \label{eqn:eqn2} \\
-\pderiv{\xx}{\nn} = -|\tau| \label{eqn:poreEvolution}
+\pderiv{\xx}{\nn} = -|\tau| \label{eqn:bodyEvolution}
 \end{gather}
@@
 The governing equations~\eqref{eqn:erosionModel} require the shear
-stress which is defined on the boundary of each pore.  The shear stress
+stress which is defined on the boundary of each body.  The shear stress
 is given by
@@
 where $\ss$ is the unit tangent vector.  We note that for the Stokes
-equations, because of the no-slip boundary condition on the pores, the
+equations, because of the no-slip boundary condition on the bodies, the
 shear stress is identical to the surface vorticity $\tau = u_y - v_x$.
@@
 
-Finally, with the pressure and shear stress, the drag on a single pore
+Finally, with the pressure and shear stress, the drag on a single body
 with boundary $\Gamma_k$ is
@@
 Once the shear stress is computed, it is used to update the shape of the
-pores according to the normal flow~\eqref{eqn:poreEvolution}.  To
+bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
 eliminate tangling and stretching of the mesh, we use a \thL
@@
 stepping method and two regularization terms that are necessary to
-control the curvature of the pores and to maintain spectral accuracy in
+control the curvature of the bodies and to maintain spectral accuracy in
 space.
@@
 \begin{enumerate}
-  \item Given a geometry, compute the shear stress of along each of the
-  pores.
+  \item Given a geometry, compute the shear stress of along the boundary
+    of each of the bodies.
   \item Given the shear stress, update the geometry according to the
@@
 
-In order to regularize boundary evolution, we modify Eq.~(\ref{eqn:poreEvolution}) to include a curvature-driven component (also corrected errors in this equation)
+In order to regularize boundary evolution, we modify
+Eq.~(\ref{eqn:bodyEvolution}) to include a curvature-driven component
+(also corrected errors in this equation)
 \begin{equation}

### 2017-08-29 docs/methods/erosion_methods.tex
worked on formulation in methods paper

@@
 \section{Formulation\label{s:formulation}} 
-We consider multiple bodies being eroded by a two-dimensional Stokesian
-fluid.  The Stokes paradox is circumvented by using a rounded-off
-rectangle that encloses the eroding bodies.  Then, the flow is driven
-by a boundary conditions, such as a Hagen-Poiseuille flow, on the
-boundary of the outer geometry \todo[inline]{Need a figure here}
-\begin{subequations}
+Let us first define the main variables used to model erosion.  We only
+consider flows that are confined by a solid wall $\Gamma$ that encloses
+$M$ eroding bodies.  The bodies are denoted as $\gamma_k$,
+$k=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup
+\gamma_M$.  Neglecting inertial forces, the dynamics of the fluid is
+fully characterized by the position of the bodies $\xx_k(s,t) \in
+\gamma_k$, where $s$ is the arclength and $t$ is time.  Given
+$\xx_k(s,t)$, $k=1,\ldots,M$, derived variables include the fluid
+velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the
+bounding wall, we prescribed a velocity $\UU(\xx,t)$.  Then, the
+governing equations are
+\begin{equation}
 \label{eqn:erosionModel}
-\begin{gather}
-eqn1 \label{eqn:eqn1} \\
-eqn2 \label{eqn:eqn2} \\
-\pderiv{\xx}{\nn} = -|\tau| \label{eqn:bodyEvolution}
-\end{gather}
-\end{subequations}
+\begin{split}
+  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{conservation
+of momentum}\\
+\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap
+&&\mbox{conservation of mass} \\
+\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{no slip on the
+bodies} \\
+\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{outer wall
+velocity} \\
+\dot{\xx}(t) = -|\tau| \nn, &\hspace{20pt} \xx \in \gamma,
+&&\mbox{erosion model},
+\end{split}
+\end{equation}
+where $\nn$ is the outward unit normal vector which points away from the
+fluid.  The outer wall is formed by rounding off the corners of $[-3,3]
+\times [-1,1]$, and we enforce the Hagen-Poiseuille flow
+\begin{align}
+  \uu(\xx) = (1-y^2,0)
+\end{align}
+on $\Gamma$.  To minimize the boundary effects of the inflow and
+outflow, we only place bodies in the center third, $[-1,1] \times
+[-1,1]$, of the fluid domain.
+\begin{figure}[htpb]
+  \centering
+  \input{figs/schematic.tikz}
+  \caption{\label{fig:schematic} A schematic for the governing
+    equations.  A no-slip boundary condition is imposed on each body
+    $\gamma_k$ whose unit normal points outward relative to the
+    geometry.  On the outer geometry $\Gamma$, a pipe flow is imposed.
+    Finally, the bodies are eroded according to the shear stress applied
+    by the Stokesian fluid.}
+\end{figure}
+
+Our erosion model is based on the shear stress, and this model is
+discussed in more detail in Section~\ref{sec:erosion}.  We then describe
+how the incompressible Stokes equations are solved in $\Omega$ using a
+boundary integral equation in Section~\ref{sec:bies}.  Then, in
+Section~\ref{sec:qois}, we discuss how the shear stress, pressure, and
+drag can all be readily computed.
 
@@
 \subsection{Erosion Model} 
-\todo[inline]{Governing equations}
+\label{sec:erosion}
+\todo[inline]{Describe the erosion model and its justification}
 
@@
 \subsection{Boundary Integral Equation Formulation} 
+\label{sec:bies}
+We use a quasi-static approximation.  That is, at each time step, we
+freeze the geometry, solve the incompressible Stokes equations, and then
+update the geometry according to the erosion model.  A flow diagram is
+illustrated in Figure~\ref{fig:workflow}.
+
 The incompressible Stokes equations are
@@
 \subsection{Computing the Shear Stress, Pressure, and Drag} 
+\label{sec:qois}
 The governing equations~\eqref{eqn:erosionModel} require the shear

### 2017-08-29 fortran_code/stokesDriver.f

@@ -4,7 +4,7 @@
 c      parameter (ninner = 4096)
       parameter (ninner = 128)
       parameter (nbodies = 1)
-      parameter (nouter = 2**12)
+      parameter (nouter = 2**8)
       parameter (ntargets = 40)
       parameter (maxbodies = 10)
 

### 2017-08-29 fortran_code/stokesSolver.f

@@ -72,20 +72,20 @@ c     load geometry of initial shape
 
 c      open(unit=1,file='output/xinner.dat')
 c      open(unit=2,file='output/yinner.dat')
-c      open(unit=3,file='output/xouter.dat')
-c      open(unit=4,file='output/youter.dat')
+      open(unit=3,file='output/xouter.dat')
+      open(unit=4,file='output/youter.dat')
 c      do k = 1,ninner*nbodies
 c        write(1,1000) x(k)
 c        write(2,1000) y(k)
 c      enddo
-c      do k = 1,nouter
-c        write(3,1000) xouter(k)
-c        write(4,1000) youter(k)
-c      enddo
+      do k = 1,nouter
+        write(3,1000) xouter(k)
+        write(4,1000) youter(k)
+      enddo
 c      close(unit=1)
 c      close(unit=2)
-c      close(unit=3)
-c      close(unit=4)
+      close(unit=3)
+      close(unit=4)
 
       call bd_condition(ninner,nbodies,x,y,nouter,xouter,youter,rhs)
 c     load boundary condition
@@ -120,7 +120,7 @@ c      close(unit=4)
 c      close(unit=5)
       
 
-c 1000 format(E25.16)
+ 1000 format(E25.16)
       end
 
 

### 2017-08-30 docs/methods/erosion_methods.tex
worked on section 2 of the methods paper

@@
 \times [-1,1]$, and we enforce the Hagen-Poiseuille flow
-\begin{align}
+\begin{align*}
   \uu(\xx) = (1-y^2,0)
-\end{align}
-on $\Gamma$.  To minimize the boundary effects of the inflow and
-outflow, we only place bodies in the center third, $[-1,1] \times
-[-1,1]$, of the fluid domain.
+\end{align*}
+on $\Gamma$.  The boundary of the fluid domain is $\bd\Omega = \gamma_1
+\cup \cdots \cup \gamma_M \cup \Gamma$.  To minimize the boundary
+effects of the inflow and outflow, we only place bodies in the center
+third, $[-1,1] \times [-1,1]$, of the fluid domain.
 \begin{figure}[htpb]
@@
     by the Stokesian fluid.}
+\end{figure}
+
+We use a quasi-static approximation.  That is, at each time step, we
+freeze the geometry, solve the incompressible Stokes equations, and then
+update the geometry according to the erosion model.  A flow diagram is
+illustrated in Figure~\ref{fig:workflow}.  The two steps inside the red
+rectangle describes a time step in the quasi-static approximation
+\begin{figure}[htpb]
+  \centering
+  \input{figs/workflow.tikz}
+  \caption{\label{fig:workflow}A caption.}
 \end{figure}
@@
 \label{sec:bies}
-We use a quasi-static approximation.  That is, at each time step, we
-freeze the geometry, solve the incompressible Stokes equations, and then
-update the geometry according to the erosion model.  A flow diagram is
-illustrated in Figure~\ref{fig:workflow}.
-
-The incompressible Stokes equations are
+Here we focus on solving the incompressible Stokes equations with
+Dirichlet boundary conditions
 \begin{alignat*}{3}
   \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
-  \grad \cdot \uu &= 0,   && \xx \in \Gamma.
+  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
+  \uu &= \ff,  && \xx \in \bd\Omega.
 \end{alignat*}
 The viscosity $\mu$ sets the time scale, and we will assume that
-$\mu=1$.  The double-layer potential
+$\mu=1$.  We start by defining the double-layer potential, which is the
+convolution of the stresslet with a function $\eeta:\bd\Omega
+\rightarrow \RR^2$,
 \begin{align}
@@
 where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
-normal, solves the incompressible Stokes equations for any sufficiently
-smooth density function $\eeta$.  However, the double-layer potential can not capture velocity fields
-corresponding to rigid body motions~\cite{pow-mir1987}.  A standard
-method to complete the double-layer potential is to introduce a
-Stokeslet and rotlet due to each interior body
+normal.  For any density function $\eeta$, the double-layer potential
+satisfies the incompressible Stokes equations, but the double-layer
+potential can not capture velocity fields corresponding to rigid body
+motions~\cite{pow-mir1987}.  A standard method to complete the
+double-layer potential is to introduce a Stokeslet and rotlet due to
+each interior body
 \begin{align}
@@
 \end{align}
-where $\cc_k$ is a point in the interior of $\Omega_k$, $\rr = \xx -
-\cc_k$, and $\rr^\perp = (r_2,-r_1)$.  Then, the solution of the Stokes
-equations with a Dirichlet boundary condition $\ff$ can be written in
-terms of the completed double-layer potential
+where $\cc_k$ is a point inside the $k^{th}$ body,  $\rr = \xx - \cc_k$,
+and $\rr^\perp = (r_2,-r_1)$.  Then, the solution of the Stokes
+equations with a Dirichlet boundary condition $\ff$ is
 \begin{align}
+  \label{eqn:completed_DLP}
   \uu(\xx) = \DD[\eeta](\xx) + \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
               \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Omega,
-  \label{eqn:completedDLP}
 \end{align}
-where the density function, Stokeslets, and rotlets satisfy the
-second-kind integral equation
+where the density function, Stokeslets, and rotlets satisfy
 \begin{subequations}
-\label{eqn:completed_DLP}
+\label{eqn:completed_BIE}
 \begin{align}
@@
 condition must satisfy 
-\begin{align}
+\begin{align*}
   \int_{\Gamma} \ff \cdot \nn \, ds_\yy = 0.
-\end{align}
-This results in a rank-one null space of
-equation~\eqref{eqn:completed_DLP} which we remove by adding the 
-rank-one modification $\NN_0[\eeta](\xx) = \int_{\Gamma_0} (\nn(\xx) \times
-\nn(\yy))\nn(\yy) \, ds_\yy$, for $\xx \in \Gamma_0$.
+\end{align*}
+The result is a rank-one null space of~\eqref{eqn:completed_BIE} which
+is removed by adding the rank-one modification $\NN_0[\eeta](\xx) =
+\int_{\Gamma_0} (\nn(\xx) \otimes \nn(\yy))\nn(\yy) \, ds_\yy$, for $\xx
+\in \Gamma_0$.
 
@@
 \label{sec:qois}
-The governing equations~\eqref{eqn:erosionModel} require the shear
-stress which is defined on the boundary of each body.  The shear stress
-is given by
+There are several quantities besides the velocity that need to be
+comnputed.  First, the shear stress along $\gamma_k$ is required by the
+governing equations~\eqref{eqn:erosionModel}.  In addition, to study
+characteristics of the flow, the pressure and drag must also be
+computed.  Once equation~\eqref{eqn:completed_DLP} is solved for the
+density function, Stokeslets, and rotlets, all of these quantities can
+be computed by evaluating layer potentials that we now derive.
+
+\subsubsection{Shear Stress}
+The shear stress is defined by
 \begin{align}
@@
 \end{align}
-where $\ss$ is the unit tangent vector.  We note that for the Stokes
-equations, because of the no-slip boundary condition on the bodies, the
-shear stress is identical to the surface vorticity $\tau = u_y - v_x$.
-However, we use equation~\eqref{eqn:shearStress} to compute the shear
-stress since the jump conditions resulting from the double-layer
-potential are known~\cite{qua-bir2014a}.  The velocity field of the
-completed double-layer potential involves three terms: the double-layer
-potential $\DD$, the Stokeslets $S$, and the rotlets $R$.  To compute
-the shear stress, we first compute the deformation tensor $\ssigma =
-\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of each of these terms
-individually.
+where $\ss$ is the unit tangent vector (Figure~\ref{fig:schematic}).  We
+note that for the Stokes equations, because of the no-slip boundary
+condition on the bodies, the shear stress is identical to the surface
+vorticity $\tau = u_y - v_x$.  However, we use
+equation~\eqref{eqn:shearStress} to compute the shear stress since the
+jump conditions resulting from the double-layer potential are
+known~\cite{qua-bir2014a}.  The velocity field of the completed
+double-layer potential~\eqref{eqn:completed_DLP} involves three terms:
+the double-layer potential $\DD$, the Stokeslets $S$, and the rotlets
+$R$.  To compute the shear stress, we first compute the deformation
+tensor $\ssigma = \frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of each of these
+terms individually.
 
-Considering the double-layer potential~\eqref{eqn:velocityDLP} evaluated
-at $\xx \in \Omega$, the deformation tensor is
-\begin{align}
-  \ssigma^\DD(\xx) = \int_{\bd\Omega} K_\ssigma(\xx,\yy) \eeta(\yy) \,ds_\yy,
+The deformation tensor of the double-layer
+potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
+\begin{equation}
   \label{eqn:shearStressDLP}
-\end{align}
-where the kernel $K_\ssigma$ is given by
-\begin{align*}
-  K_\ssigma(\xx,\yy) = \frac{1}{2\pi}\left(
+  \begin{aligned}
+  \ssigma^\DD(\xx) = \frac{1}{2\pi}\int_{\bd\Omega} &\left(
     2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
-    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) +
-    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
+    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
+    \right. \\
+    &\left.
+    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
     8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right).
-\end{align*}
+  \right) ds_\yy.
+  \end{aligned}
+\end{equation}
 We are interested in the deformation tensor at boundary points $\xx_0
@@
 value is given by~\cite{qua-bir2014a}
-\begin{align}
+\begin{align*}
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}\sigma_\DD(\xx) =
@@
   \end{array}\right] + \ssigma^\DD(\xx_0), \quad \xx_0 \in \Gamma.
-\end{align}
+\end{align*}
 
-The deformation tensor due to the Stokeslets and rotlets in
-equation~\eqref{eqn:stokeslet_rotlet} are
-\begin{align}
+The deformation tensor due to the Stokeslets and
+rotlets~\eqref{eqn:stokeslet_rotlet} are
+\begin{align*}
   \ssigma^S(\xx_0) &= \frac{\rr \cdot \llambda}{4\pi\rho^2} \left(
@@
                            \rr^\perp \otimes \rr \right).
-\end{align}
+\end{align*}
 Now that the deformation tensor of each component of the completed
 double-layer potential are computed, the shear stress at $\xx_0 \in
-\Gamma$ can be computed as
-\begin{align}
+\Gamma$ can be written as
+\begin{align*}
   \tau = \left(J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) + 
     \ssigma^S(\xx_0) + \ssigma^R(\xx_0)\right) \nn \cdot \ss.
-\end{align}
+\end{align*}
 
+\subsubsection{Pressure}
 To compute the pressure at $\xx_0 \in \Gamma$, we follow the same
 procedure used for the shear stress.  In particular, we compute the
-pressure due to each of the three terms that compose the completed
-double-layer potential.  They are given by
-\begin{align}
+pressure due to each of the three terms in the completed double-layer
+potential~\eqref{eqn:completed_DLP}.  They are given by
+\begin{align*}
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
   -\pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0),
-\end{align}
+\end{align*}
 where
-\begin{align}
+\begin{align*}
   p^\DD(\xx) = -\frac{1}{\pi}\int_{\Gamma} \frac{1}{\rho^2}
@@
     \nn \cdot \eeta(\yy) \,ds_\yy.
-\end{align}
+\end{align*}
 The pressure due to the Stokeslets is
@@
 \end{align}
-and the velocity due to a rotlet is pressure-free.  Therefore, once the
-density function and Stokeslets are computed, the pressure at a point
-$\xx_0 \in \Gamma$ is
-\begin{align}
+and the pressure of a rotlet is zero.  Therefore, once the density
+function and Stokeslets are computed, the pressure at a point $\xx_0 \in
+\Gamma$ is
+\begin{align*}
   p(\xx_0) = -\pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0) + 
               \frac{\rr \cdot \llambda}{2\pi\rho^2}.
-\end{align}
+\end{align*}
 
+\subsubsection{Drag}
 Finally, with the pressure and shear stress, the drag on a single body
 with boundary $\Gamma_k$ is
-\begin{align}
+\begin{align*}
   F_D = \int_{\Gamma_k} (-p \nn + \tau \ss)\,ds.
-\end{align}
-
-\todo[inline]{Describe convention for normal and tangent vectors}
+\end{align*}
 
@@
 For the velocity field, the kernel of the integral operator
-\begin{align}
+\begin{align*}
   D(\xx,\yy) = \frac{\rr \cdot \nn}{\rho^2} 
                \frac{\rr \otimes \rr}{\rho^2}
-\end{align}
+\end{align*}
 has a removable singularity when $\xx = \yy$.  In particular
-\begin{align}
+\begin{align*}
   \lim_{\substack{\yy \rightarrow \xx \\ \yy \in \Gamma}} D(\xx,\yy) = 
   \frac{\kappa(\xx)}{2\pi}\ss \otimes \ss,
-\end{align}
+\end{align*}
 where $\kappa(\xx)$ is the curvature of $\Gamma$ at $\xx$.  By using
@@
 double-layer potential is equivalent to
-\begin{align}
+\begin{align*}
   \ssigma^{\DD}(\xx_0) &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
@@
       (\ssigma(\yy) - \ssigma(\xx_0)) \, ds_{\yy}.
-\end{align}
+\end{align*}
 For the pressure, the double-layer potential is equivalent to
-\begin{align}
+\begin{align*}
   p^\DD(\xx) = -\frac{1}{\pi}\int_{\Gamma} \frac{1}{\rho^2}
@@
     \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
-\end{align}
+\end{align*}
 
@@
 poetntial was supplied by Manas Rachh.}.  By using the
-FMM,~\eqref{eqn:completed_DLP} can be solved with $\mathcal{O}(N)$
+FMM,~\eqref{eqn:completed_BIE} can be solved with $\mathcal{O}(N)$
 operations, where $N$ is the total number of discretization points.

### 2017-08-31 julia/main.jl
trying openmp

@@ -31,7 +31,7 @@ function erosion()
 		# Gracefully exit if all of the bodies have disappeared.
 		if endof(thlenden1.thlenvec)==0; break; end
 		# Advance the thlen vectors.
-		advance_thetalen!(thlenden1,thlenden0,params)
+	        advance_thetalen!(thlenden1,thlenden0,params)
 	end
 	# Post-process to compute the drag and other quantities.
 	#postprocess("run")

### 2017-08-31 docs/methods/erosion_methods.tex
Little chagne to latex methods
trying openmp
fixed up image and started checking for sign errors in the BIE formulation of the paper

@@
     geometry.  On the outer geometry $\Gamma$, a pipe flow is imposed.
-    Finally, the bodies are eroded according to the shear stress applied
-    by the Stokesian fluid.}
+    The bodies are eroded according to the shear stress applied by the
+    Stokesian fluid.  Finally, the bodies are constrained to the middle
+    third of the channel that is located between the dashed lines.}
 \end{figure}
@@
 \label{sec:erosion}
+
+To model erosion, we the normal velocity is prescribed to be
+proportional to the absolute value of the shear stress.  The constant of
+proportionality sets the time scale, and we set its value to be -1
+\begin{align}
+  \dot{\xx}(t) = -|\tau| \nn.
+  \label{eqn:bodyEvolution}
+\end{align}
+
 \todo[inline]{Describe the erosion model and its justification}
@@
 \subsubsection{Shear Stress}
+\todo[inline]{check all signs in this section.  Fortran code assumes an
+inward pointing normal}
 The shear stress is defined by
@@
 \subsubsection{Pressure}
+\todo[inline]{check all signs in this section.  Fortran code assumes an
+inward pointing normal}
 To compute the pressure at $\xx_0 \in \Gamma$, we follow the same
@@
 \subsubsection{Drag}
+\todo[inline]{check all signs in this section.  Fortran code assumes an
+inward pointing normal}
 Finally, with the pressure and shear stress, the drag on a single body
@@
   \lim_{\substack{\yy \rightarrow \xx \\ \yy \in \Gamma}} D(\xx,\yy) = 
-  \frac{\kappa(\xx)}{2\pi}\ss \otimes \ss,
+  -\frac{\kappa(\xx)}{2\pi}\ss \otimes \ss,
 \end{align*}
@@
 Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).
-(BRYAN: Can we use these conventions throughout the paper?)
+
+\todo[inline]{BRYAN: Can we use these conventions throughout the paper?}
 

### 2017-09-05 docs/methods/erosion_methods.tex
added voriticy to code

@@
 \begin{align}
-  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
+  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
     \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
-    \eeta \, ds_\yy, \quad \xx \in \Omega,
+    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
     \label{eqn:velocityDLP}
@@
 where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
-normal.  For any density function $\eeta$, the double-layer potential
-satisfies the incompressible Stokes equations, but the double-layer
-potential can not capture velocity fields corresponding to rigid body
-motions~\cite{pow-mir1987}.  A standard method to complete the
-double-layer potential is to introduce a Stokeslet and rotlet due to
-each interior body
+normal at $\yy$.  For any density function $\eeta$, the double-layer
+potential satisfies the incompressible Stokes equations, but the
+double-layer potential can not capture velocity fields corresponding to
+rigid body motions~\cite{pow-mir1987}.  A standard method to complete
+the double-layer potential is to introduce a Stokeslet and rotlet
+centered inside each interior body
 \begin{align}
@@
       \label{eqn:DLP}\\
-  \llambda_k &= \frac{1}{2\pi}\int_{\Gamma_k} \eeta(\yy) \, ds_\yy, 
+  \llambda_k &= \frac{1}{2\pi}\int_{\gamma_k} \eeta(\yy) \, ds_\yy, 
   \label{eqn:stokeslet} \\
-  \xi_k &= \frac{1}{2\pi}\int_{\Gamma_k} \yy^\perp \cdot \eeta(\yy)
+  \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
   \, ds_\yy.
@@
 \begin{align*}
-  \int_{\Gamma} \ff \cdot \nn \, ds_\yy = 0.
+  \int_{\bd\Omega} \ff \cdot \nn \, ds_\yy = 0.
 \end{align*}
 The result is a rank-one null space of~\eqref{eqn:completed_BIE} which
-is removed by adding the rank-one modification $\NN_0[\eeta](\xx) =
-\int_{\Gamma_0} (\nn(\xx) \otimes \nn(\yy))\nn(\yy) \, ds_\yy$, for $\xx
-\in \Gamma_0$.
+is removed by adding the rank-one modification 
+\begin{align}
+  \NN_0[\eeta](\xx) = \int_{\Gamma} 
+    (\nn(\xx) \otimes \nn(\yy))\nn(\yy) \, ds_\yy, \quad \xx \in \Gamma.
+\end{align}
 
@@
 There are several quantities besides the velocity that need to be
-comnputed.  First, the shear stress along $\gamma_k$ is required by the
-governing equations~\eqref{eqn:erosionModel}.  In addition, to study
+comnputed.  First, the governing equations~\eqref{eqn:erosionModel}
+require the shear stress along $\gamma_k$.  In addition, to study
 characteristics of the flow, the pressure and drag must also be

### 2017-09-05 fortran_code/stokesDriver.f

@@ -1,11 +1,10 @@
       program stokesDriver
       implicit real*8 (a-h,o-z)
 
-c      parameter (ninner = 4096)
       parameter (ninner = 128)
-      parameter (nbodies = 1)
+      parameter (nbodies = 2)
       parameter (nouter = 2**8)
-      parameter (ntargets = 40)
+      parameter (ntargets = 400)
       parameter (maxbodies = 10)
 
       dimension centerx(maxbodies),centery(maxbodies)
@@ -21,6 +20,7 @@ c      parameter (ninner = 4096)
       dimension utar(ntargets*ntargets)
       dimension vtar(ntargets*ntargets)
       dimension press_tar(ntargets*ntargets)
+      dimension vort_tar(ntargets*ntargets)
 
       pi = 4.d0*datan(1.d0)
       twopi = 2.d0*pi
@@ -28,21 +28,20 @@ c      parameter (ninner = 4096)
 
       centerx(1) = -0.0d0
       centery(1) = 0.0d0
-c      centerx(2) = 0.8d0
-      centerx(2) = 0.0d0
+      centerx(2) = 0.8d0
       centery(2) = -0.1d0
       radius(1) = 2.d-1
       radius(2) = 2.d-1
       phi(1) = 0.d0
       phi(2) = 0.d0
 
-      Nphi = 128
-      dphi = twopi/Nphi
-      open(unit=21,file='output/dragx.dat')
-      open(unit=22,file='output/dragy.dat')
+c      Nphi = 128
+c      dphi = twopi/Nphi
+c      open(unit=21,file='output/dragx.dat')
+c      open(unit=22,file='output/dragy.dat')
 
-      do kk = 1,Nphi
-        phi(1) = dble(kk-1)*dphi
+c      do kk = 1,Nphi
+c        phi(1) = dble(kk-1)*dphi
 
       do j = 1,nbodies
         do k = 1,ninner
@@ -50,10 +49,10 @@ c      centerx(2) = 0.8d0
           var_rad = radius(j)
           x((j-1)*ninner+k) = centerx(j) + var_rad*
      $          (dcos(phi(j))*dcos(theta) + 
-     $           dsin(phi(j))*2.d0*dsin(theta))
+     $           2.d0*dsin(phi(j))*dsin(theta))
           y((j-1)*ninner+k) = centery(j) + var_rad*
      $          (-dsin(phi(j))*dcos(theta) + 
[…]

### 2017-09-05 fortran_code/stokesSolver.f

@@ -276,6 +276,25 @@ c     generic boundary condition
       endif
 c     constant background flow on outer walls on no slip on obstacle
 
+      if (0 .eq. 1) then
+        do k = 1,nouter
+          rho2 = (xouter(k)-2.d0)**2.d0 + (youter(k)+2.d0)**2.d0
+          rhs(k) = ((youter(k)+2.d0)**2.d0 - (xouter(k)-2.d0)**2.d0)/
+     $        rho2**2.d0
+          rhs(k + nouter) = -2.d0*(xouter(k)-2.d0)*(youter(k)+2.d0)/
+     $        rho2**2.d0
+        enddo
+
+        do k = 1,ninner*nbodies
+          rho2 = (x(k)-2.d0)**2.d0 + (y(k)+2.d0)**2.d0
+          rhs(2*nouter + k) = ((y(k)+2.d0)**2.d0 - (x(k)-2.d0)**2.d0)/
+     $        rho2**2.d0
+          rhs(2*nouter + k + ninner) = -2.d0*(x(k)-2.d0)*(y(k)+2.d0)/
+     $        rho2**2.d0
+        enddo
+      endif
+
+
       do k = 1,nbodies
         rhs(2*nouter+2*ninner*nbodies+3*(k-1)+1) = 0.d0
         rhs(2*nouter+2*ninner*nbodies+3*(k-1)+2) = 0.d0
@@ -1664,7 +1683,6 @@ c     compute the deformation tensor on the boundary of the interface
 
       end
 
-
 c***********************************************************************
       subroutine computeVelocityPressureTargets(ninner,nbodies,nouter,
      $    x,y,den,ntargets,xtar,ytar,utar,vtar,press_tar)
@@ -1786,6 +1804,113 @@ c         stokeslet contribution
           utar(j) = utar(j) + rot*ry/rho2
           vtar(j) = vtar(j) - rot*rx/rho2
 c         rotlet contribution
+        enddo
+      enddo
+c     Add in contribution from Rotlets and Stokeslets
+
+
+      end
+
+c***********************************************************************
+      subroutine computeVorticityTargets(ninner,nbodies,nouter,
+     $    x,y,den,ntargets,xtar,ytar,vort_tar)
+c     Compute the vorticity at a set of target points xtar and ytar.
+c     Target points must be sufficiently far away from the each boundary since
+c     no near-singular integration is used.  It is just the vanilla trapezoid
+c     rule
[…]

### 2017-09-07 docs/methods/erosion_methods.tex
added QOI code for computing velocity, pressure, vorticity at target points

@@
 where $\cc_k$ is a point inside the $k^{th}$ body,  $\rr = \xx - \cc_k$,
-and $\rr^\perp = (r_2,-r_1)$.  Then, the solution of the Stokes
-equations with a Dirichlet boundary condition $\ff$ is
+and $\rr^\perp = (r_2,-r_1)$.  Then, any solution of the Stokes
+equations with a Dirichlet boundary condition $\ff$ can be written as
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Computing the Shear Stress, Pressure, and Drag} 
+\subsection{Computing the Shear Stress, Vorticity Pressure, and Drag} 
 \label{sec:qois}
 There are several quantities besides the velocity that need to be
-comnputed.  First, the governing equations~\eqref{eqn:erosionModel}
+computed.  First, the governing equations~\eqref{eqn:erosionModel}
 require the shear stress along $\gamma_k$.  In addition, to study
-characteristics of the flow, the pressure and drag must also be
-computed.  Once equation~\eqref{eqn:completed_DLP} is solved for the
+characteristics of the flow, the vorticity, pressure, and drag must also
+be computed.  Once equation~\eqref{eqn:completed_DLP} is solved for the
 density function, Stokeslets, and rotlets, all of these quantities can
@@
 \end{align}
-where $\ss$ is the unit tangent vector (Figure~\ref{fig:schematic}).  We
-note that for the Stokes equations, because of the no-slip boundary
-condition on the bodies, the shear stress is identical to the surface
-vorticity $\tau = u_y - v_x$.  However, we use
-equation~\eqref{eqn:shearStress} to compute the shear stress since the
-jump conditions resulting from the double-layer potential are
-known~\cite{qua-bir2014a}.  The velocity field of the completed
-double-layer potential~\eqref{eqn:completed_DLP} involves three terms:
-the double-layer potential $\DD$, the Stokeslets $S$, and the rotlets
-$R$.  To compute the shear stress, we first compute the deformation
-tensor $\ssigma = \frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of each of these
-terms individually.
+where $\ss$ and $\nn$ are the unit tangent and normal vectors,
+respectively (Figure~\ref{fig:schematic}).  We note that for the Stokes
+equations, because of the no-slip boundary condition on the bodies, the
+shear stress is identical to the surface vorticity $\tau = u_y - v_x$.
+However, we use equation~\eqref{eqn:shearStress} to compute the shear
+stress since the jump conditions resulting from the double-layer
+potential are known~\cite{qua-bir2014a}.  The velocity field of the
+completed double-layer potential~\eqref{eqn:completed_DLP} involves
+three terms: the double-layer potential $\DD$, the Stokeslets $S$, and
+the rotlets $R$.  To compute the shear stress, we first compute the
+deformation tensor $\ssigma = \frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of
+each of these terms individually.
 

### 2017-09-07 fortran_code/stokesDriver.f

@@ -1,8 +1,8 @@
       program stokesDriver
       implicit real*8 (a-h,o-z)
 
-      parameter (ninner = 4096)
-      parameter (nbodies = 2)
+      parameter (ninner = 1024)
+      parameter (nbodies = 3)
       parameter (nouter = 2**8)
       parameter (ntargets = 400)
       parameter (maxbodies = 10)
@@ -21,19 +21,24 @@
       dimension vtar(ntargets*ntargets)
       dimension press_tar(ntargets*ntargets)
       dimension vort_tar(ntargets*ntargets)
+      dimension iside(ntargets*ntargets)
+      dimension inear(ntargets*ntargets)
 
       pi = 4.d0*datan(1.d0)
       twopi = 2.d0*pi
       dtheta = twopi/dble(ninner)
 
-      centerx(1) = -0.0d0
       centery(1) = 0.0d0
       centerx(2) = 0.5d0
+      centerx(3) = -0.4d0
       centery(2) = -0.1d0
+      centery(3) = 0.1d0
       radius(1) = 2.d-1
-      radius(2) = 2.d-1
+      radius(2) = 1.d-1
+      radius(3) = 5.d-2
       phi(1) = 0.d0
       phi(2) = 0.d0
+      phi(3) = pi/4.d0
 
 c      Nphi = 128
 c      dphi = twopi/Nphi
@@ -95,13 +100,19 @@ c      enddo
 c     pass in number of points and x and y coordinates and return the
 c     density function on the boundary
 
+      call classifyPoints(ninner,nbodies,x,y,
+     $      ntargets*ntargets,xtar,ytar,iside,inear)
+c
+c      call computeVorticityTargets(ninner,nbodies,nouter,
+c     $      x,y,den,ntargets*ntargets,xtar,ytar,vort_tar)
+c
+c      call computeVelocityPressureTargets(ninner,nbodies,nouter,
+c     $    x,y,den,ntargets*ntargets,xtar,ytar,utar,vtar,press_tar)
+c
+      call computeQoiTargets(ninner,nbodies,nouter,x,y,den,
+     $  ntargets*ntargets,xtar,ytar,utar,vtar,press_tar,vort_tar)
 
-c      do k = 2*nouter+2*ninner + 1,2*nouter + 2*ninner + 3
-c        den(k) = 0.d0
-c      enddo
 
-      call computeVorticityTargets(ninner,nbodies,nouter,
[…]

### 2017-09-07 fortran_code/stokesSolver.f

@@ -1616,10 +1616,6 @@ c     Input x and y coordinates and the density function on the
 c     boundary and return the shear stress on the inner walls.  
       implicit real*8 (a-h,o-z)
 
-      parameter (nmax = 2**15)
-      parameter (maxbodies = 50)
-c     max points on the boundary of the obstacle      
-
       dimension x(ninner*nbodies),y(ninner*nbodies)
       dimension centerx(nbodies),centery(nbodies)
       dimension px(ninner*nbodies),py(ninner*nbodies)
@@ -1683,6 +1679,163 @@ c     compute the deformation tensor on the boundary of the interface
 
       end
 
+
+c***********************************************************************
+      subroutine computeQoiTargets(ninner,nbodies,nouter,
+     $    x,y,den,ntargets,xtar,ytar,utar,vtar,press_tar,vort_tar)
+c     Compute the velocity, pressure, and vorticity at a set of target 
+c     points xtar and ytar.  Target points must be sufficiently far away 
+c     from the each boundary since no near-singular integration is used.  
+c     It is just the vanilla trapezoid rule, but will assign a value of
+c     zero for points that are inside or close to the boundary
+      implicit real*8 (a-h,o-z)
+
+      dimension x(ninner*nbodies),y(ninner*nbodies)
+      dimension px(ninner*nbodies),py(ninner*nbodies)
+      dimension cur(ninner*nbodies),speed(ninner*nbodies)
+      dimension centerx(nbodies),centery(nbodies)
+      dimension xouter(nouter),youter(nouter)
+c     x and y coordinates of confining wall
+      dimension px0(nouter), py0(nouter)
+c     x and y coordinates of the normal of the confining wall
+      dimension cur0(nouter), speed0(nouter)
+c     Jacobian and curvature of the confining wall
+      dimension den(2*nouter + 2*ninner*nbodies + 3*nbodies)
+      dimension denx(max(ninner,nouter)),deny(max(ninner,nouter))
+
+      dimension xtar(ntargets),ytar(ntargets)
+      dimension utar(ntargets),vtar(ntargets)
+      dimension press_tar(ntargets)
+      dimension vort_tar(ntargets)
+
+      dimension iside(ntargets)
[…]

### 2017-09-21 docs/methods/erosion_methods.tex
worked on Section 2.2 of methods paper

@@
   \quad \text{and} \quad
-  R[\xi_k,\cc_k] = \frac{\rr^\perp}{\rho^2}\xi_k,
+  R[\xi_k,\cc_k] = \frac{\rr_k^\perp}{\rho^2}\xi_k,
   \label{eqn:stokeslet_rotlet}
 \end{align}
-where $\cc_k$ is a point inside the $k^{th}$ body,  $\rr = \xx - \cc_k$,
-and $\rr^\perp = (r_2,-r_1)$.  Then, any solution of the Stokes
-equations with a Dirichlet boundary condition $\ff$ can be written as
+where  $\rr = \xx - \cc_k$, $\cc_k$ is a point inside the $k^{th}$ body,
+$\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then, any solution of
+the Stokes equations with a Dirichlet boundary condition $\ff$ can be
+written as
 \begin{align}
@@
       \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
-      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Gamma, 
+      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \bd\Omega, 
       \label{eqn:DLP}\\
@@
   \NN_0[\eeta](\xx) = \int_{\Gamma} 
-    (\nn(\xx) \otimes \nn(\yy))\nn(\yy) \, ds_\yy, \quad \xx \in \Gamma.
+    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy, \quad \xx \in \Gamma.
 \end{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Computing the Shear Stress, Vorticity Pressure, and Drag} 
+\subsection{Computing the Shear Stress, Vorticity, Pressure, and Drag} 
 \label{sec:qois}
@@
 \subsubsection{Shear Stress}
-\todo[inline]{check all signs in this section.  Fortran code assumes an
-inward pointing normal}
 The shear stress is defined by
-\begin{align}
-  \tau = \left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss,
-  \label{eqn:shearStress}
-\end{align}
+\begin{align*}
+  \tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss,
+\end{align*}
 where $\ss$ and $\nn$ are the unit tangent and normal vectors,
-respectively (Figure~\ref{fig:schematic}).  We note that for the Stokes
-equations, because of the no-slip boundary condition on the bodies, the
-shear stress is identical to the surface vorticity $\tau = u_y - v_x$.
-However, we use equation~\eqref{eqn:shearStress} to compute the shear
-stress since the jump conditions resulting from the double-layer
-potential are known~\cite{qua-bir2014a}.  The velocity field of the
+respectively (Figure~\ref{fig:schematic}).  The velocity field of the
 completed double-layer potential~\eqref{eqn:completed_DLP} involves
 three terms: the double-layer potential $\DD$, the Stokeslets $S$, and
-the rotlets $R$.  To compute the shear stress, we first compute the
-deformation tensor $\ssigma = \frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of
-each of these terms individually.
+the rotlets $R$.  We first compute the deformation tensor $\ssigma =
+\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ for each of these terms
+individually.
 
@@
 \end{equation}
-We are interested in the deformation tensor at boundary points $\xx_0
-\in \bd\Omega$, and this requires an expression for the jump in
-$\ssigma^\DD(\xx)$ as $\xx \rightarrow \xx_0 \in \Gamma$.  The limiting
-value is given by~\cite{qua-bir2014a}
+We require the deformation tensor on $\bd\Omega$, and this requires
+taking the limit of equation~\eqref{eqn:shearStressDLP} when $\xx$ tends
+to $\xx_0 \in \bd\Omega$.  This limiting value is given
+by~\cite{qua-bir2014a}
 \begin{align*}
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}\sigma_\DD(\xx) =
-  J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) = 
-  \frac{1}{2}\pderiv{\eeta}{\ss} \cdot \ss
+  J[\eeta](\xx_0) + \ssigma^\DD(\xx_0), \quad \xx_0 \in \bd\Omega,
+\end{align*} 
+where
+\begin{align*}
+  J[\eeta](\xx_0) = \frac{1}{2}\pderiv{\eeta}{\ss} \cdot \ss
   \left[ \begin{array}{cc}
     s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
-  \end{array}\right] + \ssigma^\DD(\xx_0), \quad \xx_0 \in \Gamma.
+  \end{array}\right].
 \end{align*}
-
 The deformation tensor due to the Stokeslets and
@@
 \begin{align*}
-  \ssigma^S(\xx_0) &= \frac{\rr \cdot \llambda}{4\pi\rho^2} \left(
+  \ssigma^S(\xx_0) &= \sum_{k=1}^{M}
+    \frac{\rr \cdot \llambda_k}{4\pi\rho^2} \left(
     \II - \frac{2}{\rho^2} \rr \otimes \rr \right),  \\
-  \ssigma^R(\xx_0) &= -\frac{\xi}{\rho^4} \left(\rr \otimes \rr^\perp + 
-                           \rr^\perp \otimes \rr \right).
+  \ssigma^R(\xx_0) &= \sum_{k=1}^M
+    -\frac{\xi_k}{\rho^4} \left(\rr \otimes \rr^\perp + 
+    \rr^\perp \otimes \rr \right),
 \end{align*}
-Now that the deformation tensor of each component of the completed
-double-layer potential are computed, the shear stress at $\xx_0 \in
-\Gamma$ can be written as
+where $\rr = \xx - \cc_k$, $\cc_k$ is the point chosen inside body
+$\gamma_k$, and $\rho = \|\rr_k\|$.  Now that the deformation tensor of
+each component of the completed double-layer potential are computed, the
+shear stress at $\xx_0 \in \bd\Omega$ can be computed as
 \begin{align*}
-  \tau = \left(J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) + 
+  \tau = -2 \left(J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) + 
     \ssigma^S(\xx_0) + \ssigma^R(\xx_0)\right) \nn \cdot \ss.
@@
 
+\subsubsection{Vorticity}
+For the Stokes equations, on boundaries that have a no-slip boundary
+condition, the shear stress is equivalent to the vorticity $w = v_x -
+u_y$.  Therefore, to compute the $w(\xx)$ for $\xx \in
+\overline{\Omega}$, we only need to compute $w(\xx)$ for $\xx\Omega$.
+As we did for the shear stress, we compute the vorticity due to the
+double-layer potential, Stokeslets, and rotlets individually.  The
+vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at
+$\xx \in \Omega$ is
+\begin{align}
+  w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
+    \frac{(\xx \cdot \eeta)(\xx \cdot \nn^\perp) + 
+    (\xx \cdot \nn)(\xx \cdot \eeta)}{\rho^4}ds_{\yy}.
+  \label{eqn:vorticityDLP}
+\end{align}
+The vorticity due to the Stokeslet is
+\begin{align*}
+  w^S(\xx) = -\frac{1}{\pi} \sum_{k=1}^{M} 
+    \frac{\rr \cdot \llambda_k^\perp}{\rho^2},
+\end{align*}
+and the vorticity of a rotlet is zero.  Therefore, once the density
+function and Stokeslets are computed, the vorticity at $\xx \in \Omega$
+is
+\begin{align*}
+  w(\xx) = w^\DD(\xx) + w^S(\xx).
+\end{align*}
+
 \subsubsection{Pressure}
-\todo[inline]{check all signs in this section.  Fortran code assumes an
-inward pointing normal}
-To compute the pressure at $\xx_0 \in \Gamma$, we follow the same
-procedure used for the shear stress.  In particular, we compute the
-pressure due to each of the three terms in the completed double-layer
-potential~\eqref{eqn:completed_DLP}.  They are given by
+To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
+same procedure used for the shear stress.  We first find the pressure of
+the double-layer potential for $\xx \in \Omega$, and the find the jump
+that results from taking the limit of $\xx$ to $\xx_0 \in \Gamma$.
+Then, we compute the pressure due to the Stokestlet and rotlet
+terms~\eqref{eqn:stokeslet_rotlet}.   For $\xx \in \Omega$,
+the pressure is
+\begin{align}
+  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
+    \nn \cdot \eeta(\yy) \,ds_\yy.
+  \label{eqn:pressureDLP}
+\end{align}
+To compute the pressure at $\xx_0 \in \bd\Omega$, we must take the limit
+of equation~\eqref{eqn:pressureDLP} when $\xx$ tends to $\xx_0$.  The
+limiting value is given by~\cite{qua-bir2014a}
 \begin{align*}
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
-  -\pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0),
-\end{align*}
-where
-\begin{align*}
-  p^\DD(\xx) = -\frac{1}{\pi}\int_{\Gamma} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot \eeta(\yy) \,ds_\yy.
+    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
 \end{align*}
 The pressure due to the Stokeslets is
-\begin{align}
+\begin{align*}
   p^S(\xx_0) = \frac{\rr \cdot \llambda}{2\pi\rho^2},
-  \label{eqn:pressureDLP}
-\end{align}
-and the pressure of a rotlet is zero.  Therefore, once the density
-function and Stokeslets are computed, the pressure at a point $\xx_0 \in
-\Gamma$ is
+\end{align*}
+and the pressure due to the rotlets is zero.  Therefore, once the
+density function and Stokeslets are computed, the pressure at a point
+$\xx_0 \in \bd\Omega$ is
 \begin{align*}
-  p(\xx_0) = -\pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0) + 
-              \frac{\rr \cdot \llambda}{2\pi\rho^2}.
+  p(\xx_0) = \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0) + 
+              p^{S}(\xx_0).
 \end{align*}
@@
 \subsubsection{Drag}
-\todo[inline]{check all signs in this section.  Fortran code assumes an
-inward pointing normal}
+\todo[inline]{check all signs in this section.  Fortran code assumes a
+normal pointing into the eroding body and a tangent vector that
+corresponds to a couterclockwise parameterization}
 Finally, with the pressure and shear stress, the drag on a single body
-with boundary $\Gamma_k$ is
+with boundary $\gamma_k$ is
 \begin{align*}
-  F_D = \int_{\Gamma_k} (-p \nn + \tau \ss)\,ds.
+  F_D = \int_{\gamma_k} (-p \nn + \tau \ss)\,ds.
 \end{align*}
@@
 double-layer potential velocity field~\eqref{eqn:velocityDLP}, the shear
-stress~\eqref{eqn:shearStressDLP}, and the
-pressure~\eqref{eqn:pressureDLP}.  By using carefully choosing the
-quadrature rules, high-order solutions can be computed.  For all the
+stress~\eqref{eqn:shearStressDLP}, vorticity~\eqref{eqn:vorticityDLP},
+and the pressure~\eqref{eqn:pressureDLP}.  By using carefully choosing
+the quadrature rules, high-order solutions can be computed.  For all the
 integrals, the trapezoid rule is used since it achieves spectral
@@
 \begin{align*}
-  \lim_{\substack{\yy \rightarrow \xx \\ \yy \in \Gamma}} D(\xx,\yy) = 
+  \lim_{\substack{\yy \rightarrow \xx \\ \yy \in \bd\Omega}} D(\xx,\yy) = 
   -\frac{\kappa(\xx)}{2\pi}\ss \otimes \ss,
 \end{align*}
-where $\kappa(\xx)$ is the curvature of $\Gamma$ at $\xx$.  By using
+where $\kappa(\xx)$ is the curvature of $\bd\Omega$ at $\xx$.  By using
 this limiting term in when applying the trapezoid rule, spectral
@@
 \begin{align*}
-  p^\DD(\xx) = -\frac{1}{\pi}\int_{\Gamma} \frac{1}{\rho^2}
+  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 

### 2017-09-21 docs/methods/erosion_methods.tex
starting to work on numerical methods section

@@
 rigid body motions~\cite{pow-mir1987}.  A standard method to complete
-the double-layer potential is to introduce a Stokeslet and rotlet
+the double-layer potential is to introduce a Stokeslets and rotlets
 centered inside each interior body
@@
   R[\xi_k,\cc_k] = \frac{\rr_k^\perp}{\rho^2}\xi_k, 
+  \quad k=1,\ldots,M
   \label{eqn:stokeslet_rotlet}
@@
 \section{Numerical Methods\label{s:method}} 
+There are several 
 We discretize the second-kind integral equation~\eqref{eqn:DLP} using a
@@
 \todo[inline]{Describe the upcoming subsections better}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spatial Discretization}
+\todo[inline]{compute all derivatives in spectral space}
 

### 2017-09-22 docs/methods/erosion_methods.tex
worked a bit more on the numerics section

@@
   \llambda_k &= \frac{1}{2\pi}\int_{\gamma_k} \eeta(\yy) \, ds_\yy,
+  \quad k=1,\ldots,M
   \label{eqn:stokeslet} \\
   \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
-  \, ds_\yy.
+  \, ds_\yy, \quad k=1,\ldots,M.
   \label{eqn:rotlet}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Computing the Shear Stress, Vorticity, Pressure, and Drag} 
+\subsection{Computing Quantities of Interest}
 \label{sec:qois}
@@
 require the shear stress along $\gamma_k$.  In addition, to study
-characteristics of the flow, the vorticity, pressure, and drag must also
-be computed.  Once equation~\eqref{eqn:completed_DLP} is solved for the
-density function, Stokeslets, and rotlets, all of these quantities can
-be computed by evaluating layer potentials that we now derive.
+characteristics of the flow, the vorticity, pressure, and drag, and
+resistivity will also be computed.  Once
+equation~\eqref{eqn:completed_DLP} is solved for the density function,
+Stokeslets, and rotlets, all of these quantities can be computed by
+evaluating layer potentials that we now derive.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Shear Stress}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Vorticity}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Pressure}
@@
 limiting value is given by~\cite{qua-bir2014a}
-\begin{align*}
+\begin{align}
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
     \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
-\end{align*}
+  \label{eqn:pressureDLPdiag}
+\end{align}
 The pressure due to the Stokeslets is
 \begin{align*}
-  p^S(\xx_0) = \frac{\rr \cdot \llambda}{2\pi\rho^2},
+  p^S(\xx_0) = \sum_{k=1}^{M}\frac{\rr \cdot \llambda_k}{2\pi\rho^2},
 \end{align*}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Drag}
@@
 with boundary $\gamma_k$ is
+\begin{align}
+  F_D = \int_{\gamma_k} (-p \nn + \tau \ss)\,ds.
+  \label{eqn:drag}
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Resistivity}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Methods\label{s:method}} 
+There are three main numerical methods that need to developed: the
+boundary integral equation solver~\eqref{eqn:completed_BIE}, computing
+the quantities of interest in Section~\ref{sec:qois}, and updating the
+shape of the eroding bodies with equation~\eqref{eqn:bodyEvolution}.  In
+order to compute stable simulations with long time horizons, we use
+numerical methods that achieve spectral accuracy in space, second-order
+in time, and maintain an equispaced discretization of the bodies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spatial Discretization}
+Each body will be represented with $N_\iin$ points.  Because
+the boundary of each body is closed, it can be represented with spectral
+accuracy as a Fourier series
 \begin{align*}
-  F_D = \int_{\gamma_k} (-p \nn + \tau \ss)\,ds.
+  \xx^k(\theta) = \sum_{j = -N/2}^{N/2-1} \hat{x}_j^k e^{ij\theta}.
+\end{align*}
+There are several instances where derivatives of the shape must be
+taken, and this is done with spectral accuracy by differentiating the
+Fourier series term-by-term
+\begin{align*}
+  \frac{d\xx^k(\theta)}{d\theta} = 
+      \sum_{j = -N/2}^{N/2-1} ij\hat{x}_j^k e^{ij\theta}.
 \end{align*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Methods\label{s:method}} 
-There are several 
-We discretize the second-kind integral equation~\eqref{eqn:DLP} using a
-Nystr\"om method.  The equations for the
-Stokeslets~\eqref{eqn:stokeslet} and rotlets~\eqref{eqn:rotlet} are
-approximated with the trapezoid rule.  By applying a quadrature method,
-this results in a dense linear system which we solve with fast multipole
-accelerated GMRES.  Because of the second-kind nature of the integral
-equation, the number of GMRES iterations is mesh independent (but not
-geometry independent), and the overall complexity of the Stokes solver
-is proportional to the cost of a single matrix-vector multiplication.
-The shear stress, pressure, and drag must also be computed using
-quadrature, and this can be interpreted as a post-processing step once
-the density function, Stokeslets, and rotlets are computed.  All the
-quadrature methods are described in Section~\ref{sec:quadrature}
+\subsection{Quadrature} 
+There are several integrals that need to be evaluated.  This includes
+the double-layer potential for target points both
+off~\eqref{eqn:velocityDLP} and on~\eqref{eqn:DLP} the $\bd\Omega$, the
+shear stress~\eqref{eqn:shearStressDLP}, the
+vorticity~\eqref{eqn:vorticityDLP}, the pressure both
+off~\eqref{eqn:pressureDLP} and on~\eqref{eqn:pressureDLPdiag} the
+boundary, the drag~\eqref{eqn:drag}, and the resistivity.  Most of the
+integrands involved in these calculations are both smooth and periodic,
+and the suitably adjusted trapezoid rule will result in spectral
+accuracy~\cite{tre-wei2014}.
+
+To numerically solve the completed double-layer
+potential~\eqref{eqn:completed_BIE}, we start by discretizing each
+interior body $\gamma_k$ with $N_\iin$ points, and the outer geometry
+$\Gamma$ with $N_\out$ points.  We let $N = MN_\iin + N_\out$ be the
+total number of discretization points, and we apply the trapezoid rule
+which results in the linear system
+\begin{align*}
+  \ff(\xx_i^k) = \sum_{\ell = 1}^{M}\sum_{j=1}^{N} 
+    K(\xx_i^k,\xx_j^\ell) \eeta(\xx_j^\ell) 
+      \Delta s_{j}^{\ell}, \quad i=1,\ldots,N, \: k=1\ldots,M
+\end{align*}
+where $\Delta s_j^\ell$ is the arclength term of $\gamma_\ell$ at
+$\xx_j^\ell \in \gamma_\ell$, or the corresponding term if $\xx_k \in
+\Gamma$, and
+\begin{align*}
+  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
+      \frac{\rr \otimes \rr}{\rho^2},
+\end{align*}
+where $\rr = \xx - \yy$, and $\rho = \|\rr\|$, is the kernel of the
+double-layer potential.  The Stokeslet~\eqref{eqn:stokeslet} and
+rotlet~\eqref{eqn:rotlet} strengths are also discretized with the
+trapezoid rule
+\begin{align*}
+  \llambda_k &= \sum_{k=1}^{N_\iin} \eeta(\xx_k) 
+    \Delta s_{k} \quad \text{and} \quad
+  \mu_k = \sum_{k=1}^{N_\iin} \xx_k^\perp \cdot
+    \eeta(\xx_k) \Delta s_{k}.
+\end{align*}
+\todo[inline]{need to pick a good notation for the indices}
+
+By applying a quadrature method, this results in a dense linear system
+which we solve with fast multipole accelerated GMRES.  Because of the
+second-kind nature of the integral equation, the number of GMRES
+iterations is mesh independent (but not geometry independent), and the
+overall complexity of the Stokes solver is proportional to the cost of a
+single matrix-vector multiplication.  The shear stress, pressure, and
+drag must also be computed using quadrature, and this can be interpreted
+as a post-processing step once the density function, Stokeslets, and
+rotlets are computed.  All the quadrature methods are described in
+Section~\ref{sec:quadrature}
 
@@
 
-\todo[inline]{Describe the upcoming subsections better}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Spatial Discretization}
-\todo[inline]{compute all derivatives in spectral space}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quadrature} 
 \label{sec:quadrature}

### 2017-09-27 docs/methods/erosion_methods.tex
In methods paper, corrected sign in the erosion law (since n points inwards)
Made some small changes to the methods tex file.

@@
   \item Avoiding stokes paradox
-  \item \thL formulation
+  \item {\thL} formulation
   \item Regularization
@@
 velocity} \\
-\dot{\xx}(t) = -|\tau| \nn, &\hspace{20pt} \xx \in \gamma,
+\dot{\xx}(t) = \abs{\tau} \nn, &\hspace{20pt} \xx \in \gamma,
 &&\mbox{erosion model},
@@
 \begin{align}
-  \dot{\xx}(t) = -|\tau| \nn.
+  \dot{\xx}(t) = \abs{\tau} \nn.
   \label{eqn:bodyEvolution}
@@
 bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
-eliminate tangling and stretching of the mesh, we use a \thL
+eliminate tangling and stretching of the mesh, we use a {\thL}
 formulation~\cite{hou-low-she1994} which is described in
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\thL Formulation} 
+\subsection{{\thL} Formulation} 
 \label{sec:thetaL}
@@
 \vsp{2}
-To handle boundary evolution, we use the \thL    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems.
+To handle boundary evolution, we use the {\thL}    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems.
 Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).
-
-\todo[inline]{BRYAN: Can we use these conventions throughout the paper?}
 
@@
 \begin{equation}
-\pderiv{\xx}{t} = |\tau| \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
+\dot{\xx}(t) = \abs{\tau} \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
 \end{equation}
 The curvature term acts to smooth bodies that have high-frequency oscillations.
+
+Simple form for my talk
+\begin{equation}
+\dot{\xx}(t) = \abs{\tau} \nn + \eps \kappa
+\end{equation}
 

### 2017-10-02 docs/methods/erosion_methods.tex
worked on numerics section of methods paper

@@
 \end{itemize}
-
-\cite{moo-ris-chi-zha-she2013}
 
@@
 \todo[inline]{Describe the erosion model and its justification}
+\cite{moo-ris-chi-zha-she2013}
 
@@
 \section{Numerical Methods\label{s:method}} 
-There are three main numerical methods that need to developed: the
+There are three main numerical methods that need to be developed:~the
 boundary integral equation solver~\eqref{eqn:completed_BIE}, computing
@@
 \subsection{Spatial Discretization}
-Each body will be represented with $N_\iin$ points.  Because
-the boundary of each body is closed, it can be represented with spectral
-accuracy as a Fourier series
+Each body will be represented with $N_\iin$ points.  The boundary is
+represented with the Fourier series
 \begin{align*}
@@
 \end{align*}
-There are several instances where derivatives of the shape must be
-taken, and this is done with spectral accuracy by differentiating the
-Fourier series term-by-term
+Derivatives of the shape must be taken which is easily done by
+differentiating the Fourier series term-by-term
 \begin{align*}
@@
 \subsection{Quadrature} 
-There are several integrals that need to be evaluated.  This includes
-the double-layer potential for target points both
-off~\eqref{eqn:velocityDLP} and on~\eqref{eqn:DLP} the $\bd\Omega$, the
-shear stress~\eqref{eqn:shearStressDLP}, the
-vorticity~\eqref{eqn:vorticityDLP}, the pressure both
-off~\eqref{eqn:pressureDLP} and on~\eqref{eqn:pressureDLPdiag} the
-boundary, the drag~\eqref{eqn:drag}, and the resistivity.  Most of the
-integrands involved in these calculations are both smooth and periodic,
-and the suitably adjusted trapezoid rule will result in spectral
-accuracy~\cite{tre-wei2014}.
+Integrals that need to be approximated are the double-layer potential
+for target points both off the boundary~\eqref{eqn:velocityDLP} and on
+the boundary~\eqref{eqn:DLP}, the shear
+stress~\eqref{eqn:shearStressDLP}, the
+vorticity~\eqref{eqn:vorticityDLP}, the pressure both off the
+boundary~\eqref{eqn:pressureDLP} and on the
+boundary~\eqref{eqn:pressureDLPdiag}, the drag~\eqref{eqn:drag}, and the
+resistivity.  The integrands of each of these integrals, except for the
+resistivity, are smooth and periodic.  Under this condition the
+trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.
+However, before the trapezoid rule can be applied, singularity
+subtraction and odd-even integration~\cite{sid-isr1988} method must be
+used.
 
-To numerically solve the completed double-layer
+\subsubsection{Velocity}
+To numerically evaluate the completed double-layer
 potential~\eqref{eqn:completed_BIE}, we start by discretizing each
-interior body $\gamma_k$ with $N_\iin$ points, and the outer geometry
-$\Gamma$ with $N_\out$ points.  We let $N = MN_\iin + N_\out$ be the
-total number of discretization points, and we apply the trapezoid rule
-which results in the linear system
-\begin{align*}
-  \ff(\xx_i^k) = \sum_{\ell = 1}^{M}\sum_{j=1}^{N} 
+interior body $\gamma_k$ with $N_\iin$ points, the outer geometry
+$\Gamma$ with $N_\out$ points, and define $N = MN_\iin + N_\out$ to be
+the total number of discretization points.  The double-layer potential
+in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
+\begin{align}
+  \DD[\eeta](\xx_i^k) = \sum_{\ell = 1}^{M}\sum_{j=1}^{N} 
     K(\xx_i^k,\xx_j^\ell) \eeta(\xx_j^\ell) 
-      \Delta s_{j}^{\ell}, \quad i=1,\ldots,N, \: k=1\ldots,M
-\end{align*}
+      \Delta s_{j}^{\ell}, \quad i=1,\ldots,N, \: k=1\ldots,M,
+  \label{eqn:trapDLP}
+\end{align}
 where $\Delta s_j^\ell$ is the arclength term of $\gamma_\ell$ at
@@
 \end{align*}
-where $\rr = \xx - \yy$, and $\rho = \|\rr\|$, is the kernel of the
-double-layer potential.  The Stokeslet~\eqref{eqn:stokeslet} and
+where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the
+double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is
+replaced with the limiting value of the double-layer potential
+\begin{align*}
+  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)),
+\end{align*}
+where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
+vector at $\xx \in \bd\Omega$.  The Stokeslet~\eqref{eqn:stokeslet} and
 rotlet~\eqref{eqn:rotlet} strengths are also discretized with the
-trapezoid rule
-\begin{align*}
-  \llambda_k &= \sum_{k=1}^{N_\iin} \eeta(\xx_k) 
-    \Delta s_{k} \quad \text{and} \quad
-  \mu_k = \sum_{k=1}^{N_\iin} \xx_k^\perp \cdot
-    \eeta(\xx_k) \Delta s_{k}.
-\end{align*}
-\todo[inline]{need to pick a good notation for the indices}
+trapezoid rule, and the resulting discretization
+of~\eqref{eqn:completed_BIE} is
+\begin{equation}
+  \label{eqn:completed_BIE_discretized}
+  \begin{aligned}
+    \ff(\xx_i^k) &= -\frac{1}{2}\ssigma(\xx_i^k) + 
+      \sum_{\ell = 1}^{M}\sum_{j=1}^{N} 
+      K(\xx_i^k,\xx_j^\ell) \eeta(\xx_j^\ell) \Delta s_{j}^{\ell} +
+      \sum_{\ell=1}^M S[\llambda_k,\cc_k](\xx_i^k) +
+      \sum_{\ell=1}^M R[\xi_k,\cc_k](\xx_i^k), \\
+    \llambda_k &= \sum_{i=1}^{N_\iin} \eeta(\xx_i^k) 
+      \Delta s_i^k \\ 
+    \mu_k &= \sum_{i=1}^{N_\iin} {(\xx_i^k)}^\perp \cdot
+      \eeta(\xx_i^k) \Delta s_i^k,
+  \end{aligned}
+\end{equation}
+for $i=1,\ldots,N$, $k=1,\ldots,M$.
 
-By applying a quadrature method, this results in a dense linear system
-which we solve with fast multipole accelerated GMRES.  Because of the
-second-kind nature of the integral equation, the number of GMRES
-iterations is mesh independent (but not geometry independent), and the
-overall complexity of the Stokes solver is proportional to the cost of a
-single matrix-vector multiplication.  The shear stress, pressure, and
-drag must also be computed using quadrature, and this can be interpreted
-as a post-processing step once the density function, Stokeslets, and
-rotlets are computed.  All the quadrature methods are described in
-Section~\ref{sec:quadrature}
+The dense linear system~\eqref{eqn:completed_BIE_discretized} is solved
+iteratively with GMRES.  The most expensive part is computing the
+double sum for all target and source points.  A direct summation would
+require $\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$ by
+using the Fast Mutlipole method for the Stokes double-layer
+potential~\cite{gre-rok1987,rac-???} \todo[inline]{sent email to Manas
+asking about this}.  Since we are discretizing a second-kind integral
+equation, the number of GMRES iterations is bounded independent of
+$N$~\cite{cam-ips-kel-mey-xue1996}, and the overall complexity for
+solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
+
+\subsubsection{Shear Stress}
+In our erosion model, the shear stress must be computed which requires
+evaulating the layer potential~\eqref{eqn:shearStressDLP}.  In our
+implementation, this calculation is done directly which requires
+$\bigO(N^2)$ operations.  This complexity could be reduced with
+the kernel-independent FMM~\cite{yin-bir-zor2004}.  However, since this
+calculation is only computed once per time step, unlike the velocity
+double-layer potential that must be evaluated at each GMRES iteration.
+
+\subsubsection{Vorticity}
+
+\subsubsection{Pressure}
+
+\subsubsection{Drag}
+
+\subsubsection{Resistivity}
+
+The shear stress, pressure, and drag must also be computed using
+quadrature, and this can be interpreted as a post-processing step once
+the density function, Stokeslets, and rotlets are computed.  All the
+quadrature methods are described in Section~\ref{sec:quadrature}
 
@@
 
-\label{sec:quadrature}
-There are several integrals that we need to compute including the
-double-layer potential velocity field~\eqref{eqn:velocityDLP}, the shear
-stress~\eqref{eqn:shearStressDLP}, vorticity~\eqref{eqn:vorticityDLP},
-and the pressure~\eqref{eqn:pressureDLP}.  By using carefully choosing
-the quadrature rules, high-order solutions can be computed.  For all the
-integrals, the trapezoid rule is used since it achieves spectral
-accuracy for smooth periodic functions.  However, care must be taken
-when the source point and target points coincide.
-
-For the velocity field, the kernel of the integral operator
-\begin{align*}
-  D(\xx,\yy) = \frac{\rr \cdot \nn}{\rho^2} 
-               \frac{\rr \otimes \rr}{\rho^2}
-\end{align*}
-has a removable singularity when $\xx = \yy$.  In particular
-\begin{align*}
-  \lim_{\substack{\yy \rightarrow \xx \\ \yy \in \bd\Omega}} D(\xx,\yy) = 
-  -\frac{\kappa(\xx)}{2\pi}\ss \otimes \ss,
-\end{align*}
-where $\kappa(\xx)$ is the curvature of $\bd\Omega$ at $\xx$.  By using
-this limiting term in when applying the trapezoid rule, spectral
-accuracy is achieved because of the smoothness and periodicity of the
-integrand~\cite{tre-wei2014}.
-
 For the shear stress and the pressure, we will use odd-even integration
 which achieves spectral accuracy if the integrand is no stronger than
-$\mathcal{O}(\rho^{-1})$.  Since both these integrands are too strong,
-the singularity must be weakened.  This can be done by adding a constant
+$\bigO(\rho^{-1})$.  Since both these integrands are too strong, the
+singularity must be weakened.  This can be done by adding a constant
 density function which has no effect on the shear stress and
@@
 \end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fast Summation} 
-The majority of the computational cost comes from evaluating the the
-double-layer potential $\mathcal{D}$ in equation~\eqref{eqn:DLP}.  This
-layer potential can be efficiently evaluated using a fast summation
-method such as the Fast Multipole Method
-(FMM)~\cite{gre-rok1987}\footnote{The FMM for the Stokes double-layer
-poetntial was supplied by Manas Rachh.}.  By using the
-FMM,~\eqref{eqn:completed_BIE} can be solved with $\mathcal{O}(N)$
-operations, where $N$ is the total number of discretization points.
-
-In our erosion model, the shear stress must be computed which requires
-evaulating the layer potential~\eqref{eqn:shearStressDLP}.  In our
-implementation, this calculation is done directly which requires
-$\mathcal{O}(N^2)$ operations.  This complexity could be reduced with
-the kernel-independent FMM~\cite{yin-bir-zor2004}.  However, since this
-calculation is only computed once per time step, unlike the velocity
-double-layer potential that must be evaluated at each GMRES iteration.
 

### 2017-10-07 julia/thetalen.jl
Took debugging print lines out of thetalne.jl

@@ -74,13 +74,6 @@ function advance_theta!(thlen2::ThetaLenType, thlen1::ThetaLenType, thlen0::Thet
 	alpha = getalpha(endof(theta1))
 	# The function that enters the sigmas of the Guassian filter.
 	lenfun(len::Float64) = abs(len)^(-2)*cdfscale(abs(len))
-	
-	println("len1 = ", len1)
-	println("len2 = ", len2)
-	println("lenfun(len1) = ", lenfun(len1))
-	println("lenfun(len2) = ", lenfun(len2))
-	println()
-
 	# The first value used in the Gaussian filter.
 	sig1 = sqrt( lenfun(len1) + lenfun(len2) )
 	sig1 *= 2*pi*sqrt(epsilon*dt)

### 2017-10-08 docs/methods/erosion_methods.tex
fixed merge conflict
worked on methods paper

@@
 where $\nn$ is the outward unit normal vector which points away from the
-fluid.  The outer wall is formed by rounding off the corners of $[-3,3]
-\times [-1,1]$, and we enforce the Hagen-Poiseuille flow
+fluid, and $\mu$ is the fluid viscosity.  The outer wall is formed by
+rounding off the corners of $[-3,3] \times [-1,1]$, and we enforce the
+Hagen-Poiseuille flow
 \begin{align*}
@@
     geometry.  On the outer geometry $\Gamma$, a pipe flow is imposed.
-    The bodies are eroded according to the shear stress applied by the
-    Stokesian fluid.  Finally, the bodies are constrained to the middle
-    third of the channel that is located between the dashed lines.}
+    The bodies are eroded at a rate that is proportional to the
+    magnitude of the shear stress applied by the Stokesian fluid.  The
+    bodies are constrained to the middle third of the channel that is
+    located between the dashed lines.}
 \end{figure}
@@
 \label{sec:bies}
-Here we focus on solving the incompressible Stokes equations with
-Dirichlet boundary conditions
+Here we describe a boundary integral equation for the governing
+equations.   This requires solving the incompressible Stokes equations
+with Dirichlet boundary conditions 
 \begin{alignat*}{3}
@@
 \end{alignat*}
-The viscosity $\mu$ sets the time scale, and we will assume that
-$\mu=1$.  We start by defining the double-layer potential, which is the
-convolution of the stresslet with a function $\eeta:\bd\Omega
-\rightarrow \RR^2$,
+and also computing several quantities of interest, including the shear
+stress.  The viscosity $\mu$ sets the time scale, and we will assume
+that $\mu=1$.  We start by defining the double-layer potential, which is
+the convolution of the stresslet with a density function
+$\eeta:\bd\Omega \rightarrow \RR^2$,
 \begin{align}
@@
 normal at $\yy$.  For any density function $\eeta$, the double-layer
-potential satisfies the incompressible Stokes equations, but the
-double-layer potential can not capture velocity fields corresponding to
-rigid body motions~\cite{pow-mir1987}.  A standard method to complete
-the double-layer potential is to introduce a Stokeslets and rotlets
-centered inside each interior body
+potential satisfies the incompressible Stokes equations, but it can not
+capture velocity fields corresponding to rigid body
+motions~\cite{pow-mir1987}.  A standard method to remove this rank
+deficiency is to complement the double-layer potential with a Stokeslets
+and rotlets centered inside each interior body
 \begin{align}
@@
   R[\xi_k,\cc_k] = \frac{\rr_k^\perp}{\rho^2}\xi_k, 
-  \quad k=1,\ldots,M
+  \quad k=1,\ldots,M,
   \label{eqn:stokeslet_rotlet}
@@
 the Stokes equations with a Dirichlet boundary condition $\ff$ can be
-written as
+written in terms of the completed double-layer potential
 \begin{align}
@@
       \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
-      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \bd\Omega, 
+      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx) + \NN_0[\eeta](\xx),
+      \quad \xx \in \bd\Omega, 
       \label{eqn:DLP}\\
   \llambda_k &= \frac{1}{2\pi}\int_{\gamma_k} \eeta(\yy) \, ds_\yy,
-  \quad k=1,\ldots,M
+  \quad k=1,\ldots,M,
   \label{eqn:stokeslet} \\
   \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
-  \, ds_\yy, \quad k=1,\ldots,M.
+  \, ds_\yy, \quad k=1,\ldots,M,
   \label{eqn:rotlet}
@@
 \end{subequations}
-Finally, because of the incompressibility constraint, the boundary
-condition must satisfy 
+where 
 \begin{align*}
-  \int_{\bd\Omega} \ff \cdot \nn \, ds_\yy = 0.
+  \NN_0[\eeta](\xx) = \int_{\Gamma} 
+    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy,
 \end{align*}
-The result is a rank-one null space of~\eqref{eqn:completed_BIE} which
-is removed by adding the rank-one modification 
-\begin{align}
-  \NN_0[\eeta](\xx) = \int_{\Gamma} 
-    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy, \quad \xx \in \Gamma.
-\end{align}
+is being used to remove the rank one null space that results from the
+compatibility constraint that results from the flux-free requirement of
+$\ff$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Computing Quantities of Interest}
+\subsection{Layer Potentials for Quantities of Interest}
 \label{sec:qois}
@@
 taking the limit of equation~\eqref{eqn:shearStressDLP} when $\xx$ tends
-to $\xx_0 \in \bd\Omega$.  This limiting value is given
+to $\xx_0 \in \bd\Omega$.  The limiting value is given
 by~\cite{qua-bir2014a}
@@
 \end{align*}
-The deformation tensor due to the Stokeslets and
+The deformation tensor of the Stokeslets and
 rotlets~\eqref{eqn:stokeslet_rotlet} are
@@
     \II - \frac{2}{\rho^2} \rr \otimes \rr \right),  \\
-  \ssigma^R(\xx_0) &= \sum_{k=1}^M
-    -\frac{\xi_k}{\rho^4} \left(\rr \otimes \rr^\perp + 
+  \ssigma^R(\xx_0) &= -\sum_{k=1}^M
+    \frac{\xi_k}{\rho^4} \left(\rr \otimes \rr^\perp + 
     \rr^\perp \otimes \rr \right),
@@
 $\gamma_k$, and $\rho = \|\rr_k\|$.  Now that the deformation tensor of
-each component of the completed double-layer potential are computed, the
-shear stress at $\xx_0 \in \bd\Omega$ can be computed as
+each component of the completed double-layer potential is computed, the
+shear stress at $\xx_0 \in \bd\Omega$ is
 \begin{align*}
@@
 u_y$.  Therefore, to compute the $w(\xx)$ for $\xx \in
-\overline{\Omega}$, we only need to compute $w(\xx)$ for $\xx\Omega$.
-As we did for the shear stress, we compute the vorticity due to the
-double-layer potential, Stokeslets, and rotlets individually.  The
-vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at
+\overline{\Omega}$, we only need to compute $w(\xx)$ for $\xx \in
+\Omega$.  As we did for the shear stress, we compute the vorticity due
+to the double-layer potential, Stokeslets, and rotlets individually.
+The vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at
 $\xx \in \Omega$ is
@@
   w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
-    \frac{(\xx \cdot \eeta)(\xx \cdot \nn^\perp) + 
-    (\xx \cdot \nn)(\xx \cdot \eeta)}{\rho^4}ds_{\yy}.
+    \frac{(\rr \cdot \eeta)(\rr \cdot \nn^\perp) + 
+    (\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^4}ds_{\yy}.
   \label{eqn:vorticityDLP}
@@
 \end{align*}
-and the vorticity of a rotlet is zero.  Therefore, once the density
-function and Stokeslets are computed, the vorticity at $\xx \in \Omega$
-is
+and the vorticity of a rotlet is zero.  Therefore, the vorticity at $\xx
+\in \Omega$ is
 \begin{align*}
@@
 To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
-same procedure used for the shear stress.  We first find the pressure of
-the double-layer potential for $\xx \in \Omega$, and the find the jump
-that results from taking the limit of $\xx$ to $\xx_0 \in \Gamma$.
-Then, we compute the pressure due to the Stokestlet and rotlet
-terms~\eqref{eqn:stokeslet_rotlet}.   For $\xx \in \Omega$,
-the pressure is
+same procedure used for the shear stress.  We start by computing the
+pressure of the double-layer potential for $\xx \in \Omega$ and add the
+appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
+is
 \begin{align}
@@
     \nn \cdot \eeta(\yy) \,ds_\yy.
-  \label{eqn:pressureDLP}
 \end{align}
-To compute the pressure at $\xx_0 \in \bd\Omega$, we must take the limit
-of equation~\eqref{eqn:pressureDLP} when $\xx$ tends to $\xx_0$.  The
-limiting value is given by~\cite{qua-bir2014a}
-\begin{align}
+To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
+as $\xx$ tends to $\xx_0$.  The limiting value is given
+by~\cite{qua-bir2014a}
+\begin{align*}
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
     \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
-  \label{eqn:pressureDLPdiag}
-\end{align}
+\end{align*}
 The pressure due to the Stokeslets is
@@
 \end{align*}
-and the pressure due to the rotlets is zero.  Therefore, once the
-density function and Stokeslets are computed, the pressure at a point
-$\xx_0 \in \bd\Omega$ is
-\begin{align*}
-  p(\xx_0) = \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0) + 
-              p^{S}(\xx_0).
-\end{align*}
+and the pressure due to the rotlets is zero.  Therefore, the pressure is
+\begin{equation}
+\label{eqn:pressureDLP}
+\begin{aligned}
+  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
+  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
+              p^{S}(\xx), && \xx \in \bd\Omega.
+\end{aligned}
+\end{equation}
 
@@
 There are three main numerical methods that need to be developed:~the
-boundary integral equation solver~\eqref{eqn:completed_BIE}, computing
-the quantities of interest in Section~\ref{sec:qois}, and updating the
-shape of the eroding bodies with equation~\eqref{eqn:bodyEvolution}.  In
-order to compute stable simulations with long time horizons, we use
-numerical methods that achieve spectral accuracy in space, second-order
-in time, and maintain an equispaced discretization of the bodies.
+boundary integral equation solver for
+equation~\eqref{eqn:completed_BIE}, computing the quantities of interest
+in Section~\ref{sec:qois}, and updating the shape of the eroding bodies
+with equation~\eqref{eqn:bodyEvolution}.  So that we can form stable
+simulations with long time horizons, we use numerical methods that
+achieve spectral accuracy in space, second-order accuracy in time, and
+maintain an equispaced discretization of the bodies.
 
@@
 \subsection{Spatial Discretization}
-Each body will be represented with $N_\iin$ points.  The boundary is
-represented with the Fourier series
+Each body is represented with at $N_\iin$ points as the Fourier series
 \begin{align*}
-  \xx^k(\theta) = \sum_{j = -N/2}^{N/2-1} \hat{x}_j^k e^{ij\theta}.
+  \xx^k(\theta) = \sum_{j = -N/2}^{N/2-1} \hat{x}_j^k e^{ij\theta},
+    \quad k=1,\ldots,M.
 \end{align*}
-Derivatives of the shape must be taken which is easily done by
-differentiating the Fourier series term-by-term
+The exterior geometry is represented with a Fourier series using
+$N_\out$ points.  Derivatives of the shape are computed in Fourier space
 \begin{align*}
   \frac{d\xx^k(\theta)}{d\theta} = 
-      \sum_{j = -N/2}^{N/2-1} ij\hat{x}_j^k e^{ij\theta}.
+    \sum_{j = -N/2}^{N/2-1} ij\hat{x}_j^k e^{ij\theta},
+    \quad k=1,\ldots,M.
 \end{align*}
@@
 stress~\eqref{eqn:shearStressDLP}, the
-vorticity~\eqref{eqn:vorticityDLP}, the pressure both off the
-boundary~\eqref{eqn:pressureDLP} and on the
-boundary~\eqref{eqn:pressureDLPdiag}, the drag~\eqref{eqn:drag}, and the
-resistivity.  The integrands of each of these integrals, except for the
-resistivity, are smooth and periodic.  Under this condition the
-trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.
-However, before the trapezoid rule can be applied, singularity
-subtraction and odd-even integration~\cite{sid-isr1988} method must be
-used.
+vorticity~\eqref{eqn:vorticityDLP}, the pressure both off and on the
+boundary~\eqref{eqn:pressureDLP}, the drag~\eqref{eqn:drag}, and the
+resistivity.   The shear stress, pressure, and drag must also be
+computed using quadrature, and this can be interpreted as a
+post-processing step once the density function, Stokeslets, and rotlets
+are computed.
+
+The integrands of each of these integrals, except for the resistivity,
+are smooth and periodic.  Therefore, the trapezoid rule guarantees
+spectral accuracy~\cite{tre-wei2014}.  However, before the trapezoid
+rule can be applied, singularity subtraction and odd-even
+integration~\cite{sid-isr1988} method must be used.  In addition, when
+the target point is near $\bd\Omega$, a near-singular integration scheme
+must be used.
 
@@
 To numerically evaluate the completed double-layer
-potential~\eqref{eqn:completed_BIE}, we start by discretizing each
-interior body $\gamma_k$ with $N_\iin$ points, the outer geometry
-$\Gamma$ with $N_\out$ points, and define $N = MN_\iin + N_\out$ to be
-the total number of discretization points.  The double-layer potential
-in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
+potential~\eqref{eqn:completed_BIE}, we define $N = MN_\iin + N_\out$ to
+be the total number of discretization points of $\bd\Omega$.  The
+double-layer potential in~\eqref{eqn:DLP} is discretized with the
+trapezoid rule as
 \begin{align}
-  \DD[\eeta](\xx_i^k) = \sum_{\ell = 1}^{M}\sum_{j=1}^{N} 
-    K(\xx_i^k,\xx_j^\ell) \eeta(\xx_j^\ell) 
-      \Delta s_{j}^{\ell}, \quad i=1,\ldots,N, \: k=1\ldots,M,
+  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
+      \Delta s_{j}, \quad i=1,\ldots,N,
   \label{eqn:trapDLP}
 \end{align}
-where $\Delta s_j^\ell$ is the arclength term of $\gamma_\ell$ at
-$\xx_j^\ell \in \gamma_\ell$, or the corresponding term if $\xx_k \in
-\Gamma$, and
+where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
+$\xx_j$, and
 \begin{align*}
@@
 where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
-vector at $\xx \in \bd\Omega$.  The Stokeslet~\eqref{eqn:stokeslet} and
-rotlet~\eqref{eqn:rotlet} strengths are also discretized with the
-trapezoid rule, and the resulting discretization
-of~\eqref{eqn:completed_BIE} is
+vector at $\xx \in \bd\Omega$.  The equations for the strengths of the
+Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are
+also discretized with the trapezoid rule.  Applying this discretization
+strategy to~\eqref{eqn:completed_BIE}, the dense linear system that
+needs to be solved is
 \begin{equation}
@@
   \begin{aligned}
-    \ff(\xx_i^k) &= -\frac{1}{2}\ssigma(\xx_i^k) + 
-      \sum_{\ell = 1}^{M}\sum_{j=1}^{N} 
-      K(\xx_i^k,\xx_j^\ell) \eeta(\xx_j^\ell) \Delta s_{j}^{\ell} +
-      \sum_{\ell=1}^M S[\llambda_k,\cc_k](\xx_i^k) +
-      \sum_{\ell=1}^M R[\xi_k,\cc_k](\xx_i^k), \\
-    \llambda_k &= \sum_{i=1}^{N_\iin} \eeta(\xx_i^k) 
-      \Delta s_i^k \\ 
-    \mu_k &= \sum_{i=1}^{N_\iin} {(\xx_i^k)}^\perp \cdot
-      \eeta(\xx_i^k) \Delta s_i^k,
+    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
+      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} +
+      \sum_{k=1}^M S[\llambda_k,\cc_k](\xx_i) +
+      \sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) + 
+      \sum_{\xx_j \in \Gamma} \nn(\xx_i) \otimes
+      \nn(\xx_j)\eeta(\xx_j), \\
+    \llambda_k &= \sum_{\xx_i \in \gamma_k} \eeta(\xx_i) 
+      \Delta s_i \\ 
+    \mu_k &= \sum_{\xx_i \in \gamma_k}
+      {(\xx_i^k)}^\perp \cdot \eeta(\xx_i^k) \Delta s_i^k,
   \end{aligned}
@@
 The dense linear system~\eqref{eqn:completed_BIE_discretized} is solved
-iteratively with GMRES.  The most expensive part is computing the
-double sum for all target and source points.  A direct summation would
-require $\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$ by
-using the Fast Mutlipole method for the Stokes double-layer
+iteratively with GMRES.  The most expensive part is computing the $N$
+term sum for all target points.  A direct summation would require
+$\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$ by using the
+Fast Mutlipole method for the Stokes double-layer
 potential~\cite{gre-rok1987,rac-???} \todo[inline]{sent email to Manas
@@
 \subsubsection{Shear Stress}
-In our erosion model, the shear stress must be computed which requires
-evaulating the layer potential~\eqref{eqn:shearStressDLP}.  In our
-implementation, this calculation is done directly which requires
-$\bigO(N^2)$ operations.  This complexity could be reduced with
-the kernel-independent FMM~\cite{yin-bir-zor2004}.  However, since this
-calculation is only computed once per time step, unlike the velocity
-double-layer potential that must be evaluated at each GMRES iteration.
+We have decomposed the shear stress into the contributions due to three
+different terms.  The contributions from the Stokeslets and the rotlets
+can be directly evaluated since $\rr \neq 0$ for all $\xx \in \gamma$.
+However, the kernel of the shear stress due to the double-layer
+potential~\eqref{eqn:shearStressDLP} has a singularity that is
+asymptotic to $\bigO(\rho^2)$ when $\yy \rightarrow \xx$.  The strength
+of this singularity can be reduced  by taking advantage of
+the fact that a velocity field due to a constant density function has no
+shear stress~\cite{poz1992}.  Therefore, the shear stress can be
+evaluated as 
+\begin{align*}
+  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
+      (\ssigma(\yy) - \ssigma(\xx)) \, ds_{\yy},
+\end{align*}
+This expression for the shear stress has a singularity that is
+asymptotic to $\bigO(\rho)$ when $\yy \rightarrow \xx$.  Finally, to
+achieve a spectrally accurate discretization for the shear stress, we
+use odd-even integration~\cite{sid-isr1988}.  That is, the shear stress
+due to the double-layer potential on body $k$ is approximated by using
+the trapezoid rule using all points $\xx_i \notin \gamma_k$ and the even
+(odd) indexed points if $i$ is odd (even).
+
+In our implementation, the shear stress is computed with a direct
+summation, and this requires $\bigO(N^2)$ operations.  Since this
+calculation is only computed once per time step, while the velocity is
+calculated at each GMRES iteration, the computational cost is
+manageable.  However, in future work, to simulate erosion in a
+dense packing of grains, a fast summation method, such as the
+kernel-independent FMM~\cite{yin-bir-zor2004}, will be incorporated.
 
@@
 \subsubsection{Pressure}
-
-\subsubsection{Drag}
-
-\subsubsection{Resistivity}
-
-The shear stress, pressure, and drag must also be computed using
-quadrature, and this can be interpreted as a post-processing step once
-the density function, Stokeslets, and rotlets are computed.  All the
-quadrature methods are described in Section~\ref{sec:quadrature}
-
-Once the shear stress is computed, it is used to update the shape of the
-bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
-eliminate tangling and stretching of the mesh, we use a {\thL}
-formulation~\cite{hou-low-she1994} which is described in
-Section~\ref{sec:thetaL}.  In this section, we also describe our time
-stepping method and two regularization terms that are necessary to
-control the curvature of the bodies and to maintain spectral accuracy in
-space.
-
-For the shear stress and the pressure, we will use odd-even integration
-which achieves spectral accuracy if the integrand is no stronger than
-$\bigO(\rho^{-1})$.  Since both these integrands are too strong, the
-singularity must be weakened.  This can be done by adding a constant
-density function which has no effect on the shear stress and
-pressure~\cite{poz1992}.  In particular, the shear stress due to the
-double-layer potential is equivalent to
-\begin{align*}
-  \ssigma^{\DD}(\xx_0) &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
-      \ssigma(\yy) \, ds_{\yy} \\ 
-      &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
-      (\ssigma(\yy) - \ssigma(\xx_0)) \, ds_{\yy}.
-\end{align*}
 For the pressure, the double-layer potential is equivalent to
@@
 
+\subsubsection{Drag}
+
+\subsubsection{Resistivity}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:thetaL}
+
+In this section, we also describe our time stepping method and two
+regularization terms that are necessary to control the curvature of the
+bodies and to maintain spectral accuracy in space.
+
+Once the shear stress is computed, it is used to update the shape of the
+bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
+eliminate tangling and stretching of the mesh, we use a {\thL}
+formulation~\cite{hou-low-she1994} which is described in
+Section~\ref{sec:thetaL}.
 

### 2017-10-08 docs/methods/erosion_methods.tex
Changed some things. Worked on tex a little.

--- 2017-10-02 docs/methods/erosion_methods.tex
@@
 
+The shear stress, pressure, and drag must also be computed using
+quadrature, and this can be interpreted as a post-processing step once
+the density function, Stokeslets, and rotlets are computed.
+
 \subsubsection{Velocity}
@@
 
-\subsubsection{Vorticity}
-
-\subsubsection{Pressure}
-
-\subsubsection{Drag}
-
-\subsubsection{Resistivity}
-
-The shear stress, pressure, and drag must also be computed using
-quadrature, and this can be interpreted as a post-processing step once
-the density function, Stokeslets, and rotlets are computed.  All the
-quadrature methods are described in Section~\ref{sec:quadrature}
-
-Once the shear stress is computed, it is used to update the shape of the
-bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
-eliminate tangling and stretching of the mesh, we use a {\thL}
-formulation~\cite{hou-low-she1994} which is described in
-Section~\ref{sec:thetaL}.  In this section, we also describe our time
-stepping method and two regularization terms that are necessary to
-control the curvature of the bodies and to maintain spectral accuracy in
-space.
-
 For the shear stress and the pressure, we will use odd-even integration
@@
 \end{align*}
+
+Once the shear stress is computed, it is used to update the shape of the
+bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
+eliminate tangling and stretching of the mesh, we use a {\thL}
+formulation~\cite{hou-low-she1994} which is described in
+Section~\ref{sec:thetaL}.
+
+\subsubsection{Vorticity}
+
+\subsubsection{Pressure}
 For the pressure, the double-layer potential is equivalent to
@@
 \label{sec:thetaL}
+
+In this section, we also describe our time stepping method and two
+regularization terms that are necessary to control the curvature of the
+bodies and to maintain spectral accuracy in space.
 
@@
 
-In order to regularize boundary evolution, we modify
-Eq.~(\ref{eqn:bodyEvolution}) to include a curvature-driven component
-(also corrected errors in this equation)
+In order to regularize boundary evolution, we modify the normal velocity in Eq.~(\ref{eqn:bodyEvolution}) as follows
 \begin{equation}
-\dot{\xx}(t) = \abs{\tau} \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
+\Vn = \abs{\tau} + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
 \end{equation}
-The curvature term acts to smooth bodies that have high-frequency oscillations.
+Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body.
+The second term on the right acts to smooth bodies that have high-frequency oscillations.
+Since we have subtracted the mean curvature, $2\pi/L$, this term is area-preserving, so that the only material loss is due to the shear stress.
+We chose the prefactor $\log^{-1} \left(2\pi/L \right)$, so that, for 2D Stokes flow, this term scales the same as shear stress as $L \to 0$.
+Thus, the relative strength of the smoothing is always the same.
 
-Simple form for my talk
+We now introduce the tangent angle, $\theta$, defined through the relation
 \begin{equation}
-\dot{\xx}(t) = \abs{\tau} \nn + \eps \kappa
+(x_s, y_s) = (\cos \theta, \sin \theta)
 \end{equation}
+where $s$ is arc length. We also introduce the normalized arc length $\alpha = s / L$. In terms of these new variables, the curvature can be expressed as
+\begin{equation}
+\kappa = \frac{1}{L} \pderiv{\theta}{\alpha}
+\end{equation}
+Substitution into Eq.~(\ref{})
 
+\vsp{5}
 \todo[inline]{Artificial Diffusion} 

### 2017-10-10 docs/methods/erosion_methods.tex
Working on methods latex, section theta-L.
Working on theta-L in methods papers

@@
 \vsp{2}
-To handle boundary evolution, we use the {\thL}    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems.
+To handle boundary evolution, we use the {\thL}    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems \cite{hou-low-she1994}.
 Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).
@@
 \begin{equation}
-\Vn = \abs{\tau} + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
+\label{eqn:Vn}
+\Vn = \atau + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
 \end{equation}
@@
 \end{equation}
-Substitution into Eq.~(\ref{})
+Substitution into Eq.~(\ref{eqn:Vn}) gives
+\begin{equation}
+\label{eqn:Vn2}
+\Vn = \atau + \frac{\eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 2 \pi \right)
+\end{equation}
+The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced.
+The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
+\begin{equation}
+\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
+\end{equation}
+The interface evolution is then given by
+\begin{equation}
+\dot{\xx}(t) = \Vn \nn + \Vs \ss.
+\end{equation}
+Upon transforming to the variables $\theta(\alpha,t)$ and $L(t)$, we obtain the evolution equations
+\begin{align}
+& \tderiv{L}{t} = - \mean{\thalpha \Vn} \\
+& \pderiv{\theta}{t} = L^{-1} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
+\end{align}
+Inserting Eq.~(\ref{eqn:Vn2}) for the normal velocity gives
+\begin{equation}
+\pderiv{\theta}{t} = \frac{\eps}{L^{2} \log \left(2\pi/L \right)} \ppd{\theta}{\alpha} 
++ \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
+\end{equation}
+For simplicity, we introduce the variables
+\begin{align}
+& M = - \mean{\thalpha \Vn} \\
+& N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
+& \elfun(L) = \frac{1}{L^{2} \log \left(2\pi/L \right)}
+\end{align}
+Then the evolution equations can be expressed as
+\begin{align}
+& \tderiv{L}{t} = M \\
+& \pderiv{\theta}{t} = \eps \elfun(L) \ppd{\theta}{\alpha} + N
+\end{align}
+We treat $\theta$ spectrally
+\begin{equation}
+\theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha}
+\end{equation}
+Then we get
+\begin{equation}
+\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun(L) \thhat_k = \hat{N}_k
+\end{equation}
+We introduce the integrating factor
+\begin{equation}
+\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun(L) dt \right)
+\end{equation}
+so that the solution can be represented as
+\begin{align}
+\thhat_k(t) & = \frac{1}{\mu} \int \mu \hat{N}_k dt 
+= \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun(L) dt'' \right) \hat{N}_k \, dt'
+% LONGER FORM
+%& = \exp \left( -4 \eps \pi^2 k^2 \int_0^t \elfun(L) ds \right) \, 
+%\int_0^t \exp \left( 4 \eps \pi^2 k^2 \int_0^s \elfun(L) ds' \right) \hat{N}_k ds \\
+\end{align}
+where $t'$ and $t''$ are simply dummy variables for integration. We can get the exact relationship
+\begin{equation}
+\thhat_k(t + \Delta t) = \thhat_k(t) + \int_t^{t+\Delta t}
+\end{equation}
 

### 2017-10-13 docs/methods/erosion_methods.tex
NM
small changes to numerics section of methods paper

@@
 rotlets~\eqref{eqn:stokeslet_rotlet} are
-\begin{align*}
+\begin{equation}
+  \label{eqn:shearStressSR}
+  \begin{aligned}
   \ssigma^S(\xx_0) &= \sum_{k=1}^{M}
@@
     \rr^\perp \otimes \rr \right),
-\end{align*}
+  \end{aligned}
+\end{equation}
 where $\rr = \xx - \cc_k$, $\cc_k$ is the point chosen inside body
@@
       \sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) + 
-      \sum_{\xx_j \in \Gamma} \nn(\xx_i) \otimes
-      \nn(\xx_j)\eeta(\xx_j), \\
+      \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
+      \nn(\xx_j))\eeta(\xx_j), \\
     \llambda_k &= \sum_{\xx_i \in \gamma_k} \eeta(\xx_i) 
@@
     \mu_k &= \sum_{\xx_i \in \gamma_k}
-      {(\xx_i^k)}^\perp \cdot \eeta(\xx_i^k) \Delta s_i^k,
+      {(\xx_i^k - \cc_k)}^\perp \cdot \eeta(\xx_i^k) \Delta s_i^k,
   \end{aligned}
@@
 \subsubsection{Shear Stress}
-We have decomposed the shear stress into the contributions due to three
-different terms.  The contributions from the Stokeslets and the rotlets
-can be directly evaluated since $\rr \neq 0$ for all $\xx \in \gamma$.
-However, the kernel of the shear stress due to the double-layer
-potential~\eqref{eqn:shearStressDLP} has a singularity that is
-asymptotic to $\bigO(\rho^2)$ when $\yy \rightarrow \xx$.  The strength
-of this singularity can be reduced  by taking advantage of
-the fact that a velocity field due to a constant density function has no
-shear stress~\cite{poz1992}.  Therefore, the shear stress can be
-evaluated as 
+We have decomposed the deformation tensor into the contributions due to
+three different terms.  The contributions from the Stokeslets and the
+rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
+\gamma$.  However, the kernel of the deformation tensor due to the
+double-layer potential~\eqref{eqn:shearStressDLP} has a singularity that
+is asymptotic to $\bigO(\rho^2)$ when $\yy \rightarrow \xx$.  The
+strength of this singularity can be reduced  by using the fact that a
+velocity field due to a constant density function is
+constant~\cite{poz1992}.  Therefore, the first part of the deformation
+tensor can be evaluated as 
 \begin{align*}
   \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
-      (\ssigma(\yy) - \ssigma(\xx)) \, ds_{\yy},
+      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega
 \end{align*}
-This expression for the shear stress has a singularity that is
+\todo[inline]{haven't said what $K_\ssigma$ is}
+This expression for the deformation tensor has a singularity that is
 asymptotic to $\bigO(\rho)$ when $\yy \rightarrow \xx$.  Finally, to
-achieve a spectrally accurate discretization for the shear stress, we
-use odd-even integration~\cite{sid-isr1988}.  That is, the shear stress
-due to the double-layer potential on body $k$ is approximated by using
-the trapezoid rule using all points $\xx_i \notin \gamma_k$ and the even
-(odd) indexed points if $i$ is odd (even).
+achieve a spectrally accurate discretization for the deformation tensor,
+we use odd-even integration~\cite{sid-isr1988}.  That is, the
+deformation tensor due to the double-layer potential at a discretization
+point $\xx_i$ on body $\gamma_k$, with $i$ being odd, is approximated as
+\begin{align*}
+  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_k}
+    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
+  \sum_{\substack{\xx_j \in \gamma_k \\ j \: \mathtt{even}}}
+    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
+\end{align*}
+and a similar approximation is used when $i$ is even.  The deformation
+tensor due to the Stokeslets and rotlets is given in
+equation~\eqref{eqn:shearStressSR}, and then the shear stress can be
+computed by computing the deformation tensor in the normal direction,
+and taking the inner product with the tangent direction.
 
-In our implementation, the shear stress is computed with a direct
+In our implementation, the deformation tensor is computed with a direct
 summation, and this requires $\bigO(N^2)$ operations.  Since this
@@
 calculated at each GMRES iteration, the computational cost is
-manageable.  However, in future work, to simulate erosion in a
-dense packing of grains, a fast summation method, such as the
+manageable.  However, in future work, to simulate erosion in a dense
+packing of grains, a fast summation method, such as the
 kernel-independent FMM~\cite{yin-bir-zor2004}, will be incorporated.
@@
 \subsubsection{Vorticity}
+Since the vorticity is equivalent to the shear stress on $\bd\Omega$, we
+only need to compute the vorticity at target points $\xx \in \Omega$ in
+the interior.  This is done with the trapezoid rule by computing
+\begin{align*}
+  \omega(\xx_i) = \sum_{j=1}^N \frac{}{}
+\end{align*}
 
@@
 & \tderiv{L}{t} = - \mean{\thalpha \Vn} \\
-& \pderiv{\theta}{t} = L^{-1} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
+& \pderiv{\theta}{t} = \frac{1}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
 \end{align}
@@
 & N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
-& \elfun(L) = \frac{1}{L^{2} \log \left(2\pi/L \right)}
+& \elfun = \frac{1}{L^{2} \log \left(2\pi/L \right)}
 \end{align}
@@
 & \tderiv{L}{t} = M \\
-& \pderiv{\theta}{t} = \eps \elfun(L) \ppd{\theta}{\alpha} + N
+& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
 \end{align}
@@
 \begin{equation}
-\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun(L) \thhat_k = \hat{N}_k
+\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
 \end{equation}
@@
 \begin{equation}
-\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun(L) dt \right)
+\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
 \end{equation}
@@
 \begin{align}
-\thhat_k(t) & = \frac{1}{\mu} \int \mu \hat{N}_k dt 
-= \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun(L) dt'' \right) \hat{N}_k \, dt'
+\thhat_k(t) & = \frac{1}{\mu} \int^t \mu \hat{N}_k dt'
+= \thhat_k(0) + \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun dt'' \right) \hat{N}_k \, dt'
 % LONGER FORM
@@
 \begin{equation}
-\thhat_k(t + \Delta t) = \thhat_k(t) + \int_t^{t+\Delta t}
+\thhat_k(t + \Delta t) = \thhat_k(t) 
++ \int_t^{t+\Delta t} \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^{t+\Delta t} \elfun dt'' \right) \hat{N}_k \, dt'
 \end{equation}

### 2017-10-14 docs/methods/erosion_methods.tex
Simplified my latex notes. Removed a bunch of obselete things and improved the theta-L section.
small changes to numerics section

@@
     8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right) ds_\yy.
+  \right) \eeta(\yy) ds_\yy.
   \end{aligned}
@@
   w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
-    \frac{(\rr \cdot \eeta)(\rr \cdot \nn^\perp) + 
-    (\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^4}ds_{\yy}.
+    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}
+    (\rr \cdot \eeta) ds_{\yy}.
   \label{eqn:vorticityDLP}
@@
 \gamma$.  However, the kernel of the deformation tensor due to the
-double-layer potential~\eqref{eqn:shearStressDLP} has a singularity that
-is asymptotic to $\bigO(\rho^2)$ when $\yy \rightarrow \xx$.  The
-strength of this singularity can be reduced  by using the fact that a
-velocity field due to a constant density function is
-constant~\cite{poz1992}.  Therefore, the first part of the deformation
-tensor can be evaluated as 
+double-layer potential~\eqref{eqn:shearStressDLP} 
+\begin{align*}
+  K_\ssigma(\xx,\yy) = \frac{1}{2\pi} \left(
+    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
+    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) +
+    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
+    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
+  \right),
+\end{align*}
+has a singularity that is asymptotic to $\bigO(\rho^2)$ when $\yy
+\rightarrow \xx$.  The strength of this singularity can be reduced  by
+using the fact that a velocity field due to a constant density function
+is constant~\cite{poz1992}.  Therefore, the first part of the
+deformation tensor can be evaluated as 
 \begin{align*}
   \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
-      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega
+      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
 \end{align*}
-\todo[inline]{haven't said what $K_\ssigma$ is}
 This expression for the deformation tensor has a singularity that is
@@
 \begin{align*}
-  \omega(\xx_i) = \sum_{j=1}^N \frac{}{}
+  \omega(\xx_i) = \sum_{j=1}^N K_\omega (\xx_i,\xx_j) \cdot \eeta_j 
+    \Delta s_j,
+\end{align*}
+where
+\begin{align*}
+  K_\omega (\xx,\yy) =  -\frac{\rr}{\pi}
+    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}.
 \end{align*}

### 2017-10-14 docs/TexNotes/Notes.tex
highlighting in Saverio's paper?
Took debugging print lines out of thetalne.jl

@@
 
+% FROM METHODS TEX
+\newcommand{\xx}{{\mathbf{x}}}
+\renewcommand{\ss}{{\mathbf{s}}}
+\newcommand{\nn}{{\mathbf{n}}}
+% Derivatives
+\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
+\newcommand{\tderiv}[2]{\frac{d #1}{d #2}}
+% Nick's commands
+\newcommand{\thL}{$\theta$--$L$}
+\newcommand{\Vn}{V_n}
+\newcommand{\Vs}{V_s}
+\newcommand{\thalpha}{\pderiv{\theta}{\alpha}}
+\newcommand{\elfun}{\zeta}
+\newcommand{\thhat}{\hat{\theta}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-where $C$ is a constant.
+where $C$ is a constant. In what follows, we will scale time on an erosion timescale (non-dimensionalize) and thus set $C=1$.
 
@@
 \end{equation}
-where $V$ and $L$ are a characteristic velocity and length scale respectively.
-To evolve the interface in our numerical method, we will probably need to introduce some smoothing to mitigate high frequencies.
-A common approach is to introduce a small curvature term into the interface velocity, sometimes called the method of vanishing viscosity.
-The most basic implementation would be
+where $V$ and $L$ are a characteristic velocity and length scale respectively.  However, for 2D Stokes flow we have Stokes paradox and slender body effects. The analogous scaling of the stress is
 \begin{equation}
-V_n = - C \atau - \eps \kappa
+\tau \sim \frac{\mu V}{L \log(W/L)}
 \end{equation}
-where $\eps$ is a small parameter and $\kappa$ is the surface curvature. However, we have two additional preferences
-\begin{enumerate}
-\item As the body changes size, we would like the influence of the curvature term relative to the shear stress to remain the same.
-\item We prefer the curvature term not to change the size of the body.
-\end{enumerate}
-Fortunately, the first requirement is already satisfied since both $\tau$ and $\kappa$ scale like $1/L$.
-To satisfy the second requirement, we replace $\kappa$ with this same quantity minus its mean.
-To allow for some generality, we allow the curvature term by to be scaled by a power of $L$, giving
-\begin{equation}
-V_n = - C \atau - \eps L^{\beta} \left(\kappa - \frac{2 \pi}{L} \right)
-\end{equation}
-Thus, for the present case of Stokes flow $\beta=0$, but for the previous case of high-Reynolds-number flow $\beta=1/2$.
-
-\section{Numerical interface evolution}
-
-To evolve the interface numerically, we use the $\theta$-$L$ method.
-Rather than re-derive the formulas, I will use the convention from Shelley 1994, with the curve parameterized in the CCW direction and the normal vector pointing {\em inward}.
-With this convention, the normal interface velocity is the negative of what it was previously, giving
-\begin{equation}
-\label{Vn1}
-V_n = C \atau + \eps L^{\beta} \left(\kappa - \frac{2 \pi}{L} \right)
-\end{equation}
-Recall that for Stokes flow, $\beta = 0$.
-
-Now, the interface $\X = (x,y)$ evolves according to
-\begin{equation}
-\pd{\bvec{X}}{t} = V_n \nhat + V_s \shat
-\end{equation}
-where $\nhat = (-y_s, x_s)$ is the inward pointing normal vector and $\shat = (x_s, y_s)$ is the tangential vector (running in the CCW direction).
-Here, we have introduced a tangential velocity $V_s$ that will be chosen to keep the curve in the equal-arclength parameterization.
-We will frequently use a normalized arclength $\alpha = s/L$, where $L$ is the total length of the curve.
-
-We introduce the tangent angle $\theta$, defined by
-\begin{equation}
-(x_s, y_s) = (\cos \theta, \sin \theta)
-\end{equation}
-so that we have
-\begin{equation}
-\tan \theta = y_s/x_s = y_\alpha / x_\alpha
-\end{equation}
-Remember the identity that $x_s^2 + y_s^2 = 1$ as this is very useful.
-The curvature is given by
-\begin{equation}
-\kappa = x_s y_{ss} - x_{ss} y_s = \pd{\theta}{s} = L^{-1} \pd{\theta}{\alpha}
-\end{equation}
-We are using the standard convention, where a convex shape, like a circle, has positive curvature. The normal velocity now can be written as
-\begin{equation}
-\label{Vn2}
-V_n = C \atau + \eps L^{\beta-1} \left(\pd{\theta}{\alpha} - 2 \pi \right)
-\end{equation}
-
-We now discuss how to choose $V_s$ to remain in the equal-arclength frame of reference. We will use the term
-\begin{equation}
-\gamma = \pd{\theta}{\alpha} V_n
-\end{equation}
-Then the necessary tangential velocity is determined by
-\begin{equation}
-\td{V_s}{\alpha} = \gamma - \mean{\gamma}
-\end{equation}
-where $\mean{}$ indicates the mean value.
-
-We now discuss how to evolve $\theta$ and $L$ forward in time according to the interface velocity given above. The resulting evolution equations are
-\begin{align}
-& \td{L}{t} = - \mean{\gamma} \\
-& \pd{\theta}{t} = L^{-1} \left( \pd{V_n}{\alpha} + \pd{\theta}{\alpha} V_s \right)
-\end{align}
-Then, using the above $V_n$, the equation for $\theta$ simplifies to
-\begin{equation}
-\label{thetaEvolve}
-\pd{\theta}{t} = \eps L^{\beta-2} \ppd{\theta}{\alpha} + L^{-1} \left( C \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
-\end{equation}
-
-We now discuss the numerical methods used to solve the above evolution equations. For $L$, we use an explicit method
-\begin{equation}
-L^{(n+1)} = L^{(n)} + \frac{\Dt}{2} \left( 3 M^{(n)} - M^{(n-1)} \right)
-\end{equation}
-where
-\begin{equation}
-M = \td{L}{t} = -\mean{\gamma}
-\end{equation}
-For $\theta$, we use a spectral method, giving
-\begin{equation}
-\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{\beta-2} \thh_k = \hat{N}_k
-\end{equation}
-where the nonlinear terms are grouped together as
-\begin{equation}
-N = L^{-1} \left( C \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
-\end{equation}
-We evolve with the integrating-factor method. When recast in terms of Gaussian filters, this gives
-\begin{equation}
-\label{intfact}
-\thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
-+ \frac{\Dt}{2} \left( 3 \GG(N^{(n)}, \sigma_1) - \GG(N^{(n-1)}), \sigma_2 \right)
-\end{equation}
-where
-\begin{align}
-& \sigma_1 = 2 \pi \sqrt{\eps \Dt} \sqrt{(L^{n})^{\beta-2} + (L^{n+1})^{\beta-2} } 	\\
-& \sigma_2 = 2 \pi \sqrt{\eps \Dt} \sqrt{(L^{n-1})^{\beta-2} + 2 (L^{n})^{\beta-2} + (L^{n+1})^{\beta-2} }
-\end{align}
-
-\subsection{Different scaling of the stress}
-Some numerical tests reveal that for 2D Stokes flow the stress scales like $\tau \sim 1/(L \log L)$, instead of the naive $1/L$.
-This is because we are in a 2D bounded domain (Stokes paradox type stuff).
-So we need to modify the curvature driven flow to have the same scaling.
-To this end, modify Eq.~(\ref{Vn1}) to read
-\begin{equation}
-V_n = \atau + \eps f(L) \left(\kappa - \frac{2 \pi}{L} \right)
-\end{equation}
-For 2D Stokes flow, we have 
-\begin{equation}
-f(L) = \frac{1}{\log (W/L)}
-\end{equation}
-where $W$ is the lengthscale of the 3rd dimension (e.g.
-the length of a long cylinder).
-The 2D approximation requires $W \gg L$, and in the code I chose $W = 2 \pi$.
-Carrying through this change, Eq.~(\ref{Vn2}) becomes
-\begin{equation}
-V_n = \atau + \eps L^{-1} f(L) \left(\pd{\theta}{\alpha} - 2 \pi \right)
-\end{equation}
-and Eq.~(\ref{thetaEvolve}) becomes
-\begin{equation}
-\pd{\theta}{t} = \eps L^{-2} f(L) \ppd{\theta}{\alpha} + L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
-\end{equation}
-Then to evolve $\theta$ spectrally, we use
-\begin{equation}
-\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{-2} f(L)  \thh_k = \hat{N}_k
-\end{equation}
-where the nonlinear terms are grouped together as
-\begin{equation}
-N = L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
-\end{equation}
-We evolve with the integrating-factor method. When recast in terms of Gaussian filters, this gives
-\begin{equation}
-\label{intfact}
-\thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
-+ \frac{\Dt}{2} \left( 3 \GG(N^{(n)}, \sigma_1) - \GG(N^{(n-1)}), \sigma_2 \right)
-\end{equation}
-where
-\begin{align}
-& \sigma_1 = 2 \pi \sqrt{\eps \Dt} \sqrt{g(L^{n}) + g(L^{n+1}) } 	\\
-& \sigma_2 = 2 \pi \sqrt{\eps \Dt} \sqrt{g(L^{n-1}) + 2 g(L^{n}) + g(L^{n+1}) }
-\end{align}
-where $g(L) = L^{-2} f(L)$.
+where $W$ is the width in the third dimension. In the following, we will take $W = 2\pi$, since a body cannot have a length greater than $2\pi$ and still fit inside the domain.
 
@@
 \begin{equation}
-\dot{A} = -C \abs{\tau} L
+\dot{A} = - \abs{\tau} L
 \end{equation}
@@
 
+\section{Numerical interface evolution}
+
+To handle boundary evolution, we use the {\thL} method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems.
+Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).
+
+In order to regularize boundary evolution, we modify the normal velocity as follows
+\begin{equation}
+\label{eqn:Vn}
+\Vn = \atau + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
+\end{equation}
+Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body.
+The second term on the right acts to smooth bodies that have high-frequency oscillations.
+This is sometimes called the method of vanishing viscosity.
+Since we have subtracted the mean curvature, $2\pi/L$, this term is area-preserving, so that the only material loss is due to the shear stress.
+We chose the prefactor $\log^{-1} \left(2\pi/L \right)$, so that, for 2D Stokes flow, this term scales the same as shear stress as $L \to 0$.
+Thus, the relative strength of the smoothing is always the same.
+
+Note: The curvature is given by
+\begin{equation}
+\kappa = x_s y_{ss} - x_{ss} y_s = \pd{\theta}{s} = L^{-1} \pd{\theta}{\alpha}
+\end{equation}
+We are using the standard convention, where a convex shape, like a circle, has positive curvature.
+
+We now introduce the tangent angle, $\theta$, defined through the relation
+\begin{equation}
+\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin \theta \right)
+\end{equation}
+where $s$ is arc length. We also introduce the normalized arc length $\alpha = s / L$.
+
+Note: We have this relation
+\begin{equation}
+\tan \theta = y_s/x_s = y_\alpha / x_\alpha
+\end{equation}
+and remember the identity that $x_s^2 + y_s^2 = 1$ as this is very useful.
+
+In terms of these new variables, the curvature can be expressed as
+\begin{equation}
+\kappa = \frac{1}{L} \pderiv{\theta}{\alpha}
+\end{equation}
+Substitution into Eq.~(\ref{eqn:Vn}) gives
+\begin{equation}
+\label{eqn:Vn2}
+\Vn = \atau + \frac{\eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 2 \pi \right)
+\end{equation}
+The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced.
+The tangential velocity that does the trick is determined by Shelley 1994 as
+\begin{equation}
+\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
+\end{equation}
+The interface evolution is then given by
+\begin{equation}
+\dot{\xx}(t) = \Vn \nn + \Vs \ss.
+\end{equation}
+
+Note: with the above conventions, we have $\nn = (-y_s, x_s)$ as the inward pointing normal vector and $\ss = (x_s, y_s)$ as the tangential vector (running in the CCW direction).
+
+Upon transforming to the variables $\theta(\alpha,t)$ and $L(t)$, we obtain the evolution equations
+\begin{align}
+& \tderiv{L}{t} = - \mean{\thalpha \Vn} \\
+& \pderiv{\theta}{t} = \frac{1}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
+\end{align}
+Inserting Eq.~(\ref{eqn:Vn2}) for the normal velocity gives
+\begin{equation}
+\pderiv{\theta}{t} = \frac{\eps}{L^{2} \log \left(2\pi/L \right)} \ppd{\theta}{\alpha} 
++ \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
+\end{equation}
+For simplicity, we introduce the variables
+\begin{align}
+& M = - \mean{\thalpha \Vn} \\
+& N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
+& \elfun = \frac{1}{L^{2} \log \left(2\pi/L \right)}
+\end{align}
+Then the evolution equations can be expressed as
+\begin{align}
+& \tderiv{L}{t} = M \\
+& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
+\end{align}
+We treat $\theta$ spectrally
+\begin{equation}
+\theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha}
+\end{equation}
+Then we get
+\begin{equation}
+\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
+\end{equation}
+We introduce the integrating factor
+\begin{equation}
+\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
+\end{equation}
+so that the solution can be represented as
+\begin{align}
+\thhat_k(t) & = \frac{1}{\mu} \int^t \mu \hat{N}_k dt'
+= \thhat_k(0) + \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun dt'' \right) \hat{N}_k \, dt'
+% LONGER FORM
+%& = \exp \left( -4 \eps \pi^2 k^2 \int_0^t \elfun(L) ds \right) \, 
+%\int_0^t \exp \left( 4 \eps \pi^2 k^2 \int_0^s \elfun(L) ds' \right) \hat{N}_k ds \\
+\end{align}
+where $t'$ and $t''$ are simply dummy variables for integration. We can get the exact relationship
+\begin{equation}
+\thhat_k(t + \Delta t) = \thhat_k(t) 
++ \int_t^{t+\Delta t} \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^{t+\Delta t} \elfun dt'' \right) \hat{N}_k \, dt'
+\end{equation}
+
 \subsection{How to scale smoothing parameters?}
@@
 
-The calculation is based on looking at Eq.~(\ref{intfact}), where $\sigma_1 \sim 2 \pi \sqrt{\eps \Delta t}$.
+The calculation is based on looking at Eq.~?, where $\sigma_1 \sim 2 \pi \sqrt{\eps \Delta t}$.
 For the largest wavenumbers, $k_{max} \sim N/2$, we want the smoothing to beat the nonlinear term (so that overall, these modes decay).

### 2017-10-16 docs/methods/erosion_methods.tex
worked on numerics section

@@
 Integrals that need to be approximated are the double-layer potential
-for target points both off the boundary~\eqref{eqn:velocityDLP} and on
-the boundary~\eqref{eqn:DLP}, the shear
-stress~\eqref{eqn:shearStressDLP}, the
+for for the velocity at target points both off the
+boundary~\eqref{eqn:velocityDLP} and on the boundary~\eqref{eqn:DLP},
+the shear stress~\eqref{eqn:shearStressDLP}, the
 vorticity~\eqref{eqn:vorticityDLP}, the pressure both off and on the
@@
 
-The integrands of each of these integrals, except for the resistivity,
-are smooth and periodic.  Therefore, the trapezoid rule guarantees
-spectral accuracy~\cite{tre-wei2014}.  However, before the trapezoid
-rule can be applied, singularity subtraction and odd-even
-integration~\cite{sid-isr1988} method must be used.  In addition, when
-the target point is near $\bd\Omega$, a near-singular integration scheme
-must be used.
+All the integrands, except for the resistivity, are periodic, so the
+trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.
+However, before the trapezoid rule can be applied, singularity
+subtraction and odd-even integration~\cite{sid-isr1988} must be used.
+In addition, when the target point is near $\bd\Omega$, a near-singular
+integration scheme must be used.
 
+\todo[inline]{Organize as first doing points on the boundary (velocity,
+shear stress, pressure, drag) and the points off the boundary (velocity,
+vorticity, pressure, resistivity)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Velocity}
@@
 where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
-vector at $\xx \in \bd\Omega$.  The equations for the strengths of the
+vector at $\xx \in \bd\Omega$.  The strengths of the
 Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are
@@
 \end{equation}
-for $i=1,\ldots,N$, $k=1,\ldots,M$.
+for $i=1,\ldots,N$, $k=1,\ldots,M$.  Since all the integrands are smooth
+and periodic, by using the trapezoid rule, we are guaranteed that the
+numerical solutions converges to the true solution with spectral
+accuracy.
 
 The dense linear system~\eqref{eqn:completed_BIE_discretized} is solved
-iteratively with GMRES.  The most expensive part is computing the $N$
-term sum for all target points.  A direct summation would require
-$\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$ by using the
-Fast Mutlipole method for the Stokes double-layer
+iteratively with GMRES~\cite{saa-sch1986}.  The most expensive part is
+computing the $N$ term sum for all target points.  A direct summation
+would require $\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$
+by using the Fast Mutlipole method for the Stokes double-layer
 potential~\cite{gre-rok1987,rac-???} \todo[inline]{sent email to Manas
@@
 
+To compute the velocity at an interior point $\xx \in \Omega$, the
+integrand is periodic and smooth, so the trapezoid rule rule achieves
+spectral accuracy.  Therefore, the velocity at a target points $\xx \in
+\Omega$ is approximate by
+\begin{align*}
+  \uu(\xx) = \sum_{j=1}^N K(\xx,\xx_j) \eeta(\xx_j) \Delta s_j.
+\end{align*}
+If the velocity needs to be computed at $N_\tar$ points in $\Omega$,
+where $N_\tar$ is large, the FMM is used to reduce the complexity from
+$\bigO(N_\tar N)$ to $\bigO(N_\tar + N)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Shear Stress}
@@
 \end{align*}
-has a singularity that is asymptotic to $\bigO(\rho^2)$ when $\yy
-\rightarrow \xx$.  The strength of this singularity can be reduced  by
-using the fact that a velocity field due to a constant density function
-is constant~\cite{poz1992}.  Therefore, the first part of the
-deformation tensor can be evaluated as 
+has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
+\rightarrow \xx$.  The singularity strength can be reduced since the
+velocity corresponding to a constant density function is
+constant~\cite{poz1992}.  Therefore, the deformation tensor of the
+double-layer potential is equivalent to
 \begin{align*}
@@
 This expression for the deformation tensor has a singularity that is
-asymptotic to $\bigO(\rho)$ when $\yy \rightarrow \xx$.  Finally, to
-achieve a spectrally accurate discretization for the deformation tensor,
-we use odd-even integration~\cite{sid-isr1988}.  That is, the
-deformation tensor due to the double-layer potential at a discretization
-point $\xx_i$ on body $\gamma_k$, with $i$ being odd, is approximated as
+asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
+to achieve spectral accuracy, we apply odd-even
+integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
+the double-layer potential at a discretization point $\xx_i$ on body
+$\gamma_k$, with $i$ being odd, is approximated as
 \begin{align*}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Vorticity}
 Since the vorticity is equivalent to the shear stress on $\bd\Omega$, we
-only need to compute the vorticity at target points $\xx \in \Omega$ in
-the interior.  This is done with the trapezoid rule by computing
+only need to compute the vorticity at target points at interior points
+$\xx \in \Omega$.  This is done with the trapezoid rule by computing
 \begin{align*}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Drag}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Resistivity}
@@
 \vsp{2}
-To handle boundary evolution, we use the {\thL}    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems \cite{hou-low-she1994}.
-Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).
+To handle boundary evolution, we use the {\thL}    method, which offers
+certain advantages in the ability to stabilize fluid-structure
+interaction problems \cite{hou-low-she1994}. Throughout this section, we
+use the following conventions: the bodies are parametrized in the CCW
+direction and the normal vector points into the bodies (our out of the
+fluid).
 
-In order to regularize boundary evolution, we modify the normal velocity in Eq.~(\ref{eqn:bodyEvolution}) as follows
+In order to regularize boundary evolution, we modify the normal velocity
+in Eq.~(\ref{eqn:bodyEvolution}) as follows
 \begin{equation}
@@
 \begin{equation}
-(x_s, y_s) = (\cos \theta, \sin \theta)
+\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin \theta \right)
 \end{equation}

### 2017-10-19 docs/TexNotes/Notes.tex
Working on chaning multistep to RK2.

@@
 \newcommand{\thhat}{\hat{\theta}}
+\newcommand{\dt}{\Delta t}
 
@@
 \begin{equation}
+\label{thODEs}
 \tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
@@
 \begin{equation}
-\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
+\mu_k = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
 \end{equation}
-so that the solution can be represented as
+so that our system becomes
 \begin{align}
-\thhat_k(t) & = \frac{1}{\mu} \int^t \mu \hat{N}_k dt'
-= \thhat_k(0) + \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun dt'' \right) \hat{N}_k \, dt'
-% LONGER FORM
-%& = \exp \left( -4 \eps \pi^2 k^2 \int_0^t \elfun(L) ds \right) \, 
-%\int_0^t \exp \left( 4 \eps \pi^2 k^2 \int_0^s \elfun(L) ds' \right) \hat{N}_k ds \\
+\label{Leq}
+& \tderiv{L}{t} = M \\
+\label{theq}
+& \tderiv{}{t}\left( \mu_k \theta_k \right) = \mu_k \hat{N}_k
 \end{align}
-where $t'$ and $t''$ are simply dummy variables for integration. We can get the exact relationship
+We discretize Eqs.~(\ref{Leq})--(\ref{theq}) with a second-order Runge-Kutta method (the midpoint RK2). In the first step, we go from time $t_n$ and take a half-step to $t_{n+1/2}$
+\begin{align}
+& L^{(n+1/2)}  = L^{(n)} + \frac{1}{2}\dt \, M^{(n)} \\
+& \theta_k^{(n+1/2)} = \nu \left( \theta_k^{(n)} + \frac{1}{2} \dt \,  \hat{N}_k^{(n)} \right)
+\end{align}
+Here, we have introduced
 \begin{equation}
-\thhat_k(t + \Delta t) = \thhat_k(t) 
-+ \int_t^{t+\Delta t} \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^{t+\Delta t} \elfun dt'' \right) \hat{N}_k \, dt'
+\nu = \frac{\mu_k^{(n)}}{\mu_k^{(n+1/2)}} = \exp \left( -4 \eps \pi^2 k^2 \int_{t_n}^{t_{n+1/2}} \zeta \, dt \right)
+\end{equation}
+Discretizing with trapezoid rule (and using the fact that $L$ can be solved for first to get $L^{(n+1/2)}$) gives
+\begin{equation}
+\nu = \exp \left(-2 \eps \pi^2 k^2 \dt \left( \elfun^{(n+1/2)} + \elfun^{n}\right)\right)
+\end{equation}
+Then we take the second step to $t_{n+1}$ as follows
+\begin{align}
+& L^{(n+1)}  = L^{(n)} + \dt \, M^{(n+1/2)} \\
+& \theta_k^{(n+1)} = \nu \left( \theta_k^{(n)} + \dt \,  \hat{N}_k^{(n+1/2)} \right)
+\end{align}
+where now we have
+\begin{equation}
+\nu = \frac{\mu_k^{(n)}}{\mu_k^{(n+1)}} = \exp \left( -4 \eps \pi^2 k^2 \int_{t_n}^{t_{n+1}} \zeta \, dt \right)
+\end{equation}
+which when discretized becomes
+\begin{equation}
+\nu = \exp \left(-4 \eps \pi^2 k^2 \dt \left( \elfun^{(n+1)} + \elfun^{n}\right)\right)
 \end{equation}

### 2017-10-19 julia/basic.jl

@@ -8,9 +8,7 @@ end
 # ThetaLenType: includes the geometry data for each body and memory terms.
 type ThetaLenType
 	theta::Vector{Float64}; len::Float64; xsm::Float64; ysm::Float64;
-	xx::Vector{Float64}; yy::Vector{Float64};
-	atau::Vector{Float64}; mterm::Float64; nterm::Vector{Float64}; 
-	xsmdot::Float64; ysmdot::Float64;
+	xx::Vector{Float64}; yy::Vector{Float64}; atau::Vector{Float64}; 
 end
 # ThLenDenType: includes the vector of all thlen's and the density function.
 type ThLenDenType
@@ -32,11 +30,13 @@ function new_thlenvec(nbods::Int)
 	return [new_thlen() for nn=1:nbods]
 end
 function new_thlen()
-	return ThetaLenType(evec(),0.,0.,0.,evec(),evec(),evec(),0.,evec(),0.,0.)
+	return ThetaLenType(evec(),0.,0.,0.,evec(),evec(),evec())
 end
 function evec()
 	return Array(Float64,0)
 end
+
+
 # Copy all contents from thlen1 to thlen2.
 function copy_thlen!(thlen1::ThetaLenType, thlen2::ThetaLenType)
 	thlen2.theta = thlen1.theta
@@ -59,12 +59,6 @@ Computes the smoothed stress atau and saves it in thlenden.thlenvec.atau. =#
 function getstress!(thlenden::ThLenDenType, params::ParamType, olddensity::Vector{Float64}=evec())
 	# Compute the density (if not loaded already).
 	compute_density!(thlenden, params, olddensity)
-	
-
-	# Also compute the density on the rotated grid to save in data files.
-	#compute_denrot!(thlenden, params)
-	
-
 	# Compute the stress.
 	tau = compute_stress(thlenden, params.nouter)	
 	# Smooth atau and save it in each of the thlen variables.

### 2017-10-19 julia/main.jl

@@ -14,27 +14,28 @@ function erosion()
 	thlenden0,params,paramvec,nsteps,nout,datafolder,plotfolder = startup()
 	# Begin the erosion computation with the RK starter.
 	t0 = time()
-	thlenden1 = RKstarter!(thlenden0, params)
 	plotnsave(thlenden0,params,paramvec,datafolder,plotfolder,0.,0)
-	# Enter the time loop to use the multi-step method.
+	
+	# Enter the time loop and apply RK2.
 	nfile = 1
 	for nn = 1:nsteps
+
+
+
+
 		# Compute the density function and stress for thlenden1.
 		getstress!(thlenden1,params)
 		# Plot and save the data in thlenden1 if appropriate.
 		if mod(nn,nout)==0
-			tt = nn*params.dt
+			tt = ???
+			compute_denrot!(thlenden, params)	
 			paramvec[end] = (time()-t0)/60.
 			plotnsave(thlenden1,params,paramvec,datafolder,plotfolder,tt,nfile)
 			nfile += 1
 		end
 		# Gracefully exit if all of the bodies have disappeared.
 		if endof(thlenden1.thlenvec)==0; break; end
-		# Advance the thlen vectors.
-		advance_thetalen!(thlenden1,thlenden0,params)
 	end
-	# Post-process to compute the drag and other quantities.
-	#postprocess("run")
 	return
 end
 

### 2017-10-19 julia/thetalen.jl

@@ -21,82 +21,44 @@ function cdfscale(len::Float64)
 	return 1./log(2*pi/len)
 end
 
-#--------------- MULTISTEP METHOD FOR THETA AND LEN ---------------#
-# advance_thetalen!: Dispatch for ThLenDenType.
-function advance_thetalen!(thlenden1::ThLenDenType, thlenden0::ThLenDenType, params::ParamType)
-	advance_thetalen!(thlenden1.thlenvec, thlenden0.thlenvec, params)
-	thlenden0.density = thlenden1.density
-	thlenden1.density = evec()
-	thlenden1.denrot = evec()
-	return
-end
-# advance_thetalen!: Dispatch for vectors of ThetaLenType to handle multiple bodies.
-function advance_thetalen!(thlenvec1::Vector{ThetaLenType}, thlenvec0::Vector{ThetaLenType}, params::ParamType)
-	# Call advance_thetalen for each element of the thlenvec.
-	for nn = 1:endof(thlenvec0)
-		advance_thetalen!(thlenvec1[nn],thlenvec0[nn],params)
-	end
-	# Remove curves with non-positive length.
-	trimthlenvec!(thlenvec1, thlenvec0)
-	return
-end
-#= advance_thetalen: Advance theta and len from time-step n=1 to n=2.
-This is a multi-step method and uses some values from n=0 too.
-Note: thlen1 must already be loaded with the correct atua, which is used in getmn!() =#
-function advance_thetalen!(thlen1::ThetaLenType, thlen0::ThetaLenType, params::ParamType)
-	# Extract the needed variables.
-	dt, m0, len1 = params.dt, thlen0.mterm, thlen1.len
-	# Calculate mterm and nterm at time n=1.
-	m1 = getmn!(thlen1,params.epsilon)
-	# Update len with an explicit, multistep method.
-	len2 = len1 + 0.5*dt*(3*m1-m0)
-	# Create a new ThetaLenType variable and save the new len.
-	thlen2 = new_thlen()
-	thlen2.len = len2
-	# Update theta with a multistep, integrating-factor method.
-	advance_theta!(thlen2,thlen1,thlen0,params)
-	# Update surface-mean coordinates with an explicit, multistep method.
[…]

### 2017-10-19 julia/thetalen.jl
Still working

@@ -14,12 +14,6 @@ I use the same convention for tangential and normal vectors as Shelley 1994.
 That is, I assume the curve is parameterized in the counter-clockwise (CCW) direction, 
 and I use the inward pointing normal vector. =#
 
-#= cdfscale: The function to scale the curvature-driven flow appropriately with the shear stress. 
-2D Stokes: cdfscale = 1/log(W/L), where W > L is lengthscale of 3rd dimension.
-3D Stokes, cdfscale = 1; high Reynolds, cdfscale = sqrt(L) =#
-function cdfscale(len::Float64)
-	return 1./log(2*pi/len)
-end
 
 
 
@@ -29,7 +23,7 @@ function RK2(thld0::ThLenDenType)
 	getstress!(thld05, params)
 	thld1 = feuler(thld0, dt, thld05)
 end
-
+# feuler: Update ThLenDenType with forward Euler and integrating factor.
 function feuler(thld0::ThLenDenType, dt, derivs::ThLenDenType)
 	npts, nbods = getnvals(thld0.thlenvec)
 	thlv1 = new_thlenvec(npts)
@@ -39,15 +33,29 @@ function feuler(thld0::ThLenDenType, dt, derivs::ThLenDenType)
 	thld1 = new_thlenden(thlv1)
 	return thld1
 end
-
+# feuler: Update theta and len with forward Euler and integrating factor.
 function feuler(thl0::ThetaLenType, dt::Float64, atau::Vector{Float64})
+	th0, len0 = thl0.theta, thl0.len
+	xsm0, ysm0 = thl0.xsm, thl0.ysm
 	mterm, nterm, xsmdot, ysmdot = getmn( ??? )
-	len05 = thl0.len + dt*mterm
-
-	theta05 = gaussfilter(thl0.theta + dt*nterm)
-
-
-
+	# Advance len first with forward Euler.
+	len1 = len0 + dt*mterm
+	# Advance theta with combination of integrating factor and forward Euler.
+	sigma = 2*pi*sqrt(epsilon*dt*(elfun(len0)+elfun(len1)))
+	th1 = gaussfilter(th0+dt*nterm, sigma)
+	# Advance xsm and ysm with forward Euler.
+	xsm1 = xsm0 + dt*xsmdot
+	ysm1 = ysm0 + dt*ysmdot 
+	# Save new values in thlen type.
+	thl1 = new_thlen()
[…]

### 2017-10-19 julia/postprocess.jl
Working hard

@@ -147,3 +147,21 @@ function setuptargets(xlocs::Vector{Float64}, ylocs::Vector{Float64})
 	targets.ytar = ytar
 	return targets
 end
+
+# getns: Get the normal and tangent directions.
+# Convention: CCW parameterization and inward pointing normal.
+function getns(theta::Vector{Float64})
+	# CCW tangent vector.
+	sx, sy = cos(theta), sin(theta)
+	# Inward pointing normal vector.
+	nx, ny = -sy, sx
+	return sx,sy,nx,ny
+end
+# getns: Get the normal and tangent directions on the rotated grid.
+function getnsrot(theta::Vector{Float64})
+	# CCW tangent vector.
+	sx, sy = -sin(theta), cos(theta)
+	# Inward pointing normal vector.
+	nx, ny = -sy, sx
+	return sx,sy,nx,ny
+end

### 2017-10-19 julia/thetalen.jl

@@ -15,37 +15,30 @@ That is, I assume the curve is parameterized in the counter-clockwise (CCW) dire
 and I use the inward pointing normal vector. =#
 
 
+#--------------- TIME-STEPPING ROUTINES ---------------#
+# rungekutta4: Take a step forward with 4th order Runge-Kutta.
+function rungekutta4(thld0::ThLenDenType, params::ParamType)
 
-
-
-
-
-
-
-
-
-
-function RK4(thld0::ThLenDenType, params::ParamType)
-	
-	epsilon = params.epsilon
+	# NEXT: specify dt adaptively
 
 	# Compute the derivatives k1.
 	k1 = getderivs(thld0, params)
 	# Compute the derivatives k2.
-	thldtemp = feuler(thld0, 0.5*dt, k1, epsilon)
+	thldtemp = feuler(thld0, 0.5*dt, k1, params.epsilon)
 	k2 = getderivs(thldtemp, params)
 	# Compute the derivatives k3.
-	thldtemp = feuler(thld0, 0.5*dt, k2)
+	thldtemp = feuler(thld0, 0.5*dt, k2, params.epsilon)
 	k3 = getderivs(thldtemp, params)
 	# Compute the derivatives k4.
-	thldtemp = feuler(thld0, dt, k3)
+	thldtemp = feuler(thld0, dt, k3, params.epsilon)
 	k4 = getderivs(thldtemp, params)
 	# Compute the average derivatives and take the RK4 step.
 	kavg = getkavg(k1,k2,k3,k4)
-	thld1 = feuler(thld0, dt, kavg)
+	thld1 = feuler(thld0, dt, kavg, params.epsilon)
 	return thld1
 end
-# feuler: Take a step of forward Euler with the derivatives specified by dvec.
+#= feuler: Take a step of forward Euler for all of the bodies.
+The derivatives specified by dvec. =#
 function feuler(thld0::ThLenDenType, dt::Float64, dvec::Vector{DerivsType}, epsilon::Float64)
 	npts, nbods = getnvals(thld0.thlenvec)
 	thlv1 = new_thlenvec(nbods)
@@ -59,8 +52,8 @@ function feuler(thld0::ThLenDenType, dt::Float64, dvec::Vector{DerivsType}, epsi
 		# Advance len with forward Euler first.
 		len1 = len0 + dt*mterm
 		# Advance theta with combination of integrating factor and forward Euler.
[…]

### 2017-10-19 docs/methods/erosion_methods.tex
worked on numerics section of methods paper

@@
 proportional to the absolute value of the shear stress.  The constant of
-proportionality sets the time scale, and we set its value to be -1
+proportionality sets the time scale, and we set its value to be 1
 \begin{align}
@@
     \nn \cdot \eeta(\yy) \,ds_\yy.
+    \label{eqn:pressureDLP}
 \end{align}
@@
 and the pressure due to the rotlets is zero.  Therefore, the pressure is
-\begin{equation}
-\label{eqn:pressureDLP}
-\begin{aligned}
+\begin{align*}
   p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
@@
               p^{S}(\xx), && \xx \in \bd\Omega.
-\end{aligned}
-\end{equation}
+\end{align*}
 
@@
 \subsubsection{Resistivity}
+\begin{align}
+  some equation
+  \label{eqn:resistivity}
+\end{align}
 
@@
 
+In Section~\ref{sec:spatial_discretization}, we describe how the
+geometry is represented.  Then, Sections~\ref{sec:on_boundary}
+and~\ref{sec:off_boundary} describe how the velocity and other
+quantities of interest are computed at points on and off the boundary,
+respectively.  Then, in Section~\ref{sec:thetaL}, methods used to update
+the shape are described.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Spatial Discretization}
+\label{sec:spatial_discretization}
 Each body is represented with at $N_\iin$ points as the Fourier series
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quadrature} 
-Integrals that need to be approximated are the double-layer potential
-for for the velocity at target points both off the
-boundary~\eqref{eqn:velocityDLP} and on the boundary~\eqref{eqn:DLP},
-the shear stress~\eqref{eqn:shearStressDLP}, the
-vorticity~\eqref{eqn:vorticityDLP}, the pressure both off and on the
-boundary~\eqref{eqn:pressureDLP}, the drag~\eqref{eqn:drag}, and the
-resistivity.   The shear stress, pressure, and drag must also be
-computed using quadrature, and this can be interpreted as a
-post-processing step once the density function, Stokeslets, and rotlets
-are computed.
+\subsection{Quadrature: On Boundary Calculations} 
+\label{sec:on_boundary}
+We start by discussing the quadrature methods that are used to compute
+the velocity~\eqref{eqn:DLP}, shear stress~\ref{eqn:shearStressDLP},
+pressure~\eqref{eqn:pressureDLP}, and drag~\eqref{eqn:drag} at target
+points on the boundary of the domain.  The velocity on $\bd\Omega$ is
+required to solve the integral equation~\eqref{eqn:completed_BIE} for
+the density function, Stokeslets and rotlets.  Once these are computed,
+computing the shear stress, pressure, and drag is a post-processing
+step.
 
-All the integrands, except for the resistivity, are periodic, so the
-trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.
-However, before the trapezoid rule can be applied, singularity
-subtraction and odd-even integration~\cite{sid-isr1988} must be used.
-In addition, when the target point is near $\bd\Omega$, a near-singular
-integration scheme must be used.
-
-\todo[inline]{Organize as first doing points on the boundary (velocity,
-shear stress, pressure, drag) and the points off the boundary (velocity,
-vorticity, pressure, resistivity)}
+All these integrals involve integrands that are both periodic and
+smooth, so the trapezoid rule guarantees spectral
+accuracy~\cite{tre-wei2014}.  However, before the trapezoid rule can be
+applied, singularity subtraction and odd-even
+integration~\cite{sid-isr1988} must be used.
 
@@
       K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
-      \sum_{k=1}^M S[\llambda_k,\cc_k](\xx_i) +
-      \sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) + 
-      \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
+      \sum_{k=1}^M S[\llambda_k,\cc_k](\xx_i) \\
+      &\hspace{40pt}
+      +\sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) 
+      +\sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
       \nn(\xx_j))\eeta(\xx_j), \\
@@
 accuracy.
-
-The dense linear system~\eqref{eqn:completed_BIE_discretized} is solved
-iteratively with GMRES~\cite{saa-sch1986}.  The most expensive part is
-computing the $N$ term sum for all target points.  A direct summation
-would require $\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$
-by using the Fast Mutlipole method for the Stokes double-layer
-potential~\cite{gre-rok1987,rac-???} \todo[inline]{sent email to Manas
-asking about this}.  Since we are discretizing a second-kind integral
-equation, the number of GMRES iterations is bounded independent of
-$N$~\cite{cam-ips-kel-mey-xue1996}, and the overall complexity for
-solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
-
-To compute the velocity at an interior point $\xx \in \Omega$, the
-integrand is periodic and smooth, so the trapezoid rule rule achieves
-spectral accuracy.  Therefore, the velocity at a target points $\xx \in
-\Omega$ is approximate by
-\begin{align*}
-  \uu(\xx) = \sum_{j=1}^N K(\xx,\xx_j) \eeta(\xx_j) \Delta s_j.
-\end{align*}
-If the velocity needs to be computed at $N_\tar$ points in $\Omega$,
-where $N_\tar$ is large, the FMM is used to reduce the complexity from
-$\bigO(N_\tar N)$ to $\bigO(N_\tar + N)$.
 
@@
 $\gamma_k$, with $i$ being odd, is approximated as
-\begin{align*}
+\begin{align}
   \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_k}
@@
     K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
-\end{align*}
+  \label{eqn:stressOddEven}
+\end{align}
 and a similar approximation is used when $i$ is even.  The deformation
@@
 and taking the inner product with the tangent direction.
+
+\todo[inline]{discuss how we handle jump condition ... Fourier
+differentiation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Pressure}
+Similar to the shear stress, the singularity of the pressure
+corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
+too strong for the trapezoid rule to be directly applied.  Therefore, we
+again subtract a constant density function and write the pressure as
+\begin{align*}
+  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
+    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
+\end{align*}
+Then, identical to how the shear stress is
+computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
+evaluate this layer potential for pressure.
+
+\todo[inline]{discuss how we handle jump condition ... Fourier
+differentiation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Drag}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Quadrature: Off Boundary Calculations} 
+\label{sec:off_boundary}
+To analyze the flow, we compute quantities at target points that are in
+the interior of the domain.  In particular, we develop numerical methods
+to compute the velocity~\eqref{eqn:velocityDLP},
+pressure~\eqref{eqn:pressureDLP}, vorticity~\eqref{eqn:vorticityDLP} and
+resistivity~\eqref{eqn:resistivity}.
+
+Similar to when the target points are on the boundary of the domain, all
+the integrals, except for the resistivity, involve integrands that are
+both periodic and smooth.  However, when the target points are close to
+the boundary of the domain, the integrand becomes nearly-singular, and
+these large derivatives result in a loss of accuracy that needs to be
+rectified.  We will be adopting a near-singular integration scheme that
+allows us to compute all quantities of interest sufficiently close to
+$\bd\Omega$ for the results we are untested in.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Near-singular integration}
+To accurately compute quantities such as the velocity at points $\xx \in
+\Omega$, we adopt a near-singular integration scheme entirely based on
+upsampling.  Since we are only interested in computing the velocity and
+vorticity for visualizing the flow, and the pressure is only required
+far away from any boundary, only a finite amount of upsampling is
+required to achieve an acceptable error.
+
+Computing the velocity, pressure, and vorticity at a point $\xx \in
+\Omega$ requires evaluating the layer potential
+\begin{align*}
+  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy,
+\end{align*}
+where $\phi$ is either the velocity, pressure, or vorticity, and the
+kernel $K$ is in
+equations~\eqref{eqn:velocityDLP},~\eqref{eqn:vorticityDLP},
+and~\eqref{eqn:pressureDLP}.  This integral is approximated with a
+trapezoid rule, which can be easily done with the $N$ points where the
+density function has been solved
+\begin{align}
+  \phi(\xx) \approx \sum_{k=1}^N q_k K(\xx,\yy_k),
+  \label{eqn:layerPotential}
+\end{align}
+where $q$ contains the quadrature weights, Jacobian, and density
+function.  Based on numerical experiments, the error of the $N$-point
+trapezoid rule is acceptable for points $\xx$ that are more than 5
+arclength spacings from $\bd\Omega$.
+
+For points that are closer than 5 arclength spacings to $\bd\Omega$, we
+use an upsampled trapezoid rule.  The required upsampling of the
+geometry and the density function is done with a Fourier interpolant.
+To minimize the number of discretization points that are used to
+approximate the layer potential~\eqref{eqn:layerPotential}, we the
+upsampling rate given in Table~\ref{tbl:upsampling}.  For points that
+are closer than $5/16$ of an arclength from $\bd\Omega$, a value of 0 is
+simply assigned to $\phi$.
+
+In future work, such as sedimenting eroding bodies, bodies will come too
+close to one another for upsampling to only used.  Therefore, we plan to
+implement a near-singular integration scheme that uses either
+near-singular interpolation~\cite{qua-bir2014a}, quadrature by
+expansion~\cite{klo-bar-gre-one2013}, Barycentric
+interpolation~\cite{bar-wu-vee2015}, or panel-based
+quadrature~\cite{hel-oja2008a}.
+
+\begin{table}[htpb]
+\centering
+\begin{tabular}{|c|ccccc|}
+  \hline
+  $d(\xx,\bd\Omega)$ &
+  $[5h,\infty]$ &
+  $[\frac{5}{2}h,5h]$ &
+  $[\frac{5}{4}h,\frac{5}{2}h]$ & 
+  $[\frac{5}{8}h,\frac{5}{4}h]$ &
+  $[\frac{5}{16}h,\frac{5}{8}h]$ \\ [2ex]
+  \hline
+  Upsample Rate & 1 & 2 & 4 & 8 & 16 \\
+  \hline
+\end{tabular}
+\caption{\label{tbl:upsampling}The upsampling rate used in our
+near-singular integration scheme.  $d(\xx,\bd\Omega)$ is the distance
+between a points $\xx \in \Omega$ and the boundary of the domain
+$\bd\Omega$, and $h$ is an arclength spacing.}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Resistivity}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Accelerating the Layer Potential Evaluations}
+To compute the velocity at an interior point $\xx \in \Omega$, the
+integrand is periodic and smooth, so the trapezoid rule rule achieves
+spectral accuracy.  Therefore, the velocity at a target points $\xx \in
+\Omega$ is approximate by
+\begin{align*}
+  \uu(\xx) = \sum_{j=1}^N K(\xx,\xx_j) \eeta(\xx_j) \Delta s_j.
+\end{align*}
+If the velocity needs to be computed at $N_\tar$ points in $\Omega$,
+where $N_\tar$ is large, the FMM is used to reduce the complexity from
+$\bigO(N_\tar N)$ to $\bigO(N_\tar + N)$.
+
+The dense linear system~\eqref{eqn:completed_BIE_discretized} is solved
+iteratively with GMRES~\cite{saa-sch1986}.  The most expensive part is
+computing the $N$ term sum for all target points.  A direct summation
+would require $\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$
+by using the Fast Mutlipole method for the Stokes double-layer
+potential~\cite{gre-rok1987,rac-???} \todo[inline]{sent email to Manas
+asking about this}.  Since we are discretizing a second-kind integral
+equation, the number of GMRES iterations is bounded independent of
+$N$~\cite{cam-ips-kel-mey-xue1996}, and the overall complexity for
+solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
 
@@
 kernel-independent FMM~\cite{yin-bir-zor2004}, will be incorporated.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Vorticity}
-Since the vorticity is equivalent to the shear stress on $\bd\Omega$, we
-only need to compute the vorticity at target points at interior points
-$\xx \in \Omega$.  This is done with the trapezoid rule by computing
-\begin{align*}
-  \omega(\xx_i) = \sum_{j=1}^N K_\omega (\xx_i,\xx_j) \cdot \eeta_j 
-    \Delta s_j,
-\end{align*}
-where
-\begin{align*}
-  K_\omega (\xx,\yy) =  -\frac{\rr}{\pi}
-    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}.
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Pressure}
-For the pressure, the double-layer potential is equivalent to
-\begin{align*}
-  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Drag}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Resistivity}
 

### 2017-10-20 docs/methods/erosion_methods.tex
small changes to numerics

@@
 where
-\begin{align*}
+\begin{align}
   J[\eeta](\xx_0) = \frac{1}{2}\pderiv{\eeta}{\ss} \cdot \ss
@@
   \end{array}\right].
-\end{align*}
+  \label{eqn:shearStressJump}
+\end{align}
 The deformation tensor of the Stokeslets and
@@
 by~\cite{qua-bir2014a}
-\begin{align*}
+\begin{align}
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
     \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
-\end{align*}
+  \label{eqn:pressureJump}
+\end{align}
 The pressure due to the Stokeslets is
@@
 tensor due to the Stokeslets and rotlets is given in
-equation~\eqref{eqn:shearStressSR}, and then the shear stress can be
-computed by computing the deformation tensor in the normal direction,
-and taking the inner product with the tangent direction.
-
-\todo[inline]{discuss how we handle jump condition ... Fourier
-differentiation}
+equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
+deformation tensor~\eqref{eqn:shearStressJump} is added, and the
+required arclength derivative is computed in Fourier space.  Then, the
+shear stress can be computed by computing the deformation tensor in the
+normal direction, and taking the inner product with the tangent
+direction.
 
@@
 computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
-evaluate this layer potential for pressure.
-
-\todo[inline]{discuss how we handle jump condition ... Fourier
-differentiation}
+evaluate this layer potential for pressure.  Finally, to add the jump
+condition~\eqref{eqn:pressureJump}, Fourier differentiation is used to
+compute the arclength derivative.
 

### 2017-10-23 docs/methods/erosion_methods.tex
worked on numerics and formulation sections

@@
   \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
-  \uu &= \ff,  && \xx \in \bd\Omega.
+  \uu &= \ff,  && \xx \in \bd\Omega,
 \end{alignat*}
@@
   \quad \text{and} \quad
-  R[\xi_k,\cc_k] = \frac{\rr_k^\perp}{\rho^2}\xi_k, 
+  R[\xi_k,\cc_k] = \frac{\rr^\perp}{\rho^2}\xi_k, 
   \quad k=1,\ldots,M,
@@
   \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
-  \, ds_\yy, \quad k=1,\ldots,M,
+  \, ds_\yy, \quad k=1,\ldots,M.
   \label{eqn:rotlet}
@@
 \end{subequations}
-where 
+Here,
 \begin{align*}
   \NN_0[\eeta](\xx) = \int_{\Gamma} 
-    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy,
+    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy
 \end{align*}
@@
 \subsubsection{Shear Stress}
-The shear stress is defined by
+The shear stress is
 \begin{align*}
@@
 \begin{align}
-  J[\eeta](\xx_0) = \frac{1}{2}\pderiv{\eeta}{\ss} \cdot \ss
-  \left[ \begin{array}{cc}
+  J[\eeta](\xx_0) = \frac{1}{2}\left(\pderiv{\eeta}{\ss} 
+    \cdot \ss\right) \left[ 
+  \begin{array}{cc}
     s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
@@
 condition, the shear stress is equivalent to the vorticity $w = v_x -
-u_y$.  Therefore, to compute the $w(\xx)$ for $\xx \in
-\overline{\Omega}$, we only need to compute $w(\xx)$ for $\xx \in
-\Omega$.  As we did for the shear stress, we compute the vorticity due
-to the double-layer potential, Stokeslets, and rotlets individually.
-The vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at
-$\xx \in \Omega$ is
+u_y$.  Therefore, to compute $w(\xx)$ for $\xx \in \overline{\Omega}$,
+we only need to compute $w(\xx)$ for $\xx \in \Omega$.  As we did for
+the shear stress, we compute the vorticity due to the double-layer
+potential, Stokeslets, and rotlets individually.  The vorticity of the
+double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
 \begin{align}
@@
 corresponds to a couterclockwise parameterization}
-Finally, with the pressure and shear stress, the drag on a single body
-with boundary $\gamma_k$ is
+With the pressure and shear stress, the drag on a single body with
+boundary $\gamma_k$ is
 \begin{align}
@@
 simulations with long time horizons, we use numerical methods that
-achieve spectral accuracy in space, second-order accuracy in time, and
+achieve spectral accuracy in space, fourth-order accuracy in time, and
 maintain an equispaced discretization of the bodies.
@@
 quantities of interest are computed at points on and off the boundary,
-respectively.  Then, in Section~\ref{sec:thetaL}, methods used to update
-the shape are described.
+respectively.  Section~\ref{sec:fmm} describes how the layer potentials
+are computed efficiently.  Finally, in Section~\ref{sec:thetaL}, methods
+used to update the shape are described.
 
@@
 \label{sec:spatial_discretization}
-Each body is represented with at $N_\iin$ points as the Fourier series
+Each body is represented with $N_\iin$ points as the Fourier series
 \begin{align*}
-  \xx^k(\theta) = \sum_{j = -N/2}^{N/2-1} \hat{x}_j^k e^{ij\theta},
+  \xx^k(\theta) = \sum_{j = -N_\iin /2}^{N_\iin /2-1} \hat{x}_j^k e^{ij\theta},
     \quad k=1,\ldots,M.
@@
   \frac{d\xx^k(\theta)}{d\theta} = 
-    \sum_{j = -N/2}^{N/2-1} ij\hat{x}_j^k e^{ij\theta},
+    \sum_{j = -N_\out /2}^{N_\out /2-1} ij\hat{x}_j^k e^{ij\theta},
     \quad k=1,\ldots,M.
@@
 We start by discussing the quadrature methods that are used to compute
-the velocity~\eqref{eqn:DLP}, shear stress~\ref{eqn:shearStressDLP},
+the velocity~\eqref{eqn:DLP}, shear stress~\eqref{eqn:shearStressDLP},
 pressure~\eqref{eqn:pressureDLP}, and drag~\eqref{eqn:drag} at target
@@
 computing the shear stress, pressure, and drag is a post-processing
-step.
-
-All these integrals involve integrands that are both periodic and
-smooth, so the trapezoid rule guarantees spectral
-accuracy~\cite{tre-wei2014}.  However, before the trapezoid rule can be
-applied, singularity subtraction and odd-even
+step.  All these integrals involve integrands that are periodic.  For
+smooth integrands, the trapezoid rule guarantees spectral
+accuracy~\cite{tre-wei2014}.  However, some of the integrands contain a
+singularity whose strength will be reduced with singularity subtraction,
+and then spectral accuracy is achieved with odd-even
 integration~\cite{sid-isr1988} must be used.
@@
 To numerically evaluate the completed double-layer
-potential~\eqref{eqn:completed_BIE}, we define $N = MN_\iin + N_\out$ to
-be the total number of discretization points of $\bd\Omega$.  The
-double-layer potential in~\eqref{eqn:DLP} is discretized with the
-trapezoid rule as
+potential~\eqref{eqn:completed_BIE}, we le $N = MN_\iin + N_\out$ be the
+total number of discretization points of $\bd\Omega$.  The double-layer
+potential in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
 \begin{align}
@@
     \llambda_k &= \sum_{\xx_i \in \gamma_k} \eeta(\xx_i) 
-      \Delta s_i \\ 
+      \Delta s_i, \\ 
     \mu_k &= \sum_{\xx_i \in \gamma_k}
-      {(\xx_i^k - \cc_k)}^\perp \cdot \eeta(\xx_i^k) \Delta s_i^k,
+      {(\xx_i - \cc_k)}^\perp \cdot \eeta(\xx_i) \Delta s_i,
   \end{aligned}
@@
 \begin{align*}
-  K_\ssigma(\xx,\yy) = \frac{1}{2\pi} \left(
+  K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
     2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
-    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) +
+    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn)
+    \right. \\ & \hspace{25pt}+ \left.
     \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
@@
 \subsection{Accelerating the Layer Potential Evaluations}
+\label{sec:fmm}
 To compute the velocity at an interior point $\xx \in \Omega$, the

### 2017-10-24 docs/methods/erosion_methods.tex
worked on formulation and numerics.  Wrote a plan for numerical examples

@@
 The pressure due to the Stokeslets is
-\begin{align*}
+\begin{align}
   p^S(\xx_0) = \sum_{k=1}^{M}\frac{\rr \cdot \llambda_k}{2\pi\rho^2},
-\end{align*}
+  \label{eqn:shearPressureSR}
+\end{align}
 and the pressure due to the rotlets is zero.  Therefore, the pressure is
@@
 shear stress can be computed by computing the deformation tensor in the
-normal direction, and taking the inner product with the tangent
-direction.
+normal vector, and taking the inner product with the tangent vector.
 
@@
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
+    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
+    \quad \xx \in \bd\Omega
 \end{align*}
@@
 computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
-evaluate this layer potential for pressure.  Finally, to add the jump
-condition~\eqref{eqn:pressureJump}, Fourier differentiation is used to
-compute the arclength derivative.
+evaluate this layer potential for pressure.  The pressure due to the
+Stokeslets are given in equation~\eqref{eqn:shearPressureSR}.  Finally,
+to add the jump condition~\eqref{eqn:pressureJump}, Fourier
+differentiation is used to compute the arclength derivative.
 
@@
 pressure~\eqref{eqn:pressureDLP}, vorticity~\eqref{eqn:vorticityDLP} and
-resistivity~\eqref{eqn:resistivity}.
-
-Similar to when the target points are on the boundary of the domain, all
-the integrals, except for the resistivity, involve integrands that are
-both periodic and smooth.  However, when the target points are close to
-the boundary of the domain, the integrand becomes nearly-singular, and
-these large derivatives result in a loss of accuracy that needs to be
-rectified.  We will be adopting a near-singular integration scheme that
-allows us to compute all quantities of interest sufficiently close to
-$\bd\Omega$ for the results we are untested in.
+resistivity~\eqref{eqn:resistivity}.  Since the target points are not on
+the boundary of the domain, all the integrals, except for the
+resistivity, involve integrands that are both periodic and smooth.
+However, when the target points are close to the boundary of the domain,
+the integrand becomes nearly-singular, and these large derivatives
+result in a loss of accuracy that needs to be rectified.  We will be
+adopting a near-singular integration scheme that allows us to compute
+all quantities of interest sufficiently close to $\bd\Omega$ for the
+quantities of interest.
 
@@
 equations~\eqref{eqn:velocityDLP},~\eqref{eqn:vorticityDLP},
-and~\eqref{eqn:pressureDLP}.  This integral is approximated with a
-trapezoid rule, which can be easily done with the $N$ points where the
-density function has been solved
+or~\eqref{eqn:pressureDLP}.  This integral is approximated with a
+trapezoid rule, 
 \begin{align}
-  \phi(\xx) \approx \sum_{k=1}^N q_k K(\xx,\yy_k),
+  \phi(\xx) = \sum_{k=1}^N q_k K(\xx,\yy_k),
   \label{eqn:layerPotential}
@@
 where $q$ contains the quadrature weights, Jacobian, and density
-function.  Based on numerical experiments, the error of the $N$-point
-trapezoid rule is acceptable for points $\xx$ that are more than 5
-arclength spacings from $\bd\Omega$.
+function.  Note that this sum can only be computed once
+equation~\eqref{eqn:completed_BIE} has been solved for the density
+function $\eeta$.  Based on numerical experiments, the error of the
+$N$-point trapezoid rule is acceptable for points $\xx$ that are more
+than 5 arclength spacings from $\bd\Omega$.
 
@@
 To minimize the number of discretization points that are used to
-approximate the layer potential~\eqref{eqn:layerPotential}, we the
-upsampling rate given in Table~\ref{tbl:upsampling}.  For points that
-are closer than $5/16$ of an arclength from $\bd\Omega$, a value of 0 is
-simply assigned to $\phi$.
-
-In future work, such as sedimenting eroding bodies, bodies will come too
-close to one another for upsampling to only used.  Therefore, we plan to
-implement a near-singular integration scheme that uses either
-near-singular interpolation~\cite{qua-bir2014a}, quadrature by
-expansion~\cite{klo-bar-gre-one2013}, Barycentric
-interpolation~\cite{bar-wu-vee2015}, or panel-based
-quadrature~\cite{hel-oja2008a}.
-
+approximate the layer potential~\eqref{eqn:layerPotential}, we use the
+same upsampling rate for all target points that are in the same dyadic
+interval (Table~\ref{tbl:upsampling}).  For points that are closer than
+$5/16$ of an arclength from $\bd\Omega$, a value of 0 is simply assigned
+to $\phi$.
 \begin{table}[htpb]
@@
 
+In future work, such as sedimenting eroding bodies, bodies will come too
+close to one another for upsampling to only used.  Therefore, we plan to
+implement a near-singular integration scheme that uses either
+near-singular interpolation~\cite{qua-bir2014a}, quadrature by
+expansion~\cite{klo-bar-gre-one2013}, Barycentric
+interpolation~\cite{bar-wu-vee2015}, or panel-based
+quadrature~\cite{hel-oja2008a}.  In addition, even with accurate
+quadrature, bodies can overlap because of discretization errors, and
+this can be avoided with contact algorithms such as, for example, recent
+work of Lu et al.~\cite{lu-rah-zor2017}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:fmm}
-To compute the velocity at an interior point $\xx \in \Omega$, the
-integrand is periodic and smooth, so the trapezoid rule rule achieves
-spectral accuracy.  Therefore, the velocity at a target points $\xx \in
-\Omega$ is approximate by
-\begin{align*}
-  \uu(\xx) = \sum_{j=1}^N K(\xx,\xx_j) \eeta(\xx_j) \Delta s_j.
-\end{align*}
-If the velocity needs to be computed at $N_\tar$ points in $\Omega$,
-where $N_\tar$ is large, the FMM is used to reduce the complexity from
-$\bigO(N_\tar N)$ to $\bigO(N_\tar + N)$.
-
-The dense linear system~\eqref{eqn:completed_BIE_discretized} is solved
-iteratively with GMRES~\cite{saa-sch1986}.  The most expensive part is
-computing the $N$ term sum for all target points.  A direct summation
-would require $\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$
-by using the Fast Mutlipole method for the Stokes double-layer
-potential~\cite{gre-rok1987,rac-???} \todo[inline]{sent email to Manas
-asking about this}.  Since we are discretizing a second-kind integral
-equation, the number of GMRES iterations is bounded independent of
-$N$~\cite{cam-ips-kel-mey-xue1996}, and the overall complexity for
+The bulk of the computational work is evaluating discretizations of
+layer potentials~\eqref{eqn:layerPotential} at a large number of points.
+If a direct summation method is used to evaluate these sums at $N_\tar$
+points, this requires $\bigO(NN_\tar)$ operations.  The layer potential
+that is evaluated most frequently is in the GMRES iteration where the
+layer potential $\DD$ is evaluated to compute the velocity at all points
+on the boundary must be evaluated~\eqref{eqn:DLP}.  To reduce the
+computational cost of this calculation, we use the Fast Multipole Method
+(FMM)~\cite{gre-rok1987, gre-gre-may1992} to reduce the complexity from
+$\bigO(N^2)$ to $\bigO(N)$.  Since we are discretizing a second-kind
+integral equation, the number of GMRES iterations is bounded independent
+of $N$~\cite{cam-ips-kel-mey-xue1996}, and the overall complexity for
 solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
 
-In our implementation, the deformation tensor is computed with a direct
-summation, and this requires $\bigO(N^2)$ operations.  Since this
-calculation is only computed once per time step, while the velocity is
-calculated at each GMRES iteration, the computational cost is
-manageable.  However, in future work, to simulate erosion in a dense
-packing of grains, a fast summation method, such as the
-kernel-independent FMM~\cite{yin-bir-zor2004}, will be incorporated.
+In our implementation, the deformation tensor and vorticity are computed
+with a direct summation, and this requires $\bigO(N^2)$ and $\bigO(N
+N_\tar)$ operations, respectively.  Since this calculation is only
+computed once per time step, while the velocity is calculated at each
+GMRES iteration, the computational cost is manageable.  However, in
+future work, to simulate erosion in a dense packing of grains, a fast
+summation method, such as the kernel-independent
+FMM~\cite{yin-bir-zor2004}, will be incorporated.
 
@@
 
+Runs to do
+\begin{itemize}
+  \item Single body
+  \begin{itemize}
+    \item Aspect ratio and opening angle
+    \item Drag and resistivity
+    \item Anisotropy
+    \item Vorticity
+  \end{itemize}
+  \item $\bigO(5)$ bodies
+  \begin{itemize}
+    \item Drag and resistivity
+    \item Anisotropy
+    \item Long channels between flat faces
+    \item Vorticity
+  \end{itemize}
+  \item $\bigO(50)$ bodies
+  \begin{itemize}
+    \item Drag and resistivity
+    \item Anisotropy
+    \item Vorticity
+  \end{itemize}
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions\label{s:conclusions}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{\bf Acknowledgments} The authors would like to thank Manas Rachh
+for supplying the FMM for the Stokes double-layer potential.
 

### 2017-11-08 docs/methods/erosion_methods.tex
Working on theta-L section.

@@
 \section{Introduction\label{s:intro}}
+
+\todo[inline]{Bryan, I think you should be first author on this paper.}
 
@@
 \end{equation}
+
 The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced.
@@
 \begin{align}
+\label{eqn:Levo0}
 & \tderiv{L}{t} = - \mean{\thalpha \Vn} \\
+\label{eqn:thetaevo0}
 & \pderiv{\theta}{t} = \frac{1}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
@@
 \end{equation}
+
 For simplicity, we introduce the variables
 \begin{align}
+\label{eq:M}
 & M = - \mean{\thalpha \Vn} \\
+\label{eq:N}
 & N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
@@
 \end{align} 
-Then the evolution equations can be expressed as
+Then Eq.~(\ref{eqn:thetaevo0}) can be rewritten as
+\begin{equation}
+\label{eqn:thetaevo1}
+\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
+\end{equation}
+Note that the $\elfun$ depends only on $L(t)$, and so the highest order derivative in Eq.~(\ref{eqn:thetaevo1}) is {\em linear} in the variable $\alpha$.
+This is the key to the {\thL} method, and allows us to use very stable, implicit methods for the stiff term.
+We will evolve $\theta$ in spectral space, and so introduce the transforms
 \begin{align}
-& \tderiv{L}{t} = M \\
-& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
+& \theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha} \\
+& N(\alpha,t)  = \sum_{k = -\infty}^{\infty} \hat{N}_k e^{2\pi i k \alpha}
 \end{align}
-We treat $\theta$ spectrally
-\begin{equation}
-\theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha}
-\end{equation}
-Then we get
+Equation (\ref{eqn:thetaevo1}) gives a set of ODEs for the coefficients
 \begin{equation}
@@
 \begin{equation}
-\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
+\label{eq:mu}
+\mu_k = \exp \left( 4 \eps \pi^2 k^2 \int \elfun \, dt \right)
 \end{equation}
-so that the solution can be represented as
+Then the evolution equations for $L$ and $\theta$ can be recast as the coupled system of ODEs
 \begin{align}
-\thhat_k(t) & = \frac{1}{\mu} \int^t \mu \hat{N}_k dt'
-= \thhat_k(0) + \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun dt'' \right) \hat{N}_k \, dt'
-% LONGER FORM
-%& = \exp \left( -4 \eps \pi^2 k^2 \int_0^t \elfun(L) ds \right) \, 
-%\int_0^t \exp \left( 4 \eps \pi^2 k^2 \int_0^s \elfun(L) ds' \right) \hat{N}_k ds \\
+\label{eqn:Levo2}
+& \tderiv{L}{t} = M \\
+\label{eqn:thetaevo2}
+& \tderiv{}{t}\left( \mu_k \theta_k \right) = \mu_k \hat{N}_k
 \end{align}
-where $t'$ and $t''$ are simply dummy variables for integration. We can get the exact relationship
-\begin{equation}
-\thhat_k(t + \Delta t) = \thhat_k(t) 
-+ \int_t^{t+\Delta t} \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^{t+\Delta t} \elfun dt'' \right) \hat{N}_k \, dt'
-\end{equation}
+We solve system (\ref{eqn:Levo2})--(\ref{eqn:thetaevo2}) for the variables $L$ and $\{ \mu_k \theta_k \}$ with a 4th-order Runge-Kutta method.
+At each stage, we must recover $\theta(\alpha,t)$ from  $\{ \mu_k \theta_k \}$ in order to compute the shear stress as needed in Eqs.~(\ref{eq:M}) and (\ref{eq:N}) for $M$ and $N$.
+For this, we compute $\mu_k$ from Eq.~(\ref{eq:mu}) using the trapezoid rule, then recover $\theta(\alpha, t)$ via a Gaussian filter....
 

### 2017-11-08 julia/ioroutines.jl

@@ -60,7 +60,8 @@ function save_params(params::ParamType, nfile::Int, outparamsfile::AbstractStrin
 	cputime = round( (time()-params.cput0)/60. , 2)
 	label1 = "# Input Parameters: geoinfile, nouter, tfin, dtout, dtfac, epsfac, sigfac, iffm, fixarea"
 	label2 = "# Calculated Parameters: npts, cntout, last file number, cputime (minutes)"
-	paramdata = [label1; paramvec; label2; params.npts; params.cntout; nfile; cputime]
+	paramdata = [label1; paramvec; label2; 
+		params.npts; params.cntout; nfile; cputime]
 	writedata(paramdata, outparamsfile)
 	return
 end

### 2017-11-08 julia/thetalen.jl

@@ -63,7 +63,7 @@ function feuler(thld0::ThLenDenType, dt::Float64, dvec::Vector{DerivsType}, epsi
 		# Advance theta with combination of integrating factor and forward Euler.
 		sig1 = 2*pi*sqrt(epsilon*dt*(elfun(len0)+elfun(len1)))
 		alpha = getalpha(npts)
-		th1 = gaussfilter(th0-2*pi*alpha+dt*nterm, sig1) + 2*pi*alpha
+		th1 = gaussfilter(th0-2*pi*alpha + dt*nterm, sig1) + 2*pi*alpha
 		# Advance xsm and ysm with forward Euler.
 		xsm1 = xsm0 + dt*xsmdot
 		ysm1 = ysm0 + dt*ysmdot 

### 2017-11-08 docs/methods/erosion_methods.tex
Just realized that my trapezoid rule for computing the integrating factor is only 2nd order in time, so it makes no sense to use RK4. I should just use RK2 so that everything is second order in time.

@@
 \end{align}
-We solve system (\ref{eqn:Levo2})--(\ref{eqn:thetaevo2}) for the variables $L$ and $\{ \mu_k \theta_k \}$ with a 4th-order Runge-Kutta method.
+We solve system (\ref{eqn:Levo2})--(\ref{eqn:thetaevo2}) for the variables $L$ and $\{ \mu_k \theta_k \}$ with a 2nd-order Runge-Kutta method.
 At each stage, we must recover $\theta(\alpha,t)$ from  $\{ \mu_k \theta_k \}$ in order to compute the shear stress as needed in Eqs.~(\ref{eq:M}) and (\ref{eq:N}) for $M$ and $N$.

### 2017-11-08 julia/main.jl

@@ -16,7 +16,7 @@ function erosion()
 	plotnsave(nfile,tt,thlenden,params)
 	
 	# Enter the time loop to apply Runge-Kutta.
-	while(tt <= params.tfin && endof(thlenden.thlenvec) > 0)
+	while(tt < params.tfin - 0.1*params.dt && endof(thlenden.thlenvec) > 0)
 		# Advance the variables forward one timestep with RK4.
 		nn += 1
 		println("\n\n\n\nTIME STEP ", nn)

### 2017-11-08 docs/methods/erosion_methods.tex
minior latex changes to paper

@@
 
+\author[Bryan]{Bryan D.~Quaife}
 \author[Nick]{M.~Nicholas J.~Moore}
-\author[Bryan]{Bryan D.~Quaife}
 \address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
@@
 \section{Introduction\label{s:intro}}
-
-\todo[inline]{Bryan, I think you should be first author on this paper.}
 
@@
 \begin{align*}
-  \xx^k(\theta) = \sum_{j = -N_\iin /2}^{N_\iin /2-1} \hat{x}_j^k e^{ij\theta},
-    \quad k=1,\ldots,M.
+  \xx^k(\alpha) = \sum_{j = -N_\iin /2}^{N_\iin /2-1} 
+    \hat{x}_j^k e^{ij\alpha}, \quad k=1,\ldots,M.
 \end{align*}
@@
 \begin{align*}
-  \frac{d\xx^k(\theta)}{d\theta} = 
-    \sum_{j = -N_\out /2}^{N_\out /2-1} ij\hat{x}_j^k e^{ij\theta},
+  \frac{d\xx^k(\alpha)}{d\alpha} = 
+    \sum_{j = -N_\out /2}^{N_\out /2-1} ij\hat{x}_j^k e^{ij\alpha},
     \quad k=1,\ldots,M.
@@
 In order to regularize boundary evolution, we modify the normal velocity
-in Eq.~(\ref{eqn:bodyEvolution}) as follows
+in Eq.~\eqref{eqn:bodyEvolution} as follows
 \begin{equation}
@@
 \end{equation}
-Substitution into Eq.~(\ref{eqn:Vn}) gives
+Substitution into Eq.~\eqref{eqn:Vn} gives
 \begin{equation}
@@
 \end{align}
-Inserting Eq.~(\ref{eqn:Vn2}) for the normal velocity gives
+Inserting Eq.~\eqref{eqn:Vn2} for the normal velocity gives
 \begin{equation}
@@
 \end{align} 
-Then Eq.~(\ref{eqn:thetaevo0}) can be rewritten as
+Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
 \begin{equation}
@@
 \end{equation}
-Note that the $\elfun$ depends only on $L(t)$, and so the highest order derivative in Eq.~(\ref{eqn:thetaevo1}) is {\em linear} in the variable $\alpha$.
+Note that the $\elfun$ depends only on $L(t)$, and so the highest order
+derivative in Eq.~\eqref{eqn:thetaevo1} is {\em linear} in the variable $\alpha$.
 This is the key to the {\thL} method, and allows us to use very stable, implicit methods for the stiff term.
@@
 \end{align}
-Equation (\ref{eqn:thetaevo1}) gives a set of ODEs for the coefficients
+\todo[inline]{Earlier, I assumed the geometry is $2\pi$ periodic.  Is it
+possible to use this convention cleanly for the presentation?  This
+allows us to avoid the long superscripts $2\pi i k \alpha$}
+Equation~\eqref{eqn:thetaevo1} gives a set of ODEs for the coefficients
 \begin{equation}
@@
 \end{align}
-We solve system (\ref{eqn:Levo2})--(\ref{eqn:thetaevo2}) for the variables $L$ and $\{ \mu_k \theta_k \}$ with a 2nd-order Runge-Kutta method.
-At each stage, we must recover $\theta(\alpha,t)$ from  $\{ \mu_k \theta_k \}$ in order to compute the shear stress as needed in Eqs.~(\ref{eq:M}) and (\ref{eq:N}) for $M$ and $N$.
-For this, we compute $\mu_k$ from Eq.~(\ref{eq:mu}) using the trapezoid rule, then recover $\theta(\alpha, t)$ via a Gaussian filter....
+We solve system~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} for the
+variables $L$ and $\{ \mu_k \theta_k \}$ with a 2nd-order Runge-Kutta
+method. At each stage, we must recover $\theta(\alpha,t)$ from  $\{
+  \mu_k \theta_k \}$ in order to compute the shear stress as needed in
+  Eqs.~\eqref{eq:M} and~\eqref{eq:N} for $M$ and $N$. For this, we
+  compute $\mu_k$ from Eq.~\eqref{eq:mu} using the trapezoid rule, then recover $\theta(\alpha, t)$ via a Gaussian filter....
 

### 2017-11-11 docs/methods/erosion_methods.tex
Worked on methods paper, theta-L evolution with RK2.

@@
 & N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
+\label{eq:elfun}
 & \elfun = \frac{1}{L^{2} \log \left(2\pi/L \right)}
@@
 \label{eqn:thetaevo2}
-& \tderiv{}{t}\left( \mu_k \theta_k \right) = \mu_k \hat{N}_k
+& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{N}_k
 \end{align}
-We solve system~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} for the
-variables $L$ and $\{ \mu_k \theta_k \}$ with a 2nd-order Runge-Kutta
-method. At each stage, we must recover $\theta(\alpha,t)$ from  $\{
-  \mu_k \theta_k \}$ in order to compute the shear stress as needed in
-  Eqs.~\eqref{eq:M} and~\eqref{eq:N} for $M$ and $N$. For this, we
-  compute $\mu_k$ from Eq.~\eqref{eq:mu} using the trapezoid rule, then recover $\theta(\alpha, t)$ via a Gaussian filter....
+We solve system \eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with a combination of an explicit, second-order Runge-Kutta method (RK2) and trapezoid rule to compute the integrating factor, $\mu_k$.
+There is not a unique second-order Runge-Kutta method, and we choose the {\em midpoint} version to maximize the smoothing effect of the curvature term.
+
+At the first stage of RK2 (the half step), we discretize Eqs.~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} as
+\begin{align}
+\label{eq:L12}
+& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = M^{(n)} \\
+& \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \thhat_k^{(n)}}{\Dt/2} = \hat{N}_k^{(n)}
+\end{align}
+where the superscript indicates the time step.
+For simplicity, we have chosen the constant of integration in the exponent of Eq.~\eqref{eq:mu} so that $\mu_k^{(n)} = 1$.
+At the next stage of RK2, we must compute $M^{(n+1/2)}$ and $\hat{N}_k^{(n+1/2)}$, which requires a call to the Stokes solver.
+Hence, we must compute compute $\mu_k^{(n+1/2})$, so that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the mid-step can be computed.
+To compute $\mu_k^{(n+1/2)}$, we use the trapezoid rule
+\begin{equation}
+\mu_k^{(n+1/2)} = \exp \left( \eps \pi^2 k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
+\end{equation}
+Notice in Eq.~\eqref{eq:elfun}, that $\elfun$ depends only on $L(t)$.
+Hence, we just need to update $L^{(n+1/2)}$ first via Eq.~\eqref{eq:L12}, and we have what we need to compute $\mu_k^{(n+1/2)}$.
+It is instructive to recast as
+\begin{equation}
+\thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{N}_k^{(n)} \right)
+\exp \left( - \eps \pi^2 k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
+\end{equation}
+so that the smoothing effect of the exponential is obvious. With $\thhat_k^{(n+1/2)}$ computed, it is now possible to compute $M^{(n+1/2)}$ and $\hat{N}_k^{(n+1/2)}$.
+
+Next, at the second stage of RK2, we discretize as
+\begin{align}
+& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = M^{(n+1/2)} \\
+& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \hat{N}_k^{(n+1/2)}
+\end{align}
+We again compute the integrating factor, $\mu_k^{(n+1)}$ via the trapezoid rule, giving
+\begin{equation}
+\thhat_k^{(n+1)} = \left( \thhat_k^{(n)} + \Dt \, \hat{N}_k^{(n+1/2)} \right)
+\exp \left( - 2 \eps \pi^2 k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1)} \right) \right)
+\end{equation}
 

### 2017-11-15 docs/methods/erosion_methods.tex
Fixed some mistakes
Changed the parameterization variable to be alpha = 2pi s / L in the methods paper

@@
 \end{equation}
-where $s$ is arc length. We also introduce the normalized arc length $\alpha = s / L$. In terms of these new variables, the curvature can be expressed as
+where $s$ is arc length. We also introduce the normalized arc length $\alpha = 2 \pi s / L$. In terms of these new variables, the curvature can be expressed as
 \begin{equation}
-\kappa = \frac{1}{L} \pderiv{\theta}{\alpha}
+\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha}
 \end{equation}
@@
 \label{eqn:Vn2}
-\Vn = \atau + \frac{\eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 2 \pi \right)
+\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
 \end{equation}
@@
 \label{eqn:Levo0}
-& \tderiv{L}{t} = - \mean{\thalpha \Vn} \\
+& \tderiv{L}{t} = - 2 \pi \mean{\thalpha \Vn} \\
 \label{eqn:thetaevo0}
-& \pderiv{\theta}{t} = \frac{1}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
+& \pderiv{\theta}{t} = \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
 \end{align}
@@
 \begin{equation}
-\pderiv{\theta}{t} = \frac{\eps}{L^{2} \log \left(2\pi/L \right)} \ppd{\theta}{\alpha} 
-+ \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
+\pderiv{\theta}{t} = \frac{4 \pi^2 \eps}{L^{2} \log \left(2\pi/L \right)} \ppd{\theta}{\alpha} 
++ \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
 \end{equation}
@@
 \label{eq:M}
-& M = - \mean{\thalpha \Vn} \\
+& M = - 2 \pi \mean{\thalpha \Vn} \\
 \label{eq:N}
-& N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
+& N = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
 \label{eq:elfun}
-& \elfun = \frac{1}{L^{2} \log \left(2\pi/L \right)}
+& \elfun = \frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
 \end{align} 
@@
 \begin{align}
-& \theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha} \\
-& N(\alpha,t)  = \sum_{k = -\infty}^{\infty} \hat{N}_k e^{2\pi i k \alpha}
+& \theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{ i k \alpha} \\
+& N(\alpha,t)  = \sum_{k = -\infty}^{\infty} \hat{N}_k e^{ i k \alpha}
 \end{align}
-\todo[inline]{Earlier, I assumed the geometry is $2\pi$ periodic.  Is it
-possible to use this convention cleanly for the presentation?  This
-allows us to avoid the long superscripts $2\pi i k \alpha$}
 Equation~\eqref{eqn:thetaevo1} gives a set of ODEs for the coefficients
 \begin{equation}
-\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
+\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{N}_k
 \end{equation}
@@
 \label{eq:mu}
-\mu_k = \exp \left( 4 \eps \pi^2 k^2 \int \elfun \, dt \right)
+\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right)
 \end{equation}
@@
 \begin{equation}
-\mu_k^{(n+1/2)} = \exp \left( \eps \pi^2 k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
+\mu_k^{(n+1/2)} = \exp \left( \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
 \end{equation}
@@
 \thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{N}_k^{(n)} \right)
-\exp \left( - \eps \pi^2 k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
+\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
 \end{equation}
@@
 & \frac{L^{(n+1)} - L^{(n)}}{\Dt} = M^{(n+1/2)} \\
-& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \hat{N}_k^{(n+1/2)}
+& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \mu_k^{(n+1/2)} \hat{N}_k^{(n+1/2)}
 \end{align}
 We again compute the integrating factor, $\mu_k^{(n+1)}$ via the trapezoid rule, giving
-\begin{equation}
-\thhat_k^{(n+1)} = \left( \thhat_k^{(n)} + \Dt \, \hat{N}_k^{(n+1/2)} \right)
-\exp \left( - 2 \eps \pi^2 k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1)} \right) \right)
-\end{equation}
+\begin{align}
+\thhat_k^{(n+1)} = & \thhat_k^{(n)}
+\exp \left( - \frac{1}{2} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1)} \right) \right) +  \\
+& \Dt \, \hat{N}_k^{(n+1/2)}
+\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n+1/2)} + \elfun^{(n+1)} \right) \right)
+\end{align}
+CHECK
 

### 2017-11-18 docs/methods/erosion_methods.tex
Wrote todo note
updated notation of k to \ell for bodies ... reserving k for wave number

@@
 consider flows that are confined by a solid wall $\Gamma$ that encloses
-$M$ eroding bodies.  The bodies are denoted as $\gamma_k$,
-$k=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup
+$M$ eroding bodies.  The bodies are denoted as $\gamma_\ell$,
+$\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup
 \gamma_M$.  Neglecting inertial forces, the dynamics of the fluid is
-fully characterized by the position of the bodies $\xx_k(s,t) \in
-\gamma_k$, where $s$ is the arclength and $t$ is time.  Given
-$\xx_k(s,t)$, $k=1,\ldots,M$, derived variables include the fluid
+fully characterized by the position of the bodies $\xx_\ell(s,t) \in
+\gamma_\ell$, where $s$ is the arclength and $t$ is time.  Given
+$\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid
 velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the
@@
     equations.  A no-slip boundary condition is imposed on each body
-    $\gamma_k$ whose unit normal points outward relative to the
+    $\gamma_\ell$ whose unit normal points outward relative to the
     geometry.  On the outer geometry $\Gamma$, a pipe flow is imposed.
@@
 \begin{align}
-  S[\llambda_k,\cc_k] = \frac{1}{4\pi} \left(-\log \rho \II + 
-    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_k
+  S[\llambda_\ell,\cc_\ell] = \frac{1}{4\pi} \left(-\log \rho \II + 
+    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_\ell
   \quad \text{and} \quad
-  R[\xi_k,\cc_k] = \frac{\rr^\perp}{\rho^2}\xi_k, 
-  \quad k=1,\ldots,M,
+  R[\xi_\ell,\cc_\ell] = \frac{\rr^\perp}{\rho^2}\xi_\ell, 
+  \quad \ell=1,\ldots,M,
   \label{eqn:stokeslet_rotlet}
 \end{align}
-where  $\rr = \xx - \cc_k$, $\cc_k$ is a point inside the $k^{th}$ body,
-$\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then, any solution of
-the Stokes equations with a Dirichlet boundary condition $\ff$ can be
-written in terms of the completed double-layer potential
+where  $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
+$\ell^{th}$ body, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then,
+any solution of the Stokes equations with a Dirichlet boundary condition
+$\ff$ can be written in terms of the completed double-layer potential
 \begin{align}
   \label{eqn:completed_DLP}
-  \uu(\xx) = \DD[\eeta](\xx) + \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
-              \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Omega,
+  \uu(\xx) = \DD[\eeta](\xx) + 
+    \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
+    \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
 \end{align}
@@
   \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
-      \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
-      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx) + \NN_0[\eeta](\xx),
+      \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
+      \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx) + \NN_0[\eeta](\xx),
       \quad \xx \in \bd\Omega, 
       \label{eqn:DLP}\\
-  \llambda_k &= \frac{1}{2\pi}\int_{\gamma_k} \eeta(\yy) \, ds_\yy,
-  \quad k=1,\ldots,M,
+  \llambda_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \eeta(\yy) \, ds_\yy,
+  \quad \ell=1,\ldots,M,
   \label{eqn:stokeslet} \\
-  \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
-  \, ds_\yy, \quad k=1,\ldots,M.
+  \xi_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \yy^\perp \cdot \eeta(\yy)
+  \, ds_\yy, \quad \ell=1,\ldots,M.
   \label{eqn:rotlet}
@@
 computed.  First, the governing equations~\eqref{eqn:erosionModel}
-require the shear stress along $\gamma_k$.  In addition, to study
+require the shear stress along $\gamma_\ell$.  In addition, to study
 characteristics of the flow, the vorticity, pressure, and drag, and
@@
   \begin{aligned}
-  \ssigma^S(\xx_0) &= \sum_{k=1}^{M}
-    \frac{\rr \cdot \llambda_k}{4\pi\rho^2} \left(
+  \ssigma^S(\xx_0) &= \sum_{\ell=1}^{M}
+    \frac{\rr \cdot \llambda_\ell}{4\pi\rho^2} \left(
     \II - \frac{2}{\rho^2} \rr \otimes \rr \right),  \\
-  \ssigma^R(\xx_0) &= -\sum_{k=1}^M
-    \frac{\xi_k}{\rho^4} \left(\rr \otimes \rr^\perp + 
+  \ssigma^R(\xx_0) &= -\sum_{\ell=1}^M
+    \frac{\xi_\ell}{\rho^4} \left(\rr \otimes \rr^\perp + 
     \rr^\perp \otimes \rr \right),
@@
 \end{equation}
-where $\rr = \xx - \cc_k$, $\cc_k$ is the point chosen inside body
-$\gamma_k$, and $\rho = \|\rr_k\|$.  Now that the deformation tensor of
-each component of the completed double-layer potential is computed, the
-shear stress at $\xx_0 \in \bd\Omega$ is
+where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is the point chosen inside body
+$\gamma_\ell$, and $\rho = \|\rr_\ell\|$.  Now that the deformation
+tensor of each component of the completed double-layer potential is
+computed, the shear stress at $\xx_0 \in \bd\Omega$ is
 \begin{align*}
@@
 \begin{align*}
-  w^S(\xx) = -\frac{1}{\pi} \sum_{k=1}^{M} 
-    \frac{\rr \cdot \llambda_k^\perp}{\rho^2},
+  w^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
+    \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2},
 \end{align*}
@@
 \begin{align}
-  p^S(\xx_0) = \sum_{k=1}^{M}\frac{\rr \cdot \llambda_k}{2\pi\rho^2},
+  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
   \label{eqn:shearPressureSR}
@@
 With the pressure and shear stress, the drag on a single body with
-boundary $\gamma_k$ is
+boundary $\gamma_\ell$ is
 \begin{align}
-  F_D = \int_{\gamma_k} (-p \nn + \tau \ss)\,ds.
+  F_D = \int_{\gamma_\ell} (-p \nn + \tau \ss)\,ds.
   \label{eqn:drag}
@@
 \begin{align*}
-  \xx^k(\alpha) = \sum_{j = -N_\iin /2}^{N_\iin /2-1} 
-    \hat{x}_j^k e^{ij\alpha}, \quad k=1,\ldots,M.
+  \xx^\ell(\alpha) = \sum_{k = -N_\iin /2}^{N_\iin /2-1} 
+    \hat{x}_k^\ell e^{ik\alpha}, \quad \ell=1,\ldots,M.
 \end{align*}
@@
 \begin{align*}
-  \frac{d\xx^k(\alpha)}{d\alpha} = 
-    \sum_{j = -N_\out /2}^{N_\out /2-1} ij\hat{x}_j^k e^{ij\alpha},
-    \quad k=1,\ldots,M.
+  \frac{d\xx^\ell(\alpha)}{d\alpha} = 
+    \sum_{k = -N_\out /2}^{N_\out /2-1} ik\hat{x}_k^\ell e^{ik\alpha},
+    \quad \ell=1,\ldots,M.
 \end{align*}
@@
       K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
-      \sum_{k=1}^M S[\llambda_k,\cc_k](\xx_i) \\
+      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) \\
       &\hspace{40pt}
-      +\sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) 
+      +\sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) 
       +\sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
       \nn(\xx_j))\eeta(\xx_j), \\
-    \llambda_k &= \sum_{\xx_i \in \gamma_k} \eeta(\xx_i) 
+    \llambda_\ell &= \sum_{\xx_i \in \gamma_\ell} \eeta(\xx_i) 
       \Delta s_i, \\ 
-    \mu_k &= \sum_{\xx_i \in \gamma_k}
-      {(\xx_i - \cc_k)}^\perp \cdot \eeta(\xx_i) \Delta s_i,
+    \mu_\ell &= \sum_{\xx_i \in \gamma_\ell}
+      {(\xx_i - \cc_\ell)}^\perp \cdot \eeta(\xx_i) \Delta s_i,
   \end{aligned}
 \end{equation}
-for $i=1,\ldots,N$, $k=1,\ldots,M$.  Since all the integrands are smooth
-and periodic, by using the trapezoid rule, we are guaranteed that the
-numerical solutions converges to the true solution with spectral
+for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  Since all the integrands are
+smooth and periodic, by using the trapezoid rule, we are guaranteed that
+the numerical solutions converges to the true solution with spectral
 accuracy.
@@
 the double-layer potential at a discretization point $\xx_i$ on body
-$\gamma_k$, with $i$ being odd, is approximated as
+$\gamma_\ell$, with $i$ being odd, is approximated as
 \begin{align}
-  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_k}
+  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_\ell}
     K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
-  \sum_{\substack{\xx_j \in \gamma_k \\ j \: \mathtt{even}}}
+  \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
     K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
@@
 \begin{align}
-  \phi(\xx) = \sum_{k=1}^N q_k K(\xx,\yy_k),
+  \phi(\xx) = \sum_{j=1}^N q_j K(\xx,\yy_j),
   \label{eqn:layerPotential}

### 2017-11-20 docs/methods/erosion_methods.tex
Added some figures to the paper
Added note

@@
 \end{equation}
+\todo[inline]{Change $N$ to something else $\mathcal{N}$}
 Note that the $\elfun$ depends only on $L(t)$, and so the highest order
@@
 
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.9 \textwidth]{./figs/fig3.pdf}
+\caption{Shrinking body and area.}
+\label{fig1}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
+\caption{Final shape.}
+\label{fig2}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+
 Runs to do

### 2017-11-29 docs/methods/erosion_methods.tex
small changes
NM

@@
 \end{itemize}
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.9 \textwidth]{./figs/20bod.pdf}
+\caption{20 bodies with vorticity}
+\label{}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 
@@
 \begin{align*}
-  \frac{d\xx^\ell(\alpha)}{d\alpha} = 
-    \sum_{k = -N_\out /2}^{N_\out /2-1} ik\hat{x}_k^\ell e^{ik\alpha},
-    \quad \ell=1,\ldots,M.
+  \frac{d\xx(\alpha)}{d\alpha} = 
+    \sum_{k = -N_\out /2}^{N_\out /2-1} ik\hat{x}_k e^{ik\alpha}.
 \end{align*}
@@
 \label{eqn:Vn}
-\Vn = \atau + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
+\Vn = \atau + \eps \mean{\atau} \left( \frac{L \kappa}{2\pi} - 1 \right)
+%\Vn = \atau + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
 \end{equation}
@@
 Since we have subtracted the mean curvature, $2\pi/L$, this term is area-preserving, so that the only material loss is due to the shear stress.
+\todo[inline]{Modify the text here.}
 We chose the prefactor $\log^{-1} \left(2\pi/L \right)$, so that, for 2D Stokes flow, this term scales the same as shear stress as $L \to 0$.
@@
 \label{eqn:Vn2}
-\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
+\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right)
+%\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
 \end{equation}
@@
 \begin{equation}
-\pderiv{\theta}{t} = \frac{4 \pi^2 \eps}{L^{2} \log \left(2\pi/L \right)} \ppd{\theta}{\alpha} 
-+ \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
+\pderiv{\theta}{t} = \frac{2\pi}{L} \left(
+\eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
 \end{equation}
@@
 \label{eq:elfun}
-& \elfun = \frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
+& \elfun = \frac{2 \pi  \mean{\atau}}{L}
+%\frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
 \end{align} 
@@
 Hence, we must compute compute $\mu_k^{(n+1/2})$, so that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the mid-step can be computed.
-To compute $\mu_k^{(n+1/2)}$, we use the trapezoid rule
+To compute $\mu_k^{(n+1/2)}$, we use the left-end-point rule (first order, consistent with first forward Euler step of RK2)
 \begin{equation}
-\mu_k^{(n+1/2)} = \exp \left( \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
+\mu_k^{(n+1/2)} = \exp \left( \epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
+%\exp \left( \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
 \end{equation}
+\todo[inline]{modify text below}
 Notice in Eq.~\eqref{eq:elfun}, that $\elfun$ depends only on $L(t)$.
@@
 \thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{N}_k^{(n)} \right)
-\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
+\exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
+%\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
 \end{equation}
@@
 \end{align}
-We again compute the integrating factor, $\mu_k^{(n+1)}$ via the trapezoid rule, giving
+We again compute the integrating factor, $\mu_k^{(n+1)}$ via the ( insert integration rule), giving
 \begin{align}
-\thhat_k^{(n+1)} = & \thhat_k^{(n)}
-\exp \left( - \frac{1}{2} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1)} \right) \right) +  \\
+\thhat_k^{(n+1)} = 
+& \thhat_k^{(n)}
+\exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
 & \Dt \, \hat{N}_k^{(n+1/2)}
-\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n+1/2)} + \elfun^{(n+1)} \right) \right)
+\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right)
+%& \thhat_k^{(n)}
+%\exp \left( - \frac{1}{2} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1)} \right) \right) +  \\
+%& \Dt \, \hat{N}_k^{(n+1/2)}
+%\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n+1/2)} + \elfun^{(n+1)} \right) \right)
 \end{align}

### 2017-11-29 julia/basic.jl

@@ -212,7 +212,7 @@ end
 function getnxyden(thlenden::ThLenDenType, nouter::Int, fixpdrop::Bool, rotation::Bool)
 	npts,nbods,xv,yv = getnxy(thlenden)
 	# Consider fixpdrop.
-	rescale = getrescale(thlenden, nouter, fixpdrop)
+	rescale = getumax(thlenden, nouter, fixpdrop)
 	# Consider rotation.
 	if rotation
 		xv,yv = xyrot(xv,yv)
@@ -222,16 +222,16 @@ function getnxyden(thlenden::ThLenDenType, nouter::Int, fixpdrop::Bool, rotation
 	end
 	return npts,nbods,xv,yv,density
 end
-# getrescale: Get the rescale factor.
-function getrescale(thlenden::ThLenDenType, nouter::Int, fixpdrop::Bool)
+# getumax: Get umax to rescael the density function.
+function getumax(thlenden::ThLenDenType, nouter::Int, fixpdrop::Bool)
 	# NOTE: With u = 1-y^2 and x0 = 2, the pressure drop is pdrop = 8.
-	rescale = 1.
+	umax = 1.
 	if fixpdrop
 		pdrop = getpdrop(thlenden, nouter)[1]
-		rescale =  10 * 8./pdrop
-		println("Fixing pdrop, rescale factor = ", rescale)
+		umax =  10 * 8./pdrop
+		println("Fixing pdrop, umax = ", umax)
 	end
-	return rescale
+	return umax
 end
 #= getpdrop: Calculate the pressure drop from -x0 to x0. 
 Also get the average flux while at it. =#

### 2017-11-29 julia/ioroutines.jl

@@ -204,35 +204,3 @@ function plot_curves(thlenvec::Vector{ThetaLenType}, figname::AbstractString)
 	return
 end
 
-#--------------- Tests for the theta vector ---------------#
-#= test_theta_means: Test that cos(theta) and sin(theta) have zero mean.
-These are conditions for theta to describe a closed curve 
-in the equal arc length frame. =#
-function test_theta_means(theta::Vector{Float64})
-	npts = endof(theta)
-	m1 = mean(cos(theta))
-	m2 = mean(sin(theta))
-	maxmean = maximum(abs([m1,m2]))
-	thresh = 20./npts
-	if maxmean > thresh
-		warn("theta means")
-		println("The max mean of sin, cos is: ", 
-			signif(maxmean,3), " > ", signif(thresh,3))
-	end
-	return
-end
-#= test_theta_ends: Test that the difference between the 
-first and last tangent angles is 2pi. =#
-function test_theta_ends(theta::Vector{Float64}, thresh::Float64 = 0.2)
-	# Use quadratic extrapolation to estimate theta at alpha=0 from both sides.
-	th0left = 15/8*theta[1] - 5/4*theta[2] + 3/8*theta[3]
-	th0right = 15/8*theta[end] - 5/4*theta[end-1] + 3/8*theta[end-2] - 2*pi
-	# Compare the two extrpaolations.
-	th0diff = abs(th0left - th0right)
-	if th0diff > thresh
-		warn("theta ends") 
-		println("The difference between the ends is: ", 
-			signif(th0diff,3), " > ", signif(thresh,3))
-	end
-	return
-end

### 2017-11-29 julia/spectral.jl

@@ -23,7 +23,7 @@ function kvec(nn::Integer, hmode=0)
 end
 #= specdiff: Compute the derivative of fx spectrally.
 Default: assumes that the length of the interval is 1.0 =#
-function specdiff(fx::Vector, intvlen::Float64=1.0)	
+function specdiff(fx::Vector, intvlen::Float64=2*pi)	
 	fh = fftnice(fx)
 	kv = kvec(length(fx), 0)
 	dfh = 2*pi*im * kv.*fh
@@ -34,7 +34,7 @@ end
 #= specint: Compute the antiderivative of fx spectrally.
 Assumes that the input fx has mean-zero and 
 forces the output Fx to have mean-zero. =#
-function specint(fx::Vector, intvlen::Float64=1.0)
+function specint(fx::Vector, intvlen::Float64=2*pi)
 	fh = fftnice(fx)
 	kv = kvec(length(fx), 0)
 	Fh = fh./(2*pi*im*kv)
@@ -44,23 +44,41 @@ function specint(fx::Vector, intvlen::Float64=1.0)
 	imagtest(Fx)
 	return real(Fx)*intvlen	
 end
-# gaussfilter: Apply a Gaussian filter of width sigma.
-function gaussfilter(fx::Vector, sigma::Float64)
-	fh = fftnice(fx)
-	kv = kvec(length(fx), 1)
-	fh .*= exp(-0.5*sigma^2 * abs(kv).^2)
-	fs = ifftnice(fh)
-	return real(fs)
-end
 # imagtest: Test that the imaginary part is negligible.
 function imagtest(fx::Vector, relthold::Float64=1e-8)
-	maximrel = maxabs(imag(fx))/maxabs(fx)
-	if maximrel > relthold
-		warn("imag part too big: ", maximrel)
-	end
-	return
+    maximrel = maxabs(imag(fx))/maxabs(fx)
+    if maximrel > relthold
+        warn("imag part too big: ", maximrel)
+    end
+    return
 end
-#= krasnyfilter: Apply a Krasny filter to the spectrum.
+
+
+# expsmooth: Equivalent to a Gaussian filter.
+function expsmooth(fx::Vector, factor::Float64)
+    fh = fftnice(fx)
+    kv = kvec(length(fx), 1)
+    fh .*= exp(-factor*abs(kv).^2)
+    fs = ifftnice(fh)
+    imagtest(fs)
+    return real(fs) 
+end
[…]

### 2017-11-29 julia/thetalen.jl

@@ -35,7 +35,11 @@ function timestep!(thld0::ThLenDenType, thld_derivs::ThLenDenType,
 		dt1::Float64, dt2::Float64, params::ParamType)
 	# Compute the time derivatives and umax = rescale factor.
 	dvec = getderivs(thld_derivs, params)
-	umax = getrescale(thld_derivs, params.nouter, params.fixpdrop)
+
+
+###	umax = getumax(thld_derivs, params.nouter, params.fixpdrop)	
+
+
 	# Remove small bodies if needed.
 	deletevec = delete_indices(thld0, dvec, dt1)
 	deleteat!(thld0.thlenvec, deletevec)
@@ -58,13 +62,22 @@ function timestep!(thld0::ThLenDenType, thld_derivs::ThLenDenType,
 		# Advance len first.
 		len1 = len0 + dt1*mterm
 		assert(len1 > 0.)	
+
+
+
+		# MODIFY
 		# Compute the sigmas for the Guassian filters.
 		sig1 = 2*pi*sqrt(epsilon*dt1*(elfun(len0,umax)+elfun(len1,umax)))
 		sig2 = 2*pi*sqrt(epsilon*dt2*(elfun(lenderivs,umax)+elfun(len1,umax)))
 		# Advance theta using integrating factor and explicit term.
 		alpha = getalpha(npts)
-		th1 = gaussfilter(th0-2*pi*alpha, sig1) + 2*pi*alpha
+		th1 = gaussfilter(th0 - alpha, sig1) + alpha
 		th1 += gaussfilter(dt1*nterm, sig2)
+
+
+
+
+
 		# Advance xsm and ysm with forward Euler.
 		xsm1 = xsm0 + dt1*xsmdot
 		ysm1 = ysm0 + dt1*ysmdot 
@@ -76,35 +89,55 @@ function timestep!(thld0::ThLenDenType, thld_derivs::ThLenDenType,
 	return thld1
 end
 
+
+
+# zetafun: How to scale the smoothing with len and matau = mean(abs(tau)).
+function zetafun(len::Float64, matau::Float64)
+	return 2*pi/len * matau
+end
+
+
+
+
 #--------------- ROUTINES TO SUPPORT TIMESTEPPING ---------------#
 # getderivs: Get the derivative terms for all of the bodies.
 function getderivs(thlenden::ThLenDenType, params::ParamType)
 	getstress!(thlenden, params)
-	umax = getrescale(thlenden, params.nouter, params.fixpdrop)
+
+
[…]

### 2017-12-04 docs/methods/erosion_methods.tex
Changes to latex methods paper.

@@
 simulations with long time horizons, we use numerical methods that
-achieve spectral accuracy in space, fourth-order accuracy in time, and
+achieve spectral accuracy in space, second-order accuracy in time, and
 maintain an equispaced discretization of the bodies.
@@
 \begin{align*}
-  \xx^\ell(\alpha) = \sum_{k = -N_\iin /2}^{N_\iin /2-1} 
-    \hat{x}_k^\ell e^{ik\alpha}, \quad \ell=1,\ldots,M.
+  \xx^\ell(\alpha) = \FourierSum \hat{x}_k^\ell e^{ik\alpha}, \quad \ell=1,\ldots,M.
 \end{align*}
@@
 \begin{align*}
-  \frac{d\xx(\alpha)}{d\alpha} = 
-    \sum_{k = -N_\out /2}^{N_\out /2-1} ik\hat{x}_k e^{ik\alpha}.
+  \frac{d\xx(\alpha)}{d\alpha} = \FourierSum ik\hat{x}_k e^{ik\alpha}.
 \end{align*}
@@
 
-In this section, we also describe our time stepping method and two
-regularization terms that are necessary to control the curvature of the
-bodies and to maintain spectral accuracy in space.
+% BRYAN'S ORIGINAL TEXT
+%In this section, we also describe our time stepping method and two regularization terms that are necessary to control the curvature of the bodies and to maintain spectral accuracy in space.
 
-Once the shear stress is computed, it is used to update the shape of the
-bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
-eliminate tangling and stretching of the mesh, we use a {\thL}
-formulation~\cite{hou-low-she1994} which is described in
-Section~\ref{sec:thetaL}.
+%Once the shear stress is computed, it is used to update the shape of the bodies according to the normal flow~\eqref{eqn:bodyEvolution}.
+To eliminate tangling and stretching of the mesh, we use a {\thL}formulation~\cite{hou-low-she1994} which is described in Section~\ref{sec:thetaL}.
 
-We use a quasi-static approximation so that the velocity field
-instantaneously changes with the changing geometry.  Therefore, we can
-alternate between the two main aspects of our simulation
-\begin{enumerate}
-  \item Given a geometry, compute the shear stress of along the boundary
-    of each of the bodies.
-  \item Given the shear stress, update the geometry according to the
-    erosion model.
-\end{enumerate}
+%We use a quasi-static approximation so that the velocity field instantaneously changes with the changing geometry.  Therefore, we can alternate between the two main aspects of our simulation
+%\begin{enumerate}
+%\item Given a geometry, compute the shear stress of along the boundary of each of the bodies.
+%\item Given the shear stress, update the geometry according to the erosion model.
+%\end{enumerate}
 
-\vsp{2}
 To handle boundary evolution, we use the {\thL}    method, which offers
@@
 \end{equation}
-Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body.
-The second term on the right acts to smooth bodies that have high-frequency oscillations.
-Since we have subtracted the mean curvature, $2\pi/L$, this term is area-preserving, so that the only material loss is due to the shear stress.
-\todo[inline]{Modify the text here.}
-We chose the prefactor $\log^{-1} \left(2\pi/L \right)$, so that, for 2D Stokes flow, this term scales the same as shear stress as $L \to 0$.
-Thus, the relative strength of the smoothing is always the same.
+Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean.
+The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity.
+Since a closed body has a mean curvature of $\mean{\kappa} = 2\pi / L$, the term in parentheses has mean zero.
+Thus, this term is area-preserving, so that the only material loss is due to the shear stress itself.
+In addition, we have scaled this term on the $\mean{\atau}$, the average absolute stress, so that it is always proportional to the true source of erosion $\atau$, even as bodies vanish (reword).
 
@@
 \label{eq:M}
-& M = - 2 \pi \mean{\thalpha \Vn} \\
+& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
 \label{eq:N}
-& N = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
+& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
 \label{eq:elfun}
@@
 \label{eqn:thetaevo1}
-\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
+\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
 \end{equation}
-\todo[inline]{Change $N$ to something else $\mathcal{N}$}
-Note that the $\elfun$ depends only on $L(t)$, and so the highest order
-derivative in Eq.~\eqref{eqn:thetaevo1} is {\em linear} in the variable $\alpha$.
-This is the key to the {\thL} method, and allows us to use very stable, implicit methods for the stiff term.
+Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}.
+This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.
 We will evolve $\theta$ in spectral space, and so introduce the transforms
 \begin{align}
-& \theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{ i k \alpha} \\
-& N(\alpha,t)  = \sum_{k = -\infty}^{\infty} \hat{N}_k e^{ i k \alpha}
+& \theta(\alpha,t) = \FourierSum \thhat_k e^{ i k \alpha} \\
+& \NLterm(\alpha,t)  = \FourierSum \hat{\NLterm}_k e^{ i k \alpha}
 \end{align}
@@
 \begin{equation}
-\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{N}_k
+\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{\NLterm}_k
 \end{equation}
@@
 \label{eqn:Levo2}
-& \tderiv{L}{t} = M \\
+& \tderiv{L}{t} = \Mterm \\
 \label{eqn:thetaevo2}
-& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{N}_k
+& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{\NLterm}_k
 \end{align}
-We solve system \eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with a combination of an explicit, second-order Runge-Kutta method (RK2) and trapezoid rule to compute the integrating factor, $\mu_k$.
-There is not a unique second-order Runge-Kutta method, and we choose the {\em midpoint} version to maximize the smoothing effect of the curvature term.
+We solve system \eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an explicit, second-order Runge-Kutta method (RK2).
+In particular, we choose the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature term.
 
@@
 \label{eq:L12}
-& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = M^{(n)} \\
-& \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \thhat_k^{(n)}}{\Dt/2} = \hat{N}_k^{(n)}
+& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)} \\
+& \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \thhat_k^{(n)}}{\Dt/2} = \hat{\NLterm}_k^{(n)}
 \end{align}
@@
 For simplicity, we have chosen the constant of integration in the exponent of Eq.~\eqref{eq:mu} so that $\mu_k^{(n)} = 1$.
-At the next stage of RK2, we must compute $M^{(n+1/2)}$ and $\hat{N}_k^{(n+1/2)}$, which requires a call to the Stokes solver.
-Hence, we must compute compute $\mu_k^{(n+1/2})$, so that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the mid-step can be computed.
+At the next stage of RK2, we must compute $\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$, which requires a call to the Stokes solver.
+Hence, we must compute $\mu_k^{(n+1/2})$, so that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the mid-step can be computed.
 To compute $\mu_k^{(n+1/2)}$, we use the left-end-point rule (first order, consistent with first forward Euler step of RK2)
@@
 \mu_k^{(n+1/2)} = \exp \left( \epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
-%\exp \left( \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
 \end{equation}
-\todo[inline]{modify text below}
-Notice in Eq.~\eqref{eq:elfun}, that $\elfun$ depends only on $L(t)$.
-Hence, we just need to update $L^{(n+1/2)}$ first via Eq.~\eqref{eq:L12}, and we have what we need to compute $\mu_k^{(n+1/2)}$.
 It is instructive to recast as
 \begin{equation}
-\thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{N}_k^{(n)} \right)
+\thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{\NLterm}_k^{(n)} \right)
 \exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
-%\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1/2)} \right) \right)
 \end{equation}
-so that the smoothing effect of the exponential is obvious. With $\thhat_k^{(n+1/2)}$ computed, it is now possible to compute $M^{(n+1/2)}$ and $\hat{N}_k^{(n+1/2)}$.
+so that the smoothing effect of the exponential is obvious. With $\thhat_k^{(n+1/2)}$ computed, it is now possible to compute $\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$.
 
@@
 \begin{align}
-& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = M^{(n+1/2)} \\
-& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \mu_k^{(n+1/2)} \hat{N}_k^{(n+1/2)}
+& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)} \\
+& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}
 \end{align}
@@
 \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
-& \Dt \, \hat{N}_k^{(n+1/2)}
+& \Dt \, \hat{\NLterm}_k^{(n+1/2)}
 \exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right)
-%& \thhat_k^{(n)}
-%\exp \left( - \frac{1}{2} \eps k^2 \Dt \left( \elfun^{(n)} + \elfun^{(n+1)} \right) \right) +  \\
-%& \Dt \, \hat{N}_k^{(n+1/2)}
-%\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( \elfun^{(n+1/2)} + \elfun^{(n+1)} \right) \right)
 \end{align}
-CHECK
 
-\vsp{5}
+\newpage
 \todo[inline]{Artificial Diffusion} 

### 2017-12-07 docs/methods/erosion_methods.tex
NM

@@
 \label{eqn:Vn}
-\Vn = \atau + \eps \mean{\atau} \left( \frac{L \kappa}{2\pi} - 1 \right)
-%\Vn = \atau + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
+\Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right)
 \end{equation}
@@
 \end{align}
-
-\newpage
-\todo[inline]{Artificial Diffusion} 
 \todo[inline]{Gaussian Filter}
@@
 \section{Results\label{s:results}}
+
+\subsection{Single-body validation results}
+
+\subsubsection{The uniform stress geometry}
+
+\subsubsection{The vanishing rate of area}
+In three-dimensional Stokes flow, the shear stress vanishes as
+\begin{equation}
+\tau_{3D} \sim \mu V/L
+\end{equation}
+However, this law must be modified for 2D flow, which represents 3D bodies of large extent.
+As the body vanishes, the walls have an ever decreasing influence.
+Thus, the stress must be consistent with free-space slender-body theory as it vanishes.
+The stress law consistent with slender body theory (a long cylinder held perpendicular to a flow) is
+\begin{equation}
+\tau_{2D} \sim \frac{4 \pi \mu V}{L \log(W/L)}
+\end{equation}
+
+% NEWPAGE
+\newpage
 

### 2017-12-18 tests/circle_packing.m
added new geometries

@@ -58,7 +58,7 @@ end
 %xc = 0;
 %yc = 0;
 
-N = 512;
+N = 128;
 theta = (0:N-1)'*2*pi/N;
 clf; hold on
 for k = 1:numel(xc)

### 2017-12-18 docs/methods/erosion_methods.tex
Updated figure 1bod_seq
NM
Working on figures in methods tex

@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure generated using 20circ128.in with epsfac = 8, sigfac = 8, dt = 2e-4, fixpdrop = 1.
+% Figure was made after the code changes regarding scaling the smoothing on the average stress on each body.
 
@@
 $\ff$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Interface evolution in the {\thL} framework} 
+\label{sec:thetaL}
+
+% BRYAN'S ORIGINAL TEXT
+%In this section, we also describe our time stepping method and two regularization terms that are necessary to control the curvature of the bodies and to maintain spectral accuracy in space.
+
+%Once the shear stress is computed, it is used to update the shape of the bodies according to the normal flow~\eqref{eqn:bodyEvolution}.
+To eliminate tangling and stretching of the mesh, we use a {\thL}formulation~\cite{hou-low-she1994} which is described in Section~\ref{sec:thetaL}.
+
+%We use a quasi-static approximation so that the velocity field instantaneously changes with the changing geometry.  Therefore, we can alternate between the two main aspects of our simulation
+%\begin{enumerate}
+%\item Given a geometry, compute the shear stress of along the boundary of each of the bodies.
+%\item Given the shear stress, update the geometry according to the erosion model.
+%\end{enumerate}
+
+To handle boundary evolution, we use the {\thL} framework, which offers
+certain advantages in the ability to stabilize fluid-structure
+interaction problems \cite{hou-low-she1994}. Throughout this section, we
+use the following conventions: the bodies are parametrized in the CCW
+direction and the normal vector points into the bodies (our out of the
+fluid).
+
+In order to regularize boundary evolution, we modify the normal velocity
+in Eq.~\eqref{eqn:bodyEvolution} as follows
+\begin{equation}
+\label{eqn:Vn}
+\Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right)
+\end{equation}
+Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean.
+The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity.
+Since a closed body has a mean curvature of $\mean{\kappa} = 2\pi / L$, the term in parentheses has mean zero.
+Thus, this term is area-preserving, so that the only material loss is due to the shear stress itself.
+In addition, we have scaled this term on the $\mean{\atau}$, the average absolute stress, so that it is always proportional to the true source of erosion $\atau$, even as bodies vanish (reword).
+
+We now introduce the tangent angle, $\theta$, defined through the relation
+\begin{equation}
+\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin \theta \right)
+\end{equation}
+where $s$ is arc length. We also introduce the normalized arc length $\alpha = 2 \pi s / L$. In terms of these new variables, the curvature can be expressed as
+\begin{equation}
+\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha}
+\end{equation}
+Substitution into Eq.~\eqref{eqn:Vn} gives
+\begin{equation}
+\label{eqn:Vn2}
+\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right)
+%\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
+\end{equation}
+
+The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced.
+The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
+\begin{equation}
+\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
+\end{equation}
+The interface evolution is then given by
+\begin{equation}
+\dot{\xx}(t) = \Vn \nn + \Vs \ss.
+\end{equation}
+Upon transforming to the variables $\theta(\alpha,t)$ and $L(t)$, we obtain the evolution equations
+\begin{align}
+\label{eqn:Levo0}
+& \tderiv{L}{t} = - 2 \pi \mean{\thalpha \Vn} \\
+\label{eqn:thetaevo0}
+& \pderiv{\theta}{t} = \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
+\end{align}
+Inserting Eq.~\eqref{eqn:Vn2} for the normal velocity gives
+\begin{equation}
+\pderiv{\theta}{t} = \frac{2\pi}{L} \left(
+\eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
+\end{equation}
+
+For simplicity, we introduce the variables
+\begin{align}
+\label{eq:M}
+& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
+\label{eq:N}
+& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
+\label{eq:elfun}
+& \elfun = \frac{2 \pi  \mean{\atau}}{L}
+%\frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
+\end{align} 
+Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
+\begin{equation}
+\label{eqn:thetaevo1}
+\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
+\end{equation}
+Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}.
+This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{{\thL} Formulation} 
-\label{sec:thetaL}
-
-% BRYAN'S ORIGINAL TEXT
-%In this section, we also describe our time stepping method and two regularization terms that are necessary to control the curvature of the bodies and to maintain spectral accuracy in space.
-
-%Once the shear stress is computed, it is used to update the shape of the bodies according to the normal flow~\eqref{eqn:bodyEvolution}.
-To eliminate tangling and stretching of the mesh, we use a {\thL}formulation~\cite{hou-low-she1994} which is described in Section~\ref{sec:thetaL}.
-
-%We use a quasi-static approximation so that the velocity field instantaneously changes with the changing geometry.  Therefore, we can alternate between the two main aspects of our simulation
-%\begin{enumerate}
-%\item Given a geometry, compute the shear stress of along the boundary of each of the bodies.
-%\item Given the shear stress, update the geometry according to the erosion model.
-%\end{enumerate}
-
-To handle boundary evolution, we use the {\thL}    method, which offers
-certain advantages in the ability to stabilize fluid-structure
-interaction problems \cite{hou-low-she1994}. Throughout this section, we
-use the following conventions: the bodies are parametrized in the CCW
-direction and the normal vector points into the bodies (our out of the
-fluid).
-
-In order to regularize boundary evolution, we modify the normal velocity
-in Eq.~\eqref{eqn:bodyEvolution} as follows
-\begin{equation}
-\label{eqn:Vn}
-\Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right)
-\end{equation}
-Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean.
-The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity.
-Since a closed body has a mean curvature of $\mean{\kappa} = 2\pi / L$, the term in parentheses has mean zero.
-Thus, this term is area-preserving, so that the only material loss is due to the shear stress itself.
-In addition, we have scaled this term on the $\mean{\atau}$, the average absolute stress, so that it is always proportional to the true source of erosion $\atau$, even as bodies vanish (reword).
-
-We now introduce the tangent angle, $\theta$, defined through the relation
-\begin{equation}
-\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin \theta \right)
-\end{equation}
-where $s$ is arc length. We also introduce the normalized arc length $\alpha = 2 \pi s / L$. In terms of these new variables, the curvature can be expressed as
-\begin{equation}
-\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha}
-\end{equation}
-Substitution into Eq.~\eqref{eqn:Vn} gives
-\begin{equation}
-\label{eqn:Vn2}
-\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right)
-%\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
-\end{equation}
-
-The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced.
-The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
-\begin{equation}
-\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
-\end{equation}
-The interface evolution is then given by
-\begin{equation}
-\dot{\xx}(t) = \Vn \nn + \Vs \ss.
-\end{equation}
-Upon transforming to the variables $\theta(\alpha,t)$ and $L(t)$, we obtain the evolution equations
+%% TIME-STEPPING %%
+\subsection{Time-stepping with the {\thL} method} 
+We will evolve $\theta$ in spectral space, and so introduce the transforms
+\todo[inline]{Check theta equation}
 \begin{align}
-\label{eqn:Levo0}
-& \tderiv{L}{t} = - 2 \pi \mean{\thalpha \Vn} \\
-\label{eqn:thetaevo0}
-& \pderiv{\theta}{t} = \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
-\end{align}
-Inserting Eq.~\eqref{eqn:Vn2} for the normal velocity gives
-\begin{equation}
-\pderiv{\theta}{t} = \frac{2\pi}{L} \left(
-\eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
-\end{equation}
-
-For simplicity, we introduce the variables
-\begin{align}
-\label{eq:M}
-& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
-\label{eq:N}
-& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
-\label{eq:elfun}
-& \elfun = \frac{2 \pi  \mean{\atau}}{L}
-%\frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
-\end{align} 
-Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
-\begin{equation}
-\label{eqn:thetaevo1}
-\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
-\end{equation}
-Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}.
-This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.
-We will evolve $\theta$ in spectral space, and so introduce the transforms
-\begin{align}
-& \theta(\alpha,t) = \FourierSum \thhat_k e^{ i k \alpha} \\
+& \theta(\alpha,t) = \alpha + \FourierSum \thhat_k e^{ i k \alpha} \\
 & \NLterm(\alpha,t)  = \FourierSum \hat{\NLterm}_k e^{ i k \alpha}
@@
 
-\subsubsection{The uniform stress geometry}
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.9 \textwidth]{./figs/01bodseq.pdf}
+\caption{One body}
+\label{}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure from datafile 01circ1024aa;
+% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixpdrop = 0
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.99 \textwidth]{./figs/IntfacesStressArea.pdf}
+\caption{One body}
+\label{}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure from datafile 01circ1024aa;
+% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixpdrop = 0
 
@@
 
+\subsubsection{The uniform stress geometry}
+
 % NEWPAGE
 \newpage
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.9 \textwidth]{./figs/fig3.pdf}
-\caption{Shrinking body and area.}
-\label{fig1}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 

### 2017-12-18 docs/methods/erosion_methods.tex
worked on intro section

@@
 \section{Introduction\label{s:intro}}
+
+\paragraph{Contributions}
+
+\paragraph{Limitations} There are two main limitations of the current
+work.  First, the flow is assumed to be two-dimensional.  Although
+several flows can be described to good accuracy under a two-dimensional
+approximation, certain phenomena occur only in three-dimensional.  The
+boundary integral equation formulation for the fluid solver exists, and
+the main challenges of a BIE solver have been addressed by other groups
+including surface representation~\cite{yin-bir-zor2006,
+vee-rah-bir-zor2011}, near-singular integration~\cite{yin-bir-zor2006,
+kli-tor2016b}, and fast summation methods~\cite{yin-bir-zor2004,
+ros-ols2015}.  The more significant challenge of extending our work to
+three dimensions is guaranteeing that the mesh does not become
+distorted, which can be done, for example, by using an extension of the
+two-dimensional {\thL} formulation~\cite{amb-sie-tlu2013}.
+
+The second limitation is that the eroding bodies are fixed.  While
+mobile eroding bodies have been considered~\cite{Mitchell2016}, only a
+single body is simulated.  When multiple bodies are present, especially
+in dense suspensions, numerical errors can cause bodies to unphysically
+come into contact.  However, by including a small force and
+torque~\cite{lu-rah-zor2017}, contact can be avoided.
+
+\paragraph{Related work}
+
+\paragraph{Outline of the paper}
 
@@
 Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}.
-This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.
+This is the key to the \thL method, and allows us to use very stable, implicit methods for this stiff term.
 

### 2017-12-20 docs/methods/erosion_methods.tex
added figures
NM
Modified figures
Working on paper
Added area-drag figure
Writing a bit

@@
 \begin{center}
-\includegraphics[width = 0.9 \textwidth]{./figs/20bod.pdf}
+\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
 \caption{20 bodies with vorticity}
@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure generated using 20circ128.in with epsfac = 8, sigfac = 8, dt = 2e-4, fixpdrop = 1.
-% Figure was made after the code changes regarding scaling the smoothing on the average stress on each body.
+% Figure generated using 50circ128.in with epsfac = 10, sigfac = 10, dt = 2e-4, fixpdrop = 1.
 
@@
 Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}.
-This is the key to the \thL method, and allows us to use very stable, implicit methods for this stiff term.
+This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.
 
@@
 We will evolve $\theta$ in spectral space, and so introduce the transforms
-\todo[inline]{Check theta equation}
 \begin{align}
@@
 \end{align}
+Recall that $\alpha = 2 \pi s / L$ is a normalized arc length.
 Equation~\eqref{eqn:thetaevo1} gives a set of ODEs for the coefficients
@@
 
-\subsection{Single-body validation results}
+With the description of the numerical methods complete, we now present results on bodies eroding in Stokes flow.
+We first discuss simulations of a single eroding body, which can be compared with analytical results for validation, before discussing the erosion of many bodies.
+
+\subsection{The erosion of a single body}
+
+In the case of a single eroding body, certain analytical results can be derived regarding the limiting shape and vanishing rate. These results allow validation of our simulation.
 
@@
 \begin{center}
-\includegraphics[width = 0.99 \textwidth]{./figs/IntfacesStressArea.pdf}
+\includegraphics[width = 0.8 \textwidth]{./figs/shrink_intface.pdf}
 \caption{One body}
@@
 % Figure from datafile 01circ1024aa;
-% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixpdrop = 0
+% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.8 \textwidth]{./figs/area_drag.pdf}
+\caption{One body}
+\label{}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure from datafile 01circ1024aa;
+% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.8 \textwidth]{./figs/fixed_intface.pdf}
+\caption{One body fixed area}
+\label{}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure from datafile 01circ1024c5
+% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.8 \textwidth]{./figs/arangle.pdf}
+\caption{Aspect ration and opening angle}
+\label{}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure from datafile 01circ1024c5
+% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+% Table
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{table}%[htbp]
+\begin{center}
+\caption{Final aspect ratio and opening angle
+} 
+\vspace{0.3 pc}
+%\label{aaa}
+\begin{tabular}{c c c}
+\hline
+\hspace{0.5pc} smoothing parameters, $\eps, \sigma$
+\hspace{0.5pc} & final aspect ratio 
+\hspace{0.5pc} & final opening angle \\
+\hline
+20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
+10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
+5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+
+%\begin{comment}
+% Table
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{table}%[htbp]
+\begin{center}
+\caption{Final aspect ratio and opening angle
+} 
+\vspace{0.3 pc}
+%\label{aaa}
+\begin{tabular}{l | c c c c}
+\hline
+{} & $\eps, \sigma = 20/1024$ & $\eps, \sigma = 10/1024$ & $\eps, \sigma = 5/1024$ & theoretical \\
+\hline
+final aspect ratio & 2.55 & 2.62 & 2.65 & -- \\
+final opening angle & $110^\circ \pm 6^\circ$ & $104^\circ \pm 4^\circ$ & $102^\circ \pm 2^\circ$ & $102^\circ$
+\end{tabular}
+\end{center}
+\end{table}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+%\end{comment}
 
@@
 \newpage
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
-\caption{Final shape.}
-\label{fig2}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 

### 2017-12-21 docs/methods/erosion_methods.tex
changed 50 body figure
Chiping away at writing in results section

@@
 \includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
-\caption{20 bodies with vorticity}
+\caption{50 bodies with vorticity}
 \label{}
@@
 
+\subsubsection{Shape evolution}
+
+We first show a single body eroding, with the surrounding vorticity field visualized in Fig.~4.
+The body develops a corner at its front and rear stagnation points.
+It maintains for-aft symmetry due to the time-reversibility of Stokes flow.
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
+In Fig.~5a, we visualize the interfaces color coded in time.
+In Fig.~5b, we show the absolute shear stress, $\atau$, as it varies over the surface of the body.
+Initially, the shear stress is a hump shape.
+As time progresses, the stress becomes more evenly distributed, with the exception of the front/rear corner where the curvature is high.
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 % Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
+
+\subsubsection{The vanishing rate of area}
+In three-dimensional Stokes flow, the shear stress vanishes as
+\begin{equation}
+\tauD{3} \sim \mu V/L
+\end{equation}
+However, this law must be modified for 2D flow, which represents 3D bodies of large extent.
+As the body vanishes, the walls have an ever decreasing influence.
+Thus, the stress must be consistent with free-space slender-body theory as it vanishes.
+The stress law consistent with slender body theory (a long cylinder held perpendicular to a flow) is
+\begin{equation}
+\tauD{2} \sim \frac{\mu V}{L \log(W/L)}
+\end{equation}
+% Could include 4 \pi factor, which is appropriate for a circular cylinder
+
+Then the rate of change of the body area is proportional to the shear stress times the total arc length exposed
+\begin{equation}
+\dot{A} = \int \atauD{2} \, ds = \mean{\atauD{2}} L
+\sim \frac{\mu V}{\log(W/L)}
+%\sim - \mean{\abs{\tauD{2}}} L
+\end{equation}
+Solving gives (redo this calculation)
+\begin{equation}
+A (1 - \log A) = C (t_f - t)
+\end{equation}
+where $C$ is a constant.
+
+In Fig.~6a, we show the body area vs time measured in the simulation against the above scaling law. In the scaling law, we chose, $C = 0.42$ (check this?)
 
@@
 %\end{comment}
-
-\subsubsection{The vanishing rate of area}
-In three-dimensional Stokes flow, the shear stress vanishes as
-\begin{equation}
-\tau_{3D} \sim \mu V/L
-\end{equation}
-However, this law must be modified for 2D flow, which represents 3D bodies of large extent.
-As the body vanishes, the walls have an ever decreasing influence.
-Thus, the stress must be consistent with free-space slender-body theory as it vanishes.
-The stress law consistent with slender body theory (a long cylinder held perpendicular to a flow) is
-\begin{equation}
-\tau_{2D} \sim \frac{4 \pi \mu V}{L \log(W/L)}
-\end{equation}
 

### 2018-01-04 docs/methods/erosion_methods.tex
started working on intro again ...

@@
 \section{Introduction\label{s:intro}}
-
-\paragraph{Contributions}
+Erosion by flowing fluid plays an essential role in diverse processes.
+Many of the flows are geophysical, such as the formation of sand dunes
+or erosion due to groundwater flow.  In both these examples, there is a
+feedback process between the flow and the erodible body.  In particular,
+the shape of the eroding body affects the flow, while the flow changes
+the shape of the eroding body.
+
+\paragraph{Contributions} The present study will develop numerical
+methods to simulate viscous erosion of a multiply-connected
+two-dimensional geometry.  By assuming the flow is viscous, we are
+assuming the flow is very slow, such as in groundwater flow.  Moreover,
+by allowing for complex multiply-connected domains, the erosion caused
+by the non-local complex interactions between different bodies is
+modeled.
+
+Because of the low Reyonlds number assumption, the flow will be assumed
+to be Stokesian.  Then, to create high-fidelity and computationally
+efficient numerical methods, two fast and accurate methods will be
+employed:
+\begin{enumerate}
+  \item The fluid equations will be solved with spectral accuracy by
+  using an efficient boundary integral equation method. Moreover, the
+  rate of erosion will be computed and the rate of erosion will be
+  computed with spectral accuracy.
+  \item Given a rate of erosion, the shape will be integrated in time
+  with second-order accuracy.  All spatial derivatives will be computed
+  in Fourier space, resulting in spectral accuracy in space.
+\end{enumerate}
 

### 2018-01-05 julia/zconv_test.jl
Doing convergence test for shape and putting in methods paper.

@@ -58,5 +58,5 @@ function convtest(tfin::Float64, nits::Int)
 	println("\nThe shape errors: ", round(err_shape,4))
 	println("The shape order: ", round(order_shape,2))
 	println()
-	return err_shape,order_shape
+	return dtv,err_shape,order_shape
 end

### 2018-01-05 julia/zconv_test.jl
NM

@@ -1,5 +1,5 @@
 # Test the 2nd order convergence in dt.
-# In typically use 01circ256, with tfin = 1e-2 and nits = 4 or higher.
+# I typically use 01circ256, with tfin = 1e-2, dt0 = 1e-3, nits = 4 or higher.
 # Vanishing time for 01circ1024aa is 0.017938. So 1e-2 is 56% of vanishing time.
 # The runtime for nits = 4 is about 40 seconds.
 
@@ -19,7 +19,7 @@ function shape_error(thld1::ThLenDenType, thld0::ThLenDenType)
 end
 
 # Test the convergence wrt dt.
-function convtest(tfin::Float64, nits::Int)
+function convtest(tfin::Float64, dt0::Float64, nits::Int)
 	# Initialize simulation variables.
 	paramsfile = "params.in"
 	thld1,params = startup(paramsfile)
@@ -28,7 +28,7 @@ function convtest(tfin::Float64, nits::Int)
 	dragv,dtv,tv = [zeros(Float64,nits) for ii=1:3]
 	err_shape,err_drag = [zeros(Float64,nits-1) for ii=1:2]
 	# Loop over different dt values.
-	dt = 2e-3
+	dt = dt0
 	for nn=1:nits
 		println("\n\nCONVERGENCE TEST: running number ", nn, " out of ", nits)
 		thld0 = deepcopy(thld1)

### 2018-01-05 julia/zconv_test.jl
NM

@@ -1,7 +1,7 @@
 # Test the 2nd order convergence in dt.
-# I typically use 01circ256, with tfin = 1e-2, dt0 = 1e-3, nits = 4 or higher.
+# I typically use 01circ256, with tfin = 1e-2, dt0 = 1e-4, nits = 3 or higher.
 # Vanishing time for 01circ1024aa is 0.017938. So 1e-2 is 56% of vanishing time.
-# The runtime for nits = 4 is about 40 seconds.
+# The runtime for nits = 3 is about 16 minutes.
 
 include("main.jl")
 

### 2018-01-08 docs/methods/erosion_methods.tex
Doing convergence test for shape and putting in methods paper.
NM
Put convergence test in methods paper
started the introduction

@@
 the shape of the eroding body affects the flow, while the flow changes
-the shape of the eroding body.
+the shape of the eroding body.  This fluid-mechanical feedback
+system has be simulated in idealized cases such as a single eroding body
+in a uniform flow~\cite{moo-ris-chi-zha-she2013}.  To further develop
+insight into the effect of two-dimensional erosion, we consider erosion
+of a multiply-connected domain (Figure~\ref{fig:50bodies}), such as a
+porous media that is typically used to model groundwater flow.
+
+Because of the scales involved with groundwater flow, we will restrict
+our attention to Stokesian dynamics.  That is, the fluid equations will
+be governed by the incompressible Stokes equations.  Because of the
+linearity of the underlying equations, a boundary integral equation is
+well-suited as it can resolve complex geometries, the interactions
+between bodies, all the while achieving high-order accuracy and
+computational efficiency.
 
@@
 two-dimensional geometry.  By assuming the flow is viscous, we are
-assuming the flow is very slow, such as in groundwater flow.  Moreover,
-by allowing for complex multiply-connected domains, the erosion caused
-by the non-local complex interactions between different bodies is
-modeled.
+assuming the flow is very slow and in small length scales, as is the
+case in groundwater flow.  Moreover, by allowing for complex
+multiply-connected domains, the erosion caused by the non-local complex
+interactions between different bodies is modeled.
 
@@
 \paragraph{Related work}
+Simulating eroding bodies has been studied analytically, experimentally,
+and numerically.  Because of the scales involves with geophysical flows,
+most of these works consider high Reynolds number flows.  For instance,
+the experimental work of Moore et al.~\cite{moo-ris-chi-zha-she2013}
+considers on the order of $10^4$.  For low Reynolds number flows,
+Mitchell and Spagnolie~\cite{Mitchell2016} simulate the erosion of a
+mobile body in three dimensions, but they only consider single body.
+
+To simulate multiple bodies, it is essential to resolve the nonlocal
+effects between the different bodies.  In this work, these interactions
+are included with high-order accuracy by using an integral equation
+method.  Integral equations have been used extensively to simulate
+viscous fluids in complex geometries.  One particular application are
+particulate flows, such as bubbles or droplets, and the classic book of
+Pozrikidis~\cite{poz1992} describes boundary integral formulations for
+such problems.
 
 \paragraph{Outline of the paper}
-
-This is a methods paper
-\begin{itemize}
-  \item Boundary integral equation formulation
-  \item How we compute the shear stress and pressure
-  \item Multiple bodies
-  \item Avoiding stokes paradox
-  \item {\thL} formulation
-  \item Regularization
-\end{itemize}
+In Section~\ref{s:formulation}, we describe the governing equations for
+both the fluid and describe the erosion model using a \thL framework.
+In Section~\ref{s:method}, the numerical methods in both space and time
+are described.  Section~\ref{s:results} gives several numerical
+examples.  Finally, concluding remarks are made in
+Section~\ref{s:conclusions}
 
@@
 \includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
-\caption{50 bodies with vorticity}
-\label{}
+\caption{\label{fig:50bodies} 50 bodies with vorticity}
 \end{center}
@@
 
+% Table
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{table}%[htbp]
+\begin{center}
+\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is 56\% of the vanishing time.
+} 
+\vspace{0.3 pc}
+\label{convtab}
+\begin{tabular}{c l l}
+\hline
+\hspace{0.5pc} $\Delta t/t_s$
+\hspace{0.5pc} & error 
+\hspace{0.5pc} & order \\
+\hline
+1/100	& 4.69E-6		& --		\\
+1/200	& 1.26E-6		& 1.90	\\
+1/400	& 3.26E-7		& 1.95	\\
+1/800	& 8.28E-8		& 1.98	\\
+1/1600	& 2.09E-8		& 1.99	\\
+1/3200	& 5.26E-9		& 1.99	\\
+1/6400	& --			& --		\\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+
 \subsubsection{The uniform stress geometry}

### 2018-01-09 docs/methods/erosion_methods.tex
worked on intro

@@
 
-\title{Methods paper for erosion}
+\title{Viscous Erosion in Porous Media}
 
@@
 \begin{keyword}
-  Stokes flow \sep Erosion \sep Boundary integral method \sep
-  Fluid-structure interaction \sep Fast multipole methods 
+  Stokes flow \sep Erosion \sep Boundary integral method \sep Shear
+  stress \sep \thL~formulation
 \end{keyword}
@@
 \section{Introduction\label{s:intro}}
-Erosion by flowing fluid plays an essential role in diverse processes.
-Many of the flows are geophysical, such as the formation of sand dunes
-or erosion due to groundwater flow.  In both these examples, there is a
-feedback process between the flow and the erodible body.  In particular,
-the shape of the eroding body affects the flow, while the flow changes
-the shape of the eroding body.  This fluid-mechanical feedback
-system has be simulated in idealized cases such as a single eroding body
-in a uniform flow~\cite{moo-ris-chi-zha-she2013}.  To further develop
-insight into the effect of two-dimensional erosion, we consider erosion
-of a multiply-connected domain (Figure~\ref{fig:50bodies}), such as a
-porous media that is typically used to model groundwater flow.
+Erosion is a fluid-mechanical process that occurs when a fluid alters
+the geometry.  Erosion is responsible for a variety of processes, many
+of which are geophysical.  For example, sand dunes are longer on the
+windward side because of the wind erosion.  Another applications is
+erosion caused by groundwater flow, where a slow moving fluid erodes
+channels, or conduits, in the earth which creates a heterogeneous media
+that has a large effect on the resulting flow.  In both these examples,
+there is a feedback process between the flow and the erodible
+bodies---the shape of the eroding body affects the flow, while the flow
+changes the shape of the eroding body.  This fluid-mechanical feedback
+system has been simulated in idealized cases such as a single eroding
+two-dimensional body in a uniform flow~\cite{moo-ris-chi-zha-she2013} or
+a single mobile eroding three-dimensional body~\cite{mit-spa2016}. To
+further develop insight into the effect of two-dimensional erosion, we
+consider erosion of a multiply-connected domain
+(Figure~\ref{fig:50bodies}), such as a porous media that is typically
+used to model groundwater flow.
 
 Because of the scales involved with groundwater flow, we will restrict
-our attention to Stokesian dynamics.  That is, the fluid equations will
-be governed by the incompressible Stokes equations.  Because of the
-linearity of the underlying equations, a boundary integral equation is
-well-suited as it can resolve complex geometries, the interactions
-between bodies, all the while achieving high-order accuracy and
-computational efficiency.
+our attention to Stokesian dynamics.  For groundwater flow, Darcy's
+equation are often used, but this assumes a homogeneous geometry which
+is not always a fair assumption.  Instead, we will use the
+incompressible Stokes equations to represent the flow, and the
+individual pores will be be resolved, resulting in a complex
+multiply-connected geometry.  A boundary integral equation is
+well-suited as it can resolve complex geometries and the non-negligible
+interactions between bodies are resolved, all the while high-order
+accuracy and computational efficiency are achieved.  To simulate the
+erosion, each body will erode at a rate that is proportional to the
+shear stress.  To further visualize the effect of erosion, we compute
+the vorticity of the flow (Figure~\ref{fig:50bodies}) which is equal to
+the shear stress in the Stokesian limit.  Finally, to evolve the
+geometry, a second-order time stepping method that guarantees that the
+mesh does not become distorted will be employed.
 
 \paragraph{Contributions} The present study will develop numerical
-methods to simulate viscous erosion of a multiply-connected
-two-dimensional geometry.  By assuming the flow is viscous, we are
+methods to simulate viscous erosion of multiply-connected
+two-dimensional geometries.  By assuming the flow is viscous, we are
 assuming the flow is very slow and in small length scales, as is the
 case in groundwater flow.  Moreover, by allowing for complex
-multiply-connected domains, the erosion caused by the non-local complex
-interactions between different bodies is modeled.
+multiply-connected domains, the effects due to interacting bodies on the
+erosion are captured.
 
@@
 several flows can be described to good accuracy under a two-dimensional
-approximation, certain phenomena occur only in three-dimensional.  The
+approximation, certain phenomena occur only in three dimensions.  The
 boundary integral equation formulation for the fluid solver exists, and
@@
 
-The second limitation is that the eroding bodies are fixed.  While
-mobile eroding bodies have been considered~\cite{Mitchell2016}, only a
-single body is simulated.  When multiple bodies are present, especially
-in dense suspensions, numerical errors can cause bodies to unphysically
-come into contact.  However, by including a small force and
-torque~\cite{lu-rah-zor2017}, contact can be avoided.
+The second limitation is that the eroding bodies are fixed.  Mitchell
+and Spagnolie~\cite{mit-spa2016} simulate a single mobile eroding body
+in three dimensions have been considered~\cite{mit-spa2016}, but
+additional challenges are caused when there are multiple bodies. In
+particular, especially in dense suspensions, bodies can become extremely
+close to one another, and the interaction between the bodies is
+difficult to resolve unless the underlying mesh is refined to levels
+that are intractable. In future work we plan to consider mobile eroding
+bodies, but include a small force and torque so that unphysical contact
+is avoided~\cite{lu-rah-zor2017}.
 
@@
 considers on the order of $10^4$.  For low Reynolds number flows,
-Mitchell and Spagnolie~\cite{Mitchell2016} simulate the erosion of a
+Mitchell and Spagnolie~\cite{mit-spa2016} simulate the erosion of a
 mobile body in three dimensions, but they only consider single body.
@@
 In Section~\ref{s:formulation}, we describe the governing equations for
-both the fluid and describe the erosion model using a \thL framework.
+both the fluid and describe the erosion model using a \thL~framework.
 In Section~\ref{s:method}, the numerical methods in both space and time
@@
 \includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
-\caption{\label{fig:50bodies} 50 bodies with vorticity}
+\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
+viscous flow.  The boundary conditions are a constant pressure drop that
+creates a flow from the left to right.  The rate of erosion is
+proportional to the shear stress which is equivalent to the vorticity
+evaluated on the bodies.  The colors represent the vorticity, so regions
+with large vorticity (in magnitude) are regions where the flow will
+erode the fastest.}
 \end{center}

### 2018-01-09 docs/methods/erosion_methods.tex
worked on intro

@@
 channels, or conduits, in the earth which creates a heterogeneous media
-that has a large effect on the resulting flow.  In both these examples,
+that has a large effect on the resulting flow. Erosion is also important
+in the biophysical community. Plaque erosion in arteries is
+key to understanding heart disease~\cite{sha2002,
+gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can
+be explained by erosion~\cite{pic-van-hei2000}. In all these examples,
 there is a feedback process between the flow and the erodible
 bodies---the shape of the eroding body affects the flow, while the flow
-changes the shape of the eroding body.  This fluid-mechanical feedback
-system has been simulated in idealized cases such as a single eroding
-two-dimensional body in a uniform flow~\cite{moo-ris-chi-zha-she2013} or
-a single mobile eroding three-dimensional body~\cite{mit-spa2016}. To
-further develop insight into the effect of two-dimensional erosion, we
-consider erosion of a multiply-connected domain
-(Figure~\ref{fig:50bodies}), such as a porous media that is typically
-used to model groundwater flow.
+changes the shape by fluidizing the eroding body.  This fluid-mechanical
+feedback system has been simulated in idealized cases such as a single
+eroding two-dimensional body in a uniform
+flow~\cite{moo-ris-chi-zha-she2013} or a single mobile eroding
+three-dimensional body~\cite{mit-spa2016}. To further develop insight
+into the effect of two-dimensional erosion, we consider erosion of a
+multiply-connected domain (Figure~\ref{fig:50bodies}), such as a porous
+media that is typically used to model groundwater flow.
 
@@
 interactions between bodies are resolved, all the while high-order
-accuracy and computational efficiency are achieved.  To simulate the
-erosion, each body will erode at a rate that is proportional to the
-shear stress.  To further visualize the effect of erosion, we compute
-the vorticity of the flow (Figure~\ref{fig:50bodies}) which is equal to
-the shear stress in the Stokesian limit.  Finally, to evolve the
-geometry, a second-order time stepping method that guarantees that the
-mesh does not become distorted will be employed.
+accuracy and computational efficiency are achieved. To link the body and
+fluid dynamics, the body is eroded in the normal direction at a rate
+that is proportional to the magnitude of the shear
+stress~\cite{ris-moo-chi-she-zha2012}.  To further visualize the effect
+of erosion, we compute the vorticity of the flow
+(Figure~\ref{fig:50bodies}) which is equal to the shear stress in the
+Stokesian limit.  Finally, to evolve the geometry, a second-order time
+stepping method that guarantees that the mesh does not become distorted
+will be employed.
 
@@
 multiply-connected domains, the effects due to interacting bodies on the
-erosion are captured.
-
-Because of the low Reyonlds number assumption, the flow will be assumed
+erosion are captured.  We start by authenticating our method on a single
+circular body placed symmetrically in a pipe flow.  By artificially
+fixing the area of the body as a function of time, we are able to
+characterize the long-time behavior of the shape and the resulting flow.
+Then, we compute the vorticity of erosion in multiply-connected
+geometries to better characterize erosion in porous media.
+
+Because of the low Reynolds number assumption, the flow will be assumed
 to be Stokesian.  Then, to create high-fidelity and computationally
@@
 \end{enumerate}
+We use a quasi-steady assumption so that these two steps can be iterated
+to simulate the dynamics.
+
+The effect of erosion on a geometry is quite rich.  For instance, it has
+been hypothesized and numerically observed that the erosion leads to a
+shear stress that is uniform on the body which results in a uniform
+erosion rate.  The shape that has a uniform shear stress is analyzed in
+three dimensions by Montenegro-Johnson and Lauga~\cite{mon-lau2015}
+which is an extension of the analysis done by Pironneau~\cite{pir1973}
+to find a Stokesian drag minimizing shape.  However, the effect of
+erosion on a porous media is less understood.  With the methods
+developed in this paper, quantities such as the total drag across a
+porous region as a function of time can be computed in future work.
+
+A challenge with erosion is that it creates corners at points on the
+body where the shear stress vanishes.  While recent work does allow for
+integral equation methods to resolve a corner, we employ a different
+method.  First, we add a regularization term to the shear stress to
+penalize regions of high curvature.  Second, we apply a Gaussian filter
+to smooth the absolute value of the shear stress before the body shape
+is updated.
 
@@
 To model erosion, we the normal velocity is prescribed to be
-proportional to the absolute value of the shear stress.  The constant of
-proportionality sets the time scale, and we set its value to be 1
+proportional to the absolute value of the shear stress.  This choice is
+based on experimental work of Ristroph et
+al.~\cite{ris-moo-chi-she-zha2012}, but other models for erosion are
+possible.  For example, some models use an erosion rate that is
+proportional to a power of the magnitude of the shear
+stress~\cite{par-izu2000}, while others introduced a shear stress below
+which erosion does not occur~\cite{lag2000}.
+
+The constant of proportionality sets the time scale, and we set its
+value to be 1
 \begin{align}

### 2018-01-09 docs/methods/erosion_methods.tex
modified area_drag.pdf

@@
   Stokes flow \sep Erosion \sep Boundary integral method \sep Shear
-  stress \sep \thL~formulation
+  stress \sep {\thL} formulation
 \end{keyword}
@@
 \hline
-\hspace{0.5pc} smoothing parameters, $\eps, \sigma$
+\hspace{0.5pc} smoothing parameters: $\eps$ and $\sigma$
 \hspace{0.5pc} & final aspect ratio 
@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-
-%\begin{comment}
-% Table
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{table}%[htbp]
-\begin{center}
-\caption{Final aspect ratio and opening angle
-} 
-\vspace{0.3 pc}
-%\label{aaa}
-\begin{tabular}{l | c c c c}
-\hline
-{} & $\eps, \sigma = 20/1024$ & $\eps, \sigma = 10/1024$ & $\eps, \sigma = 5/1024$ & theoretical \\
-\hline
-final aspect ratio & 2.55 & 2.62 & 2.65 & -- \\
-final opening angle & $110^\circ \pm 6^\circ$ & $104^\circ \pm 4^\circ$ & $102^\circ \pm 2^\circ$ & $102^\circ$
-\end{tabular}
-\end{center}
-\end{table}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-%\end{comment}
+% npts = 1024
 

### 2018-01-09 docs/methods/erosion_methods.tex
Worked on writing in theta-L numerical methods. Soon, I plan to write in the results section to explain the area scaling laws, the terminal angle, and the tables.

@@
 In order to regularize boundary evolution, we modify the normal velocity
-in Eq.~\eqref{eqn:bodyEvolution} as follows
+in \eqref{eqn:bodyEvolution} as follows
 \begin{equation}
@@
 \end{equation}
-Substitution into Eq.~\eqref{eqn:Vn} gives
+Substitution into \eqref{eqn:Vn} gives
 \begin{equation}
@@
 \end{equation}
-Upon transforming to the variables $\theta(\alpha,t)$ and $L(t)$, we obtain the evolution equations
-\begin{align}
-\label{eqn:Levo0}
+This evolution equation can be recast in the variables $\theta$ and $L$ as
+\begin{align}
+\label{eqn:Levo1}
 & \tderiv{L}{t} = - 2 \pi \mean{\thalpha \Vn} \\
@@
 \end{align}
-Inserting Eq.~\eqref{eqn:Vn2} for the normal velocity gives
-\begin{equation}
+Inserting \eqref{eqn:Vn2} for the normal velocity gives
+\begin{equation}
+\label{eqn:thetaevo1}
 \pderiv{\theta}{t} = \frac{2\pi}{L} \left(
@@
 \end{equation}
-
-For simplicity, we introduce the variables
-\begin{align}
-\label{eq:M}
-& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
-\label{eq:N}
-& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
-\label{eq:elfun}
-& \elfun = \frac{2 \pi  \mean{\atau}}{L}
-%\frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
-\end{align} 
-Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
-\begin{equation}
-\label{eqn:thetaevo1}
-\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
-\end{equation}
-Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}.
+Note that the highest-order, i.e.~stiff, term in \eqref{eqn:thetaevo1} is {\em quasi-linear}.
 This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.
@@
 \subsection{Time-stepping with the {\thL} method}
+
+With the shear stress computed, we are now ready to evolve the interface of each body.
+As described in Section \ref{sec:thetaL}, we use the {\thL} framework, with $\theta$ being the tangent angle and $L$ the total arc length of a given boundary.
+
+First, we introduce the variables
+\begin{align}
+\label{eq:M}
+& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
+\label{eq:N}
+& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
+\label{eq:elfun}
+& \elfun = \frac{2 \pi  \mean{\atau}}{L}
+\end{align} 
+so that evolution equations \eqref{eqn:Levo1} and \eqref{eqn:thetaevo1} can be compactly expressed as
+\begin{align}
+\label{eqn:Levo2}
+& \tderiv{L}{t} = \Mterm \\
+\label{eqn:thetaevo2}
+& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
+\end{align}
 We will evolve $\theta$ in spectral space, and so introduce the transforms
@@
 \end{align}
-Recall that $\alpha = 2 \pi s / L$ is a normalized arc length.
-Equation~\eqref{eqn:thetaevo1} gives a set of ODEs for the coefficients
+Recall that $\alpha = 2 \pi s / L$ is a normalized arc length. In spectral space, \eqref{eqn:thetaevo2} produces the system of ODEs
 \begin{equation}
@@
 \end{equation}
-We introduce the integrating factor
+Each ODE is first-order and linear (though variable-coefficient due to $\elfun$) and thus can be solved by the integrating factor
 \begin{equation}
@@
 \end{equation}
-Then the evolution equations for $L$ and $\theta$ can be recast as the coupled system of ODEs
+We are therefore led to the coupled system of ODEs
 \begin{align}
@@
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
+\begin{figure}[p]%[htbp]
 \begin{center}
 \includegraphics[width = 0.8 \textwidth]{./figs/arangle.pdf}
-\caption{Aspect ration and opening angle}
+\caption{Aspect ratio and opening angle}
 \label{}
@@
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{table}%[htbp]
+\begin{table}[p]%[htbp]
 \begin{center}

### 2018-01-10 docs/methods/erosion_methods.tex
NM

@@
 
-% BRYAN'S ORIGINAL TEXT
-%In this section, we also describe our time stepping method and two regularization terms that are necessary to control the curvature of the bodies and to maintain spectral accuracy in space.
-
-%Once the shear stress is computed, it is used to update the shape of the bodies according to the normal flow~\eqref{eqn:bodyEvolution}.
-To eliminate tangling and stretching of the mesh, we use a {\thL}formulation~\cite{hou-low-she1994} which is described in Section~\ref{sec:thetaL}.
-
+% Quasi-steady comment
 %We use a quasi-static approximation so that the velocity field instantaneously changes with the changing geometry.  Therefore, we can alternate between the two main aspects of our simulation
@@
 fluid).
+
+For the sake of numerical stability, we will regularize the boundary evolution in two ways. First, we will smooth the absolute
 
@@
 \end{align}
+Here $\NLterm$ represents the nonlinear terms (and nonlocal etc) in the PDE for $\theta$.
 We will evolve $\theta$ in spectral space, and so introduce the transforms
@@
 \end{equation}
-Each ODE is first-order and linear (though variable-coefficient due to $\elfun$) and thus can be solved by the integrating factor
+Each ODE is first-order and linear (though variable-coefficient due to $\elfun$) and thus can be solved by using the integrating factor
 \begin{equation}

### 2018-01-10 docs/methods/erosion_methods.tex
Put Gaussian filter in paper

@@
 \end{align}
+For the sake of numerical stability, we modify this law in Section \ref{sec:thetaL}.
 
@@
 
-% Quasi-steady comment
 %We use a quasi-static approximation so that the velocity field instantaneously changes with the changing geometry.  Therefore, we can alternate between the two main aspects of our simulation
@@
 To handle boundary evolution, we use the {\thL} framework, which offers
-certain advantages in the ability to stabilize fluid-structure
-interaction problems \cite{hou-low-she1994}. Throughout this section, we
-use the following conventions: the bodies are parametrized in the CCW
+certain advantages in the ability to stabilize fluid-structure interaction problems \cite{hou-low-she1994}.
+Throughout this section, we use the following conventions: the bodies are parametrized in the CCW
 direction and the normal vector points into the bodies (our out of the
@@
 
-For the sake of numerical stability, we will regularize the boundary evolution in two ways. First, we will smooth the absolute
-
-In order to regularize boundary evolution, we modify the normal velocity
+For the sake of numerical stability, we will modify the erosion law \eqref{eqn:bodyEvolution} to include a term that depends on the local curvature $\kappa$.
+The idea is to prevent regions of very high curvature.
+The modified normal velocity is
 in \eqref{eqn:bodyEvolution} as follows
@@
 \end{equation}
-Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean.
+Here, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean.
 The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity.
@@
 With the shear stress computed, we are now ready to evolve the interface of each body.
-As described in Section \ref{sec:thetaL}, we use the {\thL} framework, with $\theta$ being the tangent angle and $L$ the total arc length of a given boundary.
-
-First, we introduce the variables
+As described in Section \ref{sec:thetaL}, we use the {\thL} framework, with $\theta$ being the tangent angle and $L$ the total arc length of a given boundary, and with the boundaries parameterized by normalized arc length $\alpha = 2 \pi s / L$.
+
+In addition to the curvature-dependent term in \eqref{eqn:Vn}, we regularize boundary evolution by applying a narrow Gaussian filter to absolute shear stress
+\begin{equation}
+\atausig = \int_{\gamma} \frac{1}{\sqrt{2\pi} \sigma} \exp \left(- \frac{\alpha'^2}{2 \sigma^2}\right) \abs{ \tau(\alpha - \alpha') } \, d\alpha'
+\end{equation}
+Here $\sigma$ is the small parameter that determines the width of the filter. The corresponding normal and tangential interface velocities are the given by
+\begin{align}
+& \Vnsig = \atausig +  \eps \mean{\atausig}   \left(\pderiv{\theta}{\alpha} - 1 \right) \\
+& \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig}
+\end{align}
+
+%The interface evolution is then given by
+%\begin{equation}
+%\dot{\xx}(t) = \Vn \nn + \Vs \ss.
+%\end{equation}
+
+For simplicity, we introduce the variables
 \begin{align}
 \label{eq:M}
-& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
+& \Mterm = - 2 \pi \mean{\thalpha \Vnsig} \\
 \label{eq:N}
-& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
+& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha \Vssig \right) \\
 \label{eq:elfun}
-& \elfun = \frac{2 \pi  \mean{\atau}}{L}
-\end{align} 
-so that evolution equations \eqref{eqn:Levo1} and \eqref{eqn:thetaevo1} can be compactly expressed as
+& \elfun = \frac{2 \pi  \mean{\atausig}}{L}
+\end{align}
+So that evolution equations \eqref{eqn:Levo1} and \eqref{eqn:thetaevo1} can be compactly expressed as
 \begin{align}
@@
 \end{align}
+
 Here $\NLterm$ represents the nonlinear terms (and nonlocal etc) in the PDE for $\theta$.
-We will evolve $\theta$ in spectral space, and so introduce the transforms
+We will evolve $\theta$ in spectral space, and so introduce the Fourier series
 \begin{align}
@@
 \end{align}
-Recall that $\alpha = 2 \pi s / L$ is a normalized arc length. In spectral space, \eqref{eqn:thetaevo2} produces the system of ODEs
+The careful reader will notice that we have separated out the linear part of $\theta$, so that the remaining function is smooth and has a rapidly decaying Fourier series.
+In spectral space, \eqref{eqn:thetaevo2} produces the system of ODEs
 \begin{equation}
@@
 \end{align}
-\todo[inline]{Gaussian Filter}
 

### 2018-01-11 docs/methods/erosion_methods.tex
started to rearrange the paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Interface evolution in the {\thL} framework} 
-\label{sec:thetaL}
-
-%We use a quasi-static approximation so that the velocity field instantaneously changes with the changing geometry.  Therefore, we can alternate between the two main aspects of our simulation
-%\begin{enumerate}
-%\item Given a geometry, compute the shear stress of along the boundary of each of the bodies.
-%\item Given the shear stress, update the geometry according to the erosion model.
-%\end{enumerate}
-
-To handle boundary evolution, we use the {\thL} framework, which offers
-certain advantages in the ability to stabilize fluid-structure interaction problems \cite{hou-low-she1994}.
-Throughout this section, we use the following conventions: the bodies are parametrized in the CCW
-direction and the normal vector points into the bodies (our out of the
-fluid).
-
-For the sake of numerical stability, we will modify the erosion law \eqref{eqn:bodyEvolution} to include a term that depends on the local curvature $\kappa$.
-The idea is to prevent regions of very high curvature.
-The modified normal velocity is
-in \eqref{eqn:bodyEvolution} as follows
-\begin{equation}
-\label{eqn:Vn}
-\Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right)
-\end{equation}
-Here, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean.
-The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity.
-Since a closed body has a mean curvature of $\mean{\kappa} = 2\pi / L$, the term in parentheses has mean zero.
-Thus, this term is area-preserving, so that the only material loss is due to the shear stress itself.
-In addition, we have scaled this term on the $\mean{\atau}$, the average absolute stress, so that it is always proportional to the true source of erosion $\atau$, even as bodies vanish (reword).
-
-We now introduce the tangent angle, $\theta$, defined through the relation
-\begin{equation}
-\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin \theta \right)
-\end{equation}
-where $s$ is arc length. We also introduce the normalized arc length $\alpha = 2 \pi s / L$. In terms of these new variables, the curvature can be expressed as
-\begin{equation}
-\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha}
-\end{equation}
-Substitution into \eqref{eqn:Vn} gives
-\begin{equation}
-\label{eqn:Vn2}
-\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right)
-%\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
-\end{equation}
-
-The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced.
-The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
-\begin{equation}
-\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
-\end{equation}
-The interface evolution is then given by
-\begin{equation}
-\dot{\xx}(t) = \Vn \nn + \Vs \ss.
-\end{equation}
-This evolution equation can be recast in the variables $\theta$ and $L$ as
-\begin{align}
-\label{eqn:Levo1}
-& \tderiv{L}{t} = - 2 \pi \mean{\thalpha \Vn} \\
-\label{eqn:thetaevo0}
-& \pderiv{\theta}{t} = \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
-\end{align}
-Inserting \eqref{eqn:Vn2} for the normal velocity gives
-\begin{equation}
-\label{eqn:thetaevo1}
-\pderiv{\theta}{t} = \frac{2\pi}{L} \left(
-\eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
-\end{equation}
-Note that the highest-order, i.e.~stiff, term in \eqref{eqn:thetaevo1} is {\em quasi-linear}.
-This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Layer Potentials for Quantities of Interest}
-\label{sec:qois}
-There are several quantities besides the velocity that need to be
-computed.  First, the governing equations~\eqref{eqn:erosionModel}
-require the shear stress along $\gamma_\ell$.  In addition, to study
-characteristics of the flow, the vorticity, pressure, and drag, and
-resistivity will also be computed.  Once
-equation~\eqref{eqn:completed_DLP} is solved for the density function,
-Stokeslets, and rotlets, all of these quantities can be computed by
-evaluating layer potentials that we now derive.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Shear Stress}
+\subsection{Computing the Shear Stress}
 The shear stress is
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Vorticity}
-For the Stokes equations, on boundaries that have a no-slip boundary
-condition, the shear stress is equivalent to the vorticity $w = v_x -
-u_y$.  Therefore, to compute $w(\xx)$ for $\xx \in \overline{\Omega}$,
-we only need to compute $w(\xx)$ for $\xx \in \Omega$.  As we did for
-the shear stress, we compute the vorticity due to the double-layer
-potential, Stokeslets, and rotlets individually.  The vorticity of the
-double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
-\begin{align}
-  w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
-    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}
-    (\rr \cdot \eeta) ds_{\yy}.
-  \label{eqn:vorticityDLP}
-\end{align}
-The vorticity due to the Stokeslet is
-\begin{align*}
-  w^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
-    \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2},
-\end{align*}
-and the vorticity of a rotlet is zero.  Therefore, the vorticity at $\xx
-\in \Omega$ is
-\begin{align*}
-  w(\xx) = w^\DD(\xx) + w^S(\xx).
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Pressure}
-To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
-same procedure used for the shear stress.  We start by computing the
-pressure of the double-layer potential for $\xx \in \Omega$ and add the
-appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
-is
-\begin{align}
-  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot \eeta(\yy) \,ds_\yy.
-    \label{eqn:pressureDLP}
-\end{align}
-To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
-as $\xx$ tends to $\xx_0$.  The limiting value is given
-by~\cite{qua-bir2014a}
-\begin{align}
-  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
-    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
-  \label{eqn:pressureJump}
-\end{align}
-The pressure due to the Stokeslets is
-\begin{align}
-  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
-  \label{eqn:shearPressureSR}
-\end{align}
-and the pressure due to the rotlets is zero.  Therefore, the pressure is
-\begin{align*}
-  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
-  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
-              p^{S}(\xx), && \xx \in \bd\Omega.
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Drag}
-\todo[inline]{check all signs in this section.  Fortran code assumes a
-normal pointing into the eroding body and a tangent vector that
-corresponds to a couterclockwise parameterization}
-With the pressure and shear stress, the drag on a single body with
-boundary $\gamma_\ell$ is
-\begin{align}
-  F_D = \int_{\gamma_\ell} (-p \nn + \tau \ss)\,ds.
-  \label{eqn:drag}
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Resistivity}
-\begin{align}
-  some equation
-  \label{eqn:resistivity}
-\end{align}
+We have decomposed the deformation tensor into the contributions due to
+three different terms.  The contributions from the Stokeslets and the
+rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
+\gamma$.  However, the kernel of the deformation tensor due to the
+double-layer potential~\eqref{eqn:shearStressDLP} 
+\begin{align*}
+  K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
+    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
+    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn)
+    \right. \\ & \hspace{25pt}+ \left.
+    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
+    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
+  \right),
+\end{align*}
+has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
+\rightarrow \xx$.  The singularity strength can be reduced since the
+velocity corresponding to a constant density function is
+constant~\cite{poz1992}.  Therefore, the deformation tensor of the
+double-layer potential is equivalent to
+\begin{align*}
+  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
+      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
+\end{align*}
+This expression for the deformation tensor has a singularity that is
+asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
+to achieve spectral accuracy, we apply odd-even
+integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
+the double-layer potential at a discretization point $\xx_i$ on body
+$\gamma_\ell$, with $i$ being odd, is approximated as
+\todo[inline]{fix up this section and move numerics to the next section}
+\begin{align}
+  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_\ell}
+    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
+  \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
+    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
+  \label{eqn:stressOddEven}
+\end{align}
+and a similar approximation is used when $i$ is even.  The deformation
+tensor due to the Stokeslets and rotlets is given in
+equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
+deformation tensor~\eqref{eqn:shearStressJump} is added, and the
+required arclength derivative is computed in Fourier space.  Then, the
+shear stress can be computed by computing the deformation tensor in the
+normal vector, and taking the inner product with the tangent vector.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Interface evolution in the {\thL} framework} 
+\label{sec:thetaL}
+
+%We use a quasi-static approximation so that the velocity field instantaneously changes with the changing geometry.  Therefore, we can alternate between the two main aspects of our simulation
+%\begin{enumerate}
+%\item Given a geometry, compute the shear stress of along the boundary of each of the bodies.
+%\item Given the shear stress, update the geometry according to the erosion model.
+%\end{enumerate}
+
+To handle boundary evolution, we use the {\thL} framework, which offers
+certain advantages in the ability to stabilize fluid-structure interaction problems \cite{hou-low-she1994}.
+Throughout this section, we use the following conventions: the bodies are parametrized in the CCW
+direction and the normal vector points into the bodies (our out of the
+fluid).
+
+For the sake of numerical stability, we will modify the erosion law \eqref{eqn:bodyEvolution} to include a term that depends on the local curvature $\kappa$.
+The idea is to prevent regions of very high curvature.
+The modified normal velocity is
+in \eqref{eqn:bodyEvolution} as follows
+\begin{equation}
+\label{eqn:Vn}
+\Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right)
+\end{equation}
+Here, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean.
+The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity.
+Since a closed body has a mean curvature of $\mean{\kappa} = 2\pi / L$, the term in parentheses has mean zero.
+Thus, this term is area-preserving, so that the only material loss is due to the shear stress itself.
+In addition, we have scaled this term on the $\mean{\atau}$, the average absolute stress, so that it is always proportional to the true source of erosion $\atau$, even as bodies vanish (reword).
+
+We now introduce the tangent angle, $\theta$, defined through the relation
+\begin{equation}
+\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin \theta \right)
+\end{equation}
+where $s$ is arc length. We also introduce the normalized arc length $\alpha = 2 \pi s / L$. In terms of these new variables, the curvature can be expressed as
+\begin{equation}
+\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha}
+\end{equation}
+Substitution into \eqref{eqn:Vn} gives
+\begin{equation}
+\label{eqn:Vn2}
+\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right)
+%\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
+\end{equation}
+
+The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced.
+The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
+\begin{equation}
+\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
+\end{equation}
+The interface evolution is then given by
+\begin{equation}
+\dot{\xx}(t) = \Vn \nn + \Vs \ss.
+\end{equation}
+This evolution equation can be recast in the variables $\theta$ and $L$ as
+\begin{align}
+\label{eqn:Levo1}
+& \tderiv{L}{t} = - 2 \pi \mean{\thalpha \Vn} \\
+\label{eqn:thetaevo0}
+& \pderiv{\theta}{t} = \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
+\end{align}
+Inserting \eqref{eqn:Vn2} for the normal velocity gives
+\begin{equation}
+\label{eqn:thetaevo1}
+\pderiv{\theta}{t} = \frac{2\pi}{L} \left(
+\eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
+\end{equation}
+Note that the highest-order, i.e.~stiff, term in \eqref{eqn:thetaevo1}
+is {\em quasi-linear}. This is the key to the {\thL} method, and allows
+us to use very stable, implicit methods for this stiff term.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quadrature: On Boundary Calculations} 
-\label{sec:on_boundary}
 We start by discussing the quadrature methods that are used to compute
-the velocity~\eqref{eqn:DLP}, shear stress~\eqref{eqn:shearStressDLP},
-pressure~\eqref{eqn:pressureDLP}, and drag~\eqref{eqn:drag} at target
-points on the boundary of the domain.  The velocity on $\bd\Omega$ is
-required to solve the integral equation~\eqref{eqn:completed_BIE} for
-the density function, Stokeslets and rotlets.  Once these are computed,
-computing the shear stress, pressure, and drag is a post-processing
-step.  All these integrals involve integrands that are periodic.  For
-smooth integrands, the trapezoid rule guarantees spectral
-accuracy~\cite{tre-wei2014}.  However, some of the integrands contain a
-singularity whose strength will be reduced with singularity subtraction,
-and then spectral accuracy is achieved with odd-even
-integration~\cite{sid-isr1988} must be used.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Velocity}
+the velocity~\eqref{eqn:DLP} and shear stress~\eqref{eqn:shearStressDLP}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Solving the BIE}
 To numerically evaluate the completed double-layer
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Shear Stress}
-We have decomposed the deformation tensor into the contributions due to
-three different terms.  The contributions from the Stokeslets and the
-rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
-\gamma$.  However, the kernel of the deformation tensor due to the
-double-layer potential~\eqref{eqn:shearStressDLP} 
-\begin{align*}
-  K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
-    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
-    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn)
-    \right. \\ & \hspace{25pt}+ \left.
-    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
-    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right),
-\end{align*}
-has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
-\rightarrow \xx$.  The singularity strength can be reduced since the
-velocity corresponding to a constant density function is
-constant~\cite{poz1992}.  Therefore, the deformation tensor of the
-double-layer potential is equivalent to
-\begin{align*}
-  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
-      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
-\end{align*}
-This expression for the deformation tensor has a singularity that is
-asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
-to achieve spectral accuracy, we apply odd-even
-integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
-the double-layer potential at a discretization point $\xx_i$ on body
-$\gamma_\ell$, with $i$ being odd, is approximated as
-\begin{align}
-  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_\ell}
-    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
-  \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
-    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
-  \label{eqn:stressOddEven}
-\end{align}
-and a similar approximation is used when $i$ is even.  The deformation
-tensor due to the Stokeslets and rotlets is given in
-equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
-deformation tensor~\eqref{eqn:shearStressJump} is added, and the
-required arclength derivative is computed in Fourier space.  Then, the
-shear stress can be computed by computing the deformation tensor in the
-normal vector, and taking the inner product with the tangent vector.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Pressure}
-Similar to the shear stress, the singularity of the pressure
-corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
-too strong for the trapezoid rule to be directly applied.  Therefore, we
-again subtract a constant density function and write the pressure as
-\begin{align*}
-  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
-    \quad \xx \in \bd\Omega
-\end{align*}
-Then, identical to how the shear stress is
-computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
-evaluate this layer potential for pressure.  The pressure due to the
-Stokeslets are given in equation~\eqref{eqn:shearPressureSR}.  Finally,
-to add the jump condition~\eqref{eqn:pressureJump}, Fourier
-differentiation is used to compute the arclength derivative.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Drag}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quadrature: Off Boundary Calculations} 
-\label{sec:off_boundary}
-To analyze the flow, we compute quantities at target points that are in
-the interior of the domain.  In particular, we develop numerical methods
-to compute the velocity~\eqref{eqn:velocityDLP},
-pressure~\eqref{eqn:pressureDLP}, vorticity~\eqref{eqn:vorticityDLP} and
-resistivity~\eqref{eqn:resistivity}.  Since the target points are not on
-the boundary of the domain, all the integrals, except for the
-resistivity, involve integrands that are both periodic and smooth.
-However, when the target points are close to the boundary of the domain,
-the integrand becomes nearly-singular, and these large derivatives
-result in a loss of accuracy that needs to be rectified.  We will be
-adopting a near-singular integration scheme that allows us to compute
-all quantities of interest sufficiently close to $\bd\Omega$ for the
-quantities of interest.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Near-singular integration}
+\subsection{Shear Stress}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Near-singular integration}
 To accurately compute quantities such as the velocity at points $\xx \in
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Resistivity}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Accelerating the Layer Potential Evaluations}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% TIME-STEPPING %%
@@
 
-With the shear stress computed, we are now ready to evolve the interface of each body.
-As described in Section \ref{sec:thetaL}, we use the {\thL} framework, with $\theta$ being the tangent angle and $L$ the total arc length of a given boundary, and with the boundaries parameterized by normalized arc length $\alpha = 2 \pi s / L$.
-
-In addition to the curvature-dependent term in \eqref{eqn:Vn}, we regularize boundary evolution by applying a narrow Gaussian filter to absolute shear stress
+With the shear stress computed, we are now ready to evolve the interface
+of each body. As described in Section~\ref{sec:thetaL}, we use the
+{\thL} framework, with $\theta$ being the tangent angle and $L$ the
+total arc length of a given boundary, and with the boundaries
+parameterized by normalized arc length $\alpha = 2 \pi s / L$.
+
+In addition to the curvature-dependent term in~\eqref{eqn:Vn}, we
+regularize boundary evolution by applying a narrow Gaussian filter to
+absolute shear stress
 \begin{equation}
@@
 \end{equation}
-Here $\sigma$ is the small parameter that determines the width of the filter. The corresponding normal and tangential interface velocities are the given by
+Here $\sigma$ is the small parameter that determines the width of the
+filter. The corresponding normal and tangential interface velocities are
+the given by
 \begin{align}
@@
 \end{align}
-
-%The interface evolution is then given by
-%\begin{equation}
-%\dot{\xx}(t) = \Vn \nn + \Vs \ss.
-%\end{equation}
 
@@
 \end{align}
-So that evolution equations \eqref{eqn:Levo1} and \eqref{eqn:thetaevo1} can be compactly expressed as
+So that evolution equations`\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1}
+can be compactly expressed as
 \begin{align}
@@
 
-Here $\NLterm$ represents the nonlinear terms (and nonlocal etc) in the PDE for $\theta$.
-We will evolve $\theta$ in spectral space, and so introduce the Fourier series
+Here $\NLterm$ represents the nonlinear terms (and nonlocal etc) in the
+PDE for $\theta$.  We will evolve $\theta$ in spectral space, and so
+introduce the Fourier series
 \begin{align}
@@
 \end{align}
-The careful reader will notice that we have separated out the linear part of $\theta$, so that the remaining function is smooth and has a rapidly decaying Fourier series.
-In spectral space, \eqref{eqn:thetaevo2} produces the system of ODEs
+The careful reader will notice that we have separated out the linear
+part of $\theta$, so that the remaining function is smooth and has a
+rapidly decaying Fourier series.  In spectral
+space,~\eqref{eqn:thetaevo2} produces the system of ODEs
 \begin{equation}
@@
 \end{equation}
-Each ODE is first-order and linear (though variable-coefficient due to $\elfun$) and thus can be solved by using the integrating factor
+Each ODE is first-order and linear (though variable-coefficient due to
+$\elfun$) and thus can be solved by using the integrating factor
 \begin{equation}
@@
 \end{align}
-We solve system \eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an explicit, second-order Runge-Kutta method (RK2).
-In particular, we choose the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature term.
-
-At the first stage of RK2 (the half step), we discretize Eqs.~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} as
+We solve system~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an
+explicit, second-order Runge-Kutta method (RK2). In particular, we
+choose the {\em midpoint} RK2 method so as to maximize the smoothing
+effect of the curvature term.
+
+At the first stage of RK2 (the half step), we discretize
+Eqs.~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} as
 \begin{align}
@@
 \end{align}
-where the superscript indicates the time step.
-For simplicity, we have chosen the constant of integration in the exponent of Eq.~\eqref{eq:mu} so that $\mu_k^{(n)} = 1$.
-At the next stage of RK2, we must compute $\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$, which requires a call to the Stokes solver.
-Hence, we must compute $\mu_k^{(n+1/2})$, so that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the mid-step can be computed.
-To compute $\mu_k^{(n+1/2)}$, we use the left-end-point rule (first order, consistent with first forward Euler step of RK2)
+where the superscript indicates the time step. For simplicity, we have
+chosen the constant of integration in the exponent of Eq.~\eqref{eq:mu}
+so that $\mu_k^{(n)} = 1$. At the next stage of RK2, we must compute
+$\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$, which requires a
+call to the Stokes solver. Hence, we must compute $\mu_k^{(n+1/2})$, so
+that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the
+mid-step can be computed. To compute $\mu_k^{(n+1/2)}$, we use the
+left-end-point rule (first order, consistent with first forward Euler
+step of RK2)
 \begin{equation}
@@
 \end{equation}
-so that the smoothing effect of the exponential is obvious. With $\thhat_k^{(n+1/2)}$ computed, it is now possible to compute $\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$.
+so that the smoothing effect of the exponential is obvious. With
+$\thhat_k^{(n+1/2)}$ computed, it is now possible to compute
+$\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$.
 
@@
 \end{align}
-We again compute the integrating factor, $\mu_k^{(n+1)}$ via the ( insert integration rule), giving
+We again compute the integrating factor, $\mu_k^{(n+1)}$ via the (
+insert integration rule), giving
 \begin{align}
@@
 \end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Post Processing Quantities of Interest\label{s:qoi}}
+
+There are several quantities besides the velocity that need to be
+computed.  First, the governing equations~\eqref{eqn:erosionModel}
+require the shear stress along $\gamma_\ell$.  In addition, to study
+characteristics of the flow, the vorticity, pressure, and drag, and
+resistivity will also be computed.  Once
+equation~\eqref{eqn:completed_DLP} is solved for the density function,
+Stokeslets, and rotlets, all of these quantities can be computed by
+evaluating layer potentials that we now derive.
+
+pressure~\eqref{eqn:pressureDLP}, and drag~\eqref{eqn:drag} at target
+points on the boundary of the domain.  The velocity on $\bd\Omega$ is
+required to solve the integral equation~\eqref{eqn:completed_BIE} for
+the density function, Stokeslets and rotlets.  Once these are computed,
+computing the shear stress, pressure, and drag is a post-processing
+step.  All these integrals involve integrands that are periodic.  For
+smooth integrands, the trapezoid rule guarantees spectral
+accuracy~\cite{tre-wei2014}.  However, some of the integrands contain a
+singularity whose strength will be reduced with singularity subtraction,
+and then spectral accuracy is achieved with odd-even
+integration~\cite{sid-isr1988} must be used.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Vorticity}
+For the Stokes equations, on boundaries that have a no-slip boundary
+condition, the shear stress is equivalent to the vorticity $w = v_x -
+u_y$.  Therefore, to compute $w(\xx)$ for $\xx \in \overline{\Omega}$,
+we only need to compute $w(\xx)$ for $\xx \in \Omega$.  As we did for
+the shear stress, we compute the vorticity due to the double-layer
+potential, Stokeslets, and rotlets individually.  The vorticity of the
+double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
+\begin{align}
+  w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
+    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}
+    (\rr \cdot \eeta) ds_{\yy}.
+  \label{eqn:vorticityDLP}
+\end{align}
+The vorticity due to the Stokeslet is
+\begin{align*}
+  w^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
+    \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2},
+\end{align*}
+and the vorticity of a rotlet is zero.  Therefore, the vorticity at $\xx
+\in \Omega$ is
+\begin{align*}
+  w(\xx) = w^\DD(\xx) + w^S(\xx).
+\end{align*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Pressure}
+To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
+same procedure used for the shear stress.  We start by computing the
+pressure of the double-layer potential for $\xx \in \Omega$ and add the
+appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
+is
+\begin{align}
+  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
+    \nn \cdot \eeta(\yy) \,ds_\yy.
+    \label{eqn:pressureDLP}
+\end{align}
+To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
+as $\xx$ tends to $\xx_0$.  The limiting value is given
+by~\cite{qua-bir2014a}
+\begin{align}
+  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
+    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
+  \label{eqn:pressureJump}
+\end{align}
+The pressure due to the Stokeslets is
+\begin{align}
+  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
+  \label{eqn:shearPressureSR}
+\end{align}
+and the pressure due to the rotlets is zero.  Therefore, the pressure is
+\begin{align*}
+  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
+  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
+              p^{S}(\xx), && \xx \in \bd\Omega.
+\end{align*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Drag}
+\todo[inline]{check all signs in this section.  Fortran code assumes a
+normal pointing into the eroding body and a tangent vector that
+corresponds to a couterclockwise parameterization}
+With the pressure and shear stress, the drag on a single body with
+boundary $\gamma_\ell$ is
+\begin{align}
+  F_D = \int_{\gamma_\ell} (-p \nn + \tau \ss)\,ds.
+  \label{eqn:drag}
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Pressure}
+Similar to the shear stress, the singularity of the pressure
+corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
+too strong for the trapezoid rule to be directly applied.  Therefore, we
+again subtract a constant density function and write the pressure as
+\begin{align*}
+  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
+    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
+    \quad \xx \in \bd\Omega
+\end{align*}
+Then, identical to how the shear stress is
+computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
+evaluate this layer potential for pressure.  The pressure due to the
+Stokeslets are given in equation~\eqref{eqn:shearPressureSR}.  Finally,
+to add the jump condition~\eqref{eqn:pressureJump}, Fourier
+differentiation is used to compute the arclength derivative.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Drag}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Quadrature: Off Boundary Calculations} 
+\label{sec:off_boundary}
+To analyze the flow, we compute quantities at target points that are in
+the interior of the domain.  In particular, we develop numerical methods
+to compute the velocity~\eqref{eqn:velocityDLP},
+pressure~\eqref{eqn:pressureDLP}, vorticity~\eqref{eqn:vorticityDLP} and
+resistivity~\eqref{eqn:resistivity}.  Since the target points are not on
+the boundary of the domain, all the integrals, except for the
+resistivity, involve integrands that are both periodic and smooth.
+However, when the target points are close to the boundary of the domain,
+the integrand becomes nearly-singular, and these large derivatives
+result in a loss of accuracy that needs to be rectified.  We will be
+adopting a near-singular integration scheme that allows us to compute
+all quantities of interest sufficiently close to $\bd\Omega$ for the
+quantities of interest.
 

### 2018-01-11 docs/methods/erosion_methods.tex
continued rearrangment of paper

@@
 computed, the shear stress at $\xx_0 \in \bd\Omega$ is
-\begin{align*}
+\begin{align}
   \tau = -2 \left(J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) + 
     \ssigma^S(\xx_0) + \ssigma^R(\xx_0)\right) \nn \cdot \ss.
-\end{align*}
-
-We have decomposed the deformation tensor into the contributions due to
-three different terms.  The contributions from the Stokeslets and the
-rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
-\gamma$.  However, the kernel of the deformation tensor due to the
-double-layer potential~\eqref{eqn:shearStressDLP} 
-\begin{align*}
-  K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
-    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
-    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn)
-    \right. \\ & \hspace{25pt}+ \left.
-    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
-    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right),
-\end{align*}
-has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
-\rightarrow \xx$.  The singularity strength can be reduced since the
-velocity corresponding to a constant density function is
-constant~\cite{poz1992}.  Therefore, the deformation tensor of the
-double-layer potential is equivalent to
-\begin{align*}
-  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
-      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
-\end{align*}
-This expression for the deformation tensor has a singularity that is
-asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
-to achieve spectral accuracy, we apply odd-even
-integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
-the double-layer potential at a discretization point $\xx_i$ on body
-$\gamma_\ell$, with $i$ being odd, is approximated as
-\todo[inline]{fix up this section and move numerics to the next section}
-\begin{align}
-  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_\ell}
-    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
-  \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
-    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
-  \label{eqn:stressOddEven}
-\end{align}
-and a similar approximation is used when $i$ is even.  The deformation
-tensor due to the Stokeslets and rotlets is given in
-equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
-deformation tensor~\eqref{eqn:shearStressJump} is added, and the
-required arclength derivative is computed in Fourier space.  Then, the
-shear stress can be computed by computing the deformation tensor in the
-normal vector, and taking the inner product with the tangent vector.
+  \label{eqn:shearStressLP}
+\end{align}
 
@@
 boundary integral equation solver for
-equation~\eqref{eqn:completed_BIE}, computing the quantities of interest
-in Section~\ref{sec:qois}, and updating the shape of the eroding bodies
-with equation~\eqref{eqn:bodyEvolution}.  So that we can form stable
-simulations with long time horizons, we use numerical methods that
-achieve spectral accuracy in space, second-order accuracy in time, and
-maintain an equispaced discretization of the bodies.
+equation~\eqref{eqn:completed_BIE}, computing the layer potential for
+the shear stress~\eqref{eqn:shearStressLP}, and updating the shape of
+the eroding bodies with equation~\eqref{eqn:bodyEvolution}.  So that we
+can form stable simulations with long time horizons, we use numerical
+methods that achieve spectral accuracy in space, second-order accuracy
+in time, and maintain an equispaced discretization of the bodies.
 
 In Section~\ref{sec:spatial_discretization}, we describe how the
-geometry is represented.  Then, Sections~\ref{sec:on_boundary}
-and~\ref{sec:off_boundary} describe how the velocity and other
-quantities of interest are computed at points on and off the boundary,
-respectively.  Section~\ref{sec:fmm} describes how the layer potentials
-are computed efficiently.  Finally, in Section~\ref{sec:thetaL}, methods
-used to update the shape are described.
+geometry is represented.  Then, Section~\ref{sec:BIE}, we describe how
+the BIE~\eqref{eqn:completed_BIE} is solved.
+Once the density function is found, Section~\ref{sec:shearStress}
+describes how the shear stress is computed.  Then, in
+Section~\ref{timeStepping}, numerical methods for evolving the interface
+are described.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We start by discussing the quadrature methods that are used to compute
-the velocity~\eqref{eqn:DLP} and shear stress~\eqref{eqn:shearStressDLP}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Solving the BIE}
+\label{sec:BIE}
 To numerically evaluate the completed double-layer
@@
 
+The linear system~\eqref{eqn:completed_BIE_discretized} is solved
+iteratively with the generalized minimal residual method
+(GMRES)~\cite{saa-sch1986}.  Since the BIE is second-kind, this
+guarantees that a mesh-independent number of GMRES iterations are
+required~\cite{cam-ips-kel-mey-xue1996}.  Therefore, the asymptotic cost
+is determined by the cost of performing a matrix-vector multiplication,
+and the bulk of the most expensive part is evaluating the $N$-term sum
+in~\eqref{eqn:completed_BIE_discretized}.  Naively, evaluating this sum
+at all points $\xx_i$, $i=1,N$ requires $\bigO(N^2)$ operations.  To
+reduce the computational cost of this calculation, we use the Fast
+Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} to reduce the
+complexity from $\bigO(N^2)$ to $\bigO(N)$.  Since the number of
+required GMRES iterations is mesh-independent, the overall complexity
+for solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Shear Stress}
-
+\label{sec:shearStress}
+We have decomposed the deformation tensor into the contributions due to
+three different terms.  The contributions from the Stokeslets and the
+rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
+\gamma$.  However, the kernel of the deformation tensor due to the
+double-layer potential~\eqref{eqn:shearStressDLP} 
+\begin{align*}
+  K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
+    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
+    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn)
+    \right. \\ & \hspace{25pt}+ \left.
+    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
+    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
+  \right),
+\end{align*}
+has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
+\rightarrow \xx$.  The singularity strength can be reduced since the
+velocity corresponding to a constant density function is
+constant~\cite{poz1992}.  Therefore, the deformation tensor of the
+double-layer potential is equivalent to
+\begin{align*}
+  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
+      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
+\end{align*}
+This expression for the deformation tensor has a singularity that is
+asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
+to achieve spectral accuracy, we apply odd-even
+integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
+the double-layer potential at a discretization point $\xx_i$ on body
+$\gamma_\ell$, with $i$ being odd, is approximated as
+\begin{align}
+  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_\ell}
+    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
+  \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
+    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
+  \label{eqn:stressOddEven}
+\end{align}
+and a similar approximation is used when $i$ is even.  The deformation
+tensor due to the Stokeslets and rotlets is given in
+equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
+deformation tensor~\eqref{eqn:shearStressJump} is added, and the
+required arclength derivative is computed in Fourier space.  Then, the
+shear stress can be computed by computing the deformation tensor in the
+normal vector, and taking the inner product with the tangent vector.
+
+We do not employ an FMM to evaluate the shear stress, so the cost of
+evaluating the shear stress is $\bigO(N^2)$.  However, this calculation
+is only performed once per time step as opposed to the velocity
+double-layer potential that must be evaluated at each GMRES iteration.
+In future work, we plan to use a kernel-independent
+FMM~\cite{yin-bir-zor2004} to evaluate the shear stress with $\bigO(N)$
+operations.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% TIME-STEPPING %%
+\subsection{Time-stepping with the {\thL} method} 
+\label{sec:timeStepping}
+
+With the shear stress computed, we are now ready to evolve the interface
+of each body. As described in Section~\ref{sec:thetaL}, we use the
+{\thL} framework, with $\theta$ being the tangent angle and $L$ the
+total arc length of a given boundary, and with the boundaries
+parameterized by normalized arc length $\alpha = 2 \pi s / L$.
+
+In addition to the curvature-dependent term in~\eqref{eqn:Vn}, we
+regularize boundary evolution by applying a narrow Gaussian filter to
+absolute shear stress
+\begin{equation}
+\atausig = \int_{\gamma} \frac{1}{\sqrt{2\pi} \sigma} \exp \left(- \frac{\alpha'^2}{2 \sigma^2}\right) \abs{ \tau(\alpha - \alpha') } \, d\alpha'
+\end{equation}
+Here $\sigma$ is the small parameter that determines the width of the
+filter. The corresponding normal and tangential interface velocities are
+the given by
+\begin{align}
+& \Vnsig = \atausig +  \eps \mean{\atausig}   \left(\pderiv{\theta}{\alpha} - 1 \right) \\
+& \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig}
+\end{align}
+
+For simplicity, we introduce the variables
+\begin{align}
+\label{eq:M}
+& \Mterm = - 2 \pi \mean{\thalpha \Vnsig} \\
+\label{eq:N}
+& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha \Vssig \right) \\
+\label{eq:elfun}
+& \elfun = \frac{2 \pi  \mean{\atausig}}{L}
+\end{align}
+So that evolution equations`\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1}
+can be compactly expressed as
+\begin{align}
+\label{eqn:Levo2}
+& \tderiv{L}{t} = \Mterm \\
+\label{eqn:thetaevo2}
+& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
+\end{align}
+
+Here $\NLterm$ represents the nonlinear terms (and nonlocal etc) in the
+PDE for $\theta$.  We will evolve $\theta$ in spectral space, and so
+introduce the Fourier series
+\begin{align}
+& \theta(\alpha,t) = \alpha + \FourierSum \thhat_k e^{ i k \alpha} \\
+& \NLterm(\alpha,t)  = \FourierSum \hat{\NLterm}_k e^{ i k \alpha}
+\end{align}
+The careful reader will notice that we have separated out the linear
+part of $\theta$, so that the remaining function is smooth and has a
+rapidly decaying Fourier series.  In spectral
+space,~\eqref{eqn:thetaevo2} produces the system of ODEs
+\begin{equation}
+\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{\NLterm}_k
+\end{equation}
+Each ODE is first-order and linear (though variable-coefficient due to
+$\elfun$) and thus can be solved by using the integrating factor
+\begin{equation}
+\label{eq:mu}
+\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right)
+\end{equation}
+We are therefore led to the coupled system of ODEs
+\begin{align}
+\label{eqn:Levo2}
+& \tderiv{L}{t} = \Mterm \\
+\label{eqn:thetaevo2}
+& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{\NLterm}_k
+\end{align}
+We solve system~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an
+explicit, second-order Runge-Kutta method (RK2). In particular, we
+choose the {\em midpoint} RK2 method so as to maximize the smoothing
+effect of the curvature term.
+
+At the first stage of RK2 (the half step), we discretize
+Eqs.~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} as
+\begin{align}
+\label{eq:L12}
+& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)} \\
+& \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \thhat_k^{(n)}}{\Dt/2} = \hat{\NLterm}_k^{(n)}
+\end{align}
+where the superscript indicates the time step. For simplicity, we have
+chosen the constant of integration in the exponent of Eq.~\eqref{eq:mu}
+so that $\mu_k^{(n)} = 1$. At the next stage of RK2, we must compute
+$\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$, which requires a
+call to the Stokes solver. Hence, we must compute $\mu_k^{(n+1/2})$, so
+that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the
+mid-step can be computed. To compute $\mu_k^{(n+1/2)}$, we use the
+left-end-point rule (first order, consistent with first forward Euler
+step of RK2)
+\begin{equation}
+\mu_k^{(n+1/2)} = \exp \left( \epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
+\end{equation}
+It is instructive to recast as
+\begin{equation}
+\thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{\NLterm}_k^{(n)} \right)
+\exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
+\end{equation}
+so that the smoothing effect of the exponential is obvious. With
+$\thhat_k^{(n+1/2)}$ computed, it is now possible to compute
+$\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$.
+
+Next, at the second stage of RK2, we discretize as
+\begin{align}
+& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)} \\
+& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}
+\end{align}
+We again compute the integrating factor, $\mu_k^{(n+1)}$ via the (
+insert integration rule), giving
+\begin{align}
+\thhat_k^{(n+1)} = 
+& \thhat_k^{(n)}
+\exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
+& \Dt \, \hat{\NLterm}_k^{(n+1/2)}
+\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right)
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Post Processing Quantities of Interest\label{s:qoi}}
+
+To study characteristics of the flow, the vorticity
+(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
+and drag (Section~\ref{sec:drag}) will be computed.  Once
+equation~\eqref{eqn:completed_DLP} is solved for the density function,
+Stokeslets, and rotlets, all of these quantities can be computed by
+evaluating layer potentials that we now derive.  All layer potentials
+involve integrands that are periodic, so the trapezoid rule guarantees
+spectral accuracy if the integrand is smooth~\cite{tre-wei2014}.
+However, some of the integrands contain a singularity whose strength
+will be reduced with singularity subtraction, and then spectral accuracy
+is achieved with odd-even integration~\cite{sid-isr1988} must be used.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Vorticity}
+\label{sec:vorticity}
+For the Stokes equations, on boundaries that have a no-slip boundary
+condition, the shear stress is equivalent to the vorticity $w = v_x -
+u_y$.  Therefore, to compute $w(\xx)$ for $\xx \in \overline{\Omega}$,
+we only need to compute $w(\xx)$ for $\xx \in \Omega$.  As we did for
+the shear stress, we compute the vorticity due to the double-layer
+potential, Stokeslets, and rotlets individually.  The vorticity of the
+double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
+\begin{align}
+  w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
+    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}
+    (\rr \cdot \eeta) ds_{\yy}.
+  \label{eqn:vorticityDLP}
+\end{align}
+The vorticity due to the Stokeslet is
+\begin{align*}
+  w^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
+    \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2},
+\end{align*}
+and the vorticity of a rotlet is zero.  Therefore, the vorticity at $\xx
+\in \Omega$ is
+\begin{align*}
+  w(\xx) = w^\DD(\xx) + w^S(\xx).
+\end{align*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Pressure}
+\label{sec:pressure}
+To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
+same procedure used for the shear stress.  We start by computing the
+pressure of the double-layer potential for $\xx \in \Omega$ and add the
+appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
+is
+\begin{align}
+  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
+    \nn \cdot \eeta(\yy) \,ds_\yy.
+    \label{eqn:pressureDLP}
+\end{align}
+To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
+as $\xx$ tends to $\xx_0$.  The limiting value is given
+by~\cite{qua-bir2014a}
+\begin{align}
+  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
+    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
+  \label{eqn:pressureJump}
+\end{align}
+The pressure due to the Stokeslets is
+\begin{align}
+  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
+  \label{eqn:shearPressureSR}
+\end{align}
+and the pressure due to the rotlets is zero.  Therefore, the pressure is
+\begin{align*}
+  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
+  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
+              p^{S}(\xx), && \xx \in \bd\Omega.
+\end{align*}
+
+Similar to the shear stress, the singularity of the pressure
+corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
+too strong for the trapezoid rule to be directly applied.  Therefore, we
+again subtract a constant density function and write the pressure as
+\begin{align*}
+  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
+    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
+    \quad \xx \in \bd\Omega
+\end{align*}
+Then, identical to how the shear stress is
+computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
+evaluate this layer potential for pressure.  The pressure due to the
+Stokeslets are given in equation~\eqref{eqn:shearPressureSR}.  Finally,
+to add the jump condition~\eqref{eqn:pressureJump}, Fourier
+differentiation is used to compute the arclength derivative.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Drag}
+\label{sec:drag}
+\todo[inline]{check all signs in this section.  Fortran code assumes a
+normal pointing into the eroding body and a tangent vector that
+corresponds to a couterclockwise parameterization}
+With the pressure and shear stress, the drag on a single body with
+boundary $\gamma_\ell$ is
+\begin{align}
+  F_D = \int_{\gamma_\ell} (-p \nn + \tau \ss)\,ds.
+  \label{eqn:drag}
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Quadrature: Off Boundary Calculations} 
+\label{sec:off_boundary}
+To analyze the flow, we compute quantities at target points that are in
+the interior of the domain.  In particular, we develop numerical methods
+to compute the velocity~\eqref{eqn:velocityDLP},
+pressure~\eqref{eqn:pressureDLP}, vorticity~\eqref{eqn:vorticityDLP} and
+resistivity~\eqref{eqn:resistivity}.  Since the target points are not on
+the boundary of the domain, all the integrals, except for the
+resistivity, involve integrands that are both periodic and smooth.
+However, when the target points are close to the boundary of the domain,
+the integrand becomes nearly-singular, and these large derivatives
+result in a loss of accuracy that needs to be rectified.  We will be
+adopting a near-singular integration scheme that allows us to compute
+all quantities of interest sufficiently close to $\bd\Omega$ for the
+quantities of interest.
+
+\todo[inline]{DUMP OF OLD TEXT}
+discretizations of
+layer potentials~\eqref{eqn:layerPotential} at a large number of points.
+If a direct summation method is used to evaluate these sums at $N_\tar$
+points, this requires $\bigO(NN_\tar)$ operations.  The layer potential
+that is evaluated most frequently is in the GMRES iteration where the
+layer potential $\DD$ is evaluated to compute the velocity at all points
+on the boundary must be evaluated~\eqref{eqn:DLP}.
+
+In our implementation, the deformation tensor and vorticity are computed
+with a direct summation, and this requires $\bigO(N^2)$ and $\bigO(N
+N_\tar)$ operations, respectively.  Since this calculation is only
+computed once per time step, while the velocity is calculated at each
+GMRES iteration, the computational cost is manageable.  However, in
+future work, to simulate erosion in a dense packing of grains, a fast
+summation method, such as the kernel-independent
+FMM~\cite{yin-bir-zor2004}, will be incorporated.
+
+\todo[inline]{DUMP OF OLD TEXT}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Accelerating the Layer Potential Evaluations}
-\label{sec:fmm}
-The bulk of the computational work is evaluating discretizations of
-layer potentials~\eqref{eqn:layerPotential} at a large number of points.
-If a direct summation method is used to evaluate these sums at $N_\tar$
-points, this requires $\bigO(NN_\tar)$ operations.  The layer potential
-that is evaluated most frequently is in the GMRES iteration where the
-layer potential $\DD$ is evaluated to compute the velocity at all points
-on the boundary must be evaluated~\eqref{eqn:DLP}.  To reduce the
-computational cost of this calculation, we use the Fast Multipole Method
-(FMM)~\cite{gre-rok1987, gre-gre-may1992} to reduce the complexity from
-$\bigO(N^2)$ to $\bigO(N)$.  Since we are discretizing a second-kind
-integral equation, the number of GMRES iterations is bounded independent
-of $N$~\cite{cam-ips-kel-mey-xue1996}, and the overall complexity for
-solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
-
-In our implementation, the deformation tensor and vorticity are computed
-with a direct summation, and this requires $\bigO(N^2)$ and $\bigO(N
-N_\tar)$ operations, respectively.  Since this calculation is only
-computed once per time step, while the velocity is calculated at each
-GMRES iteration, the computational cost is manageable.  However, in
-future work, to simulate erosion in a dense packing of grains, a fast
-summation method, such as the kernel-independent
-FMM~\cite{yin-bir-zor2004}, will be incorporated.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% TIME-STEPPING %%
-\subsection{Time-stepping with the {\thL} method}
-
-With the shear stress computed, we are now ready to evolve the interface
-of each body. As described in Section~\ref{sec:thetaL}, we use the
-{\thL} framework, with $\theta$ being the tangent angle and $L$ the
-total arc length of a given boundary, and with the boundaries
-parameterized by normalized arc length $\alpha = 2 \pi s / L$.
-
-In addition to the curvature-dependent term in~\eqref{eqn:Vn}, we
-regularize boundary evolution by applying a narrow Gaussian filter to
-absolute shear stress
-\begin{equation}
-\atausig = \int_{\gamma} \frac{1}{\sqrt{2\pi} \sigma} \exp \left(- \frac{\alpha'^2}{2 \sigma^2}\right) \abs{ \tau(\alpha - \alpha') } \, d\alpha'
-\end{equation}
-Here $\sigma$ is the small parameter that determines the width of the
-filter. The corresponding normal and tangential interface velocities are
-the given by
-\begin{align}
-& \Vnsig = \atausig +  \eps \mean{\atausig}   \left(\pderiv{\theta}{\alpha} - 1 \right) \\
-& \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig}
-\end{align}
-
-For simplicity, we introduce the variables
-\begin{align}
-\label{eq:M}
-& \Mterm = - 2 \pi \mean{\thalpha \Vnsig} \\
-\label{eq:N}
-& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha \Vssig \right) \\
-\label{eq:elfun}
-& \elfun = \frac{2 \pi  \mean{\atausig}}{L}
-\end{align}
-So that evolution equations`\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1}
-can be compactly expressed as
-\begin{align}
-\label{eqn:Levo2}
-& \tderiv{L}{t} = \Mterm \\
-\label{eqn:thetaevo2}
-& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
-\end{align}
-
-Here $\NLterm$ represents the nonlinear terms (and nonlocal etc) in the
-PDE for $\theta$.  We will evolve $\theta$ in spectral space, and so
-introduce the Fourier series
-\begin{align}
-& \theta(\alpha,t) = \alpha + \FourierSum \thhat_k e^{ i k \alpha} \\
-& \NLterm(\alpha,t)  = \FourierSum \hat{\NLterm}_k e^{ i k \alpha}
-\end{align}
-The careful reader will notice that we have separated out the linear
-part of $\theta$, so that the remaining function is smooth and has a
-rapidly decaying Fourier series.  In spectral
-space,~\eqref{eqn:thetaevo2} produces the system of ODEs
-\begin{equation}
-\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{\NLterm}_k
-\end{equation}
-Each ODE is first-order and linear (though variable-coefficient due to
-$\elfun$) and thus can be solved by using the integrating factor
-\begin{equation}
-\label{eq:mu}
-\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right)
-\end{equation}
-We are therefore led to the coupled system of ODEs
-\begin{align}
-\label{eqn:Levo2}
-& \tderiv{L}{t} = \Mterm \\
-\label{eqn:thetaevo2}
-& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{\NLterm}_k
-\end{align}
-We solve system~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an
-explicit, second-order Runge-Kutta method (RK2). In particular, we
-choose the {\em midpoint} RK2 method so as to maximize the smoothing
-effect of the curvature term.
-
-At the first stage of RK2 (the half step), we discretize
-Eqs.~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} as
-\begin{align}
-\label{eq:L12}
-& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)} \\
-& \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \thhat_k^{(n)}}{\Dt/2} = \hat{\NLterm}_k^{(n)}
-\end{align}
-where the superscript indicates the time step. For simplicity, we have
-chosen the constant of integration in the exponent of Eq.~\eqref{eq:mu}
-so that $\mu_k^{(n)} = 1$. At the next stage of RK2, we must compute
-$\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$, which requires a
-call to the Stokes solver. Hence, we must compute $\mu_k^{(n+1/2})$, so
-that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the
-mid-step can be computed. To compute $\mu_k^{(n+1/2)}$, we use the
-left-end-point rule (first order, consistent with first forward Euler
-step of RK2)
-\begin{equation}
-\mu_k^{(n+1/2)} = \exp \left( \epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
-\end{equation}
-It is instructive to recast as
-\begin{equation}
-\thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{\NLterm}_k^{(n)} \right)
-\exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
-\end{equation}
-so that the smoothing effect of the exponential is obvious. With
-$\thhat_k^{(n+1/2)}$ computed, it is now possible to compute
-$\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$.
-
-Next, at the second stage of RK2, we discretize as
-\begin{align}
-& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)} \\
-& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}
-\end{align}
-We again compute the integrating factor, $\mu_k^{(n+1)}$ via the (
-insert integration rule), giving
-\begin{align}
-\thhat_k^{(n+1)} = 
-& \thhat_k^{(n)}
-\exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
-& \Dt \, \hat{\NLterm}_k^{(n+1/2)}
-\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right)
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Post Processing Quantities of Interest\label{s:qoi}}
-
-There are several quantities besides the velocity that need to be
-computed.  First, the governing equations~\eqref{eqn:erosionModel}
-require the shear stress along $\gamma_\ell$.  In addition, to study
-characteristics of the flow, the vorticity, pressure, and drag, and
-resistivity will also be computed.  Once
-equation~\eqref{eqn:completed_DLP} is solved for the density function,
-Stokeslets, and rotlets, all of these quantities can be computed by
-evaluating layer potentials that we now derive.
-
-pressure~\eqref{eqn:pressureDLP}, and drag~\eqref{eqn:drag} at target
-points on the boundary of the domain.  The velocity on $\bd\Omega$ is
-required to solve the integral equation~\eqref{eqn:completed_BIE} for
-the density function, Stokeslets and rotlets.  Once these are computed,
-computing the shear stress, pressure, and drag is a post-processing
-step.  All these integrals involve integrands that are periodic.  For
-smooth integrands, the trapezoid rule guarantees spectral
-accuracy~\cite{tre-wei2014}.  However, some of the integrands contain a
-singularity whose strength will be reduced with singularity subtraction,
-and then spectral accuracy is achieved with odd-even
-integration~\cite{sid-isr1988} must be used.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Vorticity}
-For the Stokes equations, on boundaries that have a no-slip boundary
-condition, the shear stress is equivalent to the vorticity $w = v_x -
-u_y$.  Therefore, to compute $w(\xx)$ for $\xx \in \overline{\Omega}$,
-we only need to compute $w(\xx)$ for $\xx \in \Omega$.  As we did for
-the shear stress, we compute the vorticity due to the double-layer
-potential, Stokeslets, and rotlets individually.  The vorticity of the
-double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
-\begin{align}
-  w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
-    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}
-    (\rr \cdot \eeta) ds_{\yy}.
-  \label{eqn:vorticityDLP}
-\end{align}
-The vorticity due to the Stokeslet is
-\begin{align*}
-  w^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
-    \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2},
-\end{align*}
-and the vorticity of a rotlet is zero.  Therefore, the vorticity at $\xx
-\in \Omega$ is
-\begin{align*}
-  w(\xx) = w^\DD(\xx) + w^S(\xx).
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pressure}
-To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
-same procedure used for the shear stress.  We start by computing the
-pressure of the double-layer potential for $\xx \in \Omega$ and add the
-appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
-is
-\begin{align}
-  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot \eeta(\yy) \,ds_\yy.
-    \label{eqn:pressureDLP}
-\end{align}
-To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
-as $\xx$ tends to $\xx_0$.  The limiting value is given
-by~\cite{qua-bir2014a}
-\begin{align}
-  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
-    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
-  \label{eqn:pressureJump}
-\end{align}
-The pressure due to the Stokeslets is
-\begin{align}
-  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
-  \label{eqn:shearPressureSR}
-\end{align}
-and the pressure due to the rotlets is zero.  Therefore, the pressure is
-\begin{align*}
-  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
-  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
-              p^{S}(\xx), && \xx \in \bd\Omega.
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Drag}
-\todo[inline]{check all signs in this section.  Fortran code assumes a
-normal pointing into the eroding body and a tangent vector that
-corresponds to a couterclockwise parameterization}
-With the pressure and shear stress, the drag on a single body with
-boundary $\gamma_\ell$ is
-\begin{align}
-  F_D = \int_{\gamma_\ell} (-p \nn + \tau \ss)\,ds.
-  \label{eqn:drag}
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pressure}
-Similar to the shear stress, the singularity of the pressure
-corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
-too strong for the trapezoid rule to be directly applied.  Therefore, we
-again subtract a constant density function and write the pressure as
-\begin{align*}
-  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
-    \quad \xx \in \bd\Omega
-\end{align*}
-Then, identical to how the shear stress is
-computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
-evaluate this layer potential for pressure.  The pressure due to the
-Stokeslets are given in equation~\eqref{eqn:shearPressureSR}.  Finally,
-to add the jump condition~\eqref{eqn:pressureJump}, Fourier
-differentiation is used to compute the arclength derivative.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Drag}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quadrature: Off Boundary Calculations} 
-\label{sec:off_boundary}
-To analyze the flow, we compute quantities at target points that are in
-the interior of the domain.  In particular, we develop numerical methods
-to compute the velocity~\eqref{eqn:velocityDLP},
-pressure~\eqref{eqn:pressureDLP}, vorticity~\eqref{eqn:vorticityDLP} and
-resistivity~\eqref{eqn:resistivity}.  Since the target points are not on
-the boundary of the domain, all the integrals, except for the
-resistivity, involve integrands that are both periodic and smooth.
-However, when the target points are close to the boundary of the domain,
-the integrand becomes nearly-singular, and these large derivatives
-result in a loss of accuracy that needs to be rectified.  We will be
-adopting a near-singular integration scheme that allows us to compute
-all quantities of interest sufficiently close to $\bd\Omega$ for the
-quantities of interest.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results\label{s:results}}
 
-With the description of the numerical methods complete, we now present results on bodies eroding in Stokes flow.
-We first discuss simulations of a single eroding body, which can be compared with analytical results for validation, before discussing the erosion of many bodies.
+With the description of the numerical methods complete, we now present
+results on bodies eroding in Stokes flow. We first discuss simulations
+of a single eroding body, which can be compared with analytical results
+for validation, before discussing the erosion of many bodies.
 
@@
 
-In the case of a single eroding body, certain analytical results can be derived regarding the limiting shape and vanishing rate. These results allow validation of our simulation.
+In the case of a single eroding body, certain analytical results can be
+derived regarding the limiting shape and vanishing rate. These results
+allow validation of our simulation.
 
@@
 
-We first show a single body eroding, with the surrounding vorticity field visualized in Fig.~4.
-The body develops a corner at its front and rear stagnation points.
-It maintains for-aft symmetry due to the time-reversibility of Stokes flow.
+We first show a single body eroding, with the surrounding vorticity
+field visualized in Fig.~4. The body develops a corner at its front and
+rear stagnation points. It maintains for-aft symmetry due to the
+time-reversibility of Stokes flow.
 
@@
 
-In Fig.~5a, we visualize the interfaces color coded in time.
-In Fig.~5b, we show the absolute shear stress, $\atau$, as it varies over the surface of the body.
-Initially, the shear stress is a hump shape.
-As time progresses, the stress becomes more evenly distributed, with the exception of the front/rear corner where the curvature is high.
+In Fig.~5a, we visualize the interfaces color coded in time. In Fig.~5b,
+we show the absolute shear stress, $\atau$, as it varies over the
+surface of the body. Initially, the shear stress is a hump shape. As
+time progresses, the stress becomes more evenly distributed, with the
+exception of the front/rear corner where the curvature is high.
 
@@
 \end{equation}
-However, this law must be modified for 2D flow, which represents 3D bodies of large extent.
-As the body vanishes, the walls have an ever decreasing influence.
-Thus, the stress must be consistent with free-space slender-body theory as it vanishes.
-The stress law consistent with slender body theory (a long cylinder held perpendicular to a flow) is
+However, this law must be modified for 2D flow, which represents 3D
+bodies of large extent. As the body vanishes, the walls have an ever
+decreasing influence. Thus, the stress must be consistent with
+free-space slender-body theory as it vanishes. The stress law consistent
+with slender body theory (a long cylinder held perpendicular to a flow)
+is
 \begin{equation}
@@
 
-Then the rate of change of the body area is proportional to the shear stress times the total arc length exposed
+Then the rate of change of the body area is proportional to the shear
+stress times the total arc length exposed
 \begin{equation}
@@
 
-In Fig.~6a, we show the body area vs time measured in the simulation against the above scaling law. In the scaling law, we chose, $C = 0.42$ (check this?)
+In Fig.~6a, we show the body area vs time measured in the simulation
+against the above scaling law. In the scaling law, we chose, $C = 0.42$
+(check this?)
 
@@
 \begin{center}
-\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is 56\% of the vanishing time.
+\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is
+56\% of the vanishing time.
 } 

### 2018-01-12 docs/methods/erosion_methods.tex
what did I change? I thought I pushed???
edited section 4

@@
 \section{Introduction\label{s:intro}}
-Erosion is a fluid-mechanical process that occurs when a fluid alters
-the geometry.  Erosion is responsible for a variety of processes, many
-of which are geophysical.  For example, sand dunes are longer on the
-windward side because of the wind erosion.  Another applications is
-erosion caused by groundwater flow, where a slow moving fluid erodes
-channels, or conduits, in the earth which creates a heterogeneous media
-that has a large effect on the resulting flow. Erosion is also important
-in the biophysical community. Plaque erosion in arteries is
-key to understanding heart disease~\cite{sha2002,
+Erosion is one example of a fluid-mechanical process that occurs when a
+fluid alters the geometry.  Erosion is responsible for a variety of
+processes, many of which are geophysical.  For example, sand dunes are
+longer on the windward side because of the wind erosion.  Another
+applications is erosion caused by groundwater flow, where a slow moving
+fluid erodes channels, or conduits, in the earth which creates a
+heterogeneous media that has a large effect on the resulting flow.
+Erosion is also important in the biophysical community. Plaque erosion
+in arteries is key to understanding heart disease~\cite{sha2002,
 gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can
@@
 
+\todo[inline]{DUMP OF TEXT}
+This choice is based on experimental work of Ristroph et
+al.~\cite{ris-moo-chi-she-zha2012}, but other models for erosion are
+possible.  For example, some models use an erosion rate that is
+proportional to a power of the magnitude of the shear
+stress~\cite{par-izu2000}, while others introduced a shear stress below
+which erosion does not occur~\cite{lag2000}.
+\todo[inline]{DUMP OF TEXT}
+
 \paragraph{Limitations} There are two main limitations of the current
-work.  First, the flow is assumed to be two-dimensional.  Although
-several flows can be described to good accuracy under a two-dimensional
-approximation, certain phenomena occur only in three dimensions.  The
-boundary integral equation formulation for the fluid solver exists, and
-the main challenges of a BIE solver have been addressed by other groups
-including surface representation~\cite{yin-bir-zor2006,
-vee-rah-bir-zor2011}, near-singular integration~\cite{yin-bir-zor2006,
-kli-tor2016b}, and fast summation methods~\cite{yin-bir-zor2004,
-ros-ols2015}.  The more significant challenge of extending our work to
-three dimensions is guaranteeing that the mesh does not become
-distorted, which can be done, for example, by using an extension of the
-two-dimensional {\thL} formulation~\cite{amb-sie-tlu2013}.
+work.  First, the flow is assumed to be two-dimensional.  However, by
+assuming that the flow is two-dimensional, we are able to simulate the
+erosion of more bodies and with higher resolution than would be
+available in three dimensions.  Moreover, Several flows can be described
+to good accuracy under a two-dimensional approximation, certain
+phenomena occur only in three dimensions.  The boundary integral
+equation formulation for the fluid solver exists, and the main
+challenges of a BIE solver have been addressed by other groups including
+surface representation~\cite{yin-bir-zor2006, vee-rah-bir-zor2011},
+near-singular integration~\cite{yin-bir-zor2006, kli-tor2016b}, and fast
+summation methods~\cite{yin-bir-zor2004, ros-ols2015}.  The more
+significant challenge of extending our work to three dimensions is
+guaranteeing that the mesh does not become distorted, which can be done,
+for example, by using an extension of the two-dimensional {\thL}
+formulation~\cite{amb-sie-tlu2013}.
 
@@
 \section{Formulation\label{s:formulation}} 
-Let us first define the main variables used to model erosion.  We only
+We start by defining the main variables used to model erosion.  We only
 consider flows that are confined by a solid wall $\Gamma$ that encloses
@@
 velocity} \\
-\dot{\xx}(t) = \abs{\tau} \nn, &\hspace{20pt} \xx \in \gamma,
+V_\nn = \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
 &&\mbox{erosion model},
@@
 \end{equation}
-where $\nn$ is the outward unit normal vector which points away from the
-fluid, and $\mu$ is the fluid viscosity.  The outer wall is formed by
-rounding off the corners of $[-3,3] \times [-1,1]$, and we enforce the
-Hagen-Poiseuille flow
+where $V_\nn$ is the normal velocity of the interface and $\mu$ is the
+fluid viscosity.  The outer wall is formed by rounding off the corners
+of $[-3,3] \times [-1,1]$, and we enforce the Hagen-Poiseuille flow
 \begin{align*}
@@
 how the incompressible Stokes equations are solved in $\Omega$ using a
-boundary integral equation in Section~\ref{sec:bies}.  Then, in
-Section~\ref{sec:qois}, we discuss how the shear stress, pressure, and
-drag can all be readily computed.
+boundary integral equation in Section~\ref{sec:bies}.  In
+Section~\ref{sec:shearStressLP}, we discuss how the shear stress is
+computed.  Finally, in Section~\ref{sec:thetaL}, we describe how corners
+in the geometry are avoided and perform a change of coordinates that
+linearizes a stiff term.
 
@@
 
-To model erosion, we the normal velocity is prescribed to be
-proportional to the absolute value of the shear stress.  This choice is
-based on experimental work of Ristroph et
-al.~\cite{ris-moo-chi-she-zha2012}, but other models for erosion are
-possible.  For example, some models use an erosion rate that is
-proportional to a power of the magnitude of the shear
-stress~\cite{par-izu2000}, while others introduced a shear stress below
-which erosion does not occur~\cite{lag2000}.
-
-The constant of proportionality sets the time scale, and we set its
-value to be 1
-\begin{align}
-  \dot{\xx}(t) = \abs{\tau} \nn.
+To model erosion, the normal velocity is prescribed to be
+proportional to the absolute value of the shear stress.   Since the
+constant of proportionality only sets the time scale, we let $V_\nn =
+|\tau|$ as described in equation~\eqref{eqn:erosionModel}.
+\begin{align}
+  V{\nn} = \abs{\tau} \nn.
   \label{eqn:bodyEvolution}
 \end{align}
-For the sake of numerical stability, we modify this law in Section \ref{sec:thetaL}.
-
-\todo[inline]{Describe the erosion model and its justification}
-\cite{moo-ris-chi-zha-she2013}
+For the sake of numerical stability, we modify this law in
+Section~\ref{sec:thetaL}.
 
@@
 \label{sec:bies}
-Here we describe a boundary integral equation for the governing
-equations.   This requires solving the incompressible Stokes equations
+Here we describe a boundary integral equation to solve the fluid
+equations. In particular, we solve the incompressible Stokes equations
 with Dirichlet boundary conditions 
@@
   \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
-  \uu &= \ff,  && \xx \in \bd\Omega,
+  \uu &= \ff,  && \xx \in \bd\Omega.
 \end{alignat*}
-and also computing several quantities of interest, including the shear
-stress.  The viscosity $\mu$ sets the time scale, and we will assume
-that $\mu=1$.  We start by defining the double-layer potential, which is
-the convolution of the stresslet with a density function
+As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.  We
+start by defining the double-layer potential
 $\eeta:\bd\Omega \rightarrow \RR^2$,
@@
 \end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
-normal at $\yy$.  For any density function $\eeta$, the double-layer
-potential satisfies the incompressible Stokes equations, but it can not
-capture velocity fields corresponding to rigid body
-motions~\cite{pow-mir1987}.  A standard method to remove this rank
-deficiency is to complement the double-layer potential with a Stokeslets
-and rotlets centered inside each interior body
+where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
+normal at $\yy$, and $\eeta$ is an unknown density function.  The
+double-layer potential can not capture velocity fields corresponding to
+rigid body motions~\cite{pow-mir1987}, and this is rectified by
+introducing additional terms for each body.  The rank deficiency removed
+by complementing the double-layer potential with a Stokeslets and
+rotlets centered inside each interior body
 \begin{align}
@@
 \end{align*}
-is being used to remove the rank one null space that results from the
-compatibility constraint that results from the flux-free requirement of
-$\ff$.
+removes the rank one null space that results from the compatibility
+constraint that results from the flux-free requirement of $\ff$.
 
@@
 \subsection{Computing the Shear Stress}
+\label{sec:shearStressLP}
 The shear stress is
@@
 completed double-layer potential~\eqref{eqn:completed_DLP} involves
-three terms: the double-layer potential $\DD$, the Stokeslets $S$, and
-the rotlets $R$.  We first compute the deformation tensor $\ssigma =
+three terms: the double-layer potential, the Stokeslets, and the
+rotlets.  We compute the deformation tensor $\ssigma =
 \frac{1}{2}(\nabla\uu + \nabla\uu^T)$ for each of these terms
@@
 
-%We use a quasi-static approximation so that the velocity field instantaneously changes with the changing geometry.  Therefore, we can alternate between the two main aspects of our simulation
-%\begin{enumerate}
-%\item Given a geometry, compute the shear stress of along the boundary of each of the bodies.
-%\item Given the shear stress, update the geometry according to the erosion model.
-%\end{enumerate}
-
 To handle boundary evolution, we use the {\thL} framework, which offers
-certain advantages in the ability to stabilize fluid-structure interaction problems \cite{hou-low-she1994}.
-Throughout this section, we use the following conventions: the bodies are parametrized in the CCW
-direction and the normal vector points into the bodies (our out of the
+certain advantages in the ability to stabilize fluid-structure
+interaction problems \cite{hou-low-she1994}. Throughout this section, we
+use the following conventions: the bodies are parametrized in the CCW
+direction and the normal vector points into the bodies (or out of the
 fluid).
 
-For the sake of numerical stability, we will modify the erosion law \eqref{eqn:bodyEvolution} to include a term that depends on the local curvature $\kappa$.
-The idea is to prevent regions of very high curvature.
-The modified normal velocity is
-in \eqref{eqn:bodyEvolution} as follows
-\begin{equation}
+For the sake of numerical stability, we modify the erosion law in
+equation~\eqref{eqn:bodyEvolution} to include a term that depends on the
+local curvature $\kappa$. The idea is to prevent regions of very high
+curvature. The modified normal velocity is 
+\begin{align}
   \label{eqn:Vn}
   \Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right)
-\end{equation}
-Here, $\eps$ is a small parameter, and $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a surface mean.
-The second term on the right acts to smooth bodies with high-frequency oscillations by introducing a {\em curvature}-dependent component in the interface velocity.
-Since a closed body has a mean curvature of $\mean{\kappa} = 2\pi / L$, the term in parentheses has mean zero.
-Thus, this term is area-preserving, so that the only material loss is due to the shear stress itself.
-In addition, we have scaled this term on the $\mean{\atau}$, the average absolute stress, so that it is always proportional to the true source of erosion $\atau$, even as bodies vanish (reword).
+\end{align}
+Here, $\eps$ is a small parameter, $L$ is the total arc length of the
+body, and $\mean{\cdot}$ indicates a boundary mean. The second term on
+the right acts to smooth bodies with high-frequency oscillations by
+introducing a {\em curvature}-dependent component in the interface
+velocity. Since a closed body has a mean curvature of $\mean{\kappa} =
+2\pi / L$, the term in parentheses has mean zero. Thus, this term is
+area-preserving, so that the only material loss is due to the shear
+stress itself. In addition, we have scaled this term on the
+$\mean{\atau}$, the average absolute stress, so that it is always
+proportional to the true source of erosion $\atau$, even as bodies
+vanish \todo[inline]{reword}.
 
 We now introduce the tangent angle, $\theta$, defined through the relation
-\begin{equation}
-\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin \theta \right)
-\end{equation}
+\begin{align*}
+\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin
+\theta \right),
+\end{align*}
 where $s$ is arc length. We also introduce the normalized arc length $\alpha = 2 \pi s / L$. In terms of these new variables, the curvature can be expressed as
-\begin{equation}
-\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha}
-\end{equation}
-Substitution into \eqref{eqn:Vn} gives
-\begin{equation}
+\begin{align*}
+\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha}.
+\end{align*}
+Substitution into~\eqref{eqn:Vn} gives
+\begin{align}
 \label{eqn:Vn2}
@@
 %\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
-\end{equation}
-
-The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced.
-The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
-\begin{equation}
-\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
-\end{equation}
+\end{align}
+
+The main idea is to introduce an artificial tangential velocity that
+keeps collocation points equally spaced with respect to arc length;
+i.e.~the grid of $\alpha$ should always remain equally spaced. The
+tangential velocity that does the trick satisfies~\cite{hou-low-she1994}
+\begin{align*}
+\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}.
+\end{align*}
 The interface evolution is then given by
-\begin{equation}
+\begin{align*}
 \dot{\xx}(t) = \Vn \nn + \Vs \ss.
-\end{equation}
-This evolution equation can be recast in the variables $\theta$ and $L$ as
+\end{align*}
+This evolution equation can be recast in the variables $\theta$ and $L$
+as
+\begin{align*}
+\tderiv{L}{t} &= - 2 \pi \mean{\thalpha \Vn}, \\
+\pderiv{\theta}{t} &= \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} +
+\thalpha \Vs \right).
+\end{align*}
+Inserting~\eqref{eqn:Vn2} for the normal velocity gives
 \begin{align}
 \label{eqn:Levo1}
-& \tderiv{L}{t} = - 2 \pi \mean{\thalpha \Vn} \\
-\label{eqn:thetaevo0}
-& \pderiv{\theta}{t} = \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
-\end{align}
-Inserting \eqref{eqn:Vn2} for the normal velocity gives
-\begin{equation}
+\tderiv{L}{t} &= - 2 \pi \mean{\thalpha \Vn}, \\
 \label{eqn:thetaevo1}
-\pderiv{\theta}{t} = \frac{2\pi}{L} \left(
+\pderiv{\theta}{t} &= \frac{2\pi}{L} \left(
 \eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
-\end{equation}
-Note that the highest-order, i.e.~stiff, term in \eqref{eqn:thetaevo1}
-is {\em quasi-linear}. This is the key to the {\thL} method, and allows
-us to use very stable, implicit methods for this stiff term.
+\end{align}
+Note that stiffest term in~\eqref{eqn:thetaevo1} involving the
+second-order derivative is {\em quasi-linear}. This is the key to the
+{\thL} method, and allows us to use very stable, implicit methods for
+this stiff term that are described in Section~\ref{sec:timeStepping}.
 
@@
 \section{Numerical Methods\label{s:method}} 
-There are three main numerical methods that need to be developed:~the
-boundary integral equation solver for
-equation~\eqref{eqn:completed_BIE}, computing the layer potential for
-the shear stress~\eqref{eqn:shearStressLP}, and updating the shape of
-the eroding bodies with equation~\eqref{eqn:bodyEvolution}.  So that we
-can form stable simulations with long time horizons, we use numerical
-methods that achieve spectral accuracy in space, second-order accuracy
-in time, and maintain an equispaced discretization of the bodies.
-
-In Section~\ref{sec:spatial_discretization}, we describe how the
-geometry is represented.  Then, Section~\ref{sec:BIE}, we describe how
-the BIE~\eqref{eqn:completed_BIE} is solved.
-Once the density function is found, Section~\ref{sec:shearStress}
-describes how the shear stress is computed.  Then, in
-Section~\ref{timeStepping}, numerical methods for evolving the interface
-are described.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Spatial Discretization}
-\label{sec:spatial_discretization}
-Each body is represented with $N_\iin$ points as the Fourier series
-\begin{align*}
-  \xx^\ell(\alpha) = \FourierSum \hat{x}_k^\ell e^{ik\alpha}, \quad \ell=1,\ldots,M.
-\end{align*}
-The exterior geometry is represented with a Fourier series using
-$N_\out$ points.  Derivatives of the shape are computed in Fourier space
-\begin{align*}
-  \frac{d\xx(\alpha)}{d\alpha} = \FourierSum ik\hat{x}_k e^{ik\alpha}.
-\end{align*}
+There are three main numerical methods that need to be developed.  In
+Section~\ref{sec:BIE}, we describe how the BIE~\eqref{eqn:completed_BIE}
+is solved.  Once the density function is found,
+Section~\ref{sec:shearStress} describes how the shear
+stress~\eqref{eqn:shearStressLP} is computed.  Then, in
+Section~\ref{sec:timeStepping}, a time stepping method for evolving the
+interface according to equations~\eqref{eqn:Levo1}
+and~\eqref{eqn:thetaevo1} are described.
+
+So that we can form stable simulations with long time horizons, we use
+numerical methods that achieve spectral accuracy in space, second-order
+accuracy in time, and maintain an equispaced discretization of the
+bodies.  The boundaries are represented in Fourier space, and all
+derivatives are computed with spectral accuracy using Fourier
+differentiation.
 
@@
 \label{sec:BIE}
+
 To numerically evaluate the completed double-layer
-potential~\eqref{eqn:completed_BIE}, we le $N = MN_\iin + N_\out$ be the
-total number of discretization points of $\bd\Omega$.  The double-layer
-potential in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
+potential~\eqref{eqn:completed_BIE}, we let $N_\iin$ be the number of
+points on each of the $M$ bodies, and $N_\out$ be the number of points
+on the outer boundary.  Then, $N = MN_\iin + N_\out$ is the total number
+of discretization points of $\bd\Omega$.  The double-layer potential
+in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
 \begin{align}
@@
 where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
-vector at $\xx \in \bd\Omega$.  The strengths of the
+vector at $\xx \in \bd\Omega$.  The equations for the
 Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are
@@
 iteratively with the generalized minimal residual method
-(GMRES)~\cite{saa-sch1986}.  Since the BIE is second-kind, this
-guarantees that a mesh-independent number of GMRES iterations are
+(GMRES)~\cite{saa-sch1986}.  Since the BIE is second-kind, only a
+mesh-independent number of GMRES iterations are
 required~\cite{cam-ips-kel-mey-xue1996}.  Therefore, the asymptotic cost
 is determined by the cost of performing a matrix-vector multiplication,
-and the bulk of the most expensive part is evaluating the $N$-term sum
+and the bulk of the cost is evaluating the $N$-term sum
 in~\eqref{eqn:completed_BIE_discretized}.  Naively, evaluating this sum
-at all points $\xx_i$, $i=1,N$ requires $\bigO(N^2)$ operations.  To
-reduce the computational cost of this calculation, we use the Fast
-Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} to reduce the
-complexity from $\bigO(N^2)$ to $\bigO(N)$.  Since the number of
-required GMRES iterations is mesh-independent, the overall complexity
-for solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
+at all points $\xx_i$, $i=1,\ldots,N$ requires $\bigO(N^2)$ operations.
+To reduce the computational cost, we use the Fast Multipole Method
+(FMM)~\cite{gre-rok1987, gre-gre-may1992} to reduce the complexity from
+$\bigO(N^2)$ to $\bigO(N)$.  Since the number of required GMRES
+iterations is mesh-independent, the overall complexity for
+solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
 
@@
 to achieve spectral accuracy, we apply odd-even
-integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
+integration~\cite{sid-isr1988}.  Therefore, the deformation tensor of
 the double-layer potential at a discretization point $\xx_i$ on body
@@
 equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
-deformation tensor~\eqref{eqn:shearStressJump} is added, and the
-required arclength derivative is computed in Fourier space.  Then, the
-shear stress can be computed by computing the deformation tensor in the
-normal vector, and taking the inner product with the tangent vector.
-
-We do not employ an FMM to evaluate the shear stress, so the cost of
-evaluating the shear stress is $\bigO(N^2)$.  However, this calculation
-is only performed once per time step as opposed to the velocity
-double-layer potential that must be evaluated at each GMRES iteration.
-In future work, we plan to use a kernel-independent
-FMM~\cite{yin-bir-zor2004} to evaluate the shear stress with $\bigO(N)$
-operations.
+deformation tensor~\eqref{eqn:shearStressJump} is computed with Fourier
+differentiation.  Then, the shear stress is computed by multiplying the
+deformation tensor by the normal vector, and taking the inner product
+with the tangent vector.
+
+We do not employ an FMM to evaluate the shear stress at $\xx_i$,
+$i=1,\ldots,N$, so the cost of evaluating the shear stress is
+$\bigO(N^2)$.  However, this calculation is only performed once per time
+step as opposed to the velocity double-layer potential that must be
+evaluated at each GMRES iteration.  In future work, we plan to use a
+kernel-independent FMM~\cite{yin-bir-zor2004} to evaluate the shear
+stress with $\bigO(N)$ operations.
 
@@
 With the shear stress computed, we are now ready to evolve the interface
-of each body. As described in Section~\ref{sec:thetaL}, we use the
-{\thL} framework, with $\theta$ being the tangent angle and $L$ the
-total arc length of a given boundary, and with the boundaries
+of each body using equations~\eqref{eqn:Levo1}
+and~\eqref{eqn:thetaevo1}. As described in Section~\ref{sec:thetaL}, we
+use the {\thL} framework, with $\theta$ being the tangent angle and $L$
+the total arc length of a given boundary, and with the boundaries
 parameterized by normalized arc length $\alpha = 2 \pi s / L$.
@@
 absolute shear stress
-\begin{equation}
-\atausig = \int_{\gamma} \frac{1}{\sqrt{2\pi} \sigma} \exp \left(- \frac{\alpha'^2}{2 \sigma^2}\right) \abs{ \tau(\alpha - \alpha') } \, d\alpha'
-\end{equation}
-Here $\sigma$ is the small parameter that determines the width of the
+\begin{align*}
+\atausig = \int_{\gamma} \frac{1}{\sqrt{2\pi} \sigma} \exp \left(-
+\frac{\alpha'^2}{2 \sigma^2}\right) \abs{ \tau(\alpha - \alpha') } \,
+d\alpha'.
+\end{align*}
+Here $\sigma$ is a small parameter that determines the width of the
 filter. The corresponding normal and tangential interface velocities are
 the given by
-\begin{align}
-& \Vnsig = \atausig +  \eps \mean{\atausig}   \left(\pderiv{\theta}{\alpha} - 1 \right) \\
-& \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig}
-\end{align}
+\begin{align*}
+& \Vnsig = \atausig +  \eps \mean{\atausig}
+\left(\pderiv{\theta}{\alpha} - 1 \right), \\
+& \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig}.
+\end{align*}
 
 For simplicity, we introduce the variables
-\begin{align}
-\label{eq:M}
-& \Mterm = - 2 \pi \mean{\thalpha \Vnsig} \\
-\label{eq:N}
-& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha \Vssig \right) \\
-\label{eq:elfun}
-& \elfun = \frac{2 \pi  \mean{\atausig}}{L}
-\end{align}
-So that evolution equations`\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1}
-can be compactly expressed as
+\begin{align*}
+%\label{eq:M}
+& \Mterm = - 2 \pi \mean{\thalpha \Vnsig}, \\
+%\label{eq:N}
+& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha
+\Vssig \right), \\
+%\label{eq:elfun}
+& \elfun = \frac{2 \pi  \mean{\atausig}}{L}.
+\end{align*}
+Then, the evolution equations~\eqref{eqn:Levo1}
+and~\eqref{eqn:thetaevo1} can be compactly expressed as
 \begin{align}
 \label{eqn:Levo2}
-& \tderiv{L}{t} = \Mterm \\
+& \tderiv{L}{t} = \Mterm, \\
 \label{eqn:thetaevo2}
-& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
-\end{align}
-
-Here $\NLterm$ represents the nonlinear terms (and nonlocal etc) in the
-PDE for $\theta$.  We will evolve $\theta$ in spectral space, and so
-introduce the Fourier series
-\begin{align}
-& \theta(\alpha,t) = \alpha + \FourierSum \thhat_k e^{ i k \alpha} \\
-& \NLterm(\alpha,t)  = \FourierSum \hat{\NLterm}_k e^{ i k \alpha}
+& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm.
+\end{align}
+Here $\NLterm$ represents the nonlinear terms (and nonlocal terms) in
+the PDE for $\theta$.
+
+We can evolve $\theta$ in spectral space since $\theta(\alpha)$ is
+periodic up to a jump of $2\pi$ for $\alpha \in [0,2\pi]$.  Therefore,
+we introduce the Fourier series
+\begin{align}
+ \theta(\alpha,t) &= \alpha + \FourierSum \thhat_k e^{ i k \alpha}, \\
+ \NLterm(\alpha,t)  &= \FourierSum \widehat{\NLterm}_k e^{ i k \alpha}.
 \end{align}
@@
 space,~\eqref{eqn:thetaevo2} produces the system of ODEs
-\begin{equation}
-\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{\NLterm}_k
-\end{equation}
+\begin{align*}
+\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \widehat{\NLterm}_k.
+\end{align*}
 Each ODE is first-order and linear (though variable-coefficient due to
 $\elfun$) and thus can be solved by using the integrating factor
-\begin{equation}
+\begin{align}
   \label{eq:mu}
-\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right)
-\end{equation}
+  \mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right).
+\end{align}
 We are therefore led to the coupled system of ODEs
@@
 \label{eqn:Levo2}
-& \tderiv{L}{t} = \Mterm \\
+& \tderiv{L}{t} = \Mterm, \\
 \label{eqn:thetaevo2}
-& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{\NLterm}_k
-\end{align}
+& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \widehat{\NLterm}_k.
+\end{align}
+\todo[inline]{multiply defined references here}
 We solve system~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an
@@
 At the first stage of RK2 (the half step), we discretize
-Eqs.~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} as
+equations~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} as
 \begin{align}
@@
 where the superscript indicates the time step. For simplicity, we have
-chosen the constant of integration in the exponent of Eq.~\eqref{eq:mu}
-so that $\mu_k^{(n)} = 1$. At the next stage of RK2, we must compute
-$\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$, which requires a
-call to the Stokes solver. Hence, we must compute $\mu_k^{(n+1/2})$, so
-that $\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the
-mid-step can be computed. To compute $\mu_k^{(n+1/2)}$, we use the
-left-end-point rule (first order, consistent with first forward Euler
-step of RK2)
-\begin{equation}
-\mu_k^{(n+1/2)} = \exp \left( \epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
-\end{equation}
+chosen the constant of integration in the exponent of
+equation~\eqref{eq:mu} so that $\mu_k^{(n)} = 1$. At the next stage of
+RK2, we must compute $\Mterm^{(n+1/2)}$ and
+$\widehat{\NLterm}_k^{(n+1/2)}$, which requires a call to the Stokes
+solver. Hence, we must compute $\mu_k^{(n+1/2)}$, so that
+$\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the mid-step
+can be computed. To compute $\mu_k^{(n+1/2)}$, we use the left-end-point
+rule (first order, consistent with first forward Euler step of RK2)
+\begin{align*}
+\mu_k^{(n+1/2)} = \exp \left( \epsilon k^2 \frac{\Dt}{2}
+\elfun^{(n)}\right).
+\end{align*}
 It is instructive to recast as
-\begin{equation}
+\begin{align*}
 \thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{\NLterm}_k^{(n)} \right)
 \exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
-\end{equation}
+\end{align*}
 so that the smoothing effect of the exponential is obvious. With
 $\thhat_k^{(n+1/2)}$ computed, it is now possible to compute
-$\Mterm^{(n+1/2)}$ and $\hat{\NLterm}_k^{(n+1/2)}$.
+$\Mterm^{(n+1/2)}$ and $\widehat{\NLterm}_k^{(n+1/2)}$.
 
 Next, at the second stage of RK2, we discretize as
-\begin{align}
-& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)} \\
-& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} = \mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}
-\end{align}
-We again compute the integrating factor, $\mu_k^{(n+1)}$ via the (
-insert integration rule), giving
-\begin{align}
+\begin{align*}
+\frac{L^{(n+1)} - L^{(n)}}{\Dt} &= \Mterm^{(n+1/2)}, \\
+\frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} &=
+\mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}.
+\end{align*}
+We again compute the integrating factor, $\mu_k^{(n+1)}$ via the
+\todo[inline]{insert integration rule}, giving
+\begin{align*}
 \thhat_k^{(n+1)} = 
@@
 & \Dt \, \hat{\NLterm}_k^{(n+1/2)}
-\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right)
-\end{align}
+\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} -
+\elfun^{(n)} \right) \right).
+\end{align*}
 
@@
 equation~\eqref{eqn:completed_DLP} is solved for the density function,
-Stokeslets, and rotlets, all of these quantities can be computed by
-evaluating layer potentials that we now derive.  All layer potentials
+Stokeslets, and rotlets, all of these quantities can be computed.  For
+target points in the fluid domain, the resulting layer potentials
 involve integrands that are periodic, so the trapezoid rule guarantees
-spectral accuracy if the integrand is smooth~\cite{tre-wei2014}.
-However, some of the integrands contain a singularity whose strength
-will be reduced with singularity subtraction, and then spectral accuracy
-is achieved with odd-even integration~\cite{sid-isr1988} must be used.
+spectral accuracy since the integrand is smooth~\cite{tre-wei2014}.
+However, if the target point is close to a boundary, a nearly-singular
+integrand must be integrated, and this requires upsampling that is
+described in Section~\ref{sec:NSI}.  When the target points is on the
+boundary, the integrands involve singularities that are evaluated by
+combining singularity subtraction and odd-even
+integration~\cite{sid-isr1988}.
 
@@
 \label{sec:vorticity}
-For the Stokes equations, on boundaries that have a no-slip boundary
-condition, the shear stress is equivalent to the vorticity $w = v_x -
-u_y$.  Therefore, to compute $w(\xx)$ for $\xx \in \overline{\Omega}$,
-we only need to compute $w(\xx)$ for $\xx \in \Omega$.  As we did for
-the shear stress, we compute the vorticity due to the double-layer
-potential, Stokeslets, and rotlets individually.  The vorticity of the
-double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
+We start by computing the vorticity $w(\xx) = v_x - u_y$ for $\xx \in
+\Omega$.  As we did for the shear stress, we compute the vorticity due
+to the double-layer potential, Stokeslets, and rotlets individually.
+The vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at
+$\xx \in \Omega$ is
 \begin{align}
@@
 \end{align*}
+To compute~\eqref{eqn:vorticityDLP} numerically, we apply the trapezoid
+rule with an upsampling scheme described in Section~\ref{sec:NSI}.
+
+For the Stokes equations, on boundaries that have a no-slip boundary
+condition, the shear stress is equivalent to the vorticity $w = v_x -
+u_y$.  Therefore, we do not need to compute the vorticity for $\xx \in
+\bd\Omega$.
 
@@
 \label{sec:pressure}
-To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
+To compute the pressure at $\xx \in \Omega$, we follow the
 same procedure used for the shear stress.  We start by computing the
@@
 \end{align}
+The pressure due to the Stokeslets is
+\begin{align}
+  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
+  \label{eqn:shearPressureSR}
+\end{align}
+and the pressure due to the rotlets is zero.  Therefore, the pressure is
+\begin{align*}
+  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
+  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
+              p^{S}(\xx), && \xx \in \bd\Omega.
+\end{align*}
+To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid
+rule with an upsampling scheme described in Section~\ref{sec:NSI}.
+
 To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
@@
 \end{align}
-The pressure due to the Stokeslets is
-\begin{align}
-  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
-  \label{eqn:shearPressureSR}
-\end{align}
-and the pressure due to the rotlets is zero.  Therefore, the pressure is
-\begin{align*}
-  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
-  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
-              p^{S}(\xx), && \xx \in \bd\Omega.
-\end{align*}
-
 Similar to the shear stress, the singularity of the pressure
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quadrature: Off Boundary Calculations} 
-\label{sec:off_boundary}
-To analyze the flow, we compute quantities at target points that are in
-the interior of the domain.  In particular, we develop numerical methods
-to compute the velocity~\eqref{eqn:velocityDLP},
-pressure~\eqref{eqn:pressureDLP}, vorticity~\eqref{eqn:vorticityDLP} and
-resistivity~\eqref{eqn:resistivity}.  Since the target points are not on
-the boundary of the domain, all the integrals, except for the
-resistivity, involve integrands that are both periodic and smooth.
-However, when the target points are close to the boundary of the domain,
-the integrand becomes nearly-singular, and these large derivatives
-result in a loss of accuracy that needs to be rectified.  We will be
-adopting a near-singular integration scheme that allows us to compute
-all quantities of interest sufficiently close to $\bd\Omega$ for the
-quantities of interest.
-
-\todo[inline]{DUMP OF OLD TEXT}
-discretizations of
-layer potentials~\eqref{eqn:layerPotential} at a large number of points.
-If a direct summation method is used to evaluate these sums at $N_\tar$
-points, this requires $\bigO(NN_\tar)$ operations.  The layer potential
-that is evaluated most frequently is in the GMRES iteration where the
-layer potential $\DD$ is evaluated to compute the velocity at all points
-on the boundary must be evaluated~\eqref{eqn:DLP}.
-
-In our implementation, the deformation tensor and vorticity are computed
-with a direct summation, and this requires $\bigO(N^2)$ and $\bigO(N
-N_\tar)$ operations, respectively.  Since this calculation is only
-computed once per time step, while the velocity is calculated at each
-GMRES iteration, the computational cost is manageable.  However, in
-future work, to simulate erosion in a dense packing of grains, a fast
-summation method, such as the kernel-independent
-FMM~\cite{yin-bir-zor2004}, will be incorporated.
-
-\todo[inline]{DUMP OF OLD TEXT}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Near-singular integration}
-To accurately compute quantities such as the velocity at points $\xx \in
-\Omega$, we adopt a near-singular integration scheme entirely based on
-upsampling.  Since we are only interested in computing the velocity and
-vorticity for visualizing the flow, and the pressure is only required
-far away from any boundary, only a finite amount of upsampling is
-required to achieve an acceptable error.
+\label{sec:NSI}
+To accurately compute the velocity~\eqref{eqn:velocityDLP},
+vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP}
+at points $\xx \in \Omega$, we adopt a near-singular integration scheme
+based entirely on upsampling.  We are only interested in computing the
+velocity and vorticity for visualizing the flow, and it is not necessary
+that we resolve the integrands for arbitrarily close target points
 
@@
 where $\phi$ is either the velocity, pressure, or vorticity, and the
-kernel $K$ is in
+kernel $K$ are defined in
 equations~\eqref{eqn:velocityDLP},~\eqref{eqn:vorticityDLP},
@@
 to $\phi$.
+\newcolumntype{V}{>{\centering\arraybackslash}m{4em}}
+\newcolumntype{N}{@{}m{0pt}@{}}
 \begin{table}[htpb]
 \centering
-\begin{tabular}{|c|ccccc|}
+%\begin{tabular}{|c|ccccc|}
+\begin{tabular}{|V|V|V|V|V|V|N}
   \hline
@@
   $[\frac{5}{8}h,\frac{5}{4}h]$ &
-  $[\frac{5}{16}h,\frac{5}{8}h]$ \\ [2ex]
+  $[\frac{5}{16}h,\frac{5}{8}h]$ & \\ [2ex] 
   \hline
-  Upsample Rate & 1 & 2 & 4 & 8 & 16 \\
+  Upsample Rate & 1 & 2 & 4 & 8 & 16 & \\
   \hline
@@
 
-In future work, such as sedimenting eroding bodies, bodies will come too
-close to one another for upsampling to only used.  Therefore, we plan to
-implement a near-singular integration scheme that uses either
-near-singular interpolation~\cite{qua-bir2014a}, quadrature by
+In future work, upsampling will not be adequate.  For example, if
+eroding bodies are also sedimenting, bodies will come too close to one
+another for upsampling to only used.  Therefore, we plan to implement a
+near-singular integration scheme that uses either near-singular
+interpolation~\cite{qua-bir2014a}, quadrature by
 expansion~\cite{klo-bar-gre-one2013}, Barycentric
 interpolation~\cite{bar-wu-vee2015}, or panel-based
-quadrature~\cite{hel-oja2008a}.  In addition, even with accurate
-quadrature, bodies can overlap because of discretization errors, and
-this can be avoided with contact algorithms such as, for example, recent
-work of Lu et al.~\cite{lu-rah-zor2017}.
+quadrature~\cite{hel-oja2008a}.
 
@@
 
-With the description of the numerical methods complete, we now present
-results on bodies eroding in Stokes flow. We first discuss simulations
-of a single eroding body, which can be compared with analytical results
-for validation, before discussing the erosion of many bodies.
-
-\subsection{The erosion of a single body}
-
-In the case of a single eroding body, certain analytical results can be
-derived regarding the limiting shape and vanishing rate. These results
-allow validation of our simulation.
-
-\subsubsection{Shape evolution}
-
-We first show a single body eroding, with the surrounding vorticity
-field visualized in Fig.~4. The body develops a corner at its front and
-rear stagnation points. It maintains for-aft symmetry due to the
-time-reversibility of Stokes flow.
+With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow.
+We first discuss the case of a single eroding body, as certain features can be predicted analytically and thus used for validation.
+We then discuss the erosion of multiple bodies and, in particular, important differences that arise as compared to the single-body case.
+
+\subsection{Shape evolution of a single eroding body}
 
@@
 \begin{center}
-\includegraphics[width = 0.9 \textwidth]{./figs/01bodseq.pdf}
-\caption{One body}
-\label{}
+\includegraphics[width = 0.85 \textwidth]{./figs/01bodseq.pdf}
+\caption{A single body eroding in Stokes flow.
+As the body erodes, it develops a corner at its front and rear stagnation points, while remaining for-aft symmetric due to time-reversibility.
+Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress.
+In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.
+FYI, the body vanishes at time $t_{f} = 1.79E-2$.}
+\label{01bodseq}
 \end{center}
@@
 % Figure from datafile 01circ1024aa;
-% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixpdrop = 0
+% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
+
+Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points.
+The figure shows the body at three evenly spaced times during the erosion process, with the color map to indicate the vorticity of the surrounding flow.
+When evaluated on the boundary, the vorticity indicates the shear stress and thus the local erosion rate.
+As seen in the figure, the body is initially circular, with strongest vorticity above and below it.
+The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, and vorticity vanishes at the body's front and rear stagnation points.
+At the next time step, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
+The greatest material loss has occurred at the body's top and bottom, where shear is strongest.
+Interestingly, the body has developed well-defined corners at its front and rear stagnation points.
+This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry.
+As shown in the third snapshot, this corner persists as the bodies becomes even more slender while vanishing.
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.80 \textwidth]{./figs/shrink_intface.pdf}
+\caption{One body}
+\label{shrink_intface}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure from datafile 01circ1024aa;
+% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
+
+To better understand the shape change, we show in Fig.~\ref{shrink_intface}(a) the interfaces of the body at several evenly spaced times.
+Here, color indicates time in relation to the time at which the body completely vanishes $t_{f} = 1.79E-2$.
+
+\vsp{5}
+Later, as a segue to discuss the vanishing of area, I can point out that the interface spacing becomes greater at later times in Fig. 5a.
+
+\subsubsection{Shape evolution}
 
@@
 exception of the front/rear corner where the curvature is high.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.8 \textwidth]{./figs/shrink_intface.pdf}
-\caption{One body}
-\label{}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024aa;
-% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
 
@@
 \begin{center}
+\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is 56\% of the vanishing time.
+GOOD TERM: Cauchy-convergence.} 
 \caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is

### 2018-01-14 julia/zconv_test.jl
Slight changes to convergence test

@@ -19,7 +19,7 @@ function shape_error(thld1::ThLenDenType, thld0::ThLenDenType)
 end
 
 # Test the convergence wrt dt.
-function convtest(tfin::Float64, dt0::Float64, nits::Int)
+function convtest(nits::Int=3, dt0::Float64=1e-4, tfin::Float64=1e-2)
 	# Initialize simulation variables.
 	paramsfile = "params.in"
 	thld1,params = startup(paramsfile)

### 2018-01-14 docs/methods/erosion_methods.tex
NM
small changes to near singular section

@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure generated using 50circ128.in with epsfac = 10, sigfac = 10, dt = 2e-4, fixpdrop = 1.
+% Figure generated from data file 50circ512p5, 
+%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
 
@@
 \label{sec:NSI}
-To accurately compute the velocity~\eqref{eqn:velocityDLP},
+The layer potentials for the~\eqref{eqn:velocityDLP},
 vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP}
-at points $\xx \in \Omega$, we adopt a near-singular integration scheme
-based entirely on upsampling.  We are only interested in computing the
-velocity and vorticity for visualizing the flow, and it is not necessary
-that we resolve the integrands for arbitrarily close target points
-
-Computing the velocity, pressure, and vorticity at a point $\xx \in
-\Omega$ requires evaluating the layer potential
-\begin{align*}
-  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy,
-\end{align*}
-where $\phi$ is either the velocity, pressure, or vorticity, and the
-kernel $K$ are defined in
-equations~\eqref{eqn:velocityDLP},~\eqref{eqn:vorticityDLP},
-or~\eqref{eqn:pressureDLP}.  This integral is approximated with a
-trapezoid rule,
+need to be evaluated at points $\xx \in \Omega$. We write the general
+layer potential as
+\begin{align}
+  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy.
+  \label{eqn:genericLP}
+\end{align}
+Since the integrand is periodic and smooth, the trapezoid rule
+guarantees spectral accuracy.  However, when the target point $\xx$ is
+close to $\bd\Omega$, the integrand is nearly-singular, and the accuracy
+of the trapezoid rule deteriorates unless a large number of
+discretization points are used.  We are only interested in computing the
+velocity, vorticity, and pressure to visualize the flow, so it is not
+necessary that we resolve the integrands for arbitrarily close target
+points
+
+The layer potential~\eqn{eqn:genericLP} is approximated with the
+trapezoid rule 
 \begin{align}
@@
 where $q$ contains the quadrature weights, Jacobian, and density
-function.  Note that this sum can only be computed once
-equation~\eqref{eqn:completed_BIE} has been solved for the density
-function $\eeta$.  Based on numerical experiments, the error of the
-$N$-point trapezoid rule is acceptable for points $\xx$ that are more
-than 5 arclength spacings from $\bd\Omega$.
+function.  Based on numerical experiments, the error of the $N$-point
+trapezoid rule is acceptable for points $\xx$ that are more than 5
+arclength spacings from $\bd\Omega$.
 

### 2018-01-14 julia/zconv_test.jl
NM

@@ -1,7 +1,8 @@
 # Test the 2nd order convergence in dt.
-# I typically use 01circ256, with tfin = 1e-2, dt0 = 1e-4, nits = 3 or higher.
+# I typically use 01circ256, with nits = 3 or higher, dt0 = 1e-4, tfin = 1e-2.
 # Vanishing time for 01circ1024aa is 0.017938. So 1e-2 is 56% of vanishing time.
 # The runtime for nits = 3 is about 16 minutes.
+# For the test in the paper, I used nits = 7.
 
 include("main.jl")
 

### 2018-01-15 docs/methods/erosion_methods.tex
NM

@@
 proportional to the true source of erosion $\atau$, even as bodies
-vanish \todo[inline]{reword}.
+vanish. \todo[inline]{reword}
 
@@
 
-For simplicity, we introduce the variables
+For convenience, we introduce the variables
 \begin{align*}
@@
 \begin{align}
-\label{eqn:Levo2}
+\label{eqn:Levo3}
 & \tderiv{L}{t} = \Mterm, \\
-\label{eqn:thetaevo2}
+\label{eqn:thetaevo3}
 & \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \widehat{\NLterm}_k.
 \end{align}
-\todo[inline]{multiply defined references here}
-We solve system~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an
+We solve system~\eqref{eqn:Levo3}--\eqref{eqn:thetaevo3} with an
 explicit, second-order Runge-Kutta method (RK2). In particular, we
@@
 At the first stage of RK2 (the half step), we discretize
-equations~\eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} as
+equations~\eqref{eqn:Levo3}--\eqref{eqn:thetaevo3} as
 \begin{align}
@@
 
-The layer potential~\eqn{eqn:genericLP} is approximated with the
+The layer potential~\eqref{eqn:genericLP} is approximated with the
 trapezoid rule 
@@
 We first discuss the case of a single eroding body, as certain features can be predicted analytically and thus used for validation.
-We then discuss the erosion of multiple bodies and, in particular, important differences that arise as compared to the single-body case.
+We then discuss the erosion of multiple bodies and highlight important differences that arise as compared to the single-body case.
 
@@
 The figure shows the body at three evenly spaced times during the erosion process, with the color map to indicate the vorticity of the surrounding flow.
-When evaluated on the boundary, the vorticity indicates the shear stress and thus the local erosion rate.
+When evaluated on the boundary, the vorticity is equivalent to shear stress and thus indicates the local erosion rate.
 As seen in the figure, the body is initially circular, with strongest vorticity above and below it.
@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Parameters in this test are: 01circ256, nits = 7, dt0 = 1e-4, tfin = 1e-2
+% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0
 

### 2018-01-16 docs/methods/erosion_methods.tex
small changes to intro

@@
 that is proportional to the magnitude of the shear
-stress~\cite{ris-moo-chi-she-zha2012}.  To further visualize the effect
-of erosion, we compute the vorticity of the flow
-(Figure~\ref{fig:50bodies}) which is equal to the shear stress in the
-Stokesian limit.  Finally, to evolve the geometry, a second-order time
-stepping method that guarantees that the mesh does not become distorted
-will be employed.
-
+stress~\cite{ris-moo-chi-she-zha2012}. Other models for erosion include
+ones that use an erosion rate that is proportional to a power of the
+magnitude of the shear stress~\cite{par-izu2000}, or ones that use a
+critical shear stress below which erosion does not occur~\cite{lag2000}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Contributions} The present study will develop numerical
@@
 fixing the area of the body as a function of time, we are able to
-characterize the long-time behavior of the shape and the resulting flow.
-Then, we compute the vorticity of erosion in multiply-connected
-geometries to better characterize erosion in porous media.
+characterize the long-time behavior of the shape and the resulting flow
+and compare these results with analytical results.  Then, we compute the
+vorticity of erosion in multiply-connected geometries to better
+characterize erosion in porous media.
 
@@
 
-\todo[inline]{DUMP OF TEXT}
-This choice is based on experimental work of Ristroph et
-al.~\cite{ris-moo-chi-she-zha2012}, but other models for erosion are
-possible.  For example, some models use an erosion rate that is
-proportional to a power of the magnitude of the shear
-stress~\cite{par-izu2000}, while others introduced a shear stress below
-which erosion does not occur~\cite{lag2000}.
-\todo[inline]{DUMP OF TEXT}
-
+To further visualize the effect of erosion, we compute the vorticity of
+the flow (Figure~\ref{fig:50bodies}) which is equal to the shear stress
+in the Stokesian limit.  Finally, to evolve the geometry, a second-order
+time stepping method that guarantees that the mesh does not become
+distorted will be employed.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Limitations} There are two main limitations of the current
@@
 
-\paragraph{Related work}
-Simulating eroding bodies has been studied analytically, experimentally,
-and numerically.  Because of the scales involves with geophysical flows,
-most of these works consider high Reynolds number flows.  For instance,
-the experimental work of Moore et al.~\cite{moo-ris-chi-zha-she2013}
-considers on the order of $10^4$.  For low Reynolds number flows,
-Mitchell and Spagnolie~\cite{mit-spa2016} simulate the erosion of a
-mobile body in three dimensions, but they only consider single body.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Related work} Simulating eroding bodies has been studied
+analytically, experimentally, and numerically.  Because of the scales
+involves with geophysical flows, most of these works consider high
+Reynolds number flows.  For instance, the experimental work of Moore et
+al.~\cite{moo-ris-chi-zha-she2013} considers on the order of $10^4$.
+For low Reynolds number flows, Mitchell and Spagnolie~\cite{mit-spa2016}
+simulate the erosion of a mobile body in three dimensions, but they only
+consider single body.
 
@@
 
-\paragraph{Outline of the paper}
-In Section~\ref{s:formulation}, we describe the governing equations for
-both the fluid and describe the erosion model using a \thL~framework.
-In Section~\ref{s:method}, the numerical methods in both space and time
-are described.  Section~\ref{s:results} gives several numerical
-examples.  Finally, concluding remarks are made in
-Section~\ref{s:conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Outline of the paper} In Section~\ref{s:formulation}, we
+describe the governing equations for both the fluid and describe the
+erosion model using a \thL~framework.  In Section~\ref{s:method}, the
+numerical methods in both space and time are described.
+Section~\ref{s:results} gives several numerical examples.  Finally,
+concluding remarks are made in Section~\ref{s:conclusions}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Formulation\label{s:formulation}} 
+\section{Formulation}
+\label{s:formulation}
 We start by defining the main variables used to model erosion.  We only
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Methods\label{s:method}} 
+\section{Numerical Methods}
+\label{s:method}
 There are three main numerical methods that need to be developed.  In
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Post Processing Quantities of Interest\label{s:qoi}}
-
+\section{Post Processing Quantities of Interest}
+\label{s:qoi}
 To study characteristics of the flow, the vorticity
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results\label{s:results}}
-
+\section{Results}
+\label{s:results}
 With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{\bf Acknowledgments} The authors would like to thank Manas Rachh
-for supplying the FMM for the Stokes double-layer potential.
+\paragraph{\bf Acknowledgments} The authors would like to thank Manas
+Rachh for supplying the FMM for the Stokes double-layer potential.
 

### 2018-01-18 docs/methods/erosion_methods.tex
Working on methods paper text.

@@
 We first discuss the case of a single eroding body, as certain features can be predicted analytically and thus used for validation.
-We then discuss the erosion of multiple bodies and highlight important differences that arise as compared to the single-body case.
+We then discuss the erosion of multiple bodies and highlight important differences compared to the single-body case.
 
@@
 Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress.
-In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.
-FYI, the body vanishes at time $t_{f} = 1.79E-2$.}
+In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
 \label{01bodseq}
@@
 
-Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points.
-The figure shows the body at three evenly spaced times during the erosion process, with the color map to indicate the vorticity of the surrounding flow.
-When evaluated on the boundary, the vorticity is equivalent to shear stress and thus indicates the local erosion rate.
-As seen in the figure, the body is initially circular, with strongest vorticity above and below it.
-The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, and vorticity vanishes at the body's front and rear stagnation points.
-At the next time step, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
+Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points, and shown at three evenly spaced times.
+Here, color represents the vorticity of the surrounding flow, which, when evaluated on the boundary, indicates the shear stress and thus the local erosion rate.
+As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it.
+The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations and vorticity vanishes at the body's front and rear stagnation points.
+At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
 The greatest material loss has occurred at the body's top and bottom, where shear is strongest.
@@
 This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry.
-As shown in the third snapshot, this corner persists as the bodies becomes even more slender while vanishing.
+As shown in the third snapshot, this corner persists as the bodies becomes even more slender while wasting away.
+In this simulation, the body completely vanishes at a final time of $t_f = 1.79E-2$.
 
@@
 \includegraphics[width = 0.80 \textwidth]{./figs/shrink_intface.pdf}
-\caption{One body}
+\caption{Shape and stress evolution.
+(a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
+Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes.
+(b) The distribution of absolute shear stress, $\atau$, along each of the interfaces.
+Initially the stress is distributed non-uniformly, but becomes more uniform
+}
 \label{shrink_intface}
@@
 
-To better understand the shape change, we show in Fig.~\ref{shrink_intface}(a) the interfaces of the body at several evenly spaced times.
-Here, color indicates time in relation to the time at which the body completely vanishes $t_{f} = 1.79E-2$.
+To better understand the body's shape evolution in this simulation, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
+The interfaces are color-coded by normalized time $t/t_f$.
+The body seems to converge to a shape that resembles an American football -- a fairly slender, for-aft symmetric shape with corners at the front and back.
+Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
+The normalized arc length $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point.
+At early times (yellow to orange), the stress is distributed non-uniformly, with highest values at the top and bottom of the body.
+As time proceeds, though, the stress becomes more evenly distributed along the body's surface (red).
+As the body nears the final stages of erosion (dark red), the stress actually becomes slightly higher near the stagnation points.
+A close look reveals that {\em at} the stagnation points, the stress always vanishes, though in a region that becomes increasingly narrow.
 

### 2018-01-18 docs/methods/erosion_methods.tex
Working on paper.

@@
 \begin{center}
-\includegraphics[width = 0.85 \textwidth]{./figs/01bodseq.pdf}
+\includegraphics[width = 0.80 \textwidth]{./figs/01bodseq.pdf}
 \caption{A single body eroding in Stokes flow.
@@
 
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.80 \textwidth]{./figs/shrink_intface.pdf}
-\caption{Shape and stress evolution.
-(a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
-Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes.
-(b) The distribution of absolute shear stress, $\atau$, along each of the interfaces.
-Initially the stress is distributed non-uniformly, but becomes more uniform
-}
-\label{shrink_intface}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024aa;
-% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
-
 To better understand the body's shape evolution in this simulation, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
@@
 
-\vsp{5}
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.75 \textwidth]{./figs/shrink_intface.pdf}
+\caption{Shape and stress evolution.
+(a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
+Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes.
+(b) The distribution of absolute shear stress, $\atau$, along each of these interfaces.
+Normalized arc length, $s/L$, runs counterclockwise from the rear stagnation point.
+The stress initially varies over the body's surface, but becomes more uniform over time.
+}
+\label{shrink_intface}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure from datafile 01circ1024aa;
+% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
+
+\subsection{Scaling law for the vanishing rate}
+
+Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing.
+Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu V / L$, since stress is inversely proportional to body size.
+In two dimensions, though, this law is modified.
+The correct modification can be inferred
+
+Interestingly, the spacing between successive interfaces in Fig.~\ref{shrink_intface}(a) becomes larger as time progresses
+
+\subsection{The limiting shape}
+
+\vsp{30}
 Later, as a segue to discuss the vanishing of area, I can point out that the interface spacing becomes greater at later times in Fig. 5a.
-
-\subsubsection{Shape evolution}
-
-In Fig.~5a, we visualize the interfaces color coded in time. In Fig.~5b,
-we show the absolute shear stress, $\atau$, as it varies over the
-surface of the body. Initially, the shear stress is a hump shape. As
-time progresses, the stress becomes more evenly distributed, with the
-exception of the front/rear corner where the curvature is high.
 
@@
 
+In the table, we measure the error in the shape by computing the L2-difference of the interfaces.
+
 \subsubsection{The uniform stress geometry}

### 2018-01-18 docs/methods/erosion_methods.tex
Working on paper

@@
 
+\todo[inline]{I am not sure if $V$ has been defined previously. If not, need to define it.}
+
 Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing.
-Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu V / L$, since stress is inversely proportional to body size.
-In two dimensions, though, this law is modified.
-The correct modification can be inferred
-
-Interestingly, the spacing between successive interfaces in Fig.~\ref{shrink_intface}(a) becomes larger as time progresses
+Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu V / L$, since stress is inversely proportional to body scale $L$.
+This law must be modified in 2D, though.
+The modification is made non-trivial by subtleties associated with the Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory.
+For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to $\mu V W/ \log(W/L)$.
+This relationship implies that, for a 2D cross-section perpendicular to the long axis, the stress can be estimated by
+\begin{equation}
+\tau \sim \frac{\mu V}{L \log(W/L)}
+\end{equation}
+In interpreting our 2D simulations, we will treat $W$ as fixed (and must remember the requirement $W \gg L$).
+
+\vsp{30}
 
@@
 
-\vsp{30}
-Later, as a segue to discuss the vanishing of area, I can point out that the interface spacing becomes greater at later times in Fig. 5a.
-
 \subsubsection{The vanishing rate of area}
-In three-dimensional Stokes flow, the shear stress vanishes as
-\begin{equation}
-\tauD{3} \sim \mu V/L
-\end{equation}
-However, this law must be modified for 2D flow, which represents 3D
-bodies of large extent. As the body vanishes, the walls have an ever
-decreasing influence. Thus, the stress must be consistent with
-free-space slender-body theory as it vanishes. The stress law consistent
-with slender body theory (a long cylinder held perpendicular to a flow)
-is
-\begin{equation}
-\tauD{2} \sim \frac{\mu V}{L \log(W/L)}
-\end{equation}
-% Could include 4 \pi factor, which is appropriate for a circular cylinder
 

### 2018-01-18 docs/methods/erosion_methods.tex
NM

@@
 velocity} \\
-V_\nn = \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
+\Vn = \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
 &&\mbox{erosion model},
@@
 \end{equation}
-where $V_\nn$ is the normal velocity of the interface and $\mu$ is the
+where $\Vn$ is the normal velocity of the interface and $\mu$ is the
 fluid viscosity.  The outer wall is formed by rounding off the corners
@@
 \begin{align*}
-  \uu(\xx) = (1-y^2,0)
-\end{align*}
-on $\Gamma$.  The boundary of the fluid domain is $\bd\Omega = \gamma_1
+  \UU(\xx) = \umax (1-y^2,0)
+\end{align*}
+on $\Gamma$.  H
+The boundary of the fluid domain is $\bd\Omega = \gamma_1
 \cup \cdots \cup \gamma_M \cup \Gamma$.  To minimize the boundary
@@
 proportional to the absolute value of the shear stress.   Since the
-constant of proportionality only sets the time scale, we let $V_\nn =
+constant of proportionality only sets the time scale, we let $\Vn =
 |\tau|$ as described in equation~\eqref{eqn:erosionModel}.
 \begin{align}
-  V{\nn} = \abs{\tau} \nn.
+  \Vn = \abs{\tau} \nn.
   \label{eqn:bodyEvolution}
@@
 \begin{equation}
+\label{eq:stresslaw}
 \tau \sim \frac{\mu V}{L \log(W/L)}
@@
 
-\vsp{30}
-
-\subsection{The limiting shape}
-
-\subsubsection{The vanishing rate of area}
-
-Then the rate of change of the body area is proportional to the shear
-stress times the total arc length exposed
+Now, the body's rate of area reduction is given by integrating the absolute shear stress around the boundary
 \begin{equation}
-\dot{A} = \int \atauD{2} \, ds = \mean{\atauD{2}} L
-\sim \frac{\mu V}{\log(W/L)}
-%\sim - \mean{\abs{\tauD{2}}} L
+\dot{A} = \int_{\gamma} \atau \, ds \, ,
 \end{equation}
-Solving gives (redo this calculation)
+which gives the exact relationship
+\begin{equation}
+\dot{A} = \mean{\atau} L \, .
+\end{equation}
+Thus, the area-loss rate is given by the product of the mean shear $\mean{\atau}$ and the total perimeter $L$. Inserting the scaling law \eqref{eq:stresslaw} gives
+ \begin{equation}
+\dot{A} \sim \frac{\mu V}{\log(W/L)} \, .
+\end{equation}
+Noting that $A \sim L^2$ allows one to solve this ODE to get
 \begin{equation}
@@
 \end{equation}
-where $C$ is a constant.
+This is an {\em implicit} relationship for how the area scales down in time during erosion.
+
+\todo[inline]{Define $C$; also maybe need to use a different letter.}
 
@@
 % Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
+
+\vsp{30}
+
+\subsection{The limiting shape}
 

### 2018-01-18 docs/methods/erosion_methods.tex
NM

@@
 \end{align*}
-on $\Gamma$.  H
+on $\Gamma$.
+Here, $U$ sets the maximum of the imposed Poiseuille flow.
+Often, we will simply set $U=1$, but in some instances we will change $U$ dynamically to enforce that the pressure drop across the computational cell is constant as bodies erode within it.
 The boundary of the fluid domain is $\bd\Omega = \gamma_1
@@
 
-\todo[inline]{I am not sure if $V$ has been defined previously. If not, need to define it.}
-
 Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing.
-Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu V / L$, since stress is inversely proportional to body scale $L$.
+Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / L$, since stress is inversely proportional to body scale $L$.
 This law must be modified in 2D, though.
 The modification is made non-trivial by subtleties associated with the Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory.
-For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to $\mu V W/ \log(W/L)$.
-This relationship implies that, for a 2D cross-section perpendicular to the long axis, the stress can be estimated by
+For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to $\mu \umax W/ \log(W/L)$.
+This relationship implies that, for a 2D cross-section perpendicular to the long axis, the stress (per unit $W$) can be estimated by
 \begin{equation}
 \label{eq:stresslaw}
-\tau \sim \frac{\mu V}{L \log(W/L)}
+\tau \sim \frac{\mu \umax}{L \log(W/L)}
 \end{equation}
-In interpreting our 2D simulations, we will treat $W$ as fixed (and must remember the requirement $W \gg L$).
+In interpreting our 2D simulations, we will treat $W$ as fixed and must remember the requirement $W \gg L$.
 
@@
  \begin{equation}
-\dot{A} \sim \frac{\mu V}{\log(W/L)} \, .
+\dot{A} \sim \frac{\mu \umax}{\log(W/L)} \, .
 \end{equation}

### 2018-01-25 docs/methods/erosion_methods.tex
NM
Writing methods paper, section on uniform stress opening angle

@@
 
-\vsp{30}
-
 \subsection{The limiting shape}
+
+With the vanishing rate understood, we now seek to quantify the limiting shape formed by a single eroding body.
+
+Certain features of this shape can be predicted analytically by appealing to the principal of uniform stress distribution.
+In particular, consider the angle formed at the front and rear stagnation points.
+In long time, the stress becomes uniform, in particular in a small vicinity of this front angle in which body curvature can be ignored.
+Zooming in on the front angle, we can consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$
+\vsp{30}. Exact solutions can be obtained to this problem via separation of variables in polar coordinates \cite{poz1997}.
 
@@
 
-\subsubsection{The uniform stress geometry}
-
 % NEWPAGE

### 2018-01-25 docs/methods/erosion_methods.tex
Need to get Pozrikidis book to do writing here.
NM

@@
 In long time, the stress becomes uniform, in particular in a small vicinity of this front angle in which body curvature can be ignored.
-Zooming in on the front angle, we can consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$
-\vsp{30}. Exact solutions can be obtained to this problem via separation of variables in polar coordinates \cite{poz1997}.
+Zooming in on the front angle, we can consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$.
+Exact solutions can be obtained to this problem via separation of variables in polar coordinates \cite{poz1997}.
+The corresponding stream function is $\psi = r^{\lambda}f(\theta)$, where $f$ satisfies the 4th order ODE
+\begin{equation}
+f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0
+\end{equation}
+subject to boundary conditions.
+The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\alpha)$.
+Thus, the wedge of uniform stress corresponds to $\lambda = 2$.
+For this value, the general solution for $f$ is
+\begin{equation}
+f(\theta) = B \sin(2\theta - \beta) + C \theta + D
+\end{equation}
+where $B, C$ are complex constants and $\beta$ is a real constant.
+
+% Pozrikidis page 239: symmetric flow.
+
+\vsp{30}
 

### 2018-01-25 docs/methods/erosion_methods.tex
NM

@@
 \end{equation}
-subject to boundary conditions.
+subject to boundary conditions $f(\alpha) = f'(\alpha) = 0$ and $f(0) = f''(0) = 0$.
 The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\alpha)$.
 Thus, the wedge of uniform stress corresponds to $\lambda = 2$.
-For this value, the general solution for $f$ is
+For this value, the solution for $f$ that satisfies the appropriate symmetry across $\theta = 0$ is
 \begin{equation}
-f(\theta) = B \sin(2\theta - \beta) + C \theta + D
+f(\theta) = B \sin (2 \theta) + C \theta
 \end{equation}
-where $B, C$ are complex constants and $\beta$ is a real constant.
+
+%\begin{equation}
+%f(\theta) = B \sin(2\theta - \beta) + C \theta + D
+%\end{equation}
+%where $B, C$ are complex constants and $\beta$ is a real constant.
 

### 2018-01-25 docs/methods/erosion_methods.tex
NM

--- 2018-01-25 docs/methods/erosion_methods.tex
@@
 
+% Pozrikidis page 239: symmetric flow.
 Certain features of this shape can be predicted analytically by appealing to the principal of uniform stress distribution.
@@
 Zooming in on the front angle, we can consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$.
-Exact solutions can be obtained to this problem via separation of variables in polar coordinates \cite{poz1997}.
+Exact solutions can be obtained to this problem via separation of variables in polar coordinates $(r, \theta)$ \cite{poz1997}.
+In this section alone, $\theta$ denotes the polar angle and not the tangent angle of the body.
 The corresponding stream function is $\psi = r^{\lambda}f(\theta)$, where $f$ satisfies the 4th order ODE
@@
 \end{equation}
-subject to boundary conditions.
-The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\alpha)$.
+This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down symmetry of the flow).
+The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\thb)$.
 Thus, the wedge of uniform stress corresponds to $\lambda = 2$.
-For this value, the general solution for $f$ is
+For this value, the solution for $f$ satisfying odd symmetry is
 \begin{equation}
-f(\theta) = B \sin(2\theta - \beta) + C \theta + D
+f(\theta) = B \sin (2 \theta) + C \theta
 \end{equation}
-where $B, C$ are complex constants and $\beta$ is a real constant.
-
-% Pozrikidis page 239: symmetric flow.
+Then the eigenvalue problem
 

### 2018-01-29 docs/methods/erosion_methods.tex
NM
worked on intro

@@
 \section{Introduction\label{s:intro}}
-Erosion is one example of a fluid-mechanical process that occurs when a
-fluid alters the geometry.  Erosion is responsible for a variety of
-processes, many of which are geophysical.  For example, sand dunes are
-longer on the windward side because of the wind erosion.  Another
-applications is erosion caused by groundwater flow, where a slow moving
-fluid erodes channels, or conduits, in the earth which creates a
-heterogeneous media that has a large effect on the resulting flow.
-Erosion is also important in the biophysical community. Plaque erosion
-in arteries is key to understanding heart disease~\cite{sha2002,
+Erosion is a fluid-mechanical process that is responsible for a variety
+of geophysical and other processes.  For example, wind erosion causes
+sand dunes to be  longer on the windward side~\cite{han1969}, and
+erosion is responsible for branching structures of streams and
+rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  Erosion is also important in
+the biophysical community. Plaque erosion in arteries is key to
+understanding heart disease~\cite{sha2002,
 gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can
-be explained by erosion~\cite{pic-van-hei2000}. In all these examples,
-there is a feedback process between the flow and the erodible
+be explained by erosion~\cite{pic-van-hei2000}.  Another applications is
+erosion caused by groundwater flow, where a slow moving fluid erodes
+channels, or conduits, in the ground.  This results in a heterogeneous
+media that has a large effect on the resulting flow.  In all these
+examples, there is a feedback process between the flow and the erodible
 bodies---the shape of the eroding body affects the flow, while the flow
@@
 into the effect of two-dimensional erosion, we consider erosion of a
-multiply-connected domain (Figure~\ref{fig:50bodies}), such as a porous
-media that is typically used to model groundwater flow.
+multiply-connected domain (Figure~\ref{fig:50bodies}), such as the
+porous geometry of many groundwater flows.
 
 Because of the scales involved with groundwater flow, we will restrict
-our attention to Stokesian dynamics.  For groundwater flow, Darcy's
-equation are often used, but this assumes a homogeneous geometry which
-is not always a fair assumption.  Instead, we will use the
-incompressible Stokes equations to represent the flow, and the
-individual pores will be be resolved, resulting in a complex
+our attention to Stokesian dynamics.  For groundwater flow, Darcy's law
+is often used, but this assumes a homogeneous geometry which is often
+not valid, and the method does not resolve the pore structure.  Instead, we
+will use the incompressible Stokes equations to represent the flow, and
+the individual pores will be be resolved, resulting in a complex
 multiply-connected geometry.  A boundary integral equation is
 well-suited as it can resolve complex geometries and the non-negligible
-interactions between bodies are resolved, all the while high-order
-accuracy and computational efficiency are achieved. To link the body and
+interactions between bodies are resolved. Moreover, high-order
+accuracy and computational efficiency are obtained. To link the body and
 fluid dynamics, the body is eroded in the normal direction at a rate
 that is proportional to the magnitude of the shear
-stress~\cite{ris-moo-chi-she-zha2012}. Other models for erosion include
-ones that use an erosion rate that is proportional to a power of the
-magnitude of the shear stress~\cite{par-izu2000}, or ones that use a
-critical shear stress below which erosion does not occur~\cite{lag2000}.
+stress~\cite{ris-moo-chi-she-zha2012}.  Tracking the interface of
+fluid-structure interaction problems with a long time horizon is
+particularly---the mesh is easily distorted and tangled by the dynamics
+and regions of high curvature develop.  We adopt a \thL~framework that
+keeps the mesh equidistributed in arclength, and a curvature
+penalization term can be added without introducing any non-linear
+stiffness.
+\todo[inline]{rework this}
 
@@
 such problems.
+
+Several groups consider the optimal body in a Stokes fluid that
+optimizes some quantity.  For example, Pironneau~\cite{pir1973} found
+the axisymmetric shape of a fixed volume body that minimizes drag is
+similar to an American football with an opening angle of 60 degrees, and
+this shape corresponds to a body with constant surface vorticity.  This
+analysis is taken further by Montenegro-Johnson and
+Lauga~\cite{mon-lau2015} where the optimal axisymmetric shape of fixed
+surface area is computed.  We include a similar calculation for the
+two-dimensional Stokes equations, and the resulting shape agrees with
+our numerical solution.
+
+\todo[inline]{Dump of text}
+Other models for erosion include ones that use an erosion rate that is
+proportional to a power of the magnitude of the shear
+stress~\cite{par-izu2000}, or ones that use a critical shear stress
+below which erosion does not occur~\cite{lag2000}.
+\todo[inline]{Dump of text}
 
@@
 \end{equation}
-Then the eigenvalue problem
+Imposing the no-slip boundary conditions gives the condition
+\begin{equation}
+\sin(2 \thb) - 2 \thb \cos(2 \thb) = 0
+\end{equation}
+which has solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(\pi - \thb) \approx 102$ degrees.
 

### 2018-01-30 docs/methods/erosion_methods.tex
Methods paper.

@@
 With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow.
-We first discuss the case of a single eroding body, as certain features can be predicted analytically and thus used for validation.
-We then discuss the erosion of multiple bodies and highlight important differences compared to the single-body case.
+We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation.
+We then discuss the erosion of multiple bodies and highlight important differences that arise as compared to the single-body case.
 

### 2018-01-30 docs/methods/erosion_methods.tex
NM

@@
 We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation.
-We then discuss the erosion of multiple bodies and highlight important differences that arise as compared to the single-body case.
+We then discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.
 
@@
 
-Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points, and shown at three evenly spaced times.
+Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times.
 Here, color represents the vorticity of the surrounding flow, which, when evaluated on the boundary, indicates the shear stress and thus the local erosion rate.
 As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it.
-The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations and vorticity vanishes at the body's front and rear stagnation points.
+The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points.
 At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
@@
 
-To better understand the body's shape evolution in this simulation, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
+To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
 The interfaces are color-coded by normalized time $t/t_f$.
@@
 Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / L$, since stress is inversely proportional to body scale $L$.
-This law must be modified in 2D, though.
-The modification is made non-trivial by subtleties associated with the Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory.
+This law must be modified in two dimensions, though.
+The modification (made non-trivial by subtleties of the Stokes paradox) can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory.
 For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to $\mu \umax W/ \log(W/L)$.
@@
 \end{equation}
-In interpreting our 2D simulations, we will treat $W$ as fixed and must remember the requirement $W \gg L$.
+In interpreting our 2D simulations, we will treat $W$ as fixed with the requirement $W \gg L$.
 
@@
 \end{equation}
-which gives the exact relationship
+giving the exact relationship
 \begin{equation}
@@
 \end{equation}
-Noting that $A \sim L^2$ allows one to solve this ODE to get
+Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
 \begin{equation}
-A (1 - \log A) = C (t_f - t)
+A (1 - \log A) = \areaconst (t_f - t)
 \end{equation}
@@
 
-\todo[inline]{Define $C$; also maybe need to use a different letter.}
+\todo[inline]{Define $\areaconst$; also maybe need to use a different letter.}
 
 In Fig.~6a, we show the body area vs time measured in the simulation
-against the above scaling law. In the scaling law, we chose, $C = 0.42$
+against the above scaling law. In the scaling law, we chose, $\areaconst = 0.42$
 (check this?)
@@
 
-With the vanishing rate understood, we now seek to quantify the limiting shape formed by a single eroding body.
+With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}a.
 
@@
 In this section alone, $\theta$ denotes the polar angle and not the tangent angle of the body.
-The corresponding stream function is $\psi = r^{\lambda}f(\theta)$, where $f$ satisfies the 4th order ODE
+The corresponding stream function is assumed to take the form $\psi = r^{\lambda}f(\theta)$, with $\Delta^2 \psi = 0$, which gives the 4th order ODE \cite{poz1997}
 \begin{equation}

### 2018-01-30 docs/methods/erosion_methods.tex
NM

@@
 \end{equation}
+where $c_A$ is a constant.
 This is an {\em implicit} relationship for how the area scales down in time during erosion.
-
-\todo[inline]{Define $\areaconst$; also maybe need to use a different letter.}
-
-In Fig.~6a, we show the body area vs time measured in the simulation
-against the above scaling law. In the scaling law, we chose, $\areaconst = 0.42$
-(check this?)
+In Fig.~6a, we show the body area as a function of time measured in the simulation
+against the above scaling law with $\areaconst = 0.42$.
 
@@
 which has solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(\pi - \thb) \approx 102$ degrees.
+
+We aim to measure the opening angle in our simulation, but, curiously, the body vanishes before a steady-state is definitively reached.
+To obtain the true terminal shape, we could restart our simulation with the final eroded body scaled up and iterate this process until reaching steady state.
+A simpler solution, though, is to remove the effect of shrinking during the erosion process by simply modifying the normal velocity $\Vn$ to have zero mean
 

### 2018-01-30 docs/methods/erosion_methods.tex
NM

@@
 A simpler solution, though, is to remove the effect of shrinking during the erosion process by simply modifying the normal velocity $\Vn$ to have zero mean
-
-\vsp{30}
+\begin{equation}
+\Vn \leftarrow \Vn - \mean{\Vn}
+\end{equation}
+This modification allows erosion to modify the body shape as it would normally, but artificially keeps the area of the body fixed.
+We show in Fig.~\ref{fixed_intface}a several interfaces at equally spaced times.
+Notice the body obtains the slender, football shape seen previously, but here more precision is available.
+We also show in Fig.~\ref{fixed_intface}b the stress, showing that the stress becomes much more evenly distributed as time proceeds.
+In this figure, time is normalized by the same vanishing time $t_f = 1.79E-2$ as the simulation shown in Fig.~\ref{shrink_intface}.
+Curiously, about 3 multiples of $t_f$ are required to reach a visually satisfying stead-state.
+This is very much in contrast to previous studies of erosion in high-Reynold's number flows, in which a reasonable steady-state was reached before the body vanished.
+
+\todo{Cite previous erosion papers}
 
@@
 \caption{One body fixed area}
-\label{}
+\label{fixed_intface}
 \end{center}
@@
 % Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+The fixed-area simulations allow us to make precise measurements of the body's opening angle and aspect ratio.
+
+\vsp{30}
 

### 2018-01-31 docs/methods/erosion_methods.tex
worked on intro

@@
 Erosion is a fluid-mechanical process that is responsible for a variety
-of geophysical and other processes.  For example, wind erosion causes
-sand dunes to be  longer on the windward side~\cite{han1969}, and
-erosion is responsible for branching structures of streams and
-rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  Erosion is also important in
-the biophysical community. Plaque erosion in arteries is key to
-understanding heart disease~\cite{sha2002,
+of phenomena in geophysical fluids and other processes.  For example,
+wind erosion causes sand dunes to be  longer on the windward
+side~\cite{han1969}, and erosion is responsible for branching structures
+of streams and rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  Erosion is
+also important in the biophysical community. Plaque erosion in arteries
+is key to understanding heart disease~\cite{sha2002,
 gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can
-be explained by erosion~\cite{pic-van-hei2000}.  Another applications is
-erosion caused by groundwater flow, where a slow moving fluid erodes
-channels, or conduits, in the ground.  This results in a heterogeneous
-media that has a large effect on the resulting flow.  In all these
-examples, there is a feedback process between the flow and the erodible
-bodies---the shape of the eroding body affects the flow, while the flow
-changes the shape by fluidizing the eroding body.  This fluid-mechanical
-feedback system has been simulated in idealized cases such as a single
-eroding two-dimensional body in a uniform
-flow~\cite{moo-ris-chi-zha-she2013} or a single mobile eroding
-three-dimensional body~\cite{mit-spa2016}. To further develop insight
-into the effect of two-dimensional erosion, we consider erosion of a
-multiply-connected domain (Figure~\ref{fig:50bodies}), such as the
-porous geometry of many groundwater flows.
-
-Because of the scales involved with groundwater flow, we will restrict
-our attention to Stokesian dynamics.  For groundwater flow, Darcy's law
-is often used, but this assumes a homogeneous geometry which is often
-not valid, and the method does not resolve the pore structure.  Instead, we
-will use the incompressible Stokes equations to represent the flow, and
-the individual pores will be be resolved, resulting in a complex
+be explained by erosion~\cite{pic-van-hei2000}.  Another application,
+which motivates the current work, is erosion caused by groundwater flow.
+Here, a slow moving fluid erodes channels in the ground, and this
+affects the fluid transport.  In all these examples, there is a feedback
+process between the flow and the eroding bodies---the shape of the
+bodies affect the flow, while the flow changes the shape by fluidizing
+each body.  This fluid-mechanical feedback system has been simulated in
+idealized cases such as a single eroding two-dimensional body in a
+uniform flow~\cite{moo-ris-chi-zha-she2013} or a single mobile eroding
+three-dimensional body~\cite{mit-spa2016}. However, to better understand
+the effect of erosion on groundwater flow, multiply-connected domains
+must be considered.  Here we simulate two-dimensional erosion, in
+multiply-connected domain such as the porous geometry of many
+groundwater flows (Figure~\ref{fig:50bodies}).
+
+Because of the length and velocity scales of groundwater flow, we
+restrict our attention to small Reynolds number flows.  For groundwater flow,
+Darcy's law is often used, but this does not resolve the pore structure
+and assumes a homogeneous geometry which is often not valid.  Instead,
+we use the incompressible Stokes equations to represent the flow, and
+the individual pores are resolved which results in a complex
 multiply-connected geometry.  A boundary integral equation is
-well-suited as it can resolve complex geometries and the non-negligible
-interactions between bodies are resolved. Moreover, high-order
-accuracy and computational efficiency are obtained. To link the body and
+well-suited for solving the incompressible Stokes equations in a complex
+geometry since it can resolve individual grains and the non-negligible
+interactions between bodies are resolved. Moreover, high-order accuracy
+and computational efficiency are obtained. To link the eroding body and
 fluid dynamics, the body is eroded in the normal direction at a rate
@@
 fluid-structure interaction problems with a long time horizon is
-particularly---the mesh is easily distorted and tangled by the dynamics
-and regions of high curvature develop.  We adopt a \thL~framework that
-keeps the mesh equidistributed in arclength, and a curvature
-penalization term can be added without introducing any non-linear
-stiffness.
-\todo[inline]{rework this}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Contributions} The present study will develop numerical
-methods to simulate viscous erosion of multiply-connected
-two-dimensional geometries.  By assuming the flow is viscous, we are
-assuming the flow is very slow and in small length scales, as is the
-case in groundwater flow.  Moreover, by allowing for complex
-multiply-connected domains, the effects due to interacting bodies on the
-erosion are captured.  We start by authenticating our method on a single
-circular body placed symmetrically in a pipe flow.  By artificially
-fixing the area of the body as a function of time, we are able to
-characterize the long-time behavior of the shape and the resulting flow
-and compare these results with analytical results.  Then, we compute the
-vorticity of erosion in multiply-connected geometries to better
-characterize erosion in porous media.
-
-Because of the low Reynolds number assumption, the flow will be assumed
-to be Stokesian.  Then, to create high-fidelity and computationally
-efficient numerical methods, two fast and accurate methods will be
-employed:
-\begin{enumerate}
-  \item The fluid equations will be solved with spectral accuracy by
-  using an efficient boundary integral equation method. Moreover, the
-  rate of erosion will be computed and the rate of erosion will be
-  computed with spectral accuracy.
-  \item Given a rate of erosion, the shape will be integrated in time
-  with second-order accuracy.  All spatial derivatives will be computed
-  in Fourier space, resulting in spectral accuracy in space.
-\end{enumerate}
-We use a quasi-steady assumption so that these two steps can be iterated
-to simulate the dynamics.
+particularly---the mesh is often distorted and tangled by the dynamics
+and regions of high curvature develop.  These two issues are resolved
+by, first, introducing a tangential velocity field to maintain a grid
+that is equispaced in arclength, but that does not affect the dynamics,
+and, second, a curvature penalization term.  Furthermore, the frame of
+reference is changed to \thL~variables so that the curvature term
+appears as a linear diffusive term that can easily be treated implicitly
+to avoid stiffness.
+
+In addition to simulating the eroding grains, the flow is further
+characterized by computing the vorticity in the flow.  The vorticity is
+particularly insightful since it is identical to the shear stress on
+no-slip boundaries in the Stokesian limit.  Therefore, by computing the
+vorticity, we are able to locate regions where the erosion rates will be
+fastest or slowest.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Contributions} The present study develops numerical methods
+to simulate erosion of multiply-connected two-dimensional geometries.
+Since groundwater flow occurs at small spatial and velocity scales, we
+assume the flow is viscous (ie.~zero Reynolds number).  By allowing for
+complex multiply-connected domains, we capture the effect that
+interacting bodies have on erosion, and the grains in the flow are
+individually resolved rather than homogenized.  We start by validating
+our method on a single circular body placed symmetrically in a pipe
+flow.  By artificially fixing the area of the body as a function of
+time, we are able to characterize the long-time behavior of the shape
+and the resulting flow and compare these results with analytical
+results.  Then, we compute the vorticity of erosion in
+multiply-connected geometries to better characterize erosion in porous
+media.
+
+To create high-fidelity and computationally efficient numerical methods,
+two fast and accurate methods are employed.  First, the fluid equations
+and the erosion rate (shear stress) are efficiently solved with spectral
+accuracy by using a fast multipole accelerated boundary integral
+equation method.  Given the rate of erosion, the shape is integrated in
+time with second-order accuracy.  All spatial derivatives are be
+computed in Fourier space, resulting in spectral accuracy in space.
+Then, to further visualize the effect of erosion, we compute the
+vorticity of the flow (Figure~\ref{fig:50bodies}) to visualize regions
+of high and low erosion.
+
+A challenge with erosion is that it creates corners at points on the
+body where the shear stress vanishes.  While recent work does allow for
+integral equation methods to resolve corners, we employ a different
+method.  First, we add a regularization term to the shear stress to
+penalize regions of high curvature.  Second, we apply a Gaussian filter
+to smooth the absolute value of the shear stress before the body shape
+is updated.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Limitations} There are two main limitations of the current
+work.  First, the flow is assumed to be two-dimensional.  However, by
+assuming that the flow is two-dimensional, we are able to simulate the
+erosion of more bodies and with higher resolution than would be
+available in three dimensions.  Moreover, several flows can be described
+to good accuracy under a two-dimensional approximation, certain
+phenomena occur only in three dimensions.  Extending the current work to
+three dimensions is possible with a boundary integral equation
+formulation.  In particular, the fluid solvers exist~\cite{mal-bir2015},
+and the main challenges of a BIE solver have been addressed by other
+groups including surface representation~\cite{yin-bir-zor2006,
+vee-rah-bir-zor2011}, near-singular integration~\cite{yin-bir-zor2006,
+kli-tor2016b}, and fast summation methods~\cite{yin-bir-zor2004,
+ros-ols2015}.  The more significant challenge of extending our work to
+three dimensions is guaranteeing that the mesh does not become
+distorted, which can be done, for example, by using an extension of the
+two-dimensional {\thL} formulation~\cite{amb-sie-tlu2013}.
+
+The second limitation is that the eroding bodies are fixed.  Mitchell
+and Spagnolie~\cite{mit-spa2016} simulate a single mobile eroding body
+in three dimensions~\cite{mit-spa2016}, but additional challenges are
+caused when there are multiple bodies. In particular, especially in
+dense suspensions, bodies can become extremely close to one another, and
+the interaction between the bodies is difficult to resolve unless the
+underlying mesh is refined to levels that are intractable. In future
+work we plan to consider mobile eroding bodies, but include a small
+force and torque so that unphysical contact is
+avoided~\cite{lu-rah-zor2017}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Related work} Simulating eroding bodies has been studied
+analytically, experimentally, and numerically.  Because of the scales
+involves with geophysical flows, most of these works consider high
+Reynolds number flows.  For instance, the experimental work of Moore et
+al.~\cite{moo-ris-chi-zha-she2013} considers on the order of $10^4$.
+For low Reynolds number flows, Mitchell and Spagnolie~\cite{mit-spa2016}
+simulate the erosion of a mobile body in three dimensions, but they only
+consider single body.
+
+Mitchell and Spagnolie~\cite{mit-spa2016} formulate the traction jump as
+a DLP using Lorentz Reciprocal Theorem so that additional layer
+potentials have to be evaluated.  That is, they never find the density
+function.
 
@@
 porous region as a function of time can be computed in future work.
-
-A challenge with erosion is that it creates corners at points on the
-body where the shear stress vanishes.  While recent work does allow for
-integral equation methods to resolve a corner, we employ a different
-method.  First, we add a regularization term to the shear stress to
-penalize regions of high curvature.  Second, we apply a Gaussian filter
-to smooth the absolute value of the shear stress before the body shape
-is updated.
-
-To further visualize the effect of erosion, we compute the vorticity of
-the flow (Figure~\ref{fig:50bodies}) which is equal to the shear stress
-in the Stokesian limit.  Finally, to evolve the geometry, a second-order
-time stepping method that guarantees that the mesh does not become
-distorted will be employed.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Limitations} There are two main limitations of the current
-work.  First, the flow is assumed to be two-dimensional.  However, by
-assuming that the flow is two-dimensional, we are able to simulate the
-erosion of more bodies and with higher resolution than would be
-available in three dimensions.  Moreover, Several flows can be described
-to good accuracy under a two-dimensional approximation, certain
-phenomena occur only in three dimensions.  The boundary integral
-equation formulation for the fluid solver exists, and the main
-challenges of a BIE solver have been addressed by other groups including
-surface representation~\cite{yin-bir-zor2006, vee-rah-bir-zor2011},
-near-singular integration~\cite{yin-bir-zor2006, kli-tor2016b}, and fast
-summation methods~\cite{yin-bir-zor2004, ros-ols2015}.  The more
-significant challenge of extending our work to three dimensions is
-guaranteeing that the mesh does not become distorted, which can be done,
-for example, by using an extension of the two-dimensional {\thL}
-formulation~\cite{amb-sie-tlu2013}.
-
-The second limitation is that the eroding bodies are fixed.  Mitchell
-and Spagnolie~\cite{mit-spa2016} simulate a single mobile eroding body
-in three dimensions have been considered~\cite{mit-spa2016}, but
-additional challenges are caused when there are multiple bodies. In
-particular, especially in dense suspensions, bodies can become extremely
-close to one another, and the interaction between the bodies is
-difficult to resolve unless the underlying mesh is refined to levels
-that are intractable. In future work we plan to consider mobile eroding
-bodies, but include a small force and torque so that unphysical contact
-is avoided~\cite{lu-rah-zor2017}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Related work} Simulating eroding bodies has been studied
-analytically, experimentally, and numerically.  Because of the scales
-involves with geophysical flows, most of these works consider high
-Reynolds number flows.  For instance, the experimental work of Moore et
-al.~\cite{moo-ris-chi-zha-she2013} considers on the order of $10^4$.
-For low Reynolds number flows, Mitchell and Spagnolie~\cite{mit-spa2016}
-simulate the erosion of a mobile body in three dimensions, but they only
-consider single body.
 

### 2018-01-31 docs/methods/erosion_methods.tex
NM

@@
 
-The fixed-area simulations allow us to make precise measurements of the body's opening angle and aspect ratio.
-
-\vsp{30}
+The fixed-area simulations allow us to make precise measurements of the body's opening angle and aspect ratio as displayed in Fig.~\ref{arangle}.
+Figure \ref{arangle}a shows the aspect ratio, defined as the body's horizontal compared to its vertical width.
+The initial circular geometry has an aspect ratio of unity.
+As erosion causes the body to become more slender, the aspect ratio increases and tends to a value of $2.6$ in long time.
 
@@
 \caption{Aspect ratio and opening angle}
-\label{}
+\label{arangle}
 \end{center}
@@
 % Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+\vsp{30}
 

### 2018-01-31 docs/methods/erosion_methods.tex
NM

@@
 
+\todo[inline]{Explain the drag here too}
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 The initial circular geometry has an aspect ratio of unity.
-As erosion causes the body to become more slender, the aspect ratio increases and tends to a value of $2.6$ in long time.
+As erosion causes the body to become more slender, the aspect ratio increases and tends to a value of $2.65$ in long time.
+Figure \ref{arangle}b shows the body's opening angle, which we measure by fitting the tangent angle $\theta(\alpha)$ with a 7th degree polynomial over a region excluding the front/rear stagnation point (where there is high curvature that approximates an angle).
+The polynomial fit is then extrapolated to the stagnation point to get an angle estimate (subject to some uncertainty, which we quantify below).
+As seen in Fig.~\ref{arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
+Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the predicted value of $102^\circ$ in long time.
 

### 2018-01-31 docs/methods/erosion_methods.tex
NM

--- 2018-01-31 docs/methods/erosion_methods.tex
@@
 
-The fixed-area simulations allow us to make precise measurements of the body's opening angle and aspect ratio.
-
-\vsp{30}
+The fixed-area simulations allow us to make precise measurements of the body's opening angle and aspect ratio as displayed in Fig.~\ref{fig:arangle}.
+Figure \ref{fig:arangle}a shows the aspect ratio, defined as the body's horizontal compared to its vertical width.
+The initial circular geometry has an aspect ratio of unity.
+As erosion causes the body to become more slender, the aspect ratio increases and tends to a value of $2.7$ in long time.
+Figure \ref{fig:arangle}b shows the body's opening angle, which we measure by fitting the tangent angle $\theta(\alpha)$ with a 7th degree polynomial over a region excluding the front/rear stagnation point (where there is high curvature that approximates an angle).
+The polynomial fit is then extrapolated to the stagnation point to get an angle estimate (subject to some uncertainty, which we estimate below).
+As seen in Fig.~\ref{arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
+Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in long time.
+This coincides exactly with the valued predicted by our local solutions.
 
@@
 \caption{Aspect ratio and opening angle}
-\label{}
+\label{fig:arangle}
 \end{center}
@@
 % Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+To examine the influence of the smoothing parameters, $\eps$ and $\sigma$, we show in Table~\ref{table:arangle} the measurements of aspect ratio and opening angle for different simulations.
+We fix the total number of discretization points at $N_\iin = 1024$ and sequently reduce the smoothing with $\eps$ and $\sigma$ always equal.
+We choose the values $20/1024$, $10/1024$, and $5/1024$.
+Roughly, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively.
+As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$.
+We also estimate the uncertainty in the angle measurements by varying the region of the polynomial fit and the degree of the fit.
+As shown in the table, as the smoothing parameters are reduced, the angle measurements become more precise.
 
@@
 \vspace{0.3 pc}
-%\label{aaa}
+\label{table:arangle}
 \begin{tabular}{c c c}
@@
 % npts = 1024
+
+\vsp{30}
 

### 2018-01-31 docs/methods/erosion_methods.tex
NM

@@
 Curiously, about 3 multiples of $t_f$ are required to reach a visually satisfying stead-state.
-This is very much in contrast to previous studies of erosion in high-Reynold's number flows, in which a reasonable steady-state was reached before the body vanished.
-
-\todo{Cite previous erosion papers}
+This is very much in contrast to previous studies of erosion in high-Reynold's number flows, in which a reasonable steady-state was reached before the body vanished \cite{moo-ris-chi-zha-she2013}.
 
@@
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}[p]%[htbp]
+\begin{figure}%[htbp]
 \begin{center}
@@
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{table}[p]%[htbp]
+\begin{table}%[htbp]
 \begin{center}

### 2018-01-31 docs/methods/erosion_methods.tex
NM

@@
 The polynomial fit is then extrapolated to the stagnation point to get an angle estimate (subject to some uncertainty, which we estimate below).
-As seen in Fig.~\ref{arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
+As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
 Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in long time.
 This coincides exactly with the valued predicted by our local solutions.
+
+\todo[inline]{Also point to figure 7a, with the smoothed out corner}
 

### 2018-02-02 docs/methods/erosion_methods.tex
small changes to method paper

@@
 Because of the length and velocity scales of groundwater flow, we
-restrict our attention to small Reynolds number flows.  For groundwater flow,
-Darcy's law is often used, but this does not resolve the pore structure
-and assumes a homogeneous geometry which is often not valid.  Instead,
-we use the incompressible Stokes equations to represent the flow, and
-the individual pores are resolved which results in a complex
+restrict our attention to small Reynolds number flows.  For groundwater
+flow, Darcy's law is often used, but this does not resolve the pore
+structure and assumes a homogeneous geometry which is often not valid.
+Instead, we use the incompressible Stokes equations to represent the
+flow, and the individual pores are resolved which results in a complex
 multiply-connected geometry.  A boundary integral equation is
@@
 available in three dimensions.  Moreover, several flows can be described
-to good accuracy under a two-dimensional approximation, certain
+to good accuracy under a two-dimensional approximation, but certain
 phenomena occur only in three dimensions.  Extending the current work to
@@
 velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the
-bounding wall, we prescribed a velocity $\UU(\xx,t)$.  Then, the
+bounding wall, we prescribe a velocity $\UU(\xx,t)$.  Then, the
 governing equations are
@@
 \grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap
-&&\mbox{conservation of mass} \\
-\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{no slip on the
+&&\mbox{\em conservation of mass} \\
+\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
 bodies} \\
-\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{outer wall
+\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
 velocity} \\
 \Vn = \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
-&&\mbox{erosion model},
+&&\mbox{\em erosion model},
 \end{split}
@@
 \begin{align*}
-  \UU(\xx) = \umax (1-y^2,0)
-\end{align*}
-on $\Gamma$.
-Here, $U$ sets the maximum of the imposed Poiseuille flow.
-Often, we will simply set $U=1$, but in some instances we will change $U$ dynamically to enforce that the pressure drop across the computational cell is constant as bodies erode within it.
-The boundary of the fluid domain is $\bd\Omega = \gamma_1
-\cup \cdots \cup \gamma_M \cup \Gamma$.  To minimize the boundary
-effects of the inflow and outflow, we only place bodies in the center
-third, $[-1,1] \times [-1,1]$, of the fluid domain.
+  \UU(\xx) = \umax (1-y^2,0), \quad \xx \in \Gamma,
+\end{align*}
+where $U$ sets the maximum of the imposed Poiseuille flow. Often, we
+will simply set $U=1$, but in some instances we change $U$ dynamically
+to enforce that the pressure drop across the computational cell is
+constant as bodies erode within it.  The boundary of the fluid domain is
+$\bd\Omega = \gamma_1 \cup \cdots \cup \gamma_M \cup \Gamma$.  To
+minimize the boundary effects of the inflow and outflow, we only place
+bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.
 \begin{figure}[htpb]
@@
     $\gamma_\ell$ whose unit normal points outward relative to the
-    geometry.  On the outer geometry $\Gamma$, a pipe flow is imposed.
-    The bodies are eroded at a rate that is proportional to the
-    magnitude of the shear stress applied by the Stokesian fluid.  The
-    bodies are constrained to the middle third of the channel that is
-    located between the dashed lines.}
+    geometry.  On the outer geometry $\Gamma$, a Hagen-Poiseuille flow
+    is imposed.  The bodies are eroded at a rate that is proportional to
+    the magnitude of the shear stress applied by the Stokesian fluid.
+    The bodies are constrained to the middle third of the channel that
+    is located between the dashed lines.}
 \end{figure}
@@
 freeze the geometry, solve the incompressible Stokes equations, and then
-update the geometry according to the erosion model.  A flow diagram is
-illustrated in Figure~\ref{fig:workflow}.  The two steps inside the red
-rectangle describes a time step in the quasi-static approximation
-\begin{figure}[htpb]
-  \centering
-  \input{figs/workflow.tikz}
-  \caption{\label{fig:workflow}A caption.}
-\end{figure}
+update the geometry according to the erosion model.  The two steps
+inside the red rectangle describes a time step in the quasi-static
+approximation.
+%A flow diagram is illustrated in Figure~\ref{fig:workflow}.  
+%\begin{figure}[htpb]
+%  \centering
+%  \input{figs/workflow.tikz}
+%  \caption{\label{fig:workflow}A caption.}
+%\end{figure}
 
@@
 
-To model erosion, the normal velocity is prescribed to be
-proportional to the absolute value of the shear stress.   Since the
-constant of proportionality only sets the time scale, we let $\Vn =
-|\tau|$ as described in equation~\eqref{eqn:erosionModel}.
-\begin{align}
-  \Vn = \abs{\tau} \nn.
-  \label{eqn:bodyEvolution}
-\end{align}
-For the sake of numerical stability, we modify this law in
-Section~\ref{sec:thetaL}.
+To model erosion, the normal velocity is  proportional to the absolute
+value of the shear stress.   Since the constant of proportionality only
+sets the time scale, we let $\Vn = |\tau|$ as described in
+equation~\eqref{eqn:erosionModel}. For the sake of numerical stability,
+we modify this law in Section~\ref{sec:thetaL}.
 
@@
 \end{alignat*}
-As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.  We
-start by defining the double-layer potential
-$\eeta:\bd\Omega \rightarrow \RR^2$,
+The boundary condition $\ff$ is the prescribed velocity $\UU$ on
+$\Gamma$, and it is zero on the grains $\gamma$.  As the viscosity $\mu$
+also sets the time scale, we take $\mu=1$.  We start by defining the
+double-layer potential
 \begin{align}
@@
 double-layer potential can not capture velocity fields corresponding to
-rigid body motions~\cite{pow-mir1987}, and this is rectified by
-introducing additional terms for each body.  The rank deficiency removed
+rigid body motions~\cite{pow-mir1987}.  The rank deficiency is removed
 by complementing the double-layer potential with a Stokeslets and
@@
 For the sake of numerical stability, we modify the erosion law in
-equation~\eqref{eqn:bodyEvolution} to include a term that depends on the
+equation~\eqref{eqn:erosionModel} to include a term that depends on the
 local curvature $\kappa$. The idea is to prevent regions of very high

### 2018-02-02 docs/methods/erosion_methods.tex
round of edits

@@
 multiply-connected domain such as the porous geometry of many
-groundwater flows (Figure~\ref{fig:50bodies}).
+groundwater flows (Fig.~\ref{fig:50bodies}).
 
@@
 Then, to further visualize the effect of erosion, we compute the
-vorticity of the flow (Figure~\ref{fig:50bodies}) to visualize regions
+vorticity of the flow (Fig.~\ref{fig:50bodies}) to visualize regions
 of high and low erosion.
@@
 \label{sec:shearStressLP}
+To compute the shear stress, there are two options.  First, instead of
+solving the BIE~\eqref{eqn:completed_BIE} for an arbitrary density
+function, a similar BIE can be solved for the
+traction~\cite{mit-spa2016}.  Alternatively, the traction corresponding
+to the double-layer potential of the velocity~\eqref{eqn:velocityDLP}
+can be computed using appropriate layer potentials.  While the first
+method bypasses a step by not forming a density function, this method
+does not allow us to compute other quantities such as the vorticity.
+Therefore, we use the second method.
+
 The shear stress is
@@
 where $\ss$ and $\nn$ are the unit tangent and normal vectors,
-respectively (Figure~\ref{fig:schematic}).  The velocity field of the
+respectively (Fig.~\ref{fig:schematic}).  The velocity field of the
 completed double-layer potential~\eqref{eqn:completed_DLP} involves
@@
 The deformation tensor of the double-layer
-potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
+potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$
+is~\cite{qua-bir2014a}
 \begin{equation}
@@
 taking the limit of equation~\eqref{eqn:shearStressDLP} when $\xx$ tends
-to $\xx_0 \in \bd\Omega$.  The limiting value is given
-by~\cite{qua-bir2014a}
+to $\xx_0 \in \bd\Omega$.  The limiting value is given by
 \begin{align*}
@@
     \frac{\xi_\ell}{\rho^4} \left(\rr \otimes \rr^\perp + 
-    \rr^\perp \otimes \rr \right),
+    \rr^\perp \otimes \rr \right).
   \end{aligned}
 \end{equation}
-where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is the point chosen inside body
-$\gamma_\ell$, and $\rho = \|\rr_\ell\|$.  Now that the deformation
-tensor of each component of the completed double-layer potential is
-computed, the shear stress at $\xx_0 \in \bd\Omega$ is
+Now that the deformation tensor of each component of the completed
+double-layer potential is computed, the shear stress at $\xx_0 \in
+\bd\Omega$ is
 \begin{align}
@@
 interaction problems \cite{hou-low-she1994}. Throughout this section, we
-use the following conventions: the bodies are parametrized in the CCW
-direction and the normal vector points into the bodies (or out of the
-fluid).
+use the following conventions: the bodies are parametrized in the
+counterclockwise direction and the normal vector points into the bodies
+(Fig.~\ref{fig:schematic}).
 
@@
   \label{eqn:Vn}
-  \Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right)
+  \Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1
+  \right).
 \end{align}
@@
 \label{eqn:Vn2}
-\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right)
+\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1
+\right).
 %\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
@@
 \pderiv{\theta}{t} &= \frac{2\pi}{L} \left(
-\eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
+\eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} +
+\thalpha \Vs \right).
 \end{align}
@@
 interface according to equations~\eqref{eqn:Levo1}
-and~\eqref{eqn:thetaevo1} are described.
-
-So that we can form stable simulations with long time horizons, we use
-numerical methods that achieve spectral accuracy in space, second-order
-accuracy in time, and maintain an equispaced discretization of the
-bodies.  The boundaries are represented in Fourier space, and all
-derivatives are computed with spectral accuracy using Fourier
-differentiation.
+and~\eqref{eqn:thetaevo1} are described. So that we can form stable
+simulations with long time horizons, we use numerical methods that
+achieve spectral accuracy in space, second-order accuracy in time, and
+maintain an equispaced discretization of the bodies.  The boundaries are
+represented in Fourier space, giving us a set of discretization points
+$\xx_i$ of each body, and all derivatives and integrals (the arclength,
+curvature, and mean values) are computed with spectral accuracy using
+the Fourier representation.
 
@@
 To numerically evaluate the completed double-layer
-potential~\eqref{eqn:completed_BIE}, we let $N_\iin$ be the number of
+potential~\eqref{eqn:completed_BIE}, let $N_\iin$ be the number of
 points on each of the $M$ bodies, and $N_\out$ be the number of points
@@
       \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) \\
-      &\hspace{40pt}
+      &\hspace{53pt}
       +\sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) 
@@
       \nn(\xx_j))\eeta(\xx_j), \\
-    \llambda_\ell &= \sum_{\xx_i \in \gamma_\ell} \eeta(\xx_i) 
-      \Delta s_i, \\ 
-    \mu_\ell &= \sum_{\xx_i \in \gamma_\ell}
-      {(\xx_i - \cc_\ell)}^\perp \cdot \eeta(\xx_i) \Delta s_i,
+    \llambda_\ell &= \sum_{\xx_j \in \gamma_\ell} \eeta(\xx_j) 
+      \Delta s_j, \\ 
+    \mu_\ell &= \sum_{\xx_j \in \gamma_\ell}
+      {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j,
   \end{aligned}
@@
 in~\eqref{eqn:completed_BIE_discretized}.  Naively, evaluating this sum
-at all points $\xx_i$, $i=1,\ldots,N$ requires $\bigO(N^2)$ operations.
-To reduce the computational cost, we use the Fast Multipole Method
+at all points requires $\bigO(N^2)$ operations.  To reduce the
+computational cost, we use the Fast Multipole Method
 (FMM)~\cite{gre-rok1987, gre-gre-may1992} to reduce the complexity from
@@
 rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
-\gamma$.  However, the kernel of the deformation tensor due to the
+\gamma$.  For the layer potential term, we would like to use the
+trapezoid rule, but the kernel of the deformation tensor due to the
 double-layer potential~\eqref{eqn:shearStressDLP} 
@@
 and a similar approximation is used when $i$ is even.  The deformation
-tensor due to the Stokeslets and rotlets is given in
+tensor due to the Stokeslets and rotlets are given in
 equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
@@
 \label{s:results}
-With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow.
-We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation.
-We then discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.
+With the description of the methods complete, we now present numerical
+results on bodies eroding in Stokes flow. We first discuss the case of a
+single body, as certain features can be predicted analytically and thus
+used for validation. We then discuss the erosion of multiple bodies and
+highlight important differences that arise compared to the single-body
+case.
 
@@
 \includegraphics[width = 0.80 \textwidth]{./figs/01bodseq.pdf}
-\caption{A single body eroding in Stokes flow.
-As the body erodes, it develops a corner at its front and rear stagnation points, while remaining for-aft symmetric due to time-reversibility.
-Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress.
-In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
-\label{01bodseq}
+\caption{\label{01bodseq} A single body eroding in Stokes flow. As the
+body erodes, it develops a corner at its front and rear stagnation
+points, while remaining for-aft symmetric due to time-reversibility.
+Color indicates the vorticity of the surrounding flow, which, when
+evaluated on the boundary, gives the local shear stress. In this
+simulation, we use $N_\iin = 1024$ discretization points on the body,
+$N_\out = 1024$ points on the outer boundary, a time-step of $\Dt =
+1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma =
+10/1024$.}
 \end{center}
@@
 
-Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times.
-Here, color represents the vorticity of the surrounding flow, which, when evaluated on the boundary, indicates the shear stress and thus the local erosion rate.
-As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it.
-The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points.
-At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
-The greatest material loss has occurred at the body's top and bottom, where shear is strongest.
-Interestingly, the body has developed well-defined corners at its front and rear stagnation points.
-This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry.
-As shown in the third snapshot, this corner persists as the bodies becomes even more slender while wasting away.
-In this simulation, the body completely vanishes at a final time of $t_f = 1.79E-2$.
-
-To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
-The interfaces are color-coded by normalized time $t/t_f$.
-The body seems to converge to a shape that resembles an American football -- a fairly slender, for-aft symmetric shape with corners at the front and back.
-Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
-The normalized arc length $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point.
-At early times (yellow to orange), the stress is distributed non-uniformly, with highest values at the top and bottom of the body.
-As time proceeds, though, the stress becomes more evenly distributed along the body's surface (red).
-As the body nears the final stages of erosion (dark red), the stress actually becomes slightly higher near the stagnation points.
-A close look reveals that {\em at} the stagnation points, the stress always vanishes, though in a region that becomes increasingly narrow.
+Fig.~\ref{01bodseq} shows the erosion of a single body, numerically
+simulated with $N_\iin = 1024$ discretization points and shown at three
+evenly spaced times. Here, color represents the vorticity of the
+surrounding flow, which, when evaluated on the boundary, indicates the
+shear stress and thus the local erosion rate. As seen in the left-most
+snapshot, the body is initially circular and has the strongest vorticity
+above and below it. The flow is for-aft symmetric as a result of the
+time-reversibility of the Stokes equations, with vorticity vanishing at
+the body's front and rear stagnation points. At the next instance, the
+body has lost material due to erosion, but remains for-aft symmetric due
+to the flow symmetry. The greatest material loss has occurred at the
+body's top and bottom, where shear is strongest. Interestingly, the body
+has developed well-defined corners at its front and rear stagnation
+points. This geometric feature is a consequence of the erosion law,
+which depends on the {\em absolute} shear stress: wherever the stress
+vanishes, $\atau$ exhibits a corner, which manifests as a corner in the
+geometry. As shown in the third snapshot, this corner persists as the
+bodies becomes even more slender while wasting away. In this simulation,
+the body completely vanishes at a final time of $t_f = 1.79E-2$.
+
+To better understand the shape evolution, Fig.~\ref{shrink_intface}(a)
+shows several superimposed interfaces at evenly spaced times. The
+interfaces are color-coded by normalized time $t/t_f$. The body seems to
+converge to a shape that resembles an American football---a fairly
+slender, for-aft symmetric shape with corners at the front and back.
+Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress,
+$\atau$, is distributed along each of these interfaces. The normalized
+arc length $s/L$ runs counterclockwise around the body, with $s/L = 0$
+corresponding to the rear stagnation point and $s/L = 0.5$ the front
+stagnation point. At early times (yellow to orange), the stress is
+distributed non-uniformly, with highest values at the top and bottom of
+the body. As time proceeds, though, the stress becomes more evenly
+distributed along the body's surface (red). As the body nears the final
+stages of erosion (dark red), the stress actually becomes slightly
+higher near the stagnation points. A close look reveals that {\em at}
+the stagnation points, the stress always vanishes, though in a region
+that becomes increasingly narrow.
 
@@
 \includegraphics[width = 0.75 \textwidth]{./figs/shrink_intface.pdf}
-\caption{Shape and stress evolution.
-(a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
-Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes.
-(b) The distribution of absolute shear stress, $\atau$, along each of these interfaces.
-Normalized arc length, $s/L$, runs counterclockwise from the rear stagnation point.
-The stress initially varies over the body's surface, but becomes more uniform over time.
-}
-\label{shrink_intface}
+\caption{\label{shrink_intface} Shape and stress evolution. (a)
+Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced
+time intervals. Color indicates normalized time, $t/t_f$, where $t_f =
+1.79E-2$ is the time at which the body completely vanishes. (b) The
+distribution of absolute shear stress, $\atau$, along each of these
+interfaces. Normalized arc length, $s/L$, runs counterclockwise from the
+rear stagnation point. The stress initially varies over the body's
+surface, but becomes more uniform over time.}
 \end{center}
@@
 
-Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing.
-Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / L$, since stress is inversely proportional to body scale $L$.
-This law must be modified in two dimensions, though.
-The modification (made non-trivial by subtleties of the Stokes paradox) can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory.
-For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to $\mu \umax W/ \log(W/L)$.
-This relationship implies that, for a 2D cross-section perpendicular to the long axis, the stress (per unit $W$) can be estimated by
-\begin{equation}
-\label{eq:stresslaw}
-\tau \sim \frac{\mu \umax}{L \log(W/L)}
-\end{equation}
-In interpreting our 2D simulations, we will treat $W$ as fixed with the requirement $W \gg L$.
-
-Now, the body's rate of area reduction is given by integrating the absolute shear stress around the boundary
-\begin{equation}
+Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that
+the spacing between successive interfaces becomes larger as the body
+shrinks, suggesting that the overall shear stress is growing. Of course,
+such a relationship is consistent with the well-known 3D Stokes drag
+law, $\tau \sim \mu \umax / L$, since stress is inversely proportional
+to body scale $L$. This law must be modified in two dimensions, though.
+The modification (made non-trivial by subtleties of the Stokes paradox)
+can be correctly deduced by noting that, as the body vanishes, its drag
+must be consistent with slender-body theory. For a slender body in flow
+perpendicular to its long-axis $W \gg L$, the drag is proportional to
+$\mu \umax W/ \log(W/L)$. This relationship implies that, for a 2D
+cross-section perpendicular to the long axis, the stress (per unit $W$)
+can be estimated by
+\begin{align}
+  \label{eqn:stresslaw}
+  \tau \sim \frac{\mu \umax}{L \log(W/L)}.
+\end{align}
+In interpreting our 2D simulations, we will treat $W$ as fixed with the
+requirement $W \gg L$.
+
+Now, the body's rate of area reduction is given by integrating the
+absolute shear stress around the boundary
+\begin{align*}
   \dot{A} = \int_{\gamma} \atau \, ds \, ,
-\end{equation}
+\end{align*}
 giving the exact relationship
-\begin{equation}
+\begin{align*}
   \dot{A} = \mean{\atau} L \, .
-\end{equation}
-Thus, the area-loss rate is given by the product of the mean shear $\mean{\atau}$ and the total perimeter $L$. Inserting the scaling law \eqref{eq:stresslaw} gives
- \begin{equation}
+\end{align*}
+Thus, the area-loss rate is given by the product of the mean shear
+$\mean{\atau}$ and the total perimeter $L$. Inserting the scaling
+law~\eqref{eqn:stresslaw} gives
+\begin{align*}
   \dot{A} \sim \frac{\mu \umax}{\log(W/L)} \, .
-\end{equation}
+\end{align*}
 Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
-\begin{equation}
+\begin{align*}
   A (1 - \log A) = \areaconst (t_f - t)
-\end{equation}
+\end{align*}
 where $c_A$ is a constant.
@@
 
-With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}a.
+With the vanishing rate understood, we now seek to quantify the limiting
+shape observed in Fig.~\ref{shrink_intface}a.
 
 % Pozrikidis page 239: symmetric flow.
-Certain features of this shape can be predicted analytically by appealing to the principal of uniform stress distribution.
-In particular, consider the angle formed at the front and rear stagnation points.
-In long time, the stress becomes uniform, in particular in a small vicinity of this front angle in which body curvature can be ignored.
-Zooming in on the front angle, we can consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$.
-Exact solutions can be obtained to this problem via separation of variables in polar coordinates $(r, \theta)$ \cite{poz1997}.
-In this section alone, $\theta$ denotes the polar angle and not the tangent angle of the body.
-The corresponding stream function is assumed to take the form $\psi = r^{\lambda}f(\theta)$, with $\Delta^2 \psi = 0$, which gives the 4th order ODE \cite{poz1997}
-\begin{equation}
+Certain features of this shape can be predicted analytically by
+appealing to the principal of uniform stress distribution. In
+particular, consider the angle formed at the front and rear stagnation
+points. In long time, the stress becomes uniform, in particular in a
+small vicinity of this front angle in which body curvature can be
+ignored. Zooming in on the front angle, we can consider the problem of
+Stokes flow around an infinite wedge of opening angle $\oangle$. Exact
+solutions can be obtained to this problem via separation of variables in
+polar coordinates $(r, \theta)$~\cite{poz1997}. In this section alone,
+$\theta$ denotes the polar angle and not the tangent angle of the body.
+The corresponding stream function is assumed to take the form $\psi =
+r^{\lambda}f(\theta)$, with $\Delta^2 \psi = 0$, which gives the 4th
+order ODE~\cite{poz1997}
+\begin{align*}
   f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0
-\end{equation}
-This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down symmetry of the flow).
-The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\thb)$.
-Thus, the wedge of uniform stress corresponds to $\lambda = 2$.
-For this value, the solution for $f$ satisfying odd symmetry is
-\begin{equation}
+\end{align*}
+This ODE is subject to no-slip boundary conditions along the wedge
+$f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the
+condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down
+symmetry of the flow).  The corresponding shear stress evaluated on the
+surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\thb)$. Thus, the
+wedge of uniform stress corresponds to $\lambda = 2$. For this value,
+the solution for $f$ satisfying odd symmetry is
+\begin{align*}
   f(\theta) = B \sin (2 \theta) + C \theta
-\end{equation}
+\end{align*}
 Imposing the no-slip boundary conditions gives the condition
-\begin{equation}
+\begin{align*}
   \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0
-\end{equation}
-which has solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(\pi - \thb) \approx 102$ degrees.
-
-We aim to measure the opening angle in our simulation, but, curiously, the body vanishes before a steady-state is definitively reached.
-To obtain the true terminal shape, we could restart our simulation with the final eroded body scaled up and iterate this process until reaching steady state.
-A simpler solution, though, is to remove the effect of shrinking during the erosion process by simply modifying the normal velocity $\Vn$ to have zero mean
-\begin{equation}
+\end{align*}
+which has a solution $\thb \approx 129$ degrees. This gives an opening
+angle of $\oangle = 2(\pi - \thb) \approx 102$ degrees.
+
+We aim to measure the opening angle in our simulation, but, curiously,
+the body vanishes before a steady-state is definitively reached. To
+obtain the true terminal shape, we could restart our simulation with the
+final eroded body scaled up and iterate this process until reaching
+steady state. A simpler solution, though, is to remove the effect of
+shrinking during the erosion process by simply modifying the normal
+velocity $\Vn$ to have zero mean
+\begin{align*}
   \Vn \leftarrow \Vn - \mean{\Vn}
-\end{equation}
-This modification allows erosion to modify the body shape as it would normally, but artificially keeps the area of the body fixed.
-We show in Fig.~\ref{fixed_intface}a several interfaces at equally spaced times.
-Notice the body obtains the slender, football shape seen previously, but here more precision is available.
-We also show in Fig.~\ref{fixed_intface}b the stress, showing that the stress becomes much more evenly distributed as time proceeds.
-In this figure, time is normalized by the same vanishing time $t_f = 1.79E-2$ as the simulation shown in Fig.~\ref{shrink_intface}.
-Curiously, about 3 multiples of $t_f$ are required to reach a visually satisfying stead-state.
-This is very much in contrast to previous studies of erosion in high-Reynold's number flows, in which a reasonable steady-state was reached before the body vanished \cite{moo-ris-chi-zha-she2013}.
+\end{align*}
+This modification allows erosion to modify the body shape as it would
+normally, but artificially keeps the area of the body fixed. We show in
+Fig.~\ref{fixed_intface}a several interfaces at equally spaced times.
+Notice the body obtains the slender, football shape seen previously, but
+here more precision is available. We also show in
+Fig.~\ref{fixed_intface}b the stress, showing that the stress becomes
+much more evenly distributed as time proceeds. In this figure, time is
+normalized by the same vanishing time $t_f = 1.79E-2$ as the simulation
+shown in Fig.~\ref{shrink_intface}. Curiously, about 3 multiples of
+$t_f$ are required to reach a visually satisfying stead-state. This is
+very much in contrast to previous studies of erosion in high-Reynold's
+number flows, in which a reasonable steady-state was reached before the
+body vanished~\cite{moo-ris-chi-zha-she2013}.
 
@@
 
-The fixed-area simulations allow us to make precise measurements of the body's opening angle and aspect ratio as displayed in Fig.~\ref{fig:arangle}.
-Figure \ref{fig:arangle}a shows the aspect ratio, defined as the body's horizontal compared to its vertical width.
-The initial circular geometry has an aspect ratio of unity.
-As erosion causes the body to become more slender, the aspect ratio increases and tends to a value of $2.7$ in long time.
-Figure \ref{fig:arangle}b shows the body's opening angle, which we measure by fitting the tangent angle $\theta(\alpha)$ with a 7th degree polynomial over a region excluding the front/rear stagnation point (where there is high curvature that approximates an angle).
-The polynomial fit is then extrapolated to the stagnation point to get an angle estimate (subject to some uncertainty, which we estimate below).
-As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
-Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in long time.
-This coincides exactly with the valued predicted by our local solutions.
+The fixed-area simulations allow us to make precise measurements of the
+body's opening angle and aspect ratio as displayed in
+Fig.~\ref{fig:arangle}. Fig.~\ref{fig:arangle}a shows the aspect
+ratio, defined as the body's horizontal compared to its vertical width.
+The initial circular geometry has an aspect ratio of unity. As erosion
+causes the body to become more slender, the aspect ratio increases and
+tends to a value of $2.7$ in long time. Fig.~\ref{fig:arangle}b shows
+the body's opening angle, which we measure by fitting the tangent angle
+$\theta(\alpha)$ with a 7th degree polynomial over a region excluding
+the front/rear stagnation point (where there is high curvature that
+approximates an angle). The polynomial fit is then extrapolated to the
+stagnation point to get an angle estimate (subject to some uncertainty,
+which we estimate below). As seen in Fig.~\ref{fig:arangle}a, the
+opening angle is initially $180^\circ$, corresponding to the initially
+circular geometry. Erosion causes the angle to form after a short time,
+and the angle becomes increasingly sharp as it converges to the value
+$102^\circ$ in long time. This coincides exactly with the valued
+predicted by our local solutions.
 
@@
 
-To examine the influence of the smoothing parameters, $\eps$ and $\sigma$, we show in Table~\ref{table:arangle} the measurements of aspect ratio and opening angle for different simulations.
-We fix the total number of discretization points at $N_\iin = 1024$ and sequently reduce the smoothing with $\eps$ and $\sigma$ always equal.
-We choose the values $20/1024$, $10/1024$, and $5/1024$.
-Roughly, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively.
-As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$.
-We also estimate the uncertainty in the angle measurements by varying the region of the polynomial fit and the degree of the fit.
-As shown in the table, as the smoothing parameters are reduced, the angle measurements become more precise.
+To examine the influence of the smoothing parameters, $\eps$ and
+$\sigma$, we show in Table~\ref{table:arangle} the measurements of
+aspect ratio and opening angle for different simulations. We fix the
+total number of discretization points at $N_\iin = 1024$ and
+sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal.
+We choose the values $20/1024$, $10/1024$, and $5/1024$. Roughly, this
+corresponds to smoothing over the nearest 20, 10, and 5 grid points
+respectively. As seen in the table, the aspect ratio converges to a
+values of $2.65$ and the opening angle converges to $102^{\circ}$. We
+also estimate the uncertainty in the angle measurements by varying the
+region of the polynomial fit and the degree of the fit. As shown in the
+table, as the smoothing parameters are reduced, the angle measurements
+become more
+precise.
 
@@
 \begin{center}
-\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is 56\% of the vanishing time.
-GOOD TERM: Cauchy-convergence.} 
+\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is
+56\% of the vanishing time.  GOOD TERM: Cauchy-convergence.} 
 \caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is

### 2018-02-18 julia/thetalen.jl
The new time-stepping method passes the convergence test. It is 2nd order accurate.

@@ -69,9 +69,10 @@ function timestep!(thld0::ThLenDenType, thld_derivs::ThLenDenType,
 		# To advance theta, need zeta.
 		zeta0 = zetafun(len0,matau0)
 		zetad = zetafun(lend,mataud)
-		# The factors in the exponential smoothing.
+		# The first factor in the exponential smoothing.
 		fac1 = epsilon*dt1*zetad
 		
+		# The second factor, for which there are two possible approaches.
 		#fac2 = epsilon*dt2*0.5*(3*zetad-zeta0)	# Old Rule: uses trapezoid and midpoint combination.
 		fac2 = epsilon*dt2*(2*zetad-zeta0)		# New Rule: uses RK2 for everything.
 		

### 2018-02-18 docs/methods/erosion_methods.tex
Writing up the simpler time-stepping rule in the methods paper.
NM

@@
 use the {\thL} framework, with $\theta$ being the tangent angle and $L$
-the total arc length of a given boundary, and with the boundaries
+the total arc length of a given boundary. Each boundary is
 parameterized by normalized arc length $\alpha = 2 \pi s / L$.
@@
 \end{align*}
-We again compute the integrating factor, $\mu_k^{(n+1)}$ via the
-\todo[inline]{insert integration rule}, giving
-\begin{align*}
-\thhat_k^{(n+1)} = 
-& \thhat_k^{(n)}
-\exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
-& \Dt \, \hat{\NLterm}_k^{(n+1/2)}
-\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} -
-\elfun^{(n)} \right) \right).
-\end{align*}
+
+We compute the integrating factor with RK2 to get
+\begin{align}
+\thhat_k^{(n+1)} = & \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
+& \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
+\end{align}
+
+%We again compute the integrating factor, $\mu_k^{(n+1)}$ via the
+%\todo[inline]{insert integration rule}, giving
+%\begin{align*}
+%\thhat_k^{(n+1)} = & \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
+%& \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
+%\end{align*}
 

### 2018-02-19 docs/methods/erosion_methods.tex
Finally wrote the time-stepping section in a way that I am happy with. It is more elegant with applying RK2 directly to the argument of the integrating factor.

@@
 
-In addition to the curvature-dependent term in~\eqref{eqn:Vn}, we
-regularize boundary evolution by applying a narrow Gaussian filter to
-absolute shear stress
+In addition to the curvature-dependent term in~\eqref{eqn:Vn}, we regularize boundary evolution by applying a narrow Gaussian filter to absolute shear stress
 \begin{align*}
@@
 \end{align*}
-Here $\sigma$ is a small parameter that determines the width of the
-filter. The corresponding normal and tangential interface velocities are
-the given by
+Here $\sigma$ sets the width of the filter. The corresponding normal and tangential interface velocities are then given by
 \begin{align*}
@@
 %\label{eq:elfun}
-& \elfun = \frac{2 \pi  \mean{\atausig}}{L}.
+& \elfun = \frac{2 \pi}{L}  \mean{\atausig} \, .
 \end{align*}
@@
 
-We can evolve $\theta$ in spectral space since $\theta(\alpha)$ is
-periodic up to a jump of $2\pi$ for $\alpha \in [0,2\pi]$.  Therefore,
-we introduce the Fourier series
-\begin{align}
+We will evolve $\theta(\alpha)$ spectrally and so introduce the Fourier series
+\begin{align}
+\label{thetaSeries}
  \theta(\alpha,t) &= \alpha + \FourierSum \thhat_k e^{ i k \alpha}, \\
@@
 \end{align}
-The careful reader will notice that we have separated out the linear
-part of $\theta$, so that the remaining function is smooth and has a
-rapidly decaying Fourier series.  In spectral
-space,~\eqref{eqn:thetaevo2} produces the system of ODEs
+The careful reader will notice that in \eqref{thetaSeries}, we have decomposed $\theta(\alpha)$ into a linear component and a periodic component.
+In spectral space,~\eqref{eqn:thetaevo2} produces the system of ODEs
 \begin{align*}
@@
 \label{eqn:thetaevo3}
-& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \widehat{\NLterm}_k.
-\end{align}
-We solve system~\eqref{eqn:Levo3}--\eqref{eqn:thetaevo3} with an
-explicit, second-order Runge-Kutta method (RK2). In particular, we
-choose the {\em midpoint} RK2 method so as to maximize the smoothing
-effect of the curvature term.
-
-At the first stage of RK2 (the half step), we discretize
-equations~\eqref{eqn:Levo3}--\eqref{eqn:thetaevo3} as
-\begin{align}
-\label{eq:L12}
+& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \widehat{\NLterm}_k \, ,
+\qquad k = -N_\iin/2, \ldots, N_\iin/2 -1
+\end{align}
+We solve system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an
+explicit, second-order Runge-Kutta method (RK2). In particular, we choose the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature term.
+
+At the first stage of RK2 (the half step) we discretize \eqref{eq:mu}--\eqref{eqn:thetaevo3} as
+\begin{align}
+\label{eq:mu12d}
+& \mu_k^{(n+1/2)} = \mu_k^{(n)} \exp \left( \eps k^2 \frac{\Dt}{2} \zeta^{(n)} \right) \\
+\label{eq:L12d}
 & \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)} \\
-& \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \thhat_k^{(n)}}{\Dt/2} = \hat{\NLterm}_k^{(n)}
-\end{align}
-where the superscript indicates the time step. For simplicity, we have
-chosen the constant of integration in the exponent of
-equation~\eqref{eq:mu} so that $\mu_k^{(n)} = 1$. At the next stage of
-RK2, we must compute $\Mterm^{(n+1/2)}$ and
-$\widehat{\NLterm}_k^{(n+1/2)}$, which requires a call to the Stokes
-solver. Hence, we must compute $\mu_k^{(n+1/2)}$, so that
-$\thhat_k^{(n+1/2)}$ can be recovered and the geometry at the mid-step
-can be computed. To compute $\mu_k^{(n+1/2)}$, we use the left-end-point
-rule (first order, consistent with first forward Euler step of RK2)
-\begin{align*}
-\mu_k^{(n+1/2)} = \exp \left( \epsilon k^2 \frac{\Dt}{2}
-\elfun^{(n)}\right).
-\end{align*}
-It is instructive to recast as
-\begin{align*}
+\label{eq:th12d}
+& \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \mu_k^{(n)} \thhat_k^{(n)}}{\Dt/2} 
+= \mu_k^{(n)} \hat{\NLterm}_k^{(n)}
+\end{align}
+where the superscript indicates the time step.
+At the next stage of RK2 it will be necessary to evaluate derivates at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the shape of the bodies must be known through $\theta^{(n+1/2)}$.
+We therefore use \eqref{eq:mu12d} to solve \eqref{eq:th12d} for $\theta^{(n+1/2)}$, giving
+\begin{align}
+\label{eq:th12}
 \thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{\NLterm}_k^{(n)} \right)
 \exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
-\end{align*}
-so that the smoothing effect of the exponential is obvious. With
-$\thhat_k^{(n+1/2)}$ computed, it is now possible to compute
-$\Mterm^{(n+1/2)}$ and $\widehat{\NLterm}_k^{(n+1/2)}$.
-
-Next, at the second stage of RK2, we discretize as
-\begin{align*}
-\frac{L^{(n+1)} - L^{(n)}}{\Dt} &= \Mterm^{(n+1/2)}, \\
-\frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} &=
+\end{align}
+Since $\zeta >0$, the exponential term always acts to smooth the geometry and thus mitigate numerical instabilities.
+With the geometry at step $n+1/2$ known, a call to the Stokes solver allows one to compute the terms $\Mterm^{(n+1/2)}$, $\widehat{\NLterm}_k^{(n+1/2)}$, and $\zeta^{(n+1/2)}$.
+
+At the second stage of RK2, we discretize \eqref{eq:mu}--\eqref{eqn:thetaevo3} as 
+\begin{align}
+\label{eq:mu1d}
+& \mu_k^{(n+1)} = \mu_k^{(n)} \exp \left( \eps k^2 {\Dt} \, \zeta^{(n+1/2)} \right) \\
+\label{eq:L1d}
+& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)}, \\
+\label{eq:th1d}
+& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \mu_k^{(n)} \thhat_k^{(n)}}{\Dt} =
 \mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}.
-\end{align*}
-
-We compute the integrating factor with RK2 to get
-\begin{align}
-\thhat_k^{(n+1)} = & \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
-& \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
-\end{align}
-
-%We again compute the integrating factor, $\mu_k^{(n+1)}$ via the
-%\todo[inline]{insert integration rule}, giving
-%\begin{align*}
-%\thhat_k^{(n+1)} = & \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
-%& \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
-%\end{align*}
+\end{align}
+Once again, we must eventually compute the geometry at step $n+1$, and so we use \eqref{eq:mu1d} to solve \eqref{eq:th1d} for $\theta^{(n+1)}$, giving
+\begin{align}
+\thhat_k^{(n+1)} = & \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) + \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
+\end{align}
+Again, both exponential terms act to reduce high-frequency oscillations in shape.
 

### 2018-02-22 docs/methods/erosion_methods.tex
NM
Making minor changes to intro

@@
 \section{Introduction\label{s:intro}}
-Erosion is a fluid-mechanical process that is responsible for a variety
-of phenomena in geophysical fluids and other processes.  For example,
+Erosion is a fluid-mechanical process responsible for a variety
+of phenomena in geophysical and other settings.  For example,
 wind erosion causes sand dunes to be  longer on the windward
-side~\cite{han1969}, and erosion is responsible for branching structures
-of streams and rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  Erosion is
-also important in the biophysical community. Plaque erosion in arteries
+side~\cite{han1969}, while stream-bed erosion is responsible for branching structures
+of rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  Erosion is
+also important in biophysical applications, for example plaque erosion in arteries
 is key to understanding heart disease~\cite{sha2002,
@@
 reference is changed to \thL~variables so that the curvature term
-appears as a linear diffusive term that can easily be treated implicitly
+appears as a diffusive term that can easily be treated implicitly
 to avoid stiffness.
@@
 \end{align}
-Again, both exponential terms act to reduce high-frequency oscillations in shape.
+Again, both exponential terms act to reduce high-frequency oscillations in shape. We note that the above approach would generalize to higher-order Runge-Kutta methods, such as RK4.
 

### 2018-02-22 docs/methods/erosion_methods.tex
NM

@@
 by, first, introducing a tangential velocity field to maintain a grid
-that is equispaced in arclength, but that does not affect the dynamics,
+that is equispaced in arc length, but that does not affect the dynamics,
 and, second, a curvature penalization term.  Furthermore, the frame of
@@
 particularly insightful since it is identical to the shear stress on
-no-slip boundaries in the Stokesian limit.  Therefore, by computing the
+no-slip boundaries.  Therefore, by computing the
 vorticity, we are able to locate regions where the erosion rates will be
 fastest or slowest.
+
+\todo[inline]{Note: I took out 'in the Stokesian limit' because the vorticity matches the shear stress on the boundary no matter what the Reynolds number is.}
 
@@
 and the erosion rate (shear stress) are efficiently solved with spectral
-accuracy by using a fast multipole accelerated boundary integral
+accuracy by using a fast-multipole-accelerated boundary integral
 equation method.  Given the rate of erosion, the shape is integrated in
@@
 computed in Fourier space, resulting in spectral accuracy in space.
-Then, to further visualize the effect of erosion, we compute the
+To further visualize the effect of erosion, we compute the
 vorticity of the flow (Fig.~\ref{fig:50bodies}) to visualize regions
@@
 underlying mesh is refined to levels that are intractable. In future
-work we plan to consider mobile eroding bodies, but include a small
-force and torque so that unphysical contact is
-avoided~\cite{lu-rah-zor2017}.
+work we plan to consider mobile eroding bodies by including a small
+force and torque to prevent unphysical contact~\cite{lu-rah-zor2017}.
 
@@
 approximation.
+\todo[inline]{Appeal to separation of scales to justify this quasi-static approximation; i.e.~the timescale of erosion is much longer than that of the flow.}
+
 %A flow diagram is illustrated in Figure~\ref{fig:workflow}.  
@@
 computed.  Finally, in Section~\ref{sec:thetaL}, we describe how corners
-in the geometry are avoided and perform a change of coordinates that
-linearizes a stiff term.
+in the geometry are avoided and perform a change of coordinates to treat a stiff term.
+\todo[inline]{I took out all references to the stiff term being linear, because with the new scaling we use (computing the mean shear stress on each body) the diffusive term is actually nonlinear (because the mean shear stress depends on theta).
+Nonetheless, the integrating-factor method still works.}
 

### 2018-02-22 docs/methods/erosion_methods.tex
NM

@@
 normal at $\yy$, and $\eeta$ is an unknown density function.  The
-double-layer potential can not capture velocity fields corresponding to
+double-layer potential cannot capture velocity fields corresponding to
 rigid body motions~\cite{pow-mir1987}.  The rank deficiency is removed
@@
 removes the rank one null space that results from the compatibility
-constraint that results from the flux-free requirement of $\ff$.
+constraint associated with the flux-free requirement of $\ff$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Interface evolution in the {\thL} framework} 
+\subsection{Boundary evolution in the {\thL} framework} 
 \label{sec:thetaL}
 
-To handle boundary evolution, we use the {\thL} framework, which offers
-certain advantages in the ability to stabilize fluid-structure
+To evolve the boundaries, we use the {\thL} framework, which offers
+certain advantages in stabilizing fluid-structure
 interaction problems \cite{hou-low-she1994}. Throughout this section, we
@@
 (Fig.~\ref{fig:schematic}).
-
-For the sake of numerical stability, we modify the erosion law in
-equation~\eqref{eqn:erosionModel} to include a term that depends on the
-local curvature $\kappa$. The idea is to prevent regions of very high
-curvature. The modified normal velocity is 
+\todo[inline]{These conventions are probably already stated, right?}
+
+For numerical stability, we modify the erosion law \eqref{eqn:erosionModel} to include a term that depends on the local curvature $\kappa$. The idea is to prevent regions of very high
+curvature from developing, as these regions would reduce the accuracy of our fluid solver. We thus modify the normal velocity of each interface as follows
 \begin{align}
@@
 \end{align}
-Here, $\eps$ is a small parameter, $L$ is the total arc length of the
-body, and $\mean{\cdot}$ indicates a boundary mean. The second term on
-the right acts to smooth bodies with high-frequency oscillations by
-introducing a {\em curvature}-dependent component in the interface
-velocity. Since a closed body has a mean curvature of $\mean{\kappa} =
-2\pi / L$, the term in parentheses has mean zero. Thus, this term is
-area-preserving, so that the only material loss is due to the shear
-stress itself. In addition, we have scaled this term on the
-$\mean{\atau}$, the average absolute stress, so that it is always
-proportional to the true source of erosion $\atau$, even as bodies
-vanish. \todo[inline]{reword}
+The second term on the right is the curvature-dependent modification, the strength of which is controlled by the small parameter $\eps \ll 1$.
+Here, $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a boundary mean.
+This term causes regions of high curvature to recede more rapidly, thus smoothing any high-frequency oscillations that my exist.
+Since a closed body has mean curvature $\mean{\kappa} = 2\pi / L$, this smoothing term has mean zero and and thus preserves area.
+Therefore, the only source of material loss is the shear-stress itself.
+In addition, we have scaled the smoothing term on the mean absolute shear, $\mean{\atau}$, so that the ratio of smoothing-to-erosion always remains fixed, even as bodies vanish.
 

### 2018-02-22 docs/methods/erosion_methods.tex
NM

@@
 
-To evolve the boundaries, we use the {\thL} framework, which offers
-certain advantages in stabilizing fluid-structure
-interaction problems \cite{hou-low-she1994}. Throughout this section, we
-use the following conventions: the bodies are parametrized in the
-counterclockwise direction and the normal vector points into the bodies
-(Fig.~\ref{fig:schematic}).
+To evolve the boundaries, we use the {\thL} framework, which offers certain advantages in stabilizing fluid-structure interaction problems \cite{hou-low-she1994}. Throughout this section, we
+use the following conventions: the bodies are parametrized in the counterclockwise direction and the normal vector points into the bodies (Fig.~\ref{fig:schematic}).
 \todo[inline]{These conventions are probably already stated, right?}
@@
 For numerical stability, we modify the erosion law \eqref{eqn:erosionModel} to include a term that depends on the local curvature $\kappa$. The idea is to prevent regions of very high
-curvature from developing, as these regions would reduce the accuracy of our fluid solver. We thus modify the normal velocity of each interface as follows
+curvature from developing, as these regions would compromise the accuracy and stability of our fluid solver. We thus modify the normal velocity of each interface as follows
 \begin{align}
@@
 \end{align}
-Note that stiffest term in~\eqref{eqn:thetaevo1} involving the
-second-order derivative is {\em quasi-linear}. This is the key to the
-{\thL} method, and allows us to use very stable, implicit methods for
-this stiff term that are described in Section~\ref{sec:timeStepping}.
+System \eqref{eqn:Levo1}--\eqref{eqn:thetaevo1} comprise the main evolution equations that we will solve numerically in Section~\ref{sec:timeStepping}.
 

### 2018-02-22 docs/methods/erosion_methods.tex
NM

@@
 fastest or slowest.
-
-\todo[inline]{Note: I took out 'in the Stokesian limit' because the vorticity matches the shear stress on the boundary no matter what the Reynolds number is.}
 
@@
 
-With the shear stress computed, we are now ready to evolve the interface
-of each body using equations~\eqref{eqn:Levo1}
-and~\eqref{eqn:thetaevo1}. As described in Section~\ref{sec:thetaL}, we
-use the {\thL} framework, with $\theta$ being the tangent angle and $L$
-the total arc length of a given boundary. Each boundary is
-parameterized by normalized arc length $\alpha = 2 \pi s / L$.
+With the shear stress computed, we are now ready to evolve the boundary of each body using equations~\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1}.
+As described in Section~\ref{sec:thetaL}, we use the {\thL} framework, with $\theta$ being the tangent angle and $L$ the total arc length of a given boundary.
+Each boundary is parameterized by normalized arc length $\alpha = 2 \pi s / L$.
 
@@
 \end{align}
-Here $\NLterm$ represents the nonlinear terms (and nonlocal terms) in
-the PDE for $\theta$.
+Here $\NLterm$ represents the nonlinear terms (and nonlocal terms) in the PDE for $\theta$.
+
+\todo[inline]{Need to remind reader that the diffusive term comes from smoothing and that this is the stiff term that could potential cause numerical problems.}
 
@@
 \end{align*}
-Each ODE is first-order and linear (though variable-coefficient due to
-$\elfun$) and thus can be solved by using the integrating factor
+These ODEs can be solved by using the integrating factor
 \begin{align}
@@
 where the superscript indicates the time step.
-At the next stage of RK2 it will be necessary to evaluate derivates at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the shape of the bodies must be known through $\theta^{(n+1/2)}$.
-We therefore use \eqref{eq:mu12d} to solve \eqref{eq:th12d} for $\theta^{(n+1/2)}$, giving
+At the next stage of RK2 it will be necessary to evaluate derivates at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the body shapes must be known.
+We therefore insert \eqref{eq:mu12d} into \eqref{eq:th12d} and solve for $\theta^{(n+1/2)}$, giving
 \begin{align}
@@
 \thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{\NLterm}_k^{(n)} \right)
-\exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right)
+\exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right) \, .
 \end{align}
 Since $\zeta >0$, the exponential term always acts to smooth the geometry and thus mitigate numerical instabilities.
-With the geometry at step $n+1/2$ known, a call to the Stokes solver allows one to compute the terms $\Mterm^{(n+1/2)}$, $\widehat{\NLterm}_k^{(n+1/2)}$, and $\zeta^{(n+1/2)}$.
+With the geometry at step $n+1/2$ known, a call to the Stokes solver allows the computation of $\Mterm^{(n+1/2)}$, $\widehat{\NLterm}_k^{(n+1/2)}$, and $\zeta^{(n+1/2)}$.
 
@@
 \end{align}
-Once again, we must eventually compute the geometry at step $n+1$, and so we use \eqref{eq:mu1d} to solve \eqref{eq:th1d} for $\theta^{(n+1)}$, giving
+Once again, we must eventually compute the geometry at step $n+1$, and so we insert \eqref{eq:mu1d} into \eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
 \begin{align}
@@
 \end{align}
-Again, both exponential terms act to reduce high-frequency oscillations in shape. We note that the above approach would generalize to higher-order Runge-Kutta methods, such as RK4.
+Again, both exponential terms act to smooth high-frequency oscillations in shape. We note that the above approach would generalize to higher-order Runge-Kutta methods, such as RK4.
 
@@
 We start by computing the vorticity $w(\xx) = v_x - u_y$ for $\xx \in
-\Omega$.  As we did for the shear stress, we compute the vorticity due
+\Omega$.  
+\todo[inline]{Shouldn't we use $\omega$ (lower-case omega) for vorticity?}
+As we did for the shear stress, we compute the vorticity due
 to the double-layer potential, Stokeslets, and rotlets individually.
@@
 \label{sec:drag}
-\todo[inline]{check all signs in this section.  Fortran code assumes a
-normal pointing into the eroding body and a tangent vector that
-corresponds to a couterclockwise parameterization}
 With the pressure and shear stress, the drag on a single body with
@@
 \begin{align}
-  F_D = \int_{\gamma_\ell} (-p \nn + \tau \ss)\,ds.
+  F_D = \int_{\gamma_\ell} p \nn + \tau \ss \,ds.
   \label{eqn:drag}
 \end{align}
+The reader may notice an unusual sign convention for pressure in this formula, which is simply due to the normal direction pointing {\em into} the bodies.
 
@@
 
-Fig.~\ref{01bodseq} shows the erosion of a single body, numerically
+Figure \ref{01bodseq} shows the erosion of a single body, numerically
 simulated with $N_\iin = 1024$ discretization points and shown at three
 evenly spaced times. Here, color represents the vorticity of the
-surrounding flow, which, when evaluated on the boundary, indicates the
+surrounding flow, which, when evaluated on the boundary, corresponds to the
 shear stress and thus the local erosion rate. As seen in the left-most
@@
 geometry. As shown in the third snapshot, this corner persists as the
-bodies becomes even more slender while wasting away. In this simulation,
+bodies becomes even more slender and continues to shrink. In this simulation,
 the body completely vanishes at a final time of $t_f = 1.79E-2$.
@@
 interfaces are color-coded by normalized time $t/t_f$. The body seems to
-converge to a shape that resembles an American football---a fairly
+converge to a shape that resembles an American football --- a fairly
 slender, for-aft symmetric shape with corners at the front and back.
@@
 
-Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that
+A brief look at Fig.~\ref{shrink_intface}(a) reveals that
 the spacing between successive interfaces becomes larger as the body
@@
 to body scale $L$. This law must be modified in two dimensions, though.
-The modification (made non-trivial by subtleties of the Stokes paradox)
-can be correctly deduced by noting that, as the body vanishes, its drag
-must be consistent with slender-body theory. For a slender body in flow
-perpendicular to its long-axis $W \gg L$, the drag is proportional to
+The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory. 
+\todo[inline]{Here: add slender citations}
+For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to
 $\mu \umax W/ \log(W/L)$. This relationship implies that, for a 2D
-cross-section perpendicular to the long axis, the stress (per unit $W$)
-can be estimated by
+cross-section, the stress per unit span can be estimated by
 \begin{align}
@@
 \end{align}
-In interpreting our 2D simulations, we will treat $W$ as fixed with the
+In interpreting our 2D simulations, we will treat the span, $W$, as fixed with the
 requirement $W \gg L$.
 
-Now, the body's rate of area reduction is given by integrating the
+The body's rate of area reduction is given by integrating the
 absolute shear stress around the boundary
@@
 \end{align*}
-giving the exact relationship
+which gives the exact relationship
 \begin{align*}

### 2018-02-22 docs/methods/erosion_methods.tex
NM

@@
 consider flows that are confined by a solid wall $\Gamma$ that encloses
-$M$ eroding bodies.  The bodies are denoted as $\gamma_\ell$,
-$\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup
-\gamma_M$.  Neglecting inertial forces, the dynamics of the fluid is
+$M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.  The bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.
+On each body, $\nn$ and $\ss$ denote the unit normal and unit tangent vectors respectively.
+Throughout the paper, we adopt the convention that $\ss$ points in the counterclockwise direction and $\nn$ points out of the fluid domain (i.e.~into the bodies).
+Neglecting inertial forces, the dynamics of the fluid is
 fully characterized by the position of the bodies $\xx_\ell(s,t) \in
@@
 \end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
-normal at $\yy$, and $\eeta$ is an unknown density function.  The
+where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  The
 double-layer potential cannot capture velocity fields corresponding to
@@
 \end{align*}
+\todo[inline]{Check the sign with the Fortran code.}
 where $\ss$ and $\nn$ are the unit tangent and normal vectors,
@@
 
-To evolve the boundaries, we use the {\thL} framework, which offers certain advantages in stabilizing fluid-structure interaction problems \cite{hou-low-she1994}. Throughout this section, we
-use the following conventions: the bodies are parametrized in the counterclockwise direction and the normal vector points into the bodies (Fig.~\ref{fig:schematic}).
-\todo[inline]{These conventions are probably already stated, right?}
+To evolve the boundaries, we use the {\thL} framework, which offers certain advantages in stabilizing fluid-structure interaction problems \cite{hou-low-she1994}.
 

### 2018-02-22 docs/methods/erosion_methods.tex
NM

@@
 \begin{align*}
-  \tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss,
-\end{align*}
-\todo[inline]{Check the sign with the Fortran code.}
-where $\ss$ and $\nn$ are the unit tangent and normal vectors,
-respectively (Fig.~\ref{fig:schematic}).  The velocity field of the
+  \tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss \, .
+\end{align*}
+The reader may notice an unusual sign convention above, but this is simply a consequence of our conventions for $\nn$ and $\ss$ (see Fig.~\ref{fig:schematic}). 
+The velocity field of the
 completed double-layer potential~\eqref{eqn:completed_DLP} involves
@@
 \label{sec:vorticity}
-We start by computing the vorticity $w(\xx) = v_x - u_y$ for $\xx \in
-\Omega$.  
-\todo[inline]{Shouldn't we use $\omega$ (lower-case omega) for vorticity?}
-As we did for the shear stress, we compute the vorticity due
+We start by computing the vorticity $\omega(\xx) = v_x - u_y$ for $\xx \in
+\Omega$.  As we did for the shear stress, we compute the vorticity due
 to the double-layer potential, Stokeslets, and rotlets individually.
@@
 \begin{align}
-  w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
+  \omega^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
     \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}
@@
 \begin{align*}
-  w^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
+  \omega^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
     \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2},
@@
 \begin{align*}
-  w(\xx) = w^\DD(\xx) + w^S(\xx).
+  \omega(\xx) = \omega^\DD(\xx) + \omega^S(\xx).
 \end{align*}
@@
 For the Stokes equations, on boundaries that have a no-slip boundary
-condition, the shear stress is equivalent to the vorticity $w = v_x -
+condition, the shear stress is equivalent to the vorticity $\omega = v_x -
 u_y$.  Therefore, we do not need to compute the vorticity for $\xx \in
@@
 \begin{align}
-  F_D = \int_{\gamma_\ell} p \nn + \tau \ss \,ds.
+  \FD = \int_{\gamma_\ell} p \nn + \tau \ss \,ds.
   \label{eqn:drag}

### 2018-02-24 docs/methods/erosion_methods.tex
Added tracking of surface mean

@@
 \end{align}
-The second term on the right is the curvature-dependent modification, the strength of which is controlled by the small parameter $\eps \ll 1$.
+The second term on the right is the curvature-dependent modification, the strength of which is controlled by the parameter $\eps \ll 1$.
 Here, $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a boundary mean.
@@
 System \eqref{eqn:Levo1}--\eqref{eqn:thetaevo1} comprise the main evolution equations that we will solve numerically in Section~\ref{sec:timeStepping}.
+In addition, it is necessary to track a reference point for each body, so that the variables $\theta$ and $L$ can be converted back into a cartesian grid.
+We choose to track the coordinates of the surface mean $\mean{\xx}$, which moves according to
+\begin{align}
+\frac{d}{dt} \mean{\xx} = \mean{ V_s \ss + V_n \nn }
+\end{align}
+Tracking the surface mean is somewhat simpler than tracking the center of mass, but either choice would be valid.
 

### 2018-02-24 docs/methods/erosion_methods.tex
Adding some references

@@
 \section{Introduction\label{s:intro}}
+
 Erosion is a fluid-mechanical process responsible for a variety
@@
 gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can
-be explained by erosion~\cite{pic-van-hei2000}.  Another application,
+be explained by erosion~\cite{pic-van-hei2000}. 
+Much recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}.
+These processes can be linked conceptually as `sculpting with flow' \cite{ristroph2018sculpting}.
+
+Another application,
 which motivates the current work, is erosion caused by groundwater flow.
@@
 System \eqref{eqn:Levo1}--\eqref{eqn:thetaevo1} comprise the main evolution equations that we will solve numerically in Section~\ref{sec:timeStepping}.
+
 In addition, it is necessary to track a reference point for each body, so that the variables $\theta$ and $L$ can be converted back into a cartesian grid.
@@
 \begin{align}
+\label{eq:xsurf}
 \frac{d}{dt} \mean{\xx} = \mean{ V_s \ss + V_n \nn }
@@
 \end{align}
-Again, both exponential terms act to smooth high-frequency oscillations in shape. We note that the above approach would generalize to higher-order Runge-Kutta methods, such as RK4.
+Again, both exponential terms act to smooth high-frequency oscillations in shape.
+We note that the above approach would generalize to higher-order Runge-Kutta methods, such as RK4.
+Finally, we track the reference point $\mean{x}$ of each body by simply discretizing \eqref{eq:xsurf} with the same RK2 method.
 
@@
 
-A brief look at Fig.~\ref{shrink_intface}(a) reveals that
-the spacing between successive interfaces becomes larger as the body
-shrinks, suggesting that the overall shear stress is growing. Of course,
-such a relationship is consistent with the well-known 3D Stokes drag
-law, $\tau \sim \mu \umax / L$, since stress is inversely proportional
-to body scale $L$. This law must be modified in two dimensions, though.
-The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory. 
+Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing.
+This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / L$, since stress is inversely proportional to body scale $L$.
+This law must be modified in two dimensions, though.
+The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012}.
 \todo[inline]{Here: add slender citations}

### 2018-02-24 docs/methods/erosion_methods.tex
NM

@@
 Much recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}.
-These processes can be linked conceptually as `sculpting with flow' \cite{ristroph2018sculpting}.
+All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow' \cite{ristroph2018sculpting}.
 
@@
 \label{sec:bies}
-Here we describe a boundary integral equation to solve the fluid
-equations. In particular, we solve the incompressible Stokes equations
+
+In this section, we describe the boundary integral equations employed for the fluid
+equations \cite{Moore2007}
+\todo[inline]{Bryan do you want to add a bunch of references to your boundary integral papers here (or somewhere else)?}
+In particular, we solve the incompressible Stokes equations
 with Dirichlet boundary conditions 
@@
 This law must be modified in two dimensions, though.
-The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012}.
+The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012, zhao2015transportation}.
 \todo[inline]{Here: add slender citations}

### 2018-02-25 docs/methods/erosion_methods.tex
Editing paper

@@
 in the geometry are avoided and perform a change of coordinates to treat a stiff term.
-\todo[inline]{I took out all references to the stiff term being linear, because with the new scaling we use (computing the mean shear stress on each body) the diffusive term is actually nonlinear (because the mean shear stress depends on theta).
-Nonetheless, the integrating-factor method still works.}
 
@@
 
-Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing.
+Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress is growing as the body vanishes.
 This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / L$, since stress is inversely proportional to body scale $L$.
@@
 The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012, zhao2015transportation}.
-\todo[inline]{Here: add slender citations}
 For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to
@@
 \begin{align*}
-  \dot{A} = \int_{\gamma} \atau \, ds \, ,
-\end{align*}
-which gives the exact relationship
-\begin{align*}
-  \dot{A} = \mean{\atau} L \, .
+  \dot{A} = \int_{\gamma} \atau \, ds \,  = \mean{\atau} L \, .
 \end{align*}
 Thus, the area-loss rate is given by the product of the mean shear
-$\mean{\atau}$ and the total perimeter $L$. Inserting the scaling
-law~\eqref{eqn:stresslaw} gives
+$\mean{\atau}$ and the total perimeter $L$. Inserting scaling law~\eqref{eqn:stresslaw} gives
 \begin{align*}
@@
 \end{align*}
-This ODE is subject to no-slip boundary conditions along the wedge
-$f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the
-condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down
-symmetry of the flow).  The corresponding shear stress evaluated on the
-surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\thb)$. Thus, the
-wedge of uniform stress corresponds to $\lambda = 2$. For this value,
-the solution for $f$ satisfying odd symmetry is
+This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down symmetry of the flow).
+The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\thb)$.
+Thus, the wedge of uniform stress corresponds to $\lambda = 2$.
+For this value, the solution for $f$ satisfying odd symmetry is
 \begin{align*}
@@
 \end{align*}
-which has a solution $\thb \approx 129$ degrees. This gives an opening
-angle of $\oangle = 2(\pi - \thb) \approx 102$ degrees.
-
-We aim to measure the opening angle in our simulation, but, curiously,
-the body vanishes before a steady-state is definitively reached. To
-obtain the true terminal shape, we could restart our simulation with the
-final eroded body scaled up and iterate this process until reaching
-steady state. A simpler solution, though, is to remove the effect of
-shrinking during the erosion process by simply modifying the normal
-velocity $\Vn$ to have zero mean
+which has a solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(\pi - \thb) \approx 102$ degrees.
+
+We aim to measure the opening angle in our simulation, but, curiously, the body vanishes before a steady-state is definitively reached.
+To obtain the true terminal shape, we could restart our simulation with the final eroded body scaled up and iterate this process until reaching steady state.
+A simpler solution, though, is to remove the effect of shrinking during the erosion process by simply modifying the normal velocity $\Vn$ to have zero mean
 \begin{align*}
@@
 \end{align*}
-This modification allows erosion to modify the body shape as it would
-normally, but artificially keeps the area of the body fixed. We show in
-Fig.~\ref{fixed_intface}a several interfaces at equally spaced times.
-Notice the body obtains the slender, football shape seen previously, but
-here more precision is available. We also show in
-Fig.~\ref{fixed_intface}b the stress, showing that the stress becomes
-much more evenly distributed as time proceeds. In this figure, time is
-normalized by the same vanishing time $t_f = 1.79E-2$ as the simulation
-shown in Fig.~\ref{shrink_intface}. Curiously, about 3 multiples of
-$t_f$ are required to reach a visually satisfying stead-state. This is
-very much in contrast to previous studies of erosion in high-Reynold's
-number flows, in which a reasonable steady-state was reached before the
-body vanished~\cite{moo-ris-chi-zha-she2013}.
+This modification allows erosion to modify the body shape as it would normally, but artificially keeps the area of the body fixed.
+We show in Fig.~\ref{fixed_intface}a several interfaces at equally spaced times.
+Notice the body obtains the slender, football shape seen previously, but here more precision is available.
+We also show in Fig.~\ref{fixed_intface}b the stress, showing that the stress becomes much more evenly distributed as time proceeds.
+In this figure, time is normalized by the same vanishing time $t_f = 1.79E-2$ as the simulation shown in Fig.~\ref{shrink_intface}.
+Curiously, about 3 multiples of $t_f$ are required to reach a visually satisfying stead-state.
+This is very much in contrast to previous studies of erosion in high-Reynold's number flows, in which an approximate steady-state was reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
 

### 2018-02-25 docs/methods/erosion_methods.tex
NM

@@
 \includegraphics[width = 0.80 \textwidth]{./figs/01bodseq.pdf}
-\caption{\label{01bodseq} A single body eroding in Stokes flow. As the
-body erodes, it develops a corner at its front and rear stagnation
-points, while remaining for-aft symmetric due to time-reversibility.
-Color indicates the vorticity of the surrounding flow, which, when
-evaluated on the boundary, gives the local shear stress. In this
-simulation, we use $N_\iin = 1024$ discretization points on the body,
-$N_\out = 1024$ points on the outer boundary, a time-step of $\Dt =
-1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma =
-10/1024$.}
+\caption{A single body eroding in Stokes flow.
+As the body erodes, it develops a corner at its front and rear stagnation points, while remaining for-aft symmetric due to time-reversibility.
+Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress.
+In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
+\label{01bodseq} 
 \end{center}
@@
 \includegraphics[width = 0.75 \textwidth]{./figs/shrink_intface.pdf}
-\caption{\label{shrink_intface} Shape and stress evolution. (a)
-Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced
-time intervals. Color indicates normalized time, $t/t_f$, where $t_f =
-1.79E-2$ is the time at which the body completely vanishes. (b) The
-distribution of absolute shear stress, $\atau$, along each of these
-interfaces. Normalized arc length, $s/L$, runs counterclockwise from the
-rear stagnation point. The stress initially varies over the body's
-surface, but becomes more uniform over time.}
+\caption{
+Shape and stress evolution.
+(a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
+Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes.
+(b) The distribution of absolute shear stress, $\atau$, along each of these interfaces.
+Normalized arc length, $s/L$, runs counterclockwise from the rear stagnation point.
+The stress initially varies over the body's surface, but becomes more uniform over time.}
+\label{shrink_intface}
 \end{center}
@@
 \subsection{Scaling law for the vanishing rate}
+\label{sec:scaling}
 
@@
 
-The body's rate of area reduction is given by integrating the
-absolute shear stress around the boundary
-\begin{align*}
-  \dot{A} = \int_{\gamma} \atau \, ds \,  = \mean{\atau} L \, .
-\end{align*}
-Thus, the area-loss rate is given by the product of the mean shear
-$\mean{\atau}$ and the total perimeter $L$. Inserting scaling law~\eqref{eqn:stresslaw} gives
-\begin{align*}
-  \dot{A} \sim \frac{\mu \umax}{\log(W/L)} \, .
-\end{align*}
-Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
-\begin{align*}
-  A (1 - \log A) = \areaconst (t_f - t)
-\end{align*}
-where $c_A$ is a constant.
-This is an {\em implicit} relationship for how the area scales down in time during erosion.
-In Fig.~6a, we show the body area as a function of time measured in the simulation
-against the above scaling law with $\areaconst = 0.42$.
-
-\todo[inline]{Explain the drag here too}
-
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
+The body's rate of area reduction is given by integrating the absolute shear stress around the boundary
+\begin{align*}
+  \dot{A} = \int_{\gamma} \atau \, ds \,  = \mean{\atau} L \, .
+\end{align*}
+Thus, the area-loss rate is given by the product of the mean shear
+$\mean{\atau}$ and the total perimeter $L$. Inserting scaling law~\eqref{eqn:stresslaw} gives
+\begin{align*}
+  \dot{A} \sim \frac{\mu \umax}{\log(W/L)} \, .
+\end{align*}
+Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
+\begin{align*}
+  A (1 - \log A) = \areaconst (t_f - t)
+\end{align*}
+where $c_A$ is a constant.
+This is an {\em implicit} relationship for how the area scales down in time during erosion.
+In Fig.~6a, we show the body area as a function of time measured in the simulation against the above scaling law with $\areaconst = 0.42$.
+
+\todo[inline]{Explain the drag here too}
+
 \subsection{The limiting shape}
 
-With the vanishing rate understood, we now seek to quantify the limiting
-shape observed in Fig.~\ref{shrink_intface}a.
-
-% Pozrikidis page 239: symmetric flow.
-Certain features of this shape can be predicted analytically by
-appealing to the principal of uniform stress distribution. In
-particular, consider the angle formed at the front and rear stagnation
-points. In long time, the stress becomes uniform, in particular in a
-small vicinity of this front angle in which body curvature can be
-ignored. Zooming in on the front angle, we can consider the problem of
-Stokes flow around an infinite wedge of opening angle $\oangle$. Exact
-solutions can be obtained to this problem via separation of variables in
-polar coordinates $(r, \theta)$~\cite{poz1997}. In this section alone,
-$\theta$ denotes the polar angle and not the tangent angle of the body.
-The corresponding stream function is assumed to take the form $\psi =
-r^{\lambda}f(\theta)$, with $\Delta^2 \psi = 0$, which gives the 4th
-order ODE~\cite{poz1997}
+With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
+Certain features of this shape can be predicted analytically by appealing to the principal that, in long time, the shear stress becomes uniformly distributed along the body.
+In particular, consider the angle formed at the front and rear stagnation points.
+In a small region around this point, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge.
+We aim to determine the wedge's opening angle, $\oangle$, through the principle of uniform stress.
+Exact solutions can be obtained to this problem via separation of variables in polar coordinates $(r, \theta)$~\cite{poz1997}.
+In this section alone, $\theta$ denotes the polar coordinate (not the local tangent angle along the body).
+The corresponding stream function is assumed to take the form $\psi = r^{\lambda}f(\theta)$, with $\Delta^2 \psi = 0$, which gives the 4th order ODE~\cite{poz1997}
 \begin{align*}
@@
 \end{align*}
-which has a solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(\pi - \thb) \approx 102$ degrees.
-
-We aim to measure the opening angle in our simulation, but, curiously, the body vanishes before a steady-state is definitively reached.
-To obtain the true terminal shape, we could restart our simulation with the final eroded body scaled up and iterate this process until reaching steady state.
-A simpler solution, though, is to remove the effect of shrinking during the erosion process by simply modifying the normal velocity $\Vn$ to have zero mean
-\begin{align*}
-  \Vn \leftarrow \Vn - \mean{\Vn}
-\end{align*}
-This modification allows erosion to modify the body shape as it would normally, but artificially keeps the area of the body fixed.
-We show in Fig.~\ref{fixed_intface}a several interfaces at equally spaced times.
-Notice the body obtains the slender, football shape seen previously, but here more precision is available.
-We also show in Fig.~\ref{fixed_intface}b the stress, showing that the stress becomes much more evenly distributed as time proceeds.
-In this figure, time is normalized by the same vanishing time $t_f = 1.79E-2$ as the simulation shown in Fig.~\ref{shrink_intface}.
-Curiously, about 3 multiples of $t_f$ are required to reach a visually satisfying stead-state.
-This is very much in contrast to previous studies of erosion in high-Reynold's number flows, in which an approximate steady-state was reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
+which has a solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(180^{\circ} - \thb) \approx 102$ degrees. 
+% Pozrikidis page 239: symmetric flow.
+
+We note that this uniform-stress shape is closely related to the so-called `optimal profile in Stokes flow' found by Pironneau (1973) \cite{pir1973}, who determined the shape that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume (see also \cite{mon-lau2015} for an interesting related shape).
+Pironneau's 3D shape has an opening angle of $120^{\circ}$ and ours is simply the 2D counterpart with its slightly different $102^{\circ}$ opening angle.
+Previous numerical simulations on erosion in 3D Stokes flow revealed that, in long time, an eroding body tends to a shape that is approximately (though not precisely) Pironneau's optimal profile \cite{mit-spa2016}.
+
+To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations.
+However, our simulations lose accuracy just at the final moments before the body vanishes as a result of the shear stress blowing up (in accordance with the scaling laws discussed in Section \ref{sec:scaling}).
+To circumvent this problem, we could restart our simulation with a scaled-up version of the the near-final  body as the initial condition, and iterate this process until convergence.
+A simpler solution, though, is to remove the effect of shrinking by modifying the normal velocity $\Vn$ to have zero mean,
+\begin{align*}
+  \Vn \leftarrow \Vn - \mean{\Vn} \, .
+\end{align*}
+This modification allows erosion sculpt the body as it would normally, but artificially keeps the area fixed.
+We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process at equally-spaced times.
+Notice the body obtains a similar profile as observed previously, but with fixed area.
+Importantly, more numerical accuracy is now available to quantify the terminal state.
+The inset in Fig.~\ref{fixed_intface}(a) shows a zoom of the body's rear stagnation point, demonstrating that the near-corner is actually smooth on a fine scale, in accordance with our numerical smoothing.
+
+Figure~\ref{fixed_intface}(b) shows the stress distribution on the evolving body, revealing that stress becomes more uniform as time proceeds.
+Interestingly, the slight rise in shear near the front/rear corners that was seen in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that the effect was due to loss of accuracy.
+Here, time is normalized by the same vanishing time $t_f = 1.79E-2$ as in Fig.~\ref{shrink_intface}.
+Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynold's-number erosion, where a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
 
@@
 
-The fixed-area simulations allow us to make precise measurements of the
-body's opening angle and aspect ratio as displayed in
-Fig.~\ref{fig:arangle}. Fig.~\ref{fig:arangle}a shows the aspect
-ratio, defined as the body's horizontal compared to its vertical width.
-The initial circular geometry has an aspect ratio of unity. As erosion
-causes the body to become more slender, the aspect ratio increases and
-tends to a value of $2.7$ in long time. Fig.~\ref{fig:arangle}b shows
-the body's opening angle, which we measure by fitting the tangent angle
-$\theta(\alpha)$ with a 7th degree polynomial over a region excluding
-the front/rear stagnation point (where there is high curvature that
-approximates an angle). The polynomial fit is then extrapolated to the
-stagnation point to get an angle estimate (subject to some uncertainty,
-which we estimate below). As seen in Fig.~\ref{fig:arangle}a, the
-opening angle is initially $180^\circ$, corresponding to the initially
-circular geometry. Erosion causes the angle to form after a short time,
-and the angle becomes increasingly sharp as it converges to the value
-$102^\circ$ in long time. This coincides exactly with the valued
-predicted by our local solutions.
-
-\todo[inline]{Also point to figure 7a, with the smoothed out corner}
+The fixed-area simulations allow us to precisely measure the body's opening angle and aspect ratio as displayed in Fig.~\ref{fig:arangle}.
+Fig.~\ref{fig:arangle}a shows the aspect ratio, defined as the body's horizontal compared to its vertical width.
+The initial circular geometry has an aspect ratio of unity.
+As erosion causes the body to become more slender, the aspect ratio increases and tends to a value of $2.7$ in long time.
+Fig.~\ref{fig:arangle}b shows the body's opening angle, which we measure by fitting the tangent angle $\theta(\alpha)$ with a 7th degree polynomial over a region excluding the front/rear stagnation point (where a near-corner is approximated by a smooth curve of very high curvature).
+The polynomial fit is then extrapolated to the stagnation point to get an angle estimate (subject to some uncertainty, which we estimate below).
+As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
+Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in long time.
+This coincides exactly with the valued predicted by our local solutions.
 
@@
 
-To examine the influence of the smoothing parameters, $\eps$ and
-$\sigma$, we show in Table~\ref{table:arangle} the measurements of
-aspect ratio and opening angle for different simulations. We fix the
-total number of discretization points at $N_\iin = 1024$ and
-sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal.
-We choose the values $20/1024$, $10/1024$, and $5/1024$. Roughly, this
-corresponds to smoothing over the nearest 20, 10, and 5 grid points
-respectively. As seen in the table, the aspect ratio converges to a
-values of $2.65$ and the opening angle converges to $102^{\circ}$. We
-also estimate the uncertainty in the angle measurements by varying the
-region of the polynomial fit and the degree of the fit. As shown in the
-table, as the smoothing parameters are reduced, the angle measurements
-become more
-precise.
+To examine the influence of the smoothing parameters, $\eps$ and $\sigma$, we show in Table~\ref{table:arangle} the measurements of aspect ratio and opening angle for different simulations.
+We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal.
+We choose the values $20/1024$, $10/1024$, and $5/1024$.
+Loosely, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively.
+As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$.
+We also estimate the uncertainty in the angle measurements by varying the region of the polynomial fit and the degree of the fit.
+As shown in the table, as the smoothing parameters are reduced, the angle measurements become more precise.
 
@@
 
-\vsp{30}
+\subsection{Convergence tests}
+
+As a final validation, we now aim to verify the second-order convergence rate (in time) of our method.
+To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} to a stopping time of $t_s = 1E-2$, which is 56\% of the time it takes for the body to vanish completely.
+By this time, the body has eroded substantially, but is not so small that accuracy is lost.
+We assess error by measuring the difference between simulations of successive resolution (i.e.~we verify Cauchy convergence).
+In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time, $t_s$, while successively doubling the temporal resolution.
+Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations.
+The table confirms that our method to converges with second-order accuracy.
 
@@
 \begin{center}
-\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is
-56\% of the vanishing time.  GOOD TERM: Cauchy-convergence.} 
-\caption{Convergence test: the stopping time is $t_s =$ 1E-2, which is
-56\% of the vanishing time.
+\caption{Convergence test: we run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution.
+The tests confirm the method to be second-order accurate in time.
 }
@@
 
-In the table, we measure the error in the shape by computing the L2-difference of the interfaces.
+\vsp{30}
 

### 2018-02-25 docs/methods/erosion_methods.tex
NM

@@
 
-As a final validation, we now aim to verify the second-order convergence rate (in time) of our method.
+As a final validation, we now aim to verify the second-order temporal convergence rate of our method.
 To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} to a stopping time of $t_s = 1E-2$, which is 56\% of the time it takes for the body to vanish completely.
 By this time, the body has eroded substantially, but is not so small that accuracy is lost.
-We assess error by measuring the difference between simulations of successive resolution (i.e.~we verify Cauchy convergence).
-In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time, $t_s$, while successively doubling the temporal resolution.
+We assess error by measuring the difference between simulations of successive temporal resolution (i.e.~we verify Cauchy convergence).
+In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time, $t_s$, while successively halving the timestep $\Delta t$.
 Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations.
@@
 \hline
-1/100	& 4.69E-6		& --		\\
-1/200	& 1.26E-6		& 1.90	\\
-1/400	& 3.26E-7		& 1.95	\\
-1/800	& 8.28E-8		& 1.98	\\
-1/1600	& 2.09E-8		& 1.99	\\
-1/3200	& 5.26E-9		& 1.99	\\
+%
+1/50		& 1.68E-5		& --		\\
+1/100	& 4.84E-6		& 1.79	\\
+1/200	& 1.30E-6		& 1.90	\\
+1/400	& 3.36E-7		& 1.95	\\
+1/800	& 8.54E-8		& 1.98	\\
+1/1600	& 2.15E-8		& 1.99	\\
+1/3200	& 5.40E-9		& 1.99	\\
 1/6400	& --			& --		\\
+%
 \hline
@@
 % epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0
+
+\todo[inline]{Could put CPU time in table too}
 

### 2018-02-26 docs/methods/erosion_methods.tex
Modified codes for convergence test to output CPU time too.

@@
 
-Figure \ref{01bodseq} shows the erosion of a single body, numerically
-simulated with $N_\iin = 1024$ discretization points and shown at three
-evenly spaced times. Here, color represents the vorticity of the
-surrounding flow, which, when evaluated on the boundary, corresponds to the
-shear stress and thus the local erosion rate. As seen in the left-most
-snapshot, the body is initially circular and has the strongest vorticity
-above and below it. The flow is for-aft symmetric as a result of the
-time-reversibility of the Stokes equations, with vorticity vanishing at
-the body's front and rear stagnation points. At the next instance, the
-body has lost material due to erosion, but remains for-aft symmetric due
-to the flow symmetry. The greatest material loss has occurred at the
-body's top and bottom, where shear is strongest. Interestingly, the body
-has developed well-defined corners at its front and rear stagnation
-points. This geometric feature is a consequence of the erosion law,
-which depends on the {\em absolute} shear stress: wherever the stress
-vanishes, $\atau$ exhibits a corner, which manifests as a corner in the
-geometry. As shown in the third snapshot, this corner persists as the
-bodies becomes even more slender and continues to shrink. In this simulation,
-the body completely vanishes at a final time of $t_f = 1.79E-2$.
-
-To better understand the shape evolution, Fig.~\ref{shrink_intface}(a)
-shows several superimposed interfaces at evenly spaced times. The
-interfaces are color-coded by normalized time $t/t_f$. The body seems to
-converge to a shape that resembles an American football --- a fairly
-slender, for-aft symmetric shape with corners at the front and back.
-Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress,
-$\atau$, is distributed along each of these interfaces. The normalized
-arc length $s/L$ runs counterclockwise around the body, with $s/L = 0$
-corresponding to the rear stagnation point and $s/L = 0.5$ the front
-stagnation point. At early times (yellow to orange), the stress is
-distributed non-uniformly, with highest values at the top and bottom of
-the body. As time proceeds, though, the stress becomes more evenly
-distributed along the body's surface (red). As the body nears the final
-stages of erosion (dark red), the stress actually becomes slightly
-higher near the stagnation points. A close look reveals that {\em at}
-the stagnation points, the stress always vanishes, though in a region
-that becomes increasingly narrow.
+Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times.
+Here, color represents the vorticity of the surrounding flow, which, when evaluated on the boundary, corresponds to the shear stress and thus the local erosion rate.
+As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it.
+The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points.
+At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
+The greatest material loss has occurred at the body's top and bottom, where shear is strongest.
+Interestingly, the body has developed well-defined corners at its front and rear stagnation points.
+This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry.
+As shown in the third snapshot, this corner persists as the bodies becomes even more slender and continues to shrink.
+In this simulation, the body completely vanishes at a final time of $t_f = 1.79E-2$.
+
+To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
+The interfaces are color-coded by normalized time $t/t_f$.
+The body seems to converge to a shape that resembles an American football --- a fairly slender, for-aft symmetric shape with corners at the front and back.
+Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
+The normalized arc length $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point.
+At early times (yellow to orange), the stress is distributed non-uniformly, with highest values at the top and bottom of the body.
+As time proceeds, though, the stress becomes more evenly distributed along the body's surface (red).
+As the body nears the final stages of erosion (dark red), the stress actually becomes slightly higher near the stagnation points.
+A close look reveals that {\em at} the stagnation points, the stress always vanishes, though in a region that becomes increasingly narrow.
 
@@
 \caption{
-Shape and stress evolution.
-(a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
+Shape and stress evolution: (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
 Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes.
@@
 \includegraphics[width = 0.8 \textwidth]{./figs/fixed_intface.pdf}
-\caption{One body fixed area}
+\caption{Fixed-area simulations: (a) Interfaces of a body eroding under shear stress but with the area artifically kept constant.
+Inset: zoom near the rear stagnation point, showing that the corner is actually smooth on a fine scale.
+(b) The stress distribution on the surface of the body.
+Over time, the stress becomes more uniform.}
 \label{fixed_intface}
@@
 As a final validation, we now aim to verify the second-order temporal convergence rate of our method.
-To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} to a stopping time of $t_s = 1E-2$, which is 56\% of the time it takes for the body to vanish completely.
-By this time, the body has eroded substantially, but is not so small that accuracy is lost.
+To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with $N_\iin=128$) to a stopping time of $t_s = 1E-2$.
+This stopping time is 56\% of the time it takes for the body to vanish completely, so that the body has eroded substantially, but is not so small that accuracy is lost.
 We assess error by measuring the difference between simulations of successive temporal resolution (i.e.~we verify Cauchy convergence).
@@
 \begin{center}
-\caption{Convergence test: we run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution.
+\caption{Convergence test: We run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution.
 The tests confirm the method to be second-order accurate in time.
@@
 \label{convtab}
-\begin{tabular}{c l l}
+\begin{tabular}{l l l l}
 \hline
-\hspace{0.5pc} $\Delta t/t_s$
+\hspace{0.0pc} $\Delta t/t_s$
 \hspace{0.5pc} & error 
-\hspace{0.5pc} & order \\
+\hspace{0.5pc} & order
+\hspace{0.5pc} & CPU time \\
 \hline
 %
-1/50		& 1.68E-5		& --		\\
-1/100	& 4.84E-6		& 1.79	\\
-1/200	& 1.30E-6		& 1.90	\\
-1/400	& 3.36E-7		& 1.95	\\
-1/800	& 8.54E-8		& 1.98	\\
-1/1600	& 2.15E-8		& 1.99	\\
-1/3200	& 5.40E-9		& 1.99	\\
-1/6400	& --			& --		\\
+1/50		& 1.68E-5		& --		& 55 secs		\\
+1/100	& 4.84E-6		& 1.79	& 1.8 mins		\\
+1/200	& 1.30E-6		& 1.90	&	\\
+1/400	& 3.36E-7		& 1.95	&	\\
+1/800	& 8.54E-8		& 1.98	&	\\
+1/1600	& 2.15E-8		& 1.99	&	\\
+1/3200	& 5.40E-9		& 1.99	&	\\
+1/6400	& --			& --		&	\\
 %

### 2018-02-26 docs/methods/erosion_methods.tex
NM

@@
 
-As a final validation, we now aim to verify the second-order temporal convergence rate of our method.
-To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with $N_\iin=128$) to a stopping time of $t_s = 1E-2$.
-This stopping time is 56\% of the time it takes for the body to vanish completely, so that the body has eroded substantially, but is not so small that accuracy is lost.
+As a final validation, we now aim to verify that our method converges with the predicted second order rate in time.
+To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=128$) to a stopping time of $t_s = 1E-2$.
+This stopping time is 56\% of the vanishing time and was chosen so that the body will have eroded substantially, but is not so small that accuracy is lost.
 We assess error by measuring the difference between simulations of successive temporal resolution (i.e.~we verify Cauchy convergence).
@@
 The table confirms that our method to converges with second-order accuracy.
+In the table, we also show the CPU time of the simulation run on a single processor (though the algorithm is easily parallelized).
 
@@
 1/100	& 4.84E-6		& 1.79	& 1.8 mins		\\
-1/200	& 1.30E-6		& 1.90	&	\\
-1/400	& 3.36E-7		& 1.95	&	\\
-1/800	& 8.54E-8		& 1.98	&	\\
-1/1600	& 2.15E-8		& 1.99	&	\\
-1/3200	& 5.40E-9		& 1.99	&	\\
-1/6400	& --			& --		&	\\
+1/200	& 1.30E-6		& 1.90	& 3.5 mins		\\
+1/400	& 3.36E-7		& 1.95	& 7.2 mins		\\
+1/800	& 8.54E-8		& 1.98	& 14 mins (?)	\\
+1/1600	& 2.15E-8		& 1.99	& 28 mins (?)	\\
+1/3200	& 5.40E-9		& 1.99	& 56 mins (?)	\\
+1/6400	& --			& --		& 1.9 hours(?)	\\
 %
@@
 % epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0
-
-\todo[inline]{Could put CPU time in table too}
 

### 2018-02-26 docs/methods/erosion_methods.tex
NM

--- 2018-02-26 docs/methods/erosion_methods.tex
@@
 All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow' \cite{ristroph2018sculpting}.
-
-Another application,
-which motivates the current work, is erosion caused by groundwater flow.
+% Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.
+
+Another application, which motivates the current work, is erosion caused by groundwater flow.
 Here, a slow moving fluid erodes channels in the ground, and this
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary evolution in the {\thL} framework} 
+\subsection{Boundary evolution in the {\thL} framework and regularization} 
 \label{sec:thetaL}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%-----------------------------------------------------------------%%
+% RESULTS SECTION
+%%-----------------------------------------------------------------%%
 \section{Results}
@@
 
-\subsection{Shape evolution of a single eroding body}
+\subsection{A single body eroding in Stokes flow}
 
@@
 
-\subsection{The limiting shape}
+\subsection{Local analysis for the limiting shape}
 
@@
 
-\subsection{Convergence tests}
-
-As a final validation, we now aim to verify the second-order temporal convergence rate of our method.
-To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with $N_\iin=128$) to a stopping time of $t_s = 1E-2$.
-This stopping time is 56\% of the time it takes for the body to vanish completely, so that the body has eroded substantially, but is not so small that accuracy is lost.
-We assess error by measuring the difference between simulations of successive temporal resolution (i.e.~we verify Cauchy convergence).
-In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time, $t_s$, while successively halving the timestep $\Delta t$.
+\subsection{Convergence test}
+
+As a final validation, we now aim to verify that our method converges with second-order accuracy in time.
+To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 1E-2$.
+This stopping time is 56\% of the time it takes the body to vanish, and was chosen so that the body will have eroded substantially but is not so small that accuracy is lost.
+We assess error by measuring the difference between simulations of successive resolutions (i.e.~we verify Cauchy convergence).
+In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time.
+At each stage we halve the timestep $\Delta t$.
 Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations.
 The table confirms that our method to converges with second-order accuracy.
+In the table, we also show the CPU time of the simulation run on a single processor (though the algorithm is easily parallelized), showing a linear increase in computational time.
 
@@
 1/100	& 4.84E-6		& 1.79	& 1.8 mins		\\
-1/200	& 1.30E-6		& 1.90	&	\\
-1/400	& 3.36E-7		& 1.95	&	\\
-1/800	& 8.54E-8		& 1.98	&	\\
-1/1600	& 2.15E-8		& 1.99	&	\\
-1/3200	& 5.40E-9		& 1.99	&	\\
-1/6400	& --			& --		&	\\
+1/200	& 1.30E-6		& 1.90	& 3.5 mins		\\
+1/400	& 3.36E-7		& 1.95	& 7.2 mins		\\
+1/800	& 8.54E-8		& 1.98	& 15 mins		\\
+1/1600	& 2.15E-8		& 1.99	& 30 mins (?)	\\
+1/3200	& 5.40E-9		& 1.99	& 60 mins (?)	\\
+1/6400	& --			& --		& 2.0 hours(?)	\\
 %
@@
 
-\todo[inline]{Could put CPU time in table too}
+\subsection{Multiple-body simulations}
+With the numerical method validated, we are now ready to simulate the erosion of multiple bodies.
+
+Possible list:
+\begin{itemize}
+\item Show multiple body simulation with fixed flow rate
+\item Then simulation with fixed pressure drop
+\end{itemize}
 
@@
   \begin{itemize}
-    \item Aspect ratio and opening angle
     \item Drag and resistivity
-    \item Anisotropy
-    \item Vorticity
   \end{itemize}

### 2018-02-26 docs/TexNotes/Notes.tex
Still working
Working hard
NM

--- 2017-10-14 docs/TexNotes/Notes.tex
@@
 \begin{equation}
-\theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha}
+\theta(\alpha,t) = 2 \pi \alpha + \sum_{k = -\infty}^{\infty} \thhat_k(t) e^{2\pi i k \alpha}
 \end{equation}
-Then we get
+where $2 \pi \alpha$ is the linear part and does not depend on time. Then we get
 \begin{equation}
+\label{thODEs}
 \tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
@@
 \begin{equation}
-\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
+\mu_k = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
 \end{equation}
-so that the solution can be represented as
+so that our system becomes
 \begin{align}
-\thhat_k(t) & = \frac{1}{\mu} \int^t \mu \hat{N}_k dt'
-= \thhat_k(0) + \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun dt'' \right) \hat{N}_k \, dt'
-% LONGER FORM
-%& = \exp \left( -4 \eps \pi^2 k^2 \int_0^t \elfun(L) ds \right) \, 
-%\int_0^t \exp \left( 4 \eps \pi^2 k^2 \int_0^s \elfun(L) ds' \right) \hat{N}_k ds \\
+\label{Leq}
+& \tderiv{L}{t} = M \\
+\label{theq}
+& \tderiv{}{t}\left( \mu_k \theta_k \right) = \mu_k \hat{N}_k
 \end{align}
-where $t'$ and $t''$ are simply dummy variables for integration. We can get the exact relationship
-\begin{equation}
-\thhat_k(t + \Delta t) = \thhat_k(t) 
-+ \int_t^{t+\Delta t} \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^{t+\Delta t} \elfun dt'' \right) \hat{N}_k \, dt'
-\end{equation}
-
-\subsection{How to scale smoothing parameters?}
-We have two smoothing parameters: $\eps$ and $\sigma$.
-How should they scale with the simulation resolution parameters?
-The most important resolution parameter is $N$, the total number of points on each body, but there is also $\Delta t$ and maybe some others.
-Figuring out $\sigma$ is the easier part: $\sigma$ is a lengthscale and should go like $1/N$.
-On the other hand, $\eps$ is a diffusivity in dimensions.
-I did a calculation and found that $\eps$ should scale like $2/(\pi^2 N^2)$.
-
-The calculation is based on looking at Eq.~?, where $\sigma_1 \sim 2 \pi \sqrt{\eps \Delta t}$.
-For the largest wavenumbers, $k_{max} \sim N/2$, we want the smoothing to beat the nonlinear term (so that overall, these modes decay).
-So we need $e^{-\pi^2 \eps \Delta t N^2 / 2} < 1 - C\Delta t$, which gives $\eps > 2C/(\pi^2 N^2)$, independent of $\Delta t$.
-If $C=1$, this gives roughly $\eps > 0.2/ N^2$.
-However, this analysis did not take into account how the spectrum of the nonlinear term decays (or maybe it even grows???)
+We discretize Eqs.~(\ref{Leq})--(\ref{theq}) with a second-order Runge-Kutta method (the midpoint RK2). See the methods paper for details.
 
@@
 % END CENTER OF MASS
-
-\subsection{Benchmark the interface evolution}
-It would be good to test the interface evolution, in particular verify that the curvature-driven-flow (CDF) is 2nd order accurate in time.
-Initially, I thought I would be able to get exact solutions for CDF, but it turns out that the PDE (\ref{thetaEvolve}) does not reduce to simply a diffusion equation, but instead still has nonlinear terms, thus making exact solutions impractical.
-I also tried to recast CDF in polar coordinates for star-shapes, but still the governing PDE is not simple enough to get exact solutions.
-Also, in the $\theta$-$L$ formulation I tried to determine the normal velocity to make the nonlinear terms vanish, but this does not appear possible either.
-Instead, I can do a completely numerical convergence test.
 

### 2018-02-26 docs/methods/erosion_methods.tex
NM

@@
   \label{eqn:stresslaw}
-  \tau \sim \frac{\mu \umax}{L \log(W/L)}.
+  \tau \sim \frac{\mu \umax}{L \log(W/L)} \qquad \text{as } L \to 0 \, .
 \end{align}
@@
 \begin{align*}
-  \dot{A} = \int_{\gamma} \atau \, ds \,  = \mean{\atau} L \, .
+  \dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
 \end{align*}
@@
 
-To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations.
-However, our simulations lose accuracy just at the final moments before the body vanishes as a result of the shear stress blowing up (in accordance with the scaling laws discussed in Section \ref{sec:scaling}).
-To circumvent this problem, we could restart our simulation with a scaled-up version of the the near-final  body as the initial condition, and iterate this process until convergence.
-A simpler solution, though, is to remove the effect of shrinking by modifying the normal velocity $\Vn$ to have zero mean,
-\begin{align*}
-  \Vn \leftarrow \Vn - \mean{\Vn} \, .
-\end{align*}
-This modification allows erosion sculpt the body as it would normally, but artificially keeps the area fixed.
-We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process at equally-spaced times.
-Notice the body obtains a similar profile as observed previously, but with fixed area.
-Importantly, more numerical accuracy is now available to quantify the terminal state.
-The inset in Fig.~\ref{fixed_intface}(a) shows a zoom of the body's rear stagnation point, demonstrating that the near-corner is actually smooth on a fine scale, in accordance with our numerical smoothing.
-
-Figure~\ref{fixed_intface}(b) shows the stress distribution on the evolving body, revealing that stress becomes more uniform as time proceeds.
-Interestingly, the slight rise in shear near the front/rear corners that was seen in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that the effect was due to loss of accuracy.
-Here, time is normalized by the same vanishing time $t_f = 1.79E-2$ as in Fig.~\ref{shrink_intface}.
-Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynold's-number erosion, where a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
-
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 \begin{center}
-\includegraphics[width = 0.8 \textwidth]{./figs/fixed_intface.pdf}
+\includegraphics[width = 0.85 \textwidth]{./figs/fixed_intface.pdf}
 \caption{Fixed-area simulations: (a) Interfaces of a body eroding under shear stress but with the area artifically kept constant.
@@
 
-The fixed-area simulations allow us to precisely measure the body's opening angle and aspect ratio as displayed in Fig.~\ref{fig:arangle}.
-Fig.~\ref{fig:arangle}a shows the aspect ratio, defined as the body's horizontal compared to its vertical width.
-The initial circular geometry has an aspect ratio of unity.
-As erosion causes the body to become more slender, the aspect ratio increases and tends to a value of $2.7$ in long time.
-Fig.~\ref{fig:arangle}b shows the body's opening angle, which we measure by fitting the tangent angle $\theta(\alpha)$ with a 7th degree polynomial over a region excluding the front/rear stagnation point (where a near-corner is approximated by a smooth curve of very high curvature).
-The polynomial fit is then extrapolated to the stagnation point to get an angle estimate (subject to some uncertainty, which we estimate below).
-As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
-Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in long time.
-This coincides exactly with the valued predicted by our local solutions.
+To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations.
+However, our simulations lose accuracy just in the final moments as the body is vanishing due to the shear stress blowing up (in accordance with the scaling laws discussed in Section \ref{sec:scaling}).
+To circumvent this problem, we could restart our simulation with a scaled-up version of the the near-final  body as the initial condition and iterate the process until convergence.
+A simpler solution, though, is to remove the effect of shrinking by modifying the normal velocity $\Vn$ to have zero mean,
+\begin{align*}
+  \Vn \leftarrow \Vn - \mean{\Vn} \, .
+\end{align*}
+This modification allows erosion sculpt the body as it normally would but artificially keeps the area fixed.
+We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process at equally-spaced times.
+Notice the body obtains a similar profile as observed previously, but with fixed area.
+Importantly, more numerical accuracy is now available to quantify the terminal state.
+The inset in Fig.~\ref{fixed_intface}(a) shows a zoom of the body's rear stagnation point, demonstrating that the near-corner is actually smooth on a fine scale, in accordance with our numerical smoothing.
+Likewise, Fig.~\ref{fixed_intface}(b) shows the stress distribution on the evolving body, revealing that stress becomes more uniform as time proceeds.
+Interestingly, the slight rise in shear near the front/rear corners that was seen in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that the effect was due to loss of accuracy.
+Here, time is normalized by the same vanishing time $t_f = 1.79E-2$ as in Fig.~\ref{shrink_intface}.
+Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynold's-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
 
@@
 \begin{center}
-\includegraphics[width = 0.8 \textwidth]{./figs/arangle.pdf}
-\caption{Aspect ratio and opening angle}
+\includegraphics[width = 0.85 \textwidth]{./figs/arangle.pdf}
+\caption{Shape characteristics of an eroding body: (a) The aspect ratio, defined as the width to height, versus time.
+(b) The measured opening angle versus time.
+For both measurements, we show three cases of the smoothing parameters: $\eps = \sigma = 20/1024$, $\eps = \sigma = 10/1024$, and $\eps = \sigma = 5/1024$.
+In the most resolved simulation (the case 5/1024) the aspect ratio converges to 2.7 and the opening angle converges to the predicted value of $102^{\circ}$.}
 \label{fig:arangle}
@@
 % Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+The fixed-area simulations allow for us to precisely measure characteristics of the shape.
+In particular, Fig.~\ref{fig:arangle} shows measurements of the body's aspect ratio (its width to height) and the front opening angle as they vary in time.
+We show these measurements for three simulations in which the smoothing parameters, $\eps$ and $\sigma$, are sequentially reduced, allowing us to assess convergence in these parameters.
+As shown in Fig.~\ref{fig:arangle}(a), the aspect ratio begins at one for the initial circular geometry and increases in time as erosion sculpts a more slender shape.
+The aspect ratio reaches a long time limit of about 2.7 in the most resolved simulation.
+Fig.~\ref{fig:arangle}b shows the body's opening angle, which we measure by fitting the tangent angle $\theta(\alpha)$ with a 7th degree polynomial over a region excluding the front/rear stagnation point (where a near-corner is approximated by a smooth curve of very high curvature).
+The polynomial fit is then extrapolated to the stagnation point to obtain an angle estimate (subject to some uncertainty, which we estimate below).
+As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
+Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in the most resolved simulation.
+This coincides exactly with the valued predicted by our local solutions.
 

### 2018-02-26 docs/TexNotes/Notes.tex
NM

@@
 \subsection{The vanishing rate of the area}
+
+The area loss rate is given by
+\begin{align}
+\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
+\end{align}
+The above is an exact relation. Substitution of the scaling law gives
+\begin{align}
+\dot{A} \sim \frac{ - \mu V}{\log(W/L)} \, .
+\end{align}
+Inserting $A \sim L^2$ and rearranging gives
+\begin{align}
+\log (C_2 A/W^2) dA = C_1 \mu V dt
+\end{align}
+Integrating gives
+\begin{align}
+A \left(1 - \log(C_2 A/W^2) \right) = C_1 \mu U (t_f - t)
+\end{align}
+In the limit of $A \to 0$, the log-term on the left-hand-side will win, giving
+\begin{align}
+A(1 - \log(A) ) \sim c_A (t_f - t)
+\end{align}
+I have kept the one above, just so the graph of the scaling law doesn't look funny for bigger $A$.
+
+\vsp{5}
+TO KILL:
+
 The rate of area loss is given by

### 2018-02-26 docs/methods/erosion_methods.tex
NM

@@
 \begin{center}
-\includegraphics[width = 0.8 \textwidth]{./figs/area_drag.pdf}
-\caption{One body}
-\label{}
+\includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
+\caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction \eqref{area_predict} (dotted red).
+The two are nearly indistinguishable.
+(b) The horizontal drag (black) on the body as it erodes, along with the viscous (green) and pressure (blue) contributions.
+The scaling prediction can be rearranged to give estimate \eqref{viscdrag} for the viscous drag (dotted red).}
+\label{area_drag}
 \end{center}
@@
 The body's rate of area reduction is given by integrating the absolute shear stress around the boundary
-\begin{align*}
+\begin{align}
 \dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
-\end{align*}
+\end{align}
 Thus, the area-loss rate is given by the product of the mean shear
 $\mean{\atau}$ and the total perimeter $L$. Inserting scaling law~\eqref{eqn:stresslaw} gives
-\begin{align*}
-  \dot{A} \sim \frac{\mu \umax}{\log(W/L)} \, .
-\end{align*}
+\begin{align}
+\dot{A} \sim \frac{ - \mu \umax}{\log(W/L)} \quad \text{as } L \to 0 \, . 
+\end{align}
 Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
-\begin{align*}
-  A (1 - \log A) = \areaconst (t_f - t)
-\end{align*}
-where $c_A$ is a constant.
+\begin{align}
+\label{area_predict}
+A (c_1 - \log A) \sim c_2 (t_f - t) \qquad \text{as } t \to t_f \, .
+\end{align}
+where $c_1$ and $c_2$ are constants.
 This is an {\em implicit} relationship for how the area scales down in time during erosion.
-In Fig.~6a, we show the body area as a function of time measured in the simulation against the above scaling law with $\areaconst = 0.42$.
-
-\todo[inline]{Explain the drag here too}
+In Fig.~\ref{area_drag}a, we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 =2.2$ and $c_2 = 30$.
+The comparison shows close agreement between the two (they are indistinguishable).
+
+In Fig.~\ref{area_drag}(b), we show the drag $F_D$ measured on the body as it erodes.
+The drag decreases gradually, then takes a nose dive in the final moments when the body vanishes, as is consistent with the logarithmic dependence on lengthscale $L$ in 2D Stokes flow.
+We also show in the figure the separate contributions of the viscous and the pressure drag.
+As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
+\begin{align}
+\label{viscdrag}
+F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
+\end{align}
+This scaling law is shown in the figure (red, dotted curve) and shows good agreement with the viscous drag.
+Of course, \eqref{viscdrag} is less accurate than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.
 

### 2018-02-26 docs/methods/erosion_methods.tex
NM

@@
 \begin{center}
-\includegraphics[width = 0.75 \textwidth]{./figs/shrink_intface.pdf}
+\includegraphics[width = 0.8 \textwidth]{./figs/shrink_intface.pdf}
 \caption{
@@
 \end{align*}
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.4 \textwidth]{./figs/corner.pdf}
+\caption{2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function $\psi(r,\theta)$ for $\theta \in [-\theta_0, \theta_0]$}.
+\label{corner}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+
 This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down symmetry of the flow).

### 2018-02-26 docs/methods/erosion_methods.tex
NM

@@
 \title{Viscous Erosion in Porous Media}
+
+% OTHER TITLE POSSIBILITIES
+% A fast and accurate method for viscous erosion in a 2D porous medium
 
@@
 
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
+\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
+viscous flow.  The boundary conditions are a constant pressure drop that
+creates a flow from the left to right.  The rate of erosion is
+proportional to the shear stress which is equivalent to the vorticity
+evaluated on the bodies.  The colors represent the vorticity, so regions
+with large vorticity (in magnitude) are regions where the flow will
+erode the fastest.}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure generated from data file 50circ512p5, 
+%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
+
 To create high-fidelity and computationally efficient numerical methods,
@@
 concluding remarks are made in Section~\ref{s:conclusions}
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
-\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
-viscous flow.  The boundary conditions are a constant pressure drop that
-creates a flow from the left to right.  The rate of erosion is
-proportional to the shear stress which is equivalent to the vorticity
-evaluated on the bodies.  The colors represent the vorticity, so regions
-with large vorticity (in magnitude) are regions where the flow will
-erode the fastest.}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure generated from data file 50circ512p5, 
-%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
 
@@
 bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.
+
 \begin{figure}[htpb]
@@
 \begin{center}
-\includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
+\includegraphics[width = 0.85 \textwidth]{./figs/area_drag.pdf}
 \caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction \eqref{area_predict} (dotted red).
@@
 (b) The measured opening angle versus time.
-For both measurements, we show three cases of the smoothing parameters: $\eps = \sigma = 20/1024$, $\eps = \sigma = 10/1024$, and $\eps = \sigma = 5/1024$.
-In the most resolved simulation (the case 5/1024) the aspect ratio converges to 2.7 and the opening angle converges to the predicted value of $102^{\circ}$.}
+For both measurements, we show three cases of the smoothing parameters: $\eps = \sigma = 20/1024, 10/1024,$ and 5/1024.
+In the most resolved simulation (5/1024) the aspect ratio converges to 2.7 and the opening angle converges to the predicted value of $102^{\circ}$ in long time.}
 \label{fig:arangle}

### 2018-02-26 docs/methods/erosion_methods.tex
NM

@@
 \begin{center}
-\caption{Convergence test: We run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution.
+\caption{Convergence test: We run single-body erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$-difference in shapes obtained with successive temporal resolutions.
 The tests confirm the method to be second-order accurate in time.

### 2018-02-26 docs/methods/erosion_methods.tex
NM

@@
 %
-1/50		& 1.68E-5		& --		& 55 secs		\\
+1/50		& 1.68E-5		& --		& 53 secs     	\\
 1/100	& 4.84E-6		& 1.79	& 1.8 mins   	\\
 1/200	& 1.30E-6		& 1.90	& 3.5 mins  	\\
-1/400	& 3.36E-7		& 1.95	& 7.2 mins		\\
-1/800	& 8.54E-8		& 1.98	& 15 mins		\\
-1/1600	& 2.15E-8		& 1.99	& 30 mins (?)	\\
-1/3200	& 5.40E-9		& 1.99	& 60 mins (?)	\\
-1/6400	& --			& --		& 2.0 hours(?)	\\
+1/400	& 3.36E-7		& 1.95	& 6.9 mins  	\\
+1/800	& 8.54E-8		& 1.98	& 14 mins   	\\
+1/1600	& 2.15E-8		& 1.99	& 28 mins  	\\
+1/3200	& 5.40E-9		& 1.99	& 56 mins    	\\
+1/6400	& --			& --		& 111 mins	\\
 %

### 2018-02-27 docs/methods/erosion_methods.tex
NM

@@
 This scaling law is shown in the figure (red, dotted curve) and shows good agreement with the viscous drag.
-Of course, \eqref{viscdrag} is less accurate than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.
+Of course, \eqref{viscdrag} is less exact than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.
 

### 2018-02-27 docs/methods/erosion_methods.tex
NM

@@
 \includegraphics[width = 0.4 \textwidth]{./figs/corner.pdf}
-\caption{2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function $\psi(r,\theta)$ for $\theta \in [-\theta_0, \theta_0]$}.
+\caption{Schematic of 2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function $\psi(r,\theta)$ for $\theta \in [-\theta_0, \theta_0]$}.
 \label{corner}

### 2018-02-27 docs/methods/erosion_methods.tex
NM
Adding GMRES count table

@@
 The tests confirm the method to be second-order accurate in time.
+The last column shows the measured CPU time which increases linearly as the time-step is refined.
 }
@@
 \subsection{Multiple-body simulations}
+
 With the numerical method validated, we are now ready to simulate the erosion of multiple bodies.
-
+We make one important conceptual change to our model.
+For a realistic porous medium composed of many solid bodies, the condition of a fixed incoming flow rate $\umax$ is somewhat artificial.
+A more realistic condition is that the pressure difference from one end to another is held fixed.
+For example, in groundwater flow, this condition would correspond to a recharge region of given hydraulic head connecting to a discharge region of another hydraulic head.
+
+We therefore impose the condition of a fixed pressure difference by controlling the incoming flow-rate $\umax$ at each time-step.
+This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed, then measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies.
+These upstream and downstream pressures are given by
+\begin{align}
+& p_{-} = \frac{1}{2} \int_{-1}^{1} p(-2,y) \, dy \, , \\
+& p_{+} = \frac{1}{2} \int_{-1}^{1} p(+2,y) \, dy \, .
+\end{align}
+We then rescale the computed density function by the pressure difference
+\begin{align}
+\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})} \, ,
+\end{align}
+This rescaling maintains a {\em fixed} pressure difference.
+Because the Stokes equations are linear, such a rescaling is permissible and does not alter the accuracy of our method.
+Furthermore, rescaling by a different factor at each time-step is also permissible because the Stokes equations are memoryless (i.e.~there is no time derivative present in the PDEs).
+
+Briefly, to confirm that the rescaling does not alter accuracy, we show HERE a convergence test for 20 bodies with the condition of a fixed pressure drop.
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.9 \textwidth]{./figs/06bod.pdf}
+\caption{\label{fig:50bodies} 6 bodies
+}
+%A time lapse of 50 bodies eroding in a viscous flow.
+The boundary conditions are a constant pressure drop that creates a flow from the left to right.
+The rate of erosion is proportional to the shear stress which is equivalent to the vorticity evaluated on the bodies.
+The colors represent the vorticity, so regions with large vorticity (in magnitude) are regions where the flow will erode the fastest.
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure generated from data file 50circ512p5, 
+%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
+
+\vsp{10}
+
+% Table
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{table}%[htbp]
+\begin{center}
+\caption{GMRES Iterations
+}
+\vspace{0.3 pc}
+\label{itertab}
+\begin{tabular}{c c | c c}
+\hline
+\hspace{0.0pc} Number of bodies
+\hspace{0.5pc} & GMRES iterations 
+\hspace{0.5pc} & aaa
+\hspace{0.5pc} & bbb \\
+\hline
+%
+10	& 223	& a	& b	\\
+15	& 292	& a	& b	\\
+20	& 363	& a	& b	\\
+30	& 496	& a	& b	\\
+40	& 676	& a	& b	\\
+50	& 991	& a	& b	\\
+%
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% In these tests I always use 128 points per body.
+
+\vsp{10}
 Possible list:
@@
 \item Then simulation with fixed pressure drop
-\end{itemize}
-
-\vsp{30}
-
-% NEWPAGE
-\newpage
-
-Runs to do
+\item GMRES counts
+%
+\item $\bigO(5-10)$ bodies
 	\begin{itemize}
-  \item Single body
-  \begin{itemize}
-    \item Drag and resistivity
-  \end{itemize}
-  \item $\bigO(5)$ bodies
-  \begin{itemize}
-    \item Drag and resistivity
-    \item Anisotropy
+	\item Area and Drag
 	\item Long channels between flat faces
-    \item Vorticity
 	\end{itemize}
@@
 	\begin{itemize}
-    \item Drag and resistivity
-    \item Anisotropy
-    \item Vorticity
+	\item Area and Drag
 	\end{itemize}

### 2018-02-28 docs/methods/erosion_methods.tex
NM
Working on figure for 6 body simulation.

@@
 \begin{align}
-& p_{-} = \frac{1}{2} \int_{-1}^{1} p(-2,y) \, dy \, , \\
-& p_{+} = \frac{1}{2} \int_{-1}^{1} p(+2,y) \, dy \, .
+p_{-} = \frac{1}{2} \int_{-1}^{1} p(-2,y) \, dy \, , \qquad
+p_{+} = \frac{1}{2} \int_{-1}^{1} p(+2,y) \, dy \, .
 \end{align}
@@
 \begin{align}
-\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})} \, ,
+\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})} \, .
 \end{align}
@@
 
+% Table
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{table}%[htbp]
+\begin{center}
+\caption{Convergence test for multiple-body erosion with fixed pressure drop.
+}
+\vspace{0.3 pc}
+\label{convtab}
+\begin{tabular}{l l l l}
+\hline
+\hspace{0.0pc} $\Delta t/t_s$
+\hspace{0.5pc} & error 
+\hspace{0.5pc} & order
+\hspace{0.5pc} & CPU time \\
+\hline
+%
+1/10     	& 2.67E-5  	& --        	& 14 mins  	\\
+1/20     	& 7.23E-6  	& 1.88 	& 27 mins  	\\
+1/40     	& 1.95E-6  	& 1.89 	& 52 mins  	\\
+1/80     	& 4.90E-7  	& 1.99 	& 1.7 hours	\\
+1/160     	& 1.25E-7  	& 1.97  	& 3.4 hours	\\
+%
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Parameters in this test are: 20circ128, nits = 5, dt0 = 4e-4, tfin = 4e-3
+% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 1
+
+\vsp{10}
+
+6 body simulations.
+Point out that the bodies tend to develop flat faces wherever there is a nearby body (now that the bodies are numbered, can refer to specific bodies).
+Point out high vorticity in this channels between bodies.
+Spontaneous channelization.
+Point out that our algorithm allows bodies to vanish seamlessly, for example body 4.
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 \includegraphics[width = 0.9 \textwidth]{./figs/06bod.pdf}
-\caption{\label{fig:50bodies} 6 bodies
+\caption{\label{fig:50bodies} 6 bodies. TO DO HERE: Number the bodies so that I can describe them.
 }
@@
 %which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
-
-\vsp{10}
 

### 2018-02-28 docs/methods/erosion_methods.tex
NM

@@
 We make one important conceptual change to our model.
-For a realistic porous medium composed of many solid bodies, the condition of a fixed incoming flow rate $\umax$ is somewhat artificial.
+For a realistic porous medium composed of many solid bodies, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
 A more realistic condition is that the pressure difference from one end to another is held fixed.
@@
 
-We therefore impose the condition of a fixed pressure difference by controlling the incoming flow-rate $\umax$ at each time-step.
+We therefore impose the condition of a fixed pressure difference by controlling the incoming flow-rate, $\umax$, at each time-step.
 This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed, then measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies.
-These upstream and downstream pressures are given by
+The vertically-averaged upstream and downstream pressures are given by
 \begin{align}
@@
 
-Briefly, to confirm that the rescaling does not alter accuracy, we show HERE a convergence test for 20 bodies with the condition of a fixed pressure drop.
-
-% Table
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 \begin{center}
-\caption{Convergence test for multiple-body erosion with fixed pressure drop.
+\caption{Convergence test for multiple-body erosion with fixed-pressure drop condition.
+In this test, we use 20 bodies with $N_{\iin} = 128$ grid points on each.
+We run the simulations to a stopping time of $t_s = 4E-3$, which is 24\% of the time it takes for {\em all} bodies to vanish.
+We measure the {\em combined} $L^2$-difference in the shapes of {\em all} bodies.
+The table confirms that the method maintains second-order accuracy in time, even with multiple bodies and a time-varying inflow rate $\umax$.
 }
@@
 
-\vsp{10}
-
-6 body simulations.
+Briefly, to confirm that the rescaling does not alter accuracy, we show in Table \ref{convtab} a convergence test for a 20-body simulation with the condition of fixed pressure drop imposed.
+The table shows the method to retain second-order accuracy in time.
+In the last column, we show the computational times, indicating that the 20-body simulations require more runtime than the single-body case.
+Although the GMRES-iteration count is independent of the spatial resolution, $N_{\iin}$, it can depend on the number of bodies and/or their configuration.
+To illustrate this point, we show in Table \ref{itertab} the GMRES count for various cases ...
+
+% Table: GMRES iterations
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{table}%[htbp]
+\begin{center}
+\caption{GMRES Iterations
+}
+\vspace{0.3 pc}
+\label{itertab}
+\begin{tabular}{c c | c c}
+\hline
+\hspace{0.5pc} Number of bodies
+\hspace{0.5pc} & GMRES iterations 
+\hspace{0.5pc} & Resolution, $N_{\iin}$
+\hspace{0.5pc} & GMRES iterations  \\
+\hspace{0.0pc} ($N_\iin = 128$ in each) & 
+\hspace{0.5pc} &(10 bodies in each) & \\
+\hline
+%
+10	& 223	& 32	    	& ?	\\
+15	& 292	& 64    	& ?	\\
+20	& 363	& 128	& ?	\\
+30	& 496	& 256	& ?	\\
+40	& 676	& 512	& ?	\\
+50	& 991	& 1024	& ?	\\
+%
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% In these tests I always use 128 points per body.
+
+\vsp{20}
+6 body simulations. Point out that this arrangement was designed to have some near contacts (e.g. between bodies 1 and 2) and the simulation handles this fine.
 Point out that the bodies tend to develop flat faces wherever there is a nearby body (now that the bodies are numbered, can refer to specific bodies).
@@
 Point out that our algorithm allows bodies to vanish seamlessly, for example body 4.
+Point out that the vorticity levels increases as the flow rate increases (due to fixing the pressure drop).
 
@@
 
-% Table
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{table}%[htbp]
-\begin{center}
-\caption{GMRES Iterations
-}
-\vspace{0.3 pc}
-\label{itertab}
-\begin{tabular}{c c | c c}
-\hline
-\hspace{0.0pc} Number of bodies
-\hspace{0.5pc} & GMRES iterations 
-\hspace{0.5pc} & aaa
-\hspace{0.5pc} & bbb \\
-\hline
-%
-10	& 223	& a	& b	\\
-15	& 292	& a	& b	\\
-20	& 363	& a	& b	\\
-30	& 496	& a	& b	\\
-40	& 676	& a	& b	\\
-50	& 991	& a	& b	\\
-%
-\hline
-\end{tabular}
-\end{center}
-\end{table}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% In these tests I always use 128 points per body.
+\newpage
 

### 2018-02-28 docs/methods/erosion_methods.tex
NM

@@
 To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 1E-2$.
-This stopping time is 56\% of the time it takes the body to vanish, and was chosen so that the body will have eroded substantially but is not so small that accuracy is lost.
+This stopping time is 56\% of the time it takes the body to vanish, and was chosen so that the body will have eroded substantially but is not so small that accuracy is compromised.
 We assess error by measuring the difference between simulations of successive resolutions (i.e.~we verify Cauchy convergence).
@@
 \begin{center}
-\caption{Convergence test for multiple-body erosion with fixed-pressure drop condition.
+\caption{Convergence test for multiple-body erosion with fixed-pressure-drop condition.
 In this test, we use 20 bodies with $N_{\iin} = 128$ grid points on each.
-We run the simulations to a stopping time of $t_s = 4E-3$, which is 24\% of the time it takes for {\em all} bodies to vanish.
+We run the simulations to a stopping time of $t_s = 4E-3$ (24\% of the time it takes for {\em all} bodies to vanish).
 We measure the {\em combined} $L^2$-difference in the shapes of {\em all} bodies.
 The table confirms that the method maintains second-order accuracy in time, even with multiple bodies and a time-varying inflow rate $\umax$.
+%We compare the shapes of {\em all} bodies from simulations of successive resolution using {\combined} $L^2$-norm
 }
@@
 \hspace{0.5pc} & GMRES iterations  \\
-\hspace{0.0pc} ($N_\iin = 128$ in each) & 
-\hspace{0.5pc} &(10 bodies in each) & \\
+\hspace{0.0pc} ($N_\iin = 128$ fixed) & 
+\hspace{0.5pc} &(10 bodies) & \\
 \hline
@@
 % In these tests I always use 128 points per body.
+
+With the multiple-body simulations validated, we now discuss the emergent physics of viscous erosion with multiple bodies...
 

### 2018-03-03 docs/methods/erosion_methods.tex
Adding comments for intro section.

@@
 reference is changed to \thL~variables so that the curvature term
-appears as a diffusive term that can easily be treated implicitly
-to avoid stiffness.
+appears as a diffusive term that can easily be handled in a 
+numerically stable fashion, e.g.~via an exponential integrator or an implicit method.
 
@@
 individually resolved rather than homogenized.  We start by validating
-our method on a single circular body placed symmetrically in a pipe
+our method on a single circular body placed symmetrically in a CHANNEL
 flow.  By artificially fixing the area of the body as a function of
@@
 integral equation methods to resolve corners, we employ a different
-method.  First, we add a regularization term to the shear stress to
+method.  
+\todo[inline]{Maybe point out some drawbacks of using one of these BIE methods that allows corners.
+For example, are these methods more conceptually complex and/or more expensive?
+Maybe they are not quite at a mature stage for application?
+Another point: in the simulations we cannot predict where corners will form and so would have to identify them on the fly.
+Would this cause a problem if we tried to use a corner-resolving BIE?}
+\todo[inline]{Could say our approach is simpler because  by smoothing corners, we can use the bare-bones BIE methods that are more well established compared to these newer, corner-resolving methods.
+Just some thoughts.}
+First, we add a regularization term to the shear stress to
 penalize regions of high curvature.  Second, we apply a Gaussian filter
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Limitations} There are two main limitations of the current
+\paragraph{Limitations}
+
+\todo[inline]{These are some of my thoughts on reworking this first paragraph. See if you like it.}
+We begin by making two fundamental design choices: first, we restrict ourselves to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
+The restriction to 2D allows us to simulate the erosion of many bodies (order 50-100) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium.
+While BIE methods are available in 3D, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
+The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
+While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
+
+\todo[inline]{This is the original below:}
+There are two main limitations of the current
 work.  First, the flow is assumed to be two-dimensional.  However, by
@@
 double-layer potential
+\todo[inline]{Do you think we should flesh out this time-scale stuff more precisely?
+i.e.~By setting $\mu = 1$ and $C = 1$ (the erosion constant), what exactly is the timescale that defines our dimensionless time.}
 \begin{align}
@@
 Here, $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a boundary mean.
-This term causes regions of high curvature to recede more rapidly, thus smoothing any high-frequency oscillations that my exist.
+This term causes regions of high curvature to recede more rapidly, thus smoothing any high-frequency oscillations that may exist.
 Since a closed body has mean curvature $\mean{\kappa} = 2\pi / L$, this smoothing term has mean zero and and thus preserves area.
@@
 Each boundary is parameterized by normalized arc length $\alpha = 2 \pi s / L$.
+
+\todo[inline]{Mention key term exponential integrator for stiff term.}
 

### 2018-03-03 docs/methods/erosion_methods.tex
NM

@@
 fluid-structure interaction problems with a long time horizon is
-particularly---the mesh is often distorted and tangled by the dynamics
+particularly (???) ---the mesh is often distorted and tangled by the dynamics
 and regions of high curvature develop.  These two issues are resolved
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary evolution in the {\thL} framework and regularization} 
+\subsection{Boundary evolution in the {\thL} framework} 
 \label{sec:thetaL}
 
-To evolve the boundaries, we use the {\thL} framework, which offers certain advantages in stabilizing fluid-structure interaction problems \cite{hou-low-she1994}.
-
-For numerical stability, we modify the erosion law \eqref{eqn:erosionModel} to include a term that depends on the local curvature $\kappa$. The idea is to prevent regions of very high
-curvature from developing, as these regions would compromise the accuracy and stability of our fluid solver. We thus modify the normal velocity of each interface as follows
+To evolve the boundaries of eroding bodies, we will use the {\thL} framework which offers certain advantages in numerically stabilizing moving-interface problems \cite{hou-low-she1994}.
+Here, $\theta$ is the local tangent angle and $L$ the total perimeter of a given boundary.
+For a boundary parametrized by arc length $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin
+\theta \right)$.
+
+For numerical stability, we modify the erosion law \eqref{eqn:erosionModel} to include a term that penalizes curvature $\kappa$.
+The idea is to prevent regions of extremely high curvature from developing, as these regions would compromise the accuracy and stability of our fluid solver.
+We thus modify \eqref{eqn:erosionModel} follows
 \begin{align}
 \label{eqn:Vn}
-  \Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1
-  \right).
-\end{align}
-The second term on the right is the curvature-dependent modification, the strength of which is controlled by the parameter $\eps \ll 1$.
-Here, $L$ is the total arc length of the body, and $\mean{\cdot}$ indicates a boundary mean.
-This term causes regions of high curvature to recede more rapidly, thus smoothing any high-frequency oscillations that may exist.
-Since a closed body has mean curvature $\mean{\kappa} = 2\pi / L$, this smoothing term has mean zero and and thus preserves area.
-Therefore, the only source of material loss is the shear-stress itself.
-In addition, we have scaled the smoothing term on the mean absolute shear, $\mean{\atau}$, so that the ratio of smoothing-to-erosion always remains fixed, even as bodies vanish.
-
-We now introduce the tangent angle, $\theta$, defined through the relation
-\begin{align*}
-\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin
-\theta \right),
-\end{align*}
-where $s$ is arc length. We also introduce the normalized arc length $\alpha = 2 \pi s / L$. In terms of these new variables, the curvature can be expressed as
-\begin{align*}
-\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha}.
-\end{align*}
-Substitution into~\eqref{eqn:Vn} gives
+\Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right).
+\end{align}
+The parameter $\eps \ll 1$ controls the strength of the curvature-penalization.
+This term causes regions of high curvature to recede more rapidly and thus smooths out any high-frequency oscillations that may exist.
+Above, $\mean{\cdot}$ indicates a boundary mean.
+Since a closed body has mean curvature $\mean{\kappa} = 2\pi / L$, the penalty term has mean zero and and thus preserves area.
+The only source of material loss is therefore the shear-stress itself.
+In addition, we have scaled the penalty term on the mean absolute shear, $\mean{\atau}$, so that the ratio of smoothing-to-erosion always remains fixed, even as bodies vanish.
+
+In the following, we parameterize each boundary by normalized arc length, $\alpha = 2 \pi s / L$. In terms of $\alpha$, the curvature is given by
+\begin{align}
+\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha} \, ,
+\end{align}
+and substitution into~\eqref{eqn:Vn} gives
 \begin{align}
 \label{eqn:Vn2}
-\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1
-\right).
-%\Vn = \atau + \frac{2 \pi \eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 1 \right)
-\end{align}
-
-The main idea is to introduce an artificial tangential velocity that
-keeps collocation points equally spaced with respect to arc length;
-i.e.~the grid of $\alpha$ should always remain equally spaced. The
-tangential velocity that does the trick satisfies~\cite{hou-low-she1994}
-\begin{align*}
-\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}.
-\end{align*}
-The interface evolution is then given by
-\begin{align*}
-\dot{\xx}(t) = \Vn \nn + \Vs \ss.
-\end{align*}
-This evolution equation can be recast in the variables $\theta$ and $L$
-as
-\begin{align*}
+\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right) \, .
+\end{align}
+
+The boundary of each body will be represented by a grid of collocation points.
+If we were to simply evolve the interfaces under \eqref{eqn:Vn2}, this grid would become distorted, which, if unchecked, could lead to severe tangling and numerical instability.
+We therefore introduce an artificial tangential velocity $\Vs$ that always keeps the grid points equally spaced in arclength \cite{hou-low-she1994}.
+The appropriate tangential velocity satisfies
+\begin{align}
+\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn} \, ,
+\end{align}
+The evolution of the interface is then given by the combination of the normal and tangential velocity
+\begin{align}
+\dot{\xx}(t) = \Vn \nn + \Vs \ss \, .
+\end{align}
+Since $\Vs$ is tangential, it does not modify the erosion law \eqref{eqn:Vn}, only the collocation grid.
+
+When recast in the variables $\theta$ and $L$, the interface evolution becomes
+\begin{align}
 \tderiv{L}{t} &= - 2 \pi \mean{\thalpha \Vn}, \\
@@
 \thalpha \Vs \right).
-\end{align*}
+\end{align}
 Inserting~\eqref{eqn:Vn2} for the normal velocity gives
@@
 \end{align}
-System \eqref{eqn:Levo1}--\eqref{eqn:thetaevo1} comprise the main evolution equations that we will solve numerically in Section~\ref{sec:timeStepping}.
-
-In addition, it is necessary to track a reference point for each body, so that the variables $\theta$ and $L$ can be converted back into a cartesian grid.
-We choose to track the coordinates of the surface mean $\mean{\xx}$, which moves according to
+System \eqref{eqn:Levo1}--\eqref{eqn:thetaevo1} comprise the main evolution equations to be solved numerically in Section~\ref{sec:timeStepping}.
+
+In addition, it is necessary to track a reference point for each body, so that the variables $\theta$ and $L$ can be converted back to cartesian coordinates.
+We track the coordinates of the surface mean $\mean{\xx}$, which moves according to
 \begin{align}
@@
 \end{align}
-Tracking the surface mean is somewhat simpler than tracking the center of mass, but either choice would be valid.
+We note that tracking the center of mass is also a valid choice, but the surface mean gives a somewhat simpler formula.
 

### 2018-03-03 docs/methods/erosion_methods.tex
NM
Put final touches on theta-L and timestepping sections.

@@
 \end{align}
-Since $\Vs$ is tangential, it does not modify the erosion law \eqref{eqn:Vn}, only the collocation grid.
+Since $\Vs$ is tangential, it does not modify the physics of erosion, only the grid spacing.
 
@@
 \end{align}
-System \eqref{eqn:Levo1}--\eqref{eqn:thetaevo1} comprise the main evolution equations to be solved numerically in Section~\ref{sec:timeStepping}.
-
-In addition, it is necessary to track a reference point for each body, so that the variables $\theta$ and $L$ can be converted back to cartesian coordinates.
+These are the main evolution equations for $\theta(\alpha,t)$ and $L(t)$.
+In addition, it is necessary to track a reference point for each body, so that the {\thL} variables can be converted back to cartesian coordinates.
 We track the coordinates of the surface mean $\mean{\xx}$, which moves according to
@@
 We note that tracking the center of mass is also a valid choice, but the surface mean gives a somewhat simpler formula.
+Equations \eqref{eqn:Levo1}--\eqref{eq:xsurf} comprise the main system of equations to be solve numerically in Section~\ref{sec:timeStepping}.
 
@@
 
-With the shear stress computed, we are now ready to evolve the boundary of each body using equations~\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1}.
-As described in Section~\ref{sec:thetaL}, we use the {\thL} framework, with $\theta$ being the tangent angle and $L$ the total arc length of a given boundary.
-Each boundary is parameterized by normalized arc length $\alpha = 2 \pi s / L$.
-
-\todo[inline]{Mention key term exponential integrator for stiff term.}
-
-In addition to the curvature-dependent term in~\eqref{eqn:Vn}, we regularize boundary evolution by applying a narrow Gaussian filter to absolute shear stress
-\begin{align*}
-\atausig = \int_{\gamma} \frac{1}{\sqrt{2\pi} \sigma} \exp \left(-
-\frac{\alpha'^2}{2 \sigma^2}\right) \abs{ \tau(\alpha - \alpha') } \,
-d\alpha'.
-\end{align*}
-Here $\sigma$ sets the width of the filter. The corresponding normal and tangential interface velocities are then given by
-\begin{align*}
+With the shear stress computed, we are now ready to numerically evolve the boundaries using the {\thL} framework.
+The main equations to be solved are \eqref{eqn:Levo1}--\eqref{eq:xsurf}.
+In Section~\ref{sec:thetaL} we introduced a curvature-penalization term into the erosion law \eqref{eqn:Vn}.
+This term smooths out high-frequency oscillations, but also introduces {\em stiffness} into evolution equation \eqref{eqn:thetaevo1} for $\theta(\alpha,t)$.
+For numerical stability, we will treat the stiff term with an exponential integrator, while handling all other terms in \eqref{eqn:Levo1}--\eqref{eq:xsurf} with an explicit Runge-Kutta method.
+Ultimately, we will arrive at a method that is second-order in time.
+
+First, we must address a second potential source of numerical instability.
+The erosion law \eqref{eqn:Vn} depends on the {\em absolute value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$ changes sign (a stagnation point).
+This corner in $\atau$ introduces high frequencies into \eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
+To avoid these difficulties, we smooth $\atau$ via a narrow Gaussian filter of width $\sigma$
+\begin{align}
+\atausig = \int_{\gamma} \frac{1}{\sqrt{2\pi} \sigma}
+ \exp \left(- \frac{\alpha'^2}{2 \sigma^2}\right) \abs{ \tau(\alpha - \alpha') } \, d\alpha' \, ,
+\end{align}
+with corresponding normal and tangential interface velocities
+\begin{align}
 & \Vnsig = \atausig +  \eps \mean{\atausig}
@@
 & \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig}.
-\end{align*}
-
-For convenience, we introduce the variables
-\begin{align*}
+\end{align}
+
+We now consider the system of evolution equations given by \eqref{eqn:Levo1}--\eqref{eq:xsurf}. For convenience, we introduce the following variables
+\begin{align}
 %\label{eq:M}
@@
 & \elfun = \frac{2 \pi}{L}  \mean{\atausig} \, .
-\end{align*}
-Then, the evolution equations~\eqref{eqn:Levo1}
-and~\eqref{eqn:thetaevo1} can be compactly expressed as
+\end{align}
+Then, ~\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1} can be compactly expressed as
 \begin{align}
@@
 \end{align}
-Here $\NLterm$ represents the nonlinear terms (and nonlocal terms) in the PDE for $\theta$.
-
-\todo[inline]{Need to remind reader that the diffusive term comes from smoothing and that this is the stiff term that could potential cause numerical problems.}
-
-We will evolve $\theta(\alpha)$ spectrally and so introduce the Fourier series
+The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term that results from the curvature penalization.
+This term is multiplied by $\zeta$, which is spatially constant but time dependent (due to $L$ and $\mean{\atau}$).
+The second term, $\NLterm$, represents the rest of the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity.
+Since the local shear stress depends on interactions between bodies, $\NLterm$ is both a nonlinear and nonlocal.
+
+We will evolve $\theta(\alpha,t)$ spectrally and so introduce the Fourier series
 \begin{align}
 \label{thetaSeries}
- \theta(\alpha,t) &= \alpha + \FourierSum \thhat_k e^{ i k \alpha}, \\
- \NLterm(\alpha,t)  &= \FourierSum \widehat{\NLterm}_k e^{ i k \alpha}.
+ \theta(\alpha,t) &= \alpha + \FourierSum \thhat_k e^{ i k \alpha} \, , \\
+ \NLterm(\alpha,t)  &= \FourierSum \widehat{\NLterm}_k e^{ i k \alpha} \, .
 \end{align}
@@
 \begin{align*}
-\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \widehat{\NLterm}_k.
-\end{align*}
-These ODEs can be solved by using the integrating factor
+\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \widehat{\NLterm}_k \, .
+\end{align*}
+These ODEs can be solved by applying the integrating factor
 \begin{align}
 \label{eq:mu}
-\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right).
-\end{align}
-We are therefore led to the coupled system of ODEs
+\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right) \, ,
+\end{align}
+which leads to the coupled system of ODEs
 \begin{align}

### 2018-03-04 docs/methods/erosion_methods.tex
NM

@@
 The parameter $\eps \ll 1$ controls the strength of the curvature-penalization.
-This term causes regions of high curvature to recede more rapidly and thus smooths out any high-frequency oscillations that may exist.
+This term causes regions of high curvature to recede more rapidly and thus suppresses any high-frequency oscillations that may exist.
 Above, $\mean{\cdot}$ indicates a boundary mean.
@@
 \end{align}
-Since $\Vs$ is tangential, it does not modify the physics of erosion, only the grid spacing.
+Since $\Vs$ is tangential, it does not modify the physics of erosion, only the parameterization of the boundaries.
 
@@
 The main equations to be solved are \eqref{eqn:Levo1}--\eqref{eq:xsurf}.
-In Section~\ref{sec:thetaL} we introduced a curvature-penalization term into the erosion law \eqref{eqn:Vn}.
-This term smooths out high-frequency oscillations, but also introduces {\em stiffness} into evolution equation \eqref{eqn:thetaevo1} for $\theta(\alpha,t)$.
+In Section~\ref{sec:thetaL} we introduced a curvature-penalizing term into the erosion law \eqref{eqn:Vn}.
+This term suppresses high-frequency oscillations, but also introduces {\em stiffness} into evolution equation \eqref{eqn:thetaevo1} for $\theta(\alpha,t)$.
 For numerical stability, we will treat the stiff term with an exponential integrator, while handling all other terms in \eqref{eqn:Levo1}--\eqref{eq:xsurf} with an explicit Runge-Kutta method.

### 2018-03-04 docs/methods/erosion_methods.tex
NM

@@
 In Section~\ref{sec:thetaL} we introduced a curvature-penalizing term into the erosion law \eqref{eqn:Vn}.
-This term suppresses high-frequency oscillations, but also introduces {\em stiffness} into evolution equation \eqref{eqn:thetaevo1} for $\theta(\alpha,t)$.
-For numerical stability, we will treat the stiff term with an exponential integrator, while handling all other terms in \eqref{eqn:Levo1}--\eqref{eq:xsurf} with an explicit Runge-Kutta method.
-Ultimately, we will arrive at a method that is second-order in time.
+This term suppresses high-frequency oscillations, but also introduces {\em stiffness} into evolution equation \eqref{eqn:thetaevo1}.
+We will therefore use a combined exponential-integrator/Runge-Kutta method to solve system \eqref{eqn:Levo1}--\eqref{eq:xsurf}.
+The exponential integrator will handle the stiff term in a numerically stable fashion, while the Runge-Kutta method will treat the nonlinear terms explicitly.
+Our overall time-stepping method will be second order.
 

### 2018-03-04 docs/methods/erosion_methods.tex
NM

@@
 We will therefore use a combined exponential-integrator/Runge-Kutta method to solve system \eqref{eqn:Levo1}--\eqref{eq:xsurf}.
-The exponential integrator will handle the stiff term in a numerically stable fashion, while the Runge-Kutta method will treat the nonlinear terms explicitly.
+The exponential integrator will handle the stiff term in a numerically stable fashion, while the Runge-Kutta method will treat nonlinear terms explicitly.
 Our overall time-stepping method will be second order.
@@
 First, we must address a second potential source of numerical instability.
-The erosion law \eqref{eqn:Vn} depends on the {\em absolute value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$ changes sign (a stagnation point).
-This corner in $\atau$ introduces high frequencies into \eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
+The erosion law \eqref{eqn:Vn} depends on the {\em absolute value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$ changes sign (i.e.~at a stagnation point).
+The corner in $\atau$ introduces high frequencies into \eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
 To avoid these difficulties, we smooth $\atau$ via a narrow Gaussian filter of width $\sigma$
@@
 \end{align}
+This smoothing further suppresses feedback between high frequencies in $\atau$ and body geometry.
 
@@
 \end{align}
-The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term that results from the curvature penalization.
-This term is multiplied by $\zeta$, which is spatially constant but time dependent (due to $L$ and $\mean{\atau}$).
-The second term, $\NLterm$, represents the rest of the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity.
+The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity gives rise to a diffusive term for the tangent angle $\theta$.
+This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$ being time dependent).
+Meanwhile, $\NLterm$, represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
 Since the local shear stress depends on interactions between bodies, $\NLterm$ is both a nonlinear and nonlocal.
 
-We will evolve $\theta(\alpha,t)$ spectrally and so introduce the Fourier series
+We will evolve $\theta(\alpha,t)$ in spectral space and so introduce the Fourier series for $\theta$ and $\NLterm$
 \begin{align}
@@
 \end{align*}
-These ODEs can be solved by applying the integrating factor
+These ODEs can be simplified by applying the integrating factor
 \begin{align}
@@
 \end{align}
-which leads to the coupled system of ODEs
+which leads to the coupled system
 \begin{align}
@@
 \end{align}
-We solve system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an
-explicit, second-order Runge-Kutta method (RK2). In particular, we choose the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature term.
+Note that the diffusive term from \eqref{eqn:thetaevo2} does not appear explicitly in \eqref{eqn:thetaevo3}, but rather is implied by the integrating factor \eqref{eq:mu}; i.e.~we have applied an exponential integrator.
+We solve the resulting system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an
+explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature penalization.
 
@@
 \end{align}
-Since $\zeta >0$, the exponential term always acts to smooth the geometry and thus mitigate numerical instabilities.
+Since $\zeta >0$, the exponential term always {\em suppresses} high-frequencies, i.e.~it is a smoothing term.
 With the geometry at step $n+1/2$ known, a call to the Stokes solver allows the computation of $\Mterm^{(n+1/2)}$, $\widehat{\NLterm}_k^{(n+1/2)}$, and $\zeta^{(n+1/2)}$.
@@
 \end{align}
-Again, both exponential terms act to smooth high-frequency oscillations in shape.
-We note that the above approach would generalize to higher-order Runge-Kutta methods, such as RK4.
-Finally, we track the reference point $\mean{x}$ of each body by simply discretizing \eqref{eq:xsurf} with the same RK2 method.
+Once again, both exponential terms are smoothing. To track the reference point, $\mean{x}$, we simply apply the same RK2 method to \eqref{eq:xsurf}.
+
+We point out that most exponential-integrator methods use some form of quadrature to treat \eqref{eq:mu}, but, here, we have simply applied the same RK2 method that is used for the rest of the system.
+We believe this to be a simple approach to arrive at a self-consistent discretization of desired accuracy because it avoids choices regarding which quadrature to use (midpoint, trapezoid, Simpson's etc.) and can be generalized to other time-stepping methods, such as fourth-order Runge-Kutta.
 

### 2018-03-04 docs/methods/erosion_methods.tex
NM

@@
 
-We point out that most exponential-integrator methods use some form of quadrature to treat \eqref{eq:mu}, but, here, we have simply applied the same RK2 method that is used for the rest of the system.
-We believe this to be a simple approach to arrive at a self-consistent discretization of desired accuracy because it avoids choices regarding which quadrature to use (midpoint, trapezoid, Simpson's etc.) and can be generalized to other time-stepping methods, such as fourth-order Runge-Kutta.
+We point out that most exponential integrators use some form of quadrature to treat \eqref{eq:mu}, but, here, we have simply applied the same RK2 method that is used for the rest of the system.
+We believe this to be a simple, systematic approach to arrive at a self-consistent discretization of desired accuracy because it avoids choices regarding which quadrature to use (midpoint, trapezoid, Simpson's, etc.) and can be easily generalized to other time-stepping methods, such as fourth-order Runge-Kutta.
 

### 2018-03-04 docs/methods/erosion_methods.tex
NM

@@
 \end{align}
-Since $\zeta >0$, the exponential term always {\em suppresses} high-frequencies, i.e.~it is a smoothing term.
+Since $\zeta >0$, the exponential term always {\em suppresses} high-frequencies in proportion to $k^2$.
+In other words, this is a smoothing term.
 With the geometry at step $n+1/2$ known, a call to the Stokes solver allows the computation of $\Mterm^{(n+1/2)}$, $\widehat{\NLterm}_k^{(n+1/2)}$, and $\zeta^{(n+1/2)}$.
@@
 \begin{align}
-\thhat_k^{(n+1)} = & \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) + \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
-\end{align}
-Once again, both exponential terms are smoothing. To track the reference point, $\mean{x}$, we simply apply the same RK2 method to \eqref{eq:xsurf}.
+\thhat_k^{(n+1)} =  \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) + \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
+\end{align}
+Once again, both exponential terms act to smooth geometry in proportion to $k^2$. Finally, to track the reference point, $\mean{x}$, we simply apply the same RK2 method to \eqref{eq:xsurf}.
 

### 2018-03-04 docs/methods/erosion_methods.tex
NM

@@
 The idea is to prevent regions of extremely high curvature from developing, as these regions would compromise the accuracy and stability of our fluid solver.
-We thus modify \eqref{eqn:erosionModel} follows
+We thus modify \eqref{eqn:erosionModel} as follows
 \begin{align}
@@
 We note that tracking the center of mass is also a valid choice, but the surface mean gives a somewhat simpler formula.
-Equations \eqref{eqn:Levo1}--\eqref{eq:xsurf} comprise the main system of equations to be solve numerically in Section~\ref{sec:timeStepping}.
+Equations \eqref{eqn:Levo1}--\eqref{eq:xsurf} comprise the main system of equations to be solved numerically in Section~\ref{sec:timeStepping}.
 
@@
 
-With the shear stress computed, we are now ready to numerically evolve the boundaries using the {\thL} framework.
+With the shear stress computed, we are now ready to numerically evolve the boundary of each body using the {\thL} framework.
 The main equations to be solved are \eqref{eqn:Levo1}--\eqref{eq:xsurf}.
@@
 \end{align}
-This smoothing further suppresses feedback between high frequencies in $\atau$ and body geometry.
+This smoothing further suppresses the feedback of high frequencies betweeen $\atau$ and body shape.
 
@@
 \end{align}
-The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity gives rise to a diffusive term for the tangent angle $\theta$.
-This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$ being time dependent).
+The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity gives rise to a diffusive term in the tangent angle $\theta$.
+This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$).
 Meanwhile, $\NLterm$, represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.

### 2018-03-04 docs/methods/erosion_methods.tex
NM

@@
 To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 1E-2$.
-This stopping time is 56\% of the time it takes the body to vanish, and was chosen so that the body will have eroded substantially but is not so small that accuracy is compromised.
+This stopping time is 56\% of the time it takes the body to vanish, and was selected so that the body will have eroded substantially but is not so small that accuracy is compromised.
 We assess error by measuring the difference between simulations of successive resolutions (i.e.~we verify Cauchy convergence).
@@
 
-We therefore impose the condition of a fixed pressure difference by controlling the incoming flow-rate, $\umax$, at each time-step.
+We therefore impose the condition of a fixed pressure difference by dynamically controlling the incoming flow-rate, $\umax$.
 This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed, then measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies.
@@
 \end{align}
-This rescaling maintains a {\em fixed} pressure difference.
+This rescaling maintains a {\em fixed} pressure difference between the upstream ($x=-2$) and downstream ($x=2$) positions.
 Because the Stokes equations are linear, such a rescaling is permissible and does not alter the accuracy of our method.
-Furthermore, rescaling by a different factor at each time-step is also permissible because the Stokes equations are memoryless (i.e.~there is no time derivative present in the PDEs).
+Furthermore, {\em dynamic} rescaling is also permissible because the Stokes equations are memoryless (i.e.~there is no time derivative present in the PDEs).
 

### 2018-03-04 docs/methods/erosion_methods.tex
Writing multiple body results section.

@@
 
-With the multiple-body simulations validated, we now discuss the emergent physics of viscous erosion with multiple bodies...
-
-\vsp{20}
-6 body simulations. Point out that this arrangement was designed to have some near contacts (e.g. between bodies 1 and 2) and the simulation handles this fine.
-Point out that the bodies tend to develop flat faces wherever there is a nearby body (now that the bodies are numbered, can refer to specific bodies).
-Point out high vorticity in this channels between bodies.
-Spontaneous channelization.
-Point out that our algorithm allows bodies to vanish seamlessly, for example body 4.
-Point out that the vorticity levels increases as the flow rate increases (due to fixing the pressure drop).
+We now discuss some physical aspects of multi-body erosion revealed by our simulations.
+In Fig.~\ref{fig:06bodies} we show a simulation of 6 eroding bodies, each initially circles of various sizes and positions.
+Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerable.
+As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable (such as the foremost and aft-most points on the body).
+Rather, when and where these sharp features develop depends on inter-body feedback as mediated by the Stokes flow.
 
@@
 \includegraphics[width = 0.9 \textwidth]{./figs/06bod.pdf}
-\caption{\label{fig:50bodies} 6 bodies. TO DO HERE: Number the bodies so that I can describe them.
+\caption{\label{fig:06bodies} 6 bodies.
 }
@@
 %which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
+
+The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several near contacts between bodies, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
+Our method handles these near contacts without difficulty.
+Interestingly, erosion appears to preferentially remove material from these regions of near contact, as the narrow spacing between bodies expands rather rapidly.
+For example, the spacing between bodies 1 \& 2 was initially very small but is already comparable to the spacing between bodies 3 \& 4 by the second frame.
+Even more interesting, the bodies tend to develop flat faces wherever near contact occurs, which leads to the appearance of straight channels in between bodies.
+Such channels are apparent between bodies 1 \& 2, 3 \& 5, and 5 \& 6, and they {\em persist} for the duration of the simulation.
+
+\vsp{20}
+Point out high vorticity in this channels between bodies.
+Spontaneous channelization.
+Point out that our algorithm allows bodies to vanish seamlessly, for example body 4.
+Point out that the vorticity levels increases as the flow rate increases (due to fixing the pressure drop).
 

### 2018-03-04 docs/methods/erosion_methods.tex
NM

@@
 Even more interesting, the bodies tend to develop flat faces wherever near contact occurs, which leads to the appearance of straight channels in between bodies.
-Such channels are apparent between bodies 1 \& 2, 3 \& 5, and 5 \& 6, and they {\em persist} for the duration of the simulation.
+Such channels are apparent between bodies 1 \& 2, 3 \& 5, and 5 \& 6, and they {persist} for the duration of the simulation.
+
+The vorticity field (color) is useful to infer both the regions of highest shear and the regions of most intense flow.
+Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel running horizontally, below bodies 1 \& 2 and above bodies 3 \& 6.
+This main channel widens the fastest as the high-flow rate leads to greater shearing on the boundaries.
+As discussed above, the pressure drop across the cell is fixed in these simulations, and so as the bodies diminish the flow rate increases, which can be seen by the increase in the vorticity magnitude.
+By the final frame shown, body 4 has vanished completely and our method handles this event seamlessly.
 
 \vsp{20}
-Point out high vorticity in this channels between bodies.
-Spontaneous channelization.
-Point out that our algorithm allows bodies to vanish seamlessly, for example body 4.
-Point out that the vorticity levels increases as the flow rate increases (due to fixing the pressure drop).
+Good word: Spontaneous channelization
 

### 2018-03-05 docs/methods/erosion_methods.tex
NM
Working over 1-body drag text.

@@
 \begin{align}
-  \FD = \int_{\gamma_\ell} p \nn + \tau \ss \,ds.
+  \FFD = \int_{\gamma_\ell} p \nn + \tau \ss \,ds.
   \label{eqn:drag}
@@
 
-In Fig.~\ref{area_drag}(b), we show the drag $F_D$ measured on the body as it erodes.
-The drag decreases gradually, then takes a nose dive in the final moments when the body vanishes, as is consistent with the logarithmic dependence on lengthscale $L$ in 2D Stokes flow.
+In Fig.~\ref{area_drag}(b), we show the horizontal drag $F_D$ measured on the body as it erodes.
+Note that, in the context of 3D slender-body theory, $F_D$ is drag per unit span.
+The figure shows the drag to decrease  gradually at first, then abruptly tend to zero in the final moments of the body vanishing.
+This behavior is consistent with fact that drag vanishes {\em logarithmically} with $L$  in 2D Stokes flow.
 We also show in the figure the separate contributions of the viscous and the pressure drag.
+Initially, these two contributions are comparable, with a slightly greater level of pressure drag.
+However, as the body erodes and assumes a more slender form, the pressure drag vanishes much more rapidly than viscous drag.
+
 As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
@@
 
-\vsp{20}
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.99 \textwidth]{./figs/06plots.pdf}
+\caption{\label{fig:06plots} plots to go with 6 body simulation.
+}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure generated from data file 50circ512p5, 
+%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
+
+\newpage
+
 Good word: Spontaneous channelization
 
-\newpage
-
-\vsp{10}
+\vsp{3}
 Possible list:

### 2018-03-05 docs/methods/erosion_methods.tex
Normalized area and drag in plots and text.

@@
 \begin{center}
-\includegraphics[width = 0.85 \textwidth]{./figs/area_drag.pdf}
+\includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
 \caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction \eqref{area_predict} (dotted red).
@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024aa;
+% Figure from datafile 01circ1024aaa;
 % Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
@@
 \label{area_predict}
-A (c_1 - \log A) \sim c_2 (t_f - t) \qquad \text{as } t \to t_f \, .
-\end{align}
-where $c_1$ and $c_2$ are constants.
+\frac{A}{A_0} \left( 1 - c_1 \log{\frac{A}{A_0}} \right) = \frac{t_f - t}{t_f}
+%A (c_1 - \log A) \sim c_2 (t_f - t) \qquad \text{as } t \to t_f \, .
+\end{align}
+where $c_1$ is a constant.
 This is an {\em implicit} relationship for how the area scales down in time during erosion.
-In Fig.~\ref{area_drag}a, we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 =2.2$ and $c_2 = 30$.
+In Fig.~\ref{area_drag}a, we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 = 0.24$.
 The comparison shows close agreement between the two (they are indistinguishable).
 
-In Fig.~\ref{area_drag}(b), we show the horizontal drag $F_D$ measured on the body as it erodes.
+In Fig.~\ref{area_drag}(b), we show the horizontal drag $F_D$ measured on the body as it erodes. This drag is normalized by a characteristic value $F_c = A_0/t_f$.
 Note that, in the context of 3D slender-body theory, $F_D$ is drag per unit span.
@@
 
-As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
+As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component, $F_{\mu} \approx \mean{\atau} L$, which gives
 \begin{align}
 \label{viscdrag}
-F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
+\frac{F_{\mu}}{F_c} \sim \frac{1}{1 - c_1 (1 + \log{A/A_0})}
+%F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
 \end{align}

### 2018-03-06 docs/TexNotes/Notes.tex
Working on drag. It is kind of subtle to get estimates with slender-body theory.

--- 2018-02-26 docs/TexNotes/Notes.tex
@@
 \begin{equation}
-\tau \sim \mu V/L
+\tau \sim \mu U/a
 \end{equation}
-where $V$ and $L$ are a characteristic velocity and length scale respectively.  However, for 2D Stokes flow we have Stokes paradox and slender body effects. The analogous scaling of the stress is
+where $U$ and $a$ are a characteristic velocity and length scale respectively.  However, for 2D Stokes flow we have Stokes paradox and slender body effects. The analogous scaling of the stress is
 \begin{equation}
-\tau \sim \frac{\mu V}{L \log(W/L)}
+\tau \sim \frac{\mu U}{a \log(\ell/a)}
 \end{equation}
-where $W$ is the width in the third dimension. In the following, we will take $W = 2\pi$, since a body cannot have a length greater than $2\pi$ and still fit inside the domain.
+where $\ell$ is the width in the third dimension. 
+%For example, we can take $\ell = 2\pi$, since a body cannot have a length greater than $2\pi$ and still fit inside the domain.
 
 \subsection{The vanishing rate of the area}
-The rate of area loss is given by
+
+The area loss rate is given by
+\begin{align}
+\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
+\end{align}
+The above is an exact relation. Substitution of the scaling law gives
+\begin{align}
+\dot{A} \sim \frac{ - \mu U}{\log(\ell/a)} \, .
+\end{align}
+Inserting $A \sim a^2$ and rearranging gives
+\begin{align}
+\log (c_2 A/\ell^2) dA = c_3 \mu U dt
+\end{align}
+Integrating gives
+\begin{align}
+A \left(1 - \log(c_2 A/\ell^2) \right) = c_3 \mu U (t_f - t)
+\end{align}
+Rearranging and setting some constants based on knowing $A(t=0) = A_0$ gives
+\begin{align}
+\label{area_predict}
+\frac{A}{A_0} \left( 1 - c_1 \log{\frac{A}{A_0}} \right) \sim \frac{t_f - t}{t_f} \quad \text{as } t \to t_f \, .
+\end{align}
+where $c_1$ is a constant, and I find $c_1 = 0.24$ gives an excellent fit to the data.
+
+Now differentiation the result with respect to time gives
+\begin{align}
+\dot{A} = \frac{A_0/t_f}{1 - c_1 (1 + \log(A/A_0))} \sim - \frac{\mu U}{\log(\ell / a)}
+\end{align}
+Now, doing some manipulations, using that $A = c_3 a^2$ and $A_0 = c_3 a_0^2$, gives the nice relationship
+\begin{align}
+\ell = a_0 e^{\frac{1-c_1}{2 c_1}} = 4.87 a_0 
+\end{align}
+
+Now, to estimate the drag, use the slender-body formula for drag per unit span, $\ell$, which is
+\begin{align}
+F_D \sim \frac{4 \pi \mu U}{\log(\ell/a)}
+\end{align}
+The $4 \pi$ coefficient is exact (in the slender-body framework) for a circular cylinder. Substituting the value we found $\ell = 4.87 a_0$, gives
+\begin{align}
+F_D \sim \frac{4 \pi \mu U}{\log(4.87 a_0/a)}
+\end{align}
+For non-circular bodies, we can define $a = \sqrt{A/\pi}$ since this is the value that would be consistent with a circle. This gives
+\begin{align}
+F_D \sim \frac{4 \pi \mu U}{\log(4.87 \sqrt{A_0/A})}
+\end{align}
+or
 \begin{equation}
-\dot{A} = - \abs{\tau} L
+F_D \sim \frac{8 \pi \mu U}{\log(23.7 A_0/A)}
 \end{equation}
-We then insert the scaling $\abs{\tau} \sim -1/(L \log L)$ and simplify to get
-\begin{equation}
-\dot{A} = C/\log{A}
-\end{equation}
-which we solve to get
-\begin{equation}
-A (1 - \log A) = C (t_f - t)
-\end{equation}
-In particular, I believe the signs are correct here.
-BUT, I am not so sure of this calculation anymore, now that $W$ is included.
+
+Alternatively we can just treat $\ell$ as a fit parameter.
 

### 2018-03-06 docs/methods/erosion_methods.tex
NM
Methods paper NM
Working on drag. It is kind of subtle to get estimates with slender-body theory.

--- 2018-03-05 docs/methods/erosion_methods.tex
@@
 Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress is growing as the body vanishes.
-This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / L$, since stress is inversely proportional to body scale $L$.
+This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / a$, in which drag is inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is taken to be the radius).
 This law must be modified in two dimensions, though.
 The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012, zhao2015transportation}.
-For a slender body in flow perpendicular to its long-axis $W \gg L$, the drag is proportional to
-$\mu \umax W/ \log(W/L)$. This relationship implies that, for a 2D
-cross-section, the stress per unit span can be estimated by
+For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
+$\mu \umax \ell/ \log(\ell/a)$, where $a$ is a lengthscale of the cross-section and $a \ll \ell$. This relationship implies that the stress per unit span on a 2D cross-section can be estimated by
 \begin{align}
   \label{eqn:stresslaw}
-  \tau \sim \frac{\mu \umax}{L \log(W/L)} \qquad \text{as } L \to 0 \, .
-\end{align}
-In interpreting our 2D simulations, we will treat the span, $W$, as fixed with the
-requirement $W \gg L$.
+  \tau \sim \frac{\mu \umax}{a \log(\ell/a)} \qquad \text{for } a \ll \ell \, .
+\end{align}
+In interpreting our 2D simulations, we will treat the span, $\ell$, as fixed.
+Recall that $L$ denotes the total perimeter of the cross-section, and therefore $a$ and $L$ can often be used interchangeable in scaling analysis, since they each represent a lengthscale of the cross-section.
 
@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024aa;
-% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
+% Figure from datafile 01circ1024aaa;
+% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-7, fixarea = 0, fixpdrop = 0
 
@@
 Thus, the area-loss rate is given by the product of the mean shear
-$\mean{\atau}$ and the total perimeter $L$. Inserting scaling law~\eqref{eqn:stresslaw} gives
-\begin{align}
-\dot{A} \sim \frac{ - \mu \umax}{\log(W/L)} \quad \text{as } L \to 0 \, . 
-\end{align}
-Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
+$\mean{\atau}$ and the total perimeter $L$, which is an exact relationship. Inserting scaling law~\eqref{eqn:stresslaw} gives
+\begin{align}
+\dot{A} \sim \frac{ - \mu \umax}{\log(\ell/a)} \qquad \text{as } a \to 0 \, . 
+\end{align}
+Noting that $A \sim a^2$ allows one to solve the ODE to determine how the body area changes with time
 \begin{align}
 \label{area_predict}
-A (c_1 - \log A) \sim c_2 (t_f - t) \qquad \text{as } t \to t_f \, .
-\end{align}
-where $c_1$ and $c_2$ are constants.
-This is an {\em implicit} relationship for how the area scales down in time during erosion.
-In Fig.~\ref{area_drag}a, we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 =2.2$ and $c_2 = 30$.
+\frac{A}{A_0} \left( 1 - c_1 \log{\frac{A}{A_0}} \right) \sim \frac{t_f - t}{t_f} \quad \text{as } t \to t_f \, .
+\end{align}
+Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area, and $c_1$ is a free constant.
+The above is an {\em implicit} relationship for how the area scales down in time during erosion.
+In Fig.~\ref{area_drag}a, we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 = 0.24$ a fit parameter.
 The comparison shows close agreement between the two (they are indistinguishable).
@@
 The figure shows the drag to decrease  gradually at first, then abruptly tend to zero in the final moments of the body vanishing.
-This behavior is consistent with fact that drag vanishes {\em logarithmically} with $L$  in 2D Stokes flow.
+This behavior is consistent with fact that drag vanishes {\em logarithmically} with body-size $a$  in 2D Stokes flow.
 We also show in the figure the separate contributions of the viscous and the pressure drag.
@@
 
-As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
-\begin{align}
-\label{viscdrag}
-F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
-\end{align}
-This scaling law is shown in the figure (red, dotted curve) and shows good agreement with the viscous drag.
-Of course, \eqref{viscdrag} is less exact than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.
+As a final check, we can estimate the drag (per unit span) using slender-body theory via the formula
+\begin{align}
+F_D \sim \frac{4 \pi \mu U}{\log(\ell/a)}
+\end{align}
+For a circular cylinder, $a$ is the radius and the prefactor $4 \pi$ above gives an exact result within the slender-body framework.
+To generalize to other shapes, we define $a = \sqrt{A/\pi}$ and fit $\ell$ to get $\ell = 2.3 a_0$.
+
+\todo[inline]{Clean up this section}
 

### 2018-03-06 docs/methods/erosion_methods.tex
NM

@@
 (b) The horizontal drag (black) on the body as it erodes, along with the viscous (green) and pressure (blue) contributions.
-The scaling prediction can be rearranged to give estimate \eqref{viscdrag} for the viscous drag (dotted red).}
+The scaling prediction can be rearranged to give estimate \eqref{dragscaling} for the viscous drag (dotted red).}
 \label{area_drag}
@@
 \begin{align}
-F_D \sim \frac{4 \pi \mu U}{\log(\ell/a)}
-\end{align}
-For a circular cylinder, $a$ is the radius and the prefactor $4 \pi$ above gives an exact result within the slender-body framework.
+\label{dragscaling}
+\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}
+\end{align}
+For a {\em circular} cylinder, $a$ is the radius and the normalization factor $4 \pi$ is exact within the slender-body framework.
 To generalize to other shapes, we define $a = \sqrt{A/\pi}$ and fit $\ell$ to get $\ell = 2.3 a_0$.

### 2018-03-07 docs/methods/erosion_methods.tex
small changes to paper

@@
 A challenge with erosion is that it creates corners at points on the
-body where the shear stress vanishes.  While recent work does allow for
-integral equation methods to resolve corners, we employ a different
-method.  
-\todo[inline]{Maybe point out some drawbacks of using one of these BIE methods that allows corners.
-For example, are these methods more conceptually complex and/or more expensive?
-Maybe they are not quite at a mature stage for application?
-Another point: in the simulations we cannot predict where corners will form and so would have to identify them on the fly.
-Would this cause a problem if we tried to use a corner-resolving BIE?}
-\todo[inline]{Could say our approach is simpler because  by smoothing corners, we can use the bare-bones BIE methods that are more well established compared to these newer, corner-resolving methods.
-Just some thoughts.}
-First, we add a regularization term to the shear stress to
+body where the shear stress vanishes.  There is recent work for solving
+boundary integral equations in geometries with corners by using
+carefully chosen local expansions around each corner~\cite{rac-ser2017,
+ser-rok2016} or panel-based graded meshes~\cite{hel2011,
+gil-hao-mar2014, bre2012}.  The limitation of these methods is that they
+require the corner's location, a non-uniform spaced mesh, and some of
+the methods have a large condition number.  So that we can use a uniform
+grid, we instead slightly modify the geometry to maintain sufficient
+regularity.  First, we add a regularization term to the shear stress to
 penalize regions of high curvature.  Second, we apply a Gaussian filter
@@
 
-\todo[inline]{These are some of my thoughts on reworking this first paragraph. See if you like it.}
+%\todo[inline]{These are some of my thoughts on reworking this first paragraph. See if you like it.}
 We begin by making two fundamental design choices: first, we restrict ourselves to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
@@
 
-\todo[inline]{This is the original below:}
-There are two main limitations of the current
-work.  First, the flow is assumed to be two-dimensional.  However, by
-assuming that the flow is two-dimensional, we are able to simulate the
-erosion of more bodies and with higher resolution than would be
-available in three dimensions.  Moreover, several flows can be described
-to good accuracy under a two-dimensional approximation, but certain
-phenomena occur only in three dimensions.  Extending the current work to
-three dimensions is possible with a boundary integral equation
-formulation.  In particular, the fluid solvers exist~\cite{mal-bir2015},
-and the main challenges of a BIE solver have been addressed by other
-groups including surface representation~\cite{yin-bir-zor2006,
-vee-rah-bir-zor2011}, near-singular integration~\cite{yin-bir-zor2006,
-kli-tor2016b}, and fast summation methods~\cite{yin-bir-zor2004,
-ros-ols2015}.  The more significant challenge of extending our work to
-three dimensions is guaranteeing that the mesh does not become
-distorted, which can be done, for example, by using an extension of the
-two-dimensional {\thL} formulation~\cite{amb-sie-tlu2013}.
-
-The second limitation is that the eroding bodies are fixed.  Mitchell
-and Spagnolie~\cite{mit-spa2016} simulate a single mobile eroding body
-in three dimensions~\cite{mit-spa2016}, but additional challenges are
-caused when there are multiple bodies. In particular, especially in
-dense suspensions, bodies can become extremely close to one another, and
-the interaction between the bodies is difficult to resolve unless the
-underlying mesh is refined to levels that are intractable. In future
-work we plan to consider mobile eroding bodies by including a small
-force and torque to prevent unphysical contact~\cite{lu-rah-zor2017}.
+%\todo[inline]{This is the original below:}
+%There are two main limitations of the current
+%work.  First, the flow is assumed to be two-dimensional.  However, by
+%assuming that the flow is two-dimensional, we are able to simulate the
+%erosion of more bodies and with higher resolution than would be
+%available in three dimensions.  Moreover, several flows can be described
+%to good accuracy under a two-dimensional approximation, but certain
+%phenomena occur only in three dimensions.  Extending the current work to
+%three dimensions is possible with a boundary integral equation
+%formulation.  In particular, the fluid solvers exist~\cite{mal-bir2015},
+%and the main challenges of a BIE solver have been addressed by other
+%groups including surface representation~\cite{yin-bir-zor2006,
+%vee-rah-bir-zor2011}, near-singular integration~\cite{yin-bir-zor2006,
+%kli-tor2016b}, and fast summation methods~\cite{yin-bir-zor2004,
+%ros-ols2015}.  The more significant challenge of extending our work to
+%three dimensions is guaranteeing that the mesh does not become
+%distorted, which can be done, for example, by using an extension of the
+%two-dimensional {\thL} formulation~\cite{amb-sie-tlu2013}.
+%
+%The second limitation is that the eroding bodies are fixed.  Mitchell
+%and Spagnolie~\cite{mit-spa2016} simulate a single mobile eroding body
+%in three dimensions~\cite{mit-spa2016}, but additional challenges are
+%caused when there are multiple bodies. In particular, especially in
+%dense suspensions, bodies can become extremely close to one another, and
+%the interaction between the bodies is difficult to resolve unless the
+%underlying mesh is refined to levels that are intractable. In future
+%work we plan to consider mobile eroding bodies by including a small
+%force and torque to prevent unphysical contact~\cite{lu-rah-zor2017}.
 
@@
 our numerical solution.
-
-\todo[inline]{Dump of text}
-Other models for erosion include ones that use an erosion rate that is
-proportional to a power of the magnitude of the shear
-stress~\cite{par-izu2000}, or ones that use a critical shear stress
-below which erosion does not occur~\cite{lag2000}.
-\todo[inline]{Dump of text}
 
@@
 
-We use a quasi-static approximation.  That is, at each time step, we
-freeze the geometry, solve the incompressible Stokes equations, and then
-update the geometry according to the erosion model.  The two steps
-inside the red rectangle describes a time step in the quasi-static
-approximation.
-\todo[inline]{Appeal to separation of scales to justify this quasi-static approximation; i.e.~the timescale of erosion is much longer than that of the flow.}
-
-%A flow diagram is illustrated in Figure~\ref{fig:workflow}.  
-%\begin{figure}[htpb]
-%  \centering
-%  \input{figs/workflow.tikz}
-%  \caption{\label{fig:workflow}A caption.}
-%\end{figure}
+To perform the simulations, we freeze the geometry at each time step,
+solve the incompressible Stokes equations, and then update the geometry
+according to the erosion model.  The separation between these two
+processes is justified since the time scale of erosion is much longer
+than that of the flow.
+
+%We use a quasi-static approximation.  That is, at each time step, we
+%freeze the geometry, solve the incompressible Stokes equations, and then
+%update the geometry according to the erosion model.  The two steps
+%inside the red rectangle describes a time step in the quasi-static
+%approximation.
+%\todo[inline]{Appeal to separation of scales to justify this quasi-static approximation; i.e.~the timescale of erosion is much longer than that of the flow.}
 
@@
 
+Other models for erosion include ones that use an erosion rate that is
+proportional to a power of the magnitude of the shear
+stress~\cite{par-izu2000}, or ones that use a critical shear stress
+below which erosion does not occur~\cite{lag2000}.
+
 To model erosion, the normal velocity is  proportional to the absolute
@@
 
-In this section, we describe the boundary integral equations employed for the fluid
-equations \cite{Moore2007}
+In this section, we describe the boundary integral equations employed
+for the fluid equations \cite{Moore2007}
 \todo[inline]{Bryan do you want to add a bunch of references to your boundary integral papers here (or somewhere else)?}

### 2018-03-08 docs/methods/erosion_methods.tex
Added values to GMRES table.
NM

@@
 \end{align}
-The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity gives rise to a diffusive term in the tangent angle $\theta$.
+The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity is associated with diffusion of the tangent angle $\theta$.
 This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$).
@@
 \begin{center}
-\caption{GMRES Iterations
+\caption{GMRES Iterations: the tolerance is 1E-8.
 }
@@
 %
-10	& 223	& 32	    	& ?	\\
-15	& 292	& 64    	& ?	\\
-20	& 363	& 128	& ?	\\
-30	& 496	& 256	& ?	\\
-40	& 676	& 512	& ?	\\
-50	& 991	& 1024	& ?	\\
+10	& 223	& 32	    	& 228	\\
+15	& 292	& 64    	& 226	\\
+20	& 363	& 128	& 223	\\
+30	& 496	& 256	& 223	\\
+40	& 676	& 512	& 223	\\
+50	& 991	& 1024	& 223	\\
 %

### 2018-03-08 docs/methods/erosion_methods.tex
NM

@@
 \end{align}
-The careful reader will notice that in \eqref{thetaSeries}, we have decomposed $\theta(\alpha)$ into a linear component and a periodic component.
+The careful reader will notice that in \eqref{thetaSeries} we have decomposed $\theta(\alpha)$ into a linear component and a periodic component.
 In spectral space,~\eqref{eqn:thetaevo2} produces the system of ODEs
@@
 \end{align}
-Since $\zeta >0$, the exponential term always {\em suppresses} high-frequencies in proportion to $k^2$.
+Since $\zeta >0$, the exponential term always {\em suppresses} high-frequencies (exponentially with $k^2$).
 In other words, this is a smoothing term.
@@
 \end{align}
-Once again, both exponential terms act to smooth geometry in proportion to $k^2$. Finally, to track the reference point, $\mean{x}$, we simply apply the same RK2 method to \eqref{eq:xsurf}.
-
-We point out that most exponential integrators use some form of quadrature to treat \eqref{eq:mu}, but, here, we have simply applied the same RK2 method that is used for the rest of the system.
+Once again, both exponential terms act to smooth geometry. Finally, to track the reference point, $\mean{x}$, we simply apply the same RK2 method to \eqref{eq:xsurf}.
+
+We point out that most exponential integrators use some form of quadrature to treat \eqref{eq:mu}, but, here, we have simply applied the same RK2 method used for the rest of the system.
 We believe this to be a simple, systematic approach to arrive at a self-consistent discretization of desired accuracy because it avoids choices regarding which quadrature to use (midpoint, trapezoid, Simpson's, etc.) and can be easily generalized to other time-stepping methods, such as fourth-order Runge-Kutta.
@@
 Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times.
-Here, color represents the vorticity of the surrounding flow, which, when evaluated on the boundary, corresponds to the shear stress and thus the local erosion rate.
+Here, color represents the vorticity of the surrounding flow.
+When evaluated on the boundary, vorticity corresponds to the shear stress and thus the local erosion rate.
 As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it.
@@
 As the body nears the final stages of erosion (dark red), the stress actually becomes slightly higher near the stagnation points.
-A close look reveals that {\em at} the stagnation points, the stress always vanishes, though in a region that becomes increasingly narrow.
+A close look reveals that the stress always vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow.
 
@@
 
-Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress is growing as the body vanishes.
+Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress is increasing as the body vanishes.
 This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / a$, in which drag is inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is taken to be the radius).
@@
 In Fig.~\ref{area_drag}(b), we show the horizontal drag $F_D$ measured on the body as it erodes.
-Note that, in the context of 3D slender-body theory, $F_D$ is drag per unit span.
-The figure shows the drag to decrease  gradually at first, then abruptly tend to zero in the final moments of the body vanishing.
+Note that, in the context of 3D slender-body theory, this $F_D$ should be interpreted as the drag per unit span.
+The figure shows the drag to decrease  gradually at first, then abruptly tend to zero in the final moments as the body vanishes.
 This behavior is consistent with fact that drag vanishes {\em logarithmically} with body-size $a$  in 2D Stokes flow.
@@
 Initially, these two contributions are comparable, with a slightly greater level of pressure drag.
-However, as the body erodes and assumes a more slender form, the pressure drag vanishes much more rapidly than viscous drag.
+However, as the body erodes and assumes a more slender form, the pressure drag decays more rapidly and viscous drag dominates.
 

### 2018-03-11 docs/methods/erosion_methods.tex
NM

@@
 numerical methods in both space and time are described.
-Section~\ref{s:results} gives several numerical examples.  Finally,
+Section~\ref{SingleResults} gives several numerical examples.  Finally,
 concluding remarks are made in Section~\ref{s:conclusions}
@@
 %%-----------------------------------------------------------------%%
-\section{Results}
-\label{s:results}
-With the description of the methods complete, we now present numerical
-results on bodies eroding in Stokes flow. We first discuss the case of a
-single body, as certain features can be predicted analytically and thus
-used for validation. We then discuss the erosion of multiple bodies and
-highlight important differences that arise compared to the single-body
-case.
+\section{Results: single-body erosion}
+\label{SingleResults}
+With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow.
+We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation.
+In Section \ref{MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.
 
@@
 
-\subsection{Scaling law for the vanishing rate}
+\subsection{Scaling laws for area and drag}
 \label{sec:scaling}
@@
 % Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+\subsection{Fixed-area simulations}
 
@@
 
-\subsection{Multiple-body simulations}
+\section{Results: multi-body erosion}
+\label{MultiResults}
+
+\subsection{Fixed pressure drop condition and validation}
 
@@
 
-Briefly, to confirm that the rescaling does not alter accuracy, we show in Table \ref{convtab} a convergence test for a 20-body simulation with the condition of fixed pressure drop imposed.
-The table shows the method to retain second-order accuracy in time.
+Briefly, to verity that the rescaling does not alter accuracy, we show in Table \ref{convtab} a convergence test for a 20-body simulation with the condition of fixed pressure drop imposed.
+The table confirms that the method retains second-order accuracy in time.
 In the last column, we show the computational times, indicating that the 20-body simulations require more runtime than the single-body case.
@@
 
+\subsection{Multi-body erosion}
+
 We now discuss some physical aspects of multi-body erosion revealed by our simulations.

### 2018-03-11 docs/methods/erosion_methods.tex
NM

@@
 We now discuss some physical aspects of multi-body erosion revealed by our simulations.
-In Fig.~\ref{fig:06bodies} we show a simulation of 6 eroding bodies, each initially circles of various sizes and positions.
+Figure~\ref{fig:06bodies} shows a simulation of 6 eroding bodies, each initially circles of various sizes and positions.
 Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerable.
-As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable (such as the foremost and aft-most points on the body).
+As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable.
 Rather, when and where these sharp features develop depends on inter-body feedback as mediated by the Stokes flow.
@@
 Interestingly, erosion appears to preferentially remove material from these regions of near contact, as the narrow spacing between bodies expands rather rapidly.
-For example, the spacing between bodies 1 \& 2 was initially very small but is already comparable to the spacing between bodies 3 \& 4 by the second frame.
-Even more interesting, the bodies tend to develop flat faces wherever near contact occurs, which leads to the appearance of straight channels in between bodies.
-Such channels are apparent between bodies 1 \& 2, 3 \& 5, and 5 \& 6, and they {persist} for the duration of the simulation.
-
-The vorticity field (color) is useful to infer both the regions of highest shear and the regions of most intense flow.
-Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel running horizontally, below bodies 1 \& 2 and above bodies 3 \& 6.
-This main channel widens the fastest as the high-flow rate leads to greater shearing on the boundaries.
-As discussed above, the pressure drop across the cell is fixed in these simulations, and so as the bodies diminish the flow rate increases, which can be seen by the increase in the vorticity magnitude.
+For example, the spacing between bodies 1 \& 2 is initially very small, but by the second frame, is comparable to the spacing between bodies 3 \& 4.
+Even more interesting, the bodies tend to develop flat faces where there are near contacts.
+This effect leads to the appearance of straight channels in between bodies, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
+Once formed, these straight channels persist until the bodies have nearly vanished.
+
+The vorticity field not only allows us to visualize regions of high shear, but also allows us to identify preferred channels with most intense flow.
+Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
+This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \&2 or 3 \& 5 or 5 \& 6) follow.
+Since the pressure drop across the cell is fixed, the overall flow rate increases as the bodies erode.
+This can be seen by the overall vorticity magnitude growing in time.
 By the final frame shown, body 4 has vanished completely and our method handles this event seamlessly.

### 2018-03-11 docs/methods/erosion_methods.tex
small changes to BIE section

@@
 require the corner's location, a non-uniform spaced mesh, and some of
-the methods have a large condition number.  So that we can use a uniform
-grid, we instead slightly modify the geometry to maintain sufficient
-regularity.  First, we add a regularization term to the shear stress to
-penalize regions of high curvature.  Second, we apply a Gaussian filter
-to smooth the absolute value of the shear stress before the body shape
-is updated.
+the methods have a large condition number.  One solution is to use two
+meshes---one for the quadrature the other for the interface tracking.
+Then, interpolation between the two grids is required, and this is the
+approach taken by Ojala and Tornberg~\cite{oja-tor2015}.  Instead of
+using two grids and interpolation operators, we only require the uniform
+grid by slightly modify the geometry to maintain sufficient regularity.
+First, we add a regularization term to the shear stress to penalize
+regions of high curvature.  Second, we apply a Gaussian filter to smooth
+the absolute value of the shear stress before the body shape is updated.
 
@@
 %\todo[inline]{These are some of my thoughts on reworking this first paragraph. See if you like it.}
-We begin by making two fundamental design choices: first, we restrict ourselves to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
-The restriction to 2D allows us to simulate the erosion of many bodies (order 50-100) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium.
-While BIE methods are available in 3D, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
+We begin by making two fundamental design choices: first, we restrict
+ourselves to two spatial dimensions, and second the bodies are
+considered immobile (i.e.~fixed to their initial locations). The
+restriction to 2D allows us to simulate the erosion of many bodies
+(up to $50$ in this manuscript) with high resolution, giving us the
+ability to accurately characterize the erosion of a porous medium. While
+boundary integral equation (BIE) methods are available in 3D, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
 The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
@@
 In this section, we describe the boundary integral equations employed
-for the fluid equations \cite{Moore2007}
+for the fluid equations.  We will start by writing the velocity field in
+terms of the standard double-layer potential~\cite{laz1963,poz1992}.
+Since the double-layer potential representation is only able to
+represent force-free and torque-free velocity fields, Power and
+Miranda~\cite{pow-mir1987} completed the BIE formulation by introducing
+a Stokeslet and Rotlet.  This methodology was extended by Power for
+multiply-connected domains~\cite{pow1993}.  In two-dimensions, a stream
+function formulation can be used in which case the biharmonic equation
+must be solved, and this can be done using BIEs by using analytic
+function theory~\cite{gre-kro-may1996}.
+
+  \cite{Moore2007}
 \todo[inline]{Bryan do you want to add a bunch of references to your boundary integral papers here (or somewhere else)?}

### 2018-03-12 docs/methods/erosion_methods.tex
NM
small edits to text

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Erosion Model} 
+\subsection{Erosion model} 
 \label{sec:erosion}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary Integral Equation Formulation} 
+\subsection{Boundary integral equation formulation} 
 \label{sec:bies}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Computing the Shear Stress}
+\subsection{Computing the shear stress}
 \label{sec:shearStressLP}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Methods}
+\section{Numerical methods}
 \label{s:method}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Shear Stress}
+\subsection{Shear stress}
 \label{sec:shearStress}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Post Processing Quantities of Interest}
+\section{Post processing quantities of interest}
 \label{s:qoi}
@@
 %%-----------------------------------------------------------------%%
-\section{Results: single-body erosion}
+\section{Results: Single-body erosion}
 \label{SingleResults}
@@
 For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
-$\mu \umax \ell/ \log(\ell/a)$, where $a$ is a lengthscale of the cross-section and $a \ll \ell$. This relationship implies that the stress per unit span on a 2D cross-section can be estimated by
+$\mu \umax \ell/ \log(\ell/a)$, where $a$ is a length scale of the cross-section and $a \ll \ell$. This relationship implies that the stress per unit span on a 2D cross-section can be estimated by
 \begin{align}
@@
 \end{align}
-In interpreting our 2D simulations, we will treat the span, $\ell$, as fixed.
-Recall that $L$ denotes the total perimeter of the cross-section, and therefore $a$ and $L$ can often be used interchangeable in scaling analysis, since they each represent a lengthscale of the cross-section.
+In interpreting our 2D simulations, we will treat the span, $\ell$, as
+fixed. Recall that $L$ denotes the total perimeter of the cross-section,
+and therefore $a$ and $L$ can often be used interchangeable in scaling
+analysis, since they each represent a length scale of the cross-section.
 
@@
 \end{align}
-Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area, and $c_1$ is a free constant.
-The above is an {\em implicit} relationship for how the area scales down in time during erosion.
-In Fig.~\ref{area_drag}a, we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 = 0.24$ a fit parameter.
+Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area,
+and $c_1$ is a free constant. The above is an {\em implicit}
+relationship for how the area scales down in time during erosion. In
+Fig.~\ref{area_drag}(a), we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 = 0.24$ a fit parameter.
 The comparison shows close agreement between the two (they are indistinguishable).
@@
 \label{dragscaling}
-\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}
+\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}.
 \end{align}
@@
 \begin{align*}
-  f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0
+  f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f =
+  0.
 \end{align*}
@@
 \begin{align*}
-  f(\theta) = B \sin (2 \theta) + C \theta
+  f(\theta) = B \sin (2 \theta) + C \theta.
 \end{align*}
@@
 \begin{align*}
-  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0
+  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0,
 \end{align*}
@@
 \end{align*}
-This modification allows erosion sculpt the body as it normally would but artificially keeps the area fixed.
+This modification allows erosion to sculpt the body as it normally would but artificially keeps the area fixed.
 We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process at equally-spaced times.
@@
 Here, time is normalized by the same vanishing time $t_f = 1.79E-2$ as in Fig.~\ref{shrink_intface}.
-Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynold's-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
+Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
 
@@
 
-To examine the influence of the smoothing parameters, $\eps$ and $\sigma$, we show in Table~\ref{table:arangle} the measurements of aspect ratio and opening angle for different simulations.
+To examine the influence of the smoothing parameters, $\eps$ and
+$\sigma$, we show in Table~\ref{table:arangle} the measurements of the
+aspect ratio and the opening angle for different simulations.
 We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal.
@@
 
-\section{Results: multi-body erosion}
+\section{Results: Multi-body erosion}
 \label{MultiResults}
@@
 \begin{center}
-\includegraphics[width = 0.99 \textwidth]{./figs/06plots.pdf}
+\includegraphics[width = 0.85 \textwidth]{./figs/06plots.pdf}
 \caption{\label{fig:06plots} plots to go with 6 body simulation.

### 2018-03-12 docs/methods/erosion_methods.tex
small changes to paper

@@
 In this section, we describe the boundary integral equations employed
-for the fluid equations.  We will start by writing the velocity field in
-terms of the standard double-layer potential~\cite{laz1963,poz1992}.
-Since the double-layer potential representation is only able to
-represent force-free and torque-free velocity fields, Power and
-Miranda~\cite{pow-mir1987} completed the BIE formulation by introducing
-a Stokeslet and Rotlet.  This methodology was extended by Power for
-multiply-connected domains~\cite{pow1993}.  In two-dimensions, a stream
-function formulation can be used in which case the biharmonic equation
-must be solved, and this can be done using BIEs by using analytic
-function theory~\cite{gre-kro-may1996}.
-
-  \cite{Moore2007}
-\todo[inline]{Bryan do you want to add a bunch of references to your boundary integral papers here (or somewhere else)?}
-In particular, we solve the incompressible Stokes equations
-with Dirichlet boundary conditions 
+for the fluid equations.  In particular, we solve the incompressible
+Stokes equations with Dirichlet boundary conditions 
 \begin{alignat*}{3}
@@
 The boundary condition $\ff$ is the prescribed velocity $\UU$ on
-$\Gamma$, and it is zero on the grains $\gamma$.  As the viscosity $\mu$
-also sets the time scale, we take $\mu=1$.  We start by defining the
-double-layer potential
-\todo[inline]{Do you think we should flesh out this time-scale stuff more precisely?
-i.e.~By setting $\mu = 1$ and $C = 1$ (the erosion constant), what exactly is the timescale that defines our dimensionless time.}
+$\Gamma$, and it is zero on the grains $\gamma$.  Since we are
+interested in two dimensions, a stream function formulation can be used
+by recasting the governing equations as a problem in analytic function
+theory~\cite{gre-kro-may1996}.  We instead work with the primitive
+variables by writing the velocity in terms of the standard double-layer
+potential~\cite{lad1963,poz1992}
 \begin{align}
@@
 \end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  The
+where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  The double-layer potential representation is only able to
+represent force- and torque-free velocity fields, so we complete the
+velocity representation with Stokeslets and
+Rotlets~\cite{pow-mir1987,pow1993}.
+
+  \cite{Moore2007}
+As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.  We
+start by defining the double-layer potential
+\todo[inline]{Do you think we should flesh out this time-scale stuff more precisely?
+i.e.~By setting $\mu = 1$ and $C = 1$ (the erosion constant), what exactly is the timescale that defines our dimensionless time.}
+The
 double-layer potential cannot capture velocity fields corresponding to

### 2018-03-13 docs/methods/erosion_methods.tex
NM

@@
 The exponential integrator will handle the stiff term in a numerically stable fashion, while the Runge-Kutta method will treat nonlinear terms explicitly.
-Our overall time-stepping method will be second order.
+Our overall time-stepping method will be second-order accurate.
 
@@
 \end{align}
-The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity is associated with diffusion of the tangent angle $\theta$.
+The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity gives rise to diffusion of the tangent angle $\theta$.
 This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$).

### 2018-03-13 docs/methods/erosion_methods.tex
NM

@@
 \end{align}
-The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity gives rise to diffusion of the tangent angle $\theta$.
+The diffusive term on the right of \eqref{eqn:thetaevo2} results from the curvature penalization and is the stiffest term present.
 This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$).
@@
 \end{align}
-Note that the diffusive term from \eqref{eqn:thetaevo2} does not appear explicitly in \eqref{eqn:thetaevo3}, but rather is implied by the integrating factor \eqref{eq:mu}; i.e.~we have applied an exponential integrator.
+Note that the diffusive term from \eqref{eqn:thetaevo2} does not appear explicitly in \eqref{eqn:thetaevo3}, but rather is implied by the integrating factor \eqref{eq:mu}.
+This is the idea of an exponential integrator.
 We solve the resulting system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an
-explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature penalization.
+explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method so as to maximize the smoothing effect of the diffusive term.
 
@@
 \end{align}
-Once again, we must eventually compute the geometry at step $n+1$, and so we insert \eqref{eq:mu1d} into \eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
+We must eventually compute the geometry at step $n+1$, and so we insert \eqref{eq:mu1d} into \eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
 \begin{align}

### 2018-03-13 docs/methods/erosion_methods.tex
working on paper

--- 2018-03-12 docs/methods/erosion_methods.tex
@@
 flow, and the individual pores are resolved which results in a complex
-multiply-connected geometry.  A boundary integral equation is
+multiply-connected geometry.  A boundary integral equation (BIE) is
 well-suited for solving the incompressible Stokes equations in a complex
@@
 and the erosion rate (shear stress) are efficiently solved with spectral
-accuracy by using a fast-multipole-accelerated boundary integral
-equation method.  Given the rate of erosion, the shape is integrated in
-time with second-order accuracy.  All spatial derivatives are be
-computed in Fourier space, resulting in spectral accuracy in space.
-To further visualize the effect of erosion, we compute the
-vorticity of the flow (Fig.~\ref{fig:50bodies}) to visualize regions
-of high and low erosion.
+accuracy by using a fast-multipole-accelerated BIE method.  Given the
+rate of erosion, the shape is integrated in time with second-order
+accuracy.  All spatial derivatives are be computed in Fourier space,
+resulting in spectral accuracy in space.  To further visualize the
+effect of erosion, we compute the vorticity of the flow
+(Fig.~\ref{fig:50bodies}) to visualize regions of high and low erosion.
 
@@
 body where the shear stress vanishes.  There is recent work for solving
-boundary integral equations in geometries with corners by using
+BIEs in geometries with corners by using
 carefully chosen local expansions around each corner~\cite{rac-ser2017,
@@
 ability to accurately characterize the erosion of a porous medium. While
-boundary integral equation (BIE) methods are available in 3D, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
+BIEs are available in 3D, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
 The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
@@
 particulate flows, such as bubbles or droplets, and the classic book of
-Pozrikidis~\cite{poz1992} describes boundary integral formulations for
-such problems.
+Pozrikidis~\cite{poz1992} describes BIEs for such problems.
 
@@
 In this section, we describe the boundary integral equations employed
-for the fluid equations.  In particular, we solve the incompressible
+for the fluid equations.  In particular, we recast the incompressible
 Stokes equations with Dirichlet boundary conditions 
@@
   \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
-  \uu &= \ff,  && \xx \in \bd\Omega.
+  \uu &= \ff,  && \xx \in \bd\Omega,
 \end{alignat*}
-The boundary condition $\ff$ is the prescribed velocity $\UU$ on
-$\Gamma$, and it is zero on the grains $\gamma$.  Since we are
-interested in two dimensions, a stream function formulation can be used
-by recasting the governing equations as a problem in analytic function
-theory~\cite{gre-kro-may1996}.  We instead work with the primitive
-variables by writing the velocity in terms of the standard double-layer
+into an equivalent BIE.  The boundary condition $\ff$ is the prescribed
+velocity $\UU$ on $\Gamma$, and it is zero on the grains $\gamma$.
+Since we are interested in two dimensions, a stream function formulation
+can be used by recasting the governing equations as a problem in
+analytic function theory~\cite{gre-kro-may1996}.  So that our work can
+extended to three dimensions, we instead use primitive variables by
+writing the velocity in terms of the standard double-layer
 potential~\cite{lad1963,poz1992}
@@
 \end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  The double-layer potential representation is only able to
-represent force- and torque-free velocity fields, so we complete the
-velocity representation with Stokeslets and
-Rotlets~\cite{pow-mir1987,pow1993}.
-
-  \cite{Moore2007}
-As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.  We
-start by defining the double-layer potential
-\todo[inline]{Do you think we should flesh out this time-scale stuff more precisely?
-i.e.~By setting $\mu = 1$ and $C = 1$ (the erosion constant), what exactly is the timescale that defines our dimensionless time.}
-The
-double-layer potential cannot capture velocity fields corresponding to
-rigid body motions~\cite{pow-mir1987}.  The rank deficiency is removed
-by complementing the double-layer potential with a Stokeslets and
-rotlets centered inside each interior body
+where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown
+density function.  As the viscosity $\mu$ also sets the time scale, we
+take $\mu=1$.  \todo[inline]{Do you think we should flesh out this
+time-scale stuff more precisely? i.e.~By setting $\mu = 1$ and $C = 1$
+(the erosion constant), what exactly is the timescale that defines our
+dimensionless time.} \todo[inline]{This might be worth doing.  Is it
+something you can do quickly or do you want me to take a crack at it?}
+
+The double-layer potential representation is only able to represent
+force- and torque-free velocity fields, so we complete the velocity
+representation with Stokeslets and Rotlets~\cite{pow-mir1987,pow1993}.
+This is done by complementing the double-layer potential with Stokeslets
+and rotlets centered inside each interior body
 \begin{align}
@@
 \end{align*}
-removes the rank one null space that results from the compatibility
-constraint associated with the flux-free requirement of $\ff$.
+removes the rank one null space resulting from the flux-free requirement
+of $\ff$.
 
@@
 can be computed using appropriate layer potentials.  While the first
-method bypasses a step by not forming a density function, this method
-does not allow us to compute other quantities such as the vorticity.
-Therefore, we use the second method.
+method bypasses a step by forming the traction jump directly, it does
+not allow us to directly compute other quantities such as the vorticity,
+so we use the second method.
 
@@
 
-To evolve the boundaries of eroding bodies, we will use the {\thL} framework which offers certain advantages in numerically stabilizing moving-interface problems \cite{hou-low-she1994}.
-Here, $\theta$ is the local tangent angle and $L$ the total perimeter of a given boundary.
-For a boundary parametrized by arc length $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin
-\theta \right)$.
-
-For numerical stability, we modify the erosion law \eqref{eqn:erosionModel} to include a term that penalizes curvature $\kappa$.
+To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in numerically stabilizing moving-interface problems \cite{hou-low-she1994}.
+Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary.
+For a boundary parametrized by arc length $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin \theta \right)$.
+
+For numerical stability, we modify the erosion law~\eqref{eqn:erosionModel} to include a term that penalizes curvature $\kappa$.
 The idea is to prevent regions of extremely high curvature from developing, as these regions would compromise the accuracy and stability of our fluid solver.
-We thus modify \eqref{eqn:erosionModel} as follows
+We thus replace~\eqref{eqn:erosionModel} with
 \begin{align}
@@
 Above, $\mean{\cdot}$ indicates a boundary mean.
-Since a closed body has mean curvature $\mean{\kappa} = 2\pi / L$, the penalty term has mean zero and and thus preserves area.
+Since a closed body has mean curvature $\mean{\kappa} = 2\pi / L$, the penalty term has mean zero and thus preserves area.
 The only source of material loss is therefore the shear-stress itself.
@@
 The boundary of each body will be represented by a grid of collocation points.
-If we were to simply evolve the interfaces under \eqref{eqn:Vn2}, this grid would become distorted, which, if unchecked, could lead to severe tangling and numerical instability.
+If we were to simply evolve the interfaces under~\eqref{eqn:Vn2}, this grid would become distorted, which, if unchecked, could lead to severe tangling and numerical instability.
 We therefore introduce an artificial tangential velocity $\Vs$ that always keeps the grid points equally spaced in arclength \cite{hou-low-she1994}.
@@
 \begin{align}
-\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn} \, ,
+\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn} \, .
 \end{align}
@@
 \eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} +
-\thalpha \Vs \right).
+\thalpha \Vs \right)\,.
 \end{align}
@@
 \label{eq:xsurf}
-\frac{d}{dt} \mean{\xx} = \mean{ V_s \ss + V_n \nn }
+\frac{d}{dt} \mean{\xx} = \mean{ V_s \ss + V_n \nn } \, .
 \end{align}
 We note that tracking the center of mass is also a valid choice, but the surface mean gives a somewhat simpler formula.
-Equations \eqref{eqn:Levo1}--\eqref{eq:xsurf} comprise the main system of equations to be solved numerically in Section~\ref{sec:timeStepping}.
+Equations~\eqref{eqn:Levo1}--\eqref{eq:xsurf} comprise the main system of equations to be solved numerically in Section~\ref{sec:timeStepping}.
 
@@
 interface according to equations~\eqref{eqn:Levo1}
-and~\eqref{eqn:thetaevo1} are described. So that we can form stable
+and~\eqref{eqn:thetaevo1} is described. So that we can form stable
 simulations with long time horizons, we use numerical methods that
@@
 \label{sec:shearStress}
-We have decomposed the deformation tensor into the contributions due to
-three different terms.  The contributions from the Stokeslets and the
-rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
-\gamma$.  For the layer potential term, we would like to use the
-trapezoid rule, but the kernel of the deformation tensor due to the
-double-layer potential~\eqref{eqn:shearStressDLP} 
+We have decomposed the deformation tensor into contributions from three
+different terms.  The contributions from the Stokeslets and the rotlets
+can be directly evaluated since $\rr \neq 0$ for all $\xx \in \gamma$.
+For the shear stress of the double-layer potential, we would like to use
+the trapezoid rule. The kernel of the deformation tensor due to
+the double-layer potential~\eqref{eqn:shearStressDLP} is 
 \begin{align*}
@@
     8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right),
-\end{align*}
-has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
-\rightarrow \xx$.  The singularity strength can be reduced since the
-velocity corresponding to a constant density function is
+  \right).
+\end{align*}
+Unfortunately, this kernel has a singularity that is asymptotic to
+$\bigO(\rho^{-2})$ when $\yy \rightarrow \xx$, and this is too strong
+for the trapezoid rule.  The singularity strength can be reduced since
+the velocity corresponding to a constant density function is
 constant~\cite{poz1992}.  Therefore, the deformation tensor of the
@@
 deformation tensor~\eqref{eqn:shearStressJump} is computed with Fourier
-differentiation.  Then, the shear stress is computed by multiplying the
+differentiation.  Finally, the shear stress is computed by multiplying the
 deformation tensor by the normal vector, and taking the inner product
@@
 With the shear stress computed, we are now ready to numerically evolve the boundary of each body using the {\thL} framework.
-The main equations to be solved are \eqref{eqn:Levo1}--\eqref{eq:xsurf}.
-In Section~\ref{sec:thetaL} we introduced a curvature-penalizing term into the erosion law \eqref{eqn:Vn}.
-This term suppresses high-frequency oscillations, but also introduces {\em stiffness} into evolution equation \eqref{eqn:thetaevo1}.
-We will therefore use a combined exponential-integrator/Runge-Kutta method to solve system \eqref{eqn:Levo1}--\eqref{eq:xsurf}.
+The main equations to be solved are~\eqref{eqn:Levo1}--\eqref{eq:xsurf}.
+In Section~\ref{sec:thetaL} we introduced a curvature-penalizing term into the erosion law~\eqref{eqn:Vn}.
+This term suppresses high-frequency oscillations, but also introduces {\em stiffness} into evolution equation~\eqref{eqn:thetaevo1}.
+We will therefore use a combined exponential-integrator/Runge-Kutta method to solve system~\eqref{eqn:Levo1}--\eqref{eq:xsurf}.
 The exponential integrator will handle the stiff term in a numerically stable fashion, while the Runge-Kutta method will treat nonlinear terms explicitly.
@@
 
-First, we must address a second potential source of numerical instability.
-The erosion law \eqref{eqn:Vn} depends on the {\em absolute value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$ changes sign (i.e.~at a stagnation point).
-The corner in $\atau$ introduces high frequencies into \eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
+First, we must address a second potential source of numerical
+instability. The erosion law~\eqref{eqn:Vn} depends on the {\em absolute
+value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$
+changes sign (i.e.~at a stagnation point). The corner in $\atau$
+introduces high frequencies into~\eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
 To avoid these difficulties, we smooth $\atau$ via a narrow Gaussian filter of width $\sigma$
@@
 \end{align}
-This smoothing further suppresses the feedback of high frequencies betweeen $\atau$ and body shape.
-
-We now consider the system of evolution equations given by \eqref{eqn:Levo1}--\eqref{eq:xsurf}. For convenience, we introduce the following variables
+This smoothing further suppresses the feedback of high frequencies between $\atau$ and the body shape.
+
+We now consider the system of evolution equations given by~\eqref{eqn:Levo1}--\eqref{eq:xsurf}. For convenience, we introduce the following variables
 \begin{align}
@@
 \end{align}
-Then, ~\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1} can be compactly expressed as
+Then,~\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1} can be compactly expressed as
 \begin{align}
@@
 \end{align}
-The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity is associated with diffusion of the tangent angle $\theta$.
+The first term on the right-hand-side of~\eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity is associated with diffusion of the tangent angle $\theta$.
 This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$).
-Meanwhile, $\NLterm$, represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
+Meanwhile, $\NLterm$ represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
 Since the local shear stress depends on interactions between bodies, $\NLterm$ is both a nonlinear and nonlocal.
@@
 \end{align}
-The careful reader will notice that in \eqref{thetaSeries} we have decomposed $\theta(\alpha)$ into a linear component and a periodic component.
+The careful reader will notice that in~\eqref{thetaSeries} we have decomposed $\theta(\alpha)$ into a linear component and a periodic component.
 In spectral space,~\eqref{eqn:thetaevo2} produces the system of ODEs
 \begin{align*}
-\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \widehat{\NLterm}_k \, .
+\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \widehat{\NLterm}_k,
+\qquad k=-N_\iin/2,\ldots,N_\iin/2-1\, .
 \end{align*}
@@
 & \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \widehat{\NLterm}_k \, ,
-\qquad k = -N_\iin/2, \ldots, N_\iin/2 -1
-\end{align}
-Note that the diffusive term from \eqref{eqn:thetaevo2} does not appear explicitly in \eqref{eqn:thetaevo3}, but rather is implied by the integrating factor \eqref{eq:mu}; i.e.~we have applied an exponential integrator.
+\qquad k = -N_\iin/2, \ldots, N_\iin/2 -1.
+\end{align}
+Note that the diffusive term from~\eqref{eqn:thetaevo2} does not appear explicitly in~\eqref{eqn:thetaevo3}, but rather is implied by the integrating factor~\eqref{eq:mu}; i.e.~we have applied an exponential integrator.
 We solve the resulting system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an
 explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature penalization.
-
-At the first stage of RK2 (the half step) we discretize \eqref{eq:mu}--\eqref{eqn:thetaevo3} as
+\todo[inline]{Last sentence might need to be clarified.  Not sure about
+using `so as to'}
+
+At the first stage of RK2 (the half step) we discretize~\eqref{eq:mu}--\eqref{eqn:thetaevo3} as
 \begin{align}
 \label{eq:mu12d}
-& \mu_k^{(n+1/2)} = \mu_k^{(n)} \exp \left( \eps k^2 \frac{\Dt}{2} \zeta^{(n)} \right) \\
+& \mu_k^{(n+1/2)} = \mu_k^{(n)} \exp \left( \eps k^2 \frac{\Dt}{2}
+\zeta^{(n)} \right), \\
 \label{eq:L12d}
-& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)} \\
+& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)}, \\
 \label{eq:th12d}
 & \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \mu_k^{(n)} \thhat_k^{(n)}}{\Dt/2} 
-= \mu_k^{(n)} \hat{\NLterm}_k^{(n)}
+= \mu_k^{(n)} \hat{\NLterm}_k^{(n)},
 \end{align}
@@
 At the next stage of RK2 it will be necessary to evaluate derivates at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the body shapes must be known.
-We therefore insert \eqref{eq:mu12d} into \eqref{eq:th12d} and solve for $\theta^{(n+1/2)}$, giving
+We therefore insert~\eqref{eq:mu12d} into~\eqref{eq:th12d} and solve for $\theta^{(n+1/2)}$, giving
 \begin{align}
@@
 
-At the second stage of RK2, we discretize \eqref{eq:mu}--\eqref{eqn:thetaevo3} as 
+At the second stage of RK2, we discretize~\eqref{eq:mu}--\eqref{eqn:thetaevo3} as 
 \begin{align}
 \label{eq:mu1d}
-& \mu_k^{(n+1)} = \mu_k^{(n)} \exp \left( \eps k^2 {\Dt} \, \zeta^{(n+1/2)} \right) \\
+& \mu_k^{(n+1)} = \mu_k^{(n)} \exp \left( \eps k^2 {\Dt} \,
+\zeta^{(n+1/2)} \right), \\
 \label{eq:L1d}
@@
 \end{align}
-Once again, we must eventually compute the geometry at step $n+1$, and so we insert \eqref{eq:mu1d} into \eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
+Once again, we must eventually compute the geometry at step $n+1$, and so we insert~\eqref{eq:mu1d} into~\eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
 \begin{align}
@@
 \end{align}
-Once again, both exponential terms act to smooth geometry. Finally, to track the reference point, $\mean{x}$, we simply apply the same RK2 method to \eqref{eq:xsurf}.
-
-We point out that most exponential integrators use some form of quadrature to treat \eqref{eq:mu}, but, here, we have simply applied the same RK2 method used for the rest of the system.
+Once again, both exponential terms act to smooth the geometry. Finally, to track the reference point, $\mean{x}$, we simply apply the same RK2 method to~\eqref{eq:xsurf}.
+
+We point out that most exponential integrators use some form of quadrature to treat~\eqref{eq:mu}, but, here, we have simply applied the same RK2 method used for the rest of the system.
 We believe this to be a simple, systematic approach to arrive at a self-consistent discretization of desired accuracy because it avoids choices regarding which quadrature to use (midpoint, trapezoid, Simpson's, etc.) and can be easily generalized to other time-stepping methods, such as fourth-order Runge-Kutta.
@@
 \includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
-\caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction \eqref{area_predict} (dotted red).
+\caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction~\eqref{area_predict} (dotted red).
 The two are nearly indistinguishable.
 (b) The horizontal drag (black) on the body as it erodes, along with the viscous (green) and pressure (blue) contributions.
-The scaling prediction can be rearranged to give estimate \eqref{dragscaling} for the viscous drag (dotted red).}
+The scaling prediction can be rearranged to give estimate~\eqref{dragscaling} for the viscous drag (dotted red).}
 \label{area_drag}

### 2018-03-13 docs/methods/erosion_methods.tex

@@
 \end{align}
-The first term on the right-hand-side of~\eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity is associated with diffusion of the tangent angle $\theta$.
+The diffusive term on the right of~\eqref{eqn:thetaevo2} results from the curvature penalization and is the stiffest term present.
 This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$).
-Meanwhile, $\NLterm$ represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
+Meanwhile, $\NLterm$, represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
 Since the local shear stress depends on interactions between bodies, $\NLterm$ is both a nonlinear and nonlocal.
@@
 \end{align}
-Note that the diffusive term from~\eqref{eqn:thetaevo2} does not appear explicitly in~\eqref{eqn:thetaevo3}, but rather is implied by the integrating factor~\eqref{eq:mu}; i.e.~we have applied an exponential integrator.
+Note that the diffusive term from~\eqref{eqn:thetaevo2} does not appear explicitly in~\eqref{eqn:thetaevo3}, but rather is implied by the integrating factor~\eqref{eq:mu}.
+This is the idea of an exponential integrator.
 We solve the resulting system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an
-explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature penalization.
+explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method so as to maximize the smoothing effect of the diffusive term.
 \todo[inline]{Last sentence might need to be clarified.  Not sure about
@@
 \end{align}
-Once again, we must eventually compute the geometry at step $n+1$, and so we insert~\eqref{eq:mu1d} into~\eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
+We must eventually compute the geometry at step $n+1$, and so we insert~\eqref{eq:mu1d} into~\eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
 \begin{align}

### 2018-03-13 docs/methods/erosion_methods.tex
made small changes throughout

@@
 by, first, introducing a tangential velocity field to maintain a grid
-that is equispaced in arc length, but that does not affect the dynamics,
+that is equispaced in arclength, but that does not affect the dynamics,
 and, second, a curvature penalization term.  Furthermore, the frame of
@@
 Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary.
-For a boundary parametrized by arc length $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin \theta \right)$.
+For a boundary parametrized by arclength $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin \theta \right)$.
 
@@
 
-In the following, we parameterize each boundary by normalized arc length, $\alpha = 2 \pi s / L$. In terms of $\alpha$, the curvature is given by
+In the following, we parameterize each boundary by normalized arclength, $\alpha = 2 \pi s / L$. In terms of $\alpha$, the curvature is given by
 \begin{align}
@@
 
-The boundary of each body will be represented by a grid of collocation points.
-If we were to simply evolve the interfaces under~\eqref{eqn:Vn2}, this grid would become distorted, which, if unchecked, could lead to severe tangling and numerical instability.
-We therefore introduce an artificial tangential velocity $\Vs$ that always keeps the grid points equally spaced in arclength \cite{hou-low-she1994}.
-The appropriate tangential velocity satisfies
+The boundary of each body will be represented by a grid of collocation
+points. If we were to simply evolve the interfaces
+under~\eqref{eqn:Vn2}, this grid would become distorted, which, if
+unchecked, could lead to severe tangling and numerical instability. We
+therefore introduce an artificial tangential velocity $\Vs$ that always
+keeps the grid points equally spaced in arclength \cite{hou-low-she1994}. The appropriate tangential velocity satisfies 
 \begin{align}
@@
 target points in the fluid domain, the resulting layer potentials
-involve integrands that are periodic, so the trapezoid rule guarantees
-spectral accuracy since the integrand is smooth~\cite{tre-wei2014}.
-However, if the target point is close to a boundary, a nearly-singular
-integrand must be integrated, and this requires upsampling that is
-described in Section~\ref{sec:NSI}.  When the target points is on the
-boundary, the integrands involve singularities that are evaluated by
-combining singularity subtraction and odd-even
-integration~\cite{sid-isr1988}.
+involve integrands that are periodic and smooth, so the trapezoid rule
+guarantees spectral accuracy~\cite{tre-wei2014}.  However, if the target
+point is close to $\bd \Omega$, a nearly-singular integrand must be
+integrated, and this requires upsampling that is described in
+Section~\ref{sec:NSI}.  When the target points is on the boundary, the
+integrands involve singularities that are evaluated by combining
+singularity subtraction and odd-even integration~\cite{sid-isr1988}.
 
@@
 \begin{align}
-  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+  p^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
@@
 and the pressure due to the rotlets is zero.  Therefore, the pressure is
-\begin{align*}
-  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
+\begin{alignat*}{3}
+  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), &&\xx \in \Omega,\\
   p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
-              p^{S}(\xx), && \xx \in \bd\Omega.
-\end{align*}
+              p^{S}(\xx), \quad && \xx \in \bd\Omega.
+\end{alignat*}
 To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid
@@
     \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
-    \quad \xx \in \bd\Omega
+    \quad \xx \in \bd\Omega.
 \end{align*}
@@
 \label{sec:NSI}
-The layer potentials for the~\eqref{eqn:velocityDLP},
+The layer potentials for the velocity~\eqref{eqn:velocityDLP},
 vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP}
@@
 necessary that we resolve the integrands for arbitrarily close target
-points
+points.
 
@@
 trapezoid rule is acceptable for points $\xx$ that are more than 5
-arclength spacings from $\bd\Omega$.
-
-For points that are closer than 5 arclength spacings to $\bd\Omega$, we
-use an upsampled trapezoid rule.  The required upsampling of the
-geometry and the density function is done with a Fourier interpolant.
-To minimize the number of discretization points that are used to
-approximate the layer potential~\eqref{eqn:layerPotential}, we use the
-same upsampling rate for all target points that are in the same dyadic
-interval (Table~\ref{tbl:upsampling}).  For points that are closer than
-$5/16$ of an arclength from $\bd\Omega$, a value of 0 is simply assigned
-to $\phi$.
+arclength spacings from $\bd\Omega$. For points that are closer than 5
+arclength spacings to $\bd\Omega$, we use an upsampled trapezoid rule.
+The required upsampling of the geometry and the density function is done
+with a Fourier interpolant.  To minimize the number of discretization
+points that are used to approximate the layer
+potential~\eqref{eqn:layerPotential}, we use the same upsampling rate
+for all target points that are in the same dyadic interval
+(Table~\ref{tbl:upsampling}).  For points that are closer than $5/16$ of
+an arclength from $\bd\Omega$, a value of 0 is simply assigned to
+$\phi$.
 \newcolumntype{V}{>{\centering\arraybackslash}m{4em}}
@@
   $d(\xx,\bd\Omega)$ &
-  $[5h,\infty]$ &
-  $[\frac{5}{2}h,5h]$ &
-  $[\frac{5}{4}h,\frac{5}{2}h]$ & 
-  $[\frac{5}{8}h,\frac{5}{4}h]$ &
-  $[\frac{5}{16}h,\frac{5}{8}h]$ & \\ [2ex] 
+  $\left[5h,\infty\right]$ &
+  $\left[\frac{5}{2}h,5h\right]$ &
+  $\left[\frac{5}{4}h,\frac{5}{2}h\right]$ & 
+  $\left[\frac{5}{8}h,\frac{5}{4}h\right]$ &
+  $\left[\frac{5}{16}h,\frac{5}{8}h\right]$ & \\ [2ex] 
   \hline
@@
 \end{tabular}
-\caption{\label{tbl:upsampling}The upsampling rate used in our
-near-singular integration scheme.  $d(\xx,\bd\Omega)$ is the distance
-between a points $\xx \in \Omega$ and the boundary of the domain
-$\bd\Omega$, and $h$ is an arclength spacing.}
+\caption{\label{tbl:upsampling}The upsampling rate of our near-singular
+integration scheme.  $d(\xx,\bd\Omega)$ is the distance between a point
+$\xx \in \Omega$ and the boundary of the domain $\bd\Omega$, and $h$ is
+an arclength spacing.}
 \end{table}
@@
 eroding bodies are also sedimenting, bodies will come too close to one
-another for upsampling to only used.  Therefore, we plan to implement a
-near-singular integration scheme that uses either near-singular
-interpolation~\cite{qua-bir2014a}, quadrature by
+another for upsampling to be sufficient.  Therefore, we plan to
+implement a near-singular integration scheme that uses either
+near-singular interpolation~\cite{qua-bir2014a}, quadrature by
 expansion~\cite{klo-bar-gre-one2013}, Barycentric
@@
 In this simulation, the body completely vanishes at a final time of $t_f = 1.79E-2$.
+\todo[inline]{Is this the notation we want to use for scientific
+notation? Could instead use $1.79 \times 10^{-2}$?}
 
@@
 Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
-The normalized arc length $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point.
+The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point.
 At early times (yellow to orange), the stress is distributed non-uniformly, with highest values at the top and bottom of the body.
@@
 (b) The distribution of absolute shear stress, $\atau$, along each of these interfaces.
-Normalized arc length, $s/L$, runs counterclockwise from the rear stagnation point.
+Normalized arclength, $s/L$, runs counterclockwise from the rear stagnation point.
 The stress initially varies over the body's surface, but becomes more uniform over time.}

### 2018-03-13 docs/methods/erosion_methods.tex
Added plots for 6 and 50 body simulations.
NM

@@
 Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
-This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \&2 or 3 \& 5 or 5 \& 6) follow.
+This main channel widens the fastest, and secondary channels follow (e.g.~between bodies 1 \&2 or 3 \& 5 or 5 \& 6).
 Since the pressure drop across the cell is fixed, the overall flow rate increases as the bodies erode.
@@
 \begin{center}
-\includegraphics[width = 0.85 \textwidth]{./figs/06plots.pdf}
-\caption{\label{fig:06plots} plots to go with 6 body simulation.
+\includegraphics[width = 0.95 \textwidth]{./figs/mbodyplots.pdf}
+\caption{\label{fig:mbodyplots} plots to go with 6 body simulation.
 }

### 2018-03-13 docs/methods/erosion_methods.tex
NM

@@
 
+We further quantify many of these observations in Fig.~\ref{fig:mbodyplots}.
+First, Fig.~\ref{fig:mbodyplots}(a) shows area fraction versus time.
+The area fraction is the total area of all bodies as compared to the domain area, i.e.~the 2D counterpart of volume fraction.
+The initial configuration of 6 circles comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode.
+Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time.
+
 \newpage

### 2018-03-13 docs/methods/erosion_methods.tex
NM

@@
 Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time.
+Since we have fixed the pressure drop across the cell in these simulations, $\umax$ steadily increases as the bodies diminish and provide less resistance.
+Here, the vertical axis is logarithmic, and so the plot suggests exponential increase of $\umax$ at early times.
+This rapid increase in flow is likely due to the erosion-induced channelization observed above.
+In Fig.~\ref{fig:mbodyplots}(b) we show the total drag, summed over all bodies, versus time.
+Though the bodies diminish due to erosion, the steady increase of $\umax$ causes the total drag to remain relatively constant.
+Only near the end of the simulation does the drag decrease rapidly to zero.
 

### 2018-03-13 docs/methods/erosion_methods.tex
NM

@@
 This rapid increase in flow is likely due to the erosion-induced channelization observed above.
-In Fig.~\ref{fig:mbodyplots}(b) we show the total drag, summed over all bodies, versus time.
+In Fig.~\ref{fig:mbodyplots}(c) we show the total drag, summed over all bodies, versus time.
 Though the bodies diminish due to erosion, the steady increase of $\umax$ causes the total drag to remain relatively constant.
 Only near the end of the simulation does the drag decrease rapidly to zero.
+To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the total drag scaled on $\umax$.
+This value is a measure for the aggregate {\em resistance} of all bodies.
+Due to linearity of the Stokes equations, this measure does not depend on the flow-rate $\umax$, only on the bodies and their configuration.
+As seen here, the resistance decreases rapidly as the bodies erode.
+Accounting for the logarithmic vertical axis suggests an exponential decrease in resistance at early times, which is likely connected to the channelization process.
 

### 2018-03-13 docs/methods/erosion_methods.tex
NM

@@
 As seen here, the resistance decreases rapidly as the bodies erode.
-Accounting for the logarithmic vertical axis suggests an exponential decrease in resistance at early times, which is likely connected to the channelization process.
+Since the vertical axis is logarithmic, the plot suggests an exponential decrease in resistance at early times, which is likely connected to the channelization process.
 

### 2018-03-13 docs/methods/erosion_methods.tex
NM

@@
 
+In Fig.~\ref{fig:mbodyplots} we also plot the same quantities for the 50-body simulation that was shown in Fig.~\ref{fig:50bodies} of the introduction.
+Overall, these plots support the same trends seen in the 6-body simulation.
+The initial area-fraction of the 50-body simulation is only slightly higher, about 45\%, and this fraction decreases steadily as bodies erode.
+The flow rate $\umax$ again increases very rapidly with time, though with a significantly smaller initial value due to the higher resistance provided by 50 bodies.
+As before, the total drag remains relatively constant throughout most of the simulation and then abruptly decreases to zero in the final moments.
+Our measure of resistance, $F_D/(4 \pi \umax)$, again decreases very rapidly in the early moments when channels are initially formed.
+Though the area fractions of the two simulations are nearly the same, the 50-body configuration provides about 5 times more resistance.
+
 \newpage

### 2018-03-15 docs/methods/erosion_methods.tex
Abstract

@@
 \begin{abstract} 
-We consider two dimensional eroding bodies in Stokes flow
+We develop numerical methods to simulate the fluid-mechanical erosion of many bodies (order 50) in 2D Stokes flow.
+The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with resolution at the grain scale.
+Our fluid solver is based on a boundary-integral formulation of the Stokes equations.
+We solve the associated linear system iteratively with GMRES and use the fast-multipole method (FMM) to accelerate the matrix-vector products.
+
+To evolve individual grains according to shear-driven erosion in a numerically stable manner, we regularize interface motion through curvature-penalization.
+
+%{\thL} method, which allows us to regularize 
 \end{abstract}

### 2018-03-15 docs/methods/erosion_methods.tex
I took a shot at the abstract.

--- 2018-03-13 docs/methods/erosion_methods.tex
@@
 \begin{abstract} 
-We consider two dimensional eroding bodies in Stokes flow
+We develop numerical methods to simulate the fluid-mechanical erosion of many bodies (order 50) in 2D Stokes flow.
+The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with resolution at the grain scale.
+Our fluid solver is based on a boundary-integral formulation of the Stokes equations with a double-layer potential.
+We solve the associated linear system iteratively with GMRES and use the fast-multipole method (FMM) for acceleration.
+Since the underlying integral equation is second-kind, GMRES achieves a bounded iteration count (independent of the number of unknowns).
+To evolve the individual grains under shear-driven erosion, we regularize via curvature-penalization and solve the associated system using the {\thL} formulation.
+This framework allows numerically stable treatment of stiff terms and thus permits large time steps.
+The overall accuracy of our method is exponential in space and second-order in time.
+The method is computationally efficient, with the main part of the solver having an $O(N)$ cost, and a one-time $O(N^2)$ computation.
+We benchmark single-body results against analytical predictions.
+In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact.
+The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
 \end{abstract}

### 2018-03-15 docs/methods/erosion_methods.tex
NM

@@
 We solve the resulting system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an
-explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method so as to maximize the smoothing effect of the diffusive term.
+explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method because it maximizes the smoothing effect of the diffusive term.
 \todo[inline]{Last sentence might need to be clarified.  Not sure about
@@
 Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress.
-In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
+In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 10^{-6}$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
 \label{01bodseq} 
@@
 As shown in the third snapshot, this corner persists as the bodies becomes even more slender and continues to shrink.
-In this simulation, the body completely vanishes at a final time of $t_f = 1.79E-2$.
+In this simulation, the body completely vanishes at a final time of $t_f = 1.79 \times 10^{-2}$.
 \todo[inline]{Is this the notation we want to use for scientific
-notation? Could instead use $1.79 \times 10^{-2}$?}
+notation? Could instead use $1.79 \times 10^{-2}$? \\
+Fine by me (Nick). What about for tables (e.g. table 4)? For tables, I am more used to seeing the 1.79E-2 notation. How about you?}
 
@@
 Shape and stress evolution: (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
-Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes.
+Color indicates normalized time, $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body completely vanishes.
 (b) The distribution of absolute shear stress, $\atau$, along each of these interfaces.
@@
 As a final validation, we now aim to verify that our method converges with second-order accuracy in time.
-To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 1E-2$.
+To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
 This stopping time is 56\% of the time it takes the body to vanish, and was selected so that the body will have eroded substantially but is not so small that accuracy is compromised.
@@
 \begin{center}
-\caption{Convergence test: We run single-body erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$-difference in shapes obtained with successive temporal resolutions.
+\caption{Convergence test: We run single-body erosion simulations to a stopping time of $t_s = 10^{-2}$ (56\% of the vanishing time) and measure the $L^2$-difference in shapes obtained with successive temporal resolutions.
 The tests confirm the method to be second-order accurate in time.
@@
 In this test, we use 20 bodies with $N_{\iin} = 128$ grid points on each.
-We run the simulations to a stopping time of $t_s = 4E-3$ (24\% of the time it takes for {\em all} bodies to vanish).
+We run the simulations to a stopping time of $t_s = 4 \times 10^{-3}$ (24\% of the time it takes for {\em all} bodies to vanish).
 We measure the {\em combined} $L^2$-difference in the shapes of {\em all} bodies.

### 2018-03-16 docs/methods/erosion_methods.tex
NM

@@
 Our fluid solver is based on a boundary-integral formulation of the Stokes equations with a double-layer potential.
-We solve the associated linear system iteratively with GMRES and use the fast-multipole method (FMM) for acceleration.
+We solve the associated linear system iteratively using GMRES and the fast-multipole method (FMM) for acceleration.
 Since the underlying integral equation is second-kind, GMRES achieves a bounded iteration count (independent of the number of unknowns).
 To evolve the individual grains under shear-driven erosion, we regularize via curvature-penalization and solve the associated system using the {\thL} formulation.
-This framework allows numerically stable treatment of stiff terms and thus permits large time steps.
+This framework allows numerically stable treatment of stiff terms, thus permitting large time steps.
 The overall accuracy of our method is exponential in space and second-order in time.
@@
 
-Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress is increasing as the body vanishes.
+Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress grows as the body vanishes.
 This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / a$, in which drag is inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is taken to be the radius).
@@
 For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
-$\mu \umax \ell/ \log(\ell/a)$, where $a$ is a length scale of the cross-section and $a \ll \ell$. This relationship implies that the stress per unit span on a 2D cross-section can be estimated by
+$\mu \umax \ell/ \log(\ell/a)$, where $a$ is a length scale of the cross-section and $a \ll \ell$. This relationship implies that the stress-per-unit-span on a 2D cross-section can be estimated as
 \begin{align}
@@
 In interpreting our 2D simulations, we will treat the span, $\ell$, as
-fixed. Recall that $L$ denotes the total perimeter of the cross-section,
-and therefore $a$ and $L$ can often be used interchangeable in scaling
-analysis, since they each represent a length scale of the cross-section.
+fixed.
+Recall that $L$ denotes the total perimeter of the 2D cross-section.
+Since $L$ and $a$ each represent a characteristic scale of the cross-section, they can often be interchanged in scaling analysis.
 
@@
 \includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
-\caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction~\eqref{area_predict} (dotted red).
-The two are nearly indistinguishable.
+\caption{Area and drag: (a) The body area measured in the simulations (black) shown against the scaling-law prediction~\eqref{area_predict} (dotted red), the two of which agree closely.
 (b) The horizontal drag (black) on the body as it erodes, along with the viscous (green) and pressure (blue) contributions.
@@
 \begin{align}
-\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
-\end{align}
-Thus, the area-loss rate is given by the product of the mean shear
-$\mean{\atau}$ and the total perimeter $L$, which is an exact relationship. Inserting scaling law~\eqref{eqn:stresslaw} gives
+\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, ,
+\end{align}
+which is an {\em exact} relationship. Inserting scaling law~\eqref{eqn:stresslaw} gives
 \begin{align}
@@
 \end{align}
-Noting that $A \sim a^2$ allows one to solve the ODE to determine how the body area changes with time
+Noting that $A \sim a^2$ allows one to solve the ODE, giving
 \begin{align}
@@
 \end{align}
-Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area,
-and $c_1$ is a free constant. The above is an {\em implicit}
-relationship for how the area scales down in time during erosion. In
-Fig.~\ref{area_drag}(a), we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 = 0.24$ a fit parameter.
-The comparison shows close agreement between the two (they are indistinguishable).
+Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area, and $c_1$ is a free constant.
+The above is an {\em implicit} relationship for how the area of an eroding body scales down in time, which we can use to test our numerical simulation.
+In Fig.~\ref{area_drag}(a) compare the area measured in our numerical simulation (black curve) against the above scaling law (red dotted curve) with $c_1 = 0.24$ a fit parameter.
+The two agree remarkable well throughout the entire simulation, thus co-validating the simulation and asymptotic results.
+
+The drag exerted by the eroding body
+
+The drag on the eroding body offers a second check on our simulation. This quantity will also be of great interest in its own right for characterizing a porous-medium.
+
+%\ref{eqn:drag}
 
@@
 The figure shows the drag to decrease  gradually at first, then abruptly tend to zero in the final moments as the body vanishes.
-This behavior is consistent with fact that drag vanishes {\em logarithmically} with body-size $a$  in 2D Stokes flow.
+This behavior is consistent with fact that drag vanishes {\em logarithmically} with body-size in 2D Stokes flow.
 We also show in the figure the separate contributions of the viscous and the pressure drag.
@@
 \end{align}
-For a {\em circular} cylinder, $a$ is the radius and the normalization factor $4 \pi$ is exact within the slender-body framework.
+The normalization factor of $4 \pi$ produces an {\em exact} relationship (under the assumptions of slender-body theory) for the case of a {\em circular} cylinder, where $a$ is taken to be the radius.
 To generalize to other shapes, we define $a = \sqrt{A/\pi}$ and fit $\ell$ to get $\ell = 2.3 a_0$.

### 2018-03-16 docs/methods/erosion_methods.tex
NM

@@
 As shown in the third snapshot, this corner persists as the bodies becomes even more slender and continues to shrink.
-In this simulation, the body completely vanishes at a final time of $t_f = 1.79 \times 10^{-2}$.
 \todo[inline]{Is this the notation we want to use for scientific
@@
 To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
-The interfaces are color-coded by normalized time $t/t_f$.
-The body seems to converge to a shape that resembles an American football --- a fairly slender, for-aft symmetric shape with corners at the front and back.
+The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes.
+The body converges to a fairly slender, for-aft symmetric shape with corners at its front and back --- somewhat reminiscent of an American football.
 Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
-The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point.
-At early times (yellow to orange), the stress is distributed non-uniformly, with highest values at the top and bottom of the body.
+The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0 and 0.5 corresponding to the rear and front stagnation points respectively.
+At early times (yellow to orange), the stress is highly variables, with highest values at the top and bottom of the body.
 As time proceeds, though, the stress becomes more evenly distributed along the body's surface (red).
@@
 \caption{
-Shape and stress evolution: (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals.
+Shape and stress evolution: (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} shown at evenly-spaced time intervals.
 Color indicates normalized time, $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body completely vanishes.

### 2018-03-16 docs/methods/erosion_methods.tex
NM

@@
 To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
-The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes.
+The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes in the simulation.
 The body converges to a fairly slender, for-aft symmetric shape with corners at its front and back --- somewhat reminiscent of an American football.
@@
 The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0 and 0.5 corresponding to the rear and front stagnation points respectively.
-At early times (yellow to orange), the stress is highly variables, with highest values at the top and bottom of the body.
-As time proceeds, though, the stress becomes more evenly distributed along the body's surface (red).
-As the body nears the final stages of erosion (dark red), the stress actually becomes slightly higher near the stagnation points.
-A close look reveals that the stress always vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow.
+At early times (yellow curves), the stress varies significantly, with more stress concentrated at the top and bottom of the body.
+As erosion alters the body's shape, though, the stress becomes more uniformly distributed over the entire surface (red curves).
+As the body nears the final stages of erosion (dark red), $\atau$ shows slight peaks near the stagnation points.
+Upon close inspection, the stress always vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow.
 
@@
 \end{align}
-which is an {\em exact} relationship. Inserting scaling law~\eqref{eqn:stresslaw} gives
+Thus, the rate of area reduction is given by the product of the mean shear stress $\mean{\atau}$ and the perimeter $L$, which is an {\em exact} relation.
+Inserting scaling law~\eqref{eqn:stresslaw} gives the estimate
 \begin{align}
@@
 Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area, and $c_1$ is a free constant.
-The above is an {\em implicit} relationship for how the area of an eroding body scales down in time, which we can use to test our numerical simulation.
-In Fig.~\ref{area_drag}(a) compare the area measured in our numerical simulation (black curve) against the above scaling law (red dotted curve) with $c_1 = 0.24$ a fit parameter.
+The above is an {\em implicit} relationship for how area scales down in time.
+We can use this prediction to test our numerical simulation.
+In Fig.~\ref{area_drag}(a) we compare the area measured in our numerical simulation (black curve) against the above scaling law (red dotted curve) with $c_1 = 0.24$ a fit parameter.
 The two agree remarkable well throughout the entire simulation, thus co-validating the simulation and asymptotic results.
+
+The drag exerted by the body offers
 

### 2018-03-16 docs/methods/erosion_methods.tex
NM

@@
 The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes in the simulation.
-The body converges to a fairly slender, for-aft symmetric shape with corners at its front and back --- somewhat reminiscent of an American football.
+As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape with corners at its front and back --- somewhat reminiscent of an American football.
 Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
@@
 At early times (yellow curves), the stress varies significantly, with more stress concentrated at the top and bottom of the body.
-As erosion alters the body's shape, though, the stress becomes more uniformly distributed over the entire surface (red curves).
-As the body nears the final stages of erosion (dark red), $\atau$ shows slight peaks near the stagnation points.
-Upon close inspection, the stress always vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow.
+However, as erosion alters the body's shape, the stress becomes more uniformly distributed over the entire surface (red curves).
+The absolute stress $\atau$ shows slight peaks near the stagnation points as the bodies nears the final stages of erosion (dark red).
+Closer inspection reveals that the stress actually vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow with time.
 
@@
 
-The drag exerted by the body offers
-
-The drag exerted by the eroding body
-
-The drag on the eroding body offers a second check on our simulation. This quantity will also be of great interest in its own right for characterizing a porous-medium.
-
-%\ref{eqn:drag}
-
-In Fig.~\ref{area_drag}(b), we show the horizontal drag $F_D$ measured on the body as it erodes.
-Note that, in the context of 3D slender-body theory, this $F_D$ should be interpreted as the drag per unit span.
-The figure shows the drag to decrease  gradually at first, then abruptly tend to zero in the final moments as the body vanishes.
-This behavior is consistent with fact that drag vanishes {\em logarithmically} with body-size in 2D Stokes flow.
-We also show in the figure the separate contributions of the viscous and the pressure drag.
-Initially, these two contributions are comparable, with a slightly greater level of pressure drag.
-However, as the body erodes and assumes a more slender form, the pressure drag decays more rapidly and viscous drag dominates.
-
-As a final check, we can estimate the drag (per unit span) using slender-body theory via the formula
+	The drag exerted by the eroding body offers a second check on the simulation.
+Figure~\ref{area_drag}(b) shows the horizontal drag, $F_D$, calculated in the simulations (black curve) using Eq.~\eqref{eqn:drag}.
+In the context of slender-body theory, $F_D$ should be interpreted as drag-per-unit-span.
+As seen in Fig.~\ref{area_drag}(b), the drag decreases gradually at first and then abruptly tends to zero in the very final moments.
+This behavior, though perhaps surprising, is consistent with the fact that drag vanishes {\em logarithmically} with body-size in 2D Stokes flow.
+Equation \eqref{eqn:drag} also allows us to calculate the separate contributions of pressure and viscous drag, and we show these with the blue and green curves in Fig.~\ref{area_drag}(b).
+Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag.
+However,  as the body erodes and assumes a more slender form, the pressure drag decreases much more rapidly, leaving viscous drag to dominate.
+This behavior is associated with the tendency towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
+
+As a check on these results, we can use slender-body theory to estimate the drag-per-unit-span
 \begin{align}
 \label{dragscaling}
-\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}.
-\end{align}
-The normalization factor of $4 \pi$ produces an {\em exact} relationship (under the assumptions of slender-body theory) for the case of a {\em circular} cylinder, where $a$ is taken to be the radius.
-To generalize to other shapes, we define $a = \sqrt{A/\pi}$ and fit $\ell$ to get $\ell = 2.3 a_0$.
-
-\todo[inline]{Clean up this section}
+\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}	\qquad \text{for } a \ll \ell \, .
+\end{align}
+For the case of a {\em circular} cylinder, the normalization factor of $4 \pi$ produces an {\em exact} relationship (under the slender-body assumptions), where $a$ is taken to be the radius.
+For other shapes the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale (since it generalizes the case of a circle).
+In Fig.~\ref{area_drag}(b) we show this scaling prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ the radius of the initially circular body.
+The scaling law agrees closely with the simulated drag as the body vanishes, thus providing validation.
 
 \subsection{Local analysis for the limiting shape}
+\label{LimitingShape}
+
+\todo[inline]{Here in revising}
 

### 2018-03-16 docs/methods/erosion_methods.tex
NM

@@
 Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag.
-However,  as the body erodes and assumes a more slender form, the pressure drag decreases much more rapidly, leaving viscous drag to dominate.
+As the body erodes and assumes a more slender form, though, the pressure drag decreases much more rapidly, leaving viscous drag to dominate.
 This behavior is associated with the tendency towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
@@
 \end{align}
-For the case of a {\em circular} cylinder, the normalization factor of $4 \pi$ produces an {\em exact} relationship (under the slender-body assumptions), where $a$ is taken to be the radius.
+For the case of a {\em circular} cylinder, the normalization factor of $4 \pi$ produces an {\em exact} relationship (under the slender-body assumptions), with $a$ taken to be the radius.
 For other shapes the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale (since it generalizes the case of a circle).
-In Fig.~\ref{area_drag}(b) we show this scaling prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ the radius of the initially circular body.
-The scaling law agrees closely with the simulated drag as the body vanishes, thus providing validation.
+In Fig.~\ref{area_drag}(b) we show this scaling prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
+The scaling law and measured drag agree closely as the body vanishes.
 

### 2018-03-19 docs/methods/erosion_methods.tex
NM

@@
 explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method because it maximizes the smoothing effect of the diffusive term.
-\todo[inline]{Last sentence might need to be clarified.  Not sure about
-using `so as to'}
 
@@
 As shown in the third snapshot, this corner persists as the bodies becomes even more slender and continues to shrink.
-\todo[inline]{Is this the notation we want to use for scientific
-notation? Could instead use $1.79 \times 10^{-2}$? \\
-Fine by me (Nick). What about for tables (e.g. table 4)? For tables, I am more used to seeing the 1.79E-2 notation. How about you?}
 
@@
 The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes in the simulation.
-As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape with corners at its front and back --- somewhat reminiscent of an American football.
+As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape that has corners at its front and back --- somewhat reminiscent of an American football.
 Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.

### 2018-03-20 docs/methods/erosion_methods.tex
touched up intro

@@
 \begin{abstract} 
-We develop numerical methods to simulate the fluid-mechanical erosion of many bodies (order 50) in 2D Stokes flow.
-The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with resolution at the grain scale.
-Our fluid solver is based on a boundary-integral formulation of the Stokes equations with a double-layer potential.
-We solve the associated linear system iteratively using GMRES and the fast-multipole method (FMM) for acceleration.
-Since the underlying integral equation is second-kind, GMRES achieves a bounded iteration count (independent of the number of unknowns).
-To evolve the individual grains under shear-driven erosion, we regularize via curvature-penalization and solve the associated system using the {\thL} formulation.
-This framework allows numerically stable treatment of stiff terms, thus permitting large time steps.
-The overall accuracy of our method is exponential in space and second-order in time.
-The method is computationally efficient, with the main part of the solver having an $O(N)$ cost, and a one-time $O(N^2)$ computation.
+We develop numerical methods to simulate the fluid-mechanical erosion of
+many bodies (order 50) in a two-dimensional Stokes flow. The broad aim
+is to simulate the erosion of a porous medium (e.g.~ground water flow)
+with grain scale resolution. Our fluid solver is based on a
+boundary integral formulation of the Stokes equations. We solve the
+associated linear system with a fast-multipole-accelerated GMRES iteration. We use a second-kind integral equation so
+that GMRES requires a bounded iteration count (independent of the number
+of unknowns). To evolve the individual grains under shear-driven
+erosion, we regularize via curvature-penalization and solve the
+associated system using the {\thL} formulation. This framework allows
+numerically stable treatment of stiff terms, thus permitting large time
+steps. The overall accuracy of our method is exponential in space and
+second-order in time. The method is computationally efficient, with the
+fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration, and a one-time
+$\mathcal{O}(N^2)$ computation to compute the shear stress.
 We benchmark single-body results against analytical predictions.
@@
 of rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  Erosion is
-also important in biophysical applications, for example plaque erosion in arteries
+also important in biophysical applications---plaque erosion in arteries
 is key to understanding heart disease~\cite{sha2002,
@@
 be explained by erosion~\cite{pic-van-hei2000}. 
-Much recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}.
-All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow' \cite{ristroph2018sculpting}.
+Recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}.
+All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow'~\cite{ristroph2018sculpting}.
 % Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.
@@
 that is proportional to the magnitude of the shear
-stress~\cite{ris-moo-chi-she-zha2012}.  Tracking the interface of
+stress~\cite{ris-moo-chi-she-zha2012}.  However, tracking the interface of
 fluid-structure interaction problems with a long time horizon is
-particularly (???) ---the mesh is often distorted and tangled by the dynamics
+particularly difficult---the mesh is often distorted and tangled by the dynamics
 and regions of high curvature develop.  These two issues are resolved
@@
 individually resolved rather than homogenized.  We start by validating
-our method on a single circular body placed symmetrically in a CHANNEL
+our method on a single circular body placed symmetrically in a pipe
 flow.  By artificially fixing the area of the body as a function of
@@
 rate of erosion, the shape is integrated in time with second-order
-accuracy.  All spatial derivatives are be computed in Fourier space,
+accuracy.  All spatial derivatives are computed in Fourier space,
 resulting in spectral accuracy in space.  To further visualize the
@@
 (Fig.~\ref{fig:50bodies}) to visualize regions of high and low erosion.
-
-A challenge with erosion is that it creates corners at points on the
-body where the shear stress vanishes.  There is recent work for solving
-BIEs in geometries with corners by using
-carefully chosen local expansions around each corner~\cite{rac-ser2017,
-ser-rok2016} or panel-based graded meshes~\cite{hel2011,
-gil-hao-mar2014, bre2012}.  The limitation of these methods is that they
-require the corner's location, a non-uniform spaced mesh, and some of
-the methods have a large condition number.  One solution is to use two
-meshes---one for the quadrature the other for the interface tracking.
-Then, interpolation between the two grids is required, and this is the
-approach taken by Ojala and Tornberg~\cite{oja-tor2015}.  Instead of
-using two grids and interpolation operators, we only require the uniform
-grid by slightly modify the geometry to maintain sufficient regularity.
-First, we add a regularization term to the shear stress to penalize
-regions of high curvature.  Second, we apply a Gaussian filter to smooth
-the absolute value of the shear stress before the body shape is updated.
 
@@
 considered immobile (i.e.~fixed to their initial locations). The
-restriction to 2D allows us to simulate the erosion of many bodies
+restriction to two dimensions allows us to simulate the erosion of many bodies
 (up to $50$ in this manuscript) with high resolution, giving us the
 ability to accurately characterize the erosion of a porous medium. While
-BIEs are available in 3D, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
+BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
 The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
@@
 For low Reynolds number flows, Mitchell and Spagnolie~\cite{mit-spa2016}
-simulate the erosion of a mobile body in three dimensions, but they only
-consider single body.
-
-Mitchell and Spagnolie~\cite{mit-spa2016} formulate the traction jump as
-a DLP using Lorentz Reciprocal Theorem so that additional layer
-potentials have to be evaluated.  That is, they never find the density
-function.
+use a BIE for the traction jump to simulate the erosion of a mobile body
+in three dimensions, but they only consider single body.
 
@@
 developed in this paper, quantities such as the total drag across a
-porous region as a function of time can be computed in future work.
+porous region as a function of time can be computed.
 
@@
 particulate flows, such as bubbles or droplets, and the classic book of
-Pozrikidis~\cite{poz1992} describes BIEs for such problems.
+Pozrikidis~\cite{poz1992} describes BIEs for such problems.  For nearly
+touching bodies, the quadrature associated with discretizing a BIE can
+lead to instabilities of specialized quadrature is not applied.  Since
+our bodies do not move, we are able to use upsampling, but future work
+will require a near-singular integration scheme~\cite{qua-bir2014a,
+klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.
+
+Another numerical challenge with simulating erosion is that
+corners develop at points where the shear stress vanishes.  There is recent work for solving
+BIEs in geometries with corners by using
+carefully chosen local expansions around each corner~\cite{rac-ser2017,
+ser-rok2016} or panel-based graded meshes~\cite{hel2011,
+gil-hao-mar2014, bre2012}.  The limitation of these methods is that they
+require the corner's location, a non-uniform spaced mesh, and some of
+the methods have a large condition number.  One solution is to use two
+meshes---one for the quadrature the other for the interface tracking.
+Then, interpolation between the two grids is required, and this is the
+approach taken by Ojala and Tornberg~\cite{oja-tor2015}.  Instead of
+using two grids and interpolation operators, we only require the uniform
+grid by slightly modify the geometry to maintain sufficient regularity.
+First, we add a regularization term to the shear stress to penalize
+regions of high curvature.  Second, we apply a Gaussian filter to smooth
+the absolute value of the shear stress before the body shape is updated.
 
@@
 erosion model using a \thL~framework.  In Section~\ref{s:method}, the
-numerical methods in both space and time are described.
-Section~\ref{SingleResults} gives several numerical examples.  Finally,
-concluding remarks are made in Section~\ref{s:conclusions}
+numerical methods in both space and time are described and
+Section~\ref{s:qoi} describes how to compute the vorticity, pressure,
+and drag. Section~\ref{s:SingleResults} gives several numerical examples
+for a single body, and Section~\ref{s:MultiResults} presents numerical
+  examples for multiply-connected domains.  Finally, concluding remarks are made in Section~\ref{s:conclusions}
 
@@
 \section{Results: Single-body erosion}
-\label{SingleResults}
-With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow.
-We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation.
-In Section \ref{MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.
+\label{s:SingleResults}
+With the description of the methods complete, we now present numerical
+results on bodies eroding in Stokes flow. We first discuss the case of a
+single body, as certain features can be predicted analytically and thus
+used for validation. In Section~\ref{s:MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.
 
@@
 \section{Results: Multi-body erosion}
-\label{MultiResults}
+\label{s:MultiResults}
 

### 2018-03-20 docs/methods/erosion_methods.tex
NM

@@
 Interestingly, the slight rise in shear near the front/rear corners that was seen in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that the effect was due to loss of accuracy.
-Here, time is normalized by the same vanishing time $t_f = 1.79E-2$ as in Fig.~\ref{shrink_intface}.
+Here, time is normalized by the same vanishing time $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
 Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
@@
 Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
-This main channel widens the fastest, and secondary channels follow (e.g.~between bodies 1 \&2 or 3 \& 5 or 5 \& 6).
+This main channel widens the fastest, and secondary channels follow (e.g.~between bodies 1 \& 2 or 3 \& 5 or 5 \& 6).
 Since the pressure drop across the cell is fixed, the overall flow rate increases as the bodies erode.

### 2018-03-20 docs/methods/erosion_methods.tex
small changs to intro

--- 2018-03-20 docs/methods/erosion_methods.tex
@@
 We develop numerical methods to simulate the fluid-mechanical erosion of
-many bodies (order 50) in a two-dimensional Stokes flow. The broad aim
+many bodies in a two-dimensional Stokes flow. The broad aim
 is to simulate the erosion of a porous medium (e.g.~ground water flow)
-with grain scale resolution. Our fluid solver is based on a
-boundary integral formulation of the Stokes equations. We solve the
-associated linear system with a fast-multipole-accelerated GMRES iteration. We use a second-kind integral equation so
-that GMRES requires a bounded iteration count (independent of the number
-of unknowns). To evolve the individual grains under shear-driven
+with grain-scale resolution. Our fluid solver is based on a
+second-kind boundary integral formulation of the Stokes equations that is
+discretized with a spectrally-accurate Nystr\"om method and solved
+with a fast-multipole-accelerated GMRES iteration. To evolve the individual grains under shear-driven
 erosion, we regularize via curvature-penalization and solve the
@@
 second-order in time. The method is computationally efficient, with the
-fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration, and a one-time
+fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration,
+a mesh-independent number of GMRES iterations, and a one-time
 $\mathcal{O}(N^2)$ computation to compute the shear stress.
@@
 \begin{keyword}
-  Stokes flow \sep Erosion \sep Boundary integral method \sep Shear
-  stress \sep {\thL} formulation
+  Porous medium \sep Stokes flow \sep Erosion \sep Boundary integral
+  equations \sep Shear stress \sep {\thL} formulation
 \end{keyword}
@@
 
-\newpage
-
-Good word: Spontaneous channelization
-
-\vsp{3}
-Possible list:
-\begin{itemize}
-\item Show multiple body simulation with fixed flow rate
-\item Then simulation with fixed pressure drop
-\item GMRES counts
-%
-\item $\bigO(5-10)$ bodies
-	\begin{itemize}
-	\item Area and Drag
-	\item Long channels between flat faces
-	\end{itemize}
-\item $\bigO(50)$ bodies
-	\begin{itemize}
-	\item Area and Drag
-	\end{itemize}
-\end{itemize}
+{\bf Good word: Spontaneous channelization}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{appendices}
-\section{Error estimates for near-singular integration \label{A:AppendixA}} 
-\end{appendices}
+\todo[inline]{paper of Bryan, Eric, and Pieter and one with Pietro,
+George, and Ruben}
 

### 2018-03-20 docs/methods/erosion_methods.tex
NM

@@
 Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress grows as the body vanishes.
-This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / a$, in which drag is inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is taken to be the radius).
+This observation is consistent with the well-known 3D Stokes drag law, in which stress, $\tau \sim \mu \umax / a$, scales inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is taken to be the radius).
 This law must be modified in two dimensions, though.

### 2018-03-20 docs/methods/erosion_methods.tex
NM

--- 2018-03-20 docs/methods/erosion_methods.tex
@@
 Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress grows as the body vanishes.
-This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / a$, in which drag is inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is taken to be the radius).
+This observation is consistent with the well-known 3D Stokes drag law, in which stress, $\tau \sim \mu \umax / a$, scales inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is the radius).
 This law must be modified in two dimensions, though.
@@
 Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area, and $c_1$ is a free constant.
-The above is an {\em implicit} relationship for how area scales down in time.
-We can use this prediction to test our numerical simulation.
+The above is an {\em implicit} relationship for how area scales down in time, and we can use this prediction to test our numerical simulation.
 In Fig.~\ref{area_drag}(a) we compare the area measured in our numerical simulation (black curve) against the above scaling law (red dotted curve) with $c_1 = 0.24$ a fit parameter.
@@
 
-	The drag exerted by the eroding body offers a second check on the simulation.
+	Another important quantity that can be used to test our simulations is the drag exerted by the body as it erodes.
 Figure~\ref{area_drag}(b) shows the horizontal drag, $F_D$, calculated in the simulations (black curve) using Eq.~\eqref{eqn:drag}.
@@
 \end{align}
-For the case of a {\em circular} cylinder, the normalization factor of $4 \pi$ produces an {\em exact} relationship (under the slender-body assumptions), with $a$ taken to be the radius.
-For other shapes the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale (since it generalizes the case of a circle).
+For the case of a {\em circular} cylinder, the normalization factor of $4 \pi$ produces an {\em exact} relationship (under the slender-body assumptions), where $a$ is taken to be the radius.
+For other shapes the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale since it generalizes the case of a circle.
 In Fig.~\ref{area_drag}(b) we show this scaling prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
-The scaling law and measured drag agree closely as the body vanishes.
+The scaling law and measured drag agree closely as $t \to t_f$, thus confirming that our simulation accurately captures the slender-body limit as the shape disappears.
 
@@
 \label{LimitingShape}
-
-\todo[inline]{Here in revising}
 
@@
 % Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+\todo[inline]{Here in revising}
 

### 2018-03-20 docs/methods/erosion_methods.tex
NM

@@
 
-With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
-Certain features of this shape can be predicted analytically by appealing to the principal that, in long time, the shear stress becomes uniformly distributed along the body.
-In particular, consider the angle formed at the front and rear stagnation points.
-In a small region around this point, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge.
-We aim to determine the wedge's opening angle, $\oangle$, through the principle of uniform stress.
-Exact solutions can be obtained to this problem via separation of variables in polar coordinates $(r, \theta)$~\cite{poz1997}.
-In this section alone, $\theta$ denotes the polar coordinate (not the local tangent angle along the body).
-The corresponding stream function is assumed to take the form $\psi = r^{\lambda}f(\theta)$, with $\Delta^2 \psi = 0$, which gives the 4th order ODE~\cite{poz1997}
-\begin{align*}
-  f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f =
-  0.
-\end{align*}
-
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
-This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down symmetry of the flow).
-The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\thb)$.
-Thus, the wedge of uniform stress corresponds to $\lambda = 2$.
-For this value, the solution for $f$ satisfying odd symmetry is
-\begin{align*}
-  f(\theta) = B \sin (2 \theta) + C \theta.
-\end{align*}
-Imposing the no-slip boundary conditions gives the condition
-\begin{align*}
-  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0,
-\end{align*}
-which has a solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(180^{\circ} - \thb) \approx 102$ degrees. 
+With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
+Certain features of this shape can be predicted analytically by appealing to the principal that, in long time, the shear stress becomes uniformly distributed along the body.
+In particular, consider the angle formed at the front and rear stagnation points.
+In a small region around this point, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$.
+See Fig.~\ref{corner} for a schematic.
+This problem can be solved exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$.
+(In this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
+
+The corresponding stream function is biharmonic, $\Delta^2 \psi = 0$, and the ansatz $\psi = r^{\lambda}f(\theta)$ gives the 4th-order ODE~\cite{poz1997}
+\begin{align}
+\label{fODE}
+f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0.
+\end{align}
+This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$ and odd symmetry about the horizontal axis, $f(0) = f''(0) = 0$.
+For arbitrary opening angle $\beta$, ODE \eqref{fODE} and its boundary conditions constitute an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
+We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and thus set $\lambda = 2$.
+The corresponding solution to \eqref{fODE} that satisfies odd symmetry is given by
+\begin{align}
+  f(\theta) = B \sin (2 \theta) + C \theta \, ,
+\end{align}
+and imposing the no-slip boundary conditions gives the condition
+\begin{align}
+  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0 \, .
+\end{align}
+This nonlinear equation has solution $\thb \approx 129^\circ$, which gives the uniform-stress opening angle as $\oangle \approx 102^\circ$ degrees. 
 % Pozrikidis page 239: symmetric flow.

### 2018-03-20 docs/methods/erosion_methods.tex
NM

@@
 
+\todo[inline]{Here in revising}
+
 We note that this uniform-stress shape is closely related to the so-called `optimal profile in Stokes flow' found by Pironneau (1973) \cite{pir1973}, who determined the shape that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume (see also \cite{mon-lau2015} for an interesting related shape).
@@
 \includegraphics[width = 0.85 \textwidth]{./figs/fixed_intface.pdf}
-\caption{Fixed-area simulations: (a) Interfaces of a body eroding under shear stress but with the area artifically kept constant.
+\caption{Fixed-area simulations: (a) Interfaces of a body eroding under shear stress but with the area artificially kept constant.
 Inset: zoom near the rear stagnation point, showing that the corner is actually smooth on a fine scale.
-(b) The stress distribution on the surface of the body.
-Over time, the stress becomes more uniform.}
+(b) The shear-stress distribution on each of these interfaces.
+As the body erodes and converges to a terminal form, the stress becomes more uniformly distributed over the entire surface.}
 \label{fixed_intface}
@@
 
-\todo[inline]{Here in revising}
-
 \subsection{Fixed-area simulations}
@@
 To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations.
-However, our simulations lose accuracy just in the final moments as the body is vanishing due to the shear stress blowing up (in accordance with the scaling laws discussed in Section \ref{sec:scaling}).
-To circumvent this problem, we could restart our simulation with a scaled-up version of the the near-final  body as the initial condition and iterate the process until convergence.
-A simpler solution, though, is to remove the effect of shrinking by modifying the normal velocity $\Vn$ to have zero mean,
-\begin{align*}
+Section \ref{sec:scaling}, however, shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy just in the final critical moments when the body is expected to approach its limiting form.
+To circumvent this problem, we modify the normal velocity $\Vn$ to have zero mean,
+\begin{align}
 \Vn \leftarrow \Vn - \mean{\Vn} \, .
-\end{align*}
-This modification allows erosion to sculpt the body as it normally would but artificially keeps the area fixed.
-We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process at equally-spaced times.
+\end{align}
+This modification allows erosion to sculpt the shape as it would normally, but with the area artificially held fixed.
+
+	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process.
 Notice the body obtains a similar profile as observed previously, but with fixed area.
@@
 Here, time is normalized by the same vanishing time $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
-Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
+Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state.
+This contrasts with previous studies of high-Reynolds-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
 

### 2018-03-20 docs/methods/erosion_methods.tex
NM

@@
 
+With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
+Certain features of this shape can be predicted analytically by appealing to the principal that, in long time, the shear stress becomes uniformly distributed along the body.
+In particular, consider the angle formed at the front and rear stagnation points.
+In a small region around this point, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$.
+See Fig.~\ref{corner} for a schematic.
+This problem can be solved exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$.
+(In this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
-With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
-Certain features of this shape can be predicted analytically by appealing to the principal that, in long time, the shear stress becomes uniformly distributed along the body.
-In particular, consider the angle formed at the front and rear stagnation points.
-In a small region around this point, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$.
-See Fig.~\ref{corner} for a schematic.
-This problem can be solved exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$.
-(In this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
-
 The corresponding stream function is biharmonic, $\Delta^2 \psi = 0$, and the ansatz $\psi = r^{\lambda}f(\theta)$ gives the 4th-order ODE~\cite{poz1997}
@@
 Previous numerical simulations on erosion in 3D Stokes flow revealed that, in long time, an eroding body tends to a shape that is approximately (though not precisely) Pironneau's optimal profile \cite{mit-spa2016}.
+
+\subsection{Fixed-area simulations}
 
@@
 
-\subsection{Fixed-area simulations}
-
 To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations.
-Section \ref{sec:scaling}, however, shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy just in the final critical moments when the body is expected to approach its limiting form.
-To circumvent this problem, we modify the normal velocity $\Vn$ to have zero mean,
+Section \ref{sec:scaling}, however, shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy just in the final critical moments when the body is expected to approach its limiting shape.
+To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
 \begin{align}

### 2018-03-20 docs/methods/erosion_methods.tex
toned down the intro

@@
 Here, a slow moving fluid erodes channels in the ground, and this
-affects the fluid transport.  In all these examples, there is a feedback
-process between the flow and the eroding bodies---the shape of the
-bodies affect the flow, while the flow changes the shape by fluidizing
-each body.  This fluid-mechanical feedback system has been simulated in
-idealized cases such as a single eroding two-dimensional body in a
-uniform flow~\cite{moo-ris-chi-zha-she2013} or a single mobile eroding
-three-dimensional body~\cite{mit-spa2016}. However, to better understand
+affects the fluid transport.  To better understand
 the effect of erosion on groundwater flow, multiply-connected domains
@@
 Because of the length and velocity scales of groundwater flow, we
-restrict our attention to small Reynolds number flows.  For groundwater
+restrict our attention to zero Reynolds number flows.  For groundwater
 flow, Darcy's law is often used, but this does not resolve the pore
 structure and assumes a homogeneous geometry which is often not valid.
-Instead, we use the incompressible Stokes equations to represent the
-flow, and the individual pores are resolved which results in a complex
-multiply-connected geometry.  A boundary integral equation (BIE) is
-well-suited for solving the incompressible Stokes equations in a complex
-geometry since it can resolve individual grains and the non-negligible
-interactions between bodies are resolved. Moreover, high-order accuracy
-and computational efficiency are obtained. To link the eroding body and
-fluid dynamics, the body is eroded in the normal direction at a rate
-that is proportional to the magnitude of the shear
-stress~\cite{ris-moo-chi-she-zha2012}.  However, tracking the interface of
-fluid-structure interaction problems with a long time horizon is
-particularly difficult---the mesh is often distorted and tangled by the dynamics
-and regions of high curvature develop.  These two issues are resolved
-by, first, introducing a tangential velocity field to maintain a grid
-that is equispaced in arclength, but that does not affect the dynamics,
-and, second, a curvature penalization term.  Furthermore, the frame of
-reference is changed to \thL~variables so that the curvature term
-appears as a diffusive term that can easily be handled in a 
-numerically stable fashion, e.g.~via an exponential integrator or an implicit method.
-
-In addition to simulating the eroding grains, the flow is further
-characterized by computing the vorticity in the flow.  The vorticity is
-particularly insightful since it is identical to the shear stress on
-no-slip boundaries.  Therefore, by computing the
-vorticity, we are able to locate regions where the erosion rates will be
-fastest or slowest.
+Instead, we use the incompressible Stokes equations as the governing
+fluid equations, and the individual pores are resolved which results in
+a complex multiply-connected geometry.  The dynamics of the individual
+pores are modelled with an erosion model that where the erosion rate is
+proportional to the magnitude of the shear stress.
 
@@
 to simulate erosion of multiply-connected two-dimensional geometries.
-Since groundwater flow occurs at small spatial and velocity scales, we
-assume the flow is viscous (ie.~zero Reynolds number).  By allowing for
-complex multiply-connected domains, we capture the effect that
-interacting bodies have on erosion, and the grains in the flow are
-individually resolved rather than homogenized.  We start by validating
-our method on a single circular body placed symmetrically in a pipe
-flow.  By artificially fixing the area of the body as a function of
-time, we are able to characterize the long-time behavior of the shape
-and the resulting flow and compare these results with analytical
-results.  Then, we compute the vorticity of erosion in
-multiply-connected geometries to better characterize erosion in porous
-media.
+In this fashion, individual pores are resolved rather than
+homogenized.  A boundary integral equation (BIE) is used to solve the
+incompressible Stokes equations in the complex geometry.  We resolve
+individual grains and the non-negligible interactions between bodies.
+To link the eroding body and fluid dynamics, the body is eroded in the
+normal direction at a rate that is proportional to the magnitude of the
+shear stress.
+
+To create high-fidelity and computationally efficient numerical methods,
+two fast and accurate methods are employed.  First, the fluid velocity
+and the erosion rate (shear stress) are efficiently computed with
+spectral accuracy by using a fast-multipole-accelerated BIE method.  The
+required spatial derivatives are computed with spectral accuracy in
+Fourier space.  In addition to compute the shear stress, we also compute
+the vorticity in the fluid bulk.  The vorticity is
+particularly insightful since it is identical to the shear stress on
+no-slip boundaries.  Therefore, by computing the vorticity, we are able
+to locate regions where the erosion rates will be fastest or slowest
+(Fig.~\ref{fig:50bodies}).
+
+Once the erosion rate is computed, the shape is integrated in time with
+second-order accuracy.  Tracking the interface of fluid-structure
+interaction problems with a long time horizon is particularly
+difficult---the mesh is often distorted and tangled by the dynamics and
+regions of high curvature develop.  These two issues are resolved by,
+first, introducing a tangential velocity field to maintain a grid that
+is equispaced in arclength, but that does not affect the dynamics, and,
+second, a curvature penalization term.  Furthermore, the frame of
+reference is changed to \thL~variables so that the curvature term
+appears as a diffusive term that can easily be handled in a numerically
+stable fashion, e.g.~via an exponential integrator or an implicit
+method.
+
+We validate our method on a single circular body placed symmetrically in
+a pipe flow.  By artificially fixing the area of the body as a function
+of time, we are able to characterize the long-time behavior of the shape
+and the resulting flow and these results agree with analytical results.
+Then, we compute the vorticity of erosion in multiply-connected
+geometries to better characterize erosion in porous media.
 
@@
 
-To create high-fidelity and computationally efficient numerical methods,
-two fast and accurate methods are employed.  First, the fluid equations
-and the erosion rate (shear stress) are efficiently solved with spectral
-accuracy by using a fast-multipole-accelerated BIE method.  Given the
-rate of erosion, the shape is integrated in time with second-order
-accuracy.  All spatial derivatives are computed in Fourier space,
-resulting in spectral accuracy in space.  To further visualize the
-effect of erosion, we compute the vorticity of the flow
-(Fig.~\ref{fig:50bodies}) to visualize regions of high and low erosion.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\todo[inline]{These are some of my thoughts on reworking this first paragraph. See if you like it.}
 We begin by making two fundamental design choices: first, we restrict
@@
 
-%\todo[inline]{This is the original below:}
-%There are two main limitations of the current
-%work.  First, the flow is assumed to be two-dimensional.  However, by
-%assuming that the flow is two-dimensional, we are able to simulate the
-%erosion of more bodies and with higher resolution than would be
-%available in three dimensions.  Moreover, several flows can be described
-%to good accuracy under a two-dimensional approximation, but certain
-%phenomena occur only in three dimensions.  Extending the current work to
-%three dimensions is possible with a boundary integral equation
-%formulation.  In particular, the fluid solvers exist~\cite{mal-bir2015},
-%and the main challenges of a BIE solver have been addressed by other
-%groups including surface representation~\cite{yin-bir-zor2006,
-%vee-rah-bir-zor2011}, near-singular integration~\cite{yin-bir-zor2006,
-%kli-tor2016b}, and fast summation methods~\cite{yin-bir-zor2004,
-%ros-ols2015}.  The more significant challenge of extending our work to
-%three dimensions is guaranteeing that the mesh does not become
-%distorted, which can be done, for example, by using an extension of the
-%two-dimensional {\thL} formulation~\cite{amb-sie-tlu2013}.
-%
-%The second limitation is that the eroding bodies are fixed.  Mitchell
-%and Spagnolie~\cite{mit-spa2016} simulate a single mobile eroding body
-%in three dimensions~\cite{mit-spa2016}, but additional challenges are
-%caused when there are multiple bodies. In particular, especially in
-%dense suspensions, bodies can become extremely close to one another, and
-%the interaction between the bodies is difficult to resolve unless the
-%underlying mesh is refined to levels that are intractable. In future
-%work we plan to consider mobile eroding bodies by including a small
-%force and torque to prevent unphysical contact~\cite{lu-rah-zor2017}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Related work} Simulating eroding bodies has been studied
-analytically, experimentally, and numerically.  Because of the scales
-involves with geophysical flows, most of these works consider high
-Reynolds number flows.  For instance, the experimental work of Moore et
-al.~\cite{moo-ris-chi-zha-she2013} considers on the order of $10^4$.
-For low Reynolds number flows, Mitchell and Spagnolie~\cite{mit-spa2016}
-use a BIE for the traction jump to simulate the erosion of a mobile body
-in three dimensions, but they only consider single body.
+analytically, experimentally, and numerically.  Many of these works are
+motivated by high Reynolds number geophysical applications, such as the
+work of the second author~\cite{moo-ris-chi-zha-she2013,
+ris-moo-chi-she-zha2012, moore2017riemann} and others~\cite{par-izu2000,
+lag2000, coh-dev-sey-yi-szy-rot2015, han1969, Rothman2012,
+hewett2017evolution, ristroph2018sculpting, lopez2018cfd,
+lachaussee2018competitive, cohen2016erosion}.  The work most closely
+related to ours simulates erosion in a three-dimensional incompressible
+Stokesian fluid~\cite{mit-spa2016}, but they only consider single
+eroding body.
 
@@
 which is an extension of the analysis done by Pironneau~\cite{pir1973}
-to find a Stokesian drag minimizing shape.  However, the effect of
-erosion on a porous media is less understood.  With the methods
-developed in this paper, quantities such as the total drag across a
-porous region as a function of time can be computed.
+to find a Stokesian drag minimizing shape.  In this idealized case,
+analytical axisymmetric shapes that minimize the drag can be found.
+However, the effect of erosion on a porous media is less understood.
 
@@
 
-Another numerical challenge with simulating erosion is that
-corners develop at points where the shear stress vanishes.  There is recent work for solving
-BIEs in geometries with corners by using
-carefully chosen local expansions around each corner~\cite{rac-ser2017,
-ser-rok2016} or panel-based graded meshes~\cite{hel2011,
-gil-hao-mar2014, bre2012}.  The limitation of these methods is that they
-require the corner's location, a non-uniform spaced mesh, and some of
-the methods have a large condition number.  One solution is to use two
-meshes---one for the quadrature the other for the interface tracking.
-Then, interpolation between the two grids is required, and this is the
-approach taken by Ojala and Tornberg~\cite{oja-tor2015}.  Instead of
-using two grids and interpolation operators, we only require the uniform
-grid by slightly modify the geometry to maintain sufficient regularity.
-First, we add a regularization term to the shear stress to penalize
-regions of high curvature.  Second, we apply a Gaussian filter to smooth
-the absolute value of the shear stress before the body shape is updated.
-
-Several groups consider the optimal body in a Stokes fluid that
-optimizes some quantity.  For example, Pironneau~\cite{pir1973} found
-the axisymmetric shape of a fixed volume body that minimizes drag is
-similar to an American football with an opening angle of 60 degrees, and
-this shape corresponds to a body with constant surface vorticity.  This
-analysis is taken further by Montenegro-Johnson and
-Lauga~\cite{mon-lau2015} where the optimal axisymmetric shape of fixed
-surface area is computed.  We include a similar calculation for the
-two-dimensional Stokes equations, and the resulting shape agrees with
-our numerical solution.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{s:formulation}
-We start by defining the main variables used to model erosion.  We only
+We start by defining the main variables used to model erosion.  We
 consider flows that are confined by a solid wall $\Gamma$ that encloses
-$M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.  The bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.
-On each body, $\nn$ and $\ss$ denote the unit normal and unit tangent vectors respectively.
-Throughout the paper, we adopt the convention that $\ss$ points in the counterclockwise direction and $\nn$ points out of the fluid domain (i.e.~into the bodies).
-Neglecting inertial forces, the dynamics of the fluid is
-fully characterized by the position of the bodies $\xx_\ell(s,t) \in
-\gamma_\ell$, where $s$ is the arclength and $t$ is time.  Given
+$M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.  The
+bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write
+$\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.  On each body, $\nn$ and
+$\ss$ denote the unit normal and unit tangent vectors respectively.
+Throughout the paper, we adopt the convention that $\ss$ points in the
+counterclockwise direction and $\nn$ points out of the fluid domain
+(i.e.~into the bodies). Neglecting inertial forces, the dynamics of the
+fluid is fully determined by the position of the bodies $\xx_\ell(s,t)
+\in \gamma_\ell$, where $s$ is the arclength and $t$ is time.  Given
 $\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid
@@
 
-To perform the simulations, we freeze the geometry at each time step,
-solve the incompressible Stokes equations, and then update the geometry
-according to the erosion model.  The separation between these two
-processes is justified since the time scale of erosion is much longer
-than that of the flow.
-
-%We use a quasi-static approximation.  That is, at each time step, we
-%freeze the geometry, solve the incompressible Stokes equations, and then
-%update the geometry according to the erosion model.  The two steps
-%inside the red rectangle describes a time step in the quasi-static
-%approximation.
-%\todo[inline]{Appeal to separation of scales to justify this quasi-static approximation; i.e.~the timescale of erosion is much longer than that of the flow.}
-
-Our erosion model is based on the shear stress, and this model is
-discussed in more detail in Section~\ref{sec:erosion}.  We then describe
-how the incompressible Stokes equations are solved in $\Omega$ using a
-boundary integral equation in Section~\ref{sec:bies}.  In
-Section~\ref{sec:shearStressLP}, we discuss how the shear stress is
+There are several models for erosion that involve the shear
+stress~\cite{par-izu2000,lag2000}.  The erosion model we adopt
+prescribes that erosion occurs in the normal direction at a rate that is
+proportional to the magnitude of the shear
+stress~\cite{moo-ris-chi-zha-she2013}.  The constant of proportionality
+only sets the time scale, so we let $\Vn = |\tau|$ as described in
+equation~\eqref{eqn:erosionModel}.  For the sake of numerical stability,
+we modify this law in Section~\ref{sec:thetaL}. To perform the
+simulations, we freeze the geometry at each time step, solve the
+incompressible Stokes equations, and then update the geometry according
+to the erosion model.  The separation between these two processes is
+justified since the time scale of erosion is much longer than that of
+the flow.
+
+We describe how the incompressible Stokes equations are solved in
+$\Omega$ using a boundary integral equation in Section~\ref{sec:bies}.
+In Section~\ref{sec:shearStressLP}, we discuss how the shear stress is
 computed.  Finally, in Section~\ref{sec:thetaL}, we describe how corners
-in the geometry are avoided and perform a change of coordinates to treat a stiff term.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Erosion model} 
-\label{sec:erosion}
-
-Other models for erosion include ones that use an erosion rate that is
-proportional to a power of the magnitude of the shear
-stress~\cite{par-izu2000}, or ones that use a critical shear stress
-below which erosion does not occur~\cite{lag2000}.
-
-To model erosion, the normal velocity is  proportional to the absolute
-value of the shear stress.   Since the constant of proportionality only
-sets the time scale, we let $\Vn = |\tau|$ as described in
-equation~\eqref{eqn:erosionModel}. For the sake of numerical stability,
-we modify this law in Section~\ref{sec:thetaL}.
+in the geometry are avoided and perform a change of coordinates to treat
+a stiff term.
 
@@
 into an equivalent BIE.  The boundary condition $\ff$ is the prescribed
-velocity $\UU$ on $\Gamma$, and it is zero on the grains $\gamma$.
-Since we are interested in two dimensions, a stream function formulation
-can be used by recasting the governing equations as a problem in
-analytic function theory~\cite{gre-kro-may1996}.  So that our work can
-extended to three dimensions, we instead use primitive variables by
-writing the velocity in terms of the standard double-layer
+velocity $\UU$ on $\Gamma$, and it is zero on the grains $\gamma$.  In
+two dimensions, a BIE for a stream function formulation is
+possible~\cite{gre-kro-may1996}, but this does not extend to three
+dimensions.  Therefore, we adopt a primitive variable formulation where
+the velocity is written in terms of the standard double-layer
 potential~\cite{lad1963,poz1992}
@@
 \end{align}
+
+One challenge with simulating erosion is that corners develop at points
+where the shear stress vanishes.  There is recent work for solving BIEs
+in geometries with corners by using carefully chosen local expansions
+around each corner~\cite{rac-ser2017, ser-rok2016} or panel-based graded
+meshes~\cite{hel2011, gil-hao-mar2014, bre2012}.  The limitation of
+these methods is that they require the corner's location, a non-uniform
+spaced mesh, and some of the methods have a large condition number.  One
+solution is to use two meshes---one for the quadrature the other for the
+interface tracking.  Then, interpolation between the two grids is
+required, and this is the approach taken by Ojala and
+Tornberg~\cite{oja-tor2015}.  Instead of using two grids and
+interpolation operators, we only require the uniform grid by slightly
+modify the geometry to maintain sufficient regularity.  First, we add a
+regularization term to the shear stress to penalize regions of high
+curvature.  Second, we apply a Gaussian filter to smooth the absolute
+value of the shear stress before the body shape is updated.
 

### 2018-03-21 docs/methods/erosion_methods.tex
working on edits

@@
 where $\Vn$ is the normal velocity of the interface and $\mu$ is the
-fluid viscosity.  The outer wall is formed by rounding off the corners
-of $[-3,3] \times [-1,1]$, and we enforce the Hagen-Poiseuille flow
+fluid viscosity.  There are several models for
+erosion~\cite{par-izu2000,lag2000}, but we have adopted the model that
+erosion occurs in the normal direction at a rate that is proportional to
+the magnitude of the shear stress~\cite{moo-ris-chi-zha-she2013}.  The
+constant of proportionality only sets the time scale, so we have set
+$\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.  For
+the sake of numerical stability, we modify this law in
+Section~\ref{sec:thetaL}.
+
+The outer wall is formed by rounding off the corners
+of $[-3,3] \times [-1,1]$, and we impose the Hagen-Poiseuille flow
 \begin{align*}
@@
 
-There are several models for erosion that involve the shear
-stress~\cite{par-izu2000,lag2000}.  The erosion model we adopt
-prescribes that erosion occurs in the normal direction at a rate that is
-proportional to the magnitude of the shear
-stress~\cite{moo-ris-chi-zha-she2013}.  The constant of proportionality
-only sets the time scale, so we let $\Vn = |\tau|$ as described in
-equation~\eqref{eqn:erosionModel}.  For the sake of numerical stability,
-we modify this law in Section~\ref{sec:thetaL}. To perform the
-simulations, we freeze the geometry at each time step, solve the
-incompressible Stokes equations, and then update the geometry according
-to the erosion model.  The separation between these two processes is
-justified since the time scale of erosion is much longer than that of
-the flow.
-
 We describe how the incompressible Stokes equations are solved in
@@
 
-In this section, we describe the boundary integral equations employed
-for the fluid equations.  In particular, we recast the incompressible
-Stokes equations with Dirichlet boundary conditions 
-\begin{alignat*}{3}
+In this section, we describe an equivalent BIE formulation of the
+incompressible Stokes equations with Dirichlet boundary conditions
+\begin{equation}
+  \begin{split}
   \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
   \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
-  \uu &= \ff,  && \xx \in \bd\Omega,
-\end{alignat*}
-into an equivalent BIE.  The boundary condition $\ff$ is the prescribed
-velocity $\UU$ on $\Gamma$, and it is zero on the grains $\gamma$.  In
-two dimensions, a BIE for a stream function formulation is
+  \uu &= \ff,  && \xx \in \bd\Omega.
+  \end{split}
+  \label{eqn:stokes}
+\end{equation}
+The boundary condition $\ff$ is the prescribed velocity $\UU$ on
+$\Gamma$, and it is zero on the eroding grains $\gamma$.  In two
+dimensions, a BIE for a stream function formulation is
 possible~\cite{gre-kro-may1996}, but this does not extend to three
@@
 
-The double-layer potential representation is only able to represent
-force- and torque-free velocity fields, so we complete the velocity
-representation with Stokeslets and Rotlets~\cite{pow-mir1987,pow1993}.
-This is done by complementing the double-layer potential with Stokeslets
-and rotlets centered inside each interior body
+Since the double-layer potential is not able to represent force- and
+torque-free velocity fields,  we complete the double-layer potential
+with Stokeslets and rotlets~\cite{pow-mir1987, pow1993}
 \begin{align}
@@
 where  $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
-$\ell^{th}$ body, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then,
-any solution of the Stokes equations with a Dirichlet boundary condition
-$\ff$ can be written in terms of the completed double-layer potential
+$\ell^{th}$ grainy, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.
+Then, the solution of~\eqref{eqn:stokes} is
 \begin{align}
@@
 
+This BIE formulation requires that $\bd\Omega$ is smooth.
+Unfortunately, smoothness is not guaranteed erosion since corners
+develop at locations where the shear stress vanishes.  One option is to
+modify our BIE to handle corners~\cite{rac-ser2017,
+ser-rok2016, hel2011, gil-hao-mar2014, bre2012}, but these methods
+require the corner's location, or a non-uniform spaced mesh, or are
+ill-conditioned.  Instead, make a slight modification to the erosion
+model in Section~\ref{sec:thetaL} which allows us to control the
+smoothness of the grains.  In this manner, the BIE as described above
+can be applied.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:shearStressLP}
-To compute the shear stress, there are two options.  First, instead of
-solving the BIE~\eqref{eqn:completed_BIE} for an arbitrary density
-function, a similar BIE can be solved for the
-traction~\cite{mit-spa2016}.  Alternatively, the traction corresponding
-to the double-layer potential of the velocity~\eqref{eqn:velocityDLP}
-can be computed using appropriate layer potentials.  While the first
-method bypasses a step by forming the traction jump directly, it does
-not allow us to directly compute other quantities such as the vorticity,
-so we use the second method.
-
-The shear stress is
+Once the density function, Stokeslets, and rotlets are computed, any
+desired quantity, including the shear stress, can be computed.  The
+shear stress is
 \begin{align*}
@@
 \end{align*}
-The reader may notice an unusual sign convention above, but this is simply a consequence of our conventions for $\nn$ and $\ss$ (see Fig.~\ref{fig:schematic}). 
-The velocity field of the
-completed double-layer potential~\eqref{eqn:completed_DLP} involves
-three terms: the double-layer potential, the Stokeslets, and the
+The reader may notice an unusual sign convention above, but this is
+simply a consequence of our conventions for $\nn$ and $\ss$ (see
+Fig.~\ref{fig:schematic}).  The velocity field of the completed
+double-layer potential~\eqref{eqn:completed_DLP} includes velocities
+from three terms: the double-layer potential, the Stokeslets, and the
 rotlets.  We compute the deformation tensor $\ssigma =
-\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ for each of these terms
-individually.
+\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of these terms individually.
 
 The deformation tensor of the double-layer
-potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$
+potential~\eqref{eqn:velocityDLP} at an interior point $\xx \in \Omega$
 is~\cite{qua-bir2014a}
@@
 taking the limit of equation~\eqref{eqn:shearStressDLP} when $\xx$ tends
-to $\xx_0 \in \bd\Omega$.  The limiting value is given by
+to $\xx_0 \in \bd\Omega$.  The limiting value is
 \begin{align*}
@@
 \end{align}
-The deformation tensor of the Stokeslets and
+Next, the deformation tensor of the Stokeslets and
 rotlets~\eqref{eqn:stokeslet_rotlet} are
@@
 \end{equation}
-Now that the deformation tensor of each component of the completed
-double-layer potential is computed, the shear stress at $\xx_0 \in
+Combining these deformation tensors, the shear stress at $\xx_0 \in
 \bd\Omega$ is
@@
 \end{align}
-
-One challenge with simulating erosion is that corners develop at points
-where the shear stress vanishes.  There is recent work for solving BIEs
-in geometries with corners by using carefully chosen local expansions
-around each corner~\cite{rac-ser2017, ser-rok2016} or panel-based graded
-meshes~\cite{hel2011, gil-hao-mar2014, bre2012}.  The limitation of
-these methods is that they require the corner's location, a non-uniform
-spaced mesh, and some of the methods have a large condition number.  One
-solution is to use two meshes---one for the quadrature the other for the
-interface tracking.  Then, interpolation between the two grids is
-required, and this is the approach taken by Ojala and
-Tornberg~\cite{oja-tor2015}.  Instead of using two grids and
-interpolation operators, we only require the uniform grid by slightly
-modify the geometry to maintain sufficient regularity.  First, we add a
-regularization term to the shear stress to penalize regions of high
-curvature.  Second, we apply a Gaussian filter to smooth the absolute
-value of the shear stress before the body shape is updated.
 
@@
 These are the main evolution equations for $\theta(\alpha,t)$ and $L(t)$.
-In addition, it is necessary to track a reference point for each body, so that the {\thL} variables can be converted back to cartesian coordinates.
+In addition, it is necessary to track a reference point for each body, so that the {\thL} variables can be converted back to Cartesian coordinates.
 We track the coordinates of the surface mean $\mean{\xx}$, which moves according to
@@
 \label{s:method}
-There are three main numerical methods that need to be developed.  In
-Section~\ref{sec:BIE}, we describe how the BIE~\eqref{eqn:completed_BIE}
-is solved.  Once the density function is found,
-Section~\ref{sec:shearStress} describes how the shear
-stress~\eqref{eqn:shearStressLP} is computed.  Then, in
+\todo[inline]{Here on Bryan's sections of editing}
+To perform the simulations, we freeze the geometry at each time step,
+solve the incompressible Stokes equations, and then update the geometry
+according to the erosion model.  The separation between these two
+processes is justified since the time scale of erosion is much longer
+than that of the flow.
+
+Given this separation of time scales, there are three main numerical
+methods that need to be developed.  In Section~\ref{sec:BIE}, we
+describe how the BIE~\eqref{eqn:completed_BIE} is solved.  Once the
+density function is found, Section~\ref{sec:shearStress} describes how
+the shear stress~\eqref{eqn:shearStressLP} is computed.  Then, in
 Section~\ref{sec:timeStepping}, a time stepping method for evolving the
@@
 Although the GMRES-iteration count is independent of the spatial resolution, $N_{\iin}$, it can depend on the number of bodies and/or their configuration.
-To illustrate this point, we show in Table \ref{itertab} the GMRES count for various cases ...
+To illustrate this point, we show in Table~\ref{itertab} the GMRES count for various cases ...
+\todo[inline]{preconditioning papers are~\cite{qua-cou-dar2018}
+and~\cite{qua-bir2015a}}
 

### 2018-03-23 docs/methods/erosion_methods.tex
NM

@@
 For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
-$\mu \umax \ell/ \log(\ell/a)$, where $a$ is a length scale of the cross-section and $a \ll \ell$. This relationship implies that the stress-per-unit-span on a 2D cross-section can be estimated as
+$\mu \umax \ell/ \log(\ell/a)$, where $a \ll \ell $ is a length scale of the cross-section. This relationship implies that the stress-per-unit-span on a 2D cross-section can be estimated as
 \begin{align}

### 2018-03-23 docs/methods/erosion_methods.tex
NM

@@
 For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
-$\mu \umax \ell/ \log(\ell/a)$, where $a \ll \ell $ is a length scale of the cross-section. This relationship implies that the stress-per-unit-span on a 2D cross-section can be estimated as
+$\mu \umax \ell/ \log(\ell/a)$, where $a \ll \ell $ is a length scale of the cross-section. This law implies that the stress-per-unit-span on a 2D cross-section is approximately
 \begin{align}
@@
 
-	Another important quantity that can be used to test our simulations is the drag exerted by the body as it erodes.
-Figure~\ref{area_drag}(b) shows the horizontal drag, $F_D$, calculated in the simulations (black curve) using Eq.~\eqref{eqn:drag}.
+	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, which offers a second check on our numerics.
+In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it erodes.
+The drag is calculated using ...
+
+	Figure~\ref{area_drag}(b) shows the horizontal drag, $F_D$, measured in the simulations (black curve) using Eq.~\eqref{eqn:drag}.
 In the context of slender-body theory, $F_D$ should be interpreted as drag-per-unit-span.

### 2018-03-23 docs/methods/erosion_methods.tex
NM

@@
 	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, which offers a second check on our numerics.
-In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it erodes.
-The drag is calculated using ...
-
-	Figure~\ref{area_drag}(b) shows the horizontal drag, $F_D$, measured in the simulations (black curve) using Eq.~\eqref{eqn:drag}.
-In the context of slender-body theory, $F_D$ should be interpreted as drag-per-unit-span.
-As seen in Fig.~\ref{area_drag}(b), the drag decreases gradually at first and then abruptly tends to zero in the very final moments.
+In Fig.~\ref{area_drag}(b), we show the horizontal drag on the simulated body as it erodes (black curve).
+The drag, $F_D$, is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, should be interpreted as the drag-per-unit-span on a 2D cross-section.
+As seen in the figure, $F_D$ decreases gradually at first, then abruptly tends to zero in the final moments as the vanishes.
 This behavior, though perhaps surprising, is consistent with the fact that drag vanishes {\em logarithmically} with body-size in 2D Stokes flow.

### 2018-03-23 docs/methods/erosion_methods.tex
edited section 3.1

@@
 \label{s:method}
-\todo[inline]{Here on Bryan's sections of editing}
-To perform the simulations, we freeze the geometry at each time step,
-solve the incompressible Stokes equations, and then update the geometry
-according to the erosion model.  The separation between these two
-processes is justified since the time scale of erosion is much longer
-than that of the flow.
-
-Given this separation of time scales, there are three main numerical
-methods that need to be developed.  In Section~\ref{sec:BIE}, we
-describe how the BIE~\eqref{eqn:completed_BIE} is solved.  Once the
-density function is found, Section~\ref{sec:shearStress} describes how
-the shear stress~\eqref{eqn:shearStressLP} is computed.  Then, in
+To perform numerical simulations, we exploit the difference
+between the erosion and fluid time scales.  Since erosion occurs
+much slower, we freeze the geometry at each time
+step, solve the incompressible Stokes equations, and then update the
+geometry according to the erosion model.  Therefore, there are three
+main numerical methods that need to be developed.  In
+Section~\ref{sec:BIE}, we describe how the BIE~\eqref{eqn:completed_BIE}
+is solved.  Once the density function is found,
+Section~\ref{sec:shearStress} describes how the shear
+stress~\eqref{eqn:shearStressLP} is computed.  Then, in
 Section~\ref{sec:timeStepping}, a time stepping method for evolving the
 interface according to equations~\eqref{eqn:Levo1}
-and~\eqref{eqn:thetaevo1} is described. So that we can form stable
-simulations with long time horizons, we use numerical methods that
-achieve spectral accuracy in space, second-order accuracy in time, and
-maintain an equispaced discretization of the bodies.  The boundaries are
-represented in Fourier space, giving us a set of discretization points
-$\xx_i$ of each body, and all derivatives and integrals (the arclength,
-curvature, and mean values) are computed with spectral accuracy using
-the Fourier representation.
+and~\eqref{eqn:thetaevo1} is described.
+
+To form stable simulations with long time horizons, we use numerical
+methods that achieve spectral accuracy in space, second-order accuracy
+in time, and maintain an equispaced discretization of the bodies.  The
+boundaries are represented in Fourier space, giving us a set of
+discretization points $\xx_i$ of each body, and all derivatives and
+integrals (the arclength, curvature, and mean values) are computed with
+spectral accuracy using the Fourier representation.
 
@@
 
-To numerically evaluate the completed double-layer
-potential~\eqref{eqn:completed_BIE}, let $N_\iin$ be the number of
-points on each of the $M$ bodies, and $N_\out$ be the number of points
-on the outer boundary.  Then, $N = MN_\iin + N_\out$ is the total number
-of discretization points of $\bd\Omega$.  The double-layer potential
+To numerically compute the completed double-layer
+potential~\eqref{eqn:completed_BIE}, we discretize each of the $M$
+bodies with  $N_\iin$ points, and the outer boundary with $N_\out$
+points.  Then, $N = MN_\iin + N_\out$ is the total number of
+discretization points of $\bd\Omega$.  The double-layer potential
 in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
@@
 \end{equation}
-for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  Since all the integrands are
-smooth and periodic, by using the trapezoid rule, we are guaranteed that
-the numerical solutions converges to the true solution with spectral
-accuracy.
+for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  We have applied the trapezoid
+rule since all the integrands are smooth and periodic, and this
+guarantees that the numerical solutions converges to the true solution
+with spectral accuracy.
 
@@
 and the bulk of the cost is evaluating the $N$-term sum
-in~\eqref{eqn:completed_BIE_discretized}.  Naively, evaluating this sum
-at all points requires $\bigO(N^2)$ operations.  To reduce the
-computational cost, we use the Fast Multipole Method
-(FMM)~\cite{gre-rok1987, gre-gre-may1992} to reduce the complexity from
-$\bigO(N^2)$ to $\bigO(N)$.  Since the number of required GMRES
-iterations is mesh-independent, the overall complexity for
-solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.
+in~\eqref{eqn:completed_BIE_discretized}. We use the Fast Multipole
+Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} so that the cost of
+solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$ operations.
 
@@
 \label{sec:shearStress}
+\todo[inline]{Bryan is here on editing}
 We have decomposed the deformation tensor into contributions from three

### 2018-03-24 docs/methods/erosion_methods.tex
NM

@@
 This law must be modified in two dimensions, though.
-The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012, zhao2015transportation}.
+The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012}.
 For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to

### 2018-03-24 docs/methods/erosion_methods.tex
NM

@@
 This law must be modified in two dimensions, though.
-The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012}.
+The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{batchelor1970slender, MooreJFM2012}.
 For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to

### 2018-03-25 docs/methods/erosion_methods.tex
small edits

--- 2018-03-23 docs/methods/erosion_methods.tex
@@
 \label{sec:shearStress}
-\todo[inline]{Bryan is here on editing}
 We have decomposed the deformation tensor into contributions from three
-different terms.  The contributions from the Stokeslets and the rotlets
-can be directly evaluated since $\rr \neq 0$ for all $\xx \in \gamma$.
-For the shear stress of the double-layer potential, we would like to use
-the trapezoid rule. The kernel of the deformation tensor due to
-the double-layer potential~\eqref{eqn:shearStressDLP} is 
+different terms.  The contributions from the Stokeslets and the
+rotlets~\eqref{eqn:shearStressSR} can be immediately evaluated since
+they do not involve any integration that needs to be approximated.  For
+the shear stress of the double-layer potential, we use a slight variant
+of the trapezoid rule. The kernel of the deformation tensor due to the
+double-layer
+potential~\eqref{eqn:shearStressDLP} is 
 \begin{align*}
@@
 \end{align*}
-Unfortunately, this kernel has a singularity that is asymptotic to
-$\bigO(\rho^{-2})$ when $\yy \rightarrow \xx$, and this is too strong
-for the trapezoid rule.  The singularity strength can be reduced since
-the velocity corresponding to a constant density function is
+This kernel has a singularity that is asymptotic to $\bigO(\rho^{-2})$
+when $\yy \rightarrow \xx$, and this is too strong for the unmodified
+trapezoid rule.  The singularity strength can be reduced since the
+velocity corresponding to a constant density function is
 constant~\cite{poz1992}.  Therefore, the deformation tensor of the
@@
 \end{align*}
-This expression for the deformation tensor has a singularity that is
-asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
-to achieve spectral accuracy, we apply odd-even
+This expression has a singularity that is asymptotic to
+$\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Then, to achieve
+spectral accuracy, we apply the trapezoid rule with odd-even
 integration~\cite{sid-isr1988}.  Therefore, the deformation tensor of
@@
 \end{align}
-and a similar approximation is used when $i$ is even.  The deformation
-tensor due to the Stokeslets and rotlets are given in
-equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
-deformation tensor~\eqref{eqn:shearStressJump} is computed with Fourier
-differentiation.  Finally, the shear stress is computed by multiplying the
-deformation tensor by the normal vector, and taking the inner product
-with the tangent vector.
+and a similar approximation is used when $i$ is even.  We also need to
+approximate the jump in the deformation
+tensor~\eqref{eqn:shearStressJump}, and this is done with Fourier
+differentiation.  Finally, the shear stress is computed by multiplying
+the deformation tensor by the normal vector, and taking the inner
+product with the tangent vector.
 
@@
 $\bigO(N^2)$.  However, this calculation is only performed once per time
-step as opposed to the velocity double-layer potential that must be
-evaluated at each GMRES iteration.  In future work, we plan to use a
-kernel-independent FMM~\cite{yin-bir-zor2004} to evaluate the shear
-stress with $\bigO(N)$ operations.
+step as opposed to the velocity double-layer potential, where we do
+employ the FMM, that must be evaluated at each GMRES iteration.  In
+future work, we plan to use a kernel-independent
+FMM~\cite{yin-bir-zor2004} to evaluate the shear stress with $\bigO(N)$
+operations.
 
@@
 \label{s:qoi}
+\todo[inline]{Bryan is here}
 To study characteristics of the flow, the vorticity

### 2018-03-25 docs/methods/erosion_methods.tex

@@
 This law must be modified in two dimensions, though.
-The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012, zhao2015transportation}.
+The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{batchelor1970slender, MooreJFM2012}.
 For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to

### 2018-03-25 docs/methods/erosion_methods.tex
NM

--- 2018-03-24 docs/methods/erosion_methods.tex
@@
 
-	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, which offers a second check on our numerics.
-In Fig.~\ref{area_drag}(b), we show the horizontal drag on the simulated body as it erodes (black curve).
-The drag, $F_D$, is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, should be interpreted as the drag-per-unit-span on a 2D cross-section.
-As seen in the figure, $F_D$ decreases gradually at first, then abruptly tends to zero in the final moments as the vanishes.
-This behavior, though perhaps surprising, is consistent with the fact that drag vanishes {\em logarithmically} with body-size in 2D Stokes flow.
-Equation \eqref{eqn:drag} also allows us to calculate the separate contributions of pressure and viscous drag, and we show these with the blue and green curves in Fig.~\ref{area_drag}(b).
+	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, offering a second check on our numerics.
+In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it erodes (black curve).
+The drag is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, this should be interpreted as the drag-per-unit-span.
+As seen in the figure, $F_D$ decreases gradually at first, then abruptly tends to zero in the final moments as the body vanishes.
+Though it may seem peculiar, the sudden drop to zero  is consistent with the fact that drag vanishes {\em logarithmically} with body size in 2D Stokes flow.
+Equation \eqref{eqn:drag} also permits us to calculate the contributions of pressure and viscous drag separately, which are shown by the blue and green curves in Fig.~\ref{area_drag}(b).
 Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag.
-As the body erodes and assumes a more slender form, though, the pressure drag decreases much more rapidly, leaving viscous drag to dominate.
-This behavior is associated with the tendency towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
+As the body erodes and assumes a more slender form, though, the pressure drag decreases more rapidly, leaving viscous drag to dominate.
+This behavior is associated with convergence towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
 
@@
 \end{align}
-For the case of a {\em circular} cylinder, the normalization factor of $4 \pi$ produces an {\em exact} relationship (under the slender-body assumptions), where $a$ is taken to be the radius.
+For a {\em circular} cylinder, the normalization factor $4 \pi$ produces an {\em exact} relationship (within the context of slender-body theory), where $a$ is taken to be the radius.
 For other shapes the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale since it generalizes the case of a circle.
-In Fig.~\ref{area_drag}(b) we show this scaling prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
-The scaling law and measured drag agree closely as $t \to t_f$, thus confirming that our simulation accurately captures the slender-body limit as the shape disappears.
+In Fig.~\ref{area_drag}(b) we show the drag scaling prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
+The scaling law and measured drag agree closely as $t \to t_f$, confirming that our simulation accurately captures the slender-body limit as the shape disappears.
 
@@
 With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
-Certain features of this shape can be predicted analytically by appealing to the principal that, in long time, the shear stress becomes uniformly distributed along the body.
-In particular, consider the angle formed at the front and rear stagnation points.
-In a small region around this point, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$.
-See Fig.~\ref{corner} for a schematic.
-This problem can be solved exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$.
+In particular, consider the corner formed at the front and rear of the body.
+Locally, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge; see Fig.~\ref{corner} for a schematic.
+We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface.
+The surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$.
 (In this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).

### 2018-03-25 docs/methods/erosion_methods.tex
NM

@@
 This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$ and odd symmetry about the horizontal axis, $f(0) = f''(0) = 0$.
-For arbitrary opening angle $\beta$, ODE \eqref{fODE} and its boundary conditions constitute an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
-We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and thus set $\lambda = 2$.
-The corresponding solution to \eqref{fODE} that satisfies odd symmetry is given by
-\begin{align}
-  f(\theta) = B \sin (2 \theta) + C \theta \, ,
-\end{align}
-and imposing the no-slip boundary conditions gives the condition
+For arbitrary opening angle, ODE \eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
+We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and therefore set $\lambda = 2$.
+The odd-symmetric solution to \eqref{fODE} that corresponds to $\lambda=2$ is given by
+\begin{align}
+  f(\theta) = B \sin (2 \theta) + C \theta \, .
+\end{align}
+Imposing the no-slip boundary conditions gives the condition
 \begin{align}
@@
 \end{align}
-This nonlinear equation has solution $\thb \approx 129^\circ$, which gives the uniform-stress opening angle as $\oangle \approx 102^\circ$ degrees. 
+This nonlinear equation has solution $\thb \approx 129^\circ$, which implies that the the uniform-stress wedge has an opening angle of $\oangle \approx 102^\circ$.
 % Pozrikidis page 239: symmetric flow.
 
-\todo[inline]{Here in revising}
+We comment
 
@@
 Previous numerical simulations on erosion in 3D Stokes flow revealed that, in long time, an eroding body tends to a shape that is approximately (though not precisely) Pironneau's optimal profile \cite{mit-spa2016}.
+
+\todo[inline]{Here in revising}
 

### 2018-03-25 docs/methods/erosion_methods.tex
edited some more

--- 2018-03-25 docs/methods/erosion_methods.tex
@@
 for a single body, and Section~\ref{s:MultiResults} presents numerical
-  examples for multiply-connected domains.  Finally, concluding remarks are made in Section~\ref{s:conclusions}
+examples for multiply-connected domains.  Finally, concluding remarks
+are made in Section~\ref{s:conclusions}
 
@@
 rotlets~\eqref{eqn:shearStressSR} can be immediately evaluated since
-they do not involve any integration that needs to be approximated.  For
-the shear stress of the double-layer potential, we use a slight variant
-of the trapezoid rule. The kernel of the deformation tensor due to the
-double-layer
-potential~\eqref{eqn:shearStressDLP} is 
+they do not involve any integration to approximate.  For the shear
+stress of the double-layer potential, we use a slight variant of the
+trapezoid rule. The kernel of the deformation tensor due to the
+double-layer potential~\eqref{eqn:shearStressDLP} is 
 \begin{align*}
@@
 \label{s:qoi}
-\todo[inline]{Bryan is here}
-To study characteristics of the flow, the vorticity
+We further characterize the flow by computing the vorticity
 (Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
-and drag (Section~\ref{sec:drag}) will be computed.  Once
-equation~\eqref{eqn:completed_DLP} is solved for the density function,
-Stokeslets, and rotlets, all of these quantities can be computed.  For
-target points in the fluid domain, the resulting layer potentials
-involve integrands that are periodic and smooth, so the trapezoid rule
-guarantees spectral accuracy~\cite{tre-wei2014}.  However, if the target
-point is close to $\bd \Omega$, a nearly-singular integrand must be
-integrated, and this requires upsampling that is described in
-Section~\ref{sec:NSI}.  When the target points is on the boundary, the
-integrands involve singularities that are evaluated by combining
-singularity subtraction and odd-even integration~\cite{sid-isr1988}.
+and drag (Section~\ref{sec:drag}).  Once
+equation~\eqref{eqn:completed_DLP} is solved, the vorticity, pressure,
+and drag can be computed at arbitrary target points.  For target points
+in the fluid domain, the integrands of the layer potentials are periodic
+and smooth, and the trapezoid rule guarantees spectral
+accuracy~\cite{tre-wei2014}.  However, if the target point is close to
+$\bd \Omega$, a nearly-singular integrand must be integrated, and this
+requires upsampling that is described in Section~\ref{sec:NSI}.  When
+the target points is on the boundary, the integrands involve
+singularities that are evaluated by combining singularity subtraction
+and odd-even integration~\cite{sid-isr1988}.
 
@@
 \label{sec:vorticity}
-We start by computing the vorticity $\omega(\xx) = v_x - u_y$ for $\xx \in
-\Omega$.  As we did for the shear stress, we compute the vorticity due
-to the double-layer potential, Stokeslets, and rotlets individually.
-The vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at
+We start by computing the vorticity $\omega(\xx) = v_x - u_y$ for $\xx
+\in \Omega$ which we decompose into contributions from the double-layer
+potential, Stokeslets, and rotlets.  The vorticity of the double-layer
+potential~\eqref{eqn:velocityDLP} at
 $\xx \in \Omega$ is
@@
 \end{align}
-The vorticity due to the Stokeslet is
+To compute~\eqref{eqn:vorticityDLP} numerically, we apply the trapezoid
+rule with an upsampling scheme described in Section~\ref{sec:NSI}.
+Next, the vorticity due to the Stokeslet is
 \begin{align*}
@@
 \end{align*}
-To compute~\eqref{eqn:vorticityDLP} numerically, we apply the trapezoid
-rule with an upsampling scheme described in Section~\ref{sec:NSI}.
 
 For the Stokes equations, on boundaries that have a no-slip boundary
-condition, the shear stress is equivalent to the vorticity $\omega = v_x -
-u_y$.  Therefore, we do not need to compute the vorticity for $\xx \in
-\bd\Omega$.
+condition, the shear stress is equivalent to the vorticity.  Therefore,
+the vorticity is computed on the grains $\gamma_\ell$ by numerically
+compute the shear stress as described in Section~\ref{sec:shearStress}.
 
@@
 \label{sec:pressure}
-To compute the pressure at $\xx \in \Omega$, we follow the
-same procedure used for the shear stress.  We start by computing the
-pressure of the double-layer potential for $\xx \in \Omega$ and add the
-appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
-is
+To compute the pressure at $\xx \in \Omega$, we follow the same
+procedure used for the shear stress.  We first compute the pressure of
+the double-layer potential for $\xx \in \Omega$ and add the appropriate
+jump if $\xx \in \Gamma$. By taking the Laplacian of the Stokes
+double-layer potential~\eqref{eqn:velocityDLP}, the pressure at $\xx \in
+\Omega$ is
 \begin{align}
@@
 The pressure due to the Stokeslets is
-\begin{align}
+\begin{align*}
   p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
-  \label{eqn:shearPressureSR}
-\end{align}
+\end{align*}
 and the pressure due to the rotlets is zero.  Therefore, the pressure is
-\begin{alignat*}{3}
-  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), &&\xx \in \Omega,\\
-  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
-              p^{S}(\xx), \quad && \xx \in \bd\Omega.
-\end{alignat*}
+\begin{align*}
+  p(\xx) = p^{\DD}(\xx) + p^{S}(\xx), \quad \xx \in \Omega,
+\end{align*}
 To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid
@@
 
-To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
-as $\xx$ tends to $\xx_0$.  The limiting value is given
-by~\cite{qua-bir2014a}
-\begin{align}
-  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
-    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
+For target points on the boundary of the geometry, $\xx \in \bd \Omega$,
+there is an additional term resulting from a jump in the pressure
+double-layer potential~\cite{poz1992}
+\begin{align}
+  p(\xx)= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
+              p^{S}(\xx), \quad \xx \in \bd\Omega.
   \label{eqn:pressureJump}
@@
 corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
-too strong for the trapezoid rule to be directly applied.  Therefore, we
-again subtract a constant density function and write the pressure as
+too strong when $\xx \in \bd\Omega$ for the trapezoid rule to be
+directly applied.  Therefore, we again subtract a constant density
+function and write the pressure as
 \begin{align*}
@@
 computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
-evaluate this layer potential for pressure.  The pressure due to the
-Stokeslets are given in equation~\eqref{eqn:shearPressureSR}.  Finally,
-to add the jump condition~\eqref{eqn:pressureJump}, Fourier
-differentiation is used to compute the arclength derivative.
+evaluate this layer potential for pressure, and the jump condition
+in~\eqref{eqn:pressureJump} is computed with Fourier differentiation.
 
@@
 \label{sec:drag}
-With the pressure and shear stress, the drag on a single body with
-boundary $\gamma_\ell$ is
+Once the pressure and shear stress is computed, the drag on a single
+body with boundary $\gamma_\ell$ is
 \begin{align}
@@
 function.  Based on numerical experiments, the error of the $N$-point
-trapezoid rule is acceptable for points $\xx$ that are more than 5
-arclength spacings from $\bd\Omega$. For points that are closer than 5
-arclength spacings to $\bd\Omega$, we use an upsampled trapezoid rule.
-The required upsampling of the geometry and the density function is done
-with a Fourier interpolant.  To minimize the number of discretization
-points that are used to approximate the layer
+trapezoid rule is acceptable for points $\xx$ that are more than five 
+arclength spacings from $\bd\Omega$. For points that are closer than
+five arclength spacings to $\bd\Omega$, we use an upsampled trapezoid
+rule.  The required upsampling of the geometry and the density function
+is done with a Fourier interpolant.  To minimize the number of
+discretization points that are used to approximate the layer
 potential~\eqref{eqn:layerPotential}, we use the same upsampling rate
@@
 another for upsampling to be sufficient.  Therefore, we plan to
-implement a near-singular integration scheme that uses either
-near-singular interpolation~\cite{qua-bir2014a}, quadrature by
-expansion~\cite{klo-bar-gre-one2013}, Barycentric
-interpolation~\cite{bar-wu-vee2015}, or panel-based
-quadrature~\cite{hel-oja2008a}.
+implement one of several near-singular integration schemes available in
+the literature~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
+hel-oja2008a}.
 

### 2018-03-25 docs/methods/erosion_methods.tex

@@
 
-As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, which offers a second check on our numerics.
-In Fig.~\ref{area_drag}(b), we show the horizontal drag on the simulated body as it erodes (black curve).
-The drag, $F_D$, is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, should be interpreted as the drag-per-unit-span on a 2D cross-section.
-As seen in the figure, $F_D$ decreases gradually at first, then abruptly tends to zero in the final moments as the vanishes.
-This behavior, though perhaps surprising, is consistent with the fact that drag vanishes {\em logarithmically} with body-size in 2D Stokes flow.
-Equation \eqref{eqn:drag} also allows us to calculate the separate contributions of pressure and viscous drag, and we show these with the blue and green curves in Fig.~\ref{area_drag}(b).
+	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, offering a second check on our numerics.
+In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it erodes (black curve).
+The drag is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, this should be interpreted as the drag-per-unit-span.
+As seen in the figure, $F_D$ decreases gradually at first, then abruptly tends to zero in the final moments as the body vanishes.
+Though it may seem peculiar, the sudden drop to zero  is consistent with the fact that drag vanishes {\em logarithmically} with body size in 2D Stokes flow.
+Equation \eqref{eqn:drag} also permits us to calculate the contributions of pressure and viscous drag separately, which are shown by the blue and green curves in Fig.~\ref{area_drag}(b).
 Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag.
-As the body erodes and assumes a more slender form, though, the pressure drag decreases much more rapidly, leaving viscous drag to dominate.
-This behavior is associated with the tendency towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
+As the body erodes and assumes a more slender form, though, the pressure drag decreases more rapidly, leaving viscous drag to dominate.
+This behavior is associated with convergence towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
 

### 2018-03-26 docs/methods/erosion_methods.tex
NM

@@
 	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, offering a second check on our numerics.
-In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it erodes (black curve).
+In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it changes in time (black curve).
 The drag is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, this should be interpreted as the drag-per-unit-span.
 As seen in the figure, $F_D$ decreases gradually at first, then abruptly tends to zero in the final moments as the body vanishes.
-Though it may seem peculiar, the sudden drop to zero  is consistent with the fact that drag vanishes {\em logarithmically} with body size in 2D Stokes flow.
-Equation \eqref{eqn:drag} also permits us to calculate the contributions of pressure and viscous drag separately, which are shown by the blue and green curves in Fig.~\ref{area_drag}(b).
+Though it may seem peculiar, the sudden drop to zero  is consistent with the 2D Stokes law in which drag vanishes {\em logarithmically} with body size.
+Additionally, \eqref{eqn:drag} permits us to calculate the separate contributions of pressure and viscous drag, shown by the blue and green curves in Fig.~\ref{area_drag}(b).
 Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag.
 As the body erodes and assumes a more slender form, though, the pressure drag decreases more rapidly, leaving viscous drag to dominate.
-This behavior is associated with convergence towards a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
+This behavior is associated with convergence to a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
 
@@
 For other shapes the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale since it generalizes the case of a circle.
-In Fig.~\ref{area_drag}(b) we show the drag scaling prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
-The scaling law and measured drag agree closely as $t \to t_f$, confirming that our simulation accurately captures the slender-body limit as the shape disappears.
+In Fig.~\ref{area_drag}(b) we show this prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
+The scaling law and measured drag agree closely as $t \to t_f$, confirming that the simulation accurately captures the slender-body limit as the solid disappears.
 
@@
 
-We comment
-
-We note that this uniform-stress shape is closely related to the so-called `optimal profile in Stokes flow' found by Pironneau (1973) \cite{pir1973}, who determined the shape that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume (see also \cite{mon-lau2015} for an interesting related shape).
-Pironneau's 3D shape has an opening angle of $120^{\circ}$ and ours is simply the 2D counterpart with its slightly different $102^{\circ}$ opening angle.
-Previous numerical simulations on erosion in 3D Stokes flow revealed that, in long time, an eroding body tends to a shape that is approximately (though not precisely) Pironneau's optimal profile \cite{mit-spa2016}.
+\subsection{Fixed-area simulations}
 
 \todo[inline]{Here in revising}
-
-\subsection{Fixed-area simulations}
 
@@
 % npts = 1024
+
+\todo[inline]{Here in revising}
+%We comment
+ %A comment on how these results compare to erosion in 3D Stokes flow is in order.
+
+We note that this uniform-stress shape is closely related to the so-called `optimal profile in Stokes flow' found by Pironneau (1973) \cite{pir1973}, who determined the shape that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume (see also \cite{mon-lau2015} for an interesting related shape).
+Pironneau's 3D shape has an opening angle of $120^{\circ}$ and ours is simply the 2D counterpart with its slightly different $102^{\circ}$ opening angle.
+Previous numerical simulations on erosion in 3D Stokes flow revealed that, in long time, an eroding body tends to a shape that is approximately (though not precisely) Pironneau's optimal profile \cite{mit-spa2016}.
 

### 2018-03-26 docs/methods/erosion_methods.tex
NM

@@
 The drag is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, this should be interpreted as the drag-per-unit-span.
-As seen in the figure, $F_D$ decreases gradually at first, then abruptly tends to zero in the final moments as the body vanishes.
-Though it may seem peculiar, the sudden drop to zero  is consistent with the 2D Stokes law in which drag vanishes {\em logarithmically} with body size.
-Additionally, \eqref{eqn:drag} permits us to calculate the separate contributions of pressure and viscous drag, shown by the blue and green curves in Fig.~\ref{area_drag}(b).
+As seen in the figure, $F_D$ decreases gradually at first, then abruptly drops to zero in the final moments as the body vanishes.
+Though it may seem peculiar, the sudden drop is consistent with the 2D Stokes law in which drag vanishes {\em logarithmically} with body size.
+Additionally, \eqref{eqn:drag} permits us to calculate the separate contributions of pressure and viscous drag, which we show by the blue and green curves in Fig.~\ref{area_drag}(b) respectively.
 Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag.
@@
 In Fig.~\ref{area_drag}(b) we show this prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
-The scaling law and measured drag agree closely as $t \to t_f$, confirming that the simulation accurately captures the slender-body limit as the solid disappears.
+The scaling law and measured drag agree closely as $t \to t_f$, confirming that the simulation accurately captures the slender limit as the body disappears.
 
@@
 We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface.
-The surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$.
+For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$.
 (In this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
@@
 This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$ and odd symmetry about the horizontal axis, $f(0) = f''(0) = 0$.
-For arbitrary opening angle, ODE \eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
+For arbitrary $\beta$, ODE \eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
 We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and therefore set $\lambda = 2$.
@@
 
-\todo[inline]{Here in revising}
+To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations.
+Section \ref{sec:scaling}, however, shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy in the critical moments when the body is expected to approach its limiting shape.
+To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
+\begin{align}
+\Vn \leftarrow \Vn - \mean{\Vn} \, .
+\end{align}
+This modification allows erosion to sculpt the shape as it would normally, but with the area artificially held fixed.
 
@@
 
-To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations.
-Section \ref{sec:scaling}, however, shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy just in the final critical moments when the body is expected to approach its limiting shape.
-To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
-\begin{align}
-\Vn \leftarrow \Vn - \mean{\Vn} \, .
-\end{align}
-This modification allows erosion to sculpt the shape as it would normally, but with the area artificially held fixed.
-
 	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process.
@@
 The inset in Fig.~\ref{fixed_intface}(a) shows a zoom of the body's rear stagnation point, demonstrating that the near-corner is actually smooth on a fine scale, in accordance with our numerical smoothing.
-Likewise, Fig.~\ref{fixed_intface}(b) shows the stress distribution on the evolving body, revealing that stress becomes more uniform as time proceeds.
+Figure~\ref{fixed_intface}(b) shows the stress distribution on the evolving body, revealing that stress becomes more uniform as time proceeds.
 Interestingly, the slight rise in shear near the front/rear corners that was seen in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that the effect was due to loss of accuracy.
 Here, time is normalized by the same vanishing time $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
-Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state.
-This contrasts with previous studies of high-Reynolds-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
+Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
 
@@
 The fixed-area simulations allow for us to precisely measure characteristics of the shape.
-In particular, Fig.~\ref{fig:arangle} shows measurements of the body's aspect ratio (its width to height) and the front opening angle as they vary in time.
+In particular, Fig.~\ref{fig:arangle} shows measurements of the body's aspect ratio (its width to height) and the front opening angle as they change in time.
 We show these measurements for three simulations in which the smoothing parameters, $\eps$ and $\sigma$, are sequentially reduced, allowing us to assess convergence in these parameters.
@@
 \todo[inline]{Here in revising}
-%We comment
+
  %A comment on how these results compare to erosion in 3D Stokes flow is in order.

### 2018-03-26 docs/methods/erosion_methods.tex
small edits to methods paper

@@
 are included with high-order accuracy by using an integral equation
-method.  Integral equations have been used extensively to simulate
-viscous fluids in complex geometries.  One particular application are
-particulate flows, such as bubbles or droplets, and the classic book of
-Pozrikidis~\cite{poz1992} describes BIEs for such problems.  For nearly
+method~\cite{poz1992}.  Integral equations have been used extensively to
+simulate viscous fluids in complex geometries, including porous media
+flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.  For nearly
 touching bodies, the quadrature associated with discretizing a BIE can
@@
 
-\todo[inline]{paper of Bryan, Eric, and Pieter and one with Pietro,
-George, and Ruben}
-
 \bibliographystyle{plainnat} 

### 2018-03-26 docs/methods/erosion_methods.tex
NM

@@
 Locally, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge; see Fig.~\ref{corner} for a schematic.
-We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface.
-For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$.
-(In this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
+We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface \cite{moo-ris-chi-zha-she2013, moore2017riemann}.
+For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$ (in this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
 
@@
 This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$ and odd symmetry about the horizontal axis, $f(0) = f''(0) = 0$.
-For arbitrary $\beta$, ODE \eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
+For arbitrary opening angle, ODE \eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
 We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and therefore set $\lambda = 2$.
@@
 \end{align}
-Imposing the no-slip boundary conditions gives the condition
+Imposing no slip along the wedge surface gives the condition
 \begin{align}
@@
 
-To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations.
-Section \ref{sec:scaling}, however, shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy in the critical moments when the body is expected to approach its limiting shape.
+We now aim to measure the opening angle formed in our simulations for comparison with the above prediction.
+However, Section \ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy in the critical moments when the body is expected to approach its limiting shape.
 To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,

### 2018-03-26 docs/methods/erosion_methods.tex
NM

@@
 
-We now aim to measure the opening angle formed in our simulations for comparison with the above prediction.
-However, Section \ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy in the critical moments when the body is expected to approach its limiting shape.
+We now aim to measure the opening angles formed in our simulations for comparison with this prediction.
+However, Section \ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
 To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
@@
 Importantly, more numerical accuracy is now available to quantify the terminal state.
-The inset in Fig.~\ref{fixed_intface}(a) shows a zoom of the body's rear stagnation point, demonstrating that the near-corner is actually smooth on a fine scale, in accordance with our numerical smoothing.
-Figure~\ref{fixed_intface}(b) shows the stress distribution on the evolving body, revealing that stress becomes more uniform as time proceeds.
-Interestingly, the slight rise in shear near the front/rear corners that was seen in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that the effect was due to loss of accuracy.
-Here, time is normalized by the same vanishing time $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
-Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
+The inset in Fig.~\ref{fixed_intface}(a) is a zoom demonstrating that, due to our numerical regularization, the near corner at the body's rear is actually smooth on a fine scale.
+We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces.
+As observed before, the stress becomes more evenly distributed as erosion reshapes the body.
+The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy.
+Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points.
+In this figure, time is normalized by the same value $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
+Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state
+
+%Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
 

### 2018-03-26 docs/methods/erosion_methods.tex
NM

@@
 \includegraphics[width = 0.4 \textwidth]{./figs/corner.pdf}
-\caption{Schematic of 2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function $\psi(r,\theta)$ for $\theta \in [-\theta_0, \theta_0]$}.
+\caption{Schematic of 2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function in polar coordinates $\psi(r,\theta)$, for $\theta \in [-\theta_0, \theta_0]$}.
 \label{corner}
@@
 
-We now aim to measure the opening angles formed in our simulations for comparison with this prediction.
+We now aim to measure the opening angles formed in our numerical simulations to compare against this prediction.
 However, Section \ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
@@
 Importantly, more numerical accuracy is now available to quantify the terminal state.
-The inset in Fig.~\ref{fixed_intface}(a) is a zoom demonstrating that, due to our numerical regularization, the near corner at the body's rear is actually smooth on a fine scale.
+The inset in Fig.~\ref{fixed_intface}(a) is a zoom showing that, due to our numerical regularization, the near corner at the body's rear is actually smooth on a fine scale.
 We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces.
@@
 In this figure, time is normalized by the same value $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
-Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state
 
@@
 % Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state.
+In particular, we measure the aspect ratio of the body (the ratio of width to height) and the opening angle of the front/rear corner.
+As shown in Fig.~\ref{fig:arangle}(a)
 

### 2018-03-26 docs/methods/erosion_methods.tex
NM

@@
 
-	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process.
+	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process, with the same spatial resolution, $N_\iin = 1024$, as before.
 Notice the body obtains a similar profile as observed previously, but with fixed area.
@@
 \includegraphics[width = 0.85 \textwidth]{./figs/arangle.pdf}
-\caption{Shape characteristics of an eroding body: (a) The aspect ratio, defined as the width to height, versus time.
+\caption{Shape characteristics of an eroding body: (a) The aspect ratio (width to height) versus time.
 (b) The measured opening angle versus time.
 For both measurements, we show three cases of the smoothing parameters: $\eps = \sigma = 20/1024, 10/1024,$ and 5/1024.
-In the most resolved simulation (5/1024) the aspect ratio converges to 2.7 and the opening angle converges to the predicted value of $102^{\circ}$ in long time.}
+In the finest simulation ($5/1024$) the aspect ratio converges to 2.7 and the opening angle converges to the predicted value of $102^{\circ}$ in long time.}
 \label{fig:arangle}
@@
 These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state.
-In particular, we measure the aspect ratio of the body (the ratio of width to height) and the opening angle of the front/rear corner.
-As shown in Fig.~\ref{fig:arangle}(a)
+In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corner as they vary in time.
+In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters: $\eps = \sigma = 20/1024, 10/1024,$ and 5/1024.
 

### 2018-03-26 docs/methods/erosion_methods.tex
NM

@@
 These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state.
-In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corner as they vary in time.
-In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters: $\eps = \sigma = 20/1024, 10/1024,$ and 5/1024.
-
-The fixed-area simulations allow for us to precisely measure characteristics of the shape.
-In particular, Fig.~\ref{fig:arangle} shows measurements of the body's aspect ratio (its width to height) and the front opening angle as they change in time.
-We show these measurements for three simulations in which the smoothing parameters, $\eps$ and $\sigma$, are sequentially reduced, allowing us to assess convergence in these parameters.
-As shown in Fig.~\ref{fig:arangle}(a), the aspect ratio begins at one for the initial circular geometry and increases in time as erosion sculpts a more slender shape.
-The aspect ratio reaches a long time limit of about 2.7 in the most resolved simulation.
-Fig.~\ref{fig:arangle}b shows the body's opening angle, which we measure by fitting the tangent angle $\theta(\alpha)$ with a 7th degree polynomial over a region excluding the front/rear stagnation point (where a near-corner is approximated by a smooth curve of very high curvature).
-The polynomial fit is then extrapolated to the stagnation point to obtain an angle estimate (subject to some uncertainty, which we estimate below).
+In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
+In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma = 20/1024, 10/1024,$ and 5/1024) so that we can assess how the numerical smoothing influences shape.
+Figure\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
+The initially circular geometry has an aspect ratio of unity, and, as erosion carves a more slender form, the aspect ratio increases monotonically.
+The three simulations are all very close to one another, which demonstrates convergence as the smoothing parameters are reduced.
+In the most accurate simulation (i.e.~the least smoothing), the aspect ratio tends to a value of 2.7 in long time.
+
+Next, we aim to measure the opening angle that develops at the front and rear of the body.
+Since these simulations are actually smooth on a fine scale, a true corner does not exist and we must instead estimate the apparent angle that results from a small region of high curvature.
+To this end, we first fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region that excludes a small vicinity of the front/rear stagnation points ($\alpha = 0, 0.5$).
+We then extrapolate the polynomial to the stagnation points which gives an estimate of the angle there.
+This protocol is subject to some uncertainty, which we will examine further below.
+
 As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.

### 2018-03-26 docs/methods/erosion_methods.tex
NM

@@
 Next, we aim to measure the opening angle that develops at the front and rear of the body.
-Since these simulations are actually smooth on a fine scale, a true corner does not exist and we must instead estimate the apparent angle that results from a small region of high curvature.
-To this end, we first fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region that excludes a small vicinity of the front/rear stagnation points ($\alpha = 0, 0.5$).
-We then extrapolate the polynomial to the stagnation points which gives an estimate of the angle there.
-This protocol is subject to some uncertainty, which we will examine further below.
-
-As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
+Since these simulations are actually smooth on a fine scale, a true corner does not exist and we must instead estimate the apparent angle due to a small region of high curvature.
+To this end, we first fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the front/rear stagnation points ($\alpha = 0, 0.5$).
+We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there.
+Although it is subject to some uncertainty (to be examined below), we have found this strategy to give robust angle measurements.
+In Fig.~\ref{fig:arangle}(b), we show the opening angle on the eroding body for the same three cases of smoothing parameters.
+The method gives an angle measurement of $180^{\circ}$ for the initially circular geometry, thus providing some confirmation.
+As time moves forward, erosion carves a sharper corner and the angle decreases monotonically.
+Here, the effect of the smoothing parameters is more visible, but we still see convergence as $\eps, \sigma \to 0$.
+In the most accurate simulation (black), the opening angle converges to a value of $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.
+
+%As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
 Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in the most resolved simulation.
@@
 
-To examine the influence of the smoothing parameters, $\eps$ and
-$\sigma$, we show in Table~\ref{table:arangle} the measurements of the
-aspect ratio and the opening angle for different simulations.
+To examine in more detail the influence of the smoothing parameters, we show in Table
+
+We now examine in detail the influence of the smoothing parameters and the uncertainty in the angle measurements...
+
+\todo[inline]{Here in revising}
+
+To examine the influence of the smoothing parameters, $\eps$ and $\sigma$, we show in Table~\ref{table:arangle} the measurements of the aspect ratio and the opening angle for different simulations.
 We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal.
@@
 % npts = 1024
-
-\todo[inline]{Here in revising}
 

### 2018-03-26 docs/methods/erosion_methods.tex
edits to paper

@@
 homogenized.  A boundary integral equation (BIE) is used to solve the
-incompressible Stokes equations in the complex geometry.  We resolve
-individual grains and the non-negligible interactions between bodies.
-To link the eroding body and fluid dynamics, the body is eroded in the
-normal direction at a rate that is proportional to the magnitude of the
-shear stress.
+incompressible Stokes equations in the complex geometry.  The resulting
+method resolves individual grains and the non-negligible interactions
+between bodies.  To link the eroding body and fluid dynamics, the body
+is eroded in the normal direction at a rate that is proportional to the
+magnitude of the shear stress.
 
@@
 two fast and accurate methods are employed.  First, the fluid velocity
-and the erosion rate (shear stress) are efficiently computed with
-spectral accuracy by using a fast-multipole-accelerated BIE method.  The
-required spatial derivatives are computed with spectral accuracy in
-Fourier space.  In addition to compute the shear stress, we also compute
-the vorticity in the fluid bulk.  The vorticity is
-particularly insightful since it is identical to the shear stress on
-no-slip boundaries.  Therefore, by computing the vorticity, we are able
-to locate regions where the erosion rates will be fastest or slowest
-(Fig.~\ref{fig:50bodies}).
+and the erosion rate (shear stress) are computed with a
+fast-multipole-accelerated Kryolv method applied to a spectrally
+accurate discretization of the governing equations.  In particular,
+GMRES~\cite{saa-sch1986} is applied to a spectrally-accurate Nystr\"om
+discretization of the BIE~\cite{tre-wei2014}, a spectrally accurate
+quadrature rule is used to compute the shear stress~\cite{sid-isr1988},
+and all arclength derivatives are computed with Fourier differentiation.
+In addition to compute the shear stress, we also compute the vorticity
+in the fluid bulk.  The vorticity is particularly insightful since it is
+identical to the shear stress on no-slip boundaries.  Therefore, by
+computing the vorticity, we are able to identify regions where the
+erosion rate will be fast or slow (Fig.~\ref{fig:50bodies}).
 
@@
 interaction problems with a long time horizon is particularly
-difficult---the mesh is often distorted and tangled by the dynamics and
-regions of high curvature develop.  These two issues are resolved by,
-first, introducing a tangential velocity field to maintain a grid that
-is equispaced in arclength, but that does not affect the dynamics, and,
-second, a curvature penalization term.  Furthermore, the frame of
-reference is changed to \thL~variables so that the curvature term
+difficult---the mesh is often distorted and tangled.  Moreover, erosion
+naturally leads to regions of high or infinite (i.e.~corners) curvature.
+These interface tracking issues are resolved by, first, introducing a
+tangential velocity field to maintain a grid that is equispaced in
+arclength, but that does not affect the dynamics, and, second, a tunable
+term that penalizes regions of high curvature.  Furthermore, the frame
+of reference is changed to \thL~variables so that the curvature term
 appears as a diffusive term that can easily be handled in a numerically
-stable fashion, e.g.~via an exponential integrator or an implicit
-method.
+stable fashion with an exponential integrator.
 
@@
 geometries to better characterize erosion in porous media. 
+\todo[inline]{Bryan is here in editing}
 

### 2018-03-27 docs/methods/erosion_methods.tex
went through intro again

@@
 geometries to better characterize erosion in porous media.
-\todo[inline]{Bryan is here in editing}
 
@@
 \paragraph{Limitations} 
-
-We begin by making two fundamental design choices: first, we restrict
-ourselves to two spatial dimensions, and second the bodies are
-considered immobile (i.e.~fixed to their initial locations). The
-restriction to two dimensions allows us to simulate the erosion of many bodies
-(up to $50$ in this manuscript) with high resolution, giving us the
-ability to accurately characterize the erosion of a porous medium. While
-BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
+We begin by making two fundamental design choices: first, we restrict ourselves to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
+The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium.
+While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
 The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Related work} Simulating eroding bodies has been studied
-analytically, experimentally, and numerically.  Many of these works are
-motivated by high Reynolds number geophysical applications, such as the
-work of the second author~\cite{moo-ris-chi-zha-she2013,
-ris-moo-chi-she-zha2012, moore2017riemann} and others~\cite{par-izu2000,
-lag2000, coh-dev-sey-yi-szy-rot2015, han1969, Rothman2012,
-hewett2017evolution, ristroph2018sculpting, lopez2018cfd,
-lachaussee2018competitive, cohen2016erosion}.  The work most closely
-related to ours simulates erosion in a three-dimensional incompressible
-Stokesian fluid~\cite{mit-spa2016}, but they only consider single
-eroding body.
+\paragraph{Related work} Simulating eroding bodies has been studied analytically, experimentally, and numerically.
+Many of these works are motivated by high Reynolds number geophysical applications, such as the work of the second author~\cite{moo-ris-chi-zha-she2013, ris-moo-chi-she-zha2012, moore2017riemann} and others~\cite{par-izu2000, lag2000, coh-dev-sey-yi-szy-rot2015, han1969, Rothman2012, hewett2017evolution, ristroph2018sculpting, lopez2018cfd, lachaussee2018competitive, cohen2016erosion}.
+The work most closely related to ours simulates erosion in a three-dimensional incompressible Stokesian fluid~\cite{mit-spa2016}, but they only consider single eroding body.
 
@@
 simulate viscous fluids in complex geometries, including porous media
-flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.  For nearly
-touching bodies, the quadrature associated with discretizing a BIE can
-lead to instabilities of specialized quadrature is not applied.  Since
-our bodies do not move, we are able to use upsampling, but future work
-will require a near-singular integration scheme~\cite{qua-bir2014a,
+flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}. Challenges of a
+BIE formulation include resolving the interactions between nearly
+touching bodies and developing efficient preconditioners for the
+discretized system.  Possible preconditioners include
+multigrid~\cite{qua-bir2015a} and the inverse fast multipole
+method~\cite{qua-cou-dar2018}, but the results presented in this work
+require no more than $\mathcal{O}(100)$ GMRES iterations which is too
+small to make preconditioners for BIEs effective; preconditioners will
+be considered further in future work when there are many more grains
+that are also dynamic.  To address the nearly-singular integrands, we
+take advantage of the fact that the grains are eroding and not moving,
+so their separation increases with time.  Therefore, in this work, we
+apply an upsampling scheme, but in future work, we will require a
+near-singular integration scheme~\cite{qua-bir2014a,
 klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.

### 2018-03-27 docs/methods/erosion_methods.tex
NM

@@
 We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and therefore set $\lambda = 2$.
-The odd-symmetric solution to \eqref{fODE} that corresponds to $\lambda=2$ is given by
+The odd-symmetric solution to \eqref{fODE} corresponding to $\lambda=2$ is
 \begin{align}
@@
 
-We now aim to measure the opening angles formed in our numerical simulations to compare against this prediction.
+We now aim to measure the opening angles formed in the numerical simulations to compare against the above prediction.
 However, Section \ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
@@
 Importantly, more numerical accuracy is now available to quantify the terminal state.
-The inset in Fig.~\ref{fixed_intface}(a) is a zoom showing that, due to our numerical regularization, the near corner at the body's rear is actually smooth on a fine scale.
+The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear of the body to demonstrate that, due to our numerical regularization, what appears to be a corner is actually smooth on a fine scale.
 We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces.

### 2018-03-27 docs/methods/erosion_methods.tex
NM

@@
 We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces.
-As observed before, the stress becomes more evenly distributed as erosion reshapes the body.
+As observed previously, the stress becomes more evenly distributed as erosion reshapes the body.
 The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy.
 Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points.
-In this figure, time is normalized by the same value $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
-
+
+%In this figure, time is normalized by the same value $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
 %Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
@@
 In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
-In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma = 20/1024, 10/1024,$ and 5/1024) so that we can assess how the numerical smoothing influences shape.
-Figure\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
+In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma = 20/1024, 10/1024,$ and 5/1024) so that we can assess how the numerical regularization influences shape.
+Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
 The initially circular geometry has an aspect ratio of unity, and, as erosion carves a more slender form, the aspect ratio increases monotonically.
-The three simulations are all very close to one another, which demonstrates convergence as the smoothing parameters are reduced.
+The three simulations are all very close to one another, demonstrating convergence as $\eps, \sigma \to 0$.
 In the most accurate simulation (i.e.~the least smoothing), the aspect ratio tends to a value of 2.7 in long time.

### 2018-03-27 docs/methods/erosion_methods.tex
NM

@@
 Importantly, more numerical accuracy is now available to quantify the terminal state.
-The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear of the body to demonstrate that, due to our numerical regularization, what appears to be a corner is actually smooth on a fine scale.
+The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear corner demonstrate that, due to our numerical regularization, the body is actually smooth on a fine scale.
 We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces.
@@
 In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
-In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma = 20/1024, 10/1024,$ and 5/1024) so that we can assess how the numerical regularization influences shape.
+In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma$ taking the values 20/1024, 10/1024, and 5/1024) to assess how the numerical regularization influences shape.
 Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
@@
 The three simulations are all very close to one another, demonstrating convergence as $\eps, \sigma \to 0$.
-In the most accurate simulation (i.e.~the least smoothing), the aspect ratio tends to a value of 2.7 in long time.
-
-Next, we aim to measure the opening angle that develops at the front and rear of the body.
-Since these simulations are actually smooth on a fine scale, a true corner does not exist and we must instead estimate the apparent angle due to a small region of high curvature.
-To this end, we first fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the front/rear stagnation points ($\alpha = 0, 0.5$).
+In the simulation with these least smoothing ($\eps = \sigma = 5/1024$), the aspect ratio tends to a value of 2.7 in long time.
+
+Next, we aim to measure the opening angle of the front/rear corner.
+Since these simulated bodies are actually smooth, though, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points.
+To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5).
 We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there.
-Although it is subject to some uncertainty (to be examined below), we have found this strategy to give robust angle measurements.
+Although this procedure is subject to some uncertainty (to be examined below), we have found it to give robust angle measurements.
 In Fig.~\ref{fig:arangle}(b), we show the opening angle on the eroding body for the same three cases of smoothing parameters.

### 2018-03-28 docs/methods/erosion_methods.tex
NM

@@
 (b) The shear-stress distribution on each of these interfaces.
-As the body erodes and converges to a terminal form, the stress becomes more uniformly distributed over the entire surface.}
+As the body erodes and converges to a terminal form, the stress becomes more uniformly distributed over the entire surface.
+Here time is normalize by the same value $t_f = 1.79 \times 10^{-2}$ from Fig.~\ref{shrink_intface}.}
 \label{fixed_intface}

### 2018-03-28 docs/methods/erosion_methods.tex
NM

@@
 Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points.
-
-%In this figure, time is normalized by the same value $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.
-%Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.
+In this figure, time is normalized by the vanishing time $t_f = 1.79 \times 10^{-2}$ from the shrinking simulations (Fig.~\ref{shrink_intface}).
+Curiously, about 3 multiples of $t_f$ are required to reach a visual steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state emerges more quickly \cite{moo-ris-chi-zha-she2013}.
 

### 2018-03-28 docs/methods/erosion_methods.tex
NM

@@
 In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
-In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma$ taking the values 20/1024, 10/1024, and 5/1024) to assess how the numerical regularization influences shape.
+In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters (keeping $\eps = \sigma$ and taking the values 20/1024, 10/1024, and 5/1024) to assess how the numerical regularization influences shape.
 Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
@@
 Next, we aim to measure the opening angle of the front/rear corner.
-Since these simulated bodies are actually smooth, though, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points.
+Since these simulated bodies are actually smooth, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points.
 To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5).

### 2018-03-28 docs/methods/erosion_methods.tex
NM

@@
 Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points.
-In this figure, time is normalized by the vanishing time $t_f = 1.79 \times 10^{-2}$ from the shrinking simulations (Fig.~\ref{shrink_intface}).
-Curiously, about 3 multiples of $t_f$ are required to reach a visual steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state emerges more quickly \cite{moo-ris-chi-zha-she2013}.
+In this figure, time is normalized by the vanishing time $t_f = 1.79 \times 10^{-2}$ from the shrinking simulations (i.e.~Fig.~\ref{shrink_intface}).
+Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerges before the body vanishes \cite{moo-ris-chi-zha-she2013}.
 
@@
 In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
-In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters (keeping $\eps = \sigma$ and taking the values 20/1024, 10/1024, and 5/1024) to assess how the numerical regularization influences shape.
+In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters to assess how the numerical regularization influences shape.
+In all three cases, we keep the two parameters equal $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and 5/1024.
 Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.

### 2018-03-28 docs/methods/erosion_methods.tex
NM

@@
 In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters to assess how the numerical regularization influences shape.
-In all three cases, we keep the two parameters equal $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and 5/1024.
+In all three cases, we keep the two parameters equal $\eps = \sigma$ and set to the values 20/1024, 10/1024, and 5/1024 respectively.
 Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
@@
 	Next, we aim to measure the opening angle of the front/rear corner.
-Since these simulated bodies are actually smooth, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points.
+Since these simulated bodies are actually smooth on a fine scale, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points.
 To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5).
@@
 Although this procedure is subject to some uncertainty (to be examined below), we have found it to give robust angle measurements.
-In Fig.~\ref{fig:arangle}(b), we show the opening angle on the eroding body for the same three cases of smoothing parameters.
-The method gives an angle measurement of $180^{\circ}$ for the initially circular geometry, thus providing some confirmation.
-As time moves forward, erosion carves a sharper corner and the angle decreases monotonically.
-Here, the effect of the smoothing parameters is more visible, but we still see convergence as $\eps, \sigma \to 0$.
-In the most accurate simulation (black), the opening angle converges to a value of $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.
-
-%As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry.
-Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in the most resolved simulation.
-This coincides exactly with the valued predicted by our local solutions.
-
-To examine in more detail the influence of the smoothing parameters, we show in Table
-
-We now examine in detail the influence of the smoothing parameters and the uncertainty in the angle measurements...
+Figure \ref{fig:arangle}(b) shows the opening angle, $\beta$, as it varies in time for the three cases of smoothing parameters.
+For the initially circular geometry, our procedure yields the correct result of a $180^{\circ}$ opening angle, i.e.~a flat front face.
+As time proceeds, erosion carves a sharper corner and $\beta$ decreases monotonically.
+Here, the three curves are more easily distinguished than in Fig.~\ref{fig:arangle}(a), implying that the opening angle is more sensitive to the level of numerical smoothing.
+Nonetheless, the curves show convergence as $\eps, \sigma \to 0$.
+In the finest simulation ($\eps = \sigma = 5/1024$), $\beta$ converges to the value $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.
+
+	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening-angle measurements for the three cases.
+Loosely, with $N_\iin = 1024$ fixed, the values 20/1024, 10/1024, and 5/1024 correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
+As seen in the table, both the aspect ratio and the opening angle converge as $\eps, \sigma \to 0$ with roughly first order.
+To quantify the uncertainty involved in our angle measurement procedure, we show the estimated uncertainty, which is obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation point....
 
@@
 
-To examine the influence of the smoothing parameters, $\eps$ and $\sigma$, we show in Table~\ref{table:arangle} the measurements of the aspect ratio and the opening angle for different simulations.
-We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal.
-We choose the values $20/1024$, $10/1024$, and $5/1024$.
-Loosely, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively.
-As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$.
+%We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal. 
+%Loosely, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively. 
+%As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$.
 We also estimate the uncertainty in the angle measurements by varying the region of the polynomial fit and the degree of the fit.

### 2018-03-29 docs/methods/erosion_methods.tex
NM

@@
 For a {\em circular} cylinder, the normalization factor $4 \pi$ produces an {\em exact} relationship (within the context of slender-body theory), where $a$ is taken to be the radius.
-For other shapes the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale since it generalizes the case of a circle.
+For other shapes, the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale since it generalizes the case of a circle.
 In Fig.~\ref{area_drag}(b) we show this prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
@@
 	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process, with the same spatial resolution, $N_\iin = 1024$, as before.
-Notice the body obtains a similar profile as observed previously, but with fixed area.
-Importantly, more numerical accuracy is now available to quantify the terminal state.
+Notice the body obtains a similar profile as observed previously, but now with fixed area.
+Importantly, more numerical accuracy is available to quantify the terminal state.
 The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear corner demonstrate that, due to our numerical regularization, the body is actually smooth on a fine scale.
@@
 
-	These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state.
+	These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches the terminal state.
 In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
-In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters to assess how the numerical regularization influences shape.
-In all three cases, we keep the two parameters equal $\eps = \sigma$ and set to the values 20/1024, 10/1024, and 5/1024 respectively.
+In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters, $\eps$ and $\sigma$, to assess how the numerical regularization influences shape.
+In the three cases, we keep $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and 5/1024 respectively.
 Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
@@
 Figure \ref{fig:arangle}(b) shows the opening angle, $\beta$, as it varies in time for the three cases of smoothing parameters.
-For the initially circular geometry, our procedure yields the correct result of a $180^{\circ}$ opening angle, i.e.~a flat front face.
+For the initially circular geometry, our procedure yields the correct opening angle of $180^{\circ}$, i.e.~a flat front face.
 As time proceeds, erosion carves a sharper corner and $\beta$ decreases monotonically.
-Here, the three curves are more easily distinguished than in Fig.~\ref{fig:arangle}(a), implying that the opening angle is more sensitive to the level of numerical smoothing.
-Nonetheless, the curves show convergence as $\eps, \sigma \to 0$.
+Here, the three simulation curves are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing.
+The curves nevertheless show convergence as $\eps, \sigma \to 0$.
 In the finest simulation ($\eps = \sigma = 5/1024$), $\beta$ converges to the value $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.
 
-	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening-angle measurements for the three cases.
+	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three simulations.
 Loosely, with $N_\iin = 1024$ fixed, the values 20/1024, 10/1024, and 5/1024 correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.

### 2018-03-29 docs/methods/erosion_methods.tex
NM

@@
 	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three simulations.
-Loosely, with $N_\iin = 1024$ fixed, the values 20/1024, 10/1024, and 5/1024 correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
-As seen in the table, both the aspect ratio and the opening angle converge as $\eps, \sigma \to 0$ with roughly first order.
-To quantify the uncertainty involved in our angle measurement procedure, we show the estimated uncertainty, which is obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation point....
+Loosely speaking, since $N_\iin = 1024$ is fixed, the values $\eps = \sigma = $ 20/1024, 10/1024, and 5/1024 correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
+The table shows that both the aspect ratio and opening angle converge with roughly first-order as $\eps, \sigma \to 0$.
+In addition, we show an estimate of the uncertainty involved in our angle measurement, which is obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
+The estimates show that as $\eps, \sigma \to 0$ the angle-measurements become more precise and converge to the predicted value of $102^{\circ}$.
 
 \todo[inline]{Here in revising}
-
-%We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal. 
-%Loosely, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively. 
-%As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$.
-We also estimate the uncertainty in the angle measurements by varying the region of the polynomial fit and the degree of the fit.
-As shown in the table, as the smoothing parameters are reduced, the angle measurements become more precise.
 

### 2018-03-29 docs/methods/erosion_methods.tex
NM

@@
 As time proceeds, erosion carves a sharper corner and $\beta$ decreases monotonically.
-Here, the three simulation curves are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing.
+Here, the three simulation curves are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing than is the aspect ratio.
 The curves nevertheless show convergence as $\eps, \sigma \to 0$.
@@
 The table shows that both the aspect ratio and opening angle converge with roughly first-order as $\eps, \sigma \to 0$.
-In addition, we show an estimate of the uncertainty involved in our angle measurement, which is obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
+In addition, we show an estimate of the uncertainty involved in our angle measurement, which we obtain by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
 The estimates show that as $\eps, \sigma \to 0$ the angle-measurements become more precise and converge to the predicted value of $102^{\circ}$.
-
-\todo[inline]{Here in revising}
 
@@
 
- %A comment on how these results compare to erosion in 3D Stokes flow is in order.
-
-We note that this uniform-stress shape is closely related to the so-called `optimal profile in Stokes flow' found by Pironneau (1973) \cite{pir1973}, who determined the shape that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume (see also \cite{mon-lau2015} for an interesting related shape).
-Pironneau's 3D shape has an opening angle of $120^{\circ}$ and ours is simply the 2D counterpart with its slightly different $102^{\circ}$ opening angle.
-Previous numerical simulations on erosion in 3D Stokes flow revealed that, in long time, an eroding body tends to a shape that is approximately (though not precisely) Pironneau's optimal profile \cite{mit-spa2016}.
+	In summary, we have found that a single-body eroding in 2D Stokes flow converges to a terminal form characterized by nearly uniform shear stress along its surface.
+The final shape is fairly slender, with an aspect ratio of 2.7, and distinguished by  corners of opening angle $102^{\circ}$ at the front and rear.
+This shape is closely related to the drag-minimizing profile found by Pironneau (1973) --- the geometry that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume \cite{pir1973}.
+Using variational principles, Pironneau showed that the drag-minimizing form has constant shear (or vorticity) along its surface.
+The resulting axisymmetric shape has an aspect ratio of 2.1 and opening-angles of $120^{\circ}$ \cite{pir1973, mit-spa2016}.
+Interestingly, simulations of 3D viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form \cite{mit-spa2016}.
+It was shown that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
+Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ \cite{pir1973, mit-spa2016}.
+Pironneau's argument that the drag-minimizing form has constant surface stress easily generalizes to 2D.
+Therefore, the final shape observed in our simulations is very nearly the form that minimizes drag in 2D Stokes flow subject to fixed area, with the only deviation being how much the surface stress fails to be precisely uniform.
 
@@
 
+\todo[inline]{Here in revising}
+
 \section{Results: Multi-body erosion}

### 2018-03-29 docs/methods/erosion_methods.tex
NM

@@
 
-As a final validation, we now aim to verify that our method converges with second-order accuracy in time.
-To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
-This stopping time is 56\% of the time it takes the body to vanish, and was selected so that the body will have eroded substantially but is not so small that accuracy is compromised.
-We assess error by measuring the difference between simulations of successive resolutions (i.e.~we verify Cauchy convergence).
-In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time.
-At each stage we halve the timestep $\Delta t$.
-Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations.
-The table confirms that our method to converges with second-order accuracy.
-In the table, we also show the CPU time of the simulation run on a single processor (though the algorithm is easily parallelized), showing a linear increase in computational time.
+As a final validation, we now verify that our method converges with the expected second-order accuracy in time.
+For this, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
+This stopping time is 56\% of the vanishing time, and was selected so that the body will have eroded substantially but is not small enough to compromise accuracy (due to the stress diverging).
+We assess error by measuring the $L^2$-difference in the body shape obtained from simulations of successive resolution, with $\Delta t$ halved at each stage.
+In Table \ref{convtab}, we report these errors along with the order of accuracy as obtained by Richardson-extrapolation-type calculations.
+The table confirms that our method converges with expected second-order accuracy.
+The last column of the table shows the CPU time taken for the simulation to run on a single-processor machine, demonstrating a nearly linear increase in computational time.
+Though the main parts of the algorithm are easily paralyzed, the single-processor times provide a simple assessment of method's complexity.
 
@@
 
-\todo[inline]{Here in revising}
-
 \section{Results: Multi-body erosion}
@@
 \subsection{Fixed pressure drop condition and validation}
+
+\todo[inline]{Here in revising}
 

### 2018-03-29 docs/methods/erosion_methods.tex
NM

@@
 
-\todo[inline]{Here in revising}
-
 With the numerical method validated, we are now ready to simulate the erosion of multiple bodies.
@@
 We therefore impose the condition of a fixed pressure difference by dynamically controlling the incoming flow-rate, $\umax$.
-This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed, then measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies.
+This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed and measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies.
 The vertically-averaged upstream and downstream pressures are given by
@@
 \end{align}
-We then rescale the computed density function by the pressure difference
+Next, we rescale the computed density function by the pressure difference
 \begin{align}
@@
 
+\todo[inline]{Here in revising}
+
 Briefly, to verity that the rescaling does not alter accuracy, we show in Table \ref{convtab} a convergence test for a 20-body simulation with the condition of fixed pressure drop imposed.

### 2018-03-30 docs/methods/erosion_methods.tex
NM

@@
 The table shows that both the aspect ratio and opening angle converge with roughly first-order as $\eps, \sigma \to 0$.
-In addition, we show an estimate of the uncertainty involved in our angle measurement, which we obtain by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
+In addition, we show an estimate of the uncertainty involved in our angle measurement, obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
 The estimates show that as $\eps, \sigma \to 0$ the angle-measurements become more precise and converge to the predicted value of $102^{\circ}$.

### 2018-03-30 docs/methods/erosion_methods.tex
NM

@@
 Using variational principles, Pironneau showed that the drag-minimizing form has constant shear (or vorticity) along its surface.
-The resulting axisymmetric shape has an aspect ratio of 2.1 and opening-angles of $120^{\circ}$ \cite{pir1973, mit-spa2016}.
-Interestingly, simulations of 3D viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form \cite{mit-spa2016}.
+The resulting {\em axisymmetric} shape has an aspect ratio of 2.1 and opening-angles of $120^{\circ}$ \cite{pir1973, mit-spa2016}.
+Interestingly, 3D simulations of viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form \cite{mit-spa2016}.
 It was shown that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
 Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ \cite{pir1973, mit-spa2016}.
-Pironneau's argument that the drag-minimizing form has constant surface stress easily generalizes to 2D.
-Therefore, the final shape observed in our simulations is very nearly the form that minimizes drag in 2D Stokes flow subject to fixed area, with the only deviation being how much the surface stress fails to be precisely uniform.
+Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well, and, therefore, the shape we observe to develop is approximately the form that minimizes drag subject to fixed area.
+%Therefore, the final shape observed in our simulations is very nearly the form that minimizes drag in 2D Stokes flow subject to fixed area, with the only deviation being how much the surface stress fails to be precisely uniform.
 

### 2018-03-30 docs/methods/erosion_methods.tex
NM

@@
 Using variational principles, Pironneau showed that the drag-minimizing form has constant shear (or vorticity) along its surface.
-The resulting {\em axisymmetric} shape has an aspect ratio of 2.1 and opening-angles of $120^{\circ}$ \cite{pir1973, mit-spa2016}.
+The resulting {\em axisymmetric} shape has an aspect ratio of 2.1 and front/rear opening-angles of $120^{\circ}$ \cite{pir1973, mit-spa2016}.
 Interestingly, 3D simulations of viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form \cite{mit-spa2016}.
 It was shown that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
-Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ \cite{pir1973, mit-spa2016}.
-Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well, and, therefore, the shape we observe to develop is approximately the form that minimizes drag subject to fixed area.
-%Therefore, the final shape observed in our simulations is very nearly the form that minimizes drag in 2D Stokes flow subject to fixed area, with the only deviation being how much the surface stress fails to be precisely uniform.
+Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ for self-similar reduction \cite{pir1973, mit-spa2016}.
+Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well, and, therefore, the shape that develops in our simulations is approximately the form that minimizes drag subject to fixed area.
+%with the only deviation being how much the surface stress fails to be precisely uniform.
 

### 2018-03-31 docs/methods/erosion_methods.tex
NM

@@
 	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three simulations.
-Loosely speaking, since $N_\iin = 1024$ is fixed, the values $\eps = \sigma = $ 20/1024, 10/1024, and 5/1024 correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
-The table shows that both the aspect ratio and opening angle converge with roughly first-order as $\eps, \sigma \to 0$.
+Since $N_\iin = 1024$ is fixed, the values $\eps = \sigma = $ 20/1024, 10/1024, and 5/1024 roughly correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
+The table shows that both the aspect ratio and opening angle converge with first-order as $\eps, \sigma \to 0$.
 In addition, we show an estimate of the uncertainty involved in our angle measurement, obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
@@
 Interestingly, 3D simulations of viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form \cite{mit-spa2016}.
-It was shown that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
+It was found that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
 Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ for self-similar reduction \cite{pir1973, mit-spa2016}.
-Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well, and, therefore, the shape that develops in our simulations is approximately the form that minimizes drag subject to fixed area.
-%with the only deviation being how much the surface stress fails to be precisely uniform.
+Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well.
+Therefore, the shape observed to develop in our simulations is approximately the form that minimizes drag subject to fixed area.
+How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, which can be seen in Fig.~\ref{shrink_intface}(b).
 
@@
 We assess error by measuring the $L^2$-difference in the body shape obtained from simulations of successive resolution, with $\Delta t$ halved at each stage.
-In Table \ref{convtab}, we report these errors along with the order of accuracy as obtained by Richardson-extrapolation-type calculations.
+In Table \ref{convtab}, we report these errors along with the order of accuracy, obtained by Richardson-extrapolation-type calculations.
 The table confirms that our method converges with expected second-order accuracy.
@@
 With the numerical method validated, we are now ready to simulate the erosion of multiple bodies.
-We make one important conceptual change to our model.
-For a realistic porous medium composed of many solid bodies, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
-A more realistic condition is that the pressure difference from one end to another is held fixed.
-For example, in groundwater flow, this condition would correspond to a recharge region of given hydraulic head connecting to a discharge region of another hydraulic head.
-
-We therefore impose the condition of a fixed pressure difference by dynamically controlling the incoming flow-rate, $\umax$.
-This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed and measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies.
-The vertically-averaged upstream and downstream pressures are given by
+First, though, we will make one important conceptual change to the model.
+For a realistic porous medium, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
+In groundwater flow, for example, it is more realistic to have an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
+In our simulations, we will therefore impose the condition that the pressure difference across the domain remains fixed.
+
+To impose the condition of a fixed pressure difference, we will dynamically control the incoming flow rate, $\umax$.
+To this end, we first compute the Stokes flow with $\umax = 1$ prescribed and measure the corresponding pressure at an upstream ($x = -2$) and downstream ($x=2$) location.
+We define the vertically-averaged upstream and downstream pressures as
 \begin{align}
@@
 \end{align}
-This rescaling maintains a {\em fixed} pressure difference between the upstream ($x=-2$) and downstream ($x=2$) positions.
-Because the Stokes equations are linear, such a rescaling is permissible and does not alter the accuracy of our method.
-Furthermore, {\em dynamic} rescaling is also permissible because the Stokes equations are memoryless (i.e.~there is no time derivative present in the PDEs).
+The velocity and pressure fields depend linearly on $\eeta$ and so this rescaling maintains a {\em fixed} pressure difference between the upstream and downstream locations.
+Since the Stokes equations are linear, the rescaled flow remains a solution to the PDE system (valid to the same numerical accuracy).
+Furthermore, since the Stokes equations are time-independent, rescaling $U$ by a different value at each time step does not introduce any additional error.
 
@@
 
-\todo[inline]{Here in revising}
-
 Briefly, to verity that the rescaling does not alter accuracy, we show in Table \ref{convtab} a convergence test for a 20-body simulation with the condition of fixed pressure drop imposed.
@@
 and~\cite{qua-bir2015a}}
+
+%Briefly, to verify that these rescaled solutions achieve the same order of accuracy, we report a convergence test in Table \ref{convtab}. In
 
@@
 
+\todo[inline]{Here in revising}
+
 \subsection{Multi-body erosion}

### 2018-03-31 docs/methods/erosion_methods.tex
NM

@@
 With the numerical method validated, we are now ready to simulate the erosion of multiple bodies.
-First, though, we will make one important conceptual change to the model.
+We will first make one conceptual change to the model though.
 For a realistic porous medium, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
-In groundwater flow, for example, it is more realistic to have an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
-In our simulations, we will therefore impose the condition that the pressure difference across the domain remains fixed.
-
-To impose the condition of a fixed pressure difference, we will dynamically control the incoming flow rate, $\umax$.
-To this end, we first compute the Stokes flow with $\umax = 1$ prescribed and measure the corresponding pressure at an upstream ($x = -2$) and downstream ($x=2$) location.
+In groundwater flow, for example, the more common situation would be an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
+Motivated by this example, we will impose the condition that the pressure difference across our computational domain remains fixed in time.
+As a consequence, we expect the flow rate, $\umax$, to increase over time as the bodies erode inside the cell and thus provide less resistance.
+
+We impose the fixed-pressure-drop condition by dynamically controlling the incoming flow rate, $\umax$.
+We first compute the Stokes flow with $\umax = 1$ prescribed and measure the corresponding pressure at an upstream ($x = -2$) and downstream ($x=2$) location.
 We define the vertically-averaged upstream and downstream pressures as
@@
 \end{align}
-The velocity and pressure fields depend linearly on $\eeta$ and so this rescaling maintains a {\em fixed} pressure difference between the upstream and downstream locations.
+The velocity and pressure fields depend linearly on $\eeta$ and so this rescaling maintains a {\em fixed} pressure difference across the subdomain $-2 \le x \le 2$.
 Since the Stokes equations are linear, the rescaled flow remains a solution to the PDE system (valid to the same numerical accuracy).
@@
 
-Briefly, to verity that the rescaling does not alter accuracy, we show in Table \ref{convtab} a convergence test for a 20-body simulation with the condition of fixed pressure drop imposed.
-The table confirms that the method retains second-order accuracy in time.
-In the last column, we show the computational times, indicating that the 20-body simulations require more runtime than the single-body case.
+Briefly, to validate the multi-body simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}.
+In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$.
+This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$.
+To assess error, we measure the aggregate $L_2$ difference in the shape of {\em all} of the bodies, comparing simulations of successive time-resolution.
+Note that this error metric is sensitive to numerical errors in any of the simulated bodies.
+The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure for imposing the fixed-pressure-drop conditions and confirming that multi-body interactions are handled correctly by the Stokes solver.
+The last column of the table shows the computational time of each simulation.
+The CPU time still scales linearly with temporal resolution and, naturally, the 20-body simulations require significantly more time than do the single-body simulations.
+
+Lastly, we want to briefly assess the number of GMRES iterations required by our simulations, since this is the most computationally expensive part.
+Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
+The iteration count, however, may depend on the number of bodies, as well as other factors such as the shapes of the bodies, their configuration, etc.
+To examine a few of these factors, we show in Table~\ref{itertab} the GMRES iterations required in several different simulations.
+First, the left
+
 Although the GMRES-iteration count is independent of the spatial resolution, $N_{\iin}$, it can depend on the number of bodies and/or their configuration.
@@
 and~\cite{qua-bir2015a}}
-
-%Briefly, to verify that these rescaled solutions achieve the same order of accuracy, we report a convergence test in Table \ref{convtab}. In
 

### 2018-03-31 docs/methods/erosion_methods.tex
NM

@@
 
-Lastly, we want to briefly assess the number of GMRES iterations required by our simulations, since this is the most computationally expensive part.
+Lastly, we want to briefly assess the number of GMRES iterations required by our simulations since this is the most  expensive part of the computation.
 Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
 The iteration count, however, may depend on the number of bodies, as well as other factors such as the shapes of the bodies, their configuration, etc.
-To examine a few of these factors, we show in Table~\ref{itertab} the GMRES iterations required in several different simulations.
-First, the left
-
-Although the GMRES-iteration count is independent of the spatial resolution, $N_{\iin}$, it can depend on the number of bodies and/or their configuration.
-To illustrate this point, we show in Table~\ref{itertab} the GMRES count for various cases ...
-\todo[inline]{preconditioning papers are~\cite{qua-cou-dar2018}
-and~\cite{qua-bir2015a}}
+To examine a few of these factors, we show in Table~\ref{itertab} the number of GMRES iterations required to reach a specified tolerance of 1E-8 in several different simulations.
+The left side of the table shows the results for a 10-body simulation, in which we vary the spatial resolution $N_{\iin}$.
+As seen in the table, the iteration count remains essentially fixed as the resolution increases.
+In the right side of the table, we show the results for simulations in which we vary the number of bodies and keep the spatial resolution fixed.
+The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
+The table shows that the GMRES count increases with the number of bodies at a rate that is close to linear.
+
+\todo[inline]{preconditioning papers are~\cite{qua-cou-dar2018} and~\cite{qua-bir2015a}}
 
@@
 \hline
-\hspace{0.5pc} Number of bodies
+\hspace{0.5pc} Resolution, $N_{\iin}$
 \hspace{0.5pc} & GMRES iterations 
-\hspace{0.5pc} & Resolution, $N_{\iin}$
+\hspace{0.5pc} &  Number of bodies
 \hspace{0.5pc} & GMRES iterations  \\
-\hspace{0.0pc} ($N_\iin = 128$ fixed) & 
-\hspace{0.5pc} &(10 bodies) & \\
+\hspace{0.0pc} (10 bodies) &
+\hspace{0.5pc} & ($N_\iin = 128$ fixed) & \\
 \hline
 %
-10	& 223	& 32	    	& 228	\\
-15	& 292	& 64    	& 226	\\
-20	& 363	& 128	& 223	\\
-30	& 496	& 256	& 223	\\
-40	& 676	& 512	& 223	\\
-50	& 991	& 1024	& 223	\\
+32	& 228	& 10 	& 223	\\
+64    	& 226	& 15 	& 292	\\
+128	& 223	& 20 	& 363	\\
+256	& 223	& 30 	& 496	\\
+512	& 223	& 40 	& 676	\\
+1024	& 223	& 50 	& 991	\\
 %

### 2018-03-31 docs/methods/erosion_methods.tex
worked on intro and bibliography

--- 2018-03-31 docs/methods/erosion_methods.tex
@@
 and all arclength derivatives are computed with Fourier differentiation.
-In addition to compute the shear stress, we also compute the vorticity
+In addition to computing the shear stress, we also compute the vorticity
 in the fluid bulk.  The vorticity is particularly insightful since it is
@@
 naturally leads to regions of high or infinite (i.e.~corners) curvature.
-These interface tracking issues are resolved by, first, introducing a
+The interface tracking issues are resolved by, first, introducing a
 tangential velocity field to maintain a grid that is equispaced in
-arclength, but that does not affect the dynamics, and, second, a tunable
-term that penalizes regions of high curvature.  Furthermore, the frame
-of reference is changed to \thL~variables so that the curvature term
+arclength, but does not affect the dynamics, and, second, a tunable term
+that penalizes regions of high curvature.  Furthermore, the frame of
+reference is changed to \thL~variables so that the curvature term
 appears as a diffusive term that can easily be handled in a numerically
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Related work} Simulating eroding bodies has been studied analytically, experimentally, and numerically.
+\paragraph{Related work} The effect of erosion on a geometry is quite
+rich.  For instance, it has been hypothesized and numerically observed
+that the erosion leads to a shear stress that is uniform on the body
+which results in a uniform erosion rate.  The shape that has a uniform
+shear stress is analyzed in three dimensions by Montenegro-Johnson and
+Lauga~\cite{mon-lau2015} which is an extension of the analysis done by
+Pironneau~\cite{pir1973} to find a Stokesian drag minimizing shape.  In
+this idealized case, analytical axisymmetric shapes that minimize the
+drag can be found.  However, the effect of erosion on a porous media is
+less understood.
+
+Simulating eroding bodies has been studied analytically, experimentally, and numerically.
 Many of these works are motivated by high Reynolds number geophysical applications, such as the work of the second author~\cite{moo-ris-chi-zha-she2013, ris-moo-chi-she-zha2012, moore2017riemann} and others~\cite{par-izu2000, lag2000, coh-dev-sey-yi-szy-rot2015, han1969, Rothman2012, hewett2017evolution, ristroph2018sculpting, lopez2018cfd, lachaussee2018competitive, cohen2016erosion}.
 The work most closely related to ours simulates erosion in a three-dimensional incompressible Stokesian fluid~\cite{mit-spa2016}, but they only consider single eroding body.
-
-The effect of erosion on a geometry is quite rich.  For instance, it has
-been hypothesized and numerically observed that the erosion leads to a
-shear stress that is uniform on the body which results in a uniform
-erosion rate.  The shape that has a uniform shear stress is analyzed in
-three dimensions by Montenegro-Johnson and Lauga~\cite{mon-lau2015}
-which is an extension of the analysis done by Pironneau~\cite{pir1973}
-to find a Stokesian drag minimizing shape.  In this idealized case,
-analytical axisymmetric shapes that minimize the drag can be found.
-However, the effect of erosion on a porous media is less understood.
 
@@
 be considered further in future work when there are many more grains
-that are also dynamic.  To address the nearly-singular integrands, we
-take advantage of the fact that the grains are eroding and not moving,
-so their separation increases with time.  Therefore, in this work, we
-apply an upsampling scheme, but in future work, we will require a
-near-singular integration scheme~\cite{qua-bir2014a,
+that are also being transported by the flow.  To address the
+nearly-singular integrands, we use the fact that the grains are eroding
+and not moving, so their separation increases with time.  Therefore, in
+this work, we apply an upsampling scheme, but in future work, we will
+require a near-singular integration scheme~\cite{qua-bir2014a,
 klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.
@@
 \paragraph{Outline of the paper} In Section~\ref{s:formulation}, we
-describe the governing equations for both the fluid and describe the
-erosion model using a \thL~framework.  In Section~\ref{s:method}, the
-numerical methods in both space and time are described and
-Section~\ref{s:qoi} describes how to compute the vorticity, pressure,
-and drag. Section~\ref{s:SingleResults} gives several numerical examples
-for a single body, and Section~\ref{s:MultiResults} presents numerical
+describe the governing equations for both the fluid and the erosion
+model in a \thL~framework.  In Section~\ref{s:method}, the numerical
+methods in both space and time are described and Section~\ref{s:qoi}
+describes how to compute the vorticity, pressure, and drag.
+Section~\ref{s:SingleResults} gives several numerical examples for a
+single body, and Section~\ref{s:MultiResults} presents numerical
 examples for multiply-connected domains.  Finally, concluding remarks
-are made in Section~\ref{s:conclusions}
+are made in Section~\ref{s:conclusions}.
 
@@
 	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three simulations.
-Since $N_\iin = 1024$ is fixed, the values $\eps = \sigma = $ 20/1024, 10/1024, and 5/1024 roughly correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
-The table shows that both the aspect ratio and opening angle converge with first-order as $\eps, \sigma \to 0$.
+Loosely speaking, since $N_\iin = 1024$ is fixed, the values $\eps = \sigma = $ 20/1024, 10/1024, and 5/1024 correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
+The table shows that both the aspect ratio and opening angle converge with roughly first-order as $\eps, \sigma \to 0$.
 In addition, we show an estimate of the uncertainty involved in our angle measurement, obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
@@
 Interestingly, 3D simulations of viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form \cite{mit-spa2016}.
-It was found that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
+It was shown that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
 Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ for self-similar reduction \cite{pir1973, mit-spa2016}.
-Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well.
-Therefore, the shape observed to develop in our simulations is approximately the form that minimizes drag subject to fixed area.
-How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, which can be seen in Fig.~\ref{shrink_intface}(b).
+Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well, and, therefore, the shape that develops in our simulations is approximately the form that minimizes drag subject to fixed area.
+How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{shrink_intface}(b).
 
@@
 We assess error by measuring the $L^2$-difference in the body shape obtained from simulations of successive resolution, with $\Delta t$ halved at each stage.
-In Table \ref{convtab}, we report these errors along with the order of accuracy, obtained by Richardson-extrapolation-type calculations.
+In Table \ref{convtab}, we report these errors along with the order of accuracy as obtained by Richardson-extrapolation-type calculations.
 The table confirms that our method converges with expected second-order accuracy.
@@
 With the numerical method validated, we are now ready to simulate the erosion of multiple bodies.
-First, though, we will make one important conceptual change to the model.
-For a realistic porous medium, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
-In groundwater flow, for example, it is more realistic to have an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
-In our simulations, we will therefore impose the condition that the pressure difference across the domain remains fixed.
-
-To impose the condition of a fixed pressure difference, we will dynamically control the incoming flow rate, $\umax$.
-To this end, we first compute the Stokes flow with $\umax = 1$ prescribed and measure the corresponding pressure at an upstream ($x = -2$) and downstream ($x=2$) location.
-We define the vertically-averaged upstream and downstream pressures as
+We make one important conceptual change to our model.
+For a realistic porous medium composed of many solid bodies, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
+A more realistic condition is that the pressure difference from one end to another is held fixed.
+For example, in groundwater flow, this condition would correspond to a recharge region of given hydraulic head connecting to a discharge region of another hydraulic head.
+
+We therefore impose the condition of a fixed pressure difference by dynamically controlling the incoming flow-rate, $\umax$.
+This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed and measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies.
+The vertically-averaged upstream and downstream pressures are given by
 \begin{align}
@@
 \end{align}
-The velocity and pressure fields depend linearly on $\eeta$ and so this rescaling maintains a {\em fixed} pressure difference between the upstream and downstream locations.
-Since the Stokes equations are linear, the rescaled flow remains a solution to the PDE system (valid to the same numerical accuracy).
-Furthermore, since the Stokes equations are time-independent, rescaling $U$ by a different value at each time step does not introduce any additional error.
+This rescaling maintains a {\em fixed} pressure difference between the upstream ($x=-2$) and downstream ($x=2$) positions.
+Because the Stokes equations are linear, such a rescaling is permissible and does not alter the accuracy of our method.
+Furthermore, {\em dynamic} rescaling is also permissible because the Stokes equations are memoryless (i.e.~there is no time derivative present in the PDEs).
 
@@
 
-\todo[inline]{Here in revising}
-
 \subsection{Multi-body erosion}

### 2018-04-02 docs/methods/erosion_methods.tex
removed a todo
NM

@@
 With the numerical method validated, we are now ready to simulate the erosion of multiple bodies.
-We will first make one conceptual change to the model though.
+We will first make one conceptual change to the model.
 For a realistic porous medium, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
-In groundwater flow, for example, the more common situation would be an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
-Motivated by this example, we will impose the condition that the pressure difference across our computational domain remains fixed in time.
-As a consequence, we expect the flow rate, $\umax$, to increase over time as the bodies erode inside the cell and thus provide less resistance.
+In groundwater flow, for example, the more common situation is an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
+Motivated by this example, we will impose the condition that the pressure difference across the computational domain remains fixed in time.
+As a consequence, the flow rate, $\umax$, will increase over time as the bodies erode inside the cell and thus provide less resistance.
 
@@
 The velocity and pressure fields depend linearly on $\eeta$ and so this rescaling maintains a {\em fixed} pressure difference across the subdomain $-2 \le x \le 2$.
-Since the Stokes equations are linear, the rescaled flow remains a solution to the PDE system (valid to the same numerical accuracy).
+Since the Stokes equations are linear, the rescaled flow remains a solution to the PDE system (valid to the same order of accuracy).
 Furthermore, since the Stokes equations are time-independent, rescaling $U$ by a different value at each time step does not introduce any additional error.
@@
 This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$.
-To assess error, we measure the aggregate $L_2$ difference in the shape of {\em all} of the bodies, comparing simulations of successive time-resolution.
-Note that this error metric is sensitive to numerical errors in any of the simulated bodies.
-The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure for imposing the fixed-pressure-drop conditions and confirming that multi-body interactions are handled correctly by the Stokes solver.
-The last column of the table shows the computational time of each simulation.
-The CPU time still scales linearly with temporal resolution and, naturally, the 20-body simulations require significantly more time than do the single-body simulations.
-
-Lastly, we want to briefly assess the number of GMRES iterations required by our simulations since this is the most  expensive part of the computation.
+To assess error, we measure the aggregate $L_2$ difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution.
+Note that this metric is sensitive to numerical errors in any of the simulated bodies.
+The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multi-body interactions are handled correctly by the Stokes solver.
+The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution.
+Naturally, these 20-body simulations require significantly more time than do the single-body simulations.
+
+Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since it is the most  expensive part of the computation.
 Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
@@
 To examine a few of these factors, we show in Table~\ref{itertab} the number of GMRES iterations required to reach a specified tolerance of 1E-8 in several different simulations.
-The left side of the table shows the results for a 10-body simulation, in which we vary the spatial resolution $N_{\iin}$.
+The left side of the table shows the results for a 10-body simulation, in which we keep the geometry fixed and vary the spatial resolution $N_{\iin}$.
 As seen in the table, the iteration count remains essentially fixed as the resolution increases.
-In the right side of the table, we show the results for simulations in which we vary the number of bodies and keep the spatial resolution fixed.
-The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
-The table shows that the GMRES count increases with the number of bodies at a rate that is close to linear.
-
-\todo[inline]{preconditioning papers are~\cite{qua-cou-dar2018} and~\cite{qua-bir2015a}}
+In the right side of the table, we keep the spatial resolution fixed and vary the number of simulated bodies from 10 to 50.
+These bodies are all circular with randomly assigned positions and radii (with overlap avoided).
+The table shows that the GMRES count is indeed sensitive to the number of bodies, increasing at a rate close to linear.
 
@@
 \begin{center}
-\caption{GMRES Iterations: the tolerance is 1E-8.
+\caption{The number of GMRES iterations required to reach a fixed tolerance of 1E-8 in our simulations.
+The left side shows a case of fixed geometry, 10 circular bodies, with increasing spatial resolution, $N_\iin$, demonstrating that the iteration count is independent of resolution.
+In the right side, we fix the resolution and sequentially increase the number of bodies (all circular) from 10 to 50.
+The iteration count increases with the number of bodies.
 }
@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% In these tests I always use 128 points per body.
-
-\todo[inline]{Here in revising}
 
@@
 %which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
+
+\todo[inline]{Here in revising}
 

### 2018-04-03 docs/methods/erosion_methods.tex
NM

@@
 \includegraphics[width = 0.4 \textwidth]{./figs/corner.pdf}
-\caption{Schematic of 2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function in polar coordinates $\psi(r,\theta)$, for $\theta \in [-\theta_0, \theta_0]$}.
+\caption{Schematic of 2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function in polar coordinates $\psi(r,\theta)$, for $\theta \in [-\theta_0, \theta_0]$.}
 \label{corner}
@@
 \label{fODE}
-f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0.
+f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0 \, .
 \end{align}
@@
 
-\subsection{Fixed pressure drop condition and validation}
+\subsection{Fixed pressure-drop condition and validation}
 

### 2018-04-03 docs/methods/erosion_methods.tex
NM

@@
 Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well.
-Therefore, the shape observed to develop in our simulations is approximately the form that minimizes drag subject to fixed area.
-How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, which can be seen in Fig.~\ref{shrink_intface}(b).
+Therefore, the shape observed to develop in our simulations is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape.
+How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{shrink_intface}(b).
 
@@
 As a final validation, we now verify that our method converges with the expected second-order accuracy in time.
-For this, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
+For this, we run the same single-body simulation shown in Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
 This stopping time is 56\% of the vanishing time, and was selected so that the body will have eroded substantially but is not small enough to compromise accuracy (due to the stress diverging).

### 2018-04-03 docs/methods/erosion_methods.tex
NM

@@
 While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
+We defer a study of these complex effects for future work.
 
@@
 
-To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in numerically stabilizing moving-interface problems \cite{hou-low-she1994}.
+To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in the ability to numerically stabilize moving-interface problems \cite{hou-low-she1994}.
 Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary.
@@
 
-\subsection{Fixed pressure-drop condition and validation}
+\subsection{Fixed pressure-drop condition}
 
@@
 For a realistic porous medium, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
-In groundwater flow, for example, the more common situation is an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
-Motivated by this example, we will impose the condition that the pressure difference across the computational domain remains fixed in time.
-As a consequence, the flow rate, $\umax$, will increase over time as the bodies erode inside the cell and thus provide less resistance.
-
-We impose the fixed-pressure-drop condition by dynamically controlling the incoming flow rate, $\umax$.
+In groundwater flow, for example, it is more common to encounter an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
+Motivated by this example, we will impose the condition that the pressure drop across the computational domain remains fixed in time.
+Consequently, we would expect the flow rate, $\umax$, to increase over time as the bodies erode inside the cell and thus provide less resistance.
+
+We will impose the fixed-pressure-drop condition by dynamically controlling the incoming flow rate, $\umax$.
 We first compute the Stokes flow with $\umax = 1$ prescribed and measure the corresponding pressure at an upstream ($x = -2$) and downstream ($x=2$) location.
-We define the vertically-averaged upstream and downstream pressures as
+We next calculate the vertically-averaged upstream and downstream pressures, defined as
 \begin{align}
@@
 \end{align}
-Next, we rescale the computed density function by the pressure difference
+We then rescale the computed density function by the pressure difference
 \begin{align}
@@
 Furthermore, since the Stokes equations are time-independent, rescaling $U$ by a different value at each time step does not introduce any additional error.
+
+\subsection{Validation}
+
+Briefly, to validate the multi-body simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}.
+In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$.
+This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$.
+To assess error, we measure the aggregate $L_2$ difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution.
+Note that this metric is sensitive to numerical errors in any of the simulated bodies.
+The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multi-body interactions are handled correctly by the Stokes solver.
+The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution.
+Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.
 
@@
 
-Briefly, to validate the multi-body simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}.
-In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$.
-This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$.
-To assess error, we measure the aggregate $L_2$ difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution.
-Note that this metric is sensitive to numerical errors in any of the simulated bodies.
-The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multi-body interactions are handled correctly by the Stokes solver.
-The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution.
-Naturally, these 20-body simulations require significantly more time than do the single-body simulations.
-
-Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since it is the most  expensive part of the computation.
+Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since this is typically the most expensive step of the computation.
 Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
@@
 In the right side of the table, we keep the spatial resolution fixed and vary the number of simulated bodies from 10 to 50.
-These bodies are all circular with randomly assigned positions and radii (with overlap avoided).
-The table shows that the GMRES count is indeed sensitive to the number of bodies, increasing at a rate close to linear.
+The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
+The table shows that the GMRES count, and therefore the computational time, increases roughly linearly with the number of bodies.
+Thus, with everything else equal, the 50-body simulation from Fig.~\ref{fig:50bodies} is about 50 times more expensive than the single-body simulations.
 
@@
 In the right side, we fix the resolution and sequentially increase the number of bodies (all circular) from 10 to 50.
-The iteration count increases with the number of bodies.
+The iteration count increases roughly linearly with the number of bodies.
 }
@@
 
-\subsection{Multi-body erosion}
+\subsection{Multi-body results}
 

### 2018-04-03 docs/methods/erosion_methods.tex
NM

@@
 unchecked, could lead to severe tangling and numerical instability. We
-therefore introduce an artificial tangential velocity $\Vs$ that always
-keeps the grid points equally spaced in arclength \cite{hou-low-she1994}. The appropriate tangential velocity satisfies 
+therefore introduce an artificial tangential velocity $\Vs$ to keep the grid points equally spaced in arclength \cite{hou-low-she1994}. The appropriate tangential velocity satisfies 
 \begin{align}
@@
 value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$
-changes sign (i.e.~at a stagnation point). The corner in $\atau$
+changes sign, i.e.~at a stagnation point. The corner in $\atau$
 introduces high frequencies into~\eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
@@
 At early times (yellow curves), the stress varies significantly, with more stress concentrated at the top and bottom of the body.
-However, as erosion alters the body's shape, the stress becomes more uniformly distributed over the entire surface (red curves).
+However, as erosion reshapes the body, the stress becomes more uniformly distributed over the entire surface (red curves).
 The absolute stress $\atau$ shows slight peaks near the stagnation points as the bodies nears the final stages of erosion (dark red).
@@
 The drag is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, this should be interpreted as the drag-per-unit-span.
-As seen in the figure, $F_D$ decreases gradually at first, then abruptly drops to zero in the final moments as the body vanishes.
+As seen in the figure, $F_D$ decreases gradually at first, then abruptly drops to zero in the final moments of the body's existence.
 Though it may seem peculiar, the sudden drop is consistent with the 2D Stokes law in which drag vanishes {\em logarithmically} with body size.
@@
 As the body erodes and assumes a more slender form, though, the pressure drag decreases more rapidly, leaving viscous drag to dominate.
-This behavior is associated with convergence to a drag-minimizing profile, which will be discussed in Section \ref{LimitingShape}.
+This behavior is associated with convergence to a drag-minimizing profile, which is discussed in Section \ref{LimitingShape}.
 
@@
 In this figure, time is normalized by the vanishing time $t_f = 1.79 \times 10^{-2}$ from the shrinking simulations (i.e.~Fig.~\ref{shrink_intface}).
-Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerges before the body vanishes \cite{moo-ris-chi-zha-she2013}.
+Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerged before the body disappeared \cite{moo-ris-chi-zha-she2013}.
 
@@
 In the three cases, we keep $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and 5/1024 respectively.
+Loosely, these values correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
 Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
@@
 	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three simulations.
-Since $N_\iin = 1024$ is fixed, the values $\eps = \sigma = $ 20/1024, 10/1024, and 5/1024 roughly correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
 The table shows that both the aspect ratio and opening angle converge with first-order as $\eps, \sigma \to 0$.

### 2018-04-03 docs/methods/erosion_methods.tex
NM

@@
 As time proceeds, erosion carves a sharper corner and $\beta$ decreases monotonically.
-Here, the three simulation curves are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing than is the aspect ratio.
+Here, the three cases of smoothing parameters are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing than is the aspect ratio.
 The curves nevertheless show convergence as $\eps, \sigma \to 0$.
@@
 
-	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three simulations.
-The table shows that both the aspect ratio and opening angle converge with first-order as $\eps, \sigma \to 0$.
+	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three cases.
+The table shows that both the aspect ratio and opening angle converge with roughly first-order as $\eps, \sigma \to 0$.
 In addition, we show an estimate of the uncertainty involved in our angle measurement, obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
@@
 Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well.
-Therefore, the shape observed to develop in our simulations is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape.
+Therefore, the shape observed in our simulation is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape.
 How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{shrink_intface}(b).
@@
 
-We now discuss some physical aspects of multi-body erosion revealed by our simulations.
-Figure~\ref{fig:06bodies} shows a simulation of 6 eroding bodies, each initially circles of various sizes and positions.
+With the validation complete, we now discuss some of the emergent physics of multi-body erosion revealed by our simulations.
+We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}).
+Figure~\ref{fig:06bodies} shows the simulated erosion of 6 bodies, each initial circles of various sizes and positions.
 Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerable.
 As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable.
-Rather, when and where these sharp features develop depends on inter-body feedback as mediated by the Stokes flow.
+Rather, when and where these corners form depends on how neighboring bodies interact as mediated by the Stokes flow.
 
@@
 \includegraphics[width = 0.9 \textwidth]{./figs/06bod.pdf}
-\caption{\label{fig:06bodies} 6 bodies.
+\caption{\label{fig:06bodies} The simulated erosion of 6 bodies with the fixed-pressure drop condition.
+Erosion causes flat faces to develop wherever bodies were initially very close to one another.
+This effect leads to the appearance of straight channels between bodies, and causes the bodies themselves to appear distinctly polygonal.
+The vorticity field (color-bar at right) shows that the flow is concentrated primarily in a single channel that runs horizontally across the domain.
 }
-%A time lapse of 50 bodies eroding in a viscous flow.
-The boundary conditions are a constant pressure drop that creates a flow from the left to right.
-The rate of erosion is proportional to the shear stress which is equivalent to the vorticity evaluated on the bodies.
-The colors represent the vorticity, so regions with large vorticity (in magnitude) are regions where the flow will erode the fastest.
 \end{center}
@@
 
-\todo[inline]{Here in revising}
-
-The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several near contacts between bodies, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
-Our method handles these near contacts without difficulty.
-Interestingly, erosion appears to preferentially remove material from these regions of near contact, as the narrow spacing between bodies expands rather rapidly.
+The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several points at which the bodies nearly contact one another, for example bodies 1 \& 2, 3 \& 5, and 5 ur \& 6.
+Intriguingly, erosion appears to remove material preferentially from these near-contact regions, as the narrow spacing between neighboring bodies expands rather rapidly.
 For example, the spacing between bodies 1 \& 2 is initially very small, but by the second frame, is comparable to the spacing between bodies 3 \& 4.
-Even more interesting, the bodies tend to develop flat faces where there are near contacts.
-This effect leads to the appearance of straight channels in between bodies, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
-Once formed, these straight channels persist until the bodies have nearly vanished.
-
-The vorticity field not only allows us to visualize regions of high shear, but also allows us to identify preferred channels with most intense flow.
-Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
-This main channel widens the fastest, and secondary channels follow (e.g.~between bodies 1 \& 2 or 3 \& 5 or 5 \& 6).
-Since the pressure drop across the cell is fixed, the overall flow rate increases as the bodies erode.
-This can be seen by the overall vorticity magnitude growing in time.
-By the final frame shown, body 4 has vanished completely and our method handles this event seamlessly.
+Furthermore, the bodies tend to develop flat faces at the locations of near contact, leading to the appearance of straight channels between bodies.
+Straight channels can be seen, for example, between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
+Once formed, these channels persist until the bodies have nearly vanished.
+Notice that by the final frame, body 4 has vanished completely, and the simulation handles this event without difficulty.
+
+The vorticity field helps not only to visualize regions of high shear, but also to identify the certain preferred channels in which the flow is most intense.
+As seen in Fig.~\ref{fig:06bodies}, the flow is concentrated primarily in a single channel running horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
+This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \& 2 or 3 \& 5 or 5 \& 6) follow.
+Notice that, in these simulations, the overall vorticity magnitude increases in time as a result of fixing the pressure-drop across the cell.
 

### 2018-04-03 docs/methods/erosion_methods.tex
NM

@@
 This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$.
-To assess error, we measure the aggregate $L_2$ difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution.
+To assess error, we measure the aggregate $L^2$-difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution.
 Note that this metric is sensitive to numerical errors in any of the simulated bodies.

### 2018-04-03 docs/methods/erosion_methods.tex
NM

@@
 
-Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since this is typically the most expensive step of the computation.
+Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since this is typically the most expensive step.
 Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
@@
 The table shows that the GMRES count, and therefore the computational time, increases roughly linearly with the number of bodies.
-Thus, with everything else equal, the 50-body simulation from Fig.~\ref{fig:50bodies} is about 50 times more expensive than the single-body simulations.
+Thus, with everything else equal, the 50-body simulation from Fig.~\ref{fig:50bodies} is about 50 times more expensive than a single-body simulation.
 
@@
 
-With the validation complete, we now discuss some of the emergent physics of multi-body erosion revealed by our simulations.
+With the validation complete, we now discuss the emergent physics of multi-body erosion revealed by our simulations.
 We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}).
@@
 As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable.
-Rather, when and where these corners form depends on how neighboring bodies interact as mediated by the Stokes flow.
+Rather, when and where these corners form depends on how neighboring bodies interact with one another as mediated by the Stokes flow.
 
@@
 \begin{center}
-\includegraphics[width = 0.9 \textwidth]{./figs/06bod.pdf}
+\includegraphics[width = 0.85 \textwidth]{./figs/06bod.pdf}
 \caption{\label{fig:06bodies} The simulated erosion of 6 bodies with the fixed-pressure drop condition.
@@
 
-The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several points at which the bodies nearly contact one another, for example bodies 1 \& 2, 3 \& 5, and 5 ur \& 6.
-Intriguingly, erosion appears to remove material preferentially from these near-contact regions, as the narrow spacing between neighboring bodies expands rather rapidly.
-For example, the spacing between bodies 1 \& 2 is initially very small, but by the second frame, is comparable to the spacing between bodies 3 \& 4.
-Furthermore, the bodies tend to develop flat faces at the locations of near contact, leading to the appearance of straight channels between bodies.
+The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several points at which the bodies nearly contact one another, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
+Intriguingly, erosion appears to remove material preferentially from these near-contact regions, as the narrow spacing between neighboring bodies expands rather quickly.
+For example, the spacing between bodies 1 \& 2 is initially quite small, but by the second frame, is comparable to the spacing between bodies 3 \& 4.
+Moreover, the bodies tend to develop flat faces at the locations of near contact, leading to the appearance of straight channels between bodies.
 Straight channels can be seen, for example, between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
@@
 
-The vorticity field helps not only to visualize regions of high shear, but also to identify the certain preferred channels in which the flow is most intense.
-As seen in Fig.~\ref{fig:06bodies}, the flow is concentrated primarily in a single channel running horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
+The vorticity field helps not only in visualizing regions of high shear, but also in identifying certain preferred channels in which the flow is most intense.
+Figure~\ref{fig:06bodies} shows the flow to be concentrated primarily within a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
 This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \& 2 or 3 \& 5 or 5 \& 6) follow.
@@
 \begin{center}
-\includegraphics[width = 0.95 \textwidth]{./figs/mbodyplots.pdf}
-\caption{\label{fig:mbodyplots} plots to go with 6 body simulation.
+\includegraphics[width = 0.90 \textwidth]{./figs/mbodyplots.pdf}
+\caption{\label{fig:mbodyplots} 
+Multi-body simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation.
+(a) The area fraction of the eroding bodies as it changes in time.
+(b) The incoming flow rate $\umax$ versus time.
+The fixed-pressure-drop condition causes $\umax$ to increase as the bodies erode.
+(c) The total drag exerted by all bodies.
+Due to the fact that $\umax$ increases as the bodies erode, the total drag remains nearly constant and then drops suddenly as the bodies vanish.
+(d) Normalizing the total drag by the flow rate provides a measurement of the resistance provided by the porous matrix.
+The resistance decreases rapidly as the bodies erode.
 }
@@
 %which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
-
-\todo[inline]{Here in revising}
 
@@
 
+\todo[inline]{Here in revising}
+
 In Fig.~\ref{fig:mbodyplots} we also plot the same quantities for the 50-body simulation that was shown in Fig.~\ref{fig:50bodies} of the introduction.

### 2018-04-03 docs/methods/erosion_methods.tex
NM

@@
 We benchmark single-body results against analytical predictions.
-In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact.
+In our multibody simulations, we find that erosion leads to spontaneous channelization between bodies in near contact.
 The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
@@
 \begin{center}
-\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
+\includegraphics[width = 0.80 \textwidth]{./figs/50bod.pdf}
 \caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
@@
 
-\section{Results: Multi-body erosion}
+\section{Results: Multibody erosion}
 \label{s:MultiResults}
@@
 
-Briefly, to validate the multi-body simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}.
+Briefly, to validate the multibody simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}.
 In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$.
@@
 Note that this metric is sensitive to numerical errors in any of the simulated bodies.
-The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multi-body interactions are handled correctly by the Stokes solver.
+The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multibody interactions are handled correctly by the Stokes solver.
 The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution.
@@
 
-\subsection{Multi-body results}
-
-With the validation complete, we now discuss the emergent physics of multi-body erosion revealed by our simulations.
+\subsection{Multibody results}
+
+With the validation complete, we now discuss the emergent physics of multibody erosion revealed by our simulations.
 We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}).
@@
 \begin{center}
-\includegraphics[width = 0.85 \textwidth]{./figs/06bod.pdf}
+\includegraphics[width = 0.80 \textwidth]{./figs/06bod.pdf}
 \caption{\label{fig:06bodies} The simulated erosion of 6 bodies with the fixed-pressure drop condition.
@@
 The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several points at which the bodies nearly contact one another, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
-Intriguingly, erosion appears to remove material preferentially from these near-contact regions, as the narrow spacing between neighboring bodies expands rather quickly.
+Intriguingly, erosion appears to remove material preferentially from these sights, as the narrow spacing between neighboring bodies expands rather quickly.
 For example, the spacing between bodies 1 \& 2 is initially quite small, but by the second frame, is comparable to the spacing between bodies 3 \& 4.
-Moreover, the bodies tend to develop flat faces at the locations of near contact, leading to the appearance of straight channels between bodies.
+Moreover, the bodies tend to develop flat faces at the points of near contact, leading to the appearance of straight channels between bodies.
 Straight channels can be seen, for example, between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
@@
 
-The vorticity field helps not only in visualizing regions of high shear, but also in identifying certain preferred channels in which the flow is most intense.
-Figure~\ref{fig:06bodies} shows the flow to be concentrated primarily within a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
+In Fig.~\ref{fig:06bodies}, we also show the vorticity field of the surrounding flow.
+Not only does this field help visualize regions of high shear, but it also allows us to identify certain preferred channels in which the flow is most intense.
+As seen in the figure, the flow appears to be concentrated primarily within a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
 This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \& 2 or 3 \& 5 or 5 \& 6) follow.
-Notice that, in these simulations, the overall vorticity magnitude increases in time as a result of fixing the pressure-drop across the cell.
+Notice that, in these simulations, the overall vorticity magnitude increases in time due to $\umax$ increasing from keeping the pressure drop fixed.
 
@@
 \caption{\label{fig:mbodyplots} 
-Multi-body simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation.
-(a) The area fraction of the eroding bodies as it changes in time.
+Multibody simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation.
+(a) The area fraction of the eroding bodies versus time.
 (b) The incoming flow rate $\umax$ versus time.
-The fixed-pressure-drop condition causes $\umax$ to increase as the bodies erode.
+The fixed-pressure-drop condition causes $\umax$ to increase as bodies erode.
 (c) The total drag exerted by all bodies.
-Due to the fact that $\umax$ increases as the bodies erode, the total drag remains nearly constant and then drops suddenly as the bodies vanish.
-(d) Normalizing the total drag by the flow rate provides a measurement of the resistance provided by the porous matrix.
+Because $\umax$ increases as the bodies erode, the drag remains nearly constant throughout much of the simulation.
+In the very last moments, the drag drops suddenly to zero.
+(d) Normalizing the drag by $\umax$ provides gives an estimate of how much resistance the porous matrix provides.
 The resistance decreases rapidly as the bodies erode.
@@
 %which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
+
+To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
+In all cases, the black curves correspond to the 6-body simulation and gray curves correspond to the 50-body simulation that was shown in Fig.~\ref{fig:50bodies}.
+First, Fig.~\ref{fig:mbodyplots}(a) shows the area fraction of the solid bodies versus time (i.e.~the 2D counterpart of the volume fraction).
+
+\todo[inline]{Here in revising}
 
@@
 
-\todo[inline]{Here in revising}
-
 In Fig.~\ref{fig:mbodyplots} we also plot the same quantities for the 50-body simulation that was shown in Fig.~\ref{fig:50bodies} of the introduction.

### 2018-04-04 docs/methods/erosion_methods.tex
NM

@@
 In Fig.~\ref{fig:06bodies}, we also show the vorticity field of the surrounding flow.
-Not only does this field help visualize regions of high shear, but it also allows us to identify certain preferred channels in which the flow is most intense.
+This field helps not only to visualize regions of high shear, but also to identify certain preferred channels in which the flow is most intense.
 As seen in the figure, the flow appears to be concentrated primarily within a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
 This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \& 2 or 3 \& 5 or 5 \& 6) follow.
-Notice that, in these simulations, the overall vorticity magnitude increases in time due to $\umax$ increasing from keeping the pressure drop fixed.
+Notice that the overall vorticity magnitude increases in time as the flow rate $\umax$ increases due to keeping the pressure drop fixed.
 
@@
 
-To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
-In all cases, the black curves correspond to the 6-body simulation and gray curves correspond to the 50-body simulation that was shown in Fig.~\ref{fig:50bodies}.
-First, Fig.~\ref{fig:mbodyplots}(a) shows the area fraction of the solid bodies versus time (i.e.~the 2D counterpart of the volume fraction).
+To further quantify our observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
+In all cases, the black curves correspond to the 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}.
+First, Fig.~\ref{fig:mbodyplots}(a) shows the fraction of area occupied by the solid bodies as it varies in time.
+In the 6-body simulation, the initial configuration comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode.
+The 50-body simulation shows a similar trend.
+Figure \ref{fig:mbodyplots}(b) shows how the flow rate, $\umax$, changes in time as a result of fixing the pressure drop across the cell.
+Notice that, in this figure, the vertical axis is logarithmic.
+Both simulations show the flow rate to increase rapidly, even during the early stages of erosion when the area fraction has not changed that significantly.
+In fact, due to the logarithmic axis, the nearly linear trend seen in the figures corresponds to exponential growth of $\umax$.
+The change in area-fraction alone is not enough to account for this rapid growth, implying that it is the way in which erosion reshapes the bodies that allows for high flow rates.
 
@@
 
-We further quantify many of these observations in Fig.~\ref{fig:mbodyplots}.
-First, Fig.~\ref{fig:mbodyplots}(a) shows area fraction versus time.
-The area fraction is the total area of all bodies as compared to the domain area, i.e.~the 2D counterpart of volume fraction.
-The initial configuration of 6 circles comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode.
 Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time.

### 2018-04-04 docs/methods/erosion_methods.tex
NM

@@
 
-Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since this is typically the most expensive step.
-Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
-The iteration count, however, may depend on the number of bodies, as well as other factors such as the shapes of the bodies, their configuration, etc.
-To examine a few of these factors, we show in Table~\ref{itertab} the number of GMRES iterations required to reach a specified tolerance of 1E-8 in several different simulations.
-The left side of the table shows the results for a 10-body simulation, in which we keep the geometry fixed and vary the spatial resolution $N_{\iin}$.
-As seen in the table, the iteration count remains essentially fixed as the resolution increases.
-In the right side of the table, we keep the spatial resolution fixed and vary the number of simulated bodies from 10 to 50.
-The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
-The table shows that the GMRES count, and therefore the computational time, increases roughly linearly with the number of bodies.
-Thus, with everything else equal, the 50-body simulation from Fig.~\ref{fig:50bodies} is about 50 times more expensive than a single-body simulation.
-
 % Table: GMRES iterations
@@
 
+Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since this is typically the most expensive step.
+Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
+The iteration count, however, may depend on the number of bodies, as well as other factors such as the shapes of the bodies, their configuration, etc.
+To examine a few of these factors, we show in Table~\ref{itertab} the number of GMRES iterations required to reach a specified tolerance of 1E-8 in several different simulations.
+The left side of the table shows the results for a 10-body simulation, in which we keep the geometry fixed and vary the spatial resolution $N_{\iin}$.
+As seen in the table, the iteration count remains essentially fixed as the resolution increases.
+In the right side of the table, we keep the spatial resolution fixed and vary the number of simulated bodies from 10 to 50.
+The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
+The table shows that the GMRES count, and therefore the computational time, increases roughly linearly with the number of bodies.
+Thus, with everything else equal, the 50-body simulation from Fig.~\ref{fig:50bodies} is about 50 times more expensive than a single-body simulation.
+
 \subsection{Multibody results}
@@
 
-To further quantify our observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
-In all cases, the black curves correspond to the 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}.
+To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
+In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}.
 First, Fig.~\ref{fig:mbodyplots}(a) shows the fraction of area occupied by the solid bodies as it varies in time.
@@
 The 50-body simulation shows a similar trend.
-Figure \ref{fig:mbodyplots}(b) shows how the flow rate, $\umax$, changes in time as a result of fixing the pressure drop across the cell.
+
+Next, Figure \ref{fig:mbodyplots}(b) shows how the flow rate, $\umax$, changes in time as a result of fixing the pressure drop across the cell.
 Notice that, in this figure, the vertical axis is logarithmic.
@@
 In fact, due to the logarithmic axis, the nearly linear trend seen in the figures corresponds to exponential growth of $\umax$.
-The change in area-fraction alone is not enough to account for this rapid growth, implying that it is the way in which erosion reshapes the bodies that allows for high flow rates.
+The change in area-fraction alone cannot account for this rapid growth, suggesting the reshaping process to be vital.
+In particular, the formations of channels observed in Fig.~\ref{fig:06bodies} is most likely the key feature that enables the higher flow rates.
+
+Naturally, the flow rate allowed by the bodies is connected to the amount of drag that they exert.
+We therefore show in Fig.~\ref{fig:mbodyplots}(c) the total drag exerted by all bodies as it varies in time.
+In both cases, the drag remains nearly constant throughout much of the simulation and then drops to zero in the final moments.
+Here, the rapid increase of $\umax$ offsets the reduction in body size to create the nearly constant drag.
+
+To remove this effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag by $\umax$.
+Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies.
+In this way, we can interpret $F_D / (4 \pi \umax)$ as the {\em resistance} associated with the porous network.
+%
+The figure shows the resistance to decrease rapidly as the bodies erode.
+Once again the vertical axis is logarithmic, and so the linear trend corresponds to exponential decay of $F_D / (4 \pi \umax)$.
+We propose that the channelization is responsible for creating such a rapid decline in the network resistance.
 
@@
 
-Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time.
-Since we have fixed the pressure drop across the cell in these simulations, $\umax$ steadily increases as the bodies diminish and provide less resistance.
-Here, the vertical axis is logarithmic, and so the plot suggests exponential increase of $\umax$ at early times.
-This rapid increase in flow is likely due to the erosion-induced channelization observed above.
-In Fig.~\ref{fig:mbodyplots}(c) we show the total drag, summed over all bodies, versus time.
-Though the bodies diminish due to erosion, the steady increase of $\umax$ causes the total drag to remain relatively constant.
-Only near the end of the simulation does the drag decrease rapidly to zero.
-To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the total drag scaled on $\umax$.
-This value is a measure for the aggregate {\em resistance} of all bodies.
-Due to linearity of the Stokes equations, this measure does not depend on the flow-rate $\umax$, only on the bodies and their configuration.
-As seen here, the resistance decreases rapidly as the bodies erode.
-Since the vertical axis is logarithmic, the plot suggests an exponential decrease in resistance at early times, which is likely connected to the channelization process.
-
-In Fig.~\ref{fig:mbodyplots} we also plot the same quantities for the 50-body simulation that was shown in Fig.~\ref{fig:50bodies} of the introduction.
-Overall, these plots support the same trends seen in the 6-body simulation.
-The initial area-fraction of the 50-body simulation is only slightly higher, about 45\%, and this fraction decreases steadily as bodies erode.
-The flow rate $\umax$ again increases very rapidly with time, though with a significantly smaller initial value due to the higher resistance provided by 50 bodies.
-As before, the total drag remains relatively constant throughout most of the simulation and then abruptly decreases to zero in the final moments.
-Our measure of resistance, $F_D/(4 \pi \umax)$, again decreases very rapidly in the early moments when channels are initially formed.
+% corresponds, pertains, is connected to, involves, is related to, concerns
+
+Comparing the 50 and 6-body simualtions...
 Though the area fractions of the two simulations are nearly the same, the 50-body configuration provides about 5 times more resistance.

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 \section{Introduction\label{s:intro}}
+
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to smaller-scale structures and patterns \cite{}.
+Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay), along with small-scale biological structures such as biofilms.
+Motivated by these small-scale applications, this work focuses on developing numerical methods to simulate the erosion of solid material in Stokes flow.
+
+Recent work on high-Reynolds number erosion has recognized the importance of shape-flow feedback
+
+%% ORIGINAL %%%
 
@@
 \begin{center}
-\caption{Final aspect ratio and opening angle
+\caption{The long-time aspect ratio and opening-angle measurements for three...
 } 
@@
 For example, the spacing between bodies 1 \& 2 is initially quite small, but by the second frame, is comparable to the spacing between bodies 3 \& 4.
-Moreover, the bodies tend to develop flat faces at the points of near contact, leading to the appearance of straight channels between bodies.
+Moreover, the bodies tend to develop flat faces at these points of near contact, leading to the appearance of straight channels between bodies.
 Straight channels can be seen, for example, between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
@@
 
+Look back at Fig. 1 and notice similar features: channelization, sort-of polygonal bodies, etc.
+
 {\bf Good word: Spontaneous channelization}

### 2018-04-05 docs/methods/erosion_methods.tex
NM

--- 2018-04-04 docs/methods/erosion_methods.tex
@@
 
-Erosion is a fluid-mechanical process responsible for a variety
-of phenomena in geophysical and other settings.  For example,
-wind erosion causes sand dunes to be  longer on the windward
-side~\cite{han1969}, while stream-bed erosion is responsible for branching structures
-of rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  Erosion is
-also important in biophysical applications---plaque erosion in arteries
-is key to understanding heart disease~\cite{sha2002,
-gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can
-be explained by erosion~\cite{pic-van-hei2000}. 
+Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to human-scale structures and patterns \cite{}.
+Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay), as well as biological structures like plaque and biofilms.
+Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most appropriate regime for groundwater flow and the aforementioned biological examples.
+
+Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{}, as well as related processes such as dissolution \cite{} and melting \cite{}.
+In such cases, the flow alters the shape of the structure, which in turn modifies the surrounding flow, and so on --- a reciprocal process that can be summarized as `sculpting with flow'~\cite{ristroph2018sculpting}.
+The example of an eroding porous medium presents new challenges and opportunities in that multiply connected domains must be considered.
+Furthermore, the long-range effects of Stokes flow facilitates even stronger coupling between bodies.
+
+The example of an eroding porous medium presents new and interesting opportunities in a few ways.
+First of all, the medium is composed of many bodies and so multiply-connected domains most be considered.
+These bodies can interact via the surrounding flow.
+In particular, Stokes flow enables long-range interactions, which strongly couples the shape evolution of difference bodies.
+
+%% ORIGINAL %%%
+\vsp{5}
+%sand dunes to be  longer on the windward side~\cite{han1969}, 
+%stream-bed erosion is responsible for branching structures of rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  
+%Erosion is also important in biophysical applications---plaque erosion in arteries is key to understanding heart disease~\cite{sha2002, gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can be explained by erosion~\cite{pic-van-hei2000}.
+
 Recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}.
+
 All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow'~\cite{ristroph2018sculpting}.
@@
 Another application, which motivates the current work, is erosion caused by groundwater flow.
-Here, a slow moving fluid erodes channels in the ground, and this
-affects the fluid transport.  To better understand
-the effect of erosion on groundwater flow, multiply-connected domains
-must be considered.  Here we simulate two-dimensional erosion, in
-multiply-connected domain such as the porous geometry of many
-groundwater flows (Fig.~\ref{fig:50bodies}).
+Here, a slow moving fluid erodes channels in the ground, and this affects the fluid transport.
+To better understand the effect of erosion on groundwater flow, multiply-connected domains must be considered.
+Here we simulate two-dimensional erosion, in multiply-connected domain such as the porous geometry of many groundwater flows (Fig.~\ref{fig:50bodies}).
 
@@
 
+\vsp{5}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 
-\title{Viscous Erosion in Porous Media}
+\title{A boundary-integral framework to simulate \\ the viscous erosion of a porous medium}
 
 % OTHER TITLE POSSIBILITIES
-% A fast and accurate method for viscous erosion in a 2D porous medium
+% Viscous Erosion in Porous Media (change 'in' to 'of'?)
+% A fast and accurate method for viscous erosion of a 2D porous medium
+% A boundary-integral method for viscous erosion of a porous medium
+% A computational framework to simulate the viscous erosion of a porous medium
 
@@
 Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to human-scale structures and patterns \cite{}.
-Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay), as well as biological structures like plaque and biofilms.
+Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms.
 Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most appropriate regime for groundwater flow and the aforementioned biological examples.
@@
 In particular, Stokes flow enables long-range interactions, which strongly couples the shape evolution of difference bodies.
+
+% a class of problems (processes) collectively referred to as sculpting with flow.
 

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 
-Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to human-scale structures and patterns \cite{}.
-Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms.
-Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most appropriate regime for groundwater flow and the aforementioned biological examples.
-
-Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{}, as well as related processes such as dissolution \cite{} and melting \cite{}.
+Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, coh-dev-sey-yi-szy-rot2015} down to human-scale structures and patterns \cite{daerr2003erosion}.
+Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
+Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater flow and the aforementioned biological examples.
+
+Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, moore2017riemann}, as well as during related processes such as dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion}.
 In such cases, the flow alters the shape of the structure, which in turn modifies the surrounding flow, and so on --- a reciprocal process that can be summarized as `sculpting with flow'~\cite{ristroph2018sculpting}.
@@
 
+% Other possible refs for erosion: mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd
+
+% Other possible refs for dissolution/melting: yuan2017dynamics, claudin2017dissolution, hewett2017pear
+
 %% ORIGINAL %%%
 \vsp{5}
-%sand dunes to be  longer on the windward side~\cite{han1969}, 
-%stream-bed erosion is responsible for branching structures of rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  
-%Erosion is also important in biophysical applications---plaque erosion in arteries is key to understanding heart disease~\cite{sha2002, gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can be explained by erosion~\cite{pic-van-hei2000}.
-
-Recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}.
 

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 
-Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, coh-dev-sey-yi-szy-rot2015} down to human-scale structures and patterns \cite{daerr2003erosion}.
+Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale structures and patterns \cite{daerr2003erosion}.
 Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
@@
 
-Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, moore2017riemann}, as well as during related processes such as dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion}.
+Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and during related processes such as dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In such cases, the flow alters the shape of the structure, which in turn modifies the surrounding flow, and so on --- a reciprocal process that can be summarized as `sculpting with flow'~\cite{ristroph2018sculpting}.
@@
 
-% Other possible refs for erosion: mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd
-
-% Other possible refs for dissolution/melting: yuan2017dynamics, claudin2017dissolution, hewett2017pear
+% Other possible refs for erosion: mit-spa2016, lachaussee2018competitive, lopez2018cfd
+% Other possible refs for dissolution/melting: yuan2017dynamics, 
+% Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.
+% formations, features
 
@@
 \vsp{5}
-
 All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow'~\cite{ristroph2018sculpting}.
-% Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.
 

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 erosion occurs in the normal direction at a rate that is proportional to
-the magnitude of the shear stress~\cite{moo-ris-chi-zha-she2013}.  The
-constant of proportionality only sets the time scale, so we have set
+the magnitude of the shear stress~\cite{moo-ris-chi-zha-she2013}.  
+\todo[inline]{This makes it sound the erosion law sound too will-nilly; like anyone can come up with their own erosion law tomorrow and it would be equally valid.
+This is not the case.
+We use the law in which erosion is proportional to shear stress because {\em that is what the laboratory experiments show is true} (Ristoph 2012).}
+
+The constant of proportionality only sets the time scale, so we have set
 $\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.  For

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale structures and patterns \cite{daerr2003erosion}.
-Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater flow and the aforementioned biological examples.
+Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
+Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.
 
@@
 
+\vsp{2}
 The example of an eroding porous medium presents new and interesting opportunities in a few ways.
@@
 Lauga~\cite{mon-lau2015} which is an extension of the analysis done by
-Pironneau~\cite{pir1973} to find a Stokesian drag minimizing shape.  In
-this idealized case, analytical axisymmetric shapes that minimize the
+Pironneau~\cite{pir1973} to find a Stokesian drag minimizing shape. 
+\todo[inline]{Double check this statement. I am not sure that the shape found by Lauga has uniform shear stress. The shape found by Pironneau does.}
+In this idealized case, analytical axisymmetric shapes that minimize the
 drag can be found.  However, the effect of erosion on a porous media is

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
-We defer a study of these complex effects for future work.
+We therefore defer the study of these effects to future work.
 
@@
 Pironneau~\cite{pir1973} to find a Stokesian drag minimizing shape. 
-\todo[inline]{Double check this statement. I am not sure that the shape found by Lauga has uniform shear stress. The shape found by Pironneau does.}
+%\todo[inline]{Double check this statement. I am not sure that the shape found by Lauga has uniform shear stress. The shape found by Pironneau does.}
 In this idealized case, analytical axisymmetric shapes that minimize the

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 
-Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale structures and patterns \cite{daerr2003erosion}.
+Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale features and patterns \cite{daerr2003erosion}.
 Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.
-
-Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and during related processes such as dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
-In such cases, the flow alters the shape of the structure, which in turn modifies the surrounding flow, and so on --- a reciprocal process that can be summarized as `sculpting with flow'~\cite{ristroph2018sculpting}.
-The example of an eroding porous medium presents new challenges and opportunities in that multiply connected domains must be considered.
-Furthermore, the long-range effects of Stokes flow facilitates even stronger coupling between bodies.
-
-\vsp{2}
-The example of an eroding porous medium presents new and interesting opportunities in a few ways.
-First of all, the medium is composed of many bodies and so multiply-connected domains most be considered.
-These bodies can interact via the surrounding flow.
-In particular, Stokes flow enables long-range interactions, which strongly couples the shape evolution of difference bodies.
-
-% a class of problems (processes) collectively referred to as sculpting with flow.
+Motivated by such small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.
+
+Recent work in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, as well as during related processes such as dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+In such cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on.
+This class of processes has been collectively referred to as `sculpting with flow'~\cite{ristroph2018sculpting}.
+From this viewpoint, the example of an eroding porous medium presents a new opportunities and challenges.
+First, the medium itself is composed of many solid constituents, and so multi-body interactions, especially close interactions, are key.
+Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of different bodies.
+
+The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} in the case of 50 bodies of randomly assigned sizes and positions.
+In this work, mechanical erosion arises from the shear-stress induced by the flow, as has been experimentally confirmed \cite{ris-moo-chi-she-zha2012}.
+In Fig., color shows the vorticity of the surrounding flow.
+When evaluated on the solid boundaries, vorticity is equivalent to shear, and thus provides a convenient tool for visualizing local erosion rates.
+As shown in the figure, our simulations allows solid bodies to diminish in size and vanish in finite time, while other larger bodies persist.
+
+% Point out complex shapes with sharp features, maybe polygonal.
+% Point out channel structures develop.
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.80 \textwidth]{./figs/50bod.pdf}
+\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
+viscous flow.  The boundary conditions are a constant pressure drop that
+creates a flow from the left to right.  The rate of erosion is
+proportional to the shear stress which is equivalent to the vorticity
+evaluated on the bodies.  The colors represent the vorticity, so regions
+with large vorticity (in magnitude) are regions where the flow will
+erode the fastest.}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Figure generated from data file 50circ512p5, 
+%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
 
@@
 % Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.
-% formations, features
-
-%% ORIGINAL %%%
-\vsp{5}
-All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow'~\cite{ristroph2018sculpting}.
-
-Another application, which motivates the current work, is erosion caused by groundwater flow.
-Here, a slow moving fluid erodes channels in the ground, and this affects the fluid transport.
-To better understand the effect of erosion on groundwater flow, multiply-connected domains must be considered.
-Here we simulate two-dimensional erosion, in multiply-connected domain such as the porous geometry of many groundwater flows (Fig.~\ref{fig:50bodies}).
-
-Because of the length and velocity scales of groundwater flow, we
-restrict our attention to zero Reynolds number flows.  For groundwater
-flow, Darcy's law is often used, but this does not resolve the pore
-structure and assumes a homogeneous geometry which is often not valid.
-Instead, we use the incompressible Stokes equations as the governing
-fluid equations, and the individual pores are resolved which results in
-a complex multiply-connected geometry.  The dynamics of the individual
-pores are modelled with an erosion model that where the erosion rate is
-proportional to the magnitude of the shear stress.
-
-\vsp{5}
+% Land formations, geophysical features, structures, patterns
+
+% For groundwater flow, Darcy's law is often used, but this does not resolve the pore structure and assumes a homogeneous geometry which is often not valid.
+Instead, we use the incompressible Stokes equations as the governing fluid equations, and the individual pores are resolved which results in a complex multiply-connected geometry.
+
+\vsp{2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 magnitude of the shear stress.
+
+% Redundant statement: individual pores are resolved; individual grains are resolved.
 
@@
 geometries to better characterize erosion in porous media.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.80 \textwidth]{./figs/50bod.pdf}
-\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
-viscous flow.  The boundary conditions are a constant pressure drop that
-creates a flow from the left to right.  The rate of erosion is
-proportional to the shear stress which is equivalent to the vorticity
-evaluated on the bodies.  The colors represent the vorticity, so regions
-with large vorticity (in magnitude) are regions where the flow will
-erode the fastest.}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure generated from data file 50circ512p5, 
-%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
 

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 In such cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on.
-This class of processes has been collectively referred to as `sculpting with flow'~\cite{ristroph2018sculpting}.
-From this viewpoint, the example of an eroding porous medium presents a new opportunities and challenges.
+Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}.
+From this perspective, the example of an eroding porous medium presents a new opportunities and challenges.
 First, the medium itself is composed of many solid constituents, and so multi-body interactions, especially close interactions, are key.
@@
 In this work, mechanical erosion arises from the shear-stress induced by the flow, as has been experimentally confirmed \cite{ris-moo-chi-she-zha2012}.
-In Fig., color shows the vorticity of the surrounding flow.
+In Fig.~\ref{fig:50bodies}, color represents the vorticity of the surrounding flow.
 When evaluated on the solid boundaries, vorticity is equivalent to shear, and thus provides a convenient tool for visualizing local erosion rates.

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@
 
-Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale features and patterns \cite{daerr2003erosion}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale features and patterns \cite{daerr2003erosion}.
 Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
@@
 
-Recent work in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, as well as during related processes such as dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+Recent work in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}.
+A similar feedback mechanism is at work in the related processes of dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In such cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on.
 Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}.
-From this perspective, the example of an eroding porous medium presents a new opportunities and challenges.
-First, the medium itself is composed of many solid constituents, and so multi-body interactions, especially close interactions, are key.
-Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of different bodies.
-
-The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} in the case of 50 bodies of randomly assigned sizes and positions.
+From this viewpoint, the example of an eroding porous medium presents a new opportunities and challenges.
+First, the medium itself is composed of many solid constituents, and so multi-body interactions, especially close interactions, must be considered.
+Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of multiple bodies.
+
+The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} in for a medium composed of 50 bodies with randomly assigned initial positions and sizes.
 In this work, mechanical erosion arises from the shear-stress induced by the flow, as has been experimentally confirmed \cite{ris-moo-chi-she-zha2012}.

### 2018-04-06 docs/methods/erosion_methods.tex
NM

@@
 
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale features and patterns \cite{daerr2003erosion}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns \cite{daerr2003erosion}.
 Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by such small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.
-
-Recent work in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}.
-A similar feedback mechanism is at work in the related processes of dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+Motivated by such applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.
+
+Recent work in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, and a similar feedback occurs in the related processes of dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In such cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on.
@@
 First, the medium itself is composed of many solid constituents, and so multi-body interactions, especially close interactions, must be considered.
-Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of multiple bodies.
-
-The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} in for a medium composed of 50 bodies with randomly assigned initial positions and sizes.
-In this work, mechanical erosion arises from the shear-stress induced by the flow, as has been experimentally confirmed \cite{ris-moo-chi-she-zha2012}.
-In Fig.~\ref{fig:50bodies}, color represents the vorticity of the surrounding flow.
-When evaluated on the solid boundaries, vorticity is equivalent to shear, and thus provides a convenient tool for visualizing local erosion rates.
-As shown in the figure, our simulations allows solid bodies to diminish in size and vanish in finite time, while other larger bodies persist.
+Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of neighboring bodies, making their interactions even more important.
+
+\paragraph{Contributions}
+The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
+In this work, erosion of solid material arises from the mechanical stress induced by the surrounding flow.
+In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress -- a law that has been verified by laboratory experiments \cite{ris-moo-chi-she-zha2012}.
+As seen in the figure, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
+Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them.
+In the figure, color represents the vorticity of the surrounding flow, which, evaluated on solid boundaries, reduces to shear.
+In this way, vorticity provides a convenient tool for visualizing local erosion rates.
 
@@
 
-\vsp{2}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Contributions} The present study develops numerical methods
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The present study develops numerical methods
 to simulate erosion of multiply-connected two-dimensional geometries.

### 2018-04-06 docs/methods/erosion_methods.tex
NM

@@
 The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
-In this work, erosion of solid material arises from the mechanical stress induced by the surrounding flow.
+Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
 In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress -- a law that has been verified by laboratory experiments \cite{ris-moo-chi-she-zha2012}.
@@
 Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them.
-In the figure, color represents the vorticity of the surrounding flow, which, evaluated on solid boundaries, reduces to shear.
-In this way, vorticity provides a convenient tool for visualizing local erosion rates.
+In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vsp{2}
 The present study develops numerical methods

### 2018-04-06 docs/methods/erosion_methods.tex
small changes

@@
 discretized with a spectrally-accurate Nystr\"om method and solved
-with a fast-multipole-accelerated GMRES iteration. To evolve the individual grains under shear-driven
+with a fast-multipole-accelerated GMRES. To evolve the individual grains under shear-driven
 erosion, we regularize via curvature-penalization and solve the
@@
 numerically stable treatment of stiff terms, thus permitting large time
-steps. The overall accuracy of our method is exponential in space and
+steps. The overall accuracy of our method is spectral in space and
 second-order in time. The method is computationally efficient, with the
@@
 a mesh-independent number of GMRES iterations, and a one-time
-$\mathcal{O}(N^2)$ computation to compute the shear stress.
-We benchmark single-body results against analytical predictions.
-In our multibody simulations, we find that erosion leads to spontaneous channelization between bodies in near contact.
+$\mathcal{O}(N^2)$ computation to compute the shear stress. We benchmark
+single-body results against analytical predictions.
+In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact.
 The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
@@
 \section{Introduction\label{s:intro}}
-
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns \cite{daerr2003erosion}.
-Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by such applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.
-
-Recent work in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, and a similar feedback occurs in the related processes of dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}.
+Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
+Motivated by such applications, we develop numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.
+
+Recent work in the high-Reynolds number regime has highlighted the importance
+of the feedback between flow and morphology that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, and a similar feedback occurs in the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In such cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on.
 Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}.
-From this viewpoint, the example of an eroding porous medium presents a new opportunities and challenges.
-First, the medium itself is composed of many solid constituents, and so multi-body interactions, especially close interactions, must be considered.
+From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
+First, the medium itself is composed of many solid constituents, so multi-body interactions, especially close interactions, must be considered.
 Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of neighboring bodies, making their interactions even more important.
@@
 Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
-In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress -- a law that has been verified by laboratory experiments \cite{ris-moo-chi-she-zha2012}.
-As seen in the figure, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
+In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress --- a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
+As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
 Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them.
@@
 \vsp{2}
-The present study develops numerical methods
-to simulate erosion of multiply-connected two-dimensional geometries.
-In this fashion, individual pores are resolved rather than
-homogenized.  A boundary integral equation (BIE) is used to solve the
-incompressible Stokes equations in the complex geometry.  The resulting
-method resolves individual grains and the non-negligible interactions
-between bodies.  To link the eroding body and fluid dynamics, the body
-is eroded in the normal direction at a rate that is proportional to the
-magnitude of the shear stress.
+The present study develops numerical methods to simulate erosion of multiply-connected two-dimensional geometries.
+In this fashion, individual pores are resolved rather than homogenized.
+A boundary integral equation (BIE) is used to solve the incompressible Stokes equations in the complex geometry.
+The resulting method resolves individual grains and the non-negligible interactions between bodies.
+To link the eroding body and fluid dynamics, the body is eroded in the normal direction at a rate that is proportional to the magnitude of the shear stress.
 
@@
 
-To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in the ability to numerically stabilize moving-interface problems \cite{hou-low-she1994}.
+To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in the ability to numerically stabilize moving-interface problems~\cite{hou-low-she1994}.
 Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary.
@@
 unchecked, could lead to severe tangling and numerical instability. We
-therefore introduce an artificial tangential velocity $\Vs$ to keep the grid points equally spaced in arclength \cite{hou-low-she1994}. The appropriate tangential velocity satisfies 
+therefore introduce an artificial tangential velocity $\Vs$ to keep the grid points equally spaced in arclength~\cite{hou-low-she1994}. The appropriate tangential velocity satisfies 
 \begin{align}
@@
 This law must be modified in two dimensions, though.
-The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{batchelor1970slender, MooreJFM2012}.
+The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory~\cite{batchelor1970slender, MooreJFM2012}.
 For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
@@
 Locally, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge; see Fig.~\ref{corner} for a schematic.
-We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface \cite{moo-ris-chi-zha-she2013, moore2017riemann}.
+We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface~\cite{moo-ris-chi-zha-she2013, moore2017riemann}.
 For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$ (in this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
@@
 In this figure, time is normalized by the vanishing time $t_f = 1.79 \times 10^{-2}$ from the shrinking simulations (i.e.~Fig.~\ref{shrink_intface}).
-Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerged before the body disappeared \cite{moo-ris-chi-zha-she2013}.
+Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerged before the body disappeared~\cite{moo-ris-chi-zha-she2013}.
 
@@
 
-	In summary, we have found that a single-body eroding in 2D Stokes flow converges to a terminal form characterized by nearly uniform shear stress along its surface.
-The final shape is fairly slender, with an aspect ratio of 2.7, and distinguished by  corners of opening angle $102^{\circ}$ at the front and rear.
-This shape is closely related to the drag-minimizing profile found by Pironneau (1973) --- the geometry that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume \cite{pir1973}.
-Using variational principles, Pironneau showed that the drag-minimizing form has constant shear (or vorticity) along its surface.
-The resulting {\em axisymmetric} shape has an aspect ratio of 2.1 and front/rear opening-angles of $120^{\circ}$ \cite{pir1973, mit-spa2016}.
-Interestingly, 3D simulations of viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form \cite{mit-spa2016}.
-It was found that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
-Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ for self-similar reduction \cite{pir1973, mit-spa2016}.
+	In summary, we have found that a single-body eroding in 2D
+        Stokes flow converges to a terminal form characterized by nearly
+        uniform shear stress along its surface. The final shape is
+        fairly slender, with an aspect ratio of 2.7, and distinguished
+        by  corners of opening angle $102^{\circ}$ at the front and
+        rear. This shape is closely related to the drag-minimizing
+        profile found by Pironneau (1973) --- the geometry that
+        minimizes drag in 3D Stokes flow subject to the constraint of
+        fixed volume~\cite{pir1973}. Using variational principles,
+        Pironneau showed that the drag-minimizing form has constant
+        shear (or vorticity) along its surface. The resulting {\em
+        axisymmetric} shape has an aspect ratio of 2.1 and front/rear
+        opening-angles of $120^{\circ}$~\cite{pir1973, mit-spa2016}.
+        Interestingly, 3D simulations of viscous erosion showed close
+        resemblance between the shape formed by a single eroding body
+        and this Pironneau form~\cite{mit-spa2016}. It was found that
+        the eroding body does not converge {\em precisely} to the
+        Pironneau shape because the long-time surface-stress
+        distribution created by erosion is only {\em approximately}
+        uniform. Rather than strict uniformity, variations in body
+        curvature must be offset by slight variations in $\Vn$ for
+        self-similar reduction~\cite{pir1973, mit-spa2016}.
 Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well.
@@
 
-\section{Results: Multibody erosion}
+\section{Results: Multi-body erosion}
 \label{s:MultiResults}
@@
 
-Briefly, to validate the multibody simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}.
-In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$.
-This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$.
-To assess error, we measure the aggregate $L^2$-difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution.
-Note that this metric is sensitive to numerical errors in any of the simulated bodies.
-The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multibody interactions are handled correctly by the Stokes solver.
+Briefly, to validate the multi-body simulations with this new
+fixed-pressure-drop condition, we report a convergence test in Table
+\ref{convtab}. In this test, we simulate the erosion of 20 bodies to a
+stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of
+the time required for {\em all} bodies to vanish, and, in fact, a few of
+the bodies will have already vanished by $t_s$. To assess error, we
+measure the aggregate $L^2$-difference in the shape of {\em all} of the
+bodies, comparing simulations of successive temporal resolution. Note
+that this metric is sensitive to numerical errors in any of the
+simulated bodies. The table confirms that our method retains
+second-order accuracy in time, thus validating our rescaling procedure
+and confirming that multi-body interactions are handled correctly by the Stokes solver.
 The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution.
@@
 
-\subsection{Multibody results}
-
-With the validation complete, we now discuss the emergent physics of multibody erosion revealed by our simulations.
+\subsection{Multi-body results}
+
+With the validation complete, we now discuss the emergent physics of
+multi-body erosion revealed by our simulations.
 We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}).
@@
 \caption{\label{fig:mbodyplots} 
-Multibody simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation.
+Multi-body simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation.
 (a) The area fraction of the eroding bodies versus time.
@@
 
-To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
+To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows
+several measurements taken from the multi-body simulations.
 In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}.

### 2018-04-06 docs/methods/erosion_methods.tex
NM
small changes

@@
 \begin{abstract} 
-We develop numerical methods to simulate the fluid-mechanical erosion of
-many bodies in a two-dimensional Stokes flow. The broad aim
-is to simulate the erosion of a porous medium (e.g.~ground water flow)
-with grain-scale resolution. Our fluid solver is based on a
-second-kind boundary integral formulation of the Stokes equations that is
-discretized with a spectrally-accurate Nystr\"om method and solved
-with a fast-multipole-accelerated GMRES. To evolve the individual grains under shear-driven
-erosion, we regularize via curvature-penalization and solve the
-associated system using the {\thL} formulation. This framework allows
-numerically stable treatment of stiff terms, thus permitting large time
-steps. The overall accuracy of our method is spectral in space and
-second-order in time. The method is computationally efficient, with the
-fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration,
-a mesh-independent number of GMRES iterations, and a one-time
-$\mathcal{O}(N^2)$ computation to compute the shear stress. We benchmark
-single-body results against analytical predictions.
+We develop numerical methods to simulate the fluid-mechanical erosion of many bodies in a two-dimensional Stokes flow.
+The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with grain-scale resolution.
+Our fluid solver is based on a second-kind boundary integral formulation of the Stokes equations that is discretized with a spectrally-accurate Nystr\"om method and solved with a fast-multipole-accelerated GMRES.
+To evolve the individual grains under shear-driven erosion, we regularize via curvature-penalization and solve the associated system using the {\thL} formulation.
+This framework allows numerically stable treatment of stiff terms, thus permitting large time
+steps.
+The overall accuracy of our method is spectral in space and second-order in time.
+The method is computationally efficient, with the fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration, a mesh-independent number of GMRES iterations, and a one-time $\mathcal{O}(N^2)$ computation to compute the shear stress.
+We benchmark single-body results against analytical predictions.
 In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact.
@@
 Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by such applications, we develop numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.
+Motivated by such applications, we develop numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow---the most relevant regime for groundwater and bio-fluid applications.
 
@@
 
-\paragraph{Contributions}
 The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
 Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
-In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress --- a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
+In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress---a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
 As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
@@
 \includegraphics[width = 0.80 \textwidth]{./figs/50bod.pdf}
-\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a
-viscous flow.  The boundary conditions are a constant pressure drop that
-creates a flow from the left to right.  The rate of erosion is
-proportional to the shear stress which is equivalent to the vorticity
-evaluated on the bodies.  The colors represent the vorticity, so regions
-with large vorticity (in magnitude) are regions where the flow will
-erode the fastest.}
+\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a viscous flow.
+The boundary conditions are a constant pressure drop that creates a flow from the left to right.
+The rate of erosion is proportional to the shear stress which is equivalent to the vorticity evaluated on the bodies.
+The colors represent the vorticity, so regions with large vorticity (in magnitude) are regions where the flow will erode the fastest.}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vsp{2}
+To solve the incompressible Stokes equations in the complex geometry, we
+employ a boundary integral equation (BIE) method.
 The present study develops numerical methods to simulate erosion of multiply-connected two-dimensional geometries.

### 2018-04-06 docs/methods/erosion_methods.tex
NM

@@
 Both simulations show the flow rate to increase rapidly, even during the early stages of erosion when the area fraction has not changed that significantly.
-In fact, due to the logarithmic axis, the nearly linear trend seen in the figures corresponds to exponential growth of $\umax$.
+Due to the logarithmic axis, the nearly linear trend seen in the figure corresponds to exponential growth of $\umax$.
 The change in area-fraction alone cannot account for this rapid growth, suggesting the reshaping process to be vital.
-In particular, the formations of channels observed in Fig.~\ref{fig:06bodies} is most likely the key feature that enables the higher flow rates.
-
-Naturally, the flow rate allowed by the bodies is connected to the amount of drag that they exert.
+In particular, the formation of channels observed in Fig.~\ref{fig:06bodies} is most likely responsible for these higher flow rates.
+
+Naturally, the flow allowed by the medium is connected to the amount of drag the bodies exert.
 We therefore show in Fig.~\ref{fig:mbodyplots}(c) the total drag exerted by all bodies as it varies in time.
 In both cases, the drag remains nearly constant throughout much of the simulation and then drops to zero in the final moments.
-Here, the rapid increase of $\umax$ offsets the reduction in body size to create the nearly constant drag.
-
-To remove this effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag by $\umax$.
+Although all of the bodies are diminishing in size, the rapid increase in $\umax$ leads to the nearly constant drag that is observed.
+
+To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag normalized by $\umax$.
 Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies.
 In this way, we can interpret $F_D / (4 \pi \umax)$ as the {\em resistance} associated with the porous network.
+As seen in the figure, the medium's resistance decreases rapidly as its constituents erode.
+Since the vertical axis is logarithmic, the rate is roughly exponential at early times.
+
 %

### 2018-04-06 docs/methods/erosion_methods.tex
NM

@@
 In both cases, the drag remains nearly constant throughout much of the simulation and then drops to zero in the final moments.
-Although all of the bodies are diminishing in size, the rapid increase in $\umax$ leads to the nearly constant drag that is observed.
+Although all bodies are diminishing in size, the associated increase in $\umax$ leads to the nearly constant drag that is observed.
 
@@
 Since the vertical axis is logarithmic, the rate is roughly exponential at early times.
-
-%
-The figure shows the resistance to decrease rapidly as the bodies erode.
-Once again the vertical axis is logarithmic, and so the linear trend corresponds to exponential decay of $F_D / (4 \pi \umax)$.
-We propose that the channelization is responsible for creating such a rapid decline in the network resistance.
+As before, the reduction in area-fraction is not sufficient to explain this rapid decrease, leaving the channelization process as the most likely explanation.
 

### 2018-04-06 docs/methods/erosion_methods.tex
working on intro

--- 2018-04-06 docs/methods/erosion_methods.tex
@@
 
-The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
-Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
-In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress---a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
-As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
-Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them.
-In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.
+The methods developed here will allow us to simulate the erosion of many
+bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50
+bodies (of randomly assigned initial sizes and positions). Here, the
+erosion of solid material arises from the mechanical stress induced by
+the surrounding flow. In particular, we take the local rate of erosion
+to be proportional to the magnitude of the shear stress---a law that has
+been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
+As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size
+of the bodies, but also alters their shapes considerably. Notice, in
+particular, that many bodies develop corner-like features and nearly
+flat faces, with straight channels intervening between them. In the
+figure, color represents the vorticity of the surrounding flow, which
+reduces to shear on solid boundaries and thus provides a convenient tool
+for visualizing local erosion rates. To perform this simulation of
+Stokesian erosion of a porous media, two fast and accurate methods are
+employed---one to solve the fluid equations and the other to integrate
+the eroding grains.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-To solve the incompressible Stokes equations in the complex geometry, we
-employ a boundary integral equation (BIE) method.
-The present study develops numerical methods to simulate erosion of multiply-connected two-dimensional geometries.
-In this fashion, individual pores are resolved rather than homogenized.
-A boundary integral equation (BIE) is used to solve the incompressible Stokes equations in the complex geometry.
-The resulting method resolves individual grains and the non-negligible interactions between bodies.
-To link the eroding body and fluid dynamics, the body is eroded in the normal direction at a rate that is proportional to the magnitude of the shear stress.
-
-% Redundant statement: individual pores are resolved; individual grains are resolved.
-
-To create high-fidelity and computationally efficient numerical methods,
-two fast and accurate methods are employed.  First, the fluid velocity
-and the erosion rate (shear stress) are computed with a
-fast-multipole-accelerated Kryolv method applied to a spectrally
-accurate discretization of the governing equations.  In particular,
-GMRES~\cite{saa-sch1986} is applied to a spectrally-accurate Nystr\"om
-discretization of the BIE~\cite{tre-wei2014}, a spectrally accurate
-quadrature rule is used to compute the shear stress~\cite{sid-isr1988},
-and all arclength derivatives are computed with Fourier differentiation.
-In addition to computing the shear stress, we also compute the vorticity
-in the fluid bulk.  The vorticity is particularly insightful since it is
-identical to the shear stress on no-slip boundaries.  Therefore, by
-computing the vorticity, we are able to identify regions where the
-erosion rate will be fast or slow (Fig.~\ref{fig:50bodies}).
-
-Once the erosion rate is computed, the shape is integrated in time with
+The fluid equations are reformulated in terms of a boundary integral
+equation (BIE).  Since the boundary conditions are Dirichlet, we use a
+double-layer potential formulation so that the resulting BIE is
+second-kind.  This second-kind BIE is discretized with the spectrally
+accurate trapezoid rule~\cite{tre-wei2014} which results in a
+well-conditioned dense linear system for an unknown density function.
+This linear system is solved using fast-multipole-accelerated
+GMRES~\cite{saa-sch1986}.  Once the density function is computed, the
+erosion rate (shear stress) is computed with a spectrally accurate
+odd-even quadrature rule~\cite{sid-isr1988}.  In addition, the pressure
+and vorticity are computed in the fluid bulk (Fig.~\ref{fig:50bodies})
+with an upsampled trapezoid rule in the fluid bulk to assist with
+visualizing the effect of erosion in porous media.
+
+%
+%To create high-fidelity and computationally efficient numerical methods,
+%two fast and accurate methods are employed.  First, the fluid velocity
+%and the erosion rate (shear stress) are computed with a
+%fast-multipole-accelerated Kryolv method applied to a spectrally
+%accurate discretization of the governing equations.  In particular,
+%GMRES~\cite{saa-sch1986} is applied to a spectrally-accurate Nystr\"om
+%discretization of the BIE~\cite{tre-wei2014}, a spectrally accurate
+%quadrature rule is used to compute the shear stress~\cite{sid-isr1988},
+%and all arclength derivatives are computed with Fourier differentiation.
+%In addition to computing the shear stress, we also compute the vorticity
+%in the fluid bulk.  The vorticity is particularly insightful since it is
+%identical to the shear stress on no-slip boundaries.  Therefore, by
+%computing the vorticity, we are able to identify regions where the
+%erosion rate will be fast or slow (Fig.~\ref{fig:50bodies}).
+
+Once the erosion rate is computed, the grains are integrated in time with
 second-order accuracy.  Tracking the interface of fluid-structure
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Limitations} 
-We begin by making two fundamental design choices: first, we restrict ourselves to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
-The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium.
-While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
-The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
-While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
-We therefore defer the study of these effects to future work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Related work} The effect of erosion on a geometry is quite
-rich.  For instance, it has been hypothesized and numerically observed
-that the erosion leads to a shear stress that is uniform on the body
-which results in a uniform erosion rate.  The shape that has a uniform
-shear stress is analyzed in three dimensions by Montenegro-Johnson and
-Lauga~\cite{mon-lau2015} which is an extension of the analysis done by
-Pironneau~\cite{pir1973} to find a Stokesian drag minimizing shape. 
+The effect of erosion on a geometry is quite rich.  For instance, it has
+been hypothesized and numerically observed that the erosion leads to a
+shear stress that is uniform on the body which results in a uniform
+erosion rate.  The shape that has a uniform shear stress is analyzed in
+three dimensions by Montenegro-Johnson and Lauga~\cite{mon-lau2015}
+which is an extension of the analysis done by Pironneau~\cite{pir1973}
+to find a Stokesian drag minimizing shape. 
 %\todo[inline]{Double check this statement. I am not sure that the shape found by Lauga has uniform shear stress. The shape found by Pironneau does.}
@@
 drag can be found.  However, the effect of erosion on a porous media is
-less understood.
-
-Simulating eroding bodies has been studied analytically, experimentally, and numerically.
-Many of these works are motivated by high Reynolds number geophysical applications, such as the work of the second author~\cite{moo-ris-chi-zha-she2013, ris-moo-chi-she-zha2012, moore2017riemann} and others~\cite{par-izu2000, lag2000, coh-dev-sey-yi-szy-rot2015, han1969, Rothman2012, hewett2017evolution, ristroph2018sculpting, lopez2018cfd, lachaussee2018competitive, cohen2016erosion}.
-The work most closely related to ours simulates erosion in a three-dimensional incompressible Stokesian fluid~\cite{mit-spa2016}, but they only consider single eroding body.
+less understood.  The work most closely related to ours simulates erosion in a three-dimensional incompressible Stokesian fluid~\cite{mit-spa2016}, but they only consider single eroding body.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Outline of the paper} In Section~\ref{s:formulation}, we
-describe the governing equations for both the fluid and the erosion
-model in a \thL~framework.  In Section~\ref{s:method}, the numerical
-methods in both space and time are described and Section~\ref{s:qoi}
-describes how to compute the vorticity, pressure, and drag.
-Section~\ref{s:SingleResults} gives several numerical examples for a
-single body, and Section~\ref{s:MultiResults} presents numerical
-examples for multiply-connected domains.  Finally, concluding remarks
-are made in Section~\ref{s:conclusions}.
+We make two fundamental design choices: first, we restrict ourselves to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
+The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium.
+While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
+The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
+While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
+We therefore defer the study of these effects to future work.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In Section~\ref{s:formulation}, we describe the governing equations for
+both the fluid and the erosion model in a \thL~framework.  In
+Section~\ref{s:method}, the numerical methods in both space and time are
+described and Section~\ref{s:qoi} describes how to compute the
+vorticity, pressure, and drag.  Section~\ref{s:SingleResults} gives
+several numerical examples for a single body, and
+Section~\ref{s:MultiResults} presents numerical examples for
+multiply-connected domains.  Finally, concluding remarks are made in
+Section~\ref{s:conclusions}.
 
@@
 Both simulations show the flow rate to increase rapidly, even during the early stages of erosion when the area fraction has not changed that significantly.
-In fact, due to the logarithmic axis, the nearly linear trend seen in the figures corresponds to exponential growth of $\umax$.
+Due to the logarithmic axis, the nearly linear trend seen in the figures corresponds to exponential growth of $\umax$.
 The change in area-fraction alone cannot account for this rapid growth, suggesting the reshaping process to be vital.

### 2018-04-06 docs/methods/erosion_methods.tex

@@
 Both simulations show the flow rate to increase rapidly, even during the early stages of erosion when the area fraction has not changed that significantly.
-Due to the logarithmic axis, the nearly linear trend seen in the figures corresponds to exponential growth of $\umax$.
+Due to the logarithmic axis, the nearly linear trend seen in the figure corresponds to exponential growth of $\umax$.
 The change in area-fraction alone cannot account for this rapid growth, suggesting the reshaping process to be vital.
-In particular, the formations of channels observed in Fig.~\ref{fig:06bodies} is most likely the key feature that enables the higher flow rates.
-
-Naturally, the flow rate allowed by the bodies is connected to the amount of drag that they exert.
+In particular, the formation of channels observed in Fig.~\ref{fig:06bodies} is most likely responsible for these higher flow rates.
+
+Naturally, the flow allowed by the medium is connected to the amount of drag the bodies exert.
 We therefore show in Fig.~\ref{fig:mbodyplots}(c) the total drag exerted by all bodies as it varies in time.
 In both cases, the drag remains nearly constant throughout much of the simulation and then drops to zero in the final moments.
-Here, the rapid increase of $\umax$ offsets the reduction in body size to create the nearly constant drag.
-
-To remove this effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag by $\umax$.
+Although all bodies are diminishing in size, the associated increase in $\umax$ leads to the nearly constant drag that is observed.
+
+To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag normalized by $\umax$.
 Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies.
 In this way, we can interpret $F_D / (4 \pi \umax)$ as the {\em resistance} associated with the porous network.
-%
-The figure shows the resistance to decrease rapidly as the bodies erode.
-Once again the vertical axis is logarithmic, and so the linear trend corresponds to exponential decay of $F_D / (4 \pi \umax)$.
-We propose that the channelization is responsible for creating such a rapid decline in the network resistance.
+As seen in the figure, the medium's resistance decreases rapidly as its constituents erode.
+Since the vertical axis is logarithmic, the rate is roughly exponential at early times.
+As before, the reduction in area-fraction is not sufficient to explain this rapid decrease, leaving the channelization process as the most likely explanation.
 

### 2018-04-06 docs/methods/erosion_methods.tex
NM

@@
 The change in area-fraction alone cannot account for this rapid growth, suggesting the reshaping process to be vital.
-In particular, the formation of channels observed in Fig.~\ref{fig:06bodies} is most likely responsible for these higher flow rates.
+In particular, the formation of channels observed in Fig.~\ref{fig:06bodies} may account for these higher flow rates.
 
@@
 In both cases, the drag remains nearly constant throughout much of the simulation and then drops to zero in the final moments.
-Although all bodies are diminishing in size, the associated increase in $\umax$ leads to the nearly constant drag that is observed.
+Although all bodies are diminishing in size, the associated increase in $\umax$ leads to the nearly constant drag that is observed here.
 
@@
 Since the vertical axis is logarithmic, the rate is roughly exponential at early times.
-As before, the reduction in area-fraction is not sufficient to explain this rapid decrease, leaving the channelization process as the most likely explanation.
+As before, the reduction in area-fraction is not sufficient to explain this rapid decline, leaving the channelization process as the most likely mechanism.
+
+%Comparing the 50 and 6-body simualtions... Though the area fractions of the two simulations are nearly the same, the 50-body configuration provides about 5 times more resistance.
+
+% Good word: Spontaneous channelization
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions\label{s:conclusions}}
 
 \todo[inline]{Here in revising}
-
-% corresponds, pertains, is connected to, involves, is related to, concerns
-
-Comparing the 50 and 6-body simualtions...
-Though the area fractions of the two simulations are nearly the same, the 50-body configuration provides about 5 times more resistance.
-
-Look back at Fig. 1 and notice similar features: channelization, sort-of polygonal bodies, etc.
-
-{\bf Good word: Spontaneous channelization}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions\label{s:conclusions}}
 

### 2018-04-06 docs/methods/erosion_methods.tex
work on intro

--- 2018-04-06 docs/methods/erosion_methods.tex
@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}.
-Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by such applications, we develop numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow---the most relevant regime for groundwater and bio-fluid applications.
-
-Recent work in the high-Reynolds number regime has highlighted the importance
-of the feedback between flow and morphology that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, and a similar feedback occurs in the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
-In such cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on.
-Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}.
-From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
-First, the medium itself is composed of many solid constituents, so multi-body interactions, especially close interactions, must be considered.
-Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of neighboring bodies, making their interactions even more important.
+Flow-induced erosion deteriorates and reshapes solid material over a
+range of scales found in nature, from large geological
+formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down
+to human-scale features and patterns~\cite{daerr2003erosion}. Though
+less visible, these same forces are at work at the very smallest scales,
+slowly deteriorating the individual constituents of porous media
+(e.g.~solid, sand, or clay) or biological structures like plaque and
+biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such applications, we
+develop numerical methods to simulate fluid-mechanical erosion of
+multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and bio-fluid applications.
+
+Recent work in the high-Reynolds number regime has highlighted the
+importance of the feedback between flow and morphology that occurs
+during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013,
+hewett2017evolution, moore2017riemann}, and a similar feedback occurs in
+the related processes of dissolution and melting~\cite{Huang2015,
+kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion,
+hewett2017pear, claudin2017dissolution}. In such cases, the flow alters
+the shape of the immersed structures, which in turn modifies the
+surrounding flow, and so on. Collectively, such processes have been
+referred to as `sculpting with flow'~\cite{ristroph2018sculpting}. From
+this viewpoint, the example of an eroding porous medium presents new
+opportunities and challenges. First, the medium itself is composed of
+many solid constituents, so multi-body interactions, especially close
+interactions, must be considered. Second, the long-range interactions
+facilitated by Stokes flow makes all the interactions between bodies important.
 
@@
 reduces to shear on solid boundaries and thus provides a convenient tool
-for visualizing local erosion rates. To perform this simulation of
-Stokesian erosion of a porous media, two fast and accurate methods are
-employed---one to solve the fluid equations and the other to integrate
-the eroding grains.
+for visualizing local erosion rates.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The fluid equations are reformulated in terms of a boundary integral
-equation (BIE).  Since the boundary conditions are Dirichlet, we use a
+To perform this simulation of Stokesian erosion of a porous media, two
+fast and accurate methods are employed---one to solve the fluid
+equations and the other to integrate the eroding grains.  The fluid
+equations are reformulated in terms of a boundary integral equation
+(BIE).  Since the boundary conditions are Dirichlet, we use a
 double-layer potential formulation so that the resulting BIE is

### 2018-04-06 docs/methods/erosion_methods.tex
NM

@@
 
-Once the erosion rate is computed, the grains are integrated in time with
-second-order accuracy.  Tracking the interface of fluid-structure
-interaction problems with a long time horizon is particularly
-difficult---the mesh is often distorted and tangled.  Moreover, erosion
-naturally leads to regions of high or infinite (i.e.~corners) curvature.
-The interface tracking issues are resolved by, first, introducing a
-tangential velocity field to maintain a grid that is equispaced in
-arclength, but does not affect the dynamics, and, second, a tunable term
-that penalizes regions of high curvature.  Furthermore, the frame of
-reference is changed to \thL~variables so that the curvature term
+Next, the computed shear stress is used to evolve the solid boundaries.
+Tracking the interface of fluid-structure interaction problems with a long time horizon is particularly
+difficult as the mesh can become distorted and tangled. 
+Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
+The interface tracking issues are addressed in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect the interface dynamics; second, we introduce a curvature-penalizing term into the normal interface velocity to suppress high-frequency oscillations associated with nearly singular curvature.
+Furthermore, the frame of reference is changed to \thL~variables so that the curvature term
 appears as a diffusive term that can easily be handled in a numerically

### 2018-04-06 docs/methods/erosion_methods.tex
NM

@@
 The interface tracking issues are addressed in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect the interface dynamics; second, we introduce a curvature-penalizing term into the normal interface velocity to suppress high-frequency oscillations associated with nearly singular curvature.
-Furthermore, the frame of reference is changed to \thL~variables so that the curvature term
-appears as a diffusive term that can easily be handled in a numerically
-stable fashion with an exponential integrator.
+Furthermore, the interface is parametrized in the so-called {\thL} coordinate-system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.
 

### 2018-04-06 docs/methods/erosion_methods.tex
small changes

--- 2018-04-06 docs/methods/erosion_methods.tex
@@
 this viewpoint, the example of an eroding porous medium presents new
-opportunities and challenges. First, the medium itself is composed of
-many solid constituents, so multi-body interactions, especially close
-interactions, must be considered. Second, the long-range interactions
-facilitated by Stokes flow makes all the interactions between bodies important.
+opportunities and challenges. For example, the medium itself is composed
+of many solid constituents, so multi-body interactions, especially close
+interactions, must be considered.
+%Second, the long-range interactions
+%facilitated by Stokes flow makes all the interactions between bodies important.
 
@@
 equations are reformulated in terms of a boundary integral equation
-(BIE).  Since the boundary conditions are Dirichlet, we use a
-double-layer potential formulation so that the resulting BIE is
+(BIE)~\cite{poz1992}.  Since the boundary conditions are Dirichlet, we
+use a double-layer potential formulation so that the resulting BIE is
 second-kind.  This second-kind BIE is discretized with the spectrally
@@
 
-To simulate multiple bodies, it is essential to resolve the nonlocal
-effects between the different bodies.  In this work, these interactions
-are included with high-order accuracy by using an integral equation
-method~\cite{poz1992}.  Integral equations have been used extensively to
-simulate viscous fluids in complex geometries, including porous media
+To simulate Stokesian erosion, it is essential to resolve the nonlocal
+effects between the different bodies.  BIEs naturally resolve these
+interactions, and they have been used extensively to simulate viscous
+fluids in complex geometries, including porous media
 flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}. Challenges of a
@@
 multigrid~\cite{qua-bir2015a} and the inverse fast multipole
-method~\cite{qua-cou-dar2018}, but the results presented in this work
-require no more than $\mathcal{O}(100)$ GMRES iterations which is too
-small to make preconditioners for BIEs effective; preconditioners will
-be considered further in future work when there are many more grains
-that are also being transported by the flow.  To address the
-nearly-singular integrands, we use the fact that the grains are eroding
-and not moving, so their separation increases with time.  Therefore, in
-this work, we apply an upsampling scheme, but in future work, we will
-require a near-singular integration scheme~\cite{qua-bir2014a,
-klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.
-
-We make two fundamental design choices: first, we restrict ourselves to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
-The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium.
-While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
-The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
-While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
-We therefore defer the study of these effects to future work.
+method~\cite{qua-cou-dar2018, cou-pou-dar2017}, but the results
+presented in this work require no more than $\mathcal{O}(100)$ GMRES
+iterations which is too small to make preconditioners for BIEs
+effective; preconditioners will be considered in future work when many
+more grains are eroding and being transported by the flow.  To address
+the nearly-singular integrands, we use the fact that the grains are
+eroding and not moving, so their separation increases with time.
+Therefore, in this work, we apply an upsampling scheme, but in future
+work, we will require a near-singular integration
+scheme~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
+hel-oja2008a, bea-lai2001}.
+
+We make two fundamental design choices: first, we restrict ourselves to
+two spatial dimensions, and second the bodies are considered immobile
+(i.e.~fixed to their initial locations). The restriction to two
+dimensions allows us to simulate the erosion of many bodies (up to $50$
+in this manuscript) with high resolution, giving us the ability to
+accurately characterize the erosion of a porous medium. While BIEs are
+available in three dimensions, the extra computational cost limits the
+number of bodies that could be practically simulated, making
+porous-medium simulations less feasible. The second assumption of
+immobile bodies affords a simple framework to study the effects of
+erosion in isolation. While other effects, such as sedimentation or
+transport, undoubtedly play a role in real applications, these effects
+would introduce additional complexity, both conceptually and
+numerically. We therefore defer the study of these effects to future
+work.
 
@@
 \section{Conclusions\label{s:conclusions}}
+We have developed a numerical framework for simulating two-dimensional
+Stokesian erosion in a porous media.  By using a BIE formulation of the
+fluid equations and a {\thL}, we achieve spectral accuracy
 

### 2018-04-06 docs/methods/erosion_methods.tex

@@
 
-Once the erosion rate is computed, the grains are integrated in time with
-second-order accuracy.  Tracking the interface of fluid-structure
-interaction problems with a long time horizon is particularly
-difficult---the mesh is often distorted and tangled.  Moreover, erosion
-naturally leads to regions of high or infinite (i.e.~corners) curvature.
-The interface tracking issues are resolved by, first, introducing a
-tangential velocity field to maintain a grid that is equispaced in
-arclength, but does not affect the dynamics, and, second, a tunable term
-that penalizes regions of high curvature.  Furthermore, the frame of
-reference is changed to \thL~variables so that the curvature term
-appears as a diffusive term that can easily be handled in a numerically
-stable fashion with an exponential integrator.
+Next, the computed shear stress is used to evolve the solid boundaries.
+Tracking the interface of fluid-structure interaction problems with a long time horizon is particularly
+difficult as the mesh can become distorted and tangled. 
+Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
+The interface tracking issues are addressed in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect the interface dynamics; second, we introduce a curvature-penalizing term into the normal interface velocity to suppress high-frequency oscillations associated with nearly singular curvature.
+Furthermore, the interface is parametrized in the so-called {\thL} coordinate-system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.
 

### 2018-04-06 docs/methods/erosion_methods.tex
added paragraph headings

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Contributions}
 To perform this simulation of Stokesian erosion of a porous media, two
@@
 
+\paragraph{Related Work}
 The effect of erosion on a geometry is quite rich.  For instance, it has
@@
 
+\paragraph{Limitations}
 We make two fundamental design choices: first, we restrict ourselves to
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Outline of the Paper}
 In Section~\ref{s:formulation}, we describe the governing equations for

### 2018-04-06 docs/methods/erosion_methods.tex
rearranged

@@
 The interface tracking issues are addressed in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect the interface dynamics; second, we introduce a curvature-penalizing term into the normal interface velocity to suppress high-frequency oscillations associated with nearly singular curvature.
-Furthermore, the interface is parametrized in the so-called {\thL} coordinate-system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.
+Furthermore, the interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.
 
@@
 geometries to better characterize erosion in porous media.
+
+\paragraph{Limitations}
+We make two fundamental design choices: first, we restrict ourselves to
+two spatial dimensions, and second the bodies are considered immobile
+(i.e.~fixed to their initial locations). The restriction to two
+dimensions allows us to simulate the erosion of many bodies (up to $50$
+in this manuscript) with high resolution, giving us the ability to
+accurately characterize the erosion of a porous medium. While BIEs are
+available in three dimensions, the extra computational cost limits the
+number of bodies that could be practically simulated, making
+porous-medium simulations less feasible. The second assumption of
+immobile bodies affords a simple framework to study the effects of
+erosion in isolation. While other effects, such as sedimentation or
+transport, undoubtedly play a role in real applications, these effects
+would introduce additional complexity, both conceptually and
+numerically. We therefore defer the study of these effects to future
+work.
 
@@
 hel-oja2008a, bea-lai2001}.
-
-\paragraph{Limitations}
-We make two fundamental design choices: first, we restrict ourselves to
-two spatial dimensions, and second the bodies are considered immobile
-(i.e.~fixed to their initial locations). The restriction to two
-dimensions allows us to simulate the erosion of many bodies (up to $50$
-in this manuscript) with high resolution, giving us the ability to
-accurately characterize the erosion of a porous medium. While BIEs are
-available in three dimensions, the extra computational cost limits the
-number of bodies that could be practically simulated, making
-porous-medium simulations less feasible. The second assumption of
-immobile bodies affords a simple framework to study the effects of
-erosion in isolation. While other effects, such as sedimentation or
-transport, undoubtedly play a role in real applications, these effects
-would introduce additional complexity, both conceptually and
-numerically. We therefore defer the study of these effects to future
-work.
 
@@
 Stokesian erosion in a porous media.  By using a BIE formulation of the
-fluid equations and a {\thL}, we achieve spectral accuracy
+fluid equations and a {\thL}, we achieve spectral accuracy in space and
+second-order accuracy in time.  In addition, the non-negligible
+interactions between different bodies are accurately resolved.
 

### 2018-04-06 docs/methods/erosion_methods.tex
NM
language changes

@@
 GMRES~\cite{saa-sch1986}.  Once the density function is computed, the
-erosion rate (shear stress) is computed with a spectrally accurate
+shear stress is computed with a spectrally accurate
 odd-even quadrature rule~\cite{sid-isr1988}.  In addition, the pressure
@@
 We validate our method on a single circular body placed symmetrically in
-a pipe flow.  By artificially fixing the area of the body as a function
+a channel flow.  By artificially fixing the area of the body as a function
 of time, we are able to characterize the long-time behavior of the shape

### 2018-04-06 docs/methods/erosion_methods.tex

@@
 
-We validate our method on a single circular body placed symmetrically in
-a channel flow.  By artificially fixing the area of the body as a function
-of time, we are able to characterize the long-time behavior of the shape
-and the resulting flow and these results agree with analytical results.
-Then, we compute the vorticity of erosion in multiply-connected
-geometries to better characterize erosion in porous media.
+We supplement our primarily computational study with a few analytical results.
+In particular, we find a single body eroding in Stokes flow tends to a slender, for-aft symmetric form with sharp corners at its front and rear.
+By appealing to the principle that erosion more evenly distributes the shear stress along the surface, we can analytically predict the opening angle formed at the front and rear.
+In addition, drag laws from slender-body theory allows us to derive scaling laws for the rate of the body's area and drag reduction.
+These analytical results, in addition to having value in their own right, allow us to conclusively validate our simulation.
 
 \paragraph{Limitations}
-We make two fundamental design choices: first, we restrict ourselves to
+We make two fundamental design choices in our simulation: first, we restrict ourselves to
 two spatial dimensions, and second the bodies are considered immobile
@@
 \paragraph{Related Work}
-The effect of erosion on a geometry is quite rich.  For instance, it has
-been hypothesized and numerically observed that the erosion leads to a
-shear stress that is uniform on the body which results in a uniform
-erosion rate.  The shape that has a uniform shear stress is analyzed in
-three dimensions by Montenegro-Johnson and Lauga~\cite{mon-lau2015}
-which is an extension of the analysis done by Pironneau~\cite{pir1973}
-to find a Stokesian drag minimizing shape. 
-%\todo[inline]{Double check this statement. I am not sure that the shape found by Lauga has uniform shear stress. The shape found by Pironneau does.}
-In this idealized case, analytical axisymmetric shapes that minimize the
-drag can be found.  However, the effect of erosion on a porous media is
-less understood.  The work most closely related to ours simulates erosion in a three-dimensional incompressible Stokesian fluid~\cite{mit-spa2016}, but they only consider single eroding body.
-
-To simulate Stokesian erosion, it is essential to resolve the nonlocal
-effects between the different bodies.  BIEs naturally resolve these
-interactions, and they have been used extensively to simulate viscous
-fluids in complex geometries, including porous media
-flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}. Challenges of a
-BIE formulation include resolving the interactions between nearly
-touching bodies and developing efficient preconditioners for the
-discretized system.  Possible preconditioners include
+
+The most closely related work to ours is Mitchell \& Spagnolie \cite{mit-spa2016}, who developed methods to simulate viscous erosion in three dimensions.
+That work employed a traction integral equation to solve for the surrounding Stokes flow.
+The advantage to this formulation is that it immediately provides the shear stress required to evolve boundaries.
+However, the standard double-layer potential used here will allow us to compute certain quantities in the fluid bulk, such as vorticity and pressure, that will facilitate our understanding of the erosion process.
+Furthermore, our primary aim is to simulate the erosion of multiple bodies held fixed within a porous network, whereas Mitchell \& Spagnolie simulated a single eroding body that is mobile.
+
+For these porous network simulations, it is essential to resolve the nonlocal effects between the different bodies.
+BIEs naturally resolve these interactions, and they have been used extensively to simulate viscous fluids in complex geometries, including porous media flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.
+Common challenges of a BIE formulation include developing efficient preconditioners for the discretized system and numerical difficulties associated with nearly touching bodies.
+In this work, we consider geometries requiring $\mathcal{O}(100)$ GMRES iterations, so that preconditioners are not necessary.
+In future work, we will address mobile bodies for which near contacts may necessitate the preconditoners.
+Similarly, near-singular schemes will not be necessary due to the fact that the spacing between receding bodies of fixed position always grows in time.
+Again, the future consideration of mobile bodies may necessitate these near-singular schemes.
+
+Possible preconditioners include
 multigrid~\cite{qua-bir2015a} and the inverse fast multipole
@@
 effective; preconditioners will be considered in future work when many
-more grains are eroding and being transported by the flow.  To address
-the nearly-singular integrands, we use the fact that the grains are
+more grains are eroding and being transported by the flow.  
+To address the nearly-singular integrands, we use the fact that the grains are
 eroding and not moving, so their separation increases with time.
@@
 where $\Vn$ is the normal velocity of the interface and $\mu$ is the
-fluid viscosity.  There are several models for
-erosion~\cite{par-izu2000,lag2000}, but we have adopted the model that
-erosion occurs in the normal direction at a rate that is proportional to
-the magnitude of the shear stress~\cite{moo-ris-chi-zha-she2013}.  
-\todo[inline]{This makes it sound the erosion law sound too will-nilly; like anyone can come up with their own erosion law tomorrow and it would be equally valid.
-This is not the case.
-We use the law in which erosion is proportional to shear stress because {\em that is what the laboratory experiments show is true} (Ristoph 2012).}
-
+fluid viscosity.   
 The constant of proportionality only sets the time scale, so we have set
@@
 density function.  As the viscosity $\mu$ also sets the time scale, we
-take $\mu=1$.  \todo[inline]{Do you think we should flesh out this
-time-scale stuff more precisely? i.e.~By setting $\mu = 1$ and $C = 1$
-(the erosion constant), what exactly is the timescale that defines our
-dimensionless time.} \todo[inline]{This might be worth doing.  Is it
-something you can do quickly or do you want me to take a crack at it?}
+take $\mu=1$.
 

### 2018-04-06 docs/methods/erosion_methods.tex
NM

@@
 \paragraph{Limitations}
-We make two fundamental design choices in our simulation: first, we restrict ourselves to
+We make two fundamental design choices in our simulation: first, we restrict attention to
 two spatial dimensions, and second the bodies are considered immobile

### 2018-04-06 docs/methods/erosion_methods.tex
round of revisions

@@
 The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with grain-scale resolution.
-Our fluid solver is based on a second-kind boundary integral formulation of the Stokes equations that is discretized with a spectrally-accurate Nystr\"om method and solved with a fast-multipole-accelerated GMRES.
+Our fluid solver is based on a second-kind boundary integral formulation of the Stokes equations that is discretized with a spectrally-accurate Nystr\"om method and solved with fast-multipole-accelerated GMRES.
 To evolve the individual grains under shear-driven erosion, we regularize via curvature-penalization and solve the associated system using the {\thL} formulation.
@@
 accurate trapezoid rule~\cite{tre-wei2014} which results in a
-well-conditioned dense linear system for an unknown density function.
-This linear system is solved using fast-multipole-accelerated
+well-conditioned dense linear system for an unknown density function,
+and the linear system is solved using fast-multipole-accelerated
 GMRES~\cite{saa-sch1986}.  Once the density function is computed, the
@@
 and vorticity are computed in the fluid bulk (Fig.~\ref{fig:50bodies})
-with an upsampled trapezoid rule in the fluid bulk to assist with
-visualizing the effect of erosion in porous media.
-
-%
-%To create high-fidelity and computationally efficient numerical methods,
-%two fast and accurate methods are employed.  First, the fluid velocity
-%and the erosion rate (shear stress) are computed with a
-%fast-multipole-accelerated Kryolv method applied to a spectrally
-%accurate discretization of the governing equations.  In particular,
-%GMRES~\cite{saa-sch1986} is applied to a spectrally-accurate Nystr\"om
-%discretization of the BIE~\cite{tre-wei2014}, a spectrally accurate
-%quadrature rule is used to compute the shear stress~\cite{sid-isr1988},
-%and all arclength derivatives are computed with Fourier differentiation.
-%In addition to computing the shear stress, we also compute the vorticity
-%in the fluid bulk.  The vorticity is particularly insightful since it is
-%identical to the shear stress on no-slip boundaries.  Therefore, by
-%computing the vorticity, we are able to identify regions where the
-%erosion rate will be fast or slow (Fig.~\ref{fig:50bodies}).
+with an upsampled trapezoid rule to assist with visualizing the effect of erosion in porous media.
 
@@
 
-For these porous network simulations, it is essential to resolve the nonlocal effects between the different bodies.
-BIEs naturally resolve these interactions, and they have been used extensively to simulate viscous fluids in complex geometries, including porous media flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.
-Common challenges of a BIE formulation include developing efficient preconditioners for the discretized system and numerical difficulties associated with nearly touching bodies.
-In this work, we consider geometries requiring $\mathcal{O}(100)$ GMRES iterations, so that preconditioners are not necessary.
-In future work, we will address mobile bodies for which near contacts may necessitate the preconditoners.
-Similarly, near-singular schemes will not be necessary due to the fact that the spacing between receding bodies of fixed position always grows in time.
-Again, the future consideration of mobile bodies may necessitate these near-singular schemes.
-
-Possible preconditioners include
-multigrid~\cite{qua-bir2015a} and the inverse fast multipole
-method~\cite{qua-cou-dar2018, cou-pou-dar2017}, but the results
-presented in this work require no more than $\mathcal{O}(100)$ GMRES
-iterations which is too small to make preconditioners for BIEs
-effective; preconditioners will be considered in future work when many
-more grains are eroding and being transported by the flow.  
-To address the nearly-singular integrands, we use the fact that the grains are
-eroding and not moving, so their separation increases with time.
-Therefore, in this work, we apply an upsampling scheme, but in future
-work, we will require a near-singular integration
-scheme~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
+For these porous network simulations, it is essential to resolve the
+nonlocal effects between the different bodies.  BIEs naturally resolve
+these interactions, and they have been used extensively to simulate
+viscous fluids in complex geometries, including porous media
+flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.  Common challenges
+of a BIE formulation include developing efficient preconditioners for
+the discretized system and numerical difficulties associated with nearly
+touching bodies. In this work, we consider geometries requiring
+$\mathcal{O}(100)$ GMRES iterations, so that preconditioners are not
+necessary. In future work, we will address mobile bodies for which near
+contacts may necessitate preconditoners~\cite{qua-bir2015a,
+qua-cou-dar2018, cou-pou-dar2017}. Similarly, near-singular schemes will
+not be necessary due to the fact that the spacing between receding
+bodies of fixed position always grows in time. Again, the future
+consideration of mobile bodies may necessitate near-singular
+schemes~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
 hel-oja2008a, bea-lai2001}.
@@
 fluid viscosity.   
-The constant of proportionality only sets the time scale, so we have set
+The constant of proportionality of the erosion law only sets the time scale, so we have set
 $\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.  For
@@
 of $[-3,3] \times [-1,1]$, and we impose the Hagen-Poiseuille flow
-\begin{align*}
+\begin{align}
   \UU(\xx) = \umax (1-y^2,0), \quad \xx \in \Gamma,
-\end{align*}
+\end{align}
 where $U$ sets the maximum of the imposed Poiseuille flow. Often, we
@@
 computed.  Finally, in Section~\ref{sec:thetaL}, we describe how corners
-in the geometry are avoided and perform a change of coordinates to treat
+in the bodies are avoided and perform a change of coordinates to treat
 a stiff term.
@@
 where  $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
-$\ell^{th}$ grainy, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.
+$\ell^{th}$ grain, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.
 Then, the solution of~\eqref{eqn:stokes} is
@@
 This BIE formulation requires that $\bd\Omega$ is smooth.
-Unfortunately, smoothness is not guaranteed erosion since corners
+Unfortunately, smoothness is not guaranteed by erosion since corners
 develop at locations where the shear stress vanishes.  One option is to
@@
 ser-rok2016, hel2011, gil-hao-mar2014, bre2012}, but these methods
-require the corner's location, or a non-uniform spaced mesh, or are
+require the corner's location, a non-uniform spaced mesh, or are
 ill-conditioned.  Instead, make a slight modification to the erosion
@@
 to $\xx_0 \in \bd\Omega$.  The limiting value is
-\begin{align*}
+\begin{align}
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}\sigma_\DD(\xx) =
   J[\eeta](\xx_0) + \ssigma^\DD(\xx_0), \quad \xx_0 \in \bd\Omega,
-\end{align*} 
+\end{align} 
 where
@@
 Section~\ref{sec:timeStepping}, a time stepping method for evolving the
-interface according to equations~\eqref{eqn:Levo1}
-and~\eqref{eqn:thetaevo1} is described.
+interface according to equations~\eqref{eqn:Levo1}--\eqref{eq:xsurf}
+are described.
 
@@
 $\xx_j$, and
-\begin{align*}
+\begin{align}
   K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
       \frac{\rr \otimes \rr}{\rho^2},
-\end{align*}
+\end{align}
 where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the
@@
 replaced with the limiting value of the double-layer potential
-\begin{align*}
+\begin{align}
   D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)),
-\end{align*}
+\end{align}
 where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
@@
 also discretized with the trapezoid rule.  Applying this discretization
-strategy to~\eqref{eqn:completed_BIE}, the dense linear system that
-needs to be solved is
+strategy to~\eqref{eqn:completed_BIE}, the dense linear system is solved is
 \begin{equation}
@@
 guarantees that the numerical solutions converges to the true solution
-with spectral accuracy.
+with spectral accuracy~\cite{tre-wei2014}.
 
@@
 double-layer potential~\eqref{eqn:shearStressDLP} is 
-\begin{align*}
+\begin{equation}
+\begin{aligned}
   K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
@@
   \right).
-\end{align*}
+\end{aligned}
+\end{equation}
 This kernel has a singularity that is asymptotic to $\bigO(\rho^{-2})$
@@
 double-layer potential is equivalent to
-\begin{align*}
+\begin{align}
   \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
       (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
-\end{align*}
+\end{align}
 This expression has a singularity that is asymptotic to
@@
 Meanwhile, $\NLterm$, represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
-Since the local shear stress depends on interactions between bodies, $\NLterm$ is both a nonlinear and nonlocal.
+Since the local shear stress depends on interactions between bodies, $\NLterm$ is both nonlinear and nonlocal.
 
@@
 In spectral space,~\eqref{eqn:thetaevo2} produces the system of ODEs
-\begin{align*}
+\begin{align}
 \tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \widehat{\NLterm}_k,
 \qquad k=-N_\iin/2,\ldots,N_\iin/2-1\, .
-\end{align*}
+\end{align}
 These ODEs can be simplified by applying the integrating factor
@@
 We therefore insert~\eqref{eq:mu12d} into~\eqref{eq:th12d} and solve for $\theta^{(n+1/2)}$, giving
+\todo[inline]{are we solving for $\theta$ or $\hat{\theta}_k?$.}
 \begin{align}
@@
 We must eventually compute the geometry at step $n+1$, and so we insert~\eqref{eq:mu1d} into~\eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
+\todo[inline]{are we solving for $\theta$ or $\hat{\theta}_k?$.}
 \begin{align}
@@
 and drag (Section~\ref{sec:drag}).  Once
-equation~\eqref{eqn:completed_DLP} is solved, the vorticity, pressure,
-and drag can be computed at arbitrary target points.  For target points
+equation~\eqref{eqn:completed_DLP} is solved, the vorticity and pressure
+will be computed at points both inside the fluid bulk and on the
+along individual bodies, and then the drag of individual bodies will be computed.  For target points
 in the fluid domain, the integrands of the layer potentials are periodic
@@
 Next, the vorticity due to the Stokeslet is
-\begin{align*}
+\begin{align}
   \omega^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
     \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2},
-\end{align*}
+\end{align}
 and the vorticity of a rotlet is zero.  Therefore, the vorticity at $\xx
 \in \Omega$ is
-\begin{align*}
+\begin{align}
   \omega(\xx) = \omega^\DD(\xx) + \omega^S(\xx).
-\end{align*}
+\end{align}
 
@@
 the double-layer potential for $\xx \in \Omega$ and add the appropriate
-jump if $\xx \in \Gamma$. By taking the Laplacian of the Stokes
-double-layer potential~\eqref{eqn:velocityDLP}, the pressure at $\xx \in
-\Omega$ is
+jump if $\xx \in \Gamma$. The pressure of the double-layer
+potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
 \begin{align}
@@
 \end{align}
-The pressure due to the Stokeslets is
-\begin{align*}
-  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
-\end{align*}
+To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid
+rule with an upsampling scheme described in Section~\ref{sec:NSI}.  The
+pressure due to the Stokeslets is
+\begin{align}
+  p^S(\xx) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
+\end{align}
 and the pressure due to the rotlets is zero.  Therefore, the pressure is
-\begin{align*}
+\begin{align}
   p(\xx) = p^{\DD}(\xx) + p^{S}(\xx), \quad \xx \in \Omega,
-\end{align*}
-To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid
-rule with an upsampling scheme described in Section~\ref{sec:NSI}.
+\end{align}
 
@@
 function and write the pressure as
-\begin{align*}
+\begin{equation}
+\begin{aligned}
   p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
@@
     \quad \xx \in \bd\Omega.
-\end{align*}
+\end{aligned}
+\end{equation}
 Then, identical to how the shear stress is
@@
 of the trapezoid rule deteriorates unless a large number of
-discretization points are used.  We are only interested in computing the
-velocity, vorticity, and pressure to visualize the flow, so it is not
-necessary that we resolve the integrands for arbitrarily close target
-points.
+discretization points are used~\cite{bar2014}.  We are only interested
+in computing the velocity, vorticity, and pressure to visualize the
+flow, so it is not necessary that we resolve the integrands for
+arbitrarily close target points.
 
@@
 potential~\eqref{eqn:layerPotential}, we use the same upsampling rate
-for all target points that are in the same dyadic interval
-(Table~\ref{tbl:upsampling}).  For points that are closer than $5/16$ of
-an arclength from $\bd\Omega$, a value of 0 is simply assigned to
-$\phi$.
+for all target points in dyadic intervals (Table~\ref{tbl:upsampling}).
+For points that are closer than $5/16$ of an arclength from $\bd\Omega$,
+a value of 0 is simply assigned to $\phi$.
 \newcolumntype{V}{>{\centering\arraybackslash}m{4em}}
@@
 
-In future work, upsampling will not be adequate.  For example, if
-eroding bodies are also sedimenting, bodies will come too close to one
-another for upsampling to be sufficient.  Therefore, we plan to
-implement one of several near-singular integration schemes available in
+If eroding bodies are also sedimenting, bodies will come too close to
+one another for upsampling to be sufficient.  Therefore, future work
+will apply one of several near-singular integration schemes available in
 the literature~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
@@
 
-Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times.
-Here, color represents the vorticity of the surrounding flow.
-When evaluated on the boundary, vorticity corresponds to the shear stress and thus the local erosion rate.
-As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it.
-The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points.
+Figure \ref{01bodseq} shows the erosion of a single body, numerically
+simulated with $N_\iin = 1024$ discretization points and shown at three
+evenly spaced times. Here, color represents the vorticity of the
+surrounding flow. When evaluated on the boundary, vorticity corresponds
+to the shear stress and thus the local erosion rate. As seen in the
+left-most snapshot, the body is initially circular and has the strongest
+vorticity at its top and bottom. The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points. 
 At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
@@
 The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes in the simulation.
-As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape that has corners at its front and back --- somewhat reminiscent of an American football.
-Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
-The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0 and 0.5 corresponding to the rear and front stagnation points respectively.
-At early times (yellow curves), the stress varies significantly, with more stress concentrated at the top and bottom of the body.
-However, as erosion reshapes the body, the stress becomes more uniformly distributed over the entire surface (red curves).
-The absolute stress $\atau$ shows slight peaks near the stagnation points as the bodies nears the final stages of erosion (dark red).
+As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape that has corners at its front and back---somewhat reminiscent of an American football.
+Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress,
+$\atau$, is distributed along each of these interfaces. The normalized
+arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0
+and 0.5 corresponding to the rear and front stagnation points
+respectively. At early times (yellow curves), the stress varies
+significantly, with more stress concentrated at the top and bottom of
+the body. However, as erosion reshapes the body, the stress becomes more
+uniformly distributed over the entire surface (red curves). The absolute
+stress $\atau$ shows slight peaks near the stagnation points as the body nears the final stages of erosion (dark red).
 Closer inspection reveals that the stress actually vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow with time.
@@
   \label{eqn:stresslaw}
-  \tau \sim \frac{\mu \umax}{a \log(\ell/a)} \qquad \text{for } a \ll \ell \, .
+  \tau \sim \frac{\mu \umax}{a \log(\ell/a)}, \qquad \text{for } a \ll \ell \, .
 \end{align}
@@
 \begin{align}
-\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, ,
+\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
 \end{align}
@@
 In Fig.~\ref{area_drag}(a) we compare the area measured in our numerical simulation (black curve) against the above scaling law (red dotted curve) with $c_1 = 0.24$ a fit parameter.
-The two agree remarkable well throughout the entire simulation, thus co-validating the simulation and asymptotic results.
+The two agree remarkably well throughout the entire simulation, thus co-validating the simulation and asymptotic results.
 
@@
 \label{dragscaling}
-\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}	\qquad \text{for } a \ll \ell \, .
+\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)},	\qquad \text{for } a \ll \ell \, .
 \end{align}
@@
 
-	These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches the terminal state.
-In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
-In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters, $\eps$ and $\sigma$, to assess how the numerical regularization influences shape.
-In the three cases, we keep $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and 5/1024 respectively.
-Loosely, these values correspond to smoothing over the nearest 20, 10, and 5 grid points respectively.
+	These fixed-area simulations enable us to precisely characterize
+        the changing geometry as it approaches the terminal state. In
+        particular, we measure the aspect ratio of the body (the width
+        to height) and the opening angle of the front/rear corners. In
+        these tests, we keep the spatial resolution fixed, $N_\iin =
+        1024$, and show three different cases of the smoothing
+        parameters, $\eps$ and $\sigma$, to assess how the numerical
+        regularization influences shape. In the three cases, we keep
+        $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and
+        5/1024 respectively. Loosely, these values correspond to
+        smoothing over the nearest 20, 10, and 5 grid points, respectively.
 Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
@@
         rear. This shape is closely related to the drag-minimizing
-        profile found by Pironneau (1973) --- the geometry that
+        profile found by Pironneau (1973)---the geometry that
         minimizes drag in 3D Stokes flow subject to the constraint of
@@
 \begin{align}
-\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})} \, .
-\end{align}
-The velocity and pressure fields depend linearly on $\eeta$ and so this rescaling maintains a {\em fixed} pressure difference across the subdomain $-2 \le x \le 2$.
+\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})}, \quad 
+\llambda \leftarrow \frac{\llambda}{(p_{-} - p_{+})}, \quad 
+\xi \leftarrow \frac{\xi}{(p_{-} - p_{+})}\, .
+\end{align}
+The velocity and pressure fields depend linearly on $\eeta$,
+$\llambda$, and $\xi$, so this rescaling maintains a {\em fixed} pressure difference across the subdomain $-2 \le x \le 2$.
 Since the Stokes equations are linear, the rescaled flow remains a solution to the PDE system (valid to the same order of accuracy).
@@
 
-Briefly, to validate the multi-body simulations with this new
+To validate the multi-body simulations with this new
 fixed-pressure-drop condition, we report a convergence test in Table
@@
 \begin{center}
-\caption{The number of GMRES iterations required to reach a fixed tolerance of 1E-8 in our simulations.
+\caption{The number of GMRES iterations required to reach a fixed
+tolerance of $10^{-}8$ in our simulations.
 The left side shows a case of fixed geometry, 10 circular bodies, with increasing spatial resolution, $N_\iin$, demonstrating that the iteration count is independent of resolution.
@@
 
-Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since this is typically the most expensive step.
-Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
-The iteration count, however, may depend on the number of bodies, as well as other factors such as the shapes of the bodies, their configuration, etc.
-To examine a few of these factors, we show in Table~\ref{itertab} the number of GMRES iterations required to reach a specified tolerance of 1E-8 in several different simulations.
-The left side of the table shows the results for a 10-body simulation, in which we keep the geometry fixed and vary the spatial resolution $N_{\iin}$.
-As seen in the table, the iteration count remains essentially fixed as the resolution increases.
-In the right side of the table, we keep the spatial resolution fixed and vary the number of simulated bodies from 10 to 50.
+Lastly, we want to briefly examine the number of GMRES iterations
+required by our simulations since this is typically the most expensive
+step. Due to our {\em second-kind} boundary integral formulation, we
+expect the number of GMRES iterations to be independent of the spatial
+resolution, $N_{\iin}$. The iteration count, however, may depend on the
+number of bodies, as well as other factors such as the shapes of the
+bodies and their configuration. To examine a few of these factors, we
+show in Table~\ref{itertab} the number of GMRES iterations required to
+reach a specified tolerance of $10^{-8}$ in several different
+simulations. The left side of the table shows the results for a 10-body
+simulation, in which we keep the geometry fixed and vary the spatial
+resolution $N_{\iin}$. As seen in the table, the iteration count remains
+essentially fixed as the resolution increases. In the right side of the
+table, we keep the spatial resolution per body fixed and vary the number of simulated bodies from 10 to 50.
 The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
@@
 With the validation complete, we now discuss the emergent physics of
-multi-body erosion revealed by our simulations.
-We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}).
-Figure~\ref{fig:06bodies} shows the simulated erosion of 6 bodies, each initial circles of various sizes and positions.
-Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerable.
+multi-body erosion revealed by our simulations. We begin with a
+relatively simple case of 6 eroding bodies, as this will allow us to
+identify key principles at work in more complex cases (e.g.~the 50-body
+simulation in Fig.~\ref{fig:50bodies}). Figure~\ref{fig:06bodies} shows
+the simulated erosion of 6 bodies, each initial circles of various sizes
+and positions. Over time, erosion not only diminishes the size of the
+bodies, but also alters their shapes considerably.
 As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable.

### 2018-04-06 docs/methods/erosion_methods.tex
fixed spacing in equations

@@
 \begin{align}
-  \UU(\xx) = \umax (1-y^2,0), \quad \xx \in \Gamma,
+  \UU(\xx) = \umax (1-y^2,0)\, , \quad \xx \in \Gamma\, ,
 \end{align}
@@
   \begin{split}
-  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
+  \mu\Delta \uu &= \grad p\, , \qquad && \xx \in \Omega, \\
   \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
@@
     \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
-    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
+    \eeta(\yy) \, ds_\yy\, , \quad \xx \in \Omega \, ,
     \label{eqn:velocityDLP}
@@
   \quad \text{and} \quad
-  R[\xi_\ell,\cc_\ell] = \frac{\rr^\perp}{\rho^2}\xi_\ell, 
-  \quad \ell=1,\ldots,M,
+  R[\xi_\ell,\cc_\ell] = \frac{\rr^\perp}{\rho^2}\xi_\ell\, , 
+  \quad \ell=1,\ldots,M \, ,
   \label{eqn:stokeslet_rotlet}
@@
     \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
-    \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
+    \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx)\, , \quad \xx \in \Omega \, ,
 \end{align}
@@
       \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
-      \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx) + \NN_0[\eeta](\xx),
-      \quad \xx \in \bd\Omega, 
+      \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx) + \NN_0[\eeta](\xx)\, ,
+      \quad \xx \in \bd\Omega \, , 
       \label{eqn:DLP}\\
-  \llambda_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \eeta(\yy) \, ds_\yy,
-  \quad \ell=1,\ldots,M,
+  \llambda_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \eeta(\yy) \,
+  ds_\yy\, ,
+  \quad \ell=1,\ldots,M \, ,
   \label{eqn:stokeslet} \\
   \xi_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \yy^\perp \cdot \eeta(\yy)
-  \, ds_\yy, \quad \ell=1,\ldots,M.
+  \, ds_\yy\, , \quad \ell=1,\ldots,M \, .
   \label{eqn:rotlet}
@@
     8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right) \eeta(\yy) ds_\yy.
+  \right) \eeta(\yy) \, ds_\yy \, .
   \end{aligned}
@@
   \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}\sigma_\DD(\xx) =
-  J[\eeta](\xx_0) + \ssigma^\DD(\xx_0), \quad \xx_0 \in \bd\Omega,
+  J[\eeta](\xx_0) + \ssigma^\DD(\xx_0)\, , \quad \xx_0 \in \bd\Omega \, ,
 \end{align} 
@@
     s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
-  \end{array}\right].
+  \end{array}\right] \, .
   \label{eqn:shearStressJump}
@@
     \frac{\xi_\ell}{\rho^4} \left(\rr \otimes \rr^\perp + 
-    \rr^\perp \otimes \rr \right).
+    \rr^\perp \otimes \rr \right) \, .
   \end{aligned}
@@
   \tau = -2 \left(J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) + 
-    \ssigma^S(\xx_0) + \ssigma^R(\xx_0)\right) \nn \cdot \ss.
+    \ssigma^S(\xx_0) + \ssigma^R(\xx_0)\right) \nn \cdot \ss \, .
   \label{eqn:shearStressLP}
@@
   \label{eqn:Vn}
-  \Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1 \right).
+  \Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1
+  \right) \, .
 \end{align}
@@
 \pderiv{\theta}{t} &= \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} +
-\thalpha \Vs \right).
+\thalpha \Vs \right) \, .
 \end{align}
@@
   \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
-      \Delta s_{j}, \quad i=1,\ldots,N,
+      \Delta s_{j}\, , \quad i=1,\ldots,N \, ,
   \label{eqn:trapDLP}
@@
   K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
-      \frac{\rr \otimes \rr}{\rho^2},
+      \frac{\rr \otimes \rr}{\rho^2} \, ,
 \end{align}
@@
 \begin{align}
-  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)),
+  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)) \, ,
 \end{align}
@@
       +\sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
-      \nn(\xx_j))\eeta(\xx_j), \\
+      \nn(\xx_j))\eeta(\xx_j) \, , \\
     \llambda_\ell &= \sum_{\xx_j \in \gamma_\ell} \eeta(\xx_j) 
-      \Delta s_j, \\ 
+      \Delta s_j \, , \\ 
     \mu_\ell &= \sum_{\xx_j \in \gamma_\ell}
-      {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j,
+      {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j \, ,
   \end{aligned}
@@
     8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right).
+  \right) \, .
 \end{aligned}
@@
   \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
-      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
+      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}\, , \quad \xx \in \bd\Omega \, .
 \end{align}
@@
   \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
-    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
+    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j \, ,
   \label{eqn:stressOddEven}
@@
 \left(\pderiv{\theta}{\alpha} - 1 \right), \\
-& \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig}.
+& \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig} \, .
 \end{align}
@@
 %\label{eq:M}
-& \Mterm = - 2 \pi \mean{\thalpha \Vnsig}, \\
+& \Mterm = - 2 \pi \mean{\thalpha \Vnsig} \, , \\
 %\label{eq:N}
 & \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha
-\Vssig \right), \\
+\Vssig \right) \, , \\
 %\label{eq:elfun}
@@
 \label{eqn:Levo2}
-& \tderiv{L}{t} = \Mterm, \\
+& \tderiv{L}{t} = \Mterm \, , \\
 \label{eqn:thetaevo2}
-& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm.
+& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm \,.
 \end{align}
@@
 \begin{align}
-\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \widehat{\NLterm}_k,
+\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k =
+\widehat{\NLterm}_k\, ,
 \qquad k=-N_\iin/2,\ldots,N_\iin/2-1\, .
@@
 \label{eqn:Levo3}
-& \tderiv{L}{t} = \Mterm, \\
+& \tderiv{L}{t} = \Mterm \, , \\
 \label{eqn:thetaevo3}
 & \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \widehat{\NLterm}_k \, ,
-\qquad k = -N_\iin/2, \ldots, N_\iin/2 -1.
+\qquad k = -N_\iin/2, \ldots, N_\iin/2 -1 \, .
 \end{align}
@@
 & \mu_k^{(n+1/2)} = \mu_k^{(n)} \exp \left( \eps k^2 \frac{\Dt}{2}
-\zeta^{(n)} \right), \\
+\zeta^{(n)} \right) \, , \\
 \label{eq:L12d}
-& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)}, \\
+& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)} \, , \\
 \label{eq:th12d}
 & \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \mu_k^{(n)} \thhat_k^{(n)}}{\Dt/2} 
-= \mu_k^{(n)} \hat{\NLterm}_k^{(n)},
-\end{align}
-where the superscript indicates the time step.
-At the next stage of RK2 it will be necessary to evaluate derivates at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the body shapes must be known.
+= \mu_k^{(n)} \hat{\NLterm}_k^{(n)} \, ,
+\end{align}
+where the superscript indicates the time step. At the next stage of RK2
+it will be necessary to evaluate derivatives at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the body shapes must be known.
 We therefore insert~\eqref{eq:mu12d} into~\eqref{eq:th12d} and solve for $\theta^{(n+1/2)}$, giving
@@
 & \mu_k^{(n+1)} = \mu_k^{(n)} \exp \left( \eps k^2 {\Dt} \,
-\zeta^{(n+1/2)} \right), \\
+\zeta^{(n+1/2)} \right) \, , \\
 \label{eq:L1d}
-& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)}, \\
+& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)} \, , \\
 \label{eq:th1d}
 & \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \mu_k^{(n)} \thhat_k^{(n)}}{\Dt} =
-\mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}.
+\mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)} \, .
 \end{align}
@@
 \begin{align}
-\thhat_k^{(n+1)} =  \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) + \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
+\thhat_k^{(n+1)} =  \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt
+\elfun^{(n+1/2)} \right) + \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left(
+- \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)}
+\right) \right) \, .
 \end{align}
@@
     \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}
-    (\rr \cdot \eeta) ds_{\yy}.
+    (\rr \cdot \eeta) \, ds_{\yy}\, .
   \label{eqn:vorticityDLP}
@@
   \omega^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
-    \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2},
+    \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2}\, ,
 \end{align}
@@
 \begin{align}
-  \omega(\xx) = \omega^\DD(\xx) + \omega^S(\xx).
+  \omega(\xx) = \omega^\DD(\xx) + \omega^S(\xx)\, .
 \end{align}
@@
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot \eeta(\yy) \,ds_\yy.
+    \nn \cdot \eeta(\yy) \,ds_\yy \, .
     \label{eqn:pressureDLP}
@@
 \begin{align}
-  p^S(\xx) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
+  p^S(\xx) = \sum_{\ell=1}^{M}\frac{\rr \cdot
+  \llambda_\ell}{2\pi\rho^2}\, ,
 \end{align}
@@
 \begin{align}
-  p(\xx) = p^{\DD}(\xx) + p^{S}(\xx), \quad \xx \in \Omega,
+  p(\xx) = p^{\DD}(\xx) + p^{S}(\xx)\, , \quad \xx \in \Omega \, ,
 \end{align}
@@
   p(\xx)= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
-              p^{S}(\xx), \quad \xx \in \bd\Omega.
+              p^{S}(\xx)\, , \quad \xx \in \bd\Omega \, .
   \label{eqn:pressureJump}
@@
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
-    \quad \xx \in \bd\Omega.
+    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy\, , 
+    \quad \xx \in \bd\Omega\, .
 \end{aligned}
@@
 \begin{align}
-\FFD = \int_{\gamma_\ell} p \nn + \tau \ss \,ds.
+\FFD = \int_{\gamma_\ell} p \nn + \tau \ss \,ds\, .
 \label{eqn:drag}
@@
 \begin{align}
-  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy.
+  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) \, ds_\yy\, .
   \label{eqn:genericLP}
@@
 \begin{align}
-  \phi(\xx) = \sum_{j=1}^N q_j K(\xx,\yy_j),
+  \phi(\xx) = \sum_{j=1}^N q_j K(\xx,\yy_j)\, ,
   \label{eqn:layerPotential}
@@
 
-Figure \ref{01bodseq} shows the erosion of a single body, numerically
+Figure~\ref{01bodseq} shows the erosion of a single body, numerically
 simulated with $N_\iin = 1024$ discretization points and shown at three
@@
   \label{eqn:stresslaw}
-  \tau \sim \frac{\mu \umax}{a \log(\ell/a)}, \qquad \text{for } a \ll \ell \, .
+  \tau \sim \frac{\mu \umax}{a \log(\ell/a)}\, , \qquad \text{for } a \ll \ell \, .
 \end{align}
@@
 
-	As the body shrinks in accordance with \eqref{area_predict}, the drag that it exerts decreases at a related rate, offering a second check on our numerics.
+	As the body shrinks in accordance with~\eqref{area_predict}, the drag that it exerts decreases at a related rate, offering a second check on our numerics.
 In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it changes in time (black curve).
-The drag is calculated using \eqref{eqn:drag} and, in the context of slender-body theory, this should be interpreted as the drag-per-unit-span.
+The drag is calculated using~\eqref{eqn:drag} and, in the context of slender-body theory, this should be interpreted as the drag-per-unit-span.
 As seen in the figure, $F_D$ decreases gradually at first, then abruptly drops to zero in the final moments of the body's existence.
 Though it may seem peculiar, the sudden drop is consistent with the 2D Stokes law in which drag vanishes {\em logarithmically} with body size.
-Additionally, \eqref{eqn:drag} permits us to calculate the separate contributions of pressure and viscous drag, which we show by the blue and green curves in Fig.~\ref{area_drag}(b) respectively.
+Additionally,~\eqref{eqn:drag} permits us to calculate the separate contributions of pressure and viscous drag, which we show by the blue and green curves in Fig.~\ref{area_drag}(b) respectively.
 Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag.
 As the body erodes and assumes a more slender form, though, the pressure drag decreases more rapidly, leaving viscous drag to dominate.
-This behavior is associated with convergence to a drag-minimizing profile, which is discussed in Section \ref{LimitingShape}.
+This behavior is associated with convergence to a drag-minimizing profile, which is discussed in Section~\ref{LimitingShape}.
 
@@
 \label{dragscaling}
-\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)},	\qquad \text{for } a \ll \ell \, .
+\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}\, ,	\qquad \text{for } a \ll \ell \, .
 \end{align}
@@
 This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$ and odd symmetry about the horizontal axis, $f(0) = f''(0) = 0$.
-For arbitrary opening angle, ODE \eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
+For arbitrary opening angle, ODE~\eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
 We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and therefore set $\lambda = 2$.
-The odd-symmetric solution to \eqref{fODE} corresponding to $\lambda=2$ is
+The odd-symmetric solution to~\eqref{fODE} corresponding to $\lambda=2$ is
 \begin{align}
@@
 \end{align}
-This nonlinear equation has solution $\thb \approx 129^\circ$, which implies that the the uniform-stress wedge has an opening angle of $\oangle \approx 102^\circ$.
+This nonlinear equation has solution $\thb \approx 129^\circ$, which implies that the uniform-stress wedge has an opening angle of $\oangle \approx 102^\circ$.
 % Pozrikidis page 239: symmetric flow.
@@
 
-We now aim to measure the opening angles formed in the numerical simulations to compare against the above prediction.
-However, Section \ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
+We now aim to measure the opening angles formed in the numerical
+simulations to compare against the above prediction.
+However, Section~\ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
 To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
@@
 
-	Next, we aim to measure the opening angle of the front/rear corner.
-Since these simulated bodies are actually smooth on a fine scale, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points.
-To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5).
-We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there.
-Although this procedure is subject to some uncertainty (to be examined below), we have found it to give robust angle measurements.
-Figure \ref{fig:arangle}(b) shows the opening angle, $\beta$, as it varies in time for the three cases of smoothing parameters.
-For the initially circular geometry, our procedure yields the correct opening angle of $180^{\circ}$, i.e.~a flat front face.
-As time proceeds, erosion carves a sharper corner and $\beta$ decreases monotonically.
-Here, the three cases of smoothing parameters are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing than is the aspect ratio.
-The curves nevertheless show convergence as $\eps, \sigma \to 0$.
-In the finest simulation ($\eps = \sigma = 5/1024$), $\beta$ converges to the value $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.
+	Next, we aim to measure the opening angle of the front/rear
+        corner. Since these simulated bodies are actually smooth on a
+        fine scale, we must have a procedure to estimate the apparent
+        angle that results from the high (but finite) curvature at the
+        stagnation points. To this end, we fit the tangent angle
+        $\theta(\alpha)$ with a 7th-degree polynomial over a region
+        excluding the stagnation points ($\alpha = 0$ and 0.5). We then
+        extrapolate the polynomial to the stagnation points, which gives
+        an estimate of the angle there. Although this procedure is
+        subject to some uncertainty (to be examined below), we have
+        found it to give robust angle measurements.
+        Figure~\ref{fig:arangle}(b) shows the opening angle, $\beta$, as
+        it varies in time for the three cases of smoothing parameters.
+        For the initially circular geometry, our procedure yields the
+        correct opening angle of $180^{\circ}$, i.e.~a flat front face.
+        As time proceeds, erosion carves a sharper corner and $\beta$
+        decreases monotonically. Here, the three cases of smoothing
+        parameters are more easily distinguished, implying that the
+        opening angle is more sensitive to the level of numerical
+        smoothing than is the aspect ratio. The curves nevertheless show
+        convergence as $\eps, \sigma \to 0$. In the finest simulation
+        ($\eps = \sigma = 5/1024$), $\beta$ converges to the value
+        $102^{\circ}$, which agrees precisely with the analytical
+        prediction from Section~\ref{LimitingShape}.
 
@@
         curvature must be offset by slight variations in $\Vn$ for
-        self-similar reduction~\cite{pir1973, mit-spa2016}.
-Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well.
-Therefore, the shape observed in our simulation is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape.
-How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{shrink_intface}(b).
+        self-similar reduction~\cite{pir1973, mit-spa2016}. Pironneau's
+        argument that the drag-minimizing form has constant surface
+        stress applies to 2D as well. Therefore, the shape observed in
+        our simulation is approximately the form that minimizes drag
+        subject to fixed area, i.e.~the 2D counterpart to Pironneau's
+        shape. How close this shape is to the true drag-minimizer is
+        related to how close the stress distributions are to uniform, as
+        can be seen in Fig.~\ref{shrink_intface}(b).
 
@@
 
-As a final validation, we now verify that our method converges with the expected second-order accuracy in time.
-For this, we run the same single-body simulation shown in Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
+As a final validation, we now verify that our method converges with the
+expected second-order accuracy in time. For this, we run the same
+single-body simulation shown in Figs.~\ref{01bodseq} and~\ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
 This stopping time is 56\% of the vanishing time, and was selected so that the body will have eroded substantially but is not small enough to compromise accuracy (due to the stress diverging).
 We assess error by measuring the $L^2$-difference in the body shape obtained from simulations of successive resolution, with $\Delta t$ halved at each stage.
-In Table \ref{convtab}, we report these errors along with the order of accuracy, obtained by Richardson-extrapolation-type calculations.
+In Table~\ref{convtab}, we report these errors along with the order of accuracy, obtained by Richardson-extrapolation-type calculations.
 The table confirms that our method converges with expected second-order accuracy.
@@
 \begin{align}
-\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})}, \quad 
-\llambda \leftarrow \frac{\llambda}{(p_{-} - p_{+})}, \quad 
+\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})}\, , \quad 
+\llambda \leftarrow \frac{\llambda}{(p_{-} - p_{+})}\, , \quad 
 \xi \leftarrow \frac{\xi}{(p_{-} - p_{+})}\, .
@@
 To validate the multi-body simulations with this new
-fixed-pressure-drop condition, we report a convergence test in Table
-\ref{convtab}. In this test, we simulate the erosion of 20 bodies to a
+fixed-pressure-drop condition, we report a convergence test in
+Table~\ref{convtab2}. In this test, we simulate the erosion of 20 bodies to a
 stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of
@@
 \vspace{0.3 pc}
-\label{convtab}
+\label{convtab2}
 \begin{tabular}{l l l l}
@@
 
-Next, Figure \ref{fig:mbodyplots}(b) shows how the flow rate, $\umax$, changes in time as a result of fixing the pressure drop across the cell.
+Next, Figure~\ref{fig:mbodyplots}(b) shows how the flow rate, $\umax$, changes in time as a result of fixing the pressure drop across the cell.
 Notice that, in this figure, the vertical axis is logarithmic.

### 2018-04-07 docs/methods/erosion_methods.tex
fixed bibliography

@@
 viscous fluids in complex geometries, including porous media
-flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.  Common challenges
+flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.  Common challenges
 of a BIE formulation include developing efficient preconditioners for

### 2018-04-08 docs/methods/erosion_methods.tex
worked on conclusion .... suddenly kids need to discuss future odd squad seasons they plan to write

@@
 Stokesian erosion in a porous media.  By using a BIE formulation of the
-fluid equations and a {\thL}, we achieve spectral accuracy in space and
-second-order accuracy in time.  In addition, the non-negligible
-interactions between different bodies are accurately resolved.
+fluid equations and a {\thL} change of variables, we achieve spectral
+accuracy in space and second-order accuracy in time.  In addition, the
+non-negligible interactions between different bodies are accurately
+resolved.  Using slender body theory and flow past a wedge, the method
+is verified against analytical results for the area, opening angle, and
+total drag of a single eroding body.  Then, for multi-body erosion, a
+more realistic pressure drop boundary condition, and we compute the area
+fraction, flow rate, and total drag in the channel.
 

### 2018-04-08 docs/methods/erosion_methods.tex
wrote first round of conclusion

--- 2018-04-07 docs/methods/erosion_methods.tex
@@
 \section{Conclusions\label{s:conclusions}}
-We have developed a numerical framework for simulating two-dimensional
-Stokesian erosion in a porous media.  By using a BIE formulation of the
-fluid equations and a {\thL}, we achieve spectral accuracy in space and
-second-order accuracy in time.  In addition, the non-negligible
-interactions between different bodies are accurately resolved.
-
-\todo[inline]{Here in revising}
+We have combined two accurate and stable numerical methods to simulate
+two-dimensional viscous erosion in a porous medium.  First, a BIE
+formulation of the incompressible Stokes equations discretizes only the
+boundary of the bodies and resolves their non-negligible interactions.
+Second, the bodies are evolved with the so-called {\thL} variables to
+avoid tangling and distortion of the mesh.  The resulting numerical
+method is spectral in space, second-order in time, and is accelerated
+with the fast multipole method.
+
+Using slender body theory and flow past a wedge, the method is verified
+against analytical results for the area, opening angle, and total drag
+of a single eroding body.  Then, for multi-body erosion with a realistic
+pressure drop boundary condition, we compute the area fraction, flow
+rate, and total drag across a channel.  We observe that erosion leads to
+channelization, and this reduces the resistance more than would be
+expected if the area fraction were reduced by simply scaling down the
+size of the bodies.  This indicates that the area fraction can not fully
+characterize flow in eroding porous media since the interactions between
+the bodies plays a role in the resistance.
 

### 2018-04-09 docs/methods/erosion_methods.tex
NM

@@
 to human-scale features and patterns~\cite{daerr2003erosion}. Though
-less visible, these same forces are at work at the very smallest scales,
+less visible, these same forces are working at the very smallest scales,
 slowly deteriorating the individual constituents of porous media
@@
 develop numerical methods to simulate fluid-mechanical erosion of
-multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and bio-fluid applications.
+multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
 
@@
 during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013,
-hewett2017evolution, moore2017riemann}, and a similar feedback occurs in
+hewett2017evolution, moore2017riemann}; a similar feedback occurs in
 the related processes of dissolution and melting~\cite{Huang2015,
@@
 The interface tracking issues are addressed in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect the interface dynamics; second, we introduce a curvature-penalizing term into the normal interface velocity to suppress high-frequency oscillations associated with nearly singular curvature.
-Furthermore, the interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.
+The interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.
 
@@
 
-The most closely related work to ours is Mitchell \& Spagnolie \cite{mit-spa2016}, who developed methods to simulate viscous erosion in three dimensions.
+In closely related work, Mitchell \& Spagnolie developed methods to simulate viscous erosion in three dimensions  \cite{mit-spa2016}.
 That work employed a traction integral equation to solve for the surrounding Stokes flow.

### 2018-04-09 docs/methods/erosion_methods.tex
NM

@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a
-range of scales found in nature, from large geological
-formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down
-to human-scale features and patterns~\cite{daerr2003erosion}. Though
-less visible, these same forces are working at the very smallest scales,
-slowly deteriorating the individual constituents of porous media
-(e.g.~solid, sand, or clay) or biological structures like plaque and
-biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such applications, we
-develop numerical methods to simulate fluid-mechanical erosion of
-multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
-
-Recent work in the high-Reynolds number regime has highlighted the
-importance of the feedback between flow and morphology that occurs
-during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013,
-hewett2017evolution, moore2017riemann}; a similar feedback occurs in
-the related processes of dissolution and melting~\cite{Huang2015,
-kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion,
-hewett2017pear, claudin2017dissolution}. In such cases, the flow alters
-the shape of the immersed structures, which in turn modifies the
-surrounding flow, and so on. Collectively, such processes have been
-referred to as `sculpting with flow'~\cite{ristroph2018sculpting}. From
-this viewpoint, the example of an eroding porous medium presents new
-opportunities and challenges. For example, the medium itself is composed
-of many solid constituents, so multi-body interactions, especially close
-interactions, must be considered.
-%Second, the long-range interactions
-%facilitated by Stokes flow makes all the interactions between bodies important.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}.
+Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
+Motivated by such examples, we develop in this paper numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
+
+Recent work in the high-Reynolds number regime has highlighted the importance of feedback between flow and morphology that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, as well as related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion,
+hewett2017pear, claudin2017dissolution}. 
+In these cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on.
+Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}.
+From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
+For example, the medium itself is composed of many solid constituents, so multi-body interactions, especially close interactions, must be considered.
 
@@
 
-% Point out complex shapes with sharp features, maybe polygonal.
-% Point out channel structures develop.
-
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 %which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
-
-% Other possible refs for erosion: mit-spa2016, lachaussee2018competitive, lopez2018cfd
-% Other possible refs for dissolution/melting: yuan2017dynamics, 
-% Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.
-% Land formations, geophysical features, structures, patterns
-
-% For groundwater flow, Darcy's law is often used, but this does not resolve the pore structure and assumes a homogeneous geometry which is often not valid.
-Instead, we use the incompressible Stokes equations as the governing fluid equations, and the individual pores are resolved which results in a complex multiply-connected geometry.
 

### 2018-04-09 docs/methods/erosion_methods.tex
NM

@@
 Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}.
-Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
+Though less visible, these same forces work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
 Motivated by such examples, we develop in this paper numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
 
-Recent work in the high-Reynolds number regime has highlighted the importance of feedback between flow and morphology that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, as well as related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion,
-hewett2017pear, claudin2017dissolution}. 
-In these cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on.
-Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}.
+Recent work in the high-Reynolds number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
+Such processes of `sculpting with flow' \cite{ristroph2018sculpting} have been examined in the context of a single body \cite{ris-moo-chi-she-zha2012} and, more recently, multiple bodies whose shape evolution is coupled through the flow \cite{hewett2017evolution, moore2017riemann}.
 From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
-For example, the medium itself is composed of many solid constituents, so multi-body interactions, especially close interactions, must be considered.
-
-The methods developed here will allow us to simulate the erosion of many
-bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50
-bodies (of randomly assigned initial sizes and positions). Here, the
-erosion of solid material arises from the mechanical stress induced by
-the surrounding flow. In particular, we take the local rate of erosion
-to be proportional to the magnitude of the shear stress---a law that has
-been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
-As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size
-of the bodies, but also alters their shapes considerably. Notice, in
-particular, that many bodies develop corner-like features and nearly
-flat faces, with straight channels intervening between them. In the
-figure, color represents the vorticity of the surrounding flow, which
-reduces to shear on solid boundaries and thus provides a convenient tool
-for visualizing local erosion rates.
+First, since the medium is composed of many individual constituents, multi-body interactions must be considered.
+Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than they would be in any other regime.
+
+The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
+Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
+In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress---a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
+As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
+Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them.
+In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.
 

### 2018-04-09 docs/methods/erosion_methods.tex
NM

@@
 \paragraph{Limitations}
-We make two fundamental design choices in our simulation: first, we restrict attention to
-two spatial dimensions, and second the bodies are considered immobile
-(i.e.~fixed to their initial locations). The restriction to two
-dimensions allows us to simulate the erosion of many bodies (up to $50$
-in this manuscript) with high resolution, giving us the ability to
-accurately characterize the erosion of a porous medium. While BIEs are
-available in three dimensions, the extra computational cost limits the
-number of bodies that could be practically simulated, making
-porous-medium simulations less feasible. The second assumption of
-immobile bodies affords a simple framework to study the effects of
-erosion in isolation. While other effects, such as sedimentation or
-transport, undoubtedly play a role in real applications, these effects
-would introduce additional complexity, both conceptually and
-numerically. We therefore defer the study of these effects to future
-work.
+We make two fundamental design choices in our simulation: first, we restrict attention to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
+The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium.
+While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
+The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
+While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
+We therefore defer the study of these effects to future work.
 
@@
 
-In closely related work, Mitchell \& Spagnolie developed methods to simulate viscous erosion in three dimensions  \cite{mit-spa2016}.
-That work employed a traction integral equation to solve for the surrounding Stokes flow.
+In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}.
+Their formulation was flexible enough to simulate a {\em mobile} body that erodes in various background flows (uniform flow, shear flow, etc.).
+An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.
+
+Since our aim is to simulate porous-medium erosion, we will consider {\em many} bodies and, further,  we choose to fix these bodies to their initial locations.
+Thus, instead of a single, mobile body, we will consider multiple, immobile bodies.
+Rather than the traction-formulation, we will employ a standard double-layer formulation which will easily allow us to compute bulk quantities such as pressure and vorticity as a post-processing step.
+
+%That work employed a traction integral equation to solve for the surrounding Stokes flow.
 The advantage to this formulation is that it immediately provides the shear stress required to evolve boundaries.

### 2018-04-09 docs/methods/erosion_methods.tex
NM

@@
 
-Recent work in the high-Reynolds number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
@@
 First, since the medium is composed of many individual constituents, multi-body interactions must be considered.
-Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than they would be in any other regime.
+Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than in any other regime.
 
@@
 An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.
-
+%
 Since our aim is to simulate porous-medium erosion, we will consider {\em many} bodies and, further,  we choose to fix these bodies to their initial locations.

### 2018-04-09 docs/methods/erosion_methods.tex
NM

@@
 
-\title{A boundary-integral framework to simulate \\ the viscous erosion of a porous medium}
+\title{A boundary-integral framework to simulate \\ viscous erosion of a porous medium}
 
@@
 Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}.
-Though less visible, these same forces work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by such examples, we develop in this paper numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
-
-Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
+Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
+
+Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
@@
 An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.
-%
-Since our aim is to simulate porous-medium erosion, we will consider {\em many} bodies and, further,  we choose to fix these bodies to their initial locations.
-Thus, instead of a single, mobile body, we will consider multiple, immobile bodies.
-Rather than the traction-formulation, we will employ a standard double-layer formulation which will easily allow us to compute bulk quantities such as pressure and vorticity as a post-processing step.
-
-%That work employed a traction integral equation to solve for the surrounding Stokes flow.
-The advantage to this formulation is that it immediately provides the shear stress required to evolve boundaries.
-However, the standard double-layer potential used here will allow us to compute certain quantities in the fluid bulk, such as vorticity and pressure, that will facilitate our understanding of the erosion process.
-Furthermore, our primary aim is to simulate the erosion of multiple bodies held fixed within a porous network, whereas Mitchell \& Spagnolie simulated a single eroding body that is mobile.
+In the present work, we aim to simulate the erosion of a porous medium and further we choose to fix the bodies to their initial locations.
+Thus, instead than simulating a single, mobile body as in \cite{mit-spa2016}, we will simulate the erosion of many, immobile bodies.
+Furthermore, we will employ a standard double-layer formulation, as it allows us to easily calculate bulk quantities such as vorticity, pressure, and velocity in a post-processing step.
 

### 2018-04-09 docs/methods/erosion_methods.tex
NM

@@
 it will be necessary to evaluate derivatives at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the body shapes must be known.
-We therefore insert~\eqref{eq:mu12d} into~\eqref{eq:th12d} and solve for $\theta^{(n+1/2)}$, giving
-\todo[inline]{are we solving for $\theta$ or $\hat{\theta}_k?$.}
+We therefore insert~\eqref{eq:mu12d} into~\eqref{eq:th12d} and solve for $\thhat_k^{(n+1/2)}$, giving
 \begin{align}
@@
 \end{align}
-We must eventually compute the geometry at step $n+1$, and so we insert~\eqref{eq:mu1d} into~\eqref{eq:th1d} and solve for $\theta^{(n+1)}$, giving
-\todo[inline]{are we solving for $\theta$ or $\hat{\theta}_k?$.}
+We must eventually compute the geometry at step $n+1$, and so we insert~\eqref{eq:mu1d} into~\eqref{eq:th1d} and solve for $\thhat_k^{(n+1)}$, giving
 \begin{align}

### 2018-04-09 docs/methods/erosion_methods.tex
parsed the tex code so there's no line breaks

@@
 To evolve the individual grains under shear-driven erosion, we regularize via curvature-penalization and solve the associated system using the {\thL} formulation.
-This framework allows numerically stable treatment of stiff terms, thus permitting large time
-steps.
+This framework allows numerically stable treatment of stiff terms, thus permitting large time steps.
 The overall accuracy of our method is spectral in space and second-order in time.
@@
 \paragraph{Contributions}
-To perform this simulation of Stokesian erosion of a porous media, two
-fast and accurate methods are employed---one to solve the fluid
-equations and the other to integrate the eroding grains.  The fluid
-equations are reformulated in terms of a boundary integral equation
-(BIE)~\cite{poz1992}.  Since the boundary conditions are Dirichlet, we
-use a double-layer potential formulation so that the resulting BIE is
-second-kind.  This second-kind BIE is discretized with the spectrally
-accurate trapezoid rule~\cite{tre-wei2014} which results in a
-well-conditioned dense linear system for an unknown density function,
-and the linear system is solved using fast-multipole-accelerated
-GMRES~\cite{saa-sch1986}.  Once the density function is computed, the
-shear stress is computed with a spectrally accurate
-odd-even quadrature rule~\cite{sid-isr1988}.  In addition, the pressure
-and vorticity are computed in the fluid bulk (Fig.~\ref{fig:50bodies})
-with an upsampled trapezoid rule to assist with visualizing the effect of erosion in porous media.
+To perform this simulation of Stokesian erosion of a porous media, two fast and accurate methods are employed---one to solve the fluid equations and the other to integrate the eroding grains.
+The fluid equations are reformulated in terms of a boundary integral equation (BIE)~\cite{poz1992}.
+Since the boundary conditions are Dirichlet, we use a double-layer potential formulation so that the resulting BIE is second-kind.
+This second-kind BIE is discretized with the spectrally accurate trapezoid rule~\cite{tre-wei2014} which results in a well-conditioned dense linear system for an unknown density function, and the linear system is solved using fast-multipole-accelerated GMRES~\cite{saa-sch1986}.
+Once the density function is computed, the shear stress is computed with a spectrally accurate odd-even quadrature rule~\cite{sid-isr1988}.
+In addition, the pressure and vorticity are computed in the fluid bulk (Fig.~\ref{fig:50bodies}) with an upsampled trapezoid rule to assist with visualizing the effect of erosion in porous media.
 
 Next, the computed shear stress is used to evolve the solid boundaries.
-Tracking the interface of fluid-structure interaction problems with a long time horizon is particularly
-difficult as the mesh can become distorted and tangled. 
+Tracking the interface of fluid-structure interaction problems with a long time horizon is particularly difficult as the mesh can become distorted and tangled.
 Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
@@
 \paragraph{Related Work}
-
 In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}.
@@
 
-For these porous network simulations, it is essential to resolve the
-nonlocal effects between the different bodies.  BIEs naturally resolve
-these interactions, and they have been used extensively to simulate
-viscous fluids in complex geometries, including porous media
-flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.  Common challenges
-of a BIE formulation include developing efficient preconditioners for
-the discretized system and numerical difficulties associated with nearly
-touching bodies. In this work, we consider geometries requiring
-$\mathcal{O}(100)$ GMRES iterations, so that preconditioners are not
-necessary. In future work, we will address mobile bodies for which near
-contacts may necessitate preconditoners~\cite{qua-bir2015a,
-qua-cou-dar2018, cou-pou-dar2017}. Similarly, near-singular schemes will
-not be necessary due to the fact that the spacing between receding
-bodies of fixed position always grows in time. Again, the future
-consideration of mobile bodies may necessitate near-singular
-schemes~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
-hel-oja2008a, bea-lai2001}.
+For these porous network simulations, it is essential to resolve the nonlocal effects between the different bodies.
+BIEs naturally resolve these interactions, and they have been used extensively to simulate viscous fluids in complex geometries, including porous media flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.
+Common challenges of a BIE formulation include developing efficient preconditioners for the discretized system and numerical difficulties associated with nearly touching bodies.
+In this work, we consider geometries requiring $\mathcal{O}(100)$ GMRES iterations, so that preconditioners are not necessary.
+In future work, we will address mobile bodies for which near contacts may necessitate preconditoners~\cite{qua-bir2015a, qua-cou-dar2018, cou-pou-dar2017}.
+Similarly, near-singular schemes will not be necessary due to the fact that the spacing between receding bodies of fixed position always grows in time.
+Again, the future consideration of mobile bodies may necessitate near-singular schemes~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.
 
@@
 \paragraph{Outline of the Paper}
-In Section~\ref{s:formulation}, we describe the governing equations for
-both the fluid and the erosion model in a \thL~framework.  In
-Section~\ref{s:method}, the numerical methods in both space and time are
-described and Section~\ref{s:qoi} describes how to compute the
-vorticity, pressure, and drag.  Section~\ref{s:SingleResults} gives
-several numerical examples for a single body, and
-Section~\ref{s:MultiResults} presents numerical examples for
-multiply-connected domains.  Finally, concluding remarks are made in
-Section~\ref{s:conclusions}.
+In Section~\ref{s:formulation}, we describe the governing equations for both the fluid and the erosion model in a \thL~framework.
+In Section~\ref{s:method}, the numerical methods in both space and time are described and Section~\ref{s:qoi} describes how to compute the vorticity, pressure, and drag.
+Section~\ref{s:SingleResults} gives several numerical examples for a single body, and Section~\ref{s:MultiResults} presents numerical examples for multiply-connected domains.
+Finally, concluding remarks are made in Section~\ref{s:conclusions}.
 
@@
 \label{s:formulation}
-We start by defining the main variables used to model erosion.  We
-consider flows that are confined by a solid wall $\Gamma$ that encloses
-$M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.  The
-bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write
-$\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.  On each body, $\nn$ and
-$\ss$ denote the unit normal and unit tangent vectors respectively.
-Throughout the paper, we adopt the convention that $\ss$ points in the
-counterclockwise direction and $\nn$ points out of the fluid domain
-(i.e.~into the bodies). Neglecting inertial forces, the dynamics of the
-fluid is fully determined by the position of the bodies $\xx_\ell(s,t)
-\in \gamma_\ell$, where $s$ is the arclength and $t$ is time.  Given
-$\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid
-velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the
-bounding wall, we prescribe a velocity $\UU(\xx,t)$.  Then, the
-governing equations are
+We start by defining the main variables used to model erosion.
+We consider flows that are confined by a solid wall $\Gamma$ that encloses $M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.
+The bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.
+On each body, $\nn$ and $\ss$ denote the unit normal and unit tangent vectors respectively.
+Throughout the paper, we adopt the convention that $\ss$ points in the counterclockwise direction and $\nn$ points out of the fluid domain (i.e.~into the bodies).
+Neglecting inertial forces, the dynamics of the fluid is fully determined by the position of the bodies $\xx_\ell(s,t) \in \gamma_\ell$, where $s$ is the arclength and $t$ is time.
+Given $\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid velocity $\uu$, the pressure $p$, and the shear stress $\tau$.
+On the bounding wall, we prescribe a velocity $\UU(\xx,t)$.
+Then, the governing equations are
 \begin{equation}
@@
 of momentum}\\
-\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap
-&&\mbox{\em conservation of mass} \\
+\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
 \uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
@@
 \end{equation}
-where $\Vn$ is the normal velocity of the interface and $\mu$ is the
-fluid viscosity.   
-The constant of proportionality of the erosion law only sets the time scale, so we have set
-$\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.  For
-the sake of numerical stability, we modify this law in
-Section~\ref{sec:thetaL}.
-
-The outer wall is formed by rounding off the corners
-of $[-3,3] \times [-1,1]$, and we impose the Hagen-Poiseuille flow
+where $\Vn$ is the normal velocity of the interface and $\mu$ is the fluid viscosity.
+The constant of proportionality of the erosion law only sets the time scale, so we have set $\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.
+For the sake of numerical stability, we modify this law in Section~\ref{sec:thetaL}.
+
+The outer wall is formed by rounding off the corners of $[-3,3] \times [-1,1]$, and we impose the Hagen-Poiseuille flow
 \begin{align}
@@
 \end{align}
-where $U$ sets the maximum of the imposed Poiseuille flow. Often, we
-will simply set $U=1$, but in some instances we change $U$ dynamically
-to enforce that the pressure drop across the computational cell is
-constant as bodies erode within it.  The boundary of the fluid domain is
-$\bd\Omega = \gamma_1 \cup \cdots \cup \gamma_M \cup \Gamma$.  To
-minimize the boundary effects of the inflow and outflow, we only place
-bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.
+where $U$ sets the maximum of the imposed Poiseuille flow.
+Often, we will simply set $U=1$, but in some instances we change $U$ dynamically to enforce that the pressure drop across the computational cell is constant as bodies erode within it.
+The boundary of the fluid domain is $\bd\Omega = \gamma_1 \cup \cdots \cup \gamma_M \cup \Gamma$.
+To minimize the boundary effects of the inflow and outflow, we only place bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.
 
@@
   \input{figs/schematic.tikz}
-  \caption{\label{fig:schematic} A schematic for the governing
-    equations.  A no-slip boundary condition is imposed on each body
-    $\gamma_\ell$ whose unit normal points outward relative to the
-    geometry.  On the outer geometry $\Gamma$, a Hagen-Poiseuille flow
-    is imposed.  The bodies are eroded at a rate that is proportional to
-    the magnitude of the shear stress applied by the Stokesian fluid.
-    The bodies are constrained to the middle third of the channel that
-    is located between the dashed lines.}
+  \caption{\label{fig:schematic} A schematic for the governing equations.
+A no-slip boundary condition is imposed on each body $\gamma_\ell$ whose unit normal points outward relative to the geometry.
+On the outer geometry $\Gamma$, a Hagen-Poiseuille flow is imposed.
+The bodies are eroded at a rate that is proportional to the magnitude of the shear stress applied by the Stokesian fluid.
+The bodies are constrained to the middle third of the channel that is located between the dashed lines.}
 \end{figure}
 
-We describe how the incompressible Stokes equations are solved in
-$\Omega$ using a boundary integral equation in Section~\ref{sec:bies}.
-In Section~\ref{sec:shearStressLP}, we discuss how the shear stress is
-computed.  Finally, in Section~\ref{sec:thetaL}, we describe how corners
-in the bodies are avoided and perform a change of coordinates to treat
-a stiff term.
+We describe how the incompressible Stokes equations are solved in $\Omega$ using a boundary integral equation in Section~\ref{sec:bies}.
+In Section~\ref{sec:shearStressLP}, we discuss how the shear stress is computed.
+Finally, in Section~\ref{sec:thetaL}, we describe how corners in the bodies are avoided and perform a change of coordinates to treat a stiff term.
 
@@
 
-In this section, we describe an equivalent BIE formulation of the
-incompressible Stokes equations with Dirichlet boundary conditions
+In this section, we describe an equivalent BIE formulation of the incompressible Stokes equations with Dirichlet boundary conditions
 \begin{equation}
@@
 \end{equation}
-The boundary condition $\ff$ is the prescribed velocity $\UU$ on
-$\Gamma$, and it is zero on the eroding grains $\gamma$.  In two
-dimensions, a BIE for a stream function formulation is
-possible~\cite{gre-kro-may1996}, but this does not extend to three
-dimensions.  Therefore, we adopt a primitive variable formulation where
-the velocity is written in terms of the standard double-layer
-potential~\cite{lad1963,poz1992}
+The boundary condition $\ff$ is the prescribed velocity $\UU$ on $\Gamma$, and it is zero on the eroding grains $\gamma$.
+In two dimensions, a BIE for a stream function formulation is possible~\cite{gre-kro-may1996}, but this does not extend to three dimensions.
+Therefore, we adopt a primitive variable formulation where the velocity is written in terms of the standard double-layer potential~\cite{lad1963,poz1992}
 \begin{align}
@@
 \end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown
-density function.  As the viscosity $\mu$ also sets the time scale, we
-take $\mu=1$.
-
-Since the double-layer potential is not able to represent force- and
-torque-free velocity fields,  we complete the double-layer potential
-with Stokeslets and rotlets~\cite{pow-mir1987, pow1993}
+where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.
+
+Since the double-layer potential is not able to represent force- and torque-free velocity fields,  we complete the double-layer potential with Stokeslets and rotlets~\cite{pow-mir1987, pow1993}
 \begin{align}
@@
 \end{align}
-where  $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
-$\ell^{th}$ grain, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.
-Then, the solution of~\eqref{eqn:stokes} is
+where  $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the $\ell^{th}$ grain, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then, the solution of~\eqref{eqn:stokes} is
 \begin{align}
@@
 \end{align*}
-removes the rank one null space resulting from the flux-free requirement
-of $\ff$.
+removes the rank one null space resulting from the flux-free requirement of $\ff$.
 
 This BIE formulation requires that $\bd\Omega$ is smooth.
-Unfortunately, smoothness is not guaranteed by erosion since corners
-develop at locations where the shear stress vanishes.  One option is to
-modify our BIE to handle corners~\cite{rac-ser2017,
-ser-rok2016, hel2011, gil-hao-mar2014, bre2012}, but these methods
-require the corner's location, a non-uniform spaced mesh, or are
-ill-conditioned.  Instead, make a slight modification to the erosion
-model in Section~\ref{sec:thetaL} which allows us to control the
-smoothness of the grains.  In this manner, the BIE as described above
-can be applied.
+Unfortunately, smoothness is not guaranteed by erosion since corners develop at locations where the shear stress vanishes.
+One option is to modify our BIE to handle corners~\cite{rac-ser2017, ser-rok2016, hel2011, gil-hao-mar2014, bre2012}, but these methods require the corner's location, a non-uniform spaced mesh, or are ill-conditioned.
+Instead, make a slight modification to the erosion model in Section~\ref{sec:thetaL} which allows us to control the smoothness of the grains.
+In this manner, the BIE as described above can be applied.
 
@@
 \label{sec:shearStressLP}
-Once the density function, Stokeslets, and rotlets are computed, any
-desired quantity, including the shear stress, can be computed.  The
-shear stress is
+Once the density function, Stokeslets, and rotlets are computed, any desired quantity, including the shear stress, can be computed.  The shear stress is
 \begin{align*}
@@
 \end{align*}
-The reader may notice an unusual sign convention above, but this is
-simply a consequence of our conventions for $\nn$ and $\ss$ (see
-Fig.~\ref{fig:schematic}).  The velocity field of the completed
-double-layer potential~\eqref{eqn:completed_DLP} includes velocities
-from three terms: the double-layer potential, the Stokeslets, and the
-rotlets.  We compute the deformation tensor $\ssigma =
-\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of these terms individually.
-
-The deformation tensor of the double-layer
-potential~\eqref{eqn:velocityDLP} at an interior point $\xx \in \Omega$
-is~\cite{qua-bir2014a}
+The reader may notice an unusual sign convention above, but this is simply a consequence of our conventions for $\nn$ and $\ss$ (see Fig.~\ref{fig:schematic}).
+The velocity field of the completed double-layer potential~\eqref{eqn:completed_DLP} includes velocities from three terms: the double-layer potential, the Stokeslets, and the rotlets.
+We compute the deformation tensor $\ssigma = \frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of these terms individually.
+
+The deformation tensor of the double-layer potential~\eqref{eqn:velocityDLP} at an interior point $\xx \in \Omega$ is~\cite{qua-bir2014a}
 \begin{equation}
@@
 \end{equation}
-We require the deformation tensor on $\bd\Omega$, and this requires
-taking the limit of equation~\eqref{eqn:shearStressDLP} when $\xx$ tends
-to $\xx_0 \in \bd\Omega$.  The limiting value is
+We require the deformation tensor on $\bd\Omega$, and this requires taking the limit of equation~\eqref{eqn:shearStressDLP} when $\xx$ tends to $\xx_0 \in \bd\Omega$.  The limiting value is
 \begin{align}
@@
 \end{align}
-Next, the deformation tensor of the Stokeslets and
-rotlets~\eqref{eqn:stokeslet_rotlet} are
+Next, the deformation tensor of the Stokeslets and rotlets~\eqref{eqn:stokeslet_rotlet} are
 \begin{equation}
@@
 \end{equation}
-Combining these deformation tensors, the shear stress at $\xx_0 \in
-\bd\Omega$ is
+Combining these deformation tensors, the shear stress at $\xx_0 \in \bd\Omega$ is
 \begin{align}
@@
 
-The boundary of each body will be represented by a grid of collocation
-points. If we were to simply evolve the interfaces
-under~\eqref{eqn:Vn2}, this grid would become distorted, which, if
-unchecked, could lead to severe tangling and numerical instability. We
-therefore introduce an artificial tangential velocity $\Vs$ to keep the grid points equally spaced in arclength~\cite{hou-low-she1994}. The appropriate tangential velocity satisfies 
+The boundary of each body will be represented by a grid of collocation points.
+If we were to simply evolve the interfaces under~\eqref{eqn:Vn2}, this grid would become distorted, which, if unchecked, could lead to severe tangling and numerical instability.
+We therefore introduce an artificial tangential velocity $\Vs$ to keep the grid points equally spaced in arclength~\cite{hou-low-she1994}.
+The appropriate tangential velocity satisfies
 \begin{align}
@@
   \tderiv{L}{t} &= - 2 \pi \mean{\thalpha \Vn}, \\
-\pderiv{\theta}{t} &= \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} +
-\thalpha \Vs \right) \, .
+  \pderiv{\theta}{t} &= \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right) \, .
 \end{align}
@@
 \label{s:method}
-To perform numerical simulations, we exploit the difference
-between the erosion and fluid time scales.  Since erosion occurs
-much slower, we freeze the geometry at each time
-step, solve the incompressible Stokes equations, and then update the
-geometry according to the erosion model.  Therefore, there are three
-main numerical methods that need to be developed.  In
-Section~\ref{sec:BIE}, we describe how the BIE~\eqref{eqn:completed_BIE}
-is solved.  Once the density function is found,
-Section~\ref{sec:shearStress} describes how the shear
-stress~\eqref{eqn:shearStressLP} is computed.  Then, in
-Section~\ref{sec:timeStepping}, a time stepping method for evolving the
-interface according to equations~\eqref{eqn:Levo1}--\eqref{eq:xsurf}
-are described.
-
-To form stable simulations with long time horizons, we use numerical
-methods that achieve spectral accuracy in space, second-order accuracy
-in time, and maintain an equispaced discretization of the bodies.  The
-boundaries are represented in Fourier space, giving us a set of
-discretization points $\xx_i$ of each body, and all derivatives and
-integrals (the arclength, curvature, and mean values) are computed with
-spectral accuracy using the Fourier representation.
+To perform numerical simulations, we exploit the difference between the erosion and fluid time scales.
+Since erosion occurs much slower, we freeze the geometry at each time step, solve the incompressible Stokes equations, and then update the geometry according to the erosion model.
+Therefore, there are three main numerical methods that need to be developed.
+In Section~\ref{sec:BIE}, we describe how the BIE~\eqref{eqn:completed_BIE} is solved.
+Once the density function is found, Section~\ref{sec:shearStress} describes how the shear stress~\eqref{eqn:shearStressLP} is computed.
+Then, in Section~\ref{sec:timeStepping}, a time stepping method for evolving the interface according to equations~\eqref{eqn:Levo1}--\eqref{eq:xsurf} are described.
+
+To form stable simulations with long time horizons, we use numerical methods that achieve spectral accuracy in space, second-order accuracy in time, and maintain an equispaced discretization of the bodies.
+The boundaries are represented in Fourier space, giving us a set of discretization points $\xx_i$ of each body, and all derivatives and integrals (the arclength, curvature, and mean values) are computed with spectral accuracy using the Fourier representation.
 
@@
 
-To numerically compute the completed double-layer
-potential~\eqref{eqn:completed_BIE}, we discretize each of the $M$
-bodies with  $N_\iin$ points, and the outer boundary with $N_\out$
-points.  Then, $N = MN_\iin + N_\out$ is the total number of
-discretization points of $\bd\Omega$.  The double-layer potential
-in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
+To numerically compute the completed double-layer potential~\eqref{eqn:completed_BIE}, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
+Then, $N = MN_\iin + N_\out$ is the total number of discretization points of $\bd\Omega$.
+The double-layer potential in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
 \begin{align}
@@
 \end{align}
-where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the
-double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is
-replaced with the limiting value of the double-layer potential
+where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is replaced with the limiting value of the double-layer potential
 \begin{align}
@@
 \end{align}
-where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
-vector at $\xx \in \bd\Omega$.  The equations for the
-Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are
-also discretized with the trapezoid rule.  Applying this discretization
-strategy to~\eqref{eqn:completed_BIE}, the dense linear system is solved is
+where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent vector at $\xx \in \bd\Omega$.
+The equations for the Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are also discretized with the trapezoid rule.
+Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system is solved is
 \begin{equation}
@@
 \end{equation}
-for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  We have applied the trapezoid
-rule since all the integrands are smooth and periodic, and this
-guarantees that the numerical solutions converges to the true solution
-with spectral accuracy~\cite{tre-wei2014}.
-
-The linear system~\eqref{eqn:completed_BIE_discretized} is solved
-iteratively with the generalized minimal residual method
-(GMRES)~\cite{saa-sch1986}.  Since the BIE is second-kind, only a
-mesh-independent number of GMRES iterations are
-required~\cite{cam-ips-kel-mey-xue1996}.  Therefore, the asymptotic cost
-is determined by the cost of performing a matrix-vector multiplication,
-and the bulk of the cost is evaluating the $N$-term sum
-in~\eqref{eqn:completed_BIE_discretized}. We use the Fast Multipole
-Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} so that the cost of
-solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$ operations.
+for $i=1,\ldots,N$, $\ell=1,\ldots,M$.
+We have applied the trapezoid rule since all the integrands are smooth and periodic, and this guarantees that the numerical solutions converges to the true solution with spectral accuracy~\cite{tre-wei2014}.
+
+The linear system~\eqref{eqn:completed_BIE_discretized} is solved iteratively with the generalized minimal residual method (GMRES)~\cite{saa-sch1986}.
+Since the BIE is second-kind, only a mesh-independent number of GMRES iterations are required~\cite{cam-ips-kel-mey-xue1996}.
+Therefore, the asymptotic cost is determined by the cost of performing a matrix-vector multiplication, and the bulk of the cost is evaluating the $N$-term sum in~\eqref{eqn:completed_BIE_discretized}.
+We use the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} so that the cost of solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$ operations.
 
@@
 \label{sec:shearStress}
-We have decomposed the deformation tensor into contributions from three
-different terms.  The contributions from the Stokeslets and the
-rotlets~\eqref{eqn:shearStressSR} can be immediately evaluated since
-they do not involve any integration to approximate.  For the shear
-stress of the double-layer potential, we use a slight variant of the
-trapezoid rule. The kernel of the deformation tensor due to the
-double-layer potential~\eqref{eqn:shearStressDLP} is 
+We have decomposed the deformation tensor into contributions from three different terms.
+The contributions from the Stokeslets and the rotlets~\eqref{eqn:shearStressSR} can be immediately evaluated since they do not involve any integration to approximate.
+For the shear stress of the double-layer potential, we use a slight variant of the trapezoid rule.
+The kernel of the deformation tensor due to the double-layer potential~\eqref{eqn:shearStressDLP} is
 \begin{equation}
@@
 \end{equation}
-This kernel has a singularity that is asymptotic to $\bigO(\rho^{-2})$
-when $\yy \rightarrow \xx$, and this is too strong for the unmodified
-trapezoid rule.  The singularity strength can be reduced since the
-velocity corresponding to a constant density function is
-constant~\cite{poz1992}.  Therefore, the deformation tensor of the
-double-layer potential is equivalent to
+This kernel has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy \rightarrow \xx$, and this is too strong for the unmodified trapezoid rule.
+The singularity strength can be reduced since the velocity corresponding to a constant density function is constant~\cite{poz1992}.
+Therefore, the deformation tensor of the double-layer potential is equivalent to
 \begin{align}
@@
 \end{align}
-This expression has a singularity that is asymptotic to
-$\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Then, to achieve
-spectral accuracy, we apply the trapezoid rule with odd-even
-integration~\cite{sid-isr1988}.  Therefore, the deformation tensor of
-the double-layer potential at a discretization point $\xx_i$ on body
-$\gamma_\ell$, with $i$ being odd, is approximated as
+This expression has a singularity that is asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.
+Then, to achieve spectral accuracy, we apply the trapezoid rule with odd-even integration~\cite{sid-isr1988}.
+Therefore, the deformation tensor of the double-layer potential at a discretization point $\xx_i$ on body $\gamma_\ell$, with $i$ being odd, is approximated as
 \begin{align}
@@
 \end{align}
-and a similar approximation is used when $i$ is even.  We also need to
-approximate the jump in the deformation
-tensor~\eqref{eqn:shearStressJump}, and this is done with Fourier
-differentiation.  Finally, the shear stress is computed by multiplying
-the deformation tensor by the normal vector, and taking the inner
-product with the tangent vector.
-
-We do not employ an FMM to evaluate the shear stress at $\xx_i$,
-$i=1,\ldots,N$, so the cost of evaluating the shear stress is
-$\bigO(N^2)$.  However, this calculation is only performed once per time
-step as opposed to the velocity double-layer potential, where we do
-employ the FMM, that must be evaluated at each GMRES iteration.  In
-future work, we plan to use a kernel-independent
-FMM~\cite{yin-bir-zor2004} to evaluate the shear stress with $\bigO(N)$
-operations.
+and a similar approximation is used when $i$ is even.
+We also need to approximate the jump in the deformation tensor~\eqref{eqn:shearStressJump}, and this is done with Fourier differentiation.
+Finally, the shear stress is computed by multiplying the deformation tensor by the normal vector, and taking the inner product with the tangent vector.
+
+We do not employ an FMM to evaluate the shear stress at $\xx_i$, $i=1,\ldots,N$, so the cost of evaluating the shear stress is $\bigO(N^2)$.
+However, this calculation is only performed once per time step as opposed to the velocity double-layer potential, where we do employ the FMM, that must be evaluated at each GMRES iteration.
+In future work, we plan to use a kernel-independent FMM~\cite{yin-bir-zor2004} to evaluate the shear stress with $\bigO(N)$ operations.
 
@@
 
-First, we must address a second potential source of numerical
-instability. The erosion law~\eqref{eqn:Vn} depends on the {\em absolute
-value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$
-changes sign, i.e.~at a stagnation point. The corner in $\atau$
-introduces high frequencies into~\eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
+First, we must address a second potential source of numerical instability.
+The erosion law~\eqref{eqn:Vn} depends on the {\em absolute value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$ changes sign, i.e.~at a stagnation point.
+The corner in $\atau$ introduces high frequencies into~\eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
 To avoid these difficulties, we smooth $\atau$ via a narrow Gaussian filter of width $\sigma$
@@
 This is the idea of an exponential integrator.
-We solve the resulting system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an
-explicit, second-order Runge-Kutta method (RK2). In particular, we use the {\em midpoint} RK2 method because it maximizes the smoothing effect of the diffusive term.
+We solve the resulting system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an explicit, second-order Runge-Kutta method (RK2).
+In particular, we use the {\em midpoint} RK2 method because it maximizes the smoothing effect of the diffusive term.
 
@@
 \end{align}
-where the superscript indicates the time step. At the next stage of RK2
-it will be necessary to evaluate derivatives at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the body shapes must be known.
+where the superscript indicates the time step.
+At the next stage of RK2 it will be necessary to evaluate derivatives at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the body shapes must be known.
 We therefore insert~\eqref{eq:mu12d} into~\eqref{eq:th12d} and solve for $\thhat_k^{(n+1/2)}$, giving
@@
 \label{s:qoi}
-We further characterize the flow by computing the vorticity
-(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
-and drag (Section~\ref{sec:drag}).  Once
-equation~\eqref{eqn:completed_DLP} is solved, the vorticity and pressure
-will be computed at points both inside the fluid bulk and on the
-along individual bodies, and then the drag of individual bodies will be computed.  For target points
-in the fluid domain, the integrands of the layer potentials are periodic
-and smooth, and the trapezoid rule guarantees spectral
-accuracy~\cite{tre-wei2014}.  However, if the target point is close to
-$\bd \Omega$, a nearly-singular integrand must be integrated, and this
-requires upsampling that is described in Section~\ref{sec:NSI}.  When
-the target points is on the boundary, the integrands involve
-singularities that are evaluated by combining singularity subtraction
-and odd-even integration~\cite{sid-isr1988}.
+We further characterize the flow by computing the vorticity (Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}), and drag (Section~\ref{sec:drag}).
+Once equation~\eqref{eqn:completed_DLP} is solved, the vorticity and pressure will be computed at points both inside the fluid bulk and on the along individual bodies, and then the drag of individual bodies will be computed.
+For target points in the fluid domain, the integrands of the layer potentials are periodic and smooth, and the trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.
+However, if the target point is close to $\bd \Omega$, a nearly-singular integrand must be integrated, and this requires upsampling that is described in Section~\ref{sec:NSI}.
+When the target points is on the boundary, the integrands involve singularities that are evaluated by combining singularity subtraction and odd-even integration~\cite{sid-isr1988}.
 
@@
 \label{sec:vorticity}
-We start by computing the vorticity $\omega(\xx) = v_x - u_y$ for $\xx
-\in \Omega$ which we decompose into contributions from the double-layer
-potential, Stokeslets, and rotlets.  The vorticity of the double-layer
-potential~\eqref{eqn:velocityDLP} at
-$\xx \in \Omega$ is
+We start by computing the vorticity $\omega(\xx) = v_x - u_y$ for $\xx \in \Omega$ which we decompose into contributions from the double-layer potential, Stokeslets, and rotlets.
+The vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
 \begin{align}
@@
 \end{align}
-To compute~\eqref{eqn:vorticityDLP} numerically, we apply the trapezoid
-rule with an upsampling scheme described in Section~\ref{sec:NSI}.
-Next, the vorticity due to the Stokeslet is
+To compute~\eqref{eqn:vorticityDLP} numerically, we apply the trapezoid rule with an upsampling scheme described in Section~\ref{sec:NSI}.  Next, the vorticity due to the Stokeslet is
 \begin{align}
@@
 
-For the Stokes equations, on boundaries that have a no-slip boundary
-condition, the shear stress is equivalent to the vorticity.  Therefore,
-the vorticity is computed on the grains $\gamma_\ell$ by numerically
-compute the shear stress as described in Section~\ref{sec:shearStress}.
+For the Stokes equations, on boundaries that have a no-slip boundary condition, the shear stress is equivalent to the vorticity.
+Therefore, the vorticity is computed on the grains $\gamma_\ell$ by numerically compute the shear stress as described in Section~\ref{sec:shearStress}.
 
@@
 \label{sec:pressure}
-To compute the pressure at $\xx \in \Omega$, we follow the same
-procedure used for the shear stress.  We first compute the pressure of
-the double-layer potential for $\xx \in \Omega$ and add the appropriate
-jump if $\xx \in \Gamma$. The pressure of the double-layer
-potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
+To compute the pressure at $\xx \in \Omega$, we follow the same procedure used for the shear stress.
+We first compute the pressure of the double-layer potential for $\xx \in \Omega$ and add the appropriate jump if $\xx \in \Gamma$.
+The pressure of the double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
 \begin{align}
@@
 \end{align}
-To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid
-rule with an upsampling scheme described in Section~\ref{sec:NSI}.  The
-pressure due to the Stokeslets is
+To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid rule with an upsampling scheme described in Section~\ref{sec:NSI}.  The pressure due to the Stokeslets is
 \begin{align}
@@
 
-For target points on the boundary of the geometry, $\xx \in \bd \Omega$,
-there is an additional term resulting from a jump in the pressure
-double-layer potential~\cite{poz1992}
+For target points on the boundary of the geometry, $\xx \in \bd \Omega$, there is an additional term resulting from a jump in the pressure double-layer potential~\cite{poz1992}
 \begin{align}
@@
 \end{align}
-Similar to the shear stress, the singularity of the pressure
-corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
-too strong when $\xx \in \bd\Omega$ for the trapezoid rule to be
-directly applied.  Therefore, we again subtract a constant density
-function and write the pressure as
+Similar to the shear stress, the singularity of the pressure corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is too strong when $\xx \in \bd\Omega$ for the trapezoid rule to be directly applied.
+Therefore, we again subtract a constant density function and write the pressure as
 \begin{equation}
@@
 \end{equation}
-Then, identical to how the shear stress is
-computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
-evaluate this layer potential for pressure, and the jump condition
-in~\eqref{eqn:pressureJump} is computed with Fourier differentiation.
+Then, identical to how the shear stress is computed~\eqref{eqn:stressOddEven}, odd-even integration is used to evaluate this layer potential for pressure, and the jump condition in~\eqref{eqn:pressureJump} is computed with Fourier differentiation.
 
@@
 \label{sec:drag}
-Once the pressure and shear stress is computed, the drag on a single
-body with boundary $\gamma_\ell$ is
+Once the pressure and shear stress is computed, the drag on a single body with boundary $\gamma_\ell$ is
 \begin{align}
@@
 \label{sec:NSI}
-The layer potentials for the velocity~\eqref{eqn:velocityDLP},
-vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP}
-need to be evaluated at points $\xx \in \Omega$. We write the general
-layer potential as
+The layer potentials for the velocity~\eqref{eqn:velocityDLP}, vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP} need to be evaluated at points $\xx \in \Omega$.
+We write the general layer potential as
 \begin{align}
@@
 \end{align}
-Since the integrand is periodic and smooth, the trapezoid rule
-guarantees spectral accuracy.  However, when the target point $\xx$ is
-close to $\bd\Omega$, the integrand is nearly-singular, and the accuracy
-of the trapezoid rule deteriorates unless a large number of
-discretization points are used~\cite{bar2014}.  We are only interested
-in computing the velocity, vorticity, and pressure to visualize the
-flow, so it is not necessary that we resolve the integrands for
-arbitrarily close target points.
-
-The layer potential~\eqref{eqn:genericLP} is approximated with the
-trapezoid rule 
+Since the integrand is periodic and smooth, the trapezoid rule guarantees spectral accuracy.
+However, when the target point $\xx$ is close to $\bd\Omega$, the integrand is nearly-singular, and the accuracy of the trapezoid rule deteriorates unless a large number of discretization points are used~\cite{bar2014}.
+We are only interested in computing the velocity, vorticity, and pressure to visualize the flow, so it is not necessary that we resolve the integrands for arbitrarily close target points.
+
+The layer potential~\eqref{eqn:genericLP} is approximated with the trapezoid rule 
 \begin{align}
@@
 \end{align}
-where $q$ contains the quadrature weights, Jacobian, and density
-function.  Based on numerical experiments, the error of the $N$-point
-trapezoid rule is acceptable for points $\xx$ that are more than five 
-arclength spacings from $\bd\Omega$. For points that are closer than
-five arclength spacings to $\bd\Omega$, we use an upsampled trapezoid
-rule.  The required upsampling of the geometry and the density function
-is done with a Fourier interpolant.  To minimize the number of
-discretization points that are used to approximate the layer
-potential~\eqref{eqn:layerPotential}, we use the same upsampling rate
-for all target points in dyadic intervals (Table~\ref{tbl:upsampling}).
-For points that are closer than $5/16$ of an arclength from $\bd\Omega$,
-a value of 0 is simply assigned to $\phi$.
+where $q$ contains the quadrature weights, Jacobian, and density function.
+Based on numerical experiments, the error of the $N$-point trapezoid rule is acceptable for points $\xx$ that are more than five arclength spacings from $\bd\Omega$.
+For points that are closer than five arclength spacings to $\bd\Omega$, we use an upsampled trapezoid rule.
+The required upsampling of the geometry and the density function is done with a Fourier interpolant.
+To minimize the number of discretization points that are used to approximate the layer potential~\eqref{eqn:layerPotential}, we use the same upsampling rate for all target points in dyadic intervals (Table~\ref{tbl:upsampling}).
+For points that are closer than $5/16$ of an arclength from $\bd\Omega$, a value of 0 is simply assigned to $\phi$.
 \newcolumntype{V}{>{\centering\arraybackslash}m{4em}}
@@
 \centering
-%\begin{tabular}{|c|ccccc|}
 \begin{tabular}{|V|V|V|V|V|V|N}
@@
 \end{tabular}
-\caption{\label{tbl:upsampling}The upsampling rate of our near-singular
-integration scheme.  $d(\xx,\bd\Omega)$ is the distance between a point
-$\xx \in \Omega$ and the boundary of the domain $\bd\Omega$, and $h$ is
-an arclength spacing.}
+\caption{\label{tbl:upsampling}The upsampling rate of our near-singular integration scheme.
+$d(\xx,\bd\Omega)$ is the distance between a point $\xx \in \Omega$ and the boundary of the domain $\bd\Omega$, and $h$ is an arclength spacing.}
 \end{table}
 
-If eroding bodies are also sedimenting, bodies will come too close to
-one another for upsampling to be sufficient.  Therefore, future work
-will apply one of several near-singular integration schemes available in
-the literature~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015,
-hel-oja2008a}.
+If eroding bodies are also sedimenting, bodies will come too close to one another for upsampling to be sufficient.
+Therefore, future work will apply one of several near-singular integration schemes available in the literature~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a}.
 
@@
 \label{s:SingleResults}
-With the description of the methods complete, we now present numerical
-results on bodies eroding in Stokes flow. We first discuss the case of a
-single body, as certain features can be predicted analytically and thus
-used for validation. In Section~\ref{s:MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.
+With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow.
+We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation.
+In Section~\ref{s:MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.
 
@@
 
-Figure~\ref{01bodseq} shows the erosion of a single body, numerically
-simulated with $N_\iin = 1024$ discretization points and shown at three
-evenly spaced times. Here, color represents the vorticity of the
-surrounding flow. When evaluated on the boundary, vorticity corresponds
-to the shear stress and thus the local erosion rate. As seen in the
-left-most snapshot, the body is initially circular and has the strongest
-vorticity at its top and bottom. The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points. 
+Figure~\ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times.
+Here, color represents the vorticity of the surrounding flow.
+When evaluated on the boundary, vorticity corresponds to the shear stress and thus the local erosion rate.
+As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity at its top and bottom.
+The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points.
 At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
@@
 As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape that has corners at its front and back---somewhat reminiscent of an American football.
-Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress,
-$\atau$, is distributed along each of these interfaces. The normalized
-arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0
-and 0.5 corresponding to the rear and front stagnation points
-respectively. At early times (yellow curves), the stress varies
-significantly, with more stress concentrated at the top and bottom of
-the body. However, as erosion reshapes the body, the stress becomes more
-uniformly distributed over the entire surface (red curves). The absolute
-stress $\atau$ shows slight peaks near the stagnation points as the body nears the final stages of erosion (dark red).
+Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
+The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0 and 0.5 corresponding to the rear and front stagnation points respectively.
+At early times (yellow curves), the stress varies significantly, with more stress concentrated at the top and bottom of the body.
+However, as erosion reshapes the body, the stress becomes more uniformly distributed over the entire surface (red curves).
+The absolute stress $\atau$ shows slight peaks near the stagnation points as the body nears the final stages of erosion (dark red).
 Closer inspection reveals that the stress actually vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow with time.
@@
 The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory~\cite{batchelor1970slender, MooreJFM2012}.
-For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
-$\mu \umax \ell/ \log(\ell/a)$, where $a \ll \ell $ is a length scale of the cross-section. This law implies that the stress-per-unit-span on a 2D cross-section is approximately
+For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to $\mu \umax \ell/ \log(\ell/a)$, where $a \ll \ell $ is a length scale of the cross-section.
+This law implies that the stress-per-unit-span on a 2D cross-section is approximately
 \begin{align}
@@
 \end{align}
-In interpreting our 2D simulations, we will treat the span, $\ell$, as
-fixed.
+In interpreting our 2D simulations, we will treat the span, $\ell$, as fixed.
 Recall that $L$ denotes the total perimeter of the 2D cross-section.
@@
 
-We now aim to measure the opening angles formed in the numerical
-simulations to compare against the above prediction.
+We now aim to measure the opening angles formed in the numerical simulations to compare against the above prediction.
 However, Section~\ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
@@
 Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerged before the body disappeared~\cite{moo-ris-chi-zha-she2013}.
-
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
-	These fixed-area simulations enable us to precisely characterize
-        the changing geometry as it approaches the terminal state. In
-        particular, we measure the aspect ratio of the body (the width
-        to height) and the opening angle of the front/rear corners. In
-        these tests, we keep the spatial resolution fixed, $N_\iin =
-        1024$, and show three different cases of the smoothing
-        parameters, $\eps$ and $\sigma$, to assess how the numerical
-        regularization influences shape. In the three cases, we keep
-        $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and
-        5/1024 respectively. Loosely, these values correspond to
-        smoothing over the nearest 20, 10, and 5 grid points, respectively.
+These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches the terminal state.
+In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
+In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters, $\eps$ and $\sigma$, to assess how the numerical regularization influences shape.
+In the three cases, we keep $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and 5/1024 respectively.
+Loosely, these values correspond to smoothing over the nearest 20, 10, and 5 grid points, respectively.
 Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
@@
 
-	Next, we aim to measure the opening angle of the front/rear
-        corner. Since these simulated bodies are actually smooth on a
-        fine scale, we must have a procedure to estimate the apparent
-        angle that results from the high (but finite) curvature at the
-        stagnation points. To this end, we fit the tangent angle
-        $\theta(\alpha)$ with a 7th-degree polynomial over a region
-        excluding the stagnation points ($\alpha = 0$ and 0.5). We then
-        extrapolate the polynomial to the stagnation points, which gives
-        an estimate of the angle there. Although this procedure is
-        subject to some uncertainty (to be examined below), we have
-        found it to give robust angle measurements.
-        Figure~\ref{fig:arangle}(b) shows the opening angle, $\beta$, as
-        it varies in time for the three cases of smoothing parameters.
-        For the initially circular geometry, our procedure yields the
-        correct opening angle of $180^{\circ}$, i.e.~a flat front face.
-        As time proceeds, erosion carves a sharper corner and $\beta$
-        decreases monotonically. Here, the three cases of smoothing
-        parameters are more easily distinguished, implying that the
-        opening angle is more sensitive to the level of numerical
-        smoothing than is the aspect ratio. The curves nevertheless show
-        convergence as $\eps, \sigma \to 0$. In the finest simulation
-        ($\eps = \sigma = 5/1024$), $\beta$ converges to the value
-        $102^{\circ}$, which agrees precisely with the analytical
-        prediction from Section~\ref{LimitingShape}.
+Next, we aim to measure the opening angle of the front/rear corner.
+Since these simulated bodies are actually smooth on a fine scale, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points.
+To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5).
+We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there.
+Although this procedure is subject to some uncertainty (to be examined below), we have found it to give robust angle measurements.
+Figure~\ref{fig:arangle}(b) shows the opening angle, $\beta$, as it varies in time for the three cases of smoothing parameters.
+For the initially circular geometry, our procedure yields the correct opening angle of $180^{\circ}$, i.e.~a flat front face.
+As time proceeds, erosion carves a sharper corner and $\beta$ decreases monotonically.
+Here, the three cases of smoothing parameters are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing than is the aspect ratio.
+The curves nevertheless show convergence as $\eps, \sigma \to 0$.
+In the finest simulation ($\eps = \sigma = 5/1024$), $\beta$ converges to the value $102^{\circ}$, which agrees precisely with the analytical prediction from Section~\ref{LimitingShape}.
 
@@
 \begin{center}
+\todo[inline]{finish caption (just didn't want to forget it)}
 \caption{The long-time aspect ratio and opening-angle measurements for three...
@@
 
-	In summary, we have found that a single-body eroding in 2D
-        Stokes flow converges to a terminal form characterized by nearly
-        uniform shear stress along its surface. The final shape is
-        fairly slender, with an aspect ratio of 2.7, and distinguished
-        by  corners of opening angle $102^{\circ}$ at the front and
-        rear. This shape is closely related to the drag-minimizing
-        profile found by Pironneau (1973)---the geometry that
-        minimizes drag in 3D Stokes flow subject to the constraint of
-        fixed volume~\cite{pir1973}. Using variational principles,
-        Pironneau showed that the drag-minimizing form has constant
-        shear (or vorticity) along its surface. The resulting {\em
-        axisymmetric} shape has an aspect ratio of 2.1 and front/rear
-        opening-angles of $120^{\circ}$~\cite{pir1973, mit-spa2016}.
-        Interestingly, 3D simulations of viscous erosion showed close
-        resemblance between the shape formed by a single eroding body
-        and this Pironneau form~\cite{mit-spa2016}. It was found that
-        the eroding body does not converge {\em precisely} to the
-        Pironneau shape because the long-time surface-stress
-        distribution created by erosion is only {\em approximately}
-        uniform. Rather than strict uniformity, variations in body
-        curvature must be offset by slight variations in $\Vn$ for
-        self-similar reduction~\cite{pir1973, mit-spa2016}. Pironneau's
-        argument that the drag-minimizing form has constant surface
-        stress applies to 2D as well. Therefore, the shape observed in
-        our simulation is approximately the form that minimizes drag
-        subject to fixed area, i.e.~the 2D counterpart to Pironneau's
-        shape. How close this shape is to the true drag-minimizer is
-        related to how close the stress distributions are to uniform, as
-        can be seen in Fig.~\ref{shrink_intface}(b).
+In summary, we have found that a single-body eroding in 2D Stokes flow converges to a terminal form characterized by nearly uniform shear stress along its surface.
+The final shape is fairly slender, with an aspect ratio of 2.7, and distinguished by  corners of opening angle $102^{\circ}$ at the front and rear.
+This shape is closely related to the drag-minimizing profile found by Pironneau (1973)---the geometry that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume~\cite{pir1973}.
+Using variational principles, Pironneau showed that the drag-minimizing form has constant shear (or vorticity) along its surface.
+The resulting {\em axisymmetric} shape has an aspect ratio of 2.1 and front/rear opening-angles of $120^{\circ}$~\cite{pir1973, mit-spa2016}.
+Interestingly, 3D simulations of viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form~\cite{mit-spa2016}.
+It was found that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
+Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ for self-similar reduction~\cite{pir1973, mit-spa2016}.
+Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well.
+Therefore, the shape observed in our simulation is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape.
+How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{shrink_intface}(b).
 
 \subsection{Convergence test}
-
-As a final validation, we now verify that our method converges with the
-expected second-order accuracy in time. For this, we run the same
-single-body simulation shown in Figs.~\ref{01bodseq} and~\ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
+As a final validation, we now verify that our method converges with the expected second-order accuracy in time.
+For this, we run the same single-body simulation shown in Figs.~\ref{01bodseq} and~\ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
 This stopping time is 56\% of the vanishing time, and was selected so that the body will have eroded substantially but is not small enough to compromise accuracy (due to the stress diverging).
@@
 \end{align}
-The velocity and pressure fields depend linearly on $\eeta$,
-$\llambda$, and $\xi$, so this rescaling maintains a {\em fixed} pressure difference across the subdomain $-2 \le x \le 2$.
+The velocity and pressure fields depend linearly on $\eeta$, $\llambda$, and $\xi$, so this rescaling maintains a {\em fixed} pressure difference across the subdomain $-2 \le x \le 2$.
 Since the Stokes equations are linear, the rescaled flow remains a solution to the PDE system (valid to the same order of accuracy).
@@
 
-To validate the multi-body simulations with this new
-fixed-pressure-drop condition, we report a convergence test in
-Table~\ref{convtab2}. In this test, we simulate the erosion of 20 bodies to a
-stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of
-the time required for {\em all} bodies to vanish, and, in fact, a few of
-the bodies will have already vanished by $t_s$. To assess error, we
-measure the aggregate $L^2$-difference in the shape of {\em all} of the
-bodies, comparing simulations of successive temporal resolution. Note
-that this metric is sensitive to numerical errors in any of the
-simulated bodies. The table confirms that our method retains
-second-order accuracy in time, thus validating our rescaling procedure
-and confirming that multi-body interactions are handled correctly by the Stokes solver.
+To validate the multi-body simulations with this new fixed-pressure-drop condition, we report a convergence test in Table~\ref{convtab2}.
+In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$.
+This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$.
+To assess error, we measure the aggregate $L^2$-difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution.
+Note that this metric is sensitive to numerical errors in any of the simulated bodies.
+The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multi-body interactions are handled correctly by the Stokes solver.
 The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution.
@@
 \begin{center}
-\caption{The number of GMRES iterations required to reach a fixed
-tolerance of $10^{-}8$ in our simulations.
+\caption{The number of GMRES iterations required to reach a fixed tolerance of $10^{-8}$ in our simulations.
 The left side shows a case of fixed geometry, 10 circular bodies, with increasing spatial resolution, $N_\iin$, demonstrating that the iteration count is independent of resolution.
@@
 
-Lastly, we want to briefly examine the number of GMRES iterations
-required by our simulations since this is typically the most expensive
-step. Due to our {\em second-kind} boundary integral formulation, we
-expect the number of GMRES iterations to be independent of the spatial
-resolution, $N_{\iin}$. The iteration count, however, may depend on the
-number of bodies, as well as other factors such as the shapes of the
-bodies and their configuration. To examine a few of these factors, we
-show in Table~\ref{itertab} the number of GMRES iterations required to
-reach a specified tolerance of $10^{-8}$ in several different
-simulations. The left side of the table shows the results for a 10-body
-simulation, in which we keep the geometry fixed and vary the spatial
-resolution $N_{\iin}$. As seen in the table, the iteration count remains
-essentially fixed as the resolution increases. In the right side of the
-table, we keep the spatial resolution per body fixed and vary the number of simulated bodies from 10 to 50.
+Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since this is typically the most expensive step.
+Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
+The iteration count, however, may depend on the number of bodies, as well as other factors such as the shapes of the bodies and their configuration.
+To examine a few of these factors, we show in Table~\ref{itertab} the number of GMRES iterations required to reach a specified tolerance of $10^{-8}$ in several different simulations.
+The left side of the table shows the results for a 10-body simulation, in which we keep the geometry fixed and vary the spatial resolution $N_{\iin}$.
+As seen in the table, the iteration count remains essentially fixed as the resolution increases.
+In the right side of the table, we keep the spatial resolution per body fixed and vary the number of simulated bodies from 10 to 50.
 The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
@@
 
-With the validation complete, we now discuss the emergent physics of
-multi-body erosion revealed by our simulations. We begin with a
-relatively simple case of 6 eroding bodies, as this will allow us to
-identify key principles at work in more complex cases (e.g.~the 50-body
-simulation in Fig.~\ref{fig:50bodies}). Figure~\ref{fig:06bodies} shows
-the simulated erosion of 6 bodies, each initial circles of various sizes
-and positions. Over time, erosion not only diminishes the size of the
-bodies, but also alters their shapes considerably.
+With the validation complete, we now discuss the emergent physics of multi-body erosion revealed by our simulations.
+We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}).
+Figure~\ref{fig:06bodies} shows the simulated erosion of 6 bodies, each initial circles of various sizes and positions.
+Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
 As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable.
@@
 
-To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows
-several measurements taken from the multi-body simulations.
+To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multi-body simulations.
 In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}.
@@
 \section{Conclusions\label{s:conclusions}}
-We have combined two accurate and stable numerical methods to simulate
-two-dimensional viscous erosion in a porous medium.  First, a BIE
-formulation of the incompressible Stokes equations discretizes only the
-boundary of the bodies and resolves their non-negligible interactions.
-Second, the bodies are evolved with the so-called {\thL} variables to
-avoid tangling and distortion of the mesh.  The resulting numerical
-method is spectral in space, second-order in time, and is accelerated
-with the fast multipole method.
-
-Using slender body theory and flow past a wedge, the method is verified
-against analytical results for the area, opening angle, and total drag
-of a single eroding body.  Then, for multi-body erosion with a realistic
-pressure drop boundary condition, we compute the area fraction, flow
-rate, and total drag across a channel.  We observe that erosion leads to
-channelization, and this reduces the resistance more than would be
-expected if the area fraction were reduced by simply scaling down the
-size of the bodies.  This indicates that the area fraction can not fully
-characterize flow in eroding porous media since the interactions between
-the bodies plays a role in the resistance.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{\bf Acknowledgments} The authors would like to thank Manas
-Rachh for supplying the FMM for the Stokes double-layer potential.
+We have combined two accurate and stable numerical methods to simulate two-dimensional viscous erosion in a porous medium.
+First, a BIE formulation of the incompressible Stokes equations discretizes only the boundary of the bodies and resolves their non-negligible interactions.
+Second, the bodies are evolved with the so-called {\thL} variables to avoid tangling and distortion of the mesh.
+The resulting numerical method is spectral in space, second-order in time, and is accelerated with the fast multipole method.
+
+Using slender body theory and flow past a wedge, the method is verified against analytical results for the area, opening angle, and total drag of a single eroding body.
+Then, for multi-body erosion with a realistic pressure drop boundary condition, we compute the area fraction, flow rate, and total drag across a channel.
+We observe that erosion leads to channelization, and this reduces the resistance more than would be expected if the area fraction were reduced by simply scaling down the size of the bodies.
+This indicates that the area fraction can not fully characterize flow in eroding porous media since the interactions between the bodies plays a role in the resistance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{\bf Acknowledgments} The authors would like to thank Manas Rachh for supplying the FMM for the Stokes double-layer potential.
 

### 2018-04-10 docs/methods/erosion_methods.tex
NM

@@
 Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than in any other regime.
+% in particular close-contacts?
 
@@
 \section{Conclusions\label{s:conclusions}}
+
 We have combined two accurate and stable numerical methods to simulate two-dimensional viscous erosion in a porous medium.
@@
 
-Using slender body theory and flow past a wedge, the method is verified against analytical results for the area, opening angle, and total drag of a single eroding body.
+%Using slender body theory and flow past a wedge, the method is verified against analytical results for the area, opening angle, and total drag of a single eroding body.
 Then, for multi-body erosion with a realistic pressure drop boundary condition, we compute the area fraction, flow rate, and total drag across a channel.

### 2018-04-10 docs/methods/erosion_methods.tex
NM

@@
 We have combined two accurate and stable numerical methods to simulate two-dimensional viscous erosion in a porous medium.
-First, a BIE formulation of the incompressible Stokes equations discretizes only the boundary of the bodies and resolves their non-negligible interactions.
-Second, the bodies are evolved with the so-called {\thL} variables to avoid tangling and distortion of the mesh.
-The resulting numerical method is spectral in space, second-order in time, and is accelerated with the fast multipole method.
-
-%Using slender body theory and flow past a wedge, the method is verified against analytical results for the area, opening angle, and total drag of a single eroding body.
-Then, for multi-body erosion with a realistic pressure drop boundary condition, we compute the area fraction, flow rate, and total drag across a channel.
-We observe that erosion leads to channelization, and this reduces the resistance more than would be expected if the area fraction were reduced by simply scaling down the size of the bodies.
-This indicates that the area fraction can not fully characterize flow in eroding porous media since the interactions between the bodies plays a role in the resistance.
+First, a BIE formulation of the incompressible Stokes equations discretizes only the boundaries and resolves non-negligible interactions between bodies.
+This Stokes solver enables computation of the surface shear stress, which dictates the erosion rate of solid material.
+To advance solid boundaries forward in time, we use the {\thL} framework, which prevents tangling and distortion of the mesh that would otherwise lead to numerical instability.
+The resulting method is accurate (spectral in space, second-order in time), numerically stable, and accelerated via the fast multipole method.
+
+Analytical results for the case of a single eroding body provide a stringent benchmark for our simulation.
+In particular, by appealing to the principle of long-time uniform stress, we predict a front/rear corner of 102, which matches closely the value measured in the simulations.
+Scaling laws for the asymptotic rate of area and drag reduction also match the simulation.
+
+Simulations of multiple eroding bodies reveals even more complex behavior.
+As in the single body case, we witness the formation of sharp corners, but not in locations that are easily predictable.
+Furthermore, bodies tend to form flat faces in places where there was initially near contact, which leads to the appearance of straight channels between bodies.
+The overall resistance of the porous network declines rapidly, which we attribute the channelization process.
 

### 2018-04-10 docs/methods/erosion_methods.tex
NM

@@
 Analytical results for the case of a single eroding body provide a stringent benchmark for our simulation.
-In particular, by appealing to the principle of long-time uniform stress, we predict a front/rear corner of 102, which matches closely the value measured in the simulations.
+In particular, by appealing to the principle of long-time uniform stress, we predict a front/rear corner of angle $102^{\circ}$, which matches closely the value measured in the simulations.
 Scaling laws for the asymptotic rate of area and drag reduction also match the simulation.
@@
 As in the single body case, we witness the formation of sharp corners, but not in locations that are easily predictable.
-Furthermore, bodies tend to form flat faces in places where there was initially near contact, which leads to the appearance of straight channels between bodies.
-The overall resistance of the porous network declines rapidly, which we attribute the channelization process.
+Furthermore, bodies tend to form flat faces in places where there was initially near contact, leading to the appearance of straight channels between bodies.
+The overall resistance of the porous network declines rapidly with erosion, which we attribute to the channelization process.
+
+In work currently underway, we are using this method to examine more thoroughly how bulk and statistical properties of the porous medium change with erosion.
+We are particularly interested in the development of anisotropic permeability of the medium.
+Preliminary simulations show promise.
+We furthermore would like to investigate how the statistical distribution of bodies size, shape, and orientation changes over time.
+We hope to report on these topics soon.
+
+As a longer term goal, we would like to include the effect of sedimentation to more faithfully capture the physics of a porous medium.
+Sedimentation requires overcoming a few challenges.
+First, the bodies must be mobile, as has been accomplished in previous work (cite).
+Second, contacts and overlap between bodies must be prevented.
+This second requirement has been recognized as quite a challenge, with many novel methods developed to treat it (CITE STUFF HERE).
+Incorporation of one or more of these schemes, will enable simulations of a porous medium undergoing simultaneous erosion and sedimentation.
 

### 2018-04-10 docs/methods/erosion_methods.tex
NM

@@
 In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters, $\eps$ and $\sigma$, to assess how the numerical regularization influences shape.
-In the three cases, we keep $\eps = \sigma$ and set them to the values 20/1024, 10/1024, and 5/1024 respectively.
+In the three cases, we keep $\eps = \sigma$ always and set them to the values 20/1024, 10/1024, and 5/1024.
 Loosely, these values correspond to smoothing over the nearest 20, 10, and 5 grid points, respectively.
@@
 As time proceeds, erosion carves a sharper corner and $\beta$ decreases monotonically.
-Here, the three cases of smoothing parameters are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing than is the aspect ratio.
+Here, the three cases of smoothing parameters are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing than the aspect ratio is.
 The curves nevertheless show convergence as $\eps, \sigma \to 0$.
@@
 To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three cases.
-The table shows that both the aspect ratio and opening angle converge with roughly first-order as $\eps, \sigma \to 0$.
+The table shows that both the aspect ratio and opening angle converge at a rate that is nearly linear as $\eps, \sigma \to 0$.
 In addition, we show an estimate of the uncertainty involved in our angle measurement, obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
@@
 \begin{center}
-\todo[inline]{finish caption (just didn't want to forget it)}
-\caption{The long-time aspect ratio and opening-angle measurements for three...
+\caption{The long-time aspect ratio and opening-angle measurements for three cases of numerical smoothing.
+In these runs, we fix the resolution $N_\iin = 1024$, and vary the two smoothing parameters, $\eps, \sigma$.
+As $\eps, \sigma \to 0$, the aspect ratio tends to roughly 2.7 and the opening angle converges to the predicted value of $102^{\circ}$.
+Furthermore, the uncertainty in the angle measurement becomes smaller.
 } 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{\bf Acknowledgments} The authors would like to thank Manas Rachh for supplying the FMM for the Stokes double-layer potential.
+\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for supplying the FMM for the Stokes double-layer potential. 
+%We would like to thank Saverio Spagnolie, William Mitchell, Daniel Rothman, Michael Shelley, ....
 

### 2018-04-10 docs/methods/erosion_methods.tex
NM

@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large-scale land formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}.
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
@@
 In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
-Such processes of `sculpting with flow' \cite{ristroph2018sculpting} have been examined in the context of a single body \cite{ris-moo-chi-she-zha2012} and, more recently, multiple bodies whose shape evolution is coupled through the flow \cite{hewett2017evolution, moore2017riemann}.
+Such processes of `sculpting with flow' \cite{ristroph2018sculpting} have been examined in the context of a single body \cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is coupled through the flow \cite{hewett2017evolution}.
 From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
@@
 In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}.
-Their formulation was flexible enough to simulate a {\em mobile} body that erodes in various background flows (uniform flow, shear flow, etc.).
-An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.
-In the present work, we aim to simulate the erosion of a porous medium and further we choose to fix the bodies to their initial locations.
-Thus, instead than simulating a single, mobile body as in \cite{mit-spa2016}, we will simulate the erosion of many, immobile bodies.
-Furthermore, we will employ a standard double-layer formulation, as it allows us to easily calculate bulk quantities such as vorticity, pressure, and velocity in a post-processing step.
-
-For these porous network simulations, it is essential to resolve the nonlocal effects between the different bodies.
+The flexibility of their formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).
+Another advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.
+In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations.
+Thus, rather than a single, mobile body as considered in \cite{mit-spa2016}, we will simulate the erosion of many, immobile bodies.
+Although the traction formulation has several attractive features, we will instead employ a standard double-layer formulation, since it allows us to easily calculate bulk quantities such as vorticity, pressure, and velocity, that will facilitate our understanding of the erosion.
+
+For the porous network simulations considered here, it is essential to resolve nonlocal effects between the different bodies.
 BIEs naturally resolve these interactions, and they have been used extensively to simulate viscous fluids in complex geometries, including porous media flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.
@@
 
-With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
-In particular, consider the corner formed at the front and rear of the body.
-Locally, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge; see Fig.~\ref{corner} for a schematic.
-We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface~\cite{moo-ris-chi-zha-she2013, moore2017riemann}.
-For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$ (in this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
-
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
+With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
+In particular, consider the corner formed at the front and rear of the body.
+Locally, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge; see Fig.~\ref{corner} for a schematic.
+We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface~\cite{moo-ris-chi-zha-she2013, moore2017riemann}.
+For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$ (in this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
+
 The corresponding stream function is biharmonic, $\Delta^2 \psi = 0$, and the ansatz $\psi = r^{\lambda}f(\theta)$ gives the 4th-order ODE~\cite{poz1997}
@@
 \subsection{Fixed-area simulations}
-
-We now aim to measure the opening angles formed in the numerical simulations to compare against the above prediction.
-However, Section~\ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
-To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
-\begin{align}
-\Vn \leftarrow \Vn - \mean{\Vn} \, .
-\end{align}
-This modification allows erosion to sculpt the shape as it would normally, but with the area artificially held fixed.
 
@@
 % Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
+
+We now aim to measure the opening angles formed in the numerical simulations to compare against the above prediction.
+However, Section~\ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
+To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
+\begin{align}
+\Vn \leftarrow \Vn - \mean{\Vn} \, .
+\end{align}
+This modification allows erosion to sculpt the shape as it would normally, but with the area artificially held fixed.
 

### 2018-04-10 docs/methods/erosion_methods.tex
NM

@@
 Thus, rather than a single, mobile body as considered in \cite{mit-spa2016}, we will simulate the erosion of many, immobile bodies.
-Although the traction formulation has several attractive features, we will instead employ a standard double-layer formulation, since it allows us to easily calculate bulk quantities such as vorticity, pressure, and velocity, that will facilitate our understanding of the erosion.
+Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities, such as vorticity, pressure, and velocity, that will assist our understanding of the erosion process.
 

### 2018-04-10 docs/methods/erosion_methods.tex
NM

@@
 In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations.
-Thus, rather than a single, mobile body as considered in \cite{mit-spa2016}, we will simulate the erosion of many, immobile bodies.
-Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities, such as vorticity, pressure, and velocity, that will assist our understanding of the erosion process.
+Thus, rather than a {\em single, mobile} body as considered in \cite{mit-spa2016}, we aim to simulate the erosion of {\em many, immobile} bodies.
+Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities (e.g.~vorticity, pressure, and velocity) that will assist our understanding of the erosion process.
 

### 2018-04-10 docs/methods/erosion_methods.tex
added references to conclusions

@@
 Sedimentation requires overcoming a few challenges.
-First, the bodies must be mobile, as has been accomplished in previous work (cite).
+First, the bodies must be mobile, as has been accomplished in previous work for dense concentrations of deformable and rigid bodies~\cite{qua-bir2014a, cor-gre-rac-vee2017, cor-vee2017, kli-tor2016b, rac-gre2016}.
 Second, contacts and overlap between bodies must be prevented.
-This second requirement has been recognized as quite a challenge, with many novel methods developed to treat it (CITE STUFF HERE).
+This second requirement has been recognized as quite a challenge, with many novel methods developed to treat it~\cite{lu-rah-zor2017, kab-qua-bir2018, san-mo1994}.
 Incorporation of one or more of these schemes, will enable simulations of a porous medium undergoing simultaneous erosion and sedimentation.

### 2018-04-11 docs/methods/erosion_methods.tex
small changes to language and formatting

@@
 In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
-Such processes of `sculpting with flow' \cite{ristroph2018sculpting} have been examined in the context of a single body \cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is coupled through the flow \cite{hewett2017evolution}.
+Such processes of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is coupled through the flow~\cite{hewett2017evolution}.
 From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
@@
 \paragraph{Contributions}
-To perform this simulation of Stokesian erosion of a porous media, two fast and accurate methods are employed---one to solve the fluid equations and the other to integrate the eroding grains.
+To perform this simulation of Stokesian erosion of a porous media, two fast and accurate methods are employed---one to solve the fluid equations and the other to time advance the eroding grains.
 The fluid equations are reformulated in terms of a boundary integral equation (BIE)~\cite{poz1992}.
@@
 \paragraph{Related Work}
-In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}.
+In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions~\cite{mit-spa2016}.
 The flexibility of their formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).
@@
 In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations.
-Thus, rather than a {\em single, mobile} body as considered in \cite{mit-spa2016}, we aim to simulate the erosion of {\em many, immobile} bodies.
+Thus, rather than a {\em single, mobile} body as considered in~\cite{mit-spa2016}, we aim to simulate the erosion of {\em many, immobile} bodies.
 Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities (e.g.~vorticity, pressure, and velocity) that will assist our understanding of the erosion process.
@@
 Here,
-\begin{align*}
+\begin{align}
   \NN_0[\eeta](\xx) = \int_{\Gamma} 
     (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy
-\end{align*}
+\end{align}
 removes the rank one null space resulting from the flux-free requirement of $\ff$.
@@
 Once the density function, Stokeslets, and rotlets are computed, any desired quantity, including the shear stress, can be computed.  The shear stress is
-\begin{align*}
+\begin{align}
   \tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss \, .
-\end{align*}
+\end{align}
 The reader may notice an unusual sign convention above, but this is simply a consequence of our conventions for $\nn$ and $\ss$ (see Fig.~\ref{fig:schematic}).
@@
 The equations for the Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are also discretized with the trapezoid rule.
-Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system is solved is
+Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system that solved is
 \begin{equation}
@@
       \Delta s_j \, , \\ 
-    \mu_\ell &= \sum_{\xx_j \in \gamma_\ell}
+    \xi_\ell &= \sum_{\xx_j \in \gamma_\ell}
       {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j \, ,
@@
 \end{equation}
-Then, identical to how the shear stress is computed~\eqref{eqn:stressOddEven}, odd-even integration is used to evaluate this layer potential for pressure, and the jump condition in~\eqref{eqn:pressureJump} is computed with Fourier differentiation.
+Then, identical to how the shear stress is computed in~\eqref{eqn:stressOddEven}, odd-even integration is used to evaluate this layer potential for pressure, and the jump condition in~\eqref{eqn:pressureJump} is computed with Fourier differentiation.
 
@@
 Sedimentation requires overcoming a few challenges.
-First, the bodies must be mobile, as has been accomplished in previous work for dense concentrations of deformable and rigid bodies~\cite{qua-bir2014a, cor-gre-rac-vee2017, cor-vee2017, kli-tor2016b, rac-gre2016}.
+First, the bodies must be mobile, as has been accomplished in previous work for dense concentrations of deformable and rigid bodies~\cite{qua-bir2014a, cor-gre-rac-vee2017, cor-vee2017, kli-tor2016b, rac-gre2016, qua-bir2016}.
 Second, contacts and overlap between bodies must be prevented.

### 2018-04-11 docs/methods/significance_and_novelty.tex
added significance and novelty

\documentclass[11pt]{article}

\begin{document}
\begin{center}
  {\bf Significance and Novelty} \\
  A boundary-integral framework to simulate \\ viscous erosion of a
  porous medium \\
  Bryan D.~Quaife and M.~Nicholas J.~Moore
\end{center}
In this paper we describe a numerical method to simulate viscous erosion
of a two-dimensional porous medium with a long-term goal of simulating
groundwater erosion.  Based on previous experimental results, the
erosion rate is assumed to be proportional to the magnitude of the shear
stress.  To increase the numerical stability, this law is supplemented
with a regularization term that penalizes high curvature regions.  We
avert stiffness with a change of variables that results in a system of
differential equations with a stiff linear, and these are solved with a
second-order exponential time stepping method.

To compute the shear stress, we assume the fluid is viscous---a
standard model for groundwater flow.  Then, the governing equations
(incompressible Stokes) are formulated as a well-conditioned boundary
integral equation formulation.  The integral equation resolves
inter-body interactions and is discretized with spectral accuracy and
solved with fast-multipole-accelerated GMRES.  Then, to further
characterize the flow, we compute the drag of the bodies and the
vorticity in the bulk which is used to characterize the erosion rate.

The numerical simulation of a single eroding body is compared with
analytical solutions.  We show good agreement between the eroding body's
numerical and analytical opening angle, area, and drag.  Then, erosion
is simulated for multi-body problems. We observe channelization of the
flow caused by long flat faces that develop between bodies that are
initially close together.  This has a large effect on the time-dependent
drag and resistance of the flow.

\end{document}

### 2018-04-12 docs/methods/significance_and_novelty.tex
worked on significance

@@
 In this paper we describe a numerical method to simulate viscous erosion
-of a two-dimensional porous medium with a long-term goal of simulating
-groundwater erosion.  Based on previous experimental results, the
-erosion rate is assumed to be proportional to the magnitude of the shear
-stress.  To increase the numerical stability, this law is supplemented
-with a regularization term that penalizes high curvature regions.  We
-avert stiffness with a change of variables that results in a system of
-differential equations with a stiff linear, and these are solved with a
-second-order exponential time stepping method.
+of a two-dimensional porous medium.  This is a step towards a long-term
+goal of developing stable, accurate, and fast numerical methods to
+simulate and understand groundwater erosion.
 
-To compute the shear stress, we assume the fluid is viscous---a
-standard model for groundwater flow.  Then, the governing equations
-(incompressible Stokes) are formulated as a well-conditioned boundary
-integral equation formulation.  The integral equation resolves
-inter-body interactions and is discretized with spectral accuracy and
-solved with fast-multipole-accelerated GMRES.  Then, to further
-characterize the flow, we compute the drag of the bodies and the
-vorticity in the bulk which is used to characterize the erosion rate.
+Based on previous experimental results, the erosion rate is assumed to
+be proportional to the magnitude of the shear stress.  To increase the
+numerical stability, this law is supplemented with a regularization term
+that penalizes high curvature regions and smooths the erosion rate at
+regions where the shear stress changes sign.  We use a change of
+variables to linearize stiffness, and the resulting system of
+differential equations is solved with a second-order exponential time
+stepping method.
+
+To compute the shear stress, we assume the fluid is viscous---a standard
+model for groundwater flow.  The governing equations (incompressible
+Stokes) are formulated as a well-conditioned boundary integral equation.
+The integral equation discretion resolves the non-negligible inter-body
+interactions with spectral accuracy and is solved with
+fast-multipole-accelerated GMRES.  To further characterize the flow, we
+compute the drag of the bodies and the vorticity in the bulk which is
+used to characterize the erosion rate.
 

### 2018-04-12 docs/methods/research_highlights.tex
added research highlights

\documentclass[11pt]{article}

\begin{document}
\begin{center}
  {\bf Research Highlights} \\
  A boundary-integral framework to simulate \\ viscous erosion of a
  porous medium \\
  Bryan D.~Quaife and M.~Nicholas J.~Moore
\end{center}

\begin{itemize}
  \item A highly accurate numerical method for the simulation of erosion
    in a two-dimensional porous medium that resolves inter-body
    interactions
  \item A method to allow for erosion while artificially fixing the area
    so that numerical and analytical results can be compared
  \item A demonstration of channelization occurring in porous medium and
    the resulting drag and resistivity of the flow

\end{itemize}

\end{document}

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large-scale land formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}.
-Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion}.
+Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
 Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
 
-Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
@@
 \includegraphics[width = 0.80 \textwidth]{./figs/50bod.pdf}
-\caption{\label{fig:50bodies} A time lapse of 50 bodies eroding in a viscous flow.
-The boundary conditions are a constant pressure drop that creates a flow from the left to right.
-The rate of erosion is proportional to the shear stress which is equivalent to the vorticity evaluated on the bodies.
-The colors represent the vorticity, so regions with large vorticity (in magnitude) are regions where the flow will erode the fastest.}
+\caption{\label{fig:50bodies} Simulation of 50 bodies eroding in Stokes flow under the action of fluid-mechanical shear.
+The flow is horizontal (left to right) and the 6 snapshots are evenly spaced in time.
+Color represents vorticity, which provides a convenient way to visualize local shear rates.
+Erosion not only diminishes the size of the bodies but also alters their shapes considerably.
+A few well-defined channels develop in the space between bodies.
+Several of the bodies vanish in finite time and the simulation continues.
+}
 \end{center}

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
-Such processes of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is coupled through the flow~\cite{hewett2017evolution}.
+Such examples of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is coupled through the flow~\cite{hewett2017evolution}.
 From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
 First, since the medium is composed of many individual constituents, multi-body interactions must be considered.
-Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than in any other regime.
-% in particular close-contacts?
+Second, the tight-packing present in many porous-media applications means that close-contacts must be resolved.
+Finally, long-range effects inherent to Stokes flow couples the shape evolution of {\em all} bodies, more so than in any other flow regime.
+
+% close contact, close proximity, nearby
 

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 
-% close contact, close proximity, nearby
-
-The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
+Ultimately, the methods developed here will lead to high-fidelity simulations of multi-body Stokes erosion as illustrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
 Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
@@
 As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
-Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them.
-In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.
+In particular, several bodies develop corner-like features and nearly flat faces, with straight channels intervening between them.
+In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient way to visualize local erosion rates.
+Several bodies vanish in finite time and the simulation continues without interruption.
 
@@
 A few well-defined channels develop in the space between bodies.
-Several of the bodies vanish in finite time and the simulation continues.
+Several of the bodies vanish in finite time and the simulation continues without interruption.
 }
@@
 \paragraph{Contributions}
-To perform this simulation of Stokesian erosion of a porous media, two fast and accurate methods are employed---one to solve the fluid equations and the other to time advance the eroding grains.
+To perform the above simulation, two fast and accurate methods are employed---one to solve the fluid equations and the other to evolve the eroding grains.
 The fluid equations are reformulated in terms of a boundary integral equation (BIE)~\cite{poz1992}.
-Since the boundary conditions are Dirichlet, we use a double-layer potential formulation so that the resulting BIE is second-kind.
-This second-kind BIE is discretized with the spectrally accurate trapezoid rule~\cite{tre-wei2014} which results in a well-conditioned dense linear system for an unknown density function, and the linear system is solved using fast-multipole-accelerated GMRES~\cite{saa-sch1986}.
-Once the density function is computed, the shear stress is computed with a spectrally accurate odd-even quadrature rule~\cite{sid-isr1988}.
-In addition, the pressure and vorticity are computed in the fluid bulk (Fig.~\ref{fig:50bodies}) with an upsampled trapezoid rule to assist with visualizing the effect of erosion in porous media.
-
-Next, the computed shear stress is used to evolve the solid boundaries.
-Tracking the interface of fluid-structure interaction problems with a long time horizon is particularly difficult as the mesh can become distorted and tangled.
+Since the boundary conditions are Dirichlet, we employ a double-layer potential so that the resulting BIE is second-kind.
+This second-kind BIE is discretized with a spectrally accurate trapezoid rule~\cite{tre-wei2014} which results in a well-conditioned dense linear system for an unknown density function.
+The linear system is solved using fast-multipole-accelerated GMRES~\cite{saa-sch1986}.
+Once the density function is determined, we compute the shear stress with a spectrally accurate odd-even quadrature rule~\cite{sid-isr1988}.
+
+At the next stage, we must use this shear stress to advance solid boundaries.
+Tracking fluid-structure interfaces with long time horizons presents numerical challenges in that the underlying mesh can become distorted and tangled.
 Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
-The interface tracking issues are addressed in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect the interface dynamics; second, we introduce a curvature-penalizing term into the normal interface velocity to suppress high-frequency oscillations associated with nearly singular curvature.
-The interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.
+We address these tracking issues in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect dynamics; second, we suppress high-frequency oscillations in the interface evolution via a curvature-penalization.
+The interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term.
+This term can be easily be handled in a numerically stable fashion with an exponential integrator.
+Once the simulation is complete, we perform a post-processing step in which we compute bulk properties, such as vorticity and pressure, using an upsampled trapezoid rule.
 
 We supplement our primarily computational study with a few analytical results.
-In particular, we find a single body eroding in Stokes flow tends to a slender, for-aft symmetric form with sharp corners at its front and rear.
-By appealing to the principle that erosion more evenly distributes the shear stress along the surface, we can analytically predict the opening angle formed at the front and rear.
-In addition, drag laws from slender-body theory allows us to derive scaling laws for the rate of the body's area and drag reduction.
-These analytical results, in addition to having value in their own right, allow us to conclusively validate our simulation.
+In particular, our simulation shows that a single eroding body tends to a slender, for-aft symmetric form characterized by nearly uniform shear stress along its surface.
+This body features sharp corners at its front and rear stagnation points.
+The principle of long-time uniform stress combined with some local analysis leads to an analytical prediction for the opening angles formed at the front and rear.
+Additionally, drag laws from slender-body theory allows us to derive scaling laws for the rate of the body's area and drag reduction.
+These analytical results, in addition to their own intrinsic value, allow us to conclusively validate the numerical simulation.
 
@@
 We make two fundamental design choices in our simulation: first, we restrict attention to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
-The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium.
-While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible.
-The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation.
-While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
-We therefore defer the study of these effects to future work.
+The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, enabling accurate characterization of porous-medium erosion.
+While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated and makes porous-medium simulations less feasible.
+Second, the assumption of immobile bodies affords a simple framework to analyze the effects of erosion in isolation.
+While other mechanisms, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
+We therefore defer to future work the incorporation of these additional mechanisms.
 
 \paragraph{Related Work}
-In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions~\cite{mit-spa2016}.
+In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions~\cite{mit-spa2016}.
 The flexibility of their formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).
-Another advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.
+An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.
 In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
-First, since the medium is composed of many individual constituents, multi-body interactions must be considered.
-Second, the tight-packing present in many porous-media applications means that close-contacts must be resolved.
-Finally, long-range effects inherent to Stokes flow couples the shape evolution of {\em all} bodies, more so than in any other flow regime.
+First, since the medium is composed of many individual constituents, multiple bodies must be considered.
+Second, the tight-packing present in typical porous-media applications means that close-range interactions must be resolved.
+Finally, long-range effects inherent to Stokes flow couples the shape evolution of {\em all} bodies to a greater degree than any other flow regime.
 

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 While other mechanisms, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
-We therefore defer to future work the incorporation of these additional mechanisms.
+We therefore defer the incorporation of these mechanisms to future work.
 
@@
 In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions~\cite{mit-spa2016}.
-The flexibility of their formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).
+The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).
 An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion}.
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
@@
 
-Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, dallaston2015channelization, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion, domokos2014river}.
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

--- 2018-04-12 docs/methods/erosion_methods.tex
@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, perron2009formation, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, domokos2014river}.
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

--- 2018-04-12 docs/methods/erosion_methods.tex
@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, perron2009formation, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, berhanu2012shape, domokos2014river}.
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

--- 2018-04-12 docs/methods/erosion_methods.tex
@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015}, to centimeter-scale features and patterns~\cite{daerr2003erosion, domokos2014river}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, perron2009formation, abrams2009growth, petroff2011geometry, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, berhanu2012shape, domokos2014river}.
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

--- 2018-04-12 docs/methods/erosion_methods.tex
@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, perron2009formation, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, domokos2014river}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, perron2009formation, abrams2009growth, petroff2011geometry, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, berhanu2012shape, nienhuis2014wavelength, domokos2014river}.
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
@@
 
-Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, dallaston2015channelization, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann, lopez2018cfd} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, dallaston2015channelization, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
 In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
@@
 We address these tracking issues in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect dynamics; second, we suppress high-frequency oscillations in the interface evolution via a curvature-penalization.
-The interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term.
+The interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term \cite{hou-low-she1994}.
 This term can be easily be handled in a numerically stable fashion with an exponential integrator.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, perron2009formation, abrams2009growth, petroff2011geometry, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, berhanu2012shape, nienhuis2014wavelength, domokos2014river}.
-Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{bear2013dynamics, pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.
+Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~soil, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
+Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater \cite{bear2013dynamics, cao2010coupled} and the aforementioned bio-fluid applications.
 
 Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann, lopez2018cfd} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, dallaston2015channelization, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
-In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on.
-Such examples of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is coupled through the flow~\cite{hewett2017evolution}.
+In these cases, the fluid alters the morphology of the immersed structures, which in turn modifies the surrounding flow field, and so on.
+Such examples of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shapes coevolve as mediated by the flow~\cite{hewett2017evolution}.
 From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
 First, since the medium is composed of many individual constituents, multiple bodies must be considered.
-Second, the tight-packing present in typical porous-media applications means that close-range interactions must be resolved.
+Second, the tight-packing present in typical porous-media applications implies that close-range interactions must be resolved.
 Finally, long-range effects inherent to Stokes flow couples the shape evolution of {\em all} bodies to a greater degree than any other flow regime.

### 2018-04-12 docs/methods/erosion_methods.tex
NM

@@
 For example, the spacing between bodies 1 \& 2 is initially quite small, but by the second frame, is comparable to the spacing between bodies 3 \& 4.
-Moreover, the bodies tend to develop flat faces at these points of near contact, leading to the appearance of straight channels between bodies.
+Moreover, the bodies tend to develop flat faces at the sites of near contact, leading to the appearance of straight channels between bodies.
 Straight channels can be seen, for example, between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
@@
 Notice that the overall vorticity magnitude increases in time as the flow rate $\umax$ increases due to keeping the pressure drop fixed.
+
+Looking back at the 50-body simulation in Fig.~\ref{fig:50bodies}, many of these same features can be observed.
+Bodies tends to develop corner-like features connected by flat faces, which causes them to appear polygonal.
+Nearly straight channels form between the bodies, and a few of these appear to be preferred channels which transmit the most flow and therefore open the fastest.
 
@@
 
-In work currently underway, we are using this method to examine more thoroughly how bulk and statistical properties of the porous medium change with erosion.
+In work currently underway, we are using this method to more thoroughly examine how bulk and statistical properties of the porous medium change with erosion.
 We are particularly interested in the development of anisotropic permeability of the medium.
 Preliminary simulations show promise.
-We furthermore would like to investigate how the statistical distribution of bodies size, shape, and orientation changes over time.
+We furthermore would like to investigate how the statistical distribution of body size, shape, and alignment changes over time.
 We hope to report on these topics soon.

### 2018-04-13 docs/methods/erosion_methods.tex
NM

@@
 \begin{abstract} 
-We develop numerical methods to simulate the fluid-mechanical erosion of many bodies in a two-dimensional Stokes flow.
+We develop numerical methods to simulate the fluid-mechanical erosion of many bodies in two-dimensional Stokes flow.
 The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with grain-scale resolution.
@@
 First, since the medium is composed of many individual constituents, multiple bodies must be considered.
-Second, the tight-packing present in typical porous-media applications implies that close-range interactions must be resolved.
+Second, the dense packing present in typical porous-media applications requires close-range interactions to be resolved.
 Finally, long-range effects inherent to Stokes flow couples the shape evolution of {\em all} bodies to a greater degree than any other flow regime.
@@
 
-%Comparing the 50 and 6-body simualtions... Though the area fractions of the two simulations are nearly the same, the 50-body configuration provides about 5 times more resistance.
-
-% Good word: Spontaneous channelization
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-04-13 docs/methods/significance_and_novelty.tex
added accidentiy deleted significance file

@@
 \begin{center}
-  {\bf Significance and Novelty} \\
+  {\bf Significant and Novelty} \\
   A boundary-integral framework to simulate \\ viscous erosion of a
@@
 \end{center}
+
 In this paper we describe a numerical method to simulate viscous erosion
@@
 variables to linearize stiffness, and the resulting system of
-differential equations is solved with a second-order exponential time
+differential equations is solved with a second- order exponential time
 stepping method.
 
-To compute the shear stress, we assume the fluid is viscous---a standard
+To compute the shear stress, we assume the fluid is viscous—--a standard
 model for groundwater flow. The governing equations (incompressible
@@
 The integral equation discretion resolves the non-negligible inter-body
-interactions with spectral accuracy and is solved with
+inter- actions with spectral accuracy and is solved with
 fast-multipole-accelerated GMRES. To further characterize the flow, we
@@
 analytical solutions. We show good agreement between the eroding body's
-numerical and analytical opening angle, area, and drag.  Then, erosion
-is simulated for multi-body problems. We observe channelization of the
-flow caused by long flat faces that develop between bodies that are
-initially close together.  This has a large effect on the time-dependent
-drag and resistance of the flow.
+numerical and analytical opening angle, area, and drag. Then, erosion is
+simulated for multi-body problems. We observe channelization of the flow
+caused by long flat faces that develop between bodies that are initially
+close together. This has a large effect on the time-dependent drag and
+resistance of the flow.
 

### 2018-04-14 docs/methods/erosion_methods.tex
NM

@@
 \includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
-\caption{Area and drag: (a) The body area measured in the simulations (black) shown against the scaling-law prediction~\eqref{area_predict} (dotted red), the two of which agree closely.
-(b) The horizontal drag (black) on the body as it erodes, along with the viscous (green) and pressure (blue) contributions.
-The scaling prediction can be rearranged to give estimate~\eqref{dragscaling} for the viscous drag (dotted red).}
+\caption{Area and drag: (a) The area of the eroding body as measured in the simulations (black) shown against scaling law~\eqref{area_predict} (dotted red).
+The prediction and measurements agree closely.
+(b) The total horizontal drag exerted by body (black), along with the viscous (green) and pressure (blue) contributions.
+Slender-body theory yields the drag estimate~\eqref{dragscaling} (dotted red), which agrees well with the simulation as $t \to t_f$.}
 \label{area_drag}
@@
 Therefore, the shape observed in our simulation is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape.
-How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{shrink_intface}(b).
+How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{fixed_intface}(b).
 

### 2018-04-14 docs/methods/erosion_methods.tex
NM

@@
 Our fluid solver is based on a second-kind boundary integral formulation of the Stokes equations that is discretized with a spectrally-accurate Nystr\"om method and solved with fast-multipole-accelerated GMRES.
-To evolve the individual grains under shear-driven erosion, we regularize via curvature-penalization and solve the associated system using the {\thL} formulation.
-This framework allows numerically stable treatment of stiff terms, thus permitting large time steps.
+The fluid solver provides the surface shear stress which is used to advance solid boundaries.
+We regularize interface evolution via curvature penalization and solve the associated system using the {\thL} formulation.
+This framework allows numerically stable treatment of stiff terms and therefore permits large time steps.
 The overall accuracy of our method is spectral in space and second-order in time.
 The method is computationally efficient, with the fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration, a mesh-independent number of GMRES iterations, and a one-time $\mathcal{O}(N^2)$ computation to compute the shear stress.
-We benchmark single-body results against analytical predictions.
-In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact.
+We benchmark single-body results against analytical predictions for the limiting morphology and vanishing rate.
+Multibody simulations reveal the spontaneous formation of channels between bodies of close initial proximity.
 The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.

### 2018-04-14 docs/methods/erosion_methods.tex
NM

@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large land formations~\cite{han1969, perron2009formation, abrams2009growth, petroff2011geometry, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, berhanu2012shape, nienhuis2014wavelength, domokos2014river}.
+Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from massive land formations~\cite{han1969, perron2009formation, abrams2009growth, petroff2011geometry, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, berhanu2012shape, nienhuis2014wavelength, domokos2014river}.
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~soil, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
@@
 
-Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann, lopez2018cfd} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, dallaston2015channelization, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
-In these cases, the fluid alters the morphology of the immersed structures, which in turn modifies the surrounding flow field, and so on.
-Such examples of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shapes coevolve as mediated by the flow~\cite{hewett2017evolution}.
+Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann, lopez2018cfd} and the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, dallaston2015channelization, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
+In these cases, the fluid alters the morphology of immersed structures, which in turn modifies the surrounding flow field, and so on.
+Such examples of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is intertwined~\cite{hewett2017evolution}.
 From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
@@
 Second, the dense packing present in typical porous-media applications requires close-range interactions to be resolved.
-Finally, long-range effects inherent to Stokes flow couples the shape evolution of {\em all} bodies to a greater degree than any other flow regime.
+Finally, long-range effects inherent to the Stokes limit couples the shape evolution of {\em all} bodies to a greater degree than any other regime.
 
@@
 
-At the next stage, we must use this shear stress to advance solid boundaries.
+At the next stage, we must use the shear stress to advance solid boundaries.
 Tracking fluid-structure interfaces with long time horizons presents numerical challenges in that the underlying mesh can become distorted and tangled.
 Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
-We address these tracking issues in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect dynamics; second, we suppress high-frequency oscillations in the interface evolution via a curvature-penalization.
+We address these tracking issues in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect dynamics; second, we suppress high-frequency oscillations in the interface evolution via curvature penalization.
 The interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term \cite{hou-low-she1994}.
@@
 In particular, our simulation shows that a single eroding body tends to a slender, for-aft symmetric form characterized by nearly uniform shear stress along its surface.
-This body features sharp corners at its front and rear stagnation points.
+This body exhibits sharp corners at its front and rear.
 The principle of long-time uniform stress combined with some local analysis leads to an analytical prediction for the opening angles formed at the front and rear.
-Additionally, drag laws from slender-body theory allows us to derive scaling laws for the rate of the body's area and drag reduction.
+Additionally, slender-body theory gives rise to scaling laws for the reduction rate of the body's area and drag.
 These analytical results, in addition to their own intrinsic value, allow us to conclusively validate the numerical simulation.
@@
 \paragraph{Limitations}
-We make two fundamental design choices in our simulation: first, we restrict attention to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
-The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, enabling accurate characterization of porous-medium erosion.
+We make two fundamental design choices in the simulations described here: first, we restrict attention to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
+By restricting to two dimensions, we can simulate many bodies (up to $50$ in this manuscript) with high resolution, enabling accurate characterization of porous-medium erosion.
 While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated and makes porous-medium simulations less feasible.
-Second, the assumption of immobile bodies affords a simple framework to analyze the effects of erosion in isolation.
+Meanwhile, the second assumption of immobile bodies affords a simple framework to explore the effects of erosion in isolation.
 While other mechanisms, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
-We therefore defer the incorporation of these mechanisms to future work.
+We therefore defer their study to future work.
 
 \paragraph{Related Work}
-In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions~\cite{mit-spa2016}.
+In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate the viscous erosion of a single body in three dimensions~\cite{mit-spa2016}.
 The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).
-An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.
+An advantage of the traction formulation is that is directly provides the shear stress needed to evolve surfaces.
 In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations.

### 2018-04-14 docs/methods/erosion_methods.tex
NM

@@
 We develop numerical methods to simulate the fluid-mechanical erosion of many bodies in two-dimensional Stokes flow.
-The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with grain-scale resolution.
+The broad aim is to simulate the erosion of a porous medium (e.g.~groundwater flow) with grain-scale resolution.
 Our fluid solver is based on a second-kind boundary integral formulation of the Stokes equations that is discretized with a spectrally-accurate Nystr\"om method and solved with fast-multipole-accelerated GMRES.
@@
 
-Ultimately, the methods developed here will lead to high-fidelity simulations of multi-body Stokes erosion as illustrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
+Ultimately, the methods developed here will lead to high-fidelity simulations of multibody Stokes erosion as illustrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
 Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
@@
 
-To validate the multi-body simulations with this new fixed-pressure-drop condition, we report a convergence test in Table~\ref{convtab2}.
+To validate the multibody simulations with this new fixed-pressure-drop condition, we report a convergence test in Table~\ref{convtab2}.
 In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$.
@@
 \caption{\label{fig:mbodyplots} 
-Multi-body simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation.
+Multibody simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation.
 (a) The area fraction of the eroding bodies versus time.
@@
 
-To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multi-body simulations.
+To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
 In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}.

### 2018-04-14 docs/methods/erosion_methods.tex
NM

@@
 The fluid solver provides the surface shear stress which is used to advance solid boundaries.
-We regularize interface evolution via curvature penalization and solve the associated system using the {\thL} formulation.
-This framework allows numerically stable treatment of stiff terms and therefore permits large time steps.
+We regularize interface evolution via curvature penalization using the {\thL} formulation, which affords numerically stable treatment of stiff terms and therefore permits large time steps.
 The overall accuracy of our method is spectral in space and second-order in time.

### 2018-04-14 docs/methods/erosion_methods.tex
NM

@@
 Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~soil, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater \cite{bear2013dynamics, cao2010coupled} and the aforementioned bio-fluid applications.
+Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow---the most relevant regime for groundwater \cite{bear2013dynamics, cao2010coupled} and the aforementioned bio-fluid applications.
 
@@
 Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
-In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress---a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
+In particular, we take the local erosion rate to be proportional to the magnitude of the shear stress---a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
 As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
@@
 The constant of proportionality of the erosion law only sets the time scale, so we have set $\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.
-For the sake of numerical stability, we modify this law in Section~\ref{sec:thetaL}.
+\todo[inline]{The above sentence is awkard.
+Could it be rephrased?
+First, the reader probably does not know what constant of proportionality you are referring to because we do not have one in the equation.
+Second, there are too many 'ofs' in a row.}
+For the sake of numerical stability, we will modify this law in Section~\ref{sec:thetaL}.
 
@@
 \end{figure}
+\todo[inline]{Here is an example where you can avoid the passive voice because it is totally unnecessary.
+Instead of saying 'the bodies are eroded', simply say 'the bodies erode'.
+Also, a fluid cannot be Stokesian, since the Reynolds number depends on the length scale and velocity scale.
+It is the flow that is Stokes.}
 
@@
 Instead, make a slight modification to the erosion model in Section~\ref{sec:thetaL} which allows us to control the smoothness of the grains.
+\todo[inline]{There is a typo in the above sentence (missing 'we'?).
+Also, technically there is  a dangling participle here; i.e.~is it the erosion model which is in Section 2.3 or the modification?
+A slight rephrasing might clarify.}
 In this manner, the BIE as described above can be applied.
@@
 Once the density function is found, Section~\ref{sec:shearStress} describes how the shear stress~\eqref{eqn:shearStressLP} is computed.
-Then, in Section~\ref{sec:timeStepping}, a time stepping method for evolving the interface according to equations~\eqref{eqn:Levo1}--\eqref{eq:xsurf} are described.
-
-To form stable simulations with long time horizons, we use numerical methods that achieve spectral accuracy in space, second-order accuracy in time, and maintain an equispaced discretization of the bodies.
+Then, Section~\ref{sec:timeStepping} describes a time stepping method for advancing the interface according to equations~\eqref{eqn:Levo1}--\eqref{eq:xsurf}.
+
+To create stable simulations with long time horizons, we use numerical methods that achieve spectral accuracy in space, second-order accuracy in time, and maintain an equispaced discretization of the bodies.
 The boundaries are represented in Fourier space, giving us a set of discretization points $\xx_i$ of each body, and all derivatives and integrals (the arclength, curvature, and mean values) are computed with spectral accuracy using the Fourier representation.
@@
 Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system that solved is
+\todo[inline]{Typo above}
 \begin{equation}
@@
 We have applied the trapezoid rule since all the integrands are smooth and periodic, and this guarantees that the numerical solutions converges to the true solution with spectral accuracy~\cite{tre-wei2014}.
+\todo[inline]{The above sentence strikes me as awkward and verbose. Rephrase? \\
+How about this: Since all integrands are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy.}
 

### 2018-04-14 docs/methods/erosion_methods.tex
NM

@@
 \todo[inline]{There is a typo in the above sentence (missing 'we'?).
-Also, technically there is  a dangling participle here; i.e.~is it the erosion model which is in Section 2.3 or the modification?
+Also, technically there is  a dangling participle; i.e.~is it the erosion model which is in Section 2.3 or the modification?
 A slight rephrasing might clarify.}
@@
 However, this calculation is only performed once per time step as opposed to the velocity double-layer potential, where we do employ the FMM, that must be evaluated at each GMRES iteration.
+\todo[inline]{The above sentence is confusing. Try to rephrase and shorten it.}
 In future work, we plan to use a kernel-independent FMM~\cite{yin-bir-zor2004} to evaluate the shear stress with $\bigO(N)$ operations.
@@
 
-First, we must address a second potential source of numerical instability.
+First, we must address another potential source of numerical instability.
 The erosion law~\eqref{eqn:Vn} depends on the {\em absolute value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$ changes sign, i.e.~at a stagnation point.
 The corner in $\atau$ introduces high frequencies into~\eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
-To avoid these difficulties, we smooth $\atau$ via a narrow Gaussian filter of width $\sigma$
+To avoid these difficulties, we smooth $\atau$ via a narrow Gaussian filter of width $\sigma \ll 1$
 \begin{align}
@@
 The three simulations are all very close to one another, demonstrating convergence as $\eps, \sigma \to 0$.
-In the simulation with these least smoothing ($\eps = \sigma = 5/1024$), the aspect ratio tends to a value of 2.7 in long time.
+In the simulation with the least smoothing ($\eps = \sigma = 5/1024$), the aspect ratio tends to a value of 2.7 in long time.
 
@@
 The last column of the table shows the CPU time taken for the simulation to run on a single-processor machine, demonstrating a nearly linear increase in computational time.
-Though the main parts of the algorithm are easily paralyzed, the single-processor times provide a simple assessment of method's complexity.
+Though the main parts of the algorithm are easily paralyzed, the single-processor times provide a simple assessment of the overall complexity.
 
@@
 Looking back at the 50-body simulation in Fig.~\ref{fig:50bodies}, many of these same features can be observed.
-Bodies tends to develop corner-like features connected by flat faces, which causes them to appear polygonal.
-Nearly straight channels form between the bodies, and a few of these appear to be preferred channels which transmit the most flow and therefore open the fastest.
+Bodies tend to develop corner-like features connected by flat faces, which causes them to appear polygonal.
+Nearly straight channels form between the bodies, and a few of these appear to be preferred channels which transmit the most flow and therefore widen the fastest.
 
@@
 To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
-In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}.
+In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation.
 First, Fig.~\ref{fig:mbodyplots}(a) shows the fraction of area occupied by the solid bodies as it varies in time.
@@
 Due to the logarithmic axis, the nearly linear trend seen in the figure corresponds to exponential growth of $\umax$.
-The change in area-fraction alone cannot account for this rapid growth, suggesting the reshaping process to be vital.
+The change in area fraction alone cannot account for this rapid growth, suggesting the reshaping process to be vital.
 In particular, the formation of channels observed in Fig.~\ref{fig:06bodies} may account for these higher flow rates.
 
-Naturally, the flow allowed by the medium is connected to the amount of drag the bodies exert.
+Naturally, the flow transmitted by the medium is tied to the amount of drag the bodies exert.
 We therefore show in Fig.~\ref{fig:mbodyplots}(c) the total drag exerted by all bodies as it varies in time.

### 2018-04-16 docs/methods/erosion_methods.tex
NM
addressed Nick's todo comments

@@
 \paragraph{Contributions}
-To perform the above simulation, two fast and accurate methods are employed---one to solve the fluid equations and the other to evolve the eroding grains.
+To perform the above simulation, two fast and accurate methods are
+employed---one to solve the fluid equations and the other to evolve the
+eroding bodies.
 The fluid equations are reformulated in terms of a boundary integral equation (BIE)~\cite{poz1992}.
@@
 where $\Vn$ is the normal velocity of the interface and $\mu$ is the fluid viscosity.
-The constant of proportionality of the erosion law only sets the time scale, so we have set $\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.
-\todo[inline]{The above sentence is awkard.
+A scaling constant often appears in the erosion model in~\eqref{eqn:erosionModel}, but in the Stokes limit, the constant only sets the time scale, so we have taken it to be one.
+For the sake of numerical stability, we will modify the erosion model in Section~\ref{sec:thetaL}.
+
+%The constant of proportionality of the erosion law only sets the time scale, so we have set $\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.  
+%\todo[inline]{The above sentence is awkard.
 Could it be rephrased?
@@
 Second, there are too many 'ofs' in a row.}
-For the sake of numerical stability, we will modify this law in Section~\ref{sec:thetaL}.
 
@@
 On the outer geometry $\Gamma$, a Hagen-Poiseuille flow is imposed.
-The bodies are eroded at a rate that is proportional to the magnitude of the shear stress applied by the Stokesian fluid.
+The bodies erode at a rate that is proportional to the magnitude of the shear stress applied by the fluid.
 The bodies are constrained to the middle third of the channel that is located between the dashed lines.}
 \end{figure}
-\todo[inline]{Here is an example where you can avoid the passive voice because it is totally unnecessary.
+%\todo[inline]{Here is an example where you can avoid the passive voice because it is totally unnecessary.
 Instead of saying 'the bodies are eroded', simply say 'the bodies erode'.
@@
 \end{equation}
-The boundary condition $\ff$ is the prescribed velocity $\UU$ on $\Gamma$, and it is zero on the eroding grains $\gamma$.
+The boundary condition $\ff$ is the prescribed velocity $\UU$ on
+$\Gamma$, and it is zero on the eroding bodies $\gamma$.
 In two dimensions, a BIE for a stream function formulation is possible~\cite{gre-kro-may1996}, but this does not extend to three dimensions.
@@
 One option is to modify our BIE to handle corners~\cite{rac-ser2017, ser-rok2016, hel2011, gil-hao-mar2014, bre2012}, but these methods require the corner's location, a non-uniform spaced mesh, or are ill-conditioned.
-Instead, make a slight modification to the erosion model in Section~\ref{sec:thetaL} which allows us to control the smoothness of the grains.
-\todo[inline]{There is a typo in the above sentence (missing 'we'?).
+Instead, we slightly modify the erosion model in Section~\ref{sec:thetaL} so that we can control the smoothness of the bodies.
+In this manner, the BIE as described above can be applied.
+
+%\todo[inline]{There is a typo in the above sentence (missing 'we'?).
 Also, technically there is  a dangling participle; i.e.~is it the erosion model which is in Section 2.3 or the modification?
 A slight rephrasing might clarify.}
-In this manner, the BIE as described above can be applied.
 
@@
 The equations for the Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are also discretized with the trapezoid rule.
-Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system that solved is
-\todo[inline]{Typo above}
+Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
+%\todo[inline]{Typo above}
 \begin{equation}
@@
 \end{equation}
-for $i=1,\ldots,N$, $\ell=1,\ldots,M$.
-We have applied the trapezoid rule since all the integrands are smooth and periodic, and this guarantees that the numerical solutions converges to the true solution with spectral accuracy~\cite{tre-wei2014}.
-\todo[inline]{The above sentence strikes me as awkward and verbose. Rephrase? \\
-How about this: Since all integrands are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy.}
+for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  Since all integrands are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.
+
+%We have applied the trapezoid rule since all the integrands are smooth and periodic, and this guarantees that the numerical solutions converges to the true solution with spectral accuracy~\cite{tre-wei2014}.
+%\todo[inline]{The above sentence strikes me as awkward and verbose. Rephrase? \\
+%How about this: Since all integrands are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy.}
 
@@
 We do not employ an FMM to evaluate the shear stress at $\xx_i$, $i=1,\ldots,N$, so the cost of evaluating the shear stress is $\bigO(N^2)$.
-However, this calculation is only performed once per time step as opposed to the velocity double-layer potential, where we do employ the FMM, that must be evaluated at each GMRES iteration.
-\todo[inline]{The above sentence is confusing. Try to rephrase and shorten it.}
+However, unlike the velocity double-layer potential that is evaluated at each GMRES iteration, the shear stress is only computed once per time step.
 In future work, we plan to use a kernel-independent FMM~\cite{yin-bir-zor2004} to evaluate the shear stress with $\bigO(N)$ operations.
+
+%However, this calculation is only performed once per time step as opposed to the velocity double-layer potential, where we do employ the FMM, that must be evaluated at each GMRES iteration. 
+%\todo[inline]{The above sentence is confusing. Try to rephrase and shorten it.}
 
@@
 
-For the Stokes equations, on boundaries that have a no-slip boundary condition, the shear stress is equivalent to the vorticity.
-Therefore, the vorticity is computed on the grains $\gamma_\ell$ by numerically compute the shear stress as described in Section~\ref{sec:shearStress}.
+For the Stokes equations, on boundaries that have a no-slip boundary
+condition, the shear stress is equivalent to the vorticity.  Therefore,
+the vorticity is computed on the bodies $\gamma_\ell$ by numerically compute the shear stress as described in Section~\ref{sec:shearStress}.
 
@@
 
-Naturally, the flow transmitted by the medium is tied to the amount of drag the bodies exert.
+Naturally, the flow transmitted by the medium is linked to the amount of drag the bodies exert.
 We therefore show in Fig.~\ref{fig:mbodyplots}(c) the total drag exerted by all bodies as it varies in time.

### 2018-04-16 docs/methods/erosion_methods.tex
small changes and added one todo

@@
 
-\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}}
-\newcommand{\secref}[1]{\ref{#1}}
+\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}} \newcommand{\secref}[1]{\ref{#1}}
 
@@
 Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
-We address these tracking issues in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect dynamics; second, we suppress high-frequency oscillations in the interface evolution via curvature penalization.
+We address these tracking issues in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arclength but that does not affect dynamics; second, we suppress high-frequency oscillations in the interface evolution via curvature penalization.
 The interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term \cite{hou-low-she1994}.
@@
 The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).
-An advantage of the traction formulation is that is directly provides the shear stress needed to evolve surfaces.
+An advantage of the traction formulation is that it directly provides the shear stress needed to evolve surfaces.
 In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations.
@@
 Common challenges of a BIE formulation include developing efficient preconditioners for the discretized system and numerical difficulties associated with nearly touching bodies.
-In this work, we consider geometries requiring $\mathcal{O}(100)$ GMRES iterations, so that preconditioners are not necessary.
+In this work, we consider geometries requiring $\mathcal{O}(100)$ GMRES iterations, so preconditioners are currently unnecessary.
 In future work, we will address mobile bodies for which near contacts may necessitate preconditoners~\cite{qua-bir2015a, qua-cou-dar2018, cou-pou-dar2017}.
@@
 The bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.
+Therefore, the boundary of the fluid domain is $\bd\Omega = \Gamma \cup \gamma$.
 On each body, $\nn$ and $\ss$ denote the unit normal and unit tangent vectors respectively.
@@
 Often, we will simply set $U=1$, but in some instances we change $U$ dynamically to enforce that the pressure drop across the computational cell is constant as bodies erode within it.
-The boundary of the fluid domain is $\bd\Omega = \gamma_1 \cup \cdots \cup \gamma_M \cup \Gamma$.
 To minimize the boundary effects of the inflow and outflow, we only place bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.
-
 \begin{figure}[htpb]
@@
 On the outer geometry $\Gamma$, a Hagen-Poiseuille flow is imposed.
-The bodies erode at a rate that is proportional to the magnitude of the shear stress applied by the fluid.
+The bodies erode at a rate that is equal to the magnitude of the shear stress applied by the fluid.
 The bodies are constrained to the middle third of the channel that is located between the dashed lines.}
@@
   \NN_0[\eeta](\xx) = \int_{\Gamma} 
-    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy
+    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy, \quad \xx \in
+    \Gamma\, ,
 \end{align}
@@
 \end{align} 
-The evolution of the interface is then given by the combination of the normal and tangential velocity
+The evolution of the interface is then given by the combination of the normal and tangential velocities
 \begin{align}
@@
 To perform numerical simulations, we exploit the difference between the erosion and fluid time scales.
-Since erosion occurs much slower, we freeze the geometry at each time step, solve the incompressible Stokes equations, and then update the geometry according to the erosion model.
+Since erosion occurs much slower, we freeze the geometry at each time step, solve the incompressible Stokes equations, compute the shear stress, and then update the geometry according to the erosion model.
 Therefore, there are three main numerical methods that need to be developed.
@@
 %\todo[inline]{Typo above}
-\begin{equation}
+%\begin{equation}
+\begin{subequations}
   \label{eqn:completed_BIE_discretized}
-  \begin{aligned}
+  \begin{align}
+  \label{eqn:discretized_DLP}
+%  \begin{aligned} 
+%    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
+%      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
+%      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) \\
+%      &\hspace{53pt}
+%      +\sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) 
+%      +\sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
+%      \nn(\xx_j))\eeta(\xx_j) \, , \\
     \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
       K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
-      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) \\
-      &\hspace{53pt}
-      +\sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) 
-      +\sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
-      \nn(\xx_j))\eeta(\xx_j) \, , \\
+      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) +
+      \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) \\
     \llambda_\ell &= \sum_{\xx_j \in \gamma_\ell} \eeta(\xx_j) 
@@
       {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j \, ,
-  \end{aligned}
-\end{equation}
-for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  Since all integrands are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.
-
+    \end{align}
+%  \end{aligned}
+\end{subequations}
+%\end{equation}
+for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  When $\xx_i \in \Gamma$, the term 
+\begin{align}
+  \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
+      \nn(\xx_j))\eeta(\xx_j) \, ,
+\end{align}
+is added to~\eqref{eqn:discretized_DLP}.  Since we are discetizing integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.  
 %We have applied the trapezoid rule since all the integrands are smooth and periodic, and this guarantees that the numerical solutions converges to the true solution with spectral accuracy~\cite{tre-wei2014}.
@@
 Since the BIE is second-kind, only a mesh-independent number of GMRES iterations are required~\cite{cam-ips-kel-mey-xue1996}.
-Therefore, the asymptotic cost is determined by the cost of performing a matrix-vector multiplication, and the bulk of the cost is evaluating the $N$-term sum in~\eqref{eqn:completed_BIE_discretized}.
+Therefore, the asymptotic cost is determined by the cost of performing a matrix-vector multiplication, and the bulk of the cost is evaluating the $N$-term sum in~\eqref{eqn:discretized_DLP}.
 We use the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} so that the cost of solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$ operations.
@@
 This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$).
-Meanwhile, $\NLterm$, represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
+Meanwhile, $\NLterm$ represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
 Since the local shear stress depends on interactions between bodies, $\NLterm$ is both nonlinear and nonlocal.
@@
 \end{align}
-Once again, both exponential terms act to smooth the geometry. Finally, to track the reference point, $\mean{x}$, we simply apply the same RK2 method to~\eqref{eq:xsurf}.
+Once again, both exponential terms act to smooth the geometry. Finally, to track the reference point, $\mean{\xx}$, we simply apply the same RK2 method to~\eqref{eq:xsurf}.
 
@@
 
-For the Stokes equations, on boundaries that have a no-slip boundary
-condition, the shear stress is equivalent to the vorticity.  Therefore,
-the vorticity is computed on the bodies $\gamma_\ell$ by numerically compute the shear stress as described in Section~\ref{sec:shearStress}.
+For the Stokes equations, on boundaries that have a no-slip boundary condition, the shear stress is equivalent to the vorticity.
+Therefore, the vorticity is computed on the bodies $\gamma_\ell$ by numerically computing the shear stress as described in Section~\ref{sec:shearStress}.
 
@@
 \label{sec:pressure}
-To compute the pressure at $\xx \in \Omega$, we follow the same procedure used for the shear stress.
+To compute the pressure at $\xx \in \Omega$, we follow the same procedure used for the shear stress and vorticity.
 We first compute the pressure of the double-layer potential for $\xx \in \Omega$ and add the appropriate jump if $\xx \in \Gamma$.
@@
 \begin{align}
-  p(\xx) = p^{\DD}(\xx) + p^{S}(\xx)\, , \quad \xx \in \Omega \, ,
+  p(\xx) = p^{\DD}(\xx) + p^{S}(\xx)\, , \quad \xx \in \Omega \, .
 \end{align}
@@
 \end{align}
-Similar to the shear stress, the singularity of the pressure corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is too strong when $\xx \in \bd\Omega$ for the trapezoid rule to be directly applied.
+Similar to the shear stress, the singularity of the kernel~\eqref{eqn:pressureDLP} is too strong when $\xx \in \bd\Omega$ for the trapezoid rule to be directly applied.
 Therefore, we again subtract a constant density function and write the pressure as
-\begin{equation}
-\begin{aligned}
+\begin{align}
   p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
@@
     \quad \xx \in \bd\Omega\, .
-\end{aligned}
-\end{equation}
-Then, identical to how the shear stress is computed in~\eqref{eqn:stressOddEven}, odd-even integration is used to evaluate this layer potential for pressure, and the jump condition in~\eqref{eqn:pressureJump} is computed with Fourier differentiation.
+  \label{eqn:pressureOddEven}
+\end{align}
+Then, identical to how the shear stress is computed in~\eqref{eqn:stressOddEven}, odd-even integration is used to evaluate~\eqref{eqn:pressureOddEven}, and the jump condition in~\eqref{eqn:pressureJump} is computed with Fourier differentiation.
 
@@
 \label{sec:drag}
-Once the pressure and shear stress is computed, the drag on a single body with boundary $\gamma_\ell$ is
+Once the pressure and shear stress are computed, the drag on a single body with boundary $\gamma_\ell$ is
 \begin{align}
@@
 \begin{align}
-  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) \, ds_\yy\, .
+  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) \, ds_\yy\,, \quad \xx \in \Omega\, .
   \label{eqn:genericLP}
@@
 \end{align}
-where $q$ contains the quadrature weights, Jacobian, and density function.
+where $q$ contains the quadrature weights, Jacobian, and density function, and $N$ depends on the distance between $\xx$ and $\bd\Omega$.
 Based on numerical experiments, the error of the $N$-point trapezoid rule is acceptable for points $\xx$ that are more than five arclength spacings from $\bd\Omega$.
@@
 \begin{table}[htpb]
-\centering
+\begin{center}
+\caption{\label{tbl:upsampling}The upsampling rate of our near-singular integration scheme.
+$d(\xx,\bd\Omega)$ is the distance between $\xx \in \Omega$ and $\bd\Omega$, and $h$ is an arclength spacing.}
+\vspace{0.3 pc}
+\label{table:arangle}
 \begin{tabular}{|V|V|V|V|V|V|N}
@@
 \end{tabular}
-\caption{\label{tbl:upsampling}The upsampling rate of our near-singular integration scheme.
-$d(\xx,\bd\Omega)$ is the distance between a point $\xx \in \Omega$ and the boundary of the domain $\bd\Omega$, and $h$ is an arclength spacing.}
+\end{center}
 \end{table}
@@
 For a {\em circular} cylinder, the normalization factor $4 \pi$ produces an {\em exact} relationship (within the context of slender-body theory), where $a$ is taken to be the radius.
-For other shapes, the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic lengthscale since it generalizes the case of a circle.
+For other shapes, the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic length scale since it generalizes the case of a circle.
 In Fig.~\ref{area_drag}(b) we show this prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
@@
 Importantly, more numerical accuracy is available to quantify the terminal state.
-The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear corner demonstrate that, due to our numerical regularization, the body is actually smooth on a fine scale.
+The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear corner and demonstrates that, due to our numerical regularization, the body is actually smooth on a fine scale.
 We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces.
@@
 \vspace{0.3 pc}
-\label{table:arangle}
 \begin{tabular}{c c c}
@@
 Though the main parts of the algorithm are easily paralyzed, the single-processor times provide a simple assessment of the overall complexity.
+\todo[inline]{Aren't the CPU scaling times we report obvious.
+If we take a time step size half the size, it will of course take twice as long.
+We report these numbers in a couple of tables.
+We have not reported CPU time versus the spatial resolution which is where the value of the FMM would be obvious.}
 
@@
 \end{align}
-We then rescale the computed density function by the pressure difference
+We then rescale the computed density function, Stokeslets, and rotlets  by the pressure difference
 \begin{align}
@@
 \begin{center}
-\caption{Convergence test for multiple-body erosion with fixed-pressure-drop condition.
+\caption{Convergence test for multiple-body erosion with a fixed-pressure-drop condition.
 In this test, we use 20 bodies with $N_{\iin} = 128$ grid points on each.
@@
 \includegraphics[width = 0.80 \textwidth]{./figs/06bod.pdf}
-\caption{\label{fig:06bodies} The simulated erosion of 6 bodies with the fixed-pressure drop condition.
+\caption{\label{fig:06bodies} The simulated erosion of 6 bodies with the fixed-pressure-drop condition.
 Erosion causes flat faces to develop wherever bodies were initially very close to one another.

### 2018-04-16 docs/methods/erosion_methods.tex
Looked at the todo's. Everything looks good to me.
NM

--- 2018-04-16 docs/methods/erosion_methods.tex
@@
 
-%The constant of proportionality of the erosion law only sets the time scale, so we have set $\Vn = |\tau|$ as described in equation~\eqref{eqn:erosionModel}.  
-%\todo[inline]{The above sentence is awkard.
-Could it be rephrased?
-First, the reader probably does not know what constant of proportionality you are referring to because we do not have one in the equation.
-Second, there are too many 'ofs' in a row.}
-
 The outer wall is formed by rounding off the corners of $[-3,3] \times [-1,1]$, and we impose the Hagen-Poiseuille flow
@@
 \end{figure}
-%\todo[inline]{Here is an example where you can avoid the passive voice because it is totally unnecessary.
-Instead of saying 'the bodies are eroded', simply say 'the bodies erode'.
-Also, a fluid cannot be Stokesian, since the Reynolds number depends on the length scale and velocity scale.
-It is the flow that is Stokes.}
 
@@
 In this manner, the BIE as described above can be applied.
-
-%\todo[inline]{There is a typo in the above sentence (missing 'we'?).
-Also, technically there is  a dangling participle; i.e.~is it the erosion model which is in Section 2.3 or the modification?
-A slight rephrasing might clarify.}
 
@@
 Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
-%\todo[inline]{Typo above}
 \begin{equation}
@@
 for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  Since all integrands are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.
-
-%We have applied the trapezoid rule since all the integrands are smooth and periodic, and this guarantees that the numerical solutions converges to the true solution with spectral accuracy~\cite{tre-wei2014}.
-%\todo[inline]{The above sentence strikes me as awkward and verbose. Rephrase? \\
-%How about this: Since all integrands are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy.}
 
@@
 
-%However, this calculation is only performed once per time step as opposed to the velocity double-layer potential, where we do employ the FMM, that must be evaluated at each GMRES iteration. 
-%\todo[inline]{The above sentence is confusing. Try to rephrase and shorten it.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
-The table shows that the GMRES count, and therefore the computational time, increases roughly linearly with the number of bodies.
-Thus, with everything else equal, the 50-body simulation from Fig.~\ref{fig:50bodies} is about 50 times more expensive than a single-body simulation.
+The table shows that the GMRES count increases roughly linearly with the number of bodies.
+%Thus, with everything else equal, the 50-body simulation from Fig.~\ref{fig:50bodies} is about 50 times more expensive than a single-body simulation.
 

### 2018-04-16 docs/methods/erosion_methods.tex
fixed merge conflict

--- 2018-04-16 docs/methods/erosion_methods.tex
@@
 Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
+%\begin{equation}
 %\todo[inline]{Typo above}
@@
   \end{align}
-%  \end{aligned}
 \end{subequations}
-%\end{equation}
 for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  When $\xx_i \in \Gamma$, the term 
@@
 \end{align}
-is added to~\eqref{eqn:discretized_DLP}.  Since we are discetizing integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.  
+is added to~\eqref{eqn:discretized_DLP}.  Since we discetize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.  
 %We have applied the trapezoid rule since all the integrands are smooth and periodic, and this guarantees that the numerical solutions converges to the true solution with spectral accuracy~\cite{tre-wei2014}.

### 2018-04-16 docs/methods/erosion_methods.tex
NM

@@
 Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
-%\begin{equation}
-%\todo[inline]{Typo above}
-%\begin{equation}
 \begin{subequations}
@@
   \label{eqn:discretized_DLP}
-%  \begin{aligned} 
-%    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
-%      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
-%      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) \\
-%      &\hspace{53pt}
-%      +\sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) 
-%      +\sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
-%      \nn(\xx_j))\eeta(\xx_j) \, , \\
     \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
@@
 is added to~\eqref{eqn:discretized_DLP}.  Since we discetize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.
-%We have applied the trapezoid rule since all the integrands are smooth and periodic, and this guarantees that the numerical solutions converges to the true solution with spectral accuracy~\cite{tre-wei2014}.
-%\todo[inline]{The above sentence strikes me as awkward and verbose. Rephrase? \\
-%How about this: Since all integrands are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy.}
 
@@
 The table confirms that our method converges with expected second-order accuracy.
-The last column of the table shows the CPU time taken for the simulation to run on a single-processor machine, demonstrating a nearly linear increase in computational time.
-Though the main parts of the algorithm are easily paralyzed, the single-processor times provide a simple assessment of the overall complexity.
-\todo[inline]{Aren't the CPU scaling times we report obvious.
-If we take a time step size half the size, it will of course take twice as long.
-We report these numbers in a couple of tables.
-We have not reported CPU time versus the spatial resolution which is where the value of the FMM would be obvious.}
+The last column of the table shows the CPU time taken for the simulation to run on a single-processor machine.
+%, demonstrating a nearly linear increase in computational time with refinement of the time step. 
+%Though the main parts of the algorithm are easily paralyzed, the single-processor times provide a simple assessment of the overall complexity.
 

### 2018-04-16 docs/methods/erosion_methods.tex
NM
moved bibliography to .tex file

@@
 In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate the viscous erosion of a single body in three dimensions~\cite{mit-spa2016}.
-The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).
+The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em arbitrary} background flow (e.g.~uniform flow, shear flow, etc.).
 An advantage of the traction formulation is that it directly provides the shear stress needed to evolve surfaces.
@@
 
-For the porous network simulations considered here, it is essential to resolve nonlocal effects between the different bodies.
-BIEs naturally resolve these interactions, and they have been used extensively to simulate viscous fluids in complex geometries, including porous media flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.
-Common challenges of a BIE formulation include developing efficient preconditioners for the discretized system and numerical difficulties associated with nearly touching bodies.
-In this work, we consider geometries requiring $\mathcal{O}(100)$ GMRES iterations, so preconditioners are currently unnecessary.
-In future work, we will address mobile bodies for which near contacts may necessitate preconditoners~\cite{qua-bir2015a, qua-cou-dar2018, cou-pou-dar2017}.
+For the porous network simulations considered here, it is essential to
+resolve nonlocal effects between the different bodies.  BIEs naturally
+resolve these interactions, and they have been used extensively to
+simulate viscous fluids in complex geometries, including porous media
+flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.  Common challenges
+of a BIE formulation include developing efficient preconditioners for
+the discretized system and numerical difficulties associated with nearly
+touching bodies. In this work, we consider geometries requiring
+$\mathcal{O}(100)$ GMRES iterations, so preconditioners are currently
+unnecessary. In future work, we will address mobile bodies for which
+near contacts may necessitate preconditioners~\cite{qua-bir2015a, qua-cou-dar2018, cou-pou-dar2017}.
 Similarly, near-singular schemes will not be necessary due to the fact that the spacing between receding bodies of fixed position always grows in time.
@@
 \end{align}
-is added to~\eqref{eqn:discretized_DLP}.  Since we discetize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.
+is added to~\eqref{eqn:discretized_DLP}.  Since we discretize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.
 
@@
 The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multibody interactions are handled correctly by the Stokes solver.
-The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution.
+The last column of the table shows the computational time of each simulation, demonstrating a linear increase with refinement of the time step.
 Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.
@@
 \paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for supplying the FMM for the Stokes double-layer potential.
-%We would like to thank Saverio Spagnolie, William Mitchell, Daniel Rothman, Michael Shelley, ....
 
 \bibliographystyle{plainnat} 
-\bibliography{refs}
 \biboptions{sort&compress}
+
+\begin{thebibliography}{72}
+\providecommand{\natexlab}[1]{#1}
+\providecommand{\url}[1]{\texttt{#1}}
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{doi: #1}\else
+  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi
+
+\bibitem[Abrams et~al.(2009)Abrams, Lobkovsky, Petroff, Straub, McElroy,
+  Mohrig, Kudrolli, and Rothman]{abrams2009growth}
+Daniel~M Abrams, Alexander~E Lobkovsky, Alexander~P Petroff, Kyle~M Straub,
+  Brandon McElroy, David~C Mohrig, Arshad Kudrolli, and Daniel~H Rothman.
+\newblock Growth laws for channel networks incised by groundwater flow.
+\newblock \emph{Nature Geoscience}, 2\penalty0 (3):\penalty0 193, 2009.
+
+\bibitem[af~Klinteberg and Tornberg(2016)]{kli-tor2016b}
+Ludvig af~Klinteberg and Anna-Karin Tornberg.
+\newblock A fast integral equation method for solid particles in viscous flow
+  using quadrature by expansion.
+\newblock \emph{Journal of Computational Physics}, 326:\penalty0 420--445,
+  2016.
+
+\bibitem[Barnett et~al.(2015)Barnett, Wu, and Veerapaneni]{bar-wu-vee2015}
+Alex Barnett, Bowei Wu, and Shravan Veerapaneni.
+\newblock {Spectrally-Accurate Quadratures for Evaluation of Layer Potentials
+  Close to the Boundary for the 2D Stokes and Laplace Equations}.
+\newblock \emph{SIAM Journal on Scientific Computing}, 37\penalty0
+  (4):\penalty0 B519--B542, 2015.
+
+\bibitem[Barnett et~al.(2018)Barnett, Marple, Veerapaneni, and
+  Zhao]{bar-mar-vee-zha2018}
+Alex Barnett, Gary Marple, Shravan Veerapaneni, and Lin Zhao.
+\newblock {A unified integral equation scheme for doubly-periodic Laplace and
+  Stokes boundary value problems in two dimensions}.
+\newblock \emph{Communications on Pure and Applied Mathematic}, 2018.
+\newblock In press.
+
+\bibitem[Barnett(2014)]{bar2014}
+Alex~H. Barnett.
+\newblock {Evaluation of layer potentials close to the boundary for Laplace and
+  Helmholtz problems on analytic planar domains}.
+\newblock \emph{SIAM Journal on Scientific Computing}, 36\penalty0
+  (2):\penalty0 A427--A451, 2014.
+
+\bibitem[Batchelor(1970)]{batchelor1970slender}
+GK~Batchelor.
+\newblock {Slender-body theory for particles of arbitrary cross-section in
+  Stokes flow}.
+\newblock \emph{Journal of Fluid Mechanics}, 44\penalty0 (3):\penalty0
+  419--440, 1970.
+
+\bibitem[Beale and Lai(2001)]{bea-lai2001}
+J.T. Beale and M.-C. Lai.
+\newblock {A Method for Computing Nearly Singular Integrals}.
+\newblock \emph{SIAM Journal on Numerical Analysis}, 38\penalty0 (6):\penalty0
+  1902--1925, 2001.
+
+\bibitem[Bear(2013)]{bear2013dynamics}
+Jacob Bear.
+\newblock \emph{Dynamics of fluids in porous media}.
+\newblock Courier Corporation, 2013.
+
+\bibitem[Berhanu et~al.(2012)Berhanu, Petroff, Devauchelle, Kudrolli, and
+  Rothman]{berhanu2012shape}
+Michael Berhanu, Alexander Petroff, Olivier Devauchelle, Arshad Kudrolli, and
+  Daniel~H Rothman.
+\newblock Shape and dynamics of seepage erosion in a horizontal granular bed.
+\newblock \emph{Physical Review E}, 86\penalty0 (4):\penalty0 041304, 2012.
+
+\bibitem[Bremer(2012)]{bre2012}
+James Bremer.
+\newblock {On the Nystr\"om discretization of integral equations on planar
+  curves with corners}.
+\newblock \emph{Applied and Computational Harmonic Analysis}, 32:\penalty0
+  45--64, 2012.
+
+\bibitem[Camassa et~al.(2012)Camassa, McLaughlin, Moore, and Yu]{MooreJFM2012}
+R.~Camassa, R.M. McLaughlin, M.N.J. Moore, and K.~Yu.
+\newblock Stratified flows with vertical layering of density: experimental and
+  theoretical study of flow configurations and their stability.
+\newblock \emph{Journal of Fluid Mechanics}, 690:\penalty0 571--606, 2012.
+
+\bibitem[Campbell et~al.(1996)Campbell, Ipsen, Kelley, Meyer, and
+  Xue]{cam-ips-kel-mey-xue1996}
+S.~L. Campbell, I.~C.~F. Ipsen, C.~T. Kelley, C.~D. Meyer, and Z.~Q. Xue.
+\newblock {Convergence estimates for solution of integral equations with
+  GMRES}.
+\newblock \emph{Journal of Integral Equations and Applications}, 8\penalty0
+  (1):\penalty0 19--34, 1996.
+
+\bibitem[Cao et~al.(2010)Cao, Gunzburger, Hua, Wang, et~al.]{cao2010coupled}
+Yanzhao Cao, Max Gunzburger, Fei Hua, Xiaoming Wang, et~al.
+\newblock Coupled stokes-darcy model with beavers-joseph interface boundary
+  condition.
+\newblock \emph{Communications in Mathematical Sciences}, 8\penalty0
+  (1):\penalty0 1--25, 2010.
+
+\bibitem[Claudin et~al.(2017)Claudin, Dur{\'a}n, and
+  Andreotti]{claudin2017dissolution}
+Philippe Claudin, Orencio Dur{\'a}n, and Bruno Andreotti.
+\newblock Dissolution instability and roughening transition.
+\newblock \emph{Journal of Fluid Mechanics}, 832, 2017.
+
+\bibitem[Cohen et~al.(2016)Cohen, Berhanu, Derr, and du~Pont]{cohen2016erosion}
+Caroline Cohen, Michael Berhanu, Julien Derr, and Sylvain~Courrech du~Pont.
+\newblock Erosion patterns on dissolving and melting bodies.
+\newblock \emph{Physical Review Fluids}, 1\penalty0 (5):\penalty0 050508, 2016.
+
+\bibitem[Cohen et~al.(2015)Cohen, Devauchelle, Seybold, Yi, Szymczak, and
+  Rothman]{coh-dev-sey-yi-szy-rot2015}
+Yossi Cohen, Olivier Devauchelle, Hansj{\"o}rg~F. Seybold, Robert~S. Yi, Piotr
+  Szymczak, and Daniel~H. Rothman.
+\newblock Path selection in the growth of rivers.
+\newblock \emph{Proceedings of the National Academy of Sciences}, 112\penalty0
+  (46):\penalty0 14132--14137, 2015.
+
+\bibitem[Corona and Veerapaneni(2017)]{cor-vee2017}
+Eduardo Corona and Shravan Veerapaneni.
+\newblock {Boundary integral equation analysis for suspension of spheres in
+  Stokes flow}.
+\newblock \emph{arxiv}, 1707.06551, 2017.
+
+\bibitem[Corona et~al.(2017)Corona, Greengard, Rachh, and
+  Veerapaneni]{cor-gre-rac-vee2017}
+Eduardo Corona, Leslie Greengard, Manas Rachh, and Shravan Veerapaneni.
+\newblock {An integral equation formulation for rigid bodies in Stokes flow in
+  three dimensions}.
+\newblock \emph{Journal of Computational Physics}, 332:\penalty0 504--519,
+  2017.
+
+\bibitem[Coulier et~al.(2017)Coulier, Pouransari, and Darve]{cou-pou-dar2017}
+Pieter Coulier, Hadi Pouransari, and Eric Darve.
+\newblock {The Inverse Fast Multipole Method: Using a Fast Approximate Diret
+  Solver as a Preconditioner for Dense Linear Systems}.
+\newblock \emph{SIAM Journal on Scientific Computing}, 39\penalty0
+  (3):\penalty0 A761--A796, 2017.
+
+\bibitem[Daerr et~al.(2003)Daerr, Lee, Lanuza, and
+  Cl{\'e}ment]{daerr2003erosion}
+Adrian Daerr, Peter Lee, Jos{\'e} Lanuza, and {\'E}ric Cl{\'e}ment.
+\newblock Erosion patterns in a sediment layer.
+\newblock \emph{Physical Review E}, 67\penalty0 (6):\penalty0 065201, 2003.
+
+\bibitem[Dallaston et~al.(2015)Dallaston, Hewitt, and
+  Wells]{dallaston2015channelization}
+MC~Dallaston, IJ~Hewitt, and AJ~Wells.
+\newblock Channelization of plumes beneath ice shelves.
+\newblock \emph{Journal of Fluid Mechanics}, 785:\penalty0 109--134, 2015.
+
+\bibitem[de~Anna et~al.(2018)de~Anna, Quaife, Biros, and
+  Juanes]{dea-qua-bir-jua2018}
+Pietro de~Anna, Bryan Quaife, George Biros, and Ruben Juanes.
+\newblock {Prediction of velocity distribution from pore structure in simple
+  porous media}.
+\newblock \emph{Physical Review Fluids}, 2\penalty0 (12):\penalty0 124103,
+  2018.
+
+\bibitem[Devauchelle et~al.(2012)Devauchelle, Petroff, Seybold, and
+  Rothman]{Rothman2012}
+O.~Devauchelle, A.P. Petroff, H.F. Seybold, and D.H. Rothman.
+\newblock Ramification of stream networks.
+\newblock \emph{Proceedings of the National Academy of Sciences}, 109\penalty0
+  (51):\penalty0 20832--20836, 2012.
+
+\bibitem[Domokos et~al.(2014)Domokos, Jerolmack, Sipos, and
+  T{\"o}r{\"o}k]{domokos2014river}
+Gabor Domokos, Douglas~J Jerolmack, Andras~{\'A} Sipos, and {\'A}kos
+  T{\"o}r{\"o}k.
+\newblock How river rocks round: resolving the shape-size paradox.
+\newblock \emph{PloS One}, 9\penalty0 (2):\penalty0 e88657, 2014.
+
+\bibitem[Gillman et~al.(2014)Gillman, Hao, and Martinsson]{gil-hao-mar2014}
+A.~Gillman, S.~Hao, and P.G. Martinsson.
+\newblock {A simplified technique for the efficient and highly accurate
+  discretization of boundary integral equations in 2D on domains with corners}.
+\newblock \emph{Journal of Computational Physics}, 256:\penalty0 214--219,
+  2014.
+
+\bibitem[Greenbaum et~al.(1992)Greenbaum, Greengard, and Mayo]{gre-gre-may1992}
+Anne Greenbaum, Leslie Greengard, and Anita Mayo.
+\newblock On the numerical solution of the biharmonic equation in the plane.
+\newblock \emph{Physica D: Nonlinear Phenomena}, 60:\penalty0 216--225, 1992.
+
+\bibitem[Greengard and Rokhlin(1987)]{gre-rok1987}
+L.~Greengard and V.~Rokhlin.
+\newblock {A Fast Algorithm for Particle Simulations}.
+\newblock \emph{Journal of Computational Physics}, 73:\penalty0 325--348, 1987.
+
+\bibitem[Greengard et~al.(1996)Greengard, Kropinski, and Mayo]{gre-kro-may1996}
+L.~Greengard, M.C. Kropinski, and A.~Mayo.
+\newblock {Integral Equation Methods for Stokes Flow and Isotropic Elasticity
+  in the Plane}.
+\newblock \emph{Journal of Computational Physics}, 125\penalty0 (2):\penalty0
+  403--414, 1996.
+
+\bibitem[Groen et~al.(2007)Groen, Gijsen, van~der Lugt, Ferguson, Hatsukami,
+  van~der Steen, Yuan, and Wentzel]{gro-gij-van-fer-hat-van-yua-wen2007}
+Harald~C. Groen, Frank~J.H. Gijsen, Aad van~der Lugt, Marina~S. Ferguson,
+  Thomas~S. Hatsukami, Anton~F.W. van~der Steen, Chun Yuan, and Jolanda~J.
+  Wentzel.
+\newblock {Plaque Rupture in the Carotid Artery Is Localized at the High Shear
+  Stress Region: A Case Report}.
+\newblock \emph{Stroke}, 38:\penalty0 2379--2381, 2007.
+
+\bibitem[Hanna(1969)]{han1969}
+Steven~R. Hanna.
+\newblock {The Formation of Longitudinal Sand Dunes by Large Helical Eddies in
+  the Atmosphere}.
+\newblock \emph{Journal of Applied Meteorology}, 8\penalty0 (6):\penalty0
+  874--883, 1969.
+
+\bibitem[Helsing(2011)]{hel2011}
+J.~Helsing.
+\newblock {A Fast and Stable Solver for Singular Integral Equations and
+  Piecewise Smooth Curves}.
+\newblock \emph{SIAM Journal on Scientific Comuting}, 33:\penalty0 153--174,
+  2011.
+
+\bibitem[Helsing and Ojala(2008)]{hel-oja2008a}
+Johan Helsing and Rikard Ojala.
+\newblock On the evaluation of layer potentials close to their sources.
+\newblock \emph{Journal of Computational Physics}, 227:\penalty0 2899--2921,
+  2008.
+
+\bibitem[Hewett and Sellier(2017{\natexlab{a}})]{hewett2017evolution}
+James~N Hewett and Mathieu Sellier.
+\newblock Evolution of an eroding cylinder in single and lattice arrangements.
+\newblock \emph{Journal of Fluids and Structures}, 70:\penalty0 295--313,
+  2017{\natexlab{a}}.
+
+\bibitem[Hewett and Sellier(2017{\natexlab{b}})]{hewett2017pear}
+James~N Hewett and Mathieu Sellier.
+\newblock The pear-shaped fate of an ice melting front.
+\newblock \emph{arXiv preprint arXiv:1705.02536}, 2017{\natexlab{b}}.
+
+\bibitem[Hou et~al.(1994)Hou, Lowengrub, and Shelley]{hou-low-she1994}
+Thomas~Y. Hou, John~S. Lowengrub, and Michael~J. Shelley.
+\newblock {Removing the Stiffness for Interfacial Flows with Surface Tension}.
+\newblock \emph{Journal of Computational Physics}, 114:\penalty0 312--338,
+  1994.
+
+\bibitem[Huang et~al.(2015)Huang, Moore, and Ristroph]{Huang2015}
+J.~M. Huang, M.N.J. Moore, and L.~Ristroph.
+\newblock Shape dynamics and scaling laws for a body dissolving in fluid flow.
+\newblock \emph{Journal of Fluid Mechanics}, 765, 2 2015.
+\newblock ISSN 1469-7645.
+
+\bibitem[Jerolmack et~al.(2012)Jerolmack, Ewing, Falcini, Martin, Masteller,
+  Phillips, Reitz, and Buynevich]{jerolmack2012internal}
+Douglas~J Jerolmack, Ryan~C Ewing, Federico Falcini, Raleigh~L Martin, Claire
+  Masteller, Colin Phillips, Meredith~D Reitz, and Ilya Buynevich.
+\newblock Internal boundary layer model for the evolution of desert dune
+  fields.
+\newblock \emph{Nature Geoscience}, 5\penalty0 (3):\penalty0 206, 2012.
+
+\bibitem[Kabacao\u{g}lu et~al.(2018)Kabacao\u{g}lu, Quaife, and
+  Biros]{kab-qua-bir2018}
+Gokberk Kabacao\u{g}lu, Bryan Quaife, and George Biros.
+\newblock {Low-resolution simulations of vesicle suspensions in 2D}.
+\newblock \emph{Journal of Computational Physics}, 357:\penalty0 43--77, 2018.
+
+\bibitem[Kl\"{o}ckner et~al.(2013)Kl\"{o}ckner, Barnett, Greengard, and
+  O'Neil]{klo-bar-gre-one2013}
+Andreas Kl\"{o}ckner, Alexander Barnett, Leslie Greengard, and Michael O'Neil.
+\newblock {Quadrature by expansion: A new method for the evaluation of layer
+  potentials}.
+\newblock \emph{Journal of Computational Physics}, 252:\penalty0 332--349,
+  2013.
+
+\bibitem[Kondratiuk and Szymczak(2015)]{kondratiuk2015steadily}
+Pawe{\l} Kondratiuk and Piotr Szymczak.
+\newblock {Steadily Translating Parabolic Dissolution Fingers}.
+\newblock \emph{SIAM Journal on Applied Mathematics}, 75\penalty0 (5):\penalty0
+  2193--2213, 2015.
+
+\bibitem[Ladyzhenskaya(1963)]{lad1963}
+O.~A. Ladyzhenskaya.
+\newblock \emph{{The Mathematical Theory of Viscous Incompressible Flow}}.
+\newblock Gordon and Breach Science, 1963.
+
+\bibitem[L{\'o}pez et~al.(2018)L{\'o}pez, Stickland, and
+  Dempster]{lopez2018cfd}
+Alejandro L{\'o}pez, Matthew~T Stickland, and William~M Dempster.
+\newblock Cfd study of fluid flow changes with erosion.
+\newblock \emph{Computer Physics Communications}, 2018.
+
+\bibitem[Lu et~al.(2017)Lu, Rahimian, and Zorin]{lu-rah-zor2017}
+Libin Lu, Abtin Rahimian, and Denis Zorin.
+\newblock {Contact-aware simulations of particulate Stokesian suspensions}.
+\newblock \emph{Journal of Computational Physics}, 347:\penalty0 160--182,
+  2017.
+
+\bibitem[Mitchell and Spagnolie(2016)]{mit-spa2016}
+W.H. Mitchell and S.E. Spagnolie.
+\newblock A generalized traction integral equation for {S}tokes flow, with
+  applications to near-wall particle mobility and viscous erosion.
+\newblock \emph{Journal of Computational Physics}, 2016.
+
+\bibitem[Moore(2017)]{moore2017riemann}
+M~Nicholas~J Moore.
+\newblock {Riemann-Hilbert Problems for the Shapes Formed by Bodies Dissolving,
+  Melting, and Eroding in Fluid Flows}.
+\newblock \emph{Communications on Pure and Applied Mathematics}, 70\penalty0
+  (9):\penalty0 1810--1831, 2017.
+
+\bibitem[Moore et~al.(2013)Moore, Ristroph, Childress, Zhang, and
+  Shelley]{moo-ris-chi-zha-she2013}
+Matthew N.~J. Moore, Leif Ristroph, Stephen Childress, Jun Zhang, and
+  Michael~J. Shelley.
+\newblock Self-similar evolution of a body eroding in a fluid flow.
+\newblock \emph{Physics of Fluids}, 25:\penalty0 116602, 2013.
+
+\bibitem[Nienhuis et~al.(2014)Nienhuis, Perron, Kao, and
+  Myrow]{nienhuis2014wavelength}
+Jaap~H Nienhuis, J~Taylor Perron, Justin~CT Kao, and Paul~M Myrow.
+\newblock Wavelength selection and symmetry breaking in orbital wave ripples.
+\newblock \emph{Journal of Geophysical Research: Earth Surface}, 119\penalty0
+  (10):\penalty0 2239--2257, 2014.
+
+\bibitem[O.Pironneau(1973)]{pir1973}
+O.Pironneau.
+\newblock {On optimum profiles in Stokes flow}.
+\newblock \emph{Journal of Fluid Mehanics}, 59\penalty0 (1):\penalty0 117--128,
+  1973.
+
+\bibitem[Perkins et~al.(2015)Perkins, Finnegan, and
+  De~Silva]{perkins2015amplification}
+Jonathan~P Perkins, Noah~J Finnegan, and Shanaka~L De~Silva.
+\newblock Amplification of bedrock canyon incision by wind.
+\newblock \emph{Nature Geoscience}, 8\penalty0 (4):\penalty0 305, 2015.
+
+\bibitem[Perron et~al.(2009)Perron, Kirchner, and
+  Dietrich]{perron2009formation}
+J~Taylor Perron, James~W Kirchner, and William~E Dietrich.
+\newblock Formation of evenly spaced ridges and valleys.
+\newblock \emph{Nature}, 460\penalty0 (7254):\penalty0 502, 2009.
+
+\bibitem[Petroff et~al.(2011)Petroff, Devauchelle, Abrams, Lobkovsky, Kudrolli,
+  and Rothman]{petroff2011geometry}
+Alexander~P Petroff, Olivier Devauchelle, Daniel~M Abrams, Alexander~E
+  Lobkovsky, Arshad Kudrolli, and Daniel~H Rothman.
+\newblock Geometry of valley growth.
+\newblock \emph{Journal of Fluid Mechanics}, 673:\penalty0 245--254, 2011.
+
+\bibitem[Picioreanu et~al.(2001)Picioreanu, van Loosdrecht, and
+  Heijnen]{pic-van-hei2000}
+Cristian Picioreanu, Mark C.~M. van Loosdrecht, and Joseph~J. Heijnen.
+\newblock {Two-Dimensional Model of Biofilm Detachment Caused by Internal
+  Stress from Liquid Flow}.
+\newblock \emph{Biotechnology and Bioengineering}, 72\penalty0 (2):\penalty0
+  205--218, 2001.
+
+\bibitem[Power(1993)]{pow1993}
+H.~Power.
+\newblock {The completed double layer boundary integral equation method for
+  two-dimensional Stokes flow}.
+\newblock \emph{IMA Journal of Applied Mathematics}, 51\penalty0 (2):\penalty0
+  123--145, 1993.
+
+\bibitem[Power and Miranda(1987)]{pow-mir1987}
+H.~Power and G.~Miranda.
+\newblock Second kind integral equation formulation of stokes' flows past a
+  particle of arbitrary shape.
+\newblock \emph{SIAM Journal on Applied Mathematics}, 47\penalty0 (4):\penalty0
+  689--698, 1987.
+
+\bibitem[Pozrikidis(1992)]{poz1992}
+C.~Pozrikidis.
+\newblock \emph{{Boundary Integral and Singularity Methods for Linearized
+  Viscous Flow}}.
+\newblock Cambridge University Press, New York, NY, USA, 1992.
+
+\bibitem[Pozrikidis(1997)]{poz1997}
+C.~Pozrikidis.
+\newblock \emph{Introduction to Theoretical and Computational Fluid Dynamics}.
+\newblock Oxford University Press, New York, 1997.
+
+\bibitem[Quaife and Biros(2014)]{qua-bir2014a}
+Bryan Quaife and George Biros.
+\newblock High-volume fraction simulations of two-dimensional vesicle
+  suspensions.
+\newblock \emph{Journal of Computational Physics}, 274:\penalty0 245--267,
+  2014.
+
+\bibitem[Quaife and Biros(2015)]{qua-bir2015a}
+Bryan Quaife and George Biros.
+\newblock {On preconditioners for the Laplace double-layer potential in 2D}.
+\newblock \emph{Numerical Linear Algebra with Applications}, 22:\penalty0
+  101--122, 2015.
+
+\bibitem[Quaife and Biros(2016)]{qua-bir2016}
+Bryan Quaife and George Biros.
+\newblock {Adaptive time stepping for vesicle simulations}.
+\newblock \emph{Journal of Computational Physics}, 306:\penalty0 478--499,
+  2016.
+
+\bibitem[Quaife et~al.(2018)Quaife, Coulier, and Darve]{qua-cou-dar2018}
+Bryan Quaife, Pieter Coulier, and Eric Darve.
+\newblock {An efficient preconditioner for the fast simulation of a 2D Stokes
+  flow in porous media}.
+\newblock \emph{International Journal for Numerical Methods in Engineering},
+  113:\penalty0 561--580, 2018.
+
+\bibitem[Rachh and Serkh(2017)]{rac-ser2017}
+M.~Rachh and K.~Serkh.
+\newblock {On the solution of Stokes equation on regions with corners}.
+\newblock \emph{arxiv}, 1711.04072, 2017.
+
+\bibitem[Rachh and Greengard(2016)]{rac-gre2016}
+Manas Rachh and L.~Greengard.
+\newblock Integral equation methods for elastance and mobility problems in two
+  dimensions.
+\newblock \emph{SIAM Journal on Numerical Analysis}, 54\penalty0 (5):\penalty0
+  2889--2909, 2016.
+
+\bibitem[Ristroph(2018)]{ristroph2018sculpting}
+Leif Ristroph.
+\newblock Sculpting with flow.
+\newblock \emph{Journal of Fluid Mechanics}, 838:\penalty0 1--4, 2018.
+
+\bibitem[Ristroph et~al.(2012)Ristroph, Moore, Childress, Shelley, and
+  Zhang]{ris-moo-chi-she-zha2012}
+Leif Ristroph, Matthew N.~J. Moore, Stephen Childress, Michael~J. Shelley, and
+  Jun Zhang.
+\newblock Sculpting of an erodible body in flowing water.
+\newblock \emph{Proceedings of the National Academy of Sciences}, 109\penalty0
+  (48):\penalty0 19606--19609, 2012.
+
+\bibitem[Rycroft and Bazant(2016)]{rycroft2016asymmetric}
+Chris~H. Rycroft and Martin~Z. Bazant.
+\newblock Asymmetric collapse by dissolution or melting in a uniform flow.
+\newblock In \emph{Proc. R. Soc. A}, volume 472, page 20150531. The Royal
+  Society, 2016.
+
+\bibitem[Saad and Schultz(1986)]{saa-sch1986}
+Y.~Saad and M.H. Schultz.
+\newblock {GMRES: A Generalized Minimal Residual Algorithm for Solving
+  Nonsymmetric Linear Systems}.
+\newblock \emph{SIAM Journal on Scientific and Statistical Computing},
+  7:\penalty0 856--869, 1986.
+
+\bibitem[Sangani and Mo(1994)]{san-mo1994}
+Ashok~S. Sangani and Guobiao Mo.
+\newblock Inclusion of lubrication forces in dynamic simulations.
+\newblock \emph{Physics of fluids}, 6\penalty0 (5):\penalty0 1653--1662, 1994.
+
+\bibitem[Serkh and Rokhlin(2016)]{ser-rok2016}
+K.~Serkh and V.~Rokhlin.
+\newblock On the solution of elliptic partial differential equations on regions
+  with corners.
+\newblock \emph{Journal of Computational Physics}, 305:\penalty0 150--171,
+  2016.
+
+\bibitem[Shah(2002)]{sha2002}
+Prediman~K. Shah.
+\newblock {Pathophysiology of coronary thrombosis: role of plaque rupture and
+  plaque erosion}.
+\newblock \emph{Progress in Cardiovascular Diseases}, 44\penalty0 (5):\penalty0
+  357--368, 2002.
+
+\bibitem[Sidi and Israeli(1988)]{sid-isr1988}
+Avram Sidi and Moshe Israeli.
+\newblock Quadrature {M}ethods for {P}eriodic {S}ingular and {W}eakly
+  {S}ingular {F}redholm {I}ntegral {E}quations.
+\newblock \emph{Journal of Scientific Computing}, 3\penalty0 (2):\penalty0
+  201--231, 1988.
+
+\bibitem[Trefethen and Weideman(2014)]{tre-wei2014}
+Lloyd~N. Trefethen and J.~A.~C. Weideman.
+\newblock {The Exponentially Convergent Trapezoidal Rule}.
+\newblock \emph{SIAM Review}, 56\penalty0 (3):\penalty0 385--458, 2014.
+
+\bibitem[Ying et~al.(2004)Ying, Biros, and Zorin]{yin-bir-zor2004}
+L.~Ying, G.~Biros, and D.~Zorin.
+\newblock {A kernel-independent adaptive fast multipole algorithm in two and
+  three dimensions}.
+\newblock \emph{Journal of Computational Physics}, 194\penalty0 (2):\penalty0
+  591--626, 2004.
+
+\end{thebibliography}
+
+%\bibliography{refs}
+
 \end{document}

### 2018-04-17 docs/methods/erosion_methods.tex
final edits and submitted to JCP and arxiv

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for supplying the FMM for the Stokes double-layer potential.
+\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for
+supplying the FMM for the Stokes double-layer potential. BQ and NM were
+supported by Florida State University startup funds and Simons
+Foundation Mathematics and Physical Sciences-Collaboration Grants for
+Mathematicians.
 
@@
 Yanzhao Cao, Max Gunzburger, Fei Hua, Xiaoming Wang, et~al.
-\newblock Coupled stokes-darcy model with beavers-joseph interface boundary
+\newblock Coupled Stokes-Darcy model with Beavers-Joseph interface boundary
   condition.
@@
 H.~Power and G.~Miranda.
-\newblock Second kind integral equation formulation of stokes' flows past a
+\newblock Second kind integral equation formulation of Stokes' flows past a
   particle of arbitrary shape.

### 2018-06-07 docs/PhysicsPaper/StokesErosion.tex
Working on tex for PhysicsPaper
NM
Added fig2
Starting work on physics paper

@@
 \section{Introduction}
-Stuff \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017} and other stuff \cite{Rycroft2016, Mitchell2016}.
 
+Effects of flow-induced erosion are visible across a range of scales in nature, from massive geological structures, to mesoscopic patterns, and finally down to the tiny granular constituents that comprise a porous medium.
+In the case of a porous medium specifically, it has been long recognized that bulk properties of mediums encountered in nature are typically anisotropic, so that the medium allows flow in a preferred direction more easily.
+This anisotropy is commonly attributed to how grains are deposited, with their longest dimension parallel to the settling bed, so that they allow flow preferentially in the horizontal direction.
+Controlled experiments, however, have not been performed to test this hypothesis.
+Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.
+
+Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in Stokes flow---the regime of groundwater flow.
+This method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can practically simulate the erosion of order hundreds of solid bodies.
+
+%Stuff to cite \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017} and other stuff \cite{Rycroft2016, Mitchell2016}.
+
+\begin{comment}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 \begin{center}
-\includegraphics[width = 0.5 \textwidth]{./Figs/shapes.pdf}
-\caption{
-Shapes.}
+\includegraphics[width = 0.9 \textwidth]{./Figs/fig1.pdf}
+\caption{caption}
 \label{fig1}
@@
 
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.9 \textwidth]{./Figs/fig2.pdf}
+\caption{caption}
+\label{fig2}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\end{comment}
+
 \bibliographystyle{plain}

### 2018-07-03 docs/methods/erosion_methods.tex
fixed typo Lukas found in equation (10)
Making edits for the erosion timescale (Ref 3, comment 1)

@@
 velocity} \\
-\Vn = \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
-&&\mbox{\em erosion model},
+\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
+&&\mbox{\em erosion model} .
 \end{split}
 \end{equation}
-where $\Vn$ is the normal velocity of the interface and $\mu$ is the fluid viscosity.
-A scaling constant often appears in the erosion model in~\eqref{eqn:erosionModel}, but in the Stokes limit, the constant only sets the time scale, so we have taken it to be one.
+where $\Vn$ is the normal velocity of the interface. The parameters in this system are $\mu$ the fluid viscosity and $\CE$ the mater-dependent erosion constant.
+%A scaling constant often appears in the erosion model in~\eqref{eqn:erosionModel}, but in the Stokes limit, the constant only sets the time scale, so we have taken it to be one.
 For the sake of numerical stability, we will modify the erosion model in Section~\ref{sec:thetaL}.
@@
     8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right) \eeta(\yy) \, ds_\yy \, .
+  \right) \, ds_\yy \, .
   \end{aligned}

### 2018-07-03 docs/methods/erosion_methods.tex
continued edits for erosion timescale

@@
 \end{equation}
-where $\Vn$ is the normal velocity of the interface. The parameters in this system are $\mu$ the fluid viscosity and $\CE$ the mater-dependent erosion constant.
-%A scaling constant often appears in the erosion model in~\eqref{eqn:erosionModel}, but in the Stokes limit, the constant only sets the time scale, so we have taken it to be one.
+where $\Vn$ is the normal velocity of the interface.
+Parameters include the fluid viscosity $\mu$ and the material-dependent erosion constant $\CE$, as well as a characteristic flow speed $U^*$ and domain scale $L^*$.
+Non-dimensionalization, however, allows us to remove these parameters from consideration.
+We non-dimensionalize the Stokes equations in the standard way, equivalent to setting $\mu = 1$ above.
+For interface evolution, we scale time on the so-called erosion timescale $T^* = {L^*}^2/(\CE \mu U)$, which can be achieved by simply setting $\CE = 1$ above.
 For the sake of numerical stability, we will modify the erosion model in Section~\ref{sec:thetaL}.
@@
 \end{align}
-where $U$ sets the maximum of the imposed Poiseuille flow.
+where $U$ (dimensionless) sets the maximum of the imposed Poiseuille flow.
 Often, we will simply set $U=1$, but in some instances we change $U$ dynamically to enforce that the pressure drop across the computational cell is constant as bodies erode within it.
 To minimize the boundary effects of the inflow and outflow, we only place bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.
+
 \begin{figure}[htpb]
@@
   \begin{split}
-  \mu\Delta \uu &= \grad p\, , \qquad && \xx \in \Omega, \\
+  \Delta \uu &= \grad p\, , \qquad && \xx \in \Omega, \\
   \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
@@
 \end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.
+where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  
+%As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.
 

### 2018-07-03 docs/methods/erosion_methods.tex
NM

@@
 We non-dimensionalize the Stokes equations in the standard way, equivalent to setting $\mu = 1$ above.
-For interface evolution, we scale time on the so-called erosion timescale $T^* = {L^*}^2/(\CE \mu U)$, which can be achieved by simply setting $\CE = 1$ above.
-For the sake of numerical stability, we will modify the erosion model in Section~\ref{sec:thetaL}.
+For interface evolution, we scale time on the so-called erosion timescale $T^* = {L^*}^2/(\CE \mu U^*)$, which can be achieved by simply setting $\CE = 1$ above.
+In Section~\ref{sec:thetaL}, we will make slight modifications to the erosion model for better numerical stability.
 

### 2018-07-03 docs/methods/erosion_methods.tex
Addressed Reviewer 1

@@
   \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
-      \nn(\xx_j))\eeta(\xx_j) \, ,
+      \nn(\xx_j))\eeta(\xx_j) \Delta s_j \, ,
 \end{align}
@@
 \label{s:qoi}
-We further characterize the flow by computing the vorticity (Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}), and drag (Section~\ref{sec:drag}).
-Once equation~\eqref{eqn:completed_DLP} is solved, the vorticity and pressure will be computed at points both inside the fluid bulk and on the along individual bodies, and then the drag of individual bodies will be computed.
-For target points in the fluid domain, the integrands of the layer potentials are periodic and smooth, and the trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.
-However, if the target point is close to $\bd \Omega$, a nearly-singular integrand must be integrated, and this requires upsampling that is described in Section~\ref{sec:NSI}.
-When the target points is on the boundary, the integrands involve singularities that are evaluated by combining singularity subtraction and odd-even integration~\cite{sid-isr1988}.
+We further characterize the flow by computing the vorticity
+(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
+and drag (Section~\ref{sec:drag}).  Once
+equation~\eqref{eqn:completed_DLP} is solved for the velocity, $\uu =
+(u,v)$, the vorticity and pressure will be computed at points both
+inside the fluid bulk and on the along individual bodies, and then the
+drag of individual bodies will be computed.  For target points in the
+fluid domain, the integrands of the layer potentials are periodic and
+smooth, and the trapezoid rule guarantees spectral
+accuracy~\cite{tre-wei2014}.  However, if the target point is close to
+$\bd \Omega$, a nearly-singular integrand must be integrated, and this
+requires upsampling that is described in Section~\ref{sec:NSI}.  When
+the target points is on the boundary, the integrands involve
+singularities that are evaluated by combining singularity subtraction
+and odd-even integration~\cite{sid-isr1988}.
 

### 2018-07-03 docs/methods/revisions.tex
Addressed Reviewer 1

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{amsmath,amsfonts,amssymb,stmaryrd}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
We thank the reviewers for their reviews.  Below is a summary of the
changes.  The revised manuscript also addresses a typo that was in
equation (10).

\section*{Reviewer 1}

\noindent
\comment{In section 3.1, formula 29 is missing a $\Delta s_{j}$}
\begin{itemize}
  \item Fixed
\end{itemize}

\noindent
\comment{In section 4.1, the symbols $v$ and $u$ haven't been defined
previously}
\begin{itemize}
  \item $\mathbf{u} = (u,v)$ is now defined leading up to Section 4.1.
\end{itemize}

\section*{Reviewer 2}
\noindent
\comment{The time scale of erosion totally disappears from the analysis.
How would this time scale be set in practise?}
\begin{itemize}
  \item After equation (1), the erosion timescale is described.
\end{itemize}

\noindent
\comment{On page 23: the scaling of Fd with 4*pi*U is not dimensionless.
It seems to me like the drag coefficient might be a better quantity to
base the discussion on.}
\begin{itemize}
  \item 
\end{itemize}

\noindent
\comment{The aft and rear stagnation points both recede eventhough they
are subject to zero shear. Is it just a consequence of the
regularization?}
\begin{itemize}
  \item 
\end{itemize}

\end{document}

### 2018-07-09 docs/methods/erosion_methods.tex
Addressing Ref 3 comments

@@
 Closer inspection reveals that the stress actually vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow with time.
+We note that, since the stress vanishes at the stagnation points, the recession of these points is due to the numerical smoothing (both the curvature regularization and the smoothing of the stress distribution).
+Recession of stagnation points has been observed in laboratory experiments, leading us to believe that the numerical smoothing represents a real physical mechanism \cite{ris-moo-chi-she-zha2012}.
 

### 2018-07-09 docs/methods/erosion_methods.tex
Revisions

--- 2018-07-03 docs/methods/erosion_methods.tex
@@
 Closer inspection reveals that the stress actually vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow with time.
+We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing).
+Interestingly, stagnation points do indeed recede in laboratory experiments on erosion  \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013}, leading us to believe that the numerical smoothing represents a real physical mechanism (see \cite{moo-ris-chi-zha-she2013} for discussion).
 

### 2018-07-09 docs/methods/revisions.tex
Addressing Ref 3 comments
Revisions

@@
 \noindent
-\comment{The aft and rear stagnation points both recede eventhough they
+\comment{The aft and rear stagnation points both recede even though they
 are subject to zero shear. Is it just a consequence of the
@@
 \item
+This is a good question.
+Indeed, the recession of the stagnation points is a result of the numerical smoothing (both the curvature penalization and the smoothing of the stress distribution).
+However, in laboratory experiments, stagnation points do indeed recede, which leads us to believe that the numerical smoothing represents a real mechanism.
+For example, the smoothing could plausibly represent small-scale drifting of the stagnation point resulting from noise, or perhaps a second-order pressure dependence in the erosion rate.
+If you are interested, there is a discussion of these possibilities in Moore et al.~{\it POF} 2013.
+
+We have added the following text at the end of section 5.1:
+\begin{quotation}
+We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing).
+Interestingly, stagnation points do indeed recede in laboratory experiments on erosion, leading us to believe that the numerical smoothing represents a real physical mechanism (see [46] for discussion).
+\end{quotation}
+
 \end{itemize}

### 2018-07-09 docs/methods/erosion_methods.tex
NM

@@
 To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag normalized by $\umax$.
-Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies.
-In this way, we can interpret $F_D / (4 \pi \umax)$ as the {\em resistance} associated with the porous network.
+Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \mu \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies.
+In this way, we can interpret $F_D / (4 \pi \mu \umax)$ as the {\em resistance} associated with the porous network.
 As seen in the figure, the medium's resistance decreases rapidly as its constituents erode.

### 2018-07-09 docs/methods/revisions.tex
NM

@@
 \begin{itemize}
-  \item 
+\item Yes, we agree that it makes more sense to make this normalization dimensionless.
+Accordingly, we have now included the viscosity in the denominator, so that we are dealing with the quantity $F_D /(4 \pi \mu U)$.
+This modification does not actually change the numbers in the plot since we have already set $\mu =1$ to non-dimensionalize, but it would make it easier to apply our results to laboratory or field studies (which is a driving interest of ours).
+
+As a side-note, in case you are concerned that there should be a lengthscale included in the denominator, remember that, since these are 2D simulations, $F_D$ is actually the drag-per-unit span (as discussed in Section 5.2).
 \end{itemize}

### 2018-07-09 docs/methods/revisions.tex
NM

@@
 \begin{itemize}
-  \item After equation (1), the erosion timescale is described.
+\item This is a great question and an issue that admittedly was skirted in the original manuscript.
+In the revised manuscript, we have more carefully explained the non-dimensionalization.
+See the text immediately below Eq.~(1).
+In particular, the erosion timescale is given by $T^* = {L^*}^2/(C_E \mu U^*)$, where $C_E$ is the erosion constant (a material property), $L^*$ is a characteristic lengthscale and $U^*$ a characteristic flow rate.
 \end{itemize}
@@
 \begin{itemize}
-\item Yes, we agree that it makes more sense to make this normalization dimensionless.
+\item Yes, we agree that it makes more sense to have this normalization be dimensionless.
 Accordingly, we have now included the viscosity in the denominator, so that we are dealing with the quantity $F_D /(4 \pi \mu U)$.
-This modification does not actually change the numbers in the plot since we have already set $\mu =1$ to non-dimensionalize, but it would make it easier to apply our results to laboratory or field studies (which is a driving interest of ours).
+This modification does not actually change the values shown in the plot because we have already set $\mu =1$ in order to non-dimensionalize.
+However, it would make it easier to apply our results to laboratory or field studies, which is a driving interest of ours.
 
@@
 This is a good question.
-Indeed, the recession of the stagnation points is a result of the numerical smoothing (both the curvature penalization and the smoothing of the stress distribution).
-However, in laboratory experiments, stagnation points do indeed recede, which leads us to believe that the numerical smoothing represents a real mechanism.
-For example, the smoothing could plausibly represent small-scale drifting of the stagnation point resulting from noise, or perhaps a second-order pressure dependence in the erosion rate.
-If you are interested, there is a discussion of these possibilities in Moore et al.~{\it POF} 2013.
+Indeed, the recession of the stagnation points is a result of the numerical smoothing (both the curvature penalization and the smoothing of the stress distribution) in our simulations.
+Stagnation points, however, do actually recede in laboratory experiments on erosion, leading us to believe that the numerical smoothing represents a real mechanism.
+For example, the smoothing could plausibly represent small-scale drifting of the stagnation point due to noise, or perhaps a second-order pressure dependence in the erosion rate.
+If you are interested, various possibilities are discussed in Moore et al.~{\it POF} 2013.
 

### 2018-07-09 docs/methods/revisions.tex
finalize revisions

@@
 \begin{itemize}
-  \item Fixed
+  \item The arclength term is now included in equation (29).
 \end{itemize}
@@
 \begin{quotation}
-We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing).
+We note that the recession of the stagnation points, since the stress
+vanishes there, is due entirely to the numerical smoothing (both the
+curvature penalization and the stress-distribution smoothing).
+Interestingly, stagnation points do indeed recede in laboratory
+experiments on erosion [46, 64], leading us to believe that the
+numerical smoothing represents a real physical mechanism (see [46] for
+discussion).
+%
+%We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing).
 Interestingly, stagnation points do indeed recede in laboratory experiments on erosion, leading us to believe that the numerical smoothing represents a real physical mechanism (see [46] for discussion).

### 2018-07-09 docs/methods/erosion_methods.tex
NM

@@
 \bibitem[Huang et~al.(2015)Huang, Moore, and Ristroph]{Huang2015}
-J.~M. Huang, M.N.J. Moore, and L.~Ristroph.
+J.M. Huang, M.N.J. Moore, and L.~Ristroph.
 \newblock Shape dynamics and scaling laws for a body dissolving in fluid flow.
@@
 \bibitem[Moore(2017)]{moore2017riemann}
-M~Nicholas~J Moore.
+M.N.J. Moore.
 \newblock {Riemann-Hilbert Problems for the Shapes Formed by Bodies Dissolving,
@@
   Shelley]{moo-ris-chi-zha-she2013}
-Matthew N.~J. Moore, Leif Ristroph, Stephen Childress, Jun Zhang, and
+Matthew N.J. Moore, Leif Ristroph, Stephen Childress, Jun Zhang, and
   Michael~J. Shelley.

### 2018-07-10 docs/methods/revisions.tex
fixed small statement in revision doc
finished up jcp revisions

@@
 \noindent
-We thank the reviewers for their reviews.  Below is a summary of the
-changes.  The revised manuscript also addresses a typo that was in
-equation (10).
+Dear Eric Darve,
+\\ \\
+\noindent
+Thank you for handling the manuscript, and we would like to thank the
+reviewers for their positive and constructive comments.  The attached
+manuscript addresses all the reviewers' comments and the result is what
+we believe is a stronger manuscript.  
+\\ \\
+\noindent
+We also note that a few typos from the manuscript's original form have
+been addressed.  In particular, a small typo in equation (10) is
+resolved and some formatting issues were resolved in the bibliography.
+An itemized list of the changes addressing the reviewers' comments are
+below.
+\\ \\
+\noindent
+Sincerely,
+\\
+\noindent
+Bryan Quaife and Nick Moore
 
@@
 \begin{itemize}
-  \item The arclength term is now included in equation (29).
+  \item We thank the reviewer for noticing this typo.  The arclength
+    term is now included in equation (29).
 \end{itemize}

### 2018-12-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 % Journal of Computational Sciences
-\documentclass[3p]{elsarticle}
+%\documentclass[3p]{elsarticle}
+
+% AIP and APS Journals use revtex package.
+%\documentclass[aip, pof, reprint]{revtex4-1} 
+%\documentclass[reprint,superscriptaddress]{revtex4-1}
+% Note: I believe PRL is APS.
+
+\documentclass[reprint,superscriptaddress,notitlepage]{revtex4-1}
+% PRF is APS
 
@@
 %
-\author[Nick]{M.~Nicholas J.~Moore}
-\author[Bryan]{Bryan D.~Quaife}
-\address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
-\address[Bryan]{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+\author{M.~N.~J.~Moore}
+\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+\author{Bryan D.~Quaife}
+\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
 \begin{abstract}

### 2018-12-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{document}
-%\title{An eroding porous medium}
-\title{The development of anisotropy in an eroding porous medium}
+\title{Erosion leads to anisotropy in a porous medium}
+%\title{The development of anisotropy in an eroding porous medium}
 %
@@
 Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in Stokes flow---the regime of groundwater flow.
-This method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can practically simulate the erosion of order hundreds of solid bodies.
+This method is documented, validated, benchmarked in \cite{Quaife2018}, and can practically simulate the erosion of order hundreds of solid bodies.
 

### 2019-01-25 docs/transport/erosion_transport.tex
started to lay out transport methods paper

--- 2018-07-09 docs/methods/erosion_methods.tex
@@
 
-\title{A boundary-integral framework to simulate \\ viscous erosion of a porous medium}
+\title{Viscous Transport in Eroding Porous Media}
 
@@
 
+\author[SH]{Shang-Huan Chiu}
+\author[Nick]{M.~Nicholas J.~Moore}
 \author[Bryan]{Bryan D.~Quaife}
-\author[Nick]{M.~Nicholas J.~Moore}
+
+\address[SH]{Department of Scientific Computing, Florida State
+University, Tallahassee, FL, 32306.}
 \address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
@@
 \begin{abstract} 
-We develop numerical methods to simulate the fluid-mechanical erosion of many bodies in two-dimensional Stokes flow.
-The broad aim is to simulate the erosion of a porous medium (e.g.~groundwater flow) with grain-scale resolution.
-Our fluid solver is based on a second-kind boundary integral formulation of the Stokes equations that is discretized with a spectrally-accurate Nystr\"om method and solved with fast-multipole-accelerated GMRES.
-The fluid solver provides the surface shear stress which is used to advance solid boundaries.
-We regularize interface evolution via curvature penalization using the {\thL} formulation, which affords numerically stable treatment of stiff terms and therefore permits large time steps.
-The overall accuracy of our method is spectral in space and second-order in time.
-The method is computationally efficient, with the fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration, a mesh-independent number of GMRES iterations, and a one-time $\mathcal{O}(N^2)$ computation to compute the shear stress.
-We benchmark single-body results against analytical predictions for the limiting morphology and vanishing rate.
-Multibody simulations reveal the spontaneous formation of channels between bodies of close initial proximity.
-The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
+  An abstract
 \end{abstract}
@@
 \begin{keyword}
-  Porous medium \sep Stokes flow \sep Erosion \sep Boundary integral
-  equations \sep Shear stress \sep {\thL} formulation
+  Keyword 1 \sep Keyword 2 \sep Keyword 3 
 \end{keyword}
@@
 \section{Introduction\label{s:intro}}
-Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from massive land formations~\cite{han1969, perron2009formation, abrams2009growth, petroff2011geometry, jerolmack2012internal, Rothman2012, coh-dev-sey-yi-szy-rot2015, perkins2015amplification}, to centimeter-scale features and patterns~\cite{daerr2003erosion, berhanu2012shape, nienhuis2014wavelength, domokos2014river}.
-Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~soil, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}.
-Motivated by such examples, this paper develops numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow---the most relevant regime for groundwater \cite{bear2013dynamics, cao2010coupled} and the aforementioned bio-fluid applications.
-
-Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann, lopez2018cfd} and the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, dallaston2015channelization, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.
-In these cases, the fluid alters the morphology of immersed structures, which in turn modifies the surrounding flow field, and so on.
-Such examples of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is intertwined~\cite{hewett2017evolution}.
-From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges.
-First, since the medium is composed of many individual constituents, multiple bodies must be considered.
-Second, the dense packing present in typical porous-media applications requires close-range interactions to be resolved.
-Finally, long-range effects inherent to the Stokes limit couples the shape evolution of {\em all} bodies to a greater degree than any other regime.
-
-Ultimately, the methods developed here will lead to high-fidelity simulations of multibody Stokes erosion as illustrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions).
-Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow.
-In particular, we take the local erosion rate to be proportional to the magnitude of the shear stress---a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}.
-As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
-In particular, several bodies develop corner-like features and nearly flat faces, with straight channels intervening between them.
-In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient way to visualize local erosion rates.
-Several bodies vanish in finite time and the simulation continues without interruption.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.80 \textwidth]{./figs/50bod.pdf}
-\caption{\label{fig:50bodies} Simulation of 50 bodies eroding in Stokes flow under the action of fluid-mechanical shear.
-The flow is horizontal (left to right) and the 6 snapshots are evenly spaced in time.
-Color represents vorticity, which provides a convenient way to visualize local shear rates.
-Erosion not only diminishes the size of the bodies but also alters their shapes considerably.
-A few well-defined channels develop in the space between bodies.
-Several of the bodies vanish in finite time and the simulation continues without interruption.
-}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure generated from data file 50circ512p5, 
-%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
+A continuation of the methods paper~\cite{qua-moo2018}.
 
@@
 \paragraph{Contributions}
-To perform the above simulation, two fast and accurate methods are
-employed---one to solve the fluid equations and the other to evolve the
-eroding bodies.
-The fluid equations are reformulated in terms of a boundary integral equation (BIE)~\cite{poz1992}.
-Since the boundary conditions are Dirichlet, we employ a double-layer potential so that the resulting BIE is second-kind.
-This second-kind BIE is discretized with a spectrally accurate trapezoid rule~\cite{tre-wei2014} which results in a well-conditioned dense linear system for an unknown density function.
-The linear system is solved using fast-multipole-accelerated GMRES~\cite{saa-sch1986}.
-Once the density function is determined, we compute the shear stress with a spectrally accurate odd-even quadrature rule~\cite{sid-isr1988}.
-
-At the next stage, we must use the shear stress to advance solid boundaries.
-Tracking fluid-structure interfaces with long time horizons presents numerical challenges in that the underlying mesh can become distorted and tangled.
-Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
-We address these tracking issues in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arclength but that does not affect dynamics; second, we suppress high-frequency oscillations in the interface evolution via curvature penalization.
-The interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term \cite{hou-low-she1994}.
-This term can be easily be handled in a numerically stable fashion with an exponential integrator.
-Once the simulation is complete, we perform a post-processing step in which we compute bulk properties, such as vorticity and pressure, using an upsampled trapezoid rule.
-
-We supplement our primarily computational study with a few analytical results.
-In particular, our simulation shows that a single eroding body tends to a slender, for-aft symmetric form characterized by nearly uniform shear stress along its surface.
-This body exhibits sharp corners at its front and rear.
-The principle of long-time uniform stress combined with some local analysis leads to an analytical prediction for the opening angles formed at the front and rear.
-Additionally, slender-body theory gives rise to scaling laws for the reduction rate of the body's area and drag.
-These analytical results, in addition to their own intrinsic value, allow us to conclusively validate the numerical simulation.
+\begin{itemize}
+  \item Use novel near-singular Barycentric integration scheme for
+    Stokes equation outlined in~\cite{bar-wu-vee2015}.
+  \item Need to compute one additional derivative since we need the
+    derivative of the velocity to find the vorticity and stress tensor
+  \item Tracer trajectories at different time steps
+  \item Compute the anomalous diffusion rate using similar techniques as
+    the paper with Pietro~\cite{dea-qua-bir-jua2018}
+  \item Need a novel way to do time stepping through the complex
+    geometry
+\end{itemize}
 
 \paragraph{Limitations}
-We make two fundamental design choices in the simulations described here: first, we restrict attention to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations).
-By restricting to two dimensions, we can simulate many bodies (up to $50$ in this manuscript) with high resolution, enabling accurate characterization of porous-medium erosion.
-While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated and makes porous-medium simulations less feasible.
-Meanwhile, the second assumption of immobile bodies affords a simple framework to explore the effects of erosion in isolation.
-While other mechanisms, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.
-We therefore defer their study to future work.
+\begin{itemize}
+  \item Bodies are still pinned
+  \item Bodies are still two dimensional
+\end{itemize}
 
 \paragraph{Related Work}
-In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate the viscous erosion of a single body in three dimensions~\cite{mit-spa2016}.
-The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em arbitrary} background flow (e.g.~uniform flow, shear flow, etc.).
-An advantage of the traction formulation is that it directly provides the shear stress needed to evolve surfaces.
-In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations.
-Thus, rather than a {\em single, mobile} body as considered in~\cite{mit-spa2016}, we aim to simulate the erosion of {\em many, immobile} bodies.
-Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities (e.g.~vorticity, pressure, and velocity) that will assist our understanding of the erosion process.
-
-For the porous network simulations considered here, it is essential to
-resolve nonlocal effects between the different bodies.  BIEs naturally
-resolve these interactions, and they have been used extensively to
-simulate viscous fluids in complex geometries, including porous media
-flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.  Common challenges
-of a BIE formulation include developing efficient preconditioners for
-the discretized system and numerical difficulties associated with nearly
-touching bodies. In this work, we consider geometries requiring
-$\mathcal{O}(100)$ GMRES iterations, so preconditioners are currently
-unnecessary. In future work, we will address mobile bodies for which
-near contacts may necessitate preconditioners~\cite{qua-bir2015a, qua-cou-dar2018, cou-pou-dar2017}.
-Similarly, near-singular schemes will not be necessary due to the fact that the spacing between receding bodies of fixed position always grows in time.
-Again, the future consideration of mobile bodies may necessitate near-singular schemes~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.
 
@@
 \paragraph{Outline of the Paper}
-In Section~\ref{s:formulation}, we describe the governing equations for both the fluid and the erosion model in a \thL~framework.
-In Section~\ref{s:method}, the numerical methods in both space and time are described and Section~\ref{s:qoi} describes how to compute the vorticity, pressure, and drag.
-Section~\ref{s:SingleResults} gives several numerical examples for a single body, and Section~\ref{s:MultiResults} presents numerical examples for multiply-connected domains.
-Finally, concluding remarks are made in Section~\ref{s:conclusions}.
 
@@
 \label{s:formulation}
-We start by defining the main variables used to model erosion.
-We consider flows that are confined by a solid wall $\Gamma$ that encloses $M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.
-The bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.
-Therefore, the boundary of the fluid domain is $\bd\Omega = \Gamma \cup \gamma$.
-On each body, $\nn$ and $\ss$ denote the unit normal and unit tangent vectors respectively.
-Throughout the paper, we adopt the convention that $\ss$ points in the counterclockwise direction and $\nn$ points out of the fluid domain (i.e.~into the bodies).
-Neglecting inertial forces, the dynamics of the fluid is fully determined by the position of the bodies $\xx_\ell(s,t) \in \gamma_\ell$, where $s$ is the arclength and $t$ is time.
-Given $\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid velocity $\uu$, the pressure $p$, and the shear stress $\tau$.
-On the bounding wall, we prescribe a velocity $\UU(\xx,t)$.
-Then, the governing equations are
-\begin{equation}
-\label{eqn:erosionModel}
-\begin{split}
-  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{conservation
-of momentum}\\
-\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
-\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
-bodies} \\
-\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
-velocity} \\
-\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
-&&\mbox{\em erosion model} .
-\end{split}
-\end{equation}
-where $\Vn$ is the normal velocity of the interface.
-Parameters include the fluid viscosity $\mu$ and the material-dependent erosion constant $\CE$, as well as a characteristic flow speed $U^*$ and domain scale $L^*$.
-Non-dimensionalization, however, allows us to remove these parameters from consideration.
-We non-dimensionalize the Stokes equations in the standard way, equivalent to setting $\mu = 1$ above.
-For interface evolution, we scale time on the so-called erosion timescale $T^* = {L^*}^2/(\CE \mu U^*)$, which can be achieved by simply setting $\CE = 1$ above.
-In Section~\ref{sec:thetaL}, we will make slight modifications to the erosion model for better numerical stability.
-
-The outer wall is formed by rounding off the corners of $[-3,3] \times [-1,1]$, and we impose the Hagen-Poiseuille flow
-\begin{align}
-  \UU(\xx) = \umax (1-y^2,0)\, , \quad \xx \in \Gamma\, ,
-\end{align}
-where $U$ (dimensionless) sets the maximum of the imposed Poiseuille flow.
-Often, we will simply set $U=1$, but in some instances we change $U$ dynamically to enforce that the pressure drop across the computational cell is constant as bodies erode within it.
-To minimize the boundary effects of the inflow and outflow, we only place bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.
-
-\begin{figure}[htpb]
-  \centering
-  \input{figs/schematic.tikz}
-  \caption{\label{fig:schematic} A schematic for the governing equations.
-A no-slip boundary condition is imposed on each body $\gamma_\ell$ whose unit normal points outward relative to the geometry.
-On the outer geometry $\Gamma$, a Hagen-Poiseuille flow is imposed.
-The bodies erode at a rate that is equal to the magnitude of the shear stress applied by the fluid.
-The bodies are constrained to the middle third of the channel that is located between the dashed lines.}
-\end{figure}
-
-We describe how the incompressible Stokes equations are solved in $\Omega$ using a boundary integral equation in Section~\ref{sec:bies}.
-In Section~\ref{sec:shearStressLP}, we discuss how the shear stress is computed.
-Finally, in Section~\ref{sec:thetaL}, we describe how corners in the bodies are avoided and perform a change of coordinates to treat a stiff term.
+Similar to the JCP methods paper.  However, need to put everything into
+complex variables formulation so that we can use Barycentric ideas.
 
@@
 
-In this section, we describe an equivalent BIE formulation of the incompressible Stokes equations with Dirichlet boundary conditions
-\begin{equation}
-  \begin{split}
-  \Delta \uu &= \grad p\, , \qquad && \xx \in \Omega, \\
-  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
-  \uu &= \ff,  && \xx \in \bd\Omega.
-  \end{split}
-  \label{eqn:stokes}
-\end{equation}
-The boundary condition $\ff$ is the prescribed velocity $\UU$ on
-$\Gamma$, and it is zero on the eroding bodies $\gamma$.
-In two dimensions, a BIE for a stream function formulation is possible~\cite{gre-kro-may1996}, but this does not extend to three dimensions.
-Therefore, we adopt a primitive variable formulation where the velocity is written in terms of the standard double-layer potential~\cite{lad1963,poz1992}
-\begin{align}
-  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
-    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
-    \eeta(\yy) \, ds_\yy\, , \quad \xx \in \Omega \, ,
-    \label{eqn:velocityDLP}
-\end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown density function.  
-%As the viscosity $\mu$ also sets the time scale, we take $\mu=1$.
-
-Since the double-layer potential is not able to represent force- and torque-free velocity fields,  we complete the double-layer potential with Stokeslets and rotlets~\cite{pow-mir1987, pow1993}
-\begin{align}
-  S[\llambda_\ell,\cc_\ell] = \frac{1}{4\pi} \left(-\log \rho \II + 
-    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_\ell
-  \quad \text{and} \quad
-  R[\xi_\ell,\cc_\ell] = \frac{\rr^\perp}{\rho^2}\xi_\ell\, , 
-  \quad \ell=1,\ldots,M \, ,
-  \label{eqn:stokeslet_rotlet}
-\end{align}
-where  $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the $\ell^{th}$ grain, $\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then, the solution of~\eqref{eqn:stokes} is
-\begin{align}
-  \label{eqn:completed_DLP}
-  \uu(\xx) = \DD[\eeta](\xx) + 
-    \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
-    \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx)\, , \quad \xx \in \Omega \, ,
-\end{align}
-where the density function, Stokeslets, and rotlets satisfy
-\begin{subequations}
-\label{eqn:completed_BIE}
-\begin{align}
-  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
-      \sum_{\ell=1}^{M} S[\llambda_\ell,\cc_\ell](\xx) +
-      \sum_{\ell=1}^{M} R[\xi_\ell,\cc_\ell](\xx) + \NN_0[\eeta](\xx)\, ,
-      \quad \xx \in \bd\Omega \, , 
-      \label{eqn:DLP}\\
-  \llambda_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \eeta(\yy) \,
-  ds_\yy\, ,
-  \quad \ell=1,\ldots,M \, ,
-  \label{eqn:stokeslet} \\
-  \xi_\ell &= \frac{1}{2\pi}\int_{\gamma_\ell} \yy^\perp \cdot \eeta(\yy)
-  \, ds_\yy\, , \quad \ell=1,\ldots,M \, .
-  \label{eqn:rotlet}
-\end{align}
-\end{subequations}
-Here,
-\begin{align}
-  \NN_0[\eeta](\xx) = \int_{\Gamma} 
-    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy, \quad \xx \in
-    \Gamma\, ,
-\end{align}
-removes the rank one null space resulting from the flux-free requirement of $\ff$.
-
-This BIE formulation requires that $\bd\Omega$ is smooth.
-Unfortunately, smoothness is not guaranteed by erosion since corners develop at locations where the shear stress vanishes.
-One option is to modify our BIE to handle corners~\cite{rac-ser2017, ser-rok2016, hel2011, gil-hao-mar2014, bre2012}, but these methods require the corner's location, a non-uniform spaced mesh, or are ill-conditioned.
-Instead, we slightly modify the erosion model in Section~\ref{sec:thetaL} so that we can control the smoothness of the bodies.
-In this manner, the BIE as described above can be applied.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:shearStressLP}
-Once the density function, Stokeslets, and rotlets are computed, any desired quantity, including the shear stress, can be computed.  The shear stress is
-\begin{align}
-  \tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss \, .
-\end{align}
-The reader may notice an unusual sign convention above, but this is simply a consequence of our conventions for $\nn$ and $\ss$ (see Fig.~\ref{fig:schematic}).
-The velocity field of the completed double-layer potential~\eqref{eqn:completed_DLP} includes velocities from three terms: the double-layer potential, the Stokeslets, and the rotlets.
-We compute the deformation tensor $\ssigma = \frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of these terms individually.
-
-The deformation tensor of the double-layer potential~\eqref{eqn:velocityDLP} at an interior point $\xx \in \Omega$ is~\cite{qua-bir2014a}
-\begin{equation}
-  \label{eqn:shearStressDLP}
-  \begin{aligned}
-  \ssigma^\DD(\xx) = \frac{1}{2\pi}\int_{\bd\Omega} &\left(
-    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
-    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
-    \right. \\
-    &\left.
-    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
-    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right) \, ds_\yy \, .
-  \end{aligned}
-\end{equation}
-We require the deformation tensor on $\bd\Omega$, and this requires taking the limit of equation~\eqref{eqn:shearStressDLP} when $\xx$ tends to $\xx_0 \in \bd\Omega$.  The limiting value is
-\begin{align}
-  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}\sigma_\DD(\xx) =
-  J[\eeta](\xx_0) + \ssigma^\DD(\xx_0)\, , \quad \xx_0 \in \bd\Omega \, ,
-\end{align} 
-where
-\begin{align}
-  J[\eeta](\xx_0) = \frac{1}{2}\left(\pderiv{\eeta}{\ss} 
-    \cdot \ss\right) \left[ 
-  \begin{array}{cc}
-    s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
-  \end{array}\right] \, .
-  \label{eqn:shearStressJump}
-\end{align}
-Next, the deformation tensor of the Stokeslets and rotlets~\eqref{eqn:stokeslet_rotlet} are
-\begin{equation}
-  \label{eqn:shearStressSR}
-  \begin{aligned}
-  \ssigma^S(\xx_0) &= \sum_{\ell=1}^{M}
-    \frac{\rr \cdot \llambda_\ell}{4\pi\rho^2} \left(
-    \II - \frac{2}{\rho^2} \rr \otimes \rr \right),  \\
-  \ssigma^R(\xx_0) &= -\sum_{\ell=1}^M
-    \frac{\xi_\ell}{\rho^4} \left(\rr \otimes \rr^\perp + 
-    \rr^\perp \otimes \rr \right) \, .
-  \end{aligned}
-\end{equation}
-Combining these deformation tensors, the shear stress at $\xx_0 \in \bd\Omega$ is
-\begin{align}
-  \tau = -2 \left(J[\eeta](\xx_0) + \ssigma^\DD(\xx_0) + 
-    \ssigma^S(\xx_0) + \ssigma^R(\xx_0)\right) \nn \cdot \ss \, .
-  \label{eqn:shearStressLP}
-\end{align}
 
@@
 
-To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in the ability to numerically stabilize moving-interface problems~\cite{hou-low-she1994}.
-Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary.
-For a boundary parametrized by arclength $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin \theta \right)$.
-
-For numerical stability, we modify the erosion law~\eqref{eqn:erosionModel} to include a term that penalizes curvature $\kappa$.
-The idea is to prevent regions of extremely high curvature from developing, as these regions would compromise the accuracy and stability of our fluid solver.
-We thus replace~\eqref{eqn:erosionModel} with
-\begin{align}
-  \label{eqn:Vn}
-  \Vn = \atau + \eps \mean{\atau} \left( \frac{L }{2\pi} \kappa - 1
-  \right) \, .
-\end{align}
-The parameter $\eps \ll 1$ controls the strength of the curvature-penalization.
-This term causes regions of high curvature to recede more rapidly and thus suppresses any high-frequency oscillations that may exist.
-Above, $\mean{\cdot}$ indicates a boundary mean.
-Since a closed body has mean curvature $\mean{\kappa} = 2\pi / L$, the penalty term has mean zero and thus preserves area.
-The only source of material loss is therefore the shear-stress itself.
-In addition, we have scaled the penalty term on the mean absolute shear, $\mean{\atau}$, so that the ratio of smoothing-to-erosion always remains fixed, even as bodies vanish.
-
-In the following, we parameterize each boundary by normalized arclength, $\alpha = 2 \pi s / L$. In terms of $\alpha$, the curvature is given by
-\begin{align}
-\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha} \, ,
-\end{align}
-and substitution into~\eqref{eqn:Vn} gives
-\begin{align}
-\label{eqn:Vn2}
-  \Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right) \, .
-\end{align}
-
-The boundary of each body will be represented by a grid of collocation points.
-If we were to simply evolve the interfaces under~\eqref{eqn:Vn2}, this grid would become distorted, which, if unchecked, could lead to severe tangling and numerical instability.
-We therefore introduce an artificial tangential velocity $\Vs$ to keep the grid points equally spaced in arclength~\cite{hou-low-she1994}.
-The appropriate tangential velocity satisfies
-\begin{align}
-  \pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn} \, .
-\end{align} 
-The evolution of the interface is then given by the combination of the normal and tangential velocities
-\begin{align}
-  \dot{\xx}(t) = \Vn \nn + \Vs \ss \, .
-\end{align}
-Since $\Vs$ is tangential, it does not modify the physics of erosion, only the parameterization of the boundaries.
-
-When recast in the variables $\theta$ and $L$, the interface evolution becomes
-\begin{align}
-  \tderiv{L}{t} &= - 2 \pi \mean{\thalpha \Vn}, \\
-  \pderiv{\theta}{t} &= \frac{2 \pi}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right) \, .
-\end{align}
-Inserting~\eqref{eqn:Vn2} for the normal velocity gives
-\begin{align}
-\label{eqn:Levo1}
-\tderiv{L}{t} &= - 2 \pi \mean{\thalpha \Vn}, \\
-\label{eqn:thetaevo1}
-  \pderiv{\theta}{t} &= \frac{2\pi}{L} \left(
-  \eps \mean{\atau} \ppd{\theta}{\alpha} + \pderiv{\atau}{\alpha} +
-  \thalpha \Vs \right)\,.
-\end{align}
-These are the main evolution equations for $\theta(\alpha,t)$ and $L(t)$.
-In addition, it is necessary to track a reference point for each body, so that the {\thL} variables can be converted back to Cartesian coordinates.
-We track the coordinates of the surface mean $\mean{\xx}$, which moves according to
-\begin{align}
-\label{eq:xsurf}
-\frac{d}{dt} \mean{\xx} = \mean{ V_s \ss + V_n \nn } \, .
-\end{align}
-We note that tracking the center of mass is also a valid choice, but the surface mean gives a somewhat simpler formula.
-Equations~\eqref{eqn:Levo1}--\eqref{eq:xsurf} comprise the main system of equations to be solved numerically in Section~\ref{sec:timeStepping}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{s:method}
-To perform numerical simulations, we exploit the difference between the erosion and fluid time scales.
-Since erosion occurs much slower, we freeze the geometry at each time step, solve the incompressible Stokes equations, compute the shear stress, and then update the geometry according to the erosion model.
-Therefore, there are three main numerical methods that need to be developed.
-In Section~\ref{sec:BIE}, we describe how the BIE~\eqref{eqn:completed_BIE} is solved.
-Once the density function is found, Section~\ref{sec:shearStress} describes how the shear stress~\eqref{eqn:shearStressLP} is computed.
-Then, Section~\ref{sec:timeStepping} describes a time stepping method for advancing the interface according to equations~\eqref{eqn:Levo1}--\eqref{eq:xsurf}.
 
-To create stable simulations with long time horizons, we use numerical methods that achieve spectral accuracy in space, second-order accuracy in time, and maintain an equispaced discretization of the bodies.
-The boundaries are represented in Fourier space, giving us a set of discretization points $\xx_i$ of each body, and all derivatives and integrals (the arclength, curvature, and mean values) are computed with spectral accuracy using the Fourier representation.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fast Summation Methods}
+\label{sec:FMM}
 
@@
 
-To numerically compute the completed double-layer potential~\eqref{eqn:completed_BIE}, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
-Then, $N = MN_\iin + N_\out$ is the total number of discretization points of $\bd\Omega$.
-The double-layer potential in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
-\begin{align}
-  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
-      \Delta s_{j}\, , \quad i=1,\ldots,N \, ,
-  \label{eqn:trapDLP}
-\end{align}
-where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
-$\xx_j$, and
-\begin{align}
-  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
-      \frac{\rr \otimes \rr}{\rho^2} \, ,
-\end{align}
-where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is replaced with the limiting value of the double-layer potential
-\begin{align}
-  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)) \, ,
-\end{align}
-where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent vector at $\xx \in \bd\Omega$.
-The equations for the Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are also discretized with the trapezoid rule.
-Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
-\begin{subequations}
-  \label{eqn:completed_BIE_discretized}
-  \begin{align}
-  \label{eqn:discretized_DLP}
-    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
-      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
-      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) +
-      \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) \\
-    \llambda_\ell &= \sum_{\xx_j \in \gamma_\ell} \eeta(\xx_j) 
-      \Delta s_j \, , \\ 
-    \xi_\ell &= \sum_{\xx_j \in \gamma_\ell}
-      {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j \, ,
-  \end{align}
-\end{subequations}
-for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  When $\xx_i \in \Gamma$, the term 
-\begin{align}
-  \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
-      \nn(\xx_j))\eeta(\xx_j) \Delta s_j \, ,
-\end{align}
-is added to~\eqref{eqn:discretized_DLP}.  Since we discretize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.
-
-The linear system~\eqref{eqn:completed_BIE_discretized} is solved iteratively with the generalized minimal residual method (GMRES)~\cite{saa-sch1986}.
-Since the BIE is second-kind, only a mesh-independent number of GMRES iterations are required~\cite{cam-ips-kel-mey-xue1996}.
-Therefore, the asymptotic cost is determined by the cost of performing a matrix-vector multiplication, and the bulk of the cost is evaluating the $N$-term sum in~\eqref{eqn:discretized_DLP}.
-We use the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} so that the cost of solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$ operations.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:shearStress}
-We have decomposed the deformation tensor into contributions from three different terms.
-The contributions from the Stokeslets and the rotlets~\eqref{eqn:shearStressSR} can be immediately evaluated since they do not involve any integration to approximate.
-For the shear stress of the double-layer potential, we use a slight variant of the trapezoid rule.
-The kernel of the deformation tensor due to the double-layer potential~\eqref{eqn:shearStressDLP} is
-\begin{equation}
-\begin{aligned}
-  K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
-    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
-    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn)
-    \right. \\ & \hspace{25pt}+ \left.
-    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
-    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-  \right) \, .
-\end{aligned}
-\end{equation}
-This kernel has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy \rightarrow \xx$, and this is too strong for the unmodified trapezoid rule.
-The singularity strength can be reduced since the velocity corresponding to a constant density function is constant~\cite{poz1992}.
-Therefore, the deformation tensor of the double-layer potential is equivalent to
-\begin{align}
-  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
-      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}\, , \quad \xx \in \bd\Omega \, .
-\end{align}
-This expression has a singularity that is asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.
-Then, to achieve spectral accuracy, we apply the trapezoid rule with odd-even integration~\cite{sid-isr1988}.
-Therefore, the deformation tensor of the double-layer potential at a discretization point $\xx_i$ on body $\gamma_\ell$, with $i$ being odd, is approximated as
-\begin{align}
-  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_\ell}
-    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
-  \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
-    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j \, ,
-  \label{eqn:stressOddEven}
-\end{align}
-and a similar approximation is used when $i$ is even.
-We also need to approximate the jump in the deformation tensor~\eqref{eqn:shearStressJump}, and this is done with Fourier differentiation.
-Finally, the shear stress is computed by multiplying the deformation tensor by the normal vector, and taking the inner product with the tangent vector.
-
-We do not employ an FMM to evaluate the shear stress at $\xx_i$, $i=1,\ldots,N$, so the cost of evaluating the shear stress is $\bigO(N^2)$.
-However, unlike the velocity double-layer potential that is evaluated at each GMRES iteration, the shear stress is only computed once per time step.
-In future work, we plan to use a kernel-independent FMM~\cite{yin-bir-zor2004} to evaluate the shear stress with $\bigO(N)$ operations.
 
@@
 
-With the shear stress computed, we are now ready to numerically evolve the boundary of each body using the {\thL} framework.
-The main equations to be solved are~\eqref{eqn:Levo1}--\eqref{eq:xsurf}.
-In Section~\ref{sec:thetaL} we introduced a curvature-penalizing term into the erosion law~\eqref{eqn:Vn}.
-This term suppresses high-frequency oscillations, but also introduces {\em stiffness} into evolution equation~\eqref{eqn:thetaevo1}.
-We will therefore use a combined exponential-integrator/Runge-Kutta method to solve system~\eqref{eqn:Levo1}--\eqref{eq:xsurf}.
-The exponential integrator will handle the stiff term in a numerically stable fashion, while the Runge-Kutta method will treat nonlinear terms explicitly.
-Our overall time-stepping method will be second-order accurate.
-
-First, we must address another potential source of numerical instability.
-The erosion law~\eqref{eqn:Vn} depends on the {\em absolute value} of shear stress, $\atau$, which exhibits a corner anywhere $\tau$ changes sign, i.e.~at a stagnation point.
-The corner in $\atau$ introduces high frequencies into~\eqref{eqn:thetaevo1} which could result in either numerical instability or an extremely stringent step-size restriction.
-To avoid these difficulties, we smooth $\atau$ via a narrow Gaussian filter of width $\sigma \ll 1$
-\begin{align}
-\atausig = \int_{\gamma} \frac{1}{\sqrt{2\pi} \sigma}
- \exp \left(- \frac{\alpha'^2}{2 \sigma^2}\right) \abs{ \tau(\alpha - \alpha') } \, d\alpha' \, ,
-\end{align}
-with corresponding normal and tangential interface velocities
-\begin{align}
-& \Vnsig = \atausig +  \eps \mean{\atausig}
-\left(\pderiv{\theta}{\alpha} - 1 \right), \\
-& \pderiv{\Vssig}{\alpha} = \thalpha \Vnsig - \mean{\thalpha \Vnsig} \, .
-\end{align}
-This smoothing further suppresses the feedback of high frequencies between $\atau$ and the body shape.
-
-We now consider the system of evolution equations given by~\eqref{eqn:Levo1}--\eqref{eq:xsurf}. For convenience, we introduce the following variables
-\begin{align}
-%\label{eq:M}
-& \Mterm = - 2 \pi \mean{\thalpha \Vnsig} \, , \\
-%\label{eq:N}
-& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha
-\Vssig \right) \, , \\
-%\label{eq:elfun}
-& \elfun = \frac{2 \pi}{L}  \mean{\atausig} \, .
-\end{align}
-Then,~\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1} can be compactly expressed as
-\begin{align}
-\label{eqn:Levo2}
-& \tderiv{L}{t} = \Mterm \, , \\
-\label{eqn:thetaevo2}
-& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm \,.
-\end{align}
-The diffusive term on the right of~\eqref{eqn:thetaevo2} results from the curvature penalization and is the stiffest term present.
-This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$).
-Meanwhile, $\NLterm$ represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$.
-Since the local shear stress depends on interactions between bodies, $\NLterm$ is both nonlinear and nonlocal.
-
-We will evolve $\theta(\alpha,t)$ in spectral space and so introduce the Fourier series for $\theta$ and $\NLterm$
-\begin{align}
-\label{thetaSeries}
- \theta(\alpha,t) &= \alpha + \FourierSum \thhat_k e^{ i k \alpha} \, , \\
- \NLterm(\alpha,t)  &= \FourierSum \widehat{\NLterm}_k e^{ i k \alpha} \, .
-\end{align}
-The careful reader will notice that in~\eqref{thetaSeries} we have decomposed $\theta(\alpha)$ into a linear component and a periodic component.
-In spectral space,~\eqref{eqn:thetaevo2} produces the system of ODEs
-\begin{align}
-\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k =
-\widehat{\NLterm}_k\, ,
-\qquad k=-N_\iin/2,\ldots,N_\iin/2-1\, .
-\end{align}
-These ODEs can be simplified by applying the integrating factor
-\begin{align}
-\label{eq:mu}
-\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right) \, ,
-\end{align}
-which leads to the coupled system
-\begin{align}
-\label{eqn:Levo3}
-& \tderiv{L}{t} = \Mterm \, , \\
-\label{eqn:thetaevo3}
-& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \widehat{\NLterm}_k \, ,
-\qquad k = -N_\iin/2, \ldots, N_\iin/2 -1 \, .
-\end{align}
-Note that the diffusive term from~\eqref{eqn:thetaevo2} does not appear explicitly in~\eqref{eqn:thetaevo3}, but rather is implied by the integrating factor~\eqref{eq:mu}.
-This is the idea of an exponential integrator.
-We solve the resulting system~\eqref{eq:mu}--\eqref{eqn:thetaevo3} with an explicit, second-order Runge-Kutta method (RK2).
-In particular, we use the {\em midpoint} RK2 method because it maximizes the smoothing effect of the diffusive term.
-
-At the first stage of RK2 (the half step) we discretize~\eqref{eq:mu}--\eqref{eqn:thetaevo3} as
-\begin{align}
-\label{eq:mu12d}
-& \mu_k^{(n+1/2)} = \mu_k^{(n)} \exp \left( \eps k^2 \frac{\Dt}{2}
-\zeta^{(n)} \right) \, , \\
-\label{eq:L12d}
-& \frac{L^{(n+1/2)} - L^{(n)}}{\Dt/2} = \Mterm^{(n)} \, , \\
-\label{eq:th12d}
-& \frac{ \mu_k^{(n+1/2)} \thhat_k^{(n+1/2)} - \mu_k^{(n)} \thhat_k^{(n)}}{\Dt/2} 
-= \mu_k^{(n)} \hat{\NLterm}_k^{(n)} \, ,
-\end{align}
-where the superscript indicates the time step.
-At the next stage of RK2 it will be necessary to evaluate derivatives at the half step $n+1/2$, thus requiring a call to the Stokes solver for which the body shapes must be known.
-We therefore insert~\eqref{eq:mu12d} into~\eqref{eq:th12d} and solve for $\thhat_k^{(n+1/2)}$, giving
-\begin{align}
-\label{eq:th12}
-\thhat_k^{(n+1/2)} = \left( \thhat_k^{(n)} + \frac{1}{2} \Dt \, \hat{\NLterm}_k^{(n)} \right)
-\exp \left( -\epsilon k^2 \frac{\Dt}{2} \elfun^{(n)}\right) \, .
-\end{align}
-Since $\zeta >0$, the exponential term always {\em suppresses} high-frequencies (exponentially with $k^2$).
-In other words, this is a smoothing term.
-With the geometry at step $n+1/2$ known, a call to the Stokes solver allows the computation of $\Mterm^{(n+1/2)}$, $\widehat{\NLterm}_k^{(n+1/2)}$, and $\zeta^{(n+1/2)}$.
-
-At the second stage of RK2, we discretize~\eqref{eq:mu}--\eqref{eqn:thetaevo3} as 
-\begin{align}
-\label{eq:mu1d}
-& \mu_k^{(n+1)} = \mu_k^{(n)} \exp \left( \eps k^2 {\Dt} \,
-\zeta^{(n+1/2)} \right) \, , \\
-\label{eq:L1d}
-& \frac{L^{(n+1)} - L^{(n)}}{\Dt} = \Mterm^{(n+1/2)} \, , \\
-\label{eq:th1d}
-& \frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \mu_k^{(n)} \thhat_k^{(n)}}{\Dt} =
-\mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)} \, .
-\end{align}
-We must eventually compute the geometry at step $n+1$, and so we insert~\eqref{eq:mu1d} into~\eqref{eq:th1d} and solve for $\thhat_k^{(n+1)}$, giving
-\begin{align}
-\thhat_k^{(n+1)} =  \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt
-\elfun^{(n+1/2)} \right) + \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left(
-- \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)}
-\right) \right) \, .
-\end{align}
-Once again, both exponential terms act to smooth the geometry. Finally, to track the reference point, $\mean{\xx}$, we simply apply the same RK2 method to~\eqref{eq:xsurf}.
-
-We point out that most exponential integrators use some form of quadrature to treat~\eqref{eq:mu}, but, here, we have simply applied the same RK2 method used for the rest of the system.
-We believe this to be a simple, systematic approach to arrive at a self-consistent discretization of desired accuracy because it avoids choices regarding which quadrature to use (midpoint, trapezoid, Simpson's, etc.) and can be easily generalized to other time-stepping methods, such as fourth-order Runge-Kutta.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{s:qoi}
-We further characterize the flow by computing the vorticity
-(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
-and drag (Section~\ref{sec:drag}).  Once
-equation~\eqref{eqn:completed_DLP} is solved for the velocity, $\uu =
-(u,v)$, the vorticity and pressure will be computed at points both
-inside the fluid bulk and on the along individual bodies, and then the
-drag of individual bodies will be computed.  For target points in the
-fluid domain, the integrands of the layer potentials are periodic and
-smooth, and the trapezoid rule guarantees spectral
-accuracy~\cite{tre-wei2014}.  However, if the target point is close to
-$\bd \Omega$, a nearly-singular integrand must be integrated, and this
-requires upsampling that is described in Section~\ref{sec:NSI}.  When
-the target points is on the boundary, the integrands involve
-singularities that are evaluated by combining singularity subtraction
-and odd-even integration~\cite{sid-isr1988}.
 
@@
 \subsection{Vorticity}
-\label{sec:vorticity}
-We start by computing the vorticity $\omega(\xx) = v_x - u_y$ for $\xx \in \Omega$ which we decompose into contributions from the double-layer potential, Stokeslets, and rotlets.
-The vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
-\begin{align}
-  \omega^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
-    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}
-    (\rr \cdot \eeta) \, ds_{\yy}\, .
-  \label{eqn:vorticityDLP}
-\end{align}
-To compute~\eqref{eqn:vorticityDLP} numerically, we apply the trapezoid rule with an upsampling scheme described in Section~\ref{sec:NSI}.  Next, the vorticity due to the Stokeslet is
-\begin{align}
-  \omega^S(\xx) = -\frac{1}{\pi} \sum_{\ell=1}^{M} 
-    \frac{\rr \cdot \llambda_\ell^\perp}{\rho^2}\, ,
-\end{align}
-and the vorticity of a rotlet is zero.  Therefore, the vorticity at $\xx
-\in \Omega$ is
-\begin{align}
-  \omega(\xx) = \omega^\DD(\xx) + \omega^S(\xx)\, .
-\end{align}
-
-For the Stokes equations, on boundaries that have a no-slip boundary condition, the shear stress is equivalent to the vorticity.
-Therefore, the vorticity is computed on the bodies $\gamma_\ell$ by numerically computing the shear stress as described in Section~\ref{sec:shearStress}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:pressure}
-To compute the pressure at $\xx \in \Omega$, we follow the same procedure used for the shear stress and vorticity.
-We first compute the pressure of the double-layer potential for $\xx \in \Omega$ and add the appropriate jump if $\xx \in \Gamma$.
-The pressure of the double-layer potential~\eqref{eqn:velocityDLP} at $\xx \in \Omega$ is
-\begin{align}
-  p^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot \eeta(\yy) \,ds_\yy \, .
-    \label{eqn:pressureDLP}
-\end{align}
-To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid rule with an upsampling scheme described in Section~\ref{sec:NSI}.  The pressure due to the Stokeslets is
-\begin{align}
-  p^S(\xx) = \sum_{\ell=1}^{M}\frac{\rr \cdot
-  \llambda_\ell}{2\pi\rho^2}\, ,
-\end{align}
-and the pressure due to the rotlets is zero.  Therefore, the pressure is
-\begin{align}
-  p(\xx) = p^{\DD}(\xx) + p^{S}(\xx)\, , \quad \xx \in \Omega \, .
-\end{align}
-
-For target points on the boundary of the geometry, $\xx \in \bd \Omega$, there is an additional term resulting from a jump in the pressure double-layer potential~\cite{poz1992}
-\begin{align}
-  p(\xx)= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
-              p^{S}(\xx)\, , \quad \xx \in \bd\Omega \, .
-  \label{eqn:pressureJump}
-\end{align}
-Similar to the shear stress, the singularity of the kernel~\eqref{eqn:pressureDLP} is too strong when $\xx \in \bd\Omega$ for the trapezoid rule to be directly applied.
-Therefore, we again subtract a constant density function and write the pressure as
-\begin{align}
-  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
-    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy\, , 
-    \quad \xx \in \bd\Omega\, .
-  \label{eqn:pressureOddEven}
-\end{align}
-Then, identical to how the shear stress is computed in~\eqref{eqn:stressOddEven}, odd-even integration is used to evaluate~\eqref{eqn:pressureOddEven}, and the jump condition in~\eqref{eqn:pressureJump} is computed with Fourier differentiation.
 
@@
 \label{sec:drag}
-Once the pressure and shear stress are computed, the drag on a single body with boundary $\gamma_\ell$ is
-\begin{align}
-\FFD = \int_{\gamma_\ell} p \nn + \tau \ss \,ds\, .
-\label{eqn:drag}
-\end{align}
-The reader may notice an unusual sign convention for pressure in this formula, which is simply due to the normal direction pointing {\em into} the bodies.
 
@@
 \label{sec:NSI}
-The layer potentials for the velocity~\eqref{eqn:velocityDLP}, vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP} need to be evaluated at points $\xx \in \Omega$.
-We write the general layer potential as
-\begin{align}
-  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) \, ds_\yy\,, \quad \xx \in \Omega\, .
-  \label{eqn:genericLP}
-\end{align}
-Since the integrand is periodic and smooth, the trapezoid rule guarantees spectral accuracy.
-However, when the target point $\xx$ is close to $\bd\Omega$, the integrand is nearly-singular, and the accuracy of the trapezoid rule deteriorates unless a large number of discretization points are used~\cite{bar2014}.
-We are only interested in computing the velocity, vorticity, and pressure to visualize the flow, so it is not necessary that we resolve the integrands for arbitrarily close target points.
-
-The layer potential~\eqref{eqn:genericLP} is approximated with the trapezoid rule 
-\begin{align}
-  \phi(\xx) = \sum_{j=1}^N q_j K(\xx,\yy_j)\, ,
-  \label{eqn:layerPotential}
-\end{align}
-where $q$ contains the quadrature weights, Jacobian, and density function, and $N$ depends on the distance between $\xx$ and $\bd\Omega$.
-Based on numerical experiments, the error of the $N$-point trapezoid rule is acceptable for points $\xx$ that are more than five arclength spacings from $\bd\Omega$.
-For points that are closer than five arclength spacings to $\bd\Omega$, we use an upsampled trapezoid rule.
-The required upsampling of the geometry and the density function is done with a Fourier interpolant.
-To minimize the number of discretization points that are used to approximate the layer potential~\eqref{eqn:layerPotential}, we use the same upsampling rate for all target points in dyadic intervals (Table~\ref{tbl:upsampling}).
-For points that are closer than $5/16$ of an arclength from $\bd\Omega$, a value of 0 is simply assigned to $\phi$.
-\newcolumntype{V}{>{\centering\arraybackslash}m{4em}}
-\newcolumntype{N}{@{}m{0pt}@{}}
-\begin{table}[htpb]
-\begin{center}
-\caption{\label{tbl:upsampling}The upsampling rate of our near-singular integration scheme.
-$d(\xx,\bd\Omega)$ is the distance between $\xx \in \Omega$ and $\bd\Omega$, and $h$ is an arclength spacing.}
-\vspace{0.3 pc}
-\label{table:arangle}
-\begin{tabular}{|V|V|V|V|V|V|N}
-  \hline
-  $d(\xx,\bd\Omega)$ &
-  $\left[5h,\infty\right]$ &
-  $\left[\frac{5}{2}h,5h\right]$ &
-  $\left[\frac{5}{4}h,\frac{5}{2}h\right]$ & 
-  $\left[\frac{5}{8}h,\frac{5}{4}h\right]$ &
-  $\left[\frac{5}{16}h,\frac{5}{8}h\right]$ & \\ [2ex] 
-  \hline
-  Upsample Rate & 1 & 2 & 4 & 8 & 16 & \\
-  \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-If eroding bodies are also sedimenting, bodies will come too close to one another for upsampling to be sufficient.
-Therefore, future work will apply one of several near-singular integration schemes available in the literature~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a}.
 
@@
 \label{s:SingleResults}
-With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow.
-We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation.
-In Section~\ref{s:MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.
 
 \subsection{A single body eroding in Stokes flow}
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.80 \textwidth]{./figs/01bodseq.pdf}
-\caption{A single body eroding in Stokes flow.
-As the body erodes, it develops a corner at its front and rear stagnation points, while remaining for-aft symmetric due to time-reversibility.
-Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress.
-In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 10^{-6}$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
-\label{01bodseq} 
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024aa;
-% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
-
-Figure~\ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times.
-Here, color represents the vorticity of the surrounding flow.
-When evaluated on the boundary, vorticity corresponds to the shear stress and thus the local erosion rate.
-As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity at its top and bottom.
-The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points.
-At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry.
-The greatest material loss has occurred at the body's top and bottom, where shear is strongest.
-Interestingly, the body has developed well-defined corners at its front and rear stagnation points.
-This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry.
-As shown in the third snapshot, this corner persists as the bodies becomes even more slender and continues to shrink.
-
-To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times.
-The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes in the simulation.
-As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape that has corners at its front and back---somewhat reminiscent of an American football.
-Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces.
-The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0 and 0.5 corresponding to the rear and front stagnation points respectively.
-At early times (yellow curves), the stress varies significantly, with more stress concentrated at the top and bottom of the body.
-However, as erosion reshapes the body, the stress becomes more uniformly distributed over the entire surface (red curves).
-The absolute stress $\atau$ shows slight peaks near the stagnation points as the body nears the final stages of erosion (dark red).
-Closer inspection reveals that the stress actually vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow with time.
-We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing).
-Interestingly, stagnation points do indeed recede in laboratory experiments on erosion  \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013}, leading us to believe that the numerical smoothing represents a real physical mechanism (see \cite{moo-ris-chi-zha-she2013} for discussion).
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.8 \textwidth]{./figs/shrink_intface.pdf}
-\caption{
-Shape and stress evolution: (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} shown at evenly-spaced time intervals.
-Color indicates normalized time, $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body completely vanishes.
-(b) The distribution of absolute shear stress, $\atau$, along each of these interfaces.
-Normalized arclength, $s/L$, runs counterclockwise from the rear stagnation point.
-The stress initially varies over the body's surface, but becomes more uniform over time.}
-\label{shrink_intface}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024aa;
-% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
 
@@
 
-Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress grows as the body vanishes.
-This observation is consistent with the well-known 3D Stokes drag law, in which stress, $\tau \sim \mu \umax / a$, scales inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is the radius).
-This law must be modified in two dimensions, though.
-The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory~\cite{batchelor1970slender, MooreJFM2012}.
-For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to $\mu \umax \ell/ \log(\ell/a)$, where $a \ll \ell $ is a length scale of the cross-section.
-This law implies that the stress-per-unit-span on a 2D cross-section is approximately
-\begin{align}
-  \label{eqn:stresslaw}
-  \tau \sim \frac{\mu \umax}{a \log(\ell/a)}\, , \qquad \text{for } a \ll \ell \, .
-\end{align}
-In interpreting our 2D simulations, we will treat the span, $\ell$, as fixed.
-Recall that $L$ denotes the total perimeter of the 2D cross-section.
-Since $L$ and $a$ each represent a characteristic scale of the cross-section, they can often be interchanged in scaling analysis.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
-\caption{Area and drag: (a) The area of the eroding body as measured in the simulations (black) shown against scaling law~\eqref{area_predict} (dotted red).
-The prediction and measurements agree closely.
-(b) The total horizontal drag exerted by body (black), along with the viscous (green) and pressure (blue) contributions.
-Slender-body theory yields the drag estimate~\eqref{dragscaling} (dotted red), which agrees well with the simulation as $t \to t_f$.}
-\label{area_drag}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024aaa;
-% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-7, fixarea = 0, fixpdrop = 0
-
-The body's rate of area reduction is given by integrating the absolute shear stress around the boundary
-\begin{align}
-\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
-\end{align}
-Thus, the rate of area reduction is given by the product of the mean shear stress $\mean{\atau}$ and the perimeter $L$, which is an {\em exact} relation.
-Inserting scaling law~\eqref{eqn:stresslaw} gives the estimate
-\begin{align}
-\dot{A} \sim \frac{ - \mu \umax}{\log(\ell/a)} \qquad \text{as } a \to 0 \, . 
-\end{align}
-Noting that $A \sim a^2$ allows one to solve the ODE, giving
-\begin{align}
-\label{area_predict}
-\frac{A}{A_0} \left( 1 - c_1 \log{\frac{A}{A_0}} \right) \sim \frac{t_f - t}{t_f} \quad \text{as } t \to t_f \, .
-\end{align}
-Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area, and $c_1$ is a free constant.
-The above is an {\em implicit} relationship for how area scales down in time, and we can use this prediction to test our numerical simulation.
-In Fig.~\ref{area_drag}(a) we compare the area measured in our numerical simulation (black curve) against the above scaling law (red dotted curve) with $c_1 = 0.24$ a fit parameter.
-The two agree remarkably well throughout the entire simulation, thus co-validating the simulation and asymptotic results.
-
-As the body shrinks in accordance with~\eqref{area_predict}, the drag that it exerts decreases at a related rate, offering a second check on our numerics.
-In Fig.~\ref{area_drag}(b), we show the horizontal drag, $F_D$, on the simulated body as it changes in time (black curve).
-The drag is calculated using~\eqref{eqn:drag} and, in the context of slender-body theory, this should be interpreted as the drag-per-unit-span.
-As seen in the figure, $F_D$ decreases gradually at first, then abruptly drops to zero in the final moments of the body's existence.
-Though it may seem peculiar, the sudden drop is consistent with the 2D Stokes law in which drag vanishes {\em logarithmically} with body size.
-Additionally,~\eqref{eqn:drag} permits us to calculate the separate contributions of pressure and viscous drag, which we show by the blue and green curves in Fig.~\ref{area_drag}(b) respectively.
-Initially, pressure and viscous drag are comparable, with the circular geometry having a slightly higher level of pressure drag.
-As the body erodes and assumes a more slender form, though, the pressure drag decreases more rapidly, leaving viscous drag to dominate.
-This behavior is associated with convergence to a drag-minimizing profile, which is discussed in Section~\ref{LimitingShape}.
-
-As a check on these results, we can use slender-body theory to estimate the drag-per-unit-span
-\begin{align}
-\label{dragscaling}
-\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}\, ,	\qquad \text{for } a \ll \ell \, .
-\end{align}
-For a {\em circular} cylinder, the normalization factor $4 \pi$ produces an {\em exact} relationship (within the context of slender-body theory), where $a$ is taken to be the radius.
-For other shapes, the formula will be approximate and we define $a = \sqrt{A/\pi}$ as the characteristic length scale since it generalizes the case of a circle.
-In Fig.~\ref{area_drag}(b) we show this prediction (red dotted curve), where $\ell = 2.3 a_0$ is a fit parameter and $a_0 = 0.2$ is the radius of the initially circular body.
-The scaling law and measured drag agree closely as $t \to t_f$, confirming that the simulation accurately captures the slender limit as the body disappears.
-
-\subsection{Local analysis for the limiting shape}
-\label{LimitingShape}
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.4 \textwidth]{./figs/corner.pdf}
-\caption{Schematic of 2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function in polar coordinates $\psi(r,\theta)$, for $\theta \in [-\theta_0, \theta_0]$.}
-\label{corner}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-
-With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a).
-In particular, consider the corner formed at the front and rear of the body.
-Locally, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge; see Fig.~\ref{corner} for a schematic.
-We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface~\cite{moo-ris-chi-zha-she2013, moore2017riemann}.
-For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$ (in this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).
-
-The corresponding stream function is biharmonic, $\Delta^2 \psi = 0$, and the ansatz $\psi = r^{\lambda}f(\theta)$ gives the 4th-order ODE~\cite{poz1997}
-\begin{align}
-\label{fODE}
-f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0 \, .
-\end{align}
-This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$ and odd symmetry about the horizontal axis, $f(0) = f''(0) = 0$.
-For arbitrary opening angle, ODE~\eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$.
-We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and therefore set $\lambda = 2$.
-The odd-symmetric solution to~\eqref{fODE} corresponding to $\lambda=2$ is
-\begin{align}
-  f(\theta) = B \sin (2 \theta) + C \theta \, .
-\end{align}
-Imposing no slip along the wedge surface gives the condition
-\begin{align}
-  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0 \, .
-\end{align}
-This nonlinear equation has solution $\thb \approx 129^\circ$, which implies that the uniform-stress wedge has an opening angle of $\oangle \approx 102^\circ$.
-% Pozrikidis page 239: symmetric flow.
-
-\subsection{Fixed-area simulations}
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.85 \textwidth]{./figs/fixed_intface.pdf}
-\caption{Fixed-area simulations: (a) Interfaces of a body eroding under shear stress but with the area artificially kept constant.
-Inset: zoom near the rear stagnation point, showing that the corner is actually smooth on a fine scale.
-(b) The shear-stress distribution on each of these interfaces.
-As the body erodes and converges to a terminal form, the stress becomes more uniformly distributed over the entire surface.
-Here time is normalize by the same value $t_f = 1.79 \times 10^{-2}$ from Fig.~\ref{shrink_intface}.}
-\label{fixed_intface}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024c5
-% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
-
-We now aim to measure the opening angles formed in the numerical simulations to compare against the above prediction.
-However, Section~\ref{sec:scaling} shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations to lose accuracy in the final, critical moments when the body is expected to approach its limiting shape.
-To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
-\begin{align}
-\Vn \leftarrow \Vn - \mean{\Vn} \, .
-\end{align}
-This modification allows erosion to sculpt the shape as it would normally, but with the area artificially held fixed.
-
-We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process, with the same spatial resolution, $N_\iin = 1024$, as before.
-Notice the body obtains a similar profile as observed previously, but now with fixed area.
-Importantly, more numerical accuracy is available to quantify the terminal state.
-The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear corner and demonstrates that, due to our numerical regularization, the body is actually smooth on a fine scale.
-We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces.
-As observed previously, the stress becomes more evenly distributed as erosion reshapes the body.
-The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy.
-Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points.
-In this figure, time is normalized by the vanishing time $t_f = 1.79 \times 10^{-2}$ from the shrinking simulations (i.e.~Fig.~\ref{shrink_intface}).
-Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerged before the body disappeared~\cite{moo-ris-chi-zha-she2013}.
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.85 \textwidth]{./figs/arangle.pdf}
-\caption{Shape characteristics of an eroding body: (a) The aspect ratio (width to height) versus time.
-(b) The measured opening angle versus time.
-For both measurements, we show three cases of the smoothing parameters: $\eps = \sigma = 20/1024, 10/1024,$ and 5/1024.
-In the finest simulation ($5/1024$) the aspect ratio converges to 2.7 and the opening angle converges to the predicted value of $102^{\circ}$ in long time.}
-\label{fig:arangle}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure from datafile 01circ1024c5
-% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0
-
-These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches the terminal state.
-In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners.
-In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters, $\eps$ and $\sigma$, to assess how the numerical regularization influences shape.
-In the three cases, we keep $\eps = \sigma$ always and set them to the values 20/1024, 10/1024, and 5/1024.
-Loosely, these values correspond to smoothing over the nearest 20, 10, and 5 grid points, respectively.
-Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time.
-The initially circular geometry has an aspect ratio of unity, and, as erosion carves a more slender form, the aspect ratio increases monotonically.
-The three simulations are all very close to one another, demonstrating convergence as $\eps, \sigma \to 0$.
-In the simulation with the least smoothing ($\eps = \sigma = 5/1024$), the aspect ratio tends to a value of 2.7 in long time.
-
-Next, we aim to measure the opening angle of the front/rear corner.
-Since these simulated bodies are actually smooth on a fine scale, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points.
-To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5).
-We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there.
-Although this procedure is subject to some uncertainty (to be examined below), we have found it to give robust angle measurements.
-Figure~\ref{fig:arangle}(b) shows the opening angle, $\beta$, as it varies in time for the three cases of smoothing parameters.
-For the initially circular geometry, our procedure yields the correct opening angle of $180^{\circ}$, i.e.~a flat front face.
-As time proceeds, erosion carves a sharper corner and $\beta$ decreases monotonically.
-Here, the three cases of smoothing parameters are more easily distinguished, implying that the opening angle is more sensitive to the level of numerical smoothing than the aspect ratio is.
-The curves nevertheless show convergence as $\eps, \sigma \to 0$.
-In the finest simulation ($\eps = \sigma = 5/1024$), $\beta$ converges to the value $102^{\circ}$, which agrees precisely with the analytical prediction from Section~\ref{LimitingShape}.
-
-To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three cases.
-The table shows that both the aspect ratio and opening angle converge at a rate that is nearly linear as $\eps, \sigma \to 0$.
-In addition, we show an estimate of the uncertainty involved in our angle measurement, obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points.
-The estimates show that as $\eps, \sigma \to 0$ the angle-measurements become more precise and converge to the predicted value of $102^{\circ}$.
-
-% Table
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{table}%[htbp]
-\begin{center}
-\caption{The long-time aspect ratio and opening-angle measurements for three cases of numerical smoothing.
-In these runs, we fix the resolution $N_\iin = 1024$, and vary the two smoothing parameters, $\eps, \sigma$.
-As $\eps, \sigma \to 0$, the aspect ratio tends to roughly 2.7 and the opening angle converges to the predicted value of $102^{\circ}$.
-Furthermore, the uncertainty in the angle measurement becomes smaller.
-} 
-\vspace{0.3 pc}
-\begin{tabular}{c c c}
-\hline
-\hspace{0.5pc} smoothing parameters: $\eps$ and $\sigma$
-\hspace{0.5pc} & final aspect ratio 
-\hspace{0.5pc} & final opening angle \\
-\hline
-20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
-10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
-5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% npts = 1024
-
-In summary, we have found that a single-body eroding in 2D Stokes flow converges to a terminal form characterized by nearly uniform shear stress along its surface.
-The final shape is fairly slender, with an aspect ratio of 2.7, and distinguished by  corners of opening angle $102^{\circ}$ at the front and rear.
-This shape is closely related to the drag-minimizing profile found by Pironneau (1973)---the geometry that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume~\cite{pir1973}.
-Using variational principles, Pironneau showed that the drag-minimizing form has constant shear (or vorticity) along its surface.
-The resulting {\em axisymmetric} shape has an aspect ratio of 2.1 and front/rear opening-angles of $120^{\circ}$~\cite{pir1973, mit-spa2016}.
-Interestingly, 3D simulations of viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form~\cite{mit-spa2016}.
-It was found that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform.
-Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ for self-similar reduction~\cite{pir1973, mit-spa2016}.
-Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well.
-Therefore, the shape observed in our simulation is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape.
-How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{fixed_intface}(b).
-
-\subsection{Convergence test}
-As a final validation, we now verify that our method converges with the expected second-order accuracy in time.
-For this, we run the same single-body simulation shown in Figs.~\ref{01bodseq} and~\ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$.
-This stopping time is 56\% of the vanishing time, and was selected so that the body will have eroded substantially but is not small enough to compromise accuracy (due to the stress diverging).
-We assess error by measuring the $L^2$-difference in the body shape obtained from simulations of successive resolution, with $\Delta t$ halved at each stage.
-In Table~\ref{convtab}, we report these errors along with the order of accuracy, obtained by Richardson-extrapolation-type calculations.
-The table confirms that our method converges with expected second-order accuracy.
-The last column of the table shows the CPU time taken for the simulation to run on a single-processor machine.
-%, demonstrating a nearly linear increase in computational time with refinement of the time step. 
-%Though the main parts of the algorithm are easily paralyzed, the single-processor times provide a simple assessment of the overall complexity.
-
-% Table
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{table}%[htbp]
-\begin{center}
-\caption{Convergence test: We run single-body erosion simulations to a stopping time of $t_s = 10^{-2}$ (56\% of the vanishing time) and measure the $L^2$-difference in shapes obtained with successive temporal resolutions.
-The tests confirm the method to be second-order accurate in time.
-The last column shows the measured CPU time which increases linearly as the time-step is refined.
-}
-\vspace{0.3 pc}
-\label{convtab}
-\begin{tabular}{l l l l}
-\hline
-\hspace{0.0pc} $\Delta t/t_s$
-\hspace{0.5pc} & error 
-\hspace{0.5pc} & order
-\hspace{0.5pc} & CPU time \\
-\hline
-%
-1/50		& 1.68E-5		& --		& 53 secs     	\\
-1/100	& 4.84E-6		& 1.79	& 1.8 mins   	\\
-1/200	& 1.30E-6		& 1.90	& 3.5 mins  	\\
-1/400	& 3.36E-7		& 1.95	& 6.9 mins  	\\
-1/800	& 8.54E-8		& 1.98	& 14 mins   	\\
-1/1600	& 2.15E-8		& 1.99	& 28 mins  	\\
-1/3200	& 5.40E-9		& 1.99	& 56 mins    	\\
-1/6400	& --			& --		& 111 mins	\\
-%
-\hline
-\end{tabular}
-\end{center}
-\end{table}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Parameters in this test are: 01circ256, nits = 7, dt0 = 1e-4, tfin = 1e-2
-% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0
-
-\section{Results: Multibody erosion}
-\label{s:MultiResults}
-
-\subsection{Fixed pressure-drop condition}
-
-With the numerical method validated, we are now ready to simulate the erosion of multiple bodies.
-We will first make one conceptual change to the model.
-For a realistic porous medium, the condition of a fixed incoming flow rate, $\umax$, is somewhat artificial.
-In groundwater flow, for example, it is more common to encounter an upstream (recharge) region of given hydraulic head that connects to a downstream (discharge) region of another head.
-Motivated by this example, we will impose the condition that the pressure drop across the computational domain remains fixed in time.
-Consequently, we would expect the flow rate, $\umax$, to increase over time as the bodies erode inside the cell and thus provide less resistance.
-
-We will impose the fixed-pressure-drop condition by dynamically controlling the incoming flow rate, $\umax$.
-We first compute the Stokes flow with $\umax = 1$ prescribed and measure the corresponding pressure at an upstream ($x = -2$) and downstream ($x=2$) location.
-We next calculate the vertically-averaged upstream and downstream pressures, defined as
-\begin{align}
-p_{-} = \frac{1}{2} \int_{-1}^{1} p(-2,y) \, dy \, , \qquad
-p_{+} = \frac{1}{2} \int_{-1}^{1} p(+2,y) \, dy \, .
-\end{align}
-We then rescale the computed density function, Stokeslets, and rotlets  by the pressure difference
-\begin{align}
-\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})}\, , \quad 
-\llambda \leftarrow \frac{\llambda}{(p_{-} - p_{+})}\, , \quad 
-\xi \leftarrow \frac{\xi}{(p_{-} - p_{+})}\, .
-\end{align}
-The velocity and pressure fields depend linearly on $\eeta$, $\llambda$, and $\xi$, so this rescaling maintains a {\em fixed} pressure difference across the subdomain $-2 \le x \le 2$.
-Since the Stokes equations are linear, the rescaled flow remains a solution to the PDE system (valid to the same order of accuracy).
-Furthermore, since the Stokes equations are time-independent, rescaling $U$ by a different value at each time step does not introduce any additional error.
-
-\subsection{Validation}
-
-To validate the multibody simulations with this new fixed-pressure-drop condition, we report a convergence test in Table~\ref{convtab2}.
-In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$.
-This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$.
-To assess error, we measure the aggregate $L^2$-difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution.
-Note that this metric is sensitive to numerical errors in any of the simulated bodies.
-The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multibody interactions are handled correctly by the Stokes solver.
-The last column of the table shows the computational time of each simulation, demonstrating a linear increase with refinement of the time step.
-Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{table}%[htbp]
-\begin{center}
-\caption{Convergence test for multiple-body erosion with a fixed-pressure-drop condition.
-In this test, we use 20 bodies with $N_{\iin} = 128$ grid points on each.
-We run the simulations to a stopping time of $t_s = 4 \times 10^{-3}$ (24\% of the time it takes for {\em all} bodies to vanish).
-We measure the {\em combined} $L^2$-difference in the shapes of {\em all} bodies.
-The table confirms that the method maintains second-order accuracy in time, even with multiple bodies and a time-varying inflow rate $\umax$.
-%We compare the shapes of {\em all} bodies from simulations of successive resolution using {\combined} $L^2$-norm
-}
-\vspace{0.3 pc}
-\label{convtab2}
-\begin{tabular}{l l l l}
-\hline
-\hspace{0.0pc} $\Delta t/t_s$
-\hspace{0.5pc} & error 
-\hspace{0.5pc} & order
-\hspace{0.5pc} & CPU time \\
-\hline
-%
-1/10     	& 2.67E-5  	& --        	& 14 mins  	\\
-1/20     	& 7.23E-6  	& 1.88 	& 27 mins  	\\
-1/40     	& 1.95E-6  	& 1.89 	& 52 mins  	\\
-1/80     	& 4.90E-7  	& 1.99 	& 1.7 hours	\\
-1/160     	& 1.25E-7  	& 1.97  	& 3.4 hours	\\
-%
-\hline
-\end{tabular}
-\end{center}
-\end{table}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Parameters in this test are: 20circ128, nits = 5, dt0 = 4e-4, tfin = 4e-3
-% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 1
-
-% Table: GMRES iterations
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{table}%[htbp]
-\begin{center}
-\caption{The number of GMRES iterations required to reach a fixed tolerance of $10^{-8}$ in our simulations.
-The left side shows a case of fixed geometry, 10 circular bodies, with increasing spatial resolution, $N_\iin$, demonstrating that the iteration count is independent of resolution.
-In the right side, we fix the resolution and sequentially increase the number of bodies (all circular) from 10 to 50.
-The iteration count increases roughly linearly with the number of bodies.
-}
-\vspace{0.3 pc}
-\label{itertab}
-\begin{tabular}{c c | c c}
-\hline
-\hspace{0.5pc} Resolution, $N_{\iin}$
-\hspace{0.5pc} & GMRES iterations 
-\hspace{0.5pc} &  Number of bodies
-\hspace{0.5pc} & GMRES iterations  \\
-\hspace{0.0pc} (10 bodies) &
-\hspace{0.5pc} & ($N_\iin = 128$ fixed) & \\
-\hline
-%
-32	& 228	& 10 	& 223	\\
-64    	& 226	& 15 	& 292	\\
-128	& 223	& 20 	& 363	\\
-256	& 223	& 30 	& 496	\\
-512	& 223	& 40 	& 676	\\
-1024	& 223	& 50 	& 991	\\
-%
-\hline
-\end{tabular}
-\end{center}
-\end{table}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-
-Lastly, we want to briefly examine the number of GMRES iterations required by our simulations since this is typically the most expensive step.
-Due to our {\em second-kind} boundary integral formulation, we expect the number of GMRES iterations to be independent of the spatial resolution, $N_{\iin}$.
-The iteration count, however, may depend on the number of bodies, as well as other factors such as the shapes of the bodies and their configuration.
-To examine a few of these factors, we show in Table~\ref{itertab} the number of GMRES iterations required to reach a specified tolerance of $10^{-8}$ in several different simulations.
-The left side of the table shows the results for a 10-body simulation, in which we keep the geometry fixed and vary the spatial resolution $N_{\iin}$.
-As seen in the table, the iteration count remains essentially fixed as the resolution increases.
-In the right side of the table, we keep the spatial resolution per body fixed and vary the number of simulated bodies from 10 to 50.
-The bodies are all circular with randomly assigned positions and radii (overlapping bodies are avoided).
-The table shows that the GMRES count increases roughly linearly with the number of bodies.
-%Thus, with everything else equal, the 50-body simulation from Fig.~\ref{fig:50bodies} is about 50 times more expensive than a single-body simulation.
-
-\subsection{Multibody results}
-
-With the validation complete, we now discuss the emergent physics of multibody erosion revealed by our simulations.
-We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}).
-Figure~\ref{fig:06bodies} shows the simulated erosion of 6 bodies, each initial circles of various sizes and positions.
-Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerably.
-As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable.
-Rather, when and where these corners form depends on how neighboring bodies interact with one another as mediated by the Stokes flow.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.80 \textwidth]{./figs/06bod.pdf}
-\caption{\label{fig:06bodies} The simulated erosion of 6 bodies with the fixed-pressure-drop condition.
-Erosion causes flat faces to develop wherever bodies were initially very close to one another.
-This effect leads to the appearance of straight channels between bodies, and causes the bodies themselves to appear distinctly polygonal.
-The vorticity field (color-bar at right) shows that the flow is concentrated primarily in a single channel that runs horizontally across the domain.
-}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure generated from data file 50circ512p5, 
-%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
-
-The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several points at which the bodies nearly contact one another, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
-Intriguingly, erosion appears to remove material preferentially from these sights, as the narrow spacing between neighboring bodies expands rather quickly.
-For example, the spacing between bodies 1 \& 2 is initially quite small, but by the second frame, is comparable to the spacing between bodies 3 \& 4.
-Moreover, the bodies tend to develop flat faces at the sites of near contact, leading to the appearance of straight channels between bodies.
-Straight channels can be seen, for example, between bodies 1 \& 2, 3 \& 5, and 5 \& 6.
-Once formed, these channels persist until the bodies have nearly vanished.
-Notice that by the final frame, body 4 has vanished completely, and the simulation handles this event without difficulty.
-
-In Fig.~\ref{fig:06bodies}, we also show the vorticity field of the surrounding flow.
-This field helps not only to visualize regions of high shear, but also to identify certain preferred channels in which the flow is most intense.
-As seen in the figure, the flow appears to be concentrated primarily within a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6.
-This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \& 2 or 3 \& 5 or 5 \& 6) follow.
-Notice that the overall vorticity magnitude increases in time as the flow rate $\umax$ increases due to keeping the pressure drop fixed.
-
-Looking back at the 50-body simulation in Fig.~\ref{fig:50bodies}, many of these same features can be observed.
-Bodies tend to develop corner-like features connected by flat faces, which causes them to appear polygonal.
-Nearly straight channels form between the bodies, and a few of these appear to be preferred channels which transmit the most flow and therefore widen the fastest.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.90 \textwidth]{./figs/mbodyplots.pdf}
-\caption{\label{fig:mbodyplots} 
-Multibody simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation.
-(a) The area fraction of the eroding bodies versus time.
-(b) The incoming flow rate $\umax$ versus time.
-The fixed-pressure-drop condition causes $\umax$ to increase as bodies erode.
-(c) The total drag exerted by all bodies.
-Because $\umax$ increases as the bodies erode, the drag remains nearly constant throughout much of the simulation.
-In the very last moments, the drag drops suddenly to zero.
-(d) Normalizing the drag by $\umax$ provides gives an estimate of how much resistance the porous matrix provides.
-The resistance decreases rapidly as the bodies erode.
-}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Figure generated from data file 50circ512p5, 
-%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
-
-To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations.
-In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation.
-First, Fig.~\ref{fig:mbodyplots}(a) shows the fraction of area occupied by the solid bodies as it varies in time.
-In the 6-body simulation, the initial configuration comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode.
-The 50-body simulation shows a similar trend.
-
-Next, Figure~\ref{fig:mbodyplots}(b) shows how the flow rate, $\umax$, changes in time as a result of fixing the pressure drop across the cell.
-Notice that, in this figure, the vertical axis is logarithmic.
-Both simulations show the flow rate to increase rapidly, even during the early stages of erosion when the area fraction has not changed that significantly.
-Due to the logarithmic axis, the nearly linear trend seen in the figure corresponds to exponential growth of $\umax$.
-The change in area fraction alone cannot account for this rapid growth, suggesting the reshaping process to be vital.
-In particular, the formation of channels observed in Fig.~\ref{fig:06bodies} may account for these higher flow rates.
-
-Naturally, the flow transmitted by the medium is linked to the amount of drag the bodies exert.
-We therefore show in Fig.~\ref{fig:mbodyplots}(c) the total drag exerted by all bodies as it varies in time.
-In both cases, the drag remains nearly constant throughout much of the simulation and then drops to zero in the final moments.
-Although all bodies are diminishing in size, the associated increase in $\umax$ leads to the nearly constant drag that is observed here.
-
-To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag normalized by $\umax$.
-Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \mu \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies.
-In this way, we can interpret $F_D / (4 \pi \mu \umax)$ as the {\em resistance} associated with the porous network.
-As seen in the figure, the medium's resistance decreases rapidly as its constituents erode.
-Since the vertical axis is logarithmic, the rate is roughly exponential at early times.
-As before, the reduction in area-fraction is not sufficient to explain this rapid decline, leaving the channelization process as the most likely mechanism.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions\label{s:conclusions}}
-
-We have combined two accurate and stable numerical methods to simulate two-dimensional viscous erosion in a porous medium.
-First, a BIE formulation of the incompressible Stokes equations discretizes only the boundaries and resolves non-negligible interactions between bodies.
-This Stokes solver enables computation of the surface shear stress, which dictates the erosion rate of solid material.
-To advance solid boundaries forward in time, we use the {\thL} framework, which prevents tangling and distortion of the mesh that would otherwise lead to numerical instability.
-The resulting method is accurate (spectral in space, second-order in time), numerically stable, and accelerated via the fast multipole method.
-
-Analytical results for the case of a single eroding body provide a stringent benchmark for our simulation.
-In particular, by appealing to the principle of long-time uniform stress, we predict a front/rear corner of angle $102^{\circ}$, which matches closely the value measured in the simulations.
-Scaling laws for the asymptotic rate of area and drag reduction also match the simulation.
-
-Simulations of multiple eroding bodies reveals even more complex behavior.
-As in the single body case, we witness the formation of sharp corners, but not in locations that are easily predictable.
-Furthermore, bodies tend to form flat faces in places where there was initially near contact, leading to the appearance of straight channels between bodies.
-The overall resistance of the porous network declines rapidly with erosion, which we attribute to the channelization process.
-
-In work currently underway, we are using this method to more thoroughly examine how bulk and statistical properties of the porous medium change with erosion.
-We are particularly interested in the development of anisotropic permeability of the medium.
-Preliminary simulations show promise.
-We furthermore would like to investigate how the statistical distribution of body size, shape, and alignment changes over time.
-We hope to report on these topics soon.
-
-As a longer term goal, we would like to include the effect of sedimentation to more faithfully capture the physics of a porous medium.
-Sedimentation requires overcoming a few challenges.
-First, the bodies must be mobile, as has been accomplished in previous work for dense concentrations of deformable and rigid bodies~\cite{qua-bir2014a, cor-gre-rac-vee2017, cor-vee2017, kli-tor2016b, rac-gre2016, qua-bir2016}.
-Second, contacts and overlap between bodies must be prevented.
-This second requirement has been recognized as quite a challenge, with many novel methods developed to treat it~\cite{lu-rah-zor2017, kab-qua-bir2018, san-mo1994}.
-Incorporation of one or more of these schemes, will enable simulations of a porous medium undergoing simultaneous erosion and sedimentation.
 
@@
 \biboptions{sort&compress}
-
-\begin{thebibliography}{72}
-\providecommand{\natexlab}[1]{#1}
-\providecommand{\url}[1]{\texttt{#1}}
-\expandafter\ifx\csname urlstyle\endcsname\relax
-  \providecommand{\doi}[1]{doi: #1}\else
-  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi
-
-\bibitem[Abrams et~al.(2009)Abrams, Lobkovsky, Petroff, Straub, McElroy,
-  Mohrig, Kudrolli, and Rothman]{abrams2009growth}
-Daniel~M Abrams, Alexander~E Lobkovsky, Alexander~P Petroff, Kyle~M Straub,
-  Brandon McElroy, David~C Mohrig, Arshad Kudrolli, and Daniel~H Rothman.
-\newblock Growth laws for channel networks incised by groundwater flow.
-\newblock \emph{Nature Geoscience}, 2\penalty0 (3):\penalty0 193, 2009.
-
-\bibitem[af~Klinteberg and Tornberg(2016)]{kli-tor2016b}
-Ludvig af~Klinteberg and Anna-Karin Tornberg.
-\newblock A fast integral equation method for solid particles in viscous flow
-  using quadrature by expansion.
-\newblock \emph{Journal of Computational Physics}, 326:\penalty0 420--445,
-  2016.
-
-\bibitem[Barnett et~al.(2015)Barnett, Wu, and Veerapaneni]{bar-wu-vee2015}
-Alex Barnett, Bowei Wu, and Shravan Veerapaneni.
-\newblock {Spectrally-Accurate Quadratures for Evaluation of Layer Potentials
-  Close to the Boundary for the 2D Stokes and Laplace Equations}.
-\newblock \emph{SIAM Journal on Scientific Computing}, 37\penalty0
-  (4):\penalty0 B519--B542, 2015.
-
-\bibitem[Barnett et~al.(2018)Barnett, Marple, Veerapaneni, and
-  Zhao]{bar-mar-vee-zha2018}
-Alex Barnett, Gary Marple, Shravan Veerapaneni, and Lin Zhao.
-\newblock {A unified integral equation scheme for doubly-periodic Laplace and
-  Stokes boundary value problems in two dimensions}.
-\newblock \emph{Communications on Pure and Applied Mathematic}, 2018.
-\newblock In press.
-
-\bibitem[Barnett(2014)]{bar2014}
-Alex~H. Barnett.
-\newblock {Evaluation of layer potentials close to the boundary for Laplace and
-  Helmholtz problems on analytic planar domains}.
-\newblock \emph{SIAM Journal on Scientific Computing}, 36\penalty0
-  (2):\penalty0 A427--A451, 2014.
-
-\bibitem[Batchelor(1970)]{batchelor1970slender}
-GK~Batchelor.
-\newblock {Slender-body theory for particles of arbitrary cross-section in
-  Stokes flow}.
-\newblock \emph{Journal of Fluid Mechanics}, 44\penalty0 (3):\penalty0
-  419--440, 1970.
-
-\bibitem[Beale and Lai(2001)]{bea-lai2001}
-J.T. Beale and M.-C. Lai.
-\newblock {A Method for Computing Nearly Singular Integrals}.
-\newblock \emph{SIAM Journal on Numerical Analysis}, 38\penalty0 (6):\penalty0
-  1902--1925, 2001.
-
-\bibitem[Bear(2013)]{bear2013dynamics}
-Jacob Bear.
-\newblock \emph{Dynamics of fluids in porous media}.
-\newblock Courier Corporation, 2013.
-
-\bibitem[Berhanu et~al.(2012)Berhanu, Petroff, Devauchelle, Kudrolli, and
-  Rothman]{berhanu2012shape}
-Michael Berhanu, Alexander Petroff, Olivier Devauchelle, Arshad Kudrolli, and
-  Daniel~H Rothman.
-\newblock Shape and dynamics of seepage erosion in a horizontal granular bed.
-\newblock \emph{Physical Review E}, 86\penalty0 (4):\penalty0 041304, 2012.
-
-\bibitem[Bremer(2012)]{bre2012}
-James Bremer.
-\newblock {On the Nystr\"om discretization of integral equations on planar
-  curves with corners}.
-\newblock \emph{Applied and Computational Harmonic Analysis}, 32:\penalty0
-  45--64, 2012.
-
-\bibitem[Camassa et~al.(2012)Camassa, McLaughlin, Moore, and Yu]{MooreJFM2012}
-R.~Camassa, R.M. McLaughlin, M.N.J. Moore, and K.~Yu.
-\newblock Stratified flows with vertical layering of density: experimental and
-  theoretical study of flow configurations and their stability.
-\newblock \emph{Journal of Fluid Mechanics}, 690:\penalty0 571--606, 2012.
-
-\bibitem[Campbell et~al.(1996)Campbell, Ipsen, Kelley, Meyer, and
-  Xue]{cam-ips-kel-mey-xue1996}
-S.~L. Campbell, I.~C.~F. Ipsen, C.~T. Kelley, C.~D. Meyer, and Z.~Q. Xue.
-\newblock {Convergence estimates for solution of integral equations with
-  GMRES}.
-\newblock \emph{Journal of Integral Equations and Applications}, 8\penalty0
-  (1):\penalty0 19--34, 1996.
-
-\bibitem[Cao et~al.(2010)Cao, Gunzburger, Hua, Wang, et~al.]{cao2010coupled}
-Yanzhao Cao, Max Gunzburger, Fei Hua, Xiaoming Wang, et~al.
-\newblock Coupled Stokes-Darcy model with Beavers-Joseph interface boundary
-  condition.
-\newblock \emph{Communications in Mathematical Sciences}, 8\penalty0
-  (1):\penalty0 1--25, 2010.
-
-\bibitem[Claudin et~al.(2017)Claudin, Dur{\'a}n, and
-  Andreotti]{claudin2017dissolution}
-Philippe Claudin, Orencio Dur{\'a}n, and Bruno Andreotti.
-\newblock Dissolution instability and roughening transition.
-\newblock \emph{Journal of Fluid Mechanics}, 832, 2017.
-
-\bibitem[Cohen et~al.(2016)Cohen, Berhanu, Derr, and du~Pont]{cohen2016erosion}
-Caroline Cohen, Michael Berhanu, Julien Derr, and Sylvain~Courrech du~Pont.
-\newblock Erosion patterns on dissolving and melting bodies.
-\newblock \emph{Physical Review Fluids}, 1\penalty0 (5):\penalty0 050508, 2016.
-
-\bibitem[Cohen et~al.(2015)Cohen, Devauchelle, Seybold, Yi, Szymczak, and
-  Rothman]{coh-dev-sey-yi-szy-rot2015}
-Yossi Cohen, Olivier Devauchelle, Hansj{\"o}rg~F. Seybold, Robert~S. Yi, Piotr
-  Szymczak, and Daniel~H. Rothman.
-\newblock Path selection in the growth of rivers.
-\newblock \emph{Proceedings of the National Academy of Sciences}, 112\penalty0
-  (46):\penalty0 14132--14137, 2015.
-
-\bibitem[Corona and Veerapaneni(2017)]{cor-vee2017}
-Eduardo Corona and Shravan Veerapaneni.
-\newblock {Boundary integral equation analysis for suspension of spheres in
-  Stokes flow}.
-\newblock \emph{arxiv}, 1707.06551, 2017.
-
-\bibitem[Corona et~al.(2017)Corona, Greengard, Rachh, and
-  Veerapaneni]{cor-gre-rac-vee2017}
-Eduardo Corona, Leslie Greengard, Manas Rachh, and Shravan Veerapaneni.
-\newblock {An integral equation formulation for rigid bodies in Stokes flow in
-  three dimensions}.
-\newblock \emph{Journal of Computational Physics}, 332:\penalty0 504--519,
-  2017.
-
-\bibitem[Coulier et~al.(2017)Coulier, Pouransari, and Darve]{cou-pou-dar2017}
-Pieter Coulier, Hadi Pouransari, and Eric Darve.
-\newblock {The Inverse Fast Multipole Method: Using a Fast Approximate Diret
-  Solver as a Preconditioner for Dense Linear Systems}.
-\newblock \emph{SIAM Journal on Scientific Computing}, 39\penalty0
-  (3):\penalty0 A761--A796, 2017.
-
-\bibitem[Daerr et~al.(2003)Daerr, Lee, Lanuza, and
-  Cl{\'e}ment]{daerr2003erosion}
-Adrian Daerr, Peter Lee, Jos{\'e} Lanuza, and {\'E}ric Cl{\'e}ment.
-\newblock Erosion patterns in a sediment layer.
-\newblock \emph{Physical Review E}, 67\penalty0 (6):\penalty0 065201, 2003.
-
-\bibitem[Dallaston et~al.(2015)Dallaston, Hewitt, and
-  Wells]{dallaston2015channelization}
-MC~Dallaston, IJ~Hewitt, and AJ~Wells.
-\newblock Channelization of plumes beneath ice shelves.
-\newblock \emph{Journal of Fluid Mechanics}, 785:\penalty0 109--134, 2015.
-
-\bibitem[de~Anna et~al.(2018)de~Anna, Quaife, Biros, and
-  Juanes]{dea-qua-bir-jua2018}
-Pietro de~Anna, Bryan Quaife, George Biros, and Ruben Juanes.
-\newblock {Prediction of velocity distribution from pore structure in simple
-  porous media}.
-\newblock \emph{Physical Review Fluids}, 2\penalty0 (12):\penalty0 124103,
-  2018.
-
-\bibitem[Devauchelle et~al.(2012)Devauchelle, Petroff, Seybold, and
-  Rothman]{Rothman2012}
-O.~Devauchelle, A.P. Petroff, H.F. Seybold, and D.H. Rothman.
-\newblock Ramification of stream networks.
-\newblock \emph{Proceedings of the National Academy of Sciences}, 109\penalty0
-  (51):\penalty0 20832--20836, 2012.
-
-\bibitem[Domokos et~al.(2014)Domokos, Jerolmack, Sipos, and
-  T{\"o}r{\"o}k]{domokos2014river}
-Gabor Domokos, Douglas~J Jerolmack, Andras~{\'A} Sipos, and {\'A}kos
-  T{\"o}r{\"o}k.
-\newblock How river rocks round: resolving the shape-size paradox.
-\newblock \emph{PloS One}, 9\penalty0 (2):\penalty0 e88657, 2014.
-
-\bibitem[Gillman et~al.(2014)Gillman, Hao, and Martinsson]{gil-hao-mar2014}
-A.~Gillman, S.~Hao, and P.G. Martinsson.
-\newblock {A simplified technique for the efficient and highly accurate
-  discretization of boundary integral equations in 2D on domains with corners}.
-\newblock \emph{Journal of Computational Physics}, 256:\penalty0 214--219,
-  2014.
-
-\bibitem[Greenbaum et~al.(1992)Greenbaum, Greengard, and Mayo]{gre-gre-may1992}
-Anne Greenbaum, Leslie Greengard, and Anita Mayo.
-\newblock On the numerical solution of the biharmonic equation in the plane.
-\newblock \emph{Physica D: Nonlinear Phenomena}, 60:\penalty0 216--225, 1992.
-
-\bibitem[Greengard and Rokhlin(1987)]{gre-rok1987}
-L.~Greengard and V.~Rokhlin.
-\newblock {A Fast Algorithm for Particle Simulations}.
-\newblock \emph{Journal of Computational Physics}, 73:\penalty0 325--348, 1987.
-
-\bibitem[Greengard et~al.(1996)Greengard, Kropinski, and Mayo]{gre-kro-may1996}
-L.~Greengard, M.C. Kropinski, and A.~Mayo.
-\newblock {Integral Equation Methods for Stokes Flow and Isotropic Elasticity
-  in the Plane}.
-\newblock \emph{Journal of Computational Physics}, 125\penalty0 (2):\penalty0
-  403--414, 1996.
-
-\bibitem[Groen et~al.(2007)Groen, Gijsen, van~der Lugt, Ferguson, Hatsukami,
-  van~der Steen, Yuan, and Wentzel]{gro-gij-van-fer-hat-van-yua-wen2007}
-Harald~C. Groen, Frank~J.H. Gijsen, Aad van~der Lugt, Marina~S. Ferguson,
-  Thomas~S. Hatsukami, Anton~F.W. van~der Steen, Chun Yuan, and Jolanda~J.
-  Wentzel.
-\newblock {Plaque Rupture in the Carotid Artery Is Localized at the High Shear
-  Stress Region: A Case Report}.
-\newblock \emph{Stroke}, 38:\penalty0 2379--2381, 2007.
-
-\bibitem[Hanna(1969)]{han1969}
-Steven~R. Hanna.
-\newblock {The Formation of Longitudinal Sand Dunes by Large Helical Eddies in
-  the Atmosphere}.
-\newblock \emph{Journal of Applied Meteorology}, 8\penalty0 (6):\penalty0
-  874--883, 1969.
-
-\bibitem[Helsing(2011)]{hel2011}
-J.~Helsing.
-\newblock {A Fast and Stable Solver for Singular Integral Equations and
-  Piecewise Smooth Curves}.
-\newblock \emph{SIAM Journal on Scientific Comuting}, 33:\penalty0 153--174,
-  2011.
-
-\bibitem[Helsing and Ojala(2008)]{hel-oja2008a}
-Johan Helsing and Rikard Ojala.
-\newblock On the evaluation of layer potentials close to their sources.
-\newblock \emph{Journal of Computational Physics}, 227:\penalty0 2899--2921,
-  2008.
-
-\bibitem[Hewett and Sellier(2017{\natexlab{a}})]{hewett2017evolution}
-James~N Hewett and Mathieu Sellier.
-\newblock Evolution of an eroding cylinder in single and lattice arrangements.
-\newblock \emph{Journal of Fluids and Structures}, 70:\penalty0 295--313,
-  2017{\natexlab{a}}.
-
-\bibitem[Hewett and Sellier(2017{\natexlab{b}})]{hewett2017pear}
-James~N Hewett and Mathieu Sellier.
-\newblock The pear-shaped fate of an ice melting front.
-\newblock \emph{arXiv preprint arXiv:1705.02536}, 2017{\natexlab{b}}.
-
-\bibitem[Hou et~al.(1994)Hou, Lowengrub, and Shelley]{hou-low-she1994}
-Thomas~Y. Hou, John~S. Lowengrub, and Michael~J. Shelley.
-\newblock {Removing the Stiffness for Interfacial Flows with Surface Tension}.
-\newblock \emph{Journal of Computational Physics}, 114:\penalty0 312--338,
-  1994.
-
-\bibitem[Huang et~al.(2015)Huang, Moore, and Ristroph]{Huang2015}
-J.M. Huang, M.N.J. Moore, and L.~Ristroph.
-\newblock Shape dynamics and scaling laws for a body dissolving in fluid flow.
-\newblock \emph{Journal of Fluid Mechanics}, 765, 2 2015.
-\newblock ISSN 1469-7645.
-
-\bibitem[Jerolmack et~al.(2012)Jerolmack, Ewing, Falcini, Martin, Masteller,
-  Phillips, Reitz, and Buynevich]{jerolmack2012internal}
-Douglas~J Jerolmack, Ryan~C Ewing, Federico Falcini, Raleigh~L Martin, Claire
-  Masteller, Colin Phillips, Meredith~D Reitz, and Ilya Buynevich.
-\newblock Internal boundary layer model for the evolution of desert dune
-  fields.
-\newblock \emph{Nature Geoscience}, 5\penalty0 (3):\penalty0 206, 2012.
-
-\bibitem[Kabacao\u{g}lu et~al.(2018)Kabacao\u{g}lu, Quaife, and
-  Biros]{kab-qua-bir2018}
-Gokberk Kabacao\u{g}lu, Bryan Quaife, and George Biros.
-\newblock {Low-resolution simulations of vesicle suspensions in 2D}.
-\newblock \emph{Journal of Computational Physics}, 357:\penalty0 43--77, 2018.
-
-\bibitem[Kl\"{o}ckner et~al.(2013)Kl\"{o}ckner, Barnett, Greengard, and
-  O'Neil]{klo-bar-gre-one2013}
-Andreas Kl\"{o}ckner, Alexander Barnett, Leslie Greengard, and Michael O'Neil.
-\newblock {Quadrature by expansion: A new method for the evaluation of layer
-  potentials}.
-\newblock \emph{Journal of Computational Physics}, 252:\penalty0 332--349,
-  2013.
-
-\bibitem[Kondratiuk and Szymczak(2015)]{kondratiuk2015steadily}
-Pawe{\l} Kondratiuk and Piotr Szymczak.
-\newblock {Steadily Translating Parabolic Dissolution Fingers}.
-\newblock \emph{SIAM Journal on Applied Mathematics}, 75\penalty0 (5):\penalty0
-  2193--2213, 2015.
-
-\bibitem[Ladyzhenskaya(1963)]{lad1963}
-O.~A. Ladyzhenskaya.
-\newblock \emph{{The Mathematical Theory of Viscous Incompressible Flow}}.
-\newblock Gordon and Breach Science, 1963.
-
-\bibitem[L{\'o}pez et~al.(2018)L{\'o}pez, Stickland, and
-  Dempster]{lopez2018cfd}
-Alejandro L{\'o}pez, Matthew~T Stickland, and William~M Dempster.
-\newblock Cfd study of fluid flow changes with erosion.
-\newblock \emph{Computer Physics Communications}, 2018.
-
-\bibitem[Lu et~al.(2017)Lu, Rahimian, and Zorin]{lu-rah-zor2017}
-Libin Lu, Abtin Rahimian, and Denis Zorin.
-\newblock {Contact-aware simulations of particulate Stokesian suspensions}.
-\newblock \emph{Journal of Computational Physics}, 347:\penalty0 160--182,
-  2017.
-
-\bibitem[Mitchell and Spagnolie(2016)]{mit-spa2016}
-W.H. Mitchell and S.E. Spagnolie.
-\newblock A generalized traction integral equation for {S}tokes flow, with
-  applications to near-wall particle mobility and viscous erosion.
-\newblock \emph{Journal of Computational Physics}, 2016.
-
-\bibitem[Moore(2017)]{moore2017riemann}
-M.N.J. Moore.
-\newblock {Riemann-Hilbert Problems for the Shapes Formed by Bodies Dissolving,
-  Melting, and Eroding in Fluid Flows}.
-\newblock \emph{Communications on Pure and Applied Mathematics}, 70\penalty0
-  (9):\penalty0 1810--1831, 2017.
-
-\bibitem[Moore et~al.(2013)Moore, Ristroph, Childress, Zhang, and
-  Shelley]{moo-ris-chi-zha-she2013}
-Matthew N.J. Moore, Leif Ristroph, Stephen Childress, Jun Zhang, and
-  Michael~J. Shelley.
-\newblock Self-similar evolution of a body eroding in a fluid flow.
-\newblock \emph{Physics of Fluids}, 25:\penalty0 116602, 2013.
-
-\bibitem[Nienhuis et~al.(2014)Nienhuis, Perron, Kao, and
-  Myrow]{nienhuis2014wavelength}
-Jaap~H Nienhuis, J~Taylor Perron, Justin~CT Kao, and Paul~M Myrow.
-\newblock Wavelength selection and symmetry breaking in orbital wave ripples.
-\newblock \emph{Journal of Geophysical Research: Earth Surface}, 119\penalty0
-  (10):\penalty0 2239--2257, 2014.
-
-\bibitem[O.Pironneau(1973)]{pir1973}
-O.Pironneau.
-\newblock {On optimum profiles in Stokes flow}.
-\newblock \emph{Journal of Fluid Mehanics}, 59\penalty0 (1):\penalty0 117--128,
-  1973.
-
-\bibitem[Perkins et~al.(2015)Perkins, Finnegan, and
-  De~Silva]{perkins2015amplification}
-Jonathan~P Perkins, Noah~J Finnegan, and Shanaka~L De~Silva.
-\newblock Amplification of bedrock canyon incision by wind.
-\newblock \emph{Nature Geoscience}, 8\penalty0 (4):\penalty0 305, 2015.
-
-\bibitem[Perron et~al.(2009)Perron, Kirchner, and
-  Dietrich]{perron2009formation}
-J~Taylor Perron, James~W Kirchner, and William~E Dietrich.
-\newblock Formation of evenly spaced ridges and valleys.
-\newblock \emph{Nature}, 460\penalty0 (7254):\penalty0 502, 2009.
-
-\bibitem[Petroff et~al.(2011)Petroff, Devauchelle, Abrams, Lobkovsky, Kudrolli,
-  and Rothman]{petroff2011geometry}
-Alexander~P Petroff, Olivier Devauchelle, Daniel~M Abrams, Alexander~E
-  Lobkovsky, Arshad Kudrolli, and Daniel~H Rothman.
-\newblock Geometry of valley growth.
-\newblock \emph{Journal of Fluid Mechanics}, 673:\penalty0 245--254, 2011.
-
-\bibitem[Picioreanu et~al.(2001)Picioreanu, van Loosdrecht, and
-  Heijnen]{pic-van-hei2000}
-Cristian Picioreanu, Mark C.~M. van Loosdrecht, and Joseph~J. Heijnen.
-\newblock {Two-Dimensional Model of Biofilm Detachment Caused by Internal
-  Stress from Liquid Flow}.
-\newblock \emph{Biotechnology and Bioengineering}, 72\penalty0 (2):\penalty0
-  205--218, 2001.
-
-\bibitem[Power(1993)]{pow1993}
-H.~Power.
-\newblock {The completed double layer boundary integral equation method for
-  two-dimensional Stokes flow}.
-\newblock \emph{IMA Journal of Applied Mathematics}, 51\penalty0 (2):\penalty0
-  123--145, 1993.
-
-\bibitem[Power and Miranda(1987)]{pow-mir1987}
-H.~Power and G.~Miranda.
-\newblock Second kind integral equation formulation of Stokes' flows past a
-  particle of arbitrary shape.
-\newblock \emph{SIAM Journal on Applied Mathematics}, 47\penalty0 (4):\penalty0
-  689--698, 1987.
-
-\bibitem[Pozrikidis(1992)]{poz1992}
-C.~Pozrikidis.
-\newblock \emph{{Boundary Integral and Singularity Methods for Linearized
-  Viscous Flow}}.
-\newblock Cambridge University Press, New York, NY, USA, 1992.
-
-\bibitem[Pozrikidis(1997)]{poz1997}
-C.~Pozrikidis.
-\newblock \emph{Introduction to Theoretical and Computational Fluid Dynamics}.
-\newblock Oxford University Press, New York, 1997.
-
-\bibitem[Quaife and Biros(2014)]{qua-bir2014a}
-Bryan Quaife and George Biros.
-\newblock High-volume fraction simulations of two-dimensional vesicle
-  suspensions.
-\newblock \emph{Journal of Computational Physics}, 274:\penalty0 245--267,
-  2014.
-
-\bibitem[Quaife and Biros(2015)]{qua-bir2015a}
-Bryan Quaife and George Biros.
-\newblock {On preconditioners for the Laplace double-layer potential in 2D}.
-\newblock \emph{Numerical Linear Algebra with Applications}, 22:\penalty0
-  101--122, 2015.
-
-\bibitem[Quaife and Biros(2016)]{qua-bir2016}
-Bryan Quaife and George Biros.
-\newblock {Adaptive time stepping for vesicle simulations}.
-\newblock \emph{Journal of Computational Physics}, 306:\penalty0 478--499,
-  2016.
-
-\bibitem[Quaife et~al.(2018)Quaife, Coulier, and Darve]{qua-cou-dar2018}
-Bryan Quaife, Pieter Coulier, and Eric Darve.
-\newblock {An efficient preconditioner for the fast simulation of a 2D Stokes
-  flow in porous media}.
-\newblock \emph{International Journal for Numerical Methods in Engineering},
-  113:\penalty0 561--580, 2018.
-
-\bibitem[Rachh and Serkh(2017)]{rac-ser2017}
-M.~Rachh and K.~Serkh.
-\newblock {On the solution of Stokes equation on regions with corners}.
-\newblock \emph{arxiv}, 1711.04072, 2017.
-
-\bibitem[Rachh and Greengard(2016)]{rac-gre2016}
-Manas Rachh and L.~Greengard.
-\newblock Integral equation methods for elastance and mobility problems in two
-  dimensions.
-\newblock \emph{SIAM Journal on Numerical Analysis}, 54\penalty0 (5):\penalty0
-  2889--2909, 2016.
-
-\bibitem[Ristroph(2018)]{ristroph2018sculpting}
-Leif Ristroph.
-\newblock Sculpting with flow.
-\newblock \emph{Journal of Fluid Mechanics}, 838:\penalty0 1--4, 2018.
-
-\bibitem[Ristroph et~al.(2012)Ristroph, Moore, Childress, Shelley, and
-  Zhang]{ris-moo-chi-she-zha2012}
-Leif Ristroph, Matthew N.~J. Moore, Stephen Childress, Michael~J. Shelley, and
-  Jun Zhang.
-\newblock Sculpting of an erodible body in flowing water.
-\newblock \emph{Proceedings of the National Academy of Sciences}, 109\penalty0
-  (48):\penalty0 19606--19609, 2012.
-
-\bibitem[Rycroft and Bazant(2016)]{rycroft2016asymmetric}
-Chris~H. Rycroft and Martin~Z. Bazant.
-\newblock Asymmetric collapse by dissolution or melting in a uniform flow.
-\newblock In \emph{Proc. R. Soc. A}, volume 472, page 20150531. The Royal
-  Society, 2016.
-
-\bibitem[Saad and Schultz(1986)]{saa-sch1986}
-Y.~Saad and M.H. Schultz.
-\newblock {GMRES: A Generalized Minimal Residual Algorithm for Solving
-  Nonsymmetric Linear Systems}.
-\newblock \emph{SIAM Journal on Scientific and Statistical Computing},
-  7:\penalty0 856--869, 1986.
-
-\bibitem[Sangani and Mo(1994)]{san-mo1994}
-Ashok~S. Sangani and Guobiao Mo.
-\newblock Inclusion of lubrication forces in dynamic simulations.
-\newblock \emph{Physics of fluids}, 6\penalty0 (5):\penalty0 1653--1662, 1994.
-
-\bibitem[Serkh and Rokhlin(2016)]{ser-rok2016}
-K.~Serkh and V.~Rokhlin.
-\newblock On the solution of elliptic partial differential equations on regions
-  with corners.
-\newblock \emph{Journal of Computational Physics}, 305:\penalty0 150--171,
-  2016.
-
-\bibitem[Shah(2002)]{sha2002}
-Prediman~K. Shah.
-\newblock {Pathophysiology of coronary thrombosis: role of plaque rupture and
-  plaque erosion}.
-\newblock \emph{Progress in Cardiovascular Diseases}, 44\penalty0 (5):\penalty0
-  357--368, 2002.
-
-\bibitem[Sidi and Israeli(1988)]{sid-isr1988}
-Avram Sidi and Moshe Israeli.
-\newblock Quadrature {M}ethods for {P}eriodic {S}ingular and {W}eakly
-  {S}ingular {F}redholm {I}ntegral {E}quations.
-\newblock \emph{Journal of Scientific Computing}, 3\penalty0 (2):\penalty0
-  201--231, 1988.
-
-\bibitem[Trefethen and Weideman(2014)]{tre-wei2014}
-Lloyd~N. Trefethen and J.~A.~C. Weideman.
-\newblock {The Exponentially Convergent Trapezoidal Rule}.
-\newblock \emph{SIAM Review}, 56\penalty0 (3):\penalty0 385--458, 2014.
-
-\bibitem[Ying et~al.(2004)Ying, Biros, and Zorin]{yin-bir-zor2004}
-L.~Ying, G.~Biros, and D.~Zorin.
-\newblock {A kernel-independent adaptive fast multipole algorithm in two and
-  three dimensions}.
-\newblock \emph{Journal of Computational Physics}, 194\penalty0 (2):\penalty0
-  591--626, 2004.
-
-\end{thebibliography}
-
-%\bibliography{refs}
+\bibliography{refs}
 

### 2019-01-25 fortran_code/stokesDriver.f

@@ -125,10 +125,14 @@ c        endif
 c        enddo
 c      enddo            
 c      
-      xmin = -0.111
-      xmax = 0.71
-      ymin = -0.31
-      ymax = 0.51
+c      xmin = -0.111
+c      xmax = 0.71
+c      ymin = -0.31
+c      ymax = 0.51
+      xmin = -1.d0
+      xmax = 2.d0
+      ymin = -0.99d0
+      ymax = 0.99d0
       nx = ntargets
       ny = ntargets
       dx = (xmax - xmin)/dble(nx-1)

### 2019-03-22 docs/transport/erosion_transport.tex
start to type formula in erosion_transport paper

@@
 \newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}} \newcommand{\secref}[1]{\ref{#1}}
+\newcommand{\Cdb}{\mbox{$\mathbb{C}$}}
+\newcommand{\Rdb}{\mbox{$\mathbb{R}$}}
+
+\newcommand{\D}{\mbox{${\mathcal D}$}}
+
+\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
 
@@
 \label{sec:bies}
+Add an introduction why we do not use the double-layer potentials of Stokes equations but the double-layer potentials of Laplace equations to solve Stokes equation when we use Barycentric approach (or complex variable approach).
+\subsubsection{Laplace's equations from $\Rdb^2$ to $\Cdb$ }
+
+Let $\Omega$ be the domain of fluid. The boundary of $\Omega$ is $\Gamma$ and the outward normal vector on $\Gamma$ is ${\bf n_y}=(n_1,n_2)$.
+
+Consider a Laplace's equations with Dirichlet boundary condition
+\begin{equation}\label{Laplace}
+  \begin{cases}
+    \Delta {\bf u}=0, & \text{in}\,\,\, \Omega \in \Rdb^2;\\
+    {\bf u}={\bf f}, & \text{on}\,\,\, \Gamma.
+  \end{cases}
+\end{equation}
+
+Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
+The double-layer potential which solves \eqref{Laplace} is 
+\begin{align*}
+\D[\sigma]({\bf x})&=\frac{1}{2\pi}\displaystyle\int_{\Gamma} \frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma({\bf y})dS_y,
+%\frac{1}{2\pi}\displaystyle\int_{\Gamma}\frac{\partial}{\partial {\bf n_y}} \log |{\bf x}-{\bf y}| \sigma({\bf y})dS_y,\\ \\
+%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{{\bf r}\cdot{\bf n_y}}{\rho^2} \sigma({\bf y})dS_y\\ \\
+%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{n_1(x_1-y_1)+n_2(x_2-y_2)}{(x_1-y_1)^2+(x_2-y_2)^2} \sigma({\bf y})dS_y 
+\numberthis\label{DLP:real}
+\end{align*}
+where $\sigma$ is the density function on the boundary $\Gamma$.
+
+Consider a Cauchy integral 
+\begin{equation}\label{CI}
+v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{\sigma({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+\end{equation}
+where ${ x}=x_1+ix_2$, $ { y}=y_1+iy_2$, ${ n_y}=n_1+i n_2$ and $d{ y}=i {n_y}dS_y$. It is easy to show that 
+the real part of the Cauchy integral in \eqref{CI} is equivalent to the double-layer potential in \eqref{DLP:real}.
+
+\subsubsection{From Stokes DLP to Laplace DLPs}
+
+Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
+
+The Stokes double-layer potential  is
+\begin{equation}\label{StokesDLP1}
+\D[\boldsymbol\sigma]({\bf x}):=\frac{1}{\pi}\int_{\Gamma}\left(\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\frac{{\bf r} \otimes {\bf r}}{\rho^2}\right) {\boldsymbol\sigma({\bf y})} d S_y.
+\end{equation}
+We could rewrite the Stokes DLP in terms of the Laplace DLP as
+\begin{align*}\label{StokesDLP2}
+\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})dS_y+\frac{1}{2\pi}\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})dS_y\\
+&-\frac{1}{2\pi}x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1dS_y-\frac{1}{2\pi}x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2dS_y. \numberthis
+\end{align*}
 
@@
 \label{sec:shearStressLP}
+
+To calculate the shear stress, we need to know the gradient of double-layer potential in \eqref{StokesDLP2} 
+\begin{align*}\label{SSLP}
+\nabla\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\nabla\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})dS_y+\frac{1}{2\pi}\nabla^2\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})dS_y\\
+&-\frac{1}{2\pi}\nabla\left(x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1dS_y\right)-\frac{1}{2\pi}\nabla\left(x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2dS_y\right).
+\numberthis
+\end{align*}
 
@@
 \label{sec:BIE}
+\subsubsection{Interior Case}
+Consider a Cauchy integral 
+\begin{equation}\label{NCI}
+v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+\end{equation}
+By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{{ y}-{ x}} d{ y}=1,$ we can rewrtie \eqref{NCI} and get 
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)}{{ y}-{ x}} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+\end{equation}
+\begin{equation}\label{dNCI}
+v'({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{(y- x)^2} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+\end{equation}
+By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{dNCI} and get 
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)-(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+\end{equation}
+
+\subsubsection{Exterior case}
 
@@
 \label{sec:shearStress}
+\subsubsection{Interior Case}
+\begin{equation}\label{ddNCI}
+v''({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})}{(y- x)^3} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+\end{equation}
+By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{ddNCI} and get 
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+\end{equation}
+\subsubsection{Exterior case}
 

### 2019-03-25 docs/transport/erosion_transport.tex
type the numerical method of exterior part

--- 2019-01-25 docs/transport/erosion_transport.tex
@@
 \label{sec:bies}
+Add an introduction why we do not use the double-layer potentials of Stokes equations but the double-layer potentials of Laplace equations to solve Stokes equation when we use Barycentric approach (or complex variable approach).
+\subsubsection{Laplace's equations from $\Rdb^2$ to $\Cdb$ }
+
+Let $\Omega$ be the domain of fluid. The boundary of $\Omega$ is $\Gamma$ and the outward normal vector on $\Gamma$ is ${\bf n_y}=(n_1,n_2)$.
+
+Consider a Laplace's equations with Dirichlet boundary condition
+\begin{equation}\label{Laplace}
+  \begin{cases}
+    \Delta {\bf u}=0, & \text{in}\,\,\, \Omega \in \Rdb^2;\\
+    {\bf u}={\bf f}, & \text{on}\,\,\, \Gamma.
+  \end{cases}
+\end{equation}
+
+Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
+The double-layer potential which solves \eqref{Laplace} is 
+\begin{align*}
+\D[\sigma]({\bf x})&=\frac{1}{2\pi}\displaystyle\int_{\Gamma} \frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma({\bf y})ds_y,
+%\frac{1}{2\pi}\displaystyle\int_{\Gamma}\frac{\partial}{\partial {\bf n_y}} \log |{\bf x}-{\bf y}| \sigma({\bf y})ds_y,\\ \\
+%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{{\bf r}\cdot{\bf n_y}}{\rho^2} \sigma({\bf y})ds_y\\ \\
+%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{n_1(x_1-y_1)+n_2(x_2-y_2)}{(x_1-y_1)^2+(x_2-y_2)^2} \sigma({\bf y})ds_y 
+\numberthis\label{DLP:real}
+\end{align*}
+where $\sigma$ is the density function on the boundary $\Gamma$.
+
+Consider a Cauchy integral 
+\begin{equation}\label{CI}
+v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{\sigma({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+\end{equation}
+where ${ x}=x_1+ix_2$, $ { y}=y_1+iy_2$, ${ n_y}=n_1+i n_2$ and $d{ y}=i {n_y}ds_y$. It can be showed that 
+the real part of the Cauchy integral in \eqref{CI} is equivalent to the double-layer potential in \eqref{DLP:real}.
+
+\subsubsection{From Stokes DLP to Laplace DLPs}
+
+Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
+
+The Stokes double-layer potential  is
+\begin{equation}\label{StokesDLP1}
+\D[\boldsymbol\sigma]({\bf x}):=\frac{1}{\pi}\int_{\Gamma}\left(\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\frac{{\bf r} \otimes {\bf r}}{\rho^2}\right) {\boldsymbol\sigma({\bf y})} d s_y.
+\end{equation}
+We could rewrite the Stokes DLP in terms of the Laplace DLP as
+\begin{align*}\label{StokesDLP2}
+\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
+&-\frac{1}{2\pi}x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y-\frac{1}{2\pi}x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y. \numberthis
+\end{align*}
 
@@
 \label{sec:shearStressLP}
+
+To calculate the shear stress, we need to know the gradient of double-layer potential in \eqref{StokesDLP2} 
+\begin{align*}\label{SSLP}
+\nabla\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\nabla\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla^2\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
+&-\frac{1}{2\pi}\nabla\left(x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y\right)-\frac{1}{2\pi}\nabla\left(x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y\right).
+\numberthis
+\end{align*}
 
@@
 \label{sec:BIE}
+\subsubsection{Interior Case}
+Consider a Cauchy integral 
+\begin{align}\label{CIFI}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{{ y}-{ x}} d{ y}
+&=\begin{cases}
+\,v(x), &{ x} \in \Omega,\\ 
+\,0,  &{ x} \in \Cdb\setminus \bar{\Omega}.
+\end{cases}
+\end{align}
+By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{{ y}-{ x}} d{ y}=1,$ we can rewrtie \eqref{CIFI} and get 
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)}{{ y}-{ x}} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+\end{equation}
+\begin{equation}\label{dNCI}
+v'({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{(y- x)^2} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+\end{equation}
+By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{dNCI} and get 
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)-(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+\end{equation}
+
+\subsubsection{Exterior case}
+Consider a Cauchy integral formula for the exterior domain
+\begin{align}\label{CIFE}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})}{{ y}-{ x}} d{ y}
+&=\begin{cases}
+\,v_{\infty}, &{ x} \in \Omega,\\ 
+\,-v(x)+v_{\infty},  &{ x} \in \Omega^c,
+\end{cases}
+\end{align}
+where $v_{\infty}=\displaystyle\lim_{x \to \infty}v(x)$.
+\begin{equation}
+\frac{1}{x-a}=\frac{-1}{2 \pi i} \int_{\Gamma}\frac{(y-a)^{-1}}{y-x} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
+\end{equation}
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-(y-a)^{-1}(x-a)v(x)}{y-x} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
+\end{equation}
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-v(x)-(y-a)^{-1}(x-a)(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
+\end{equation}
 
@@
 \label{sec:shearStress}
-
+\subsubsection{Interior Case}
+\begin{equation}\label{ddNCI}
+v''({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})}{(y- x)^3} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+\end{equation}
+By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{ddNCI} and get 
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+\end{equation}
+\subsubsection{Exterior case}
+\begin{equation}
+\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^+({ y})-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
+\end{equation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-21 fortran_code/stokesDriver.f
upload the new stokesSolver.f with modified criterion

@@ -3,7 +3,7 @@
 
       parameter (ninner = 2**8)
       parameter (nbodies = 2)
-      parameter (nouter = 2**8)
+      parameter (nouter = 2**10)
       parameter (ntargets = 500)
       parameter (maxbodies = 10)
 

### 2019-04-21 fortran_code/stokesSolver.f

@@ -600,7 +600,8 @@ c     potential
       dimension px(nmax),py(nmax)
       dimension cur(nmax),speed(nmax)
       dimension centerx(maxbodies),centery(maxbodies)
-
+      dimension rtar(nbodies)
+      
       dimension xouter(nmax),youter(nmax)
       dimension px0(nmax),py0(nmax)
       dimension cur0(nmax),speed0(nmax)
@@ -701,12 +702,32 @@ c     start the wall-to-bodies part
         deny(k) = den(k + nouter)
       enddo      
 
+      alpha1 = 4.d0! the criterion parameter for B2Bs
+      alpha2 = 4.d0! the criterion parameter for W2Bs
+c     Find the radii of bodies      
+      do itar = 1, nbodies
+        rtar(itar) = 0.d0
+        do k = 1, ninner
+          rtar(itar) = rtar(itar) + speed((itar-1)*ninner+k)  
+        enddo
+        rtar(itar) = rtar(itar)/ninner
+      enddo
+c     Find the length of wall      
+      lw = 0.d0
+      do k=1, nouter
+        lw = lw + speed0(k)
+      enddo
+      lw = lw/nouter      
+      
       m=1
       do itar = 1,nbodies
-
 c       loop over target points
 c       when the distancce between wall and bodies is closed
-        if( abs(centery(itar)) .ge. 0.5d0) then
+
+c       the criterion of W2Bs
+        dsum = rtar(itar) + alpha2*lw*twopi/nouter
+        dsum2 = 1.d0 - dsum
+        if( abs(centery(itar)) .ge. dsum2) then
 
           do k=1,ninner
             xtarloc(k)=x((itar-1)*ninner+k)
@@ -715,7 +736,7 @@ c       when the distancce between wall and bodies is closed
             denyb(k) = den(2*nouter + (itar-1)*2*ninner + k + ninner)
 c           save xtarloc, ytarloc, denxb, and denyb for body-to-wall barycentric           
           
-            if(abs(y((itar-1)*ninner+k)) .ge. 0.5d0)  then
+            if(abs(y((itar-1)*ninner+k)) .ge. dsum2)  then
               ux(k) = 0.d0
               uy(k) = 0.d0
               xtar(m) = x((itar-1)*ninner+k)
@@ -751,17 +772,12 @@ c         end of the wall-to-bodies part and save the index indw2b for doing bar
[…]

### 2019-04-21 docs/proposals/ErosionWhitePaper.tex

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[sort,nocompress]{cite}
\usepackage{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{lastpage}
\usepackage{pgfplots}
\usepackage{rotating}
\usepackage{siunitx}
\usepackage{subfigure}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usepackage{titlesec}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{verbatim}
%\usepackage{showkeys}

\usetikzlibrary{shapes,arrows}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}
% For 11pt size

\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}

\newcommand{\bd}{\partial}
\newcommand{\BL}{\mathrm{BL}}
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\cc}{\mathbf{c}}
\newcommand{\dlp}{{\mathrm{dlp}}}
\newcommand{\ee}{\mathbf{e}}
\newcommand{\ff}{\mathbf{f}}
\newcommand{\FF}{\mathbf{F}}
\renewcommand{\gg}{\mathbf{g}}
\newcommand{\II}{\mathcal{I}}
\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}}
\newcommand{\nn}{\mathbf{n}}
\newcommand{\NN}{{\mathbf{N}}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\pderivtwo}[2]{\frac{\partial^{2} #1}{\partial #2^{2}}}
\newcommand{\pphi}{{\boldsymbol{\phi}}}
\renewcommand{\Re}{{\textrm{Re}}}
\newcommand{\rr}{{\mathbf{r}}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\slp}{{\mathrm{slp}}}
\newcommand{\ssigma}{{\boldsymbol{\sigma}}}
\newcommand{\SLP}{{\mathtt{SLP}}}
\newcommand{\DD}{{\mathcal{D}}}
\renewcommand{\SS}{{\mathcal{S}}}
\newcommand{\ttau}{{\boldsymbol{\tau}}}
\newcommand{\uu}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\VV}{{\mathcal{V}}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\thL}{$\theta$--$L$}

\pagestyle{fancy}
\lhead{\footnotesize Bryan Quaife}
\chead{\footnotesize Viscous Erosion of a Porous Medium}
\rhead{\footnotesize \thepage}
\cfoot{}

%\usepgfplotslibrary{external}
%\tikzexternalize

\begin{document}
\begin{center}
Viscous Erosion of a Porous Medium \\
Bryan Quaife, Assistant Professor \\
Florida State University \\
512-436-1148, bquaife@fsu.edu \\
DOE/Office of Science Program Office: ASCR-Applied Mathematics \\
Funding Opportunity Announcement Number: DE-FOA-0001968
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Flow-induced erosion deteriorates and reshapes solid material over a
range of scales found in nature, from massive land formations to
centimeter-scale features and patterns. Though less visible, these same
forces are working at the very smallest scales, slowly deteriorating the
individual constituents of porous media (e.g.~soil, sand, or clay) or
biological structures like plaque and biofilms. Motivated by such
examples, we are interested in studying fluid-mechanical erosion in
Stokes flow---the most relevant regime for groundwater and bio-fluid
applications.

\begin{figure}[htp]
\includegraphics[width=\textwidth]{figs/50bod.pdf}
\caption{\label{fig:50bod} Simulation of 50 bodies eroding in Stokes
flow under the action of fluid-mechanical shear. The flow is horizontal
(left to right) and the 6 snapshots are evenly spaced in time. Color
represents vorticity, which provides a convenient way to visualize local
shear rates. Erosion not only diminishes the size of the bodies but also
alters their shapes considerably. A few well-defined channels develop in
the space between bodies.}
\end{figure}

In our recent publication~\cite{qua-moo2018}, we described a suite of
numerical methods to simulate erosion in a viscous fluid
(Figure~\ref{fig:50bod}).  The highlights of our numerical methods are:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
  \item {\bf Boundary Integral Equation Fluid Solver}: The
  incompressible Stokes equations are solved with a boundary integral
  equation (BIE).  By using a BIE, the complex geometries are naturally
  handled, high-order accurate discretizations are deployed, and fast
  summation methods result in optimal complexity.

  \item {\bf Interface Tracking}: Instead of tracking the $(x,y)$
  coordinates of the boundary of the eroding bodies interface, we track
  the \thL coordinates, where $\theta$ is a local tangent angle, and $L$
  is the total length.  The governing equations of the \thL coordinates
  offers several advantages in the ability to numerically stabilize the
  evolving interface

  \item {\bf Regularizations of the Interface}: Erosion results in
  corners of the bodies at stagnation points of the flow.  We 
  use a regularization term and a smoothing operation to control the
  smoothness of the moving interface.

  \item {\bf Analysis of Single Eroding Bodies}: We validate our method
  by comparing numerical simulations with scaling laws.
\end{enumerate}

\section{Proposed Work}
Having developed and validated numerical methods for simulating viscous
erosion, there are two main directions that our research will follow.
First, additional numerical tools are required to simulate more
realistic scenarios such as bodies that erode and transport, and
extending our work to three dimensions.  Second, we will investigate
physically motivated questions regarding the geometry and flow inside an
eroding porous medium

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improved Numerical Methods}
In its current formulation, our bodies are fixed in space.  However, in
reality, eroding bodies are also transported by the flow.  To allow the
bodies to move, there are two additional tools that we will develop.
Bodies get close.

\paragraph{Transport of Bodies:} The PI is experienced with simulating
moving interfaces in Stokes flow.  For example, he has developed
high-order adaptive time stepping methods for simulating deformable
bodies (vesicles) in a viscous fluid~\cite{qua-bir2015b, qua-bir2014,
qua-2016}.   More recently, the PI has graduated a Ph.D.~student that
developed time stepping methods for rigid bodies in a viscous
fluid~\cite{bys-sha-qua2018}.  This work introduces a new time stepping
method

A recent Ph.D.~student from his group

\paragraph{Improved Quadrature:}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Physics-Based Understanding of Viscous Erosion}
\todo[inline]{Characterizing anisotropy}
\todo[inline]{Coarse-grained transport (anomalous diffusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Biographical Information}
Since 2015, {\bf Bryan Quaife} has been an Assistant Professor in the
Department of Scientific Computing at Florida State University.  He is
also a Research Associate in FSU's Geophysical Fluid Dynamics Institute.
Dr.~Quaife received his Ph.D.~in 2011 in Applied and Computational
Mathematics at Simon Fraser University.  He was a postdoctoral fellow
for four years in Dr.~George Biros' group at the Institute for
Computational Science and Engineering at the University of Texas.  His
research interests include the development of  high-fidelity and
efficient numerical methods for simulating fluid dynamics in complex
geometries.

The co-PI of this project is {\bf Nick Moore}.  Since 2014, Dr.~Moore
has been an Assistant Professor in the Department of Mathematics at
Florida State University.  He is also a Research Associate in FSU's
Geophysical Fluid Dynamics Institute. \todo[inline]{A bit more}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Expected Budget}
\todo[inline]{I can have Michelle put one together.  Funds are needed
for the following}
\begin{itemize}
  \item Summer salary (1 month a year for 3 years)
  \item 2 RA (1 in Math, 1 on DSC)
  \item 1 joint postdoc
  \item Travel
  \item Computers
  \item FSU overhead
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{refs}

\end{document}

### 2019-04-22 docs/proposals/ErosionWhitePaper.tex
working on DOE white paper

@@
 \section{Introduction}
-Flow-induced erosion deteriorates and reshapes solid material over a
-range of scales found in nature, from massive land formations to
-centimeter-scale features and patterns. Though less visible, these same
-forces are working at the very smallest scales, slowly deteriorating the
-individual constituents of porous media (e.g.~soil, sand, or clay) or
-biological structures like plaque and biofilms. Motivated by such
-examples, we are interested in studying fluid-mechanical erosion in
-Stokes flow---the most relevant regime for groundwater and bio-fluid
-applications.
-
-\begin{figure}[htp]
-\includegraphics[width=\textwidth]{figs/50bod.pdf}
-\caption{\label{fig:50bod} Simulation of 50 bodies eroding in Stokes
-flow under the action of fluid-mechanical shear. The flow is horizontal
-(left to right) and the 6 snapshots are evenly spaced in time. Color
-represents vorticity, which provides a convenient way to visualize local
-shear rates. Erosion not only diminishes the size of the bodies but also
+\begin{wrapfigure}[24]{r}{0.7\textwidth}
+\centering
+\includegraphics[width=0.68\textwidth]{figs/50bod.pdf}
+\caption{\label{fig:50bod} \em Simulation of 50 bodies eroding in Stokes
+flow under the action of fluid-mechanical erosion. The flow is
+horizontal (left to right) and the 6 snapshots are evenly spaced in
+time.  The local erosion rate on the bodies is proportional to the
+magnitude of the vorticity which we compute in the fluid bulk (color
+scale).  Erosion not only diminishes the size of the bodies but also
 alters their shapes considerably. A few well-defined channels develop in
 the space between bodies.}
-\end{figure}
+\end{wrapfigure}
 
-In our recent publication~\cite{qua-moo2018}, we described a suite of
+Flow-induced erosion deteriorates and reshapes solid material over a
+range of scales found in nature, including massive land formations
+(mountains undergoing wind erosion) and watercourses (rivers and streams
+undergoing hydraulic erosion).  Though less visible, erosion is working
+at the very smallest scales, slowly deteriorating the individual
+constituents of porous media (e.g.~soil, sand, or clay) or biological
+structures like plaque and biofilms. Motivated by such examples, we are
+interested in studying fluid-mechanical erosion in Stokes flow---the
+most relevant regime for groundwater and bio-fluid applications.
+
+In our recent publication~\cite{qua-moo2018}, we describe a suite of
 numerical methods to simulate erosion in a viscous fluid
@@
   \item {\bf Interface Tracking}: Instead of tracking the $(x,y)$
-  coordinates of the boundary of the eroding bodies interface, we track
-  the \thL coordinates, where $\theta$ is a local tangent angle, and $L$
-  is the total length.  The governing equations of the \thL coordinates
-  offers several advantages in the ability to numerically stabilize the
-  evolving interface
+  coordinates of the of the eroding interfaces, we track the {\thL}
+  coordinates, where $\theta$ is a local tangent angle, and $L$ is the
+  total interface length.  The governing equations of the {\thL}
+  coordinates offers several advantages in the ability to numerically
+  stabilize the evolving interface.
 
   \item {\bf Regularizations of the Interface}: Erosion results in
-  corners of the bodies at stagnation points of the flow.  We 
-  use a regularization term and a smoothing operation to control the
-  smoothness of the moving interface.
+  numerically challenging corners of the bodies at stagnation points of
+  the flow.  We use a regularization term and a smoothing operation to
+  control the smoothness of the moving interface.
 
@@
 First, additional numerical tools are required to simulate more
-realistic scenarios such as bodies that erode and transport, and
-extending our work to three dimensions.  Second, we will investigate
-physically motivated questions regarding the geometry and flow inside an
-eroding porous medium
+realistic scenarios such as denser packings, transport, and
+three-dimensional erosion.  Second, we will investigate physically
+motivated questions regarding the geometry and flow inside an eroding
+porous medium.
 
@@
 \subsection{Improved Numerical Methods}
+\begin{wrapfigure}[22]{r}{0.4\textwidth}
+\centering
+\input{figs/vort1.tikz}
+\caption{\label{fig:vort1} \em The vorticity a vertical slice cutting
+through a single body.  There are solid walls at $y = \pm 1$, and an
+eroding body at $y = (-0.5,0.5)$.  The trapezoid rule gives large errors
+near the solid walls, while the Barycentric quadrature formula results
+in a smooth vorticity field.}
+\end{wrapfigure}
+
 In its current formulation, our bodies are fixed in space.  However, in
@@
 bodies to move, there are two additional tools that we will develop.
-Bodies get close.
-
-\paragraph{Transport of Bodies:} The PI is experienced with simulating
-moving interfaces in Stokes flow.  For example, he has developed
-high-order adaptive time stepping methods for simulating deformable
-bodies (vesicles) in a viscous fluid~\cite{qua-bir2015b, qua-bir2014,
-qua-2016}.   More recently, the PI has graduated a Ph.D.~student that
-developed time stepping methods for rigid bodies in a viscous
-fluid~\cite{bys-sha-qua2018}.  This work introduces a new time stepping
-method
-
-A recent Ph.D.~student from his group
-
-\paragraph{Improved Quadrature:}
+The PI is experienced with simulating moving interfaces in Stokes flow.
+For example, he has developed high-order adaptive time stepping methods
+for simulating deformable bodies (vesicles) in a viscous
+fluid~\cite{qua-bir2015b, qua-bir2014, qua-bir2016}. More recently, the
+PI and his former Ph.D.~student developed time stepping methods for
+rigid body transport in a viscous fluid~\cite{bys-sha-qua2018}.  This
+work extends a contact algorithm, originally developed by Lu et
+al.~\cite{lu-rah-zor2017}, to accuratly simulate the dynamics of
+nearly-touching rigid bodies.  The contact algorithm resolves errors
+introduced by time stepping, but quadrature error introduced by the
+integral equation formulation must also be addressed.  A postdoc in the
+PI's group is extending a Barycentric near-singular integration scheme
+developed by Barnett et al.~\cite{bar-wu-vee2015} to develop quadrature
+formula to compute the shear stress and vorticity.  In
+Figure~\ref{fig:vort1}, the vorticity is computed along a vertical slice
+that cuts through a single eroding body.  The trapezoid rule is accurate
+far from the solid walls ($y = \pm 1$) and the boundary of the eroding
+body ($y = \pm 0.5$), but introduces large errors near the walls and
+body.  However, the Barycentric quadrature rule is uniformly accurate
+throughout the entire fluid domain.
 
@@
 \todo[inline]{Characterizing anisotropy}
-\todo[inline]{Coarse-grained transport (anomalous diffusion}
+\todo[inline]{Coarse-grained transport (anomalous diffusion)}
 
@@
 \bibliographystyle{plain}
-\bibliography{refs}
+\footnotesize{\bibliography{refs}}
 

### 2019-04-22 docs/proposals/ErosionWhitePaper.tex
worked on white paper

@@
 \section{Introduction}
-\begin{wrapfigure}[24]{r}{0.7\textwidth}
+\begin{wrapfigure}[22]{r}{0.6\textwidth}
 \centering
-\includegraphics[width=0.68\textwidth]{figs/50bod.pdf}
+\includegraphics[width=0.58\textwidth]{figs/50bod.pdf}
 \caption{\label{fig:50bod} \em Simulation of 50 bodies eroding in Stokes
@@
 magnitude of the vorticity which we compute in the fluid bulk (color
-scale).  Erosion not only diminishes the size of the bodies but also
-alters their shapes considerably. A few well-defined channels develop in
-the space between bodies.}
+scale).  Erosion both diminishes the size of the bodies and considerably
+alters their shapes.}
 \end{wrapfigure}
@@
   \item {\bf Boundary Integral Equation Fluid Solver}: The
-  incompressible Stokes equations are solved with a boundary integral
-  equation (BIE).  By using a BIE, the complex geometries are naturally
-  handled, high-order accurate discretizations are deployed, and fast
-  summation methods result in optimal complexity.
-
-  \item {\bf Interface Tracking}: Instead of tracking the $(x,y)$
-  coordinates of the of the eroding interfaces, we track the {\thL}
-  coordinates, where $\theta$ is a local tangent angle, and $L$ is the
-  total interface length.  The governing equations of the {\thL}
-  coordinates offers several advantages in the ability to numerically
-  stabilize the evolving interface.
+  fluid equations are solved with a boundary integral equation (BIE).
+  The BIE formulation achives high-order accuracy in complex geometries
+  with optimal computational complexity.
 
   \item {\bf Regularizations of the Interface}: Erosion results in
-  numerically challenging corners of the bodies at stagnation points of
-  the flow.  We use a regularization term and a smoothing operation to
-  control the smoothness of the moving interface.
+  numerically challenging corners of the bodies.  We use a
+  regularization term and a smoothing operation to control the
+  smoothness of the moving interface.
 
-  \item {\bf Analysis of Single Eroding Bodies}: We validate our method
-  by comparing numerical simulations with scaling laws.
+  \item {\bf Interface Tracking}: We describe the interface using
+  {\thL} coordinates, where $\theta$ is a local tangent angle, and $L$
+  is the total interface length.  In these coordinates, the
+  stiff terms are linear and are be discretized implicitly.
+
+  \item {\bf Validation}: We compare the numerical simulations with
+  scaling laws.
 \end{enumerate}
@@
 erosion, there are two main directions that our research will follow.
-First, additional numerical tools are required to simulate more
+First, {\bf additional numerical tools are required to simulate more
 realistic scenarios such as denser packings, transport, and
-three-dimensional erosion.  Second, we will investigate physically
+three-dimensional erosion}.  Second, {\bf we will investigate physically
 motivated questions regarding the geometry and flow inside an eroding
-porous medium.
+porous medium}.
 
@@
 \input{figs/vort1.tikz}
-\caption{\label{fig:vort1} \em The vorticity a vertical slice cutting
-through a single body.  There are solid walls at $y = \pm 1$, and an
-eroding body at $y = (-0.5,0.5)$.  The trapezoid rule gives large errors
-near the solid walls, while the Barycentric quadrature formula results
-in a smooth vorticity field.}
+\caption{\label{fig:vort1} \em The vorticity along a vertical slice
+cutting through a single body.  There are solid walls at $y = \pm 1$,
+and an eroding body at $y = (-0.5,0.5)$.  The trapezoid rule gives large
+errors near the solid walls, while the Barycentric quadrature formula
+results in a smooth vorticity field.}
 \end{wrapfigure}
 
-In its current formulation, our bodies are fixed in space.  However, in
-reality, eroding bodies are also transported by the flow.  To allow the
-bodies to move, there are two additional tools that we will develop.
-The PI is experienced with simulating moving interfaces in Stokes flow.
-For example, he has developed high-order adaptive time stepping methods
-for simulating deformable bodies (vesicles) in a viscous
-fluid~\cite{qua-bir2015b, qua-bir2014, qua-bir2016}. More recently, the
-PI and his former Ph.D.~student developed time stepping methods for
-rigid body transport in a viscous fluid~\cite{bys-sha-qua2018}.  This
-work extends a contact algorithm, originally developed by Lu et
-al.~\cite{lu-rah-zor2017}, to accuratly simulate the dynamics of
-nearly-touching rigid bodies.  The contact algorithm resolves errors
-introduced by time stepping, but quadrature error introduced by the
-integral equation formulation must also be addressed.  A postdoc in the
-PI's group is extending a Barycentric near-singular integration scheme
-developed by Barnett et al.~\cite{bar-wu-vee2015} to develop quadrature
-formula to compute the shear stress and vorticity.  In
-Figure~\ref{fig:vort1}, the vorticity is computed along a vertical slice
-that cuts through a single eroding body.  The trapezoid rule is accurate
-far from the solid walls ($y = \pm 1$) and the boundary of the eroding
-body ($y = \pm 0.5$), but introduces large errors near the walls and
-body.  However, the Barycentric quadrature rule is uniformly accurate
-throughout the entire fluid domain.
+Our current formulation fixes all bodies space.  However, in reality,
+the bodies are also transported by the flow.  The PI has simulated
+moving interfaces in Stokes flow~\cite{qua-bir2015b, qua-bir2014,
+qua-bir2016}. More recently, the PI and his former Ph.D.~student
+developed time stepping methods for rigid body transport in Stokes
+flow~\cite{bys-sha-qua2018}.  This work extends a contact algorithm,
+originally developed by Lu et al.~\cite{lu-rah-zor2017}, to accuratly
+simulate the dynamics of nearly-touching rigid bodies.  The contact
+algorithm resolves errors introduced by time stepping, but quadrature
+error introduced by the BIE formulation must also be addressed.  A
+postdoc in the PI's group is extending a Barycentric near-singular
+integration scheme developed by Barnett et al.~\cite{bar-wu-vee2015} to
+develop quadrature formula to accurately compute the shear stress,
+vorticity, and other physical quantities.  In Figure~\ref{fig:vort1},
+the vorticity is computed along a vertical slice that cuts through a
+single eroding body.  The trapezoid rule is accurate far from the solid
+walls ($y = \pm 1$) and the boundary of the eroding body ($y = \pm
+0.5$), but introduces large errors near the walls and body.  However,
+our new Barycentric quadrature rule is uniformly accurate throughout the
+entire fluid domain.
 

### 2019-04-22 docs/proposals/ErosionWhitePaper.tex
fixed small typo in white paper

@@
 cutting through a single body.  There are solid walls at $y = \pm 1$,
-and an eroding body at $y = (-0.5,0.5)$.  The trapezoid rule gives large
+and an eroding body at $y = [-0.3,0.5]$.  The trapezoid rule gives large
 errors near the solid walls, while the Barycentric quadrature formula
@@
 single eroding body.  The trapezoid rule is accurate far from the solid
-walls ($y = \pm 1$) and the boundary of the eroding body ($y = \pm
-0.5$), but introduces large errors near the walls and body.  However,
-our new Barycentric quadrature rule is uniformly accurate throughout the
-entire fluid domain.
+walls ($y = \pm 1$) and the boundary of the eroding body ($y \in
+[-0.3,0.5]$), but introduces large errors near the walls and body.
+However, our new Barycentric quadrature rule is uniformly accurate
+throughout the entire fluid domain.
 

### 2019-04-25 docs/transport/erosion_transport.tex
type the numerical method of exterior part
working on transport paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Governing Equations}
+\begin{equation}
+\label{eqn:erosionModel}
+\begin{split}
+  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation
+of momentum}\\
+\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
+\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
+bodies} \\
+\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
+velocity} \\
+\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
+&&\mbox{\em erosion model}.
+\end{split}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Contributions}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Formulation}
+\section{Boundary Integral Equation Formulation}
 \label{s:formulation}
+Continuing on our previous work~\cite{qua-moo2018}, we use a completed
+double-layer potential formulation for the velocity $\uu$.  The
+double-layer potential is
+\begin{align}
+  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
+    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+    \eeta(\yy) ds_\yy,
+\end{align}
+where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown
+density function.  The double-layer potential itself can not represent
+all solutions of the incompressible Stokes equations.  Therefore, we
+complete the integral equation formulation following the work of Power
+and Miranda~\cite{pow-mir1987}.  The completion depends on the
+Stokeslets and rotlets
+\begin{align}
+  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
+    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \qquad
+  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
+\end{align}
+where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
+$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
+\|\rr\|$.  Then, the solution of the Stokes equation is
+\begin{align}
+  \uu(\xx) = \DDD[\eeta](\xx) + 
+    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
+    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx),
+\end{align}
+where the density function, Stokeslets, and rotlets satisfy
+\begin{align}
+  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
+    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
+    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
+    \NN_0(\eeta](\xx), \qquad \xx \in \bd\Omega, \\
+  \lambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
+    \eeta(\yy) ds_\yy \qquad \ell = 1,\ldots,M, \\
+  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
+    (\yy - \cc_\ell)^\perp  \eeta(\yy) ds_\yy 
+    \qquad \ell = 1,\ldots,M.
+\end{align}
+The Stokes double-layer potential can be written as
+\begin{align}
+  \DDD[\eeta](\xx) &= 
+    \frac{1}{2\pi} \int_{\Gamma} 
+      \frac{\nn}{\rho^2} (\rr \cdot \eeta) ds_\yy + 
+    \frac{1}{2\pi} \nabla \int_{\Gamma}
+      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta)ds_\yy \\
+    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
+      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
+    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
+      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy,
+\end{align}
+and this formulation is convenient since each of the integrals can be
+written as a Laplacian double-layer potential,
+\begin{align}
+  \DD[\tau](\xx) = -\frac{1}{2\pi} \int_{\Gamma} \pderiv{}{\nn_\yy}
+    \log(\rho) \tau(\yy) ds_\yy.
+\end{align}
+Finally, by identifying $\RR^2$ with $\CC$, for purely real $\tau$, the
+Laplacian double-layer potential can be written as the real part of a
+Cauchy integral
+\begin{align}
+  \DD[\tau](x) = \Re (v(x)),
+  \qquad \text{where} \qquad
+  v(x) = \frac{1}{2\pi i} \int_\Gamma \frac{\tau(y)}{x - y} dy.
+\end{align}
+Therefore, the Stokes double-layer potential can be written as five
+Cauchy integrals and their derivatives with the density functions $\yy
+\cdot \nn$, $\eta_1$, and $\eta_2.$
+
+Since the rate of erosion is proportional to the shear stress, we also
+require the gradient of the Stokes double-layer potential $\nabla
+\DDD[\eeta](\xx)$.  Using the Cauchy integral formulation, the shear
+stress of the double-layer potential velocity is
+\begin{align}
+  \nabla\D[\eeta](\xx) = \frac{1}{2\pi}\nabla\int_{\Gamma}
+    &\frac{\nn}{\rho^2}(\rr \cdot \eeta)ds_\yy +
+  \frac{1}{2\pi}\nabla\nabla\int_{\Gamma}
+    \frac{\rr \cdot \nn}{\rho^2}({\yy} \cdot\eeta) ds_y \\
+  &- \frac{1}{2\pi} \nabla x_1 \nabla \int_{\Gamma}
+      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
+  \frac{1}{2\pi} \nabla x_2 \nabla \int_{\Gamma}
+      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy.
+\end{align}
+
+\section{New Section}
+A standard discretization of these equations approximates the
+double-layer potential with the trapezoid rule.  This quadrature rule is
+appropriate if the integrands are sufficiently smooth, where the
+smoothness depends on the number of discretization points.  However,
+given a fixed resolution, if the target point $\xx$ is too close to $\bd
+\Omega$, the trapezoid rule becomes inaccurate and the overall method
+becomes unstable.  There have been a variety of near-singular
+integration schemes developed, and we extend a method first outlined by
+Barnett et al.~\cite{bar-wu-vee2015} which we will call the {\em
+Barycentric quadrature rule}.  Here, we briefly describe this quadrature
+method, and then derive a necessary extension to simulate erosion.
+
+The Barycentric quadrature rule was first described for the single- and
+double-layer potentials corresponding to Laplace's equation.
+
+A quadrature scheme for $v(x)$, for a target point $x$, is
+\begin{align}
+  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^N 
+    w_j \frac{\tau(y_j)}{x - y_j},
+\end{align}
+where $w_j$ are the quadrature weights and $y_j \in \Gamma$ are the
+quadrature nodes.  If the trapezoid rule is used, the quadrature rule
+has spectral accuracy.  However, for a fixed resolution $N$, the error
+grows without bound as $x$ approaches $\Gamma$.  As outline by Barnett
+et al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
+Barycentric quadrature rule
+\begin{align}
+  v(x) \approx \frac{\sum_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
+    {\sum_{j=1}^N \frac{1}{y_j-x}w_j},  \qquad
+  v'(x) \approx \frac{\sum_{j=1}^N \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
+    {\sum_{j=1}^N \frac{1}{y_j-x}w_j}, 
+\end{align}
+is used, where $x$ is a target point that is interior to $\Gamma$,
+and $v_j^-$ is the value of $v(y_j)$.  Modifications of this formula
+exist if $x$ is exterior to $\Gamma$.
+
 Similar to the JCP methods paper.  However, need to put everything into
@@
 Add an introduction why we do not use the double-layer potentials of Stokes equations but the double-layer potentials of Laplace equations to solve Stokes equation when we use Barycentric approach (or complex variable approach).
-\subsubsection{Laplace's equations from $\Rdb^2$ to $\Cdb$ }
 
-Let $\Omega$ be the domain of fluid. The boundary of $\Omega$ is $\Gamma$ and the outward normal vector on $\Gamma$ is ${\bf n_y}=(n_1,n_2)$.
-
-Consider a Laplace's equations with Dirichlet boundary condition
-\begin{equation}\label{Laplace}
-  \begin{cases}
-    \Delta {\bf u}=0, & \text{in}\,\,\, \Omega \in \Rdb^2;\\
-    {\bf u}={\bf f}, & \text{on}\,\,\, \Gamma.
-  \end{cases}
-\end{equation}
-
-Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
-The double-layer potential which solves \eqref{Laplace} is 
-\begin{align*}
-\D[\sigma]({\bf x})&=\frac{1}{2\pi}\displaystyle\int_{\Gamma} \frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma({\bf y})ds_y,
-%\frac{1}{2\pi}\displaystyle\int_{\Gamma}\frac{\partial}{\partial {\bf n_y}} \log |{\bf x}-{\bf y}| \sigma({\bf y})ds_y,\\ \\
-%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{{\bf r}\cdot{\bf n_y}}{\rho^2} \sigma({\bf y})ds_y\\ \\
-%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{n_1(x_1-y_1)+n_2(x_2-y_2)}{(x_1-y_1)^2+(x_2-y_2)^2} \sigma({\bf y})ds_y 
-\numberthis\label{DLP:real}
-\end{align*}
-where $\sigma$ is the density function on the boundary $\Gamma$.
-
-Consider a Cauchy integral 
-\begin{equation}\label{CI}
-v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{\sigma({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
-\end{equation}
-where ${ x}=x_1+ix_2$, $ { y}=y_1+iy_2$, ${ n_y}=n_1+i n_2$ and $d{ y}=i {n_y}ds_y$. It can be showed that 
-the real part of the Cauchy integral in \eqref{CI} is equivalent to the double-layer potential in \eqref{DLP:real}.
-
-\subsubsection{From Stokes DLP to Laplace DLPs}
-
-Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
-
-The Stokes double-layer potential  is
-\begin{equation}\label{StokesDLP1}
-\D[\boldsymbol\sigma]({\bf x}):=\frac{1}{\pi}\int_{\Gamma}\left(\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\frac{{\bf r} \otimes {\bf r}}{\rho^2}\right) {\boldsymbol\sigma({\bf y})} d s_y.
-\end{equation}
-We could rewrite the Stokes DLP in terms of the Laplace DLP as
-\begin{align*}\label{StokesDLP2}
-\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
-&-\frac{1}{2\pi}x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y-\frac{1}{2\pi}x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y. \numberthis
-\end{align*}
+%\subsubsection{Laplace's equations from $\Rdb^2$ to $\Cdb$ }
+%
+%Let $\Omega$ be the domain of fluid. The boundary of $\Omega$ is $\Gamma$ and the outward normal vector on $\Gamma$ is ${\bf n_y}=(n_1,n_2)$.
+%
+%Consider a Laplace's equations with Dirichlet boundary condition
+%\begin{equation}\label{Laplace}
+%  \begin{cases}
+%    \Delta {\bf u}=0, & \text{in}\,\,\, \Omega \in \Rdb^2;\\
+%    {\bf u}={\bf f}, & \text{on}\,\,\, \Gamma.
+%  \end{cases}
+%\end{equation}
+%
+%Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
+%The double-layer potential which solves \eqref{Laplace} is 
+%\begin{align*}
+%\D[\sigma]({\bf x})&=\frac{1}{2\pi}\displaystyle\int_{\Gamma} \frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma({\bf y})ds_y,
+%%\frac{1}{2\pi}\displaystyle\int_{\Gamma}\frac{\partial}{\partial {\bf n_y}} \log |{\bf x}-{\bf y}| \sigma({\bf y})ds_y,\\ \\
+%%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{{\bf r}\cdot{\bf n_y}}{\rho^2} \sigma({\bf y})ds_y\\ \\
+%%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{n_1(x_1-y_1)+n_2(x_2-y_2)}{(x_1-y_1)^2+(x_2-y_2)^2} \sigma({\bf y})ds_y 
+%\numberthis\label{DLP:real}
+%\end{align*}
+%where $\sigma$ is the density function on the boundary $\Gamma$.
+%
+%
+%Consider a Cauchy integral 
+%\begin{equation}\label{CI}
+%v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{\sigma({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
+%\end{equation}
+%where ${ x}=x_1+ix_2$, $ { y}=y_1+iy_2$, ${ n_y}=n_1+i n_2$ and $d{ y}=i {n_y}ds_y$. It can be shown that 
+%the real part of the Cauchy integral in \eqref{CI} is equivalent to the double-layer potential in \eqref{DLP:real}. 
+%
+%
+%\subsubsection{From Stokes DLP to Laplace DLPs}
+%
+%Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
+%
+%
+%The Stokes double-layer potential  is
+%\begin{equation}\label{StokesDLP1}
+%\D[\boldsymbol\sigma]({\bf x}):=\frac{1}{\pi}\int_{\Gamma}\left(\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\frac{{\bf r} \otimes {\bf r}}{\rho^2}\right) {\boldsymbol\sigma({\bf y})} d s_y.
+%\end{equation}
+%We could rewrite the Stokes DLP in terms of the Laplace DLP as
+%\begin{align*}\label{StokesDLP2}
+%\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
+%&-\frac{1}{2\pi}x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y-\frac{1}{2\pi}x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y. \numberthis
+%\end{align*}
+%
 

### 2019-04-26 docs/transport/erosion_transport.tex
doing tranposrt paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction\label{s:intro}}
+\section{Introduction}
+\label{s:intro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 A continuation of the methods paper~\cite{qua-moo2018}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Governing Equations}
@@
 \end{align}
+
+We will apply a quadrature rule that requires that the double-layer
+potential representations of the velocity, shear stress, pressure, and
+vorticity are written in terms of the Cauchy integral and its first two
+derivatives
+\begin{align}
+  \label{eqn:Cauchy}
+  v(x) &= \frac{1}{2\pi i} \int_\Gamma 
+    \frac{\tau(y)}{x - y} dy, \\
+  v'(x) &= -\frac{1}{2\pi i} \int_\Gamma 
+    \frac{\tau(y)}{(x - y)^2} dy, \\
+  v''(x) &= \frac{2}{2\pi i} \int_\Gamma 
+    \frac{\tau(y)}{(x - y)^3} dy.
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Cauchy Integral Representation of the Velocity}
 The Stokes double-layer potential can be written as
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Cauchy Integral Representation of the Shear Stress}
 Since the rate of erosion is proportional to the shear stress, we also
 require the gradient of the Stokes double-layer potential $\nabla
-\DDD[\eeta](\xx)$.  Using the Cauchy integral formulation, the shear
-stress of the double-layer potential velocity is
+\DDD[\eeta](\xx)$.  Using the Cauchy integral formulation, the gradient
+of of the double-layer potential velocity is
 \begin{align}
@@
 \end{align}
+Then, the deformation tensor can be written in terms of Cauchy integrals
+\todo[inline]{For S-H to fill in}
+\begin{align}
+  \ssigma = \frac{1}{2} 
+    \left(\nabla \DDD[\eeta] + \nabla^T \DDD[\eeta] \right) 
+      \nn \cdot \ss = \ldots
+\end{align}
 
-\section{New Section}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Cauchy Integral Representation of the Vorticity}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Cauchy Integral Representation of the Pressure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Transport, Tracers, and Tortuosity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Erosion leads to interesting porous geometries, and we are interested in
+characterizing transport in these geometries.  To characterize the
+transport, we first require tracer trajectories (streamlines) that are
+governed by
+\begin{align}
+  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
+\end{align}
+Instead of allowing the transport and erosion to happen simultaneously,
+we freeze the geometry and compute the streamlines in this fixed
+geometry.  Therefore, the velocity $\uu$ has no temporal dependence when
+we characterize the transport.
+
+The tortuosity measures ...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Methods}
+\label{s:method}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 A standard discretization of these equations approximates the
@@
 
-The Barycentric quadrature rule was first described for the single- and
-double-layer potentials corresponding to Laplace's equation.
-
-A quadrature scheme for $v(x)$, for a target point $x$, is
+Since we are able to write on all our quantities of interest in terms of
+a Cauchy integral and its derivatives, we only require a near-singular
+integration method for equation~\eqref{eqn:Cauchy}.  A quadrature scheme
+for $v(x)$, for a target point $x$, is
 \begin{align}
@@
 
-Similar to the JCP methods paper.  However, need to put everything into
-complex variables formulation so that we can use Barycentric ideas.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Barcyentric Quadrature for $v''(x)$}
+In order to simulate erosion, we require the deformation gradient which
+means that a quadrature rule for $v''(x)$ is required.  Using the same
+techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
+quadrature rule for the second derivative can be constructed using the
+identities
+\begin{alignat}{3}
+  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{v^-(y)-v(x)}{y-x} dy, &&x \in \Omega, \\
+  0 &= \frac{1}{2\pi i}\int_{\Gamma}
+    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
+    {(y-x)^3} dy, \quad &&x \in \Omega^c.
+\end{alignat}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary integral equation formulation} 
-\label{sec:bies}
-Add an introduction why we do not use the double-layer potentials of Stokes equations but the double-layer potentials of Laplace equations to solve Stokes equation when we use Barycentric approach (or complex variable approach).
+\subsection{Fast Summation Methods}
+\label{sec:fmm}
+\begin{itemize}
+  \item Apply trapezoid rule as a first pass
+  \item Efficiently find points that are too close for trapezoid
+  \item Subtract off trapezoid rule directly
+  \item Add on Barycentric directly
+\end{itemize}
 
-%\subsubsection{Laplace's equations from $\Rdb^2$ to $\Cdb$ }
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Results}
+\label{s:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We do some simulations.  The parameters are
+\begin{itemize}
+  \item time step size
+  \item regularization and smoothing parameters
+  \item resolution on bodies and solid wall
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{A single body close to a wall}
+\todo[inline]{Do a single body that is extremely close one of the two
+horizontal walls.  This can be compared to some of the
+results~\cite{mit-spa2017}.  Do for a variety of distances to
+demonstrate how close we can put it to the wall with no need to increase
+the resolution}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{20 nearly touching bodies}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{50 nearly touching bodies}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+\label{s:conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for
+supplying the FMM for the Stokes double-layer potential. BQ and NM were
+supported by Florida State University startup funds and Simons
+Foundation Mathematics and Physical Sciences-Collaboration Grants for
+Mathematicians.
+
+\bibliographystyle{plainnat} 
+\biboptions{sort&compress}
+\bibliography{refs}
+
+\end{document}
+
+%old stuff%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{boundary integral equation formulation} 
+%\label{sec:bies}
+%add an introduction why we do not use the double-layer potentials of stokes equations but the double-layer potentials of laplace equations to solve stokes equation when we use barycentric approach (or complex variable approach).
 %
-%Let $\Omega$ be the domain of fluid. The boundary of $\Omega$ is $\Gamma$ and the outward normal vector on $\Gamma$ is ${\bf n_y}=(n_1,n_2)$.
+%\subsubsection{laplace's equations from $\rdb^2$ to $\cdb$ }
 %
-%Consider a Laplace's equations with Dirichlet boundary condition
-%\begin{equation}\label{Laplace}
+%let $\omega$ be the domain of fluid. the boundary of $\omega$ is $\gamma$ and the outward normal vector on $\gamma$ is ${\bf n_y}=(n_1,n_2)$.
+%
+%consider a laplace's equations with dirichlet boundary condition
+%\begin{equation}\label{laplace}
 %  \begin{cases}
-%    \Delta {\bf u}=0, & \text{in}\,\,\, \Omega \in \Rdb^2;\\
-%    {\bf u}={\bf f}, & \text{on}\,\,\, \Gamma.
+%    \delta {\bf u}=0, & \text{in}\,\,\, \omega \in \rdb^2;\\
+%    {\bf u}={\bf f}, & \text{on}\,\,\, \gamma.
 %  \end{cases}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Computing the shear stress}
-\label{sec:shearStressLP}
-
-To calculate the shear stress, we need to know the gradient of double-layer potential in \eqref{StokesDLP2} 
-\begin{align*}\label{SSLP}
-\nabla\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\nabla\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla^2\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
-&-\frac{1}{2\pi}\nabla\left(x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y\right)-\frac{1}{2\pi}\nabla\left(x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y\right).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Computing the shear stress}
+%\label{sec:shearStressLP}
+%
+%To calculate the shear stress, we need to know the gradient of double-layer potential in \eqref{StokesDLP2} 
+%\begin{align*}\label{SSLP}
+%\nabla\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\nabla\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla^2\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
+%&-\frac{1}{2\pi}\nabla\left(x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y\right)-\frac{1}{2\pi}\nabla\left(x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y\right).
 \numberthis
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary evolution in the {\thL} framework} 
-\label{sec:thetaL}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical methods}
-\label{s:method}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fast Summation Methods}
-\label{sec:FMM}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Solving the BIE}
-\label{sec:BIE}
-\subsubsection{Interior Case}
-Consider a Cauchy integral 
-\begin{align}\label{CIFI}
-\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{{ y}-{ x}} d{ y}
-&=\begin{cases}
-\,v(x), &{ x} \in \Omega,\\ 
-\,0,  &{ x} \in \Cdb\setminus \bar{\Omega}.
-\end{cases}
-\end{align}
-By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{{ y}-{ x}} d{ y}=1,$ we can rewrtie \eqref{CIFI} and get 
-\begin{equation}
-\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)}{{ y}-{ x}} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-\end{equation}
-\begin{equation}\label{dNCI}
-v'({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{(y- x)^2} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-\end{equation}
-By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{dNCI} and get 
-\begin{equation}
-\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)-(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-\end{equation}
-
-\subsubsection{Exterior case}
-Consider a Cauchy integral formula for the exterior domain
-\begin{align}\label{CIFE}
-\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})}{{ y}-{ x}} d{ y}
-&=\begin{cases}
-\,v_{\infty}, &{ x} \in \Omega,\\ 
-\,-v(x)+v_{\infty},  &{ x} \in \Omega^c,
-\end{cases}
-\end{align}
-where $v_{\infty}=\displaystyle\lim_{x \to \infty}v(x)$.
-\begin{equation}
-\frac{1}{x-a}=\frac{-1}{2 \pi i} \int_{\Gamma}\frac{(y-a)^{-1}}{y-x} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
-\end{equation}
-\begin{equation}
-\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-(y-a)^{-1}(x-a)v(x)}{y-x} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
-\end{equation}
-\begin{equation}
-\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-v(x)-(y-a)^{-1}(x-a)(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Shear stress}
-\label{sec:shearStress}
-\subsubsection{Interior Case}
-\begin{equation}\label{ddNCI}
-v''({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})}{(y- x)^3} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-\end{equation}
-By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{ddNCI} and get 
-\begin{equation}
-\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-\end{equation}
-\subsubsection{Exterior case}
-\begin{equation}
-\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^+({ y})-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
-\end{equation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% TIME-STEPPING %%
-\subsection{Time-stepping with the {\thL} method} 
-\label{sec:timeStepping}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Post processing quantities of interest}
-\label{s:qoi}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Vorticity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pressure}
-\label{sec:pressure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Drag}
-\label{sec:drag}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Near-singular integration}
-\label{sec:NSI}
-
-%%-----------------------------------------------------------------%%
-% RESULTS SECTION
-%%-----------------------------------------------------------------%%
-\section{Results: Single-body erosion}
-\label{s:SingleResults}
-
-\subsection{A single body eroding in Stokes flow}
-
-\subsection{Scaling laws for area and drag}
-\label{sec:scaling}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions\label{s:conclusions}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for
-supplying the FMM for the Stokes double-layer potential. BQ and NM were
-supported by Florida State University startup funds and Simons
-Foundation Mathematics and Physical Sciences-Collaboration Grants for
-Mathematicians.
-
-\bibliographystyle{plainnat} 
-\biboptions{sort&compress}
-\bibliography{refs}
-
-\end{document}
+%\end{align*}
+%
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Boundary evolution in the {\thL} framework} 
+%\label{sec:thetaL}
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Solving the BIE}
+%\label{sec:BIE}
+%\subsubsection{Interior Case}
+%Consider a Cauchy integral 
+%\begin{align}\label{CIFI}
+%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{{ y}-{ x}} d{ y}
+%&=\begin{cases}
+%\,v(x), &{ x} \in \Omega,\\ 
+%\,0,  &{ x} \in \Cdb\setminus \bar{\Omega}.
+%\end{cases}
+%\end{align}
+%By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{{ y}-{ x}} d{ y}=1,$ we can rewrtie \eqref{CIFI} and get 
+%\begin{equation}
+%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)}{{ y}-{ x}} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+%\end{equation}
+%\begin{equation}\label{dNCI}
+%v'({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{(y- x)^2} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+%\end{equation}
+%By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{dNCI} and get 
+%\begin{equation}
+%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)-(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+%\end{equation}
+%
+%\subsubsection{Exterior case}
+%Consider a Cauchy integral formula for the exterior domain
+%\begin{align}\label{CIFE}
+%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})}{{ y}-{ x}} d{ y}
+%&=\begin{cases}
+%\,v_{\infty}, &{ x} \in \Omega,\\ 
+%\,-v(x)+v_{\infty},  &{ x} \in \Omega^c,
+%\end{cases}
+%\end{align}
+%where $v_{\infty}=\displaystyle\lim_{x \to \infty}v(x)$.
+%\begin{equation}
+%\frac{1}{x-a}=\frac{-1}{2 \pi i} \int_{\Gamma}\frac{(y-a)^{-1}}{y-x} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
+%\end{equation}
+%\begin{equation}
+%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-(y-a)^{-1}(x-a)v(x)}{y-x} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
+%\end{equation}
+%\begin{equation}
+%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-v(x)-(y-a)^{-1}(x-a)(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
+%\end{equation}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Shear stress}
+%\label{sec:shearStress}
+%\subsubsection{Interior Case}
+%\begin{equation}\label{ddNCI}
+%v''({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})}{(y- x)^3} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+%\end{equation}
+%By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{ddNCI} and get 
+%\begin{equation}
+%\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
+%\end{equation}
+%\subsubsection{Exterior case}
+%\begin{equation}
+%\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^+({ y})-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
+%\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% TIME-STEPPING %%
+%\subsection{Time-stepping with the {\thL} method} 
+%\label{sec:timeStepping}
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Post processing quantities of interest}
+%\label{s:qoi}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Vorticity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Pressure}
+%\label{sec:pressure}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Drag}
+%\label{sec:drag}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Near-singular integration}
+%\label{sec:NSI}
+%

### 2019-05-01 docs/transport/erosion_transport.tex
doing tranposrt paper

@@
 Cauchy integrals and their derivatives with the density functions $\yy
-\cdot \nn$, $\eta_1$, and $\eta_2.$
-
+\cdot {\color{red}\eeta}$, $\eta_1$, and $\eta_2,$
+{\color{red}
+\begin{align}
+ u_1(\xx)&= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
+           -x_1\Re (v'[\eta_1](x)) -x_2\Re (v'[\eta_2](x)),\\
+ u_2(\xx)&= \Re (v[\tau_2](x)) - \operatorname{Im} (v'[\yy\cdot\eeta](x)) 
+       +x_1\operatorname{Im} (v'[\eta_1](x)) 
+      +x_2\operatorname{Im} (v'[\eta_2](x)),
+\end{align}
+where
+\begin{align*} 
+\DD[\eeta](\xx)=(u_1(\xx),u_2(\xx)), \,\, 
+\xx=x_1+x_2, \,\,
+\tau_1=(\eta_1+i\eta_2)\frac{\Re \, n}{n}, \text{ and }
+\tau_2=(\eta_1+i\eta_2)\frac{\operatorname{Im} n}{n}.
+\end{align*}
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 of of the double-layer potential velocity is
+{\color{red}
 \begin{align}
-  \nabla\D[\eeta](\xx) = \frac{1}{2\pi}\nabla\int_{\Gamma}
-    &\frac{\nn}{\rho^2}(\rr \cdot \eeta)ds_\yy +
-  \frac{1}{2\pi}\nabla\nabla\int_{\Gamma}
-    \frac{\rr \cdot \nn}{\rho^2}({\yy} \cdot\eeta) ds_y \\
-  &- \frac{1}{2\pi} \nabla x_1 \nabla \int_{\Gamma}
-      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
-  \frac{1}{2\pi} \nabla x_2 \nabla \int_{\Gamma}
-      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy.
+ \nabla\D[\eeta] (\xx)=
+\left[
+\begin{matrix}
+\displaystyle\frac{\partial u_1(\xx)}{x_1} & \displaystyle\frac{\partial u_1(\xx)}{x_2}\\ \\
+\displaystyle\frac{\partial u_2(\xx)}{x_1} & \displaystyle\frac{\partial u_2(\xx)}{x_2}
+\end{matrix}
+\right],
 \end{align}
+where 
+\begin{align}
+\frac{\partial u_1(\xx)}{x_1}&= \Re (v'[\tau_1](x)) + \Re (v''[\yy\cdot\eeta](x)) 
+           -\Re (v'[\eta_1](x)) -x_1\Re (v''[\eta_1](x))-x_2\Re (v''[\eta_2](x)),\\
+\frac{\partial u_1(\xx)}{x_2}&= - \operatorname{Im} (v'[\tau_1](x)) 
+      - \operatorname{Im} (v''[\yy\cdot\eeta](x)) 
+       +x_1\operatorname{Im} (v''[\eta_1](x)) 
+       -\Re (v'[\eta_2](x))
+      +x_2\operatorname{Im} (v''[\eta_2](x)),\\
+\frac{\partial v_1(\xx)}{x_1}&= \Re (v'[\tau_2](x)) 
+      -\operatorname{Im} (v''[\yy\cdot\eeta](x)) 
+       +\operatorname{Im} (v'[\eta_1](x))
+       +x_1\operatorname{Im} (v''[\eta_1](x)) 
+      +x_2\operatorname{Im} (v''[\eta_2](x)),\\
+\frac{\partial v_2(\xx)}{x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 
+      -\Re (v''[\yy\cdot\eeta](x)) 
+       +x_1\Re (v''[\eta_1](x)) 
+      +\operatorname{Im} (v'[\eta_2](x)
+      +x_2\operatorname{Im} (v''[\eta_2](x)).
+\end{align}
+}
+%\begin{align}
+%  \nabla\D[\eeta](\xx) = \frac{1}{2\pi}\nabla\int_{\Gamma}
+%    &\frac{\nn}{\rho^2}(\rr \cdot \eeta)ds_\yy +
+%  \frac{1}{2\pi}\nabla\nabla\int_{\Gamma}
+%    \frac{\rr \cdot \nn}{\rho^2}({\yy} \cdot\eeta) ds_y \\
+%  &- \frac{1}{2\pi} \nabla x_1 \nabla \int_{\Gamma}
+%      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
+%  \frac{1}{2\pi} \nabla x_2 \nabla \int_{\Gamma}
+%      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy.
+%\end{align}
 Then, the deformation tensor can be written in terms of Cauchy integrals

### 2019-05-02 docs/transport/erosion_transport.tex
correct an error in tranposrt paper
doing tranposrt paper

@@
 \DD[\eeta](\xx)=(u_1(\xx),u_2(\xx)), \,\, 
-\xx=x_1+x_2, \,\,
+\xx=(x_1,x_2), \,\,
 \tau_1=(\eta_1+i\eta_2)\frac{\Re \, n}{n}, \text{ and }
@@
       +x_2\operatorname{Im} (v''[\eta_2](x)),\\
-\frac{\partial v_1(\xx)}{x_1}&= \Re (v'[\tau_2](x)) 
+\frac{\partial u_2(\xx)}{x_1}&= \Re (v'[\tau_2](x)) 
       -\operatorname{Im} (v''[\yy\cdot\eeta](x)) 
@@
       +x_2\operatorname{Im} (v''[\eta_2](x)),\\
-\frac{\partial v_2(\xx)}{x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 
+\frac{\partial u_2(\xx)}{x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 
       -\Re (v''[\yy\cdot\eeta](x)) 
@@
       +\operatorname{Im} (v'[\eta_2](x)
-      +x_2\operatorname{Im} (v''[\eta_2](x)).
+      +x_2\Re (v''[\eta_2](x)).
 \end{align}
@@
 \begin{align}
-  v(x) \approx \frac{\sum_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
-    {\sum_{j=1}^N \frac{1}{y_j-x}w_j},  \qquad
-  v'(x) \approx \frac{\sum_{j=1}^N \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
-    {\sum_{j=1}^N \frac{1}{y_j-x}w_j}, 
+  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
+    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j},  \qquad
+  v'(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
+    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
 \end{align}
@@
 identities
+{\color{red}
 \begin{alignat}{3}
   0 &= \frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{v^-(y)-v(x)}{y-x} dy, &&x \in \Omega, \\
+    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3}, &&x \in \Omega, \\
   0 &= \frac{1}{2\pi i}\int_{\Gamma}
     \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
-    {(y-x)^3} dy, \quad &&x \in \Omega^c.
+    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
 \end{alignat}
+and the quadrature formulations are
+\begin{alignat}{3}
+  v''(x) &\approx
+    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
+    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
+  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
+    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
+    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
+\end{alignat}
+where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
+
+}
 
@@
   \item Efficiently find points that are too close for trapezoid
+
+{\color{red}
+To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
+Let $L_w$ be the length of the boundary of wall and $L_{b}$ be length of the boundary of body where $b=1, \cdots, M$.
+Here are the criteria to see if two points are too close for trapezoid.
+For criterion of wall to body,  let $d$ be the minimum distance between wall to a point $x_i$ on the body $b$, we define they are too close when
+$$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
+where $\alpha_1$ is a constant. 
+For criterion between two bodies, let $d$ be the minimum distance between a point $y_j$ on the body $b_1$ to a point $x_i$ on the body $b_2$, we define they are too close when
+$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_1}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
+where $\alpha_2$ is a constant.
+
+}
   \item Subtract off trapezoid rule directly

### 2019-05-02 docs/transport/erosion_transport.tex
doing tranposrt paper

@@
   0 &= \frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3}, &&x \in \Omega, \\
+    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
   0 &= \frac{1}{2\pi i}\int_{\Gamma}
@@
   v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
-    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
+    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
     , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
@@
 \label{sec:fmm}
+{\color{red}
+To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
+}
 \begin{itemize}
   \item Apply trapezoid rule as a first pass
+
+{\color{red} We use the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} with trapezoid rule to calculate the double-layer potential.
+}
   \item Efficiently find points that are too close for trapezoid
@@
 {\color{red}
-To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
-Let $L_w$ be the length of the boundary of wall and $L_{b}$ be length of the boundary of body where $b=1, \cdots, M$.
+ Let $L_w$ be the length of the outer boundary and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$.
 Here are the criteria to see if two points are too close for trapezoid.
-For criterion of wall to body,  let $d$ be the minimum distance between wall to a point $x_i$ on the body $b$, we define they are too close when
+For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to wall if
 $$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
 where $\alpha_1$ is a constant. 
-For criterion between two bodies, let $d$ be the minimum distance between a point $y_j$ on the body $b_1$ to a point $x_i$ on the body $b_2$, we define they are too close when
-$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_1}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
+For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
+$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
 where $\alpha_2$ is a constant.
@@
 \end{itemize}
+{\color{red} Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency?}
 

### 2019-05-02 docs/transport/erosion_transport.tex
doing in tranposrt paper

@@
 \begin{matrix}
-\displaystyle\frac{\partial u_1(\xx)}{x_1} & \displaystyle\frac{\partial u_1(\xx)}{x_2}\\ \\
-\displaystyle\frac{\partial u_2(\xx)}{x_1} & \displaystyle\frac{\partial u_2(\xx)}{x_2}
+\displaystyle\frac{\partial u_1(\xx)}{\partial x_1} & 
+\displaystyle\frac{\partial u_1(\xx)}{\partial x_2}\\ \\
+\displaystyle\frac{\partial u_2(\xx)}{\partial x_1} & 
+\displaystyle\frac{\partial u_2(\xx)}{\partial x_2}
 \end{matrix}
@@
 \begin{align}
-\frac{\partial u_1(\xx)}{x_1}&= \Re (v'[\tau_1](x)) + \Re (v''[\yy\cdot\eeta](x)) 
+\frac{\partial u_1(\xx)}{\partial x_1}&= \Re (v'[\tau_1](x)) + \Re (v''[\yy\cdot\eeta](x)) 
            -\Re (v'[\eta_1](x)) -x_1\Re (v''[\eta_1](x))-x_2\Re (v''[\eta_2](x)),\\
-\frac{\partial u_1(\xx)}{x_2}&= - \operatorname{Im} (v'[\tau_1](x)) 
+\frac{\partial u_1(\xx)}{\partial x_2}&= - \operatorname{Im} (v'[\tau_1](x)) 
       - \operatorname{Im} (v''[\yy\cdot\eeta](x)) 
@@
       +x_2\operatorname{Im} (v''[\eta_2](x)),\\
-\frac{\partial u_2(\xx)}{x_1}&= \Re (v'[\tau_2](x)) 
+\frac{\partial u_2(\xx)}{\partial x_1}&= \Re (v'[\tau_2](x)) 
       -\operatorname{Im} (v''[\yy\cdot\eeta](x)) 
@@
       +x_2\operatorname{Im} (v''[\eta_2](x)),\\
-\frac{\partial u_2(\xx)}{x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 
+\frac{\partial u_2(\xx)}{\partial x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 
       -\Re (v''[\yy\cdot\eeta](x)) 
@@
 Here are the criteria to see if two points are too close for trapezoid.
-For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to wall if
+For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to outer boundary if
 $$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$

### 2019-05-06 docs/transport/erosion_transport.tex
doing in tranposrt paper

@@
 \label{sec:fmm}
+
 {\color{red}
+To numerically approach the nearly singular integraton by using Barycentric quadrature rule,
+
 To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
@@
 For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to outer boundary if
-$$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
+\begin{equation}\label{eqn:Cw2b}
+d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}
+\end{equation}
 where $\alpha_1$ is a constant. 
 For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
-$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
+\begin{equation}\label{eqn:Cb2b}
+d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
+\end{equation}
 where $\alpha_2$ is a constant.
@@
   \item Add on Barycentric directly
+
+{\color{red} \item Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency
+
+To find the suitable values of $\alpha_1$ and $\alpha_2$ in~\eqref{eqn:Cw2b} and \eqref{eqn:Cb2b}, we set $\alpha_1=\alpha_2=1, 2, 3$, and $4$ to test the criteria on a 20-body problem with $N_\out = 1024$ and $N_\iin = 128, 256$, and $512$.
+To check the accuracy of the simulations, we use (?)
+To see how efficient our code is, we record the cpu time for each step.
+
+}
 \end{itemize}
-{\color{red} Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency?}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the resolution}
+{\color{red} We first consider a circular body in a shear flow.
+The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners.
+The velocity of flow form the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$.
+Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the initial minimum distance from body to wall.
+To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.
 
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{20 nearly touching bodies}
-
+{\color{red} To 
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-05-06 docs/transport/erosion_transport.tex
doing in tranposrt paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Barcyentric Quadrature for $v''(x)$}
+\subsection{Barycentric Quadrature for $v''(x)$}
 In order to simulate erosion, we require the deformation gradient which
@@
 {\color{red}
-To numerically approach the nearly singular integraton by using Barycentric quadrature rule,
+By using Barycentric quadrature rule to approach integrations, we get a reasonable(?) double-layer potential and quantities of interest at target points but it requires $\mathcal{O}(N^2)$ operations per target point which is computational expensive if we impose it on all the target points.
+In order to accelerate the process and keep the accuracy, it is a compromise that we use Barycentric quadrature rule to approach the nearly singular integratons but apply trapezoid rule when the target point is far from source points.
 
 To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
+The following is the four-step fast summation methods.
 }
@@
   \item Add on Barycentric directly
-
-{\color{red} \item Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency
+\end{itemize}
+{\color{red}  (Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency)
 
 To find the suitable values of $\alpha_1$ and $\alpha_2$ in~\eqref{eqn:Cw2b} and \eqref{eqn:Cb2b}, we set $\alpha_1=\alpha_2=1, 2, 3$, and $4$ to test the criteria on a 20-body problem with $N_\out = 1024$ and $N_\iin = 128, 256$, and $512$.
-To check the accuracy of the simulations, we use (?)
+To check the accuracy of the simulations, we use the solution calculated by \todo[inline]{what method} to \todo[inline]{...}
 To see how efficient our code is, we record the cpu time for each step.
@@
 }
-\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the resolution}
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
+\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
+\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
+\caption{A single body eroding in Stokes flow.
+Color indicates the local shear stress on the body.
+In this simulation, we use three the minimum body-to-wall initial distance $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
+\label{01bodseq} 
+\end{center}
+\end{figure}
 {\color{red} We first consider a circular body in a shear flow.
@@
 The velocity of flow form the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$.
-Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the initial minimum distance from body to wall.
+Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number of discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the minimum initial distance from body to wall.
 To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.

### 2019-05-07 docs/transport/erosion_transport.tex
doing the transport paper

@@
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
-
+\usepackage{float}
 \input{preambles.tex}
@@
 \caption{A single body eroding in Stokes flow.
-Color indicates the local shear stress on the body.
-In this simulation, we use three the minimum body-to-wall initial distance $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
-\label{01bodseq} 
+Color indicates the shear stress on the body.
+In this simulation, we use three minimum body-to-wall initial distances $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
+\label{} 
 \end{center}
 \end{figure}
-{\color{red} We first consider a circular body in a shear flow.
+{\color{red} We first consider a single circular body in a shear flow.
 The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners.
-The velocity of flow form the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$.
+The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$.
 Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number of discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the minimum initial distance from body to wall.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_1}
+\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_101}\\
+
+\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_201}
+\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
+\caption{Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition.
+The color is the vorticity of fluid.
+The 4 snapshots are evenly spaced in time.
+In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps $ and $\sigma $.}
+\label{} 
+\end{center}
+\end{figure}
 \subsection{20 nearly touching bodies}
-{\color{red} To 
+{\color{red} 
+By using Barycentric quadrature rule, we are able to capture the details in the fluid when wall and bodies or body and bodies are close to each other.
+The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow.
+The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners.
+The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$.
+The number of discretization points $N_\iin$ on the bodies is 256 and the number of discretization points $N_\out$ on the outer boundary is 1024.
 }
+
+\begin{figure}[H]
+\begin{center}
+\caption{The trajectories of tracers in the fluid with 20 bodies. The 6 snapshots are evenly spaced in time.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\caption{The tortuosity of the 20 nearly touching bodies}
+\end{center}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{50 nearly touching bodies}
-
+{\color{red}
+The first nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-05-08 docs/transport/erosion_transport.tex
add new figs of the transport paper

@@
 \begin{center}
-\caption{The trajectories of tracers in the fluid with 20 bodies. The 6 snapshots are evenly spaced in time.}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b30}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b60}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b90}\\
+
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b120}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b150}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b180}\\
+
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270}
+\caption{The trajectories of tracers in the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.}
 \end{center}
@@
 {\color{red}
-The first nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
+The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
 }

### 2019-05-08 docs/transport/erosion_transport.tex
doing the transport paper

@@
 The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$.
-Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number of discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the minimum initial distance from body to wall.
+Let the initial radius of the body be $r$, the initial length of the body be $L$, $N_\iin$ and $N_\out$ be the number of discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the minimum initial distance from body to wall.
 To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.
@@
 \includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
-\caption{Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition.
+\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition.
 The color is the vorticity of fluid.
 The 4 snapshots are evenly spaced in time.
-In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps $ and $\sigma $.}
-\label{} 
+In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.}
 \end{center}
@@
 The number of discretization points $N_\iin$ on the bodies is 256 and the number of discretization points $N_\out$ on the outer boundary is 1024.
-}
+
+The snapshots of the process of 20 nearly touching bodies eroding are in Fig.~\ref{fig:Eroding20vort}. 
+We place some bodies to nearly contact not only one another but also the outer boundary.
+For example, bodies 1, 6, 13, and 15 are very close to outer boundary.
+In~\cite{qua-moo2018} we reported the quick expanding space at the narrow channel between neighboring bodies, the developing flat faces at the sites of near contact, and bodies vanishing.
+In this nearly touching bodies structure, we also observe these phenomena but with more new details.
+For the speed of expanding space at the narrow channel, we see some narrow channels do expand faster than other wider channels.
+For example, the spacing between bodies 14 \& 18 is smaller than the spacing between bodies
+ 7 \& 14 initially and the former one is comparable to the latter one by the second frame.
+But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9.
+We could find the explanation from the tracer test in Fig.~\ref{fig:Eroding20tracer}.
+Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally.
+If the trajectory of tracer }
 
@@
 \includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270}
-\caption{The trajectories of tracers in the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.}
+\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in the fluid with 20 bodies.
+The 9 snapshots are evenly spaced in time.
+The tracers are evenly spread in the $x_2-$direction and released at $x_1=-1$.}
 \end{center}
@@
 The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
+}
+
+\subsection{100 bodies}
+{\color{red}
+This case is 100 bodies in a Hagen-Poiseuille flow.
 }

### 2019-05-08 docs/transport/erosion_transport.tex
working on early sections

--- 2019-05-08 docs/transport/erosion_transport.tex
@@
 
-\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}} \newcommand{\secref}[1]{\ref{#1}}
-\newcommand{\Cdb}{\mbox{$\mathbb{C}$}}
-\newcommand{\Rdb}{\mbox{$\mathbb{R}$}}
-
-\newcommand{\D}{\mbox{${\mathcal D}$}}
-
-\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
-\usepackage{float}
 \input{preambles.tex}
@@
 % OTHER TITLE POSSIBILITIES
-% Viscous Erosion in Porous Media (change 'in' to 'of'?)
-% A fast and accurate method for viscous erosion of a 2D porous medium
-% A boundary-integral method for viscous erosion of a porous medium
-% A computational framework to simulate the viscous erosion of a porous medium
+% ???
 
@@
     \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
-    \eeta(\yy) ds_\yy,
+    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
+  \label{eqn:stokesDLP}
 \end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown
-density function.  The double-layer potential itself can not represent
-all solutions of the incompressible Stokes equations.  Therefore, we
-complete the integral equation formulation following the work of Power
-and Miranda~\cite{pow-mir1987}.  The completion depends on the
-Stokeslets and rotlets
+where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
+normal at $\yy$, and $\eeta$ is an unknown density function.  The Stokes
+double-layer potential can be as the sum of the Laplace double-layer
+potential and its gradient.  By identifying $\xx,\yy \in \RR^2$ with the
+points $x,y \in \CC$, the Laplace double-layer potential for a
+real-valued density function $\eta$ can also be written as the real part
+of the Cauchy integral
+\begin{align}
+  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
+    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy = 
+  \Re \left( \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x - y} \, dy \right).
+\end{align}
+Therefore, the Stokes double-layer potential can be written in terms of
+Cauchy integrals and its first derivative.  In addition, we also require
+expressions for the derivative of the velocity field which can be
+written in terms of a Cauchy integral and its first two derivatives.
+Therefore, we introduce the notation
+\begin{align}
+  \label{eqn:cauchy}
+  v[\eta](x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x - y} \, dy,  \quad
+  v'[\eta](x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{(x - y)^2} \, dy, \quad
+  v''[\eta](x) = \frac{1}{\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{(x - y)^3} \, dy.
+\end{align}
+To simplify notation, whenever it will not cause confusion, we exclude
+$\tau$ and instead write $v(x)$, $v'(x)$, and $v''(x)$.
+
+The Stokes double-layer potential itself can not represent all solutions
+of the incompressible Stokes equations.  Therefore, we complete the
+integral equation formulation following the work of Power and
+Miranda~\cite{pow-mir1987}.  The completion depends on the Stokeslets
+and rotlets
 \begin{align}
   S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
-    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \qquad
+    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \quad
   R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
@@
     \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
-    \NN_0(\eeta](\xx), \qquad \xx \in \bd\Omega, \\
-  \lambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
-    \eeta(\yy) ds_\yy \qquad \ell = 1,\ldots,M, \\
+    \NN_0(\eeta](\xx), \quad \xx \in \bd\Omega, \\
+  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
+    \eeta(\yy) ds_\yy \quad \ell = 1,\ldots,M, \\
   \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
-    (\yy - \cc_\ell)^\perp  \eeta(\yy) ds_\yy 
-    \qquad \ell = 1,\ldots,M.
+    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy) ds_\yy 
+    \quad \ell = 1,\ldots,M,
 \end{align}
-
-We will apply a quadrature rule that requires that the double-layer
-potential representations of the velocity, shear stress, pressure, and
-vorticity are written in terms of the Cauchy integral and its first two
-derivatives
-\begin{align}
-  \label{eqn:Cauchy}
-  v(x) &= \frac{1}{2\pi i} \int_\Gamma 
-    \frac{\tau(y)}{x - y} dy, \\
-  v'(x) &= -\frac{1}{2\pi i} \int_\Gamma 
-    \frac{\tau(y)}{(x - y)^2} dy, \\
-  v''(x) &= \frac{2}{2\pi i} \int_\Gamma 
-    \frac{\tau(y)}{(x - y)^3} dy.
-\end{align}
+where $\ff$ is the prescribed Dirichlet boundary condition of the
+velocity on the outer wall and eroding bodies.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Cauchy Integral Representation of the Velocity}
-The Stokes double-layer potential can be written as
+\subsection{Cauchy Integral Representation of the Double-Layer
+Potential}
+The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
+decomposed as
 \begin{align}
@@
     \frac{1}{2\pi} \int_{\Gamma} 
-      \frac{\nn}{\rho^2} (\rr \cdot \eeta) ds_\yy + 
+      \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
     \frac{1}{2\pi} \nabla \int_{\Gamma}
-      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta)ds_\yy \\
+      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
     &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
-      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
+      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
     \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
-      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy,
+      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
 \end{align}
-and this formulation is convenient since each of the integrals can be
-written as a Laplacian double-layer potential,
+All these integrals but the first are a gradient of a Laplace layer
+potential with the density functions $\eta_1$, $\eta_2$, and $\yy \cdot
+\eeta$.  In addition, each component of the first integral can be
+written as a Cauchy integral with a complex-valued
+densities~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
+potential can be written as five Cauchy integrals and their derivatives
+with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
+The individual velocity components are
 \begin{align}
-  \DD[\tau](\xx) = -\frac{1}{2\pi} \int_{\Gamma} \pderiv{}{\nn_\yy}
-    \log(\rho) \tau(\yy) ds_\yy.
-\end{align}
-Finally, by identifying $\RR^2$ with $\CC$, for purely real $\tau$, the
-Laplacian double-layer potential can be written as the real part of a
-Cauchy integral
-\begin{align}
-  \DD[\tau](x) = \Re (v(x)),
-  \qquad \text{where} \qquad
-  v(x) = \frac{1}{2\pi i} \int_\Gamma \frac{\tau(y)}{x - y} dy.
-\end{align}
-Therefore, the Stokes double-layer potential can be written as five
-Cauchy integrals and their derivatives with the density functions $\yy
-\cdot {\color{red}\eeta}$, $\eta_1$, and $\eta_2,$
-{\color{red}
-\begin{align}
- u_1(\xx)&= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
-           -x_1\Re (v'[\eta_1](x)) -x_2\Re (v'[\eta_2](x)),\\
- u_2(\xx)&= \Re (v[\tau_2](x)) - \operatorname{Im} (v'[\yy\cdot\eeta](x)) 
-       +x_1\operatorname{Im} (v'[\eta_1](x)) 
-      +x_2\operatorname{Im} (v'[\eta_2](x)),
-\end{align}
-where
-\begin{align*} 
-\DD[\eeta](\xx)=(u_1(\xx),u_2(\xx)), \,\, 
-\xx=(x_1,x_2), \,\,
-\tau_1=(\eta_1+i\eta_2)\frac{\Re \, n}{n}, \text{ and }
-\tau_2=(\eta_1+i\eta_2)\frac{\operatorname{Im} n}{n}.
-\end{align*}
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Cauchy Integral Representation of the Shear Stress}
-Since the rate of erosion is proportional to the shear stress, we also
-require the gradient of the Stokes double-layer potential $\nabla
-\DDD[\eeta](\xx)$.  Using the Cauchy integral formulation, the gradient
-of of the double-layer potential velocity is
-{\color{red}
-\begin{align}
- \nabla\D[\eeta] (\xx)=
-\left[
-\begin{matrix}
-\displaystyle\frac{\partial u_1(\xx)}{\partial x_1} & 
-\displaystyle\frac{\partial u_1(\xx)}{\partial x_2}\\ \\
-\displaystyle\frac{\partial u_2(\xx)}{\partial x_1} & 
-\displaystyle\frac{\partial u_2(\xx)}{\partial x_2}
-\end{matrix}
-\right],
+  u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
+           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)),\\
+  u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
+       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
 \end{align}
@@
 \begin{align} 
-\frac{\partial u_1(\xx)}{\partial x_1}&= \Re (v'[\tau_1](x)) + \Re (v''[\yy\cdot\eeta](x)) 
-           -\Re (v'[\eta_1](x)) -x_1\Re (v''[\eta_1](x))-x_2\Re (v''[\eta_2](x)),\\
-\frac{\partial u_1(\xx)}{\partial x_2}&= - \operatorname{Im} (v'[\tau_1](x)) 
-      - \operatorname{Im} (v''[\yy\cdot\eeta](x)) 
-       +x_1\operatorname{Im} (v''[\eta_1](x)) 
-       -\Re (v'[\eta_2](x))
-      +x_2\operatorname{Im} (v''[\eta_2](x)),\\
-\frac{\partial u_2(\xx)}{\partial x_1}&= \Re (v'[\tau_2](x)) 
-      -\operatorname{Im} (v''[\yy\cdot\eeta](x)) 
-       +\operatorname{Im} (v'[\eta_1](x))
-       +x_1\operatorname{Im} (v''[\eta_1](x)) 
-      +x_2\operatorname{Im} (v''[\eta_2](x)),\\
-\frac{\partial u_2(\xx)}{\partial x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 
-      -\Re (v''[\yy\cdot\eeta](x)) 
-       +x_1\Re (v''[\eta_1](x)) 
-      +\operatorname{Im} (v'[\eta_2](x)
-      +x_2\Re (v''[\eta_2](x)).
+  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
+  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
 \end{align}
-}
-%\begin{align}
-%  \nabla\D[\eeta](\xx) = \frac{1}{2\pi}\nabla\int_{\Gamma}
-%    &\frac{\nn}{\rho^2}(\rr \cdot \eeta)ds_\yy +
-%  \frac{1}{2\pi}\nabla\nabla\int_{\Gamma}
-%    \frac{\rr \cdot \nn}{\rho^2}({\yy} \cdot\eeta) ds_y \\
-%  &- \frac{1}{2\pi} \nabla x_1 \nabla \int_{\Gamma}
-%      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
-%  \frac{1}{2\pi} \nabla x_2 \nabla \int_{\Gamma}
-%      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy.
-%\end{align}
-Then, the deformation tensor can be written in terms of Cauchy integrals
-\todo[inline]{For S-H to fill in}
+and $n \in \CC$ is the complex representation of $\nn \in \RR^2$
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Cauchy Integral Representation of the Shear Stress}
+To compute the rate of erosion, we must compute the shear stress of the
+double-layer potential
 \begin{align}
-  \ssigma = \frac{1}{2} 
-    \left(\nabla \DDD[\eeta] + \nabla^T \DDD[\eeta] \right) 
-      \nn \cdot \ss = \ldots
+  \tau(\xx) = \left(\nabla \DDD[\eeta](\xx) + 
+    \nabla^T \DDD[\eeta](\xx) \right) \nn \cdot \ss,
 \end{align}
+where $\nn$ and $\ss$ are the unit normal and tangent vectors at $\xx$,
+respectively.  Each term of the gradient of the velocity field can be
+written in terms of Cauchy integrals as
+\todo[inline]{not clear enough how we got these equations.  Need to show
+how we do one of them and say the rest are calculated similarly.}
+\begin{align}
+  \pderiv{u_1}{x_1}(\xx) &= \Re (v'[\tau_1](x)) + 
+    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
+    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
+  \pderiv{u_1}{x_2}(\xx) &= - \Im (v'[\tau_1](x)) - 
+    \Im (v''[\yy\cdot\eeta](x)) + \Im (v''[\eta_1](x)) - 
+    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
+  \pderiv{u_2}{x_1}(\xx) &= \Re (v'[\tau_2](x)) - 
+    \Im (v''[\yy\cdot\eeta](x)) + \Im (v'[\eta_1](x)) +
+    x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
+  \pderiv{u_2}{x_2}(\xx) &= -\Im (v'[\tau_2](x)) - 
+    \Re (v''[\yy\cdot\eeta](x)) + x_1\Re (v''[\eta_1](x)) +
+    \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
+\end{align}
+\todo[inline]{S-H: last term seems to be missing an $x_1$.  Some of the
+other terms seem to be a bit off.  It might be partially my fault from
+when I updated some of the tex.}
 
@@
 \subsection{Cauchy Integral Representation of the Vorticity}
+Having calculated all derivatives of the double-layer potential, the
+vorticity can written in terms of Cauchy integrals.  In particular
+\begin{align}
+  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
+\end{align}
+\todo[inline]{For S-H to fill in}
 
@@
 \subsection{Cauchy Integral Representation of the Pressure}
+The pressure of the double-layer potential is
+\begin{align}
+  p(\xx) = -\frac{1}{\pi} \int_{\bd\Omega} \frac{1}{\rho^2}
+    \left(1 - 2 \frac{\rr \otimes \rr}{\rho^2} \right) \nn
+    \cdot \eeta(\yy) \, ds_\yy.
+\end{align}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A standard discretization of these equations approximates the
-double-layer potential with the trapezoid rule.  This quadrature rule is
-appropriate if the integrands are sufficiently smooth, where the
+We are interested in computing the velocity, shear stress, vorticity,
+and pressure of the Stokes double-layer potential.  We have shown that
+all these quantities can be written in terms of Cauchy integrals and its
+first two derivatives.  Therefore, we require quadrature methods to
+evaluate the expressions in equation~\eqref{eqn:cauchy}.  The trapezoid
+rule is appropriate if the integrands are sufficiently smooth, where the
 smoothness depends on the number of discretization points.  However,
 given a fixed resolution, if the target point $\xx$ is too close to $\bd
-\Omega$, the trapezoid rule becomes inaccurate and the overall method
-becomes unstable.  There have been a variety of near-singular
-integration schemes developed, and we extend a method first outlined by
-Barnett et al.~\cite{bar-wu-vee2015} which we will call the {\em
-Barycentric quadrature rule}.  Here, we briefly describe this quadrature
-method, and then derive a necessary extension to simulate erosion.
+\Omega$, the trapezoid rule becomes inaccurate and the overall method is
+unstable.  There have been a variety of near-singular integration
+schemes developed, and we extend a method first outlined by Barnett et
+al.~\cite{bar-wu-vee2015} which we will call the {\em Barycentric
+quadrature rule}.  Here, we briefly describe this quadrature method, and
+then derive a necessary extension to simulate erosion.
 
-Since we are able to write on all our quantities of interest in terms of
-a Cauchy integral and its derivatives, we only require a near-singular
-integration method for equation~\eqref{eqn:Cauchy}.  A quadrature scheme
-for $v(x)$, for a target point $x$, is
+The Barycentric quadrature rule starts with a general quadrature rule
+for $v(x)$
 \begin{align}
@@
 where $w_j$ are the quadrature weights and $y_j \in \Gamma$ are the
-quadrature nodes.  If the trapezoid rule is used, the quadrature rule
-has spectral accuracy.  However, for a fixed resolution $N$, the error
-grows without bound as $x$ approaches $\Gamma$.  As outline by Barnett
-et al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
+quadrature nodes.  We will use the trapezoid rule because of its
+superior accuracy when $x$ is sufficiently far from $\Gamma$.  However,
+for a fixed resolution $N$, the error grows without bound as $x$
+approaches $\Gamma$.  As outline by Barnett et
+al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
 Barycentric quadrature rule
@@
   v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
-    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j},  \qquad
-  v'(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
+    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}
+  \quad \text{and} \quad
+  v'(x) \approx \frac{\sum\limits_{j=1}^N 
+    \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
     {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
@@
 \subsection{Barycentric Quadrature for $v''(x)$}
-In order to simulate erosion, we require the deformation gradient which
-means that a quadrature rule for $v''(x)$ is required.  Using the same
-techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
-quadrature rule for the second derivative can be constructed using the
-identities
-{\color{red}
+While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
+developed~\cite{bar-wu-vee2015}, this work requires a similar quadrature
+rule for $v''(x)$.  We mimic the approach developed
+in~\cite{bar-wu-vee2015} by starting with the identities
+\todo[inline]{S-H: How do we get these identities?}
 \begin{alignat}{3}
@@
 \end{alignat}
+{\color{red}
 and the quadrature formulations are

### 2019-05-09 docs/transport/erosion_transport.tex
doing the transport paper

@@
   u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
-           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)),\\
+           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \label{eqn:cauchy1}\\
   u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
@@
     \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
-    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
+    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \label{eqn:pderiv1} \\
   \pderiv{u_1}{x_2}(\xx) &= - \Im (v'[\tau_1](x)) - 
-    \Im (v''[\yy\cdot\eeta](x)) + \Im (v''[\eta_1](x)) - 
-    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
+    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
+    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)),  \label{eqn:pderiv2}\\
   \pderiv{u_2}{x_1}(\xx) &= \Re (v'[\tau_2](x)) - 
@@
 \end{align}
+{\color{red}
+Here we derive the equations~\eqref{eqn:pderiv1}-\eqref{eqn:pderiv2} 
+and the other two are similar.
+To derive equations~\eqref{eqn:pderiv1} and \eqref{eqn:pderiv2}, 
+we need to apply the fact that if a real function $u$ is equivalent to 
+the real part of a complex varaible function $f$, 
+then we have $\nabla u=(\Re(f'),-\Im(f'))$.
+Let $f_1(x)= v[\tau_1](x)$, $f_2(x)=v'[\yy\cdot\eeta](x)$, $f_3(x)=v'[\eta_1](x)$,
+and $f_4(x)= v'[\eta_2](x)$. Then we can rewrite equation~\eqref{eqn:cauchy1}
+\begin{align*}
+u_1(\xx)&= u_{11}(\xx) +  u_{12}(\xx) +u_{13}(\xx)+u_{14}(\xx) \\
+&=\Re (f_1(x)) + \Re (f_2(x))-x_1\Re (f_3(x)) - x_2\Re (f_4(x)).
+\end{align*}
+To get the gradient of $u_1(x)$, we have
+\begin{align*}
+\nabla u_1(x)&= \nabla u_{11}(x)+\nabla  u_{12}(x) 
++\nabla u_{13}(x)+\nabla u_{14}(x) \\ \\
+&=\begin{bmatrix}
+\Re(f_1'(x))\\ \\
+-\Im(f_1'(x))
+\end{bmatrix}+
+\begin{bmatrix}
+\Re(f_2'(x))\\ \\
+-\Im(f_2'(x))
+\end{bmatrix}
++
+\begin{bmatrix}
+-\Re(f_3(x))-x_1\Re(f_3'(x))\\ \\
+x_1\Im(f_3'(x))
+\end{bmatrix}
++
+\begin{bmatrix}
+-x_2\Re(f_4'(x))\\ \\
+-\Re(f_4(x))+x_2\Im(f_4'(x))
+\end{bmatrix}\\ \\
+&=
+\begin{bmatrix}
+\Re (v'[\tau_1](x)) + 
+    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
+    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x))\\ \\
+- \Im (v'[\tau_1](x)) - 
+    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
+    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x))
+\end{bmatrix}.
+\end{align*}
+
+}
 \todo[inline]{S-H: last term seems to be missing an $x_1$.  Some of the
@@
 vorticity can written in terms of Cauchy integrals.  In particular
+{\color{red}
 \begin{align}
   \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
+\Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
+ + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)).
 \end{align}
+}
 \todo[inline]{For S-H to fill in}
@@
 rule for $v''(x)$.  We mimic the approach developed
-in~\cite{bar-wu-vee2015} by starting with the identities
+in~\cite{bar-wu-vee2015} by starting with the Cauchy integral identities
+{\color{red}
+\begin{alignat}{3}
+1 &= \frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
+\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
+    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
+\end{alignat}
+and the contour integral 
+\begin{align}\label{eqn:cauchyId3}
+0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
+\end{align}
+Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
+the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
+\begin{align*}
+0 &= \frac{1}{2\pi i} \int_{\Gamma}
+    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
+&= \frac{1}{2\pi i} \int_{\Gamma}
+    \frac{2v^-(y)}{(y - x)^3} \, dy 
+-v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{1}{y-x} dy\\
+&= \frac{1}{2\pi i} \int_{\Gamma}
+    \frac{2v^-(y)}{(y - x)^3} \, dy 
+-\frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
+-\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
+-\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
+&= \frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
+\end{align*}
+}
 \todo[inline]{S-H: How do we get these identities?}

### 2019-05-10 docs/transport/erosion_transport.tex
working on early sections of paper

--- 2019-05-08 docs/transport/erosion_transport.tex
@@
 \label{s:formulation}
-Continuing on our previous work~\cite{qua-moo2018}, we use a completed
+Continuing with our previous work~\cite{qua-moo2018}, we use a completed
 double-layer potential formulation for the velocity $\uu$.  The
@@
 All these integrals but the first are a gradient of a Laplace layer
-potential with the density functions $\eta_1$, $\eta_2$, and $\yy \cdot
-\eeta$.  In addition, each component of the first integral can be
-written as a Cauchy integral with a complex-valued
-densities~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
+potential.  In addition, each component of the first integral can be
+written as a Cauchy integral with a complex-valued density
+function~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
 potential can be written as five Cauchy integrals and their derivatives
@@
 \begin{align}
+  \label{eqn:cauchy1}
   u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
-           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)),\\
+           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
   u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
@@
 \end{align}
-and $n \in \CC$ is the complex representation of $\nn \in \RR^2$
+and $n \in \CC$ is the complex representation of the outward unit normal
+$\nn \in \RR^2$
 
@@
     \nabla^T \DDD[\eeta](\xx) \right) \nn \cdot \ss,
+\end{align} where $\nn$ and $\ss$ are the unit normal and tangent
+vectors at $\xx$, respectively.  Each term of the gradient of the
+velocity field can be written in terms of Cauchy integrals.  For
+example,
+\begin{align}
+  \pderiv{u_1}{x_2} &= \Re(iv'[\tau_1](x)) + 
+      \Re(i v''[\yy \cdot \nn](x)) -
+      x_1\Re(i v''[\eta_1](x))  -
+      \Re(v'[\eta_2](x)) - x_2 \Re(iv''[\eta_2](x)) \\
+    &= -\Im(v''[\tau_1](x)) - 
+      \Im(v''[\yy \cdot \nn](x)) +
+      x_1\Im(v''[\eta_1](x)) -
+      \Re(v'[\eta_2](x)) + x_2 \Im(v''[\eta_2](x)).
 \end{align}
-where $\nn$ and $\ss$ are the unit normal and tangent vectors at $\xx$,
-respectively.  Each term of the gradient of the velocity field can be
-written in terms of Cauchy integrals as
-\todo[inline]{not clear enough how we got these equations.  Need to show
-how we do one of them and say the rest are calculated similarly.}
+Similarly, the other three components of $\nabla \DDD[\eeta]$ can be
+calculated
 \begin{align}
-  \pderiv{u_1}{x_1}(\xx) &= \Re (v'[\tau_1](x)) + 
+  \pderiv{u_1}{x_1} &= \Re (v'[\tau_1](x)) + 
     \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
     x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
-  \pderiv{u_1}{x_2}(\xx) &= - \Im (v'[\tau_1](x)) - 
-    \Im (v''[\yy\cdot\eeta](x)) + \Im (v''[\eta_1](x)) - 
+  \pderiv{u_1}{x_2} &= - \Im (v'[\tau_1](x)) - 
+    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
     \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
-  \pderiv{u_2}{x_1}(\xx) &= \Re (v'[\tau_2](x)) - 
+  \pderiv{u_2}{x_1} &= \Re (v'[\tau_2](x)) - 
     \Im (v''[\yy\cdot\eeta](x)) + \Im (v'[\eta_1](x)) +
     x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
-  \pderiv{u_2}{x_2}(\xx) &= -\Im (v'[\tau_2](x)) - 
+  \pderiv{u_2}{x_2} &= -\Im (v'[\tau_2](x)) - 
     \Re (v''[\yy\cdot\eeta](x)) + x_1\Re (v''[\eta_1](x)) +
@@
 \end{align}
-\todo[inline]{S-H: last term seems to be missing an $x_1$.  Some of the
-other terms seem to be a bit off.  It might be partially my fault from
-when I updated some of the tex.}
 
@@
 Having calculated all derivatives of the double-layer potential, the
-vorticity can written in terms of Cauchy integrals.  In particular
+vorticity can written in terms of Cauchy integrals.  In particular,
 \begin{align}
   \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
+\Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
+ + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)).
 \end{align}
-\todo[inline]{For S-H to fill in}
 
@@
 %
+%
+%{\color{red}
+%Here we derive the equations~\eqref{eqn:pderiv1}-\eqref{eqn:pderiv2} 
+%and the other two are similar.
+%To derive equations~\eqref{eqn:pderiv1} and \eqref{eqn:pderiv2}, 
+%we need to apply the fact that if a real function $u$ is equivalent to 
+%the real part of a complex varaible function $f$, 
+%then we have $\nabla u=(\Re(f'),-\Im(f'))$.
+%Let $f_1(x)= v[\tau_1](x)$, $f_2(x)=v'[\yy\cdot\eeta](x)$, $f_3(x)=v'[\eta_1](x)$,
+%and $f_4(x)= v'[\eta_2](x)$. Then we can rewrite equation~\eqref{eqn:cauchy1}
+%\begin{align*}
+%u_1(\xx)&= u_{11}(\xx) +  u_{12}(\xx) +u_{13}(\xx)+u_{14}(\xx) \\
+%&=\Re (f_1(x)) + \Re (f_2(x))-x_1\Re (f_3(x)) - x_2\Re (f_4(x)).
+%\end{align*}
+%To get the gradient of $u_1(x)$, we have
+%\begin{align*}
+%\nabla u_1(x)&= \nabla u_{11}(x)+\nabla  u_{12}(x) 
+%+\nabla u_{13}(x)+\nabla u_{14}(x) \\ \\
+%&=\begin{bmatrix}
+%\Re(f_1'(x))\\ \\
+%-\Im(f_1'(x))
+%\end{bmatrix}+
+%\begin{bmatrix}
+%\Re(f_2'(x))\\ \\
+%-\Im(f_2'(x))
+%\end{bmatrix}
+%+
+%\begin{bmatrix}
+%-\Re(f_3(x))-x_1\Re(f_3'(x))\\ \\
+%x_1\Im(f_3'(x))
+%\end{bmatrix}
+%+
+%\begin{bmatrix}
+%-x_2\Re(f_4'(x))\\ \\
+%-\Re(f_4(x))+x_2\Im(f_4'(x))
+%\end{bmatrix}\\ \\
+%&=
+%\begin{bmatrix}
+%\Re (v'[\tau_1](x)) + 
+%    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
+%    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x))\\ \\
+%- \Im (v'[\tau_1](x)) - 
+%    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
+%    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x))
+%\end{bmatrix}.
+%\end{align*}

### 2019-05-10 docs/transport/erosion_transport.tex
worked on numerics

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We are interested in computing the velocity, shear stress, vorticity,
-and pressure of the Stokes double-layer potential.  We have shown that
-all these quantities can be written in terms of Cauchy integrals and its
-first two derivatives.  Therefore, we require quadrature methods to
-evaluate the expressions in equation~\eqref{eqn:cauchy}.  The trapezoid
-rule is appropriate if the integrands are sufficiently smooth, where the
-smoothness depends on the number of discretization points.  However,
-given a fixed resolution, if the target point $\xx$ is too close to $\bd
-\Omega$, the trapezoid rule becomes inaccurate and the overall method is
-unstable.  There have been a variety of near-singular integration
-schemes developed, and we extend a method first outlined by Barnett et
-al.~\cite{bar-wu-vee2015} which we will call the {\em Barycentric
-quadrature rule}.  Here, we briefly describe this quadrature method, and
-then derive a necessary extension to simulate erosion.
+We have shown that the velocity, shear stress, vorticity, and pressure
+of the double-layer potential can all be written in terms of Cauchy
+integrals and its first two derivatives.  Therefore, we require
+quadrature methods to evaluate the expressions in
+equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
+periodic, the Trapezoid rule has spectral accuracy.  However, the
+integrand is nearly singular if $x$ is close to $\bd\Omega$, and the
+quadrature error is arbitrarily large if the resolution $N$ is fixed.
+There have been a variety of near-singular integration schemes
+developed, and we extend a method first outlined by Barnett et
+al.~\cite{bar-wu-vee2015} which we call the {\em Barycentric quadrature
+rule}.  This method first uses the density function $\tau(y)$ to compute
+the boundary data of $v$, denoted by $v^-{y}$.  Then, it makes use
+of the identity
+\begin{align}
+  v(x) = \int_{\Gamma} \frac{v^{-}(y)}{y-x} \, dy, 
+  \quad x \in \Omega.
+\end{align}
 
-The Barycentric quadrature rule starts with a general quadrature rule
-for $v(x)$
+Here, we briefly describe this quadrature method, and then derive a
+necessary extension to simulate erosion.  The Barycentric quadrature
+rule starts with a quadrature rule with nodes $y_j \in \Gamma$ and
+weights $w_j$. We use the trapezoid rule because of its superior
+accuracy when $x$ is sufficiently far from $\Gamma$.  However, as $x$
+approaches $\Gamma$, the integrand becomes nearly singular and the
+quality of the trapezoid rule deteriorates. To eliminate the
+nearly-singular integrand, we use the identity
 \begin{align}
-  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^N 
-    w_j \frac{\tau(y_j)}{x - y_j},
+  \int_{\Gamma} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0.
 \end{align}
-where $w_j$ are the quadrature weights and $y_j \in \Gamma$ are the
-quadrature nodes.  We will use the trapezoid rule because of its
-superior accuracy when $x$ is sufficiently far from $\Gamma$.  However,
-for a fixed resolution $N$, the error grows without bound as $x$
-approaches $\Gamma$.  As outline by Barnett et
-al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
-Barycentric quadrature rule
+Then, even if $x$ is close to $\Gamma$, the integrand is no longer
+nearly-singular and the accuracy of the trapezoid rule is bounded
+independent of $x$.  A similar identity identity involving $v'(x)$ also
+holds.   Now, applying the spectrally accurate trapezoid rule, the
+quadrature error of the Barycentric quadrature rule
 \begin{align}
@@
     {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
+  \label{eqn:vvpQuadrature}
 \end{align}
-is used, where $x$ is a target point that is interior to $\Gamma$,
-and $v_j^-$ is the value of $v(y_j)$.  Modifications of this formula
-exist if $x$ is exterior to $\Gamma$.
+is uniformly bounded~\cite{bar-wu-vee2015}.  A slight modification of
+these formulae are applied if $x \in \Omega^{c}$.
 
@@
 rule for $v''(x)$.  We mimic the approach developed
-in~\cite{bar-wu-vee2015} by starting with the Cauchy integral identities
-{\color{red}
-\begin{alignat}{3}
-1 &= \frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
-\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
-    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
-\end{alignat}
-and the contour integral 
-\begin{align}\label{eqn:cauchyId3}
-0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
+in~\cite{bar-wu-vee2015}.  First, if $x \in \Omega$ and $n \in
+\mathbb{N}$, then 
+\begin{align}
+  \frac{1}{2\pi i}\int_{\Gamma} \frac{1}{(y-x)^n}\, dy = 
+  \left\{
+    \begin{array}{ll}
+      1, & n = 1, \\
+      0, & n > 1. \\
+    \end{array}
+  \right.
 \end{align}
-Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
-the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
-\begin{align*}
+Applying this identity to the Cauchy integral theorem for $v''(x)$, we
+have
+\begin{align}
   0 &= \frac{1}{2\pi i} \int_{\Gamma} 
-    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
+      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x) \\
     &= \frac{1}{2\pi i} \int_{\Gamma} 
-    \frac{2v^-(y)}{(y - x)^3} \, dy 
--v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{1}{y-x} dy\\
-&= \frac{1}{2\pi i} \int_{\Gamma}
-    \frac{2v^-(y)}{(y - x)^3} \, dy 
--\frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
--\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
--\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
-&= \frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
-\end{align*}
-}
-\todo[inline]{S-H: How do we get these identities?}
-\begin{alignat}{3}
-  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
-  0 &= \frac{1}{2\pi i}\int_{\Gamma}
-    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
-    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
-\end{alignat}
-{\color{red}
-and the quadrature formulations are
-\begin{alignat}{3}
-  v''(x) &\approx
-    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
-    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
+      \frac{2v^{-}(y)}{(y-x)^3}\,dy - 
+    \frac{1}{2\pi i} \int_{\Gamma} 
+      \frac{(y-x)^2 v''(x)}{(y-x)^3}\,dy -
+    \frac{1}{2\pi i} \int_{\Gamma} 
+      \frac{2v(x)}{(y-x)^3}\, dy -
+    \frac{1}{2\pi i} \int_{\Gamma} 
+      \frac{2(y-x)v'(x)}{(y-x)^3}\, dy \\
+    &= \frac{1}{2\pi i}
+      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
+      {(y-x)^3}\, dy.
+\end{align}
+Since we have constructed the integrand so that it is bounded for for
+all $x \in \Omega$, the quadrature error of the trapezoid rule is
+acceptable.  Applying the quadrature rule and solving for $v''(x)$, the
+Barycentric quadrature rule for the second derivative is
+\begin{align}
+  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
+    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
+    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}.
+\end{align}
+To compute $v(x)$ and $v'(x)$, the Barycentric quadrature rule in
+equation~\eqref{eqn:vvpQuadrature} is used. If $x \in \Omega^c$, the
+identity
+\begin{align}
+\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{(y-a)^{-1}}{y-x} dy, 
+\end{align}
+is used, and the resulting Barycentric quadrature formula is
+\begin{align}
   v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
-    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
-    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
-\end{alignat}
-where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
-
-}
+    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
+    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}.
+\end{align}
 
@@
 \label{sec:fmm}
+The Barycentric quadrature rule achieves acceptable accuracy for
+computing the velocity, shear stress, and vorticity.  However, applied
+naively, it requires $\mathcal{O}(N^2)$ operations to directly.  Since
+the shear stress must only be computed once per time step, and the
+vorticity is only used as a post-processing step, we accept the
+$\mathcal{O}(N^2)$ algorithm.  However, the velocity must be computed at
+every GMRES iteration, so a fast algorithm is used.
+
+To compute the velocity with $\mathcal{O}(N)$ operations, we start by
+using the trapezoid rule accelerated with the fast multipole method
+(FMM). Since the trapezoid rule is inaccurate when $x$ is close to
+$\Gamma$, we replace the trapezoid rule with the Barycentric quadrature
+rule for such points.
+
+This
+cost can be reduced to $\mathcal{O}(N)$ by applying the fast multipole
+method (FMM).  Rather than developing an FMM for layer potentials that
+involve high-order derivatives of the Green's functions, we
 
@@
 %\end{align*}
+
+%{\color{red}
+%\begin{alignat}{3}
+%1 &= \frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
+%\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
+%    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
+%\end{alignat}
+%and the contour integral 
+%\begin{align}\label{eqn:cauchyId3}
+%0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
+%\end{align}
+%Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
+%the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
+%\begin{align*}
+%0 &= \frac{1}{2\pi i} \int_{\Gamma}
+%    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
+%&= \frac{1}{2\pi i} \int_{\Gamma}
+%    \frac{2v^-(y)}{(y - x)^3} \, dy 
+%-v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{1}{y-x} dy\\
+%&= \frac{1}{2\pi i} \int_{\Gamma}
+%    \frac{2v^-(y)}{(y - x)^3} \, dy 
+%-\frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
+%-\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
+%-\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
+%&= \frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
+%\end{align*}
+%}
+%\todo[inline]{S-H: How do we get these identities?}
+%\begin{alignat}{3}
+%  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
+%  0 &= \frac{1}{2\pi i}\int_{\Gamma}
+%    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
+%    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
+%\end{alignat}
+%{\color{red}
+%and the quadrature formulations are
+%\begin{alignat}{3}
+%  v''(x) &\approx
+%    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
+%    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
+%  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
+%    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
+%    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
+%\end{alignat}
+%where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
+%
+%}

### 2019-05-11 docs/transport/erosion_transport.tex
doing the transport paper
small changes to notation

@@
   \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
-    \eeta(\yy) ds_\yy \quad \ell = 1,\ldots,M, \\
+    \eeta(\yy)\, ds_\yy \quad \ell = 1,\ldots,M, \\
   \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
-    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy) ds_\yy 
+    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy 
     \quad \ell = 1,\ldots,M,
@@
   \DDD[\eeta](\xx) &= 
-    \frac{1}{2\pi} \int_{\Gamma} 
+    \frac{1}{2\pi} \int_{\bd\Omega} 
       \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
-    \frac{1}{2\pi} \nabla \int_{\Gamma}
+    \frac{1}{2\pi} \nabla \int_{\bd\Omega}
       \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
-    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
+    &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
       \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
-    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
+    \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
       \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
@@
 \begin{align}
-  v(x) = \int_{\Gamma} \frac{v^{-}(y)}{y-x} \, dy, 
+  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
   \quad x \in \Omega.
@@
 necessary extension to simulate erosion.  The Barycentric quadrature
-rule starts with a quadrature rule with nodes $y_j \in \Gamma$ and
+rule starts with a quadrature rule with nodes $y_j \in \bd\Omega$ and
 weights $w_j$. We use the trapezoid rule because of its superior
-accuracy when $x$ is sufficiently far from $\Gamma$.  However, as $x$
-approaches $\Gamma$, the integrand becomes nearly singular and the
+accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, as $x$
+approaches $\bd\Omega$, the integrand becomes nearly singular and the
 quality of the trapezoid rule deteriorates. To eliminate the
@@
 \begin{align}
-  \int_{\Gamma} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0.
+  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0.
 \end{align}
-Then, even if $x$ is close to $\Gamma$, the integrand is no longer
+Then, even if $x$ is close to $\bd\Omega$, the integrand is no longer
 nearly-singular and the accuracy of the trapezoid rule is bounded
@@
 \begin{align}
-  \frac{1}{2\pi i}\int_{\Gamma} \frac{1}{(y-x)^n}\, dy = 
+  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
   \left\{
@@
 \begin{align}
-  0 &= \frac{1}{2\pi i} \int_{\Gamma} 
+  0 &= \frac{1}{2\pi i} \int_{\bd\Omega} 
       \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x) \\
-    &= \frac{1}{2\pi i} \int_{\Gamma} 
+    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
       \frac{2v^{-}(y)}{(y-x)^3}\,dy - 
-    \frac{1}{2\pi i} \int_{\Gamma} 
+    \frac{1}{2\pi i} \int_{\bd\Omega} 
       \frac{(y-x)^2 v''(x)}{(y-x)^3}\,dy -
-    \frac{1}{2\pi i} \int_{\Gamma} 
+    \frac{1}{2\pi i} \int_{\bd\Omega} 
       \frac{2v(x)}{(y-x)^3}\, dy -
-    \frac{1}{2\pi i} \int_{\Gamma} 
+    \frac{1}{2\pi i} \int_{\bd\Omega} 
       \frac{2(y-x)v'(x)}{(y-x)^3}\, dy \\
-    &= \frac{1}{2\pi i}
+    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
       \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
@@
 \begin{align}
-\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\Gamma} 
+\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
     \frac{(y-a)^{-1}}{y-x} dy, 
@@
 (FMM). Since the trapezoid rule is inaccurate when $x$ is close to
-$\Gamma$, we replace the trapezoid rule with the Barycentric quadrature
-rule for such points.
+$\bd\Omega$, we replace the trapezoid rule with the Barycentric
+quadrature rule for such points.
 

### 2019-05-11 docs/transport/erosion_transport.tex
added a todo for Bryan
worked on numerics

@@
 Therefore, we introduce the notation
+\todo[inline]{BQ: Need to discuss boundary data and how to get it from
+density $\eta$}
 \begin{align}
@@
       \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x) \\
-    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
-      \frac{2v^{-}(y)}{(y-x)^3}\,dy - 
-    \frac{1}{2\pi i} \int_{\bd\Omega} 
-      \frac{(y-x)^2 v''(x)}{(y-x)^3}\,dy -
-    \frac{1}{2\pi i} \int_{\bd\Omega} 
-      \frac{2v(x)}{(y-x)^3}\, dy -
-    \frac{1}{2\pi i} \int_{\bd\Omega} 
-      \frac{2(y-x)v'(x)}{(y-x)^3}\, dy \\
+%    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
+%      \frac{2v^{-}(y)}{(y-x)^3}\,dy - 
+%    \frac{1}{2\pi i} \int_{\bd\Omega} 
+%      \frac{(y-x)^2 v''(x)}{(y-x)^3}\,dy -
+%    \frac{1}{2\pi i} \int_{\bd\Omega} 
+%      \frac{2v(x)}{(y-x)^3}\, dy -
+%    \frac{1}{2\pi i} \int_{\bd\Omega} 
+%      \frac{2(y-x)v'(x)}{(y-x)^3}\, dy \\
     &= \frac{1}{2\pi i} \int_{\bd\Omega} 
@@
 computing the velocity, shear stress, and vorticity.  However, applied
-naively, it requires $\mathcal{O}(N^2)$ operations to directly.  Since
-the shear stress must only be computed once per time step, and the
-vorticity is only used as a post-processing step, we accept the
-$\mathcal{O}(N^2)$ algorithm.  However, the velocity must be computed at
-every GMRES iteration, so a fast algorithm is used.
+directly, it requires $\mathcal{O}(N^2)$ operations.  Since the shear
+stress must only be computed once per time step, and the vorticity is
+only used as a post-processing step, we accept the $\mathcal{O}(N^2)$
+algorithm.  However, the velocity must be computed at every GMRES
+iteration, which would make the overall method impractical without a
+fast algorithm.
 
@@
 using the trapezoid rule accelerated with the fast multipole method
-(FMM). Since the trapezoid rule is inaccurate when $x$ is close to
-$\bd\Omega$, we replace the trapezoid rule with the Barycentric
-quadrature rule for such points.
+(FMM) \todo[inline]{reference here}. For target points that are
+sufficiently far from $\bd\Omega$, the resulting velocity is
+sufficiently accurate.  However, the velocity at points that are too
+close to $\bd\Omega$ must be corrected.  For a general point $\xx$,
+\begin{align}
+  \vv(\xx) = \int_{\Gamma} D(\xx,\yy) \eeta(\yy)\, ds_\yy + 
+    \sum_{k=1}^{M} \int_{\gamma_k} D(\xx,\yy) \eeta(\yy)\, ds_\yy.
+\end{align}
+Assuming that $\xx$ is too close to $\gamma_i$, we first subtract the
+velocity contribution of $\vv(\xx)$ due to $\gamma_i$.  Then, the
+Barycentric quadrature rule is used to compute the velocity due to
+$\gamma_i$ with more accuracy.  This is correction is applied to all
+points that are close to an eroding body or the outer wall $\Gamma$.
 
-This
-cost can be reduced to $\mathcal{O}(N)$ by applying the fast multipole
-method (FMM).  Rather than developing an FMM for layer potentials that
-involve high-order derivatives of the Green's functions, we
+The same strategy of using the trapezoid rule and then correcting with
+the Barycentric quadrature is used to compute the shear stress on
+$\bd\Omega$ and vorticity in $\Omega$.  The trapezoid rule is applied
+with a direct summation, but this cost is only incurred once per time
+step, and the majority of the computational effort is still required to
+compute the velocity using the fast summation method.
+
+To determine if a point $\xx \in \gamma_i$ needs to be corrected with
+the Barycentric quadrature rule, we first estimate the proximity of
+$\xx$ to $\bd\Omega$.  The criteria depends on the length of the outer
+wall, $L_w$, the length of the eroding bodies $L_i$, $i=1,\ldots,M$, and
+the number of discretization points $N_\out$ and $N_\iin$.
 

### 2019-05-13 docs/transport/erosion_transport.tex
add modified figures of transport paper
making small changes

@@
 normal at $\yy$, and $\eeta$ is an unknown density function.  The Stokes
-double-layer potential can be as the sum of the Laplace double-layer
-potential and its gradient.  By identifying $\xx,\yy \in \RR^2$ with the
-points $x,y \in \CC$, the Laplace double-layer potential for a
-real-valued density function $\eta$ can also be written as the real part
-of the Cauchy integral
+double-layer potential can also be expressed as the sum of a Laplace
+double-layer potential 
 \begin{align}
   \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
-    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy = 
-  \Re \left( \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy \right).
+    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy
+\end{align}
+and its gradient.  By identifying $\xx,\yy \in
+\RR^2$ with the points $x,y \in \CC$, the Laplace double-layer potential
+for a real-valued density function $\eta$ can also be written as the
+real part of the Cauchy integral
+\begin{align}
+  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
+  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x - y} \, dy.
 \end{align}
 Therefore, the Stokes double-layer potential can be written in terms of
-Cauchy integrals and its first derivative.  In addition, we also require
+Cauchy integrals and its first derivative.  Rather than immediately
+applying a quadrature rule to compute $v(x)$, we will first compute the
+boundary data of $v(x)$ by applying the Sokhotski-Plemelj jump relation
+\begin{align}
+  v^{-}(x) = -\frac{1}{2} \eta(x) - \frac{1}{2\pi i} \text{PV}
+\end{align}
+
+In addition, we also require
 expressions for the derivative of the velocity field which can be

### 2019-05-13 docs/transport/erosion_transport.tex
do caption of Figure 2 in transport paper

@@
 \begin{center}
-\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_1}
-\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_101}\\
+\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
+\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\
 
-\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_201}
-\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
+\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
+\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
 \caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition.
@@
 The 4 snapshots are evenly spaced in time.
-In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.}
+In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
+In the forth snapshot, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
 \end{center}
@@
 Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally.
-If the trajectory of tracer }
+If the trajectories of tracer  }
 

### 2019-05-13 docs/transport/erosion_transport.tex
do the result section of transport paper

@@
 In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
-In the forth snapshot, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
+In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
 \end{center}
@@
 But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9.
-We could find the explanation from the tracer test in Fig.~\ref{fig:Eroding20tracer}.
-Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally.
-If the trajectories of tracer  }
+We could find the explanation from the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.
+Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.
+}
 

### 2019-05-13 docs/transport/erosion_transport.tex
do the result section of transport paper

@@
 The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. 
-Let the initial radius of the body be $r$, the initial length of the body be $L$, $N_\iin$ and $N_\out$ be the number of discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the minimum initial distance from body to wall.
-To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.
+Let the initial radius of the body be $r$, 
+the initial length of the body be $L$, $N_\iin$ and 
+$N_\out$ be the number of discretization points 
+on the body and wall respectively, 
+$h=L/N_\iin$ be the resolution mesh size of the body, 
+and $d$ be the minimum initial distance from body to wall. 
+To investigate the shape of eroding body when it is close to wall, 
+we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ 
+with respect to three different $d=h, h/2$, and $ h/10$.
 
@@
 {\color{red} 
-By using Barycentric quadrature rule, we are able to capture the details in the fluid when wall and bodies or body and bodies are close to each other.
+By using Barycentric quadrature rule, 
+we are able to capture the details in the fluid when wall and bodies or body and bodies 
+are close to each other. 
 The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
@@
 The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. 
-The number of discretization points $N_\iin$ on the bodies is 256 and the number of discretization points $N_\out$ on the outer boundary is 1024.
+The number of discretization points $N_\iin$ on the bodies is 256 and the number 
+of discretization points $N_\out$ on the outer boundary is 1024.
 
-The snapshots of the process of 20 nearly touching bodies eroding are in Fig.~\ref{fig:Eroding20vort}. 
-We place some bodies to nearly contact not only one another but also the outer boundary.
-For example, bodies 1, 6, 13, and 15 are very close to outer boundary.
-In~\cite{qua-moo2018} we reported the quick expanding space at the narrow channel between neighboring bodies, the developing flat faces at the sites of near contact, and bodies vanishing.
-In this nearly touching bodies structure, we also observe these phenomena but with more new details.
-For the speed of expanding space at the narrow channel, we see some narrow channels do expand faster than other wider channels.
-For example, the spacing between bodies 14 \& 18 is smaller than the spacing between bodies
- 7 \& 14 initially and the former one is comparable to the latter one by the second frame.
-But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9.
-We could find the explanation from the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.
-Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.
-}
+The snapshots of the process of 20 nearly touching bodies 
+eroding are in Fig.~\ref{fig:Eroding20vort}. 
+We place some bodies to nearly contact not only one another 
+but also the outer boundary. For example, bodies 1, 6, 13, and 15 
+are very close to outer boundary. In~\cite{qua-moo2018} 
+we reported the quick expanding space at the narrow channel 
+between neighboring bodies, the developing flat faces at the sites 
+of near contact, and bodies vanishing. In this nearly touching bodies 
+structure, we also observe these phenomena but with more new details.
+
+For the speed of expanding space at the narrow channel, we see some 
+narrow channels do expand faster than other wider channels. 
+For example, the spacing between bodies 14 \& 18 is smaller 
+than the spacing between bodies 7 \& 14 initially and the former one is 
+comparable to the latter one by the second frame. But there are some 
+small initial spacings that do not expand that much at all by the fourth frame, 
+for example between bodies 1 \& 6, 3 \& 9. 
+We could find the explanation from the vorticity of fluid 
+in Fig.~\ref{fig:Eroding20vort}. 
+Since the eroding velocity on the body is proportional to the 
+absolute value of vorticity in our erosion model,  
+then when the  absolute value of vorticity is small 
+there is not much erosion on the body. 
+In all four frames of Fig.~\ref{fig:Eroding20vort}, 
+the vorticity is relatively small between bodies 1 \& 6 and 3 \& 9.
+
+Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.  }
 

### 2019-05-13 docs/transport/erosion_transport.tex
do the result section of transport paper

@@
 
+Besides the channels between two bodies, there is a single channel
+
+For the flat faces at the sites of near contact, since we put the body be close to one another
+so we are able to see all the channels between two close bodies have flat faces. 
+Besides the channels between bodies, we also observe the flat faces on the bodies 
+which are close to the outer boundary. For example, we see the flat faces 
+on the top of bodies 1 \& 6 and the bottom of bodies 13 \& 15.
+
 Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.  }

### 2019-05-14 docs/transport/erosion_transport.tex
changes to section 2 of transport paper

--- 2019-05-13 docs/transport/erosion_transport.tex
@@
 \label{s:formulation}
-Continuing with our previous work~\cite{qua-moo2018}, we use a completed
+Continuing with our previous work~\cite{qua-moo2018}, we use a
 double-layer potential formulation for the velocity $\uu$.  The
@@
 \begin{align}
-  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
+  \uu(\xx) = \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
     \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
@@
 where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
-normal at $\yy$, and $\eeta$ is an unknown density function.  The Stokes
-double-layer potential can also be expressed as the sum of a Laplace
-double-layer potential 
+normal at $\yy$, and $\eeta$ is an unknown density function.  In
+Section~\ref{sec:DLPcomplex}, we show how the Stokes double-layer
+potential can also be expressed as the sum of a Laplacian double-layer
+potential 
 \begin{align}
@@
 \end{align}
-and its gradient.  By identifying $\xx,\yy \in
-\RR^2$ with the points $x,y \in \CC$, the Laplace double-layer potential
-for a real-valued density function $\eta$ can also be written as the
-real part of the Cauchy integral
+and its gradient.  Since the Laplacian double-layer potential can be
+written as a Cauchy integral
 \begin{align}
@@
   v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy.
+    \frac{\eta(y)}{x - y} \, dy,
+  \label{eqn:laplaceComplex}
 \end{align}
-Therefore, the Stokes double-layer potential can be written in terms of
-Cauchy integrals and its first derivative.  Rather than immediately
-applying a quadrature rule to compute $v(x)$, we will first compute the
-boundary data of $v(x)$ by applying the Sokhotski-Plemelj jump relation
+where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
+the Stokes double-layer potential can be written in terms of Cauchy
+integrals and its first derivative.  We also require the derivative of
+the Stokes double-layer potential which requires the second derivative
+of Cauchy integrals.
+
+We will be using quadrature formulae to compute $v$ and its derivatives
+that rely on the Cauchy integral theorem.  Since $v$ is holomorphic, its
+value only depends on its boundary data.  The boundary data satisfies
+the Sokhotski-Plemelj jump relation
 \begin{align}
-  v^{-}(x) = -\frac{1}{2} \eta(x) - \frac{1}{2\pi i} \text{PV}
+  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
 \end{align}
-
-In addition, we also require
-expressions for the derivative of the velocity field which can be
-written in terms of a Cauchy integral and its first two derivatives.
-Therefore, we introduce the notation
-\todo[inline]{BQ: Need to discuss boundary data and how to get it from
-density $\eta$}
+Once the boundary data of $v$ is computed, we have
 \begin{align}
   \label{eqn:cauchy}
-  v[\eta](x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy,  \quad
-  v'[\eta](x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{(x - y)^2} \, dy, \quad
-  v''[\eta](x) = \frac{1}{\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{(x - y)^3} \, dy.
+  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
+    \frac{v(y)}{y-x} \,dy, \quad
+  v'(x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^2} \, dy, \quad
+  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^3} \, dy.
 \end{align}
-To simplify notation, whenever it will not cause confusion, we exclude
-$\tau$ and instead write $v(x)$, $v'(x)$, and $v''(x)$.
+for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
+\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
+function defined in equation~\eqref{eqn:laplaceComplex}, and the
+derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
 
@@
 Potential}
+\label{sec:DLPcomplex}
 The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
@@
   \label{eqn:cauchy1}
-  u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
+  u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
            -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
-  u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
+  u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
        +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
 \end{align}
-where
+where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
 \begin{align} 
@@
   \pderiv{u_1}{x_2} &= \Re(iv'[\tau_1](x)) + 
-      \Re(i v''[\yy \cdot \nn](x)) -
+      \Re(i v''[y \cdot \eta](x)) -
       x_1\Re(i v''[\eta_1](x))  -
@@
     &= -\Im(v''[\tau_1](x)) - 
-      \Im(v''[\yy \cdot \nn](x)) +
+      \Im(v''[y \cdot \eta](x)) +
       x_1\Im(v''[\eta_1](x)) -
@@
   \pderiv{u_1}{x_1} &= \Re (v'[\tau_1](x)) + 
-    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
+    \Re (v''[y\cdot\eta](x)) - \Re (v'[\eta_1](x)) - 
     x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
   \pderiv{u_1}{x_2} &= - \Im (v'[\tau_1](x)) - 
-    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
+    \Im (v''[y\cdot\eta](x)) + x_1\Im (v''[\eta_1](x)) - 
     \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
   \pderiv{u_2}{x_1} &= \Re (v'[\tau_2](x)) - 
-    \Im (v''[\yy\cdot\eeta](x)) + \Im (v'[\eta_1](x)) +
+    \Im (v''[y\cdot\eta](x)) + \Im (v'[\eta_1](x)) +
     x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
   \pderiv{u_2}{x_2} &= -\Im (v'[\tau_2](x)) - 
-    \Re (v''[\yy\cdot\eeta](x)) + x_1\Re (v''[\eta_1](x)) +
+    \Re (v''[y\cdot\eta](x)) + x_1\Re (v''[\eta_1](x)) +
     \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
@@
 \begin{center}
-\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
-\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\
+\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_1}
+\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_101}\\
 
-\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
-\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
+\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_201}
+\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
 \caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition.
@@
 The 4 snapshots are evenly spaced in time.
-In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
-In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
+In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.}
 \end{center}
@@
 But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9.
-We could find the explanation from the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.
-Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.
-}
+We could find the explanation from the tracer test in Fig.~\ref{fig:Eroding20tracer}.
+Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally.
+If the trajectory of tracer }
 

### 2019-05-14 docs/transport/erosion_transport.tex

@@
 In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.}
+\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
+\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
+\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition.
+The color is the vorticity of fluid.
+The 4 snapshots are evenly spaced in time.
+In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
+In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
 \end{center}
@@
 The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. 
-The number of discretization points $N_\iin$ on the bodies is 256 and the number of discretization points $N_\out$ on the outer boundary is 1024.
+The number of discretization points $N_\iin$ on the bodies is 256 and the number 
+of discretization points $N_\out$ on the outer boundary is 1024.
 
-The snapshots of the process of 20 nearly touching bodies eroding are in Fig.~\ref{fig:Eroding20vort}. 
-We place some bodies to nearly contact not only one another but also the outer boundary.
-For example, bodies 1, 6, 13, and 15 are very close to outer boundary.
-In~\cite{qua-moo2018} we reported the quick expanding space at the narrow channel between neighboring bodies, the developing flat faces at the sites of near contact, and bodies vanishing.
-In this nearly touching bodies structure, we also observe these phenomena but with more new details.
-For the speed of expanding space at the narrow channel, we see some narrow channels do expand faster than other wider channels.
-For example, the spacing between bodies 14 \& 18 is smaller than the spacing between bodies
- 7 \& 14 initially and the former one is comparable to the latter one by the second frame.
-But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9.
-We could find the explanation from the tracer test in Fig.~\ref{fig:Eroding20tracer}.
-Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally.
-If the trajectory of tracer }
+The snapshots of the process of 20 nearly touching bodies 
+eroding are in Fig.~\ref{fig:Eroding20vort}. 
+We place some bodies to nearly contact not only one another 
+but also the outer boundary. For example, bodies 1, 6, 13, and 15 
+are very close to outer boundary. In~\cite{qua-moo2018} 
+we reported the quick expanding space at the narrow channel 
+between neighboring bodies, the developing flat faces at the sites 
+of near contact, and bodies vanishing. In this nearly touching bodies 
+structure, we also observe these phenomena but with more new details.
+
+For the speed of expanding space at the narrow channel, we see some 
+narrow channels do expand faster than other wider channels. 
+For example, the spacing between bodies 14 \& 18 is smaller 
+than the spacing between bodies 7 \& 14 initially and the former one is 
+comparable to the latter one by the second frame. But there are some 
+small initial spacings that do not expand that much at all by the fourth frame, 
+for example between bodies 1 \& 6, 3 \& 9. 
+We could find the explanation from the vorticity of fluid 
+in Fig.~\ref{fig:Eroding20vort}. 
+Since the eroding velocity on the body is proportional to the 
+absolute value of vorticity in our erosion model,  
+then when the  absolute value of vorticity is small 
+there is not much erosion on the body. 
+In all four frames of Fig.~\ref{fig:Eroding20vort}, 
+the vorticity is relatively small between bodies 1 \& 6 and 3 \& 9.
+
+Besides the channels between two bodies, there is a single channel
+
+For the flat faces at the sites of near contact, since we put the body be close to one another
+so we are able to see all the channels between two close bodies have flat faces. 
+Besides the channels between bodies, we also observe the flat faces on the bodies 
+which are close to the outer boundary. For example, we see the flat faces 
+on the top of bodies 1 \& 6 and the bottom of bodies 13 \& 15.
+
+Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.  }
 

### 2019-05-15 docs/transport/erosion_transport.tex
remove the repeat part of Fig.2 in transport paper
NM

@@
 \author[SH]{Shang-Huan Chiu}
-\author[Nick]{M.~Nicholas J.~Moore}
+\author[Nick]{M.~N.~J.~Moore}
 \author[Bryan]{Bryan D.~Quaife}
@@
     derivative of the velocity to find the vorticity and stress tensor
+  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
   \item Tracer trajectories at different time steps
@@
 \begin{center}
-\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_1}
-\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_101}\\
+\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
+\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\
 
-\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_201}
-\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
-\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition.
-The color is the vorticity of fluid.
-The 4 snapshots are evenly spaced in time.
-In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.}
 \includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}

### 2019-05-15 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 \author[SH]{Shang-Huan Chiu}
-\author[Nick]{M.~N.~J.~Moore}
+\author[Nick]{M.~Nicholas J.~Moore}
 \author[Bryan]{Bryan D.~Quaife}
@@
     derivative of the velocity to find the vorticity and stress tensor
-  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
   \item Tracer trajectories at different time steps
@@
 
-Besides the channels between two bodies, there is a single channel
+Besides the channels between two bodies, there is a single channel across from left to right of the domain and the flow has been concentrated in this channel.
+In the second frame of Fig.~\ref{fig:Eroding20vort}, this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19.
+We can get a better understanding from the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.
+In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
+the flow (or tracer) first comes from three small channels between outer boundary \& body 10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become one main channel between bodies 1 \& 9.
+After
 

### 2019-05-15 docs/transport/erosion_transport.tex
Added Shelley refrence
do the result section in transport paper

--- 2019-05-15 docs/transport/erosion_transport.tex
@@
   \item Use novel near-singular Barycentric integration scheme for
-    Stokes equation outlined in~\cite{bar-wu-vee2015}.
+    Stokes equation outlined in~\cite{bar-wu-vee2015}. (Remember to include historically significant reference Shelley \cite{baker1986boundary}).
   \item Need to compute one additional derivative since we need the
@@
 Besides the channels between two bodies, there is a single channel 
+goes across the domain horizontally and
+ the flow has been concentrated in this channel. 
+In the second frame of Fig.~\ref{fig:Eroding20vort},
+ this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19. 
+We can get a better understanding of this channel from 
+the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. 
+In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
+the flow (or tracer) first comes from three small channels 
+between outer boundary \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
+then the three branches become one and go into the main channel between bodies 1 \& 9. 
+From the first frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, 
+this channel is expanding faster than other channel 
+and bodies 4 \& 12 has vanished and body 19 is almost gone in the forth frame. 
+The reason of fast expansion of this channel is the high vorticity. 
+In the forth frame of Fig.~\ref{fig:Eroding20tracer}, 
+we could see the vorticity is relatively high on the side of bodies which form this channel
+so the bodies are eroded fast on the side of this channel or have vanished completely.
+
+Furthermore, how long the body lasts for depends on not only the size of the body 
+but also the location of the body. 
+For example, the first three vanishing bodies are 
+body 12 (as t=0.0256), 4 (as t=0.0278), then 17 (as t=0.0287). 
+Since body 4 is located in the main flow channel so 
+the body 4 is vanished earlier than body 17 
+even the initial size of body 4 is larger than the size of body 17.
+This channel will keep expanding and the bodies around this channel will vanish earlier than others. 
+After body 17, the next 8 vanishing bodies with respect to time are body 19 (as t=0.0312),  
+ body 7 (as t=0.0325), body 20 (as t=0.0329), body 8 (as t=0.0349), body 10 (as t=0.0353),
+ body 3 (as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  
+All of these eight bodies are around this channel.
 
@@
 
-Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.  }
+Although the direction of flow is from left to right, 
+the tracers will not only travel horizontally but vertically. 
+In the last three frames of Fig.~\ref{fig:Eroding20tracer},  }
 

### 2019-05-16 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 This channel will keep expanding and the bodies around this channel will vanish earlier than others. 
-After body 17, the next 8 vanishing bodies with respect to time are body 19 (as t=0.0312),  
+After body 17, the next 8 vanished bodies with respect to time are body 19 (as t=0.0312),  
  body 7 (as t=0.0325), body 20 (as t=0.0329), body 8 (as t=0.0349), body 10 (as t=0.0353),
  body 3 (as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  
-All of these eight bodies are around this channel.
+All of these eight bodies were around this channel.
 

### 2019-05-16 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 the body 4 is vanished earlier than body 17 
-even the initial size of body 4 is larger than the size of body 17.
+although the initial size of body 4 is larger than the size of body 17.
 This channel will keep expanding and the bodies around this channel will vanish earlier than others. 
@@
  body 3 (as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  
-All of these eight bodies were around this channel.
+All of these eight bodies were around this channel before they are gone.
 

### 2019-05-16 docs/transport/erosion_transport.tex
do and add new figures in the result section of transport paper

@@
 
+Since we use a Barycentric quadrature rule to approximate the velocity of tracers
+and apply fourth order Runge Kutta method to find the new locations of tracers in each step,
+the tracers can be very close to but not penetrate the bodies. 
+Those body-closed tracers are moving perfectly 
+so we are able to observe the details of the interaction of bodies and fluid.
 Although the direction of flow is from left to right, 
-the tracers will not only travel horizontally but vertically. 
-In the last three frames of Fig.~\ref{fig:Eroding20tracer},  }
+the tracers will not only travel horizontally but also vertically. 
+In the last three frames of Fig.~\ref{fig:Eroding20tracer}, 
+some tracers climb up from right to left around the body. 
+There are zoom windows of the climbing tracers trajectories 
+in Fig.~\ref{fig:Eroding20zoom} and they are taken from the 
+last three frames of Fig.~\ref{fig:Eroding20tracer} with more tracers. 
+In Fig.~\ref{fig:Eroding20zoom} the tracers around 
+the center body first go from the channel below the body, 
+climb up to the left, then go to the right and join another tracers 
+in the channel above the body. 
+ }
 
@@
 The tracers are evenly spread in the $x_2-$direction and released at $x_1=-1$.}
+\end{center}
+\end{figure}
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210_zoom}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240_zoom}
+\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270_zoom}
+\caption{\label{fig:Eroding20zoom}The zoom windows in the last three frames of Fig.~\ref{fig:Eroding20tracer}.
+The trajectories of tracers around the bodies.
+Since we use a Barycentric quadrature rule and fourth order Runge Kutta method, the tracers can be very close to but not penetrate the bodies.
+}
 \end{center}

### 2019-05-16 docs/transport/erosion_transport.tex
do the result section of transport paper

@@
 Since we use a Barycentric quadrature rule to approximate the velocity of tracers
-and apply fourth order Runge Kutta method to find the new locations of tracers in each step,
+and apply the fourth order Runge Kutta method to find the new locations of tracers in each step,
 the tracers can be very close to but not penetrate the bodies. 
@@
 The trajectories of tracers around the bodies.
-Since we use a Barycentric quadrature rule and fourth order Runge Kutta method, the tracers can be very close to but not penetrate the bodies.
+Since we use a Barycentric quadrature rule and the fourth order Runge Kutta method, the tracers can be very close to but not penetrate the bodies.
 }

### 2019-05-17 docs/transport/erosion_transport.tex
worked on numerics

@@
   \item Use novel near-singular Barycentric integration scheme for
-    Stokes equation outlined in~\cite{bar-wu-vee2015}. (Remember to include historically significant reference Shelley \cite{baker1986boundary}).
+    Stokes equation outlined in~\cite{bar-wu-vee2015}. (Remember to
+    include historically significant reference Shelley
+    \cite{baker1986boundary}).  Also need discuss Helsing and Ojala who
+    did a similar panel-based quadrature~\cite{hel-oja2008}
   \item Need to compute one additional derivative since we need the
@@
 \begin{align}
-  \uu(\xx) = \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
+  \uu(\xx) = \DDD[\eeta](\xx) = 
+    \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
+  \frac{1}{\pi}\int_{\bd\Omega} 
     \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
@@
 \end{align}
-where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
-normal at $\yy$, and $\eeta$ is an unknown density function.  In
-Section~\ref{sec:DLPcomplex}, we show how the Stokes double-layer
-potential can also be expressed as the sum of a Laplacian double-layer
-potential 
+where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
+$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
+is an unknown density function.  In Section~\ref{sec:DLPcomplex}, we
+show how the Stokes double-layer potential can also be expressed as the
+sum of a Laplacian double-layer potential 
 \begin{align}
@@
 \begin{align}
+  \label{eqn:SPrelation}
   v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
@@
 decomposed as
-\begin{align}
+\begin{equation}
+  \label{eqn:Stokes2Laplace}
+  \begin{aligned}
     \DDD[\eeta](\xx) &= 
@@
         \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
-\end{align}
+  \end{aligned}
+\end{equation}
 All these integrals but the first are a gradient of a Laplace layer
@@
 rule}.  This method first uses the density function $\tau(y)$ to compute
-the boundary data of $v$, denoted by $v^-{y}$.  Then, it makes use
+the boundary data of $v$, denoted by $v^-(y)$.  Then, it makes use
 of the identity
@@
 \end{align}
-Then, even if $x$ is close to $\bd\Omega$, the integrand is no longer
-nearly-singular and the accuracy of the trapezoid rule is bounded
-independent of $x$.  A similar identity identity involving $v'(x)$ also
-holds.   Now, applying the spectrally accurate trapezoid rule, the
-quadrature error of the Barycentric quadrature rule
+Rearranging for $v(x)$, we have
+\begin{align}
+  v(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y)}{y-x}\, dy}
+    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
+\end{align}
+Of course, the denominator is simply $1$, but applying a quadrature rule
+to both integrands results in a uniform bound on the quadrature error.
+Differentiating Cauchy's integral theorem, the derivative of $v$ is
+\begin{align}
+  v'(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
+    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spatial Discretization}
+\label{s:spatialDiscretization}
+By using an integral equation formulation, we only have to discretize
+the boundary of the domain.  Therefore, we only have to discretize
+one-dimensional closed-curves, allowing us to use the spectrally
+accurate trapezoid rule~\cite{tre-wei2014} and Fourier differentiation.
+Moreover, since we only discretize the boundary of the domain, resolving
+the complex eroding bodies is straightforward.
+
+Consider eroding bodies $\gamma_k$, $k=1,\ldots,M$, in a fluid domain
+$\Omega$ with boundary $\Gamma$.  Let the length of $\Gamma$ be $L_{0}$,
+and the length of $\gamma_k$ be $L_k$.  We discretize each eroding body
+$\gamma_k$ with $N_\iin$ points and discretize $\Gamma$ with $N_\out$
+points.  The $j^{th}$ discretization point on $\Gamma$ is denoted by
+$\yy_j^0$, and the $j^{th}$ discretization point on $\gamma_k$ is
+denoted by $\yy^k_j$.  The discretization points are initially
+distributed evenly in arclength, and this equispacing is maintained for
+the entire simulation by using a {\thL}
+formulation~\cite{hou-low-she1994}.  In addition, we apply mild
+smoothing strategies~\cite{qua-moo2018} to avoid the corners that
+erosion inevitably develop.    Since the points are equispaced, the
+trapezoid rule to evaluate the velocity at a target point $\xx$ is
+\begin{align}
+  \label{eqn:trap}
+  \uu(\xx) \approx \frac{L_0}{N_\out} \sum_{j=1}^{N_\out} 
+    D(\xx,\yy^0_j) \eeta_j +
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
+    D(\xx,\yy^k_j) \eeta^k_j,
+\end{align}
+where $D$ is the kernel of the Stokes double-layer potential defined in
+Equation~\eqref{eqn:stokesDLP}.
+
+As previously mentioned, the quadrature error of the trapezoid rule is
+large if $\xx$ is close to $\bd\Omega$.  The proximity between $\xx$ and
+$\bd\Omega$ occurs in dense packings, and also when evaluating the
+velocity in the fluid bulk.  For these nearby points, instead of
+applying the trapezoid rule, the Barycentric quadrature rule is applied.
+In particular, the Stokes double-layer potential is decomposed into
+Laplacian double-layer potentials~\eqref{eqn:Stokes2Laplace}.  Then, for
+each of these Laplacian double-layer potentials, the density function is
+used to find the boundary values of the analytic function whose real
+part is the layer potential of interest~\eqref{eqn:SPrelation}.
+Finally, instead of applying the trapezoid rule to compute the Cauchy
+integrals, the quadrature rule outlined by Barnet et.~al is used
 \begin{align}
@@
 \end{align}
+Then, even if $x$ is close to $\bd\Omega$, the integrand is no longer
+nearly-singular and the accuracy of the trapezoid rule is bounded
+independent of $x$.  A similar identity identity involving $v'(x)$ also
+holds.   Now, applying the spectrally accurate trapezoid rule, the
+quadrature error of the Barycentric quadrature rule
 is uniformly bounded~\cite{bar-wu-vee2015}.  A slight modification of
@@
 While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
-developed~\cite{bar-wu-vee2015}, this work requires a similar quadrature
-rule for $v''(x)$.  We mimic the approach developed
-in~\cite{bar-wu-vee2015}.  First, if $x \in \Omega$ and $n \in
-\mathbb{N}$, then 
+developed~\cite{bar-wu-vee2015}, computing the shear stress and
+vorticity requires a Barycentric quadrature rule for $v''(x)$.  We mimic
+the approach developed in~\cite{bar-wu-vee2015}.  First, if $x \in
+\Omega$ and $n \in \mathbb{N}$, then 
 \begin{align}
@@
 
-To compute the velocity with $\mathcal{O}(N)$ operations, we start by
-using the trapezoid rule accelerated with the fast multipole method
-(FMM) \todo[inline]{reference here}. For target points that are
-sufficiently far from $\bd\Omega$, the resulting velocity is
-sufficiently accurate.  However, the velocity at points that are too
-close to $\bd\Omega$ must be corrected.  For a general point $\xx$,
+At each GMRES iteration, we must compute the velocity at each
+discretization point on $\bd\Omega$.  To reduce the cost of computing
+the velocity, we start by using the trapezoid rule~\eqref{eqn:trap}
+accelerated with the fast multipole method (FMM)~\cite{gre-rok1987},
+which requires $\mathcal{O}(N)$ operations, and we call this velocity
+$v_\trap(\xx)$.  For target points that are sufficiently far from
+$\bd\Omega$, $v_\trap(\xx)$ is sufficiently accurate.  However, this
+velocity is inaccurate at points that are too close to $\bd\Omega$, and
+the velocity must be corrected.  Assuming that $\xx$ is too close to
+$\gamma_k$, only the velocity due to $\gamma_k$ must be corrected. We
+first subtract the velocity contribution of $\vv(\xx)$ due to
+$\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
+the velocity due to $\gamma_i$ with more accuracy.  That is, the
+final velocity is
 \begin{align}
-  \vv(\xx) = \int_{\Gamma} D(\xx,\yy) \eeta(\yy)\, ds_\yy + 
-    \sum_{k=1}^{M} \int_{\gamma_k} D(\xx,\yy) \eeta(\yy)\, ds_\yy.
+  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_k} \sum_{j=1}^{N_\iin} 
+    D(\xx,\yy^k_j) \eeta(\yy_j) + v^k_\bary(\xx),
 \end{align}
-Assuming that $\xx$ is too close to $\gamma_i$, we first subtract the
-velocity contribution of $\vv(\xx)$ due to $\gamma_i$.  Then, the
-Barycentric quadrature rule is used to compute the velocity due to
-$\gamma_i$ with more accuracy.  This is correction is applied to all
-points that are close to an eroding body or the outer wall $\Gamma$.
+where $v^k_\bary(\xx)$ is the velocity at $\xx$ resulting from applying
+the Barycentric quadrature rule due to $\gamma_k$.  This method
+naturally extends to points that are close to $\Gamma$, and to the
+scenario when $\xx$ is simultaneously close to multiple components of
+$\bd\Omega$.
+
+We do not use any fast summation methods to apply the Barycentric
+quadrature rule.  Therefore, to it is imperative that we only apply
+the Barycentric quadrature at target points where they are required.
 
@@
 step, and the majority of the computational effort is still required to
-compute the velocity using the fast summation method.
+compute the velocity using the fast summation method.\todo[inline]{BQ:
+Discuss how we don't do Barycentric everywhere since it involves several
+$N$ body calculations, while the trapezoid rule only requires a single
+one}
 
@@
 }
-  \item Subtract off trapezoid rule directly
-  \item Add on Barycentric directly
 \end{itemize}

### 2019-05-17 docs/transport/erosion_transport.tex
do the result section of transport paper

--- 2019-05-16 docs/transport/erosion_transport.tex
@@
 }
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
+\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the fixed-pressure-drop condition.
+The color is the vorticity of fluid.
+In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $}
+\end{center}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-05-21 docs/proposals/ErosionWhitePaper.tex
NM

@@
   is the total interface length.  In these coordinates, the
-  stiff terms are linear and are be discretized implicitly.
+  stiff terms are linear which allows implicit methods to be used for time discretization.
 
-  \item {\bf Validation}: We compare the numerical simulations with
-  scaling laws.
+  \item {\bf Validation}: We compare the numerical simulations against analytical predictions for the limiting shape of a single body and scaling laws for its vanishing rate.
 \end{enumerate}
@@
 three-dimensional erosion}.  Second, {\bf we will investigate physically
-motivated questions regarding the geometry and flow inside an eroding
+motivated questions regarding the reconfiguration of geometry and flow inside an eroding
 porous medium}.

### 2019-05-21 docs/proposals/ErosionWhitePaper.tex
NM

@@
 \subsection{Physics-Based Understanding of Viscous Erosion}
-\todo[inline]{Characterizing anisotropy}
+
+Armed with these new tools, we plan to investigate how erosion alters a porous medium through a reshaping process that occurs on the grain scale.
+Initial investigations showed that, as bodies erode and reduce in size, the permeability of the medium increases.
+The rate of increase, however, cannot be explained by the reduction in grain size alone, as the reshaping and associated formation of channels are vital elements.
+The new methods will allow us to examine these features in more detail.
+In particular, we anticipate that erosion may also lead to the development of {\bf anisotropic} permeability, as the medium gradually reconfigures to transmit flow more easily in the direction of the initial flow.
+The new methods will allow us to characterize the changes in permeability and anisotropy especially in nearly-touching body configurations, in more dense packings, and eventually in configurations of mobile and/or sedimenting grains.
+
 \todo[inline]{Coarse-grained transport (anomalous diffusion)}
+\todo[inline]{Nick: I am not an expert on anomalous diffusion. Bryan, do you want to write this paragraph?}
 

### 2019-05-21 docs/proposals/ErosionWhitePaper.tex
NM

@@
 Florida State University.  He is also a Research Associate in FSU's
-Geophysical Fluid Dynamics Institute. \todo[inline]{A bit more}
+Geophysical Fluid Dynamics Institute. 
+Dr.~Moore received his Ph.D.~in 2010 in Mathematics at the University of North Carolina, Chapel Hill.
+He was a postdoctoral researcher at the Courant Institute of Mathematical Sciences from 2010-2014 working with Michael Shelley and others.
+His expertise includes modeling dynamic interactions between fluids and structures, especially in geophysically and biologically motivated settings.
 

### 2019-05-24 docs/transport/erosion_transport.tex
add tracer figure of 100 bodies in transport paper
add definition of porosity in transport paper
add tortuousity figures in transport paper
add a tortuousity figure in transport paper
small changes addressing S-H's email
redo the result section in transport paper

@@
     \frac{v(y)}{y-x} \,dy, \quad
-  v'(x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
+  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
     \frac{v(y)}{(y-x)^2} \, dy, \quad
@@
 
+{\color{red} the definition of porosity is the ratio 
+$$\phi=\frac{A_v}{A_T}$$
+where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     D(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
+  \sum_{k=1}^M \frac{L_k}{N_\iin} \sum_{j=1}^{N_\iin}
     D(\xx,\yy^k_j) \eeta^k_j,
@@
   \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_k} \sum_{j=1}^{N_\iin} 
-    D(\xx,\yy^k_j) \eeta(\yy_j) + v^k_\bary(\xx),
+    D(\xx,\yy^k_j) \eeta(\yy_j) + \vv^k_\bary(\xx),
 \end{align}
@@
 \end{itemize}
-
+{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid.
+The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$.
+We impose the fixed-pressure-drop condition on the simulation
+ smoothing parameters of $\eps$ and $\sigma $.
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Color indicates the shear stress on the body.
-In this simulation, we use three minimum body-to-wall initial distances $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
+In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=0.0001$, and smoothing parameters of $\eps$ and $\sigma $.}
 \label{} 
@@
 \begin{center}
+\includegraphics[width = 0.45 \textwidth]{./figs/velocity_loc}
+\includegraphics[width = 0.45 \textwidth]{./figs/tort_local}\\
+
+\includegraphics[width = 0.45 \textwidth]{./figs/tortU_local}
+\includegraphics[width = 0.45 \textwidth]{./figs/uminDumax}
+
 \caption{The tortuosity of the 20 nearly touching bodies}
@@
 \end{figure}
-
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
+\caption{\label{fig:Eroding100tracer} The trajectories of 200 tracers in the fluid with 100 bodies}
+\end{center}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-05-24 docs/transport/erosion_transport.tex
small changes to methods

@@
 \begin{align}
-  \pderiv{u_1}{x_1} &= \Re (v'[\tau_1](x)) + 
+  \pderiv{u_1}{x_1} &= +\Re (v'[\tau_1](x)) + 
     \Re (v''[y\cdot\eta](x)) - \Re (v'[\eta_1](x)) - 
@@
     \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
-  \pderiv{u_2}{x_1} &= \Re (v'[\tau_2](x)) - 
+  \pderiv{u_2}{x_1} &= +\Re (v'[\tau_2](x)) - 
     \Im (v''[y\cdot\eta](x)) + \Im (v'[\eta_1](x)) +
@@
 integrand is nearly singular if $x$ is close to $\bd\Omega$, and the
-quadrature error is arbitrarily large if the resolution $N$ is fixed.
-There have been a variety of near-singular integration schemes
-developed, and we extend a method first outlined by Barnett et
+quadrature error is arbitrarily large for a fixed resolution.  There
+have been a variety of near-singular integration schemes developed, and
+we extend a method first outlined by Barnett et
 al.~\cite{bar-wu-vee2015} which we call the {\em Barycentric quadrature
 rule}.  This method first uses the density function $\tau(y)$ to compute
-the boundary data of $v$, denoted by $v^-(y)$.  Then, it makes use
-of the identity
+the boundary data of $v$, denoted by $v^-(y)$.  Then, it makes use of
+the identity
 \begin{align}
@@
 which requires $\mathcal{O}(N)$ operations, and we call this velocity
-$v_\trap(\xx)$.  For target points that are sufficiently far from
-$\bd\Omega$, $v_\trap(\xx)$ is sufficiently accurate.  However, this
+$\vv_\trap(\xx)$.  For target points that are sufficiently far from
+$\bd\Omega$, $\vv_\trap(\xx)$ is sufficiently accurate.  However, this
 velocity is inaccurate at points that are too close to $\bd\Omega$, and
@@
 $\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
-the velocity due to $\gamma_i$ with more accuracy.  That is, the
-final velocity is
+the velocity due to $\gamma_i$ with more accuracy.  That is, the final
+velocity is
 \begin{align}
@@
 \end{align}
-where $v^k_\bary(\xx)$ is the velocity at $\xx$ resulting from applying
-the Barycentric quadrature rule due to $\gamma_k$.  This method
+where $\vv^k_\bary(\xx)$ is the velocity at $\xx$ resulting from
+applying the Barycentric quadrature rule due to $\gamma_k$.  This method
 naturally extends to points that are close to $\Gamma$, and to the
@@
 
-We do not use any fast summation methods to apply the Barycentric
-quadrature rule.  Therefore, to it is imperative that we only apply
-the Barycentric quadrature at target points where they are required.
+Similarly, to compute the vorticity and shear stress, the trapezoid rule
+is first used.  Then, if $\xx$ is close to $\gamma_k$, the trapezoid
+quadrature rule contribution due to $\gamma_k$ is subtracted and the
+Barycentric quadrature rule contribution due to $\gamma_k$ is added.
+Since the shear stress and vorticity are only computed once per time
+step, we use a direct summation rather than the FMM.  Relative to the
+cost of applying GMRES with the FMM, the additional once-per-time-step
+cost is minimal.
+
+We also do not use any fast summation methods to apply the Barycentric
+quadrature rule.  Since this quadrature rule is applied at every GMRES
+iteration, it is imperative that we only apply the Barycentric
+quadrature at target points where they are required.  As a rule of
+thumb, the trapezoid rule due to $\gamma_k$ is accurate if
+\begin{align}
+  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| < 
+    5 \frac{L_k}{N_\iin}.
+\end{align}
+To avoid having to check if a target point $\xx$ satisifies
 
@@
 \end{itemize}
-{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid.
-The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$.
-We impose the fixed-pressure-drop condition on the simulation
- smoothing parameters of $\eps$ and $\sigma $.
-}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Color indicates the shear stress on the body.
-In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=0.0001$, and smoothing parameters of $\eps$ and $\sigma $.}
+In this simulation, we use three minimum body-to-wall initial distances $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
 \label{} 

### 2019-05-24 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 \begin{align}
-  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| < 
+  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
     5 \frac{L_k}{N_\iin}.
@@
 The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$.
-We impose the fixed-pressure-drop condition on the simulation
- smoothing parameters of $\eps$ and $\sigma $.
+There are $N_\out = 1024$ points on the outer boundary for all the simultions.
+We impose the fixed pressure drop condition.
+We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies.
 }
@@
 Color indicates the shear stress on the body.
-In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=0.0001$, and smoothing parameters of $\eps$ and $\sigma $.}
+In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=0.0001$, and $\eps = 15/256$ and $\sigma=10/256$.}
 \label{} 
@@
 {\color{red} We first consider a single circular body in a shear flow. 
-The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
 The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. 
 Let the initial radius of the body be $r$, 
-the initial length of the body be $L$, $N_\iin$ and 
-$N_\out$ be the number of discretization points 
-on the body and wall respectively, 
+the initial length of the body be $L$, $N_\iin$ be the number of discretization points 
+on the body, 
 $h=L/N_\iin$ be the resolution mesh size of the body, 
@@
 \includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
-\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition.
+\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed pressure drop condition.
 The color is the vorticity of fluid.
 The 4 snapshots are evenly spaced in time.
-In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
+In this simulation, we use $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
 In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
@@
 The reason of fast expansion of this channel is the high vorticity. 
-In the forth frame of Fig.~\ref{fig:Eroding20tracer}, 
+In the forth frame of Fig.~\ref{fig:Eroding20vort}, 
 we could see the vorticity is relatively high on the side of bodies which form this channel

### 2019-05-30 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$.
-There are $N_\out = 1024$ points on the outer boundary for all the simultions.
-We impose the fixed pressure drop condition.
-We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies.
+Let the initial radius of the body be $r$, the initial length of the body be $L$,
+and $d$ be the minimum initial distance from body to wall.
+Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer boundary and discretization points on the bodies, respectively.
+We fix $N_\out=1024$ for all the simultions.
+We impose the fixed pressure drop condition on our numerical results to satisfy the physical phenomenon which has been introduced in~\cite{qua-moo2018}.
+We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies and the parameters $\alpha_1$ and $\alpha_2$ to determine if the target point is close enough to boundary.
 }
@@
 Color indicates the shear stress on the body.
-In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=0.0001$, and $\eps = 15/256$ and $\sigma=10/256$.}
+In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and $\eps = 15/256$ and $\sigma=10/256$.}
 \label{} 
@@
 \end{figure}
-{\color{red} We first consider a single circular body in a shear flow. 
-The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. 
-Let the initial radius of the body be $r$, 
-the initial length of the body be $L$, $N_\iin$ be the number of discretization points 
-on the body, 
-$h=L/N_\iin$ be the resolution mesh size of the body, 
-and $d$ be the minimum initial distance from body to wall. 
-To investigate the shape of eroding body when it is close to wall, 
-we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ 
-with respect to three different $d=h, h/2$, and $ h/10$.
+{\color{red} We first consider a single circular body in the shear flow. 
+This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
+The velocity of flow from the left side of $\Omega$ is 
+$$\vv=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
+We place a single eroding body close to the no-slip wall ($y=-1$).
+This example has no pressure drop. 
+We investigate the shape of eroding body when it is close to a solid wall at the three  
+distances $d=h, h/2$, and $ h/10$ where $h=L/N_\iin$ is the arclength spacing correponding to the initial radius $r$ of 0.4 and $N_\iin=256$ discretization points .
 
@@
 \caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed pressure drop condition.
-The color is the vorticity of fluid.
+The color is the vorticity of the fluid.
 The 4 snapshots are evenly spaced in time.
-In this simulation, we use $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
-In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
+We use $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
+In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 has almost completely eroded.}
 \end{center}
@@
 By using Barycentric quadrature rule, 
-we are able to capture the details in the fluid when wall and bodies or body and bodies 
-are close to each other. 
+we are able to capture the details in the fluid when wall 
+and bodies or body and bodies are close to each other. 
 The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
-The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
-The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. 
-The number of discretization points $N_\iin$ on the bodies is 256 and the number 
-of discretization points $N_\out$ on the outer boundary is 1024.
+The initial velocity of flow from the left side of $\Omega$ is 
+$$\vv=U\begin{bmatrix} 1-y^2\\ 0\end{bmatrix},$$ 
+where $U$ is chosen such that 
+the pressure drop between  $x=-2$ and $x=2$ remains fixed at 8.
+With this choice, the velocity in the absent of grains has flow rate $U=1$.
+The number of discretization points is $N_\iin = 256$.
 
@@
 eroding are in Fig.~\ref{fig:Eroding20vort}. 
-We place some bodies to nearly contact not only one another 
+We initially place some bodies to nearly contact not only one another 
 but also the outer boundary. For example, bodies 1, 6, 13, and 15 
@@
 of near contact, and bodies vanishing. In this nearly touching bodies 
-structure, we also observe these phenomena but with more new details.
-
+structure, we also observe these similar phenomena but not totally the same.
 For the speed of expanding space at the narrow channel, we see some 
 narrow channels do expand faster than other wider channels. 
-For example, the spacing between bodies 14 \& 18 is smaller 
-than the spacing between bodies 7 \& 14 initially and the former one is 
+For example, the spacing between bodies 14 and 18 is smaller 
+than the spacing between bodies 7 and 14 initially and the former one is 
 comparable to the latter one by the second frame. But there are some 

### 2019-05-31 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 in the channel above the body.
+
+In Fig.~\ref{fig:Eroding20area} we measure the area occupied by bodies and the flow rate $U$ quantifily during the eroding.
+At the beggining, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies.
+Then the eroding speed is increasing
+
+The flow rate increases exponentially with growth rate close to $\ln10^4$. 
  }
@@
 \begin{center}
+\includegraphics[width = 0.45 \textwidth]{./figs/porosity20dense}
+\includegraphics[width = 0.45 \textwidth]{./figs/flow_rate20dense}
+\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly touching eroding bodies and the incoming flow rate of U verse time.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
 \includegraphics[width = 0.45 \textwidth]{./figs/velocity_loc}
@@
 
-\caption{The tortuosity of the 20 nearly touching bodies}
+\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
 \end{center}

### 2019-05-31 docs/transport/erosion_transport.tex
do the result section in transport paper

--- 2019-05-30 docs/transport/erosion_transport.tex
@@
 This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
-The velocity of flow from the left side of $\Omega$ is 
-$$\vv=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
+The initial velocity of flow from the left side of $\Omega$ is 
+$$\UU(\xx)=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
 We place a single eroding body close to the no-slip wall ($y=-1$).
@@
 The initial velocity of flow from the left side of $\Omega$ is 
-$$\vv=U\begin{bmatrix} 1-y^2\\ 0\end{bmatrix},$$ 
+$$\UU(\xx)=U\begin{bmatrix} 1-y^2\\ 0\end{bmatrix},$$ 
 where $U$ is chosen such that 
@@
 in the channel above the body.
+
+In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we measure the area occupied by bodies and the flow rate $U$ quantifily during the eroding.
+At the beggining, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies.
+Then the eroding speed is increasing
+
+The flow rate increases exponentially with growth rate close to $\ln10^4$. 
  }
@@
 \begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/porosity20dense}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/erodingspeed20dense}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly touching eroding bodies and the eroding speed verse time.}
+\end{figure}
+
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of U verse time.}
+\end{figure}
+
+\begin{figure}[H]
 \begin{center}

### 2019-05-31 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 
-To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
+To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer wall with $N_\out$ points.
 The following is the four-step fast summation methods.
@@
 {\color{red}
- Let $L_w$ be the length of the outer boundary and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$.
+ Let $L_w$ be the length of the outer wall and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$.
 Here are the criteria to see if two points are too close for trapezoid.
-For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to outer boundary if
+For criterion of outer wall to body,  let $d$ be the minimum distance between outer wall and a point $x$ on the body $b$, we say $x$ is too close to outer wall if
 \begin{equation}\label{eqn:Cw2b}
-d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}
+d< \alpha_1\frac{L_w}{N_\out}
 \end{equation}
@@
 \begin{equation}\label{eqn:Cb2b}
-d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
+d<\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
 \end{equation}
@@
 and $d$ be the minimum initial distance from body to wall.
-Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer boundary and discretization points on the bodies, respectively.
+Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer wall and discretization points on the bodies, respectively.
 We fix $N_\out=1024$ for all the simultions.
@@
 We initially place some bodies to nearly contact not only one another 
-but also the outer boundary. For example, bodies 1, 6, 13, and 15 
-are very close to outer boundary. In~\cite{qua-moo2018} 
+but also the outer wall. For example, bodies 1, 6, 13, and 15 
+are very close to outer wall: 
+the distance between body 1 and outer wall is $1.3025h$, 
+the distance between body 6 and outer wall is $2.9275h$,
+the distance between body 13 and outer wall is $2.8447h$,
+the distance between body 15 and outer wall is $1.3352h$ 
+where $h=L_w/N_\out$ is the arclength spacing correponding to the outer wall.
+ In~\cite{qua-moo2018} 
 we reported the quick expanding space at the narrow channel 
@@
 the flow (or tracer) first comes from three small channels 
-between outer boundary \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
+between outer wall \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
 then the three branches become one and go into the main channel between bodies 1 \& 9. 
@@
 Besides the channels between bodies, we also observe the flat faces on the bodies 
-which are close to the outer boundary. For example, we see the flat faces 
+which are close to the outer wall. For example, we see the flat faces 
 on the top of bodies 1 \& 6 and the bottom of bodies 13 \& 15.
@@
 In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we measure the area occupied by bodies and the flow rate $U$ quantifily during the eroding.
-At the beggining, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies.
-Then the eroding speed is increasing
+In the beginning, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies.
+Then the eroding speed is increasing when more and more bodies are vanished in the fluid.
 
@@
 The color is the vorticity of fluid.
-In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $}
+In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer wall, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $}
 \end{center}

### 2019-06-03 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
-periodic, the Trapezoid rule has spectral accuracy.  However, the
-integrand is nearly singular if $x$ is close to $\bd\Omega$, and the
+periodic, the trapezoid rule has spectral accuracy.  However, the
+integrand becomes nearly singular as $x$ approaches $\bd\Omega$, and the
 quadrature error is arbitrarily large for a fixed resolution.  There
@@
 
-Here, we briefly describe this quadrature method, and then derive a
-necessary extension to simulate erosion.  The Barycentric quadrature
-rule starts with a quadrature rule with nodes $y_j \in \bd\Omega$ and
-weights $w_j$. We use the trapezoid rule because of its superior
-accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, as $x$
-approaches $\bd\Omega$, the integrand becomes nearly singular and the
-quality of the trapezoid rule deteriorates. To eliminate the
-nearly-singular integrand, we use the identity
-\begin{align}
-  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0.
+Here, we briefly describe the Barycentric quadrature method, and then
+derive a necessary extension to simulate erosion.  The method starts
+with a quadrature rule with nodes $y_j \in \bd\Omega$ and weights $w_j$,
+$j=1,\ldots,N$.  We use the trapezoid rule because of its superior
+accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, at a
+fixed resolution, if $x$ is sufficiently close to $\bd\Omega$, each of
+the integrands in equation~\eqref{eqn:cauchy} are nearly-singular and
+the quadrature error is prohibitively large.  However, the trapezoid
+rule applied to the identity
+\begin{align}
+  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
+\end{align}
+has a uniformly bounded error since the integrand is not nearly-singular
+as $x$ approaches $\bd\Omega$.  That is,
+\begin{align}
+  \sum_{j=1}^{N} \frac{v^{-}(y_j) - v(x)}{y_j - x} w_j \approx 0.
 \end{align}
 Rearranging for $v(x)$, we have
+\begin{align*}
+  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
+  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j},
+\end{align*}
+which is simply the trapezoid rule applied to the two integrals in the
+identity
 \begin{align}
@@
 \end{align}
-Of course, the denominator is simply $1$, but applying a quadrature rule
-to both integrands results in a uniform bound on the quadrature error.
-Differentiating Cauchy's integral theorem, the derivative of $v$ is
-\begin{align}
-  v'(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
-    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
+Of course, the denominator is simply $1$, but by applying the trapezoid
+rule to both integrands, the result is an error with a uniform bound.
+To compute $v'(x)$, the identity
+\begin{align}
+  v'(x) = \frac{\int\limits_{\bd\Omega} 
+    \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
+  {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy},
+\end{align}
+is used, and applying the trapezoid rule
+\begin{align}
+  v'(x) \approx \frac{\sum\limits_{j=1}^{N}
+    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
+  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
 \end{align}
@@
 The flow rate increases exponentially with growth rate close to $\ln10^4$.
- }
+
+In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field. }
 

### 2019-06-03 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 
-In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field. }
+In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field.
+In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the x-component velocity u(-1, y) to its maximum velocity, namely, $u_{max}=6.2281 \times 10^{-4}$ at equal spreading tracers on the cross section at x=-1 and y in [-1,1].
+The velocity is continuous along the cross section and acting as several Poiseuille flows.
+This velocity graph is different from the one in~\cite{matyka2008tortuosity} since we choose our cross section to be the beginning of the flow before the fluid touches any body.
+In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity $\tau$ of the tracers at the cross section.
+This graph is not continuous and the jumps in $\tau$ mean that the initial neighbor tracers have been seperated by the bodies.
+
+In Fig.~\ref{fig:Eroding20tort}(c)
+In Fig.~\ref{fig:Eroding20tort}(d) }
 
@@
 \begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.45 \textwidth]{./figs/velocity_loc}
-\includegraphics[width = 0.45 \textwidth]{./figs/tort_local}\\
-
-\includegraphics[width = 0.45 \textwidth]{./figs/tortU_local}
-\includegraphics[width = 0.45 \textwidth]{./figs/uminDumax}
-
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/velocity_loc}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/tort_local}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/tortU_local}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/uminDumax}
+\caption{}
+\end{subfigure}
 \caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
-\end{center}
 \end{figure}

### 2019-06-03 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field.
-In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the x-component velocity u(-1, y) to its maximum velocity, namely, $u_{max}=6.2281 \times 10^{-4}$ at equal spreading tracers on the cross section at x=-1 and y in [-1,1].
+In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281 \times 10^{-4}$ at equal spreading tracers on the cross section (x=-1 and y in [-1,1]).
 The velocity is continuous along the cross section and acting as several Poiseuille flows.

### 2019-06-07 docs/transport/erosion_transport.tex
worked in section 4.3

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fast Summation Methods}
+\subsection{Efficiently Applying Quadrature}
 \label{sec:fmm}
@@
 \begin{align}
+  \label{eqn:TrapCutoff}
   d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
@@
 \end{align}
-To avoid having to check if a target point $\xx$ satisifies
-
-The same strategy of using the trapezoid rule and then correcting with
-the Barycentric quadrature is used to compute the shear stress on
-$\bd\Omega$ and vorticity in $\Omega$.  The trapezoid rule is applied
-with a direct summation, but this cost is only incurred once per time
-step, and the majority of the computational effort is still required to
-compute the velocity using the fast summation method.\todo[inline]{BQ:
-Discuss how we don't do Barycentric everywhere since it involves several
-$N$ body calculations, while the trapezoid rule only requires a single
-one}
-
-To determine if a point $\xx \in \gamma_i$ needs to be corrected with
-the Barycentric quadrature rule, we first estimate the proximity of
-$\xx$ to $\bd\Omega$.  The criteria depends on the length of the outer
-wall, $L_w$, the length of the eroding bodies $L_i$, $i=1,\ldots,M$, and
-the number of discretization points $N_\out$ and $N_\iin$.
-
-{\color{red}
-By using Barycentric quadrature rule to approach integrations, we get a reasonable(?) double-layer potential and quantities of interest at target points but it requires $\mathcal{O}(N^2)$ operations per target point which is computational expensive if we impose it on all the target points.
-In order to accelerate the process and keep the accuracy, it is a compromise that we use Barycentric quadrature rule to approach the nearly singular integratons but apply trapezoid rule when the target point is far from source points.
-
-To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer wall with $N_\out$ points.
-The following is the four-step fast summation methods.
-}
-\begin{itemize}
-  \item Apply trapezoid rule as a first pass
-
-{\color{red} We use the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} with trapezoid rule to calculate the double-layer potential.
-}
-  \item Efficiently find points that are too close for trapezoid
-
-{\color{red}
- Let $L_w$ be the length of the outer wall and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$.
-Here are the criteria to see if two points are too close for trapezoid.
-For criterion of outer wall to body,  let $d$ be the minimum distance between outer wall and a point $x$ on the body $b$, we say $x$ is too close to outer wall if
-\begin{equation}\label{eqn:Cw2b}
-d< \alpha_1\frac{L_w}{N_\out}
-\end{equation}
-where $\alpha_1$ is a constant. 
-For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
-\begin{equation}\label{eqn:Cb2b}
-d<\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
-\end{equation}
-where $\alpha_2$ is a constant.
-
-}
-\end{itemize}
-{\color{red}  (Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency)
-
-To find the suitable values of $\alpha_1$ and $\alpha_2$ in~\eqref{eqn:Cw2b} and \eqref{eqn:Cb2b}, we set $\alpha_1=\alpha_2=1, 2, 3$, and $4$ to test the criteria on a 20-body problem with $N_\out = 1024$ and $N_\iin = 128, 256$, and $512$.
-To check the accuracy of the simulations, we use the solution calculated by \todo[inline]{what method} to \todo[inline]{...}
-To see how efficient our code is, we record the cpu time for each step.
-
-}
+To avoid checking if a target point $\xx$
+satisfies~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
+First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
+lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
+if
+\begin{align}
+  \label{eqn:BodyCutoff}
+  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
+    \alpha \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
+\end{align}
+where $\alpha /geq 1$ is a free parameter that needs to be chosen.
+In this manner, we are checking the proximity of the two circles with
+centers $\cc_i$ and $\cc_j$, and with radii $L_i$ and $L_j$, where
+$\alpha$.  This criteria allows us to quickly determine bodies that
+contain discretization points where the Barycentric quadrature rule
+should be applied.  Assuming that the two bodies $\gamma_i$ and
+$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
+\in \gamma_j$, we check if
+\begin{align}
+  \label{eqn:PointsCutoff}
+  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \alpha_\iin 
+    \left(\frac{L_i}{N_\iin} \right).
+\end{align}
+By applying this method, we do not have to do an all-to-all comparison
+of the discretization points on two eroding bodies.
+
+To determine an appropriate value for $\alpha_\iin$, we first compute an
+accurate solution by using the Barycentric quadrature rule for all
+discretization points.  Then, for multiple values of $\alpha_\iin$, we
+compute the velocity field with the trapezoid rule for all points that
+do not satisfy~\eqref{eqn:PointsCutoff}.  By comparing these two
+velocities, we find that a value of $\alpha_\iin = ???$ gives sufficient
+accuracy while keeping the number of points that require the expensive
+Barycentric quadrature rule to a minimum.
+
+Given an eroding body $\gamma_i$, to determine if a target point $\xx$
+that is in the fluid bulk rather than on another eroding body requires
+the Barycentric quadrature rule, we only check
+condition~\eqref{eqn:PointCutoff}.  Finally, to determine if points on
+$\gamma_i$ are too close to the outer wall, we make use of the fact that
+the outer wall is bounded in $[-3,3] \times [-1,1]$, and that the bodies
+are all contained in $[-1,1] \times [-1,1]$.  Therefore, we first check
+if
+\begin{align}
+  \|\cc_i \pm 1\| < L_i + \alpha_\out \frac{L_\out}{N_\out}.
+\end{align}
+If body $\gamma_i$ satisfies this condition, for each point $\xx \in
+\gamma_i$, we apply the Barycentric rule to points that satisfy
+\begin{align}
+  \|\xx \pm 1\| < \alpha_\out \frac{L_\out}{N_\out}.
+\end{align}
+Using the same strategy as we used for body-body interactions, we find
+that an appropriate safety parameter is $\alpha_\out = ???$.
 
@@
 %}
+
+%{\color{red}
+%By using Barycentric quadrature rule to approach integrations, we get a reasonable(?) double-layer potential and quantities of interest at target points but it requires $\mathcal{O}(N^2)$ operations per target point which is computational expensive if we impose it on all the target points.
+In order to accelerate the process and keep the accuracy, it is a compromise that we use Barycentric quadrature rule to approach the nearly singular integratons but apply trapezoid rule when the target point is far from source points.
+%
+%
+%To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer wall with $N_\out$ points.
+The following is the four-step fast summation methods.
+%}
+%\begin{itemize}
+%  \item Apply trapezoid rule as a first pass
+%
+%{\color{red} We use the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} with trapezoid rule to calculate the double-layer potential.
+%}
+%  \item Efficiently find points that are too close for trapezoid
+%
+%{\color{red}
+% Let $L_w$ be the length of the outer wall and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$.
+Here are the criteria to see if two points are too close for trapezoid.
+For criterion of outer wall to body,  let $d$ be the minimum distance between outer wall and a point $x$ on the body $b$, we say $x$ is too close to outer wall if
+%\begin{equation}\label{eqn:Cw2b}
+%d< \alpha_1\frac{L_w}{N_\out}
+%\end{equation}
+%where $\alpha_1$ is a constant. 
+%For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
+%\begin{equation}\label{eqn:Cb2b}
+%d<\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
+%\end{equation}
+%where $\alpha_2$ is a constant. 
+%
+%}
+%\end{itemize}
+%{\color{red}  (Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency)
+%
+%To find the suitable values of $\alpha_1$ and $\alpha_2$ in~\eqref{eqn:Cw2b} and \eqref{eqn:Cb2b}, we set $\alpha_1=\alpha_2=1, 2, 3$, and $4$ to test the criteria on a 20-body problem with $N_\out = 1024$ and $N_\iin = 128, 256$, and $512$.
+To check the accuracy of the simulations, we use the solution calculated by \todo[inline]{what method} to \todo[inline]{...}
+%To see how efficient our code is, we record the cpu time for each step.
+%
+%}

### 2019-06-07 julia_code/postprocess.jl
NM

@@ -6,7 +6,7 @@ using LinearAlgebra
 function postprocess(foldername::AbstractString)
 	println("\n\n%------------------------------------------------------%")
 	t1 = time()
-	println("Beginning postprocess on ", foldername)
+	println("Beginning postprocess on ", foldername, "\n")
 	pp1(foldername)
 	pp2(foldername)
 	pp3(foldername)
@@ -18,11 +18,10 @@ end
 
 # pp1: Postprocess the fast stuff: area and resistivity.
 function pp1(foldername::AbstractString)
-	println("\nBeggining pp1.")
 	datafolder,ntimes,params = startpostprocess(foldername)
 	# Read the data at each time step.
 	for cnt=0:ntimes
-		print("Step ", cnt, " of ", ntimes, ": ")
+		print("pp1 step ", cnt, " of ", ntimes, ": ")
 		thlenden, cntstr = get_thlenden(datafolder,cnt)
 		npts,nbods = getnvals(thlenden.thlenvec)
 		#--------------------------------------#
@@ -46,16 +45,15 @@ function pp1(foldername::AbstractString)
 		# Print progress.
 		println("resistivity completed; ")
 	end
-	println("Finished pp1.\n")
+	println("Finished pp1.")
 	return
 end
 # pp2: Postprocess the slower stuff: drag and stress.
 function pp2(foldername::AbstractString)
-	println("\nBeggining pp2.")
 	datafolder,ntimes,params = startpostprocess(foldername)
 	# Read the data at each time step.
 	for cnt=0:ntimes
-		println("Beggining step ", cnt, " of ", ntimes, ".")
+		println("\npp2 beggining step ", cnt, " of ", ntimes, ".")
 		thlenden, cntstr = get_thlenden(datafolder,cnt)
 		npts,nbods = getnvals(thlenden.thlenvec)
 		#--------------------------------------#
@@ -77,17 +75,15 @@ function pp2(foldername::AbstractString)
 		stressfile = string(datafolder,"stress",cntstr,".dat")
 		label = string("# Smoothed atau, Raw atau ")
 		writedata([label; atauv; tauv], stressfile)
-		println("Finished step ", cnt, " of ", ntimes, ".\n")
 	end
 	println("Finished pp2.\n")
 end
 # pp3: Postprocess the slowest stuff: quantities of interest at the target points.
 function pp3(foldername::AbstractString)
-	println("\nBeggining pp3.")
[…]

### 2019-06-09 docs/transport/erosion_transport.tex
worked on section 4.3

@@
 \end{align}
-To avoid checking if a target point $\xx$
+To avoid checking if all target point $\xx$
 satisfies~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
@@
   \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
-    \alpha \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
-\end{align}
-where $\alpha /geq 1$ is a free parameter that needs to be chosen.
-In this manner, we are checking the proximity of the two circles with
-centers $\cc_i$ and $\cc_j$, and with radii $L_i$ and $L_j$, where
-$\alpha$.  This criteria allows us to quickly determine bodies that
-contain discretization points where the Barycentric quadrature rule
-should be applied.  Assuming that the two bodies $\gamma_i$ and
+    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
+\end{align}
+where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
+In this manner, rather than using an expensive all-to-all algorithm to
+compute the distance between all pairs of discretization points, we
+compute the distance between pairs of circles.  This criteria allows us
+to quickly determine bodies that contain discretization points where the
+Barycentric quadrature rule may need to be applied, and the parameter
+$\alpha_\iin$ is accounts for the fact that the bodies are being
+approximated with circles.  Assuming that the two bodies $\gamma_i$ and
 $\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
@@
 \begin{align}
-  \label{eqn:PointsCutoff}
+  \label{eqn:PointsBodyCutoff}
   \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \alpha_\iin 
@@
 \end{align}
-By applying this method, we do not have to do an all-to-all comparison
-of the discretization points on two eroding bodies.
-
-To determine an appropriate value for $\alpha_\iin$, we first compute an
-accurate solution by using the Barycentric quadrature rule for all
-discretization points.  Then, for multiple values of $\alpha_\iin$, we
-compute the velocity field with the trapezoid rule for all points that
-do not satisfy~\eqref{eqn:PointsCutoff}.  By comparing these two
-velocities, we find that a value of $\alpha_\iin = ???$ gives sufficient
+
+To determine if points on $\gamma_i$ are too close to the outer wall, we
+use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
+and that the bodies are all contained in $[-1,1] \times [-1,1]$.
+Therefore, we first check if
+\begin{align}
+  \left\|\cc_i - \left[
+    \begin{array}{c}
+      0 \\ \pm 1
+    \end{array}
+    \right]
+  \right\| < L_i + \alpha_\out \frac{L_\out}{N_\out}.
+\end{align}
+If body $\gamma_i$ satisfies this condition, for each point $\xx \in
+\gamma_i$, we apply the Barycentric rule to points that satisfy
+\begin{align}
+  \label{eqn:PointsWallCutoff}
+  \|\xx \pm 1\| < \alpha_\out \frac{L_\out}{N_\out}.
+\end{align}
+
+To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
+we first compute an accurate solution by using the Barycentric
+quadrature rule for all discretization points.  Then, for multiple
+values of $\alpha_\iin$ and $\alpha_\out$, we compute the velocity field
+with the trapezoid rule for all points that do not satisfy
+conditions~\eqref{eqn:PointsBodyCutoff}
+and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
+find that $\alpha_\iin = ???$ and $\alpha_\out = ???$ give sufficient
 accuracy while keeping the number of points that require the expensive
@@
 
-Given an eroding body $\gamma_i$, to determine if a target point $\xx$
-that is in the fluid bulk rather than on another eroding body requires
-the Barycentric quadrature rule, we only check
-condition~\eqref{eqn:PointCutoff}.  Finally, to determine if points on
-$\gamma_i$ are too close to the outer wall, we make use of the fact that
-the outer wall is bounded in $[-3,3] \times [-1,1]$, and that the bodies
-are all contained in $[-1,1] \times [-1,1]$.  Therefore, we first check
-if
-\begin{align}
-  \|\cc_i \pm 1\| < L_i + \alpha_\out \frac{L_\out}{N_\out}.
-\end{align}
-If body $\gamma_i$ satisfies this condition, for each point $\xx \in
-\gamma_i$, we apply the Barycentric rule to points that satisfy
-\begin{align}
-  \|\xx \pm 1\| < \alpha_\out \frac{L_\out}{N_\out}.
-\end{align}
-Using the same strategy as we used for body-body interactions, we find
-that an appropriate safety parameter is $\alpha_\out = ???$.
+Finally, to determine if a target point $\xx$ that is in the fluid bulk
+rather than on another eroding body requires the Barycentric quadrature
+rule, we only check conditions~\eqref{eqn:PointsBodyCutoff}
+and~\eqref{eqn:PointsWallCutoff}.
 

### 2019-06-09 docs/transport/erosion_transport.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We do some simulations.  The parameters are
-\begin{itemize}
-  \item time step size
-  \item regularization and smoothing parameters
-  \item resolution on bodies and solid wall
-\end{itemize}
-{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid.
-The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$.
-Let the initial radius of the body be $r$, the initial length of the body be $L$,
-and $d$ be the minimum initial distance from body to wall.
-Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer wall and discretization points on the bodies, respectively.
-We fix $N_\out=1024$ for all the simultions.
-We impose the fixed pressure drop condition on our numerical results to satisfy the physical phenomenon which has been introduced in~\cite{qua-moo2018}.
-We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies and the parameters $\alpha_1$ and $\alpha_2$ to determine if the target point is close enough to boundary.
-}
+In this section, we present the numerical simulations of dense packings
+of eroding bodies.  The computational domain $\Omega$ is a rectangle
+$[-3,3] \times [-1,1]$ with rounded off corners and we place bodies only
+in $[-1,1] \times [-1,1]$.  For all simulations, we discretize $\Gamma =
+\bd \Omega$ with $N_\out=1024$ points.  The Dirichlet boundary condition
+on $\Gamma$ is a Hagen-Poiseuille flow.  As the bodies erode, the flow
+rate is adjusted to maintain the physical constant pressure drop
+boundary condition.  To maintain this pressure drop, we compute the
+pressure at near the inlet and outlet at each time step as described in
+our previous work~\cite{qua-moo2018}.
+
+The initial shape of the eroding body $\gamma_i$ is a circle centered at
+$\cc_i$ with radius $r_i$ and length $L_i = 2\pi r_i$, and each
+$\gamma_i$ is discretized with $N_\iin$ points.  Using the annealing
+algorithm described in Section ???, the initial configuration has the
+desired initial porosity, and the minimum separation between any pair of
+bodies and between the bodies and solid wall is $d$.  A no-slip boundary
+condition is imposed on $\gamma$.  To round off inevitable corners on
+the eroding bodies, we apply smoothing the smoothing parameters
+$\eps=???$ and $\sigma=???$, as described in~\cite{qua-moo2018}, for all
+simulations.
+
+Finally, the parameters used to determine if a point uses the trapezoid
+or Barycentric quadrature rule are $\alpha_\iin = ???$ and
+$\alpha_\out=???$.
+
+\todo[inline]{time step size}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-06-10 docs/transport/erosion_transport.tex
worked on results

@@
 \label{s:formulation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Continuing with our previous work~\cite{qua-moo2018}, we use a
@@
 \label{sec:DLPcomplex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
@@
 \subsection{Cauchy Integral Representation of the Shear Stress}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 To compute the rate of erosion, we must compute the shear stress of the
@@
 \subsection{Cauchy Integral Representation of the Vorticity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Having calculated all derivatives of the double-layer potential, the
@@
 \subsection{Cauchy Integral Representation of the Pressure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The pressure of the double-layer potential is
@@
 \label{s:spatialDiscretization}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 By using an integral equation formulation, we only have to discretize
@@
 \subsection{Barycentric Quadrature for $v''(x)$}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
@@
 \label{sec:fmm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The Barycentric quadrature rule achieves acceptable accuracy for
@@
 
+We reuse the time stepping method outlined in our previous
+work~\cite{qua-moo2018}.  Rather than tracking the $(x,y)$
+coordinates, the {\thL} variables are tracked. A second-order
+Implicit-Explicit method is used. In particular, the diffusive term
+corresponding to the curvature penalization term is discretized
+implicitly, and all other terms, which are non-stiff, are treated
+explicitly.
+
 Finally, the parameters used to determine if a point uses the trapezoid
@@
 
-\todo[inline]{time step size}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A single body close to a wall}
-\todo[inline]{Do a single body that is extremely close one of the two
-horizontal walls.  This can be compared to some of the
-results~\cite{mit-spa2017}.  Do for a variety of distances to
-demonstrate how close we can put it to the wall with no need to increase
-the resolution}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{A Single Body Close to a Wall}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We consider a single eroding body close to a solid wall.  To compare our
+results with a similar numerical experiment performed by Mitchell and
+Spagnolie~\cite{mit-spa2017}, rather a pressure drop boundary condition,
+we impose the shear flow
+\begin{align}
+  \UU(\xx)=\left[
+  \begin{array}{c}
+    y+1 \\ 0
+  \end{array}
+  \right],
+\end{align}
+on the outer wall.  The eroding body is initially a circle of
+radius $r=0.4$, length $L = 2\pi r$, and is placed near the no-slip wall
+at $y=-1$.  We discretize the eroding body with $N_\iin=256$
+discretization points, and the center of the eroding body is initially
+placed at $h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N\iin$.  For all
+three simulations, we use the time step size $\Delta t=10^{-4}$.
+
+With this setup, many of the discretization points on the eroding body
+are too close to the outer wall for the trapezoid rule to achieve
+sufficient accuracy.  However, by using the Barycentric quadrature rule,
+the numerical stable simulations are possible.  In
+Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
+several equispaced time steps, and the color of indicates the erosion
+rate (magnitude of the shear stress).  Comparing our results to Mitchell
+and Spagnolie~\cite{mit-spa2017} (Figure 7(b)), we see similar results
+where the shear stress is smallest near the zero background flow line
+$y=-1$.  Moreover, since the shear stress is everywhere positive, the
+erosion rate, which is the magnitude of the shear stress, is a smooth
+function.  The result is that the eroding shape does not have any
+stagnation points where corners will develop.
+
 \begin{figure}[htbp]
@@
 \includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
-\caption{A single body eroding in Stokes flow.
-Color indicates the shear stress on the body.
-In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and $\eps = 15/256$ and $\sigma=10/256$.}
-\label{} 
+\caption{\label{fig:NearWall} 
+  A single body eroding in Stokes flow. The color indicates the shear
+  stress on the body. Therefore, erosion is fastest in the yellow
+  regions and slowest in the blue regions.  In this simulation, we use
+  three minimum body-to-wall initial distances $d=h$ (left), $h/2$
+  (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points
+  on the body, a time step size of $\Dt=10^{-4}$, and smoothing
+  parameters $\eps = 15/256$ and $\sigma=10/256$.}
 \end{center}
 \end{figure}
-{\color{red} We first consider a single circular body in the shear flow. 
-This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
-The initial velocity of flow from the left side of $\Omega$ is 
-$$\UU(\xx)=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
-We place a single eroding body close to the no-slip wall ($y=-1$).
-This example has no pressure drop. 
-We investigate the shape of eroding body when it is close to a solid wall at the three  
-distances $d=h, h/2$, and $ h/10$ where $h=L/N_\iin$ is the arclength spacing correponding to the initial radius $r$ of 0.4 and $N_\iin=256$ discretization points .
-
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{20 nearly touching bodies}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We consider 20 eroding bodies a Hagen-Poiseuille flow.  The background
+flow is 
+\begin{align}
+  \UU(\xx)=U \left[
+  \begin{array}{c}
+    1-y^2 \\ 0
+  \end{array}
+  \right].
+\end{align}
+Initially, $U=1$, and then $U$ is updated at each time step so that the
+pressure drop from $x=-2$ to $x=2$ remains constant.  Snapshots of the
+bodies at four equispaced times are shown in
+Figure~\ref{fig:Eroding20vort}.   The colormap is the vorticity which is
+equivalent to the shear stress when restricted to the eroding bodies.
+Therefore, erosion is fastest in regions where the magnitude of the
+vorticity is largest.
+
+Initially, several of the eroding bodies are close to the outer wall.
+In particular, with $h=L_2/N_\out$, the distance between bodies 1, 6,
+13, and 15 are $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively.  In
+addition, since each body is discretized with $N_\iin=256$ points, the
+distance between several pairs of eroding bodies is too small to be
+accurately resolved at the prescribed resolution.  Particular pairs
+include bodies 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18.  By using the
+Barycentric quadrature rule, the interaction between these
+nearly-touching bodies can be accurately resolved at the prescribed
+resolution.
+
+In~\cite{qua-moo2018}, we observed that erosion causes the space
+between nearly touching bodies to quickly expand, and flat faces develop
+along the region of near contact.  This qualitative behavior is also
+observed In Figure~\ref{fig:Eroding20vort}, such as between bodies 3
+\&4 and 15 \& 16.  However, by resolving bodies that are
+much closer to one another when compared to our previous
+work~\cite{qua-moo2018}, we see that it is possible for very little
+erosion to occur between a pair of bodies.  In particular, for pairs of
+bodies where the channel between the bodies is nearly perpendicular to
+the main flow direction (bodies 1 \&6, 3 \& 9, and 13 \& 15), there is
+very little shear stress and the effect of erosion is slight.
 
@@
 \begin{center}
-\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
-\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\
-
-\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
-\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
-\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed pressure drop condition.
-The color is the vorticity of the fluid.
-The 4 snapshots are evenly spaced in time.
-We use $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.
-In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 has almost completely eroded.}
+  \includegraphics[height=0.43\textwidth]{./figs/20b_dense1}
+  \includegraphics[height=0.43\textwidth]{./figs/20b_dense101} \\
+  \includegraphics[height=0.43\textwidth]{./figs/20b_dense201}
+  \includegraphics[height=0.43\textwidth]{./figs/20b_dense301}
+%\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
+%\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\
+%\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
+%\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
+\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
+  with the fixed pressure drop condition. The color is the vorticity of
+  the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
+  256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
+  and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In
+  the forth frame, bodies 4, 12, and 17 have vanished completely, and
+  body 19 has almost completely eroded.}
 \end{center}
 \end{figure}
-\subsection{20 nearly touching bodies}
 {\color{red} 
-By using Barycentric quadrature rule, 
-we are able to capture the details in the fluid when wall 
-and bodies or body and bodies are close to each other. 
-The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
-The initial velocity of flow from the left side of $\Omega$ is 
-$$\UU(\xx)=U\begin{bmatrix} 1-y^2\\ 0\end{bmatrix},$$ 
-where $U$ is chosen such that 
-the pressure drop between  $x=-2$ and $x=2$ remains fixed at 8.
-With this choice, the velocity in the absent of grains has flow rate $U=1$.
-The number of discretization points is $N_\iin = 256$.
-
-The snapshots of the process of 20 nearly touching bodies 
-eroding are in Fig.~\ref{fig:Eroding20vort}. 
-We initially place some bodies to nearly contact not only one another 
-but also the outer wall. For example, bodies 1, 6, 13, and 15 
-are very close to outer wall: 
-the distance between body 1 and outer wall is $1.3025h$, 
-the distance between body 6 and outer wall is $2.9275h$,
-the distance between body 13 and outer wall is $2.8447h$,
-the distance between body 15 and outer wall is $1.3352h$ 
-where $h=L_w/N_\out$ is the arclength spacing correponding to the outer wall.
- In~\cite{qua-moo2018} 
-we reported the quick expanding space at the narrow channel 
-between neighboring bodies, the developing flat faces at the sites 
-of near contact, and bodies vanishing. In this nearly touching bodies 
-structure, we also observe these similar phenomena but not totally the same.
-For the speed of expanding space at the narrow channel, we see some 
-narrow channels do expand faster than other wider channels. 
-For example, the spacing between bodies 14 and 18 is smaller 
+In~\cite{qua-moo2018} we reported the quick expanding space at
+the narrow channel between neighboring bodies, the developing flat faces
+at the sites of near contact, and bodies vanishing. In this nearly
+touching bodies structure, we also observe these similar phenomena but
+not totally the same.  For the speed of expanding space at the narrow
+channel, we see some narrow channels do expand faster than other wider
+channels.  For example, the spacing between bodies 14 and 18 is smaller
 than the spacing between bodies 7 and 14 initially and the former one is
 comparable to the latter one by the second frame. But there are some
-small initial spacings that do not expand that much at all by the fourth frame, 
-for example between bodies 1 \& 6, 3 \& 9. 
-We could find the explanation from the vorticity of fluid 
-in Fig.~\ref{fig:Eroding20vort}. 
-Since the eroding velocity on the body is proportional to the 
-absolute value of vorticity in our erosion model,  
-then when the  absolute value of vorticity is small 
-there is not much erosion on the body. 
-In all four frames of Fig.~\ref{fig:Eroding20vort}, 
-the vorticity is relatively small between bodies 1 \& 6 and 3 \& 9.
-
-Besides the channels between two bodies, there is a single channel 
-goes across the domain horizontally and
- the flow has been concentrated in this channel. 
-In the second frame of Fig.~\ref{fig:Eroding20vort},
- this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19. 
-We can get a better understanding of this channel from 
-the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. 
-In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
-the flow (or tracer) first comes from three small channels 
-between outer wall \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
-then the three branches become one and go into the main channel between bodies 1 \& 9. 
-From the first frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, 
-this channel is expanding faster than other channel 
-and bodies 4 \& 12 has vanished and body 19 is almost gone in the forth frame. 
-The reason of fast expansion of this channel is the high vorticity. 
-In the forth frame of Fig.~\ref{fig:Eroding20vort}, 
-we could see the vorticity is relatively high on the side of bodies which form this channel
-so the bodies are eroded fast on the side of this channel or have vanished completely.
-
-Furthermore, how long the body lasts for depends on not only the size of the body 
-but also the location of the body. 
-For example, the first three vanishing bodies are 
-body 12 (as t=0.0256), 4 (as t=0.0278), then 17 (as t=0.0287). 
-Since body 4 is located in the main flow channel so 
-the body 4 is vanished earlier than body 17 
-although the initial size of body 4 is larger than the size of body 17.
-This channel will keep expanding and the bodies around this channel will vanish earlier than others. 
-After body 17, the next 8 vanished bodies with respect to time are body 19 (as t=0.0312),  
- body 7 (as t=0.0325), body 20 (as t=0.0329), body 8 (as t=0.0349), body 10 (as t=0.0353),
- body 3 (as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  
-All of these eight bodies were around this channel before they are gone.
-
-For the flat faces at the sites of near contact, since we put the body be close to one another
-so we are able to see all the channels between two close bodies have flat faces. 
-Besides the channels between bodies, we also observe the flat faces on the bodies 
-which are close to the outer wall. For example, we see the flat faces 
-on the top of bodies 1 \& 6 and the bottom of bodies 13 \& 15.
-
-Since we use a Barycentric quadrature rule to approximate the velocity of tracers
-and apply the fourth order Runge Kutta method to find the new locations of tracers in each step,
-the tracers can be very close to but not penetrate the bodies. 
-Those body-closed tracers are moving perfectly 
-so we are able to observe the details of the interaction of bodies and fluid.
-Although the direction of flow is from left to right, 
-the tracers will not only travel horizontally but also vertically. 
-In the last three frames of Fig.~\ref{fig:Eroding20tracer}, 
-some tracers climb up from right to left around the body. 
-There are zoom windows of the climbing tracers trajectories 
-in Fig.~\ref{fig:Eroding20zoom} and they are taken from the 
-last three frames of Fig.~\ref{fig:Eroding20tracer} with more tracers. 
-In Fig.~\ref{fig:Eroding20zoom} the tracers around 
-the center body first go from the channel below the body, 
-climb up to the left, then go to the right and join another tracers 
-in the channel above the body.
-
-In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we measure the area occupied by bodies and the flow rate $U$ quantifily during the eroding.
-In the beginning, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies.
-Then the eroding speed is increasing when more and more bodies are vanished in the fluid.
-
-The flow rate increases exponentially with growth rate close to $\ln10^4$.
-
-In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field.
-In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281 \times 10^{-4}$ at equal spreading tracers on the cross section (x=-1 and y in [-1,1]).
-The velocity is continuous along the cross section and acting as several Poiseuille flows.
-This velocity graph is different from the one in~\cite{matyka2008tortuosity} since we choose our cross section to be the beginning of the flow before the fluid touches any body.
-In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity $\tau$ of the tracers at the cross section.
-This graph is not continuous and the jumps in $\tau$ mean that the initial neighbor tracers have been seperated by the bodies.
+small initial spacings that do not expand that much at all by the fourth
+frame, for example between bodies 1 \& 6, 3 \& 9.  We could find the
+explanation from the vorticity of fluid in Fig.~\ref{fig:Eroding20vort}.
+Since the eroding velocity on the body is proportional to the absolute
+value of vorticity in our erosion model,  then when the  absolute value
+of vorticity is small there is not much erosion on the body.  In all
+four frames of Fig.~\ref{fig:Eroding20vort}, the vorticity is relatively
+small between bodies 1 \& 6 and 3 \& 9.
+
+Besides the channels between two bodies, there is a single channel goes
+across the domain horizontally and the flow has been concentrated in
+this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
+channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
+12, and 6 \& 19.  We can get a better understanding of this channel from
+the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In the
+top three frames of  Fig.~\ref{fig:Eroding20tracer}, the flow (or
+tracer) first comes from three small channels between outer wall \& body
+10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
+one and go into the main channel between bodies 1 \& 9.  From the first
+frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
+is expanding faster than other channel and bodies 4 \& 12 has vanished
+and body 19 is almost gone in the forth frame.  The reason of fast
+expansion of this channel is the high vorticity.  In the forth frame of
+Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
+high on the side of bodies which form this channel so the bodies are
+eroded fast on the side of this channel or have vanished completely.
+
+Furthermore, how long the body lasts for depends on not only the size of
+the body but also the location of the body.  For example, the first
+three vanishing bodies are body 12 (as t=0.0256), 4 (as t=0.0278), then
+17 (as t=0.0287).  Since body 4 is located in the main flow channel so
+the body 4 is vanished earlier than body 17 although the initial size of
+body 4 is larger than the size of body 17.  This channel will keep
+expanding and the bodies around this channel will vanish earlier than
+others.  After body 17, the next 8 vanished bodies with respect to time
+are body 19 (as t=0.0312),  body 7 (as t=0.0325), body 20 (as t=0.0329),
+body 8 (as t=0.0349), body 10 (as t=0.0353), body 3 (as t=0.0356), body
+14 (as t=0.0363), then body 9 (as t=0.0376).  All of these eight bodies
+were around this channel before they are gone.
+
+For the flat faces at the sites of near contact, since we put the body
+be close to one another so we are able to see all the channels between
+two close bodies have flat faces.  Besides the channels between bodies,
+we also observe the flat faces on the bodies which are close to the
+outer wall. For example, we see the flat faces on the top of bodies 1 \&
+6 and the bottom of bodies 13 \& 15.
+
+Since we use a Barycentric quadrature rule to approximate the velocity
+of tracers and apply the fourth order Runge Kutta method to find the new
+locations of tracers in each step, the tracers can be very close to but
+not penetrate the bodies.  Those body-closed tracers are moving
+perfectly so we are able to observe the details of the interaction of
+bodies and fluid.  Although the direction of flow is from left to right,
+the tracers will not only travel horizontally but also vertically.  In
+the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
+climb up from right to left around the body.  There are zoom windows of
+the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
+they are taken from the last three frames of
+Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
+Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
+from the channel below the body, climb up to the left, then go to the
+right and join another tracers in the channel above the body.
+
+In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we
+measure the area occupied by bodies and the flow rate $U$ quantifily
+during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
+[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
+when more and more bodies are vanished in the fluid.
+
+The flow rate increases exponentially with growth rate close to
+$\ln10^4$.
+
+In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect
+of the geometrical structure on fluid velocity field. In
+Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
+x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
+\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
+and y in [-1,1]). The velocity is continuous along the cross section and
+acting as several Poiseuille flows. This velocity graph is different
+from the one in~\cite{matyka2008tortuosity} since we choose our cross
+section to be the beginning of the flow before the fluid touches any
+body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity
+$\tau$ of the tracers at the cross section. This graph is not continuous
+and the jumps in $\tau$ mean that the initial neighbor tracers have been
+seperated by the bodies.
 
 In Fig.~\ref{fig:Eroding20tort}(c)
-In Fig.~\ref{fig:Eroding20tort}(d) }
+In Fig.~\ref{fig:Eroding20tort}(d) 
+}
 
@@
 \includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270}
-\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in the fluid with 20 bodies.
-The 9 snapshots are evenly spaced in time.
-The tracers are evenly spread in the $x_2-$direction and released at $x_1=-1$.}
+\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
+  the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.
+  The tracers are evenly spread in the $x_2-$direction and released at
+  $x_1=-1$.}
 \end{center}
@@
 \includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270_zoom}
-\caption{\label{fig:Eroding20zoom}The zoom windows in the last three frames of Fig.~\ref{fig:Eroding20tracer}.
-The trajectories of tracers around the bodies.
-Since we use a Barycentric quadrature rule and the fourth order Runge Kutta method, the tracers can be very close to but not penetrate the bodies.
-}
+\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
+  frames of Fig.~\ref{fig:Eroding20tracer}. The trajectories of tracers
+  around the bodies. Since we use a Barycentric quadrature rule and the
+  fourth order Runge Kutta method, the tracers can be very close to but
+  not penetrate the bodies. }
 \end{center}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly touching eroding bodies and the eroding speed verse time.}
+\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
+  touching eroding bodies and the eroding speed verse time.}
 \end{figure}
@@
 \subsection{50 nearly touching bodies}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 {\color{red}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{100 bodies}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 {\color{red}
@@
 \includegraphics[width = 0.8\textwidth]{./figs/100b_50}
-\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the fixed-pressure-drop condition.
-The color is the vorticity of fluid.
-In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer wall, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $}
+\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
+  fixed-pressure-drop condition. The color is the vorticity of fluid. In
+  this simulation, we use $N_\iin = 256$ discretization points on the
+  body, $N_\out = 1024$ points on the outer wall, a time-step of
+  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
+  $\sigma=10/256 $}
 \end{center}
@@
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for
-supplying the FMM for the Stokes double-layer potential. BQ and NM were
-supported by Florida State University startup funds and Simons
-Foundation Mathematics and Physical Sciences-Collaboration Grants for
-Mathematicians.
+\paragraph{\bf Acknowledgments} BQ and NM were supported by Florida
+State University startup funds and Simons Foundation Mathematics and
+Physical Sciences-Collaboration Grants for Mathematicians.
 
@@
 %}
+
+%{\color{red} 
+%By using Barycentric quadrature rule, we are able to capture the details
+%in the fluid when wall and bodies or body and bodies are close to each
+%other.  The first nearly touching bodies case is 20 bodies in a
+%Hagen-Poiseuille flow.  The initial velocity of flow from the left side
+%of $\Omega$ is $$\UU(\xx)=U\begin{bmatrix} 1-y^2\\ 0\end{bmatrix},$$
+%where $U$ is chosen such that the pressure drop between  $x=-2$ and
+%$x=2$ remains fixed at 8.  With this choice, the velocity in the absent
+%of grains has flow rate $U=1$.  The number of discretization points is
+%$N_\iin = 256$.
+%
+%The snapshots of the process of 20 nearly touching bodies eroding are in
+%Fig.~\ref{fig:Eroding20vort}.  We initially place some bodies to nearly
+%contact not only one another but also the outer wall. For example,
+%bodies 1, 6, 13, and 15 are very close to outer wall: the distance
+%between body 1 and outer wall is $1.3025h$, the distance between body 6
+%and outer wall is $2.9275h$, the distance between body 13 and outer wall
+%is $2.8447h$, the distance between body 15 and outer wall is $1.3352h$
+%where $h=L_w/N_\out$ is the arclength spacing correponding to the outer
+%wall.  In~\cite{qua-moo2018} we reported the quick expanding space at
+%the narrow channel between neighboring bodies, the developing flat faces
+%at the sites of near contact, and bodies vanishing. In this nearly
+%touching bodies structure, we also observe these similar phenomena but
+%not totally the same.  For the speed of expanding space at the narrow
+%channel, we see some narrow channels do expand faster than other wider
+%channels.  For example, the spacing between bodies 14 and 18 is smaller
+%than the spacing between bodies 7 and 14 initially and the former one is
+%comparable to the latter one by the second frame. But there are some
+%small initial spacings that do not expand that much at all by the fourth
+%frame, for example between bodies 1 \& 6, 3 \& 9.  We could find the
+%explanation from the vorticity of fluid in Fig.~\ref{fig:Eroding20vort}.
+%Since the eroding velocity on the body is proportional to the absolute
+%value of vorticity in our erosion model,  then when the  absolute value
+%of vorticity is small there is not much erosion on the body.  In all
+%four frames of Fig.~\ref{fig:Eroding20vort}, the vorticity is relatively
+%small between bodies 1 \& 6 and 3 \& 9.
+%
+%Besides the channels between two bodies, there is a single channel goes
+%across the domain horizontally and the flow has been concentrated in
+%this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
+%channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
+%12, and 6 \& 19.  We can get a better understanding of this channel from
+%the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In the
+%top three frames of  Fig.~\ref{fig:Eroding20tracer}, the flow (or
+%tracer) first comes from three small channels between outer wall \& body
+%10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
+%one and go into the main channel between bodies 1 \& 9.  From the first
+%frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
+%is expanding faster than other channel and bodies 4 \& 12 has vanished
+%and body 19 is almost gone in the forth frame.  The reason of fast
+%expansion of this channel is the high vorticity.  In the forth frame of
+%Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
+%high on the side of bodies which form this channel so the bodies are
+%eroded fast on the side of this channel or have vanished completely.
+%
+%Furthermore, how long the body lasts for depends on not only the size of
+%the body but also the location of the body.  For example, the first
+%three vanishing bodies are body 12 (as t=0.0256), 4 (as t=0.0278), then
+%17 (as t=0.0287).  Since body 4 is located in the main flow channel so
+%the body 4 is vanished earlier than body 17 although the initial size of
+%body 4 is larger than the size of body 17.  This channel will keep
+%expanding and the bodies around this channel will vanish earlier than
+%others.  After body 17, the next 8 vanished bodies with respect to time
+%are body 19 (as t=0.0312),  body 7 (as t=0.0325), body 20 (as t=0.0329),
+%body 8 (as t=0.0349), body 10 (as t=0.0353), body 3 (as t=0.0356), body
+%14 (as t=0.0363), then body 9 (as t=0.0376).  All of these eight bodies
+%were around this channel before they are gone.
+%
+%For the flat faces at the sites of near contact, since we put the body
+%be close to one another so we are able to see all the channels between
+%two close bodies have flat faces.  Besides the channels between bodies,
+%we also observe the flat faces on the bodies which are close to the
+%outer wall. For example, we see the flat faces on the top of bodies 1 \&
+%6 and the bottom of bodies 13 \& 15.  
+%
+%Since we use a Barycentric quadrature rule to approximate the velocity
+%of tracers and apply the fourth order Runge Kutta method to find the new
+%locations of tracers in each step, the tracers can be very close to but
+%not penetrate the bodies.  Those body-closed tracers are moving
+%perfectly so we are able to observe the details of the interaction of
+%bodies and fluid.  Although the direction of flow is from left to right,
+%the tracers will not only travel horizontally but also vertically.  In
+%the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
+%climb up from right to left around the body.  There are zoom windows of
+%the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
+%they are taken from the last three frames of
+%Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
+%Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
+%from the channel below the body, climb up to the left, then go to the
+%right and join another tracers in the channel above the body. 
+%
+%In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we
+%measure the area occupied by bodies and the flow rate $U$ quantifily
+%during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
+%[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
+%when more and more bodies are vanished in the fluid. 
+%
+%The flow rate increases exponentially with growth rate close to
+%$\ln10^4$. 
+%
+%
+%In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect
+%of the geometrical structure on fluid velocity field. In
+%Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
+%x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
+%\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
+%and y in [-1,1]). The velocity is continuous along the cross section and
+%acting as several Poiseuille flows. This velocity graph is different
+%from the one in~\cite{matyka2008tortuosity} since we choose our cross
+%section to be the beginning of the flow before the fluid touches any
+%body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity
+%$\tau$ of the tracers at the cross section. This graph is not continuous
+%and the jumps in $\tau$ mean that the initial neighbor tracers have been
+%seperated by the bodies. 
+%
+%In Fig.~\ref{fig:Eroding20tort}(c)
+%In Fig.~\ref{fig:Eroding20tort}(d) 
+%}

### 2019-06-10 docs/transport/erosion_transport.tex
do the section 4.3 in transport paper

@@
 \in \gamma_j$, we check if
+{\color{red}
 \begin{align}
   \label{eqn:PointsBodyCutoff}
-  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \alpha_\iin 
-    \left(\frac{L_i}{N_\iin} \right).
-\end{align}
-
+  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi}
++ \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right).
+\end{align}
+}
 To determine if points on $\gamma_i$ are too close to the outer wall, we
@@
 Therefore, we first check if
+{\color{red}
 \begin{align}
@@
     \begin{array}{c}
-      0 \\ \pm 1
+      x_{\cc_i } \\ \pm 1
     \end{array}
     \right]
-  \right\| < L_i + \alpha_\out \frac{L_\out}{N_\out}.
-\end{align}
-If body $\gamma_i$ satisfies this condition, for each point $\xx \in
-\gamma_i$, we apply the Barycentric rule to points that satisfy
+  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out}
+\end{align}
+where $x_{\cc_i } $ is the x coordinate of $\cc_i$.}
+If body $\gamma_i$ satisfies this condition, for each point {\color{red}$\xx=(x,y) \in
+\gamma_i$}, we apply the Barycentric rule to points that satisfy
+{\color{red}
 \begin{align}
   \label{eqn:PointsWallCutoff}
-  \|\xx \pm 1\| < \alpha_\out \frac{L_\out}{N_\out}.
-\end{align}
+  \|y \pm 1\| <  \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
+\end{align}}
 
@@
 and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
-find that $\alpha_\iin = ???$ and $\alpha_\out = ???$ give sufficient
+find that {\color{red}$\alpha_\iin = 4$ and $\alpha_\out = 4$ }give sufficient
 accuracy while keeping the number of points that require the expensive
@@
 condition is imposed on $\gamma$.  To round off inevitable corners on
-the eroding bodies, we apply smoothing the smoothing parameters
-$\eps=???$ and $\sigma=???$, as described in~\cite{qua-moo2018}, for all
+the eroding bodies, we apply smoothing the smoothing parameters {\color{red}
+$\eps=15/256$ and $\sigma=10/256$,} as described in~\cite{qua-moo2018}, for all
 simulations.
@@
 Finally, the parameters used to determine if a point uses the trapezoid
-or Barycentric quadrature rule are $\alpha_\iin = ???$ and
-$\alpha_\out=???$.
+or Barycentric quadrature rule are $\alpha_\iin = 4$ and
+$\alpha_\out=4$.
 

### 2019-06-10 docs/transport/erosion_transport.tex
working on results

--- 2019-06-10 docs/transport/erosion_transport.tex
@@
 bodies where the channel between the bodies is nearly perpendicular to
-the main flow direction (bodies 1 \&6, 3 \& 9, and 13 \& 15), there is
+the main flow direction (bodies 1 \& 6, 3 \& 9, and 13 \& 15), there is
 very little shear stress and the effect of erosion is slight.
@@
 \end{figure}
+
+In this example, we also observe that erosion creates a network of
+channels from the inlet to outlet where the velocity and vorticity, and
+therefore erosion rate, are much larger than the other regions.  These
+channels can be further visualized by considering the streamlines at
+several configurations of the eroding body.  In
+Figure~\ref{fig:Eroding20tracer}, we simulate 200 tracers that are
+initially to the left of the porous region and equispaced in $y$.  There
+are two clear region where the tracers pass through the geometry
+much faster than the other regions.  To illustrate the ability of the
+Barycentric quadrature formula, streamlines very close to the eroding
+bodies are illustrated in Figure~\ref{fig:Eroding20zoom}.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b60}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}\\
+
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b120}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b180}\\
+
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b240}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
+\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
+  the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.
+  The tracers are evenly spread in the $y$-direction and released at
+  $x=-1$.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
+\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
+\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
+\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
+  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
+  tracers around the bodies. Since we use a Barycentric quadrature rule
+  and the fourth order Runge Kutta method, the tracers can be very close
+  to but not penetrate the bodies.}
+\end{center}
+\end{figure}
+
 {\color{red} 
-In~\cite{qua-moo2018} we reported the quick expanding space at
-the narrow channel between neighboring bodies, the developing flat faces
-at the sites of near contact, and bodies vanishing. In this nearly
-touching bodies structure, we also observe these similar phenomena but
-not totally the same.  For the speed of expanding space at the narrow
-channel, we see some narrow channels do expand faster than other wider
-channels.  For example, the spacing between bodies 14 and 18 is smaller
-than the spacing between bodies 7 and 14 initially and the former one is
-comparable to the latter one by the second frame. But there are some
-small initial spacings that do not expand that much at all by the fourth
-frame, for example between bodies 1 \& 6, 3 \& 9.  We could find the
-explanation from the vorticity of fluid in Fig.~\ref{fig:Eroding20vort}.
-Since the eroding velocity on the body is proportional to the absolute
-value of vorticity in our erosion model,  then when the  absolute value
-of vorticity is small there is not much erosion on the body.  In all
-four frames of Fig.~\ref{fig:Eroding20vort}, the vorticity is relatively
-small between bodies 1 \& 6 and 3 \& 9.
-
 Besides the channels between two bodies, there is a single channel goes
@@
 }
-
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b30}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b60}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b90}\\
-
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b120}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b150}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b180}\\
-
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270}
-\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
-  the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.
-  The tracers are evenly spread in the $x_2-$direction and released at
-  $x_1=-1$.}
-\end{center}
-\end{figure}
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210_zoom}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240_zoom}
-\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270_zoom}
-\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
-  frames of Fig.~\ref{fig:Eroding20tracer}. The trajectories of tracers
-  around the bodies. Since we use a Barycentric quadrature rule and the
-  fourth order Runge Kutta method, the tracers can be very close to but
-  not penetrate the bodies. }
-\end{center}
-\end{figure}
 

### 2019-06-10 docs/transport/erosion_transport.tex
do the result section in transport paper

--- 2019-06-10 docs/transport/erosion_transport.tex
@@
 
-In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we
-measure the area occupied by bodies and the flow rate $U$ quantifily
+In Fig.~\ref{fig:Eroding20area} we
+measure the area occupied by bodies 
 during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
 [-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
-when more and more bodies are vanished in the fluid.
-
-The flow rate increases exponentially with growth rate close to
-$\ln10^4$.
+when more and more bodies are vanished in the fluid and 
+the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
+[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
+all the bodies are vanished completely.
+
+Fig.~\ref{fig:Eroding20flowrate} we record the flow rate $U$ quantifily
+during the eroding. Since we simulate the erosion by applying fixed pressure drop 
+the flow rate $U$ is small when there are many bodies in the fluid and 
+when the area occupied by bodies is getting smaller $U$ is getting larger.
+When all the bodies have vanished completely the flow rate $U$ is equal to 1.
+In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
+with growth rate close to $\ln10^4$.
 
@@
 
-In Fig.~\ref{fig:Eroding20tort}(c)
+In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
+and draw 
 In Fig.~\ref{fig:Eroding20tort}(d) 
@@
 \begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
-\caption{}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
-\caption{}
-\end{subfigure}
+%\begin{subfigure}[b]{0.5\textwidth}
+\center
+\includegraphics*[width =0.5\linewidth]{./figs/flow_rate20dense}
+%\caption{}
+%\end{subfigure}%
+%\begin{subfigure}[b]{0.5\textwidth}
+%\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
+%\caption{}
+%\end{subfigure}
 \caption{\label{fig:Eroding20flowrate}  The incoming flow rate of U verse time.}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/tortU_local}
+\includegraphics*[width =\linewidth]{./figs/diff_tort}
 \caption{}
@@
 \caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
+\end{figure}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top20}
+\caption{\label{fig:Eroding20tort_traj} The largest 20 difference of the length of 
+two neighbor tracers' trajectories in
+ 20 nearly touching bodies eroding}
 \end{figure}

### 2019-06-10 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 
-Fig.~\ref{fig:Eroding20flowrate} we record the flow rate $U$ quantifily
-during the eroding. Since we simulate the erosion by applying fixed pressure drop 
+We record the flow rate $U$ quantifily in log scale
+during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
+Since we simulate the erosion by applying fixed pressure drop 
 the flow rate $U$ is small when there are many bodies in the fluid and 
@@
 In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
-and draw 
-In Fig.~\ref{fig:Eroding20tort}(d) 
+and draw the trajectories of neighboring tracers in Fig.~\ref{fig:Eroding20tort_traj}
+if the difference of length of the neighboring trajectories is large. From this figure, we are able to 
+tell the neighboring trajectories will be very different if they are separated by bodies. 
 }

### 2019-06-11 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 \includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top20}
-\caption{\label{fig:Eroding20tort_traj} The largest 20 difference of the length of 
-two neighbor tracers' trajectories in
- 20 nearly touching bodies eroding}
+\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of the length of 
+local tortuosity $\tau$ at two neighboring tracers in
+ 20 nearly touching bodies eroding. The same color of a pair of trajectories 
+means they are from two neighboring tracers.}
 \end{figure}

### 2019-06-11 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 and draw the trajectories of neighboring tracers in Fig.~\ref{fig:Eroding20tort_traj}
-if the difference of length of the neighboring trajectories is large. From this figure, we are able to 
-tell the neighboring trajectories will be very different if they are separated by bodies. 
+if the difference of length of the neighboring trajectories is large. From Fig.~\ref{fig:Eroding20tort_traj},
+ we are able to tell the neighboring trajectories will be very 
+different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
+we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
+draw the pair of trajectories in the same color. For each pair of trajectories, 
+they are splitted by the body at the left side of the body, then
+one of them goes up and the other one goes down along the body 
+until they rejoin with each other at the right side of body.  
+The pair trajectories could be splitted by more than one body, 
+for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
+are splitted by three close bodies. 
 }

### 2019-06-12 docs/transport/erosion_transport.tex
add new figs in transport paper
do the result section in transport paper

@@
 where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.
-}
+
+We define the local tortuosity
+$$\tau(y)=\frac{\lambda(y)}{d}$$ 
+of the tracers at $y$ on the starting cross section
+where $\lambda(y)$ is the trajectory length of the tracer at y 
+and $d$ is the distance from the starting cross section to 
+the endding starting cross section. }
 
@@
 
-In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect
+In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
+from the starting cross section x = -1 to 
+the endding starting cross section x = 1 and 
+use the local tortuosity to analysis the effect
 of the geometrical structure on fluid velocity field. In
@@
 x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
-\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
-and y in [-1,1]). The velocity is continuous along the cross section and
+\times 10^{-4}$ at equal spreading tracers on the starting cross section.
+The velocity is continuous along the starting cross section and
 acting as several Poiseuille flows. This velocity graph is different
@@
 section to be the beginning of the flow before the fluid touches any
-body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity
-$\tau$ of the tracers at the cross section. This graph is not continuous
+body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
+$\tau(y)=\lambda(y)/d$
+of the tracers at $y$ on the starting cross section x = -1 
+where $d = 2$.
+This graph is not continuous
 and the jumps in $\tau$ mean that the initial neighbor tracers have been
@@
 
-In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
-and draw the trajectories of neighboring tracers in Fig.~\ref{fig:Eroding20tort_traj}
-if the difference of length of the neighboring trajectories is large. From Fig.~\ref{fig:Eroding20tort_traj},
+In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
+$\tau$ at two neighboring tracers 
+and draw the trajectories of neighboring tracers in 
+Fig.~\ref{fig:Eroding20tort_traj}
+if the difference of $\tau$ at the neighboring tracers is large. 
+From Fig.~\ref{fig:Eroding20tort_traj},
  we are able to tell the neighboring trajectories will be very 
@@
 until they rejoin with each other at the right side of body.  
-The pair trajectories could be splitted by more than one body, 
+Furthermore, the pair trajectories could be splitted by more than one body, 
 for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
@@
 \caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
-  touching eroding bodies and the eroding speed verse time.}
+  touching eroding bodies and the eroding speed verse time. }
 \end{figure}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
+\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
+(a) The 
+x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=6.2281
+\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
+(b) The local tortuosity $\tau(y)$ on the cross section x = -1.  }
 \end{figure}
@@
 {\color{red}
-This case is 100 bodies in a Hagen-Poiseuille flow.
+This case is 100 bodies in a Hagen-Poiseuille flow. The background
+flow is 
+\begin{align}
+  \UU(\xx)=U \left[
+  \begin{array}{c}
+    1-y^2 \\ 0
+  \end{array}
+  \right]
+\end{align}
+with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
+In Fig.~\ref{fig:Eroding100vort}
+
+In Fig.~\ref{fig:Eroding100tracer}
+
+In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
+x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
+\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
+and y in [-1,1]).
+
+In Fig.~\ref{fig:Eroding100tort_traj}
+
 }
@@
 
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/tort_local100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/diff_tort100}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/uminDumax100}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies}
+\end{figure}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
+\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of the length of 
+local tortuosity $\tau$ at two neighboring tracers in
+100 bodies eroding. The same color of a pair of trajectories 
+means they are from two neighboring tracers.}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-06-12 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 and $d$ is the distance from the starting cross section to 
-the endding starting cross section. }
+the end cross section. }
 
@@
 from the starting cross section x = -1 to 
-the endding starting cross section x = 1 and 
+the end cross section x = 1 and 
 use the local tortuosity to analysis the effect
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\color{red}
-This case is 100 bodies in a Hagen-Poiseuille flow. The background
-flow is 
-\begin{align}
-  \UU(\xx)=U \left[
-  \begin{array}{c}
-    1-y^2 \\ 0
-  \end{array}
-  \right]
-\end{align}
-with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
-In Fig.~\ref{fig:Eroding100vort}
-
-In Fig.~\ref{fig:Eroding100tracer}
-
-In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
-x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
-\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
-and y in [-1,1]).
-
-In Fig.~\ref{fig:Eroding100tort_traj}
-
-}
 \begin{figure}[H]
@@
 \end{figure}
+
+{\color{red}
+This case is 100 bodies in a Hagen-Poiseuille flow. The background
+flow is 
+\begin{align}
+  \UU(\xx)=U \left[
+  \begin{array}{c}
+    1-y^2 \\ 0
+  \end{array}
+  \right]
+\end{align}
+with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
+In Fig.~\ref{fig:Eroding100vort}
+
+To study the behavior of fluid in the porous media with multiple bodies, 
+we release 1000 equal spreeding tracers from the 
+starting cross section x = -1 and record their trajectories and velocities
+until they arrive the end cross section x = 1. 
+To understand the global action of fluid qualitatively, 
+we only draw 200 historical trajectories from x = -1 to x = 1 
+in Fig.~\ref{fig:Eroding100tracer}.
+
+To measure the local behavior of fluid quantitatively, 
+we use the velocities and local tortuosities at the starting cross section 
+to analysis the interaction of fluid and bodies until the end cross section 
+in Fig.~\ref{fig:Eroding100tort}.
+In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
+x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
+\times 10^{-4}$ at equal spreading tracers on the strating cross section.
+
+In Fig.~\ref{fig:Eroding100tort_traj}
+
+}
 \begin{figure}[H]
@@
 \includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
-\caption{\label{fig:Eroding100tracer} The trajectories of 200 tracers in the fluid with 100 bodies}
+\caption{\label{fig:Eroding100tracer} The historical trajectories of 
+200 tracers released at x = -1 in the fluid with multiple bodies}
 \end{center}

### 2019-06-12 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
-\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
-\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
-\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
-  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
-  tracers around the bodies. Since we use a Barycentric quadrature rule
-  and the fourth order Runge Kutta method, the tracers can be very close
-  to but not penetrate the bodies.}
-\end{center}
-\end{figure}
-
 {\color{red} 
@@
 right and join another tracers in the channel above the body. 
-
+}
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
+\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
+\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
+\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
+  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
+  tracers around the bodies. Since we use a Barycentric quadrature rule
+  and the fourth order Runge Kutta method, the tracers can be very close
+  to but not penetrate the bodies.}
+\end{center}
+\end{figure}
+{\color{red}
 In Fig.~\ref{fig:Eroding20area} we
@@
 seperated by the bodies. 
-
+}
+
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/porosity20dense}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/erodingspeed20dense}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
+  touching eroding bodies and the eroding speed verse time. }
+\end{figure}
+
+{\color{red}
 In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
@@
 }
-
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/porosity20dense}
-\caption{}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/erodingspeed20dense}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
-  touching eroding bodies and the eroding speed verse time. }
-\end{figure}
 

### 2019-06-12 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 \times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
-(b) The local tortuosity $\tau(y)$ on the cross section x = -1.  }
+(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
+(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
+(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
 \end{figure}
@@
 \includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top20}
-\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of the length of 
+\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
 local tortuosity $\tau$ at two neighboring tracers in
@@
 \includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
-\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of the length of 
+\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of 
 local tortuosity $\tau$ at two neighboring tracers in

### 2019-06-12 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 This graph is not continuous
-and the jumps in $\tau$ mean that the initial neighbor tracers have been
+and the jumps in $\tau$ mean that the initial neighboring tracers have been
 seperated by the bodies. 
@@
 %\end{subfigure}
-\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of U verse time.}
+\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of $U$ in log scale verse time. 
+Under fixed pressure drop condition, $U$ will be small initially,
+increase when bodies are eroding, and grow exponentially 
+to 1 when there is no body in the fluid. }
 \end{figure}
@@
   $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
-  $\sigma=10/256 $}
+  $\sigma=10/256$.}
 \end{center}
@@
 \caption{\label{fig:Eroding100tracer} The historical trajectories of 
-200 tracers released at x = -1 in the fluid with multiple bodies}
+200 tracers released at x = -1 in the fluid with multiple bodies.}
 \end{center}

### 2019-06-13 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 use the local tortuosity to analysis the effect
-of the geometrical structure on fluid velocity field. In
-Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
+of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
+In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
 x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
@@
 starting cross section x = -1 and record their trajectories and velocities
-until they arrive the end cross section x = 1. 
+until they arrive the end cross section x = 1 
+and the porosity of this geometric structure is 62.98 \%. 
 To understand the global action of fluid qualitatively, 
@@
 \times 10^{-4}$ at equal spreading tracers on the strating cross section.
+As in the case of 20 nearly touching bodies, the velocity is continuous along
+the starting cross section and acting as a Poiseuille flow in the channel between
+bodies. But the velocity of the fluid with 100 bodies on the starting cross section 
+changes more rapidly than the velocity of the fluid with 20 bodies 
+and the local maximum velocity of the fluid with 100 bodies 
+on the starting cross section is higher than the maximum velocity 
+of the fluid with 20 bodies. The reason of the rapid change and 
+high velocity on the starting cross section of 100-body case is because there are 
+more bodies near the starting cross section in
+100-body case than in the 20-body case. So the inlet flow in 100-body case
+will be separated into more branches than the flow in 20-body case. 
+Furthermore, under the fixed pressure drop condition the speed of flow in a channel is faster 
+when the channel is smaller.
 

### 2019-06-13 docs/transport/erosion_transport.tex
add new figs in transport paper
redo figs in transport paper

@@
 for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
-are splitted by three close bodies. 
+are splitted by two close bodies. (?)
 }
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/velocity_loc}
+\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
 \caption{}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/tort_local}
+\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
 \caption{}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/diff_tort}
+\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
 \caption{}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/uminDumax}
+\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
 \caption{}
@@
 \center
-\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top20}
+\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
 \caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 

### 2019-06-14 docs/transport/erosion_transport.tex
do the result in transport paper

@@
 In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
-x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
-\times 10^{-4}$ at equal spreading tracers on the starting cross section.
+x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
+\times 10^{-3}$ at equal spreading tracers on the starting cross section.
 The velocity is continuous along the starting cross section and
@@
 seperated by the bodies. 
+The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
 }
@@
 for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
-are splitted by two close bodies. (?)
+are splitted by two close bodies.
 }
@@
 (a) The 
-x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=6.2281
-\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
+x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
+\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
 (b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
@@
 the starting cross section and acting as a Poiseuille flow in the channel between
-bodies. But the velocity of the fluid with 100 bodies on the starting cross section 
-changes more rapidly than the velocity of the fluid with 20 bodies 
-and the local maximum velocity of the fluid with 100 bodies 
-on the starting cross section is higher than the maximum velocity 
-of the fluid with 20 bodies. The reason of the rapid change and 
-high velocity on the starting cross section of 100-body case is because there are 
+bodies. When the fluid is close to bodies
+the speed of fluid will be slow down because of the no-slip condition on the bodies
+and this causes the separated branches of the inlet flow.
+The maximum velocity of the fluid with 100 bodies on the starting cross 
+section is slower than the maximum velocity of the fluid with 20 bodies
+but the velocity in the case of 100 bodies 
+changes more rapidly than the velocity of the fluid with 20 bodies.
+The reason of the rapid change on the starting cross section of 
+100-body case is because there are 
 more bodies near the starting cross section in
-100-body case than in the 20-body case. So the inlet flow in 100-body case
+100-body case than in the 20-body case. 
+so the inlet flow in 100-body case
 will be separated into more branches than the flow in 20-body case.
-Furthermore, under the fixed pressure drop condition the speed of flow in a channel is faster 
-when the channel is smaller.
-
-In Fig.~\ref{fig:Eroding100tort_traj}
+
+In Fig.~\ref{fig:Eroding100tort}(b) we record the 
+local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
+It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is
+
+has more jumps than the one in the case of 20 bodies. 
+The jump in this graph means the neighboring trajectories are splitted by bodies
+so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
+since there are more bodies in the former case. In Fig.~\ref{fig:Eroding100tort}(c) 
+we use the data we got from local tortuosity $\tau(y)$
+to find the difference of $\tau$ at the neighboring tracers and
+draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
+in Fig.~\ref{fig:Eroding100tort_traj}. 
+The maximum of $\tau$ is 1.2547 and the minimum is 1.0003.
 

### 2019-06-14 docs/transport/erosion_transport.tex
do the result in transport paper

@@
 It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is
-
-has more jumps than the one in the case of 20 bodies. 
+is 1.2547 and the minimum is 1.0003. This function $\tau$
+has more jumps than the one in the case of 20 bodies but its maximum 
+is smaller than the maximum in the case of 20 bodies. 
 The jump in this graph means the neighboring trajectories are splitted by bodies
 so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
-since there are more bodies in the former case. In Fig.~\ref{fig:Eroding100tort}(c) 
-we use the data we got from local tortuosity $\tau(y)$
-to find the difference of $\tau$ at the neighboring tracers and
-draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
-in Fig.~\ref{fig:Eroding100tort_traj}. 
-The maximum of $\tau$ is 1.2547 and the minimum is 1.0003.
+since there are more bodies in the former case. To understand the meaning of jump 
+of $\tau$, we use the data we got from local tortuosity $\tau(y)$
+to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
+and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
+in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
+then rejoin with each other and it causes the difference of $\tau$ with respect to the neighboring trajectories.   
+We also can get the idea why the maximum value of $\tau$ is smaller 
+than the one in the case of 20 bodies . 
+The most of the bodies in this case are smaller than those in the case of 20 bodies.
+So when two neighboring trajectories are splitted on the left side by a smaller body they do not
+travel as far as the two splitted by a bigger body do after they rejoin on the right side.
 

### 2019-06-14 docs/transport/erosion_transport.tex
do the result in transport paper

@@
 \end{subfigure}
-\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
+\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies 
+when the porosity is 62.9 \% and the tortuosity is 2.1957.
 (a) The 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies}
+\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies when the porosity is 62.98 \%
+and the tortuosity is 2.2363.}
 \end{figure}

### 2019-06-14 docs/transport/erosion_transport.tex
do the tortuosity in transport paper
do the tortuosity in section 3 of transport paper

--- 2019-06-14 docs/transport/erosion_transport.tex
@@
 we characterize the transport.
-
-The tortuosity measures ...
-
-{\color{red} the definition of porosity is the ratio 
+{\color{red}
+To study the interaction of fluid and fixed bodies in the porous media,
+some parameters can be used to describle the interation quantitively,
+for example the porosity, the permeability, and the tortuosity. 
+The relation of porosity and tortuosity has been studied in~\cite{matyka2008tortuosity}.
+The definition of porosity is the ratio 
 $$\phi=\frac{A_v}{A_T}$$
-where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.
-
-We define the local tortuosity
-$$\tau(y)=\frac{\lambda(y)}{d}$$ 
-of the tracers at $y$ on the starting cross section
-where $\lambda(y)$ is the trajectory length of the tracer at y 
-and $d$ is the distance from the starting cross section to 
-the end cross section. }
+where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.}
+The tortuosity ...
+{\color{red} represents the weighted average travel distance of a tracer in a porous media. 
+The definition of tortuosity is 
+$$T=\frac{1}{d}\frac{\displaystyle\int_{S}u_x(y) \lambda(y)dy}{\displaystyle\int_{S}u_x(y)dy}$$
+where $S$ is an arbitrary cross section which is perpendicular to the x axis,
+$\lambda(y)$ is the length of streamline at y on $S$, 
+$u_x(y)$ is the component of velocity at y which is normal to $S$, and 
+$d$ is the distance from $S$ to the end cross section.
+It depends on not only the geometric structure but also the velocity of the fluid 
+which is different from the porosity since porosity only depends on the geometric structure.}
+{\color{red}Beisdes, the local tortuosity has been used to analysis 
+the local behavior of steamline around a body
+in~\cite{matyka2008tortuosity}.
+The definition of local tortuosity of the tracers at $y$ on $S$ is
+$$\tau(y)=\frac{\lambda(y)}{d}.$$ 
+}
 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
+\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies 
+when the porosity is 62.9 \% and the tortuosity is 1.0979.
 (a) The 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies}
+\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies when the porosity is 62.98 \%
+and the tortuosity is 1.1182.}
 \end{figure}

### 2019-06-14 docs/transport/erosion_transport.tex
do the result in transport paper

@@
 \end{subfigure}
-\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies 
-when the porosity is 62.9 \% and the tortuosity is 1.0979.
+\caption{\label{fig:Eroding20tort} The tortuosity study in the fluid with 20 nearly touching bodies.
 (a) The 
@@
 local tortuosity $\tau$ at two neighboring tracers in
- 20 nearly touching bodies eroding. The same color of a pair of trajectories 
+ 20 nearly touching bodies eroding when the porosity is 62.9 \% 
+and the tortuosity is 1.0979. The same color of a pair of trajectories 
 means they are from two neighboring tracers.}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies when the porosity is 62.98 \%
-and the tortuosity is 1.1182.}
+\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid with 100 bodies. }
 \end{figure}
@@
 local tortuosity $\tau$ at two neighboring tracers in
-100 bodies eroding. The same color of a pair of trajectories 
+100 bodies eroding when the porosity is 62.98 \%
+and the tortuosity is 1.1182. The same color of a pair of trajectories 
 means they are from two neighboring tracers.}

### 2019-06-18 docs/transport/erosion_transport.tex
do the tortuosity in section 3 of transport paper

@@
 $$\tau(y)=\frac{\lambda(y)}{d}.$$ 
-}
+To calculate tortuosity $T$ numerically, we use the simple quaduature rule
+$$T=\frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} u_x(y_i) \lambda(y_i) \Delta y_i}{\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i},$$ 
+where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.}
 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20tort} The tortuosity study in the fluid with 20 nearly touching bodies.
+\caption{\label{fig:Eroding20tort} The tortuosity study in the fluid with 
+20 nearly touching bodies when the porosity is 62.9 \%.
 (a) The 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid with 100 bodies. }
+\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid with 100 bodies 
+when the porosity is 62.98 \%.
+(a) The 
+x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.9021
+\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
+(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
+(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
+(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
 \end{figure}

### 2019-06-19 docs/transport/erosion_transport.tex
add new figs in transport paper
do the result section in transport paper

@@
 along the region of near contact.  This qualitative behavior is also
-observed In Figure~\ref{fig:Eroding20vort}, such as between bodies 3
+observed in Figure~\ref{fig:Eroding20vort}, such as between bodies 3
 \&4 and 15 \& 16.  However, by resolving bodies that are
@@
 bodies where the channel between the bodies is nearly perpendicular to
-the main flow direction (bodies 1 \& 6, 3 \& 9, and 13 \& 15), there is
+the main flow direction (bodies 1 \& 6, 3 \& 9, and 5 \& 13), there is
 very little shear stress and the effect of erosion is slight.
@@
 \begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
+ \begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
+\caption{100 bodies at t= 0.005}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
+\caption{99 bodies at t= 0.01}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
+\caption{94 bodies at t= 0.015}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
+\caption{82 bodies at t= 0.02}
+\end{subfigure}
 \caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
@@
   $\sigma=10/256$.}
-\end{center}
 \end{figure}
@@
 with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
-In Fig.~\ref{fig:Eroding100vort}
+We record the vorticity of 
+fluid during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
+measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four time steps.
+
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/gap_hist100_50}
+\caption{100 bodies with 318 gaps at t= 0.005}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/gap_hist100_100}
+\caption{99 bodies with 312 gaps at t= 0.01}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/gap_hist100_150}
+\caption{94 bodies with 294 gaps at t= 0.015}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/gap_hist100_200}
+\caption{82 bodies with 254 gaps at t= 0.02}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap} The histograms of gaps in the case of erosion of 100 bodies at four time steps.}
+\end{figure}
 
@@
 travel as far as the two splitted by a bigger body do after they rejoin on the right side. 
-
 }
+
 \begin{figure}[H]

### 2019-06-19 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 We record the vorticity of 
-fluid during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
-measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four time steps.
+fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
+measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
+Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
+the magnitude of the vorticity is larger,
 
@@
 local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
-It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is
+It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies
 is 1.2547 and the minimum is 1.0003. This function $\tau$
@@
 in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
-then rejoin with each other and it causes the difference of $\tau$ with respect to the neighboring trajectories.   
+then rejoin with each other and the splitting-rejoining behavior causes the difference of $\tau$ with respect to the neighboring trajectories.   
 We also can get the idea why the maximum value of $\tau$ is smaller 

### 2019-06-20 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.}
-The tortuosity ...
-{\color{red} represents the weighted average travel distance of a tracer in a porous media. 
+{\color{red} The tortuosity represents the weighted average travel distance of a tracer in a porous media. 
 The definition of tortuosity is 
@@
 which is different from the porosity since porosity only depends on the geometric structure.}
-{\color{red}Beisdes, the local tortuosity has been used to analysis 
-the local behavior of steamline around a body
-in~\cite{matyka2008tortuosity}.
+{\color{red}Beisdes, the local tortuosity~\cite{matyka2008tortuosity} has been used to analysis 
+the local behavior of steamline around a body. 
 The definition of local tortuosity of the tracers at $y$ on $S$ is
@@
 \includegraphics*[width =0.9\linewidth]{./figs/100b_50}
-\caption{100 bodies at t= 0.005}
+\caption{100 bodies and porosity = 55.54\% at t= 0.005}
 \end{subfigure}%
@@
 \includegraphics*[width =1.1\linewidth]{./figs/100b_100}
-\caption{99 bodies at t= 0.01}
+\caption{99 bodies and porosity = 62.98\% at t= 0.01}
 \end{subfigure}
@@
 \includegraphics*[width =0.9\linewidth]{./figs/100b_150}
-\caption{94 bodies at t= 0.015}
+\caption{94 bodies and porosity = 72.22\% at t= 0.015}
 \end{subfigure}%
@@
 \includegraphics*[width =1.1\linewidth]{./figs/100b_200}
-\caption{82 bodies at t= 0.02}
+\caption{82 bodies and porosity = 83.37\% at t= 0.02}
 \end{subfigure}
@@
 Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
-the magnitude of the vorticity is larger,
-
+the magnitude of the vorticity is larger 
+so the erosion is getting faster and faster 
+from the first snapshot to the forth one in Fig.~\ref{fig:Eroding100vort}.
+At t = 0.005 the porosity is 55.54\% and the most gap sizes between bodies are less than 0.015 in 
+Fig.~\ref{fig:Eroding100gap}(a). Since some of the bodies are vanished in the fluid, the numner of gaps 
+decreases and the gap sizes get larger and larger between the remaining bodies. 
+In Fig.~\ref{fig:Eroding100gap}(b) and (c) we still can see small gap sizes are in the majority but 
+it is not as concentrated as the one we see in  Fig.~\ref{fig:Eroding100gap}(a). 
 \begin{figure}[H]

### 2019-06-27 docs/transport/erosion_transport.tex
do the result section in transport paper

@@
 it is not as concentrated as the one we see in Fig.~\ref{fig:Eroding100gap}(a). 
+In Fig.~\ref{fig:Eroding100gap}(d) there are only 254 gaps between 82 bodies and 
+the distribution of gap sizes spreads over without any major pack.  
 \begin{figure}[H]
@@
 To study the behavior of fluid in the porous media with multiple bodies, 
-we release 1000 equal spreeding tracers from the 
-starting cross section x = -1 and record their trajectories and velocities
+we release 1000 tracers equispaced in $y$ from the 
+cross section x = -1 and record their trajectories and velocities
 until they arrive the end cross section x = 1 
@@
 in Fig.~\ref{fig:Eroding100tracer}. 
+When equispaced tracers are released in a 2D tube without any grains, 
+the streamlines are straight 
+and the intersection points of streamlines and any cross section are equispaced. 
+But it is not the same when there are bodies in the fluid. 
+In Fig.~\ref{fig:Eroding100tracer}
+even the tracers are equispaced in $y$ on the cross section $S$, 
+the streamlines have been push up and down by the bodies and
+some of them are close together.
 

### 2019-07-07 docs/transport/erosion_transport.tex
add new figs in transport paper
small changes to paper

@@
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  In Section~\ref{sec:DLPcomplex}, we
-show how the Stokes double-layer potential can also be expressed as the
-sum of a Laplacian double-layer potential 
+is an unknown density function.  In Section~\ref{s:DLPcomplex}, we show
+how the Stokes double-layer potential can also be expressed as the sum
+of a Laplacian double-layer potential 
 \begin{align}
@@
 Potential}
-\label{sec:DLPcomplex}
+\label{s:DLPcomplex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align}
+  \label{eqn:trajectories}
   \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
@@
 we characterize the transport.
-{\color{red}
-To study the interaction of fluid and fixed bodies in the porous media,
-some parameters can be used to describle the interation quantitively,
-for example the porosity, the permeability, and the tortuosity. 
-The relation of porosity and tortuosity has been studied in~\cite{matyka2008tortuosity}.
-The definition of porosity is the ratio 
-$$\phi=\frac{A_v}{A_T}$$
-where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.}
-{\color{red} The tortuosity represents the weighted average travel distance of a tracer in a porous media. 
-The definition of tortuosity is 
-$$T=\frac{1}{d}\frac{\displaystyle\int_{S}u_x(y) \lambda(y)dy}{\displaystyle\int_{S}u_x(y)dy}$$
-where $S$ is an arbitrary cross section which is perpendicular to the x axis,
-$\lambda(y)$ is the length of streamline at y on $S$, 
-$u_x(y)$ is the component of velocity at y which is normal to $S$, and 
-$d$ is the distance from $S$ to the end cross section.
-It depends on not only the geometric structure but also the velocity of the fluid 
-which is different from the porosity since porosity only depends on the geometric structure.}
-{\color{red}Beisdes, the local tortuosity~\cite{matyka2008tortuosity} has been used to analysis 
-the local behavior of steamline around a body. 
-The definition of local tortuosity of the tracers at $y$ on $S$ is
-$$\tau(y)=\frac{\lambda(y)}{d}.$$ 
-To calculate tortuosity $T$ numerically, we use the simple quaduature rule
-$$T=\frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} u_x(y_i) \lambda(y_i) \Delta y_i}{\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i},$$ 
-where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.}
+
+Key variables that are used to characterize porous media flow is the
+porosity (area of void space), permeability, and tortuosity.  The
+tortuosity, which  quantifies the amount of turning made by a
+streamline, is
+\begin{align*}
+  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
+  {\displaystyle\int_{S}u_x(y)\,dy},
+\end{align*}
+where $S$ is an cross-section perpendicular to the $x$ axis with length
+$d$, $\lambda(y)$ is the length of the streamline that is initizalized
+at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
+the velocity at the $y$-coordinate along $S$.  There have been efforts
+to relate the tortuosity to the porosity~\cite{matyka2008tortuosity},
+but these results can not be universal since the porosity which depends
+on only a single number, the tortuosity is affected by the distribution
+of pores within the porous network.  In addition to the hydraulic
+tortuosity, a local tortuosity can be used to analyze the local behavior
+of a streamline near a body~\cite{matyka2008tortuosity}.  The local
+tortuosity of a streamline initialized at $y$ along $S$ is
+\begin{align*}
+  \tau(y) = \frac{\lambda(y)}{d}.
+\end{align*}
 
@@
 \subsection{Efficiently Applying Quadrature}
-\label{sec:fmm}
+\label{s:fmm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 and~\eqref{eqn:PointsWallCutoff}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Streamlines and Tortuosity}
+\label{s:streamlines}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Having developed numerically accurate methods to compute the velocity
+$\uu$ at points close to the bodies, we are able to compute the
+trajectories of particles passing through an eroded body.  To find the
+trajectory governed by equation~\eqref{eqn:trajectories}, we use the
+fourth-order explicit Runge-Kutta method with a fixed time step size.
+Since our method is both high-order in time and space, we are able to
+simulate dynamics very close to the eroding bodies.  Resolving the flow
+in these small velocity regions is essential to accurately describe
+anomalous diffusion and mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.
+
+{\color{red}
+To calculate tortuosity $T$ numerically, we use the simple quaduature
+rule
+$$T=\frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} u_x(y_i) \lambda(y_i) \Delta y_i}{\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i},$$ 
+where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.}
 
@@
 
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d}
+\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
+ 20 nearly touching bodies with respect to two prosities. }
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %}
+%
+%{\color{red}
+%To study the interaction of fluid and fixed bodies in the porous media,
+%some parameters can be used to describle the interation quantitively,
+%for example the porosity, the permeability, and the tortuosity. 
+%The relation of porosity and tortuosity has been studied in~\cite{matyka2008tortuosity}.
+%The definition of porosity is the ratio 
+%$$\phi=\frac{A_v}{A_T}$$
+%where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.}
+%{\color{red} The tortuosity represents the weighted average travel distance of a tracer in a porous media. 
+%The definition of tortuosity is 
+%$$T=\frac{1}{d}\frac{\displaystyle\int_{S}u_x(y) \lambda(y)dy}{\displaystyle\int_{S}u_x(y)dy}$$
+%where $S$ is an arbitrary cross section which is perpendicular to the x axis,
+%$\lambda(y)$ is the length of streamline at y on $S$, 
+%$u_x(y)$ is the component of velocity at y which is normal to $S$, and 
+%$d$ is the distance from $S$ to the end cross section.
+%It depends on not only the geometric structure but also the velocity of the fluid 
+%which is different from the porosity since porosity only depends on the geometric structure.}
+%{\color{red}Beisdes, the local tortuosity~\cite{matyka2008tortuosity} has been used to analysis 
+%the local behavior of steamline around a body. 
+%The definition of local tortuosity of the tracers at $y$ on $S$ is
+%$$\tau(y)=\frac{\lambda(y)}{d}.$$ 
+%}

### 2019-07-07 docs/transport/erosion_transport.tex
small changes to paper

@@
 To avoid checking if all target point $\xx$
-satisfies~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
+satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
 First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
@@
 }
+\todo[inline]{This doesn't seem right.  $\xx$ is already on the boundary
+of the jth body, so $L_j$ should not be part of the criteria.  Should be
+something more like equation (44).}
 To determine if points on $\gamma_i$ are too close to the outer wall, we
 use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
-and that the bodies are all contained in $[-1,1] \times [-1,1]$.
-Therefore, we first check if
-{\color{red}
+and that the bodies are all contained in $[-1,1] \times [-1,1]$.  We
+first check if
 \begin{align}
@@
 \end{align}
-where $x_{\cc_i } $ is the x coordinate of $\cc_i$.}
-If body $\gamma_i$ satisfies this condition, for each point {\color{red}$\xx=(x,y) \in
-\gamma_i$}, we apply the Barycentric rule to points that satisfy
-{\color{red}
+where $x_{\cc_i } $ is the x coordinate of $\cc_i$. If body $\gamma_i$
+satisfies this condition, for each point $\xx=(x,y) \in \gamma_i$, we
+apply the Barycentric rule to points that satisfy
 \begin{align}
   \label{eqn:PointsWallCutoff}
-  \|y \pm 1\| <  \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
-\end{align}}
+  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
+\end{align}
 
@@
 and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
-find that {\color{red}$\alpha_\iin = 4$ and $\alpha_\out = 4$ }give sufficient
+find that $\alpha_\iin = 4$ and $\alpha_\out = 4$ give sufficient
 accuracy while keeping the number of points that require the expensive

### 2019-07-12 docs/transport/erosion_transport.tex
working on intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A continuation of the methods paper~\cite{qua-moo2018}.
-\paragraph{Governing Equations}
-\begin{equation}
-\label{eqn:erosionModel}
-\begin{split}
-  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation
-of momentum}\\
-\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
-\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
-bodies} \\
-\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
-velocity} \\
-\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
-&&\mbox{\em erosion model}.
-\end{split}
-\end{equation}
+Flow-induced erosion deteriorates and reshapes solid material over a
+range of scales.  At small scales, such as in groundwater flow,
+fluid-mechanical erosion significantly alters the geometry, and
+ultimately changes the process of transport through the media.  This
+paper extends a quadrature method first outlined by
+Barnett~\cite{bar2014} and Barnett, Wu, and
+Veerapaneni~\cite{bar-wu-vee2015} to simulate dense packings of eroding
+bodies, and then studies coarse-grained variables to characterize
+transport in eroded geometries.
+
+The authors previous work~\cite{qua-moo2018} developed numerical methods
+to simulate erosion of multiple bodies suspended in a Stokes flow.  The
+numerical methods can be broadly separated into two classes---a
+high-order method to solve the Stokes equations and the erosion rate in
+a complex geometry, and a time stepping method to evolve the eroding
+bodies.  The fluid solver uses a second-kind integral equation that is
+discretized with the trapezoid rule and solved iteratively with fast
+multipole accelerated GMRES, and then the trapezoid rule is used to
+compute the shear stress which is required to find the erosion rate.
+Once the erosion rate is computed, the bodies are eroded using a {\thL}
+coordinate system.  This allows us to maintain a discretization of the
+eroding bodies that is equally spaced in arclength, and is guaranteed to
+not tangle.
+
+The trapezoid rule is spectrally accurate discretization of integral
+equation formulations of the two-dimensional Stokes equation.  However,
+at a fixed resolution, the quadrature error of the trapezoid rule is
+arbitrarily large near the eroding bodies.  Therefore, simply upsampling
+to evaluate the velocity near the eroding bodies is not sufficient.  In
+our previous work~\cite{qua-moo2018}, we restrict the proximity between
+eroding bodies.  In addition, since we only visualized the velocity and
+vorticity in the fluid bulk once per time step, we used an expensive
+upsampling scheme.  However, upsampling is not practical when if it is
+required at each GMRES iteration or when simulating tracers in the flow.
+Therefore, in this paper, we apply a Barycentric quadrature rule to
+evaluate the Stokes double-layer potential~\cite{bar-wu-vee2015}.
+However, to compute derivatives of the flow, such as the vorticity and
+the shear stress, we extend this work to compute the required
+derivatives of the double-layer potential.
+
+Since erosion alters the geometry, it also affects coarse-grained
+variables.  In this paper, we examine two particular variables that can
+be used to understand transport in porous media---the tortuosity and the
+anomalous diffusion rates.   The tortuosity quantifies the twisting of
+particle trajectories in a medium, and in laminar flow, the tortuosity
+is one.  While a porous media often has a large tortuosity, as erosion
+creates preferential channels, large numbers of particles become more
+laminar, and we expect the tortuosity to decrease.  Anomalous diffusion
+is often used to describe transport in a porous media, and it quantifies
+the dispersion of particles in the flow.  Again, as the geometry erodes,
+particles behave more as a ballistic particle, and we expect less
+dispersion.  In this paper, we compute both the tortuosity and the
+anomalous diffusion rates of several geometries that form via erosion.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Continuing with our previous work~\cite{qua-moo2018}, we use a
-double-layer potential formulation for the velocity $\uu$.  The
-double-layer potential is
+We start by defining the main variables used to model erosion.  We
+consider flows inside a confined geometry $\Omega$ that contains $M$
+eroding bodies with boundary $\gamma_\ell$.  The boundary of the
+bounding geometry is $\Gamma$, and the fluid domain is bounded by $\bd
+\Omega = \Gamma \cup \gamma_1 \cup \cdots \cup \gamma_M$.  On each
+eroding body, $\nn$ is the normal vector pointing into the body, and
+$\ss$ is the unit tangent vector pointing in the counterclockwise
+direction.  The normal vector on $\Gamma$ is the outward unit normal.
+Neglecting inertial forces, the governing equations are
+\begin{equation}
+\label{eqn:erosionModel}
+\begin{split}
+  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation
+of momentum}\\
+\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
+\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
+bodies} \\
+\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
+velocity} \\
+\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
+&&\mbox{\em erosion model}.
+\end{split}
+\end{equation}
+Here, $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
+prescribed Hagen-Poiseuille velocity field, and
+\begin{align}
+  \tau = -(\nabla \uu + \nabla \uu^T) \nn \cdot \ss
+  \label{eqn:shearStress}
+\end{align}
+is the shear stress on the eroding bodies.  Continuing with our previous
+work~\cite{qua-moo2018}, we use a double-layer potential formulation for
+the velocity $\uu$.  The double-layer potential is
 \begin{align}
@@
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  In Section~\ref{s:DLPcomplex}, we show
-how the Stokes double-layer potential can also be expressed as the sum
-of a Laplacian double-layer potential 
-\begin{align}
-  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
-    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy
-\end{align}
-and its gradient.  Since the Laplacian double-layer potential can be
-written as a Cauchy integral
-\begin{align}
-  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
-  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy,
-  \label{eqn:laplaceComplex}
-\end{align}
-where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
-the Stokes double-layer potential can be written in terms of Cauchy
-integrals and its first derivative.  We also require the derivative of
-the Stokes double-layer potential which requires the second derivative
-of Cauchy integrals.
-
-We will be using quadrature formulae to compute $v$ and its derivatives
-that rely on the Cauchy integral theorem.  Since $v$ is holomorphic, its
-value only depends on its boundary data.  The boundary data satisfies
-the Sokhotski-Plemelj jump relation
-\begin{align}
-  \label{eqn:SPrelation}
-  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
-\end{align}
-Once the boundary data of $v$ is computed, we have
-\begin{align}
-  \label{eqn:cauchy}
-  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
-    \frac{v(y)}{y-x} \,dy, \quad
-  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^2} \, dy, \quad
-  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^3} \, dy.
-\end{align}
-for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
-\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
-function defined in equation~\eqref{eqn:laplaceComplex}, and the
-derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
-
-The Stokes double-layer potential itself can not represent all solutions
-of the incompressible Stokes equations.  Therefore, we complete the
-integral equation formulation following the work of Power and
-Miranda~\cite{pow-mir1987}.  The completion depends on the Stokeslets
-and rotlets
+is an unknown density function.  The Stokes double-layer potential
+itself can not represent all solutions of the incompressible Stokes
+equations.  Therefore, we complete the integral equation formulation
+following the work of Power and Miranda~\cite{pow-mir1987}.  The
+completion depends on the Stokeslets and rotlets
 \begin{align}
@@
 where $\ff$ is the prescribed Dirichlet boundary condition of the
-velocity on the outer wall and eroding bodies.
+velocity on the outer wall and eroding bodies.  Then, once the unknown
+density function is computed, the shear stress is found by first
+computing the deformation tensors of the double-layer potential,
+Stokeslets, and rotlets, and then forming the shear stress as defined in
+equation~\eqref{eqn:shearStress}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
-decomposed as
+Using the trapezoid rule to discretize the double-layer
+potential~\eqref{eqn:stokesDLP}, and to compute its deformation tensor,
+results in large quadrature errors if $\xx$ is close to $\bd\Omega$.  We
+apply a quadrature method that is constructed in terms of holomorphic
+functions, so we must first write all the layer potentials in terms of
+Cauchy integrals and their derivatives.  The first step is to write the
+Stokes double-layer potential as the sum of a Laplacian double-layer
+potential
+\begin{align}
+  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
+    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy,
+\end{align}
+and its gradient.  One such decomposition is
 \begin{equation}
@@
 \end{equation}
+Next, since the Laplacian double-layer potential can be written as the
+Cauchy integral
+\begin{align}
+  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
+  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x - y} \, dy,
+  \label{eqn:laplaceComplex}
+\end{align}
+where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
+the Stokes double-layer potential can be written in terms of Cauchy
+integrals and its first derivative.
+
+We also require the derivative of
+the Stokes double-layer potential which requires the second derivative
+of Cauchy integrals.
+
+We will be using quadrature formulae to compute $v$ and its derivatives
+that rely on the Cauchy integral theorem.  Since $v$ is holomorphic, its
+value only depends on its boundary data.  The boundary data satisfies
+the Sokhotski-Plemelj jump relation
+\begin{align}
+  \label{eqn:SPrelation}
+  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
+\end{align}
+Once the boundary data of $v$ is computed, we have
+\begin{align}
+  \label{eqn:cauchy}
+  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
+    \frac{v(y)}{y-x} \,dy, \quad
+  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^2} \, dy, \quad
+  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^3} \, dy.
+\end{align}
+for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
+\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
+function defined in equation~\eqref{eqn:laplaceComplex}, and the
+derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
+
+The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
+decomposed as
 All these integrals but the first are a gradient of a Laplace layer
@@
 where $S$ is an cross-section perpendicular to the $x$ axis with length
-$d$, $\lambda(y)$ is the length of the streamline that is initizalized
+$d$, $\lambda(y)$ is the length of the streamline that is initialized
 at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
@@
 \bd \Omega$ with $N_\out=1024$ points.  The Dirichlet boundary condition
-on $\Gamma$ is a Hagen-Poiseuille flow.  As the bodies erode, the flow
+on $\Gamma$ is a hagen-poiseuille flow.  As the bodies erode, the flow
 rate is adjusted to maintain the physical constant pressure drop

### 2019-07-15 docs/transport/erosion_transport.tex
editing in transport paper

@@
   \label{eqn:PointsBodyCutoff}
-  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi}
-+ \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right).
+  \|\xx - \cc_i\| < \frac{L_i}{2\pi}
++ \alpha_\iin \left(\frac{L_i}{N_\iin} \right).
 \end{align}
@@
 {\color{red}
-In Fig.~\ref{fig:Eroding20area} we
+In Fig.~\ref{fig:Eroding20area} (a) we
 measure the area occupied by bodies 
@@
 We record the flow rate $U$ quantifily in log scale
-during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
+during the eroding in Fig.~\ref{fig:Eroding20area} (b). 
 Since we simulate the erosion by applying fixed pressure drop 
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/erodingspeed20dense}
+\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
 \caption{}
 \end{subfigure}
-\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
-  touching eroding bodies and the eroding speed verse time. }
+\caption{\label{fig:Eroding20area}  (a) The area fraction of 20 nearly
+  touching eroding bodies and the eroding speed versus time. 
+(b) The incoming flow rate of $U$ in log scale versus time. 
+Under fixed pressure drop condition, $U$ will be small initially,
+increase when bodies are eroding, and grow exponentially 
+to 1 when there is no body in the fluid. }
 \end{figure}
@@
 }
-
-\begin{figure}[H]
-%\begin{subfigure}[b]{0.5\textwidth}
-\center
-\includegraphics*[width =0.5\linewidth]{./figs/flow_rate20dense}
-%\caption{}
-%\end{subfigure}%
-%\begin{subfigure}[b]{0.5\textwidth}
-%\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
-%\caption{}
-%\end{subfigure}
-\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of $U$ in log scale verse time. 
-Under fixed pressure drop condition, $U$ will be small initially,
-increase when bodies are eroding, and grow exponentially 
-to 1 when there is no body in the fluid. }
-\end{figure}
 

### 2019-07-15 docs/transport/erosion_transport.tex
added a todo
editing in transport paper

@@
 {\color{red}
-In Fig.~\ref{fig:Eroding20area} (a) we
+In Fig.~\ref{fig:Eroding20area}(a) we
 measure the area occupied by bodies 
@@
 We record the flow rate $U$ quantifily in log scale
-during the eroding in Fig.~\ref{fig:Eroding20area} (b). 
+during the eroding in Fig.~\ref{fig:Eroding20area}(b). 
 Since we simulate the erosion by applying fixed pressure drop 
@@
 When all the bodies have vanished completely the flow rate $U$ is equal to 1.
-In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
+In Fig.~\ref{fig:Eroding20area}(b), the flow rate increases exponentially 
 with growth rate close to $\ln10^4$.

### 2019-07-16 docs/transport/erosion_transport.tex
add new fig in transport paper

@@
 anomalous diffusion rates of several geometries that form via erosion.
+
+\todo[inline]{gap size growth as a function of time}
 
@@
 \center
-\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d}
+\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
 \caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
- 20 nearly touching bodies with respect to two prosities. }
+ 20 nearly touching bodies with respect to six porosities. }
 \end{figure}

### 2019-07-16 docs/transport/erosion_transport.tex
working on early parts of paper

@@
 is one.  While a porous media often has a large tortuosity, as erosion
-creates preferential channels, large numbers of particles become more
-laminar, and we expect the tortuosity to decrease.  Anomalous diffusion
-is often used to describe transport in a porous media, and it quantifies
-the dispersion of particles in the flow.  Again, as the geometry erodes,
-particles behave more as a ballistic particle, and we expect less
-dispersion.  In this paper, we compute both the tortuosity and the
-anomalous diffusion rates of several geometries that form via erosion.
-
-\todo[inline]{gap size growth as a function of time}
+increases the gaps between bodies, preferential channels are created,
+large numbers of particles become more laminar, and we expect the
+tortuosity to decrease.  Anomalous diffusion is often used to describe
+transport in a porous media, and it quantifies the dispersion of
+particles in the flow.  Again, as the geometry erodes, particles behave
+more as a ballistic particle, and we expect less dispersion.  In this
+paper, we compute both the tortuosity and the anomalous diffusion rates
+of several geometries that form via erosion.
 
@@
 \end{align}
-is the shear stress on the eroding bodies.  Continuing with our previous
-work~\cite{qua-moo2018}, we use a double-layer potential formulation for
-the velocity $\uu$.  The double-layer potential is
+is the shear stress on the eroding bodies.  Using the same approach as
+our previous work~\cite{qua-moo2018}, we use a double-layer potential
+formulation for the velocity $\uu$.  The double-layer potential is
 \begin{align}
@@
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  The Stokes double-layer potential
-itself can not represent all solutions of the incompressible Stokes
-equations.  Therefore, we complete the integral equation formulation
-following the work of Power and Miranda~\cite{pow-mir1987}.  The
-completion depends on the Stokeslets and rotlets
+is an unknown density function.  Since the Stokes double-layer potential
+can not represent all solutions of the incompressible Stokes equations,
+we complete the integral equation formulation by adding the Stokeslets
+and rotlets~\cite{pow-mir1987}
 \begin{align}
@@
     \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
-    \NN_0(\eeta](\xx), \quad \xx \in \bd\Omega, \\
+    \NN_0[\eeta](\xx), \quad \xx \in \bd\Omega, \\
   \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
@@
 where $\ff$ is the prescribed Dirichlet boundary condition of the
-velocity on the outer wall and eroding bodies.  Then, once the unknown
-density function is computed, the shear stress is found by first
-computing the deformation tensors of the double-layer potential,
-Stokeslets, and rotlets, and then forming the shear stress as defined in
-equation~\eqref{eqn:shearStress}.
+velocity on the outer wall and eroding bodies, and $\NN_0$ is the
+integral operator with kernel $\nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in
+\Gamma$, which removes the rank one null space resulting from the
+flux-free requirement of $\ff$. Once the unknown density function is
+computed, the shear stress is found by first computing the deformation
+tensors of the double-layer potential, Stokeslets, and rotlets, and then
+forming the shear stress as defined in equation~\eqref{eqn:shearStress}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Using the trapezoid rule to discretize the double-layer
-potential~\eqref{eqn:stokesDLP}, and to compute its deformation tensor,
-results in large quadrature errors if $\xx$ is close to $\bd\Omega$.  We
-apply a quadrature method that is constructed in terms of holomorphic
-functions, so we must first write all the layer potentials in terms of
-Cauchy integrals and their derivatives.  The first step is to write the
-Stokes double-layer potential as the sum of a Laplacian double-layer
-potential
-\begin{align}
-  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
-    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy,
-\end{align}
-and its gradient.  One such decomposition is
+The layer potential representations of $\uu$~\eqref{eqn:stokesDLP} and
+its gradient are written in terms of contour integrals in $\RR^2$. We
+will be applying a quadrature method for holomorphic functions, so we
+must convert these layer potentials in $\RR^2$ to contour integrals in
+$\CC$.  The first step is to write the Stokes double-layer potential as
+the sum of a Laplacian double-layer potential and its gradient
 \begin{equation}
@@
 where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
-the Stokes double-layer potential can be written in terms of Cauchy
-integrals and its first derivative.
-
-We also require the derivative of
-the Stokes double-layer potential which requires the second derivative
-of Cauchy integrals.
-
-We will be using quadrature formulae to compute $v$ and its derivatives
-that rely on the Cauchy integral theorem.  Since $v$ is holomorphic, its
-value only depends on its boundary data.  The boundary data satisfies
-the Sokhotski-Plemelj jump relation
+the Stokes double-layer potential can be written in terms of a complex
+integral and its first derivative.  In addition, the derivative of the
+Stokes double-layer potential can be written in terms of a complex
+integral and its first two derivatives.
+
+Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
+integral by first finding boundary data of $v$ which satisfies the
+Sokhotski-Plemelj jump relation
 \begin{align}
@@
 \end{align}
-Once the boundary data of $v$ is computed, we have
+Once the boundary data of $v$ is formed, we have
 \begin{align}
@@
 \end{align}
-for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
-\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
-function defined in equation~\eqref{eqn:laplaceComplex}, and the
-derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
-
-The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
-decomposed as
-All these integrals but the first are a gradient of a Laplace layer
-potential.  In addition, each component of the first integral can be
-written as a Cauchy integral with a complex-valued density
-function~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
-potential can be written as five Cauchy integrals and their derivatives
-with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
-The individual velocity components are
-\begin{align}
-  \label{eqn:cauchy1}
+for $x \in \Omega$.
+
+In equation~\eqref{eqn:cauchy}, $v(x)$ depends on the density function
+$\eta \in \CC$, so we use the notation $v[\eta](x)$ to denote the
+holomorphic function defined in equation~\eqref{eqn:laplaceComplex}, and
+the derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  Having
+introduced this notation, the components of the Stokes double-layer
+potential are~\cite{bar-wu-vee2015}
+\begin{equation}
+  \begin{aligned}
     u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
@@
          +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
-\end{align}
+  \end{aligned}
+  \label{eqn:cauchy1}
+\end{equation}
 where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
@@
 and $n \in \CC$ is the complex representation of the outward unit normal
-$\nn \in \RR^2$
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Cauchy Integral Representation of the Shear Stress}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-To compute the rate of erosion, we must compute the shear stress of the
-double-layer potential
-\begin{align}
-  \tau(\xx) = \left(\nabla \DDD[\eeta](\xx) + 
-    \nabla^T \DDD[\eeta](\xx) \right) \nn \cdot \ss,
-\end{align} where $\nn$ and $\ss$ are the unit normal and tangent
-vectors at $\xx$, respectively.  Each term of the gradient of the
-velocity field can be written in terms of Cauchy integrals.  For
-example,
-\begin{align}
-  \pderiv{u_1}{x_2} &= \Re(iv'[\tau_1](x)) + 
-      \Re(i v''[y \cdot \eta](x)) -
-      x_1\Re(i v''[\eta_1](x))  -
-      \Re(v'[\eta_2](x)) - x_2 \Re(iv''[\eta_2](x)) \\
-    &= -\Im(v''[\tau_1](x)) - 
-      \Im(v''[y \cdot \eta](x)) +
-      x_1\Im(v''[\eta_1](x)) -
-      \Re(v'[\eta_2](x)) + x_2 \Im(v''[\eta_2](x)).
-\end{align}
-Similarly, the other three components of $\nabla \DDD[\eeta]$ can be
-calculated
+$\nn \in \RR^2$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Cauchy Integral Representation for the Gradient of
+the Velocity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We require complex-valued representations of both the shear stress and
+the vorticity.  Both these quantities depend on the gradient of the
+velocity.  Each term of the gradient of the velocity field can be
+written in terms of Cauchy integrals.  Taking the derivatives of
+equation~\eqref{eqn:cauchy1} with respect to $x_1$ and $x_2$, we have 
 \begin{align}
@@
 \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Cauchy Integral Representation of the Vorticity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Having calculated all derivatives of the double-layer potential, the
-vorticity can written in terms of Cauchy integrals.  In particular,
+With these four expressions, the deformation tensor of the
+double-layer potential, $\ssigma^D = \frac{1}{2} (\nabla \uu + \nabla
+\uu^T)$, is written in terms of Cauchy integrals.  In addition, the
+vorticity can be written as
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Cauchy Integral Representation of the Pressure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The pressure of the double-layer potential is
-\begin{align}
-  p(\xx) = -\frac{1}{\pi} \int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(1 - 2 \frac{\rr \otimes \rr}{\rho^2} \right) \nn
-    \cdot \eeta(\yy) \, ds_\yy.
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Transport, Tracers, and Tortuosity}
@@
 Erosion leads to interesting porous geometries, and we are interested in
-characterizing transport in these geometries.  To characterize the
-transport, we first require tracer trajectories (streamlines) that are
-governed by
+characterizing transport in these geometries.  For porous media, two of
+the most important variables are the porosity and the permeability.
+However, additional properties of the flow are revealed by computing
+the anomalous diffusion rate, the tortuosity, and the distribution the
+gap sizes.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Anomalous Diffusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The dynamics of fluid in porous media can be characterized in terms of
+anomalous diffusion.  However, the anomalous diffusion rate depends on
+the properties of the geometry.  In addition to the porosity, the
+distribution of the grains affects the anomalous diffusion rates.  To
+quantify this rate, we require tracer trajectories that are governed by
 \begin{align}
@@
 \end{align}
-Instead of allowing the transport and erosion to happen simultaneously,
-we freeze the geometry and compute the streamlines in this fixed
-geometry.  Therefore, the velocity $\uu$ has no temporal dependence when
-we characterize the transport.
-
-Key variables that are used to characterize porous media flow is the
-porosity (area of void space), permeability, and tortuosity.  The
-tortuosity, which  quantifies the amount of turning made by a
-streamline, is
-\begin{align*}
+Given a trajectory, we define $\lambda_j(t)$ to be the distance
+travelled by the particle
+\begin{align}
+  \lambda_j(t) = \int_{0}^t \|\ss_j(\tau)\|\, d\tau.
+\end{align}
+Having formed $N_p$ trajectories, the first and second ensemble moments
+are
+\begin{align}
+  \langle \lambda \rangle (t) = 
+    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
+    \sigma_\lambda^2(t) = \frac{1}{N_p} 
+    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2.
+\end{align}
+If the particle spreading scales with time as $\sigma_\lambda^2 \sim
+t^\alpha$, with $\alpha < 1$, this indicates that the particle
+trajectories are sub-diffusive.  In contrast, if $\sigma_\lambda^2 \sim
+t^2$, the particle trajectories are undergoing a ballistic motion and
+are not affected by the grains.
+
+For early times when the geometry has not eroded, we expect the
+trajectories to be sub-diffusive.  However, as the bodies erode and
+straight preferential channels are formed, we expect the dynamics to
+resemble a ballistic motion.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tortuosity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The tortuosity of a geometry quantifies the average amount of turning
+made by a streamline.  Mathematically, it is defined as
+\begin{align}
   T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
   {\displaystyle\int_{S}u_x(y)\,dy},
-\end{align*}
+  \label{eqn:tortuosity1}
+\end{align}
 where $S$ is an cross-section perpendicular to the $x$ axis with length
@@
 at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
-the velocity at the $y$-coordinate along $S$.  There have been efforts
-to relate the tortuosity to the porosity~\cite{matyka2008tortuosity},
-but these results can not be universal since the porosity which depends
-on only a single number, the tortuosity is affected by the distribution
-of pores within the porous network.  In addition to the hydraulic
-tortuosity, a local tortuosity can be used to analyze the local behavior
-of a streamline near a body~\cite{matyka2008tortuosity}.  The local
-tortuosity of a streamline initialized at $y$ along $S$ is
+the velocity at the $y$-coordinate along $S$.  Under the assumptions
+that the flow is incompressible and not reentrant, the tortuosity can be
+equivalently measured as~\cite{dud-koz-mat2011}
+\begin{align}
+  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
+           {\displaystyle\int_\Omega u_x(\yy)\, d\yy}.
+  \label{eqn:tortuosity2}
+\end{align}
+The flow is reentrant if all streamlines connect the inlet to the
+outlet.  Recirculation zones are possible in viscous fluids, but they
+only constitute a small fraction of the total porous media.  Therefore,
+the tortuosity defined in equation~\eqref{eqn:tortuosity2} is an upper
+bound for the definition in equation~\eqref{eqn:tortuosity1}.  We have
+used formulas for a particular geometry, and the difference is
+negligible.  Since equation~\eqref{eqn:tortuosity2} does not require the
+additional work of computing particle trajectories, we use this
+definition for the tortuosity.
+
+There have been efforts to relate the tortuosity to the
+porosity~\cite{matyka2008tortuosity}, but these results can not be
+universal since the porosity which depends on only a single number, the
+tortuosity is affected by the distribution of pores within the porous
+network.  In addition to the hydraulic tortuosity, a local tortuosity
+can be used to analyze the local behavior of a streamline near a
+body~\cite{matyka2008tortuosity}.  The local tortuosity of a streamline
+initialized at $y$ along $S$ is
 \begin{align*}
@@
 \end{align*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Gap Distribution}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Cauchy Integral Representation of the Pressure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%The pressure of the double-layer potential is
+%\begin{align}
+%  p(\xx) = -\frac{1}{\pi} \int_{\bd\Omega} \frac{1}{\rho^2}
+%    \left(1 - 2 \frac{\rr \otimes \rr}{\rho^2} \right) \nn
+%    \cdot \eeta(\yy) \, ds_\yy.
+%\end{align}
+%
+%
+%

### 2019-07-23 docs/transport/erosion_transport.tex
working on erosion paper

@@
 \paragraph{Related Work}
+
+\begin{itemize}
+\item \cite{dar-mcc1998} show that if there is a region with high
+porosity, this greatly affects the relationships between the porosity
+and permeability.  Uses a Lattice-Boltzmann method.
+
+\item Continuous Time Random Walks
+
+\item Rothman in 1988 did CA for flow in 2D porous media
+
+\item ``Canductivity and permeability af rocks" 1984
+
+\item ``An Analytical Study on Natural Convection in Isotropic and .
+Anisotropic Porous Channels" shows how anisotropy affects heat transfer
+in porous media.
+
+\item "The Effect of Anisotropic Permeability on Free Convective
+Boundary Layer Flow in Porous Media" is the same as last bullet
+
+\item Near-singular integration such as regularization, QBX, Lagrange
+interpolation, panel-based quadrature, etc.
+
+\end{itemize}
 
@@
 \end{align}
+\todo[inline]{Need to be careful about interior and exterior limits}
 Once the boundary data of $v$ is formed, we have
@@
 at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
-the velocity at the $y$-coordinate along $S$.  Under the assumptions
-that the flow is incompressible and not reentrant, the tortuosity can be
-equivalently measured as~\cite{dud-koz-mat2011}
+the velocity at the $y$-coordinate along $S$.  Following~\cite{}, the
+trajectories are formed until they cross a second cross-section.  In our
+work, we always initialize the trajectories at $x=-1$ and stop them when
+they reach $x=1$.
+
+Under the assumptions that the flow is incompressible and not reentrant,
+the tortuosity can be equivalently measured as~\cite{dud-koz-mat2011}
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Gap Distribution}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Pore Throat Size}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{itemize}
+  \item Pore throat sizes affect many things such as first passage time,
+  mixing, chemical reactions, heat conduction, biological activities
+\end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We have shown that the velocity, shear stress, vorticity, and pressure
-of the double-layer potential can all be written in terms of Cauchy
-integrals and its first two derivatives.  Therefore, we require
-quadrature methods to evaluate the expressions in
-equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
-periodic, the trapezoid rule has spectral accuracy.  However, the
-integrand becomes nearly singular as $x$ approaches $\bd\Omega$, and the
-quadrature error is arbitrarily large for a fixed resolution.  There
-have been a variety of near-singular integration schemes developed, and
-we extend a method first outlined by Barnett et
-al.~\cite{bar-wu-vee2015} which we call the {\em Barycentric quadrature
-rule}.  This method first uses the density function $\tau(y)$ to compute
-the boundary data of $v$, denoted by $v^-(y)$.  Then, it makes use of
-the identity
+We have shown that the velocity, shear stress, and vorticity of the
+double-layer potential can all be written in terms of Cauchy integrals
+and its first two derivatives.  Therefore, we require quadrature methods
+to evaluate the expressions in equation~\eqref{eqn:cauchy}.  Since the
+integrands are all smooth and periodic, the trapezoid rule has spectral
+accuracy.  However, the integrand becomes nearly singular as $x$
+approaches $\bd\Omega$, and the quadrature error is arbitrarily large at
+a fixed resolution.  There have been a variety of near-singular
+integration schemes developed.   We opt to use a method first outlined
+by Barnett et al.~\cite{bar-wu-vee2015} which we call the {\em
+Barycentric quadrature rule}.  Quadrature rules for only the Cauchy
+integral and its first derivative are presented, and we extend this
+result to include the second derivative.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spatial Discretization}
+\label{s:spatialDiscretization}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+By using an integral equation formulation, we only have to discretize
+the one-dimensional boundary of the domain.  Therefore, we easily
+resolve complex geometries, and differentiation can be performed with
+spectral accuracy in Fourier space.  We discretize each eroding body
+$\gamma_k$ with $N_\iin$ points and discretize the outer wall $\Gamma$
+with $N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ is
+denoted by $\yy_j^0$, and the $j^{th}$ discretization point on
+$\gamma_k$ is denoted by $\yy^k_j$.  The discretization points are
+initially distributed evenly in arclength, and this equispacing is
+maintained for the entire simulation by using a {\thL}
+formulation~\cite{hou-low-she1994}.  In addition, we apply mild
+smoothing strategies~\cite{qua-moo2018} to avoid the corners that
+erosion inevitably develop.
+
+Given these discretization points, the velocity at $\xx$ can be
+approximated with the quadrature formula
+\begin{align}
+  \label{eqn:trap}
+  \uu(\xx) \approx \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j,
+\end{align}
+$w^k_j$ are quadrature weights (which depend on $N_\iin$, $N_\out$, and
+the lengths of $\gamma^k$), and $D$ is the kernel of the Stokes
+double-layer potential defined in Equation~\eqref{eqn:stokesDLP}.
+Matching the limiting behavior of the velocity with the boundary
+condition, the density function at the quadrature point solves
+\begin{align}
+  \UU_\ell &= \sum_{j=1}^{N_\out} 
+    w^0_j D(\yy^0_\ell,\yy^0_j) \eeta_j +
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
+    w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j, 
+    \quad \ell = 1,\ldots,N_\out \\
+  0 &= \sum_{j=1}^{N_\out} 
+    w^0_j D(\yy^m_\ell,\yy^0_j) \eeta_j +
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin} 
+    w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j, 
+    \quad \ell = 1,\ldots,N_\iin, \: m=1,\ldots,M. 
+\end{align}
+
+Once the density function is found at the quadrature points, the shear
+stress and vorticity can be approximated.  In particular,
+the deformation tensor is
+\begin{align}
+  \ssigma(\xx) = \frac{1}{2}(\nabla \uu + \nabla \uu^T) = 
+\end{align}
+and the vorticity is
+\begin{align}
+  w(\xx) = 
+\end{align}
+
+The choice of the quadrature rule determines the overall accuracy of the
+method.  To simulate dense suspensions of eroding bodies, it is
+imperative that the error of the chosen quadrature rule is bounded for
+independent of the configuration of the bodies.  To achieve this goal,
+we apply a Barycentric quadrature rule
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Barycentric Quadrature for $v''(x)$}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Barycentric quadrature rule developed by Barnett et
+al.~\cite{bar-wu-vee2015} approximates the double-layer potential for
+the velocity~\eqref{eqn:stokesDLP} with bounded error.  However, to
+compute the shear stress and vorticity, the method must be extended.  We
+first briefly describe the original Barycentric quadrature method, and
+then derive a necessary extension to simulate erosion.  We present the
+quadrature for a simply-connected domain $\Omega$, and the method
+naturally extends to the eroding geometry by applying the quadrature to
+each of its connected component.  The method starts with an underlying
+quadrature rule, and we use the trapezoid rule because of its superior
+accuracy for smooth periodic functions~\cite{tre-wei2014}.  Since the
+quadrature points are uniformly distributed, the quadrature weights are
+$w_j = L/N$, $j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
+
+We next identify all the discretization points, the normal vector, and
+the density function with their complex-value counterparts.  Then, all
+the layer potentials are a combination of a Cauchy integral and its
+first two derivatives.  Given a density function $\tau(y)$, the boundary
+data is solved using the Sokhotski-Plemelj jump
+relation~\eqref{eqn:SPrelation}.  If $x \in \Omega$ is too close to
+$\bd\Omega$ and the trapezoid rule is applied to the identity
 \begin{align}
   v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
-  \quad x \in \Omega.
-\end{align}
-
-Here, we briefly describe the Barycentric quadrature method, and then
-derive a necessary extension to simulate erosion.  The method starts
-with a quadrature rule with nodes $y_j \in \bd\Omega$ and weights $w_j$,
-$j=1,\ldots,N$.  We use the trapezoid rule because of its superior
-accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, at a
-fixed resolution, if $x$ is sufficiently close to $\bd\Omega$, each of
-the integrands in equation~\eqref{eqn:cauchy} are nearly-singular and
-the quadrature error is prohibitively large.  However, the trapezoid
-rule applied to the identity
+  \quad x \in \Omega,
+\end{align}
+the quadrature error is large since the integrand has a large
+derivative.  However, if the trapezoid rule is applied to
 \begin{align}
@@
 \end{align}
-has a uniformly bounded error since the integrand is not nearly-singular
-as $x$ approaches $\bd\Omega$.  That is,
+the quadrature error is bounded since the integrand and all its
+derivatives are bounded with respect to $x$. That is,
 \begin{align}
@@
 Rearranging for $v(x)$, we have
-\begin{align*}
+\begin{align}
   v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
-  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j},
-\end{align*}
-which is simply the trapezoid rule applied to the two integrals in the
-identity
-\begin{align}
-  v(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y)}{y-x}\, dy}
-    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
-\end{align}
-Of course, the denominator is simply $1$, but by applying the trapezoid
-rule to both integrands, the result is an error with a uniform bound.
-To compute $v'(x)$, the identity
+  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}.
+  \label{eqn:Baryv}
+\end{align}
+\todo[inline]{Need to cite work that Barnett et al. reference} 
+To approximate $v'(x)$, the trapezoid rule is applied to the two
+integrals in the identity
 \begin{align}
@@
 \end{align}
-is used, and applying the trapezoid rule
+resulting in the quadrature rule
 \begin{align}
@@
   {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Spatial Discretization}
-\label{s:spatialDiscretization}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-By using an integral equation formulation, we only have to discretize
-the boundary of the domain.  Therefore, we only have to discretize
-one-dimensional closed-curves, allowing us to use the spectrally
-accurate trapezoid rule~\cite{tre-wei2014} and Fourier differentiation.
-Moreover, since we only discretize the boundary of the domain, resolving
-the complex eroding bodies is straightforward.
-
-Consider eroding bodies $\gamma_k$, $k=1,\ldots,M$, in a fluid domain
-$\Omega$ with boundary $\Gamma$.  Let the length of $\Gamma$ be $L_{0}$,
-and the length of $\gamma_k$ be $L_k$.  We discretize each eroding body
-$\gamma_k$ with $N_\iin$ points and discretize $\Gamma$ with $N_\out$
-points.  The $j^{th}$ discretization point on $\Gamma$ is denoted by
-$\yy_j^0$, and the $j^{th}$ discretization point on $\gamma_k$ is
-denoted by $\yy^k_j$.  The discretization points are initially
-distributed evenly in arclength, and this equispacing is maintained for
-the entire simulation by using a {\thL}
-formulation~\cite{hou-low-she1994}.  In addition, we apply mild
-smoothing strategies~\cite{qua-moo2018} to avoid the corners that
-erosion inevitably develop.    Since the points are equispaced, the
-trapezoid rule to evaluate the velocity at a target point $\xx$ is
-\begin{align}
-  \label{eqn:trap}
-  \uu(\xx) \approx \frac{L_0}{N_\out} \sum_{j=1}^{N_\out} 
-    D(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \frac{L_k}{N_\iin} \sum_{j=1}^{N_\iin}
-    D(\xx,\yy^k_j) \eeta^k_j,
-\end{align}
-where $D$ is the kernel of the Stokes double-layer potential defined in
-Equation~\eqref{eqn:stokesDLP}.
-
-As previously mentioned, the quadrature error of the trapezoid rule is
-large if $\xx$ is close to $\bd\Omega$.  The proximity between $\xx$ and
-$\bd\Omega$ occurs in dense packings, and also when evaluating the
-velocity in the fluid bulk.  For these nearby points, instead of
-applying the trapezoid rule, the Barycentric quadrature rule is applied.
-In particular, the Stokes double-layer potential is decomposed into
-Laplacian double-layer potentials~\eqref{eqn:Stokes2Laplace}.  Then, for
-each of these Laplacian double-layer potentials, the density function is
-used to find the boundary values of the analytic function whose real
-part is the layer potential of interest~\eqref{eqn:SPrelation}.
-Finally, instead of applying the trapezoid rule to compute the Cauchy
-integrals, the quadrature rule outlined by Barnet et.~al is used
-\begin{align}
-  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
-    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}
-  \quad \text{and} \quad
-  v'(x) \approx \frac{\sum\limits_{j=1}^N 
-    \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
-    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
-  \label{eqn:vvpQuadrature}
-\end{align}
-Then, even if $x$ is close to $\bd\Omega$, the integrand is no longer
-nearly-singular and the accuracy of the trapezoid rule is bounded
-independent of $x$.  A similar identity identity involving $v'(x)$ also
-holds.   Now, applying the spectrally accurate trapezoid rule, the
-quadrature error of the Barycentric quadrature rule
-is uniformly bounded~\cite{bar-wu-vee2015}.  A slight modification of
-these formulae are applied if $x \in \Omega^{c}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Barycentric Quadrature for $v''(x)$}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
-developed~\cite{bar-wu-vee2015}, computing the shear stress and
-vorticity requires a Barycentric quadrature rule for $v''(x)$.  We mimic
-the approach developed in~\cite{bar-wu-vee2015}.  First, if $x \in
-\Omega$ and $n \in \mathbb{N}$, then 
+  \label{eqn:Baryvprime}
+\end{align}
+
+To compute the shear stress and vorticity, we require a Barycentric
+quadrature rule for $v''(x)$.  Mimicking the construction of the
+quadrature rule for $v(x)$ and $v'(x)$, we start with the second
+derivative of the Cauchy integral theorem
+\begin{align}
+  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
+      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x).
+\end{align}
+Using the identity
 \begin{align}
@@
       1, & n = 1, \\
-      0, & n > 1. \\
+      0, & n > 1, \\
     \end{array}
@@
 \end{align}
-Applying this identity to the Cauchy integral theorem for $v''(x)$, we
-have
-\begin{align}
-  0 &= \frac{1}{2\pi i} \int_{\bd\Omega} 
-      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x) \\
-%    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
-%      \frac{2v^{-}(y)}{(y-x)^3}\,dy - 
-%    \frac{1}{2\pi i} \int_{\bd\Omega} 
-%      \frac{(y-x)^2 v''(x)}{(y-x)^3}\,dy -
-%    \frac{1}{2\pi i} \int_{\bd\Omega} 
-%      \frac{2v(x)}{(y-x)^3}\, dy -
-%    \frac{1}{2\pi i} \int_{\bd\Omega} 
-%      \frac{2(y-x)v'(x)}{(y-x)^3}\, dy \\
-    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
+where $x \in \Omega$ and $n \in \mathbb{N}$, we have
+\begin{align}
+  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
       \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
@@
 \end{align}
-Since we have constructed the integrand so that it is bounded for for
-all $x \in \Omega$, the quadrature error of the trapezoid rule is
-acceptable.  Applying the quadrature rule and solving for $v''(x)$, the
-Barycentric quadrature rule for the second derivative is
+This integrand is constructed so that it is bounded for all $x \in
+\Omega$, and applying the trapezoid rule, we have
+\begin{align}
+  0 \approx  \sum_{j=1}^{N} 
+      \frac{2v^{-}(y_j) - v''(x)(y_j-x)^2 - 2v(x) - 2(y_j-x)v'(x)}
+      {(y_j-x)^3} w_j,
+\end{align}
+where the accuracy is independent of the proximity of $x$ to
+$\bd\Omega$. Solving for $v''(x)$, the Barycentric quadrature rule for
+the second derivative is
 \begin{align}
@@
 \end{align}
-To compute $v(x)$ and $v'(x)$, the Barycentric quadrature rule in
-equation~\eqref{eqn:vvpQuadrature} is used. If $x \in \Omega^c$, the
-identity
+This formula requires accurate approximations of $v(x)$ and $v'(x)$, but
+these are available in equations~\eqref{eqn:Baryv}
+and~\eqref{eqn:Baryvprime}.
+
+To apply the quadrature to multiply-connected domains, we must all
+consider exterior points $x \in \Omega^c$.  Mimicking the construction
+in~\cite{bar-wu-vee2015}, we use the quadrature rule
 \begin{align}
@@
 \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Efficiently Applying Quadrature}
+Again, values of $v(x)$ and $v'(x)$ are required, and these are
+available in~\cite{bar-wu-vee2015}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Efficiently Applying the Quadrature}
 \label{s:fmm}
@@
 \in \gamma_j$, we check if
-{\color{red}
 \begin{align}
@@
 \end{align}
-}
-\todo[inline]{This doesn't seem right.  $\xx$ is already on the boundary
-of the jth body, so $L_j$ should not be part of the criteria.  Should be
-something more like equation (44).}
 To determine if points on $\gamma_i$ are too close to the outer wall, we
@@
 accuracy while keeping the number of points that require the expensive
-Barycentric quadrature rule to a minimum.
+Barycentric quadrature rule to a minimum.  We use these values for all
+of our numerical simulations.
 
@@
 Since our method is both high-order in time and space, we are able to
-simulate dynamics very close to the eroding bodies.  Resolving the flow
-in these small velocity regions is essential to accurately describe
-anomalous diffusion and mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.
-
-{\color{red}
-To calculate tortuosity $T$ numerically, we use the simple quaduature
-rule
-$$T=\frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} u_x(y_i) \lambda(y_i) \Delta y_i}{\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i},$$ 
-where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Results}
-\label{s:results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this section, we present the numerical simulations of dense packings
-of eroding bodies.  The computational domain $\Omega$ is a rectangle
-$[-3,3] \times [-1,1]$ with rounded off corners and we place bodies only
-in $[-1,1] \times [-1,1]$.  For all simulations, we discretize $\Gamma =
-\bd \Omega$ with $N_\out=1024$ points.  The Dirichlet boundary condition
-on $\Gamma$ is a hagen-poiseuille flow.  As the bodies erode, the flow
-rate is adjusted to maintain the physical constant pressure drop
-boundary condition.  To maintain this pressure drop, we compute the
-pressure at near the inlet and outlet at each time step as described in
-our previous work~\cite{qua-moo2018}.
-
-The initial shape of the eroding body $\gamma_i$ is a circle centered at
-$\cc_i$ with radius $r_i$ and length $L_i = 2\pi r_i$, and each
-$\gamma_i$ is discretized with $N_\iin$ points.  Using the annealing
-algorithm described in Section ???, the initial configuration has the
-desired initial porosity, and the minimum separation between any pair of
-bodies and between the bodies and solid wall is $d$.  A no-slip boundary
-condition is imposed on $\gamma$.  To round off inevitable corners on
-the eroding bodies, we apply smoothing the smoothing parameters {\color{red}
-$\eps=15/256$ and $\sigma=10/256$,} as described in~\cite{qua-moo2018}, for all
-simulations.
-
+simulate dynamics very close to the eroding bodies (Figure~\ref{fig:}
+\todo[inline]{reference a figure or two from the results section)}.
+Resolving the flow in these small velocity regions is essential to
+accurately describe anomalous diffusion and
+mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.
+
+To calculate tortuosity $T$, we use the simple quadrature rule
+\begin{align}
+  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} 
+    u_x(y_i) \lambda(y_i) \Delta y_i}
+  {\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i}, 
+\end{align}
+where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Time Integration}
+\label{s:time}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 We reuse the time stepping method outlined in our previous
@@
 
-Finally, the parameters used to determine if a point uses the trapezoid
-or Barycentric quadrature rule are $\alpha_\iin = 4$ and
-$\alpha_\out=4$.
+\todo[inline]{Talk about time integration for erosion and for tracers}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Results}
+\label{s:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this section, we apply our new quadrature method to simulate erosion
+of several different configurations of eroding bodies.  The fluid domain
+is $\Omega$ whose outer solid walls is a rectangle $[-3,3] \times
+[-1,1]$ with rounded off corners.  We only place bodies only in $[-1,1]
+\times [-1,1]$.  For all simulations, we discretize $\Gamma = \bd
+\Omega$ with $N_\out=1024$ points.  For all but the first example, the
+Dirichlet boundary condition on $\Gamma$ is a hagen-poiseuille flow.  As
+the bodies erode, the flow rate is adjusted to maintain the physical
+constant pressure drop boundary condition.  To maintain this pressure
+drop, we compute the pressure at near the inlet and outlet at each time
+step as described in our previous work~\cite{qua-moo2018}.
+
+The initial shape of the eroding body $\gamma_i$ is a circle centered at
+$\cc_i$ with radius $r_i$ and length $L_i = 2\pi r_i$, and each
+$\gamma_i$ is discretized with $N_\iin$ points.  A no-slip boundary
+condition is imposed on $\gamma_i$.  The initial configuration is
+constructed with an annealing algorithm and has the desired initial
+porosity, and a user-specified minimum distance between any two eroding
+bodies and the eroding body and solid wall.  To round off inevitable
+corners on the eroding bodies, for all simulations we apply smoothing
+the smoothing parameters $\eps=15/256$ and $\sigma=10/256$, as described
+in~\cite{qua-moo2018}.
+
+The common characteristic of each of the experiments is near-contact
+between the eroding bodies and outer walls. Once we have simulated
+erosion, we compute velocities, streamlines, trajectories, and vorticity
+so that the flow can be visualized and analyzed.  The experiments we
+perform are:
+\begin{itemize}
+  \item{\bf Single Body Close to a Wall}: We consider a single eroding
+  body close to the outer wall at $y=-1$.  Using a shear flow that
+  vanishes on $y=-1$, we compare the eroding body's shape to a similar
+  experiment of Spagnolie and Mitchell~\cite{mit-spa2017}.
+
+  \item{\bf 20 Bodies at a Medium Porosity}: We consider 20 eroding
+  bodies with a medium initial porosity.  After computing accurate
+  tracer trajectories, the tortuosity and anomalous diffusion rates are
+  computed and compared to those of an open channel.
+
+  \item{\bf 20 Bodies at a Low Porosity}: We consider 20 eroding bodies
+  with a low initial porosity.  We examine the effect of the lower
+  porosity on the tortuosity and anomalous diffusion rates.
+
+  \item{\bf 50 Bodies at a Low Porosity}: We consider 50 eroding bodies
+  with a low initial porosity.  In addition to the tortuosity and
+  anomalous diffusion rates, we compute distributions of the pore throat
+  sizes and examine their response to erosion.
+
+  \item{\bf 100 Bodies at a Medium Porosity}: We consider 100 eroding
+  bodies with a medium porosity.  We compute the tortuosity, anomalous
+  diffusion rates, and the pore throat distributions.
+\end{itemize}
 

### 2019-07-23 docs/transport/erosion_transport.tex
add figs in transport paper
add modified figs in transport paper

@@
 Initially, $U=1$, and then $U$ is updated at each time step so that the
-pressure drop from $x=-2$ to $x=2$ remains constant.  Snapshots of the
+pressure drop from $x=-2$ to $x=2$ remains constant.  
+{\color{red}
+We record the flow rate $U$ quantifily in log scale
+during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
+Since we simulate the erosion by applying fixed pressure drop 
+the flow rate $U$ is small when there are many bodies in the fluid and 
+when the area occupied by bodies is getting smaller $U$ is getting larger.
+When all the bodies have vanished completely the flow rate $U$ is equal to 1.
+In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
+with growth rate close to $\ln10^4$. }
+
+\begin{figure}[H]
+\center
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
+%\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20flowrate} The incoming flow rate of $U$ in log scale versus time. 
+Under fixed pressure drop condition, $U$ will be small initially,
+increase when bodies are eroding, and grow exponentially 
+to 1 when there is no body in the fluid. }
+\end{figure}
+
+Snapshots of the
 bodies at four equispaced times are shown in
@@
 \begin{center}
-  \includegraphics[height=0.43\textwidth]{./figs/20b_dense1}
-  \includegraphics[height=0.43\textwidth]{./figs/20b_dense101} \\
-  \includegraphics[height=0.43\textwidth]{./figs/20b_dense201}
-  \includegraphics[height=0.43\textwidth]{./figs/20b_dense301}
+  \includegraphics[height=0.23\textwidth]{./figs/20b_dense1}
+  \includegraphics[height=0.23\textwidth]{./figs/20b_dense101}
+  \includegraphics[height=0.23\textwidth]{./figs/20b_dense201}
+  \includegraphics[height=0.23\textwidth]{./figs/20b_dense301}
 %\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
@@
 Barycentric quadrature formula, streamlines very close to the eroding
-bodies are illustrated in Figure~\ref{fig:Eroding20zoom}.
+bodies are illustrated in the last frame of Figure~\ref{fig:Eroding20tracer}.
 
@@
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b60}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}\\
-
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b120}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b180}\\
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
 
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b240}
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}\\
+
+%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
+%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b240}
+%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
 \caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
-  the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.
+  the fluid with 20 bodies. The five first snapshots are evenly spaced in time.
   The tracers are evenly spread in the $y$-direction and released at
-  $x=-1$.}
+  $x=-1$. The sixth frame is a zoom window of the fifth frames. 
+Since we use a Barycentric quadrature rule
+  and the fourth order Runge Kutta method, the tracers can be very close
+  to but not penetrate the bodies.}
 \end{center}
@@
 the tracers will not only travel horizontally but also vertically.  In
-the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
-climb up from right to left around the body.  There are zoom windows of
-the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
-they are taken from the last three frames of
-Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
-Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
+the fifth frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
+climb up from right to left around the body.  There is a zoom windows of
+the climbing tracers trajectories in the last frame of Fig.~\ref{fig:Eroding20tracer} and
+they are taken from the fifth frame of
+Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the last frame of 
+Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
 from the channel below the body, climb up to the left, then go to the
@@
 }
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
-\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
-\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
-\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
-  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
-  tracers around the bodies. Since we use a Barycentric quadrature rule
-  and the fourth order Runge Kutta method, the tracers can be very close
-  to but not penetrate the bodies.}
-\end{center}
-\end{figure}
+%\begin{figure}[H]
+%\begin{center}
+%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
+%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
+%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
+%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
+%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
+%  tracers around the bodies. Since we use a Barycentric quadrature rule
+ % and the fourth order Runge Kutta method, the tracers can be very close
+ % to but not penetrate the bodies.}
+%\end{center}
+%\end{figure}
 {\color{red}
-In Fig.~\ref{fig:Eroding20area}(a) we
-measure the area occupied by bodies 
-during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
-[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
-when more and more bodies are vanished in the fluid and 
-the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
-[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
-all the bodies are vanished completely.
-
-We record the flow rate $U$ quantifily in log scale
-during the eroding in Fig.~\ref{fig:Eroding20area}(b). 
-Since we simulate the erosion by applying fixed pressure drop 
-the flow rate $U$ is small when there are many bodies in the fluid and 
-when the area occupied by bodies is getting smaller $U$ is getting larger.
-When all the bodies have vanished completely the flow rate $U$ is equal to 1.
-In Fig.~\ref{fig:Eroding20area}(b), the flow rate increases exponentially 
-with growth rate close to $\ln10^4$.
 
@@
 
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/porosity20dense}
-\caption{}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding20area}  (a) The area fraction of 20 nearly
-  touching eroding bodies and the eroding speed versus time. 
-(b) The incoming flow rate of $U$ in log scale versus time. 
-Under fixed pressure drop condition, $U$ will be small initially,
-increase when bodies are eroding, and grow exponentially 
-to 1 when there is no body in the fluid. }
-\end{figure}
-
 {\color{red}
@@
 $\tau$ at two neighboring tracers 
-and draw the trajectories of neighboring tracers in 
-Fig.~\ref{fig:Eroding20tort_traj}
+and draw the trajectories of neighboring tracers
 if the difference of $\tau$ at the neighboring tracers is large. 
-From Fig.~\ref{fig:Eroding20tort_traj},
+From Fig.~\ref{fig:Eroding20tort}(c),
  we are able to tell the neighboring trajectories will be very 
-different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
+different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort}(c)
 we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
@@
 Furthermore, the pair trajectories could be splitted by more than one body, 
-for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
+for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
 are splitted by two close bodies.
@@
 \begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
+\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{\textwidth}
 \includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
 \caption{}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
+\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
 \includegraphics*[width =\linewidth]{./figs/tort_local20_268}
@@
 \end{subfigure}
+\end{subfigure}
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
-\caption{}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
+\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
 \caption{}
@@
 (b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
-(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
-(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
-\end{figure}
-
-\begin{figure}[H]
-\center
-\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
-\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
+(c) The largest 10 difference of 
 local tortuosity $\tau$ at two neighboring tracers in
@@
 means they are from two neighboring tracers.}
+%(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
+%(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
 \end{figure}
+{\color{red}
+In Fig.~\ref{fig:Eroding20area} we
+measure the area occupied by bodies 
+during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
+[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
+when more and more bodies are vanished in the fluid and 
+the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
+[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
+all the bodies are vanished completely.}
+
+\begin{figure}[H]
+\center
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/porosity20dense}
+%\caption{}
+\end{subfigure}%
+\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
+  touching eroding bodies and the eroding speed versus time. 
+}
+\end{figure}
+
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
+%\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
+%local tortuosity $\tau$ at two neighboring tracers in
+% 20 nearly touching bodies eroding when the porosity is 62.9 \% 
+%and the tortuosity is 1.0979. The same color of a pair of trajectories 
+%means they are from two neighboring tracers.}
+%\end{figure}
 
@@
 \begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
+\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{\textwidth}
 \includegraphics*[width =\linewidth]{./figs/velocity_loc100}
 \caption{}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
+\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
 \includegraphics*[width =\linewidth]{./figs/tort_local100}
@@
 \end{subfigure}
+\end{subfigure}
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/diff_tort100}
-\caption{}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/uminDumax100}
+\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
 \caption{}
@@
 (b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
-(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
-(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
+(c) The historical trajectories of 
+200 tracers released at x = -1 in the fluid with multiple bodies.}
+%(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
+%(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
 \end{figure}

### 2019-07-24 docs/transport/erosion_transport.tex
editing in transport paper

@@
 {\color{red}
-We record the flow rate $U$ quantifily in log scale
+We
+measure the area occupied by bodies 
+during the eroding and record the flow rate $U$ quantifily in log scale
 during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
@@
 the flow rate $U$ is small when there are many bodies in the fluid and 
-when the area occupied by bodies is getting smaller $U$ is getting larger.
+when the area fraction is getting smaller $U$ is getting larger.
+In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
+[-1,1]$ is occupied by 20 bodies initially and the flow rate U starts from $9.86\times 10^{-5}$. 
+Then the eroding speed is increasing
+when more and more bodies are vanished in the fluid and 
+the maximum eroding speed happens when the area fraction equals 7.57\% 
+which is occupied by 8 bodies.
 When all the bodies have vanished completely the flow rate $U$ is equal to 1.
-In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
+In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate U increases exponentially 
 with growth rate close to $\ln10^4$. }
@@
 \begin{figure}[H]
-\center
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/porosity20dense}
+\caption{}
+\end{subfigure}
 \begin{subfigure}[b]{0.5\textwidth}
 \includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
-%\caption{}
+\caption{}
 \end{subfigure}
-\caption{\label{fig:Eroding20flowrate} The incoming flow rate of $U$ in log scale versus time. 
+\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20 nearly
+ touching eroding bodies and the eroding speed versus time. 
+(b) The incoming flow rate of $U$ in log scale versus time. 
 Under fixed pressure drop condition, $U$ will be small initially,
@@
 %(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
-\end{figure}
-{\color{red}
-In Fig.~\ref{fig:Eroding20area} we
-measure the area occupied by bodies 
-during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
-[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
-when more and more bodies are vanished in the fluid and 
-the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
-[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
-all the bodies are vanished completely.}
-
-\begin{figure}[H]
-\center
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/porosity20dense}
-%\caption{}
-\end{subfigure}%
-\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
-  touching eroding bodies and the eroding speed versus time. 
-}
 \end{figure}

### 2019-07-24 docs/transport/erosion_transport.tex
editing in transport paper

@@
 In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
-[-1,1]$ is occupied by 20 bodies initially and the flow rate U starts from $9.86\times 10^{-5}$. 
+[-1,1]$ is occupied by 20 bodies initially and the flow rate $U$ starts from $9.86\times 10^{-5}$. 
 Then the eroding speed is increasing
@@
 When all the bodies have vanished completely the flow rate $U$ is equal to 1.
-In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate U increases exponentially 
+In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate $U$ increases exponentially 
 with growth rate close to $\ln10^4$. }
@@
   The tracers are evenly spread in the $y$-direction and released at
-  $x=-1$. The sixth frame is a zoom window of the fifth frames. 
+  $x=-1$. The bottom right frame is a zoom window of the bottom middle frames. 
 Since we use a Barycentric quadrature rule
@@
 12, and 6 \& 19.  We can get a better understanding of this channel from
-the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In the
-top three frames of  Fig.~\ref{fig:Eroding20tracer}, the flow (or
-tracer) first comes from three small channels between outer wall \& body
+the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In Fig.~\ref{fig:Eroding20tracer}, 
+the flow (or tracer) first comes from three small channels between outer wall \& body
 10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
@@
 
-Furthermore, how long the body lasts for depends on not only the size of
+Furthermore, how long the body lasts in the fluid depends on not only the size of
 the body but also the location of the body.  For example, the first
@@
 the tracers will not only travel horizontally but also vertically.  In
-the fifth frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
+the bottom middle frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
 climb up from right to left around the body.  There is a zoom windows of
-the climbing tracers trajectories in the last frame of Fig.~\ref{fig:Eroding20tracer} and
-they are taken from the fifth frame of
-Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the last frame of 
+the climbing tracers trajectories in the bottom right frame of Fig.~\ref{fig:Eroding20tracer} and
+they are taken from the bottom middle frame of
+Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the bottom right frame of 
 Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go

### 2019-07-24 docs/transport/erosion_transport.tex
editing in transport paper

@@
 %\end{figure}
-{\color{red}
-
-In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
-from the starting cross section x = -1 to 
-the end cross section x = 1 and 
-use the local tortuosity to analysis the effect
-of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
-In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
-x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
-\times 10^{-3}$ at equal spreading tracers on the starting cross section.
-The velocity is continuous along the starting cross section and
-acting as several Poiseuille flows. This velocity graph is different
-from the one in~\cite{matyka2008tortuosity} since we choose our cross
-section to be the beginning of the flow before the fluid touches any
-body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
-$\tau(y)=\lambda(y)/d$
-of the tracers at $y$ on the starting cross section x = -1 
-where $d = 2$.
-This graph is not continuous 
-and the jumps in $\tau$ mean that the initial neighboring tracers have been
-seperated by the bodies. 
-The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
-}
-
-{\color{red}
-In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
-$\tau$ at two neighboring tracers 
-and draw the trajectories of neighboring tracers
-if the difference of $\tau$ at the neighboring tracers is large. 
-From Fig.~\ref{fig:Eroding20tort}(c),
- we are able to tell the neighboring trajectories will be very 
-different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort}(c)
-we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
-draw the pair of trajectories in the same color. For each pair of trajectories, 
-they are splitted by the body at the left side of the body, then
-one of them goes up and the other one goes down along the body 
-until they rejoin with each other at the right side of body.  
-Furthermore, the pair trajectories could be splitted by more than one body, 
-for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
-are splitted by two close bodies.
-}
 
@@
 \end{figure}
+
+{\color{red}
+In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
+from the starting cross section x = -1 to 
+the end cross section x = 1 and 
+use the local tortuosity to analysis the effect
+of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
+In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
+x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
+\times 10^{-3}$ at equal spreading tracers on the starting cross section.
+The velocity is continuous along the starting cross section and
+acting as several Poiseuille flows. This velocity graph is different
+from the one in~\cite{matyka2008tortuosity} since we choose our cross
+section to be the beginning of the flow before the fluid touches any
+body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
+$\tau(y)=\lambda(y)/d$
+of the tracers at $y$ on the starting cross section x = -1 
+where $d = 2$.
+This graph is not continuous 
+and the jumps in $\tau$ mean that the initial neighboring tracers have been
+seperated by the bodies. 
+The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
+}
+
+{\color{red}
+In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
+$\tau$ at two neighboring tracers 
+and draw the trajectories of neighboring tracers
+if the difference of $\tau$ at the neighboring tracers is large. 
+From Fig.~\ref{fig:Eroding20tort}(c), we collect the 10 largest difference of $\tau$ 
+at the neighboring tracers and 
+draw the pair of trajectories in the same color and 
+are able to tell the neighboring trajectories will be very 
+different if they are separated by bodies.
+For each pair of trajectories, 
+they are splitted by the body at the left side of the body, then
+one of them goes up and the other one goes down along the body 
+until they rejoin with each other at the right side of body.  
+Furthermore, the pair trajectories could be splitted by more than one body, 
+for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
+are splitted by two close bodies.
+}
 

### 2019-07-24 docs/transport/erosion_transport.tex
editing in transport paper

@@
 we only draw 200 historical trajectories from x = -1 to x = 1 
-in Fig.~\ref{fig:Eroding100tracer}. 
+in Fig.~\ref{fig:Eroding100tort}(a). 
 When equispaced tracers are released in a 2D tube without any grains, 
@@
 But it is not the same when there are bodies in the fluid. 
-In Fig.~\ref{fig:Eroding100tracer}
+In Fig.~\ref{fig:Eroding100tort}(a)
 even the tracers are equispaced in $y$ on the cross section $S$, 
@@
 to analysis the interaction of fluid and bodies until the end cross section 
-in Fig.~\ref{fig:Eroding100tort}.
-In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
+in Fig.~\ref{fig:Eroding100tort}(b) and (c).
+In Fig.~\ref{fig:Eroding100tort}(b) the graph represents the ratio of the
 x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
@@
 
-In Fig.~\ref{fig:Eroding100tort}(b) we record the 
+In Fig.~\ref{fig:Eroding100tort}(c) we record the 
 local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
@@
 so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
-since there are more bodies in the former case. To understand the meaning of jump 
-of $\tau$, we use the data we got from local tortuosity $\tau(y)$
-to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
-and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
-in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
-then rejoin with each other and the splitting-rejoining behavior causes the difference of $\tau$ with respect to the neighboring trajectories.   
-We also can get the idea why the maximum value of $\tau$ is smaller 
-than the one in the case of 20 bodies . 
-The most of the bodies in this case are smaller than those in the case of 20 bodies.
-So when two neighboring trajectories are splitted on the left side by a smaller body they do not
-travel as far as the two splitted by a bigger body do after they rejoin on the right side. 
+since there are more bodies in the former case.
+
+%To understand the meaning of jump 
+%of $\tau$, we use the data we got from local tortuosity $\tau(y)$
+%to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
+%and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
+%in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
+%then rejoin with each other and the splitting-rejoining behavior causes the difference of $\tau$ with respect to the neighboring trajectories.   
+%We also can get the idea why the maximum value of $\tau$ is smaller 
+%than the one in the case of 20 bodies . 
+%The most of the bodies in this case are smaller than those in the case of 20 bodies.
+%So when two neighboring trajectories are splitted on the left side by a smaller body they do not
+%travel as far as the two splitted by a bigger body do after they rejoin on the right side. 
 }
 
+%\begin{figure}[H]
+%\begin{center}
+%\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
+%\caption{\label{fig:Eroding100tracer} The historical trajectories of 
+%200 tracers released at x = -1 in the fluid with multiple bodies.}
+%\end{center}
+%\end{figure}
+
 \begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
-\caption{\label{fig:Eroding100tracer} The historical trajectories of 
-200 tracers released at x = -1 in the fluid with multiple bodies.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
+\caption{}
+\end{subfigure}
 \begin{subfigure}[b]{0.45\textwidth}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
-\caption{}
-\end{subfigure}
+
 \caption{\label{fig:Eroding100tort} The tortuosity study in the fluid with 100 bodies 
 when the porosity is 62.98 \%.
-(a) The 
+(a) The historical trajectories of 
+200 tracers released at x = -1 in the fluid with multiple bodies.
+(b) The 
 x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.9021
 \times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
-(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
-(c) The historical trajectories of 
-200 tracers released at x = -1 in the fluid with multiple bodies.}
+(c) The local tortuosity $\tau(y)$ on the cross section x = -1. 
+}
 %(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
@@
 
-\begin{figure}[H]
-\center
-\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
-\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of 
-local tortuosity $\tau$ at two neighboring tracers in
-100 bodies eroding when the porosity is 62.98 \%
-and the tortuosity is 1.1182. The same color of a pair of trajectories 
-means they are from two neighboring tracers.}
-\end{figure}
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
+%\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of 
+%local tortuosity $\tau$ at two neighboring tracers in
+%100 bodies eroding when the porosity is 62.98 \%
+%and the tortuosity is 1.1182. The same color of a pair of trajectories 
+%means they are from two neighboring tracers.}
+%\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-07-25 docs/transport/erosion_transport.tex
adding a few references

@@
 interpolation, panel-based quadrature, etc.
+
+\item The classic work of Carman~\cite{car1937} reviews early work on
+granular flow.
+
+\item Thermal boundary layer flow in anisotropic porous media is
+investigated by Nilsen and Storesletten~\cite{nil-sto1990} and Rees and
+Storesletten~\cite{ree-sto1995}.
+
+\item \cite{won-kop-tom1984} investigates relationships between the
+porosity of a rock to its permeability, surface area, and the electrical
+conductivity of salt water within the rock.  They show that the pore
+size distribution influences both the conductivity and permeability.
+
+\item In~\cite{rot1988}, Rothman applies a cellular automaton method to
+simulate flow in porous media.  The method is probabilistic and agrees
+well with analytic solutions.  However, the resulting flow is not
+smooth, so quantities such as the shear stress is challenging to stably
+compute.
+
+\item In~\cite{leb-den-car2008}, a statistical model is used to describe
+transport in a high heterogeneous porous media.
 

### 2019-07-27 docs/transport/erosion_transport.tex

@@
 \end{align}
-on the outer wall.  The eroding body is initially a circle of
-radius $r=0.4$, length $L = 2\pi r$, and is placed near the no-slip wall
-at $y=-1$.  We discretize the eroding body with $N_\iin=256$
-discretization points, and the center of the eroding body is initially
-placed at $h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N\iin$.  For all
-three simulations, we use the time step size $\Delta t=10^{-4}$.
+on the outer wall.  In their experiment, Mitchell and Spagnolie place
+the center of the eroding body $1.5$ times the body's radius above the
+solid wall.  By using the numerical integration scheme described in
+Section~\ref{s:method}, the eroding body can be placed much closer to
+the solid wall.  In the following experiments, we consider an eroding
+body that is initially a circle of radius $r=0.4$ and is placed near the
+no-slip wall at $y=-1$.  We discretize the eroding body with
+$N_\iin=256$ discretization points, and the center of the eroding body
+is initially placed at $h/2$, $h/4$, and $h/10$, where $h = 2\pi
+r/N\iin$.  For all three simulations, we use the time step size $\Delta
+t=10^{-4}$.
 
@@
 rate (magnitude of the shear stress).  Comparing our results to Mitchell
-and Spagnolie~\cite{mit-spa2017} (Figure 7(b)), we see similar results
+and Spagnolie~\cite{mit-spa2017} (Figure 7(c)), we see similar results.
+In particular, between the eroding body and the solid wall the flow is
+very small and there is no recirculation, and this is consistent with
+three-dimensional results~\cite{cah-feu2002}.  Moreover, for all three
+distances, the shear stress is positive \todo[inline]{S-H: Is this
+right?  Is the shear stress ever negative?  I might expect so since
+there are two stagnation points}, so the erosion is smooth.
+
 where the shear stress is smallest near the zero background flow line

### 2019-07-29 docs/transport/erosion_transport.tex
worked on transport paper

@@
 ultimately changes the process of transport through the media.  This
-paper extends a quadrature method first outlined by
-Barnett~\cite{bar2014} and Barnett, Wu, and
+paper extends a quadrature method first outlined by Barnett, Wu, and
 Veerapaneni~\cite{bar-wu-vee2015} to simulate dense packings of eroding
@@
 
+\item In~\cite{bar2014}, a local expansion technique similar to QBX is
+used.  The advantage is that this extends naturally to 3D.  Also,
+Barnett analyzed the error of the Laplace DLP and SLP and compared the
+numerical results to the theory.
+
+\item Suite of near-singular integration methods such as QBX,
+panel-based quadrature, other local interpolants, regularization.
+
+\item \cite{ioa-pap-per1991} were the first to develop quadrature for
+analytic functions in the interior case.
+
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Boundary Integral Equation Formulation}
+\section{Governing Equations}
 \label{s:formulation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We start by defining the main variables used to model erosion.  We
+We start by defining the main variables used to model erosion.  A more
+detailed description is in our previous work~\cite{qua-moo2018}.  We
 consider flows inside a confined geometry $\Omega$ that contains $M$
@@
   \begin{split}
-  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation
-of momentum}\\
-\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
-\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
-bodies} \\
-\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
-velocity} \\
+    \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap 
+      &&\mbox{\em conservation of momentum}\\
+    \grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap 
+      &&\mbox{\em conservation of mass} \\
+    \uu = 0, &\hspace{20pt} \xx \in \gamma, \gap 
+      &&\mbox{\em no slip on the bodies} \\
+    \uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap 
+      &&\mbox{\em outer wall velocity} \\
     \Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
@@
 Here, $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
-prescribed Hagen-Poiseuille velocity field, and
+prescribed Hagen-Poiseuille velocity field, $\Vn$ is the normal velocity
+of $\gamma$, and
 \begin{align}
@@
 \end{align}
-is the shear stress on the eroding bodies.  Using the same approach as
+is the shear stress on $\gamma$.
+
+The erosion rate loses differentiability if the shear stress changes
+sign, and this leads to corners developing on $\gamma$ and can lead to
+numerical instabilities.  Therefore, we supplement the erosion rate with
+a curvature penalization term by replacing the erosion model
+in~\eqref{eqn:erosionModel} with 
+\begin{align}
+  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
+    \frac{L}{2\pi} \kappa - 1 \right),
+\end{align}
+where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average,
+$L$ is the length of $\gamma$, and $\kappa$ is the curvature of
+$\gamma$.  The normalization term guarantees that the regularization
+only changes the body's shape, but not its total length.  Finally, to
+increase the overall stability of the method, a narrow Gaussian filter
+is applied to the erosion rate.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Boundary Integral Equation Formulation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Using the same approach as
 our previous work~\cite{qua-moo2018}, we use a double-layer potential
@@
 \begin{align}
-  \uu(\xx) = \DDD[\eeta](\xx) = 
-    \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
+  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
   \frac{1}{\pi}\int_{\bd\Omega} 
@@
 $\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
-\|\rr\|$.  Then, the solution of the Stokes equation is
+\|\rr\|$.  Then, for any sufficiently smooth geometry $\Omega$, the
+solution of the incompressible Stokes equation with a Dirichlet boundary
+condition $\ff$ is
 \begin{align}
@@
     (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy 
-    \quad \ell = 1,\ldots,M,
-\end{align}
-where $\ff$ is the prescribed Dirichlet boundary condition of the
-velocity on the outer wall and eroding bodies, and $\NN_0$ is the
-integral operator with kernel $\nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in
-\Gamma$, which removes the rank one null space resulting from the
-flux-free requirement of $\ff$. Once the unknown density function is
-computed, the shear stress is found by first computing the deformation
-tensors of the double-layer potential, Stokeslets, and rotlets, and then
-forming the shear stress as defined in equation~\eqref{eqn:shearStress}.
+    \quad \ell = 1,\ldots,M.
+\end{align}
+For our particular problem, $\ff$ is the prescribed velocity on the
+outer wall and is zero on the eroding bodies.  The operator $\NN_0$ is
+the integral operator with kernel $\nn(\xx) \otimes \nn(\yy)$, $\xx,\yy
+\in \Gamma$, which removes the rank one null space resulting from the
+flux-free requirement of $\ff$.
+
+The deformation tensor, pressure, and vorticity of the double-layer
+potential, Stokeslets, and rotlets, can be all be computed analytically
+in terms of the density function.  For $\xx \in \Omega$, the deformation
+tensor, pressure, and vorticity of the double-layer
+potential~\eqref{eqn:stokesDLP} are
+\begin{align}
+  \label{eqn:deformationDLP} 
+  \ssigma^\DD(\xx) &= \frac{1}{2\pi}\int_{\bd\Omega} \left(
+    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
+    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
+    \right. \nonumber \\
+    & \qquad\qquad \left.
+    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
+    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
+    \right) \, ds_\yy, \\
+  p^\DD(\xx) &= -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
+      \eeta(\yy)\,ds_\yy, \\
+  \omega^\DD(\xx) &= -\frac{1}{\pi} \int_{\bd\Omega}
+    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
+      (\rr \cdot \eeta) \, ds_\yy,
+\end{align}
+respectively. We require the deformation tensor of the double-layer potential at
+$\xx \in \bd \Omega$.  Since the deformation tensor of the double-layer
+potential is discontinuous across $\bd\Omega$, a jump term must be added
+to $\ssigma^\DD(\xx)$ for $\xx \in \gamma$.  Finally, the deformation
+tensor, pressure, and vorticity due to the Stokeslets and rotlets are
+straightforward to compute~\cite{qua-moo2018}.  Having computed the
+deformation tensor on $\gamma$, the shear stress is computed as defined
+in equation~\eqref{eqn:shearStress}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The layer potential representations of $\uu$~\eqref{eqn:stokesDLP} and
-its gradient are written in terms of contour integrals in $\RR^2$. We
-will be applying a quadrature method for holomorphic functions, so we
-must convert these layer potentials in $\RR^2$ to contour integrals in
-$\CC$.  The first step is to write the Stokes double-layer potential as
-the sum of a Laplacian double-layer potential and its gradient
+In equations~\eqref{eqn:stokesDLP} and~\eqref{eqn:deformationDLP}, $\uu$
+and its deformation tensor are written as a contour integral in $\RR^2$,
+respectively.  However, these layer potentials can be rewritten in terms
+of Cauchy integrals and its derivatives in $\CC$.  The first step is to
+write the Stokes double-layer potential as the sum of a Laplacian
+double-layer potential and its gradient
 \begin{equation}
@@
 Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
-integral by first finding boundary data of $v$ which satisfies the
-Sokhotski-Plemelj jump relation
+integral by first finding boundary data of $v$.  We assume that $\Omega$
+is a simply-connected interior domain.  Analogous formulas exist for
+exterior domains, and for multiply-connected domains, $\bd\Omega$ is
+simply decomposed into its different connected components.  The boundary
+data of $v$ satisfies the Sokhotski-Plemelj jump relation
 \begin{align}
   \label{eqn:SPrelation}
-  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
+  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
     \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
 \end{align}
-\todo[inline]{Need to be careful about interior and exterior limits}
-Once the boundary data of $v$ is formed, we have
+Since $v$ is a holomorphic function and we have its boundary data, by
+the Cauchy integral theorem we have
 \begin{align}
@@
 the derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  Having
-introduced this notation, the components of the Stokes double-layer
+introduced this notation, the two components of the Stokes double-layer
 potential are~\cite{bar-wu-vee2015}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Cauchy Integral Representation for the Gradient of
-the Velocity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We require complex-valued representations of both the shear stress and
-the vorticity.  Both these quantities depend on the gradient of the
-velocity.  Each term of the gradient of the velocity field can be
-written in terms of Cauchy integrals.  Taking the derivatives of
+\subsection{Cauchy Integral Representation for the Gradient of the
+Double-Layer Potential}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In addition to the velocity, we require a complex-valued representation
+of the gradient of the velocity so that we can compute the shear stress
+and the vorticity.  Each term of the gradient of the velocity field can
+be written in terms of Cauchy integrals.  Taking the derivatives of
 equation~\eqref{eqn:cauchy1} with respect to $x_1$ and $x_2$, we have 
@@
 \end{align}
-With these four expressions, the deformation tensor of the
-double-layer potential, $\ssigma^D = \frac{1}{2} (\nabla \uu + \nabla
-\uu^T)$, is written in terms of Cauchy integrals.  In addition, the
-vorticity can be written as
+With these four expressions, the deformation tensor of the double-layer
+potential, $\ssigma^D = \frac{1}{2} (\nabla \uu + \nabla \uu^T)$, is
+written in terms of Cauchy integrals.  In addition, the vorticity is
 \begin{align}
@@
 \end{align}
-\todo[inline]{Need to cite work that Barnett et al. reference} 
+\todo[inline]{Need to cite~\cite{ioa-pap-per1991}.  They write formulas
+for $v''(x)$ in this paper.  Need to be clear wrt what we did and what
+  others have done} 
 To approximate $v'(x)$, the trapezoid rule is applied to the two

### 2019-07-30 docs/transport/erosion_transport.tex
working on quadrature section

@@
 \input{preambles.tex}
+\usepackage{showkeys}
 \begin{document}
@@
 integral by first finding boundary data of $v$.  We assume that $\Omega$
-is a simply-connected interior domain.  Analogous formulas exist for
+is a simply-connected interior domain.  Similar formulas exist for
 exterior domains, and for multiply-connected domains, $\bd\Omega$ is
@@
 \end{align}
-for $x \in \Omega$.
+for $x \in \Omega$.  A quadrature method to compute these Cauchy
+integrals with a uniform error for all $x \in \Omega$ is presented in
+Section~\ref{sec:bary}.
 
@@
   \end{aligned}
-  \label{eqn:cauchy1}
+  \label{eqn:cauchyVelocity}
 \end{equation}
@@
 be written in terms of Cauchy integrals.  Taking the derivatives of
-equation~\eqref{eqn:cauchy1} with respect to $x_1$ and $x_2$, we have 
-\begin{align}
+equation~\eqref{eqn:cauchyVelocity} with respect to $x_1$ and $x_2$, we
+have 
+\begin{equation}
+\label{eqn:cauchyGradient}
+  \begin{aligned}
     \pderiv{u_1}{x_1} &= +\Re (v'[\tau_1](x)) + 
@@
       \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
-\end{align}
+  \end{aligned}
+\end{equation}
 With these four expressions, the deformation tensor of the double-layer
@@
 \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Transport, Tracers, and Tortuosity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Erosion leads to interesting porous geometries, and we are interested in
-characterizing transport in these geometries.  For porous media, two of
-the most important variables are the porosity and the permeability.
-However, additional properties of the flow are revealed by computing
-the anomalous diffusion rate, the tortuosity, and the distribution the
-gap sizes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Anomalous Diffusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The dynamics of fluid in porous media can be characterized in terms of
-anomalous diffusion.  However, the anomalous diffusion rate depends on
-the properties of the geometry.  In addition to the porosity, the
-distribution of the grains affects the anomalous diffusion rates.  To
-quantify this rate, we require tracer trajectories that are governed by
-\begin{align}
-  \label{eqn:trajectories}
-  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
-\end{align}
-Given a trajectory, we define $\lambda_j(t)$ to be the distance
-travelled by the particle
-\begin{align}
-  \lambda_j(t) = \int_{0}^t \|\ss_j(\tau)\|\, d\tau.
-\end{align}
-Having formed $N_p$ trajectories, the first and second ensemble moments
-are
-\begin{align}
-  \langle \lambda \rangle (t) = 
-    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
-    \sigma_\lambda^2(t) = \frac{1}{N_p} 
-    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2.
-\end{align}
-If the particle spreading scales with time as $\sigma_\lambda^2 \sim
-t^\alpha$, with $\alpha < 1$, this indicates that the particle
-trajectories are sub-diffusive.  In contrast, if $\sigma_\lambda^2 \sim
-t^2$, the particle trajectories are undergoing a ballistic motion and
-are not affected by the grains.
-
-For early times when the geometry has not eroded, we expect the
-trajectories to be sub-diffusive.  However, as the bodies erode and
-straight preferential channels are formed, we expect the dynamics to
-resemble a ballistic motion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tortuosity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The tortuosity of a geometry quantifies the average amount of turning
-made by a streamline.  Mathematically, it is defined as
-\begin{align}
-  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
-  {\displaystyle\int_{S}u_x(y)\,dy},
-  \label{eqn:tortuosity1}
-\end{align}
-where $S$ is an cross-section perpendicular to the $x$ axis with length
-$d$, $\lambda(y)$ is the length of the streamline that is initialized
-at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
-the velocity at the $y$-coordinate along $S$.  Following~\cite{}, the
-trajectories are formed until they cross a second cross-section.  In our
-work, we always initialize the trajectories at $x=-1$ and stop them when
-they reach $x=1$.
-
-Under the assumptions that the flow is incompressible and not reentrant,
-the tortuosity can be equivalently measured as~\cite{dud-koz-mat2011}
-\begin{align}
-  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
-           {\displaystyle\int_\Omega u_x(\yy)\, d\yy}.
-  \label{eqn:tortuosity2}
-\end{align}
-The flow is reentrant if all streamlines connect the inlet to the
-outlet.  Recirculation zones are possible in viscous fluids, but they
-only constitute a small fraction of the total porous media.  Therefore,
-the tortuosity defined in equation~\eqref{eqn:tortuosity2} is an upper
-bound for the definition in equation~\eqref{eqn:tortuosity1}.  We have
-used formulas for a particular geometry, and the difference is
-negligible.  Since equation~\eqref{eqn:tortuosity2} does not require the
-additional work of computing particle trajectories, we use this
-definition for the tortuosity.
-
-There have been efforts to relate the tortuosity to the
-porosity~\cite{matyka2008tortuosity}, but these results can not be
-universal since the porosity which depends on only a single number, the
-tortuosity is affected by the distribution of pores within the porous
-network.  In addition to the hydraulic tortuosity, a local tortuosity
-can be used to analyze the local behavior of a streamline near a
-body~\cite{matyka2008tortuosity}.  The local tortuosity of a streamline
-initialized at $y$ along $S$ is
-\begin{align*}
-  \tau(y) = \frac{\lambda(y)}{d}.
-\end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pore Throat Size}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{itemize}
-  \item Pore throat sizes affect many things such as first passage time,
-  mixing, chemical reactions, heat conduction, biological activities
-\end{itemize}
 
@@
 \subsection{Barycentric Quadrature for $v''(x)$}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Barycentric quadrature rule developed by Barnett et
-al.~\cite{bar-wu-vee2015} approximates the double-layer potential for
-the velocity~\eqref{eqn:stokesDLP} with bounded error.  However, to
-compute the shear stress and vorticity, the method must be extended.  We
-first briefly describe the original Barycentric quadrature method, and
-then derive a necessary extension to simulate erosion.  We present the
-quadrature for a simply-connected domain $\Omega$, and the method
-naturally extends to the eroding geometry by applying the quadrature to
-each of its connected component.  The method starts with an underlying
-quadrature rule, and we use the trapezoid rule because of its superior
-accuracy for smooth periodic functions~\cite{tre-wei2014}.  Since the
-quadrature points are uniformly distributed, the quadrature weights are
-$w_j = L/N$, $j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
-
-We next identify all the discretization points, the normal vector, and
-the density function with their complex-value counterparts.  Then, all
-the layer potentials are a combination of a Cauchy integral and its
-first two derivatives.  Given a density function $\tau(y)$, the boundary
-data is solved using the Sokhotski-Plemelj jump
-relation~\eqref{eqn:SPrelation}.  If $x \in \Omega$ is too close to
-$\bd\Omega$ and the trapezoid rule is applied to the identity
-\begin{align}
-  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
-  \quad x \in \Omega,
-\end{align}
-the quadrature error is large since the integrand has a large
-derivative.  However, if the trapezoid rule is applied to
+\label{sec:bary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Equations~\eqref{eqn:cauchyVelocity} and~\eqref{eqn:cauchyGradient} show
+that computing the Stokes velocity, shear stress, and vorticity hinge on
+accurate quadrature methods for the Cauchy integral and its first two
+derivatives as defined in equation~\eqref{eqn:cauchy}.  Even though the
+trapezoid rule is spectrally accurate for a fixed $x \in
+\Omega$~\cite{tre-wei2014}, its error depends on bounds of the
+derivative of the integrand.  Therefore for a fixed resolution, as $x$
+approaches $\bd\Omega$, causing the integrands to become more singular,
+the error grows without bound.  Ioakimidis et al.~\cite{ioa-pap-per1991}
+developed quadrature methods to compute Cauchy integrals and their
+derivatives with an error bound that is independent of $x$.  Then,
+Barnett et al.~\cite{bar-wu-vee2015} applied these quadratur emethods to
+compute the Stokes double-layer potential representation of the
+velocity~\eqref{eqn:stokesDLP}.  To compute the shear stress and
+vorticity with the same accuracy, we extend the method by using
+Barycentric quadrature methods for the second derivative of a Cauchy
+integral.
+
+We briefly summarize the Baryncentric quadrature method for computing
+the velocity~\cite{bar-wu-vee2015}.  Then, we apply additional
+quadrature methods to compute the gradient of the velocity so that we
+can simulate erosion.  We present the quadrature for a simply-connected
+interior domain $\Omega$, and we consider the target points $x \in
+\Omega$ and $x \in \Omega^c$. Then, the method naturally extends to the
+eroding geometry by applying the quadrature to each of its connected
+component.  The method starts with an underlying quadrature rule, and we
+use the spectrally accurate trapezoid rule.  Since the quadrature points
+are uniformly distributed, the quadrature weights are $w_j = L/N$,
+$j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
+
+Again, given a density function $\tau$, the boundary data of $v$ as
+defined in equation~\eqref{eqn:laplaceComplex} can be found by applying
+the Sokhotski-Plemelj jump relation~\eqref{eqn:SPrelation}.  The
+boundary data differs if we are considering the interior problem ($x \in
+\Omega$) or the exterior problem ($x \in \Omega^c$).  Therfore, for the
+boundary data we use the notation $v^-$ for the interior problem and
+$v^+$ for the exterior problem.  Rather than directly applying the
+trapezoid rule to $v(x)$, we start with the identity
 \begin{align}
@@
 \end{align}
-the quadrature error is bounded since the integrand and all its
-derivatives are bounded with respect to $x$. That is,
-\begin{align}
-  \sum_{j=1}^{N} \frac{v^{-}(y_j) - v(x)}{y_j - x} w_j \approx 0.
-\end{align}
-Rearranging for $v(x)$, we have
-\begin{align}
-  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
+where we are considering the interior problem.  Since the integrand is
+bounded as $x$ approaches $\bd\Omega$, we can apply the trapezoid rule
+\begin{align}
+  \sum_{j=1}^{N} \frac{v^{-}(y_j) - v(x)}{y_j - x} w_j \approx 0,
+\end{align}
+and the error is independent of $x$.  Rearranging for $v(x)$, we have
+the quadrature formula
+\begin{align}
+  v(x) = \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
   {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}.
-  \label{eqn:Baryv}
-\end{align}
-\todo[inline]{Need to cite~\cite{ioa-pap-per1991}.  They write formulas
-for $v''(x)$ in this paper.  Need to be clear wrt what we did and what
-  others have done} 
-To approximate $v'(x)$, the trapezoid rule is applied to the two
-integrals in the identity
-\begin{align}
-  v'(x) = \frac{\int\limits_{\bd\Omega} 
-    \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
-  {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy},
-\end{align}
-resulting in the quadrature rule
-\begin{align}
-  v'(x) \approx \frac{\sum\limits_{j=1}^{N}
+  \label{eqn:BaryvInterior}
+\end{align}
+Using a similar construction and letting $a$ be any point inside
+$\Omega$, the Barycentric quadrature rule for the exterior problem is
+\begin{align}
+  v(x) = \frac{1}{x-a} 
+    \frac{\sum\limits_{j=1}^N \frac{v^+(y_j)}{y_j - x}w_j}
+    {\sum\limits_{j=1}^N \frac{(y_j - a)^{-1}}{y_j - x}w_j}.
+  \label{eqn:BaryvExterior}
+\end{align}
+
+Similar constructions can be used to derive quadrature rules
+for $v'(x)$.  For $x \in \Omega$, we have the identity
+\begin{align}
+  \int_{\bd\Omega} \frac{v^-(y) - v(x) + (y-x)v'(x)}{(y - x)^2} = 0,
+\end{align}
+and the integrand is bounded for all $x$.  Therefore, upon applying the
+quadrature rule and rearranging for $v'(x)$, we have
+\begin{align}
+  v'(x) = \frac{\sum\limits_{j=1}^{N}
     \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
   {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
-  \label{eqn:Baryvprime}
-\end{align}
+  \label{eqn:BaryvprimeInterior}
+\end{align}
+Using a similar construction, the Barycentric quadrature rule to compute
+$v'(x)$ in $\Omega^c$ is
+\begin{align}
+  v'(x) = \frac{1}{x-a} \frac{\sum\limits_{j=1}^N
+    \frac{v^+_j - v(x)}{(y_j - x)^2} w_j}
+    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j - x} w_j}.
+  \label{eqn:BaryvprimeExterior}
+\end{align}
+Note that the value $v(x)$ is required to compute $v'(x)$ for both the
+interior and exterior case.  These are computed using the quadrature
+methods in equations~\eqref{eqn:BaryvInterior}
+and~\eqref{eqn:BaryvExterior}.
 
 To compute the shear stress and vorticity, we require a Barycentric
-quadrature rule for $v''(x)$.  Mimicking the construction of the
-quadrature rule for $v(x)$ and $v'(x)$, we start with the second
-derivative of the Cauchy integral theorem
+quadrature rule for $v''(x)$.  Following the work of Ioakimidis et
+al~\cite{ioa-pap-per1991} (see equation (2.12)), we mimick the
+construction of the quadrature rule for $v(x)$ and $v'(x)$. We start
+with the second derivative of the Cauchy integral theorem
 \begin{align}
@@
 \end{align}
-Using the identity
+For the interior case, $x \in \Omega$, we use the identity
 \begin{align}
@@
       1, & n = 1, \\
-      0, & n > 1, \\
+      0, & n = 2,3,\ldots. \\
     \end{array}
@@
 \end{align}
-where $x \in \Omega$ and $n \in \mathbb{N}$, we have
+Combining this identity with the Cauchy integral representation of
+$v''(x)$, we have
 \begin{align}
@@
 \end{align}
-where the accuracy is independent of the proximity of $x$ to
-$\bd\Omega$. Solving for $v''(x)$, the Barycentric quadrature rule for
-the second derivative is
+where the accuracy is independent of $x$.  Solving for $v''(x)$, the
+Barycentric quadrature rule for the second derivative is
 \begin{align}
@@
 \end{align}
-This formula requires accurate approximations of $v(x)$ and $v'(x)$, but
-these are available in equations~\eqref{eqn:Baryv}
-and~\eqref{eqn:Baryvprime}.
-
-To apply the quadrature to multiply-connected domains, we must all
-consider exterior points $x \in \Omega^c$.  Mimicking the construction
-in~\cite{bar-wu-vee2015}, we use the quadrature rule
+For the exterior case, $x \in \Omega^c$, we start with the identity
 \begin{align}
 \frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
-    \frac{(y-a)^{-1}}{y-x} dy, 
-\end{align}
-is used, and the resulting Barycentric quadrature formula is
+    \frac{(y-a)^{-1}}{y-x} dy. 
+\end{align}
+Combining this identity with the Cauchy integral representation of
+$v''(x)$, we have
+\begin{align}
+  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
+    \frac{2v^+(y) - 2v(x) - 2(y-x)v'(x) + (y-a)^{-1} (x-a) (y-x)^2 v''(x)}
+    {(y-x)^3}.
+\end{align}
+As in the interior case, the integrand is chosen so that it is bounded
+for all $x \in \Omega$.  Therefore, after applying the trapezoid rule
+  and solving for $v''(x)$, we have the Barycentric quadrature rule
 \begin{align}
@@
 \end{align}
-Again, values of $v(x)$ and $v'(x)$ are required, and these are
-available in~\cite{bar-wu-vee2015}.
+Similar to the quadrature rule for $v'(x)$ requring the value $v(x)$,
+the quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$.
+Both these quantities are computed using the quadrature rules in
+equations~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},
+and~\eqref{eqn:BaryvprimeExterior}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Time Integration}
+\label{s:time}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We reuse the time stepping method outlined in our previous
+work~\cite{qua-moo2018}.  Rather than tracking the $(x,y)$
+coordinates, the {\thL} variables are tracked. A second-order
+Implicit-Explicit method is used. In particular, the diffusive term
+corresponding to the curvature penalization term is discretized
+implicitly, and all other terms, which are non-stiff, are treated
+explicitly.
+
+\todo[inline]{Talk about time integration for erosion and for tracers}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Transport, Tracers, and Tortuosity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Erosion leads to interesting porous geometries, and we are interested in
+characterizing transport in these geometries.  For porous media, two of
+the most important variables are the porosity and the permeability.
+However, additional properties of the flow are revealed by computing
+the anomalous diffusion rate, the tortuosity, and the distribution the
+gap sizes.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Anomalous Diffusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The dynamics of fluid in porous media can be characterized in terms of
+anomalous diffusion.  However, the anomalous diffusion rate depends on
+the properties of the geometry.  In addition to the porosity, the
+distribution of the grains affects the anomalous diffusion rates.  To
+quantify this rate, we require tracer trajectories that are governed by
+\begin{align}
+  \label{eqn:trajectories}
+  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
+\end{align}
+Given a trajectory, we define $\lambda_j(t)$ to be the distance
+travelled by the particle
+\begin{align}
+  \lambda_j(t) = \int_{0}^t \|\ss_j(\tau)\|\, d\tau.
+\end{align}
+Having formed $N_p$ trajectories, the first and second ensemble moments
+are
+\begin{align}
+  \langle \lambda \rangle (t) = 
+    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
+    \sigma_\lambda^2(t) = \frac{1}{N_p} 
+    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2.
+\end{align}
+If the particle spreading scales with time as $\sigma_\lambda^2 \sim
+t^\alpha$, with $\alpha < 1$, this indicates that the particle
+trajectories are sub-diffusive.  In contrast, if $\sigma_\lambda^2 \sim
+t^2$, the particle trajectories are undergoing a ballistic motion and
+are not affected by the grains.
+
+For early times when the geometry has not eroded, we expect the
+trajectories to be sub-diffusive.  However, as the bodies erode and
+straight preferential channels are formed, we expect the dynamics to
+resemble a ballistic motion.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tortuosity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The tortuosity of a geometry quantifies the average amount of turning
+made by a streamline.  Mathematically, it is defined as
+\begin{align}
+  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
+  {\displaystyle\int_{S}u_x(y)\,dy},
+  \label{eqn:tortuosity1}
+\end{align}
+where $S$ is an cross-section perpendicular to the $x$ axis with length
+$d$, $\lambda(y)$ is the length of the streamline that is initialized
+at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
+the velocity at the $y$-coordinate along $S$.  Following~\cite{}, the
+trajectories are formed until they cross a second cross-section.  In our
+work, we always initialize the trajectories at $x=-1$ and stop them when
+they reach $x=1$.
+
+Under the assumptions that the flow is incompressible and not reentrant,
+the tortuosity can be equivalently measured as~\cite{dud-koz-mat2011}
+\begin{align}
+  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
+           {\displaystyle\int_\Omega u_x(\yy)\, d\yy}.
+  \label{eqn:tortuosity2}
+\end{align}
+The flow is reentrant if all streamlines connect the inlet to the
+outlet.  Recirculation zones are possible in viscous fluids, but they
+only constitute a small fraction of the total porous media.  Therefore,
+the tortuosity defined in equation~\eqref{eqn:tortuosity2} is an upper
+bound for the definition in equation~\eqref{eqn:tortuosity1}.  We have
+used formulas for a particular geometry, and the difference is
+negligible.  Since equation~\eqref{eqn:tortuosity2} does not require the
+additional work of computing particle trajectories, we use this
+definition for the tortuosity.
+
+There have been efforts to relate the tortuosity to the
+porosity~\cite{matyka2008tortuosity}, but these results can not be
+universal since the porosity which depends on only a single number, the
+tortuosity is affected by the distribution of pores within the porous
+network.  In addition to the hydraulic tortuosity, a local tortuosity
+can be used to analyze the local behavior of a streamline near a
+body~\cite{matyka2008tortuosity}.  The local tortuosity of a streamline
+initialized at $y$ along $S$ is
+\begin{align*}
+  \tau(y) = \frac{\lambda(y)}{d}.
+\end{align*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Streamlines and Tortuosity}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Dump of earlier section for now ... need to fix how this
+is worked into the section}
 Having developed numerically accurate methods to compute the velocity
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Time Integration}
-\label{s:time}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We reuse the time stepping method outlined in our previous
-work~\cite{qua-moo2018}.  Rather than tracking the $(x,y)$
-coordinates, the {\thL} variables are tracked. A second-order
-Implicit-Explicit method is used. In particular, the diffusive term
-corresponding to the curvature penalization term is discretized
-implicitly, and all other terms, which are non-stiff, are treated
-explicitly.
-
-\todo[inline]{Talk about time integration for erosion and for tracers}
+\subsection{Pore Throat Size}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{itemize}
+  \item Pore throat sizes affect many things such as first passage time,
+  mixing, chemical reactions, heat conduction, biological activities
+\end{itemize}
 
@@
 $N_\iin=256$ discretization points, and the center of the eroding body
-is initially placed at $h/2$, $h/4$, and $h/10$, where $h = 2\pi
-r/N\iin$.  For all three simulations, we use the time step size $\Delta
-t=10^{-4}$.
+is initially chosen so that the distance between the body and the solid
+wall are $h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  For all
+three simulations, we use the time step size $\Delta t=10^{-4}$.
 
@@
 \bibliography{refs}
-
-\end{document}
 
@@
 
-%{\color{red}
-%\begin{alignat}{3}
-%1 &= \frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
-%\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
-%    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
-%\end{alignat}
-%and the contour integral 
-%\begin{align}\label{eqn:cauchyId3}
-%0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
-%\end{align}
-%Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
-%the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
-%\begin{align*}
-%0 &= \frac{1}{2\pi i} \int_{\Gamma}
-%    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
-%&= \frac{1}{2\pi i} \int_{\Gamma}
-%    \frac{2v^-(y)}{(y - x)^3} \, dy 
-%-v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{1}{y-x} dy\\
-%&= \frac{1}{2\pi i} \int_{\Gamma}
-%    \frac{2v^-(y)}{(y - x)^3} \, dy 
-%-\frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
-%-\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
-%-\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
-%&= \frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
-%\end{align*}
-%}
-%\todo[inline]{S-H: How do we get these identities?}
-%\begin{alignat}{3}
-%  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
-%  0 &= \frac{1}{2\pi i}\int_{\Gamma}
-%    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
-%    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
-%\end{alignat}
-%{\color{red}
-%and the quadrature formulations are
-%\begin{alignat}{3}
-%  v''(x) &\approx
-%    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
-%    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
-%  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
-%    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
-%    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
-%\end{alignat}
-%where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
-%
-%}
+{\color{red}
+\begin{alignat}{3}
+1 &= \frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
+\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
+    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
+\end{alignat}
+and the contour integral 
+\begin{align}\label{eqn:cauchyId3}
+0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
+\end{align}
+Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
+the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
+\begin{align*}
+0 &= \frac{1}{2\pi i} \int_{\Gamma}
+    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
+&= \frac{1}{2\pi i} \int_{\Gamma}
+    \frac{2v^-(y)}{(y - x)^3} \, dy 
+-v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{1}{y-x} dy\\
+&= \frac{1}{2\pi i} \int_{\Gamma}
+    \frac{2v^-(y)}{(y - x)^3} \, dy 
+-\frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
+-\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
+-\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
+&= \frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
+\end{align*}
+}
+\todo[inline]{S-H: How do we get these identities?}
+\begin{alignat}{3}
+  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
+    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
+  0 &= \frac{1}{2\pi i}\int_{\Gamma}
+    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
+    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
+\end{alignat}
+{\color{red}
+and the quadrature formulations are
+\begin{alignat}{3}
+  v''(x) &\approx
+    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
+    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
+  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
+    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
+    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
+\end{alignat}
+where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
+
+}
 
@@
 %
+
+\end{document}

### 2019-07-30 docs/transport/erosion_transport.tex
working on paper

@@
 \input{preambles.tex}
-\usepackage{showkeys}
+%\usepackage{showkeys}
 \begin{document}
@@
 and the error is independent of $x$.  Rearranging for $v(x)$, we have
-the quadrature formula
+the interior Barycentric quadrature formula 
 \begin{align}
   v(x) = \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
-  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}.
+  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}, \quad x \in \Omega.
   \label{eqn:BaryvInterior}
@@
 Using a similar construction and letting $a$ be any point inside
-$\Omega$, the Barycentric quadrature rule for the exterior problem is
+$\Omega$, the exterior Barycentric quadrature rule is
 \begin{align}
@@
     \frac{\sum\limits_{j=1}^N \frac{v^+(y_j)}{y_j - x}w_j}
-    {\sum\limits_{j=1}^N \frac{(y_j - a)^{-1}}{y_j - x}w_j}.
+    {\sum\limits_{j=1}^N \frac{(y_j - a)^{-1}}{y_j - x}w_j},
+    \quad x \in \Omega^c.
   \label{eqn:BaryvExterior}
@@
 \end{align}
-and the integrand is bounded for all $x$.  Therefore, upon applying the
-quadrature rule and rearranging for $v'(x)$, we have
+and the integrand is bounded for all $x \in \Omega$.  Therefore, upon
+applying the quadrature rule and rearranging for $v'(x)$, we have the
+interior Barycentric quadrature rule
 \begin{align}
@@
     \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
-  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
+  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}, 
+  \quad x \in \Omega.
   \label{eqn:BaryvprimeInterior}
 \end{align}
-Using a similar construction, the Barycentric quadrature rule to compute
-$v'(x)$ in $\Omega^c$ is
+Using a similar construction, the exterior Barycentric quadrature rule
+for the the first derivative is
 \begin{align}
@@
     \frac{v^+_j - v(x)}{(y_j - x)^2} w_j}
-    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j - x} w_j}.
+    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j - x} w_j},
+    \quad x \in \Omega^c.
   \label{eqn:BaryvprimeExterior}
@@
 where the accuracy is independent of $x$.  Solving for $v''(x)$, the
-Barycentric quadrature rule for the second derivative is
+Barycentric quadrature rule for the interior second derivative is
 \begin{align}
@@
     \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
-    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}.
+    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, \quad x \in \Omega.
 \end{align}
@@
 As in the interior case, the integrand is chosen so that it is bounded
-for all $x \in \Omega$.  Therefore, after applying the trapezoid rule
-  and solving for $v''(x)$, we have the Barycentric quadrature rule
+for all $x \in \Omega^c$.  Therefore, after applying the trapezoid rule
+and solving for $v''(x)$, we have the Barycentric quadrature rule for
+the exterior second derivate
 \begin{align}
@@
     \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
-    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}.
+    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}, 
+    \quad x \in \Omega^c.
 \end{align}
@@
 computing the velocity, shear stress, and vorticity.  However, applied
-directly, it requires $\mathcal{O}(N^2)$ operations.  Since the shear
-stress must only be computed once per time step, and the vorticity is
-only used as a post-processing step, we accept the $\mathcal{O}(N^2)$
-algorithm.  However, the velocity must be computed at every GMRES
-iteration, which would make the overall method impractical without a
-fast algorithm.
-
-At each GMRES iteration, we must compute the velocity at each
-discretization point on $\bd\Omega$.  To reduce the cost of computing
-the velocity, we start by using the trapezoid rule~\eqref{eqn:trap}
-accelerated with the fast multipole method (FMM)~\cite{gre-rok1987},
-which requires $\mathcal{O}(N)$ operations, and we call this velocity
-$\vv_\trap(\xx)$.  For target points that are sufficiently far from
-$\bd\Omega$, $\vv_\trap(\xx)$ is sufficiently accurate.  However, this
-velocity is inaccurate at points that are too close to $\bd\Omega$, and
-the velocity must be corrected.  Assuming that $\xx$ is too close to
-$\gamma_k$, only the velocity due to $\gamma_k$ must be corrected. We
-first subtract the velocity contribution of $\vv(\xx)$ due to
-$\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
-the velocity due to $\gamma_i$ with more accuracy.  That is, the final
-velocity is
+directly, it requires $\mathcal{O}(N^2)$ operations.  By using a fast
+algorithm such as the fast multipole method~\cite{gre-rok1987}, this
+cost can be reduced to $\mathcal{O}(N)$ operations.  However, the
+Barycentric quadrature formulas require several $N$-body calculations
+which we would like to avoid.  Instead, we use a hybrid method where the
+fast multipole accelerate trapezoid rule is used to compute the velocity
+at most of the discretization points, and the non-accelerated
+Barycentric quadrature rule is used to locally correct the trapezoid
+rule.
+
+We start by using the trapezoid rule~\eqref{eqn:trap} accelerated with
+the FMM, which requires $\mathcal{O}(N)$ operations, and we call this
+velocity $\vv_\trap(\xx)$.  For target points that are sufficiently far
+from $\bd\Omega$, $\vv_\trap(\xx)$ is sufficiently accurate.  However,
+if $\xx$ is sufficiently close to one of the eroding bodies $\gamma_k$,
+or the outer wall $\Gamma$, the velocity contribution from that
+particular component of $\bd\Omega$ is inaccurate and it must be
+corrected.  Assuming that $\xx$ is too close to $\gamma_k$, we first
+subtract the velocity contribution of $\vv(\xx)$ due to $\gamma_k$.
+Then, the Barycentric quadrature rule is used to compute the velocity
+due to $\gamma_k$ with more accuracy.  That is, the final velocity is
 \begin{align}
@@
     D(\xx,\yy^k_j) \eeta(\yy_j) + \vv^k_\bary(\xx),
+  \label{eqn:velocityDecomp}
 \end{align}
 where $\vv^k_\bary(\xx)$ is the velocity at $\xx$ resulting from
-applying the Barycentric quadrature rule due to $\gamma_k$.  This method
-naturally extends to points that are close to $\Gamma$, and to the
-scenario when $\xx$ is simultaneously close to multiple components of
-$\bd\Omega$.
-
-Similarly, to compute the vorticity and shear stress, the trapezoid rule
-is first used.  Then, if $\xx$ is close to $\gamma_k$, the trapezoid
-quadrature rule contribution due to $\gamma_k$ is subtracted and the
-Barycentric quadrature rule contribution due to $\gamma_k$ is added.
-Since the shear stress and vorticity are only computed once per time
-step, we use a direct summation rather than the FMM.  Relative to the
-cost of applying GMRES with the FMM, the additional once-per-time-step
-cost is minimal.
-
-We also do not use any fast summation methods to apply the Barycentric
-quadrature rule.  Since this quadrature rule is applied at every GMRES
-iteration, it is imperative that we only apply the Barycentric
-quadrature at target points where they are required.  As a rule of
-thumb, the trapezoid rule due to $\gamma_k$ is accurate if
+applying the Barycentric quadrature rule due to $\gamma_k$.  This
+strategy naturally extends to points that are close to $\Gamma$, and to
+the scenario when $\xx$ is simultaneously close to multiple components
+of $\bd\Omega$.  While the term $\vv_\trap(\xx)$ in
+equation~\eqref{eqn:velocityDecomp} is computed for all target points
+using the FMM, the other two terms are computed with a direct summation.
+However, these terms are only required for target points near an eroding
+body or the outer wall, and the number of such points is much less than
+$N$.  An identical quadrature method is used to compute the vorticity
+and shear stress.  That is, these quantities are computed using the
+trapezoid rule, and then updates due to inaccuracies of the trapezoid
+rule are made.  However, since the shear stress and vorticity are only
+computed once per time step, the trapezoid rule is applied with a direct
+summation rather than the FMM.  Relative to the cost of applying GMRES
+with the FMM, the additional once-per-time-step cost is minimal.
+
+Per grid point, evaluating the Barycentric quadrature rules dominates
+the computational cost. Therefore, it is imperative that we only apply
+the Barycentric quadrature when the trapezoid rule is inaccurate.  As a
+rule of thumb, the trapezoid rule due to $\gamma_k$ is
+accurate~\cite{bar2014} if
 \begin{align}
@@
 \end{align}
-where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
-In this manner, rather than using an expensive all-to-all algorithm to
+where $\alpha_\iin \geq 1$ is a parameter that needs to be chosen.  In
+this manner, rather than using an expensive all-to-all algorithm to
 compute the distance between all pairs of discretization points, we
@@
 Barycentric quadrature rule may need to be applied, and the parameter
-$\alpha_\iin$ is accounts for the fact that the bodies are being
+$\alpha_\iin$ accounts for the fact that the bodies are being
 approximated with circles.  Assuming that the two bodies $\gamma_i$ and
@@
     \begin{array}{c}
-      x_{\cc_i } \\ \pm 1
+      x_i \\ \pm 1
     \end{array}
@@
 \end{align}
-where $x_{\cc_i } $ is the x coordinate of $\cc_i$. If body $\gamma_i$
-satisfies this condition, for each point $\xx=(x,y) \in \gamma_i$, we
-apply the Barycentric rule to points that satisfy
+where $x_i$ is the x coordinate of $\cc_i$. If body $\gamma_i$ satisfies
+this condition, for each point $\xx=(x,y) \in \gamma_i$, we apply the
+Barycentric rule to points that satisfy
 \begin{align}
@@
 \end{align}
+Finally, to determine if a target point $\xx$ that is in the fluid bulk
+rather than on another eroding body requires the Barycentric quadrature
+rule, we only check conditions~\eqref{eqn:PointsBodyCutoff}
+and~\eqref{eqn:PointsWallCutoff}.
 
 To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
-we first compute an accurate solution by using the Barycentric
-quadrature rule for all discretization points.  Then, for multiple
-values of $\alpha_\iin$ and $\alpha_\out$, we compute the velocity field
-with the trapezoid rule for all points that do not satisfy
-conditions~\eqref{eqn:PointsBodyCutoff}
+we fix a eroded geometry and we compute an accurate solution by using
+the Barycentric quadrature rule for all discretization points.  Then,
+for multiple values of $\alpha_\iin$ and $\alpha_\out$, we compute the
+velocity field with the trapezoid rule for all points that do not
+satisfy conditions~\eqref{eqn:PointsBodyCutoff}
 and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
@@
 
-Finally, to determine if a target point $\xx$ that is in the fluid bulk
-rather than on another eroding body requires the Barycentric quadrature
-rule, we only check conditions~\eqref{eqn:PointsBodyCutoff}
-and~\eqref{eqn:PointsWallCutoff}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We reuse the time stepping method outlined in our previous
-work~\cite{qua-moo2018}.  Rather than tracking the $(x,y)$
-coordinates, the {\thL} variables are tracked. A second-order
-Implicit-Explicit method is used. In particular, the diffusive term
-corresponding to the curvature penalization term is discretized
-implicitly, and all other terms, which are non-stiff, are treated
-explicitly.
-
-\todo[inline]{Talk about time integration for erosion and for tracers}
+work~\cite{qua-moo2018}.  Rather than tracking the $(x,y)$ coordinates,
+the {\thL} variables are tracked. In addition, a tangential velocity
+field is added to each body so that the discretization points remain
+equispaced for all time.  A second-order Implicit-Explicit method is
+used. In particular, the diffusive term corresponding to the curvature
+penalization term is discretized implicitly, and all other terms, which
+are non-stiff, are treated explicitly.  By using this time stepping
+method in conjunction with the curvature penalization and Gaussian
+filter, we stably evolve the eroding bodies.   An in depth description
+of the time stepping method for erosion is in Section 3.3 of our
+previous work~\cite{qua-moo2018}.
+
+In Section~\ref{s:transport}, we we analyze passive tracers suspended in
+an eroded geometry.  Give such a geometry $\Omega$, a tracer $\ss(t)$
+initialized at $\ss_0$ is governed by 
+\begin{align}
+  \label{eqn:trajectories}
+  \frac{d\ss}{dt} = \uu(\ss), \quad \ss(0) = \ss_0.
+\end{align}
+To compute such a trajectory, we apply the standard fourth-order
+Runge-Kutta method.  To evaluate $\uu(\ss)$, depending on the proximity
+of $\ss$ to $\bd\Omega$, we either use the trapezoid rule or the
+Barycentric quadrature rule as described in Section~\ref{s:fmm}.
 
@@
 \section{Transport, Tracers, and Tortuosity}
+\label{s:transport}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 quantify this rate, we require tracer trajectories that are governed by
-\begin{align}
-  \label{eqn:trajectories}
-  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
-\end{align}
-Given a trajectory, we define $\lambda_j(t)$ to be the distance
-travelled by the particle
-\begin{align}
-  \lambda_j(t) = \int_{0}^t \|\ss_j(\tau)\|\, d\tau.
+equation~\eqref{eqn:trajectories}.  Given a trajectory, we define
+$\lambda_j(t)$ to be the distance travelled by the particle
+\begin{align}
+  \lambda_j(t) = \int_{0}^t \|\ss_j(\tau)\|\, d\tau, 
+    \quad j=1,\ldots,N_p.
 \end{align}
@@
 %\end{align*}
-
-{\color{red}
-\begin{alignat}{3}
-1 &= \frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
-\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
-    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
-\end{alignat}
-and the contour integral 
-\begin{align}\label{eqn:cauchyId3}
-0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
-\end{align}
-Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
-the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
-\begin{align*}
-0 &= \frac{1}{2\pi i} \int_{\Gamma}
-    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
-&= \frac{1}{2\pi i} \int_{\Gamma}
-    \frac{2v^-(y)}{(y - x)^3} \, dy 
--v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{1}{y-x} dy\\
-&= \frac{1}{2\pi i} \int_{\Gamma}
-    \frac{2v^-(y)}{(y - x)^3} \, dy 
--\frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
--\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
--\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
-&= \frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
-\end{align*}
-}
-\todo[inline]{S-H: How do we get these identities?}
-\begin{alignat}{3}
-  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
-    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
-  0 &= \frac{1}{2\pi i}\int_{\Gamma}
-    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
-    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
-\end{alignat}
-{\color{red}
-and the quadrature formulations are
-\begin{alignat}{3}
-  v''(x) &\approx
-    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
-    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
-  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
-    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
-    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
-\end{alignat}
-where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
-
-}
-
+%
+%{\color{red}
+%\begin{alignat}{3}
+%1 &= \frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
+%\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
+%    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
+%\end{alignat}
+%and the contour integral 
+%\begin{align}\label{eqn:cauchyId3}
+%0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
+%\end{align}
+%Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
+%the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
+%\begin{align*}
+%0 &= \frac{1}{2\pi i} \int_{\Gamma}
+%    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
+%&= \frac{1}{2\pi i} \int_{\Gamma}
+%    \frac{2v^-(y)}{(y - x)^3} \, dy 
+%-v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{1}{y-x} dy\\
+%&= \frac{1}{2\pi i} \int_{\Gamma}
+%    \frac{2v^-(y)}{(y - x)^3} \, dy 
+%-\frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
+%-\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
+%-\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
+%&= \frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
+%\end{align*}
+%}
+%\todo[inline]{S-H: How do we get these identities?}
+%\begin{alignat}{3}
+%  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
+%    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
+%  0 &= \frac{1}{2\pi i}\int_{\Gamma}
+%    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
+%    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
+%\end{alignat}
+%{\color{red}
+%and the quadrature formulations are
+%\begin{alignat}{3}
+%  v''(x) &\approx
+%    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
+%    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
+%  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
+%    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
+%    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
+%\end{alignat}
+%where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
+%
+%}
+%
 %{\color{red}

### 2019-07-30 docs/transport/erosion_transport.tex
add modified figs in transport paper
small changes to tortuosity

@@
 \input{preambles.tex}
-%\usepackage{showkeys}
+\usepackage{showkeys}
 \begin{document}
@@
 \end{align}
-To compute such a trajectory, we apply the standard fourth-order
-Runge-Kutta method.  To evaluate $\uu(\ss)$, depending on the proximity
-of $\ss$ to $\bd\Omega$, we either use the trapezoid rule or the
-Barycentric quadrature rule as described in Section~\ref{s:fmm}.
+To compute such a trajectory, we apply the standard explicit
+fourth-order Runge-Kutta method.  To evaluate $\uu(\ss)$, depending on
+the proximity of $\ss$ to $\bd\Omega$, we either use the trapezoid rule
+or the Barycentric quadrature rule as described in Section~\ref{s:fmm}.
 
@@
 
+Having developed numerically accurate methods to compute the velocity
+$\uu$ at points close to the bodies, we are able to compute the
+trajectories of particles passing through an eroded body.  Since the
+trajectories are computed with high-order methods in both space and
+time,  we are able to simulate dynamics very close to the eroding bodies
+(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
+Resolving the flow in these small velocity regions is essential to
+accurately describe anomalous diffusion and
+mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The dynamics of fluid in porous media can be characterized in terms of
-anomalous diffusion.  However, the anomalous diffusion rate depends on
-the properties of the geometry.  In addition to the porosity, the
-distribution of the grains affects the anomalous diffusion rates.  To
-quantify this rate, we require tracer trajectories that are governed by
-equation~\eqref{eqn:trajectories}.  Given a trajectory, we define
-$\lambda_j(t)$ to be the distance travelled by the particle
+The dynamics of fluid in porous media is often characterized in terms of
+anomalous diffusion~\cite{} \todo[inline]{need references}, and the
+anomalous diffusion rate depends on the properties of the geometry.  The
+anomalous diffusion depends on the porosity~\cite{}, but the
+distribution of the bodies also affects the anomalous diffusion rates.
+Since erosion causes certain structure in porous media, calculating the
+anomalous diffusion rates in these geometries is important.
+
+One way to define the anomalous diffusion rate is by using tracer
+trajectories that are governed by equation~\eqref{eqn:trajectories}.
+Given a set of trajectories, we define $\lambda_j(t)$ to be the distance
+travelled by the particle
 \begin{align}
@@
 \end{align}
-If the particle spreading scales with time as $\sigma_\lambda^2 \sim
-t^\alpha$, with $\alpha < 1$, this indicates that the particle
-trajectories are sub-diffusive.  In contrast, if $\sigma_\lambda^2 \sim
-t^2$, the particle trajectories are undergoing a ballistic motion and
-are not affected by the grains.
-
-For early times when the geometry has not eroded, we expect the
-trajectories to be sub-diffusive.  However, as the bodies erode and
-straight preferential channels are formed, we expect the dynamics to
-resemble a ballistic motion.
+At early times, the particles have not explored much of the geometry,
+and we expect a ballistic motion $\sigma_\lambda^2 \sim t^2$.  However,
+as the particles pass the grains, their trajectories are altered, and we
+expect that $\sigma_\lambda^2 \sim t^\alpha$, with $\alpha < 1$, which
+would indicate that the flow is sub-diffusive.  With respect to erosion,
+as the bodies erode, we expect that the channelization of the geometry
+results in more trajectories undergoing a ballistic motion, and this
+would indicate a larger anomalous diffusion rate.
 
@@
 The tortuosity of a geometry quantifies the average amount of turning
-made by a streamline.  Mathematically, it is defined as
+made by a streamline.  The choice of how to average is not universal,
+and Duda et al.~\cite{dud-koz-mat2011} summarize several options for
+averaging.  One particular choice, which we shall adopt, allows us to
+compute the tortuosity in terms of trajectories, or by using an area
+integral over the fluid geometry.  Another advantage of this choice is
+that it is not affected by regions of recirculation.  Mathematically,
+the definition of tortuosity that we use is
 \begin{align}
@@
 at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
-the velocity at the $y$-coordinate along $S$.  Following~\cite{}, the
-trajectories are formed until they cross a second cross-section.  In our
-work, we always initialize the trajectories at $x=-1$ and stop them when
-they reach $x=1$.
+the velocity at the $y$-coordinate along $S$.
+Following~\cite{dud-koz-mat2011}, the trajectories are formed until they
+cross a second cross-section that is parallel to the initial
+cross-section.  In our work, we always initialize the trajectories at
+$x=-1$ and stop them when they reach $x=1$.
 
@@
 outlet.  Recirculation zones are possible in viscous fluids, but they
-only constitute a small fraction of the total porous media.  Therefore,
-the tortuosity defined in equation~\eqref{eqn:tortuosity2} is an upper
-bound for the definition in equation~\eqref{eqn:tortuosity1}.  We have
-used formulas for a particular geometry, and the difference is
-negligible.  Since equation~\eqref{eqn:tortuosity2} does not require the
-additional work of computing particle trajectories, we use this
-definition for the tortuosity.
+only constitute a small fraction of the total porous media and tend to
+have very small velocities.  Therefore, the tortuosity defined in
+equation~\eqref{eqn:tortuosity2} is an upper bound for the definition in
+equation~\eqref{eqn:tortuosity1}, but for the geometries we consider, we
+will show that their difference is negligible.  Since
+equation~\eqref{eqn:tortuosity2} does not require the additional work of
+computing particle trajectories, we use this definition for the
+tortuosity.
+
+The first method to compute numerically compute the tortuosity uses $N_p$ trajectories
+that are initially at $(1,y_i)$, $i=1,\ldots,N_p$, and stopped when
+their $x$ coordinate is 1.  T
+
+with originating at $x=-1$ and terminating at $x=1$, we use the approximation 
+\begin{align}
+  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N_p} 
+    u_x(y_i) \lambda(y_i) \Delta y_i}
+  {\displaystyle\sum_{i=1}^{N_p} u_x(y_i) \Delta y_i}, 
+\end{align}
+where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.
+Similarly, to compute the tortuosity in terms of the Eulerian velocity
+field, we use the approximation
+\begin{align}
+  T = \frac{\sum\limits_{i,j=1}^N \|\uu(\yy_{i,j})\|\Delta x_i \Delta y_j}
+      {\sum\limits_{i,j=1}^N u(\yy_{i,j}) \Delta x_i\Delta y_j},
+\end{align}
+where $\Delta x_i = 1/N$
 
@@
 \end{align*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Streamlines and Tortuosity}
-\label{s:streamlines}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Dump of earlier section for now ... need to fix how this
-is worked into the section}
-Having developed numerically accurate methods to compute the velocity
-$\uu$ at points close to the bodies, we are able to compute the
-trajectories of particles passing through an eroded body.  To find the
-trajectory governed by equation~\eqref{eqn:trajectories}, we use the
-fourth-order explicit Runge-Kutta method with a fixed time step size.
-Since our method is both high-order in time and space, we are able to
-simulate dynamics very close to the eroding bodies (Figure~\ref{fig:}
-\todo[inline]{reference a figure or two from the results section)}.
-Resolving the flow in these small velocity regions is essential to
-accurately describe anomalous diffusion and
-mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.
-
-To calculate tortuosity $T$, we use the simple quadrature rule
-\begin{align}
-  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} 
-    u_x(y_i) \lambda(y_i) \Delta y_i}
-  {\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i}, 
-\end{align}
-where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.
 

### 2019-07-30 docs/transport/erosion_transport.tex
started 20 body numerical results

@@
   v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
-    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
+    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
     {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}, 
@@
 
-The first method to compute numerically compute the tortuosity uses $N_p$ trajectories
-that are initially at $(1,y_i)$, $i=1,\ldots,N_p$, and stopped when
-their $x$ coordinate is 1.  T
-
-with originating at $x=-1$ and terminating at $x=1$, we use the approximation 
+The first method to compute numerically compute the tortuosity uses
+$N_p$ trajectories that are initially at $(1,y_i)$, $i=1,\ldots,N_p$,
+and stopped when their $x$ coordinate is 1.  We choose $y_i$ so that the
+trajectories are initially uniformly spaced in $(-1,1)$.  Having
+computed these trajectories, the tortuosity is approximated as
 \begin{align}
   T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N_p} 
-    u_x(y_i) \lambda(y_i) \Delta y_i}
+    u_x(y_i) \lambda(y_i) \Delta y}
   {\displaystyle\sum_{i=1}^{N_p} u_x(y_i) \Delta y_i}, 
 \end{align}
-where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.
-Similarly, to compute the tortuosity in terms of the Eulerian velocity
-field, we use the approximation
-\begin{align}
-  T = \frac{\sum\limits_{i,j=1}^N \|\uu(\yy_{i,j})\|\Delta x_i \Delta y_j}
-      {\sum\limits_{i,j=1}^N u(\yy_{i,j}) \Delta x_i\Delta y_j},
-\end{align}
-where $\Delta x_i = 1/N$
+where $\Delta y = 2/(N_p + 1)$ and $y_i = -1 + i \Delta y$,
+$i=1,\ldots,N_p$.  Alternatively, to compute the tortuosity in terms of
+the Eulerian velocity field, we first compute the velocity at $(x_i,y_j)
+= (-1 + i\Delta x, -1 + j\Delta y)$, $i,j=1,\ldots,N$, where $\Delta x =
+\Delta y = 2/N$, and the velocity at points inside an eroding body are
+assigned a value of 0.  Then, the tortuosity is approximated as
+\begin{align}
+  T = \frac{\sum\limits_{i,j=1}^N \|\uu(x_i,y_j)\|\Delta x \Delta y}
+      {\sum\limits_{i,j=1}^N u(x_i,y_j) \Delta x \Delta y},
+\end{align}
+where $\uu = (u,v)$.
 
@@
 \end{align*}
+\todo[inline]{Need to flesh this out more}
 
@@
 \includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
-\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
+\includegraphics[width = 0.38 \textwidth]{./figs/1b_0d4r0d1h_shear}
 \caption{\label{fig:NearWall} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider 20 eroding bodies a Hagen-Poiseuille flow.  The background
-flow is 
+We consider 20 eroding bodies initially placed in $[-1,1] \times
+[-1,1]$.  The background flow is the Hagen-Poiseuille flow
 \begin{align}
@@
   \end{array}
-  \right].
-\end{align}
-Initially, $U=1$, and then $U$ is updated at each time step so that the
-pressure drop from $x=-2$ to $x=2$ remains constant.  
+  \right],
+\end{align}
+where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
+to $x=2$ is held fixed at 2.  For equispaced instances of the
+configuration are plotted in Figure~\ref{fig:Eroding20vort}.  The color
+in these plots is the vorticity, and this can be used to determine
+regions of high and low erosion---erosion happens fastest along regions
+of the eroding bodies with a large vorticity in magnitude.  In
+Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
+function of normalized time.  Initially, 62\%  of the geometry eroded
+bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
+area fraction decreases towards 0.  The trend of the area fraction
+resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
+but with a larger initial area fraction.  We also compute the flow rate
+$U$ required to maintain a constant pressure drop across the channel in
+Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
+resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
+except that the initial flow rate is an order of magnitude smaller
+because of the larger initial area fraction.
+
+\begin{figure}[H]
+\begin{center}
+  \includegraphics[height=0.23\textwidth]{./figs/20b_dense1}
+  \includegraphics[height=0.23\textwidth]{./figs/20b_dense101}
+  \includegraphics[height=0.23\textwidth]{./figs/20b_dense201}
+  \includegraphics[height=0.23\textwidth]{./figs/20b_dense301}
+\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
+with the fixed pressure drop condition. The color is the vorticity of
+the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
+256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
+and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the
+forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
+has almost completely eroded.}
+\end{center}
+\end{figure}
+
 {\color{red}
@@
 \includegraphics*[width =\linewidth]{./figs/porosity20dense}
+\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
+no need to make it go below 0}
 \caption{}
@@
 very little shear stress and the effect of erosion is slight.
-
-\begin{figure}[H]
-\begin{center}
-  \includegraphics[height=0.23\textwidth]{./figs/20b_dense1}
-  \includegraphics[height=0.23\textwidth]{./figs/20b_dense101}
-  \includegraphics[height=0.23\textwidth]{./figs/20b_dense201}
-  \includegraphics[height=0.23\textwidth]{./figs/20b_dense301}
-%\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
-%\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\
-%\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
-%\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
-\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
-  with the fixed pressure drop condition. The color is the vorticity of
-  the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
-  256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
-  and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In
-  the forth frame, bodies 4, 12, and 17 have vanished completely, and
-  body 19 has almost completely eroded.}
-\end{center}
-\end{figure}
 
@@
 (a) The 
-x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
+x-component velocity u(-1, y) with respect to its maximum velocity
+$u_{\max}=2.9828
 \times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 

### 2019-07-31 docs/transport/erosion_transport.tex
add new figs in transport paper
working on 20 body example

@@
 
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
+\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
+\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
+\caption{\label{fig:NearWall_vort} }
+\end{center}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
-to $x=2$ is held fixed at 2.  For equispaced instances of the
-configuration are plotted in Figure~\ref{fig:Eroding20vort}.  The color
-in these plots is the vorticity, and this can be used to determine
-regions of high and low erosion---erosion happens fastest along regions
-of the eroding bodies with a large vorticity in magnitude.  In
+to $x=2$ is held fixed at 2.  We start by analyzing the effect of
+erosion on the area fraction and the flow rate.  In
 Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
@@
 except that the initial flow rate is an order of magnitude smaller
-because of the larger initial area fraction.
+because of the larger initial area fraction.  Starting around normalized
+time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
+which indicates that the flow rate can be written as a power law.  Using
+a line of best fit, the flow rate is approximately \begin{align} U
+\approx \left(\frac{t}{t_f}\right)^{15/4}, \end{align}
+\todo[inline]{update this with whatever S-H gets} which is the dashed
+line in Figure~\ref{fig:Eroding20flowrate}(b).
+
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/porosity20dense}
+\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
+no need to make it go below 0}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
+\todo[inline]{SH: In this figure, can you superimpose a line of best fit
+from about normalized time 0.2 to normalize time 1.  Doing this crudely,
+I got a slope of 15/4}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20 nearly
+ touching eroding bodies and the eroding speed versus time. 
+(b) The incoming flow rate of $U$ in log scale versus time. 
+Under fixed pressure drop condition, $U$ will be small initially,
+increase when bodies are eroding, and grow exponentially 
+to 1 when there is no body in the fluid. }
+\end{figure}
+
+Snapshots of the bodies at four equispaced times are shown in
+Figure~\ref{fig:Eroding20vort}.   The colormap is the vorticity which is
+equivalent to the shear stress when restricted to the eroding bodies.
+Therefore, erosion is fastest in regions where the magnitude of the
+vorticity is largest.  Initially, several of the eroding bodies are
+close to the outer wall.  In particular, with $h=L_2/N_\out$, the
+distance between bodies 1, 6, 13, and 15 are $1.3h$, $2.9h$, $2.8h$, and
+$1.3h$, respectively.  In addition, since each body is discretized with
+$N_\iin=256$ points, the distance between several pairs of eroding
+bodies is too small to be accurately resolved with the trapezoid rule at
+the prescribed resolution.  Particular pairs include bodies 1 \& 6, 3 \&
+9, 6 \& 8, and 14 \& 18.  By using the Barycentric quadrature rule, the
+interaction between these nearly-touching bodies can be accurately
+resolved at the prescribed resolution.
 
@@
 
-{\color{red}
-We
-measure the area occupied by bodies 
-during the eroding and record the flow rate $U$ quantifily in log scale
-during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
-Since we simulate the erosion by applying fixed pressure drop 
-the flow rate $U$ is small when there are many bodies in the fluid and 
-when the area fraction is getting smaller $U$ is getting larger.
-In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
-[-1,1]$ is occupied by 20 bodies initially and the flow rate $U$ starts from $9.86\times 10^{-5}$. 
-Then the eroding speed is increasing
-when more and more bodies are vanished in the fluid and 
-the maximum eroding speed happens when the area fraction equals 7.57\% 
-which is occupied by 8 bodies.
-When all the bodies have vanished completely the flow rate $U$ is equal to 1.
-In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate $U$ increases exponentially 
-with growth rate close to $\ln10^4$. }
-
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/porosity20dense}
-\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
-no need to make it go below 0}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20 nearly
- touching eroding bodies and the eroding speed versus time. 
-(b) The incoming flow rate of $U$ in log scale versus time. 
-Under fixed pressure drop condition, $U$ will be small initially,
-increase when bodies are eroding, and grow exponentially 
-to 1 when there is no body in the fluid. }
-\end{figure}
-
-Snapshots of the
-bodies at four equispaced times are shown in
-Figure~\ref{fig:Eroding20vort}.   The colormap is the vorticity which is
-equivalent to the shear stress when restricted to the eroding bodies.
-Therefore, erosion is fastest in regions where the magnitude of the
-vorticity is largest.
-
-Initially, several of the eroding bodies are close to the outer wall.
-In particular, with $h=L_2/N_\out$, the distance between bodies 1, 6,
-13, and 15 are $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively.  In
-addition, since each body is discretized with $N_\iin=256$ points, the
-distance between several pairs of eroding bodies is too small to be
-accurately resolved at the prescribed resolution.  Particular pairs
-include bodies 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18.  By using the
-Barycentric quadrature rule, the interaction between these
-nearly-touching bodies can be accurately resolved at the prescribed
-resolution.
-
-In~\cite{qua-moo2018}, we observed that erosion causes the space
-between nearly touching bodies to quickly expand, and flat faces develop
-along the region of near contact.  This qualitative behavior is also
-observed in Figure~\ref{fig:Eroding20vort}, such as between bodies 3
-\&4 and 15 \& 16.  However, by resolving bodies that are
-much closer to one another when compared to our previous
-work~\cite{qua-moo2018}, we see that it is possible for very little
-erosion to occur between a pair of bodies.  In particular, for pairs of
-bodies where the channel between the bodies is nearly perpendicular to
-the main flow direction (bodies 1 \& 6, 3 \& 9, and 5 \& 13), there is
-very little shear stress and the effect of erosion is slight.
+In~\cite{qua-moo2018}, we observed that erosion causes the space between
+nearly touching bodies to quickly expand, and flat faces develop along
+the region of near contact.  This qualitative behavior is also observed
+in Figure~\ref{fig:Eroding20vort}, such as between bodies 3 \& 4 and 15
+\& 16.  However, by resolving bodies that are much closer to one another
+when compared to our previous work~\cite{qua-moo2018}, we see that it is
+possible for very little erosion to occur between a pair of bodies.  In
+particular, for pairs of bodies where the channel between the bodies is
+nearly perpendicular to the main flow direction (bodies 1 \& 6, 3 \& 9,
+and 5 \& 13), there is very little shear stress and the effect of
+erosion is slight.
 
@@
 therefore erosion rate, are much larger than the other regions.  These
-channels can be further visualized by considering the streamlines at
-several configurations of the eroding body.  In
-Figure~\ref{fig:Eroding20tracer}, we simulate 200 tracers that are
-initially to the left of the porous region and equispaced in $y$.  There
-are two clear region where the tracers pass through the geometry
-much faster than the other regions.  To illustrate the ability of the
-Barycentric quadrature formula, streamlines very close to the eroding
-bodies are illustrated in the last frame of Figure~\ref{fig:Eroding20tracer}.
+channels can be further visualized by considering the streamlines.  In
+Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
+time step in Figure~\ref{fig:Eroding20vort}, and we simulate 200
+tracers.  The tracers are initially placed at $x=-1$ and equispaced in
+$y$.  There are two clear region where the tracers pass through the
+geometry much faster than the other regions.  One of these fast regions
+is located between the bodies and the solid wall at $y=1$, and the other
+cuts through the porous region with the upper part of the channel formed
+by bodies 1, 4, 6, and 8.  To illustrate the ability of the Barycentric
+quadrature formula, streamlines very close to the eroding bodies are
+illustrated in the last frame of Figure~\ref{fig:Eroding20tracer}.
 
@@
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
-
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}\\
-
-%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
-%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b240}
-%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
 \caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
-  the fluid with 20 bodies. The five first snapshots are evenly spaced in time.
-  The tracers are evenly spread in the $y$-direction and released at
-  $x=-1$. The bottom right frame is a zoom window of the bottom middle frames. 
-Since we use a Barycentric quadrature rule
-  and the fourth order Runge Kutta method, the tracers can be very close
-  to but not penetrate the bodies.}
+the fluid with 20 bodies. The five first snapshots are evenly spaced in
+time.  The tracers are evenly spread in the $y$-direction and released
+at $x=-1$. The bottom right frame is a zoom window of the bottom middle
+frames.  Since we use a Barycentric quadrature rule and the fourth order
+Runge Kutta method, the tracers can be very close to but not penetrate
+the bodies.}
 \end{center}
@@
 %
+%{\color{red}
+%We
+%measure the area occupied by bodies 
+%during the eroding and record the flow rate $U$ quantifily in log scale
+%during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
+%Since we simulate the erosion by applying fixed pressure drop 
+%the flow rate $U$ is small when there are many bodies in the fluid and 
+%when the area fraction is getting smaller $U$ is getting larger.
+%In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
+%[-1,1]$ is occupied by 20 bodies initially and the flow rate $U$ starts from $9.86\times 10^{-5}$. 
+%Then the eroding speed is increasing
+%when more and more bodies are vanished in the fluid and 
+%the maximum eroding speed happens when the area fraction equals 7.57\% 
+%which is occupied by 8 bodies.
+%When all the bodies have vanished completely the flow rate $U$ is equal to 1.
+%In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate $U$ increases exponentially 
+%with growth rate close to $\ln10^4$. }
 

### 2019-07-31 docs/transport/erosion_transport.tex
editing in transport paper

--- 2019-07-30 docs/transport/erosion_transport.tex
@@
   A single body eroding in Stokes flow. The color indicates the shear
-  stress on the body. Therefore, erosion is fastest in the yellow
+  stress on the body in log scale. Therefore, erosion is fastest in the red
   regions and slowest in the blue regions.  In this simulation, we use
@@
 \end{figure}
-
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
+\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
+\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
+\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a single body eroding 
+at time t=0.1001. The initial distances from body to wall are $h$ (left), $h/2$
+  (middle), and $h/10$ (right).  }
+\end{center}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-07-31 docs/transport/erosion_transport.tex

--- 2019-07-31 docs/transport/erosion_transport.tex
@@
 \end{figure}
-
 \begin{figure}[H]
@@
 \includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
-\caption{\label{fig:NearWall_vort} }
+\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a single body eroding 
+at time t=0.1001. The initial distances from body to wall are $h$ (left), $h/2$
+  (middle), and $h/10$ (right).  }
 \end{center}

### 2019-07-31 docs/transport/erosion_transport.tex
some small changes to 20 body section

--- 2019-07-31 docs/transport/erosion_transport.tex
@@
 Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
-function of normalized time.  Initially, 62\%  of the geometry eroded
-bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
-area fraction decreases towards 0.  The trend of the area fraction
+function of normalized time.  Initially, 62\% of the geometry is eroded
+bodies corresponding to a porosity of $0.38$, and the area fraction
+decreases to 0 as the bodies erode.  The trend of the area fraction
 resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20 nearly
- touching eroding bodies and the eroding speed versus time. 
-(b) The incoming flow rate of $U$ in log scale versus time. 
-Under fixed pressure drop condition, $U$ will be small initially,
-increase when bodies are eroding, and grow exponentially 
-to 1 when there is no body in the fluid. }
+\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
+nearly touching eroding bodies versus normalized time. (b): The incoming
+flow rate, $U$, for a fixed pressure drop across the channel versus
+normalized time.  The flow rate is initially very small, but it
+eventually increases as a power law (dashed line) towards the flow rate
+$U=1$ that occurs once all the bodies have eroded.}
 \end{figure}
@@
   \includegraphics[height=0.23\textwidth]{./figs/20b_dense301}
+  \todo[inline]{S-H: Increase the font of the colorbar}
 \caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies

### 2019-07-31 docs/transport/erosion_transport.tex
increase the font of fig. 4 in transport paper
modify fig. 3(a) in transport paper
working on single body text

@@
 \section{Introduction}
-\label{s:intro}
+\label{sec:intro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Governing Equations}
-\label{s:formulation}
+\label{sec:formulation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Potential}
-\label{s:DLPcomplex}
+\label{sec:DLPcomplex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Numerical Methods}
-\label{s:method}
+\label{sec:method}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Spatial Discretization}
-\label{s:spatialDiscretization}
+\label{sec:spatialDiscretization}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Efficiently Applying the Quadrature}
-\label{s:fmm}
+\label{sec:fmm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Time Integration}
-\label{s:time}
+\label{sec:time}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In Section~\ref{s:transport}, we we analyze passive tracers suspended in
+In Section~\ref{sec:transport}, we we analyze passive tracers suspended in
 an eroded geometry.  Give such a geometry $\Omega$, a tracer $\ss(t)$
@@
 the proximity of $\ss$ to $\bd\Omega$, we either use the trapezoid rule
-or the Barycentric quadrature rule as described in Section~\ref{s:fmm}.
+or the Barycentric quadrature rule as described in Section~\ref{sec:fmm}.
 
@@
 \section{Transport, Tracers, and Tortuosity}
-\label{s:transport}
+\label{sec:transport}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Numerical Results}
-\label{s:results}
+\label{sec:results}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the center of the eroding body $1.5$ times the body's radius above the
-solid wall.  By using the numerical integration scheme described in
-Section~\ref{s:method}, the eroding body can be placed much closer to
-the solid wall.  In the following experiments, we consider an eroding
+solid wall.  By using the Barycentric quadrature rule described in
+Section~\ref{sec:bary} rather than the trapezoid rule, the eroding body
+can be placed much closer to the solid wall without requiring an
+unreasonable number of discretization points.  We consider an eroding
 body that is initially a circle of radius $r=0.4$ and is placed near the
@@
 
-With this setup, many of the discretization points on the eroding body
-are too close to the outer wall for the trapezoid rule to achieve
-sufficient accuracy.  However, by using the Barycentric quadrature rule,
-the numerical stable simulations are possible.  In
-Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
-several equispaced time steps, and the color of indicates the erosion
-rate (magnitude of the shear stress).  Comparing our results to Mitchell
-and Spagnolie~\cite{mit-spa2017} (Figure 7(c)), we see similar results.
-In particular, between the eroding body and the solid wall the flow is
-very small and there is no recirculation, and this is consistent with
-three-dimensional results~\cite{cah-feu2002}.  Moreover, for all three
-distances, the shear stress is positive \todo[inline]{S-H: Is this
-right?  Is the shear stress ever negative?  I might expect so since
-there are two stagnation points}, so the erosion is smooth.
-
-where the shear stress is smallest near the zero background flow line
-$y=-1$.  Moreover, since the shear stress is everywhere positive, the
-erosion rate, which is the magnitude of the shear stress, is a smooth
-function.  The result is that the eroding shape does not have any
-stagnation points where corners will develop.
+In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
+several equispaced time steps.  For the three initial configurations,
+the shear stress is positive for all time, but varies over several
+orders of magnitude.  Therefore, we color eroding body's boundary
+according to the logarithm of the shear stress.  Comparing our results
+to Mitchell and Spagnolie~\cite{mit-spa2017} (Figure 7(c)), we see that
+the body shapes are similar.  The differences we can attribute to our
+assumption of a two-dimensional flow.  In three dimensions, there is no
+recirculation between the solid wall and the spherical
+body~\cite{cha-feu2003}.  In contrast, between a two dimensional
+circular body and a solid wall, there are regions of recirculation on
+the fore and aft sides of the body.  In Figure~\ref{fig:NearWall_vort},
+we plot the vorticity at the final configuration, and the where the
+vorticity is smallest corresponds to the region where there is a slow
+recirculation.
+
+Since the shear stress is always positive, the erosion rate is a smooth
+function and does not lead to the development of corners.  However,
+since the location where the shear stress is minimized is close to
+regions of high shear stress, the rate of erosion changes quickly, and
+the result is a body that seems to be developing a corner, although it
+is not.  Similar to the three dimensional case~\cite{mit-spa2017}, this
+region of high curvature develops in the top half of the eroding body.
 
@@
 \caption{\label{fig:NearWall} 
-  A single body eroding in Stokes flow. The color indicates the shear
-  stress on the body in log scale. Therefore, erosion is fastest in the red
-  regions and slowest in the blue regions.  In this simulation, we use
-  three minimum body-to-wall initial distances $d=h$ (left), $h/2$
-  (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points
-  on the body, a time step size of $\Dt=10^{-4}$, and smoothing
-  parameters $\eps = 15/256$ and $\sigma=10/256$.}
+  A single body eroding in a Stokes flow. The color denotes the
+  logarithm of the shear stress on the body. Therefore, erosion is
+  fastest in the red regions (top half)and slowest in the blue regions
+  (lower half).  The body is initialized at three different distances
+  from the lower wall: $d=h$ (left), $h/2$ (middle), and $h/10$
+  (right).}
 \end{center}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/porosity20dense}
+\includegraphics*[width =\linewidth]{./figs/porosity20dense_new}
 \todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
-no need to make it go below 0}
+no need to make it go below 0. Done 07312019}
 \caption{}
@@
 \begin{center}
-  \includegraphics[height=0.23\textwidth]{./figs/20b_dense1}
-  \includegraphics[height=0.23\textwidth]{./figs/20b_dense101}
-  \includegraphics[height=0.23\textwidth]{./figs/20b_dense201}
-  \includegraphics[height=0.23\textwidth]{./figs/20b_dense301}
-  \todo[inline]{S-H: Increase the font of the colorbar}
+  \includegraphics[height=0.22\textwidth]{./figs/20b_dense1}
+  \includegraphics[height=0.22\textwidth]{./figs/20b_dense101}
+  \includegraphics[height=0.22\textwidth]{./figs/20b_dense201}
+  \includegraphics[height=0.22\textwidth]{./figs/20b_dense301_new}
+  \todo[inline]{S-H: Increase the font of the colorbar.   DONE 07312019}
 \caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
@@
 \section{Conclusions}
-\label{s:conclusions}
+\label{sec:conclusions}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-08-01 docs/transport/erosion_transport.tex
modify figures in transport paper
worked on numerical results

@@
 initialized at $y$ along $S$ is
-\begin{align*}
+\begin{align}
   \tau(y) = \frac{\lambda(y)}{d}.
-\end{align*}
+  \label{eqn:localTort}
+\end{align}
 \todo[inline]{Need to flesh this out more}
@@
 results with a similar numerical experiment performed by Mitchell and
-Spagnolie~\cite{mit-spa2017}, rather a pressure drop boundary condition,
-we impose the shear flow
+Spagnolie~\cite{mit-spa2017}, rather than a pressure drop boundary
+condition, we impose the shear flow
 \begin{align}
@@
 unreasonable number of discretization points.  We consider an eroding
-body that is initially a circle of radius $r=0.4$ and is placed near the
-no-slip wall at $y=-1$.  We discretize the eroding body with
-$N_\iin=256$ discretization points, and the center of the eroding body
-is initially chosen so that the distance between the body and the solid
-wall are $h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  For all
-three simulations, we use the time step size $\Delta t=10^{-4}$.
+body that is initially a circle of radius $r=0.4$.  We discretize the
+eroding body with $N_\iin=256$ discretization points, and its center is
+chosen so that the distance between the body and the solid wall is
+$h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  For all three
+simulations, we use the time step size $\Delta t=10^{-4}$.
 
 In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
-several equispaced time steps.  For the three initial configurations,
-the shear stress is positive for all time, but varies over several
-orders of magnitude.  Therefore, we color eroding body's boundary
-according to the logarithm of the shear stress.  Comparing our results
-to Mitchell and Spagnolie~\cite{mit-spa2017} (Figure 7(c)), we see that
-the body shapes are similar.  The differences we can attribute to our
-assumption of a two-dimensional flow.  In three dimensions, there is no
+equispaced time steps.  For the three initial configurations, the shear
+stress is positive for all time, but varies over several orders of
+magnitude.  Therefore, we color the eroding body's boundary with the
+logarithm of the shear stress.  Since the shear stress is always
+positive, the erosion rate is a smooth function and does not lead to the
+development of corners.  However, the shear stress varies over several
+orders of magnitude, and this leads to interesting shapes.  For
+instance, in the top hemisphere, there is a sudden increase in the shear
+stress, and this leads to a region of high curvature.  This behavior is
+also present in three dimensions~\cite{mit-spa2017} (Figure 7(c)).  The
+biggest difference between the two- and three-dimensional results is the
+presence of a recirculation zone.  In three dimensions, there is no
 recirculation between the solid wall and the spherical
-body~\cite{cha-feu2003}.  In contrast, between a two dimensional
-circular body and a solid wall, there are regions of recirculation on
-the fore and aft sides of the body.  In Figure~\ref{fig:NearWall_vort},
-we plot the vorticity at the final configuration, and the where the
-vorticity is smallest corresponds to the region where there is a slow
-recirculation.
-
-Since the shear stress is always positive, the erosion rate is a smooth
-function and does not lead to the development of corners.  However,
-since the location where the shear stress is minimized is close to
-regions of high shear stress, the rate of erosion changes quickly, and
-the result is a body that seems to be developing a corner, although it
-is not.  Similar to the three dimensional case~\cite{mit-spa2017}, this
-region of high curvature develops in the top half of the eroding body.
+body~\cite{cha-feu2003}.  In contrast, the two-dimensional flow Stokes
+flow can have recirculation zones~\cite{chw-wu1975, hig1985}. To
+visualize the flow, we plot the vorticity of the final time step from
+Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  The region
+where the vorticity is smallest corresponds to the recirculation region.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider 20 eroding bodies initially placed in $[-1,1] \times
-[-1,1]$.  The background flow is the Hagen-Poiseuille flow
+We consider 20 eroding bodies that are discretized with $N_\iin=256$
+points and are initially placed in $[-1,1] \times [-1,1]$.  The
+background flow is the Hagen-Poiseuille flow
 \begin{align}
@@
 which indicates that the flow rate can be written as a power law.  Using
-a line of best fit, the flow rate is approximately \begin{align} U
-\approx \left(\frac{t}{t_f}\right)^{15/4}, \end{align}
-\todo[inline]{update this with whatever S-H gets} which is the dashed
-line in Figure~\ref{fig:Eroding20flowrate}(b).
+a line of best fit, the flow rate is approximately 
+\begin{align} 
+  U \approx \left(\frac{t}{t_f}\right)^{3.43},
+\end{align}
+which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).
 
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/porosity20dense_new}
-\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
-no need to make it go below 0. Done 07312019}
+\includegraphics*[width =\linewidth]{./figs/porosity20dense}
 \caption{}
 \end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
+\begin{subfigure}[b]{0.51\textwidth}
 \includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
-\todo[inline]{SH: In this figure, can you superimpose a line of best fit
-from about normalized time 0.2 to normalize time 1.  Doing this crudely,
-I got a slope of 15/4}
 \caption{}
@@
 Snapshots of the bodies at four equispaced times are shown in
-Figure~\ref{fig:Eroding20vort}.   The colormap is the vorticity which is
+Figure~\ref{fig:Eroding20vort}.  The color is the vorticity which is
 equivalent to the shear stress when restricted to the eroding bodies.
@@
 vorticity is largest.  Initially, several of the eroding bodies are
-close to the outer wall.  In particular, with $h=L_2/N_\out$, the
-distance between bodies 1, 6, 13, and 15 are $1.3h$, $2.9h$, $2.8h$, and
-$1.3h$, respectively.  In addition, since each body is discretized with
-$N_\iin=256$ points, the distance between several pairs of eroding
-bodies is too small to be accurately resolved with the trapezoid rule at
-the prescribed resolution.  Particular pairs include bodies 1 \& 6, 3 \&
-9, 6 \& 8, and 14 \& 18.  By using the Barycentric quadrature rule, the
+closer to the outer wall than the $5h$ threshold required to guarantee
+sufficiently accurate quadrature with the trapezoid rule.  In
+particular, with $h=L_2/N_\out$, the distance between bodies 1, 6, 13,
+and 15 are $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively.  In
+addition, the distance between several pairs of eroding bodies is too
+small to be accurately resolved with the trapezoid rule at the
+prescribed resolution.  Particular pairs include bodies 1 \& 6, 3 \& 9,
+6 \& 8, and 14 \& 18.  By using the Barycentric quadrature rule, the
 interaction between these nearly-touching bodies can be accurately
@@
 \begin{center}
-  \includegraphics[height=0.22\textwidth]{./figs/20b_dense1}
-  \includegraphics[height=0.22\textwidth]{./figs/20b_dense101}
-  \includegraphics[height=0.22\textwidth]{./figs/20b_dense201}
-  \includegraphics[height=0.22\textwidth]{./figs/20b_dense301_new}
-  \todo[inline]{S-H: Increase the font of the colorbar.   DONE 07312019}
+  \includegraphics[height=0.225\textwidth]{./figs/20b_dense1}
+  \includegraphics[height=0.225\textwidth]{./figs/20b_dense101}
+  \includegraphics[height=0.225\textwidth]{./figs/20b_dense201}
+  \includegraphics[height=0.225\textwidth]{./figs/20b_dense301}
 \caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
@@
 nearly touching bodies to quickly expand, and flat faces develop along
-the region of near contact.  This qualitative behavior is also observed
-in Figure~\ref{fig:Eroding20vort}, such as between bodies 3 \& 4 and 15
-\& 16.  However, by resolving bodies that are much closer to one another
-when compared to our previous work~\cite{qua-moo2018}, we see that it is
-possible for very little erosion to occur between a pair of bodies.  In
-particular, for pairs of bodies where the channel between the bodies is
-nearly perpendicular to the main flow direction (bodies 1 \& 6, 3 \& 9,
-and 5 \& 13), there is very little shear stress and the effect of
-erosion is slight.
+the region of near contact.  This qualitative behavior is present in
+Figure~\ref{fig:Eroding20vort} between bodies 3 \& 4, 15 \& 16, and
+others.  However, now that we can resolve bodies that are much closer
+together, we observe that, at least initially, very little erosion
+occurs between certain pairs of bodies.  For instance the opening
+between bodies 1 \& 6 grows much slower than the opening between bodies
+15 \& 16.  A common feature of the openings that grow slowly is that
+they are nearly perpendicular to the main flow direction, and this
+results in very low erosion because of the small shearing.  For example,
+the openings between the pair of bodies 1 \& 6, 3 \& 9, and 5 \& 13.
 
@@
 Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
-time step in Figure~\ref{fig:Eroding20vort}, and we simulate 200
-tracers.  The tracers are initially placed at $x=-1$ and equispaced in
-$y$.  There are two clear region where the tracers pass through the
-geometry much faster than the other regions.  One of these fast regions
-is located between the bodies and the solid wall at $y=1$, and the other
-cuts through the porous region with the upper part of the channel formed
-by bodies 1, 4, 6, and 8.  To illustrate the ability of the Barycentric
-quadrature formula, streamlines very close to the eroding bodies are
-illustrated in the last frame of Figure~\ref{fig:Eroding20tracer}.
+time step from Figure~\ref{fig:Eroding20vort}, and we simulate 200
+tracers.  The tracers are initially placed at $x=-1$ and are equispaced
+in $y$.  The trajectories are shown at 5 different times, and the final
+plot is a zoom in of the lower right quadrant of the fifth time step.
+There are three clear regions where the tracers pass through the
+geometry fastest.  Two of these regions are located between the bodies
+and the solid walls at $y=\pm 1$, and the third cuts through the porous
+region with the upper part of the channel formed by bodies 1, 4, 6, and
+8.  Since the flow is fastest in these regions, the shearing is largest,
+and this causes these openings to grow fastest which can be observed in
+Figure~\ref{fig:Eroding20vort}.
 
@@
 \caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
-the fluid with 20 bodies. The five first snapshots are evenly spaced in
-time.  The tracers are evenly spread in the $y$-direction and released
-at $x=-1$. The bottom right frame is a zoom window of the bottom middle
-frames.  Since we use a Barycentric quadrature rule and the fourth order
-Runge Kutta method, the tracers can be very close to but not penetrate
-the bodies.}
+the second geometry from Figure~\ref{fig:Eroding20vort}. The tracers are
+initialized at $x=-1$ and are evenly spaced in the $y$-direction. The
+first five snapshots are evenly spaced in time.  The bottom right frame
+is a zoom window of the fifth snapshot.  Since we use a Barycentric
+quadrature rule and the fourth-order Runge-Kutta method, the tracers can
+be very close to but not penetrate the bodies.}
 \end{center}
@@
 
-{\color{red} 
-Besides the channels between two bodies, there is a single channel goes
-across the domain horizontally and the flow has been concentrated in
-this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
-channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
-12, and 6 \& 19.  We can get a better understanding of this channel from
-the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In Fig.~\ref{fig:Eroding20tracer}, 
-the flow (or tracer) first comes from three small channels between outer wall \& body
-10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
-one and go into the main channel between bodies 1 \& 9.  From the first
-frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
-is expanding faster than other channel and bodies 4 \& 12 has vanished
-and body 19 is almost gone in the forth frame.  The reason of fast
-expansion of this channel is the high vorticity.  In the forth frame of
-Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
-high on the side of bodies which form this channel so the bodies are
-eroded fast on the side of this channel or have vanished completely.
-
-Furthermore, how long the body lasts in the fluid depends on not only the size of
-the body but also the location of the body.  For example, the first
-three vanishing bodies are body 12 (as t=0.0256), 4 (as t=0.0278), then
-17 (as t=0.0287).  Since body 4 is located in the main flow channel so
-the body 4 is vanished earlier than body 17 although the initial size of
-body 4 is larger than the size of body 17.  This channel will keep
-expanding and the bodies around this channel will vanish earlier than
-others.  After body 17, the next 8 vanished bodies with respect to time
-are body 19 (as t=0.0312),  body 7 (as t=0.0325), body 20 (as t=0.0329),
-body 8 (as t=0.0349), body 10 (as t=0.0353), body 3 (as t=0.0356), body
-14 (as t=0.0363), then body 9 (as t=0.0376).  All of these eight bodies
-were around this channel before they are gone.
-
-For the flat faces at the sites of near contact, since we put the body
-be close to one another so we are able to see all the channels between
-two close bodies have flat faces.  Besides the channels between bodies,
-we also observe the flat faces on the bodies which are close to the
-outer wall. For example, we see the flat faces on the top of bodies 1 \&
-6 and the bottom of bodies 13 \& 15.
-
-Since we use a Barycentric quadrature rule to approximate the velocity
-of tracers and apply the fourth order Runge Kutta method to find the new
-locations of tracers in each step, the tracers can be very close to but
-not penetrate the bodies.  Those body-closed tracers are moving
-perfectly so we are able to observe the details of the interaction of
-bodies and fluid.  Although the direction of flow is from left to right,
-the tracers will not only travel horizontally but also vertically.  In
-the bottom middle frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
-climb up from right to left around the body.  There is a zoom windows of
-the climbing tracers trajectories in the bottom right frame of Fig.~\ref{fig:Eroding20tracer} and
-they are taken from the bottom middle frame of
-Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the bottom right frame of 
-Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
-from the channel below the body, climb up to the left, then go to the
-right and join another tracers in the channel above the body. 
-}
-%\begin{figure}[H]
-%\begin{center}
-%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
-%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
-%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
-%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
-%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
-%  tracers around the bodies. Since we use a Barycentric quadrature rule
- % and the fourth order Runge Kutta method, the tracers can be very close
- % to but not penetrate the bodies.}
-%\end{center}
-%\end{figure}
+Next, we use the tracer trajectories to compute the anomalous diffusion
+rates and the tortuosities in the eroding geometry.  Since these
+calculations use a statistical analysis of the tracer trajectories, we
+increase the number of trajectories to $N_p = 1000$.  Again, the tracers
+are initialized at $x=-1$, and their $y$ coordinates are distributed
+evenly across the entire channel.  To compute the tortuosity, we
+require the velocity at the initialization points of the tracers.  These
+normalized velocities are plotted in Figure~ref{fig:Eroding20tort}(a)
+for the eroded geometry with porosity 62.9\% (see
+Figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
+work of Matyka et al.~\cite{matyka2008tortuosity} (see Figure 4(a)),
+except that our cross-section does not cut through any of the bodies.
+Next, in Figure~\ref{fig:Eroding20tort}(b), we plot the local
+tortuosity~\eqref{eqn:localTort} by calculating the length of each
+trajectory as it traverses the channel from $x=-1$ to $x=1$ in
+Figure~\ref{fig:Eroding20tort}(b), and dividing by the length of the
+channel.  The local tortuosity ranges from 1 to 1.27, meaning that one
+of the tracers travelled 27\% farther than it would have if the bodies
+had been absent.  The average tracer travelled 9.79\% farther than if
+the bodies had been absent, meaning that the tortuosity of the eroded
+channel is $1.098$.  Again, comparing the local tortuosity to
+Matyka~\cite{matyka2008tortuosity} (Figure 4(b)), the results are
+qualitatively similar. However, since our initial cross-section does not
+cut through any bodies, the local tortuosity does not have any gaps.
+The discontinuities correspond to neighboring tracers with one traveling
+much farther than the other.  In Figure~\ref{fig:Eroding20tort}(c), we
+plot pairs of trajectories that correspond to the ten largest jumps in
+the local tortuosity.  Corresponding pairs are always plotted in the
+same color.  The discrepancy between the trajectory lengths can be
+attributed to the tracers diverging from one another as they approach
+opposite sides of a stagnation point in the flow.
 
@@
 \includegraphics*[width =\linewidth]{./figs/tort_local20_268}
+\todo[inline]{S-H: Can cut the ylimit at 1.3}
 \caption{}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20tort} The tortuosity study in the fluid with 
-20 nearly touching bodies when the porosity is 62.9 \%.
-(a) The 
-x-component velocity u(-1, y) with respect to its maximum velocity
-$u_{\max}=2.9828
-\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
-(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
-(c) The largest 10 difference of 
-local tortuosity $\tau$ at two neighboring tracers in
- 20 nearly touching bodies eroding when the porosity is 62.9 \% 
-and the tortuosity is 1.0979. The same color of a pair of trajectories 
-means they are from two neighboring tracers.}
-%(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
-%(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
+\caption{\label{fig:Eroding20tort} The tortuosity of an eroded geometry
+with porosity 62.9\%. (a) The x-component of the velocity $u(-1, y)$
+normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
+local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
+averaged tortuosity through the channel is $1.098$.  (c) The
+trajectories resulting in the ten largest differences between
+neighboring trajectories.  Neighboring trajectories have the same
+color.}
 \end{figure}
-
-{\color{red}
-In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
-from the starting cross section x = -1 to 
-the end cross section x = 1 and 
-use the local tortuosity to analysis the effect
-of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
-In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
-x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
-\times 10^{-3}$ at equal spreading tracers on the starting cross section.
-The velocity is continuous along the starting cross section and
-acting as several Poiseuille flows. This velocity graph is different
-from the one in~\cite{matyka2008tortuosity} since we choose our cross
-section to be the beginning of the flow before the fluid touches any
-body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
-$\tau(y)=\lambda(y)/d$
-of the tracers at $y$ on the starting cross section x = -1 
-where $d = 2$.
-This graph is not continuous 
-and the jumps in $\tau$ mean that the initial neighboring tracers have been
-seperated by the bodies. 
-The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
-}
-
-{\color{red}
-In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
-$\tau$ at two neighboring tracers 
-and draw the trajectories of neighboring tracers
-if the difference of $\tau$ at the neighboring tracers is large. 
-From Fig.~\ref{fig:Eroding20tort}(c), we collect the 10 largest difference of $\tau$ 
-at the neighboring tracers and 
-draw the pair of trajectories in the same color and 
-are able to tell the neighboring trajectories will be very 
-different if they are separated by bodies.
-For each pair of trajectories, 
-they are splitted by the body at the left side of the body, then
-one of them goes up and the other one goes down along the body 
-until they rejoin with each other at the right side of body.  
-Furthermore, the pair trajectories could be splitted by more than one body, 
-for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
-are splitted by two close bodies.
-}
 
@@
 %with growth rate close to $\ln10^4$. }
+%Besides the channels between two bodies, there is a single channel goes
+%across the domain horizontally and the flow has been concentrated in
+%this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
+%channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
+%12, and 6 \& 19.  We can get a better understanding of this channel from
+%the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In Fig.~\ref{fig:Eroding20tracer}, 
+%the flow (or tracer) first comes from three small channels between outer wall \& body
+%10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
+%one and go into the main channel between bodies 1 \& 9.  From the first
+%frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
+%is expanding faster than other channel and bodies 4 \& 12 has vanished
+%and body 19 is almost gone in the forth frame.  The reason of fast
+%expansion of this channel is the high vorticity.  In the forth frame of
+%Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
+%high on the side of bodies which form this channel so the bodies are
+%eroded fast on the side of this channel or have vanished completely.
+%{\color{red} 
+%Furthermore, how long the body lasts in the fluid depends on not only
+%the size of the body but also the location of the body.  For example,
+%the first three vanishing bodies are body 12 (as t=0.0256), 4 (as
+%t=0.0278), then 17 (as t=0.0287).  Since body 4 is located in the main
+%flow channel so the body 4 is vanished earlier than body 17 although the
+%initial size of body 4 is larger than the size of body 17.  This channel
+%will keep expanding and the bodies around this channel will vanish
+%earlier than others.  After body 17, the next 8 vanished bodies with
+%respect to time are body 19 (as t=0.0312),  body 7 (as t=0.0325), body
+%20 (as t=0.0329), body 8 (as t=0.0349), body 10 (as t=0.0353), body 3
+%(as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  All of
+%these eight bodies were around this channel before they are gone.
+%
+%For the flat faces at the sites of near contact, since we put the body
+%be close to one another so we are able to see all the channels between
+%two close bodies have flat faces.  Besides the channels between bodies,
+%we also observe the flat faces on the bodies which are close to the
+%outer wall. For example, we see the flat faces on the top of bodies 1 \&
+%6 and the bottom of bodies 13 \& 15.  
+%
+%Since we use a Barycentric quadrature rule to approximate the velocity
+%of tracers and apply the fourth order Runge Kutta method to find the new
+%locations of tracers in each step, the tracers can be very close to but
+%not penetrate the bodies.  Those body-closed tracers are moving
+%perfectly so we are able to observe the details of the interaction of
+%bodies and fluid.  Although the direction of flow is from left to right,
+%the tracers will not only travel horizontally but also vertically.  In
+%the bottom middle frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
+%climb up from right to left around the body.  There is a zoom windows of
+%the climbing tracers trajectories in the bottom right frame of Fig.~\ref{fig:Eroding20tracer} and
+%they are taken from the bottom middle frame of
+%Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the bottom right frame of 
+%Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
+%from the channel below the body, climb up to the left, then go to the
+%right and join another tracers in the channel above the body. 
+%}
+%\begin{figure}[H]
+%\begin{center}
+%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
+%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
+%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
+%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
+%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
+%  tracers around the bodies. Since we use a Barycentric quadrature rule
+ % and the fourth order Runge Kutta method, the tracers can be very close
+ % to but not penetrate the bodies.}
+%\end{center}
+%\end{figure}
+%{\color{red}
+%In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
+%from the starting cross section x = -1 to 
+%the end cross section x = 1 and 
+%use the local tortuosity to analysis the effect
+%of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
+%In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
+%x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
+%\times 10^{-3}$ at equal spreading tracers on the starting cross section.
+%The velocity is continuous along the starting cross section and
+%acting as several Poiseuille flows. This velocity graph is different
+%from the one in~\cite{matyka2008tortuosity} since we choose our cross
+%section to be the beginning of the flow before the fluid touches any
+%body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
+%$\tau(y)=\lambda(y)/d$
+%of the tracers at $y$ on the starting cross section x = -1 
+%where $d = 2$.
+%This graph is not continuous 
+%and the jumps in $\tau$ mean that the initial neighboring tracers have been
+%seperated by the bodies. 
+%The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
+%}
+%{\color{red}
+%In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
+%$\tau$ at two neighboring tracers 
+%and draw the trajectories of neighboring tracers
+%if the difference of $\tau$ at the neighboring tracers is large. 
+%From Fig.~\ref{fig:Eroding20tort}(c), we collect the 10 largest difference of $\tau$ 
+%at the neighboring tracers and 
+%draw the pair of trajectories in the same color and 
+%are able to tell the neighboring trajectories will be very 
+%different if they are separated by bodies.
+%For each pair of trajectories, 
+%they are splitted by the body at the left side of the body, then
+%one of them goes up and the other one goes down along the body 
+%until they rejoin with each other at the right side of body.  
+%Furthermore, the pair trajectories could be splitted by more than one body, 
+%for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
+%are splitted by two close bodies.
+%}
 

### 2019-08-02 docs/transport/erosion_transport.tex
add new figs in transport paper

@@
 
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian}
+\caption{\label{fig:Eroding20tort_all} The Eulerian and Lagrangian approach of tortuosity. 
+The blue dots are Eulerian approach of tortuosity and the red stars and 
+square are Lagrangian approach of tortuosity.}
+\end{figure}
 %\begin{figure}[H]
@@
 \caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
- 20 nearly touching bodies with respect to six porosities. }
+ 20 nearly touching bodies with respect to six porosities.}
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
+\end{figure}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
+\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
+The blue dots are Eulerian approach of tortuosity and the red stars and 
+square are Lagrangian approach of tortuosity.}
 \end{figure}

### 2019-08-02 julia_code/basic.jl

@@ -80,11 +80,11 @@ function compute_density!(thlenden::ThLenDenType, params::ParamType; rotation::B
 		println("Computing the density function.")
 		npts,nbods,xv,yv = getnxy(thlenden)
 		thlenden.density = compute_density(xv,yv,npts,nbods,params.nouter,params.ifmm,params.ibary,params.maxl)
-	elseif (rotation == true && length(thlenden.denrot) == 0)
-		println("Computing the rotated density function.")
-		npts,nbods,xv,yv = getnxy(thlenden)
-		xrot,yrot = xyrot(xv,yv)
-		thlenden.denrot = compute_density(xrot,yrot,npts,nbods,params.nouter,params.ifmm,params.ibary,params.maxl)
+#	elseif (rotation == true && length(thlenden.denrot) == 0)
+#		println("Computing the rotated density function.")
+#		npts,nbods,xv,yv = getnxy(thlenden)
+#		xrot,yrot = xyrot(xv,yv)
+#		thlenden.denrot = compute_density(xrot,yrot,npts,nbods,params.nouter,params.ifmm,params.ibary,params.maxl)
 	end
 	return
 end

### 2019-08-05 docs/transport/erosion_transport.tex
add new figs in transport paper

@@
 \center
-\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
+\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
+\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment}
 \caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
- 20 nearly touching bodies with respect to six porosities.}
+ 20 nearly touching bodies with respect to six porosities and the reference line of 100\% porosity.}
 \end{figure}

### 2019-08-05 docs/transport/erosion_transport.tex
editing the caption of fig.8 in transport paper

@@
 \caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
- 20 nearly touching bodies with respect to six porosities and the reference line of 100\% porosity.}
+ 20 nearly touching bodies with respect to six porosities and the reference line of 100\% porosity.
+The first moment (left) is the mean length of streamlines and the second moment (right) is the }
 \end{figure}

### 2019-08-05 docs/transport/erosion_transport.tex
add new figs in transport paper
small changes to paper

--- 2019-08-02 docs/transport/erosion_transport.tex
@@
 \begin{align}
-  \lambda_j(t) = \int_{0}^t \|\ss_j(\tau)\|\, d\tau, 
+  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
     \quad j=1,\ldots,N_p.
@@
 would indicate a larger anomalous diffusion rate.
+
+Towards the end of the erosion simulation, the porosity is low, and we
+expect that the ensemble moments behave similarly to transport in a
+pipe.  In a grainless geometry, the trajectory originating at
+$(x_0,y_0)$ is
+\begin{align}
+  s_1(t) &= (1-y_0^2)t + x_0, \\
+  s_2(t) &= y_0.
+\end{align}
+Averaging over $y_0 \in [-1,1]$, the first and second ensemble moments
+are
+\begin{align}
+  \langle \lambda \rangle (t) = \frac{2}{3}t, \quad 
+    \sigma_\lambda^2(t) = \frac{4}{45}t^2.
+\end{align}
 
@@
 
+In Figure~\ref{fig:Eroding20tort_all}, we plot the tortuosity as a
+function of the porosity from the initial porosity of $0.38$ until all
+the bodies have eroded.  The tortuosity is computed with both the
+length of the Lagrangian trackers~\eqref{eqn:tortuosity1} and using the
+spatial average of the velocity on an Eulerian
+grid~\eqref{eqn:tortuosity2}.  The red square mark corresponds to the
+porosity in Figure~\ref{fig:Eroding20tort}(c).  The two methods of
+calculating the tortuosity give similar results with any discrepancy
+being accounted for by slow regions of recirculation.  Computing the
+velocity on an Eulerian grid is computationally easier than simulating
+many trajectories, so we use the Eulerian approach for all future
+examples.  As the bodies erode, this creates wide channels where
+trajectories undergo only minor vertical deflections, and this explains
+why the tortuosity eventually decreases with porosity.  However, at the
+early stages of the erosion, the tortuosity increases with porosity,
+which can be explain as follows.   In the absence of erosion
+(left plot in Figure~\ref{fig:Eroding20vort}), many of the trajectories,
+such as those initialized between bodies 15 \& 18, only perform minor
+deflections to pass through the narrow regions, albeit, very slowly.
+However, as erosion starts to open the channels, the trajectories
+deflect into the fast regions, and this increases the amount of vertical
+deflection, and therefore the tortuosity.
+\todo[inline]{BQ: Need to work on this paragraph}
+
 \begin{figure}[H]
@@
 \includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian}
-\caption{\label{fig:Eroding20tort_all} The Eulerian and Lagrangian approach of tortuosity. 
-The blue dots are Eulerian approach of tortuosity and the red stars and 
-square are Lagrangian approach of tortuosity.}
+\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
+eroding geometry initialized with 20 bodies.  The tortuosity is
+calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
+and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
+square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).}
 \end{figure}
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
-%\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
-%local tortuosity $\tau$ at two neighboring tracers in
-% 20 nearly touching bodies eroding when the porosity is 62.9 \% 
-%and the tortuosity is 1.0979. The same color of a pair of trajectories 
-%means they are from two neighboring tracers.}
-%\end{figure}
 
@@
 \includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
-\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
- 20 nearly touching bodies with respect to six porosities.}
+%\caption{\label{fig:Eroding20anomalous} The
+%mean squared displacement of the tracer trajectories  at several
+%different stages of the erosion process.  As the porosity increases, the
+%mean squared displacement tends towards $\sigma^2_\lambda(t) \sim t^$
+%}
 \end{figure}

### 2019-08-05 docs/transport/erosion_transport.tex

@@
 %}
+\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
+\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment}
+\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
+ 20 nearly touching bodies with respect to six porosities and the reference line of 100\% porosity.
+The first moment (left) is the mean length of streamlines and the second moment (right) is the }
 \end{figure}
@@
 square are Lagrangian approach of tortuosity.}
+\end{figure}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
+\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
+\caption{\label{fig:Eroding100anomalous} The analysis of anomalous diffusion in
+ 100 bodies with respect to six porosities and the reference line of 100\% porosity.
+The first moment (left) is the mean length of streamlines and the second moment (right) is the }
 \end{figure}

### 2019-08-05 docs/transport/erosion_transport.tex
editing the tex of fig.8 in transport paper
small change of caption of fig. 13 in transport paper

@@
 \begin{figure}[H]
-\center
-\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
 %\caption{\label{fig:Eroding20anomalous} The
@@
 \caption{\label{fig:Eroding100anomalous} The analysis of anomalous diffusion in
- 100 bodies with respect to six porosities and the reference line of 100\% porosity.
+ 100 bodies with respect to five porosities and the reference line of 100\% porosity.
 The first moment (left) is the mean length of streamlines and the second moment (right) is the }

### 2019-08-05 docs/transport/erosion_transport.tex
added some references

@@
 The dynamics of fluid in porous media is often characterized in terms of
-anomalous diffusion~\cite{} \todo[inline]{need references}, and the
+anomalous diffusion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}, and the
 anomalous diffusion rate depends on the properties of the geometry.  The
-anomalous diffusion depends on the porosity~\cite{}, but the
-distribution of the bodies also affects the anomalous diffusion rates.
-Since erosion causes certain structure in porous media, calculating the
-anomalous diffusion rates in these geometries is important.
+anomalous diffusion depends on the porosity and
+permeability~\cite{koc-bra1988}, but the distribution of the bodies also
+affects the anomalous diffusion rates.  Since erosion causes certain
+structure in porous media, calculating the anomalous diffusion rates in
+these geometries is important.
 

### 2019-08-05 docs/transport/erosion_transport.tex
modify figures of transport paper

@@
 \end{subfigure}
-\begin{subfigure}[b]{0.51\textwidth}
+\begin{subfigure}[b]{0.5\textwidth}
 \includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
@@
 \begin{subfigure}[b]{\textwidth}
-\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
+\includegraphics*[width =0.97\linewidth]{./figs/tort_local20_268}
 \todo[inline]{S-H: Can cut the ylimit at 1.3}
@@
 The blue dots are Eulerian approach of tortuosity and the red stars and 
-square are Lagrangian approach of tortuosity.}
+square are Lagrangian approach of tortuosity. 
+The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
+the the sum $S$ of squared residuals is 0.0075.}
 \end{figure}

### 2019-08-05 docs/transport/erosion_transport.tex
modify figures caption of transport paper
small changes

--- 2019-08-05 docs/transport/erosion_transport.tex
@@
 pipe.  In a grainless geometry, the trajectory originating at
-$(x_0,y_0)$ is
-\begin{align}
-  s_1(t) &= (1-y_0^2)t + x_0, \\
-  s_2(t) &= y_0.
-\end{align}
-Averaging over $y_0 \in [-1,1]$, the first and second ensemble moments
-are
+$(s_1(0),s_2(0))$ is
+\begin{align}
+  s_1(t) &= (1-s_2(0)^2)t + s_1(0), \\
+  s_2(t) &= s_2(0).
+\end{align}
+Averaging over $s_2(0) \in [-1,1]$, the first and second ensemble
+moments are
 \begin{align}
@@
 where $S$ is an cross-section perpendicular to the $x$ axis with length
-$d$, $\lambda(y)$ is the length of the streamline that is initialized
-at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
-the velocity at the $y$-coordinate along $S$.
-Following~\cite{dud-koz-mat2011}, the trajectories are formed until they
-cross a second cross-section that is parallel to the initial
-cross-section.  In our work, we always initialize the trajectories at
-$x=-1$ and stop them when they reach $x=1$.
+$d$, $\lambda(y)$ is the length of the streamline that is initialized at
+the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of the
+velocity at the $y$-coordinate along $S$.  Since the flow is laminar in
+the absence of grains, the tortuosity of a straight channel is $T=1$.
+Following~\cite{dud-koz-mat2011}, two parallel cross-sections are
+chosen, and the trajectories that pass between them are formed.  In our
+work, we initialize the trajectories at $x=-1$ and terminate them at
+$x=1$.
 
 Under the assumptions that the flow is incompressible and not reentrant,
-the tortuosity can be equivalently measured as~\cite{dud-koz-mat2011}
+meaning that all streamlines connect the two cross-sections, the
+tortuosity can be equivalently measured as~\cite{dud-koz-mat2011}
 \begin{align}
@@
 \end{align}
-The flow is reentrant if all streamlines connect the inlet to the
-outlet.  Recirculation zones are possible in viscous fluids, but they
-only constitute a small fraction of the total porous media and tend to
-have very small velocities.  Therefore, the tortuosity defined in
-equation~\eqref{eqn:tortuosity2} is an upper bound for the definition in
-equation~\eqref{eqn:tortuosity1}, but for the geometries we consider, we
-will show that their difference is negligible.  Since
+Recirculation zones are possible in viscous fluids, but they only
+constitute a small fraction of the total porous media, and in our
+examples, their velocities are very small.  Therefore, the tortuosity
+defined in equation~\eqref{eqn:tortuosity2} is an upper bound for the
+definition in equation~\eqref{eqn:tortuosity1}, but for the geometries
+we consider, we will show that their difference is negligible (see
+Figure~\ref{fig:Eroding20tort_all}).  Since
 equation~\eqref{eqn:tortuosity2} does not require the additional work of
 computing particle trajectories, we use this definition for the
-tortuosity.
-
-The first method to compute numerically compute the tortuosity uses
-$N_p$ trajectories that are initially at $(1,y_i)$, $i=1,\ldots,N_p$,
-and stopped when their $x$ coordinate is 1.  We choose $y_i$ so that the
+majority of the tortuosity calculations.
+
+The first method to numerically compute the tortuosity uses $N_p$
+trajectories that are initially at $(-1,y_i)$, $i=1,\ldots,N_p$, and
+stopped when their $x$ coordinate is 1.  We choose $y_i$ so that the
 trajectories are initially uniformly spaced in $(-1,1)$.  Having
@@
   T = \frac{\sum\limits_{i,j=1}^N \|\uu(x_i,y_j)\|\Delta x \Delta y}
-      {\sum\limits_{i,j=1}^N u(x_i,y_j) \Delta x \Delta y},
-\end{align}
-where $\uu = (u,v)$.
+      {\sum\limits_{i,j=1}^N u_x(x_i,y_j) \Delta x \Delta y}.
+\end{align}
 
@@
 \todo[inline]{Need to flesh this out more}
+\todo[inline]{Talk about the different relationships between tortuosity
+and porosity from the literature}
 

### 2019-08-05 docs/transport/erosion_transport.tex

@@
 The blue dots are Eulerian approach of tortuosity and the red stars and 
-square are Lagrangian approach of tortuosity.}
+square are Lagrangian approach of tortuosity. 
+The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
+the sum $S$ of squared residuals is 0.0075.}
 \end{figure}

### 2019-08-05 docs/transport/erosion_transport.tex
modify figure of transport paper

--- 2019-08-05 docs/transport/erosion_transport.tex
@@
 and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
-square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).}
+square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
+The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2228$ and 
+the sum $S$ of squared residuals is 0.0166.}
 \end{figure}
@@
 The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
-the the sum $S$ of squared residuals is 0.0075.}
+the sum $S$ of squared residuals is 0.0075.}
 \end{figure}

### 2019-08-05 docs/transport/erosion_transport.tex
worked on tortuosity and anomalous diffusion sections

--- 2019-08-05 docs/transport/erosion_transport.tex
@@
 The dynamics of fluid in porous media is often characterized in terms of
-anomalous diffusion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}, and the
-anomalous diffusion rate depends on the properties of the geometry.  The
+anomalous diffusion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.  The
 anomalous diffusion depends on the porosity and
@@
 
-One way to define the anomalous diffusion rate is by using tracer
-trajectories that are governed by equation~\eqref{eqn:trajectories}.
-Given a set of trajectories, we define $\lambda_j(t)$ to be the distance
-travelled by the particle
+We calculate the anomalous diffusion rates by analyzing the tracer
+trajectories governed by equation~\eqref{eqn:trajectories} for
+geometries that are formed by erosion.  Given a set of trajectories, we
+define $\lambda_j(t)$ to be the arclength of the trajectory
 \begin{align}
@@
 \end{align}
-Having formed $N_p$ trajectories, the first and second ensemble moments
-are
+Then, the first and second ensemble moments are
 \begin{align}
@@
 \end{align}
+Then, particle dispersion is characterized as $\sqrt{\sigma_\lambda^2}$.
 At early times, the particles have not explored much of the geometry,
@@
 as the particles pass the grains, their trajectories are altered, and we
-expect that $\sigma_\lambda^2 \sim t^\alpha$, with $\alpha < 1$, which
-would indicate that the flow is sub-diffusive.  With respect to erosion,
-as the bodies erode, we expect that the channelization of the geometry
+expect that $\sigma_\lambda^2 \sim t^\alpha$, with $\alpha < 1$,
+indicating that the flow is sub-diffusive.  With respect to erosion, as
+the bodies erode, we expect that the channelization of the geometry
 results in more trajectories undergoing a ballistic motion, and this
-would indicate a larger anomalous diffusion rate.
-
-Towards the end of the erosion simulation, the porosity is low, and we
-expect that the ensemble moments behave similarly to transport in a
-pipe.  In a grainless geometry, the trajectory originating at
+would indicate decrease particle dispersion, meaning a larger anomalous
+diffusion rate.
+
+At early times, the geometry has not been altered by erosion, and we
+expect large amounts of dispersion.  However, as the bodies erode, the
+porosity increases and the trajectories behave more closely to laminar
+trajectories in an open channel.  To be able to compare the dispersion
+of an eroded geometry with that of an open channel, we consider
+trajectories in an open channel.  The trajectory originating at
 $(s_1(0),s_2(0))$ is
@@
 \end{align}
+In Section~\ref{sec:results}, we compare these moments in an open
+channel with the trajectories in an eroding geometry.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The tortuosity of a geometry quantifies the average amount of turning
-made by a streamline.  The choice of how to average is not universal,
-and Duda et al.~\cite{dud-koz-mat2011} summarize several options for
-averaging.  One particular choice, which we shall adopt, allows us to
-compute the tortuosity in terms of trajectories, or by using an area
-integral over the fluid geometry.  Another advantage of this choice is
-that it is not affected by regions of recirculation.  Mathematically,
-the definition of tortuosity that we use is
+The tortuosity of a geometry, denoted by $T \geq 1$, is a dimensionless
+number that quantifies the average amount of turning made by
+trajectories passing through the geometry.  The local tortuosity
+\begin{align}
+  \tau(y) = \frac{\lambda(y)}{d}.
+  \label{eqn:localTort}
+\end{align}
+considers the length of a single trajectory, $\lambda$ whose initial
+$y$-coordinate is a value $y$ on a cross-section of length $d$.  Taking
+the average over all points on the cross-section defines the hydraulic
+tortuosity
 \begin{align}
@@
 \end{align}
-where $S$ is an cross-section perpendicular to the $x$ axis with length
-$d$, $\lambda(y)$ is the length of the streamline that is initialized at
+where $S$ is a cross-section perpendicular to the $x$-axis with length
+$d$, $\lambda(y)$ is the length of the trajectory that is initialized at
 the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of the
@@
 the absence of grains, the tortuosity of a straight channel is $T=1$.
-Following~\cite{dud-koz-mat2011}, two parallel cross-sections are
-chosen, and the trajectories that pass between them are formed.  In our
-work, we initialize the trajectories at $x=-1$ and terminate them at
-$x=1$.
-
-Under the assumptions that the flow is incompressible and not reentrant,
-meaning that all streamlines connect the two cross-sections, the
-tortuosity can be equivalently measured as~\cite{dud-koz-mat2011}
+The choice for the trajectory with length $\lambda(y)$ is not universal,
+and Duda et al.~\cite{dud-koz-mat2011} summarize several options. One
+choice, which we adopt, considers trajectories that originate at $S$ and
+terminate at a parallel cross-section.  We use the cross-sections $x=-1$
+and $x=1$.  This choice of averaging allows us to also compute the
+tortuosity in terms of an area integral.  Under the assumptions that the
+flow is incompressible and not reentrant, meaning that all streamlines
+connect the two cross-sections, the tortuosity in
+equation~\eqref{eqn:tortuosity1} is equivalent to~\cite{dud-koz-mat2011}
 \begin{align}
   T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
-           {\displaystyle\int_\Omega u_x(\yy)\, d\yy}.
+           {\displaystyle\int_\Omega u_x(\yy)\, d\yy},
   \label{eqn:tortuosity2}
 \end{align}
-Recirculation zones are possible in viscous fluids, but they only
-constitute a small fraction of the total porous media, and in our
-examples, their velocities are very small.  Therefore, the tortuosity
-defined in equation~\eqref{eqn:tortuosity2} is an upper bound for the
-definition in equation~\eqref{eqn:tortuosity1}, but for the geometries
-we consider, we will show that their difference is negligible (see
+where $\Omega$ is the region between the inlet and outlet
+cross-sections.  Recirculation zones are possible in viscous
+fluids~\cite{hig1985}, but they only constitute a small fraction of the
+total porous media, and in our examples, their velocities are very
+small.  Therefore, the tortuosity defined in
+equation~\eqref{eqn:tortuosity2} is a tight upper bound for the
+definition in equation~\eqref{eqn:tortuosity1}.  For the geometries we
+consider, we will show that their difference is negligible (see
 Figure~\ref{fig:Eroding20tort_all}).  Since
 equation~\eqref{eqn:tortuosity2} does not require the additional work of
-computing particle trajectories, we use this definition for the
-majority of the tortuosity calculations.
+computing particle trajectories, we use this definition for the majority
+of the tortuosity calculations.
 
 The first method to numerically compute the tortuosity uses $N_p$
-trajectories that are initially at $(-1,y_i)$, $i=1,\ldots,N_p$, and
+trajectories that are initialized at $(-1,y_i)$, $i=1,\ldots,N_p$, and
 stopped when their $x$ coordinate is 1.  We choose $y_i$ so that the
@@
     u_x(y_i) \lambda(y_i) \Delta y}
-  {\displaystyle\sum_{i=1}^{N_p} u_x(y_i) \Delta y_i}, 
+  {\displaystyle\sum_{i=1}^{N_p} u_x(y_i) \Delta y}, 
 \end{align}
@@
 There have been efforts to relate the tortuosity to the
-porosity~\cite{matyka2008tortuosity}, but these results can not be
-universal since the porosity which depends on only a single number, the
-tortuosity is affected by the distribution of pores within the porous
-network.  In addition to the hydraulic tortuosity, a local tortuosity
-can be used to analyze the local behavior of a streamline near a
-body~\cite{matyka2008tortuosity}.  The local tortuosity of a streamline
-initialized at $y$ along $S$ is
-\begin{align}
-  \tau(y) = \frac{\lambda(y)}{d}.
-  \label{eqn:localTort}
-\end{align}
-\todo[inline]{Need to flesh this out more}
-\todo[inline]{Talk about the different relationships between tortuosity
-and porosity from the literature}
+porosity~\cite{matyka2008tortuosity}.  For example, Matyka et
+al.~\cite{matyka2008tortuosity} propose the models
+\begin{align}
+  T(\phi) &= \phi^{-p}, \\
+  T(\phi) &= 1-p \log \phi, \\
+  T(\phi) &= 1+p (1-\phi), \\
+  T(\phi) &= (1+p (1-\phi))^2, 
+\end{align}
+where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
+compare these four models with the tortuosity of eroding geometries.
 

### 2019-08-06 docs/transport/erosion_transport.tex
modify figure of transport paper

@@
 \begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
+\begin{subfigure}[b]{0.55\textwidth}
 \includegraphics*[width =\linewidth]{./figs/porosity20dense}
@@
 square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
-The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2228$ and 
-the sum $S$ of squared residuals is 0.0166.}
+The dash line is the fitting line $\hat{T}(\phi)=\phi^p$ as $p=-0.2064$ and 
+the root mean square deviation is $5.9 \times 10^{-3}$.}
 \end{figure}
@@
 The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
-the sum $S$ of squared residuals is 0.0075.}
+the root mean square deviation is $5.2 \times 10^{-3}$.}
 \end{figure}

### 2019-08-07 docs/transport/erosion_transport.tex
add new figs in transport paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{20 nearly touching bodies}
+\subsection{20 Bodies at a Medium Porosity}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The first moment (left) is the mean length of streamlines and the second moment (right) is the }
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{20 Bodies at a Low Porosity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\begin{center}
+  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort1}
+  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort150}
+  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort300}
+  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort450}
+\caption{\label{fig:ErodingLow20vort} Erosion of 20 nearly touching bodies
+with the fixed pressure drop condition. The color is the vorticity of
+the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
+256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
+and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. }
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian20b}
+\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
+eroding geometry initialized with 20 bodies.  The tortuosity is
+calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots).
+The dash line is the fitting line $\hat{T}(\phi)=\phi^p$ as $p=-0.1669$ and 
+the root mean square deviation is $1.13 \times 10^{-2}$.}
 \end{figure}

### 2019-08-08 docs/transport/erosion_transport.tex
small changes
small changes in results

@@
 al.~\cite{matyka2008tortuosity} propose the models
-\begin{align}
-  T(\phi) &= \phi^{-p}, \\
-  T(\phi) &= 1-p \log \phi, \\
-  T(\phi) &= 1+p (1-\phi), \\
-  T(\phi) &= (1+p (1-\phi))^2, 
-\end{align}
+\begin{subequations}
+  \label{eqn:tortuosityModels}
+  \begin{align}
+    \widehat{T}(\phi) &= \phi^{-p}, \\
+    \widehat{T}(\phi) &= 1-p \log \phi, \\
+    \widehat{T}(\phi) &= 1+p (1-\phi), \\
+    \widehat{T}(\phi) &= (1+p (1-\phi))^2, 
+  \end{align}
+\end{subequations}
 where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
@@
 \includegraphics*[width =0.97\linewidth]{./figs/tort_local20_268}
-\todo[inline]{S-H: Can cut the ylimit at 1.3}
 \caption{}
@@
 square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
-The dash line is the fitting line $\hat{T}(\phi)=\phi^p$ as $p=-0.2064$ and 
-the root mean square deviation is $5.9 \times 10^{-3}$.}
+The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ as
+$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$.}
 \end{figure}
@@
 \includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment}
-\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
- 20 nearly touching bodies with respect to six porosities and the reference line of 100\% porosity.
-The first moment (left) is the mean length of streamlines and the second moment (right) is the }
+\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
+diffusion in 20 nearly touching bodies with respect to six porosities
+and the reference line of 100\% porosity.  The first moment (left) is
+the mean length of streamlines and the second moment (right) is the }
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We consider a second example with 20 eroding bodies, but with a smaller
+initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
+eroding geometry and porosity at four evenly spaced instances in time.
+Again, the color is the vorticity in the bulk whose magnitude is
+equivalent to the erosion rate.  Each body is discretized with $N_\iin =
+256$, and the smallest distance between two bodies at the initial
+condition is ???\todo[inline]{SH: Fill in this number}.  At this
+resolution, this corresponds to a spacing of ???$h$ which is much
+too small for the trapezoid rule.  By applying the Barycentric
+quadrature rule, there is no issue simulating the erosion until all the
+bodies have eroded.
+
 \begin{figure}[H]
@@
   \includegraphics[height=0.225\textwidth]{./figs/20b2_vort450}
-\caption{\label{fig:ErodingLow20vort} Erosion of 20 nearly touching bodies
-with the fixed pressure drop condition. The color is the vorticity of
-the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
-256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
-and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. }
 \end{center}
+\caption{\label{fig:ErodingLow20vort} Erosion of 20 nearly touching
+bodies with the fixed pressure drop condition. The color is the
+vorticity of the fluid. The 4 snapshots are evenly spaced in time. We
+use $N_\iin = 256$ discretization points on the body, a time-step of
+$\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
+$\sigma=10/256 $. }
 \end{figure}
+
+We compute the tortuosity using the Eulerian
+method~\eqref{eqn:tortuosity2}. In Figure~\ref{fig:ErodingLow20tort}, we
+plot the tortuosity with respect to the porosity (blue) and a line of
+best fit (black) using the power law $\widehat{T}(\phi) =
+\phi^{-p}$~\cite{matyka2008tortuosity}.  This model outperformed the
+other three models described in equation~\eqref{eqn:tortuosityModels}.
+The root-mean-squared error of the power law is $1.13 \times 10^{-2}$.
+
+Unlike the previous 20 body simulation, the tortuosity decreases
+monotonically with the porosity. \todo[inline]{BQ: Why is this the case?
+What is special about the last example?}
 
@@
 eroding geometry initialized with 20 bodies.  The tortuosity is
-calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots).
-The dash line is the fitting line $\hat{T}(\phi)=\phi^p$ as $p=-0.1669$ and 
-the root mean square deviation is $1.13 \times 10^{-2}$.}
+calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
+dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
+as $p=0.1669$ and the root mean square deviation is $1.13 \times
+10^{-2}$.}
 \end{figure}
@@
 \includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
-\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
-The blue dots are Eulerian approach of tortuosity and the red stars and 
-square are Lagrangian approach of tortuosity. 
-The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
-the root mean square deviation is $5.2 \times 10^{-3}$.}
+\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
+approach of tortuosity.  The blue dots are Eulerian approach of
+tortuosity and the red stars and square are Lagrangian approach of
+tortuosity.  The dash line is the fitting line
+$\widehat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and the root mean square
+deviation is $5.2 \times 10^{-3}$.}
 \end{figure}

### 2019-08-08 docs/transport/erosion_transport.tex
small changes

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{50 nearly touching bodies}
+\subsection{50 eroding bodies}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{100 bodies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{100 eroding bodies}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+As a final example, we consider 100 eroding bodies with an initial
+porosity near 55\%.  Snapshots of the configurations and vorticity are
+in Figure~\ref{fig:Eroding100vort}.
+
 \begin{figure}[H]
@@
   $\sigma=10/256$.}
+\end{figure}
+
+To quantify the tortuosity, we compute the relative velocity
+(Figure~\ref{fig:Eroding100tort}(a)) and the local tortuosity
+(Figure~\ref{fig:Eroding100tort}(b)) of 1000 tracers placed immediately
+to the left of the porous region at $x=-1$.  The porosity at this
+instance in time is $62.98\%$ and the maximum velocity at $x=-1$ is
+$3.90 \times 10^{-4}$. The initial velocity of the tracers is
+qualitatively similar to the 20 body example
+(Figure~\ref{fig:Eroding20tort}(a)), except with additional maximum and
+minimums because of the additional bodies.  Compared to
+Figure~\ref{fig:Eroding20tort}(b), the local tortuosity is much more
+discontinuous.  These discontinuities can be explained by examining the
+trajectories of tracers in Figure~\ref{fig:Eroding100tort}(c).  Here,
+there are many instances of neighboring trajectories that are deflected
+apart from one another as they tend to a stagnation point in the flow,
+and this results in trajectories with significantly different lengths.
+At this instance in time one the tracers travels 25.5\% farther than it
+would have if the bodies had been absent, and the average tracer
+travelled ???\% farther than it would have if the bodies were absent.
+Therefore, at this instance in time, the tortuosity is $1.???$
+\todo[inline]{S-H: Fill in the numbers in this paragraph}
+
+\begin{figure}[H]
+\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{\textwidth}
+\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
+\includegraphics*[width =\linewidth]{./figs/tort_local100}
+\caption{}
+\end{subfigure}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid
+with 100 bodies when the porosity is 62.98\%.  (a) The x-component
+velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.9021
+\times 10^{-4}$ at equal spreading tracers on the cross section x = -1.
+(b) The local tortuosity $\tau(y)$ on the cross section x = -1. (c) The
+trajectories of 200 tracers released at $x = -1$ in the fluid with
+multiple bodies.}
 \end{figure}
@@
 
-To measure the local behavior of fluid quantitatively, 
-we use the velocities and local tortuosities at the starting cross section 
-to analysis the interaction of fluid and bodies until the end cross section 
-in Fig.~\ref{fig:Eroding100tort}(b) and (c).
-In Fig.~\ref{fig:Eroding100tort}(b) the graph represents the ratio of the
-x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
-\times 10^{-4}$ at equal spreading tracers on the strating cross section.
-As in the case of 20 nearly touching bodies, the velocity is continuous along
-the starting cross section and acting as a Poiseuille flow in the channel between
-bodies. When the fluid is close to bodies
-the speed of fluid will be slow down because of the no-slip condition on the bodies
-and this causes the separated branches of the inlet flow.
-The maximum velocity of the fluid with 100 bodies on the starting cross 
-section is slower than the maximum velocity of the fluid with 20 bodies
-but the velocity in the case of 100 bodies 
-changes more rapidly than the velocity of the fluid with 20 bodies.
-The reason of the rapid change on the starting cross section of 
-100-body case is because there are 
-more bodies near the starting cross section in
-100-body case than in the 20-body case. 
-so the inlet flow in 100-body case
-will be separated into more branches than the flow in 20-body case.
-
-In Fig.~\ref{fig:Eroding100tort}(c) we record the 
-local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
-It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies
-is 1.2547 and the minimum is 1.0003. This function $\tau$
-has more jumps than the one in the case of 20 bodies but its maximum 
-is smaller than the maximum in the case of 20 bodies. 
-The jump in this graph means the neighboring trajectories are splitted by bodies
-so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
-since there are more bodies in the former case.
-
 %To understand the meaning of jump 
@@
 \begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.45\textwidth}
-\begin{subfigure}[b]{\textwidth}
-\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-\includegraphics*[width =\linewidth]{./figs/tort_local100}
-\caption{}
-\end{subfigure}
-\end{subfigure}
-
-\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid with 100 bodies 
-when the porosity is 62.98 \%.
-(a) The historical trajectories of 
-200 tracers released at x = -1 in the fluid with multiple bodies.
-(b) The 
-x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.9021
-\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
-(c) The local tortuosity $\tau(y)$ on the cross section x = -1. 
-}
-%(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
-%(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
-\end{figure}
-
-\begin{figure}[H]
 \center
@@
 \includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
-\caption{\label{fig:Eroding100anomalous} The analysis of anomalous diffusion in
- 100 bodies with respect to five porosities and the reference line of 100\% porosity.
-The first moment (left) is the mean length of streamlines and the second moment (right) is the }
+\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
+diffusion in 100 bodies with respect to five porosities and the
+reference line of 100\% porosity.  The first moment (left) is the mean
+length of streamlines and the second moment (right) is the 
+\todo[inline]{Slope of the top black line is 0.8715}
+}
 \end{figure}
@@
 
+%To measure the local behavior of fluid quantitatively, 
+%we use the velocities and local tortuosities at the starting cross section 
+%to analysis the interaction of fluid and bodies until the end cross section 
+%in Fig.~\ref{fig:Eroding100tort}(b) and (c).
+%In Fig.~\ref{fig:Eroding100tort}(b) the graph represents the ratio of the
+%x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
+%\times 10^{-4}$ at equal spreading tracers on the strating cross section.
+%As in the case of 20 nearly touching bodies, the velocity is continuous along
+%the starting cross section and acting as a Poiseuille flow in the channel between
+%bodies. When the fluid is close to bodies
+%the speed of fluid will be slow down because of the no-slip condition on the bodies
+%and this causes the separated branches of the inlet flow.
+%The maximum velocity of the fluid with 100 bodies on the starting cross 
+%section is slower than the maximum velocity of the fluid with 20 bodies
+%but the velocity in the case of 100 bodies 
+%changes more rapidly than the velocity of the fluid with 20 bodies.
+%The reason of the rapid change on the starting cross section of 
+%100-body case is because there are 
+%more bodies near the starting cross section in
+%100-body case than in the 20-body case. 
+%so the inlet flow in 100-body case
+%will be separated into more branches than the flow in 20-body case. 
+%
+%In Fig.~\ref{fig:Eroding100tort}(c) we record the 
+%local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
+%It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies
+%is 1.2547 and the minimum is 1.0003. This function $\tau$
+%has more jumps than the one in the case of 20 bodies but its maximum 
+%is smaller than the maximum in the case of 20 bodies. 
+%The jump in this graph means the neighboring trajectories are splitted by bodies
+%so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
+%since there are more bodies in the former case.
+
 \end{document}

### 2019-08-08 docs/transport/erosion_transport.tex
worked on results section for 100 bodies

@@
 as the particles pass the grains, their trajectories are altered, and we
-expect that $\sigma_\lambda^2 \sim t^\alpha$, with $\alpha < 1$,
+expect that $\sigma_\lambda \sim t^\alpha$, with $\alpha < 1$,
 indicating that the flow is sub-diffusive.  With respect to erosion, as
@@
 travelled ???\% farther than it would have if the bodies were absent.
-Therefore, at this instance in time, the tortuosity is $1.???$
+Therefore, at this instance in time, the tortuosity is $1.???$.
 \todo[inline]{S-H: Fill in the numbers in this paragraph}
@@
 
-{\color{red}
-This case is 100 bodies in a Hagen-Poiseuille flow. The background
-flow is 
-\begin{align}
-  \UU(\xx)=U \left[
-  \begin{array}{c}
-    1-y^2 \\ 0
-  \end{array}
-  \right]
-\end{align}
-with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
-We record the vorticity of 
-fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
-measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
-Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
-the magnitude of the vorticity is larger 
-so the erosion is getting faster and faster 
-from the first snapshot to the forth one in Fig.~\ref{fig:Eroding100vort}.
-At t = 0.005 the porosity is 55.54\% and the most gap sizes between bodies are less than 0.015 in 
-Fig.~\ref{fig:Eroding100gap}(a). Since some of the bodies are vanished in the fluid, the numner of gaps 
-decreases and the gap sizes get larger and larger between the remaining bodies. 
-In Fig.~\ref{fig:Eroding100gap}(b) and (c) we still can see small gap sizes are in the majority but 
-it is not as concentrated as the one we see in Fig.~\ref{fig:Eroding100gap}(a). 
-In Fig.~\ref{fig:Eroding100gap}(d) there are only 254 gaps between 82 bodies and 
-the distribution of gap sizes spreads over without any major pack.  
+The tortuosity at all porosities from the initial condition until all
+the bodies have eroded is in Figure~\ref{fig:Eroding100tort_all}.  The
+initial tortuosity is around $T=1.2$ and decays towards $T=1$.  The
+tortuosities indicated by the blue dots are calculated using the
+Eulerian approach~\eqref{eqn:tortuosity2}, while the red marks use the
+Lagrangian approach~\eqref{eqn:tortuosity1}.  Again, the two methods
+give comparable results indicating that any recirculation is small and
+negligible.  As in the previous examples, the tortuosity depends on the
+porosity through a power law model with a small root-mean-squared error
+of $5.2 \times 10^{-3}$.  For this example, the logarithm tortuosity
+model $\hat{T}(\phi) = 1 - p \ln(\phi)$ achieves a similar
+root-mean-squared error.  The tortuosity has one interesting feature
+near the end of the simulation where it suddenly increases.  This
+behavior can be explained by ... \todo[inline]{S-H: Show me what is
+going on here as we discussed.}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
+\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
+approach of tortuosity.  The blue dots are Eulerian approach of
+tortuosity and the red stars and square are Lagrangian approach of
+tortuosity.  The dash line is the fitting line
+$\widehat{T}(\phi)=\phi^{-p}$ as $p=0.2459$ and the root-mean-square
+error is $5.5 \times 10^{-3}$.  We note that the model
+$\widehat{T}(\phi) = 1-p\ln(\phi)$, with $p=0.2631$ has a comparable
+root-mean-square error of $5.2 \times 10^{-3}$.}
+\end{figure}
+
+Next, we use the 1000 tracer trajectories to compute the first
+(Figure~\ref{fig:Eroding100anomalous}(a)) and second
+(Figure~\ref{fig:Eroding100anomalous}(b)) moments of the streamlines at
+various porosities.  At high porosities, the first moment is similar to
+the first-moment of trajectories in a empty channel (black dashed line).
+At smaller porosities, the first moment is always linear, but larger
+slopes indicate that the length of the trajectories are longer at lower
+porosities \todo[inline]{Don't understand how this is the case}.  The
+onset of anomalous diffusion is observed in
+Figure~\ref{fig:Eroding100anomalous}(b). At early times, the particle
+spreading is comparable to that of an open channel (dashed curve)
+corresponding to the ballistic regime.  However, as the trajectories
+traverse the geometry, a transition to a sub-diffusion case, especially
+at low porosities, is evident.  The dashed-dotted line corresponds has a
+slope less than 1 indicating the long time behavior of the trajectories
+\begin{align*}
+  \sigma_\lambda \sim t^{0.8715}.
+\end{align*}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
+\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
+\caption{\label{fig:Eroding100anomalous} The first and second moments of
+trajectories passing through an eroding geometry at several porosities.
+The dashed black line corresponds to a porosity of 100\%, and the
+dashed-dotted line is a line of best fit with slope 0.8715.}
+\end{figure}
+
+Finally, using network models for flow in porous media~\cite{}, the
+anomalous diffusion rate can be linked to channel widths between solid
+bodies.  We construct a Delaunay triangulation with the centers of the
+eroding bodies corresponding to the vertices of the triangles.  Then, if
+the side of a triangle connects two vertices, we call the bodies
+neighbors.  Then, for each pair of neighbors, we measure the distance
+between the bodies.  Once a Delaunay triangulation is formed, it is used
+for all subsequent time steps until a body completely disappears.  At
+this point, a new Delaunay triangulation is formed.
+
+We plot the distribution of the gap sizes at four equally spaced points
+in time in Figure~\ref{fig:Eroding100gap}.  At the initial configuration, there
+are 100 bodies and 318 pairs of neighbors.  The mean distance between
+these neighbors is $???  \times 10^{-???}$ and the variance is $???
+\times 10^{???}$.  As the bodies erode, the mean and variance of the
+distance between the bodies increases.  Finally, at the final time step,
+there are only 82 bodies and 254 pairs of neighbors.
 \begin{figure}[H]
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap} The histograms of gaps in the case of erosion of 100 bodies at four time steps.}
+\caption{\label{fig:Eroding100gap} The distribution of the gaps in the
+case of erosion of 100 bodies at four time steps.}
 \end{figure}
-
-To study the behavior of fluid in the porous media with multiple bodies, 
-we release 1000 tracers equispaced in $y$ from the 
-cross section x = -1 and record their trajectories and velocities
-until they arrive the end cross section x = 1 
-and the porosity of this geometric structure is 62.98 \%. 
-To understand the global action of fluid qualitatively, 
-we only draw 200 historical trajectories from x = -1 to x = 1 
-in Fig.~\ref{fig:Eroding100tort}(a). 
-When equispaced tracers are released in a 2D tube without any grains, 
-the streamlines are straight 
-and the intersection points of streamlines and any cross section are equispaced. 
-But it is not the same when there are bodies in the fluid. 
-In Fig.~\ref{fig:Eroding100tort}(a)
-even the tracers are equispaced in $y$ on the cross section $S$, 
-the streamlines have been push up and down by the bodies and
-some of them are close together.
-
-%To understand the meaning of jump 
-%of $\tau$, we use the data we got from local tortuosity $\tau(y)$
-%to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
-%and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
-%in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
-%then rejoin with each other and the splitting-rejoining behavior causes the difference of $\tau$ with respect to the neighboring trajectories.   
-%We also can get the idea why the maximum value of $\tau$ is smaller 
-%than the one in the case of 20 bodies . 
-%The most of the bodies in this case are smaller than those in the case of 20 bodies.
-%So when two neighboring trajectories are splitted on the left side by a smaller body they do not
-%travel as far as the two splitted by a bigger body do after they rejoin on the right side. 
-}
 
@@
 %\end{figure}
-
-\begin{figure}[H]
-\center
-\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
-\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
-approach of tortuosity.  The blue dots are Eulerian approach of
-tortuosity and the red stars and square are Lagrangian approach of
-tortuosity.  The dash line is the fitting line
-$\widehat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and the root mean square
-deviation is $5.2 \times 10^{-3}$.}
-\end{figure}
-
-\begin{figure}[H]
-\center
-\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
-\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
-\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
-diffusion in 100 bodies with respect to five porosities and the
-reference line of 100\% porosity.  The first moment (left) is the mean
-length of streamlines and the second moment (right) is the 
-\todo[inline]{Slope of the top black line is 0.8715}
-}
-\end{figure}
 
@@
 
+%To study the behavior of fluid in the porous media with multiple bodies, 
+%we release 1000 tracers equispaced in $y$ from the 
+%cross section x = -1 and record their trajectories and velocities
+%until they arrive the end cross section x = 1 
+%and the porosity of this geometric structure is 62.98 \%. 
+%To understand the global action of fluid qualitatively, 
+%we only draw 200 historical trajectories from x = -1 to x = 1 
+%in Fig.~\ref{fig:Eroding100tort}(a). 
+%When equispaced tracers are released in a 2D tube without any grains, 
+%the streamlines are straight 
+%and the intersection points of streamlines and any cross section are equispaced. 
+%But it is not the same when there are bodies in the fluid. 
+%In Fig.~\ref{fig:Eroding100tort}(a)
+%even the tracers are equispaced in $y$ on the cross section $S$, 
+%the streamlines have been push up and down by the bodies and
+%some of them are close together. 
+%
+%
+%%To understand the meaning of jump 
+%%of $\tau$, we use the data we got from local tortuosity $\tau(y)$
+%%to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
+%%and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
+%%in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
+%%then rejoin with each other and the splitting-rejoining behavior causes the difference of $\tau$ with respect to the neighboring trajectories.   
+%%We also can get the idea why the maximum value of $\tau$ is smaller 
+%%than the one in the case of 20 bodies . 
+%%The most of the bodies in this case are smaller than those in the case of 20 bodies.
+%%So when two neighboring trajectories are splitted on the left side by a smaller body they do not
+%%travel as far as the two splitted by a bigger body do after they rejoin on the right side.
+
+%{\color{red}
+%This case is 100 bodies in a Hagen-Poiseuille flow. The background
+%flow is 
+%\begin{align}
+%  \UU(\xx)=U \left[
+%  \begin{array}{c}
+%    1-y^2 \\ 0
+%  \end{array}
+%  \right]
+%\end{align}
+%with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
+%We record the vorticity of 
+%fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
+%measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
+%Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
+%the magnitude of the vorticity is larger 
+%so the erosion is getting faster and faster 
+%from the first snapshot to the forth one in Fig.~\ref{fig:Eroding100vort}.
+%At t = 0.005 the porosity is 55.54\% and the most gap sizes between bodies are less than 0.015 in 
+%Fig.~\ref{fig:Eroding100gap}(a). Since some of the bodies are vanished in the fluid, the numner of gaps 
+%decreases and the gap sizes get larger and larger between the remaining bodies. 
+%In Fig.~\ref{fig:Eroding100gap}(b) and (c) we still can see small gap sizes are in the majority but 
+%it is not as concentrated as the one we see in Fig.~\ref{fig:Eroding100gap}(a). 
+%In Fig.~\ref{fig:Eroding100gap}(d) there are only 254 gaps between 82 bodies and 
+%the distribution of gap sizes spreads over without any major pack.  
+%}
+%
+
 \end{document}

### 2019-08-10 docs/transport/erosion_transport.tex
small changes throughout

@@
 with the fixed pressure drop condition. The color is the vorticity of
-the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
-256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
-and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the
+the fluid. The four snapshots are evenly spaced in time. We use $N_\iin
+= 256$ discretization points on the bodies and $\Dt=10^{-4}$.  In the
 forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
@@
 channels from the inlet to outlet where the velocity and vorticity, and
-therefore erosion rate, are much larger than the other regions.  These
+therefore erosion rate, are much larger than in other regions.  These
 channels can be further visualized by considering the streamlines.  In
 Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
-time step from Figure~\ref{fig:Eroding20vort}, and we simulate 200
-tracers.  The tracers are initially placed at $x=-1$ and are equispaced
-in $y$.  The trajectories are shown at 5 different times, and the final
-plot is a zoom in of the lower right quadrant of the fifth time step.
-There are three clear regions where the tracers pass through the
-geometry fastest.  Two of these regions are located between the bodies
-and the solid walls at $y=\pm 1$, and the third cuts through the porous
-region with the upper part of the channel formed by bodies 1, 4, 6, and
-8.  Since the flow is fastest in these regions, the shearing is largest,
-and this causes these openings to grow fastest which can be observed in
+time step from Figure~\ref{fig:Eroding20vort}, and we plot 200
+trajectories that are initialized at $x=-1$ and equispaced in $y$.  The
+trajectories are shown at 5 different times, and the final plot is a
+zoom in of the lower right quadrant of the fifth time step.  There are
+three clear regions where the tracers pass through the geometry fastest.
+Two of these regions are located between the bodies and the solid walls
+at $y=\pm 1$, and the third cuts through the porous region with the
+upper part of the channel formed by bodies 1, 4, 6, and 8.  Since the
+flow is fastest in these regions, the shearing is largest, and this
+causes these openings to grow fastest which can be observed in
 Figure~\ref{fig:Eroding20vort}.
@@
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
-\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
-the second geometry from Figure~\ref{fig:Eroding20vort}. The tracers are
-initialized at $x=-1$ and are evenly spaced in the $y$-direction. The
+\caption{\label{fig:Eroding20tracer}200 trajectories in the second
+geometry from Figure~\ref{fig:Eroding20vort}. The trajectories are
+initialized at $x=-1$ and are equally spaced in the $y$-direction. The
 first five snapshots are evenly spaced in time.  The bottom right frame
@@
 function of the porosity from the initial porosity of $0.38$ until all
-the bodies have eroded.  The tortuosity is computed with both the
-length of the Lagrangian trackers~\eqref{eqn:tortuosity1} and using the
+the bodies have eroded.  The tortuosity is computed with both the length
+of the trajectories~\eqref{eqn:tortuosity1} (red marks) and using the
 spatial average of the velocity on an Eulerian
-grid~\eqref{eqn:tortuosity2}.  The red square mark corresponds to the
-porosity in Figure~\ref{fig:Eroding20tort}(c).  The two methods of
-calculating the tortuosity give similar results with any discrepancy
-being accounted for by slow regions of recirculation.  Computing the
-velocity on an Eulerian grid is computationally easier than simulating
-many trajectories, so we use the Eulerian approach for all future
-examples.  As the bodies erode, this creates wide channels where
+grid~\eqref{eqn:tortuosity2}.  The red square corresponds to the
+porosity in Figure~\ref{fig:Eroding20tort}(c).  The methods give similar
+results with any discrepancy being accounted for by slow regions of
+recirculation.  As the bodies erode, this creates wide channels where
 trajectories undergo only minor vertical deflections, and this explains
-why the tortuosity eventually decreases with porosity.  However, at the
-early stages of the erosion, the tortuosity increases with porosity,
-which can be explain as follows.   In the absence of erosion
+why the tortuosity eventually decreases with porosity.  The increase in
+tortuosity for small porosities occurs because in the absence of erosion
 (left plot in Figure~\ref{fig:Eroding20vort}), many of the trajectories,
@@
 However, as erosion starts to open the channels, the trajectories
-deflect into the fast regions, and this increases the amount of vertical
-deflection, and therefore the tortuosity.
-\todo[inline]{BQ: Need to work on this paragraph}
+deflect into the fast regions, such as the region above body 11, and
+this increases the amount of vertical deflection, and therefore the
+tortuosity.
 

### 2019-08-11 docs/transport/erosion_transport.tex
put some papers in the bib file for the introduction

@@
 \begin{itemize}
+\item Porous aquifers are a good application of our work
+
 \item \cite{dar-mcc1998} show that if there is a region with high
@@
 
-\item Continuous Time Random Walks
+\item Continuous Time Random Walks~\cite{ber-cor-den-sch2006}
 
@@
 accurately describe anomalous diffusion and
-mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.
+mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
 

### 2019-08-14 docs/transport/erosion_transport.tex
started to rewrite the introduction

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Flow in many natural occurring geometries involves flows that vary over
+many orders of magnitude.  Porous media are one such geometry where the
+length scales in a single geometry can vary from $10^{-6}m$ to
+$10^{-1}m$~\cite{mil-chr-imh-mob-ped1998}.  Simulating such a wide range
+of length scales is impractical, and constitutive laws that link the
+microscopic scale to macroscopic scale must be
+developed~\cite{mil-chr-imh-mob-ped1998}.  However, to find closure
+formulas, accurate simulations at microscopic scales must be performed
+and analyzed.
+\todo[inline]{Talk about aquifers here}
+
+At microscopic scales, the Reynolds number is small, and the fluid is
+governed by the incompressible Stokes equations (for example, see
+~\cite{hym-den-hag-kan2019, den-ica-hid2018, bar-mar-vee-zha2018})
+\begin{align}
+  \mu \Delta \uu = \nabla p, \quad \nabla \cdot \uu = 0,
+\end{align}
+where $\uu$ is the velocity, $p$ is the pressure, and $\mu$ is the fluid
+viscosity.  Even though the pore-scale geometry can be complex, the
+Stokes equations can be accurately solved in these complex geometries by
+using an integral equation method.  In addition to being accurate and
+able to resolve complex geometries, integral equation methods
+automatically satisfy mass conservation, result in a dimension
+reduction, and can be solved in optimal time by using a fast summation
+method.
+
+Once the governing equations are solved, the flow can characterized
+statistically~\cite{}.  For example, dispersion is described by the
+second moment of particle trajectories.  Other measures of the flow
+involve computing distributions of the velocity on Eulerian
+grids~\cite{} and Lagrangian grids~\cite{}, calculating the
+distribution of the time required for a trajectory to pass from the
+inlet to the outlet of the geometry, and by computing the length of
+streamlines passing from the inlet to the outlet.
+
+A common necessity to describe the microscopic scale is describe
+transport through the complex geometry.  Depending on the application,
+the transport may be passive and be described by pure
+advection~\cite{}, it may describe a concentration field, such as a
+contaminant, and be governed by a finite Peclet number
+advection-diffusion equation, or they may stochastic and be described
+using a random walk~\cite{}.  In this work, we focus on pure
+advection so that we are interested in passive tracers whose
+trajectories, or equivalently, the streamlines, are governed by
+\begin{align}
+  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
+\end{align}
+
+In many applications, the fluid transport continuously changes the
+pore structure.  This is particularly common in geophysical flows where
+erosion alters the porous matrix.
+
 Flow-induced erosion deteriorates and reshapes solid material over a

### 2019-08-16 docs/TexNotes/Notes.tex
NM
Updating notes

@@
 \newcommand{\dt}{\Delta t}
+% New
+\newcommand{\pup}{p_{1}}
+\newcommand{\pdn}{p_{2}}
+\newcommand{\qavg}{q_{avg}}
 
@@
 
+\subsection{Permeability and resistivity}
 Darcy's law is
@@
 \begin{equation}
-q = \frac{1}{2w} \int_{-w}^{w} u(z) dz = - \frac{ p_x w^2}{3 \mu} 
+\qavg = \frac{1}{2w} \int_{-w}^{w} u(z) dz = - \frac{ p_x w^2}{3 \mu} 
 \end{equation}
@@
 
+If we define $u(z) = U(w^2 - z^2)$, then $U = -p_x / (2 \mu)$, so that we get
+\begin{align}
+\qavg = \frac{2}{3} U w^2
+\end{align}
+
 Next, consider the flow through a porous matrix (and set $\mu=1$ via nondimensionalization).
-Measure the pressure and velocity along two vertical lines, one at $x = x_0$ and another at $x = -x_0$, and average to get $p^+ = \left< p(x_0) \right>$, $p^- = \left<p(-x_0) \right>$ and the same for $q$.
+Measure the pressure and velocity along two vertical lines, one upstream at $x = -x_0$ and another at the symmetric downstream location $x = x_0$.
+Average to get $\pup = \left<p(-x_0) \right>$ and $\pdn = \left< p(x_0) \right>$, and the same for $q$.
 Then the {\em total} resistivity (that of the porous matrix and the channel walls together) is
 \begin{equation}
-r_{tot} = \frac{p^- - p^+}{2 x_0 q_{avg}}
+r_{tot} = \frac{\pup - \pdn}{2 x_0 \, \qavg}
 \end{equation}
-This total resistivity reflects the resistivity from the porous matrix as well as the channel walls.
+
+\subsection{Removing the contribution of channel walls}
+The above total resistivity reflects the resistivity from the porous matrix as well as the channel walls.
 There is a buffer region that lies outside the porous-matrix region ($x_0$ lies in the bugger region), and we would like to remove the contribution from this region.
@@
 
+\subsection{Relationship to total drag}
+
+Consider the stress tensor
+\begin{equation}
+\bvec{\sigma} = -p \bvec{I} + \mu \left( \grad \bu + \grad \bu^T \right)
+\end{equation}
+Below we will set $\mu=1$. The Stokes equation is
+\begin{equation}
+\grad \cdot \bvec{\sigma} = 0
+\end{equation}
+By the divergence theorem we have
+\begin{equation}
+0 = \int_{\Omega} \grad \cdot \bvec{\sigma} = \int_{\partial \Omega}
+\end{equation}
+
 \end{document}

### 2019-08-16 docs/TexNotes/Notes.tex
NM

@@
 \begin{equation}
-0 = \int_{\Omega} \grad \cdot \bvec{\sigma} = \int_{\partial \Omega}
+\label{divthm}
+0 = \int_{\Omega} \grad \cdot \bvec{\sigma} \, dV 
+= \int_{\partial \Omega} \bvec{\sigma} \cdot \nhat \, dS
 \end{equation}
+for any domain $\Omega$.
+Now consider $\Omega$ to be a section of the channel $-x_0 < x < x_0$ and spanning the entire width $-w < y < w$.
+Then the integral on the right-hand-side of \eqref{divthm} has two contributions: first, the total drag arising from all immersed bodies as well as from the top and bottom walls, and second, the difference between the upstream and downstream pressures (we have implicitly assumed that $x_0$ is sufficiently distant from the bodies so that $\grad \bvec{u}$ is nearly zero).
+Since the total integral above vanishes, we have
+\begin{equation}
+F_D = \pup - \pdn
+\end{equation}
+where $F_D$ is the total drag force from all bodies and from the top and bottom walls.
 

### 2019-08-16 docs/TexNotes/Notes.tex
NM

@@
 
-\subsection{Permeability and resistivity}
+\subsection{Total permeability and resistivity}
 Darcy's law is
@@
 
-\subsection{Removing the contribution of channel walls}
+\subsection{Isolating the resistivity due to the bodies}
 The above total resistivity reflects the resistivity from the porous matrix as well as the channel walls.
-There is a buffer region that lies outside the porous-matrix region ($x_0$ lies in the bugger region), and we would like to remove the contribution from this region.
+There is a buffer region that lies outside the porous-matrix region ($x_0$ lies in the buffer region), and we would like to remove the contribution from this region.
 Lets regard the total resistivity as an area-integral of resistivity-density, so that we can write the total in terms of the areas of the regions
@@
 The area of the included buffer region depends on $x_0$ via $A_b = 4(x_0 - 1)$.
-The area of the matrix region is always $A_m = 4$, and $A_t = A_b + A_m$.
+The area of the matrix region is always $A_m = 4$, and $A_t = A_b + A_m = 4 x_0$.
 The resulting resistivity in the matrix, $r_m$, includes the contribution from the bodies as well as the channel walls.
@@
 
-\subsection{Relationship to total drag}
+\subsection{Relationship between resistivity and total drag}
 
@@
 Then the integral on the right-hand-side of \eqref{divthm} has two contributions: first, the total drag arising from all immersed bodies as well as from the top and bottom walls, and second, the difference between the upstream and downstream pressures (we have implicitly assumed that $x_0$ is sufficiently distant from the bodies so that $\grad \bvec{u}$ is nearly zero).
-Since the total integral above vanishes, we have
+Since the total integral above vanishes, we have the approximate relationship
 \begin{equation}
-F_D = \pup - \pdn
+F_D \approx 2 w \left( \pup - \pdn \right)
 \end{equation}
 where $F_D$ is the total drag force from all bodies and from the top and bottom walls.
-
+The error in this approximation is due to neglecting the contribution of $\grad \bvec{u}$ in the stress tensor at the upstream and downstream positions.
+We thus have for the permeability
+\begin{equation}
+k_{tot} = \frac{2 x_0 \, \qavg}{\pup-\pdn} \approx 4 x_0 w \qavg F_D^{-1}
+\end{equation}
+and the resistivity
+\begin{equation}
+r_{tot} = \frac{\pup-\pdn}{2 x_0 \, \qavg} \approx \frac{F_D}{4 x_0 w \qavg}
+\end{equation}
 \end{document}

### 2019-08-19 docs/TexNotes/Notes.tex
NM

@@
 
-If we define $u(z) = U(w^2 - z^2)$, then $U = -p_x / (2 \mu)$, so that we get
+If we define $u(z) = U(w^2 - z^2)/w^2$, then $U = -w^2 p_x / (2 \mu)$ and $U$ is the maximum velocity that is obtained. Calculation gives
 \begin{align}
-\qavg = \frac{2}{3} U w^2
+\qavg = \frac{2}{3} U
 \end{align}
@@
 \begin{equation}
-r_m = \frac{A_t r_t - A_b r_b}{A_m}
+r_m = \frac{A_t r_t - A_b r_b}{A_m} = x_0(r_t - 3) + 3
 \end{equation}
@@
 \begin{equation}
-r_{tot} = \frac{\pup-\pdn}{2 x_0 \, \qavg} \approx \frac{F_D}{4 x_0 w \qavg}
+r_{tot} = \frac{\pup-\pdn}{2 x_0 \, \qavg} \approx \frac{F_D}{4 x_0 w \qavg} = \frac{3 F_D}{8 x_0 w U}
 \end{equation}
+Where we have used $\qavg = \frac{2}{3} U$.
+These are the permeability and resistivity for the entire region $-x_0 < x < x_0$.
+In particular, the resistivity of the porous matrix will be averaged with the much lower permeability of the buffer region.
+To remove the contribution from the buffer region, and thus isolate the resistivity due to the porous matrix of bodies, we can simply set $x_0 = 1$ above.
+With also setting $w=1$, we get
+\begin{equation}
+r_{tot} = \frac{3}{8} \frac{F_D}{U}
+\end{equation}
+
 \end{document}

### 2019-08-19 docs/transport/erosion_transport.tex
worked on introduction

--- 2019-08-11 docs/transport/erosion_transport.tex
@@
 University, Tallahassee, FL, 32306.}
-\address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
-\address[Bryan]{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+\address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics
+Institute, Florida State University, Tallahassee, FL, 32306.}
+\address[Bryan]{Department of Scientific Computing and Geophysical Fluid
+Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Flow-induced erosion deteriorates and reshapes solid material over a
-range of scales.  At small scales, such as in groundwater flow,
-fluid-mechanical erosion significantly alters the geometry, and
-ultimately changes the process of transport through the media.  This
-paper extends a quadrature method first outlined by Barnett, Wu, and
-Veerapaneni~\cite{bar-wu-vee2015} to simulate dense packings of eroding
-bodies, and then studies coarse-grained variables to characterize
-transport in eroded geometries.
-
-The authors previous work~\cite{qua-moo2018} developed numerical methods
-to simulate erosion of multiple bodies suspended in a Stokes flow.  The
-numerical methods can be broadly separated into two classes---a
-high-order method to solve the Stokes equations and the erosion rate in
-a complex geometry, and a time stepping method to evolve the eroding
-bodies.  The fluid solver uses a second-kind integral equation that is
-discretized with the trapezoid rule and solved iteratively with fast
-multipole accelerated GMRES, and then the trapezoid rule is used to
-compute the shear stress which is required to find the erosion rate.
-Once the erosion rate is computed, the bodies are eroded using a {\thL}
-coordinate system.  This allows us to maintain a discretization of the
-eroding bodies that is equally spaced in arclength, and is guaranteed to
-not tangle.
+Flow in many natural occurring geometries involves flows that vary over
+many orders of magnitude.  For example, the length scales of a porous
+media can vary from $10^{-6}m$ to
+$10^{-1}m$~\cite{mil-chr-imh-mcb-ped1998}.  Porous media flow plays an
+important role in several environmental and industrial applications.
+Therefore, understanding the dynamics of pore-scale flow is central to
+upscale the governing fluid equations, characterize
+dispersion~\cite{saf1959}, and quantify mixing. However, because of the
+large disparity of length and velocity scales, constitutive laws that
+link the microscopic scale to macroscopic scale must be
+developed~\cite{mil-chr-imh-mcb-ped1998}.  Therefore, to find closure
+formulas, accurate simulations at microscopic scales must be performed
+and analyzed.  A few examples of closure formulas and coarse-grained
+variables include
+pressure-saturation-permeability~\cite{mil-chr-imh-mcb-ped1998}, first
+passage time distribution~\cite{ber-sch-sil2000, hym-den-hag-kan2019,
+cve-che-wen1996}, tortuosity~\cite{hak-com-den2019,
+matyka2008tortuosity, dud-koz-mat2011, kop-kat-tim1996}, concentration
+distributions~\cite{ica-den2019, bel-sal-rin1992}, flow
+distributions~\cite{ali-par-wei-bre2017}, geometry
+connectivity~\cite{knu-car2005, wes-blo-gra2001}, pore
+distributions~\cite{ali-par-wei-bre2017}, and anomalous
+diffusion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
+sie-ili-pri-riv-gua2019}.
+
+In many applications, the fluid transport continuously changes the pore
+structure.  This is particularly common in geophysical flows where
+erosion alters the porous matrix.  In this work, we investigate flow in
+eroded porous media.  By introducing erosion, there is a two-way
+coupling between the hydrodynamics and the mechanical alteration of the
+complex porous geometry.  Transport in porous geometries that have
+undergone erosion finds applications in aquifers~\cite{cve-che-wen1996,
+sud1986}, solute transport in groundwater flow~\cite{dag1987,
+kon-bre1978}.  Porous geometries that have undergone erosion have
+certain characteristics.  For example, the geometry often has regions of
+high porosity that connect the inlet to the outlet.  This channelization
+results in velocity scales that can vary over several orders of
+magnitude~\cite{}.  Moreover, the channelization results in a geometry
+that is largely heterogeneous and anisotropic.  Others have studied
+transport in heterogeneous geometries (for example,
+see~\cite{mil-chr-imh-mcb-ped1998, ber-sch-sil2000, hak-com-den2019,
+suo-liu-gan2019, cus-hu-den1995, cve-che-wen1996, leb-ded-dav-bou2007,
+knu-car2005, bel-sal-rin1992}). However, to the best of our knowledge, a
+detailed study of transport in eroded geometries has not been performed.
+
+To describe the relevant hydrodynamics, we model two-dimensional
+microscopic scales where the fluid is governed by the incompressible
+Stokes equations (for example, see~\cite{hym-den-hag-kan2019,
+den-ica-hid2018, bar-mar-vee-zha2018}).  To couple the erosion and the
+hydrodynamics, the grains of the porous media are eroded at a rate that
+is proportional to the hydrodynamic shear stress~\cite{wan-fel2004,
+ris-moo-chi-she-zha2012, qua-moo2018}.  The incompressible Stokes
+equation are solved by first recasting them as a boundary integral
+equation (BIE).  The BIE is discretized with a high-order quadrature
+method that resolves nearly touching bodies with a near-singular
+integration scheme~\cite{bar-wu-vee2015}.  The erosion dynamics are
+simulated by applying a stable second-order time stepping Runge-Kutta
+method to the {\thL} formulation~\cite{hou-low-she1994} of the eroding
+bodies.  Given the solution of the incompressible Stokes equations are
+solved in an eroded porous geometry, we investigate different metrics to
+characterize transport.  We focus on three metrics: the tortuosity, the
+anomalous diffusion, and the distribution of geometrical channels.
+
+The first two of these metrics can be defined in terms of statistical
+moments of trajectories.  Depending on the application, transport at the
+microscale can be modelled as pure advection~\cite{dea-qua-bir-jua2018,
+leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019}, and advection
+diffusion equation~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
+with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
+this work, we assume that the trajectories are governed purely by
+advection (ie.~no diffusion).  Therefore, a trajectory $\ss(t)$
+initialized at $\ss_0$ is governed by
+\begin{align}
+  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0,
+\end{align}
+where $\uu$ is the fluid velocity.  Since there is no diffusion, all
+dispersion is a result of the particle spreading induced by the porous
+geometry.
+
+In a porous geometry, the length of a particle path is larger than the
+distance travelled if the grains were absent.  To quantify the amount of
+winding a particle takes, we use the tortuosity that is defined as the
+ratio of the particle paths length to the distance between the inlet and
+outlet.  In fractured media, the local tortuosity can be over
+2.5~\cite{hym-den-hag-kan2019}, and in porous media, depending on the
+porosity, the local tortuosity can be greater than
+1.5~\cite{kop-kat-tim1996, matyka2008tortuosity}, or greater than
+2~\cite{dud-koz-mat2011}.  The tortuosity of the geometry is defined by
+averaging over the entire inlet.  Therefore, the geometry's tortuosity
+can be used to characterize average particle
+motions~\cite{hak-com-den2019}.
+
+Anomalous diffusion  ...
+\cite{cus-hu-den1995}
+
+Gap sizes are important for network models ...
+
+The numerical methods to solve the governing fluid and erosion equations
+are based on previous work of the authors~\cite{qua-moo2018}.  The fluid
+solver uses a second-kind integral equation that is discretized with the
+trapezoid rule and solved iteratively with fast multipole accelerated
+GMRES, and then the trapezoid rule is used to compute the shear stress
+which is required to find the erosion rate.  The integral
+equation formulation only requires discretizing the boundary of the
+geometry, the complex porous matrix can be easily resolved.  Once the
+erosion rate is computed, the bodies are eroded using a
+{\thL}~\cite{hou-low-she1994} coordinate system.  This allows us to
+maintain a discretization of the eroding bodies that is equally spaced
+in arclength, and is guaranteed to not tangle.
 
@@
 derivatives of the double-layer potential.
-
-Since erosion alters the geometry, it also affects coarse-grained
-variables.  In this paper, we examine two particular variables that can
-be used to understand transport in porous media---the tortuosity and the
-anomalous diffusion rates.   The tortuosity quantifies the twisting of
-particle trajectories in a medium, and in laminar flow, the tortuosity
-is one.  While a porous media often has a large tortuosity, as erosion
-increases the gaps between bodies, preferential channels are created,
-large numbers of particles become more laminar, and we expect the
-tortuosity to decrease.  Anomalous diffusion is often used to describe
-transport in a porous media, and it quantifies the dispersion of
-particles in the flow.  Again, as the geometry erodes, particles behave
-more as a ballistic particle, and we expect less dispersion.  In this
-paper, we compute both the tortuosity and the anomalous diffusion rates
-of several geometries that form via erosion.
 

### 2019-08-20 docs/transport/erosion_transport.tex
working on intro of transport paper

@@
 is proportional to the hydrodynamic shear stress~\cite{wan-fel2004,
-ris-moo-chi-she-zha2012, qua-moo2018}.  The incompressible Stokes
-equation are solved by first recasting them as a boundary integral
-equation (BIE).  The BIE is discretized with a high-order quadrature
-method that resolves nearly touching bodies with a near-singular
-integration scheme~\cite{bar-wu-vee2015}.  The erosion dynamics are
-simulated by applying a stable second-order time stepping Runge-Kutta
-method to the {\thL} formulation~\cite{hou-low-she1994} of the eroding
-bodies.  Given the solution of the incompressible Stokes equations are
-solved in an eroded porous geometry, we investigate different metrics to
-characterize transport.  We focus on three metrics: the tortuosity, the
-anomalous diffusion, and the distribution of geometrical channels.
+ris-moo-chi-she-zha2012, qua-moo2018, par-izu2000}.  The incompressible
+Stokes equation are solved by first recasting them as a boundary
+integral equation (BIE).  The BIE is discretized with a high-order
+quadrature method that resolves nearly touching bodies with a
+near-singular integration scheme~\cite{bar-wu-vee2015}.  The erosion
+dynamics are simulated by applying a stable second-order time stepping
+Runge-Kutta method to the {\thL} formulation~\cite{hou-low-she1994} of
+the eroding bodies.  Given the solution of the incompressible Stokes
+equations are solved in an eroded porous geometry, we investigate
+different metrics to characterize transport.  We focus on three metrics:
+the tortuosity, the anomalous diffusion, and the distribution of
+geometrical channels.
 
@@
 
-Gap sizes are important for network models ...
+Rather than solving the fluid equations in a complex porous matrix,
+network models can be used to describe the flow.  Here, the pores
+between neighboring grains are thought of as small channels, and the
+geometry consists of a connected network of these
+channels~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} with the
+flow resembling a Hagen-Poiseuille profile in each channel.  So that
+network models can be applied to an eroding geometry, we characterize
+the pore sizes between neighboring grains as a function of the
+geometry's porosity.  The pore size distribution can be used to quantify
+velocity distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
+channelization~\cite{sie-ili-pri-riv-gua2019}, and
+connectivity~\cite{knu-car2005, wes-blo-gra2001}.
 
 The numerical methods to solve the governing fluid and erosion equations
-are based on previous work of the authors~\cite{qua-moo2018}.  The fluid
-solver uses a second-kind integral equation that is discretized with the
-trapezoid rule and solved iteratively with fast multipole accelerated
-GMRES, and then the trapezoid rule is used to compute the shear stress
-which is required to find the erosion rate.  The integral
-equation formulation only requires discretizing the boundary of the
-geometry, the complex porous matrix can be easily resolved.  Once the
-erosion rate is computed, the bodies are eroded using a
-{\thL}~\cite{hou-low-she1994} coordinate system.  This allows us to
-maintain a discretization of the eroding bodies that is equally spaced
-in arclength, and is guaranteed to not tangle.
-
-The trapezoid rule is spectrally accurate discretization of integral
-equation formulations of the two-dimensional Stokes equation.  However,
-at a fixed resolution, the quadrature error of the trapezoid rule is
-arbitrarily large near the eroding bodies.  Therefore, simply upsampling
-to evaluate the velocity near the eroding bodies is not sufficient.  In
-our previous work~\cite{qua-moo2018}, we restrict the proximity between
-eroding bodies.  In addition, since we only visualized the velocity and
-vorticity in the fluid bulk once per time step, we used an expensive
-upsampling scheme.  However, upsampling is not practical when if it is
-required at each GMRES iteration or when simulating tracers in the flow.
-Therefore, in this paper, we apply a Barycentric quadrature rule to
-evaluate the Stokes double-layer potential~\cite{bar-wu-vee2015}.
-However, to compute derivatives of the flow, such as the vorticity and
-the shear stress, we extend this work to compute the required
-derivatives of the double-layer potential.
+are based on previous work of the authors~\cite{qua-moo2018}.  We
+continue to use a boundary integral equation (BIE) formulation of the
+incompressible Stokes equations and a second-order Runge-Kutta method
+applied to a smoothed version of the magnitude of the shear stress.  In
+our previous work, we discretized the BIE with the trapezoid rule whose
+accuracy grows when evaluating layer potentials close to the fluid
+boundary.  Therefore, given a fixed resolution, our previous work
+required a minimum separation distance between all bodies to maintain
+stability.  In recent years, many near-singular integration schemes have
+been developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a,
+bea-yin-wil2016, bea-lai2001, klo-bar-gre-one2013}.  In this work, we
+use a Barycentric quadrature method~\cite{bar2014, bar-wu-vee2015} since
+it is a non-intrusive modification of the trapezoid rule, and the error
+is guaranteed to be uniformly bounded.  In this work, we extend this
+quadrature method so that it can be used to compute the gradient of the
+velocity which is required to compute the shear stress and the fluid
+vorticity.
 
@@
 \end{align}
-Then, particle dispersion is characterized as $\sqrt{\sigma_\lambda^2}$.
-At early times, the particles have not explored much of the geometry,
-and we expect a ballistic motion $\sigma_\lambda^2 \sim t^2$.  However,
-as the particles pass the grains, their trajectories are altered, and we
-expect that $\sigma_\lambda \sim t^\alpha$, with $\alpha < 1$,
-indicating that the flow is sub-diffusive.  With respect to erosion, as
-the bodies erode, we expect that the channelization of the geometry
-results in more trajectories undergoing a ballistic motion, and this
-would indicate decrease particle dispersion, meaning a larger anomalous
-diffusion rate.
+Since we compute second-order statistics, we use 1000 tracers so that
+the statistics have converged~\cite{bel-sal-rin1992}.  Then, particle
+dispersion is characterized as $\sqrt{\sigma_\lambda^2}$.  At early
+times, the particles have not explored much of the geometry, and we
+expect a ballistic motion $\sigma_\lambda^2 \sim t^2$.  However, as the
+particles pass the grains, their trajectories are altered, and we expect
+that $\sigma_\lambda \sim t^\alpha$, with $\alpha < 1$, indicating that
+the flow is sub-diffusive.  With respect to erosion, as the bodies
+erode, we expect that the channelization of the geometry results in more
+trajectories undergoing a ballistic motion, and this would indicate
+decrease particle dispersion, meaning a larger anomalous diffusion rate.
 

### 2019-08-20 docs/transport/erosion_transport.tex
add a new figure in transport paper

@@
 %}
-\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
-\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment}
+%\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
+\center
+\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment_long}
 \caption{\label{fig:Eroding20anomalous} The analysis of anomalous
-diffusion in 20 nearly touching bodies with respect to six porosities
-and the reference line of 100\% porosity.  The first moment (left) is
-the mean length of streamlines and the second moment (right) is the }
+diffusion in 20 nearly touching bodies with respect to initial porosity (37.68\%) and another six porosities
+during the eroding. The dashed line correspondes to a porosity of 100\% and the dashed-dotted line is a 
+line of best fit with slope 0.5742.}
 \end{figure}

### 2019-08-21 docs/transport/erosion_transport.tex
small changes
replaced diffusion with dispersion in most locations

@@
 distributions~\cite{ali-par-wei-bre2017}, and anomalous
-diffusion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
+dispersion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
 sie-ili-pri-riv-gua2019}.
@@
 results in velocity scales that can vary over several orders of
-magnitude~\cite{}.  Moreover, the channelization results in a geometry
-that is largely heterogeneous and anisotropic.  Others have studied
-transport in heterogeneous geometries (for example,
+magnitude~\cite{all-hea-lab-rei2002}.  Moreover, the channelization
+results in a geometry that is largely heterogeneous and anisotropic.
+Others have studied transport in heterogeneous geometries (for example,
 see~\cite{mil-chr-imh-mcb-ped1998, ber-sch-sil2000, hak-com-den2019,
@@
 different metrics to characterize transport.  We focus on three metrics:
-the tortuosity, the anomalous diffusion, and the distribution of
+the tortuosity, the anomalous dispersion, and the distribution of
 geometrical channels.
@@
 leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019}, and advection
-diffusion equation~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
+dispersion equation~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
 with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
@@
 
-Anomalous diffusion  ...
-\cite{cus-hu-den1995}
+The tortuosity is a first statistical moment of the tracer trajectories.
+However, to measure spread of trajectories, second-order moments are
+computed. By computing the variance of the lengths of trajectories in a
+porous media, non-local anomalous dispersion is
+observed~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
+dea-leb-den-tar-bol-dav2013}, resulting in super-diffusive dispersion.
+Anomalous dispersion has been investigated for a variety of porous
+geometries, but the effect of erosion on the anomalous dispersion rate
+is lacking.
 
@@
   \item Tracer trajectories at different time steps
-  \item Compute the anomalous diffusion rate using similar techniques as
-    the paper with Pietro~\cite{dea-qua-bir-jua2018}
+  \item Compute the anomalous dispersion rate using similar techniques
+  as the paper with Pietro~\cite{dea-qua-bir-jua2018}
   \item Need a novel way to do time stepping through the complex
@@
 However, additional properties of the flow are revealed by computing
-the anomalous diffusion rate, the tortuosity, and the distribution the
+the anomalous dispersion rate, the tortuosity, and the distribution the
 gap sizes.
@@
 Resolving the flow in these small velocity regions is essential to
-accurately describe anomalous diffusion and
+accurately describe anomalous dispersion and
 mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
@@
 The dynamics of fluid in porous media is often characterized in terms of
-anomalous diffusion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.  The
-anomalous diffusion depends on the porosity and
+anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.  The
+anomalous dispersion depends on the porosity and
 permeability~\cite{koc-bra1988}, but the distribution of the bodies also
-affects the anomalous diffusion rates.  Since erosion causes certain
-structure in porous media, calculating the anomalous diffusion rates in
+affects the anomalous dispersion rates.  Since erosion causes certain
+structure in porous media, calculating the anomalous dispersion rates in
 these geometries is important.
 
-We calculate the anomalous diffusion rates by analyzing the tracer
+We calculate the anomalous dispersion rates by analyzing the tracer
 trajectories governed by equation~\eqref{eqn:trajectories} for
@@
 trajectories undergoing a ballistic motion, and this would indicate
-decrease particle dispersion, meaning a larger anomalous diffusion rate.
+decrease particle dispersion, meaning a larger anomalous dispersion
+rate.
 
@@
   bodies with a medium initial porosity.  After computing accurate
-  tracer trajectories, the tortuosity and anomalous diffusion rates are
+  tracer trajectories, the tortuosity and anomalous dispersion rates are
   computed and compared to those of an open channel.
@@
   with a low initial porosity.  We examine the effect of the lower
-  porosity on the tortuosity and anomalous diffusion rates.
+  porosity on the tortuosity and anomalous dispersion rates.
 
@@
   with a low initial porosity.  In addition to the tortuosity and
-  anomalous diffusion rates, we compute distributions of the pore throat
-  sizes and examine their response to erosion.
+  anomalous dispersion rates, we compute distributions of the pore
+  throat sizes and examine their response to erosion.
 
@@
   bodies with a medium porosity.  We compute the tortuosity, anomalous
-  diffusion rates, and the pore throat distributions.
+  dispersion rates, and the pore throat distributions.
 \end{itemize}
@@
 
-Next, we use the tracer trajectories to compute the anomalous diffusion
+Next, we use the tracer trajectories to compute the anomalous dispersion
 rates and the tortuosities in the eroding geometry.  Since these
@@
 \caption{\label{fig:Eroding20anomalous} The analysis of anomalous
-diffusion in 20 nearly touching bodies with respect to initial porosity (37.68\%) and another six porosities
-during the eroding. The dashed line correspondes to a porosity of 100\% and the dashed-dotted line is a 
-line of best fit with slope 0.5742.}
+dispersion in 20 nearly touching bodies with respect to initial porosity
+(37.68\%) and another six porosities during the eroding. The dashed line
+correspondes to a porosity of 100\% and the dashed-dotted line is a line
+of best fit with slope 0.5742.}
 \end{figure}
@@
 porosities \todo[inline]{Don't understand how this is the case}.  The
-onset of anomalous diffusion is observed in
+onset of anomalous dispersion is observed in
 Figure~\ref{fig:Eroding100anomalous}(b). At early times, the particle
@@
 corresponding to the ballistic regime.  However, as the trajectories
-traverse the geometry, a transition to a sub-diffusion case, especially
-at low porosities, is evident.  The dashed-dotted line corresponds has a
-slope less than 1 indicating the long time behavior of the trajectories
+traverse the geometry, a transition to a super-dispersive case,
+especially at low porosities, is evident.  The dashed-dotted line
+corresponds has a slope less than 1 indicating the long time behavior of
+the trajectories
 \begin{align*}
@@
 Finally, using network models for flow in porous media~\cite{}, the
-anomalous diffusion rate can be linked to channel widths between solid
+anomalous dispersion rate can be linked to channel widths between solid
 bodies.  We construct a Delaunay triangulation with the centers of the

### 2019-08-21 docs/transport/erosion_transport.tex
working on intro and other sections

@@
 variables include
-pressure-saturation-permeability~\cite{mil-chr-imh-mcb-ped1998}, first
-passage time distribution~\cite{ber-sch-sil2000, hym-den-hag-kan2019,
-cve-che-wen1996}, tortuosity~\cite{hak-com-den2019,
+pressure-saturation-permeability~\cite{mil-chr-imh-mcb-ped1998},
+permeability-porosity~\cite{dar-mcc1998, car1937, won-kop-tom1984},
+first passage time distribution~\cite{ber-sch-sil2000,
+hym-den-hag-kan2019, cve-che-wen1996}, tortuosity~\cite{hak-com-den2019,
 matyka2008tortuosity, dud-koz-mat2011, kop-kat-tim1996}, concentration
@@
 is proportional to the hydrodynamic shear stress~\cite{wan-fel2004,
-ris-moo-chi-she-zha2012, qua-moo2018, par-izu2000}.  The incompressible
-Stokes equation are solved by first recasting them as a boundary
-integral equation (BIE).  The BIE is discretized with a high-order
-quadrature method that resolves nearly touching bodies with a
-near-singular integration scheme~\cite{bar-wu-vee2015}.  The erosion
-dynamics are simulated by applying a stable second-order time stepping
-Runge-Kutta method to the {\thL} formulation~\cite{hou-low-she1994} of
-the eroding bodies.  Given the solution of the incompressible Stokes
-equations are solved in an eroded porous geometry, we investigate
-different metrics to characterize transport.  We focus on three metrics:
-the tortuosity, the anomalous dispersion, and the distribution of
-geometrical channels.
+ris-moo-chi-she-zha2012, qua-moo2018, par-izu2000}.  A variety of
+numerical methods can be applied to solve the incompressible Stokes
+equations such as a lattice-gas model~\cite{kop-kat-tim1996}, finite
+volume~\cite{suo-liu-gan2019, den-ica-hid2018, sie-ili-pri-riv-gua2019},
+finite differences~\cite{leb-ded-dav-bou2007, knu-car2005}, and cellular
+automata~\cite{rot1988}. In this work, we instead solve an equivalent
+boundary integral equation (BIE) formulation of the incompressible
+Stokes equation.  The BIE is discretized with a high-order quadrature
+method that resolves nearly touching bodies with a near-singular
+integration scheme~\cite{bar-wu-vee2015}.  The erosion dynamics are
+simulated by applying a stable second-order time stepping Runge-Kutta
+method to the {\thL} formulation~\cite{hou-low-she1994} of the eroding
+bodies.  Given the solution of the incompressible Stokes equations are
+solved in an eroded porous geometry, we investigate different metrics to
+characterize transport.  We focus on three metrics: the tortuosity, the
+anomalous dispersion, and the distribution of geometrical channels.
 
@@
   \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0,
+  \label{eqn:tracers}
 \end{align}
@@
 dispersion is a result of the particle spreading induced by the porous
-geometry.
+geometry.  Since there is no diffusion, we apply a high-order explicit
+Runge-Kutta time stepping method to compute tracer trajectories.
+However, other groups have simulated trajectories using continuous time
+random walks~\cite{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
+ber-cor-den-sch2006} and a Fokker-Planck equation~\cite{ica-den2019}.
 
@@
 dea-leb-den-tar-bol-dav2013}, resulting in super-diffusive dispersion.
-Anomalous dispersion has been investigated for a variety of porous
-geometries, but the effect of erosion on the anomalous dispersion rate
-is lacking.
+The dispersion depends on the amount of time trajectories spend in low
+and high velocity regimes~\cite{ber-sch2001}.  Anomalous dispersion has
+been investigated for a variety of porous geometries, but not in the
+context of eroding porous geometries.
 
@@
     include historically significant reference Shelley
-    \cite{baker1986boundary}).  Also need discuss Helsing and Ojala who
-    did a similar panel-based quadrature~\cite{hel-oja2008}
+    \cite{bak-she1986}).
   \item Need to compute one additional derivative since we need the
     derivative of the velocity to find the vorticity and stress tensor
-  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
+  \item Annealing algorithm to create initial body configurations of
   \item Tracer trajectories at different time steps
@@
 \begin{itemize}
-\item Porous aquifers are a good application of our work
-
 \item \cite{dar-mcc1998} show that if there is a region with high
@@
 
-\item Continuous Time Random Walks~\cite{ber-cor-den-sch2006}
-
 \item Rothman in 1988 did CA for flow in 2D porous media
@@
 
-\item Near-singular integration such as regularization, QBX, Lagrange
-interpolation, panel-based quadrature, etc.
-
-\item The classic work of Carman~\cite{car1937} reviews early work on
-granular flow.
-
 \item Thermal boundary layer flow in anisotropic porous media is
@@
 Storesletten~\cite{ree-sto1995}.
-
-\item \cite{won-kop-tom1984} investigates relationships between the
-porosity of a rock to its permeability, surface area, and the electrical
-conductivity of salt water within the rock.  They show that the pore
-size distribution influences both the conductivity and permeability.
-
-\item In~\cite{rot1988}, Rothman applies a cellular automaton method to
-simulate flow in porous media.  The method is probabilistic and agrees
-well with analytic solutions.  However, the resulting flow is not
-smooth, so quantities such as the shear stress is challenging to stably
-compute.
-
-\item In~\cite{leb-den-car2008}, a statistical model is used to describe
-transport in a high heterogeneous porous media.
-
-\item In~\cite{bar2014}, a local expansion technique similar to QBX is
-used.  The advantage is that this extends naturally to 3D.  Also,
-Barnett analyzed the error of the Laplace DLP and SLP and compared the
-numerical results to the theory.
-
-\item Suite of near-singular integration methods such as QBX,
-panel-based quadrature, other local interpolants, regularization.
-
-\item \cite{ioa-pap-per1991} were the first to develop quadrature for
-analytic functions in the interior case.
 
@@
 is $\Omega$ whose outer solid walls is a rectangle $[-3,3] \times
-[-1,1]$ with rounded off corners.  We only place bodies only in $[-1,1]
-\times [-1,1]$.  For all simulations, we discretize $\Gamma = \bd
-\Omega$ with $N_\out=1024$ points.  For all but the first example, the
-Dirichlet boundary condition on $\Gamma$ is a hagen-poiseuille flow.  As
-the bodies erode, the flow rate is adjusted to maintain the physical
-constant pressure drop boundary condition.  To maintain this pressure
-drop, we compute the pressure at near the inlet and outlet at each time
-step as described in our previous work~\cite{qua-moo2018}.
+[-1,1]$ with rounded off corners.  We initialize the bodies randomly in
+$[-1,1] \times [-1,1]$ using a randomized method that chooses a random
+center and radii, and then accepts the new body if it is sufficiently
+separated from all other bodies.  Since the error of our quadrature
+method is bounded independent of the geometry, we consider bodies that
+are separated by less than 10\% of an arclength spacing.  For all
+simulations, we discretize $\Gamma = \bd \Omega$ with $N_\out=1024$
+points.  For all but the first example, the Dirichlet boundary condition
+on $\Gamma$ is a hagen-poiseuille flow.  As the bodies erode, the flow
+rate is adjusted to maintain the physical constant pressure drop
+boundary condition.  To maintain this pressure drop, we compute the
+pressure at near the inlet and outlet at each time step as described in
+our previous work~\cite{qua-moo2018}.
 

### 2019-08-21 docs/transport/erosion_transport.tex
small changes

@@
 \paragraph{Contributions}
-\begin{itemize}
-  \item Use novel near-singular Barycentric integration scheme for
-    Stokes equation outlined in~\cite{bar-wu-vee2015}. (Remember to
-    include historically significant reference Shelley
-    \cite{bak-she1986}).
-  \item Need to compute one additional derivative since we need the
-    derivative of the velocity to find the vorticity and stress tensor
-  \item Annealing algorithm to create initial body configurations of
-  \item Tracer trajectories at different time steps
-  \item Compute the anomalous dispersion rate using similar techniques
-  as the paper with Pietro~\cite{dea-qua-bir-jua2018}
-  \item Need a novel way to do time stepping through the complex
-    geometry
-\end{itemize}
-
+Our first main contribution is extending the work of Barnett et
+al.~\cite{bar-wu-vee2015} so that high-order accurate derivatives of
+solutions of the Stokes equations can be computed.  Using this new
+quadrature method, we can accurately compute erosion rates, and
+therefore stably simulate erosion.  Moreover, we use the quadrature
+method to visualize the vorticity in the fluid bulk.  The vorticity is
+convenient to visualize since, in the zero Reynolds number limit, it is
+equivalent to the shear stress on the eroding bodies, and therefore its
+magnitude is the erosion rate.
+
+Our second contribution is computing trajectories in the eroded
+geometries.  These trajectories are used to characterize the transport
+by computing local tortuosities of the trajectories, the tortuosity of
+the eroded geometry, and the anomalous dispersion rates in the geometry.
+Again, by using an appropriate quadrature method~\cite{bar-wu-vee2015},
+and a fourth-order Runge-Kutta method, we are able to stably compute
+trajectories that spend large amounts of time in the slow velocity
+regions near the eroding bodies, and computing these trajectories
+reliably is essential to characterize the flow.  We compare our
+tortuosity and dispersion rates with models available in the literature.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Limitations}
-\begin{itemize}
-  \item Bodies are still pinned
-  \item Bodies are still two dimensional
-\end{itemize}
+As in our previous work~\cite{qua-moo2018}, this work considers
+two-dimensional immobile bodies. However, this new work does not have a
+limitation on the packing of the bodies. Compared to our previous work,
+we are able to simulate much denser suspensions with a comparable number
+of discretization points.  While we do investigate transport in this
+work, we only consider passive particles that are undergoing only
+advection. To model other physical processes, such as contaminant
+transport, we plan to simulate a finite Peclet number
+advection-diffusion equation in eroded geometries.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\cite{bak-she1986}
+
 We start by defining the main variables used to model erosion.  A more
@@
 would have if the bodies had been absent, and the average tracer
-travelled ???\% farther than it would have if the bodies were absent.
-Therefore, at this instance in time, the tortuosity is $1.???$.
-\todo[inline]{S-H: Fill in the numbers in this paragraph}
+travelled 12\% farther than it would have if the bodies were absent.
+Therefore, at this instance in time, the tortuosity is $1.12$.
 

### 2019-08-21 docs/transport/erosion_transport.tex
do result section in transport paper

--- 2019-08-21 docs/transport/erosion_transport.tex
@@
 256$, and the smallest distance between two bodies at the initial
-condition is ???\todo[inline]{SH: Fill in this number}.  At this
-resolution, this corresponds to a spacing of ???$h$ which is much
+condition is 0.0216\todo[inline]{SH: Fill in this number}.  At this
+resolution, this corresponds to a spacing of $h$ which is much
 too small for the trapezoid rule.  By applying the Barycentric

### 2019-08-21 docs/transport/erosion_transport.tex
finished a very rough first draft of the intro

--- 2019-08-21 docs/transport/erosion_transport.tex
@@
 magnitude~\cite{all-hea-lab-rei2002}.  Moreover, the channelization
-results in a geometry that is largely heterogeneous and anisotropic.
-Others have studied transport in heterogeneous geometries (for example,
-see~\cite{mil-chr-imh-mcb-ped1998, ber-sch-sil2000, hak-com-den2019,
-suo-liu-gan2019, cus-hu-den1995, cve-che-wen1996, leb-ded-dav-bou2007,
-knu-car2005, bel-sal-rin1992}). However, to the best of our knowledge, a
-detailed study of transport in eroded geometries has not been performed.
+results in a geometry that is largely heterogeneous and anisotropic, and
+this affects heat transfer through the medium~\cite{nil-sto1990,
+ree-sto1995}.  Others have studied transport in heterogeneous geometries
+(for example, see~\cite{mil-chr-imh-mcb-ped1998, ber-sch-sil2000,
+hak-com-den2019, suo-liu-gan2019, cus-hu-den1995, cve-che-wen1996,
+leb-ded-dav-bou2007, knu-car2005, bel-sal-rin1992}). However, to the
+best of our knowledge, a detailed study of transport in eroded
+geometries has not been performed.
 
@@
 numerical methods can be applied to solve the incompressible Stokes
-equations such as a lattice-gas model~\cite{kop-kat-tim1996}, finite
+equations such as a lattice-gas or lattice Boltzmann
+model~\cite{kop-kat-tim1996, dar-mcc1998}, finite
 volume~\cite{suo-liu-gan2019, den-ica-hid2018, sie-ili-pri-riv-gua2019},
@@
 required a minimum separation distance between all bodies to maintain
-stability.  In recent years, many near-singular integration schemes have
-been developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a,
-bea-yin-wil2016, bea-lai2001, klo-bar-gre-one2013}.  In this work, we
-use a Barycentric quadrature method~\cite{bar2014, bar-wu-vee2015} since
-it is a non-intrusive modification of the trapezoid rule, and the error
-is guaranteed to be uniformly bounded.  In this work, we extend this
+stability.  One of the earliest works on near-singular integration was
+developed by Baker and Shelley~\cite{bak-she1986}, and in recent years,
+many other near-singular integration schemes have been
+developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
+bea-lai2001, klo-bar-gre-one2013}.  In this work, we use a Barycentric
+quadrature method~\cite{bar2014, bar-wu-vee2015} since it is a
+non-intrusive modification of the trapezoid rule, and the error is
+guaranteed to be uniformly bounded.  In this work, we extend this
 quadrature method so that it can be used to compute the gradient of the
@@
 
-\paragraph{Related Work}
-
-\begin{itemize}
-\item \cite{dar-mcc1998} show that if there is a region with high
-porosity, this greatly affects the relationships between the porosity
-and permeability.  Uses a Lattice-Boltzmann method.
-
-\item Rothman in 1988 did CA for flow in 2D porous media
-
-\item ``Canductivity and permeability af rocks" 1984
-
-\item ``An Analytical Study on Natural Convection in Isotropic and .
-Anisotropic Porous Channels" shows how anisotropy affects heat transfer
-in porous media.
-
-\item "The Effect of Anisotropic Permeability on Free Convective
-Boundary Layer Flow in Porous Media" is the same as last bullet
-
-\item Thermal boundary layer flow in anisotropic porous media is
-investigated by Nilsen and Storesletten~\cite{nil-sto1990} and Rees and
-Storesletten~\cite{ree-sto1995}.
-
-\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Outline of the Paper}
+In Section~\ref{sec:formulation}, we briefly summarize the model that we
+describe in detail in our previous work~\cite{qua-moo2018}.  In
+Section~\ref{sec:DLP}, we recast all the governing equations as layer
+potentials defined in both $\RR^2$ and in $\CC$.
+Section~\ref{sec:method} describes the numerical methods, with special
+attention paid to the new quadrature method to compute the shear stress
+and vorticity.  Section~\ref{sec:transport} describes measures for
+characterizing the geometry, transport, and dispersion.
+Section~\ref{sec:results} presents numerical examples for a variety of
+dense packings of bodies.  Finally, concluding remarks are made in
+Section~\ref{sec:conclusions}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\cite{bak-she1986}
-
 We start by defining the main variables used to model erosion.  A more
@@
 \section{Boundary Integral Equation Formulation}
+\label{sec:DLP}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-08-21 docs/transport/erosion_transport.tex
do result section in transport paper

@@
 256$, and the smallest distance between two bodies at the initial
-condition is ???\todo[inline]{SH: Fill in this number}.  At this
-resolution, this corresponds to a spacing of ???$h$ which is much
+condition is 0.0216\todo[inline]{SH: Fill in this number}.  At this
+resolution, this corresponds to a spacing of $3.0814h$ which is much
 too small for the trapezoid rule.  By applying the Barycentric

### 2019-08-22 docs/transport/erosion_transport.tex
add a new figure in transport paper

@@
 \center
-\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment_long}
+\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long}
 \caption{\label{fig:Eroding20anomalous} The analysis of anomalous
@@
 10^{-2}$.}
+\end{figure}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
+\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
+dispersion in 20 nearly touching bodies with respect to initial porosity
+(30.67\%) and another seven porosities during the eroding. The dashed line
+correspondes to a porosity of 100\% and the dashed-dotted lines are lines
+of best fit with slope 0.9194 (95\%), 0.8666 (85.17\%), 0.8682(75.10\%), 0.9087 (65.02\%), 
+0.9054(55.08\%), 0.7234(45.03\%), 0.6895(35.05\%), and 0.9225(30.67\%).}
 \end{figure}

### 2019-08-22 docs/transport/erosion_transport.tex
edit the caption of figure in transport paper

--- 2019-08-21 docs/transport/erosion_transport.tex
@@
 10^{-2}$.}
+\end{figure}
+
+\begin{figure}[H]
+\center
+\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
+\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
+dispersion in 20 nearly touching bodies with respect to initial porosity
+(p=30.67\%) and another seven porosities during the eroding. The dashed line
+correspondes to a porosity of 100\% and the dashed-dotted lines are lines
+of best fit with slope 0.9194 (as p=95\%), 0.8666 (as p=85.17\%), 
+0.8682 (as p=75.10\%), 0.9087 (as p=65.02\%), 
+0.9054 (as p=55.08\%), 0.7234 (as p=45.03\%), 
+0.6895 (as p=35.05\%), and 0.9225 (as p=30.67\%).}
 \end{figure}

### 2019-08-22 docs/transport/erosion_transport.tex
deleted a few lines
add a new figure in transport paper

@@
 \center
-\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long}
+\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long_ref}
 \caption{\label{fig:Eroding20anomalous} The analysis of anomalous
 dispersion in 20 nearly touching bodies with respect to initial porosity
-(37.68\%) and another six porosities during the eroding. The dashed line
-correspondes to a porosity of 100\% and the dashed-dotted line is a line
-of best fit with slope 0.5742.}
+(as p=37.68\%) and another six porosities during the eroding. The dashed line
+correspondes to a porosity of 100\% and the dashed-dotted lines are lines
+of best fit with slope 1.0644 (as p=95.1\%), 1.0673 (as p=85.09\%), 
+1.0594 (as p=75.15\%), 0.9664 (as p=65.09\%), 
+0.7766 (as p=55.10\%), 0.7475 (as p=45.08\%), 
+and 0.5607 (as p=37.68\%.}
 \end{figure}
@@
 dispersion in 20 nearly touching bodies with respect to initial porosity
-(p=30.67\%) and another seven porosities during the eroding. The dashed line
+(as p=30.67\%) and another seven porosities during the eroding. The dashed line
 correspondes to a porosity of 100\% and the dashed-dotted lines are lines

### 2019-08-23 docs/transport/erosion_transport.tex
modify figures in transport paper
edited up to end of section 4

@@
 
+\todo[inline]{Dump of text}
+Resolving the flow in these small velocity regions is essential to
+accurately describe anomalous dispersion and
+mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
+\todo[inline]{Dump of text}
+
 In a porous geometry, the length of a particle path is larger than the
@@
 observed~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
-dea-leb-den-tar-bol-dav2013}, resulting in super-diffusive dispersion.
-The dispersion depends on the amount of time trajectories spend in low
-and high velocity regimes~\cite{ber-sch2001}.  Anomalous dispersion has
-been investigated for a variety of porous geometries, but not in the
-context of eroding porous geometries.
+dea-leb-den-tar-bol-dav2013}, resulting in super-dispersion.  The
+dispersion depends on the amount of time trajectories spend in low and
+high velocity regimes~\cite{ber-sch2001}.  Anomalous dispersion has been
+investigated for a variety of porous geometries, but not in the context
+of eroding porous geometries.
 
@@
 consider flows inside a confined geometry $\Omega$ that contains $M$
-eroding bodies with boundary $\gamma_\ell$.  The boundary of the
-bounding geometry is $\Gamma$, and the fluid domain is bounded by $\bd
-\Omega = \Gamma \cup \gamma_1 \cup \cdots \cup \gamma_M$.  On each
-eroding body, $\nn$ is the normal vector pointing into the body, and
-$\ss$ is the unit tangent vector pointing in the counterclockwise
-direction.  The normal vector on $\Gamma$ is the outward unit normal.
-Neglecting inertial forces, the governing equations are
+eroding bodies with boundary $\gamma_\ell$, $\ell = 1,\ldots,M$.  The
+boundary of the bounding geometry is $\Gamma$, and the fluid domain is
+bounded by $\bd \Omega = \Gamma \cup \gamma_1 \cup \cdots \cup
+\gamma_M$.  On each eroding body, $\nn$ is the normal vector pointing
+into the body, and $\ss$ is the unit tangent vector pointing in the
+counterclockwise direction.  The normal vector on $\Gamma$ is the
+outward unit normal.  Neglecting inertial forces, the governing
+equations are
 \begin{equation}
@@
 The erosion rate loses differentiability if the shear stress changes
-sign, and this leads to corners developing on $\gamma$ and can lead to
-numerical instabilities.  Therefore, we supplement the erosion rate with
-a curvature penalization term by replacing the erosion model
-in~\eqref{eqn:erosionModel} with 
+sign, and this leads to corners developing on $\gamma$ and numerical
+instabilities.  Therefore, we modify the erosion rate by adding a
+curvature penalization. That is, the erosion model
+in~\eqref{eqn:erosionModel} is replaced with 
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Using the same approach as
-our previous work~\cite{qua-moo2018}, we use a double-layer potential
-formulation for the velocity $\uu$.  The double-layer potential is
+Applying the same approach as our previous work~\cite{qua-moo2018}, we
+use a double-layer potential formulation for the velocity $\uu$.  The
+double-layer potential is
 \begin{align}
@@
 \end{align}
-For our particular problem, $\ff$ is the prescribed velocity on the
-outer wall and is zero on the eroding bodies.  The operator $\NN_0$ is
-the integral operator with kernel $\nn(\xx) \otimes \nn(\yy)$, $\xx,\yy
-\in \Gamma$, which removes the rank one null space resulting from the
-flux-free requirement of $\ff$.
+The operator $\NN_0$ is the integral operator with kernel $\nn(\xx)
+\otimes \nn(\yy)$, $\xx,\yy \in \Gamma$, which removes the rank one null
+space resulting from the flux-free requirement of $\ff$.  In this work,
+$\ff$ is the prescribed velocity, $\UU$, on the outer wall, $\Gamma$,
+and is zero on the eroding bodies, $\gamma_\ell$, $\ell=1,\ldots,M$.
 
 The deformation tensor, pressure, and vorticity of the double-layer
-potential, Stokeslets, and rotlets, can be all be computed analytically
-in terms of the density function.  For $\xx \in \Omega$, the deformation
-tensor, pressure, and vorticity of the double-layer
-potential~\eqref{eqn:stokesDLP} are
+potential, Stokeslets, and rotlets, can all be computed analytically in
+terms of the density function and the strengths of the Stokeslets and
+rotlets.  For $\xx \in \Omega$, the deformation tensor, pressure, and
+vorticity of the double-layer potential~\eqref{eqn:stokesDLP} are
 \begin{align}
@@
 $\xx \in \bd \Omega$.  Since the deformation tensor of the double-layer
-potential is discontinuous across $\bd\Omega$, a jump term must be added
-to $\ssigma^\DD(\xx)$ for $\xx \in \gamma$.  Finally, the deformation
-tensor, pressure, and vorticity due to the Stokeslets and rotlets are
-straightforward to compute~\cite{qua-moo2018}.  Having computed the
-deformation tensor on $\gamma$, the shear stress is computed as defined
-in equation~\eqref{eqn:shearStress}.
+potential is discontinuous across $\bd\Omega$, the jump term 
+\begin{align}
+  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
+    \begin{array}{cc}
+      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
+    \end{array}
+  \right],
+  \label{eqn:defJump}
+\end{align}
+must be added to $\ssigma^\DD(\xx)$ for $\xx \in \gamma$.  Finally, the
+Stokeslets and rotlets do not have any jumps on $\gamma$, so the
+deformation tensor, pressure, and vorticity due to the Stokeslets and
+rotlets are straightforward to compute~\cite{poz1992} \todo[inline]{BQ:
+Make sure this is the right reference}.  Having computed the deformation
+tensor on $\gamma$, the shear stress is computed as defined in
+equation~\eqref{eqn:shearStress}.
 
@@
 In equations~\eqref{eqn:stokesDLP} and~\eqref{eqn:deformationDLP}, $\uu$
-and its deformation tensor are written as a contour integral in $\RR^2$,
-respectively.  However, these layer potentials can be rewritten in terms
-of Cauchy integrals and its derivatives in $\CC$.  The first step is to
-write the Stokes double-layer potential as the sum of a Laplacian
-double-layer potential and its gradient
+and its deformation tensor are written as a contour integral in $\RR^2$.
+However, so that we can apply a particular quadrature method, we need to
+write these layer potentials in terms of Cauchy integrals in $\CC$ and
+their derivatives.  The first step is to write the Laplace double-layer potential as the complex integral
+\begin{align}
+  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
+    \frac{\rr \cdot \nn}{\rho^2}\, ds_\yy = \Re (v(x)) \quad 
+    \text{where} \quad v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x - y} \, dy,
+  \label{eqn:laplaceComplex}
+\end{align}
+where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$.
+Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
+integral by first finding the boundary data of $v$.  We assume that
+$\Omega$ is a simply-connected interior domain. Then, the boundary data
+of $v$ satisfies the Sokhotski-Plemelj jump relation
+\begin{align}
+  \label{eqn:SPrelation}
+  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
+\end{align}
+For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
+for multiply-connected domains, such as a porous media, $\bd\Omega$ is
+simply decomposed into its different connected components and the
+appropriate Cauchy integral is evaluated.  Since $v$ is a holomorphic
+function and we have its boundary data, by the Cauchy integral theorem
+we have
+\begin{align}
+  \label{eqn:cauchy}
+  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
+    \frac{v(y)}{y-x} \,dy, \quad
+  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^2} \, dy, \quad
+  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^3} \, dy,
+\end{align}
+for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
+\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
+function defined in equation~\eqref{eqn:laplaceComplex}, and its first
+two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
+
+To rewrite the Stokes double-layer potential~\eqref{eqn:stokesDLP} in
+terms of Cauchy integrals and their derivatives, we write it in terms of
+Laplace layer potentials
 \begin{equation}
@@
 \end{equation}
-Next, since the Laplacian double-layer potential can be written as the
-Cauchy integral
-\begin{align}
-  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
-  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy,
-  \label{eqn:laplaceComplex}
-\end{align}
-where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
-the Stokes double-layer potential can be written in terms of a complex
-integral and its first derivative.  In addition, the derivative of the
-Stokes double-layer potential can be written in terms of a complex
-integral and its first two derivatives.
-
-Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
-integral by first finding boundary data of $v$.  We assume that $\Omega$
-is a simply-connected interior domain.  Similar formulas exist for
-exterior domains, and for multiply-connected domains, $\bd\Omega$ is
-simply decomposed into its different connected components.  The boundary
-data of $v$ satisfies the Sokhotski-Plemelj jump relation
-\begin{align}
-  \label{eqn:SPrelation}
-  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
-\end{align}
-Since $v$ is a holomorphic function and we have its boundary data, by
-the Cauchy integral theorem we have
-\begin{align}
-  \label{eqn:cauchy}
-  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
-    \frac{v(y)}{y-x} \,dy, \quad
-  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^2} \, dy, \quad
-  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^3} \, dy.
-\end{align}
-for $x \in \Omega$.  A quadrature method to compute these Cauchy
-integrals with a uniform error for all $x \in \Omega$ is presented in
-Section~\ref{sec:bary}.
-
-In equation~\eqref{eqn:cauchy}, $v(x)$ depends on the density function
-$\eta \in \CC$, so we use the notation $v[\eta](x)$ to denote the
-holomorphic function defined in equation~\eqref{eqn:laplaceComplex}, and
-the derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  Having
-introduced this notation, the two components of the Stokes double-layer
-potential are~\cite{bar-wu-vee2015}
+Therefore, the Stokes double-layer potential can be written in terms of
+Cauchy integrals and their first derivative  as~\cite{bar-wu-vee2015}
 \begin{equation}
@@
 \begin{align} 
-  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
+  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad
   \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
@@
 of the gradient of the velocity so that we can compute the shear stress
-and the vorticity.  Each term of the gradient of the velocity field can
-be written in terms of Cauchy integrals.  Taking the derivatives of
-equation~\eqref{eqn:cauchyVelocity} with respect to $x_1$ and $x_2$, we
-have 
+and the vorticity.  The deformation tensor at $x \in \Omega$ is found by
+computing the derivatives of $u_1$ and $u_2$ as defined in
+equation~\eqref{eqn:cauchyVelocity}  
 \begin{equation}
@@
 \end{equation}
-With these four expressions, the deformation tensor of the double-layer
-potential, $\ssigma^D = \frac{1}{2} (\nabla \uu + \nabla \uu^T)$, is
-written in terms of Cauchy integrals.  In addition, the vorticity is
+The same expressions are used to compute the deformation tensor for $x
+\in \bd\Omega$, except that the jump condition~\eqref{eqn:defJump} is
+included.  Finally, to compute the shear stress, the deformation tensor
+on $\bd\Omega$ is applied to the normal and tangent vectors as defined
+in equation~\eqref{eqn:shearStress}.
+
+In a shear flow, the vorticity is equivalent to the shear stress.  Since
+the erosion rate is proportional to the magnitude of the shear stress,
+it is constructive to visualize the vorticity of the fluid.  For $x \in
+\Omega$, the Cauchy integral representation of the vorticity is
 \begin{align}
@@
 \Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
- + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)).
-\end{align}
+ + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)), \quad x \in \Omega.
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Transport, Tracers, and Tortuosity}
+\label{sec:transport}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Erosion leads to interesting porous geometries, and we are interested in
+characterizing transport in these geometries.  In our previous
+work~\cite{qua-moo2018}, we examined the effect of erosion on
+the area fraction, flow rate, and the total drag.  However, to
+characerize transport, other quantities must be examined.  Here, we
+compute the anomalous dispersion rate, the tortuosity, and the
+distribution of the gap sizes.  The first two metrics can be defined in
+terms of tracer trajectories governed by an advection
+equation~\eqref{eqn:tracers}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Anomalous Disperision}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The dynamics of fluid in porous media is often characterized in terms of
+anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.  The
+anomalous dispersion rate depends on the porosity and
+permeability~\cite{koc-bra1988}, but the distribution of the bodies also
+affects the anomalous dispersion rates.  Since erosion causes certain
+structure in porous media, calculating the anomalous dispersion rates in
+these geometries is important.
+
+We calculate the anomalous dispersion rates by analyzing the tracer
+trajectories governed by equation~\eqref{eqn:tracers} for geometries
+that are formed by erosion.  Given a set of trajectories, we define
+$\lambda_j(t)$ to be the arclength of the trajectory
+\begin{align}
+  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
+    \quad j=1,\ldots,N_p.
+\end{align}
+Then, the first and second ensemble moments are
+\begin{align}
+  \langle \lambda \rangle (t) = 
+    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
+    \sigma_\lambda^2(t) = \frac{1}{N_p} 
+    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2.
+\end{align}
+Since we compute second-order statistics, we use 1000 tracers so that
+the statistics have converged~\cite{bel-sal-rin1992}.  Then, particle
+dispersion is characterized as $\sigma_\lambda$.  At early times, the
+particles have not explored much of the geometry, and we expect a
+ballistic motion $\sigma_\lambda \sim t$.  However, as the particles
+pass the grains, their trajectories are altered, and we expect that
+$\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$, indicating
+that the flow is super-dispersive.
+
+To establish an anomalous dispersion rate, the trajectories must pass
+several grains so that an asymptotic regime is reached. The geometries
+that we consider are too short to observe the asymptotic dispersion, so
+we use a reinsertion method to form longer trajectories. Similar to the
+work of others~\cite{dea-qua-bir-jua2018, puy-gou-den2019}, once a
+particle reaches the end of the porous region, it is reinserted at the
+start of the porous region.  To minimize errors caused by the
+reinsertion, the particle is initialized at the discretization point
+that has the closest velocity to the particles velocity at the outlet.
+After a single trajectory is formed, it has undergone a collection of
+reinsertions.  The fore, as a post-processing step, the trajectory is made
+continuous by attaching the tail of each segment to the origin of the
+next segment.
+
+We consider trajectories in an open channel so that they can be compared
+to trajectories in eroded geometries with large permeability.  The
+trajectory originating at $(s_1(0),s_2(0))$ is
+\begin{align}
+  s_1(t) = (1-s_2(0)^2)t + s_1(0), \quad
+  s_2(t) = s_2(0).
+\end{align}
+Averaging over $s_2(0) \in [-1,1]$, the first and second ensemble
+moments are
+\begin{align}
+  \langle \lambda \rangle (t) = \frac{2}{3}t, \quad 
+    \sigma_\lambda^2(t) = \frac{4}{45}t^2,
+\end{align}
+so the particle motion is ballistic since $\sigma_\lambda \sim t$.  In
+Section~\ref{sec:results}, we compare these moments in an open channel
+with the trajectories in an eroded geometry.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tortuosity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The tortuosity of a geometry, denoted by $T \geq 1$, is a dimensionless
+number that quantifies the average amount of turning made by
+trajectories passing through the geometry.  Unlike the for the
+dispersion, we do not use reinsertion to form long trajectories.  The
+local tortuosity
+\begin{align}
+  \tau(y) = \frac{\lambda(y)}{d},
+  \label{eqn:localTort}
+\end{align}
+is the length of a single trajectory, $\lambda(y)$, whose initial
+$y$-coordinate is a value $y$ on a cross-section of length $d$.  Taking
+the average over all points on the cross-section defines the hydraulic
+tortuosity
+\begin{align}
+  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
+  {\displaystyle\int_{S}u_x(y)\,dy},
+  \label{eqn:tortuosity1}
+\end{align}
+where $S$ is a cross-section perpendicular to the $x$-axis with length
+$d$, $\lambda(y)$ is the length of the trajectory that is initialized at
+the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of the
+velocity at the $y$-coordinate along $S$.  Therefore, the tortuosity
+satisfies $T \geq 1$, and $T=1$ only if no grains are present.
+
+The choice for the trajectory with length $\lambda(y)$ is not universal,
+and Duda et al.~\cite{dud-koz-mat2011} summarize several options. One
+choice, which we adopt, considers trajectories that originate at $S$ and
+terminate at a parallel cross-section.  We use the cross-sections $x=-1$
+and $x=1$.  This choice of averaging allows us to also compute the
+tortuosity in terms of an area integral.  Under the assumptions that the
+flow is incompressible and not re-entrant, meaning that all streamlines
+connect the two cross-sections, the tortuosity in
+equation~\eqref{eqn:tortuosity1} is equivalent to~\cite{dud-koz-mat2011}
+\begin{align}
+  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
+           {\displaystyle\int_\Omega u_x(\yy)\, d\yy},
+  \label{eqn:tortuosity2}
+\end{align}
+where $\Omega$ is the fluid region between the inlet and outlet
+cross-sections.  Recirculation zones are possible in viscous
+fluids~\cite{hig1985}, but they are very small in the examples we
+consider and have a negligible effect on the tortuosity (for example,
+see Figure~\ref{fig:Eroding20tort_all}).  Since
+equation~\eqref{eqn:tortuosity2} does not require the additional work of
+computing particle trajectories at every time step, we use this
+definition for the majority of the tortuosity calculations.
+
+There have been efforts to relate the tortuosity to the
+porosity~\cite{matyka2008tortuosity}.  For example, Matyka et
+al.~\cite{matyka2008tortuosity} propose the models
+\begin{subequations}
+  \label{eqn:tortuosityModels}
+  \begin{align}
+    \widehat{T}(\phi) &= \phi^{-p}, \\
+    \widehat{T}(\phi) &= 1-p \log \phi, \\
+    \widehat{T}(\phi) &= 1+p (1-\phi), \\
+    \widehat{T}(\phi) &= (1+p (1-\phi))^2, 
+  \end{align}
+\end{subequations}
+where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
+compare these four models with the tortuosity of eroding geometries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Pore Throat Size}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{itemize}
+  \item Pore throat sizes affect many things such as first passage time,
+  mixing, chemical reactions, heat conduction, biological activities
+\end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We have shown that the velocity, shear stress, and vorticity of the
-double-layer potential can all be written in terms of Cauchy integrals
-and its first two derivatives.  Therefore, we require quadrature methods
-to evaluate the expressions in equation~\eqref{eqn:cauchy}.  Since the
-integrands are all smooth and periodic, the trapezoid rule has spectral
-accuracy.  However, the integrand becomes nearly singular as $x$
-approaches $\bd\Omega$, and the quadrature error is arbitrarily large at
-a fixed resolution.  There have been a variety of near-singular
-integration schemes developed.   We opt to use a method first outlined
-by Barnett et al.~\cite{bar-wu-vee2015} which we call the {\em
-Barycentric quadrature rule}.  Quadrature rules for only the Cauchy
-integral and its first derivative are presented, and we extend this
-result to include the second derivative.
+In line with our previous work~\cite{qua-moo2018}, we use two meshes to
+simulate erosion.   The integral equation is solved with a collocation
+method (Section~\ref{sec:spatialDiscretization}).  Depending on the
+proximity of the target and source points, either the trapezoid rule or
+the Barycentric quadrature rule (Section~\ref{sec:bary}) is applied.  A
+selection algorithm that determines which quadrature method is applied
+is described in Section~\ref{sec:fmm}.  Once the shear stress is
+computed, the bodies are converted to a {\thL}
+framework~\cite{hou-low-she1994}.  Then, the erosion model is integrated
+forward a single time step.  By using a {\thL} formulation, the stiff
+curvature term is linear and the discretization points remain equispaced
+in arclength.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Barycentric Quadrature for $v''(x)$}
+\subsection{Barycentric Quadrature Formulas}
 \label{sec:bary}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\todo[inline]{Dump of text}
+Having developed numerically accurate methods to compute the velocity
+$\uu$ at points close to the bodies, we are able to compute the
+trajectories of particles passing through an eroded body.  Since the
+trajectories are computed with high-order methods in both space and
+time,  we are able to simulate dynamics very close to the eroding bodies
+(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
+
+We have shown that the velocity, shear stress, and vorticity of the
+double-layer representation can all be written in terms of Cauchy
+integrals and its first two derivatives.  Therefore, we require
+quadrature methods to evaluate the expressions in
+equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
+periodic, the trapezoid rule has spectral accuracy.  However, the
+integrand becomes nearly singular as $x$ approaches $\bd\Omega$, and the
+quadrature error is arbitrarily large at a fixed resolution.  There have
+been a variety of near-singular integration schemes developed.   We opt
+to use a method first outlined by Barnett et al.~\cite{bar-wu-vee2015}
+which we call the {\em Barycentric quadrature rule}.  Quadrature rules
+for only the Cauchy integral and its first derivative are presented, and
+we extend this result to include the second derivative.
+\todo[inline]{Dump of text}
+
 Equations~\eqref{eqn:cauchyVelocity} and~\eqref{eqn:cauchyGradient} show
@@
 \frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
-    \frac{(y-a)^{-1}}{y-x} dy. 
+    \frac{(y-a)^{-1}}{y-x}\, dy. 
 \end{align}
@@
 
-In Section~\ref{sec:transport}, we we analyze passive tracers suspended in
-an eroded geometry.  Give such a geometry $\Omega$, a tracer $\ss(t)$
-initialized at $\ss_0$ is governed by 
+In Section~\ref{sec:transport}, we require trajectories of passive
+tracers passing through an eroded geometry.  Given such a geometry
+$\Omega$, a tracer $\ss(t)$ initialized at $\ss_0$ is governed by 
 \begin{align}
@@
 fourth-order Runge-Kutta method.  To evaluate $\uu(\ss)$, depending on
-the proximity of $\ss$ to $\bd\Omega$, we either use the trapezoid rule
-or the Barycentric quadrature rule as described in Section~\ref{sec:fmm}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Transport, Tracers, and Tortuosity}
-\label{sec:transport}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Erosion leads to interesting porous geometries, and we are interested in
-characterizing transport in these geometries.  For porous media, two of
-the most important variables are the porosity and the permeability.
-However, additional properties of the flow are revealed by computing
-the anomalous dispersion rate, the tortuosity, and the distribution the
-gap sizes.
-
-Having developed numerically accurate methods to compute the velocity
-$\uu$ at points close to the bodies, we are able to compute the
-trajectories of particles passing through an eroded body.  Since the
-trajectories are computed with high-order methods in both space and
-time,  we are able to simulate dynamics very close to the eroding bodies
-(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
-Resolving the flow in these small velocity regions is essential to
-accurately describe anomalous dispersion and
-mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Anomalous Diffusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The dynamics of fluid in porous media is often characterized in terms of
-anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.  The
-anomalous dispersion depends on the porosity and
-permeability~\cite{koc-bra1988}, but the distribution of the bodies also
-affects the anomalous dispersion rates.  Since erosion causes certain
-structure in porous media, calculating the anomalous dispersion rates in
-these geometries is important.
-
-We calculate the anomalous dispersion rates by analyzing the tracer
-trajectories governed by equation~\eqref{eqn:trajectories} for
-geometries that are formed by erosion.  Given a set of trajectories, we
-define $\lambda_j(t)$ to be the arclength of the trajectory
-\begin{align}
-  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
-    \quad j=1,\ldots,N_p.
-\end{align}
-Then, the first and second ensemble moments are
-\begin{align}
-  \langle \lambda \rangle (t) = 
-    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
-    \sigma_\lambda^2(t) = \frac{1}{N_p} 
-    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2.
-\end{align}
-Since we compute second-order statistics, we use 1000 tracers so that
-the statistics have converged~\cite{bel-sal-rin1992}.  Then, particle
-dispersion is characterized as $\sqrt{\sigma_\lambda^2}$.  At early
-times, the particles have not explored much of the geometry, and we
-expect a ballistic motion $\sigma_\lambda^2 \sim t^2$.  However, as the
-particles pass the grains, their trajectories are altered, and we expect
-that $\sigma_\lambda \sim t^\alpha$, with $\alpha < 1$, indicating that
-the flow is sub-diffusive.  With respect to erosion, as the bodies
-erode, we expect that the channelization of the geometry results in more
-trajectories undergoing a ballistic motion, and this would indicate
-decrease particle dispersion, meaning a larger anomalous dispersion
-rate.
-
-At early times, the geometry has not been altered by erosion, and we
-expect large amounts of dispersion.  However, as the bodies erode, the
-porosity increases and the trajectories behave more closely to laminar
-trajectories in an open channel.  To be able to compare the dispersion
-of an eroded geometry with that of an open channel, we consider
-trajectories in an open channel.  The trajectory originating at
-$(s_1(0),s_2(0))$ is
-\begin{align}
-  s_1(t) &= (1-s_2(0)^2)t + s_1(0), \\
-  s_2(t) &= s_2(0).
-\end{align}
-Averaging over $s_2(0) \in [-1,1]$, the first and second ensemble
-moments are
-\begin{align}
-  \langle \lambda \rangle (t) = \frac{2}{3}t, \quad 
-    \sigma_\lambda^2(t) = \frac{4}{45}t^2.
-\end{align}
-In Section~\ref{sec:results}, we compare these moments in an open
-channel with the trajectories in an eroding geometry.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tortuosity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The tortuosity of a geometry, denoted by $T \geq 1$, is a dimensionless
-number that quantifies the average amount of turning made by
-trajectories passing through the geometry.  The local tortuosity
-\begin{align}
-  \tau(y) = \frac{\lambda(y)}{d}.
-  \label{eqn:localTort}
-\end{align}
-considers the length of a single trajectory, $\lambda$ whose initial
-$y$-coordinate is a value $y$ on a cross-section of length $d$.  Taking
-the average over all points on the cross-section defines the hydraulic
-tortuosity
-\begin{align}
-  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
-  {\displaystyle\int_{S}u_x(y)\,dy},
-  \label{eqn:tortuosity1}
-\end{align}
-where $S$ is a cross-section perpendicular to the $x$-axis with length
-$d$, $\lambda(y)$ is the length of the trajectory that is initialized at
-the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of the
-velocity at the $y$-coordinate along $S$.  Since the flow is laminar in
-the absence of grains, the tortuosity of a straight channel is $T=1$.
-The choice for the trajectory with length $\lambda(y)$ is not universal,
-and Duda et al.~\cite{dud-koz-mat2011} summarize several options. One
-choice, which we adopt, considers trajectories that originate at $S$ and
-terminate at a parallel cross-section.  We use the cross-sections $x=-1$
-and $x=1$.  This choice of averaging allows us to also compute the
-tortuosity in terms of an area integral.  Under the assumptions that the
-flow is incompressible and not reentrant, meaning that all streamlines
-connect the two cross-sections, the tortuosity in
-equation~\eqref{eqn:tortuosity1} is equivalent to~\cite{dud-koz-mat2011}
-\begin{align}
-  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
-           {\displaystyle\int_\Omega u_x(\yy)\, d\yy},
-  \label{eqn:tortuosity2}
-\end{align}
-where $\Omega$ is the region between the inlet and outlet
-cross-sections.  Recirculation zones are possible in viscous
-fluids~\cite{hig1985}, but they only constitute a small fraction of the
-total porous media, and in our examples, their velocities are very
-small.  Therefore, the tortuosity defined in
-equation~\eqref{eqn:tortuosity2} is a tight upper bound for the
-definition in equation~\eqref{eqn:tortuosity1}.  For the geometries we
-consider, we will show that their difference is negligible (see
-Figure~\ref{fig:Eroding20tort_all}).  Since
-equation~\eqref{eqn:tortuosity2} does not require the additional work of
-computing particle trajectories, we use this definition for the majority
-of the tortuosity calculations.
-
+the proximity of $\ss(t)$ to $\bd\Omega$, we either use the trapezoid
+rule or the Barycentric quadrature rule as described in
+Section~\ref{sec:fmm}.
+
+\todo[inline]{Dump of text}
 The first method to numerically compute the tortuosity uses $N_p$
@@
 \end{align}
-
-There have been efforts to relate the tortuosity to the
-porosity~\cite{matyka2008tortuosity}.  For example, Matyka et
-al.~\cite{matyka2008tortuosity} propose the models
-\begin{subequations}
-  \label{eqn:tortuosityModels}
-  \begin{align}
-    \widehat{T}(\phi) &= \phi^{-p}, \\
-    \widehat{T}(\phi) &= 1-p \log \phi, \\
-    \widehat{T}(\phi) &= 1+p (1-\phi), \\
-    \widehat{T}(\phi) &= (1+p (1-\phi))^2, 
-  \end{align}
-\end{subequations}
-where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
-compare these four models with the tortuosity of eroding geometries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pore Throat Size}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{itemize}
-  \item Pore throat sizes affect many things such as first passage time,
-  mixing, chemical reactions, heat conduction, biological activities
-\end{itemize}
+\todo[inline]{Dump of text}
 
@@
 \center
-\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian}
+\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian}
 \caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
@@
 \center
-\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian20b}
+\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian20b}
 \caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
@@
 \center
-\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
+\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian100}
 \caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian

### 2019-08-23 docs/transport/erosion_transport.tex
NM

@@
 Flow in many natural occurring geometries involves flows that vary over
-many orders of magnitude.  For example, the length scales of a porous
+many orders of magnitude.  \todo[]{The grammar in the first sentence is awkward: Flow in ... involves flows?}
+For example, the length scales of a porous
 media can vary from $10^{-6}m$ to

### 2019-08-23 docs/transport/erosion_transport.tex
pushing cause nick just pushed ...

--- 2019-08-23 docs/transport/erosion_transport.tex
@@
     \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
-  \label{eqn:stokesDLP}
+  \label{eqn:velocityDLP}
 \end{align}
@@
   S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
-    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \quad
+    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2}
+    \right)\llambda_\ell, \quad
   R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
@@
 where the density function, Stokeslets, and rotlets satisfy
+\begin{subequations}
+\label{eqn:BIE}
 \begin{align}
@@
 \end{align}
-The operator $\NN_0$ is the integral operator with kernel $\nn(\xx)
-\otimes \nn(\yy)$, $\xx,\yy \in \Gamma$, which removes the rank one null
-space resulting from the flux-free requirement of $\ff$.  In this work,
-$\ff$ is the prescribed velocity, $\UU$, on the outer wall, $\Gamma$,
-and is zero on the eroding bodies, $\gamma_\ell$, $\ell=1,\ldots,M$.
+\end{subequations}
+The operator $\NN_0$ is the integral operator with kernel
+$N_(0)(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$,
+which removes the rank one null space resulting from the flux-free
+requirement of $\ff$.  In this work, $\ff$ is the prescribed velocity,
+$\UU$, on the outer wall, $\Gamma$, and is zero on the eroding bodies,
+$\gamma_\ell$, $\ell=1,\ldots,M$.
 
@@
 rotlets.  For $\xx \in \Omega$, the deformation tensor, pressure, and
-vorticity of the double-layer potential~\eqref{eqn:stokesDLP} are
+vorticity of the double-layer potential~\eqref{eqn:velocityDLP} are
 \begin{align}
   \label{eqn:deformationDLP} 
-  \ssigma^\DD(\xx) &= \frac{1}{2\pi}\int_{\bd\Omega} \left(
+  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
+      \eeta(\yy) ds_{\yy} 
+  = \frac{1}{2\pi}\int_{\bd\Omega} \left(
     2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
@@
     \right. \nonumber \\
-    & \qquad\qquad \left.
+    & \qquad\qquad\qquad\qquad\qquad\qquad \left.
     +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
@@
     \right) \, ds_\yy, \\
-  p^\DD(\xx) &= -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+%
+  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
+      \eeta(\yy) ds_{\yy} 
+  = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
       \eeta(\yy)\,ds_\yy, \\
-  \omega^\DD(\xx) &= -\frac{1}{\pi} \int_{\bd\Omega}
+%
+  \label{eqn:vorticityDLP} 
+  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
+      \eeta(\yy) ds_{\yy} 
+  = -\frac{1}{\pi} \int_{\bd\Omega}
     \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
@@
   \right],
-  \label{eqn:defJump}
-\end{align}
-must be added to $\ssigma^\DD(\xx)$ for $\xx \in \gamma$.  Finally, the
+  \label{eqn:deformationJump}
+\end{align}
+must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
 Stokeslets and rotlets do not have any jumps on $\gamma$, so the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In equations~\eqref{eqn:stokesDLP} and~\eqref{eqn:deformationDLP}, $\uu$
-and its deformation tensor are written as a contour integral in $\RR^2$.
-However, so that we can apply a particular quadrature method, we need to
-write these layer potentials in terms of Cauchy integrals in $\CC$ and
-their derivatives.  The first step is to write the Laplace double-layer potential as the complex integral
+In equations~\eqref{eqn:velocityDLP} and~\eqref{eqn:deformationDLP},
+$\uu$ and its deformation tensor are written as a contour integral in
+$\RR^2$.  However, so that we can apply a particular quadrature method,
+we need to write these layer potentials in terms of Cauchy integrals in
+$\CC$ and their derivatives.  The first step is to write the Laplace
+double-layer potential as the complex integral
 \begin{align}
@@
 
-To rewrite the Stokes double-layer potential~\eqref{eqn:stokesDLP} in
+To rewrite the Stokes double-layer potential~\eqref{eqn:velocityDLP} in
 terms of Cauchy integrals and their derivatives, we write it in terms of
@@
 Double-Layer Potential}
+\label{sec:gradDLPcomplex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The same expressions are used to compute the deformation tensor for $x
-\in \bd\Omega$, except that the jump condition~\eqref{eqn:defJump} is
-included.  Finally, to compute the shear stress, the deformation tensor
-on $\bd\Omega$ is applied to the normal and tangent vectors as defined
-in equation~\eqref{eqn:shearStress}.
+\in \bd\Omega$, except that the jump
+condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
+the shear stress, the deformation tensor on $\bd\Omega$ is applied to
+the normal and tangent vectors as defined in
+equation~\eqref{eqn:shearStress}.
 
@@
 fluids~\cite{hig1985}, but they are very small in the examples we
-consider and have a negligible effect on the tortuosity (for example,
-see Figure~\ref{fig:Eroding20tort_all}).  Since
+consider and have a negligible effect on the tortuosity.  Since
 equation~\eqref{eqn:tortuosity2} does not require the additional work of
 computing particle trajectories at every time step, we use this
-definition for the majority of the tortuosity calculations.
+definition for the majority of the tortuosity calculations.  However, we
+do compare the two formulas for the tortuosity at several time steps in
+Section~\ref{sec:results}.
 
@@
 In line with our previous work~\cite{qua-moo2018}, we use two meshes to
-simulate erosion.   The integral equation is solved with a collocation
-method (Section~\ref{sec:spatialDiscretization}).  Depending on the
-proximity of the target and source points, either the trapezoid rule or
-the Barycentric quadrature rule (Section~\ref{sec:bary}) is applied.  A
-selection algorithm that determines which quadrature method is applied
-is described in Section~\ref{sec:fmm}.  Once the shear stress is
-computed, the bodies are converted to a {\thL}
-framework~\cite{hou-low-she1994}.  Then, the erosion model is integrated
-forward a single time step.  By using a {\thL} formulation, the stiff
-curvature term is linear and the discretization points remain equispaced
-in arclength.
+simulate erosion. The integral equation is solved by discretizing the
+boundary of the geometry at a set of points distributed equally in
+arclength, and then applying a collocation method
+(Section~\ref{sec:spatialDiscretization}).  The quadrature rule is
+either the trapezoid rule or the Barycentric quadrature rule
+(Section~\ref{sec:bary}).  The selection algorithm that determines which
+quadrature method is applied is described in Section~\ref{sec:fmm}.
+Once the shear stress is computed, the bodies are eroded a single time
+step by using a {\thL} discretization~\cite{hou-low-she1994}.  By using
+a {\thL} formulation, the stiff curvature term is linear and the
+discretization points remain equispaced in arclength.  Finally, time
+stepping methods for the eroding bodies and passive particles are
+described in Section~\ref{sec:time}
 
@@
 the one-dimensional boundary of the domain.  Therefore, we easily
-resolve complex geometries, and differentiation can be performed with
+resolve complex geometries, and differentiation is performed with
 spectral accuracy in Fourier space.  We discretize each eroding body
 $\gamma_k$ with $N_\iin$ points and discretize the outer wall $\Gamma$
-with $N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ is
-denoted by $\yy_j^0$, and the $j^{th}$ discretization point on
-$\gamma_k$ is denoted by $\yy^k_j$.  The discretization points are
-initially distributed evenly in arclength, and this equispacing is
-maintained for the entire simulation by using a {\thL}
-formulation~\cite{hou-low-she1994}.  In addition, we apply mild
-smoothing strategies~\cite{qua-moo2018} to avoid the corners that
-erosion inevitably develop.
-
-Given these discretization points, the velocity at $\xx$ can be
-approximated with the quadrature formula
-\begin{align}
-  \label{eqn:trap}
-  \uu(\xx) \approx \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j,
-\end{align}
-$w^k_j$ are quadrature weights (which depend on $N_\iin$, $N_\out$, and
-the lengths of $\gamma^k$), and $D$ is the kernel of the Stokes
-double-layer potential defined in Equation~\eqref{eqn:stokesDLP}.
-Matching the limiting behavior of the velocity with the boundary
-condition, the density function at the quadrature point solves
-\begin{align}
+with $N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ and
+$\gamma_k$ are denoted by $\yy_j^0$ and $\yy^k_j$, respectively.  The
+discretization points are initially distributed evenly in arclength, and
+this equispacing is maintained for the entire simulation by using the
+{\thL} formulation.  In addition, we apply mild smoothing
+strategies~\cite{qua-moo2018} to avoid the corners that erosion
+inevitably develop.
+
+Given the discretization points of $\bd\Omega$, applying the trapezoid
+rule results in the collocation method for~\eqref{eqn:BIE} 
+\begin{subequations}
+\label{eqn:trapLinearSystem}
+  \begin{alignat}{3}
   \UU_\ell &= \sum_{j=1}^{N_\out} 
@@
   \sum_{k=1}^M \sum_{j=1}^{N_\iin}
-    w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j, 
-    \quad \ell = 1,\ldots,N_\out \\
-  0 &= \sum_{j=1}^{N_\out} 
+    w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j +
+  \sum_{j=1}^{N_\out} w^0_j N_0(\yy^0_\ell,\yy^0_j) \nonumber \\
+  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^0_\ell) + 
+  \sum_{k=1}^M R[\xi_k,\cc_k](\yy^0_\ell),
+    &&\hspace{-30pt} \ell = 1,\ldots,N_\out, \\
+%
+  \mathbf{0} &= \sum_{j=1}^{N_\out} 
     w^0_j D(\yy^m_\ell,\yy^0_j) \eeta_j +
   \sum_{k=1}^M \sum_{j=1}^{N_\iin}
-    w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j, 
-    \quad \ell = 1,\ldots,N_\iin, \: m=1,\ldots,M. 
-\end{align}
-
-Once the density function is found at the quadrature points, the shear
-stress and vorticity can be approximated.  In particular,
-the deformation tensor is
-\begin{align}
-  \ssigma(\xx) = \frac{1}{2}(\nabla \uu + \nabla \uu^T) = 
-\end{align}
-and the vorticity is
-\begin{align}
-  w(\xx) = 
-\end{align}
-
-The choice of the quadrature rule determines the overall accuracy of the
-method.  To simulate dense suspensions of eroding bodies, it is
-imperative that the error of the chosen quadrature rule is bounded for
-independent of the configuration of the bodies.  To achieve this goal,
-we apply a Barycentric quadrature rule
+    w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j \nonumber \\
+  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^m_\ell) + 
+  \sum_{k=1}^M R[\xi_k,\cc_k](\yy^m_\ell),
+    &&\hspace{-30pt}\ell = 1,\ldots,N_\iin, \: m=1,\ldots,M, \\
+%
+  \llambda_m &= \frac{1}{2\pi} \sum_{j=1}^{N_\iin} \eeta^m_j,  \quad
+  \xi_m = \frac{1}{2\pi} \sum_{j=1}^{N_\iin}
+    (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
+    &&\hspace{-30pt} m=1,\ldots,M,
+\end{alignat}
+\end{subequations}
+where $w^k_j$ are quadrature weights (which depend on $N_\iin$,
+$N_\out$, and the lengths of $\gamma^k$), and $D$ is the kernel of the
+Stokes double-layer potential defined in
+Equation~\eqref{eqn:velocityDLP}.  The linear
+system~\eqref{eqn:trapLinearSystem} is a well-conditioned second-kind
+integral equation that is solved iteratively with GMRES.  If the number
+of discretization points is sufficiently large, then the solution
+of~\eqref{eqn:trapLinearSystem} is an accurate approximation of the
+density function, Stokeslets, and rotlets.   Then, if $\xx \in \Omega$
+is sufficiently far from $\bd\Omega$, an approximation of the velocity,
+deformation tensor, and vorticity due to the double-layer potential is
+found by applying the trapezoid rule to \eqref{eqn:velocityDLP},
+\eqref{eqn:deformationDLP}, and~\eqref{eqn:vorticityDLP}, respectively.
+In particular,
+\begin{align}
+  \label{eqn:trap}
+  \uu(\xx) &= \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j, \\
+%
+  \ssigma(\xx) &= \sum_{j=1}^{N_\out} w^0_j \mathbf{D}_\ssigma(\xx,\yy^0_j) \eeta_j +
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j \mathbf{D}_\ssigma(\xx,\yy^k_j)
+  \eeta^k_j, \\
+%
+  w(\xx) &= \sum_{j=1}^{N_\out} w^0_j D_\omega(\xx,\yy^0_j) \eeta_j +
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D_\omega(\xx,\yy^k_j)
+  \eeta^k_j.
+\end{align}
+The contributions due to the Stokeslets and rotlets require no
+quadrature and are easily included in the velocity, deformation tensor,
+and vorticity.  Finally, to compute the shear stress, we apply the
+trapezoid rule with Fourier differentiation to approximate the jump
+term~\eqref{eqn:deformationJump} of the deformation tensor, and then the
+tensor is applied to the normal and tangent vectors as defined in
+equation~\eqref{eqn:shearStress}.
+
+Once the velocity is computed in $\Omega$, the tortuosity can be
+computed with the Eulerian velocity field~\eqref{eqn:tortuosity2}.  We
+first compute the velocity at $\xx_{ij} = (-1 + i\Delta x, -1 + j\Delta
+y)$, $i,j=1,\ldots,N$, where $\Delta x = \Delta y = 2/N$, and the
+velocity at points inside an eroding body are assigned a value of 0.
+Then, the tortuosity is approximated as
+\begin{align}
+  T = \frac{\sum\limits_{i,j=1}^N \|\uu(\xx_{ij})\|\Delta x \Delta y}
+      {\sum\limits_{i,j=1}^N u_x(\xx_{ij}) \Delta x \Delta y}.
+\end{align}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo[inline]{Dump of text}
-Having developed numerically accurate methods to compute the velocity
-$\uu$ at points close to the bodies, we are able to compute the
-trajectories of particles passing through an eroded body.  Since the
-trajectories are computed with high-order methods in both space and
-time,  we are able to simulate dynamics very close to the eroding bodies
-(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
-
-We have shown that the velocity, shear stress, and vorticity of the
-double-layer representation can all be written in terms of Cauchy
-integrals and its first two derivatives.  Therefore, we require
-quadrature methods to evaluate the expressions in
-equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
-periodic, the trapezoid rule has spectral accuracy.  However, the
-integrand becomes nearly singular as $x$ approaches $\bd\Omega$, and the
-quadrature error is arbitrarily large at a fixed resolution.  There have
-been a variety of near-singular integration schemes developed.   We opt
-to use a method first outlined by Barnett et al.~\cite{bar-wu-vee2015}
-which we call the {\em Barycentric quadrature rule}.  Quadrature rules
-for only the Cauchy integral and its first derivative are presented, and
-we extend this result to include the second derivative.
-\todo[inline]{Dump of text}
-
-Equations~\eqref{eqn:cauchyVelocity} and~\eqref{eqn:cauchyGradient} show
-that computing the Stokes velocity, shear stress, and vorticity hinge on
-accurate quadrature methods for the Cauchy integral and its first two
-derivatives as defined in equation~\eqref{eqn:cauchy}.  Even though the
-trapezoid rule is spectrally accurate for a fixed $x \in
-\Omega$~\cite{tre-wei2014}, its error depends on bounds of the
-derivative of the integrand.  Therefore for a fixed resolution, as $x$
-approaches $\bd\Omega$, causing the integrands to become more singular,
-the error grows without bound.  Ioakimidis et al.~\cite{ioa-pap-per1991}
-developed quadrature methods to compute Cauchy integrals and their
-derivatives with an error bound that is independent of $x$.  Then,
-Barnett et al.~\cite{bar-wu-vee2015} applied these quadratur emethods to
-compute the Stokes double-layer potential representation of the
-velocity~\eqref{eqn:stokesDLP}.  To compute the shear stress and
-vorticity with the same accuracy, we extend the method by using
-Barycentric quadrature methods for the second derivative of a Cauchy
-integral.
+Since the error of the trapezoid rule applied to periodic functions
+depends on the derivative of the integrand~\cite{tre-wei2014}, the
+trapezoid rule applied in Section~\ref{sec:spatialDiscretization} is
+only appropriate if the target point is sufficiently separated from all
+eroding bodies and the outer wall.  Therefore, if the trapezoid rule is
+applied when bodies are in near-contact, or when a layer potential is
+evaluated at a point close to $\bd\Omega$, then the results become
+unreliable and ultimately unusable.  Hence, we require a quadrature
+method whose error is bounded independent of the target location.
+
+We showed in Sections~\ref{sec:DLPcomplex} and
+Section~\ref{sec:gradDLPcomplex} that the velocity, shear stress, and
+vorticity of the double-layer representation can all be written in terms
+of Cauchy integrals and its first two derivatives.  Therefore, if we
+develop quadrature rules with a uniformly bounded error for Cauchy
+integrals and its derivatives~\eqref{eqn:cauchy}, then the quadrature
+method can be used to accurately compute the velocity, shear stress, and
+vorticity.  Ioakimidis et al.~\cite{ioa-pap-per1991} developed
+quadrature methods, that we call {\em Barycentric quadrature rules}, to
+compute Cauchy integrals and their derivatives with an error bound that
+is independent of $x$.  Then, Barnett et al.~\cite{bar-wu-vee2015}
+applied these quadrature methods to compute the Stokes double-layer
+potential representation of the velocity~\eqref{eqn:velocityDLP}.  We
+build on this method so that the shear stress and vorticity can be
+computed with a uniform error bound.
 
 We briefly summarize the Baryncentric quadrature method for computing
-the velocity~\cite{bar-wu-vee2015}.  Then, we apply additional
-quadrature methods to compute the gradient of the velocity so that we
-can simulate erosion.  We present the quadrature for a simply-connected
-interior domain $\Omega$, and we consider the target points $x \in
-\Omega$ and $x \in \Omega^c$. Then, the method naturally extends to the
-eroding geometry by applying the quadrature to each of its connected
-component.  The method starts with an underlying quadrature rule, and we
-use the spectrally accurate trapezoid rule.  Since the quadrature points
-are uniformly distributed, the quadrature weights are $w_j = L/N$,
-$j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
-
-Again, given a density function $\tau$, the boundary data of $v$ as
-defined in equation~\eqref{eqn:laplaceComplex} can be found by applying
-the Sokhotski-Plemelj jump relation~\eqref{eqn:SPrelation}.  The
-boundary data differs if we are considering the interior problem ($x \in
-\Omega$) or the exterior problem ($x \in \Omega^c$).  Therfore, for the
-boundary data we use the notation $v^-$ for the interior problem and
-$v^+$ for the exterior problem.  Rather than directly applying the
+the velocity~\cite{bar-wu-vee2015}.  Then, so that we can simulate and
+visualize erosion, we apply similar techniques to compute Barycentric
+quadrature rules for the gradient of the velocity.  We present the
+quadrature for a simply-connected interior domain $\Omega$, and we
+consider the target points $x \in \Omega$ and $x \in \Omega^c$. Then,
+the method naturally extends to the eroding geometry by applying the
+quadrature to each of its connected component.  The method starts with
+an underlying quadrature rule, and we use the spectrally accurate
+trapezoid rule.  Since the quadrature points are uniformly distributed,
+the quadrature weights are $w_j = L/N$, $j=1,\ldots,N$, where $L$ is the
+length of $\bd\Omega$.
+
+Again, given a density function $\eta$, the boundary data of
+$v[\eta](\xx)$, as defined in equation~\eqref{eqn:laplaceComplex},
+satisfies the Sokhotski-Plemelj jump relation~\eqref{eqn:SPrelation}.
+Since the boundary data of $v$ differs when considering $x \in \Omega$
+and $x \in \Omega^c$, we denote the boundary data as $v^-$ for $x \in
+\Omega$, and as $v^+$ otherwise.  Rather than directly applying the
 trapezoid rule to $v(x)$, we start with the identity
@@
   \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
+    \quad x \in \Omega,
 \end{align}
@@
 and the error is independent of $x$.  Rearranging for $v(x)$, we have
-the interior Barycentric quadrature formula 
+the interior Barycentric quadrature rule
 \begin{align}
@@
 \end{align}
-and the integrand is bounded for all $x \in \Omega$.  Therefore, upon
-applying the quadrature rule and rearranging for $v'(x)$, we have the
+and the integrand is bounded for all $x \in \Omega$.  Therefore, after
+applying the trapezoid rule and rearranging for $v'(x)$, we have the
 interior Barycentric quadrature rule
@@
 Note that the value $v(x)$ is required to compute $v'(x)$ for both the
-interior and exterior case.  These are computed using the quadrature
-methods in equations~\eqref{eqn:BaryvInterior}
-and~\eqref{eqn:BaryvExterior}.
+interior and exterior case, and these are available using the quadrature
+rules~\eqref{eqn:BaryvInterior} and~\eqref{eqn:BaryvExterior}.
 
 To compute the shear stress and vorticity, we require a Barycentric
-quadrature rule for $v''(x)$.  Following the work of Ioakimidis et
-al~\cite{ioa-pap-per1991} (see equation (2.12)), we mimick the
-construction of the quadrature rule for $v(x)$ and $v'(x)$. We start
-with the second derivative of the Cauchy integral theorem
+quadrature rule for $v''(x)$.  The derivation is largely based on the
+work of Ioakimidis et al.~\cite{ioa-pap-per1991} (see equation (2.12)).
+We start with the second derivative of the Cauchy integral theorem
 \begin{align}
@@
 and solving for $v''(x)$, we have the Barycentric quadrature rule for
-the exterior second derivate
+the exterior second derivative
 \begin{align}
@@
 \end{align}
-Similar to the quadrature rule for $v'(x)$ requring the value $v(x)$,
+Similar to the quadrature rule for $v'(x)$ requiring the value $v(x)$,
 the quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$.
@@
 directly, it requires $\mathcal{O}(N^2)$ operations.  By using a fast
-algorithm such as the fast multipole method~\cite{gre-rok1987}, this
-cost can be reduced to $\mathcal{O}(N)$ operations.  However, the
-Barycentric quadrature formulas require several $N$-body calculations
-which we would like to avoid.  Instead, we use a hybrid method where the
-fast multipole accelerate trapezoid rule is used to compute the velocity
-at most of the discretization points, and the non-accelerated
-Barycentric quadrature rule is used to locally correct the trapezoid
-rule.
+summation method, such as the fast multipole method~\cite{gre-rok1987},
+this cost can be reduced to $\mathcal{O}(N)$ operations.  However, the
+Barycentric quadrature formulas require several $N$-body calculations,
+and they must be done for each component of $\bd\Omega$ individually.
+The resulting cost would be prohibitive, so we use a hybrid method that
+combines the Barycentric quadrature rules and the trapezoid rule.  In
+short, the fast multipole accelerated trapezoid rule is used to compute
+the velocity at most of the discretization points, and the
+non-accelerated Barycentric quadrature rule is used to locally correct
+the trapezoid rule.
 
@@
 where $\Delta y = 2/(N_p + 1)$ and $y_i = -1 + i \Delta y$,
-$i=1,\ldots,N_p$.  Alternatively, to compute the tortuosity in terms of
-the Eulerian velocity field, we first compute the velocity at $(x_i,y_j)
-= (-1 + i\Delta x, -1 + j\Delta y)$, $i,j=1,\ldots,N$, where $\Delta x =
-\Delta y = 2/N$, and the velocity at points inside an eroding body are
-assigned a value of 0.  Then, the tortuosity is approximated as
-\begin{align}
-  T = \frac{\sum\limits_{i,j=1}^N \|\uu(x_i,y_j)\|\Delta x \Delta y}
-      {\sum\limits_{i,j=1}^N u_x(x_i,y_j) \Delta x \Delta y}.
-\end{align}
+$i=1,\ldots,N_p$.
+
+Having developed numerically accurate methods to compute the velocity
+$\uu$ at points close to the bodies, we are able to compute the
+trajectories of particles passing through an eroded body.  Since the
+trajectories are computed with high-order methods in both space and
+time,  we are able to simulate dynamics very close to the eroding bodies
+(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
+
 \todo[inline]{Dump of text}

### 2019-08-23 docs/transport/erosion_transport.tex
working on section 5

@@
   \sum_{k=1}^M R[\xi_k,\cc_k](\yy^0_\ell),
-    &&\hspace{-30pt} \ell = 1,\ldots,N_\out, \\
+    &&\hspace{-60pt} \ell = 1,\ldots,N_\out, \\
 %
@@
   \sum_{k=1}^M R[\xi_k,\cc_k](\yy^m_\ell),
-    &&\hspace{-30pt}\ell = 1,\ldots,N_\iin, \: m=1,\ldots,M, \\
+    &&\hspace{-60pt}\ell = 1,\ldots,N_\iin, \: m=1,\ldots,M, \\
 %
@@
     (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
-    &&\hspace{-30pt} m=1,\ldots,M,
+    &&\hspace{-60pt} m=1,\ldots,M,
 \end{alignat}
@@
 non-accelerated Barycentric quadrature rule is used to locally correct
-the trapezoid rule.
-
-We start by using the trapezoid rule~\eqref{eqn:trap} accelerated with
-the FMM, which requires $\mathcal{O}(N)$ operations, and we call this
-velocity $\vv_\trap(\xx)$.  For target points that are sufficiently far
-from $\bd\Omega$, $\vv_\trap(\xx)$ is sufficiently accurate.  However,
-if $\xx$ is sufficiently close to one of the eroding bodies $\gamma_k$,
-or the outer wall $\Gamma$, the velocity contribution from that
-particular component of $\bd\Omega$ is inaccurate and it must be
-corrected.  Assuming that $\xx$ is too close to $\gamma_k$, we first
-subtract the velocity contribution of $\vv(\xx)$ due to $\gamma_k$.
-Then, the Barycentric quadrature rule is used to compute the velocity
-due to $\gamma_k$ with more accuracy.  That is, the final velocity is
+the trapezoid rule.  Note that for the source points of the layer
+potential is always one of the eroding bodies or the outer wall, but the
+target point can either be on another component of $\bd\Omega$ or it can
+be in the fluid bulk $\Omega$.
+
+To compute the velocity double-layer potential, we start by applying the
+trapezoid rule~\eqref{eqn:trap} accelerated with the FMM.  This
+calculation requires $\mathcal{O}(N)$ operations, and we call the
+resulting velocity $\vv_\trap(\xx)$.  Depending on the number of
+discretization points $N_\iin$ and $N_\out$, there is a region separated
+from $\bd\Omega$ where the error of $\vv_\trap(\xx)$ is less than a
+user-specified tolerance.  However, for the other points in $\Omega$,
+the trapezoid rule needs to be replaced with a more accurate quadrature
+rule.  Note, however, that since a point is typically only close to one
+or two components of $\bd\Omega$, only the contribution of these nearby
+bodies need to be replaced.  Assuming that $\xx$ is too close to
+$\gamma_k$, we first subtract the inaccurate approximation of the
+double-layer potential due to $\gamma_k$.  Then, the Barycentric
+quadrature rule is used to compute the velocity due to $\gamma_k$ with
+more accuracy.  That is, the final velocity is
 \begin{align}
@@
 where $\vv^k_\bary(\xx)$ is the velocity at $\xx$ resulting from
-applying the Barycentric quadrature rule due to $\gamma_k$.  This
-strategy naturally extends to points that are close to $\Gamma$, and to
-the scenario when $\xx$ is simultaneously close to multiple components
-of $\bd\Omega$.  While the term $\vv_\trap(\xx)$ in
-equation~\eqref{eqn:velocityDecomp} is computed for all target points
-using the FMM, the other two terms are computed with a direct summation.
-However, these terms are only required for target points near an eroding
-body or the outer wall, and the number of such points is much less than
-$N$.  An identical quadrature method is used to compute the vorticity
-and shear stress.  That is, these quantities are computed using the
-trapezoid rule, and then updates due to inaccuracies of the trapezoid
-rule are made.  However, since the shear stress and vorticity are only
-computed once per time step, the trapezoid rule is applied with a direct
-summation rather than the FMM.  Relative to the cost of applying GMRES
-with the FMM, the additional once-per-time-step cost is minimal.
-
-Per grid point, evaluating the Barycentric quadrature rules dominates
-the computational cost. Therefore, it is imperative that we only apply
-the Barycentric quadrature when the trapezoid rule is inaccurate.  As a
-rule of thumb, the trapezoid rule due to $\gamma_k$ is
-accurate~\cite{bar2014} if
+applying the Barycentric quadrature rule to the double-layer potential
+due to $\gamma_k$.  This strategy naturally extends to points that are
+close to $\Gamma$, and to the scenario when $\xx$ is simultaneously
+close to multiple components of $\bd\Omega$.  While the term
+$\vv_\trap(\xx)$ in equation~\eqref{eqn:velocityDecomp} is computed for
+all target points using the FMM, the other two terms are computed with a
+direct summation.  However, these terms are only required for target
+points near an eroding body or the outer wall, and these points make up
+only a small fraction of the total number of points.
+
+An identical strategy is used to compute the vorticity and the
+deformation tensor.  That is, the trapezoid rule is used as a first pass
+to form the vorticity and deformation tensor, and then local corrections
+are made to replace the inaccuracies of the trapezoid rule.  However,
+since the shear stress and vorticity are only computed once per time
+step, the trapezoid rule is applied with a direct summation rather than
+the FMM.  Relative to the cost of computing the velocity at each
+iteration of GMRES with the FMM, the additional once-per-time-step cost
+to compute the vorticity and deformation tensor is minimal.
+
+Per grid point, applying the Barycentric quadrature rules dominates the
+computational cost. Therefore, it is imperative that we only apply the
+Barycentric quadrature when the trapezoid rule is inaccurate.  As a rule
+of thumb, the trapezoid rule due to $\gamma_k$ achieves machine epsilon
+accuracy if~\cite{bar2014}
 \begin{align}
@@
 First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
-lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
-if
+lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we check if
 \begin{align}
@@
 To determine if points on $\gamma_i$ are too close to the outer wall, we
-use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
-and that the bodies are all contained in $[-1,1] \times [-1,1]$.  We
+recall that the outer wall is bounded in $[-3,3] \times [-1,1]$, and
+that the bodies are all contained in $[-1,1] \times [-1,1]$.  Therefore,
+a target point can only be too close to the lines $y = \pm 1$, so we
 first check if
@@
     \right]
-  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out}
-\end{align}
+  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out},
+\end{align}
+\todo[inline]{Bryan is here}
 where $x_i$ is the x coordinate of $\cc_i$. If body $\gamma_i$ satisfies

### 2019-08-23 docs/transport/erosion_transport.tex
add new figures in transport paper

--- 2019-08-23 docs/transport/erosion_transport.tex
@@
 vorticity.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b1}
+\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b80}
+\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b160}\\
+\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b240}
+\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b320}
+%\includegraphics[width = 0.37 \textwidth]{./figs/vort_50b160}
+\caption{\label{fig:Eroding50vort} Erosion of 50 nearly touching
+bodies with the fixed pressure drop condition. The color is the
+vorticity of the fluid. The 6 snapshots are evenly spaced in time.}
+\end{center}
+\end{figure}
 
@@
     \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
-  \label{eqn:velocityDLP}
+  \label{eqn:stokesDLP}
 \end{align}
@@
   S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
-    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2}
-    \right)\llambda_\ell, \quad
+    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \quad
   R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
@@
 where the density function, Stokeslets, and rotlets satisfy
-\begin{subequations}
-\label{eqn:BIE}
 \begin{align}
@@
 \end{align}
-\end{subequations}
-The operator $\NN_0$ is the integral operator with kernel
-$N_(0)(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$,
-which removes the rank one null space resulting from the flux-free
-requirement of $\ff$.  In this work, $\ff$ is the prescribed velocity,
-$\UU$, on the outer wall, $\Gamma$, and is zero on the eroding bodies,
-$\gamma_\ell$, $\ell=1,\ldots,M$.
+The operator $\NN_0$ is the integral operator with kernel $\nn(\xx)
+\otimes \nn(\yy)$, $\xx,\yy \in \Gamma$, which removes the rank one null
+space resulting from the flux-free requirement of $\ff$.  In this work,
+$\ff$ is the prescribed velocity, $\UU$, on the outer wall, $\Gamma$,
+and is zero on the eroding bodies, $\gamma_\ell$, $\ell=1,\ldots,M$.
 
@@
 rotlets.  For $\xx \in \Omega$, the deformation tensor, pressure, and
-vorticity of the double-layer potential~\eqref{eqn:velocityDLP} are
+vorticity of the double-layer potential~\eqref{eqn:stokesDLP} are
 \begin{align}
   \label{eqn:deformationDLP} 
-  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
-      \eeta(\yy) ds_{\yy} 
-  = \frac{1}{2\pi}\int_{\bd\Omega} \left(
+  \ssigma^\DD(\xx) &= \frac{1}{2\pi}\int_{\bd\Omega} \left(
     2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
@@
     \right. \nonumber \\
-    & \qquad\qquad\qquad\qquad\qquad\qquad \left.
+    & \qquad\qquad \left.
     +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
@@
     \right) \, ds_\yy, \\
-%
-  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
-      \eeta(\yy) ds_{\yy} 
-  = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+  p^\DD(\xx) &= -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
       \eeta(\yy)\,ds_\yy, \\
-%
-  \label{eqn:vorticityDLP} 
-  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
-      \eeta(\yy) ds_{\yy} 
-  = -\frac{1}{\pi} \int_{\bd\Omega}
+  \omega^\DD(\xx) &= -\frac{1}{\pi} \int_{\bd\Omega}
     \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
@@
   \right],
-  \label{eqn:deformationJump}
-\end{align}
-must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
+  \label{eqn:defJump}
+\end{align}
+must be added to $\ssigma^\DD(\xx)$ for $\xx \in \gamma$.  Finally, the
 Stokeslets and rotlets do not have any jumps on $\gamma$, so the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In equations~\eqref{eqn:velocityDLP} and~\eqref{eqn:deformationDLP},
-$\uu$ and its deformation tensor are written as a contour integral in
-$\RR^2$.  However, so that we can apply a particular quadrature method,
-we need to write these layer potentials in terms of Cauchy integrals in
-$\CC$ and their derivatives.  The first step is to write the Laplace
-double-layer potential as the complex integral
+In equations~\eqref{eqn:stokesDLP} and~\eqref{eqn:deformationDLP}, $\uu$
+and its deformation tensor are written as a contour integral in $\RR^2$.
+However, so that we can apply a particular quadrature method, we need to
+write these layer potentials in terms of Cauchy integrals in $\CC$ and
+their derivatives.  The first step is to write the Laplace double-layer potential as the complex integral
 \begin{align}
@@
 
-To rewrite the Stokes double-layer potential~\eqref{eqn:velocityDLP} in
+To rewrite the Stokes double-layer potential~\eqref{eqn:stokesDLP} in
 terms of Cauchy integrals and their derivatives, we write it in terms of
@@
 Double-Layer Potential}
-\label{sec:gradDLPcomplex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The same expressions are used to compute the deformation tensor for $x
-\in \bd\Omega$, except that the jump
-condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
-the shear stress, the deformation tensor on $\bd\Omega$ is applied to
-the normal and tangent vectors as defined in
-equation~\eqref{eqn:shearStress}.
+\in \bd\Omega$, except that the jump condition~\eqref{eqn:defJump} is
+included.  Finally, to compute the shear stress, the deformation tensor
+on $\bd\Omega$ is applied to the normal and tangent vectors as defined
+in equation~\eqref{eqn:shearStress}.
 
@@
 fluids~\cite{hig1985}, but they are very small in the examples we
-consider and have a negligible effect on the tortuosity.  Since
+consider and have a negligible effect on the tortuosity (for example,
+see Figure~\ref{fig:Eroding20tort_all}).  Since
 equation~\eqref{eqn:tortuosity2} does not require the additional work of
 computing particle trajectories at every time step, we use this
-definition for the majority of the tortuosity calculations.  However, we
-do compare the two formulas for the tortuosity at several time steps in
-Section~\ref{sec:results}.
+definition for the majority of the tortuosity calculations.
 
@@
 In line with our previous work~\cite{qua-moo2018}, we use two meshes to
-simulate erosion. The integral equation is solved by discretizing the
-boundary of the geometry at a set of points distributed equally in
-arclength, and then applying a collocation method
-(Section~\ref{sec:spatialDiscretization}).  The quadrature rule is
-either the trapezoid rule or the Barycentric quadrature rule
-(Section~\ref{sec:bary}).  The selection algorithm that determines which
-quadrature method is applied is described in Section~\ref{sec:fmm}.
-Once the shear stress is computed, the bodies are eroded a single time
-step by using a {\thL} discretization~\cite{hou-low-she1994}.  By using
-a {\thL} formulation, the stiff curvature term is linear and the
-discretization points remain equispaced in arclength.  Finally, time
-stepping methods for the eroding bodies and passive particles are
-described in Section~\ref{sec:time}
+simulate erosion.   The integral equation is solved with a collocation
+method (Section~\ref{sec:spatialDiscretization}).  Depending on the
+proximity of the target and source points, either the trapezoid rule or
+the Barycentric quadrature rule (Section~\ref{sec:bary}) is applied.  A
+selection algorithm that determines which quadrature method is applied
+is described in Section~\ref{sec:fmm}.  Once the shear stress is
+computed, the bodies are converted to a {\thL}
+framework~\cite{hou-low-she1994}.  Then, the erosion model is integrated
+forward a single time step.  By using a {\thL} formulation, the stiff
+curvature term is linear and the discretization points remain equispaced
+in arclength.
 
@@
 the one-dimensional boundary of the domain.  Therefore, we easily
-resolve complex geometries, and differentiation is performed with
+resolve complex geometries, and differentiation can be performed with
 spectral accuracy in Fourier space.  We discretize each eroding body
 $\gamma_k$ with $N_\iin$ points and discretize the outer wall $\Gamma$
-with $N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ and
-$\gamma_k$ are denoted by $\yy_j^0$ and $\yy^k_j$, respectively.  The
-discretization points are initially distributed evenly in arclength, and
-this equispacing is maintained for the entire simulation by using the
-{\thL} formulation.  In addition, we apply mild smoothing
-strategies~\cite{qua-moo2018} to avoid the corners that erosion
-inevitably develop.
-
-Given the discretization points of $\bd\Omega$, applying the trapezoid
-rule results in the collocation method for~\eqref{eqn:BIE} 
-\begin{subequations}
-\label{eqn:trapLinearSystem}
-  \begin{alignat}{3}
+with $N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ is
+denoted by $\yy_j^0$, and the $j^{th}$ discretization point on
+$\gamma_k$ is denoted by $\yy^k_j$.  The discretization points are
+initially distributed evenly in arclength, and this equispacing is
+maintained for the entire simulation by using a {\thL}
+formulation~\cite{hou-low-she1994}.  In addition, we apply mild
+smoothing strategies~\cite{qua-moo2018} to avoid the corners that
+erosion inevitably develop.
+
+Given these discretization points, the velocity at $\xx$ can be
+approximated with the quadrature formula
+\begin{align}
+  \label{eqn:trap}
+  \uu(\xx) \approx \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j,
+\end{align}
+$w^k_j$ are quadrature weights (which depend on $N_\iin$, $N_\out$, and
+the lengths of $\gamma^k$), and $D$ is the kernel of the Stokes
+double-layer potential defined in Equation~\eqref{eqn:stokesDLP}.
+Matching the limiting behavior of the velocity with the boundary
+condition, the density function at the quadrature point solves
+\begin{align}
   \UU_\ell &= \sum_{j=1}^{N_\out} 
@@
   \sum_{k=1}^M \sum_{j=1}^{N_\iin}
-    w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j +
-  \sum_{j=1}^{N_\out} w^0_j N_0(\yy^0_\ell,\yy^0_j) \nonumber \\
-  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^0_\ell) + 
-  \sum_{k=1}^M R[\xi_k,\cc_k](\yy^0_\ell),
-    &&\hspace{-30pt} \ell = 1,\ldots,N_\out, \\
-%
-  \mathbf{0} &= \sum_{j=1}^{N_\out} 
+    w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j, 
+    \quad \ell = 1,\ldots,N_\out \\
+  0 &= \sum_{j=1}^{N_\out} 
     w^0_j D(\yy^m_\ell,\yy^0_j) \eeta_j +
   \sum_{k=1}^M \sum_{j=1}^{N_\iin} 
-    w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j \nonumber \\
-  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^m_\ell) + 
-  \sum_{k=1}^M R[\xi_k,\cc_k](\yy^m_\ell),
-    &&\hspace{-30pt}\ell = 1,\ldots,N_\iin, \: m=1,\ldots,M, \\
-%
-  \llambda_m &= \frac{1}{2\pi} \sum_{j=1}^{N_\iin} \eeta^m_j,  \quad
-  \xi_m = \frac{1}{2\pi} \sum_{j=1}^{N_\iin}
-    (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
-    &&\hspace{-30pt} m=1,\ldots,M,
-\end{alignat}
-\end{subequations}
-where $w^k_j$ are quadrature weights (which depend on $N_\iin$,
-$N_\out$, and the lengths of $\gamma^k$), and $D$ is the kernel of the
-Stokes double-layer potential defined in
-Equation~\eqref{eqn:velocityDLP}.  The linear
-system~\eqref{eqn:trapLinearSystem} is a well-conditioned second-kind
-integral equation that is solved iteratively with GMRES.  If the number
-of discretization points is sufficiently large, then the solution
-of~\eqref{eqn:trapLinearSystem} is an accurate approximation of the
-density function, Stokeslets, and rotlets.   Then, if $\xx \in \Omega$
-is sufficiently far from $\bd\Omega$, an approximation of the velocity,
-deformation tensor, and vorticity due to the double-layer potential is
-found by applying the trapezoid rule to \eqref{eqn:velocityDLP},
-\eqref{eqn:deformationDLP}, and~\eqref{eqn:vorticityDLP}, respectively.
-In particular,
-\begin{align}
-  \label{eqn:trap}
-  \uu(\xx) &= \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j, \\
-%
-  \ssigma(\xx) &= \sum_{j=1}^{N_\out} w^0_j \mathbf{D}_\ssigma(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j \mathbf{D}_\ssigma(\xx,\yy^k_j)
-  \eeta^k_j, \\
-%
-  w(\xx) &= \sum_{j=1}^{N_\out} w^0_j D_\omega(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D_\omega(\xx,\yy^k_j)
-  \eeta^k_j.
-\end{align}
-The contributions due to the Stokeslets and rotlets require no
-quadrature and are easily included in the velocity, deformation tensor,
-and vorticity.  Finally, to compute the shear stress, we apply the
-trapezoid rule with Fourier differentiation to approximate the jump
-term~\eqref{eqn:deformationJump} of the deformation tensor, and then the
-tensor is applied to the normal and tangent vectors as defined in
-equation~\eqref{eqn:shearStress}.
-
-Once the velocity is computed in $\Omega$, the tortuosity can be
-computed with the Eulerian velocity field~\eqref{eqn:tortuosity2}.  We
-first compute the velocity at $\xx_{ij} = (-1 + i\Delta x, -1 + j\Delta
-y)$, $i,j=1,\ldots,N$, where $\Delta x = \Delta y = 2/N$, and the
-velocity at points inside an eroding body are assigned a value of 0.
-Then, the tortuosity is approximated as
-\begin{align}
-  T = \frac{\sum\limits_{i,j=1}^N \|\uu(\xx_{ij})\|\Delta x \Delta y}
-      {\sum\limits_{i,j=1}^N u_x(\xx_{ij}) \Delta x \Delta y}.
-\end{align}
+    w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j, 
+    \quad \ell = 1,\ldots,N_\iin, \: m=1,\ldots,M. 
+\end{align}
+
+Once the density function is found at the quadrature points, the shear
+stress and vorticity can be approximated.  In particular,
+the deformation tensor is
+\begin{align}
+  \ssigma(\xx) = \frac{1}{2}(\nabla \uu + \nabla \uu^T) = 
+\end{align}
+and the vorticity is
+\begin{align}
+  w(\xx) = 
+\end{align}
+
+The choice of the quadrature rule determines the overall accuracy of the
+method.  To simulate dense suspensions of eroding bodies, it is
+imperative that the error of the chosen quadrature rule is bounded for
+independent of the configuration of the bodies.  To achieve this goal,
+we apply a Barycentric quadrature rule
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since the error of the trapezoid rule applied to periodic functions
-depends on the derivative of the integrand~\cite{tre-wei2014}, the
-trapezoid rule applied in Section~\ref{sec:spatialDiscretization} is
-only appropriate if the target point is sufficiently separated from all
-eroding bodies and the outer wall.  Therefore, if the trapezoid rule is
-applied when bodies are in near-contact, or when a layer potential is
-evaluated at a point close to $\bd\Omega$, then the results become
-unreliable and ultimately unusable.  Hence, we require a quadrature
-method whose error is bounded independent of the target location.
-
-We showed in Sections~\ref{sec:DLPcomplex} and
-Section~\ref{sec:gradDLPcomplex} that the velocity, shear stress, and
-vorticity of the double-layer representation can all be written in terms
-of Cauchy integrals and its first two derivatives.  Therefore, if we
-develop quadrature rules with a uniformly bounded error for Cauchy
-integrals and its derivatives~\eqref{eqn:cauchy}, then the quadrature
-method can be used to accurately compute the velocity, shear stress, and
-vorticity.  Ioakimidis et al.~\cite{ioa-pap-per1991} developed
-quadrature methods, that we call {\em Barycentric quadrature rules}, to
-compute Cauchy integrals and their derivatives with an error bound that
-is independent of $x$.  Then, Barnett et al.~\cite{bar-wu-vee2015}
-applied these quadrature methods to compute the Stokes double-layer
-potential representation of the velocity~\eqref{eqn:velocityDLP}.  We
-build on this method so that the shear stress and vorticity can be
-computed with a uniform error bound.
+
+\todo[inline]{Dump of text}
+Having developed numerically accurate methods to compute the velocity
+$\uu$ at points close to the bodies, we are able to compute the
+trajectories of particles passing through an eroded body.  Since the
+trajectories are computed with high-order methods in both space and
+time,  we are able to simulate dynamics very close to the eroding bodies
+(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
+
+We have shown that the velocity, shear stress, and vorticity of the
+double-layer representation can all be written in terms of Cauchy
+integrals and its first two derivatives.  Therefore, we require
+quadrature methods to evaluate the expressions in
+equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
+periodic, the trapezoid rule has spectral accuracy.  However, the
+integrand becomes nearly singular as $x$ approaches $\bd\Omega$, and the
+quadrature error is arbitrarily large at a fixed resolution.  There have
+been a variety of near-singular integration schemes developed.   We opt
+to use a method first outlined by Barnett et al.~\cite{bar-wu-vee2015}
+which we call the {\em Barycentric quadrature rule}.  Quadrature rules
+for only the Cauchy integral and its first derivative are presented, and
+we extend this result to include the second derivative.
+\todo[inline]{Dump of text}
+
+Equations~\eqref{eqn:cauchyVelocity} and~\eqref{eqn:cauchyGradient} show
+that computing the Stokes velocity, shear stress, and vorticity hinge on
+accurate quadrature methods for the Cauchy integral and its first two
+derivatives as defined in equation~\eqref{eqn:cauchy}.  Even though the
+trapezoid rule is spectrally accurate for a fixed $x \in
+\Omega$~\cite{tre-wei2014}, its error depends on bounds of the
+derivative of the integrand.  Therefore for a fixed resolution, as $x$
+approaches $\bd\Omega$, causing the integrands to become more singular,
+the error grows without bound.  Ioakimidis et al.~\cite{ioa-pap-per1991}
+developed quadrature methods to compute Cauchy integrals and their
+derivatives with an error bound that is independent of $x$.  Then,
+Barnett et al.~\cite{bar-wu-vee2015} applied these quadratur emethods to
+compute the Stokes double-layer potential representation of the
+velocity~\eqref{eqn:stokesDLP}.  To compute the shear stress and
+vorticity with the same accuracy, we extend the method by using
+Barycentric quadrature methods for the second derivative of a Cauchy
+integral.
 
 We briefly summarize the Baryncentric quadrature method for computing
-the velocity~\cite{bar-wu-vee2015}.  Then, so that we can simulate and
-visualize erosion, we apply similar techniques to compute Barycentric
-quadrature rules for the gradient of the velocity.  We present the
-quadrature for a simply-connected interior domain $\Omega$, and we
-consider the target points $x \in \Omega$ and $x \in \Omega^c$. Then,
-the method naturally extends to the eroding geometry by applying the
-quadrature to each of its connected component.  The method starts with
-an underlying quadrature rule, and we use the spectrally accurate
-trapezoid rule.  Since the quadrature points are uniformly distributed,
-the quadrature weights are $w_j = L/N$, $j=1,\ldots,N$, where $L$ is the
-length of $\bd\Omega$.
-
-Again, given a density function $\eta$, the boundary data of
-$v[\eta](\xx)$, as defined in equation~\eqref{eqn:laplaceComplex},
-satisfies the Sokhotski-Plemelj jump relation~\eqref{eqn:SPrelation}.
-Since the boundary data of $v$ differs when considering $x \in \Omega$
-and $x \in \Omega^c$, we denote the boundary data as $v^-$ for $x \in
-\Omega$, and as $v^+$ otherwise.  Rather than directly applying the
+the velocity~\cite{bar-wu-vee2015}.  Then, we apply additional
+quadrature methods to compute the gradient of the velocity so that we
+can simulate erosion.  We present the quadrature for a simply-connected
+interior domain $\Omega$, and we consider the target points $x \in
+\Omega$ and $x \in \Omega^c$. Then, the method naturally extends to the
+eroding geometry by applying the quadrature to each of its connected
+component.  The method starts with an underlying quadrature rule, and we
+use the spectrally accurate trapezoid rule.  Since the quadrature points
+are uniformly distributed, the quadrature weights are $w_j = L/N$,
+$j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
+
+Again, given a density function $\tau$, the boundary data of $v$ as
+defined in equation~\eqref{eqn:laplaceComplex} can be found by applying
+the Sokhotski-Plemelj jump relation~\eqref{eqn:SPrelation}.  The
+boundary data differs if we are considering the interior problem ($x \in
+\Omega$) or the exterior problem ($x \in \Omega^c$).  Therfore, for the
+boundary data we use the notation $v^-$ for the interior problem and
+$v^+$ for the exterior problem.  Rather than directly applying the
 trapezoid rule to $v(x)$, we start with the identity
@@
   \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
-    \quad x \in \Omega,
 \end{align}
@@
 and the error is independent of $x$.  Rearranging for $v(x)$, we have
-the interior Barycentric quadrature rule
+the interior Barycentric quadrature formula 
 \begin{align}
@@
 \end{align}
-and the integrand is bounded for all $x \in \Omega$.  Therefore, after
-applying the trapezoid rule and rearranging for $v'(x)$, we have the
+and the integrand is bounded for all $x \in \Omega$.  Therefore, upon
+applying the quadrature rule and rearranging for $v'(x)$, we have the
 interior Barycentric quadrature rule
@@
 Note that the value $v(x)$ is required to compute $v'(x)$ for both the
-interior and exterior case, and these are available using the quadrature
-rules~\eqref{eqn:BaryvInterior} and~\eqref{eqn:BaryvExterior}.
+interior and exterior case.  These are computed using the quadrature
+methods in equations~\eqref{eqn:BaryvInterior}
+and~\eqref{eqn:BaryvExterior}.
 
 To compute the shear stress and vorticity, we require a Barycentric
-quadrature rule for $v''(x)$.  The derivation is largely based on the
-work of Ioakimidis et al.~\cite{ioa-pap-per1991} (see equation (2.12)).
-We start with the second derivative of the Cauchy integral theorem
+quadrature rule for $v''(x)$.  Following the work of Ioakimidis et
+al~\cite{ioa-pap-per1991} (see equation (2.12)), we mimick the
+construction of the quadrature rule for $v(x)$ and $v'(x)$. We start
+with the second derivative of the Cauchy integral theorem
 \begin{align}
@@
 and solving for $v''(x)$, we have the Barycentric quadrature rule for
-the exterior second derivative
+the exterior second derivate
 \begin{align}
@@
 \end{align}
-Similar to the quadrature rule for $v'(x)$ requiring the value $v(x)$,
+Similar to the quadrature rule for $v'(x)$ requring the value $v(x)$,
 the quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$.
@@
 directly, it requires $\mathcal{O}(N^2)$ operations.  By using a fast
-summation method, such as the fast multipole method~\cite{gre-rok1987},
-this cost can be reduced to $\mathcal{O}(N)$ operations.  However, the
-Barycentric quadrature formulas require several $N$-body calculations,
-and they must be done for each component of $\bd\Omega$ individually.
-The resulting cost would be prohibitive, so we use a hybrid method that
-combines the Barycentric quadrature rules and the trapezoid rule.  In
-short, the fast multipole accelerated trapezoid rule is used to compute
-the velocity at most of the discretization points, and the
-non-accelerated Barycentric quadrature rule is used to locally correct
-the trapezoid rule.
+algorithm such as the fast multipole method~\cite{gre-rok1987}, this
+cost can be reduced to $\mathcal{O}(N)$ operations.  However, the
+Barycentric quadrature formulas require several $N$-body calculations
+which we would like to avoid.  Instead, we use a hybrid method where the
+fast multipole accelerate trapezoid rule is used to compute the velocity
+at most of the discretization points, and the non-accelerated
+Barycentric quadrature rule is used to locally correct the trapezoid
+rule.
 
@@
 where $\Delta y = 2/(N_p + 1)$ and $y_i = -1 + i \Delta y$,
-$i=1,\ldots,N_p$.
-
-Having developed numerically accurate methods to compute the velocity
-$\uu$ at points close to the bodies, we are able to compute the
-trajectories of particles passing through an eroded body.  Since the
-trajectories are computed with high-order methods in both space and
-time,  we are able to simulate dynamics very close to the eroding bodies
-(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
-
+$i=1,\ldots,N_p$.  Alternatively, to compute the tortuosity in terms of
+the Eulerian velocity field, we first compute the velocity at $(x_i,y_j)
+= (-1 + i\Delta x, -1 + j\Delta y)$, $i,j=1,\ldots,N$, where $\Delta x =
+\Delta y = 2/N$, and the velocity at points inside an eroding body are
+assigned a value of 0.  Then, the tortuosity is approximated as
+\begin{align}
+  T = \frac{\sum\limits_{i,j=1}^N \|\uu(x_i,y_j)\|\Delta x \Delta y}
+      {\sum\limits_{i,j=1}^N u_x(x_i,y_j) \Delta x \Delta y}.
+\end{align}
 \todo[inline]{Dump of text}

### 2019-08-25 docs/transport/erosion_transport.tex
started to go through results section

--- 2019-08-23 docs/transport/erosion_transport.tex
@@
 hym-den-hag-kan2019, cve-che-wen1996}, tortuosity~\cite{hak-com-den2019,
-matyka2008tortuosity, dud-koz-mat2011, kop-kat-tim1996}, concentration
+mat-kha-koz2008, dud-koz-mat2011, kop-kat-tim1996}, concentration
 distributions~\cite{ica-den2019, bel-sal-rin1992}, flow
@@
 porosity, the local tortuosity can be greater than
-1.5~\cite{kop-kat-tim1996, matyka2008tortuosity}, or greater than
+1.5~\cite{kop-kat-tim1996, mat-kha-koz2008}, or greater than
 2~\cite{dud-koz-mat2011}.  The tortuosity of the geometry is defined by
@@
 \subsection{Anomalous Disperision}
+\label{sec:dispersion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align}
+  \label{eqn:moments}
   \langle \lambda \rangle (t) = 
@@
 
-There have been efforts to relate the tortuosity to the
-porosity~\cite{matyka2008tortuosity}.  For example, Matyka et
-al.~\cite{matyka2008tortuosity} propose the models
+There have been efforts to relate the tortuosity to the porosity.  For
+example, Matyka et al.~\cite{mat-kha-koz2008} propose the models
 \begin{subequations}
@@
 To determine if points on $\gamma_i$ are too close to the outer wall, we
-recall that the outer wall is bounded in $[-3,3] \times [-1,1]$, and
-that the bodies are all contained in $[-1,1] \times [-1,1]$.  Therefore,
-a target point can only be too close to the lines $y = \pm 1$, so we
-first check if
+recall that the geometry is contained in a rounded-off version of
+$[-3,3] \times [-1,1]$, and that the bodies are all contained in $[-1,1]
+\times [-1,1]$, so a target point can only be too close to the lines $y
+= \pm 1$. Therefore, we first check if
 \begin{align}
@@
 \end{align}
-\todo[inline]{Bryan is here}
 where $x_i$ is the x coordinate of $\cc_i$. If body $\gamma_i$ satisfies
@@
 \end{align}
-Finally, to determine if a target point $\xx$ that is in the fluid bulk
-rather than on another eroding body requires the Barycentric quadrature
-rule, we only check conditions~\eqref{eqn:PointsBodyCutoff}
+Finally, to determine if a target point $\xx$ in the fluid bulk requires
+the Barycentric quadrature rule, we only check
+conditions~\eqref{eqn:PointsBodyCutoff}
 and~\eqref{eqn:PointsWallCutoff}.
@@
 To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
-we fix a eroded geometry and we compute an accurate solution by using
+we fixed an eroded geometry and computed an accurate solution by using
 the Barycentric quadrature rule for all discretization points.  Then,
-for multiple values of $\alpha_\iin$ and $\alpha_\out$, we compute the
+for multiple values of $\alpha_\iin$ and $\alpha_\out$, we computed the
 velocity field with the trapezoid rule for all points that do not
@@
 of our numerical simulations.
+\todo[inline]{S-H: What kind of accuracy did this give?  This is less
+than the value used by Barnett in his single author quadrature paper.
+He said that 5 arclength spacings is the right amount to guarantee
+machine precision.}
 
@@
 We reuse the time stepping method outlined in our previous
-work~\cite{qua-moo2018}.  Rather than tracking the $(x,y)$ coordinates,
-the {\thL} variables are tracked. In addition, a tangential velocity
-field is added to each body so that the discretization points remain
-equispaced for all time.  A second-order Implicit-Explicit method is
-used. In particular, the diffusive term corresponding to the curvature
+work~\cite{qua-moo2018} which we briefly summarize here.  Rather than
+tracking the $(x,y)$ coordinates, the {\thL} variables are tracked. In
+addition, a tangential velocity field is added to each body so that the
+discretization points remain equispaced in arclength for all time.  A
+second-order Implicit-Explicit Runge-Kutta method is used. In
+particular, the diffusive term corresponding to the curvature
 penalization term is discretized implicitly, and all other terms, which
 are non-stiff, are treated explicitly.  By using this time stepping
-method in conjunction with the curvature penalization and Gaussian
-filter, we stably evolve the eroding bodies.   An in depth description
-of the time stepping method for erosion is in Section 3.3 of our
-previous work~\cite{qua-moo2018}.
-
-In Section~\ref{sec:transport}, we require trajectories of passive
-tracers passing through an eroded geometry.  Given such a geometry
-$\Omega$, a tracer $\ss(t)$ initialized at $\ss_0$ is governed by 
-\begin{align}
-  \label{eqn:trajectories}
-  \frac{d\ss}{dt} = \uu(\ss), \quad \ss(0) = \ss_0.
-\end{align}
-To compute such a trajectory, we apply the standard explicit
-fourth-order Runge-Kutta method.  To evaluate $\uu(\ss)$, depending on
-the proximity of $\ss(t)$ to $\bd\Omega$, we either use the trapezoid
-rule or the Barycentric quadrature rule as described in
-Section~\ref{sec:fmm}.
-
-\todo[inline]{Dump of text}
-The first method to numerically compute the tortuosity uses $N_p$
-trajectories that are initialized at $(-1,y_i)$, $i=1,\ldots,N_p$, and
-stopped when their $x$ coordinate is 1.  We choose $y_i$ so that the
-trajectories are initially uniformly spaced in $(-1,1)$.  Having
-computed these trajectories, the tortuosity is approximated as
+method in conjunction, we stably evolve the eroding bodies.   An in
+depth description of the time stepping method for erosion is in Section
+3.3 of our previous work~\cite{qua-moo2018}.
+
+To compute the tortuosity and the anomalous dispersion rates
+(Section~\ref{sec:transport}), we require trajectories of passive
+tracers, governed by equation~\eqref{eqn:tracers}.  To reliably
+characterize the transport, it is crucial that the trajectories are
+computed accurately.  If a low-order time stepping method is used, or if
+$\uu(\ss(t))$ is inaccurate, then a trajectory $\ss(t)$ can unphysically
+enter a grain, rendering the trajectory meaningless to quantify
+transport.  However, if we simply ignored trajectories that pass close
+to grains, this would considerably skew the characterization of the
+transport. Therefore, we use high-order quadrature and time stepping
+methods.  In particular, depending on the proximity of $\ss(t)$ to
+$\bd\Omega$ (Section~\ref{sec:fmm}, we apply the trapezoid rule or the
+Barycentric quadrature rule.  For time stepping, we use a fourth-order
+explicit Runge-Kutta method.  Since the trajectories are computed with
+high-order methods in both space and time,  we are able to simulate
+dynamics very close to the eroding bodies (see
+Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}).
+
+Once a collection of trajectories are formed, they are used to quantify
+the dispersion and the tortuosity.  The dispersion simply computes the
+second-moment of the trajectories as described in
+equation~\eqref{eqn:moments}.  However, as described in
+Section~\ref{sec:dispersion}, a reinsertion method is used to compute
+trajectories that are sufficiently long to observe an asymptotic
+anomalous dispersion rate.  To compute the tortuosity using the
+trajectories, we consider trajectories crossing between the two
+cross-sections $x=-1$ and $x=1$.  Then, we discretize
+equation~\eqref{eqn:tortuosity1} as
 \begin{align}
@@
 
-Having developed numerically accurate methods to compute the velocity
-$\uu$ at points close to the bodies, we are able to compute the
-trajectories of particles passing through an eroded body.  Since the
-trajectories are computed with high-order methods in both space and
-time,  we are able to simulate dynamics very close to the eroding bodies
-(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
-
-\todo[inline]{Dump of text}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this section, we apply our new quadrature method to simulate erosion
-of several different configurations of eroding bodies.  The fluid domain
-is $\Omega$ whose outer solid walls is a rectangle $[-3,3] \times
-[-1,1]$ with rounded off corners.  We initialize the bodies randomly in
-$[-1,1] \times [-1,1]$ using a randomized method that chooses a random
-center and radii, and then accepts the new body if it is sufficiently
-separated from all other bodies.  Since the error of our quadrature
-method is bounded independent of the geometry, we consider bodies that
-are separated by less than 10\% of an arclength spacing.  For all
-simulations, we discretize $\Gamma = \bd \Omega$ with $N_\out=1024$
+In this section, we apply our new quadrature method to (1) simulate
+erosion of several different configurations of eroding bodies, and (2)
+characterize transport inside eroded geometries.  Each eroding body is
+initially a circle with center $\cc_i$ and radius $r_i$.  The center and
+radius are chosen at random, and the body is accepted as long as it is
+contained in $[-1,1] \times [-1,1]$ and is sufficiently separated from
+all other bodies.  Since the error of our quadrature method is bounded
+independent of the geometry, we consider bodies that are separated by
+less than 10\% of an arclength spacing.  The randomized method is
+repeated until the initial geometry reaches a desired initial porosity.
+
+Once the geometry is initialized, each body has length $L_i = 2\pi r_i$,
+and they are each discretized with $N_\iin$ points.  A no-slip boundary
+condition is imposed on each eroding body $\gamma_i$.  For all
+simulations, we discretize the outer wall $\Gamma$ with $N_\out=1024$
 points.  For all but the first example, the Dirichlet boundary condition
@@
 
-The initial shape of the eroding body $\gamma_i$ is a circle centered at
-$\cc_i$ with radius $r_i$ and length $L_i = 2\pi r_i$, and each
-$\gamma_i$ is discretized with $N_\iin$ points.  A no-slip boundary
-condition is imposed on $\gamma_i$.  The initial configuration is
-constructed with an annealing algorithm and has the desired initial
-porosity, and a user-specified minimum distance between any two eroding
-bodies and the eroding body and solid wall.  To round off inevitable
-corners on the eroding bodies, for all simulations we apply smoothing
-the smoothing parameters $\eps=15/256$ and $\sigma=10/256$, as described
-in~\cite{qua-moo2018}.
+In each of the examples, we include plots of the vorticity in the fluid
+bulk.  Since the vorticity and the shear stress agree on surface of the
+eroding bodies, the vorticity is a useful method to visualize the
+erosion rate.  In particular, the rate of erosion is largest in regions
+where the magnitude of the vorticity is largest.
+
+Because of the definition of the erosion rate, there is a loss of
+regularity, and this inevitably leads to corners developing on the
+eroding bodies.  Therefore, as described in
+Section~\ref{sec:formulation} and our previous work~\cite{qua-moo2018},
+we introduce a curvature penalization term and a Gaussian smoothing
+step.  For all examples, we use the smoothing parameters $\eps=15/256$
+and $\sigma=10/256$.
 
 The common characteristic of each of the experiments is near-contact
-between the eroding bodies and outer walls. Once we have simulated
-erosion, we compute velocities, streamlines, trajectories, and vorticity
-so that the flow can be visualized and analyzed.  The experiments we
-perform are:
+between the eroding bodies, outer walls, and passive tracers. We use our
+numerical methods to describe and visualize the following examples:
 \begin{itemize}
@@
   porosity on the tortuosity and anomalous dispersion rates.
-
-  \item{\bf 50 Bodies at a Low Porosity}: We consider 50 eroding bodies
-  with a low initial porosity.  In addition to the tortuosity and
-  anomalous dispersion rates, we compute distributions of the pore
-  throat sizes and examine their response to erosion.
 
@@
 chosen so that the distance between the body and the solid wall is
-$h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  For all three
+$h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  If we were to use
+the trapezoid rule and require an error that is comparable to the
+Barycentric quadrature rule, the body with an initial distance of $h/10$
+from the solid wall would require $6,400$ discretization points, and the
+outer wall would require $50,000$ discretization points.  For all three
 simulations, we use the time step size $\Delta t=10^{-4}$.
@@
 logarithm of the shear stress.  Since the shear stress is always
-positive, the erosion rate is a smooth function and does not lead to the
-development of corners.  However, the shear stress varies over several
-orders of magnitude, and this leads to interesting shapes.  For
-instance, in the top hemisphere, there is a sudden increase in the shear
-stress, and this leads to a region of high curvature.  This behavior is
-also present in three dimensions~\cite{mit-spa2017} (Figure 7(c)).  The
-biggest difference between the two- and three-dimensional results is the
-presence of a recirculation zone.  In three dimensions, there is no
-recirculation between the solid wall and the spherical
-body~\cite{cha-feu2003}.  In contrast, the two-dimensional flow Stokes
-flow can have recirculation zones~\cite{chw-wu1975, hig1985}. To
-visualize the flow, we plot the vorticity of the final time step from
-Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  The region
-where the vorticity is smallest corresponds to the recirculation region.
+positive, the erosion rate is smooth and corners do not develop.
+However, the shear stress varies over several orders of magnitude, and
+this leads to interesting shapes.  For instance, in the top half of the
+body, there is a sudden increase in the shear stress, and this leads to
+a region of high curvature.  This behavior is also present in three
+dimensions~\cite{mit-spa2017} (Figure 7(c)).  The biggest difference
+between the two- and three-dimensional results is the presence of a
+recirculation zone.  In three dimensions, there is no recirculation
+between the solid wall and the spherical body~\cite{cha-feu2003}.  In
+contrast, the two-dimensional flow Stokes flow can have recirculation
+zones~\cite{chw-wu1975, hig1985}. To visualize the flow, we plot the
+vorticity of the final time step from Figure~\ref{fig:NearWall} in
+Figure~\ref{fig:NearWall_vort}.  The recirculation is present in the
+region where the vorticity is smallest.
 
@@
 \begin{center}
-\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
-\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
-\includegraphics[width = 0.38 \textwidth]{./figs/1b_0d4r0d1h_shear}
-\caption{\label{fig:NearWall} 
-  A single body eroding in a Stokes flow. The color denotes the
-  logarithm of the shear stress on the body. Therefore, erosion is
-  fastest in the red regions (top half)and slowest in the blue regions
-  (lower half).  The body is initialized at three different distances
-  from the lower wall: $d=h$ (left), $h/2$ (middle), and $h/10$
-  (right).}
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics[width = \textwidth]{./figs/1b_0d4r1h_shear}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics[width = \textwidth]{./figs/1b_0d4r0d5h_shear}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.38\textwidth}
+\includegraphics[width =\textwidth]{./figs/1b_0d4r0d1h_shear}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:NearWall} A single body eroding in a Stokes flow.
+The color is the logarithm of the shear stress. Therefore, erosion is
+fastest in the red regions (upper half) and slowest in the blue regions
+(lower half).  The body is initialized at three different distances from
+the lower wall: (a) $d=h$, (b) $h/2$, and (c) $h/10$.}
 \end{center}
@@
 \begin{center}
-\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
-\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
-\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
-\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a single body eroding 
-at time t=0.1001. The initial distances from body to wall are $h$ (left), $h/2$
-  (middle), and $h/10$ (right).  }
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics[width = \textwidth]{./figs/1b_0d4r1h_vort}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics[width = \textwidth]{./figs/1b_0d4r0d5h_vort}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.33\textwidth}
+\includegraphics[width = \textwidth]{./figs/1b_0d4r0d1h_vort}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a
+single body eroding at time t=0.1. The initial distance from the body to
+the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
 \end{center}
@@
 
+\todo[inline]{Bryan is here}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 are initialized at $x=-1$, and their $y$ coordinates are distributed
-evenly across the entire channel.  To compute the tortuosity, we
-require the velocity at the initialization points of the tracers.  These
+evenly across the entire channel.  To compute the tortuosity, we require
+the velocity at the initialization points of the tracers.  These
 normalized velocities are plotted in Figure~ref{fig:Eroding20tort}(a)
@@
   Figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
-work of Matyka et al.~\cite{matyka2008tortuosity} (see Figure 4(a)),
-except that our cross-section does not cut through any of the bodies.
-Next, in Figure~\ref{fig:Eroding20tort}(b), we plot the local
+  work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure 4(a)), except
+  that our cross-section does not cut through any of the bodies.  Next,
+  in Figure~\ref{fig:Eroding20tort}(b), we plot the local
   tortuosity~\eqref{eqn:localTort} by calculating the length of each
@@
   channel is $1.098$.  Again, comparing the local tortuosity to
-Matyka~\cite{matyka2008tortuosity} (Figure 4(b)), the results are
-qualitatively similar. However, since our initial cross-section does not
-cut through any bodies, the local tortuosity does not have any gaps.
-The discontinuities correspond to neighboring tracers with one traveling
-much farther than the other.  In Figure~\ref{fig:Eroding20tort}(c), we
-plot pairs of trajectories that correspond to the ten largest jumps in
-the local tortuosity.  Corresponding pairs are always plotted in the
-same color.  The discrepancy between the trajectory lengths can be
-attributed to the tracers diverging from one another as they approach
-opposite sides of a stagnation point in the flow.
+  Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
+  qualitatively similar. However, since our initial cross-section does
+  not cut through any bodies, the local tortuosity does not have any
+  gaps.  The discontinuities correspond to neighboring tracers with one
+  traveling much farther than the other.  In
+  Figure~\ref{fig:Eroding20tort}(c), we plot pairs of trajectories that
+  correspond to the ten largest jumps in the local tortuosity.
+  Corresponding pairs are always plotted in the same color.  The
+  discrepancy between the trajectory lengths can be attributed to the
+  tracers diverging from one another as they approach opposite sides of
+  a stagnation point in the flow.
 
@@
 \begin{figure}[H]
-%\caption{\label{fig:Eroding20anomalous} The
-%mean squared displacement of the tracer trajectories  at several
-%different stages of the erosion process.  As the porosity increases, the
-%mean squared displacement tends towards $\sigma^2_\lambda(t) \sim t^$
-%}
-%\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
 \center
 \includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long_ref}
-\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
+\caption{\label{fig:Eroding20anomalousMedium} The analysis of anomalous
 dispersion in 20 nearly touching bodies with respect to initial porosity
@@
 best fit (black) using the power law $\widehat{T}(\phi) =
-\phi^{-p}$~\cite{matyka2008tortuosity}.  This model outperformed the
-other three models described in equation~\eqref{eqn:tortuosityModels}.
-The root-mean-squared error of the power law is $1.13 \times 10^{-2}$.
+\phi^{-p}$~\cite{mat-kha-koz2008}.  This model outperformed the other
+three models described in equation~\eqref{eqn:tortuosityModels}.  The
+root-mean-squared error of the power law is $1.13 \times 10^{-2}$.
 
@@
 \includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
-\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
+\caption{\label{fig:Eroding20anomalousLow} The analysis of anomalous
 dispersion in 20 nearly touching bodies with respect to initial porosity
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{50 eroding bodies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\color{red}
-The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
-}
 

### 2019-08-25 docs/transport/erosion_transport.tex
add a new figure in transport paper

@@
 
-Next, we use the 1000 tracer trajectories to compute the first
-(Figure~\ref{fig:Eroding100anomalous}(a)) and second
-(Figure~\ref{fig:Eroding100anomalous}(b)) moments of the streamlines at
+Next, we use the 1000 tracer trajectories to compute the second
+(Figure~\ref{fig:Eroding100anomalous}) moments of the streamlines at
 various porosities.  At high porosities, the first moment is similar to
@@
 onset of anomalous dispersion is observed in
-Figure~\ref{fig:Eroding100anomalous}(b). At early times, the particle
+Figure~\ref{fig:Eroding100anomalous}. At early times, the particle
 spreading is comparable to that of an open channel (dashed curve)
@@
 
-\begin{figure}[H]
+\begin{figure}
 \center
-\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
-\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
-\caption{\label{fig:Eroding100anomalous} The first and second moments of
-trajectories passing through an eroding geometry at several porosities.
-The dashed black line corresponds to a porosity of 100\%, and the
-dashed-dotted line is a line of best fit with slope 0.8715.}
+\includegraphics*[width =0.55\linewidth]{./figs/100b_second_moment_long_ref}
+\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
+dispersion in 100 bodies with respect to initial porosity
+(as p=50.09\%) and another five porosities during the eroding. The dashed line
+correspondes to a porosity of 100\% and the dashed-dotted lines are lines
+of best fit with slope 1.1135 (as p=95.12\%), 0.6825 (as p=85.07\%), 
+0.7347 (as p=75.14\%), 0.5915 (as p=65.03\%), 
+0.6107 (as p=55.02\%), and 0.7 (as p=50.09\%).}
 \end{figure}

### 2019-08-25 docs/transport/erosion_transport.tex
working on results

--- 2019-08-25 docs/transport/erosion_transport.tex
@@
 
-\todo[inline]{Bryan is here}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We consider 20 eroding bodies that are discretized with $N_\iin=256$
-points and are initially placed in $[-1,1] \times [-1,1]$.  The
-background flow is the Hagen-Poiseuille flow
+points and a time step size of $\Delta t = 10^{-4}$.  The background
+flow is the Hagen-Poiseuille flow
 \begin{align}
@@
 resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
-but with a larger initial area fraction.  We also compute the flow rate
-$U$ required to maintain a constant pressure drop across the channel in
-Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
-resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
-except that the initial flow rate is an order of magnitude smaller
-because of the larger initial area fraction.  Starting around normalized
-time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
-which indicates that the flow rate can be written as a power law.  Using
-a line of best fit, the flow rate is approximately 
+but with a larger initial area fraction.  In
+Figure~\ref{fig:Eroding20flowrate}(b), we plot flow rate $U$ required to
+maintain a constant pressure drop across the channel.  Again, the trend
+of $U$ resembles that of our previous work~\cite{qua-moo2018} (Figure
+10(b)), except that the initial flow rate is an order of magnitude
+smaller because of the larger initial area fraction.  Starting around
+normalized time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly
+linear which indicates that the flow rate can be written as a power law.
+Using a line of best fit, the flow rate is approximately 
 \begin{align} 
@@
 \caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
-nearly touching eroding bodies versus normalized time. (b): The incoming
-flow rate, $U$, for a fixed pressure drop across the channel versus
+nearly touching eroding bodies versus normalized time. (b): The flow
+rate, $U$, for a fixed pressure drop across the channel versus
 normalized time.  The flow rate is initially very small, but it
@@
 vorticity is largest.  Initially, several of the eroding bodies are
-closer to the outer wall than the $5h$ threshold required to guarantee
-sufficiently accurate quadrature with the trapezoid rule.  In
+closer to the outer wall than the $5h$ threshold required to guarantee a
+machine precision quadrature error for the trapezoid rule.  In
 particular, with $h=L_2/N_\out$, the distance between bodies 1, 6, 13,
-and 15 are $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively.  In
-addition, the distance between several pairs of eroding bodies is too
-small to be accurately resolved with the trapezoid rule at the
-prescribed resolution.  Particular pairs include bodies 1 \& 6, 3 \& 9,
-6 \& 8, and 14 \& 18.  By using the Barycentric quadrature rule, the
-interaction between these nearly-touching bodies can be accurately
-resolved at the prescribed resolution.
+and 15 and the outer wall are $1.3h$, $2.9h$, $2.8h$, and $1.3h$,
+respectively.  In addition, the distance between several pairs of
+eroding bodies is too small to be accurately resolved with the trapezoid
+rule at the prescribed resolution.  Particular pairs include bodies 1 \&
+6, 3 \& 9, 6 \& 8, and 14 \& 18.  By using the Barycentric quadrature
+rule, the interaction between these nearly-touching bodies can be
+accurately resolved at the prescribed resolution.
 
@@
 the fluid. The four snapshots are evenly spaced in time. We use $N_\iin
-= 256$ discretization points on the bodies and $\Dt=10^{-4}$.  In the
-forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
-has almost completely eroded.}
+= 256$ discretization points on the bodies.  In the fourth frame, bodies
+4, 12, and 17 have vanished completely, and body 19 has almost
+completely eroded.}
 \end{center}

### 2019-08-25 docs/transport/erosion_transport.tex
working on first 20 body example

@@
 occurs between certain pairs of bodies.  For instance the opening
-between bodies 1 \& 6 grows much slower than the opening between bodies
-15 \& 16.  A common feature of the openings that grow slowly is that
-they are nearly perpendicular to the main flow direction, and this
-results in very low erosion because of the small shearing.  For example,
-the openings between the pair of bodies 1 \& 6, 3 \& 9, and 5 \& 13.
-
-In this example, we also observe that erosion creates a network of
-channels from the inlet to outlet where the velocity and vorticity, and
-therefore erosion rate, are much larger than in other regions.  These
-channels can be further visualized by considering the streamlines.  In
+between bodies 1 \& 6, 3 \& 9, and 5 \& 13 grow much slower than the
+opening between bodies 15 \& 16.  A common feature of the openings that
+grow slowly is that they are nearly perpendicular to the main flow
+direction, and this results in very low erosion because of the slow flow
+between the bodies.
+
+We also observe that erosion creates a network of channels from the
+inlet to outlet where the velocity and vorticity, and therefore erosion
+rate, are much larger when compared to other regions.  These channels
+can be further visualized by considering the streamlines.  In
 Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
@@
 trajectories that are initialized at $x=-1$ and equispaced in $y$.  The
-trajectories are shown at 5 different times, and the final plot is a
-zoom in of the lower right quadrant of the fifth time step.  There are
-three clear regions where the tracers pass through the geometry fastest.
-Two of these regions are located between the bodies and the solid walls
-at $y=\pm 1$, and the third cuts through the porous region with the
-upper part of the channel formed by bodies 1, 4, 6, and 8.  Since the
-flow is fastest in these regions, the shearing is largest, and this
-causes these openings to grow fastest which can be observed in
+trajectories are shown at five different times, and the final plot is a
+zoom in of the lower right quadrant of the fifth time step.  Since we
+use a high-order quadrature rule and a high-order time stepper, we are
+able to resolve trajectories that come very close to the eroded bodies.
+There are three clear regions where the tracers pass through the
+geometry fastest.  Two of these regions are located between the bodies
+and the solid walls at $y=\pm 1$, and the third cuts through the porous
+region with the upper part of the channel formed by bodies 1, 4, 6, and
+8.  Since the flow is fastest in these regions, the shearing is largest,
+and this causes these openings to grow fastest which can be observed in
 Figure~\ref{fig:Eroding20vort}.
@@
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
-\caption{\label{fig:Eroding20tracer}200 trajectories in the second
+\caption{\label{fig:Eroding20tracer} 200 trajectories in the second
 geometry from Figure~\ref{fig:Eroding20vort}. The trajectories are
@@
 first five snapshots are evenly spaced in time.  The bottom right frame
-is a zoom window of the fifth snapshot.  Since we use a Barycentric
+is a zoom in of the fifth snapshot.  Since we use the Barycentric
 quadrature rule and the fourth-order Runge-Kutta method, the tracers can
-be very close to but not penetrate the bodies.}
+be very close to but not unphysically penetrate the bodies.}
 \end{center}
@@
 calculations use a statistical analysis of the tracer trajectories, we
-increase the number of trajectories to $N_p = 1000$.  Again, the tracers
-are initialized at $x=-1$, and their $y$ coordinates are distributed
-evenly across the entire channel.  To compute the tortuosity, we require
-the velocity at the initialization points of the tracers.  These
-normalized velocities are plotted in Figure~ref{fig:Eroding20tort}(a)
-for the eroded geometry with porosity 62.9\% (see
-  Figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
-  work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure 4(a)), except
-  that our cross-section does not cut through any of the bodies.  Next,
-  in Figure~\ref{fig:Eroding20tort}(b), we plot the local
-  tortuosity~\eqref{eqn:localTort} by calculating the length of each
-  trajectory as it traverses the channel from $x=-1$ to $x=1$ in
-  Figure~\ref{fig:Eroding20tort}(b), and dividing by the length of the
-  channel.  The local tortuosity ranges from 1 to 1.27, meaning that one
-  of the tracers travelled 27\% farther than it would have if the bodies
-  had been absent.  The average tracer travelled 9.79\% farther than if
-  the bodies had been absent, meaning that the tortuosity of the eroded
-  channel is $1.098$.  Again, comparing the local tortuosity to
-  Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
-  qualitatively similar. However, since our initial cross-section does
-  not cut through any bodies, the local tortuosity does not have any
-  gaps.  The discontinuities correspond to neighboring tracers with one
-  traveling much farther than the other.  In
+increase the number of trajectories to $N_p =
+1000$~\cite{bel-sal-rin1992}.  Again, the tracers are initialized at
+$x=-1$, and their $y$ coordinates are distributed evenly across the
+entire channel.  To compute the tortuosity, we require the velocity at
+the initialization points of the tracers.  These normalized velocities
+are plotted in Figure~ref{fig:Eroding20tort}(a) for the eroded geometry
+with porosity 62.9\% (see Figure~\ref{fig:Eroding20tort}(c)).  The
+velocities are similar to the work of Matyka et
+al.~\cite{mat-kha-koz2008} (see Figure 4(a)), except that our
+cross-section does not cut through any of the bodies.  Next, in
+Figure~\ref{fig:Eroding20tort}(b), we plot the local
+tortuosity~\eqref{eqn:localTort} by calculating the relative length of
+each trajectory as it traverses the channel from $x=-1$ to $x=1$.  The
+local tortuosity ranges from 1 to 1.27, meaning that one of the tracers
+travelled 27\% farther than it would have if the bodies had been absent.
+The average tracer travelled 9.79\% farther than if the bodies had been
+absent, meaning that the tortuosity of the eroded channel is $1.098$.
+Again, comparing the local tortuosity to Matyka~\cite{mat-kha-koz2008}
+(Figure 4(b)), the results are qualitatively similar. However, since our
+initial cross-section does not cut through any bodies, the local
+tortuosity does not have any gaps.  The discontinuities correspond to
+neighboring tracers with one traveling much farther than the other.  In
 Figure~\ref{fig:Eroding20tort}(c), we plot pairs of trajectories that
 correspond to the ten largest jumps in the local tortuosity.
-  Corresponding pairs are always plotted in the same color.  The
-  discrepancy between the trajectory lengths can be attributed to the
-  tracers diverging from one another as they approach opposite sides of
-  a stagnation point in the flow.
+Corresponding pairs are plotted in the same color.  The discrepancy
+between the trajectory lengths can be attributed to the tracers
+diverging from one another as they approach opposite sides of a
+stagnation point in the flow.
 
@@
 normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
-local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
-averaged tortuosity through the channel is $1.098$.  (c) The
+local tortuosity $\tau(y)$ along the cross section $x = -1$.  The
+spatially averaged tortuosity through the channel is $1.098$.  (c) The
 trajectories resulting in the ten largest differences between
@@
 grid~\eqref{eqn:tortuosity2}.  The red square corresponds to the
-porosity in Figure~\ref{fig:Eroding20tort}(c).  The methods give similar
-results with any discrepancy being accounted for by slow regions of
-recirculation.  As the bodies erode, this creates wide channels where
-trajectories undergo only minor vertical deflections, and this explains
-why the tortuosity eventually decreases with porosity.  The increase in
-tortuosity for small porosities occurs because in the absence of erosion
-(left plot in Figure~\ref{fig:Eroding20vort}), many of the trajectories,
-such as those initialized between bodies 15 \& 18, only perform minor
+porosity in Figure~\ref{fig:Eroding20tort}(c).  The two tortuosity
+calculations give similar results with any discrepancy being accounted
+for by slow regions of recirculation.  As the bodies erode, this creates
+wide channels where trajectories undergo only minor vertical
+deflections, and this explains why the tortuosity eventually decreases
+with porosity.  We computed computed lines of best fit using the
+porosity-tortuosity models~\eqref{eqn:tortuosityModels}, and the power
+law model gave the smallest error.  The  black
+dashed line in Figure~\ref{fig:Eroding20tort_all} is the line of best
+fit
+\begin{align}
+  \widehat{T}(\phi) = \phi^{-0.2064}
+\end{align}
+with a root-mean-square error of $5.9 \times 10^{-3}$.  The initial
+increase in tortuosity occurs because in the absence of erosion (left
+plot in Figure~\ref{fig:Eroding20vort}), many of the trajectories, such
+as those initialized between bodies 15 \& 18, only perform minor
 deflections to pass through the narrow regions, albeit, very slowly.
@@
 
+\todo[inline]{BQ: Need to fix the references to this new figure}
+
 \begin{figure}[H]
-\center
-\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian}
-\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/20b_second_moment_long_ref}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20Tranposrt} (a): The tortuosity inside of an
 eroding geometry initialized with 20 bodies.  The tortuosity is
@@
 The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ as
-$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$.}
+$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$. (b):
+The analysis of anomalous dispersion in 20 nearly touching bodies with
+respect to initial porosity (as p=37.68\%) and another six porosities
+during the eroding. The dashed line correspondes to a porosity of 100\%
+and the dashed-dotted lines are lines of best fit with slope 1.0644 (as
+p=95.1\%), 1.0673 (as p=85.09\%), 1.0594 (as p=75.15\%), 0.9664 (as
+p=65.09\%), 0.7766 (as p=55.10\%), 0.7475 (as p=45.08\%), and 0.5607 (as
+p=37.68\%.}
 \end{figure}
 
-\begin{figure}[H]
-\center
-\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long_ref}
-\caption{\label{fig:Eroding20anomalousMedium} The analysis of anomalous
-dispersion in 20 nearly touching bodies with respect to initial porosity
-(as p=37.68\%) and another six porosities during the eroding. The dashed line
-correspondes to a porosity of 100\% and the dashed-dotted lines are lines
-of best fit with slope 1.0644 (as p=95.1\%), 1.0673 (as p=85.09\%), 
-1.0594 (as p=75.15\%), 0.9664 (as p=65.09\%), 
-0.7766 (as p=55.10\%), 0.7475 (as p=45.08\%), 
-and 0.5607 (as p=37.68\%.}
-\end{figure}
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width = 0.55\linewidth]{./figs/tort_eulerian}
+%\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
+%eroding geometry initialized with 20 bodies.  The tortuosity is
+%calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
+%and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
+%square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
+%The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ as
+%$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$.}
+%\end{figure}
+%
+%
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long_ref}
+%\caption{\label{fig:Eroding20anomalousMedium} The analysis of anomalous
+%dispersion in 20 nearly touching bodies with respect to initial porosity
+%(as p=37.68\%) and another six porosities during the eroding. The dashed
+%line correspondes to a porosity of 100\% and the dashed-dotted lines are
+%lines of best fit with slope 1.0644 (as p=95.1\%), 1.0673 (as
+%p=85.09\%), 1.0594 (as p=75.15\%), 0.9664 (as p=65.09\%), 0.7766 (as
+%p=55.10\%), 0.7475 (as p=45.08\%), and 0.5607 (as p=37.68\%.}
+%\end{figure}
+%
 

### 2019-08-26 docs/transport/erosion_transport.tex
worked on second numerical example

@@
 geometry.  Since there is no diffusion, we apply a high-order explicit
-Runge-Kutta time stepping method to compute tracer trajectories.
-However, other groups have simulated trajectories using continuous time
-random walks~\cite{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
+Runge-Kutta time stepping method to compute streamlines.  However, other
+groups have simulated trajectories using continuous time random
+walks~\cite{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
 ber-cor-den-sch2006} and a Fokker-Planck equation~\cite{ica-den2019}.
@@
 
-The tortuosity is a first statistical moment of the tracer trajectories.
+The tortuosity is a first statistical moment of the streamlines.
 However, to measure spread of trajectories, second-order moments are
@@
 characterizing transport in these geometries.  In our previous
-work~\cite{qua-moo2018}, we examined the effect of erosion on
-the area fraction, flow rate, and the total drag.  However, to
-characerize transport, other quantities must be examined.  Here, we
-compute the anomalous dispersion rate, the tortuosity, and the
-distribution of the gap sizes.  The first two metrics can be defined in
-terms of tracer trajectories governed by an advection
-equation~\eqref{eqn:tracers}.
+work~\cite{qua-moo2018}, we examined the effect of erosion on the area
+fraction, flow rate, and the total drag.  However, to characerize
+transport, other quantities must be examined.  Here, we compute the
+anomalous dispersion rate, the tortuosity, and the distribution of the
+gap sizes.  The first two metrics can be defined in terms of streamline
+governed by an advection autonomous equation~\eqref{eqn:tracers}.
 
@@
 
-We calculate the anomalous dispersion rates by analyzing the tracer
-trajectories governed by equation~\eqref{eqn:tracers} for geometries
-that are formed by erosion.  Given a set of trajectories, we define
-$\lambda_j(t)$ to be the arclength of the trajectory
+We calculate the anomalous dispersion rates by analyzing the streamlines
+governed by equation~\eqref{eqn:tracers} for geometries that are formed
+by erosion.  Given a set of trajectories, we define $\lambda_j(t)$ to be
+the arclength of the trajectory
 \begin{align}
@@
 \end{align}
-Since we compute second-order statistics, we use 1000 tracers so that
-the statistics have converged~\cite{bel-sal-rin1992}.  Then, particle
-dispersion is characterized as $\sigma_\lambda$.  At early times, the
-particles have not explored much of the geometry, and we expect a
-ballistic motion $\sigma_\lambda \sim t$.  However, as the particles
-pass the grains, their trajectories are altered, and we expect that
-$\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$, indicating
-that the flow is super-dispersive.
+Since we compute second-order statistics, we use 1000 streamlines so
+that the statistics have converged~\cite{bel-sal-rin1992}.  Then,
+particle dispersion is characterized as $\sigma_\lambda$.  At early
+times, the particles have not explored much of the geometry, and we
+expect a ballistic motion $\sigma_\lambda \sim t$.  However, as the
+particles pass the grains, their trajectories are altered, and we expect
+that $\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$,
+indicating that the flow is super-dispersive.
 
@@
 To compute the tortuosity and the anomalous dispersion rates
-(Section~\ref{sec:transport}), we require trajectories of passive
-tracers, governed by equation~\eqref{eqn:tracers}.  To reliably
-characterize the transport, it is crucial that the trajectories are
+(Section~\ref{sec:transport}), we require the streamlines governed by equation~\eqref{eqn:tracers}.  To reliably
+characterize the transport, it is crucial that the streamlines are
 computed accurately.  If a low-order time stepping method is used, or if
@@
 The common characteristic of each of the experiments is near-contact
-between the eroding bodies, outer walls, and passive tracers. We use our
+between the eroding bodies, outer walls, and streamlines. We use our
 numerical methods to describe and visualize the following examples:
@@
   bodies with a medium initial porosity.  After computing accurate
-  tracer trajectories, the tortuosity and anomalous dispersion rates are
+  streamlines, the tortuosity and anomalous dispersion rates are
   computed and compared to those of an open channel.
@@
 where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
-to $x=2$ is held fixed at 2.  We start by analyzing the effect of
-erosion on the area fraction and the flow rate.  In
-Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
-function of normalized time.  Initially, 62\% of the geometry is eroded
-bodies corresponding to a porosity of $0.38$, and the area fraction
-decreases to 0 as the bodies erode.  The trend of the area fraction
-resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
-but with a larger initial area fraction.  In
-Figure~\ref{fig:Eroding20flowrate}(b), we plot flow rate $U$ required to
-maintain a constant pressure drop across the channel.  Again, the trend
-of $U$ resembles that of our previous work~\cite{qua-moo2018} (Figure
-10(b)), except that the initial flow rate is an order of magnitude
-smaller because of the larger initial area fraction.  Starting around
-normalized time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly
-linear which indicates that the flow rate can be written as a power law.
-Using a line of best fit, the flow rate is approximately 
-\begin{align} 
-  U \approx \left(\frac{t}{t_f}\right)^{3.43},
-\end{align}
-which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).
-
-\begin{figure}[H]
-\begin{subfigure}[b]{0.55\textwidth}
-\includegraphics*[width =\linewidth]{./figs/porosity20dense}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
-nearly touching eroding bodies versus normalized time. (b): The flow
-rate, $U$, for a fixed pressure drop across the channel versus
-normalized time.  The flow rate is initially very small, but it
-eventually increases as a power law (dashed line) towards the flow rate
-$U=1$ that occurs once all the bodies have eroded.}
-\end{figure}
-
-Snapshots of the bodies at four equispaced times are shown in
-Figure~\ref{fig:Eroding20vort}.  The color is the vorticity which is
-equivalent to the shear stress when restricted to the eroding bodies.
-Therefore, erosion is fastest in regions where the magnitude of the
-vorticity is largest.  Initially, several of the eroding bodies are
-closer to the outer wall than the $5h$ threshold required to guarantee a
-machine precision quadrature error for the trapezoid rule.  In
-particular, with $h=L_2/N_\out$, the distance between bodies 1, 6, 13,
-and 15 and the outer wall are $1.3h$, $2.9h$, $2.8h$, and $1.3h$,
-respectively.  In addition, the distance between several pairs of
-eroding bodies is too small to be accurately resolved with the trapezoid
-rule at the prescribed resolution.  Particular pairs include bodies 1 \&
-6, 3 \& 9, 6 \& 8, and 14 \& 18.  By using the Barycentric quadrature
-rule, the interaction between these nearly-touching bodies can be
-accurately resolved at the prescribed resolution.
+to $x=2$ is held fixed at 2.  Snapshots of the bodies at four equispaced
+times are shown in Figure~\ref{fig:Eroding20vort}.  The color is the
+vorticity which is equivalent to the shear stress when restricted to the
+eroding bodies.  Therefore, the rate of erosion is fastest in regions
+where the magnitude of the vorticity is largest.  Initially, several of
+the eroding bodies are closer to the outer wall than the $5h$ threshold
+required to guarantee that the trapezoid rule achieves machine
+precision.  In particular, with $h=L_2/N_\out$, the distance between
+bodies 1, 6, 13, and 15 and the outer wall are $1.3h$, $2.9h$, $2.8h$,
+and $1.3h$, respectively.  In addition, the distance between several
+pairs of eroding bodies is too small to be accurately resolved with the
+trapezoid rule at the prescribed resolution.  Particular pairs include
+bodies 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18.  By using the Barycentric
+quadrature rule, the interaction between these nearly-touching bodies
+can be accurately resolved at the prescribed resolution, and erosion can
+be simulated until all the bodies have vanished.
 
@@
 
-In~\cite{qua-moo2018}, we observed that erosion causes the space between
-nearly touching bodies to quickly expand, and flat faces develop along
-the region of near contact.  This qualitative behavior is present in
-Figure~\ref{fig:Eroding20vort} between bodies 3 \& 4, 15 \& 16, and
-others.  However, now that we can resolve bodies that are much closer
-together, we observe that, at least initially, very little erosion
-occurs between certain pairs of bodies.  For instance the opening
-between bodies 1 \& 6, 3 \& 9, and 5 \& 13 grow much slower than the
-opening between bodies 15 \& 16.  A common feature of the openings that
-grow slowly is that they are nearly perpendicular to the main flow
-direction, and this results in very low erosion because of the slow flow
-between the bodies.
-
-We also observe that erosion creates a network of channels from the
-inlet to outlet where the velocity and vorticity, and therefore erosion
-rate, are much larger when compared to other regions.  These channels
-can be further visualized by considering the streamlines.  In
+We observe that erosion creates a network of channels from the inlet to
+outlet where the velocity and vorticity, and therefore erosion rate, are
+much larger when compared to other regions.  These channels can be
+further visualized by considering the streamlines.  In
 Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
 time step from Figure~\ref{fig:Eroding20vort}, and we plot 200
-trajectories that are initialized at $x=-1$ and equispaced in $y$.  The
-trajectories are shown at five different times, and the final plot is a
+streamlines that are initialized at $x=-1$ and equispaced in $y$.  The
+streamlines are shown at five different times, and the final plot is a
 zoom in of the lower right quadrant of the fifth time step.  Since we
-use a high-order quadrature rule and a high-order time stepper, we are
-able to resolve trajectories that come very close to the eroded bodies.
-There are three clear regions where the tracers pass through the
-geometry fastest.  Two of these regions are located between the bodies
-and the solid walls at $y=\pm 1$, and the third cuts through the porous
-region with the upper part of the channel formed by bodies 1, 4, 6, and
-8.  Since the flow is fastest in these regions, the shearing is largest,
-and this causes these openings to grow fastest which can be observed in
-Figure~\ref{fig:Eroding20vort}.
+use a high-order quadrature rule and a high-order time stepping method,
+we resolve streamlines that come very close to the eroded bodies.  There
+are three clear regions where the streamlines are concentrated, and this
+corresponds to regions of high velocity.  Two of these regions are
+located between the bodies and the solid walls at $y=\pm 1$, and the
+third cuts through the porous region with the upper part of the channel
+formed by bodies 1, 4, 6, and 8.  Since the flow is fastest in these
+regions, the shearing is largest, and this causes these openings to grow
+fastest which can be observed in Figure~\ref{fig:Eroding20vort}.
+
+Similar to our previous work, erosion causes the space between nearly
+touching bodies to quickly expand, and flat faces develop along the
+region of near contact.  This qualitative behavior is present in
+Figure~\ref{fig:Eroding20vort} between bodies 3 \& 4, 15 \& 16, and
+others.  However, by resolving the interaction betweeen bodies that are
+much closer together than in our previous work, we observe that, at
+least initially, very little erosion occurs between certain pairs of
+bodies.  For instance the opening between bodies 1 \& 6, 3 \& 9, and 5
+\& 13 grow much slower than the opening between bodies 15 \& 16.  A
+common feature of the openings that grow slowly is that they are nearly
+perpendicular to the main flow direction, and this results in a small
+velocity, and hence a slow erosion rate.  In fact, when plotting the
+streamlines, only a small fraction of the plotted streamlines pass
+between theese pairs of bodies indicating a very small velocity.
 
@@
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
-\caption{\label{fig:Eroding20tracer} 200 trajectories in the second
-geometry from Figure~\ref{fig:Eroding20vort}. The trajectories are
+\caption{\label{fig:Eroding20tracer} 200 streamlines in the second
+geometry from Figure~\ref{fig:Eroding20vort}. The streamlines are
 initialized at $x=-1$ and are equally spaced in the $y$-direction. The
@@
 is a zoom in of the fifth snapshot.  Since we use the Barycentric
-quadrature rule and the fourth-order Runge-Kutta method, the tracers can
-be very close to but not unphysically penetrate the bodies.}
+quadrature rule and the fourth-order Runge-Kutta method, the streamlines
+can be very close to but not unphysically penetrate the bodies.}
 \end{center}
@@
 
-Next, we use the tracer trajectories to compute the anomalous dispersion
-rates and the tortuosities in the eroding geometry.  Since these
-calculations use a statistical analysis of the tracer trajectories, we
-increase the number of trajectories to $N_p =
-1000$~\cite{bel-sal-rin1992}.  Again, the tracers are initialized at
-$x=-1$, and their $y$ coordinates are distributed evenly across the
-entire channel.  To compute the tortuosity, we require the velocity at
-the initialization points of the tracers.  These normalized velocities
-are plotted in Figure~ref{fig:Eroding20tort}(a) for the eroded geometry
-with porosity 62.9\% (see Figure~\ref{fig:Eroding20tort}(c)).  The
-velocities are similar to the work of Matyka et
-al.~\cite{mat-kha-koz2008} (see Figure 4(a)), except that our
-cross-section does not cut through any of the bodies.  Next, in
-Figure~\ref{fig:Eroding20tort}(b), we plot the local
+Next, we use the streamlines to compute the local tortuosity and the
+anomalous dispersion rate of eroding geometries.  Since these
+calculations are statistical, we use $N_p = 1000$
+streamlines~\cite{bel-sal-rin1992}.  To compute the tortuosity, we
+require the velocity at the start of the streamlines.  These normalized
+velocities are plotted in Figure~\ref{fig:Eroding20tort}(a) for the
+eroded geometry with porosity 62.9\% (see
+Figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
+work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure 4(a)), except
+that our cross-section, by construction, does not cut through any of the
+bodies.  Next, in Figure~\ref{fig:Eroding20tort}(b), we plot the local
 tortuosity~\eqref{eqn:localTort} by calculating the relative length of
-each trajectory as it traverses the channel from $x=-1$ to $x=1$.  The
-local tortuosity ranges from 1 to 1.27, meaning that one of the tracers
-travelled 27\% farther than it would have if the bodies had been absent.
-The average tracer travelled 9.79\% farther than if the bodies had been
-absent, meaning that the tortuosity of the eroded channel is $1.098$.
-Again, comparing the local tortuosity to Matyka~\cite{mat-kha-koz2008}
-(Figure 4(b)), the results are qualitatively similar. However, since our
-initial cross-section does not cut through any bodies, the local
-tortuosity does not have any gaps.  The discontinuities correspond to
-neighboring tracers with one traveling much farther than the other.  In
-Figure~\ref{fig:Eroding20tort}(c), we plot pairs of trajectories that
+each streamline as it traverses the channel from $x=-1$ to $x=1$.  The
+local tortuosity ranges from 1 to 1.27, meaning that one of the
+streamlines is 27\% longer than it would have been if the bodies were
+absent.  The average streamline length is 9.79\% longer than if the
+bodies had been absent, so the tortuosity of the eroded channel is
+$1.098$.  Again, comparing the local tortuosity to
+Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
+qualitatively similar. However, since our initial cross-section does not
+cut through any bodies, the local tortuosity does not have any gaps.
+The discontinuities in the local tortuosity happens neighboring
+streamlines diverge on opposite sides of a body.  In
+Figure~\ref{fig:Eroding20tort}(c), we plot pairs of streamline that
 correspond to the ten largest jumps in the local tortuosity.
-Corresponding pairs are plotted in the same color.  The discrepancy
-between the trajectory lengths can be attributed to the tracers
-diverging from one another as they approach opposite sides of a
-stagnation point in the flow.
+Corresponding pairs are plotted in the same color.
 
@@
 \caption{\label{fig:Eroding20tort} The tortuosity of an eroded geometry
-with porosity 62.9\%. (a) The x-component of the velocity $u(-1, y)$
+with porosity 62.9\%. (a) The $x$-component of the velocity, $u(-1,y)$,
 normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
@@
 spatially averaged tortuosity through the channel is $1.098$.  (c) The
-trajectories resulting in the ten largest differences between
-neighboring trajectories.  Neighboring trajectories have the same
-color.}
+streamlines resulting in the ten largest differences between neighboring
+streamlines.  Neighboring streamlines have the same color.}
 \end{figure}
 
-In Figure~\ref{fig:Eroding20tort_all}, we plot the tortuosity as a
+In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
 function of the porosity from the initial porosity of $0.38$ until all
 the bodies have eroded.  The tortuosity is computed with both the length
-of the trajectories~\eqref{eqn:tortuosity1} (red marks) and using the
+of the streamlines~\eqref{eqn:tortuosity1} (red marks) and using the
 spatial average of the velocity on an Eulerian
-grid~\eqref{eqn:tortuosity2}.  The red square corresponds to the
-porosity in Figure~\ref{fig:Eroding20tort}(c).  The two tortuosity
-calculations give similar results with any discrepancy being accounted
-for by slow regions of recirculation.  As the bodies erode, this creates
-wide channels where trajectories undergo only minor vertical
-deflections, and this explains why the tortuosity eventually decreases
-with porosity.  We computed computed lines of best fit using the
-porosity-tortuosity models~\eqref{eqn:tortuosityModels}, and the power
-law model gave the smallest error.  The  black
-dashed line in Figure~\ref{fig:Eroding20tort_all} is the line of best
-fit
+grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
+to the porosity of the geometry in Figure~\ref{fig:Eroding20tort}(c).
+The two tortuosity formulas give similar results, and any discrepancy
+can be accounted for by slow regions of recirculation and quadrature
+error induced by the integrals in the tortuosity definitions.  As the
+bodies erode, this creates wide channels where streamlines undergo only
+minor vertical deflections, and this explains why the tortuosity
+eventually decreases with porosity.  We computed lines of best fit using
+the porosity-tortuosity models~\eqref{eqn:tortuosityModels}, and the
+power law model gave the smallest error.  The  black dashed line in
+Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
 \begin{align}
@@
 increase in tortuosity occurs because in the absence of erosion (left
-plot in Figure~\ref{fig:Eroding20vort}), many of the trajectories, such
+plot in Figure~\ref{fig:Eroding20vort}), many of the streamlines, such
 as those initialized between bodies 15 \& 18, only perform minor
 deflections to pass through the narrow regions, albeit, very slowly.
-However, as erosion starts to open the channels, the trajectories
-deflect into the fast regions, such as the region above body 11, and
-this increases the amount of vertical deflection, and therefore the
+However, as erosion starts to open the channels, the streamlines deflect
+into the fast regions, such as the region above body 11, and this
+increases the amount of vertical deflection, and therefore the
 tortuosity.
 
-\todo[inline]{BQ: Need to fix the references to this new figure}
+\todo[inline]{Nothing about the anomalous dispersion rate here}
+At high porosities, the dispersion rate is close to 1, and this can be
+caused by one of two reasons.  1) There is no measurable anomalous
+dispersion; or, 2) The streamlines are too short to see the anomalous
+dispersion.
 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20Tranposrt} (a): The tortuosity inside of an
+\caption{\label{fig:Eroding20Transport} (a): The tortuosity inside of an
 eroding geometry initialized with 20 bodies.  The tortuosity is
@@
 square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
-The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ as
-$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$. (b):
-The analysis of anomalous dispersion in 20 nearly touching bodies with
-respect to initial porosity (as p=37.68\%) and another six porosities
-during the eroding. The dashed line correspondes to a porosity of 100\%
-and the dashed-dotted lines are lines of best fit with slope 1.0644 (as
-p=95.1\%), 1.0673 (as p=85.09\%), 1.0594 (as p=75.15\%), 0.9664 (as
-p=65.09\%), 0.7766 (as p=55.10\%), 0.7475 (as p=45.08\%), and 0.5607 (as
-p=37.68\%.}
+The dash line is the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with
+$p=0.2064$, and the corresponding root-mean-square error is $5.9 \times
+10^{-3}$. (b): The temporal evolution of $\sigma_\lambda$ as a function
+of time at seven different porosities.  The dashed, which has slope one,
+corresponds to $\sigma_\lambda$ if no bodies were present.  At early
+times, the particles undergo a ballistic motion, but once they have
+traversed a few grains, the dispersion becomes super-dispersive.  The
+dashed-dotted lines are lines of best fit with slopes $1.0644$
+($\phi=95.1\%$), $1.0673$ ($\phi=85.09\%$), $1.0594$ ($\phi=75.15\%$),
+$0.9664$ ($\phi=65.09\%$), $0.7766$ ($\phi=55.10\%$), $0.7475$
+($\phi=45.08\%$), and $0.5607$ ($\phi=37.68\%$).}
 \end{figure}
 
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width = 0.55\linewidth]{./figs/tort_eulerian}
-%\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
-%eroding geometry initialized with 20 bodies.  The tortuosity is
-%calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
-%and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
-%square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
-%The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ as
-%$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$.}
-%\end{figure}
-%
-%
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long_ref}
-%\caption{\label{fig:Eroding20anomalousMedium} The analysis of anomalous
-%dispersion in 20 nearly touching bodies with respect to initial porosity
-%(as p=37.68\%) and another six porosities during the eroding. The dashed
-%line correspondes to a porosity of 100\% and the dashed-dotted lines are
-%lines of best fit with slope 1.0644 (as p=95.1\%), 1.0673 (as
-%p=85.09\%), 1.0594 (as p=75.15\%), 0.9664 (as p=65.09\%), 0.7766 (as
-%p=55.10\%), 0.7475 (as p=45.08\%), and 0.5607 (as p=37.68\%.}
-%\end{figure}
-%
+Finally, following our previous work~\cite{qua-moo2018}, we analyze the
+effect of erosion on the area fraction and the flow rate.  In
+Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
+function of normalized time.  Initially, 62\% of the geometry contains
+eroding bodies corresponding to a porosity of $0.38$, and the area
+fraction decreases to 0 as the bodies erode.  The trend of the area
+fraction resembles our previous work~\cite{qua-moo2018} (Figure 10(a)),
+but with a larger initial area fraction.  In
+Figure~\ref{fig:Eroding20flowrate}(b), we plot the flow rate $U$
+required to maintain a constant pressure drop across the channel.
+Again, the trend of $U$ resembles that of our previous
+work~\cite{qua-moo2018} (Figure 10(b)), except that the initial flow
+rate is an order of magnitude smaller because of the larger initial area
+fraction.  Starting around normalized time $0.2$,
+Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
+that the flow rate can be written as a power law.  Using a line of best
+fit, the flow rate is approximately 
+\begin{align} 
+  U \approx \left(\frac{t}{t_f}\right)^{3.43},
+\end{align}
+which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).
+
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.7\linewidth]{./figs/porosity20dense}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.7\linewidth]{./figs/flow_rate20dense}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
+nearly touching eroding bodies versus normalized time. (b): The flow
+rate, $U$, for a fixed pressure drop across the channel versus
+normalized time.  The flow rate is initially very small, but it
+eventually increases as a power law (dashed line) towards the flow rate
+$U=1$ that occurs once all the bodies have eroded. \todo[inline]{S-H:
+Let's bring the black dashed line closer to the blue line}}
+\end{figure}
 
@@
 %
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width = 0.55\linewidth]{./figs/tort_eulerian}
+%\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
+%eroding geometry initialized with 20 bodies.  The tortuosity is
+%calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
+%and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
+%square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
+%The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ as
+%$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$.}
+%\end{figure}
+%
+%
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long_ref}
+%\caption{\label{fig:Eroding20anomalousMedium} The analysis of anomalous
+%dispersion in 20 nearly touching bodies with respect to initial porosity
+%(as p=37.68\%) and another six porosities during the eroding. The dashed
+%line correspondes to a porosity of 100\% and the dashed-dotted lines are
+%lines of best fit with slope 1.0644 (as p=95.1\%), 1.0673 (as
+%p=85.09\%), 1.0594 (as p=75.15\%), 0.9664 (as p=65.09\%), 0.7766 (as
+%p=55.10\%), 0.7475 (as p=45.08\%), and 0.5607 (as p=37.68\%.}
+%\end{figure}
+%
 

### 2019-08-27 docs/transport/erosion_transport.tex
add a new figure in transport paper
removed a todo

@@
 \includegraphics[width = 0.3 \textwidth]{./figs/vort_50b320}
-%\includegraphics[width = 0.37 \textwidth]{./figs/vort_50b160}
+\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b400}
 \caption{\label{fig:Eroding50vort} Erosion of 50 nearly touching
@@
 find that $\alpha_\iin = 4$ and $\alpha_\out = 4$ give sufficient
-accuracy while keeping the number of points that require the expensive
-Barycentric quadrature rule to a minimum.  We use these values for all
-of our numerical simulations.
-\todo[inline]{S-H: What kind of accuracy did this give?  This is less
-than the value used by Barnett in his single author quadrature paper.
-He said that 5 arclength spacings is the right amount to guarantee
-machine precision.}
+accuracy to maintain stability while keeping the number of points that
+require the expensive Barycentric quadrature rule to a minimum.  We use
+these values for all of our numerical simulations.
 
@@
 256$, and the smallest distance between two bodies at the initial
-condition is 0.0216\todo[inline]{SH: Fill in this number}.  At this
-resolution, this corresponds to a spacing of $3.0814h$ which is much
-too small for the trapezoid rule.  By applying the Barycentric
-quadrature rule, there is no issue simulating the erosion until all the
-bodies have eroded.
+condition is $2.16 \times 10^{-2}$.  At this resolution, this
+corresponds to a spacing of $3.0814h$ which is too small for the
+trapezoid rule to guarantee a sufficiently small quadrature error.  By
+applying the Barycentric quadrature rule, there is no issue simulating
+the erosion until all the bodies have eroded.
 

### 2019-08-27 docs/transport/erosion_transport.tex
correct the minimum distance in transport paper

@@
 256$, and the smallest distance between two bodies at the initial
-condition is $2.16 \times 10^{-2}$.  At this resolution, this
-corresponds to a spacing of $3.0814h$ which is too small for the
+condition is $3.29 \times 10^{-4}$.  At this resolution, this
+corresponds to a spacing of $0.0471h$ which is too small for the
 trapezoid rule to guarantee a sufficiently small quadrature error.  By

### 2019-08-27 docs/transport/erosion_transport.tex
finished up a first draft for section 6.2

@@
 
-\todo[inline]{Nothing about the anomalous dispersion rate here}
-At high porosities, the dispersion rate is close to 1, and this can be
-caused by one of two reasons.  1) There is no measurable anomalous
-dispersion; or, 2) The streamlines are too short to see the anomalous
-dispersion.
+In Figure~\ref{fig:Eroding20Transport}(b), we plot the temporal
+evolution of the particle spreading $\sigma_\lambda$.  The spreading is
+computed at several geometries that are formed during the erosion
+process.  So that the spreading reaches a statistical equilibrium, we
+use the reinsertion algorithm described in Section~\ref{sec:dispersion}
+to form sufficiently long trajectories.  For all the reported
+porosities, the particle dispersion exhibits two power low regimes.
+Initially, the dispersion is ballistic ($\sigma_\lambda \sim t$) since
+individual fluid particles have not yet explored enough space to
+significantly alter their velocity.  However, once the particles have
+been subjected to a range of velocities, their dispersion slows down,
+and we observe super-diffusive ($\sigma_\lambda \sim t^\alpha$, $\alpha
+\in (1/2,1)$) behavior over at least one order of magnitude in time.
+Before any erosion takes place, the anomalous dispersion coefficient is
+$\alpha = 0.56$.  Then, as the bodies begin to erode, the dispersion
+rate grows towards the ballistic regime that corresponds to the absence
+of bodies.  The monotonic increase in dispersion with respect to the
+porosity is explained by the onset of channels where many tracers
+experience less variability in their velocities.
 
@@
 of time at seven different porosities.  The dashed, which has slope one,
-corresponds to $\sigma_\lambda$ if no bodies were present.  At early
-times, the particles undergo a ballistic motion, but once they have
-traversed a few grains, the dispersion becomes super-dispersive.  The
-dashed-dotted lines are lines of best fit with slopes $1.0644$
-($\phi=95.1\%$), $1.0673$ ($\phi=85.09\%$), $1.0594$ ($\phi=75.15\%$),
-$0.9664$ ($\phi=65.09\%$), $0.7766$ ($\phi=55.10\%$), $0.7475$
-($\phi=45.08\%$), and $0.5607$ ($\phi=37.68\%$).}
+corresponds to $\sigma_\lambda \sim t$ if no bodies were present.  At
+early times, the particles undergo a ballistic motion, but once they
+have traversed a few grains, the dispersion becomes super-dispersive
+with $\sigma_\lambda \sim t^\alpha$, $\alpha \in (1/2,1)$.  The
+dashed-dotted lines are lines of best fit with slopes $\alpha = 1.06$
+($\phi=95.1\%$), $\alpha = 1.07$ ($\phi=85.09\%$), $\alpha = 1.06$
+($\phi=75.15\%$), $\alpha = 0.97$ ($\phi=65.09\%$), $\alpha = 0.78$
+($\phi=55.10\%$), $\alpha = 0.75$ ($\phi=45.08\%$), and $\alpha = 0.56$
+($\phi=37.68\%$).  Values greater than 1 are a result of using a
+least-squares fit for the tails of the particle spreading.}
 \end{figure}

### 2019-08-27 docs/transport/erosion_transport.tex
add the minimum distance in second 20-body case in transport paper

@@
 256$, and the smallest distance between two bodies at the initial
-condition is $3.29 \times 10^{-4}$.  At this resolution, this
-corresponds to a spacing of $0.0471h$ which is too small for the
+condition is $3.29 \times 10^{-4}$. 
+{\color{red} Besides close bodies, we also place some bodies to be close to wall 
+and the smallest distance between wall and bodies is $4.5 \times 10^{-3}$.} 
+At this resolution, this
+corresponds to a spacing of $0.0471h$ 
+{\color{red}(between two bodies) and $0.8297h$ (between wall and body)
+} which is too small for the
 trapezoid rule to guarantee a sufficiently small quadrature error.  By

### 2019-08-27 docs/transport/erosion_transport.tex
add the minimum distance in second 20-body case in transport paper

--- 2019-08-27 docs/transport/erosion_transport.tex
@@
 256$, and the smallest distance between two bodies at the initial
-condition is $3.29 \times 10^{-4}$.  At this resolution, this
-corresponds to a spacing of $0.0471h$ which is too small for the
+condition is $3.29 \times 10^{-4}$. 
+{\color{red} Besides close bodies, we also place some bodies to be close to wall 
+and the smallest distance between wall and bodies is $4.5 \times 10^{-3}$.} 
+At this resolution, {\color{red} these two minimum distances correspond to a spacing of $0.0471h$ 
+(between two bodies) and $0.8297h$ (between wall and body)
+} which are too small for the
 trapezoid rule to guarantee a sufficiently small quadrature error.  By

### 2019-08-29 docs/transport/erosion_transport.tex
small changes to section 6.3

--- 2019-08-27 docs/transport/erosion_transport.tex
@@
 eventually increases as a power law (dashed line) towards the flow rate
-$U=1$ that occurs once all the bodies have eroded. \todo[inline]{S-H:
-Let's bring the black dashed line closer to the blue line}}
+$U=1$ that occurs once all the bodies have eroded.}
 \end{figure}
@@
 Again, the color is the vorticity in the bulk whose magnitude is
-equivalent to the erosion rate.  Each body is discretized with $N_\iin =
-256$, and the smallest distance between two bodies at the initial
-condition is $3.29 \times 10^{-4}$.  At this resolution, this
-corresponds to a spacing of $0.0471h$ which is too small for the
-trapezoid rule to guarantee a sufficiently small quadrature error.  By
-applying the Barycentric quadrature rule, there is no issue simulating
-the erosion until all the bodies have eroded.
+equivalent to the erosion rate.   Initially, the smallest distance
+between pairs of bodies is $3.29 \times 10^{-4}$, and the smallest
+distance between the bodies and solid wall is $4.50 \times 10^{-3}$.  At
+these distances, a resolution of approximately $N_\iin = 27,000$ and
+$N_\out = 18,000$ discretization points is required to satisfy the $5h$
+rule of thumb that is required for the trapezoid rule to achieve machine
+epsilon accuracy.  By applying the Barycentric quadrature rule, we
+stably simulate erosion at the much coarser resolution of $N_\iin = 256$
+and $N_\out = 1024$ discretization points.
 

### 2019-09-02 docs/transport/erosion_transport.tex
modify something  in transport paper
worked on low porosity 20 body example

@@
 \end{align}
-with a root-mean-square error of $5.9 \times 10^{-3}$.  The initial
+with a root-mean-square error of $5.90 \times 10^{-3}$.  The initial
 increase in tortuosity occurs because in the absence of erosion (left
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20Transport} (a): The tortuosity inside of an
+\caption{\label{fig:Eroding20Transport} (a): The tortuosity of an
 eroding geometry initialized with 20 bodies.  The tortuosity is
@@
 The dash line is the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with
-$p=0.2064$, and the corresponding root-mean-square error is $5.9 \times
+$p=0.2064$, and the corresponding root-mean-square error is $5.90 \times
 10^{-3}$. (b): The temporal evolution of $\sigma_\lambda$ as a function
-of time at seven different porosities.  The dashed, which has slope one,
-corresponds to $\sigma_\lambda \sim t$ if no bodies were present.  At
-early times, the particles undergo a ballistic motion, but once they
-have traversed a few grains, the dispersion becomes super-dispersive
-with $\sigma_\lambda \sim t^\alpha$, $\alpha \in (1/2,1)$.  The
-dashed-dotted lines are lines of best fit with slopes $\alpha = 1.06$
-($\phi=95.1\%$), $\alpha = 1.07$ ($\phi=85.09\%$), $\alpha = 1.06$
-($\phi=75.15\%$), $\alpha = 0.97$ ($\phi=65.09\%$), $\alpha = 0.78$
-($\phi=55.10\%$), $\alpha = 0.75$ ($\phi=45.08\%$), and $\alpha = 0.56$
-($\phi=37.68\%$).  Values greater than 1 are a result of using a
-least-squares fit for the tails of the particle spreading.}
+of time at seven different porosities.  The dashed line, which has slope
+one, corresponds to the ballistic dispersion $\sigma_\lambda \sim t$ if
+no bodies were present. At early times, the particles undergo a
+ballistic motion, but once they have traversed a few grains, the
+dispersion becomes super-dispersive with $\sigma_\lambda \sim t^\alpha$,
+$\alpha \in (1/2,1)$.  The dashed-dotted lines are lines of best fit
+with slopes $\alpha = 1.06$ ($\phi=95.10\%$), $\alpha = 1.07$
+($\phi=85.09\%$), $\alpha = 1.06$ ($\phi=75.15\%$), $\alpha = 0.97$
+($\phi=65.09\%$), $\alpha = 0.78$ ($\phi=55.10\%$), $\alpha = 0.75$
+($\phi=45.08\%$), and $\alpha = 0.56$ ($\phi=37.68\%$).  Values greater
+than 1 are a result of using a least-squares fit for the tails of the
+particle spreading.}
 \end{figure}
@@
 $N_\out = 18,000$ discretization points is required to satisfy the $5h$
-rule of thumb that is required for the trapezoid rule to achieve machine
-epsilon accuracy.  By applying the Barycentric quadrature rule, we
-stably simulate erosion at the much coarser resolution of $N_\iin = 256$
-and $N_\out = 1024$ discretization points.
+rule of thumb for the trapezoid rule to achieve machine epsilon
+accuracy.  By applying the Barycentric quadrature rule, we stably
+simulate erosion at the much coarser resolution of $N_\iin = 256$ and
+$N_\out = 1024$ discretization points.
 
@@
 vorticity of the fluid. The 4 snapshots are evenly spaced in time. We
-use $N_\iin = 256$ discretization points on the body, a time-step of
-$\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
-$\sigma=10/256 $. }
+use $N_\iin = 256$ discretization points on the bodies.  In
+addition to the channels that develop between the bodies and the solid
+walls, Erosion leads to two main channels through the geometry---one in
+the top half and one near the middle.}
 \end{figure}
@@
 We compute the tortuosity using the Eulerian
-method~\eqref{eqn:tortuosity2}. In Figure~\ref{fig:ErodingLow20tort}, we
-plot the tortuosity with respect to the porosity (blue) and a line of
-best fit (black) using the power law $\widehat{T}(\phi) =
-\phi^{-p}$~\cite{mat-kha-koz2008}.  This model outperformed the other
-three models described in equation~\eqref{eqn:tortuosityModels}.  The
-root-mean-squared error of the power law is $1.13 \times 10^{-2}$.
-
-Unlike the previous 20 body simulation, the tortuosity decreases
-monotonically with the porosity. \todo[inline]{BQ: Why is this the case?
-What is special about the last example?}
+method~\eqref{eqn:tortuosity2}. In
+Figure~\ref{fig:ErodingLow20Transport}(a), we plot the tortuosity with
+respect to the porosity (blue) and the line of best fit (black) using
+the power law 
+\begin{align}
+  \widehat{T}(\phi) = \phi^{-0.1669}.
+\end{align}
+This model outperformed the other three models in
+equation~\eqref{eqn:tortuosityModels} that were proposed by Matyka et
+al.~\cite{mat-kha-koz2008}.  The root-mean-squared error of the power
+law is $1.13 \times 10^{-2}$.  As the bodies erode, the number of
+streamlines that take a direct path through the geometry increases,
+and this decreases the tortuosity.  However, there is also an increase
+in the number of streamlines that increase their length since they
+deflect their trajectory to move from a low porosity region (high
+pressure) to a high porosity region (low pressure), and this decreases
+the tortuosity. For this example, we see that the net effect is a
+decrease in the tortuosity for all time.
+
+In Figure~\ref{fig:ErodingLow20Transport}(b), we plot the temporal
+evolution of the particle spreading $\sigma_\lambda$.  As in the last
+example, we analyze the spreading at several different
+porosities and we use the reinsertion algorithm described in Section~\ref{sec:dispersion}
+to form sufficiently long trajectories.  For all the reported
+porosities, the particle dispersion exhibits two power low regimes, with
+the lowest porosity geometry, $\phi=37.68\%$ having the clearest
+transition.  Again, the dispersion transforms from a ballistic to
+super-diffusive, and the anomalous disperion rate increases with the
+porosity.  For this example, the dispersion is nearly Fickean at the
+smallest porosity.
+\todo[inline]{BQ: This paragraph has some false statements.  Need to
+look closer at the data.  Might have accidently been looking at the
+other 20 body example ie. Fickean dispersion}
 
 \begin{figure}[H]
-\center
-\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian20b}
-\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
-eroding geometry initialized with 20 bodies.  The tortuosity is
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian20b}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height=0.8\linewidth]{./figs/20b_dense_second_moment_ref}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:ErodingLow20Transport} (a): The tortuosity of an
+eroding geometry initialized with 20 bodies.  When compared to the last
+example, the bodies are initially much closer together, and the porosity
+is smaller.  The tortuosity is
 calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
 dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
-as $p=0.1669$ and the root mean square deviation is $1.13 \times
-10^{-2}$.}
-\end{figure}
-
-\begin{figure}[H]
-\center
-\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
-\caption{\label{fig:Eroding20anomalousLow} The analysis of anomalous
-dispersion in 20 nearly touching bodies with respect to initial porosity
-(as p=30.67\%) and another seven porosities during the eroding. The dashed line
-correspondes to a porosity of 100\% and the dashed-dotted lines are lines
-of best fit with slope 0.9194 (as p=95\%), 0.8666 (as p=85.17\%), 
-0.8682 (as p=75.10\%), 0.9087 (as p=65.02\%), 
-0.9054 (as p=55.08\%), 0.7234 (as p=45.03\%), 
-0.6895 (as p=35.05\%), and 0.9225 (as p=30.67\%).}
+with $p=0.1669$, and the root mean square deviation is $1.13 \times
+10^{-2}$.  (b): The temporal evolution of $\sigma_\lambda$ as a function
+of time at eight different porosities.  The dashed line, which has slope
+one, corresponds to the ballistic dispersion $\sigma_\lambda \sim t$ if
+no bodies were present.  At early times, the particles undergo a
+ballistic motion, but once they have traveresd a few grains, the
+dispersion becomes super-dispersive with $\sigma_\lambda \sim
+t^{\alpha}$, $\alpha \in (1/2,1)$.  The dashed-dotted lines are lines of
+best fit with slope $0.92$ ($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$),
+$0.87$ ($\phi=75.10\%$), $0.91$ ($\phi=65.02\%$), $0.91$
+($\phi=55.08\%$), $0.72$ ($\phi=45.03\%$), $0.69$ ($\phi=35.05\%$), and
+$0.92$ ($\phi=30.67\%$).}
 \end{figure}
@@
 
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian20b}
+%\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
+%eroding geometry initialized with 20 bodies.  The tortuosity is
+%calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
+%dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
+%as $p=0.1669$ and the root mean square deviation is $1.13 \times
+%10^{-2}$.}
+%\end{figure}
+%
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
+%\caption{\label{fig:Eroding20anomalousLow} The analysis of anomalous
+%dispersion in 20 nearly touching bodies with respect to initial porosity
+%(as p=30.67\%) and another seven porosities during the eroding. The
+%dashed line correspondes to a porosity of 100\% and the dashed-dotted
+%lines are lines of best fit with slope 0.9194 (as p=95\%), 0.8666 (as
+%p=85.17\%), 0.8682 (as p=75.10\%), 0.9087 (as p=65.02\%), 0.9054 (as
+%p=55.08\%), 0.7234 (as p=45.03\%), 0.6895 (as p=35.05\%), and 0.9225 (as
+%p=30.67\%).}
+%\end{figure}
+
 \end{document}

### 2019-09-03 docs/transport/erosion_transport.tex
add two gap figures in section 4 of transport paper
add eight figures in section 6 of transport paper

@@
 vorticity. 
-
 \begin{figure}[H]
@@
 
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap} (a): The Delaunay triangulation of the porous media. 
+(b): The distribution of gaps from (a).}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We plot the distribution of the gap sizes at four equally spaced points
-in time in Figure~\ref{fig:Eroding100gap}.  At the initial configuration, there
-are 100 bodies and 318 pairs of neighbors.  The mean distance between
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with respect to porosity $\phi$.  
+(b): The variance of gaps with respect to porosity $\phi$.}
+\end{figure}
+
+We plot the distribution of the gap sizes at six porosities
+in Figure~\ref{fig:Eroding100gap_hist}.  At the initial configuration, there
+are 100 bodies and 258 pairs of neighbors.  The mean distance between
 these neighbors is $???  \times 10^{-???}$ and the variance is $???
 \times 10^{???}$.  As the bodies erode, the mean and variance of the
-distance between the bodies increases.  Finally, at the final time step,
-there are only 82 bodies and 254 pairs of neighbors.
+distance between the bodies increases.  Finally, when the porosity reaches $95.12\%$
+there are only 34 bodies and 74 pairs of neighbors.
+
 \begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/gap_hist100_50}
-\caption{100 bodies with 318 gaps at t= 0.005}
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics*[width =\linewidth]{./figs/hist100b_1}
+\caption{}
 \end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/gap_hist100_100}
-\caption{99 bodies with 312 gaps at t= 0.01}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/gap_hist100_150}
-\caption{94 bodies with 294 gaps at t= 0.015}
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics*[width =\linewidth]{./figs/hist100b_46}
+\caption{}
 \end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/gap_hist100_200}
-\caption{82 bodies with 254 gaps at t= 0.02}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap} The distribution of the gaps in the
-case of erosion of 100 bodies at four time steps.}
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics*[width =\linewidth]{./figs/hist100b_112}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics*[width =\linewidth]{./figs/hist100b_164}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics*[width =\linewidth]{./figs/hist100b_207}
+\caption{}
+\end{subfigure}%
+\begin{subfigure}[b]{0.3\textwidth}
+\includegraphics*[width =\linewidth]{./figs/hist100b_246}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap_hist} The distribution of the gaps in the
+case of erosion of 100 bodies at six porosities. (a) 100 bodies with 258 gaps as porosity $\phi = 50.09 \%$. 
+(b) 100 bodies with 258 gaps as porosity $\phi = 55.02 \%$. 
+(c) 97 bodies with 249 gaps as porosity $\phi = 65.03 \%$. 
+(d) 92 bodies with 234 gaps as porosity $\phi = 75.14 \%$. 
+(e) 75 bodies with 189 gaps as porosity $\phi = 85.07 \%$. 
+(f)} 34 bodies with 74 gaps as porosity $\phi = 95.12 \%$. 
 \end{figure}

### 2019-09-04 docs/transport/erosion_transport.tex
editing in section 6 of transport paper
add seven figures in section 4 & 6 of transport paper

@@
 \caption{\label{fig:Eroding100gap} (a): The Delaunay triangulation of the porous media. 
-(b): The distribution of gaps from (a).}
+(b): The distribution of gaps from (a) with the fitting curve of Weibull distribution.}
 \end{figure}
@@
 this point, a new Delaunay triangulation is formed. 
-
+{\color{red}In Figure~\ref{fig:Eroding100gap_mean_var}, 
+we record the gap distances between bodies neighbors and
+calculate the mean and variance with respect to porosities. 
+For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
+which means the eroding . 
+For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  }
 \begin{figure}[H]
@@
 \caption{\label{fig:Eroding100gap_hist} The distribution of the gaps in the
-case of erosion of 100 bodies at six porosities. (a) 100 bodies with 258 gaps as porosity $\phi = 50.09 \%$. 
-(b) 100 bodies with 258 gaps as porosity $\phi = 55.02 \%$. 
-(c) 97 bodies with 249 gaps as porosity $\phi = 65.03 \%$. 
-(d) 92 bodies with 234 gaps as porosity $\phi = 75.14 \%$. 
-(e) 75 bodies with 189 gaps as porosity $\phi = 85.07 \%$. 
-(f)} 34 bodies with 74 gaps as porosity $\phi = 95.12 \%$. 
+case of erosion of 100 bodies at six porosities and the fitting curves of Weibull distribution 
+described by the shape parameter $k > 0$ and the scale parameter $\lambda > 0$. 
+(a) 100 bodies with 258 gaps as porosity $\phi = 50.09 \%$ 
+and $(k, \lambda)=(1 .4650, 0.0605)$ for Weibull distribution. 
+(b) 100 bodies with 258 gaps as porosity $\phi = 55.02 \%$ 
+and $(k, \lambda)=( 1.9485, 0.0737)$ for Weibull distribution. 
+(c) 97 bodies with 249 gaps as porosity $\phi = 65.03 \%$ 
+and $(k, \lambda)=( 2.5682, 0.0965)$ for Weibull distribution. 
+(d) 92 bodies with 234 gaps as porosity $\phi = 75.14 \%$ 
+and $(k, \lambda)=( 2.7771, 0.1255)$ for Weibull distribution. 
+(e) 75 bodies with 189 gaps as porosity $\phi = 85.07 \%$ 
+and $(k, \lambda)=( 2.6235, 0.1713)$ for Weibull distribution. 
+(f) 34 bodies with 74 gaps as porosity $\phi = 95.12 \%$ 
+and $(k, \lambda)=( 1.9840, 0.3194)$ for Weibull distribution. }
 \end{figure}

### 2019-09-05 docs/transport/erosion_transport.tex
modify the caption of Figure 16 in transport paper

@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with respect to porosity $\phi$.  
-(b): The variance of gaps with respect to porosity $\phi$.}
+\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
+the variancewith of gaps in (b) with respect to porosity $\phi$. 
+Red stars are six selected porosities to have the details of  
+the disturbutions of gaps and fitting curves of the disturbutions 
+in Figure~\ref{fig:Eroding100gap_hist}.}
 \end{figure}

### 2019-09-05 docs/transport/erosion_transport.tex
small changes to results

--- 2019-09-04 docs/transport/erosion_transport.tex
@@
 \subsection{20 Bodies at a Medium Porosity}
+\label{sec:Eroding20}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 porosity is explained by the onset of channels where many tracers
-experience less variability in their velocities.
+experience less variability in their velocities.  For this example, the
+dispersion is nearly Fickean at the smallest porosity.
 
@@
 evolution of the particle spreading $\sigma_\lambda$.  As in the last
-example, we analyze the spreading at several different
-porosities and we use the reinsertion algorithm described in Section~\ref{sec:dispersion}
-to form sufficiently long trajectories.  For all the reported
-porosities, the particle dispersion exhibits two power low regimes, with
-the lowest porosity geometry, $\phi=37.68\%$ having the clearest
-transition.  Again, the dispersion transforms from a ballistic to
-super-diffusive, and the anomalous disperion rate increases with the
-porosity.  For this example, the dispersion is nearly Fickean at the
-smallest porosity.
-\todo[inline]{BQ: This paragraph has some false statements.  Need to
-look closer at the data.  Might have accidently been looking at the
-other 20 body example ie. Fickean dispersion}
+example, we analyze the spreading at several different porosities and we
+use the reinsertion algorithm described in Section~\ref{sec:dispersion}
+to form sufficiently long trajectories to observe an asymptotic
+dispersion rate.  For all the porosities, the dispersion is much closer
+to ballistic when compared to the results in
+Figure~\ref{fig:Eroding20Transport}.  However, there are still clear
+transitions from ballistic dynamics at early times to asymptotic
+super-diffusive dynamics.  In contrast to the lower porosity initial
+condition (Section~\ref{sec:Eroding20}), at early times the erosion
+results in a decrease in particle spreading. In particular, once erosion
+has eroded the first 5\% of the bodies, the particle spreading
+transitions from $\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim
+t^{0.69}$.  To explain this behavior, note that the velocity is fairly
+uniform, albeit small, at the initial condition (see
+Figure~\ref{fig:ErodingLow20vort}).  Then as the geometry erodes, the
+ratio of the fast and slow regions increases.  Since super-diffusive
+dispersion results from a tracers spending times in a both slow and fast
+regions, this results in an increase in the amount of super-dispersion.
+\todo[inline]{Still need to work on this and explain how it contrasts
+from the other 20 body example}
+\todo[inline]{Need a reference for last sentence}
 
@@
 example, the bodies are initially much closer together, and the porosity
-is smaller.  The tortuosity is
-calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
-dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
-with $p=0.1669$, and the root mean square deviation is $1.13 \times
-10^{-2}$.  (b): The temporal evolution of $\sigma_\lambda$ as a function
-of time at eight different porosities.  The dashed line, which has slope
-one, corresponds to the ballistic dispersion $\sigma_\lambda \sim t$ if
-no bodies were present.  At early times, the particles undergo a
-ballistic motion, but once they have traveresd a few grains, the
-dispersion becomes super-dispersive with $\sigma_\lambda \sim
-t^{\alpha}$, $\alpha \in (1/2,1)$.  The dashed-dotted lines are lines of
-best fit with slope $0.92$ ($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$),
-$0.87$ ($\phi=75.10\%$), $0.91$ ($\phi=65.02\%$), $0.91$
-($\phi=55.08\%$), $0.72$ ($\phi=45.03\%$), $0.69$ ($\phi=35.05\%$), and
-$0.92$ ($\phi=30.67\%$).}
+is smaller.  The tortuosity is calculated using the Eulerian
+method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
+fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.1669$, and the root
+mean square deviation is $1.13 \times 10^{-2}$.  (b): The temporal
+evolution of $\sigma_\lambda$ as a function of time at eight different
+porosities.  The dashed line, which has slope one, corresponds to the
+ballistic dispersion $\sigma_\lambda \sim t$ if no bodies were present.
+At early times, the particles undergo a ballistic motion, but once they
+have traversed a few grains, the dispersion becomes super-dispersive
+with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
+dashed-dotted lines are lines of best fit with slope $0.92$
+($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$), $0.87$ ($\phi=75.10\%$),
+$0.91$ ($\phi=65.02\%$), $0.91$ ($\phi=55.08\%$), $0.72$
+($\phi=45.03\%$), $0.69$ ($\phi=35.05\%$), and $0.92$ ($\phi=30.67\%$).}
 \end{figure}
@@
 porosity near 55\%.  Snapshots of the configurations and vorticity are
-in Figure~\ref{fig:Eroding100vort}.
+in Figure~\ref{fig:Eroding100vort}.  Again, by resolving near-contacts
+with the Barycentric quadrature rule, a stable simulation is possible
+with only $N_\iin = 256$ discretization points.  We use a time step size
+of $\Delta t = 10^{-4}.$
 
@@
 \includegraphics*[width =0.9\linewidth]{./figs/100b_50}
-\caption{100 bodies and porosity = 55.54\% at t= 0.005}
+\caption{}
+%\caption{100 bodies and porosity = 55.54\% at t= 0.005}
 \end{subfigure}%
@@
 \includegraphics*[width =1.1\linewidth]{./figs/100b_100}
-\caption{99 bodies and porosity = 62.98\% at t= 0.01}
+\caption{}
+%\caption{99 bodies and porosity = 62.98\% at t= 0.01}
 \end{subfigure}
@@
 \includegraphics*[width =0.9\linewidth]{./figs/100b_150}
-\caption{94 bodies and porosity = 72.22\% at t= 0.015}
+\caption{}
+%\caption{94 bodies and porosity = 72.22\% at t= 0.015}
 \end{subfigure}%
@@
 \includegraphics*[width =1.1\linewidth]{./figs/100b_200}
-\caption{82 bodies and porosity = 83.37\% at t= 0.02}
+\caption{}
+%\caption{82 bodies and porosity = 83.37\% at t= 0.02}
 \end{subfigure}
@@
   body, $N_\out = 1024$ points on the outer wall, a time-step of
-  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
-  $\sigma=10/256$.}
+  $\Dt=10^{-4}$.  Because of the large number of bodies, erosion creates
+  many channels connecting the inlet to the outlet.}
 \end{figure}
@@
 \begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height=0.8\linewidth]{./figs/100b_second_moment_long_ref}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100Transport} (a): The tortuosity of an
+eroding geometry initialized with 20 bodies.  When compared to the last
+example, the bodies are initially much closer together, and the porosity
+is smaller.  The tortuosity is calculated using the Eulerian
+method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
+fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.1669$, and the root
+mean square deviation is $1.13 \times 10^{-2}$.  (b): The temporal
+evolution of $\sigma_\lambda$ as a function of time at eight different
+porosities.  The dashed line, which has slope one, corresponds to the
+ballistic dispersion $\sigma_\lambda \sim t$ if no bodies were present.
+At early times, the particles undergo a ballistic motion, but once they
+have traversed a few grains, the dispersion becomes super-dispersive
+with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
+dashed-dotted lines are lines of best fit with slope $0.92$
+($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$), $0.87$ ($\phi=75.10\%$),
+$0.91$ ($\phi=65.02\%$), $0.91$ ($\phi=55.08\%$), $0.72$
+($\phi=45.03\%$), $0.69$ ($\phi=35.05\%$), and $0.92$ ($\phi=30.67\%$).}
+\caption[inline]{Fix this caption}
+\end{figure}
+
+\begin{figure}[H]
 \center
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with respect to porosity $\phi$.  
-(b): The variance of gaps with respect to porosity $\phi$.}
+\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with
+respect to porosity $\phi$.  (b): The variance of gaps with respect to
+porosity $\phi$.}
 \end{figure}

### 2019-09-05 docs/transport/erosion_transport.tex

@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with
-respect to porosity $\phi$.  (b): The variance of gaps with respect to
-porosity $\phi$.}
+\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
+the variancewith of gaps in (b) with respect to porosity $\phi$. 
+Red stars are six selected porosities to have the details of  
+the disturbutions of gaps and fitting curves of the disturbutions 
+in Figure~\ref{fig:Eroding100gap_hist}.}
 \end{figure}

### 2019-09-05 docs/transport/erosion_transport.tex
small change in the caption of Figure 16 in transport paper

--- 2019-09-05 docs/transport/erosion_transport.tex
@@
 \caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
-the variancewith of gaps in (b) with respect to porosity $\phi$. 
+the variance of gaps in (b) with respect to porosity $\phi$ of an
+eroding geometry initialized with 100 bodies . 
 Red stars are six selected porosities to have the details of  

### 2019-09-05 docs/transport/erosion_transport.tex
working on 100 body example

--- 2019-09-05 docs/transport/erosion_transport.tex
@@
 The tortuosity at all porosities from the initial condition until all
-the bodies have eroded is in Figure~\ref{fig:Eroding100tort_all}.  The
-initial tortuosity is around $T=1.2$ and decays towards $T=1$.  The
+the bodies have eroded is in Figure~\ref{fig:Eroding100Transport}(a).
+The initial tortuosity is around $T=1.2$ and decays towards $T=1$.  The
 tortuosities indicated by the blue dots are calculated using the
@@
 
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian100}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height=0.8\linewidth]{./figs/100b_second_moment_long_ref}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100Transport} (a): The tortuosity of an
-eroding geometry initialized with 20 bodies.  When compared to the last
-example, the bodies are initially much closer together, and the porosity
-is smaller.  The tortuosity is calculated using the Eulerian
-method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
-fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.1669$, and the root
-mean square deviation is $1.13 \times 10^{-2}$.  (b): The temporal
-evolution of $\sigma_\lambda$ as a function of time at eight different
-porosities.  The dashed line, which has slope one, corresponds to the
-ballistic dispersion $\sigma_\lambda \sim t$ if no bodies were present.
-At early times, the particles undergo a ballistic motion, but once they
-have traversed a few grains, the dispersion becomes super-dispersive
-with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
-dashed-dotted lines are lines of best fit with slope $0.92$
-($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$), $0.87$ ($\phi=75.10\%$),
-$0.91$ ($\phi=65.02\%$), $0.91$ ($\phi=55.08\%$), $0.72$
-($\phi=45.03\%$), $0.69$ ($\phi=35.05\%$), and $0.92$ ($\phi=30.67\%$).}
-\caption[inline]{Fix this caption}
-\end{figure}
-
-\begin{figure}[H]
-\center
-\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian100}
-\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
-approach of tortuosity.  The blue dots are Eulerian approach of
-tortuosity and the red stars and square are Lagrangian approach of
-tortuosity.  The dash line is the fitting line
-$\widehat{T}(\phi)=\phi^{-p}$ as $p=0.2459$ and the root-mean-square
-error is $5.5 \times 10^{-3}$.  We note that the model
-$\widehat{T}(\phi) = 1-p\ln(\phi)$, with $p=0.2631$ has a comparable
-root-mean-square error of $5.2 \times 10^{-3}$.}
-\end{figure}
-
 Next, we use the 1000 tracer trajectories to compute the second
-(Figure~\ref{fig:Eroding100anomalous}) moments of the streamlines at
+(Figure~\ref{fig:Eroding100Transport}(b)) moments of the streamlines at
 various porosities.  At high porosities, the first moment is similar to
@@
 
-\begin{figure}
-\center
-\includegraphics*[width =0.55\linewidth]{./figs/100b_second_moment_long_ref}
-\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
-dispersion in 100 bodies with respect to initial porosity
-(as p=50.09\%) and another five porosities during the eroding. The dashed line
-correspondes to a porosity of 100\% and the dashed-dotted lines are lines
-of best fit with slope 1.1135 (as p=95.12\%), 0.6825 (as p=85.07\%), 
-0.7347 (as p=75.14\%), 0.5915 (as p=65.03\%), 
-0.6107 (as p=55.02\%), and 0.7 (as p=50.09\%).}
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height=0.8\linewidth]{./figs/100b_second_moment_long_ref}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100Transport} (a): The tortuosity of an
+eroding geometry initialized with 100 bodies.  The tortuosity is calculated using the Eulerian
+method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
+fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2459$, and the root
+mean square deviation is $5.50 \times 10^{-3}$.  We note that the model
+$\widehat{T}(\phi) = 1 - p \ln (\phi)$, with $p=0.2631$ has a comparable
+root-mean-square error of $5.20 \times 10^{-3}$.  (b): The temporal
+evolution of $\sigma_\lambda$ as a function of time at six different
+porosities.  The dashed line, which has slope one, corresponds to the
+ballistic dispersion $\sigma_\lambda \sim t$ if no bodies were present.
+At early times, the particles undergo a ballistic motion, but once they
+have traversed a few grains, the dispersion becomes super-dispersive
+with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
+dashed-dotted lines are lines of best fit with slope $1.11$
+($\phi=95.12\%$), $0.68$ ($\phi=85.07\%$), $0.73$ ($\phi=75.14\%$),
+$0.59$ ($\phi=65.03\%$), $0.61$ ($\phi=55.02\%$), and $0.70$
+($\phi=50.09\%$).}
 \end{figure}
@@
 %\end{figure}
+%
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian100}
+%\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
+%approach of tortuosity.  The blue dots are Eulerian approach of
+%tortuosity and the red stars and square are Lagrangian approach of
+%tortuosity.  The dash line is the fitting line
+%$\widehat{T}(\phi)=\phi^{-p}$ as $p=0.2459$ and the root-mean-square
+%error is $5.5 \times 10^{-3}$.  We note that the model
+%$\widehat{T}(\phi) = 1-p\ln(\phi)$, with $p=0.2631$ has a comparable
+%root-mean-square error of $5.2 \times 10^{-3}$.}
+%\end{figure}
+%
+%\begin{figure}
+%\center
+%\includegraphics*[width =0.55\linewidth]{./figs/100b_second_moment_long_ref}
+%\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
+%dispersion in 100 bodies with respect to initial porosity
+%(as p=50.09\%) and another five porosities during the eroding. The dashed line
+%correspondes to a porosity of 100\% and the dashed-dotted lines are lines
+%of best fit with slope 1.1135 (as p=95.12\%), 0.6825 (as p=85.07\%), 
+%0.7347 (as p=75.14\%), 0.5915 (as p=65.03\%), 
+%0.6107 (as p=55.02\%), and 0.7 (as p=50.09\%).}
+%\end{figure}
 

### 2019-09-06 docs/transport/erosion_transport.tex
working on results section

--- 2019-09-05 docs/transport/erosion_transport.tex
@@
 \subsection{Pore Throat Size}
+\label{sec:throats}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
-function of the porosity from the initial porosity of $0.38$ until all
-the bodies have eroded.  The tortuosity is computed with both the length
-of the streamlines~\eqref{eqn:tortuosity1} (red marks) and using the
-spatial average of the velocity on an Eulerian
+function of the porosity. The initial porosity is $\phi = 37.68\%$, and
+the initial tortuosity is $1.16$.  The tortuosity is computed with both
+the length of the streamlines~\eqref{eqn:tortuosity1} (red marks) and
+using the spatial average of the velocity on an Eulerian
 grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
@@
 Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
-function of normalized time.  Initially, 62\% of the geometry contains
-eroding bodies corresponding to a porosity of $0.38$, and the area
-fraction decreases to 0 as the bodies erode.  The trend of the area
-fraction resembles our previous work~\cite{qua-moo2018} (Figure 10(a)),
-but with a larger initial area fraction.  In
+function of normalized time.  The general trend of the area fraction
+resembles our previous work~\cite{qua-moo2018} (Figure 10(a)), but with
+a larger initial area fraction.  In
 Figure~\ref{fig:Eroding20flowrate}(b), we plot the flow rate $U$
@@
 We compute the tortuosity using the Eulerian
-method~\eqref{eqn:tortuosity2}. In
+method~\eqref{eqn:tortuosity2}.  The initial porosity is $30.67\%$ and
+the initial tortuosity is $1.24$.  In
 Figure~\ref{fig:ErodingLow20Transport}(a), we plot the tortuosity with
@@
 t^{0.69}$.  To explain this behavior, note that the velocity is fairly
-uniform, albeit small, at the initial condition (see
+uniform, albeit small, at the initial configuration (see
 Figure~\ref{fig:ErodingLow20vort}).  Then as the geometry erodes, the
@@
 dispersion results from a tracers spending times in a both slow and fast
-regions, this results in an increase in the amount of super-dispersion.
+regions, this results in an increase in the rate of super-dispersion.
 \todo[inline]{Still need to work on this and explain how it contrasts
@@
 As a final example, we consider 100 eroding bodies with an initial
-porosity near 55\%.  Snapshots of the configurations and vorticity are
-in Figure~\ref{fig:Eroding100vort}.  Again, by resolving near-contacts
-with the Barycentric quadrature rule, a stable simulation is possible
-with only $N_\iin = 256$ discretization points.  We use a time step size
-of $\Delta t = 10^{-4}.$
+porosity near 50\%.  Snapshots of the configurations and vorticity are in
+Figure~\ref{fig:Eroding100vort}.  Again, by resolving near-contacts with
+the Barycentric quadrature rule, a stable simulation is possible with
+only $N_\iin = 256$ discretization points.  We use a time step size of
+$\Delta t = 10^{-4}.$
 
@@
 \includegraphics*[width =0.9\linewidth]{./figs/100b_50}
-\caption{}
-%\caption{100 bodies and porosity = 55.54\% at t= 0.005}
+\caption{100 bodies, $\phi = 55.54\%$}
 \end{subfigure}%
@@
 \includegraphics*[width =1.1\linewidth]{./figs/100b_100}
-\caption{}
-%\caption{99 bodies and porosity = 62.98\% at t= 0.01}
+\caption{99 bodies, $\phi = 62.98\%$}
 \end{subfigure}
@@
 \includegraphics*[width =0.9\linewidth]{./figs/100b_150}
-\caption{}
-%\caption{94 bodies and porosity = 72.22\% at t= 0.015}
+\caption{94 bodies, $\phi = 72.22\%$}
 \end{subfigure}%
@@
 \includegraphics*[width =1.1\linewidth]{./figs/100b_200}
-\caption{}
-%\caption{82 bodies and porosity = 83.37\% at t= 0.02}
+\caption{82 bodies, $\phi = 83.67\%$}
 \end{subfigure}
@@
 to the left of the porous region at $x=-1$.  The porosity at this
-instance in time is $62.98\%$ and the maximum velocity at $x=-1$ is
+time is $62.98\%$ and the maximum velocity at $x=-1$ is
 $3.90 \times 10^{-4}$. The initial velocity of the tracers is
@@
 and this results in trajectories with significantly different lengths.
-At this instance in time one the tracers travels 25.5\% farther than it
-would have if the bodies had been absent, and the average tracer
-travelled 12\% farther than it would have if the bodies were absent.
-Therefore, at this instance in time, the tortuosity is $1.12$.
+At this time one the tracers travels 25.5\% farther than it would have
+if the bodies had been absent, and the average tracer travelled 12\%
+farther than it would have if the bodies were absent, so the tortuosity
+is $1.12$.
 
@@
 with 100 bodies when the porosity is 62.98\%.  (a) The x-component
-velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.9021
+velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.90
 \times 10^{-4}$ at equal spreading tracers on the cross section x = -1.
@@
 trajectories of 200 tracers released at $x = -1$ in the fluid with
-multiple bodies.}
+multiple bodies.  The discontinuities in the local tortuosity correspond
+to neighboring streamlines whose lengths are significantly different
+because they pass opposite sides of an eroding body.}
 \end{figure}
 
-The tortuosity at all porosities from the initial condition until all
-the bodies have eroded is in Figure~\ref{fig:Eroding100Transport}(a).
-The initial tortuosity is around $T=1.2$ and decays towards $T=1$.  The
-tortuosities indicated by the blue dots are calculated using the
-Eulerian approach~\eqref{eqn:tortuosity2}, while the red marks use the
-Lagrangian approach~\eqref{eqn:tortuosity1}.  Again, the two methods
-give comparable results indicating that any recirculation is small and
-negligible.  As in the previous examples, the tortuosity depends on the
-porosity through a power law model with a small root-mean-squared error
-of $5.2 \times 10^{-3}$.  For this example, the logarithm tortuosity
-model $\hat{T}(\phi) = 1 - p \ln(\phi)$ achieves a similar
-root-mean-squared error.  The tortuosity has one interesting feature
-near the end of the simulation where it suddenly increases.  This
-behavior can be explained by ... \todo[inline]{S-H: Show me what is
-going on here as we discussed.}
-
+In Figure~\ref{fig:Eroding100Transport}(a), we plot the tortuosity as a
+function of the porosity.  The initial geometry has a porosity of $\phi
+= 50.09\%$ and the tortuosity is $T = 1.20$.  The tortuosity is computed
+with both the length of the streamlines~\eqref{eqn:tortuosity1} (red
+marks) and using the spatial average of the velocity on an Eulerian
+grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
+to the porosity of the geometry in Figure~\ref{fig:Eroding100tort}(c).
+Again, the two tortuosity formulas give similar results.  For this
+geometry, the tortuosity decreases monotonically at almost all
+porosities.  However, the tortuosity undergoes a sudden increase near
+the end of the simulation.  The increase is caused by a single small
+body near the middle of the channel being completely eroded.  While this
+results in straighter streamlines, therefore reducing $\lambda$, the
+horizontal flow, $u_x(y)$ increases since there is no longer a no-slip
+boundary.  At the very late stages of erosion, we have observed that
+when a single small body finishes eroding, this can result in a sudden
+increase in the tortuosity.  We also computed the lines of best fit
+using the porosity-tortuosity models~\eqref{eqn:tortuosityModels}.  The
+black dashed line in Figure~\ref{fig:Eroding100Transport}(a) is the line
+of best fit
+\begin{align}
+  \widehat{T}(\phi) = \phi^{-0.2459}
+\end{align}
+with a root-mean-square error of $5.50 \times 10^{-3}$.  We note a
+slightly better root-mean-square error of $5.20 \times 10^{-3}$ is
+possible with the model
+\begin{align}
+  \widehat{T}(\phi) = 1 - 0.2631 \ln(\phi).
+\end{align}
+
+\todo[inline]{do better job of explaining why diesperions does what it
+does.  For this problem, there are lots more of small bodies rather than
+a few big ones.  Therefore, after reinsertion, many of the bodies are
+placed in a ballistic regime which means that anoamlous dispersion is no
+longer observed.}
 Next, we use the 1000 tracer trajectories to compute the second
@@
 the first-moment of trajectories in a empty channel (black dashed line).
-At smaller porosities, the first moment is always linear, but larger
-slopes indicate that the length of the trajectories are longer at lower
-porosities \todo[inline]{Don't understand how this is the case}.  The
-onset of anomalous dispersion is observed in
-Figure~\ref{fig:Eroding100anomalous}. At early times, the particle
-spreading is comparable to that of an open channel (dashed curve)
-corresponding to the ballistic regime.  However, as the trajectories
-traverse the geometry, a transition to a super-dispersive case,
-especially at low porosities, is evident.  The dashed-dotted line
-corresponds has a slope less than 1 indicating the long time behavior of
-the trajectories
-\begin{align*}
-  \sigma_\lambda \sim t^{0.8715}.
-\end{align*}
+Similar to the other previous examples, we initially observe ballistic
+motion, and then super-diffusive dispersion.  However, similar to the
+example in Figure~\ref{fig:ErodingLow20Transport}(b), the anomalous
+dispersion rate is not growing with the porosity.  Therefore, it appears
+that the dispersion rate in an eroding geometry depends not only the
+porosity, but also the location and shape of the bodies.
 
@@
 \caption{\label{fig:Eroding100Transport} (a): The tortuosity of an
-eroding geometry initialized with 100 bodies.  The tortuosity is calculated using the Eulerian
-method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
-fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2459$, and the root
-mean square deviation is $5.50 \times 10^{-3}$.  We note that the model
-$\widehat{T}(\phi) = 1 - p \ln (\phi)$, with $p=0.2631$ has a comparable
-root-mean-square error of $5.20 \times 10^{-3}$.  (b): The temporal
-evolution of $\sigma_\lambda$ as a function of time at six different
-porosities.  The dashed line, which has slope one, corresponds to the
-ballistic dispersion $\sigma_\lambda \sim t$ if no bodies were present.
-At early times, the particles undergo a ballistic motion, but once they
-have traversed a few grains, the dispersion becomes super-dispersive
-with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
-dashed-dotted lines are lines of best fit with slope $1.11$
-($\phi=95.12\%$), $0.68$ ($\phi=85.07\%$), $0.73$ ($\phi=75.14\%$),
-$0.59$ ($\phi=65.03\%$), $0.61$ ($\phi=55.02\%$), and $0.70$
-($\phi=50.09\%$).}
+eroding geometry initialized with 100 bodies.  The tortuosity is
+calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
+dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
+with $p=0.2459$, and the root mean square deviation is $5.50 \times
+10^{-3}$.  We note that the model $\widehat{T}(\phi) = 1 - p \ln
+(\phi)$, with $p=0.2631$ has a comparable root-mean-square error of
+$5.20 \times 10^{-3}$.  (b): The temporal evolution of $\sigma_\lambda$
+as a function of time at six different porosities.  The dashed line,
+which has slope one, corresponds to the ballistic dispersion
+$\sigma_\lambda \sim t$ if no bodies were present.  At early times, the
+particles undergo a ballistic motion, but once they have traversed a few
+grains, the dispersion becomes super-dispersive with $\sigma_\lambda
+\sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The dashed-dotted lines are
+lines of best fit with slope $1.11$ ($\phi=95.12\%$), $0.68$
+($\phi=85.07\%$), $0.73$ ($\phi=75.14\%$), $0.59$ ($\phi=65.03\%$),
+$0.61$ ($\phi=55.02\%$), and $0.70$ ($\phi=50.09\%$).}
 \end{figure}
@@
 anomalous dispersion rate can be linked to channel widths between solid
-bodies.  We construct a Delaunay triangulation with the centers of the
-eroding bodies corresponding to the vertices of the triangles.  Then, if
-the side of a triangle connects two vertices, we call the bodies
-neighbors.  Then, for each pair of neighbors, we measure the distance
-between the bodies.  Once a Delaunay triangulation is formed, it is used
-for all subsequent time steps until a body completely disappears.  At
-this point, a new Delaunay triangulation is formed. 
-{\color{red}In Figure~\ref{fig:Eroding100gap_mean_var}, 
-we record the gap distances between bodies neighbors and
-calculate the mean and variance with respect to porosities. 
-For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
-which means the eroding . 
-For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  }
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
-the variancewith of gaps in (b) with respect to porosity $\phi$. 
-Red stars are six selected porosities to have the details of  
-the disturbutions of gaps and fitting curves of the disturbutions 
-in Figure~\ref{fig:Eroding100gap_hist}.}
-\end{figure}
-
-We plot the distribution of the gap sizes at six porosities
-in Figure~\ref{fig:Eroding100gap_hist}.  At the initial configuration, there
-are 100 bodies and 258 pairs of neighbors.  The mean distance between
-these neighbors is $???  \times 10^{-???}$ and the variance is $???
-\times 10^{???}$.  As the bodies erode, the mean and variance of the
-distance between the bodies increases.  Finally, when the porosity reaches $95.12\%$
-there are only 34 bodies and 74 pairs of neighbors.
+bodies.  As described in Section~\ref{sec:throats}, we use a Delaunay
+triangulation to define neighboring eroding bodies, and we compute the
+throat size by finding the closest distance between all neighboring
+bodies.  Once all throat sizes are computed, we analyze their
+distribution as a function of the porosity.  In
+Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the throat
+sizes at six porosities throughout the erosion process.
 
@@
 \end{figure}
+
+In Figure~\ref{fig:Eroding100gap_mean_var},
+we plot the mean and variance of the throat sizes as a function of the
+porosity.  While the mean steadily grows with the porosity, the variance
+remains relatively flat for a wide range of porosities.
+
+In Figure~\ref{fig:Eroding100gap_mean_var}, 
+we record the gap distances between bodies neighbors and
+calculate the mean and variance with respect to porosities. 
+For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
+which means the eroding . 
+For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and
+the variance with of gaps in (b) with respect to porosity $\phi$.  Red
+stars are six selected porosities to have the details of  the
+distribution of gaps and fitting curves of the distributions in
+Figure~\ref{fig:Eroding100gap_hist}.}
+\end{figure}
+
+We plot the distribution of the gap sizes at six porosities
+in Figure~\ref{fig:Eroding100gap_hist}.  At the initial configuration, there
+are 100 bodies and 258 pairs of neighbors.  The mean distance between
+these neighbors is $???  \times 10^{-???}$ and the variance is $???
+\times 10^{???}$.  As the bodies erode, the mean and variance of the
+distance between the bodies increases.  Finally, when the porosity reaches $95.12\%$
+there are only 34 bodies and 74 pairs of neighbors.
 

### 2019-09-09 docs/transport/erosion_transport.tex
working through some of the results

@@
 Figure~\ref{fig:Eroding20Transport}.  However, there are still clear
-transitions from ballistic dynamics at early times to asymptotic
-super-diffusive dynamics.  In contrast to the lower porosity initial
-condition (Section~\ref{sec:Eroding20}), at early times the erosion
-results in a decrease in particle spreading. In particular, once erosion
-has eroded the first 5\% of the bodies, the particle spreading
-transitions from $\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim
-t^{0.69}$.  To explain this behavior, note that the velocity is fairly
-uniform, albeit small, at the initial configuration (see
-Figure~\ref{fig:ErodingLow20vort}).  Then as the geometry erodes, the
-ratio of the fast and slow regions increases.  Since super-diffusive
-dispersion results from a tracers spending times in a both slow and fast
-regions, this results in an increase in the rate of super-dispersion.
-\todo[inline]{Still need to work on this and explain how it contrasts
-from the other 20 body example}
-\todo[inline]{Need a reference for last sentence}
+transitions from ballistic dynamics to asymptotic super-diffusive
+dynamics.  In contrast to the lower porosity initial condition
+(Section~\ref{sec:Eroding20}), at early times the erosion results in a
+decrease in dispersion rate. In particular, once erosion has eroded the
+first 5\% of the bodies, the particle spreading transitions from
+$\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim t^{0.69}$.  To
+explain this behavior, recall that anomalous dispersion is caused by
+tracers spending time in both the fast and slow regimes.  Since the
+initial configuration has a reasonably uniform velocity (see
+Figure~\ref{fig:ErodingLow20vort}), albeit a small one, the dispersion
+is nearly ballistic. However, as the geometry erodes, the flow becomes
+more intermittent, and this results in an increased anomalous dispersion
+rate~\cite{dea-leb-den-tar-bol-dav2013}.  Then, as the bodies continue
+to erode, the geometry channelizes, and most tracers are transported
+with a large velocity through the channels, again resulting in a nearly
+ballistic motion~\cite{sie-ili-pri-riv-gua2019}.
 
@@
 
-\todo[inline]{do better job of explaining why diesperions does what it
-does.  For this problem, there are lots more of small bodies rather than
-a few big ones.  Therefore, after reinsertion, many of the bodies are
-placed in a ballistic regime which means that anoamlous dispersion is no
-longer observed.}
-Next, we use the 1000 tracer trajectories to compute the second
-(Figure~\ref{fig:Eroding100Transport}(b)) moments of the streamlines at
-various porosities.  At high porosities, the first moment is similar to
-the first-moment of trajectories in a empty channel (black dashed line).
-Similar to the other previous examples, we initially observe ballistic
-motion, and then super-diffusive dispersion.  However, similar to the
-example in Figure~\ref{fig:ErodingLow20Transport}(b), the anomalous
-dispersion rate is not growing with the porosity.  Therefore, it appears
-that the dispersion rate in an eroding geometry depends not only the
-porosity, but also the location and shape of the bodies.
+In Figure~\ref{fig:Eroding100Transport}(b), we use the 1000 tracer
+trajectories to compute the asymptotic dispersion rates at various
+porosities.  Again, we initially observe ballistic motion (black dashed
+line), and then super-diffusive dispersion.  Similar to the example in
+Figure~\ref{fig:ErodingLow20Transport}(b), the anomalous dispersion rate
+is not growing with the porosity.  Therefore, it appears that the
+dispersion rate in an eroding geometry depends not only the porosity,
+but also the location and shape of the bodies.  Finally, at the highest
+porosity, anomalous dispersion is only observed briefly in the time
+interval $(0.5,1)$, and then transitions back to a ballistic regime.
+Since the bodies are so small at this high porosity, after reinsertion,
+the streamline is not significantly deflected by any of the bodies, and
+this results in a ballistic regime.
 
@@
 
-Finally, using network models for flow in porous media~\cite{}, the
-anomalous dispersion rate can be linked to channel widths between solid
-bodies.  As described in Section~\ref{sec:throats}, we use a Delaunay
-triangulation to define neighboring eroding bodies, and we compute the
-throat size by finding the closest distance between all neighboring
-bodies.  Once all throat sizes are computed, we analyze their
-distribution as a function of the porosity.  In
-Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the throat
-sizes at six porosities throughout the erosion process.
+Finally, we investigate the effects of erosion on pore sizes.  The
+distribution of the pore sizes can be directly related to the
+distribution of the velocity, and thus effects the
+tortuosity~\cite{den-ica-hid2018} and anomalous
+dispersion~\cite{dea-qua-bir-jua2018}. In addition, the pore sizes are
+required in network models~\cite{bry-mel-cad1993, bry-kin-mel1993}.  As
+described in Section~\ref{sec:throats}, we use a Delaunay triangulation
+to define neighboring eroding bodies, and we compute the throat size by
+finding the closest distance between all neighboring bodies.  Once all
+throat sizes are computed, we analyze their distribution as a function
+of the porosity.
+
+In Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the pore
+throat sizes at six porosities of the erosion process. These
+distributions have been modelled with Weibull
+distributions~\cite{ioa-cha1993}, and we superimpose the Weibull
+distribution with the same first two moments as the data.  The
+parameters that parameterize the distribution, $(k,\lambda)$, are
+included in the caption of Figure~\ref{fig:Eroding100gap_hist}.  In
+Figure~\ref{fig:Eroding100gap_mean_var}, we plot the mean and variance
+of the throat sizes as a function of the porosity.  At low porosities,
+the mean grows roughly linearly and the variance is roughly constant
+until about porosity $\phi = 0.85$.  At this point, both the mean and
+variance of the gap sizes quickly grow.
 
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_1}
-\caption{}
+\caption{100 bodies, 258 gaps}
 \end{subfigure}%
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_46}
-\caption{}
+\caption{100 gaps, 258 gaps}
 \end{subfigure}%
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_112}
-\caption{}
+\caption{97 bodies, 249 gaps}
 \end{subfigure}
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_164}
-\caption{}
+\caption{92 bodies, 234 gaps}
 \end{subfigure}%
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_207}
-\caption{}
+\caption{75 bodies, 189 gaps}
 \end{subfigure}%
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_246}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap_hist} The distribution of the gaps in the
-case of erosion of 100 bodies at six porosities and the fitting curves of Weibull distribution 
-described by the shape parameter $k > 0$ and the scale parameter $\lambda > 0$. 
-(a) 100 bodies with 258 gaps as porosity $\phi = 50.09 \%$ 
-and $(k, \lambda)=(1 .4650, 0.0605)$ for Weibull distribution. 
-(b) 100 bodies with 258 gaps as porosity $\phi = 55.02 \%$ 
-and $(k, \lambda)=( 1.9485, 0.0737)$ for Weibull distribution. 
-(c) 97 bodies with 249 gaps as porosity $\phi = 65.03 \%$ 
-and $(k, \lambda)=( 2.5682, 0.0965)$ for Weibull distribution. 
-(d) 92 bodies with 234 gaps as porosity $\phi = 75.14 \%$ 
-and $(k, \lambda)=( 2.7771, 0.1255)$ for Weibull distribution. 
-(e) 75 bodies with 189 gaps as porosity $\phi = 85.07 \%$ 
-and $(k, \lambda)=( 2.6235, 0.1713)$ for Weibull distribution. 
-(f) 34 bodies with 74 gaps as porosity $\phi = 95.12 \%$ 
-and $(k, \lambda)=( 1.9840, 0.3194)$ for Weibull distribution. }
+\caption{34 bodies, 74 gaps}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap_hist} The distribution of the gaps in
+the case of 100 bodies eroding at six porosities. The black curves are
+Weibull distributions whose first and second moments agree with the
+data. The porosities and Weibull distribution parameters $(k,\lambda)$
+at each of the porosities are: (a) $\phi = 50.09\%$ and
+$(k,\lambda)=(1.4650,0.0605)$; (b) $\phi = 55.02\%$ and
+$(k,\lambda)=(1.9485,0.0737)$; (c) $\phi = 65.03\%$ and
+$(k,\lambda)=(2.5682,0.0965)$; (d) $\phi = 75.14\%$ and
+$(k,\lambda)=(2.7771,0.1255)$; (e) $\phi = 85.07\%$ and
+$(k,\lambda)=(2.6235,0.1713)$; (f) $\phi = 95.12\%$ and
+$(k,\lambda)=(1.9840, 0.3194)$.}
 \end{figure}
 
-In Figure~\ref{fig:Eroding100gap_mean_var},
-we plot the mean and variance of the throat sizes as a function of the
-porosity.  While the mean steadily grows with the porosity, the variance
-remains relatively flat for a wide range of porosities.
-
-In Figure~\ref{fig:Eroding100gap_mean_var}, 
-we record the gap distances between bodies neighbors and
-calculate the mean and variance with respect to porosities. 
-For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
-which means the eroding . 
-For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  
 \begin{figure}[H]
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and
-the variance with of gaps in (b) with respect to porosity $\phi$.  Red
-stars are six selected porosities to have the details of  the
-distribution of gaps and fitting curves of the distributions in
-Figure~\ref{fig:Eroding100gap_hist}.}
+\caption{\label{fig:Eroding100gap_mean_var} The mean (a) and variance
+(b) of the gap sizes of an eroding geometry.  The red stars correspond
+to the six porosities in Figure~\ref{fig:Eroding100gap_hist}.}
 \end{figure}
-
-We plot the distribution of the gap sizes at six porosities
-in Figure~\ref{fig:Eroding100gap_hist}.  At the initial configuration, there
-are 100 bodies and 258 pairs of neighbors.  The mean distance between
-these neighbors is $???  \times 10^{-???}$ and the variance is $???
-\times 10^{???}$.  As the bodies erode, the mean and variance of the
-distance between the bodies increases.  Finally, when the porosity reaches $95.12\%$
-there are only 34 bodies and 74 pairs of neighbors.
-
-%\begin{figure}[H]
-%\begin{center}
-%\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
-%\caption{\label{fig:Eroding100tracer} The historical trajectories of 
-%200 tracers released at x = -1 in the fluid with multiple bodies.}
-%\end{center}
-%\end{figure}
-
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
-%\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of 
-%local tortuosity $\tau$ at two neighboring tracers in
-%100 bodies eroding when the porosity is 62.98 \%
-%and the tortuosity is 1.1182. The same color of a pair of trajectories 
-%means they are from two neighboring tracers.}
-%\end{figure}
 
@@
 %\end{figure}
+%
+%\begin{figure}[H]
+%\begin{center}
+%\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
+%\caption{\label{fig:Eroding100tracer} The historical trajectories of 
+%200 tracers released at x = -1 in the fluid with multiple bodies.}
+%\end{center}
+%\end{figure}
+
+%\begin{figure}[H]
+%\center
+%\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
+%\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of 
+%local tortuosity $\tau$ at two neighboring tracers in
+%100 bodies eroding when the porosity is 62.98 \%
+%and the tortuosity is 1.1182. The same color of a pair of trajectories 
+%means they are from two neighboring tracers.}
+%\end{figure}
 

### 2019-09-11 docs/transport/erosion_transport.tex
working on edits to intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Flow in many natural occurring geometries involves flows that vary over
-many orders of magnitude.  \todo[]{The grammar in the first sentence is awkward: Flow in ... involves flows?}
-For example, the length scales of a porous
-media can vary from $10^{-6}m$ to
-$10^{-1}m$~\cite{mil-chr-imh-mcb-ped1998}.  Porous media flow plays an
-important role in several environmental and industrial applications.
-Therefore, understanding the dynamics of pore-scale flow is central to
-upscale the governing fluid equations, characterize
-dispersion~\cite{saf1959}, and quantify mixing. However, because of the
-large disparity of length and velocity scales, constitutive laws that
-link the microscopic scale to macroscopic scale must be
-developed~\cite{mil-chr-imh-mcb-ped1998}.  Therefore, to find closure
-formulas, accurate simulations at microscopic scales must be performed
-and analyzed.  A few examples of closure formulas and coarse-grained
-variables include
-pressure-saturation-permeability~\cite{mil-chr-imh-mcb-ped1998},
-permeability-porosity~\cite{dar-mcc1998, car1937, won-kop-tom1984},
-first passage time distribution~\cite{ber-sch-sil2000,
-hym-den-hag-kan2019, cve-che-wen1996}, tortuosity~\cite{hak-com-den2019,
-mat-kha-koz2008, dud-koz-mat2011, kop-kat-tim1996}, concentration
+Porous media flow plays an important role in several environmental and
+industrial applications.  To understand flow in a porous media, it is
+important to accurately characterize the length scales and velocity
+scales. However, this is very challenging since for a single porous
+geometry, the length scales that can vary from $10^{-6}m$ to
+$10^{-1}m$~\cite{mil-chr-imh-mcb-ped1998}, and the velocity scales that
+can vary from $10^{-1}m/$day to $10m/$day~\cite{kut-scr-dav-ham1995}.
+However, resolving all these scales is fundamental to develop meaningful
+constitutive relationships that link the microscopic to the macroscopic
+scale~\cite{mil-chr-imh-mcb-ped1998}, characterize
+dispersion~\cite{saf1959}, and quantify
+mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
+Coarse-grained variables are often used to study flow in a porous media,
+and examples include pressure-saturation-permeability
+relationships~\cite{mil-chr-imh-mcb-ped1998}, permeability-porosity
+relationships~\cite{dar-mcc1998, car1937, won-kop-tom1984}, first
+passage time distributions~\cite{ber-sch-sil2000, hym-den-hag-kan2019,
+cve-che-wen1996}, tortuosities~\cite{hak-com-den2019, mat-kha-koz2008,
+dud-koz-mat2011, kop-kat-tim1996}, concentration
 distributions~\cite{ica-den2019, bel-sal-rin1992}, flow
@@
 connectivity~\cite{knu-car2005, wes-blo-gra2001}, pore
-distributions~\cite{ali-par-wei-bre2017}, and anomalous
+distributions~\cite{ali-par-wei-bre2017}, anomalous
 dispersion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
-sie-ili-pri-riv-gua2019}.
-
-In many applications, the fluid transport continuously changes the pore
-structure.  This is particularly common in geophysical flows where
-erosion alters the porous matrix.  In this work, we investigate flow in
-eroded porous media.  By introducing erosion, there is a two-way
-coupling between the hydrodynamics and the mechanical alteration of the
-complex porous geometry.  Transport in porous geometries that have
-undergone erosion finds applications in aquifers~\cite{cve-che-wen1996,
-sud1986}, solute transport in groundwater flow~\cite{dag1987,
-kon-bre1978}.  Porous geometries that have undergone erosion have
+sie-ili-pri-riv-gua2019}, and more.
+
+Flow in porous media is often studied for a fixed geometry, but for many
+physical processes, the geometry evolves with the flow. For example,
+melting~\cite{}\todo[inline]{Natural convection solid/liquid phase
+change in porous media}, dissolution~\cite{kan-zha-che-he2002},
+deposition~\cite{joh-eli1995}, and biofilm
+growth~\cite{tan-val-wer2015}.  Here, we focus on erosion which is
+fluid-mechanical process that is prevalent in many geophysical and
+hydrological applications.  For example, contaminant transport through
+aquifers~\cite{cve-che-wen1996} and groundwater~\cite{dag1987,
+kon-bre1978} is largely effected by the nature of the eroded porous
+geometry.  Porous geometries that have undergone erosion have
 certain characteristics.  For example, the geometry often has regions of
 high porosity that connect the inlet to the outlet.  This channelization
-results in velocity scales that can vary over several orders of
-magnitude~\cite{all-hea-lab-rei2002}.  Moreover, the channelization
-results in a geometry that is largely heterogeneous and anisotropic, and
-this affects heat transfer through the medium~\cite{nil-sto1990,
+results in velocity scales that vary over several orders of
+magnitude~\cite{all-hea-lab-rei2002} (see
+Figure~\ref{fig:Eroding50vel}).  Moreover, the channelization results in
+a geometry that is largely heterogeneous and anisotropic, and this
+affects the transfer other other quantities such as a contaminant or
+heat~\cite{nil-sto1990,
 ree-sto1995}.  Others have studied transport in heterogeneous geometries
@@
 den-ica-hid2018, bar-mar-vee-zha2018}).  To couple the erosion and the
-hydrodynamics, the grains of the porous media are eroded at a rate that
+fluid, the grains of the porous media are eroded at a rate that
 is proportional to the hydrodynamic shear stress~\cite{wan-fel2004,
@@
 method to the {\thL} formulation~\cite{hou-low-she1994} of the eroding
-bodies.  Given the solution of the incompressible Stokes equations are
-solved in an eroded porous geometry, we investigate different metrics to
+bodies.  Given the solution of the incompressible Stokes equations in
+an eroded porous geometry, we investigate different different but
+related metrics to
 characterize transport.  We focus on three metrics: the tortuosity, the
@@
 leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019}, and advection
-dispersion equation~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
+diffusion equation~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
 with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
@@
 \end{align}
-where $\uu$ is the fluid velocity.  Since there is no diffusion, all
-dispersion is a result of the particle spreading induced by the porous
-geometry.  Since there is no diffusion, we apply a high-order explicit
-Runge-Kutta time stepping method to compute streamlines.  However, other
-groups have simulated trajectories using continuous time random
-walks~\cite{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
-ber-cor-den-sch2006} and a Fokker-Planck equation~\cite{ica-den2019}.
-
-\todo[inline]{Dump of text}
-Resolving the flow in these small velocity regions is essential to
-accurately describe anomalous dispersion and
-mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
-\todo[inline]{Dump of text}
+where $\uu$ is the fluid velocity.  Tracer trajectories can be simulated
+with a continuous time random walks~\cite{mon-wei1965,
+den-cor-sch-ber2004, leb-den-car2008, ber-cor-den-sch2006} or with a
+Fokker-Planck equation~\cite{ica-den2019}.  Instead, since there is no
+stiff diffusive term in~\eqref{eqn:tracers}, we compute streamlines by
+applying a high-order explicit Runge-Kutta time stepping method.
+
+\todo[inline]{Bryan left off here}
 
@@
 vorticity.
+
+\begin{figure}[H]
+\begin{center}
+\todo[inline]{plots of the magnitude of the velocity on a log based 10
+scale}
+\caption{\label{fig:Eroding50vel} Erosion of 50 nearly touching bodies
+with the fixed pressure drop condition. The color is the vorticity of
+the fluid. The 6 snapshots are evenly spaced in time.}
+\end{center}
+\end{figure}
+
 \begin{figure}[H]

### 2019-09-11 docs/transport/erosion_transport.tex
few changes in intro

@@
 Figure~\ref{fig:Eroding50vel}).  Moreover, the channelization results in
-a geometry that is largely heterogeneous and anisotropic, and this
+a geometries that are largely heterogeneous and anisotropic, and this
 affects the transfer other other quantities such as a contaminant or
-heat~\cite{nil-sto1990,
-ree-sto1995}.  Others have studied transport in heterogeneous geometries
-(for example, see~\cite{mil-chr-imh-mcb-ped1998, ber-sch-sil2000,
-hak-com-den2019, suo-liu-gan2019, cus-hu-den1995, cve-che-wen1996,
-leb-ded-dav-bou2007, knu-car2005, bel-sal-rin1992}). However, to the
-best of our knowledge, a detailed study of transport in eroded
-geometries has not been performed.
+heat~\cite{nil-sto1990, ree-sto1995}.  Others have studied transport in
+heterogeneous geometries (for example,
+see~\cite{mil-chr-imh-mcb-ped1998, ber-sch-sil2000, hak-com-den2019,
+suo-liu-gan2019, cus-hu-den1995, cve-che-wen1996, leb-ded-dav-bou2007,
+knu-car2005, bel-sal-rin1992}). However, to the best of our knowledge, a
+detailed study of transport in eroded geometries has not been performed.
 
@@
 is proportional to the hydrodynamic shear stress~\cite{wan-fel2004,
-ris-moo-chi-she-zha2012, qua-moo2018, par-izu2000}.  A variety of
+ris-moo-chi-she-zha2012, par-izu2000}.  Porous geometries
+that have undergone erosion differ from standard porous geometry because
+of large amounts of anisotropy and channelization. This work
+addresses the effects that erosion has on the transport through a porous
+media.  Our contributions are two-fold. First, starting with our
+previous work~\cite{qua-moo2018}, we develop new numerical methods to
+simulate erosion of geometries with low porosities and nearly-touching
+grains. Second, we compute and analyze three different metrics of
+transport throughout the erosion process: the tortuosity, the anomalous
+dispersion, and the pore size distribution.
+
+To calculate the tortuosity and dispersion
+The first two of these metrics can be defined in terms of statistical
+moments of trajectories.  Depending on the application, transport at the
+microscale can be modelled as pure advection~\cite{dea-qua-bir-jua2018,
+leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019}, and advection
+diffusion equation~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
+with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
+this work, we assume that the trajectories are governed purely by
+advection (ie.~no diffusion).  Therefore, a trajectory $\ss(t)$
+initialized at $\ss_0$ is governed by
+\begin{align}
+  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0,
+  \label{eqn:tracers}
+\end{align}
+where $\uu$ is the fluid velocity.  Tracer trajectories can be simulated
+with a continuous time random walks~\cite{mon-wei1965,
+den-cor-sch-ber2004, leb-den-car2008, ber-cor-den-sch2006} or with a
+Fokker-Planck equation~\cite{ica-den2019}.  Instead, since there is no
+stiff diffusive term in~\eqref{eqn:tracers}, we compute streamlines by
+applying a high-order explicit Runge-Kutta time stepping method.
+
+In a porous geometry, the length of a particle path is larger than the
+distance travelled if the grains were absent.  To quantify the amount of
+winding a particle takes, we use the tortuosity that is defined as the
+ratio of the particle paths length to the distance between the inlet and
+outlet.  In fractured media, the local tortuosity can be over
+2.5~\cite{hym-den-hag-kan2019}, and in porous media, depending on the
+porosity, the local tortuosity can be greater than
+1.5~\cite{kop-kat-tim1996, mat-kha-koz2008}, or greater than
+2~\cite{dud-koz-mat2011}.  The tortuosity of the geometry is defined by
+averaging over the entire inlet.  Therefore, the geometry's tortuosity
+can be used to characterize average particle
+motions~\cite{hak-com-den2019}.
+
+The tortuosity is a first statistical moment of the streamlines.
+However, to measure spread of trajectories, second-order moments are
+computed. By computing the variance of the lengths of trajectories in a
+porous media, non-local anomalous dispersion is
+observed~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
+dea-leb-den-tar-bol-dav2013}, resulting in super-dispersion.  The
+dispersion depends on the amount of time trajectories spend in low and
+high velocity regimes~\cite{ber-sch2001}.  Anomalous dispersion has been
+investigated for a variety of porous geometries, but not in the context
+of eroding porous geometries.
+
+Rather than solving the fluid equations in a complex porous matrix,
+network models can be used to describe the flow.  Here, the pores
+between neighboring grains are thought of as small channels, and the
+geometry consists of a connected network of these
+channels~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} with the
+flow resembling a Hagen-Poiseuille profile in each channel.  So that
+network models can be applied to an eroding geometry, we characterize
+the pore sizes between neighboring grains as a function of the
+geometry's porosity.  The pore size distribution can be used to quantify
+velocity distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
+channelization~\cite{sie-ili-pri-riv-gua2019}, and
+connectivity~\cite{knu-car2005, wes-blo-gra2001}.
+
+A variety of
 numerical methods can be applied to solve the incompressible Stokes
@@
 method to the {\thL} formulation~\cite{hou-low-she1994} of the eroding
-bodies.  Given the solution of the incompressible Stokes equations in
-an eroded porous geometry, we investigate different different but
-related metrics to
-characterize transport.  We focus on three metrics: the tortuosity, the
-anomalous dispersion, and the distribution of geometrical channels.
-
-The first two of these metrics can be defined in terms of statistical
-moments of trajectories.  Depending on the application, transport at the
-microscale can be modelled as pure advection~\cite{dea-qua-bir-jua2018,
-leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019}, and advection
-diffusion equation~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
-with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
-this work, we assume that the trajectories are governed purely by
-advection (ie.~no diffusion).  Therefore, a trajectory $\ss(t)$
-initialized at $\ss_0$ is governed by
-\begin{align}
-  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0,
-  \label{eqn:tracers}
-\end{align}
-where $\uu$ is the fluid velocity.  Tracer trajectories can be simulated
-with a continuous time random walks~\cite{mon-wei1965,
-den-cor-sch-ber2004, leb-den-car2008, ber-cor-den-sch2006} or with a
-Fokker-Planck equation~\cite{ica-den2019}.  Instead, since there is no
-stiff diffusive term in~\eqref{eqn:tracers}, we compute streamlines by
-applying a high-order explicit Runge-Kutta time stepping method.
-
-\todo[inline]{Bryan left off here}
-
-In a porous geometry, the length of a particle path is larger than the
-distance travelled if the grains were absent.  To quantify the amount of
-winding a particle takes, we use the tortuosity that is defined as the
-ratio of the particle paths length to the distance between the inlet and
-outlet.  In fractured media, the local tortuosity can be over
-2.5~\cite{hym-den-hag-kan2019}, and in porous media, depending on the
-porosity, the local tortuosity can be greater than
-1.5~\cite{kop-kat-tim1996, mat-kha-koz2008}, or greater than
-2~\cite{dud-koz-mat2011}.  The tortuosity of the geometry is defined by
-averaging over the entire inlet.  Therefore, the geometry's tortuosity
-can be used to characterize average particle
-motions~\cite{hak-com-den2019}.
-
-The tortuosity is a first statistical moment of the streamlines.
-However, to measure spread of trajectories, second-order moments are
-computed. By computing the variance of the lengths of trajectories in a
-porous media, non-local anomalous dispersion is
-observed~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
-dea-leb-den-tar-bol-dav2013}, resulting in super-dispersion.  The
-dispersion depends on the amount of time trajectories spend in low and
-high velocity regimes~\cite{ber-sch2001}.  Anomalous dispersion has been
-investigated for a variety of porous geometries, but not in the context
-of eroding porous geometries.
-
-Rather than solving the fluid equations in a complex porous matrix,
-network models can be used to describe the flow.  Here, the pores
-between neighboring grains are thought of as small channels, and the
-geometry consists of a connected network of these
-channels~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} with the
-flow resembling a Hagen-Poiseuille profile in each channel.  So that
-network models can be applied to an eroding geometry, we characterize
-the pore sizes between neighboring grains as a function of the
-geometry's porosity.  The pore size distribution can be used to quantify
-velocity distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
-channelization~\cite{sie-ili-pri-riv-gua2019}, and
-connectivity~\cite{knu-car2005, wes-blo-gra2001}.
+bodies.
 

### 2019-09-11 docs/PhysicsPaper/StokesErosion.tex
NM

@@
-% Journal of Computational Sciences
 %\documentclass[3p]{elsarticle}
 
-% AIP and APS Journals use revtex package.
-%\documentclass[aip, pof, reprint]{revtex4-1} 
-%\documentclass[reprint,superscriptaddress]{revtex4-1}
-% Note: I believe PRL is APS.
-
-\documentclass[reprint,superscriptaddress,notitlepage]{revtex4-1}
-% PRF is APS
+% APS journals: PRL and PRF
+% Note: All AIP and APS journals use the revtex package; both PRL and PRF are APS.
+\documentclass[reprint, superscriptaddress, notitlepage]{revtex4-1}
 
@@
 \usepackage{natbib, hyperref, url}
-\usepackage{algorithm, algpseudocode, pifont, longtable}
+\usepackage{algorithm, algpseudocode, pifont, longtable, subfigure}
 %\usepackage[justification=RaggedRight]{caption}
@@
 \begin{document}
-\title{Erosion leads to anisotropy in a porous medium}
+\title{Fluid-mechanical erosion generates anisotropy in porous media}
+%\title{Erosion leads to anisotropy in a porous medium}
 %\title{The development of anisotropy in an eroding porous medium}
 %
+
 \author{M.~N.~J.~Moore}
@@
 \affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+\author{Shang-Huan Chiu}
+\affiliation{Department of Scientific Computing, Florida State
+University, Tallahassee, FL, 32306.}
+
 \begin{abstract}
@@
 
-Effects of flow-induced erosion are visible across a range of scales in nature, from massive geological structures, to mesoscopic patterns, and finally down to the tiny granular constituents that comprise a porous medium.
+Effects of flow-induced erosion are visible across a range of scales in nature, from massive geological structures, to mesoscopic patterns, and down to the tiny granular constituents that comprise a porous medium.
 In the case of a porous medium specifically, it has been long recognized that bulk properties of mediums encountered in nature are typically anisotropic, so that the medium allows flow in a preferred direction more easily.
@@
 
-Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in Stokes flow---the regime of groundwater flow.
-This method is documented, validated, benchmarked in \cite{Quaife2018}, and can practically simulate the erosion of order hundreds of solid bodies.
+Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in the Stokes regime of groundwater flow \cite{Quaife2018}.
+Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{Quaife2018}, and can simulate the erosion of order hundreds of solid bodies (please see \cite{Mitchell2016} for related work).
+The recent incorporation of barycentric interpolation methods permits simulation of tightly packed configurations (cite new paper with Shang).
 
-%Stuff to cite \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017} and other stuff \cite{Rycroft2016, Mitchell2016}.
+Figure \ref{FigVortVel} shows an example illustration of 80 eroding bodies
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure*}[] %\centering
+        \subfigure[ Vorticity field]{ \label{FigVort}
+            \includegraphics[width=0.9 \textwidth]{figs/80circ8vort.pdf} } \\
+        \subfigure[ Velocity magnitude]{ \label{FigVel}
+            \includegraphics[width=0.9 \textwidth]{figs/80circ8vel.pdf} }
+   \caption{80 eroding bodies}
+   \label{FigVortVel}
+\end{figure*}
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+% Data from 80circ8
+
+%Maybe cite: \cite{Rycroft2016}
 
@@
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.9 \textwidth]{./Figs/fig1.pdf}
+\begin{figure*}%[htbp]
+\centering \label{fig1}
+\includegraphics[width = 0.9 \textwidth]{./figs/80circ8vel.pdf}
 \caption{caption}
-\label{fig1}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.9 \textwidth]{./Figs/fig2.pdf}
-\caption{caption}
-\label{fig2}
-\end{center}
-\end{figure}
+\end{figure*}
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

### 2019-09-18 docs/transport/erosion_transport.tex
working on edits

--- 2019-09-09 docs/transport/erosion_transport.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Flow in many natural occurring geometries involves flows that vary over
-many orders of magnitude.  \todo[]{The grammar in the first sentence is awkward: Flow in ... involves flows?}
-For example, the length scales of a porous
-media can vary from $10^{-6}m$ to
-$10^{-1}m$~\cite{mil-chr-imh-mcb-ped1998}.  Porous media flow plays an
-important role in several environmental and industrial applications.
-Therefore, understanding the dynamics of pore-scale flow is central to
-upscale the governing fluid equations, characterize
-dispersion~\cite{saf1959}, and quantify mixing. However, because of the
-large disparity of length and velocity scales, constitutive laws that
-link the microscopic scale to macroscopic scale must be
-developed~\cite{mil-chr-imh-mcb-ped1998}.  Therefore, to find closure
-formulas, accurate simulations at microscopic scales must be performed
-and analyzed.  A few examples of closure formulas and coarse-grained
-variables include
-pressure-saturation-permeability~\cite{mil-chr-imh-mcb-ped1998},
-permeability-porosity~\cite{dar-mcc1998, car1937, won-kop-tom1984},
-first passage time distribution~\cite{ber-sch-sil2000,
-hym-den-hag-kan2019, cve-che-wen1996}, tortuosity~\cite{hak-com-den2019,
-mat-kha-koz2008, dud-koz-mat2011, kop-kat-tim1996}, concentration
+Porous media flow plays an important role in many environmental and
+industrial applications.  Depending on the application, length scales
+can vary from $10^{-6}\mathrm{m}$ to
+$10^{-1}\mathrm{m}$~\cite{mil-chr-imh-mcb-ped1998}, velocity scales can
+be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}, and
+the scales of a single porous media can range over several orders of
+magnitude. Numerical methods that accurately address all of these scales
+are essential to develop meaningful constitutive relationships between
+the microscopic and macroscopic scales~\cite{mil-chr-imh-mcb-ped1998},
+to characterize dispersion~\cite{saf1959}, and to quantify
+mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
+Flow in porous media is further complicated when there is a two-way
+coupling between the flow and the geometry. For example, the grains of a
+porous media evolve in applications involving
+melting~\cite{bec-vis1998}, dissolution~\cite{kan-zha-che-he2002},
+deposition~\cite{joh-eli1995}, and biofilm
+growth~\cite{tan-val-wer2015}.  We focus on erosion, a fluid-mechanical
+process that is prevalent in many geophysical and hydrological
+applications.
+
+Examples of coarse-grained models for porous media flow include
+pressure-saturation-permeability
+relationships~\cite{mil-chr-imh-mcb-ped1998}, permeability-porosity
+relationships~\cite{dar-mcc1998, car1937, won-kop-tom1984}, first
+passage time distributions~\cite{ber-sch-sil2000, hym-den-hag-kan2019,
+cve-che-wen1996}, tortuosities~\cite{hak-com-den2019, mat-kha-koz2008,
+dud-koz-mat2011, kop-kat-tim1996}, concentration
 distributions~\cite{ica-den2019, bel-sal-rin1992}, flow
@@
 connectivity~\cite{knu-car2005, wes-blo-gra2001}, pore
-distributions~\cite{ali-par-wei-bre2017}, and anomalous
+distributions~\cite{ali-par-wei-bre2017}, anomalous
 dispersion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
-sie-ili-pri-riv-gua2019}.
-
-In many applications, the fluid transport continuously changes the pore
-structure.  This is particularly common in geophysical flows where
-erosion alters the porous matrix.  In this work, we investigate flow in
-eroded porous media.  By introducing erosion, there is a two-way
-coupling between the hydrodynamics and the mechanical alteration of the
-complex porous geometry.  Transport in porous geometries that have
-undergone erosion finds applications in aquifers~\cite{cve-che-wen1996,
-sud1986}, solute transport in groundwater flow~\cite{dag1987,
-kon-bre1978}.  Porous geometries that have undergone erosion have
-certain characteristics.  For example, the geometry often has regions of
-high porosity that connect the inlet to the outlet.  This channelization
-results in velocity scales that can vary over several orders of
-magnitude~\cite{all-hea-lab-rei2002}.  Moreover, the channelization
-results in a geometry that is largely heterogeneous and anisotropic, and
-this affects heat transfer through the medium~\cite{nil-sto1990,
-ree-sto1995}.  Others have studied transport in heterogeneous geometries
-(for example, see~\cite{mil-chr-imh-mcb-ped1998, ber-sch-sil2000,
-hak-com-den2019, suo-liu-gan2019, cus-hu-den1995, cve-che-wen1996,
-leb-ded-dav-bou2007, knu-car2005, bel-sal-rin1992}). However, to the
-best of our knowledge, a detailed study of transport in eroded
-geometries has not been performed.
-
-To describe the relevant hydrodynamics, we model two-dimensional
-microscopic scales where the fluid is governed by the incompressible
-Stokes equations (for example, see~\cite{hym-den-hag-kan2019,
-den-ica-hid2018, bar-mar-vee-zha2018}).  To couple the erosion and the
-hydrodynamics, the grains of the porous media are eroded at a rate that
-is proportional to the hydrodynamic shear stress~\cite{wan-fel2004,
-ris-moo-chi-she-zha2012, qua-moo2018, par-izu2000}.  A variety of
-numerical methods can be applied to solve the incompressible Stokes
-equations such as a lattice-gas or lattice Boltzmann
-model~\cite{kop-kat-tim1996, dar-mcc1998}, finite
-volume~\cite{suo-liu-gan2019, den-ica-hid2018, sie-ili-pri-riv-gua2019},
-finite differences~\cite{leb-ded-dav-bou2007, knu-car2005}, and cellular
-automata~\cite{rot1988}. In this work, we instead solve an equivalent
-boundary integral equation (BIE) formulation of the incompressible
-Stokes equation.  The BIE is discretized with a high-order quadrature
-method that resolves nearly touching bodies with a near-singular
-integration scheme~\cite{bar-wu-vee2015}.  The erosion dynamics are
-simulated by applying a stable second-order time stepping Runge-Kutta
-method to the {\thL} formulation~\cite{hou-low-she1994} of the eroding
-bodies.  Given the solution of the incompressible Stokes equations are
-solved in an eroded porous geometry, we investigate different metrics to
-characterize transport.  We focus on three metrics: the tortuosity, the
-anomalous dispersion, and the distribution of geometrical channels.
-
-The first two of these metrics can be defined in terms of statistical
-moments of trajectories.  Depending on the application, transport at the
-microscale can be modelled as pure advection~\cite{dea-qua-bir-jua2018,
-leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019}, and advection
-dispersion equation~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
+sie-ili-pri-riv-gua2019}, and more.  Some of these works consider
+heterogeneous porous geometries, but to the best of our knowledge, a
+detailed study of transport in eroded geometries has not been performed.
+This paper characterizes transport in eroded geometries by computing and
+analyzing a variety of coarse-grained variables.
+
+When a porous geometry erodes, certain qualitative characteristics are
+unveiled that affect transport through the geometry. For example, an
+eroded geometry often contains channels of high porosity that connect
+the inlet to the outlet, and this results in velocities that vary over
+several orders of magnitude~\cite{all-hea-lab-rei2002}.  Moreover,
+channelized geometries are heterogeneous and anisotropic, and this
+affects the transfer of quantities such as
+contaminants~\cite{cve-che-wen1996, dag1987, kon-bre1978} and
+heat~\cite{nil-sto1990, ree-sto1995}.  To characterize the transport in
+eroded geometries, we must complete three main tasks.  The first two are
+forming high-fidelity numerical solutions of the fluid equations, and
+eroding the grains according to an erosion model. These two tasks are
+performed using our previous work~\cite{qua-moo2018}, but we improve our
+numerical methods so that simulations of more realistic dense
+suspensions of eroding grains are possible
+(Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  Finally,
+in this paper, we simulate and characterize transport through eroded
+porous geometries.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b1}
+\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b80}
+\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b160}\\
+\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b240}
+\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b320}
+\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b400}
+\caption{\label{fig:Eroding50vel} Six evenly spaced snapshots of 50
+eroding bodies.  The background velocity is a Hagen-Poiseuille flow with
+a varying flow strength that corresponds to a constant pressure drop
+across the channel. The color is the magnitude of the velocity in a
+logarithmic scale. The flow velocity varies over several orders of
+magnitude, the grains form irregular shapes with large aspect ratios,
+and the geometry becomes channelized and anisotropic.}
+\end{center}
+\end{figure}
+
+Because of the length and velocity scales in hydrological applications
+such as groundwater flow~\cite{bea1972}, we model the hydrodynamics with
+the two-dimensional incompressible Stokes equations. A variety of
+numerical methods are available to solve the incompressible Stokes
+equations including lattice-gas or lattice
+Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998}, finite
+volumes~\cite{suo-liu-gan2019, den-ica-hid2018,
+sie-ili-pri-riv-gua2019}, finite differences~\cite{leb-ded-dav-bou2007,
+knu-car2005}, and cellular automata~\cite{rot1988}.  However, to
+accurately simulate erosion and transport, we require a high-order
+method that is able to resolve geometries with arbitrarily shaped and
+nearly-touching grains.  Therefore, we solve the incompressible Stokes
+equations with a boundary integral equation (BIE).  To couple erosion
+with the fluid, the grains are eroded at a rate that is proportional to
+the magnitude of the hydrodynamic shear stress~\cite{wan-fel2004,
+ris-moo-chi-she-zha2012, par-izu2000}.  Since the vorticity and the
+shear stress are equivalent on the grains in the zero Reynolds number
+limit, we also compute the vorticity in the fluid bulk
+(Figure~\ref{fig:Eroding50vort}).
+
+To characterize the transport, particle trajectories need to be
+computed. Depending on the application, microscale transport can be
+modelled as pure advection~\cite{dea-qua-bir-jua2018,
+leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019},
+advection-diffusion~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
 with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
@@
 \end{align}
-where $\uu$ is the fluid velocity.  Since there is no diffusion, all
-dispersion is a result of the particle spreading induced by the porous
-geometry.  Since there is no diffusion, we apply a high-order explicit
-Runge-Kutta time stepping method to compute streamlines.  However, other
-groups have simulated trajectories using continuous time random
-walks~\cite{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
-ber-cor-den-sch2006} and a Fokker-Planck equation~\cite{ica-den2019}.
-
-\todo[inline]{Dump of text}
-Resolving the flow in these small velocity regions is essential to
-accurately describe anomalous dispersion and
-mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
-\todo[inline]{Dump of text}
-
-In a porous geometry, the length of a particle path is larger than the
-distance travelled if the grains were absent.  To quantify the amount of
-winding a particle takes, we use the tortuosity that is defined as the
-ratio of the particle paths length to the distance between the inlet and
-outlet.  In fractured media, the local tortuosity can be over
-2.5~\cite{hym-den-hag-kan2019}, and in porous media, depending on the
-porosity, the local tortuosity can be greater than
-1.5~\cite{kop-kat-tim1996, mat-kha-koz2008}, or greater than
-2~\cite{dud-koz-mat2011}.  The tortuosity of the geometry is defined by
-averaging over the entire inlet.  Therefore, the geometry's tortuosity
-can be used to characterize average particle
-motions~\cite{hak-com-den2019}.
-
-The tortuosity is a first statistical moment of the streamlines.
-However, to measure spread of trajectories, second-order moments are
-computed. By computing the variance of the lengths of trajectories in a
-porous media, non-local anomalous dispersion is
-observed~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
-dea-leb-den-tar-bol-dav2013}, resulting in super-dispersion.  The
-dispersion depends on the amount of time trajectories spend in low and
-high velocity regimes~\cite{ber-sch2001}.  Anomalous dispersion has been
-investigated for a variety of porous geometries, but not in the context
-of eroding porous geometries.
-
-Rather than solving the fluid equations in a complex porous matrix,
-network models can be used to describe the flow.  Here, the pores
-between neighboring grains are thought of as small channels, and the
-geometry consists of a connected network of these
-channels~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} with the
-flow resembling a Hagen-Poiseuille profile in each channel.  So that
-network models can be applied to an eroding geometry, we characterize
-the pore sizes between neighboring grains as a function of the
-geometry's porosity.  The pore size distribution can be used to quantify
-velocity distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
-channelization~\cite{sie-ili-pri-riv-gua2019}, and
-connectivity~\cite{knu-car2005, wes-blo-gra2001}.
-
-The numerical methods to solve the governing fluid and erosion equations
-are based on previous work of the authors~\cite{qua-moo2018}.  We
-continue to use a boundary integral equation (BIE) formulation of the
-incompressible Stokes equations and a second-order Runge-Kutta method
-applied to a smoothed version of the magnitude of the shear stress.  In
-our previous work, we discretized the BIE with the trapezoid rule whose
-accuracy grows when evaluating layer potentials close to the fluid
-boundary.  Therefore, given a fixed resolution, our previous work
-required a minimum separation distance between all bodies to maintain
-stability.  One of the earliest works on near-singular integration was
-developed by Baker and Shelley~\cite{bak-she1986}, and in recent years,
-many other near-singular integration schemes have been
+where $\uu$ is the fluid velocity, and the trajectories are simply the
+streamlines. Since there is no stiff diffusive term
+in~\eqref{eqn:tracers}, we use a high-order explicit Runge-Kutta time
+stepping method. Other methods to compute streamlines include a
+continuous time random walk~\cite{mon-wei1965, den-cor-sch-ber2004,
+leb-den-car2008, ber-cor-den-sch2006}.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b1}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b80}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b160}\\
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b240}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b320}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b400}
+\caption{\label{fig:Eroding50vort} The same six snapshots from
+Figure~\ref{fig:Eroding50vel}.  The color is the vorticity of the fluid.
+Since the rate of erosion is equivalent to the magnitude of the
+vorticity, erosion is fastest in the yellow and blue regions and slowest
+in the green regions.}
+\end{center}
+\end{figure}
+
+To be able to compute stable simulations of erosion and accurate
+streamline trajectories, we use high-order methods in both space and
+time. The erosion rate is singular at stagnation points, so we apply a
+mild regularization and smoothing terms to eliminate numerical
+instabilities.  As described in our previous work~\cite{qua-moo2018}, we
+apply a stable second-order Runge-Kutta method is applied to the {\thL}
+coordinates~\cite{hou-low-she1994} of the eroding grains.  In these
+coordinates, the stiff term is linear and treated implicitly, so we are
+able to take large time step sizes. In our previous work, after
+discretizing the BIE, the trapezoid rule is used to approximate the
+integrals. The accuracy of the trapezoid rule is sufficiently accurate
+if all the bodies are sufficiently separated~\cite{tre-wei2014}, but
+nearly-singular integrals must be computed when two grains are
+nearly-touching or when evaluating the velocity or vorticity near an
+eroding grain.  One of the earliest works on near-singular integration
+was developed by Baker and Shelley~\cite{bak-she1986}, and in recent
+years, many other near-singular integration schemes have been
 developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
@@
 non-intrusive modification of the trapezoid rule, and the error is
-guaranteed to be uniformly bounded.  In this work, we extend this
-quadrature method so that it can be used to compute the gradient of the
-velocity which is required to compute the shear stress and the fluid
-vorticity. 
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b1}
-\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b80}
-\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b160}\\
-\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b240}
-\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b320}
-\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b400}
-\caption{\label{fig:Eroding50vort} Erosion of 50 nearly touching
-bodies with the fixed pressure drop condition. The color is the
-vorticity of the fluid. The 6 snapshots are evenly spaced in time.}
-\end{center}
-\end{figure}
+guaranteed to be uniformly bounded.  We extend the original quadrature
+method so that it can be used to compute the gradient of the velocity
+that is required to compute the shear stress and the fluid vorticity. In
+addition, the quadrature method is used to accurately compute streamline
+trajectories that pass through the very slow regions close to the
+eroding grains.
+
+Once streamlines in an eroded geometry are computed, we characterize the
+transport by computing and analyzing three different metrics: the
+tortuosity, the anomalous dispersion, and the pore size distribution.
+The local tortuosity of a streamline connecting the inlet to the outlet
+is the streamline's length normalized by the distance between the inlet
+and the outlet.  In porous media, depending on several factors including
+the porosity, the local tortuosity can be greater than
+1.5~\cite{kop-kat-tim1996, mat-kha-koz2008}, or even
+2~\cite{dud-koz-mat2011}.  The tortuosity of a geometry is defined by
+averaging the local tortuosity over all streamlines that are initialized
+at the inlet, and the geometry's tortuosity can be used to characterize
+average particle motions~\cite{hak-com-den2019}.  To characterize
+spreading, the fluid dispersion is computed as the variance of the
+streamline lengths. In porous media, this spreading can often be
+characterized with a super-diffusive anomalous dispersion
+rate~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
+dea-leb-den-tar-bol-dav2013}. An accurate solution near the grains is
+crucial since the anomalous dispersion is caused by streamlines spending
+time in both the high and low velocity regimes~\cite{ber-sch2001}.
+Finally, the third metric, pore size distribution, is useful to quantify
+velocity distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
+channelization~\cite{sie-ili-pri-riv-gua2019},
+connectivity~\cite{knu-car2005, wes-blo-gra2001}, and to develop network
+models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
 
@@
 \paragraph{Contributions}
-Our first main contribution is extending the work of Barnett et
+Our first contribution is extending the work of Barnett et
 al.~\cite{bar-wu-vee2015} so that high-order accurate derivatives of
 solutions of the Stokes equations can be computed.  Using this new
-quadrature method, we can accurately compute erosion rates, and
-therefore stably simulate erosion.  Moreover, we use the quadrature
-method to visualize the vorticity in the fluid bulk.  The vorticity is
-convenient to visualize since, in the zero Reynolds number limit, it is
-equivalent to the shear stress on the eroding bodies, and therefore its
-magnitude is the erosion rate.
-
-Our second contribution is computing trajectories in the eroded
-geometries.  These trajectories are used to characterize the transport
-by computing local tortuosities of the trajectories, the tortuosity of
-the eroded geometry, and the anomalous dispersion rates in the geometry.
-Again, by using an appropriate quadrature method~\cite{bar-wu-vee2015},
-and a fourth-order Runge-Kutta method, we are able to stably compute
-trajectories that spend large amounts of time in the slow velocity
-regions near the eroding bodies, and computing these trajectories
-reliably is essential to characterize the flow.  We compare our
-tortuosity and dispersion rates with models available in the literature.
+quadrature method, we accurately compute erosion rates and stably
+simulate erosion.  Moreover, we use the quadrature method to visualize
+the vorticity in the fluid bulk.  The vorticity is convenient to
+visualize since, in the zero Reynolds number limit, it is equivalent to
+the shear stress on the eroding bodies, and therefore its magnitude is
+the erosion rate.
+
+Our second contribution is computing and analyzing trajectories in the
+eroded geometries.  These trajectories are used to characterize the
+transport by computing local tortuosities of the trajectories, the
+tortuosity of the eroded geometry, and the anomalous dispersion rates in
+the geometry.  By using the same quadrature rule and a fourth-order
+Runge-Kutta method, we are able to accurately compute trajectories that
+spend large amounts of time in the slow velocity regions near the
+eroding bodies, and computing these trajectories reliably is essential
+to characterize the flow~\cite{dea-leb-den-tar-bol-dav2013}.  We compare
+our tortuosity and dispersion rates with models available in the
+literature.  Finally, we analyze the effect of erosion on the pore size
+distribution.
 
@@
 \paragraph{Limitations}
-As in our previous work~\cite{qua-moo2018}, this work considers
-two-dimensional immobile bodies. However, this new work does not have a
-limitation on the packing of the bodies. Compared to our previous work,
-we are able to simulate much denser suspensions with a comparable number
-of discretization points.  While we do investigate transport in this
-work, we only consider passive particles that are undergoing only
-advection. To model other physical processes, such as contaminant
-transport, we plan to simulate a finite Peclet number
+As in our previous work~\cite{qua-moo2018}, we consider two-dimensional
+immobile eroding grains. However, this new work does not have a limitation on
+the proximity of the bodies. Compared to our previous work, we are able to
+simulate much denser suspensions with a comparable number of
+discretization points and without upsampling.  While we do investigate
+transport in this work, we only consider passive particles that are only
+advected by the flow.  To model other physical processes, such as
+contaminant transport, we plan to simulate a finite Peclet number
 advection-diffusion equation in eroded geometries.
@@
 \paragraph{Outline of the Paper}
-In Section~\ref{sec:formulation}, we briefly summarize the model that we
+In Section~\ref{sec:formulation}, we summarize the model that we
 describe in detail in our previous work~\cite{qua-moo2018}.  In
@@
 potentials defined in both $\RR^2$ and in $\CC$.
-Section~\ref{sec:method} describes the numerical methods, with special
-attention paid to the new quadrature method to compute the shear stress
-and vorticity.  Section~\ref{sec:transport} describes measures for
-characterizing the geometry, transport, and dispersion.
+Section~\ref{sec:transport} describes measures for characterizing the
+geometry, transport, and dispersion. Section~\ref{sec:method} describes
+the numerical methods, with special attention paid to the new quadrature
+method to compute the shear stress and vorticity.
 Section~\ref{sec:results} presents numerical examples for a variety of
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We start by defining the main variables used to model erosion.  A more
-detailed description is in our previous work~\cite{qua-moo2018}.  We
-consider flows inside a confined geometry $\Omega$ that contains $M$
-eroding bodies with boundary $\gamma_\ell$, $\ell = 1,\ldots,M$.  The
-boundary of the bounding geometry is $\Gamma$, and the fluid domain is
-bounded by $\bd \Omega = \Gamma \cup \gamma_1 \cup \cdots \cup
-\gamma_M$.  On each eroding body, $\nn$ is the normal vector pointing
-into the body, and $\ss$ is the unit tangent vector pointing in the
-counterclockwise direction.  The normal vector on $\Gamma$ is the
-outward unit normal.  Neglecting inertial forces, the governing
-equations are
+We start by defining the main variables used to model erosion.  We only
+summarize the model, and a more detailed description is in our previous
+work~\cite{qua-moo2018}.  We consider flows inside a confined geometry
+$\Omega$ that contains $M$ eroding bodies with boundaries $\gamma_\ell$,
+$\ell = 1,\ldots,M$.  The boundary of the bounding geometry is $\Gamma$,
+so the fluid domain is bounded by $\bd \Omega = \Gamma \cup \gamma_1
+\cup \cdots \cup \gamma_M$.  In all examples, we let $\Gamma$ be a
+slightly rounded-off version of $[-3,3] \times [-1,1]$, and we only
+place eroding bodies in the region $[-1,1] \times [-1,1]$.  On each
+eroding body, $\nn$ is the normal vector pointing into the body, and
+$\ss$ is the unit tangent vector pointing in the counterclockwise
+direction.  The normal vector on $\Gamma$ is the outward unit normal.
+Neglecting inertial forces, the governing equations are
 \begin{equation}
@@
 \end{align}
-is the shear stress on $\gamma$.
+is the shear stress on $\gamma$.  The erosion process is simulated by
+alternating between solving the fluid equations and adancing the grains
+according to the erosion rate for a small time step.
 
@@
 sign, and this leads to corners developing on $\gamma$ and numerical
-instabilities.  Therefore, we modify the erosion rate by adding a
-curvature penalization. That is, the erosion model
-in~\eqref{eqn:erosionModel} is replaced with 
+instabilities.  Therefore, we modify the erosion rate, $V_\nn$ in
+equation~\eqref{eqn:erosionModel}, with
 \begin{align}
@@
 $L$ is the length of $\gamma$, and $\kappa$ is the curvature of
-$\gamma$.  The normalization term guarantees that the regularization
-only changes the body's shape, but not its total length.  Finally, to
-increase the overall stability of the method, a narrow Gaussian filter
-is applied to the erosion rate.
+$\gamma$.  This new term penalizations regions of high curvature, and
+the normalization term guarantees that the regularization only changes
+the body's shape, but not its total length.  Finally, to increase the
+overall stability of the method, a narrow Gaussian filter is applied to
+the erosion rate at each time step.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Since require a method to solve the incompressible Stokes equations in
+complex two-dimensional porous geometries, we reformulated the governing
+PDE as a boundary integral equation. This has the advantage that only
+the one-dimensional boundary of the domain must be discretized, and if
+appropriate quadrature formula and fast summation methods are used, the
+result is a high-fidelity numerical simulation that is computed with
+near-optimal complexity.
+
+\subsection{Double-Layer Potential Fromulation in $\RR^2$}
 Applying the same approach as our previous work~\cite{qua-moo2018}, we
-use a double-layer potential formulation for the velocity $\uu$.  The
-double-layer potential is
+write the velocity $\uu$ as a double-layer potential 
 \begin{align}
@@
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  Since the Stokes double-layer potential
-can not represent all solutions of the incompressible Stokes equations,
-we complete the integral equation formulation by adding the Stokeslets
-and rotlets~\cite{pow-mir1987}
+is an unknown density function.  The double-layer potential can not
+represent all solutions of the incompressible Stokes equations, so we
+complete the integral equation formulation by adding the Stokeslets and
+rotlets~\cite{pow-mir1987}
 \begin{align}
@@
     \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
-    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx),
+    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
 \end{align}
@@
 \label{eqn:BIE}
-\begin{align}
+\begin{alignat}{3}
   \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
@@
     \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
-    \NN_0[\eeta](\xx), \quad \xx \in \bd\Omega, \\
+    \NN_0[\eeta](\xx), \quad &&\xx \in \bd\Omega, \\
   \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
-    \eeta(\yy)\, ds_\yy \quad \ell = 1,\ldots,M, \\
+    \eeta(\yy)\, ds_\yy &&\ell = 1,\ldots,M, \\
   \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
     (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy 
-    \quad \ell = 1,\ldots,M.
-\end{align}
+    &&\ell = 1,\ldots,M.
+\end{alignat}
 \end{subequations}
 The operator $\NN_0$ is the integral operator with kernel
-$N_(0)(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$,
+$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$,
 which removes the rank one null space resulting from the flux-free
@@
 
-The deformation tensor, pressure, and vorticity of the double-layer
-potential, Stokeslets, and rotlets, can all be computed analytically in
-terms of the density function and the strengths of the Stokeslets and
-rotlets.  For $\xx \in \Omega$, the deformation tensor, pressure, and
-vorticity of the double-layer potential~\eqref{eqn:velocityDLP} are
+Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
+Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, the deformation
+tensor, pressure, and vorticity of the double-layer potential can all be
+computed analytically.  For $\xx \in \Omega$, the deformation tensor,
+pressure, and vorticity of the double-layer
+potential~\eqref{eqn:velocityDLP} are
 \begin{align}
@@
 $\RR^2$.  However, so that we can apply a particular quadrature method,
-we need to write these layer potentials in terms of Cauchy integrals in
+we write these layer potentials as Cauchy integrals in
 $\CC$ and their derivatives.  The first step is to write the Laplace
@@
 where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$.
-Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
-integral by first finding the boundary data of $v$.  We assume that
-$\Omega$ is a simply-connected interior domain. Then, the boundary data
+Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy
+integral by first finding the boundary data of $v$.  Assuming that
+$\Omega$ is a simply-connected interior domain, the boundary data
 of $v$ satisfies the Sokhotski-Plemelj jump relation
@@
 terms of Cauchy integrals and their derivatives, we write it in terms of
-Laplace layer potentials
+Laplace layer potentials~\cite{bar-wu-vee2015}
 \begin{equation}
@@
 Therefore, the Stokes double-layer potential can be written in terms of
-Cauchy integrals and their first derivative  as~\cite{bar-wu-vee2015}
+Cauchy integrals and their first derivative as
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In addition to the velocity, we require a complex-valued representation
+In addition to the velocity, we require a complex-valued layer potential representation
 of the gradient of the velocity so that we can compute the shear stress
@@
 
-In a shear flow, the vorticity is equivalent to the shear stress.  Since
-the erosion rate is proportional to the magnitude of the shear stress,
-it is constructive to visualize the vorticity of the fluid.  For $x \in
-\Omega$, the Cauchy integral representation of the vorticity is
+The gradient of the velocity field can also be used to compute the
+vorticity in the fluid bulk. Since the vorticity of a Stokes flow on
+no-slip walls is equivalent to the shear stress, we make use of the
+vorticity to better understand where the porous media will undergo large
+and small amounts of erosion.  For $x \in \Omega$, the Cauchy integral
+representation of the vorticity is
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Erosion leads to interesting porous geometries, and we are interested in
-characterizing transport in these geometries.  In our previous
-work~\cite{qua-moo2018}, we examined the effect of erosion on the area
-fraction, flow rate, and the total drag.  However, to characerize
-transport, other quantities must be examined.  Here, we compute the
-anomalous dispersion rate, the tortuosity, and the distribution of the
-gap sizes.  The first two metrics can be defined in terms of streamline
-governed by an advection autonomous equation~\eqref{eqn:tracers}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Anomalous Disperision}
+Erosion in porous geometries leads to particular phenomena such as
+channelization, and we are interested in characterizing transport in
+such geometries.  In our previous work~\cite{qua-moo2018}, we examined
+the effect of erosion on the area fraction, flow rate, and the total
+drag.  However, to characterize transport, other quantities must be
+examined.  Here, we compute the anomalous dispersion rate, the
+tortuosity, and the distribution of the gap sizes.  The first two
+metrics can be defined in terms of streamline governed by an advection
+autonomous equation~\eqref{eqn:tracers}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Anomalous Dispersion}
 \label{sec:dispersion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The dynamics of fluid in porous media is often characterized in terms of
-anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.  The
-anomalous dispersion rate depends on the porosity and
-permeability~\cite{koc-bra1988}, but the distribution of the bodies also
-affects the anomalous dispersion rates.  Since erosion causes certain
-structure in porous media, calculating the anomalous dispersion rates in
-these geometries is important.
-
-We calculate the anomalous dispersion rates by analyzing the streamlines
-governed by equation~\eqref{eqn:tracers} for geometries that are formed
-by erosion.  Given a set of trajectories, we define $\lambda_j(t)$ to be
-the arclength of the trajectory
+The dynamics of fluid in a porous media is often characterized in terms
+of anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.
+The anomalous dispersion rate depends on the porosity and
+permeability~\cite{koc-bra1988}, but it is also affected by the
+distribution and shape of the grains. We calculate the anomalous
+dispersion rates by analyzing the streamlines governed by
+equation~\eqref{eqn:tracers} in eroded geometries. Given a set of $N_p$
+trajectories, we define $\lambda_j(t)$ to be the arclength of the
+trajectory
 \begin{align}
   \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
-    \quad j=1,\ldots,N_p.
-\end{align}
-Then, the first and second ensemble moments are
+    \quad j=1,\ldots,N_p,
+\end{align}
+and the first and second ensemble moments
 \begin{align}
@@
 \end{align}
-Since we compute second-order statistics, we use 1000 streamlines so
-that the statistics have converged~\cite{bel-sal-rin1992}.  Then,
+Then,
 particle dispersion is characterized as $\sigma_\lambda$.  At early
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Dump of text}
+In the numerical simulations, we use $N_p = 1000$ streamlines so
+that the statistics have converged~\cite{bel-sal-rin1992}.  
+\todo[inline]{Dump of text}
+
 In this section, we apply our new quadrature method to (1) simulate
@@
 
+Finally, using network models for flow in porous media~\cite{}, the
+anomalous dispersion rate can be linked to channel widths between solid
+bodies.  We construct a Delaunay triangulation with the centers of the
+eroding bodies corresponding to the vertices of the triangles.  Then, if
+the side of a triangle connects two vertices, we call the bodies
+neighbors.  Then, for each pair of neighbors, we measure the distance
+between the bodies.  Once a Delaunay triangulation is formed, it is used
+for all subsequent time steps until a body completely disappears.  At
+this point, a new Delaunay triangulation is formed. 
+{\color{red}In Figure~\ref{fig:Eroding100gap_mean_var}, 
+we record the gap distances between bodies neighbors and
+calculate the mean and variance with respect to porosities. 
+For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
+which means the eroding . 
+For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  }
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
+the variance of gaps in (b) with respect to porosity $\phi$ of an
+eroding geometry initialized with 100 bodies . 
+Red stars are six selected porosities to have the details of  
+the disturbutions of gaps and fitting curves of the disturbutions 
+in Figure~\ref{fig:Eroding100gap_hist}.}
+\end{figure}
+
+We plot the distribution of the gap sizes at six porosities
+in Figure~\ref{fig:Eroding100gap_hist}.  At the initial configuration, there
+are 100 bodies and 258 pairs of neighbors.  The mean distance between
+these neighbors is $???  \times 10^{-???}$ and the variance is $???
+\times 10^{???}$.  As the bodies erode, the mean and variance of the
+distance between the bodies increases.  Finally, when the porosity reaches $95.12\%$
+there are only 34 bodies and 74 pairs of neighbors.
+=======
+bodies.  As described in Section~\ref{sec:throats}, we use a Delaunay
+triangulation to define neighboring eroding bodies, and we compute the
+throat size by finding the closest distance between all neighboring
+bodies.  Once all throat sizes are computed, we analyze their
+distribution as a function of the porosity.  In
+Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the throat
+sizes at six porosities throughout the erosion process.
+>>>>>>> 7bba99dc1bad2c9b798e001a13a21b8206449a25
+=======
 Finally, we investigate the effects of erosion on pore sizes.  The
@@
 variance of the gap sizes quickly grow.
+>>>>>>> 95eee70f74046c43a90121249c7d61943d2f436b
 

### 2019-09-18 docs/transport/erosion_transport.tex
edits up to the numerical results

@@
 
-The erosion rate loses differentiability if the shear stress changes
-sign, and this leads to corners developing on $\gamma$ and numerical
-instabilities.  Therefore, we modify the erosion rate, $V_\nn$ in
-equation~\eqref{eqn:erosionModel}, with
-\begin{align}
-  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
-    \frac{L}{2\pi} \kappa - 1 \right),
-\end{align}
-where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average,
-$L$ is the length of $\gamma$, and $\kappa$ is the curvature of
-$\gamma$.  This new term penalizations regions of high curvature, and
-the normalization term guarantees that the regularization only changes
-the body's shape, but not its total length.  Finally, to increase the
-overall stability of the method, a narrow Gaussian filter is applied to
-the erosion rate at each time step.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 deformation tensor, pressure, and vorticity due to the Stokeslets and
-rotlets are straightforward to compute~\cite{poz1992} \todo[inline]{BQ:
-Make sure this is the right reference}.  Having computed the deformation
-tensor on $\gamma$, the shear stress is computed as defined in
-equation~\eqref{eqn:shearStress}.
+rotlets are straightforward to compute~\cite{poz1992}.  Having computed
+the deformation tensor on $\gamma$, the shear stress is computed as
+defined in equation~\eqref{eqn:shearStress}.
 
@@
 \begin{align}
-  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
-    \frac{\rr \cdot \nn}{\rho^2}\, ds_\yy = \Re (v(x)) \quad 
+  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
+    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Re (v(x)) \quad 
     \text{where} \quad v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
@@
 \end{align}
-Then,
-particle dispersion is characterized as $\sigma_\lambda$.  At early
+Particle dispersion is characterized as $\sigma_\lambda$.  At early
 times, the particles have not explored much of the geometry, and we
@@
 particle reaches the end of the porous region, it is reinserted at the
-start of the porous region.  To minimize errors caused by the
-reinsertion, the particle is initialized at the discretization point
-that has the closest velocity to the particles velocity at the outlet.
-After a single trajectory is formed, it has undergone a collection of
-reinsertions.  The fore, as a post-processing step, the trajectory is made
-continuous by attaching the tail of each segment to the origin of the
-next segment.
+start of the porous region.  To minimize errors caused by reinsertion,
+the particle is initialized at the discretization point that has the
+closest velocity to the particle's velocity at the outlet.  After a
+single trajectory is formed, it has undergone a collection of
+reinsertions.  Therefore, as a post-processing step, the trajectory is
+made continuous by attaching the tail of each segment to the origin of
+the next segment.
 
@@
   \langle \lambda \rangle (t) = \frac{2}{3}t, \quad 
-    \sigma_\lambda^2(t) = \frac{4}{45}t^2,
-\end{align}
-so the particle motion is ballistic since $\sigma_\lambda \sim t$.  In
-Section~\ref{sec:results}, we compare these moments in an open channel
-with the trajectories in an eroded geometry.
+    \sigma_\lambda^2(t) = \frac{4}{45}t^2.
+\end{align}
+In Section~\ref{sec:results}, we compare these moments in an open
+channel with the trajectories in an eroded geometry.
 
@@
 
-The choice for the trajectory with length $\lambda(y)$ is not universal,
-and Duda et al.~\cite{dud-koz-mat2011} summarize several options. One
-choice, which we adopt, considers trajectories that originate at $S$ and
-terminate at a parallel cross-section.  We use the cross-sections $x=-1$
-and $x=1$.  This choice of averaging allows us to also compute the
-tortuosity in terms of an area integral.  Under the assumptions that the
-flow is incompressible and not re-entrant, meaning that all streamlines
-connect the two cross-sections, the tortuosity in
+The definition for the tortuosity depends on how the streamlines are
+defined, and Duda et al.~\cite{dud-koz-mat2011} summarize several
+options. One choice, that we adopt, considers streamlines that originate
+at $S$ and terminate at a parallel cross-section.  We use the
+cross-sections $x=-1$ and $x=1$.  This choice of averaging allows us to
+also compute the tortuosity in terms of an area integral.  Under the
+assumptions that the flow is incompressible and not re-entrant, meaning
+that all streamlines connect the two cross-sections, the tortuosity in
 equation~\eqref{eqn:tortuosity1} is equivalent to~\cite{dud-koz-mat2011}
@@
 definition for the majority of the tortuosity calculations.  However, we
-do compare the two formulas for the tortuosity at several time steps in
-Section~\ref{sec:results}.
+do compare the two definitions for the tortuosity at several time steps
+in Section~\ref{sec:results}.
 
@@
 \end{subequations}
-where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
-compare these four models with the tortuosity of eroding geometries.
+where $\phi$ is the porosity and $p>0$ is a fitting parameter.  In
+Section~\ref{sec:results}, we compare these four models with the
+tortuosity of eroding geometries.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{itemize}
-  \item Pore throat sizes affect many things such as first passage time,
-  mixing, chemical reactions, heat conduction, biological activities
-\end{itemize}
+While transport in a porous media depends on the porosity, it also
+depends on the placement of the grains.  In particular, the grain
+placement affects velocity scales~\cite{ali-par-wei-bre2017},
+correlation structures~\cite{leb-ded-dav-bou2007}, contaminant
+transport~\cite{knu-car2005},
+channelization~\cite{sie-ili-pri-riv-gua2019}, and more. In addition,
+pore network models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}
+rely on descriptions of the pore throat sizes. To characterize the grain
+placement, we compute distributions of gap sizes between neighboring
+grains.  To define neighboring grains, we form a Delaunay triangulation
+of nodes placed at the center of each eroding grain and at a collection
+of points around the boundary of the porous region.  Then, we say that
+two grains are neighbors if their centers share an edge of the
+triangulation~\cite{dea-qua-bir-jua2018}.  Finally, we compute the
+minimum distance between all pairs of neighboring grains.  In
+Figure~\ref{fig:Eroding100gap}(a), we plot a histogram of the pore size
+of 100 eroded bodies.  The black curve is an un-normalized Weibull
+distribution with the same mean and variance as the measured data.  In
+Figure~\ref{fig:Eroding100gap}(b), we plot lines connected the two
+closest points of all neighboring gaps. We do not consider pores between
+eroding bodies and the solid and the artificial points placed around the
+porous region, so some of the grains near the porous region boundary
+only have two neighbors.
 
 \begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
+\caption{}
+\end{subfigure}
 \begin{subfigure}[b]{0.5\textwidth}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap} (a): The Delaunay triangulation of the porous media. 
-(b): The distribution of gaps from (a) with the fitting curve of Weibull distribution.}
+\caption{\label{fig:Eroding100gap} (a): The distribution of the pore
+sizes of an eroded geometry. The pores are defined as the space between
+neighboring grains.  The black curve is the Weibull distribution with
+the same first two moments as the data. (b): Two grains are neighbors if
+they share a edge in a Delaunay triangulation of the centers of the
+grains.}
 \end{figure}
@@
 arclength, and then applying a collocation method
-(Section~\ref{sec:spatialDiscretization}).  The quadrature rule is
-either the trapezoid rule or the Barycentric quadrature rule
+(Section~\ref{sec:spatialDiscretization}).  Depending on the proximity
+of the target point to the source points, the quadrature rule is either
+the trapezoid rule or the Barycentric quadrature rule
 (Section~\ref{sec:bary}).  The selection algorithm that determines which
@@
 step by using a {\thL} discretization~\cite{hou-low-she1994}.  By using
-a {\thL} formulation, the stiff curvature term is linear and the
-discretization points remain equispaced in arclength.  Finally, time
-stepping methods for the eroding bodies and passive particles are
-described in Section~\ref{sec:time}
+a {\thL} formulation, the stiff curvature term is linear, treated
+implicitly, and the discretization points remain equispaced in
+arclength.  Finally, time stepping methods for the eroding bodies and
+passive particles are described in Section~\ref{sec:time}
 
@@
 {\thL} formulation.  In addition, we apply mild smoothing
-strategies~\cite{qua-moo2018} to avoid the corners that erosion
-inevitably develop.
+strategies~\cite{qua-moo2018} to avoid the corners that inevitably
+develop in erosion.
 
@@
   \UU_\ell &= \sum_{j=1}^{N_\out} 
-    w^0_j D(\yy^0_\ell,\yy^0_j) \eeta_j +
+    w^0_j D(\yy^0_\ell,\yy^0_j) \eeta_j^0 +
   \sum_{k=1}^M \sum_{j=1}^{N_\iin}
     w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j +
-  \sum_{j=1}^{N_\out} w^0_j N_0(\yy^0_\ell,\yy^0_j) \nonumber \\
+  \sum_{j=1}^{N_\out} w^0_j N_0(\yy^0_\ell,\yy^0_j)\eeta_j^0 
+    \nonumber \\
   &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^0_\ell) + 
@@
   \mathbf{0} &= \sum_{j=1}^{N_\out} 
-    w^0_j D(\yy^m_\ell,\yy^0_j) \eeta_j +
+    w^0_j D(\yy^m_\ell,\yy^0_j) \eeta_j^0 +
   \sum_{k=1}^M \sum_{j=1}^{N_\iin}
@@
 %
-  \llambda_m &= \frac{1}{2\pi} \sum_{j=1}^{N_\iin} \eeta^m_j,  \quad
-  \xi_m = \frac{1}{2\pi} \sum_{j=1}^{N_\iin}
+  \llambda_m &= \frac{1}{2\pi} \sum_{j=1}^{N_\iin} w_j^m \eeta^m_j,
+  \quad \xi_m = \frac{1}{2\pi} \sum_{j=1}^{N_\iin} w_j^m
     (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
@@
 \end{subequations}
-where $w^k_j$ are quadrature weights (which depend on $N_\iin$,
-$N_\out$, and the lengths of $\gamma^k$), and $D$ is the kernel of the
+where $w^k_j$ are quadrature weights that depend on $N_\iin$,
+$N_\out$, and the lengths of $\gamma^k$, and $D$ is the kernel of the
 Stokes double-layer potential defined in
-Equation~\eqref{eqn:velocityDLP}.  The linear
+equation~\eqref{eqn:velocityDLP}.  The linear
 system~\eqref{eqn:trapLinearSystem} is a well-conditioned second-kind
@@
 computed with the Eulerian velocity field~\eqref{eqn:tortuosity2}.  We
-first compute the velocity at $\xx_{ij} = (-1 + i\Delta x, -1 + j\Delta
-y)$, $i,j=1,\ldots,N$, where $\Delta x = \Delta y = 2/N$, and the
-velocity at points inside an eroding body are assigned a value of 0.
-Then, the tortuosity is approximated as
+compute the velocity at $\xx_{ij} = (-1 + i\Delta x, -1 + j\Delta y)$,
+$i,j=1,\ldots,N$, where $\Delta x = \Delta y = 2/N$, and the velocity at
+points inside an eroding body are assigned a value of 0.  Then, the
+tortuosity is approximated as
 \begin{align}
@@
 evaluated at a point close to $\bd\Omega$, then the results become
-unreliable and ultimately unusable.  Hence, we require a quadrature
-method whose error is bounded independent of the target location.
-
-We showed in Sections~\ref{sec:DLPcomplex} and
-Section~\ref{sec:gradDLPcomplex} that the velocity, shear stress, and
-vorticity of the double-layer representation can all be written in terms
-of Cauchy integrals and its first two derivatives.  Therefore, if we
-develop quadrature rules with a uniformly bounded error for Cauchy
-integrals and its derivatives~\eqref{eqn:cauchy}, then the quadrature
-method can be used to accurately compute the velocity, shear stress, and
-vorticity.  Ioakimidis et al.~\cite{ioa-pap-per1991} developed
-quadrature methods, that we call {\em Barycentric quadrature rules}, to
-compute Cauchy integrals and their derivatives with an error bound that
-is independent of $x$.  Then, Barnett et al.~\cite{bar-wu-vee2015}
-applied these quadrature methods to compute the Stokes double-layer
-potential representation of the velocity~\eqref{eqn:velocityDLP}.  We
-build on this method so that the shear stress and vorticity can be
-computed with a uniform error bound.
-
-We briefly summarize the Baryncentric quadrature method for computing
-the velocity~\cite{bar-wu-vee2015}.  Then, so that we can simulate and
-visualize erosion, we apply similar techniques to compute Barycentric
-quadrature rules for the gradient of the velocity.  We present the
-quadrature for a simply-connected interior domain $\Omega$, and we
-consider the target points $x \in \Omega$ and $x \in \Omega^c$. Then,
-the method naturally extends to the eroding geometry by applying the
-quadrature to each of its connected component.  The method starts with
-an underlying quadrature rule, and we use the spectrally accurate
-trapezoid rule.  Since the quadrature points are uniformly distributed,
-the quadrature weights are $w_j = L/N$, $j=1,\ldots,N$, where $L$ is the
-length of $\bd\Omega$.
-
-Again, given a density function $\eta$, the boundary data of
-$v[\eta](\xx)$, as defined in equation~\eqref{eqn:laplaceComplex},
+unreliable and the method ultimately becomes unstable.  Therefore, we
+require a quadrature method whose error is bounded independent of the
+target location.
+
+We showed in Sections~\ref{sec:DLPcomplex} and~\ref{sec:gradDLPcomplex}
+that the velocity, shear stress, and vorticity of the double-layer
+representation can all be written in terms of Cauchy integrals and its
+first two derivatives.  Therefore, if we develop quadrature rules with a
+uniformly bounded error for Cauchy integrals and its
+derivatives~\eqref{eqn:cauchy}, then the quadrature method can be used
+to accurately compute the velocity, shear stress, and vorticity.
+Ioakimidis et al.~\cite{ioa-pap-per1991} developed quadrature rules,
+that we call {\em Barycentric quadrature rules}, to compute Cauchy
+integrals and their derivatives with an error bound that is independent
+of $x$.  Then, Barnett et al.~\cite{bar-wu-vee2015} applied these
+quadrature methods to compute the Stokes double-layer potential
+representation of the velocity~\eqref{eqn:velocityDLP}.  We build on
+this method so that the shear stress and vorticity can be computed with
+a uniform error bound.  We briefly summarize the Baryncentric quadrature
+method for computing the velocity, and we develop similar quadrature
+rules for the gradient of the Stokes double-layer potential.
+
+We present the quadrature rules for a simply-connected interior domain
+$\Omega \subset \CC$, with a point $a \in \Omega$, and we consider the
+target points $x \in \Omega$ and $x \in \Omega^c$. Then, these
+quadrature rules can be applied to individual components of a
+multiply-connected domain to compute layer potentials of a porous media.
+The method starts with an underlying quadrature rule, and we use the
+spectrally accurate trapezoid rule.  Since the quadrature points are
+uniformly distributed, the quadrature weights are $w_j = L/N$,
+$j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
+
+Again, given a complex-valued density function $\eta$, the boundary data
+of $v[\eta](x)$, as defined in equation~\eqref{eqn:laplaceComplex},
 satisfies the Sokhotski-Plemelj jump relation~\eqref{eqn:SPrelation}.
@@
 and $x \in \Omega^c$, we denote the boundary data as $v^-$ for $x \in
-\Omega$, and as $v^+$ otherwise.  Rather than directly applying the
-trapezoid rule to $v(x)$, we start with the identity
+\Omega$, and as $v^+$ for $x \in \Omega^c$.  Rather than directly
+applying the trapezoid rule to $v(x)$, we start with the identity
 \begin{align}
   \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
-    \quad x \in \Omega,
-\end{align}
-where we are considering the interior problem.  Since the integrand is
-bounded as $x$ approaches $\bd\Omega$, we can apply the trapezoid rule
+    \quad x \in \Omega.
+\end{align}
+Since the integrand is bounded as $x$ approaches $\bd\Omega$, we can
+apply the trapezoid rule
 \begin{align}
@@
 Note that the value $v(x)$ is required to compute $v'(x)$ for both the
-interior and exterior case, and these are available using the quadrature
-rules~\eqref{eqn:BaryvInterior} and~\eqref{eqn:BaryvExterior}.
+interior and exterior case, and these are available using the
+Barycentric quadrature rules~\eqref{eqn:BaryvInterior}
+and~\eqref{eqn:BaryvExterior}.
 
@@
 equations~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},
-and~\eqref{eqn:BaryvprimeExterior}.
+and~\eqref{eqn:BaryvprimeExterior}. In Section~\ref{sec:results}, these
+quadrature rules are used to form stable eroding simulations of
+nearly-touching grains, and to study dynamics of the flow in regions
+arbitrarily close to eroding grains.
 
@@
 this cost can be reduced to $\mathcal{O}(N)$ operations.  However, the
-Barycentric quadrature formulas require several $N$-body calculations,
-and they must be done for each component of $\bd\Omega$ individually.
-The resulting cost would be prohibitive, so we use a hybrid method that
+Barycentric quadrature rules require several $N$-body calculations, and
+they must be done for each component of $\bd\Omega$ individually.  The
+resulting cost would be prohibitive, so we use a hybrid method that
 combines the Barycentric quadrature rules and the trapezoid rule.  In
 short, the fast multipole accelerated trapezoid rule is used to compute
-the velocity at most of the discretization points, and the
-non-accelerated Barycentric quadrature rule is used to locally correct
-the trapezoid rule.  Note that for the source points of the layer
-potential is always one of the eroding bodies or the outer wall, but the
-target point can either be on another component of $\bd\Omega$ or it can
-be in the fluid bulk $\Omega$.
+the velocity at all the discretization points, and the non-accelerated
+Barycentric quadrature rule is used to locally correct the errors
+introduced by the trapezoid rule.  Note that the source points of the
+layer potential is always one of the eroding bodies or the outer wall,
+but the target point can either be on another component of $\bd\Omega$
+or it can be in the fluid bulk $\Omega$.
 
@@
 To avoid checking if all target point $\xx$
-satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
-First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
+satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL}
+variables~\cite{hou-low-she1994}.  First, given two eroding bodies $\gamma_i$ and $\gamma_j$ with
 lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we check if
@@
 \end{align}
-where $\alpha_\iin \geq 1$ is a parameter that needs to be chosen.  In
-this manner, rather than using an expensive all-to-all algorithm to
+where $\alpha_\iin \geq 1$ is a parameter that needs to be determined.
+In this manner, rather than using an expensive all-to-all algorithm to
 compute the distance between all pairs of discretization points, we
-compute the distance between pairs of circles.  This criteria allows us
-to quickly determine bodies that contain discretization points where the
-Barycentric quadrature rule may need to be applied, and the parameter
-$\alpha_\iin$ accounts for the fact that the bodies are being
+compute the distance between pairs of circle centers.  This criteria
+allows us to quickly determine bodies that contain discretization points
+where the Barycentric quadrature rule may need to be applied, and the
+parameter $\alpha_\iin$ accounts for the fact that the bodies are being
 approximated with circles.  Assuming that the two bodies $\gamma_i$ and
@@
 $[-3,3] \times [-1,1]$, and that the bodies are all contained in $[-1,1]
-\times [-1,1]$, so a target point can only be too close to the lines $y
-= \pm 1$. Therefore, we first check if
+\times [-1,1]$, so a target point can only be close to the lines $y =
+\pm 1$. Therefore, we first check if
 \begin{align}
@@
 \end{align}
-where $x_i$ is the x coordinate of $\cc_i$. If body $\gamma_i$ satisfies
-this condition, for each point $\xx=(x,y) \in \gamma_i$, we apply the
-Barycentric rule to points that satisfy
+where $x_i$ is the $x$-coordinate of $\cc_i$. If body $\gamma_i$
+satisfies this condition, for each point $\xx=(x,y) \in \gamma_i$, we
+apply the Barycentric rule to points that satisfy
 \begin{align}
@@
 
-To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
+To determine appropriate values for $\alpha_\iin$ and $\alpha_\out$,
 we fixed an eroded geometry and computed an accurate solution by using
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We reuse the time stepping method outlined in our previous
-work~\cite{qua-moo2018} which we briefly summarize here.  Rather than
-tracking the $(x,y)$ coordinates, the {\thL} variables are tracked. In
-addition, a tangential velocity field is added to each body so that the
-discretization points remain equispaced in arclength for all time.  A
-second-order Implicit-Explicit Runge-Kutta method is used. In
+We use the time stepping method outlined in Section 3.3 of our previous
+work~\cite{qua-moo2018} which we briefly summarize here.  The erosion
+rate loses differentiability if the shear stress changes sign, and this
+leads to corners developing on $\gamma$ and numerical instabilities.
+Therefore, we modify the erosion rate, $V_\nn$ in
+equation~\eqref{eqn:erosionModel}, with
+\begin{align}
+  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
+    \frac{L}{2\pi} \kappa - 1 \right),
+\end{align}
+where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average,
+$L$ is the length of $\gamma$, and $\kappa$ is the curvature of
+$\gamma$.  This new term penalizations regions of high curvature, and
+the normalization term guarantees that the regularization only changes
+the body's shape, but not its total length.
+
+Rather than tracking the $(x,y)$ coordinates, the {\thL} variables are
+tracked. In addition, a tangential velocity field is added to each body
+so that the discretization points remain equispaced in arclength for all
+time.  A second-order Implicit-Explicit Runge-Kutta method is used. In
 particular, the diffusive term corresponding to the curvature
@@
 are non-stiff, are treated explicitly.  By using this time stepping
-method in conjunction, we stably evolve the eroding bodies.   An in
-depth description of the time stepping method for erosion is in Section
-3.3 of our previous work~\cite{qua-moo2018}.
+method in conjunction with the Barycentric rule, we stably evolve the
+eroding bodies.  Finally, to increase the overall stability of the
+method, a narrow Gaussian filter is applied to the erosion rate at each
+time step.
 
 To compute the tortuosity and the anomalous dispersion rates
-(Section~\ref{sec:transport}), we require the streamlines governed by equation~\eqref{eqn:tracers}.  To reliably
-characterize the transport, it is crucial that the streamlines are
-computed accurately.  If a low-order time stepping method is used, or if
-$\uu(\ss(t))$ is inaccurate, then a trajectory $\ss(t)$ can unphysically
-enter a grain, rendering the trajectory meaningless to quantify
-transport.  However, if we simply ignored trajectories that pass close
-to grains, this would considerably skew the characterization of the
-transport. Therefore, we use high-order quadrature and time stepping
-methods.  In particular, depending on the proximity of $\ss(t)$ to
-$\bd\Omega$ (Section~\ref{sec:fmm}, we apply the trapezoid rule or the
-Barycentric quadrature rule.  For time stepping, we use a fourth-order
-explicit Runge-Kutta method.  Since the trajectories are computed with
-high-order methods in both space and time,  we are able to simulate
-dynamics very close to the eroding bodies (see
-Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}).
+(Section~\ref{sec:transport}), we require the streamlines that are
+governed by equation~\eqref{eqn:tracers}.  To characterize the
+transport, it is crucial that the streamlines are computed accurately.
+If a low-order time stepping method is used, or if $\uu(\ss(t))$ is
+inaccurate, then a trajectory $\ss(t)$ can unphysically enter a grain,
+rendering the trajectory meaningless to quantify transport.  However, if
+we simply ignore trajectories that pass close to grains, this would
+significantly skew the characterization of the transport. Therefore, we
+use high-order quadrature and time stepping methods.  In particular,
+depending on the proximity of $\ss(t)$ to $\bd\Omega$
+(Section~\ref{sec:fmm}), we apply the trapezoid rule or the Barycentric
+quadrature rule.  For time stepping, we use a fourth-order explicit
+Runge-Kutta method.  Since the trajectories are computed with high-order
+methods in both space and time,  we are able to simulate dynamics very
+close to the eroding bodies (see Figures~\ref{fig:Eroding20tracer}
+and~\ref{fig:Eroding100tort}).
 
@@
 second-moment of the trajectories as described in
-equation~\eqref{eqn:moments}.  However, as described in
-Section~\ref{sec:dispersion}, a reinsertion method is used to compute
-trajectories that are sufficiently long to observe an asymptotic
-anomalous dispersion rate.  To compute the tortuosity using the
-trajectories, we consider trajectories crossing between the two
+equation~\eqref{eqn:moments}.  We use $N_p = 1000$ streamlines so that
+the statistics have converged~\cite{bel-sal-rin1992}.  However, as
+described in Section~\ref{sec:dispersion}, a reinsertion method is used
+to compute trajectories that are sufficiently long to observe an
+asymptotic anomalous dispersion rate.  To compute the tortuosity using
+the trajectories, we consider trajectories crossing between the two
 cross-sections $x=-1$ and $x=1$.  Then, we discretize
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Dump of text}
-In the numerical simulations, we use $N_p = 1000$ streamlines so
-that the statistics have converged~\cite{bel-sal-rin1992}.  
-\todo[inline]{Dump of text}
-
 In this section, we apply our new quadrature method to (1) simulate
@@
 Because of the definition of the erosion rate, there is a loss of
-regularity, and this inevitably leads to corners developing on the
+regularity, and inevitably leads to corners developing on the
 eroding bodies.  Therefore, as described in
@@
 for all subsequent time steps until a body completely disappears.  At
-this point, a new Delaunay triangulation is formed. 
-{\color{red}In Figure~\ref{fig:Eroding100gap_mean_var}, 
-we record the gap distances between bodies neighbors and
-calculate the mean and variance with respect to porosities. 
-For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
-which means the eroding . 
-For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  }
+this point, a new Delaunay triangulation is formed.  {\color{red}In
+Figure~\ref{fig:Eroding100gap_mean_var}, we record the gap distances
+between bodies neighbors and calculate the mean and variance with
+respect to porosities.  For the mean of gap distances, it is linearly
+increacing until $\phi = 85\%$ which means the eroding .  For the
+variance of gap distances, it is almost a constant function until $\phi=
+85\%$  }
 \begin{figure}[H]
@@
 
-We plot the distribution of the gap sizes at six porosities
-in Figure~\ref{fig:Eroding100gap_hist}.  At the initial configuration, there
-are 100 bodies and 258 pairs of neighbors.  The mean distance between
-these neighbors is $???  \times 10^{-???}$ and the variance is $???
-\times 10^{???}$.  As the bodies erode, the mean and variance of the
-distance between the bodies increases.  Finally, when the porosity reaches $95.12\%$
-there are only 34 bodies and 74 pairs of neighbors.
-=======
-bodies.  As described in Section~\ref{sec:throats}, we use a Delaunay
-triangulation to define neighboring eroding bodies, and we compute the
-throat size by finding the closest distance between all neighboring
-bodies.  Once all throat sizes are computed, we analyze their
-distribution as a function of the porosity.  In
-Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the throat
-sizes at six porosities throughout the erosion process.
->>>>>>> 7bba99dc1bad2c9b798e001a13a21b8206449a25
-=======
 Finally, we investigate the effects of erosion on pore sizes.  The
@@
 throat sizes are computed, we analyze their distribution as a function
-of the porosity.
-
-In Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the pore
-throat sizes at six porosities of the erosion process. These
-distributions have been modelled with Weibull
+of the porosity.  In Figure~\ref{fig:Eroding100gap_hist}, we plot
+histograms of the pore throat sizes at six porosities of the erosion
+process. These distributions have been modelled with Weibull
 distributions~\cite{ioa-cha1993}, and we superimpose the Weibull
@@
 variance of the gap sizes quickly grow.
->>>>>>> 95eee70f74046c43a90121249c7d61943d2f436b
 

### 2019-09-19 docs/transport/erosion_transport.tex
worked on abstract and pore size sections

@@
-\documentclass[preprint, 10pt]{elsarticle}
+\documentclass[preprint,10pt]{elsarticle}
 
@@
 \begin{abstract} 
-  An abstract
+  We extend our previous work, [Journal of Computational Physics, {\bf
+  375}:1--21, 2018], to simulate dense suspensions of fluid-mechanical
+  erosion of two-dimensional erosion of porous media. By using a
+  Barycentric quadrature rule, we resolve interactions
+  between nearly touching bodies without requiring an unfeasible number
+  of discretization points.  Since the Barycentric quadrature rule is
+  computationally expensive, it is only used when necessary, and the
+  spectrally accurate trapezoid rule is used otherwise. Our final fluid
+  solver only requires $\mathcal{O}(N)$ iterations per time step. Next,
+  we simulate and analyze transport through eroded porous geometries.
+  Our results demonstrate the effects of erosion on tortuosity,
+  dispersion, and pore size distributions.
 \end{abstract}
@@
 \begin{keyword}
-  Keyword 1 \sep Keyword 2 \sep Keyword 3 
+  Porous media \sep Stokes flow \sep Erosion \sep Quadrature \sep
+  Transport \sep Tortuosity \sep Anomalous dispersion \sep Pore size
+  distributions
 \end{keyword}
@@
 
-Finally, using network models for flow in porous media~\cite{}, the
-anomalous dispersion rate can be linked to channel widths between solid
-bodies.  We construct a Delaunay triangulation with the centers of the
-eroding bodies corresponding to the vertices of the triangles.  Then, if
-the side of a triangle connects two vertices, we call the bodies
-neighbors.  Then, for each pair of neighbors, we measure the distance
-between the bodies.  Once a Delaunay triangulation is formed, it is used
-for all subsequent time steps until a body completely disappears.  At
-this point, a new Delaunay triangulation is formed.  {\color{red}In
-Figure~\ref{fig:Eroding100gap_mean_var}, we record the gap distances
-between bodies neighbors and calculate the mean and variance with
-respect to porosities.  For the mean of gap distances, it is linearly
-increacing until $\phi = 85\%$ which means the eroding .  For the
-variance of gap distances, it is almost a constant function until $\phi=
-85\%$  }
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
-the variance of gaps in (b) with respect to porosity $\phi$ of an
-eroding geometry initialized with 100 bodies . 
-Red stars are six selected porosities to have the details of  
-the disturbutions of gaps and fitting curves of the disturbutions 
-in Figure~\ref{fig:Eroding100gap_hist}.}
-\end{figure}
-
 Finally, we investigate the effects of erosion on pore sizes.  The
@@
 described in Section~\ref{sec:throats}, we use a Delaunay triangulation
-to define neighboring eroding bodies, and we compute the throat size by
+to define neighboring eroding bodies, and we compute the pore size by
 finding the closest distance between all neighboring bodies.  Once all
-throat sizes are computed, we analyze their distribution as a function
+pore sizes are computed, we analyze their distribution as a function
 of the porosity.  In Figure~\ref{fig:Eroding100gap_hist}, we plot
-histograms of the pore throat sizes at six porosities of the erosion
+histograms of the pore pore sizes at six porosities of the erosion
 process. These distributions have been modelled with Weibull
@@
 Figure~\ref{fig:Eroding100gap_mean_var}, we plot the mean and variance
-of the throat sizes as a function of the porosity.  At low porosities,
-the mean grows roughly linearly and the variance is roughly constant
-until about porosity $\phi = 0.85$.  At this point, both the mean and
-variance of the gap sizes quickly grow.
+of the pore sizes as a function of the porosity.  Interestingly, for
+porosities less than $\phi = 85\%$, the mean pore size grows linearly
+and the variance remains nearly flat. Since a channelized geometry has
+large variance, this indicates that channelization is less prevalent at
+low porosities.
 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap_mean_var} The mean (a) and variance
-(b) of the gap sizes of an eroding geometry.  The red stars correspond
-to the six porosities in Figure~\ref{fig:Eroding100gap_hist}.}
+\caption{\label{fig:Eroding100gap_mean_var} The effect of erosion on the
+mean (a) and the variance (b) of the pore sizes. The geometry initially
+contains 100 eroding bodies.  The distributions of the pore sizes in
+Figure~\ref{fig:Eroding100gap_hist} are indicated by the red stars.}
 \end{figure}

### 2019-09-23 docs/transport/erosion_transport.tex
went through intro

@@
 mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
-Flow in porous media is further complicated when there is a two-way
-coupling between the flow and the geometry. For example, the grains of a
-porous media evolve in applications involving
-melting~\cite{bec-vis1998}, dissolution~\cite{kan-zha-che-he2002},
-deposition~\cite{joh-eli1995}, and biofilm
-growth~\cite{tan-val-wer2015}.  We focus on erosion, a fluid-mechanical
-process that is prevalent in many geophysical and hydrological
-applications.
-
 Examples of coarse-grained models for porous media flow include
@@
 dispersion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
-sie-ili-pri-riv-gua2019}, and more.  Some of these works consider
-heterogeneous porous geometries, but to the best of our knowledge, a
-detailed study of transport in eroded geometries has not been performed.
-This paper characterizes transport in eroded geometries by computing and
-analyzing a variety of coarse-grained variables.
-
-When a porous geometry erodes, certain qualitative characteristics are
-unveiled that affect transport through the geometry. For example, an
-eroded geometry often contains channels of high porosity that connect
-the inlet to the outlet, and this results in velocities that vary over
-several orders of magnitude~\cite{all-hea-lab-rei2002}.  Moreover,
-channelized geometries are heterogeneous and anisotropic, and this
-affects the transfer of quantities such as
+sie-ili-pri-riv-gua2019}, and more.
+
+Flow in porous media is further complicated when there is a two-way
+coupling between the flow and the geometry. For example, the grains of a
+porous media evolve in time in applications involving
+melting~\cite{bec-vis1998}, dissolution~\cite{kan-zha-che-he2002},
+deposition~\cite{joh-eli1995}, and biofilm
+growth~\cite{tan-val-wer2015}.  We focus on erosion, a fluid-mechanical
+process that is prevalent in many geophysical and hydrological
+applications.  When a porous geometry erodes, certain qualitative
+characteristics are unveiled that affect transport through the geometry.
+For example, an eroded geometry often contains channels of high porosity
+that connect the inlet to the outlet, and this results in velocities
+that vary over several orders of magnitude~\cite{all-hea-lab-rei2002}.
+Moreover, channelized geometries are heterogeneous and anisotropic, and
+this affects the transport of quantities such as
 contaminants~\cite{cve-che-wen1996, dag1987, kon-bre1978} and
-heat~\cite{nil-sto1990, ree-sto1995}.  To characterize the transport in
-eroded geometries, we must complete three main tasks.  The first two are
-forming high-fidelity numerical solutions of the fluid equations, and
-eroding the grains according to an erosion model. These two tasks are
-performed using our previous work~\cite{qua-moo2018}, but we improve our
-numerical methods so that simulations of more realistic dense
-suspensions of eroding grains are possible
-(Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  Finally,
-in this paper, we simulate and characterize transport through eroded
-porous geometries.
+heat~\cite{nil-sto1990, ree-sto1995}.  To characterize transport in
+eroded geometries, we complete two undertakings: forming realistic
+eroded porous geometries and characterizing transport through these
+geometries.  The modelling effort and numerical methods used to simulate
+erosion are largely based on our previous work~\cite{qua-moo2018}.
+However, we improve our numerical methods so that simulations of more
+realistic dense suspensions of eroding grains are possible
+(Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To
+characterize transport in eroded porous geometries, we apply statistical
+methods to develop coarse-grained variables.
 
@@
 such as groundwater flow~\cite{bea1972}, we model the hydrodynamics with
-the two-dimensional incompressible Stokes equations. A variety of
-numerical methods are available to solve the incompressible Stokes
-equations including lattice-gas or lattice
-Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998}, finite
-volumes~\cite{suo-liu-gan2019, den-ica-hid2018,
-sie-ili-pri-riv-gua2019}, finite differences~\cite{leb-ded-dav-bou2007,
-knu-car2005}, and cellular automata~\cite{rot1988}.  However, to
-accurately simulate erosion and transport, we require a high-order
-method that is able to resolve geometries with arbitrarily shaped and
-nearly-touching grains.  Therefore, we solve the incompressible Stokes
-equations with a boundary integral equation (BIE).  To couple erosion
+the two-dimensional incompressible Stokes equations.  To couple erosion
 with the fluid, the grains are eroded at a rate that is proportional to
@@
 limit, we also compute the vorticity in the fluid bulk
-(Figure~\ref{fig:Eroding50vort}).
-
-To characterize the transport, particle trajectories need to be
-computed. Depending on the application, microscale transport can be
-modelled as pure advection~\cite{dea-qua-bir-jua2018,
-leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019},
-advection-diffusion~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
-with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
-this work, we assume that the trajectories are governed purely by
-advection (ie.~no diffusion).  Therefore, a trajectory $\ss(t)$
-initialized at $\ss_0$ is governed by
-\begin{align}
-  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0,
-  \label{eqn:tracers}
-\end{align}
-where $\uu$ is the fluid velocity, and the trajectories are simply the
-streamlines. Since there is no stiff diffusive term
-in~\eqref{eqn:tracers}, we use a high-order explicit Runge-Kutta time
-stepping method. Other methods to compute streamlines include a
-continuous time random walk~\cite{mon-wei1965, den-cor-sch-ber2004,
-leb-den-car2008, ber-cor-den-sch2006}.
+(Figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
+the fluid solver are available including lattice-gas or lattice
+Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998}, finite
+volumes~\cite{suo-liu-gan2019, den-ica-hid2018,
+sie-ili-pri-riv-gua2019}, finite differences~\cite{leb-ded-dav-bou2007,
+knu-car2005}, and cellular automata~\cite{rot1988}.  However, simulating
+erosion requires a method that is high-order, can resolve
+nearly-touching arbitrarily shaped grains, and can accurately compute
+derivatives of the velocity field.  Since the governing equations are
+linear and homogeneous, we address these challenges by converting the
+fluid equations to a boundary integral equation (BIE).
+
+To compute stable simulations of erosion, we use high-order methods in
+both space and time. The time integration method is unchanged from our
+previous work~\cite{qua-moo2018}.  We apply a mild regularization and a
+smoothing term to eliminate numerical instabilities caused by changes in
+sign of the shear stress, and we use a stable second-order Runge-Kutta
+method applied to the {\thL} coordinates~\cite{hou-low-she1994} of the
+eroding grains.  In this work, we do introduce a new quadrature method
+to resolve dense suspensions of eroding grains.  The accuracy of the
+trapezoid rule, which we used in our previous work, is sufficient for
+bodies that are sufficiently separated~\cite{tre-wei2014}. However, it
+is inaccurate when two grains are nearly-touching.  One of the earliest
+works that addresses quadrature methods for nearly-singular integrands
+was developed by Baker and Shelley~\cite{bak-she1986}, and in recent
+years, many other near-singular integration schemes have been
+developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
+bea-lai2001, klo-bar-gre-one2013}.  We use a Barycentric quadrature
+rule~\cite{bar2014, bar-wu-vee2015} since it is a non-intrusive
+modification of the trapezoid rule, and the error is guaranteed to be
+uniformly bounded.  We extend the original quadrature method so that it
+can be used to compute the gradient of the velocity that is required to
+compute the shear stress and the fluid vorticity.
 
@@
 \includegraphics[height = 0.3 \textwidth]{./figs/vort_50b400}
-\caption{\label{fig:Eroding50vort} The same six snapshots from
+\caption{\label{fig:Eroding50vort} The same six snapshots as
 Figure~\ref{fig:Eroding50vel}.  The color is the vorticity of the fluid.
@@
 
-To be able to compute stable simulations of erosion and accurate
-streamline trajectories, we use high-order methods in both space and
-time. The erosion rate is singular at stagnation points, so we apply a
-mild regularization and smoothing terms to eliminate numerical
-instabilities.  As described in our previous work~\cite{qua-moo2018}, we
-apply a stable second-order Runge-Kutta method is applied to the {\thL}
-coordinates~\cite{hou-low-she1994} of the eroding grains.  In these
-coordinates, the stiff term is linear and treated implicitly, so we are
-able to take large time step sizes. In our previous work, after
-discretizing the BIE, the trapezoid rule is used to approximate the
-integrals. The accuracy of the trapezoid rule is sufficiently accurate
-if all the bodies are sufficiently separated~\cite{tre-wei2014}, but
-nearly-singular integrals must be computed when two grains are
-nearly-touching or when evaluating the velocity or vorticity near an
-eroding grain.  One of the earliest works on near-singular integration
-was developed by Baker and Shelley~\cite{bak-she1986}, and in recent
-years, many other near-singular integration schemes have been
-developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
-bea-lai2001, klo-bar-gre-one2013}.  In this work, we use a Barycentric
-quadrature method~\cite{bar2014, bar-wu-vee2015} since it is a
-non-intrusive modification of the trapezoid rule, and the error is
-guaranteed to be uniformly bounded.  We extend the original quadrature
-method so that it can be used to compute the gradient of the velocity
-that is required to compute the shear stress and the fluid vorticity. In
-addition, the quadrature method is used to accurately compute streamline
-trajectories that pass through the very slow regions close to the
-eroding grains.
+To characterize the transport, particle trajectories need to be
+computed. Depending on the application, microscale transport can be
+modelled as pure advection~\cite{dea-qua-bir-jua2018,
+leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019},
+advection-diffusion~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
+with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
+this work, we assume that the trajectories are governed purely by
+advection (ie.~no diffusion). Therefore, the particle trajectories are
+identical to the streamlines, and they can be found, for example, with a
+continuous time random walk~\cite{mon-wei1965, den-cor-sch-ber2004,
+leb-den-car2008, ber-cor-den-sch2006}.  Instead,  we compute
+trajectories $\ss(t)$ that are initialized at $\ss_0$ by solving
+\begin{align}
+  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0,
+  \label{eqn:tracers}
+\end{align}
+where $\uu$ is the fluid velocity.  Since there is no stiff diffusive
+term in~\eqref{eqn:tracers}, we use a fourth-order explicit Runge-Kutta
+time stepping method.  In addition, the Barycentric quadrature rule is used to
+accurately compute trajectories that are close to an eroding grain.
 
@@
 average particle motions~\cite{hak-com-den2019}.  To characterize
-spreading, the fluid dispersion is computed as the variance of the
-streamline lengths. In porous media, this spreading can often be
+spreading, the fluid dispersion is computed by calculating the variance
+of the streamline lengths. In porous media, this spreading can often be
 characterized with a super-diffusive anomalous dispersion
@@
 solutions of the Stokes equations can be computed.  Using this new
-quadrature method, we accurately compute erosion rates and stably
-simulate erosion.  Moreover, we use the quadrature method to visualize
-the vorticity in the fluid bulk.  The vorticity is convenient to
-visualize since, in the zero Reynolds number limit, it is equivalent to
-the shear stress on the eroding bodies, and therefore its magnitude is
-the erosion rate.
-
-Our second contribution is computing and analyzing trajectories in the
+quadrature rule, we accurately compute erosion rates and stably simulate
+erosion.  Moreover, we use the quadrature method to visualize the
+vorticity in the fluid bulk.  The vorticity is convenient to visualize
+since, in the zero Reynolds number limit, it is equivalent to the shear
+stress on the eroding bodies, and therefore its magnitude is the erosion
+rate.
+
+Our second contribution is computing and analyzing trajectories in
 eroded geometries.  These trajectories are used to characterize the
-transport by computing local tortuosities of the trajectories, the
-tortuosity of the eroded geometry, and the anomalous dispersion rates in
-the geometry.  By using the same quadrature rule and a fourth-order
-Runge-Kutta method, we are able to accurately compute trajectories that
-spend large amounts of time in the slow velocity regions near the
-eroding bodies, and computing these trajectories reliably is essential
-to characterize the flow~\cite{dea-leb-den-tar-bol-dav2013}.  We compare
-our tortuosity and dispersion rates with models available in the
-literature.  Finally, we analyze the effect of erosion on the pore size
-distribution.
+transport by computing the local tortuosity of trajectories, and the
+tortuosity and dispersion rate of eroded geometries. By using the same
+quadrature rule and a fourth-order Runge-Kutta method, we are able to
+accurately compute trajectories that spend large amounts of time in the
+slow velocity regions near the eroding bodies, and reliably computing
+these trajectories is essential to characterize the
+flow~\cite{dea-leb-den-tar-bol-dav2013}.  We compare our tortuosity and
+dispersion rates with models available in the literature.  Finally, we
+analyze the effect of erosion on the pore size distribution.
 
@@
 As in our previous work~\cite{qua-moo2018}, we consider two-dimensional
-immobile eroding grains. However, this new work does not have a limitation on
-the proximity of the bodies. Compared to our previous work, we are able to
-simulate much denser suspensions with a comparable number of
+immobile eroding grains. However, this work does not have a limitation
+on the proximity of the grains. Compared to our previous work, we are
+able to simulate much denser suspensions with a comparable number of
 discretization points and without upsampling.  While we do investigate
-transport in this work, we only consider passive particles that are only
+transport in this work, we only consider passive particles that are
 advected by the flow.  To model other physical processes, such as

### 2019-09-24 docs/transport/erosion_transport.tex
editing transport paper

@@
 $\ell = 1,\ldots,M$.  The boundary of the bounding geometry is $\Gamma$,
-so the fluid domain is bounded by $\bd \Omega = \Gamma \cup \gamma_1
-\cup \cdots \cup \gamma_M$.  In all examples, we let $\Gamma$ be a
-slightly rounded-off version of $[-3,3] \times [-1,1]$, and we only
+so the boundary of the fluid domain is $\bd \Omega = \Gamma \cup
+\gamma_1 \cup \cdots \cup \gamma_M$.  In all examples, we let $\Gamma$
+be a slightly rounded-off version of $[-3,3] \times [-1,1]$, and we only
 place eroding bodies in the region $[-1,1] \times [-1,1]$.  On each
@@
     \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap 
-      &&\mbox{\em conservation of momentum}\\
+      &&\mbox{\em conservation of momentum}, \\
     \grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap 
-      &&\mbox{\em conservation of mass} \\
+      &&\mbox{\em conservation of mass}, \\
     \uu = 0, &\hspace{20pt} \xx \in \gamma, \gap 
-      &&\mbox{\em no slip on the bodies} \\
+      &&\mbox{\em no slip on the bodies}, \\
     \uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap 
-      &&\mbox{\em outer wall velocity} \\
+      &&\mbox{\em outer wall velocity}, \\
     \Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
@@
 \end{align}
-is the shear stress on $\gamma$.  The erosion process is simulated by
-alternating between solving the fluid equations and adancing the grains
-according to the erosion rate for a small time step.
+is the shear stress on $\gamma$.  The strength of $\UU$ is adjusted at
+each time step so that there is a constant pressure drop across the
+channel.  We simulate erosion by alternating between solving the fluid
+equations and adancing the grains according to the erosion rate for a
+small time step.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since require a method to solve the incompressible Stokes equations in
-complex two-dimensional porous geometries, we reformulated the governing
-PDE as a boundary integral equation. This has the advantage that only
-the one-dimensional boundary of the domain must be discretized, and if
-appropriate quadrature formula and fast summation methods are used, the
-result is a high-fidelity numerical simulation that is computed with
-near-optimal complexity.
-
-\subsection{Double-Layer Potential Fromulation in $\RR^2$}
+Since we require a method to solve the incompressible Stokes equations in
+complex two-dimensional porous geometries, we reformulated the
+incompressible Stokes equations as a boundary integral equation. This
+has the advantage that only the one-dimensional boundary of the domain
+must be discretized, and if appropriate quadrature formula and fast
+summation methods are used, the result is a high-fidelity numerical
+simulation that is computed with near-optimal complexity.
+
+\subsection{Double-Layer Potential Formulation in $\RR^2$}
 Applying the same approach as our previous work~\cite{qua-moo2018}, we
@@
 \end{align}
-where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
+where $D$ is an kernel of the integral operator, $\rr = \xx - \yy$,
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
@@
 Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, the deformation
-tensor, pressure, and vorticity of the double-layer potential can all be
-computed analytically.  For $\xx \in \Omega$, the deformation tensor,
-pressure, and vorticity of the double-layer
-potential~\eqref{eqn:velocityDLP} are
+tensor, pressure, and vorticity at $\xx \in \Omega$ are
 \begin{align}
@@
 In equations~\eqref{eqn:velocityDLP} and~\eqref{eqn:deformationDLP},
-$\uu$ and its deformation tensor are written as a contour integral in
-$\RR^2$.  However, so that we can apply a particular quadrature method,
-we write these layer potentials as Cauchy integrals in
-$\CC$ and their derivatives.  The first step is to write the Laplace
-double-layer potential as the complex integral
+$\uu$ and its deformation tensor are written as layer potentials in
+$\RR^2$.  However, the quadrature method we introduce in
+Section~\ref{sec:method} requires a complex-valued representation of the
+layer potentials. The first step is to write the Laplace double-layer
+potential as the complex integral
 \begin{align}
@@
 for multiply-connected domains, such as a porous media, $\bd\Omega$ is
-simply decomposed into its different connected components and the
-appropriate Cauchy integral is evaluated.  Since $v$ is a holomorphic
-function and we have its boundary data, by the Cauchy integral theorem
-we have
+decomposed into its different connected components and the appropriate
+Cauchy integral is evaluated.  Since $v$ is a holomorphic function and
+we have its boundary data, by the Cauchy integral theorem we have
 \begin{align}
@@
 \end{align}
-for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
-\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
-function defined in equation~\eqref{eqn:laplaceComplex}, and its first
-two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
+for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
+function $\eta$, we use the notation $v[\eta](x)$ to denote the
+holomorphic function defined in equation~\eqref{eqn:laplaceComplex}, and
+its first two derivatives are written as $v'[\eta](x)$ and
+$v''[\eta](x)$.
 
 To rewrite the Stokes double-layer potential~\eqref{eqn:velocityDLP} in
-terms of Cauchy integrals and their derivatives, we write it in terms of
-Laplace layer potentials~\cite{bar-wu-vee2015}
+terms of Cauchy integrals and their derivatives, we start by converting
+it into a sequence of Laplace layer potentials~\cite{bar-wu-vee2015}
 \begin{equation}
@@
 the normal and tangent vectors as defined in
-equation~\eqref{eqn:shearStress}.
-
-The gradient of the velocity field can also be used to compute the
-vorticity in the fluid bulk. Since the vorticity of a Stokes flow on
-no-slip walls is equivalent to the shear stress, we make use of the
-vorticity to better understand where the porous media will undergo large
-and small amounts of erosion.  For $x \in \Omega$, the Cauchy integral
-representation of the vorticity is
+equation~\eqref{eqn:shearStress}.  The gradient of the velocity field is
+also used to compute the vorticity in the fluid bulk.  For $x \in
+\Omega$, the Cauchy integral representation of the vorticity is
 \begin{align}
@@
 examined.  Here, we compute the anomalous dispersion rate, the
-tortuosity, and the distribution of the gap sizes.  The first two
-metrics can be defined in terms of streamline governed by an advection
+tortuosity, and the distribution of the pore sizes.  The first two
+metrics can be defined in terms of streamlines governed by an advection
 autonomous equation~\eqref{eqn:tracers}.
@@
 The anomalous dispersion rate depends on the porosity and
-permeability~\cite{koc-bra1988}, but it is also affected by the
+permeability~\cite{koc-bra1988}, but is also affected by the
 distribution and shape of the grains. We calculate the anomalous
@@
   \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
-    \quad j=1,\ldots,N_p,
-\end{align}
-and the first and second ensemble moments
+    \quad j=1,\ldots,N_p.
+\end{align}
+Then, the first and second ensemble moments are
 \begin{align}
@@
     \sigma_\lambda^2(t) = \frac{1}{N_p} 
-    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2.
-\end{align}
-Particle dispersion is characterized as $\sigma_\lambda$.  At early
-times, the particles have not explored much of the geometry, and we
-expect a ballistic motion $\sigma_\lambda \sim t$.  However, as the
-particles pass the grains, their trajectories are altered, and we expect
-that $\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$,
-indicating that the flow is super-dispersive.
+    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2,
+\end{align}
+and $\sigma_\lambda$ characterizes particle dispersion.  At early times,
+the particles have not explored much of the geometry, and we expect a
+ballistic motion $\sigma_\lambda \sim t$.  However, as the particles
+pass the grains, their trajectories are altered, and we expect that
+$\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$, indicating
+that the flow is super-dispersive.
 
@@
 
+\todo[inline]{left off here}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-24 docs/transport/erosion_transport.tex
working on edits

@@
 
-\todo[inline]{left off here}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The tortuosity of a geometry, denoted by $T \geq 1$, is a dimensionless
-number that quantifies the average amount of turning made by
-trajectories passing through the geometry.  Unlike the for the
-dispersion, we do not use reinsertion to form long trajectories.  The
-local tortuosity
-\begin{align}
-  \tau(y) = \frac{\lambda(y)}{d},
+The tortuosity is a dimensionless number that quantifies the amount of
+twisting of streamlines. Unlike the dispersion calculations, we do not
+use reinsertion to form long trajectories.  The local tortuosity is
+\begin{align}
+  \tau(y_0) = \frac{\lambda(y_0)}{d}.
   \label{eqn:localTort}
 \end{align}
-is the length of a single trajectory, $\lambda(y)$, whose initial
-$y$-coordinate is a value $y$ on a cross-section of length $d$.  Taking
-the average over all points on the cross-section defines the hydraulic
-tortuosity
-\begin{align}
-  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
-  {\displaystyle\int_{S}u_x(y)\,dy},
+Here, the streamline is initialized at the point $(x_0,y_0)$ on a
+vertical cross-section of length $d$.  The hydraulic tortuosity is
+defined by taking the average over all points on the cross-section
+\begin{align}
+  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_1(x_0,y_0)\lambda(y_0)\,dy_0}
+  {\displaystyle\int_{S}u_1(x_0,y_0)\,dy_0},
   \label{eqn:tortuosity1}
 \end{align}
-where $S$ is a cross-section perpendicular to the $x$-axis with length
-$d$, $\lambda(y)$ is the length of the trajectory that is initialized at
-the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of the
-velocity at the $y$-coordinate along $S$.  Therefore, the tortuosity
-satisfies $T \geq 1$, and $T=1$ only if no grains are present.
-
-The definition for the tortuosity depends on how the streamlines are
+where $S$ is the cross-section $x = x_0$ that is perpendicular to the
+$x$-axis with length $d$, and $u_1(y_0)$ is the $x$ component of the
+velocity at the initial point of the streamline. Therefore, the
+tortuosity satisfies $T \geq 1$, and $T=1$ only if no grains are
+present.
+
+The tortuosity definition depends on how the streamlines are
 defined, and Duda et al.~\cite{dud-koz-mat2011} summarize several
-options. One choice, that we adopt, considers streamlines that originate
-at $S$ and terminate at a parallel cross-section.  We use the
-cross-sections $x=-1$ and $x=1$.  This choice of averaging allows us to
-also compute the tortuosity in terms of an area integral.  Under the
-assumptions that the flow is incompressible and not re-entrant, meaning
-that all streamlines connect the two cross-sections, the tortuosity in
+options. One choice, that we adopt, uses streamlines that originate at
+$S$ and terminate at a parallel cross-section.  We use the
+cross-sections $x=-1$ and $x=1$ that are at the start and end of the
+porous region.  This choice of averaging allows us to also compute the
+tortuosity in terms of an area integral.  Assuming that the flow is
+incompressible and not re-entrant, meaning that all streamlines connect
+the two cross-sections, the tortuosity in
 equation~\eqref{eqn:tortuosity1} is equivalent to~\cite{dud-koz-mat2011}
@@
   T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
-           {\displaystyle\int_\Omega u_x(\yy)\, d\yy},
+           {\displaystyle\int_\Omega u_1(\yy)\, d\yy},
   \label{eqn:tortuosity2}
@@
 definition for the majority of the tortuosity calculations.  However, we
-do compare the two definitions for the tortuosity at several time steps
+do compare the two definitions for the tortuosity at several porosities
 in Section~\ref{sec:results}.
@@
 Section~\ref{sec:results}, we compare these four models with the
-tortuosity of eroding geometries.
+tortuosity of eroding porous geometries.
 
@@
 channelization~\cite{sie-ili-pri-riv-gua2019}, and more. In addition,
-pore network models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}
-rely on descriptions of the pore throat sizes. To characterize the grain
-placement, we compute distributions of gap sizes between neighboring
+the grain configuration is important for pore network
+models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} that rely on
+descriptions of the pore throat sizes. To characterize the grain
+placement, we compute distributions of pore sizes between neighboring
 grains.  To define neighboring grains, we form a Delaunay triangulation
-of nodes placed at the center of each eroding grain and at a collection
+using nodes placed at the center of each eroding grain and at a collection
 of points around the boundary of the porous region.  Then, we say that
@@
 Figure~\ref{fig:Eroding100gap}(a), we plot a histogram of the pore size
-of 100 eroded bodies.  The black curve is an un-normalized Weibull
+of 100 eroded bodies.  The black curve is an unnormalized Weibull
 distribution with the same mean and variance as the measured data.  In
-Figure~\ref{fig:Eroding100gap}(b), we plot lines connected the two
-closest points of all neighboring gaps. We do not consider pores between
-eroding bodies and the solid and the artificial points placed around the
-porous region, so some of the grains near the porous region boundary
-only have two neighbors.
+Figure~\ref{fig:Eroding100gap}(b), we plot illustrate the pore throat
+sizes by drawing the shortest lines between neighboring grains.  We do
+not consider pores between eroding bodies and the solid and the
+artificial points placed around the porous region, so some of the grains
+near the porous region boundary only have two neighbors.
 
@@
 \caption{\label{fig:Eroding100gap} (a): The distribution of the pore
-sizes of an eroded geometry. The pores are defined as the space between
-neighboring grains.  The black curve is the Weibull distribution with
-the same first two moments as the data. (b): Two grains are neighbors if
-they share a edge in a Delaunay triangulation of the centers of the
-grains.}
+sizes of an eroded geometry. The black curve is the Weibull distribution
+with the same first two moments as the data. (b): We only consider pore
+sizes between neighboring grains, where two grains are neighbors if they
+share a edge in a Delaunay triangulation using nodes placed at the
+center of each eroding grain.}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{left off here}
 In line with our previous work~\cite{qua-moo2018}, we use two meshes to
@@
   T = \frac{\sum\limits_{i,j=1}^N \|\uu(\xx_{ij})\|\Delta x \Delta y}
-      {\sum\limits_{i,j=1}^N u_x(\xx_{ij}) \Delta x \Delta y}.
+      {\sum\limits_{i,j=1}^N u_1(\xx_{ij}) \Delta x \Delta y}.
 \end{align}
@@
   T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N_p} 
-    u_x(y_i) \lambda(y_i) \Delta y}
-  {\displaystyle\sum_{i=1}^{N_p} u_x(y_i) \Delta y}, 
+    u_1(y_i) \lambda(y_i) \Delta y}
+  {\displaystyle\sum_{i=1}^{N_p} u_1(y_i) \Delta y}, 
 \end{align}
@@
 results in straighter streamlines, therefore reducing $\lambda$, the
-horizontal flow, $u_x(y)$ increases since there is no longer a no-slip
+horizontal flow, $u_1(y)$ increases since there is no longer a no-slip
 boundary.  At the very late stages of erosion, we have observed that

### 2019-09-24 docs/transport/erosion_transport.tex
still editing ...

@@
 term in~\eqref{eqn:tracers}, we use a fourth-order explicit Runge-Kutta
-time stepping method.  In addition, the Barycentric quadrature rule is used to
-accurately compute trajectories that are close to an eroding grain.
+time stepping method.  In addition, the Barycentric quadrature rule is
+used to accurately compute trajectories that are close to an eroding
+grain.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{left off here}
 In line with our previous work~\cite{qua-moo2018}, we use two meshes to
 simulate erosion. The integral equation is solved by discretizing the
-boundary of the geometry at a set of points distributed equally in
-arclength, and then applying a collocation method
-(Section~\ref{sec:spatialDiscretization}).  Depending on the proximity
-of the target point to the source points, the quadrature rule is either
-the trapezoid rule or the Barycentric quadrature rule
-(Section~\ref{sec:bary}).  The selection algorithm that determines which
-quadrature method is applied is described in Section~\ref{sec:fmm}.
-Once the shear stress is computed, the bodies are eroded a single time
-step by using a {\thL} discretization~\cite{hou-low-she1994}.  By using
-a {\thL} formulation, the stiff curvature term is linear, treated
-implicitly, and the discretization points remain equispaced in
-arclength.  Finally, time stepping methods for the eroding bodies and
-passive particles are described in Section~\ref{sec:time}
+boundary of the geometry at a set of collocation points distributed
+equally in arclength (Section~\ref{sec:spatialDiscretization}).
+Depending on the proximity of the target point to the source points, the
+quadrature rule is either the trapezoid rule or the Barycentric
+quadrature rule (Section~\ref{sec:bary}).  The selection algorithm that
+determines which quadrature method is applied is described in
+Section~\ref{sec:fmm}.  Once the shear stress is computed, the bodies
+are eroded a single time step by using a {\thL}
+discretization~\cite{hou-low-she1994}.  The time stepping methods for
+erosion and passive particles are described in Section~\ref{sec:time}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-By using an integral equation formulation, we only have to discretize
-the one-dimensional boundary of the domain.  Therefore, we easily
-resolve complex geometries, and differentiation is performed with
-spectral accuracy in Fourier space.  We discretize each eroding body
-$\gamma_k$ with $N_\iin$ points and discretize the outer wall $\Gamma$
-with $N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ and
+Since we use a BIE formulation, we only have to discretize the
+one-dimensional boundary of the domain.  Therefore, we easily resolve
+complex geometries, and differentiation is performed with spectral
+accuracy in Fourier space.  We discretize each eroding body $\gamma_k$
+with $N_\iin$ points and discretize the outer wall $\Gamma$ with
+$N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ and
 $\gamma_k$ are denoted by $\yy_j^0$ and $\yy^k_j$, respectively.  The
@@
 \end{subequations}
-where $w^k_j$ are quadrature weights that depend on $N_\iin$,
-$N_\out$, and the lengths of $\gamma^k$, and $D$ is the kernel of the
+where $w^k_j$ are quadrature weights that depend on $N_\iin$, $N_\out$,
+and the lengths of $\gamma^k$ and $\Gamma$, and $D$ is the kernel of the
 Stokes double-layer potential defined in
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since the error of the trapezoid rule applied to periodic functions
-depends on the derivative of the integrand~\cite{tre-wei2014}, the
-trapezoid rule applied in Section~\ref{sec:spatialDiscretization} is
-only appropriate if the target point is sufficiently separated from all
-eroding bodies and the outer wall.  Therefore, if the trapezoid rule is
-applied when bodies are in near-contact, or when a layer potential is
-evaluated at a point close to $\bd\Omega$, then the results become
-unreliable and the method ultimately becomes unstable.  Therefore, we
-require a quadrature method whose error is bounded independent of the
-target location.
+Since we are applying quadrature to periodic smooth functions, the
+trapezoid rule is spectrally accurate~\cite{tre-wei2014}. However, since
+the derivative of the integrands grows as the target point $\xx$
+approaches $\bd\Omega$, the error bound of the trapezoid rule depends on
+the location of the target point. Therefore, if the trapezoid rule, as
+described in Section~\ref{sec:spatialDiscretization}, is applied when
+bodies are in near-contact, or when a layer potential is evaluated at a
+point close to $\bd\Omega$, then the results become unreliable and the
+method ultimately becomes unstable.  Thus, we require a quadrature
+method with an error bound that is independent of the target location.
 
@@
 that the velocity, shear stress, and vorticity of the double-layer
-representation can all be written in terms of Cauchy integrals and its
-first two derivatives.  Therefore, if we develop quadrature rules with a
-uniformly bounded error for Cauchy integrals and its
-derivatives~\eqref{eqn:cauchy}, then the quadrature method can be used
-to accurately compute the velocity, shear stress, and vorticity.
-Ioakimidis et al.~\cite{ioa-pap-per1991} developed quadrature rules,
-that we call {\em Barycentric quadrature rules}, to compute Cauchy
-integrals and their derivatives with an error bound that is independent
-of $x$.  Then, Barnett et al.~\cite{bar-wu-vee2015} applied these
-quadrature methods to compute the Stokes double-layer potential
-representation of the velocity~\eqref{eqn:velocityDLP}.  We build on
-this method so that the shear stress and vorticity can be computed with
-a uniform error bound.  We briefly summarize the Baryncentric quadrature
-method for computing the velocity, and we develop similar quadrature
-rules for the gradient of the Stokes double-layer potential.
+representation can all be written as the sum of Cauchy integrals and its
+first two derivatives.  Therefore, we can accurately compute the
+velocity, shear stress, and vorticity at any target location if we
+develop a quadrature rules with a uniform error bounded for Cauchy
+integrals and its derivatives~\eqref{eqn:cauchy}.  Ioakimidis et
+al.~\cite{ioa-pap-per1991} developed quadrature rules, that we call {\em
+Barycentric quadrature rules}, to compute Cauchy integrals and their
+derivatives with an error bound that is independent of $x \in \CC$.
+Then, Barnett et al.~\cite{bar-wu-vee2015} used these quadrature rules
+to compute the Stokes double-layer potential representation of the
+velocity~\eqref{eqn:velocityDLP}, and we briefly summarize their method.
+Then, we build on this work to accurately compute the gradient of the
+Stokes double-layer potential so that we form the shear stress and
+vorticity.
 
@@
 satisfies the Sokhotski-Plemelj jump relation~\eqref{eqn:SPrelation}.
-Since the boundary data of $v$ differs when considering $x \in \Omega$
-and $x \in \Omega^c$, we denote the boundary data as $v^-$ for $x \in
-\Omega$, and as $v^+$ for $x \in \Omega^c$.  Rather than directly
-applying the trapezoid rule to $v(x)$, we start with the identity
+Since the limiting boundary data of $v$ differs when considering $x \in
+\Omega$ and $x \in \Omega^c$, we denote the boundary data as $v^-$ for
+$x \in \Omega$, and as $v^+$ for $x \in \Omega^c$.  Rather than directly
+applying the trapezoid rule to approximate $v(x)$ in
+equation~\eqref{eqn:cauchy}, we start with the identity
 \begin{align}
@@
 \end{align}
-Since the integrand is bounded as $x$ approaches $\bd\Omega$, we can
-apply the trapezoid rule
+Since the integrand is bounded for all $x \in \Omega$, we can apply the
+trapezoid rule
 \begin{align}
@@
 \end{align}
-Similar to the quadrature rule for $v'(x)$ requiring the value $v(x)$,
-the quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$.
-Both these quantities are computed using the quadrature rules in
+The quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$,
+and theses are computed using the quadrature rules in
 equations~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Barycentric quadrature rule achieves acceptable accuracy for
-computing the velocity, shear stress, and vorticity.  However, applied
-directly, it requires $\mathcal{O}(N^2)$ operations.  By using a fast
-summation method, such as the fast multipole method~\cite{gre-rok1987},
-this cost can be reduced to $\mathcal{O}(N)$ operations.  However, the
-Barycentric quadrature rules require several $N$-body calculations, and
-they must be done for each component of $\bd\Omega$ individually.  The
-resulting cost would be prohibitive, so we use a hybrid method that
-combines the Barycentric quadrature rules and the trapezoid rule.  In
-short, the fast multipole accelerated trapezoid rule is used to compute
-the velocity at all the discretization points, and the non-accelerated
-Barycentric quadrature rule is used to locally correct the errors
-introduced by the trapezoid rule.  Note that the source points of the
-layer potential is always one of the eroding bodies or the outer wall,
-but the target point can either be on another component of $\bd\Omega$
-or it can be in the fluid bulk $\Omega$.
-
+By using the Barycentric quadrature rule, the velocity, shear stress,
+and vorticity are computed with an error that is bounded independent of
+the target location. However, applied directly, it requires
+$\mathcal{O}(N^2)$ operations.  By using a fast summation method, such
+as the fast multipole method~\cite{gre-rok1987}, this cost can be
+reduced to $\mathcal{O}(N)$ operations.  However, the Barycentric
+quadrature rules require several $N$-body calculations, and they must be
+done for each component of $\bd\Omega$ individually.  The resulting cost
+would be prohibitive, so we introduce a hybrid method that combines the
+Barycentric quadrature rule and the trapezoid rule.  In short, the fast
+multipole accelerated trapezoid rule is used to compute the velocity at
+all the discretization points, and the non-accelerated Barycentric
+quadrature rule is used to locally correct the errors introduced by the
+trapezoid rule.  Note that the source points of the layer potential is
+always one of the eroding bodies or the outer wall, but the target point
+can either be on another component of $\bd\Omega$ or it can be in the
+fluid bulk $\Omega$.
+
+\todo[inline]{left off here}
 To compute the velocity double-layer potential, we start by applying the

### 2019-09-24 docs/transport/erosion_transport.tex
NM

--- 2019-09-24 docs/transport/erosion_transport.tex
@@
 $10^{-1}\mathrm{m}$~\cite{mil-chr-imh-mcb-ped1998}, velocity scales can
-be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}, and
+be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}, \nick{and
 the scales of a single porous media can range over several orders of
-magnitude. Numerical methods that accurately address all of these scales
+magnitude.}\todo[inline]{Nick: I am confused by the last part of the sentence.
+What 'scale' are you referring to?
+Length?
+You already described the length scales in the first part of the sentence.
+Maybe you mean to distinguish between the grain length scales and the overall length scales of the system.
+If so, you can use adjectives like `grain' and `macroscopic' or `overall' to clarify that.}
+Numerical methods that accurately address all of these scales
 are essential to develop meaningful constitutive relationships between

### 2019-09-24 docs/transport/erosion_transport.tex
edited up to numerical results

--- 2019-09-24 docs/transport/erosion_transport.tex
@@
 would be prohibitive, so we introduce a hybrid method that combines the
-Barycentric quadrature rule and the trapezoid rule.  In short, the fast
-multipole accelerated trapezoid rule is used to compute the velocity at
-all the discretization points, and the non-accelerated Barycentric
-quadrature rule is used to locally correct the errors introduced by the
-trapezoid rule.  Note that the source points of the layer potential is
-always one of the eroding bodies or the outer wall, but the target point
-can either be on another component of $\bd\Omega$ or it can be in the
-fluid bulk $\Omega$.
-
-\todo[inline]{left off here}
+Barycentric quadrature rule and the trapezoid rule.  Note that the
+source points of the layer potential is always one of the eroding bodies
+or the outer wall, but the target point can either be on another
+component of $\bd\Omega$ or it can be in the fluid bulk $\Omega$.
+
 To compute the velocity double-layer potential, we start by applying the
@@
 calculation requires $\mathcal{O}(N)$ operations, and we call the
-resulting velocity $\vv_\trap(\xx)$.  Depending on the number of
-discretization points $N_\iin$ and $N_\out$, there is a region separated
-from $\bd\Omega$ where the error of $\vv_\trap(\xx)$ is less than a
-user-specified tolerance.  However, for the other points in $\Omega$,
-the trapezoid rule needs to be replaced with a more accurate quadrature
-rule.  Note, however, that since a point is typically only close to one
-or two components of $\bd\Omega$, only the contribution of these nearby
-bodies need to be replaced.  Assuming that $\xx$ is too close to
-$\gamma_k$, we first subtract the inaccurate approximation of the
-double-layer potential due to $\gamma_k$.  Then, the Barycentric
-quadrature rule is used to compute the velocity due to $\gamma_k$ with
-more accuracy.  That is, the final velocity is
+resulting velocity $\vv_\trap(\xx)$.  Since the trapezoid rule is
+spectrally accurate, the error of $\vv_\trap(\xx)$ is small for points
+sufficiently far from $\bd\Omega$, and this region depends on the number
+of discretization points $N_\iin$ and $N_\out$.  However, the trapezoid
+rule needs to be replaced with a more accurate quadrature rule for
+points that are too close to $\bd\Omega$.  Note, however, that since a
+point is typically only close to one or two components of $\bd\Omega$,
+only the contribution of these nearby bodies needs to be replaced.
+Assuming that $\xx$ is too close to $\gamma_k$, we first subtract the
+inaccurate trapezoid rule approximation of the double-layer potential
+due to $\gamma_k$.  Then, the Barycentric quadrature rule is used to
+compute the velocity due to $\gamma_k$ with more accuracy.  That is, the
+final velocity is
 \begin{align}
@@
 the FMM.  Relative to the cost of computing the velocity at each
-iteration of GMRES with the FMM, the additional once-per-time-step cost
-to compute the vorticity and deformation tensor is minimal.
+iteration of GMRES with the FMM, the additional once-per-time-step costs
+to compute the vorticity and deformation tensor are minimal.
 
@@
 allows us to quickly determine bodies that contain discretization points
-where the Barycentric quadrature rule may need to be applied, and the
+where the Barycentric quadrature rule might need to be applied, and the
 parameter $\alpha_\iin$ accounts for the fact that the bodies are being
@@
 To determine if points on $\gamma_i$ are too close to the outer wall, we
-recall that the geometry is contained in a rounded-off version of
-$[-3,3] \times [-1,1]$, and that the bodies are all contained in $[-1,1]
-\times [-1,1]$, so a target point can only be close to the lines $y =
-\pm 1$. Therefore, we first check if
+recall that the eroding bodies are all contained in $[-1,1] \times
+[-1,1]$, so a target point can only be close to the lines $y = \pm 1$.
+Therefore, we first check if
 \begin{align}
@@
 so that the discretization points remain equispaced in arclength for all
-time.  A second-order Implicit-Explicit Runge-Kutta method is used. In
-particular, the diffusive term corresponding to the curvature
-penalization term is discretized implicitly, and all other terms, which
-are non-stiff, are treated explicitly.  By using this time stepping
-method in conjunction with the Barycentric rule, we stably evolve the
-eroding bodies.  Finally, to increase the overall stability of the
-method, a narrow Gaussian filter is applied to the erosion rate at each
-time step.
+time.  Additionally, to increase the overall stability of the method, a
+narrow Gaussian filter is applied to the erosion rate at each time step.
+Time stepping is performed with a second-order Implicit-Explicit
+Runge-Kutta method. In particular, the diffusive term corresponding to
+the curvature penalization term is discretized implicitly, and all other
+terms, which are non-stiff, are treated explicitly.  By using this time
+stepping method in conjunction with the Barycentric rule, we stably
+evolve the eroding bodies.
 
@@
 Once a collection of trajectories are formed, they are used to quantify
-the dispersion and the tortuosity.  The dispersion simply computes the
-second-moment of the trajectories as described in
-equation~\eqref{eqn:moments}.  We use $N_p = 1000$ streamlines so that
-the statistics have converged~\cite{bel-sal-rin1992}.  However, as
+the dispersion and the tortuosity.  We use $N_p = 1000$ streamlines so
+that the statistics have converged~\cite{bel-sal-rin1992}.  However, as
 described in Section~\ref{sec:dispersion}, a reinsertion method is used
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{here}
 In this section, we apply our new quadrature method to (1) simulate

### 2019-09-24 docs/transport/erosion_transport.tex
NM

--- 2019-09-24 docs/transport/erosion_transport.tex
@@
 the scales of a single porous media can range over several orders of
-magnitude.}\todo[inline]{Nick: I am confused by the last part of the sentence.
-What 'scale' are you referring to?
+magnitude.}
+%
+\todo[inline]{Nick: I am confused by the last part of the sentence (highlighted in red).
+What `scale' are you referring to?
 Length?
@@
 If so, you can use adjectives like `grain' and `macroscopic' or `overall' to clarify that.}
-Numerical methods that accurately address all of these scales
-are essential to develop meaningful constitutive relationships between
-the microscopic and macroscopic scales~\cite{mil-chr-imh-mcb-ped1998},
-to characterize dispersion~\cite{saf1959}, and to quantify
-mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
+%
+Numerical methods that \st{accurately address all of these} \nick{resolve this range of} scales offer the ability to: (i) characterize dispersion~\cite{saf1959}, (ii) quantify mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}, and (iii) potentially develop meaningful constitutive relationships that link the microscopic and macroscopic realms~\cite{mil-chr-imh-mcb-ped1998}.
+%
+\todo[inline]{Nick: I reworded the above sentence. See if you agree with my changes.}
+%
 Examples of coarse-grained models for porous media flow include
@@
 porous media evolve in time in applications involving
-melting~\cite{bec-vis1998}, dissolution~\cite{kan-zha-che-he2002},
-deposition~\cite{joh-eli1995}, and biofilm
-growth~\cite{tan-val-wer2015}.  We focus on erosion, a fluid-mechanical
+melting~\cite{bec-vis1998, rycroft2016asymmetric, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, wykes2018self},
+deposition~\cite{joh-eli1995}, biofilm growth~\cite{tan-val-wer2015}, and \nick{crack formation} \cite{cho2019crack}.  
+%
+\todo[inline]{Nick: I added some references.
+Check out the last one on crack formation in shrinkable, granular packings.
+It is really cool work done by an excellent experimentalist Sujit Datta.
+I met him and he voiced a strong interest in our work, so wanted to make you aware.}
+%
+We focus on erosion, a fluid-mechanical
 process that is prevalent in many geophysical and hydrological

### 2019-09-24 docs/transport/erosion_transport.tex

--- 2019-09-24 docs/transport/erosion_transport.tex
@@
 $10^{-1}\mathrm{m}$~\cite{mil-chr-imh-mcb-ped1998}, velocity scales can
-be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}, and
+be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}, \nick{and
 the scales of a single porous media can range over several orders of
-magnitude. Numerical methods that accurately address all of these scales
-are essential to develop meaningful constitutive relationships between
-the microscopic and macroscopic scales~\cite{mil-chr-imh-mcb-ped1998},
-to characterize dispersion~\cite{saf1959}, and to quantify
-mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
+magnitude.}
+%
+\todo[inline]{Nick: I am confused by the last part of the sentence (highlighted in red).
+What `scale' are you referring to?
+Length?
+You already described the length scales in the first part of the sentence.
+Maybe you mean to distinguish between the grain length scales and the overall length scales of the system.
+If so, you can use adjectives like `grain' and `macroscopic' or `overall' to clarify that.}
+%
+Numerical methods that \st{accurately address all of these} \nick{resolve this range of} scales offer the ability to: (i) characterize dispersion~\cite{saf1959}, (ii) quantify mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}, and (iii) potentially develop meaningful constitutive relationships that link the microscopic and macroscopic realms~\cite{mil-chr-imh-mcb-ped1998}.
+%
+\todo[inline]{Nick: I reworded the above sentence. See if you agree with my changes.}
+%
 Examples of coarse-grained models for porous media flow include

### 2019-09-24 docs/transport/erosion_transport.tex
NM

@@
 $10^{-1}\mathrm{m}$~\cite{mil-chr-imh-mcb-ped1998}, velocity scales can
-be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}, \nick{and
+be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}, \awk{and
 the scales of a single porous media can range over several orders of
@@
 %
-\todo[inline]{Nick: I am confused by the last part of the sentence (highlighted in red).
+\todo[inline]{Nick: I am confused by the last part of the sentence (highlighted in purple).
 What `scale' are you referring to?
@@
 coupling between the flow and the geometry. For example, the grains of a
-porous media evolve in time in applications involving
-melting~\cite{bec-vis1998, rycroft2016asymmetric, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, wykes2018self},
-deposition~\cite{joh-eli1995}, biofilm growth~\cite{tan-val-wer2015}, and \nick{crack formation} \cite{cho2019crack}.  
+porous media evolve in time in applications involving melting~\cite{bec-vis1998, rycroft2016asymmetric, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moore2017riemann, wykes2018self}, deposition~\cite{joh-eli1995, hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and \nick{crack formation} \cite{cho2019crack}.
 %
@@
 We focus on erosion, a fluid-mechanical
-process that is prevalent in many geophysical and hydrological
-applications.  When a porous geometry erodes, certain qualitative
-characteristics are unveiled that affect transport through the geometry.
-For example, an eroded geometry often contains channels of high porosity
-that connect the inlet to the outlet, and this results in velocities
+process that is prevalent in many geophysical, hydrological, \nick{and industrial} 
+applications \cite{berhanu2012shape, hewett2017evolution, lopez2018cfd, allen2019sde, amin2019role}.
+\todo[inline]{Nick: Check out the first reference, Berhanu, Kudrolli, Rothman PRE 2012.
+Maybe we can cite it a couple more times throughout since it has both the words `erosion' and `granular bed' in the title :)}
+When a porous geometry erodes, certain qualitative characteristics are unveiled that affect transport through the geometry.
+For example, an eroded geometry may contain channels of high porosity, \nick{which, though few in number and modest in volume fraction, transmit a large portion of the flux}.
+This arrangement results in velocities
 that vary over several orders of magnitude~\cite{all-hea-lab-rei2002}.
-Moreover, channelized geometries are heterogeneous and anisotropic, and
-this affects the transport of quantities such as
+%
+\todo[inline]{Nick: I rearranged the above two sentences. See if you like it.}
+%
+Moreover, \nick{channelization creates a heterogeneous and anisotropic medium properties}, \st{and
+this affects} \nick{affecting} the transport of \st{quantities} \nick{tracers} such as
 contaminants~\cite{cve-che-wen1996, dag1987, kon-bre1978} and
-heat~\cite{nil-sto1990, ree-sto1995}.  To characterize transport in
+heat~\cite{nil-sto1990, ree-sto1995}.  \awk{To characterize transport in
 eroded geometries, we complete two undertakings: forming realistic
 eroded porous geometries and characterizing transport through these
-geometries.  The modelling effort and numerical methods used to simulate
-erosion are largely based on our previous work~\cite{qua-moo2018}.
-However, we improve our numerical methods so that simulations of more
-realistic dense suspensions of eroding grains are possible
-(Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To
-characterize transport in eroded porous geometries, we apply statistical
-methods to develop coarse-grained variables.
+geometries}.  
+\todo[inline]{Nick: The purple sentence is redundant: `To \underline{characterize transport} ...
+we undertake ...
+\underline{characterizing transport} through these geometries.
+Maybe try something like this:}
+\nick{This study consists of two main undertakings: First, high-fidelity simulations of porous-medium erosion, and, second, the characterization of transport through the resulting geometries.}
+Our modeling efforts build on previous work \cite{ris-moo-chi-she-zha2012, moore2013self, moore2017riemann}, in particular recent numerical methods developed to simulate erosion in the regime of Stokes flow \cite{qua-moo2018}.
+We, however, make a few key improvements to the numerical methods from \cite{qua-moo2018} to enable simulations of more realistic, dense suspensions of eroding grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).
+To characterize transport in the resulting geometries, \st{we apply statistical methods to develop coarse-grained variables} \nick{examine coarse-grained variables through statistical analysis of tracer trajectories}.
+\todo[inline]{I'm not sure about my modification above, but see if it gets across the message that was intended.}
 
@@
 
-Because of the length and velocity scales in hydrological applications
-such as groundwater flow~\cite{bea1972}, we model the hydrodynamics with
-the two-dimensional incompressible Stokes equations.  To couple erosion
-with the fluid, the grains are eroded at a rate that is proportional to
-the magnitude of the hydrodynamic shear stress~\cite{wan-fel2004,
-ris-moo-chi-she-zha2012, par-izu2000}.  Since the vorticity and the
-shear stress are equivalent on the grains in the zero Reynolds number
-limit, we also compute the vorticity in the fluid bulk
-(Figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
+\st{Because of the length and velocity scales in hydrological applications
+such as groundwater flow} \nick{Owing to the scales present in groundwater flow} \cite{bea1972}, we model the hydrodynamics with
+the two-dimensional incompressible Stokes equations.  \st{To couple erosion
+with the fluid} Meanwhile, individual grains erode at a rate \st{that is} proportional to \st{the magnitude of} the hydrodynamic shear stress~\cite{wan-fel2004,
+ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  Since the vorticity and the shear stress are equivalent on the grains in the zero Reynolds number
+limit, we also compute the vorticity in the fluid bulk \nick{for visualization purposes} (Figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
 the fluid solver are available including lattice-gas or lattice

### 2019-09-25 docs/transport/erosion_transport.tex
few changes that S-H found

@@
 channel.  We simulate erosion by alternating between solving the fluid
-equations and adancing the grains according to the erosion rate for a
+equations and advancing the grains according to the erosion rate for a
 small time step.
@@
   \begin{aligned}
-    u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
+    u_1(x) &= \Re (v[\psi_1](x)) + \Re (v'[y\cdot\eta](x)) 
              -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
-    u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
+    u_2(x) &= \Re (v[\psi_2](x)) - \Im (v'[y\cdot\eta](x)) 
          +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
@@
 \begin{align} 
-  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad
-  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
+  \psi_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad
+  \psi_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
 \end{align}
@@
   \begin{aligned}
-    \pderiv{u_1}{x_1} &= +\Re (v'[\tau_1](x)) + 
+    \pderiv{u_1}{x_1} &= +\Re (v'[\psi_1](x)) + 
       \Re (v''[y\cdot\eta](x)) - \Re (v'[\eta_1](x)) - 
       x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
-    \pderiv{u_1}{x_2} &= - \Im (v'[\tau_1](x)) - 
+    \pderiv{u_1}{x_2} &= - \Im (v'[\psi_1](x)) - 
       \Im (v''[y\cdot\eta](x)) + x_1\Im (v''[\eta_1](x)) - 
       \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
-    \pderiv{u_2}{x_1} &= +\Re (v'[\tau_2](x)) - 
+    \pderiv{u_2}{x_1} &= +\Re (v'[\psi_2](x)) - 
       \Im (v''[y\cdot\eta](x)) + \Im (v'[\eta_1](x)) +
       x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
-    \pderiv{u_2}{x_2} &= -\Im (v'[\tau_2](x)) - 
+    \pderiv{u_2}{x_2} &= -\Im (v'[\psi_2](x)) - 
       \Re (v''[y\cdot\eta](x)) + x_1\Re (v''[\eta_1](x)) +
@@
   \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
-\Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
+\Re (v'[\psi_2](x)) + \Im (v'[\psi_1](x)) 
  + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)), \quad x \in \Omega.
@@
 \begin{align}
-  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
+  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tilde{t})\|\, d\tilde{t}, 
     \quad j=1,\ldots,N_p.
@@
 \end{align}
-Here, the streamline is initialized at the point $(x_0,y_0)$ on a
-vertical cross-section of length $d$.  The hydraulic tortuosity is
-defined by taking the average over all points on the cross-section
+Here, the streamline originates at $(x_0,y_0)$ on the inlet and its
+arclength is calculated once it passes the parallel outlet $x = x_0 +
+d$.  The hydraulic tortuosity is defined by taking the average over all
+points on the cross-section
 \begin{align}
@@
 \end{align}
-where $S$ is the cross-section $x = x_0$ that is perpendicular to the
-$x$-axis with length $d$, and $u_1(y_0)$ is the $x$ component of the
-velocity at the initial point of the streamline. Therefore, the
-tortuosity satisfies $T \geq 1$, and $T=1$ only if no grains are
-present.
+where $S$ is the inlet cross-section $x = x_0$ that is perpendicular to
+the $x$-axis, $u_1(y_0)$ is the $x$ component of the velocity at the
+initial point of the streamline, and $d$ is still the distance between
+the inlet and outlet. Therefore, the tortuosity satisfies $T \geq 1$,
+and $T=1$ only if no grains are present.
 
@@
 sizes by drawing the shortest lines between neighboring grains.  We do
-not consider pores between eroding bodies and the solid and the
-artificial points placed around the porous region, so some of the grains
-near the porous region boundary only have two neighbors.
+not consider pores between eroding bodies and the solid wall $\Gamma$,
+so some of the grains near the porous region boundary only have two
+neighbors.
 

### 2019-09-26 docs/transport/erosion_transport.tex
edit in transport paper
working on section 6

@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap} (a): The distribution of the pore
+\caption{\label{fig:Eroding100gap} (a) The distribution of the pore
 sizes of an eroded geometry. The black curve is the Weibull distribution
-with the same first two moments as the data. (b): We only consider pore
+with the same first two moments as the data. (b) We only consider pore
 sizes between neighboring grains, where two grains are neighbors if they
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{here}
-In this section, we apply our new quadrature method to (1) simulate
-erosion of several different configurations of eroding bodies, and (2)
-characterize transport inside eroded geometries.  Each eroding body is
-initially a circle with center $\cc_i$ and radius $r_i$.  The center and
-radius are chosen at random, and the body is accepted as long as it is
-contained in $[-1,1] \times [-1,1]$ and is sufficiently separated from
-all other bodies.  Since the error of our quadrature method is bounded
-independent of the geometry, we consider bodies that are separated by
-less than 10\% of an arclength spacing.  The randomized method is
-repeated until the initial geometry reaches a desired initial porosity.
+In this section, we apply our new quadrature method to simulate
+erosion of several different configurations of nearly-touching eroding
+bodies, and to characterize transport inside eroded geometries.  Each
+eroding body is initially a circle with center $\cc_i$ and radius $r_i$.
+The center and radius are chosen at random, and the body is accepted as
+long as it is contained in $[-1,1] \times [-1,1]$ and is sufficiently
+separated from all other bodies.  Since the error of our quadrature
+method is bounded independent of the geometry, we consider bodies that
+are separated by less than 10\% of an arclength spacing.  The randomized
+method is repeated until the initial geometry reaches a desired initial
+porosity.
 
@@
 points.  For all but the first example, the Dirichlet boundary condition
-on $\Gamma$ is a hagen-poiseuille flow.  As the bodies erode, the flow
-rate is adjusted to maintain the physical constant pressure drop
-boundary condition.  To maintain this pressure drop, we compute the
-pressure at near the inlet and outlet at each time step as described in
-our previous work~\cite{qua-moo2018}.
-
-In each of the examples, we include plots of the vorticity in the fluid
-bulk.  Since the vorticity and the shear stress agree on surface of the
-eroding bodies, the vorticity is a useful method to visualize the
-erosion rate.  In particular, the rate of erosion is largest in regions
-where the magnitude of the vorticity is largest.
-
-Because of the definition of the erosion rate, there is a loss of
-regularity, and inevitably leads to corners developing on the
-eroding bodies.  Therefore, as described in
-Section~\ref{sec:formulation} and our previous work~\cite{qua-moo2018},
-we introduce a curvature penalization term and a Gaussian smoothing
-step.  For all examples, we use the smoothing parameters $\eps=15/256$
-and $\sigma=10/256$.
+on $\Gamma$ is a Hagen-Poiseuille flow, and the flow rate is adjusted at
+each time step to maintain a constant pressure drop. Since the fluid
+equations are linear, this is achieved by computing the pressure near
+the inlet and outlet at each time step, and then scaling the flow rate
+appropriately~\cite{qua-moo2018}.
+
+In each of the examples, we plot the vorticity in the fluid bulk.  Since
+the vorticity and the shear stress agree on surface of the eroding
+bodies, the vorticity is a useful method to visualize the erosion rate.
+In particular, the rate of erosion is largest in regions where the
+magnitude of the vorticity is largest.
+
+The erosion rate has a loss of regularity at stagnation points, and this
+inevitably leads to corners developing on the eroding bodies.
+Therefore, as described in Section~\ref{sec:formulation} and our
+previous work~\cite{qua-moo2018}, we introduce a curvature penalization
+term and a Gaussian smoothing step.  For all examples, we use the
+smoothing parameters $\eps=15/256$ and $\sigma=10/256$.
 
@@
   \item{\bf Single Body Close to a Wall}: We consider a single eroding
-  body close to the outer wall at $y=-1$.  Using a shear flow that
-  vanishes on $y=-1$, we compare the eroding body's shape to a similar
+  body close to the outer wall at $y=-1$.  We impose a shear flow
+  centered at $y=-1$, we compare the eroding body's shape to a similar
   experiment of Spagnolie and Mitchell~\cite{mit-spa2017}.
@@
   bodies with a medium porosity.  We compute the tortuosity, anomalous
-  dispersion rates, and the pore throat distributions.
+  dispersion rates, and the pore throat size distributions.
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider a single eroding body close to a solid wall.  To compare our
-results with a similar numerical experiment performed by Mitchell and
-Spagnolie~\cite{mit-spa2017}, rather than a pressure drop boundary
-condition, we impose the shear flow
+We consider a single eroding body close to a solid wall with the
+shear flow
 \begin{align}
@@
 \end{align}
-on the outer wall.  In their experiment, Mitchell and Spagnolie place
-the center of the eroding body $1.5$ times the body's radius above the
-solid wall.  By using the Barycentric quadrature rule described in
-Section~\ref{sec:bary} rather than the trapezoid rule, the eroding body
-can be placed much closer to the solid wall without requiring an
-unreasonable number of discretization points.  We consider an eroding
-body that is initially a circle of radius $r=0.4$.  We discretize the
-eroding body with $N_\iin=256$ discretization points, and its center is
-chosen so that the distance between the body and the solid wall is
-$h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  If we were to use
-the trapezoid rule and require an error that is comparable to the
-Barycentric quadrature rule, the body with an initial distance of $h/10$
-from the solid wall would require $6,400$ discretization points, and the
-outer wall would require $50,000$ discretization points.  For all three
-simulations, we use the time step size $\Delta t=10^{-4}$.
+imposed on the outer wall. Mitchell and Spagnolie~\mit{spa-spa2017} did
+a similar three-dimensional experiment using a second-order quadrature
+method. Here, they initialized the eroding body so that its center $1.5$
+times the body's radius above the solid wall.  In two dimensions, the
+trapezoid rule is spectrally accurate, and an analogous initial
+configuration is possible. However, unless the number of discretization
+points is increased, the trapezoid rule becomes obsolete if the eroding
+body is initialized closer to the solid wall. Therefore, to simulate
+erosion near a solid wall at reasonable levels of discretization, we use
+our hybrid method that combines the trapezoid rule and the Barycentric
+quadrature rule.
+
+We consider an eroding body that is initially a circle of radius
+$r=0.4$.  We discretize the eroding body with $N_\iin=256$
+discretization points, and its center is chosen so that the distance
+between the body and the solid wall is $h/2$, $h/4$, and $h/10$, where
+$h = 2\pi r/N_\iin$.  If we used the trapezoid rule and required an
+error that is comparable to the Barycentric quadrature rule, the body
+with an initial distance of $h/10$ from the solid wall would require
+$6,400$ discretization points, and the outer wall would require $50,000$
+discretization points.  For all three simulations, we use the time step
+size $\Delta t=10^{-4}$.
 
@@
 logarithm of the shear stress.  Since the shear stress is always
-positive, the erosion rate is smooth and corners do not develop.
-However, the shear stress varies over several orders of magnitude, and
-this leads to interesting shapes.  For instance, in the top half of the
-body, there is a sudden increase in the shear stress, and this leads to
-a region of high curvature.  This behavior is also present in three
+positive, the erosion rate is smooth and corners do not develop, but
+interesting shapes form nonetheless.  For instance, in the top half of
+the body, there is a sudden increase in the shear stress, and this leads
+to a region of high curvature.  This behavior is also present in three
 dimensions~\cite{mit-spa2017} (Figure 7(c)).  The biggest difference
@@
 recirculation zone.  In three dimensions, there is no recirculation
-between the solid wall and the spherical body~\cite{cha-feu2003}.  In
-contrast, the two-dimensional flow Stokes flow can have recirculation
-zones~\cite{chw-wu1975, hig1985}. To visualize the flow, we plot the
-vorticity of the final time step from Figure~\ref{fig:NearWall} in
-Figure~\ref{fig:NearWall_vort}.  The recirculation is present in the
-region where the vorticity is smallest.
+between the solid wall and the spherical body~\cite{cha-feu2003}, but
+this is possible in two dimensions~\cite{chw-wu1975, hig1985}. To
+visualize the flow, we plot the vorticity of the final time step from
+Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  The
+recirculation is present in the region where the vorticity is smallest,
+but its size is very small.
 
@@
 (lower half).  The body is initialized at three different distances from
-the lower wall: (a) $d=h$, (b) $h/2$, and (c) $h/10$.}
+the lower wall: (a) $h$, (b) $h/2$, and (c) $h/10$.}
 \end{center}
@@
 times are shown in Figure~\ref{fig:Eroding20vort}.  The color is the
-vorticity which is equivalent to the shear stress when restricted to the
-eroding bodies.  Therefore, the rate of erosion is fastest in regions
-where the magnitude of the vorticity is largest.  Initially, several of
-the eroding bodies are closer to the outer wall than the $5h$ threshold
-required to guarantee that the trapezoid rule achieves machine
-precision.  In particular, with $h=L_2/N_\out$, the distance between
-bodies 1, 6, 13, and 15 and the outer wall are $1.3h$, $2.9h$, $2.8h$,
-and $1.3h$, respectively.  In addition, the distance between several
-pairs of eroding bodies is too small to be accurately resolved with the
-trapezoid rule at the prescribed resolution.  Particular pairs include
-bodies 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18.  By using the Barycentric
-quadrature rule, the interaction between these nearly-touching bodies
-can be accurately resolved at the prescribed resolution, and erosion can
-be simulated until all the bodies have vanished.
+vorticity, and the erosion rate is proportional to the vorticity.
+Initially, several of the eroding bodies are closer to the outer wall
+than the $5h$ threshold required to guarantee that the trapezoid rule
+achieves machine precision.  In particular, the distance between bodies
+1, 6, 13, and 15 and the outer wall is $1.3h$, $2.9h$, $2.8h$, and
+$1.3h$, respectively, where $h$ is the arclength spacing of the outer
+wall $\Gamma$.  In addition, the distance between several pairs of
+eroding bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and 14\& 18, is too
+small to be accurately resolved with the trapezoid rule.  By using the
+Barycentric quadrature rule, the interaction between these
+nearly-touching bodies can be accurately resolved at the prescribed
+resolution, and erosion can be simulated until all the bodies have
+vanished.
 
@@
   \includegraphics[height=0.225\textwidth]{./figs/20b_dense301}
-\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
-with the fixed pressure drop condition. The color is the vorticity of
-the fluid. The four snapshots are evenly spaced in time. We use $N_\iin
-= 256$ discretization points on the bodies.  In the fourth frame, bodies
-4, 12, and 17 have vanished completely, and body 19 has almost
-completely eroded.}
+\caption{\label{fig:Eroding20vort} The erosion of 20 nearly touching
+bodies, each discretized with $N_\iin=256$ points, in a Hagen-Poiseuille
+flow.  The four snapshots are evenly spaced in time, and the color is
+the fluid vorticity. In the fourth frame, bodies 4, 12, and 17 have
+vanished completely, and body 19 has almost completely eroded.}
 \end{center}
@@
 
-We observe that erosion creates a network of channels from the inlet to
-outlet where the velocity and vorticity, and therefore erosion rate, are
-much larger when compared to other regions.  These channels can be
-further visualized by considering the streamlines.  In
-Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
-time step from Figure~\ref{fig:Eroding20vort}, and we plot 200
-streamlines that are initialized at $x=-1$ and equispaced in $y$.  The
-streamlines are shown at five different times, and the final plot is a
-zoom in of the lower right quadrant of the fifth time step.  Since we
-use a high-order quadrature rule and a high-order time stepping method,
-we resolve streamlines that come very close to the eroded bodies.  There
-are three clear regions where the streamlines are concentrated, and this
-corresponds to regions of high velocity.  Two of these regions are
-located between the bodies and the solid walls at $y=\pm 1$, and the
-third cuts through the porous region with the upper part of the channel
-formed by bodies 1, 4, 6, and 8.  Since the flow is fastest in these
-regions, the shearing is largest, and this causes these openings to grow
-fastest which can be observed in Figure~\ref{fig:Eroding20vort}.
-
 Similar to our previous work, erosion causes the space between nearly
 touching bodies to quickly expand, and flat faces develop along the
-region of near contact.  This qualitative behavior is present in
+regions of near contact.  This qualitative behavior is present in
 Figure~\ref{fig:Eroding20vort} between bodies 3 \& 4, 15 \& 16, and
-others.  However, by resolving the interaction betweeen bodies that are
+others.  However, by resolving the interaction between bodies that are
 much closer together than in our previous work, we observe that, at
@@
 \& 13 grow much slower than the opening between bodies 15 \& 16.  A
-common feature of the openings that grow slowly is that they are nearly
+common feature of the pores that grow slowly is that they are nearly
 perpendicular to the main flow direction, and this results in a small
-velocity, and hence a slow erosion rate.  In fact, when plotting the
-streamlines, only a small fraction of the plotted streamlines pass
-between theese pairs of bodies indicating a very small velocity.
-
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
-\caption{\label{fig:Eroding20tracer} 200 streamlines in the second
-geometry from Figure~\ref{fig:Eroding20vort}. The streamlines are
-initialized at $x=-1$ and are equally spaced in the $y$-direction. The
-first five snapshots are evenly spaced in time.  The bottom right frame
-is a zoom in of the fifth snapshot.  Since we use the Barycentric
-quadrature rule and the fourth-order Runge-Kutta method, the streamlines
-can be very close to but not unphysically penetrate the bodies.}
-\end{center}
-\end{figure}
-
-Next, we use the streamlines to compute the local tortuosity and the
-anomalous dispersion rate of eroding geometries.  Since these
-calculations are statistical, we use $N_p = 1000$
-streamlines~\cite{bel-sal-rin1992}.  To compute the tortuosity, we
-require the velocity at the start of the streamlines.  These normalized
-velocities are plotted in Figure~\ref{fig:Eroding20tort}(a) for the
-eroded geometry with porosity 62.9\% (see
-Figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
-work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure 4(a)), except
-that our cross-section, by construction, does not cut through any of the
-bodies.  Next, in Figure~\ref{fig:Eroding20tort}(b), we plot the local
-tortuosity~\eqref{eqn:localTort} by calculating the relative length of
-each streamline as it traverses the channel from $x=-1$ to $x=1$.  The
-local tortuosity ranges from 1 to 1.27, meaning that one of the
-streamlines is 27\% longer than it would have been if the bodies were
-absent.  The average streamline length is 9.79\% longer than if the
-bodies had been absent, so the tortuosity of the eroded channel is
-$1.098$.  Again, comparing the local tortuosity to
-Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
-qualitatively similar. However, since our initial cross-section does not
-cut through any bodies, the local tortuosity does not have any gaps.
-The discontinuities in the local tortuosity happens neighboring
-streamlines diverge on opposite sides of a body.  In
-Figure~\ref{fig:Eroding20tort}(c), we plot pairs of streamline that
-correspond to the ten largest jumps in the local tortuosity.
-Corresponding pairs are plotted in the same color.
-
-\begin{figure}[H]
-\begin{subfigure}[b]{0.45\textwidth}
-\begin{subfigure}[b]{\textwidth}
-\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-\includegraphics*[width =0.97\linewidth]{./figs/tort_local20_268}
-\caption{}
-\end{subfigure}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding20tort} The tortuosity of an eroded geometry
-with porosity 62.9\%. (a) The $x$-component of the velocity, $u(-1,y)$,
-normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
-local tortuosity $\tau(y)$ along the cross section $x = -1$.  The
-spatially averaged tortuosity through the channel is $1.098$.  (c) The
-streamlines resulting in the ten largest differences between neighboring
-streamlines.  Neighboring streamlines have the same color.}
-\end{figure}
-
-In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
-function of the porosity. The initial porosity is $\phi = 37.68\%$, and
-the initial tortuosity is $1.16$.  The tortuosity is computed with both
-the length of the streamlines~\eqref{eqn:tortuosity1} (red marks) and
-using the spatial average of the velocity on an Eulerian
-grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
-to the porosity of the geometry in Figure~\ref{fig:Eroding20tort}(c).
-The two tortuosity formulas give similar results, and any discrepancy
-can be accounted for by slow regions of recirculation and quadrature
-error induced by the integrals in the tortuosity definitions.  As the
-bodies erode, this creates wide channels where streamlines undergo only
-minor vertical deflections, and this explains why the tortuosity
-eventually decreases with porosity.  We computed lines of best fit using
-the porosity-tortuosity models~\eqref{eqn:tortuosityModels}, and the
-power law model gave the smallest error.  The  black dashed line in
-Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
-\begin{align}
-  \widehat{T}(\phi) = \phi^{-0.2064}
-\end{align}
-with a root-mean-square error of $5.90 \times 10^{-3}$.  The initial
-increase in tortuosity occurs because in the absence of erosion (left
-plot in Figure~\ref{fig:Eroding20vort}), many of the streamlines, such
-as those initialized between bodies 15 \& 18, only perform minor
-deflections to pass through the narrow regions, albeit, very slowly.
-However, as erosion starts to open the channels, the streamlines deflect
-into the fast regions, such as the region above body 11, and this
-increases the amount of vertical deflection, and therefore the
-tortuosity.
-
-In Figure~\ref{fig:Eroding20Transport}(b), we plot the temporal
-evolution of the particle spreading $\sigma_\lambda$.  The spreading is
-computed at several geometries that are formed during the erosion
-process.  So that the spreading reaches a statistical equilibrium, we
-use the reinsertion algorithm described in Section~\ref{sec:dispersion}
-to form sufficiently long trajectories.  For all the reported
-porosities, the particle dispersion exhibits two power low regimes.
-Initially, the dispersion is ballistic ($\sigma_\lambda \sim t$) since
-individual fluid particles have not yet explored enough space to
-significantly alter their velocity.  However, once the particles have
-been subjected to a range of velocities, their dispersion slows down,
-and we observe super-diffusive ($\sigma_\lambda \sim t^\alpha$, $\alpha
-\in (1/2,1)$) behavior over at least one order of magnitude in time.
-Before any erosion takes place, the anomalous dispersion coefficient is
-$\alpha = 0.56$.  Then, as the bodies begin to erode, the dispersion
-rate grows towards the ballistic regime that corresponds to the absence
-of bodies.  The monotonic increase in dispersion with respect to the
-porosity is explained by the onset of channels where many tracers
-experience less variability in their velocities.  For this example, the
-dispersion is nearly Fickean at the smallest porosity.
-
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/20b_second_moment_long_ref}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding20Transport} (a): The tortuosity of an
-eroding geometry initialized with 20 bodies.  The tortuosity is
-calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
-and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
-square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
-The dash line is the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with
-$p=0.2064$, and the corresponding root-mean-square error is $5.90 \times
-10^{-3}$. (b): The temporal evolution of $\sigma_\lambda$ as a function
-of time at seven different porosities.  The dashed line, which has slope
-one, corresponds to the ballistic dispersion $\sigma_\lambda \sim t$ if
-no bodies were present. At early times, the particles undergo a
-ballistic motion, but once they have traversed a few grains, the
-dispersion becomes super-dispersive with $\sigma_\lambda \sim t^\alpha$,
-$\alpha \in (1/2,1)$.  The dashed-dotted lines are lines of best fit
-with slopes $\alpha = 1.06$ ($\phi=95.10\%$), $\alpha = 1.07$
-($\phi=85.09\%$), $\alpha = 1.06$ ($\phi=75.15\%$), $\alpha = 0.97$
-($\phi=65.09\%$), $\alpha = 0.78$ ($\phi=55.10\%$), $\alpha = 0.75$
-($\phi=45.08\%$), and $\alpha = 0.56$ ($\phi=37.68\%$).  Values greater
-than 1 are a result of using a least-squares fit for the tails of the
-particle spreading.}
-\end{figure}
-
-Finally, following our previous work~\cite{qua-moo2018}, we analyze the
-effect of erosion on the area fraction and the flow rate.  In
+erosion rate.
+
+Following our previous work~\cite{qua-moo2018}, we begin by analyzing
+the effect of erosion on the area fraction and the flow rate.  In
 Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
-nearly touching eroding bodies versus normalized time. (b): The flow
+\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20
+nearly touching eroding bodies versus normalized time. (b) The flow
 rate, $U$, for a fixed pressure drop across the channel versus
@@
 
+In Figure~\ref{fig:Eroding20vort}, we observe that erosion creates a
+network of channels from the inlet to outlet where the velocity and
+vorticity, and therefore erosion rate, are much larger than other
+regions.  These channels can be further visualized by considering the
+streamlines.  In Figure~\ref{fig:Eroding20tracer}, we freeze the
+geometry at the second snapshot from Figure~\ref{fig:Eroding20vort}, and
+we plot 200 streamlines that are initialized at $x=-1$ and equally
+spaced in $y \in (-1,1)$.  The streamlines are shown at five different
+times, and the final plot is a zoom in of the lower right quadrant of
+the fifth time step.  Since we use a high-order quadrature rule and time
+stepping method, we resolve streamlines that come very close to the
+eroded bodies.  There are three clear regions where the streamlines are
+concentrated, and this corresponds to regions of high velocity.  Two of
+these regions are located between the bodies and the solid walls at
+$y=\pm 1$, and the third cuts through the porous region with the upper
+part of the channel formed by bodies 1, 4, 6, and 8.  Since the flow is
+fastest in these regions, the shearing is largest, and this causes the
+channels to continue to open fastest which can be observed in
+Figure~\ref{fig:Eroding20vort}.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
+\caption{\label{fig:Eroding20tracer} 200 streamlines in the second
+geometry from Figure~\ref{fig:Eroding20vort}. The streamlines are
+initialized at $x=-1$ and are equally spaced in $y \in (-1,1)$. The
+first five snapshots are evenly spaced in time.  The bottom right frame
+is a zoom in of the fifth snapshot.  Since we use the Barycentric
+quadrature rule and the fourth-order Runge-Kutta method, some
+streamlines are very close to the grains without penetrating them.}
+\end{center}
+\end{figure}
+
+Next, we use the streamlines to compute the local tortuosity and the
+anomalous dispersion rate of eroding geometries.  To achieve statistical
+convergence, we use $N_p = 1000$ streamlines~\cite{bel-sal-rin1992}. To
+compute the tortuosity, we require the velocity at the inlet $x=-1$.
+These normalized velocities are plotted in
+Figure~\ref{fig:Eroding20tort}(a) for the eroded geometry with porosity
+62.9\% (see Figure~\ref{fig:Eroding20tort}(c)).  The velocities are
+similar to the work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure
+4(a)), except that our cross-section, by construction, does not cut
+through any of the grains.  Next, in Figure~\ref{fig:Eroding20tort}(b),
+we plot the local tortuosity~\eqref{eqn:localTort} by calculating the
+relative length of each streamline as it traverses the channel from
+$x=-1$ to $x=1$.  The local tortuosity ranges from 1 to 1.27, meaning
+that one of the streamlines is 27\% longer than it would have been if
+the grains were absent.  The average streamline length is 9.79\% longer
+than if the grains had been absent, so the tortuosity of the eroded
+channel is $1.098$.  Again, comparing the local tortuosity to
+Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
+qualitatively similar. However, since our initial cross-section does not
+cut through the grains, the local tortuosity does not have any gaps.
+The discontinuities in the local tortuosity happens when nearby
+streamlines diverge on opposite sides of a grain.  In
+Figure~\ref{fig:Eroding20tort}(c), we plot the pairs of streamlines that
+correspond to the ten largest jumps in the local tortuosity.
+Corresponding pairs are plotted in the same color.
+
+\begin{figure}[H]
+\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{\textwidth}
+\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
+\includegraphics*[width =0.97\linewidth]{./figs/tort_local20_268}
+\caption{}
+\end{subfigure}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20tort} The tortuosity of a porous geometry
+that initially had 20 grains and has eroded to a porosity of 62.9\%.
+(a) The $x$-component of the velocity at the inlet, $u_1(-1,y)$,
+normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
+local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
+averaged tortuosity through the channel is $1.098$.  (c) The streamlines
+resulting in the ten largest differences between neighboring
+streamlines.  Neighboring streamlines have the same color.}
+\end{figure}
+
+In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
+function of the porosity. The initial porosity is $\phi = 37.68\%$, and
+the initial tortuosity is $T = 1.16$.  The tortuosity is computed with both
+the length of the streamlines~\eqref{eqn:tortuosity1} (red stars) and
+using the spatial average of the velocity on an Eulerian
+grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
+to the porosity of the geometry in Figure~\ref{fig:Eroding20tort}(c).
+The two tortuosity formulas give similar results, and any discrepancy
+can be accounted for by slow regions of recirculation and from applying
+quadrature to compute the tortuosity.  As the bodies erode, wide
+channels form where streamlines undergo only minor vertical deflections,
+and this explains why the tortuosity eventually decreases with porosity.
+We computed lines of best fit using the porosity-tortuosity
+models~\eqref{eqn:tortuosityModels}, and the power law model gave the
+smallest error.  The  black dashed line in
+Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
+\begin{align}
+  \widehat{T}(\phi) = \phi^{-0.2064}
+\end{align}
+with a root-mean-square error of $5.90 \times 10^{-3}$.  Interestingly,
+at the low porosities, the tortuosity initially increases. This increase
+occurs because in the absence of erosion (left plot in
+Figure~\ref{fig:Eroding20vort}), many of the streamlines, such as those
+initialized between bodies 15 \& 18, only perform minor deflections to
+pass through the narrow regions, albeit, very slowly.  However, as
+erosion starts to open the channels, the streamlines deflect into the
+fast regions, such as the region above body 11, and this increases the
+amount of vertical deflection, and therefore the tortuosity.
+
+In Figure~\ref{fig:Eroding20Transport}(b), we plot the temporal
+evolution of the particle spreading $\sigma_\lambda$.  The spreading is
+computed at seven geometries of different porosities that are formed
+during the erosion process.  So that the spreading reaches a statistical
+equilibrium, we use the reinsertion algorithm described in
+Section~\ref{sec:dispersion} to form sufficiently long trajectories.
+For all the reported porosities, the particle dispersion exhibits two
+power low regimes.  Initially, the dispersion is ballistic
+($\sigma_\lambda \sim t$) since individual fluid particles have not yet
+explored enough space to significantly alter their velocity.  However,
+once the particles have been subjected to a range of velocities, their
+dispersion slows down, and we observe super-dispersive ($\sigma_\lambda
+\sim t^\alpha$, $\alpha \in (1/2,1)$) behavior over at least one order
+of magnitude in time.  Before any erosion takes place, the anomalous
+dispersion coefficient is $\alpha = 0.56$.  Then, as the grains begin to
+erode, the dispersion rate grows towards the ballistic regime that
+occurs in the absence of grains.  The monotonic increase in dispersion
+with respect to the porosity is explained by the onset of channels where
+many tracers experience less variability in their velocities.
+
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/20b_second_moment_long_ref}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20Transport} (a) The tortuosity of an eroding
+geometry initialized with 20 grains.  The tortuosity is calculated using
+the Eulerian method~\eqref{eqn:tortuosity2} (blue dots) and Lagrangian
+method~\eqref{eqn:tortuosity1} (red stars).  The red square corresponds
+to the geometry in Figure~\ref{fig:Eroding20tort}(c).  The dash line is
+the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2064$, and
+the corresponding root-mean-square error is $5.90 \times 10^{-3}$. (b)
+The temporal evolution of $\sigma_\lambda$ as a function of time at
+seven different porosities.  The dashed line, which has slope one,
+corresponds to ballistic dispersion $\sigma_\lambda \sim t$ that occurs
+if no grains are present. At early times, the particles undergo a
+ballistic motion, but once they have traversed a few grains, the
+spreading becomes super-dispersive with $\sigma_\lambda \sim t^\alpha$,
+$\alpha \in (1/2,1)$.  The dashed-dotted lines are lines of best fit
+with slopes $\alpha = 1.06$ ($\phi=95.10\%$), $\alpha = 1.07$
+($\phi=85.09\%$), $\alpha = 1.06$ ($\phi=75.15\%$), $\alpha = 0.97$
+($\phi=65.09\%$), $\alpha = 0.78$ ($\phi=55.10\%$), $\alpha = 0.75$
+($\phi=45.08\%$), and $\alpha = 0.56$ ($\phi=37.68\%$).  Values greater
+than 1 are a result of using a least-squares fit for the tails of the
+particle spreading.}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
-eroding geometry and porosity at four evenly spaced instances in time.
-Again, the color is the vorticity in the bulk whose magnitude is
-equivalent to the erosion rate.   Initially, the smallest distance
-between pairs of bodies is $3.29 \times 10^{-4}$, and the smallest
-distance between the bodies and solid wall is $4.50 \times 10^{-3}$.  At
-these distances, a resolution of approximately $N_\iin = 27,000$ and
-$N_\out = 18,000$ discretization points is required to satisfy the $5h$
-rule of thumb for the trapezoid rule to achieve machine epsilon
-accuracy.  By applying the Barycentric quadrature rule, we stably
-simulate erosion at the much coarser resolution of $N_\iin = 256$ and
-$N_\out = 1024$ discretization points.
+eroding geometry and vorticity at four evenly spaced instances in time.
+Initially, the smallest distance between pairs of bodies is $3.29 \times
+10^{-4}$, and the smallest distance between the bodies and solid wall is
+$4.50 \times 10^{-3}$.  At these distances, a resolution of
+approximately $N_\iin = 27,000$ and $N_\out = 18,000$ discretization
+points is required to satisfy the $5h$ threshold required to guarantee
+that the trapezoid rule achieves machine precision.  By applying the
+Barycentric quadrature rule, we stably simulate erosion at the much
+coarser resolution of $N_\iin = 256$ and $N_\out = 1024$ discretization
+points.
 
@@
 \end{center}
-\caption{\label{fig:ErodingLow20vort} Erosion of 20 nearly touching
-bodies with the fixed pressure drop condition. The color is the
-vorticity of the fluid. The 4 snapshots are evenly spaced in time. We
-use $N_\iin = 256$ discretization points on the bodies.  In
-addition to the channels that develop between the bodies and the solid
-walls, Erosion leads to two main channels through the geometry---one in
-the top half and one near the middle.}
+\caption{\label{fig:ErodingLow20vort} The erosion of 20 nearly touching
+bodies, each discretized with $N_\iin = 256$ points, in a
+Hagen-Poiseuille flow. The 4 snapshots are evenly spaced in time, and
+the color is the fluid vorticity. In addition to the channels that
+develop between the bodies and the solid walls, erosion leads to two
+main channels through the geometry---one in the top half and one near
+the middle.}
 \end{figure}
 
-We compute the tortuosity using the Eulerian
+To avoid computing streamlines at every time step during the erosion
+process, we compute the tortuosity using the Eulerian
 method~\eqref{eqn:tortuosity2}.  The initial porosity is $30.67\%$ and
-the initial tortuosity is $1.24$.  In
+the initial tortuosity is $T = 1.24$.  In
 Figure~\ref{fig:ErodingLow20Transport}(a), we plot the tortuosity with
@@
 This model outperformed the other three models in
-equation~\eqref{eqn:tortuosityModels} that were proposed by Matyka et
-al.~\cite{mat-kha-koz2008}.  The root-mean-squared error of the power
-law is $1.13 \times 10^{-2}$.  As the bodies erode, the number of
-streamlines that take a direct path through the geometry increases,
-and this decreases the tortuosity.  However, there is also an increase
-in the number of streamlines that increase their length since they
-deflect their trajectory to move from a low porosity region (high
-pressure) to a high porosity region (low pressure), and this decreases
-the tortuosity. For this example, we see that the net effect is a
-decrease in the tortuosity for all time.
+equation~\eqref{eqn:tortuosityModels}, and its root-mean-squared error
+is $1.13 \times 10^{-2}$.  As grains erode, there is an increase in the
+number of streamlines that take a nearly direct pact through the
+geometry, and this decreases the tortuosity. However, the channelization
+effect of erosion results in an increase in the tortuosity since the
+length of many of the streamlines increases when they deflect from a
+high porosity region (low pressure) to a low porosity region (high
+pressure). For this example, we see that the net effect is a decrease in
+the tortuosity for all time.
 
@@
 Figure~\ref{fig:Eroding20Transport}.  However, there are still clear
-transitions from ballistic dynamics to asymptotic super-diffusive
-dynamics.  In contrast to the lower porosity initial condition
+transitions from ballistic dynamics to asymptotic super-dispersive
+spreading.  In contrast to the lower porosity initial condition
 (Section~\ref{sec:Eroding20}), at early times the erosion results in a
-decrease in dispersion rate. In particular, once erosion has eroded the
-first 5\% of the bodies, the particle spreading transitions from
+decrease in the dispersion rate. In particular, once erosion has eroded
+the first 5\% of the bodies, the particle spreading transitions from
 $\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim t^{0.69}$.  To
@@
 \end{subfigure}
-\caption{\label{fig:ErodingLow20Transport} (a): The tortuosity of an
-eroding geometry initialized with 20 bodies.  When compared to the last
+\caption{\label{fig:ErodingLow20Transport} (a) The tortuosity of an
+eroding geometry initialized with 20 grains.  When compared to the last
 example, the bodies are initially much closer together, and the porosity
-is smaller.  The tortuosity is calculated using the Eulerian
+is smaller.  The tortuosity is calculated with the Eulerian
 method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
 fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.1669$, and the root
-mean square deviation is $1.13 \times 10^{-2}$.  (b): The temporal
+mean square deviation is $1.13 \times 10^{-2}$.  (b) The temporal
 evolution of $\sigma_\lambda$ as a function of time at eight different
-porosities.  The dashed line, which has slope one, corresponds to the
-ballistic dispersion $\sigma_\lambda \sim t$ if no bodies were present.
-At early times, the particles undergo a ballistic motion, but once they
-have traversed a few grains, the dispersion becomes super-dispersive
-with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
-dashed-dotted lines are lines of best fit with slope $0.92$
-($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$), $0.87$ ($\phi=75.10\%$),
-$0.91$ ($\phi=65.02\%$), $0.91$ ($\phi=55.08\%$), $0.72$
-($\phi=45.03\%$), $0.69$ ($\phi=35.05\%$), and $0.92$ ($\phi=30.67\%$).}
+porosities.  The dashed line, which has slope one, corresponds to
+ballistic dispersion $\sigma_\lambda \sim t$ that occurs if no grains
+are present.  At early times, the particles undergo a ballistic motion,
+but once they have traversed a few grains, the spreading becomes
+super-dispersive with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in
+(1/2,1)$.  The dashed-dotted lines are lines of best fit with slope
+$0.92$ ($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$), $0.87$
+($\phi=75.10\%$), $0.91$ ($\phi=65.02\%$), $0.91$ ($\phi=55.08\%$),
+$0.72$ ($\phi=45.03\%$), $0.69$ ($\phi=35.05\%$), and $0.92$
+($\phi=30.67\%$).}
 \end{figure}
 
+\todo[inline]{HERE}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid
-with 100 bodies when the porosity is 62.98\%.  (a) The x-component
-velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.90
-\times 10^{-4}$ at equal spreading tracers on the cross section x = -1.
-(b) The local tortuosity $\tau(y)$ on the cross section x = -1. (c) The
-trajectories of 200 tracers released at $x = -1$ in the fluid with
-multiple bodies.  The discontinuities in the local tortuosity correspond
-to neighboring streamlines whose lengths are significantly different
-because they pass opposite sides of an eroding body.}
+\caption{\label{fig:Eroding100tort} The tortuosity of a porous geometry
+that initially had 100 grains and has eroded to a porosity of 63.0\%.
+(a) The $x$-component of the velocity at the inlet, $u_1(-1, y)$,
+normalized by its maximum velocity $u_{max}=3.90 \times 10^{-4}$.  (b)
+The local tortuosity $\tau(y)$ on the cross section $x = -1$. The
+spatially averaged tortuosity through the channel is $1.12$. (c) The
+trajectories of 200 tracers initialized at $x = -1$.  The
+discontinuities in the local tortuosity correspond to nearby streamlines
+whose lengths are significantly different because they pass opposite
+sides of an eroding body. Compared to Figure~\ref{fig:Eroding20tort},
+this example has more small bodies, and this results in many more
+discontinuities.}
 \end{figure}
@@
 with both the length of the streamlines~\eqref{eqn:tortuosity1} (red
-marks) and using the spatial average of the velocity on an Eulerian
+stars) and using the spatial average of the velocity on an Eulerian
 grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100Transport} (a): The tortuosity of an
-eroding geometry initialized with 100 bodies.  The tortuosity is
-calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
-dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
-with $p=0.2459$, and the root mean square deviation is $5.50 \times
-10^{-3}$.  We note that the model $\widehat{T}(\phi) = 1 - p \ln
-(\phi)$, with $p=0.2631$ has a comparable root-mean-square error of
-$5.20 \times 10^{-3}$.  (b): The temporal evolution of $\sigma_\lambda$
-as a function of time at six different porosities.  The dashed line,
-which has slope one, corresponds to the ballistic dispersion
-$\sigma_\lambda \sim t$ if no bodies were present.  At early times, the
-particles undergo a ballistic motion, but once they have traversed a few
-grains, the dispersion becomes super-dispersive with $\sigma_\lambda
-\sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The dashed-dotted lines are
-lines of best fit with slope $1.11$ ($\phi=95.12\%$), $0.68$
-($\phi=85.07\%$), $0.73$ ($\phi=75.14\%$), $0.59$ ($\phi=65.03\%$),
-$0.61$ ($\phi=55.02\%$), and $0.70$ ($\phi=50.09\%$).}
+\caption{\label{fig:Eroding100Transport} (a) The tortuosity of an
+eroding geometry initialized with 100 grains.  The tortuosity is
+calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
+and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The dash
+line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2459$,
+and the root mean square deviation is $5.50 \times 10^{-3}$.  We note
+that the model $\widehat{T}(\phi) = 1 - p \ln (\phi)$, with $p=0.2631$,
+has a comparable root-mean-square error of $5.20 \times 10^{-3}$.  (b)
+The temporal evolution of $\sigma_\lambda$ as a function of time at six
+different porosities.  The dashed line, which has slope one, corresponds
+to ballistic dispersion $\sigma_\lambda \sim t$ that occurs if no bodies
+are present.  At early times, the particles undergo a ballistic motion,
+but once they have traversed a few grains, the spreading becomes
+super-dispersive with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in
+(1/2,1)$.  The dashed-dotted lines are lines of best fit with slope
+$1.11$ ($\phi=95.12\%$), $0.68$ ($\phi=85.07\%$), $0.73$
+($\phi=75.14\%$), $0.59$ ($\phi=65.03\%$), $0.61$ ($\phi=55.02\%$), and
+$0.70$ ($\phi=50.09\%$).}
 \end{figure}

### 2019-09-26 docs/transport/erosion_transport.tex
worked through rest of paper and Nick's comments

@@
 \begin{abstract} 
-  We extend our previous work, [Journal of Computational Physics, {\bf
-  375}:1--21, 2018], to simulate dense suspensions of fluid-mechanical
-  erosion of two-dimensional erosion of porous media. By using a
-  Barycentric quadrature rule, we resolve interactions
-  between nearly touching bodies without requiring an unfeasible number
-  of discretization points.  Since the Barycentric quadrature rule is
-  computationally expensive, it is only used when necessary, and the
-  spectrally accurate trapezoid rule is used otherwise. Our final fluid
-  solver only requires $\mathcal{O}(N)$ iterations per time step. Next,
-  we simulate and analyze transport through eroded porous geometries.
-  Our results demonstrate the effects of erosion on tortuosity,
-  dispersion, and pore size distributions.
+  We extend upon our previous work, [Journal of Computational Physics,
+  {\bf 375}:1--21, 2018], to simulate dense suspensions of
+  fluid-mechanical erosion of two-dimensional erosion of porous media.
+  The method combines a boundary integral equation (BIE) fluid solver
+  and a numerically stable time stepping method for the evolution of the
+  eroding bodies. Originally, the eroding bodies had to be sufficiently
+  separated to guarantee that the trapezoid rule provided a sufficient
+  level of accuracy. In this work, we develop resolve interactions
+  between nearly touching bodies with a Barycentric quadrature rule
+  whose error is independent of the geometry.  Since the Barycentric
+  quadrature rule is computationally expensive, it is only used when
+  necessary, and the spectrally accurate trapezoid rule is used
+  otherwise. Our final fluid solver only requires $\mathcal{O}(N)$
+  iterations per time step. Next, we simulate and analyze transport
+  through eroded porous geometries.  Our results demonstrate the effects
+  of erosion on tortuosity, dispersion, and pore size distributions.
 \end{abstract}
@@
 can vary from $10^{-6}\mathrm{m}$ to
-$10^{-1}\mathrm{m}$~\cite{mil-chr-imh-mcb-ped1998}, velocity scales can
-be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}, \awk{and
-the scales of a single porous media can range over several orders of
-magnitude.}
-%
-\todo[inline]{Nick: I am confused by the last part of the sentence (highlighted in purple).
-What `scale' are you referring to?
-Length?
-You already described the length scales in the first part of the sentence.
-Maybe you mean to distinguish between the grain length scales and the overall length scales of the system.
-If so, you can use adjectives like `grain' and `macroscopic' or `overall' to clarify that.}
-%
-Numerical methods that \st{accurately address all of these} \nick{resolve this range of} scales offer the ability to: (i) characterize dispersion~\cite{saf1959}, (ii) quantify mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}, and (iii) potentially develop meaningful constitutive relationships that link the microscopic and macroscopic realms~\cite{mil-chr-imh-mcb-ped1998}.
-%
-\todo[inline]{Nick: I reworded the above sentence. See if you agree with my changes.}
-%
-Examples of coarse-grained models for porous media flow include
-pressure-saturation-permeability
+$10^{-1}\mathrm{m}$~\cite{mil-chr-imh-mcb-ped1998} and velocity scales
+can be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}.
+Moreover, for a single porous geometry, the pore sizes and velocities
+can range over several orders of magnitude.  Numerical methods that
+resolve this range of scales offer the ability to: (i) characterize
+dispersion~\cite{saf1959}, (ii) quantify
+mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}, and
+(iii) potentially develop meaningful constitutive relationships that
+link the microscopic and macroscopic
+realms~\cite{mil-chr-imh-mcb-ped1998}.  Examples of coarse-grained
+models for porous media flow include pressure-saturation-permeability
 relationships~\cite{mil-chr-imh-mcb-ped1998}, permeability-porosity
@@
 coupling between the flow and the geometry. For example, the grains of a
-porous media evolve in time in applications involving melting~\cite{bec-vis1998, rycroft2016asymmetric, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moore2017riemann, wykes2018self}, deposition~\cite{joh-eli1995, hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and \nick{crack formation} \cite{cho2019crack}.
-%
-\todo[inline]{Nick: I added some references.
-Check out the last one on crack formation in shrinkable, granular packings.
-It is really cool work done by an excellent experimentalist Sujit Datta.
-I met him and he voiced a strong interest in our work, so wanted to make you aware.}
-%
-We focus on erosion, a fluid-mechanical
-process that is prevalent in many geophysical, hydrological, \nick{and industrial} 
-applications \cite{berhanu2012shape, hewett2017evolution, lopez2018cfd, allen2019sde, amin2019role}.
-\todo[inline]{Nick: Check out the first reference, Berhanu, Kudrolli, Rothman PRE 2012.
-Maybe we can cite it a couple more times throughout since it has both the words `erosion' and `granular bed' in the title :)}
-When a porous geometry erodes, certain qualitative characteristics are unveiled that affect transport through the geometry.
-For example, an eroded geometry may contain channels of high porosity, \nick{which, though few in number and modest in volume fraction, transmit a large portion of the flux}.
-This arrangement results in velocities
-that vary over several orders of magnitude~\cite{all-hea-lab-rei2002}.
-%
-\todo[inline]{Nick: I rearranged the above two sentences. See if you like it.}
-%
-Moreover, \nick{channelization creates a heterogeneous and anisotropic medium properties}, \st{and
-this affects} \nick{affecting} the transport of \st{quantities} \nick{tracers} such as
-contaminants~\cite{cve-che-wen1996, dag1987, kon-bre1978} and
-heat~\cite{nil-sto1990, ree-sto1995}.  \awk{To characterize transport in
-eroded geometries, we complete two undertakings: forming realistic
-eroded porous geometries and characterizing transport through these
-geometries}.  
-\todo[inline]{Nick: The purple sentence is redundant: `To \underline{characterize transport} ...
-we undertake ...
-\underline{characterizing transport} through these geometries.
-Maybe try something like this:}
-\nick{This study consists of two main undertakings: First, high-fidelity simulations of porous-medium erosion, and, second, the characterization of transport through the resulting geometries.}
-Our modeling efforts build on previous work \cite{ris-moo-chi-she-zha2012, moore2013self, moore2017riemann}, in particular recent numerical methods developed to simulate erosion in the regime of Stokes flow \cite{qua-moo2018}.
-We, however, make a few key improvements to the numerical methods from \cite{qua-moo2018} to enable simulations of more realistic, dense suspensions of eroding grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).
-To characterize transport in the resulting geometries, \st{we apply statistical methods to develop coarse-grained variables} \nick{examine coarse-grained variables through statistical analysis of tracer trajectories}.
-\todo[inline]{I'm not sure about my modification above, but see if it gets across the message that was intended.}
+porous media evolve in time in applications involving
+melting~\cite{bec-vis1998, rycroft2016asymmetric, favier2019rayleigh,
+morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape,
+moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
+hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and crack
+formation~\cite{cho2019crack}. We focus on erosion, a fluid-mechanical
+process that is prevalent in many geophysical, hydrological, and
+industrial applications~\cite{berhanu2012shape, hewett2017evolution,
+lopez2018cfd, allen2019sde, amin2019role}.  When a porous geometry
+erodes, certain qualitative characteristics are unveiled that affect
+transport through the geometry.  For example, an eroded geometry may
+contain channels of high porosity, which, though few in number and
+modest in volume fraction, transmit a large portion of the flux. This
+arrangement results in velocities that vary over several orders of
+magnitude~\cite{all-hea-lab-rei2002}.  Moreover, channelization creates
+a heterogeneous and anisotropic medium properties affecting the
+transport of tracers such as contaminants~\cite{cve-che-wen1996,
+dag1987, kon-bre1978} and heat~\cite{nil-sto1990, ree-sto1995}.
+
+This study consists of two main undertakings: first, high-fidelity
+simulations of eroding porous media, and, second, characterizing
+transport through the resulting geometries. Our modeling efforts build
+on previous work~\cite{ris-moo-chi-she-zha2012, moore2013self, moo2017},
+in particular recent numerical methods developed to simulate erosion in
+the regime of Stokes flow~\cite{qua-moo2018}. We, however, make a few
+key improvements to the numerical methods from~\cite{qua-moo2018} to
+enable simulations of more realistic, dense suspensions of eroding
+grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To
+characterize transport in the resulting geometries, examine
+coarse-grained variables through statistical analysis of tracer
+trajectories.
 
@@
 
-\st{Because of the length and velocity scales in hydrological applications
-such as groundwater flow} \nick{Owing to the scales present in groundwater flow} \cite{bea1972}, we model the hydrodynamics with
-the two-dimensional incompressible Stokes equations.  \st{To couple erosion
-with the fluid} Meanwhile, individual grains erode at a rate \st{that is} proportional to \st{the magnitude of} the hydrodynamic shear stress~\cite{wan-fel2004,
-ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  Since the vorticity and the shear stress are equivalent on the grains in the zero Reynolds number
-limit, we also compute the vorticity in the fluid bulk \nick{for visualization purposes} (Figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
-the fluid solver are available including lattice-gas or lattice
-Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998}, finite
-volumes~\cite{suo-liu-gan2019, den-ica-hid2018,
+Owing to the scales present in groundwater flow~\cite{bea1972}, we model
+the hydrodynamics with the two-dimensional incompressible Stokes
+equations.  Meanwhile, individual grains erode at a rate proportional to
+the hydrodynamic shear stress~\cite{wan-fel2004,
+ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  Since the
+vorticity and the shear stress are equivalent on the grains in the zero
+Reynolds number limit, we also compute the vorticity in the fluid bulk
+for visualization purposes (Figure~\ref{fig:Eroding50vort}).  A variety
+of numerical methods for the fluid solver are available including
+lattice-gas or lattice Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998},
+finite volumes~\cite{suo-liu-gan2019, den-ica-hid2018,
 sie-ili-pri-riv-gua2019}, finite differences~\cite{leb-ded-dav-bou2007,
@@
 Erosion in porous geometries leads to particular phenomena such as
-channelization, and we are interested in characterizing transport in
-such geometries.  In our previous work~\cite{qua-moo2018}, we examined
-the effect of erosion on the area fraction, flow rate, and the total
-drag.  However, to characterize transport, other quantities must be
-examined.  Here, we compute the anomalous dispersion rate, the
-tortuosity, and the distribution of the pore sizes.  The first two
-metrics can be defined in terms of streamlines governed by an advection
-autonomous equation~\eqref{eqn:tracers}.
+channelization~\cite{berhanu2012shape}, and we are interested in
+characterizing transport in such geometries.  In our previous
+work~\cite{qua-moo2018}, we examined the effect of erosion on the area
+fraction, flow rate, and the total drag.  However, to characterize
+transport, other quantities must be examined.  Here, we compute the
+anomalous dispersion rate, the tortuosity, and the distribution of the
+pore sizes.  The first two metrics can be defined in terms of
+streamlines governed by an advection autonomous
+equation~\eqref{eqn:tracers}.
 
@@
 transport~\cite{knu-car2005},
-channelization~\cite{sie-ili-pri-riv-gua2019}, and more. In addition,
-the grain configuration is important for pore network
+channelization~\cite{sie-ili-pri-riv-gua2019,berhanu2012shape}, and
+more. In addition, the grain configuration is important for pore network
 models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} that rely on
@@
 grains.  To define neighboring grains, we form a Delaunay triangulation
-using nodes placed at the center of each eroding grain and at a collection
-of points around the boundary of the porous region.  Then, we say that
-two grains are neighbors if their centers share an edge of the
+using nodes placed at the center of each eroding grain and at a
+collection of points around the boundary of the porous region.  Then, we
+say that two grains are neighbors if their centers share an edge of the
 triangulation~\cite{dea-qua-bir-jua2018}.  Finally, we compute the
@@
 so some of the grains near the porous region boundary only have two
-neighbors.
+neighbors.  To analyze the effect of erosion on pore sizes, we use a
+single Delaunay triangulation to define the neighbors up until a body
+has completely eroded. At this point, a new Delanuay triangulation is
+formed.
 
@@
 term and a Gaussian smoothing step.  For all examples, we use the
-smoothing parameters $\eps=15/256$ and $\sigma=10/256$.
+smoothing parameters $\eps=15/256$ and $\sigma=10/256$, and the time
+step size is $\Delta t = 10^{-4}$.
 
@@
 $6,400$ discretization points, and the outer wall would require $50,000$
-discretization points.  For all three simulations, we use the time step
-size $\Delta t=10^{-4}$.
+discretization points.
 
@@
 We consider 20 eroding bodies that are discretized with $N_\iin=256$
-points and a time step size of $\Delta t = 10^{-4}$.  The background
-flow is the Hagen-Poiseuille flow
+points.  The background flow is the Hagen-Poiseuille flow
 \begin{align}
@@
 
-Next, we use the streamlines to compute the local tortuosity and the
-anomalous dispersion rate of eroding geometries.  To achieve statistical
+Next, we use the streamlines to compute the tortuosity and the anomalous
+dispersion rate of eroding geometries.  To achieve statistical
 convergence, we use $N_p = 1000$ streamlines~\cite{bel-sal-rin1992}. To
@@
 These normalized velocities are plotted in
-Figure~\ref{fig:Eroding20tort}(a) for the eroded geometry with porosity
-62.9\% (see Figure~\ref{fig:Eroding20tort}(c)).  The velocities are
+Figure~\ref{fig:Eroding20tort}(a) for the eroded geometry at porosity
+$\phi = 62.9\%$ (Figure~\ref{fig:Eroding20tort}(c)).  The velocities are
 similar to the work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure
@@
 bodies, each discretized with $N_\iin = 256$ points, in a
-Hagen-Poiseuille flow. The 4 snapshots are evenly spaced in time, and
+Hagen-Poiseuille flow. The four snapshots are evenly spaced in time, and
 the color is the fluid vorticity. In addition to the channels that
@@
 
-\todo[inline]{HERE}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 As a final example, we consider 100 eroding bodies with an initial
-porosity near 50\%.  Snapshots of the configurations and vorticity are in
-Figure~\ref{fig:Eroding100vort}.  Again, by resolving near-contacts with
-the Barycentric quadrature rule, a stable simulation is possible with
-only $N_\iin = 256$ discretization points.  We use a time step size of
-$\Delta t = 10^{-4}.$
+porosity near 50\%.  Snapshots of the configurations and vorticity are
+in Figure~\ref{fig:Eroding100vort}.  Again, by resolving near-contacts
+with the Barycentric quadrature rule, a stable simulation is possible
+with only $N_\iin = 256$ discretization points.
 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
-  fixed-pressure-drop condition. The color is the vorticity of fluid. In
-  this simulation, we use $N_\iin = 256$ discretization points on the
-  body, $N_\out = 1024$ points on the outer wall, a time-step of
-  $\Dt=10^{-4}$.  Because of the large number of bodies, erosion creates
-  many channels connecting the inlet to the outlet.}
+\caption{\label{fig:Eroding100vort} The erosion of 100 nearly
+touching grains, each discretized with $N_\iin = 256$ points, in a
+Hagen-Poiseuille flow. The color is the vorticity of fluid. The four
+snapshots are evenly spaced in time, and the color is the fluid
+vorticity.  Because of the large number of bodies, erosion creates many
+channels connecting the inlet to the outlet.}
 \end{figure}
 
-To quantify the tortuosity, we compute the relative velocity
-(Figure~\ref{fig:Eroding100tort}(a)) and the local tortuosity
-(Figure~\ref{fig:Eroding100tort}(b)) of 1000 tracers placed immediately
-to the left of the porous region at $x=-1$.  The porosity at this
-time is $62.98\%$ and the maximum velocity at $x=-1$ is
-$3.90 \times 10^{-4}$. The initial velocity of the tracers is
-qualitatively similar to the 20 body example
+We compute the tortuosity using both the
+Lagrangian~\eqref{eqn:tortuosity1} and Eulerian
+methods~\eqref{eqn:tortuosity2}. Therefore, we must compute the velocity
+at $N_p = 1000$ points along the inlet $x=-1$. These normalized
+velocities are plotted in Figure~\ref{fig:Eroding100tort}(a) for the
+eroded geometry at porosity $\phi = 63.0\%$
+(Figure~\ref{fig:Eroding100tort}(c)).  The initial velocity of the
+tracers is qualitatively similar to the 20 body example
 (Figure~\ref{fig:Eroding20tort}(a)), except with additional maximum and
-minimums because of the additional bodies.  Compared to
-Figure~\ref{fig:Eroding20tort}(b), the local tortuosity is much more
-discontinuous.  These discontinuities can be explained by examining the
-trajectories of tracers in Figure~\ref{fig:Eroding100tort}(c).  Here,
-there are many instances of neighboring trajectories that are deflected
-apart from one another as they tend to a stagnation point in the flow,
-and this results in trajectories with significantly different lengths.
-At this time one the tracers travels 25.5\% farther than it would have
-if the bodies had been absent, and the average tracer travelled 12\%
-farther than it would have if the bodies were absent, so the tortuosity
-is $1.12$.
+minimums because of the additional bodies.  Next, in
+Figure~\ref{fig:Eroding100tort}(b), we plot the local tortuosity by
+finding the length of the streamlines as they pass from $x=-1$ to $x=1$.
+Compared to Figure~\ref{fig:Eroding20tort}(b), the local tortuosity is
+much more discontinuous.  These discontinuities can be explained by
+examining the trajectories of tracers in
+Figure~\ref{fig:Eroding100tort}(c).  Here, there are many instances of
+nearby streamlines that are deflected apart from one another as they
+tend to a stagnation point in the flow, and this results in trajectories
+with significantly different lengths.  At this porosity, one of the
+tracers travels 25.5\% farther than it would have if the bodies had been
+absent, and the average tracer travelled 12\% farther than it would have
+if the bodies were absent, so the tortuosity is $1.12$.
 
@@
 (a) The $x$-component of the velocity at the inlet, $u_1(-1, y)$,
-normalized by its maximum velocity $u_{max}=3.90 \times 10^{-4}$.  (b)
-The local tortuosity $\tau(y)$ on the cross section $x = -1$. The
+normalized by its maximum velocity $u_{max}=3.90 \times 10^{-4}$.  Note
+that this maximum velocity is about a order of magnitude smaller than
+when compared to the 20 body example in Figure~\ref{fig:Eroding20tort}.
+(b) The local tortuosity $\tau(y)$ on the cross section $x = -1$. The
 spatially averaged tortuosity through the channel is $1.12$. (c) The
@@
 porosities.  However, the tortuosity undergoes a sudden increase near
-the end of the simulation.  The increase is caused by a single small
-body near the middle of the channel being completely eroded.  While this
-results in straighter streamlines, therefore reducing $\lambda$, the
-horizontal flow, $u_1(y)$ increases since there is no longer a no-slip
-boundary.  At the very late stages of erosion, we have observed that
-when a single small body finishes eroding, this can result in a sudden
-increase in the tortuosity.  We also computed the lines of best fit
-using the porosity-tortuosity models~\eqref{eqn:tortuosityModels}.  The
-black dashed line in Figure~\ref{fig:Eroding100Transport}(a) is the line
-of best fit
+the end of the simulation, and we have observed this behavior in other
+examples.  The increase is caused by a single small body near the middle
+of the channel being completely eroded.  While this results in
+straighter streamlines, therefore reducing $\lambda$, the horizontal
+flow, $u_1(y)$ increases since there is no longer a no-slip boundary.
+We also computed the lines of best fit using the porosity-tortuosity
+models~\eqref{eqn:tortuosityModels}.  The black dashed line in
+Figure~\ref{fig:Eroding100Transport}(a) is the line of best fit
 \begin{align}
@@
 
-In Figure~\ref{fig:Eroding100Transport}(b), we use the 1000 tracer
-trajectories to compute the asymptotic dispersion rates at various
+In Figure~\ref{fig:Eroding100Transport}(b), we plot the temporal
+evolution of the particle spreading $\sigma_\lambda$ at six different
 porosities. Again, we initially observe ballistic motion (black dashed
-line), and then super-diffusive dispersion.  Similar to the example in
+line), and then super-dispersion.  Similar to the example in
 Figure~\ref{fig:ErodingLow20Transport}(b), the anomalous dispersion rate
@@
 finding the closest distance between all neighboring bodies.  Once all
-pore sizes are computed, we analyze their distribution as a function
-of the porosity.  In Figure~\ref{fig:Eroding100gap_hist}, we plot
-histograms of the pore pore sizes at six porosities of the erosion
-process. These distributions have been modelled with Weibull
+pore sizes are computed, we analyze their distribution as a function of
+the porosity.  In Figure~\ref{fig:Eroding100gap_hist}, we plot
+histograms of the pore pore sizes at six porosities during the erosion
+process. These types of distributions have been described with Weibull
 distributions~\cite{ioa-cha1993}, and we superimpose the Weibull
 distribution with the same first two moments as the data.  The
-parameters that parameterize the distribution, $(k,\lambda)$, are
-included in the caption of Figure~\ref{fig:Eroding100gap_hist}.  In
+parameters of the distribution, $(k,\lambda)$, are included in the
+caption of Figure~\ref{fig:Eroding100gap_hist}.  In
 Figure~\ref{fig:Eroding100gap_mean_var}, we plot the mean and variance
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap_hist} The distribution of the gaps in
-the case of 100 bodies eroding at six porosities. The black curves are
+\caption{\label{fig:Eroding100gap_hist} The distribution of the pore
+sizes of 100 eroding bodies at six porosities. The black curves are
 Weibull distributions whose first and second moments agree with the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+As a continuation of our previous work~\cite{qua-moo2018}, we have
+simulated dense suspensions and characterized transport in viscous
+erosion of porous media. A BIE formulation is used to solve the Stokes
+equations and to compute the shear stress. However, to simulate
+nearly-touching grains and to consider transport, it is necessary to
+integrate near-singular functions. This is achieved by extending a
+Barycentric quadrature rule~\cite{bar-wu-vee2015} to accurately compute
+the erosion rate and vorticity. By using this quadrature rule, we are
+able to form stable simulations of erosion with $N = \mathcal{O}(100)$
+discretization points, while the trapezoid rule would require
+$\mathcal{O}(10^5)$ discretization points.
+
+The transport is characterized in terms of tortuosity and anomalous
+dispersion. The local tortuosity agrees qualitatively with
+other works~\cite{mat-kha-koz2008}. However, the tortuosity of the
+eroded geometries can not be completely described in terms of the
+porosity. In particular, we observe that for certain porous media, the
+tortuosity can increase when the porosity increases under erosion. We
+also observe super-dispersive spreading, and the rate of dispersion
+significantly depends not only on the porosity, but also the number of
+eroding bodies.
+
+To further our understanding of erosion, we are examining other bulk and
+statistical properties of an eroding porous media. In this work, we
+provide preliminary results for the pore throat sizes which affect the
+anomalous dispersion rate~\cite{dea-qua-bir-jua2018}.  At a later date,
+we will report results on the  development of anisotropic effects and
+the distributions of grain sizes, shapes, and opening angles.
+
+As a long term goal, we would like to include the effect of inertia and
+other transport models. Including inertia requires an integral equation
+formulation for the Navier-Stokes equations, and one approach has
+recently been developed~\cite{kli-ask-kro2019}. Regarding other
+transport models, this would involve a diffusive term to consider the
+transport of heat or a contaminant. Forming high-fidelity simulations of
+such an advection-diffusion equation can be accomplished by using time
+splitting methods and recent work on heat solvers in complex
+geometries~\cite{fry-kro-tor2019}.
 

### 2019-09-27 docs/transport/erosion_transport.tex
small edits from S-H

@@
 We present the quadrature rules for a simply-connected interior domain
-$\Omega \subset \CC$, with a point $a \in \Omega$, and we consider the
+$\Omega \subset \CC$, with any point $a \in \Omega$, and we consider the
 target points $x \in \Omega$ and $x \in \Omega^c$. Then, these
@@
 $\mathcal{O}(N^2)$ operations.  By using a fast summation method, such
-as the fast multipole method~\cite{gre-rok1987}, this cost can be
+as the fast multipole method (FMM)~\cite{gre-rok1987}, this cost can be
 reduced to $\mathcal{O}(N)$ operations.  However, the Barycentric
@@
 rule needs to be replaced with a more accurate quadrature rule for
-points that are too close to $\bd\Omega$.  Note, however, that since a
-point is typically only close to one or two components of $\bd\Omega$,
-only the contribution of these nearby bodies needs to be replaced.
-Assuming that $\xx$ is too close to $\gamma_k$, we first subtract the
-inaccurate trapezoid rule approximation of the double-layer potential
-due to $\gamma_k$.  Then, the Barycentric quadrature rule is used to
-compute the velocity due to $\gamma_k$ with more accuracy.  That is, the
-final velocity is
+points that are too close to $\bd\Omega$.  Note that since a point is
+typically only close to one or two components of $\bd\Omega$, only the
+contribution of these nearby bodies needs to be replaced.  Assuming that
+$\xx$ is too close to $\gamma_k$, we first subtract the inaccurate
+trapezoid rule approximation of the double-layer potential due to
+$\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
+the velocity due to $\gamma_k$ with more accuracy.  That is, the final
+velocity is
 \begin{align}
@@
 satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL}
-variables~\cite{hou-low-she1994}.  First, given two eroding bodies $\gamma_i$ and $\gamma_j$ with
-lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we check if
+variables~\cite{hou-low-she1994}.  First, given two eroding bodies
+$\gamma_i$ and $\gamma_j$ with lengths $L_i$ and $L_j$, and centroids
+$\cc_i$ and $\cc_j$, we check if
 \begin{align}

### 2019-09-30 docs/transport/erosion_transport.tex
did revions to abstract

@@
 \begin{abstract} 
-  We extend upon our previous work, [Journal of Computational Physics,
-  {\bf 375}:1--21, 2018], to simulate dense suspensions of
-  fluid-mechanical erosion of two-dimensional erosion of porous media.
-  The method combines a boundary integral equation (BIE) fluid solver
-  and a numerically stable time stepping method for the evolution of the
-  eroding bodies. Originally, the eroding bodies had to be sufficiently
-  separated to guarantee that the trapezoid rule provided a sufficient
-  level of accuracy. In this work, we develop resolve interactions
-  between nearly touching bodies with a Barycentric quadrature rule
-  whose error is independent of the geometry.  Since the Barycentric
-  quadrature rule is computationally expensive, it is only used when
-  necessary, and the spectrally accurate trapezoid rule is used
-  otherwise. Our final fluid solver only requires $\mathcal{O}(N)$
-  iterations per time step. Next, we simulate and analyze transport
-  through eroded porous geometries.  Our results demonstrate the effects
-  of erosion on tortuosity, dispersion, and pore size distributions.
+  We extend our previous work, [{\em Journal of Computational Physics},
+  {\bf 375}:1--21, 2018], to simulate fluid-mechanical erosion of
+  two-dimensional porous media with nearly-touching grains.  The method
+  continues to use a boundary integral equation (BIE) method to solve
+  the fluid equations and to compute the erosion rate, and a stable
+  second-order time stepping method to erode the grains.  In our
+  original work, we required that the eroding grains were sufficiently
+  separated to guarantee that the trapezoid rule provides a sufficient
+  amount of accuracy. We now remove this restriction by introducing a
+  Barycentric quadrature rule whose error is bounded independent of the
+  geometry.  The Barycentric quadrature rule is computationally
+  expensive, so it is only used when necessary, and the spectrally
+  accurate trapezoid rule is used otherwise. We also simulate and
+  analyze transport through eroded porous geometries.  By using the
+  Barycentric quadrature rule, the analysis examines flow both in the
+  fast and slow regions with high-order accuracy. Our results
+  demonstrate the effects of erosion on tortuosity, dispersion, and pore
+  size distributions.
 \end{abstract}

### 2019-09-30 docs/transport/erosion_transport.tex
small changes to intro and abstract

@@
   continues to use a boundary integral equation (BIE) method to solve
-  the fluid equations and to compute the erosion rate, and a stable
-  second-order time stepping method to erode the grains.  In our
-  original work, we required that the eroding grains were sufficiently
-  separated to guarantee that the trapezoid rule provides a sufficient
-  amount of accuracy. We now remove this restriction by introducing a
-  Barycentric quadrature rule whose error is bounded independent of the
-  geometry.  The Barycentric quadrature rule is computationally
-  expensive, so it is only used when necessary, and the spectrally
-  accurate trapezoid rule is used otherwise. We also simulate and
-  analyze transport through eroded porous geometries.  By using the
-  Barycentric quadrature rule, the analysis examines flow both in the
-  fast and slow regions with high-order accuracy. Our results
-  demonstrate the effects of erosion on tortuosity, dispersion, and pore
-  size distributions.
+  the fluid equations, and a stable second-order time stepping method to
+  erode the grains.  In our previous work, we required that the eroding
+  grains were sufficiently separated to guarantee that the trapezoid
+  rule provides a sufficient amount of accuracy. We now remove this
+  restriction by introducing a Barycentric quadrature rule whose error
+  is bounded independent of the geometry.  The Barycentric quadrature
+  rule is computationally expensive, so it is only used when necessary,
+  and the spectrally accurate fast-multipole-accelerated trapezoid rule
+  is used otherwise. We also simulate and analyze transport through
+  eroded porous media.  By using the Barycentric quadrature rule, the
+  analysis examines flow both in the fast and slow regions with
+  high-order accuracy. Our results reveal several interesting  effects
+  of erosion on the tortuosity, dispersion, and pore size distributions.
 \end{abstract}
@@
 grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To
-characterize transport in the resulting geometries, examine
+characterize transport in the resulting geometries, we examine
 coarse-grained variables through statistical analysis of tracer
@@
 averaging the local tortuosity over all streamlines that are initialized
-at the inlet, and the geometry's tortuosity can be used to characterize
-average particle motions~\cite{hak-com-den2019}.  To characterize
-spreading, the fluid dispersion is computed by calculating the variance
-of the streamline lengths. In porous media, this spreading can often be
-characterized with a super-diffusive anomalous dispersion
-rate~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
-dea-leb-den-tar-bol-dav2013}. An accurate solution near the grains is
-crucial since the anomalous dispersion is caused by streamlines spending
-time in both the high and low velocity regimes~\cite{ber-sch2001}.
-Finally, the third metric, pore size distribution, is useful to quantify
-velocity distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
-channelization~\cite{sie-ili-pri-riv-gua2019},
+at the inlet, and the geometry's tortuosity characterizes average
+particle motions~\cite{hak-com-den2019}.  To characterize spreading, the
+fluid dispersion is computed by calculating the variance of the
+streamline lengths. In porous media, this spreading is often
+super-dispersive~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
+dea-leb-den-tar-bol-dav2013}. Accurately resolving the streamlines near
+the grains is crucial since the anomalous dispersion is caused by
+streamlines spending time in both the high and low velocity
+regimes~\cite{ber-sch2001}.  Finally, since they are required to
+quantify velocity distributions~\cite{ali-par-wei-bre2017,
+dea-qua-bir-jua2018}, channelization~\cite{sie-ili-pri-riv-gua2019},
 connectivity~\cite{knu-car2005, wes-blo-gra2001}, and to develop network
-models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
+models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}, we form the
+pore size distribution throughout the erosion process.
 
@@
 \paragraph{Contributions}
-Our first contribution is extending the work of Barnett et
-al.~\cite{bar-wu-vee2015} so that high-order accurate derivatives of
-solutions of the Stokes equations can be computed.  Using this new
-quadrature rule, we accurately compute erosion rates and stably simulate
-erosion.  Moreover, we use the quadrature method to visualize the
-vorticity in the fluid bulk.  The vorticity is convenient to visualize
-since, in the zero Reynolds number limit, it is equivalent to the shear
-stress on the eroding bodies, and therefore its magnitude is the erosion
-rate.
+Our first contribution is extending the Barycentric quadrature rule of
+Barnett et al.~\cite{bar-wu-vee2015} so that high-order accurate
+derivatives of solutions of the Stokes equations can be computed.  Using
+this new quadrature rule, we accurately compute erosion rates and stably
+simulate erosion.  Moreover, we use the quadrature method to visualize
+the vorticity in the fluid bulk.
 
@@
 transport by computing the local tortuosity of trajectories, and the
-tortuosity and dispersion rate of eroded geometries. By using the same
-quadrature rule and a fourth-order Runge-Kutta method, we are able to
+tortuosity and dispersion rate of eroded geometries. By using the
+Barycentric quadrature rule and a fourth-order Runge-Kutta method, we
 accurately compute trajectories that spend large amounts of time in the
-slow velocity regions near the eroding bodies, and reliably computing
-these trajectories is essential to characterize the
-flow~\cite{dea-leb-den-tar-bol-dav2013}.  We compare our tortuosity and
-dispersion rates with models available in the literature.  Finally, we
-analyze the effect of erosion on the pore size distribution.
+slow velocity regions near the eroding bodies, a necessity to
+characterize the flow~\cite{dea-leb-den-tar-bol-dav2013}.  We compare
+our tortuosity and dispersion rates with models available in the
+literature.  Finally, we analyze the effect of erosion on the pore size
+distribution.
 
@@
 As in our previous work~\cite{qua-moo2018}, we consider two-dimensional
-immobile eroding grains. However, this work does not have a limitation
-on the proximity of the grains. Compared to our previous work, we are
-able to simulate much denser suspensions with a comparable number of
+immobile eroding grains. However, this work is not limited by the
+proximity of the grains. Compared to our previous work, we are able to
+simulate much denser suspensions with a comparable number of
 discretization points and without upsampling.  While we do investigate
@@
 \paragraph{Outline of the Paper}
-In Section~\ref{sec:formulation}, we summarize the model that we
+In Section~\ref{sec:formulation}, we summarize the erosion model that we
 describe in detail in our previous work~\cite{qua-moo2018}.  In
@@
 \gamma_1 \cup \cdots \cup \gamma_M$.  In all examples, we let $\Gamma$
-be a slightly rounded-off version of $[-3,3] \times [-1,1]$, and we only
+be a slightly smoothed version of $[-3,3] \times [-1,1]$, and we only
 place eroding bodies in the region $[-1,1] \times [-1,1]$.  On each
@@
       &&\mbox{\em conservation of mass}, \\
-    \uu = 0, &\hspace{20pt} \xx \in \gamma, \gap 
-      &&\mbox{\em no slip on the bodies}, \\
+    \uu = \mathbf{0}, &\hspace{20pt} \xx \in \gamma, \gap 
+      &&\mbox{\em no slip on the eroding bodies}, \\
     \uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since we require a method to solve the incompressible Stokes equations in
-complex two-dimensional porous geometries, we reformulated the
-incompressible Stokes equations as a boundary integral equation. This
-has the advantage that only the one-dimensional boundary of the domain
-must be discretized, and if appropriate quadrature formula and fast
-summation methods are used, the result is a high-fidelity numerical
-simulation that is computed with near-optimal complexity.
+Since we require an accurate solution of the incompressible Stokes
+equations in complex two-dimensional porous media, we reformulated the
+incompressible Stokes equations as a BIE.  This has the advantage that
+only the one-dimensional boundary of the domain must be discretized, and
+if appropriate quadrature formula and fast summation methods are used,
+the result is a high-fidelity numerical simulation that is computed with
+near-optimal complexity.
 

### 2019-09-30 docs/transport/erosion_transport.tex
NM

@@
 porous media evolve in time in applications involving
-melting~\cite{bec-vis1998, rycroft2016asymmetric, favier2019rayleigh,
-morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape,
-moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
+melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
 hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and crack
@@
 process that is prevalent in many geophysical, hydrological, and
-industrial applications~\cite{berhanu2012shape, hewett2017evolution,
-lopez2018cfd, allen2019sde, amin2019role}.  When a porous geometry
-erodes, certain qualitative characteristics are unveiled that affect
-transport through the geometry.  For example, an eroded geometry may
+industrial applications~\cite{berhanu2012shape, hewett2017evolution, lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
+When a porous geometry erodes, certain qualitative characteristics are unveiled that affect transport through the geometry.
+For example, an eroded geometry may
 contain channels of high porosity, which, though few in number and
@@
 are eroded a single time step by using a {\thL}
-discretization~\cite{hou-low-she1994}.  The time stepping methods for
+discretization~\cite{hou-low-she1994, moore2013self}.  The time stepping methods for
 erosion and passive particles are described in Section~\ref{sec:time}

### 2019-09-30 docs/transport/erosion_transport.tex
small edits

--- 2019-09-30 docs/transport/erosion_transport.tex
@@
 Since we require an accurate solution of the incompressible Stokes
-equations in complex two-dimensional porous media, we reformulated the
+equations in complex two-dimensional geometries, we reformulated the
 incompressible Stokes equations as a BIE.  This has the advantage that
 only the one-dimensional boundary of the domain must be discretized, and
-if appropriate quadrature formula and fast summation methods are used,
-the result is a high-fidelity numerical simulation that is computed with
-near-optimal complexity.
+near-optimal complexity can be achieved by using appropriate quadrature
+formula and fast summation methods.
 
@@
 represent all solutions of the incompressible Stokes equations, so we
-complete the integral equation formulation by adding the Stokeslets and
-rotlets~\cite{pow-mir1987}
+complete the integral equation formulation by adding the $M$ Stokeslets
+and rotlets~\cite{pow-mir1987}
 \begin{align}
@@
 \end{subequations}
-The operator $\NN_0$ is the integral operator with kernel
-$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$,
-which removes the rank one null space resulting from the flux-free
-requirement of $\ff$.  In this work, $\ff$ is the prescribed velocity,
-$\UU$, on the outer wall, $\Gamma$, and is zero on the eroding bodies,
-$\gamma_\ell$, $\ell=1,\ldots,M$.
+Here, the null space associated with the flux-free condition of $\ff$ is
+addressed with the integral operator $\NN_0$ which has the integral
+kernel $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.
+In this work, $\ff$ is the prescribed velocity, $\UU$, on the outer
+wall, $\Gamma$, and is zero on the eroding bodies, $\gamma_\ell$,
+$\ell=1,\ldots,M$.
 
@@
 \end{align}
-respectively. We require the deformation tensor of the double-layer potential at
-$\xx \in \bd \Omega$.  Since the deformation tensor of the double-layer
+respectively.  Since the deformation tensor of the double-layer
 potential is discontinuous across $\bd\Omega$, the jump term 
@@
 \end{align}
-must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
-Stokeslets and rotlets do not have any jumps on $\gamma$, so the
-deformation tensor, pressure, and vorticity due to the Stokeslets and
-rotlets are straightforward to compute~\cite{poz1992}.  Having computed
-the deformation tensor on $\gamma$, the shear stress is computed as
-defined in equation~\eqref{eqn:shearStress}.
+must be added to compute $\ssigma(\xx)$ for $\xx \in \bd\Omega$.
+Finally, the Stokeslets and rotlets do not have any jumps on $\gamma$,
+so the deformation tensor, pressure, and vorticity due to the Stokeslets
+and rotlets are straightforward to compute~\cite{poz1992}.  Having
+computed the deformation tensor on $\gamma$, the shear stress is
+computed as defined in equation~\eqref{eqn:shearStress}.
 
@@
 $\uu$ and its deformation tensor are written as layer potentials in
-$\RR^2$.  However, the quadrature method we introduce in
+$\RR^2$, but the quadrature method we introduce in
 Section~\ref{sec:method} requires a complex-valued representation of the

### 2019-09-30 docs/transport/erosion_transport.tex
NM

--- 2019-09-30 docs/transport/erosion_transport.tex
@@
 
-Flow in porous media is further complicated when there is a two-way
-coupling between the flow and the geometry. For example, the grains of a
-porous media evolve in time in applications involving
-melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
+%Flow in porous media is further complicated when there is a two-way coupling between the flow and the geometry. For example, the grains of a porous media evolve in time in applications involving
+\nick{Flow in porous media is further complicated when boundaries evolve dynamically in response to the fluid flow.
+This type of coupling between geometry and flow occurs, for example, in applications involving} melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
 hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and crack

### 2019-09-30 docs/transport/erosion_transport.tex
NM

@@
 arrangement results in velocities that vary over several orders of
-magnitude~\cite{all-hea-lab-rei2002}.  Moreover, channelization creates
-a heterogeneous and anisotropic medium properties affecting the
-transport of tracers such as contaminants~\cite{cve-che-wen1996,
+magnitude~\cite{all-hea-lab-rei2002}.  \nick{Moreover, channelization creates heterogeneous and anisotropic medium properties, which affect the
+transport of tracers} such as contaminants~\cite{cve-che-wen1996,
 dag1987, kon-bre1978} and heat~\cite{nil-sto1990, ree-sto1995}.
@@
 This study consists of two main undertakings: first, high-fidelity
-simulations of eroding porous media, and, second, characterizing
-transport through the resulting geometries. Our modeling efforts build
-on previous work~\cite{ris-moo-chi-she-zha2012, moore2013self, moo2017},
-in particular recent numerical methods developed to simulate erosion in
-the regime of Stokes flow~\cite{qua-moo2018}. We, however, make a few
+simulations of eroding porous media, and, second, \nick{characterization of tracer transport through the dynamic geometries that result}.
+Our modeling efforts build on previous work~\cite{ris-moo-chi-she-zha2012, moore2013self, moo2017}, in particular recent numerical methods developed to simulate erosion in the regime of Stokes flow~\cite{qua-moo2018}.
+We, however, make a few
 key improvements to the numerical methods from~\cite{qua-moo2018} to
 enable simulations of more realistic, dense suspensions of eroding
-grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To
-characterize transport in the resulting geometries, we examine
+grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To characterize transport through these \nick{configurations}, we examine
 coarse-grained variables through statistical analysis of tracer

### 2019-09-30 docs/transport/erosion_transport.tex
small changes

--- 2019-09-30 docs/transport/erosion_transport.tex
@@
 \end{align}
-where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$.
-Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy
-integral by first finding the boundary data of $v$.  Assuming that
-$\Omega$ is a simply-connected interior domain, the boundary data
-of $v$ satisfies the Sokhotski-Plemelj jump relation
+where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
+and $\eta$ is the complex-valued counterpart of $\eeta$.
+Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
+first finding the boundary data of $v$.  Assuming that $\Omega$ is a
+simply-connected interior domain, the boundary data of $v$ satisfies the
+Sokhotski-Plemelj jump relation
 \begin{align}
@@
 decomposed into its different connected components and the appropriate
-Cauchy integral is evaluated.  Since $v$ is a holomorphic function and
-we have its boundary data, by the Cauchy integral theorem we have
+jump relation is applied.  Since $v$ is a holomorphic function and we
+have its boundary data, by the Cauchy integral theorem we have
 \begin{align}
@@
       \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
-        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
+        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy,
   \end{aligned}
 \end{equation}
-Therefore, the Stokes double-layer potential can be written in terms of
-Cauchy integrals and their first derivative as
+where $\xx = (x_1,x_2)$. Therefore, the Stokes double-layer potential
+can be written as a sum of Cauchy integrals and its first derivative 
 \begin{equation}

### 2019-09-30 docs/transport/erosion_transport.tex
NM

--- 2019-09-30 docs/transport/erosion_transport.tex
@@
 method applied to the {\thL} coordinates~\cite{hou-low-she1994} of the
-eroding grains.  In this work, we do introduce a new quadrature method
+eroding grains.  In this work, we \st{do} introduce a new quadrature method
 to resolve dense suspensions of eroding grains.  The accuracy of the
-trapezoid rule, which we used in our previous work, is sufficient for
-bodies that are sufficiently separated~\cite{tre-wei2014}. However, it
-is inaccurate when two grains are nearly-touching.  One of the earliest
-works that addresses quadrature methods for nearly-singular integrands
-was developed by Baker and Shelley~\cite{bak-she1986}, and in recent
-years, many other near-singular integration schemes have been
-developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
-bea-lai2001, klo-bar-gre-one2013}.  We use a Barycentric quadrature
-rule~\cite{bar2014, bar-wu-vee2015} since it is a non-intrusive
+trapezoid rule, which we used in our previous work, is \st{sufficient} \nick{adequate} for bodies that are sufficiently separated~\cite{tre-wei2014}. 
+\todo[inline]{I changed the above to `adequate' so that `sufficient' would not be used twice in a row.} 
+However, it \nick{loses accuracy} whenever \st{two} grains are nearly-touching.
+One of the earliest works \nick{to address} quadrature methods for nearly-singular integrands was developed by Baker and Shelley~\cite{bak-she1986}, and in recent years, many other near-singular integration schemes have been \nick{followed}~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016, bea-lai2001, klo-bar-gre-one2013}.
+We use a Barycentric quadrature
+\nick{method}~\cite{bar2014, bar-wu-vee2015} since it is a non-intrusive
 modification of the trapezoid rule, and the error is guaranteed to be
-uniformly bounded.  We extend the original quadrature method so that it
-can be used to compute the gradient of the velocity that is required to
-compute the shear stress and the fluid vorticity.
+uniformly bounded.  We extend the original quadrature method \nick{to compute the velocity gradient, which is needed to evaluate shear stress and fluid vorticity}.
 
@@
 
-To characterize the transport, particle trajectories need to be
+To characterize the transport, particle trajectories \nick{must} be
 computed. Depending on the application, microscale transport can be
@@
 with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
-this work, we assume that the trajectories are governed purely by
-advection (ie.~no diffusion). Therefore, the particle trajectories are
+this work, we assume trajectories \nick{to be governed by pure advection} (ie.~no diffusion). Therefore, the particle trajectories are
 identical to the streamlines, and they can be found, for example, with a
 continuous time random walk~\cite{mon-wei1965, den-cor-sch-ber2004,
-leb-den-car2008, ber-cor-den-sch2006}.  Instead,  we compute
+leb-den-car2008, ber-cor-den-sch2006}.  
+\todo[inline]{The logic from the sentence above to the one below seems awkward to me.
+The above sentence makes me think that a continuous time random-walk will be used in our paper.
+Then, suddenly, we say we are going to do something else instead.
+Maybe we can kill the above sentence and dump the references (if you want to keep them) into the earlier sentence that mentions a random walk?
+Or maybe just a slight rephrasing would make the transition less awkward.}
+Instead,  we compute
 trajectories $\ss(t)$ that are initialized at $\ss_0$ by solving

### 2019-09-30 docs/transport/erosion_transport.tex
NM

--- 2019-09-30 docs/transport/erosion_transport.tex
@@
 
-Once streamlines in an eroded geometry are computed, we characterize the
-transport by computing and analyzing three different metrics: the
-tortuosity, the anomalous dispersion, and the pore size distribution.
-The local tortuosity of a streamline connecting the inlet to the outlet
-is the streamline's length normalized by the distance between the inlet
-and the outlet.  In porous media, depending on several factors including
-the porosity, the local tortuosity can be greater than
-1.5~\cite{kop-kat-tim1996, mat-kha-koz2008}, or even
-2~\cite{dud-koz-mat2011}.  The tortuosity of a geometry is defined by
-averaging the local tortuosity over all streamlines that are initialized
-at the inlet, and the geometry's tortuosity characterizes average
-particle motions~\cite{hak-com-den2019}.  To characterize spreading, the
-fluid dispersion is computed by calculating the variance of the
-streamline lengths. In porous media, this spreading is often
+Once \nick{the streamlines are computed, we characterize
+transport by analyzing} three different metrics: the tortuosity, the anomalous dispersion, and the pore size distribution. 
+The local tortuosity of a streamline \nick{that connects the inlet to the outlet is defined as the streamline's length normalized by the linear inlet-to-outlet distance}.
+In porous media, the local tortuosity can be greater than 1.5~\cite{kop-kat-tim1996, mat-kha-koz2008} or even 2~\cite{dud-koz-mat2011}, \nick{depending on several factors such as the porosity.} 
+The tortuosity of a geometry is defined by averaging the local tortuosity over all streamlines initialized at the inlet, and the geometry's tortuosity characterizes average particle motions~\cite{hak-com-den2019}.
+To characterize spreading, the fluid dispersion is computed by calculating the variance of the streamline lengths.
+In porous media, this spreading is often
 super-dispersive~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
-dea-leb-den-tar-bol-dav2013}. Accurately resolving the streamlines near
-the grains is crucial since the anomalous dispersion is caused by
-streamlines spending time in both the high and low velocity
-regimes~\cite{ber-sch2001}.  Finally, since they are required to
-quantify velocity distributions~\cite{ali-par-wei-bre2017,
-dea-qua-bir-jua2018}, channelization~\cite{sie-ili-pri-riv-gua2019},
-connectivity~\cite{knu-car2005, wes-blo-gra2001}, and to develop network
-models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}, we form the
-pore size distribution throughout the erosion process.
+dea-leb-den-tar-bol-dav2013}. \nick{Since anomalous dispersion results from streamlines spending time in both the high and low velocity}
+regimes~\cite{ber-sch2001}, it is crucial to accurately resolve  streamlines near grain boundaries, as achieved in this work.
+Finally, \nick{the distribution of pore sizes is required to} quantify velocity distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018}, channelization~\cite{sie-ili-pri-riv-gua2019}, connectivity~\cite{knu-car2005, wes-blo-gra2001}, and to develop network models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
+\nick{Hence, we construct the pore-size distribution throughout the erosion process.}
 
@@
 Our first contribution is extending the Barycentric quadrature rule of
-Barnett et al.~\cite{bar-wu-vee2015} so that high-order accurate
-derivatives of solutions of the Stokes equations can be computed.  Using
-this new quadrature rule, we accurately compute erosion rates and stably
-simulate erosion.  Moreover, we use the quadrature method to visualize
-the vorticity in the fluid bulk.
+Barnett et al.~\cite{bar-wu-vee2015} \nick{to accurately compute velocity gradients associated with Stokes flow.}
+\nick{This new quadrature rule permits accurate and stable simulations of erosion, and, moreover, enables visualization of the vorticity field throughout.}
 
@@
 As in our previous work~\cite{qua-moo2018}, we consider two-dimensional
-immobile eroding grains. However, this work is not limited by the
-proximity of the grains. Compared to our previous work, we are able to
+immobile eroding grains. However, this work \nick{does not limit} the proximity of  grains. Compared to our previous work, we are able to
 simulate much denser suspensions with a comparable number of
@@
 \paragraph{Outline of the Paper}
-In Section~\ref{sec:formulation}, we summarize the erosion model that we
-describe in detail in our previous work~\cite{qua-moo2018}.  In
+In Section~\ref{sec:formulation}, we summarize the erosion model \nick{that is described in more detail in} previous work~\cite{qua-moo2018}.  In
 Section~\ref{sec:DLP}, we recast all the governing equations as layer
@@
 the numerical methods, with special attention paid to the new quadrature
-method to compute the shear stress and vorticity.
+method \nick{for computing} shear stress and vorticity.
 Section~\ref{sec:results} presents numerical examples for a variety of

### 2019-09-30 docs/transport/erosion_transport.tex
NM

@@
 method applied to the {\thL} coordinates~\cite{hou-low-she1994} of the
-eroding grains.  In this work, we \st{do} introduce a new quadrature method
-to resolve dense suspensions of eroding grains.  The accuracy of the
+eroding grains.  In this work, we \nick{\st{do}} introduce a new quadrature method to resolve dense suspensions of eroding grains.  The accuracy of the
 trapezoid rule, which we used in our previous work, is \st{sufficient} \nick{adequate} for bodies that are sufficiently separated~\cite{tre-wei2014}. 
 \todo[inline]{I changed the above to `adequate' so that `sufficient' would not be used twice in a row.} 
-However, it \nick{loses accuracy} whenever \st{two} grains are nearly-touching.
+However, it \nick{loses accuracy whenever \st{two} grains come in close contact}.
 One of the earliest works \nick{to address} quadrature methods for nearly-singular integrands was developed by Baker and Shelley~\cite{bak-she1986}, and in recent years, many other near-singular integration schemes have been \nick{followed}~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016, bea-lai2001, klo-bar-gre-one2013}.
@@
 We start by defining the main variables used to model erosion.  We only
-summarize the model, and a more detailed description is in our previous
-work~\cite{qua-moo2018}.  We consider flows inside a confined geometry
-$\Omega$ that contains $M$ eroding bodies with boundaries $\gamma_\ell$,
-$\ell = 1,\ldots,M$.  The boundary of the bounding geometry is $\Gamma$,
-so the boundary of the fluid domain is $\bd \Omega = \Gamma \cup
-\gamma_1 \cup \cdots \cup \gamma_M$.  In all examples, we let $\Gamma$
-be a slightly smoothed version of $[-3,3] \times [-1,1]$, and we only
-place eroding bodies in the region $[-1,1] \times [-1,1]$.  On each
+\nick{briefly summarize the model, since a more detailed description can be found in previous} work~\cite{qua-moo2018}.
+We consider flows inside a confined geometry $\Omega$ that contains $M$ eroding bodies with boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$.
+\nick{The boundary of the fluid domain is $\bd \Omega = \Gamma \cup
+\gamma_1 \cup \cdots \cup \gamma_M$, where $\Gamma$ is the outer boundary, taken to be a slightly smoothed version of $[-3,3] \times [-1,1]$}. 
+\nick{We only place eroding bodies in $[-1,1] \times [-1,1]$ so as to create a buffer region for the flow profile imposed at the inlet to transition to the more complex flow intervening between the bodies}.
+On each
 eroding body, $\nn$ is the normal vector pointing into the body, and
@@
 is the shear stress on $\gamma$.  The strength of $\UU$ is adjusted at
-each time step so that there is a constant pressure drop across the
+each time step \nick{to achieve} a constant pressure drop across the
 channel.  We simulate erosion by alternating between solving the fluid
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since we require an accurate solution of the incompressible Stokes
-equations in complex two-dimensional porous media, we reformulated the
-incompressible Stokes equations as a BIE.  This has the advantage that
-only the one-dimensional boundary of the domain must be discretized, and
-if appropriate quadrature formula and fast summation methods are used,
-the result is a high-fidelity numerical simulation that is computed with
-near-optimal complexity.
+\nick{To solve} the incompressible Stokes
+equations in complex two-dimensional porous media, we \nick{reformulate\st{d}} the incompressible Stokes equations as a BIE.  This has the advantage that
+only the one-dimensional boundary of the domain must be discretized, and,
+\nick{with an appropriate quadrature formula and fast summation methods,
+the result is a high-fidelity numerical simulation of near-optimal computational complexity.}
 
@@
 \end{align}
-where $D$ is an kernel of the integral operator, $\rr = \xx - \yy$,
+where $D$ is \nick{\st{an} a} kernel of the integral operator, $\rr = \xx - \yy$,
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
@@
 $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$,
-which removes the rank one null space resulting from the flux-free
+which removes the rank one null space \nick{\st{resulting} that results} from the flux-free
 requirement of $\ff$.  In this work, $\ff$ is the prescribed velocity,

### 2019-09-30 docs/transport/erosion_transport.tex
NM

@@
 distribution.
+
+\todo[inline]{The above paragraph seems to repeat a lot of what has been mentioned already, but maybe that is okay.}
 
@@
 Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
-Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, the deformation
-tensor, pressure, and vorticity at $\xx \in \Omega$ are
+Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, \nick{we are able to compute the deformation tensor, pressure, and vorticity, defined respectively as}
 \begin{align}
@@
 \end{align}
-respectively. We require the deformation tensor of the double-layer potential at
-$\xx \in \bd \Omega$.  Since the deformation tensor of the double-layer
-potential is discontinuous across $\bd\Omega$, the jump term 
+\nick{\st{We require the deformation tensor of the double-layer potential at
+$\xx \in \bd \Omega$.}}
+Since the deformation tensor of the double-layer potential is discontinuous across the boundary $\bd\Omega$, the jump term 
 \begin{align}
@@
 must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
-Stokeslets and rotlets do not have any jumps on $\gamma$, so the
-deformation tensor, pressure, and vorticity due to the Stokeslets and
-rotlets are straightforward to compute~\cite{poz1992}.  Having computed
+Stokeslets and rotlets \nick{do not exhibit such jumps, and so the associated components of the deformation tensor, pressure, and vorticity} are straightforward to compute~\cite{poz1992}.
+Having computed
 the deformation tensor on $\gamma$, the shear stress is computed as

### 2019-09-30 docs/transport/erosion_transport.tex
fixed merge conflicts

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\nick{To solve} the incompressible Stokes
-equations in complex two-dimensional porous media, we \nick{reformulate\st{d}} the incompressible Stokes equations as a BIE.  This has the advantage that
-only the one-dimensional boundary of the domain must be discretized, and,
-\nick{with an appropriate quadrature formula and fast summation methods,
-the result is a high-fidelity numerical simulation of near-optimal computational complexity.}
+Since we require an accurate solution of the incompressible Stokes
+equations in complex two-dimensional geometries, we reformulate the
+incompressible Stokes equations as a BIE.  This has the advantage that
+only the one-dimensional boundary of the domain must be discretized,
+and, with an appropriate quadrature formula and fast summation methods,
+the result is a high-fidelity numerical simulation of near-optimal
+computational complexity.
 
@@
 \end{align}
-where $D$ is \nick{\st{an} a} kernel of the integral operator, $\rr = \xx - \yy$,
-$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  The double-layer potential can not
-represent all solutions of the incompressible Stokes equations, so we
-complete the integral equation formulation by adding the Stokeslets and
-rotlets~\cite{pow-mir1987}
+where $D$ is \nick{\st{an} a} kernel of the integral operator, $\rr =
+\xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$,
+and $\eeta$ is an unknown density function.  The double-layer potential
+can not represent all solutions of the incompressible Stokes equations,
+so we complete the integral equation formulation by adding the $M$
+Stokeslets and rotlets~\cite{pow-mir1987}
 \begin{align}
@@
 \end{subequations}
-The operator $\NN_0$ is the integral operator with kernel
-$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$,
-which removes the rank one null space \nick{\st{resulting} that results} from the flux-free
-requirement of $\ff$.  In this work, $\ff$ is the prescribed velocity,
-$\UU$, on the outer wall, $\Gamma$, and is zero on the eroding bodies,
-$\gamma_\ell$, $\ell=1,\ldots,M$.
+Here, the null space associated with the flux-free condition of $\ff$ is
+addressed with the integral operator $\NN_0$ which has the integral
+kernel $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.
+In this work, $\ff$ is the prescribed velocity, $\UU$, on the outer
+wall, $\Gamma$, and is zero on the eroding bodies, $\gamma_\ell$,
+$\ell=1,\ldots,M$.
 
@@
 \end{align}
-\nick{\st{We require the deformation tensor of the double-layer potential at
-$\xx \in \bd \Omega$.}}
-Since the deformation tensor of the double-layer potential is discontinuous across the boundary $\bd\Omega$, the jump term 
+respectively.  Since the deformation tensor of the double-layer
+potential is discontinuous across $\bd\Omega$, the jump term 
 \begin{align}
@@
 \end{align}
-must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
-Stokeslets and rotlets \nick{do not exhibit such jumps, and so the associated components of the deformation tensor, pressure, and vorticity} are straightforward to compute~\cite{poz1992}.
-Having computed
-the deformation tensor on $\gamma$, the shear stress is computed as
-defined in equation~\eqref{eqn:shearStress}.
+must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.
+Finally, the Stokeslets and rotlets do not exhibit any jumps
+across $\gamma$, and so the associated components of the deformation tensor, pressure, and vorticity due to the Stokeslets
+and rotlets are straightforward to compute~\cite{poz1992}.  Having
+computed the deformation tensor on $\gamma$, the shear stress is
+computed as defined in equation~\eqref{eqn:shearStress}.
 

### 2019-10-01 docs/transport/erosion_transport.tex
leaving off at start of sec 3.2

@@
 
-%Flow in porous media is further complicated when there is a two-way coupling between the flow and the geometry. For example, the grains of a porous media evolve in time in applications involving
-\nick{Flow in porous media is further complicated when boundaries evolve dynamically in response to the fluid flow.
-This type of coupling between geometry and flow occurs, for example, in applications involving} melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
-hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and crack
+Flow in porous media is further complicated when boundaries dynamically
+evolve in response to the fluid flow. This type of coupling between the
+geometry and the flow occurs, for example, in applications involving
+melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular,
+favier2019rayleigh, morrow2019moving},
+dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017,
+wykes2018self}, deposition~\cite{joh-eli1995, hewett2018modelling},
+biofilm growth~\cite{tan-val-wer2015}, and crack
 formation~\cite{cho2019crack}. We focus on erosion, a fluid-mechanical
 process that is prevalent in many geophysical, hydrological, and
-industrial applications~\cite{berhanu2012shape, hewett2017evolution, lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
-When a porous geometry erodes, certain qualitative characteristics are unveiled that affect transport through the geometry.
-For example, an eroded geometry may
-contain channels of high porosity, which, though few in number and
-modest in volume fraction, transmit a large portion of the flux. This
-arrangement results in velocities that vary over several orders of
-magnitude~\cite{all-hea-lab-rei2002}.  \nick{Moreover, channelization creates heterogeneous and anisotropic medium properties, which affect the
-transport of tracers} such as contaminants~\cite{cve-che-wen1996,
-dag1987, kon-bre1978} and heat~\cite{nil-sto1990, ree-sto1995}.
+industrial applications~\cite{berhanu2012shape, hewett2017evolution,
+lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
+When a porous geometry erodes, certain qualitative characteristics are
+unveiled that affect transport through the geometry.  For example, an
+eroded geometry may contain channels of high porosity, which, though few
+in number and modest in volume fraction, transmit a large portion of the
+flux. This arrangement results in velocities that vary over several
+orders of magnitude~\cite{all-hea-lab-rei2002}.  Moreover,
+channelization creates heterogeneous and anisotropic medium properties,
+which affect the transport of tracers such as
+contaminants~\cite{cve-che-wen1996, dag1987, kon-bre1978} and
+heat~\cite{nil-sto1990, ree-sto1995}.
 
 This study consists of two main undertakings: first, high-fidelity
-simulations of eroding porous media, and, second, \nick{characterization of tracer transport through the dynamic geometries that result}.
-Our modeling efforts build on previous work~\cite{ris-moo-chi-she-zha2012, moore2013self, moo2017}, in particular recent numerical methods developed to simulate erosion in the regime of Stokes flow~\cite{qua-moo2018}.
-We, however, make a few
-key improvements to the numerical methods from~\cite{qua-moo2018} to
-enable simulations of more realistic, dense suspensions of eroding
-grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To characterize transport through these \nick{configurations}, we examine
+simulations of eroding porous media, and, second, characterization of
+tracer transport through the resulting eroded geometries. Our modeling
+efforts build on previous work~\cite{ris-moo-chi-she-zha2012,
+moore2013self, moo2017}, in particular recent numerical methods
+developed to simulate erosion in the regime of Stokes flow
+regime~\cite{qua-moo2018}. We, however, make key improvements to the
+numerical methods from~\cite{qua-moo2018} to enable simulations of more
+realistic, dense suspensions of eroding grains
+(Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To
+characterize transport through these configurations, we examine
 coarse-grained variables through statistical analysis of tracer
@@
 method applied to the {\thL} coordinates~\cite{hou-low-she1994} of the
-eroding grains.  In this work, we \nick{\st{do}} introduce a new quadrature method to resolve dense suspensions of eroding grains.  The accuracy of the
-trapezoid rule, which we used in our previous work, is \st{sufficient} \nick{adequate} for bodies that are sufficiently separated~\cite{tre-wei2014}. 
-\todo[inline]{I changed the above to `adequate' so that `sufficient' would not be used twice in a row.} 
-However, it \nick{loses accuracy whenever \st{two} grains come in close contact}.
-One of the earliest works \nick{to address} quadrature methods for nearly-singular integrands was developed by Baker and Shelley~\cite{bak-she1986}, and in recent years, many other near-singular integration schemes have been \nick{followed}~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016, bea-lai2001, klo-bar-gre-one2013}.
-We use a Barycentric quadrature
-\nick{method}~\cite{bar2014, bar-wu-vee2015} since it is a non-intrusive
+eroding grains.  In this work, we introduce a new quadrature method to
+resolve dense suspensions of eroding grains.  The accuracy of the
+trapezoid rule, which we used in our previous work, is adequate for
+bodies that are sufficiently separated~\cite{tre-wei2014}.  However, it
+loses accuracy whenever grains are in close contact.  One of the
+earliest works to address quadrature methods for nearly-singular
+integrands was developed by Baker and Shelley~\cite{bak-she1986}, and in
+recent years, many other near-singular integration schemes have
+followed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
+bea-lai2001, klo-bar-gre-one2013}.  We use a Barycentric quadrature
+method~\cite{bar2014, bar-wu-vee2015} since it is a non-intrusive
 modification of the trapezoid rule, and the error is guaranteed to be
-uniformly bounded.  We extend the original quadrature method \nick{to compute the velocity gradient, which is needed to evaluate shear stress and fluid vorticity}.
+uniformly bounded.  We extend the original quadrature method to compute
+the velocity gradient, which is needed to evaluate shear stress and
+fluid vorticity.
 
@@
 
-To characterize the transport, particle trajectories \nick{must} be
-computed. Depending on the application, microscale transport can be
-modelled as pure advection~\cite{dea-qua-bir-jua2018,
-leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019},
+To characterize the transport, particle trajectories must be computed.
+Depending on the application, microscale transport can be modelled as
+pure advection~\cite{dea-qua-bir-jua2018, leb-ded-dav-bou2007,
+cve-che-wen1996, puy-gou-den2019},
 advection-diffusion~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
 with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
-this work, we assume trajectories \nick{to be governed by pure advection} (ie.~no diffusion). Therefore, the particle trajectories are
-identical to the streamlines, and they can be found, for example, with a
-continuous time random walk~\cite{mon-wei1965, den-cor-sch-ber2004,
-leb-den-car2008, ber-cor-den-sch2006}.  
-\todo[inline]{The logic from the sentence above to the one below seems awkward to me.
-The above sentence makes me think that a continuous time random-walk will be used in our paper.
-Then, suddenly, we say we are going to do something else instead.
-Maybe we can kill the above sentence and dump the references (if you want to keep them) into the earlier sentence that mentions a random walk?
-Or maybe just a slight rephrasing would make the transition less awkward.}
-Instead,  we compute
-trajectories $\ss(t)$ that are initialized at $\ss_0$ by solving
+this work, we assume trajectories to be governed by pure advection
+(ie.~no diffusion), so the particle trajectories are identical to the
+streamlines. We compute trajectories $\ss(t)$ that are initialized at
+$\ss_0$ by solving the advection equation
 \begin{align}
@@
 used to accurately compute trajectories that are close to an eroding
-grain.
-
-Once \nick{the streamlines are computed, we characterize
-transport by analyzing} three different metrics: the tortuosity, the anomalous dispersion, and the pore size distribution. 
-The local tortuosity of a streamline \nick{that connects the inlet to the outlet is defined as the streamline's length normalized by the linear inlet-to-outlet distance}.
-In porous media, the local tortuosity can be greater than 1.5~\cite{kop-kat-tim1996, mat-kha-koz2008} or even 2~\cite{dud-koz-mat2011}, \nick{depending on several factors such as the porosity.} 
-The tortuosity of a geometry is defined by averaging the local tortuosity over all streamlines initialized at the inlet, and the geometry's tortuosity characterizes average particle motions~\cite{hak-com-den2019}.
-To characterize spreading, the fluid dispersion is computed by calculating the variance of the streamline lengths.
-In porous media, this spreading is often
+grain. We note that an alternative approach to compute trajectories is
+to form a distribution of velocities $\uu$ and use a continuous time
+random walk~\cite{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
+ber-cor-den-sch2006}.
+
+Once the streamlines are computed, we characterize transport by
+analyzing three different metrics: the tortuosity, the anomalous
+dispersion, and the pore size distribution.  The local tortuosity of a
+streamline that connects the inlet to the outlet is defined as the
+streamline's length normalized by the linear inlet-to-outlet distance.
+In porous media, the local tortuosity can be greater than
+1.5~\cite{kop-kat-tim1996, mat-kha-koz2008} or even
+2~\cite{dud-koz-mat2011}, depending on several factors such as the
+porosity. The tortuosity of a geometry is defined by averaging the local
+tortuosity over all streamlines initialized at the inlet, and the
+geometry's tortuosity characterizes average particle
+motions~\cite{hak-com-den2019}.  To characterize spreading, the fluid
+dispersion is computed by calculating the variance of the streamline
+lengths. In porous media, this spreading is often
 super-dispersive~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
-dea-leb-den-tar-bol-dav2013}. \nick{Since anomalous dispersion results from streamlines spending time in both the high and low velocity}
-regimes~\cite{ber-sch2001}, it is crucial to accurately resolve  streamlines near grain boundaries, as achieved in this work.
-Finally, \nick{the distribution of pore sizes is required to} quantify velocity distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018}, channelization~\cite{sie-ili-pri-riv-gua2019}, connectivity~\cite{knu-car2005, wes-blo-gra2001}, and to develop network models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
-\nick{Hence, we construct the pore-size distribution throughout the erosion process.}
+dea-leb-den-tar-bol-dav2013}. Since anomalous dispersion results from
+streamlines spending time in both the high and low velocity
+regimes~\cite{ber-sch2001}, it is crucial to accurately resolve
+streamlines near grain boundaries, as achieved in this work.  Finally,
+the distribution of pore sizes is required to quantify velocity
+distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
+channelization~\cite{sie-ili-pri-riv-gua2019},
+connectivity~\cite{knu-car2005, wes-blo-gra2001}, and to develop network
+models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}. Hence, we
+construct the pore-size distribution throughout the erosion process.
 
@@
 Our first contribution is extending the Barycentric quadrature rule of
-Barnett et al.~\cite{bar-wu-vee2015} \nick{to accurately compute velocity gradients associated with Stokes flow.}
-\nick{This new quadrature rule permits accurate and stable simulations of erosion, and, moreover, enables visualization of the vorticity field throughout.}
+Barnett et al.~\cite{bar-wu-vee2015} to accurately compute velocity
+gradients associated with Stokes flow. This new quadrature rule permits
+accurate and stable simulations of erosion, and, moreover, enables
+visualization of the vorticity field throughout.
 
 Our second contribution is computing and analyzing trajectories in
-eroded geometries.  These trajectories are used to characterize the
-transport by computing the local tortuosity of trajectories, and the
-tortuosity and dispersion rate of eroded geometries. By using the
-Barycentric quadrature rule and a fourth-order Runge-Kutta method, we
-accurately compute trajectories that spend large amounts of time in the
-slow velocity regions near the eroding bodies, a necessity to
-characterize the flow~\cite{dea-leb-den-tar-bol-dav2013}.  We compare
-our tortuosity and dispersion rates with models available in the
-literature.  Finally, we analyze the effect of erosion on the pore size
+eroded geometries.  These trajectories are formed by combining the
+Barycentric quadrature rule and a fourth-order Runge-Kutta method. Then,
+they are used to compute tortuosities and dispersion rates of eroded
+geometries. Finally, we analyze the effect of erosion on the pore size
 distribution.
-
-\todo[inline]{The above paragraph seems to repeat a lot of what has been mentioned already, but maybe that is okay.}
 
@@
 As in our previous work~\cite{qua-moo2018}, we consider two-dimensional
-immobile eroding grains. However, this work \nick{does not limit} the proximity of  grains. Compared to our previous work, we are able to
-simulate much denser suspensions with a comparable number of
-discretization points and without upsampling.  While we do investigate
-transport in this work, we only consider passive particles that are
-advected by the flow.  To model other physical processes, such as
-contaminant transport, we plan to simulate a finite Peclet number
-advection-diffusion equation in eroded geometries.
+immobile eroding grains. However, this work does not limit the proximity
+of  grains. Compared to our previous work, we are able to simulate much
+denser suspensions with a comparable number of discretization points and
+without upsampling.  While we do investigate transport in this work, we
+only consider passive particles that are advected by the flow.  To model
+other physical processes, such as contaminant transport, we plan to
+simulate a finite Peclet number advection-diffusion equation in eroded
+geometries.
 
@@
 \paragraph{Outline of the Paper}
-In Section~\ref{sec:formulation}, we summarize the erosion model \nick{that is described in more detail in} previous work~\cite{qua-moo2018}.  In
+In Section~\ref{sec:formulation}, we summarize the erosion model that is
+described in more detail in previous work~\cite{qua-moo2018}.  In
 Section~\ref{sec:DLP}, we recast all the governing equations as layer
@@
 the numerical methods, with special attention paid to the new quadrature
-method \nick{for computing} shear stress and vorticity.
+method for computing the shear stress and the vorticity.
 Section~\ref{sec:results} presents numerical examples for a variety of
@@
 We start by defining the main variables used to model erosion.  We only
-\nick{briefly summarize the model, since a more detailed description can be found in previous} work~\cite{qua-moo2018}.
-We consider flows inside a confined geometry $\Omega$ that contains $M$ eroding bodies with boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$.
-\nick{The boundary of the fluid domain is $\bd \Omega = \Gamma \cup
-\gamma_1 \cup \cdots \cup \gamma_M$, where $\Gamma$ is the outer boundary, taken to be a slightly smoothed version of $[-3,3] \times [-1,1]$}. 
-\nick{We only place eroding bodies in $[-1,1] \times [-1,1]$ so as to create a buffer region for the flow profile imposed at the inlet to transition to the more complex flow intervening between the bodies}.
-On each
-eroding body, $\nn$ is the normal vector pointing into the body, and
-$\ss$ is the unit tangent vector pointing in the counterclockwise
-direction.  The normal vector on $\Gamma$ is the outward unit normal.
-Neglecting inertial forces, the governing equations are
+briefly summarize the model, and a more detailed description can be
+found in previous work~\cite{qua-moo2018}.  We consider flows inside a
+confined geometry $\Omega$ that contains $M$ eroding bodies with
+boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$.  The boundary of the
+fluid domain is $\bd \Omega = \Gamma \cup \gamma_1 \cup \cdots \cup
+\gamma_M$, where $\Gamma$ is the outer boundary, taken to be a slightly
+smoothed version of $[-3,3] \times [-1,1]$.  We only place eroding
+bodies in $[-1,1] \times [-1,1]$ so as to create a buffer region for the
+flow profile imposed at the inlet to transition to the more complex flow
+intervening between the bodies. On each eroding body, $\nn$ is the
+normal vector pointing into the body, and $\ss$ is the unit tangent
+vector pointing in the counterclockwise direction.  The normal vector on
+$\Gamma$ is the outward unit normal.  Neglecting inertial forces, the
+governing equations are
 \begin{equation}
@@
 \end{align}
-is the shear stress on $\gamma$.  The strength of $\UU$ is adjusted at
-each time step \nick{to achieve} a constant pressure drop across the
-channel.  We simulate erosion by alternating between solving the fluid
-equations and advancing the grains according to the erosion rate for a
-small time step.
+is the shear stress on $\gamma$. We simulate erosion by alternating
+between solving the fluid equations nd advancing the grains according to
+the erosion rate for a small time step. The strength of $\UU$ is
+adjusted at each time step to achieve a constant pressure drop across
+the channel.
 
@@
 and, with an appropriate quadrature formula and fast summation methods,
-the result is a high-fidelity numerical simulation of near-optimal
+the result is a high-fidelity numerical simulation with near-optimal
 computational complexity.
@@
 \end{align}
-where $D$ is \nick{\st{an} a} kernel of the integral operator, $\rr =
-\xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$,
-and $\eeta$ is an unknown density function.  The double-layer potential
-can not represent all solutions of the incompressible Stokes equations,
-so we complete the integral equation formulation by adding the $M$
-Stokeslets and rotlets~\cite{pow-mir1987}
+where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
+$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
+is an unknown density function.  The double-layer potential can not
+represent all solutions of the incompressible Stokes equations, so we
+complete the integral equation formulation by adding the $M$ Stokeslets
+and rotlets~\cite{pow-mir1987}
 \begin{align}
@@
   R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
+  \quad \ell=1,\ldots,M,
 \end{align}
@@
 Here, the null space associated with the flux-free condition of $\ff$ is
-addressed with the integral operator $\NN_0$ which has the integral
-kernel $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.
-In this work, $\ff$ is the prescribed velocity, $\UU$, on the outer
-wall, $\Gamma$, and is zero on the eroding bodies, $\gamma_\ell$,
-$\ell=1,\ldots,M$.
+addressed with the integral operator $\NN_0$ which is the integral
+operator with kernel $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$,
+$\xx,\yy \in \Gamma$.  In this work, $\ff$ is the prescribed velocity,
+$\UU$, on the outer wall, $\Gamma$, and is zero on the eroding bodies,
+$\gamma_\ell$, $\ell=1,\ldots,M$.
 
 Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
-Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, \nick{we are able to compute the deformation tensor, pressure, and vorticity, defined respectively as}
+Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, we are able to
+compute the deformation tensor, pressure, and vorticity, defined
+respectively as
 \begin{align}
@@
     \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
-      (\rr \cdot \eeta) \, ds_\yy,
-\end{align}
-respectively.  Since the deformation tensor of the double-layer
-potential is discontinuous across $\bd\Omega$, the jump term 
+      (\rr \cdot \eeta) \, ds_\yy.
+\end{align}
+Since the deformation tensor of the double-layer potential is
+discontinuous across $\bd\Omega$, the jump term 
 \begin{align}
@@
 \end{align}
-must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.
-Finally, the Stokeslets and rotlets do not exhibit any jumps
-across $\gamma$, and so the associated components of the deformation tensor, pressure, and vorticity due to the Stokeslets
-and rotlets are straightforward to compute~\cite{poz1992}.  Having
-computed the deformation tensor on $\gamma$, the shear stress is
-computed as defined in equation~\eqref{eqn:shearStress}.
+must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
+Stokeslets and rotlets do not exhibit any jumps across $\gamma$, so the
+associated components of the deformation tensor, pressure, and vorticity
+due to the Stokeslets and rotlets are straightforward to
+compute~\cite{poz1992}.  Having computed the deformation tensor on
+$\gamma$, the shear stress is computed as defined in
+equation~\eqref{eqn:shearStress}.
 
@@
 Section~\ref{sec:method} requires a complex-valued representation of the
-layer potentials. The first step is to write the Laplace double-layer
-potential as the complex integral
+layer potentials. The first step to find such a representation is to
+write the Laplace double-layer potential as the complex integral
 \begin{align}
@@
 \end{align}
-imposed on the outer wall. Mitchell and Spagnolie~\mit{spa-spa2017} did
+imposed on the outer wall. Mitchell and Spagnolie~\cite{mit-spa2017} did
 a similar three-dimensional experiment using a second-order quadrature

### 2019-10-01 docs/transport/erosion_transport.tex
finished up section 3

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Double-Layer Potential Formulation in $\RR^2$}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Applying the same approach as our previous work~\cite{qua-moo2018}, we
@@
 Section~\ref{sec:method} requires a complex-valued representation of the
-layer potentials. The first step to find such a representation is to
+layer potentials. The first step to form a complex representation is to
 write the Laplace double-layer potential as the complex integral
@@
     \text{where} \quad v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy,
+    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega,
   \label{eqn:laplaceComplex}
 \end{align}
-where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
-and $\eta$ is the complex-valued counterpart of $\eeta$.
+where $x,y \in \CC$ are the complex counterparts of $\xx,\yy \in \RR^2$,
+and $\eta$ is the complex counterpart of $\eeta$.
 Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
@@
 for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
-function $\eta$, we use the notation $v[\eta](x)$ to denote the
-holomorphic function defined in equation~\eqref{eqn:laplaceComplex}, and
-its first two derivatives are written as $v'[\eta](x)$ and
-$v''[\eta](x)$.
-
-To rewrite the Stokes double-layer potential~\eqref{eqn:velocityDLP} in
-terms of Cauchy integrals and their derivatives, we start by converting
-it into a sequence of Laplace layer potentials~\cite{bar-wu-vee2015}
+function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
+function defined in equation~\eqref{eqn:laplaceComplex}, and its first
+two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
+
+The Stokes double-layer potential~\eqref{eqn:velocityDLP} can be written
+as~\cite{bar-wu-vee2015}
 \begin{equation}
@@
 \end{align}
-and $n \in \CC$ is the complex representation of the outward unit normal
+and $n \in \CC$ is the complex counterpart of the outward unit normal
 $\nn \in \RR^2$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In addition to the velocity, we require a complex-valued layer potential representation
-of the gradient of the velocity so that we can compute the shear stress
-and the vorticity.  The deformation tensor at $x \in \Omega$ is found by
-computing the derivatives of $u_1$ and $u_2$ as defined in
+Computing the shear stress and vorticity requires a complex-valued layer
+potential representation of the gradient of the velocity.  The
+deformation tensor at $x \in \Omega$ is found by computing the
+derivatives of the expressions for $u_1$ and $u_2$ in
 equation~\eqref{eqn:cauchyVelocity}  

### 2019-10-01 docs/transport/erosion_transport.tex
small changes

@@
 fraction, flow rate, and the total drag.  However, to characterize
-transport, other quantities must be examined.  Here, we compute the
-anomalous dispersion rate, the tortuosity, and the distribution of the
-pore sizes.  The first two metrics can be defined in terms of
-streamlines governed by an advection autonomous
-equation~\eqref{eqn:tracers}.
+macroscopic signatures of the transport, other quantities must be
+examined.  Here, we compute the anomalous dispersion rate, the
+tortuosity, and the distribution of the pore sizes.  The first two
+metrics can be defined in terms of streamlines governed by an advection
+autonomous equation~\eqref{eqn:tracers}.
 
@@
 discretization points, and its center is chosen so that the distance
-between the body and the solid wall is $h/2$, $h/4$, and $h/10$, where
-$h = 2\pi r/N_\iin$.  If we used the trapezoid rule and required an
-error that is comparable to the Barycentric quadrature rule, the body
-with an initial distance of $h/10$ from the solid wall would require
-$6,400$ discretization points, and the outer wall would require $50,000$
+between the body and the solid wall is $h$, $h/2$, and $h/10$, where $h
+= 2\pi r/N_\iin$.  If we used the trapezoid rule and required an error
+that is comparable to the Barycentric quadrature rule, the body with an
+initial distance of $h/10$ from the solid wall would require $6,400$
+discretization points, and the outer wall would require $50,000$
 discretization points.
@@
 where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
-to $x=2$ is held fixed at 2.  Snapshots of the bodies at four equispaced
-times are shown in Figure~\ref{fig:Eroding20vort}.  The color is the
-vorticity, and the erosion rate is proportional to the vorticity.
-Initially, several of the eroding bodies are closer to the outer wall
-than the $5h$ threshold required to guarantee that the trapezoid rule
-achieves machine precision.  In particular, the distance between bodies
-1, 6, 13, and 15 and the outer wall is $1.3h$, $2.9h$, $2.8h$, and
-$1.3h$, respectively, where $h$ is the arclength spacing of the outer
-wall $\Gamma$.  In addition, the distance between several pairs of
-eroding bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and 14\& 18, is too
-small to be accurately resolved with the trapezoid rule.  By using the
-Barycentric quadrature rule, the interaction between these
-nearly-touching bodies can be accurately resolved at the prescribed
-resolution, and erosion can be simulated until all the bodies have
-vanished.
+to $x=2$ is held fixed at 8. Therefore, $U=1$ once all the bodies have
+vanished.  Snapshots of the bodies at four equispaced times are shown in
+Figure~\ref{fig:Eroding20vort}.  The color is the vorticity, and the
+erosion rate is proportional to the vorticity.  Initially, several of
+the eroding bodies are closer to the outer wall than the $5h$ threshold
+required to guarantee that the trapezoid rule achieves machine
+precision.  In particular, the distance between bodies 1, 6, 13, and 15
+and the outer wall is $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively,
+where $h$ is the arclength spacing of the outer wall $\Gamma$.  In
+addition, the distance between several pairs of eroding bodies,
+including 1 \& 6, 3 \& 9, 6 \& 8, and 14\& 18, is too small to be
+accurately resolved with the trapezoid rule.  By using the Barycentric
+quadrature rule, the interaction between these nearly-touching bodies
+can be accurately resolved at the prescribed resolution, and erosion can
+be simulated until all the bodies have vanished.
 
@@
 transitions from ballistic dynamics to asymptotic super-dispersive
-spreading.  In contrast to the lower porosity initial condition
+spreading.  In contrast to the higher porosity initial condition
 (Section~\ref{sec:Eroding20}), at early times the erosion results in a

### 2019-10-01 docs/transport/erosion_transport.tex
NM

@@
 in number and modest in volume fraction, transmit a large portion of the
-flux. This arrangement results in velocities that vary over several
+flux \cite{qua-moo2018}. This arrangement results in velocities that vary over several
 orders of magnitude~\cite{all-hea-lab-rei2002}.  Moreover,
@@
 moore2013self, moo2017}, in particular recent numerical methods
-developed to simulate erosion in the regime of Stokes flow
+developed to simulate erosion in the Stokes-flow
 regime~\cite{qua-moo2018}. We, however, make key improvements to the
@@
 ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  Since the
-vorticity and the shear stress are equivalent on the grains in the zero
-Reynolds number limit, we also compute the vorticity in the fluid bulk
-for visualization purposes (Figure~\ref{fig:Eroding50vort}).  A variety
-of numerical methods for the fluid solver are available including
+vorticity and the shear stress are equivalent on \nick{solid boundaries}, we also compute the fluid vorticity for visualization purposes (Figure~\ref{fig:Eroding50vort}).
+A variety of numerical methods for the fluid solver are available including
 lattice-gas or lattice Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998},
@@
 To compute stable simulations of erosion, we use high-order methods in
-both space and time. The time integration method is unchanged from our
+both space and time. The time integration method is unchanged from
 previous work~\cite{qua-moo2018}.  We apply a mild regularization and a
-smoothing term to eliminate numerical instabilities caused by changes in
+smoothing term to eliminate numerical instabilities that can be triggered by changes in
 sign of the shear stress, and we use a stable second-order Runge-Kutta
@@
 eroding grains.  In this work, we introduce a new quadrature method to
-resolve dense suspensions of eroding grains.  The accuracy of the
-trapezoid rule, which we used in our previous work, is adequate for
+resolve dense suspensions.  The accuracy of the
+trapezoid rule, which was used in previous work, is adequate for
 bodies that are sufficiently separated~\cite{tre-wei2014}.  However, it
@@
 
-To characterize the transport, particle trajectories must be computed.
-Depending on the application, microscale transport can be modelled as
+To characterize transport \nick{through the resulting configurations}, particle trajectories must be computed. Depending on the application, microscale transport can be modelled as
 pure advection~\cite{dea-qua-bir-jua2018, leb-ded-dav-bou2007,
@@
 they are used to compute tortuosities and dispersion rates of eroded
-geometries. Finally, we analyze the effect of erosion on the pore size
+geometries. Finally, we examine the effect of erosion on the pore size
 distribution.
@@
 is the shear stress on $\gamma$. We simulate erosion by alternating
-between solving the fluid equations nd advancing the grains according to
+between solving the fluid equations \nick{and} advancing the grains according to
 the erosion rate for a small time step. The strength of $\UU$ is

### 2019-10-01 docs/transport/erosion_transport.tex
NM

@@
 is the shear stress on $\gamma$. We simulate erosion by alternating
-between solving the fluid equations \nick{and} advancing the grains according to
-the erosion rate for a small time step. The strength of $\UU$ is
-adjusted at each time step to achieve a constant pressure drop across
+between solving the fluid equations \nick{and} advancing the \nick{erodible boundaries}. The strength of $\UU$ is adjusted at each time step to achieve a constant pressure drop across
 the channel.
@@
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  The double-layer potential can not
+is an unknown density function.  The double-layer potential \nick{cannot}
 represent all solutions of the incompressible Stokes equations, so we
@@
 Here, the null space associated with the flux-free condition of $\ff$ is
-addressed with the integral operator $\NN_0$ which is the integral
-operator with kernel $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$,
-$\xx,\yy \in \Gamma$.  In this work, $\ff$ is the prescribed velocity,
-$\UU$, on the outer wall, $\Gamma$, and is zero on the eroding bodies,
-$\gamma_\ell$, $\ell=1,\ldots,M$.
+addressed with \nick{\st{the integral operator}} $\NN_0$ which is the integral
+operator having kernel $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$,
+$\xx,\yy \in \Gamma$.  In this work, $\ff$ is the prescribed velocity, \nick{which is equal to  $\UU$ on the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
+$\gamma_\ell$, $\ell=1,\ldots,M$.}
 
@@
 compute~\cite{poz1992}.  Having computed the deformation tensor on
-$\gamma$, the shear stress is computed as defined in
+$\gamma$, the shear stress is computed using
 equation~\eqref{eqn:shearStress}.
@@
     \text{where} \quad v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega,
+    \frac{\eta(y)}{x - y} \, dy, \quad x \in \nick{ \CC(\Omega) },
   \label{eqn:laplaceComplex}
@@
 where $x,y \in \CC$ are the complex counterparts of $\xx,\yy \in \RR^2$,
-and $\eta$ is the complex counterpart of $\eeta$.
+and $\eta$ the complex counterpart of $\eeta$. \nick{We use the notation $\CC(\Omega)$ to denote the physical domain $\Omega$ represented in complex coordinates.}
+\todo[inline]{What do you think of this notation I introduced to distinguish between $\Omega$ as a real versus complex domain?
+I was skimming over this section and was very confused about what $x$ and $y$ were, having naively assumed they were physical $x$ and $y$ coordinates instead of complex numbers.
+Hence I wanted to make their definitions more prominent.
+I realize that you state $x$ and $y$ are complex numbers, but it is in the text and could be missed by the careless reader (i.e.
+me).}
 Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
-first finding the boundary data of $v$.  Assuming that $\Omega$ is a
+first finding the boundary data of $v$.  Assuming that $\nick{\CC(\Omega)}$ is a
 simply-connected interior domain, the boundary data of $v$ satisfies the
@@
   v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
+    \frac{\eta(y)}{x-y}\, dy, \quad x \in \nick{\CC(\bd\Omega)}.
 \end{align}
@@
 \end{align}
-for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
+for $x \in \nick{\CC(\Omega)}$.  Since $v(x)$ depends on the complex-valued density
 function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
@@
 Computing the shear stress and vorticity requires a complex-valued layer
-potential representation of the gradient of the velocity.  The
+potential representation of the \nick{velocity gradient}.  The
 deformation tensor at $x \in \Omega$ is found by computing the
@@
 the shear stress, the deformation tensor on $\bd\Omega$ is applied to
-the normal and tangent vectors as defined in
-equation~\eqref{eqn:shearStress}.  The gradient of the velocity field is
+the normal and tangent vectors as in
+equation~\eqref{eqn:shearStress}.  The \nick{velocity gradient} is
 also used to compute the vorticity in the fluid bulk.  For $x \in
-\Omega$, the Cauchy integral representation of the vorticity is
+\nick{\CC(\Omega)}$, the Cauchy integral representation of the vorticity is
 \begin{align}
@@
 work of others~\cite{dea-qua-bir-jua2018, puy-gou-den2019}, once a
-particle reaches the end of the porous region, it is reinserted at the
-start of the porous region.  To minimize errors caused by reinsertion,
-the particle is initialized at the discretization point that has the
-closest velocity to the particle's velocity at the outlet.  After a
+particle reaches the \nick{outlet} of the porous region, it is reinserted at the \nick{inlet}.
+To minimize errors caused by reinsertion, the particle is initialized at the discretization point that has the closest velocity to the particle's velocity at the outlet.
+After a
 single trajectory is formed, it has undergone a collection of
@@
 defined, and Duda et al.~\cite{dud-koz-mat2011} summarize several
-options. One choice, that we adopt, uses streamlines that originate at
-$S$ and terminate at a parallel cross-section.  We use the
+options.  
+\todo[inline]{What does it mean `how streamlines are defined'?
+I had thought that the definition of a streamline is unambiguous.
+Do you mean which streamlines are used?
+i.e.~If there is a bias towards either shorter or longer streamlines?}
+\nick{\st{One choice, that we adopt, uses }} The choice adopted here is to use
+streamlines that originate at $S$ and terminate at a parallel cross-section.  We use the
 cross-sections $x=-1$ and $x=1$ that are at the start and end of the
@@
 formed.
+
+\todo[inline]{This figure seemed out of place to me because you do not present in other graphs yet, only the distribution of pores, and it is before the numerical methods are explained.
+HOWEVER, I think I see what you are driving towards: I think you want to give the reader a little teaser of the results, so that they are more inclined to make it through the methods section without losing interest (is that more or less right?).
+So perhaps just a few words to indicate our intent would prevent the reader from getting whiplash; maybe phrases like ``As illustration of the statistical results that will be elaborated in Section blah, we show here....''
+}
 

### 2019-10-01 docs/transport/erosion_transport.tex
NM

@@
 I realize that you state $x$ and $y$ are complex numbers, but it is in the text and could be missed by the careless reader (i.e.
-me).}
+me).
+However, I am not married to this notation and could easily be convinced just to leave it as you had it.}
 Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
@@
 
-\todo[inline]{This figure seemed out of place to me because you do not present in other graphs yet, only the distribution of pores, and it is before the numerical methods are explained.
+\todo[inline]{This figure seemed out of place to me because you do not present other graphs yet, only the distribution of pores, and it is before the numerical methods are explained.
 HOWEVER, I think I see what you are driving towards: I think you want to give the reader a little teaser of the results, so that they are more inclined to make it through the methods section without losing interest (is that more or less right?).
@@
 this equispacing is maintained for the entire simulation by using the
-{\thL} formulation.  In addition, we apply mild smoothing
-strategies~\cite{qua-moo2018} to avoid the corners that inevitably
-develop in erosion.
+{\thL} formulation.  In addition, we apply regularization~\cite{qua-moo2018} to \nick{\st{avoid} slightly smooth} the corners that inevitably develop during erosion.
+\todo[inline]{Note: We do not want to say that we avoid corners because that makes it sound like our numerical simulation fails to capture the real physical phenomenon of corner formation.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since we are applying quadrature to periodic smooth functions, the
-trapezoid rule is spectrally accurate~\cite{tre-wei2014}. However, since
+\st{Since we are applying quadrature to periodic smooth functions, the
+trapezoid rule is spectrally accurate. However, since
 the derivative of the integrands grows as the target point $\xx$
 approaches $\bd\Omega$, the error bound of the trapezoid rule depends on
-the location of the target point. Therefore, if the trapezoid rule, as
-described in Section~\ref{sec:spatialDiscretization}, is applied when
-bodies are in near-contact, or when a layer potential is evaluated at a
-point close to $\bd\Omega$, then the results become unreliable and the
-method ultimately becomes unstable.  Thus, we require a quadrature
-method with an error bound that is independent of the target location.
+the location of the target point.}
+\nick{While the trapezoid rule is spectrally accurate for smooth, periodic functions~\cite{tre-wei2014}, the derivative of the integrands grows as the target point $\xx$ approaches $\bd\Omega$ and so the error bound depends on the location of the target point.} Therefore, if the trapezoid rule is applied when bodies are in near-contact, or when a layer potential is evaluated at a point close to $\bd\Omega$, then the results become unreliable and the \nick{simulation} ultimately becomes unstable.
+We thus \nick{desire a quadrature method whose error bound does not depend on the target location}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this section, we apply our new quadrature method to simulate
+\nick{In this section, we apply our new quadrature method to simulate
 erosion of several different configurations of nearly-touching eroding
-bodies, and to characterize transport inside eroded geometries.  Each
-eroding body is initially a circle with center $\cc_i$ and radius $r_i$.
-The center and radius are chosen at random, and the body is accepted as
-long as it is contained in $[-1,1] \times [-1,1]$ and is sufficiently
+bodies, and to characterize transport inside eroded geometries.}
+\todo[inline]{This opening sentence is awkward and seems like a run-on sentence.}
+Each eroding body is initially a circle with center $\cc_i$ and radius $r_i$.
+The center and radius are chosen at random, and the body is accepted \nick{if} it is contained in $[-1,1] \times [-1,1]$ and is sufficiently
 separated from all other bodies.  Since the error of our quadrature
@@
 
-The erosion rate has a loss of regularity at stagnation points, and this
-inevitably leads to corners developing on the eroding bodies.
-Therefore, as described in Section~\ref{sec:formulation} and our
+The erosion rate \nick{\st{has a loss of regularity} loses regularity at stagnation points, which inevitably leads to corner formation on the bodies.} 
+As described in Section~\ref{sec:formulation} and our
 previous work~\cite{qua-moo2018}, we introduce a curvature penalization
-term and a Gaussian smoothing step.  For all examples, we use the
-smoothing parameters $\eps=15/256$ and $\sigma=10/256$, and the time
+term and a Gaussian smoothing step in order to ameliorate corner formation.  
+For all examples, we use the smoothing parameters $\eps=15/256$ and $\sigma=10/256$, and the time
 step size is $\Delta t = 10^{-4}$.
@@
   body close to the outer wall at $y=-1$.  We impose a shear flow
-  centered at $y=-1$, we compare the eroding body's shape to a similar
+  centered at $y=-1$ \nick{and} compare the eroding body's shape to a similar
   experiment of Spagnolie and Mitchell~\cite{mit-spa2017}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider a single eroding body close to a solid wall with the
+\nick{\st{We} First,} consider a single eroding body close to a solid wall with the
 shear flow
@@
 \end{align}
-imposed on the outer wall. Mitchell and Spagnolie~\cite{mit-spa2017} did
-a similar three-dimensional experiment using a second-order quadrature
-method. Here, they initialized the eroding body so that its center $1.5$
-times the body's radius above the solid wall.  In two dimensions, the
+imposed on the outer wall. Mitchell and Spagnolie~\cite{mit-spa2017} \nick{\st{did} performed} a similar three-dimensional experiment using a second-order quadrature
+method. \st{Here} They initialized the \st{eroding} body \st{so that} with its center located $1.5$ \nick{radii} above the solid wall.  In two dimensions, the
 trapezoid rule is spectrally accurate, and an analogous initial

### 2019-10-01 docs/transport/erosion_transport.tex
started fixing up nick's changes

@@
 ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  Since the
-vorticity and the shear stress are equivalent on \nick{solid boundaries}, we also compute the fluid vorticity for visualization purposes (Figure~\ref{fig:Eroding50vort}).
-A variety of numerical methods for the fluid solver are available including
-lattice-gas or lattice Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998},
-finite volumes~\cite{suo-liu-gan2019, den-ica-hid2018,
+vorticity and the shear stress are equivalent on solid boundaries, we
+also compute the fluid vorticity for visualization purposes
+(Figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
+the fluid solver are available including lattice-gas or lattice
+Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998}, finite
+volumes~\cite{suo-liu-gan2019, den-ica-hid2018,
 sie-ili-pri-riv-gua2019}, finite differences~\cite{leb-ded-dav-bou2007,
@@
 
-To characterize transport \nick{through the resulting configurations}, particle trajectories must be computed. Depending on the application, microscale transport can be modelled as
-pure advection~\cite{dea-qua-bir-jua2018, leb-ded-dav-bou2007,
-cve-che-wen1996, puy-gou-den2019},
+To characterize transport through the resulting configurations, particle
+trajectories must be computed. Depending on the application, microscale
+transport can be modelled as pure advection~\cite{dea-qua-bir-jua2018,
+leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019},
 advection-diffusion~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
@@
 is the shear stress on $\gamma$. We simulate erosion by alternating
-between solving the fluid equations \nick{and} advancing the \nick{erodible boundaries}. The strength of $\UU$ is adjusted at each time step to achieve a constant pressure drop across
-the channel.
+between solving the fluid equations and advancing the erodible
+boundaries. The strength of $\UU$ is adjusted at each time step to
+achieve a constant pressure drop across the channel.
 
@@
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  The double-layer potential \nick{cannot}
+is an unknown density function.  The double-layer potential cannot
 represent all solutions of the incompressible Stokes equations, so we
@@
 Here, the null space associated with the flux-free condition of $\ff$ is
-addressed with \nick{\st{the integral operator}} $\NN_0$ which is the integral
-operator having kernel $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$,
-$\xx,\yy \in \Gamma$.  In this work, $\ff$ is the prescribed velocity, \nick{which is equal to  $\UU$ on the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
-$\gamma_\ell$, $\ell=1,\ldots,M$.}
+addressed with  $\NN_0$ which is the integral operator having kernel
+$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
+this work, $\ff$ is the prescribed velocity, which is equal to $\UU$ on
+the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
+$\gamma_\ell$, $\ell=1,\ldots,M$.
 
@@
 Computing the shear stress and vorticity requires a complex-valued layer
-potential representation of the \nick{velocity gradient}.  The
-deformation tensor at $x \in \Omega$ is found by computing the
-derivatives of the expressions for $u_1$ and $u_2$ in
-equation~\eqref{eqn:cauchyVelocity}  
+potential representation of the velocity gradient.  The deformation
+tensor at $x \in \Omega$ is found by computing the derivatives of the
+expressions for $u_1$ and $u_2$ in equation~\eqref{eqn:cauchyVelocity}  
 \begin{equation}
@@
 the shear stress, the deformation tensor on $\bd\Omega$ is applied to
-the normal and tangent vectors as in
-equation~\eqref{eqn:shearStress}.  The \nick{velocity gradient} is
-also used to compute the vorticity in the fluid bulk.  For $x \in
-\nick{\CC(\Omega)}$, the Cauchy integral representation of the vorticity is
+the normal and tangent vectors as in equation~\eqref{eqn:shearStress}.
+The velocity gradient is also used to compute the vorticity in the fluid
+bulk.  For $x \in \nick{\CC(\Omega)}$, the Cauchy integral
+representation of the vorticity is
 \begin{align}
@@
 work of others~\cite{dea-qua-bir-jua2018, puy-gou-den2019}, once a
-particle reaches the \nick{outlet} of the porous region, it is reinserted at the \nick{inlet}.
-To minimize errors caused by reinsertion, the particle is initialized at the discretization point that has the closest velocity to the particle's velocity at the outlet.
-After a
-single trajectory is formed, it has undergone a collection of
-reinsertions.  Therefore, as a post-processing step, the trajectory is
-made continuous by attaching the tail of each segment to the origin of
-the next segment.
+particle reaches the outlet of the porous region, it is reinserted at
+the inlet.  To minimize errors caused by reinsertion, the particle is
+initialized at the discretization point that has the closest velocity to
+the particle's velocity at the outlet.  After a single trajectory is
+formed, it has undergone a collection of reinsertions.  Therefore, as a
+post-processing step, the trajectory is made continuous by attaching the
+tail of each segment to the origin of the next segment.
 
@@
 this equispacing is maintained for the entire simulation by using the
-{\thL} formulation.  In addition, we apply regularization~\cite{qua-moo2018} to \nick{\st{avoid} slightly smooth} the corners that inevitably develop during erosion.
-\todo[inline]{Note: We do not want to say that we avoid corners because that makes it sound like our numerical simulation fails to capture the real physical phenomenon of corner formation.}
+{\thL} formulation.  In addition, we apply
+regularization~\cite{qua-moo2018} to slightly smooth the corners that
+inevitably develop during erosion.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\st{Since we are applying quadrature to periodic smooth functions, the
-trapezoid rule is spectrally accurate. However, since
-the derivative of the integrands grows as the target point $\xx$
-approaches $\bd\Omega$, the error bound of the trapezoid rule depends on
-the location of the target point.}
-\nick{While the trapezoid rule is spectrally accurate for smooth, periodic functions~\cite{tre-wei2014}, the derivative of the integrands grows as the target point $\xx$ approaches $\bd\Omega$ and so the error bound depends on the location of the target point.} Therefore, if the trapezoid rule is applied when bodies are in near-contact, or when a layer potential is evaluated at a point close to $\bd\Omega$, then the results become unreliable and the \nick{simulation} ultimately becomes unstable.
-We thus \nick{desire a quadrature method whose error bound does not depend on the target location}.
+While the trapezoid rule is spectrally accurate for smooth, periodic
+functions~\cite{tre-wei2014}, the derivative of the integrands grows as
+the target point $\xx$ approaches $\bd\Omega$ and so the error bound
+depends on the location of the target point. Therefore, if the trapezoid
+rule is applied when bodies are in near-contact, or when a layer
+potential is evaluated at a point close to $\bd\Omega$, then the results
+become unreliable and the simulation ultimately becomes unstable.  We
+thus desire a quadrature method whose error bound does not depend on the
+target location.
 
@@
 bodies, and to characterize transport inside eroded geometries.}
-\todo[inline]{This opening sentence is awkward and seems like a run-on sentence.}
-Each eroding body is initially a circle with center $\cc_i$ and radius $r_i$.
-The center and radius are chosen at random, and the body is accepted \nick{if} it is contained in $[-1,1] \times [-1,1]$ and is sufficiently
-separated from all other bodies.  Since the error of our quadrature
-method is bounded independent of the geometry, we consider bodies that
-are separated by less than 10\% of an arclength spacing.  The randomized
-method is repeated until the initial geometry reaches a desired initial
-porosity.
+\todo[inline]{This opening sentence is awkward and seems like a run-on
+sentence.} Each eroding body is initially a circle with center $\cc_i$
+and radius $r_i$.  The center and radius are chosen at random, and the
+body is accepted if it is contained in $[-1,1] \times [-1,1]$ and is
+sufficiently separated from all other bodies.  Since the error of our
+quadrature method is bounded independent of the geometry, we consider
+bodies that are separated by less than 10\% of an arclength spacing.
+The randomized method is repeated until the initial geometry reaches a
+desired initial porosity.
 
@@
 
-The erosion rate \nick{\st{has a loss of regularity} loses regularity at stagnation points, which inevitably leads to corner formation on the bodies.} 
-As described in Section~\ref{sec:formulation} and our
-previous work~\cite{qua-moo2018}, we introduce a curvature penalization
-term and a Gaussian smoothing step in order to ameliorate corner formation.  
-For all examples, we use the smoothing parameters $\eps=15/256$ and $\sigma=10/256$, and the time
+The erosion rate loses regularity at stagnation points, which inevitably
+leads to corner formation on the bodies.  As described in
+Section~\ref{sec:formulation} and our previous work~\cite{qua-moo2018},
+we introduce a curvature penalization term and a Gaussian smoothing step
+in order to ameliorate corner formation.  For all examples, we use the
+smoothing parameters $\eps=15/256$ and $\sigma=10/256$, and the time
 step size is $\Delta t = 10^{-4}$.
@@
   body close to the outer wall at $y=-1$.  We impose a shear flow
-  centered at $y=-1$ \nick{and} compare the eroding body's shape to a similar
+  centered at $y=-1$ and compare the eroding body's shape to a similar
   experiment of Spagnolie and Mitchell~\cite{mit-spa2017}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\nick{\st{We} First,} consider a single eroding body close to a solid wall with the
+First, consider a single eroding body close to a solid wall with the
 shear flow
@@
 \end{align}
-imposed on the outer wall. Mitchell and Spagnolie~\cite{mit-spa2017} \nick{\st{did} performed} a similar three-dimensional experiment using a second-order quadrature
-method. \st{Here} They initialized the \st{eroding} body \st{so that} with its center located $1.5$ \nick{radii} above the solid wall.  In two dimensions, the
-trapezoid rule is spectrally accurate, and an analogous initial
-configuration is possible. However, unless the number of discretization
-points is increased, the trapezoid rule becomes obsolete if the eroding
-body is initialized closer to the solid wall. Therefore, to simulate
-erosion near a solid wall at reasonable levels of discretization, we use
-our hybrid method that combines the trapezoid rule and the Barycentric
-quadrature rule.
+imposed on the outer wall. Mitchell and Spagnolie~\cite{mit-spa2017}
+performed a similar three-dimensional experiment using a second-order
+quadrature method.  They initialized the \st{eroding} body \st{so that}
+with its center located $1.5$ radii above the solid wall.  In two
+dimensions, the trapezoid rule is spectrally accurate, and an analogous
+initial configuration is possible. However, unless the number of
+discretization points is increased, the trapezoid rule becomes obsolete
+if the eroding body is initialized closer to the solid wall. Therefore,
+to simulate erosion near a solid wall at reasonable levels of
+discretization, we use our hybrid method that combines the trapezoid
+rule and the Barycentric quadrature rule.
 
@@
 addition, the distance between several pairs of eroding bodies,
-including 1 \& 6, 3 \& 9, 6 \& 8, and 14\& 18, is too small to be
+including 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18, is too small to be
 accurately resolved with the trapezoid rule.  By using the Barycentric
@@
 velocities are plotted in Figure~\ref{fig:Eroding100tort}(a) for the
-eroded geometry at porosity $\phi = 63.0\%$
+eroded geometry at porosity $\phi = 63.0\%$ \todo[inline]{Make
+consistent with caption in figu 13 and another caption somwhere else in
+this section}
 (Figure~\ref{fig:Eroding100tort}(c)).  The initial velocity of the

### 2019-10-02 docs/transport/erosion_transport.tex
finished up nick's comments

@@
     \text{where} \quad v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy, \quad x \in \nick{ \CC(\Omega) },
+    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega,
   \label{eqn:laplaceComplex}
 \end{align}
-where $x,y \in \CC$ are the complex counterparts of $\xx,\yy \in \RR^2$,
-and $\eta$ the complex counterpart of $\eeta$. \nick{We use the notation $\CC(\Omega)$ to denote the physical domain $\Omega$ represented in complex coordinates.}
-\todo[inline]{What do you think of this notation I introduced to distinguish between $\Omega$ as a real versus complex domain?
-I was skimming over this section and was very confused about what $x$ and $y$ were, having naively assumed they were physical $x$ and $y$ coordinates instead of complex numbers.
-Hence I wanted to make their definitions more prominent.
-I realize that you state $x$ and $y$ are complex numbers, but it is in the text and could be missed by the careless reader (i.e.
-me).
-However, I am not married to this notation and could easily be convinced just to leave it as you had it.}
+where $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
+counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
+\eta_1 + i \eta_2$ is the complex counterpart of $\eeta =
+(\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
+potential, the space $\Omega$ can be interpreted as a subset of $\RR^2$
+or the corresponding subset of $\CC$.
 Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
-first finding the boundary data of $v$.  Assuming that $\nick{\CC(\Omega)}$ is a
+first finding the boundary data of $v$.  Assuming that $\Omega$ is a
 simply-connected interior domain, the boundary data of $v$ satisfies the
@@
   v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x-y}\, dy, \quad x \in \nick{\CC(\bd\Omega)}.
+    \frac{\eta(y)}{x-y}\, dy, \quad x \in \Omega.
 \end{align}
@@
 \end{align}
-for $x \in \nick{\CC(\Omega)}$.  Since $v(x)$ depends on the complex-valued density
+for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
 function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
@@
 The velocity gradient is also used to compute the vorticity in the fluid
-bulk.  For $x \in \nick{\CC(\Omega)}$, the Cauchy integral
-representation of the vorticity is
+bulk.  For $x \in \Omega$, the Cauchy integral representation of the
+vorticity is
 \begin{align}
@@
 
-The tortuosity definition depends on how the streamlines are
-defined, and Duda et al.~\cite{dud-koz-mat2011} summarize several
-options.  
-\todo[inline]{What does it mean `how streamlines are defined'?
-I had thought that the definition of a streamline is unambiguous.
-Do you mean which streamlines are used?
-i.e.~If there is a bias towards either shorter or longer streamlines?}
-\nick{\st{One choice, that we adopt, uses }} The choice adopted here is to use
-streamlines that originate at $S$ and terminate at a parallel cross-section.  We use the
-cross-sections $x=-1$ and $x=1$ that are at the start and end of the
-porous region.  This choice of averaging allows us to also compute the
-tortuosity in terms of an area integral.  Assuming that the flow is
-incompressible and not re-entrant, meaning that all streamlines connect
-the two cross-sections, the tortuosity in
+The tortuosity is defined in terms of the length of streamlines between
+a starting and ending point. The starting point is typically along a
+cross-section $S$, but there are several options for the ending
+point~\cite{dud-koz-mat2011}.  The choice adopted here is to use
+streamlines that originate at $S$ and terminate at a parallel
+cross-section.  We use the cross-sections $x=-1$ and $x=1$ that are at
+the start and end of the porous region.  This choice of averaging allows
+us to also compute the tortuosity in terms of an area integral.
+Assuming that the flow is incompressible and not re-entrant, meaning
+that all streamlines connect the two cross-sections, the tortuosity in
 equation~\eqref{eqn:tortuosity1} is equivalent to~\cite{dud-koz-mat2011}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap} (a) The pore sizes between
+neighboring grains. Two grains are said to be neighbors if they share an
+edge of a Delanuay configuration that uses nodes placed at the center of
+each eroding grain. (b) The distribution of the pore sizes of an eroded
+geometry. The black curve is the Weibull distribution with the same
+first two moments as the data.}
+\end{figure}
+
 While transport in a porous media depends on the porosity, it also
@@
 say that two grains are neighbors if their centers share an edge of the
-triangulation~\cite{dea-qua-bir-jua2018}.  Finally, we compute the
-minimum distance between all pairs of neighboring grains.  In
-Figure~\ref{fig:Eroding100gap}(a), we plot a histogram of the pore size
-of 100 eroded bodies.  The black curve is an unnormalized Weibull
-distribution with the same mean and variance as the measured data.  In
-Figure~\ref{fig:Eroding100gap}(b), we plot illustrate the pore throat
-sizes by drawing the shortest lines between neighboring grains.  We do
-not consider pores between eroding bodies and the solid wall $\Gamma$,
-so some of the grains near the porous region boundary only have two
-neighbors.  To analyze the effect of erosion on pore sizes, we use a
-single Delaunay triangulation to define the neighbors up until a body
-has completely eroded. At this point, a new Delanuay triangulation is
-formed.
-
-\todo[inline]{This figure seemed out of place to me because you do not present other graphs yet, only the distribution of pores, and it is before the numerical methods are explained.
-HOWEVER, I think I see what you are driving towards: I think you want to give the reader a little teaser of the results, so that they are more inclined to make it through the methods section without losing interest (is that more or less right?).
-So perhaps just a few words to indicate our intent would prevent the reader from getting whiplash; maybe phrases like ``As illustration of the statistical results that will be elaborated in Section blah, we show here....''
-}
-
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap} (a) The distribution of the pore
-sizes of an eroded geometry. The black curve is the Weibull distribution
-with the same first two moments as the data. (b) We only consider pore
-sizes between neighboring grains, where two grains are neighbors if they
-share a edge in a Delaunay triangulation using nodes placed at the
-center of each eroding grain.}
-\end{figure}
+triangulation~\cite{dea-qua-bir-jua2018}. The pores for a eroded
+geometry are illustrated in Figure~\ref{fig:Eroding100gap}(a). We do not
+consider pores between eroding bodies and the solid wall $\Gamma$, so
+some of the grains near the porous region boundary only have two
+neighbors. Having defined the pore sizes, we form its distribution and
+compare it with the Weibull distribution (black curve) in
+Figure~\ref{fig:Eroding100gap}(b) . A more complete statistical analysis
+of the pore size distribution is in Section~\ref{sec:Eroding100}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\nick{In this section, we apply our new quadrature method to simulate
-erosion of several different configurations of nearly-touching eroding
-bodies, and to characterize transport inside eroded geometries.}
-\todo[inline]{This opening sentence is awkward and seems like a run-on
-sentence.} Each eroding body is initially a circle with center $\cc_i$
-and radius $r_i$.  The center and radius are chosen at random, and the
-body is accepted if it is contained in $[-1,1] \times [-1,1]$ and is
-sufficiently separated from all other bodies.  Since the error of our
-quadrature method is bounded independent of the geometry, we consider
-bodies that are separated by less than 10\% of an arclength spacing.
-The randomized method is repeated until the initial geometry reaches a
-desired initial porosity.
+We now present numerical results on dense packings of bodies eroding in
+Stokes flow. Moreover, we analyze transport through the eroded
+geometries by examining coarse-grained variables.  Each eroding body is
+initially a circle with center $\cc_i$ and radius $r_i$.  The center and
+radius are chosen at random, and the body is accepted if it is contained
+in $[-1,1] \times [-1,1]$ and is sufficiently separated from all other
+bodies.  Since the error of our quadrature method is bounded independent
+of the geometry, we consider bodies that are separated by less than 10\%
+of an arclength spacing.  The randomized method is repeated until the
+initial geometry reaches a desired initial porosity.
 
@@
 \subsection{100 eroding bodies}
+\label{sec:Eroding100}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 velocities are plotted in Figure~\ref{fig:Eroding100tort}(a) for the
-eroded geometry at porosity $\phi = 63.0\%$ \todo[inline]{Make
-consistent with caption in figu 13 and another caption somwhere else in
-this section}
+eroded geometry at porosity $\phi = 62.98\%$
 (Figure~\ref{fig:Eroding100tort}(c)).  The initial velocity of the
@@
 \caption{\label{fig:Eroding100tort} The tortuosity of a porous geometry
-that initially had 100 grains and has eroded to a porosity of 63.0\%.
+that initially had 100 grains and has eroded to a porosity of 62.98\%.
 (a) The $x$-component of the velocity at the inlet, $u_1(-1, y)$,
@@
 to define neighboring eroding bodies, and we compute the pore size by
-finding the closest distance between all neighboring bodies.  Once all
+finding the closest distance between all neighboring bodies.  Instead of
+computing a Delanuay configuration at each time step, which would result
+in new definitions for the pores at each time step, we only compute a
+new Delaunay triangulation when a grain completely erodes.  Once all
 pore sizes are computed, we analyze their distribution as a function of
-the porosity.  In Figure~\ref{fig:Eroding100gap_hist}, we plot
+the porosity.
+
+In Figure~\ref{fig:Eroding100gap_hist}, we plot
 histograms of the pore pore sizes at six porosities during the erosion

### 2019-10-02 docs/transport/erosion_transport.tex
small changes in language
NM

@@
 performed a similar three-dimensional experiment using a second-order
-quadrature method.  They initialized the \st{eroding} body \st{so that}
-with its center located $1.5$ radii above the solid wall.  In two
+quadrature method.  They initialized the \nick{\st{eroding} body \st{so that}
+with its center located} $1.5$ radii above the solid wall.  In two
 dimensions, the trapezoid rule is spectrally accurate, and an analogous
@@
 vanished.  Snapshots of the bodies at four equispaced times are shown in
-Figure~\ref{fig:Eroding20vort}.  The color is the vorticity, and the
-erosion rate is proportional to the vorticity.  Initially, several of
-the eroding bodies are closer to the outer wall than the $5h$ threshold
-required to guarantee that the trapezoid rule achieves machine
+Figure~\ref{fig:Eroding20vort}.  The color is the vorticity, \nick{which is proportional to the erosion rate on solid boundaries}.
+Initially, several of the eroding bodies are closer to the outer wall than the $5h$ threshold \nick{required \st{to guarantee that} for} the trapezoid rule to achieve machine
 precision.  In particular, the distance between bodies 1, 6, 13, and 15
@@
 quadrature rule, the interaction between these nearly-touching bodies
-can be accurately resolved at the prescribed resolution, and erosion can
+can be accurately resolved \nick{\st{at the prescribed resolution} to the desired accuracy}, and erosion can
 be simulated until all the bodies have vanished.
@@
 
-Similar to our previous work, erosion causes the space between nearly
+\nick{\st{Similar to our previous work,}} Erosion causes the space between nearly
 touching bodies to quickly expand, and flat faces develop along the
-regions of near contact.  This qualitative behavior is present in
-Figure~\ref{fig:Eroding20vort} between bodies 3 \& 4, 15 \& 16, and
-others.  However, by resolving the interaction between bodies that are
-much closer together than in our previous work, we observe that, at
-least initially, very little erosion occurs between certain pairs of
-bodies.  For instance the opening between bodies 1 \& 6, 3 \& 9, and 5
+regions of near contact.  This qualitative behavior is seen in Figure~\ref{fig:Eroding20vort} between bodies 3 \& 4, 15 \& 16, and
+\nick{was also witnessed in previous work}.  
+However, by resolving the interaction between bodies that are
+much closer together than in previous work, we observe that very little erosion occurs between certain pairs of bodies, at least initially.  
+For instance the opening between bodies 1 \& 6, 3 \& 9, and 5
 \& 13 grow much slower than the opening between bodies 15 \& 16.  A
 common feature of the pores that grow slowly is that they are nearly
-perpendicular to the main flow direction, and this results in a small
+perpendicular to the main flow direction, \nick{resulting} in a small
 erosion rate.
@@
 fraction.  Starting around normalized time $0.2$,
-Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
+Figure~\ref{fig:Eroding20flowrate}(b) \nick{is roughly linear which indicates
 that the flow rate can be written as a power law.  Using a line of best
@@
 \end{align}
-which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).
+which is the dashed line in} Figure~\ref{fig:Eroding20flowrate}(b).
+
+\todo[inline]{WAIT.... Fig 7b is a semi-log plot with the x-axis linear and the y-axis logarithmic. Therefore, a straight line indicates exponential increase, not a power law.}
 
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_1}
-\caption{100 bodies, 258 gaps}
+\caption{100 bodies, 258 pores}
 \end{subfigure}%
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_46}
-\caption{100 gaps, 258 gaps}
+\caption{100 bodies, 258 pores}
 \end{subfigure}%
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_112}
-\caption{97 bodies, 249 gaps}
+\caption{97 bodies, 249 pores}
 \end{subfigure}
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_164}
-\caption{92 bodies, 234 gaps}
+\caption{92 bodies, 234 pores}
 \end{subfigure}%
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_207}
-\caption{75 bodies, 189 gaps}
+\caption{75 bodies, 189 pores}
 \end{subfigure}%
@@
 \includegraphics*[width =\linewidth]{./figs/hist100b_246}
-\caption{34 bodies, 74 gaps}
+\caption{34 bodies, 74 pores}
 \end{subfigure}

### 2019-10-02 docs/transport/erosion_transport.tex
NM

@@
 
-\todo[inline]{WAIT.... Fig 7b is a semi-log plot with the x-axis linear and the y-axis logarithmic. Therefore, a straight line indicates exponential increase, not a power law.}
+\todo[inline]{WAIT! Fig 7b is a semi-log plot with the x-axis linear and the y-axis logarithmic. Therefore, a straight line indicates exponential increase, not a power law.}
 
@@
 streamlines.  In Figure~\ref{fig:Eroding20tracer}, we freeze the
-geometry at the second snapshot from Figure~\ref{fig:Eroding20vort}, and
-we plot 200 streamlines that are initialized at $x=-1$ and equally
+geometry at the second snapshot from Figure~\ref{fig:Eroding20vort} and plot 200 streamlines that are initialized at $x=-1$ and equally
 spaced in $y \in (-1,1)$.  The streamlines are shown at five different
@@
 stepping method, we resolve streamlines that come very close to the
-eroded bodies.  There are three clear regions where the streamlines are
-concentrated, and this corresponds to regions of high velocity.  Two of
-these regions are located between the bodies and the solid walls at
+eroded bodies.  There are three clear regions where the streamlines are \nick{most}
+concentrated, \nick{\st{and this}} corresponding to the regions of highest velocity.  Two of these regions are located between the bodies and the solid walls at
 $y=\pm 1$, and the third cuts through the porous region with the upper
-part of the channel formed by bodies 1, 4, 6, and 8.  Since the flow is
-fastest in these regions, the shearing is largest, and this causes the
+part of the channel formed by bodies 1, 4, 6, and 8.  
+\todo[inline]{Right now, this description has the reader looking at Fig.
+8, but the bodies are not numbered in that figure, so they don't know which ones are 1, 4, 6, 8 without flipping back and forth with the previous figures to try to match corresponding bodes.}
+Since the flow is fastest in these regions, the shearing is largest, and this causes the
 channels to continue to open fastest which can be observed in

### 2019-10-02 docs/transport/erosion_transport.tex
NM

@@
 Since the flow is fastest in these regions, the shearing is largest, and this causes the
-channels to continue to open fastest which can be observed in
+channels to continue to open fastest \nick{\st{which can be} as} observed in
 Figure~\ref{fig:Eroding20vort}.

### 2019-10-02 docs/transport/erosion_transport.tex
NM

@@
 Next, we use the streamlines to compute the tortuosity and the anomalous
-dispersion rate of eroding geometries.  To achieve statistical
+dispersion rate\nick{s} of eroding geometries.  To achieve statistical
 convergence, we use $N_p = 1000$ streamlines~\cite{bel-sal-rin1992}. To
@@
 that one of the streamlines is 27\% longer than it would have been if
-the grains were absent.  The average streamline length is 9.79\% longer
-than if the grains had been absent, so the tortuosity of the eroded
-channel is $1.098$.  Again, comparing the local tortuosity to
+the grains were absent.  The average streamline is 9.79\% longer
+\nick{\st{than if the grains had been absent}, \st{so the} or equivalently the tortuosity of the \st{eroded channel} geometry is $1.098$}.  Again, comparing the local tortuosity to
 Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
@@
 cut through the grains, the local tortuosity does not have any gaps.
-The discontinuities in the local tortuosity happens when nearby
+\nick{Discontinuities in local tortuosity \st{happens} occur} when nearby
 streamlines diverge on opposite sides of a grain.  In

### 2019-10-02 docs/transport/erosion_transport.tex
NM

@@
 \nick{Discontinuities in local tortuosity \st{happens} occur} when nearby
-streamlines diverge on opposite sides of a grain.  In
-Figure~\ref{fig:Eroding20tort}(c), we plot the pairs of streamlines that
-correspond to the ten largest jumps in the local tortuosity.
-Corresponding pairs are plotted in the same color.
+streamlines diverge \nick{\st{on opposite sides of a grain} to circumvent a grain}.  In
+Figure~\ref{fig:Eroding20tort}(c), we plot pairs of streamlines \nick{associate with the ten largest jumps in the local tortuosity, with each pair of corresponding streamlines plotted in the same color.}
 

### 2019-10-02 docs/transport/erosion_transport.tex
NM

@@
 We computed lines of best fit using the porosity-tortuosity
-models~\eqref{eqn:tortuosityModels}, and the power law model gave the
+models~\eqref{eqn:tortuosityModels} and \nick{found the power law to give} the
 smallest error.  The  black dashed line in
@@
 
+\todo[inline]{I wonder if this initial increase in the tortuosity is specific to the process of erosion, or if it would also occur if we simply took a collection of circular bodies and changed the porosity by controlling the radii?
+We don't have to answer this question now, but it would be interesting to consider in the future.}
+
 In Figure~\ref{fig:Eroding20Transport}(b), we plot the temporal
 evolution of the particle spreading $\sigma_\lambda$.  The spreading is
-computed at seven geometries of different porosities that are formed
+computed \nick{\st{at} for} seven geometries of different porosities that are formed
 during the erosion process.  So that the spreading reaches a statistical
@@
 Section~\ref{sec:dispersion} to form sufficiently long trajectories.
-For all the reported porosities, the particle dispersion exhibits two
-power low regimes.  Initially, the dispersion is ballistic
+For all the reported porosities, the particle dispersion exhibits two \nick{distinct
+power \st{low} law} regimes.  Initially, the dispersion is ballistic
 ($\sigma_\lambda \sim t$) since individual fluid particles have not yet
@@
 once the particles have been subjected to a range of velocities, their
-dispersion slows down, and we observe super-dispersive ($\sigma_\lambda
+dispersion slows \nick{\st{down}}, and we observe super-dispersive ($\sigma_\lambda
 \sim t^\alpha$, $\alpha \in (1/2,1)$) behavior over at least one order

### 2019-10-03 docs/transport/erosion_transport.tex
NM
working on Nick's revisions

@@
 performed a similar three-dimensional experiment using a second-order
-quadrature method.  They initialized the \nick{\st{eroding} body \st{so that}
-with its center located} $1.5$ radii above the solid wall.  In two
-dimensions, the trapezoid rule is spectrally accurate, and an analogous
-initial configuration is possible. However, unless the number of
-discretization points is increased, the trapezoid rule becomes obsolete
-if the eroding body is initialized closer to the solid wall. Therefore,
-to simulate erosion near a solid wall at reasonable levels of
-discretization, we use our hybrid method that combines the trapezoid
-rule and the Barycentric quadrature rule.
+quadrature method.  They initialized the body with its center located
+$1.5$ radii above the solid wall.  In two dimensions, the trapezoid rule
+is spectrally accurate, and an analogous initial configuration is
+possible. However, unless the number of discretization points is
+increased, the trapezoid rule becomes obsolete if the eroding body is
+initialized closer to the solid wall. Therefore, to simulate erosion
+near a solid wall at reasonable levels of discretization, we use our
+hybrid method that combines the trapezoid rule and the Barycentric
+quadrature rule.
 
@@
 vanished.  Snapshots of the bodies at four equispaced times are shown in
-Figure~\ref{fig:Eroding20vort}.  The color is the vorticity, \nick{which is proportional to the erosion rate on solid boundaries}.
-Initially, several of the eroding bodies are closer to the outer wall than the $5h$ threshold \nick{required \st{to guarantee that} for} the trapezoid rule to achieve machine
-precision.  In particular, the distance between bodies 1, 6, 13, and 15
-and the outer wall is $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively,
-where $h$ is the arclength spacing of the outer wall $\Gamma$.  In
-addition, the distance between several pairs of eroding bodies,
-including 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18, is too small to be
-accurately resolved with the trapezoid rule.  By using the Barycentric
-quadrature rule, the interaction between these nearly-touching bodies
-can be accurately resolved \nick{\st{at the prescribed resolution} to the desired accuracy}, and erosion can
-be simulated until all the bodies have vanished.
+Figure~\ref{fig:Eroding20vort}.  The color is the vorticity, whose
+absolute value is proportional to the erosion rate on solid boundaries.
+Initially, several of the eroding bodies are closer to the outer wall
+than the $5h$ threshold required for the trapezoid rule to achieve
+machine precision.  In particular, the distance between bodies 1, 6, 13,
+and 15 and the outer wall is $1.3h$, $2.9h$, $2.8h$, and $1.3h$,
+respectively, where $h$ is the arclength spacing of the outer wall
+$\Gamma$.  In addition, the distance between several pairs of eroding
+bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18, is too small to
+be accurately resolved with the trapezoid rule.  By using the
+Barycentric quadrature rule, the interaction between these
+nearly-touching bodies can be accurately resolved to the desired
+accuracy, and erosion can be simulated until all the bodies have
+vanished.
 
@@
 
-\nick{\st{Similar to our previous work,}} Erosion causes the space between nearly
-touching bodies to quickly expand, and flat faces develop along the
-regions of near contact.  This qualitative behavior is seen in Figure~\ref{fig:Eroding20vort} between bodies 3 \& 4, 15 \& 16, and
-\nick{was also witnessed in previous work}.  
-However, by resolving the interaction between bodies that are
-much closer together than in previous work, we observe that very little erosion occurs between certain pairs of bodies, at least initially.  
-For instance the opening between bodies 1 \& 6, 3 \& 9, and 5
-\& 13 grow much slower than the opening between bodies 15 \& 16.  A
-common feature of the pores that grow slowly is that they are nearly
-perpendicular to the main flow direction, \nick{resulting} in a small
-erosion rate.
+Erosion causes the space between nearly touching bodies to quickly
+expand, and flat faces develop along the regions of near contact.  This
+qualitative behavior is seen in Figure~\ref{fig:Eroding20vort} between
+bodies 3 \& 4, 15 \& 16, and was also observed in previous work.
+However, by resolving the interaction between bodies that are much
+closer together than in previous work, we observe that very little
+erosion occurs between certain pairs of bodies, at least initially.  For
+instance the opening between bodies 1 \& 6, 3 \& 9, and 5 \& 13 grow
+much slower than the opening between bodies 15 \& 16.  A common feature
+of the pores that grow slowly is that they are nearly perpendicular to
+the main flow direction, resulting in a small erosion rate.
 
@@
 fraction.  Starting around normalized time $0.2$,
-Figure~\ref{fig:Eroding20flowrate}(b) \nick{is roughly linear which indicates
-that the flow rate can be written as a power law.  Using a line of best
-fit, the flow rate is approximately 
-\begin{align} 
-  U \approx \left(\frac{t}{t_f}\right)^{3.43},
-\end{align}
-which is the dashed line in} Figure~\ref{fig:Eroding20flowrate}(b).
-
-\todo[inline]{WAIT! Fig 7b is a semi-log plot with the x-axis linear and the y-axis logarithmic. Therefore, a straight line indicates exponential increase, not a power law.}
+Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
+that the flow rate can be written as a exponential law.  The line of
+best fit is
+\begin{align} 
+  \log_{10} U \approx 3.43 \frac{t}{t_f} + c, 
+\end{align}
+$t_f$ is the time required for all the bodies to erode, and $c$ is a
+fitting parameter. By construction $U = 1$ when $t=t_f$, so $c=-3.43$,
+and the flow rate is approximated as
+\begin{align}
+  U \approx \exp\left(7.90 \left(\frac{t - t_f}{t_f} \right)\right),
+\end{align}
+which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).
 
@@
 stepping method, we resolve streamlines that come very close to the
-eroded bodies.  There are three clear regions where the streamlines are \nick{most}
-concentrated, \nick{\st{and this}} corresponding to the regions of highest velocity.  Two of these regions are located between the bodies and the solid walls at
-$y=\pm 1$, and the third cuts through the porous region with the upper
-part of the channel formed by bodies 1, 4, 6, and 8.  
+eroded bodies.  There are three clear regions where the streamlines are
+most concentrated, corresponding to the regions of highest velocity.
+Two of these regions are located between the bodies and the solid walls
+at $y=\pm 1$, and the third cuts through the porous region with the
+upper part of the channel formed by bodies 1, 4, 6, and 8.
 \todo[inline]{Right now, this description has the reader looking at Fig.
-8, but the bodies are not numbered in that figure, so they don't know which ones are 1, 4, 6, 8 without flipping back and forth with the previous figures to try to match corresponding bodes.}
-Since the flow is fastest in these regions, the shearing is largest, and this causes the
-channels to continue to open fastest \nick{\st{which can be} as} observed in
+8, but the bodies are not numbered in that figure, so they don't know
+which ones are 1, 4, 6, 8 without flipping back and forth with the
+previous figures to try to match corresponding bodes.} Since the flow is
+fastest in these regions, the shearing is largest, and this causes the
+channels to continue to open fastest as observed in
 Figure~\ref{fig:Eroding20vort}.
@@
 Next, we use the streamlines to compute the tortuosity and the anomalous
-dispersion rate\nick{s} of eroding geometries.  To achieve statistical
+dispersion rates of eroding geometries.  To achieve statistical
 convergence, we use $N_p = 1000$ streamlines~\cite{bel-sal-rin1992}. To
@@
 that one of the streamlines is 27\% longer than it would have been if
-the grains were absent.  The average streamline is 9.79\% longer
-\nick{\st{than if the grains had been absent}, \st{so the} or equivalently the tortuosity of the \st{eroded channel} geometry is $1.098$}.  Again, comparing the local tortuosity to
-Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results are
-qualitatively similar. However, since our initial cross-section does not
-cut through the grains, the local tortuosity does not have any gaps.
-\nick{Discontinuities in local tortuosity \st{happens} occur} when nearby
-streamlines diverge \nick{\st{on opposite sides of a grain} to circumvent a grain}.  In
-Figure~\ref{fig:Eroding20tort}(c), we plot pairs of streamlines \nick{associate with the ten largest jumps in the local tortuosity, with each pair of corresponding streamlines plotted in the same color.}
+the grains were absent.  The average streamline is 9.79\% longer or
+equivalently the tortuosity of the geometry is $1.098$.  Again,
+comparing the local tortuosity to Matyka~\cite{mat-kha-koz2008} (Figure
+4(b)), the results are qualitatively similar. However, since our initial
+cross-section does not cut through the grains, the local tortuosity does
+not have any gaps.  Discontinuities in local tortuosity occur when
+nearby streamlines diverge to circumvent a grain.  In
+Figure~\ref{fig:Eroding20tort}(c), we plot pairs of streamlines
+associated with the ten largest jumps in the local tortuosity, with each
+pair of corresponding streamlines plotted in the same color.
 
@@
 function of the porosity. The initial porosity is $\phi = 37.68\%$, and
-the initial tortuosity is $T = 1.16$.  The tortuosity is computed with both
-the length of the streamlines~\eqref{eqn:tortuosity1} (red stars) and
-using the spatial average of the velocity on an Eulerian
+the initial tortuosity is $T = 1.16$.  The tortuosity is computed with
+both the length of the streamlines~\eqref{eqn:tortuosity1} (red stars)
+and using the spatial average of the velocity on an Eulerian
 grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
@@
 We computed lines of best fit using the porosity-tortuosity
-models~\eqref{eqn:tortuosityModels} and \nick{found the power law to give} the
+models~\eqref{eqn:tortuosityModels} and found the power law to give the
 smallest error.  The  black dashed line in
@@
 evolution of the particle spreading $\sigma_\lambda$.  The spreading is
-computed \nick{\st{at} for} seven geometries of different porosities that are formed
+computed for seven geometries of different porosities that are formed
 during the erosion process.  So that the spreading reaches a statistical
@@
 Section~\ref{sec:dispersion} to form sufficiently long trajectories.
-For all the reported porosities, the particle dispersion exhibits two \nick{distinct
-power \st{low} law} regimes.  Initially, the dispersion is ballistic
+For all the reported porosities, the particle dispersion exhibits two
+distinct power law regimes.  Initially, the dispersion is ballistic
 ($\sigma_\lambda \sim t$) since individual fluid particles have not yet
@@
 once the particles have been subjected to a range of velocities, their
-dispersion slows \nick{\st{down}}, and we observe super-dispersive ($\sigma_\lambda
-\sim t^\alpha$, $\alpha \in (1/2,1)$) behavior over at least one order
-of magnitude in time.  Before any erosion takes place, the anomalous
+dispersion slows, and we observe super-dispersive ($\sigma_\lambda \sim
+t^\alpha$, $\alpha \in (1/2,1)$) behavior over at least one order of
+magnitude in time.  Before any erosion takes place, the anomalous
 dispersion coefficient is $\alpha = 0.56$.  Then, as the grains begin to
@@
 \end{figure}
+
+\todo[inline]{Nick made it to here.}
 

### 2019-10-03 docs/transport/erosion_transport.tex
looked at last two comments. Have sent a few figure updates to S-H

@@
 fast regions, such as the region above body 11, and this increases the
-amount of vertical deflection, and therefore the tortuosity.
-
-\todo[inline]{I wonder if this initial increase in the tortuosity is specific to the process of erosion, or if it would also occur if we simply took a collection of circular bodies and changed the porosity by controlling the radii?
-We don't have to answer this question now, but it would be interesting to consider in the future.}
+amount of vertical deflection, and therefore the tortuosity. While this
+increase in tortuosity is interesting, in the next two examples we will
+see that the tortuosity does not initially increase.
 

### 2019-10-03 docs/transport/erosion_transport.tex
modify figs in transport paper
small change

@@
 at $y=\pm 1$, and the third cuts through the porous region with the
-upper part of the channel formed by bodies 1, 4, 6, and 8.
-\todo[inline]{Right now, this description has the reader looking at Fig.
-8, but the bodies are not numbered in that figure, so they don't know
-which ones are 1, 4, 6, 8 without flipping back and forth with the
-previous figures to try to match corresponding bodes.} Since the flow is
-fastest in these regions, the shearing is largest, and this causes the
-channels to continue to open fastest as observed in
+upper part of the channel formed by bodies 1, 4, 6, and 8.  Since the
+flow is fastest in these regions, the shearing is largest, and this
+causes the channels to continue to open fastest as observed in
 Figure~\ref{fig:Eroding20vort}.
@@
 \begin{center}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
-\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30n}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90n}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150n}\\
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210n}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270n}
+\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270n_zoom}
 \caption{\label{fig:Eroding20tracer} 200 streamlines in the second

### 2019-10-03 docs/transport/erosion_transport.tex
small change

@@
 \begin{align} 
-  \log_{10} U \approx 3.43 \frac{t}{t_f} + c, 
+  \log_{10} U \approx 4.32 \frac{t}{t_f} + c, 
 \end{align}
 $t_f$ is the time required for all the bodies to erode, and $c$ is a
-fitting parameter. By construction $U = 1$ when $t=t_f$, so $c=-3.43$,
+fitting parameter. By construction $U = 1$ when $t=t_f$, so $c=-4,32$,
 and the flow rate is approximated as
 \begin{align}
-  U \approx \exp\left(7.90 \left(\frac{t - t_f}{t_f} \right)\right),
+  U \approx \exp\left(9.94 \left(\frac{t - t_f}{t_f} \right)\right),
 \end{align}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.7\linewidth]{./figs/flow_rate20dense}
+\includegraphics*[height = 0.7\linewidth]{./figs/flow_rate20densen}
 \caption{}
@@
 times, and the final plot is a zoom in of the lower right quadrant of
-the fifth time step.  Since we use a high-order quadrature rule and time
-stepping method, we resolve streamlines that come very close to the
-eroded bodies.  There are three clear regions where the streamlines are
-most concentrated, corresponding to the regions of highest velocity.
-Two of these regions are located between the bodies and the solid walls
-at $y=\pm 1$, and the third cuts through the porous region with the
-upper part of the channel formed by bodies 1, 4, 6, and 8.  Since the
-flow is fastest in these regions, the shearing is largest, and this
-causes the channels to continue to open fastest as observed in
-Figure~\ref{fig:Eroding20vort}.
+the fifth time step, but with additional streamlines.  Since we use a
+high-order quadrature rule and time stepping method, we resolve
+streamlines that come very close to the eroded bodies.  There are three
+clear regions where the streamlines are most concentrated, corresponding
+to the regions of highest velocity.  Two of these regions are located
+between the bodies and the solid walls at $y=\pm 1$, and the third cuts
+through the porous region with the upper part of the channel formed by
+bodies 1, 4, 6, and 8.  Since the flow is fastest in these regions, the
+shearing is largest, and this causes the channels to continue to open
+fastest as observed in Figure~\ref{fig:Eroding20vort}.
 
@@
 first five snapshots are evenly spaced in time.  The bottom right frame
-is a zoom in of the fifth snapshot.  Since we use the Barycentric
-quadrature rule and the fourth-order Runge-Kutta method, some
-streamlines are very close to the grains without penetrating them.}
+is a zoom in of the fifth snapshot, but with additional streamlines.
+Since we use the Barycentric quadrature rule and the fourth-order
+Runge-Kutta method, some streamlines are very close to the grains
+without penetrating them.}
 \end{center}

### 2019-10-03 docs/transport/erosion_transport.tex
NM

@@
 approximately $N_\iin = 27,000$ and $N_\out = 18,000$ discretization
-points is required to satisfy the $5h$ threshold required to guarantee
-that the trapezoid rule achieves machine precision.  By applying the
+points is required to satisfy the $5h$ threshold required \nick{\st{to guarantee
+that} for} the trapezoid rule achieves machine precision.  By applying the
 Barycentric quadrature rule, we stably simulate erosion at the much

### 2019-10-03 docs/transport/erosion_transport.tex
NM

--- 2019-10-03 docs/transport/erosion_transport.tex
@@
 approximately $N_\iin = 27,000$ and $N_\out = 18,000$ discretization
-points is required to satisfy the $5h$ threshold required to guarantee
-that the trapezoid rule achieves machine precision.  By applying the
+points is required to satisfy the $5h$ threshold \nick{\st{required to guarantee
+that} needed for} the trapezoid rule to achieve machine precision.  By applying the
 Barycentric quadrature rule, we stably simulate erosion at the much
@@
 is $1.13 \times 10^{-2}$.  As grains erode, there is an increase in the
-number of streamlines that take a nearly direct pact through the
+number of streamlines that take a nearly direct \nick{\st{pact} path} through the
 geometry, and this decreases the tortuosity. However, the channelization
@@
 (Section~\ref{sec:Eroding20}), at early times the erosion results in a
-decrease in the dispersion rate. In particular, once erosion has eroded
+decrease in the dispersion rate. In particular, \nick{once erosion has eroded}
+\todo[inline]{Erosion has eroded?}
 the first 5\% of the bodies, the particle spreading transitions from
@@
 tracers travels 25.5\% farther than it would have if the bodies had been
-absent, and the average tracer travelled 12\% farther than it would have
-if the bodies were absent, so the tortuosity is $1.12$.
+absent, and the average tracer travelled 12\% farther \nick{\st{than it would have
+if the bodies were absent,} indicating a tortuosity of $1.12$.}
+\todo[inline]{Here and in a previous example, I believe the qualifier `than it would have if the bodies were absent' is obvious from the first part of the sentence and does not need to be repeated because it makes the sentence very verbose.}
 

### 2019-10-03 docs/transport/erosion_transport.tex
NM

@@
 the erosion rate and vorticity. By using this quadrature rule, we are
-able to form stable simulations of erosion with $N = \mathcal{O}(100)$
+able to \nick{per}form stable simulations of erosion with $N = \mathcal{O}(100)$
 discretization points, while the trapezoid rule would require

### 2019-10-03 docs/transport/erosion_transport.tex
NM

@@
 other works~\cite{mat-kha-koz2008}. However, the tortuosity of the
-eroded geometries can not be completely described in terms of the
+eroded geometries \nick{\st{can not} cannot} be completely described in terms of the
 porosity. In particular, we observe that for certain porous media, the
@@
 other transport models. Including inertia requires an integral equation
-formulation for the Navier-Stokes equations, and one approach has
-recently been developed~\cite{kli-ask-kro2019}. Regarding other
-transport models, this would involve a diffusive term to consider the
+formulation of the Navier-Stokes equations, \nick{which is an active area of research with a few promising algorithms recently proposed}~\cite{gray2019boundary, kli-ask-kro2019}. 
+\todo[inline]{Okay with you if I include my work with Lenny here? After all, the end goal of it is to solve Navier-Stokes with boundary integrals :)}
+Regarding other transport models, this would involve a diffusive term to consider the
 transport of heat or a contaminant. Forming high-fidelity simulations of

### 2019-10-03 docs/transport/erosion_transport.tex
NM
finished nick's revisions

--- 2019-10-03 docs/transport/erosion_transport.tex
@@
   the fluid equations, and a stable second-order time stepping method to
-  erode the grains.  In our previous work, we required that the eroding
-  grains were sufficiently separated to guarantee that the trapezoid
-  rule provides a sufficient amount of accuracy. We now remove this
+  erode the grains.  In our previous work, we required eroding grains
+  that were sufficiently separated to guarantee that the trapezoid rule
+  provides a sufficient amount of accuracy. We now remove this
   restriction by introducing a Barycentric quadrature rule whose error
@@
 
-\todo[inline]{Nick made it to here.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 approximately $N_\iin = 27,000$ and $N_\out = 18,000$ discretization
-points is required to satisfy the $5h$ threshold \nick{\st{required to guarantee
-that} needed for} the trapezoid rule to achieve machine precision.  By applying the
+points is required to satisfy the $5h$ threshold needed for the
+trapezoid rule to achieve machine precision.  By applying the
 Barycentric quadrature rule, we stably simulate erosion at the much
@@
 is $1.13 \times 10^{-2}$.  As grains erode, there is an increase in the
-number of streamlines that take a nearly direct \nick{\st{pact} path} through the
+number of streamlines that take a nearly direct path through the
 geometry, and this decreases the tortuosity. However, the channelization
@@
 (Section~\ref{sec:Eroding20}), at early times the erosion results in a
-decrease in the dispersion rate. In particular, \nick{once erosion has eroded}
-\todo[inline]{Erosion has eroded?}
-the first 5\% of the bodies, the particle spreading transitions from
+decrease in the dispersion rate. In particular, the first 5\% of the
+bodies have eroded, the particle spreading transitions from
 $\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim t^{0.69}$.  To
@@
 tracers travels 25.5\% farther than it would have if the bodies had been
-absent, and the average tracer travelled 12\% farther \nick{\st{than it would have
-if the bodies were absent,} indicating a tortuosity of $1.12$.}
-\todo[inline]{Here and in a previous example, I believe the qualifier `than it would have if the bodies were absent' is obvious from the first part of the sentence and does not need to be repeated because it makes the sentence very verbose.}
+absent, and the average tracer travelled 12\% farther indicating a
+tortuosity of $1.12$.
 
@@
 the erosion rate and vorticity. By using this quadrature rule, we are
-able to form stable simulations of erosion with $N = \mathcal{O}(100)$
-discretization points, while the trapezoid rule would require
-$\mathcal{O}(10^5)$ discretization points.
+able to perform stable simulations of erosion with $N =
+\mathcal{O}(100)$ discretization points, while the trapezoid rule would
+require $\mathcal{O}(10^5)$ discretization points.
 
 The transport is characterized in terms of tortuosity and anomalous
-dispersion. The local tortuosity agrees qualitatively with
-other works~\cite{mat-kha-koz2008}. However, the tortuosity of the
-eroded geometries can not be completely described in terms of the
-porosity. In particular, we observe that for certain porous media, the
-tortuosity can increase when the porosity increases under erosion. We
-also observe super-dispersive spreading, and the rate of dispersion
-significantly depends not only on the porosity, but also the number of
-eroding bodies.
+dispersion. The local tortuosity agrees qualitatively with other
+works~\cite{mat-kha-koz2008}. However, the tortuosity of the eroded
+geometries cannot be completely described in terms of the porosity. In
+particular, we observe that for certain porous media, the tortuosity can
+increase when the porosity increases under erosion. We also observe
+super-dispersive spreading, and the rate of dispersion significantly
+depends not only on the porosity, but also the number of eroding bodies.
 
@@
 other transport models. Including inertia requires an integral equation
-formulation for the Navier-Stokes equations, and one approach has
-recently been developed~\cite{kli-ask-kro2019}. Regarding other
+formulation of the Navier-Stokes equations, which is an active area of
+research with a few promising algorithms recently
+proposed~\cite{gray2019boundary, kli-ask-kro2019}.  Regarding other
 transport models, this would involve a diffusive term to consider the

### 2019-10-03 docs/transport/erosion_transport.tex
small changes to intro

@@
 mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}, and
-(iii) potentially develop meaningful constitutive relationships that
-link the microscopic and macroscopic
-realms~\cite{mil-chr-imh-mcb-ped1998}.  Examples of coarse-grained
-models for porous media flow include pressure-saturation-permeability
+(iii) develop meaningful constitutive relationships that link the
+microscopic and macroscopic realms~\cite{mil-chr-imh-mcb-ped1998}.
+Examples of coarse-grained models for porous media flow include
+pressure-saturation-permeability
 relationships~\cite{mil-chr-imh-mcb-ped1998}, permeability-porosity
@@
 dud-koz-mat2011, kop-kat-tim1996}, concentration
-distributions~\cite{ica-den2019, bel-sal-rin1992}, flow
+distributions~\cite{ica-den2019, bel-sal-rin1992}, pore and flow
 distributions~\cite{ali-par-wei-bre2017}, geometry
-connectivity~\cite{knu-car2005, wes-blo-gra2001}, pore
-distributions~\cite{ali-par-wei-bre2017}, anomalous
+connectivity~\cite{knu-car2005, wes-blo-gra2001}, anomalous
 dispersion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
@@
 Flow in porous media is further complicated when boundaries dynamically
-evolve in response to the fluid flow. This type of coupling between the
-geometry and the flow occurs, for example, in applications involving
+evolve in response to the fluid flow. This coupling between the geometry
+and the flow occurs, for example, in applications involving
 melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular,
@@
 in number and modest in volume fraction, transmit a large portion of the
-flux \cite{qua-moo2018}. This arrangement results in velocities that vary over several
-orders of magnitude~\cite{all-hea-lab-rei2002}.  Moreover,
-channelization creates heterogeneous and anisotropic medium properties,
-which affect the transport of tracers such as
+flux \cite{qua-moo2018}. This arrangement results in velocities that
+vary over several orders of magnitude~\cite{all-hea-lab-rei2002}.
+Moreover, channelization creates heterogeneous and anisotropic medium
+properties, which affect the transport of tracers such as
 contaminants~\cite{cve-che-wen1996, dag1987, kon-bre1978} and
@@
 realistic, dense suspensions of eroding grains
-(Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To
+(Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  Then, to
 characterize transport through these configurations, we examine
@@
 uniformly bounded.  We extend the original quadrature method to compute
-the velocity gradient, which is needed to evaluate shear stress and
-fluid vorticity.
+the velocity gradient, which is needed to evaluate the shear stress and
+the fluid vorticity.
 
@@
 streamlines near grain boundaries, as achieved in this work.  Finally,
-the distribution of pore sizes is required to quantify velocity
+we construct the pore-size distribution throughout the erosion process.
+These distributions are required to quantify velocity
 distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
@@
 connectivity~\cite{knu-car2005, wes-blo-gra2001}, and to develop network
-models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}. Hence, we
-construct the pore-size distribution throughout the erosion process.
+models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
 
@@
 Section~\ref{sec:transport} describes measures for characterizing the
-geometry, transport, and dispersion. Section~\ref{sec:method} describes
-the numerical methods, with special attention paid to the new quadrature
-method for computing the shear stress and the vorticity.
-Section~\ref{sec:results} presents numerical examples for a variety of
-dense packings of bodies.  Finally, concluding remarks are made in
-Section~\ref{sec:conclusions}.
+geometry and transport. Section~\ref{sec:method} describes the numerical
+methods, with special attention paid to the new quadrature method for
+computing the shear stress and the vorticity.  Section~\ref{sec:results}
+presents numerical examples for a variety of dense packings of bodies.
+Finally, concluding remarks are made in Section~\ref{sec:conclusions}.
 

### 2019-10-03 docs/transport/erosion_transport.tex
editing whole doc

@@
 \gamma_M$, where $\Gamma$ is the outer boundary, taken to be a slightly
-smoothed version of $[-3,3] \times [-1,1]$.  We only place eroding
-bodies in $[-1,1] \times [-1,1]$ so as to create a buffer region for the
-flow profile imposed at the inlet to transition to the more complex flow
-intervening between the bodies. On each eroding body, $\nn$ is the
-normal vector pointing into the body, and $\ss$ is the unit tangent
-vector pointing in the counterclockwise direction.  The normal vector on
-$\Gamma$ is the outward unit normal.  Neglecting inertial forces, the
-governing equations are
+smoothed version of the boundary of $[-3,3] \times [-1,1]$.  We only
+place eroding bodies in $[-1,1] \times [-1,1]$ to create a buffer region
+for the flow profile imposed at the inlet to transition to the more
+complex flow intervening between the bodies. On each eroding body, $\nn$
+is the normal vector pointing into the body, and $\ss$ is the unit
+tangent vector pointing in the counterclockwise direction.  The normal
+vector on $\Gamma$ is the outward unit normal.  Neglecting inertial
+forces, the governing equations are
 \begin{equation}
@@
 equations in complex two-dimensional geometries, we reformulate the
-incompressible Stokes equations as a BIE.  This has the advantage that
-only the one-dimensional boundary of the domain must be discretized,
-and, with an appropriate quadrature formula and fast summation methods,
-the result is a high-fidelity numerical simulation with near-optimal
-computational complexity.
+equations as a BIE.  This has the advantage that only the
+one-dimensional boundary of the domain must be discretized, and, with
+appropriate quadrature formulas and fast summation methods, the result
+is a high-fidelity numerical simulation with near-optimal computational
+complexity.
 
@@
 Applying the same approach as our previous work~\cite{qua-moo2018}, we
-write the velocity $\uu$ as a double-layer potential 
+start with the double-layer potential 
 \begin{align}
@@
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  The double-layer potential cannot
-represent all solutions of the incompressible Stokes equations, so we
-complete the integral equation formulation by adding the $M$ Stokeslets
-and rotlets~\cite{pow-mir1987}
+is an unknown density function.  The double-layer potential is a
+solution of the incompressible Stokes equations, but it cannot represent
+all the solutions. Therefore, we complete the integral equation
+formulation by adding the $M$ Stokeslets and rotlets~\cite{pow-mir1987}
 \begin{align}
@@
 $\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
-\|\rr\|$.  Then, for any sufficiently smooth geometry $\Omega$, the
-solution of the incompressible Stokes equation with a Dirichlet boundary
-condition $\ff$ is
+\|\rr\|$. Here, $\llambda_\ell$ and $\xi_\ell$ are the Stokeslet and
+rotlet strengths, respectively, corresponding to the $\ell^{th}$ body.
+Then, for any sufficiently smooth geometry $\Omega$, the solution of the
+incompressible Stokes equation with a Dirichlet boundary condition $\ff$
+is
 \begin{align}
@@
   \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
-    \eeta(\yy)\, ds_\yy &&\ell = 1,\ldots,M, \\
+    \eeta(\yy)\, ds_\yy, &&\ell = 1,\ldots,M, \\
   \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
-    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy 
+    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
     &&\ell = 1,\ldots,M.
@@
 Here, the null space associated with the flux-free condition of $\ff$ is
-addressed with  $\NN_0$ which is the integral operator having kernel
+addressed with  $\NN_0$ which is the integral operator with kernel
 $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
@@
 Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, we are able to
-compute the deformation tensor, pressure, and vorticity, defined
-respectively as
+compute, for $\xx \in \Omega$, the deformation tensor, pressure, and
+vorticity, defined respectively as
 \begin{align}
@@
 associated components of the deformation tensor, pressure, and vorticity
-due to the Stokeslets and rotlets are straightforward to
-compute~\cite{poz1992}.  Having computed the deformation tensor on
-$\gamma$, the shear stress is computed using
+are straightforward to compute~\cite{poz1992}.  Having computed the
+deformation tensor on $\gamma$, the shear stress is computed using
 equation~\eqref{eqn:shearStress}.
@@
 Potential}
+\todo[inline]{Bryan is here}
 \label{sec:DLPcomplex}

### 2019-10-05 docs/transport/erosion_transport.tex
working through the paper

@@
 %
+  \label{eqn:pressureDLP}
   p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
@@
 Potential}
-\todo[inline]{Bryan is here}
 \label{sec:DLPcomplex}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In equations~\eqref{eqn:velocityDLP} and~\eqref{eqn:deformationDLP},
-$\uu$ and its deformation tensor are written as layer potentials in
-$\RR^2$, but the quadrature method we introduce in
-Section~\ref{sec:method} requires a complex-valued representation of the
-layer potentials. The first step to form a complex representation is to
-write the Laplace double-layer potential as the complex integral
+In
+equations~\eqref{eqn:velocityDLP},~\eqref{eqn:deformationDLP},~\eqref{eqn:pressureDLP},
+and~\eqref{eqn:vorticityDLP}, the fluid velocity, deformation tensor,
+pressure, and vorticity are all written as layer potentials in $\RR^2$.
+However, the quadrature method we introduce in Section~\ref{sec:method}
+requires a complex-valued representation of the layer potentials for the
+velocity, deformation tensor, and vorticity. The first step to form a
+complex representation is to write the Laplace double-layer potential as
+the complex integral
 \begin{align}
@@
 (\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
-potential, the space $\Omega$ can be interpreted as a subset of $\RR^2$
-or the corresponding subset of $\CC$.
-Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
-first finding the boundary data of $v$.  Assuming that $\Omega$ is a
-simply-connected interior domain, the boundary data of $v$ satisfies the
-Sokhotski-Plemelj jump relation
+potential, $\Omega$ is being interpreted as a subset of $\RR^2$ or
+$\CC$. Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy
+integral by first finding the boundary data of $v$.  Assuming that
+$\Omega$ is a simply-connected interior domain, the boundary data of $v$
+satisfies the Sokhotski-Plemelj jump relation
 \begin{align}
@@
 decomposed into its different connected components and the appropriate
-jump relation is applied.  Since $v$ is a holomorphic function and we
-have its boundary data, by the Cauchy integral theorem we have
+jump relation is applied.  Having computed the boundary data of the
+holomorphic function $v$, by the Cauchy integral theorem we have
 \begin{align}
@@
 
-The Stokes double-layer potential~\eqref{eqn:velocityDLP} can be written
-as~\cite{bar-wu-vee2015}
+Finally, the Stokes double-layer potential~\eqref{eqn:velocityDLP} can
+be written using a Laplace double-layer
+potential~\eqref{eqn:laplaceComplex} and its gradients 
 \begin{equation}
@@
       \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
-        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy,
+        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
   \end{aligned}
 \end{equation}
-where $\xx = (x_1,x_2)$. Therefore, the Stokes double-layer potential
-can be written as a sum of Cauchy integrals and its first derivative 
+Therefore, the Stokes double-layer potential can be written as a sum of
+Cauchy integrals and its first derivative~\cite{bar-wu-vee2015}
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Erosion in porous geometries leads to particular phenomena such as
+Erosion in porous media leads to particular phenomena such as
 channelization~\cite{berhanu2012shape}, and we are interested in
@@
 tortuosity, and the distribution of the pore sizes.  The first two
-metrics can be defined in terms of streamlines governed by an advection
-autonomous equation~\eqref{eqn:tracers}.
+metrics can be defined in terms of streamlines governed by the
+autonomous advection equation~\eqref{eqn:tracers}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The dynamics of fluid in a porous media is often characterized in terms
+The spreading of fluid in a porous media is often characterized in terms
 of anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.
@@
 several grains so that an asymptotic regime is reached. The geometries
-that we consider are too short to observe the asymptotic dispersion, so
-we use a reinsertion method to form longer trajectories. Similar to the
+that we consider are too short to observe asymptotic dispersion, so we
+use a reinsertion method to form longer trajectories. Similar to the
 work of others~\cite{dea-qua-bir-jua2018, puy-gou-den2019}, once a
@@
 the particle's velocity at the outlet.  After a single trajectory is
-formed, it has undergone a collection of reinsertions.  Therefore, as a
+formed, it has undergone a collection of reinsertions.  Then, as a
 post-processing step, the trajectory is made continuous by attaching the
@@
 \end{align}
-In Section~\ref{sec:results}, we compare these moments in an open
+In Section~\ref{sec:results}, we compare the second moment in an open
 channel with the trajectories in an eroded geometry.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Bryan is here}
 The tortuosity is a dimensionless number that quantifies the amount of

### 2019-10-05 docs/transport/erosion_transport.tex
working on edits

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Bryan is here}
 The tortuosity is a dimensionless number that quantifies the amount of
@@
 \end{align}
-Here, the streamline originates at $(x_0,y_0)$ on the inlet and its
-arclength is calculated once it passes the parallel outlet $x = x_0 +
-d$.  The hydraulic tortuosity is defined by taking the average over all
-points on the cross-section
+Here, the streamline originates on the inlet cross-section $x=x_0$ at
+$(x_0,y_0)$, and its arclength, $\lambda(y_0)$, is calculated until the
+streamline passes the parallel outlet cross-section $x = x_0 + d$.  In
+this work, we consider streamlines originating at $x=-1$ and terminating
+at $x=1$, so $d=2$.  However, other choices for the terminal point when
+computing the tortuosity are sometime used~\cite{dud-koz-mat2011}.  The
+hydraulic tortuosity is defined by taking the average over all points on
+the inlet cross-section
 \begin{align}
@@
 \end{align} 
-where $S$ is the inlet cross-section $x = x_0$ that is perpendicular to
-the $x$-axis, $u_1(y_0)$ is the $x$ component of the velocity at the
-initial point of the streamline, and $d$ is still the distance between
-the inlet and outlet. Therefore, the tortuosity satisfies $T \geq 1$,
-and $T=1$ only if no grains are present.
-
-The tortuosity is defined in terms of the length of streamlines between
-a starting and ending point. The starting point is typically along a
-cross-section $S$, but there are several options for the ending
-point~\cite{dud-koz-mat2011}.  The choice adopted here is to use
-streamlines that originate at $S$ and terminate at a parallel
-cross-section.  We use the cross-sections $x=-1$ and $x=1$ that are at
-the start and end of the porous region.  This choice of averaging allows
-us to also compute the tortuosity in terms of an area integral.
-Assuming that the flow is incompressible and not re-entrant, meaning
-that all streamlines connect the two cross-sections, the tortuosity in
+where $S$ is the inlet cross-section $x = -1$, $u_1(y_0)$ is the
+$x$-component of the velocity at the initial point of the streamline,
+and $d=2$ is the distance between the inlet and outlet.  Note that $T
+\geq 1$, and $T=1$ only if no grains are present.
+
+The definition we made for the tortuosity allows us to compute the
+tortuosity in terms of an area integral.  Assuming that the flow is
+incompressible and not re-entrant, meaning that all streamlines connect
+the two cross-sections, the tortuosity in
 equation~\eqref{eqn:tortuosity1} is equivalent to~\cite{dud-koz-mat2011}
@@
 
-There have been efforts to relate the tortuosity to the porosity.  For
-example, Matyka et al.~\cite{mat-kha-koz2008} propose the models
+There have been efforts to relate the tortuosity, $T$, to the porosity,
+$\phi$.  For example, Matyka et al.~\cite{mat-kha-koz2008} propose the
+models
 \begin{subequations}
@@
 \end{subequations}
-where $\phi$ is the porosity and $p>0$ is a fitting parameter.  In
-Section~\ref{sec:results}, we compare these four models with the
-tortuosity of eroding porous geometries.
+where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
+compare these four models with the tortuosity of eroding porous
+geometries.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+While transport in porous media depends on the porosity, it also depends
+on the placement of the grains.  In particular, grain placement affects
+velocity scales~\cite{ali-par-wei-bre2017}, correlation
+structures~\cite{leb-ded-dav-bou2007}, contaminant
+transport~\cite{knu-car2005},
+channelization~\cite{sie-ili-pri-riv-gua2019,berhanu2012shape}, and pore
+network models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}. To
+characterize the grain placement, we compute distributions of pore sizes
+between neighboring grains.  To define neighboring grains, we form a
+Delaunay triangulation using nodes placed at the center of each eroding
+grain and at a collection of points around the boundary of the porous
+media.  Then, we say that two grains are neighbors if their centers
+share an edge of the triangulation~\cite{dea-qua-bir-jua2018}. The pores
+of an eroded geometry are illustrated in
+Figure~\ref{fig:Eroding100gap}(a). We do not consider pores between
+eroding bodies and the solid wall $\Gamma$, so some of the grains near
+the porous region boundary only have two neighbors. Having defined the
+pore sizes, we plot its distribution in
+Figure~\ref{fig:Eroding100gap}(b) and compare it with the Weibull
+distribution, a distribution used by others to characterize pore
+sizes~\cite{ioa-cha1993}.  In Section~\ref{sec:Eroding100}, we
+investigate the effect of erosion on the pore size distribution.
 \begin{figure}[H]
@@
 neighboring grains. Two grains are said to be neighbors if they share an
-edge of a Delanuay configuration that uses nodes placed at the center of
-each eroding grain. (b) The distribution of the pore sizes of an eroded
+edge of a Delanuay triangulation with nodes at the center of each
+eroding grain. (b) The distribution of the pore sizes of an eroded
 geometry. The black curve is the Weibull distribution with the same
@@
 
-While transport in a porous media depends on the porosity, it also
-depends on the placement of the grains.  In particular, the grain
-placement affects velocity scales~\cite{ali-par-wei-bre2017},
-correlation structures~\cite{leb-ded-dav-bou2007}, contaminant
-transport~\cite{knu-car2005},
-channelization~\cite{sie-ili-pri-riv-gua2019,berhanu2012shape}, and
-more. In addition, the grain configuration is important for pore network
-models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} that rely on
-descriptions of the pore throat sizes. To characterize the grain
-placement, we compute distributions of pore sizes between neighboring
-grains.  To define neighboring grains, we form a Delaunay triangulation
-using nodes placed at the center of each eroding grain and at a
-collection of points around the boundary of the porous region.  Then, we
-say that two grains are neighbors if their centers share an edge of the
-triangulation~\cite{dea-qua-bir-jua2018}. The pores for a eroded
-geometry are illustrated in Figure~\ref{fig:Eroding100gap}(a). We do not
-consider pores between eroding bodies and the solid wall $\Gamma$, so
-some of the grains near the porous region boundary only have two
-neighbors. Having defined the pore sizes, we form its distribution and
-compare it with the Weibull distribution (black curve) in
-Figure~\ref{fig:Eroding100gap}(b) . A more complete statistical analysis
-of the pore size distribution is in Section~\ref{sec:Eroding100}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Bryan is here}
 In line with our previous work~\cite{qua-moo2018}, we use two meshes to
@@
 
+HERE
 In Figure~\ref{fig:Eroding100gap_hist}, we plot

### 2019-10-07 docs/transport/erosion_transport.tex
working through edits

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Bryan is here}
 In line with our previous work~\cite{qua-moo2018}, we use two meshes to
@@
 quadrature rule is either the trapezoid rule or the Barycentric
-quadrature rule (Section~\ref{sec:bary}).  The selection algorithm that
-determines which quadrature method is applied is described in
+quadrature rule (Section~\ref{sec:bary}).  The criteria that determines
+which quadrature method is applied is described in
 Section~\ref{sec:fmm}.  Once the shear stress is computed, the bodies
 are eroded a single time step by using a {\thL}
-discretization~\cite{hou-low-she1994, moore2013self}.  The time stepping methods for
-erosion and passive particles are described in Section~\ref{sec:time}
+discretization~\cite{hou-low-she1994, moore2013self}.  The time stepping
+methods for erosion and passive particles are described in
+Section~\ref{sec:time}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since we use a BIE formulation, we only have to discretize the
+Since we use a BIE formulation, we only need to discretize the
 one-dimensional boundary of the domain.  Therefore, we easily resolve
 complex geometries, and differentiation is performed with spectral
-accuracy in Fourier space.  We discretize each eroding body $\gamma_k$
+accuracy in Fourier space.  We discretize each eroding grain $\gamma_k$
 with $N_\iin$ points and discretize the outer wall $\Gamma$ with
@@
 discretization points are initially distributed evenly in arclength, and
-this equispacing is maintained for the entire simulation by using the
-{\thL} formulation.  In addition, we apply
+this equispacing is maintained throughout the entire simulation by using
+the {\thL} formulation.  In addition, we apply
 regularization~\cite{qua-moo2018} to slightly smooth the corners that
@@
 
-Given the discretization points of $\bd\Omega$, applying the trapezoid
-rule results in the collocation method for~\eqref{eqn:BIE} 
+Given the discretization points of $\bd\Omega$, the trapezoid rule
+results in the collocation method for~\eqref{eqn:BIE}
 \begin{subequations}
@@
 Stokes double-layer potential defined in
-equation~\eqref{eqn:velocityDLP}.  The linear
+equation~\eqref{eqn:velocityDLP}.  Since the kernel is smooth, the
+diagonal terms $D(\yy_j^m,\yy_j^m)$ are replaced with the appropriate
+curvature-dependent limiting term.  The linear
 system~\eqref{eqn:trapLinearSystem} is a well-conditioned second-kind
@@
 While the trapezoid rule is spectrally accurate for smooth, periodic
-functions~\cite{tre-wei2014}, the derivative of the integrands grows as
-the target point $\xx$ approaches $\bd\Omega$ and so the error bound
-depends on the location of the target point. Therefore, if the trapezoid
-rule is applied when bodies are in near-contact, or when a layer
-potential is evaluated at a point close to $\bd\Omega$, then the results
+functions~\cite{tre-wei2014}, the derivative of the integrand grows as
+the target point $\xx$ approaches $\bd\Omega$. The result is an error
+bound depends on the location of the target point. Therefore, if the
+trapezoid rule is applied when bodies are in near-contact, or if a layer
+potential is evaluated at a point close to $\bd\Omega$, then the result
 become unreliable and the simulation ultimately becomes unstable.  We
@@
 first two derivatives.  Therefore, we can accurately compute the
-velocity, shear stress, and vorticity at any target location if we
-develop a quadrature rules with a uniform error bounded for Cauchy
-integrals and its derivatives~\eqref{eqn:cauchy}.  Ioakimidis et
-al.~\cite{ioa-pap-per1991} developed quadrature rules, that we call {\em
-Barycentric quadrature rules}, to compute Cauchy integrals and their
-derivatives with an error bound that is independent of $x \in \CC$.
-Then, Barnett et al.~\cite{bar-wu-vee2015} used these quadrature rules
-to compute the Stokes double-layer potential representation of the
+velocity, shear stress, and vorticity at any target location by using a
+quadrature rule with a uniform error bound for Cauchy integrals and its
+derivatives~\eqref{eqn:cauchy}. Ioakimidis et al.~\cite{ioa-pap-per1991}
+developed quadrature rules, that we call {\em Barycentric quadrature
+rules}, to compute Cauchy integrals and their derivatives with an error
+bound that is independent of $x \in \CC$.  Then, Barnett et
+al.~\cite{bar-wu-vee2015} used these quadrature rules to compute the
+Stokes double-layer potential representation of the
 velocity~\eqref{eqn:velocityDLP}, and we briefly summarize their method.
-Then, we build on this work to accurately compute the gradient of the
-Stokes double-layer potential so that we form the shear stress and
-vorticity.
+Then, we extend their work to compute the second derivative so that the
+shear stress and vorticity can be computed with a uniform error bound.
 
@@
 The method starts with an underlying quadrature rule, and we use the
-spectrally accurate trapezoid rule.  Since the quadrature points are
-uniformly distributed, the quadrature weights are $w_j = L/N$,
-$j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
+spectrally accurate trapezoid rule with $N$ points.  Since the
+quadrature points are uniformly distributed, the quadrature weights are
+$w_j = L/N$, $j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
 
@@
 and~\eqref{eqn:BaryvprimeExterior}. In Section~\ref{sec:results}, these
-quadrature rules are used to form stable eroding simulations of
-nearly-touching grains, and to study dynamics of the flow in regions
-arbitrarily close to eroding grains.
+quadrature rules are used to form simulations of nearly-touching eroding
+grains, and to study dynamics of the flow in regions arbitrarily close
+to eroding grains.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Bryan is here}
 By using the Barycentric quadrature rule, the velocity, shear stress,

### 2019-10-07 docs/transport/erosion_transport.tex
making small corrections

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Bryan is here}
 By using the Barycentric quadrature rule, the velocity, shear stress,
@@
 the target location. However, applied directly, it requires
-$\mathcal{O}(N^2)$ operations.  By using a fast summation method, such
-as the fast multipole method (FMM)~\cite{gre-rok1987}, this cost can be
-reduced to $\mathcal{O}(N)$ operations.  However, the Barycentric
-quadrature rules require several $N$-body calculations, and they must be
-done for each component of $\bd\Omega$ individually.  The resulting cost
-would be prohibitive, so we introduce a hybrid method that combines the
-Barycentric quadrature rule and the trapezoid rule.  Note that the
-source points of the layer potential is always one of the eroding bodies
-or the outer wall, but the target point can either be on another
-component of $\bd\Omega$ or it can be in the fluid bulk $\Omega$.
+$\mathcal{O}(N^2)$ operations, where $N$ is the total number of source
+and target points.  By using a fast summation method, such as the fast
+multipole method (FMM)~\cite{gre-rok1987}, this cost can be reduced to
+$\mathcal{O}(N)$ operations.  However, the Barycentric quadrature rules
+require several $N$-body calculations.  The resulting cost would be
+prohibitive, so we introduce a hybrid method that combines the
+Barycentric quadrature rule and an accelerated trapezoid rule.  Note
+that the source points of the layer potential is always one of the
+eroding bodies or the outer wall, but the target point can either be on
+another component of $\bd\Omega$ or it can be in the fluid bulk
+$\Omega$.
 
@@
 $\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
-the velocity due to $\gamma_k$ with more accuracy.  That is, the final
-velocity is
+the velocity due to $\gamma_k$ with more accuracy.  Finally, the
+velocity at $\xx$ is
 \begin{align}
@@
 to form the vorticity and deformation tensor, and then local corrections
-are made to replace the inaccuracies of the trapezoid rule.  However,
+are made to amend the inaccuracies of the trapezoid rule.  However,
 since the shear stress and vorticity are only computed once per time
@@
 
-Per grid point, applying the Barycentric quadrature rules dominates the
+Per grid point, applying the Barycentric quadrature rules dominate the
 computational cost. Therefore, it is imperative that we only apply the
@@
 \end{align}
-To avoid checking if all target point $\xx$
+To avoid checking if all target points $\xx$
 satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL}
@@
 the normalization term guarantees that the regularization only changes
-the body's shape, but not its total length.
-
-Rather than tracking the $(x,y)$ coordinates, the {\thL} variables are
+the body's shape, but not its total length.  Finally, to increase the
+overall stability of the method, a narrow Gaussian filter is applied to
+the erosion rate at each time step.
+
+Rather than tracking the $(x,y)$ coordinates, the {\thL} coordinates are
 tracked. In addition, a tangential velocity field is added to each body
 so that the discretization points remain equispaced in arclength for all
-time.  Additionally, to increase the overall stability of the method, a
-narrow Gaussian filter is applied to the erosion rate at each time step.
-Time stepping is performed with a second-order Implicit-Explicit
+time.  Time stepping is performed with a second-order Implicit-Explicit
 Runge-Kutta method. In particular, the diffusive term corresponding to
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We now present numerical results on dense packings of bodies eroding in
+We now present numerical results of dense packings of bodies eroding in
 Stokes flow. Moreover, we analyze transport through the eroded
@@
 
-In each of the examples, we plot the vorticity in the fluid bulk.  Since
-the vorticity and the shear stress agree on surface of the eroding
-bodies, the vorticity is a useful method to visualize the erosion rate.
-In particular, the rate of erosion is largest in regions where the
-magnitude of the vorticity is largest.
-
 The erosion rate loses regularity at stagnation points, which inevitably
@@
 we introduce a curvature penalization term and a Gaussian smoothing step
-in order to ameliorate corner formation.  For all examples, we use the
-smoothing parameters $\eps=15/256$ and $\sigma=10/256$, and the time
-step size is $\Delta t = 10^{-4}$.
+to ameliorate corner formation.  For all examples, we use the smoothing
+parameters $\eps=15/256$ and $\sigma=10/256$, and the time step size is
+$\Delta t = 10^{-4}$.
+
+In each of the examples, we plot the vorticity in the fluid bulk.  Since
+the vorticity and the shear stress agree on surface of the eroding
+bodies, the vorticity is useful to visualize the erosion rate.  In
+particular, the rate of erosion is largest in regions where the
+magnitude of the vorticity is largest.
 
@@
 between the eroding bodies, outer walls, and streamlines. We use our
-numerical methods to describe and visualize the following examples:
+numerical methods to simulate, analyze, and visualize the following
+examples:
 \begin{itemize}
@@
   centered at $y=-1$ and compare the eroding body's shape to a similar
-  experiment of Spagnolie and Mitchell~\cite{mit-spa2017}.
+  experiment of Mitchell and Spagnolie~\cite{mit-spa2017}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-First, consider a single eroding body close to a solid wall with the
-shear flow
+Consider a single eroding body close to a solid wall with the shear flow
 \begin{align}
@@
 performed a similar three-dimensional experiment using a second-order
-quadrature method.  They initialized the body with its center located
-$1.5$ radii above the solid wall.  In two dimensions, the trapezoid rule
-is spectrally accurate, and an analogous initial configuration is
-possible. However, unless the number of discretization points is
-increased, the trapezoid rule becomes obsolete if the eroding body is
-initialized closer to the solid wall. Therefore, to simulate erosion
-near a solid wall at reasonable levels of discretization, we use our
-hybrid method that combines the trapezoid rule and the Barycentric
+quadrature method.  Their initial body is a sphere with its center
+located $1.5$ radii above the solid wall.  In two dimensions, the
+trapezoid rule is spectrally accurate, and an analogous initial
+configuration is possible. However, unless the number of discretization
+points is increased, the trapezoid rule becomes obsolete if the eroding
+body is initialized too close to the solid wall. Therefore, to simulate
+erosion near a solid wall at reasonable levels of discretization, we use
+our hybrid method that combines the trapezoid rule and the Barycentric
 quadrature rule.
@@
 In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
-equispaced time steps.  For the three initial configurations, the shear
+equispaced time steps.  For all three initial configurations, the shear
 stress is positive for all time, but varies over several orders of
@@
 between the solid wall and the spherical body~\cite{cha-feu2003}, but
-this is possible in two dimensions~\cite{chw-wu1975, hig1985}. To
-visualize the flow, we plot the vorticity of the final time step from
-Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  The
-recirculation is present in the region where the vorticity is smallest,
-but its size is very small.
+recirculation is possible in two dimensions~\cite{chw-wu1975, hig1985}.
+To visualize the flow, we plot the vorticity of the final time step from
+Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  In these
+examples, a small recirculation zone, both in size and magnitude, is
+present in the region where the vorticity is smallest
 
@@
 \end{subfigure}
-\caption{\label{fig:NearWall} A single body eroding in a Stokes flow.
-The color is the logarithm of the shear stress. Therefore, erosion is
-fastest in the red regions (upper half) and slowest in the blue regions
-(lower half).  The body is initialized at three different distances from
-the lower wall: (a) $h$, (b) $h/2$, and (c) $h/10$.}
+\caption{\label{fig:NearWall} A single body eroding in a shearing Stokes
+flow.  The color is the logarithm of the shear stress. Therefore,
+erosion is fastest in the red regions (upper half) and slowest in the
+blue regions (lower half).  The body is initialized at three different
+distances from the lower wall: (a) $h$, (b) $h/2$, and (c) $h/10$.}
 \end{center}
@@
 \caption{\label{fig:NearWall_vort} The vorticity of the fluid with a
-single body eroding at time t=0.1. The initial distance from the body to
-the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
+single body eroding at time $t=0.1$. The initial distance from the body
+to the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Bryan is here}
 We consider 20 eroding bodies that are discretized with $N_\iin=256$

### 2019-10-09 docs/transport/erosion_transport.tex
worked on abstract

@@
 \begin{abstract} 
-  We extend our previous work, [{\em Journal of Computational Physics},
-  {\bf 375}:1--21, 2018], to simulate fluid-mechanical erosion of
-  two-dimensional porous media with nearly-touching grains.  The method
-  continues to use a boundary integral equation (BIE) method to solve
-  the fluid equations, and a stable second-order time stepping method to
-  erode the grains.  In our previous work, we required eroding grains
-  that were sufficiently separated to guarantee that the trapezoid rule
-  provides a sufficient amount of accuracy. We now remove this
-  restriction by introducing a Barycentric quadrature rule whose error
-  is bounded independent of the geometry.  The Barycentric quadrature
-  rule is computationally expensive, so it is only used when necessary,
-  and the spectrally accurate fast-multipole-accelerated trapezoid rule
-  is used otherwise. We also simulate and analyze transport through
-  eroded porous media.  By using the Barycentric quadrature rule, the
-  analysis examines flow both in the fast and slow regions with
-  high-order accuracy. Our results reveal several interesting  effects
-  of erosion on the tortuosity, dispersion, and pore size distributions.
+  Transport of viscous fluid through porous media is a direct
+  consequence of the pore structure. Here we investigate transport
+  through specific two-dimensional porous geometries---those that have
+  become channelized by the process of fluid-mechanical erosion.  We
+  consider passive tracers in the eroded geometries and analyze their to
+  statistical moments to investigate the effect of erosion on the
+  tortuosity and dispersion rates. We compare the computed
+  porosity-tortuosity relationship with models available in the
+  literature. Finally, we analyze the pore size distribution of an
+  eroding geometry. The simulations are performed by combining a
+  high-fidelity boundary integral equation solver for the Stokes
+  equations, a second-order stable time stepping method to simulate
+  erosion, a new numerical method to stably and accurately compute the
+  eroded geometries and particle trajectories.
+
+%  We extend our previous work, [{\em Journal of Computational Physics},
+%  {\bf 375}:1--21, 2018], to simulate fluid-mechanical erosion of
+%  two-dimensional porous media with nearly-touching grains.  The method
+%  continues to use a boundary integral equation (BIE) method to solve
+%  the fluid equations, and a stable second-order time stepping method to
+%  erode the grains.  In our previous work, we required eroding grains
+%  that were sufficiently separated to guarantee that the trapezoid rule
+%  provides a sufficient amount of accuracy. We now remove this
+%  restriction by introducing a Barycentric quadrature rule whose error
+%  is bounded independent of the geometry.  The Barycentric quadrature
+%  rule is computationally expensive, so it is only used when necessary,
+%  and the spectrally accurate fast-multipole-accelerated trapezoid rule
+%  is used otherwise. We also simulate and analyze transport through
+%  eroded porous media.  By using the Barycentric quadrature rule, the
+%  analysis examines flow both in the fast and slow regions with
+%  high-order accuracy. Our results reveal several interesting  effects
+%  of erosion on the tortuosity, dispersion, and pore size distributions.
 \end{abstract}
@@
 \begin{keyword}
-  Porous media \sep Stokes flow \sep Erosion \sep Quadrature \sep
-  Transport \sep Tortuosity \sep Anomalous dispersion \sep Pore size
-  distributions
+  Porous media \sep Stokes flow \sep Erosion \sep Transport \sep
+  Tortuosity \sep Anomalous dispersion \sep Pore size distributions \sep
+  Quadrature
 \end{keyword}
@@
 
-\begin{figure}[H]
+\begin{figure}[htp]
 \begin{center}
@@
 investigate the effect of erosion on the pore size distribution.
-\begin{figure}[H]
+\begin{figure}[htp]
 \begin{subfigure}[b]{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[htp]
 \begin{center}
-\begin{subfigure}[b]{0.3\textwidth}
-\includegraphics[width = \textwidth]{./figs/1b_0d4r1h_shear}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.74\textwidth]{./figs/1b_0d4r1h_shear}
 \caption{}
 \end{subfigure}
-\begin{subfigure}[b]{0.3\textwidth}
-\includegraphics[width = \textwidth]{./figs/1b_0d4r0d5h_shear}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.74\textwidth]{./figs/1b_0d4r0d5h_shear}
 \caption{}
 \end{subfigure}
-\begin{subfigure}[b]{0.38\textwidth}
-\includegraphics[width =\textwidth]{./figs/1b_0d4r0d1h_shear}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.74\textwidth]{./figs/1b_0d4r0d1h_shear}
 \caption{}
 \end{subfigure}
+\end{center}
 \caption{\label{fig:NearWall} A single body eroding in a shearing Stokes
@@
 distances from the lower wall: (a) $h$, (b) $h/2$, and (c) $h/10$.}
-\end{center}
 \end{figure}
-\begin{figure}[H]
+\begin{figure}[htp]
 \begin{center}
-\begin{subfigure}[b]{0.3\textwidth}
-\includegraphics[width = \textwidth]{./figs/1b_0d4r1h_vort}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r1h_vort}
 \caption{}
 \end{subfigure}
-\begin{subfigure}[b]{0.3\textwidth}
-\includegraphics[width = \textwidth]{./figs/1b_0d4r0d5h_vort}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r0d5h_vort}
 \caption{}
 \end{subfigure}
-\begin{subfigure}[b]{0.33\textwidth}
-\includegraphics[width = \textwidth]{./figs/1b_0d4r0d1h_vort}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r0d1h_vort}
 \caption{}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Bryan is here}
 We consider 20 eroding bodies that are discretized with $N_\iin=256$
@@
 \end{align}
-where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
-to $x=2$ is held fixed at 8. Therefore, $U=1$ once all the bodies have
-vanished.  Snapshots of the bodies at four equispaced times are shown in
-Figure~\ref{fig:Eroding20vort}.  The color is the vorticity, whose
-absolute value is proportional to the erosion rate on solid boundaries.
-Initially, several of the eroding bodies are closer to the outer wall
-than the $5h$ threshold required for the trapezoid rule to achieve
-machine precision.  In particular, the distance between bodies 1, 6, 13,
-and 15 and the outer wall is $1.3h$, $2.9h$, $2.8h$, and $1.3h$,
-respectively, where $h$ is the arclength spacing of the outer wall
-$\Gamma$.  In addition, the distance between several pairs of eroding
-bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18, is too small to
-be accurately resolved with the trapezoid rule.  By using the
+where the flow rate $U$ is chosen so that the average pressure drop from
+$x=-2$ to $x=2$ is held fixed at 8. Therefore, $U=1$ once all the bodies
+have vanished.  Snapshots of the bodies at four equispaced times are
+shown in Figure~\ref{fig:Eroding20vort}.  The color is the vorticity,
+whose absolute value is proportional to the erosion rate on solid
+boundaries.  Initially, several of the eroding bodies are closer to the
+outer wall than the $5h$ threshold required for the trapezoid rule to
+achieve machine precision.  In particular, the distance between bodies
+1, 6, 13, and 15 and the outer wall is $1.3h$, $2.9h$, $2.8h$, and
+$1.3h$, respectively, where $h$ is the arclength spacing of the outer
+wall $\Gamma$.  In addition, the distance between several pairs of
+eroding bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18, is too
+small to be accurately resolved with the trapezoid rule.  By using the
 Barycentric quadrature rule, the interaction between these
-nearly-touching bodies can be accurately resolved to the desired
-accuracy, and erosion can be simulated until all the bodies have
-vanished.
-
-\begin{figure}[H]
+nearly-touching bodies is accurately resolved to the desired accuracy,
+and erosion can be simulated until all the bodies have vanished.
+
+\begin{figure}[htp]
 \begin{center}
@@
 qualitative behavior is seen in Figure~\ref{fig:Eroding20vort} between
-bodies 3 \& 4, 15 \& 16, and was also observed in previous work.
-However, by resolving the interaction between bodies that are much
-closer together than in previous work, we observe that very little
-erosion occurs between certain pairs of bodies, at least initially.  For
-instance the opening between bodies 1 \& 6, 3 \& 9, and 5 \& 13 grow
-much slower than the opening between bodies 15 \& 16.  A common feature
-of the pores that grow slowly is that they are nearly perpendicular to
-the main flow direction, resulting in a small erosion rate.
-
-Following our previous work~\cite{qua-moo2018}, we begin by analyzing
-the effect of erosion on the area fraction and the flow rate.  In
-Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
-function of normalized time.  The general trend of the area fraction
-resembles our previous work~\cite{qua-moo2018} (Figure 10(a)), but with
-a larger initial area fraction.  In
+bodies 3 \& 4, 15 \& 16, and was also observed in previous
+work~\cite{qua-moo2018}. However, by resolving the interaction between
+bodies that are much closer together than in previous work, we observe
+that very little erosion occurs between certain pairs of bodies, at
+least initially.  For instance the opening between bodies 1 \& 6, 3 \&
+9, and 5 \& 13 grow much slower than the opening between bodies 15 \&
+16.  A common feature of the pores that grow slowly is that they are
+nearly perpendicular to the main flow direction, resulting in a small
+erosion rate.
+
+\begin{figure}[htp]
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.7\linewidth]{./figs/porosity20dense}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.7\linewidth]{./figs/flow_rate20densen}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20
+nearly touching eroding bodies versus normalized time. (b) The flow
+rate, $U$, for a fixed pressure drop across the channel versus
+normalized time.  The flow rate is initially very small, but it
+eventually increases as an exponential law  (dashed line) towards the
+flow rate $U=1$ that occurs once all the bodies have eroded.}
+\end{figure}
+
+We next analyze the effect of erosion on the area fraction and the flow
+rate.  In Figure~\ref{fig:Eroding20flowrate}(a), we plot the area
+fraction as a function of normalized time.  The general trend of the
+area fraction resembles our previous work~\cite{qua-moo2018} (Figure
+10(a)), but with a larger initial area fraction.  In
 Figure~\ref{fig:Eroding20flowrate}(b), we plot the flow rate $U$
@@
 Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
-that the flow rate can be written as a exponential law.  The line of
+that the flow rate can be written as an exponential law.  The line of
 best fit is
@@
 \end{align}
-$t_f$ is the time required for all the bodies to erode, and $c$ is a
-fitting parameter. By construction $U = 1$ when $t=t_f$, so $c=-4,32$,
+where $t_f$ is the time required for all the bodies to erode, and $c$ is
+a fitting parameter. By construction $U = 1$ when $t=t_f$, so $c=-4.32$,
 and the flow rate is approximated as
@@
 
-\begin{figure}[H]
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.7\linewidth]{./figs/porosity20dense}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.7\linewidth]{./figs/flow_rate20densen}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20
-nearly touching eroding bodies versus normalized time. (b) The flow
-rate, $U$, for a fixed pressure drop across the channel versus
-normalized time.  The flow rate is initially very small, but it
-eventually increases as a power law (dashed line) towards the flow rate
-$U=1$ that occurs once all the bodies have eroded.}
-\end{figure}
-
-In Figure~\ref{fig:Eroding20vort}, we observe that erosion creates a
-network of channels from the inlet to outlet where the velocity and
-vorticity, and therefore erosion rate, are much larger than other
-regions.  These channels can be further visualized by considering the
-streamlines.  In Figure~\ref{fig:Eroding20tracer}, we freeze the
-geometry at the second snapshot from Figure~\ref{fig:Eroding20vort} and plot 200 streamlines that are initialized at $x=-1$ and equally
-spaced in $y \in (-1,1)$.  The streamlines are shown at five different
-times, and the final plot is a zoom in of the lower right quadrant of
-the fifth time step, but with additional streamlines.  Since we use a
-high-order quadrature rule and time stepping method, we resolve
-streamlines that come very close to the eroded bodies.  There are three
-clear regions where the streamlines are most concentrated, corresponding
-to the regions of highest velocity.  Two of these regions are located
-between the bodies and the solid walls at $y=\pm 1$, and the third cuts
-through the porous region with the upper part of the channel formed by
-bodies 1, 4, 6, and 8.  Since the flow is fastest in these regions, the
-shearing is largest, and this causes the channels to continue to open
-fastest as observed in Figure~\ref{fig:Eroding20vort}.
-
-\begin{figure}[H]
+\begin{figure}[htp]
 \begin{center}
@@
 is a zoom in of the fifth snapshot, but with additional streamlines.
-Since we use the Barycentric quadrature rule and the fourth-order
+Since we use the Barycentric quadrature rule and a fourth-order
 Runge-Kutta method, some streamlines are very close to the grains
@@
 
-Next, we use the streamlines to compute the tortuosity and the anomalous
-dispersion rates of eroding geometries.  To achieve statistical
-convergence, we use $N_p = 1000$ streamlines~\cite{bel-sal-rin1992}. To
-compute the tortuosity, we require the velocity at the inlet $x=-1$.
-These normalized velocities are plotted in
-Figure~\ref{fig:Eroding20tort}(a) for the eroded geometry at porosity
-$\phi = 62.9\%$ (Figure~\ref{fig:Eroding20tort}(c)).  The velocities are
-similar to the work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure
-4(a)), except that our cross-section, by construction, does not cut
-through any of the grains.  Next, in Figure~\ref{fig:Eroding20tort}(b),
-we plot the local tortuosity~\eqref{eqn:localTort} by calculating the
-relative length of each streamline as it traverses the channel from
-$x=-1$ to $x=1$.  The local tortuosity ranges from 1 to 1.27, meaning
-that one of the streamlines is 27\% longer than it would have been if
-the grains were absent.  The average streamline is 9.79\% longer or
-equivalently the tortuosity of the geometry is $1.098$.  Again,
-comparing the local tortuosity to Matyka~\cite{mat-kha-koz2008} (Figure
-4(b)), the results are qualitatively similar. However, since our initial
-cross-section does not cut through the grains, the local tortuosity does
-not have any gaps.  Discontinuities in local tortuosity occur when
-nearby streamlines diverge to circumvent a grain.  In
-Figure~\ref{fig:Eroding20tort}(c), we plot pairs of streamlines
-associated with the ten largest jumps in the local tortuosity, with each
-pair of corresponding streamlines plotted in the same color.
-
-\begin{figure}[H]
+In Figure~\ref{fig:Eroding20vort}, we observe that erosion creates a
+network of channels from the inlet to outlet where the velocity and
+vorticity, and therefore erosion rate, are much larger than other
+regions.  These channels can be further visualized  with the
+streamlines.  In Figure~\ref{fig:Eroding20tracer}, we freeze the
+geometry at the second snapshot from Figure~\ref{fig:Eroding20vort} and
+plot 200 streamlines that are initialized at $x=-1$ and equally spaced
+in $y \in (-1,1)$.  The streamlines are shown at five different times,
+and the final plot is a zoom in of the lower right quadrant of the fifth
+time step, but with additional streamlines.  Since we use a high-order
+quadrature rule and time stepping method, we resolve streamlines that
+come very close to the eroded bodies.  There are three clear regions
+where the streamlines are most concentrated, corresponding to the
+regions of highest velocity.  Two of these regions are located between
+the bodies and the solid walls at $y=\pm 1$, and the third cuts through
+the porous region with the upper part of the channel formed by bodies 1,
+4, 6, and 8.  Since the flow is fastest in these regions, the shearing
+is largest, and this causes the channels to continue to open fastest as
+observed in Figure~\ref{fig:Eroding20vort}.
+
+Next, we use the $N_p = 1000$~\cite{bel-sal-rin1992} streamlines to
+compute the tortuosity of the eroding geometry.  To compute the
+tortuosity, we require the velocity at the inlet $x=-1$.  These
+normalized velocities are plotted in Figure~\ref{fig:Eroding20tort}(a)
+for the eroded geometry at porosity $\phi = 62.9\%$
+(Figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
+work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure 4(a)), except
+that our cross-section, by construction, does not cut through any of the
+grains.  Next, in Figure~\ref{fig:Eroding20tort}(b), we plot the local
+tortuosity~\eqref{eqn:localTort} by calculating the relative length of
+each streamline as it traverses the channel from $x=-1$ to $x=1$.  The
+local tortuosity ranges from 1 to 1.27, meaning that one of the
+streamlines is 27\% longer than it would have been if the grains were
+absent.  The average streamline is 9.79\% longer or equivalently the
+tortuosity of the geometry is $1.098$.  Again, comparing the local
+tortuosity to Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results
+are qualitatively similar. However, since our initial cross-section does
+not cut through the grains, the local tortuosity does not have any gaps.
+Discontinuities in local tortuosity occur when nearby streamlines
+diverge to circumvent a grain.  In Figure~\ref{fig:Eroding20tort}(c), we
+plot pairs of streamlines associated with the ten largest jumps in the
+local tortuosity, with each pair of corresponding streamlines plotted in
+the same color.
+
+\begin{figure}[htp]
 \begin{subfigure}[b]{0.45\textwidth}
@@
 averaged tortuosity through the channel is $1.098$.  (c) The streamlines
-resulting in the ten largest differences between neighboring
-streamlines.  Neighboring streamlines have the same color.}
+resulting in the ten largest differences of local tortuosity between
+neighboring streamlines.  Neighboring streamlines have the same color.}
 \end{figure}
@@
 We computed lines of best fit using the porosity-tortuosity
-models~\eqref{eqn:tortuosityModels} and found the power law to give the
-smallest error.  The  black dashed line in
+models~\eqref{eqn:tortuosityModels} and found the power law that
+minimizes the error.  The  black dashed line in
 Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
 \begin{align}
-  \widehat{T}(\phi) = \phi^{-0.2064}
+  \widehat{T}(\phi) = \phi^{-0.2064},
 \end{align}
@@
 
-In Figure~\ref{fig:Eroding20Transport}(b), we plot the temporal
-evolution of the particle spreading $\sigma_\lambda$.  The spreading is
-computed for seven geometries of different porosities that are formed
-during the erosion process.  So that the spreading reaches a statistical
-equilibrium, we use the reinsertion algorithm described in
-Section~\ref{sec:dispersion} to form sufficiently long trajectories.
-For all the reported porosities, the particle dispersion exhibits two
-distinct power law regimes.  Initially, the dispersion is ballistic
-($\sigma_\lambda \sim t$) since individual fluid particles have not yet
-explored enough space to significantly alter their velocity.  However,
-once the particles have been subjected to a range of velocities, their
-dispersion slows, and we observe super-dispersive ($\sigma_\lambda \sim
-t^\alpha$, $\alpha \in (1/2,1)$) behavior over at least one order of
-magnitude in time.  Before any erosion takes place, the anomalous
-dispersion coefficient is $\alpha = 0.56$.  Then, as the grains begin to
-erode, the dispersion rate grows towards the ballistic regime that
-occurs in the absence of grains.  The monotonic increase in dispersion
-with respect to the porosity is explained by the onset of channels where
-many tracers experience less variability in their velocities.
-
-\begin{figure}[H]
+We next use streamlines to investigate the temporal evolution of the
+particle spreading $\sigma_\lambda$.  The spreading is computed for
+seven geometries of different porosities that are formed during the
+erosion process (Figure~\ref{fig:Eroding20Transport}(b)).  So that the
+spreading reaches a statistical equilibrium, we use the reinsertion
+algorithm described in Section~\ref{sec:dispersion} to form sufficiently
+long trajectories.  For all the reported porosities, the particle
+dispersion exhibits two distinct power law regimes.  Initially, the
+dispersion is ballistic ($\sigma_\lambda \sim t$) since individual fluid
+particles have not yet explored enough space to significantly alter
+their velocity.  However, once the particles have been subjected to a
+range of velocities, their dispersion slows, and we observe
+super-dispersive ($\sigma_\lambda \sim t^\alpha$, $\alpha \in (1/2,1)$)
+behavior over at least one order of magnitude in time.  Before any
+erosion takes place, the anomalous dispersion coefficient is $\alpha =
+0.56$.  Then, as the grains begin to erode, the dispersion rate grows
+towards the ballistic regime that occurs in the absence of grains.  The
+monotonic increase in dispersion with respect to the porosity is
+explained by the onset of channels where many tracers experience less
+variability in their velocities.
+
+\begin{figure}[htp]
 \begin{subfigure}[b]{0.5\textwidth}
@@
 
-In Figure~\ref{fig:ErodingLow20Transport}(b), we plot the temporal
-evolution of the particle spreading $\sigma_\lambda$.  As in the last
-example, we analyze the spreading at several different porosities and we
-use the reinsertion algorithm described in Section~\ref{sec:dispersion}
-to form sufficiently long trajectories to observe an asymptotic
-dispersion rate.  For all the porosities, the dispersion is much closer
-to ballistic when compared to the results in
-Figure~\ref{fig:Eroding20Transport}.  However, there are still clear
-transitions from ballistic dynamics to asymptotic super-dispersive
-spreading.  In contrast to the higher porosity initial condition
-(Section~\ref{sec:Eroding20}), at early times the erosion results in a
-decrease in the dispersion rate. In particular, the first 5\% of the
-bodies have eroded, the particle spreading transitions from
-$\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim t^{0.69}$.  To
-explain this behavior, recall that anomalous dispersion is caused by
-tracers spending time in both the fast and slow regimes.  Since the
-initial configuration has a reasonably uniform velocity (see
-Figure~\ref{fig:ErodingLow20vort}), albeit a small one, the dispersion
-is nearly ballistic. However, as the geometry erodes, the flow becomes
-more intermittent, and this results in an increased anomalous dispersion
-rate~\cite{dea-leb-den-tar-bol-dav2013}.  Then, as the bodies continue
-to erode, the geometry channelizes, and most tracers are transported
-with a large velocity through the channels, again resulting in a nearly
-ballistic motion~\cite{sie-ili-pri-riv-gua2019}.
-
-\begin{figure}[H]
+\begin{figure}[htp]
 \begin{subfigure}[b]{0.5\textwidth}
@@
 
+In Figure~\ref{fig:ErodingLow20Transport}(b), we plot the temporal
+evolution of the particle spreading $\sigma_\lambda$.  As in the last
+example, we analyze the spreading at several different porosities and we
+use the reinsertion algorithm described in Section~\ref{sec:dispersion}.
+For all the porosities, the dispersion is much closer to ballistic when
+compared to the results in Figure~\ref{fig:Eroding20Transport}.
+However, there are still clear transitions from ballistic dynamics to
+asymptotic super-dispersive spreading.  In contrast to the higher
+porosity initial condition (Section~\ref{sec:Eroding20}), at early times
+the erosion results in a decrease in the dispersion rate. In particular,
+after the first 5\% of the bodies have eroded, the particle spreading
+transitions from $\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim
+t^{0.69}$.  To explain this behavior, recall that anomalous dispersion
+is caused by tracers spending time in both the fast and slow regimes.
+Since the initial configuration has a reasonably uniform velocity (see
+Figure~\ref{fig:ErodingLow20vort}), albeit a small one, the dispersion
+is nearly ballistic. However, as the geometry erodes, the flow becomes
+more intermittent, and this results in an increased anomalous dispersion
+rate~\cite{dea-leb-den-tar-bol-dav2013}.  Then, as the bodies continue
+to erode, the geometry channelizes, and most tracers are transported
+with a large velocity through the channels, again resulting in a nearly
+ballistic motion~\cite{sie-ili-pri-riv-gua2019}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-As a final example, we consider 100 eroding bodies with an initial
-porosity near 50\%.  Snapshots of the configurations and vorticity are
-in Figure~\ref{fig:Eroding100vort}.  Again, by resolving near-contacts
-with the Barycentric quadrature rule, a stable simulation is possible
-with only $N_\iin = 256$ discretization points.
-
-\begin{figure}[H]
+\begin{figure}[htp]
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
+\includegraphics*[height =0.8\linewidth]{./figs/100b_50}
 \caption{100 bodies, $\phi = 55.54\%$}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
+\includegraphics*[height =0.8\linewidth]{./figs/100b_100}
 \caption{99 bodies, $\phi = 62.98\%$}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
+\includegraphics*[height =0.8\linewidth]{./figs/100b_150}
 \caption{94 bodies, $\phi = 72.22\%$}
@@
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
+\includegraphics*[height =0.8\linewidth]{./figs/100b_200}
 \caption{82 bodies, $\phi = 83.67\%$}
@@
 
-We compute the tortuosity using both the
-Lagrangian~\eqref{eqn:tortuosity1} and Eulerian
+As a final example, we consider 100 eroding bodies, each with
+$N_\iin=256$ discretization points, with an initial porosity near 50\%.
+Snapshots of the configurations and vorticity are in
+Figure~\ref{fig:Eroding100vort}. We compute the tortuosity using both
+the Lagrangian~\eqref{eqn:tortuosity1} and Eulerian
 methods~\eqref{eqn:tortuosity2}. Therefore, we must compute the velocity
@@
 
-\begin{figure}[H]
+\begin{figure}[htp]
 \begin{subfigure}[b]{0.45\textwidth}
@@
 that this maximum velocity is about a order of magnitude smaller than
-when compared to the 20 body example in Figure~\ref{fig:Eroding20tort}.
-(b) The local tortuosity $\tau(y)$ on the cross section $x = -1$. The
-spatially averaged tortuosity through the channel is $1.12$. (c) The
-trajectories of 200 tracers initialized at $x = -1$.  The
-discontinuities in the local tortuosity correspond to nearby streamlines
-whose lengths are significantly different because they pass opposite
-sides of an eroding body. Compared to Figure~\ref{fig:Eroding20tort},
-this example has more small bodies, and this results in many more
-discontinuities.}
+the 20 body example in Figure~\ref{fig:Eroding20tort}.  (b) The local
+tortuosity $\tau(y)$ on the cross section $x = -1$. The spatially
+averaged tortuosity through the channel is $1.12$. (c) The trajectories
+of 200 tracers initialized at $x = -1$.  The discontinuities in the
+local tortuosity correspond to nearby streamlines whose lengths are
+significantly different because they pass opposite sides of an eroding
+body. Compared to Figure~\ref{fig:Eroding20tort}, this example has more
+small bodies, and this results in many more discontinuities.}
 \end{figure}
@@
 straighter streamlines, therefore reducing $\lambda$, the horizontal
-flow, $u_1(y)$ increases since there is no longer a no-slip boundary.
-We also computed the lines of best fit using the porosity-tortuosity
-models~\eqref{eqn:tortuosityModels}.  The black dashed line in
-Figure~\ref{fig:Eroding100Transport}(a) is the line of best fit
-\begin{align}
-  \widehat{T}(\phi) = \phi^{-0.2459}
+flow, $u_1(y)$ increases since there is no longer a no-slip boundary,
+and this increases the tortuosity.  We also computed the lines of best
+fit using the porosity-tortuosity models~\eqref{eqn:tortuosityModels}.
+The black dashed line in Figure~\ref{fig:Eroding100Transport}(a) is the
+line of best fit
+\begin{align}
+  \widehat{T}(\phi) = \phi^{-0.2459},
 \end{align}
@@
 
-\begin{figure}[H]
+\begin{figure}[htp]
 \begin{subfigure}[b]{0.5\textwidth}
@@
 
-HERE
-In Figure~\ref{fig:Eroding100gap_hist}, we plot
-histograms of the pore pore sizes at six porosities during the erosion
-process. These types of distributions have been described with Weibull
+In Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the pore
+pore sizes at six porosities during the erosion process. These types of
+distributions have been described with Weibull
 distributions~\cite{ioa-cha1993}, and we superimpose the Weibull
@@
 
-\begin{figure}[H]
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{figure}[htp]
+\begin{subfigure}[b]{0.33\textwidth}
 \includegraphics*[width =\linewidth]{./figs/hist100b_1}
@@
 \end{subfigure}%
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.33\textwidth}
 \includegraphics*[width =\linewidth]{./figs/hist100b_46}
@@
 \end{subfigure}%
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.33\textwidth}
 \includegraphics*[width =\linewidth]{./figs/hist100b_112}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.33\textwidth}
 \includegraphics*[width =\linewidth]{./figs/hist100b_164}
@@
 \end{subfigure}%
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.33\textwidth}
 \includegraphics*[width =\linewidth]{./figs/hist100b_207}
@@
 \end{subfigure}%
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.33\textwidth}
 \includegraphics*[width =\linewidth]{./figs/hist100b_246}
@@
 equations and to compute the shear stress. However, to simulate
-nearly-touching grains and to consider transport, it is necessary to
+nearly-touching grains and to characterize transport, it is necessary to
 integrate near-singular functions. This is achieved by extending a
@@
 super-dispersive spreading, and the rate of dispersion significantly
-depends not only on the porosity, but also the number of eroding bodies.
+depends not only on the porosity, but also the number of eroding bodies
+and their distribution.
 
@@
 
-As a long term goal, we would like to include the effect of inertia and
-other transport models. Including inertia requires an integral equation
+As a long term goal, we hope to include the inertial effects and other
+transport models. Including inertia requires an integral equation
 formulation of the Navier-Stokes equations, which is an active area of
-research with a few promising algorithms recently
+research with a few promising directions recently
 proposed~\cite{gray2019boundary, kli-ask-kro2019}.  Regarding other
@@
 State University startup funds and Simons Foundation Mathematics and
-Physical Sciences-Collaboration Grants for Mathematicians.
+Physical Sciences-Collaboration Grants for Mathematicians 527139 and
+524259.
 

### 2019-10-09 docs/transport/erosion_transport.tex
starting to move to JFM format

@@
-\documentclass[preprint,10pt]{elsarticle}
+%\documentclass[preprint,10pt]{elsarticle}
+\documentclass{jfm}
 
@@
 %\usepackage{showkeys}
+
+\usepackage{graphicx}
+\usepackage{epstopdf, epsfig}
+
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
+
+\shorttitle{Viscous Transport in Eroding Porous Media}
+\shortauthor{Chiu, Moore and Quaife}
+
+\title{Viscous Transport in Eroding Porous Media}
+
+\author{Shang-Huan Chiu\aff{1}, M.~N.~J.~Moore\aff{2}, and Bryan
+Quaife\aff{3}\corresp{\email{bquaife@fsu.edu}}}
+
+%  Alan N. Other\aff{1}
+%  \corresp{\email{jfm@damtp.cam.ac.uk}},
+%  H. - C. Smith\aff{1}
+% \and J. Q.  Public\aff{2}}
+
+\affiliation{
+\aff{1}Department of Scientific Computing, Florida State University,
+Florida State University, Tallahassee, FL 32306, USA
+\aff{2}Department of Mathematics and Geophysical Fluid Dynamics
+Institute, Florida State University, Tallahassee, FL 32306, USA
+\aff{3}Department of Scientific Computing and Geophysical Fluid Dynamics
+Institute, Florida State University, Tallahassee, FL 32306, USA
+}
+
 \begin{document}
 
-\title{Viscous Transport in Eroding Porous Media}
-
-% OTHER TITLE POSSIBILITIES
-% ???
-
-\author[SH]{Shang-Huan Chiu}
-\author[Nick]{M.~N.~J.~Moore}
-\author[Bryan]{Bryan D.~Quaife}
-
-\address[SH]{Department of Scientific Computing, Florida State
-University, Tallahassee, FL, 32306.}
-\address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics
-Institute, Florida State University, Tallahassee, FL, 32306.}
-\address[Bryan]{Department of Scientific Computing and Geophysical Fluid
-Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+%\title{Viscous Transport in Eroding Porous Media}
+%
+%\author[SH]{Shang-Huan Chiu}
+%\author[Nick]{M.~N.~J.~Moore}
+%\author[Bryan]{Bryan D.~Quaife}
+%
+%\address[SH]{Department of Scientific Computing, Florida State
+%University, Tallahassee, FL, 32306.}
+%\address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics
+%Institute, Florida State University, Tallahassee, FL, 32306.}
+%\address[Bryan]{Department of Scientific Computing and Geophysical Fluid
+%Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
 
@@
   consequence of the pore structure. Here we investigate transport
-  through specific two-dimensional porous geometries---those that have
-  become channelized by the process of fluid-mechanical erosion.  We
-  consider passive tracers in the eroded geometries and analyze their to
-  statistical moments to investigate the effect of erosion on the
-  tortuosity and dispersion rates. We compare the computed
-  porosity-tortuosity relationship with models available in the
-  literature. Finally, we analyze the pore size distribution of an
-  eroding geometry. The simulations are performed by combining a
-  high-fidelity boundary integral equation solver for the Stokes
-  equations, a second-order stable time stepping method to simulate
-  erosion, a new numerical method to stably and accurately compute the
-  eroded geometries and particle trajectories.
+  through specific two-dimensional porous geometries---those that are
+  formed by fluid-mechanical erosion.  We investigate the tortuosity and
+  dispersion by analyzing the first two statistical moments of tracer
+  trajectories. For most geometries, the tortuosity decreases as erosion
+  increases the porosity; however, interestingly, it is possible for
+  erosion to increase the tortuosity. The simulated porosity-tortuosity
+  relationships are compared with models available in the literature.
+  Unsurprisingly, the asymptotic dispersion rate is also affected by the
+  erosion process, but it is also affected by the number of and
+  distribution of the eroding bodies.  Finally, we analyze the pore size
+  distribution of an eroding geometry. The simulations are performed by
+  combining a high-fidelity boundary integral equation solver for the
+  fluid equations, a second-order stable time stepping method to
+  simulate erosion, and new numerical methods to stably and accurately
+  resolve nearly-touching eroded bodies and particle trajectories near
+  the eroding bodies.
 
@@
 
-\begin{keyword}
-  Porous media \sep Stokes flow \sep Erosion \sep Transport \sep
-  Tortuosity \sep Anomalous dispersion \sep Pore size distributions \sep
-  Quadrature
-\end{keyword}
+%\begin{keyword}
+%  Porous media \sep Stokes flow \sep Erosion \sep Transport \sep
+%  Tortuosity \sep Anomalous dispersion \sep Pore size distributions \sep
+%  Quadrature
+%\end{keyword}
 
@@
 can vary from $10^{-6}\mathrm{m}$ to
-$10^{-1}\mathrm{m}$~\cite{mil-chr-imh-mcb-ped1998} and velocity scales
-can be as small as $10^{-1}\mathrm{m/day}$~\cite{kut-scr-dav-ham1995}.
+$10^{-1}\mathrm{m}$~\citep{mil-chr-imh-mcb-ped1998} and velocity scales
+can be as small as $10^{-1}\mathrm{m/day}$~\citep{kut-scr-dav-ham1995}.
 Moreover, for a single porous geometry, the pore sizes and velocities
@@
 resolve this range of scales offer the ability to: (i) characterize
-dispersion~\cite{saf1959}, (ii) quantify
-mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}, and
+dispersion~\citep{saf1959}, (ii) quantify
+mixing~\citep{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}, and
 (iii) develop meaningful constitutive relationships that link the
-microscopic and macroscopic realms~\cite{mil-chr-imh-mcb-ped1998}.
+microscopic and macroscopic realms~\citep{mil-chr-imh-mcb-ped1998}.
 Examples of coarse-grained models for porous media flow include
 pressure-saturation-permeability
-relationships~\cite{mil-chr-imh-mcb-ped1998}, permeability-porosity
-relationships~\cite{dar-mcc1998, car1937, won-kop-tom1984}, first
-passage time distributions~\cite{ber-sch-sil2000, hym-den-hag-kan2019,
-cve-che-wen1996}, tortuosities~\cite{hak-com-den2019, mat-kha-koz2008,
+relationships~\citep{mil-chr-imh-mcb-ped1998}, permeability-porosity
+relationships~\citep{dar-mcc1998, car1937, won-kop-tom1984}, first
+passage time distributions~\citep{ber-sch-sil2000, hym-den-hag-kan2019,
+cve-che-wen1996}, tortuosities~\citep{hak-com-den2019, mat-kha-koz2008,
 dud-koz-mat2011, kop-kat-tim1996}, concentration
-distributions~\cite{ica-den2019, bel-sal-rin1992}, pore and flow
-distributions~\cite{ali-par-wei-bre2017}, geometry
-connectivity~\cite{knu-car2005, wes-blo-gra2001}, anomalous
-dispersion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
+distributions~\citep{ica-den2019, bel-sal-rin1992}, pore and flow
+distributions~\citep{ali-par-wei-bre2017}, geometry
+connectivity~\citep{knu-car2005, wes-blo-gra2001}, anomalous
+dispersion~\citep{dea-qua-bir-jua2018, den-cor-sch-ber2004,
 sie-ili-pri-riv-gua2019}, and more.
@@
 and the flow occurs, for example, in applications involving
-melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular,
+melting~\citep{bec-vis1998, rycroft2016asymmetric, jambon2018singular,
 favier2019rayleigh, morrow2019moving},
-dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017,
-wykes2018self}, deposition~\cite{joh-eli1995, hewett2018modelling},
-biofilm growth~\cite{tan-val-wer2015}, and crack
-formation~\cite{cho2019crack}. We focus on erosion, a fluid-mechanical
+dissolution~\citep{kan-zha-che-he2002, mac2015shape, moo2017,
+wykes2018self}, deposition~\citep{joh-eli1995, hewett2018modelling},
+biofilm growth~\citep{tan-val-wer2015}, and crack
+formation~\citep{cho2019crack}. We focus on erosion, a fluid-mechanical
 process that is prevalent in many geophysical, hydrological, and
-industrial applications~\cite{berhanu2012shape, hewett2017evolution,
+industrial applications~\citep{berhanu2012shape, hewett2017evolution,
 lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
@@
 in number and modest in volume fraction, transmit a large portion of the
-flux \cite{qua-moo2018}. This arrangement results in velocities that
-vary over several orders of magnitude~\cite{all-hea-lab-rei2002}.
+flux \citep{qua-moo2018}. This arrangement results in velocities that
+vary over several orders of magnitude~\citep{all-hea-lab-rei2002}.
 Moreover, channelization creates heterogeneous and anisotropic medium
 properties, which affect the transport of tracers such as
-contaminants~\cite{cve-che-wen1996, dag1987, kon-bre1978} and
-heat~\cite{nil-sto1990, ree-sto1995}.
+contaminants~\citep{cve-che-wen1996, dag1987, kon-bre1978} and
+heat~\citep{nil-sto1990, ree-sto1995}.
 
@@
 tracer transport through the resulting eroded geometries. Our modeling
-efforts build on previous work~\cite{ris-moo-chi-she-zha2012,
+efforts build on previous work~\citep{ris-moo-chi-she-zha2012,
 moore2013self, moo2017}, in particular recent numerical methods
 developed to simulate erosion in the Stokes-flow
-regime~\cite{qua-moo2018}. We, however, make key improvements to the
-numerical methods from~\cite{qua-moo2018} to enable simulations of more
+regime~\citep{qua-moo2018}. We, however, make key improvements to the
+numerical methods from~\citep{qua-moo2018} to enable simulations of more
 realistic, dense suspensions of eroding grains
-(Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  Then, to
+(figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  Then, to
 characterize transport through these configurations, we examine
@@
 
-\begin{figure}[htp]
+\begin{figure}
 \begin{center}
-\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b1}
-\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b80}
-\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b160}\\
-\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b240}
-\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b320}
-\includegraphics[height = 0.31 \textwidth]{./figs/vel_log_50b400}
+\includegraphics[height = 0.3 \textwidth]{./figs/vel_log_50b1}
+\includegraphics[height = 0.3 \textwidth]{./figs/vel_log_50b80}
+\includegraphics[height = 0.3 \textwidth]{./figs/vel_log_50b160}\\
+\includegraphics[height = 0.3 \textwidth]{./figs/vel_log_50b240}
+\includegraphics[height = 0.3 \textwidth]{./figs/vel_log_50b320}
+\includegraphics[height = 0.3 \textwidth]{./figs/vel_log_50b400}
 \caption{\label{fig:Eroding50vel} Six evenly spaced snapshots of 50
@@
 
-Owing to the scales present in groundwater flow~\cite{bea1972}, we model
+Owing to the scales present in groundwater flow~\citep{bea1972}, we model
 the hydrodynamics with the two-dimensional incompressible Stokes
 equations.  Meanwhile, individual grains erode at a rate proportional to
-the hydrodynamic shear stress~\cite{wan-fel2004,
+the hydrodynamic shear stress~\citep{wan-fel2004,
 ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  Since the
@@
 also compute the fluid vorticity for visualization purposes
-(Figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
+(figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
 the fluid solver are available including lattice-gas or lattice
-Boltzmann~\cite{kop-kat-tim1996, dar-mcc1998}, finite
-volumes~\cite{suo-liu-gan2019, den-ica-hid2018,
-sie-ili-pri-riv-gua2019}, finite differences~\cite{leb-ded-dav-bou2007,
-knu-car2005}, and cellular automata~\cite{rot1988}.  However, simulating
+Boltzmann~\citep{kop-kat-tim1996, dar-mcc1998}, finite
+volumes~\citep{suo-liu-gan2019, den-ica-hid2018,
+sie-ili-pri-riv-gua2019}, finite differences~\citep{leb-ded-dav-bou2007,
+knu-car2005}, and cellular automata~\citep{rot1988}.  However, simulating
 erosion requires a method that is high-order, can resolve
@@
 both space and time. The time integration method is unchanged from
-previous work~\cite{qua-moo2018}.  We apply a mild regularization and a
+previous work~\citep{qua-moo2018}.  We apply a mild regularization and a
 smoothing term to eliminate numerical instabilities that can be triggered by changes in
 sign of the shear stress, and we use a stable second-order Runge-Kutta
-method applied to the {\thL} coordinates~\cite{hou-low-she1994} of the
+method applied to the {\thL} coordinates~\citep{hou-low-she1994} of the
 eroding grains.  In this work, we introduce a new quadrature method to
@@
 trapezoid rule, which was used in previous work, is adequate for
-bodies that are sufficiently separated~\cite{tre-wei2014}.  However, it
+bodies that are sufficiently separated~\citep{tre-wei2014}.  However, it
 loses accuracy whenever grains are in close contact.  One of the
 earliest works to address quadrature methods for nearly-singular
-integrands was developed by Baker and Shelley~\cite{bak-she1986}, and in
+integrands was developed by Baker and Shelley~\citep{bak-she1986}, and in
 recent years, many other near-singular integration schemes have
-followed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
+followed~\citep{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
 bea-lai2001, klo-bar-gre-one2013}.  We use a Barycentric quadrature
-method~\cite{bar2014, bar-wu-vee2015} since it is a non-intrusive
+method~\citep{bar2014, bar-wu-vee2015} since it is a non-intrusive
 modification of the trapezoid rule, and the error is guaranteed to be
@@
 
-\begin{figure}[htp]
+\begin{figure}
 \begin{center}
@@
 \caption{\label{fig:Eroding50vort} The same six snapshots as
-Figure~\ref{fig:Eroding50vel}.  The color is the vorticity of the fluid.
+figure~\ref{fig:Eroding50vel}.  The color is the vorticity of the fluid.
 Since the rate of erosion is equivalent to the magnitude of the
@@
 trajectories must be computed. Depending on the application, microscale
-transport can be modelled as pure advection~\cite{dea-qua-bir-jua2018,
+transport can be modelled as pure advection~\citep{dea-qua-bir-jua2018,
 leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019},
-advection-diffusion~\cite{cus-hu-den1995, dag1987, den-ica-hid2018}, or
-with a random walk~\cite{saf1959, bij-blu2006, ber-sch-sil2000}.  In
+advection-diffusion~\citep{cus-hu-den1995, dag1987, den-ica-hid2018}, or
+with a random walk~\citep{saf1959, bij-blu2006, ber-sch-sil2000}.  In
 this work, we assume trajectories to be governed by pure advection
@@
 to form a distribution of velocities $\uu$ and use a continuous time
-random walk~\cite{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
+random walk~\citep{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
 ber-cor-den-sch2006}.
@@
 In porous media, the local tortuosity can be greater than
-1.5~\cite{kop-kat-tim1996, mat-kha-koz2008} or even
-2~\cite{dud-koz-mat2011}, depending on several factors such as the
+1.5~\citep{kop-kat-tim1996, mat-kha-koz2008} or even
+2~\citep{dud-koz-mat2011}, depending on several factors such as the
 porosity. The tortuosity of a geometry is defined by averaging the local
@@
 geometry's tortuosity characterizes average particle
-motions~\cite{hak-com-den2019}.  To characterize spreading, the fluid
+motions~\citep{hak-com-den2019}.  To characterize spreading, the fluid
 dispersion is computed by calculating the variance of the streamline
 lengths. In porous media, this spreading is often
-super-dispersive~\cite{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
+super-dispersive~\citep{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
 dea-leb-den-tar-bol-dav2013}. Since anomalous dispersion results from
 streamlines spending time in both the high and low velocity
-regimes~\cite{ber-sch2001}, it is crucial to accurately resolve
+regimes~\citep{ber-sch2001}, it is crucial to accurately resolve
 streamlines near grain boundaries, as achieved in this work.  Finally,
@@
 These distributions are required to quantify velocity
-distributions~\cite{ali-par-wei-bre2017, dea-qua-bir-jua2018},
-channelization~\cite{sie-ili-pri-riv-gua2019},
-connectivity~\cite{knu-car2005, wes-blo-gra2001}, and to develop network
-models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
+distributions~\citep{ali-par-wei-bre2017, dea-qua-bir-jua2018},
+channelization~\citep{sie-ili-pri-riv-gua2019},
+connectivity~\citep{knu-car2005, wes-blo-gra2001}, and to develop network
+models~\citep{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
 
@@
 Our first contribution is extending the Barycentric quadrature rule of
-Barnett et al.~\cite{bar-wu-vee2015} to accurately compute velocity
+Barnett et al.~\citep{bar-wu-vee2015} to accurately compute velocity
 gradients associated with Stokes flow. This new quadrature rule permits
@@
 \paragraph{Limitations}
-As in our previous work~\cite{qua-moo2018}, we consider two-dimensional
+As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
 immobile eroding grains. However, this work does not limit the proximity
@@
 In Section~\ref{sec:formulation}, we summarize the erosion model that is
-described in more detail in previous work~\cite{qua-moo2018}.  In
+described in more detail in previous work~\citep{qua-moo2018}.  In
 Section~\ref{sec:DLP}, we recast all the governing equations as layer
@@
 briefly summarize the model, and a more detailed description can be
-found in previous work~\cite{qua-moo2018}.  We consider flows inside a
+found in previous work~\citep{qua-moo2018}.  We consider flows inside a
 confined geometry $\Omega$ that contains $M$ eroding bodies with
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Applying the same approach as our previous work~\cite{qua-moo2018}, we
+Applying the same approach as our previous work~\citep{qua-moo2018}, we
 start with the double-layer potential 
@@
   \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
-  \frac{1}{\pi}\int_{\bd\Omega} 
+  \frac{1}{\upi}\int_{\bd\Omega} 
     \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
@@
 all the solutions. Therefore, we complete the integral equation
-formulation by adding the $M$ Stokeslets and rotlets~\cite{pow-mir1987}
-\begin{align}
-  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
+formulation by adding the $M$ Stokeslets and rotlets~\citep{pow-mir1987}
+\begin{align}
+  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\upi} \left( 
     -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2}
@@
     \NN_0[\eeta](\xx), \quad &&\xx \in \bd\Omega, \\
-  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
+  \llambda_\ell &= \frac{1}{2\upi} \int_{\gamma_\ell} 
     \eeta(\yy)\, ds_\yy, &&\ell = 1,\ldots,M, \\
-  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
+  \xi_\ell &= \frac{1}{2\upi} \int_{\gamma_\ell}
     (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
@@
       \eeta(\yy) ds_{\yy} 
-  = \frac{1}{2\pi}\int_{\bd\Omega} \left(
+  = \frac{1}{2\upi}\int_{\bd\Omega} \left(
     2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
@@
       \eeta(\yy) ds_{\yy} 
-  = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
+  = -\frac{1}{\upi}\int_{\bd\Omega} \frac{1}{\rho^2}
     \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
@@
       \eeta(\yy) ds_{\yy} 
-  = -\frac{1}{\pi} \int_{\bd\Omega}
+  = -\frac{1}{\upi} \int_{\bd\Omega}
     \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
@@
 associated components of the deformation tensor, pressure, and vorticity
-are straightforward to compute~\cite{poz1992}.  Having computed the
+are straightforward to compute~\citep{poz1992}.  Having computed the
 deformation tensor on $\gamma$, the shear stress is computed using
@@
 \begin{align}
-  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
+  \DD[\eeta](\xx) = \frac{1}{2\upi} \int_{\bd\Omega} 
     \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Re (v(x)) \quad 
-    \text{where} \quad v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+    \text{where} \quad v(x) = \frac{1}{2\upi i} \int_{\bd\Omega}
     \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega,
@@
   \label{eqn:SPrelation}
-  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
+  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\upi i} \int_{\bd\Omega}
     \frac{\eta(y)}{x-y}\, dy, \quad x \in \Omega.
@@
   \label{eqn:cauchy}
-  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
+  v(x) = \frac{1}{2\upi i}\int_{\bd\Omega} 
     \frac{v(y)}{y-x} \,dy, \quad
-  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+  v'(x) = \frac{1}{2\upi i} \int_{\bd\Omega}
     \frac{v(y)}{(y-x)^2} \, dy, \quad
-  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
+  v''(x) = \frac{1}{\upi i} \int_{\bd\Omega}
     \frac{v(y)}{(y-x)^3} \, dy,
@@
     \DDD[\eeta](\xx) &= 
-      \frac{1}{2\pi} \int_{\bd\Omega} 
+      \frac{1}{2\upi} \int_{\bd\Omega} 
         \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
-      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
+      \frac{1}{2\upi} \nabla \int_{\bd\Omega}
         \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
-      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
+      &- \frac{1}{2\upi} x_1 \nabla \int_{\bd\Omega}
         \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
-      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
+      \frac{1}{2\upi} x_2 \nabla \int_{\bd\Omega}
         \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
@@
 Therefore, the Stokes double-layer potential can be written as a sum of
-Cauchy integrals and its first derivative~\cite{bar-wu-vee2015}
+Cauchy integrals and its first derivative~\citep{bar-wu-vee2015}
 \begin{equation}
@@
 Erosion in porous media leads to particular phenomena such as
-channelization~\cite{berhanu2012shape}, and we are interested in
+channelization~\citep{berhanu2012shape}, and we are interested in
 characterizing transport in such geometries.  In our previous
-work~\cite{qua-moo2018}, we examined the effect of erosion on the area
+work~\citep{qua-moo2018}, we examined the effect of erosion on the area
 fraction, flow rate, and the total drag.  However, to characterize
@@
 The spreading of fluid in a porous media is often characterized in terms
-of anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.
+of anomalous dispersion~\citep{kla-rad-sok2008, den-cor-sch-ber2004}.
 The anomalous dispersion rate depends on the porosity and
-permeability~\cite{koc-bra1988}, but is also affected by the
+permeability~\citep{koc-bra1988}, but is also affected by the
 distribution and shape of the grains. We calculate the anomalous
@@
 use a reinsertion method to form longer trajectories. Similar to the
-work of others~\cite{dea-qua-bir-jua2018, puy-gou-den2019}, once a
+work of others~\citep{dea-qua-bir-jua2018, puy-gou-den2019}, once a
 particle reaches the outlet of the porous region, it is reinserted at
@@
 at $x=1$, so $d=2$.  However, other choices for the terminal point when
-computing the tortuosity are sometime used~\cite{dud-koz-mat2011}.  The
+computing the tortuosity are sometime used~\citep{dud-koz-mat2011}.  The
 hydraulic tortuosity is defined by taking the average over all points on
@@
 the two cross-sections, the tortuosity in
-equation~\eqref{eqn:tortuosity1} is equivalent to~\cite{dud-koz-mat2011}
+equation~\eqref{eqn:tortuosity1} is equivalent to~\citep{dud-koz-mat2011}
 \begin{align}
@@
 cross-sections.  Recirculation zones are possible in viscous
-fluids~\cite{hig1985}, but they are very small in the examples we
+fluids~\citep{hig1985}, but they are very small in the examples we
 consider and have a negligible effect on the tortuosity.  Since
@@
 There have been efforts to relate the tortuosity, $T$, to the porosity,
-$\phi$.  For example, Matyka et al.~\cite{mat-kha-koz2008} propose the
+$\phi$.  For example, Matyka et al.~\citep{mat-kha-koz2008} propose the
 models
@@
 on the placement of the grains.  In particular, grain placement affects
-velocity scales~\cite{ali-par-wei-bre2017}, correlation
-structures~\cite{leb-ded-dav-bou2007}, contaminant
-transport~\cite{knu-car2005},
-channelization~\cite{sie-ili-pri-riv-gua2019,berhanu2012shape}, and pore
-network models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}. To
+velocity scales~\citep{ali-par-wei-bre2017}, correlation
+structures~\citep{leb-ded-dav-bou2007}, contaminant
+transport~\citep{knu-car2005},
+channelization~\citep{sie-ili-pri-riv-gua2019,berhanu2012shape}, and pore
+network models~\citep{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}. To
 characterize the grain placement, we compute distributions of pore sizes
@@
 media.  Then, we say that two grains are neighbors if their centers
-share an edge of the triangulation~\cite{dea-qua-bir-jua2018}. The pores
+share an edge of the triangulation~\citep{dea-qua-bir-jua2018}. The pores
 of an eroded geometry are illustrated in
-Figure~\ref{fig:Eroding100gap}(a). We do not consider pores between
+figure~\ref{fig:Eroding100gap}(a). We do not consider pores between
 eroding bodies and the solid wall $\Gamma$, so some of the grains near
@@
 pore sizes, we plot its distribution in
-Figure~\ref{fig:Eroding100gap}(b) and compare it with the Weibull
+figure~\ref{fig:Eroding100gap}(b) and compare it with the Weibull
 distribution, a distribution used by others to characterize pore
-sizes~\cite{ioa-cha1993}.  In Section~\ref{sec:Eroding100}, we
+sizes~\citep{ioa-cha1993}.  In Section~\ref{sec:Eroding100}, we
 investigate the effect of erosion on the pore size distribution.
-\begin{figure}[htp]
+\begin{figure}
 \begin{subfigure}[b]{0.5\textwidth}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In line with our previous work~\cite{qua-moo2018}, we use two meshes to
+In line with our previous work~\citep{qua-moo2018}, we use two meshes to
 simulate erosion. The integral equation is solved by discretizing the
@@
 are eroded a single time step by using a {\thL}
-discretization~\cite{hou-low-she1994, moore2013self}.  The time stepping
+discretization~\citep{hou-low-she1994, moore2013self}.  The time stepping
 methods for erosion and passive particles are described in
@@
 the {\thL} formulation.  In addition, we apply
-regularization~\cite{qua-moo2018} to slightly smooth the corners that
+regularization~\citep{qua-moo2018} to slightly smooth the corners that
 inevitably develop during erosion.
@@
 %
-  \llambda_m &= \frac{1}{2\pi} \sum_{j=1}^{N_\iin} w_j^m \eeta^m_j,
-  \quad \xi_m = \frac{1}{2\pi} \sum_{j=1}^{N_\iin} w_j^m
+  \llambda_m &= \frac{1}{2\upi} \sum_{j=1}^{N_\iin} w_j^m \eeta^m_j,
+  \quad \xi_m = \frac{1}{2\upi} \sum_{j=1}^{N_\iin} w_j^m
     (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
@@
 While the trapezoid rule is spectrally accurate for smooth, periodic
-functions~\cite{tre-wei2014}, the derivative of the integrand grows as
+functions~\citep{tre-wei2014}, the derivative of the integrand grows as
 the target point $\xx$ approaches $\bd\Omega$. The result is an error
@@
 quadrature rule with a uniform error bound for Cauchy integrals and its
-derivatives~\eqref{eqn:cauchy}. Ioakimidis et al.~\cite{ioa-pap-per1991}
+derivatives~\eqref{eqn:cauchy}. Ioakimidis et al.~\citep{ioa-pap-per1991}
 developed quadrature rules, that we call {\em Barycentric quadrature
@@
 bound that is independent of $x \in \CC$.  Then, Barnett et
-al.~\cite{bar-wu-vee2015} used these quadrature rules to compute the
+al.~\citep{bar-wu-vee2015} used these quadrature rules to compute the
 Stokes double-layer potential representation of the
@@
 quadrature rule for $v''(x)$.  The derivation is largely based on the
-work of Ioakimidis et al.~\cite{ioa-pap-per1991} (see equation (2.12)).
+work of Ioakimidis et al.~\citep{ioa-pap-per1991} (see equation (2.12)).
 We start with the second derivative of the Cauchy integral theorem
 \begin{align}
-  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
+  0 = \frac{1}{2\upi i} \int_{\bd\Omega} 
       \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x).
@@
 \begin{align}
-  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
+  \frac{1}{2\upi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
   \left\{
@@
 \begin{align}
-  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
+  0 = \frac{1}{2\upi i} \int_{\bd\Omega} 
       \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
@@
 \begin{align}
-\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
+\frac{1}{x-a} &= -\frac{1}{2\upi i}\int_{\bd\Omega} 
     \frac{(y-a)^{-1}}{y-x}\, dy. 
@@
 \begin{align}
-  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
+  0 = \frac{1}{2\upi i} \int_{\bd\Omega} 
     \frac{2v^+(y) - 2v(x) - 2(y-x)v'(x) + (y-a)^{-1} (x-a) (y-x)^2 v''(x)}
@@
 and target points.  By using a fast summation method, such as the fast
-multipole method (FMM)~\cite{gre-rok1987}, this cost can be reduced to
+multipole method (FMM)~\citep{gre-rok1987}, this cost can be reduced to
 $\mathcal{O}(N)$ operations.  However, the Barycentric quadrature rules
@@
 of thumb, the trapezoid rule due to $\gamma_k$ achieves machine epsilon
-accuracy if~\cite{bar2014}
+accuracy if~\citep{bar2014}
 \begin{align}
@@
 satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL}
-variables~\cite{hou-low-she1994}.  First, given two eroding bodies
+variables~\citep{hou-low-she1994}.  First, given two eroding bodies
 $\gamma_i$ and $\gamma_j$ with lengths $L_i$ and $L_j$, and centroids
@@
   \label{eqn:BodyCutoff}
-  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
+  \|\cc_i - \cc_j\| < \frac{L_i}{2\upi} + \frac{L_j}{2\upi} + 
     \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
@@
   \label{eqn:PointsBodyCutoff}
-  \|\xx - \cc_i\| < \frac{L_i}{2\pi}
+  \|\xx - \cc_i\| < \frac{L_i}{2\upi}
 + \alpha_\iin \left(\frac{L_i}{N_\iin} \right).
@@
     \right]
-  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out},
+  \right\| < \frac{L_i}{2 \upi} + \alpha_\out \frac{L_\out}{N_\out},
 \end{align}
@@
   \label{eqn:PointsWallCutoff}
-  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
+  |y \pm 1| < \frac{L_i}{2 \upi} +\alpha_\out \frac{L_\out}{N_\out}.
 \end{align}
@@
 We use the time stepping method outlined in Section 3.3 of our previous
-work~\cite{qua-moo2018} which we briefly summarize here.  The erosion
+work~\citep{qua-moo2018} which we briefly summarize here.  The erosion
 rate loses differentiability if the shear stress changes sign, and this
@@
   \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
-    \frac{L}{2\pi} \kappa - 1 \right),
+    \frac{L}{2\upi} \kappa - 1 \right),
 \end{align}
@@
 methods in both space and time,  we are able to simulate dynamics very
-close to the eroding bodies (see Figures~\ref{fig:Eroding20tracer}
+close to the eroding bodies (see figures~\ref{fig:Eroding20tracer}
 and~\ref{fig:Eroding100tort}).
@@
 the dispersion and the tortuosity.  We use $N_p = 1000$ streamlines so
-that the statistics have converged~\cite{bel-sal-rin1992}.  However, as
+that the statistics have converged~\citep{bel-sal-rin1992}.  However, as
 described in Section~\ref{sec:dispersion}, a reinsertion method is used
@@
 
-Once the geometry is initialized, each body has length $L_i = 2\pi r_i$,
-and they are each discretized with $N_\iin$ points.  A no-slip boundary
-condition is imposed on each eroding body $\gamma_i$.  For all
+Once the geometry is initialized, each body has length $L_i = 2\upi
+r_i$, and they are each discretized with $N_\iin$ points.  A no-slip
+boundary condition is imposed on each eroding body $\gamma_i$.  For all
 simulations, we discretize the outer wall $\Gamma$ with $N_\out=1024$
@@
 the inlet and outlet at each time step, and then scaling the flow rate
-appropriately~\cite{qua-moo2018}.
+appropriately~\citep{qua-moo2018}.
 
@@
 leads to corner formation on the bodies.  As described in
-Section~\ref{sec:formulation} and our previous work~\cite{qua-moo2018},
+Section~\ref{sec:formulation} and our previous work~\citep{qua-moo2018},
 we introduce a curvature penalization term and a Gaussian smoothing step
@@
   centered at $y=-1$ and compare the eroding body's shape to a similar
-  experiment of Mitchell and Spagnolie~\cite{mit-spa2017}.
+  experiment of Mitchell and Spagnolie~\citep{mit-spa2017}.
 
@@
 \end{align}
-imposed on the outer wall. Mitchell and Spagnolie~\cite{mit-spa2017}
+imposed on the outer wall. Mitchell and Spagnolie~\citep{mit-spa2017}
 performed a similar three-dimensional experiment using a second-order
@@
 between the body and the solid wall is $h$, $h/2$, and $h/10$, where $h
-= 2\pi r/N_\iin$.  If we used the trapezoid rule and required an error
+= 2\upi r/N_\iin$.  If we used the trapezoid rule and required an error
 that is comparable to the Barycentric quadrature rule, the body with an
@@
 
-In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
+In figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
 equispaced time steps.  For all three initial configurations, the shear
@@
 to a region of high curvature.  This behavior is also present in three
-dimensions~\cite{mit-spa2017} (Figure 7(c)).  The biggest difference
+dimensions~\citep{mit-spa2017} (figure 7(c)).  The biggest difference
 between the two- and three-dimensional results is the presence of a
 recirculation zone.  In three dimensions, there is no recirculation
-between the solid wall and the spherical body~\cite{cha-feu2003}, but
-recirculation is possible in two dimensions~\cite{chw-wu1975, hig1985}.
+between the solid wall and the spherical body~\citep{cha-feu2003}, but
+recirculation is possible in two dimensions~\citep{chw-wu1975, hig1985}.
 To visualize the flow, we plot the vorticity of the final time step from
-Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  In these
+figure~\ref{fig:NearWall} in figure~\ref{fig:NearWall_vort}.  In these
 examples, a small recirculation zone, both in size and magnitude, is
@@
 \end{figure}
-\begin{figure}[htp]
+\begin{figure}
 \begin{center}
@@
 have vanished.  Snapshots of the bodies at four equispaced times are
-shown in Figure~\ref{fig:Eroding20vort}.  The color is the vorticity,
+shown in figure~\ref{fig:Eroding20vort}.  The color is the vorticity,
 whose absolute value is proportional to the erosion rate on solid
@@
 expand, and flat faces develop along the regions of near contact.  This
-qualitative behavior is seen in Figure~\ref{fig:Eroding20vort} between
+qualitative behavior is seen in figure~\ref{fig:Eroding20vort} between
 bodies 3 \& 4, 15 \& 16, and was also observed in previous
-work~\cite{qua-moo2018}. However, by resolving the interaction between
+work~\citep{qua-moo2018}. However, by resolving the interaction between
 bodies that are much closer together than in previous work, we observe
@@
 
-\begin{figure}[htp]
+\begin{figure}
 \begin{subfigure}[b]{0.5\textwidth}
@@
 We next analyze the effect of erosion on the area fraction and the flow
-rate.  In Figure~\ref{fig:Eroding20flowrate}(a), we plot the area
+rate.  In figure~\ref{fig:Eroding20flowrate}(a), we plot the area
 fraction as a function of normalized time.  The general trend of the
-area fraction resembles our previous work~\cite{qua-moo2018} (Figure
+area fraction resembles our previous work~\citep{qua-moo2018} (figure
 10(a)), but with a larger initial area fraction.  In
-Figure~\ref{fig:Eroding20flowrate}(b), we plot the flow rate $U$
+figure~\ref{fig:Eroding20flowrate}(b), we plot the flow rate $U$
 required to maintain a constant pressure drop across the channel.
 Again, the trend of $U$ resembles that of our previous
-work~\cite{qua-moo2018} (Figure 10(b)), except that the initial flow
+work~\citep{qua-moo2018} (figure 10(b)), except that the initial flow
 rate is an order of magnitude smaller because of the larger initial area
 fraction.  Starting around normalized time $0.2$,
-Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
+figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
 that the flow rate can be written as an exponential law.  The line of
@@
 \end{align}
-which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).
-
-\begin{figure}[htp]
+which is the dashed line in figure~\ref{fig:Eroding20flowrate}(b).
+
+\begin{figure}
 \begin{center}
@@
 \caption{\label{fig:Eroding20tracer} 200 streamlines in the second
-geometry from Figure~\ref{fig:Eroding20vort}. The streamlines are
+geometry from figure~\ref{fig:Eroding20vort}. The streamlines are
 initialized at $x=-1$ and are equally spaced in $y \in (-1,1)$. The
@@
 
-In Figure~\ref{fig:Eroding20vort}, we observe that erosion creates a
+In figure~\ref{fig:Eroding20vort}, we observe that erosion creates a
 network of channels from the inlet to outlet where the velocity and
@@
 regions.  These channels can be further visualized  with the
-streamlines.  In Figure~\ref{fig:Eroding20tracer}, we freeze the
-geometry at the second snapshot from Figure~\ref{fig:Eroding20vort} and
+streamlines.  In figure~\ref{fig:Eroding20tracer}, we freeze the
+geometry at the second snapshot from figure~\ref{fig:Eroding20vort} and
 plot 200 streamlines that are initialized at $x=-1$ and equally spaced
@@
 is largest, and this causes the channels to continue to open fastest as
-observed in Figure~\ref{fig:Eroding20vort}.
-
-Next, we use the $N_p = 1000$~\cite{bel-sal-rin1992} streamlines to
+observed in figure~\ref{fig:Eroding20vort}.
+
+Next, we use the $N_p = 1000$~\citep{bel-sal-rin1992} streamlines to
 compute the tortuosity of the eroding geometry.  To compute the
 tortuosity, we require the velocity at the inlet $x=-1$.  These
-normalized velocities are plotted in Figure~\ref{fig:Eroding20tort}(a)
+normalized velocities are plotted in figure~\ref{fig:Eroding20tort}(a)
 for the eroded geometry at porosity $\phi = 62.9\%$
-(Figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
-work of Matyka et al.~\cite{mat-kha-koz2008} (see Figure 4(a)), except
+(figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
+work of Matyka et al.~\citep{mat-kha-koz2008} (see figure 4(a)), except
 that our cross-section, by construction, does not cut through any of the
-grains.  Next, in Figure~\ref{fig:Eroding20tort}(b), we plot the local
+grains.  Next, in figure~\ref{fig:Eroding20tort}(b), we plot the local
 tortuosity~\eqref{eqn:localTort} by calculating the relative length of
@@
 tortuosity of the geometry is $1.098$.  Again, comparing the local
-tortuosity to Matyka~\cite{mat-kha-koz2008} (Figure 4(b)), the results
+tortuosity to Matyka~\citep{mat-kha-koz2008} (figure 4(b)), the results
 are qualitatively similar. However, since our initial cross-section does
@@
 Discontinuities in local tortuosity occur when nearby streamlines
-diverge to circumvent a grain.  In Figure~\ref{fig:Eroding20tort}(c), we
+diverge to circumvent a grain.  In figure~\ref{fig:Eroding20tort}(c), we
 plot pairs of streamlines associated with the ten largest jumps in the
@@
 
-\begin{figure}[htp]
+\begin{figure}
 \begin{subfigure}[b]{0.45\textwidth}
@@
 
-In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
+In figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
 function of the porosity. The initial porosity is $\phi = 37.68\%$, and
@@
 grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
-to the porosity of the geometry in Figure~\ref{fig:Eroding20tort}(c).
+to the porosity of the geometry in figure~\ref{fig:Eroding20tort}(c).
 The two tortuosity formulas give similar results, and any discrepancy
@@
 minimizes the error.  The  black dashed line in
-Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
+figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
 \begin{align}
@@
 occurs because in the absence of erosion (left plot in
-Figure~\ref{fig:Eroding20vort}), many of the streamlines, such as those
+figure~\ref{fig:Eroding20vort}), many of the streamlines, such as those
 initialized between bodies 15 \& 18, only perform minor deflections to
@@
 seven geometries of different porosities that are formed during the
-erosion process (Figure~\ref{fig:Eroding20Transport}(b)).  So that the
+erosion process (figure~\ref{fig:Eroding20Transport}(b)).  So that the
 spreading reaches a statistical equilibrium, we use the reinsertion
@@
 method~\eqref{eqn:tortuosity1} (red stars).  The red square corresponds
-to the geometry in Figure~\ref{fig:Eroding20tort}(c).  The dash line is
+to the geometry in figure~\ref{fig:Eroding20tort}(c).  The dash line is
 the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2064$, and
@@
 We consider a second example with 20 eroding bodies, but with a smaller
-initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
+initial porosity.  In figure~\ref{fig:ErodingLow20vort}, we plot the
 eroding geometry and vorticity at four evenly spaced instances in time.
@@
 the initial tortuosity is $T = 1.24$.  In
-Figure~\ref{fig:ErodingLow20Transport}(a), we plot the tortuosity with
+figure~\ref{fig:ErodingLow20Transport}(a), we plot the tortuosity with
 respect to the porosity (blue) and the line of best fit (black) using
@@
 
-In Figure~\ref{fig:ErodingLow20Transport}(b), we plot the temporal
+In figure~\ref{fig:ErodingLow20Transport}(b), we plot the temporal
 evolution of the particle spreading $\sigma_\lambda$.  As in the last
@@
 For all the porosities, the dispersion is much closer to ballistic when
-compared to the results in Figure~\ref{fig:Eroding20Transport}.
+compared to the results in figure~\ref{fig:Eroding20Transport}.
 However, there are still clear transitions from ballistic dynamics to
@@
 Since the initial configuration has a reasonably uniform velocity (see
-Figure~\ref{fig:ErodingLow20vort}), albeit a small one, the dispersion
+figure~\ref{fig:ErodingLow20vort}), albeit a small one, the dispersion
 is nearly ballistic. However, as the geometry erodes, the flow becomes
 more intermittent, and this results in an increased anomalous dispersion
-rate~\cite{dea-leb-den-tar-bol-dav2013}.  Then, as the bodies continue
+rate~\citep{dea-leb-den-tar-bol-dav2013}.  Then, as the bodies continue
 to erode, the geometry channelizes, and most tracers are transported
 with a large velocity through the channels, again resulting in a nearly
-ballistic motion~\cite{sie-ili-pri-riv-gua2019}.
+ballistic motion~\citep{sie-ili-pri-riv-gua2019}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htp]
+\begin{figure}
 \begin{subfigure}[b]{0.5\textwidth}
@@
 Snapshots of the configurations and vorticity are in
-Figure~\ref{fig:Eroding100vort}. We compute the tortuosity using both
+figure~\ref{fig:Eroding100vort}. We compute the tortuosity using both
 the Lagrangian~\eqref{eqn:tortuosity1} and Eulerian
@@
 at $N_p = 1000$ points along the inlet $x=-1$. These normalized
-velocities are plotted in Figure~\ref{fig:Eroding100tort}(a) for the
+velocities are plotted in figure~\ref{fig:Eroding100tort}(a) for the
 eroded geometry at porosity $\phi = 62.98\%$
-(Figure~\ref{fig:Eroding100tort}(c)).  The initial velocity of the
+(figure~\ref{fig:Eroding100tort}(c)).  The initial velocity of the
 tracers is qualitatively similar to the 20 body example
-(Figure~\ref{fig:Eroding20tort}(a)), except with additional maximum and
+(figure~\ref{fig:Eroding20tort}(a)), except with additional maximum and
 minimums because of the additional bodies.  Next, in
-Figure~\ref{fig:Eroding100tort}(b), we plot the local tortuosity by
+figure~\ref{fig:Eroding100tort}(b), we plot the local tortuosity by
 finding the length of the streamlines as they pass from $x=-1$ to $x=1$.
-Compared to Figure~\ref{fig:Eroding20tort}(b), the local tortuosity is
+Compared to figure~\ref{fig:Eroding20tort}(b), the local tortuosity is
 much more discontinuous.  These discontinuities can be explained by
 examining the trajectories of tracers in
-Figure~\ref{fig:Eroding100tort}(c).  Here, there are many instances of
+figure~\ref{fig:Eroding100tort}(c).  Here, there are many instances of
 nearby streamlines that are deflected apart from one another as they
@@
 that this maximum velocity is about a order of magnitude smaller than
-the 20 body example in Figure~\ref{fig:Eroding20tort}.  (b) The local
+the 20 body example in figure~\ref{fig:Eroding20tort}.  (b) The local
 tortuosity $\tau(y)$ on the cross section $x = -1$. The spatially
@@
 significantly different because they pass opposite sides of an eroding
-body. Compared to Figure~\ref{fig:Eroding20tort}, this example has more
+body. Compared to figure~\ref{fig:Eroding20tort}, this example has more
 small bodies, and this results in many more discontinuities.}
@@
 
-In Figure~\ref{fig:Eroding100Transport}(a), we plot the tortuosity as a
+In figure~\ref{fig:Eroding100Transport}(a), we plot the tortuosity as a
 function of the porosity.  The initial geometry has a porosity of $\phi
@@
 grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
-to the porosity of the geometry in Figure~\ref{fig:Eroding100tort}(c).
+to the porosity of the geometry in figure~\ref{fig:Eroding100tort}(c).
 Again, the two tortuosity formulas give similar results.  For this
@@
 fit using the porosity-tortuosity models~\eqref{eqn:tortuosityModels}.
-The black dashed line in Figure~\ref{fig:Eroding100Transport}(a) is the
+The black dashed line in figure~\ref{fig:Eroding100Transport}(a) is the
 line of best fit
@@
 
-In Figure~\ref{fig:Eroding100Transport}(b), we plot the temporal
+In figure~\ref{fig:Eroding100Transport}(b), we plot the temporal
 evolution of the particle spreading $\sigma_\lambda$ at six different
@@
 line), and then super-dispersion.  Similar to the example in
-Figure~\ref{fig:ErodingLow20Transport}(b), the anomalous dispersion rate
+figure~\ref{fig:ErodingLow20Transport}(b), the anomalous dispersion rate
 is not growing with the porosity.  Therefore, it appears that the
@@
 distribution of the velocity, and thus effects the
-tortuosity~\cite{den-ica-hid2018} and anomalous
-dispersion~\cite{dea-qua-bir-jua2018}. In addition, the pore sizes are
-required in network models~\cite{bry-mel-cad1993, bry-kin-mel1993}.  As
+tortuosity~\citep{den-ica-hid2018} and anomalous
+dispersion~\citep{dea-qua-bir-jua2018}. In addition, the pore sizes are
+required in network models~\citep{bry-mel-cad1993, bry-kin-mel1993}.  As
 described in Section~\ref{sec:throats}, we use a Delaunay triangulation
@@
 
-In Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the pore
+In figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the pore
 pore sizes at six porosities during the erosion process. These types of
 distributions have been described with Weibull
-distributions~\cite{ioa-cha1993}, and we superimpose the Weibull
+distributions~\citep{ioa-cha1993}, and we superimpose the Weibull
 distribution with the same first two moments as the data.  The
 parameters of the distribution, $(k,\lambda)$, are included in the
-caption of Figure~\ref{fig:Eroding100gap_hist}.  In
-Figure~\ref{fig:Eroding100gap_mean_var}, we plot the mean and variance
+caption of figure~\ref{fig:Eroding100gap_hist}.  In
+figure~\ref{fig:Eroding100gap_mean_var}, we plot the mean and variance
 of the pore sizes as a function of the porosity.  Interestingly, for
@@
 
-\begin{figure}[htp]
+\begin{figure}
 \begin{subfigure}[b]{0.33\textwidth}
@@
 contains 100 eroding bodies.  The distributions of the pore sizes in
-Figure~\ref{fig:Eroding100gap_hist} are indicated by the red stars.}
+figure~\ref{fig:Eroding100gap_hist} are indicated by the red stars.}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-As a continuation of our previous work~\cite{qua-moo2018}, we have
+As a continuation of our previous work~\citep{qua-moo2018}, we have
 simulated dense suspensions and characterized transport in viscous
@@
 integrate near-singular functions. This is achieved by extending a
-Barycentric quadrature rule~\cite{bar-wu-vee2015} to accurately compute
+Barycentric quadrature rule~\citep{bar-wu-vee2015} to accurately compute
 the erosion rate and vorticity. By using this quadrature rule, we are
@@
 dispersion. The local tortuosity agrees qualitatively with other
-works~\cite{mat-kha-koz2008}. However, the tortuosity of the eroded
+works~\citep{mat-kha-koz2008}. However, the tortuosity of the eroded
 geometries cannot be completely described in terms of the porosity. In
@@
 provide preliminary results for the pore throat sizes which affect the
-anomalous dispersion rate~\cite{dea-qua-bir-jua2018}.  At a later date,
+anomalous dispersion rate~\citep{dea-qua-bir-jua2018}.  At a later date,
 we will report results on the  development of anisotropic effects and
@@
 research with a few promising directions recently
-proposed~\cite{gray2019boundary, kli-ask-kro2019}.  Regarding other
+proposed~\citep{gray2019boundary, kli-ask-kro2019}.  Regarding other
 transport models, this would involve a diffusive term to consider the
@@
 splitting methods and recent work on heat solvers in complex
-geometries~\cite{fry-kro-tor2019}.
+geometries~\citep{fry-kro-tor2019}.
 
@@
 
-\bibliographystyle{plainnat} 
-\biboptions{sort&compress}
+\bibliographystyle{jfm} 
+%\biboptions{sort&compress}
 \bibliography{refs}
@@
 %
-%{\color{red} We use the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} with trapezoid rule to calculate the double-layer potential.
+%{\color{red} We use the Fast Multipole Method (FMM)~\citep{gre-rok1987, gre-gre-may1992} with trapezoid rule to calculate the double-layer potential.
 %}
@@
 %where $h=L_w/N_\out$ is the arclength spacing correponding to the outer
-%wall.  In~\cite{qua-moo2018} we reported the quick expanding space at
+%wall.  In~\citep{qua-moo2018} we reported the quick expanding space at
 %the narrow channel between neighboring bodies, the developing flat faces
@@
 %acting as several Poiseuille flows. This velocity graph is different
-%from the one in~\cite{matyka2008tortuosity} since we choose our cross
+%from the one in~\citep{matyka2008tortuosity} since we choose our cross
 %section to be the beginning of the flow before the fluid touches any

### 2019-10-09 docs/transport/erosion_transport.tex
continued formatting

@@
 %\usepackage{showkeys}
-
-\usepackage{graphicx}
-\usepackage{epstopdf, epsfig}
-
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
 
@@
 in number and modest in volume fraction, transmit a large portion of the
-flux \citep{qua-moo2018}. This arrangement results in velocities that
+flux~\citep{qua-moo2018}. This arrangement results in velocities that
 vary over several orders of magnitude~\citep{all-hea-lab-rei2002}.
@@
 earliest works to address quadrature methods for nearly-singular
-integrands was developed by Baker and Shelley~\citep{bak-she1986}, and in
-recent years, many other near-singular integration schemes have
+integrands was developed by~\citet{bak-she1986}, and in recent years,
+many other near-singular integration schemes have
 followed~\citep{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Contributions}
-Our first contribution is extending the Barycentric quadrature rule of
-Barnett et al.~\citep{bar-wu-vee2015} to accurately compute velocity
-gradients associated with Stokes flow. This new quadrature rule permits
-accurate and stable simulations of erosion, and, moreover, enables
-visualization of the vorticity field throughout.
+\subsection{Contributions}
+Our first contribution is extending the Barycentric quadrature rule
+of~\citet{bar-wu-vee2015} to accurately compute velocity gradients
+associated with Stokes flow. This new quadrature rule permits accurate
+and stable simulations of erosion, and, moreover, enables visualization
+of the vorticity field throughout.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Limitations}
+\subsection{Limitations}
 As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
@@
   \DD[\eeta](\xx) = \frac{1}{2\upi} \int_{\bd\Omega} 
-    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Re (v(x)) \quad 
+    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)) \quad 
     \text{where} \quad v(x) = \frac{1}{2\upi i} \int_{\bd\Omega}
@@
   \begin{aligned}
-    u_1(x) &= \Re (v[\psi_1](x)) + \Re (v'[y\cdot\eta](x)) 
-             -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
-    u_2(x) &= \Re (v[\psi_2](x)) - \Im (v'[y\cdot\eta](x)) 
-         +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
+    u_1(x) &= \Real (v[\psi_1](x)) + \Real (v'[y\cdot\eta](x)) 
+             -x_1\Real (v'[\eta_1](x)) - x_2\Real (v'[\eta_2](x)), \\
+    u_2(x) &= \Real (v[\psi_2](x)) - \Imag (v'[y\cdot\eta](x)) 
+         +x_1\Imag (v'[\eta_1](x)) + x_2\Imag (v'[\eta_2](x)),
   \end{aligned}
@@
 \begin{align} 
-  \psi_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad
-  \psi_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
+  \psi_1=(\eta_1+i\eta_2)\frac{\Real(n)}{n}, \quad
+  \psi_2=(\eta_1+i\eta_2)\frac{\Imag(n)}{n},
 \end{align}
@@
   \begin{aligned}
-    \pderiv{u_1}{x_1} &= +\Re (v'[\psi_1](x)) + 
-      \Re (v''[y\cdot\eta](x)) - \Re (v'[\eta_1](x)) - 
-      x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
-    \pderiv{u_1}{x_2} &= - \Im (v'[\psi_1](x)) - 
-      \Im (v''[y\cdot\eta](x)) + x_1\Im (v''[\eta_1](x)) - 
-      \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
-    \pderiv{u_2}{x_1} &= +\Re (v'[\psi_2](x)) - 
-      \Im (v''[y\cdot\eta](x)) + \Im (v'[\eta_1](x)) +
-      x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
-    \pderiv{u_2}{x_2} &= -\Im (v'[\psi_2](x)) - 
-      \Re (v''[y\cdot\eta](x)) + x_1\Re (v''[\eta_1](x)) +
-      \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
+    \pderiv{u_1}{x_1} &= +\Real (v'[\psi_1](x)) + 
+      \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) - 
+      x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
+    \pderiv{u_1}{x_2} &= - \Imag (v'[\psi_1](x)) - 
+      \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) - 
+      \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
+    \pderiv{u_2}{x_1} &= +\Real (v'[\psi_2](x)) - 
+      \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x)) +
+      x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
+    \pderiv{u_2}{x_2} &= -\Imag (v'[\psi_2](x)) - 
+      \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) +
+      \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
   \end{aligned}
@@
   \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
-\Re (v'[\psi_2](x)) + \Im (v'[\psi_1](x)) 
- + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)), \quad x \in \Omega.
+\Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x)) 
+ + \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)), \quad x \in \Omega.
 \end{align}
@@
 There have been efforts to relate the tortuosity, $T$, to the porosity,
-$\phi$.  For example, Matyka et al.~\citep{mat-kha-koz2008} propose the
+$\phi$.  For example,~\citet{mat-kha-koz2008} propose the
 models
@@
 transport~\citep{knu-car2005},
-channelization~\citep{sie-ili-pri-riv-gua2019,berhanu2012shape}, and pore
-network models~\citep{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}. To
-characterize the grain placement, we compute distributions of pore sizes
-between neighboring grains.  To define neighboring grains, we form a
-Delaunay triangulation using nodes placed at the center of each eroding
-grain and at a collection of points around the boundary of the porous
-media.  Then, we say that two grains are neighbors if their centers
-share an edge of the triangulation~\citep{dea-qua-bir-jua2018}. The pores
-of an eroded geometry are illustrated in
-figure~\ref{fig:Eroding100gap}(a). We do not consider pores between
-eroding bodies and the solid wall $\Gamma$, so some of the grains near
-the porous region boundary only have two neighbors. Having defined the
-pore sizes, we plot its distribution in
+channelization~\citep{sie-ili-pri-riv-gua2019,berhanu2012shape}, and
+pore network models~\citep{bry-kin-mel1993, bry-mel-cad1993,
+bij-blu2006}. To characterize the grain placement, we compute
+distributions of pore sizes between neighboring grains.  To define
+neighboring grains, we form a Delaunay triangulation using nodes placed
+at the center of each eroding grain and at a collection of points around
+the boundary of the porous media.  Then, we say that two grains are
+neighbors if their centers share an edge of the
+triangulation~\citep{dea-qua-bir-jua2018}. The pores of an eroded
+geometry are illustrated in figure~\ref{fig:Eroding100gap}(a). We do not
+consider pores between eroding bodies and the solid wall $\Gamma$, so
+some of the grains near the porous region boundary only have two
+neighbors. Having defined the pore sizes, we plot its distribution in
 figure~\ref{fig:Eroding100gap}(b) and compare it with the Weibull
@@
 quadrature rule with a uniform error bound for Cauchy integrals and its
-derivatives~\eqref{eqn:cauchy}. Ioakimidis et al.~\citep{ioa-pap-per1991}
-developed quadrature rules, that we call {\em Barycentric quadrature
-rules}, to compute Cauchy integrals and their derivatives with an error
-bound that is independent of $x \in \CC$.  Then, Barnett et
-al.~\citep{bar-wu-vee2015} used these quadrature rules to compute the
-Stokes double-layer potential representation of the
-velocity~\eqref{eqn:velocityDLP}, and we briefly summarize their method.
-Then, we extend their work to compute the second derivative so that the
-shear stress and vorticity can be computed with a uniform error bound.
+derivatives~\eqref{eqn:cauchy}. \citet{ioa-pap-per1991} developed
+quadrature rules, that we call {\em Barycentric quadrature rules}, to
+compute Cauchy integrals and their derivatives with an error bound that
+is independent of $x \in \CC$.  Then,~\citet{bar-wu-vee2015} used these
+quadrature rules to compute the Stokes double-layer potential
+representation of the velocity~\eqref{eqn:velocityDLP}, and we briefly
+summarize their method.  Then, we extend their work to compute the
+second derivative so that the shear stress and vorticity can be computed
+with a uniform error bound.
 
@@
 quadrature rule for $v''(x)$.  The derivation is largely based on the
-work of Ioakimidis et al.~\citep{ioa-pap-per1991} (see equation (2.12)).
-We start with the second derivative of the Cauchy integral theorem
+work of~\citet{ioa-pap-per1991} (see equation (2.12)).  We start with
+the second derivative of the Cauchy integral theorem
 \begin{align}
@@
 the target location. However, applied directly, it requires
-$\mathcal{O}(N^2)$ operations, where $N$ is the total number of source
+$O(N^2)$ operations, where $N$ is the total number of source
 and target points.  By using a fast summation method, such as the fast
 multipole method (FMM)~\citep{gre-rok1987}, this cost can be reduced to
-$\mathcal{O}(N)$ operations.  However, the Barycentric quadrature rules
+$O(N)$ operations.  However, the Barycentric quadrature rules
 require several $N$-body calculations.  The resulting cost would be
@@
 trapezoid rule~\eqref{eqn:trap} accelerated with the FMM.  This
-calculation requires $\mathcal{O}(N)$ operations, and we call the
+calculation requires $O(N)$ operations, and we call the
 resulting velocity $\vv_\trap(\xx)$.  Since the trapezoid rule is
@@
   centered at $y=-1$ and compare the eroding body's shape to a similar
-  experiment of Mitchell and Spagnolie~\citep{mit-spa2017}.
+  experiment of~\citet{mit-spa2017}.
 
@@
 \end{align}
-imposed on the outer wall. Mitchell and Spagnolie~\citep{mit-spa2017}
-performed a similar three-dimensional experiment using a second-order
-quadrature method.  Their initial body is a sphere with its center
-located $1.5$ radii above the solid wall.  In two dimensions, the
-trapezoid rule is spectrally accurate, and an analogous initial
-configuration is possible. However, unless the number of discretization
-points is increased, the trapezoid rule becomes obsolete if the eroding
-body is initialized too close to the solid wall. Therefore, to simulate
-erosion near a solid wall at reasonable levels of discretization, we use
-our hybrid method that combines the trapezoid rule and the Barycentric
-quadrature rule.
+imposed on the outer wall. \citet{mit-spa2017} performed a similar
+three-dimensional experiment using a second-order quadrature method.
+Their initial body is a sphere with its center located $1.5$ radii above
+the solid wall.  In two dimensions, the trapezoid rule is spectrally
+accurate, and an analogous initial configuration is possible. However,
+unless the number of discretization points is increased, the trapezoid
+rule becomes obsolete if the eroding body is initialized too close to
+the solid wall. Therefore, to simulate erosion near a solid wall at
+reasonable levels of discretization, we use our hybrid method that
+combines the trapezoid rule and the Barycentric quadrature rule.
 
@@
 (figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
-work of Matyka et al.~\citep{mat-kha-koz2008} (see figure 4(a)), except
-that our cross-section, by construction, does not cut through any of the
-grains.  Next, in figure~\ref{fig:Eroding20tort}(b), we plot the local
+work of~\citet{mat-kha-koz2008} (see figure 4(a)), except that our
+cross-section, by construction, does not cut through any of the grains.
+Next, in figure~\ref{fig:Eroding20tort}(b), we plot the local
 tortuosity~\eqref{eqn:localTort} by calculating the relative length of
@@
 tortuosity of the geometry is $1.098$.  Again, comparing the local
-tortuosity to Matyka~\citep{mat-kha-koz2008} (figure 4(b)), the results
-are qualitatively similar. However, since our initial cross-section does
-not cut through the grains, the local tortuosity does not have any gaps.
+tortuosity to~\citet{mat-kha-koz2008} (figure 4(b)), the results are
+qualitatively similar. However, since our initial cross-section does not
+cut through the grains, the local tortuosity does not have any gaps.
 Discontinuities in local tortuosity occur when nearby streamlines
@@
 the erosion rate and vorticity. By using this quadrature rule, we are
-able to perform stable simulations of erosion with $N =
-\mathcal{O}(100)$ discretization points, while the trapezoid rule would
-require $\mathcal{O}(10^5)$ discretization points.
+able to perform stable simulations of erosion with $N = O(100)$
+discretization points, while the trapezoid rule would require $O(10^5)$
+discretization points.
 

### 2019-10-09 docs/transport/erosion_transport.tex
NM

@@
 lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
-When a porous geometry erodes, certain qualitative characteristics are
+When a porous medium erodes, certain qualitative characteristics are
 unveiled that affect transport through the geometry.  For example, an
@@
 regime~\citep{qua-moo2018}. We, however, make key improvements to the
-numerical methods from~\citep{qua-moo2018} to enable simulations of more
+numerical methods \nick{(I killed the reference here because I think its redundant)} to enable simulations of more
 realistic, dense suspensions of eroding grains
@@
 the hydrodynamic shear stress~\citep{wan-fel2004,
-ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  Since the
-vorticity and the shear stress are equivalent on solid boundaries, we
-also compute the fluid vorticity for visualization purposes
-(figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
+ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.
+\nick{We compute the vorticity in the fluid bulk since, on solid boundaries, vorticity reduces to shear and thus provides a convenient way to simultaneously visualize local erosion rates and changes in the surrounding flow} (figure~\ref{fig:Eroding50vort}).
+A variety of numerical methods for
 the fluid solver are available including lattice-gas or lattice

### 2019-10-09 docs/transport/erosion_transport.tex
NMM

@@
   consequence of the pore structure. Here we investigate transport
-  through specific two-dimensional porous geometries---those that are
-  formed by fluid-mechanical erosion.  We investigate the tortuosity and
+  through \nick{a specific class of two-dimensional porous geometries, 
+  namely those formed by fluid-mechanical erosion.}  
+  We investigate the tortuosity and
   dispersion by analyzing the first two statistical moments of tracer
-  trajectories. For most geometries, the tortuosity decreases as erosion
-  increases the porosity; however, interestingly, it is possible for
-  erosion to increase the tortuosity. The simulated porosity-tortuosity
-  relationships are compared with models available in the literature.
-  Unsurprisingly, the asymptotic dispersion rate is also affected by the
-  erosion process, but it is also affected by the number of and
-  distribution of the eroding bodies.  Finally, we analyze the pore size
+  trajectories. \nick{For most initial configurations, tortuosity decreases in time 
+  as a result of erosion increasing the porosity. 
+  However, we find that tortuosity can also increase transiently in certain cases.}
+  \nick{The porosity-tortuosity relationships that result from our simulations 
+  are compared against models available in the literature.}
+  \nick{Asymptotic dispersion rates are also strongly affected by the
+  erosion process, as well as by the number and
+  distribution of the eroding bodies.}  
+  Finally, we analyze the pore size
   distribution of an eroding geometry. The simulations are performed by

### 2019-10-10 docs/transport/erosion_transport.tex
formatting equations

@@
 
-Owing to the scales present in groundwater flow~\citep{bea1972}, we model
-the hydrodynamics with the two-dimensional incompressible Stokes
+Owing to the scales present in groundwater flow~\citep{bea1972}, we
+model the hydrodynamics with the two-dimensional incompressible Stokes
 equations.  Meanwhile, individual grains erode at a rate proportional to
 the hydrodynamic shear stress~\citep{wan-fel2004,
-ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.
-\nick{We compute the vorticity in the fluid bulk since, on solid boundaries, vorticity reduces to shear and thus provides a convenient way to simultaneously visualize local erosion rates and changes in the surrounding flow} (figure~\ref{fig:Eroding50vort}).
-A variety of numerical methods for
+ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  \nick{We compute
+the vorticity in the fluid bulk since, on solid boundaries, vorticity
+reduces to shear and thus provides a convenient way to simultaneously
+visualize local erosion rates and changes in the surrounding flow}
+(figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
 the fluid solver are available including lattice-gas or lattice
@@
 sie-ili-pri-riv-gua2019}, finite differences~\citep{leb-ded-dav-bou2007,
-knu-car2005}, and cellular automata~\citep{rot1988}.  However, simulating
-erosion requires a method that is high-order, can resolve
+knu-car2005}, and cellular automata~\citep{rot1988}.  However,
+simulating erosion requires a method that is high-order, can resolve
 nearly-touching arbitrarily shaped grains, and can accurately compute
@@
 previous work~\citep{qua-moo2018}.  We apply a mild regularization and a
-smoothing term to eliminate numerical instabilities that can be triggered by changes in
-sign of the shear stress, and we use a stable second-order Runge-Kutta
-method applied to the {\thL} coordinates~\citep{hou-low-she1994} of the
-eroding grains.  In this work, we introduce a new quadrature method to
-resolve dense suspensions.  The accuracy of the
-trapezoid rule, which was used in previous work, is adequate for
-bodies that are sufficiently separated~\citep{tre-wei2014}.  However, it
-loses accuracy whenever grains are in close contact.  One of the
-earliest works to address quadrature methods for nearly-singular
+smoothing term to eliminate numerical instabilities that can be
+triggered by changes in sign of the shear stress, and we use a stable
+second-order Runge-Kutta method applied to the {\thL}
+coordinates~\citep{hou-low-she1994} of the eroding grains.  In this
+work, we introduce a new quadrature method to resolve dense suspensions.
+The accuracy of the trapezoid rule, which was used in previous work, is
+adequate for bodies that are sufficiently separated~\citep{tre-wei2014}.
+However, it loses accuracy whenever grains are in close contact.  One of
+the earliest works to address quadrature methods for nearly-singular
 integrands was developed by~\citet{bak-she1986}, and in recent years,
@@
 channelization~\citep{sie-ili-pri-riv-gua2019},
-connectivity~\citep{knu-car2005, wes-blo-gra2001}, and to develop network
-models~\citep{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
+connectivity~\citep{knu-car2005, wes-blo-gra2001}, and to develop
+network models~\citep{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Outline of the Paper}
+\subsection{Outline of the Paper}
 In Section~\ref{sec:formulation}, we summarize the erosion model that is
@@
   \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
-    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
-    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
-    \NN_0[\eeta](\xx), \quad &&\xx \in \bd\Omega, \\
+    \NN_0[\eeta](\xx) \nonumber \\
+    &\quad + \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
+    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), 
+    \quad &&\qquad\xx \in \bd\Omega, \\
   \llambda_\ell &= \frac{1}{2\upi} \int_{\gamma_\ell} 
-    \eeta(\yy)\, ds_\yy, &&\ell = 1,\ldots,M, \\
+    \eeta(\yy)\, ds_\yy, &&\qquad \ell = 1,\ldots,M, \\
   \xi_\ell &= \frac{1}{2\upi} \int_{\gamma_\ell}
     (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
-    &&\ell = 1,\ldots,M.
+    &&\qquad \ell = 1,\ldots,M.
 \end{alignat}
@@
     \right. \nonumber \\
-    & \qquad\qquad\qquad\qquad\qquad\qquad \left.
+    & \qquad\qquad\qquad\qquad \left.
     +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
@@
   \DD[\eeta](\xx) = \frac{1}{2\upi} \int_{\bd\Omega} 
-    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)) \quad 
-    \text{where} \quad v(x) = \frac{1}{2\upi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega,
+    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)),
+\end{align}
+where
+\begin{align}
+  v(x) = \frac{1}{2\upi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega.
   \label{eqn:laplaceComplex}
 \end{align}
-where $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
+Here $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
 counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
@@
 holomorphic function $v$, by the Cauchy integral theorem we have
-\begin{align}
+\begin{subequations}
+  \begin{alignat}{3}
   \label{eqn:cauchy}
-  v(x) = \frac{1}{2\upi i}\int_{\bd\Omega} 
-    \frac{v(y)}{y-x} \,dy, \quad
-  v'(x) = \frac{1}{2\upi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^2} \, dy, \quad
-  v''(x) = \frac{1}{\upi i} \int_{\bd\Omega}
+  v(x) &= \frac{1}{2\upi i}\int_{\bd\Omega} 
+    \frac{v(y)}{y-x} \,dy, \\
+  v'(x) &= \frac{1}{2\upi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^2} \, dy, \\
+  v''(x) &= \frac{1}{\upi i} \int_{\bd\Omega}
     \frac{v(y)}{(y-x)^3} \, dy,
-\end{align}
+  \end{alignat}
+\end{subequations}
 for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
@@
     \pderiv{u_1}{x_1} &= +\Real (v'[\psi_1](x)) + 
-      \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) - 
-      x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
+    \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) \\
+    &- x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
     \pderiv{u_1}{x_2} &= - \Imag (v'[\psi_1](x)) - 
-      \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) - 
-      \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
+    \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) \\
+    &- \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
     \pderiv{u_2}{x_1} &= +\Real (v'[\psi_2](x)) - 
-      \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x)) +
-      x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
+    \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x))  \\
+    &+ x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
     \pderiv{u_2}{x_2} &= -\Imag (v'[\psi_2](x)) - 
-      \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) +
-      \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
+    \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) \\
+    &+ \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
   \end{aligned}
@@
 bulk.  For $x \in \Omega$, the Cauchy integral representation of the
-vorticity is
-\begin{align}
-  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
-\Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x)) 
- + \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)), \quad x \in \Omega.
-\end{align}
+vorticity at $x \in \Omega$ is
+\begin{equation}
+  \begin{aligned}
+    \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} &= 
+      \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))  \\
+      &+ \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
+  \end{aligned}
+\end{equation}
 
@@
 are eroded a single time step by using a {\thL}
-discretization~\citep{hou-low-she1994, moore2013self}.  The time stepping
-methods for erosion and passive particles are described in
+discretization~\citep{hou-low-she1994, moore2013self}.  The time
+stepping methods for erosion and passive particles are described in
 Section~\ref{sec:time}.
@@
 results in the collocation method for~\eqref{eqn:BIE}
+\todo[inline]{left off here with formatting equations}
 \begin{subequations}
@@
 quadrature rule for $v''(x)$.  The derivation is largely based on the
-work of~\citet{ioa-pap-per1991} (see equation (2.12)).  We start with
+work of~\citet[see equation (2.12)]{ioa-pap-per1991}.  We start with
 the second derivative of the Cauchy integral theorem
@@
 to a region of high curvature.  This behavior is also present in three
-dimensions~\citep{mit-spa2017} (figure 7(c)).  The biggest difference
+dimensions~\citep[see figure 7(c)]{mit-spa2017}.  The biggest difference
 between the two- and three-dimensional results is the presence of a
@@
 fraction as a function of normalized time.  The general trend of the
-area fraction resembles our previous work~\citep{qua-moo2018} (figure
-10(a)), but with a larger initial area fraction.  In
+area fraction resembles our previous work~\citep[see][figure
+10(a)]{qua-moo2018}, but with a larger initial area fraction.  In
 figure~\ref{fig:Eroding20flowrate}(b), we plot the flow rate $U$
@@
 Again, the trend of $U$ resembles that of our previous
-work~\citep{qua-moo2018} (figure 10(b)), except that the initial flow
-rate is an order of magnitude smaller because of the larger initial area
-fraction.  Starting around normalized time $0.2$,
+work~\citep[see][figure 10(b)]{qua-moo2018}, except that the initial
+flow rate is an order of magnitude smaller because of the larger initial
+area fraction.  Starting around normalized time $0.2$,
 figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
@@
 (figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
-work of~\citet{mat-kha-koz2008} (see figure 4(a)), except that our
+work of~\citet[see figure 4(a)]{mat-kha-koz2008}, except that our
 cross-section, by construction, does not cut through any of the grains.
@@
 tortuosity of the geometry is $1.098$.  Again, comparing the local
-tortuosity to~\citet{mat-kha-koz2008} (figure 4(b)), the results are
+tortuosity to~\citet[see figure 4(b)]{mat-kha-koz2008}, the results are
 qualitatively similar. However, since our initial cross-section does not
@@
 
-%old stuff%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{boundary integral equation formulation} 
-%\label{sec:bies}
-%add an introduction why we do not use the double-layer potentials of stokes equations but the double-layer potentials of laplace equations to solve stokes equation when we use barycentric approach (or complex variable approach).
-%
-%\subsubsection{laplace's equations from $\rdb^2$ to $\cdb$ }
-%
-%let $\omega$ be the domain of fluid. the boundary of $\omega$ is $\gamma$ and the outward normal vector on $\gamma$ is ${\bf n_y}=(n_1,n_2)$.
-%
-%consider a laplace's equations with dirichlet boundary condition
-%\begin{equation}\label{laplace}
-%  \begin{cases}
-%    \delta {\bf u}=0, & \text{in}\,\,\, \omega \in \rdb^2;\\
-%    {\bf u}={\bf f}, & \text{on}\,\,\, \gamma.
-%  \end{cases}
-%\end{equation}
-%
-%Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
-%The double-layer potential which solves \eqref{Laplace} is 
-%\begin{align*}
-%\D[\sigma]({\bf x})&=\frac{1}{2\pi}\displaystyle\int_{\Gamma} \frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma({\bf y})ds_y,
-%%\frac{1}{2\pi}\displaystyle\int_{\Gamma}\frac{\partial}{\partial {\bf n_y}} \log |{\bf x}-{\bf y}| \sigma({\bf y})ds_y,\\ \\
-%%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{{\bf r}\cdot{\bf n_y}}{\rho^2} \sigma({\bf y})ds_y\\ \\
-%%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{n_1(x_1-y_1)+n_2(x_2-y_2)}{(x_1-y_1)^2+(x_2-y_2)^2} \sigma({\bf y})ds_y 
-%\numberthis\label{DLP:real}
-%\end{align*}
-%where $\sigma$ is the density function on the boundary $\Gamma$.
-%
-%
-%Consider a Cauchy integral 
-%\begin{equation}\label{CI}
-%v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{\sigma({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
-%\end{equation}
-%where ${ x}=x_1+ix_2$, $ { y}=y_1+iy_2$, ${ n_y}=n_1+i n_2$ and $d{ y}=i {n_y}ds_y$. It can be shown that 
-%the real part of the Cauchy integral in \eqref{CI} is equivalent to the double-layer potential in \eqref{DLP:real}. 
-%
-%
-%\subsubsection{From Stokes DLP to Laplace DLPs}
-%
-%Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
-%
-%
-%The Stokes double-layer potential  is
-%\begin{equation}\label{StokesDLP1}
-%\D[\boldsymbol\sigma]({\bf x}):=\frac{1}{\pi}\int_{\Gamma}\left(\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\frac{{\bf r} \otimes {\bf r}}{\rho^2}\right) {\boldsymbol\sigma({\bf y})} d s_y.
-%\end{equation}
-%We could rewrite the Stokes DLP in terms of the Laplace DLP as
-%\begin{align*}\label{StokesDLP2}
-%\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
-%&-\frac{1}{2\pi}x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y-\frac{1}{2\pi}x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y. \numberthis
-%\end{align*}
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Computing the shear stress}
-%\label{sec:shearStressLP}
-%
-%To calculate the shear stress, we need to know the gradient of double-layer potential in \eqref{StokesDLP2} 
-%\begin{align*}\label{SSLP}
-%\nabla\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\nabla\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla^2\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
-%&-\frac{1}{2\pi}\nabla\left(x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y\right)-\frac{1}{2\pi}\nabla\left(x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y\right).
-\numberthis
-%\end{align*}
-%
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Boundary evolution in the {\thL} framework} 
-%\label{sec:thetaL}
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Solving the BIE}
-%\label{sec:BIE}
-%\subsubsection{Interior Case}
-%Consider a Cauchy integral 
-%\begin{align}\label{CIFI}
-%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{{ y}-{ x}} d{ y}
-%&=\begin{cases}
-%\,v(x), &{ x} \in \Omega,\\ 
-%\,0,  &{ x} \in \Cdb\setminus \bar{\Omega}.
-%\end{cases}
-%\end{align}
-%By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{{ y}-{ x}} d{ y}=1,$ we can rewrtie \eqref{CIFI} and get 
-%\begin{equation}
-%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)}{{ y}-{ x}} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-%\end{equation}
-%\begin{equation}\label{dNCI}
-%v'({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{(y- x)^2} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-%\end{equation}
-%By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{dNCI} and get 
-%\begin{equation}
-%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)-(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-%\end{equation}
-%
-%\subsubsection{Exterior case}
-%Consider a Cauchy integral formula for the exterior domain
-%\begin{align}\label{CIFE}
-%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})}{{ y}-{ x}} d{ y}
-%&=\begin{cases}
-%\,v_{\infty}, &{ x} \in \Omega,\\ 
-%\,-v(x)+v_{\infty},  &{ x} \in \Omega^c,
-%\end{cases}
-%\end{align}
-%where $v_{\infty}=\displaystyle\lim_{x \to \infty}v(x)$.
-%\begin{equation}
-%\frac{1}{x-a}=\frac{-1}{2 \pi i} \int_{\Gamma}\frac{(y-a)^{-1}}{y-x} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
-%\end{equation}
-%\begin{equation}
-%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-(y-a)^{-1}(x-a)v(x)}{y-x} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
-%\end{equation}
-%\begin{equation}
-%\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-v(x)-(y-a)^{-1}(x-a)(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
-%\end{equation}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Shear stress}
-%\label{sec:shearStress}
-%\subsubsection{Interior Case}
-%\begin{equation}\label{ddNCI}
-%v''({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})}{(y- x)^3} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-%\end{equation}
-%By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{ddNCI} and get 
-%\begin{equation}
-%\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
-%\end{equation}
-%\subsubsection{Exterior case}
-%\begin{equation}
-%\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^+({ y})-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
-%\end{equation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% TIME-STEPPING %%
-%\subsection{Time-stepping with the {\thL} method} 
-%\label{sec:timeStepping}
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Post processing quantities of interest}
-%\label{s:qoi}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Vorticity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Pressure}
-%\label{sec:pressure}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Drag}
-%\label{sec:drag}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Near-singular integration}
-%\label{sec:NSI}
-%
-%
-%{\color{red}
-%Here we derive the equations~\eqref{eqn:pderiv1}-\eqref{eqn:pderiv2} 
-%and the other two are similar.
-%To derive equations~\eqref{eqn:pderiv1} and \eqref{eqn:pderiv2}, 
-%we need to apply the fact that if a real function $u$ is equivalent to 
-%the real part of a complex varaible function $f$, 
-%then we have $\nabla u=(\Re(f'),-\Im(f'))$.
-%Let $f_1(x)= v[\tau_1](x)$, $f_2(x)=v'[\yy\cdot\eeta](x)$, $f_3(x)=v'[\eta_1](x)$,
-%and $f_4(x)= v'[\eta_2](x)$. Then we can rewrite equation~\eqref{eqn:cauchy1}
-%\begin{align*}
-%u_1(\xx)&= u_{11}(\xx) +  u_{12}(\xx) +u_{13}(\xx)+u_{14}(\xx) \\
-%&=\Re (f_1(x)) + \Re (f_2(x))-x_1\Re (f_3(x)) - x_2\Re (f_4(x)).
-%\end{align*}
-%To get the gradient of $u_1(x)$, we have
-%\begin{align*}
-%\nabla u_1(x)&= \nabla u_{11}(x)+\nabla  u_{12}(x) 
-%+\nabla u_{13}(x)+\nabla u_{14}(x) \\ \\
-%&=\begin{bmatrix}
-%\Re(f_1'(x))\\ \\
-%-\Im(f_1'(x))
-%\end{bmatrix}+
-%\begin{bmatrix}
-%\Re(f_2'(x))\\ \\
-%-\Im(f_2'(x))
-%\end{bmatrix}
-%+
-%\begin{bmatrix}
-%-\Re(f_3(x))-x_1\Re(f_3'(x))\\ \\
-%x_1\Im(f_3'(x))
-%\end{bmatrix}
-%+
-%\begin{bmatrix}
-%-x_2\Re(f_4'(x))\\ \\
-%-\Re(f_4(x))+x_2\Im(f_4'(x))
-%\end{bmatrix}\\ \\
-%&=
-%\begin{bmatrix}
-%\Re (v'[\tau_1](x)) + 
-%    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
-%    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x))\\ \\
-%- \Im (v'[\tau_1](x)) - 
-%    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
-%    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x))
-%\end{bmatrix}.
-%\end{align*}
-%
-%{\color{red}
-%\begin{alignat}{3}
-%1 &= \frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
-%\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
-%    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
-%\end{alignat}
-%and the contour integral 
-%\begin{align}\label{eqn:cauchyId3}
-%0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
-%\end{align}
-%Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
-%the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
-%\begin{align*}
-%0 &= \frac{1}{2\pi i} \int_{\Gamma}
-%    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
-%&= \frac{1}{2\pi i} \int_{\Gamma}
-%    \frac{2v^-(y)}{(y - x)^3} \, dy 
-%-v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{1}{y-x} dy\\
-%&= \frac{1}{2\pi i} \int_{\Gamma}
-%    \frac{2v^-(y)}{(y - x)^3} \, dy 
-%-\frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
-%-\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
-%-\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
-%&= \frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
-%\end{align*}
-%}
-%\todo[inline]{S-H: How do we get these identities?}
-%\begin{alignat}{3}
-%  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
-%    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
-%  0 &= \frac{1}{2\pi i}\int_{\Gamma}
-%    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
-%    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
-%\end{alignat}
-%{\color{red}
-%and the quadrature formulations are
-%\begin{alignat}{3}
-%  v''(x) &\approx
-%    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
-%    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
-%  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
-%    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
-%    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
-%\end{alignat}
-%where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
-%
-%}
-%
-%{\color{red}
-%By using Barycentric quadrature rule to approach integrations, we get a reasonable(?) double-layer potential and quantities of interest at target points but it requires $\mathcal{O}(N^2)$ operations per target point which is computational expensive if we impose it on all the target points.
-In order to accelerate the process and keep the accuracy, it is a compromise that we use Barycentric quadrature rule to approach the nearly singular integratons but apply trapezoid rule when the target point is far from source points.
-%
-%
-%To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer wall with $N_\out$ points.
-The following is the four-step fast summation methods.
-%}
-%\begin{itemize}
-%  \item Apply trapezoid rule as a first pass
-%
-%{\color{red} We use the Fast Multipole Method (FMM)~\citep{gre-rok1987, gre-gre-may1992} with trapezoid rule to calculate the double-layer potential.
-%}
-%  \item Efficiently find points that are too close for trapezoid
-%
-%{\color{red}
-% Let $L_w$ be the length of the outer wall and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$.
-Here are the criteria to see if two points are too close for trapezoid.
-For criterion of outer wall to body,  let $d$ be the minimum distance between outer wall and a point $x$ on the body $b$, we say $x$ is too close to outer wall if
-%\begin{equation}\label{eqn:Cw2b}
-%d< \alpha_1\frac{L_w}{N_\out}
-%\end{equation}
-%where $\alpha_1$ is a constant. 
-%For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
-%\begin{equation}\label{eqn:Cb2b}
-%d<\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
-%\end{equation}
-%where $\alpha_2$ is a constant. 
-%
-%}
-%\end{itemize}
-%{\color{red}  (Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency)
-%
-%To find the suitable values of $\alpha_1$ and $\alpha_2$ in~\eqref{eqn:Cw2b} and \eqref{eqn:Cb2b}, we set $\alpha_1=\alpha_2=1, 2, 3$, and $4$ to test the criteria on a 20-body problem with $N_\out = 1024$ and $N_\iin = 128, 256$, and $512$.
-To check the accuracy of the simulations, we use the solution calculated by \todo[inline]{what method} to \todo[inline]{...}
-%To see how efficient our code is, we record the cpu time for each step.
-%
-%}
-
-%{\color{red} 
-%By using Barycentric quadrature rule, we are able to capture the details
-%in the fluid when wall and bodies or body and bodies are close to each
-%other.  The first nearly touching bodies case is 20 bodies in a
-%Hagen-Poiseuille flow.  The initial velocity of flow from the left side
-%of $\Omega$ is $$\UU(\xx)=U\begin{bmatrix} 1-y^2\\ 0\end{bmatrix},$$
-%where $U$ is chosen such that the pressure drop between  $x=-2$ and
-%$x=2$ remains fixed at 8.  With this choice, the velocity in the absent
-%of grains has flow rate $U=1$.  The number of discretization points is
-%$N_\iin = 256$.
-%
-%The snapshots of the process of 20 nearly touching bodies eroding are in
-%Fig.~\ref{fig:Eroding20vort}.  We initially place some bodies to nearly
-%contact not only one another but also the outer wall. For example,
-%bodies 1, 6, 13, and 15 are very close to outer wall: the distance
-%between body 1 and outer wall is $1.3025h$, the distance between body 6
-%and outer wall is $2.9275h$, the distance between body 13 and outer wall
-%is $2.8447h$, the distance between body 15 and outer wall is $1.3352h$
-%where $h=L_w/N_\out$ is the arclength spacing correponding to the outer
-%wall.  In~\citep{qua-moo2018} we reported the quick expanding space at
-%the narrow channel between neighboring bodies, the developing flat faces
-%at the sites of near contact, and bodies vanishing. In this nearly
-%touching bodies structure, we also observe these similar phenomena but
-%not totally the same.  For the speed of expanding space at the narrow
-%channel, we see some narrow channels do expand faster than other wider
-%channels.  For example, the spacing between bodies 14 and 18 is smaller
-%than the spacing between bodies 7 and 14 initially and the former one is
-%comparable to the latter one by the second frame. But there are some
-%small initial spacings that do not expand that much at all by the fourth
-%frame, for example between bodies 1 \& 6, 3 \& 9.  We could find the
-%explanation from the vorticity of fluid in Fig.~\ref{fig:Eroding20vort}.
-%Since the eroding velocity on the body is proportional to the absolute
-%value of vorticity in our erosion model,  then when the  absolute value
-%of vorticity is small there is not much erosion on the body.  In all
-%four frames of Fig.~\ref{fig:Eroding20vort}, the vorticity is relatively
-%small between bodies 1 \& 6 and 3 \& 9.
-%
-%Besides the channels between two bodies, there is a single channel goes
-%across the domain horizontally and the flow has been concentrated in
-%this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
-%channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
-%12, and 6 \& 19.  We can get a better understanding of this channel from
-%the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In the
-%top three frames of  Fig.~\ref{fig:Eroding20tracer}, the flow (or
-%tracer) first comes from three small channels between outer wall \& body
-%10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
-%one and go into the main channel between bodies 1 \& 9.  From the first
-%frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
-%is expanding faster than other channel and bodies 4 \& 12 has vanished
-%and body 19 is almost gone in the forth frame.  The reason of fast
-%expansion of this channel is the high vorticity.  In the forth frame of
-%Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
-%high on the side of bodies which form this channel so the bodies are
-%eroded fast on the side of this channel or have vanished completely.
-%
-%Furthermore, how long the body lasts for depends on not only the size of
-%the body but also the location of the body.  For example, the first
-%three vanishing bodies are body 12 (as t=0.0256), 4 (as t=0.0278), then
-%17 (as t=0.0287).  Since body 4 is located in the main flow channel so
-%the body 4 is vanished earlier than body 17 although the initial size of
-%body 4 is larger than the size of body 17.  This channel will keep
-%expanding and the bodies around this channel will vanish earlier than
-%others.  After body 17, the next 8 vanished bodies with respect to time
-%are body 19 (as t=0.0312),  body 7 (as t=0.0325), body 20 (as t=0.0329),
-%body 8 (as t=0.0349), body 10 (as t=0.0353), body 3 (as t=0.0356), body
-%14 (as t=0.0363), then body 9 (as t=0.0376).  All of these eight bodies
-%were around this channel before they are gone.
-%
-%For the flat faces at the sites of near contact, since we put the body
-%be close to one another so we are able to see all the channels between
-%two close bodies have flat faces.  Besides the channels between bodies,
-%we also observe the flat faces on the bodies which are close to the
-%outer wall. For example, we see the flat faces on the top of bodies 1 \&
-%6 and the bottom of bodies 13 \& 15.  
-%
-%Since we use a Barycentric quadrature rule to approximate the velocity
-%of tracers and apply the fourth order Runge Kutta method to find the new
-%locations of tracers in each step, the tracers can be very close to but
-%not penetrate the bodies.  Those body-closed tracers are moving
-%perfectly so we are able to observe the details of the interaction of
-%bodies and fluid.  Although the direction of flow is from left to right,
-%the tracers will not only travel horizontally but also vertically.  In
-%the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
-%climb up from right to left around the body.  There are zoom windows of
-%the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
-%they are taken from the last three frames of
-%Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
-%Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
-%from the channel below the body, climb up to the left, then go to the
-%right and join another tracers in the channel above the body. 
-%
-%In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we
-%measure the area occupied by bodies and the flow rate $U$ quantifily
-%during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
-%[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
-%when more and more bodies are vanished in the fluid. 
-%
-%The flow rate increases exponentially with growth rate close to
-%$\ln10^4$. 
-%
-%
-%In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect
-%of the geometrical structure on fluid velocity field. In
-%Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
-%x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
-%\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
-%and y in [-1,1]). The velocity is continuous along the cross section and
-%acting as several Poiseuille flows. This velocity graph is different
-%from the one in~\citep{matyka2008tortuosity} since we choose our cross
-%section to be the beginning of the flow before the fluid touches any
-%body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity
-%$\tau$ of the tracers at the cross section. This graph is not continuous
-%and the jumps in $\tau$ mean that the initial neighbor tracers have been
-%seperated by the bodies. 
-%
-%In Fig.~\ref{fig:Eroding20tort}(c)
-%In Fig.~\ref{fig:Eroding20tort}(d) 
-%}
-%
-%{\color{red}
-%To study the interaction of fluid and fixed bodies in the porous media,
-%some parameters can be used to describle the interation quantitively,
-%for example the porosity, the permeability, and the tortuosity. 
-%The relation of porosity and tortuosity has been studied in~\cite{matyka2008tortuosity}.
-%The definition of porosity is the ratio 
-%$$\phi=\frac{A_v}{A_T}$$
-%where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.}
-%{\color{red} The tortuosity represents the weighted average travel distance of a tracer in a porous media. 
-%The definition of tortuosity is 
-%$$T=\frac{1}{d}\frac{\displaystyle\int_{S}u_x(y) \lambda(y)dy}{\displaystyle\int_{S}u_x(y)dy}$$
-%where $S$ is an arbitrary cross section which is perpendicular to the x axis,
-%$\lambda(y)$ is the length of streamline at y on $S$, 
-%$u_x(y)$ is the component of velocity at y which is normal to $S$, and 
-%$d$ is the distance from $S$ to the end cross section.
-%It depends on not only the geometric structure but also the velocity of the fluid 
-%which is different from the porosity since porosity only depends on the geometric structure.}
-%{\color{red}Beisdes, the local tortuosity~\cite{matyka2008tortuosity} has been used to analysis 
-%the local behavior of steamline around a body. 
-%The definition of local tortuosity of the tracers at $y$ on $S$ is
-%$$\tau(y)=\frac{\lambda(y)}{d}.$$ 
-%}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Cauchy Integral Representation of the Pressure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%The pressure of the double-layer potential is
-%\begin{align}
-%  p(\xx) = -\frac{1}{\pi} \int_{\bd\Omega} \frac{1}{\rho^2}
-%    \left(1 - 2 \frac{\rr \otimes \rr}{\rho^2} \right) \nn
-%    \cdot \eeta(\yy) \, ds_\yy.
-%\end{align}
-%
-%
-%
-%{\color{red}
-%We
-%measure the area occupied by bodies 
-%during the eroding and record the flow rate $U$ quantifily in log scale
-%during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
-%Since we simulate the erosion by applying fixed pressure drop 
-%the flow rate $U$ is small when there are many bodies in the fluid and 
-%when the area fraction is getting smaller $U$ is getting larger.
-%In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
-%[-1,1]$ is occupied by 20 bodies initially and the flow rate $U$ starts from $9.86\times 10^{-5}$. 
-%Then the eroding speed is increasing
-%when more and more bodies are vanished in the fluid and 
-%the maximum eroding speed happens when the area fraction equals 7.57\% 
-%which is occupied by 8 bodies.
-%When all the bodies have vanished completely the flow rate $U$ is equal to 1.
-%In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate $U$ increases exponentially 
-%with growth rate close to $\ln10^4$. }
-%Besides the channels between two bodies, there is a single channel goes
-%across the domain horizontally and the flow has been concentrated in
-%this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
-%channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
-%12, and 6 \& 19.  We can get a better understanding of this channel from
-%the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In Fig.~\ref{fig:Eroding20tracer}, 
-%the flow (or tracer) first comes from three small channels between outer wall \& body
-%10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
-%one and go into the main channel between bodies 1 \& 9.  From the first
-%frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
-%is expanding faster than other channel and bodies 4 \& 12 has vanished
-%and body 19 is almost gone in the forth frame.  The reason of fast
-%expansion of this channel is the high vorticity.  In the forth frame of
-%Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
-%high on the side of bodies which form this channel so the bodies are
-%eroded fast on the side of this channel or have vanished completely.
-%{\color{red} 
-%Furthermore, how long the body lasts in the fluid depends on not only
-%the size of the body but also the location of the body.  For example,
-%the first three vanishing bodies are body 12 (as t=0.0256), 4 (as
-%t=0.0278), then 17 (as t=0.0287).  Since body 4 is located in the main
-%flow channel so the body 4 is vanished earlier than body 17 although the
-%initial size of body 4 is larger than the size of body 17.  This channel
-%will keep expanding and the bodies around this channel will vanish
-%earlier than others.  After body 17, the next 8 vanished bodies with
-%respect to time are body 19 (as t=0.0312),  body 7 (as t=0.0325), body
-%20 (as t=0.0329), body 8 (as t=0.0349), body 10 (as t=0.0353), body 3
-%(as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  All of
-%these eight bodies were around this channel before they are gone.
-%
-%For the flat faces at the sites of near contact, since we put the body
-%be close to one another so we are able to see all the channels between
-%two close bodies have flat faces.  Besides the channels between bodies,
-%we also observe the flat faces on the bodies which are close to the
-%outer wall. For example, we see the flat faces on the top of bodies 1 \&
-%6 and the bottom of bodies 13 \& 15.  
-%
-%Since we use a Barycentric quadrature rule to approximate the velocity
-%of tracers and apply the fourth order Runge Kutta method to find the new
-%locations of tracers in each step, the tracers can be very close to but
-%not penetrate the bodies.  Those body-closed tracers are moving
-%perfectly so we are able to observe the details of the interaction of
-%bodies and fluid.  Although the direction of flow is from left to right,
-%the tracers will not only travel horizontally but also vertically.  In
-%the bottom middle frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
-%climb up from right to left around the body.  There is a zoom windows of
-%the climbing tracers trajectories in the bottom right frame of Fig.~\ref{fig:Eroding20tracer} and
-%they are taken from the bottom middle frame of
-%Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the bottom right frame of 
-%Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
-%from the channel below the body, climb up to the left, then go to the
-%right and join another tracers in the channel above the body. 
-%}
-%\begin{figure}[H]
-%\begin{center}
-%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
-%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
-%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
-%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
-%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
-%  tracers around the bodies. Since we use a Barycentric quadrature rule
- % and the fourth order Runge Kutta method, the tracers can be very close
- % to but not penetrate the bodies.}
-%\end{center}
-%\end{figure}
-%{\color{red}
-%In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
-%from the starting cross section x = -1 to 
-%the end cross section x = 1 and 
-%use the local tortuosity to analysis the effect
-%of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
-%In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
-%x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
-%\times 10^{-3}$ at equal spreading tracers on the starting cross section.
-%The velocity is continuous along the starting cross section and
-%acting as several Poiseuille flows. This velocity graph is different
-%from the one in~\cite{matyka2008tortuosity} since we choose our cross
-%section to be the beginning of the flow before the fluid touches any
-%body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
-%$\tau(y)=\lambda(y)/d$
-%of the tracers at $y$ on the starting cross section x = -1 
-%where $d = 2$.
-%This graph is not continuous 
-%and the jumps in $\tau$ mean that the initial neighboring tracers have been
-%seperated by the bodies. 
-%The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
-%}
-%{\color{red}
-%In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
-%$\tau$ at two neighboring tracers 
-%and draw the trajectories of neighboring tracers
-%if the difference of $\tau$ at the neighboring tracers is large. 
-%From Fig.~\ref{fig:Eroding20tort}(c), we collect the 10 largest difference of $\tau$ 
-%at the neighboring tracers and 
-%draw the pair of trajectories in the same color and 
-%are able to tell the neighboring trajectories will be very 
-%different if they are separated by bodies.
-%For each pair of trajectories, 
-%they are splitted by the body at the left side of the body, then
-%one of them goes up and the other one goes down along the body 
-%until they rejoin with each other at the right side of body.  
-%Furthermore, the pair trajectories could be splitted by more than one body, 
-%for example in Fig.~\ref{fig:Eroding20tort}(c) the toppest red pair trajectories 
-%are splitted by two close bodies.
-%}
-
-%To measure the local behavior of fluid quantitatively, 
-%we use the velocities and local tortuosities at the starting cross section 
-%to analysis the interaction of fluid and bodies until the end cross section 
-%in Fig.~\ref{fig:Eroding100tort}(b) and (c).
-%In Fig.~\ref{fig:Eroding100tort}(b) the graph represents the ratio of the
-%x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
-%\times 10^{-4}$ at equal spreading tracers on the strating cross section.
-%As in the case of 20 nearly touching bodies, the velocity is continuous along
-%the starting cross section and acting as a Poiseuille flow in the channel between
-%bodies. When the fluid is close to bodies
-%the speed of fluid will be slow down because of the no-slip condition on the bodies
-%and this causes the separated branches of the inlet flow.
-%The maximum velocity of the fluid with 100 bodies on the starting cross 
-%section is slower than the maximum velocity of the fluid with 20 bodies
-%but the velocity in the case of 100 bodies 
-%changes more rapidly than the velocity of the fluid with 20 bodies.
-%The reason of the rapid change on the starting cross section of 
-%100-body case is because there are 
-%more bodies near the starting cross section in
-%100-body case than in the 20-body case. 
-%so the inlet flow in 100-body case
-%will be separated into more branches than the flow in 20-body case. 
-%
-%In Fig.~\ref{fig:Eroding100tort}(c) we record the 
-%local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
-%It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies
-%is 1.2547 and the minimum is 1.0003. This function $\tau$
-%has more jumps than the one in the case of 20 bodies but its maximum 
-%is smaller than the maximum in the case of 20 bodies. 
-%The jump in this graph means the neighboring trajectories are splitted by bodies
-%so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
-%since there are more bodies in the former case.
-
-%To study the behavior of fluid in the porous media with multiple bodies, 
-%we release 1000 tracers equispaced in $y$ from the 
-%cross section x = -1 and record their trajectories and velocities
-%until they arrive the end cross section x = 1 
-%and the porosity of this geometric structure is 62.98 \%. 
-%To understand the global action of fluid qualitatively, 
-%we only draw 200 historical trajectories from x = -1 to x = 1 
-%in Fig.~\ref{fig:Eroding100tort}(a). 
-%When equispaced tracers are released in a 2D tube without any grains, 
-%the streamlines are straight 
-%and the intersection points of streamlines and any cross section are equispaced. 
-%But it is not the same when there are bodies in the fluid. 
-%In Fig.~\ref{fig:Eroding100tort}(a)
-%even the tracers are equispaced in $y$ on the cross section $S$, 
-%the streamlines have been push up and down by the bodies and
-%some of them are close together. 
-%
-%
-%%To understand the meaning of jump 
-%%of $\tau$, we use the data we got from local tortuosity $\tau(y)$
-%%to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
-%%and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
-%%in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
-%%then rejoin with each other and the splitting-rejoining behavior causes the difference of $\tau$ with respect to the neighboring trajectories.   
-%%We also can get the idea why the maximum value of $\tau$ is smaller 
-%%than the one in the case of 20 bodies . 
-%%The most of the bodies in this case are smaller than those in the case of 20 bodies.
-%%So when two neighboring trajectories are splitted on the left side by a smaller body they do not
-%%travel as far as the two splitted by a bigger body do after they rejoin on the right side.
-
-%{\color{red}
-%This case is 100 bodies in a Hagen-Poiseuille flow. The background
-%flow is 
-%\begin{align}
-%  \UU(\xx)=U \left[
-%  \begin{array}{c}
-%    1-y^2 \\ 0
-%  \end{array}
-%  \right]
-%\end{align}
-%with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
-%We record the vorticity of 
-%fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
-%measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
-%Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
-%the magnitude of the vorticity is larger 
-%so the erosion is getting faster and faster 
-%from the first snapshot to the forth one in Fig.~\ref{fig:Eroding100vort}.
-%At t = 0.005 the porosity is 55.54\% and the most gap sizes between bodies are less than 0.015 in 
-%Fig.~\ref{fig:Eroding100gap}(a). Since some of the bodies are vanished in the fluid, the numner of gaps 
-%decreases and the gap sizes get larger and larger between the remaining bodies. 
-%In Fig.~\ref{fig:Eroding100gap}(b) and (c) we still can see small gap sizes are in the majority but 
-%it is not as concentrated as the one we see in Fig.~\ref{fig:Eroding100gap}(a). 
-%In Fig.~\ref{fig:Eroding100gap}(d) there are only 254 gaps between 82 bodies and 
-%the distribution of gap sizes spreads over without any major pack.  
-%}
-%
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width = 0.55\linewidth]{./figs/tort_eulerian}
-%\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
-%eroding geometry initialized with 20 bodies.  The tortuosity is
-%calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
-%and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
-%square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
-%The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ as
-%$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$.}
-%\end{figure}
-%
-%
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long_ref}
-%\caption{\label{fig:Eroding20anomalousMedium} The analysis of anomalous
-%dispersion in 20 nearly touching bodies with respect to initial porosity
-%(as p=37.68\%) and another six porosities during the eroding. The dashed
-%line correspondes to a porosity of 100\% and the dashed-dotted lines are
-%lines of best fit with slope 1.0644 (as p=95.1\%), 1.0673 (as
-%p=85.09\%), 1.0594 (as p=75.15\%), 0.9664 (as p=65.09\%), 0.7766 (as
-%p=55.10\%), 0.7475 (as p=45.08\%), and 0.5607 (as p=37.68\%.}
-%\end{figure}
-%
-
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian20b}
-%\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
-%eroding geometry initialized with 20 bodies.  The tortuosity is
-%calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
-%dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
-%as $p=0.1669$ and the root mean square deviation is $1.13 \times
-%10^{-2}$.}
-%\end{figure}
-%
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
-%\caption{\label{fig:Eroding20anomalousLow} The analysis of anomalous
-%dispersion in 20 nearly touching bodies with respect to initial porosity
-%(as p=30.67\%) and another seven porosities during the eroding. The
-%dashed line correspondes to a porosity of 100\% and the dashed-dotted
-%lines are lines of best fit with slope 0.9194 (as p=95\%), 0.8666 (as
-%p=85.17\%), 0.8682 (as p=75.10\%), 0.9087 (as p=65.02\%), 0.9054 (as
-%p=55.08\%), 0.7234 (as p=45.03\%), 0.6895 (as p=35.05\%), and 0.9225 (as
-%p=30.67\%).}
-%\end{figure}
-%
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian100}
-%\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
-%approach of tortuosity.  The blue dots are Eulerian approach of
-%tortuosity and the red stars and square are Lagrangian approach of
-%tortuosity.  The dash line is the fitting line
-%$\widehat{T}(\phi)=\phi^{-p}$ as $p=0.2459$ and the root-mean-square
-%error is $5.5 \times 10^{-3}$.  We note that the model
-%$\widehat{T}(\phi) = 1-p\ln(\phi)$, with $p=0.2631$ has a comparable
-%root-mean-square error of $5.2 \times 10^{-3}$.}
-%\end{figure}
-%
-%\begin{figure}
-%\center
-%\includegraphics*[width =0.55\linewidth]{./figs/100b_second_moment_long_ref}
-%\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
-%dispersion in 100 bodies with respect to initial porosity
-%(as p=50.09\%) and another five porosities during the eroding. The dashed line
-%correspondes to a porosity of 100\% and the dashed-dotted lines are lines
-%of best fit with slope 1.1135 (as p=95.12\%), 0.6825 (as p=85.07\%), 
-%0.7347 (as p=75.14\%), 0.5915 (as p=65.03\%), 
-%0.6107 (as p=55.02\%), and 0.7 (as p=50.09\%).}
-%\end{figure}
-%
-%\begin{figure}[H]
-%\begin{center}
-%\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
-%\caption{\label{fig:Eroding100tracer} The historical trajectories of 
-%200 tracers released at x = -1 in the fluid with multiple bodies.}
-%\end{center}
-%\end{figure}
-
-%\begin{figure}[H]
-%\center
-%\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
-%\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of 
-%local tortuosity $\tau$ at two neighboring tracers in
-%100 bodies eroding when the porosity is 62.98 \%
-%and the tortuosity is 1.1182. The same color of a pair of trajectories 
-%means they are from two neighboring tracers.}
-%\end{figure}
-
 \end{document}

### 2019-10-10 docs/transport/erosion_transport.tex
finished up formatting and looked at Nick's changes

@@
   consequence of the pore structure. Here we investigate transport
-  through \nick{a specific class of two-dimensional porous geometries, 
-  namely those formed by fluid-mechanical erosion.}  
-  We investigate the tortuosity and
-  dispersion by analyzing the first two statistical moments of tracer
-  trajectories. \nick{For most initial configurations, tortuosity decreases in time 
-  as a result of erosion increasing the porosity. 
-  However, we find that tortuosity can also increase transiently in certain cases.}
-  \nick{The porosity-tortuosity relationships that result from our simulations 
-  are compared against models available in the literature.}
-  \nick{Asymptotic dispersion rates are also strongly affected by the
-  erosion process, as well as by the number and
-  distribution of the eroding bodies.}  
-  Finally, we analyze the pore size
+  through a specific class of two-dimensional porous geometries, namely
+  those formed by fluid-mechanical erosion.  We investigate the
+  tortuosity and dispersion by analyzing the first two statistical
+  moments of tracer trajectories. For most initial configurations,
+  tortuosity decreases in time as a result of erosion increasing the
+  porosity.  However, we find that tortuosity can also increase
+  transiently in certain cases.  The porosity-tortuosity relationships
+  that result from our simulations are compared against models available
+  in the literature.  Asymptotic dispersion rates are also strongly
+  affected by the erosion process, as well as by the number and
+  distribution of the eroding bodies. Finally, we analyze the pore size
   distribution of an eroding geometry. The simulations are performed by
@@
 regime~\citep{qua-moo2018}. We, however, make key improvements to the
-numerical methods \nick{(I killed the reference here because I think its redundant)} to enable simulations of more
-realistic, dense suspensions of eroding grains
-(figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  Then, to
-characterize transport through these configurations, we examine
-coarse-grained variables through statistical analysis of tracer
-trajectories.
+numerical methods to enable simulations of more realistic, dense
+suspensions of eroding grains (figures~\ref{fig:Eroding50vel}
+and~\ref{fig:Eroding50vort}).  Then, to characterize transport through
+these configurations, we examine coarse-grained variables through
+statistical analysis of tracer trajectories.
 
@@
 the hydrodynamic shear stress~\citep{wan-fel2004,
-ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  \nick{We compute
-the vorticity in the fluid bulk since, on solid boundaries, vorticity
+ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  We compute the
+vorticity in the fluid bulk since, on solid boundaries, vorticity
 reduces to shear and thus provides a convenient way to simultaneously
-visualize local erosion rates and changes in the surrounding flow}
+visualize local erosion rates and changes in the surrounding flow
 (figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
@@
 results in the collocation method for~\eqref{eqn:BIE}
-\todo[inline]{left off here with formatting equations}
 \begin{subequations}
@@
     \nonumber \\
-  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^0_\ell) + 
+  &+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^0_\ell) + 
   \sum_{k=1}^M R[\xi_k,\cc_k](\yy^0_\ell), 
-    &&\hspace{-60pt} \ell = 1,\ldots,N_\out, \\
+  &&\hspace{-124pt}\ell = 1,\ldots,N_\out, \\
 %
@@
     w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j \nonumber \\
-  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^m_\ell) + 
+  &+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^m_\ell) + 
   \sum_{k=1}^M R[\xi_k,\cc_k](\yy^m_\ell),
-    &&\hspace{-60pt}\ell = 1,\ldots,N_\iin, \: m=1,\ldots,M, \\
+    &&\hspace{-124pt}m=1,\ldots,M, \: \ell = 1,\ldots,N_\iin,  \\
 %
-  \llambda_m &= \frac{1}{2\upi} \sum_{j=1}^{N_\iin} w_j^m \eeta^m_j,
-  \quad \xi_m = \frac{1}{2\upi} \sum_{j=1}^{N_\iin} w_j^m
-    (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
-    &&\hspace{-60pt} m=1,\ldots,M,
+  \llambda_m &= \frac{1}{2\upi} \sum_{j=1}^{N_\iin} 
+    w_j^m \eeta^m_j, 
+  &&\hspace{-124pt}m = 1,\ldots,M \\ 
+  \xi_m &= \frac{1}{2\upi} \sum_{j=1}^{N_\iin} 
+    w_j^m (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
+  &&\hspace{-124pt}m=1,\ldots,M,
 \end{alignat}

### 2019-10-12 docs/transport/erosion_transport.tex
NM
done up to section 6

@@
 \begin{document}
+
+\maketitle
 
@@
   transiently in certain cases.  The porosity-tortuosity relationships
-  that result from our simulations are compared against models available
-  in the literature.  Asymptotic dispersion rates are also strongly
+  that result from our simulations are compared with models available in
+  the literature.  Asymptotic dispersion rates are also strongly
   affected by the erosion process, as well as by the number and
@@
 %\end{keyword}
-
-\maketitle
 
@@
 
-This study consists of two main undertakings: first, high-fidelity
-simulations of eroding porous media, and, second, characterization of
-tracer transport through the resulting eroded geometries. Our modeling
-efforts build on previous work~\citep{ris-moo-chi-she-zha2012,
-moore2013self, moo2017}, in particular recent numerical methods
-developed to simulate erosion in the Stokes-flow
-regime~\citep{qua-moo2018}. We, however, make key improvements to the
-numerical methods to enable simulations of more realistic, dense
-suspensions of eroding grains (figures~\ref{fig:Eroding50vel}
-and~\ref{fig:Eroding50vort}).  Then, to characterize transport through
-these configurations, we examine coarse-grained variables through
-statistical analysis of tracer trajectories.
-
 \begin{figure}
@@
 \end{figure}
+
+This study consists of two main undertakings: first, high-fidelity
+simulations of eroding porous media, and, second, characterization of
+tracer transport through the resulting eroded geometries. Our modeling
+efforts build on previous work~\citep{ris-moo-chi-she-zha2012,
+moore2013self, moo2017}, in particular recent numerical methods
+developed to simulate erosion in the Stokes-flow
+regime~\citep{qua-moo2018}. We, however, make key improvements to the
+numerical methods to enable simulations of more realistic, dense
+suspensions of eroding grains (figures~\ref{fig:Eroding50vel}
+and~\ref{fig:Eroding50vort}).  Then, to characterize transport through
+these configurations, we examine coarse-grained variables through
+statistical analysis of tracer trajectories.
 
@@
 fluid equations to a boundary integral equation (BIE).
+
+\begin{figure}
+\begin{center}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b1}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b80}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b160}\\
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b240}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b320}
+\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b400}
+\caption{\label{fig:Eroding50vort} The same six snapshots as
+figure~\ref{fig:Eroding50vel}.  The color is the vorticity of the fluid.
+Since the rate of erosion is equivalent to the magnitude of the
+vorticity, erosion is fastest in the yellow and blue regions and slowest
+in the green regions.}
+\end{center}
+\end{figure}
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b1}
-\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b80}
-\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b160}\\
-\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b240}
-\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b320}
-\includegraphics[height = 0.3 \textwidth]{./figs/vort_50b400}
-\caption{\label{fig:Eroding50vort} The same six snapshots as
-figure~\ref{fig:Eroding50vel}.  The color is the vorticity of the fluid.
-Since the rate of erosion is equivalent to the magnitude of the
-vorticity, erosion is fastest in the yellow and blue regions and slowest
-in the green regions.}
-\end{center}
-\end{figure}
-
 To characterize transport through the resulting configurations, particle
@@
 where $\uu$ is the fluid velocity.  Since there is no stiff diffusive
-term in~\eqref{eqn:tracers}, we use a fourth-order explicit Runge-Kutta
-time stepping method.  In addition, the Barycentric quadrature rule is
-used to accurately compute trajectories that are close to an eroding
-grain. We note that an alternative approach to compute trajectories is
-to form a distribution of velocities $\uu$ and use a continuous time
-random walk~\citep{mon-wei1965, den-cor-sch-ber2004, leb-den-car2008,
-ber-cor-den-sch2006}.
+term, we solve~\eqref{eqn:tracers} with a fourth-order explicit
+Runge-Kutta time stepping method.  In addition, the Barycentric
+quadrature rule is used to accurately compute trajectories that are
+close to an eroding grain. 
+%We note that an alternative approach to
+%compute trajectories is to form a distribution of velocities $\uu$ and
+%use a continuous time random walk~\citep{mon-wei1965,
+%den-cor-sch-ber2004, leb-den-car2008, ber-cor-den-sch2006}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Contributions}
-Our first contribution is extending the Barycentric quadrature rule
-of~\citet{bar-wu-vee2015} to accurately compute velocity gradients
-associated with Stokes flow. This new quadrature rule permits accurate
-and stable simulations of erosion, and, moreover, enables visualization
-of the vorticity field throughout.
-
-Our second contribution is computing and analyzing trajectories in
-eroded geometries.  These trajectories are formed by combining the
-Barycentric quadrature rule and a fourth-order Runge-Kutta method. Then,
-they are used to compute tortuosities and dispersion rates of eroded
-geometries. Finally, we examine the effect of erosion on the pore size
-distribution.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Limitations}
-As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
-immobile eroding grains. However, this work does not limit the proximity
-of  grains. Compared to our previous work, we are able to simulate much
-denser suspensions with a comparable number of discretization points and
-without upsampling.  While we do investigate transport in this work, we
-only consider passive particles that are advected by the flow.  To model
-other physical processes, such as contaminant transport, we plan to
-simulate a finite Peclet number advection-diffusion equation in eroded
-geometries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Outline of the Paper}
-In Section~\ref{sec:formulation}, we summarize the erosion model that is
-described in more detail in previous work~\citep{qua-moo2018}.  In
-Section~\ref{sec:DLP}, we recast all the governing equations as layer
-potentials defined in both $\RR^2$ and in $\CC$.
-Section~\ref{sec:transport} describes measures for characterizing the
-geometry and transport. Section~\ref{sec:method} describes the numerical
-methods, with special attention paid to the new quadrature method for
-computing the shear stress and the vorticity.  Section~\ref{sec:results}
-presents numerical examples for a variety of dense packings of bodies.
-Finally, concluding remarks are made in Section~\ref{sec:conclusions}.
+%\subsection{Contributions}
+%Our first contribution is extending the Barycentric quadrature rule
+%of~\citet{bar-wu-vee2015} to accurately compute velocity gradients
+%associated with Stokes flow. This new quadrature rule permits accurate
+%and stable simulations of erosion, and, moreover, enables visualization
+%of the vorticity field throughout.
+%
+%Our second contribution is computing and analyzing trajectories in
+%eroded geometries.  These trajectories are formed by combining the
+%Barycentric quadrature rule and a fourth-order Runge-Kutta method. Then,
+%they are used to compute tortuosities and dispersion rates of eroded
+%geometries. Finally, we examine the effect of erosion on the pore size
+%distribution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Limitations}
+%As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
+%immobile eroding grains. However, this work does not limit the proximity
+%of  grains. Compared to our previous work, we are able to simulate much
+%denser suspensions with a comparable number of discretization points and
+%without upsampling.  While we do investigate transport in this work, we
+%only consider passive particles that are advected by the flow.  To model
+%other physical processes, such as contaminant transport, we plan to
+%simulate a finite Peclet number advection-diffusion equation in eroded
+%geometries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Outline of the Paper}
+This paper is organized as follows. In section~\ref{sec:formulation}, we
+summarize the erosion model that is described in more detail in previous
+work~\citep{qua-moo2018}.  In section~\ref{sec:DLP}, we recast all the
+governing equations as layer potentials defined in both $\RR^2$ and in
+$\CC$.  Section~\ref{sec:transport} describes measures for
+characterizing the geometry and transport. Section~\ref{sec:method}
+describes the numerical methods, with special attention paid to the new
+quadrature method for computing the shear stress and the vorticity.
+Section~\ref{sec:results} presents numerical examples for a variety of
+dense packings of bodies.  Finally, concluding remarks are made in
+section~\ref{sec:conclusions}.
 
@@
 is the shear stress on $\gamma$. We simulate erosion by alternating
-between solving the fluid equations and advancing the erodible
-boundaries. The strength of $\UU$ is adjusted at each time step to
-achieve a constant pressure drop across the channel.
+between solving the fluid equations and advancing the eroding grains.
+The strength of $\UU$ is adjusted at each time step to achieve a
+constant pressure drop across the channel.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since we require an accurate solution of the incompressible Stokes
+Since we require accurate solutions of the incompressible Stokes
 equations in complex two-dimensional geometries, we reformulate the
@@
 pressure, and vorticity are all written as layer potentials in $\RR^2$.
-However, the quadrature method we introduce in Section~\ref{sec:method}
+However, the quadrature method we introduce in section~\ref{sec:method}
 requires a complex-valued representation of the layer potentials for the
@@
 \begin{subequations}
+  \label{eqn:cauchy}
   \begin{alignat}{3}
-  \label{eqn:cauchy}
   v(x) &= \frac{1}{2\upi i}\int_{\bd\Omega} 
@@
 vorticity at $x \in \Omega$ is
-\begin{equation}
-  \begin{aligned}
-    \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} &= 
-      \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))  \\
-      &+ \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
-  \end{aligned}
-\end{equation}
+\begin{align}
+  \omega(x) = 
+    \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))+ 
+    \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
+\end{align}
 
@@
     \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
-    \sigma_\lambda^2(t) = \frac{1}{N_p} 
+    \sigma_\lambda^2(t) = \frac{1}{N_p} \sum_{j=1}^{N_p}
     \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2,
@@
 \end{align}
-In Section~\ref{sec:results}, we compare the second moment in an open
+In section~\ref{sec:results}, we compare the second moment in an open
 channel with the trajectories in an eroded geometry.
@@
 \end{align}
-Here, the streamline originates on the inlet cross-section $x=x_0$ at
+Here the streamline originates on the inlet cross-section $x=x_0$ at
 $(x_0,y_0)$, and its arclength, $\lambda(y_0)$, is calculated until the
@@
 
-The definition we made for the tortuosity allows us to compute the
-tortuosity in terms of an area integral.  Assuming that the flow is
-incompressible and not re-entrant, meaning that all streamlines connect
-the two cross-sections, the tortuosity in
-equation~\eqref{eqn:tortuosity1} is equivalent to~\citep{dud-koz-mat2011}
+The tortuosity can also be computed with an area integral. Assuming that
+the flow is incompressible and not re-entrant, meaning that all
+streamlines connect the two cross-sections, the tortuosity in
+equation~\eqref{eqn:tortuosity1} is equivalent
+to~\citep{dud-koz-mat2011}
 \begin{align}
@@
 do compare the two definitions for the tortuosity at several porosities
-in Section~\ref{sec:results}.
+in section~\ref{sec:results}.
 
@@
 \end{subequations}
-where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
+where $p>0$ is a fitting parameter.  In section~\ref{sec:results}, we
 compare these four models with the tortuosity of eroding porous
@@
 distribution, a distribution used by others to characterize pore
-sizes~\citep{ioa-cha1993}.  In Section~\ref{sec:Eroding100}, we
+sizes~\citep{ioa-cha1993}.  In section~\ref{sec:Eroding100}, we
 investigate the effect of erosion on the pore size distribution.
@@
 boundary of the geometry at a set of collocation points distributed
-equally in arclength (Section~\ref{sec:spatialDiscretization}).
+equally in arclength (section~\ref{sec:spatialDiscretization}).
 Depending on the proximity of the target point to the source points, the
 quadrature rule is either the trapezoid rule or the Barycentric
-quadrature rule (Section~\ref{sec:bary}).  The criteria that determines
+quadrature rule (section~\ref{sec:bary}).  The criteria that determines
 which quadrature method is applied is described in
-Section~\ref{sec:fmm}.  Once the shear stress is computed, the bodies
+section~\ref{sec:fmm}.  Once the shear stress is computed, the bodies
 are eroded a single time step by using a {\thL}
@@
 stepping methods for erosion and passive particles are described in
-Section~\ref{sec:time}.
+section~\ref{sec:time}.
 
@@
   \sum_{k=1}^M R[\xi_k,\cc_k](\yy^0_\ell), 
-  &&\hspace{-124pt}\ell = 1,\ldots,N_\out, \\
+  &&\hspace{-120pt}\ell = 1,\ldots,N_\out, \\
 %
@@
   \sum_{k=1}^M R[\xi_k,\cc_k](\yy^m_\ell),
-    &&\hspace{-124pt}m=1,\ldots,M, \: \ell = 1,\ldots,N_\iin,  \\
+    &&\hspace{-120pt}m=1,\ldots,M, \: \ell = 1,\ldots,N_\iin,  \\
 %
@@
     w_j^m \eeta^m_j, 
-  &&\hspace{-124pt}m = 1,\ldots,M \\ 
+  &&\hspace{-120pt}m = 1,\ldots,M \\ 
   \xi_m &= \frac{1}{2\upi} \sum_{j=1}^{N_\iin} 
     w_j^m (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
-  &&\hspace{-124pt}m=1,\ldots,M,
+  &&\hspace{-120pt}m=1,\ldots,M,
 \end{alignat}
@@
 system~\eqref{eqn:trapLinearSystem} is a well-conditioned second-kind
-integral equation that is solved iteratively with GMRES.  If the number
+integral equation and is solved iteratively with GMRES.  If the number
 of discretization points is sufficiently large, then the solution
@@
 
-We showed in Sections~\ref{sec:DLPcomplex} and~\ref{sec:gradDLPcomplex}
+We showed in sections~\ref{sec:DLPcomplex} and~\ref{sec:gradDLPcomplex}
 that the velocity, shear stress, and vorticity of the double-layer
 representation can all be written as the sum of Cauchy integrals and its
-first two derivatives.  Therefore, we can accurately compute the
-velocity, shear stress, and vorticity at any target location by using a
-quadrature rule with a uniform error bound for Cauchy integrals and its
+first two derivatives.  Therefore, we require quadrature rules with a
+uniform error bound for Cauchy integrals and its
 derivatives~\eqref{eqn:cauchy}. \citet{ioa-pap-per1991} developed
@@
 quadrature rules to compute the Stokes double-layer potential
-representation of the velocity~\eqref{eqn:velocityDLP}, and we briefly
-summarize their method.  Then, we extend their work to compute the
-second derivative so that the shear stress and vorticity can be computed
-with a uniform error bound.
+representation of the velocity~\eqref{eqn:velocityDLP}. After briefly
+summarizing this method, we extend the work to compute the second
+derivative so that the shear stress and vorticity can be computed with a
+uniform error bound.
 
 We present the quadrature rules for a simply-connected interior domain
-$\Omega \subset \CC$, with any point $a \in \Omega$, and we consider the
+$\Omega \subset \CC$, with any point $a \in \Omega$, and we consider
 target points $x \in \Omega$ and $x \in \Omega^c$. Then, these
 quadrature rules can be applied to individual components of a
-multiply-connected domain to compute layer potentials of a porous media.
-The method starts with an underlying quadrature rule, and we use the
-spectrally accurate trapezoid rule with $N$ points.  Since the
-quadrature points are uniformly distributed, the quadrature weights are
-$w_j = L/N$, $j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.
+multiply-connected domain to compute the velocity, vorticity, and
+deformation tensor in an eroding porous media.  The method starts with
+an underlying quadrature rule, and we use the spectrally accurate
+$N$-point trapezoid rule.  Since the quadrature points are uniformly
+distributed, the quadrature weights are $w_j = L/N$, $j=1,\ldots,N$,
+where $L$ is the length of $\bd\Omega$.
 
@@
 \end{align}
-Note that the value $v(x)$ is required to compute $v'(x)$ for both the
-interior and exterior case, and these are available using the
-Barycentric quadrature rules~\eqref{eqn:BaryvInterior}
+Note that $v(x)$ is required to compute $v'(x)$ for both the interior
+and exterior case, and this is available using the Barycentric
+quadrature rules~\eqref{eqn:BaryvInterior}
 and~\eqref{eqn:BaryvExterior}.
@@
 \end{align}
-The quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$,
-and theses are computed using the quadrature rules in
+The quadrature rule for $v''(x)$ requires $v(x)$ and $v'(x)$, and theses
+are computed using the quadrature rules in
 equations~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},
-and~\eqref{eqn:BaryvprimeExterior}. In Section~\ref{sec:results}, these
+and~\eqref{eqn:BaryvprimeExterior}. In section~\ref{sec:results}, these
 quadrature rules are used to form simulations of nearly-touching eroding
@@
 multipole method (FMM)~\citep{gre-rok1987}, this cost can be reduced to
-$O(N)$ operations.  However, the Barycentric quadrature rules
-require several $N$-body calculations.  The resulting cost would be
-prohibitive, so we introduce a hybrid method that combines the
-Barycentric quadrature rule and an accelerated trapezoid rule.  Note
-that the source points of the layer potential is always one of the
-eroding bodies or the outer wall, but the target point can either be on
-another component of $\bd\Omega$ or it can be in the fluid bulk
+$O(N)$ operations.  However, each application of the Barycentric
+quadrature rules involve several $N$-body calculations, rendering the
+computational cost prohibitive, so we introduce a hybrid method that
+combines the Barycentric quadrature rule and an accelerated trapezoid
+rule.  Note that the source points of the layer potential is always one
+of the eroding bodies or the outer wall, but the target point can either
+be on another component of $\bd\Omega$ or it can be in the fluid bulk
 $\Omega$.
@@
 \begin{align}
-  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_k} \sum_{j=1}^{N_\iin} 
+  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_\iin} \sum_{j=1}^{N_\iin} 
     D(\xx,\yy^k_j) \eeta(\yy_j) + \vv^k_\bary(\xx),
@@
 due to $\gamma_k$.  This strategy naturally extends to points that are
-close to $\Gamma$, and to the scenario when $\xx$ is simultaneously
-close to multiple components of $\bd\Omega$.  While the term
-$\vv_\trap(\xx)$ in equation~\eqref{eqn:velocityDecomp} is computed for
-all target points using the FMM, the other two terms are computed with a
-direct summation.  However, these terms are only required for target
-points near an eroding body or the outer wall, and these points make up
-only a small fraction of the total number of points.
+close to $\Gamma$, and to points that are simultaneously close to
+multiple components of $\bd\Omega$.  While the term $\vv_\trap(\xx)$ in
+equation~\eqref{eqn:velocityDecomp} is computed for all target points
+using the FMM, the other two terms are computed with a direct summation.
+However, these terms are only required for target points near an eroding
+body or the outer wall, and these points make up only a small fraction
+of the total number of points.
 
@@
 step, the trapezoid rule is applied with a direct summation rather than
-the FMM.  Relative to the cost of computing the velocity at each
-iteration of GMRES with the FMM, the additional once-per-time-step costs
-to compute the vorticity and deformation tensor are minimal.
+the FMM.  Relative to the cost of computing the velocity at each GMRES
+iteration with the FMM, the additional once-per-time-step costs to
+compute the vorticity and deformation tensor are minimal.
 
@@
 \end{align}
-To avoid checking if all target points $\xx$
-satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL}
-variables~\citep{hou-low-she1994}.  First, given two eroding bodies
-$\gamma_i$ and $\gamma_j$ with lengths $L_i$ and $L_j$, and centroids
-$\cc_i$ and $\cc_j$, we check if
+Instead of checking if all target points $\xx$
+satisfy~\eqref{eqn:TrapCutoff}, we first check, for all pairs of eroding
+grains, if
 \begin{align}
@@
 \end{align}
-where $\alpha_\iin \geq 1$ is a parameter that needs to be determined.
-In this manner, rather than using an expensive all-to-all algorithm to
-compute the distance between all pairs of discretization points, we
-compute the distance between pairs of circle centers.  This criteria
-allows us to quickly determine bodies that contain discretization points
-where the Barycentric quadrature rule might need to be applied, and the
-parameter $\alpha_\iin$ accounts for the fact that the bodies are being
-approximated with circles.  Assuming that the two bodies $\gamma_i$ and
-$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
-\in \gamma_j$, we check if
+where $\cc_i$ is the center of grain $i$, $L_i$ is the length of its
+boundary, and $\alpha_\iin \geq 1$ is a parameter that needs to be
+determined.  In this manner, rather than using an expensive all-to-all
+algorithm to compute the distance between pairs of discretization
+points, we compute the distance between pairs of circle centers.  This
+criteria allows us to quickly determine bodies that contain
+discretization points where the Barycentric quadrature rule might need
+to be applied, and the parameter $\alpha_\iin$ accounts for the
+approximation that the grains are circular.  Assuming that the two
+bodies $\gamma_i$ and $\gamma_j$ satisfy
+condition~\eqref{eqn:BodyCutoff}, for each point $\xx \in \gamma_j$, we
+check if
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We use the time stepping method outlined in Section 3.3 of our previous
-work~\citep{qua-moo2018} which we briefly summarize here.  The erosion
-rate loses differentiability if the shear stress changes sign, and this
-leads to corners developing on $\gamma$ and numerical instabilities.
-Therefore, we modify the erosion rate, $V_\nn$ in
-equation~\eqref{eqn:erosionModel}, with
+We use the time stepping method outlined in our previous
+work~\citep[see][section 3.3]{qua-moo2018} which we briefly summarize
+here.  The erosion rate loses differentiability if the shear stress
+changes sign, and this leads to corners developing on $\gamma$ and
+numerical instabilities.  Therefore, we modify the erosion rate, $V_\nn$
+in equation~\eqref{eqn:erosionModel}, with
 \begin{align}
@@
 $L$ is the length of $\gamma$, and $\kappa$ is the curvature of
-$\gamma$.  This new term penalizations regions of high curvature, and
-the normalization term guarantees that the regularization only changes
-the body's shape, but not its total length.  Finally, to increase the
+$\gamma$.  This new term penalizes regions of high curvature, and the
+normalization term guarantees that the regularization only changes the
+body's shape, but not its total length.  Finally, to increase the
 overall stability of the method, a narrow Gaussian filter is applied to
@@
 To compute the tortuosity and the anomalous dispersion rates
-(Section~\ref{sec:transport}), we require the streamlines that are
+(section~\ref{sec:transport}), we require the streamlines that are
 governed by equation~\eqref{eqn:tracers}.  To characterize the
@@
 depending on the proximity of $\ss(t)$ to $\bd\Omega$
-(Section~\ref{sec:fmm}), we apply the trapezoid rule or the Barycentric
+(section~\ref{sec:fmm}), we apply the trapezoid rule or the Barycentric
 quadrature rule.  For time stepping, we use a fourth-order explicit
-Runge-Kutta method.  Since the trajectories are computed with high-order
-methods in both space and time,  we are able to simulate dynamics very
-close to the eroding bodies (see figures~\ref{fig:Eroding20tracer}
-and~\ref{fig:Eroding100tort}).
+Runge-Kutta method.  By using these high-order methods, we are able to
+simulate dynamics very close to the eroding bodies (see
+figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}).
 
@@
 that the statistics have converged~\citep{bel-sal-rin1992}.  However, as
-described in Section~\ref{sec:dispersion}, a reinsertion method is used
+described in section~\ref{sec:dispersion}, a reinsertion method is used
 to compute trajectories that are sufficiently long to observe an
@@
 leads to corner formation on the bodies.  As described in
-Section~\ref{sec:formulation} and our previous work~\citep{qua-moo2018},
-we introduce a curvature penalization term and a Gaussian smoothing step
-to ameliorate corner formation.  For all examples, we use the smoothing
-parameters $\eps=15/256$ and $\sigma=10/256$, and the time step size is
-$\Delta t = 10^{-4}$.
+section~\ref{sec:time} and our previous work~\citep{qua-moo2018}, we
+ameliorate corner formation by introducing a curvature penalization term
+with parameter $\epsilon$ and a Gaussian smoothing step with parameter
+$\sigma$.  For all examples, we use the smoothing parameters
+$\eps=15/256$ and $\sigma=10/256$, and the time step size is $\Delta t =
+10^{-4}$.
 
@@
 spreading reaches a statistical equilibrium, we use the reinsertion
-algorithm described in Section~\ref{sec:dispersion} to form sufficiently
+algorithm described in section~\ref{sec:dispersion} to form sufficiently
 long trajectories.  For all the reported porosities, the particle
@@
 example, we analyze the spreading at several different porosities and we
-use the reinsertion algorithm described in Section~\ref{sec:dispersion}.
+use the reinsertion algorithm described in section~\ref{sec:dispersion}.
 For all the porosities, the dispersion is much closer to ballistic when
@@
 asymptotic super-dispersive spreading.  In contrast to the higher
-porosity initial condition (Section~\ref{sec:Eroding20}), at early times
+porosity initial condition (section~\ref{sec:Eroding20}), at early times
 the erosion results in a decrease in the dispersion rate. In particular,
@@
 required in network models~\citep{bry-mel-cad1993, bry-kin-mel1993}.  As
-described in Section~\ref{sec:throats}, we use a Delaunay triangulation
+described in section~\ref{sec:throats}, we use a Delaunay triangulation
 to define neighboring eroding bodies, and we compute the pore size by
@@
 
+\todo[inline]{dump of text}
+As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
+immobile eroding grains. However, this work does not limit the proximity
+of  grains. Compared to our previous work, we are able to simulate much
+denser suspensions with a comparable number of discretization points and
+without upsampling.  While we do investigate transport in this work, we
+only consider passive particles that are advected by the flow.  To model
+other physical processes, such as contaminant transport, we plan to
+simulate a finite Peclet number advection-diffusion equation in eroded
+geometries.
+\todo[inline]{dump of text}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-10-12 docs/transport/erosion_transport.tex
done up to section 6
up to section 6.3

@@
 geometries by examining coarse-grained variables.  Each eroding body is
-initially a circle with center $\cc_i$ and radius $r_i$.  The center and
-radius are chosen at random, and the body is accepted if it is contained
-in $[-1,1] \times [-1,1]$ and is sufficiently separated from all other
-bodies.  Since the error of our quadrature method is bounded independent
-of the geometry, we consider bodies that are separated by less than 10\%
-of an arclength spacing.  The randomized method is repeated until the
-initial geometry reaches a desired initial porosity.
-
-Once the geometry is initialized, each body has length $L_i = 2\upi
-r_i$, and they are each discretized with $N_\iin$ points.  A no-slip
-boundary condition is imposed on each eroding body $\gamma_i$.  For all
-simulations, we discretize the outer wall $\Gamma$ with $N_\out=1024$
-points.  For all but the first example, the Dirichlet boundary condition
-on $\Gamma$ is a Hagen-Poiseuille flow, and the flow rate is adjusted at
-each time step to maintain a constant pressure drop. Since the fluid
-equations are linear, this is achieved by computing the pressure near
-the inlet and outlet at each time step, and then scaling the flow rate
-appropriately~\citep{qua-moo2018}.
+initially a circle with center $\cc_i$, $r_i$, and length $L_i = 2\upi
+r_i$.  The center and radius are chosen at random, and the body is
+accepted if it is contained in $[-1,1] \times [-1,1]$ and is
+sufficiently separated from all other bodies.  Since the error of our
+quadrature method is bounded independent of the geometry, we consider
+bodies that are separated by less than 10\% of an arclength spacing.
+The randomized method is repeated until the initial geometry reaches a
+desired initial porosity.
+
+For all simulations, we discretize each eroding grain with $N_\iin =
+256$ points and the outer wall $\Gamma$ with $N_\out=1024$ points.  A
+no-slip boundary condition is imposed on each eroding body $\gamma_i$,
+and a Dirichlet boundary condition on $\Gamma$ is used to approximate a
+far-field boundary condition. For all but the first example, the
+Dirichlet boundary condition is a Hagen-Poiseuille flow, and the flow
+rate is adjusted at each time step to maintain a constant pressure drop.
+Since the fluid equations are linear, this is achieved by computing the
+pressure near the inlet and outlet at each time step, and then scaling
+the flow rate appropriately~\citep{qua-moo2018}.
 
@@
 ameliorate corner formation by introducing a curvature penalization term
-with parameter $\epsilon$ and a Gaussian smoothing step with parameter
+with parameter $\eps$ and a Gaussian smoothing step with parameter
 $\sigma$.  For all examples, we use the smoothing parameters
@@
 In each of the examples, we plot the vorticity in the fluid bulk.  Since
-the vorticity and the shear stress agree on surface of the eroding
-bodies, the vorticity is useful to visualize the erosion rate.  In
+the vorticity and the shear stress agree on the boundary of the eroding
+grains, the vorticity is useful to visualize the erosion rate.  In
 particular, the rate of erosion is largest in regions where the
@@
 Their initial body is a sphere with its center located $1.5$ radii above
-the solid wall.  In two dimensions, the trapezoid rule is spectrally
-accurate, and an analogous initial configuration is possible. However,
-unless the number of discretization points is increased, the trapezoid
-rule becomes obsolete if the eroding body is initialized too close to
-the solid wall. Therefore, to simulate erosion near a solid wall at
-reasonable levels of discretization, we use our hybrid method that
-combines the trapezoid rule and the Barycentric quadrature rule.
-
-We consider an eroding body that is initially a circle of radius
-$r=0.4$.  We discretize the eroding body with $N_\iin=256$
-discretization points, and its center is chosen so that the distance
-between the body and the solid wall is $h$, $h/2$, and $h/10$, where $h
-= 2\upi r/N_\iin$.  If we used the trapezoid rule and required an error
-that is comparable to the Barycentric quadrature rule, the body with an
-initial distance of $h/10$ from the solid wall would require $6,400$
-discretization points, and the outer wall would require $50,000$
+the solid wall.  We initialize the two-dimensional eroding body with
+radius $r = 0.4$, and we conduct numerical experiments where the initial
+distance between the grain and the solid wall is $h$, $h/2$, and $h/10$,
+where $h = 2\upi r/N_\iin$.  If we used the trapezoid rule and required
+an error that is comparable to the Barycentric quadrature rule, the body
+with an initial distance of $h/10$ from the solid wall would require
+$6,400$ discretization points, and the outer wall would require $50,000$
 discretization points.
@@
 logarithm of the shear stress.  Since the shear stress is always
-positive, the erosion rate is smooth and corners do not develop, but
-interesting shapes form nonetheless.  For instance, in the top half of
-the body, there is a sudden increase in the shear stress, and this leads
-to a region of high curvature.  This behavior is also present in three
-dimensions~\citep[see figure 7(c)]{mit-spa2017}.  The biggest difference
-between the two- and three-dimensional results is the presence of a
-recirculation zone.  In three dimensions, there is no recirculation
-between the solid wall and the spherical body~\citep{cha-feu2003}, but
-recirculation is possible in two dimensions~\citep{chw-wu1975, hig1985}.
-To visualize the flow, we plot the vorticity of the final time step from
-figure~\ref{fig:NearWall} in figure~\ref{fig:NearWall_vort}.  In these
-examples, a small recirculation zone, both in size and magnitude, is
-present in the region where the vorticity is smallest
+positive, the erosion rate is smooth and corners do not develop.
+However, in the top half of the body, there is a sudden increase in the
+shear stress, and this leads to a region of high curvature.  This
+behavior is also present in three dimensions~\citep[see figure
+7(c)]{mit-spa2017}.  The biggest difference between the two- and
+three-dimensional results is the presence of a recirculation zone.  In
+three dimensions, there is no recirculation between the solid wall and
+the spherical body~\citep{cha-feu2003}, but recirculation is possible in
+two dimensions~\citep{chw-wu1975, hig1985}.  To visualize the flow, we
+plot the vorticity of the final time step from figure~\ref{fig:NearWall}
+in figure~\ref{fig:NearWall_vort}.  In these examples, a small
+recirculation zone, both in size and magnitude, is present in the region
+where the vorticity is smallest
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider 20 eroding bodies that are discretized with $N_\iin=256$
-points.  The background flow is the Hagen-Poiseuille flow
+We consider 20 eroding grains with the Hagen-Poiseuille flow
 \begin{align}
@@
 \end{align}
-where the flow rate $U$ is chosen so that the average pressure drop from
-$x=-2$ to $x=2$ is held fixed at 8. Therefore, $U=1$ once all the bodies
-have vanished.  Snapshots of the bodies at four equispaced times are
-shown in figure~\ref{fig:Eroding20vort}.  The color is the vorticity,
-whose absolute value is proportional to the erosion rate on solid
-boundaries.  Initially, several of the eroding bodies are closer to the
-outer wall than the $5h$ threshold required for the trapezoid rule to
-achieve machine precision.  In particular, the distance between bodies
-1, 6, 13, and 15 and the outer wall is $1.3h$, $2.9h$, $2.8h$, and
-$1.3h$, respectively, where $h$ is the arclength spacing of the outer
-wall $\Gamma$.  In addition, the distance between several pairs of
-eroding bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18, is too
-small to be accurately resolved with the trapezoid rule.  By using the
-Barycentric quadrature rule, the interaction between these
-nearly-touching bodies is accurately resolved to the desired accuracy,
-and erosion can be simulated until all the bodies have vanished.
+imposed on $\Gamma$. The flow rate $U$ is chosen so that the average
+pressure drop from $x=-2$ to $x=2$ is held fixed at 8. Therefore, $U=1$
+once all the grains have vanished.  The vorticity and grain
+configuration at four equispaced times are shown in
+figure~\ref{fig:Eroding20vort}.  Initially, several of the grains are
+closer to the outer wall than the $5h$ threshold required for the
+trapezoid rule to achieve machine precision.  In particular, the
+distance between bodies 1, 6, 13, and 15 and the outer wall is $1.3h$,
+$2.9h$, $2.8h$, and $1.3h$, respectively, where $h$ is the arclength
+spacing of the outer wall $\Gamma$.  In addition, the distance between
+several pairs of eroding bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and
+14 \& 18, is too small to be accurately resolved with the trapezoid
+rule.  By using the Barycentric quadrature rule, the interaction between
+these nearly-touching bodies is accurately resolved to the desired
+accuracy, and erosion can be simulated until all the bodies have
+vanished.
 
@@
 \begin{center}
-  \includegraphics[height=0.225\textwidth]{./figs/20b_dense1}
-  \includegraphics[height=0.225\textwidth]{./figs/20b_dense101}
-  \includegraphics[height=0.225\textwidth]{./figs/20b_dense201}
-  \includegraphics[height=0.225\textwidth]{./figs/20b_dense301}
+  \includegraphics[height=0.227\textwidth]{./figs/20b_dense1}
+  \includegraphics[height=0.227\textwidth]{./figs/20b_dense101}
+  \includegraphics[height=0.227\textwidth]{./figs/20b_dense201}
+  \includegraphics[height=0.227\textwidth]{./figs/20b_dense301}
 \caption{\label{fig:Eroding20vort} The erosion of 20 nearly touching
-bodies, each discretized with $N_\iin=256$ points, in a Hagen-Poiseuille
-flow.  The four snapshots are evenly spaced in time, and the color is
-the fluid vorticity. In the fourth frame, bodies 4, 12, and 17 have
-vanished completely, and body 19 has almost completely eroded.}
+bodies in a Hagen-Poiseuille flow.  The four snapshots are evenly spaced
+in time, and the color is the fluid vorticity. In the fourth frame,
+bodies 4, 12, and 17 have completely vanished, and body 19 has almost
+completely eroded.}
 \end{center}
@@
 
-Erosion causes the space between nearly touching bodies to quickly
-expand, and flat faces develop along the regions of near contact.  This
-qualitative behavior is seen in figure~\ref{fig:Eroding20vort} between
-bodies 3 \& 4, 15 \& 16, and was also observed in previous
-work~\citep{qua-moo2018}. However, by resolving the interaction between
-bodies that are much closer together than in previous work, we observe
-that very little erosion occurs between certain pairs of bodies, at
-least initially.  For instance the opening between bodies 1 \& 6, 3 \&
-9, and 5 \& 13 grow much slower than the opening between bodies 15 \&
-16.  A common feature of the pores that grow slowly is that they are
-nearly perpendicular to the main flow direction, resulting in a small
-erosion rate.
+Erosion causes the some of the pore sizes to quickly grow, and flat
+faces develop along the regions of near contact.  This qualitative
+behavior is seen in figure~\ref{fig:Eroding20vort} between bodies 3 \&
+4, 15 \& 16, and was also observed in previous work~\citep{qua-moo2018}.
+However, by resolving the interaction between bodies that are much
+closer together, we observe that very little erosion occurs between
+certain pairs of bodies, at least initially.  For instance the opening
+between bodies 1 \& 6, 3 \& 9, and 5 \& 13 grow much slower than the
+opening between bodies 15 \& 16.  A common feature of the pores that
+grow slowly is that they are nearly perpendicular to the main flow
+direction, resulting in a small erosion rate.
 
@@
 \begin{align}
-  \log_{10} U \approx 4.32 \frac{t}{t_f} + c, 
-\end{align}
-where $t_f$ is the time required for all the bodies to erode, and $c$ is
-a fitting parameter. By construction $U = 1$ when $t=t_f$, so $c=-4.32$,
-and the flow rate is approximated as
-\begin{align}
   U \approx \exp\left(9.94 \left(\frac{t - t_f}{t_f} \right)\right),
@@
 geometry from figure~\ref{fig:Eroding20vort}. The streamlines are
-initialized at $x=-1$ and are equally spaced in $y \in (-1,1)$. The
-first five snapshots are evenly spaced in time.  The bottom right frame
-is a zoom in of the fifth snapshot, but with additional streamlines.
-Since we use the Barycentric quadrature rule and a fourth-order
-Runge-Kutta method, some streamlines are very close to the grains
-without penetrating them.}
+initially equispaced at $(-1,y)$, where $y \in (-1,1)$. The first five
+snapshots are evenly spaced in time.  The bottom right frame is a zoom
+in of the fifth snapshot, but with additional streamlines.  Since we use
+the Barycentric quadrature rule and a fourth-order Runge-Kutta method,
+streamlines that are very close to the grains are resolved.}
 \end{center}
@@
 In figure~\ref{fig:Eroding20vort}, we observe that erosion creates a
-network of channels from the inlet to outlet where the velocity and
-vorticity, and therefore erosion rate, are much larger than other
+network of channels from the inlet to the outlet where the velocity and
+vorticity, and therefore erosion rate, are much larger relative to other
 regions.  These channels can be further visualized  with the
@@
 geometry at the second snapshot from figure~\ref{fig:Eroding20vort} and
-plot 200 streamlines that are initialized at $x=-1$ and equally spaced
-in $y \in (-1,1)$.  The streamlines are shown at five different times,
-and the final plot is a zoom in of the lower right quadrant of the fifth
+plot 200 streamlines that are initially equispaced along $(-1,y)$, where
+$y \in (-1,1)$.  The streamlines are shown at five different times, and
+the final plot is a zoom in of the lower right quadrant of the fifth
 time step, but with additional streamlines.  Since we use a high-order
@@
 for the eroded geometry at porosity $\phi = 62.9\%$
-(figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar to the
-work of~\citet[see figure 4(a)]{mat-kha-koz2008}, except that our
+(figure~\ref{fig:Eroding20tort}(c)).  The velocities are similar those
+of~\citet[see figure 4(a)]{mat-kha-koz2008}, except that our
 cross-section, by construction, does not cut through any of the grains.
@@
 We computed lines of best fit using the porosity-tortuosity
-models~\eqref{eqn:tortuosityModels} and found the power law that
+models~\eqref{eqn:tortuosityModels} and found that the power law
 minimizes the error.  The  black dashed line in
@@
 ($\phi=45.08\%$), and $\alpha = 0.56$ ($\phi=37.68\%$).  Values greater
-than 1 are a result of using a least-squares fit for the tails of the
+than 1 result from using a least-squares fit for the tails of the
 particle spreading.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Bryan is here}
 We consider a second example with 20 eroding bodies, but with a smaller
@@
 \caption{\label{fig:ErodingLow20vort} The erosion of 20 nearly touching
-bodies, each discretized with $N_\iin = 256$ points, in a
-Hagen-Poiseuille flow. The four snapshots are evenly spaced in time, and
-the color is the fluid vorticity. In addition to the channels that
-develop between the bodies and the solid walls, erosion leads to two
-main channels through the geometry---one in the top half and one near
-the middle.}
+bodies in a Hagen-Poiseuille flow. The four snapshots are evenly spaced
+in time, and the color is the fluid vorticity. In addition to the
+channels that develop between the bodies and the solid walls, erosion
+leads to two main channels through the geometry---one in the top half
+and one near the middle.}
 \end{figure}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100vort} The erosion of 100 nearly
-touching grains, each discretized with $N_\iin = 256$ points, in a
-Hagen-Poiseuille flow. The color is the vorticity of fluid. The four
-snapshots are evenly spaced in time, and the color is the fluid
-vorticity.  Because of the large number of bodies, erosion creates many
-channels connecting the inlet to the outlet.}
+\caption{\label{fig:Eroding100vort} The erosion of 100 nearly touching
+grains in a Hagen-Poiseuille flow. The four snapshots are evenly spaced
+in time, and the color is the fluid vorticity.  Because of the large
+number of bodies, erosion creates many channels connecting the inlet to
+the outlet.}
 \end{figure}
@@
 
-\todo[inline]{dump of text}
-As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
-immobile eroding grains. However, this work does not limit the proximity
-of  grains. Compared to our previous work, we are able to simulate much
-denser suspensions with a comparable number of discretization points and
-without upsampling.  While we do investigate transport in this work, we
-only consider passive particles that are advected by the flow.  To model
-other physical processes, such as contaminant transport, we plan to
-simulate a finite Peclet number advection-diffusion equation in eroded
-geometries.
-\todo[inline]{dump of text}
+%\todo[inline]{dump of text}
+%As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
+%immobile eroding grains. However, this work does not limit the proximity
+%of  grains. Compared to our previous work, we are able to simulate much
+%denser suspensions with a comparable number of discretization points and
+%without upsampling.  While we do investigate transport in this work, we
+%only consider passive particles that are advected by the flow.  To model
+%other physical processes, such as contaminant transport, we plan to
+%simulate a finite Peclet number advection-diffusion equation in eroded
+%geometries.
+%\todo[inline]{dump of text}
 

### 2019-10-12 docs/transport/erosion_transport.tex
edited whole paper and fixed up bibliography according to JFM formatting

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Bryan is here}
 We consider a second example with 20 eroding bodies, but with a smaller
@@
 points is required to satisfy the $5h$ threshold needed for the
-trapezoid rule to achieve machine precision.  By applying the
-Barycentric quadrature rule, we stably simulate erosion at the much
-coarser resolution of $N_\iin = 256$ and $N_\out = 1024$ discretization
-points.
+trapezoid rule to achieve machine precision.
 
@@
 \begin{center}
-  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort1}
-  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort150}
-  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort300}
-  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort450}
+  \includegraphics[height=0.227\textwidth]{./figs/20b2_vort1}
+  \includegraphics[height=0.227\textwidth]{./figs/20b2_vort150}
+  \includegraphics[height=0.227\textwidth]{./figs/20b2_vort300}
+  \includegraphics[height=0.227\textwidth]{./figs/20b2_vort450}
 \end{center}
@@
 
-To avoid computing streamlines at every time step during the erosion
-process, we compute the tortuosity using the Eulerian
-method~\eqref{eqn:tortuosity2}.  The initial porosity is $30.67\%$ and
-the initial tortuosity is $T = 1.24$.  In
+We compute the tortuosity using the Eulerian
+method~\eqref{eqn:tortuosity2} at each time step. The initial porosity
+is $\phi = 30.67\%$ and the initial tortuosity is $T = 1.24$.  In
 figure~\ref{fig:ErodingLow20Transport}(a), we plot the tortuosity with
@@
 \end{align}
-This model outperformed the other three models in
+This model outperforms the other three models in
 equation~\eqref{eqn:tortuosityModels}, and its root-mean-squared error
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/100b_50}
-\caption{100 bodies, $\phi = 55.54\%$}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/100b_100}
-\caption{99 bodies, $\phi = 62.98\%$}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/100b_150}
-\caption{94 bodies, $\phi = 72.22\%$}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/100b_200}
-\caption{82 bodies, $\phi = 83.67\%$}
-\end{subfigure}
-\caption{\label{fig:Eroding100vort} The erosion of 100 nearly touching
-grains in a Hagen-Poiseuille flow. The four snapshots are evenly spaced
-in time, and the color is the fluid vorticity.  Because of the large
-number of bodies, erosion creates many channels connecting the inlet to
-the outlet.}
-\end{figure}
-
-As a final example, we consider 100 eroding bodies, each with
-$N_\iin=256$ discretization points, with an initial porosity near 50\%.
-Snapshots of the configurations and vorticity are in
-figure~\ref{fig:Eroding100vort}. We compute the tortuosity using both
+As a final example, we consider 100 eroding bodies with an initial
+porosity near 50\%.  Snapshots of the configurations and vorticity are
+in figure~\ref{fig:Eroding100vort}. We compute the tortuosity using both
 the Lagrangian~\eqref{eqn:tortuosity1} and Eulerian
-methods~\eqref{eqn:tortuosity2}. Therefore, we must compute the velocity
-at $N_p = 1000$ points along the inlet $x=-1$. These normalized
-velocities are plotted in figure~\ref{fig:Eroding100tort}(a) for the
+methods~\eqref{eqn:tortuosity2}. Therefore, we compute and plot the
+normalized velocity
+at $N_p = 1000$ points along the inlet $x=-1$ in figure~\ref{fig:Eroding100tort}(a) for the
 eroded geometry at porosity $\phi = 62.98\%$
@@
 tracers is qualitatively similar to the 20 body example
-(figure~\ref{fig:Eroding20tort}(a)), except with additional maximum and
-minimums because of the additional bodies.  Next, in
+(figure~\ref{fig:Eroding20tort}(a)), except with additional oscillations
+because of the additional grains.  In
 figure~\ref{fig:Eroding100tort}(b), we plot the local tortuosity by
@@
 tracers travels 25.5\% farther than it would have if the bodies had been
-absent, and the average tracer travelled 12\% farther indicating a
-tortuosity of $1.12$.
+absent, and the average tracer travelled 12\% farther resulting in a
+tortuosity of $T = 1.12$.
 
 \begin{figure}
-\begin{subfigure}[b]{0.45\textwidth}
-\begin{subfigure}[b]{\textwidth}
-\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-\includegraphics*[width =\linewidth]{./figs/tort_local100}
-\caption{}
-\end{subfigure}
-\end{subfigure}
 \begin{subfigure}[b]{0.5\textwidth}
-\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100tort} The tortuosity of a porous geometry
-that initially had 100 grains and has eroded to a porosity of 62.98\%.
-(a) The $x$-component of the velocity at the inlet, $u_1(-1, y)$,
-normalized by its maximum velocity $u_{max}=3.90 \times 10^{-4}$.  Note
-that this maximum velocity is about a order of magnitude smaller than
-the 20 body example in figure~\ref{fig:Eroding20tort}.  (b) The local
-tortuosity $\tau(y)$ on the cross section $x = -1$. The spatially
-averaged tortuosity through the channel is $1.12$. (c) The trajectories
-of 200 tracers initialized at $x = -1$.  The discontinuities in the
-local tortuosity correspond to nearby streamlines whose lengths are
-significantly different because they pass opposite sides of an eroding
-body. Compared to figure~\ref{fig:Eroding20tort}, this example has more
-small bodies, and this results in many more discontinuities.}
+\includegraphics*[height =0.8\linewidth]{./figs/100b_50}
+\caption{100 bodies, $\phi = 55.54\%$}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height =0.8\linewidth]{./figs/100b_100}
+\caption{99 bodies, $\phi = 62.98\%$}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height =0.8\linewidth]{./figs/100b_150}
+\caption{94 bodies, $\phi = 72.22\%$}
+\end{subfigure}%
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height =0.8\linewidth]{./figs/100b_200}
+\caption{82 bodies, $\phi = 83.67\%$}
+\end{subfigure}
+\caption{\label{fig:Eroding100vort} The erosion of 100 nearly touching
+grains in a Hagen-Poiseuille flow. The four snapshots are evenly spaced
+in time, and the color is the fluid vorticity.  Because of the large
+number of bodies, erosion creates many channels connecting the inlet to
+the outlet.}
 \end{figure}
@@
 straighter streamlines, therefore reducing $\lambda$, the horizontal
-flow, $u_1(y)$ increases since there is no longer a no-slip boundary,
-and this increases the tortuosity.  We also computed the lines of best
+flow, $u_1(y)$, increases since there is no longer a no-slip boundary,
+and this increases the tortuosity.  We also compute the lines of best
 fit using the porosity-tortuosity models~\eqref{eqn:tortuosityModels}.
@@
 \end{align}
+
+\begin{figure}
+\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{\textwidth}
+\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
+\includegraphics*[width =\linewidth]{./figs/tort_local100}
+\caption{}
+\end{subfigure}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100tort} The tortuosity of a porous geometry
+that initially had 100 grains and has eroded to a porosity of 62.98\%.
+(a) The $x$-component of the velocity at the inlet, $u_1(-1, y)$,
+normalized by its maximum velocity $u_{max}=3.90 \times 10^{-4}$.  Note
+that this maximum velocity is about a order of magnitude smaller than
+the 20 body example in figure~\ref{fig:Eroding20tort}.  (b) The local
+tortuosity $\tau(y)$ on the cross section $x = -1$. The spatially
+averaged tortuosity through the channel is $T = 1.12$. (c) The
+trajectories of 200 tracers initialized at $x = -1$.  The
+discontinuities in the local tortuosity correspond to nearby streamlines
+whose lengths are significantly different because they pass opposite
+sides of an eroding body. Compared to figure~\ref{fig:Eroding20tort},
+this example has more small bodies, and this results in many more
+discontinuities.}
+\end{figure}
 
@@
 line), and then super-dispersion.  Similar to the example in
-figure~\ref{fig:ErodingLow20Transport}(b), the anomalous dispersion rate
-is not growing with the porosity.  Therefore, it appears that the
-dispersion rate in an eroding geometry depends not only the porosity,
-but also the location and shape of the bodies.  Finally, at the highest
-porosity, anomalous dispersion is only observed briefly in the time
-interval $(0.5,1)$, and then transitions back to a ballistic regime.
-Since the bodies are so small at this high porosity, after reinsertion,
-the streamline is not significantly deflected by any of the bodies, and
-this results in a ballistic regime.
+figure~\ref{fig:ErodingLow20Transport}(b), the asymptotic anomalous
+dispersion rate is not growing with the porosity.  Therefore, it appears
+that the dispersion rate in an eroding geometry depends not only the
+porosity, but also the location and shape of the bodies.  Finally, at
+the highest porosity, anomalous dispersion is only observed briefly in
+the time interval $(0.5,1)$, and then transitions back to a ballistic
+regime.  Since the bodies are so small at this high porosity, after
+reinsertion, the streamline is not significantly deflected by any of the
+bodies, and this results in a ballistic regime.
 
@@
 line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2459$,
-and the root mean square deviation is $5.50 \times 10^{-3}$.  We note
-that the model $\widehat{T}(\phi) = 1 - p \ln (\phi)$, with $p=0.2631$,
-has a comparable root-mean-square error of $5.20 \times 10^{-3}$.  (b)
-The temporal evolution of $\sigma_\lambda$ as a function of time at six
+and the root-mean-square error is $5.50 \times 10^{-3}$.  We note that
+the model $\widehat{T}(\phi) = 1 - p \ln (\phi)$, with $p=0.2631$, has a
+comparable root-mean-square error of $5.20 \times 10^{-3}$.  (b) The
+temporal evolution of $\sigma_\lambda$ as a function of time at six
 different porosities.  The dashed line, which has slope one, corresponds
@@
 
-Finally, we investigate the effects of erosion on pore sizes.  The
-distribution of the pore sizes can be directly related to the
+Finally, we investigate the effect of erosion on pore sizes.  The
+distribution of the pore sizes is directly related to the
 distribution of the velocity, and thus effects the
@@
 dispersion~\citep{dea-qua-bir-jua2018}. In addition, the pore sizes are
-required in network models~\citep{bry-mel-cad1993, bry-kin-mel1993}.  As
+used in network models~\citep{bry-mel-cad1993, bry-kin-mel1993}.  As
 described in section~\ref{sec:throats}, we use a Delaunay triangulation
@@
 In figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the pore
-pore sizes at six porosities during the erosion process. These types of
-distributions have been described with Weibull
-distributions~\citep{ioa-cha1993}, and we superimpose the Weibull
-distribution with the same first two moments as the data.  The
-parameters of the distribution, $(k,\lambda)$, are included in the
-caption of figure~\ref{fig:Eroding100gap_hist}.  In
+pore sizes at six porosities throughout the erosion process. We
+superimpose the Weibull distribution~\citep{ioa-cha1993} with the same
+first two moments as the data.  The parameters of the distribution,
+$(k,\lambda)$, are included in the caption of
+figure~\ref{fig:Eroding100gap_hist}.  In
 figure~\ref{fig:Eroding100gap_mean_var}, we plot the mean and variance
@@
 $(k,\lambda)=(2.6235,0.1713)$; (f) $\phi = 95.12\%$ and
-$(k,\lambda)=(1.9840, 0.3194)$.}
+$(k,\lambda)=(1.9840,0.3194)$.}
 \end{figure}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap_mean_var} The effect of erosion on the
-mean (a) and the variance (b) of the pore sizes. The geometry initially
+\caption{\label{fig:Eroding100gap_mean_var} The effect of erosion on (a)
+the mean and (b) the variance of the pore sizes. The geometry initially
 contains 100 eroding bodies. The distributions of the pore sizes in
@@
 simulated dense suspensions and characterized transport in viscous
-erosion of porous media. A BIE formulation is used to solve the Stokes
-equations and to compute the shear stress. However, to simulate
-nearly-touching grains and to characterize transport, it is necessary to
-integrate near-singular functions. This is achieved by extending a
-Barycentric quadrature rule~\citep{bar-wu-vee2015} to accurately compute
-the erosion rate and vorticity. By using this quadrature rule, we are
-able to perform stable simulations of erosion with $N = O(100)$
+eroding porous media. This is accomplished by using high-order time
+stepping methods and a new quadrature methods to solve a BIE formulation
+of the Stokes equations.  By using these numerical methods, we are able
+to perform stable simulations of erosion with $N = O(100)$
 discretization points, while the trapezoid rule would require $O(10^5)$
@@
 The transport is characterized in terms of tortuosity and anomalous
-dispersion. The local tortuosity agrees qualitatively with other
-works~\citep{mat-kha-koz2008}. However, the tortuosity of the eroded
-geometries cannot be completely described in terms of the porosity. In
-particular, we observe that for certain porous media, the tortuosity can
-increase when the porosity increases under erosion. We also observe
+dispersion. While the local tortuosity agrees qualitatively with other
+works~\citep{mat-kha-koz2008}, the tortuosity of eroded geometries
+cannot be completely described in terms of the porosity. In particular,
+we observe that for certain porous media, the tortuosity can increase as
+erosion increases the porosity of the porous media. We also observe
 super-dispersive spreading, and the rate of dispersion significantly
@@
 
-As a long term goal, we hope to include the inertial effects and other
+As a long term goal, we plan to include the inertial effects and other
 transport models. Including inertia requires an integral equation
 formulation of the Navier-Stokes equations, which is an active area of
-research with a few promising directions recently
+research with promising directions recently
 proposed~\citep{gray2019boundary, kli-ask-kro2019}.  Regarding other
@@
 
-%\todo[inline]{dump of text}
-%As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
-%immobile eroding grains. However, this work does not limit the proximity
-%of  grains. Compared to our previous work, we are able to simulate much
-%denser suspensions with a comparable number of discretization points and
-%without upsampling.  While we do investigate transport in this work, we
-%only consider passive particles that are advected by the flow.  To model
-%other physical processes, such as contaminant transport, we plan to
-%simulate a finite Peclet number advection-diffusion equation in eroded
-%geometries.
-%\todo[inline]{dump of text}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliographystyle{jfm} 
-%\biboptions{sort&compress}
 \bibliography{refs}

### 2019-10-13 docs/transport/erosion_transport.tex
NM

@@
 
-Flow in porous media is further complicated when boundaries dynamically
-evolve in response to the fluid flow. This coupling between the geometry
-and the flow occurs, for example, in applications involving
+\todo[inline]{The above set of references for ``examples of course-grained models" seems very thorough and perhaps not as relevant as other references on erosion, melting, etc.
+JFMs reference format makes them take up a lot of space.
+So if there are references here that you wouldn't mind dropping, it might help.
+I wouldn't drop all of them.
+I think at least 3-4 are definitely needed.}
+
+Flow in porous media is further complicated when boundaries evolve 
+dynamically in response to the fluid flow. This coupling between geometry
+and flow occurs, for example, in applications involving
 melting~\citep{bec-vis1998, rycroft2016asymmetric, jambon2018singular,
@@
 lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
+
 When a porous medium erodes, certain qualitative characteristics are

### 2019-10-13 docs/transport/erosion_transport.tex
NM

@@
 \todo[inline]{The above set of references for ``examples of course-grained models" seems very thorough and perhaps not as relevant as other references on erosion, melting, etc.
-JFMs reference format makes them take up a lot of space.
+JFM's reference format makes them take up a lot of space.
 So if there are references here that you wouldn't mind dropping, it might help.
@@
 process that is prevalent in many geophysical, hydrological, and
-industrial applications~\citep{berhanu2012shape, hewett2017evolution,
+industrial applications~\citep{ris-moo-chi-she-zha2012, berhanu2012shape, hewett2017evolution,
 lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
@@
 sie-ili-pri-riv-gua2019}, finite differences~\citep{leb-ded-dav-bou2007,
-knu-car2005}, and cellular automata~\citep{rot1988}.  However,
-simulating erosion requires a method that is high-order, can resolve
+knu-car2005}, and cellular automata~\citep{rot1988}.  
+\todo[inline]{The set of references above seems to me like an unneeded `straw-man' argument.
+i.e.~Just because we are using a boundary integral method, does that mean we have to list every other possible way of solving the fluid equations?
+It takes up a fair amount of space.
+On the other hand, if there are references here you want to keep, by all means do it.}
+However, simulating erosion requires a method that is high-order, can resolve
 nearly-touching arbitrarily shaped grains, and can accurately compute
@@
 
-To compute stable simulations of erosion, we use high-order methods in
-both space and time. The time integration method is unchanged from
+To compute stable simulations of erosion, we use 
+\nick{methods of high order in both space and time.}
+The time integration is unchanged from
 previous work~\citep{qua-moo2018}.  We apply a mild regularization and a
@@
 The accuracy of the trapezoid rule, which was used in previous work, is
-adequate for bodies that are sufficiently separated~\citep{tre-wei2014}.
-However, it loses accuracy whenever grains are in close contact.  One of
-the earliest works to address quadrature methods for nearly-singular
+adequate for bodies that are sufficiently separated~\citep{tre-wei2014}, 
+but not for grains in close contact.  
+One of the earliest quadrature methods for nearly-singular
 integrands was developed by~\citet{bak-she1986}, and in recent years,
-many other near-singular integration schemes have
+many other \nick{\st{near-singular integration}} schemes have
 followed~\citep{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
@@
 \end{align}
+\todo[inline]{Could the above equation be changed to inline to save space?}
 where $\uu$ is the fluid velocity.  Since there is no stiff diffusive
 term, we solve~\eqref{eqn:tracers} with a fourth-order explicit
-Runge-Kutta time stepping method.  In addition, the Barycentric
+Runge-Kutta time stepping method. The Barycentric
 quadrature rule is used to accurately compute trajectories that are
@@
 place eroding bodies in $[-1,1] \times [-1,1]$ to create a buffer region
-for the flow profile imposed at the inlet to transition to the more
+that allows the flow profile imposed at the inlet to transition to the more
 complex flow intervening between the bodies. On each eroding body, $\nn$
@@
 The strength of $\UU$ is adjusted at each time step to achieve a
-constant pressure drop across the channel.
+constant pressure drop across the channel, 
+\nick{motivated by the geological situation of a porous medium connecting two regions of  fixed hydraulic heads.}
 
@@
 
+\todo[inline]{The above vertical fraction could be made into a horizontal fraction, which would save a lot of space.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{align}
+
+\todo[inline]{More prime examples of vertical fractions that could be made horizontal.}
 
@@
 
-To compute the tortuosity and the anomalous dispersion rates
-(section~\ref{sec:transport}), we require the streamlines that are
-governed by equation~\eqref{eqn:tracers}.  To characterize the
-transport, it is crucial that the streamlines are computed accurately.
+To examine the tortuosity and the anomalous dispersion rates
+(section~\ref{sec:transport}), we require accurate computation of the streamlines
+governed by equation~\eqref{eqn:tracers}.
+\nick{\st{To characterize the transport, it is crucial that the streamlines are computed accurately.}}
 If a low-order time stepping method is used, or if $\uu(\ss(t))$ is
 inaccurate, then a trajectory $\ss(t)$ can unphysically enter a grain,
-rendering the trajectory meaningless to quantify transport.  However, if
-we simply ignore trajectories that pass close to grains, this would
-significantly skew the characterization of the transport. Therefore, we
-use high-order quadrature and time stepping methods.  In particular,
+rendering the trajectory meaningless. \nick{\st{to quantify transport.}}
+\nick{\st{However, if we simply ignore trajectories that pass close to grains, this would
+significantly skew the characterization of the transport. } 
+However, simply ignoring trajectories that pass close to a grain could significantly bias the characterization of transport.}
+Therefore, we use high-order quadrature and time stepping methods.  In particular,
 depending on the proximity of $\ss(t)$ to $\bd\Omega$
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We now present numerical results of dense packings of bodies eroding in
-Stokes flow. Moreover, we analyze transport through the eroded
-geometries by examining coarse-grained variables.  Each eroding body is
-initially a circle with center $\cc_i$, $r_i$, and length $L_i = 2\upi
-r_i$.  The center and radius are chosen at random, and the body is
+We now present numerical results of dense grain packings eroding in
+Stokes flow and analyze transport through the evolving
+geometries. \nick{\st{by examining coarse-grained variables}}.  
+Each \nick{\st{eroding}} body is
+initialized as a circle of center $\cc_i$, radius $r_i$, and length $L_i = 2\upi r_i$.  
+\todo[inline]{There were too many sequential uses of the word `eroding' above, so I cut two of them out.}
+The center and radius are chosen at random, and the body is
 accepted if it is contained in $[-1,1] \times [-1,1]$ and is
-sufficiently separated from all other bodies.  Since the error of our
-quadrature method is bounded independent of the geometry, we consider
-bodies that are separated by less than 10\% of an arclength spacing.
+sufficiently separated from all other bodies.  
+\awk{Since the error of our quadrature method is bounded independent of the geometry, we consider bodies that are separated by less than 10\% of an arclength spacing.}
+\todo[inline]{The above sentence seemed like a non sequitur to me. See if I got the right idea across in the sentence below.}
+\nick{Owing to our adaptive quadrature rule, we can consider bodies that are separated by less than 10\% of an arclength spacing.}
 The randomized method is repeated until the initial geometry reaches a
@@
 recirculation zone, both in size and magnitude, is present in the region
-where the vorticity is smallest
+where the vorticity is \nick{smallest.}
+\todo[inline]{I was proud of myself for catching the missing period at the end, so had to point it out :)}
 
@@
 vanished.
+\todo[inline]{accurately resolved to the desired accuracy is redundant.}
 
@@
 which is the dashed line in figure~\ref{fig:Eroding20flowrate}(b).
+\todo[inline]{Perhaps equations like the above could be made inline to save space.}
 
@@
 \end{align}
+\todo[inline]{This one definitely seems like a candidate for an inline equation.}
 with a root-mean-square error of $5.90 \times 10^{-3}$.  Interestingly,
@@
 \end{align}
+\todo[inline]{inline?}
 This model outperforms the other three models in
@@
 \end{figure}
+
+\todo[inline]{Very long captions in Figs. 10 and 12 and maybe others.}
 
@@
 \end{align}
+\todo[inline]{More inline candidates}
 
@@
 cannot be completely described in terms of the porosity. In particular,
-we observe that for certain porous media, the tortuosity can increase as
-erosion increases the porosity of the porous media. We also observe
-super-dispersive spreading, and the rate of dispersion significantly
+we observe that for certain \nick{\st{porous media} configurations}, the tortuosity \nick{transiently increases, even though the porosity always increases due to erosion.}
+\nick{\st{as erosion increases the porosity of the porous media.}} 
+We also observe super-dispersive spreading, and the rate of dispersion significantly
 depends not only on the porosity, but also the number of eroding bodies
@@
 statistical properties of an eroding porous media. In this work, we
-provide preliminary results for the pore throat sizes which affect the
+provide \nick{\st{preliminary}} results for the pore throat sizes which affect the
 anomalous dispersion rate~\citep{dea-qua-bir-jua2018}.  At a later date,

### 2019-10-14 docs/transport/erosion_transport.tex
started changes suggested by Nick. Took off two pages.

@@
 Examples of coarse-grained models for porous media flow include
-pressure-saturation-permeability
-relationships~\citep{mil-chr-imh-mcb-ped1998}, permeability-porosity
-relationships~\citep{dar-mcc1998, car1937, won-kop-tom1984}, first
-passage time distributions~\citep{ber-sch-sil2000, hym-den-hag-kan2019,
-cve-che-wen1996}, tortuosities~\citep{hak-com-den2019, mat-kha-koz2008,
-dud-koz-mat2011, kop-kat-tim1996}, concentration
-distributions~\citep{ica-den2019, bel-sal-rin1992}, pore and flow
-distributions~\citep{ali-par-wei-bre2017}, geometry
-connectivity~\citep{knu-car2005, wes-blo-gra2001}, anomalous
-dispersion~\citep{dea-qua-bir-jua2018, den-cor-sch-ber2004,
-sie-ili-pri-riv-gua2019}, and more.
-
-\todo[inline]{The above set of references for ``examples of course-grained models" seems very thorough and perhaps not as relevant as other references on erosion, melting, etc.
-JFM's reference format makes them take up a lot of space.
-So if there are references here that you wouldn't mind dropping, it might help.
-I wouldn't drop all of them.
-I think at least 3-4 are definitely needed.}
+permeability-porosity relationships~\citep{dar-mcc1998, car1937},
+tortuosities~\citep{mat-kha-koz2008, dud-koz-mat2011, kop-kat-tim1996},
+geometry connectivity~\citep{knu-car2005}, anomalous
+dispersion~\citep{den-cor-sch-ber2004}, and more.
 
@@
 the hydrodynamic shear stress~\citep{wan-fel2004,
-ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  We compute the
-vorticity in the fluid bulk since, on solid boundaries, vorticity
-reduces to shear and thus provides a convenient way to simultaneously
-visualize local erosion rates and changes in the surrounding flow
-(figure~\ref{fig:Eroding50vort}).  A variety of numerical methods for
-the fluid solver are available including lattice-gas or lattice
-Boltzmann~\citep{kop-kat-tim1996, dar-mcc1998}, finite
-volumes~\citep{suo-liu-gan2019, den-ica-hid2018,
-sie-ili-pri-riv-gua2019}, finite differences~\citep{leb-ded-dav-bou2007,
-knu-car2005}, and cellular automata~\citep{rot1988}.  
-\todo[inline]{The set of references above seems to me like an unneeded `straw-man' argument.
-i.e.~Just because we are using a boundary integral method, does that mean we have to list every other possible way of solving the fluid equations?
-It takes up a fair amount of space.
-On the other hand, if there are references here you want to keep, by all means do it.}
-However, simulating erosion requires a method that is high-order, can resolve
-nearly-touching arbitrarily shaped grains, and can accurately compute
-derivatives of the velocity field.  Since the governing equations are
-linear and homogeneous, we address these challenges by converting the
-fluid equations to a boundary integral equation (BIE).
+ris-moo-chi-she-zha2012, moore2013self, par-izu2000}.  Since the fluid
+equations are linear and homogeneous, they are converted to a boundary
+integral equation (BIE). Therefore, we resolve the non-negligible
+interactions between nearly-touching arbitrarily shaped bodies, and the
+erosion rate is computed accurately. We also compute the vorticity in
+the fluid bulk since, on solid boundaries, vorticity reduces to shear
+and thus provides a convenient way to simultaneously visualize local
+erosion rates and changes in the surrounding flow
+(figure~\ref{fig:Eroding50vort}).
 
@@
 
-To compute stable simulations of erosion, we use 
-\nick{methods of high order in both space and time.}
-The time integration is unchanged from
-previous work~\citep{qua-moo2018}.  We apply a mild regularization and a
+To compute stable simulations of erosion, we use methods of high-order
+in both space and time. The time integration is unchanged from previous
+work~\citep{qua-moo2018}.  We apply a mild regularization and a
 smoothing term to eliminate numerical instabilities that can be
@@
 adequate for bodies that are sufficiently separated~\citep{tre-wei2014},
-but not for grains in close contact.  
-One of the earliest quadrature methods for nearly-singular
-integrands was developed by~\citet{bak-she1986}, and in recent years,
-many other \nick{\st{near-singular integration}} schemes have
+but not for grains in close contact.  One of the earliest quadrature
+methods for nearly-singular integrands was developed
+by~\citet{bak-she1986}, and in recent years, many other schemes have
 followed~\citep{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
@@
 \end{align}
-\todo[inline]{Could the above equation be changed to inline to save space?}
 where $\uu$ is the fluid velocity.  Since there is no stiff diffusive
 term, we solve~\eqref{eqn:tracers} with a fourth-order explicit
-Runge-Kutta time stepping method. The Barycentric
-quadrature rule is used to accurately compute trajectories that are
-close to an eroding grain. 
-%We note that an alternative approach to
-%compute trajectories is to form a distribution of velocities $\uu$ and
-%use a continuous time random walk~\citep{mon-wei1965,
-%den-cor-sch-ber2004, leb-den-car2008, ber-cor-den-sch2006}.
+Runge-Kutta time stepping method. The Barycentric quadrature rule is
+used to accurately compute trajectories that are close to an eroding
+grain.
 
@@
 The strength of $\UU$ is adjusted at each time step to achieve a
-constant pressure drop across the channel, 
-\nick{motivated by the geological situation of a porous medium connecting two regions of  fixed hydraulic heads.}
+constant pressure drop across the channel, motivated by the geological
+situation of a porous medium connecting two regions of  fixed hydraulic
+heads.
 
@@
 \begin{align}
-  T = \frac{\sum\limits_{i,j=1}^N \|\uu(\xx_{ij})\|\Delta x \Delta y}
-      {\sum\limits_{i,j=1}^N u_1(\xx_{ij}) \Delta x \Delta y}.
-\end{align}
-
-\todo[inline]{The above vertical fraction could be made into a horizontal fraction, which would save a lot of space.}
+  T = \left(\sum_{i,j=1}^N \|\uu(\xx_{ij})\|\Delta x \Delta y \right) 
+      \Bigg/ 
+      \left(\sum_{i,j=1}^N u_1(\xx_{ij}) \Delta x \Delta y \right)
+%  T = \frac{\sum\limits_{i,j=1}^N \|\uu(\xx_{ij})\|\Delta x \Delta y}
+%      {\sum\limits_{i,j=1}^N u_1(\xx_{ij}) \Delta x \Delta y}.
+\end{align}
 
@@
 \begin{align}
-  v(x) = \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
-  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}, \quad x \in \Omega.
+  v(x) = \left(\sum_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j \right)
+  \Bigg/
+  \left(\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
+  \quad x \in \Omega.
+%  v(x) = \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
+%  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}, \quad x \in \Omega.
   \label{eqn:BaryvInterior}
@@
   v(x) = \frac{1}{x-a} 
-    \frac{\sum\limits_{j=1}^N \frac{v^+(y_j)}{y_j - x}w_j}
-    {\sum\limits_{j=1}^N \frac{(y_j - a)^{-1}}{y_j - x}w_j},
+    \left(\sum_{j=1}^N \frac{v^+(y_j)}{y_j - x}w_j \right)
+    \Bigg/
+    \left(\sum_{j=1}^N \frac{(y_j - a)^{-1}}{y_j - x}w_j \right),
     \quad x \in \Omega^c.
+%  v(x) = \frac{1}{x-a} 
+%    \frac{\sum\limits_{j=1}^N \frac{v^+(y_j)}{y_j - x}w_j}
+%    {\sum\limits_{j=1}^N \frac{(y_j - a)^{-1}}{y_j - x}w_j},
+%    \quad x \in \Omega^c.
   \label{eqn:BaryvExterior}
 \end{align}
-
-\todo[inline]{More prime examples of vertical fractions that could be made horizontal.}
 
@@
 \begin{align}
-  v'(x) = \frac{\sum\limits_{j=1}^{N}
-    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
-  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}, 
+  v'(x) = \left(\sum_{j=1}^{N}
+    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
+  \Bigg/
+  \left(\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
   \quad x \in \Omega.
+%  v'(x) = \frac{\sum\limits_{j=1}^{N}
+%    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
+%  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}, 
+%  \quad x \in \Omega.
   \label{eqn:BaryvprimeInterior}
@@
 \begin{align}
-  v'(x) = \frac{1}{x-a} \frac{\sum\limits_{j=1}^N
-    \frac{v^+_j - v(x)}{(y_j - x)^2} w_j}
-    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j - x} w_j},
+  v'(x) = \frac{1}{x-a} \left(\sum_{j=1}^N
+    \frac{v^+_j - v(x)}{(y_j - x)^2} w_j \right)
+    \Bigg/
+    \left(\sum_{j=1}^N \frac{(y_j-a)^{-1}}{y_j - x} w_j\right),
     \quad x \in \Omega^c.
+%  v'(x) = \frac{1}{x-a} \frac{\sum\limits_{j=1}^N
+%    \frac{v^+_j - v(x)}{(y_j - x)^2} w_j}
+%    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j - x} w_j},
+%    \quad x \in \Omega^c.
   \label{eqn:BaryvprimeExterior}
@@
 where the accuracy is independent of $x$.  Solving for $v''(x)$, the
-Barycentric quadrature rule for the interior second derivative is
-\begin{align}
-  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
-    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
-    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, \quad x \in \Omega.
+Barycentric quadrature rule for the interior second derivative at $x \in
+\Omega$ is
+\begin{align}
+  v''(x) \approx \left(2\sum_{j=1}^N 
+    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
+    \Bigg/
+    \left(\sum_{j=1}^N \frac{1}{y_j-x}w_j\right).
+%  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
+%    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
+%    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, \quad x \in \Omega.
 \end{align}
@@
 and solving for $v''(x)$, we have the Barycentric quadrature rule for
-the exterior second derivative
-\begin{align}
-  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
-    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
-    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}, 
-    \quad x \in \Omega^c.
+the exterior second derivative at $x \in \Omega^c$
+\begin{align}
+  v''(x) \approx \frac{1}{x-a}\left(2\sum\limits_{j=1}^N
+    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j\right)
+    \Bigg/
+    \left(\sum_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j\right).
+%  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
+%    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
+%    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}, 
+%    \quad x \in \Omega^c.
 \end{align}
@@
 To examine the tortuosity and the anomalous dispersion rates
-(section~\ref{sec:transport}), we require accurate computation of the streamlines
-governed by equation~\eqref{eqn:tracers}.
-\nick{\st{To characterize the transport, it is crucial that the streamlines are computed accurately.}}
-If a low-order time stepping method is used, or if $\uu(\ss(t))$ is
-inaccurate, then a trajectory $\ss(t)$ can unphysically enter a grain,
-rendering the trajectory meaningless. \nick{\st{to quantify transport.}}
-\nick{\st{However, if we simply ignore trajectories that pass close to grains, this would
-significantly skew the characterization of the transport. } 
-However, simply ignoring trajectories that pass close to a grain could significantly bias the characterization of transport.}
-Therefore, we use high-order quadrature and time stepping methods.  In particular,
-depending on the proximity of $\ss(t)$ to $\bd\Omega$
-(section~\ref{sec:fmm}), we apply the trapezoid rule or the Barycentric
-quadrature rule.  For time stepping, we use a fourth-order explicit
-Runge-Kutta method.  By using these high-order methods, we are able to
-simulate dynamics very close to the eroding bodies (see
+(section~\ref{sec:transport}), we require accurate computation of the
+streamlines governed by equation~\eqref{eqn:tracers}. If a low-order
+time stepping method is used, or if $\uu(\ss(t))$ is inaccurate, then a
+trajectory $\ss(t)$ can unphysically enter a grain, rendering the
+trajectory meaningless. However, simply ignoring trajectories that pass
+close to a grain could significantly bias the characterization of
+transport.  Therefore, we use high-order quadrature and time stepping
+methods.  In particular, depending on the proximity of $\ss(t)$ to
+$\bd\Omega$ (section~\ref{sec:fmm}), we apply the trapezoid rule or the
+Barycentric quadrature rule.  For time stepping, we use a fourth-order
+explicit Runge-Kutta method.  By using these high-order methods, we are
+able to simulate dynamics very close to the eroding bodies (see
 figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}).
@@
 \begin{align}
-  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N_p} 
-    u_1(y_i) \lambda(y_i) \Delta y}
-  {\displaystyle\sum_{i=1}^{N_p} u_1(y_i) \Delta y}, 
+  T = \frac{1}{d}\left(\sum_{i=1}^{N_p} 
+    u_1(y_i) \lambda(y_i) \Delta y \right)
+  \Bigg/
+  \left(\sum_{i=1}^{N_p} u_1(y_i) \Delta y\right), 
+%  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N_p} 
+%    u_1(y_i) \lambda(y_i) \Delta y}
+%  {\displaystyle\sum_{i=1}^{N_p} u_1(y_i) \Delta y}, 
 \end{align}
@@
 We now present numerical results of dense grain packings eroding in
-Stokes flow and analyze transport through the evolving
-geometries. \nick{\st{by examining coarse-grained variables}}.  
-Each \nick{\st{eroding}} body is
-initialized as a circle of center $\cc_i$, radius $r_i$, and length $L_i = 2\upi r_i$.  
-\todo[inline]{There were too many sequential uses of the word `eroding' above, so I cut two of them out.}
-The center and radius are chosen at random, and the body is
-accepted if it is contained in $[-1,1] \times [-1,1]$ and is
-sufficiently separated from all other bodies.  
-\awk{Since the error of our quadrature method is bounded independent of the geometry, we consider bodies that are separated by less than 10\% of an arclength spacing.}
-\todo[inline]{The above sentence seemed like a non sequitur to me. See if I got the right idea across in the sentence below.}
-\nick{Owing to our adaptive quadrature rule, we can consider bodies that are separated by less than 10\% of an arclength spacing.}
-The randomized method is repeated until the initial geometry reaches a
-desired initial porosity.
+Stokes flow and analyze transport through the evolving geometries.  Each
+body is initialized as a circle of center $\cc_i$, radius $r_i$, and
+length $L_i = 2\upi r_i$.  The center and radius are chosen at random,
+and the body is accepted if it is contained in $[-1,1] \times [-1,1]$
+and is sufficiently separated from all other bodies.  Owing to our
+adaptive quadrature rule, we can consider bodies that are separated by
+less than 10\% of an arclength spacing. The randomized method is
+repeated until the initial geometry reaches a desired initial porosity.
 
@@
 recirculation zone, both in size and magnitude, is present in the region
-where the vorticity is \nick{smallest.}
-\todo[inline]{I was proud of myself for catching the missing period at the end, so had to point it out :)}
+where the vorticity is smallest.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider 20 eroding grains with the Hagen-Poiseuille flow
-\begin{align}
-  \UU(\xx)=U \left[
-  \begin{array}{c}
-    1-y^2 \\ 0
-  \end{array}
-  \right],
-\end{align}
+We consider 20 eroding grains with the Hagen-Poiseuille flow $\UU(\xx) =
+U \left(1-y^2,0 \right)$.
+%\begin{align}
+%  \UU(\xx)=U \left[
+%  \begin{array}{c}
+%    1-y^2 \\ 0
+%  \end{array}
+%  \right],
+%\end{align}
 imposed on $\Gamma$. The flow rate $U$ is chosen so that the average
@@
 several pairs of eroding bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and
-14 \& 18, is too small to be accurately resolved with the trapezoid
-rule.  By using the Barycentric quadrature rule, the interaction between
-these nearly-touching bodies is accurately resolved to the desired
-accuracy, and erosion can be simulated until all the bodies have
-vanished.
-\todo[inline]{accurately resolved to the desired accuracy is redundant.}
+14 \& 18, is too small to be resolve with the trapezoid rule.  By using
+the Barycentric quadrature rule, the interaction between these
+nearly-touching bodies is resolved to the desired accuracy, and erosion
+can be simulated until all the bodies have vanished.
 
@@
 that the flow rate can be written as an exponential law.  The line of
-best fit is
-\begin{align}
-  U \approx \exp\left(9.94 \left(\frac{t - t_f}{t_f} \right)\right),
-\end{align}
+best fit is $U \approx \exp(9.94(t-t_f)/t_f)$
+%\begin{align}
+%  U \approx \exp\left(9.94 \left(\frac{t - t_f}{t_f} \right)\right),
+%\end{align}
 which is the dashed line in figure~\ref{fig:Eroding20flowrate}(b).
-\todo[inline]{Perhaps equations like the above could be made inline to save space.}
 
@@
 figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
-\begin{align}
-  \widehat{T}(\phi) = \phi^{-0.2064},
-\end{align}
-\todo[inline]{This one definitely seems like a candidate for an inline equation.}
-with a root-mean-square error of $5.90 \times 10^{-3}$.  Interestingly,
-at the low porosities, the tortuosity initially increases. This increase
-occurs because in the absence of erosion (left plot in
-figure~\ref{fig:Eroding20vort}), many of the streamlines, such as those
-initialized between bodies 15 \& 18, only perform minor deflections to
-pass through the narrow regions, albeit, very slowly.  However, as
-erosion starts to open the channels, the streamlines deflect into the
-fast regions, such as the region above body 11, and this increases the
-amount of vertical deflection, and therefore the tortuosity. While this
-increase in tortuosity is interesting, in the next two examples we will
-see that the tortuosity does not initially increase.
+$\widehat{T}(\phi) = \phi^{-0.2064}$ with a root-mean-square error of
+$5.90 \times 10^{-3}$.  Interestingly, at the low porosities, the
+tortuosity initially increases. This increase occurs because in the
+absence of erosion (left plot in figure~\ref{fig:Eroding20vort}), many
+of the streamlines, such as those initialized between bodies 15 \& 18,
+only perform minor deflections to pass through the narrow regions,
+albeit, very slowly.  However, as erosion starts to open the channels,
+the streamlines deflect into the fast regions, such as the region above
+body 11, and this increases the amount of vertical deflection, and
+therefore the tortuosity. While this increase in tortuosity is
+interesting, in the next two examples we will see that the tortuosity
+does not initially increase.
 
@@
 method~\eqref{eqn:tortuosity1} (red stars).  The red square corresponds
-to the geometry in figure~\ref{fig:Eroding20tort}(c).  The dash line is
-the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2064$, and
-the corresponding root-mean-square error is $5.90 \times 10^{-3}$. (b)
-The temporal evolution of $\sigma_\lambda$ as a function of time at
-seven different porosities.  The dashed line, which has slope one,
-corresponds to ballistic dispersion $\sigma_\lambda \sim t$ that occurs
-if no grains are present. At early times, the particles undergo a
-ballistic motion, but once they have traversed a few grains, the
-spreading becomes super-dispersive with $\sigma_\lambda \sim t^\alpha$,
-$\alpha \in (1/2,1)$.  The dashed-dotted lines are lines of best fit
-with slopes $\alpha = 1.06$ ($\phi=95.10\%$), $\alpha = 1.07$
+to the geometry in figure~\ref{fig:Eroding20tort}(c).  The dashed line
+is the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2064$.
+(b) The temporal evolution of $\sigma_\lambda$ at seven porosities.  The
+dashed line has slope one and corresponds to ballistic dispersion.
+Asymptotically, the spreading is super-dispersive with $\sigma_\lambda
+\sim t^\alpha$, $\alpha \in (1/2,1)$.  The dashed-dotted lines of best
+fit have slopes $\alpha = 1.06$ ($\phi=95.10\%$), $\alpha = 1.07$
 ($\phi=85.09\%$), $\alpha = 1.06$ ($\phi=75.15\%$), $\alpha = 0.97$
@@
 respect to the porosity (blue) and the line of best fit (black) using
-the power law 
-\begin{align}
-  \widehat{T}(\phi) = \phi^{-0.1669}.
-\end{align}
-\todo[inline]{inline?}
-This model outperforms the other three models in
+the power law $\widehat{T}(\phi) = \phi^{-0.1669}$. This model
+outperforms the other three models in
 equation~\eqref{eqn:tortuosityModels}, and its root-mean-squared error
@@
 example, the bodies are initially much closer together, and the porosity
-is smaller.  The tortuosity is calculated with the Eulerian
-method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
-fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.1669$, and the root
-mean square deviation is $1.13 \times 10^{-2}$.  (b) The temporal
-evolution of $\sigma_\lambda$ as a function of time at eight different
-porosities.  The dashed line, which has slope one, corresponds to
-ballistic dispersion $\sigma_\lambda \sim t$ that occurs if no grains
-are present.  At early times, the particles undergo a ballistic motion,
-but once they have traversed a few grains, the spreading becomes
-super-dispersive with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in
-(1/2,1)$.  The dashed-dotted lines are lines of best fit with slope
+is smaller.  The dashed line is the line of best fit
+$\widehat{T}(\phi)=\phi^{-p}$ with $p=0.1669$.  (b) The temporal
+evolution of $\sigma_\lambda$ at eight porosities.  The dashed line has
+slope one and corresponds to ballistic motion. Asymptotically, the
+spreading is super-dispersive with $\sigma_\lambda \sim t^{\alpha}$,
+$\alpha \in (1/2,1)$.  The dashed-dotted lines of best fit have slopes
 $0.92$ ($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$), $0.87$
@@
 \end{figure}
-
-\todo[inline]{Very long captions in Figs. 10 and 12 and maybe others.}
 
@@
 calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
-and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The dash
-line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2459$,
-and the root-mean-square error is $5.50 \times 10^{-3}$.  We note that
-the model $\widehat{T}(\phi) = 1 - p \ln (\phi)$, with $p=0.2631$, has a
-comparable root-mean-square error of $5.20 \times 10^{-3}$.  (b) The
-temporal evolution of $\sigma_\lambda$ as a function of time at six
-different porosities.  The dashed line, which has slope one, corresponds
-to ballistic dispersion $\sigma_\lambda \sim t$ that occurs if no bodies
-are present.  At early times, the particles undergo a ballistic motion,
-but once they have traversed a few grains, the spreading becomes
-super-dispersive with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in
-(1/2,1)$.  The dashed-dotted lines are lines of best fit with slope
-$1.11$ ($\phi=95.12\%$), $0.68$ ($\phi=85.07\%$), $0.73$
-($\phi=75.14\%$), $0.59$ ($\phi=65.03\%$), $0.61$ ($\phi=55.02\%$), and
-$0.70$ ($\phi=50.09\%$).}
+and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The dashed
+line is the line of best fit $\widehat{T}(\phi)=\phi^{-p}$ with
+$p=0.2459$. (b) The temporal evolution of $\sigma_\lambda$ at six
+porosities.  The dashed line has slope one and corresponds to ballistic
+dispersion. Asymptotically, the spreading becomes super-dispersive with
+$\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
+dashed-dotted lines of best fit have slopes $1.11$ ($\phi=95.12\%$),
+$0.68$ ($\phi=85.07\%$), $0.73$ ($\phi=75.14\%$), $0.59$
+($\phi=65.03\%$), $0.61$ ($\phi=55.02\%$), and $0.70$ ($\phi=50.09\%$).}
 \end{figure}
@@
 \end{document}
+
+% OUTDATED STUFF
+%Examples of coarse-grained models for porous media flow include
+%pressure-saturation-permeability
+%relationships~\citep{mil-chr-imh-mcb-ped1998}, permeability-porosity
+%relationships~\citep{dar-mcc1998, car1937, won-kop-tom1984}, first
+%passage time distributions~\citep{ber-sch-sil2000, hym-den-hag-kan2019,
+%cve-che-wen1996}, tortuosities~\citep{hak-com-den2019, mat-kha-koz2008,
+%dud-koz-mat2011, kop-kat-tim1996}, concentration
+%distributions~\citep{ica-den2019, bel-sal-rin1992}, pore and flow
+%distributions~\citep{ali-par-wei-bre2017}, geometry
+%connectivity~\citep{knu-car2005, wes-blo-gra2001}, anomalous
+%dispersion~\citep{dea-qua-bir-jua2018, den-cor-sch-ber2004,
+%sie-ili-pri-riv-gua2019}, and more.
+
+%A variety of numerical methods for the fluid solver are available
+%including lattice-gas or lattice Boltzmann~\citep{kop-kat-tim1996,
+%dar-mcc1998}, finite volumes~\citep{suo-liu-gan2019, den-ica-hid2018,
+%sie-ili-pri-riv-gua2019}, finite
+%differences~\citep{leb-ded-dav-bou2007, knu-car2005}, and cellular
+%automata~\citep{rot1988}.
+
+%We note that an alternative approach to
+%compute trajectories is to form a distribution of velocities $\uu$ and
+%use a continuous time random walk~\citep{mon-wei1965,
+%den-cor-sch-ber2004, leb-den-car2008, ber-cor-den-sch2006}.

### 2019-10-15 docs/transport/erosion_transport.tex
working on formatting and simplifying

@@
 to trajectories in eroded geometries with large permeability.  The
-trajectory originating at $(s_1(0),s_2(0))$ is
-\begin{align}
-  s_1(t) = (1-s_2(0)^2)t + s_1(0), \quad
-  s_2(t) = s_2(0).
-\end{align}
+trajectories are $(s_1(t),s_2(t)) = ((1-s_2(0)^2)t + s_1(0), s_2(0))$.
+%\begin{align}
+%  s_1(t) = (1-s_2(0)^2)t + s_1(0), \quad
+%  s_2(t) = s_2(0).
+%\end{align}
 Averaging over $s_2(0) \in [-1,1]$, the first and second ensemble
@@
 \begin{align}
-  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_1(x_0,y_0)\lambda(y_0)\,dy_0}
-  {\displaystyle\int_{S}u_1(x_0,y_0)\,dy_0},
+  T = \frac{1}{d}\left(\int_{S}u_1(x_0,y_0)\lambda(y_0)\,dy_0 \right)
+  \Bigg/
+  \left(\int_{S}u_1(x_0,y_0)\,dy_0 \right),
+%  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_1(x_0,y_0)\lambda(y_0)\,dy_0}
+%  {\displaystyle\int_{S}u_1(x_0,y_0)\,dy_0},
   \label{eqn:tortuosity1}
@@
 \begin{align}
-  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
-           {\displaystyle\int_\Omega u_1(\yy)\, d\yy},
+  T = \left(\int_\Omega \|\uu(\yy)\|\, d\yy \right)
+    \Bigg/
+      \left(\int_\Omega u_1(\yy)\, d\yy \right),
+%  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
+%           {\displaystyle\int_\Omega u_1(\yy)\, d\yy},
   \label{eqn:tortuosity2}
@@
 \caption{\label{fig:Eroding100gap} (a) The pore sizes between
-neighboring grains. Two grains are said to be neighbors if they share an
-edge of a Delanuay triangulation with nodes at the center of each
-eroding grain. (b) The distribution of the pore sizes of an eroded
-geometry. The black curve is the Weibull distribution with the same
-first two moments as the data.}
+neighboring grains. Two grains are neighbors if they share an edge of
+the Delanuay triangulation with nodes at the center of each eroding
+grain. (b) The pore sizes of an eroded geometry. The black curve is the
+Weibull distribution with the same first two moments as the data.}
 \end{figure}
@@
 Consider a single eroding body close to a solid wall with the shear flow
-\begin{align}
-  \UU(\xx)=\left[
-  \begin{array}{c}
-    y+1 \\ 0
-  \end{array}
-  \right],
-\end{align}
-imposed on the outer wall. \citet{mit-spa2017} performed a similar
+$\UU(\xx) = (y+1,0)$
+%\begin{align}
+%  \UU(\xx)=\left[
+%  \begin{array}{c}
+%    y+1 \\ 0
+%  \end{array}
+%  \right],
+%\end{align}
+imposed on $\Gamma$. \citet{mit-spa2017} performed a similar
 three-dimensional experiment using a second-order quadrature method.
@@
 We consider 20 eroding grains with the Hagen-Poiseuille flow $\UU(\xx) =
-U \left(1-y^2,0 \right)$.
+U \left(1-y^2,0 \right)$
 %\begin{align}
@@
   \includegraphics[height=0.227\textwidth]{./figs/20b_dense301}
-\caption{\label{fig:Eroding20vort} The erosion of 20 nearly touching
-bodies in a Hagen-Poiseuille flow.  The four snapshots are evenly spaced
-in time, and the color is the fluid vorticity. In the fourth frame,
-bodies 4, 12, and 17 have completely vanished, and body 19 has almost
-completely eroded.}
+\caption{\label{fig:Eroding20vort} 20 bodies eroding in a
+Hagen-Poiseuille flow.  The four snapshots are equispaced in time, and
+the color is the fluid vorticity. In the fourth frame, bodies 4, 12, and
+17 have vanished, and body 19 has almost vanished.}
 \end{center}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20
-nearly touching eroding bodies versus normalized time. (b) The flow
-rate, $U$, for a fixed pressure drop across the channel versus
-normalized time.  The flow rate is initially very small, but it
-eventually increases as an exponential law  (dashed line) towards the
-flow rate $U=1$ that occurs once all the bodies have eroded.}
+\caption{\label{fig:Eroding20flowrate}(a) The time-dependent area
+fraction of a geometry with 20 eroding bodies. (b) The time-dependent
+flow rate, $U$, for a fixed pressure drop across the channel.  The flow
+rate is initially small, but it eventually increases as an exponential
+law (dashed line) towards the maximum flow rate $U=1$.}
 \end{figure}
@@
 initially equispaced at $(-1,y)$, where $y \in (-1,1)$. The first five
-snapshots are evenly spaced in time.  The bottom right frame is a zoom
-in of the fifth snapshot, but with additional streamlines.  Since we use
-the Barycentric quadrature rule and a fourth-order Runge-Kutta method,
-streamlines that are very close to the grains are resolved.}
+snapshots are equispaced in time.  The bottom right frame is a
+magnification of the fifth snapshot, but with additional streamlines.}
 \end{center}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding20tort} The tortuosity of a porous geometry
-that initially had 20 grains and has eroded to a porosity of 62.9\%.
-(a) The $x$-component of the velocity at the inlet, $u_1(-1,y)$,
-normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
-local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
-averaged tortuosity through the channel is $1.098$.  (c) The streamlines
-resulting in the ten largest differences of local tortuosity between
-neighboring streamlines.  Neighboring streamlines have the same color.}
+\caption{\label{fig:Eroding20tort} The local tortuosity of a porous
+geometry initialized with 20 grains after eroding to a porosity of
+62.9\%.  (a) The $x$-component of the velocity at the inlet,
+$u_1(-1,y)$, normalized by its maximum velocity of $2.98 \times
+10^{-3}$. (b) The local tortuosity $\tau(y)$ on the cross section $x =
+-1$. (c) The streamlines resulting in the ten largest differences of
+local tortuosity between neighboring streamlines.  Neighboring
+streamlines have the same color.}
 \end{figure}
@@
 \end{center}
-\caption{\label{fig:ErodingLow20vort} The erosion of 20 nearly touching
-bodies in a Hagen-Poiseuille flow. The four snapshots are evenly spaced
-in time, and the color is the fluid vorticity. In addition to the
-channels that develop between the bodies and the solid walls, erosion
-leads to two main channels through the geometry---one in the top half
-and one near the middle.}
+\caption{\label{fig:ErodingLow20vort} 20 bodies eroding in a
+Hagen-Poiseuille flow. The snapshots are equispaced in time, and the
+color is the fluid vorticity. In addition to the channels that develop
+between the bodies and the solid walls, erosion leads to two main
+channels through the geometry---one in the top half and one near the
+middle.}
 \end{figure}
@@
 methods~\eqref{eqn:tortuosity2}. Therefore, we compute and plot the
-normalized velocity
-at $N_p = 1000$ points along the inlet $x=-1$ in figure~\ref{fig:Eroding100tort}(a) for the
-eroded geometry at porosity $\phi = 62.98\%$
-(figure~\ref{fig:Eroding100tort}(c)).  The initial velocity of the
-tracers is qualitatively similar to the 20 body example
+normalized velocity at $N_p = 1000$ points along the inlet $x=-1$ in
+figure~\ref{fig:Eroding100tort}(a) for the eroded geometry at porosity
+$\phi = 62.98\%$ (figure~\ref{fig:Eroding100tort}(c)).  The initial
+velocity of the tracers is qualitatively similar to the 20 body example
 (figure~\ref{fig:Eroding20tort}(a)), except with additional oscillations
@@
 \begin{figure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/100b_50}
-\caption{100 bodies, $\phi = 55.54\%$}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/100b_100}
-\caption{99 bodies, $\phi = 62.98\%$}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/100b_150}
-\caption{94 bodies, $\phi = 72.22\%$}
-\end{subfigure}%
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/100b_200}
-\caption{82 bodies, $\phi = 83.67\%$}
-\end{subfigure}
-\caption{\label{fig:Eroding100vort} The erosion of 100 nearly touching
-grains in a Hagen-Poiseuille flow. The four snapshots are evenly spaced
-in time, and the color is the fluid vorticity.  Because of the large
-number of bodies, erosion creates many channels connecting the inlet to
-the outlet.}
+\begin{center}
+  \includegraphics[height=0.227\textwidth]{./figs/100b_50}
+  \includegraphics[height=0.227\textwidth, trim=0cm 0cm 2.8cm 0cm, clip=true]
+    {./figs/100b_100}
+  \includegraphics[height=0.227\textwidth]{./figs/100b_150}
+  \includegraphics[height=0.227\textwidth]{./figs/100b_200}
+\end{center}
+\caption{\label{fig:Eroding100vort} 100 bodies eroding in a
+Hagen-Poiseuille flow. The four snapshots are equispaced in time, and
+the color is the fluid vorticity.  Erosion creates many channels
+connecting the inlet to the outlet.}
 \end{figure}
+
+%\begin{figure}
+%\begin{subfigure}[b]{0.5\textwidth}
+%\includegraphics*[height =0.8\linewidth]{./figs/100b_50}
+%\caption{100 bodies, $\phi = 55.54\%$}
+%\end{subfigure}%
+%\begin{subfigure}[b]{0.5\textwidth}
+%\includegraphics*[height =0.8\linewidth]{./figs/100b_100}
+%\caption{99 bodies, $\phi = 62.98\%$}
+%\end{subfigure}
+%\begin{subfigure}[b]{0.5\textwidth}
+%\includegraphics*[height =0.8\linewidth]{./figs/100b_150}
+%\caption{94 bodies, $\phi = 72.22\%$}
+%\end{subfigure}%
+%\begin{subfigure}[b]{0.5\textwidth}
+%\includegraphics*[height =0.8\linewidth]{./figs/100b_200}
+%\caption{82 bodies, $\phi = 83.67\%$}
+%\end{subfigure}
+%\caption{\label{fig:Eroding100vort} 100 bodies eroding in a
+%Hagen-Poiseuille flow. The four snapshots are equispaced in time, and
+%the color is the fluid vorticity.  Erosion creates many channels
+%connecting the inlet to the outlet.}
+%\end{figure}
 
@@
 \end{align}
-\todo[inline]{More inline candidates}
 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100tort} The tortuosity of a porous geometry
-that initially had 100 grains and has eroded to a porosity of 62.98\%.
-(a) The $x$-component of the velocity at the inlet, $u_1(-1, y)$,
-normalized by its maximum velocity $u_{max}=3.90 \times 10^{-4}$.  Note
-that this maximum velocity is about a order of magnitude smaller than
-the 20 body example in figure~\ref{fig:Eroding20tort}.  (b) The local
-tortuosity $\tau(y)$ on the cross section $x = -1$. The spatially
-averaged tortuosity through the channel is $T = 1.12$. (c) The
-trajectories of 200 tracers initialized at $x = -1$.  The
-discontinuities in the local tortuosity correspond to nearby streamlines
-whose lengths are significantly different because they pass opposite
-sides of an eroding body. Compared to figure~\ref{fig:Eroding20tort},
-this example has more small bodies, and this results in many more
-discontinuities.}
+
+\caption{\label{fig:Eroding20tort} The local tortuosity of a porous
+geometry initialized with 20 grains after eroding to a porosity of
+62.9\%.  (a) The $x$-component of the velocity at the inlet,
+$u_1(-1,y)$, normalized by its maximum velocity of $2.98 \times
+10^{-3}$. (b) The local tortuosity $\tau(y)$ on the cross section $x =
+-1$. (c) The streamlines resulting in the ten largest differences of
+local tortuosity between neighboring streamlines.  Neighboring
+streamlines have the same color.}
+
+\caption{\label{fig:Eroding100tort} The local tortuosity of a porous
+geometry initialized with 100 grains after eroding to a porosity of
+62.98\%.  (a) The $x$-component of the velocity at the inlet, $u_1(-1,
+y)$, normalized by its maximum velocity $u_{max}=3.90 \times 10^{-4}$.
+Note that this maximum velocity is about a order of magnitude smaller
+than the 20 body example in figure~\ref{fig:Eroding20tort}.  (b) The
+local tortuosity $\tau(y)$ on the cross section $x = -1$. Compared to
+figure~\ref{fig:Eroding20tort}, this example has more small bodies, and
+this results in more discontinuities in the local tortuosity.  (c) The
+trajectories of 200 tracers initialized at $x = -1$.}
 \end{figure}
@@
 Finally, we investigate the effect of erosion on pore sizes.  The
-distribution of the pore sizes is directly related to the
-distribution of the velocity, and thus effects the
-tortuosity~\citep{den-ica-hid2018} and anomalous
-dispersion~\citep{dea-qua-bir-jua2018}. In addition, the pore sizes are
-used in network models~\citep{bry-mel-cad1993, bry-kin-mel1993}.  As
-described in section~\ref{sec:throats}, we use a Delaunay triangulation
-to define neighboring eroding bodies, and we compute the pore size by
-finding the closest distance between all neighboring bodies.  Instead of
-computing a Delanuay configuration at each time step, which would result
-in new definitions for the pores at each time step, we only compute a
-new Delaunay triangulation when a grain completely erodes.  Once all
-pore sizes are computed, we analyze their distribution as a function of
-the porosity.
+distribution of the pore sizes is directly related to the distribution
+of the velocity, and thus effects the tortuosity~\citep{den-ica-hid2018}
+and anomalous dispersion~\citep{dea-qua-bir-jua2018}. In addition, the
+pore sizes are used in network models~\citep{bry-mel-cad1993,
+bry-kin-mel1993}.  As described in section~\ref{sec:throats}, we use a
+Delaunay triangulation to define neighboring eroding bodies, and we
+compute the pore size by finding the closest distance between all
+neighboring bodies.  Instead of computing the Delanuay configuration at
+each time step, which would result in new definitions for the pores at
+each time step, we only compute a new Delaunay triangulation when a
+grain completely erodes.  Once all pore sizes are computed, we analyze
+their distribution as a function of the porosity.
 
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap_hist} The distribution of the pore
-sizes of 100 eroding bodies at six porosities. The black curves are
-Weibull distributions whose first and second moments agree with the
-data. The porosities and Weibull distribution parameters $(k,\lambda)$
-at each of the porosities are: (a) $\phi = 50.09\%$ and
-$(k,\lambda)=(1.4650,0.0605)$; (b) $\phi = 55.02\%$ and
-$(k,\lambda)=(1.9485,0.0737)$; (c) $\phi = 65.03\%$ and
+\caption{\label{fig:Eroding100gap_hist} The pore sizes of 100 eroding
+bodies at six porosities. The black curves are Weibull distributions
+whose first and second moments agree with the data. The porosities and
+Weibull distribution parameters $(k,\lambda)$ at each of the porosities
+are: (a) $\phi = 50.09\%$ and $(k,\lambda)=(1.4650,0.0605)$; (b) $\phi =
+55.02\%$ and $(k,\lambda)=(1.9485,0.0737)$; (c) $\phi = 65.03\%$ and
 $(k,\lambda)=(2.5682,0.0965)$; (d) $\phi = 75.14\%$ and
@@
 cannot be completely described in terms of the porosity. In particular,
-we observe that for certain \nick{\st{porous media} configurations}, the tortuosity \nick{transiently increases, even though the porosity always increases due to erosion.}
-\nick{\st{as erosion increases the porosity of the porous media.}} 
-We also observe super-dispersive spreading, and the rate of dispersion significantly
-depends not only on the porosity, but also the number of eroding bodies
-and their distribution.
+we observe that for certain configurations, the tortuosity transiently
+increases, even though the porosity always increases due to erosion. We
+also observe super-dispersive spreading, and the rate of dispersion
+significantly depends not only on the porosity, but also the number of
+eroding bodies and their distribution.
 
@@
 statistical properties of an eroding porous media. In this work, we
-provide \nick{\st{preliminary}} results for the pore throat sizes which affect the
-anomalous dispersion rate~\citep{dea-qua-bir-jua2018}.  At a later date,
-we will report results on the  development of anisotropic effects and
-the distributions of grain sizes, shapes, and opening angles.
+provide results for the pore throat sizes which affect the anomalous
+dispersion rate~\citep{dea-qua-bir-jua2018}.  At a later date, we will
+report results on the  development of anisotropic effects and the
+distributions of grain sizes, shapes, and opening angles.
 

### 2019-10-15 docs/transport/erosion_transport.tex
continued to condense

@@
 Flow in porous media is further complicated when boundaries evolve 
-dynamically in response to the fluid flow. This coupling between geometry
-and flow occurs, for example, in applications involving
+dynamically in response to the fluid flow. This coupling between
+geometry and flow occurs, for example, in applications involving
 melting~\citep{bec-vis1998, rycroft2016asymmetric, jambon2018singular,
@@
 process that is prevalent in many geophysical, hydrological, and
-industrial applications~\citep{ris-moo-chi-she-zha2012, berhanu2012shape, hewett2017evolution,
-lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
+industrial applications~\citep{ris-moo-chi-she-zha2012,
+berhanu2012shape, hewett2017evolution, lachaussee2018competitive,
+lopez2018cfd, allen2019sde, amin2019role}.
 
@@
 \includegraphics[height = 0.3 \textwidth]{./figs/vel_log_50b400}
-\caption{\label{fig:Eroding50vel} Six evenly spaced snapshots of 50
-eroding bodies.  The background velocity is a Hagen-Poiseuille flow with
-a varying flow strength that corresponds to a constant pressure drop
-across the channel. The color is the magnitude of the velocity in a
-logarithmic scale. The flow velocity varies over several orders of
-magnitude, the grains form irregular shapes with large aspect ratios,
-and the geometry becomes channelized and anisotropic.}
+\caption{\label{fig:Eroding50vel} 50 bodies eroding in a
+Hagen-Poiseuille flow.  The six snapshots are equispaced in time, and
+the color is the magnitude of the fluid velocity in a logarithmic scale.
+The flow velocity varies over several orders of magnitude, the grains
+form irregular shapes with large aspect ratios, and the geometry becomes
+channelized and anisotropic.}
 \end{center}
@@
 $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  The double-layer potential is a
-solution of the incompressible Stokes equations, but it cannot represent
-all the solutions. Therefore, we complete the integral equation
-formulation by adding the $M$ Stokeslets and rotlets~\citep{pow-mir1987}
-\begin{align}
-  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\upi} \left( 
-    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2}
-    \right)\llambda_\ell, \quad
-  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
-  \quad \ell=1,\ldots,M,
-\end{align}
-where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
-$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
-\|\rr\|$. Here, $\llambda_\ell$ and $\xi_\ell$ are the Stokeslet and
-rotlet strengths, respectively, corresponding to the $\ell^{th}$ body.
-Then, for any sufficiently smooth geometry $\Omega$, the solution of the
-incompressible Stokes equation with a Dirichlet boundary condition $\ff$
-is
+is an unknown density function.  We complete the integral equation
+formulation by adding the $M$ Stokeslets,
+$S[\llambda_\ell,\cc_\ell](\xx)$, and rotlets,
+$R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
+$\ell^{th}$ body~\citep{pow-mir1987}.  Here $\llambda_\ell$ and
+$\xi_\ell$ are the Stokeslet and rotlet strengths, respectively,
+corresponding to the $\ell^{th}$ body.  Then, for any sufficiently
+smooth geometry $\Omega$, the solution of the incompressible Stokes
+equation with a Dirichlet boundary condition $\ff$ is
 \begin{align}
@@
 Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
-Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, we are able to
-compute, for $\xx \in \Omega$, the deformation tensor, pressure, and
-vorticity, defined respectively as
-\begin{align}
-  \label{eqn:deformationDLP} 
-  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
-      \eeta(\yy) ds_{\yy} 
-  = \frac{1}{2\upi}\int_{\bd\Omega} \left(
-    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
-    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
-    \right. \nonumber \\
-    & \qquad\qquad\qquad\qquad \left.
-    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
-    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-    \right) \, ds_\yy, \\
-%
-  \label{eqn:pressureDLP}
-  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
-      \eeta(\yy) ds_{\yy} 
-  = -\frac{1}{\upi}\int_{\bd\Omega} \frac{1}{\rho^2}
-    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
-      \eeta(\yy)\,ds_\yy, \\
-%
-  \label{eqn:vorticityDLP} 
-  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
-      \eeta(\yy) ds_{\yy} 
-  = -\frac{1}{\upi} \int_{\bd\Omega}
-    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
-      (\rr \cdot \eeta) \, ds_\yy.
-\end{align}
-Since the deformation tensor of the double-layer potential is
-discontinuous across $\bd\Omega$, the jump term 
+corresponding deformation tensor, pressure, and vorticity at $\xx \in
+\Omega$ is written in terms of a layer potential~\cite{qua-moo2018}. To
+compute the deformation tensor for $\xx \in \gamma$, we include the jump
+term
 \begin{align}
@@
     \end{array}
-  \right],
+  \right].
   \label{eqn:deformationJump}
 \end{align}
-must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
-Stokeslets and rotlets do not exhibit any jumps across $\gamma$, so the
-associated components of the deformation tensor, pressure, and vorticity
-are straightforward to compute~\citep{poz1992}.  Having computed the
-deformation tensor on $\gamma$, the shear stress is computed using
-equation~\eqref{eqn:shearStress}.
+Finally, the deformation tensor, pressure, and vorticity due to the
+Stokeslets and rotlets are readily available~\citep{poz1992}. Having
+computed the deformation tensor on $\gamma$, the shear stress is
+computed using equation~\eqref{eqn:shearStress}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In
-equations~\eqref{eqn:velocityDLP},~\eqref{eqn:deformationDLP},~\eqref{eqn:pressureDLP},
-and~\eqref{eqn:vorticityDLP}, the fluid velocity, deformation tensor,
-pressure, and vorticity are all written as layer potentials in $\RR^2$.
-However, the quadrature method we introduce in section~\ref{sec:method}
-requires a complex-valued representation of the layer potentials for the
-velocity, deformation tensor, and vorticity. The first step to form a
-complex representation is to write the Laplace double-layer potential as
-the complex integral
+The velocity double-layer potential~\eqref{eqn:velocityDLP}, and its
+corresponding deformation tensor, pressure, and vorticity are all
+written as layer potentials in $\RR^2$.  However, the quadrature method
+we introduce in section~\ref{sec:method} requires a complex-valued
+representation of the layer potentials for the velocity, deformation
+tensor, and vorticity. The first step to form a complex representation
+is to write the Laplace double-layer potential as the complex integral
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap} (a) The pore sizes between
+neighboring grains. Two grains are neighbors if they share an edge of
+the Delanuay triangulation with nodes at the center of each eroding
+grain. (b) The pore sizes of an eroded geometry. The black curve is the
+Weibull distribution with the same first two moments as the data.}
+\end{figure}
 While transport in porous media depends on the porosity, it also depends
@@
 investigate the effect of erosion on the pore size distribution.
-\begin{figure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap} (a) The pore sizes between
-neighboring grains. Two grains are neighbors if they share an edge of
-the Delanuay triangulation with nodes at the center of each eroding
-grain. (b) The pore sizes of an eroded geometry. The black curve is the
-Weibull distribution with the same first two moments as the data.}
-\end{figure}
 
@@
 deformation tensor, and vorticity due to the double-layer potential is
-found by applying the trapezoid rule to \eqref{eqn:velocityDLP},
-\eqref{eqn:deformationDLP}, and~\eqref{eqn:vorticityDLP}, respectively.
-In particular,
+found by applying the trapezoid rule. In particular,
 \begin{align}
@@
 pressure near the inlet and outlet at each time step, and then scaling
-the flow rate appropriately~\citep{qua-moo2018}.
+the flow rate appropriately~\citep{qua-moo2018}. We also compute the
+vorticity in the fluid bulk to help visualize the erosion rate.
 
@@
 10^{-4}$.
-
-In each of the examples, we plot the vorticity in the fluid bulk.  Since
-the vorticity and the shear stress agree on the boundary of the eroding
-grains, the vorticity is useful to visualize the erosion rate.  In
-particular, the rate of erosion is largest in regions where the
-magnitude of the vorticity is largest.
 
@@
 The black dashed line in figure~\ref{fig:Eroding100Transport}(a) is the
-line of best fit
-\begin{align}
-  \widehat{T}(\phi) = \phi^{-0.2459},
-\end{align}
-with a root-mean-square error of $5.50 \times 10^{-3}$.  We note a
-slightly better root-mean-square error of $5.20 \times 10^{-3}$ is
-possible with the model
-\begin{align}
-  \widehat{T}(\phi) = 1 - 0.2631 \ln(\phi).
-\end{align}
+line of best fit $\widehat{T}(\phi) = \phi^{-0.2459}$, with a
+root-mean-square error of $5.50 \times 10^{-3}$.  We note a slightly
+better root-mean-square error of $5.20 \times 10^{-3}$ is possible with
+the model $\widehat{T}(\phi) = 1 - 0.2631 \ln(\phi)$.
 
@@
 %den-cor-sch-ber2004, leb-den-car2008, ber-cor-den-sch2006}.
+
+%we are able to compute, for $\xx \in \Omega$, the deformation tensor,
+%pressure, and vorticity.
+%defined respectively as
+%\begin{align}
+%  \label{eqn:deformationDLP} 
+%  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
+%      \eeta(\yy) ds_{\yy} 
+%  = \frac{1}{2\upi}\int_{\bd\Omega} \left(
+%    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
+%    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
+%    \right. \nonumber \\
+%    & \qquad\qquad\qquad\qquad \left.
+%    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
+%    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
+%    \right) \, ds_\yy, \\
+%%
+%  \label{eqn:pressureDLP}
+%  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
+%      \eeta(\yy) ds_{\yy} 
+%  = -\frac{1}{\upi}\int_{\bd\Omega} \frac{1}{\rho^2}
+%    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
+%      \eeta(\yy)\,ds_\yy, \\
+%%
+%  \label{eqn:vorticityDLP} 
+%  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
+%      \eeta(\yy) ds_{\yy} 
+%  = -\frac{1}{\upi} \int_{\bd\Omega}
+%    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
+%      (\rr \cdot \eeta) \, ds_\yy.
+%\end{align}
+%Since the deformation tensor of the double-layer potential is
+%discontinuous across $\bd\Omega$, the jump term 
+%added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
+%Stokeslets and rotlets do not exhibit any jumps across $\gamma$, so the
+%associated components of the deformation tensor, pressure, and vorticity
+%are straightforward to compute~\citep{poz1992}.  Having computed the
+%deformation tensor on $\gamma$, the shear stress is computed using
+%equation~\eqref{eqn:shearStress}.
+
+%\begin{align}
+%  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\upi} \left( 
+%    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2}
+%    \right)\llambda_\ell, \quad
+%  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
+%  \quad \ell=1,\ldots,M,
+%\end{align}
+%where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
+%$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
+%\|\rr\|$.

### 2019-10-15 docs/transport/erosion_transport.tex
modify figs in transport paper

@@
 \begin{figure}
-\begin{center}
-  \includegraphics[height=0.227\textwidth]{./figs/100b_50}
-  \includegraphics[height=0.227\textwidth, trim=0cm 0cm 2.8cm 0cm, clip=true]
-    {./figs/100b_100}
-  \includegraphics[height=0.227\textwidth]{./figs/100b_150}
-  \includegraphics[height=0.227\textwidth]{./figs/100b_200}
-\end{center}
-\caption{\label{fig:Eroding100vort} 100 bodies eroding in a
-Hagen-Poiseuille flow. The four snapshots are equispaced in time, and
-the color is the fluid vorticity.  Erosion creates many channels
-connecting the inlet to the outlet.}
+%<<<<<<< HEAD
+%\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[height =0.227\linewidth]{./figs/100b_50}
+%\caption{100 bodies, $\phi = 55.54\%$}
+%\end{subfigure}%
+%\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[height =0.227\linewidth]{./figs/100b_100}
+%\caption{99 bodies, $\phi = 62.98\%$}
+%\end{subfigure}
+%\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[height =0.227\linewidth]{./figs/100b_150}
+%\caption{94 bodies, $\phi = 72.22\%$}
+%\end{subfigure}%
+%\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[height =0.227\linewidth]{./figs/100b_200}
+%\caption{82 bodies, $\phi = 83.67\%$}
+%\end{subfigure}
+\caption{\label{fig:Eroding100vort} The erosion of 100 nearly touching
+grains in a Hagen-Poiseuille flow. The four snapshots are evenly spaced
+in time, and the color is the fluid vorticity.  Because of the large
+number of bodies, erosion creates many channels connecting the inlet to
+the outlet.}
+%=======
+%\begin{center}
+ % \includegraphics[height=0.227\textwidth]{./figs/100b_50}
+  %\includegraphics[height=0.227\textwidth, trim=0cm 0cm 2.8cm 0cm, clip=true]
+ %   {./figs/100b_100}
+ % \includegraphics[height=0.227\textwidth]{./figs/100b_150}
+ % \includegraphics[height=0.227\textwidth]{./figs/100b_200}
+%\end{center}
+%\caption{\label{fig:Eroding100vort} 100 bodies eroding in a
+%Hagen-Poiseuille flow. The four snapshots are equispaced in time, and
+%the color is the fluid vorticity.  Erosion creates many channels
+%connecting the inlet to the outlet.}
+%>>>>>>> 90934916f4dbe677f0ad6f05331ec1c3515ddab7
 \end{figure}

### 2019-10-15 docs/transport/erosion_transport.tex
modify figs in transport paper
giving it one more read through

@@
 equations are linear and homogeneous, they are converted to a boundary
-integral equation (BIE). Therefore, we resolve the non-negligible
-interactions between nearly-touching arbitrarily shaped bodies, and the
-erosion rate is computed accurately. We also compute the vorticity in
-the fluid bulk since, on solid boundaries, vorticity reduces to shear
-and thus provides a convenient way to simultaneously visualize local
-erosion rates and changes in the surrounding flow
+integral equation (BIE), and this allows us to naturally resolve the
+non-negligible interactions between bodies.  We also compute the
+vorticity in the fluid bulk since, on solid boundaries, vorticity
+reduces to shear and thus provides a convenient way to simultaneously
+visualize local erosion rates and changes in the surrounding flow
 (figure~\ref{fig:Eroding50vort}).
@@
 by~\citet{bak-she1986}, and in recent years, many other schemes have
-followed~\citep{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
-bea-lai2001, klo-bar-gre-one2013}.  We use a Barycentric quadrature
+followed~\citep{kli-tor2018, hel-oja2008a, bea-yin-wil2016, bea-lai2001,
+klo-bar-gre-one2013}.  We use a Barycentric quadrature
 method~\citep{bar2014, bar-wu-vee2015} since it is a non-intrusive
@@
 transport can be modelled as pure advection~\citep{dea-qua-bir-jua2018,
-leb-ded-dav-bou2007, cve-che-wen1996, puy-gou-den2019},
+cve-che-wen1996, puy-gou-den2019},
 advection-diffusion~\citep{cus-hu-den1995, dag1987, den-ica-hid2018}, or
@@
 motions~\citep{hak-com-den2019}.  To characterize spreading, the fluid
-dispersion is computed by calculating the variance of the streamline
-lengths. In porous media, this spreading is often
+dispersion is defined as the variance of the streamline lengths. In
+porous media, this spreading is often
 super-dispersive~\citep{kan-dea-nun-bij-blu-jua2014, cus-hu-den1995,
@@
 \gamma_M$, where $\Gamma$ is the outer boundary, taken to be a slightly
-smoothed version of the boundary of $[-3,3] \times [-1,1]$.  We only
-place eroding bodies in $[-1,1] \times [-1,1]$ to create a buffer region
-that allows the flow profile imposed at the inlet to transition to the more
-complex flow intervening between the bodies. On each eroding body, $\nn$
-is the normal vector pointing into the body, and $\ss$ is the unit
-tangent vector pointing in the counterclockwise direction.  The normal
-vector on $\Gamma$ is the outward unit normal.  Neglecting inertial
+smoothed version of the boundary of $[-3,3] \times [-1,1]$.  All eroding
+bodies are placed in $[-1,1] \times [-1,1]$ to create a buffer region
+that allows the flow profile imposed at the inlet to transition to the
+more complex flow intervening between the bodies. Neglecting inertial
 forces, the governing equations are
@@
 \end{equation}
-Here, $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
-prescribed Hagen-Poiseuille velocity field, $\Vn$ is the normal velocity
-of $\gamma$, and
+Here $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
+prescribed Hagen-Poiseuille velocity field, and $\Vn$ is the normal
+velocity of $\gamma$. The shear stress on $\gamma$ is
 \begin{align}
@@
 \end{align}
-is the shear stress on $\gamma$. We simulate erosion by alternating
-between solving the fluid equations and advancing the eroding grains.
-The strength of $\UU$ is adjusted at each time step to achieve a
-constant pressure drop across the channel, motivated by the geological
-situation of a porous medium connecting two regions of  fixed hydraulic
-heads.
+where, $\nn$ is the normal vector pointing into the body, and $\ss$ is
+the unit tangent vector pointing in the counterclockwise direction. We
+simulate erosion by alternating between solving the fluid equations and
+advancing the eroding grains.  The strength of $\UU$ is adjusted at each
+time step to achieve a constant pressure drop across the channel,
+motivated by the geological situation of a porous medium connecting two
+regions of  fixed hydraulic heads.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since we require accurate solutions of the incompressible Stokes
-equations in complex two-dimensional geometries, we reformulate the
-equations as a BIE.  This has the advantage that only the
-one-dimensional boundary of the domain must be discretized, and, with
-appropriate quadrature formulas and fast summation methods, the result
-is a high-fidelity numerical simulation with near-optimal computational
-complexity.
+To accurately solve the governing equations~\eqref{eqn:erosionModel} in
+complex two-dimensional geometries, we reformulate the equations as a
+BIE.  This has the advantage that only the one-dimensional boundary of
+the domain must be discretized, and, with appropriate quadrature
+formulas and fast summation methods, the result is a high-fidelity
+numerical simulation with near-optimal computational complexity.
 
@@
 corresponding deformation tensor, pressure, and vorticity at $\xx \in
-\Omega$ is written in terms of a layer potential~\cite{qua-moo2018}. To
+\Omega$ is written in terms of a layer potential~\citep{qua-moo2018}. To
 compute the deformation tensor for $\xx \in \gamma$, we include the jump
@@
 written as layer potentials in $\RR^2$.  However, the quadrature method
-we introduce in section~\ref{sec:method} requires a complex-valued
-representation of the layer potentials for the velocity, deformation
-tensor, and vorticity. The first step to form a complex representation
-is to write the Laplace double-layer potential as the complex integral
+we introduce in section~\ref{sec:method} requires complex-valued
+representations. The first step to form a complex representation is to
+write the Laplace double-layer potential as the complex integral
 \begin{align}
@@
 (\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
-potential, $\Omega$ is being interpreted as a subset of $\RR^2$ or
-$\CC$. Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy
-integral by first finding the boundary data of $v$.  Assuming that
-$\Omega$ is a simply-connected interior domain, the boundary data of $v$
+potential, $\Omega$ is interpreted as a subset of $\RR^2$ or $\CC$.
+Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
+first finding the boundary data of $v$. If $\Omega$ is a
+simply-connected interior domain, then the boundary data of $v$
 satisfies the Sokhotski-Plemelj jump relation
@@
   v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\upi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x-y}\, dy, \quad x \in \Omega.
+    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
 \end{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Erosion in porous media leads to particular phenomena such as
+Erosion in porous media leads to phenomena such as
 channelization~\citep{berhanu2012shape}, and we are interested in
@@
 tortuosity, and the distribution of the pore sizes.  The first two
-metrics can be defined in terms of streamlines governed by the
-autonomous advection equation~\eqref{eqn:tracers}.
+metrics are defined in terms of streamlines governed by the autonomous
+advection equation~\eqref{eqn:tracers}.
 
@@
 \end{align}
-and $\sigma_\lambda$ characterizes particle dispersion.  At early times,
-the particles have not explored much of the geometry, and we expect a
+and $\sigma_\lambda$ characterizes the dispersion.  At early times, the
+particles have not explored much of the geometry, and we expect a
 ballistic motion $\sigma_\lambda \sim t$.  However, as the particles
@@
 
-To establish an anomalous dispersion rate, the trajectories must pass
-several grains so that an asymptotic regime is reached. The geometries
-that we consider are too short to observe asymptotic dispersion, so we
-use a reinsertion method to form longer trajectories. Similar to the
-work of others~\citep{dea-qua-bir-jua2018, puy-gou-den2019}, once a
-particle reaches the outlet of the porous region, it is reinserted at
-the inlet.  To minimize errors caused by reinsertion, the particle is
-initialized at the discretization point that has the closest velocity to
-the particle's velocity at the outlet.  After a single trajectory is
-formed, it has undergone a collection of reinsertions.  Then, as a
-post-processing step, the trajectory is made continuous by attaching the
-tail of each segment to the origin of the next segment.
-
-We consider trajectories in an open channel so that they can be compared
-to trajectories in eroded geometries with large permeability.  The
-trajectories are $(s_1(t),s_2(t)) = ((1-s_2(0)^2)t + s_1(0), s_2(0))$.
+To establish an asymptotic anomalous dispersion rate, the trajectories
+must pass several grains. The geometries that we consider are too short
+to observe asymptotic dispersion, so we use a reinsertion method to form
+longer trajectories. Similar to the work of
+others~\citep{dea-qua-bir-jua2018, puy-gou-den2019}, once a particle
+reaches the outlet of the porous region, it is reinserted at the inlet.
+To minimize errors caused by reinsertion, the particle is initialized at
+the discretization point that has the closest velocity to the particle's
+velocity at the outlet.  After a single trajectory is formed, it has
+undergone a collection of reinsertions.  Then, as a post-processing
+step, the trajectory is made continuous by attaching the tail of each
+segment to the origin of the next segment.
+
+%We consider trajectories in an open channel so that they can be compared
+%to trajectories in eroded geometries with large permeability.  The
+%trajectories are $(s_1(t),s_2(t)) = ((1-s_2(0)^2)t + s_1(0), s_2(0))$.
+%%\begin{align}
+%%  s_1(t) = (1-s_2(0)^2)t + s_1(0), \quad
+%%  s_2(t) = s_2(0).
+%%\end{align}
+%Averaging over $s_2(0) \in [-1,1]$, the first and second ensemble
+%moments are
 %\begin{align}
-%  s_1(t) = (1-s_2(0)^2)t + s_1(0), \quad
-%  s_2(t) = s_2(0).
+%  \langle \lambda \rangle (t) = \frac{2}{3}t, \quad 
+%    \sigma_\lambda^2(t) = \frac{4}{45}t^2.
 %\end{align}
-Averaging over $s_2(0) \in [-1,1]$, the first and second ensemble
-moments are
-\begin{align}
-  \langle \lambda \rangle (t) = \frac{2}{3}t, \quad 
-    \sigma_\lambda^2(t) = \frac{4}{45}t^2.
-\end{align}
-In section~\ref{sec:results}, we compare the second moment in an open
-channel with the trajectories in an eroded geometry.
+%In section~\ref{sec:results}, we compare the second moment in an open
+%channel with the trajectories in an eroded geometry.
 
@@
 distributions of pore sizes between neighboring grains.  To define
-neighboring grains, we form a Delaunay triangulation using nodes placed
-at the center of each eroding grain and at a collection of points around
-the boundary of the porous media.  Then, we say that two grains are
-neighbors if their centers share an edge of the
+neighboring grains, we form the Delaunay triangulation using nodes
+placed at the center of each eroding grain and at a collection of points
+around the boundary of the porous media.  Then, we say that two grains
+are neighbors if their centers share an edge of the
 triangulation~\citep{dea-qua-bir-jua2018}. The pores of an eroded
@@
 Since we use a BIE formulation, we only need to discretize the
-one-dimensional boundary of the domain.  Therefore, we easily resolve
-complex geometries, and differentiation is performed with spectral
-accuracy in Fourier space.  We discretize each eroding grain $\gamma_k$
-with $N_\iin$ points and discretize the outer wall $\Gamma$ with
-$N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ and
-$\gamma_k$ are denoted by $\yy_j^0$ and $\yy^k_j$, respectively.  The
-discretization points are initially distributed evenly in arclength, and
-this equispacing is maintained throughout the entire simulation by using
-the {\thL} formulation.  In addition, we apply
-regularization~\citep{qua-moo2018} to slightly smooth the corners that
-inevitably develop during erosion.
+one-dimensional boundary of the domain.  We discretize each eroding
+grain $\gamma_k$ with $N_\iin$ points and discretize the outer wall
+$\Gamma$ with $N_\out$ points.  The $j^{th}$ discretization point on
+$\Gamma$ and $\gamma_k$ are denoted by $\yy_j^0$ and $\yy^k_j$,
+respectively.  The discretization points are initially distributed
+evenly in arclength, and this equispacing is maintained throughout the
+entire simulation by using the {\thL} formulation.  In addition, we
+apply regularization~\citep{qua-moo2018} to slightly smooth the corners
+that inevitably develop during erosion.
 
@@
 of~\eqref{eqn:trapLinearSystem} is an accurate approximation of the
-density function, Stokeslets, and rotlets.   Then, if $\xx \in \Omega$
-is sufficiently far from $\bd\Omega$, an approximation of the velocity,
-deformation tensor, and vorticity due to the double-layer potential is
-found by applying the trapezoid rule. In particular,
+density function, Stokeslets, and rotlets. Then, for $\xx \in \Omega$,
+the double-layer potential is approximated as
 \begin{align}
@@
   \uu(\xx) &= \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j, \\
-%
-  \ssigma(\xx) &= \sum_{j=1}^{N_\out} w^0_j \mathbf{D}_\ssigma(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j \mathbf{D}_\ssigma(\xx,\yy^k_j)
-  \eeta^k_j, \\
-%
-  w(\xx) &= \sum_{j=1}^{N_\out} w^0_j D_\omega(\xx,\yy^0_j) \eeta_j +
-  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D_\omega(\xx,\yy^k_j)
-  \eeta^k_j.
-\end{align}
-The contributions due to the Stokeslets and rotlets require no
-quadrature and are easily included in the velocity, deformation tensor,
-and vorticity.  Finally, to compute the shear stress, we apply the
-trapezoid rule with Fourier differentiation to approximate the jump
-term~\eqref{eqn:deformationJump} of the deformation tensor, and then the
+  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j. 
+%%
+%  \ssigma(\xx) &= \sum_{j=1}^{N_\out} w^0_j \mathbf{D}_\ssigma(\xx,\yy^0_j) \eeta_j +
+%  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j \mathbf{D}_\ssigma(\xx,\yy^k_j)
+%  \eeta^k_j, \\
+%%
+%  w(\xx) &= \sum_{j=1}^{N_\out} w^0_j D_\omega(\xx,\yy^0_j) \eeta_j +
+%  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D_\omega(\xx,\yy^k_j)
+%  \eeta^k_j.
+\end{align}
+Similarly, the corresponding layer potentials for the deformation tensor
+and vorticity are approximated with the trapezoid rule. The
+contributions due to the Stokeslets and rotlets require no quadrature
+and are easily included in the velocity, deformation tensor, and
+vorticity.  Finally, Fourier differentiation is used to compute the jump
+term~\eqref{eqn:deformationJump} of the shear stress, and then the
 tensor is applied to the normal and tangent vectors as defined in
@@
 functions~\citep{tre-wei2014}, the derivative of the integrand grows as
-the target point $\xx$ approaches $\bd\Omega$. The result is an error
-bound depends on the location of the target point. Therefore, if the
+the target point $\xx$ approaches $\bd\Omega$.  Therefore, if the
 trapezoid rule is applied when bodies are in near-contact, or if a layer
@@
 $\Omega \subset \CC$, with any point $a \in \Omega$, and we consider
-target points $x \in \Omega$ and $x \in \Omega^c$. Then, these
-quadrature rules can be applied to individual components of a
-multiply-connected domain to compute the velocity, vorticity, and
-deformation tensor in an eroding porous media.  The method starts with
-an underlying quadrature rule, and we use the spectrally accurate
-$N$-point trapezoid rule.  Since the quadrature points are uniformly
-distributed, the quadrature weights are $w_j = L/N$, $j=1,\ldots,N$,
-where $L$ is the length of $\bd\Omega$.
+target points $x \in \Omega$ and $x \in \Omega^c$. Then, the quadrature
+rules can be applied to individual components of a multiply-connected
+domain to compute the velocity, vorticity, and deformation tensor in an
+eroding porous media.  The method starts with an underlying quadrature
+rule, and we use the spectrally accurate $N$-point trapezoid rule.
+Since the quadrature points are uniformly distributed, the quadrature
+weights are $w_j = L/N$, $j=1,\ldots,N$, where $L$ is the length of
+$\bd\Omega$.
 
@@
 and target points.  By using a fast summation method, such as the fast
-multipole method (FMM)~\citep{gre-rok1987}, this cost can be reduced to
+multipole method (FMM)~\citep{gre-rok1987}, the cost can be reduced to
 $O(N)$ operations.  However, each application of the Barycentric
@@
 
-To compute the velocity double-layer potential, we start by applying the
-trapezoid rule~\eqref{eqn:trap} accelerated with the FMM.  This
-calculation requires $O(N)$ operations, and we call the
-resulting velocity $\vv_\trap(\xx)$.  Since the trapezoid rule is
+To compute the velocity double-layer potential~\eqref{eqn:velocityDLP},
+we start by applying the trapezoid rule~\eqref{eqn:trap} accelerated
+with the FMM.  This calculation requires $O(N)$ operations, and we call
+the resulting velocity $\vv_\trap(\xx)$.  Since the trapezoid rule is
 spectrally accurate, the error of $\vv_\trap(\xx)$ is small for points
@@
 \begin{align}
-  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_\iin} \sum_{j=1}^{N_\iin} 
+  \vv(\xx) = \vv_\trap(\xx) - \sum_{j=1}^{N_\iin} w_j^k
     D(\xx,\yy^k_j) \eeta(\yy_j) + \vv^k_\bary(\xx),
@@
 Per grid point, applying the Barycentric quadrature rules dominate the
-computational cost. Therefore, it is imperative that we only apply the
-Barycentric quadrature when the trapezoid rule is inaccurate.  As a rule
-of thumb, the trapezoid rule due to $\gamma_k$ achieves machine epsilon
-accuracy if~\citep{bar2014}
+computational cost, so it is imperative that it is only applied when
+necessary. As a rule of thumb, the trapezoid rule due to $\gamma_k$
+achieves machine epsilon accuracy if~\citep{bar2014}
 \begin{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo[inline]{Bryan is here}
 We use the time stepping method outlined in our previous
@@
 %  \includegraphics[height=0.227\textwidth]{./figs/100b_50}
-  %\includegraphics[height=0.227\textwidth, trim=0cm 0cm 2.8cm 0cm, clip=true]
+%  \includegraphics[height=0.227\textwidth, trim=0cm 0cm 2.8cm 0cm, clip=true]
 %    {./figs/100b_100}
@@
 \end{subfigure}
-
-\caption{\label{fig:Eroding20tort} The local tortuosity of a porous
-geometry initialized with 20 grains after eroding to a porosity of
-62.9\%.  (a) The $x$-component of the velocity at the inlet,
-$u_1(-1,y)$, normalized by its maximum velocity of $2.98 \times
-10^{-3}$. (b) The local tortuosity $\tau(y)$ on the cross section $x =
--1$. (c) The streamlines resulting in the ten largest differences of
-local tortuosity between neighboring streamlines.  Neighboring
-streamlines have the same color.}
-
 \caption{\label{fig:Eroding100tort} The local tortuosity of a porous

### 2019-10-16 docs/transport/erosion_transport.tex
gave it one last read through

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo[inline]{Bryan is here}
 We use the time stepping method outlined in our previous
@@
 $L$ is the length of $\gamma$, and $\kappa$ is the curvature of
-$\gamma$.  This new term penalizes regions of high curvature, and the
-normalization term guarantees that the regularization only changes the
-body's shape, but not its total length.  Finally, to increase the
-overall stability of the method, a narrow Gaussian filter is applied to
-the erosion rate at each time step.
+$\gamma$.  The new erosion model penalizes regions of high curvature,
+but does not change the total length of each body.  Moreover, to
+increase the overall stability of the method, a narrow Gaussian filter
+is applied to the erosion rate at each time step.
 
 Rather than tracking the $(x,y)$ coordinates, the {\thL} coordinates are
-tracked. In addition, a tangential velocity field is added to each body
-so that the discretization points remain equispaced in arclength for all
-time.  Time stepping is performed with a second-order Implicit-Explicit
-Runge-Kutta method. In particular, the diffusive term corresponding to
-the curvature penalization term is discretized implicitly, and all other
-terms, which are non-stiff, are treated explicitly.  By using this time
-stepping method in conjunction with the Barycentric rule, we stably
-evolve the eroding bodies.
+tracked. In addition, tangential velocity fields are used to maintain
+an equispaced discretization. Time stepping is performed with a
+second-order Implicit-Explicit Runge-Kutta method. In particular, the
+diffusive term corresponding to the curvature penalization term is
+discretized implicitly, and all other terms, which are non-stiff, are
+treated explicitly.  By using this time stepping method in conjunction
+with the Barycentric rule, we stably evolve the eroding bodies.
 
 To examine the tortuosity and the anomalous dispersion rates
-(section~\ref{sec:transport}), we require accurate computation of the
+(section~\ref{sec:transport}), we require accurate 
 streamlines governed by equation~\eqref{eqn:tracers}. If a low-order
@@
 the dispersion and the tortuosity.  We use $N_p = 1000$ streamlines so
-that the statistics have converged~\citep{bel-sal-rin1992}.  However, as
-described in section~\ref{sec:dispersion}, a reinsertion method is used
-to compute trajectories that are sufficiently long to observe an
-asymptotic anomalous dispersion rate.  To compute the tortuosity using
-the trajectories, we consider trajectories crossing between the two
-cross-sections $x=-1$ and $x=1$.  Then, we discretize
-equation~\eqref{eqn:tortuosity1} as
+that the statistics have converged~\citep{bel-sal-rin1992}. As described
+in section~\ref{sec:dispersion}, a reinsertion method is used to compute
+trajectories that are sufficiently long to observe an asymptotic
+anomalous dispersion rate.  To compute the tortuosity using
+equation~\eqref{eqn:tortuosity1}, we consider trajectories crossing
+between the two cross-sections $x=-1$ and $x=1$, and approximate the
+tortuosity with
 \begin{align}

### 2019-10-18 docs/transport/erosion_transport.tex
moved a directory
add modified figs in transport paper
add two bodies in caption of transport paper
fixed typos

@@
 formulation by adding the $M$ Stokeslets,
-$S[\llambda_\ell,\cc_\ell](\xx)$, and rotlets,
+$S[\llambda_\ell,\cc_\ell](\xx)$, and $M$ rotlets,
 $R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
@@
 corresponding deformation tensor, pressure, and vorticity at $\xx \in
-\Omega$ is written in terms of a layer potential~\citep{qua-moo2018}. To
-compute the deformation tensor for $\xx \in \gamma$, we include the jump
-term
+\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
+To compute the deformation tensor for $\xx \in \gamma$, we include the
+jump term
 \begin{align}
@@
 \end{equation}
-where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
+where $y \cdot \eta = y_1 \eta_1 + y_2 \eta_2$, 
 \begin{align} 
@@
 Using a similar construction, the exterior Barycentric quadrature rule
-for the the first derivative is
+for the first derivative is
 \begin{align}
@@
 \begin{center}
-  \includegraphics[height=0.227\textwidth]{./figs/20b_dense1}
-  \includegraphics[height=0.227\textwidth]{./figs/20b_dense101}
-  \includegraphics[height=0.227\textwidth]{./figs/20b_dense201}
-  \includegraphics[height=0.227\textwidth]{./figs/20b_dense301}
+  \includegraphics[height=0.227\textwidth]{./figs/20b_1}
+  \includegraphics[height=0.227\textwidth]{./figs/20b_101}
+  \includegraphics[height=0.227\textwidth]{./figs/20b_201}
+  \includegraphics[height=0.227\textwidth]{./figs/20b_301}
 \caption{\label{fig:Eroding20vort} 20 bodies eroding in a
@@
 the color is the fluid vorticity. In the fourth frame, bodies 4, 12, and
-17 have vanished, and body 19 has almost vanished.}
+17 have vanished, and bodies 7, 19, 20 have almost vanished.}
 \end{center}
@@
 compute the pore size by finding the closest distance between all
-neighboring bodies.  Instead of computing the Delanuay configuration at
+neighboring bodies.  Instead of computing the Delaunay configuration at
 each time step, which would result in new definitions for the pores at

### 2019-10-23 docs/proposals/DOE/ErosionWhitePaper.tex
added new directory for potential NSF proposal

--- 2019-05-21 docs/proposals/ErosionWhitePaper.tex
@@
   fluid equations are solved with a boundary integral equation (BIE).
-  The BIE formulation achives high-order accuracy in complex geometries
+  The BIE formulation achieves high-order accuracy in complex geometries
   with optimal computational complexity.
@@
 three-dimensional erosion}.  Second, {\bf we will investigate physically
-motivated questions regarding the reconfiguration of geometry and flow inside an eroding
-porous medium}.
+motivated questions regarding the reconfiguration of the geometry and
+transport inside an eroding porous medium}.
 
@@
 \subsection{Improved Numerical Methods}
-\begin{wrapfigure}[22]{r}{0.4\textwidth}
+\begin{wrapfigure}[20]{r}{0.35\textwidth}
 \centering
@@
 Our current formulation fixes all bodies space.  However, in reality,
-the bodies are also transported by the flow.  The PI has simulated
-moving interfaces in Stokes flow~\cite{qua-bir2015b, qua-bir2014,
-qua-bir2016}. More recently, the PI and his former Ph.D.~student
-developed time stepping methods for rigid body transport in Stokes
-flow~\cite{bys-sha-qua2018}.  This work extends a contact algorithm,
-originally developed by Lu et al.~\cite{lu-rah-zor2017}, to accuratly
-simulate the dynamics of nearly-touching rigid bodies.  The contact
-algorithm resolves errors introduced by time stepping, but quadrature
-error introduced by the BIE formulation must also be addressed.  A
-postdoc in the PI's group is extending a Barycentric near-singular
-integration scheme developed by Barnett et al.~\cite{bar-wu-vee2015} to
+the bodies are also transported by the flow.  The PI is experienced with
+simulating moving interfaces in Stokes flow~\cite{qua-bir2014,
+qua-bir2016}. Recently, the PI and his former Ph.D.~student developed
+time stepping methods for rigid body dynamics in Stokes
+flow~\cite{bys-sha-qua2018}.  This work extends a contact
+algorithm~\cite{lu-rah-zor2017} to simulate the dynamics of
+nearly-touching rigid bodies.  The contact algorithm addresses time
+stepping errors, but quadrature error introduced by the BIE formulation
+must also be addressed.  A postdoc in the PI's group is extending a
+Barycentric near-singular integration scheme~\cite{bar-wu-vee2015} to
 develop quadrature formula to accurately compute the shear stress,
@@
 \subsection{Physics-Based Understanding of Viscous Erosion}
-\todo[inline]{Characterizing anisotropy}
-\todo[inline]{Coarse-grained transport (anomalous diffusion)}
+
+Armed with these new tools, we plan to investigate how erosion alters a
+porous medium through a reshaping process that occurs on the grain
+scale. Initial investigations show that, as bodies erode and reduce in
+size, the permeability of the medium increases. The rate of increase,
+however, cannot be explained by the reduction in grain size alone, as
+the reshaping and associated formation of channels are vital elements.
+The new methods will allow us to examine these features in more detail.
+In particular, we anticipate that erosion leads to the development of
+{\bf anisotropic} permeability, as the medium gradually reconfigures to
+transmit flow more easily in the direction of the initial flow. We will
+characterize the changes in permeability and anisotropy especially in
+nearly-touching body configurations, in more dense packings, and
+eventually in configurations of mobile and sedimenting grains.
+
+We will also investigate transport in eroding geometries. Two ways to
+describe transport is with {\bf anomalous
+diffusion}~\cite{dea-qua-bir-jua2018} and {\bf tortuosity}.  Anomalous
+diffusion characterizes the spread of particles submerged in a geometry,
+and the tortuosity quantifies the length of trajectories relative to
+their size in a channel flow with no grains.  Both of these quantities
+require a statistical analysis of streamlines, and we have already begun
+these calculations (Figure~\ref{fig:streams}).  Once these quantities
+are computed, we will investigate the relationship between erosion and
+transport in eroding geometries.  The result will be new coarse-grained
+descriptions for transport in complex eroding geometries.
 
@@
 \section{Biographical Information}
+
+\begin{wrapfigure}[19]{l}{0.3\textwidth}
+\centering
+\includegraphics[width=0.28\textwidth]{figs/100b_t100tracer.pdf}
+\caption{\label{fig:streams} \em Trajectories of passive particles in an
+eroded geometry with 100 bodies.  The transport of flow in such a
+geometry will be characterized by a statistical analysis of the
+trajectories.}
+\end{wrapfigure}
 Since 2015, {\bf Bryan Quaife} has been an Assistant Professor in the
-Department of Scientific Computing at Florida State University.  He is
-also a Research Associate in FSU's Geophysical Fluid Dynamics Institute.
-Dr.~Quaife received his Ph.D.~in 2011 in Applied and Computational
-Mathematics at Simon Fraser University.  He was a postdoctoral fellow
-for four years in Dr.~George Biros' group at the Institute for
-Computational Science and Engineering at the University of Texas.  His
-research interests include the development of  high-fidelity and
-efficient numerical methods for simulating fluid dynamics in complex
+Department of Scientific Computing at Florida State University (FSU).
+He is also a Research Associate in FSU's Geophysical Fluid Dynamics
+Institute.  Dr.~Quaife received his Ph.D.~in 2011 in Applied and
+Computational Mathematics at Simon Fraser University.  He was a
+postdoctoral fellow from 2011--2015 in Dr.~George Biros' group at the
+Institute for Computational Science and Engineering at the University of
+Texas.  His research interests include the development of  high-fidelity
+and efficient numerical methods for simulating fluid dynamics in complex
 geometries.
@@
 Florida State University.  He is also a Research Associate in FSU's
-Geophysical Fluid Dynamics Institute. \todo[inline]{A bit more}
+Geophysical Fluid Dynamics Institute.  Dr.~Moore received his Ph.D.~in
+2010 in Mathematics at the University of North Carolina, Chapel Hill. He
+was a postdoctoral researcher at the Courant Institute of Mathematical
+Sciences from 2010--2014 working with Dr.~Michael Shelley and others.
+His expertise includes modeling dynamic interactions between fluids and
+structures, especially in geophysically and biologically motivated
+settings.
 
@@
 \section{Expected Budget}
-\todo[inline]{I can have Michelle put one together.  Funds are needed
-for the following}
-\begin{itemize}
-  \item Summer salary (1 month a year for 3 years)
-  \item 2 RA (1 in Math, 1 on DSC)
-  \item 1 joint postdoc
-  \item Travel
-  \item Computers
-  \item FSU overhead
-\end{itemize}
+We request funding for three years.  For the project to be successful,
+we propose one month of summer salary each year for both the PI and
+co-PI, one joint two-year postdoctoral fellow, two full-time RAs (one
+from each of our home departments), laptops, and travel money.
+Including FSU's overhead, we expect that {\bf the total cost of the
+project would be around \$750,000.}
+%\begin{itemize}
+%  \item Summer salary (1 month a year for 3 years)
+%  \item 2 RA (1 in Math, 1 on DSC)
+%  \item 1 joint postdoc
+%  \item Travel
+%  \item Computers
+%  \item FSU overhead
+%\end{itemize}
 

### 2019-10-28 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

 \documentclass[12pt]{article}

%---------------------------------------------------------------------------------------------------%
%% PACKAGES
\usepackage{fullpage}
%\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{graphicx, amsmath, amssymb, amsfonts, mathtools, mathrsfs, color}
\usepackage{comment, enumerate, tabularx}
\usepackage{natbib, hyperref, url}
%\usepackage[justification=RaggedRight]{caption}
\usepackage{outlines,enumitem}
%---------------------------------------------------------------------------------------------------%

%---------------------------------------------------------------------------------------------------%
%% LATEX DEFINITIONS
% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
\newcommand{\here}{{\color{blue} here}}
% Basic math, derivatives
\newcommand{\td}[2]{\frac{d #1 }{d #2}}
\newcommand{\ttd}[2]{\frac{d^2 #1 }{{d #2}^2}}
\newcommand{\pd}[2]{ \frac{ \partial #1}{ \partial #2 } }
\newcommand{\ppd}[2]{ \frac{ \partial^2 #1}{ {\partial #2}^2 } }
\newcommand{\mppd}[3]{ \partial_{#2 #3} #1 }
% Basic math, vectors and other
%\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\bvec}[1]{{\mathbf{#1}}}
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\tavg}[1]{\langle #1 \rangle}
\newcommand{\norm}[1]{ \left\| #1 \right\| }
\newcommand{\ip}[1]{ \langle #1 \rangle }
\newcommand{\eps}{\varepsilon}
% For real and imaginary, could use \Re or \Im, or \mathcal{R}, or \text{Re}

% Outline stuff
\setenumerate[1]{label=\Roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[3]{label=\roman*.}

% Specific
\newcommand{\uu}{\bvec{u}}
\newcommand{\xx}{\bvec{x}}
\newcommand {\qq} {\bvec{q}}
\newcommand{\nn}{{\mathbf{n}}}
\renewcommand{\ss}{{\mathbf{s}}}
\newcommand{\Vn}{V_\nn}
\newcommand{\CE}{C_E}
\newcommand {\ny}{n}
\newcommand {\bdry} {\partial B}
\newcommand{\Diff}{D}
\newcommand{\thL}{$\theta$--$L$}

%---------------------------------------------------------------------------------------------------%

%---------------------------------------------------------------------------------------------------%
%% TITLE
\begin{document}
\title{Project Description --
CAREER: Erosion, Seepage, Collapse, and Filtration in Granular and Porous Media}

% Original erosion title
%Mathematical models and analysis for erosion and dissolution in porous-media flow}
%\author{}
\date{}
\maketitle
%---------------------------------------------------------------------------------------------------%

%---------------------------------------------------------------------------------------------------%
%% INTRODUCTION
\section{Proposed Research}

\subsection{Introduction and Background}

Naturally occurring porous and granular materials, such as soil, sand, and clay, play a pivotal role in regulating earth's water resources by filtering contaminants and, over long timescales, supplying fresh water. Not only is this process essential for human water resources, but also for the ecology of rivers, estuaries, and other natural habitats. Natural water resources, however, have been placed under enormous pressure by human population growth and associated activities that can comprise the natural filtration cycle, for example expansion of industry, urbanization, pollution, and climate change. See the USGS and the UN report on water resources for further detail on the threats to water resources [USGS?] \cite{UNwater}.

To take one example of particular importance to the state of Florida, the formation of sinkholes can be triggered by certain human activities such as groundwater pumping or the weight of run-off storage ponds \cite{sandhu2018fate}. When collapse occurs below a storage pond, the underlying reservoir of pristine groundwater can be severely contaminated, thus surrendering a natural resource of great economic and societal value. Clearly, a deeper understanding of the mechanisms leading to sinkhole formation, and more generally that underly earth's natural filtration system, could reap enormous benefits in predicting and mitigating such environmental disasters. Other applications include understanding and predicting contamination by nuclear waste and by hydraulic fracturing.

This proposal aims to develop a deeper understanding of the physical processes by which groundwater flow can alter properties of a porous medium. A recognized complexity of naturally occurring media is that their macroscopic properties, e.g.~permeability and mechanical strength, can be highly heterogeneous and anisotropic {\color{blue}(cite)}. These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material. Potential exists for feedback between these timescales: for example the slow wearing process reaching a critical threshold beyond which catastrophic events become more likely. The main objective of this proposal is to gain a deeper understanding of such processes through analyzing a specific set of problems and by developing a host of new mathematical tools, ranging from analytical to computational ones.

Physical mechanisms that can dynamically alter porous-medium properties include:
\begin{itemize}
\item Erosion of solid material due to fluid-mechanical stresses or chemical dissolution.
\item Transport of grains due to intervening fluid flow and due to sedimentation.
\item Compaction of the medium due to overlying loads.
\item Gravitational collapse of a medium due to loads exceeding a threshold.
\end{itemize}
The above are roughly ordered according to timescale, from the slowest acting to the fastest. While many of these mechanisms have been studied individually in various contexts and to varying levels of rigor, very little is known about their combined effect on the dynamic evolution of a porous medium. Since we aim to build a quantitative model from the ground up, we will first focus on the slowest acting mechanisms, as these ultimately set the stage for the more rapid events like sinkhole collapse. 
In particular, we view the slow processes of erosion and dissolution as instrumental in altering porous-medium properties. First, by deteriorating solid material, erosion alters the size distribution of grains. This modified distribution can in turn affect transport by enabling smaller grains to be sieved through networks of larger ones. A second and more subtle way that erosion can alter medium properties is by changing the {\em shape} distribution of grains. For instance, erosion can carve grains into slender shapes aligned primarily in the direction of the dominant flow, thereby creating {\em anisotropic} characteristics. {\color{blue} Need to include comment on dissolution changing conduit paths.}

More generally, the coupling between shape and flow during erosion, dissolution, and related phase-change processes is a topic that has garnered recent interest in the mathematical sciences community \cite{Ristroph2012, rycroft2016asymmetric, cohen2016erosion, MooreCPAM2017, mitchell2017generalized, Quaife2018, wykes2018self, lachaussee2018competitive, lopez2018cfd, ristroph2018sculpting}. 
Erosion-induced shape change has been studied in the high Reynolds number regime, both experimentally \cite{Ristroph2012, MoorePOF2013} and theoretically \cite{MoorePOF2013, MooreCPAM2017, hewett2017evolution} and in single \cite{Ristroph2012, MoorePOF2013, MooreCPAM2017, lachaussee2018competitive} and multiple-body arrangements \cite{hewett2017evolution}. 
Studies on related processes of dissolution \cite{HuangJFM2015, kondratiuk2015steadily, cohen2016erosion, claudin2017dissolution, wykes2018self, huang2017solute}, melting \cite{Cummings1999, back2014effect, rycroft2016asymmetric, hewett2017pear, MooreCPAM2017, toppaladoddi2018combined, hewett2019evolution, favier2019rayleigh}, solidification \cite{Huppert90, Anderson95, Cummings1999, mccue2003extinction}, and deposition \cite{hewett2018modelling} exhibit intriguing similarities and differences \cite{MooreCPAM2017}.
These studies reveal a rich set of possible dynamics, from the emergence of universal morphologies that erase details of the initial state and evolve self-similarly in time \cite{MoorePOF2013, MooreCPAM2017, hewett2017pear}, to fine-scale pattern formation \cite{cohen2016erosion, claudin2017dissolution, huang2017solute},
to unstable morphologies that can retain or even amplify features present in the initial state \cite{claudin2017dissolution, wykes2018self}.

Only recently have these ideas been extended to low Reynolds number flows  \cite{mitchell2017generalized, Quaife2018} --- the regime applicable to porous media as well as biological applications like plaque erosion. While the governing fluid-flow equations become linear in this regime, porous-media applications present a host of new challenges, for example:
\begin{itemize}
\item Porous media typically involves dense packings so that close-range effects and even nearly contacting bodies must be considered {\color{blue}(cite nearly contact papers)}.
\item The Stokes limit introduces {\em longer} range effects than the inertial limit does, thus coupling the shape evolution of {\em all} grains and conduits to a higher degree.
\item Somewhat counterintuitively, erosion does not always act to smooth shapes but rather can create sharp features and corners. These features can be difficult to resolve and, further, can trigger numerical instabilities. Dissolution, meanwhile, can initiate a roughening transition {\color{blue} (cite)}, leading to similar numerical difficulties.
\item Additionally effects, such as sedimentation, transport, and compaction constantly work to reconfigure the medium as its constituents and boundaries degrade.
\end{itemize}
These challenges require innovative computational techniques, many of which have been developed recently \cite{Quaife2018} and many of which await resolution. The grand goal of achieving high-fidelity simulations of order-100 mobile bodies which undergo simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency to run large ensembles for statistical analysis, still awaits. Fortunately, some closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton \cite{bizmark2019multiscale}. The experiments offer a wonderful opportunity to guide, calibrate, and validate theoretical developments.

While erosion and dissolution correspond to gradual changes in a medium, the example of a sinkhole represents a sudden, catastrophic event. It is likely that all of the mechanisms listed above --- erosion, dissolution, transport, compaction, and gravitational collapse --- contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity. Sinkhole formation has been explored with preliminary experiments run at the Geophysical Fluid Dynamics Institute at Florida State University \cite{tao2014experimental}. These scaled-down experiments offer the ability to probe various mechanisms behind sinkhole formation, for example a difference in hydraulic head between the confined and unconfined aquifers.

	With two Mathematics PhD students, the PI has begun running preliminary simulations to model this behaviors. The simulations, which are at an early stage of development, are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively. They utilize a homogenized description of the flow field, e.g.~the Darcy or Brinkman equations.
These simulations incorporate the physical effects of:
\begin{itemize}
\item Transport of grains due to seepage force from the surrounding fluid flow.
\item Gravitational sedimentation of grains.
\item Feedback of grain-distribution onto permeability field.
\item Contact and cohesive forces between grains.
\end{itemize}
Preliminary investigation suggests that this last mechanisms of cohesion is essential to model sinkhole collapse in the system, and the simulations await careful calibration against experimental data.

The simulations do not yet incorporate the effects of erosion and dissolution. A grand goal of this proposal would be to merge these two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short term events, such as sinkhole collapse, and long-term changes in the medium. Such a framework must include the effects of erosion, dissolution, transport, sedimentation, compaction, cohesive forces, and mechanical collapse. The greatest challenge faced is the disparate temporal and spatial scales that must be considered. Our strategy is to use the high-fidelity erosion and dissolution simulations to develop reduced models (ala mean-field theory) that would be incorporated into simulations.

% McCurdy and Wang work
% Multiphase stuff too

% Could emphasize dissolution of karst more too.
% Not crazy about inverse model sentences, maybe move to end of paragraph.

%I could try to work in more mathy stuff: complex dynamical system, feedback, timescales, computational methods, analytical reductions...

%---------------------------------------------------------------------------------------------------%
\subsection{Governing equations}
At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations
\begin{equation}
\label{StokesEq}
\begin{split}
\mu \Delta \uu = \grad p,	&\hspace{20pt} \xx \in \Omega, \\
\grad \cdot \uu = 0, 		&\hspace{20pt} \xx \in \Omega,
\end{split}
\end{equation}
where $\uu$ is the velocity field, $p$ the pressure field, and $\mu$ the fluid viscosity. This microscopic description is needed to model the shape evolution of individual grains from shear-induced erosion. The description, however, becomes impractical when attempting to model seepage in very large porous systems where the microscopic geometry can be exceedingly complex. Instead, it becomes necessary to homogenize over microscopic details to arrive at an approximate description. Leading-order homogenization produces the well-known Darcy system
\begin{equation}
\label{DarcyEq}
\qq = - \bvec{K} \grad \phi
\end{equation}
where $\qq$ is the {\em specific discharge} or {\em Darcy velocity}, and $\phi = z + p/(\rho g)$ is the hydraulic head, with $\rho$ and $g$ representing the fluid density and gravitational constant respectively. Above, $\bvec{K}$ is the {\em conductivity}, which is related to the {\em permeability} $\bvec{k}$ through $\bvec{K} = \bvec{k} \rho g/\mu$. Both the conductivity and permeability are in general tensors, and they reduce to scalars in the case of an isotropic medium.
Note that the Darcy velocity is related to the tracer velocity through $\qq = \theta_f \uu$, where $\theta_f$ is porosity (i.e.~fluid volume fraction).
In the case of an isotropic medium, the Kozeny-Carman equation is often used to relate permeability to volume fraction \cite{bear2013dynamics}
% See Bear Ch. 2.8, pg. 111
\begin{equation}
k = C \frac{\theta_f^3}{(1-\theta_f)^2}
\end{equation}
The macroscopic description offered by Eq.~\eqref{DarcyEq}, although approximate, simplifies analysis tremendously in that individual grains are no longer resolved and thus the domain geometry is generally much simpler.

\subsection{Mechanical and chemical erosion of a porous medium}

%\subsubsection{Background}

The first problem discussed here is the erosion of a porous medium, as has been preliminarily investigated in \cite{Quaife2018}. We will consider erosion induced by either fluid-mechanical forces or by chemical reaction, i.e.~dissolution. In the former case, erosion results from surface shear stress
\begin{align}
\tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss \, .
\end{align}
where $\nn$ and $\ss$ are the unit normal and tangent vectors on the surface respectively and $\uu$ is the velocity field as computed from the incompressible Stokes equations \eqref{StokesEq}. 
The motion of the interface is proportional to the absolute value of shear
\begin{align}
\Vn = \CE \, \abs{\tau},
\end{align}
In the later case of chemically-induced erosion, a solute concentration field $C$ undergoes advection and diffusion:
\begin{align}
\label{Ceq}
& \pd{C}{t} + \uu \cdot \grad C = \Diff \Lap C \, ,
\end{align}
Material removal is then governed by Fick's law with interface velocity
\begin{equation}
\label{DissVn}
\Vn = \left. \Diff \pd{C}{\ny} \right. %\right\vert_{\bdry} \, ,
\end{equation}
Both processes have been investigated by the PI and collaborators in the context of single bodies in high Reynolds-number flows \cite{Ristroph2012, MoorePOF2013, HuangJFM2015, MooreCPAM2017}. In the low-Reynolds regime of porous-media flow, numerical methods have been developed by the PI and collaborators to simulate shear-induced erosion \cite{Quaife2018}. These simulations combine highly accurate boundary integral methods with stable interface evolution techniques. The boundary integral solver is accelerated by the fast multipole method \cite{gre-rok1987, gre-gre-may1992} to achieve optimal $O(N)$ complexity. Meanwhile, the so-called {\thL} method is used for interface evolution to prevent distortion and tangling of the interface meshes.
%A near-term goal is to adapt these methods to handle the case of chemically-induced dissolution.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/80circ8vort.pdf}
\caption{\label{fig1} Simulation of 80 bodies eroding in Stokes flow under the action of shear stress. Flow is left to right. Color represents vorticity, which provides a convenient way to visualize local shear rates. 
%Erosion not only diminishes the size of the bodies but also alters their shapes considerably. A few well-defined channels develop in the space between bodies. Several of the bodies vanish in finite time and the simulation continues without interruption.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

 Figure \ref{fig1} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow. The figure shows 80 bodies of initially random size and position, undergoing erosion. This figure extends previously reported 50-body simulations to 80 bodies \cite{Quaife2018} due to a recently developed barycentric interpolation scheme (CITE), which enables closer contact between bodies and thus more bodies.
The color shows the (normalized) vorticity field surrounding the bodies. Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity. Observe that erosion not only reduces the size of solid bodies, but also alters their shapes substantially. The bodies tend to become somewhat polygonal: corners develop connected by relatively flat faces. The number of faces does not appear to be easily predicted, but rather depends on the interaction with neighboring bodies as mediated by the Stokes flow. Notice that, as erosion proceeds, relatively straight channels tend to develop between the bodies. Certain channels that are initially larger can transmit more flow, which promotes local erosion rates and further widens these selected channels. In this way, erosion creates a runaway process in which small differences in initial channel size become amplified. The channelization process is made more evident by visualization of the velocity magnitude, as in Fig.~\ref{fig2}

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/80circ8vel.pdf}
\caption{\label{fig2} The same simulation as above with velocity magnitude in color. Velocity magnitude highlights the most dominant channels whose growth is reinforced by the shape-flow interaction of erosion.}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

The creation and reinforcement of channels significantly impacts the macroscopic properties of the porous medium, as the PI and collaborators have just begun to examine. Fig.~\ref{fig3} shows preliminary results on how media properties change in time. First, the left-most plot shows the rate at which the area fraction decreases as the bodies erode. Time is normalized by the value $t_f$ at which all bodies vanish and hence the area fraction is zero. Notice that the rate of area reduction does not change significantly during the simulation. The middle plot shows the resistivity, or inverse permeability of the medium. In the simulations, resistivity is calculated by measuring the total flux and the pressure upstream and downstream, then using Darcy's relation \eqref{DarcyEq} to infer $k$. Naturally, as bodies erode, the resistivity they provide decreases in time. Note, however, that the vertical axis is logarithmic. Hence, the initial linear decrease corresponds to an exponential rate of resistivity reduction. The much more mild decrease in area fraction is not sufficient to account for this exponential rate, and hence the reshaping process, in particular the formation of channels, plays a pivotal role.

Lastly, the right-most plot of Fig.~\ref{fig3} shows the anisotropy, which is calculated as the ratio of the vertical resistivity to the horizontal resistivity. The vertical resistivity is computed by rotating the configuration of bodies by 90 degrees. This plot shows the anisotropy to initial increase with time. Thus, the initially isotropic state becomes erased as bodies streamline and form primarily horizontal channels. Remarkably, the medium reaches an anisotropy of over 10, meaning that erosion can lead to a configuration that resists flow 10 times more in the vertically than horizontally.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
\caption{\label{fig3} Left: the area fraction of solid bodies versus time. Time is normalized by the vanishing time $t_f$. Middle: the resistivity of the porous matrix decrease much more rapidly than area fraction, indicating the reshaping process to be essential. Right: the anisotropy (ratio of vertical to horizontal resistivity) as it varies in time. Erosion can create a highly anisotropic medium.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

An immediate goal of the proposed work is extend the range of physical effects captured in these simulations. Very recently, we have implemented barycentric interpolation into the boundary integral solver in order to allow for more tightly spaced configurations, even bodies that nearly touch. Near-term plans are to include flow transport and gravitational sedimentation of the particles. For this extension, contact forces between bodies must be included. Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from straightforward in practice, with several competing possible strategies that are a topic of current research  {\color{blue} cite}. We plan to implement contact forces with {\color{blue} stuff}. This goal will form the PhD dissertation of a graduate student who will be supervised by myself and Prof. Bryan Quaife (FSU Scientific Computing).

Next, we plan to extend the simulation framework to handle chemical dissolution of solid bodies via physical laws \eqref{Ceq}--\eqref{DissVn}. For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations, is already in place, but the coupling to the advection-diffusion equations \eqref{Ceq} and interface law \eqref{DissVn} would need to be implemented. Once these pieces are in place, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation, would finally become possible. Such a framework could accurately simulate the geophysically relevant scenario of karst conduits with embedded granular media. The gradual changes in the medium and karst boundaries due to erosion and dissolution could create conditions favorable for mechanical failure or collapse of the structure, for example sinkholes.

\subsection{Sinkhole modeling}

Sinkhole background stuff...

Researchers at FSU's Geophysical Fluid Dynamics Institute have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments {\color{blue} cite}.

\np
\subsection{Filtration with porous membrane}

Efficient wastewater management and treatment facilities are a crucial part of clean water efforts in the United States. Most public utilities combine water pretreatment with microfiltration systems that need frequent cleaning and upkeep to ensure high production of clean water. Large-scale wastewater plants utilize hollow-fiber filtration systems where filters are built by splitting each tube into thousands of millimeter-scale capped porous tubes that run along its length [1-3]. As wastewater runs through the filter during the so-called forward filtration process, impurities accumulate and foul the membrane by occluding its pores. Pretreating the wastewater along with backwashing the filtering system (i.e. inverting the flow direction to dislodge foulants accumulated on the membranes) allows for the water production volume to be maintained [4, 5]. These dead-end microfiltration systems are widespread thanks to their success in removing solids, colloids, and difficult-to-disinfect protozoa [6, 7]; nonetheless, most research has focused on flat-membrane filters where only the tube cross-section is porous. This is mostly due to the simplicity of the cross-flow filtration and its modeling, as fouling and backwashing are spatially-uniform across the membrane [8, add reference, maybe 17?].
Our interest is in modeling hollow-fiber filtration systems to produce the maximum possible volume of clean water. We focus on a single hollow-fiber membrane system and scale its behavior up to match the ensemble filter. This will allow us to compare analytical and numerical results with experimental studies performed at the Aerosols and Water Treatment Lab with P.I. Professor Shankar Chellam at Texas A\&M University. Based on previous results [10-12], our aim is to model wastewater flow during forward filtration and foulant deposition on the membrane, which is spatially-dependent for this type of filtering system. In particular, although backwashing is an essential part of the filtration process, an optimal way of selecting its timing, frequency, duration, and flow, has yet to be found. Instead, backwashing is applied according to filter manufacturers’ recommendations based on limited on-site testing. The ultimate goal is to optimize the backwashing process and give directions to affect clean water production in large- scale plants.

%---------------------------------------------------------------------------------------------------%

\np
%---------------------------------------------------------------------------------------------------%
%% BROADER IMPACTS
%\section{Broader Impacts of the Proposed Work}
% Xiaoming
%\subsection{Broader scientific impact of the project} 
%\subsection{Student training and collaborative work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%  SECTION: Education and outreach
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Broader impacts of the proposed work}

By gaining a deeper understanding of the underlying physical processes, this investigation offers several potential benefits for managing water resources. First and foremost, a better understanding of sinkhole collapse could lead to policies to prevent these natural hazards. Second, inference of spatially-variable porous-medium properties from seepage measurements could identify locations in natural aquifers vulnerable to contamination and/or collapse. Finally, optimization of manmade filtration systems could save vast money and resource.

The above scientific impacts have been addressed throughout this proposal, and so below I expand on how this project will impact future generations of mathematical scientists through educational and outreach activities, particularly women and underrepresented minorities (URM). 
The PI is already actively involved in graduate and undergraduate research, as well as outreach to K-12 students. Further, I have successfully recruited women and underrepresented minorities in both undergraduate and graduate research. Below, I describe a range of new educational activities that are related to the proposed research.

%The fluid dynamics of bio-like propulsion is a topic that naturally captures the imagination of young students and thus serves as a wonderful opportunity in this regard.

\subsection{Undergraduate research}
The ideas in this proposal represent a rich and fascinating topic for undergraduate research, while also being approachable by the methods and tools acquired at that stage. As mentioned above, there are a number of open questions in this proposal appropriate for undergraduate research, from {\color{blue} Stuff}

At FSU, there are at least two excellent avenues to attract interested undergraduate students:  the Undergraduate Research Opportunity Program (UROP) and the IDEA grant. The UROP is a program to engage underclassmen in academic research, while the IDEA grant is a competitive program, requiring (typically advanced) students to write a proposal in which they identify a research advisor. Both programs make special efforts to recruit from underrepresented groups. I already have experience using these programs to recruit interested students as I am currently serving as the advisor for IDEA grant winner Tyler Bolles, whose proposal was ranked $\#1$ overall out of the 110 applicants.

I will use a combination of funds from the above two resources and from the current proposal to engage undergraduates in research. Since the UROP program is well-known at FSU, it is the best way to recruit young, interested students. I plan to recruit one such student who will be supported by UROP for the first summer of his/her research, and should the student wish to continue, I will fund subsequent years using the current proposal. I will also encourage the student to apply for the IDEA grant in the final year of research, as this is a prestigious award at FSU.

\subsection{Assessment for graduate and undergraduate education}

Developing strong mentoring relationships is essential to a student's intellectual development and a responsibility that the PI takes very seriously. When working with students on research (both undergraduate and graduate), I am always sure to outline the expectations of {\em both} parties -- the student and myself -- and periodically revisit the list to determine if the expectations are being met or if changes are necessary. This ensures that progress continues uninterrupted and that both parties are comfortable with their responsibilities. For the graduate seminar course, questionnaires will be provided to the students to determine how the seminar relates to their own research and their intellectual development, as well as parts of the course that were particularly beneficial and parts that could be improved. This will ensure that, once integrated into the standard curriculum, the course will maximally benefit the students' education.

\subsection{Outreach for K-12 and the general public}

I have already seized this opportunity to engage K-12 students in outreach activities. In particular, my research was the focus of an educational video created by {\bf CPALMS}, which is the State of Florida's official source for standards information and course descriptions for K-12 education. The video, which features an interview with me and animations of my research, is used to reinforce concepts from mathematics courses (grade levels 7-12), and to encourage students to consider a career in the STEM fields \cite{CPALMS}. Additionally, these videos are frequently used for the continuing education of K-12 {\em teachers}, providing them a broader perspective of mathematics that could be integrated into their teaching.

My plans for future outreach include continued collaboration with CPALMS to create a series of educational videos for both students and teachers, as well as planned activities at {\bf Math Fun Day}, which is an annual event held by the FSU Mathematics departments to engage K-12 students in the region. I have led activities at Math Fun Day in prior years and, related to the current proposal, I plan to deliver lectures and demos on porous-media flows, erosion, and sinkhole collapse.
Laboratory materials for the demo are available at the neighboring Geophysical Fluid Dynamics Institute, of which the PI is a faculty associate.

\section{Results from Prior and Current NSF Support: N/A}

%---------------------------------------------------------------------------------------------------%
%%  BIBLIOGRAPHY
\newpage
\setcounter{page}{1}
% Bibliography
\bibliographystyle{plain}
%plain, apalike, unsrt
%\bibliography{ProjBib,JCPbib}
\bibliography{ProjBib}
%---------------------------------------------------------------------------------------------------%
\end{document}

### 2019-11-09 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 % Basic editing
+\newcommand{\nick}[1]{{\color{red}#1}}
 \newcommand{\tocite}{{\color{blue}(to cite)}}
@@
 \title{Project Description --
-CAREER: Erosion, Seepage, Collapse, and Filtration in Granular and Porous Media}
+CAREER: Erosion, Seepage, Transport, and Collapse in Granular and Porous Media}
 
@@
 
-%\subsubsection{Background}
+\subsubsection{Background}
 
@@
 
+\subsubsection{Basic dynamics}
+
+ Figure \ref{fig1} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
+The figure shows 80 bodies of initially random size and position, undergoing erosion.
+This figure extends previously reported 50-body simulations to 80 bodies \cite{Quaife2018} due to a recently developed barycentric interpolation scheme \tocite, which enables closer contact between bodies and thus more bodies.
+The color shows the (normalized) vorticity field surrounding the bodies.
+Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity.
+Observe that erosion not only reduces the size of solid bodies, but also alters their shapes substantially.
+The bodies tend to become somewhat polygonal: corners develop connected by relatively flat faces.
+The number of faces does not appear to be easily predicted, but rather depends on the interaction with neighboring bodies as mediated by the Stokes flow.
+Notice that, as erosion proceeds, relatively straight channels tend to develop between the bodies.
+Certain channels that are initially larger can transmit more flow, which promotes local erosion rates and further widens these selected channels.
+In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
+The channelization process is made more evident by visualization of the velocity magnitude, as in Fig.~\ref{fig2}.
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-
- Figure \ref{fig1} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
-The figure shows 80 bodies of initially random size and position, undergoing erosion.
-This figure extends previously reported 50-body simulations to 80 bodies \cite{Quaife2018} due to a recently developed barycentric interpolation scheme (CITE), which enables closer contact between bodies and thus more bodies.
-The color shows the (normalized) vorticity field surrounding the bodies.
-Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity.
-Observe that erosion not only reduces the size of solid bodies, but also alters their shapes substantially.
-The bodies tend to become somewhat polygonal: corners develop connected by relatively flat faces.
-The number of faces does not appear to be easily predicted, but rather depends on the interaction with neighboring bodies as mediated by the Stokes flow.
-Notice that, as erosion proceeds, relatively straight channels tend to develop between the bodies.
-Certain channels that are initially larger can transmit more flow, which promotes local erosion rates and further widens these selected channels.
-In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
-The channelization process is made more evident by visualization of the velocity magnitude, as in Fig.~\ref{fig2}
 
@@
 
-\np
-\subsection{Filtration with porous membrane}
-
-Efficient wastewater management and treatment facilities are a crucial part of clean water efforts in the United States.
-Most public utilities combine water pretreatment with microfiltration systems that need frequent cleaning and upkeep to ensure high production of clean water.
-Large-scale wastewater plants utilize hollow-fiber filtration systems where filters are built by splitting each tube into thousands of millimeter-scale capped porous tubes that run along its length [1-3].
-As wastewater runs through the filter during the so-called forward filtration process, impurities accumulate and foul the membrane by occluding its pores.
-Pretreating the wastewater along with backwashing the filtering system (i.e.
-inverting the flow direction to dislodge foulants accumulated on the membranes) allows for the water production volume to be maintained [4, 5].
-These dead-end microfiltration systems are widespread thanks to their success in removing solids, colloids, and difficult-to-disinfect protozoa [6, 7]; nonetheless, most research has focused on flat-membrane filters where only the tube cross-section is porous.
-This is mostly due to the simplicity of the cross-flow filtration and its modeling, as fouling and backwashing are spatially-uniform across the membrane [8, add reference, maybe 17?].
-Our interest is in modeling hollow-fiber filtration systems to produce the maximum possible volume of clean water.
-We focus on a single hollow-fiber membrane system and scale its behavior up to match the ensemble filter.
-This will allow us to compare analytical and numerical results with experimental studies performed at the Aerosols and Water Treatment Lab with P.I.
-Professor Shankar Chellam at Texas A\&M University.
-Based on previous results [10-12], our aim is to model wastewater flow during forward filtration and foulant deposition on the membrane, which is spatially-dependent for this type of filtering system.
-In particular, although backwashing is an essential part of the filtration process, an optimal way of selecting its timing, frequency, duration, and flow, has yet to be found.
-Instead, backwashing is applied according to filter manufacturers’ recommendations based on limited on-site testing.
-The ultimate goal is to optimize the backwashing process and give directions to affect clean water production in large- scale plants.
-
 %---------------------------------------------------------------------------------------------------%
@@
 By gaining a deeper understanding of the underlying physical processes, this investigation offers several potential benefits for managing water resources.
-First and foremost, a better understanding of sinkhole collapse could lead to policies to prevent these natural hazards.
+\nick{More on erosion modifying porous medium properties etc...}
+%First and foremost, a better understanding of sinkhole collapse could lead to policies to prevent these natural hazards.
 Second, inference of spatially-variable porous-medium properties from seepage measurements could identify locations in natural aquifers vulnerable to contamination and/or collapse.
-Finally, optimization of manmade filtration systems could save vast money and resource.
 
-The above scientific impacts have been addressed throughout this proposal, and so below I expand on how this project will impact future generations of mathematical scientists through educational and outreach activities, particularly women and underrepresented minorities (URM).
-The PI is already actively involved in graduate and undergraduate research, as well as outreach to K-12 students.
-Further, I have successfully recruited women and underrepresented minorities in both undergraduate and graduate research.
-Below, I describe a range of new educational activities that are related to the proposed research.
-
-%The fluid dynamics of bio-like propulsion is a topic that naturally captures the imagination of young students and thus serves as a wonderful opportunity in this regard.
+The above scientific impacts have been addressed throughout this proposal, and so the section below expands on how this project will impact future generations of mathematical scientists through educational and outreach activities, particularly women and underrepresented minorities (URM).
+The PIs are already actively involved in graduate and undergraduate research, as well as outreach to K-12 students.
+Further, we have successfully recruited women and underrepresented minorities in both undergraduate and graduate research.
+The section below describes a range of new educational activities related to the proposed research.
 
@@
 
-Developing strong mentoring relationships is essential to a student's intellectual development and a responsibility that the PI takes very seriously.
-When working with students on research (both undergraduate and graduate), I am always sure to outline the expectations of {\em both} parties -- the student and myself -- and periodically revisit the list to determine if the expectations are being met or if changes are necessary.
+Developing strong mentoring relationships is essential to a student's intellectual development and a responsibility that the PIs takes very seriously.
+When working with students on research, whether undergraduate or graduate, we are always sure to outline the expectations of {\em both} parties -- the student and myself -- and periodically revisit the list to determine if the expectations are being met or if changes are necessary.
 This ensures that progress continues uninterrupted and that both parties are comfortable with their responsibilities.
@@
 
-I have already seized this opportunity to engage K-12 students in outreach activities.
-In particular, my research was the focus of an educational video created by {\bf CPALMS}, which is the State of Florida's official source for standards information and course descriptions for K-12 education.
-The video, which features an interview with me and animations of my research, is used to reinforce concepts from mathematics courses (grade levels 7-12), and to encourage students to consider a career in the STEM fields \cite{CPALMS}.
+The PIs have already seized the opportunity to engage K-12 students in outreach activities.
+In particular, Moore's research was the focus of an educational video created by {\bf CPALMS}, which is the State of Florida's official source for standards information and course descriptions for K-12 education.
+The video, which features an interview and animations of research, is used to reinforce concepts from mathematics courses (grade levels 7-12), and to encourage students to consider a career in the STEM fields \cite{CPALMS}.
 Additionally, these videos are frequently used for the continuing education of K-12 {\em teachers}, providing them a broader perspective of mathematics that could be integrated into their teaching.
 
-My plans for future outreach include continued collaboration with CPALMS to create a series of educational videos for both students and teachers, as well as planned activities at {\bf Math Fun Day}, which is an annual event held by the FSU Mathematics departments to engage K-12 students in the region.
-I have led activities at Math Fun Day in prior years and, related to the current proposal, I plan to deliver lectures and demos on porous-media flows, erosion, and sinkhole collapse.
+Plans for future outreach include continued collaboration with CPALMS to create a series of educational videos for both students and teachers, as well as planned activities at {\bf Math Fun Day}, which is an annual event held by the FSU Mathematics departments to engage K-12 students in the region.
+Moore has led activities at Math Fun Day in prior years and, related to the current proposal, plans to deliver lectures and demos on porous-media flows, erosion, and sinkhole collapse.
 Laboratory materials for the demo are available at the neighboring Geophysical Fluid Dynamics Institute, of which the PI is a faculty associate.

### 2019-11-10 docs/proposals/NSF/ProjDesc/ProjDesc.tex
starting to pick away at proposal

@@
 \usepackage{outlines,enumitem}
+\usepackage{wrapfig}
 %---------------------------------------------------------------------------------------------------%
@@
 % For real and imaginary, could use \Re or \Im, or \mathcal{R}, or \text{Re}
+\newcommand{\Pe}{\mathrm{Pe}}
 
@@
 \end{align}
-In the later case of chemically-induced erosion, a solute concentration field $C$ undergoes advection and diffusion:
+In the latter case of chemically-induced erosion, a solute concentration field $C$ undergoes advection and diffusion:
 \begin{align}
@@
 
+%---------------------------------------------------------------------------------------------------%
+\subsection{Transport through eroded media}
+\begin{wrapfigure}[]{r}{0.5\textwidth}
+  \includegraphics[width=0.5\textwidth]{figs/100b_t100tracer}
+  \caption{\label{fig:100tracers} A visualization of the streamlines
+  with 200 tracers passing through an eroded geometry with a porosity of
+  0.63. The tracers are initialized at the left end of the channel.}
+\end{wrapfigure}
+Transport through eroded media is a direct consequence of the pore
+structure. Qualitative properties of an eroded media, such as channels
+of high porosity can be modest in volume fraction, but still be
+responsible for a large portion of the flux~\cite{Quaife2018}. To
+increase understanding of flow through eroded media, we will simulate
+and statistically analyze transport through eroded geometries.
+
+In an eroded geometry $\Omega$, a concentration non-dimensionalized
+concentration $c$ is governed by
+\begin{align}
+  \pd{c}{t} + \uu \cdot \nabla c + \frac{1}{\Pe} \Delta c, 
+\end{align}
+where $\Pe$ is the dimensionless Peclet number. Here we assume that the
+concentration $c$ is affected by the eroded geometry, but the geometry
+is not altered further by the concentration. In the infinite Peclet
+number limit, the concentration is governed by pure advection and the
+characteristics of the concentration field are identical to the
+streamlines (Figure~\ref{fig:100tracers}).
+\begin{wrapfigure}[]{l}{0.4\textwidth}
+  \includegraphics[width=0.4\textwidth]{figs/tort_eulerian100}
+  \caption{\label{fig:100tortuosity} The tortuosity of an eroding
+  geometry. The tortuosity can be computed using two different formulas
+  (red vs.~blue marks). The red square is the tortuosity in
+  Figure~\ref{fig:100tracers}. Their is qualitative agreement between
+  our numerical simulations and a power-law model (black dashed
+  line)~\cite{mat-kha-koz2008}.}
+\end{wrapfigure}
+
+The $j^{th}$ trajectories, or characteristics, is governed by
+$\dot{ss}_j(t) = \uu(\ss_j(t))$. Once these trajectories are computed,
+using, for example, a high-order Runge-Kutta method, a statistical
+analysis be used to describe the transport. Two of the most important
+measurements are the tortuosity and the anomalous dispersion, both which
+are defined in terms of the length of the trajectories
+\begin{align}
+  \lambda_j(t) = \int_{0}^{t} \|\ss'(t')\| dt'.
+\end{align}
+Once $N_p$ trajectories are computed, the tortuosity is the
+dimensionless number
+\begin{align}
+  T = \frac{1}{d} \left(\int_{S} u_1(x_0,y_0)\lambda(y_0) dy_0\, \right)
+  \Bigg/ \left(\int_S u_1(x_0,y_0)\, dy_0 \right),
+\end{align}
+where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length,
+$u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of
+the trajectory starting at $(x_0,y_0)$ and ending at a vertical
+cross-section at the other end of the channel. Relationships between the
+tortuosity and porosity of a geometry have been developed by other
+groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and
+preliminary results indicate that such models might be appropriate for
+geometries whose porosity is increasing under the process of erosion
+(Figure~\ref{fig:100tortuosity}).
+
+While the tortuosity characterizes the amount of winding of streamlines,
+the dispersion characterizes the spreading of the trajectories.
+Dispersion can be descried using the first- and second-ensemble moments
+of the trajectories
+\begin{align}
+  \langle \lambda \rangle (t) = \frac{1}{N_p} \sum_{j=1}^{N_p}
+    \lambda_j(t), \quad \sigma_\lambda^{2}(t) = \frac{1}{N_p}
+    \sum_{j=1}^{N_p} (\lambda_j(t) - \langle \lambda \rangle(t))^2
+\end{align}
+
+%---------------------------------------------------------------------------------------------------%
 \subsection{Sinkhole modeling}

### 2019-11-11 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 \title{Project Description --
-CAREER: Erosion, Seepage, Transport, and Collapse in Granular and Porous Media}
+Erosion, Transport, Anomalous Diffusion, and Collapse in Granular and Porous Media}
 
@@
 The $j^{th}$ trajectories, or characteristics, is governed by
-$\dot{ss}_j(t) = \uu(\ss_j(t))$. Once these trajectories are computed,
+$\dot{\ss}_j(t) = \uu(\ss_j(t))$. Once these trajectories are computed,
 using, for example, a high-order Runge-Kutta method, a statistical

### 2019-11-11 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 \usepackage{outlines,enumitem}
-\usepackage{wrapfig}
+\usepackage{wrapfig, todonotes}
 %---------------------------------------------------------------------------------------------------%
@@
 Natural water resources, however, have been placed under enormous pressure by human population growth and associated activities that can comprise the natural filtration cycle, for example expansion of industry, urbanization, pollution, and climate change.
-See the USGS and the UN report on water resources for further detail on the threats to water resources [USGS?] \cite{UNwater}.
+See the UN report on water resources for further detail on the threats to water resources \cite{UNwater}.
+% Could also include USGS if needed.
 
-To take one example of particular importance to the state of Florida, the formation of sinkholes can be triggered by certain human activities such as groundwater pumping or the weight of run-off storage ponds \cite{sandhu2018fate}.
-When collapse occurs below a storage pond, the underlying reservoir of pristine groundwater can be severely contaminated, thus surrendering a natural resource of great economic and societal value.
-Clearly, a deeper understanding of the mechanisms leading to sinkhole formation, and more generally that underly earth's natural filtration system, could reap enormous benefits in predicting and mitigating such environmental disasters.
-Other applications include understanding and predicting contamination by nuclear waste and by hydraulic fracturing.
+	These filtration processes, however, rely on an understand of complex transport phenomenon in porous media.
+Further, the action of continually flowing groundwater can alter medium properties through erosive and transportive processes.
+Thus, it becomes necessary to understand the transport of tracers through complex media whose properties are changing {\em dynamically} in response to the intervening fluid flow.
 
-This proposal aims to develop a deeper understanding of the physical processes by which groundwater flow can alter properties of a porous medium.
-A recognized complexity of naturally occurring media is that their macroscopic properties, e.g.~permeability and mechanical strength, can be highly heterogeneous and anisotropic {\color{blue}(cite)}.
+	This proposal aims to develop a deeper understanding of the physical processes by which groundwater flow can alter properties of a porous medium and to characterize the associated changes in transport, e.g.~anomalous dispersion.
+A recognized complexity of naturally occurring media is that their macroscopic properties, e.g.~permeability and mechanical strength, can be highly heterogeneous and anisotropic.
 These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material.
 Potential exists for feedback between these timescales: for example the slow wearing process reaching a critical threshold beyond which catastrophic events become more likely.
-The main objective of this proposal is to gain a deeper understanding of such processes through analyzing a specific set of problems and by developing a host of new mathematical tools, ranging from analytical to computational ones.
 
@@
 Since we aim to build a quantitative model from the ground up, we will first focus on the slowest acting mechanisms, as these ultimately set the stage for the more rapid events like sinkhole collapse.
+
 In particular, we view the slow processes of erosion and dissolution as instrumental in altering porous-medium properties.
@@
 For instance, erosion can carve grains into slender shapes aligned primarily in the direction of the dominant flow, thereby creating {\em anisotropic} characteristics.
-{\color{blue} Need to include comment on dissolution changing conduit paths.}
+Likewise, chemical dissolution can carve well-defined conduit paths in karst networks which strongly alter transport properties \cite{szymczak2009wormhole}.
 
@@
 
-Only recently have these ideas been extended to low Reynolds number flows  \cite{mitchell2017generalized, Quaife2018} --- the regime applicable to porous media as well as biological applications like plaque erosion.
+Only recently have these ideas been extended to low Reynolds number flows  \cite{mitchell2017generalized, Quaife2018} --- the regime applicable to porous media.
 While the governing fluid-flow equations become linear in this regime, porous-media applications present a host of new challenges, for example:
 \begin{itemize}
-\item Porous media typically involves dense packings so that close-range effects and even nearly contacting bodies must be considered {\color{blue}(cite nearly contact papers)}.
+\item Porous media typically involves dense packings so that close-range effects and even nearly contacting bodies must be considered.
 \item The Stokes limit introduces {\em longer} range effects than the inertial limit does, thus coupling the shape evolution of {\em all} grains and conduits to a higher degree.
-\item Somewhat counterintuitively, erosion does not always act to smooth shapes but rather can create sharp features and corners.
-These features can be difficult to resolve and, further, can trigger numerical instabilities.
-Dissolution, meanwhile, can initiate a roughening transition {\color{blue} (cite)}, leading to similar numerical difficulties.
+\item Somewhat counterintuitively, erosion does not always act to smooth shapes but rather can create sharp features and corners \cite{Ristroph2012}.
+These features can be difficult to resolve and, further, can trigger numerical instabilities \cite{Quaife2018}.
+Dissolution, meanwhile, can initiate a roughening transition \cite{claudin2017dissolution}, leading to similar numerical difficulties.
 \item Additionally effects, such as sedimentation, transport, and compaction constantly work to reconfigure the medium as its constituents and boundaries degrade.
@@
 These challenges require innovative computational techniques, many of which have been developed recently \cite{Quaife2018} and many of which await resolution.
-The grand goal of achieving high-fidelity simulations of order-100 mobile bodies which undergo simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency to run large ensembles for statistical analysis, still awaits.
+An ultimate goal of this proposal is to achieve high-fidelity simulations of $O(100-1000)$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency to run large ensembles for statistical analysis.
 Fortunately, some closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton \cite{bizmark2019multiscale}.
@@
 
-While erosion and dissolution correspond to gradual changes in a medium, the example of a sinkhole represents a sudden, catastrophic event.
+While erosion and dissolution lead to gradual changes in a medium, other events like sinkhole collapse can occur suddenly and catastrophically.
 It is likely that all of the mechanisms listed above --- erosion, dissolution, transport, compaction, and gravitational collapse --- contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity.
@@
 
-	With two Mathematics PhD students, the PI has begun running preliminary simulations to model this behaviors.
+\todo[inline]{I am not sure if we will keep this much detail in the paragraphs below on the sinkhole stuff.
+It depends on how much weight we give sinkholes in the body of the proposal.
+Instead, we could replace this discussion with more depth about the tracer transport and anomalous dispersion.}
+
+	With two Mathematics PhD students, PI Moore has begun running preliminary simulations to model this behaviors.
 The simulations, which are at an early stage of development, are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
@@
 
+% Stuff we could include
 % McCurdy and Wang work
-% Multiphase stuff too
+% Multiphase work
 
-% Could emphasize dissolution of karst more too.
-% Not crazy about inverse model sentences, maybe move to end of paragraph.
-
-%I could try to work in more mathy stuff: complex dynamical system, feedback, timescales, computational methods, analytical reductions...
+% Removed this paragraph because it emphasized sinkholes too much.
+%To take one example (of particular relevance in the state of Florida) the formation of sinkholes can be triggered by certain human activities such as groundwater pumping or the weight of run-off storage ponds \cite{sandhu2018fate}.
+When collapse occurs below a storage pond, the underlying reservoir of pristine groundwater can be severely contaminated, thus surrendering a natural resource of great economic and societal value.
+Clearly, a deeper understanding of the mechanisms leading to sinkhole formation, and more generally that underly earth's natural filtration system, could reap enormous benefits in predicting and mitigating such environmental disasters.
+Other applications include understanding and predicting contamination by nuclear waste and by hydraulic fracturing.
 

### 2019-11-11 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 
- Figure \ref{fig1} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
-The figure shows 80 bodies of initially random size and position, undergoing erosion.
-This figure extends previously reported 50-body simulations to 80 bodies \cite{Quaife2018} due to a recently developed barycentric interpolation scheme \tocite, which enables closer contact between bodies and thus more bodies.
-The color shows the (normalized) vorticity field surrounding the bodies.
-Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity.
-Observe that erosion not only reduces the size of solid bodies, but also alters their shapes substantially.
-The bodies tend to become somewhat polygonal: corners develop connected by relatively flat faces.
-The number of faces does not appear to be easily predicted, but rather depends on the interaction with neighboring bodies as mediated by the Stokes flow.
-Notice that, as erosion proceeds, relatively straight channels tend to develop between the bodies.
-Certain channels that are initially larger can transmit more flow, which promotes local erosion rates and further widens these selected channels.
-In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
-The channelization process is made more evident by visualization of the velocity magnitude, as in Fig.~\ref{fig2}.
-
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
+ Figure \ref{fig1} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
+The figure shows 80 bodies of initially random size and position, undergoing erosion.
+This figure extends previously reported 50-body simulations to 80 bodies \cite{Quaife2018} due to a recently developed barycentric interpolation scheme \citep{bar2014, bar-wu-vee2015}, which enables closer contact between bodies and thus more bodies.
+The color shows the (normalized) vorticity field surrounding the bodies.
+Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity.
+Observe that erosion not only reduces the size of solid bodies, but also alters their shapes substantially.
+The bodies tend to become somewhat polygonal: corners develop connected by relatively flat faces.
+The number of faces does not appear to be easily predicted, but rather depends on the interaction with neighboring bodies as mediated by the Stokes flow.
+Notice that, as erosion proceeds, relatively straight channels tend to develop between the bodies.
+Certain channels that are initially larger can transmit more flow, which promotes local erosion rates and further widens these selected channels.
+In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
+The channelization process is made more evident by visualization of the velocity magnitude, as in Fig.~\ref{fig2}.
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
-The creation and reinforcement of channels significantly impacts the macroscopic properties of the porous medium, as the PI and collaborators have just begun to examine.
+ \vsp{5} HERE
+
+The creation and reinforcement of channels significantly impacts the macroscopic properties of the porous medium.
 Fig.~\ref{fig3} shows preliminary results on how media properties change in time.

### 2019-11-11 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM
little more stuff on transport

@@
 
- \vsp{5} HERE
+ \vsp{5}
+ \todo[inline]{Nick is here}
 
@@
 \begin{align}
-  \pd{c}{t} + \uu \cdot \nabla c + \frac{1}{\Pe} \Delta c, 
+  \pd{c}{t} + \uu \cdot \nabla c = \frac{1}{\Pe} \Delta c, 
+  \label{eqn:advectionDiffusion}
 \end{align}
@@
 \end{align}
+Then, the standard deviation $\sigma_\lambda$ characterizes the
+dispersion, and long-time behavior typically results in a power-law
+scaling $\sigma_\lambda \sim t^{\alpha}$. The power $\alpha$, which
+quantifies the long-time spreading, is $1$ in a ballistic regime which
+occurs at early times when the trajectories have not explored much of
+the porous geometry. However, once the trajectories have traversed a few
+grains, dispersion in porous media is often super-dispersive with
+$\alpha \in (0.5,1)$~\cite{}. In Figure~\ref{fig:100dispersion}, we
+investigate spreading at several different porosities of a porous
+geometry that is initialized with 100 grains.
+
+\begin{wrapfigure}[]{r}{0.5\textwidth}
+  \includegraphics[width=0.5\textwidth]{figs/100b_second_moment_long_ref}
+  \caption{\label{fig:100dispersion} The particle spreading,
+  characterized with the standard deviation $\sigma_\lambda(t)$ at 6
+  different porosities. At early times, the line of slope 1 (black
+  curve) indicates a ballistic motion. Then, at later times, the
+  dispersion becomes super-dispersive at a rate indicated by the slope
+  of the black dashed-dotted line.}
+\end{wrapfigure}
+
+We propose to extend our preliminary results for pure advection so that
+concentrations with finite Peclet numbers can be investigated.
+Numerical methods to solve the advection-diffusion
+equation~\eqref{eqn:advectionDiffusion} in a complex geometry poses
+several challenges that we will address.  We will start by splitting the
+advection and diffusion equations using a Strang splitting~\cite{}.
+Numerical solutions of the advection equation will be formed with a
+semi-Lagrangian method. These methods have the advantage that they ...?
+The forced diffusion equation is more challenging to solve in a complex
+geometry with an integral equation formulation. One particular challenge
+is extending the forcing function from the complex geometry and into a
+regular geometry, such as a square, so that a high-order volume integral
+or Fourier method can be applied. Recently, groups have used radial
+basis functions to form a sufficiently smooth extension~\cite{}
+\todo[inline]{A-K, MC}. Alternatively, others have used the space-time
+heat kernel~\cite{}, but this requires storing an entire time history of
+the solution. We propose to develop a new method that uses the Laplace
+transform.
 

### 2019-11-11 docs/proposals/NSF/ProjDesc/ProjDesc.tex
more additions

@@
- \documentclass[12pt]{article}
+\documentclass[11pt]{article}
 
@@
 %% PACKAGES
-\usepackage{fullpage}
+%\usepackage{fullpage}
 %\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
@@
 \usepackage{wrapfig, todonotes}
+\usepackage{titlesec}
+\usepackage{fancyhdr}
 %---------------------------------------------------------------------------------------------------%
+
+\addtolength{\oddsidemargin}{-0.75in}
+\addtolength{\evensidemargin}{-0.75in}
+\addtolength{\textwidth}{1.5in}
+\addtolength{\topmargin}{-0.75in}
+\addtolength{\textheight}{1.5in}
+% For 11pt size
+
+\titleformat*{\section}{\large\bfseries}
+\titleformat*{\subsection}{\normalsize\bfseries}
+
+\pagestyle{fancy}
+\lhead{\footnotesize Moore and Quaife}
+\chead{\footnotesize Erosion, Transport, and  Dispersion in Granular and
+Porous Media}
+\rhead{\footnotesize \thepage}
+\cfoot{}
 
@@
 \begin{document}
-\title{Project Description --
-Erosion, Transport, Anomalous Diffusion, and Collapse in Granular and Porous Media}
+\begin{center}
+{\large \bf Erosion, Transport, and Dispersion in Granular
+and Porous Media} 
+\end{center}
+%\title{Project Description --
+%Erosion, Transport, Anomalous Diffusion, and Collapse in Granular and Porous Media}
 
@@
 %\author{}
-\date{}
-\maketitle
+%\date{}
+%\maketitle
 %---------------------------------------------------------------------------------------------------%
@@
 
-We propose to extend our preliminary results for pure advection so that
-concentrations with finite Peclet numbers can be investigated.
-Numerical methods to solve the advection-diffusion
-equation~\eqref{eqn:advectionDiffusion} in a complex geometry poses
-several challenges that we will address.  We will start by splitting the
-advection and diffusion equations using a Strang splitting~\cite{}.
-Numerical solutions of the advection equation will be formed with a
-semi-Lagrangian method. These methods have the advantage that they ...?
-The forced diffusion equation is more challenging to solve in a complex
-geometry with an integral equation formulation. One particular challenge
-is extending the forcing function from the complex geometry and into a
+We propose to extend our preliminary results by considering
+concentrations with finite Peclet numbers. Numerical methods to solve
+the advection-diffusion equation~\eqref{eqn:advectionDiffusion} in a
+complex geometry poses several challenges that we will address.  We will
+start by splitting the advection and diffusion equations with a Strang
+splitting method~\cite{str1968}.  Numerical solutions of the advection
+equation will be formed with a semi-Lagrangian method~\cite{rob1981} so
+that it can be solved on an Eulerian grid without a restrictive CFL
+condition. PI Quaife has experience with using semi-Lagrangian
+methods for another type of complex viscous flow~\cite{kab-qua-bir2017}.
+The diffusion equation is more challenging to solve in a complex
+geometry with an integral equation formulation.  One approach is to use
+the space-time heat kernel~\cite{}, but this requires storing an entire
+time history of the solution.  Alternatively, the heat equation can be
+discretized in time and the resulting Yukawa equation is solved at each
+time step~\cite{kro-qua2010}. A particular challenge of this method is
+extending the forcing function from the complex geometry and into a
 regular geometry, such as a square, so that a high-order volume integral
 or Fourier method can be applied.  Recently, groups have used radial
-basis functions to form a sufficiently smooth extension~\cite{}
-\todo[inline]{A-K, MC}. Alternatively, others have used the space-time
-heat kernel~\cite{}, but this requires storing an entire time history of
-the solution. We propose to develop a new method that uses the Laplace
-transform.
+basis functions to form a sufficiently smooth
+extension~\cite{fry-kro-tor2019, fry-leh-tor2019}.
+
+We propose to develop a new method that uses the Laplace transform.
+Upon applying a Strang splitting, the resulting diffusion equation is
+\begin{alignat}{3}
+  \pd{c}{t} &= \frac{1}{\Pe} \Delta c, \quad &&\xx \in \Omega, \: t>0, \\
+  \pd{c}{\nn} &= 0, &&\xx \in \partial\Omega, \: t>0, \\
+  c(\xx,0) &= c_0(\xx), &&\xx \in \Omega.
+\end{alignat}
+Then, the Laplace transform, $C(\xx,s) = \mathcal{L}[c](\xx,t)$,
+satisfies
+\begin{align}
+  sC(\xx,s) - \frac{1}{\Pe} = c_0(\xx).
+\end{align}
+This PDE will be solved with high-order accuracy and efficiently by
+using fast-multipole-accelerated integral equation methods of the
+Beltrami equation~\cite{kro-qua2011}, and the concentration will be
+recovered with a inverese Laplace transform~\cite{jos-war2006}.
 

### 2019-11-11 docs/proposals/NSF/ProjDesc/ProjDesc.tex
working on proposal

@@
 \usepackage{fancyhdr}
+\usepackage{subcaption}
 %---------------------------------------------------------------------------------------------------%
@@
 and Porous Media} 
+\\
+M.J.N.~Moore and Bryan D.~Quaife
 \end{center}
@@
 \subsection{Transport through eroded media}
-\begin{wrapfigure}[]{r}{0.5\textwidth}
-  \includegraphics[width=0.5\textwidth]{figs/100b_t100tracer}
+\begin{wrapfigure}[]{r}{0.3\textwidth}
+  \includegraphics[width=0.3\textwidth]{figs/100b_t100tracer}
   \caption{\label{fig:100tracers} A visualization of the streamlines
@@
 geometry that is initialized with 100 grains.
-
 \begin{wrapfigure}[]{r}{0.5\textwidth}
@@
 \end{wrapfigure}
+
+The rate of dispersion is known to be directly related to the pore size
+distribution~\cite{dea-qua-bir-jua2018}. Therefore, there is a need to
+understand how erosion affects the pore size distribution. In
+preliminary, we define pore sizes between grains that share an edge of a
+Delanuay triangulation with vertices at the grain centers
+(Figure~\ref{fig:triangluation}). In Figure~\ref{fig:poreStats}, we plot
+the mean and variance of the pore sizes as a function of porosity.
+
+\begin{figure}
+\begin{subfigure}[b]{0.33\textwidth}
+  \includegraphics*[height=0.8\linewidth]{figs/triangulation_100b100.pdf}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.33\textwidth}
+  \includegraphics*[height = 0.8\linewidth]{figs/gap_mean}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.33\textwidth}
+  \includegraphics*[height=0.8\linewidth]{figs/gap_variance}
+\caption{}
+\end{subfigure}
+  \caption{\label{fig:Eroding100gap_mean_var} (a) The pore sizes are
+  defined in terms of a Delanuay triangulation. The effect of erosion on
+  (b) the mean and (c) the variance of the pore sizes. The geometry
+  initially contains 100 eroding bodies.}
+\end{figure}
 
@@
 \begin{align}
-  sC(\xx,s) - \frac{1}{\Pe} = c_0(\xx).
+  sC(\xx,s) - \frac{1}{\Pe}\Delta C(\xx,s) = c_0(\xx), 
+    \quad \xx \in \Omega
 \end{align}
 This PDE will be solved with high-order accuracy and efficiently by
-using fast-multipole-accelerated integral equation methods of the
-Beltrami equation~\cite{kro-qua2011}, and the concentration will be
-recovered with a inverese Laplace transform~\cite{jos-war2006}.
+using fast-multipole-accelerated integral equation methods of the Yukawa
+equation~\cite{kro-qua2011}, and the concentration will be recovered
+with an inverse Laplace transform~\cite{jos-war2006}.
 

### 2019-11-12 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 
-% Removed this paragraph because it emphasized sinkholes too much.
+% REMOVED this paragraph because it emphasized sinkholes too much.
 %To take one example (of particular relevance in the state of Florida) the formation of sinkholes can be triggered by certain human activities such as groundwater pumping or the weight of run-off storage ponds \cite{sandhu2018fate}.
@@
 \subsection{Transport through eroded media}
+
 \begin{wrapfigure}[]{r}{0.3\textwidth}
@@
 \end{wrapfigure}
+
 Transport through eroded media is a direct consequence of the pore
@@
 
-%---------------------------------------------------------------------------------------------------%
-
 \np
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%---------------------------------------------------------------------------------------------------%
 %%%%  SECTION: Education and outreach
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%---------------------------------------------------------------------------------------------------%
 \section{Broader impacts of the proposed work}
 
-By gaining a deeper understanding of the underlying physical processes, this investigation offers several potential benefits for managing water resources.
-\nick{More on erosion modifying porous medium properties etc...}
-%First and foremost, a better understanding of sinkhole collapse could lead to policies to prevent these natural hazards.
-Second, inference of spatially-variable porous-medium properties from seepage measurements could identify locations in natural aquifers vulnerable to contamination and/or collapse.
+	This research proposed here could lead to a range of societal benefits, including better management of water resources, accurate prediction of contaminant transport, and an understanding of the long-term effects of human activities, such as hydraulic fracturing or groundwater pumping, on porous media and water resources.
+In such scenarios, the slow timescales of mechanical and chemical erosion are coupled to the faster timescales of human-induced changes and/or gravitational collapse.
+Currently, the relationship between these scales is poorly understood.
+The high-fidelity, efficient computational methods proposed here will enable a deeper understanding of these processes, which is the first step towards developing effective strategies for managing water resources and mitigating catastrophic events such as contamination or structural collapse.
+For example, the insights gained here could potentially help identify locations in natural aquifers vulnerable to contamination and/or collapse.
 
-The above scientific impacts have been addressed throughout this proposal, and so the section below expands on how this project will impact future generations of mathematical scientists through educational and outreach activities, particularly women and underrepresented minorities (URM).
-The PIs are already actively involved in graduate and undergraduate research, as well as outreach to K-12 students.
-Further, we have successfully recruited women and underrepresented minorities in both undergraduate and graduate research.
-The section below describes a range of new educational activities related to the proposed research.
+	In addition to these societal impacts, the work proposed here will spur the training of mathematicians and computational scientists in fundamentally cross-disciplinary research of great societal importance.
+Further, the PIs will engage in educational and outreach activities to impact future generations of mathematical scientists, with particular focus on women and underrepresented minorities (URM).
+Both PIs are already actively involved in graduate and undergraduate research, as well as outreach to K-12 students.
+Further, we have successfully recruited women and underrepresented minorities in undergraduate, graduate, and postdoctoral research.
+
+\subsection{Graduate research}
+
+	An important benefit of the research proposed here is the potential to immerse graduate students in fundamentally {\em cross-disciplinary} research.
+This proposal involves a confluence of disciplines, most centrally computational mathematics, but also geophysics, reduced-physical modeling, hydrology, and environmental science.
+Exposure to a range of disciplines is, in the view of the PIs, an invaluable opportunity for young scientists.
+
+	Naturally, the research proposed here will form the foundation for the PhD dissertations of the graduate students involved.
+Beyond this, the students will engage in publishing articles in peer-reviewed journals of high quality and attending national and international conferences at which they will contribute presentations on their work.
+The PIs will closely mentor the graduate students to ensure their continued development, not only intellectually, but also in the `soft' skills of communication, promotion, and networking.
+Having both PIs Moore and Quaife involved in the training of each graduate student is especially valuable for offering multiple perspectives on these issues.
+The PIs will make special efforts to recruit women and underrepresented minorities as the graduate students funded by this project.
+PI Moore has already had success recruiting women in these roles, as the first graduate student to receive her PhD under Moore's advising was female (Karina Khazmutdinova, 2016).
 
 \subsection{Undergraduate research}
-The ideas in this proposal represent a rich and fascinating topic for undergraduate research, while also being approachable by the methods and tools acquired at that stage.
-As mentioned above, there are a number of open questions in this proposal appropriate for undergraduate research, from {\color{blue} Stuff}
+
+	Regarding undergraduate research, the ideas in this proposal represent a rich and fascinating topic for undergraduate students, while also being approachable these students.
+In particular, we aim to recruit at least one undergraduate student to perform laboratory experiments at the Geophysical Fluid Dynamics Institute (GFDI).
+As mentioned above, GFDI offers state-of-the-art laboratory facilities, with an already-functioning sinkhole experiment.
+The student will perform controlled experiments using natural and artificial porous media (e.g.~sand and micro-glass beads respectively) to precisely characterize the parameter regime leading to gravitational collapse.
+Parallel experiments will be conducted with erodible (bentonite clay) or dissolvable  (sucrose solids) fragments materials, which will represent the porous medium.
+These experiments will be used to guide, calibrate, and validate the computational advances.
+These undergraduate students will work closely with the graduate students to ensure that theory and experiments advance in close cooperation, with constant feedback between the two.
+
+	PI Moore already has experience successfully training undergraduate students in combined laboratory and theoretical work.
+A recent example is undergraduate student Tyler Bolles who completed an honors thesis with PI Moore at FSU on laboratory and theory of water waves.
+This work resulted in one {\em peer-reviewed} publication already \cite{Bolles2019}, with a second to be submitted soon.
 
@@
 Both programs make special efforts to recruit from underrepresented groups.
-I already have experience using these programs to recruit interested students as I am currently serving as the advisor for IDEA grant winner Tyler Bolles, whose proposal was ranked $\#1$ overall out of the 110 applicants.
-
-I will use a combination of funds from the above two resources and from the current proposal to engage undergraduates in research.
-Since the UROP program is well-known at FSU, it is the best way to recruit young, interested students.
-I plan to recruit one such student who will be supported by UROP for the first summer of his/her research, and should the student wish to continue, I will fund subsequent years using the current proposal.
-I will also encourage the student to apply for the IDEA grant in the final year of research, as this is a prestigious award at FSU.
-
-\subsection{Assessment for graduate and undergraduate education}
-
-Developing strong mentoring relationships is essential to a student's intellectual development and a responsibility that the PIs takes very seriously.
-When working with students on research, whether undergraduate or graduate, we are always sure to outline the expectations of {\em both} parties -- the student and myself -- and periodically revisit the list to determine if the expectations are being met or if changes are necessary.
-This ensures that progress continues uninterrupted and that both parties are comfortable with their responsibilities.
-For the graduate seminar course, questionnaires will be provided to the students to determine how the seminar relates to their own research and their intellectual development, as well as parts of the course that were particularly beneficial and parts that could be improved.
-This will ensure that, once integrated into the standard curriculum, the course will maximally benefit the students' education.
+PIs Moore and Quaife already have experience using these programs to recruit interested students.
 
@@
 Plans for future outreach include continued collaboration with CPALMS to create a series of educational videos for both students and teachers, as well as planned activities at {\bf Math Fun Day}, which is an annual event held by the FSU Mathematics departments to engage K-12 students in the region.
-Moore has led activities at Math Fun Day in prior years and, related to the current proposal, plans to deliver lectures and demos on porous-media flows, erosion, and sinkhole collapse.
-Laboratory materials for the demo are available at the neighboring Geophysical Fluid Dynamics Institute, of which the PI is a faculty associate.
+PI Moore has led activities at Math Fun Day in prior years and, related to the current proposal, plans to deliver lectures and demos on porous-media flows, erosion, and sinkhole collapse.
+Laboratory materials for the demo are available at GFDI.
+
+%\subsection{Assessment for graduate and undergraduate education}
+%Developing strong mentoring relationships is essential to a student's intellectual development and a responsibility that the PIs takes very seriously.
+When working with students on research, whether undergraduate or graduate, we are always sure to outline the expectations of {\em both} parties -- the student and myself -- and periodically revisit the list to determine if the expectations are being met or if changes are necessary.
+This ensures that progress continues uninterrupted and that both parties are comfortable with their responsibilities.
+For the graduate seminar course, questionnaires will be provided to the students to determine how the seminar relates to their own research and their intellectual development, as well as parts of the course that were particularly beneficial and parts that could be improved.
+This will ensure that, once integrated into the standard curriculum, the course will maximally benefit the students' education.
 

### 2019-11-12 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 \newcommand{\nick}[1]{{\color{red}#1}}
-\newcommand{\tocite}{{\color{blue}(to cite)}}
+\newcommand{\tocite}{{\color{blue}(to cite) }}
 \newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
@@
 
-	These filtration processes, however, rely on an understand of complex transport phenomenon in porous media.
+	These filtration processes, however, rely on an understanding of complex transport phenomenon in porous media.
 Further, the action of continually flowing groundwater can alter medium properties through erosive and transportive processes.
@@
 
-	This proposal aims to develop a deeper understanding of the physical processes by which groundwater flow can alter properties of a porous medium and to characterize the associated changes in transport, e.g.~anomalous dispersion.
+	This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow can alter porous-media properties and to characterize the associated changes in transport within the evolving medium, e.g.~anomalous dispersion.
 A recognized complexity of naturally occurring media is that their macroscopic properties, e.g.~permeability and mechanical strength, can be highly heterogeneous and anisotropic.
@@
 It is likely that all of the mechanisms listed above --- erosion, dissolution, transport, compaction, and gravitational collapse --- contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity.
-Sinkhole formation has been explored with preliminary experiments run at the Geophysical Fluid Dynamics Institute at Florida State University \cite{tao2014experimental}.
+Sinkhole formation has been explored with preliminary experiments run at the Geophysical Fluid Dynamics Institute (GFDI) at Florida State University \cite{tao2014experimental}.
 These scaled-down experiments offer the ability to probe various mechanisms behind sinkhole formation, for example a difference in hydraulic head between the confined and unconfined aquifers.
+An ultimate goal of this project is to merge these two lines of inquiry, on erosive processes and sinkhole formation, to gain a deeper understanding the influence of mechanically or chemically induced erosion on gravitational collapse.
+Ultimately, we envision the high-fidelity erosion simulations to inform coarse-grained models for transport and dynamics of macroscopic medium properties.
+These parameterized models could then be combined with well-developed multi-phase models \tocite to be used for the quantitative description and prediction of sinkhole collapse.
 
-\todo[inline]{I am not sure if we will keep this much detail in the paragraphs below on the sinkhole stuff.
-It depends on how much weight we give sinkholes in the body of the proposal.
-Instead, we could replace this discussion with more depth about the tracer transport and anomalous dispersion.}
+	In the following, we first describe the governing equations underlying the proposed work, then detail the computational challenges for simulation erosion, characterizing transport, and potentially modeling gravitational interactions.
 
-	With two Mathematics PhD students, PI Moore has begun running preliminary simulations to model this behaviors.
-The simulations, which are at an early stage of development, are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
-They utilize a homogenized description of the flow field, e.g.~the Darcy or Brinkman equations.
-These simulations incorporate the physical effects of:
-\begin{itemize}
-\item Transport of grains due to seepage force from the surrounding fluid flow.
-\item Gravitational sedimentation of grains.
-\item Feedback of grain-distribution onto permeability field.
-\item Contact and cohesive forces between grains.
-\end{itemize}
-Preliminary investigation suggests that this last mechanisms of cohesion is essential to model sinkhole collapse in the system, and the simulations await careful calibration against experimental data.
-
-The simulations do not yet incorporate the effects of erosion and dissolution.
-A grand goal of this proposal would be to merge these two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short term events, such as sinkhole collapse, and long-term changes in the medium.
-Such a framework must include the effects of erosion, dissolution, transport, sedimentation, compaction, cohesive forces, and mechanical collapse.
-The greatest challenge faced is the disparate temporal and spatial scales that must be considered.
-Our strategy is to use the high-fidelity erosion and dissolution simulations to develop reduced models (ala mean-field theory) that would be incorporated into simulations.
-
-% Stuff we could include
-% McCurdy and Wang work
-% Multiphase work
-
-% REMOVED this paragraph because it emphasized sinkholes too much.
-%To take one example (of particular relevance in the state of Florida) the formation of sinkholes can be triggered by certain human activities such as groundwater pumping or the weight of run-off storage ponds \cite{sandhu2018fate}.
-When collapse occurs below a storage pond, the underlying reservoir of pristine groundwater can be severely contaminated, thus surrendering a natural resource of great economic and societal value.
-Clearly, a deeper understanding of the mechanisms leading to sinkhole formation, and more generally that underly earth's natural filtration system, could reap enormous benefits in predicting and mitigating such environmental disasters.
-Other applications include understanding and predicting contamination by nuclear waste and by hydraulic fracturing.
+% Other stuff that could be included: McCurdy and Wang work, Multiphase work
 
@@
 
+\vsp{3}
+
+	With two Mathematics PhD students, PI Moore has begun running preliminary simulations to model this behaviors.
+The simulations, which are at an early stage of development, are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
+They utilize a homogenized description of the flow field, e.g.~the Darcy or Brinkman equations.
+These simulations incorporate the physical effects of:
+\begin{itemize}
+\item Transport of grains due to seepage force from the surrounding fluid flow.
+\item Gravitational sedimentation of grains.
+\item Feedback of grain-distribution onto permeability field.
+\item Contact and cohesive forces between grains.
+\end{itemize}
+Preliminary investigation suggests that this last mechanisms of cohesion is essential to model sinkhole collapse in the system, and the simulations await careful calibration against experimental data.
+
+The simulations do not yet incorporate the effects of erosion and dissolution.
+A grand goal of this proposal would be to merge these two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short term events, such as sinkhole collapse, and long-term changes in the medium.
+Such a framework must include the effects of erosion, dissolution, transport, sedimentation, compaction, cohesive forces, and mechanical collapse.
+The greatest challenge faced is the disparate temporal and spatial scales that must be considered.
+Our strategy is to use the high-fidelity erosion and dissolution simulations to develop reduced models (ala mean-field theory) that would be incorporated into simulations.
+
 \np

### 2019-11-12 docs/proposals/NSF/ProjDesc/ProjDesc.tex
worked on transport

--- 2019-11-11 docs/proposals/NSF/ProjDesc/ProjDesc.tex
@@
 geometry that is initialized with 100 grains.
-\begin{wrapfigure}[]{r}{0.5\textwidth}
-  \includegraphics[width=0.5\textwidth]{figs/100b_second_moment_long_ref}
+\begin{wrapfigure}[]{r}{0.4\textwidth}
+  \includegraphics[width=0.4\textwidth]{figs/100b_second_moment_long_ref}
   \caption{\label{fig:100dispersion} The particle spreading,
@@
 (Figure~\ref{fig:triangluation}). In Figure~\ref{fig:poreStats}, we plot
-the mean and variance of the pore sizes as a function of porosity.
+the mean and variance of the pore sizes as a function of porosity. To
+better understand how erosion affects the anomalous dispersion, we
+propose to investigate how the pores grow with erosion. We will start
+with the notion of a {\em porelet} which is an individual
+Hagen-Poiseuille flow in each of the individual
+pores~\cite{dea-qua-bib-jua2018}. By computing the strength of the
+individual Hagen-Poiseuille flows, the shear rate can be computed, and
+thus the rate of erosion can be computed.
 

### 2019-11-12 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

--- 2019-11-12 docs/proposals/NSF/ProjDesc/ProjDesc.tex
@@
 
-	These filtration processes, however, rely on an understanding of complex transport phenomenon in porous media.
+	An understanding of these filtration and contamination processes relies on the complex phenomenon of transport in porous media.
 Further, the action of continually flowing groundwater can alter medium properties through erosive and transportive processes.
-Thus, it becomes necessary to understand the transport of tracers through complex media whose properties are changing {\em dynamically} in response to the intervening fluid flow.
+Thus, it becomes necessary to understand transport through complex media whose properties change {\em dynamically} in response to the intervening fluid flow.
+Such effects become most prominent during rapid events, like the gravitational collapse of a sinkhole, during which medium properties can change suddenly and dramatically.
+Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties.
 
-	This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow can alter porous-media properties and to characterize the associated changes in transport within the evolving medium, e.g.~anomalous dispersion.
-A recognized complexity of naturally occurring media is that their macroscopic properties, e.g.~permeability and mechanical strength, can be highly heterogeneous and anisotropic.
+	This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow can alter porous-media properties and to characterize the associated changes in transport within the evolving medium, for example the anomalous dispersion of tracers.
+A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength.
 These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material.
@@
 
-In particular, we view the slow processes of erosion and dissolution as instrumental in altering porous-medium properties.
-First, by deteriorating solid material, erosion alters the size distribution of grains.
-This modified distribution can in turn affect transport by enabling smaller grains to be sieved through networks of larger ones.
+In particular, we view the accumulated effects of slow processes like erosion and dissolution as instrumental in altering porous-medium properties.
+First, by deteriorating solid material, erosion alters the size distribution of grains, enabling smaller grains to be sieved through networks of larger ones.
 A second and more subtle way that erosion can alter medium properties is by changing the {\em shape} distribution of grains.
@@
 
-Only recently have these ideas been extended to low Reynolds number flows  \cite{mitchell2017generalized, Quaife2018} --- the regime applicable to porous media.
+Only recently have these ideas been extended to the low-Reynolds-number regime that is applicable to porous media  \cite{mitchell2017generalized, Quaife2018}.
 While the governing fluid-flow equations become linear in this regime, porous-media applications present a host of new challenges, for example:
@@
 \end{itemize}
-These challenges require innovative computational techniques, many of which have been developed recently \cite{Quaife2018} and many of which await resolution.
-An ultimate goal of this proposal is to achieve high-fidelity simulations of $O(100-1000)$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency to run large ensembles for statistical analysis.
+These challenges require innovative computational techniques, some of which have been developed recently \cite{Quaife2018} and some of which await resolution.
+An ultimate goal of this proposal is to achieve high-fidelity simulations of $O(100-1000)$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.
 Fortunately, some closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton \cite{bizmark2019multiscale}.
-The experiments offer a wonderful opportunity to guide, calibrate, and validate theoretical developments.
+The experiments offer a wonderful opportunity to guide, calibrate, and validate theoretical developments, as do proposed experiments at the Geophysical Fluid Dynamics Institute.
 
 While erosion and dissolution lead to gradual changes in a medium, other events like sinkhole collapse can occur suddenly and catastrophically.
-It is likely that all of the mechanisms listed above --- erosion, dissolution, transport, compaction, and gravitational collapse --- contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity.
+Most likely, all of the mechanisms listed above --- erosion, dissolution, transport, compaction, and gravitational collapse --- contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity.
 Sinkhole formation has been explored with preliminary experiments run at the Geophysical Fluid Dynamics Institute (GFDI) at Florida State University \cite{tao2014experimental}.
 These scaled-down experiments offer the ability to probe various mechanisms behind sinkhole formation, for example a difference in hydraulic head between the confined and unconfined aquifers.
-An ultimate goal of this project is to merge these two lines of inquiry, on erosive processes and sinkhole formation, to gain a deeper understanding the influence of mechanically or chemically induced erosion on gravitational collapse.
-Ultimately, we envision the high-fidelity erosion simulations to inform coarse-grained models for transport and dynamics of macroscopic medium properties.
-These parameterized models could then be combined with well-developed multi-phase models \tocite to be used for the quantitative description and prediction of sinkhole collapse.
+An ultimate goal of this project is to merge these two lines of inquiry to gain a deeper understanding the influence of mechanically or chemically induced erosion on gravitational collapse.
+Ultimately, we envision the high-fidelity erosion simulations to inform coarse-grained models for: (i) transport and dispersion; and (ii) dynamic evolution of macroscopic medium properties.
+These parameterized models could then be combined with well-developed multi-phase models \cite{Imma2019, eastham2019multiphase} to be used for the quantitative description and prediction of sinkhole collapse.
 
 	In the following, we first describe the governing equations underlying the proposed work, then detail the computational challenges for simulation erosion, characterizing transport, and potentially modeling gravitational interactions.
-
-% Other stuff that could be included: McCurdy and Wang work, Multiphase work
 

### 2019-11-12 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 Thus, it becomes necessary to understand transport through complex media whose properties change {\em dynamically} in response to the intervening fluid flow.
-Such effects become most prominent during rapid events, like the gravitational collapse of a sinkhole, during which medium properties can change suddenly and dramatically.
+Such effects become most prominent during rapid events, like the gravitational collapse of a sinkhole \cite{sandhu2018fate}, during which medium properties can change suddenly and dramatically.
 Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties.
@@
 	This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow can alter porous-media properties and to characterize the associated changes in transport within the evolving medium, for example the anomalous dispersion of tracers.
-A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength.
+A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength \cite{lin2018randomization}.
 These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material.

### 2019-11-12 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM<

@@
 
-	In the following, we first describe the governing equations underlying the proposed work, then detail the computational challenges for simulation erosion, characterizing transport, and potentially modeling gravitational interactions.
+	In the following, we first describe the underlying governing equations, then detail the computational challenges and proposed work on simulating fluid-mechanical erosion, characterizing transport and dispersion, and modeling gravitational interactions.
 
@@
 where $\uu$ is the velocity field, $p$ the pressure field, and $\mu$ the fluid viscosity.
-This microscopic description is needed to model the shape evolution of individual grains from shear-induced erosion.
+
+	The above microscopic description is required for the shape evolution of individual grains due to fine-scale erosive effects, either mechanical or chemical.
 The description, however, becomes impractical when attempting to model seepage in very large porous systems where the microscopic geometry can be exceedingly complex.
-Instead, it becomes necessary to homogenize over microscopic details to arrive at an approximate description.
+Instead, one must homogenize over microscopic details to arrive at an approximate description.
 Leading-order homogenization produces the well-known Darcy system
@@
 
+While the most immediate proposed work on computational methods to simulate erosion will utilize \eqref{StokesEq}, the later stages of this project will also incorporate \eqref{DarcyEq}, or closely related variants known as multiphase models \cite{Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
+These models will rely on statistical analysis of the data produced by the high-fidelity erosion simulations in order to parameterize the effects of erosion, leading to deterministic or stochastic reduced-order models for porous-medium evolution and erosion, combined with other external effects such as gravitationally-induced dynamics.
+
 \subsection{Mechanical and chemical erosion of a porous medium}
 
-\subsubsection{Background}
+%\subsubsection{Background}
 
@@
 \end{equation}
-Both processes have been investigated by the PI and collaborators in the context of single bodies in high Reynolds-number flows \cite{Ristroph2012, MoorePOF2013, HuangJFM2015, MooreCPAM2017}.
-In the low-Reynolds regime of porous-media flow, numerical methods have been developed by the PI and collaborators to simulate shear-induced erosion \cite{Quaife2018}.
+Both processes have been investigated by the PIs and collaborators in the context of single bodies in high Reynolds-number flows \cite{Ristroph2012, MoorePOF2013, HuangJFM2015, MooreCPAM2017}.
+In the low-Reynolds regime of porous-media flow, numerical methods have been developed by the PIs to simulate shear-induced erosion \cite{Quaife2018}.
 These simulations combine highly accurate boundary integral methods with stable interface evolution techniques.
 The boundary integral solver is accelerated by the fast multipole method \cite{gre-rok1987, gre-gre-may1992} to achieve optimal $O(N)$ complexity.
-Meanwhile, the so-called {\thL} method is used for interface evolution to prevent distortion and tangling of the interface meshes.
+Meanwhile, the so-called {\thL} method is used for interface evolution to prevent distortion and tangling of the interface meshes \cite{hou1994removing, MoorePOF2013, Quaife2018}.
 %A near-term goal is to adapt these methods to handle the case of chemically-induced dissolution.
 
-\subsubsection{Basic dynamics}
+%\subsubsection{Basic dynamics}
 
@@
 
- \vsp{5}
- \todo[inline]{Nick is here}
+%\subsubsection{Evolution of macroscopic properties}
 
 The creation and reinforcement of channels significantly impacts the macroscopic properties of the porous medium.
-Fig.~\ref{fig3} shows preliminary results on how media properties change in time.
+Fig.~\ref{fig3} shows new, preliminary results on how media properties change in time.
 First, the left-most plot shows the rate at which the area fraction decreases as the bodies erode.
@@
 
-Lastly, the right-most plot of Fig.~\ref{fig3} shows the anisotropy, which is calculated as the ratio of the vertical resistivity to the horizontal resistivity.
+Lastly, the right-most plot of Fig.~\ref{fig3} shows the anisotropy, which is calculated as the ratio of the vertical resistivity to the horizontal resistivity, see Eq.~\eqref{DarcyEq}.
 The vertical resistivity is computed by rotating the configuration of bodies by 90 degrees.
@@
 
+%\subsubsection{Immediate goals of proposed work}
+
+\todo[inline]{Bryan, could you add some details and references to these paragraphs below?}
+
 An immediate goal of the proposed work is extend the range of physical effects captured in these simulations.
@@
 For this extension, contact forces between bodies must be included.
-Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from straightforward in practice, with several competing possible strategies that are a topic of current research  {\color{blue} cite}.
+Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research  {\color{blue} cite}.
 We plan to implement contact forces with {\color{blue} stuff}.
-This goal will form the PhD dissertation of a graduate student who will be supervised by myself and Prof.
-Bryan Quaife (FSU Scientific Computing).
+This goal will form the PhD dissertation of a graduate student who will be supervised by myself and Prof.~Bryan Quaife (FSU Scientific Computing).
 
@@
 %---------------------------------------------------------------------------------------------------%
-\subsection{Sinkhole modeling}
+% SINKHOLES AND MOBILE BODIES
+%---------------------------------------------------------------------------------------------------%
 
-Sinkhole background stuff...
+\subsection{Mobile grain simulations and sinkhole formation}
 
-Researchers at FSU's Geophysical Fluid Dynamics Institute have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments {\color{blue} cite}.
+% PREVIOUS PARAGRAPH
+%Near-term plans are to include flow transport and gravitational sedimentation of the particles.
+For this extension, contact forces between bodies must be included.
+Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research  {\color{blue} cite}.
+We plan to implement contact forces with {\color{blue} stuff}.
+This goal will form the PhD dissertation of a graduate student who will be supervised by myself and Prof.~Bryan Quaife (FSU Scientific Computing).
+
+	One central goal of this proposal is to enable the free motion of grains during the erosion processes.
+As mentioned above, this goal requires resolving contact forces between bodies, as well as the incorporation of the external buoyancy forces.
+Once this goal is achieved, it will be possible to simulate a complex porous-medium of arbitrarily sized and shaped grains undergoing the simultaneous action of mechanical-or-chemical erosion and transport due to the combined effects of seepage, contact, and buoyancy forces.
+These computations will thus simulate, with high-fidelity, the multi-physics of realistic porous-medium dynamics, albeit in a scaled down context.
+Ultimately, such simulations could be used to build an understanding of medium reconfiguration events, such as sinkhole collapse or conduit formation in karst networks.
+
+	As mentioned above, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments \cite{tao2014experimental}.
+The new simulations will compare against this experimental data and guide future experiments.
 

### 2019-11-12 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 
-	As mentioned above, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments \cite{tao2014experimental}.
-The new simulations will compare against this experimental data and guide future experiments.
-
-\vsp{3}
-
-	With two Mathematics PhD students, PI Moore has begun running preliminary simulations to model this behaviors.
-The simulations, which are at an early stage of development, are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
-They utilize a homogenized description of the flow field, e.g.~the Darcy or Brinkman equations.
-These simulations incorporate the physical effects of:
+	In very preliminary work, PI Moore has been running simplified simulations with a current graduate student.
+These preliminary simulations are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
+They utilize the homogenized description of the flow field in \eqref{DarcyEq} and incorporate the physical effects of:
 \begin{itemize}
@@
 \end{itemize}
-Preliminary investigation suggests that this last mechanisms of cohesion is essential to model sinkhole collapse in the system, and the simulations await careful calibration against experimental data.
+Preliminary investigation suggests that this last mechanisms of cohesion is essential to model sinkhole collapse in the system.
 
-The simulations do not yet incorporate the effects of erosion and dissolution.
-A grand goal of this proposal would be to merge these two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short term events, such as sinkhole collapse, and long-term changes in the medium.
-Such a framework must include the effects of erosion, dissolution, transport, sedimentation, compaction, cohesive forces, and mechanical collapse.
+These simulation have not yet begun to incorporate the slow-acting effects of mechanical and chemical erosion, and the associated gradual changes in medium properties.
+A grand goal of this proposal would be to merge the two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short term events, such as sinkhole collapse, and long-term changes in the medium.
 The greatest challenge faced is the disparate temporal and spatial scales that must be considered.
-Our strategy is to use the high-fidelity erosion and dissolution simulations to develop reduced models (ala mean-field theory) that would be incorporated into simulations.
+Our proposed strategy is to use the high-fidelity erosion simulations to parametrize the effect of erosion on medium properties.
+
+	As mentioned above, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments \cite{tao2014experimental}.
+The new simulations will compare against this experimental data and guide future experiments.
+
+MORE
 

### 2019-11-13 docs/proposals/NSF/ProjDesc/ProjDesc.tex
worked on early sections of proposal

@@
 \usepackage{comment, enumerate, tabularx}
-\usepackage{natbib, hyperref, url}
+\usepackage{hyperref, url}
 %\usepackage[justification=RaggedRight]{caption}
@@
 \usepackage{subcaption}
+\usepackage[sort,nocompress]{cite}
 %---------------------------------------------------------------------------------------------------%
@@
 \newcommand{\thL}{$\theta$--$L$}
+\newcommand{\bd}{\partial}
+\newcommand{\eeta}{\boldsymbol{\eta}}
+\newcommand{\rr}{\mathbf{r}}
+\newcommand{\ff}{\mathbf{f}}
+\newcommand{\yy}{\mathbf{y}}
 
@@
 Not only is this process essential for human water resources, but also for the ecology of rivers, estuaries, and other natural habitats.
-Natural water resources, however, have been placed under enormous pressure by human population growth and associated activities that can comprise the natural filtration cycle, for example expansion of industry, urbanization, pollution, and climate change.
-See the UN report on water resources for further detail on the threats to water resources \cite{UNwater}.
+Natural water resources, however, have been placed under enormous pressure by human population growth and associated activities that can comprise \todo[inline]{comprise or compromise?} the natural filtration cycle, for example expansion of industry, urbanization, pollution, and climate change.
+See the UN report on water resources for further detail on the threats to water resources~\cite{UNwater}.
 % Could also include USGS if needed.
@@
 Thus, it becomes necessary to understand transport through complex media whose properties change {\em dynamically} in response to the intervening fluid flow.
-Such effects become most prominent during rapid events, like the gravitational collapse of a sinkhole \cite{sandhu2018fate}, during which medium properties can change suddenly and dramatically.
+Such effects become most prominent during rapid events, like the gravitational collapse of a sinkhole~\cite{sandhu2018fate}, during which medium properties can change suddenly and dramatically.
 Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties.
@@
 This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow can alter porous-media properties and to characterize the associated changes in transport within the evolving medium, for example the anomalous dispersion of tracers.
-A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength \cite{lin2018randomization}.
+A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{lin2018randomization}.
 These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material.
 Potential exists for feedback between these timescales: for example the slow wearing process reaching a critical threshold beyond which catastrophic events become more likely.
-
 Physical mechanisms that can dynamically alter porous-medium properties include:
-\begin{itemize}
+\begin{itemize}[noitemsep]
 \item Erosion of solid material due to fluid-mechanical stresses or chemical dissolution.
@@
 For instance, erosion can carve grains into slender shapes aligned primarily in the direction of the dominant flow, thereby creating {\em anisotropic} characteristics.
-Likewise, chemical dissolution can carve well-defined conduit paths in karst networks which strongly alter transport properties \cite{szymczak2009wormhole}.
+Likewise, chemical dissolution can carve well-defined conduit paths in karst networks which strongly alter transport properties~\cite{szymczak2009wormhole}.
 
-More generally, the coupling between shape and flow during erosion, dissolution, and related phase-change processes is a topic that has garnered recent interest in the mathematical sciences community \cite{Ristroph2012, rycroft2016asymmetric, cohen2016erosion, MooreCPAM2017, mitchell2017generalized, Quaife2018, wykes2018self, lachaussee2018competitive, lopez2018cfd, ristroph2018sculpting}.
-Erosion-induced shape change has been studied in the high Reynolds number regime, both experimentally \cite{Ristroph2012, MoorePOF2013} and theoretically \cite{MoorePOF2013, MooreCPAM2017, hewett2017evolution} and in single \cite{Ristroph2012, MoorePOF2013, MooreCPAM2017, lachaussee2018competitive} and multiple-body arrangements \cite{hewett2017evolution}.
-Studies on related processes of dissolution \cite{HuangJFM2015, kondratiuk2015steadily, cohen2016erosion, claudin2017dissolution, wykes2018self, huang2017solute}, melting \cite{Cummings1999, back2014effect, rycroft2016asymmetric, hewett2017pear, MooreCPAM2017, toppaladoddi2018combined, hewett2019evolution, favier2019rayleigh}, solidification \cite{Huppert90, Anderson95, Cummings1999, mccue2003extinction}, and deposition \cite{hewett2018modelling} exhibit intriguing similarities and differences \cite{MooreCPAM2017}.
-These studies reveal a rich set of possible dynamics, from the emergence of universal morphologies that erase details of the initial state and evolve self-similarly in time \cite{MoorePOF2013, MooreCPAM2017, hewett2017pear}, to fine-scale pattern formation \cite{cohen2016erosion, claudin2017dissolution, huang2017solute},
-to unstable morphologies that can retain or even amplify features present in the initial state \cite{claudin2017dissolution, wykes2018self}.
+More generally, the coupling between shape and flow during erosion, dissolution, and related phase-change processes is a topic that has garnered recent interest in the mathematical sciences community~\cite{Ristroph2012, rycroft2016asymmetric, cohen2016erosion, MooreCPAM2017, mitchell2017generalized, Quaife2018, wykes2018self, lachaussee2018competitive, lopez2018cfd, ristroph2018sculpting}.
+Erosion-induced shape change has been studied in the high Reynolds number regime, both experimentally~\cite{Ristroph2012, MoorePOF2013} and theoretically~\cite{MoorePOF2013, MooreCPAM2017, hewett2017evolution} and in single~\cite{Ristroph2012, MoorePOF2013, MooreCPAM2017, lachaussee2018competitive} and multiple-body arrangements~\cite{hewett2017evolution}.
+Studies on related processes of dissolution~\cite{HuangJFM2015, kondratiuk2015steadily, cohen2016erosion, claudin2017dissolution, wykes2018self, huang2017solute}, melting~\cite{Cummings1999, back2014effect, rycroft2016asymmetric, hewett2017pear, MooreCPAM2017, toppaladoddi2018combined, hewett2019evolution, favier2019rayleigh}, solidification~\cite{Huppert90, Anderson95, Cummings1999, mccue2003extinction}, and deposition~\cite{hewett2018modelling} exhibit intriguing similarities and differences~\cite{MooreCPAM2017}.
+These studies reveal a rich set of possible dynamics, from the emergence of universal morphologies that erase details of the initial state and evolve self-similarly in time~\cite{MoorePOF2013, MooreCPAM2017, hewett2017pear}, to fine-scale pattern formation~\cite{cohen2016erosion, claudin2017dissolution, huang2017solute}, to unstable morphologies that can retain or even amplify features present in the initial state~\cite{claudin2017dissolution, wykes2018self}.
 
-Only recently have these ideas been extended to the low-Reynolds-number regime that is applicable to porous media  \cite{mitchell2017generalized, Quaife2018}.
+Only recently have these ideas been extended to the low-Reynolds-number regime that is applicable to porous media~\cite{mitchell2017generalized, Quaife2018}.
 While the governing fluid-flow equations become linear in this regime, porous-media applications present a host of new challenges, for example:
-\begin{itemize}
+\begin{itemize}[noitemsep]
 \item Porous media typically involves dense packings so that close-range effects and even nearly contacting bodies must be considered.
+
 \item The Stokes limit introduces {\em longer} range effects than the inertial limit does, thus coupling the shape evolution of {\em all} grains and conduits to a higher degree.
-\item Somewhat counterintuitively, erosion does not always act to smooth shapes but rather can create sharp features and corners \cite{Ristroph2012}.
-These features can be difficult to resolve and, further, can trigger numerical instabilities \cite{Quaife2018}.
-Dissolution, meanwhile, can initiate a roughening transition \cite{claudin2017dissolution}, leading to similar numerical difficulties.
+
+\item Somewhat counterintuitively, erosion does not always act to smooth shapes but rather can create sharp features and corners~\cite{Ristroph2012}.
+These features can be difficult to resolve and, further, can trigger numerical instabilities~\cite{Quaife2018}.
+Dissolution, meanwhile, can initiate a roughening transition~\cite{claudin2017dissolution}, leading to similar numerical difficulties.
+
 \item Additionally effects, such as sedimentation, transport, and compaction constantly work to reconfigure the medium as its constituents and boundaries degrade.
 \end{itemize}
-These challenges require innovative computational techniques, some of which have been developed recently \cite{Quaife2018} and some of which await resolution.
-An ultimate goal of this proposal is to achieve high-fidelity simulations of $O(100-1000)$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.
-Fortunately, some closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton \cite{bizmark2019multiscale}.
+These challenges require innovative computational techniques, some of which have been developed recently~\cite{Quaife2018} and others that await resolution.
+An ultimate goal of this proposal is to achieve high-fidelity simulations of $\mathcal{O}(100-1000)$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.
+Fortunately, some closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
 The experiments offer a wonderful opportunity to guide, calibrate, and validate theoretical developments, as do proposed experiments at the Geophysical Fluid Dynamics Institute.
+\todo[inline]{Seems like a natural place to add some letters of
+collaboration. Kevin S and/or Ming might be 2. Not sure if you have
+someone at Princeton that you would ask for one from?}
 
 While erosion and dissolution lead to gradual changes in a medium, other events like sinkhole collapse can occur suddenly and catastrophically.
-Most likely, all of the mechanisms listed above --- erosion, dissolution, transport, compaction, and gravitational collapse --- contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity.
-Sinkhole formation has been explored with preliminary experiments run at the Geophysical Fluid Dynamics Institute (GFDI) at Florida State University \cite{tao2014experimental}.
+Most likely, all of the mechanisms listed above---erosion, dissolution, transport, compaction, and gravitational collapse---contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity.
+Sinkhole formation has been explored with preliminary experiments run at the Geophysical Fluid Dynamics Institute (GFDI) at Florida State University~\cite{tao2014experimental}.
 These scaled-down experiments offer the ability to probe various mechanisms behind sinkhole formation, for example a difference in hydraulic head between the confined and unconfined aquifers.
@@
 Ultimately, we envision the high-fidelity erosion simulations to inform coarse-grained models for: (i) transport and dispersion; and (ii) dynamic evolution of macroscopic medium properties.
-These parameterized models could then be combined with well-developed multi-phase models \cite{Imma2019, eastham2019multiphase} to be used for the quantitative description and prediction of sinkhole collapse.
+These parameterized models could then be combined with well-developed multi-phase models~\cite{Imma2019, eastham2019multiphase} to be used for the quantitative description and prediction of sinkhole collapse.
 
@@
 where $\uu$ is the velocity field, $p$ the pressure field, and $\mu$ the fluid viscosity.
+Linear elliptic PDEs, such as the Stokes equations, can be reformulated as a boundary integral equation (BIE).
+BIEs have several numerical advantages including a dimension reduction, automatic mass conservation, and high-order accuracy.
+An equivalent BIE formulation of the Stokes equations in Eq.~\eqref{StokesEq} is
+\begin{align}
+  \label{eqn:BIE}
+  \ff(\xx) = -\frac{1}{2}\eeta(\xx) + \frac{1}{\pi} \int_{\bd\Omega}
+    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+    \eeta(\yy) ds_\yy, \quad \xx \in \bd\Omega
+\end{align}
+where $\ff$ is a Dirichlet boundary condition, $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the outward unit normal of $\bd\Omega$.
+Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, important quantities such as the velocity, pressure, vorticity, and deformation tensor can be computed in the fluid bulk.
+For example, the velocity at $\xx \in \Omega$ is
+\begin{align*}
+  \uu(\xx) = \frac{1}{\pi} \int_{\bd\Omega}
+    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+    \eeta(\yy) ds_\yy.
+\end{align*}
 
-	The above microscopic description is required for the shape evolution of individual grains due to fine-scale erosive effects, either mechanical or chemical.
+Eq.~\eqref{StokesEq} is a microscopic description is required to study the shape evolution of individual grains due to fine-scale erosive effects, either mechanical or chemical.
 The description, however, becomes impractical when attempting to model seepage in very large porous systems where the microscopic geometry can be exceedingly complex.
@@
 Leading-order homogenization produces the well-known Darcy system
-\begin{equation}
+\begin{align}
   \label{DarcyEq}
   \qq = - \bvec{K} \grad \phi
-\end{equation}
+\end{align}
 where $\qq$ is the {\em specific discharge} or {\em Darcy velocity}, and $\phi = z + p/(\rho g)$ is the hydraulic head, with $\rho$ and $g$ representing the fluid density and gravitational constant respectively.
@@
 Note that the Darcy velocity is related to the tracer velocity through $\qq = \theta_f \uu$, where $\theta_f$ is porosity (i.e.~fluid volume fraction).
-In the case of an isotropic medium, the Kozeny-Carman equation is often used to relate permeability to volume fraction \cite{bear2013dynamics}
+In the case of an isotropic medium, the Kozeny-Carman equation is often used to relate permeability to volume fraction~\cite{bear2013dynamics}
 % See Bear Ch. 2.8, pg. 111
-\begin{equation}
-k = C \frac{\theta_f^3}{(1-\theta_f)^2}
-\end{equation}
+\begin{align}
+  k = C \frac{\theta_f^3}{(1-\theta_f)^2}.
+\end{align}
 The macroscopic description offered by Eq.~\eqref{DarcyEq}, although approximate, simplifies analysis tremendously in that individual grains are no longer resolved and thus the domain geometry is generally much simpler.
 
-While the most immediate proposed work on computational methods to simulate erosion will utilize \eqref{StokesEq}, the later stages of this project will also incorporate \eqref{DarcyEq}, or closely related variants known as multiphase models \cite{Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
+While the most immediate proposed work on computational methods to simulate erosion will utilize~\eqref{StokesEq}, the later stages of this project will also incorporate~\eqref{DarcyEq}, or closely related variants known as multiphase models~\cite{Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
 These models will rely on statistical analysis of the data produced by the high-fidelity erosion simulations in order to parameterize the effects of erosion, leading to deterministic or stochastic reduced-order models for porous-medium evolution and erosion, combined with other external effects such as gravitationally-induced dynamics.
 
+%---------------------------------------------------------------------------------------------------%
 \subsection{Mechanical and chemical erosion of a porous medium}
 
-%\subsubsection{Background}
-
-The first problem discussed here is the erosion of a porous medium, as has been preliminarily investigated in \cite{Quaife2018}.
+The first problem discussed here is the erosion of a porous medium, as has been preliminarily investigated in~\cite{Quaife2018}.
 We will consider erosion induced by either fluid-mechanical forces or by chemical reaction, i.e.~dissolution.
@@
 \end{equation}
-Both processes have been investigated by the PIs and collaborators in the context of single bodies in high Reynolds-number flows \cite{Ristroph2012, MoorePOF2013, HuangJFM2015, MooreCPAM2017}.
-In the low-Reynolds regime of porous-media flow, numerical methods have been developed by the PIs to simulate shear-induced erosion \cite{Quaife2018}.
-These simulations combine highly accurate boundary integral methods with stable interface evolution techniques.
-The boundary integral solver is accelerated by the fast multipole method \cite{gre-rok1987, gre-gre-may1992} to achieve optimal $O(N)$ complexity.
-Meanwhile, the so-called {\thL} method is used for interface evolution to prevent distortion and tangling of the interface meshes \cite{hou1994removing, MoorePOF2013, Quaife2018}.
+Both processes have been investigated by the PIs and collaborators in
+the context of single bodies in high Reynolds-number
+flows~\cite{Ristroph2012, MoorePOF2013, HuangJFM2015, MooreCPAM2017}. In
+the low-Reynolds regime of porous-media flow, numerical methods have
+been developed by the PIs to simulate shear-induced
+erosion~\cite{Quaife2018}. These simulations combine highly accurate
+boundary integral methods with stable interface evolution techniques.
+The boundary integral solver is accelerated by the fast multipole
+method~\cite{gre-rok1987, gre-gre-may1992} to achieve optimal $O(N)$
+complexity. Meanwhile, the so-called {\thL} method is used for interface
+evolution to prevent distortion and tangling of the interface meshes~\cite{hou1994removing, MoorePOF2013, Quaife2018}.
 %A near-term goal is to adapt these methods to handle the case of chemically-induced dissolution.
@@
 The figure shows 80 bodies of initially random size and position, undergoing erosion.
-This figure extends previously reported 50-body simulations to 80 bodies \cite{Quaife2018} due to a recently developed barycentric interpolation scheme \citep{bar2014, bar-wu-vee2015}, which enables closer contact between bodies and thus more bodies.
+This figure extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015}, which enables closer contact between bodies and thus more bodies.
 The color shows the (normalized) vorticity field surrounding the bodies.
@@
 
-\todo[inline]{Bryan, could you add some details and references to these paragraphs below?}
+An immediate goal of the proposed work is extend the range of physical effects captured in these simulations.
+A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
+To address this problem, we have very recently extended a Barycentric quadrature~\cite{abr2014, bar-wu-vee2015}---we have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing.
+This quadrature approach has the advantage that it is a non-intrusive modification of the trapezoid rule, allowing us to achieve an error bound that independent of the grain configuration.
+Near-term plans are to include flow transport and gravitational sedimentation of the eroding grains.
+For this extension, contact forces between bodies must be included to eliminate unphysical contact that is inevitable due to discretization errors.
+Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research.
+One approach is to use introduce a potential with short-range repulsion~\cite{}, but such methods often introduce stiffness.
+Alternatively, a space-time interference volume can e used to guarantee a minimum separation between grains.
+In a fluid context, this method was first introduced by Lu et al.~\cite{lu-rah-zor2017}, and extended to allow for much smaller separation distances of rigid bodies by the PI's previous graduate student~\cite{bys-sha-qua2019}.
+One Ph.D.~student, who will be jointly supervised by both PIs, will simulate sedimentation of eroding bodies by developing algorithms that resolve quadrature error and contact.
 
-An immediate goal of the proposed work is extend the range of physical effects captured in these simulations.
-Very recently, we have implemented barycentric interpolation into the boundary integral solver in order to allow for more tightly spaced configurations, even bodies that nearly touch.
-Near-term plans are to include flow transport and gravitational sedimentation of the particles.
-For this extension, contact forces between bodies must be included.
-Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research  {\color{blue} cite}.
-We plan to implement contact forces with {\color{blue} stuff}.
-This goal will form the PhD dissertation of a graduate student who will be supervised by myself and Prof.~Bryan Quaife (FSU Scientific Computing).
+\todo[inline]{Bryan, could you add some details and references to the paragraph below?}
 
 Next, we plan to extend the simulation framework to handle chemical dissolution of solid bodies via physical laws \eqref{Ceq}--\eqref{DissVn}.
-For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations, is already in place, but the coupling to the advection-diffusion equations \eqref{Ceq} and interface law \eqref{DissVn} would need to be implemented.
+For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations, is already in place, but the coupling to the advection-diffusion equations~\eqref{Ceq} and interface law~\eqref{DissVn} would need to be implemented.
 Once these pieces are in place, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation, would finally become possible.
@@
 The gradual changes in the medium and karst boundaries due to erosion and dissolution could create conditions favorable for mechanical failure or collapse of the structure, for example sinkholes.
+\todo[inline]{Some of this stuff is already in the Transport section
+such as the Laplace transform idea}
 
@@
 
-The rate of dispersion is known to be directly related to the pore size
-distribution~\cite{dea-qua-bir-jua2018}. Therefore, there is a need to
-understand how erosion affects the pore size distribution. In
-preliminary, we define pore sizes between grains that share an edge of a
-Delanuay triangulation with vertices at the grain centers
-(Figure~\ref{fig:triangluation}). In Figure~\ref{fig:poreStats}, we plot
-the mean and variance of the pore sizes as a function of porosity. To
-better understand how erosion affects the anomalous dispersion, we
-propose to investigate how the pores grow with erosion. We will start
-with the notion of a {\em porelet} which is an individual
-Hagen-Poiseuille flow in each of the individual
-pores~\cite{dea-qua-bib-jua2018}. By computing the strength of the
-individual Hagen-Poiseuille flows, the shear rate can be computed, and
-thus the rate of erosion can be computed.
+The rate of dispersion is known to be directly related to the pore size distribution~\cite{dea-qua-bir-jua2018}.
+Therefore, there is a need to understand how erosion affects the pore size distribution.
+In preliminary, we define pore sizes between grains that share an edge of a Delanuay triangulation with vertices at the grain centers (Figure~\ref{fig:Eroding100gap_mean_var}(a)).
+In Figures~\ref{fig:Eroding100gap_mean_var}(a) and~\ref{fig:Eroding100gap_mean_var}(b), we plot the mean and variance of the pore sizes as a function of porosity.
+To better understand how erosion affects the anomalous dispersion, we propose to investigate how the pores grow with erosion.
+We will start with the notion of a {\em porelet} which is an individual Hagen-Poiseuille flow in each of the individual pores~\cite{dea-qua-bib-jua2018}.
+By computing the strength of the individual Hagen-Poiseuille flows, the shear rate can be computed, and thus the rate of erosion can be computed.
 
@@
 
-	As mentioned above, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments \cite{tao2014experimental}.
+As mentioned above, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments~\cite{tao2014experimental}.
 The new simulations will compare against this experimental data and guide future experiments.
@@
 A recent example is undergraduate student Tyler Bolles who completed an honors thesis with PI Moore at FSU on laboratory and theory of water waves.
-This work resulted in one {\em peer-reviewed} publication already \cite{Bolles2019}, with a second to be submitted soon.
+This work resulted in one {\em peer-reviewed} publication already~\cite{Bolles2019}, with a second to be submitted soon.
 
@@
 In particular, Moore's research was the focus of an educational video created by {\bf CPALMS}, which is the State of Florida's official source for standards information and course descriptions for K-12 education.
-The video, which features an interview and animations of research, is used to reinforce concepts from mathematics courses (grade levels 7-12), and to encourage students to consider a career in the STEM fields \cite{CPALMS}.
+The video, which features an interview and animations of research, is used to reinforce concepts from mathematics courses (grade levels 7-12), and to encourage students to consider a career in the STEM fields~\cite{CPALMS}.
 Additionally, these videos are frequently used for the continuing education of K-12 {\em teachers}, providing them a broader perspective of mathematics that could be integrated into their teaching.

### 2019-11-13 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 Not only is this process essential for human water resources, but also for the ecology of rivers, estuaries, and other natural habitats.
-Natural water resources, however, have been placed under enormous pressure by human population growth and associated activities that can comprise \todo[inline]{comprise or compromise?} the natural filtration cycle, for example expansion of industry, urbanization, pollution, and climate change.
+Natural water resources, however, have been placed under enormous pressure by human population growth and associated activities that can compromise the natural filtration cycle, for example expansion of industry, urbanization, pollution, and climate change.
 See the UN report on water resources for further detail on the threats to water resources~\cite{UNwater}.
@@
 An ultimate goal of this proposal is to achieve high-fidelity simulations of $\mathcal{O}(100-1000)$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.
-Fortunately, some closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
-The experiments offer a wonderful opportunity to guide, calibrate, and validate theoretical developments, as do proposed experiments at the Geophysical Fluid Dynamics Institute.
-\todo[inline]{Seems like a natural place to add some letters of
+This is an highly active area of research, as closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
+These experiments a great opportunity for comparison against our numerical simulations.
+Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute, which would help to guide, calibrate, and validate the computational methods.
+
+\todo[inline]{Bryan: Seems like a natural place to add some letters of
 collaboration. Kevin S and/or Ming might be 2. Not sure if you have
 someone at Princeton that you would ask for one from?}
+\todo[inline]{Nick: Good point.
+How do you include collaboration letters in the text?
+Do you cite them like a reference?
+I will ask Kevin or Ming for a collaboration letter.
+I don't think we need to ask the people at Princeton too; I meant that to mainly indicate it is an exciting, active area of research and so I rephrased the sentence.}
 
@@
 	This research proposed here could lead to a range of societal benefits, including better management of water resources, accurate prediction of contaminant transport, and an understanding of the long-term effects of human activities, such as hydraulic fracturing or groundwater pumping, on porous media and water resources.
-In such scenarios, the slow timescales of mechanical and chemical erosion are coupled to the faster timescales of human-induced changes and/or gravitational collapse.
+In such scenarios, the slow timescales of mechanical and chemical erosion are coupled to the faster timescales of human-induced changes and gravitational collapse.
 Currently, the relationship between these scales is poorly understood.

### 2019-11-13 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 Thus, it becomes necessary to understand transport through complex media whose properties change {\em dynamically} in response to the intervening fluid flow.
-Such effects become most prominent during rapid events, like the gravitational collapse of a sinkhole~\cite{sandhu2018fate}, during which medium properties can change suddenly and dramatically.
+These effects are most noticeable during rapid events, like the gravitational collapse of a sinkhole~\cite{sandhu2018fate}, during which medium properties can change dramatically over short timescales.
 Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties.
@@
 Potential exists for feedback between these timescales: for example the slow wearing process reaching a critical threshold beyond which catastrophic events become more likely.
-Physical mechanisms that can dynamically alter porous-medium properties include:
+Physical mechanisms that can alter porous-medium properties include:
 \begin{itemize}[noitemsep]
@@
 An ultimate goal of this proposal is to achieve high-fidelity simulations of $\mathcal{O}(100-1000)$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.
-This is an highly active area of research, as closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
+Dynamic erosion of porous media is a highly active area of research, as closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
 These experiments a great opportunity for comparison against our numerical simulations.
-Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute, which would help to guide, calibrate, and validate the computational methods.
+Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute, which would help to guide, calibrate, and validate the computations.
 
@@
 
-While erosion and dissolution lead to gradual changes in a medium, other events like sinkhole collapse can occur suddenly and catastrophically.
+While erosion and dissolution lead to gradual changes in a medium, other events like sinkhole collapse or hydraulic fracturing occur over much shorter timescales.
 Most likely, all of the mechanisms listed above---erosion, dissolution, transport, compaction, and gravitational collapse---contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity.
-Sinkhole formation has been explored with preliminary experiments run at the Geophysical Fluid Dynamics Institute (GFDI) at Florida State University~\cite{tao2014experimental}.
+Sinkhole formation has been explored in preliminary experiments conducted at the Geophysical Fluid Dynamics Institute (GFDI) at Florida State University~\cite{tao2014experimental}.
 These scaled-down experiments offer the ability to probe various mechanisms behind sinkhole formation, for example a difference in hydraulic head between the confined and unconfined aquifers.
-An ultimate goal of this project is to merge these two lines of inquiry to gain a deeper understanding the influence of mechanically or chemically induced erosion on gravitational collapse.
+An ultimate goal of the project proposed here is to merge these two lines of inquiry to gain a deeper understanding of the influence of mechanically or chemically induced erosion on gravitational collapse.
 Ultimately, we envision the high-fidelity erosion simulations to inform coarse-grained models for: (i) transport and dispersion; and (ii) dynamic evolution of macroscopic medium properties.
-These parameterized models could then be combined with well-developed multi-phase models~\cite{Imma2019, eastham2019multiphase} to be used for the quantitative description and prediction of sinkhole collapse.
-
-In the following, we first describe the underlying governing equations, then detail the computational challenges and proposed work on simulating fluid-mechanical erosion, characterizing transport and dispersion, and modeling gravitational interactions.
+These parameterized models could then be combined with well-developed multi-phase models~\cite{Imma2019, eastham2019multiphase} to quantitatively describe and predict sinkhole collapse.
 
@@
 \subsection{Governing equations}
+
+We first summarize governing equations underlying the proposed work.
 At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations
@@
 While the most immediate proposed work on computational methods to simulate erosion will utilize~\eqref{StokesEq}, the later stages of this project will also incorporate~\eqref{DarcyEq}, or closely related variants known as multiphase models~\cite{Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
-These models will rely on statistical analysis of the data produced by the high-fidelity erosion simulations in order to parameterize the effects of erosion, leading to deterministic or stochastic reduced-order models for porous-medium evolution and erosion, combined with other external effects such as gravitationally-induced dynamics.
+These models will rely on statistical analysis of the data produced by the high-fidelity erosion simulations in order to parameterize the effects of erosion, leading to deterministic or stochastic reduced-order models for porous-medium evolution.
+%and erosion, combined with other external effects such as gravitationally-induced dynamics.
 
@@
 First, the left-most plot shows the rate at which the area fraction decreases as the bodies erode.
-Time is normalized by the value $t_f$ at which all bodies vanish and hence the area fraction is zero.
+%Time is normalized by the value $t_f$ at which all bodies vanish and hence the area fraction is zero. 
 Notice that the rate of area reduction does not change significantly during the simulation.
 The middle plot shows the resistivity, or inverse permeability of the medium.
-In the simulations, resistivity is calculated by measuring the total flux and the pressure upstream and downstream, then using Darcy's relation \eqref{DarcyEq} to infer $k$.
+In the simulations, resistivity is calculated by measuring the total flux and the pressure upstream and downstream, then using Darcy's relation \eqref{DarcyEq} to infer the horizontal permeability $k_x$.
 Naturally, as bodies erode, the resistivity they provide decreases in time.
-Note, however, that the vertical axis is logarithmic.
-Hence, the initial linear decrease corresponds to an exponential rate of resistivity reduction.
+Note that, unlike the area plot, the vertical axis is logarithmic and so the straight line observed at early times indicates that the resistivity decreases exponentially.
 The much more mild decrease in area fraction is not sufficient to account for this exponential rate, and hence the reshaping process, in particular the formation of channels, plays a pivotal role.
@@
 A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
-To address this problem, we have very recently extended a Barycentric quadrature~\cite{abr2014, bar-wu-vee2015}---we have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing.
+To address this problem, we have very recently extended a Barycentric quadrature~\cite{abr2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing.
 This quadrature approach has the advantage that it is a non-intrusive modification of the trapezoid rule, allowing us to achieve an error bound that independent of the grain configuration.
@@
 For this extension, contact forces between bodies must be included to eliminate unphysical contact that is inevitable due to discretization errors.
+
 Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research.
 One approach is to use introduce a potential with short-range repulsion~\cite{}, but such methods often introduce stiffness.
-Alternatively, a space-time interference volume can e used to guarantee a minimum separation between grains.
+Alternatively, a space-time interference volume can guarantee a minimum separation between grains.
 In a fluid context, this method was first introduced by Lu et al.~\cite{lu-rah-zor2017}, and extended to allow for much smaller separation distances of rigid bodies by the PI's previous graduate student~\cite{bys-sha-qua2019}.
@@
 such as the Laplace transform idea}
+
+\todo[inline]{Nick to Bryan: These changes you made look good to me. Did you want to add anything else, or is it okay to delete the above todo notes?}
 
@@
 of high porosity can be modest in volume fraction, but still be
-responsible for a large portion of the flux~\cite{Quaife2018}. To
-increase understanding of flow through eroded media, we will simulate
+responsible for a large portion of the flux~\cite{Quaife2018}. 
+\todo[inline]{There is no verb in the above sentence. Is there a word left out?}
+To increase understanding of flow through eroded media, we will simulate
 and statistically analyze transport through eroded geometries.
 
-In an eroded geometry $\Omega$, a concentration non-dimensionalized
+In an eroded geometry $\Omega$, the dimensionless
 concentration $c$ is governed by
@@
 $\dot{\ss}_j(t) = \uu(\ss_j(t))$. Once these trajectories are computed,
-using, for example, a high-order Runge-Kutta method, a statistical
-analysis be used to describe the transport. Two of the most important
+using for example a high-order Runge-Kutta method, a statistical
+analysis can be used to describe the transport. Two of the most important
 measurements are the tortuosity and the anomalous dispersion, both which
@@
 
-As mentioned above, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments~\cite{tao2014experimental}.
-The new simulations will compare against this experimental data and guide future experiments.
+	More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties.
+The output of the high-fidelity simulations can be transformed into essential an image format, enabling us to use cutting-edge advancements on deep neural-networks for image analysis \cite{pelt2018mixed}.
+Some important advantages of referenced work are the use of dilated convolutions in a deeply connected network, which first mixes scales and second reduces the number of super-parameters present and thus largely averts the risk of overfitting data.
+Both PIs will supervise a graduate student who will design and implement the deep-neural network for learning the essence of the high-fidelity simulations.
+Once the essential features are learned, they will be incorporated into reduced-order models that utilize the multiphase framework to enable more efficient and larger scale coarse-grained simulations of dynamic erosion.
 
-MORE
-
-\np
-%---------------------------------------------------------------------------------------------------%
-%% BROADER IMPACTS
-%\section{Broader Impacts of the Proposed Work}
-% Xiaoming
-%\subsection{Broader scientific impact of the project} 
-%\subsection{Student training and collaborative work}
+As mentioned previously, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments~\cite{tao2014experimental}.
+Firstly, already existing data from these experiments offers a testbed for comparison against our newly developed simulations.
+Furthermore, we propose to run a set of new experiments at the facilities offered by GFDI, spearheaded by an undergraduate student in close collaboration with the graduate students and PIs.
+These new experiments will more deeply probe the mechanisms underlying sinkhole formation with the special design goal of comparison agains the numerical simulations.
+These experiments will be used to calibrate and validate our computations.
 

### 2019-11-14 docs/proposals/NSF/ProjDesc/ProjDesc.tex
picking away at proposal

@@
 These experiments a great opportunity for comparison against our numerical simulations.
-Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute, which would help to guide, calibrate, and validate the computations.
-
-\todo[inline]{Bryan: Seems like a natural place to add some letters of
-collaboration. Kevin S and/or Ming might be 2. Not sure if you have
-someone at Princeton that you would ask for one from?}
-\todo[inline]{Nick: Good point.
-How do you include collaboration letters in the text?
-Do you cite them like a reference?
-I will ask Kevin or Ming for a collaboration letter.
-I don't think we need to ask the people at Princeton too; I meant that to mainly indicate it is an exciting, active area of research and so I rephrased the sentence.}
+Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute, which would help to guide, calibrate, and validate the computations (see letter of collaboration).
 
@@
 For example, the velocity at $\xx \in \Omega$ is
-\begin{align*}
+\begin{align}
   \uu(\xx) = \frac{1}{\pi} \int_{\bd\Omega}
@@
     \eeta(\yy) ds_\yy.
-\end{align*}
+\end{align}
 
@@
 The figure shows 80 bodies of initially random size and position, undergoing erosion.
-This figure extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015}, which enables closer contact between bodies and thus more bodies.
+This figure extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed Barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015}, which enables closer contact between bodies and thus more bodies.
 The color shows the (normalized) vorticity field surrounding the bodies.
@@
 A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
-To address this problem, we have very recently extended a Barycentric quadrature~\cite{abr2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing.
+To address this problem, we have very recently extended a Barycentric quadrature~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing.
 This quadrature approach has the advantage that it is a non-intrusive modification of the trapezoid rule, allowing us to achieve an error bound that independent of the grain configuration.
@@
 
-\todo[inline]{Bryan, could you add some details and references to the paragraph below?}
-
 Next, we plan to extend the simulation framework to handle chemical dissolution of solid bodies via physical laws \eqref{Ceq}--\eqref{DissVn}.
@@
 The gradual changes in the medium and karst boundaries due to erosion and dissolution could create conditions favorable for mechanical failure or collapse of the structure, for example sinkholes.
-\todo[inline]{Some of this stuff is already in the Transport section
-such as the Laplace transform idea}
-
-\todo[inline]{Nick to Bryan: These changes you made look good to me. Did you want to add anything else, or is it okay to delete the above todo notes?}
+\todo[inline]{If we are going to propose the Laplace transform idea
+to solve advection-diffusion, this might be the place to put it}
 
@@
   with 200 tracers passing through an eroded geometry with a porosity of
-  0.63. The tracers are initialized at the left end of the channel.}
+  0.63. The tracers are initialized at the left end of the channel and
+  the flow is driven by a pressure difference from left to right.}
 \end{wrapfigure}
 
-Transport through eroded media is a direct consequence of the pore
-structure. Qualitative properties of an eroded media, such as channels
-of high porosity can be modest in volume fraction, but still be
-responsible for a large portion of the flux~\cite{Quaife2018}. 
-\todo[inline]{There is no verb in the above sentence. Is there a word left out?}
-To increase understanding of flow through eroded media, we will simulate
-and statistically analyze transport through eroded geometries.
+Transport through eroded media is a direct consequence of the pore structure.
+Qualitative properties of an eroded media, such as channels of high porosity, can be modest in volume fraction, but can be responsible for a large portion of the flux~\cite{Quaife2018}.
+To increase understanding of flow through eroded media, we will simulate and statistically analyze transport through eroded geometries.
 
@@
 streamlines (Figure~\ref{fig:100tracers}).
-\begin{wrapfigure}[]{l}{0.4\textwidth}
-  \includegraphics[width=0.4\textwidth]{figs/tort_eulerian100}
-  \caption{\label{fig:100tortuosity} The tortuosity of an eroding
-  geometry. The tortuosity can be computed using two different formulas
-  (red vs.~blue marks). The red square is the tortuosity in
-  Figure~\ref{fig:100tracers}. Their is qualitative agreement between
-  our numerical simulations and a power-law model (black dashed
-  line)~\cite{mat-kha-koz2008}.}
-\end{wrapfigure}
 
-The $j^{th}$ trajectories, or characteristics, is governed by
-$\dot{\ss}_j(t) = \uu(\ss_j(t))$. Once these trajectories are computed,
-using for example a high-order Runge-Kutta method, a statistical
-analysis can be used to describe the transport. Two of the most important
-measurements are the tortuosity and the anomalous dispersion, both which
-are defined in terms of the length of the trajectories
-\begin{align}
+The $j^{th}$ trajectory, or characteristic, is governed by $\dot{\ss}_j(t) = \uu(\ss_j(t))$.
+Once these trajectories are computed, using for example a high-order Runge-Kutta method, a statistical analysis can be used to describe the transport.
+Two of the most important measurements are the tortuosity and the anomalous dispersion, both which are defined in terms of the length of the trajectories \begin{align}
   \lambda_j(t) = \int_{0}^{t} \|\ss'(t')\| dt'.
 \end{align}
-Once $N_p$ trajectories are computed, the tortuosity is the
-dimensionless number
+Upon computing $N_p$ trajectories, the tortuosity is the dimensionless number
 \begin{align}
@@
 geometries whose porosity is increasing under the process of erosion
-(Figure~\ref{fig:100tortuosity}).
+(Figure~\ref{fig:100tortuosity}). However, preliminary results also
+indicate that erosion can increase the amount of tortuosity as is
+evident towards the at the towards the end of the erosion process in
+Figure~\ref{fig:100tortuosity}. Moreover, we have observed a significant
+increase in the tortuosity at small porosities
+(Figure~\ref{fig:20tortuosity}.
 
-While the tortuosity characterizes the amount of winding of streamlines,
-the dispersion characterizes the spreading of the trajectories.
-Dispersion can be descried using the first- and second-ensemble moments
-of the trajectories
+\begin{figure}[htp]
+  \begin{center}
+  \begin{subfigure}[b]{0.45\textwidth}
+  \includegraphics[width=\textwidth]{figs/tort_eulerian20}
+  \caption{20 eroding bodies}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+  \includegraphics[width=\textwidth]{figs/tort_eulerian100}
+  \caption{100 eroding bodies}
+  \end{subfigure}
+  \end{center}
+
+  \caption{\label{fig:100tortuosity} The tortuosity of two eroding
+  geometries. The tortuosity can be computed using two different formulas
+  (red vs.~blue marks). The red square is the tortuosity in
+  Figure~\ref{fig:100tracers}. Their is qualitative agreement between
+  our numerical simulations and a power-law model (black dashed
+  line)~\cite{mat-kha-koz2008}.}
+  \todo[inline]{Fix caption and its references}
+\end{figure}
+
+While the tortuosity characterizes the amount of winding of streamlines, the dispersion characterizes the spreading of the trajectories.
+Dispersion can be described using the first- and second-ensemble moments of the trajectories
 \begin{align}
@@
 They utilize the homogenized description of the flow field in \eqref{DarcyEq} and incorporate the physical effects of:
-\begin{itemize}
+\begin{itemize}[noitemsep]
 \item Transport of grains due to seepage force from the surrounding fluid flow.

### 2019-11-14 docs/proposals/NSF/ProjDocs/BioSketch_BQ.tex
added some auxiliary docs

\documentclass[11pt]{article}

\usepackage{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{amsmath,amsfonts,amssymb}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{mathpazo}

\renewcommand\thesubsection{(\alph{subsection})}
\renewcommand\thesubsubsection{(\roman{subsubsection})}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}
% For 11pt size

\pagestyle{fancy}
\lhead{\footnotesize Bryan Quaife}
\chead{\footnotesize Biographical Sketch}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Professional Preparation}
\begin{tabular}{m{0.25\textwidth} m{0.42\textwidth} m{0.33\textwidth}}
University of Calgary & Pure and Applied Mathematics & B.Sc.~2004 \\
University of Calgary & Applied Mathematics & M.Sc.~2006 \\
Simon Fraser University & Applied and Computational Mathematics &
Ph.D.~2011 \\
University of Texas & Computational Science and Engineering & August 2011--July 2015
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Appointments}
Associate \\
Geophysical Fluid Dynamics Institute \\
Florida State University \\
November 2015--\\

\noindent
Assistant Professor \\
Department of Scientific Computing \\
Florida State University \\
August 2015--\\

\noindent
Research Associate \\
Institute for Computational Engineering and Sciences \\
University of Texas \\
September 2014--July 2015 \\

\noindent
Postdoctoral Fellow \\
Institute for Computational Engineering and Sciences \\
University of Texas \\
September 2011--August 2014

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Publications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Publications Most Closely Related to the Proposed
Project}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt] 
  \item Lukas Bystricy, Sachin Shanbhag, and {\bf Bryan D.~Quaife}.
    Stable and contact-free time stepping for dense rigid particle
    suspensions.  International Journal for Numerical Methods in Fluids,
    arxiv.org/abs/1804.11012, 2018.  In press

\item {\bf Bryan D.~Quaife} and M.~Nicholas J.~Moore.  A
  boundary-integral framework to simulate viscous erosion of a porous
  medium.  Journal of Computational Physics, 375:1--12, 2018.

\item Pietro de Anna, {\bf Bryan Quaife}, George Biros, and Ruben
  Juanes.  Prediction of velocity distribution from pore structure in
  simple porous media. Physical Review of Fluids, 2 (12) 124103, 2017.

\item Gokberk Kabacao\u{g}lu, {\bf Bryan Quaife}, and George Biros.
  Quantification of mixing in vesicle suspensions using numerical
  simulations in two dimensions.  Physics of Fluids, 29(2):021901, 2017.

\item MCA Kropinski and {\bf BD Quaife}. Fast integral equation methods
  for the modified Helmholtz equation. Journal of Computational Physics,
    230(2):425--434, 2011.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Other Significant Publications}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item Gokberk Kabacao\u{g}lu, {\bf Bryan Quaife}, Bryan Quaife, and
  George Biros.  Low-resolution simulations of vesicle suspensions in
  2D. Journal of Computational Physics, 357:43--77, 2018.

\item {\bf Bryan Quaife}, Pieter Coulier, and Eric Darve. An efficient
  preconditioner for the fast simulation of a 2D Stokes flow in porous
  media. International Journal for Numerical Methods in Engineering,
  113(4):561--580, 2017.

\item {\bf Bryan Quaife} and George Biros. Adaptive time stepping for
  vesicle simulations. Journal of Computational Physics, 306:478--499,
  2016.

\item {\bf Bryan Quaife} and George Biros. High-order adaptive time
  stepping for vesicle suspensions with viscosity contrast. Procedia
  IUTAM, 16:89–98, 2015.

\item {\bf Bryan Quaife} and George Biros.  High-volume simulations of
  two-dimensional vesicle suspensions.  Journal of Computational
  Physics, 274:245--267, 2014.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synergistic Activities}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt] 
  \item Organized a 2017 5-day workshop at the Banff International
    Research Station (BIRS) on complex creeping flows.

  \item Supervised two high school students for six weeks in the summer
    of 2016 through the Young Scholars Program.  They studied the effect
    that regularized kernels have on particle dynamics.

  \item Supervising undergraduate projects on simulating the dynamics of
    particles on closed surfaces, simulating wildfires with cellular
    automata, and using Bayesian analysis to study ocean circulation.

  \item Organizer and co-organizer of multiple minisymposiums at SIAM
    meetings and one SIAM regional meeting.

  \item Developed the courses {\em ISC5238: Integral Equation Methods}
    and {\em ISC5935: Iterative and Direct Methods for Linear Systems}.

\end{itemize}

\end{document}

### 2019-11-14 docs/proposals/NSF/ProjDocs/dataManagement.tex
added some auxiliary docs

%\documentclass[12pt]{amsart}
\documentclass[11pt]{article}

\usepackage{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{amsmath,amsfonts,amssymb}
\usepackage{tabularx}
\usepackage{mathpazo}
\usepackage{enumitem}

%\renewcommand\thesubsection{(\alph{subsection})}
%\renewcommand\thesubsubsection{(\roman{subsubsection})}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}
% For 11pt size

\pagestyle{fancy}
\lhead{\footnotesize Moore and Quaife}
\chead{\footnotesize Data Management Plan}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

\begin{document}
\thispagestyle{fancy}
\subsection*{Products of the Research}
The following types of data will be produced as part of this project:
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt] 
\item numerical methods for simulating erosion;
\item scientific software for implementing these methods;
\item website for disseminating results;
\item peer-reviewed journal publications.
\end{itemize}

\subsection*{Data Formats}
The software product will consist of (i) exploratory MATLAB or Python
scripts for testing analyzing the algorithms, and (ii) Julia and Fortran
implementations to measure runtime efficiencies on computer
architectures available at Florida State University.  All scripts and
codes will include explanatory comments.  The website will be in ASCII
plaintext using html, php, and javascript.

\subsection*{Access to Data and Data Sharing Practices and Policies}
Source scripts and codes will be made available, often before the
acceptance of the peer-reviewed papers, using the relevant scripts and
libraries.  This software will then be available, without restriction,
to any user who wishes to download, use, or modify it.  The website will
be available on the Internet.  All materials, including movies, images,
and text, will be licensed for re-use with appropriate credit given
(using a license such as the GNU Copyleft license).  Data from the
research will be open source, and there are no significant privacy,
confidentiality, or intellectual property requirements that pertain to
this research. Educational videos will be prodced by the CPALMS
organization and made freely available to the public

\subsection*{Policies for Re-Use, Re-Distribution and Production of
Derivatives}
All data created as a result of this project will be freely available
and usable by the public, and by other researchers.  The only condition
will be a citation to the appropriate publications.  The PIs will
further request, but not require, that users of our software contribute
any changes, improvements, or additions that they make back to the
appropriate open-source software project.  Data or images that are
copyrighted (by a journal, for example) will be marked as such by
watermark or text header in the file.

\subsection*{Archiving of Data} 
Source code will be uploaded to Google Code, BitBucket, GitHub, and
other Cloud-based data providers.  Websites relating to this project,
and all of the data on the aforementioned websites, will be hosted by
Florida State University's (FSU) Information Technology group on
servers that are backed up regularly.  This data will be available to
the public for as long as the PIs remain actively employed at FSU.  If
the PIs leave FSU for any reason, steps will be taken to ensure that
this data remains available, either by moving it to another university
or making it a part of a larger, more persistent project at FSU.

\end{document}

### 2019-11-14 docs/proposals/NSF/ProjDocs/facilities.tex
added some auxiliary docs

%\documentclass[12pt]{amsart}
\documentclass[11pt]{article}

\usepackage{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{mathpazo}

%\renewcommand\thesubsection{(\alph{subsection})}
%\renewcommand\thesubsubsection{(\roman{subsubsection})}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}
% For 11pt size

\newcommand{\todo}[1]{ \fbox{{\bf TODO:} \color{red} #1}}

\pagestyle{fancy}
\lhead{\footnotesize Quaife and Moore}
\chead{\footnotesize Facilities, Equipment, and Other Resources}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

\begin{document}
\thispagestyle{fancy}

\subsection*{Computing Resources}
Florida State University's (FSU) high performance computing (HPC) and
high throughput computing (HTC) clusters are managed by the Research
Computing Center (RCC).

The FSU HPC system is comprised of 12,492 x86 64-bit compute cores
linked together by low-latency infiniband networks for MPI
communication. The aggregate peak performance of the system is 264.6
TFLOPS. Compute nodes support between 2 and 16GB of memory per core. A
redundant cluster of specialized nodes serve as the user entry points
for the system. The Slurm job scheduler handles job submission and
scheduling on the HPC system. A broad set of compilers, math and
communication libraries, and software applications are made available on
the HPC to maximize the utility of the system by users across diverse
academic disciplines.  The cluster also includes nodes with 16 NVIDIA
Tesla gpGPU cards (m2050) for a total 7,168 GPU cores for a peak system
performance of 19.8 TFLOPS.

The FSU HTC system, Condor, is comprised of 1,200 x86 64-bit compute
cores.  The system is specifically tailored to support large batches of
serial jobs where overall throughput is preferred over performance.
The aggregate peak performance of the system is 16.5 TFLOPS.  Compute
nodes support between 2 and 8 GBs of memory per core.

In addition to the HPC and HTC systems, the PI's group has access to
RCC's Spear cluster.  The Spear Cluster is comprised of 288 x86 64-bit
process cores linked together by a QDR Infiniband network.  Eight of the
Spear nodes also connect to a PCI chassis equipped with 16 Nvidia Tesla
gpGPU cards (M2050) for a total of 7,168 GPU cores for a peak system
performance of 19.8 TFLOPS.

\subsection*{Personnel}
The RCC has dedicated personnel who offer help with hardware
specification and acquisition, software acquisition and licensing,
compilation, installation, integration with the queuing system, running
benchmarks, developing computational workflows, and necessary end-user
training.  In addition, the Department of Mathematics and the Department
of Scientific Computing have systems administrators that assist with the
PIs's group's computing needs.

Both the PIs are associates in the Geophysical Fluid Dynamics Institute
(GFDI). GFDI is a fluids lab where experimental work will be performed.
The lab includes the necessary support staff, including a machinist and
system administrator, to assist with experimental setups and
computational needs.

\subsection*{Office Space}
The project will utilize office and workspace in the Department of
Mathematics, Department of Scientific Computing, and Geophysical Fluid
Dynamics Institute at Florida State University. Offices are equipped
with a standard desktop computer and internet access.

\end{document}

### 2019-11-15 docs/proposals/NSF/ProjDesc/ProjDesc.tex
worked on some rearranging and added todos

@@
 A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
-To address this problem, we have very recently extended a Barycentric quadrature~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing.
+To address this problem, we have very recently extended a Barycentric quadrature~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing~\cite{chi-moo-qua2019}.
 This quadrature approach has the advantage that it is a non-intrusive modification of the trapezoid rule, allowing us to achieve an error bound that independent of the grain configuration.
@@
 Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research.
-One approach is to use introduce a potential with short-range repulsion~\cite{}, but such methods often introduce stiffness.
+One approach is to use introduce a potential with short-range repulsion, but such methods often introduce stiffness.
 Alternatively, a space-time interference volume can guarantee a minimum separation between grains.
@@
 
-Next, we plan to extend the simulation framework to handle chemical dissolution of solid bodies via physical laws \eqref{Ceq}--\eqref{DissVn}.
-For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations, is already in place, but the coupling to the advection-diffusion equations~\eqref{Ceq} and interface law~\eqref{DissVn} would need to be implemented.
-Once these pieces are in place, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation, would finally become possible.
+Next, we plan to extend the simulation framework to handle chemical dissolution of solid bodies via physical laws~\eqref{Ceq}--\eqref{DissVn}.
+For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations, is already in place, but the coupling to the advection-diffusion equations~\eqref{Ceq} and interface law~\eqref{DissVn} need to be implemented.
+We proposed to solve the advection diffusion equation~\eqref{Ceq} by first using Strang splitting~\cite{str1968} to decompose the PDE into linear advection and diffusion.
+The advection equation will be solved with a semi-Lagrangian method~\cite{rob1981} so that it can be solved on an Eulerian grid without a restrictive CFL condition.
+PI Quaife has experience with using semi-Lagrangian methods for another type of complex viscous flow~\cite{kab-qua-bir2017}.
+The diffusion equation is more challenging to accurately solve in the complex porous geometries.
+Two approaches include a memory-intensive space-time heat kernel~\cite{bar-eps-gre-jia-wan2019, jia-gre-wan2015, li-gre2009}, and Rothe's method coupled with a Yukawa equation solver~\cite{kro-qua2010, cau-cho-chr-sea2016}.
+A particular challenge of the latter method is extending functions from the complex geometry and into a regular geometry, such as a square, so that a high-order volume integral or Fourier method can be applied, and some groups have recently developed new techniques to form such an extension~\cite{fry-kro-tor2019, fry-leh-tor2019}.
+Alternatively, we propose to use a Laplace Transform to solve the diffusion equation
+\begin{alignat}{3}
+  \pd{c}{t} &= \frac{1}{\Pe} \Delta c, \quad &&\xx \in \Omega, \: t>0, .
+\end{alignat}
+Applying the Laplace transform, $C(\xx,s) = \mathcal{L}[c](\xx,t)$ satisfies
+\begin{align}
+  sC(\xx,s) - \frac{1}{\Pe}\Delta C(\xx,s) = c_0(\xx), 
+    \quad \xx \in \Omega,
+\end{align}
+where $c_0(\xx)$ is the initial concentration.
+This PDE will be solved with high-order accuracy and efficiently by using fast-multipole-accelerated integral equation methods of the Yukawa equation~\cite{kro-qua2011}, and the concentration will be recovered with an inverse Laplace transform~\cite{jos-war2006}.
+Once a high-order advection-diffusion solver is in place, by combining it with our integral equation formulation for the Stokes equation and the shear stress, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation, would finally become possible.
 Such a framework could accurately simulate the geophysically relevant scenario of karst conduits with embedded granular media.
 The gradual changes in the medium and karst boundaries due to erosion and dissolution could create conditions favorable for mechanical failure or collapse of the structure, for example sinkholes.
-\todo[inline]{If we are going to propose the Laplace transform idea
-to solve advection-diffusion, this might be the place to put it}
 
@@
 \end{align}
-where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length,
-$u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of
-the trajectory starting at $(x_0,y_0)$ and ending at a vertical
-cross-section at the other end of the channel. Relationships between the
-tortuosity and porosity of a geometry have been developed by other
-groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and
-preliminary results indicate that such models might be appropriate for
-geometries whose porosity is increasing under the process of erosion
-(Figure~\ref{fig:100tortuosity}). However, preliminary results also
-indicate that erosion can increase the amount of tortuosity as is
-evident towards the at the towards the end of the erosion process in
-Figure~\ref{fig:100tortuosity}. Moreover, we have observed a significant
-increase in the tortuosity at small porosities
-(Figure~\ref{fig:20tortuosity}.
+where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length, $u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of the trajectory starting at $(x_0,y_0)$ and ending at a vertical cross-section at the other end of the channel.
+Relationships between the tortuosity and porosity of a geometry have been developed by other groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and preliminary results indicate that such models might be appropriate for geometries whose porosity is increasing under the process of erosion (Figure~\ref{fig:100tortuosity}).
+However, preliminary results also indicate that erosion can increase the amount of tortuosity as is evident towards the at the towards the end of the erosion process in Figure~\ref{fig:100tortuosity}.
+Moreover, we have observed a significant increase in the tortuosity at small porosities (Figure~\ref{fig:20tortuosity}.
 
@@
 To better understand how erosion affects the anomalous dispersion, we propose to investigate how the pores grow with erosion.
-We will start with the notion of a {\em porelet} which is an individual Hagen-Poiseuille flow in each of the individual pores~\cite{dea-qua-bib-jua2018}.
+We will start with the notion of a {\em porelet} which is an individual Hagen-Poiseuille flow in each of the individual pores~\cite{dea-qua-bir-jua2018}.
 By computing the strength of the individual Hagen-Poiseuille flows, the shear rate can be computed, and thus the rate of erosion can be computed.
@@
 
+\todo[inline]{Advection diffusion done with the same method used to do
+dissolution. A lot of the next few paragraphs will be simplified}
 We propose to extend our preliminary results by considering
@@
 with an inverse Laplace transform~\cite{jos-war2006}.
+
+\todo[inline]{Talk about how to develop models for the pore sizes as a
+function of time. See results from S-H}
 
@@
 Once the essential features are learned, they will be incorporated into reduced-order models that utilize the multiphase framework to enable more efficient and larger scale coarse-grained simulations of dynamic erosion.
+        \todo[inline]{Nathan Kutz has a 2017 JFM 4 page paper that talks
+        about neural networks/deep learning in fluid dynamics}
 

### 2019-11-15 docs/proposals/NSF/ProjDesc/ProjDesc.tex
adding new files and working on text

@@
 \begin{alignat}{3}
-  \pd{c}{t} &= \frac{1}{\Pe} \Delta c, \quad &&\xx \in \Omega, \: t>0, .
+  \pd{c}{t} &= \frac{1}{\Pe} \Delta c, \quad &&\xx \in \Omega, \: t>0.
 \end{alignat}
@@
 \end{align}
-where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length, $u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of the trajectory starting at $(x_0,y_0)$ and ending at a vertical cross-section at the other end of the channel.
-Relationships between the tortuosity and porosity of a geometry have been developed by other groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and preliminary results indicate that such models might be appropriate for geometries whose porosity is increasing under the process of erosion (Figure~\ref{fig:100tortuosity}).
-However, preliminary results also indicate that erosion can increase the amount of tortuosity as is evident towards the at the towards the end of the erosion process in Figure~\ref{fig:100tortuosity}.
-Moreover, we have observed a significant increase in the tortuosity at small porosities (Figure~\ref{fig:20tortuosity}.
+where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length,
+$u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of
+the trajectory starting at $(x_0,y_0)$ and ending at a vertical
+cross-section at the other end of the channel. Relationships between the
+tortuosity and porosity of a geometry have been developed by other
+groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and
+preliminary results indicate that such models might be appropriate for
+geometries whose porosity is increasing under the process of erosion
+(Figure~\ref{fig:100tortuosity}(a)). However, preliminary results also
+indicate that erosion can increase the amount of tortuosity as is
+evident towards the at the towards the end of the erosion process in
+Figure~\ref{fig:100tortuosity}(a). Moreover, we have observed a
+significant increase in the tortuosity at small porosities
+(Figure~\ref{fig:100tortuosity}(b)).
 
@@
   \begin{subfigure}[b]{0.45\textwidth}
+  \includegraphics[width=\textwidth]{figs/tort_eulerian100}
+  \caption{100 eroding bodies}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
   \includegraphics[width=\textwidth]{figs/tort_eulerian20}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.45\textwidth}
-  \includegraphics[width=\textwidth]{figs/tort_eulerian100}
-  \caption{100 eroding bodies}
-  \end{subfigure}
   \end{center}
-
-  \caption{\label{fig:100tortuosity} The tortuosity of two eroding
-  geometries. The tortuosity can be computed using two different formulas
-  (red vs.~blue marks). The red square is the tortuosity in
-  Figure~\ref{fig:100tracers}. Their is qualitative agreement between
-  our numerical simulations and a power-law model (black dashed
-  line)~\cite{mat-kha-koz2008}.}
-  \todo[inline]{Fix caption and its references}
+  \caption{\label{fig:100tortuosity} The tortuosity of two eroding geometries.
+The tortuosity can be computed using two different formulas (red vs.~blue marks).
+In the left plot, the red square is the tortuosity of the geometry in Figure~\ref{fig:100tracers}.
+In both cases, there is qualitative agreement between our numerical simulations and a power-law model (black dashed line)~\cite{mat-kha-koz2008}.}
 \end{figure}
@@
 \end{align}
-Then, the standard deviation $\sigma_\lambda$ characterizes the
-dispersion, and long-time behavior typically results in a power-law
-scaling $\sigma_\lambda \sim t^{\alpha}$. The power $\alpha$, which
-quantifies the long-time spreading, is $1$ in a ballistic regime which
-occurs at early times when the trajectories have not explored much of
-the porous geometry. However, once the trajectories have traversed a few
-grains, dispersion in porous media is often super-dispersive with
-$\alpha \in (0.5,1)$~\cite{}. In Figure~\ref{fig:100dispersion}, we
-investigate spreading at several different porosities of a porous
-geometry that is initialized with 100 grains.
+Then, the standard deviation $\sigma_\lambda$ characterizes the dispersion, and long-time behavior typically results in a power-law scaling $\sigma_\lambda \sim t^{\alpha}$.
+The power $\alpha$, which quantifies the long-time spreading, is $1$ in a ballistic regime which occurs at early times when the trajectories have not explored much of the porous geometry.
+However, once the trajectories have traversed a few grains, dispersion in porous media is often super-dispersive with $\alpha \in (0.5,1)$~\cite{dea-leb-den-tar-bol-dav2013}.
+In Figure~\ref{fig:100dispersion}, we investigate spreading at several different porosities of a porous geometry that is initialized with 100 grains.
 \begin{wrapfigure}[]{r}{0.4\textwidth}
@@
 
-The rate of dispersion is known to be directly related to the pore size distribution~\cite{dea-qua-bir-jua2018}.
-Therefore, there is a need to understand how erosion affects the pore size distribution.
-In preliminary, we define pore sizes between grains that share an edge of a Delanuay triangulation with vertices at the grain centers (Figure~\ref{fig:Eroding100gap_mean_var}(a)).
+The rate of dispersion is known to be directly related to the pore size
+distribution~\cite{dea-qua-bir-jua2018}. Therefore, there is a need to
+understand how erosion affects the pore size distribution. In
+preliminary work~\cite{chi-moo-qua2019}, we define pore sizes between grains that share an edge of a Delanuay triangulation with vertices at the grain centers (Figure~\ref{fig:Eroding100gap_mean_var}(a)).
 In Figures~\ref{fig:Eroding100gap_mean_var}(a) and~\ref{fig:Eroding100gap_mean_var}(b), we plot the mean and variance of the pore sizes as a function of porosity.
@@
 
-\begin{figure}
+We have performed a carefully chosen simulation to better understand the
+effect of erosion on the pore size. We start with a single grain inside
+the channel that is sufficiently large that the spacing between the
+initial grain and the channel walls, which is 2 units wide), is
+$10^{-3}$. Since we use a Barycentric quadrature rule, we are able to
+stably simulate erosion with only 512 points on the eroding body which
+corresponds to an arclength spacing 12 times larger than the original
+separation distance---to achieve a comparable accuracy with the spectral
+trapezoid rule, 60 times as many discretization points would be
+required. In Figure~\ref{fig:}
+
+\begin{figure}[htp]
 \begin{subfigure}[b]{0.33\textwidth}
@@
 
-\todo[inline]{Advection diffusion done with the same method used to do
-dissolution. A lot of the next few paragraphs will be simplified}
 We propose to extend our preliminary results by considering
-concentrations with finite Peclet numbers. Numerical methods to solve
-the advection-diffusion equation~\eqref{eqn:advectionDiffusion} in a
-complex geometry poses several challenges that we will address.  We will
-start by splitting the advection and diffusion equations with a Strang
-splitting method~\cite{str1968}.  Numerical solutions of the advection
-equation will be formed with a semi-Lagrangian method~\cite{rob1981} so
-that it can be solved on an Eulerian grid without a restrictive CFL
-condition. PI Quaife has experience with using semi-Lagrangian
-methods for another type of complex viscous flow~\cite{kab-qua-bir2017}.
-The diffusion equation is more challenging to solve in a complex
-geometry with an integral equation formulation.  One approach is to use
-the space-time heat kernel~\cite{}, but this requires storing an entire
-time history of the solution.  Alternatively, the heat equation can be
-discretized in time and the resulting Yukawa equation is solved at each
-time step~\cite{kro-qua2010}. A particular challenge of this method is
-extending the forcing function from the complex geometry and into a
-regular geometry, such as a square, so that a high-order volume integral
-or Fourier method can be applied.  Recently, groups have used radial
-basis functions to form a sufficiently smooth
-extension~\cite{fry-kro-tor2019, fry-leh-tor2019}.
+concentrations with finite Peclet numbers. We will deploy the same
+numerical methods to simulate dissolution and melting to study a
+concentration that is being transported through a eroded porous
+geometry. Again, this will encompass Strang splitting~\cite{str1968}, a
+semi-Lagrangian advection solver~\cite{rob1981}, and a diffusion solver
+that solves an $s$-dependent Yukawa equation, where $s$ is the Laplace
+transform variable~\eqref{eqn:DiffusionLaplace}.
 
-We propose to develop a new method that uses the Laplace transform.
-Upon applying a Strang splitting, the resulting diffusion equation is
-\begin{alignat}{3}
-  \pd{c}{t} &= \frac{1}{\Pe} \Delta c, \quad &&\xx \in \Omega, \: t>0, \\
-  \pd{c}{\nn} &= 0, &&\xx \in \partial\Omega, \: t>0, \\
-  c(\xx,0) &= c_0(\xx), &&\xx \in \Omega.
-\end{alignat}
-Then, the Laplace transform, $C(\xx,s) = \mathcal{L}[c](\xx,t)$,
-satisfies
-\begin{align}
-  sC(\xx,s) - \frac{1}{\Pe}\Delta C(\xx,s) = c_0(\xx), 
-    \quad \xx \in \Omega
-\end{align}
-This PDE will be solved with high-order accuracy and efficiently by
-using fast-multipole-accelerated integral equation methods of the Yukawa
-equation~\cite{kro-qua2011}, and the concentration will be recovered
-with an inverse Laplace transform~\cite{jos-war2006}.
+\begin{wrapfigure}[]{r}{0.4\textwidth}
+  \includegraphics[width=0.4\textwidth]{figs/porelets_geom} \\ \\ \\
+  \includegraphics[width=0.4\textwidth]{figs/porelets_size}
+\end{wrapfigure}
 

### 2019-11-15 docs/proposals/NSF/ProjDesc/ProjDesc.tex
added in a new interesting (I think) result

@@
     \quad \xx \in \Omega,
+  \label{eqn:DiffusionLaplace}
 \end{align}
@@
 In Figure~\ref{fig:100dispersion}, we investigate spreading at several different porosities of a porous geometry that is initialized with 100 grains.
-\begin{wrapfigure}[]{r}{0.4\textwidth}
+\begin{wrapfigure}[22]{r}{0.4\textwidth}
   \includegraphics[width=0.4\textwidth]{figs/100b_second_moment_long_ref}
@@
   different porosities. At early times, the line of slope 1 (black
-  curve) indicates a ballistic motion. Then, at later times, the
+  curve) indicates a ballistic motion. At later times, the
   dispersion becomes super-dispersive at a rate indicated by the slope
@@
 trapezoid rule, 60 times as many discretization points would be
-required. In Figure~\ref{fig:}
+required. In Figure~\ref{fig:porelets}(a), different shades of grey
+correspond to the configuration of the eroding grain at five equally
+spaced time steps. At three of the time steps, we plot the velocity
+between the grain and the solid wall (black line). At all three
+configurations, the flow is nearly parabolic indicating that  porelet
+model~\cite{dea-qua-bir-jua2018} is appropriate. After performing a
+thorough analysis of the pore size growth in this simple configuration,
+we will develop a more complete model for networks of pores that are
+prevalent in porous media.
 
@@
 
-\begin{wrapfigure}[]{r}{0.4\textwidth}
-  \includegraphics[width=0.4\textwidth]{figs/porelets_geom} \\ \\ \\
-  \includegraphics[width=0.4\textwidth]{figs/porelets_size}
-\end{wrapfigure}
-
-\todo[inline]{Talk about how to develop models for the pore sizes as a
-function of time. See results from S-H}
+\begin{figure}[htp]
+  \centering
+  \begin{subfigure}[b]{0.47\textwidth}
+  \begin{center}
+  \includegraphics[height=0.55\textwidth]{figs/porelets_geom}
+  \end{center}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.47\textwidth}
+  \begin{center}
+  \includegraphics[height=0.55\textwidth]{figs/porelets_size}
+  \end{center}
+  \caption{}
+  \end{subfigure}
+  \caption{\label{fig:porelets} (a) An eroding body at five equally time steps in $[0,1]$.
+The far field condition is a constant pressure drop in a channel three times as wide as the eroding grain.
+At the three intermediate time steps, the velocity field in the field, which is nearly parabolic, is included.
+(b) The pore size (black) and maximum velocity in the pore (red) as a function of time.
+As the channel opens, the flow rate increases to maintain a constant pressure drop, and this increases the rate of erosion.}
+\end{figure}
 

### 2019-11-16 docs/proposals/NSF/ProjDesc/ProjDesc.tex
worked on some of the broader impact stuff

@@
   \end{center}
-  \caption{\label{fig:100tortuosity} The tortuosity of two eroding geometries.
+  \caption{\label{fig:100tortuosity} The tortuosity of two different eroding geometries.
 The tortuosity can be computed using two different formulas (red vs.~blue marks).
@@
 One central goal of this proposal is to enable the free motion of grains during the erosion processes.
-As mentioned above, this goal requires resolving contact forces between bodies, as well as the incorporation of the external buoyancy forces.
+As mentioned earlier, this goal requires resolving contact forces between bodies, as well as the incorporation of the external buoyancy forces.
 Once this goal is achieved, it will be possible to simulate a complex porous-medium of arbitrarily sized and shaped grains undergoing the simultaneous action of mechanical-or-chemical erosion and transport due to the combined effects of seepage, contact, and buoyancy forces.
@@
 These preliminary simulations are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
-They utilize the homogenized description of the flow field in \eqref{DarcyEq} and incorporate the physical effects of:
+They utilize the homogenized description of the flow field in~\eqref{DarcyEq} and incorporate the physical effects of:
 \begin{itemize}[noitemsep]
@@
 These simulation have not yet begun to incorporate the slow-acting effects of mechanical and chemical erosion, and the associated gradual changes in medium properties.
-A grand goal of this proposal would be to merge the two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short term events, such as sinkhole collapse, and long-term changes in the medium.
+A grand goal of this proposal would be to merge the two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short-term events, such as sinkhole collapse, and long-term changes in the medium.
 The greatest challenge faced is the disparate temporal and spatial scales that must be considered.
@@
 
-	More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties.
-The output of the high-fidelity simulations can be transformed into essential an image format, enabling us to use cutting-edge advancements on deep neural-networks for image analysis \cite{pelt2018mixed}.
+More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.
+The output of the high-fidelity simulations of the grain configuration can be transformed into essentially an image format, enabling us to use cutting-edge advancements on deep neural-networks for image analysis~\cite{pelt2018mixed}.
 Some important advantages of referenced work are the use of dilated convolutions in a deeply connected network, which first mixes scales and second reduces the number of super-parameters present and thus largely averts the risk of overfitting data.
+Additionally, high-fidelity flow conditions can be used to train a neural network, and this has been successfully used by others to predict, as one example, an anisotropy tensor~\cite{ling2016reynolds}.
 Both PIs will supervise a graduate student who will design and implement the deep-neural network for learning the essence of the high-fidelity simulations.
 Once the essential features are learned, they will be incorporated into reduced-order models that utilize the multiphase framework to enable more efficient and larger scale coarse-grained simulations of dynamic erosion.
-        \todo[inline]{Nathan Kutz has a 2017 JFM 4 page paper that talks
-        about neural networks/deep learning in fluid dynamics}
 
 As mentioned previously, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments~\cite{tao2014experimental}.
-Firstly, already existing data from these experiments offers a testbed for comparison against our newly developed simulations.
-Furthermore, we propose to run a set of new experiments at the facilities offered by GFDI, spearheaded by an undergraduate student in close collaboration with the graduate students and PIs.
-These new experiments will more deeply probe the mechanisms underlying sinkhole formation with the special design goal of comparison agains the numerical simulations.
+First, already existing data from these experiments offers a testbed for comparison against our newly developed simulations.
+Furthermore, we propose to run a set of new experiments at the facilities offered by GFDI, spearheaded by an undergraduate student in close collaboration with the graduate students, PIs, and an experimentalist at GFDI.
+These new experiments will more deeply probe the mechanisms underlying sinkhole formation with the special design goal of comparison against the numerical simulations.
 These experiments will be used to calibrate and validate our computations.
@@
 
-	This research proposed here could lead to a range of societal benefits, including better management of water resources, accurate prediction of contaminant transport, and an understanding of the long-term effects of human activities, such as hydraulic fracturing or groundwater pumping, on porous media and water resources.
+The proposed research could lead to a range of societal benefits, including better management of water resources, accurate prediction of contaminant transport, and an understanding of the long-term effects of human activities, such as hydraulic fracturing or groundwater pumping, on porous media and water resources.
 In such scenarios, the slow timescales of mechanical and chemical erosion are coupled to the faster timescales of human-induced changes and gravitational collapse.
@@
 \subsection{Graduate research}
-
 An important benefit of the research proposed here is the potential to immerse graduate students in fundamentally {\em cross-disciplinary} research.
@@
 
-	Naturally, the research proposed here will form the foundation for the PhD dissertations of the graduate students involved.
-Beyond this, the students will engage in publishing articles in peer-reviewed journals of high quality and attending national and international conferences at which they will contribute presentations on their work.
-The PIs will closely mentor the graduate students to ensure their continued development, not only intellectually, but also in the `soft' skills of communication, promotion, and networking.
-Having both PIs Moore and Quaife involved in the training of each graduate student is especially valuable for offering multiple perspectives on these issues.
-The PIs will make special efforts to recruit women and underrepresented minorities as the graduate students funded by this project.
-PI Moore has already had success recruiting women in these roles, as the first graduate student to receive her PhD under Moore's advising was female (Karina Khazmutdinova, 2016).
+Naturally, the research proposed here will form the foundation for the
+PhD dissertations of the graduate students involved. Beyond this, the
+students will engage in publishing articles in peer-reviewed journals of
+high quality and attending national and international conferences where
+they will present their work and network with experts in the field. The
+PIs will closely mentor the graduate students to ensure their continued
+development, not only intellectually, but also in the `soft' skills of
+communication, promotion, and networking. Having both PIs Moore and
+Quaife involved in the training of each graduate student is especially
+valuable for offering multiple perspectives on these issues. The PIs
+will make special efforts to recruit women and underrepresented
+minorities as the graduate students funded by this project. Both PIs
+have already had success recruiting women in these roles, as the first
+graduate student to receive her PhD under Moore's advising was female
+(Karina Khazmutdinova, 2016), and Quaife's current PhD student is female
+(Ashley Gannon, 2022).
 
+\todo[inline]{Bryan is here}
 \subsection{Undergraduate research}
-
 Regarding undergraduate research, the ideas in this proposal represent a rich and fascinating topic for undergraduate students, while also being approachable these students.
@@
 
-\subsection{Outreach for K-12 and the general public}
+\subsection{Outreach for K--12 and the general public}
 
+\todo[inline]{FSU's YSP}
 The PIs have already seized the opportunity to engage K-12 students in outreach activities.

### 2019-11-16 docs/proposals/NSF/ProjDesc/ProjDesc.tex
worked on later sections and added a few comments throughout

@@
 \end{align}
-where $\nn$ and $\ss$ are the unit normal and tangent vectors on the surface respectively and $\uu$ is the velocity field as computed from the incompressible Stokes equations \eqref{StokesEq}. 
+where $\nn$ and $\ss$ are the unit normal and tangent vectors on the surface respectively and $\uu$ is the velocity field as computed from the incompressible Stokes equations~\eqref{StokesEq}. 
 The motion of the interface is proportional to the absolute value of shear
@@
 
- Figure \ref{fig1} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
+Fig.~\ref{fig1} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
 The figure shows 80 bodies of initially random size and position, undergoing erosion.
@@
 The middle plot shows the resistivity, or inverse permeability of the medium.
-In the simulations, resistivity is calculated by measuring the total flux and the pressure upstream and downstream, then using Darcy's relation \eqref{DarcyEq} to infer the horizontal permeability $k_x$.
+In the simulations, resistivity is calculated by measuring the total flux and the pressure upstream and downstream, then using Darcy's relation~\eqref{DarcyEq} to infer the horizontal permeability $k_x$.
 Naturally, as bodies erode, the resistivity they provide decreases in time.
@@
 In a fluid context, this method was first introduced by Lu et al.~\cite{lu-rah-zor2017}, and extended to allow for much smaller separation distances of rigid bodies by the PI's previous graduate student~\cite{bys-sha-qua2019}.
-One Ph.D.~student, who will be jointly supervised by both PIs, will simulate sedimentation of eroding bodies by developing algorithms that resolve quadrature error and contact.
+One PhD student, who will be jointly supervised by both PIs, will simulate sedimentation of eroding bodies by developing algorithms that resolve quadrature error and contact.
 
@@
 
-\begin{wrapfigure}[]{r}{0.3\textwidth}
-  \includegraphics[width=0.3\textwidth]{figs/100b_t100tracer}
+\begin{wrapfigure}[]{r}{0.5\textwidth}
+  \includegraphics[width=0.5\textwidth]{figs/100b_t100tracer}
   \caption{\label{fig:100tracers} A visualization of the streamlines
@@
 characteristics of the concentration field are identical to the
-streamlines (Figure~\ref{fig:100tracers}).
+streamlines (Fig.~\ref{fig:100tracers}).
 
@@
 geometries whose porosity is increasing under the process of erosion
-(Figure~\ref{fig:100tortuosity}(a)). However, preliminary results also
+(Fig.~\ref{fig:100tortuosity}(a)). However, preliminary results also
 indicate that erosion can increase the amount of tortuosity as is
 evident towards the at the towards the end of the erosion process in
-Figure~\ref{fig:100tortuosity}(a). Moreover, we have observed a
+Fig.~\ref{fig:100tortuosity}(a). Moreover, we have observed a
 significant increase in the tortuosity at small porosities
-(Figure~\ref{fig:100tortuosity}(b)).
+(Fig.~\ref{fig:100tortuosity}(b)).
 
@@
 The tortuosity can be computed using two different formulas (red vs.~blue marks).
-In the left plot, the red square is the tortuosity of the geometry in Figure~\ref{fig:100tracers}.
+In the left plot, the red square is the tortuosity of the geometry in Fig.~\ref{fig:100tracers}.
 In both cases, there is qualitative agreement between our numerical simulations and a power-law model (black dashed line)~\cite{mat-kha-koz2008}.}
@@
 \end{align}
-Then, the standard deviation $\sigma_\lambda$ characterizes the dispersion, and long-time behavior typically results in a power-law scaling $\sigma_\lambda \sim t^{\alpha}$.
-The power $\alpha$, which quantifies the long-time spreading, is $1$ in a ballistic regime which occurs at early times when the trajectories have not explored much of the porous geometry.
-However, once the trajectories have traversed a few grains, dispersion in porous media is often super-dispersive with $\alpha \in (0.5,1)$~\cite{dea-leb-den-tar-bol-dav2013}.
-In Figure~\ref{fig:100dispersion}, we investigate spreading at several different porosities of a porous geometry that is initialized with 100 grains.
+Then, the standard deviation $\sigma_\lambda$ characterizes the
+dispersion, and long-time behavior typically results in a power-law
+scaling $\sigma_\lambda \sim t^{\alpha}$. The power $\alpha$, which
+quantifies the long-time spreading, is $1$ in a ballistic regime which
+occurs at early times when the trajectories have not explored much of
+the porous geometry. However, once the trajectories have traversed a few
+grains, dispersion in porous media is often super-dispersive with
+$\alpha \in (0.5,1)$~\cite{dea-leb-den-tar-bol-dav2013}.
+In Fig.~\ref{fig:100dispersion}, we investigate spreading at several different porosities of a porous geometry that is initialized with 100 grains.
 \begin{wrapfigure}[22]{r}{0.4\textwidth}
@@
 understand how erosion affects the pore size distribution. In
-preliminary work~\cite{chi-moo-qua2019}, we define pore sizes between grains that share an edge of a Delanuay triangulation with vertices at the grain centers (Figure~\ref{fig:Eroding100gap_mean_var}(a)).
-In Figures~\ref{fig:Eroding100gap_mean_var}(a) and~\ref{fig:Eroding100gap_mean_var}(b), we plot the mean and variance of the pore sizes as a function of porosity.
+preliminary work~\cite{chi-moo-qua2019}, we define pore sizes between
+grains that share an edge of a Delanuay triangulation with vertices at
+the grain centers (Fig.~\ref{fig:Eroding100gap_mean_var}(a)).
+In Fig.~\ref{fig:Eroding100gap_mean_var}(a) and~\ref{fig:Eroding100gap_mean_var}(b), we plot the mean and variance of the pore sizes as a function of porosity.
 To better understand how erosion affects the anomalous dispersion, we propose to investigate how the pores grow with erosion.
@@
 trapezoid rule, 60 times as many discretization points would be
-required. In Figure~\ref{fig:porelets}(a), different shades of grey
+required. In Fig.~\ref{fig:porelets}(a), different shades of grey
 correspond to the configuration of the eroding grain at five equally
@@
 
-These simulation have not yet begun to incorporate the slow-acting effects of mechanical and chemical erosion, and the associated gradual changes in medium properties.
+\todo[inline]{Eventually, our FMM solver will reach its capacity. We
+need to talk about fast summation methods for the barycentric
+quadrature, deformation tensor, vorticity, and pressure. In addition to
+fast summation methods, we can talk about parallel implementations. I
+have new PhD student in DSC that wants to work on erosion and he has
+experience running MPI and OpenMP.}
+
+These simulations have not yet begun to incorporate the slow-acting effects of mechanical and chemical erosion, and the associated gradual changes in medium properties.
 A grand goal of this proposal would be to merge the two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short-term events, such as sinkhole collapse, and long-term changes in the medium.
@@
 
-\todo[inline]{Bryan is here}
 \subsection{Undergraduate research}
@@
 This work resulted in one {\em peer-reviewed} publication already~\cite{Bolles2019}, with a second to be submitted soon.
+In addition, PI Quaife successfully trained an undergraduate student, Miles Currie, in a statistical analysis of flows related to prescribed fire dynamics.
+This work resulted in a peer-reviewed publication~\cite{cur-spe-hie-obr-goo-qua2018}.
 
@@
 \subsection{Outreach for K--12 and the general public}
-
-\todo[inline]{FSU's YSP}
-The PIs have already seized the opportunity to engage K-12 students in outreach activities.
-In particular, Moore's research was the focus of an educational video created by {\bf CPALMS}, which is the State of Florida's official source for standards information and course descriptions for K-12 education.
-The video, which features an interview and animations of research, is used to reinforce concepts from mathematics courses (grade levels 7-12), and to encourage students to consider a career in the STEM fields~\cite{CPALMS}.
-Additionally, these videos are frequently used for the continuing education of K-12 {\em teachers}, providing them a broader perspective of mathematics that could be integrated into their teaching.
+The PIs have already seized the opportunity to engage K--12 students in outreach activities.
+In particular, PI Moore's research was the focus of an educational video created by {\bf CPALMS}, which is the State of Florida's official source for standards information and course descriptions for K--12 education.
+The video, which features an interview and animations of research, is used to reinforce concepts from mathematics courses (grade levels 7--12), and to encourage students to consider a career in the STEM fields~\cite{CPALMS}.
+Additionally, these videos are frequently used for the continuing education of K--12 {\em teachers}, providing them a broader perspective of mathematics that could be integrated into their teaching.
 
@@
 Laboratory materials for the demo are available at GFDI.
+
+FSU also provides an opportunity to expose high school students to university-level research through the {\bf Young Scholars Program (YSP)}.
+The YSP is a six week experience that brings Florida's brightest grade 11 students to FSU where they are exposed to university-level lectures and work with FSU faculty on a research project.
+PI Quaife participated in this program in Summer 2016.
+The PIs will propose research projects that are accessible to high school students throughout the duration of the proposed research.
+In addition to high school students receiving a high school experience, the PhD students will be tasked with much of the day-to-day interaction with the high school students.
+This offers an excellent opportunity for the PhD students to develop leadership and mentorship skills.
 

### 2019-11-16 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 Likewise, chemical dissolution can carve well-defined conduit paths in karst networks which strongly alter transport properties~\cite{szymczak2009wormhole}.
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.99 \textwidth]{./figs/collage.pdf}
+\caption{\label{fig1} Geophysical examples of chemical and mechanical erosion.
+Top from left: Diagram of a coupled karst-soil system with conduit formation \cite{watson2019sinkholes}; Limestone pavement in Dent de Crolles, France; Nohoch Ch’en Sinkhole in Belize.
+Bottom: examples of soil erosion.
+The bottom right shows the microscopic soil texture.}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 

### 2019-11-16 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 \includegraphics[width = 0.99 \textwidth]{./figs/collage.pdf}
-\caption{\label{fig1} Geophysical examples of chemical and mechanical erosion.
+\caption{\label{collage} Geophysical examples of chemical and mechanical erosion.
 Top from left: Diagram of a coupled karst-soil system with conduit formation \cite{watson2019sinkholes}; Limestone pavement in Dent de Crolles, France; Nohoch Ch’en Sinkhole in Belize.
@@
 Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute, which would help to guide, calibrate, and validate the computations (see letter of collaboration).
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htbp]
+\begin{center}
+\includegraphics[width = 0.99 \textwidth]{./figs/80circ8vel.pdf}
+\caption{\label{80circ8vel} High-fidelity numerical simulations of a configuration of densely-packed solid bodies undergoing mechanical erosion due to an intervening Stokes flow.
+Color indicates velocity magnitude which highlights the channel formation process.
+The solid bodies develop flat faces and sharp corners during evolution.
+}
+%The same simulation as above with velocity magnitude in color. Velocity magnitude highlights the most dominant channels whose growth is reinforced by the shape-flow interaction of erosion.
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 
@@
 \includegraphics[width = 0.99 \textwidth]{./figs/80circ8vort.pdf}
-\caption{\label{fig1} Simulation of 80 bodies eroding in Stokes flow under the action of shear stress.
+\caption{\label{80circ8vort} Simulation of 80 bodies eroding in Stokes flow under the action of shear stress.
 Flow is left to right.
@@
 
-Fig.~\ref{fig1} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
+Fig.~\ref{80circ8vort} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
 The figure shows 80 bodies of initially random size and position, undergoing erosion.
@@
 In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
-The channelization process is made more evident by visualization of the velocity magnitude, as in Fig.~\ref{fig2}.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.99 \textwidth]{./figs/80circ8vel.pdf}
-\caption{\label{fig2} The same simulation as above with velocity magnitude in color.
-Velocity magnitude highlights the most dominant channels whose growth is reinforced by the shape-flow interaction of erosion.}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+The channelization process is made more evident by visualization of the velocity magnitude, as seen in Fig.~\ref{80circ8vel}.
 

### 2019-11-17 docs/proposals/NSF/ProjDesc/ProjDesc.tex
working on restrucuturing and writing

@@
 %% INTRODUCTION
-\section{Proposed Research}
-
-\subsection{Introduction and Background}
-
+\section{Introduction and Background}
 Naturally occurring porous and granular materials, such as soil, sand, and clay, play a pivotal role in regulating earth's water resources by filtering contaminants and, over long timescales, supplying fresh water.
@@
 
-This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow can alter porous-media properties and to characterize the associated changes in transport within the evolving medium, for example the anomalous dispersion of tracers.
-A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{lin2018randomization}.
+{\bf This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow can alter porous-media properties and to characterize the associated changes in transport within the evolving medium.} A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{lin2018randomization}.
 These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material.
@@
 These challenges require innovative computational techniques, some of which have been developed recently~\cite{Quaife2018} and others that await resolution.
-An ultimate goal of this proposal is to achieve high-fidelity simulations of $\mathcal{O}(100-1000)$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.
-Dynamic erosion of porous media is a highly active area of research, as closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
+{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(100-1000)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} Dynamic erosion of porous media is a highly active area of research, as closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
 These experiments a great opportunity for comparison against our numerical simulations.
-Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute, which would help to guide, calibrate, and validate the computations (see letter of collaboration).
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
-\begin{center}
-\includegraphics[width = 0.99 \textwidth]{./figs/80circ8vel.pdf}
-\caption{\label{80circ8vel} High-fidelity numerical simulations of a configuration of densely-packed solid bodies undergoing mechanical erosion due to an intervening Stokes flow.
-Color indicates velocity magnitude which highlights the channel formation process.
-The solid bodies develop flat faces and sharp corners during evolution.
-}
-%The same simulation as above with velocity magnitude in color. Velocity magnitude highlights the most dominant channels whose growth is reinforced by the shape-flow interaction of erosion.
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute (see Section~\ref{sec:experiments}), which would help to guide, calibrate, and validate the computations (see letter of collaboration).
 
@@
 These scaled-down experiments offer the ability to probe various mechanisms behind sinkhole formation, for example a difference in hydraulic head between the confined and unconfined aquifers.
-An ultimate goal of the project proposed here is to merge these two lines of inquiry to gain a deeper understanding of the influence of mechanically or chemically induced erosion on gravitational collapse.
+An ultimate goal of the proposed project is to merge these two lines of inquiry to gain a deeper understanding of the influence of mechanically or chemically induced erosion on gravitational collapse.
 Ultimately, we envision the high-fidelity erosion simulations to inform coarse-grained models for: (i) transport and dispersion; and (ii) dynamic evolution of macroscopic medium properties.
@@
 
-%---------------------------------------------------------------------------------------------------%
-\subsection{Governing equations}
-
-We first summarize governing equations underlying the proposed work.
-At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations
-\begin{equation}
-\label{StokesEq}
+%----------------------------------------------------------------------%
+\subsection{Governing Equations}
+At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations \begin{equation}
+\label{eqn:StokesEq}
 \begin{split}
@@
 \end{equation}
-where $\uu$ is the velocity field, $p$ the pressure field, and $\mu$ the fluid viscosity.
-Linear elliptic PDEs, such as the Stokes equations, can be reformulated as a boundary integral equation (BIE).
-BIEs have several numerical advantages including a dimension reduction, automatic mass conservation, and high-order accuracy.
-An equivalent BIE formulation of the Stokes equations in Eq.~\eqref{StokesEq} is
+where $\uu$ is the velocity field, $p$ the pressure field, $\mu$ the
+fluid viscosity, and $\Omega$ is the fluid domain. Linear elliptic PDEs,
+such as the Stokes equations, can be reformulated as a boundary integral
+equation (BIE).  BIEs have several numerical advantages including a
+dimension reduction, automatic mass conservation, and high-order
+accuracy. An equivalent BIE formulation of the Stokes equations in
+Eq.~\eqref{eqn:StokesEq} is
 \begin{align}
@@
     \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
-    \eeta(\yy) ds_\yy, \quad \xx \in \bd\Omega
+    \eeta(\yy) ds_\yy, \quad \xx \in \bd\Omega,
 \end{align}
@@
 
-Eq.~\eqref{StokesEq} is a microscopic description is required to study the shape evolution of individual grains due to fine-scale erosive effects, either mechanical or chemical.
+Eq.~\eqref{eqn:StokesEq}, and its equivalent integral equation formulation, are microscopic descriptions that are required to study the shape evolution of individual grains due to fine-scale erosive effects, either mechanical or chemical.
 The description, however, becomes impractical when attempting to model seepage in very large porous systems where the microscopic geometry can be exceedingly complex.
@@
 
-While the most immediate proposed work on computational methods to simulate erosion will utilize~\eqref{StokesEq}, the later stages of this project will also incorporate~\eqref{DarcyEq}, or closely related variants known as multiphase models~\cite{Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
+While the most immediate proposed work on computational methods to
+simulate erosion will utilize~\eqref{eqn:StokesEq}, the later stages of this project will also incorporate~\eqref{DarcyEq}, or closely related variants known as multiphase models~\cite{Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
 These models will rely on statistical analysis of the data produced by the high-fidelity erosion simulations in order to parameterize the effects of erosion, leading to deterministic or stochastic reduced-order models for porous-medium evolution.
@@
 
-%---------------------------------------------------------------------------------------------------%
-\subsection{Mechanical and chemical erosion of a porous medium}
+%----------------------------------------------------------------------%
+\subsection{Project Overview}
 
-The first problem discussed here is the erosion of a porous medium, as has been preliminarily investigated in~\cite{Quaife2018}.
+\paragraph{Broader Impacts:} The proposed research could lead to a range of societal benefits, including better management of water resources, accurate prediction of contaminant transport, and an understanding of the long-term effects of human activities, such as hydraulic fracturing or groundwater pumping, on porous media and water resources.
+In such scenarios, the slow timescales of mechanical and chemical erosion are coupled to the faster timescales of human-induced changes and gravitational collapse.
+Currently, the relationship between these scales is poorly understood.
+The high-fidelity, efficient computational methods proposed here will enable a deeper understanding of these processes, which is the first step towards developing effective strategies for managing water resources and mitigating catastrophic events such as contamination or structural collapse.
+For example, the insights gained here could potentially help identify locations in natural aquifers vulnerable to contamination and/or collapse.
+
+In addition to these societal impacts, the work proposed here will spur the training of mathematicians and computational scientists in fundamentally cross-disciplinary research of great societal importance.
+Further, the PIs will engage in educational and outreach activities to impact future generations of mathematical scientists, with particular focus on women and underrepresented minorities (URM).
+Both PIs are already actively involved in graduate and undergraduate research, as well as outreach to K-12 students.
+Further, we have successfully recruited women and underrepresented minorities in undergraduate, graduate, and postdoctoral research.
+
+\paragraph{Intellectual Merit:} The proposed research introduces a host of new computational challenges and opportunities.
+First the range of scales is vast: spatial scales range from microscopic granular constituents to large geological aquifers; timescales range from that of a sudden sinkhole collapse to years required mechanical and chemical erosion.
+The systems are inherently multicomponent, with coupling between the fluid and solid phases.
+Although the governing PDEs are linear, the presence of moving boundaries introduces nonlinear feedback between geometry and flow.
+To tackle these challenges, the PIs will combine cutting-edge computational tools with reduced-order modeling.
+Mixed-scale, deep neural networks will be used to learn from the data generated by high-fidelity numerical simulations to parameterize coarse-grained models based on the multiphase framework.
+Additionally, controlled laboratory experiments will be used to guide and verify theory developed herein.
+
+\paragraph{Relevance to the Computational Mathematics Synopsis:}
+\begin{itemize}[noitemsep]
+  \item Computational plays an essential role to simulate erosion of porous medium.
+
+  \item The proposed research is directly applicable to several geophysical applications.
+
+  \item The proposed research is a collaborative effort and will include graduate, undergraduate, and K--12 students
+\end{itemize}
+
+\paragraph{Results from Prior NSF Support:} Neither PI has previous funding from NSF.
+
+\paragraph{PIs' Qualifications:} PI Moore joined the Department of Mathematics at Florida State University (FSU) in 2014, and is also a Research Associate in FSU's Geophysical Fluid Dynamics Institute (GFDI).
+His expertise includes modeling dynamic interactions between fluids and structures, especially in geophysical and biologically motivated settings.
+PI Quaife joined the Department of Scientific Computing at FSU in 2015 and is also a Research Associate in GFDI.
+His expertise includes high-fidelity and efficient numerical methods for fluid dynamic in complex geometries.
+
+The PIs co-authored a paper describing numerical methods for simulating erosion~\cite{Quaife2018} in a viscous fluid.
+Very recently, a second paper has been submitted to the Journal of Fluid Mechanics~\cite{chi-moo-qua2019}, where additional numerical methods are developed and characterizations of transport are presented.
+
+\paragraph{Outline of the Proposal:}
+
+\todo[inline]{Summary of what is in the proposal.}
+
+%----------------------------------------------------------------------%
+\section{Proposed Research} 
+%----------------------------------------------------------------------%
+\todo[inline]{Discuss what the main research questions are here}
+\begin{itemize}[noitemsep]
+  \item Characterize anisotropy and permeability to inform homogenized
+    models including Darcy's relation.
+
+  \item Improve numerical methods including FMM, preconditioners, and
+    quadrature.
+
+  \item Simulate erosion via chemical reactions ie.~dissolution.
+
+  \item Simulate transport of finite Peclet number species in eroded
+    geometries.
+\end{itemize}
+
+%----------------------------------------------------------------------%
+\subsection{Mechanical and Chemical Erosion of a Porous Medium}
+With the development of efficient and high-fidelity numerical methods to solve the Stokes equations, we are able to simulate erosion.
 We will consider erosion induced by either fluid-mechanical forces or by chemical reaction, i.e.~dissolution.
-In the former case, erosion results from surface shear stress
-\begin{align}
-\tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss \, .
-\end{align}
-where $\nn$ and $\ss$ are the unit normal and tangent vectors on the surface respectively and $\uu$ is the velocity field as computed from the incompressible Stokes equations~\eqref{StokesEq}. 
+In the former case, which we have already begun to investigate~\cite{Quaife2018}, erosion result from the shear stress $\tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss$, where $\nn$ and $\ss$ are the unit normal and tangent vectors on the surface respectively and $\uu$ is the velocity field as computed from the incompressible Stokes equations~\eqref{eqn:StokesEq}.
 The motion of the interface is proportional to the absolute value of shear
 \begin{align}
-\Vn = \CE \, \abs{\tau},
+  \Vn = \CE \, \abs{\tau}.
 \end{align}
-In the latter case of chemically-induced erosion, a solute concentration field $C$ undergoes advection and diffusion:
+In the case of chemically-induced erosion, a solute concentration field $C$ undergoes advection and diffusion:
 \begin{align}
   \label{Ceq}
-& \pd{C}{t} + \uu \cdot \grad C = \Diff \Lap C \, ,
+  \pd{C}{t} + \uu \cdot \grad C = \Diff \Lap C.
 \end{align}
@@
 \label{DissVn}
-\Vn = \left. \Diff \pd{C}{\ny} \right. %\right\vert_{\bdry} \, ,
+\Vn = \Diff \pd{C}{\ny}.
 \end{equation}
-Both processes have been investigated by the PIs and collaborators in
-the context of single bodies in high Reynolds-number
-flows~\cite{Ristroph2012, MoorePOF2013, HuangJFM2015, MooreCPAM2017}. In
-the low-Reynolds regime of porous-media flow, numerical methods have
-been developed by the PIs to simulate shear-induced
-erosion~\cite{Quaife2018}. These simulations combine highly accurate
-boundary integral methods with stable interface evolution techniques.
-The boundary integral solver is accelerated by the fast multipole
-method~\cite{gre-rok1987, gre-gre-may1992} to achieve optimal $O(N)$
-complexity. Meanwhile, the so-called {\thL} method is used for interface
-evolution to prevent distortion and tangling of the interface meshes~\cite{hou1994removing, MoorePOF2013, Quaife2018}.
-%A near-term goal is to adapt these methods to handle the case of chemically-induced dissolution.
-
-%\subsubsection{Basic dynamics}
+Both erosion processes have been investigated by the PIs and collaborators in the context of single bodies in high Reynolds-number flows~\cite{Ristroph2012, MoorePOF2013, HuangJFM2015, MooreCPAM2017}.
+In the context of a porous media at low Reynolds-number flows, numerical methods have been developed by the PIs to simulate shear-induced erosion~\cite{Quaife2018, chi-moo-qua2019}.
+These simulations combine highly accurate boundary integral methods with stable interface evolution techniques.
+The boundary integral solver is accelerated by the fast multipole method~\cite{gre-rok1987, gre-gre-may1992} to achieve optimal $O(N)$ complexity.
+Meanwhile, the so-called {\thL} method is used for interface evolution to prevent distortion and tangling of the interface meshes~\cite{hou1994removing, MoorePOF2013, Quaife2018}.
 
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
+\begin{figure}[htp]
 \begin{center}
@@
 Color represents vorticity, which provides a convenient way to visualize local shear rates.
-%Erosion not only diminishes the size of the bodies but also alters their shapes considerably.
-A few well-defined channels develop in the space between bodies.
-Several of the bodies vanish in finite time and the simulation continues without interruption.
 }
@@
 
-Fig.~\ref{80circ8vort} shows preliminary results of multiple bodies undergoing mechanical erosion in Stokes flow.
-The figure shows 80 bodies of initially random size and position, undergoing erosion.
-This figure extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed Barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015}, which enables closer contact between bodies and thus more bodies.
-The color shows the (normalized) vorticity field surrounding the bodies.
-Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity.
+Figs.~\ref{80circ8vort} and~\ref{80circ8vel} show preliminary results of 80 bodies, initially of random position and size, undergoing mechanical erosion in Stokes flow.
+This simulation extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed Barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015, chi-moo-qua2019}, which enables closer contact between bodies and thus more bodies.
+The color in Fig~\ref{80circ8vort} shows the (normalized) vorticity field surrounding the bodies.
+Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity (Fig.~\ref{80circ8vel}).
 Observe that erosion not only reduces the size of solid bodies, but also alters their shapes substantially.
@@
 In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
-The channelization process is made more evident by visualization of the velocity magnitude, as seen in Fig.~\ref{80circ8vel}.
 
-%\subsubsection{Evolution of macroscopic properties}
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}[htp]
+\begin{center}
+\includegraphics[width = 0.99 \textwidth]{./figs/80circ8vel.pdf}
+\caption{\label{80circ8vel} High-fidelity numerical simulations of a configuration of densely-packed solid bodies undergoing mechanical erosion due to an intervening Stokes flow.
+The color indicates velocity magnitude which highlights the channel formation process.
+The solid bodies develop flat faces and sharp corners during evolution.
+}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 
@@
 First, the left-most plot shows the rate at which the area fraction decreases as the bodies erode.
-%Time is normalized by the value $t_f$ at which all bodies vanish and hence the area fraction is zero. 
 Notice that the rate of area reduction does not change significantly during the simulation.
@@
 
-Lastly, the right-most plot of Fig.~\ref{fig3} shows the anisotropy, which is calculated as the ratio of the vertical resistivity to the horizontal resistivity, see Eq.~\eqref{DarcyEq}.
+Lastly, the right-most plot of Fig.~\ref{fig3} shows the anisotropy, which is calculated as the ratio of the vertical resistivity to the horizontal resistivity.
 The vertical resistivity is computed by rotating the configuration of bodies by 90 degrees.
@@
 Thus, the initially isotropic state becomes erased as bodies streamline and form primarily horizontal channels.
-Remarkably, the medium reaches an anisotropy of over 10, meaning that erosion can lead to a configuration that resists flow 10 times more in the vertically than horizontally.
+Remarkably, the medium reaches an anisotropy of over 10, meaning that erosion can lead to a configuration that resists flow 10 times more in the vertical direction than the horizontal direction.
 
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}%[htbp]
+\begin{figure}[htp]
 \begin{center}
 \includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
-\caption{\label{fig3} Left: the area fraction of solid bodies versus time.
+  \caption{\label{fig3} {\em Left}: The area fraction of solid bodies versus time.
 Time is normalized by the vanishing time $t_f$.
-Middle: the resistivity of the porous matrix decrease much more rapidly than area fraction, indicating the reshaping process to be essential.
-Right: the anisotropy (ratio of vertical to horizontal resistivity) as it varies in time.
-Erosion can create a highly anisotropic medium.
-}
+{\em Middle}: The resistivity of the porous matrix decrease much more rapidly than area fraction, indicating the reshaping process to be essential.
+Right: The anisotropy (ratio of vertical to horizontal resistivity) as it varies in time.
+Erosion can create a highly anisotropic medium.}
 \end{center}
@@
 
-%\subsubsection{Immediate goals of proposed work}
-
-An immediate goal of the proposed work is extend the range of physical effects captured in these simulations.
+An immediate goal of the proposed work is to extend the range of physical effects captured in these simulations.
 A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
@@
 This quadrature approach has the advantage that it is a non-intrusive modification of the trapezoid rule, allowing us to achieve an error bound that independent of the grain configuration.
-Near-term plans are to include flow transport and gravitational sedimentation of the eroding grains.
-For this extension, contact forces between bodies must be included to eliminate unphysical contact that is inevitable due to discretization errors.
-
-Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research.
-One approach is to use introduce a potential with short-range repulsion, but such methods often introduce stiffness.
-Alternatively, a space-time interference volume can guarantee a minimum separation between grains.
-In a fluid context, this method was first introduced by Lu et al.~\cite{lu-rah-zor2017}, and extended to allow for much smaller separation distances of rigid bodies by the PI's previous graduate student~\cite{bys-sha-qua2019}.
-One PhD student, who will be jointly supervised by both PIs, will simulate sedimentation of eroding bodies by developing algorithms that resolve quadrature error and contact.
+However, the implementation of the quadrature method does not fully use FMM acceleration.
+The numerical challenge is developing the required FMM expansions for the velocity, vorticity, and deformation tensor layer potentials.
+Since we require several layer potentials with different kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and its implementations that are readily available (for example, see \url{http://pvfmm.org}).
+Other challenges that will be investigated include preconditioning strategies to reduce the number of required GMRES iterations, and time adaptivity to allow for stable simulations to user-specified tolerances.
+PI Quaife has experience developing such algorithms~\cite{qua-bir2015b, qua-bir2016, qua-bir2015a, qua-cou-dar2018}.
 
@@
 For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations, is already in place, but the coupling to the advection-diffusion equations~\eqref{Ceq} and interface law~\eqref{DissVn} need to be implemented.
-We proposed to solve the advection diffusion equation~\eqref{Ceq} by first using Strang splitting~\cite{str1968} to decompose the PDE into linear advection and diffusion.
+We proposed to solve the advection-diffusion equation~\eqref{Ceq} by first using Strang splitting~\cite{str1968} to decompose the PDE into individual PDEs for linear advection and diffusion.
 The advection equation will be solved with a semi-Lagrangian method~\cite{rob1981} so that it can be solved on an Eulerian grid without a restrictive CFL condition.
@@
 Such a framework could accurately simulate the geophysically relevant scenario of karst conduits with embedded granular media.
-The gradual changes in the medium and karst boundaries due to erosion and dissolution could create conditions favorable for mechanical failure or collapse of the structure, for example sinkholes.
+The gradual changes in the medium and karst boundaries due to erosion and dissolution could create conditions favorable for mechanical failure or collapse of the structure, for example sinkholes (see Section~\ref{sec:sinkhole}).
 
-%---------------------------------------------------------------------------------------------------%
+%----------------------------------------------------------------------%
 \subsection{Transport through eroded media}
 
-\begin{wrapfigure}[]{r}{0.5\textwidth}
-  \includegraphics[width=0.5\textwidth]{figs/100b_t100tracer}
+\begin{wrapfigure}[23]{r}{0.4\textwidth}
+  \includegraphics[width=0.4\textwidth]{figs/100b_t100tracer}
   \caption{\label{fig:100tracers} A visualization of the streamlines
@@
 
-\subsection{Mobile grain simulations and sinkhole formation}
+%----------------------------------------------------------------------%
+\subsection{Mobile Grain Simulations and Sinkhole Formation}
+\label{sec:sinkhole}
+
+Near-term plans are to include flow transport and gravitational sedimentation of the eroding grains.
+For this extension, contact forces between bodies must be included to eliminate unphysical contact that is inevitable due to discretization errors.
+
+Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research.
+One approach is to use introduce a potential with short-range repulsion, but such methods often introduce stiffness.
+Alternatively, a space-time interference volume can guarantee a minimum separation between grains.
+In a fluid context, this method was first introduced by Lu et al.~\cite{lu-rah-zor2017}, and extended to allow for much smaller separation distances of rigid bodies by the PI's previous graduate student~\cite{bys-sha-qua2019}.
+One PhD student, who will be jointly supervised by both PIs, will simulate sedimentation of eroding bodies by developing algorithms that resolve quadrature error and contact.
 
@@
 
+%----------------------------------------------------------------------%
+\subsection{Parameterizations of Eroding Porous Media}
 More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.
@@
 
+\subsection{Experimental Validation}
+\label{sec:experiments}
 As mentioned previously, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments~\cite{tao2014experimental}.
@@
 
-%---------------------------------------------------------------------------------------------------%
+%----------------------------------------------------------------------%
 %%%%  SECTION: Education and outreach
-%---------------------------------------------------------------------------------------------------%
-\section{Broader impacts of the proposed work}
+%----------------------------------------------------------------------%
+\section{Outreach}
+The PIs are committed to ....
 
-The proposed research could lead to a range of societal benefits, including better management of water resources, accurate prediction of contaminant transport, and an understanding of the long-term effects of human activities, such as hydraulic fracturing or groundwater pumping, on porous media and water resources.
-In such scenarios, the slow timescales of mechanical and chemical erosion are coupled to the faster timescales of human-induced changes and gravitational collapse.
-Currently, the relationship between these scales is poorly understood.
-The high-fidelity, efficient computational methods proposed here will enable a deeper understanding of these processes, which is the first step towards developing effective strategies for managing water resources and mitigating catastrophic events such as contamination or structural collapse.
-For example, the insights gained here could potentially help identify locations in natural aquifers vulnerable to contamination and/or collapse.
-
-In addition to these societal impacts, the work proposed here will spur the training of mathematicians and computational scientists in fundamentally cross-disciplinary research of great societal importance.
-Further, the PIs will engage in educational and outreach activities to impact future generations of mathematical scientists, with particular focus on women and underrepresented minorities (URM).
-Both PIs are already actively involved in graduate and undergraduate research, as well as outreach to K-12 students.
-Further, we have successfully recruited women and underrepresented minorities in undergraduate, graduate, and postdoctoral research.
-
+%----------------------------------------------------------------------%
 \subsection{Graduate research}
@@
 
+%----------------------------------------------------------------------%
 \subsection{Undergraduate research}
@@
 
+%----------------------------------------------------------------------%
 \subsection{Outreach for K--12 and the general public}
@@
 
-\section{Results from Prior and Current NSF Support: N/A}
-
-%---------------------------------------------------------------------------------------------------%
+%----------------------------------------------------------------------%
 %%  BIBLIOGRAPHY
@@
 \bibliography{ProjBib}
-%---------------------------------------------------------------------------------------------------%
+%----------------------------------------------------------------------%
 \end{document}

### 2019-11-17 docs/proposals/NSF/ProjDesc/ProjDesc.tex
worked through proposal

@@
     geometries.
+
+  \item Understand pore size growth under erosion
+
+  \item New parameterizations using modern machine learning techniques
+
+  \item Validation with experimental results
 \end{itemize}
@@
 The numerical challenge is developing the required FMM expansions for the velocity, vorticity, and deformation tensor layer potentials.
-Since we require several layer potentials with different kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and its implementations that are readily available (for example, see \url{http://pvfmm.org}).
+Since we require several layer potentials with different kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and its HPC implementations that are readily available (for example, see \url{http://pvfmm.org}).
 Other challenges that will be investigated include preconditioning strategies to reduce the number of required GMRES iterations, and time adaptivity to allow for stable simulations to user-specified tolerances.
@@
 To increase understanding of flow through eroded media, we will simulate and statistically analyze transport through eroded geometries.
-
-In an eroded geometry $\Omega$, the dimensionless
-concentration $c$ is governed by
+In an eroded geometry $\Omega$, the dimensionless concentration $c$ is governed by
 \begin{align}
@@
 \end{align}
-where $\Pe$ is the dimensionless Peclet number. Here we assume that the
-concentration $c$ is affected by the eroded geometry, but the geometry
-is not altered further by the concentration. In the infinite Peclet
-number limit, the concentration is governed by pure advection and the
-characteristics of the concentration field are identical to the
-streamlines (Fig.~\ref{fig:100tracers}).
+where $\Pe$ is the dimensionless Peclet number.
+Here we assume that the concentration $c$ is affected by the eroded geometry, but the geometry is not altered further by the concentration (i.e.~$c$ is not responsible for dissolution).
 
+In the infinite Peclet number limit, the concentration is governed by pure advection and the characteristics of the concentration field are identical to the streamlines (Fig.~\ref{fig:100tracers}).
 The $j^{th}$ trajectory, or characteristic, is governed by $\dot{\ss}_j(t) = \uu(\ss_j(t))$.
 Once these trajectories are computed, using for example a high-order Runge-Kutta method, a statistical analysis can be used to describe the transport.
-Two of the most important measurements are the tortuosity and the anomalous dispersion, both which are defined in terms of the length of the trajectories \begin{align}
+Two of the most important measurements are the tortuosity and the anomalous dispersion, both which are defined in terms of the length of the trajectories
+\begin{align} 
   \lambda_j(t) = \int_{0}^{t} \|\ss'(t')\| dt'.
@@
 
+\begin{wrapfigure}[19]{r}{0.35\textwidth}
+  \includegraphics[width=0.35\textwidth]{figs/100b_second_moment_long_ref}
+  \caption{\label{fig:100dispersion} The particle spreading, characterized with the standard deviation $\sigma_\lambda(t)$ at six different porosities.
+At early times, the line of slope 1 (black curve) indicates a ballistic motion.
+At later times, the dispersion becomes super-dispersive at a rate indicated by the slope of the black dashed-dotted line.}
+\end{wrapfigure}
 While the tortuosity characterizes the amount of winding of streamlines, the dispersion characterizes the spreading of the trajectories.
@@
 \begin{align}
-  \langle \lambda \rangle (t) = \frac{1}{N_p} \sum_{j=1}^{N_p}
-    \lambda_j(t), \quad \sigma_\lambda^{2}(t) = \frac{1}{N_p}
-    \sum_{j=1}^{N_p} (\lambda_j(t) - \langle \lambda \rangle(t))^2
+  \begin{split}
+  \langle \lambda \rangle (t) &= \frac{1}{N_p} 
+      \sum_{j=1}^{N_p} \lambda_j(t), \\ 
+  \sigma_\lambda^{2}(t) &= \frac{1}{N_p}
+    \sum_{j=1}^{N_p} (\lambda_j(t) - \langle \lambda \rangle(t))^2.
+  \end{split}
 \end{align}
@@
 In Fig.~\ref{fig:100dispersion}, we investigate spreading at several different porosities of a porous geometry that is initialized with 100 grains.
-\begin{wrapfigure}[22]{r}{0.4\textwidth}
-  \includegraphics[width=0.4\textwidth]{figs/100b_second_moment_long_ref}
-  \caption{\label{fig:100dispersion} The particle spreading,
-  characterized with the standard deviation $\sigma_\lambda(t)$ at 6
-  different porosities. At early times, the line of slope 1 (black
-  curve) indicates a ballistic motion. At later times, the
-  dispersion becomes super-dispersive at a rate indicated by the slope
-  of the black dashed-dotted line.}
-\end{wrapfigure}
 
@@
 
-Near-term plans are to include flow transport and gravitational sedimentation of the eroding grains.
-For this extension, contact forces between bodies must be included to eliminate unphysical contact that is inevitable due to discretization errors.
-
+Upon developing and improving numerical methods to simulate mechanical
+and chemical erosion, we plan to develop methods to simulate transport,
+gravitational sedimentation, and external buoyant forces of the eroding grains.
+In addition to the new previously described quadrature, preconditioning, adaptivity, and fast summation methods,  this extension also requires contact forces between bodies to eliminate unphysical contact that is inevitable due to discretization errors.
 Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research.
@@
 
-% PREVIOUS PARAGRAPH
-%Near-term plans are to include flow transport and gravitational sedimentation of the particles.
-For this extension, contact forces between bodies must be included.
-Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research  {\color{blue} cite}.
-We plan to implement contact forces with {\color{blue} stuff}.
-This goal will form the PhD dissertation of a graduate student who will be supervised by myself and Prof.~Bryan Quaife (FSU Scientific Computing).
-
-One central goal of this proposal is to enable the free motion of grains during the erosion processes.
-As mentioned earlier, this goal requires resolving contact forces between bodies, as well as the incorporation of the external buoyancy forces.
-Once this goal is achieved, it will be possible to simulate a complex porous-medium of arbitrarily sized and shaped grains undergoing the simultaneous action of mechanical-or-chemical erosion and transport due to the combined effects of seepage, contact, and buoyancy forces.
+The central goal of simulating transport of eroding grains is to simulate a complex porous-medium of arbitrarily sized and shaped grains undergoing the simultaneous action of mechanical-or-chemical erosion and transport due to the combined effects of seepage, contact, and buoyancy forces.
 These computations will thus simulate, with high-fidelity, the multi-physics of realistic porous-medium dynamics, albeit in a scaled down context.
 Ultimately, such simulations could be used to build an understanding of medium reconfiguration events, such as sinkhole collapse or conduit formation in karst networks.
-
 In very preliminary work, PI Moore has been running simplified simulations with a current graduate student.
 These preliminary simulations are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
-They utilize the homogenized description of the flow field in~\eqref{DarcyEq} and incorporate the physical effects of:
-\begin{itemize}[noitemsep]
+They utilize the homogenized description of the flow field in~\eqref{DarcyEq} and incorporate the physical effects of: \begin{itemize}[noitemsep]
 \item Transport of grains due to seepage force from the surrounding fluid flow.
@@
 
-\todo[inline]{Eventually, our FMM solver will reach its capacity. We
-need to talk about fast summation methods for the barycentric
-quadrature, deformation tensor, vorticity, and pressure. In addition to
-fast summation methods, we can talk about parallel implementations. I
-have new PhD student in DSC that wants to work on erosion and he has
-experience running MPI and OpenMP.}
-
+%----------------------------------------------------------------------%
+\subsection{Parameterizations of Eroding Porous Media}
 These simulations have not yet begun to incorporate the slow-acting effects of mechanical and chemical erosion, and the associated gradual changes in medium properties.
@@
 
-%----------------------------------------------------------------------%
-\subsection{Parameterizations of Eroding Porous Media}
 More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.
@@
 
+%----------------------------------------------------------------------%
 \subsection{Experimental Validation}
@@
 \section{Outreach}
-The PIs are committed to ....
+The PIs are committed to utilizing and training students at various levels of their education throughout the proposed research.
+Different aspects of the proposed research are at appropriate levels for PhD students, undergraduate students, and high school students.
+Moreover, different opportunities within FSU will be used to publicize the work to K--12 students and the greater public.
 
 %----------------------------------------------------------------------%
-\subsection{Graduate research}
+\subsection{Graduate Research}
 An important benefit of the research proposed here is the potential to immerse graduate students in fundamentally {\em cross-disciplinary} research.
@@
 %----------------------------------------------------------------------%
-\subsection{Undergraduate research}
+\subsection{Undergraduate Research}
 Regarding undergraduate research, the ideas in this proposal represent a rich and fascinating topic for undergraduate students, while also being approachable these students.
@@
 %----------------------------------------------------------------------%
-\subsection{Outreach for K--12 and the general public}
+\subsection{Outreach for K--12 and the General Public}
 The PIs have already seized the opportunity to engage K--12 students in outreach activities.
@@
 
-%\subsection{Assessment for graduate and undergraduate education}
-%Developing strong mentoring relationships is essential to a student's intellectual development and a responsibility that the PIs takes very seriously.
-When working with students on research, whether undergraduate or graduate, we are always sure to outline the expectations of {\em both} parties -- the student and myself -- and periodically revisit the list to determine if the expectations are being met or if changes are necessary.
-This ensures that progress continues uninterrupted and that both parties are comfortable with their responsibilities.
-For the graduate seminar course, questionnaires will be provided to the students to determine how the seminar relates to their own research and their intellectual development, as well as parts of the course that were particularly beneficial and parts that could be improved.
-This will ensure that, once integrated into the standard curriculum, the course will maximally benefit the students' education.
+%----------------------------------------------------------------------%
+\section{Timeline and Concluding Remarks}
 

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 Natural water resources, however, have been placed under enormous pressure by human population growth and associated activities that can compromise the natural filtration cycle, for example expansion of industry, urbanization, pollution, and climate change.
-See the UN report on water resources for further detail on the threats to water resources~\cite{UNwater}.
+See the UN report on water resources for further detail on these looming threats~\cite{UNwater}.
 % Could also include USGS if needed.
 
-An understanding of these filtration and contamination processes relies on the complex phenomenon of transport in porous media.
-Further, the action of continually flowing groundwater can alter medium properties through erosive and transportive processes.
+An understanding of these filtration and contamination processes relies on the complex phenomenon of transport and dispersion in porous media.
+Further, the action of continually flowing groundwater can alter medium properties through erosive, transportive, and other processes.
 Thus, it becomes necessary to understand transport through complex media whose properties change {\em dynamically} in response to the intervening fluid flow.
@@
 
-{\bf This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow can alter porous-media properties and to characterize the associated changes in transport within the evolving medium.} A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{lin2018randomization}.
+{\bf This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow alters porous-media properties and to characterize the associated changes in dispersive transport within the evolving medium.} A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{lin2018randomization}.
 These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material.
@@
 
-In particular, we view the accumulated effects of slow processes like erosion and dissolution as instrumental in altering porous-medium properties.
+In particular, we view the slow, accumulated effects of erosion and dissolution as instrumental in altering porous-medium properties.
 First, by deteriorating solid material, erosion alters the size distribution of grains, enabling smaller grains to be sieved through networks of larger ones.
@@
 Likewise, chemical dissolution can carve well-defined conduit paths in karst networks which strongly alter transport properties~\cite{szymczak2009wormhole}.
+Some visible effects of flow-induced erosion are shown in Fig.~\ref{collage}.
+The top row shows products of primarily {\em chemically-driven} erosion, while the bottom shows effects of primarily {\em mechanically-driven} erosion.
+Throughout this proposal, we also refer to chemically-driven erosion as dissolution.
+Some examples in the figure include the rough surface of limestone pavement, a sinkhole, an erosion-curved conduit, and finally an image of the small-scale structure of soil, exhibiting polydispersity and anisotropy, resulting from a combination of erosive, compaction, and transport properties
 

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 These challenges require innovative computational techniques, some of which have been developed recently~\cite{Quaife2018} and others that await resolution.
-{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(100-1000)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} Dynamic erosion of porous media is a highly active area of research, as closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
-These experiments a great opportunity for comparison against our numerical simulations.
+{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(100-1000)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.}
+
+	There has been a recent spark in interest in dynamic erosion of porous media, both theoretically and experimentally.
+In fact, experiments on erosion of colloidal systems are currently being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
+These experiments are closely related to our proposed computational study, thus offering a great opportunity for comparison.
 Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute (see Section~\ref{sec:experiments}), which would help to guide, calibrate, and validate the computations (see letter of collaboration).

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 \subsection{Governing Equations}
+
+Here, we first outline the theoretical foundation to be used in later sections of the proposal.
 At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations \begin{equation}
@@
 \begin{itemize}[noitemsep]
-  \item Computational plays an essential role to simulate erosion of porous medium.
-
-  \item The proposed research is directly applicable to several geophysical applications.
-
-  \item The proposed research is a collaborative effort and will include graduate, undergraduate, and K--12 students
+  \item Efficient, high-fidelity computational methods form the core of the proposed work of porous-media erosion.
+Large ensembles of the high-fidelity simulations will inform the coarse-grained models that will be developed in the later stages of the proposed work.
+  \item The proposed research is interdisciplinary by nature, with immediate applications in the fields of geophysics and environmental sciences.
+The PIs already have experience collaborating with scientists from other disciplines through FSU's Geophysical Fluid Dynamics Institute, an interdisciplinary unit comprised of a diverse set of faculty from home departments in example Earth, Atmospheric, and Ocean Sciences, Geology, Physics, Civil Engineering, Environmental Engineering, and others.
+  \item The proposed research is a collaborative effort with a focus on training future generations of scientists and mathematicians.
+The proposal will include graduate, undergraduate, and K--12 students, with close cooperation between them.
 \end{itemize}
@@
 
-\paragraph{PIs' Qualifications:} PI Moore joined the Department of Mathematics at Florida State University (FSU) in 2014, and is also a Research Associate in FSU's Geophysical Fluid Dynamics Institute (GFDI).
+\paragraph{PIs' Qualifications:} PI Moore joined the Department of Mathematics at Florida State University (FSU) in 2014.
+He is also a Research Associate in FSU's Geophysical Fluid Dynamics Institute (GFDI).
 His expertise includes modeling dynamic interactions between fluids and structures, especially in geophysical and biologically motivated settings.
@@
 
-The PIs co-authored a paper describing numerical methods for simulating erosion~\cite{Quaife2018} in a viscous fluid.
-Very recently, a second paper has been submitted to the Journal of Fluid Mechanics~\cite{chi-moo-qua2019}, where additional numerical methods are developed and characterizations of transport are presented.
+The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion~\cite{Quaife2018} in the Stokes flow regime, which is the regime relevant for the currently proposed applications of groundwater flow.
+Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion \cite{chi-moo-qua2019}.
+
+%Very recently, a second paper has been submitted to the Journal of Fluid Mechanics~\cite{chi-moo-qua2019}, where additional numerical methods are developed and characterizations of transport are presented.
 

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 
-The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion~\cite{Quaife2018} in the Stokes flow regime, which is the regime relevant for the currently proposed applications of groundwater flow.
+The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion~\cite{Quaife2018} in the Stokes flow regime, which is the regime relevant for the currently proposed groundwater applications.
 Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion \cite{chi-moo-qua2019}.

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 These challenges require innovative computational techniques, some of which have been developed recently~\cite{Quaife2018} and others that await resolution.
-{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(100-1000)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.}
 
-	There has been a recent spark in interest in dynamic erosion of porous media, both theoretically and experimentally.
-In fact, experiments on erosion of colloidal systems are currently being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
+{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(100-1000)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} A major step towards this goal is illustrated in Fig.~\ref{80circ8vel}, which features high-fidelity erosion simulations of an initial configuration of 80 bodies with a volume fraction of $50 \%$.
+Color indicates the velocity magnitude, which highlights the spontaneous formation of channels during the erosion process.
+These channels arise from small variations in the initial condition.
+Once formed, the larger channels transmit more flow which reinforces their growth.
+The process of channel formation can dramatically alter medium properties and create high levels of anisotropy, which directly impacts dispersion of transported quantities, for example contaminants.
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure}%[htp]
+\begin{center}
+\includegraphics[width = 0.99 \textwidth]{./figs/80circ8vel.pdf}
+\caption{\label{80circ8vel} High-fidelity numerical simulations of a configuration of densely-packed solid bodies undergoing mechanical erosion due to an intervening Stokes flow.
+The color indicates velocity magnitude which highlights the channel formation process.
+The solid bodies develop flat faces and sharp corners during evolution.
+}
+\end{center}
+\end{figure}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+
+ \todo[inline]{I guess I really took to your strategy of including an example simulation early on in the introduction to draw in the readers interest.
+So I moved this figure up to the introduction and added some provocative text.
+Plus there are some visual similarities with the geophysical images in Fig.
+1, so it is nice to see them close to one another.}
+
+	In addition to the work of the PIs, there has been a recently sparked interest in dynamic erosion of porous media, as experiments on erosion of colloidal systems are currently being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
 These experiments are closely related to our proposed computational study, thus offering a great opportunity for comparison.
@@
 
-%Very recently, a second paper has been submitted to the Journal of Fluid Mechanics~\cite{chi-moo-qua2019}, where additional numerical methods are developed and characterizations of transport are presented.
-
 \paragraph{Outline of the Proposal:}
@@
 \subsection{Mechanical and Chemical Erosion of a Porous Medium}
-With the development of efficient and high-fidelity numerical methods to solve the Stokes equations, we are able to simulate erosion.
+
+The development of accurate and efficient numerical methods to solve the Stokes equations enables high-fidelity simulations of the erosion process.
 We will consider erosion induced by either fluid-mechanical forces or by chemical reaction, i.e.~dissolution.
@@
 In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}[htp]
-\begin{center}
-\includegraphics[width = 0.99 \textwidth]{./figs/80circ8vel.pdf}
-\caption{\label{80circ8vel} High-fidelity numerical simulations of a configuration of densely-packed solid bodies undergoing mechanical erosion due to an intervening Stokes flow.
-The color indicates velocity magnitude which highlights the channel formation process.
-The solid bodies develop flat faces and sharp corners during evolution.
-}
-\end{center}
-\end{figure}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+This channelization process is made even more apparent by viewing the velocity magnitude as in Fig.~\ref{80circ8vel}.
 
@@
 
-An immediate goal of the proposed work is to extend the range of physical effects captured in these simulations.
-A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
+{An immediate goal of the proposed work is to extend the range of physical effects captured in these simulations.} A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
 To address this problem, we have very recently extended a Barycentric quadrature~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing~\cite{chi-moo-qua2019}.

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 In addition to the new previously described quadrature, preconditioning, adaptivity, and fast summation methods,  this extension also requires contact forces between bodies to eliminate unphysical contact that is inevitable due to discretization errors.
-Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research.
+Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research \cite{yan2019computing}.
+
+\todo[inline]{Bryan, do you know any other references to include after `topic of current research'? I have Shelley and Yan's method. There were a bunch of others at Oaxaca but I don't remember names.}
+
 One approach is to use introduce a potential with short-range repulsion, but such methods often introduce stiffness.
@@
 
-More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.
+More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks \cite{ling2016reynolds, kutz2017deep, ling2016machine, pelt2018mixed} to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.
 The output of the high-fidelity simulations of the grain configuration can be transformed into essentially an image format, enabling us to use cutting-edge advancements on deep neural-networks for image analysis~\cite{pelt2018mixed}.

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 Throughout this proposal, we also refer to chemically-driven erosion as dissolution.
-Some examples in the figure include the rough surface of limestone pavement, a sinkhole, an erosion-curved conduit, and finally an image of the small-scale structure of soil, exhibiting polydispersity and anisotropy, resulting from a combination of erosive, compaction, and transport properties
+Some examples in the figure include the rough surface of limestone pavement, a sinkhole, an erosion-curved conduit, and finally an image of the small-scale structure of soil, exhibiting polydispersity and anisotropy that result from a combination of erosive, compaction, and transport actions.
 
@@
 Bottom: examples of soil erosion.
-The bottom right shows the microscopic soil texture.}
+The bottom right shows the microscopic soil texture, exhibiting polydispersity and anisotropy.}
 \end{center}
@@
   \item The proposed research is interdisciplinary by nature, with immediate applications in the fields of geophysics and environmental sciences.
-The PIs already have experience collaborating with scientists from other disciplines through FSU's Geophysical Fluid Dynamics Institute, an interdisciplinary unit comprised of a diverse set of faculty from home departments in example Earth, Atmospheric, and Ocean Sciences, Geology, Physics, Civil Engineering, Environmental Engineering, and others.
+The PIs already have experience collaborating with scientists from other disciplines \cite{Caves2018, eastham2019multiphase, Bolles2019} through FSU's Geophysical Fluid Dynamics Institute, an interdisciplinary unit comprised of a diverse set of faculty from home departments in example Earth, Atmospheric, and Ocean Sciences, Geology, Physics, Civil Engineering, Environmental Engineering, Scientific Computing, Mathematics, and others.
   \item The proposed research is a collaborative effort with a focus on training future generations of scientists and mathematicians.
@@
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure}[htp]
+\begin{figure}%[htp]
 \begin{center}
@@
 %----------------------------------------------------------------------%
-\subsection{Transport through eroded media}
+\subsection{Dispersive transport through eroded media}
 
@@
 
-\todo[inline]{Bryan, do you know any other references to include after `topic of current research'? I have Shelley and Yan's method. There were a bunch of others at Oaxaca but I don't remember names.}
+\todo[inline]{Bryan, do you know any other references to include after `topic of current research'?
+I included Shelley and Yan's method.
+There were a bunch of others at Oaxaca but I don't remember names.}
 
@@
 \subsection{Undergraduate Research}
-Regarding undergraduate research, the ideas in this proposal represent a rich and fascinating topic for undergraduate students, while also being approachable these students.
+Regarding undergraduate research, the ideas in this proposal represent a rich and fascinating topic for undergraduate students, while also being approachable by the skills acquired at that stage.
 In particular, we aim to recruit at least one undergraduate student to perform laboratory experiments at the Geophysical Fluid Dynamics Institute (GFDI).
@@
 The student will perform controlled experiments using natural and artificial porous media (e.g.~sand and micro-glass beads respectively) to precisely characterize the parameter regime leading to gravitational collapse.
-Parallel experiments will be conducted with erodible (bentonite clay) or dissolvable  (sucrose solids) fragments materials, which will represent the porous medium.
+Parallel experiments will be conducted with erodible (bentonite clay) or dissolvable  (sucrose solids) fragments materials to represent a {\em dynamically} changing porous medium.
 These experiments will be used to guide, calibrate, and validate the computational advances.

### 2019-11-19 docs/proposals/NSF/ProjDesc/ProjDesc.tex
fixed up a few things in proposal

@@
 
-{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(100-1000)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} A major step towards this goal is illustrated in Fig.~\ref{80circ8vel}, which features high-fidelity erosion simulations of an initial configuration of 80 bodies with a volume fraction of $50 \%$.
+{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(10^2-10^3)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} A major step towards this goal is illustrated in Fig.~\ref{80circ8vel}, which features high-fidelity erosion simulations of an initial configuration of 80 bodies with a volume fraction of $50 \%$.
 Color indicates the velocity magnitude, which highlights the spontaneous formation of channels during the erosion process.
@@
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-
- \todo[inline]{I guess I really took to your strategy of including an example simulation early on in the introduction to draw in the readers interest.
-So I moved this figure up to the introduction and added some provocative text.
-Plus there are some visual similarities with the geophysical images in Fig.
-1, so it is nice to see them close to one another.}
 
@@
 
-The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion~\cite{Quaife2018} in the Stokes flow regime, which is the regime relevant for the currently proposed groundwater applications.
+The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion in the Stokes flow regime~\cite{Quaife2018}, which is the regime relevant for the currently proposed groundwater applications.
 Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion \cite{chi-moo-qua2019}.
@@
 %----------------------------------------------------------------------%
-\todo[inline]{Discuss what the main research questions are here}
+The goal of the proposed research is to develop new numerical methods to
+simulate erosion processes. Specific research tasks will include:
 \begin{itemize}[noitemsep]
-  \item Characterize anisotropy and permeability to inform homogenized
-    models including Darcy's relation.
+  \item Simulating chemical erosion.
 
-  \item Improve numerical methods including FMM, preconditioners, and
-    quadrature.
+  \item Characterizing anisotropy and permeability to inform
+    homogenized models such as Darcy's relation.
 
-  \item Simulate erosion via chemical reactions ie.~dissolution.
+  \item Simulating the transport of finite Peclet number concentrations
+    inside eroded porous geometries.
 
-  \item Simulate transport of finite Peclet number species in eroded
-    geometries.
+  \item Improving numerical methods including fast summation methods,
+    preconditioners, and quadrature.
 
-  \item Understand pore size growth under erosion
+  \item Developing new models to characterize the effect of erosion on
+    pore size dynamics.
 
-  \item New parameterizations using modern machine learning techniques
+  \item Developing new parameterizations using modern machine learning
+    techniques.
 
-  \item Validation with experimental results
+  \item Validating simulations with in-house experimental results.
+
+  \item \todo[inline]{Something about transport, sedimentation, etc.}
 \end{itemize}
@@
 These simulations combine highly accurate boundary integral methods with stable interface evolution techniques.
-The boundary integral solver is accelerated by the fast multipole method~\cite{gre-rok1987, gre-gre-may1992} to achieve optimal $O(N)$ complexity.
+The boundary integral solver is accelerated by the fast multipole method~\cite{gre-rok1987, gre-gre-may1992} to achieve optimal $\mathcal{O}(N)$ complexity.
 Meanwhile, the so-called {\thL} method is used for interface evolution to prevent distortion and tangling of the interface meshes~\cite{hou1994removing, MoorePOF2013, Quaife2018}.
@@
 
-Figs.~\ref{80circ8vort} and~\ref{80circ8vel} show preliminary results of 80 bodies, initially of random position and size, undergoing mechanical erosion in Stokes flow.
+Figs.~\ref{80circ8vel} and~\ref{80circ8vort} show preliminary results of 80 bodies, initially of random position and size, undergoing mechanical erosion in Stokes flow.
 This simulation extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed Barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015, chi-moo-qua2019}, which enables closer contact between bodies and thus more bodies.
@@
   sC(\xx,s) - \frac{1}{\Pe}\Delta C(\xx,s) = c_0(\xx), 
-    \quad \xx \in \Omega,
+    \quad \xx \in \Omega, \: s \in \mathbb{C},
   \label{eqn:DiffusionLaplace}
@@
 Once these trajectories are computed, using for example a high-order Runge-Kutta method, a statistical analysis can be used to describe the transport.
-Two of the most important measurements are the tortuosity and the anomalous dispersion, both which are defined in terms of the length of the trajectories
-\begin{align} 
-  \lambda_j(t) = \int_{0}^{t} \|\ss'(t')\| dt'.
-\end{align}
+Two of the most important measurements are the tortuosity and the anomalous dispersion, both which are defined in terms of the length of the trajectories.
 Upon computing $N_p$ trajectories, the tortuosity is the dimensionless number
@@
 \end{align}
-where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length,
-$u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of
-the trajectory starting at $(x_0,y_0)$ and ending at a vertical
-cross-section at the other end of the channel. Relationships between the
-tortuosity and porosity of a geometry have been developed by other
-groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and
-preliminary results indicate that such models might be appropriate for
-geometries whose porosity is increasing under the process of erosion
-(Fig.~\ref{fig:100tortuosity}(a)). However, preliminary results also
-indicate that erosion can increase the amount of tortuosity as is
-evident towards the at the towards the end of the erosion process in
-Fig.~\ref{fig:100tortuosity}(a). Moreover, we have observed a
-significant increase in the tortuosity at small porosities
-(Fig.~\ref{fig:100tortuosity}(b)).
+where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length, $u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of the trajectory starting at $(x_0,y_0)$ and ending at a vertical cross-section at the other end of the channel.
+Relationships between the tortuosity and porosity of a geometry have been developed by other groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and preliminary results indicate that such models might be appropriate for geometries whose porosity is increasing under the process of erosion (Fig.~\ref{fig:100tortuosity}(a)).
+However, preliminary results also indicate that erosion can increase the amount of tortuosity as is evident towards the at the towards the end of the erosion process in Fig.~\ref{fig:100tortuosity}(a).
+Moreover, we have observed a significant increase in the tortuosity at small porosities (Fig.~\ref{fig:100tortuosity}(b)).
 
@@
 
-Upon developing and improving numerical methods to simulate mechanical
-and chemical erosion, we plan to develop methods to simulate transport,
-gravitational sedimentation, and external buoyant forces of the eroding grains.
+Upon developing and improving numerical methods to simulate mechanical and chemical erosion, we plan to develop methods to simulate transport, gravitational sedimentation, and external buoyant forces of the eroding grains.
 In addition to the new previously described quadrature, preconditioning, adaptivity, and fast summation methods,  this extension also requires contact forces between bodies to eliminate unphysical contact that is inevitable due to discretization errors.
-Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research \cite{yan2019computing}.
-
-\todo[inline]{Bryan, do you know any other references to include after `topic of current research'?
-I included Shelley and Yan's method.
-There were a bunch of others at Oaxaca but I don't remember names.}
+Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research \cite{yan2019computing, lu-rah-zor2017, bys-sha-qua2019}.
 
@@
 %----------------------------------------------------------------------%
-\section{Timeline and Concluding Remarks}
+\section{Timeline}
 

### 2019-11-19 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 
-An understanding of these filtration and contamination processes relies on the complex phenomenon of transport and dispersion in porous media.
+An understanding of these filtration and contamination processes relies on the complex phenomenon of transport and dispersion in porous media \cite{scheidegger1961general}.
 Further, the action of continually flowing groundwater can alter medium properties through erosive, transportive, and other processes.
@@
 These effects are most noticeable during rapid events, like the gravitational collapse of a sinkhole~\cite{sandhu2018fate}, during which medium properties can change dramatically over short timescales.
-Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties.
+Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties \cite{ellis2013dissolution}.
 
-{\bf This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow alters porous-media properties and to characterize the associated changes in dispersive transport within the evolving medium.} A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{lin2018randomization}.
+{\bf This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow alters porous-media properties and to characterize the associated changes in dispersive transport within the evolving medium.} A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{moyner2016multiscale, lin2018randomization}.
 These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material.

### 2019-11-19 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

--- 2019-11-19 docs/proposals/NSF/ProjDesc/ProjDesc.tex
@@
 
-An understanding of these filtration and contamination processes relies on the complex phenomenon of transport and dispersion in porous media.
+An understanding of these filtration and contamination processes relies on the complex phenomenon of transport and dispersion in porous media \cite{scheidegger1961general, neuman1987stochastic, delgado2007longitudinal, zhang2016backward}.
 Further, the action of continually flowing groundwater can alter medium properties through erosive, transportive, and other processes.
@@
 These effects are most noticeable during rapid events, like the gravitational collapse of a sinkhole~\cite{sandhu2018fate}, during which medium properties can change dramatically over short timescales.
-Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties.
+Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties \cite{szymczak2009wormhole, ellis2013dissolution}.
 
-{\bf This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow alters porous-media properties and to characterize the associated changes in dispersive transport within the evolving medium.} A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{lin2018randomization}.
+{\bf This proposal aims to develop a suite of computational tools geared towards developing a deeper understanding of the physical processes by which groundwater flow alters porous-media properties and to characterize the associated changes in dispersive transport within the evolving medium.} A recognized complexity of naturally occurring media is the heterogeneity and anisotropy of macroscopic properties such as permeability and mechanical strength~\cite{neuman1987stochastic, moyner2016multiscale, lin2018randomization}.
 These properties can change over short timescales, for example sinkhole collapse or hydraulic fracturing, or over long timescales, for example the slow erosion or dissolution of solid material.

### 2019-11-19 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 Some visible effects of flow-induced erosion are shown in Fig.~\ref{collage}.
-The top row shows products of primarily {\em chemically-driven} erosion, while the bottom shows effects of primarily {\em mechanically-driven} erosion.
-Throughout this proposal, we also refer to chemically-driven erosion as dissolution.
-Some examples in the figure include the rough surface of limestone pavement, a sinkhole, an erosion-curved conduit, and finally an image of the small-scale structure of soil, exhibiting polydispersity and anisotropy that result from a combination of erosive, compaction, and transport actions.
+The top row shows products of primarily {\em chemically-driven} erosion, i.e.~dissolution, while the bottom shows effects of primarily {\em mechanically-driven} erosion.
+Some examples in the figure include the rough surface of limestone pavement, a sinkhole relic in Belize, and an erosion-curved conduit.
+The final image shows the small-scale structure of soil which exhibits polydispersity and anisotropy resulting from a combination of erosive, compaction, and transport actions.
 
@@
 
-More generally, the coupling between shape and flow during erosion, dissolution, and related phase-change processes is a topic that has garnered recent interest in the mathematical sciences community~\cite{Ristroph2012, rycroft2016asymmetric, cohen2016erosion, MooreCPAM2017, mitchell2017generalized, Quaife2018, wykes2018self, lachaussee2018competitive, lopez2018cfd, ristroph2018sculpting}.
+More generally, the coupling between shape and flow during erosion, dissolution, and related phase-change processes is a vibrant research area in the mathematical sciences community~\cite{Ristroph2012, rycroft2016asymmetric, cohen2016erosion, MooreCPAM2017, mitchell2017generalized, Quaife2018, wykes2018self, lachaussee2018competitive, lopez2018cfd, ristroph2018sculpting}.
 Erosion-induced shape change has been studied in the high Reynolds number regime, both experimentally~\cite{Ristroph2012, MoorePOF2013} and theoretically~\cite{MoorePOF2013, MooreCPAM2017, hewett2017evolution} and in single~\cite{Ristroph2012, MoorePOF2013, MooreCPAM2017, lachaussee2018competitive} and multiple-body arrangements~\cite{hewett2017evolution}.
@@
 
-{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(10^2-10^3)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} A major step towards this goal is illustrated in Fig.~\ref{80circ8vel}, which features high-fidelity erosion simulations of an initial configuration of 80 bodies with a volume fraction of $50 \%$.
+{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(10^2-10^3)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} A major step towards this goal is illustrated in Fig.~\ref{80circ8vel}, which features high-fidelity erosion simulations of an initial configuration of 80 bodies of high volume fraction $50 \%$.
 Color indicates the velocity magnitude, which highlights the spontaneous formation of channels during the erosion process.
@@
 Once formed, the larger channels transmit more flow which reinforces their growth.
-The process of channel formation can dramatically alter medium properties and create high levels of anisotropy, which directly impacts dispersion of transported quantities, for example contaminants.
+The process of channel formation can dramatically alter medium properties and create high levels of anisotropy, which directly impacts dispersion of transported quantities such as contaminants.
 
@@
 
-In addition to the work of the PIs, there has been a recently sparked interest in dynamic erosion of porous media, as experiments on erosion of colloidal systems are currently being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
+In addition to the work of the PIs, dynamic erosion of a porous media is a highly active subject as laboratory experiments on erosion of colloidal systems are currently being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
 These experiments are closely related to our proposed computational study, thus offering a great opportunity for comparison.
@@
 
-While erosion and dissolution lead to gradual changes in a medium, other events like sinkhole collapse or hydraulic fracturing occur over much shorter timescales.
+While erosion and dissolution lead to gradual changes in a medium, other events like sinkhole collapse or hydraulic fracturing represent rapid changes.
 Most likely, all of the mechanisms listed above---erosion, dissolution, transport, compaction, and gravitational collapse---contribute to sinkhole formation, with the slowest acting mechanisms creating conditions favorable for the final act of gravity.
-Sinkhole formation has been explored in preliminary experiments conducted at the Geophysical Fluid Dynamics Institute (GFDI) at Florida State University~\cite{tao2014experimental}.
+Sinkhole formation has been explored in preliminary experiments conducted at the Geophysical Fluid Dynamics Institute at Florida State University~\cite{tao2014experimental}.
 These scaled-down experiments offer the ability to probe various mechanisms behind sinkhole formation, for example a difference in hydraulic head between the confined and unconfined aquifers.
@@
 Ultimately, we envision the high-fidelity erosion simulations to inform coarse-grained models for: (i) transport and dispersion; and (ii) dynamic evolution of macroscopic medium properties.
-These parameterized models could then be combined with well-developed multi-phase models~\cite{Imma2019, eastham2019multiphase} to quantitatively describe and predict sinkhole collapse.
+These parameterized models could then be combined with well-developed multi-phase models \cite{breward2003multiphase, cogan2010multiphase, Imma2019, eastham2019multiphase} to quantitatively describe and predict sinkhole collapse.
 
 %----------------------------------------------------------------------%
-\subsection{Governing Equations}
+\subsection{Theoretical Foundation and Governing Equations}
 
-Here, we first outline the theoretical foundation to be used in later sections of the proposal.
+We first outline the theoretical foundation that will be used in later sections of the proposal.
 At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations \begin{equation}
@@
 
-Eq.~\eqref{eqn:StokesEq}, and its equivalent integral equation formulation, are microscopic descriptions that are required to study the shape evolution of individual grains due to fine-scale erosive effects, either mechanical or chemical.
-The description, however, becomes impractical when attempting to model seepage in very large porous systems where the microscopic geometry can be exceedingly complex.
+Equation \eqref{eqn:StokesEq}, and its equivalent integral formulation, are microscopic descriptions required to model the shape evolution of individual grains due to fine-scale erosive effects, either mechanical or chemical.
+This microscopic description, however, becomes impractical when attempting to model seepage in very large porous systems where the microscopic geometry can be exceedingly complex.
 Instead, one must homogenize over microscopic details to arrive at an approximate description.
@@
 
-While the most immediate proposed work on computational methods to
-simulate erosion will utilize~\eqref{eqn:StokesEq}, the later stages of this project will also incorporate~\eqref{DarcyEq}, or closely related variants known as multiphase models~\cite{Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
+Whilst the most immediate proposed work on computational methods to
+simulate erosion will utilize~\eqref{eqn:StokesEq}, the later stages of this project will also incorporate~\eqref{DarcyEq}, or closely related variants known as multiphase models \cite{breward2003multiphase, cogan2010multiphase, Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
 These models will rely on statistical analysis of the data produced by the high-fidelity erosion simulations in order to parameterize the effects of erosion, leading to deterministic or stochastic reduced-order models for porous-medium evolution.
@@
 \begin{itemize}[noitemsep]
-  \item Efficient, high-fidelity computational methods form the core of the proposed work of porous-media erosion.
-Large ensembles of the high-fidelity simulations will inform the coarse-grained models that will be developed in the later stages of the proposed work.
+  \item Efficient, high-fidelity computational methods form the core of the proposed research on porous-media erosion and dispersive transport.
+Large ensembles of the high-fidelity simulations will inform the coarse-grained models to be developed in the later stages of the proposed work.
   \item The proposed research is interdisciplinary by nature, with immediate applications in the fields of geophysics and environmental sciences.
@@
   \item The proposed research is a collaborative effort with a focus on training future generations of scientists and mathematicians.
-The proposal will include graduate, undergraduate, and K--12 students, with close cooperation between them.
+The proposal will include graduate, undergraduate, and K--12 students, with close interaction and cooperation between them.
 \end{itemize}
@@
 PI Quaife joined the Department of Scientific Computing at FSU in 2015 and is also a Research Associate in GFDI.
-His expertise includes high-fidelity and efficient numerical methods for fluid dynamic in complex geometries.
+His expertise includes high-fidelity and efficient numerical methods for fluid dynamics in complex geometries.
 
-The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion in the Stokes flow regime~\cite{Quaife2018}, which is the regime relevant for the currently proposed groundwater applications.
+The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion in the Stokes flow regime~\cite{Quaife2018}, the regime relevant for the currently proposed groundwater applications.
 Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion \cite{chi-moo-qua2019}.
@@
 Figs.~\ref{80circ8vel} and~\ref{80circ8vort} show preliminary results of 80 bodies, initially of random position and size, undergoing mechanical erosion in Stokes flow.
-This simulation extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed Barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015, chi-moo-qua2019}, which enables closer contact between bodies and thus more bodies.
-The color in Fig~\ref{80circ8vort} shows the (normalized) vorticity field surrounding the bodies.
-Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity (Fig.~\ref{80circ8vel}).
+This simulation extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed Barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015, chi-moo-qua2019}, which enables more densely packed configurations.
+The color in Fig~\ref{80circ8vort} represents the vorticity field surrounding the bodies.
+Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity.
 Observe that erosion not only reduces the size of solid bodies, but also alters their shapes substantially.
@@
 The number of faces does not appear to be easily predicted, but rather depends on the interaction with neighboring bodies as mediated by the Stokes flow.
-Notice that, as erosion proceeds, relatively straight channels tend to develop between the bodies.
+As erosion proceeds, relatively straight channels tend to develop between the bodies.
 Certain channels that are initially larger can transmit more flow, which promotes local erosion rates and further widens these selected channels.
@@
 The creation and reinforcement of channels significantly impacts the macroscopic properties of the porous medium.
-Fig.~\ref{fig3} shows new, preliminary results on how media properties change in time.
-First, the left-most plot shows the rate at which the area fraction decreases as the bodies erode.
+Fig.~\ref{fig3} shows how certain medium properties change in time.
+First, the left-most plot shows the rate at which the area fraction decreases as the bodies disintegrate.
 Notice that the rate of area reduction does not change significantly during the simulation.
@@
 Note that, unlike the area plot, the vertical axis is logarithmic and so the straight line observed at early times indicates that the resistivity decreases exponentially.
-The much more mild decrease in area fraction is not sufficient to account for this exponential rate, and hence the reshaping process, in particular the formation of channels, plays a pivotal role.
+The much more modest decrease of area fraction is not sufficient to account for this exponential rate.
+Hence the reshaping process, in particular the formation of channels, plays a pivotal role the medium's macroscopic resistivity to flow.
 
-Lastly, the right-most plot of Fig.~\ref{fig3} shows the anisotropy, which is calculated as the ratio of the vertical resistivity to the horizontal resistivity.
-The vertical resistivity is computed by rotating the configuration of bodies by 90 degrees.
+Lastly, the right-most plot of Fig.~\ref{fig3} shows new, preliminary results on how medium anisotropy evolves during the reshaping process of erosion.
+Anisotropy calculated as the ratio of vertical to horizontal resistivity, with the vertical resistivity computed by rotating the configuration of bodies by 90 degrees.
 This plot shows the anisotropy to initial increase with time.
@@
 To address this problem, we have very recently extended a Barycentric quadrature~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing~\cite{chi-moo-qua2019}.
-This quadrature approach has the advantage that it is a non-intrusive modification of the trapezoid rule, allowing us to achieve an error bound that independent of the grain configuration.
-However, the implementation of the quadrature method does not fully use FMM acceleration.
-The numerical challenge is developing the required FMM expansions for the velocity, vorticity, and deformation tensor layer potentials.
-Since we require several layer potentials with different kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and its HPC implementations that are readily available (for example, see \url{http://pvfmm.org}).
-Other challenges that will be investigated include preconditioning strategies to reduce the number of required GMRES iterations, and time adaptivity to allow for stable simulations to user-specified tolerances.
-PI Quaife has experience developing such algorithms~\cite{qua-bir2015b, qua-bir2016, qua-bir2015a, qua-cou-dar2018}.
+This quadrature approach has the advantage that it is a non-intrusive modification of the trapezoid rule, permitting an error bound that is independent of the grain configuration.
+However, the current implementation does not yet fully exploit FMM acceleration.
+The numerical challenge here is to develop FMM expansions for the velocity, vorticity, and deformation-tensor layer potentials.
+Since these layer potentials each have distinct kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and their HPC implementations (for example, see \url{http://pvfmm.org}).
+Other challenges to be investigated include preconditioning strategies to reduce the number of required GMRES iterations, and time adaptivity to enable stable simulations to user-specified tolerances.
+PI Quaife is a leading expert in developing such algorithms~\cite{qua-bir2015b, qua-bir2016, qua-bir2015a, qua-cou-dar2018}.
 
 Next, we plan to extend the simulation framework to handle chemical dissolution of solid bodies via physical laws~\eqref{Ceq}--\eqref{DissVn}.
-For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations, is already in place, but the coupling to the advection-diffusion equations~\eqref{Ceq} and interface law~\eqref{DissVn} need to be implemented.
-We proposed to solve the advection-diffusion equation~\eqref{Ceq} by first using Strang splitting~\cite{str1968} to decompose the PDE into individual PDEs for linear advection and diffusion.
-The advection equation will be solved with a semi-Lagrangian method~\cite{rob1981} so that it can be solved on an Eulerian grid without a restrictive CFL condition.
-PI Quaife has experience with using semi-Lagrangian methods for another type of complex viscous flow~\cite{kab-qua-bir2017}.
+For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations and the {\thL} method for interface evolution, is already in place.
+The BIE Stokes solver, however, has not yet been coupled to the advection-diffusion equations~\eqref{Ceq} and interface law~\eqref{DissVn} required for dissolution.
+We proposed to solve the advection-diffusion equation~\eqref{Ceq} by first using Strang splitting~\cite{str1968} to decompose the system into individual PDEs for linear advection and diffusion.
+The advection equation will be handled with a semi-Lagrangian method~\cite{rob1981} so that it can be solved on an Eulerian grid without a restrictive CFL condition.
+PI Quaife has experience using semi-Lagrangian methods in the closely related context of complex viscous flow~\cite{kab-qua-bir2017}.
+
 The diffusion equation is more challenging to accurately solve in the complex porous geometries.
 Two approaches include a memory-intensive space-time heat kernel~\cite{bar-eps-gre-jia-wan2019, jia-gre-wan2015, li-gre2009}, and Rothe's method coupled with a Yukawa equation solver~\cite{kro-qua2010, cau-cho-chr-sea2016}.
-A particular challenge of the latter method is extending functions from the complex geometry and into a regular geometry, such as a square, so that a high-order volume integral or Fourier method can be applied, and some groups have recently developed new techniques to form such an extension~\cite{fry-kro-tor2019, fry-leh-tor2019}.
+A particular challenge of the latter method is extending functions from the complex geometry into a regular geometry, such as a square, so that a high-order volume integral or Fourier method can be applied~\cite{fry-kro-tor2019, fry-leh-tor2019}.
 Alternatively, we propose to use a Laplace Transform to solve the diffusion equation
@@
 \end{alignat}
-Applying the Laplace transform, $C(\xx,s) = \mathcal{L}[c](\xx,t)$ satisfies
+The transformed variable $C(\xx,s) = \mathcal{L}[c](\xx,t)$ satisfies
 \begin{align}
@@
 where $c_0(\xx)$ is the initial concentration.
-This PDE will be solved with high-order accuracy and efficiently by using fast-multipole-accelerated integral equation methods of the Yukawa equation~\cite{kro-qua2011}, and the concentration will be recovered with an inverse Laplace transform~\cite{jos-war2006}.
-Once a high-order advection-diffusion solver is in place, by combining it with our integral equation formulation for the Stokes equation and the shear stress, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation, would finally become possible.
+This PDE will be solved with high-order accuracy and efficiently by using fast-multipole-accelerated integral equation methods of the Yukawa equation~\cite{kro-qua2011}.
+The concentration field can then be recovered with an inverse Laplace transform~\cite{jos-war2006}.
+
+By combining our BIE Stokes solver with the proposed high-order, advection-diffusion solver, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation, would finally become possible.
 Such a framework could accurately simulate the geophysically relevant scenario of karst conduits with embedded granular media.

### 2019-11-19 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 Qualitative properties of an eroded media, such as channels of high porosity, can be modest in volume fraction, but can be responsible for a large portion of the flux~\cite{Quaife2018}.
-To increase understanding of flow through eroded media, we will simulate and statistically analyze transport through eroded geometries.
+\todo[inline]{The above sentence does not make sense grammatically, at least the way I am reading it.}
+To gain an understanding of transport and dispersion through the complex geometries formed by erosion, we will simulate and statistically analyze tracer trajectories as advected by the intervening flow.
 In an eroded geometry $\Omega$, the dimensionless concentration $c$ is governed by
@@
 \end{align}
-where $\Pe$ is the dimensionless Peclet number.
-Here we assume that the concentration $c$ is affected by the eroded geometry, but the geometry is not altered further by the concentration (i.e.~$c$ is not responsible for dissolution).
+where $\Pe$ is the dimensionless Peclet number. In this context, the concentration $c$ is a passive tracer and not responsible for dissolution as in the previous section.
 
@@
 where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length, $u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of the trajectory starting at $(x_0,y_0)$ and ending at a vertical cross-section at the other end of the channel.
-Relationships between the tortuosity and porosity of a geometry have been developed by other groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and preliminary results indicate that such models might be appropriate for geometries whose porosity is increasing under the process of erosion (Fig.~\ref{fig:100tortuosity}(a)).
-However, preliminary results also indicate that erosion can increase the amount of tortuosity as is evident towards the at the towards the end of the erosion process in Fig.~\ref{fig:100tortuosity}(a).
-Moreover, we have observed a significant increase in the tortuosity at small porosities (Fig.~\ref{fig:100tortuosity}(b)).
+Relationships between the tortuosity and porosity of a geometry have been developed by other groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and preliminary results indicate that such models might be appropriate for geometries whose porosity increases under the action of erosion (Fig.~\ref{fig:100tortuosity}(a)).
+Some preliminary results, however, indicate that erosion can also transiently increase the tortuosity, as seen towards the end of the erosion process in Fig.~\ref{fig:100tortuosity}(a).
+We have observed even more significant increase in the tortuosity at small porosities and early times, as in Fig.~\ref{fig:100tortuosity}(b).
+These counterintuitive results are indicative of the complex interaction between material loss and shape change that occurs during erosion, so that macroscopic quantities like tortuosity do not always behave in a strict monotone fashion.
 
@@
 dispersion, and long-time behavior typically results in a power-law
-scaling $\sigma_\lambda \sim t^{\alpha}$. The power $\alpha$, which
-quantifies the long-time spreading, is $1$ in a ballistic regime which
-occurs at early times when the trajectories have not explored much of
-the porous geometry. However, once the trajectories have traversed a few
-grains, dispersion in porous media is often super-dispersive with
-$\alpha \in (0.5,1)$~\cite{dea-leb-den-tar-bol-dav2013}.
+scaling $\sigma_\lambda \sim t^{\alpha}$, where $\alpha$ 
+quantifies the long-time spreading.
+At early times, transport is ballistic with $\alpha = 1$, as the trajectories have not explored much of the porous geometry.
+Once the trajectories have traversed a few grains, however, dispersion typically becomes super-dispersive with $\alpha \in (0.5,1)$~\cite{dea-leb-den-tar-bol-dav2013}.
 In Fig.~\ref{fig:100dispersion}, we investigate spreading at several different porosities of a porous geometry that is initialized with 100 grains.
 
-The rate of dispersion is known to be directly related to the pore size
-distribution~\cite{dea-qua-bir-jua2018}. Therefore, there is a need to
-understand how erosion affects the pore size distribution. In
-preliminary work~\cite{chi-moo-qua2019}, we define pore sizes between
-grains that share an edge of a Delanuay triangulation with vertices at
-the grain centers (Fig.~\ref{fig:Eroding100gap_mean_var}(a)).
+The rate of dispersion is known to be directly related to the pore size distribution~\cite{dea-qua-bir-jua2018}.
+As such, we must first  understand how erosion affects the pore size distributions.
+In preliminary work~\cite{chi-moo-qua2019}, we define pore sizes between grains that share an edge of a Delanuay triangulation with vertices at the grain centers (Fig.~\ref{fig:Eroding100gap_mean_var}(a)).
 In Fig.~\ref{fig:Eroding100gap_mean_var}(a) and~\ref{fig:Eroding100gap_mean_var}(b), we plot the mean and variance of the pore sizes as a function of porosity.
@@
 We will start with the notion of a {\em porelet} which is an individual Hagen-Poiseuille flow in each of the individual pores~\cite{dea-qua-bir-jua2018}.
-By computing the strength of the individual Hagen-Poiseuille flows, the shear rate can be computed, and thus the rate of erosion can be computed.
+By computing the strength of the individual Hagen-Poiseuille flows, the shear rate, and thus the local rate of erosion, can be estimated.
 
 We have performed a carefully chosen simulation to better understand the
-effect of erosion on the pore size. We start with a single grain inside
+effect of erosion on the pore size distribution. We start with a single grain inside
 the channel that is sufficiently large that the spacing between the
 initial grain and the channel walls, which is 2 units wide), is
-$10^{-3}$. Since we use a Barycentric quadrature rule, we are able to
+$10^{-3}$. 
+\todo[inline]{There is a right parenthesis, but no left parenthesis. I am not sure where the missing parenthesis should go.}
+Since we use a Barycentric quadrature rule, we are able to
 stably simulate erosion with only 512 points on the eroding body which
 corresponds to an arclength spacing 12 times larger than the original
-separation distance---to achieve a comparable accuracy with the spectral
+separation distance; to achieve a comparable accuracy with the spectral
 trapezoid rule, 60 times as many discretization points would be
@@
 between the grain and the solid wall (black line). At all three
-configurations, the flow is nearly parabolic indicating that  porelet
-model~\cite{dea-qua-bir-jua2018} is appropriate. After performing a
+configurations, the flow is observed to be nearly parabolic, which supports the validity of the porelet
+model~\cite{dea-qua-bir-jua2018}. After performing a
 thorough analysis of the pore size growth in this simple configuration,
-we will develop a more complete model for networks of pores that are
-prevalent in porous media.
+we will develop a more complete model for pore networks that are characteristic of porous media.
 
@@
 
-Upon developing and improving numerical methods to simulate mechanical and chemical erosion, we plan to develop methods to simulate transport, gravitational sedimentation, and external buoyant forces of the eroding grains.
-In addition to the new previously described quadrature, preconditioning, adaptivity, and fast summation methods,  this extension also requires contact forces between bodies to eliminate unphysical contact that is inevitable due to discretization errors.
+Upon developing and improving numerical methods to simulate mechanical and chemical erosion, we plan to develop methods to simulate the effects of seepage transport, gravitational sedimentation, and buoyancy forces acting that act on the porous media constituents.
+In addition to the new techniques of quadrature, preconditioning, adaptivity, and fast summation described in earlier sections, this extension also requires the inclusion of contact forces between bodies to eliminate unphysical overlap that is inevitable due to discretization errors.
 Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research \cite{yan2019computing, lu-rah-zor2017, bys-sha-qua2019}.
@@
 
-The central goal of simulating transport of eroding grains is to simulate a complex porous-medium of arbitrarily sized and shaped grains undergoing the simultaneous action of mechanical-or-chemical erosion and transport due to the combined effects of seepage, contact, and buoyancy forces.
+The central goal of simulating transport of eroding grains is to simulate a complex porous-medium of arbitrarily sized and shaped grains undergoing the simultaneous action of mechanical-or-chemical erosion and transport due to the combined effects of seepage, contact, and gravitational sedimentation.
 These computations will thus simulate, with high-fidelity, the multi-physics of realistic porous-medium dynamics, albeit in a scaled down context.
@@
 \subsection{Parameterizations of Eroding Porous Media}
-These simulations have not yet begun to incorporate the slow-acting effects of mechanical and chemical erosion, and the associated gradual changes in medium properties.
-A grand goal of this proposal would be to merge the two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics robust enough to capture both short-term events, such as sinkhole collapse, and long-term changes in the medium.
+These sinkhole simulations have not yet begun to incorporate the slow-acting effects of mechanical and chemical erosion, and the associated gradual changes in medium properties.
+A grand goal of this proposal would be to merge the two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics that is robust enough to capture both short-term events, such as sinkhole collapse, and long-term changes in the medium.
 The greatest challenge faced is the disparate temporal and spatial scales that must be considered.
@@
 More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks \cite{ling2016reynolds, kutz2017deep, ling2016machine, pelt2018mixed} to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.
-The output of the high-fidelity simulations of the grain configuration can be transformed into essentially an image format, enabling us to use cutting-edge advancements on deep neural-networks for image analysis~\cite{pelt2018mixed}.
-Some important advantages of referenced work are the use of dilated convolutions in a deeply connected network, which first mixes scales and second reduces the number of super-parameters present and thus largely averts the risk of overfitting data.
-Additionally, high-fidelity flow conditions can be used to train a neural network, and this has been successfully used by others to predict, as one example, an anisotropy tensor~\cite{ling2016reynolds}.
+The output of the high-fidelity simulations of the grain configuration can be transformed into essentially an image format, permitting use of cutting-edge advances in deep neural-networks for image analysis~\cite{pelt2018mixed}.
+Some important advantages of referenced work are the use of dilated convolutions in a deeply connected network, which first mixes scales and second reduces the number of super-parameters present, thus largely mitigating the risk of overfitting data.
+Additionally, high-fidelity flow conditions can be used to train a neural network --- a strategy that has been successfully used by others to predict, for example, an anisotropy tensor~\cite{ling2016reynolds}.
 Both PIs will supervise a graduate student who will design and implement the deep-neural network for learning the essence of the high-fidelity simulations.
-Once the essential features are learned, they will be incorporated into reduced-order models that utilize the multiphase framework to enable more efficient and larger scale coarse-grained simulations of dynamic erosion.
+Once the essential features are learned, they will be incorporated into reduced-order models that harness the multiphase framework.
+These reduced models will enable more efficient and larger scale coarse-grained simulations of dynamic erosion.
 
@@
 \section{Outreach}
-The PIs are committed to utilizing and training students at various levels of their education throughout the proposed research.
-Different aspects of the proposed research are at appropriate levels for PhD students, undergraduate students, and high school students.
-Moreover, different opportunities within FSU will be used to publicize the work to K--12 students and the greater public.
+The PIs are committed to the development and training of students at various levels of their education throughout the proposed research. 
+\todo[inline]{I don't think we want to say we are `utilizing' people.}
+Different aspects of the proposed research are appropriate levels for PhD research, undergraduate research, and high school student research.
+Moreover, opportunities within FSU will be seized to publicize the work to K--12 students and to the greater public.
 
@@
 An important benefit of the research proposed here is the potential to immerse graduate students in fundamentally {\em cross-disciplinary} research.
-This proposal involves a confluence of disciplines, most centrally computational mathematics, but also geophysics, reduced-physical modeling, hydrology, and environmental science.
+This proposal involves a confluence of disciplines, most centrally computational mathematics, but also geophysics, environmental science, hydrology, and physical modeling.
 Exposure to a range of disciplines is, in the view of the PIs, an invaluable opportunity for young scientists.
@@
 The student will perform controlled experiments using natural and artificial porous media (e.g.~sand and micro-glass beads respectively) to precisely characterize the parameter regime leading to gravitational collapse.
-Parallel experiments will be conducted with erodible (bentonite clay) or dissolvable  (sucrose solids) fragments materials to represent a {\em dynamically} changing porous medium.
+Parallel experiments will be conducted with erodible (bentonite clay) or dissolvable  (sucrose solids) fragmented materials to represent a {\em dynamically} changing porous medium.
 These experiments will be used to guide, calibrate, and validate the computational advances.
@@
 This work resulted in one {\em peer-reviewed} publication already~\cite{Bolles2019}, with a second to be submitted soon.
-In addition, PI Quaife successfully trained an undergraduate student, Miles Currie, in a statistical analysis of flows related to prescribed fire dynamics.
+PI Quaife successfully trained an undergraduate student, Miles Currie, in a statistical analysis of flows related to prescribed fire dynamics.
 This work resulted in a peer-reviewed publication~\cite{cur-spe-hie-obr-goo-qua2018}.
@@
 At FSU, there are at least two excellent avenues to attract interested undergraduate students:  the Undergraduate Research Opportunity Program (UROP) and the IDEA grant.
-The UROP is a program to engage underclassmen in academic research, while the IDEA grant is a competitive program, requiring (typically advanced) students to write a proposal in which they identify a research advisor.
+The UROP is a program to engage underclassmen in academic research, while the IDEA grant is a competitive program, requiring more advanced students to write a proposal in which they identify a research advisor.
 Both programs make special efforts to recruit from underrepresented groups.

### 2019-11-19 docs/proposals/NSF/ProjDesc/ProjDesc.tex
added travel doc and went through proposal

@@
 % For 11pt size
+
+%\captionsetup{belowskip=-20pt}
 
@@
 \newcommand{\CE}{C_E}
-\newcommand {\ny}{n}
+\newcommand {\ny}{\mathbf{n}}
 \newcommand {\bdry} {\partial B}
@@
 Physical mechanisms that can alter porous-medium properties include:
-\begin{itemize}[noitemsep]
+\begin{itemize}[noitemsep,topsep=0pt]
 \item Erosion of solid material due to fluid-mechanical stresses or chemical dissolution.
@@
 \includegraphics[width = 0.99 \textwidth]{./figs/collage.pdf}
-\caption{\label{collage} Geophysical examples of chemical and mechanical erosion.
+\caption{\label{collage} \em Geophysical examples of chemical and mechanical erosion.
 Top from left: Diagram of a coupled karst-soil system with conduit formation \cite{watson2019sinkholes}; Limestone pavement in Dent de Crolles, France; Nohoch Ch’en Sinkhole in Belize.
@@
 While the governing fluid-flow equations become linear in this regime, porous-media applications present a host of new challenges, for example:
-\begin{itemize}[noitemsep]
+\begin{itemize}[noitemsep,topsep=0pt]
 \item Porous media typically involves dense packings so that close-range effects and even nearly contacting bodies must be considered.
@@
 
-{\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(10^2-10^3)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} A major step towards this goal is illustrated in Fig.~\ref{80circ8vel}, which features high-fidelity erosion simulations of an initial configuration of 80 bodies of high volume fraction $50 \%$.
+{\bf An ultimate goal of this proposal is to simulate $\boldsymbol{\mathcal{O}(10^2-10^3)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with high-order accuracy and the computational efficiency required to run large ensembles for statistical analysis.} A major step towards this goal is illustrated in Fig.~\ref{80circ8vel}, which features high-fidelity erosion simulations of an initial configuration of 80 bodies of high volume fraction $50 \%$.
 Color indicates the velocity magnitude, which highlights the spontaneous formation of channels during the erosion process.
@@
 \includegraphics[width = 0.99 \textwidth]{./figs/80circ8vel.pdf}
-\caption{\label{80circ8vel} High-fidelity numerical simulations of a configuration of densely-packed solid bodies undergoing mechanical erosion due to an intervening Stokes flow.
+\caption{\label{80circ8vel} \em High-fidelity numerical simulations of a configuration of densely-packed solid bodies undergoing mechanical erosion due to an intervening Stokes flow.
 The color indicates velocity magnitude which highlights the channel formation process.
@@
 These experiments are closely related to our proposed computational study, thus offering a great opportunity for comparison.
-Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute (see Section~\ref{sec:experiments}), which would help to guide, calibrate, and validate the computations (see letter of collaboration).
+Furthermore, {\bf we propose performing a set of experiments conducted at the nearby Geophysical Fluid Dynamics Institute (see Section~\ref{sec:experiments}), which would help to guide, calibrate, and validate the computations (see letter of collaboration).}
 
@@
 These parameterized models could then be combined with well-developed multi-phase models \cite{breward2003multiphase, cogan2010multiphase, Imma2019, eastham2019multiphase} to quantitatively describe and predict sinkhole collapse.
-
+\todo[inline]{The last paragraph of this sections seems out of place.  Maybe it just needs to be reversed with the one before it?}
 %----------------------------------------------------------------------%
@@
 We first outline the theoretical foundation that will be used in later sections of the proposal.
-At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations \begin{equation}
+At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations
+\begin{align}
   \label{eqn:StokesEq}
-\begin{split}
-\mu \Delta \uu = \grad p,	&\hspace{20pt} \xx \in \Omega, \\
-\grad \cdot \uu = 0, 		&\hspace{20pt} \xx \in \Omega,
-\end{split}
-\end{equation}
-where $\uu$ is the velocity field, $p$ the pressure field, $\mu$ the
-fluid viscosity, and $\Omega$ is the fluid domain. Linear elliptic PDEs,
-such as the Stokes equations, can be reformulated as a boundary integral
-equation (BIE).  BIEs have several numerical advantages including a
-dimension reduction, automatic mass conservation, and high-order
-accuracy. An equivalent BIE formulation of the Stokes equations in
-Eq.~\eqref{eqn:StokesEq} is
+  \mu \Delta \uu = \grad p, \quad
+  \grad \cdot \uu = 0, \quad \xx \in \Omega,
+\end{align}
+%\begin{equation}
+%\label{eqn:StokesEq}
+%\begin{split}
+%\mu \Delta \uu = \grad p,	&\hspace{20pt} \xx \in \Omega, \\
+%\grad \cdot \uu = 0, 		&\hspace{20pt} \xx \in \Omega,
+%\end{split}
+%\end{equation}
+where $\uu$ is the velocity field, $p$ the pressure field, $\mu$ the fluid viscosity, and $\Omega$ the fluid domain.
+Linear elliptic PDEs, such as the Stokes equations, can be reformulated as a boundary integral equation (BIE).
+BIEs have several numerical advantages including a dimension reduction, automatic mass conservation, and high-order accuracy.
+An equivalent BIE formulation of the Stokes equations~\eqref{eqn:StokesEq} is
 \begin{align}
@@
 where $\ff$ is a Dirichlet boundary condition, $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the outward unit normal of $\bd\Omega$.
-Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, important quantities such as the velocity, pressure, vorticity, and deformation tensor can be computed in the fluid bulk.
+Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, quantities such as the velocity, pressure, vorticity, and deformation tensor can be computed in the fluid bulk.
 For example, the velocity at $\xx \in \Omega$ is
@@
 
-Whilst the most immediate proposed work on computational methods to
-simulate erosion will utilize~\eqref{eqn:StokesEq}, the later stages of this project will also incorporate~\eqref{DarcyEq}, or closely related variants known as multiphase models \cite{breward2003multiphase, cogan2010multiphase, Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
+Whilst the most immediate proposed work on computational methods to simulate erosion will utilize~\eqref{eqn:StokesEq}, the later stages of this project will incorporate~\eqref{DarcyEq}, or closely related variants known as multiphase models \cite{breward2003multiphase, cogan2010multiphase, Imma2019, eastham2019multiphase}, in order to develop coarse-grained descriptions for porous medium evolution and the associated dispersion within.
 These models will rely on statistical analysis of the data produced by the high-fidelity erosion simulations in order to parameterize the effects of erosion, leading to deterministic or stochastic reduced-order models for porous-medium evolution.
@@
 Currently, the relationship between these scales is poorly understood.
-The high-fidelity, efficient computational methods proposed here will enable a deeper understanding of these processes, which is the first step towards developing effective strategies for managing water resources and mitigating catastrophic events such as contamination or structural collapse.
+The proposed high-fidelity, efficient computational methods will enable a deeper understanding of these processes, which is the first step towards developing effective strategies for managing water resources and mitigating catastrophic events such as contamination or structural collapse.
 For example, the insights gained here could potentially help identify locations in natural aquifers vulnerable to contamination and/or collapse.
 
-In addition to these societal impacts, the work proposed here will spur the training of mathematicians and computational scientists in fundamentally cross-disciplinary research of great societal importance.
+In addition to these societal impacts, the proposed work will spur the training of mathematicians and computational scientists in fundamentally cross-disciplinary research of great societal importance.
 Further, the PIs will engage in educational and outreach activities to impact future generations of mathematical scientists, with particular focus on women and underrepresented minorities (URM).
 Both PIs are already actively involved in graduate and undergraduate research, as well as outreach to K-12 students.
-Further, we have successfully recruited women and underrepresented minorities in undergraduate, graduate, and postdoctoral research.
+Further, we have successfully recruited women and underrepresented minorities in high school, undergraduate, graduate, and postdoctoral research.
 
@@
 Large ensembles of the high-fidelity simulations will inform the coarse-grained models to be developed in the later stages of the proposed work.
+
   \item The proposed research is interdisciplinary by nature, with immediate applications in the fields of geophysics and environmental sciences.
-The PIs already have experience collaborating with scientists from other disciplines \cite{Caves2018, eastham2019multiphase, Bolles2019} through FSU's Geophysical Fluid Dynamics Institute, an interdisciplinary unit comprised of a diverse set of faculty from home departments in example Earth, Atmospheric, and Ocean Sciences, Geology, Physics, Civil Engineering, Environmental Engineering, Scientific Computing, Mathematics, and others.
+The PIs already have experience collaborating with scientists from other disciplines \cite{Caves2018, eastham2019multiphase, Bolles2019, cur-spe-hie-obr-goo-qua2018} through FSU's Geophysical Fluid Dynamics Institute, an interdisciplinary unit comprised of a diverse set of faculty from home departments in example Earth, Atmospheric, and Ocean Sciences, Geology, Physics, Civil Engineering, Environmental Engineering, Mechanical Engineering, Scientific Computing, Mathematics, and others.
+
   \item The proposed research is a collaborative effort with a focus on training future generations of scientists and mathematicians.
@@
 The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion in the Stokes flow regime~\cite{Quaife2018}, the regime relevant for the currently proposed groundwater applications.
-Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion \cite{chi-moo-qua2019}.
-
-\paragraph{Outline of the Proposal:}
-
-\todo[inline]{Summary of what is in the proposal.}
+Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion~\cite{chi-moo-qua2019}.
 
@@
 %----------------------------------------------------------------------%
-The goal of the proposed research is to develop new numerical methods to
-simulate erosion processes. Specific research tasks will include:
-\begin{itemize}[noitemsep]
-  \item Simulating chemical erosion.
+The goal of the proposed research is to develop computational methods to better understand erosion processes. Specific research tasks will include:
+\begin{enumerate}[noitemsep,label=(\arabic*)]
+  \item Simulating chemical erosion, and transport, including sedimentation and compaction, of eroding bodies
 
-  \item Characterizing anisotropy and permeability to inform
-    homogenized models such as Darcy's relation.
+  \item Characterizing anisotropy, permeability, and pore size dynamics to inform homogenized models such as Darcy's relation~\eqref{DarcyEq}.
 
-  \item Simulating the transport of finite Peclet number concentrations
-    inside eroded porous geometries.
+  \item Simulating the transport of finite Peclet number concentrations in eroded porous geometries.
 
-  \item Improving numerical methods including fast summation methods,
-    preconditioners, and quadrature.
+  \item Improving numerical methods including fast summation methods, preconditioners, and quadrature.
 
-  \item Developing new models to characterize the effect of erosion on
-    pore size dynamics.
+  \item Developing and validating new parameterizations using machine learning techniques, numerical simulations, and in-house experiments.
 
-  \item Developing new parameterizations using modern machine learning
-    techniques.
-
-  \item Validating simulations with in-house experimental results.
-
-  \item \todo[inline]{Something about transport, sedimentation, etc.}
-\end{itemize}
+\end{enumerate}
 
@@
 \end{align}
-In the case of chemically-induced erosion, a solute concentration field $C$ undergoes advection and diffusion:
+In the case of chemically-induced erosion, a solute concentration field $c$ undergoes advection and diffusion:
 \begin{align}
   \label{Ceq}
-  \pd{C}{t} + \uu \cdot \grad C = \Diff \Lap C.
+  \pd{c}{t} + \uu \cdot \grad c = \Diff \Lap c.
 \end{align}
@@
 \label{DissVn}
-\Vn = \Diff \pd{C}{\ny}.
+\Vn = \Diff \pd{c}{\ny}.
 \end{equation}
@@
 \includegraphics[width = 0.99 \textwidth]{./figs/80circ8vort.pdf}
-\caption{\label{80circ8vort} Simulation of 80 bodies eroding in Stokes flow under the action of shear stress.
+\caption{\label{80circ8vort} \em Simulation of 80 bodies eroding in Stokes flow under the action of shear stress.
 Flow is left to right.
@@
 Figs.~\ref{80circ8vel} and~\ref{80circ8vort} show preliminary results of 80 bodies, initially of random position and size, undergoing mechanical erosion in Stokes flow.
-This simulation extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed Barycentric interpolation scheme~\cite{bar2014, bar-wu-vee2015, chi-moo-qua2019}, which enables more densely packed configurations.
-The color in Fig~\ref{80circ8vort} represents the vorticity field surrounding the bodies.
+This simulation extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed barycentric quadrature scheme~\cite{bar2014, bar-wu-vee2015, chi-moo-qua2019}, which enables more densely packed configurations.
+The color in Fig.~\ref{80circ8vort} represents the vorticity field surrounding the bodies.
 Vorticity, since it reduces to shear on solid interfaces, provides a convenient way to visualize local erosion rates, as well as the local flow intensity.
@@
 In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
-This channelization process is made even more apparent by viewing the velocity magnitude as in Fig.~\ref{80circ8vel}.
+This channelization process is made even more apparent by viewing the velocity magnitude in Fig.~\ref{80circ8vel}.
 
@@
 The much more modest decrease of area fraction is not sufficient to account for this exponential rate.
-Hence the reshaping process, in particular the formation of channels, plays a pivotal role the medium's macroscopic resistivity to flow.
+Hence the reshaping process, in particular the formation of channels, plays a pivotal role in the medium's macroscopic resistivity to flow.
 
 Lastly, the right-most plot of Fig.~\ref{fig3} shows new, preliminary results on how medium anisotropy evolves during the reshaping process of erosion.
-Anisotropy calculated as the ratio of vertical to horizontal resistivity, with the vertical resistivity computed by rotating the configuration of bodies by 90 degrees.
+Anisotropy is calculated as the ratio of vertical to horizontal resistivity, with the vertical resistivity computed by rotating the configuration of bodies by 90 degrees.
 This plot shows the anisotropy to initial increase with time.
@@
 \includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
-  \caption{\label{fig3} {\em Left}: The area fraction of solid bodies versus time.
+  \caption{\label{fig3} \em Left: The area fraction of solid bodies versus time.
 Time is normalized by the vanishing time $t_f$.
-{\em Middle}: The resistivity of the porous matrix decrease much more rapidly than area fraction, indicating the reshaping process to be essential.
+Middle: The resistivity of the porous matrix decrease much more rapidly than area fraction, indicating the reshaping process to be essential.
 Right: The anisotropy (ratio of vertical to horizontal resistivity) as it varies in time.
-Erosion can create a highly anisotropic medium.}
-\end{center}
+Erosion can create a highly anisotropic medium.} \end{center}
 \end{figure}
@@
 
-{An immediate goal of the proposed work is to extend the range of physical effects captured in these simulations.} A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
-To address this problem, we have very recently extended a Barycentric quadrature~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing~\cite{chi-moo-qua2019}.
-This quadrature approach has the advantage that it is a non-intrusive modification of the trapezoid rule, permitting an error bound that is independent of the grain configuration.
+{\bf An immediate goal of the proposed work is to extend the range of physical effects captured in these simulations.} A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
+To address this problem, we have very recently extended a Barycentric quadrature method~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing~\cite{chi-moo-qua2019}.
+The quadrature method is a non-intrusive modification of the trapezoid rule and results in an error bound that is independent of the grain configuration.
 However, the current implementation does not yet fully exploit FMM acceleration.
-The numerical challenge here is to develop FMM expansions for the velocity, vorticity, and deformation-tensor layer potentials.
+The computational challenge is to develop FMM expansions for the velocity, vorticity, and deformation-tensor layer potentials.
 Since these layer potentials each have distinct kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and their HPC implementations (for example, see \url{http://pvfmm.org}).
 Other challenges to be investigated include preconditioning strategies to reduce the number of required GMRES iterations, and time adaptivity to enable stable simulations to user-specified tolerances.
-PI Quaife is a leading expert in developing such algorithms~\cite{qua-bir2015b, qua-bir2016, qua-bir2015a, qua-cou-dar2018}.
+PI Quaife is an expert in developing such algorithms~\cite{qua-bir2015b, qua-bir2016, qua-bir2015a, qua-cou-dar2018}.
 
@@
 PI Quaife has experience using semi-Lagrangian methods in the closely related context of complex viscous flow~\cite{kab-qua-bir2017}.
-
 The diffusion equation is more challenging to accurately solve in the complex porous geometries.
@@
 A particular challenge of the latter method is extending functions from the complex geometry into a regular geometry, such as a square, so that a high-order volume integral or Fourier method can be applied~\cite{fry-kro-tor2019, fry-leh-tor2019}.
-Alternatively, we propose to use a Laplace Transform to solve the diffusion equation
-\begin{alignat}{3}
-  \pd{c}{t} &= \frac{1}{\Pe} \Delta c, \quad &&\xx \in \Omega, \: t>0.
-\end{alignat}
-The transformed variable $C(\xx,s) = \mathcal{L}[c](\xx,t)$ satisfies
+Alternatively, we propose to use a Laplace Transform, $C(\xx,s) = \mathcal{L}[c](\xx,t)$, which satisfies
+\begin{wrapfigure}[19]{r}{0.3\textwidth}
+  \includegraphics[width=0.3\textwidth]{figs/100b_t100tracer}
+  \caption{\label{fig:100tracers} \em Streamlines visualized with 200 tracers passing through an eroded geometry.
+The tracers are initialized at the left end of the channel and the flow is from left to right.} \end{wrapfigure}
 \begin{align}
@@
 \end{align}
-where $c_0(\xx)$ is the initial concentration.
+where $c_0(\xx)$ is the initial concentration and $\Pe$ is the dimensionless Peclet number.
 This PDE will be solved with high-order accuracy and efficiently by using fast-multipole-accelerated integral equation methods of the Yukawa equation~\cite{kro-qua2011}.
-The concentration field can then be recovered with an inverse Laplace transform~\cite{jos-war2006}.
+The concentration field will then be recovered with an inverse Laplace transform~\cite{jos-war2006}.
 
-By combining our BIE Stokes solver with the proposed high-order, advection-diffusion solver, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation, would finally become possible.
+By combining our BIE Stokes solver with the proposed high-order, advection-diffusion solver, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation (see Section~\ref{sec:sinkhole}), would finally become possible.
 Such a framework could accurately simulate the geophysically relevant scenario of karst conduits with embedded granular media.
-The gradual changes in the medium and karst boundaries due to erosion and dissolution could create conditions favorable for mechanical failure or collapse of the structure, for example sinkholes (see Section~\ref{sec:sinkhole}).
+The gradual changes in the medium and karst boundaries due to erosion and dissolution could create conditions favorable for mechanical failure or collapse of the structure, for example sinkholes.
 
@@
 
-\begin{wrapfigure}[23]{r}{0.4\textwidth}
-  \includegraphics[width=0.4\textwidth]{figs/100b_t100tracer}
-  \caption{\label{fig:100tracers} A visualization of the streamlines
-  with 200 tracers passing through an eroded geometry with a porosity of
-  0.63. The tracers are initialized at the left end of the channel and
-  the flow is driven by a pressure difference from left to right.}
-\end{wrapfigure}
-
 Transport through eroded media is a direct consequence of the pore structure.
-Qualitative properties of an eroded media, such as channels of high porosity, can be modest in volume fraction, but can be responsible for a large portion of the flux~\cite{Quaife2018}.
-\todo[inline]{The above sentence does not make sense grammatically, at least the way I am reading it.}
 To gain an understanding of transport and dispersion through the complex geometries formed by erosion, we will simulate and statistically analyze tracer trajectories as advected by the intervening flow.
@@
 
-In the infinite Peclet number limit, the concentration is governed by pure advection and the characteristics of the concentration field are identical to the streamlines (Fig.~\ref{fig:100tracers}).
-The $j^{th}$ trajectory, or characteristic, is governed by $\dot{\ss}_j(t) = \uu(\ss_j(t))$.
-Once these trajectories are computed, using for example a high-order Runge-Kutta method, a statistical analysis can be used to describe the transport.
-Two of the most important measurements are the tortuosity and the anomalous dispersion, both which are defined in terms of the length of the trajectories.
-Upon computing $N_p$ trajectories, the tortuosity is the dimensionless number
+In the infinite Peclet number limit, the concentration is governed by pure advection and the characteristics of the concentration field satisfy $\dot{\ss}(t) = \uu(\ss(t))$ and are identical to the streamlines (Fig.~\ref{fig:100tracers}).
+Once $N_p$ trajectories are computed, using for example a high-order Runge-Kutta method, transport can be quantified.
+Two of the most important measurements to quantify transport are the tortuosity and the anomalous dispersion, both which are defined in terms of the length of the trajectories.
+The tortuosity is the dimensionless number
 \begin{align}
@@
 \end{align}
-where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length, $u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of the trajectory starting at $(x_0,y_0)$ and ending at a vertical cross-section at the other end of the channel.
+which is approximated using the $N_p$ trajectories.
+Here, $S$ is the vertical cross-section at $x=x_0$, $d$ is its length, $u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of the trajectory starting at $(x_0,y_0)$ and ending at a vertical cross-section at the other end of the channel.
 Relationships between the tortuosity and porosity of a geometry have been developed by other groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and preliminary results indicate that such models might be appropriate for geometries whose porosity increases under the action of erosion (Fig.~\ref{fig:100tortuosity}(a)).
 Some preliminary results, however, indicate that erosion can also transiently increase the tortuosity, as seen towards the end of the erosion process in Fig.~\ref{fig:100tortuosity}(a).
-We have observed even more significant increase in the tortuosity at small porosities and early times, as in Fig.~\ref{fig:100tortuosity}(b).
+We have observed an even more significant increase in the tortuosity at small porosities and early times, as in Fig.~\ref{fig:100tortuosity}(b).
 These counterintuitive results are indicative of the complex interaction between material loss and shape change that occurs during erosion, so that macroscopic quantities like tortuosity do not always behave in a strict monotone fashion.
@@
   \includegraphics[width=\textwidth]{figs/tort_eulerian100}
-  \caption{100 eroding bodies}
+  \caption{\em 100 eroding bodies}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{figs/tort_eulerian20}
-  \caption{20 eroding bodies}
+  \caption{\em 20 eroding bodies}
   \end{subfigure}
   \end{center}
-  \caption{\label{fig:100tortuosity} The tortuosity of two different eroding geometries.
+  \caption{\label{fig:100tortuosity} \em The tortuosity of two different eroding geometries.
 The tortuosity can be computed using two different formulas (red vs.~blue marks).
@@
 
-\begin{wrapfigure}[19]{r}{0.35\textwidth}
-  \includegraphics[width=0.35\textwidth]{figs/100b_second_moment_long_ref}
-  \caption{\label{fig:100dispersion} The particle spreading, characterized with the standard deviation $\sigma_\lambda(t)$ at six different porosities.
-At early times, the line of slope 1 (black curve) indicates a ballistic motion.
+While the tortuosity characterizes the amount of winding of trajectories, the dispersion characterizes their spreading.
+Dispersion can be described using the first- and second-ensemble moments of the trajectories
+\begin{align}
+  \langle \lambda \rangle (t) = \frac{1}{N_p} 
+      \sum_{j=1}^{N_p} \lambda_j(t), \quad
+  \sigma_\lambda^{2}(t) = \frac{1}{N_p}
+    \sum_{j=1}^{N_p} (\lambda_j(t) - \langle \lambda \rangle(t))^2.
+\end{align}
+\begin{wrapfigure}[22]{l}{0.4\textwidth}
+  \includegraphics[width=0.4\textwidth]{figs/100b_second_moment_long_ref}
+  \caption{\label{fig:100dispersion} \em The particle spreading, characterized with the standard deviation $\sigma_\lambda(t)$ at six different porosities.
+At early times, the line of slope 1 (black dashed curve) indicates a ballistic motion.
 At later times, the dispersion becomes super-dispersive at a rate indicated by the slope of the black dashed-dotted line.}
 \end{wrapfigure}
-While the tortuosity characterizes the amount of winding of streamlines, the dispersion characterizes the spreading of the trajectories.
-Dispersion can be described using the first- and second-ensemble moments of the trajectories
-\begin{align}
-  \begin{split}
-  \langle \lambda \rangle (t) &= \frac{1}{N_p} 
-      \sum_{j=1}^{N_p} \lambda_j(t), \\ 
-  \sigma_\lambda^{2}(t) &= \frac{1}{N_p}
-    \sum_{j=1}^{N_p} (\lambda_j(t) - \langle \lambda \rangle(t))^2.
-  \end{split}
-\end{align}
-Then, the standard deviation $\sigma_\lambda$ characterizes the
-dispersion, and long-time behavior typically results in a power-law
-scaling $\sigma_\lambda \sim t^{\alpha}$, where $\alpha$ 
-quantifies the long-time spreading.
+Then, the standard deviation $\sigma_\lambda$ characterizes the dispersion, and long-time behavior typically results in a power-law scaling $\sigma_\lambda \sim t^{\alpha}$, where $\alpha$ quantifies the long-time spreading.
 At early times, transport is ballistic with $\alpha = 1$, as the trajectories have not explored much of the porous geometry.
-Once the trajectories have traversed a few grains, however, dispersion typically becomes super-dispersive with $\alpha \in (0.5,1)$~\cite{dea-leb-den-tar-bol-dav2013}.
+Once the trajectories have traversed a few grains, however, spreading typically becomes super-dispersive with $\alpha \in (0.5,1)$~\cite{dea-leb-den-tar-bol-dav2013}.
 In Fig.~\ref{fig:100dispersion}, we investigate spreading at several different porosities of a porous geometry that is initialized with 100 grains.
 
-The rate of dispersion is known to be directly related to the pore size distribution~\cite{dea-qua-bir-jua2018}.
-As such, we must first  understand how erosion affects the pore size distributions.
+The rate of dispersion is directly related to the pore size distribution~\cite{dea-qua-bir-jua2018}.
+As such, {\bf we propose to investigate how erosion affects pore size distributions}.
 In preliminary work~\cite{chi-moo-qua2019}, we define pore sizes between grains that share an edge of a Delanuay triangulation with vertices at the grain centers (Fig.~\ref{fig:Eroding100gap_mean_var}(a)).
-In Fig.~\ref{fig:Eroding100gap_mean_var}(a) and~\ref{fig:Eroding100gap_mean_var}(b), we plot the mean and variance of the pore sizes as a function of porosity.
-To better understand how erosion affects the anomalous dispersion, we propose to investigate how the pores grow with erosion.
-We will start with the notion of a {\em porelet} which is an individual Hagen-Poiseuille flow in each of the individual pores~\cite{dea-qua-bir-jua2018}.
+We then compute and plot the mean and variance of the pore sizes as a function of porosity in Fig.~\ref{fig:Eroding100gap_mean_var}(b) and~\ref{fig:Eroding100gap_mean_var}(c).
+Continuing in this direction, we will use the notion of a {\em porelet}, an individual Hagen-Poiseuille flow in each of the individual pores~\cite{dea-qua-bir-jua2018}, to continue to investigate the effect of erosion on pores sizes.
 By computing the strength of the individual Hagen-Poiseuille flows, the shear rate, and thus the local rate of erosion, can be estimated.
-
-We have performed a carefully chosen simulation to better understand the
-effect of erosion on the pore size distribution. We start with a single grain inside
-the channel that is sufficiently large that the spacing between the
-initial grain and the channel walls, which is 2 units wide), is
-$10^{-3}$. 
-\todo[inline]{There is a right parenthesis, but no left parenthesis. I am not sure where the missing parenthesis should go.}
-Since we use a Barycentric quadrature rule, we are able to
-stably simulate erosion with only 512 points on the eroding body which
-corresponds to an arclength spacing 12 times larger than the original
-separation distance; to achieve a comparable accuracy with the spectral
-trapezoid rule, 60 times as many discretization points would be
-required. In Fig.~\ref{fig:porelets}(a), different shades of grey
-correspond to the configuration of the eroding grain at five equally
-spaced time steps. At three of the time steps, we plot the velocity
-between the grain and the solid wall (black line). At all three
-configurations, the flow is observed to be nearly parabolic, which supports the validity of the porelet
-model~\cite{dea-qua-bir-jua2018}. After performing a
-thorough analysis of the pore size growth in this simple configuration,
-we will develop a more complete model for pore networks that are characteristic of porous media.
 
@@
 \end{subfigure}
-  \caption{\label{fig:Eroding100gap_mean_var} (a) The pore sizes are
-  defined in terms of a Delanuay triangulation. The effect of erosion on
-  (b) the mean and (c) the variance of the pore sizes. The geometry
-  initially contains 100 eroding bodies.}
+  \caption{\label{fig:Eroding100gap_mean_var} \em (a) The pore sizes are defined in terms of a Delanuay triangulation.
+The effect of erosion on (b) the mean and (c) the variance of the pore sizes.
+The geometry initially contains 100 eroding bodies.}
 \end{figure}
 
-We propose to extend our preliminary results by considering
-concentrations with finite Peclet numbers. We will deploy the same
-numerical methods to simulate dissolution and melting to study a
-concentration that is being transported through a eroded porous
+We have performed a carefully chosen simulation to better understand the effect of erosion on the pore size distribution.
+We start with a single grain inside the channel that is sufficiently large that the spacing between the initial grain and the channel walls, which is 2 units wide, is $10^{-3}$.
+By using a Barycentric quadrature rule, we stably simulate erosion with only 512 points on the eroding body which corresponds to an arclength spacing 12 times larger than the original separation distance; to achieve a comparable accuracy with the spectral trapezoid rule, 60 times as many discretization points would be required.
+In Fig.~\ref{fig:porelets}(a), different shades of grey correspond to the configuration of the eroding grain at five equally spaced time steps.
+At three of the time steps, we plot the velocity between the grain and the solid wall (black line).
+At all three configurations, the flow is observed to be nearly parabolic, supporting the validity of the porelet model~\cite{dea-qua-bir-jua2018}.
+After performing a thorough analysis of the pore size growth in this simple configuration, we will develop a more complete model for pore networks that are characteristic of porous media.
+
+Finally, {\bf we propose to extend our preliminary results by
+considering concentrations with finite Peclet numbers}. We will deploy
+the same numerical methods to simulate dissolution and melting to study
+a concentration that is being transported through a eroded porous
 geometry. Again, this will encompass Strang splitting~\cite{str1968}, a
@@
   \end{subfigure}
-  \caption{\label{fig:porelets} (a) An eroding body at five equally time steps in $[0,1]$.
-The far field condition is a constant pressure drop in a channel three times as wide as the eroding grain.
-At the three intermediate time steps, the velocity field in the field, which is nearly parabolic, is included.
+  \caption{\label{fig:porelets} \em (a) An eroding body at five equally time steps.
+At the three intermediate time steps, the Stokesian velocity field in the bulk, which is nearly parabolic, is included.
 (b) The pore size (black) and maximum velocity in the pore (red) as a function of time.
-As the channel opens, the flow rate increases to maintain a constant pressure drop, and this increases the rate of erosion.}
+As the channel opens, the flow rate increases to maintain a constant pressure drop.}
 \end{figure}
@@
 
-Upon developing and improving numerical methods to simulate mechanical and chemical erosion, we plan to develop methods to simulate the effects of seepage transport, gravitational sedimentation, and buoyancy forces acting that act on the porous media constituents.
-In addition to the new techniques of quadrature, preconditioning, adaptivity, and fast summation described in earlier sections, this extension also requires the inclusion of contact forces between bodies to eliminate unphysical overlap that is inevitable due to discretization errors.
-Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research \cite{yan2019computing, lu-rah-zor2017, bys-sha-qua2019}.
+Upon developing and improving numerical methods to simulate mechanical
+and chemical erosion, {\bf we will develop methods to simulate the
+effects of seepage transport, gravitational sedimentation, and buoyancy
+forces acting that act on the porous media constituents.} In addition to
+the new techniques for quadrature, preconditioning, adaptivity, and fast
+summation described in earlier sections, this extension also requires
+the inclusion of contact forces between bodies to eliminate unphysical
+overlap that is inevitable due to discretization errors. Though
+conceptually straightforward, implementing contact forces in multibody
+fluid-structure simulations is far from simple in practice, with several
+competing possible strategies that are a topic of current research
+\cite{yan2019computing, lu-rah-zor2017, bys-sha-qua2019,
+kab-qua-bir2018, vou-har-tam-gri2011}.
 
@@
 Ultimately, such simulations could be used to build an understanding of medium reconfiguration events, such as sinkhole collapse or conduit formation in karst networks.
-In very preliminary work, PI Moore has been running simplified simulations with a current graduate student.
+In very preliminary work, PI Moore has run simplified simulations with a current graduate student.
 These preliminary simulations are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
-They utilize the homogenized description of the flow field in~\eqref{DarcyEq} and incorporate the physical effects of: \begin{itemize}[noitemsep]
+They utilize the homogenized description of the flow field in~\eqref{DarcyEq} and incorporate the physical effects of:
+\begin{itemize}[noitemsep]
 \item Transport of grains due to seepage force from the surrounding fluid flow.
@@
 \end{itemize}
-Preliminary investigation suggests that this last mechanisms of cohesion is essential to model sinkhole collapse in the system.
+Preliminary investigation suggests that this last mechanism of cohesion is essential to model sinkhole collapse in the system.
 
@@
 These sinkhole simulations have not yet begun to incorporate the slow-acting effects of mechanical and chemical erosion, and the associated gradual changes in medium properties.
-A grand goal of this proposal would be to merge the two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics that is robust enough to capture both short-term events, such as sinkhole collapse, and long-term changes in the medium.
-The greatest challenge faced is the disparate temporal and spatial scales that must be considered.
+{\bf A grand goal of this proposal is to merge the two lines of inquiry to develop a sound theoretical framework for porous-medium dynamics that is robust enough to capture both short-term events, such as sinkhole collapse, and long-term changes in the medium.} The greatest challenge faced is the disparate temporal and spatial scales that must be considered.
 Our proposed strategy is to use the high-fidelity erosion simulations to parametrize the effect of erosion on medium properties.
@@
 Some important advantages of referenced work are the use of dilated convolutions in a deeply connected network, which first mixes scales and second reduces the number of super-parameters present, thus largely mitigating the risk of overfitting data.
-Additionally, high-fidelity flow conditions can be used to train a neural network --- a strategy that has been successfully used by others to predict, for example, an anisotropy tensor~\cite{ling2016reynolds}.
-Both PIs will supervise a graduate student who will design and implement the deep-neural network for learning the essence of the high-fidelity simulations.
+Additionally, high-fidelity flow conditions can be used to train a neural network---a strategy that has been successfully used by others to predict, for example, an anisotropy tensor~\cite{ling2016reynolds}.
+Both PIs will supervise a graduate student who will design and implement deep-neural networks for learning the essence of the high-fidelity simulations.
 Once the essential features are learned, they will be incorporated into reduced-order models that harness the multiphase framework.
@@
 \label{sec:experiments}
-As mentioned previously, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments~\cite{tao2014experimental}.
-First, already existing data from these experiments offers a testbed for comparison against our newly developed simulations.
-Furthermore, we propose to run a set of new experiments at the facilities offered by GFDI, spearheaded by an undergraduate student in close collaboration with the graduate students, PIs, and an experimentalist at GFDI.
+As mentioned previously, researchers at FSU's Geophysical Fluid Dynamics
+Institute (GFDI) have investigated the mechanisms behind sinkhole
+formation with a series of scaled-down laboratory
+experiments~\cite{tao2014experimental}. First, already existing data
+from these experiments offers a testbed for comparison against our newly
+developed simulations. Furthermore, {\bf we propose to run a set of new
+experiments at the facilities offered by GFDI}, spearheaded by an undergraduate student in close collaboration with the graduate students, PIs, and an experimentalist at GFDI.
 These new experiments will more deeply probe the mechanisms underlying sinkhole formation with the special design goal of comparison against the numerical simulations.
 These experiments will be used to calibrate and validate our computations.
+\todo[inline]{We have more room at the end of the document. This
+section seems a bit brief and could maybe be expanded.}
 
@@
 \section{Outreach}
-The PIs are committed to the development and training of students at various levels of their education throughout the proposed research. 
-\todo[inline]{I don't think we want to say we are `utilizing' people.}
+The PIs are committed to the development and training of students at various levels of their education throughout the time frame of the proposed research.
 Different aspects of the proposed research are appropriate levels for PhD research, undergraduate research, and high school student research.
@@
 \subsection{Graduate Research}
-An important benefit of the research proposed here is the potential to immerse graduate students in fundamentally {\em cross-disciplinary} research.
+An important benefit of the proposed research is the potential to immerse graduate students in fundamentally {\em cross-disciplinary} research.
 This proposal involves a confluence of disciplines, most centrally computational mathematics, but also geophysics, environmental science, hydrology, and physical modeling.
@@
 
-Naturally, the research proposed here will form the foundation for the
-PhD dissertations of the graduate students involved. Beyond this, the
-students will engage in publishing articles in peer-reviewed journals of
-high quality and attending national and international conferences where
-they will present their work and network with experts in the field. The
-PIs will closely mentor the graduate students to ensure their continued
-development, not only intellectually, but also in the `soft' skills of
-communication, promotion, and networking. Having both PIs Moore and
-Quaife involved in the training of each graduate student is especially
-valuable for offering multiple perspectives on these issues. The PIs
-will make special efforts to recruit women and underrepresented
-minorities as the graduate students funded by this project. Both PIs
-have already had success recruiting women in these roles, as the first
-graduate student to receive her PhD under Moore's advising was female
-(Karina Khazmutdinova, 2016), and Quaife's current PhD student is female
-(Ashley Gannon, 2022).
+Naturally, the proposed research will form the foundation for the PhD dissertations of the supported graduate students.
+Beyond this, the students will engage in publishing articles in peer-reviewed journals of high quality and attending national and international conferences where they will present their work and network with experts in the field.
+The PIs will closely mentor the graduate students to ensure their continued development, not only intellectually, but also in the `soft' skills of communication, promotion, and networking.
+Having both PIs Moore and Quaife involved in the training of each graduate student is especially valuable for offering multiple perspectives on these issues.
+The PIs will make special efforts to recruit women and underrepresented minorities as the graduate students funded by this project.
+Both PIs have already had success recruiting women in these roles, as the first graduate student to receive her PhD under Moore's advising was female (Karina Khazmutdinova, 2016), and Quaife's current PhD student (Ashley Gannon, 2022) and Master's student (Daryn Sagel, 2020) are female.
 
@@
 At FSU, there are at least two excellent avenues to attract interested undergraduate students:  the Undergraduate Research Opportunity Program (UROP) and the IDEA grant.
-The UROP is a program to engage underclassmen in academic research, while the IDEA grant is a competitive program, requiring more advanced students to write a proposal in which they identify a research advisor.
+The UROP is a program to engage undergraduates in academic research, while the IDEA grant is a competitive program, requiring more advanced students to write a proposal in which they identify a research advisor.
 Both programs make special efforts to recruit from underrepresented groups.
@@
 
-Plans for future outreach include continued collaboration with CPALMS to create a series of educational videos for both students and teachers, as well as planned activities at {\bf Math Fun Day}, which is an annual event held by the FSU Mathematics departments to engage K-12 students in the region.
+Plans for future outreach include continued collaboration with CPALMS to create a series of educational videos for both students and teachers, as well as planned activities at {\bf Math Fun Day}, which is an annual event held by the FSU Department of Mathematics to engage K-12 students in the region.
 PI Moore has led activities at Math Fun Day in prior years and, related to the current proposal, plans to deliver lectures and demos on porous-media flows, erosion, and sinkhole collapse.
@@
 The PIs will propose research projects that are accessible to high school students throughout the duration of the proposed research.
-In addition to high school students receiving a high school experience, the PhD students will be tasked with much of the day-to-day interaction with the high school students.
+In addition to high school students receiving a university experience, the PhD students will be tasked with much of the day-to-day interaction with the high school students.
 This offers an excellent opportunity for the PhD students to develop leadership and mentorship skills.
-
-%----------------------------------------------------------------------%
-\section{Timeline}
 

### 2019-11-19 docs/proposals/NSF/ProjDocs/funding_BQ.tex
added travel doc and went through proposal

\documentclass[11pt]{article}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{amsmath,amsfonts,amssymb}
\usepackage{tabularx}
\usepackage{todonotes}
\usepackage{mathpazo}

%\renewcommand\thesubsection{(\alph{subsection})}
%\renewcommand\thesubsubsection{(\roman{subsubsection})}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}
% For 11pt size

\pagestyle{fancy}
\lhead{\footnotesize Bryan Quaife}
\chead{\footnotesize Current and Pending Support}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

\begin{document}

\subsection*{Current Support:}
{\bf Title}: Computational Methods for Complex Stokesian Fluids \\
{\bf Source}: Simons Foundation, Mathematics and Physical
Sciences-Collaboration Grants for Mathematicians \\
{\bf Total Award Amount:} \$25,200 (Travel funds only) \\
{\bf Duration:} September 1, 2017--August 31, 2020 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 0 \\

\noindent
{\bf Title}: The Role of Vorticity and Fuel Moisture on the Near-Field
Plume Structure and Ember Dynamics \\
{\bf Source}: Department of Defense, Strategic Environmental Research
and Development Program \\
{\bf Total Award Amount:} \$2,235,917 \\
{\bf Duration:} May 2020--January 2024 (This is a collaborative grant
that supports 7 PIs from 4 institutions) \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\

\vspace{-17pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Pending Support:}
{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
Media (this proposal) \\
{\bf Source}: National Science Foundation, Division of Mathematical
Sciences, Computational Mathematics \\
{\bf Total Award Amount:} \$383,086 \\
{\bf Duration:} July 1, 2020--June 30, 2023 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\

\end{document}

### 2019-11-20 docs/proposals/NSF/ProjDocs/funding_NM.tex
NM

--- 2019-11-19 docs/proposals/NSF/ProjDocs/funding_BQ.tex
@@
 \pagestyle{fancy}
-\lhead{\footnotesize Bryan Quaife}
+\lhead{\footnotesize MNJ Moore}
 \chead{\footnotesize Current and Pending Support}
@@
 \subsection*{Current Support:}
-{\bf Title}: Computational Methods for Complex Stokesian Fluids \\
+
+{\bf Title}: Dynamic interactions between fluid flows and moving boundaries \\
 {\bf Source}: Simons Foundation, Mathematics and Physical
 Sciences-Collaboration Grants for Mathematicians \\
-{\bf Total Award Amount:} \$25,200 (Travel funds only) \\
-{\bf Duration:} September 1, 2017--August 31, 2020 \\
+{\bf Total Award Amount:} \$42,000 (Travel funds only) \\
+{\bf Duration:} September 1, 2017--August 31, 2022 \\
 {\bf Person-Months Per Year Committed to Project:} Calendar: 0,
@@
 \noindent
-{\bf Title}: The Role of Vorticity and Fuel Moisture on the Near-Field
-Plume Structure and Ember Dynamics \\
-{\bf Source}: Department of Defense, Strategic Environmental Research
-and Development Program \\
-{\bf Total Award Amount:} \$2,235,917 \\
-{\bf Duration:} May 2020--January 2024 (This is a collaborative grant
-that supports 7 PIs from 4 institutions) \\
+{\bf Title}:  A Comprehensive Experimental And Computational Fluid Dynamics Analysis Of Coning In Non-Newtonian Tailings During Extraction From Tailings Ponds \\
+{\bf Source}:  Institute for Oil Sands Innovation\\
+{\bf Total Award Amount:} \$171,842 \\
+{\bf Duration:}  January 1, 2020--January 1, 2022\\
 {\bf Person-Months Per Year Committed to Project:} Calendar: 0,
-Academic: 0, Summer: 1 \\
+Academic: 0, Summer: 0.5 \\
 
-\vspace{-17pt}
+%\vspace{-17pt}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-11-20 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 In particular, we view the slow, accumulated effects of erosion and dissolution as instrumental in altering porous-medium properties.
-First, by deteriorating solid material, erosion alters the size distribution of grains, enabling smaller grains to be sieved through networks of larger ones.
-A second and more subtle way that erosion can alter medium properties is by changing the {\em shape} distribution of grains.
+First, by deteriorating solid material, erosion alters the size distribution of porous-medium constituents, enabling smaller fragments to be sieved through networks of larger ones.
+A second and more subtle way that erosion can alter medium properties is by changing the {\em shape} distribution of fragments or grains.
 For instance, erosion can carve grains  into slender shapes aligned primarily in the direction of the dominant flow, thereby creating {\em anisotropic} characteristics.
@@
 
-{\bf An ultimate goal of this proposal is to simulate $\boldsymbol{\mathcal{O}(10^2-10^3)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with high-order accuracy and the computational efficiency required to run large ensembles for statistical analysis.} A major step towards this goal is illustrated in Fig.~\ref{80circ8vel}, which features high-fidelity erosion simulations of an initial configuration of 80 bodies of high volume fraction $50 \%$.
-Color indicates the velocity magnitude, which highlights the spontaneous formation of channels during the erosion process.
-These channels arise from small variations in the initial condition.
-Once formed, the larger channels transmit more flow which reinforces their growth.
-The process of channel formation can dramatically alter medium properties and create high levels of anisotropy, which directly impacts dispersion of transported quantities such as contaminants.
+{\bf An ultimate goal of this proposal is to simulate $\boldsymbol{\mathcal{O}(10^2-10^3)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with high-order accuracy and the computational efficiency required to run large ensembles for statistical analysis.}
+This topic of the dynamic erosion of a porous medium is one that has been receiving significant recent interest.
+Laboratory experiments on erosion of colloidal systems are currently being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
+These experiments are closely related to our proposed computational study, thus offering a great opportunity for comparison.
 
@@
 
-In addition to the work of the PIs, dynamic erosion of a porous media is a highly active subject as laboratory experiments on erosion of colloidal systems are currently being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}.
-These experiments are closely related to our proposed computational study, thus offering a great opportunity for comparison.
-Furthermore, {\bf we propose performing a set of experiments conducted at the nearby Geophysical Fluid Dynamics Institute (see Section~\ref{sec:experiments}), which would help to guide, calibrate, and validate the computations (see letter of collaboration).}
+A major step towards the goal of developing high-fidelity simulations of dynamic porous-medium erosion is illustrated in Fig.~\ref{80circ8vel}.
+This figure shows simulated erosion of an initial configuration of 80 bodies of high volume fraction $50 \%$.
+Color indicates the velocity magnitude, which highlights the spontaneous formation of channels during the erosion process.
+These channels arise from small variations in the initial condition.
+Once formed, the larger channels transmit more flow which reinforces their growth.
+The process of channel formation can dramatically alter medium properties and create high levels of anisotropy, which directly impacts dispersion of transported quantities such as contaminants.
 
@@
 These parameterized models could then be combined with well-developed multi-phase models \cite{breward2003multiphase, cogan2010multiphase, Imma2019, eastham2019multiphase} to quantitatively describe and predict sinkhole collapse.
-\todo[inline]{The last paragraph of this sections seems out of place.  Maybe it just needs to be reversed with the one before it?}
+Furthermore, we propose performing a set of experiments conducted at GFDI that would help to guide, calibrate, and validate the computations; See Section~\ref{sec:experiments} and the letter of collaboration for further details.
+
+\todo[inline]{Okay, I did some rearranging. See if you like it better.}
+
 %----------------------------------------------------------------------%
@@
 Large ensembles of the high-fidelity simulations will inform the coarse-grained models to be developed in the later stages of the proposed work.
+
+\item The coarse-grained models will harness recent advances in deep neural networks \cite{ling2016reynolds, kutz2017deep, ling2016machine, pelt2018mixed} to parameterize the effects of mechanical and chemical erosion within a multiphase\cite{breward2003multiphase, cogan2010multiphase, Imma2019, eastham2019multiphase}, or similar macroscopic, framework.
 

### 2019-11-21 docs/proposals/NSF/ProjDesc/ProjDesc.tex
checked off Nick's comments
NM

@@
 \item Erosion of solid material due to fluid-mechanical stresses or chemical dissolution.
-\item Transport of grains due to intervening fluid flow and due to sedimentation.
+\item Transport of fragments and grains due to intervening fluid flow and due to sedimentation.
 \item Compaction of the medium due to overlying loads.
@@
 First, by deteriorating solid material, erosion alters the size distribution of porous-medium constituents, enabling smaller fragments to be sieved through networks of larger ones.
-A second and more subtle way that erosion can alter medium properties is by changing the {\em shape} distribution of fragments or grains.
-For instance, erosion can carve grains  into slender shapes aligned primarily in the direction of the dominant flow, thereby creating {\em anisotropic} characteristics.
+A second and more subtle way that erosion can alter medium properties is by changing the {\em shape} distribution of individual fragments or particles.
+For instance, erosion can carve particles into slender shapes aligned primarily in the direction of the dominant flow, thereby creating {\em anisotropic} characteristics.
 Likewise, chemical dissolution can carve well-defined conduit paths in karst networks which strongly alter transport properties~\cite{szymczak2009wormhole}.
@@
 
-\item The Stokes limit introduces {\em longer} range effects than the inertial limit does, thus coupling the shape evolution of {\em all} grains and conduits to a higher degree.
+\item The Stokes limit introduces {\em longer} range effects than the inertial limit does, thus coupling the shape evolution of {\em all} fragments, grains, and conduits to a higher degree.
 
@@
 
-\todo[inline]{Okay, I did some rearranging. See if you like it better.}
-
 %----------------------------------------------------------------------%
@@
 We first outline the theoretical foundation that will be used in later sections of the proposal.
-At the finest scale, the fluid flow intervening between individual grains of a porous medium is governed by the incompressible Stokes equations
+At the finest scale, the fluid flow intervening between individual constituents of a porous medium is governed by the incompressible Stokes equations
 \begin{align}
@@
 \end{align}
-\begin{wrapfigure}[22]{l}{0.4\textwidth}
+\begin{wrapfigure}[23]{l}{0.4\textwidth}
   \includegraphics[width=0.4\textwidth]{figs/100b_second_moment_long_ref}

### 2019-11-21 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

@@
 
-Equation \eqref{eqn:StokesEq}, and its equivalent integral formulation, are microscopic descriptions required to model the shape evolution of individual grains due to fine-scale erosive effects, either mechanical or chemical.
+Equation \eqref{eqn:StokesEq}, and its equivalent integral formulation, are microscopic descriptions required to model the shape evolution of individual fragments and grains due to fine-scale erosive effects, either mechanical or chemical.
 This microscopic description, however, becomes impractical when attempting to model seepage in very large porous systems where the microscopic geometry can be exceedingly complex.
@@
 
-More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks \cite{ling2016reynolds, kutz2017deep, ling2016machine, pelt2018mixed} to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.
-The output of the high-fidelity simulations of the grain configuration can be transformed into essentially an image format, permitting use of cutting-edge advances in deep neural-networks for image analysis~\cite{pelt2018mixed}.
+{\bf More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks \cite{ling2016reynolds, kutz2017deep, ling2016machine, pelt2018mixed} to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.}  The output of the high-fidelity simulations of the grain configuration can be transformed into essentially an image format, permitting use of cutting-edge advances in deep neural-networks for image analysis~\cite{pelt2018mixed}.
 Some important advantages of referenced work are the use of dilated convolutions in a deeply connected network, which first mixes scales and second reduces the number of super-parameters present, thus largely mitigating the risk of overfitting data.
@@
 Once the essential features are learned, they will be incorporated into reduced-order models that harness the multiphase framework.
-These reduced models will enable more efficient and larger scale coarse-grained simulations of dynamic erosion.
+These reduced models will enable more efficient and larger scale simulations of dynamic erosion than are feasible with the high-fidelity boundary-integral simulations.
 
@@
 \label{sec:experiments}
-As mentioned previously, researchers at FSU's Geophysical Fluid Dynamics
-Institute (GFDI) have investigated the mechanisms behind sinkhole
-formation with a series of scaled-down laboratory
-experiments~\cite{tao2014experimental}. First, already existing data
-from these experiments offers a testbed for comparison against our newly
-developed simulations. Furthermore, {\bf we propose to run a set of new
-experiments at the facilities offered by GFDI}, spearheaded by an undergraduate student in close collaboration with the graduate students, PIs, and an experimentalist at GFDI.
-These new experiments will more deeply probe the mechanisms underlying sinkhole formation with the special design goal of comparison against the numerical simulations.
-These experiments will be used to calibrate and validate our computations.
-\todo[inline]{We have more room at the end of the document. This
-section seems a bit brief and could maybe be expanded.}
+
+	As mentioned previously, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments~\cite{tao2014experimental}.
+We plan to make use of the knowledge gained from these past experiments, as well as the facilities and equipment already in place, to inform and validate our computational program.
+
+	First, already existing data from these experiments offers a wonderful testbed for comparison against the newly developed simulations.
+This data provides information about the physical conditions and broad parameter regimes required for sinkhole collapse.
+Second, and more importantly, we propose to conduct a new campaign of laboratory experiments at the GFDI facilities which will be spearheaded by PI Moore and an undergraduate student funded by the project.
+These experiments will make use of much of the same infrastructure, as well as technical staff present at GFDI with working knowledge of the specific equipment.
+The experiments will be conducted in close cooperation with the graduate students to ensure constant feedback between advances in the computational program and experiments.
+
+	The proposed experiments involve two parallel lines of inquiry that we plan to merge in later stages of the project.
+The first line of inquiry involves the dynamic erosion of a porous material by either mechanical or chemical action.
+In this context, the porous medium will be represented by fragments of either erodible material, such as bentonite clay, or dissolve material, such as sucrose solids.
+We will perform controlled experiments to examine how important macroscopic properties, such as permeability, mechanical strength, and anisotropy, evolve dynamically as the constituents disintegrate.
+These experiments will make use of Darcy-column containers that allow precise control of flux through the medium and precise hydraulic head measurements to infer permeability.
+These Darcy columns have already been fabricated and are available for use at GFDI.
+
+	The second line of inquiry will extend the sinkhole experiments that were previously conducted at GFDI, with the specific aim of informing and validating our numerical simulations.
+These experiments will build on the significant infrastructure already in place from the previous sinkhole experiments, with the express consent of our collaborator Prof.
+Ming Ye (see collaboration letter).
+This infrastructure permits precise control of the hydraulic head in a confined and unconfined aquifers -- it is the difference in the heads creates conditions favorable for sinkhole formation.
+The new experiments will use both natural (sand) and artificial (glass beads) granular materials.
+The advantage of the latter is to achieve a mono-disperse medium for direct comparison against numerical simulations.
+Time permitting, we hope to merge the two lines of inquiry to examine the influence of material erodibility on gravitational reconfiguration and specifically sinkhole formation.
+The materials available for laboratory experiments, in particular the relatively rapid rates of degradation that can be achieved, would enable us to study phenomenon that occur on much longer timescales in the natural world.
+
+\todo[inline]{Like it?}
 

### 2019-11-21 docs/proposals/NSF/ProjDesc/ProjDesc.tex
trimmed up a bit

@@
 By using a Barycentric quadrature rule, we stably simulate erosion with only 512 points on the eroding body which corresponds to an arclength spacing 12 times larger than the original separation distance; to achieve a comparable accuracy with the spectral trapezoid rule, 60 times as many discretization points would be required.
-In Fig.~\ref{fig:porelets}(a), different shades of grey correspond to the configuration of the eroding grain at five equally spaced time steps.
+In Fig.~\ref{fig:porelets}, different shades of grey correspond to the configuration of the eroding grain at five equally spaced time steps.
 At three of the time steps, we plot the velocity between the grain and the solid wall (black line).
@@
 After performing a thorough analysis of the pore size growth in this simple configuration, we will develop a more complete model for pore networks that are characteristic of porous media.
+
+\begin{wrapfigure}[13]{l}{0.4\textwidth}
+  \includegraphics[width=0.4\textwidth]{figs/porelets_geom}
+  \caption{\label{fig:porelets} \em An eroding body at five equally time steps.
+At the three intermediate time steps, the Stokesian velocity field in the bulk, which is nearly parabolic, is included.}
+\end{wrapfigure}
 
@@
 
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}[b]{0.47\textwidth}
-  \begin{center}
-  \includegraphics[height=0.55\textwidth]{figs/porelets_geom}
-  \end{center}
-  \caption{}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.47\textwidth}
-  \begin{center}
-  \includegraphics[height=0.55\textwidth]{figs/porelets_size}
-  \end{center}
-  \caption{}
-  \end{subfigure}
-  \caption{\label{fig:porelets} \em (a) An eroding body at five equally time steps.
+%\begin{figure}[htp]
+%  \centering
+%  \begin{subfigure}[b]{0.47\textwidth}
+%  \begin{center}
+%  \includegraphics[height=0.55\textwidth]{figs/porelets_geom}
+%  \end{center}
+%  \caption{}
+%  \end{subfigure}
+%  \begin{subfigure}[b]{0.47\textwidth}
+%  \begin{center}
+%  \includegraphics[height=0.55\textwidth]{figs/porelets_size}
+%  \end{center}
+%  \caption{}
+%  \end{subfigure}
+%  \caption{\label{fig:porelets} \em (a) An eroding body at five equally time steps.
 At the three intermediate time steps, the Stokesian velocity field in the bulk, which is nearly parabolic, is included.
@@
 As the channel opens, the flow rate increases to maintain a constant pressure drop.}
-\end{figure}
+%\end{figure}
 
@@
 These preliminary simulations are based on a hybrid continuum-discrete model for the permeability field and grain particle field respectively.
-They utilize the homogenized description of the flow field in~\eqref{DarcyEq} and incorporate the physical effects of:
-\begin{itemize}[noitemsep]
-\item Transport of grains due to seepage force from the surrounding fluid flow.
-\item Gravitational sedimentation of grains.
-\item Feedback of grain-distribution onto permeability field.
-\item Contact and cohesive forces between grains.
-\end{itemize}
-Preliminary investigation suggests that this last mechanism of cohesion is essential to model sinkhole collapse in the system.
+They utilize the homogenized description of the flow field in~\eqref{DarcyEq} and incorporate the seepage and gravitational forces on the grains, feedback between the grain-distribution and the permeability field, and contact and cohesive forces between the grains.
+Preliminary results suggest that cohesion is essential to model sinkhole collapse.
+
+%\begin{itemize}[noitemsep]
+%\item Transport of grains due to seepage force from the surrounding fluid flow.
+%\item Gravitational sedimentation of grains.
+%\item Feedback of grain-distribution onto permeability field.
+%\item Contact and cohesive forces between grains.
+%\end{itemize}
+%Preliminary investigation suggests that this last mechanism of cohesion is essential to model sinkhole collapse in the system.
 
@@
 
-	As mentioned previously, researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have investigated the mechanisms behind sinkhole formation with a series of scaled-down laboratory experiments~\cite{tao2014experimental}.
-We plan to make use of the knowledge gained from these past experiments, as well as the facilities and equipment already in place, to inform and validate our computational program.
-
-	First, already existing data from these experiments offers a wonderful testbed for comparison against the newly developed simulations.
-This data provides information about the physical conditions and broad parameter regimes required for sinkhole collapse.
-Second, and more importantly, we propose to conduct a new campaign of laboratory experiments at the GFDI facilities which will be spearheaded by PI Moore and an undergraduate student funded by the project.
-These experiments will make use of much of the same infrastructure, as well as technical staff present at GFDI with working knowledge of the specific equipment.
+Researchers at FSU's Geophysical Fluid Dynamics Institute (GFDI) have
+investigated the mechanisms behind sinkhole formation with a series of
+scaled-down laboratory experiments~\cite{tao2014experimental}. We will
+make use of the knowledge gained from these past experiments, and the
+facilities and equipment already in place, to inform and validate our
+computational program. In particular, existing data from these
+experiments offers a first-rate testbed for comparison against the newly
+developed simulation, and also provides information about the physical
+conditions and broad parameter regimes required for sinkhole collapse.
+Furthermore, and more importantly, {\bf we propose to conduct a new campaign of laboratory experiments at the GFDI facilities that will be spearheaded by PI Moore and an undergraduate student funded by the project.} The experiments will use much of the same infrastructure, as well as GFDI technical staff who have working knowledge of the specific equipment.
 The experiments will be conducted in close cooperation with the graduate students to ensure constant feedback between advances in the computational program and experiments.
 
-	The proposed experiments involve two parallel lines of inquiry that we plan to merge in later stages of the project.
-The first line of inquiry involves the dynamic erosion of a porous material by either mechanical or chemical action.
-In this context, the porous medium will be represented by fragments of either erodible material, such as bentonite clay, or dissolve material, such as sucrose solids.
+The proposed experiments involve two parallel lines of inquiry that will
+be merged in later stages of the project. The first line will
+investigate dynamic erosion of a porous material by mechanical or
+chemical action.
+The porous medium will be represented by fragments of either erodible material, such as bentonite clay, or dissolve material, such as sucrose solids.
 We will perform controlled experiments to examine how important macroscopic properties, such as permeability, mechanical strength, and anisotropy, evolve dynamically as the constituents disintegrate.
@@
 
-	The second line of inquiry will extend the sinkhole experiments that were previously conducted at GFDI, with the specific aim of informing and validating our numerical simulations.
-These experiments will build on the significant infrastructure already in place from the previous sinkhole experiments, with the express consent of our collaborator Prof.
-Ming Ye (see collaboration letter).
-This infrastructure permits precise control of the hydraulic head in a confined and unconfined aquifers -- it is the difference in the heads creates conditions favorable for sinkhole formation.
+The second line of inquiry will extend the previously conducted sinkhole experiments of our collaborator Prof.~Ming Ye (see letter of collaboration), with the specific aim of informing and validating our numerical simulations.
+This infrastructure permits precise control of the hydraulic head in confined and unconfined aquifers---it is the difference in the heads that creates conditions favorable for sinkhole formation.
 The new experiments will use both natural (sand) and artificial (glass beads) granular materials.
 The advantage of the latter is to achieve a mono-disperse medium for direct comparison against numerical simulations.
-Time permitting, we hope to merge the two lines of inquiry to examine the influence of material erodibility on gravitational reconfiguration and specifically sinkhole formation.
-The materials available for laboratory experiments, in particular the relatively rapid rates of degradation that can be achieved, would enable us to study phenomenon that occur on much longer timescales in the natural world.
-
-\todo[inline]{Like it?}
+Time permitting, we will merge the two lines of inquiry to examine the influence of material erodibility on gravitational reconfiguration and specifically sinkhole formation.
+The materials available for laboratory experiments, in particular the relatively rapid rates of degradation that can be achieved, will enable us to study phenomenon that occur on much longer timescales in the natural world.
 
@@
 \subsection{Undergraduate Research}
-Regarding undergraduate research, the ideas in this proposal represent a rich and fascinating topic for undergraduate students, while also being approachable by the skills acquired at that stage.
-In particular, we aim to recruit at least one undergraduate student to perform laboratory experiments at the Geophysical Fluid Dynamics Institute (GFDI).
+The proposed research represents a rich and fascinating topic for undergraduate students, while also being approachable by the skills acquired at that stage.
+We aim to recruit at least one undergraduate student to perform laboratory experiments at GFDI.
 As mentioned above, GFDI offers state-of-the-art laboratory facilities, with an already-functioning sinkhole experiment.
-The student will perform controlled experiments using natural and artificial porous media (e.g.~sand and micro-glass beads respectively) to precisely characterize the parameter regime leading to gravitational collapse.
+The student will perform controlled experiments using natural and artificial porous media to precisely characterize the parameter regime leading to gravitational collapse.
 Parallel experiments will be conducted with erodible (bentonite clay) or dissolvable (sucrose solids) fragmented materials to represent a {\em dynamically} changing porous medium.
-These experiments will be used to guide, calibrate, and validate the computational advances.
-These undergraduate students will work closely with the graduate students to ensure that theory and experiments advance in close cooperation, with constant feedback between the two.
+These experiments will guide, calibrate, and validate the computational advances.
+The undergraduate students will work closely with the PIs and the graduate students to ensure that theory and experiments advance in close cooperation, with constant feedback between the two.
 
-PI Moore already has experience successfully training undergraduate students in combined laboratory and theoretical work.
-A recent example is undergraduate student Tyler Bolles who completed an honors thesis with PI Moore at FSU on laboratory and theory of water waves.
-This work resulted in one {\em peer-reviewed} publication already~\cite{Bolles2019}, with a second to be submitted soon.
+PI Moore has experience successfully training undergraduate students in combined laboratory and theoretical work.
+A recent example is Tyler Bolles who completed an undergraduate honors thesis with PI Moore at FSU on laboratory and theory of water waves.
+This work resulted in one {\em peer-reviewed} publication~\cite{Bolles2019}, and a second to be submitted soon.
 PI Quaife successfully trained an undergraduate student, Miles Currie, in a statistical analysis of flows related to prescribed fire dynamics.
-This work resulted in a peer-reviewed publication~\cite{cur-spe-hie-obr-goo-qua2018}.
+This work resulted in a {\em peer-reviewed} publication~\cite{cur-spe-hie-obr-goo-qua2018}.
 
 At FSU, there are at least two excellent avenues to attract interested undergraduate students: the Undergraduate Research Opportunity Program (UROP) and the IDEA grant.
-The UROP is a program to engage undergraduates in academic research, while the IDEA grant is a competitive program, requiring more advanced students to write a proposal in which they identify a research advisor.
+The UROP engages undergraduates in academic research, while the IDEA grant is a competitive program, requiring more advanced students to identify a research advisor and write an internal proposal.
 Both programs make special efforts to recruit from underrepresented groups.
@@
 In particular, PI Moore's research was the focus of an educational video created by {\bf CPALMS}, which is the State of Florida's official source for standards information and course descriptions for K--12 education.
-The video, which features an interview and animations of research, is used to reinforce concepts from mathematics courses (grade levels 7--12), and to encourage students to consider a career in the STEM fields~\cite{CPALMS}.
-Additionally, these videos are frequently used for the continuing education of K--12 {\em teachers}, providing them a broader perspective of mathematics that could be integrated into their teaching.
-
-Plans for future outreach include continued collaboration with CPALMS to create a series of educational videos for both students and teachers, as well as planned activities at {\bf Math Fun Day}, which is an annual event held by the FSU Department of Mathematics to engage K-12 students in the region.
-PI Moore has led activities at Math Fun Day in prior years and, related to the current proposal, plans to deliver lectures and demos on porous-media flows, erosion, and sinkhole collapse.
+The video features an interview and animations of research, and is used to reinforce mathematics concepts (grade levels 7--12), encourage students to consider a career in the STEM fields~\cite{CPALMS}, and provides K--12 {\em teachers} with a broader perspective of mathematics that can be integrated into their teaching.
+Plans for future outreach include continued collaboration with CPALMS to create a series of educational videos.
+In addition, activities at {\bf Math Fun Day}, an annual event held by the FSU Department of Mathematics to engage regional K-12 students, will be planned.
+PI Moore has previously led activities at Math Fun Day and, related to the current proposal, will deliver lectures and demos on porous-media flows, erosion, and sinkhole collapse.
 Laboratory materials for the demo are available at GFDI.
 
-FSU also provides an opportunity to expose high school students to university-level research through the {\bf Young Scholars Program (YSP)}.
-The YSP is a six week experience that brings Florida's brightest grade 11 students to FSU where they are exposed to university-level lectures and work with FSU faculty on a research project.
-PI Quaife participated in this program in Summer 2016.
-The PIs will propose research projects that are accessible to high school students throughout the duration of the proposed research.
-In addition to high school students receiving a university experience, the PhD students will be tasked with much of the day-to-day interaction with the high school students.
-This offers an excellent opportunity for the PhD students to develop leadership and mentorship skills.
+Another opportunity to expose high school students to university-level research is FSU's {\bf Young Scholars Program (YSP)}.
+The YSP is a six week experience for Florida's brightest grade 11 students where they are exposed to university-level lectures and work with FSU faculty on a research project.
+PI Quaife participated in the YSP in 2016.
+The PIs will propose accessible projects throughout the duration of the proposed research.
+In addition to high school students receiving a university experience, the PhD students will be tasked with much of the day-to-day interaction, and this offers an excellent opportunity for the PhD students to develop leadership and mentorship skills.
 

### 2019-11-23 docs/proposals/NSF/ProjDesc/ProjDesc.tex
went through entire proposal

@@
 
-An understanding of these filtration and contamination processes relies on the complex phenomenon of transport and dispersion in porous media \cite{scheidegger1961general, neuman1987stochastic, delgado2007longitudinal, zhang2016backward}.
-Further, the action of continually flowing groundwater can alter medium properties through erosive, transportive, and other processes.
-Thus, it becomes necessary to understand transport through complex media whose properties change {\em dynamically} in response to the intervening fluid flow.
-These effects are most noticeable during rapid events, like the gravitational collapse of a sinkhole~\cite{sandhu2018fate}, during which medium properties can change dramatically over short timescales.
-Though less obvious, the accumulation of slower process, such as mechanical or chemical erosion, can also substantially alter medium properties \cite{szymczak2009wormhole, ellis2013dissolution}.
+An understanding of these filtration and contamination processes relies
+on the complex phenomenon of transport and dispersion in porous media
+\cite{scheidegger1961general, neuman1987stochastic,
+delgado2007longitudinal, zhang2016backward}. Further, the action of
+continually flowing groundwater can alter medium properties through
+erosive, transportive, and other processes. Thus, it becomes necessary
+to understand transport through complex media whose properties change
+{\em dynamically} in response to the intervening fluid flow. These
+effects are most noticeable during rapid events, like the gravitational
+collapse of a sinkhole~\cite{sandhu2018fate}, during which medium
+properties can change dramatically over short timescales. Though less
+obvious, the accumulation of slower processes, such as mechanical or chemical erosion, can also substantially alter medium properties \cite{szymczak2009wormhole, ellis2013dissolution}.
 
@@
 \item Erosion of solid material due to fluid-mechanical stresses or chemical dissolution.
-\item Transport of fragments and grains due to intervening fluid flow and due to sedimentation.
+\item Transport of fragments and grains due to intervening fluid flow and sedimentation.
 \item Compaction of the medium due to overlying loads.
@@
 \caption{\label{collage} \em Geophysical examples of chemical and mechanical erosion.
-Top from left: Diagram of a coupled karst-soil system with conduit formation \cite{watson2019sinkholes}; Limestone pavement in Dent de Crolles, France; Nohoch Ch’en Sinkhole in Belize.
-Bottom: examples of soil erosion.
+Top from left: Diagram of a coupled karst-soil system with conduit formation \cite{watson2019sinkholes}; Limestone pavement in Dent de Crolles, France; Nohoch Che'en Sinkhole in Belize.
+Bottom: Examples of soil erosion.
 The bottom right shows the microscopic soil texture, exhibiting polydispersity and anisotropy.}
@@
 
-A major step towards the goal of developing high-fidelity simulations of dynamic porous-medium erosion is illustrated in Fig.~\ref{80circ8vel}.
-This figure shows simulated erosion of an initial configuration of 80 bodies of high volume fraction $50 \%$.
-Color indicates the velocity magnitude, which highlights the spontaneous formation of channels during the erosion process.
+A major step towards the goal of developing high-fidelity simulations of
+dynamic porous-medium erosion is illustrated in Fig.~\ref{80circ8vel}.
+This figure shows simulated erosion of 80 bodies with an initial high
+volume fraction of 50\%.
+The color indicates the velocity magnitude, which highlights the spontaneous formation of channels during the erosion process.
 These channels arise from small variations in the initial condition.
@@
 %\end{equation}
-where $\uu$ is the velocity field, $p$ the pressure field, $\mu$ the fluid viscosity, and $\Omega$ the fluid domain.
-Linear elliptic PDEs, such as the Stokes equations, can be reformulated as a boundary integral equation (BIE).
+where $\uu$ is the velocity field, $p$ is the pressure field, $\mu$ is the fluid viscosity, and $\Omega$ is the fluid domain.
+Linear homogeneous elliptic PDEs, such as the Stokes equations, can be reformulated as a boundary integral equation (BIE).
 BIEs have several numerical advantages including a dimension reduction, automatic mass conservation, and high-order accuracy.
@@
 \end{align}
-where $\ff$ is a Dirichlet boundary condition, $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the outward unit normal of $\bd\Omega$.
+where $\ff$ is the Dirichlet boundary condition, $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the outward unit normal of $\bd\Omega$.
 Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, quantities such as the velocity, pressure, vorticity, and deformation tensor can be computed in the fluid bulk.
@@
 
-Equation \eqref{eqn:StokesEq}, and its equivalent integral formulation, are microscopic descriptions required to model the shape evolution of individual fragments and grains due to fine-scale erosive effects, either mechanical or chemical.
+Equation~\eqref{eqn:StokesEq}, and its equivalent BIE formulation, are microscopic descriptions required to model the shape evolution of individual fragments and grains due to fine-scale erosive effects, either mechanical or chemical.
 This microscopic description, however, becomes impractical when attempting to model seepage in very large porous systems where the microscopic geometry can be exceedingly complex.
@@
 Both the conductivity and permeability are in general tensors, and they reduce to scalars in the case of an isotropic medium.
-Note that the Darcy velocity is related to the tracer velocity through $\qq = \theta_f \uu$, where $\theta_f$ is porosity (i.e.~fluid volume fraction).
+Note that the Darcy velocity is related to the tracer velocity through $\qq = \theta_f \uu$, where $\theta_f$ is the porosity (i.e.~fluid volume fraction).
 In the case of an isotropic medium, the Kozeny-Carman equation is often used to relate permeability to volume fraction~\cite{bear2013dynamics}
@@
 Currently, the relationship between these scales is poorly understood.
-The proposed high-fidelity, efficient computational methods will enable a deeper understanding of these processes, which is the first step towards developing effective strategies for managing water resources and mitigating catastrophic events such as contamination or structural collapse.
-For example, the insights gained here could potentially help identify locations in natural aquifers vulnerable to contamination and/or collapse.
+The proposed high-fidelity and efficient computational methods will enable a deeper understanding of these processes, which is the first step towards developing effective strategies for managing water resources and mitigating catastrophic events such as contamination or structural collapse.
+For example, the insights gained here will potentially help identify locations in natural aquifers vulnerable to contamination, collapse, or both.
 
 In addition to these societal impacts, the proposed work will spur the training of mathematicians and computational scientists in fundamentally cross-disciplinary research of great societal importance.
-Further, the PIs will engage in educational and outreach activities to impact future generations of mathematical scientists, with particular focus on women and underrepresented minorities (URM).
+Further, the PIs will engage in educational and outreach activities to impact future generations of mathematical scientists, with particular focus on women and underrepresented minorities.
 Both PIs are already actively involved in graduate and undergraduate research, as well as outreach to K-12 students.
@@
 \paragraph{Intellectual Merit:} The proposed research introduces a host of new computational challenges and opportunities.
-First the range of scales is vast: spatial scales range from microscopic granular constituents to large geological aquifers; timescales range from that of a sudden sinkhole collapse to years required mechanical and chemical erosion.
+First the range of scales is vast: spatial scales range from microscopic granular constituents to large geological aquifers; timescales range from that of a sudden sinkhole collapse to years required for certain mechanical and chemical erosion processes.
 The systems are inherently multicomponent, with coupling between the fluid and solid phases.
@@
 To tackle these challenges, the PIs will combine cutting-edge computational tools with reduced-order modeling.
-Mixed-scale, deep neural networks will be used to learn from the data generated by high-fidelity numerical simulations to parameterize coarse-grained models based on the multiphase framework.
+Mixed-scale, deep neural networks will be used to learn from the data generated by high-fidelity numerical simulations and to parameterize coarse-grained models based on the multiphase framework.
 Additionally, controlled laboratory experiments will be used to guide and verify theory developed herein.
@@
   \item The proposed research is interdisciplinary by nature, with immediate applications in the fields of geophysics and environmental sciences.
-The PIs already have experience collaborating with scientists from other disciplines \cite{Caves2018, eastham2019multiphase, Bolles2019, cur-spe-hie-obr-goo-qua2018} through FSU's Geophysical Fluid Dynamics Institute, an interdisciplinary unit comprised of a diverse set of faculty from home departments in example Earth, Atmospheric, and Ocean Sciences, Geology, Physics, Civil Engineering, Environmental Engineering, Mechanical Engineering, Scientific Computing, Mathematics, and others.
+The PIs have experience collaborating with scientists from other disciplines \cite{Caves2018, eastham2019multiphase, Bolles2019, cur-spe-hie-obr-goo-qua2018} through FSU's Geophysical Fluid Dynamics Institute, an interdisciplinary unit comprised of a diverse set of faculty from home departments in example Earth, Atmospheric, and Ocean Sciences, Geology, Physics, Civil Engineering, Environmental Engineering, Mechanical Engineering, Scientific Computing, Mathematics, and others.
 
@@
 The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion in the Stokes flow regime~\cite{Quaife2018}, the regime relevant for the currently proposed groundwater applications.
-Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion~\cite{chi-moo-qua2019}.
+Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of densly packed porous-media configurations formed by erosion~\cite{chi-moo-qua2019}.
 
@@
 \begin{enumerate}[noitemsep,label=(\arabic*)]
-  \item Simulating chemical erosion, and transport, including sedimentation and compaction, of eroding bodies
+  \item Simulating mechanical and chemical erosion, as well as transport, including sedimentation and compaction, of eroding bodies.
 
@@
 
-  \item Simulating the transport of finite Peclet number concentrations in eroded porous geometries.
+  \item Simulating the transport of finite Peclet number concentrations in eroded porous medium.
 
@@
 
-The development of accurate and efficient numerical methods to solve the Stokes equations enables high-fidelity simulations of the erosion process.
-We will consider erosion induced by either fluid-mechanical forces or by chemical reaction, i.e.~dissolution.
+The development of accurate and efficient numerical methods to solve the Stokes equations enables high-fidelity simulations of erosion processes.
+We will consider erosion induced by either fluid-mechanical forces and by chemical reaction, i.e.~dissolution.
 In the former case, which we have already begun to investigate~\cite{Quaife2018}, erosion result from the shear stress $\tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss$, where $\nn$ and $\ss$ are the unit normal and tangent vectors on the surface respectively and $\uu$ is the velocity field as computed from the incompressible Stokes equations~\eqref{eqn:StokesEq}.
@@
 In the context of a porous media at low Reynolds-number flows, numerical methods have been developed by the PIs to simulate shear-induced erosion~\cite{Quaife2018, chi-moo-qua2019}.
-These simulations combine highly accurate boundary integral methods with stable interface evolution techniques.
-The boundary integral solver is accelerated by the fast multipole method~\cite{gre-rok1987, gre-gre-may1992} to achieve optimal $\mathcal{O}(N)$ complexity.
+These simulations combine highly accurate BIE methods with stable interface evolution techniques.
+The BIE solver is accelerated by the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} to achieve optimal $\mathcal{O}(N)$ complexity.
 Meanwhile, the so-called {\thL} method is used for interface evolution to prevent distortion and tangling of the interface meshes~\cite{hou1994removing, MoorePOF2013, Quaife2018}.
@@
 \includegraphics[width = 0.99 \textwidth]{./figs/80circ8vort.pdf}
-\caption{\label{80circ8vort} \em Simulation of 80 bodies eroding in Stokes flow under the action of shear stress.
+\caption{\label{80circ8vort} \em Simulation of 80 bodies mechanically eroding in Stokes flow.
 Flow is left to right.
@@
 Figs.~\ref{80circ8vel} and~\ref{80circ8vort} show preliminary results of 80 bodies, initially of random position and size, undergoing mechanical erosion in Stokes flow.
-This simulation extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed barycentric quadrature scheme~\cite{bar2014, bar-wu-vee2015, chi-moo-qua2019}, which enables more densely packed configurations.
+This simulation extends previously reported 50-body simulations to 80 bodies~\cite{Quaife2018} due to a recently developed Barycentric quadrature scheme~\cite{bar2014, bar-wu-vee2015, chi-moo-qua2019}, which enables more densely packed configurations.
 The color in Fig.~\ref{80circ8vort} represents the vorticity field surrounding the bodies.
@@
 Observe that erosion not only reduces the size of solid bodies, but also alters their shapes substantially.
-The bodies tend to become somewhat polygonal: corners develop connected by relatively flat faces.
+The bodies tend to become somewhat polygonal---corners develop connected by relatively flat faces.
 The number of faces does not appear to be easily predicted, but rather depends on the interaction with neighboring bodies as mediated by the Stokes flow.
 As erosion proceeds, relatively straight channels tend to develop between the bodies.
-Certain channels that are initially larger can transmit more flow, which promotes local erosion rates and further widens these selected channels.
+Certain channels that are initially larger transmit more flow, promoting local erosion rates and further widening these select channels.
 In this way, erosion creates a runaway process in which small differences in initial channel size become amplified.
-This channelization process is made even more apparent by viewing the velocity magnitude in Fig.~\ref{80circ8vel}.
+This channelization process is most evident by viewing the velocity magnitude in Fig.~\ref{80circ8vel}.
 
@@
 In the simulations, resistivity is calculated by measuring the total flux and the pressure upstream and downstream, then using Darcy's relation~\eqref{DarcyEq} to infer the horizontal permeability $k_x$.
-Naturally, as bodies erode, the resistivity they provide decreases in time.
-Note that, unlike the area plot, the vertical axis is logarithmic and so the straight line observed at early times indicates that the resistivity decreases exponentially.
+Naturally, as bodies erode, the resistivity they provide decreases.
+Note that, unlike the area plot, the vertical axis is logarithmic, so the straight line observed at early times indicates that the resistivity decreases exponentially.
 The much more modest decrease of area fraction is not sufficient to account for this exponential rate.
 Hence the reshaping process, in particular the formation of channels, plays a pivotal role in the medium's macroscopic resistivity to flow.
-
 Lastly, the right-most plot of Fig.~\ref{fig3} shows new, preliminary results on how medium anisotropy evolves during the reshaping process of erosion.
 Anisotropy is calculated as the ratio of vertical to horizontal resistivity, with the vertical resistivity computed by rotating the configuration of bodies by 90 degrees.
-This plot shows the anisotropy to initial increase with time.
-Thus, the initially isotropic state becomes erased as bodies streamline and form primarily horizontal channels.
+This plot shows that the anisotropy initially increase with time.
+Thus, the initial isotropy is erased as bodies streamline and form primarily horizontal channels.
 Remarkably, the medium reaches an anisotropy of over 10, meaning that erosion can lead to a configuration that resists flow 10 times more in the vertical direction than the horizontal direction.
@@
 Time is normalized by the vanishing time $t_f$.
-Middle: The resistivity of the porous matrix decrease much more rapidly than area fraction, indicating the reshaping process to be essential.
+Middle: The resistivity of the porous matrix decrease much more rapidly than the area fraction, indicating the reshaping process to be essential.
 Right: The anisotropy (ratio of vertical to horizontal resistivity) as it varies in time.
-Erosion can create a highly anisotropic medium.} \end{center}
+Erosion can create a highly anisotropic medium.}
+\end{center}
 \end{figure}
@@
 
-{\bf An immediate goal of the proposed work is to extend the range of physical effects captured in these simulations.} A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
-To address this problem, we have very recently extended a Barycentric quadrature method~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing~\cite{chi-moo-qua2019}.
-The quadrature method is a non-intrusive modification of the trapezoid rule and results in an error bound that is independent of the grain configuration.
-However, the current implementation does not yet fully exploit FMM acceleration.
-The computational challenge is to develop FMM expansions for the velocity, vorticity, and deformation-tensor layer potentials.
+{\bf An immediate goal of the proposed work is to extend the range of
+physical effects captured in these simulations.} A particular challenge
+of a BIE formulation is developing quadrature for nearly-singular
+integrands that arise when bodies are close. To address this problem, we
+have very recently extended a Barycentric quadrature
+method~\cite{bar2014, bar-wu-vee2015} and have successfully simulated
+erosion with grains that are initially separated by 1\% of an arclength
+spacing~\cite{chi-moo-qua2019}. The quadrature method is a non-intrusive
+modification of the trapezoid rule and results in an error bound that is
+independent of the grain configuration. However, the current
+implementation does not yet fully exploit FMM acceleration. The
+computational challenge is to develop FMM expansions for the velocity,
+vorticity, pressure, and deformation-tensor layer potentials.
 Since these layer potentials each have distinct kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and their HPC implementations (for example, see \url{http://pvfmm.org}).
@@
 
-Next, we plan to extend the simulation framework to handle chemical dissolution of solid bodies via physical laws~\eqref{Ceq}--\eqref{DissVn}.
-For this goal, much of the computational infrastructure, such as the boundary-integral solver for the Stokes equations and the {\thL} method for interface evolution, is already in place.
+{\bf Next, we will extend the simulation framework to handle chemical dissolution of solid bodies via physical laws~\eqref{Ceq}--\eqref{DissVn}.} For this goal, much of the computational infrastructure, such as a BIE solver for the Stokes equations and the {\thL} method for interface evolution, is already in place.
 The BIE Stokes solver, however, has not yet been coupled to the advection-diffusion equations~\eqref{Ceq} and interface law~\eqref{DissVn} required for dissolution.
-We proposed to solve the advection-diffusion equation~\eqref{Ceq} by first using Strang splitting~\cite{str1968} to decompose the system into individual PDEs for linear advection and diffusion.
-The advection equation will be handled with a semi-Lagrangian method~\cite{rob1981} so that it can be solved on an Eulerian grid without a restrictive CFL condition.
+We propose to solve the advection-diffusion equation~\eqref{Ceq} by first using Strang splitting~\cite{str1968} to decompose the equation into two PDEs---one involving only linear advection, and the other only diffusion.
+The advection equation will be solved with a semi-Lagrangian method~\cite{rob1981} so that it can be solved on an Eulerian grid without a restrictive CFL condition.
 PI Quaife has experience using semi-Lagrangian methods in the closely related context of complex viscous flow~\cite{kab-qua-bir2017}.
@@
 A particular challenge of the latter method is extending functions from the complex geometry into a regular geometry, such as a square, so that a high-order volume integral or Fourier method can be applied~\cite{fry-kro-tor2019, fry-leh-tor2019}.
-Alternatively, we propose to use a Laplace Transform, $C(\xx,s) = \mathcal{L}[c](\xx,t)$, which satisfies
-\begin{wrapfigure}[19]{r}{0.3\textwidth}
-  \includegraphics[width=0.3\textwidth]{figs/100b_t100tracer}
-  \caption{\label{fig:100tracers} \em Streamlines visualized with 200 tracers passing through an eroded geometry.
-The tracers are initialized at the left end of the channel and the flow is from left to right.} \end{wrapfigure}
+Alternatively, we propose to use the Laplace Transform, $C(\xx,s) = \mathcal{L}[c](\xx,t)$, which satisfies
 \begin{align}
-  sC(\xx,s) - \frac{1}{\Pe}\Delta C(\xx,s) = c_0(\xx), 
+  sC(\xx,s) - D\Delta C(\xx,s) = c_0(\xx), 
     \quad \xx \in \Omega, \: s \in \mathbb{C},
@@
 \end{align}
-where $c_0(\xx)$ is the initial concentration and $\Pe$ is the dimensionless Peclet number.
-This PDE will be solved with high-order accuracy and efficiently by using fast-multipole-accelerated integral equation methods of the Yukawa equation~\cite{kro-qua2011}.
+where $c_0(\xx)$ is the initial concentration.
+Equation~\eqref{eqn:DiffusionLaplace} will be solved with high-order accuracy and efficiently by using FMM-accelerated integral equation methods for the Yukawa equation~\cite{kro-qua2011}.
 The concentration field will then be recovered with an inverse Laplace transform~\cite{jos-war2006}.
 
-By combining our BIE Stokes solver with the proposed high-order, advection-diffusion solver, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation (see Section~\ref{sec:sinkhole}), would finally become possible.
+By combining our BIE Stokes solver with the proposed high-order, advection-diffusion solver, simulations of simultaneous erosion and dissolution, while also including transport and sedimentation (see Section~\ref{sec:sinkhole}), will finally be possible.
 Such a framework could accurately simulate the geophysically relevant scenario of karst conduits with embedded granular media.
@@
 
-Transport through eroded media is a direct consequence of the pore structure.
-To gain an understanding of transport and dispersion through the complex geometries formed by erosion, we will simulate and statistically analyze tracer trajectories as advected by the intervening flow.
+The transport of quantities through eroded media is a direct consequence of the pore structure.
+To gain understanding of transport and dispersion through the complex geometries formed by erosion, we will simulate and statistically analyze concentrations that are diffusing and being  advected by the intervening flow.
 In an eroded geometry $\Omega$, the dimensionless concentration $c$ is governed by
@@
 
+\begin{wrapfigure}[17]{r}{0.3\textwidth}
+  \includegraphics[width=0.3\textwidth]{figs/100b_t100tracer}
+  \caption{\label{fig:100tracers} \em Streamlines visualized with 200 tracers passing through an eroded geometry.
+The tracers are initialized at the left end of the channel and the flow is from left to right.} \end{wrapfigure}
 In the infinite Peclet number limit, the concentration is governed by pure advection and the characteristics of the concentration field satisfy $\dot{\ss}(t) = \uu(\ss(t))$ and are identical to the streamlines (Fig.~\ref{fig:100tracers}).
-Once $N_p$ trajectories are computed, using for example a high-order Runge-Kutta method, transport can be quantified.
+Once $N_p$ trajectories are computed with a high-order Runge-Kutta method, transport can be quantified.
 Two of the most important measurements to quantify transport are the tortuosity and the anomalous dispersion, both which are defined in terms of the length of the trajectories.
-The tortuosity is the dimensionless number
+The tortuosity is the average length a trajectory travels across a channel relative to the length of the channel.
+Mathematically, it is the dimensionless number
 \begin{align}
@@
 \end{align}
-which is approximated using the $N_p$ trajectories.
-Here, $S$ is the vertical cross-section at $x=x_0$, $d$ is its length, $u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of the trajectory starting at $(x_0,y_0)$ and ending at a vertical cross-section at the other end of the channel.
+which is approximated using the $N_p$ trajectories. Here, $S$ is the
+vertical cross-section at $x=x_0$, $d$ is its length, $u_1$ is the
+horizontal velocity, and $\lambda(y_0)$ is the length of the trajectory
+starting at $(x_0,y_0)$ and ending at a vertical cross-section at the
+other end of the channel.
 Relationships between the tortuosity and porosity of a geometry have been developed by other groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and preliminary results indicate that such models might be appropriate for geometries whose porosity increases under the action of erosion (Fig.~\ref{fig:100tortuosity}(a)).
@@
 At early times, the line of slope 1 (black dashed curve) indicates a ballistic motion.
-At later times, the dispersion becomes super-dispersive at a rate indicated by the slope of the black dashed-dotted line.}
+At later times, the dispersion becomes super-dispersive at a rate indicated by the slope of the black dashed-dotted lines.}
 \end{wrapfigure}
@@
 In preliminary work~\cite{chi-moo-qua2019}, we define pore sizes between grains that share an edge of a Delanuay triangulation with vertices at the grain centers (Fig.~\ref{fig:Eroding100gap_mean_var}(a)).
-We then compute and plot the mean and variance of the pore sizes as a function of porosity in Fig.~\ref{fig:Eroding100gap_mean_var}(b) and~\ref{fig:Eroding100gap_mean_var}(c).
+We then compute and plot the mean and variance of the pore sizes as a function of porosity in Figs.~\ref{fig:Eroding100gap_mean_var}(b) and~\ref{fig:Eroding100gap_mean_var}(c).
 Continuing in this direction, we will use the notion of a {\em porelet}, an individual Hagen-Poiseuille flow in each of the individual pores~\cite{dea-qua-bir-jua2018}, to continue to investigate the effect of erosion on pores sizes.
@@
 \end{subfigure}
-  \caption{\label{fig:Eroding100gap_mean_var} \em (a) The pore sizes are defined in terms of a Delanuay triangulation.
-The effect of erosion on (b) the mean and (c) the variance of the pore sizes.
+  \caption{\label{fig:Eroding100gap_mean_var} \em (a) Two grains are neighbors if they share an edge of a Delanuay triangulation.
+Then, pore sizes are defined to be the distance between neighboring grains.
+Erosion affects the (b) mean and (c) variance of the pore sizes.
 The geometry initially contains 100 eroding bodies.}
@@
 We start with a single grain inside the channel that is sufficiently large that the spacing between the initial grain and the channel walls, which is 2 units wide, is $10^{-3}$.
-By using a Barycentric quadrature rule, we stably simulate erosion with only 512 points on the eroding body which corresponds to an arclength spacing 12 times larger than the original separation distance; to achieve a comparable accuracy with the spectral trapezoid rule, 60 times as many discretization points would be required.
+Using a Barycentric quadrature rule, we stably simulate erosion with only 512 points on the eroding body which corresponds to an arclength spacing 12 times larger than the initial separation distance; to achieve a comparable accuracy with the spectral trapezoid rule, 60 times as many discretization points would be required.
 In Fig.~\ref{fig:porelets}, different shades of grey correspond to the configuration of the eroding grain at five equally spaced time steps.
 At three of the time steps, we plot the velocity between the grain and the solid wall (black line).
-At all three configurations, the flow is observed to be nearly parabolic, supporting the validity of the porelet model~\cite{dea-qua-bir-jua2018}.
+At all three configurations, the flow is nearly parabolic, supporting the validity of the porelet model~\cite{dea-qua-bir-jua2018}.
 After performing a thorough analysis of the pore size growth in this simple configuration, we will develop a more complete model for pore networks that are characteristic of porous media.
@@
   \includegraphics[width=0.4\textwidth]{figs/porelets_geom}
-  \caption{\label{fig:porelets} \em An eroding body at five equally time steps.
-At the three intermediate time steps, the Stokesian velocity field in the bulk, which is nearly parabolic, is included.}
+  \caption{\label{fig:porelets} \em An eroding body at five equally spaced time steps.  At three of the time steps, the Stokesian velocity field in the bulk, which is nearly parabolic, is included.} 
 \end{wrapfigure}
@@
 considering concentrations with finite Peclet numbers}. We will deploy
-the same numerical methods to simulate dissolution and melting to study
+the same numerical methods to simulate chemical erosion to study
 a concentration that is being transported through a eroded porous
@@
 
-Upon developing and improving numerical methods to simulate mechanical
-and chemical erosion, {\bf we will develop methods to simulate the
-effects of seepage transport, gravitational sedimentation, and buoyancy
-forces acting that act on the porous media constituents.} In addition to
-the new techniques for quadrature, preconditioning, adaptivity, and fast
-summation described in earlier sections, this extension also requires
-the inclusion of contact forces between bodies to eliminate unphysical
-overlap that is inevitable due to discretization errors. Though
-conceptually straightforward, implementing contact forces in multibody
-fluid-structure simulations is far from simple in practice, with several
-competing possible strategies that are a topic of current research
-\cite{yan2019computing, lu-rah-zor2017, bys-sha-qua2019,
-kab-qua-bir2018, vou-har-tam-gri2011}.
+Upon developing and improving numerical methods to simulate mechanical and chemical erosion, {\bf we will develop methods to simulate seepage transport, gravitational sedimentation, and buoyancy forces acting on the porous media constituents.} In addition to the new techniques for quadrature, preconditioning, adaptivity, and fast summation described in earlier sections, this extension also requires the inclusion of contact forces between bodies to eliminate unphysical overlap that is inevitable due to discretization errors.
+Though conceptually straightforward, implementing contact forces in multibody fluid-structure simulations is far from simple in practice, with several competing possible strategies that are a topic of current research \cite{yan2019computing, lu-rah-zor2017, bys-sha-qua2019, kab-qua-bir2018, vou-har-tam-gri2011}.
 
-One approach is to use introduce a potential with short-range repulsion, but such methods often introduce stiffness.
+One approach is to introduce a potential with short-range repulsion, but such methods often introduce numerical stiffness.
 Alternatively, a space-time interference volume can guarantee a minimum separation between grains.
-In a fluid context, this method was first introduced by Lu et al.~\cite{lu-rah-zor2017}, and extended to allow for much smaller separation distances of rigid bodies by the PI's previous graduate student~\cite{bys-sha-qua2019}.
-One PhD student, who will be jointly supervised by both PIs, will simulate sedimentation of eroding bodies by developing algorithms that resolve quadrature error and contact.
+In a fluid context, this method was first introduced by Lu et al.~\cite{lu-rah-zor2017}, and extended to allow for much smaller separation distances of rigid bodies by PI Quaife ad his previous PhD student~\cite{bys-sha-qua2019}.
+One PhD student, who will be jointly supervised by both PIs, will simulate transport of eroding bodies by developing algorithms that resolve quadrature error and contact.
 
-The central goal of simulating transport of eroding grains is to simulate a complex porous-medium of arbitrarily sized and shaped grains undergoing the simultaneous action of mechanical-or-chemical erosion and transport due to the combined effects of seepage, contact, and gravitational sedimentation.
+The central goal of simulating transport of eroding grains is to
+simulate a complex porous-medium of arbitrarily sized and shaped grains
+undergoing the simultaneous action of mechanical or chemical erosion and transport due to the combined effects of seepage, contact, and gravitational sedimentation.
 These computations will thus simulate, with high-fidelity, the multi-physics of realistic porous-medium dynamics, albeit in a scaled down context.
@@
 
-{\bf More specifically, we plan to run large batches of the high-fidelity boundary-integral-equation-based numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks \cite{ling2016reynolds, kutz2017deep, ling2016machine, pelt2018mixed} to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.}  The output of the high-fidelity simulations of the grain configuration can be transformed into essentially an image format, permitting use of cutting-edge advances in deep neural-networks for image analysis~\cite{pelt2018mixed}.
+{\bf More specifically, we plan to run large batches of the high-fidelity BIE numerical simulations of erosion and then leverage rapid advances in the field of machine learning and deep-neural networks \cite{ling2016reynolds, kutz2017deep, ling2016machine, pelt2018mixed} to develop reduced models that parametrize the effects of erosion on the evolution of macroscopic medium properties and the flow.}  The output of the high-fidelity simulations of the grain configuration can be transformed into essentially an image format, permitting use of cutting-edge advances in deep neural-networks for image analysis~\cite{pelt2018mixed}.
 Some important advantages of referenced work are the use of dilated convolutions in a deeply connected network, which first mixes scales and second reduces the number of super-parameters present, thus largely mitigating the risk of overfitting data.
@@
 Once the essential features are learned, they will be incorporated into reduced-order models that harness the multiphase framework.
-These reduced models will enable more efficient and larger scale simulations of dynamic erosion than are feasible with the high-fidelity boundary-integral simulations.
+These reduced models will enable more efficient and larger scale simulations of dynamic erosion than are feasible with the high-fidelity BIE simulations.
 
@@
 
-The proposed experiments involve two parallel lines of inquiry that will
-be merged in later stages of the project. The first line will
-investigate dynamic erosion of a porous material by mechanical or
-chemical action.
+The proposed experiments involve two parallel lines of inquiry that will be merged in later stages of the project.
+The first line will investigate dynamic erosion of a porous material by mechanical or chemical processes.
 The porous medium will be represented by fragments of either erodible material, such as bentonite clay, or dissolve material, such as sucrose solids.
@@
 The PIs are committed to the development and training of students at various levels of their education throughout the time frame of the proposed research.
-Different aspects of the proposed research are appropriate levels for PhD research, undergraduate research, and high school student research.
+Different aspects of the proposed research are appropriate for PhD research, undergraduate research, and high school student research.
 Moreover, opportunities within FSU will be seized to publicize the work to K--12 students and to the greater public.
@@
 \subsection{Graduate Research}
-An important benefit of the proposed research is the potential to immerse graduate students in fundamentally {\em cross-disciplinary} research.
+An important benefit of the proposed research is the immersion of graduate students in fundamentally {\em cross-disciplinary} research.
 This proposal involves a confluence of disciplines, most centrally computational mathematics, but also geophysics, environmental science, hydrology, and physical modeling.
@@
 Naturally, the proposed research will form the foundation for the PhD dissertations of the supported graduate students.
-Beyond this, the students will engage in publishing articles in peer-reviewed journals of high quality and attending national and international conferences where they will present their work and network with experts in the field.
+Beyond this, the students will engage in publishing articles in high-quality peer-reviewed journals and attending national and international conferences where they will present their work and network with experts in the field.
 The PIs will closely mentor the graduate students to ensure their continued development, not only intellectually, but also in the `soft' skills of communication, promotion, and networking.
-Having both PIs Moore and Quaife involved in the training of each graduate student is especially valuable for offering multiple perspectives on these issues.
+Having both PIs involved in the training of each graduate student is especially valuable for offering multiple perspectives on these issues.
 The PIs will make special efforts to recruit women and underrepresented minorities as the graduate students funded by this project.
@@
 
-At FSU, there are at least two excellent avenues to attract interested undergraduate students: the Undergraduate Research Opportunity Program (UROP) and the IDEA grant.
+At FSU, there are at least two excellent avenues to attract interested undergraduate students: the {\bf Undergraduate Research Opportunity Program (UROP)} and the {\bf IDEA grant}.
 The UROP engages undergraduates in academic research, while the IDEA grant is a competitive program, requiring more advanced students to identify a research advisor and write an internal proposal.

### 2019-11-23 docs/proposals/NSF/ProjDocs/funding_BQ.tex
went through entire proposal

@@
 Sciences, Computational Mathematics \\
-{\bf Total Award Amount:} \$383,086 \\
+{\bf Total Award Amount:} \$439,193 \\
 {\bf Duration:} July 1, 2020--June 30, 2023 \\

### 2019-12-01 docs/proposals/NSF/ProjDocs/funding_NM.tex
NM

@@
 Sciences, Computational Mathematics \\
-{\bf Total Award Amount:} \$439,193 \\
+{\bf Total Award Amount:} \$439,824 \\ %\$439,193 \\
 {\bf Duration:} July 1, 2020--June 30, 2023 \\

### 2019-12-01 docs/proposals/NSF/ProjDocs/funding_BQ.tex
fixed some of Dale's comments

@@
 Sciences, Computational Mathematics \\
-{\bf Total Award Amount:} \$439,193 \\
+{\bf Total Award Amount:} \$439,824 \\
 {\bf Duration:} July 1, 2020--June 30, 2023 \\

### 2019-12-13 docs/proposals/NSF/ProjDocs/funding_NM.tex
NM

--- 2019-11-23 docs/proposals/NSF/ProjDocs/funding_NM.tex
@@
 
+%\vspace{-17pt}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Pending Support:}
+
 \noindent
@@
 
-%\vspace{-17pt}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Pending Support:}
 {\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous

### 2019-12-13 docs/proposals/NSF/ProjDocs/funding_NM.tex
NM

@@
 {\bf Person-Months Per Year Committed to Project:} Calendar: 0,
-Academic: 0, Summer: 0.5 \\
+Academic: 0, Summer: 0 \\
 
+\noindent
 {\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous

### 2019-12-19 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{document}
-\title{Fluid-mechanical erosion generates anisotropy in porous media}
+\title{Fluid-mechanical erosion creates anisotropic porous media}
+%\title{Fluid-mechanical erosion generates anisotropy in porous media}
 %\title{Erosion leads to anisotropy in a porous medium}
 %\title{The development of anisotropy in an eroding porous medium}
-%
 
@@
 The solid constituents of the porous medium erode under the action of surface shear stress.
-As the particles shrink, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.
+As the particles disintegrate, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.
 \end{abstract}
@@
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+
+%Shear stress on solid surfaces drives the erosion of porous material
+
+% dematerialize, disintegrate
 
@@
 The recent incorporation of barycentric interpolation methods permits simulation of tightly packed configurations (cite new paper with Shang).
+
+% Need to include descriptor 'high-fidelity' for our simulation.
 

### 2019-12-27 docs/transport/Response_to_Reviewer_1.tex
Responses for JFM paper

\documentclass[11pt]{article}

\usepackage{todonotes}
\usepackage{fullpage}
\usepackage{amsmath,amsfonts,amssymb,stmaryrd}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Silas Alben,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments.  The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript.  We also note that formatting
issues were resolved in the bibliography. An itemized list of the
changes addressing the reviewer's comments are below.
\\ \\
\noindent
Sincerely,
\\
\noindent
Shang-Huan Chiu, Nick Moore, and Bryan Quaife

\section*{Response to Reviewer 1}

\noindent
\comment{The Barycentric formulae (5.9 \& 5.10) for the first
derivatives of Cauchy integral are incorrect. They are NOT true
barycentric form and straightforward numerical experiments will show
that all accuracies are lost up to the boundary using these formulae,
even if $v(x)$ is computed to high accuracy using the formulae (5.6 \&
5.7). (See e.g.~Sec 3.3 of Barnett et.~al.~2015 for more details.)}
\begin{itemize}
  \item response
\end{itemize}

\noindent
\comment{Likewise, the second derivative ``barycentric formulae" (5.15 \& 5.18) are incorrect, either. So the authors will need to explain how they managed to get high accuracies with the stated formulae?}
\begin{itemize}
  \item response
\end{itemize}

\noindent
\comment{In my opinion, the claim of having developed a ``new quadrature
method" is too strong. After all, there is nothing new about the
barycentric quadrature itself. Rather, I suggest that maybe a more
appropriate claim would be that the authors have developed a ``new
numerical scheme" for the Stokes porous media flow, where the accurate
quadrature is one ingredient in this scheme.}
\begin{itemize}
  \item response
\end{itemize}

\noindent
\comment{The transient increase of tortuosity is interesting, but the
explanation in Sec 6.4 is not satisfying. The authors proposed that the
increase of tortuosity can be explained by the sudden increase of
$x$-velocity when a grain vanishes. But in formula (4.4) or (4.5), the
$x$-velocity appears both in the numerator and the denominator, which
seems to me that the increase would just cancel. Then, as the authors
have pointed out, wouldn't the straighter streamlines resulted from the
vanishing of grains have decreased the tortuosity?}
\begin{itemize}
  \item response
\end{itemize}

\noindent
\comment{The porosity-tortuosity models (4.6c \& 4.6d) are not
explicitly compared in the results section. How much worse are they
comparing to the other models?}
\begin{itemize}
  \item response
\end{itemize}

\noindent
\comment{The coefficient CE in equation (2.1) is undefined.}
\begin{itemize}
  \item Thank you for pointing this out. We also realized that $\mu$ is
  undefined. We now state:
  \begin{quotation}
    \noindent
    Parameters include the fluid viscosity $\mu$ and the
    material-dependent erosion constant $C_E$. By non-dimensionalizing
    equations (2.1) (Quaife \& Moore 2018), we set both these parameters
    to one.
  \end{quotation}
\end{itemize}

\noindent
\comment{Should the shear stress formula (2.2) contain viscosity in it
based on the governing equation (2.1)?}
\begin{itemize}
  \item In general, it would. However, since we have non-dimensionalized
    following our previous work, the viscosity is assumed to be 1.
\end{itemize}

\noindent
\comment{In Figure 5, do the colors represent vorticity itself or the
log of the abs vorticity? (Which would be consistent with the colors in
Figure 4.)}
\begin{itemize}
  \item The color represents the logarithm of the absolute value of the
    vorticity.
  \item We have updated the caption to read:
    \begin{quotation}
    \noindent
      The eroded bodies from figure 4 at time $t = 0.1$. The color is
      the logarithm of the magnitude of the vorticity. The initial
      distances from the body to the solid wall are: (a) $h$, (b) $h/2$,
      and (c) $h/10$.
    \end{quotation}
  \item We have also updated the text to read:
    \begin{quotation}
    \noindent
      To visualize the flow, in figure 5 we plot the logarithm of the
      absolute value of the vorticity from the final time step in figure
      4.
    \end{quotation}
\end{itemize}

\noindent
\comment{When first introduced in Sec 4.3, the ``pore sizes" are not
clearly defined. (My first impression was that pore size = portion of an
edge of the Delaunay diagram. Only at the end in Sec 6.4 do we know that
it is defined as the closest distance between grains.)}
\begin{itemize}
  \item In Figure 3, we clarify the definition by adding the statement:
    {\em represented by the length of the red line segments}.
  \item In the text, we now state:
    \begin{quotation}
    \noindent
      Finally, we define the pore sizes to be the minimum distance
      between all pairs of neighboring grains, and these distances are
      represented by the red line segments in figure 3(a).
    \end{quotation}
\end{itemize}

\noindent
\comment{``Porosity" is undefined throughout the paper.}
\begin{itemize}
  \item We have now formally defined the porosity by rewriting the
    description of coarse-grained models as:
  \begin{quotation}
  \noindent
    Examples of coarse-grained models for porous media flow include
    tortuosities (Matyka et al.~2008; Duda et al.~2011; Koponen et
    al.~1996), geometry connectivity (Knudby \& Carrera 2005), anomalous
    dispersion (Dentz et al.~ 2004), and permeability-porosity
    relationships (Dardis \& McCloskey 1998; Carman 1937), where the
    porosity is the fraction of the geometry that is fluidized.
  \end{quotation}

\end{itemize}

\noindent
\comment{``Area fraction" is plotted in (and only in) Figure 7, while
the rest of the paper used porosity. Maybe plotting porosity here would
give a more consistent and smoother reading experience?}
\begin{itemize}
  \item We examined the area fraction and flow rate in figure 7 so that
    it could be compared to results from our previous work. The goal is
    to demonstrate that we now able to resolve smaller area fractions
    and correspondingly lower flow rates.

  \item We have updated the text to read:
    \begin{quotation}
      \noindent
      In our previous work (Quaife \& Moore 2018), we investigated the
      effects of erosion on the area fraction and flow rate of two
      different geometries. Here, we do the same analysis, but with the
      denser packing of the grains.
    \end{quotation}

\end{itemize}

\end{document}

### 2019-12-27 docs/transport/Response_to_Reviewer_2.tex
Responses for JFM paper

\documentclass[11pt]{article}

\usepackage{todonotes}
\usepackage{fullpage}
\usepackage{amsmath,amsfonts,amssymb,stmaryrd}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Silas Alben,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments.  The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript.  We also note that formatting
issues were resolved in the bibliography. An itemized list of the
changes addressing the reviewer's comments are below.
\\ \\
\noindent
Sincerely,
\\
\noindent
Shang-Huan Chiu, Nick Moore, and Bryan Quaife

\section*{Response to Reviewer 2}

\noindent
\comment{equations 2.1.  I am confused as to how the no-slip condition
is implemented as zero velocity when in fact the interface is receding
at a rate Vn.}
\begin{itemize}
  \item This comes from a quasi-steady approximation that we have used
    in our previous work as well as by others. For example, see Section
    5.2 from Mitchell and Spagnolie's JCP paper {\em A generalized
    traction integral equation for Stokes flow, with applications to
    near-wall particle mobility and viscous erosion}.

  \item In Section 2, we now state:
    \begin{quotation}
      \noindent
      Since the rate of erosion is much slower than the background flow,
      a quasi-steady approximation justifies the no-slip boundary
      condition.
    \end{quotation}
\end{itemize}

\noindent
\comment{end of section 4.1.  It seems that this protocol (matching
velocity but not position for reinsertion) results in each particle
moving through a different landscape.  Can the authors comment on the
significance of this?}
\begin{itemize}
  \item The reinsertion approach we take has been shown to not introduce
    any significantly artificial decorrelation.

  \item In Section 4.1, We have added that
    \begin{quotation}
      \noindent
      This method of reinsertion does not artificially decorrelate the
      particle velocities (Puyguiraud et al.~2019), and this allows us
      to reliably use the statistical moments (4.2) to characterize the
      anomalous dispersion.
    \end{quotation}

\end{itemize}

\noindent
\comment{p.10, end of section 4.  The authors do not explicitly say how
pore size is calculated.  Is it simply the length of the portion of a
Delaunay side that lives outside the grains?}
\begin{itemize}
 \item In Figure 3, we clarify the definition by adding the statement:
    {\em represented by the length of the red line segments}.
  \item In the text, we now state:
    \begin{quotation}
    \noindent
      Finally, we define the pore sizes to be the minimum distance
      between all pairs of neighboring grains, and these distances are
      represented by the red line segments in figure 3(a).
    \end{quotation}
\end{itemize}

\noindent
\comment{p.17 ``single body close to a wall", the 'experiment' mentioned
here is, I believe, a numerical `experiment'.  It might be good to
indicate that clearly.}
\begin{itemize}
  \item The reviewer is correct that this is a numerical experiment.

  \item There were other instances in the paper where we claimed to be
    performing an `experiment'. We have clarified each of the instances
    by referring them as a `numerical experiment'.
\end{itemize}

\noindent
\comment{sections 6.2 and 6.3.  How were these geometries of 20 grains
chosen?  Both the sizes and positions of these grains vary between
examples - it's not just the porosity that is different.}
\begin{itemize}
  \item The initial placement and radii of the bodies are chosen with a
    randomized method. The algorithm is descried at the start of Section
    6.

  \item We have updated the start of section 6.2 to read:
    \begin{quotation}
      \noindent
      We randomly initialize 20 eroding grains with an initial porosity
      of $\phi = 37.68\%$ and the Hagen-Poiseuille flow
      $\mathbf{U}(\mathbf{x}) = U (1-y^2, 0)$ imposed on $\Gamma$
    \end{quotation}

  \item We have updated the start of section 6.3 to read:
    \begin{quotation}
      \noindent
      We consider a second example with of 20 randomly initialized
      eroding bodies, but with a smaller initial porosity of $\phi =
      30.67\%$.
    \end{quotation}

  \item We have updated the start of section 6.4 to read:
    \begin{quotation}
      \noindent
        As a final example, we consider 100 randomly initialized eroding
        bodies with an initial porosity near $50\%$.
    \end{quotation}

\end{itemize}

\noindent
\comment{Figure 8.  Due to what I presume is an artifact of plotting, it
looks like lots of streamlines suddenly end, which is confusing.}
\begin{itemize}
  \item In figure 8, we freeze an eroded geometry and plot the
    trajectory of passive tracers at five different time steps. Since
    the flow is steady and the tracers are passive, the trajectories
    trace out streamlines.

  \item We have updated the caption to read:
    \begin{quotation}
      \noindent
      200 particle trajectories in the second geometry from figure 6.
      The particles are initially equispaced at $(−1,y)$, where $y \in
      (−1, 1)$. The first five snapshots are equispaced in time. The
      bottom right frame is a magnification of the fifth snapshot, but
      with additional trajectories.
    \end{quotation}

  \item We have also updated the paragraph describing figure 8 to
    clarify that it is showing tracer trajectories that trace out
    streamlines.
\end{itemize}

\noindent
\comment{Figure 9.  While the sharp features in subfigure (b) are
apparently finite cusps, they raise the question of whether any infinite
dwell times (divergent $\tau$) are ever observed in these simulations -
i.e.~are particles ever trapped inside recirculating zones?}
\begin{itemize}
  \item Thank you for pointing out this possibility. The
    recirculation zones are close to the eroding bodies and are
    typically very small. Because we measure the local tortuosity by
    initiating streamlines significantly far from the grains, each of
    them connect the inlet to the outlet.

  \item We have updated the text to read:
    \begin{quotation}
      \noindent
      We note that if a streamline originates in a recirculation zone,
      which is possible in two dimensions (Higdon 1985), then the local
      tortuosity will be infinite. However, in each of our numerical
      experiments, all the streamlines connect the inlet to the outlet.
      Having only finite local tortuosities, the hydraulic tortuosity is
      defined by taking the average over all points on the inlet cross-
      section
    \end{quotation}
\end{itemize}

\noindent
\comment{p.26 bottom paragraph typo: ``an ... media"}
\begin{itemize}
  \item This typo has been fixed
\end{itemize}

\end{document}

### 2019-12-27 docs/transport/Response_to_Reviewer_3.tex
Responses for JFM paper

\documentclass[11pt]{article}

\usepackage{todonotes}
\usepackage{fullpage}
\usepackage{amsmath,amsfonts,amssymb,stmaryrd}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Silas Alben,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments.  The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript.  We also note that formatting
issues were resolved in the bibliography. An itemized list of the
changes addressing the reviewer's comments are below.
\\ \\
\noindent
Sincerely,
\\
\noindent
Shang-Huan Chiu, Nick Moore, and Bryan Quaife

\section*{Response to Reviewer 3}

\noindent
\comment{Pores in natural porous media care of three-dimensional
geometry.  The authors may include some discussion on how to extend
their numerical method to three-dimensional problems.  In addition, they
may also discuss the limitations of the erosion analysis in
2-dimensional flow to be applied for three-dimensional flow. If the
erosion process in three-dimensional flow is very different from that in
two-dimensional flow, the analysis of this paper may have less relevant
to the analysis of erosion in natural porous media.}
\begin{itemize}
  \item The reviewer is correct that by assuming the geometry is
    two-dimensional, we have limited the applicability for natural
    porous media. There are several numerical challenges to simulate
    three-dimensional erosion, with the most significant being the
    $\theta-L$ formulation, quadrature method, spectral representation
    of the geometry, and the boundary integral equation solver.

  \item Others have developed three-dimensional numerical methods for
    removing stiffness in interfacial flow ($\theta-L$ formulation),
    spectrally representing geometries, and efficiently solving BIEs.
    The challenge with these methods is their computational cost. To
    consider suspensions with the resolution and number of grains that
    we consider, the BIE would most likely require a parallel
    implementation that would run on high-performance computing
    architectures. At this point, this is not the goal of our work.

  \item The Barycentric quadrature method relies on a complex variable
    formulation, so it is inherently two-dimensional. However, there are
    other quadrature methods that can be applied in three dimensions,
    but they are also computationally expensive.

  \item Our response to the reviewer's second comment points to a
    paragraph that has been added to the Introduction.

\end{itemize}

\noindent
\comment{In the numerical examples of the paper the grains are all
separated. In natural porous media, grains are compressed to form grain
contacts. The authors may include discussion on numerical challenges in
studying erosion process in natural porous media.}
\begin{itemize}
  \item The reviewer is correct that porous media grains are compressed
    and form grain contact. This is the result of processes such as
    sedimentation and transport of the grains themselves. This, again,
    is a limitation of our method since we only consider immobile
    bodies.

  \item We plan to consider mobile bodies in the future, and this will
    require a significant computational effort.

  \item To the best of our knowledge, nobody has studied the effect
    erosion has on transport through a porous media. Therefore, as a
    first step, we limit ourselves to two-dimensional suspensions of
    immobile bodies, and we plan to remove these limitations in the
    future. In the Introduction, we have added the following paragraph:
    \begin{quotation}
      \noindent
      While natural porous media are three-dimensional, there are
      several challenges that must be overcome to extend our high-order
      methods to three dimensions.  A three-dimensional version of a
      {$\theta-L$} formulation exists (Ambrose {\em et al.} 2013), but
      the Barycentric quadrature method relies upon a complex variable
      formulation of the BIE, making it inherently two-dimensional.
      Therefore, a different quadrature method is required. Additional
      challenges of three-dimensional simulations include spectral
      representations of the geometry and efficiently solving
      discretizations of the BIE.  While high-order methods for
      three-dimensional BIEs have been developed, their computational
      cost limits the number of bodies that can be practically
      simulated. Another limitation of this work is the assumption of
      immobile grains.  Mechanisms such as sedimentation play a role in
      real applications, and this will effect the transport properties.
      Simulating mobile grains introduces the additional challenge of
      resolving contact.  Since high-order methods have never been used
      to study transport in eroded porous media, as a first step we
      consider the case  with two-dimensional immobile grains. This
      assumption allows for a clear interpretation of the results.  For
      example, in this work we are able to simulate a large
      densely-packed suspension (up to $100$ in this manuscript).

    \end{quotation}
\end{itemize}

\end{document}

### 2019-12-27 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM
Responses for JFM paper

@@
 \begin{center}
-{\large \bf Erosion, Transport, and Dispersion in Granular
+{\large \bf Project Description: \\
+Erosion, Transport, and Dispersion in Granular
 and Porous Media} 
@@
 The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion in the Stokes flow regime~\cite{Quaife2018}, the regime relevant for the currently proposed groundwater applications.
-Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of densly packed porous-media configurations formed by erosion~\cite{chi-moo-qua2019}.
+Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of densely packed porous-media configurations formed by erosion~\cite{chi-moo-qua2019}.
 
@@
 
-{\bf An immediate goal of the proposed work is to extend the range of
-physical effects captured in these simulations.} A particular challenge
-of a BIE formulation is developing quadrature for nearly-singular
-integrands that arise when bodies are close. To address this problem, we
-have very recently extended a Barycentric quadrature
-method~\cite{bar2014, bar-wu-vee2015} and have successfully simulated
-erosion with grains that are initially separated by 1\% of an arclength
-spacing~\cite{chi-moo-qua2019}. The quadrature method is a non-intrusive
-modification of the trapezoid rule and results in an error bound that is
-independent of the grain configuration. However, the current
-implementation does not yet fully exploit FMM acceleration. The
-computational challenge is to develop FMM expansions for the velocity,
-vorticity, pressure, and deformation-tensor layer potentials.
-Since these layer potentials each have distinct kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and their HPC implementations (for example, see \url{http://pvfmm.org}).
+{\bf An immediate goal of the proposed work is to extend the range of physical effects captured in these simulations.} A particular challenge of a BIE formulation is developing quadrature for nearly-singular integrands that arise when bodies are close.
+To address this problem, we have very recently extended a Barycentric quadrature method~\cite{bar2014, bar-wu-vee2015} and have successfully simulated erosion with grains that are initially separated by 1\% of an arclength spacing~\cite{chi-moo-qua2019}.
+The quadrature method is a non-intrusive modification of the trapezoid rule and results in an error bound that is independent of the grain configuration.
+However, the current implementation does not yet fully exploit FMM acceleration.
+The computational challenge is to develop FMM expansions for the velocity, vorticity, pressure, and deformation-tensor layer potentials.
+Since these layer potentials each have distinct kernels, we will utilize kernel-independent FMMs~\cite{yin-bir-zor2004, fon-dar2009}, and their HPC implementations~\cite{pvfmm}.
 Other challenges to be investigated include preconditioning strategies to reduce the number of required GMRES iterations, and time adaptivity to enable stable simulations to user-specified tolerances.

### 2019-12-27 docs/transport/erosion_transport.tex
Responses for JFM paper

@@
-%\documentclass[preprint,10pt]{elsarticle}
 \documentclass{jfm}
@@
 Quaife\aff{3}\corresp{\email{bquaife@fsu.edu}}}
-
-%  Alan N. Other\aff{1}
-%  \corresp{\email{jfm@damtp.cam.ac.uk}},
-%  H. - C. Smith\aff{1}
-% \and J. Q.  Public\aff{2}}
 
@@
 \maketitle
-
-%\title{Viscous Transport in Eroding Porous Media}
-%
-%\author[SH]{Shang-Huan Chiu}
-%\author[Nick]{M.~N.~J.~Moore}
-%\author[Bryan]{Bryan D.~Quaife}
-%
-%\address[SH]{Department of Scientific Computing, Florida State
-%University, Tallahassee, FL, 32306.}
-%\address[Nick]{Department of Mathematics and Geophysical Fluid Dynamics
-%Institute, Florida State University, Tallahassee, FL, 32306.}
-%\address[Bryan]{Department of Scientific Computing and Geophysical Fluid
-%Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
 
@@
   the eroding bodies.
-
-%  We extend our previous work, [{\em Journal of Computational Physics},
-%  {\bf 375}:1--21, 2018], to simulate fluid-mechanical erosion of
-%  two-dimensional porous media with nearly-touching grains.  The method
-%  continues to use a boundary integral equation (BIE) method to solve
-%  the fluid equations, and a stable second-order time stepping method to
-%  erode the grains.  In our previous work, we required eroding grains
-%  that were sufficiently separated to guarantee that the trapezoid rule
-%  provides a sufficient amount of accuracy. We now remove this
-%  restriction by introducing a Barycentric quadrature rule whose error
-%  is bounded independent of the geometry.  The Barycentric quadrature
-%  rule is computationally expensive, so it is only used when necessary,
-%  and the spectrally accurate fast-multipole-accelerated trapezoid rule
-%  is used otherwise. We also simulate and analyze transport through
-%  eroded porous media.  By using the Barycentric quadrature rule, the
-%  analysis examines flow both in the fast and slow regions with
-%  high-order accuracy. Our results reveal several interesting  effects
-%  of erosion on the tortuosity, dispersion, and pore size distributions.
 \end{abstract}
@@
 Examples of coarse-grained models for porous media flow include
-permeability-porosity relationships~\citep{dar-mcc1998, car1937},
 tortuosities~\citep{mat-kha-koz2008, dud-koz-mat2011, kop-kat-tim1996},
 geometry connectivity~\citep{knu-car2005}, anomalous
-dispersion~\citep{den-cor-sch-ber2004}, and more.
+dispersion~\citep{den-cor-sch-ber2004}, and permeability-porosity
+relationships~\citep{dar-mcc1998, car1937}, where the porosity is the
+fraction of the geometry that is fluidized.
 
@@
 the fluid vorticity.
+
+While natural porous media are three-dimensional, there are several
+challenges that must be overcome to extend our high-order methods to
+three dimensions.  A three-dimensional version of a {\thL} formulation
+exists~\citep{amb-sie-tlu2013}, but the Barycentric quadrature method
+relies upon a complex variable formulation of the BIE, making it
+inherently two-dimensional. Therefore, a different quadrature method is
+required. Additional challenges of three-dimensional simulations include
+spectral representations of the geometry and efficiently solving
+discretizations of the BIE. While high-order methods for
+three-dimensional BIEs have been developed, their computational cost
+limits the number of bodies that can be practically simulated. Another
+limitation of this work is the assumption of immobile grains.
+Mechanisms such as sedimentation play a role in real applications, and
+this will effect the transport properties. Simulating mobile grains
+introduces the additional challenge of resolving contact.  Since
+high-order methods have never been used to study transport in eroded
+porous media, as a first step we consider the case  with two-dimensional
+immobile grains. This assumption allows for a clear interpretation of
+the results.  For example, in this work we are able to simulate a large
+densely-packed suspension (up to $100$ in this manuscript).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Contributions}
-%Our first contribution is extending the Barycentric quadrature rule
-%of~\citet{bar-wu-vee2015} to accurately compute velocity gradients
-%associated with Stokes flow. This new quadrature rule permits accurate
-%and stable simulations of erosion, and, moreover, enables visualization
-%of the vorticity field throughout.
-%
-%Our second contribution is computing and analyzing trajectories in
-%eroded geometries.  These trajectories are formed by combining the
-%Barycentric quadrature rule and a fourth-order Runge-Kutta method. Then,
-%they are used to compute tortuosities and dispersion rates of eroded
-%geometries. Finally, we examine the effect of erosion on the pore size
-%distribution.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Limitations}
-%As in our previous work~\citep{qua-moo2018}, we consider two-dimensional
-%immobile eroding grains. However, this work does not limit the proximity
-%of  grains. Compared to our previous work, we are able to simulate much
-%denser suspensions with a comparable number of discretization points and
-%without upsampling.  While we do investigate transport in this work, we
-%only consider passive particles that are advected by the flow.  To model
-%other physical processes, such as contaminant transport, we plan to
-%simulate a finite Peclet number advection-diffusion equation in eroded
-%geometries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Outline of the Paper}
 This paper is organized as follows. In section~\ref{sec:formulation}, we
@@
 prescribed Hagen-Poiseuille velocity field, and $\Vn$ is the normal
-velocity of $\gamma$. The shear stress on $\gamma$ is
+velocity of $\gamma$. Since the rate of erosion is much slower than the
+background flow, a quasi-steady approximation justifies the no-slip
+boundary condition. Parameters include the fluid viscosity $\mu$ and the
+material-dependent erosion constant $\CE$. By non-dimensionalizing
+equations~\eqref{eqn:erosionModel}~\citep{qua-moo2018}, we set both
+these parameters to one. The shear stress on $\gamma$ is
 \begin{align}
@@
 the discretization point that has the closest velocity to the particle's
-velocity at the outlet.  After a single trajectory is formed, it has
-undergone a collection of reinsertions.  Then, as a post-processing
-step, the trajectory is made continuous by attaching the tail of each
-segment to the origin of the next segment.
-
-%We consider trajectories in an open channel so that they can be compared
-%to trajectories in eroded geometries with large permeability.  The
-%trajectories are $(s_1(t),s_2(t)) = ((1-s_2(0)^2)t + s_1(0), s_2(0))$.
-%%\begin{align}
-%%  s_1(t) = (1-s_2(0)^2)t + s_1(0), \quad
-%%  s_2(t) = s_2(0).
-%%\end{align}
-%Averaging over $s_2(0) \in [-1,1]$, the first and second ensemble
-%moments are
-%\begin{align}
-%  \langle \lambda \rangle (t) = \frac{2}{3}t, \quad 
-%    \sigma_\lambda^2(t) = \frac{4}{45}t^2.
-%\end{align}
-%In section~\ref{sec:results}, we compare the second moment in an open
-%channel with the trajectories in an eroded geometry.
+velocity at the outlet. This method of reinsertion does not artificially
+decorrelate the particle velocities~\citep{puy-gou-den2019}, and this
+allows us to reliably use the statistical moments~\eqref{eqn:moments} to
+characterize the anomalous dispersion. After a single trajectory is
+formed, it has undergone a collection of reinsertions.  Then, as a
+post-processing step, the trajectory is made continuous by attaching the
+tail of each segment to the origin of the next segment.
 
@@
 at $x=1$, so $d=2$.  However, other choices for the terminal point when
-computing the tortuosity are sometime used~\citep{dud-koz-mat2011}.  The
-hydraulic tortuosity is defined by taking the average over all points on
-the inlet cross-section
+computing the tortuosity are sometime used~\citep{dud-koz-mat2011}.
+We note that if a streamline originates in a recirculation zone, which
+is possible in two dimensions~\citep{hig1985}, then the local tortuosity
+will be infinite. However, in each of our numerical experiments, all the
+streamlines connect the inlet to the outlet. Having only finite local
+tortuosities, the hydraulic tortuosity is defined by taking the average
+over all points on the inlet cross-section
 \begin{align}
@@
   \left(\int_{S}u_1(x_0,y_0)\,dy_0 \right),
-%  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_1(x_0,y_0)\lambda(y_0)\,dy_0}
-%  {\displaystyle\int_{S}u_1(x_0,y_0)\,dy_0},
   \label{eqn:tortuosity1}
@@
       \left(\int_\Omega u_1(\yy)\, d\yy \right),
-%  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
-%           {\displaystyle\int_\Omega u_1(\yy)\, d\yy},
   \label{eqn:tortuosity2}
@@
 \end{subfigure}
-\caption{\label{fig:Eroding100gap} (a) The pore sizes between
-neighboring grains. Two grains are neighbors if they share an edge of
-the Delanuay triangulation with nodes at the center of each eroding
-grain. (b) The pore sizes of an eroded geometry. The black curve is the
-Weibull distribution with the same first two moments as the data.}
+\caption{\label{fig:Eroding100gap} (a) The pore sizes, represented by
+the length of the red line segments, between neighboring grains. Two
+grains are neighbors if they share an edge of the Delanuay triangulation
+with nodes at the center of each eroding grain. (b) The pore sizes of an
+eroded geometry. The black curve is the Weibull distribution with the
+same first two moments as the data.}
 \end{figure}
@@
 are neighbors if their centers share an edge of the
-triangulation~\citep{dea-qua-bir-jua2018}. The pores of an eroded
-geometry are illustrated in figure~\ref{fig:Eroding100gap}(a). We do not
-consider pores between eroding bodies and the solid wall $\Gamma$, so
-some of the grains near the porous region boundary only have two
-neighbors. Having defined the pore sizes, we plot its distribution in
+triangulation~\citep{dea-qua-bir-jua2018}. Finally, we define the pore
+sizes to be the minimum distance between all pairs of neighboring
+grains, and these distances are represented by the red line segments in
+figure~\ref{fig:Eroding100gap}(a). We do not consider pores between
+eroding bodies and the solid wall $\Gamma$, so some of the grains near
+the porous region boundary only have two neighbors. Having defined the
+pore sizes, we plot its distribution in
 figure~\ref{fig:Eroding100gap}(b) and compare it with the Weibull
@@
   \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j. 
-%%
-%  \ssigma(\xx) &= \sum_{j=1}^{N_\out} w^0_j \mathbf{D}_\ssigma(\xx,\yy^0_j) \eeta_j +
-%  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j \mathbf{D}_\ssigma(\xx,\yy^k_j)
-%  \eeta^k_j, \\
-%%
-%  w(\xx) &= \sum_{j=1}^{N_\out} w^0_j D_\omega(\xx,\yy^0_j) \eeta_j +
-%  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D_\omega(\xx,\yy^k_j)
-%  \eeta^k_j.
 \end{align}
@@
       \left(\sum_{i,j=1}^N u_1(\xx_{ij}) \Delta x \Delta y \right)
-%  T = \frac{\sum\limits_{i,j=1}^N \|\uu(\xx_{ij})\|\Delta x \Delta y}
-%      {\sum\limits_{i,j=1}^N u_1(\xx_{ij}) \Delta x \Delta y}.
 \end{align}
@@
   \quad x \in \Omega.
-%  v(x) = \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
-%  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}, \quad x \in \Omega.
   \label{eqn:BaryvInterior}
@@
     \quad x \in \Omega^c.
-%  v(x) = \frac{1}{x-a} 
-%    \frac{\sum\limits_{j=1}^N \frac{v^+(y_j)}{y_j - x}w_j}
-%    {\sum\limits_{j=1}^N \frac{(y_j - a)^{-1}}{y_j - x}w_j},
-%    \quad x \in \Omega^c.
   \label{eqn:BaryvExterior}
@@
   \quad x \in \Omega.
-%  v'(x) = \frac{\sum\limits_{j=1}^{N}
-%    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
-%  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}, 
-%  \quad x \in \Omega.
   \label{eqn:BaryvprimeInterior}
@@
     \quad x \in \Omega^c.
-%  v'(x) = \frac{1}{x-a} \frac{\sum\limits_{j=1}^N
-%    \frac{v^+_j - v(x)}{(y_j - x)^2} w_j}
-%    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j - x} w_j},
-%    \quad x \in \Omega^c.
   \label{eqn:BaryvprimeExterior}
@@
     \left(\sum_{j=1}^N \frac{1}{y_j-x}w_j\right).
-%  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
-%    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
-%    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, \quad x \in \Omega.
 \end{align}
@@
     \left(\sum_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j\right).
-%  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
-%    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
-%    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}, 
-%    \quad x \in \Omega^c.
 \end{align}
@@
   \left(\sum_{i=1}^{N_p} u_1(y_i) \Delta y\right), 
-%  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N_p} 
-%    u_1(y_i) \lambda(y_i) \Delta y}
-%  {\displaystyle\sum_{i=1}^{N_p} u_1(y_i) \Delta y}, 
 \end{align}
@@
 
-The common characteristic of each of the experiments is near-contact
-between the eroding bodies, outer walls, and streamlines. We use our
-numerical methods to simulate, analyze, and visualize the following
-examples:
+The common characteristic of each of the numerical experiments is
+near-contact between the eroding bodies, outer walls, and streamlines.
+We use our numerical methods to simulate, analyze, and visualize the
+following examples:
 \begin{itemize}
@@
   centered at $y=-1$ and compare the eroding body's shape to a similar
-  experiment of~\citet{mit-spa2017}.
+  numerical experiment of~\citet{mit-spa2017}.
 
@@
 Consider a single eroding body close to a solid wall with the shear flow
-$\UU(\xx) = (y+1,0)$
-%\begin{align}
-%  \UU(\xx)=\left[
-%  \begin{array}{c}
-%    y+1 \\ 0
-%  \end{array}
-%  \right],
-%\end{align}
-imposed on $\Gamma$. \citet{mit-spa2017} performed a similar
-three-dimensional experiment using a second-order quadrature method.
-Their initial body is a sphere with its center located $1.5$ radii above
-the solid wall.  We initialize the two-dimensional eroding body with
-radius $r = 0.4$, and we conduct numerical experiments where the initial
-distance between the grain and the solid wall is $h$, $h/2$, and $h/10$,
-where $h = 2\upi r/N_\iin$.  If we used the trapezoid rule and required
-an error that is comparable to the Barycentric quadrature rule, the body
-with an initial distance of $h/10$ from the solid wall would require
-$6,400$ discretization points, and the outer wall would require $50,000$
-discretization points.
+$\UU(\xx) = (y+1,0)$ imposed on $\Gamma$. \citet{mit-spa2017} performed
+a similar three-dimensional numerical experiment using a second-order
+quadrature method.  Their initial body is a sphere with its center
+located $1.5$ radii above the solid wall.  We initialize the
+two-dimensional eroding body with radius $r = 0.4$, and we conduct
+numerical experiments where the initial distance between the grain and
+the solid wall is $h$, $h/2$, and $h/10$, where $h = 2\upi r/N_\iin$.
+If we used the trapezoid rule and required an error that is comparable
+to the Barycentric quadrature rule, the body with an initial distance of
+$h/10$ from the solid wall would require $6,400$ discretization points,
+and the outer wall would require $50,000$ discretization points.
 
@@
 the spherical body~\citep{cha-feu2003}, but recirculation is possible in
-two dimensions~\citep{chw-wu1975, hig1985}.  To visualize the flow, we
-plot the vorticity of the final time step from figure~\ref{fig:NearWall}
-in figure~\ref{fig:NearWall_vort}.  In these examples, a small
-recirculation zone, both in size and magnitude, is present in the region
-where the vorticity is smallest.
+two dimensions~\citep{chw-wu1975, hig1985}.  To visualize the flow, in
+figure~\ref{fig:NearWall_vort} we plot the logarithm of the absolute
+value of the vorticity from the final time step in
+figure~\ref{fig:NearWall}.  In these examples, a small recirculation
+zone, both in size and magnitude, is present in the region where the
+vorticity is smallest.
 
@@
 \begin{center}
-\begin{subfigure}[b]{0.32\textwidth}
-\includegraphics[height = 0.74\textwidth]{./figs/1b_0d4r1h_shear}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.32\textwidth}
-\includegraphics[height = 0.74\textwidth]{./figs/1b_0d4r0d5h_shear}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.32\textwidth}
-\includegraphics[height = 0.74\textwidth]{./figs/1b_0d4r0d1h_shear}
+\begin{subfigure}[b]{0.27\textwidth}
+\includegraphics[height = \textwidth]{./figs/1b_0d4r1h_shear}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.27\textwidth}
+\includegraphics[height = \textwidth]{./figs/1b_0d4r0d5h_shear}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.27\textwidth}
+\includegraphics[height = \textwidth]{./figs/1b_0d4r0d1h_shear}
 \caption{}
@@
 \end{subfigure}
-\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a
-single body eroding at time $t=0.1$. The initial distance from the body
-to the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
+\caption{\label{fig:NearWall_vort} The eroded bodies from
+figure~\ref{fig:NearWall} at time $t=0.1$. The color is the logarithm of
+the magnitude of the vorticity. The initial distances from the body to
+the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider 20 eroding grains with the Hagen-Poiseuille flow $\UU(\xx) =
-U \left(1-y^2,0 \right)$
-%\begin{align}
-%  \UU(\xx)=U \left[
-%  \begin{array}{c}
-%    1-y^2 \\ 0
-%  \end{array}
-%  \right],
-%\end{align}
-imposed on $\Gamma$. The flow rate $U$ is chosen so that the average
-pressure drop from $x=-2$ to $x=2$ is held fixed at 8. Therefore, $U=1$
-once all the grains have vanished.  The vorticity and grain
-configuration at four equispaced times are shown in
+We randomly initialize 20 eroding grains with an initial porosity of
+$\phi = 37.68\%$ and the Hagen-Poiseuille flow $\UU(\xx) = U
+\left(1-y^2,0 \right)$ imposed on $\Gamma$. The flow rate $U$ is chosen
+so that the average pressure drop from $x=-2$ to $x=2$ is held fixed at
+8. Therefore, $U=1$ once all the grains have vanished.  The vorticity
+and grain configuration at four equispaced times are shown in
 figure~\ref{fig:Eroding20vort}.  Initially, several of the grains are
@@
 Erosion causes the some of the pore sizes to quickly grow, and flat
-faces develop along the regions of near contact.  This qualitative
+faces develop along the regions of near-contact.  This qualitative
 behavior is seen in figure~\ref{fig:Eroding20vort} between bodies 3 \&
@@
 
-We next analyze the effect of erosion on the area fraction and the flow
-rate.  In figure~\ref{fig:Eroding20flowrate}(a), we plot the area
-fraction as a function of normalized time.  The general trend of the
-area fraction resembles our previous work~\citep[see][figure
+In our previous work~\citep{qua-moo2018}, we investigated the effects
+of erosion on the area fraction and flow rate of two different
+geometries.  Here, we do the same analysis, but with the denser packing
+of the grains. In figure~\ref{fig:Eroding20flowrate}(a), we plot the
+area fraction as a function of normalized time.  The general trend of
+the area fraction resembles our previous work~\citep[see][figure
 10(a)]{qua-moo2018}, but with a larger initial area fraction.  In
@@
 that the flow rate can be written as an exponential law.  The line of
-best fit is $U \approx \exp(9.94(t-t_f)/t_f)$
-%\begin{align}
-%  U \approx \exp\left(9.94 \left(\frac{t - t_f}{t_f} \right)\right),
-%\end{align}
-which is the dashed line in figure~\ref{fig:Eroding20flowrate}(b).
-
+best fit is $U \approx \exp(9.94(t-t_f)/t_f)$ which is the dashed line
+in figure~\ref{fig:Eroding20flowrate}(b).
 \begin{figure}
@@
 \includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270n_zoom}
-\caption{\label{fig:Eroding20tracer} 200 streamlines in the second
-geometry from figure~\ref{fig:Eroding20vort}. The streamlines are
+\caption{\label{fig:Eroding20tracer} 200 particle trajectories in the
+second geometry from figure~\ref{fig:Eroding20vort}. The particles are
 initially equispaced at $(-1,y)$, where $y \in (-1,1)$. The first five
 snapshots are equispaced in time.  The bottom right frame is a
-magnification of the fifth snapshot, but with additional streamlines.}
+magnification of the fifth snapshot, but with additional trajectories.}
 \end{center}
@@
 vorticity, and therefore erosion rate, are much larger relative to other
-regions.  These channels can be further visualized  with the
-streamlines.  In figure~\ref{fig:Eroding20tracer}, we freeze the
-geometry at the second snapshot from figure~\ref{fig:Eroding20vort} and
-plot 200 streamlines that are initially equispaced along $(-1,y)$, where
-$y \in (-1,1)$.  The streamlines are shown at five different times, and
-the final plot is a zoom in of the lower right quadrant of the fifth
-time step, but with additional streamlines.  Since we use a high-order
-quadrature rule and time stepping method, we resolve streamlines that
-come very close to the eroded bodies.  There are three clear regions
-where the streamlines are most concentrated, corresponding to the
-regions of highest velocity.  Two of these regions are located between
-the bodies and the solid walls at $y=\pm 1$, and the third cuts through
-the porous region with the upper part of the channel formed by bodies 1,
-4, 6, and 8.  Since the flow is fastest in these regions, the shearing
-is largest, and this causes the channels to continue to open fastest as
-observed in figure~\ref{fig:Eroding20vort}.
+regions.  These channels can be further visualized with particle
+trajectories that are trace out the streamlines.  In
+figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
+snapshot from figure~\ref{fig:Eroding20vort} and plot 200 trajectories
+that are initially equispaced along $(-1,y)$, where $y \in (-1,1)$.  The
+trajectories are shown at five different times, and the final plot is a
+zoom in of the lower right quadrant of the fifth time step, but with
+additional trajectories.  Since we use a high-order quadrature rule and
+time stepping method, we resolve the dynamics very close to the eroded
+bodies.  There are three clear regions where the streamlines are most
+concentrated, corresponding to the regions of highest velocity.  Two of
+these regions are located between the bodies and the solid walls at
+$y=\pm 1$, and the third cuts through the porous region with the upper
+part of the channel formed by bodies 1, 4, 6, and 8.  Since the flow is
+fastest in these regions, the shearing is largest, and this causes the
+channels to continue to open fastest as observed in
+figure~\ref{fig:Eroding20vort}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider a second example with 20 eroding bodies, but with a smaller
-initial porosity.  In figure~\ref{fig:ErodingLow20vort}, we plot the
-eroding geometry and vorticity at four evenly spaced instances in time.
-Initially, the smallest distance between pairs of bodies is $3.29 \times
-10^{-4}$, and the smallest distance between the bodies and solid wall is
-$4.50 \times 10^{-3}$.  At these distances, a resolution of
-approximately $N_\iin = 27,000$ and $N_\out = 18,000$ discretization
-points is required to satisfy the $5h$ threshold needed for the
-trapezoid rule to achieve machine precision.
+We consider a second example with of 20 randomly initialized eroding
+bodies, but with a smaller initial porosity of $\phi = 30.67\%$.  In
+figure~\ref{fig:ErodingLow20vort}, we plot the eroding geometry and
+vorticity at four evenly spaced instances in time.  Initially, the
+smallest distance between pairs of bodies is $3.29 \times 10^{-4}$, and
+the smallest distance between the bodies and solid wall is $4.50 \times
+10^{-3}$.  At these distances, a resolution of approximately $N_\iin =
+27,000$ and $N_\out = 18,000$ discretization points is required to
+satisfy the $5h$ threshold needed for the trapezoid rule to achieve
+machine precision.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-As a final example, we consider 100 eroding bodies with an initial
-porosity near 50\%.  Snapshots of the configurations and vorticity are
-in figure~\ref{fig:Eroding100vort}. We compute the tortuosity using both
-the Lagrangian~\eqref{eqn:tortuosity1} and Eulerian
-methods~\eqref{eqn:tortuosity2}. Therefore, we compute and plot the
-normalized velocity at $N_p = 1000$ points along the inlet $x=-1$ in
+As a final example, we consider 100 randomly initialized eroding bodies
+with an initial porosity near $50\%$.  Snapshots of the configurations
+and vorticity are in figure~\ref{fig:Eroding100vort}. We compute the
+tortuosity using both the Lagrangian~\eqref{eqn:tortuosity1} and
+Eulerian methods~\eqref{eqn:tortuosity2}. Therefore, we compute and plot
+the normalized velocity at $N_p = 1000$ points along the inlet $x=-1$ in
 figure~\ref{fig:Eroding100tort}(a) for the eroded geometry at porosity
@@
 \begin{figure}
-%<<<<<<< HEAD
-%\begin{subfigure}[b]{0.5\textwidth}
 \includegraphics[height =0.227\linewidth]{./figs/100b_50}
-%\caption{100 bodies, $\phi = 55.54\%$}
-%\end{subfigure}%
-%\begin{subfigure}[b]{0.5\textwidth}
 \includegraphics[height =0.227\linewidth]{./figs/100b_100}
-%\caption{99 bodies, $\phi = 62.98\%$}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.5\textwidth}
 \includegraphics[height =0.227\linewidth]{./figs/100b_150}
-%\caption{94 bodies, $\phi = 72.22\%$}
-%\end{subfigure}%
-%\begin{subfigure}[b]{0.5\textwidth}
 \includegraphics[height =0.227\linewidth]{./figs/100b_200}
-%\caption{82 bodies, $\phi = 83.67\%$}
-%\end{subfigure}
 \caption{\label{fig:Eroding100vort} The erosion of 100 nearly touching
@@
 the outlet.}
-%=======
-%\begin{center}
-%  \includegraphics[height=0.227\textwidth]{./figs/100b_50}
-%  \includegraphics[height=0.227\textwidth, trim=0cm 0cm 2.8cm 0cm, clip=true]
-%    {./figs/100b_100}
-%  \includegraphics[height=0.227\textwidth]{./figs/100b_150}
-%  \includegraphics[height=0.227\textwidth]{./figs/100b_200}
-%\end{center}
-%\caption{\label{fig:Eroding100vort} 100 bodies eroding in a
-%Hagen-Poiseuille flow. The four snapshots are equispaced in time, and
-%the color is the fluid vorticity.  Erosion creates many channels
-%connecting the inlet to the outlet.}
-%>>>>>>> 90934916f4dbe677f0ad6f05331ec1c3515ddab7
 \end{figure}
-
-%\begin{figure}
-%\begin{subfigure}[b]{0.5\textwidth}
-%\includegraphics*[height =0.8\linewidth]{./figs/100b_50}
-%\caption{100 bodies, $\phi = 55.54\%$}
-%\end{subfigure}%
-%\begin{subfigure}[b]{0.5\textwidth}
-%\includegraphics*[height =0.8\linewidth]{./figs/100b_100}
-%\caption{99 bodies, $\phi = 62.98\%$}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.5\textwidth}
-%\includegraphics*[height =0.8\linewidth]{./figs/100b_150}
-%\caption{94 bodies, $\phi = 72.22\%$}
-%\end{subfigure}%
-%\begin{subfigure}[b]{0.5\textwidth}
-%\includegraphics*[height =0.8\linewidth]{./figs/100b_200}
-%\caption{82 bodies, $\phi = 83.67\%$}
-%\end{subfigure}
-%\caption{\label{fig:Eroding100vort} 100 bodies eroding in a
-%Hagen-Poiseuille flow. The four snapshots are equispaced in time, and
-%the color is the fluid vorticity.  Erosion creates many channels
-%connecting the inlet to the outlet.}
-%\end{figure}
 
@@
 To further our understanding of erosion, we are examining other bulk and
-statistical properties of an eroding porous media. In this work, we
-provide results for the pore throat sizes which affect the anomalous
-dispersion rate~\citep{dea-qua-bir-jua2018}.  At a later date, we will
-report results on the  development of anisotropic effects and the
-distributions of grain sizes, shapes, and opening angles.
+statistical properties of eroding porous media. In this work, we provide
+results for the pore throat sizes which affect the anomalous dispersion
+rate~\citep{dea-qua-bir-jua2018}.  At a later date, we will report
+results on the  development of anisotropic effects and the distributions
+of grain sizes, shapes, and opening angles.
 
@@
 \end{document}
-
-% OUTDATED STUFF
-%Examples of coarse-grained models for porous media flow include
-%pressure-saturation-permeability
-%relationships~\citep{mil-chr-imh-mcb-ped1998}, permeability-porosity
-%relationships~\citep{dar-mcc1998, car1937, won-kop-tom1984}, first
-%passage time distributions~\citep{ber-sch-sil2000, hym-den-hag-kan2019,
-%cve-che-wen1996}, tortuosities~\citep{hak-com-den2019, mat-kha-koz2008,
-%dud-koz-mat2011, kop-kat-tim1996}, concentration
-%distributions~\citep{ica-den2019, bel-sal-rin1992}, pore and flow
-%distributions~\citep{ali-par-wei-bre2017}, geometry
-%connectivity~\citep{knu-car2005, wes-blo-gra2001}, anomalous
-%dispersion~\citep{dea-qua-bir-jua2018, den-cor-sch-ber2004,
-%sie-ili-pri-riv-gua2019}, and more.
-
-%A variety of numerical methods for the fluid solver are available
-%including lattice-gas or lattice Boltzmann~\citep{kop-kat-tim1996,
-%dar-mcc1998}, finite volumes~\citep{suo-liu-gan2019, den-ica-hid2018,
-%sie-ili-pri-riv-gua2019}, finite
-%differences~\citep{leb-ded-dav-bou2007, knu-car2005}, and cellular
-%automata~\citep{rot1988}.
-
-%We note that an alternative approach to
-%compute trajectories is to form a distribution of velocities $\uu$ and
-%use a continuous time random walk~\citep{mon-wei1965,
-%den-cor-sch-ber2004, leb-den-car2008, ber-cor-den-sch2006}.
-
-%we are able to compute, for $\xx \in \Omega$, the deformation tensor,
-%pressure, and vorticity.
-%defined respectively as
-%\begin{align}
-%  \label{eqn:deformationDLP} 
-%  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
-%      \eeta(\yy) ds_{\yy} 
-%  = \frac{1}{2\upi}\int_{\bd\Omega} \left(
-%    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
-%    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
-%    \right. \nonumber \\
-%    & \qquad\qquad\qquad\qquad \left.
-%    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
-%    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
-%    \right) \, ds_\yy, \\
-%%
-%  \label{eqn:pressureDLP}
-%  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
-%      \eeta(\yy) ds_{\yy} 
-%  = -\frac{1}{\upi}\int_{\bd\Omega} \frac{1}{\rho^2}
-%    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
-%      \eeta(\yy)\,ds_\yy, \\
-%%
-%  \label{eqn:vorticityDLP} 
-%  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
-%      \eeta(\yy) ds_{\yy} 
-%  = -\frac{1}{\upi} \int_{\bd\Omega}
-%    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
-%      (\rr \cdot \eeta) \, ds_\yy.
-%\end{align}
-%Since the deformation tensor of the double-layer potential is
-%discontinuous across $\bd\Omega$, the jump term 
-%added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
-%Stokeslets and rotlets do not exhibit any jumps across $\gamma$, so the
-%associated components of the deformation tensor, pressure, and vorticity
-%are straightforward to compute~\citep{poz1992}.  Having computed the
-%deformation tensor on $\gamma$, the shear stress is computed using
-%equation~\eqref{eqn:shearStress}.
-
-%\begin{align}
-%  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\upi} \left( 
-%    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2}
-%    \right)\llambda_\ell, \quad
-%  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
-%  \quad \ell=1,\ldots,M,
-%\end{align}
-%where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
-%$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
-%\|\rr\|$.

### 2020-01-02 docs/transport/Response_to_Reviewer_1.tex
working on revisions

@@
 \begin{itemize}
-  \item response
+  \item Leading up to equation (5.9) and (5.10), we removed all
+    instances where we had previously claimed these quadrature rules
+    were in Barycentric form.
+
+  \item After equation (5.10), we now state:
+    \begin{quotation}
+      \noindent
+      Note that $v(x)$ is required to compute $v'(x)$ for both the
+      interior and exterior case, and this is available using the
+      Barycentric quadrature rules (5.6) and (5.7). As pointed out by
+      Barnett {\em et al.}~(2015), equations (5.9) and (5.10) are not in
+      a Barycentric form since the numerators suffer from catastrophic
+      cancellation as $x$ approaches $\partial\Omega$. The result is
+      that the quadrature error is not uniformly bounded. However, since
+      these errors are sufficiently small for the geometries and
+      resolutions we consider, we use these quadrature formulas
+      nonetheless. We note that the quadrature formulas can be put into
+      true Barycentric form (Barnett {\em et al.}~2015, see equations
+      (3.11) and (3.13)), but this increases the complexity for
+      evaluating $v'(x)$ to $O(N^2)$ operations. 
+    \end{quotation}
+
 \end{itemize}
@@
 \begin{itemize}
-  \item response
+  \item Leading up to equation (5.15) and (5.18), we removed all
+    instances where we had previously claimed these quadrature rules
+    were in Barycentric form.
+
+  \item We have also updated the text so that it does not give the
+    impression that the error is uniformly bounded. However, for the
+    geometries and resolutions we consider, we found that the
+    non-Barycentric form quadrature rules are accurate enough to compute
+    the necessary quantities at the target points that are required to
+    perform the subsequent analysis in the paper.
+
+  \item After equation (5.18), we now state:
+    \begin{quotation}
+      \noindent
+      These quadrature formula are also not in a Barycentric form
+      because of catastrophic cancellation in the numerator. As is the
+      case when computing $v′(x)$, this error is sufficiently small at
+      the geometries and resolutions we consider, so we use these
+      quadrature formulas.
+    \end{quotation}
+
+  \item To make it clear which quadrature methods we apply, we have
+    added the following paragraph to the end of Section 5.2:
+    \begin{quotation}
+      \noindent
+      In section 6, the quadrature rules (5.6), (5.7), (5.9), (5.10),
+      (5.15), and (5.18) are used to form simulations of nearly-touching
+      eroding grains, and to study dynamics of the flow in regions
+      arbitrarily close to eroding grains.
+    \end{quotation}
+
+  \item In the second paragraph of Section 5.2, we updated the last
+    sentence to read:
+    \begin{quotation}
+      \noindent
+      After briefly summarizing this method, we compute the second
+      derivative so that the shear stress and vorticity can be
+      accurately computed.
+    \end{quotation}
+
+  \item We start Section 5.3 with the following revised sentence:
+    \begin{quotation}
+      \noindent
+      By using these quadrature rules, the velocity, shear stress, and
+      vorticity are calculated at the target points necessary to
+      simulate erosion and transport.
+    \end{quotation}
+
 \end{itemize}
@@
 \begin{itemize}
-  \item response
+  \item We have toned down some of the claims. The following modified
+    paragraphs and sentences are in the revised manuscript:
+    \begin{quotation}
+      \noindent
+      In previous work (Quaife \& Moore 2018), the BIE is discretized
+      with the trapezoid rule, and this is acceptable if the grains that
+      are sufficiently separated (Trefethen \& Weideman 2014). However,
+      when grains are close, the result is a nearly-singular integrand
+      and the error of the trapezoid rule is no longer acceptable. One
+      of the earliest quadrature methods for nearly-singular integrands
+      was developed by Baker \& Shelley (1986), and in recent years,
+      many other schemes have followed (af Klinteberg \& Tornberg 2018;
+      Helsing \& Ojala 2008; Beale {\em et al.}~2016; Beale \& Lai 2001;
+      Kl\"{o}ckner {\em et al.}~2013). We use a Barycentric quadrature
+      method (Barnett 2014; Barnett {\em et al.}~2015) since it is a
+      non-intrusive modification of the trapezoid rule, and the error is
+      guaranteed to be uniformly bounded. We use this quadrature method
+      to compute the velocity gradient, which is needed to evaluate the
+      shear stress and the fluid vorticity.
+    \end{quotation}
+
+    \begin{quotation}
+      \noindent
+      Section 5 describes the numerical methods, with special attention
+      paid to the quadrature method for computing the shear stress and
+      the vorticity.
+    \end{quotation}
+
+    \begin{quotation}
+      \noindent
+      As a continuation of our previous work (Quaife \& Moore 2018), we
+      have simulated dense suspensions and characterized transport in
+      viscous eroding porous media. This is accomplished by using
+      high-order time stepping methods and a combination of trapezoid
+      and Barycentric quadrature methods to solve a BIE formulation of
+      the Stokes equations. By using these numerical methods, we are
+      able to perform stable simulations of erosion with $N = O(100)$
+      discretization points, while the trapezoid rule would require
+      $O(10^5)$ discretization points.
+    \end{quotation}
 \end{itemize}
@@
 \begin{itemize}
-  \item response
+  \item We have adjusted each of the appropriate sections.
+
+  \item In Section 6.2, we have added the following sentence:
+    \begin{quotation}
+      \noindent
+      A slightly larger root-mean-square error of $6.70 \times 10^{-3}$
+      is possible with the logarithmic porosity-tortuosity model (4.6b),
+      but the other two models have a root- mean-square error that is an
+      order of magnitude larger.
+    \end{quotation}
+
+  \item In Section 6.3, we have added the following sentence:
+    \begin{quotation}
+      \noindent
+      However, the root-mean-square error of the other three models is
+      bounded by $2.38 \times 10^{-2}$.
+    \end{quotation}
+
+  \item In Section 6.4, we have added the following sentence:
+    \begin{quotation}
+      \noindent
+      We also compute the lines of best fit using the
+      porosity-tortuosity models (4.6).  Each of the models result in a
+      root-mean-squared error ranging from $4.60 \times 10^{-3}$ for
+      model (4.6c) to $7.20 \times 10^{-3}$ for model (4.6c). The black
+      dashed line in figure 15(a) is the line of best fit
+      $\widehat{T}(\phi) = \phi^{-0.2459}$, with a root-mean-square
+      error of $5.50 \times 10^{-3}$.  We note a slightly better
+      root-mean-square error of $4.60 \times 10^{-3}$ is possible with
+      the model $\widehat{T}(\phi) = \left(1 + 0.1499(1-\phi)\right)^2$.
+    \end{quotation}
+
 \end{itemize}
@@
     Examples of coarse-grained models for porous media flow include
-    tortuosities (Matyka et al.~2008; Duda et al.~2011; Koponen et
-    al.~1996), geometry connectivity (Knudby \& Carrera 2005), anomalous
-    dispersion (Dentz et al.~ 2004), and permeability-porosity
-    relationships (Dardis \& McCloskey 1998; Carman 1937), where the
-    porosity is the fraction of the geometry that is fluidized.
+    tortuosities (Matyka {\em et al.}~2008; Duda {\em et al.}~2011;
+    Koponen {\em et al.}~1996), geometry connectivity (Knudby \& Carrera
+    2005), anomalous dispersion (Dentz {\em et al.}~2004), and
+    permeability-porosity relationships (Dardis \& McCloskey 1998;
+    Carman 1937), where the porosity is the fraction of the geometry
+    that is fluidized.
   \end{quotation}

### 2020-01-02 docs/transport/Response_to_Reviewer_2.tex
working on revisions

@@
     performing an `experiment'. We have clarified each of the instances
-    by referring them as a `numerical experiment'.
+    by referring to them as a `numerical experiment'.
 \end{itemize}
@@
       Having only finite local tortuosities, the hydraulic tortuosity is
-      defined by taking the average over all points on the inlet cross-
-      section
+      defined by taking the average over all points on the inlet
+      cross-section
     \end{quotation}

### 2020-01-02 docs/transport/Response_to_Reviewer_3.tex
working on revisions

@@
 
-  \item Others have developed three-dimensional numerical methods for
-    removing stiffness in interfacial flow ($\theta-L$ formulation),
-    spectrally representing geometries, and efficiently solving BIEs.
-    The challenge with these methods is their computational cost. To
-    consider suspensions with the resolution and number of grains that
-    we consider, the BIE would most likely require a parallel
+  \item In three-dimensions, others have extended the $\theta-L$
+    formulation to remove stiffness in interfacial flow, spectrally
+    represented geometries, and efficiently solving BIEs.  The challenge
+    with these methods is their computational cost. To consider
+    suspensions with the resolution and number of grains that we
+    consider, the BIE would most likely require a parallel
     implementation that would run on high-performance computing
     architectures. At this point, this is not the goal of our work.
+    Rather, we are interested in using very high-order methods to
+    provide an analysis of the effects of erosion on transport which
+    seems to be missing from the literature.
 
@@
     other quadrature methods that can be applied in three dimensions,
-    but they are also computationally expensive.
+    but they are also computationally expensive. For example, if the
+    geometry is represented with spherical harmonics, a
+    Gaussian-Legendre quadrature method requires $\mathcal{O}(p^3)$
+    operations, where $p$ is the highest-order spherical harmonic.
 
@@
       \noindent
-      While natural porous media are three-dimensional, there are
-      several challenges that must be overcome to extend our high-order
-      methods to three dimensions.  A three-dimensional version of a
-      {$\theta-L$} formulation exists (Ambrose {\em et al.} 2013), but
-      the Barycentric quadrature method relies upon a complex variable
-      formulation of the BIE, making it inherently two-dimensional.
-      Therefore, a different quadrature method is required. Additional
-      challenges of three-dimensional simulations include spectral
-      representations of the geometry and efficiently solving
+      Since high-order methods have never been used to study transport
+      in eroding porous media, we consider, as a first step,
+      two-dimensional and immobile grains. These assumptions allow us to
+      simulate large densely-packed suspensions (up to $100$ in this
+      manuscript), and to clearly interpret the results. More realistic
+      three-dimensional and mobile configurations would require
+      overcoming a few challenges. First, a three-dimensional extension
+      of the $\theta-L$ formulation exists (Ambrose {\em et al.}~2013),
+      but the Barycentric quadrature method used here relies on a
+      complex variable formulation of the BIE, making it inherently two-
+      dimensional. Therefore, a different quadrature method would be
+      required. Additional challenges include spectral representations
+      of three-dimensional geometries and efficiently solving
       discretizations of the BIE. While high-order methods for
@@
       cost limits the number of bodies that can be practically
-      simulated. Another limitation of this work is the assumption of
-      immobile grains.  Mechanisms such as sedimentation play a role in
-      real applications, and this will effect the transport properties.
-      Simulating mobile grains introduces the additional challenge of
-      resolving contact.  Since high-order methods have never been used
-      to study transport in eroded porous media, as a first step we
-      consider the case  with two-dimensional immobile grains. This
-      assumption allows for a clear interpretation of the results.  For
-      example, in this work we are able to simulate a large
-      densely-packed suspension (up to $100$ in this manuscript).
-
+      simulated. Lastly, mechanisms such as sedimentation play a role in
+      realistic media and affect the pore structure. Simulating mobile
+      grains introduces the additional challenge of resolving contact,
+      which we plan to address in future work.
     \end{quotation}

### 2020-01-02 docs/transport/erosion_transport.tex
working on revisions

@@
 second-order Runge-Kutta method applied to the {\thL}
-coordinates~\citep{hou-low-she1994} of the eroding grains.  In this
-work, we introduce a new quadrature method to resolve dense suspensions.
-The accuracy of the trapezoid rule, which was used in previous work, is
-adequate for bodies that are sufficiently separated~\citep{tre-wei2014},
-but not for grains in close contact.  One of the earliest quadrature
-methods for nearly-singular integrands was developed
-by~\citet{bak-she1986}, and in recent years, many other schemes have
-followed~\citep{kli-tor2018, hel-oja2008a, bea-yin-wil2016, bea-lai2001,
-klo-bar-gre-one2013}.  We use a Barycentric quadrature
-method~\citep{bar2014, bar-wu-vee2015} since it is a non-intrusive
-modification of the trapezoid rule, and the error is guaranteed to be
-uniformly bounded.  We extend the original quadrature method to compute
-the velocity gradient, which is needed to evaluate the shear stress and
-the fluid vorticity.
-
-While natural porous media are three-dimensional, there are several
-challenges that must be overcome to extend our high-order methods to
-three dimensions.  A three-dimensional version of a {\thL} formulation
+coordinates~\citep{hou-low-she1994} of the eroding grains. In previous
+work~\citep{qua-moo2018}, the BIE is discretized with the trapezoid
+rule, and this is acceptable if the grains that are sufficiently
+separated~\citep{tre-wei2014}. However, when grains are close, the
+result is a nearly-singular integrand and the error of the trapezoid
+rule is no longer acceptable. One of the earliest quadrature methods for
+nearly-singular integrands was developed by~\citet{bak-she1986}, and in
+recent years, many other schemes have followed~\citep{kli-tor2018,
+hel-oja2008a, bea-yin-wil2016, bea-lai2001, klo-bar-gre-one2013}.  We
+use a Barycentric quadrature method~\citep{bar2014, bar-wu-vee2015}
+since it is a non-intrusive modification of the trapezoid rule, and the
+error is guaranteed to be uniformly bounded.  We use this quadrature
+method to compute the velocity gradient, which is needed to evaluate the
+shear stress and the fluid vorticity.
+
+Since high-order methods have never been used to study transport in
+eroding porous media, we consider, as a first step, two-dimensional and
+immobile grains. These assumptions allow us to simulate large
+densely-packed suspensions (up to $100$ in this manuscript), and to
+clearly interpret the results. More realistic three-dimensional and
+mobile configurations would require overcoming a few challenges. First,
+a three-dimensional extension of the {\thL} formulation
 exists~\citep{amb-sie-tlu2013}, but the Barycentric quadrature method
-relies upon a complex variable formulation of the BIE, making it
-inherently two-dimensional. Therefore, a different quadrature method is
-required. Additional challenges of three-dimensional simulations include
-spectral representations of the geometry and efficiently solving
+used here relies on a complex variable formulation of the BIE, making it
+inherently two-dimensional. Therefore, a different quadrature method
+would be required. Additional challenges include spectral
+representations of three-dimensional geometries and efficiently solving
 discretizations of the BIE. While high-order methods for
 three-dimensional BIEs have been developed, their computational cost
-limits the number of bodies that can be practically simulated. Another
-limitation of this work is the assumption of immobile grains.
-Mechanisms such as sedimentation play a role in real applications, and
-this will effect the transport properties. Simulating mobile grains
-introduces the additional challenge of resolving contact.  Since
-high-order methods have never been used to study transport in eroded
-porous media, as a first step we consider the case  with two-dimensional
-immobile grains. This assumption allows for a clear interpretation of
-the results.  For example, in this work we are able to simulate a large
-densely-packed suspension (up to $100$ in this manuscript).
+limits the number of bodies that can be practically simulated.  Lastly,
+mechanisms such as sedimentation play a role in realistic media and
+affect the pore structure. Simulating mobile grains introduces the
+additional challenge of resolving contact, which we plan to address in
+future work.
 
@@
 characterizing the geometry and transport. Section~\ref{sec:method}
-describes the numerical methods, with special attention paid to the new
+describes the numerical methods, with special attention paid to the
 quadrature method for computing the shear stress and the vorticity.
@@
 There have been efforts to relate the tortuosity, $T$, to the porosity,
-$\phi$.  For example,~\citet{mat-kha-koz2008} propose the
-models
+$\phi$.  For example,~\citet{mat-kha-koz2008} propose the models
 \begin{subequations}
@@
   \begin{align}
+    \label{eqn:tortuosityModels1}
     \widehat{T}(\phi) &= \phi^{-p}, \\
+    \label{eqn:tortuosityModels2}
     \widehat{T}(\phi) &= 1-p \log \phi, \\
+    \label{eqn:tortuosityModels3}
     \widehat{T}(\phi) &= 1+p (1-\phi), \\
+    \label{eqn:tortuosityModels4}
     \widehat{T}(\phi) &= (1+p (1-\phi))^2, 
@@
 potential is evaluated at a point close to $\bd\Omega$, then the result
-become unreliable and the simulation ultimately becomes unstable.  We
+becomes unreliable and the simulation ultimately becomes unstable.  We
 thus desire a quadrature method whose error bound does not depend on the
@@
 representation of the velocity~\eqref{eqn:velocityDLP}. After briefly
-summarizing this method, we extend the work to compute the second
-derivative so that the shear stress and vorticity can be computed with a
-uniform error bound.
+summarizing this method, we compute the second derivative so that the
+shear stress and vorticity can be accurately computed.
 
@@
 applying the trapezoid rule and rearranging for $v'(x)$, we have the
-interior Barycentric quadrature rule
+interior quadrature rule
 \begin{align}
@@
 \end{align}
-Using a similar construction, the exterior Barycentric quadrature rule
-for the first derivative is
+Using a similar construction, an exterior quadrature rule for the first
+derivative is
 \begin{align}
@@
 quadrature rules~\eqref{eqn:BaryvInterior}
-and~\eqref{eqn:BaryvExterior}.
-
-To compute the shear stress and vorticity, we require a Barycentric
-quadrature rule for $v''(x)$.  The derivation is largely based on the
-work of~\citet[see equation (2.12)]{ioa-pap-per1991}.  We start with
-the second derivative of the Cauchy integral theorem
+and~\eqref{eqn:BaryvExterior}. As pointed out by~\citet{bar-wu-vee2015},
+equations~\eqref{eqn:BaryvprimeInterior}
+and~\eqref{eqn:BaryvprimeExterior} are not in a Barycentric form since
+the numerators suffer from catastrophic cancellation as $x$ approaches
+$\bd\Omega$. The result is that the quadrature error is not uniformly
+bounded. However, since these errors are sufficiently small for the
+geometries and resolutions we consider, we use these quadrature formulas
+nonetheless. We note that the quadrature formulas can be put into true
+Barycentric form~\citep[see equations (3.11) and
+(3.13)]{bar-wu-vee2015}, but this increases the complexity for
+evaluating $v'(x)$ to $O(N^2)$ operations.
+
+To compute the shear stress and vorticity, we require a quadrature rule
+for $v''(x)$.  The derivation is largely based on the work of~\citet[see
+equation (2.12)]{ioa-pap-per1991}.  We start with the second derivative
+of the Cauchy integral theorem
 \begin{align}
@@
 where the accuracy is independent of $x$.  Solving for $v''(x)$, the
-Barycentric quadrature rule for the interior second derivative at $x \in
+quadrature rule for the interior second derivative at $x \in
 \Omega$ is
@@
     \left(\sum_{j=1}^N \frac{1}{y_j-x}w_j\right).
+    \label{eqn:Baryvprime2Interior}
 \end{align}
@@
 for all $x \in \Omega^c$.  Therefore, after applying the trapezoid rule
-and solving for $v''(x)$, we have the Barycentric quadrature rule for
-the exterior second derivative at $x \in \Omega^c$
+and solving for $v''(x)$, we have the quadrature rule for the exterior
+second derivative at $x \in \Omega^c$
 \begin{align}
@@
     \left(\sum_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j\right).
-\end{align}
-The quadrature rule for $v''(x)$ requires $v(x)$ and $v'(x)$, and theses
+    \label{eqn:Baryvprime2Exterior}
+\end{align}
+The quadrature rule for $v''(x)$ requires $v(x)$ and $v'(x)$, and these
 are computed using the quadrature rules in
 equations~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},
-and~\eqref{eqn:BaryvprimeExterior}. In section~\ref{sec:results}, these
-quadrature rules are used to form simulations of nearly-touching eroding
-grains, and to study dynamics of the flow in regions arbitrarily close
-to eroding grains.
+and~\eqref{eqn:BaryvprimeExterior}. These quadrature formula are also
+not in a Barycentric form because of catastrophic cancellation in the
+numerator. As is the case when computing $v'(x)$, this error is
+sufficiently small at the geometries and resolutions we consider, so we
+use these quadrature formulas.
+
+In section~\ref{sec:results}, the quadrature
+rules~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},~\eqref{eqn:BaryvprimeExterior},~\eqref{eqn:Baryvprime2Interior},
+and~\eqref{eqn:Baryvprime2Exterior} are used to form simulations of
+nearly-touching eroding grains, and to study dynamics of the flow in
+regions arbitrarily close to eroding grains.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-By using the Barycentric quadrature rule, the velocity, shear stress,
-and vorticity are computed with an error that is bounded independent of
-the target location. However, applied directly, it requires
-$O(N^2)$ operations, where $N$ is the total number of source
-and target points.  By using a fast summation method, such as the fast
-multipole method (FMM)~\citep{gre-rok1987}, the cost can be reduced to
-$O(N)$ operations.  However, each application of the Barycentric
-quadrature rules involve several $N$-body calculations, rendering the
-computational cost prohibitive, so we introduce a hybrid method that
-combines the Barycentric quadrature rule and an accelerated trapezoid
-rule.  Note that the source points of the layer potential is always one
-of the eroding bodies or the outer wall, but the target point can either
-be on another component of $\bd\Omega$ or it can be in the fluid bulk
+By using these quadrature rules, the velocity, shear stress, and
+vorticity are calculated at the target points necessary to simulate
+erosion and transport. However, applied directly, it requires $O(N^2)$
+operations, where $N$ is the total number of source and target points.
+By using a fast summation method, such as the fast multipole method
+(FMM)~\citep{gre-rok1987}, the cost can be reduced to $O(N)$ operations.
+However, each application of the Barycentric quadrature rules involve
+several $N$-body calculations, rendering the computational cost
+prohibitive, so we introduce a hybrid method that combines the
+Barycentric quadrature rule and an accelerated trapezoid rule.  Note
+that the source points of the layer potential is always one of the
+eroding bodies or the outer wall, but the target point can either be on
+another component of $\bd\Omega$ or it can be in the fluid bulk
 $\Omega$.
@@
 We computed lines of best fit using the porosity-tortuosity
-models~\eqref{eqn:tortuosityModels} and found that the power law
-minimizes the error.  The  black dashed line in
-figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
-$\widehat{T}(\phi) = \phi^{-0.2064}$ with a root-mean-square error of
-$5.90 \times 10^{-3}$.  Interestingly, at the low porosities, the
+models~\eqref{eqn:tortuosityModels} and the power
+law~\eqref{eqn:tortuosityModels1} minimizes the error.  The  black
+dashed line in figure~\ref{fig:Eroding20Transport}(a) is the line of
+best fit $\widehat{T}(\phi) = \phi^{-0.2064}$ with a root-mean-square
+error of $5.90 \times 10^{-3}$.  A slightly larger root-mean-square
+error of $6.70 \times 10^{-3}$ is possible with the logarithmic
+porosity-tortuosity model~\eqref{eqn:tortuosityModels2}, but the other
+two models have a root-mean-square error that is an order of magnitude
+larger. Interestingly, at the low porosities, the
 tortuosity initially increases. This increase occurs because in the
@@
 equation~\eqref{eqn:tortuosityModels}, and its root-mean-squared error
-is $1.13 \times 10^{-2}$.  As grains erode, there is an increase in the
-number of streamlines that take a nearly direct path through the
-geometry, and this decreases the tortuosity. However, the channelization
-effect of erosion results in an increase in the tortuosity since the
-length of many of the streamlines increases when they deflect from a
-high porosity region (low pressure) to a low porosity region (high
-pressure). For this example, we see that the net effect is a decrease in
-the tortuosity for all time.
+is $1.13 \times 10^{-2}$. However, the root-mean-square error of the
+other three models is bounded by $2.38 \times 10^{-2}$.  As grains
+erode, there is an increase in the number of streamlines that take a
+nearly direct path through the geometry, and this decreases the
+tortuosity. However, the channelization effect of erosion results in an
+increase in the tortuosity since the length of many of the streamlines
+increases when they deflect from a high porosity region (low pressure)
+to a low porosity region (high pressure). For this example, we see that
+the net effect is a decrease in the tortuosity for all time.
 
@@
 fit using the porosity-tortuosity models~\eqref{eqn:tortuosityModels}.
-The black dashed line in figure~\ref{fig:Eroding100Transport}(a) is the
-line of best fit $\widehat{T}(\phi) = \phi^{-0.2459}$, with a
-root-mean-square error of $5.50 \times 10^{-3}$.  We note a slightly
-better root-mean-square error of $5.20 \times 10^{-3}$ is possible with
-the model $\widehat{T}(\phi) = 1 - 0.2631 \ln(\phi)$.
+Each of the models result in a root-mean-squared error ranging from
+$4.60 \times 10^{-3}$ for model~\eqref{eqn:tortuosityModels4} to $7.20
+\times 10^{-3}$ for model~\eqref{eqn:tortuosityModels3}. The black
+dashed line in figure~\ref{fig:Eroding100Transport}(a) is the line of
+best fit $\widehat{T}(\phi) = \phi^{-0.2459}$, with a root-mean-square
+error of $5.50 \times 10^{-3}$.  We note a slightly better
+root-mean-square error of $4.60 \times 10^{-3}$ is possible with the
+model $\widehat{T}(\phi) = \left(1 + 0.1499(1-\phi)\right)^2$.
 
@@
 eroding porous media. This is accomplished by using high-order time
-stepping methods and a new quadrature methods to solve a BIE formulation
-of the Stokes equations.  By using these numerical methods, we are able
-to perform stable simulations of erosion with $N = O(100)$
-discretization points, while the trapezoid rule would require $O(10^5)$
-discretization points.
+stepping methods and a combination of trapezoid and Barycentric
+quadrature methods to solve a BIE formulation of the Stokes equations.
+By using these numerical methods, we are able to perform stable
+simulations of erosion with $N = O(100)$ discretization points, while
+the trapezoid rule would require $O(10^5)$ discretization points.
 

### 2020-01-02 fortran_code/stokesSolver.f

@@ -572,12 +572,9 @@ c     potential
       call cpu_time(t2)
       print *, 'GMRES  time =', t2-t1
 
-
-
       end
 
 c***********************************************************************
-
       subroutine matvec_DLP_fmmbary(ntotal,den,vel,nelt,ia,ja,a,isym)
 c     matrix vector multiplication routine for the double-layer
 c     potential
@@ -691,8 +688,8 @@ c     copy velocity on outer boundary in correct order
       enddo
 c     copy velocity on inner boundaries in correct order
 
-c    START OF REPLACING THE TRAPEZOID RUSELTS BY BARYCENTRIC ONE WHEN
-c    TWO POINTS ARE TOO CLOSED
+c     START OF REPLACING THE TRAPEZOID RESULTS BY BARYCENTRIC ONE WHEN
+c     TWO POINTS ARE TOO CLOSE
 
 
 c     START the wall-bodies section
@@ -702,10 +699,10 @@ c     start the wall-to-bodies part
         deny(k) = den(k + nouter)
       enddo      
 
-      alpha1 = 4.d0! the criterion parameter for B2Bs
-      alpha2 = 4.d0! the criterion parameter for W2Bs
+      alpha1 = 4.d0 ! the criterion parameter for B2Bs
+      alpha2 = 4.d0 ! the criterion parameter for W2Bs
 c     Find the radii of bodies      
-      do itar = 1, nbodies
+      do itar = 1,nbodies
         rtar(itar) = 0.d0
         do k = 1, ninner
           rtar(itar) = rtar(itar) + speed((itar-1)*ninner+k)  
@@ -730,8 +727,8 @@ c       the criterion of W2Bs
         if( abs(centery(itar)) .ge. dsum2) then
 
           do k=1,ninner
-            xtarloc(k)=x((itar-1)*ninner+k)
-            ytarloc(k)=y((itar-1)*ninner+k)
+            xtarloc(k) = x((itar-1)*ninner+k)
+            ytarloc(k) = y((itar-1)*ninner+k)
             denxb(k) = den(2*nouter + (itar-1)*2*ninner + k)
             denyb(k) = den(2*nouter + (itar-1)*2*ninner + k + ninner)
 c           save xtarloc, ytarloc, denxb, and denyb for body-to-wall barycentric           
@@ -5151,7 +5148,6 @@ c     put geometry in complex variables
           endif
[…]

### 2020-01-08 docs/transport/Response_to_Reviewer_1.tex
finished up all but one revision for the transport paper

@@
       By using these quadrature rules, the velocity, shear stress, and
-      vorticity are calculated at the target points necessary to
-      simulate erosion and transport.
+      vorticity are calculated at the target points to simulate erosion
+      and transport.
     \end{quotation}
@@
       In previous work (Quaife \& Moore 2018), the BIE is discretized
-      with the trapezoid rule, and this is acceptable if the grains that
-      are sufficiently separated (Trefethen \& Weideman 2014). However,
-      when grains are close, the result is a nearly-singular integrand
-      and the error of the trapezoid rule is no longer acceptable. One
-      of the earliest quadrature methods for nearly-singular integrands
-      was developed by Baker \& Shelley (1986), and in recent years,
-      many other schemes have followed (af Klinteberg \& Tornberg 2018;
+      with the trapezoid rule, and this is acceptable if the grains are
+      sufficiently separated (Trefethen \& Weideman 2014). However, when
+      grains are close, the result is a nearly-singular integrand and
+      the error of the trapezoid rule is no longer acceptable. One of
+      the earliest quadrature methods for nearly-singular integrands was
+      developed by Baker \& Shelley (1986), and in recent years, many
+      other schemes have followed (af Klinteberg \& Tornberg 2018;
       Helsing \& Ojala 2008; Beale {\em et al.}~2016; Beale \& Lai 2001;
@@
       root-mean-squared error ranging from $4.60 \times 10^{-3}$ for
-      model (4.6c) to $7.20 \times 10^{-3}$ for model (4.6c). The black
+      model (4.6d) to $7.20 \times 10^{-3}$ for model (4.6c). The black
       dashed line in figure 15(a) is the line of best fit
@@
     it could be compared to results from our previous work. The goal is
-    to demonstrate that we now able to resolve smaller area fractions
-    and correspondingly lower flow rates.
+    to demonstrate that we now are able to resolve smaller area
+    fractions and correspondingly lower flow rates.
 

### 2020-01-08 docs/transport/Response_to_Reviewer_2.tex
finished up all but one revision for the transport paper

@@
 \begin{itemize}
-  \item The reinsertion approach we take has been shown to not introduce
-    any significantly artificial decorrelation.
+  \item The reinsertion approach we take has been shown by others to not
+    introduce any significantly artificial decorrelation.
 
@@
       of $\phi = 37.68\%$ and the Hagen-Poiseuille flow
-      $\mathbf{U}(\mathbf{x}) = U (1-y^2, 0)$ imposed on $\Gamma$
+      $\mathbf{U}(\mathbf{x}) = U (1-y^2, 0)$ imposed on $\Gamma$.
     \end{quotation}
@@
       The particles are initially equispaced at $(−1,y)$, where $y \in
-      (−1, 1)$. The first five snapshots are equispaced in time. The
+      (-1, 1)$. The first five snapshots are equispaced in time. The
       bottom right frame is a magnification of the fifth snapshot, but
@@
       tortuosity will be infinite. However, in each of our numerical
-      experiments, all the streamlines connect the inlet to the outlet.
-      Having only finite local tortuosities, the hydraulic tortuosity is
-      defined by taking the average over all points on the inlet
-      cross-section
+      experiments, all the streamlines we consider connect the inlet to
+      the outlet.  Having only finite local tortuosities, the hydraulic
+      tortuosity is defined by taking the average over all points on the
+      inlet cross-section.
     \end{quotation}
@@
 \begin{itemize}
-  \item This typo has been fixed
+  \item This typo has been fixed.
 \end{itemize}

### 2020-01-08 docs/transport/Response_to_Reviewer_3.tex
finished up all but one revision for the transport paper

@@
     three-dimensional erosion, with the most significant being the
-    $\theta-L$ formulation, quadrature method, spectral representation
-    of the geometry, and the boundary integral equation solver.
+    $\theta$--$L$ formulation, quadrature method, spectral
+    representation of the geometry, and the boundary integral equation
+    solver.
 
-  \item In three-dimensions, others have extended the $\theta-L$
+  \item In three-dimensions, others have extended the $\theta$--$L$
     formulation to remove stiffness in interfacial flow, spectrally
@@
 
-  \item Our response to the reviewer's second comment points to a
-    paragraph that has been added to the Introduction.
-
+  \item The manuscript has been modified as discussed in the response to
+    the reviewer's second comment.
 \end{itemize}
@@
   \item We plan to consider mobile bodies in the future, and this will
-    require a significant computational effort.
+    require additional computational effort.
 
@@
       overcoming a few challenges. First, a three-dimensional extension
-      of the $\theta-L$ formulation exists (Ambrose {\em et al.}~2013),
-      but the Barycentric quadrature method used here relies on a
-      complex variable formulation of the BIE, making it inherently two-
-      dimensional. Therefore, a different quadrature method would be
-      required. Additional challenges include spectral representations
-      of three-dimensional geometries and efficiently solving
-      discretizations of the BIE. While high-order methods for
+      of the $\theta$--$L$ formulation exists (Ambrose {\em et
+      al.}~2013), but the Barycentric quadrature method used here relies
+      on a complex variable formulation of the BIE, making it inherently
+      two-dimensional. Therefore, a different quadrature method would
+      be required. Additional challenges include spectral
+      representations of three-dimensional geometries and efficiently
+      solving discretizations of the BIE. While high-order methods for
       three-dimensional BIEs have been developed, their computational

### 2020-01-08 docs/transport/erosion_transport.tex
finished up all but one revision for the transport paper

@@
 work~\citep{qua-moo2018}, the BIE is discretized with the trapezoid
-rule, and this is acceptable if the grains that are sufficiently
+rule, and this is acceptable if the grains are sufficiently
 separated~\citep{tre-wei2014}. However, when grains are close, the
@@
 at $x=1$, so $d=2$.  However, other choices for the terminal point when
-computing the tortuosity are sometime used~\citep{dud-koz-mat2011}.
-We note that if a streamline originates in a recirculation zone, which
-is possible in two dimensions~\citep{hig1985}, then the local tortuosity
+computing the tortuosity are sometime used~\citep{dud-koz-mat2011}.  We
+note that if a streamline originates in a recirculation zone, which is
+possible in two dimensions~\citep{hig1985}, then the local tortuosity
 will be infinite. However, in each of our numerical experiments, all the
-streamlines connect the inlet to the outlet. Having only finite local
-tortuosities, the hydraulic tortuosity is defined by taking the average
-over all points on the inlet cross-section
+streamlines we consider connect the inlet to the outlet. Having only
+finite local tortuosities, the hydraulic tortuosity is defined by taking
+the average over all points on the inlet cross-section
 \begin{align}
@@
 By using these quadrature rules, the velocity, shear stress, and
-vorticity are calculated at the target points necessary to simulate
-erosion and transport. However, applied directly, it requires $O(N^2)$
-operations, where $N$ is the total number of source and target points.
-By using a fast summation method, such as the fast multipole method
+vorticity are calculated at the target points to simulate erosion and
+transport. However, applied directly, it requires $O(N^2)$ operations,
+where $N$ is the total number of source and target points.  By using a
+fast summation method, such as the fast multipole method
 (FMM)~\citep{gre-rok1987}, the cost can be reduced to $O(N)$ operations.

### 2020-01-11 docs/transport/Response_to_Reviewer_1.tex
finished up first round of revisions

@@
 \begin{itemize}
-  \item response
+  \item This was an oversight on our behalf. The jump is actually caused
+    by a small recirculation zone that vanishes when one of the eroding
+    bodies vanishes. As the blue dots correspond to the Eulerian
+    formulation, the sudden vanishing of this recirculation zone leads
+    to a discrepancy between the two methods of calculating the local
+    tortuosity.
+
+  \item  While there is an error, at 7 of the porosity values around the
+    jump in Figure 15a, the relative error between the Eulerian and
+    Lagrangian formulations never exceeds $6 \times 10^{-3}$.
+
+  \item We have updated the explanation to read:
+    \begin{quotation}
+      \noindent
+      While it appears that the tortuosity does increase suddenly near
+      the end of the simulation, this jump is due to a recirculation
+      zone that vanishes as one of the grains completely erodes. This
+      sharp increase is not present when the Lagrangian definition of
+      the tortuosity is used. However, the relative difference between
+      the tortuosities calculated with the Eulerian and Lagrangian
+      formulations is less than $O(10^{-2})$.
+    \end{quotation}
 \end{itemize}

### 2020-01-11 docs/transport/erosion_transport.tex
finished up first round of revisions

@@
 where $\Omega$ is the fluid region between the inlet and outlet
-cross-sections.  Recirculation zones are possible in viscous
-fluids~\citep{hig1985}, but they are very small in the examples we
-consider and have a negligible effect on the tortuosity.  Since
+cross-sections.  Our examples do contain recirculation zones, but they
+are very small and have a negligible effect on the tortuosity.  Since
 equation~\eqref{eqn:tortuosity2} does not require the additional work of
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap} (a) The pore sizes, represented by
-the length of the red line segments, between neighboring grains. Two
-grains are neighbors if they share an edge of the Delanuay triangulation
-with nodes at the center of each eroding grain. (b) The pore sizes of an
-eroded geometry. The black curve is the Weibull distribution with the
-same first two moments as the data.}
-\end{figure}
 While transport in porous media depends on the porosity, it also depends
@@
 investigate the effect of erosion on the pore size distribution.
+\begin{figure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap} (a) The pore sizes, represented by
+the length of the red line segments, between neighboring grains. Two
+grains are neighbors if they share an edge of the Delanuay triangulation
+with nodes at the center of each eroding grain. (b) The pore sizes of an
+eroded geometry. The black curve is the Weibull distribution with the
+same first two moments as the data.}
+\end{figure}
 
@@
 to the porosity of the geometry in figure~\ref{fig:Eroding100tort}(c).
-Again, the two tortuosity formulas give similar results.  For this
-geometry, the tortuosity decreases monotonically at almost all
-porosities.  However, the tortuosity undergoes a sudden increase near
-the end of the simulation, and we have observed this behavior in other
-examples.  The increase is caused by a single small body near the middle
-of the channel being completely eroded.  While this results in
-straighter streamlines, therefore reducing $\lambda$, the horizontal
-flow, $u_1(y)$, increases since there is no longer a no-slip boundary,
-and this increases the tortuosity.  We also compute the lines of best
-fit using the porosity-tortuosity models~\eqref{eqn:tortuosityModels}.
-Each of the models result in a root-mean-squared error ranging from
-$4.60 \times 10^{-3}$ for model~\eqref{eqn:tortuosityModels4} to $7.20
-\times 10^{-3}$ for model~\eqref{eqn:tortuosityModels3}. The black
-dashed line in figure~\ref{fig:Eroding100Transport}(a) is the line of
-best fit $\widehat{T}(\phi) = \phi^{-0.2459}$, with a root-mean-square
-error of $5.50 \times 10^{-3}$.  We note a slightly better
-root-mean-square error of $4.60 \times 10^{-3}$ is possible with the
-model $\widehat{T}(\phi) = \left(1 + 0.1499(1-\phi)\right)^2$.
+Again, the two tortuosity formulas give similar results. While it
+appears that the tortuosity does increase suddenly near the end of the
+simulation, this jump is due to a recirculation zone that vanishes as
+one of the grains completely erodes. This sharp increase is not present
+when the Lagrangian definition of the tortuosity is used. However, the
+relative difference between the tortuosities calculated with the
+Eulerian and Lagrangian formulations is less than $O(10^{-2})$. We also
+compute the lines of best fit using the porosity-tortuosity
+models~\eqref{eqn:tortuosityModels}.  Each of the models result in a
+root-mean-squared error ranging from $4.60 \times 10^{-3}$ for
+model~\eqref{eqn:tortuosityModels4} to $7.20 \times 10^{-3}$ for
+model~\eqref{eqn:tortuosityModels3}. The black dashed line in
+figure~\ref{fig:Eroding100Transport}(a) is the line of best fit
+$\widehat{T}(\phi) = \phi^{-0.2459}$, with a root-mean-square error of
+$5.50 \times 10^{-3}$.  We note a slightly better root-mean-square error
+of $4.60 \times 10^{-3}$ is possible with the model $\widehat{T}(\phi) =
+\left(1 + 0.1499(1-\phi)\right)^2$.
 

### 2020-01-27 docs/transport/Response_to_Reviewer_1.tex
finished up reviews

--- 2020-01-08 docs/transport/Response_to_Reviewer_1.tex
@@
 we believe is a stronger manuscript.  We also note that formatting
-issues were resolved in the bibliography. An itemized list of the
-changes addressing the reviewer's comments are below.
+issues were resolved in the bibliography, and minor grammatical errors
+were corrected throughout. An itemized list of the changes addressing
+the reviewer's comments are below.
 \\ \\
@@
 \begin{itemize}
-  \item response
+  \item This was an oversight on our behalf. The jump is actually caused
+    by a grain completely vanishing, but not for the reason explained in
+    the original submission.
+
+  \item At the large porosity, there is a long chain of small bodies
+    that, relative to the rest of the geometry, creates a region of
+    large local tortuosity. When the left-most grain completely erodes,
+    this slightly changes the local tortuosity, but more importantly, it
+    increases the inlet velocity relative to the remainder of the
+    channel. Since the tortuosity is the integral of the local
+    tortuosity weighted by the initial velocity, this increase in
+    velocity creates a slight increase in the tortuosity.
+
+  \item We have updated the explanation to read:
+    \begin{quotation}
+      \noindent
+      For this geometry, the tortuosity decreases monotonically at
+      almost all porosities. However, the tortuosity slightly increases
+      near the end of the simulation. This increase is caused when a
+      grain located at the start of a region with large local tortuosity
+      completely erodes.  In this region, once the grain vanishes, the
+      large local tortuosity changes slightly, but the inlet velocity,
+      $u_1(y)$, relative to the inlet velocity in the remainder of the
+      channel, increases sharply. The result is a sudden increase in the
+      average local tortuosity when weighted by the initial velocity,
+      and this increases the tortuosity of the geometry
+    \end{quotation}
 \end{itemize}
@@
       \noindent
-      We also compute the lines of best fit using the
-      porosity-tortuosity models (4.6).  Each of the models result in a
-      root-mean-squared error ranging from $4.60 \times 10^{-3}$ for
-      model (4.6d) to $7.20 \times 10^{-3}$ for model (4.6c). The black
-      dashed line in figure 15(a) is the line of best fit
-      $\widehat{T}(\phi) = \phi^{-0.2459}$, with a root-mean-square
-      error of $5.50 \times 10^{-3}$.  We note a slightly better
-      root-mean-square error of $4.60 \times 10^{-3}$ is possible with
-      the model $\widehat{T}(\phi) = \left(1 + 0.1499(1-\phi)\right)^2$.
+      We compute the lines of best fit using the porosity-tortuosity
+      models (4.6).  Each of the models result in a root-mean-squared
+      error ranging from $4.60 \times 10^{-3}$ for model (4.6d) to $7.20
+      \times 10^{-3}$ for model (4.6c). The black dashed line in figure
+      15(a) is the line of best fit $\widehat{T}(\phi) =
+      \phi^{-0.2459}$, with a root-mean-square error of $5.50 \times
+      10^{-3}$.  We note a slightly better root-mean-square error of
+      $4.60 \times 10^{-3}$ is possible with the model
+      $\widehat{T}(\phi) = \left(1 + 0.1499(1-\phi)\right)^2$.
     \end{quotation}
@@
       different geometries. Here, we do the same analysis, but with the
-      denser packing of the grains.
+      denser initial packing of the grains.
     \end{quotation}

### 2020-01-27 docs/transport/Response_to_Reviewer_2.tex
finished up reviews

@@
       \noindent
-      We consider a second example with of 20 randomly initialized
-      eroding bodies, but with a smaller initial porosity of $\phi =
-      30.67\%$.
+      We consider a second example with 20 randomly initialized eroding
+      bodies, but with a smaller initial porosity of $\phi = 30.67\%$.
     \end{quotation}
@@
     typically very small. Because we measure the local tortuosity by
-    initiating streamlines significantly far from the grains, each of
-    them connect the inlet to the outlet.
+    initiating tracers significantly far from the grains, each of them
+    connect the inlet to the outlet.
 

### 2020-01-27 docs/transport/Response_to_Reviewer_3.tex
finished up reviews

@@
 we believe is a stronger manuscript.  We also note that formatting
-issues were resolved in the bibliography. An itemized list of the
-changes addressing the reviewer's comments are below.
-\\ \\
+issues were resolved in the bibliography, and minor grammatical errors
+were corrected throughout. An itemized list of the changes addressing
+the reviewer's comments are below.  \\ \\
 \noindent
@@
     three-dimensional erosion, with the most significant being the
-    $\theta$--$L$ formulation, quadrature method, spectral
-    representation of the geometry, and the boundary integral equation
+    $\theta$--$L$ formulation, quadrature methods, spectral
+    representations of the geometry, and the boundary integral equation
     solver.
 
-  \item In three-dimensions, others have extended the $\theta$--$L$
-    formulation to remove stiffness in interfacial flow, spectrally
-    represented geometries, and efficiently solving BIEs.  The challenge
-    with these methods is their computational cost. To consider
-    suspensions with the resolution and number of grains that we
-    consider, the BIE would most likely require a parallel
+  \item In three-dimensions, others have developed methods to extend the
+    $\theta$--$L$ formulation to remove stiffness in interfacial flow,
+    spectrally represented geometries, and efficiently solve BIEs.  The
+    challenge with these methods is their computational cost. To
+    consider suspensions with the resolution and number of grains that
+    we consider, the BIE would most likely require a parallel
     implementation that would run on high-performance computing

### 2020-01-27 docs/transport/erosion_transport.tex
finished up reviews

@@
   distribution of an eroding geometry. The simulations are performed by
-  combining a high-fidelity boundary integral equation solver for the
-  fluid equations, a second-order stable time stepping method to
-  simulate erosion, and new numerical methods to stably and accurately
-  resolve nearly-touching eroded bodies and particle trajectories near
-  the eroding bodies.
+  combining a boundary integral equation solver for the fluid equations,
+  a second-order stable time stepping method to simulate erosion, and
+  high-order numerical methods to stably and accurately resolve
+  nearly-touching eroded bodies and particle trajectories near the
+  eroding bodies.
 \end{abstract}
@@
 
-To compute stable simulations of erosion, we use methods of high-order
-in both space and time. The time integration is unchanged from previous
+To compute stable simulations of erosion, we use high-order methods in
+both space and time. The time integration is unchanged from previous
 work~\citep{qua-moo2018}.  We apply a mild regularization and a
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:Eroding100gap} (a) The pore sizes, represented by
+the length of the red line segments, between neighboring grains. Two
+grains are neighbors if they share an edge of the Delanuay triangulation
+with nodes at the center of each eroding grain. (b) The pore sizes of an
+eroded geometry. The black curve is the Weibull distribution with the
+same first two moments as the data.}
+\end{figure}
+
 While transport in porous media depends on the porosity, it also depends
@@
 investigate the effect of erosion on the pore size distribution.
-\begin{figure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:Eroding100gap} (a) The pore sizes, represented by
-the length of the red line segments, between neighboring grains. Two
-grains are neighbors if they share an edge of the Delanuay triangulation
-with nodes at the center of each eroding grain. (b) The pore sizes of an
-eroded geometry. The black curve is the Weibull distribution with the
-same first two moments as the data.}
-\end{figure}
 
@@
 Barycentric quadrature rule and an accelerated trapezoid rule.  Note
-that the source points of the layer potential is always one of the
+that the source points of the layer potential are always one of the
 eroding bodies or the outer wall, but the target point can either be on
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\begin{center}
+\begin{subfigure}[b]{0.27\textwidth}
+\includegraphics[height = \textwidth]{./figs/1b_0d4r1h_shear}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.27\textwidth}
+\includegraphics[height = \textwidth]{./figs/1b_0d4r0d5h_shear}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.27\textwidth}
+\includegraphics[height = \textwidth]{./figs/1b_0d4r0d1h_shear}
+\caption{}
+\end{subfigure}
+\end{center}
+\caption{\label{fig:NearWall} A single body eroding in a shearing Stokes
+flow.  The color is the logarithm of the shear stress. Therefore,
+erosion is fastest in the red regions (upper half) and slowest in the
+blue regions (lower half).  The body is initialized at three different
+distances from the lower wall: (a) $h$, (b) $h/2$, and (c) $h/10$.}
+\end{figure}
+\begin{figure}
+\begin{center}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r1h_vort}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r0d5h_vort}
+\caption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.32\textwidth}
+\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r0d1h_vort}
+\caption{}
+\end{subfigure}
+\caption{\label{fig:NearWall_vort} The eroded bodies from
+figure~\ref{fig:NearWall} at time $t=0.1$. The color is the logarithm of
+the magnitude of the vorticity. The initial distances from the body to
+the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
+\end{center}
+\end{figure}
+
 Consider a single eroding body close to a solid wall with the shear flow
@@
 
-\begin{figure}
-\begin{center}
-\begin{subfigure}[b]{0.27\textwidth}
-\includegraphics[height = \textwidth]{./figs/1b_0d4r1h_shear}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.27\textwidth}
-\includegraphics[height = \textwidth]{./figs/1b_0d4r0d5h_shear}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.27\textwidth}
-\includegraphics[height = \textwidth]{./figs/1b_0d4r0d1h_shear}
-\caption{}
-\end{subfigure}
-\end{center}
-\caption{\label{fig:NearWall} A single body eroding in a shearing Stokes
-flow.  The color is the logarithm of the shear stress. Therefore,
-erosion is fastest in the red regions (upper half) and slowest in the
-blue regions (lower half).  The body is initialized at three different
-distances from the lower wall: (a) $h$, (b) $h/2$, and (c) $h/10$.}
-\end{figure}
-\begin{figure}
-\begin{center}
-\begin{subfigure}[b]{0.32\textwidth}
-\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r1h_vort}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.32\textwidth}
-\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r0d5h_vort}
-\caption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.32\textwidth}
-\includegraphics[height = 0.53\textwidth]{./figs/1b_0d4r0d1h_vort}
-\caption{}
-\end{subfigure}
-\caption{\label{fig:NearWall_vort} The eroded bodies from
-figure~\ref{fig:NearWall} at time $t=0.1$. The color is the logarithm of
-the magnitude of the vorticity. The initial distances from the body to
-the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
-\end{center}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 several pairs of eroding bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and
-14 \& 18, is too small to be resolve with the trapezoid rule.  By using
-the Barycentric quadrature rule, the interaction between these
+14 \& 18, is too small to resolve with the trapezoid rule.  By using the
+Barycentric quadrature rule, the interaction between these
 nearly-touching bodies is resolved to the desired accuracy, and erosion
@@
 
-In our previous work~\citep{qua-moo2018}, we investigated the effects
-of erosion on the area fraction and flow rate of two different
-geometries.  Here, we do the same analysis, but with the denser packing
-of the grains. In figure~\ref{fig:Eroding20flowrate}(a), we plot the
-area fraction as a function of normalized time.  The general trend of
-the area fraction resembles our previous work~\citep[see][figure
+In our previous work~\citep{qua-moo2018}, we investigated the effects of
+erosion on the area fraction and flow rate of two different geometries.
+Here, we do the same analysis, but with the denser initial packing of
+the grains. In figure~\ref{fig:Eroding20flowrate}(a), we plot the area
+fraction as a function of normalized time.  The general trend of the
+area fraction resembles our previous work~\citep[see][figure
 10(a)]{qua-moo2018}, but with a larger initial area fraction.  In
@@
 regions.  These channels can be further visualized with particle
-trajectories that are trace out the streamlines.  In
+trajectories that trace out the streamlines.  In
 figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
@@
 The two tortuosity formulas give similar results, and any discrepancy
-can be accounted for by slow regions of recirculation and from applying
-quadrature to compute the tortuosity.  As the bodies erode, wide
-channels form where streamlines undergo only minor vertical deflections,
-and this explains why the tortuosity eventually decreases with porosity.
-We computed lines of best fit using the porosity-tortuosity
-models~\eqref{eqn:tortuosityModels} and the power
+can be accounted for by slow regions of recirculation and from
+quadrature error incurred when computing the tortuosity.  As the bodies
+erode, wide channels form where streamlines undergo only minor vertical
+deflections, and this explains why the tortuosity eventually decreases
+with porosity.  We computed lines of best fit using the
+porosity-tortuosity models~\eqref{eqn:tortuosityModels} and the power
 law~\eqref{eqn:tortuosityModels1} minimizes the error.  The  black
@@
 two models have a root-mean-square error that is an order of magnitude
-larger. Interestingly, at the low porosities, the
-tortuosity initially increases. This increase occurs because in the
-absence of erosion (left plot in figure~\ref{fig:Eroding20vort}), many
-of the streamlines, such as those initialized between bodies 15 \& 18,
-only perform minor deflections to pass through the narrow regions,
-albeit, very slowly.  However, as erosion starts to open the channels,
-the streamlines deflect into the fast regions, such as the region above
-body 11, and this increases the amount of vertical deflection, and
-therefore the tortuosity. While this increase in tortuosity is
-interesting, in the next two examples we will see that the tortuosity
-does not initially increase.
+larger. Interestingly, at the low porosities, the tortuosity initially
+increases. This increase occurs because in the absence of erosion (left
+plot in figure~\ref{fig:Eroding20vort}), many of the streamlines, such
+as those initialized between bodies 15 \& 18, only perform minor
+deflections to pass through the narrow regions, albeit, very slowly.
+However, as erosion starts to open the channels, the streamlines deflect
+into the fast regions, such as the region above body 11, and this
+increases the amount of vertical deflection, and therefore the
+tortuosity. While this increase in tortuosity is interesting, in the
+next two examples we will see that the tortuosity does not initially
+increase.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We consider a second example with of 20 randomly initialized eroding
+We consider a second example with 20 randomly initialized eroding
 bodies, but with a smaller initial porosity of $\phi = 30.67\%$.  In
@@
 to the porosity of the geometry in figure~\ref{fig:Eroding100tort}(c).
-Again, the two tortuosity formulas give similar results. While it
-appears that the tortuosity does increase suddenly near the end of the
-simulation, this jump is due to a recirculation zone that vanishes as
-one of the grains completely erodes. This sharp increase is not present
-when the Lagrangian definition of the tortuosity is used. However, the
-relative difference between the tortuosities calculated with the
-Eulerian and Lagrangian formulations is less than $O(10^{-2})$. We also
-compute the lines of best fit using the porosity-tortuosity
-models~\eqref{eqn:tortuosityModels}.  Each of the models result in a
+Again, the two tortuosity formulas give similar results. For this
+geometry, the tortuosity decreases monotonically at almost all
+porosities. However, the tortuosity slightly increases near the end of
+the simulation. This increase is caused when a grain located at the
+start of a region with large local tortuosity completely erodes.  In
+this region, once the grain vanishes, the large local tortuosity changes
+slightly, but the inlet velocity, $u_1(y)$, relative to the inlet
+velocity in the remainder of the channel, increases sharply. The result
+is a sudden increase in the average local tortuosity when weighted by
+the initial velocity, and this increases the tortuosity of the geometry.
+We compute the lines of best fit using the porosity-tortuosity
+models~\eqref{eqn:tortuosityModels}.  The models result in a
 root-mean-squared error ranging from $4.60 \times 10^{-3}$ for

### 2020-02-21 fortran_code/stokesDriver.f
added a uniform flow

@@ -2,9 +2,9 @@
       implicit real*8 (a-h,o-z)
 
       parameter (ninner = 2**8)
-      parameter (nbodies = 2)
+      parameter (nbodies = 5)
       parameter (nouter = 2**10)
-      parameter (ntargets = 500)
+      parameter (ntargets = 50)
       parameter (maxbodies = 10)
 
 c      parameter (ninnc = 2**8,nbeta = 1,ninner = nbeta*ninnc)      
@@ -40,7 +40,6 @@ c     Testing for stress tensor
       pi = 4.d0*datan(1.d0)
       twopi = 2.d0*pi
       dtheta = twopi/dble(ninner)
-    
 
 !      centery(1) = 0.0d0
 !      centerx(2) = 0.5d0
@@ -54,25 +53,31 @@ c     Testing for stress tensor
 !      phi(2) = 0.d0
 !      phi(3) = pi/4.d0
 
-      radius(1) = 2.d-1
-      radius(2) = 2.d-1
-      centerx(1) = 0.5d0
-      centerx(2) = 0.5d0 - radius(1) - radius(2) - 0.1d-1
-      centery(1) = 0.1d0 !+ 0.4999d0 
-      centery(2) = 0.1d0 !+ 0.4999d0
-
-c      radius(3) = 5.d-2
-      phi(1) = 0.d0
-      phi(2) = 0.d0
-c      phi(3) = pi/4.d0
-      
-c      Nphi = 128
-c      dphi = twopi/Nphi
-c      open(unit=21,file='output/dragx.dat')
-c      open(unit=22,file='output/dragy.dat')
-
-c      do kk = 1,Nphi
-c        phi(1) = dble(kk-1)*dphi
+      do k = 1,nbodies
+        radius(k) = 5.d-2
+        phi(k) = 0.d0
+      enddo
+      centerx(1) = -0.5d0
+      centerx(2) = -0.3d0
+      centerx(3) = -0.1d0
+      centerx(4) = +0.1d0
+      centerx(5) = +0.3d0
+      centerx(6) = +0.5d0
+      centery(1) = 0.d0
+      centery(2) = 0.d0
+      centery(3) = 0.d0
+      centery(4) = 0.d0
+      centery(5) = 0.d0
+      centery(6) = 0.d0
+c      
+c      radius(1) = 2.d-1
+c      radius(2) = 2.d-1
+c      centerx(1) = -0.5d0
[…]

### 2020-02-21 fortran_code/stokesSolver.f

@@ -1,5 +1,5 @@
       subroutine stokesSolver(nninner,nnbodies,nnouter,
-     $     ifmm,ibary,maxl,xx,yy,den,iter)
+     $     ifmm,ibary,ibc,maxl,xx,yy,den,iter)
 c     Input x and y coordinates and return the density function on the
 c     boundary.  Outer wall is used to enclose the inner boundary so
 c     that Stokes paradox is avoided
@@ -90,7 +90,7 @@ c      close(unit=2)
 c      close(unit=3)
 c      close(unit=4)
 
-      call bd_condition(ninner,nbodies,x,y,nouter,xouter,youter,rhs)
+      call bd_condition(ninner,nbodies,ibc,x,y,nouter,xouter,youter,rhs)
 c     load boundary condition
       print *, 'load Bd condition'
       
@@ -205,7 +205,7 @@ c     normal and curvatures need to point outwards
         
 
 c***********************************************************************
-      subroutine bd_condition(ninner,nbodies,x,y,
+      subroutine bd_condition(ninner,nbodies,ibc,x,y,
      $    nouter,xouter,youter,rhs)
 c     Boundary condition coming from the far field flow
       implicit real*8 (a-h,o-z)
@@ -259,12 +259,12 @@ c     velocity coming from the r \otimes r part of the Stokes flow
 
       if (0 .eq. 1) then
         do k = 1,nouter
-          call bgFlow(1,xouter(k),youter(k),rhs(k),rhs(k+nouter))
+          call bgFlow(1,ibc,xouter(k),youter(k),rhs(k),rhs(k+nouter))
         enddo
 
         do j = 1,nbodies
           do k = 1,ninner
-            call bgFlow(1,x((j-1)*ninner+k),y((j-1)*ninner+k),
+            call bgFlow(1,ibc,x((j-1)*ninner+k),y((j-1)*ninner+k),
      $          rhs(2*nouter+(j-1)*2*ninner+k),
      $          rhs(2*nouter+(j-1)*2*ninner+k+ninner))
           enddo
@@ -274,7 +274,7 @@ c     generic boundary condition
 
       if (1 .eq. 1) then
         do k = 1,nouter
-          call bgFlow(1,xouter(k),youter(k),rhs(k),rhs(k+nouter))
+          call bgFlow(1,ibc,xouter(k),youter(k),rhs(k),rhs(k+nouter))
[…]

### 2020-02-28 docs/TexNotes/Notes.tex
NM
NNM

@@
 \begin{equation}
+\label{rtot}
 r_{tot} = \frac{\pup - \pdn}{2 x_0 \, \qavg}
@@
 The resulting resistivity in the matrix, $r_m$, includes the contribution from the bodies as well as the channel walls.
-We can then subtract the contribution from the walls, to get $\tilde{r}_m$, the resistivity due to the bodies alone as
+We can then subtract the contribution from the walls to get $\tilde{r}_m$, the resistivity due to the bodies alone as
 \begin{equation}
@@
 \begin{equation}
+\label{resmatrix0}
 \tilde{r}_m = x_0 (r_t - 3) \, .
@@
 As convoluted as this calculation seems, it does appear to give convergent numerical results that are {\em independent of the choice of $x_0$} (to the expected order of accuracy).
+
+Using \eqref{rtot} and $\qavg = \frac{2}{3} U$ gives
+\begin{equation}
+\label{resmatrix}
+\tilde{r}_m = \frac{\pup - \pdn}{2 \qavg} - 3 x_0 = \frac{3}{4} \frac{\pup-\pdn}{U} - 3 x_0
+\end{equation}
 
@@
 These are the permeability and resistivity for the entire region $-x_0 < x < x_0$.
-In particular, the resistivity of the porous matrix will be averaged with the much lower permeability of the buffer region.
+In particular, the resistivity of the porous matrix will be averaged with the much lower resistivity of the buffer region.
 To remove the contribution from the buffer region, and thus isolate the resistivity due to the porous matrix of bodies, we can simply set $x_0 = 1$ above.
@@
 \begin{equation}
+\label{resdrag}
 r_{tot} = \frac{3}{8} \frac{F_D}{U}
 \end{equation}
+With this simplification, I see a match between measuring resistivity via the drag \eqref{resdrag} versus measuring resistivity directly via \eqref{resmatrix}.
 

### 2020-02-28 julia_code/basic.jl

@@ -231,6 +231,12 @@ function getumax(thlenden::ThLenDenType, nouter::Int, ibary::Int, fixpdrop::Bool
 	if fixpdrop
 		pdrop = getpdrop(thlenden, nouter, ibary)[1]
 		umax =  10 * 8/pdrop
+		
+
+		###umax = 1./(pdrop + epsilon)
+
+
+
 		println("Fixing pdrop, umax = ", round(umax,sigdigits=3))
 	end
 	return umax

### 2020-07-10 docs/proposals/NSF/budgets/budgetJustification.tex
adding budget and justification

\documentclass[11pt]{article}
\usepackage{fullpage}
\topmargin0.25in

\begin{document}
\thispagestyle{empty}
\sloppy

\begin{center}
\Large \bf Budget Justification
\end{center}
\vspace{0.2in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (PI: Matthew Moore, co-PI: Bryan
Quaife)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of the
PI's summer salary in each of years 1--3, one month of the co-PI's
summer salary in years 1 and 2, and 0.5 months of the co-PI's summer
salary in year 3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. The PI's monthly salary in
year one is $\$9,720$. The co-PI's monthy salary is $\$10,553$. For
years 2 and 3, a 3\% increase is included.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    PI &    $\$9,720$  & $\$10,012$ & $\$10,312$ & $\$30,044$\\
    \hline
    co-PI & $\$10,553$ & $\$10,869$ & $\$5,598$  & $\$27,020$ \\
    \hline
    Total & $\$20,273$ & $\$20,881$ & $\$15,910$ & $\$57,064$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{B: Other Personnel}
%\hfill \\
%\noindent
The requested other personnel funding includes salary for one full-time
Ph.D.~student in two semesters of each year starting at $\$21,000$.  The
Ph.D.~student will develop and perform numerical simulations. An annual
increase of 3\% is included.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Ph.D. & $\$21,000$ & $\$21,630$ & $\$22,279$ & $\$64,909$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
{\bf PI:} The fringe benefits of the PI are 17.06\%. \\
{\bf co-PI:} The fringe benefits of the co-PI are 17.06\%. \\
{\bf Ph.D.:} The fringe benefits of the graduate student are
0.1\% plus an $\$1,965$ health insurance. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    PI & $\$1,658$ & $\$1,708$ & $\$1,759$ & $\$5,125$ \\
    \hline
    co-PI & $\$1,800$ & $\$1,854$ & $\$955$ & $\$4,609$ \\
    \hline
    Ph.D. & $\$1,986$ & $\$1,987$ & $\$1,987$ & $\$5,960$ \\
    \hline
    Total & $\$5,444$ & $\$5,549$ & $\$4,701$ & $\$15,694$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to fund two total annual domestic trips
for the PI, co-PI, or the Ph.D.~student.  The expected costs per
conference participant is $\$1,750$ with a breakdown of $\$600$ for
airfare, $\$750$ for lodging, $\$56$ for local transportation, $\$144$
for meals (four days at $\$36$ per day), and $\$200$ for conference
registration.  Potential meeting venues include several SIAM Meetings
(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
appropriately themed workshops.  The PI, co-PI, and Ph.D.~student will
give presentations and actively participate in the meeting or workshop.
Travel funds for the first year are removed due to the COVID crisis
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Conferences &  & $\$3,500$ & $\$3,500$ & $\$7,000$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{G: Other Direct Costs}
%\noindent
\paragraph{\bf Materials and Supplies:} The requested materials and
supplies is to purchase two $\$1,500$ laptops with accessories, which is
not otherwise available, for the PI, co-PI, and Ph.D.~student in year 1.
The laptops will be used for developing the proposed algorithms and
presenting the results at conferences.  The laptops will give the group
members the flexibility to work on the proposed research remotely.  The
laptops will be used exclusively for the proposed research. 
\\
\paragraph{\bf Other:} The requested other direct costs are to cover the
Ph.D.~student's tuition for 18 credit hours, at a rate of $\$407.55$ per
credit hour in year 1.  An annual increase of 1\% is included per
published university projections.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Materials and Supplies & $\$3,000$ & & & $\$3,000$ \\
    \hline
    Other & $\$7,336$ & $\$7,409$ & $\$7,484$ & $\$22,229$ \\
    \hline
    Total & $\$10,336$ & $\$7,409$ & $\$7,484$ & $\$25,229$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$57,053$ & $\$58,969$ & $\$53,874$ & $\$169,896$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
Florida State University's federally negotiated indirect cost rate is
54\% for research on modified total direct costs (MTDC) which excludes
tuition.  The base for overhead is $\$49,717$ in year 1, $\$51,560$ in
year 2, and $\$46,390$ in year 3.  Florida State University defines a
fiscal year to be July 1--June 30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$26,847$ & $\$27,842$ & $\$25,051$ & $\$79,740$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$83,900$ & $\$86,811$ & $\$78,925$ & $\$249,636$ \\
    \hline
  \end{tabular}
\end{center}

\end{document}

### 2020-07-29 docs/proposals/NSF/PostDocs/PI_change_request.tex
added letter requesting change of PI

\documentclass{article}

\usepackage[dvinames]{xcolor}
% Measurements are taken directly from the guide
\usepackage[top=2in,left=1.5in,bottom=0.5in,right=0.625in]{geometry}
\usepackage{graphicx}
\usepackage[colorlinks=false,
pdfborder={0 0 0},
]{hyperref}
\usepackage[absolute]{textpos}
\usepackage{tikz}
\usetikzlibrary{calc}
% A nice serif font, but no the prescribed
% nonfree ITC stone
\usepackage[oldstylenums]{kpfonts}
\usepackage[T1]{fontenc}

\definecolor{fsugarnet}{RGB}{120,47,64}
\definecolor{fsugold}{RGB}{206,184,136}
\definecolor{fsublack}{RGB}{44,42,41}
\definecolor{fsuwhite}{RGB}{255,255,255}

% No paragraph indentation
\parindent0pt
\setlength{\parskip}{0.8\baselineskip}
\raggedright
\pagestyle{empty}
% Ensure consistency in the footer
\urlstyle{sf}

\begin{document}

\today
\bigskip

Dear Dr.~Peszynska:

I would like to request a restructuring of the NSF grant with Award
Number 2012560. PI Moore has left Florida State University (FSU) and
taken a faculty position at the US Naval Academy. Dr.~Moore's new
department does not have a graduate program, so the funded graduate
student's senior advisor will be co-PI Quaife at FSU. So that the grant
can be managed by FSU, I request that Dr.~Quaife becomes the lead PI and
Dr.~Moore becomes the co-PI. I also request permission for FSU to create
a sub-contract for the US Naval Academy that will manage Dr.~Moore's
funding.

This request is written in consultation with Dr.~Moore. Please contact
me if further clarification is required.

Sincerely,
\vspace{2\baselineskip}

Bryan Quaife \\
Assistant Professor

% -------------------------------------------------------
% Add logo, the text under the crimson line,
% and the line itself
\begin{textblock*}{2in}[0.3066,0.39](1.5in,1.33in)
\includegraphics[width=2in]{fsu_logo}
\end{textblock*}
\begin{textblock*}{6.375in}(1.5in,1.55in)
% 6.375=8.5 - 1.5 - 0.625
\sffamily
\hfill \color{fsugarnet} Department of Scientific Computing \\
\hfill Dr.~Bryan Quaife,
Assistant Professor
\end{textblock*}
\begin{tikzpicture}[remember picture,overlay]
\draw[color=fsugarnet,line width=1pt] (current page.north west)+(1.5in,-1.5in) -- ($(-0.625in,-1.5in)+(current page.north east)$);
\end{tikzpicture}

% Add the footnote. A
% better way would be to
% use fancyhdr
\vfill
{\footnotesize\color{fsugarnet}\sffamily
400 Dirac Science Library, Tallahassee, FL
32306-4120 \\
[-0.1\baselineskip]
(512) 436-1148 \textbullet\
\url{bquaife@fsu.edu}
\textbullet\
\url{http://www.sc.fsu.edu/~bquaife}
}
\end{document}

### 2020-07-29 docs/proposals/NSF/budgets/budgetImpact.tex
added letter requesting change of PI

\documentclass[11pt]{article}
\usepackage{fullpage}
\topmargin0.25in

\begin{document}
\thispagestyle{empty}
\sloppy

\begin{center}
\Large \bf Budget Impact Statement
\end{center}
\vspace{0.2in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The PI and co-PI have successful reduced the budget for this project
from the originally requested \$$439,192$ to under \$$250,000$. The
reduction will have some impact on the scope of the project, but we are
confident that we will still be able to meet the main goals of the
project. First, the largest change is that instead of (partially)
supporting two graduate students for the 3 years, only one graduate
student will be supported. This graduate student will spearhead the
implementation of novel numerical algorithms for simulating flow-induced
erosion with multi-physical effects to be used in the modeling of dense
suspensions, groundwater systems, and sinkhole collapse. The graduate
student will also explore machine learning techniques in order to inform
reduced models that learn from batches of high-fidelity simulations.
While we still expect this machine learning component to be carried out,
there may be some reduction in its extent due to the removal of the
second graduate student. Thus, the main computational thrust of the
project will remain largely intact, with possible modifications only in
the depth and extent of each component, not in the components
themselves.

Notably, we have removed all expenses pertaining to the laboratory
experiments that were originally intended to corroborate and interplay
with the numerical simulations. The cuts include the second graduate
student (who would have spent part of their time interacting with the
experiments), the funding for an undergraduate student, the funding for
the technical person, and a large portion of the materials and supplies.
While the laboratory component would have been a nice addition to the
project, its role is not as central to the project as the computational
component is. Further, this experimental component could possibly be
replaced by a collaboration with other, external experimentalists.

In addition, we have cut 1/2 month of summer salary support for co-PI
Quaife. We have retained the originally requested summer salary for PI
Moore since, with the cut of the second graduate student, the PI will
need to take on some additional burdens of the project. We have also
significantly scaled back the travel support as COVID-19 may likely
curtail the ability to travel anyway and many conferences will likely be
held remotely.

\end{document}

### 2020-07-29 docs/proposals/NSF/PostDocs/PI_change_request.tex
NM

@@
 can be managed by FSU, I request that Dr.~Quaife becomes the lead PI and
-Dr.~Moore becomes the co-PI. I also request permission for FSU to create
-a sub-contract for the US Naval Academy that will manage Dr.~Moore's
-funding.
+Dr.~Moore becomes the co-PI, with a sub-contract created for the US Naval Academy that will manage Dr.~Moore's funding.
+
+% I also request permission for FSU to create a sub-contract for the US Naval Academy that will manage Dr.~Moore's funding.
 

### 2020-08-06 docs/proposals/NSF/budgets/budgetJustificationFSU.tex
adding new budget stuff

--- 2020-07-10 docs/proposals/NSF/budgets/budgetJustification.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{A: Senior Personnel (PI: Matthew Moore, co-PI: Bryan
-Quaife)}
+\subsection*{A: Senior Personnel (PI: Bryan Quaife)}
 %\hfill \\
@@
 The requested senior personnel funding is to support one month of the
-PI's summer salary in each of years 1--3, one month of the co-PI's
-summer salary in years 1 and 2, and 0.5 months of the co-PI's summer
-salary in year 3. During this period, the PIs
-will work together to develop and implement algorithms, write papers,
-and work closely with the graduate student. The PI's monthly salary in
-year one is $\$9,720$. The co-PI's monthy salary is $\$10,553$. For
-years 2 and 3, a 3\% increase is included.
+PI's summer salary in years 1 and 2, and 0.5 months of the PI's summer
+salary in year 3. During this period, the PI will work together to
+develop and implement algorithms, write papers, and work closely with
+subcontractor Moore and the graduate student. The PI's monthly salary in
+year one is $\$10,553$. For years 2 and 3, a 3\% increase is included.
 %\hfill \\
@@
     \hline
-    PI &    $\$9,720$  & $\$10,012$ & $\$10,312$ & $\$30,044$\\
-    \hline
-    co-PI & $\$10,553$ & $\$10,869$ & $\$5,598$  & $\$27,020$ \\
-    \hline
-    Total & $\$20,273$ & $\$20,881$ & $\$15,910$ & $\$57,064$ \\
+    PI & $\$10,553$ & $\$10,869$ & $\$5,598$  & $\$27,020$ \\
     \hline
@@
 {\bf PI:} The fringe benefits of the PI are 17.06\%. \\
-{\bf co-PI:} The fringe benefits of the co-PI are 17.06\%. \\
 {\bf Ph.D.:} The fringe benefits of the graduate student are
@@
     \hline
-    PI & $\$1,658$ & $\$1,708$ & $\$1,759$ & $\$5,125$ \\
-    \hline
-    co-PI & $\$1,800$ & $\$1,854$ & $\$955$ & $\$4,609$ \\
+    PI & $\$1,800$ & $\$1,854$ & $\$955$ & $\$4,609$ \\
     \hline
@@
     \hline
-    Total & $\$5,444$ & $\$5,549$ & $\$4,701$ & $\$15,694$ \\
+    Total & $\$3,786$ & $\$3,841$ & $\$2,942$ & $\$10,569$ \\
     \hline
@@
 %\noindent
-The requested travel funds is to fund two total annual domestic trips
-for the PI, co-PI, or the Ph.D.~student.  The expected costs per
-conference participant is $\$1,750$ with a breakdown of $\$600$ for
-airfare, $\$750$ for lodging, $\$56$ for local transportation, $\$144$
-for meals (four days at $\$36$ per day), and $\$200$ for conference
-registration.  Potential meeting venues include several SIAM Meetings
-(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
-appropriately themed workshops.  The PI, co-PI, and Ph.D.~student will
-give presentations and actively participate in the meeting or workshop.
-Travel funds for the first year are removed due to the COVID crisis
+The requested travel funds is to fund an annual domestic trip for the PI
+or the Ph.D.~student.  The expected costs per conference participant is
+$\$1,750$ with a breakdown of $\$600$ for airfare, $\$750$ for lodging,
+$\$56$ for local transportation, $\$144$ for meals (four days at $\$36$
+per day), and $\$200$ for conference registration.  Potential meeting
+venues include several SIAM Meetings (Annual Meetings, CSE, Dynamical
+Systems), APS Fluids Meetings, or appropriately themed workshops.  The
+PI and Ph.D.~student will give presentations and actively participate in
+the meeting or workshop.  Travel funds for the first year are removed
+due to the COVID crisis
 %\hfill \\
@@
     \hline
-    Domestic Conferences &  & $\$3,500$ & $\$3,500$ & $\$7,000$ \\
+    Domestic Conferences &  & $\$1,750$ & $\$1,750$ & $\$3,500$ \\
     \hline
@@
 \paragraph{\bf Materials and Supplies:} The requested materials and
-supplies is to purchase two $\$1,500$ laptops with accessories, which is
-not otherwise available, for the PI, co-PI, and Ph.D.~student in year 1.
-The laptops will be used for developing the proposed algorithms and
-presenting the results at conferences.  The laptops will give the group
+supplies is to purchase one $\$1,500$ laptop with accessories, which is
+not otherwise available, for the PI and Ph.D.~student in year 1.  The
+laptop will be used for developing the proposed algorithms and
+presenting the results at conferences. The laptop will give the group
 members the flexibility to work on the proposed research remotely. The
-laptops will be used exclusively for the proposed research. 
+laptop will be used exclusively for the proposed research. 
 \\
@@
     \hline
-    Materials and Supplies & $\$3,000$ & & & $\$3,000$ \\
+    Materials and Supplies & $\$1,500$ & & & $\$1,500$ \\
     \hline
@@
     \hline
-    Total & $\$10,336$ & $\$7,409$ & $\$7,484$ & $\$25,229$ \\
+    Total & $\$8,836$ & $\$7,409$ & $\$7,484$ & $\$23,729$ \\
     \hline
@@
     \hline
-    $\$57,053$ & $\$58,969$ & $\$53,874$ & $\$169,896$ \\
+    $\$44,175$ & $\$45,499$ & $\$40,053$ & $\$129,727$ \\
     \hline
@@
 54\% for research on modified total direct costs (MTDC) which excludes
-tuition.  The base for overhead is $\$49,717$ in year 1, $\$51,560$ in
-year 2, and $\$46,390$ in year 3.  Florida State University defines a
+tuition. The base for overhead is $\$36,839$ in year 1, $\$38,090$ in
+year 2, and $\$32,569$ in year 3. Florida State University defines a
 fiscal year to be July 1--June 30.
@@
     \hline
-    $\$26,847$ & $\$27,842$ & $\$25,051$ & $\$79,740$ \\
+    $\$19,893$ & $\$20,569$ & $\$17,587$ & $\$58,049$ \\
     \hline
@@
     \hline
-    $\$83,900$ & $\$86,811$ & $\$78,925$ & $\$249,636$ \\
+    $\$64,068$ & $\$66,068$ & $\$57,640$ & $\$187,776$ \\
     \hline

### 2020-08-06 docs/proposals/NSF/budgets/budgetJustUSNA.tex
NM

--- 2020-07-10 docs/proposals/NSF/budgets/budgetJustification.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{A: Senior Personnel (PI: Matthew Moore, co-PI: Bryan
-Quaife)}
+\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
 %\hfill \\
@@
 The requested senior personnel funding is to support one month of the
-PI's summer salary in each of years 1--3, one month of the co-PI's
-summer salary in years 1 and 2, and 0.5 months of the co-PI's summer
-salary in year 3. During this period, the PIs
+co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
 will work together to develop and implement algorithms, write papers,
-and work closely with the graduate student. The PI's monthly salary in
-year one is $\$9,720$. The co-PI's monthy salary is $\$10,553$. For
-years 2 and 3, a 3\% increase is included.
+and work closely with the graduate student. 
+Co-PI Moore's salary will in years 1,2,3 will be Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
 %\hfill \\
@@
     \hline
-    PI &    $\$9,720$  & $\$10,012$ & $\$10,312$ & $\$30,044$\\
-    \hline
-    co-PI & $\$10,553$ & $\$10,869$ & $\$5,598$  & $\$27,020$ \\
-    \hline
-    Total & $\$20,273$ & $\$20,881$ & $\$15,910$ & $\$57,064$ \\
-    \hline
-  \end{tabular}
-\end{center}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{B: Other Personnel}
-%\hfill \\
-%\noindent
-The requested other personnel funding includes salary for one full-time
-Ph.D.~student in two semesters of each year starting at $\$21,000$.  The
-Ph.D.~student will develop and perform numerical simulations. An annual
-increase of 3\% is included.
-%\hfill \\
-\begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
-    \hline
-    & Year 1 & Year 2 & Year 3 & Total \\
-    \hline
-    Ph.D. & $\$21,000$ & $\$21,630$ & $\$22,279$ & $\$64,909$ \\
+    co-PI Moore & $\$9,584.61$ & $\$9,762.27$ & $\$9,977.10$  & $\$29,323.98$ \\
     \hline
@@
 \subsection*{C: Fringe Benefits}
-{\bf PI:} The fringe benefits of the PI are 17.06\%. \\
-{\bf co-PI:} The fringe benefits of the co-PI are 17.06\%. \\
-{\bf Ph.D.:} The fringe benefits of the graduate student are
-0.1\% plus an $\$1,965$ health insurance. \\
+The fringe benefits of co-PI Moore at USNA are 34\%. 
+In addition a COLA of 3\% is added: \\
 %\hfill \\
@@
     \hline
-    PI & $\$1,658$ & $\$1,708$ & $\$1,759$ & $\$5,125$ \\
+    co-PI Moore Fringe & $\$3,258.77$ & $\$3,319.17$ & $\$3,392.21$ & $\$9,970.15$ \\
     \hline
-    co-PI & $\$1,800$ & $\$1,854$ & $\$955$ & $\$4,609$ \\
+    co-PI Moore COLA & $\$287.54$ & $\$292.87$ & $\$299.31$ & $\$879.72$ \\
     \hline
-    Ph.D. & $\$1,986$ & $\$1,987$ & $\$1,987$ & $\$5,960$ \\
-    \hline
-    Total & $\$5,444$ & $\$5,549$ & $\$4,701$ & $\$15,694$ \\
+    Total & $\$3,546.31$ & $\$3,612.04$ & $\$3,691.52 $ & $\$10849.85
+$ \\
     \hline
@@
 %\noindent
-The requested travel funds is to fund two total annual domestic trips
-for the PI, co-PI, or the Ph.D.~student.  The expected costs per
+The requested travel funds is to partially fund a domestic trip
+for co-PI Moore in years 2 and 3.  The expected costs per
 conference participant is $\$1,750$ with a breakdown of $\$600$ for
@@
 (Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
-appropriately themed workshops.  The PI, co-PI, and Ph.D.~student will
-give presentations and actively participate in the meeting or workshop.
-Travel funds for the first year are removed due to the COVID crisis
+appropriately themed workshops. 
+Alternatively, co-PI Moore may use these travel funds to visit PI Quaife and the funded graduate student at FSU in order to collaborate on the project.
+Travel funds for the first year are removed due to the COVID crisis.
 %\hfill \\
@@
     \hline
-    Domestic Conferences &  & $\$3,500$ & $\$3,500$ & $\$7,000$ \\
+    Domestic Travel &  & $\$1,000$ & $\$1,000$ & $\$2,000$ \\
     \hline
@@
 \paragraph{\bf Materials and Supplies:} The requested materials and
-supplies is to purchase two $\$1,500$ laptops with accessories, which is
-not otherwise available, for the PI, co-PI, and Ph.D.~student in year 1.
-The laptops will be used for developing the proposed algorithms and
-presenting the results at conferences.  The laptops will give the group
-members the flexibility to work on the proposed research remotely.  The
-laptops will be used exclusively for the proposed research. 
+supplies of \$1000 in year 1 is to partially fund a laptop or desktop computer for co-PI Moore. The computer will be used for developing the proposed algorithms and
+presenting the results at conferences.
 \\
-\paragraph{\bf Other:} The requested other direct costs are to cover the
-Ph.D.~student's tuition for 18 credit hours, at a rate of $\$407.55$ per
-credit hour in year 1.  An annual increase of 1\% is included per
-published university projections.
-%\hfill \\
-\begin{center}
-  \begin{tabular}{|c|c|c|c|c|}
-    \hline
-    & Year 1 & Year 2 & Year 3 & Total \\
-    \hline
-    Materials and Supplies & $\$3,000$ & & & $\$3,000$ \\
-    \hline
-    Other & $\$7,336$ & $\$7,409$ & $\$7,484$ & $\$22,229$ \\
-    \hline
-    Total & $\$10,336$ & $\$7,409$ & $\$7,484$ & $\$25,229$ \\
-    \hline
-  \end{tabular}
-\end{center}
 
@@
     \hline
-    $\$57,053$ & $\$58,969$ & $\$53,874$ & $\$169,896$ \\
+    $\$14,130.92$ & $\$14,374.31$ & $\$14,668.63$ & $\$43,173.86
+$ \\
     \hline
@@
 %\noindent
-Florida State University's federally negotiated indirect cost rate is
-54\% for research on modified total direct costs (MTDC) which excludes
-tuition.  The base for overhead is $\$49,717$ in year 1, $\$51,560$ in
-year 2, and $\$46,390$ in year 3.  Florida State University defines a
-fiscal year to be July 1--June 30.
+The US Naval Academy's federally negotiated indirect cost rate is
+10\% for research on modified total direct costs (MTDC).
+The base for overhead is $\$14,130.92$ in year 1, $\$14,374.31$ in
+year 2, and $\$14,668.63$ in year 3.
 %\hfill \\
@@
     \hline
-    $\$26,847$ & $\$27,842$ & $\$25,051$ & $\$79,740$ \\
+    $\$1,413.09$ & $\$1,437.43$ & $\$1,466.86$ & $\$4,317.38$ \\
     \hline
@@
     \hline
-    $\$83,900$ & $\$86,811$ & $\$78,925$ & $\$249,636$ \\
+    $\$15,544.01$ & $\$15,811.74$ & $\$16,135.49$ & $\$47,491.24$ \\
     \hline

### 2020-08-07 docs/proposals/NSF/PostDocs/Scope_of_work_FSU.tex
starting scope of work

--- 2019-12-13 docs/proposals/NSF/ProjDocs/funding_NM.tex
@@
 \pagestyle{fancy}
-\lhead{\footnotesize MNJ Moore}
-\chead{\footnotesize Current and Pending Support}
+\lhead{\footnotesize Bryan D.~Quaife}
+\chead{\footnotesize FSU Scope of Work}
 \rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
@@
 \begin{document}
+\section*{Personnel}
+The research at FSU will be performed by PI Quaife and Ph.D.~student
+Jake Cherry for the duration of the award.
 
-\subsection*{Current Support:}
+\section*{Deliverables}
+\paragraph{Simulating mechanical and chemical erosion, as well as
+transport, including sedimentation and compaction, of eroding bodies:}
 
-{\bf Title}: Dynamic interactions between fluid flows and moving boundaries \\
-{\bf Source}: Simons Foundation, Mathematics and Physical
-Sciences-Collaboration Grants for Mathematicians \\
-{\bf Total Award Amount:} \$42,000 (Travel funds only) \\
-{\bf Duration:} September 1, 2017--August 31, 2022 \\
-{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
-Academic: 0, Summer: 0 \\
+\paragraph{Simulating the transport of finite Peclet number
+concentrations in eroded porous medium.}
 
-%\vspace{-17pt}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Pending Support:}
+\paragraph{Improving numerical methods including fast summation methods,
+preconditioners, and quadrature.}
 
-\noindent
-{\bf Title}:  A Comprehensive Experimental And Computational Fluid Dynamics Analysis Of Coning In Non-Newtonian Tailings During Extraction From Tailings Ponds \\
-{\bf Source}:  Institute for Oil Sands Innovation\\
-{\bf Total Award Amount:} \$171,842 \\
-{\bf Duration:}  January 1, 2020--January 1, 2022\\
-{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
-Academic: 0, Summer: 0.5 \\
-
-{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
-Media (this proposal) \\
-{\bf Source}: National Science Foundation, Division of Mathematical
-Sciences, Computational Mathematics \\
-{\bf Total Award Amount:} \$439,824 \\ %\$439,193 \\
-{\bf Duration:} July 1, 2020--June 30, 2023 \\
-{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
-Academic: 0, Summer: 1 \\
+\section*{Timeline}
 

### 2020-08-07 docs/proposals/NSF/PostDocs/Scope_of_work_USNA.tex
starting scope of work

\documentclass[11pt]{article}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{amsmath,amsfonts,amssymb}
\usepackage{tabularx}
\usepackage{todonotes}
\usepackage{mathpazo}

%\renewcommand\thesubsection{(\alph{subsection})}
%\renewcommand\thesubsubsection{(\roman{subsubsection})}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}
% For 11pt size

\pagestyle{fancy}
\lhead{\footnotesize M.J.N.~Moore}
\chead{\footnotesize USNA Scope of Work}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

\begin{document}
\section*{Personnel}
The research at the US Naval Academy will be performed by co-PI Moore.

\section*{Deliverables}
The deliverables from the US Naval Academy will include algorithms,
computational tools, peer-reviewed publications, presentations at
conferences, and outreach. The deliverables will be centered around the
following tasks taken directly from the Project Description.

\paragraph{1: Characterizing anisotropy, permeability, and pore size
dynamics to inform homogenized models such as Darcy’s relation.}
Resistivity of eroded and dissolved bodies will be used define the
anisotropy, permeability, and to infer horizontal permeability.

\paragraph{2: Developing and validating new parameterizations using machine
learning techniques and numerical simulations.} Large batches of
high-fidelity simulations will be used to train machine learning and
deep-neural networks. These new models will parameterize the effects of
erosion on the evolution macroscopic medium properties of the flow.

\section*{Timeline}
Years 1 and 2 will focus on deliverable 1. Years 2 and 3 will focus on
deliverable 2.

\end{document}

### 2020-08-07 docs/proposals/NSF/budgets/budgetJustUSNA.tex

@@
 %\noindent
-The requested senior personnel funding is to support one month of the
+The requested senior personnel funding is to support one month of 
 co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
@@
 and work closely with the graduate student. 
-Co-PI Moore's salary will in years 1,2,3 will be Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
+Co-PI Moore's salary will in years 1,2,3 will be USNA Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
 %\hfill \\
@@
     \hline
-    Total & $\$3,546.31$ & $\$3,612.04$ & $\$3,691.52 $ & $\$10849.85
+    Total & $\$3,546.31$ & $\$3,612.04$ & $\$3,691.52 $ & $\$10,849.85
 $ \\

### 2020-08-08 docs/proposals/NSF/PostDocs/Scope_of_work_FSU.tex
finshed up scope of work for FSU

@@
 \section*{Deliverables}
-\paragraph{Simulating mechanical and chemical erosion, as well as
-transport, including sedimentation and compaction, of eroding bodies:}
+\paragraph{1.~Simulating mechanical and chemical erosion, as well as
+transport, including sedimentation and compaction, of eroding bodies.}
+Transport of mobile eroding and dissolving bodies will be simulated.
+Dissolution will be simulated using advection-diffusion solvers for
+complex geometries that will combine semi-Lagrangian methods with a
+diffusion solver for the Laplace transformed concentration.
 
-\paragraph{Simulating the transport of finite Peclet number
-concentrations in eroded porous medium.}
+\paragraph{2.~Simulating the transport of finite Peclet number
+concentrations in eroded porous medium.} The algorithms to simulate
+dissolution will also be used to simulate transport of chemical species
+in eroded and dissolved geometries.
 
-\paragraph{Improving numerical methods including fast summation methods,
-preconditioners, and quadrature.}
+\paragraph{3.~Improving numerical methods including fast summation
+methods, preconditioners, and quadrature:} Novel computational tools
+including quadrature, preconditioning, and fast summation methods will
+be used to accurately, efficiently, and stably simulate hundreds or
+thousands of mobile eroded or dissolving bodies.
 
 \section*{Timeline}
+Deliverable 1 will be a focus of Year 1. Deliverables 2 and 3 will be
+developed over all three years of the project.
+
+\section*{Coordination with co-PI Moore}
+Throughout the project, the FSU personnel will work closely with co-PI
+Moore. This will include frequent emails and phone conversations, 1--2
+Zoom meetings per month, and the code and papers will be maintained on
+GitHub.
 

### 2020-08-11 docs/proposals/NSF/PostDocs/Scope_of_work_USNA.tex
NM

@@
 
-\paragraph{1: Characterizing anisotropy, permeability, and pore size
-dynamics to inform homogenized models such as Darcy’s relation.}
-Resistivity of eroded and dissolved bodies will be used define the
-anisotropy, permeability, and to infer horizontal permeability.
+\paragraph{1: Characterizing permeability, anisotropy, and pore size
+dynamics to inform Darcy-based homogenized models.}
+The high-fidelity numerical simulations permit precise measurements of coarse-grained quantities such as permeability and anisotropy, as they depend on medium features such as porosity and microstructure geometry.
+Statistical measurements of these properties taken from large batches of the numerical simulations will inform reduced models based on Darcy's law with variable permeability to represent unresolved pore-structure that varies dynamically in time due to erosion.
+%Resistivity of eroded and dissolved bodies will be used define the anisotropy, permeability, and to infer horizontal permeability.
 
 \paragraph{2: Developing and validating new parameterizations using machine
-learning techniques and numerical simulations.} Large batches of
-high-fidelity simulations will be used to train machine learning and
-deep-neural networks. These new models will parameterize the effects of
-erosion on the evolution macroscopic medium properties of the flow.
+learning techniques and numerical simulations.} The batches of high-fidelity simulations will be used to train machine learning and deep-neural networks.
+These new models will parameterize the effects of erosion on the evolution of macroscopic properties.
+Once trained, the networks will enable predictions of how medium properties respond dynamically to changes in environmental conditions without reliance on the (more expensive) direct physical simulations.
 
@@
 
+\section*{Coordination with PI Quaife}
+Throughout the project, co-PI Moore will work closely with both PI Quaife and the funded Ph.D.~student at FSU, Jake Cherry.
+This will include frequent emails and phone conversations, 1--2 Zoom and/or Google Meet meetings per month.
+The code and papers will be maintained on GitHub.
+
 \end{document}

### 2020-08-25 docs/proposals/NSF/budgets/budgetJustUSNA.tex
NM

@@
     \hline
-    co-PI Moore & $\$9,584.61$ & $\$9,762.27$ & $\$9,977.10$  & $\$29,323.98$ \\
+    co-PI Moore & $\$9,585$ & $\$9,762$ & $\$9,977$  & $\$29,324$ \\
     \hline
@@
 The fringe benefits of co-PI Moore at USNA are 34\%. 
-In addition a COLA of 3\% is added: \\
+In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
 %\hfill \\
@@
     \hline
-    co-PI Moore Fringe & $\$3,258.77$ & $\$3,319.17$ & $\$3,392.21$ & $\$9,970.15$ \\
+    co-PI Moore Fringe & $\$3,259$ & $\$3,319$ & $\$3,392$ & $\$9,970$ \\
     \hline
-    co-PI Moore COLA & $\$287.54$ & $\$292.87$ & $\$299.31$ & $\$879.72$ \\
+    co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
     \hline
-    Total & $\$3,546.31$ & $\$3,612.04$ & $\$3,691.52 $ & $\$10,849.85
-$ \\
+    Total & $\$3,546$ & $\$3,612$ & $\$3,692$ & $\$10,850$ \\
     \hline
@@
     \hline
-    $\$14,130.92$ & $\$14,374.31$ & $\$14,668.63$ & $\$43,173.86
-$ \\
+    $\$14,130.92$ & $\$14,374$ & $\$14,669$ & $\$43,174$ \\
     \hline
@@
 %\noindent
-The US Naval Academy's federally negotiated indirect cost rate is
+The US Naval Academy's indirect cost rate is
 10\% for research on modified total direct costs (MTDC).
@@
 year 2, and $\$14,668.63$ in year 3.
+The US Naval Academy defines a fiscal year to be July 1-June 30.
 %\hfill \\
@@
     \hline
-    $\$1,413.09$ & $\$1,437.43$ & $\$1,466.86$ & $\$4,317.38$ \\
+    $\$1,413$ & $\$1,437$ & $\$1,467$ & $\$4,317$ \\
     \hline
@@
     \hline
-    $\$15,544.01$ & $\$15,811.74$ & $\$16,135.49$ & $\$47,491.24$ \\
+    $\$15,544$ & $\$15,812$ & $\$16,135$ & $\$47,491$ \\
     \hline

### 2020-08-26 docs/proposals/NSF/PostDocs/Subaward_Justification.tex
working on budget justification

--- 2020-07-29 docs/proposals/NSF/PostDocs/PI_change_request.tex
@@
 
-I would like to request a restructuring of the NSF grant with Award
-Number 2012560. PI Moore has left Florida State University (FSU) and
-taken a faculty position at the US Naval Academy. Dr.~Moore's new
-department does not have a graduate program, so the funded graduate
-student's senior advisor will be co-PI Quaife at FSU. So that the grant
-can be managed by FSU, I request that Dr.~Quaife becomes the lead PI and
-Dr.~Moore becomes the co-PI. I also request permission for FSU to create
-a sub-contract for the US Naval Academy that will manage Dr.~Moore's
-funding.
+This letter serves as justification for a subaward of NSF grant Award
+Number 2012560. Dr.~Moore at the US Naval Academy is uniquely qualified
+to perform two deliverables:
+\begin{enumerate}
+  \item Characterizing permeability, anisotropy, and pore size dynamics
+    to inform Darcy-based homogenized models.
+  \item Developing and validating new parameterizations using machine
+    learning techniques and numerical simulations.
+\end{enumerate}
+These efforts will be coordinate with PI Quaife throughout the duration
+of the award, and they are fundamental to the success of the remaining
+deliverables.
 
-This request is written in consultation with Dr.~Moore. Please contact
-me if further clarification is required.
+Please note that Dr.~Moore was originally a PI on this proposal, but it
+was necessary to restructure his portion of the funding to a sub-award
+as he left Florida State University.
+
+This justification is written in consultation with Dr.~Moore. Please
+contact me if further clarification is required.
 

### 2020-08-26 docs/proposals/NSF/budgets/budgetJustUSNA.tex
working on budget justification

@@
     \hline
-    Total & $\$3,546$ & $\$3,612$ & $\$3,692$ & $\$10,850$ \\
+    Total & $\$3,547$ & $\$3,612$ & $\$3,691$ & $\$10,850$ \\
     \hline
@@
 for co-PI Moore in years 2 and 3.  The expected costs per
-conference participant is $\$1,750$ with a breakdown of $\$600$ for
-airfare, $\$750$ for lodging, $\$56$ for local transportation, $\$144$
+conference participant is $\$1,000$ with a breakdown of $\$300$ for
+airfare, $\$300$ for lodging, $\$56$ for local transportation, $\$144$
 for meals (four days at $\$36$ per day), and $\$200$ for conference
@@
 (Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
-appropriately themed workshops. 
-Alternatively, co-PI Moore may use these travel funds to visit PI Quaife and the funded graduate student at FSU in order to collaborate on the project.
-Travel funds for the first year are removed due to the COVID crisis.
+appropriately themed workshops.  Alternatively, co-PI Moore may use
+these travel funds to visit PI Quaife and the funded graduate student at
+FSU in order to collaborate on the project.  Travel funds for the first
+year are removed due to the COVID crisis.
 %\hfill \\
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{G: Other Direct Costs}
-%\noindent
-\paragraph{\bf Materials and Supplies:} The requested materials and
-supplies of \$1000 in year 1 is to partially fund a laptop or desktop computer for co-PI Moore. The computer will be used for developing the proposed algorithms and
-presenting the results at conferences.
-\\
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection*{G: Other Direct Costs}
+%%\noindent
+%\paragraph{\bf Materials and Supplies:} The requested materials and
+%supplies of $\$1000$ in year 1 is to partially fund a laptop or desktop
+%computer for co-PI Moore. The computer will be used for developing the
+%proposed algorithms and presenting the results at conferences.
+%\\
 
@@
     \hline
-    $\$14,130.92$ & $\$14,374$ & $\$14,669$ & $\$43,174$ \\
+    $\$13,132$ & $\$14,374$ & $\$14,668$ & $\$42,174$ \\
     \hline
@@
 %\noindent
-The US Naval Academy's indirect cost rate is
-10\% for research on modified total direct costs (MTDC).
-The base for overhead is $\$14,130.92$ in year 1, $\$14,374.31$ in
-year 2, and $\$14,668.63$ in year 3.
-The US Naval Academy defines a fiscal year to be July 1-June 30.
+The US Naval Academy's indirect cost rate is 10\% for research on
+modified total direct costs (MTDC).  The base for overhead is
+$\$13,132$ in year 1, $\$14,374$ in year 2, and $\$14,668$ in
+year 3.  The US Naval Academy defines a fiscal year to be July 1-June
+30.
 %\hfill \\
@@
     \hline
-    $\$1,413$ & $\$1,437$ & $\$1,467$ & $\$4,317$ \\
+    $\$1,313$ & $\$1,437$ & $\$1,467$ & $\$4,217$ \\
     \hline
@@
     \hline
-    $\$15,544$ & $\$15,812$ & $\$16,135$ & $\$47,491$ \\
+    $\$14,445$ & $\$15,811$ & $\$16,135$ & $\$46,391$ \\
     \hline

### 2020-08-26 docs/proposals/NSF/budgets/budgetJustificationFSU.tex
working on budget justification

@@
 \subsection*{C: Fringe Benefits}
-{\bf PI:} The fringe benefits of the PI are 17.06\%. \\
+{\bf PI:} The fringe benefits of the PI are 18.54\%. \\
 {\bf Ph.D.:} The fringe benefits of the graduate student are
-0.1\% plus an $\$1,965$ health insurance. \\
+0.6\% plus an $\$1,965$ health insurance. \\
 %\hfill \\
@@
     \hline
-    PI & $\$1,800$ & $\$1,854$ & $\$955$ & $\$4,609$ \\
+    PI & $\$1,956$ & $\$2,015$ & $\$1,037$ & $\$5,008$ \\
     \hline
-    Ph.D. & $\$1,986$ & $\$1,987$ & $\$1,987$ & $\$5,960$ \\
+    Ph.D. & $\$2,091$ & $\$2,095$ & $\$2,099$ & $\$6,285$ \\
     \hline
-    Total & $\$3,786$ & $\$3,841$ & $\$2,942$ & $\$10,569$ \\
+    Total & $\$4,047$ & $\$4,110$ & $\$3,136$ & $\$11,293$ \\
     \hline
@@
 or the Ph.D.~student.  The expected costs per conference participant is
-$\$1,750$ with a breakdown of $\$600$ for airfare, $\$750$ for lodging,
+$\$1,000$ with a breakdown of $\$300$ for airfare, $\$300$ for lodging,
 $\$56$ for local transportation, $\$144$ for meals (four days at $\$36$
-per day), and $\$200$ for conference registration.  Potential meeting
-venues include several SIAM Meetings (Annual Meetings, CSE, Dynamical
-Systems), APS Fluids Meetings, or appropriately themed workshops.  The
-PI and Ph.D.~student will give presentations and actively participate in
-the meeting or workshop.  Travel funds for the first year are removed
-due to the COVID crisis
+per day), and $\$200$ for conference registration. An additional $\$195$
+is budgeted for year 2. Potential meeting venues include several SIAM
+Meetings (Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings,
+or appropriately themed workshops. The PI and Ph.D.~student will give
+presentations and actively participate in the meeting or workshop.
+Travel funds for the first year are removed due to the COVID crisis.
 %\hfill \\
@@
     \hline
-    Domestic Conferences &  & $\$1,750$ & $\$1,750$ & $\$3,500$ \\
+    Domestic Conferences &  & $\$2,195$ & $\$2,000$ & $\$4,195$ \\
     \hline
@@
 \paragraph{\bf Materials and Supplies:} The requested materials and
-supplies is to purchase one $\$1,500$ laptop with accessories, which is
+supplies is to purchase one $\$1,359$ laptop with accessories, which is
 not otherwise available, for the PI and Ph.D.~student in year 1. The
@@
 laptop will be used exclusively for the proposed research. 
+\\
+\paragraph{\bf Subawards:} The requested subaward is for Dr.~Nick Moore
+at the US Naval Academy to provide two of the deliverables as described
+in the scope of work.
 \\
@@
     \hline
-    Materials and Supplies & $\$1,500$ & & & $\$1,500$ \\
+    Materials and Supplies & $\$1,359$ & & & $\$1,359$ \\
     \hline
-    Other & $\$7,336$ & $\$7,409$ & $\$7,484$ & $\$22,229$ \\
+    Subawards & $\$14,445$ & $\$15,811$ & $\$16,135$ & $\$46,391$ \\
     \hline
-    Total & $\$8,836$ & $\$7,409$ & $\$7,484$ & $\$23,729$ \\
+    Other & $\$7,336$ & $\$7,410$ & $\$7,484$ & $\$22,230$ \\
+    \hline
+    Total & $\$23,140$ & $\$23,221$ & $\$23,619$ & $\$69,980$ \\
     \hline
@@
     \hline
-    $\$44,175$ & $\$45,499$ & $\$40,053$ & $\$129,727$ \\
+    $\$58,740$ & $\$62,025$ & $\$56,632$ & $\$177,397$ \\
     \hline
@@
 54\% for research on modified total direct costs (MTDC) which excludes
-tuition. The base for overhead is $\$36,839$ in year 1, $\$38,090$ in
-year 2, and $\$32,569$ in year 3. Florida State University defines a
-fiscal year to be July 1--June 30.
+tuition subaward costs after the first \$25,000. The base for overhead
+is $\$51,504$ in year 1, $\$49,359$ in year 2, and $\$33,013$ in year 3.
+Florida State University defines a fiscal year to be July 1--June 30.
 %\hfill \\
@@
     \hline
-    $\$19,893$ & $\$20,569$ & $\$17,587$ & $\$58,049$ \\
+    $\$27,758$ & $\$26,654$ & $\$17,827$ & $\$72,239$ \\
     \hline
@@
     \hline
-    $\$64,068$ & $\$66,068$ & $\$57,640$ & $\$187,776$ \\
+    $\$86,498$ & $\$88,679$ & $\$74,459$ & $\$249,636$ \\
     \hline

### 2020-08-26 fortran_code/stokesDriver.f

@@ -2,7 +2,7 @@
       implicit real*8 (a-h,o-z)
 
       parameter (ninner = 2**8)
-      parameter (nbodies = 5)
+      parameter (nbodies = 1)
       parameter (nouter = 2**10)
       parameter (ntargets = 50)
       parameter (maxbodies = 10)
@@ -58,17 +58,17 @@ c     Testing for stress tensor
         phi(k) = 0.d0
       enddo
       centerx(1) = -0.5d0
-      centerx(2) = -0.3d0
-      centerx(3) = -0.1d0
-      centerx(4) = +0.1d0
-      centerx(5) = +0.3d0
-      centerx(6) = +0.5d0
+c      centerx(2) = -0.3d0
+c      centerx(3) = -0.1d0
+c      centerx(4) = +0.1d0
+c      centerx(5) = +0.3d0
+c      centerx(6) = +0.5d0
       centery(1) = 0.d0
-      centery(2) = 0.d0
-      centery(3) = 0.d0
-      centery(4) = 0.d0
-      centery(5) = 0.d0
-      centery(6) = 0.d0
+c      centery(2) = 0.d0
+c      centery(3) = 0.d0
+c      centery(4) = 0.d0
+c      centery(5) = 0.d0
+c      centery(6) = 0.d0
 c      
 c      radius(1) = 2.d-1
 c      radius(2) = 2.d-1
@@ -118,7 +118,8 @@ c      phi(2) = 0.d0
       ibary = 1
       ifmm = 1
       maxl = 2000
-      call stokesSolver(ninner,nbodies,nouter,ifmm,ibary,maxl,
+      ibc = 0;
+      call stokesSolver(ninner,nbodies,nouter,ifmm,ibary,ibc,maxl,
      $        x,y,den,iter)
 c     pass in number of points and x and y coordinates and return the
 c     density function on the boundary
@@ -137,10 +138,10 @@ c        print *, 'computeQoiTargets_Bary'
 c      else 
 c        print *, 'computeQoiTargets_trap'      
 c      endif
-      
+c      
       call computeQoiTargets(ninner,nbodies,nouter,ibary,x,y,den,
      $  ntargets*ntargets,xtar,ytar,utar,vtar,press_tar,vort_tar)
-     
+c     
 c      call computeShearStress(ninner,nbodies,nouter,x,y,den,ibary,
 c     $    shear_stress)
 c     pass in the density function and return the shear_stress
[…]

### 2021-05-21 docs/diffusion/diffusion.tex
started to outline a paper for the diffusion solver

\documentclass[preprint, 10pt]{elsarticle}

\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}} \newcommand{\secref}[1]{\ref{#1}}

\input{preambles.tex}
\begin{document}

\title{Diffusion in Cool Domains with BIEs}

\author[Bryan1]{Jesse Cherry}
\author[Alan]{Alan Lindsay}
\author[Bryan1,Bryan2]{Bryan D.~Quaife}
\author[Nick]{M.~Nicholas J.~Moore}

\address[Nick]{Department of Mathematics, United States Naval Academy,
Annapolis, MD, 21402.}
\address[Bryan1]{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
\address[Bryan2]{Geophysical Fluid Dynamics Institute, Florida State
University, Tallahassee, FL, 32306.}
\address[Alan]{Department of Applied \& Computational Math \&
Statistics, University of Notre Dame, South Bend, IN, 46656.}

\begin{abstract} 
\end{abstract}

\begin{keyword}
  keyword 1 \sep keyword 2 \sep keyword 3 
\end{keyword}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}

\cite{chi-moo-qua2020}
\cite{qua-moo2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}

\paragraph{Limitations}

\paragraph{Related Work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Outline of the Paper}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation}
\label{s:formulation}
We are interested in solving the two-dimensional dimensionless diffusion
equation in an unbounded domain $\Omega$ with a homogeneous Dirichlet
boundary condition. For the remainder of the paper, we assume the Peclet
number is one. We an initial condition that is a delta centered at
$\xx^* \in
\Omega$
\begin{subequations}
  \label{eqn:diffusion}
  \begin{alignat}{3}
    \pderiv{c}{t} &= \Delta c, &&\xx \in \Omega,  \\
    c &= 0 &&\xx \in \bd\Omega, \\
    c(\xx,0) &= \delta(\xx - \xx^*_k), \qquad &&\xx \in \Omega.
  \end{alignat}
\end{subequations}
In addition, $c(\xx,t)$ must go to zero as $|\xx|\rightarrow \infty$ for
all time. We note that our solver is easily extended to the case where
the initial condition is a finite sum of weighted delta functions.

To solve~\eqref{eqn:diffusion}, we introduced the Laplace transformed
variable
\begin{align}
  C(\xx,s) = \LL[c](s) = \int_{0}^{\infty} e^{-st} c(\xx,t)\, dt.
\end{align}
Taking the Laplace transform of equation~\eqref{eqn:diffusion}, we
arrive at the elliptic PDE
\begin{subequations}
  \begin{alignat}{3}
    (s - \Delta) C(\xx,s) &= \delta(\xx - \xx^*), \qquad 
      &&\xx \in \Omega, \\
    C(\xx,s) &= 0 &&\xx \in \bd\Omega.
  \end{alignat} 
\end{subequations}
Note that the solution of this PDE depends on $s \in \CC$. For a given
$s$, $C$ can be decomposed as
\begin{align}
  C(\xx,s) = C^{h}(\xx,s) + G(\xx-\xx^*),
\end{align}
where 
\begin{align}
  G(\xx) = \frac{1}{2\pi} K_0\left( \sqrt{s} \|\xx\| \right)
\end{align}
is the fundamental solution of the differential operator $s - \Delta$.
The homogeneous solution $C^{h}(\xx,s)$ must satisfy
\begin{subequations}
  \label{eqn:homoPDE}
  \begin{alignat}{3}
    (s - \Delta) C^{h} &= 0, &&\xx \in \Omega, \\
    C^{h}(\xx,s) &= -G(\xx-\xx^*), \qquad &&\xx \in \bd\Omega.
  \end{alignat}
\end{subequations}
and this guarantees that $C(\xx,s)$ satisfies the homogeneous Dirichlet
boundary condition.

In the following sections we describe integral equation methods to solve
both the homogeneous PDE~\eqref{eqn:homoPDE} and to construct $c(\xx,t)$
by computing a Bromwich integral.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary Integral Equation Formulation} 
\label{sec:bies}
To solve~\eqref{eqn:homoPDE}, we use a boundary integral equation (BIE)
formulation. In this manner, we are able to resolve complex geometries,
achieve high-order accuracy, and satisfy far-field boundary conditions.
Because of the Dirichlet boundary condition, we write $C^{h}(\xx,s)$ as
a double-layer potential 
\begin{align}
  \label{eqn:DLP}
  C^{h}(\xx,s) = \DD[\sigma](\xx) := 
    \frac{1}{2\pi} \int_{\bd \Omega} \pderiv{}{\nn}
    G(\xx - \yy) \sigma(\yy)\, ds_\yy, \quad \xx \in \Omega,
\end{align}
where $G$ is the fundamental solution of $s - \Delta$, and $\nn$ is the
unit outward normal of $\bd\Omega$ at $\yy$. The unknown density
function $\sigma$ satisfies the Fredholm second-kind integral equation
\begin{align}
  \label{eqn:BIE}
  \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx) = -G(\xx - \xx^*),
    \quad \xx \in \bd\Omega.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Inverting the Laplace Transform}
\label{sec:bromwich}
Having a method to solve for $C^h(\xx,s)$ for any $s \in \CC$, we
require a method to recover the $c(\xx,t)$. The inverse Laplace
transform, also known as the Bromwich integral, is
\begin{align*}
  \mathcal{L}^{-1}[C^h](\xx,s) = \frac{1}{2\pi i} 
    \int_{\alpha - i\infty} ^{\alpha + i\infty} 
    e^{st} C^h(\xx,s)\, ds, \quad \xx \in \Omega,
\end{align*}
where $\alpha$ is chosen so that it is larger than the real part of
all the singularities of $C(\xx,s)$. The right-most singularity of
$C(\xx,s)$ has real part 0, so we can choose any value $\alpha > 0$.
This contour of integration is called the Bromwich integral and denoted
by $B$.

Along the Bromwich integral, the integrand $e^{st} C^h(s,t)$ oscillates
and decays algebraically. Practically, this means that numerical
quadrature can not be used to compute the Bromwich integral. However,
the contour $B$ can be replaced with any other contour, so long as it
remains to the right of all the singularities of $C^h(s,t)$. There are a
variety of choices~\cite{tre-wei2014}, and we opt to use the Talbot
contour parameterized as
\begin{align*}
  \alpha(\theta) = ...
\end{align*}
Along this contour, the integrand $e^{st} C^h(s,t)$ does not oscillate,
decays exponentially to zero, and is scaled appropriately with respect
to $t$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the Flux Through $\bd\Omega$}
\label{sec:flux}
In many applications, the flux $c$ through $\bd\Omega$
\begin{align}
  \label{eqn:flux}
  J(t) = \int_{\bd\Omega} \pderiv{}{\nn_\xx}c(\xx,t), ds_\xx,
\end{align}
is required, where $\nn_\xx$ is the unit outward normal at $\xx$.
Computing the flux $J$ requires the flux of $C^h(\xx,s)$ through
$\bd\Omega$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical methods}
\label{s:method}
To solve equation~\eqref{eqn:diffusion}, we require three quadrature
methods. The first is used to solve the second-kind Fredholm integral
equation~\eqref{eqn:BIE} and to evaluate the double-layer
potential~\eqref{eqn:DLP}, and this is described in
Section~\ref{sec:BIE}. The second is to compute the Talbot contour, and
this is described in Section~\ref{sec:talbot}. Finally,
Section~\ref{sec:flux} discusses how the flux is computed through
$\bd\Omega$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solving the BIE}
\label{sec:BIE}
\begin{itemize}
  \item Collocation method
  \item Limiting value at diagonal
  \item Solved with GMRES
  \item Near-singular integration?
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the Inverse Laplace Transform} 
\label{sec:talbot}
\begin{itemize}
  \item Plots of the different contours
  \item Locations of the singularities of $C^h(s,t)$?
  \item Apply the midpoint rule
  \item Show that it converges with a simple numerical example?
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computing the Flux}
\label{sec:flux}
\begin{itemize}
  \item Need normal derivative of double-layer potential
  \item Trick where we add and subtract normal derivative of Laplace DLP
  \item Expected rate of convergence (we still don't fully understand
    this).
\end{itemize}

%%-----------------------------------------------------------------%%
% RESULTS SECTION
%%-----------------------------------------------------------------%%
\section{Numerical Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{\bf Acknowledgments}

\bibliographystyle{plainnat} 
%\biboptions{sort&compress}

\bibliography{refs}

\end{document}

### 2021-06-24 julia_code/postprocess.jl
NM

@@ -43,11 +43,12 @@ function getareas(thlenden::ThLenDenType)
 	if nbods == 0 areavec = [0.0] end
 	return areavec
 end
-# Compute the resistivity/permeability of the porous matrix.
+# Compute the resistivity of the porous matrix.
+# Note: resisitivity = 1/permeability.
 function resistivity(thlenden::ThLenDenType, params::ParamSet, x0::Float64=2.0; rotation::Bool=false)
-	# Retrieve the pressure drop and flux (assuming umax = 1)
+	# Retrieve the pressure drop and flux (assuming umax = 1).
 	pdrop, qavg = getpdrop(thlenden, params, x0, rotation=rotation)
-	# Calculate the total resistivity
+	# Calculate the total resistivity.
 	resist = pdrop/(2*x0*qavg)
 	# If pipe flow (ibc = 0) then remove the contribution from the walls.
 	if params.ibc == 0; resist = x0*(resist - 3); end
@@ -57,8 +58,10 @@ end
 
 #------ ROUTINES TO COMPUTE THE PRESSURE ON THE SURFACE ------#
 #= Note: The purpose of these routines is to compute the pressure on the surface
-of each body, rather than at a set of target points in the fluid domain. =#
-# Fortran wrapper.
+of each body, rather than at a set of target points in the fluid domain. 
+This pressure computation is used to compute the total drag. =#
+
+# Compute the pressure: Fortran wrapper.
 function compute_pressure(xx::Vector{Float64}, yy::Vector{Float64}, 
 		density::Vector{Float64}, npts::Int, nbods::Int, nouter::Int, ibary::Int)
 	pressure = zeros(Float64, npts*nbods)
@@ -70,7 +73,7 @@ function compute_pressure(xx::Vector{Float64}, yy::Vector{Float64},
 	end
 	return pressure
 end
-# Dispatch for ThLenDenType.
+# Compute the pressure: Dispatch for ThLenDenType.
 function compute_pressure(thlenden::ThLenDenType, params::ParamSet;
 		fixpdrop::Bool=false, rotation::Bool=false)
 	@unpack npts, nouter, ibary = params
@@ -148,7 +151,7 @@ function bodyfitgrid(thlenv::Vector{ThetaLenType}, spacevec::Vector{Float64}, np
 	end
 	return xtar, ytar
 end
-# regbodtargs: Set up target points on a regular and body fitted grid.
[…]

### 2021-07-01 docs/diffusion/diffusion.tex
fixed section structuring
layed out first pass at numerical examples

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Computing the Flux}
+\subsection{Computing the Flux}
 \label{sec:flux}
@@
 
+\subsection{Example 1}
+\begin{itemize}
+  \item Analytic solution such as circle in an infinite domain 
+  \item Boundary condition is 0 on the boundary of the circle
+  \item Initial condition is $C_0$ everywhere off the boundary of the
+    circle
+  \item Use Laplace-DLP-Talbot to compute u(x,t) at several time steps
+  \item Provide a convergence study using the exact solution
+  \item Provide a convergence study of the flux through the body
+\end{itemize}
+
+\subsection{Example 2}
+\begin{itemize}
+  \item More general shape, but only 1 of them (star, crescent, ellipse)
+\end{itemize}
+
+\subsection{Example 3}
+\begin{itemize}
+  \item Multiply-connected with all bodies having a Dirichlet boundary
+    condition
+\end{itemize}
+
+\subsection{Example 4}
+\begin{itemize}
+  \item Multiply connected with some domains insulated (Neumann) and
+    others kept at a fixed temperature (Dirichlet)
+\end{itemize}
+
+\subsection{Example 5}
+\begin{itemize}
+  \item Multiply connected with insulated bodies and an array of sinks
+    at one end and sources at the other
+  \item This is just to prove that we can handle different initial
+    conditions of the heat equation than just constant ones.
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-08-02 simulations/plot_stuff.jl
NM

@@ -16,30 +16,55 @@ It will not give two separate displays, even with the reuse=false statement.
 =#
 
 proc_file(label::AbstractString) = string("output_data/proc_data-", label, ".jld2")
+plot_folder() = "zPlots/"
 
 function plot_stuff(label::AbstractString)
 	# Read variables
+	params, thldvec, areas_vec, resist, resist_rot, resist_circs = 
+	load(proc_file(label), "params", "thldvec", "areas_vec", "resist", "resist_rot", "resist_circs")
 
-	params, thldvec, areas, resist, resist_rot = 
-	load(proc_file(label), "params", "thldvec", "areas_vec", "resist", "resist_rot")
-
-	# Extract basic stuff.
+	# Calculate the total area at each time step.
 	nlast = length(thldvec)	
-
-	# Calculate the total area at each time step and plot it.
 	areatot, tt = zeros(Float64, nlast), zeros(Float64, nlast)
 	for nn = 1:nlast 
-		areatot[nn] = sum(areas[nn])	# Sum over all the bodies.
+		areatot[nn] = sum(areas_vec[nn])	# Sum over all the bodies.
 		tt[nn] = thldvec[nn].tt
 	end
-	area_plot = plot(tt, areatot, xlabel="time", ylabel="total area", label="area")
 
-	# Plot the resistivity.
-	resist_plot = plot(tt, resist, reuse=false, xlabel="time", ylabel="resistivity", label="resist")
+	# Calculate the permeability.
+	function perm(resist)
+		abs(resist) > 10 ?  value = 1/resist : value = 0.1
+		return value
+	end
+	# Calculate the permeability ratios.
+	prat = resist_circs ./ resist
+	anis = resist_rot ./ resist
 	
-	display(area_plot)
-	display(resist_plot)
+	# Area plot
+	area_plot = plot(tt, areatot, xlabel="time", ylabel="total area", label="area")
+	
+	# Resistivity Plot
+	resist_plot = plot(tt, resist, reuse=false, xlabel="time", ylabel="resistivity", label="erosion")
+	plot!(resist_plot, tt, resist_circs, label="circles")
+	plot!(resist_plot, tt, resist_rot, label="rotated")
+
+	# Permeability Plot.
+	perm_plot = plot(tt, perm.(resist), reuse=false, xlabel="time", ylabel="permeability", label="erosion")
[…]

### 2022-05-06 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 % Note: All AIP and APS journals use the revtex package; both PRL and PRF are APS.
-\documentclass[reprint, superscriptaddress, notitlepage]{revtex4-1}
+\documentclass[preprint, superscriptaddress, notitlepage]{revtex4-1}
 
-% PACKAGES
-\usepackage{graphicx, amsmath, amssymb, amsfonts, mathtools, mathrsfs, color}
-\usepackage{comment, enumerate, tabularx, multirow}
-\usepackage{natbib, hyperref, url}
-\usepackage{algorithm, algpseudocode, pifont, longtable, subfigure}
-%\usepackage[justification=RaggedRight]{caption}
+%\documentclass{jfm}
+% NOTE: jfm documentclass needed for \upi
+%---------------------------------------------------%
+% Packages from JFM 2020
+%\usepackage[top=1.2in,bottom=1.2in,left=1in, right=1in]{geometry}
+\usepackage{amsfonts, amssymb, array}
+\usepackage[fleqn,reqno]{amsmath}
+\usepackage{graphics, graphicx, subfigure}
+% Replaced subcaption with subfigure
+\usepackage{todonotes, comment, soul, float}
+%---------------------------------------------------%
 
@@
 \newcommand{\np}{\newpage \noindent}
-\newcommand{\HERE}[1]{ \vsp{#1} {\color{blue} HERE} }
-\newcommand{\tofix}{\color{blue}}
-\newcommand{\new}{}		% \color{green}
-\newcommand{\newa}{}		% \color{red}
-\newcommand{\newb}{}		% \color{blue}
-% Basic math, derivatives
-\newcommand{\td}[2]{\frac{d #1 }{d #2}}
-\newcommand{\ttd}[2]{\frac{d^2 #1 }{{d #2}^2}}
-\newcommand{\pd}[2]{ \frac{ \partial #1}{ \partial #2 } }
-\newcommand{\ppd}[2]{ \frac{ \partial^2 #1}{ {\partial #2}^2 } }
-% Basic math, vectors and other
-\newcommand{\BigO}[1]{ \mathcal{O} \left(#1\right) }
-\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
-\newcommand{\grad}{\nabla} 
+% For real and imaginary, could use \Re or \Im, or \mathcal{R}, or \text{Re}
+\newcommand{\Real}{\Re}
+\newcommand{\Imag}{\Im}
+
+%---------------------------------------------------%
+% From JFM 2020
+\newcommand{\bd}{{\partial}}
+\newcommand{\bigO}{{\mathcal{O}}}
+\newcommand{\cc}{{\mathbf{c}}}
+\newcommand{\CC}{{\mathbb{C}}}
+\newcommand{\DD}{{\mathcal{D}}}
+\newcommand{\DDD}{{\boldsymbol{\mathcal D}}}
+\newcommand{\eeta}{{\boldsymbol\eta}}
+\newcommand{\ff}{{\mathbf{f}}}
+\newcommand{\grad}{{\nabla}}
+\newcommand{\II}{{\mathbf{I}}}
+\newcommand{\iin}{\mathrm{in}}
+\newcommand{\llambda}{{\boldsymbol\lambda}}
+\newcommand{\nn}{{\mathbf{n}}}
+\newcommand{\NN}{{\mathcal{N}}}
+\newcommand{\out}{\mathrm{out}}
+\newcommand{\rr}{{\mathbf{r}}}
+\renewcommand{\Re}{{\operatorname{Re}}}
+\renewcommand{\Im}{{\operatorname{Im}}}
+\newcommand{\RR}{{\mathbb{R}}}
+\renewcommand{\ss}{{\mathbf{s}}}
+\newcommand{\ssigma}{{\boldsymbol\sigma}}
+\newcommand{\tar}{\mathrm{tar}}
+\newcommand{\bary}{\mathrm{bary}}
+\newcommand{\trap}{\mathrm{trap}}
+\newcommand{\uu}{{\mathbf{u}}}
+\newcommand{\UU}{{\mathbf{U}}}
+\newcommand{\vv}{{\mathbf{v}}}
+\newcommand{\xx}{{\mathbf{x}}}
+\newcommand{\xxi}{{\boldsymbol{\xi}}}
+\newcommand{\yy}{{\mathbf{y}}}
+\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}} 
+\newcommand{\secref}[1]{\ref{#1}}
+\def\gap{\hspace*{.2in}}
+% Nick's below
+\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
+\newcommand{\ppd}[2]{\frac{\partial^2 #1}{{\partial #2}^2}}
 \newcommand{\abs}[1]{\left| #1 \right|}
-\newcommand{\tavg}[1]{\langle #1 \rangle}
-\newcommand{\norm}[1]{ \left\| #1 \right\| }
-\newcommand{\ip}[1]{ \langle #1 \rangle }
-% For real and imaginary, could use \Re or \Im, or \mathcal{R}, or \text{Re}
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\newcommand{\Vn}{V_\nn}
+\newcommand{\Vs}{V_\ss}
+\newcommand{\CE}{C_E}
+%---------------------------------------------------%
 
@@
 
-\author{M.~N.~J.~Moore}
+\author{Nicholas J.~Moore}
 \affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
@@
 \author{Shang-Huan Chiu}
-\affiliation{Department of Scientific Computing, Florida State
-University, Tallahassee, FL, 32306.}
+\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
 
@@
 
+%Maybe cite: \cite{Rycroft2016}
+% Cite paper by Ladd "Wormhole formation in dissolving fractures"
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
-%Maybe cite: \cite{Rycroft2016}
-
 \begin{comment}
@@
 
-\bibliographystyle{plain}
-\bibliography{refs}
+% NOTE: THIS SECTION HAS BEEN PLAGIARIZED FROM JFM 2020
+% SO WE NEED TO PARAPHRASE IT
+%\begin{comment}
+%-----------------------------------------------------------------------------------------------%
+\section{Governing Equations}
+\label{sec:formulation}
+%-----------------------------------------------------------------------------------------------%
+We start by defining the main variables used to model erosion.  We only
+briefly summarize the model, and a more detailed description can be
+found in previous work~\citep{qua-moo2018}.  We consider flows inside a
+confined geometry $\Omega$ that contains $M$ eroding bodies with
+boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$.  The boundary of the
+fluid domain is $\bd \Omega = \Gamma \cup \gamma_1 \cup \cdots \cup
+\gamma_M$, where $\Gamma$ is the outer boundary, taken to be a slightly
+smoothed version of the boundary of $[-3,3] \times [-1,1]$.  All eroding
+bodies are placed in $[-1,1] \times [-1,1]$ to create a buffer region
+that allows the flow profile imposed at the inlet to transition to the
+more complex flow intervening between the bodies. Neglecting inertial
+forces, the governing equations are
+\begin{equation}
+\label{eqn:erosionModel}
+  \begin{split}
+    \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap 
+      &&\mbox{\em conservation of momentum}, \\
+    \grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap 
+      &&\mbox{\em conservation of mass}, \\
+    \uu = \mathbf{0}, &\hspace{20pt} \xx \in \gamma, \gap 
+      &&\mbox{\em no slip on the eroding bodies}, \\
+    \uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap 
+      &&\mbox{\em outer wall velocity}, \\
+    \Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
+      &&\mbox{\em erosion model}.
+  \end{split}
+\end{equation}
+Here $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
+prescribed Hagen-Poiseuille velocity field, and $\Vn$ is the normal
+velocity of $\gamma$. Since the rate of erosion is much slower than the
+background flow, a quasi-steady approximation justifies the no-slip
+boundary condition. Parameters include the fluid viscosity $\mu$ and the
+material-dependent erosion constant $\CE$. By non-dimensionalizing
+equations~\eqref{eqn:erosionModel}~\citep{qua-moo2018}, we set both
+these parameters to one. The shear stress on $\gamma$ is
+\begin{align}
+  \tau = -(\nabla \uu + \nabla \uu^T) \nn \cdot \ss
+  \label{eqn:shearStress}
+\end{align}
+where, $\nn$ is the normal vector pointing into the body, and $\ss$ is
+the unit tangent vector pointing in the counterclockwise direction. We
+simulate erosion by alternating between solving the fluid equations and
+advancing the eroding grains.  The strength of $\UU$ is adjusted at each
+time step to achieve a constant pressure drop across the channel,
+motivated by the geological situation of a porous medium connecting two
+regions of  fixed hydraulic heads.
+
+%-----------------------------------------------------------------------------------------------%
+\section{Boundary Integral Equation Formulation}
+\label{sec:DLP}
+%-----------------------------------------------------------------------------------------------%
+To accurately solve the governing equations~\eqref{eqn:erosionModel} in
+complex two-dimensional geometries, we reformulate the equations as a
+BIE.  This has the advantage that only the one-dimensional boundary of
+the domain must be discretized, and, with appropriate quadrature
+formulas and fast summation methods, the result is a high-fidelity
+numerical simulation with near-optimal computational complexity.
+
+%-----------------------------------------------------------------------------------------------%
+\subsection{Double-Layer Potential Formulation in $\RR^2$}
+%-----------------------------------------------------------------------------------------------%
+Applying the same approach as our previous work~\citep{qua-moo2018}, we
+start with the double-layer potential 
+\begin{align}
+  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
+  \frac{1}{\pi}\int_{\bd\Omega} 
+    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
+  \label{eqn:velocityDLP}
+\end{align}
+where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
+$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
+is an unknown density function.  We complete the integral equation
+formulation by adding the $M$ Stokeslets,
+$S[\llambda_\ell,\cc_\ell](\xx)$, and $M$ rotlets,
+$R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
+$\ell^{th}$ body~\citep{pow-mir1987}.  Here $\llambda_\ell$ and
+$\xi_\ell$ are the Stokeslet and rotlet strengths, respectively,
+corresponding to the $\ell^{th}$ body.  Then, for any sufficiently
+smooth geometry $\Omega$, the solution of the incompressible Stokes
+equation with a Dirichlet boundary condition $\ff$ is
+\begin{align}
+  \uu(\xx) = \DDD[\eeta](\xx) + 
+    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
+    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
+\end{align}
+where the density function, Stokeslets, and rotlets satisfy
+\begin{subequations}
+\label{eqn:BIE}
+\begin{alignat}{3}
+  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
+    \NN_0[\eeta](\xx) \nonumber \\
+    &\quad + \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
+    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), 
+    \quad &&\qquad\xx \in \bd\Omega, \\
+  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
+    \eeta(\yy)\, ds_\yy, &&\qquad \ell = 1,\ldots,M, \\
+  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
+    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
+    &&\qquad \ell = 1,\ldots,M.
+\end{alignat}
+\end{subequations}
+Here, the null space associated with the flux-free condition of $\ff$ is
+addressed with  $\NN_0$ which is the integral operator with kernel
+$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
+this work, $\ff$ is the prescribed velocity, which is equal to $\UU$ on
+the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
+$\gamma_\ell$, $\ell=1,\ldots,M$.
+
+Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
+corresponding deformation tensor, pressure, and vorticity at $\xx \in
+\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
+To compute the deformation tensor for $\xx \in \gamma$, we include the
+jump term
+\begin{align}
+  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
+    \begin{array}{cc}
+      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
+    \end{array}
+  \right].
+  \label{eqn:deformationJump}
+\end{align}
+Finally, the deformation tensor, pressure, and vorticity due to the
+Stokeslets and rotlets are readily available~\citep{poz1992}. Having
+computed the deformation tensor on $\gamma$, the shear stress is
+computed using equation~\eqref{eqn:shearStress}.
+
+%-----------------------------------------------------------------------------------------------%
+\subsection{Cauchy Integral Representation of the Double-Layer
+Potential}
+\label{sec:DLPcomplex}
+%-----------------------------------------------------------------------------------------------%
+The velocity double-layer potential~\eqref{eqn:velocityDLP}, and its
+corresponding deformation tensor, pressure, and vorticity are all
+written as layer potentials in $\RR^2$.  However, the quadrature method
+we introduce in section~\ref{sec:method} requires complex-valued
+representations. The first step to form a complex representation is to
+write the Laplace double-layer potential as the complex integral
+\begin{align}
+  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
+    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)),
+\end{align}
+where
+\begin{align}
+  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega.
+  \label{eqn:laplaceComplex}
+\end{align}
+Here $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
+counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
+\eta_1 + i \eta_2$ is the complex counterpart of $\eeta =
+(\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
+potential, $\Omega$ is interpreted as a subset of $\RR^2$ or $\CC$.
+Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
+first finding the boundary data of $v$. If $\Omega$ is a
+simply-connected interior domain, then the boundary data of $v$
+satisfies the Sokhotski-Plemelj jump relation
+\begin{align}
+  \label{eqn:SPrelation}
+  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
+\end{align}
+For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
+for multiply-connected domains, such as a porous media, $\bd\Omega$ is
+decomposed into its different connected components and the appropriate
+jump relation is applied.  Having computed the boundary data of the
+holomorphic function $v$, by the Cauchy integral theorem we have
+\begin{subequations}
+  \label{eqn:cauchy}
+  \begin{alignat}{3}
+  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
+    \frac{v(y)}{y-x} \,dy, \\
+  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^2} \, dy, \\
+  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^3} \, dy,
+  \end{alignat}
+\end{subequations}
+for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
+function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
+function defined in equation~\eqref{eqn:laplaceComplex}, and its first
+two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
+
+Finally, the Stokes double-layer potential~\eqref{eqn:velocityDLP} can
+be written using a Laplace double-layer
+potential~\eqref{eqn:laplaceComplex} and its gradients 
+\begin{equation}
+  \label{eqn:Stokes2Laplace}
+  \begin{aligned}
+    \DDD[\eeta](\xx) &= 
+      \frac{1}{2\pi} \int_{\bd\Omega} 
+        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
+      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
+        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
+      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
+        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
+      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
+        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
+  \end{aligned}
+\end{equation}
+Therefore, the Stokes double-layer potential can be written as a sum of
+Cauchy integrals and its first derivative~\citep{bar-wu-vee2015}
+\begin{equation}
+  \begin{aligned}
+    u_1(x) &= \Real (v[\psi_1](x)) + \Real (v'[y\cdot\eta](x)) 
+             -x_1\Real (v'[\eta_1](x)) - x_2\Real (v'[\eta_2](x)), \\
+    u_2(x) &= \Real (v[\psi_2](x)) - \Imag (v'[y\cdot\eta](x)) 
+         +x_1\Imag (v'[\eta_1](x)) + x_2\Imag (v'[\eta_2](x)),
+  \end{aligned}
+  \label{eqn:cauchyVelocity}
+\end{equation}
+where $y \cdot \eta = y_1 \eta_1 + y_2 \eta_2$, 
+\begin{align} 
+  \psi_1=(\eta_1+i\eta_2)\frac{\Real(n)}{n}, \quad
+  \psi_2=(\eta_1+i\eta_2)\frac{\Imag(n)}{n},
+\end{align}
+and $n \in \CC$ is the complex counterpart of the outward unit normal
+$\nn \in \RR^2$.
+
+%-----------------------------------------------------------------------------------------------%
+\subsection{Cauchy Integral Representation for the Gradient of the
+Double-Layer Potential}
+\label{sec:gradDLPcomplex}
+%-----------------------------------------------------------------------------------------------%
+Computing the shear stress and vorticity requires a complex-valued layer
+potential representation of the velocity gradient.  The deformation
+tensor at $x \in \Omega$ is found by computing the derivatives of the
+expressions for $u_1$ and $u_2$ in equation~\eqref{eqn:cauchyVelocity}  
+\begin{equation}
+\label{eqn:cauchyGradient}
+  \begin{aligned}
+    \pderiv{u_1}{x_1} &= +\Real (v'[\psi_1](x)) + 
+    \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) \\
+    &- x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
+    \pderiv{u_1}{x_2} &= - \Imag (v'[\psi_1](x)) - 
+    \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) \\
+    &- \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
+    \pderiv{u_2}{x_1} &= +\Real (v'[\psi_2](x)) - 
+    \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x))  \\
+    &+ x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
+    \pderiv{u_2}{x_2} &= -\Imag (v'[\psi_2](x)) - 
+    \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) \\
+    &+ \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
+  \end{aligned}
+\end{equation}
+The same expressions are used to compute the deformation tensor for $x
+\in \bd\Omega$, except that the jump
+condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
+the shear stress, the deformation tensor on $\bd\Omega$ is applied to
+the normal and tangent vectors as in equation~\eqref{eqn:shearStress}.
+The velocity gradient is also used to compute the vorticity in the fluid
+bulk.  For $x \in \Omega$, the Cauchy integral representation of the
+vorticity at $x \in \Omega$ is
+\begin{align}
+  \omega(x) = 
+    \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))+ 
+    \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
+\end{align}
+%\end{comment}
+
+%\bibliographystyle{plain}
+%\bibliography{refs}
 \end{document}

### 2022-05-06 docs/TexNotes/Notes.tex
NM

@@
 
+%-------------------------------------------------------------%
+% ISOLATING RESISTIVITY DUE TO BODIES
+%-------------------------------------------------------------%
 \subsection{Isolating the resistivity due to the bodies}
@@
 There is a buffer region that lies outside the porous-matrix region ($x_0$ lies in the buffer region), and we would like to remove the contribution from this region.
-Lets regard the total resistivity as an area-integral of resistivity-density, so that we can write the total in terms of the areas of the regions
+Let's regard the total resistivity as an area-integral of resistivity-density, so that we can write the total in terms of the areas of the regions
 \begin{equation}
@@
 
+% New May 5, 2022
+\subsubsection{Modification for free-slip BCs}
+For the free-slip BCs, the resistivity of the buffer region vanishes, $r_b = 0$, giving
+\begin{equation}
+r_m = \frac{A_t}{A_m} r_t = x_0 r_t
+\end{equation}
+
+%-------------------------------------------------------------%
+% RESISTIVITY AND DRAG
+%-------------------------------------------------------------%
 \subsection{Relationship between resistivity and total drag}
@@
 \begin{equation}
-\label{resdrag}
+\label{resdrag1}
 r_{tot} = \frac{3}{8} \frac{F_D}{U}
 \end{equation}
-With this simplification, I see a match between measuring resistivity via the drag \eqref{resdrag} versus measuring resistivity directly via \eqref{resmatrix}.
+With this simplification, I see a match between measuring resistivity via the drag \eqref{resdrag1} versus measuring resistivity directly via \eqref{resmatrix}.
+
+% New May 5, 2022
+\subsubsection{Modification for free-slip BCs}
+If instead, we would like to deal with free-slip top and bottom boundaries, then $\qavg = U$, in which case
+\begin{equation}
+r_{tot} = \frac{1}{4 x_0} \frac{F_D}{U}
+\end{equation}
+where we have set $w=1$. In the post-process code, I set the default of $x_0 = 2$, which gives
+\begin{equation}
+r_{tot} = \frac{1}{8} \frac{F_D}{U}
+\end{equation}
+and this agrees pretty closely with what I see in the data.
+
+Alternatively, if I am looking at only the matrix resistivity $r_m = x_0 r_t$, then
+\begin{equation}
+r_{m} = \frac{1}{4} \frac{F_D}{U}
+\end{equation}
 

### 2022-05-06 ErosionPackage/src/PostProcess.jl

@@ -64,8 +64,18 @@ function resistivity(thlenden::ThLenDenType, params::ParamSet, x0::Float64=2.0; 
 	pdrop, qavg = getpdrop(thlenden, params, x0, rotation=rotation)
 	# Calculate the total resistivity.
 	resist = pdrop/(2*x0*qavg)
+	
+	#= If I were to rewrite this routine, I would remove 
+	the following line in favor of the block below. =#
 	# If pipe flow (ibc = 0) then remove the contribution from the walls.
 	if params.ibc == 0; resist = x0*(resist - 3); end
+
+	#= NOTE: If I were to rewrite this code, I would include the following block.
+	# If pipe flow (ibc = 0) then remove the contribution from the walls.
+	if params.ibc == 0; resist -= 3; end
+	# Remove the effect of the buffer region
+	resist *= x0
+	=#
 	return resist
 end
 

### 2022-05-06 simulations/f1plot.jl

@@ -1,31 +1,0 @@
-#= OBJECTIVE: Output data for Veusz to plot figure 1, single-run data. =#
-include("plot_defns.jl")
-
-#= Note: the format of DragData object is:
-DragData(pdragx, pdragy, vdragx, vdragy, umax, tau_all, atau_all, press_all)
-tau and press take the form tau[1:npts, bod] =#
-
-# Main routine to make plots in Veusz.
-function main(label::AbstractString)
-	# Read variables
-	thldvec, areas_vec, resist, resist_rot, resist_circs, resist_circs_rot, drag_data = 
-		load(proc_file(label), "thldvec", "areas_vec", "resist", "resist_rot", 
-		"resist_circs", "resist_circs_rot", "drag_data")
-
-	# Calculate time-dependent quantities.
-	tt = [ thldvec[nn].tt for nn in eachindex(thldvec)]
-	area = [ sum(areas_vec[nn]) for nn in eachindex(areas_vec) ]
-	hdrag = [ drag_data[nn].pdragx + drag_data[nn].vdragx for nn in eachindex(drag_data)] 
-	vdrag = [ drag_data[nn].pdragy + drag_data[nn].vdragy for nn in eachindex(drag_data)]
-	umax = [ drag_data[nn].umax for nn in eachindex(drag_data) ]
-	# Calculate more quantities.
-	perm = permeability.(resist)
-	anis = anisotropy.(resist, resist_rot)
-	#perm_ratio.(resist, resist_circs)
-
-	# Make text file for Veusz to plot.
-	vplot([tt area resist resist_rot hdrag vdrag umax perm anis], vfolder("fig1"))
-end
-
-# Possible runs: 02-1, 20-2, 20-5, 20-8, 40-3, 40-7, 40-8
-main("40-3")

### 2022-05-06 simulations/plot_defns.jl

@@ -12,7 +12,7 @@ tref() = 0:0.01:0.97		# Reference t-grid
 # Write a text file for Veusz to read for plots.
 function vplot(data::Array, file::AbstractString)
 	iostream = open(file, "w")
-	writedlm(iostream, data)
+	writedlm(iostream, Float32.(data))
 	close(iostream)
 end
 

### 2022-05-06 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 %---------------------------------------------------%
+
+% From Nick's Latex Notes
+\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
+\newcommand {\bq} {\bvec{q}}
+\newcommand{\mean}[1]{\left< #1 \right>}
+\newcommand{\qavg}{\bar{q}}
+\newcommand{\pavg}{\bar{p}}
 
@@
 
+%-----------------------------------------------------------------------------------------------%
+\section{Measuring permeability and other porous-media properties}
+\label{sec:}
+%-----------------------------------------------------------------------------------------------%
+Darcy's law is given by
+\begin{equation}
+\bq = - \bvec{K} \grad \phi
+\end{equation}
+where $\bq$ is the specific discharge, $\phi = z + p/\gamma$ is the hydraulic head, and $\gamma = \rho g$.
+The rank-2 tensor $\bvec{K}$ is the {\em conductivity}, which is related to the {\em permeability} $\bvec{k}$ via $\bvec{K} = \bvec{k} \gamma/\mu$, where $\mu$ is the viscosity of the fluid.
+The units of conductivity are length-per-time (i.e.~velocity) and the units of permeability are length squared.
+Perhaps the most standard parameter to characterize the porous medium is the permeability. We eliminate gravity from consideration to get
+\begin{equation}
+\bq = - \bvec{k} \grad p / \mu
+\end{equation}
+Henceforth, we set $\mu = 1$ by the non-dimensionalization.
+
+Consider first an isotropic medium with {\em scalar} permeability $k$.
+Equivalently, we can introduce a {\em resistivity} simply defined as the reciprocal of permeability, $r = 1/k$.
+Then taking the horizontal component gives
+\begin{equation}
+\label{q1}
+q_1(x,y) = -\frac{1}{r} \pderiv{p}{x}(x,y)
+\end{equation}
+Consider the horizontal discharge, $q_1(x,y)$, averaged over a vertical slice
+\begin{equation}
+\qavg := \frac{1}{2} \int_{-1}^{1} q_1(x_0, y) dy
+\end{equation}
+By conservation of mass, $\qavg$ is independent of the horizontal position $x_0$.
+Since $\bq$ is a volume-average of the tracer velocity, $\qavg$ can be equivalently obtained by averaging the tracer velocity, which is how we will measure this quantity in the simulations.
+
+Next, consider the pressure averaged over a vertical slice
+\begin{equation}
+\pavg(x_0) := \frac{1}{2} \int_{-1}^{1} p(x_0, y) dy
+\end{equation}
+Integrating \eqref{q1} over the domain $[-x_0, x_0] \times [-1,1]$, applying the fundamental theorem of calculus, and rearranging gives
+\begin{equation}
+r = \left( \frac{\pavg(-x_0) - \pavg(x_0)}{2 x_0 \qavg} \right)
+\end{equation}
+This formula gives the resistivity based on measurements of the pressure and discharge.
+
 %\bibliographystyle{plain}

### 2022-05-06 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-Consider first an isotropic medium with {\em scalar} permeability $k$.
-Equivalently, we can introduce a {\em resistivity} simply defined as the reciprocal of permeability, $r = 1/k$.
-Then taking the horizontal component gives
+Consider first an isotropic porous medium with {\em scalar} permeability $k$.
+Furthermore, we seek to characterize the medium by a single, bulk value permeability, so we assume that $k$ is spatially constant.
+Equivalently, we can introduce a {\em resistivity} simply defined as the reciprocal of permeability, $r = 1/k$. Then taking the horizontal component gives
 \begin{equation}
@@
 This formula gives the resistivity based on measurements of the pressure and discharge.
+In particular, to compute the resistivity of the porous matrix, we must set $x_0 =1$ in principle.
+(If a larger value of $x_0$ is chosen, then one would be in effect averaging the porous-medium resistivity with the vanishing resistivity of the empty buffer region.)
 

### 2022-05-07 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \newcommand{\pavg}{\bar{p}}
+\newcommand{\pup}{p_u}
+\newcommand{\pdn}{p_d}
+\newcommand {\bu} {\bvec{u}}
+\newcommand{\nhat}{\hat{\bvec{n}}}
+\newcommand{\shat}{\hat{\bvec{s}}}
+\newcommand{\FD}{\bvec{F_D}}
+\newcommand{\ex}{\hat{\bvec{e}}_1}
 
@@
 %-----------------------------------------------------------------------------------------------%
+
+%-----------------------------------------------------------------------------------------------%
+\subsection{Resistivity and permeability}
 Darcy's law is given by
@@
 \end{equation}
-Integrating \eqref{q1} over the domain $[-x_0, x_0] \times [-1,1]$, applying the fundamental theorem of calculus, and rearranging gives
+In particular, the upstream and downstream pressures are respectively
 \begin{equation}
-r = \left( \frac{\pavg(-x_0) - \pavg(x_0)}{2 x_0 \qavg} \right)
+\pup = \pavg(-1) \, , \quad \pdn = \pavg(1)
 \end{equation}
-This formula gives the resistivity based on measurements of the pressure and discharge.
-In particular, to compute the resistivity of the porous matrix, we must set $x_0 =1$ in principle.
-(If a larger value of $x_0$ is chosen, then one would be in effect averaging the porous-medium resistivity with the vanishing resistivity of the empty buffer region.)
+
+Integrating \eqref{q1} over the porous-medium domain $[-1, 1] \times [-1,1]$, applying the fundamental theorem of calculus, and rearranging gives
+\begin{equation}
+r = \left( \frac{\pup - \pdn}{2 \qavg} \right)
+\end{equation}
+This exact formula gives the resistivity based on measurements of the upstream/downstream pressure and the discharge.
+
+%Note: If a larger value of $x_0$ is chosen, then one would be in effect averaging the porous-medium resistivity with the vanishing resistivity of the empty buffer region.
+
+%-----------------------------------------------------------------------------------------------%
+\subsection{Relationship to total drag}
+
+The resistivity is directly related to the drag exerted by the bodies.
+Indeed, another way to express the Stokes equations is $\grad \cdot \bvec{\sigma} = 0$ where $\bvec{\sigma} = -p \bvec{I} + \mu \left( \grad \bu + \grad \bu^T \right)$ is the stress tensor.
+The divergence theorem gives
+\begin{equation}
+\label{divthm}
+0 = \int_{\Omega} \grad \cdot \bvec{\sigma} \, dV 
+= \int_{\partial \Omega} \bvec{\sigma} \cdot \nhat \, dS
+\end{equation}
+for any domain $\Omega$.  Consider $\Omega$ to be inside $[-x_0, x_0] \times [-1, 1]$, where we will choose $x_0 > 1$ so that $\Omega$ includes the entire porous region.
+The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodible bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$.
+In particular, the total drag exerted by the erodible bodies is given by
+\begin{equation}
+\FD = (D_1, D_2) = -\int_{\gamma} \bvec{\sigma} \cdot \nhat \, dS 
+\end{equation}
+which includes both pressure and viscous drag. The minus sign is due to the orientation of the normal vector. We will mostly be interested in the horizontal component $D_1$.
+
+Meanwhile, the horizontal component of the other term is
+\begin{align}
+\ex \cdot \int_{\Gamma} \bvec{\sigma} \cdot \nhat \, dS = 
+& \int_{-1}^{1} p(-x_0, y) - p(x_0, y) - 2\mu (u_x(-x_0,y) - u_x(x_0,y)) dy \, + \\
+& \int_{-x_0}^{x_0} \mu (u_y(x,1) - u_y(x,-1)) dx
+\end{align}
+If we take $x_0$ sufficiently far away, then the viscous terms involving $u_x$ will become small as the velocity field tends to a uniform flow.
+Meanwhile, the contribution from the pressure is well approximated by the upstream and downstream average pressures $\pup$ and $\pdn$ as introduced in the previous section.
+This gives
+\begin{equation}
+D_1 \approx 2 (\pup - \pdn)
+\end{equation}
+
+Therefore we have the relationship
+\begin{equation}
+r = \frac{D_1}{4 \qavg}
+\end{equation}
 

### 2022-05-08 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 % Basic editing
-\newcommand{\tocite}{{\color{blue}(to cite)}}
 \newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
 \newcommand{\np}{\newpage \noindent}
+\newcommand{\tocite}{ {\color{blue}(to cite)} }
+\newcommand{\nick}[1]{ {\color{red} #1} }
 % For real and imaginary, could use \Re or \Im, or \mathcal{R}, or \text{Re}
@@
 \renewcommand{\ss}{{\mathbf{s}}}
-\newcommand{\ssigma}{{\boldsymbol\sigma}}
 \newcommand{\tar}{\mathrm{tar}}
@@
 % From Nick's Latex Notes
-\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
+\newcommand{\bvec}[1]{\mathbf{#1}}
+%{\ensuremath{\boldsymbol{#1}}}
 \newcommand {\bq} {\bvec{q}}
@@
 \newcommand{\pdn}{p_d}
-\newcommand {\bu} {\bvec{u}}
-\newcommand{\nhat}{\hat{\bvec{n}}}
-\newcommand{\shat}{\hat{\bvec{s}}}
-\newcommand{\FD}{\bvec{F_D}}
-\newcommand{\ex}{\hat{\bvec{e}}_1}
+\newcommand{\stress}{{\boldsymbol \sigma}}
+\newcommand{\FD}{\bvec{F}_d}
+\newcommand{\ex}{ {\bvec{e}}_1}
 
@@
 \end{equation}
-Here $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
-prescribed Hagen-Poiseuille velocity field, and $\Vn$ is the normal
-velocity of $\gamma$. Since the rate of erosion is much slower than the
-background flow, a quasi-steady approximation justifies the no-slip
-boundary condition. Parameters include the fluid viscosity $\mu$ and the
-material-dependent erosion constant $\CE$. By non-dimensionalizing
-equations~\eqref{eqn:erosionModel}~\citep{qua-moo2018}, we set both
-these parameters to one. The shear stress on $\gamma$ is
+Here $\uu$ is the fluid velocity, $p$ is the pressure, \nick{\st{$\UU$ is a
+prescribed Hagen-Poiseuille velocity field}, $\UU$ will be far-field uniform flow $\UU = (U,0)$, where the value $U = U(t)$ is adjusted to keep the pressure drop constant in time,}
+%
+and $\Vn$ is the normal velocity of $\gamma$.
+Since the rate of erosion is much slower than the background flow, a quasi-steady approximation justifies the no-slip boundary condition.
+Parameters include the fluid viscosity $\mu$ and the material-dependent erosion constant $\CE$.
+By non-dimensionalizing equations~\eqref{eqn:erosionModel}~\citep{qua-moo2018}, we set both these parameters to one.
+The shear stress on $\gamma$ is
 \begin{align}
@@
 \begin{equation}
-\qavg := \frac{1}{2} \int_{-1}^{1} q_1(x_0, y) dy
+\qavg := \frac{1}{2} \int_{-1}^{1} q_1(x_0, y) dy = U
 \end{equation}
-By conservation of mass, $\qavg$ is independent of the horizontal position $x_0$.
+By conservation of mass, $\qavg$ is independent of the horizontal position $x_0$ and is equal to the imposed value $U$.
 Since $\bq$ is a volume-average of the tracer velocity, $\qavg$ can be equivalently obtained by averaging the tracer velocity, which is how we will measure this quantity in the simulations.
@@
 \begin{equation}
-r = \left( \frac{\pup - \pdn}{2 \qavg} \right)
+r = \frac{\pup - \pdn}{2 U}
 \end{equation}
@@
 The resistivity is directly related to the drag exerted by the bodies.
-Indeed, another way to express the Stokes equations is $\grad \cdot \bvec{\sigma} = 0$ where $\bvec{\sigma} = -p \bvec{I} + \mu \left( \grad \bu + \grad \bu^T \right)$ is the stress tensor.
+Indeed, another way to express the Stokes equations is $\grad \cdot \stress = 0$ where $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$ is the stress tensor.
 The divergence theorem gives
@@
 \label{divthm}
-0 = \int_{\Omega} \grad \cdot \bvec{\sigma} \, dV 
-= \int_{\partial \Omega} \bvec{\sigma} \cdot \nhat \, dS
+0 = \int_{\Omega} \grad \cdot \stress \, dV 
+= \int_{\partial \Omega} \stress \cdot \nn \, ds
 \end{equation}
@@
 \begin{equation}
-\FD = (D_1, D_2) = -\int_{\gamma} \bvec{\sigma} \cdot \nhat \, dS 
+\FD = -\int_{\gamma} \stress \cdot \nn \, ds
 \end{equation}
-which includes both pressure and viscous drag. The minus sign is due to the orientation of the normal vector. We will mostly be interested in the horizontal component $D_1$.
+which includes both pressure and viscous drag. The minus sign is due to the orientation of the normal vector. We will mostly be interested in the horizontal drag $\FD \cdot \ex$. \\
 
-Meanwhile, the horizontal component of the other term is
+\nick{Need to check sign on drag and check whether I want the drag {\em on} the bodies or exerted {\em by} the bodies.} \\
+
+Consider now the contribution to \eqref{divthm} from the outer boundary $\Gamma$. The horizontal component of this term is
 \begin{align}
-\ex \cdot \int_{\Gamma} \bvec{\sigma} \cdot \nhat \, dS = 
-& \int_{-1}^{1} p(-x_0, y) - p(x_0, y) - 2\mu (u_x(-x_0,y) - u_x(x_0,y)) dy \, + \\
+\ex \cdot \int_{\Gamma} \stress \cdot \nn \, ds = 
+& \int_{-1}^{1} p(-x_0, y) - p(x_0, y) - 2\mu (u_x(-x_0,y) - u_x(x_0,y)) \, dy \, + \\
 & \int_{-x_0}^{x_0} \mu (u_y(x,1) - u_y(x,-1)) dx
@@
 \begin{equation}
-D_1 \approx 2 (\pup - \pdn)
+\FD \cdot \ex \approx 2 (\pup - \pdn)
 \end{equation}
@@
 \begin{equation}
-r = \frac{D_1}{4 \qavg}
+r \approx \frac{1}{4 U}  \, \FD \cdot \ex
 \end{equation}

### 2022-05-08 ErosionPackage/src/PostProcess.jl

@@ -71,10 +71,9 @@ function resistivity(thlenden::ThLenDenType, params::ParamSet, x0::Float64=2.0; 
 	if params.ibc == 0; resist = x0*(resist - 3); end
 
 	#= NOTE: If I were to rewrite this code, I would include the following block.
-	# If pipe flow (ibc = 0) then remove the contribution from the walls.
-	if params.ibc == 0; resist -= 3; end
-	# Remove the effect of the buffer region
-	resist *= x0
+	resist = 0.5*pdrop/qavg
+	params.ibc == 0 && (resist -= 3*x0)
+	#params.ibc == 0 ? resist -= 3*x0 : nothing
 	=#
 	return resist
 end

### 2022-05-08 docs/PhysicsPaper/StokesErosion.tex
NM

@@
-%\documentclass[3p]{elsarticle}
+\documentclass[3p]{elsarticle}
 
@@
 % Note: All AIP and APS journals use the revtex package; both PRL and PRF are APS.
-\documentclass[preprint, superscriptaddress, notitlepage]{revtex4-1}
+%\documentclass[preprint, superscriptaddress, notitlepage]{revtex4-1}
+
+% Physica D is elsevier 
+%\documentclass[review]{elsarticle}
 
@@
 \author{Nicholas J.~Moore}
-\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+%\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
 \author{Bryan D.~Quaife}
-\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+%\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
 \author{Shang-Huan Chiu}
-\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
+%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
 
@@
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure*}[] %\centering
+\begin{figure*}[] \centering
         \subfigure[ Vorticity field]{ \label{FigVort}
@@
 
+%---------------------------------------------------------%
+\begin{figure*}%[htbp]
+\centering \label{}
+\includegraphics[width = 0.99 \textwidth]{./figs/figA.pdf}
+\caption{caption}
+\end{figure*}
+%---------------------------------------------------------%
+
 %\bibliographystyle{plain}

### 2022-05-13 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 %-----------------------------------------------------------------------------------------------%
-We start by defining the main variables used to model erosion.  We only
-briefly summarize the model, and a more detailed description can be
-found in previous work~\citep{qua-moo2018}.  We consider flows inside a
-confined geometry $\Omega$ that contains $M$ eroding bodies with
-boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$.  The boundary of the
-fluid domain is $\bd \Omega = \Gamma \cup \gamma_1 \cup \cdots \cup
-\gamma_M$, where $\Gamma$ is the outer boundary, taken to be a slightly
-smoothed version of the boundary of $[-3,3] \times [-1,1]$.  All eroding
-bodies are placed in $[-1,1] \times [-1,1]$ to create a buffer region
-that allows the flow profile imposed at the inlet to transition to the
-more complex flow intervening between the bodies. Neglecting inertial
-forces, the governing equations are
+
+Consider an incompressible, Stokes flow inside domain $\Omega$ containing $M$ erodable bodies.
+The outer boundary of the domain, denoted $\Gamma$, is a slightly smoothed version of the boundary of $[-3,3] \times [-1,1]$, with the fluid flow primarily moving from left to right.
+The erodable bodies, with boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$, all sit inside of the middle region $[-1,1] \times [-1,1]$.
+The boundary of the fluid domain is thus $\bd \Omega = \Gamma \cup \gamma_1 \cup \cdots \cup \gamma_M$.
+The space to the left and right of $[-1,1] \times [-1,1]$ serve as buffers to allow the flow profile imposed at the inlet ($x=-3$) and outlet ($x=3$) to gradually adjust to the presence of the bodies.
+The equations governing the velocity $\uu$ and pressure $p$ of the fluid consist of the incompressible, Stokes equations coupled to boundary conditions:
 \begin{equation}
-\label{eqn:erosionModel}
+\label{eqn:StokesEq}
   \begin{split}
@@
     \uu = \mathbf{0}, &\hspace{20pt} \xx \in \gamma, \gap 
-      &&\mbox{\em no slip on the eroding bodies}, \\
+      &&\mbox{\em no slip on the erodable bodies}, \\
     \uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap 
-      &&\mbox{\em outer wall velocity}, \\
-    \Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
-      &&\mbox{\em erosion model}.
+      &&\mbox{\em outer wall velocity}.
   \end{split}
 \end{equation}
-Here $\uu$ is the fluid velocity, $p$ is the pressure, \nick{\st{$\UU$ is a
-prescribed Hagen-Poiseuille velocity field}, $\UU$ will be far-field uniform flow $\UU = (U,0)$, where the value $U = U(t)$ is adjusted to keep the pressure drop constant in time,}
-%
+Above, $\UU$ represents the fluid velocity imposed along the outer boundary $\Gamma$, in particular at the inlet and outlet, as well as along the top and bottom walls.
+In this work, we impose a {\em uniform} flow profile at the inlet and outlet, i.e.~$\UU = (U,0)$ at $x=\pm 3$ (or rather, along the slightly curved version of these vertical lines, due to domain smoothing), although previous works employed a parabolic (or Poiseuille) flow profile \cite{Quaife2018, chiu2020viscous}.
+Further, we will allow the imposed flow speed to change with time $U = U(t)$ to enforce, for example, a desired pressure drop across the flow cell.
+To nondimensionalize the above system, we set the fluid viscosity to unity, $\mu = 1$.
+
+We consider erosion
+
+% REWRITTEN ABOVE
+
 and $\Vn$ is the normal velocity of $\gamma$. 
@@
 \begin{align}
+\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
+      &&\mbox{\em erosion model}. \\
 \tau = -(\nabla \uu + \nabla \uu^T) \nn \cdot \ss
@@
 regions of  fixed hydraulic heads.
+
+%to transition to the more complex flow intervening between the bodies.
 
@@
 for any domain $\Omega$.  Consider $\Omega$ to be inside $[-x_0, x_0] \times [-1, 1]$, where we will choose $x_0 > 1$ so that $\Omega$ includes the entire porous region.
-The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodible bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$.
-In particular, the total drag exerted by the erodible bodies is given by
+The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodable bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$.
+In particular, the total drag exerted by the erodable bodies is given by
 \begin{equation}
@@
 
-%\bibliographystyle{plain}
-%\bibliography{refs}
+\bibliographystyle{plain}
+\bibliography{refs}
 \end{document}

### 2022-05-13 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-Consider an incompressible, Stokes flow inside domain $\Omega$ containing $M$ erodable bodies.
-The outer boundary of the domain, denoted $\Gamma$, is a slightly smoothed version of the boundary of $[-3,3] \times [-1,1]$, with the fluid flow primarily moving from left to right.
-The erodable bodies, with boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$, all sit inside of the middle region $[-1,1] \times [-1,1]$.
+Consider an incompressible, Stokes flow inside a domain $\Omega$ containing $M$ erodable bodies.
+We take the outer boundary $\Gamma$ to be a slightly smoothed version of the boundary of $[-3,3] \times [-1,1]$, and the fluid flow is primarily from left to right.
+The erodable bodies, with boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$, all sit inside of the central region $[-1,1] \times [-1,1]$.
 The boundary of the fluid domain is thus $\bd \Omega = \Gamma \cup \gamma_1 \cup \cdots \cup \gamma_M$.
-The space to the left and right of $[-1,1] \times [-1,1]$ serve as buffers to allow the flow profile imposed at the inlet ($x=-3$) and outlet ($x=3$) to gradually adjust to the presence of the bodies.
+The empty space to the left and right of $[-1,1] \times [-1,1]$ serve as buffer regions to allow the flow profile imposed at the inlet ($x=-3$) and outlet ($x=3$) to gradually adjust to the presence of the bodies.
 The equations governing the velocity $\uu$ and pressure $p$ of the fluid consist of the incompressible, Stokes equations coupled to boundary conditions:
@@
 Above, $\UU$ represents the fluid velocity imposed along the outer boundary $\Gamma$, in particular at the inlet and outlet, as well as along the top and bottom walls.
-In this work, we impose a {\em uniform} flow profile at the inlet and outlet, i.e.~$\UU = (U,0)$ at $x=\pm 3$ (or rather, along the slightly curved version of these vertical lines, due to domain smoothing), although previous works employed a parabolic (or Poiseuille) flow profile \cite{Quaife2018, chiu2020viscous}.
-Further, we will allow the imposed flow speed to change with time $U = U(t)$ to enforce, for example, a desired pressure drop across the flow cell.
+In this work, we impose a {\em uniform} flow profile at the inlet and outlet, i.e.~$\UU = (U,0)$ at the inlet and outlet which are approximately situated at $x=\pm 3$ respectively (the actual location is modified somewhat by the domain smoothing).
+We choose the uniform flow profile, as opposed to for instance a Poiseuille flow profile employed by previous work \cite{Quaife2018, chiu2020viscous}, for a few reason.
+First, it will simplify the calculation of porous-medium properties, such as permeability and anisotropy, that will be described later, and second, it may more realistically model the flow impinging upon a porous medium.
+We will allow the imposed flow speed to change with time $U = U(t)$ to enforce, for example, a desired pressure drop across the flow cell.
 To nondimensionalize the above system, we set the fluid viscosity to unity, $\mu = 1$.
 
-We consider erosion
-
-% REWRITTEN ABOVE
-
-and $\Vn$ is the normal velocity of $\gamma$. 
-Since the rate of erosion is much slower than the background flow, a quasi-steady approximation justifies the no-slip boundary condition. 
-Parameters include the fluid viscosity $\mu$ and the material-dependent erosion constant $\CE$.
-By non-dimensionalizing equations~\eqref{eqn:erosionModel}~\citep{qua-moo2018}, we set both these parameters to one.
-The shear stress on $\gamma$ is
+The embedded bodies may erode in response to the shear stresses induced by the intervening fluid flow.
+Erosion typically occurs over much longer timescales than does the fluid flow, permitting a {\em quasi-steady} approximation.
+In this approximation, the configuration of bodies is held fixed to compute the {\em steady} Stokes flow determined by \eqref{eqn:StokesEq}, and then this flow field determines the stresses acting to erode each body.
+We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface.
+The material loss gives rise to an inward velocity of the solid surface, $\Vn$, pointing in the direction normal to the surface.
+The erosion law is thus expressed as
 \begin{align}
-\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
-      &&\mbox{\em erosion model}. \\
+\Vn = \CE \, \abs{\tau}, 
+	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em erosion model}, \\
 \tau = -(\nabla \uu + \nabla \uu^T) \nn \cdot \ss
+	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
   \label{eqn:shearStress}
 \end{align}
-where, $\nn$ is the normal vector pointing into the body, and $\ss$ is
-the unit tangent vector pointing in the counterclockwise direction. We
-simulate erosion by alternating between solving the fluid equations and
-advancing the eroding grains.  The strength of $\UU$ is adjusted at each
-time step to achieve a constant pressure drop across the channel,
-motivated by the geological situation of a porous medium connecting two
-regions of  fixed hydraulic heads.
+where $\nn$ is a unit normal vector pointing into each body, $\ss$ is
+a unit tangent vector pointing in the counterclockwise direction, and $\CE$ is a material-dependent erosion constant.
+
+% SNIPPETS 
+%The strength of $\UU$ is adjusted at each time step to achieve a constant pressure drop across the channel, motivated by the geological situation of a porous medium connecting two regions of  fixed hydraulic heads.
 

### 2022-05-13 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 %-----------------------------------------------------------------------------------------------%
+
+\vsp{2} \nick{Finished rewording up to here} \vsp{2}
+
 To accurately solve the governing equations~\eqref{eqn:erosionModel} in
@@
 
+Probably should just use
+\begin{equation}
+k = \frac{2U}{\pup - \pdn}
+\end{equation}
 %Note: If a larger value of $x_0$ is chosen, then one would be in effect averaging the porous-medium resistivity with the vanishing resistivity of the empty buffer region.
@@
 \begin{equation}
-r \approx \frac{1}{4 U}  \, \FD \cdot \ex
+\label{ResistDrag}
+1/k \approx \frac{1}{4 U}  \, \FD \cdot \ex
 \end{equation}
@@
 \centering \label{}
-\includegraphics[width = 0.99 \textwidth]{./figs/figA.pdf}
-\caption{caption}
+\includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
+\caption{A single simulation of porous-medium erosion.
+The initial configuration consists of 80 circular bodies of random size and position, as seen in Fig.~1?
+a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases.
+b) Resistance to flow can be characterized by either the inverse permeability $1/k$ or the cumulative drag, the two of which are related through \eqref{ResistDrag}.
+Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
+c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium.
+Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
+}
 \end{figure*}

### 2022-05-16 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{figure*}%[htbp]
-\centering \label{}
+\centering \label{fig2}
 \includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
 \caption{A single simulation of porous-medium erosion.
-The initial configuration consists of 80 circular bodies of random size and position, as seen in Fig.~1?
+The initial configuration consists of 100 circular bodies of random size and position, as seen in Fig.~1?
 a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases.
-b) Resistance to flow can be characterized by either the inverse permeability $1/k$ or the cumulative drag, the two of which are related through \eqref{ResistDrag}.
+b) Resistance to flow can be characterized by either the inverse permeability, $1/k$, or the cumulative drag, the two of which are related through \eqref{ResistDrag}.
 Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
@@
 %---------------------------------------------------------%
+% Data from 100-3
+
+%---------------------------------------------------------%
+\begin{figure*}%[htbp]
+\centering \label{fig3}
+\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
+\caption{
+a)
+}
+\end{figure*}
+%---------------------------------------------------------%
+% Data from 100-3
+
+Fig. 2 clearly shows a stark difference in the  permeability to flow in the horizontal versus vertical directions.
+
+Text for Fig 3: 
+The anisotropy of permeability grows large, up to a value of 4 during the middle portion of the simulation. The figure also shows the anisotropy of the circular grid.
 

### 2022-05-16 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \newcommand{\ex}{ {\bvec{e}}_1}
+
+% New
+\newcommand{\anis}{\mathcal{A}}
 
@@
 
+The anisotropy of permeability is
+\begin{equation}
+\anis = k_1 / k_2
+\end{equation}
+
+There are two possible explanations for how erosion creates anisotropy in the microstructure.
+First, the shear stresses could carve each individual body into a more slender form, thus creating anisotropy at the level of individual grains.
+Second, by removing material in a non-uniform way, could preferentially disintegrate certain bodies before others, leaving an overall configuration that exhibits anisotropy on the large scale.
+We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively.
+As an extreme example, a horizontal line of circular bodies would exhibit configurational anisotropy but no shape anisotropy.
+Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit  shape anisotropy but no configurational anisotropy.
+
+We note that channelization is related to both shape and configurational anisotropy....
+
+It is possible to device a test to isolate these two types of anisotropy.
+Introduce circular bodies with same centers of mass...
+Thus, the configurational anisotropy is defined as
+\begin{equation}
+\anis_C = k_1^{(c)} / k_2^{(c)}
+\end{equation}
+
+The total anisotropy is the produce of the shape and configurational
+\begin{equation}
+\anis = \anis_S \anis_C
+\end{equation}
+
 %---------------------------------------------------------%
@@
 
-Fig. 2 clearly shows a stark difference in the  permeability to flow in the horizontal versus vertical directions.
-
 Text for Fig 3: 

### 2022-05-16 simulations/plot_defns.jl

@@ -18,14 +18,10 @@ end
 
 # Calculate the permeability from resistivity.
 function permeability(resist::AbstractFloat)
-	rthresh = 10.0
+	rthresh = 1.0
 	resist > rthresh ? value = 1/resist : value = 1/rthresh
 	return value
 end
-# Calculate the anistropy from resistivities.
-anisotropy(resist::AbstractFloat, resist_rot::AbstractFloat) = resist_rot/resist
-# Calculate the ratio of permeabilities, comparing the eroded geometry to the circular one.
-perm_ratio(resist::AbstractFloat, resist_circs::AbstractFloat) = resist_circs/resist
 
 # Interpolate a variable (e.g. resistivity) on the reference t-grid.
 function interp(variable::Vector{<:AbstractFloat})

### 2022-05-18 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively.
-As an extreme example, a horizontal line of circular bodies would exhibit configurational anisotropy but no shape anisotropy.
-Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit  shape anisotropy but no configurational anisotropy.
+As an extreme example, a tightly spaced row of circular bodies would exhibit configurational anisotropy but no shape anisotropy.
+Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit high shape anisotropy and low configurational anisotropy.
 

### 2022-05-18 simulations/plot_defns.jl

@@ -4,14 +4,15 @@ using Erosion, FileIO, DelimitedFiles, Interpolations, Statistics
 using Plots; plotlyjs()
 
 # Set file and folder names, t-grid.
-proc_file(label::AbstractString) = "output_data/proc_data-$(label).jld2"
+proc_file(run::AbstractString) = "output_data/proc_data-$(run).jld2"
 plot_folder() = "zPlots/"	# Plot folder
 vfolder(name::AbstractString) = "veusz_data/$(name).txt"
-tref() = 0:0.01:0.97		# Reference t-grid
+tref() = 0:0.1:0.97		# Reference t-grid
 
 # Write a text file for Veusz to read for plots.
-function vdata(data::Array, file::AbstractString)
+function vdata(data::Array, desc::AbstractString, file::AbstractString)
 	iostream = open(file, "w")
+	writedlm(iostream, ["descriptor $desc"])
 	writedlm(iostream, Float32.(data))
 	close(iostream)
 end

### 2022-05-18 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in the Stokes regime of groundwater flow \cite{Quaife2018}.
-Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{Quaife2018}, and can simulate the erosion of order hundreds of solid bodies (please see \cite{Mitchell2016} for related work).
+Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}.
+Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of order hundreds of solid bodies (please see \cite{Mitchell2016} for related work).
 The recent incorporation of barycentric interpolation methods permits simulation of tightly packed configurations (cite new paper with Shang).
@@
 Consider an incompressible, Stokes flow inside a domain $\Omega$ containing $M$ erodable bodies.
-We take the outer boundary $\Gamma$ to be a slightly smoothed version of the boundary of $[-3,3] \times [-1,1]$, and the fluid flow is primarily from left to right.
+We take the outer boundary $\Gamma$ to be a slightly smoothed version of the boundary of $[-3,3] \times [-1,1]$.
+The fluid flow is primarily from left to right, so that the inlet and outlet are located at approximately $x=-3$ and $+3$ respectively (the actual locations are slightly curved versions of these vertical lines due to domain smoothing).
 The erodable bodies, with boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$, all sit inside of the central region $[-1,1] \times [-1,1]$.
 The boundary of the fluid domain is thus $\bd \Omega = \Gamma \cup \gamma_1 \cup \cdots \cup \gamma_M$.
-The empty space to the left and right of $[-1,1] \times [-1,1]$ serve as buffer regions to allow the flow profile imposed at the inlet ($x=-3$) and outlet ($x=3$) to gradually adjust to the presence of the bodies.
+The empty space to the left and right of $[-1,1] \times [-1,1]$ serve as buffer regions to allow the flow profile imposed at the inlet and outlet to gradually adjust to the presence of the bodies.
 The equations governing the velocity $\uu$ and pressure $p$ of the fluid consist of the incompressible, Stokes equations coupled to boundary conditions:
@@
 Above, $\UU$ represents the fluid velocity imposed along the outer boundary $\Gamma$, in particular at the inlet and outlet, as well as along the top and bottom walls.
-In this work, we impose a {\em uniform} flow profile at the inlet and outlet, i.e.~$\UU = (U,0)$ at the inlet and outlet which are approximately situated at $x=\pm 3$ respectively (the actual location is modified somewhat by the domain smoothing).
-We choose the uniform flow profile, as opposed to for instance a Poiseuille flow profile employed by previous work \cite{Quaife2018, chiu2020viscous}, for a few reason.
-First, it will simplify the calculation of porous-medium properties, such as permeability and anisotropy, that will be described later, and second, it may more realistically model the flow impinging upon a porous medium.
+In this work, we impose a {\em uniform} flow profile along $\Gamma$, i.e.~$\UU = (U,0)$, although other choices are possible, for example a Poiseuille profile as employed in previous work \cite{quaife2018boundary, chiu2020viscous}.
+The advantages of the uniform profile are: (1) it will simplify the calculation of porous-medium properties, such as permeability and anisotropy, that will be described later; and (2), it may more realistically model the flow impinging upon a porous medium.
 We will allow the imposed flow speed to change with time $U = U(t)$ to enforce, for example, a desired pressure drop across the flow cell.
@@
 Erosion typically occurs over much longer timescales than does the fluid flow, permitting a {\em quasi-steady} approximation.
-In this approximation, the configuration of bodies is held fixed to compute the {\em steady} Stokes flow determined by \eqref{eqn:StokesEq}, and then this flow field determines the stresses acting to erode each body.
-We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface.
+In this approximation, the configuration of bodies is held fixed in order to compute the {\em steady} Stokes flow determined by \eqref{eqn:StokesEq}, and then this flow field determines the stresses acting to erode each body.
+We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface (CITE previous erosion work).
 The material loss gives rise to an inward velocity of the solid surface, $\Vn$, pointing in the direction normal to the surface.
@@
 %-----------------------------------------------------------------------------------------------%
-\section{Boundary Integral Equation Formulation}
+\section{Boundary Integral Equation and Cauchy Integral Formulation}
 \label{sec:DLP}
+%-----------------------------------------------------------------------------------------------%
+
+In order to accurately and efficiently compute the Stokes flow governed by \eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE).
+The boundary integral equations are first formulated in $\RR^2$ and then recast in terms of a Cauchy integral.
+The Cauchy integral representation enables a barycentric quadrature method to accurately compute the flow intervening between nearly contacting bodies, as is required by the dense configurations examined in this work.
+
+% SNIPPET
+%This has the advantage that only the one-dimensional boundary of the domain must be discretized, and, with appropriate quadrature formulas and fast summation methods, the result is a high-fidelity numerical simulation with near-optimal computational complexity.
+
+%-----------------------------------------------------------------------------------------------%
+\subsection{Boundary Integral Representation in $\RR^2$}
 %-----------------------------------------------------------------------------------------------%
@@
 
-To accurately solve the governing equations~\eqref{eqn:erosionModel} in
-complex two-dimensional geometries, we reformulate the equations as a
-BIE.  This has the advantage that only the one-dimensional boundary of
-the domain must be discretized, and, with appropriate quadrature
-formulas and fast summation methods, the result is a high-fidelity
-numerical simulation with near-optimal computational complexity.
-
-%-----------------------------------------------------------------------------------------------%
-\subsection{Double-Layer Potential Formulation in $\RR^2$}
-%-----------------------------------------------------------------------------------------------%
 Applying the same approach as our previous work~\citep{qua-moo2018}, we
@@
 %-----------------------------------------------------------------------------------------------%
-\subsection{Cauchy Integral Representation of the Double-Layer
-Potential}
+\subsection{Cauchy Integral Formulation}
 \label{sec:DLPcomplex}

### 2022-05-19 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 %\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+
+\author{Jake Cherry}
+%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
+
+\author{Shang-Huan Chiu}
+%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
+
 \author{Bryan D.~Quaife}
 %\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
-\author{Shang-Huan Chiu}
-%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
 
@@
 The Cauchy integral representation enables a barycentric quadrature method to accurately compute the flow intervening between nearly contacting bodies, as is required by the dense configurations examined in this work.
+
+\nick{Perhaps you can combine the real BIE and Cauchy representation into one section to condense it and to make the complex analysis take more center stage.}
 
@@
 \label{ResistDrag}
-1/k \approx \frac{1}{4 U}  \, \FD \cdot \ex
+1/k_1 \approx \frac{1}{4 U}  \, \FD \cdot \ex
 \end{equation}
@@
 
-The total anisotropy is the produce of the shape and configurational
+The total anisotropy is the product of the shape and configurational
 \begin{equation}
@@
 
+%---------------------------------------------------------%
+\begin{figure*}%[htbp]
+\centering \label{fig4}
+\includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
+\caption{
+a) Statistics from an ensemble of runs.
+}
+\end{figure*}
+%---------------------------------------------------------%
+% Data from 100-3
+
 \bibliographystyle{plain}

### 2022-05-23 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \title{Fluid-mechanical erosion creates anisotropic porous media}
+
+% Maybe HOW fluid-mechanical erosion creates anisotropic porous media.
 %\title{Fluid-mechanical erosion generates anisotropy in porous media}
@@
 
-\nick{Perhaps you can combine the real BIE and Cauchy representation into one section to condense it and to make the complex analysis take more center stage.}
+\nick{Perhaps we can combine the real BIE and Cauchy representation into one section to condense it and to make the complex analysis take more center stage.}
 
@@
 We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively.
-As an extreme example, a tightly spaced row of circular bodies would exhibit configurational anisotropy but no shape anisotropy.
+As an extreme example, a tightly-packed horizontal row of circular bodies would exhibit configurational anisotropy but no shape anisotropy.
 Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit high shape anisotropy and low configurational anisotropy.

### 2022-05-24 docs/PhysicsPaper/StokesErosion.tex
NM
starting sec 3

--- 2022-05-19 docs/PhysicsPaper/StokesErosion.tex
@@
 
+  \todo[inline]{Emphasize the complex analysis, rewrite so it isn't
+  self-plagirized, compactify which would eliminate, for example,
+  equation (15)}
 In order to accurately and efficiently compute the Stokes flow governed by \eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE).

### 2022-05-24 docs/PhysicsPaper/StokesErosion.tex

--- 2022-05-23 docs/PhysicsPaper/StokesErosion.tex
@@
 
-\author{Nicholas J.~Moore}
-%\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+\author[Colgate]{Nicholas J.~Moore}
 
-\author{Jake Cherry}
+\author[FSU]{Jake Cherry}
+
+\author[NJIT]{Shang-Huan Chiu}
 %\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
 
-\author{Shang-Huan Chiu}
-%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
+\author[FSU]{Bryan D.~Quaife}
+%\address{\FSU}
 
-\author{Bryan D.~Quaife}
-%\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
+\address[Colgate]{Colgate University}
+\address[FSU]{Florida State University}
+\address[NJIT]{New Jersey Institute of Technology}
 

### 2022-05-24 docs/PhysicsPaper/StokesErosion.tex
started on Sec 3

@@
 %-----------------------------------------------------------------------------------------------%
+To accurately and efficently solve the Stokes
+  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
+  boundary integral equation (BIE). We represent the velocity as the sum
+  of a double-layer potential and a combination of Stokeslets and
+  rotlets~\cite{pow-mir1987}
+\begin{align}
+  \uu(\xx) = \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
+    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+    \eeta(\yy) \, ds_\yy, + \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) +
+    R[\xi_\ell](\xx)\right), \quad \xx \in \Omega.
+  \label{eqn:velocityDLP}
+\end{align}
+Note that $\bd\Omega$ includes both the eroding bodies and the outer
+  boundary. The Stokeslet and the rotlets are
+  \begin{align}
+    S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
+    \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
+    \quad
+    R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
+  \end{align}
+  where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
+  $\cc_\ell$ is a point inside body $\ell$.
 
@@
   equation (15)}
-In order to accurately and efficiently compute the Stokes flow governed by \eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE).
-The boundary integral equations are first formulated in $\RR^2$ and then recast in terms of a Cauchy integral.
-The Cauchy integral representation enables a barycentric quadrature method to accurately compute the flow intervening between nearly contacting bodies, as is required by the dense configurations examined in this work.
-
-\nick{Perhaps we can combine the real BIE and Cauchy representation into one section to condense it and to make the complex analysis take more center stage.}
+In order to accurately and efficiently compute the Stokes flow governed
+  by \eqref{eqn:StokesEq}, we reformulate the system as a boundary
+  integral equation (BIE). The boundary integral equations are first
+  formulated in $\RR^2$ and then recast in terms of a Cauchy integral.
+  The Cauchy integral representation enables a barycentric quadrature
+  method to accurately compute the flow intervening between nearly
+  contacting bodies, as is required by the dense configurations examined
+  in this work.
 

### 2022-05-25 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
+With the numerical methods in place, we now discuss how to measure the permeability and other porous-media properties of the configurations generated by fluid-mechanically induced erosion.
+
 %-----------------------------------------------------------------------------------------------%
-\subsection{Resistivity and permeability}
-Darcy's law is given by
-\begin{equation}
-\bq = - \bvec{K} \grad \phi
-\end{equation}
-where $\bq$ is the specific discharge, $\phi = z + p/\gamma$ is the hydraulic head, and $\gamma = \rho g$.
-The rank-2 tensor $\bvec{K}$ is the {\em conductivity}, which is related to the {\em permeability} $\bvec{k}$ via $\bvec{K} = \bvec{k} \gamma/\mu$, where $\mu$ is the viscosity of the fluid.
-The units of conductivity are length-per-time (i.e.~velocity) and the units of permeability are length squared.
-Perhaps the most standard parameter to characterize the porous medium is the permeability. We eliminate gravity from consideration to get
+\subsection{Permeability}
+
+While the Stokes equations \eqref{eqn:StokesEq} provides a microscopic description of the detailed flow field $\uu$ penetrating the complex configuration of erodable bodies, a coarse-grained description can be obtained by treating the collection of bodies as a single porous-medium and homogenizing the flow-field through Darcy's law,
 \begin{equation}
@@
 \end{equation}
-Henceforth, we set $\mu = 1$ by the non-dimensionalization.
+Here, $p$ and $\mu$ represent the pressure field and fluid viscosity as before, with $\mu = 1$ by the non-dimensionalization.
+Meanwhile, $\bq$ represents the {\em specific discharge}, which is the volume of water that flowing through a unit cross sectional area of porous media per unit time; $\bq$ relates to the (interstitial) velocity $\uu$, by integrating $\uu$ over a sufficiently small control region and dividing by the total volume (including both fluid and solid) of the region.
+The parameter $\bvec{k}$ represents the {\em permeability} of the porous medium, which generally takes the form of a rank-2 tensor to permit different propensities to flow in different directions, i.e.~medium anisotropy.
+The permeability may vary in space and will certainly vary in time as the bodies erode.
+
+Consider, first for simplicity, an isotropic porous medium with scalar permeability $k$.
+
+% Notes
+% Specific discharge: It represents the volume of water that flows through a unit cross sectional area of porous media per unit time. The units of permeability are length squared.
+% Reference: https://books.gw-project.org/hydrogeologic-properties-of-earth-materials-and-principles-of-groundwater-flow/chapter/darcys-law/
+
+\vsp{2} \nick{To here in editing} \vsp{2}
 

### 2022-05-26 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \newcommand{\anis}{\mathcal{A}}
+\newcommand{\diag}{\mathop{\mathrm{diag}}}
 
@@
 \begin{equation}
-\bq = - \bvec{k} \grad p / \mu
+\label{eqn:Darcy}
+\bq = - \frac{1}{\mu} \bvec{k} \grad p
 \end{equation}
 Here, $p$ and $\mu$ represent the pressure field and fluid viscosity as before, with $\mu = 1$ by the non-dimensionalization.
-Meanwhile, $\bq$ represents the {\em specific discharge}, which is the volume of water that flowing through a unit cross sectional area of porous media per unit time; $\bq$ relates to the (interstitial) velocity $\uu$, by integrating $\uu$ over a sufficiently small control region and dividing by the total volume (including both fluid and solid) of the region.
+Meanwhile, $\bq = (q_1, q_2)$ represents the {\em specific discharge}, which is the volume of water that flowing through a unit cross sectional area of porous media per unit time; $\bq$ relates to the (interstitial) velocity $\uu$, by integrating $\uu$ over a sufficiently small control region and dividing by the total volume (including both fluid and solid) of the region.
 The parameter $\bvec{k}$ represents the {\em permeability} of the porous medium, which generally takes the form of a rank-2 tensor to permit different propensities to flow in different directions, i.e.~medium anisotropy.
-The permeability may vary in space and will certainly vary in time as the bodies erode.
 
-Consider, first for simplicity, an isotropic porous medium with scalar permeability $k$.
+%The permeability may vary in space and will certainly vary in time as the bodies erode.
 
@@
 
-\vsp{2} \nick{To here in editing} \vsp{2}
-
-Consider first an isotropic porous medium with {\em scalar} permeability $k$.
-Furthermore, we seek to characterize the medium by a single, bulk value permeability, so we assume that $k$ is spatially constant.
-Equivalently, we can introduce a {\em resistivity} simply defined as the reciprocal of permeability, $r = 1/k$. Then taking the horizontal component gives
+For simplicity, we will assume $\bvec{k}  = \diag(k_{11}, k_{22})$ to be a diagonal matrix for the sake of characterizing the permeability of the porous medium.
+Because the diagonal components of $\bvec{k}$ need not be equal, the medium can have different permeabilities in the horizontal and vertical directions.
+Further, we will assume that $\bvec{k}$ to be spatially homogeneous in order to characterize the medium with a single bulk quantity at any instance in time.
+Naturally, the permeability will change over time as the bodies that comprise the medium erode.
+Consider first the horizontal component of \eqref{eqn:Darcy}
 \begin{equation}
 \label{q1}
-q_1(x,y) = -\frac{1}{r} \pderiv{p}{x}(x,y)
+q_1(x,y) = -k_{11} \pderiv{p}{x}(x,y)
 \end{equation}
-Consider the horizontal discharge, $q_1(x,y)$, averaged over a vertical slice
+
+By conservations of mass, the average of the horizontal discharge, $q_1$, over any vertical cross-section must equal the uniform flow rate $U$ imposed at the inlet/outlet.
+That is, for any location $x_0$,
 \begin{equation}
-\qavg := \frac{1}{2} \int_{-1}^{1} q_1(x_0, y) dy = U
+\qavg_1 := \frac{1}{2} \int_{-1}^{1} q_1(x_0, y) dy = U
 \end{equation}
-By conservation of mass, $\qavg$ is independent of the horizontal position $x_0$ and is equal to the imposed value $U$.
-Since $\bq$ is a volume-average of the tracer velocity, $\qavg$ can be equivalently obtained by averaging the tracer velocity, which is how we will measure this quantity in the simulations.
-
-Next, consider the pressure averaged over a vertical slice
+Above and henceforth, the overline signifies an average over a vertical cross-section. Similarly, consider the pressure averaged over a vertical cross-section at $x_0$
 \begin{equation}
@@
 \end{equation}
-In particular, the upstream and downstream pressures are respectively
+In particular, we define the {\em upstream} and {\em downstream} pressures as
 \begin{equation}
@@
 \end{equation}
+since $x_0 = -1$ lies immediately upstream of the porous medium and $x_0 = 1$ immediately downstream.
 
@@
 \begin{equation}
-r = \frac{\pup - \pdn}{2 U}
+k_{11} = \frac{2U}{\pup - \pdn}
 \end{equation}
-This exact formula gives the resistivity based on measurements of the upstream/downstream pressure and the discharge.
+This exact formula gives the permeability in terms of the total flux $U$ and measurements of the upstream/downstream pressure.
 
-Probably should just use
-\begin{equation}
-k = \frac{2U}{\pup - \pdn}
-\end{equation}
+\vsp{2} \nick{To here in editing} \vsp{2}
+
+%Since $\bq$ is a volume-average of the tracer velocity, $\qavg$ can be equivalently obtained by averaging the tracer velocity, which is how we will measure this quantity in the simulations.
+
 %Note: If a larger value of $x_0$ is chosen, then one would be in effect averaging the porous-medium resistivity with the vanishing resistivity of the empty buffer region.

### 2022-05-29 docs/PhysicsPaper/StokesErosion.tex
working on sec 3

--- 2022-05-24 docs/PhysicsPaper/StokesErosion.tex
@@
 \begin{align}
-  \uu(\xx) = \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
+  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
+    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
+    \quad \xx \in \Omega,
+  \label{eqn:velocity}
+\end{align}
+where 
+\begin{align}
+  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
   \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
-    \eeta(\yy) \, ds_\yy, + \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) +
-    R[\xi_\ell](\xx)\right), \quad \xx \in \Omega.
+  \eeta(\yy) \, ds_\yy.
   \label{eqn:velocityDLP}
@@
 $\cc_\ell$ is a point inside body $\ell$.
+
+It is convenient to write equation~\eqref{eqn:velocityDLP} in terms of
+complex variables. With this reformulation, analytic function theory can
+be used to show that a particular quadrature rule achieves spectral
+accuracy. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
+similar notation for $\yy$, and $\nn$. Then, the Stokes double-layer
+potential is 
+\begin{align}
+  \DDD[\eta](x) = \pderiv{}{x} \Re \frac{1}{2\pi i} \int_\Gamma
+    \frac{\overline{y \eta(y)}}{x-y} dy + 
+\end{align}
 

### 2022-06-01 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-05-26 docs/PhysicsPaper/StokesErosion.tex
@@
 
-\vsp{2} \nick{To here in editing} \vsp{2}
-
 %Since $\bq$ is a volume-average of the tracer velocity, $\qavg$ can be equivalently obtained by averaging the tracer velocity, which is how we will measure this quantity in the simulations.
@@
 %-----------------------------------------------------------------------------------------------%
-\subsection{Relationship to total drag}
+\subsection{Total drag}
 
-The resistivity is directly related to the drag exerted by the bodies.
-Indeed, another way to express the Stokes equations is $\grad \cdot \stress = 0$ where $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$ is the stress tensor.
-The divergence theorem gives
+The permeability of the medium is directly related to the total drag exerted by the collection of bodies.
+The stress tensor associated with the Stokes equations \eqref{eqn:StokesEq} is given by $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$, and an alternate expression of \eqref{eqn:StokesEq} is $\grad \cdot \stress = 0$.
+Integrating this form of the equations over an arbitrary domain $D$ and applying the divergence theorem gives
 \begin{equation}
 \label{divthm}
-0 = \int_{\Omega} \grad \cdot \stress \, dV 
-= \int_{\partial \Omega} \stress \cdot \nn \, ds
+0 = \int_{D} \grad \cdot \stress \, dV 
+= \int_{\partial D} \stress \cdot \nn \, ds
 \end{equation}
-for any domain $\Omega$.  Consider $\Omega$ to be inside $[-x_0, x_0] \times [-1, 1]$, where we will choose $x_0 > 1$ so that $\Omega$ includes the entire porous region.
+Consider $D \subseteq [-x_0, x_0] \times [-1, 1]$ to be the subset consisting of the fluid region (i.e.~excluding solid bodies), where $x_0 \ge 1$ will be chosen to include the entire porous region plus some amount of the buffer region.
+The boundary $\partial D$ consist of $\gamma$, the solid boundaries of all of the bodies, as well as an outer boundary.
+The total drag exerted by all of the solid bodies is given by
+\begin{equation}
+\FD = -\int_{\gamma} \stress \cdot \nn \, ds
+\end{equation}
+
+\nick{Do I want plus or minus? I decided I want the drag exerted BY the bodies and so this should point to the left.}
+
+\vsp{2} \nick{To here in editing} \vsp{2}
+
+Consider $\Omega$ to be inside $[-x_0, x_0] \times [-1, 1]$, where we will choose $x_0 > 1$ so that $\Omega$ includes the entire porous region.
 The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodable bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$.

### 2022-06-02 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-06-01 docs/PhysicsPaper/StokesErosion.tex
@@
 	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em erosion model}, \\
-\tau = -(\nabla \uu + \nabla \uu^T) \nn \cdot \ss
+\tau = -\mu \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss
 	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
@@
 
-The permeability of the medium is directly related to the total drag exerted by the collection of bodies.
-The stress tensor associated with the Stokes equations \eqref{eqn:StokesEq} is given by $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$, and an alternate expression of \eqref{eqn:StokesEq} is $\grad \cdot \stress = 0$.
-Integrating this form of the equations over an arbitrary domain $D$ and applying the divergence theorem gives
+The permeability of the medium is directly related to the drag exerted by the collection of bodies.
+The stress tensor associated with the Stokes equations \eqref{eqn:StokesEq} is given by $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$, and the Stokes equations can alternatively be expressed as $\grad \cdot \stress = 0$.
+Integrating over an arbitrary domain $D$ and applying the divergence theorem gives
 \begin{equation}
@@
 0 = \int_{D} \grad \cdot \stress \, dV 
-= \int_{\partial D} \stress \cdot \nn \, ds
+= \int_{\partial D} \stress \, \nn \, ds
 \end{equation}
 Consider $D \subseteq [-x_0, x_0] \times [-1, 1]$ to be the subset consisting of the fluid region (i.e.~excluding solid bodies), where $x_0 \ge 1$ will be chosen to include the entire porous region plus some amount of the buffer region.
-The boundary $\partial D$ consist of $\gamma$, the solid boundaries of all of the bodies, as well as an outer boundary.
-The total drag exerted by all of the solid bodies is given by
+The boundary $\partial D$ consist of all solid-body boundaries $\gamma$, along with an outer boundary.
+
+The hydrodynamic drag on the collection of bodies is obtained by integrating the surface traction over the boundary $\gamma$. The surface traction is given by 
 \begin{equation}
-\FD = -\int_{\gamma} \stress \cdot \nn \, ds
+- \stress \, \nn = p \nn + \tau \ss
+\end{equation}
+where the negative sign is a consequence of choosing the normal vector $\nn$ pointing {\em into} the bodies. The total drag on the collection of bodies is thus
+\begin{equation}
+\FD =  - \int_{\gamma} \stress \, \nn \, ds =  \int_{\gamma} p \nn + \tau \ss \, ds
 \end{equation}
 
-\nick{Do I want plus or minus? I decided I want the drag exerted BY the bodies and so this should point to the left.}
+% NOTE ON SIGN OF DRAG
+% The drag ON the bodies is F = \int p n + tau s.
+This is consistent with the JCP paper, with my code, and I have verified the calculation.
+This drag vector points to the right since it is the drag ON the bodies.
 
@@
 
-Consider $\Omega$ to be inside $[-x_0, x_0] \times [-1, 1]$, where we will choose $x_0 > 1$ so that $\Omega$ includes the entire porous region.
 The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodable bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$.
@@
 \end{equation}
-which includes both pressure and viscous drag. The minus sign is due to the orientation of the normal vector. We will mostly be interested in the horizontal drag $\FD \cdot \ex$. \\
-
-\nick{Need to check sign on drag and check whether I want the drag {\em on} the bodies or exerted {\em by} the bodies.} \\
+We will mostly be interested in the horizontal drag $\FD \cdot \ex$. \\
 

### 2022-06-02 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{equation}
+\label{eqn:k11}
 k_{11} = \frac{2U}{\pup - \pdn}
@@
 
-The hydrodynamic drag on the collection of bodies is obtained by integrating the surface traction over the boundary $\gamma$. The surface traction is given by 
+The hydrodynamic drag on the collection of bodies is obtained by integrating the surface traction over the boundary $\gamma$. The surface traction on a no-slip boundary is given by 
 \begin{equation}
@@
 \end{equation}
-where the negative sign is a consequence of choosing the normal vector $\nn$ pointing {\em into} the bodies. The total drag on the collection of bodies is thus
+where the negative sign is a consequence of choosing the normal vector $\nn$ to point out of the fluid region or {\em into} the bodies. The total drag on the collection of bodies is thus
 \begin{equation}
+\label{eqn:drag}
 \FD =  - \int_{\gamma} \stress \, \nn \, ds =  \int_{\gamma} p \nn + \tau \ss \, ds
@@
 
-\vsp{2} \nick{To here in editing} \vsp{2}
-
-The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodable bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$.
-In particular, the total drag exerted by the erodable bodies is given by
+Projecting \eqref{divthm} onto $\ex$, using \eqref{eqn:drag}, and rearranging gives the exact relationship
 \begin{equation}
-\FD = -\int_{\gamma} \stress \cdot \nn \, ds
+\label{drag_press}
+\FD \cdot \ex = \int_{-1}^{1} \left( -p(x,y) + 2 \mu u_x(x,y) \right) \big|_{x=-x_0}^{x=x_0} dy + 
+\int_{-x_0}^{x_0} \mu u_y(x,y) \big|_{y=-1}^{y=1} dx
 \end{equation}
-We will mostly be interested in the horizontal drag $\FD \cdot \ex$. \\
-
-Consider now the contribution to \eqref{divthm} from the outer boundary $\Gamma$. The horizontal component of this term is
-\begin{align}
-\ex \cdot \int_{\Gamma} \stress \cdot \nn \, ds = 
-& \int_{-1}^{1} p(-x_0, y) - p(x_0, y) - 2\mu (u_x(-x_0,y) - u_x(x_0,y)) \, dy \, + \\
-& \int_{-x_0}^{x_0} \mu (u_y(x,1) - u_y(x,-1)) dx
-\end{align}
-If we take $x_0$ sufficiently far away, then the viscous terms involving $u_x$ will become small as the velocity field tends to a uniform flow.
-Meanwhile, the contribution from the pressure is well approximated by the upstream and downstream average pressures $\pup$ and $\pdn$ as introduced in the previous section.
-This gives
+We will now make some simplifying assumptions.
+First, because the imposed flow profile is uniform $\UU = (U,0)$, slip is permitted along the top and bottom boundaries $y=\pm 1$ and so the viscous stress will generally be much smaller than on the no-slip erodable boundaries.
+We will therefore drop the contribution from the second integral above.
+Second, if $x_0 > 1$ is chosen a sufficient distance from the erodable bodies, the flow profile will approximately match the uniform profile, implying that the term involving $u_x(\pm x_0, y)$ can be dropped.
+In addition, the pressure $p(\mp x_0, y)$ will approximately match the upstream and downstream values respectively.
+With these assumptions, \eqref{drag_press} simplifies to the approximate form
 \begin{equation}
@@
 \end{equation}
+Combining with \eqref{eqn:k11} yields an approximate relationship between the horizontal components of permeability and drag 
+\begin{equation}
+\label{}
+\frac{1}{k_{11}} \approx \frac{1}{4 U}  \, \FD \cdot \ex
+\end{equation}
 
-Therefore we have the relationship
-\begin{equation}
-\label{ResistDrag}
-1/k_1 \approx \frac{1}{4 U}  \, \FD \cdot \ex
-\end{equation}
+USEFUL FOR BENCHMARK
+
+\vsp{2} \nick{To here in editing} \vsp{2}
 

### 2022-06-02 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-06-02 docs/PhysicsPaper/StokesErosion.tex
@@
 
-%-----------------------------------------------------------------------------------------------%
-\subsection{Permeability}
+%-------------------------------------------------------------------%
+\subsection{Longitudinal permeability}
+\label{LongPerm}
 
@@
 
-%-----------------------------------------------------------------------------------------------%
-\subsection{Total drag}
+%-------------------------------------------------------------------%
+\subsection{Relationship to drag}
 
@@
 \end{equation}
-Combining with \eqref{eqn:k11} yields an approximate relationship between the horizontal components of permeability and drag 
+Combining with \eqref{eqn:k11} yields a formula relating the drag and permeability in the longitudinal direction
 \begin{equation}
-\label{}
+\label{perm_drag}
 \frac{1}{k_{11}} \approx \frac{1}{4 U}  \, \FD \cdot \ex
 \end{equation}
+This formula serves as a valuable benchmark linking the microscopic (Stokes) and macroscopic (Darcy) perspectives.
+Since the drag is a quantity that can be computed with high accuracy with our Stokes solvers, verifying the relationship \eqref{perm_drag}, as will be done in Fig.~\ref{fig2}, validates a number of approximations made in the coarse-grained approach, such as (1) the homogenization of the flow field implicit in Darcy's law \eqref{eqn:Darcy}; (2) the calculation of the permeability from measurements of the flow rate and upstream/downstream pressures through \eqref{eqn:k11}.
 
-USEFUL FOR BENCHMARK
+%-------------------------------------------------------------------%
+\subsection{Transverse permeability and anisotropy}
+
+Now consider measuring the transverse permeability $k_{22}$ using Darcy's law \eqref{eqn:Darcy}. Taking the vertical component of \eqref{eqn:Darcy} yields
+\begin{equation}
+\label{q1}
+q_2(x,y) = -k_{22} \pderiv{p}{y}(x,y)
+\end{equation}
+but this form is not useful if no vertical pressure gradient is imposed, as is the case in our erosion simulations.
+It is important to recognize that the permeability is a property of the {\em medium}, not the imposed flow.
+Hence, for a frozen configuration of bodies, it is permissible to alter the imposed flow for the purpose of measuring $k_{22}$ (this altered flow is completely separate from the simulation of the erosion process that generates the configurations).
+Thus, instead of a horizontal flow in the far-field, we seek to impose a vertical one $\UU = (0,U)$.
+If this were to be done directly, the outer geometry would need to be rotated by 90 degrees about the configuration of bodies inside (which does not rotate).
+In practice, it is simpler to keep the outer geometry fixed and instead rotate the inner configuration of bodies, then simply apply the method from Section \ref{LongPerm} to measure $k_{22}$.
+
+With both the longitudinal and transverse components of permeability calculated, we define the anisotropy of the medium as the ratio
+\begin{equation}
+\anis = k_{11} / k_{22}
+\end{equation}
+Note that the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one, and as the configuration erodes, the configuration would be expected to permit flow in the longitudinal direction more easily than in the transverse direction, yielding $\anis > 1$.
+
+There are two mechanistic explanations for how erosion can create this anisotropy.
+First, the shear stresses could carve each individual body into a more slender form, thus creating anisotropy at the level of individual grains.
+Second, by removing material in a non-uniform way, could preferentially disintegrate certain bodies before others, leaving an overall configuration that exhibits anisotropy on the large scale, for example one with horizontally aligned channels.
+We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively.
+As an extreme example, a tightly-packed horizontal row of circular bodies would exhibit configurational anisotropy but no shape anisotropy.
+Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit high shape anisotropy and low configurational anisotropy.
 
 \vsp{2} \nick{To here in editing} \vsp{2}
+
+We note that channelization is related to both shape and configurational anisotropy....
+
+It is possible to device a test to isolate these two types of anisotropy.
+Introduce circular bodies with same centers of mass...
+Thus, the configurational anisotropy is defined as
+\begin{equation}
+\anis_C = k_1^{(c)} / k_2^{(c)}
+\end{equation}
+
+The total anisotropy is the product of the shape and configurational
+\begin{equation}
+\anis = \anis_S \anis_C
+\end{equation}
 
@@
 % Data from 100-3
-
-The anisotropy of permeability is
-\begin{equation}
-\anis = k_1 / k_2
-\end{equation}
-
-There are two possible explanations for how erosion creates anisotropy in the microstructure.
-First, the shear stresses could carve each individual body into a more slender form, thus creating anisotropy at the level of individual grains.
-Second, by removing material in a non-uniform way, could preferentially disintegrate certain bodies before others, leaving an overall configuration that exhibits anisotropy on the large scale.
-We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively.
-As an extreme example, a tightly-packed horizontal row of circular bodies would exhibit configurational anisotropy but no shape anisotropy.
-Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit high shape anisotropy and low configurational anisotropy.
-
-We note that channelization is related to both shape and configurational anisotropy....
-
-It is possible to device a test to isolate these two types of anisotropy.
-Introduce circular bodies with same centers of mass...
-Thus, the configurational anisotropy is defined as
-\begin{equation}
-\anis_C = k_1^{(c)} / k_2^{(c)}
-\end{equation}
-
-The total anisotropy is the product of the shape and configurational
-\begin{equation}
-\anis = \anis_S \anis_C
-\end{equation}
 

### 2022-06-02 simulations/run0.jl

@@ -4,6 +4,6 @@
 
 using Erosion
 
-params = ParamSet(label="20-11")
+params = ParamSet(label="20-14")
 run_erosion(params)
 post_process(params)

### 2022-06-07 simulations/vplots.jl
NM

@@ -8,6 +8,7 @@ using Plots; plotlyjs()
 #---------------------------------------------------------------#
 # Set file and folder names.
 proc_file(run::AbstractString) = "output_data/proc_data-$(run).jld2"
+tort_file(run::AbstractString) = "proc_data-tort/proc_data-$(run)_tortuosity_partial.jld2"
 plot_folder() = "zPlots/"	# Plot folder
 vfolder(name::AbstractString) = "veusz_data/$(name).txt"
 
@@ -49,6 +50,10 @@ function vplot_single(run::AbstractString)
 		load(proc_file(run), "thldvec", "resist", "resist_rot", 
 		"resist_circs", "resist_circs_rot", "drag_data")
 
+	# Read tortuosity variables file.
+	xtort, ytort, xcirctort, ycirctort = load(tort_file(run), 
+		"xtortuosity", "ytortuosity", "xcirctortuosity", "ycirctortuosity")
+
 	# Calculate time-dependent quantities.
 	tt = [ thldvec[nn].tt for nn in eachindex(thldvec)]
 	porosity = get_porosity(run)
@@ -60,21 +65,30 @@ function vplot_single(run::AbstractString)
 	# Modify the values that don't make sense at the final time.
 	resist[end] = resist_rot[end] = umax[end] = NaN
 
-	# Calculate anisotropy quantitites.
+	# Calculate the anisotropy of permeability.
 	anis = resist_rot ./ resist
 	anis_config = resist_circs_rot ./ resist_circs
 	anis_shape = anis ./ anis_config
+
+	# Calculate the anisotropy of tortuosity.
+	anis_tort = (ytort ./ xtort).^1
+	anis_tort_config = (ycirctort ./ xcirctort).^1
+	anis_tort_shape = anis_tort ./ anis_tort_config
 
 	# Make text file for Veusz to plot.
 	vdata([tt area porosity  umax], "time area porosity umax", vfolder("basic_vars"))
 	vdata(	[hdrag vdrag resist resist_rot resist_circs resist_circs_rot], 
 			"hdrag vdrag resist resist_rot resist_circs resist_circs_rot", vfolder("resist_vars"))
 	vdata([anis anis_config anis_shape], "anis anis_config anis_shape", vfolder("anis_vars"))
+	
+	# Make Veusz text file for tortuosity.
[…]

### 2022-06-08 simulations/vplots.jl
NM

@@ -42,6 +42,11 @@ function append_torts!(porosity, vars...)
 		append!(var, ones(length(porosity)-length(var)))
 	end
 end
+
+# Calculate the tortuosity anisotropy.
+function tort_anisotropy(xtort, ytort)
+	return (ytort .-1) ./ (xtort .-1)
+end
 #---------------------------------------------------------------#
 
 
@@ -84,8 +89,8 @@ function vplot_single(run::AbstractString)
 	anis_shape = anis ./ anis_config
 
 	# Calculate the anisotropy of tortuosity.
-	anis_tort = (ytort ./ xtort).^1
-	anis_tort_config = (ycirctort ./ xcirctort).^1
+	anis_tort = tort_anisotropy(xtort, ytort)
+	anis_tort_config = tort_anisotropy(xcirctort, ycirctort)
 	anis_tort_shape = anis_tort ./ anis_tort_config
 
 	# Make text file for Veusz to plot.
@@ -99,9 +104,9 @@ function vplot_single(run::AbstractString)
 		  "xtort ytort xcirctort ycirctort anis_tort anis_tort_config anis_tort_shape", vfolder("tort_vars"))
 end
 
-# Possible runs: 20:2,5,8; 40:3,7,8; 60:3,7,9; 80:4,7,9; 100:3,6
-# Look great for anistropy plot: 40-8, 60-9, 100-3
-vplot_single("60-9")
+# Possible runs: 20:2,5,8; 40:3,7,8; 60:3,7,9; 80:4,7,9; 100:3,6,9
+# 100-9 looks quite good showing the configuration anisotropy near the end.
+vplot_single("100-9")
 #---------------------------------------------------------------#
 
 
@@ -200,8 +205,8 @@ function vplot_stats()
 		anis_shape = anis ./ anis_config
 		
 		# Calculate the tortuosity anistropy for the ensemble.
-		anis_tort = (ytort ./ xtort).^1
-		anis_tort_config = (ycirctort ./ xcirctort).^1
+		anis_tort = tort_anisotropy(xtort, ytort)
+		anis_tort_config = tort_anisotropy(xcirctort, ycirctort)
 		anis_tort_shape = anis_tort ./ anis_tort_config
 
 		# Compute the mean and standard deviation, then save the data.

### 2022-06-09 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
+Anisotropy in groundwater is around 10 \cite{anderson2015applied}.
+
 %Maybe cite: \cite{Rycroft2016}
@@
 \caption{
-a)
+Permeability
 }
@@
 \caption{
+Tortuosity
+}
+\end{figure*}
+%---------------------------------------------------------%
+
+%---------------------------------------------------------%
+\begin{figure*}%[htbp]
+\centering \label{fig5}
+\includegraphics[width = 0.99 \textwidth]{./figs/fig5.pdf}
+\caption{
 a) Statistics from an ensemble of runs.
@@
 %---------------------------------------------------------%
-% Data from 100-3
+
+%---------------------------------------------------------%
+\begin{figure*}%[htbp]
+\centering \label{fig6}
+\includegraphics[width = 0.99 \textwidth]{./figs/fig6.pdf}
+\caption{
+a) Statistics from an ensemble of runs.
+}
+\end{figure*}
+%---------------------------------------------------------%
 

### 2022-06-10 docs/PhysicsPaper/StokesErosion.tex
worked on sec 3

@@
 To accurately and efficently solve the Stokes
-  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
-  boundary integral equation (BIE). We represent the velocity as the sum
-  of a double-layer potential and a combination of Stokeslets and
+equations~\eqref{eqn:StokesEq}, we reformulate the system as a boundary
+integral equation (BIE). We represent the velocity as the sum of a
+double-layer potential and a combination of Stokeslets and
 rotlets~\cite{pow-mir1987}
@@
 It is convenient to write equation~\eqref{eqn:velocityDLP} in terms of
-complex variables. With this reformulation, analytic function theory can
-be used to show that a particular quadrature rule achieves spectral
-accuracy. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
-similar notation for $\yy$, and $\nn$. Then, the Stokes double-layer
-potential is 
+complex variables. With this reformulation, simple quadrature rules
+achieve spectral accuracy. We identify $\xx = (x_1,x_2)$ with $x = x_1 +
+ix_x$, and use similar notation for $\yy$, $\nn$, and $\eeta$. We also
+interpret $\Gamma$, the boundary of the domain, as a collection of
+Jordan curves in $\CC$. We next introduce the functions
 \begin{align}
-  \DDD[\eta](x) = \pderiv{}{x} \Re \frac{1}{2\pi i} \int_\Gamma
-    \frac{\overline{y \eta(y)}}{x-y} dy + 
+  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
+  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
 \end{align}
+Then, we next define the five Cauchy integrals
+\begin{align}
+  v_1(x) &= \frac{1}{2\pi i} \int_{\Gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
+  \quad
+  v_2(x) = \frac{1}{2\pi i} \int_{\Gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
+  \quad
+  v_3(x) = \frac{1}{2\pi i} \int_{\Gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
+  v_4(x) &= \frac{1}{2\pi i} \int_{\Gamma} \frac{\tau_1(y)}{x-y} \, dy,
+  \quad
+  v_5(x) = \frac{1}{2\pi i} \int_{\Gamma} \frac{\tau_2(y)}{x-y} \, dy.
+\end{align}
+The boundary data of each of these Cauchy integrals satisfies the
+Sokhotski-Plemelj jump relation
+\begin{align}
+  \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\Gamma}
+    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\sigma(x_0) - 
+    \frac{1}{2\pi i} \int_{\Gamma} \frac{\eta(y)}{x-y} \, dy,
+    \quad x_0 \in \Gamma,
+\end{align}
+where the last integral is interpreted in the principal value sense.
+
+Then, the first and second components of the Stokes double-layer
+potential are
+\begin{align}
+  u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
+           \Re(v_3'(x)) + \Re(v_4(x)) \\
+  u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
+           \Im(v_3'(x)) + \Re(v_5(x)),
+\end{align}
+respectively.
 

### 2022-06-11 docs/PhysicsPaper/StokesErosion.tex
working on sec 3

--- 2022-06-09 docs/PhysicsPaper/StokesErosion.tex
@@
 %-----------------------------------------------------------------------------------------------%
-To accurately and efficently solve the Stokes
+To accurately and efficiently solve the Stokes
   equations~\eqref{eqn:StokesEq}, we reformulate the system as a
-  boundary integral equation (BIE). We represent the velocity as the sum
-  of a double-layer potential and a combination of Stokeslets and
+  boundary integral equation (BIE). Applying the same approach as our
+  previous work~\citep{qua-moo2018}, we represent the velocity as the
+  sum of a double-layer potential and a combination of Stokeslets and
   rotlets~\cite{pow-mir1987}
@@
 where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
-$\cc_\ell$ is a point inside body $\ell$.
+$\cc_\ell$ is a point inside body $\ell$. If the density function,
+Stokeslets, and rotlets satisfy the second-kind boundary integral
+equation
+\begin{subequations}
+  \label{eqn:FredBIE}
+  \begin{alignat}{3}
+    \UU(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
+      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
+      \quad &&\xx \in \Gamma, \\
+    \mathbf{0} &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
+      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
+      &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
+    \llambda_\ell &= \int_{\gamma_i} \eeta(\yy) \, ds_\yy, 
+      &&\ell = 1,\ldots,M, \\
+    \xi_\ell &= \int_{\gamma_i} (\yy - \cc_i)^\perp \cdot 
+      \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
+  \end{alignat}
+\end{subequations}
+then the representation~\eqref{eqn:velocity}
+satisfies~\eqref{eqn:StokesEq}. We solve~\eqref{eqn:FredBIE} by choosing
+equispaced collocation points on $\gamma_\ell$ and $\Gamma$, and then
+replacing the integrals with quadrature rules. This results in a linear
+system with a mesh-independent condition number, and it is solved
+iteratively with GMRES.
 
-It is convenient to write equation~\eqref{eqn:velocityDLP} in terms of
-complex variables. With this reformulation, analytic function theory can
-be used to show that a particular quadrature rule achieves spectral
-accuracy. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
-similar notation for $\yy$, and $\nn$. Then, the Stokes double-layer
-potential is 
+The accuracy of the method is determined by the accuracy of the
+quadrature rule applied to equation~\eqref{eqn:FredBIE}. A quadrature
+rule for~\eqref{eqn:velocityDLP} that achieves spectral accuracy writes
+the Stokes double-layer potential as a collection of Cauchy integrals
 \begin{align}
-  \DDD[\eta](x) = \pderiv{}{x} \Re \frac{1}{2\pi i} \int_\Gamma
-    \frac{\overline{y \eta(y)}}{x-y} dy + 
+  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
 \end{align}
+The boundary data of $v(x)$ satisfies the Sokhotski-Plemelj jump relation
+\begin{align}
+  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
+    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
+    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
+    \quad x_0 \in \gamma,
+    \label{eqn:SP}
+\end{align}
+where the last integral is interpreted in the principal value sense.
+Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
+by its boundary data alone using the Cauchy Integral Theorem
+\begin{subequations}
+  \label{eqn:cauchy}
+  \begin{alignat}{3}
+  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
+    \frac{v(y)}{y-x} \,dy, \\
+  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^2} \, dy, \\
+  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^3} \, dy.
+  \end{alignat}
+\end{subequations}
 
-  \todo[inline]{Emphasize the complex analysis, rewrite so it isn't
-  self-plagirized, compactify which would eliminate, for example,
-  equation (15)}
-In order to accurately and efficiently compute the Stokes flow governed
-  by \eqref{eqn:StokesEq}, we reformulate the system as a boundary
-  integral equation (BIE). The boundary integral equations are first
-  formulated in $\RR^2$ and then recast in terms of a Cauchy integral.
-  The Cauchy integral representation enables a barycentric quadrature
-  method to accurately compute the flow intervening between nearly
-  contacting bodies, as is required by the dense configurations examined
-  in this work.
+We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use similar
+notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the
+boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan
+curve in $\CC$. We introduce the functions
+\begin{align}
+  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
+  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
+\end{align}
+We then define the five Cauchy integrals
+\begin{align}
+  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
+  \quad
+  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
+  \quad
+  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
+  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
+  \quad
+  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
+\end{align}
+Then, the first and second components of the Stokes double-layer
+potential are
+\begin{align}
+  u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
+           \Re(v_3'(x)) + \Re(v_4(x)) \\
+  u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
+           \Im(v_3'(x)) + \Re(v_5(x)),
+\end{align}
+respectively.
+
+To apply the aforementioned spectrally accurate quadrature rule, we
+require the boundary data of the five Cauchy integrals. For $x_0 \in
+\gamma$, the boundary data of each of these Cauchy integrals satisfies
+the Sokhotski-Plemelj jump relation
+\begin{align}
+  \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
+    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
+    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
+    \quad x_0 \in \bd\Omega,
+    \label{eqn:SP}
+\end{align}
+where the last integral is interpreted in the principal value sense. For
+the Cauchy integral $v_i$, we let $v_i^-$ denote the boundary data that
+satisfies~\eqref{eqn:SP}. Once $v_i^-$ is calculated, $v(x)$ and its
+derivatives can be determined by the Cauchy Integral Theorem
+\begin{subequations}
+  \label{eqn:cauchy}
+  \begin{alignat}{3}
+  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
+    \frac{v(y)}{y-x} \,dy, \\
+  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^2} \, dy, \\
+  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
+    \frac{v(y)}{(y-x)^3} \, dy,
+  \end{alignat}
+\end{subequations}
 
@@
 
-Applying the same approach as our previous work~\citep{qua-moo2018}, we
-start with the double-layer potential 
-\begin{align}
-  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
-  \frac{1}{\pi}\int_{\bd\Omega} 
-    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
-    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
-  \label{eqn:velocityDLP}
-\end{align}
-where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
-$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-is an unknown density function.  We complete the integral equation
-formulation by adding the $M$ Stokeslets,
-$S[\llambda_\ell,\cc_\ell](\xx)$, and $M$ rotlets,
-$R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
-$\ell^{th}$ body~\citep{pow-mir1987}.  Here $\llambda_\ell$ and
-$\xi_\ell$ are the Stokeslet and rotlet strengths, respectively,
-corresponding to the $\ell^{th}$ body.  Then, for any sufficiently
-smooth geometry $\Omega$, the solution of the incompressible Stokes
-equation with a Dirichlet boundary condition $\ff$ is
-\begin{align}
-  \uu(\xx) = \DDD[\eeta](\xx) + 
-    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
-    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
-\end{align}
-where the density function, Stokeslets, and rotlets satisfy
-\begin{subequations}
-\label{eqn:BIE}
-\begin{alignat}{3}
-  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
-    \NN_0[\eeta](\xx) \nonumber \\
-    &\quad + \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
-    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), 
-    \quad &&\qquad\xx \in \bd\Omega, \\
-  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
-    \eeta(\yy)\, ds_\yy, &&\qquad \ell = 1,\ldots,M, \\
-  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
-    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
-    &&\qquad \ell = 1,\ldots,M.
-\end{alignat}
-\end{subequations}
-Here, the null space associated with the flux-free condition of $\ff$ is
-addressed with  $\NN_0$ which is the integral operator with kernel
-$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
-this work, $\ff$ is the prescribed velocity, which is equal to $\UU$ on
-the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
-$\gamma_\ell$, $\ell=1,\ldots,M$.
+%Applying the same approach as our previous work~\citep{qua-moo2018}, we
+%start with the double-layer potential 
+%\begin{align}
+%  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
+%  \frac{1}{\pi}\int_{\bd\Omega} 
+%    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+%    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
+%%  \label{eqn:velocityDLP}
+%\end{align}
+%where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
+%$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
+%is an unknown density function.  We complete the integral equation
+%formulation by adding the $M$ Stokeslets,
+%$S[\llambda_\ell,\cc_\ell](\xx)$, and $M$ rotlets,
+%$R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
+%$\ell^{th}$ body~\citep{pow-mir1987}.  Here $\llambda_\ell$ and
+%$\xi_\ell$ are the Stokeslet and rotlet strengths, respectively,
+%corresponding to the $\ell^{th}$ body.  Then, for any sufficiently
+%smooth geometry $\Omega$, the solution of the incompressible Stokes
+%equation with a Dirichlet boundary condition $\ff$ is
+%\begin{align}
+%  \uu(\xx) = \DDD[\eeta](\xx) + 
+%    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
+%    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
+%\end{align}
+%where the density function, Stokeslets, and rotlets satisfy
+%\begin{subequations}
+%\label{eqn:BIE}
+%\begin{alignat}{3}
+%  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
+%    \NN_0[\eeta](\xx) \nonumber \\
+%    &\quad + \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
+%    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), 
+%    \quad &&\qquad\xx \in \bd\Omega, \\
+%  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
+%    \eeta(\yy)\, ds_\yy, &&\qquad \ell = 1,\ldots,M, \\
+%  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
+%    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
+%    &&\qquad \ell = 1,\ldots,M.
+%\end{alignat}
+%\end{subequations}
+%Here, the null space associated with the flux-free condition of $\ff$ is
+%addressed with  $\NN_0$ which is the integral operator with kernel
+%$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
+%this work, $\ff$ is the prescribed velocity, which is equal to $\UU$ on
+%the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
+%$\gamma_\ell$, $\ell=1,\ldots,M$.
 

### 2022-06-11 docs/PhysicsPaper/StokesErosion.tex
continuing on Sec 3

@@
 
-The accuracy of the method is determined by the accuracy of the
-quadrature rule applied to equation~\eqref{eqn:FredBIE}. A quadrature
-rule for~\eqref{eqn:velocityDLP} that achieves spectral accuracy writes
-the Stokes double-layer potential as a collection of Cauchy integrals
-\begin{align}
-  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
-\end{align}
-The boundary data of $v(x)$ satisfies the Sokhotski-Plemelj jump relation
-\begin{align}
-  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
-    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
-    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
-    \quad x_0 \in \gamma,
-    \label{eqn:SP}
-\end{align}
-where the last integral is interpreted in the principal value sense.
-Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
-by its boundary data alone using the Cauchy Integral Theorem
-\begin{subequations}
-  \label{eqn:cauchy}
-  \begin{alignat}{3}
-  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
-    \frac{v(y)}{y-x} \,dy, \\
-  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^2} \, dy, \\
-  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^3} \, dy.
-  \end{alignat}
-\end{subequations}
-
 We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use similar
@@
 \end{align}
-respectively.
+respectively. The vorticity can be shown to satisfy
+\begin{align}
+  \omega(x) = \Im(v_1'(x)) + \Re(v_2'(x)) + 
+     \Re(v_5'(x)) + \Im(v_4'(x)).
+\end{align}
+We note that the vorticity only requires first derivatives of Cauchy
+integrals, but the stress tensor involves second derivatives.
 
-To apply the aforementioned spectrally accurate quadrature rule, we
-require the boundary data of the five Cauchy integrals. For $x_0 \in
-\gamma$, the boundary data of each of these Cauchy integrals satisfies
-the Sokhotski-Plemelj jump relation
+The accuracy of the method is determined by the accuracy of the
+quadrature rule applied to equation~\eqref{eqn:FredBIE}. A quadrature
+rule for~\eqref{eqn:velocityDLP} that achieves spectral accuracy writes
+the Stokes double-layer potential as a collection of Cauchy integrals
 \begin{align}
-  \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
+  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
+\end{align}
+The boundary data of $v(x)$ satisfies the Sokhotski-Plemelj jump relation
+\begin{align}
+  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
     \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
     \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
-    \quad x_0 \in \bd\Omega,
+    \quad x_0 \in \gamma,
     \label{eqn:SP}
 \end{align}
-where the last integral is interpreted in the principal value sense. For
-the Cauchy integral $v_i$, we let $v_i^-$ denote the boundary data that
-satisfies~\eqref{eqn:SP}. Once $v_i^-$ is calculated, $v(x)$ and its
-derivatives can be determined by the Cauchy Integral Theorem
+where the last integral is interpreted in the principal value sense.
+Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
+by its boundary data alone using the Cauchy Integral Theorem
 \begin{subequations}
@@
   v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
-    \frac{v(y)}{y-x} \,dy, \\
+    \frac{v^{-}(y)}{y-x} \,dy, \\
   v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^2} \, dy, \\
+    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
   v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^3} \, dy,
+    \frac{v^{-}(y)}{(y-x)^3} \, dy.
   \end{alignat}
 \end{subequations}
+Note that we require second-order derivatives to compute the shear
+stress.
 
@@
 \vsp{2} \nick{Finished rewording up to here} \vsp{2}
-
-%Applying the same approach as our previous work~\citep{qua-moo2018}, we
-%start with the double-layer potential 
-%\begin{align}
-%  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
-%  \frac{1}{\pi}\int_{\bd\Omega} 
-%    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
-%    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
-%%  \label{eqn:velocityDLP}
-%\end{align}
-%where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
-%$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
-%is an unknown density function.  We complete the integral equation
-%formulation by adding the $M$ Stokeslets,
-%$S[\llambda_\ell,\cc_\ell](\xx)$, and $M$ rotlets,
-%$R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
-%$\ell^{th}$ body~\citep{pow-mir1987}.  Here $\llambda_\ell$ and
-%$\xi_\ell$ are the Stokeslet and rotlet strengths, respectively,
-%corresponding to the $\ell^{th}$ body.  Then, for any sufficiently
-%smooth geometry $\Omega$, the solution of the incompressible Stokes
-%equation with a Dirichlet boundary condition $\ff$ is
-%\begin{align}
-%  \uu(\xx) = \DDD[\eeta](\xx) + 
-%    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
-%    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
-%\end{align}
-%where the density function, Stokeslets, and rotlets satisfy
-%\begin{subequations}
-%\label{eqn:BIE}
-%\begin{alignat}{3}
-%  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
-%    \NN_0[\eeta](\xx) \nonumber \\
-%    &\quad + \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
-%    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), 
-%    \quad &&\qquad\xx \in \bd\Omega, \\
-%  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
-%    \eeta(\yy)\, ds_\yy, &&\qquad \ell = 1,\ldots,M, \\
-%  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
-%    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
-%    &&\qquad \ell = 1,\ldots,M.
-%\end{alignat}
-%\end{subequations}
-%Here, the null space associated with the flux-free condition of $\ff$ is
-%addressed with  $\NN_0$ which is the integral operator with kernel
-%$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
-%this work, $\ff$ is the prescribed velocity, which is equal to $\UU$ on
-%the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
-%$\gamma_\ell$, $\ell=1,\ldots,M$.
 

### 2022-06-13 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{document}
-\title{Fluid-mechanical erosion creates anisotropic porous media}
+\title{How fluid-mechanical erosion creates anisotropic porous media}
 
@@
 \begin{abstract}
-We numerically simulate the erosion of a porous medium due to an internally flowing fluid.
+Using a Cauchy integral formulation of the boundary integral equations, we numerically simulation the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow.
+The bodies comprising the porous medium are resolved individually and erode under the action of surface shear stress.
+In particular, microscopic changes in the morphology of the constituents are resolved in detail, and these changes give rise to larger-scale features such as channelization of the medium.
+The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies.
+\end{abstract}
+\maketitle
+
+impinging intervening interal
+
+% Original ideas
+%We numerically simulate the erosion of a porous medium due to an internally flowing fluid, with solid constituents of the medium eroding under the action of surface shear stress. 
+%We numerically simulate the erosion of a porous medium due to an internally flowing fluid.
 The solid constituents of the porous medium erode under the action of surface shear stress.
 As the particles disintegrate, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.
-\end{abstract}
-\maketitle
+
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

### 2022-06-13 simulations/run0.jl

@@ -4,6 +4,6 @@
 
 using Erosion
 
-params = ParamSet(label="40-13")
+params = ParamSet(label="20-16")
 run_erosion(params)
 post_process(params)

### 2022-06-13 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The bodies comprising the porous medium are resolved individually and erode under the action of surface shear stress.
-In particular, microscopic changes in the morphology of the constituents are resolved in detail, and these changes give rise to larger-scale features such as channelization of the medium.
+In particular, changes in the morphology of individual bodies are resolved in detail, and these microscopic changes give rise to larger-scale features in the medium such as channelization.
 The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies.
+Armed with these methods, we observe anisotropy
 \end{abstract}

### 2022-06-13 docs/PhysicsPaper/StokesErosion.tex
working on sec 3

@@
   boundary integral equation (BIE). Applying the same approach as our
-  previous work~\citep{qua-moo2018}, we represent the velocity as the
-  sum of a double-layer potential and a combination of Stokeslets and
-  rotlets~\cite{pow-mir1987}
+  previous works~\citep{quaife2018boundary, chiu2020viscous}, we
+  represent the velocity as the sum of a double-layer potential and a
+  combination of Stokeslets and rotlets~\cite{pow-mir1987}
 \begin{align}
@@
       &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
-    \llambda_\ell &= \int_{\gamma_i} \eeta(\yy) \, ds_\yy, 
+    \llambda_\ell &= \int_{\gamma_\ell} \eeta(\yy) \, ds_\yy, 
       &&\ell = 1,\ldots,M, \\
-    \xi_\ell &= \int_{\gamma_i} (\yy - \cc_i)^\perp \cdot 
+    \xi_\ell &= \int_{\gamma_\ell} (\yy - \cc_\ell)^\perp \cdot 
       \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
@@
 \end{subequations}
-then the representation~\eqref{eqn:velocity}
-satisfies~\eqref{eqn:StokesEq}. We solve~\eqref{eqn:FredBIE} by choosing
-equispaced collocation points on $\gamma_\ell$ and $\Gamma$, and then
-replacing the integrals with quadrature rules. This results in a linear
-system with a mesh-independent condition number, and it is solved
-iteratively with GMRES.
+then the representation~\eqref{eqn:velocity} satisfies the Stokes
+equations with the required boundary conditions~\eqref{eqn:StokesEq}. We
+solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at
+equispaced collocation points, and then replacing the integrals with
+quadrature rules. This results in a linear system with a
+mesh-independent condition number, and it is solved iteratively with
+GMRES.
 
-We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use similar
-notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the
-boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan
-curve in $\CC$. We introduce the functions
+Instead of evaluating the Stokes double-layer
+potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we
+convert the integral to a sum of contour integrals around Jordan curves
+in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
+similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret
+$\gamma$, the boundary of the $i^{th}$ grain or the bounding box
+$\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
 \begin{align}
@@
 potential are
+\begin{subequations}
   \begin{align}
@@
   \end{align}
-respectively. The vorticity can be shown to satisfy
+  \label{eqn:velocityCauchy}
+\end{subequations}
+respectively. The hydrodynamic components of the deformation tensor are
+\begin{subequations}
   \begin{align}
-  \omega(x) = \Im(v_1'(x)) + \Re(v_2'(x)) + 
-     \Re(v_5'(x)) + \Im(v_4'(x)).
+    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
+                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
+    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
+                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
+    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
+                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
+    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
+                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
   \end{align}
-We note that the vorticity only requires first derivatives of Cauchy
-integrals, but the stress tensor involves second derivatives.
+  \label{eqn:deformationCauchy}
+\end{subequations}
+Having the deformation tensor at hand, the vorticity can be shown to
+satisfy
+\begin{align}
+  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
+     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
+  \label{eqn:vorticityCauchy}
+\end{align}
+We note that the deformation tensor requires second-order derivatives of
+Cauchy integrals, but the vorticity only requires first-order
+derivatives.
 
-The accuracy of the method is determined by the accuracy of the
-quadrature rule applied to equation~\eqref{eqn:FredBIE}. A quadrature
-rule for~\eqref{eqn:velocityDLP} that achieves spectral accuracy writes
-the Stokes double-layer potential as a collection of Cauchy integrals
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Quadrature for Cauchy integrals}
+The accuracy of our method is determined by the accuracy of the
+quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
+written the Stokes double-layer potential
+velocity~\eqref{eqn:velocityCauchy}, deformation
+tensor~\eqref{eqn:deformationCauchy}, and
+vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
+their derivatives, the accuracy of the method depends on the accuracy of
+computing a general Cauchy integral
 \begin{align}
   v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
+  \label{eqn:cauchy1}
 \end{align}
-The boundary data of $v(x)$ satisfies the Sokhotski-Plemelj jump relation
+Here we describe a quadrature formulae that was first used to
+approximate analytic functions~\cite{ioa-pap-per1991}, and then extended
+to Stokes layer potentials~\cite{bar-wu-vee2015}. The quadrature
+requires the boundary data of the analytic function~\eqref{eqn:cauchy1}
+which satisfies the Sokhotski-Plemelj jump relation
 \begin{align}
@@
   \begin{alignat}{3}
-  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
+  \label{eqn:cauchyv}
+  v(x) &= \frac{1}{2\pi i}\int_{\gamma} 
     \frac{v^{-}(y)}{y-x} \,dy, \\
-  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
+  v'(x) &= \frac{1}{2\pi i} \int_{\gamma}
     \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
-  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
+  v''(x) &= \frac{1}{\pi i} \int_{\gamma}
     \frac{v^{-}(y)}{(y-x)^3} \, dy.
@@
 \end{subequations}
-Note that we require second-order derivatives to compute the shear
-stress.
+
+To approximate the Cauchy integrals and its
+derivatives~\eqref{eqn:cauchy}, the trapezoid rule achieves spectral
+accuracy. For example, the Cauchy integral~\eqref{eqn:cauchyv} can be
+approximated as
+\begin{align}
+  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
+    w_j \frac{v^{-}(y_j)}{y_j - x},
+  \label{eqn:trap}
+\end{align}
+where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
+the length of $\gamma$. Because the integrand is both periodic and
+smooth, given a fixed points $x$, the trapezoid rule achieves spectral
+accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
+error is not bounded uniformly with respect to $x$ because the
+derivative of the integrand grows without bound as $x$ approaches
+$\gamma$. This error is problematic for many of our simulations since we
+allow for eroding bodies to be arbitrarily close to one another. In
+contrast to the Cauchy integral~\eqref{eqn:cauchyv}, the integrand in
+the identity
+\begin{align}
+  \frac{1}{2\pi i}\int_{\gamma} 
+    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
+  \label{eqn:trap2}
+\end{align}
+is bounded with respect to $x$, and therefore the error of the trapezoid
+rule is bounded with respect to $x$. Applying the trapezoid rule, we
+have
+\begin{align}
+  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
+    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
+\end{align}
+where the error is independent of $x$. Rearranging, we have
+\begin{align}
+  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
+    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
+  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
+  \quad x \in \Omega.
+  \label{eqn:vBary}
+\end{align}
+Note that the numerator in~\eqref{eqn:vBary} is identical to
+equation~\eqref{eqn:trap}, while the denominator is an approximation of
+the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the error
+in the numerator and denominator grow, however, since the integrand in
+equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
+the ratio is bounded independent of $x$.
 
@@
 %-----------------------------------------------------------------------------------------------%
-\subsection{Boundary Integral Representation in $\RR^2$}
+%\subsection{Boundary Integral Representation in $\RR^2$}
 %-----------------------------------------------------------------------------------------------%
 
-\vsp{2} \nick{Finished rewording up to here} \vsp{2}
+%\vsp{2} \nick{Finished rewording up to here} \vsp{2}
+%
+%Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
+%corresponding deformation tensor, pressure, and vorticity at $\xx \in
+%\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
+%To compute the deformation tensor for $\xx \in \gamma$, we include the
+%jump term
+%\begin{align}
+%  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
+%    \begin{array}{cc}
+%      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
+%    \end{array}
+%  \right].
+%  \label{eqn:deformationJump}
+%\end{align}
+%Finally, the deformation tensor, pressure, and vorticity due to the
+%Stokeslets and rotlets are readily available~\citep{poz1992}. Having
+%computed the deformation tensor on $\gamma$, the shear stress is
+%computed using equation~\eqref{eqn:shearStress}.
 
-Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
-corresponding deformation tensor, pressure, and vorticity at $\xx \in
-\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
-To compute the deformation tensor for $\xx \in \gamma$, we include the
-jump term
-\begin{align}
-  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
-    \begin{array}{cc}
-      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
-    \end{array}
-  \right].
-  \label{eqn:deformationJump}
-\end{align}
-Finally, the deformation tensor, pressure, and vorticity due to the
-Stokeslets and rotlets are readily available~\citep{poz1992}. Having
-computed the deformation tensor on $\gamma$, the shear stress is
-computed using equation~\eqref{eqn:shearStress}.
-
-%-----------------------------------------------------------------------------------------------%
-\subsection{Cauchy Integral Formulation}
-\label{sec:DLPcomplex}
-%-----------------------------------------------------------------------------------------------%
-The velocity double-layer potential~\eqref{eqn:velocityDLP}, and its
-corresponding deformation tensor, pressure, and vorticity are all
-written as layer potentials in $\RR^2$. However, the quadrature method
-we introduce in section~\ref{sec:method} requires complex-valued
-representations. The first step to form a complex representation is to
-write the Laplace double-layer potential as the complex integral
-\begin{align}
-  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
-    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)),
-\end{align}
-where
-\begin{align}
-  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega.
-  \label{eqn:laplaceComplex}
-\end{align}
-Here $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
-counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
-\eta_1 + i \eta_2$ is the complex counterpart of $\eeta =
-(\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
-potential, $\Omega$ is interpreted as a subset of $\RR^2$ or $\CC$.
-Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
-first finding the boundary data of $v$. If $\Omega$ is a
-simply-connected interior domain, then the boundary data of $v$
-satisfies the Sokhotski-Plemelj jump relation
-\begin{align}
-  \label{eqn:SPrelation}
-  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
-\end{align}
-For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
-for multiply-connected domains, such as a porous media, $\bd\Omega$ is
-decomposed into its different connected components and the appropriate
-jump relation is applied.  Having computed the boundary data of the
-holomorphic function $v$, by the Cauchy integral theorem we have
-\begin{subequations}
-  \label{eqn:cauchy}
-  \begin{alignat}{3}
-  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
-    \frac{v(y)}{y-x} \,dy, \\
-  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^2} \, dy, \\
-  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
-    \frac{v(y)}{(y-x)^3} \, dy,
-  \end{alignat}
-\end{subequations}
-for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
-function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
-function defined in equation~\eqref{eqn:laplaceComplex}, and its first
-two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.
-
-Finally, the Stokes double-layer potential~\eqref{eqn:velocityDLP} can
-be written using a Laplace double-layer
-potential~\eqref{eqn:laplaceComplex} and its gradients 
-\begin{equation}
-  \label{eqn:Stokes2Laplace}
-  \begin{aligned}
-    \DDD[\eeta](\xx) &= 
-      \frac{1}{2\pi} \int_{\bd\Omega} 
-        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
-      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
-        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
-      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
-        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
-      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
-        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
-  \end{aligned}
-\end{equation}
-Therefore, the Stokes double-layer potential can be written as a sum of
-Cauchy integrals and its first derivative~\citep{bar-wu-vee2015}
-\begin{equation}
-  \begin{aligned}
-    u_1(x) &= \Real (v[\psi_1](x)) + \Real (v'[y\cdot\eta](x)) 
-             -x_1\Real (v'[\eta_1](x)) - x_2\Real (v'[\eta_2](x)), \\
-    u_2(x) &= \Real (v[\psi_2](x)) - \Imag (v'[y\cdot\eta](x)) 
-         +x_1\Imag (v'[\eta_1](x)) + x_2\Imag (v'[\eta_2](x)),
-  \end{aligned}
-  \label{eqn:cauchyVelocity}
-\end{equation}
-where $y \cdot \eta = y_1 \eta_1 + y_2 \eta_2$, 
-\begin{align} 
-  \psi_1=(\eta_1+i\eta_2)\frac{\Real(n)}{n}, \quad
-  \psi_2=(\eta_1+i\eta_2)\frac{\Imag(n)}{n},
-\end{align}
-and $n \in \CC$ is the complex counterpart of the outward unit normal
-$\nn \in \RR^2$.
-
-%-----------------------------------------------------------------------------------------------%
-\subsection{Cauchy Integral Representation for the Gradient of the
-Double-Layer Potential}
-\label{sec:gradDLPcomplex}
-%-----------------------------------------------------------------------------------------------%
-Computing the shear stress and vorticity requires a complex-valued layer
-potential representation of the velocity gradient.  The deformation
-tensor at $x \in \Omega$ is found by computing the derivatives of the
-expressions for $u_1$ and $u_2$ in equation~\eqref{eqn:cauchyVelocity}  
-\begin{equation}
-\label{eqn:cauchyGradient}
-  \begin{aligned}
-    \pderiv{u_1}{x_1} &= +\Real (v'[\psi_1](x)) + 
-    \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) \\
-    &- x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
-    \pderiv{u_1}{x_2} &= - \Imag (v'[\psi_1](x)) - 
-    \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) \\
-    &- \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
-    \pderiv{u_2}{x_1} &= +\Real (v'[\psi_2](x)) - 
-    \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x))  \\
-    &+ x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
-    \pderiv{u_2}{x_2} &= -\Imag (v'[\psi_2](x)) - 
-    \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) \\
-    &+ \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
-  \end{aligned}
-\end{equation}
-The same expressions are used to compute the deformation tensor for $x
-\in \bd\Omega$, except that the jump
-condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
-the shear stress, the deformation tensor on $\bd\Omega$ is applied to
-the normal and tangent vectors as in equation~\eqref{eqn:shearStress}.
-The velocity gradient is also used to compute the vorticity in the fluid
-bulk.  For $x \in \Omega$, the Cauchy integral representation of the
-vorticity at $x \in \Omega$ is
-\begin{align}
-  \omega(x) = 
-    \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))+ 
-    \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
-\end{align}
+%%-----------------------------------------------------------------------------------------------%
+%\subsection{Cauchy Integral Formulation}
+%\label{sec:DLPcomplex}
+%%-----------------------------------------------------------------------------------------------%
+%The velocity double-layer potential~\eqref{eqn:velocityDLP}, and its
+%corresponding deformation tensor, pressure, and vorticity are all
+%written as layer potentials in $\RR^2$. However, the quadrature method
+%we introduce in section~\ref{sec:method} requires complex-valued
+%representations. The first step to form a complex representation is to
+%write the Laplace double-layer potential as the complex integral
+%\begin{align}
+%  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
+%    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)),
+%\end{align}
+%where
+%\begin{align}
+%  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
+%    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega.
+%  \label{eqn:laplaceComplex}
+%\end{align}
+%Here $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
+%counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
+%\eta_1 + i \eta_2$ is the complex counterpart of $\eeta =
+%(\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
+%potential, $\Omega$ is interpreted as a subset of $\RR^2$ or $\CC$.
+%Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
+%first finding the boundary data of $v$. If $\Omega$ is a
+%simply-connected interior domain, then the boundary data of $v$
+%satisfies the Sokhotski-Plemelj jump relation
+%\begin{align}
+%  \label{eqn:SPrelation}
+%  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
+%    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
+%\end{align}
+%For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
+%for multiply-connected domains, such as a porous media, $\bd\Omega$ is
+%decomposed into its different connected components and the appropriate
+%jump relation is applied.  Having computed the boundary data of the
+%holomorphic function $v$, by the Cauchy integral theorem we have
+%\begin{subequations}
+%  \label{eqn:cauchy}
+%  \begin{alignat}{3}
+%  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
+%    \frac{v(y)}{y-x} \,dy, \\
+%  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
+%    \frac{v(y)}{(y-x)^2} \, dy, \\
+%  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
+%    \frac{v(y)}{(y-x)^3} \, dy,
+%  \end{alignat}
+%\end{subequations}
+%for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
+%function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
+%function defined in equation~\eqref{eqn:laplaceComplex}, and its first
+%two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  
+%  
+%Finally, the Stokes double-layer potential~\eqref{eqn:velocityDLP} can
+%be written using a Laplace double-layer
+%potential~\eqref{eqn:laplaceComplex} and its gradients 
+%\begin{equation}
+%  \label{eqn:Stokes2Laplace}
+%  \begin{aligned}
+%    \DDD[\eeta](\xx) &= 
+%      \frac{1}{2\pi} \int_{\bd\Omega} 
+%        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
+%      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
+%        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
+%      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
+%        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
+%      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
+%        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
+%  \end{aligned}
+%\end{equation}
+%Therefore, the Stokes double-layer potential can be written as a sum of
+%Cauchy integrals and its first derivative~\citep{bar-wu-vee2015}
+%\begin{equation}
+%  \begin{aligned}
+%    u_1(x) &= \Real (v[\psi_1](x)) + \Real (v'[y\cdot\eta](x)) 
+%             -x_1\Real (v'[\eta_1](x)) - x_2\Real (v'[\eta_2](x)), \\
+%    u_2(x) &= \Real (v[\psi_2](x)) - \Imag (v'[y\cdot\eta](x)) 
+%         +x_1\Imag (v'[\eta_1](x)) + x_2\Imag (v'[\eta_2](x)),
+%  \end{aligned}
+%  \label{eqn:cauchyVelocity}
+%\end{equation}
+%where $y \cdot \eta = y_1 \eta_1 + y_2 \eta_2$, 
+%\begin{align} 
+%  \psi_1=(\eta_1+i\eta_2)\frac{\Real(n)}{n}, \quad
+%  \psi_2=(\eta_1+i\eta_2)\frac{\Imag(n)}{n},
+%\end{align}
+%and $n \in \CC$ is the complex counterpart of the outward unit normal
+%$\nn \in \RR^2$.
+%
+%%-----------------------------------------------------------------------------------------------%
+%\subsection{Cauchy Integral Representation for the Gradient of the
+%Double-Layer Potential}
+%\label{sec:gradDLPcomplex}
+%%-----------------------------------------------------------------------------------------------%
+%Computing the shear stress and vorticity requires a complex-valued layer
+%potential representation of the velocity gradient.  The deformation
+%tensor at $x \in \Omega$ is found by computing the derivatives of the
+%expressions for $u_1$ and $u_2$ in equation~\eqref{eqn:cauchyVelocity}  
+%\begin{equation}
+%\label{eqn:cauchyGradient}
+%  \begin{aligned}
+%    \pderiv{u_1}{x_1} &= +\Real (v'[\psi_1](x)) + 
+%    \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) \\
+%    &- x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
+%    \pderiv{u_1}{x_2} &= - \Imag (v'[\psi_1](x)) - 
+%    \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) \\
+%    &- \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
+%    \pderiv{u_2}{x_1} &= +\Real (v'[\psi_2](x)) - 
+%    \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x))  \\
+%    &+ x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
+%    \pderiv{u_2}{x_2} &= -\Imag (v'[\psi_2](x)) - 
+%    \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) \\
+%    &+ \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
+%  \end{aligned}
+%\end{equation}
+%The same expressions are used to compute the deformation tensor for $x
+%\in \bd\Omega$, except that the jump
+%condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
+%the shear stress, the deformation tensor on $\bd\Omega$ is applied to
+%the normal and tangent vectors as in equation~\eqref{eqn:shearStress}.
+%The velocity gradient is also used to compute the vorticity in the fluid
+%bulk.  For $x \in \Omega$, the Cauchy integral representation of the
+%vorticity at $x \in \Omega$ is
+%\begin{align}
+%  \omega(x) = 
+%    \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))+ 
+%    \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
+%\end{align}
 %\end{comment}

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{abstract}
-Using a Cauchy integral formulation of the boundary integral equations, we numerically simulation the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow.
-The bodies comprising the porous medium are resolved individually and erode under the action of surface shear stress.
-In particular, changes in the morphology of individual bodies are resolved in detail, and these microscopic changes give rise to larger-scale features in the medium such as channelization.
+Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow.
+The grains of the medium are resolved individually and erode under the action of surface shear stress.
+In particular, detailed changes in grain morphology are resolved, and these microscopic changes give rise to larger-scale features in the medium such as channelization.
 The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies.
-Armed with these methods, we observe anisotropy
+We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by a factor of roughly five.
+\\
+Tie it to alternate hypothesis in groundwater.
 \end{abstract}
 \maketitle
-
-impinging intervening interal
 
@@
 Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of order hundreds of solid bodies (please see \cite{Mitchell2016} for related work).
-The recent incorporation of barycentric interpolation methods permits simulation of tightly packed configurations (cite new paper with Shang).
+The recent incorporation of barycentric interpolation methods permits simulation of tightly packed configurations \cite{chiu2020viscous}
 
-% Need to include descriptor 'high-fidelity' for our simulation.
+% Can include descriptor 'high-fidelity' for our simulation.
 
@@
 
-% NOTE: THIS SECTION HAS BEEN PLAGIARIZED FROM JFM 2020
-% SO WE NEED TO PARAPHRASE IT
-%\begin{comment}
 %-----------------------------------------------------------------------------------------------%
@@
 
-%\vsp{2} \nick{Finished rewording up to here} \vsp{2}
 %
@@
 %\end{align}
-%\end{comment}
 

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 In particular, detailed changes in grain morphology are resolved, and these microscopic changes give rise to larger-scale features in the medium such as channelization.
-The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies.
-We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by a factor of roughly five.
+The Cauchy-integral and barycentric quadrature formulas enable us to resolve configurations of tightly packed and nearly contacting bodies.
+We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by a factor up to five.
 \\
@@
 
+% dematerialize, disintegrate
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-
-%Shear stress on solid surfaces drives the erosion of porous material
-
-% dematerialize, disintegrate
 
@@
 
-Effects of flow-induced erosion are visible across a range of scales in nature, from massive geological structures, to mesoscopic patterns, and down to the tiny granular constituents that comprise a porous medium.
+Effects of flow-induced erosion are visible across a range of scales, from massive geological structures, to mesoscopic patterns, and down to the tiny granular constituents that comprise a porous medium.
 In the case of a porous medium specifically, it has been long recognized that bulk properties of mediums encountered in nature are typically anisotropic, so that the medium allows flow in a preferred direction more easily.

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM
worked on first draft of Sec 3

--- 2022-06-13 docs/PhysicsPaper/StokesErosion.tex
@@
   equations~\eqref{eqn:StokesEq}, we reformulate the system as a
-  boundary integral equation (BIE). Applying the same approach as our
-  previous works~\citep{quaife2018boundary, chiu2020viscous}, we
-  represent the velocity as the sum of a double-layer potential and a
-  combination of Stokeslets and rotlets~\cite{pow-mir1987}
+  boundary integral equation (BIE). A BIE formulation has the advantage
+  that all the unknowns are on the one-dimensional boundary of the
+  domain. Therefore, only the boundary of the complex geometry must be
+  discretized which we do with a spectrally accurate Fourier basis.
+  Applying the same approach as our previous
+  works~\citep{quaife2018boundary, chiu2020viscous}, we represent the
+  velocity as the sum of a double-layer potential and a combination of
+  Stokeslets and rotlets~\cite{pow-mir1987}
 \begin{align}
@@
 \begin{align}
-  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
+  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(-\log \rho_\ell +
   \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
@@
 \end{align}
-where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
-$\cc_\ell$ is a point inside body $\ell$. If the density function,
-Stokeslets, and rotlets satisfy the second-kind boundary integral
-equation
+respectively, where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell =
+\|\rr_\ell\|$, and $\cc_\ell$ is a point inside body $\ell$. If the
+density function, Stokeslets, and rotlets satisfy the second-kind
+boundary integral equation
 \begin{subequations}
@@
 \end{subequations}
-respectively. The hydrodynamic components of the deformation tensor are
+respectively. The components of the deformation tensor are
 \begin{subequations}
@@
 We note that the deformation tensor requires second-order derivatives of
-Cauchy integrals, but the vorticity only requires first-order
+Cauchy integrals, while the vorticity only requires first-order
 derivatives.
@@
 approximate analytic functions~\cite{ioa-pap-per1991}, and then extended
-to Stokes layer potentials~\cite{bar-wu-vee2015}. The quadrature
+to Stokes layer potentials~\cite{bar-wu-vee2015}. The quadrature method
 requires the boundary data of the analytic function~\eqref{eqn:cauchy1}
@@
 where the last integral is interpreted in the principal value sense.
-Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
-by its boundary data alone using the Cauchy Integral Theorem
+Here we are assuming that $\Omega$ is the bounded region interior to
+$\gamma$. Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be
+determined by its boundary data alone using the Cauchy Integral Theorem
 \begin{subequations}
@@
 the length of $\gamma$. Because the integrand is both periodic and
-smooth, given a fixed points $x$, the trapezoid rule achieves spectral
+smooth, given a fixed point $x$, the trapezoid rule achieves spectral
 accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
@@
 $\gamma$. This error is problematic for many of our simulations since we
-allow for eroding bodies to be arbitrarily close to one another. In
-contrast to the Cauchy integral~\eqref{eqn:cauchyv}, the integrand in
-the identity
+allow for eroding bodies to be arbitrarily close to one another, and we
+often compute the velocity and vorticity at points in the fluid domain
+that are close to an eroding body. In contrast to the integrand in the
+Cauchy integral~\eqref{eqn:cauchyv}, the integrand in the identity
 \begin{align}
@@
 \end{align}
-where the error is independent of $x$. Rearranging, we have
+where the error is now uniformly bounded for all $x$. Rearranging, we
+have
 \begin{align}
@@
 equation~\eqref{eqn:trap}, while the denominator is an approximation of
-the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the error
+the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the errors
 in the numerator and denominator grow, however, since the integrand in
@@
 the ratio is bounded independent of $x$.
+
+The derivatives of the Cauchy integral in~\eqref{eqn:cauchy} can be
+approximated with similar quadrature rules. For $x \in \Omega$, 
+\begin{align}
+  v'(x) &\approx \left(\frac{1}{2\pi i}\sum_{j=1}^{N}
+    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
+  \Bigg/
+  \left(\frac{1}{2\pi i}\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
+  \label{eqn:D1vBary} \\
+  v''(x) &\approx \left(\frac{2}{2\pi i}\sum_{j=1}^N 
+    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
+    \Bigg/
+    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
+  \label{eqn:D2vBary}
+\end{align}
+where the quadrature rule is spectrally accurate and the error is
+independent of $x$. We note that
+equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
+and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
+is the bounded region interior to the Jordan curve $\gamma$. However, in
+our application, when $\gamma$ is one of the eroding bodies, $x$ is in
+the exterior region of the Jordan curve. In this case, slightly
+different identities are used, but they all guarantee that the trapezoid
+rule achieves spectral accuracy with an error that is independent of
+$x$. A complete description of the quadrature rules
+for~\eqref{eqn:vBary} and~\eqref{eqn:D1vBary} are described by Barnett,
+Wu, and Veerapaneni~\cite{bar-wu-vee2015}, and the quadrature rule
+for~\eqref{eqn:D2vBary} is described in our previous
+work~\cite{chiu2020viscous}.
 

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex

@@
 \begin{abstract}
-Using a Cauchy integral formulation of the boundary integral equations, we numerically simulation the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow.
-The bodies comprising the porous medium are resolved individually and erode under the action of surface shear stress.
-In particular, changes in the morphology of individual bodies are resolved in detail, and these microscopic changes give rise to larger-scale features in the medium such as channelization.
-The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies.
-Armed with these methods, we observe anisotropy
+Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow.
+The grains of the medium are resolved individually and erode under the action of surface shear stress.
+In particular, detailed changes in grain morphology are resolved, and these microscopic changes give rise to larger-scale features in the medium such as channelization.
+The Cauchy-integral and barycentric quadrature formulas enable us to resolve configurations of tightly packed and nearly contacting bodies.
+We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by a factor up to five.
+\\
+Tie it to alternate hypothesis in groundwater.
 \end{abstract}
 \maketitle
-
-impinging intervening interal
 
@@
 
-Effects of flow-induced erosion are visible across a range of scales in nature, from massive geological structures, to mesoscopic patterns, and down to the tiny granular constituents that comprise a porous medium.
+The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures, to mesoscopic patterns, and down to the  granular constituents that comprise a porous medium.
+
+% ORIGINAL BELOW
+Effects of flow-induced erosion are visible across a range of scales, from massive geological structures, to mesoscopic patterns, and down to the tiny granular constituents that comprise a porous medium.
 In the case of a porous medium specifically, it has been long recognized that bulk properties of mediums encountered in nature are typically anisotropic, so that the medium allows flow in a preferred direction more easily.

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures, to mesoscopic patterns, and down to the  granular constituents that comprise a porous medium.
+The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{bertagni2021hydrodynamic}, and down to the  granular constituents that comprise a porous medium \cite{zareei2022temporal}.
 

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
@@
 
-The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures, to mesoscopic patterns, and down to the  granular constituents that comprise a porous medium.
+The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the  granular constituents that comprise a porous medium \cite{zareei2022temporal}.
 

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
@@
 % dematerialize, disintegrate
+% internal, permeating, intervening
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
@@
 
-The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures, to mesoscopic patterns, and down to the  granular constituents that comprise a porous medium.
+The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents comprising porous media \cite{zareei2022temporal}.
+Porous media encountered in natural settings typically exhibit {\em anisotropic} material properties,
 
+\vsp{5}
 % ORIGINAL BELOW
@@
 \end{equation}
-Note that the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one, and as the configuration erodes, the configuration would be expected to permit flow in the longitudinal direction more easily than in the transverse direction, yielding $\anis > 1$.
+Note that the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one.
+As this configuration erodes, it would be expected to permit flow in the longitudinal direction more easily than in the transverse direction, yielding $\anis > 1$.
 
@@
 
-It is possible to device a test to isolate these two types of anisotropy.
+It is possible to devise a test to isolate these two types of anisotropy.
 Introduce circular bodies with same centers of mass...

### 2022-06-16 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents comprising porous media \cite{zareei2022temporal}.
-Porous media encountered in natural settings typically exhibit {\em anisotropic} material properties,
+The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents of porous media \cite{zareei2022temporal}.
+The porous media encountered in nature typically exhibit material {\em anisotropy} in that they permit seepage flow in one direction more easily than in others.
+Typically, materials can be more permeable to flow in the longitudinal direction by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}.
 

### 2022-06-16 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
@@
 
-The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents comprising porous media \cite{zareei2022temporal}.
-Porous media encountered in natural settings typically exhibit {\em anisotropic} material properties,
+Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents of porous media as they slowly disintegrate in groundwater flows \cite{zareei2022temporal}.
+The shape-flow feedback of erosion can imprint across all of these scales, affecting both large-scale features and small-scale ones, such as the microstructure of porous materials.
+The porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
+Typically, materials can be more permeable to flow in the longitudinal (or horizontal) direction than the transverse one by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}.
+Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plan of deposition \cite{bear1988dynamics}.
+Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may also be at work.
+Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.
 
 \vsp{5}
-% ORIGINAL BELOW
-Effects of flow-induced erosion are visible across a range of scales, from massive geological structures, to mesoscopic patterns, and down to the tiny granular constituents that comprise a porous medium.
-In the case of a porous medium specifically, it has been long recognized that bulk properties of mediums encountered in nature are typically anisotropic, so that the medium allows flow in a preferred direction more easily.
-This anisotropy is commonly attributed to how grains are deposited, with their longest dimension parallel to the settling bed, so that they allow flow preferentially in the horizontal direction.
-Controlled experiments, however, have not been performed to test this hypothesis.
-Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.
 

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 In particular, detailed changes in grain morphology are resolved, and these microscopic changes give rise to larger-scale features in the medium such as channelization.
-The Cauchy-integral and barycentric quadrature formulas enable us to resolve configurations of tightly packed and nearly contacting bodies.
+The Cauchy-integral formulation and associated quadrature formulas enable us to resolve configurations of tightly packed and nearly contacting bodies.
 We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by a factor up to five.
@@
 The porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
-Typically, materials can be more permeable to flow in the longitudinal (or horizontal) direction than the transverse one by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}.
+Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}.
 Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plan of deposition \cite{bear1988dynamics}.
-Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may also be at work.
+Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work.
 Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.
+
+Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods with stable interface evolution methods to simulate the erosion of dense suspensions of solid bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}.
+Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
+The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies \cite{chiu2020viscous}.
 
@@
 
-Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}.
-Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of order hundreds of solid bodies (please see \cite{Mitchell2016} for related work).
-The recent incorporation of barycentric interpolation methods permits simulation of tightly packed configurations \cite{chiu2020viscous}
-
-% Can include descriptor 'high-fidelity' for our simulation.
-
 Figure \ref{FigVortVel} shows an example illustration of 80 eroding bodies
-
-Anisotropy in groundwater is around 10 \cite{anderson2015applied}.
 

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \end{equation}
-but this form is not useful if no vertical pressure gradient is imposed, as is the case in our erosion simulations.
+This form, however, is not useful if no vertical pressure gradient is imposed, as is the case in our erosion simulations.
 It is important to recognize that the permeability is a property of the {\em medium}, not the imposed flow.
@@
 Thus, instead of a horizontal flow in the far-field, we seek to impose a vertical one $\UU = (0,U)$.
-If this were to be done directly, the outer geometry would need to be rotated by 90 degrees about the configuration of bodies inside (which does not rotate).
-In practice, it is simpler to keep the outer geometry fixed and instead rotate the inner configuration of bodies, then simply apply the method from Section \ref{LongPerm} to measure $k_{22}$.
+If this were to be done directly, the outer geometry would need to rotate by 90 degrees about the fixed configuration of bodies.
+In practice, it is simpler to keep the outer geometry fixed and rotate the inner configuration of bodies, then simply apply the method from Section \ref{LongPerm} to measure $k_{22}$.
 
-With both the longitudinal and transverse components of permeability calculated, we define the anisotropy of the medium as the ratio
+With both the longitudinal and transverse components of permeability computed, we define the anisotropy of the medium as the ratio between the two:
 \begin{equation}
@@
 
-There are two mechanistic explanations for how erosion can create this anisotropy.
+There are two mechanistic explanations for how erosion can create medium anisotropy.
 First, the shear stresses could carve each individual body into a more slender form, thus creating anisotropy at the level of individual grains.
-Second, by removing material in a non-uniform way, could preferentially disintegrate certain bodies before others, leaving an overall configuration that exhibits anisotropy on the large scale, for example one with horizontally aligned channels.
+Second, the shear stressed could preferentially remove certain bodies before others, thus creating large-scale anisotropy.
+For example, a body positioned in a high-throughput channel might disintegrate relatively quickly, thus opening the channel and creating higher overall anisotropy.
 We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively.
-As an extreme example, a tightly-packed horizontal row of circular bodies would exhibit configurational anisotropy but no shape anisotropy.
+As an extreme example, a tightly-packed horizontal row of circular bodies would exhibit high configurational anisotropy but no shape anisotropy.
 Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit high shape anisotropy and low configurational anisotropy.
+We note that channelization is likely associated with {\em both} types of anisotropy.
+Certainly the overall configuration must support a channel, and, secondly, the geometry of the individual bodies that outline the channel could control its structure to some degree.
+
+	Fortunately, it is possible to devise a test to isolate these two types of anisotropy from one another and therefore determine how much each contributes to the total anisotropy.
+In particular, for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass.
+Since the configurations resulted from the erosion of initially circular bodies, such a replacement does not lead to any overlap between bodies.
+We then measure the two permeabilities, $k_{11}^{(c)}$ and $ k_{22}^{(c)}$, of this configuration of circular bodies.
+Since all of the individual shapes are identical and isotropic (i.e.
+circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$.
+The total anisotropy, meanwhile, is the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured.
+We can therefore deduce the shape anisotropy through $\anis_S = \anis/\anis_C$.
 
 \vsp{2} \nick{To here in editing} \vsp{2}
-
-We note that channelization is related to both shape and configurational anisotropy....
-
-It is possible to devise a test to isolate these two types of anisotropy.
-Introduce circular bodies with same centers of mass...
-Thus, the configurational anisotropy is defined as
-\begin{equation}
-\anis_C = k_1^{(c)} / k_2^{(c)}
-\end{equation}
-
-The total anisotropy is the product of the shape and configurational
-\begin{equation}
-\anis = \anis_S \anis_C
-\end{equation}
 

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
N
NM

@@
 Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents of porous media as they slowly disintegrate in groundwater flows \cite{zareei2022temporal}.
-The shape-flow feedback of erosion can imprint across all of these scales, affecting both large-scale features and small-scale ones, such as the microstructure of porous materials.
+The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting both large-scale features and small-scale ones, such as the microstructure of porous materials.
 The porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
@@
 The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies \cite{chiu2020viscous}.
+Though the governing fluid-flow equations (Stokes) in this regime are linear, the feedback between complex eroding geometries and the flow leads to highly nonlinear behavior.
 
@@
 %-----------------------------------------------------------------------------------------------%
-\section{Measuring permeability and other porous-media properties}
+\section{Measuring porous-media properties: permeability, drag, and anisotropy}
 \label{sec:}
@@
 
+%-----------------------------------------------------------------------------------------------%
+\section{Results}
+%-----------------------------------------------------------------------------------------------%
+
+We now do stuff
+
 \vsp{2} \nick{To here in editing} \vsp{2}

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The grains of the medium are resolved individually and erode under the action of surface shear stress.
-In particular, detailed changes in grain morphology are resolved, and these microscopic changes give rise to larger-scale features in the medium such as channelization.
+Through nonlinear feedback with the surrounding flow fields, microscopic changes in grain morphology give way to larger-scale features in the medium such as channelization.
 The Cauchy-integral formulation and associated quadrature formulas enable us to resolve configurations of tightly packed and nearly contacting bodies.

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents of porous media as they slowly disintegrate in groundwater flows \cite{zareei2022temporal}.
-The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting both large-scale features and small-scale ones, such as the microstructure of porous materials.
-The porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
+The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting large-scale features as well as small-scale ones, such as the microstructure of porous materials.
+Porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
 Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}.

### 2022-06-17 simulations/vplots.jl
NM

@@ -106,6 +106,8 @@ end
 
 # Possible runs: 20:2,5,8; 40:3,7,8; 60:3,7,9; 80:4,7,9; 100:3,6,9
 # 100-9 looks quite good showing the configuration anisotropy near the end.
+# 80-4 is also great for configurational anisotropy.
+# 60-3 is a nice visual run for showing channelization.
 vplot_single("100-9")
 #---------------------------------------------------------------#
 

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
Added figures
NM

@@
 
-\vsp{5}
+	Figure \ref{fig1} shows an example simulation of the erosion of 80 bodies, with the local speed of the intervening fluid flow shown by color.
+This simulation illustrates the {\em channelization} process, in which regions of high flow speed create higher local shear rates, thus preferentially removing solid material, and further opening the channels.
+The positive feedback creates the channels that are clearly visible by in final two images.
 
-Figure \ref{FigVortVel} shows an example illustration of 80 eroding bodies
+%\ref{fig1}
+
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
+\begin{figure*}%[htbp]
+\centering \label{fig1}
+\includegraphics[width = 0.99 \textwidth]{./figs/Velocity-80-4.pdf}
+\caption{Numerical simulation of a dense suspension of 80 bodies eroding in a Stokes flow.
+Over time, the non-uniform erosion of material opens channels in the medium, leading to high anisotropy.}
+\end{figure*}
+ %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 
@@
 % Cite paper by Ladd "Wormhole formation in dissolving fractures"
-
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure*}[] \centering
-        \subfigure[ Vorticity field]{ \label{FigVort}
-            \includegraphics[width=0.9 \textwidth]{figs/80circ8vort.pdf} } \\
-        \subfigure[ Velocity magnitude]{ \label{FigVel}
-            \includegraphics[width=0.9 \textwidth]{figs/80circ8vel.pdf} }
-   \caption{80 eroding bodies}
-   \label{FigVortVel}
-\end{figure*}
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% Data from 80circ8
-
-\begin{comment}
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\begin{figure*}%[htbp]
-\centering \label{fig1}
-\includegraphics[width = 0.9 \textwidth]{./figs/80circ8vel.pdf}
-\caption{caption}
-\end{figure*}
- %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-\end{comment}
 
@@
 \caption{A single simulation of porous-medium erosion.
-The initial configuration consists of 100 circular bodies of random size and position, as seen in Fig.~1?
+The initial configuration consists of XX circular bodies of random size and position, as seen in Fig.~1?
 a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases.
@@
 %---------------------------------------------------------%
-% Data from 100-3
 

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \newcommand{\CE}{C_E}
+\newcommand{\thL}{$\theta$--$L$}
 %---------------------------------------------------%
@@
 %-----------------------------------------------------------------------------------------------%
+\subsection{Interface evolution}
+%-----------------------------------------------------------------------------------------------%
+
+% COPIED STRAIGHT FROM JFM 2020
+\nick{PLAGERIZED}
+We use the time stepping method outlined in our previous
+work~\citep[see][section 3.3]{qua-moo2018} which we briefly summarize
+here.  The erosion rate loses differentiability if the shear stress
+changes sign, and this leads to corners developing on $\gamma$ and
+numerical instabilities.  Therefore, we modify the erosion rate, $V_\nn$
+in equation~\eqref{eqn:erosionModel}, with
+\begin{align}
+  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
+    \frac{L}{2\pi} \kappa - 1 \right),
+\end{align}
+where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average,
+$L$ is the length of $\gamma$, and $\kappa$ is the curvature of
+$\gamma$.  The new erosion model penalizes regions of high curvature,
+but does not change the total length of each body.  Moreover, to
+increase the overall stability of the method, a narrow Gaussian filter
+is applied to the erosion rate at each time step.
+
+Rather than tracking the $(x,y)$ coordinates, the {\thL} coordinates are
+tracked. In addition, tangential velocity fields are used to maintain
+an equispaced discretization. Time stepping is performed with a
+second-order Implicit-Explicit Runge-Kutta method. In particular, the
+diffusive term corresponding to the curvature penalization term is
+discretized implicitly, and all other terms, which are non-stiff, are
+treated explicitly.  By using this time stepping method in conjunction
+with the Barycentric rule, we stably evolve the eroding bodies.
+
+%-----------------------------------------------------------------------------------------------%
 \section{Measuring porous-media properties: permeability, drag, and anisotropy}
@@
 \caption{A single simulation of porous-medium erosion.
-The initial configuration consists of XX circular bodies of random size and position, as seen in Fig.~1?
+The initial configuration consists of 80 circular bodies of random size and position, as seen in Fig.~\ref{fig1}.
 a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases.
@@
 %---------------------------------------------------------%
+% Data from 80-4
 

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{abstract}
-Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow.
+Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion a porous medium comprised of up to 100 solid bodies embedded in a Stokes flow.
 The grains of the medium are resolved individually and erode under the action of surface shear stress.
 Through nonlinear feedback with the surrounding flow fields, microscopic changes in grain morphology give way to larger-scale features in the medium such as channelization.
-The Cauchy-integral formulation and associated quadrature formulas enable us to resolve configurations of tightly packed and nearly contacting bodies.
-We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by a factor up to five.
-\\
-Tie it to alternate hypothesis in groundwater.
+The Cauchy-integral formulation and associated quadrature formulas enable us to resolve dense configurations of nearly contacting bodies.
+We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by up to a factor of five.
+These results suggest that the erosion of solid material from groundwater flows may contribute to the well-known anisotropy of natural porous media.
+%Tie it to alternate hypothesis in groundwater.
 \end{abstract}

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods with stable interface evolution methods to simulate the erosion of dense suspensions of solid bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}.
+	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods with stable interface evolution methods to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications \cite{quaife2018boundary}.
 Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
 The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies \cite{chiu2020viscous}.
-Though the governing fluid-flow equations (Stokes) in this regime are linear, the feedback between complex eroding geometries and the flow leads to highly nonlinear behavior.
+Though the governing fluid-flow equations (Stokes) are linear, the nonlinear feedback between evolving microstructure and flow give rise to highly complex and anisotropic configurations.
 
-	Figure \ref{fig1} shows an example simulation of the erosion of 80 bodies, with the local speed of the intervening fluid flow shown by color.
-This simulation illustrates the {\em channelization} process, in which regions of high flow speed create higher local shear rates, thus preferentially removing solid material, and further opening the channels.
+	Figure \ref{fig1} shows an example simulation in which 80 circular bodies of randomized sizes and positions are immersed in a Stokes flow that moves from left to right.
+Color depicts the local speed of the flow intervening between bodies to give a sense of where the flow is strongest.
+Over time, individual bodies erode in response to the shear stresses induced on them.
+The heterogeneous material removal creates visible features both at the level of individual bodies and the larger-scale configuration.
+For example, horizontally-oriented channels are clearly visible in the third and fourth frames.
+
+%which regions of high flow speed create higher local shear rates, thus preferentially removing solid material, and further opening the channels.
 The positive feedback creates the channels that are clearly visible by in final two images.
 
-%\ref{fig1}
+%Maybe cite: \cite{Rycroft2016}
+% Cite paper by Ladd "Wormhole formation in dissolving fractures"
 
@@
 \includegraphics[width = 0.99 \textwidth]{./figs/Velocity-80-4.pdf}
-\caption{Numerical simulation of a dense suspension of 80 bodies eroding in a Stokes flow.
-Over time, the non-uniform erosion of material opens channels in the medium, leading to high anisotropy.}
+\caption{The erosion of a porous medium.
+In this simulation, an initial configuration of 80 circular bodies of randomized sizes and positions are embedded in a Stokes flow that moves from left to right.
+The figure shows four snapshots, evenly spaced in time, as the bodies erode in response to the local shear stresses induced by the flow.
+The local flow speed, shown by color, highlights the appearance of horizontally-aligned channels created by the shape-flow feedback.
+These channels contribute to the high anisotropy of the medium.
+}
 \end{figure*}
  %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-
-%Maybe cite: \cite{Rycroft2016}
-% Cite paper by Ladd "Wormhole formation in dissolving fractures"
+% Times are 0, 0.28, 0.57, 0.85 of final time.
+% Porosities are 0.40, 0.49, 0.64, 0.86.
 

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 These results suggest that the erosion of solid material from groundwater flows may contribute to the well-known anisotropy of natural porous media.
-%Tie it to alternate hypothesis in groundwater.
 \end{abstract}
@@
 	Figure \ref{fig1} shows an example simulation in which 80 circular bodies of randomized sizes and positions are immersed in a Stokes flow that moves from left to right.
-Color depicts the local speed of the flow intervening between bodies to give a sense of where the flow is strongest.
-Over time, individual bodies erode in response to the shear stresses induced on them.
-The heterogeneous material removal creates visible features both at the level of individual bodies and the larger-scale configuration.
-For example, horizontally-oriented channels are clearly visible in the third and fourth frames.
+Color depicts the local speed of the flow intervening between bodies.
+Over time, individual bodies erode in response to the shear stresses induced on them, and heterogeneous material removal creates visible features both at the level of individual bodies and the larger-scale configuration.
+For example, horizontally-oriented channels are clearly visible in the third and fourth frames, and these contribute to the overall anisotropy of the medium.
 
-%which regions of high flow speed create higher local shear rates, thus preferentially removing solid material, and further opening the channels.
-The positive feedback creates the channels that are clearly visible by in final two images.
+% preferentially removing solid material, and further opening the channels. The positive feedback creates the channels that are clearly visible by in final two images.
 
@@
 % Porosities are 0.40, 0.49, 0.64, 0.86.
+
+The outline of the paper is as follows.
+In Section \ref{sec:formulation} we discuss the governing equations for the fluid flow and for interface evolution.
+In Section \ref{sec:DLP} we discuss the numerical methods.
+In Section \ref{sec:medium} we measure porous-medium properties, in particular permeability.
+In Section \ref{sec:results} we provide results and we conclude in section \ref{sec:conclusion}.
 
@@
     \uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap 
-      &&\mbox{\em outer wall velocity}.
+      &&\mbox{\em prescribed outer wall velocity}.
   \end{split}
@@
 \section{Measuring porous-media properties: permeability, drag, and anisotropy}
-\label{sec:}
+\label{sec:medium}
 %-----------------------------------------------------------------------------------------------%
@@
 \section{Results}
+\label{sec:results}
 %-----------------------------------------------------------------------------------------------%
@@
 
+%-----------------------------------------------------------------------------------------------%
+\section{Conclusion}
+\label{sec:conclusion}
+%-----------------------------------------------------------------------------------------------%
+
 \bibliographystyle{plain}

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
MM

@@
 \Vn = \CE \, \abs{\tau}, 
-	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em erosion model}, \\
+	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em erosion model}, 
+\label{Vn0} \\
 \tau = -\mu \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss
 	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
-  \label{eqn:shearStress}
+\label{tau0}
 \end{align}
@@
 %computed the deformation tensor on $\gamma$, the shear stress is
-%computed using equation~\eqref{eqn:shearStress}.
+%computed using equation~\eqref{tau0}.
 
@@
 %the shear stress, the deformation tensor on $\bd\Omega$ is applied to
-%the normal and tangent vectors as in equation~\eqref{eqn:shearStress}.
+%the normal and tangent vectors as in equation~\eqref{tau0}.
 %The velocity gradient is also used to compute the vorticity in the fluid
@@
 %-----------------------------------------------------------------------------------------------%
+
+With the flow and shear stresses computed, we seek to evolve the boundaries of erodable bodies through \eqref{Vn0}.
+For numerical stability, we modify \eqref{Vn0} to include a smoothing term that depends on local curvature $\kappa$, as in previous work \citep{quaife2018boundary}
+\begin{align}
+  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
+    \frac{L}{2\pi} \kappa - 1 \right),
+\end{align}
+The last term is the smoothing with strength $\epsilon \ll 1$.
+This term is proportion to the spatial average of the shear stress, $\langle\abs{\tau}\rangle$, and the mean curvature is subtracted inside the parenthesis so that this term preserves area.
+As such, the only source of material loss is the first term, $\CE \, \abs{\tau}$.
+
+\vsp{5}
 

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \end{align}
-The last term is the smoothing with strength $\epsilon \ll 1$.
-This term is proportion to the spatial average of the shear stress, $\langle\abs{\tau}\rangle$, and the mean curvature is subtracted inside the parenthesis so that this term preserves area.
-As such, the only source of material loss is the first term, $\CE \, \abs{\tau}$.
+The last term is a smoothing term with strength $\epsilon \ll 1$ and proportional to the spatial average of the shear stress $\langle\abs{\tau}\rangle$.
+$L$ indicates the total arc length of the body, and, inside the parenthesis,  the mean curvature is subtracted so that this term preserves area.
+As such, the only source of material loss is the first term, $\CE \, \abs{\tau}$, representing the shear-dependent erosion law.
 

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-With the flow and shear stresses computed, we seek to evolve the boundaries of erodable bodies through \eqref{Vn0}.
+With the flow and shear stresses computed, we seek to evolve the boundaries of erodable bodies.
 For numerical stability, we modify \eqref{Vn0} to include a smoothing term that depends on local curvature $\kappa$, as in previous work \citep{quaife2018boundary}
@@
 $L$ indicates the total arc length of the body, and, inside the parenthesis,  the mean curvature is subtracted so that this term preserves area.
-As such, the only source of material loss is the first term, $\CE \, \abs{\tau}$, representing the shear-dependent erosion law.
+As such, the only source of material loss is the first term, $\CE \, \abs{\tau}$, which represents the shear-dependent erosion law.
+In addition, we apply a narrow Gaussian filter to the distribution $\abs{\tau}$ to further improve stability.
 
-\vsp{5}
+Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation \nick{CITE} in which we track the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.
+In this formulation, the curvature-dependent smoothing becomes a linear diffusive term, thus enabling the use of stable, implicit schemes for this stiff term.
+The remaining nonlinear terms are not stiff and can be treated by explicit time-stepping methods.
+In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second order in time.
+
+\nick{TO HERE}
 
 % COPIED STRAIGHT FROM JFM 2020
-\nick{PLAGERIZED}
-We use the time stepping method outlined in our previous
-work~\citep[see][section 3.3]{qua-moo2018} which we briefly summarize
-here.  The erosion rate loses differentiability if the shear stress
-changes sign, and this leads to corners developing on $\gamma$ and
-numerical instabilities.  Therefore, we modify the erosion rate, $V_\nn$
-in equation~\eqref{eqn:erosionModel}, with
-\begin{align}
-  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
-    \frac{L}{2\pi} \kappa - 1 \right),
-\end{align}
-where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average,
-$L$ is the length of $\gamma$, and $\kappa$ is the curvature of
-$\gamma$.  The new erosion model penalizes regions of high curvature,
-but does not change the total length of each body.  Moreover, to
-increase the overall stability of the method, a narrow Gaussian filter
-is applied to the erosion rate at each time step.
+%We use the time stepping method outlined in our previous work~\citep[see][section 3.3]{qua-moo2018} which we briefly summarize here.
+The erosion rate loses differentiability if the shear stress changes sign, and this leads to corners developing on $\gamma$ and numerical instabilities.
+Therefore, we modify the erosion rate, $V_\nn$ in equation~\eqref{eqn:erosionModel}, with
+%\begin{align}
+% \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(\frac{L}{2\pi} \kappa - 1 \right),
+%\end{align}
+%where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average, $L$ is the length of $\gamma$, and $\kappa$ is the curvature of $\gamma$.
+The new erosion model penalizes regions of high curvature, but does not change the total length of each body.
+Moreover, to increase the overall stability of the method, a narrow Gaussian filter is applied to the erosion rate at each time step.
 
-Rather than tracking the $(x,y)$ coordinates, the {\thL} coordinates are
-tracked. In addition, tangential velocity fields are used to maintain
-an equispaced discretization. Time stepping is performed with a
-second-order Implicit-Explicit Runge-Kutta method. In particular, the
-diffusive term corresponding to the curvature penalization term is
-discretized implicitly, and all other terms, which are non-stiff, are
-treated explicitly.  By using this time stepping method in conjunction
-with the Barycentric rule, we stably evolve the eroding bodies.
+%Rather than tracking the $(x,y)$ coordinates, the {\thL} coordinates are tracked.
+In addition, tangential velocity fields are used to maintain an equispaced discretization.
+Time stepping is performed with a second-order Implicit-Explicit Runge-Kutta method.
+In particular, the diffusive term corresponding to the curvature penalization term is discretized implicitly, and all other terms, which are non-stiff, are treated explicitly.
+By using this time stepping method in conjunction with the Barycentric rule, we stably evolve the eroding bodies.
 

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \end{align}
+\todo{Maybe define what $\rr$ is.}
 Note that $\bd\Omega$ includes both the eroding bodies and the outer
@@
 convert the integral to a sum of contour integrals around Jordan curves
-in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
+in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$ \todo{It looks like there is a typo with $x_x$.}
+and use
 similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret
@@
 \end{align}
-The last term is a smoothing term with strength $\epsilon \ll 1$ and proportional to the spatial average of the shear stress $\langle\abs{\tau}\rangle$.
+The last term is a smoothing term that has strength $\epsilon \ll 1$ and that scales with spatial average of the shear stress $\langle\abs{\tau}\rangle$.
 $L$ indicates the total arc length of the body, and, inside the parenthesis,  the mean curvature is subtracted so that this term preserves area.

### 2022-06-22 simulations/vplots.jl

@@ -108,7 +108,8 @@ end
 # 100-9 looks quite good showing the configuration anisotropy near the end.
 # 80-4 is also great for configurational anisotropy.
 # 60-3 is a nice visual run for showing channelization.
-vplot_single("100-9")
+# THE WINNER is 80-4 since it is good for both flow vis and plots.
+vplot_single("80-4")
 #---------------------------------------------------------------#
 
 
@@ -120,9 +121,9 @@ vplot_single("100-9")
 # Possible runs: 20:2,5,8; 40:3,7,8; 60:3,7,9; 80:4,7,9; 100:3,6
 function get_runs(nbods::Integer)
 	if nbods == 20
-		return ["20-2", "20-5", "20-8"]
+		return ["20-2", "20-5", "20-8", "20-11", "20-14", "20-16"]
 	elseif nbods == 40
-		return ["40-3", "40-7", "40-8"]
+		return ["40-3", "40-7", "40-8", "40-13"]
 	elseif nbods == 60
 		return ["60-3", "60-7", "60-9"]
 	elseif nbods == 80

### 2022-06-22 simulations/vplots.jl
NM

@@ -118,12 +118,12 @@ vplot_single("80-4")
 # STATISTICS: Make plots in Veusz for an ensemble of runs.
 
 # For a given number of bodies, return the labels for the saved runs.
-# Possible runs: 20:2,5,8; 40:3,7,8; 60:3,7,9; 80:4,7,9; 100:3,6
+# Possible runs: 20:2,5,8, 11,14,16; 40:3,7,8, 13; 60:3,7,9; 80:4,7,9; 100:3,6
 function get_runs(nbods::Integer)
 	if nbods == 20
-		return ["20-2", "20-5", "20-8", "20-11", "20-14", "20-16"]
+		return ["20-2", "20-5", "20-8"]
 	elseif nbods == 40
-		return ["40-3", "40-7", "40-8", "40-13"]
+		return ["40-3", "40-7", "40-8"]
 	elseif nbods == 60
 		return ["60-3", "60-7", "60-9"]
 	elseif nbods == 80

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-	Fortunately, it is possible to devise a test to isolate these two types of anisotropy from one another and therefore determine how much each contributes to the total anisotropy.
+	Fortunately, it is possible to devise a test to isolate these two types of anisotropy and therefore determine how much each contributes to the total anisotropy.
 In particular, for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass.
@@
 
-We now do stuff
+With the numerical methods in place, we now present results on how fluid-mechanical erosion alters porous-media properties over time.
+We will first discuss the results from a single simulation and then generalize to statistical results from ensembles of simulations.
 
-\vsp{2} \nick{To here in editing} \vsp{2}
+\subsection{Single simulation results}
+
+To begin, we discuss a single simulation of 80 bodies eroding in Stokes flow.
+For reference, the simulation discussed here is the same one shown in Fig.~\ref{fig1}.
+The initial configuration consists of 80 circular bodies having randomized sizes and positions.
+The material-removal process alters both the shape of individual bodies as well as the overall structure of the pore network transmitting the flow, as can be seen in Fig.~\ref{fig1}.
+The initial porosity is $0.4$, which corresponds to a dense packing (see Fig.~\ref{fig1} for a visual), and Fig.~\ref{fig2}(a) shows how the porosity increases over time as the bodies vanish.
+The resistance to flow decreases with this increasing porosity, as shown in Fig.~\ref{fig2}(b)
+
+%\vsp{2} \nick{To here in editing} \vsp{2}
 
@@
 
+\subsection{Statistics of ensembles of simulations}
+
 %---------------------------------------------------------%

### 2022-06-23 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation \nick{CITE} in which we track the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.
+Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation \cite{hou-low-she1994, MooreCPAM2017, mac2022morphological} by tracking the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.
 In this formulation, the curvature-dependent smoothing becomes a linear diffusive term, thus enabling the use of stable, implicit schemes for this stiff term.
 The remaining nonlinear terms are not stiff and can be treated by explicit time-stepping methods.
-In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second order in time.
-
-\nick{TO HERE}
+In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second order in time \cite{quaife2018boundary}.
 

### 2022-06-23 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-% Original ideas
-%We numerically simulate the erosion of a porous medium due to an internally flowing fluid, with solid constituents of the medium eroding under the action of surface shear stress. 
-%We numerically simulate the erosion of a porous medium due to an internally flowing fluid.
-The solid constituents of the porous medium erode under the action of surface shear stress.
-As the particles disintegrate, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.
-
+%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 % dematerialize, disintegrate
 % internal, permeating, intervening
-%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 
@@
 
-	Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents of porous media as they slowly disintegrate in groundwater flows \cite{zareei2022temporal}.
+	Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows \cite{szymczak2009wormhole, chiu2020viscous, zareei2022temporal}.
 The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting large-scale features as well as small-scale ones, such as the microstructure of porous materials.
@@
 
-	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods with stable interface evolution methods to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications \cite{quaife2018boundary}.
+	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods \cite{baker1986boundary, moore2007evaluation} with stable interface evolution methods \cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications \cite{quaife2018boundary, chiu2020viscous}.
 Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
@@
 %Maybe cite: \cite{Rycroft2016}
-% Cite paper by Ladd "Wormhole formation in dissolving fractures"
 
@@
 In this approximation, the configuration of bodies is held fixed in order to compute the {\em steady} Stokes flow determined by \eqref{eqn:StokesEq}, and then this flow field determines the stresses acting to erode each body.
-We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface (CITE previous erosion work).
+We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface \cite{Ristroph2012, Moore2013, Mitchell2016, MooreCPAM2017, HewettJFS2017, quaife2018boundary, chiu2020viscous}.
 The material loss gives rise to an inward velocity of the solid surface, $\Vn$, pointing in the direction normal to the surface.
@@
 
-Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation \cite{hou-low-she1994, MooreCPAM2017, mac2022morphological} by tracking the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.
+Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation \cite{hou-low-she1994, Moore2013, MooreCPAM2017, mac2022morphological} by tracking the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.
 In this formulation, the curvature-dependent smoothing becomes a linear diffusive term, thus enabling the use of stable, implicit schemes for this stiff term.

### 2022-06-23 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-For simplicity, we will assume $\bvec{k}  = \diag(k_{11}, k_{22})$ to be a diagonal matrix for the sake of characterizing the permeability of the porous medium.
-Because the diagonal components of $\bvec{k}$ need not be equal, the medium can have different permeabilities in the horizontal and vertical directions.
-Further, we will assume that $\bvec{k}$ to be spatially homogeneous in order to characterize the medium with a single bulk quantity at any instance in time.
-Naturally, the permeability will change over time as the bodies that comprise the medium erode.
+For simplicity, we assume $\bvec{k}$ to be a diagonal matrix, $\bvec{k}  = \diag(k_{11}, k_{22})$, for the sake of characterizing the permeability of the porous medium.
+Because the diagonal components of $\bvec{k}$ need not be equal, the medium can have different permeabilities in the longitudinal and transverse directions.
+Further, we will assume $\bvec{k}$ to be spatially homogeneous in order to characterize the medium with a single bulk quantity at any instance in time.
+Naturally, the permeability will change over time as the bodies that comprise the medium disintegrate.
 Consider first the horizontal component of \eqref{eqn:Darcy}
@@
 
-Projecting \eqref{divthm} onto $\ex$, using \eqref{eqn:drag}, and rearranging gives the exact relationship
+Projecting \eqref{divthm} onto the horizontal direction $\ex$, using \eqref{eqn:drag}, and rearranging gives the exact relationship
 \begin{equation}
@@
 We will now make some simplifying assumptions.
-First, because the imposed flow profile is uniform $\UU = (U,0)$, slip is permitted along the top and bottom boundaries $y=\pm 1$ and so the viscous stress will generally be much smaller than on the no-slip erodable boundaries.
-We will therefore drop the contribution from the second integral above.
-Second, if $x_0 > 1$ is chosen a sufficient distance from the erodable bodies, the flow profile will approximately match the uniform profile, implying that the term involving $u_x(\pm x_0, y)$ can be dropped.
-In addition, the pressure $p(\mp x_0, y)$ will approximately match the upstream and downstream values respectively.
+First, because the imposed flow profile is uniform $\UU = (U,0)$, slip is permitted along the top and bottom boundaries $y=\pm 1$.
+Therefore the viscous stress is generally much smaller along these top and bottom surfaces than on the no-slip erodable boundaries.
+We therefore drop the contribution from the second integral above.
+Second, if $x_0 > 1$ is chosen a sufficient distance from the erodable bodies, the flow profile approximately matches the uniform profile, implying that the term involving $u_x(\pm x_0, y)$ can be dropped.
+In addition, the pressure $p(\pm x_0, y)$ approximately matches the downstream and upstream values respectively.
 With these assumptions, \eqref{drag_press} simplifies to the approximate form
@@
 \end{equation}
-Combining with \eqref{eqn:k11} yields a formula relating the drag and permeability in the longitudinal direction
+Combining with \eqref{eqn:k11} yields a formula relating the longitudinal drag and permeability
 \begin{equation}
@@
 \end{equation}
-This formula serves as a valuable benchmark linking the microscopic (Stokes) and macroscopic (Darcy) perspectives.
-Since the drag is a quantity that can be computed with high accuracy with our Stokes solvers, verifying the relationship \eqref{perm_drag}, as will be done in Fig.~\ref{fig2}, validates a number of approximations made in the coarse-grained approach, such as (1) the homogenization of the flow field implicit in Darcy's law \eqref{eqn:Darcy}; (2) the calculation of the permeability from measurements of the flow rate and upstream/downstream pressures through \eqref{eqn:k11}.
+This formula establishes an important link between the microscopic (Stokes) perspective and the macroscopic (Darcy) perspective, and it gives us a way to test the assumptions involved in coarse-graining the system to extract porous-medium properties.
+That is, the total drag is an unambiguous quantity that can be computed with high accuracy in our Stokes-based simulations.
+The extraction of permeability, on the other hand, requires a few key approximations and assumptions, for example that the length-scale of grains is sufficiently small compared to the domain scale so that the flow field can be homogenized.
+Verifying relationship \eqref{perm_drag}, as will be done in Section \ref{sec:results}, will therefore support the idea that the collection of bodies can be treated as a porous medium and meaningful bulk quantities can be extracted.
+
+%verifying the relationship \eqref{perm_drag}, as will be done in Fig.~\ref{fig2}, validates a number of approximations made in the coarse-grained approach, such as (1) the homogenization of the flow field implicit in Darcy's law \eqref{eqn:Darcy}; (2) the calculation of the permeability from measurements of the flow rate and upstream/downstream pressures through \eqref{eqn:k11}.
 
@@
 The material-removal process alters both the shape of individual bodies as well as the overall structure of the pore network transmitting the flow, as can be seen in Fig.~\ref{fig1}.
-The initial porosity is $0.4$, which corresponds to a dense packing (see Fig.~\ref{fig1} for a visual), and Fig.~\ref{fig2}(a) shows how the porosity increases over time as the bodies vanish.
-The resistance to flow decreases with this increasing porosity, as shown in Fig.~\ref{fig2}(b)
+Initially, the solid bodies occupy $60\%$ of the area, or the porosity is $\varphi = 0.4$, which corresponds to a dense packing; see Fig.~\ref{fig1} for a visual.
+Figure~\ref{fig2}(a) shows how the solid-body area decreases, or equivalently the porosity increases, over time as the bodies erode.
+The increasing porosity serves as a convenient proxy for dimensionless time that is insensitive to the end conditions that set the strength of the flow (i.e.~whether we specify the pressure drop or the end velocity to be constant in time).
+We will henceforth use porosity, $\varphi$, on the horizontal axis of many plots to represent increasing time.
+
+As the bodies disintegrate and give way to wider pores, the resistance to flow decreases as seen in Fig.~\ref{fig2}(b).
+The resistance to flow can be quantified in the two independent ways discussed in Section \ref{sec:medium}, namely: (1) We can measure the pressure drop, $\pup - \pdn$, across the cell and the total flux, $q_1$, to infer the {\em resistivity} or inverse permeability $1/k_{11}$; or (2) We can measure the combined drag on the collection of bodies.
+Figure \ref{fig2}(b) shows that these two approaches yield consistent results...
 
@@
 
-Text for Fig 3: 
-The anisotropy of permeability grows large, up to a value of 4 during the middle portion of the simulation. The figure also shows the anisotropy of the circular grid.
+%Text for Fig 3: 
+%The anisotropy of permeability grows large, up to a value of 4 during the middle portion of the simulation. The figure also shows the anisotropy of the circular grid.
 

### 2022-06-23 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 Figure~\ref{fig2}(a) shows how the solid-body area decreases, or equivalently the porosity increases, over time as the bodies erode.
-The increasing porosity serves as a convenient proxy for dimensionless time that is insensitive to the end conditions that set the strength of the flow (i.e.~whether we specify the pressure drop or the end velocity to be constant in time).
+The increasing porosity serves as a convenient proxy for dimensionless time that is insensitive to the end conditions setting the strength of the flow (i.e.~whether we specify the pressure drop or the end velocity to be constant in time).
 We will henceforth use porosity, $\varphi$, on the horizontal axis of many plots to represent increasing time.
-
-As the bodies disintegrate and give way to wider pores, the resistance to flow decreases as seen in Fig.~\ref{fig2}(b).
-The resistance to flow can be quantified in the two independent ways discussed in Section \ref{sec:medium}, namely: (1) We can measure the pressure drop, $\pup - \pdn$, across the cell and the total flux, $q_1$, to infer the {\em resistivity} or inverse permeability $1/k_{11}$; or (2) We can measure the combined drag on the collection of bodies.
-Figure \ref{fig2}(b) shows that these two approaches yield consistent results...
-
-%\vsp{2} \nick{To here in editing} \vsp{2}
 
@@
 a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases.
-b) Resistance to flow can be characterized by either the inverse permeability, $1/k$, or the cumulative drag, the two of which are related through \eqref{ResistDrag}.
-Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
-c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium.
-Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
+b) Resistance to flow can be characterized by either the inverse permeability (solid) or the cumulative drag (dots), the two of which are related through \eqref{perm_drag}.
+Both are seen to decrease as the medium erodes, and relationship \eqref{perm_drag} is confirmed by the simulation data.
+The figure also shows the inverse permeability in transverse direction (dashed).
 }
@@
 % Data from 80-4
+
+As the bodies disintegrate and give way to wider pores, the resistance to flow decreases as seen in Fig.~\ref{fig2}(b).
+The resistance to flow can be quantified in two separate ways, as outlined in Section \ref{sec:medium}, namely by computing the total drag or by extracting the permeability.
+As a reminder, the drag is a microscopic quantity that can be computed with high accuracy and without ambiguity in our Stokes-based simulations.
+The permeability, on the other hand, requires a few key assumptions and approximations to be made, but the extraction of such bulk quantities will be more valuable in characterizing the evolving configuration of bodies as a single porous medium.
+As such, it is particularly valuable to compare these two perspectives so that the assumptions underlying the coarse-grained process can be assessed.
+In particular, we aim to test the approximate formula \eqref{perm_drag}, relating the longitudinal drag $F_1$ to the inverse permeability $1/k_{11}$, sometimes called resistivity.
+Figure \ref{fig2}(b) indeed shows close agreement between these two quantities over the entire duration of the simulation, thus confirming the ability to extract medium properties during the erosion process.
+
+In Fig.~\ref{fig2}(b) we also show the transverse resistivity, $1/k_{22}$, as it decreases over the course of the simulation.
+Notice that this transverse resistivity exceeds the longitudinal resistivity by a significant margin, indicating that the configuration provides greater resistance to flow in the vertical direction.
 
@@
 % Data from 80-4
+
+%c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium.
+Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
+
+Next
 

### 2022-06-23 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{figure*}%[htbp]
-\centering \label{fig1}
+\centering
 \includegraphics[width = 0.99 \textwidth]{./figs/Velocity-80-4.pdf}
@@
 These channels contribute to the high anisotropy of the medium.
+\label{fig1}
 }
@@
 \subsection{Single simulation results}
+\label{sec:single_sim}
 
@@
 \begin{figure*}%[htbp]
-\centering \label{fig2}
+\centering
 \includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
@@
 The figure also shows the inverse permeability in transverse direction (dashed).
+ \label{fig2}
 }
@@
 The resistance to flow can be quantified in two separate ways, as outlined in Section \ref{sec:medium}, namely by computing the total drag or by extracting the permeability.
-As a reminder, the drag is a microscopic quantity that can be computed with high accuracy and without ambiguity in our Stokes-based simulations.
-The permeability, on the other hand, requires a few key assumptions and approximations to be made, but the extraction of such bulk quantities will be more valuable in characterizing the evolving configuration of bodies as a single porous medium.
-As such, it is particularly valuable to compare these two perspectives so that the assumptions underlying the coarse-grained process can be assessed.
-In particular, we aim to test the approximate formula \eqref{perm_drag}, relating the longitudinal drag $F_1$ to the inverse permeability $1/k_{11}$, sometimes called resistivity.
+As discussed in Section \ref{sec:medium}, the drag is a microscopic quantity that can be computed with high accuracy and without ambiguity in our Stokes-based simulations.
+The permeability, on the other hand, relies on a few approximations, but the extraction of such bulk quantities will be more valuable in characterizing the evolving porous medium.
+As such, it is particularly useful to compare these two perspectives so that the assumptions underlying the coarse-graining process can be assessed.
+In particular, we aim to test the approximate formula \eqref{perm_drag}, relating the longitudinal drag $F_1$ to the inverse permeability $1/k_{11}$, also known as the {\em resistivity}.
 Figure \ref{fig2}(b) indeed shows close agreement between these two quantities over the entire duration of the simulation, thus confirming the ability to extract medium properties during the erosion process.
@@
 Notice that this transverse resistivity exceeds the longitudinal resistivity by a significant margin, indicating that the configuration provides greater resistance to flow in the vertical direction.
+This trend fits the intuition that horizontally-aligned channels transmit flow more easily in the longitudinal direction.
 
@@
 \begin{figure*}%[htbp]
-\centering \label{fig3}
+\centering
 \includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
@@
 Permeability
+\label{fig3}
 }
@@
 % Data from 80-4
-
 %c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium.
@@
 
-Next
+Figure \ref{fig3}(a) shows more directly how permeability in the longitudinal, $k_{11}$ and transverse, $k_{22}$ directions increase over time as the medium erodes.
+Once again, the relationship $k_{11} > k_{22}$ indicates a higher propensity for flow in the longitudinal direction.
+Notice that the permeability increases by nearly 5 orders of magnitude over the course of the simulation, indicating that erosion substantially alters medium properties.
 
@@
 \begin{figure*}%[htbp]
-\centering \label{fig4}
+\centering
 \includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
@@
 Tortuosity
+\label{fig4}
 }
@@
 \begin{figure*}%[htbp]
-\centering \label{fig5}
+\centering
 \includegraphics[width = 0.99 \textwidth]{./figs/fig5.pdf}
@@
 a) Statistics from an ensemble of runs.
+\label{fig5}
 }
@@
 \begin{figure*}%[htbp]
-\centering \label{fig6}
+\centering
 \includegraphics[width = 0.99 \textwidth]{./figs/fig6.pdf}
@@
 a) Statistics from an ensemble of runs.
+\label{fig6}
 }

### 2022-06-24 docs/PhysicsPaper/StokesErosion.tex
NM
small changes to introduction

@@
 
-	Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows \cite{szymczak2009wormhole, chiu2020viscous, zareei2022temporal}.
+	Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water~\cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows \cite{szymczak2009wormhole, chiu2020viscous, zareei2022temporal}.
 The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting large-scale features as well as small-scale ones, such as the microstructure of porous materials.
 Porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
-Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}.
-Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plan of deposition \cite{bear1988dynamics}.
+Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely by a factor of 5--20~\cite{bear1988dynamics, anderson2015applied}.
+Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plan of deposition~\cite{bear1988dynamics}.
 Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work.
@@
 
-	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods \cite{baker1986boundary, moore2007evaluation} with stable interface evolution methods \cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications \cite{quaife2018boundary, chiu2020viscous}.
-Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
-The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies \cite{chiu2020viscous}.
+	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications~\cite{quaife2018boundary, chiu2020viscous}.
+Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $\mathcal{O}(100)$ solid bodies.
+The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}.
 Though the governing fluid-flow equations (Stokes) are linear, the nonlinear feedback between evolving microstructure and flow give rise to highly complex and anisotropic configurations.
 
-	Figure \ref{fig1} shows an example simulation in which 80 circular bodies of randomized sizes and positions are immersed in a Stokes flow that moves from left to right.
-Color depicts the local speed of the flow intervening between bodies.
+	Figure~\ref{fig1} shows an example simulation with 80 circular bodies of randomized sizes and positions immersed in a Stokes flow that moves from left to right.
+A plug flow is imposed on artificial walls to the left and right of each frame, and a no-slip boundary condition is imposed along the top and bottom of each frame.
+The color depicts the local speed of the flow intervening between bodies.
 Over time, individual bodies erode in response to the shear stresses induced on them, and heterogeneous material removal creates visible features both at the level of individual bodies and the larger-scale configuration.
@@
 \caption{The erosion of a porous medium.
-In this simulation, an initial configuration of 80 circular bodies of randomized sizes and positions are embedded in a Stokes flow that moves from left to right.
+In this simulation, an initial configuration of 80 circular bodies with random sizes and positions are embedded in a Stokes flow that moves from left to right.
 The figure shows four snapshots, evenly spaced in time, as the bodies erode in response to the local shear stresses induced by the flow.
@@
 The outline of the paper is as follows.
-In Section \ref{sec:formulation} we discuss the governing equations for the fluid flow and for interface evolution.
-In Section \ref{sec:DLP} we discuss the numerical methods.
-In Section \ref{sec:medium} we measure porous-medium properties, in particular permeability.
-In Section \ref{sec:results} we provide results and we conclude in section \ref{sec:conclusion}.
+In Section~\ref{sec:formulation} we discuss the governing equations for the fluid flow and for interface evolution.
+In Section~\ref{sec:DLP} we discuss the numerical methods.
+In Section~\ref{sec:medium} we measure porous-medium properties, in particular permeability.
+In Section~\ref{sec:results} we provide results and we conclude in section~\ref{sec:conclusion}.
 
@@
 %-----------------------------------------------------------------------------------------------%
-\section{Measuring porous-media properties: permeability, drag, and anisotropy}
+\section{Extracting porous-media properties: permeability, drag, anisotropy, tortuosity}
 \label{sec:medium}
@@
 
+\subsection{Tortuosity}
+
+We need to write this section.
+Could reference Souzy et al. JFM article on velocity distributions in porous media \cite{souzy2020velocity}
+
 %-----------------------------------------------------------------------------------------------%

### 2022-06-24 docs/PhysicsPaper/StokesErosion.tex
reading through manuscript

@@
 We take the outer boundary $\Gamma$ to be a slightly smoothed version of the boundary of $[-3,3] \times [-1,1]$.
-The fluid flow is primarily from left to right, so that the inlet and outlet are located at approximately $x=-3$ and $+3$ respectively (the actual locations are slightly curved versions of these vertical lines due to domain smoothing).
+The fluid flow is primarily from left to right, so that the inlet and outlet are located at approximately $x=\pm 3$ (the actual locations are slightly curved versions of these vertical lines due to domain smoothing).
 The erodable bodies, with boundaries $\gamma_\ell$, $\ell = 1,\ldots,M$, all sit inside of the central region $[-1,1] \times [-1,1]$.
@@
 Above, $\UU$ represents the fluid velocity imposed along the outer boundary $\Gamma$, in particular at the inlet and outlet, as well as along the top and bottom walls.
-In this work, we impose a {\em uniform} flow profile along $\Gamma$, i.e.~$\UU = (U,0)$, although other choices are possible, for example a Poiseuille profile as employed in previous work \cite{quaife2018boundary, chiu2020viscous}.
+In this work, we impose a {\em uniform} flow profile along $\Gamma$, i.e.~$\UU = (U,0)$, although other choices are possible, for example a Poiseuille profile as employed in previous work~\cite{chiu2020viscous, quaife2018boundary}.
 The advantages of the uniform profile are: (1) it will simplify the calculation of porous-medium properties, such as permeability and anisotropy, that will be described later; and (2), it may more realistically model the flow impinging upon a porous medium.
@@
 The embedded bodies may erode in response to the shear stresses induced by the intervening fluid flow.
-Erosion typically occurs over much longer timescales than does the fluid flow, permitting a {\em quasi-steady} approximation.
-In this approximation, the configuration of bodies is held fixed in order to compute the {\em steady} Stokes flow determined by \eqref{eqn:StokesEq}, and then this flow field determines the stresses acting to erode each body.
-We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface \cite{Ristroph2012, Moore2013, Mitchell2016, MooreCPAM2017, HewettJFS2017, quaife2018boundary, chiu2020viscous}.
+Erosion typically occurs over much longer timescales than the fluid flow, permitting a {\em quasi-steady} approximation.
+In this approximation, the configuration of bodies is held fixed in order to compute the {\em steady} Stokes flow determined by~\eqref{eqn:StokesEq}, and then this flow field determines the stresses acting to erode each body.
+We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface~\cite{Ristroph2012, Moore2013, Mitchell2016, MooreCPAM2017, HewettJFS2017, quaife2018boundary, chiu2020viscous}.
 The material loss gives rise to an inward velocity of the solid surface, $\Vn$, pointing in the direction normal to the surface.
@@
 \label{Vn0} \\
-\tau = -\mu \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss
+\tau = -\mu \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss,
 	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
@@
 \end{align}
-where $\nn$ is a unit normal vector pointing into each body, $\ss$ is
-a unit tangent vector pointing in the counterclockwise direction, and $\CE$ is a material-dependent erosion constant.
+where $\nn$ is the unit normal vector pointing into each body, $\ss$ is the unit tangent vector pointing in the counterclockwise direction, and $\CE$ is a material-dependent erosion constant.
 
@@
 %-----------------------------------------------------------------------------------------------%
-To accurately and efficiently solve the Stokes
-  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
-  boundary integral equation (BIE). A BIE formulation has the advantage
-  that all the unknowns are on the one-dimensional boundary of the
-  domain. Therefore, only the boundary of the complex geometry must be
-  discretized which we do with a spectrally accurate Fourier basis.
-  Applying the same approach as our previous
-  works~\citep{quaife2018boundary, chiu2020viscous}, we represent the
-  velocity as the sum of a double-layer potential and a combination of
-  Stokeslets and rotlets~\cite{pow-mir1987}
+To accurately and efficiently solve the Stokes equations~\eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE).
+A BIE formulation has the advantage that all the unknowns are on the one-dimensional boundaries of the domain.
+That is, only the boundary of the complex geometry must be discretized which we do with a spectrally accurate Fourier basis.
+Applying the same approach as our previous works~\cite{chiu2020viscous, quaife2018boundary}, we represent the velocity as the sum of a double-layer potential and a combination of Stokeslets and rotlets~\cite{pow-mir1987}
 \begin{align}
@@
   \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
-  \eeta(\yy) \, ds_\yy.
+  \eeta(\yy) \, ds_\yy,
   \label{eqn:velocityDLP}
 \end{align}
-\todo{Maybe define what $\rr$ is.}
-Note that $\bd\Omega$ includes both the eroding bodies and the outer
-boundary. The Stokeslet and the rotlets are
+where $\rr = \xx - \yy$ and $\rho = \|\rr\|$. Note that $\bd\Omega$ includes both the eroding bodies and the outer boundary. The Stokeslet and the rotlets are
 \begin{align}
@@
 \end{align}
-respectively, where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell =
-\|\rr_\ell\|$, and $\cc_\ell$ is a point inside body $\ell$. If the
-density function, Stokeslets, and rotlets satisfy the second-kind
-boundary integral equation
+respectively, where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and $\cc_\ell$ is a point inside body $\ell$.
+If the density function, Stokeslets, and rotlets satisfy the second-kind boundary integral equation
 \begin{subequations}
@@
 \end{subequations}
-then the representation~\eqref{eqn:velocity} satisfies the Stokes
-equations with the required boundary conditions~\eqref{eqn:StokesEq}. We
-solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at
-equispaced collocation points, and then replacing the integrals with
-quadrature rules. This results in a linear system with a
-mesh-independent condition number, and it is solved iteratively with
-GMRES.
+then the representation~\eqref{eqn:velocity} satisfies the Stokes equations with the required boundary conditions~\eqref{eqn:StokesEq}.
+We solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at equispaced collocation points, and then replacing the integrals with quadrature rules.
+This results in a linear system with a mesh-independent condition number, and it is solved iteratively with GMRES.
 
-Instead of evaluating the Stokes double-layer
-potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we
-convert the integral to a sum of contour integrals around Jordan curves
-in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$ \todo{It looks like there is a typo with $x_x$.}
-and use
-similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret
-$\gamma$, the boundary of the $i^{th}$ grain or the bounding box
-$\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
+\todo[inline]{Bryan left off here}
+
+Instead of evaluating the Stokes double-layer potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we convert the integral to a sum of contour integrals around Jordan curves in $\CC$.
+We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_2$ and use similar notation for $\yy$, $\nn$, and $\eeta$.
+We also interpret $\gamma$, the boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan curve in $\CC$.
+We introduce the functions
 \begin{align}
@@
 With the flow and shear stresses computed, we seek to evolve the boundaries of erodable bodies.
-For numerical stability, we modify \eqref{Vn0} to include a smoothing term that depends on local curvature $\kappa$, as in previous work \citep{quaife2018boundary}
+For numerical stability, we modify \eqref{Vn0} to include a smoothing term that depends on local curvature $\kappa$, as in previous work~\cite{quaife2018boundary}
 \begin{align}

### 2022-06-25 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{equation}
+\label{eq:anis}
 \anis = k_{11} / k_{22}
@@
 The material-removal process alters both the shape of individual bodies as well as the overall structure of the pore network transmitting the flow, as can be seen in Fig.~\ref{fig1}.
-Initially, the solid bodies occupy $60\%$ of the area, or the porosity is $\varphi = 0.4$, which corresponds to a dense packing; see Fig.~\ref{fig1} for a visual.
+Initially, the solid bodies occupy $60\%$ of the area, or the porosity is $\varphi = 0.4$, corresponding to a relatively dense packing; see Fig.~\ref{fig1} for a visual.
 Figure~\ref{fig2}(a) shows how the solid-body area decreases, or equivalently the porosity increases, over time as the bodies erode.
@@
 
+As given in \eqref{eq:anis}, the ratio of longitudinal to transverse permeability defines the anisotropy of the medium, $\anis = k_{11} / k_{22}$.
+
 %Text for Fig 3: 

### 2022-06-26 docs/PhysicsPaper/StokesErosion.tex
reading through paper and making small changes

@@
 
-\todo[inline]{Bryan left off here}
-
 Instead of evaluating the Stokes double-layer potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we convert the integral to a sum of contour integrals around Jordan curves in $\CC$.
@@
   \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
-  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
+  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)),
 \end{align}
-We then define the five Cauchy integrals
+and then define the five Cauchy integrals
 \begin{align}
-  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
+  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\Re(\eta(y))}{x-y} \,dy, 
   \quad
-  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
+  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\Im(\eta(y))}{x-y} \, dy, 
   \quad
-  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
+  v_3(x) = \frac{1}{2\pi i} \int_{\gamma}
+  \frac{\Re(\overline{y}\eta(y))}{x-y} \, dy, \\
   v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
@@
 
-To approximate the Cauchy integrals and its
-derivatives~\eqref{eqn:cauchy}, the trapezoid rule achieves spectral
-accuracy. For example, the Cauchy integral~\eqref{eqn:cauchyv} can be
-approximated as
+The trapezoid rule can be used to approximate this Cauchy integral and
+its derivatives. For example, the Cauchy integral~\eqref{eqn:cauchyv}
+can be approximated as
 \begin{align}
@@
 $\gamma$. This error is problematic for many of our simulations since we
-allow for eroding bodies to be arbitrarily close to one another, and we
+allow eroding bodies to be arbitrarily close to one another, and we
 often compute the velocity and vorticity at points in the fluid domain
@@
 The derivatives of the Cauchy integral in~\eqref{eqn:cauchy} can be
-approximated with similar quadrature rules. For $x \in \Omega$, 
+approximated with a uniformly spectral error using similar quadrature
+rules. For $x \in \Omega$, 
 \begin{align}
@@
     \Bigg/
-    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
+    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right).
   \label{eqn:D2vBary}
 \end{align}
-where the quadrature rule is spectrally accurate and the error is
-independent of $x$. We note that
-equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
+We note that equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
 and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
@@
 %This has the advantage that only the one-dimensional boundary of the domain must be discretized, and, with appropriate quadrature formulas and fast summation methods, the result is a high-fidelity numerical simulation with near-optimal computational complexity.
-
-%-----------------------------------------------------------------------------------------------%
-%\subsection{Boundary Integral Representation in $\RR^2$}
-%-----------------------------------------------------------------------------------------------%
-
-%
-%Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
-%corresponding deformation tensor, pressure, and vorticity at $\xx \in
-%\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
-%To compute the deformation tensor for $\xx \in \gamma$, we include the
-%jump term
-%\begin{align}
-%  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
-%    \begin{array}{cc}
-%      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
-%    \end{array}
-%  \right].
-%  \label{eqn:deformationJump}
-%\end{align}
-%Finally, the deformation tensor, pressure, and vorticity due to the
-%Stokeslets and rotlets are readily available~\citep{poz1992}. Having
-%computed the deformation tensor on $\gamma$, the shear stress is
-%computed using equation~\eqref{tau0}.
-
-%%-----------------------------------------------------------------------------------------------%
-%\subsection{Cauchy Integral Formulation}
-%\label{sec:DLPcomplex}
-%%-----------------------------------------------------------------------------------------------%
-%The velocity double-layer potential~\eqref{eqn:velocityDLP}, and its
-%corresponding deformation tensor, pressure, and vorticity are all
-%written as layer potentials in $\RR^2$. However, the quadrature method
-%we introduce in section~\ref{sec:method} requires complex-valued
-%representations. The first step to form a complex representation is to
-%write the Laplace double-layer potential as the complex integral
-%\begin{align}
-%  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
-%    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)),
-%\end{align}
-%where
-%\begin{align}
-%  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
-%    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega.
-%  \label{eqn:laplaceComplex}
-%\end{align}
-%Here $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
-%counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
-%\eta_1 + i \eta_2$ is the complex counterpart of $\eeta =
-%(\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
-%potential, $\Omega$ is interpreted as a subset of $\RR^2$ or $\CC$.
-%Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
-%first finding the boundary data of $v$. If $\Omega$ is a
-%simply-connected interior domain, then the boundary data of $v$
-%satisfies the Sokhotski-Plemelj jump relation
-%\begin{align}
-%  \label{eqn:SPrelation}
-%  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
-%    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
-%\end{align}
-%For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
-%for multiply-connected domains, such as a porous media, $\bd\Omega$ is
-%decomposed into its different connected components and the appropriate
-%jump relation is applied.  Having computed the boundary data of the
-%holomorphic function $v$, by the Cauchy integral theorem we have
-%\begin{subequations}
-%  \label{eqn:cauchy}
-%  \begin{alignat}{3}
-%  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
-%    \frac{v(y)}{y-x} \,dy, \\
-%  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
-%    \frac{v(y)}{(y-x)^2} \, dy, \\
-%  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
-%    \frac{v(y)}{(y-x)^3} \, dy,
-%  \end{alignat}
-%\end{subequations}
-%for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
-%function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
-%function defined in equation~\eqref{eqn:laplaceComplex}, and its first
-%two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  
-%  
-%Finally, the Stokes double-layer potential~\eqref{eqn:velocityDLP} can
-%be written using a Laplace double-layer
-%potential~\eqref{eqn:laplaceComplex} and its gradients 
-%\begin{equation}
-%  \label{eqn:Stokes2Laplace}
-%  \begin{aligned}
-%    \DDD[\eeta](\xx) &= 
-%      \frac{1}{2\pi} \int_{\bd\Omega} 
-%        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
-%      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
-%        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
-%      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
-%        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
-%      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
-%        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
-%  \end{aligned}
-%\end{equation}
-%Therefore, the Stokes double-layer potential can be written as a sum of
-%Cauchy integrals and its first derivative~\citep{bar-wu-vee2015}
-%\begin{equation}
-%  \begin{aligned}
-%    u_1(x) &= \Real (v[\psi_1](x)) + \Real (v'[y\cdot\eta](x)) 
-%             -x_1\Real (v'[\eta_1](x)) - x_2\Real (v'[\eta_2](x)), \\
-%    u_2(x) &= \Real (v[\psi_2](x)) - \Imag (v'[y\cdot\eta](x)) 
-%         +x_1\Imag (v'[\eta_1](x)) + x_2\Imag (v'[\eta_2](x)),
-%  \end{aligned}
-%  \label{eqn:cauchyVelocity}
-%\end{equation}
-%where $y \cdot \eta = y_1 \eta_1 + y_2 \eta_2$, 
-%\begin{align} 
-%  \psi_1=(\eta_1+i\eta_2)\frac{\Real(n)}{n}, \quad
-%  \psi_2=(\eta_1+i\eta_2)\frac{\Imag(n)}{n},
-%\end{align}
-%and $n \in \CC$ is the complex counterpart of the outward unit normal
-%$\nn \in \RR^2$.
-%
-%%-----------------------------------------------------------------------------------------------%
-%\subsection{Cauchy Integral Representation for the Gradient of the
-%Double-Layer Potential}
-%\label{sec:gradDLPcomplex}
-%%-----------------------------------------------------------------------------------------------%
-%Computing the shear stress and vorticity requires a complex-valued layer
-%potential representation of the velocity gradient.  The deformation
-%tensor at $x \in \Omega$ is found by computing the derivatives of the
-%expressions for $u_1$ and $u_2$ in equation~\eqref{eqn:cauchyVelocity}  
-%\begin{equation}
-%\label{eqn:cauchyGradient}
-%  \begin{aligned}
-%    \pderiv{u_1}{x_1} &= +\Real (v'[\psi_1](x)) + 
-%    \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) \\
-%    &- x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
-%    \pderiv{u_1}{x_2} &= - \Imag (v'[\psi_1](x)) - 
-%    \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) \\
-%    &- \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
-%    \pderiv{u_2}{x_1} &= +\Real (v'[\psi_2](x)) - 
-%    \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x))  \\
-%    &+ x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
-%    \pderiv{u_2}{x_2} &= -\Imag (v'[\psi_2](x)) - 
-%    \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) \\
-%    &+ \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
-%  \end{aligned}
-%\end{equation}
-%The same expressions are used to compute the deformation tensor for $x
-%\in \bd\Omega$, except that the jump
-%condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
-%the shear stress, the deformation tensor on $\bd\Omega$ is applied to
-%the normal and tangent vectors as in equation~\eqref{tau0}.
-%The velocity gradient is also used to compute the vorticity in the fluid
-%bulk.  For $x \in \Omega$, the Cauchy integral representation of the
-%vorticity at $x \in \Omega$ is
-%\begin{align}
-%  \omega(x) = 
-%    \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))+ 
-%    \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
-%\end{align}
 

### 2022-06-26 docs/PhysicsPaper/StokesErosion.tex
noted where I left off
NM

@@
 
+\todo[inline]{Bryan left off here}
+
 %-----------------------------------------------------------------------------------------------%
@@
 \subsection{Transverse permeability and anisotropy}
+\label{subsec:anis}
 
@@
 
-As given in \eqref{eq:anis}, the ratio of longitudinal to transverse permeability defines the anisotropy of the medium, $\anis = k_{11} / k_{22}$.
+As given in \eqref{eq:anis}, the ratio of longitudinal to transverse permeability defines the anisotropy of the medium, $\anis = k_{11} / k_{22}$, which is plotted in Fig.~\ref{fig3}(b) over the course fo the simulation (solid curve).
+Early in the simulation the anisotropy is nearly one, as the initial configuration of randomly placed circles has no preferred flow direction.
+The anisotropy then increases as heterogeneous rates of erosion promote longitudinal flow over transverse flow.
+The anisotropy peaks at a value of $\anis \approx 4$ later in the simulation.
+At very late times, the anisotropy approaches unity again as the bodies completely vanish and return the system to a state of no preferred flow direction.
+
+As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large-scale level.
+As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted by replacing any
 

### 2022-06-26 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large-scale level.
-As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted by replacing any
+As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted by replacing any collection of partially-eroded bodies with circles having the same areas and centers of mass and measuring the anisotropy of the resulting configuration.
+We perform this process at every time step in the simulation, and show in Fig.~\ref{fig3}(a) both permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations.
+As seen in the figure, the permeabilities of the circle configurations always lie in between the true values $k_{11}$ and $k_{22}$ of the eroded geometries.
 

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
working on edits

@@
 
-\todo[inline]{Bryan left off here}
-
 %-----------------------------------------------------------------------------------------------%
@@
 With the flow and shear stresses computed, we seek to evolve the boundaries of erodable bodies.
-For numerical stability, we modify \eqref{Vn0} to include a smoothing term that depends on local curvature $\kappa$, as in previous work~\cite{quaife2018boundary}
+For numerical stability, we modify~\eqref{Vn0} to include a smoothing term that depends on local curvature $\kappa$, as in previous work~\cite{quaife2018boundary}
 \begin{align}
   \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
-    \frac{L}{2\pi} \kappa - 1 \right),
+    \frac{L}{2\pi} \kappa - 1 \right).
 \end{align}
-The last term is a smoothing term that has strength $\epsilon \ll 1$ and that scales with spatial average of the shear stress $\langle\abs{\tau}\rangle$.
+The last term is a smoothing term that has strength $\epsilon \ll 1$ and scales with spatial average of the shear stress $\langle\abs{\tau}\rangle$.
 $L$ indicates the total arc length of the body, and, inside the parenthesis, the mean curvature is subtracted so that this term preserves area.
@@
 
-Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation \cite{hou-low-she1994, Moore2013, MooreCPAM2017, mac2022morphological} by tracking the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.
+Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation~\cite{hou-low-she1994, Moore2013, MooreCPAM2017, mac2022morphological} by tracking the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.
 In this formulation, the curvature-dependent smoothing becomes a linear diffusive term, thus enabling the use of stable, implicit schemes for this stiff term.
 The remaining nonlinear terms are not stiff and can be treated by explicit time-stepping methods.
-In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second order in time \cite{quaife2018boundary}.
+In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second-order in time~\cite{quaife2018boundary}.
 
@@
 
-While the Stokes equations \eqref{eqn:StokesEq} provides a microscopic description of the detailed flow field $\uu$ penetrating the complex configuration of erodable bodies, a coarse-grained description can be obtained by treating the collection of bodies as a single porous-medium and homogenizing the flow-field through Darcy's law,
+While the Stokes equations~\eqref{eqn:StokesEq} provides a microscopic description of the detailed flow field $\uu$ penetrating the complex configuration of erodable bodies, a coarse-grained description can be obtained by treating the collection of bodies as a single porous-medium and homogenizing the flow-field through Darcy's law,
 \begin{equation}
   \label{eqn:Darcy}
-\bq = - \frac{1}{\mu} \bvec{k} \grad p
+  \bq = - \frac{1}{\mu} \bvec{k} \grad p.
 \end{equation}
 Here, $p$ and $\mu$ represent the pressure field and fluid viscosity as before, with $\mu = 1$ by the non-dimensionalization.
-Meanwhile, $\bq = (q_1, q_2)$ represents the {\em specific discharge}, which is the volume of water that flowing through a unit cross sectional area of porous media per unit time; $\bq$ relates to the (interstitial) velocity $\uu$, by integrating $\uu$ over a sufficiently small control region and dividing by the total volume (including both fluid and solid) of the region.
+Meanwhile, $\bq = (q_1, q_2)$ represents the {\em specific discharge}, which is the volume of water flowing through a unit cross sectional area of porous media per unit time; $\bq$ relates to the (interstitial) velocity $\uu$, by integrating $\uu$ over a sufficiently small control region and dividing by the total volume (including both fluid and solid) of the region.
 The parameter $\bvec{k}$ represents the {\em permeability} of the porous medium, which generally takes the form of a rank-2 tensor to permit different propensities to flow in different directions, i.e.~medium anisotropy.
-
 %The permeability may vary in space and will certainly vary in time as the bodies erode.
@@
 
-For simplicity, we assume $\bvec{k}$ to be a diagonal matrix, $\bvec{k}  = \diag(k_{11}, k_{22})$, for the sake of characterizing the permeability of the porous medium.
-Because the diagonal components of $\bvec{k}$ need not be equal, the medium can have different permeabilities in the longitudinal and transverse directions.
-Further, we will assume $\bvec{k}$ to be spatially homogeneous in order to characterize the medium with a single bulk quantity at any instance in time.
-Naturally, the permeability will change over time as the bodies that comprise the medium disintegrate.
-Consider first the horizontal component of \eqref{eqn:Darcy}
+For simplicity, we assume $\bvec{k}$ to be a diagonal matrix, $\bvec{k}
+= \diag(k_{11}, k_{22})$, for the sake of characterizing the
+permeability of the porous medium. Because the diagonal components of
+$\bvec{k}$ need not be equal, the medium can have different
+permeabilities in the longitudinal and transverse directions. Further,
+we will assume $\bvec{k}$ to be spatially homogeneous in order to
+characterize the medium with a single bulk quantity at any instance in
+time. Naturally, the permeability will change over time as the bodies
+that comprise the medium disintegrate. Consider first the horizontal
+component of~\eqref{eqn:Darcy}
 \begin{equation}
   \label{q1}
-q_1(x,y) = -k_{11} \pderiv{p}{x}(x,y)
+  q_1(x,y) = -k_{11} \pderiv{p}{x}(x,y).
 \end{equation}
 
-By conservations of mass, the average of the horizontal discharge, $q_1$, over any vertical cross-section must equal the uniform flow rate $U$ imposed at the inlet/outlet.
+By conservations of mass, the average of the horizontal discharge, $q_1$, over any vertical cross-section must equal the uniform flow rate $U$ imposed at the inlet and outlet.
 That is, for any location $x_0$,
 \begin{equation}
-\qavg_1 := \frac{1}{2} \int_{-1}^{1} q_1(x_0, y) dy = U
+\qavg_1 := \frac{1}{2} \int_{-1}^{1} q_1(x_0, y) dy = U.
 \end{equation}
@@
 \begin{equation}
-\pavg(x_0) := \frac{1}{2} \int_{-1}^{1} p(x_0, y) dy
+  \pavg(x_0) := \frac{1}{2} \int_{-1}^{1} p(x_0, y) dy.
 \end{equation}
@@
 \begin{equation}
-\pup = \pavg(-1) \, , \quad \pdn = \pavg(1)
+  \pup = \pavg(-1) \, , \quad \pdn = \pavg(1),
 \end{equation}
@@
 
-Integrating \eqref{q1} over the porous-medium domain $[-1, 1] \times [-1,1]$, applying the fundamental theorem of calculus, and rearranging gives
+Integrating~\eqref{q1} over the porous-medium domain $[-1, 1] \times [-1,1]$, applying the fundamental theorem of calculus, and rearranging gives
 \begin{equation}
   \label{eqn:k11}
-k_{11} = \frac{2U}{\pup - \pdn}
+  k_{11} = \frac{2U}{\pup - \pdn}.
 \end{equation}
-This exact formula gives the permeability in terms of the total flux $U$ and measurements of the upstream/downstream pressure.
+This exact formula gives the permeability in terms of the total flux $U$
+and measurements of the upstream and downstream pressures.
 
@@
 The permeability of the medium is directly related to the drag exerted by the collection of bodies.
-The stress tensor associated with the Stokes equations \eqref{eqn:StokesEq} is given by $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$, and the Stokes equations can alternatively be expressed as $\grad \cdot \stress = 0$.
+The stress tensor associated with the Stokes equations~\eqref{eqn:StokesEq} is given by $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$, and the Stokes equations can alternatively be expressed as $\grad \cdot \stress = 0$.
 Integrating over an arbitrary domain $D$ and applying the divergence theorem gives
@@
   \label{divthm}
-0 = \int_{D} \grad \cdot \stress \, dV 
-= \int_{\partial D} \stress \, \nn \, ds
+  0 = \int_{D} \grad \cdot \stress \, dV,
+  = \int_{\partial D} \stress \, \nn \, ds.
 \end{equation}
@@
 \begin{equation}
-- \stress \, \nn = p \nn + \tau \ss
+  - \stress \, \nn = p \nn + \tau \ss,
 \end{equation}
@@
   \label{eqn:drag}
-\FD =  - \int_{\gamma} \stress \, \nn \, ds =  \int_{\gamma} p \nn + \tau \ss \, ds
+  \FD =  - \int_{\gamma} \stress \, \nn \, ds 
+  = \int_{\gamma} p \nn + \tau \ss \, ds.
 \end{equation}
@@
 
-Projecting \eqref{divthm} onto the horizontal direction $\ex$, using \eqref{eqn:drag}, and rearranging gives the exact relationship
+Projecting~\eqref{divthm} onto the horizontal direction $\ex$, using~\eqref{eqn:drag}, and rearranging gives the exact relationship
 \begin{equation}
@@
 \FD \cdot \ex = \int_{-1}^{1} \left( -p(x,y) + 2 \mu u_x(x,y) \right) \big|_{x=-x_0}^{x=x_0} dy + 
-\int_{-x_0}^{x_0} \mu u_y(x,y) \big|_{y=-1}^{y=1} dx
+\int_{-x_0}^{x_0} \mu u_y(x,y) \big|_{y=-1}^{y=1} dx.
 \end{equation}
@@
 In addition, the pressure $p(\pm x_0, y)$ approximately matches the downstream and upstream values respectively.
-With these assumptions, \eqref{drag_press} simplifies to the approximate form
+With these assumptions,~\eqref{drag_press} simplifies to the approximate form
 \begin{equation}
-\FD \cdot \ex \approx 2 (\pup - \pdn)
+  \FD \cdot \ex \approx 2 (\pup - \pdn).
 \end{equation}
@@
 The extraction of permeability, on the other hand, requires a few key approximations and assumptions, for example that the length-scale of grains is sufficiently small compared to the domain scale so that the flow field can be homogenized.
-Verifying relationship \eqref{perm_drag}, as will be done in Section \ref{sec:results}, will therefore support the idea that the collection of bodies can be treated as a porous medium and meaningful bulk quantities can be extracted.
+Verifying relationship~\eqref{perm_drag}, as will be done in Section~\ref{sec:results}, will therefore support the idea that the collection of bodies can be treated as a porous medium and meaningful bulk quantities can be extracted.
 
@@
 
+\todo[inline]{Bryan is here}
 %-------------------------------------------------------------------%
@@
 \begin{equation}
-\label{q1}
-q_2(x,y) = -k_{22} \pderiv{p}{y}(x,y)
+\label{q2}
+q_2(x,y) = -k_{22} \pderiv{p}{y}(x,y).
 \end{equation}

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
worked up to tortuosity section

@@
 
-\todo[inline]{Bryan is here}
 %-------------------------------------------------------------------%
@@
 
-Now consider measuring the transverse permeability $k_{22}$ using Darcy's law \eqref{eqn:Darcy}. Taking the vertical component of \eqref{eqn:Darcy} yields
+Now consider measuring the transverse permeability $k_{22}$ using Darcy's law. Taking the vertical component of~\eqref{eqn:Darcy} yields
 \begin{equation}
@@
 If this were to be done directly, the outer geometry would need to rotate by 90 degrees about the fixed configuration of bodies.
-In practice, it is simpler to keep the outer geometry fixed and rotate the inner configuration of bodies, then simply apply the method from Section \ref{LongPerm} to measure $k_{22}$.
+In practice, it is simpler to keep the outer geometry fixed and rotate the inner configuration of bodies, then simply apply the method from Section~\ref{LongPerm} to measure $k_{22}$.
 
@@
   \label{eq:anis}
-\anis = k_{11} / k_{22}
+  \anis = k_{11} / k_{22}.
 \end{equation}
@@
 For example, a body positioned in a high-throughput channel might disintegrate relatively quickly, thus opening the channel and creating higher overall anisotropy.
-We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively.
+We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy, respectively.
 As an extreme example, a tightly-packed horizontal row of circular bodies would exhibit high configurational anisotropy but no shape anisotropy.
@@
 We then measure the two permeabilities, $k_{11}^{(c)}$ and $ k_{22}^{(c)}$, of this configuration of circular bodies.
-Since all of the individual shapes are identical and isotropic (i.e.
-circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$.
+Since all of the individual shapes are identical and isotropic (i.e.~circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$.
 The total anisotropy, meanwhile, is the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured.

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
first draft on tortuosity section

@@
 \newcommand{\trap}{\mathrm{trap}}
+\newcommand{\pp}{{\mathbf{p}}}
 \newcommand{\uu}{{\mathbf{u}}}
@@
 The empty space to the left and right of $[-1,1] \times [-1,1]$ serve as buffer regions to allow the flow profile imposed at the inlet and outlet to gradually adjust to the presence of the bodies.
-The equations governing the velocity $\uu$ and pressure $p$ of the fluid consist of the incompressible, Stokes equations coupled to boundary conditions:
-\begin{equation}
+The equations governing the velocity $\uu = (u,v)$ and pressure $p$ of the fluid consist of the incompressible, Stokes equations coupled to boundary conditions: \begin{equation}
 \label{eqn:StokesEq}
@@
   \label{divthm}
-  0 = \int_{D} \grad \cdot \stress \, dV,
+  0 = \int_{D} \grad \cdot \stress \, dV
   = \int_{\partial D} \stress \, \nn \, ds.
@@
 Could reference Souzy et al. JFM article on velocity distributions in porous media \cite{souzy2020velocity}
+
+Like the permeability, the tortuosity provides a macroscopic perspective
+of the porous medium. We define the tortuosity to be the average length
+of streamlines passing through the region $[-1,1] \times [-1,1]$. In
+particular, for a particular eroded geometry with velocity field $\uu$,
+we calculate streamlines $\pp(t)$ that satisfy
+\begin{align}
+  \frac{d\pp}{dt} = \uu(\pp), \quad \pp(0) = (-1,y_0),
+\end{align}
+where $y_0 \in (-1,1)$. Then, the length of a streamline, which only
+depends on the initial $y$-coordinate, is
+\begin{align}
+  \lambda(y_0) = \int_{0}^{t(y_0)} \|\pp(t)\| \,dt.
+\end{align}
+The integral limit $t(y_0)$ is chosen so that the $x$-coordinate of
+$p(t(y_0))$ is $+1$. Then, the longitudinal tortuosity is
+\begin{align}
+  T_1 = \frac{1}{2}\left(\int_{S}u(-1,y)\lambda(y)\,dy \right)
+  \Bigg/
+  \left(\int_{S}u(x_0,y)\,dy \right).
+  \label{eqn:tortuosity_x}
+\end{align} 
+The factor of $1/2$ guarantees that $T_1 \geq 1$, and $T_1 = 1$ if and only if no grains are present.
+Identical to how we calculate the transverse permeability, we rotate each of the rotated bodies by 90 degrees and compute a transverse tortuosity $T_2$.
+Then, another measure of the anisotropy is
+\begin{align}
+  \anis = T_2/T_1.
+\end{align}
+As in the permeability definition of anisotropy, the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one.
+As this configuration erodes, the streamlines in the longitudinal direction are expected to less tortuous than those in the transverse direction, yielding $\anis > 1$.
+
+An alternative and more convenient way to compute the tortuosity is to
+use an area integral. If there is no reentrant flow in $D = [-1,1]
+\times [-1,1]$, then the longitudinal tortuosity can also be calculated
+as~\citep{dud-koz-mat2011}
+\begin{align}
+  T_1 = \left(\int_D \|\uu(\xx)\|\, d\xx \right) \Bigg/
+      \left(\int_D u(\xx)\, d\xx \right).
+  \label{eqn:tortuosity_x2}
+\end{align}
+We note that there may be slow reentrant regions in our geometries~\cite{chiu2020viscous}, but they are sufficiently small that the difference between equations~\eqref{eqn:tortuosity_x} and~\eqref{eqn:tortuosity_x2} can be neglected.
+We use a similar area integral to compute $T_2$.
 

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
edited new sec on tortuosity

@@
 
+%-------------------------------------------------------------------%
 \subsection{Tortuosity}
-
-We need to write this section.
-Could reference Souzy et al. JFM article on velocity distributions in porous media \cite{souzy2020velocity}
+%
+%We need to write this section.
+%Could reference Souzy et al. JFM article on velocity distributions in porous media \cite{souzy2020velocity}
 
@@
 \begin{align}
-  \frac{d\pp}{dt} = \uu(\pp), \quad \pp(0) = (-1,y_0),
+  \dot{\pp}(t) = \uu(\pp), \quad \pp(0) = (-1,y_0),
 \end{align}
-where $y_0 \in (-1,1)$. Then, the length of a streamline, which only
-depends on the initial $y$-coordinate, is
+where $y_0 \in (-1,1)$. The streamlines are calculated with a fourth-order Runge-Kutta method. Then, the length of each streamline, which only depends on its initial $y$-coordinate, is
 \begin{align}
@@
 The integral limit $t(y_0)$ is chosen so that the $x$-coordinate of
-$p(t(y_0))$ is $+1$. Then, the longitudinal tortuosity is
+$\pp(t(y_0))$ is $+1$. Then, the longitudinal tortuosity is
 \begin{align}
@@
 The factor of $1/2$ guarantees that $T_1 \geq 1$, and $T_1 = 1$ if and only if no grains are present.
-Identical to how we calculate the transverse permeability, we rotate each of the rotated bodies by 90 degrees and compute a transverse tortuosity $T_2$.
+Identical to how we calculate the transverse permeability, we rotate each of the eroded bodies by 90 degrees and compute a transverse tortuosity $T_2$.
 Then, another measure of the anisotropy is
@@
 
-An alternative and more convenient way to compute the tortuosity is to
-use an area integral. If there is no reentrant flow in $D = [-1,1]
-\times [-1,1]$, then the longitudinal tortuosity can also be calculated
-as~\citep{dud-koz-mat2011}
+An alternative and computationally more convenient way to compute the tortuosity is to use an area integral.
+If there is no reentrant flow in $D = [-1,1] \times [-1,1]$, then the longitudinal tortuosity can be calculated as~\citep{dud-koz-mat2011}
 \begin{align}
@@
 \end{align}
+We use a similar area integral to compute $T_2$.
 We note that there may be slow reentrant regions in our geometries~\cite{chiu2020viscous}, but they are sufficiently small that the difference between equations~\eqref{eqn:tortuosity_x} and~\eqref{eqn:tortuosity_x2} can be neglected.
-We use a similar area integral to compute $T_2$.
 

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large-scale level.
-As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted by replacing any collection of partially-eroded bodies with circles having the same areas and centers of mass and measuring the anisotropy of the resulting configuration.
-We perform this process at every time step in the simulation, and show in Fig.~\ref{fig3}(a) both permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations.
-As seen in the figure, the permeabilities of the circle configurations always lie in between the true values $k_{11}$ and $k_{22}$ of the eroded geometries.
+As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large scale.
+As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted through a process in which, at any point in time, the configuration of partially-eroded bodies is replaced with a collection of circles having the same areas and centers of mass.
+We perform this process and show in Fig.~\ref{fig3}(a) the permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations.
+As seen in the figure, the permeabilities of the circle configurations always lie in between the values, $k_{11}$ and $k_{22}$, of the true, eroded medium.
+The {\em configurational} anisotropy is then computed as the permeability ratio of the circle configuration, $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$, and then the {\em shape} anisotropy can be determined through $\anis_S = \anis/\anis_C$.
+As seen in Fig.~\ref{fig3}(b), the shape anisotropy is the larger factor throughout the majority of the simulation, implying that the shape of individual grains plays a larger role than their relative positions.
+It is only during the last 10\% of the simulation that the configurational anisotropy grows significantly and surpasses the shape anisotropy.
+This relative growth of the configurational anisotropy corresponds to the strong channelization seen in the last panel of Fig.~\ref{fig1}.
 
-%Text for Fig 3: 
-%The anisotropy of permeability grows large, up to a value of 4 during the middle portion of the simulation. The figure also shows the anisotropy of the circular grid.
+The late emergence of substantial configurational anisotropy may seem like a spurious effect that is particular to the one simulation shown in Fig.~\ref{fig3}.
+However, statistical analysis of many simulations will show this feature to emerge robustly in simulations with a relatively large number of bodies $M \ge 60$.
 

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The factor of $1/2$ guarantees that $T_1 \geq 1$, and $T_1 = 1$ if and only if no grains are present.
-Identical to how we calculate the transverse permeability, we rotate each of the eroded bodies by 90 degrees and compute a transverse tortuosity $T_2$.
+Identical to how we calculate the transverse permeability, we rotate \nick{the configuration of} eroded bodies by 90 degrees and compute a transverse tortuosity $T_2$.
 Then, another measure of the anisotropy is
@@
 The late emergence of substantial configurational anisotropy may seem like a spurious effect that is particular to the one simulation shown in Fig.~\ref{fig3}.
-However, statistical analysis of many simulations will show this feature to emerge robustly in simulations with a relatively large number of bodies $M \ge 60$.
+However, statistical analysis of many simulations will show this feature to emerge robustly in simulations featuring a relatively large number of bodies $M \ge 60$.
 
@@
 % Data from 80-4
+
+As a second way to quantify medium anisotropy, we measure the tortuosity, $T_1$ and $T_2$, in the longitudinal and transverse directions respectively.
+Figure \ref{fig4}(a), shows how both vary over the course of the simulation, with $T_2$ growing significantly larger than $T_1$, indicating that passive tracers must take more tortuous paths around the partially eroded grains when traveling transverse to the flow.
 

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \newcommand{\anis}{\mathcal{A}}
+\newcommand{\anistort}{\mathcal{A_T}}
 \newcommand{\diag}{\mathop{\mathrm{diag}}}
@@
 \end{align} 
+\todo[inline]{What is $x_0$ in the denominator? Should that be -1?}
 The factor of $1/2$ guarantees that $T_1 \geq 1$, and $T_1 = 1$ if and only if no grains are present.
@@
 \begin{align}
-  \anis = T_2/T_1.
+  \anistort = T_2/T_1.
 \end{align}
@@
 a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases.
-b) Resistance to flow can be characterized by either the inverse permeability (solid) or the cumulative drag (dots), the two of which are related through \eqref{perm_drag}.
+b) Resistance to flow can be characterized by either the resistivity (solid) or the cumulative drag (dots), the two of which are related through \eqref{perm_drag}.
 Both are seen to decrease as the medium erodes, and relationship \eqref{perm_drag} is confirmed by the simulation data.
-The figure also shows the inverse permeability in transverse direction (dashed).
+The figure also shows the resistivity in transverse direction (dashed).
  \label{fig2}
@@
 \caption{
-Permeability
+The permeability and anisotropy of the same 80-body simulation featured in Figs.~\ref{fig1} and \ref{fig2}.
+a) Both the longitudinal (solid) and transverse (dashed) permeability increase over time as the bodies erode.
+Also shown in the figure is the longitudinal and transverse permeabilities of the corresponding configurations of circles, which allows us to extract the configurational component of anisotropy.
+b) The anisotropy of the medium increases as the bodies erode and preferentially allow flow in the longitudinal direction.
+The total anisotropy is the sum of configurational and shape components.
+The shape contribution is larger throughout most of the simulation, but near the end of the simulation, the configurational contribution grows large as the channel-structure dominates.
 \label{fig3}
@@
 
+% Could reference Eastham paper on including chemistry, precipitation reaction.
+% Could discuss convection in conjunction with erosion.
+
 \bibliographystyle{plain}

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \end{align}
+\todo[inline]{Might eliminate this line so that we don't double-use anisotropy. In any case, I think $(T_2-1)/(T_1-1)$ might be more useful. Will give it thought.}
 As in the permeability definition of anisotropy, the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one.
@@
 \caption{
-Tortuosity
+Tortuosity measurements of the same 80-body simulation featured in Figs.~\ref{fig1} and \ref{fig2}.
+a) As the bodies erode, the transverse tortuosity $T_2$ exceeds the longitudinal component, indicating more convoluted paths for tracers traveling vertically, transverse to the flow.
+Also shown are the measurements for the configurations of circles.
+b) The ratio $(T_2-1)/(T_1-1)$ serves as a counterpart to the anisotropy.
+Like anisotropy, this ratio grows large over the course of erosion.
+It can be decomposed into configurational and shape components in a similar manner.
 \label{fig4}
@@
 As a second way to quantify medium anisotropy, we measure the tortuosity, $T_1$ and $T_2$, in the longitudinal and transverse directions respectively.
-Figure \ref{fig4}(a), shows how both vary over the course of the simulation, with $T_2$ growing significantly larger than $T_1$, indicating that passive tracers must take more tortuous paths around the partially eroded grains when traveling transverse to the flow.
+Figure \ref{fig4}(a), shows how both vary over the course of the simulation.
+As the bodies erode, $T_2$ grows significantly larger than $T_1$, indicating that passive tracers must follow more tortuous paths when traveling transversely and that longitudinal paths are more direct.
+The ratio $(T_2-1)/(T_1-1)$ provides a second measure of anisotropy to complement the permeability-dependent quantity.
+We have chosen to subtract one in parenthesis so that both numerator and denominator vanish when no bodies are present, as analogous to resistivity.
+As seen in Fig.~\ref{fig4}(b), the ratio $(T_2-1)/(T_1-1)$ grows significantly during erosion, up to a peak of nearly 8.
+This ratio can be decomposed into configurational and shape components, exactly as is done for the anisotropy (i.e.~by replacing a collection of eroded bodies with circles of the same areas and centers of mass).
+Figure~\ref{fig4}(b) shows that the shape component is greater for the majority of the simulation, but near the end of the simulation, the configurational component is competitive.
 

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The factor of $1/2$ guarantees that $T_1 \geq 1$, and $T_1 = 1$ if and only if no grains are present.
-Identical to how we calculate the transverse permeability, we rotate \nick{the configuration of} eroded bodies by 90 degrees and compute a transverse tortuosity $T_2$.
-Then, another measure of the anisotropy is
-\begin{align}
-  \anistort = T_2/T_1.
-\end{align}
-\todo[inline]{Might eliminate this line so that we don't double-use anisotropy. In any case, I think $(T_2-1)/(T_1-1)$ might be more useful. Will give it thought.}
-As in the permeability definition of anisotropy, the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one.
+Identical to how we calculate the transverse permeability, we rotate \nick{the configuration of} eroded bodies by 90 degrees to compute a transverse tortuosity $T_2$.
+
+% NOTE: I explain what ratio we compute in the results section, so we don't need to do it here.
+%Then, another measure of the anisotropy is
+%\begin{align}
+ % \anistort = T_2/T_1.
+%\end{align}
+%\todo[inline]{Might eliminate this line so that we don't double-use anisotropy. In any case, I think $(T_2-1)/(T_1-1)$ might be more useful. Will give it thought.}
+%As in the permeability definition of anisotropy, the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one.
 As this configuration erodes, the streamlines in the longitudinal direction are expected to less tortuous than those in the transverse direction, yielding $\anis > 1$.
@@
 
+The previous section shows many intriguing features to arise as a randomly initialized configuration of solid bodies erodes.
+These observations natural raise the question: are the trends specific to the particular initializing chosen or do are they general features that emerge robustly?
+To answer this question, we now analyze the same quantities --- permeability, tortuosity, and anisotropy --- over an ensemble of many simulations having different numbers of bodies and different random initializations.
+We analyze runs having $M$ = 20, 40, 60, 80, and 100 bodies, with at least three different instances of each.
+This data set represents roughly 2,100 hours of computational time.
+
+Figure \ref{fig5} shows the permeability and anisotropy measurements for the complete data set.
+In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean and standard deviation of each quantity are shown, and the five different values of $M$ are shown by different colors.
+As seen in Figs.~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies.
+That is, permeability monotonically decreases with the number of bodies and the error bars shows little overlap between different values of $M$ until very late in the simulation when the bodies have nearly vanished.
+
+Figure~\ref{fig5}(c) shows the corresponding statistics of anisotropy, $\anis$.
+Here, the anisotropy is not as well separated by $M$.
+That is, given the error-bars, there is significant overlap in the signal of $\anis$ across different values of $M$.
+On notable feature is second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100.
+As before, the anisotropy can be decomposed into configuration and shape components as shown in Figs.~\ref{fig5}(d)--(e)
+
 %---------------------------------------------------------%

### 2022-06-27 simulations/unpack_data.jl

@@ -36,4 +36,4 @@ function do_stuff()
 	end
 end
 
-do_stuff()
+#do_stuff()

### 2022-06-27 simulations/vplots.jl

@@ -177,6 +177,21 @@ function resist_thresh(vars...)
 	end
 end
 
+# Compute the total cpu time
+function cpu_hours_total()
+	nbod_list = [20 40 60 80 100]
+	total_hours = 0.0
+	for nbod in nbod_list
+		runs = get_runs(nbod)
+		for run in runs
+			hours = load(proc_file(run), "cpu_hours")
+			total_hours += hours
+		end
+	end
+	println("Total CPU hours = ", round(total_hours, sigdigits=3))
+end
+cpu_hours_total()
+
 # Plot the statistics
 function vplot_stats()
 	nbod_list = [20 40 60 80 100] #[20, 40, 60, 80, 100]

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 On notable feature is second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100.
-As before, the anisotropy can be decomposed into configuration and shape components as shown in Figs.~\ref{fig5}(d)--(e)
+As before, the anisotropy can be decomposed into configuration and shape components as shown in Figs.~\ref{fig5}(d)--(e).
+Here, we see the late surge in configurational anisotropy for these larger values of $M = $ 60, 80, 100.
+For these runs with a large number of bodies, the latest stages of erosion are dominated by channelization which substantially promotes the configurational anisotropy.
+The shape anisotropy, meanwhile, takes a more regular, parabolic form that is relatively insensitive to the number of bodies.
 
@@
 \includegraphics[width = 0.99 \textwidth]{./figs/fig5.pdf}
-\caption{
-a) Statistics from an ensemble of runs.
+\caption{ Permeability and anisotropy statistics from an ensemble of simulations.
+a) 
 \label{fig5}

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
+%---------------------------------------------------------%
+\begin{figure*}%[htbp]
+\centering
+\includegraphics[width = 0.9 \textwidth]{./figs/fig5.pdf}
+\caption{ Permeability and anisotropy statistics from an ensemble of simulations.
+(a)--(b) Measurements of the longitudinal (a) and transverse (b) permeability are well separated with respect to the number of bodies, $M$.
+For each $M$, the mean and standard deviation of permeability are shown for increasing porosity (or time).
+(c) In all runs, the anisotropy grows substantially and reaches a maximum value of roughly 4--6.
+Runs with a large number of bodies ($M$ = 60, 80, or 100) show a second surge in anisotropy near the end of the simulation.
+(d)--(e) The configurational and shape contributions of anisotropy.
+While the shape anisotropy varies fairly regularly with time across all runs, the configurational anisotropy shows a distinct peak late in the simulation for runs with large $M$.
+\label{fig5}
+}
+\end{figure*}
+%---------------------------------------------------------%
+
 Figure \ref{fig5} shows the permeability and anisotropy measurements for the complete data set.
@@
 \centering
-\includegraphics[width = 0.99 \textwidth]{./figs/fig5.pdf}
-\caption{ Permeability and anisotropy statistics from an ensemble of simulations.
-a) 
-\label{fig5}
+\includegraphics[width = 0.9 \textwidth]{./figs/fig6.pdf}
+\caption{
+Tortuosity statistics from an ensemble of simulations.
+(a)--(b) The longitudinal (a) and transverse tortuosity measurements are well grouped with respect to the number of bodies.
+(c)--(e) Statistics of the ratio, $(T_2 -1)/(T_1 -1)$, including its configurational and shape contribution.
+\label{fig6}
 }
@@
 
-%---------------------------------------------------------%
-\begin{figure*}%[htbp]
-\centering
-\includegraphics[width = 0.99 \textwidth]{./figs/fig6.pdf}
-\caption{
-a) Statistics from an ensemble of runs.
-\label{fig6}
-}
-\end{figure*}
-%---------------------------------------------------------%
+Similar statistical analysis is performed on the tortuosity measurements and shown in Fig.~\ref{fig6}(a)--(b).
+Much like before, the tortuosity measurements are well separated by the number of bodies, with the error bars showing little overlap across different values of $M$.
+Measurements of the ratio, $(T_2 -1)/(T_1 -1)$, however, are not well grouped with respect to $M$, as seen in Fig.~\ref{fig6}(c).
 

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 Much like before, the tortuosity measurements are well separated by the number of bodies, with the error bars showing little overlap across different values of $M$.
-Measurements of the ratio, $(T_2 -1)/(T_1 -1)$, however, are not well grouped with respect to $M$, as seen in Fig.~\ref{fig6}(c).
+Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, however, show similar behavior across different values of $M$, as seen in Fig.~\ref{fig6}(c).
+For nearly all runs, the tortuosity ratio increases as bodies erode up to a maximum of roughly $(T_2 -1)/(T_1 -1) = 8$, and then the tortuosity ratio decreases near the very end of the simulation.
+As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figs.~\ref{fig6}(d)--(e)
+
+Figures~\ref{fig6}(d)--(e) show that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
 

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
M

@@
 For nearly all runs, the tortuosity ratio increases as bodies erode up to a maximum of roughly $(T_2 -1)/(T_1 -1) = 8$, and then the tortuosity ratio decreases near the very end of the simulation.
-As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figs.~\ref{fig6}(d)--(e)
-
-Figures~\ref{fig6}(d)--(e) show that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
+As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figs.~\ref{fig6}(d)--(e).
+The figure shows that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
 

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
+In this paper, we have introduced a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow.
+The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies with statistical analysis across an ensemble of different initializations.
+By linking the governing Stokes equation to Darcy's law, we are able to extract porous media properties, like permeability, resistivity, tortuosity, and anisotropy, as they evolve over time.
+By comparing the resistivity to the directly computed drag, we find that these porous-media properties can be extracted with high accuracy.
+
+	The ratio of longitudinal to transverse permeability provides the main
+
 % Could reference Eastham paper on including chemistry, precipitation reaction.

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The Cauchy-integral formulation and associated quadrature formulas enable us to resolve dense configurations of nearly contacting bodies.
-We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by up to a factor of five.
-These results suggest that the erosion of solid material from groundwater flows may contribute to the well-known anisotropy of natural porous media.
+We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by up to a factor of six.
+These results suggest that the erosion of solid material from groundwater flows may contribute to previously observed anisotropy of natural porous media.
 \end{abstract}

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-In this paper, we have introduced a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow.
-The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies with statistical analysis across an ensemble of different initializations.
-By linking the governing Stokes equation to Darcy's law, we are able to extract porous media properties, like permeability, resistivity, tortuosity, and anisotropy, as they evolve over time.
-By comparing the resistivity to the directly computed drag, we find that these porous-media properties can be extracted with high accuracy.
+In this paper, we have presented a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow.
+The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies and statistical analysis across an ensemble of different initializations.
+By linking the governing Stokes equation to Darcy's law, we are able to extract porous media properties, including permeability, resistivity, tortuosity, and anisotropy, as they evolve over time.
+Direct comparison of resistivity with the total drag force confirms such bulk properties are extracted with high accuracy.
 
-	The ratio of longitudinal to transverse permeability provides the main
+	The ratio of longitudinal to transverse permeability provides our main diagnostic of medium anisotropy.
+Measurements indicate that the anisotropy grows substantially as a result of fluid mechanical erosion, reaching a peak of roughly six in most simulations, before the bodies completely vanish and return the system to an isotropic state.
+The anisotropy can be further decomposed into a configurational component, due only to the relative positions of bodies, and a shape component, due to the detailed geometry of each body.
+Statistical analysis across a large number of simulations reveals that if the number of bodies is sufficiently large, $M \ge 60$m, the configurational anisotropy surges near the final stages of erosion and surpasses the shape anisotropy as the primary contribution.
+This surge in configurational anisotropy is associated with the formation of visual channels that transmit a large portion of the flow.
+The tortuosity provides a second metric and also reveals strong anisotropy to develop across all simulations.
+%though this metric shows less signal in the configurational contribution.
 

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The anisotropy can be further decomposed into a configurational component, due only to the relative positions of bodies, and a shape component, due to the detailed geometry of each body.
-Statistical analysis across a large number of simulations reveals that if the number of bodies is sufficiently large, $M \ge 60$m, the configurational anisotropy surges near the final stages of erosion and surpasses the shape anisotropy as the primary contribution.
+Statistical analysis across a large number of simulations reveals that if the number of bodies is sufficiently large, $M \ge 60$, the configurational anisotropy surges near the final stages of erosion and surpasses the shape anisotropy as the primary contribution.
 This surge in configurational anisotropy is associated with the formation of visual channels that transmit a large portion of the flow.
 The tortuosity provides a second metric and also reveals strong anisotropy to develop across all simulations.
+The methodology could be extended to more complex scenarios of thermal convective flows in porous media \cite{McCurdy2019} or erodable porous structures formed by precipitation reactions \cite{eastham2020multiphase}.
+
 %though this metric shows less signal in the configurational contribution.
-
-% Could reference Eastham paper on including chemistry, precipitation reaction.
-% Could discuss convection in conjunction with erosion.
 

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-	Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water~\cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows \cite{szymczak2009wormhole, chiu2020viscous, zareei2022temporal}.
+	Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water~\cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows \cite{chiu2020viscous, szymczak2009wormhole, jager2017channelization, grodzki2019reactive, bizmark2020multiscale, derr2020flow, zareei2022temporal}.
 The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting large-scale features as well as small-scale ones, such as the microstructure of porous materials.

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications~\cite{quaife2018boundary, chiu2020viscous}.
-Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $\mathcal{O}(100)$ solid bodies.
+Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
 The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}.

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
wrapped up first read

@@
 
-\author[NJIT]{Shang-Huan Chiu}
+\author[TAMU]{Shang-Huan Chiu}
 %\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}
@@
 \address[FSU]{Florida State University}
-\address[NJIT]{New Jersey Institute of Technology}
+\address[TAMU]{Texas A\&M-San Antonio}
 
@@
 
-	Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water~\cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows \cite{chiu2020viscous, szymczak2009wormhole, jager2017channelization, grodzki2019reactive, bizmark2020multiscale, derr2020flow, zareei2022temporal}.
+Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water~\cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows~\cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows~\cite{chiu2020viscous, szymczak2009wormhole, jager2017channelization, grodzki2019reactive, bizmark2020multiscale, derr2020flow, zareei2022temporal}.
 The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting large-scale features as well as small-scale ones, such as the microstructure of porous materials.
@@
 In Section~\ref{sec:medium} we measure porous-medium properties, in particular permeability.
-In Section~\ref{sec:results} we provide results and we conclude in section~\ref{sec:conclusion}.
+In Section~\ref{sec:results} we provide results and we conclude in Section~\ref{sec:conclusion}.
 
@@
 \end{align}
-where $\rr = \xx - \yy$ and $\rho = \|\rr\|$. Note that $\bd\Omega$ includes both the eroding bodies and the outer boundary. The Stokeslet and the rotlets are
+where $\rr = \xx - \yy$ and $\rho = \|\rr\|$. Note that $\bd\Omega$ includes both the eroding bodies and the outer boundary. The Stokeslets and the rotlets are
 \begin{align}
@@
     \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
-    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
+    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x_0-y} \, dy,
     \quad x_0 \in \gamma,
@@
 approximated with a uniformly spectral error using similar quadrature
-rules. For $x \in \Omega$, 
+rules. To summarize, for $x \in \Omega$, 
 \begin{align}
@@
     \Bigg/
-    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right).
+    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
   \label{eqn:D2vBary}
@@
 Like the permeability, the tortuosity provides a macroscopic perspective
-of the porous medium. We define the tortuosity to be the average length
+of the porous medium \cite{souzy2020velocity}. We define the tortuosity to be the average length
 of streamlines passing through the region $[-1,1] \times [-1,1]$. In
@@
   \Bigg/
-  \left(\int_{S}u(x_0,y)\,dy \right).
+  \left(\int_{S}u(-1,y)\,dy \right).
   \label{eqn:tortuosity_x}
 \end{align} 
-\todo[inline]{What is $x_0$ in the denominator? Should that be -1?}
 The factor of $1/2$ guarantees that $T_1 \geq 1$, and $T_1 = 1$ if and only if no grains are present.
-Identical to how we calculate the transverse permeability, we rotate \nick{the configuration of} eroded bodies by 90 degrees to compute a transverse tortuosity $T_2$.
+Identical to how we calculate the transverse permeability, we rotate the configuration of eroded bodies by 90 degrees to compute a transverse tortuosity $T_2$.
 
@@
 With the numerical methods in place, we now present results on how fluid-mechanical erosion alters porous-media properties over time.
-We will first discuss the results from a single simulation and then generalize to statistical results from ensembles of simulations.
+We first discuss the results from a single simulation and then generalize to statistical results from ensembles of simulations.
 
@@
 To begin, we discuss a single simulation of 80 bodies eroding in Stokes flow.
-For reference, the simulation discussed here is the same one shown in Fig.~\ref{fig1}.
+The simulation discussed here is the same one shown in Figure~\ref{fig1}.
 The initial configuration consists of 80 circular bodies having randomized sizes and positions.
-The material-removal process alters both the shape of individual bodies as well as the overall structure of the pore network transmitting the flow, as can be seen in Fig.~\ref{fig1}.
-Initially, the solid bodies occupy $60\%$ of the area, or the porosity is $\varphi = 0.4$, corresponding to a relatively dense packing; see Fig.~\ref{fig1} for a visual.
+The material-removal process alters both the shape of individual bodies as well as the overall structure of the pore network transmitting the flow, as can be seen in Figure~\ref{fig1}.
+Initially, the solid bodies occupy $60\%$ of the area, or the porosity is $\varphi = 0.4$, corresponding to a relatively dense packing; see Figure~\ref{fig1} for a visual.
 Figure~\ref{fig2}(a) shows how the solid-body area decreases, or equivalently the porosity increases, over time as the bodies erode.
@@
 \caption{A single simulation of porous-medium erosion.
-The initial configuration consists of 80 circular bodies of random size and position, as seen in Fig.~\ref{fig1}.
+The initial configuration consists of 80 circular bodies of random size and position, as seen in Figure~\ref{fig1}.
 a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases.
-b) Resistance to flow can be characterized by either the resistivity (solid) or the cumulative drag (dots), the two of which are related through \eqref{perm_drag}.
-Both are seen to decrease as the medium erodes, and relationship \eqref{perm_drag} is confirmed by the simulation data.
+b) Resistance to flow can be characterized by either the resistivity (solid) or the cumulative drag (dots), the two of which are related through~\eqref{perm_drag}.
+Both are seen to decrease as the medium erodes, and relationship~\eqref{perm_drag} is confirmed by the simulation data.
 The figure also shows the resistivity in transverse direction (dashed).
@@
 
-As the bodies disintegrate and give way to wider pores, the resistance to flow decreases as seen in Fig.~\ref{fig2}(b).
-The resistance to flow can be quantified in two separate ways, as outlined in Section \ref{sec:medium}, namely by computing the total drag or by extracting the permeability.
-As discussed in Section \ref{sec:medium}, the drag is a microscopic quantity that can be computed with high accuracy and without ambiguity in our Stokes-based simulations.
+As the bodies disintegrate and give way to wider pores, the resistance to flow decreases as seen in Figure~\ref{fig2}(b).
+The resistance to flow can be quantified in two separate ways, as outlined in Section~\ref{sec:medium}, namely by computing the total drag or by extracting the permeability.
+As discussed in Section~\ref{sec:medium}, the drag is a microscopic quantity that can be computed with high accuracy and without ambiguity in our Stokes-based simulations.
 The permeability, on the other hand, relies on a few approximations, but the extraction of such bulk quantities will be more valuable in characterizing the evolving porous medium.
 As such, it is particularly useful to compare these two perspectives so that the assumptions underlying the coarse-graining process can be assessed.
-In particular, we aim to test the approximate formula \eqref{perm_drag}, relating the longitudinal drag $F_1$ to the inverse permeability $1/k_{11}$, also known as the {\em resistivity}.
-Figure \ref{fig2}(b) indeed shows close agreement between these two quantities over the entire duration of the simulation, thus confirming the ability to extract medium properties during the erosion process.
+In particular, we aim to test the approximate formula~\eqref{perm_drag}, relating the longitudinal drag $F_1$ to the inverse permeability $1/k_{11}$, also known as the {\em resistivity}.
+Figure~\ref{fig2}(b) indeed shows close agreement between these two quantities over the entire duration of the simulation, thus confirming the ability to extract medium properties during the erosion process.
 
-In Fig.~\ref{fig2}(b) we also show the transverse resistivity, $1/k_{22}$, as it decreases over the course of the simulation.
+In Figure~\ref{fig2}(b) we also show the transverse resistivity, $1/k_{22}$, as it decreases over the course of the simulation.
 Notice that this transverse resistivity exceeds the longitudinal resistivity by a significant margin, indicating that the configuration provides greater resistance to flow in the vertical direction.
@@
 \caption{
-The permeability and anisotropy of the same 80-body simulation featured in Figs.~\ref{fig1} and \ref{fig2}.
+The permeability and anisotropy of the same 80-body simulation featured in Figures~\ref{fig1} and~\ref{fig2}.
 a) Both the longitudinal (solid) and transverse (dashed) permeability increase over time as the bodies erode.
-Also shown in the figure is the longitudinal and transverse permeabilities of the corresponding configurations of circles, which allows us to extract the configurational component of anisotropy.
+Also shown is the longitudinal and transverse permeabilities of the corresponding configurations of circles, which allows us to extract the configurational component of anisotropy.
 b) The anisotropy of the medium increases as the bodies erode and preferentially allow flow in the longitudinal direction.
-The total anisotropy is the sum of configurational and shape components.
+The total anisotropy is the sum \todo[inline]{do you mean product} of configurational and shape components.
 The shape contribution is larger throughout most of the simulation, but near the end of the simulation, the configurational contribution grows large as the channel-structure dominates.
@@
 
-Figure \ref{fig3}(a) shows more directly how permeability in the longitudinal, $k_{11}$ and transverse, $k_{22}$ directions increase over time as the medium erodes.
+Figure~\ref{fig3}(a) shows more directly how permeability in the longitudinal, $k_{11}$ and transverse, $k_{22}$ directions increase over time as the medium erodes.
 Once again, the relationship $k_{11} > k_{22}$ indicates a higher propensity for flow in the longitudinal direction.
-Notice that the permeability increases by nearly 5 orders of magnitude over the course of the simulation, indicating that erosion substantially alters medium properties.
+Notice that the permeability increases by nearly five orders of magnitude over the course of the simulation, indicating that erosion substantially alters medium properties.
 
-As given in \eqref{eq:anis}, the ratio of longitudinal to transverse permeability defines the anisotropy of the medium, $\anis = k_{11} / k_{22}$, which is plotted in Fig.~\ref{fig3}(b) over the course fo the simulation (solid curve).
+As given in~\eqref{eq:anis}, the ratio of longitudinal to transverse permeability defines the anisotropy of the medium, $\anis = k_{11} / k_{22}$, which is plotted in Figure~\ref{fig3}(b) over the course of the simulation (solid curve).
 Early in the simulation the anisotropy is nearly one, as the initial configuration of randomly placed circles has no preferred flow direction.
@@
 
-As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large scale.
-As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted through a process in which, at any point in time, the configuration of partially-eroded bodies is replaced with a collection of circles having the same areas and centers of mass.
-We perform this process and show in Fig.~\ref{fig3}(a) the permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations.
+As discussed in Section~\ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large scale.
+As detailed in Section~\ref{subsec:anis}, the configurational anisotropy can be extracted through a process in which, at any point in time, the configuration of partially-eroded bodies is replaced with a collection of circles having the same areas and centers of mass.
+We perform this process and show in Figure~\ref{fig3}(a) the permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations.
 As seen in the figure, the permeabilities of the circle configurations always lie in between the values, $k_{11}$ and $k_{22}$, of the true, eroded medium.
 The {\em configurational} anisotropy is then computed as the permeability ratio of the circle configuration, $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$, and then the {\em shape} anisotropy can be determined through $\anis_S = \anis/\anis_C$.
-As seen in Fig.~\ref{fig3}(b), the shape anisotropy is the larger factor throughout the majority of the simulation, implying that the shape of individual grains plays a larger role than their relative positions.
+As seen in Figure~\ref{fig3}(b), the shape anisotropy is the larger factor throughout the majority of the simulation, implying that the shape of individual grains plays a larger role than their relative positions.
 It is only during the last 10\% of the simulation that the configurational anisotropy grows significantly and surpasses the shape anisotropy.
-This relative growth of the configurational anisotropy corresponds to the strong channelization seen in the last panel of Fig.~\ref{fig1}.
+This relative growth of the configurational anisotropy corresponds to the strong channelization seen in the last panel of Figure~\ref{fig1}.
 
-The late emergence of substantial configurational anisotropy may seem like a spurious effect that is particular to the one simulation shown in Fig.~\ref{fig3}.
-However, statistical analysis of many simulations will show this feature to emerge robustly in simulations featuring a relatively large number of bodies $M \ge 60$.
+The late emergence of substantial configurational anisotropy may seem
+like a spurious effect that is particular to the one simulation shown in
+Figure~\ref{fig3}. However, statistical analysis of many simulations will show this feature to emerge robustly in simulations featuring a relatively large number of bodies $M \ge 60$.
 
@@
 \caption{
-Tortuosity measurements of the same 80-body simulation featured in Figs.~\ref{fig1} and \ref{fig2}.
+Tortuosity measurements of the same 80-body simulation featured in Figures~\ref{fig1} and~\ref{fig2}.
 a) As the bodies erode, the transverse tortuosity $T_2$ exceeds the longitudinal component, indicating more convoluted paths for tracers traveling vertically, transverse to the flow.
@@
 
-As a second way to quantify medium anisotropy, we measure the tortuosity, $T_1$ and $T_2$, in the longitudinal and transverse directions respectively.
-Figure \ref{fig4}(a), shows how both vary over the course of the simulation.
-As the bodies erode, $T_2$ grows significantly larger than $T_1$, indicating that passive tracers must follow more tortuous paths when traveling transversely and that longitudinal paths are more direct.
-The ratio $(T_2-1)/(T_1-1)$ provides a second measure of anisotropy to complement the permeability-dependent quantity.
-We have chosen to subtract one in parenthesis so that both numerator and denominator vanish when no bodies are present, as analogous to resistivity.
-As seen in Fig.~\ref{fig4}(b), the ratio $(T_2-1)/(T_1-1)$ grows significantly during erosion, up to a peak of nearly 8.
+As a second way to quantify medium anisotropy, we measure the
+tortuosity, $T_1$ and $T_2$, in the longitudinal and transverse
+directions respectively. Figure~\ref{fig4}(a), shows how both vary over
+the course of the simulation. As the bodies erode, $T_2$ grows
+significantly larger than $T_1$, indicating that passive tracers must
+follow more tortuous paths when traveling transversely and that
+longitudinal paths are more direct. The ratio $(T_2-1)/(T_1-1)$ provides
+a second measure of anisotropy to complement the permeability-dependent
+quantity. We have chosen to subtract one in parenthesis so that both
+numerator and denominator vanish when no bodies are present, as
+analogous to resistivity.
+As seen in Figure~\ref{fig4}(b), the ratio $(T_2-1)/(T_1-1)$ grows significantly during erosion, up to a peak of nearly 8.
 This ratio can be decomposed into configurational and shape components, exactly as is done for the anisotropy (i.e.~by replacing a collection of eroded bodies with circles of the same areas and centers of mass).
@@
 These observations natural raise the question: are the trends specific to the particular initializing chosen or do are they general features that emerge robustly?
-To answer this question, we now analyze the same quantities --- permeability, tortuosity, and anisotropy --- over an ensemble of many simulations having different numbers of bodies and different random initializations.
+To answer this question, we now analyze the same quantities---permeability, tortuosity, and anisotropy---over an ensemble of many simulations having different numbers of bodies and different random initializations.
 We analyze runs having $M$ = 20, 40, 60, 80, and 100 bodies, with at least three different instances of each.
@@
 \includegraphics[width = 0.9 \textwidth]{./figs/fig5.pdf}
-\caption{ Permeability and anisotropy statistics from an ensemble of simulations.
+\caption{Permeability and anisotropy statistics from an ensemble of simulations.
 (a)--(b) Measurements of the longitudinal (a) and transverse (b) permeability are well separated with respect to the number of bodies, $M$.
@@
 
-Figure \ref{fig5} shows the permeability and anisotropy measurements for the complete data set.
+Figure~\ref{fig5} shows the permeability and anisotropy measurements for the complete data set.
 In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean and standard deviation of each quantity are shown, and the five different values of $M$ are shown by different colors.
-As seen in Figs.~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies.
+As seen in Figures~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies.
 That is, permeability monotonically decreases with the number of bodies and the error bars shows little overlap between different values of $M$ until very late in the simulation when the bodies have nearly vanished.
@@
 That is, given the error-bars, there is significant overlap in the signal of $\anis$ across different values of $M$.
-On notable feature is second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100.
-As before, the anisotropy can be decomposed into configuration and shape components as shown in Figs.~\ref{fig5}(d)--(e).
+One notable feature is a second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100.
+As before, the anisotropy can be decomposed into configuration and shape components as shown in Figures~\ref{fig5}(d)--(e).
 Here, we see the late surge in configurational anisotropy for these larger values of $M = $ 60, 80, 100.
@@
 
-Similar statistical analysis is performed on the tortuosity measurements and shown in Fig.~\ref{fig6}(a)--(b).
+Similar statistical analysis is performed on the tortuosity measurements and shown in Figure~\ref{fig6}(a)--(b).
 Much like before, the tortuosity measurements are well separated by the number of bodies, with the error bars showing little overlap across different values of $M$.
-Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, however, show similar behavior across different values of $M$, as seen in Fig.~\ref{fig6}(c).
+Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, however, show similar behavior across different values of $M$, as seen in Figure~\ref{fig6}(c).
 For nearly all runs, the tortuosity ratio increases as bodies erode up to a maximum of roughly $(T_2 -1)/(T_1 -1) = 8$, and then the tortuosity ratio decreases near the very end of the simulation.
-As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figs.~\ref{fig6}(d)--(e).
-The figure shows that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
+As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figures~\ref{fig6}(d)--(e).
+The shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
 
@@
 
-	The ratio of longitudinal to transverse permeability provides our main diagnostic of medium anisotropy.
-Measurements indicate that the anisotropy grows substantially as a result of fluid mechanical erosion, reaching a peak of roughly six in most simulations, before the bodies completely vanish and return the system to an isotropic state.
-The anisotropy can be further decomposed into a configurational component, due only to the relative positions of bodies, and a shape component, due to the detailed geometry of each body.
-Statistical analysis across a large number of simulations reveals that if the number of bodies is sufficiently large, $M \ge 60$, the configurational anisotropy surges near the final stages of erosion and surpasses the shape anisotropy as the primary contribution.
-This surge in configurational anisotropy is associated with the formation of visual channels that transmit a large portion of the flow.
-The tortuosity provides a second metric and also reveals strong anisotropy to develop across all simulations.
-The methodology could be extended to more complex scenarios of thermal convective flows in porous media \cite{McCurdy2019} or erodable porous structures formed by precipitation reactions \cite{eastham2020multiphase}.
-
-%though this metric shows less signal in the configurational contribution.
+The ratio of longitudinal to transverse permeability provides our main
+diagnostic of medium anisotropy. Measurements indicate that the
+anisotropy grows substantially as a result of fluid mechanical erosion,
+reaching a peak of roughly six in most simulations, before the bodies
+completely vanish and return the system to an isotropic state. The
+anisotropy can be further decomposed into a configurational component,
+due only to the relative positions of bodies, and a shape component, due
+to the detailed geometry of each body. Statistical analysis across a
+large number of simulations reveals that if the number of bodies is
+sufficiently large, $M \ge 60$, the configurational anisotropy surges
+near the final stages of erosion and surpasses the shape anisotropy as
+the primary contribution. This surge in configurational anisotropy is
+associated with the formation of visual channels that transmit a large
+portion of the flow. The tortuosity provides a second metric and also
+reveals strong anisotropy to develop across all simulations. The
+methodology could be extended to more complex scenarios of thermal
+convective flows in porous media~\cite{McCurdy2019}, erodable porous
+structures formed by precipitation
+reactions~\cite{eastham2020multiphase}, and first arrival statistics of
+Brownian particles~\cite{che-lin-her-qua2021}.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
fixed last typo
NM

@@
 b) The anisotropy of the medium increases as the bodies erode and preferentially allow flow in the longitudinal direction.
-The total anisotropy is the sum \todo[inline]{do you mean product} of configurational and shape components.
+The total anisotropy is the product of configurational and shape components.
 The shape contribution is larger throughout most of the simulation, but near the end of the simulation, the configurational contribution grows large as the channel-structure dominates.
@@
 % Data from 80-4
-%c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium.
-Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
 
@@
 As seen in Figure~\ref{fig3}(b), the shape anisotropy is the larger factor throughout the majority of the simulation, implying that the shape of individual grains plays a larger role than their relative positions.
-It is only during the last 10\% of the simulation that the configurational anisotropy grows significantly and surpasses the shape anisotropy.
+It is only during the last 20\% of the simulation that the configurational anisotropy grows significantly and surpasses the shape anisotropy.
 This relative growth of the configurational anisotropy corresponds to the strong channelization seen in the last panel of Figure~\ref{fig1}.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting large-scale features as well as small-scale ones, such as the microstructure of porous materials.
-Porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
+Porous media encountered in nature typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
 Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely by a factor of 5--20~\cite{bear1988dynamics, anderson2015applied}.
-Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plan of deposition~\cite{bear1988dynamics}.
+Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plane of deposition~\cite{bear1988dynamics}.
 Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work.
@@
 The more recent Cauchy reformulation of the BIE and the associated quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}.
-Though the governing fluid-flow equations (Stokes) are linear, the nonlinear feedback between evolving microstructure and flow give rise to highly complex and anisotropic configurations.
+Though the governing fluid-flow equations (Stokes) are linear, the nonlinear feedback between evolving microstructure and flow gives rise to highly complex and anisotropic configurations.
 
-Figure~\ref{fig1} shows an example simulation with 80 circular bodies of randomized sizes and positions immersed in a Stokes flow that moves from left to right.
-A plug flow is imposed on artificial walls to the left and right of each frame, and a no-slip boundary condition is imposed along the top and bottom of each frame.
-The color depicts the local speed of the flow intervening between bodies.
+Figure~\ref{fig1} shows an example simulation with 80 circular bodies of randomized sizes and positions immersed in a Stokes flow moving from left to right. 
+Color depicts the local speed of the flow intervening between bodies.
 Over time, individual bodies erode in response to the shear stresses induced on them, and heterogeneous material removal creates visible features both at the level of individual bodies and the larger-scale configuration.
@@
 
-% preferentially removing solid material, and further opening the channels. The positive feedback creates the channels that are clearly visible by in final two images.
-
-%Maybe cite: \cite{Rycroft2016}
+%A plug flow is imposed on artificial walls to the left and right of each frame, and a no-slip boundary condition is imposed along the top and bottom of each frame.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The outline of the paper is as follows.
-In Section~\ref{sec:formulation} we discuss the governing equations for the fluid flow and for interface evolution.
-In Section~\ref{sec:DLP} we discuss the numerical methods.
-In Section~\ref{sec:medium} we measure porous-medium properties, in particular permeability.
+In Section~\ref{sec:formulation} we discuss the governing equations for the fluid flow and interface evolution.
+In Section~\ref{sec:DLP} we discuss the numerical methods, including the Cauchy formulation of the BIE.
+In Section~\ref{sec:medium} we explain how to extract porous-medium properties, such permeability, anisotropy, and tortuosity.
 In Section~\ref{sec:results} we provide results and we conclude in Section~\ref{sec:conclusion}.
@@
 Cauchy integrals, while the vorticity only requires first-order
-derivatives.
+derivatives. On solid boundaries, the vorticity reduces to the shear stress given in \eqref{tau0} and needed in errosion law \eqref{Vn0} \cite{quaife2018boundary, chiu2020viscous}.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications~\cite{quaife2018boundary, chiu2020viscous}.
+Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications~\cite{quaife2018boundary, chiu2020viscous}.
 Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \end{align}
-where the last integral is interpreted in the principal value sense.
+where the last integral is interpreted in the principal-value sense.
 Here we are assuming that $\Omega$ is the bounded region interior to
@@
 
-% SNIPPET
-%This has the advantage that only the one-dimensional boundary of the domain must be discretized, and, with appropriate quadrature formulas and fast summation methods, the result is a high-fidelity numerical simulation with near-optimal computational complexity.
-
 %-----------------------------------------------------------------------------------------------%
@@
 
-With the flow and shear stresses computed, we seek to evolve the boundaries of erodable bodies.
-For numerical stability, we modify~\eqref{Vn0} to include a smoothing term that depends on local curvature $\kappa$, as in previous work~\cite{quaife2018boundary}
+With the flow computed, we extract the vorticity which reduces to shear stress, $\tau$, on solid boundaries.
+Next, we seek to evolve the boundaries of these erodable bodies.
+For numerical stability, we modify erosion law \eqref{Vn0} to include a smoothing term that depends on local curvature $\kappa$~\cite{quaife2018boundary}
 \begin{align}
@@
 \end{align}
-The last term is a smoothing term that has strength $\epsilon \ll 1$ and scales with spatial average of the shear stress $\langle\abs{\tau}\rangle$.
+The last term is a smoothing term that has strength $\epsilon \ll 1$ and scales with the spatial average of the shear stress $\langle\abs{\tau}\rangle$.
 $L$ indicates the total arc length of the body, and, inside the parenthesis, the mean curvature is subtracted so that this term preserves area.
-As such, the only source of material loss is the first term, $\CE \, \abs{\tau}$, which represents the shear-dependent erosion law.
+As such, the only source of material loss is the first term, $\CE \, \abs{\tau}$, representing the shear-dependent erosion law \eqref{Vn0}.
 In addition, we apply a narrow Gaussian filter to the distribution $\abs{\tau}$ to further improve stability.
@@
 In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second-order in time~\cite{quaife2018boundary}.
-
-% COPIED STRAIGHT FROM JFM 2020
-%We use the time stepping method outlined in our previous work~\citep[see][section 3.3]{qua-moo2018} which we briefly summarize here.
-The erosion rate loses differentiability if the shear stress changes sign, and this leads to corners developing on $\gamma$ and numerical instabilities.
-Therefore, we modify the erosion rate, $V_\nn$ in equation~\eqref{eqn:erosionModel}, with
-%\begin{align}
-% \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(\frac{L}{2\pi} \kappa - 1 \right),
-%\end{align}
-%where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average, $L$ is the length of $\gamma$, and $\kappa$ is the curvature of $\gamma$.
-The new erosion model penalizes regions of high curvature, but does not change the total length of each body.
-Moreover, to increase the overall stability of the method, a narrow Gaussian filter is applied to the erosion rate at each time step.
-
-%Rather than tracking the $(x,y)$ coordinates, the {\thL} coordinates are tracked.
-In addition, tangential velocity fields are used to maintain an equispaced discretization.
-Time stepping is performed with a second-order Implicit-Explicit Runge-Kutta method.
-In particular, the diffusive term corresponding to the curvature penalization term is discretized implicitly, and all other terms, which are non-stiff, are treated explicitly.
-By using this time stepping method in conjunction with the Barycentric rule, we stably evolve the eroding bodies.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 of streamlines passing through the region $[-1,1] \times [-1,1]$. In
-particular, for a particular eroded geometry with velocity field $\uu$,
+particular, for a partially-eroded configuration of bodies with velocity field $\uu$,
 we calculate streamlines $\pp(t)$ that satisfy
@@
 With the numerical methods in place, we now present results on how fluid-mechanical erosion alters porous-media properties over time.
-We first discuss the results from a single simulation and then generalize to statistical results from ensembles of simulations.
+We first discuss the results from a single simulation and then generalize to statistical analysis of ensembles of simulations.
 
@@
 As given in~\eqref{eq:anis}, the ratio of longitudinal to transverse permeability defines the anisotropy of the medium, $\anis = k_{11} / k_{22}$, which is plotted in Figure~\ref{fig3}(b) over the course of the simulation (solid curve).
-Early in the simulation the anisotropy is nearly one, as the initial configuration of randomly placed circles has no preferred flow direction.
+Early on, the anisotropy is nearly one, as the initial configuration of randomly placed circles has no preferred flow direction.
 The anisotropy then increases as heterogeneous rates of erosion promote longitudinal flow over transverse flow.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The previous section shows many intriguing features to arise as a randomly initialized configuration of solid bodies erodes.
-These observations natural raise the question: are the trends specific to the particular initializing chosen or do are they general features that emerge robustly?
+These observations natural raise the question: are the trends specific to the particular simulation shown or do these features emerge robustly across different simulations?
 To answer this question, we now analyze the same quantities---permeability, tortuosity, and anisotropy---over an ensemble of many simulations having different numbers of bodies and different random initializations.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
@@
 
-The previous section shows many intriguing features to arise as a randomly initialized configuration of solid bodies erodes.
-These observations natural raise the question: are the trends specific to the particular initializing chosen or do are they general features that emerge robustly?
+The previous section shows intriguing features to arise from the erosion of a random initialization of solid bodies.
+The observations natural raise the question: are the trends specific to the particular simulation shown or do these features emerge robustly across different simulations?
 To answer this question, we now analyze the same quantities---permeability, tortuosity, and anisotropy---over an ensemble of many simulations having different numbers of bodies and different random initializations.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 Figure~\ref{fig5} shows the permeability and anisotropy measurements for the complete data set.
-In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean and standard deviation of each quantity are shown, and the five different values of $M$ are shown by different colors.
+In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean and standard deviation of each quantity are shown, with different values of $M$ shown by different colors.
 As seen in Figures~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies.
@@
 Similar statistical analysis is performed on the tortuosity measurements and shown in Figure~\ref{fig6}(a)--(b).
-Much like before, the tortuosity measurements are well separated by the number of bodies, with the error bars showing little overlap across different values of $M$.
-Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, however, show similar behavior across different values of $M$, as seen in Figure~\ref{fig6}(c).
-For nearly all runs, the tortuosity ratio increases as bodies erode up to a maximum of roughly $(T_2 -1)/(T_1 -1) = 8$, and then the tortuosity ratio decreases near the very end of the simulation.
+In all simulations, the longitudinal tortuosity decreases with time as erosion allows passive tracers to take more direct paths when traveling in the flow direction.
+In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity can increase with time, as passive tracers must work to circumvent horizontally aligned bodies when traveling in the vertical direction.
+Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$ show similar behavior across different values of $M$, as seen in Figure~\ref{fig6}(c).
+For nearly all runs, the tortuosity ratio increases as bodies erode, and maximum ratio of roughly $(T_2 -1)/(T_1 -1) = 8$ is reached.
+Finally, the tortuosity ratio decreases near the very end of the simulation.
 As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figures~\ref{fig6}(d)--(e).

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies and statistical analysis across an ensemble of different initializations.
-By linking the governing Stokes equation to Darcy's law, we are able to extract porous media properties, including permeability, resistivity, tortuosity, and anisotropy, as they evolve over time.
-Direct comparison of resistivity with the total drag force confirms such bulk properties are extracted with high accuracy.
+By linking the governing Stokes equations to Darcy's law, we are able to extract porous media properties, including permeability, resistivity, tortuosity, and anisotropy, as they evolve over time.
+Direct comparison between the resistivity and the total drag force confirms such bulk properties are extracted with high accuracy.
 
-The ratio of longitudinal to transverse permeability provides our main
-diagnostic of medium anisotropy. Measurements indicate that the
-anisotropy grows substantially as a result of fluid mechanical erosion,
-reaching a peak of roughly six in most simulations, before the bodies
-completely vanish and return the system to an isotropic state. The
-anisotropy can be further decomposed into a configurational component,
-due only to the relative positions of bodies, and a shape component, due
-to the detailed geometry of each body. Statistical analysis across a
-large number of simulations reveals that if the number of bodies is
-sufficiently large, $M \ge 60$, the configurational anisotropy surges
-near the final stages of erosion and surpasses the shape anisotropy as
-the primary contribution. This surge in configurational anisotropy is
-associated with the formation of visual channels that transmit a large
-portion of the flow. The tortuosity provides a second metric and also
-reveals strong anisotropy to develop across all simulations. The
-methodology could be extended to more complex scenarios of thermal
-convective flows in porous media~\cite{McCurdy2019}, erodable porous
-structures formed by precipitation
-reactions~\cite{eastham2020multiphase}, and first arrival statistics of
-Brownian particles~\cite{che-lin-her-qua2021}.
+The ratio of longitudinal to transverse permeability provides our main diagnostic of medium anisotropy.
+Measurements indicate that the anisotropy grows substantially as a result of fluid-mechanical erosion, reaching a peak of roughly six in most simulations, before the bodies completely vanish and return the system to an isotropic state.
+The anisotropy can be further decomposed into a configurational component, due only to the relative positions of bodies, and a shape component, due to the detailed geometry of each body.
+Statistical analysis across a large number of simulations reveals that if the number of bodies is sufficiently large, $M \ge 60$, the configurational anisotropy surges near the final stages of erosion and surpasses the shape anisotropy as the primary contribution.
+This surge in configurational anisotropy is associated with the formation of visual channels that transmit a large portion of the flow.
+The tortuosity provides a second metric and also reveals strong anisotropy to develop across all simulations.
+The methodology could be extended to more complex scenarios of thermal convective flows in porous media~\cite{McCurdy2019}, erodable porous structures formed by precipitation reactions~\cite{eastham2020multiphase}, and first arrival statistics of Brownian particles~\cite{che-lin-her-qua2021}.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
N<

@@
 In all simulations, the longitudinal tortuosity decreases with time as erosion allows passive tracers to take more direct paths when traveling in the flow direction.
-In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity can increase with time, as passive tracers must work to circumvent horizontally aligned bodies when traveling in the vertical direction.
-Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$ show similar behavior across different values of $M$, as seen in Figure~\ref{fig6}(c).
-For nearly all runs, the tortuosity ratio increases as bodies erode, and maximum ratio of roughly $(T_2 -1)/(T_1 -1) = 8$ is reached.
-Finally, the tortuosity ratio decreases near the very end of the simulation.
+In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity can increase with time, as vertically-traveling passive tracers must work to circumvent horizontally aligned bodies carved by erosion.
+
+The tortuosity ratio, $(T_2 -1)/(T_1 -1)$, provides a second proxy for medium anisotropy to complement the permeability measurements.
+Figure~\ref{fig6}(c) shows that the tortuosity ratio behaves similarly across different values of $M$.
+The ratio increases substantially with erosion, reaching a peak of roughly $(T_2 -1)/(T_1 -1) = 8$, before descending during the final stages of erosion.
 As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figures~\ref{fig6}(d)--(e).
-The shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
+Here, we see that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
+This observation fits with the intuition that the main hindrance to a passive tracer should be the shape of individual obstructions, rather than how those obstructions are arranged relative to one another.
+As such, the tortuosity ratio is a less sensitive indicator of channelization than is the permeability ratio.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \caption{
-Tortuosity statistics from an ensemble of simulations.
-(a)--(b) The longitudinal (a) and transverse tortuosity measurements are well grouped with respect to the number of bodies.
+Tortuosity statistics from an ensemble of simulations. (a) \nick{WRITE STUFF}
 (c)--(e) Statistics of the ratio, $(T_2 -1)/(T_1 -1)$, including its configurational and shape contribution.
@@
 %---------------------------------------------------------%
+
+%(a)--(b) The longitudinal (a) and transverse (b) tortuosity measurements are well grouped with respect to the number of bodies.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The late emergence of substantial configurational anisotropy may seem
-like a spurious effect that is particular to the one simulation shown in
+like a spurious effect that is particular to the simulation shown in
 Figure~\ref{fig3}. However, statistical analysis of many simulations will show this feature to emerge robustly in simulations featuring a relatively large number of bodies $M \ge 60$.
@@
 (a)--(b) Measurements of the longitudinal (a) and transverse (b) permeability are well separated with respect to the number of bodies, $M$.
-For each $M$, the mean and standard deviation of permeability are shown for increasing porosity (or time).
+For each $M$, the mean and standard deviation of permeability are shown against increasing porosity (or time).
 (c) In all runs, the anisotropy grows substantially and reaches a maximum value of roughly 4--6.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 significantly larger than $T_1$, indicating that passive tracers must
-follow more tortuous paths when traveling transversely and that
-longitudinal paths are more direct. The ratio $(T_2-1)/(T_1-1)$ provides
+follow more tortuous paths when traveling transversely compared to longitudinally. The ratio $(T_2-1)/(T_1-1)$ provides
 a second measure of anisotropy to complement the permeability-dependent
 quantity. We have chosen to subtract one in parenthesis so that both
-numerator and denominator vanish when no bodies are present, as
+numerator and denominator both vanish when no bodies are present, as
 analogous to resistivity.
@@
 Figure~\ref{fig5} shows the permeability and anisotropy measurements for the complete data set.
-In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean and standard deviation of each quantity are shown, with different values of $M$ shown by different colors.
+In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean of each quantity (permeability or anisotropy) is shown with the vertical error bars representing the standard deviation.
+Different initial numbers of bodies, $M$, are shown by different colors.
 As seen in Figures~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 As seen in Figures~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies.
-That is, permeability monotonically decreases with the number of bodies and the error bars shows little overlap between different values of $M$ until very late in the simulation when the bodies have nearly vanished.
+That is, permeability monotonically decreases with the number of bodies and the error bars shows little overlap between different values of $M$, until very late in the simulation when the bodies have nearly vanished.
 
 	Figure~\ref{fig5}(c) shows the corresponding statistics of anisotropy, $\anis$.
-Here, the anisotropy is not as well separated by $M$.
+Notice that the anisotropy is not as well separated by $M$.
 That is, given the error-bars, there is significant overlap in the signal of $\anis$ across different values of $M$.
-One notable feature is a second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100.
-As before, the anisotropy can be decomposed into configuration and shape components as shown in Figures~\ref{fig5}(d)--(e).
-Here, we see the late surge in configurational anisotropy for these larger values of $M = $ 60, 80, 100.
-For these runs with a large number of bodies, the latest stages of erosion are dominated by channelization which substantially promotes the configurational anisotropy.
+For all values of $M$, the anisotropy initially increases and reaches a peak of roughly $\anis \approx 4$.
+Interestingly, for the runs featuring a large number of bodies $M = 60, 80, 100$, there is a second rise in anisotropy that occurs late in the simulation and results in a higher peak of roughly $\anis \approx 6$.
+Thus, the late surge of anisotropy, first observed in Fig.~\ref{fig3}, is not specific to that particular simulation.
+Rather, it occurs robustly across all simulations as long as the initial number of bodies is sufficiently large, $M \ge 60$.
+
+ 	As before, the anisotropy can be decomposed into configuration and shape components, and statistics of these quantities are shown in Figs.~\ref{fig5}(d)--(e).
+Most notably, the configurational anisotropy is seen to surge late in the erosion process in all of the simulations featuring a high body count, $M \ge 60$, suggesting the previously observed second rise in total anisotropy is due to the configurational component.
+
+HERE
+
+For these high-body count runs, the latest stages of erosion are dominated by channelization which substantially promotes the configurational anisotropy.
 The shape anisotropy, meanwhile, takes a more regular, parabolic form that is relatively insensitive to the number of bodies.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
@@
 The previous section shows intriguing features to arise from the erosion of a random initialization of solid bodies.
-The observations natural raise the question: are the trends specific to the particular simulation shown or do these features emerge robustly across different simulations?
-To answer this question, we now analyze the same quantities---permeability, tortuosity, and anisotropy---over an ensemble of many simulations having different numbers of bodies and different random initializations.
+The observations natural raise the question: are the trends specific to the particular simulation shown or do these features emerge robustly across different initial conditions?
+To answer this question, we now analyze the same quantities---permeability, tortuosity, and anisotropy---over an ensemble of simulations having different numbers of bodies and different random initializations.
 We analyze runs having $M$ = 20, 40, 60, 80, and 100 bodies, with at least three different instances of each.
@@
 Figure~\ref{fig5} shows the permeability and anisotropy measurements for the complete data set.
-In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean of each quantity (permeability or anisotropy) is shown with the vertical error bars representing the standard deviation.
+In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean of each quantity (permeability or anisotropy) is plotted against increasing porosity, with the standard deviation across the runs shown by the vertical error bars.
 Different initial numbers of bodies, $M$, are shown by different colors.
@@
 	Figure~\ref{fig5}(c) shows the corresponding statistics of anisotropy, $\anis$.
-Here, the anisotropy is not as well separated by $M$.
+Notice that the anisotropy is not as well separated by $M$.
 That is, given the error-bars, there is significant overlap in the signal of $\anis$ across different values of $M$.
-One notable feature is a second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100.
-As before, the anisotropy can be decomposed into configuration and shape components as shown in Figures~\ref{fig5}(d)--(e).
-Here, we see the late surge in configurational anisotropy for these larger values of $M = $ 60, 80, 100.
-For these runs with a large number of bodies, the latest stages of erosion are dominated by channelization which substantially promotes the configurational anisotropy.
-The shape anisotropy, meanwhile, takes a more regular, parabolic form that is relatively insensitive to the number of bodies.
+For all values of $M$, the anisotropy initially increases and reaches a peak of roughly $\anis \approx 4$.
+Interestingly, for the runs featuring a large number of bodies ($M$ = 60, 80, and 100) there is a second rise in anisotropy that occurs late in the simulation and results in a higher peak of roughly $\anis \approx 6$.
+Thus, the late surge of anisotropy, first observed in Fig.~\ref{fig3}, is not specific to that particular simulation.
+Rather, it occurs robustly across all simulations as long as the initial number of bodies is sufficiently large, $M \ge 60$.
+
+ 	As before, the anisotropy can be decomposed into configuration and shape components, $\anis_C$ and $\anis_S$ respectively, and the statistics of these quantities are shown in Figs.~\ref{fig5}(d)--(e).
+The shape anisotropy, seen in Fig.~\ref{fig5}(e), takes a fairly regular, parabolic arc --- first increasing due to the shapes carved by erosion and then decreasing as the bodies vanish.
+This behavior is consistent across all of the values of $M$.
+The configurational anisotropy (Fig.~\ref{fig5}(d)), however, shows less regular behavior.
+For runs with a smaller number of bodies ($M$ = 20 and 40) the configurational anisotropy remains relatively small throughout the entire simulation, indicating that the majority of observed anisotropy is due to the individual shapes of bodies.
+For the runs with a higher body count ($M $ = 60, 80, and 100), though, the configurational anisotropy grows moderately and then surges late in the simulation, as was observed in the single 80-body simulation from Fig.~\ref{fig3}.
+Since the shape anisotropy is decreasing at this time, the observed second rise in the total anisotropy is due entirely to this surge in configurational component.
+For these high-body count runs, the latest stages of erosion are dominated by channelization, which substantially promotes the configurational anisotropy over shape anisotropy.
+That is, the large-scale arrangement of the bodies has greater effect than the shape of individual bodies at this late stage.
 
@@
 
-%(a)--(b) The longitudinal (a) and transverse (b) tortuosity measurements are well grouped with respect to the number of bodies.
+We show in Figs.~\ref{fig6}(a)--(b) similar statistical analysis performed on the longitudinal and transverse tortuosity measurements, $T_1$ and $T_2$.
+Figure~\ref{fig6}(a) shows that, in all simulations, the longitudinal tortuosity decreases with time as erosion allows passive tracers to take more direct paths when traveling in the flow direction.
+In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity increases with time, as vertically-traveling passive tracers must work to circumvent the horizontally aligned bodies carved by erosion.
 
-Similar statistical analysis is performed on the tortuosity measurements and shown in Figure~\ref{fig6}(a)--(b).
-In all simulations, the longitudinal tortuosity decreases with time as erosion allows passive tracers to take more direct paths when traveling in the flow direction.
-In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity can increase with time, as vertically-traveling passive tracers must work to circumvent horizontally aligned bodies carved by erosion.
-
-The tortuosity ratio, $(T_2 -1)/(T_1 -1)$, provides a second proxy for medium anisotropy to complement the permeability measurements.
-Figure~\ref{fig6}(c) shows that the tortuosity ratio behaves similarly across different values of $M$.
-The ratio increases substantially with erosion, reaching a peak of roughly $(T_2 -1)/(T_1 -1) = 8$, before descending during the final stages of erosion.
+As before, the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, provides a second proxy for medium anisotropy to complement the permeability-based quantity.
+Figure~\ref{fig6}(c) shows that the tortuosity ratio behaves similarly across all simulations and all different values of $M$.
+The ratio increases substantially with erosion, reaching a peak of roughly $(T_2 -1)/(T_1 -1) \approx 8$, before descending during the final stages of erosion.
 As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figures~\ref{fig6}(d)--(e).
-Here, we see that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
+Here, we see that the shape component is the main contribution and the configurational component remains minimal.
 This observation fits with the intuition that the main hindrance to a passive tracer should be the shape of individual obstructions, rather than how those obstructions are arranged relative to one another.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 Also shown are the measurements for the configurations of circles.
-b) The ratio $(T_2-1)/(T_1-1)$ serves as a counterpart to the anisotropy.
+b) The ratio $(T_2-1)/(T_1-1)$ serves as a second proxy for anisotropy.
 Like anisotropy, this ratio grows large over the course of erosion.
@@
 For each $M$, the mean and standard deviation of permeability are shown against increasing porosity (or time).
-(c) In all runs, the anisotropy grows substantially and reaches a maximum value of roughly 4--6.
+(c) The same statistics for anisotropy.
+In all runs, the anisotropy grows substantially and reaches a maximum value of roughly 4--6.
 Runs with a large number of bodies ($M$ = 60, 80, or 100) show a second surge in anisotropy near the end of the simulation.
 (d)--(e) The configurational and shape contributions of anisotropy.
-While the shape anisotropy varies fairly regularly with time across all runs, the configurational anisotropy shows a distinct peak late in the simulation for runs with large $M$.
+While the shape anisotropy varies fairly regularly across all runs, the configurational anisotropy shows a distinct peak late in the simulation for runs with large $M$.
 \label{fig5}
@@
 \caption{
-Tortuosity statistics from an ensemble of simulations. (a) \nick{WRITE STUFF}
+Tortuosity statistics from an ensemble of simulations.
+(a) The longitudinal tortuosity decreases monotonically with time across all simulations as erosion allows particles to take more direct paths when traveling in the flow direction.
+(b) The transverse turtuosity initially increases with time as vertically traveling particles are forced to navigate the horizontally aligned shapes carved by erosion.
 (c)--(e) Statistics of the ratio, $(T_2 -1)/(T_1 -1)$, including its configurational and shape contribution.
+While the tortuosity ratio reaches a high peak, it is a less sensitive indicator of configurational changes such as channel formation.
 \label{fig6}
@@
 Figure~\ref{fig6}(a) shows that, in all simulations, the longitudinal tortuosity decreases with time as erosion allows passive tracers to take more direct paths when traveling in the flow direction.
-In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity increases with time, as vertically-traveling passive tracers must work to circumvent the horizontally aligned bodies carved by erosion.
+In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity increases with time, as vertically-traveling passive tracers must circumvent the horizontally aligned bodies carved by erosion.
 
-As before, the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, provides a second proxy for medium anisotropy to complement the permeability-based quantity.
+As before, the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, provides a second proxy for medium anisotropy to complement the permeability-based definition.
 Figure~\ref{fig6}(c) shows that the tortuosity ratio behaves similarly across all simulations and all different values of $M$.
@@
 This observation fits with the intuition that the main hindrance to a passive tracer should be the shape of individual obstructions, rather than how those obstructions are arranged relative to one another.
-As such, the tortuosity ratio is a less sensitive indicator of channelization than is the permeability ratio.
+As such, the tortuosity ratio is a less sensitive indicator of channelization seen to develop late in the erosion simulations.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies and statistical analysis across an ensemble of different initializations.
-By linking the governing Stokes equations to Darcy's law, we are able to extract porous media properties, including permeability, resistivity, tortuosity, and anisotropy, as they evolve over time.
+By linking the governing Stokes equations to Darcy's law, we are able to extract porous-media properties, including permeability, resistivity, tortuosity, and anisotropy, as they evolve over time.
 Direct comparison between the resistivity and the total drag force confirms such bulk properties are extracted with high accuracy.

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
-their derivatives, the accuracy of the method depends on the accuracy of
-computing a general Cauchy integral
+their derivatives, the overall accuracy hinges on the computation of a general Cauchy integral
 \begin{align}
@@
 
-The previous section shows intriguing features to arise from the erosion of a random initialization of solid bodies.
+The previous section shows intriguing features to arise from the erosion of a single, random initialization of solid bodies.
 The observations natural raise the question: are the trends specific to the particular simulation shown or do these features emerge robustly across different initial conditions?
@@
 For the runs with a higher body count ($M $ = 60, 80, and 100), though, the configurational anisotropy grows moderately and then surges late in the simulation, as was observed in the single 80-body simulation from Fig.~\ref{fig3}.
-Since the shape anisotropy is decreasing at this time, the observed second rise in the total anisotropy is due entirely to this surge in configurational component.
+Since the shape anisotropy is decreasing at this time, the observed second rise in the total anisotropy is due entirely to this surge in the configurational component.
 For these high-body count runs, the latest stages of erosion are dominated by channelization, which substantially promotes the configurational anisotropy over shape anisotropy.
-That is, the large-scale arrangement of the bodies has greater effect than the shape of individual bodies at this late stage.
+That is, the large-scale arrangement of the bodies has greater effect than the shape of individual bodies.
 
@@
 This observation fits with the intuition that the main hindrance to a passive tracer should be the shape of individual obstructions, rather than how those obstructions are arranged relative to one another.
-As such, the tortuosity ratio is a less sensitive indicator of channelization seen to develop late in the erosion simulations.
+As such, the tortuosity ratio is a less sensitive indicator of the channelization seen to develop late in the erosion simulations.
 
@@
 
-In this paper, we have presented a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow.
+In this paper, we have presented a Cauchy formulation of the boundary integral equations to simulate the fluid-mechanical erosion of many bodies in a Stokes flow.
 The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies and statistical analysis across an ensemble of different initializations.
@@
 The tortuosity provides a second metric and also reveals strong anisotropy to develop across all simulations.
-The methodology could be extended to more complex scenarios of thermal convective flows in porous media~\cite{McCurdy2019}, erodable porous structures formed by precipitation reactions~\cite{eastham2020multiphase}, and first arrival statistics of Brownian particles~\cite{che-lin-her-qua2021}.
+In the future, we hope to extend the methodology to more complex scenarios of thermal convective flows in porous media~\cite{McCurdy2019}, erodable porous structures formed by precipitation reactions~\cite{eastham2020multiphase}, and first arrival statistics of Brownian particles~\cite{che-lin-her-qua2021}.
 

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \subsection{Quadrature for Cauchy integrals}
-The accuracy of our method is determined by the accuracy of the
+The overall accuracy of our method is determined by the
 quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
@@
 equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
-the ratio is bounded independent of $x$.
+the ratio is also bounded independent of $x$.
 
 The derivatives of the Cauchy integral in~\eqref{eqn:cauchy} can be
-approximated with a uniformly spectral error using similar quadrature
+approximated with spectral accuracy, uniformly in $x$, using similar quadrature
 rules. To summarize, for $x \in \Omega$, 

### 2022-10-13 docs/proposals/NSF/budgets/budgetJust_Colgate.tex
NM

--- 2020-08-26 docs/proposals/NSF/budgets/budgetJustUSNA.tex
@@
 The requested senior personnel funding is to support one month of 
-co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
+co-PI Moore's summer salary in year 3. During this period, the PIs
 will work together to develop and implement algorithms, write papers,
 and work closely with the graduate student. 
-Co-PI Moore's salary will in years 1,2,3 will be USNA Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
+Co-PI Moore's summer salary will in year 3 will be \$93,788.
+with the monthly salary listed in the table:
 %\hfill \\
 \begin{center}
-  \begin{tabular}{|c|r|r|r|r|}
+  \begin{tabular}{|c|r|r|}
     \hline
-    & Year 1 & Year 2 & Year 3  & Total \\
+    & Year 3  & Total \\
     \hline
-    co-PI Moore & $\$9,585$ & $\$9,762$ & $\$9,977$  & $\$29,324$ \\
+    co-PI Moore & $\$10,421$  & $\$10,421$ \\
     \hline
@@
 \subsection*{C: Fringe Benefits}
-The fringe benefits of co-PI Moore at USNA are 34\%. 
-In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
+The fringe benefits of co-PI Moore at Colgate University are 32\%.  \\
+%In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
 %\hfill \\
 \begin{center}
-  \begin{tabular}{|c|r|r|r|r|}
+  \begin{tabular}{|c|r|r|}
     \hline
-    & Year 1 & Year 2 & Year 3 & Total \\
+    & Year 3 & Total \\
     \hline
-    co-PI Moore Fringe & $\$3,259$ & $\$3,319$ & $\$3,392$ & $\$9,970$ \\
+    co-PI Moore Fringe & $\$3,335$ & $\$3,335$ \\
     \hline
-    co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
+    %co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
     \hline
-    Total & $\$3,547$ & $\$3,612$ & $\$3,691$ & $\$10,850$ \\
+    Total & $\$3,335$ & $\$3,335$ \\
     \hline
@@
 The requested travel funds is to partially fund a domestic trip
-for co-PI Moore in years 2 and 3.  The expected costs per
+for co-PI Moore in year 3.  The expected costs per
 conference participant is $\$1,000$ with a breakdown of $\$300$ for
@@
 these travel funds to visit PI Quaife and the funded graduate student at
-FSU in order to collaborate on the project.  Travel funds for the first
-year are removed due to the COVID crisis.
+FSU in order to collaborate on the project.
 %\hfill \\
@@
     \hline
-    & Year 1 & Year 2 & Year 3 & Total \\
+    & Year 3 & Total \\
     \hline
-    Domestic Travel &  & $\$1,000$ & $\$1,000$ & $\$2,000$ \\
+    Domestic Travel & $\$1,000$ & $\$1,000$ \\
     \hline
@@
     \hline
-    Year 1 & Year 2 & Year 3 & Total \\
+    Year 3 & Total \\
     \hline
-    $\$13,132$ & $\$14,374$ & $\$14,668$ & $\$42,174$ \\
+    $\$14,756$ & $\$14,756$ \\
     \hline
@@
 %\noindent
-The US Naval Academy's indirect cost rate is 10\% for research on
-modified total direct costs (MTDC).  The base for overhead is
-$\$13,132$ in year 1, $\$14,374$ in year 2, and $\$14,668$ in
-year 3.  The US Naval Academy defines a fiscal year to be July 1-June
-30.
+Colgate University's indirect cost rate is 35\% for research on
+modified total direct costs (MTDC).  The base for overhead is $\$14,756$ in
+year 3.  
+%The US Naval Academy defines a fiscal year to be October 1-September 30.
 %\hfill \\
@@
     \hline
-    Year 1 & Year 2 & Year 3 & Total \\
+    Year 3 & Total \\
     \hline
-    $\$1,313$ & $\$1,437$ & $\$1,467$ & $\$4,217$ \\
+    $\$5,165$ & $\$5,165$ \\
     \hline
@@
     \hline
-    Year 1 & Year 2 & Year 3 & Total \\
+    Year 3 & Total \\
     \hline
-    $\$14,445$ & $\$15,811$ & $\$16,135$ & $\$46,391$ \\
+    $\$19,921$ & $\$19,921$ \\
     \hline

### 2022-11-30 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \begin{abstract}
-Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion a porous medium comprised of up to 100 solid bodies embedded in a Stokes flow.
+Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion of a porous medium comprised of up to 100 solid bodies embedded in a Stokes flow.
 The grains of the medium are resolved individually and erode under the action of surface shear stress.
@@
 
-By conservations of mass, the average of the horizontal discharge, $q_1$, over any vertical cross-section must equal the uniform flow rate $U$ imposed at the inlet and outlet.
+By conservation of mass, the average of the horizontal discharge, $q_1$, over any vertical cross-section must equal the uniform flow rate $U$ imposed at the inlet and outlet.
 That is, for any location $x_0$,
@@
 
+%-----------------------------------------------------------------------------------------------%
+\section*{Acknowledgements}
+N.J.M., J.C., and B.D.Q. recognize the support of NSF Grant DMS-2012560
+%-----------------------------------------------------------------------------------------------%
+
 \bibliographystyle{plain}

### 2022-11-30 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 First, the shear stresses could carve each individual body into a more slender form, thus creating anisotropy at the level of individual grains.
-Second, the shear stressed could preferentially remove certain bodies before others, thus creating large-scale anisotropy.
+Second, the shear stresses could preferentially remove certain bodies before others, thus creating large-scale anisotropy.
 For example, a body positioned in a high-throughput channel might disintegrate relatively quickly, thus opening the channel and creating higher overall anisotropy.
@@
 
-As a second way to quantify medium anisotropy, we measure the
-tortuosity, $T_1$ and $T_2$, in the longitudinal and transverse
-directions respectively. Figure~\ref{fig4}(a), shows how both vary over
-the course of the simulation. As the bodies erode, $T_2$ grows
-significantly larger than $T_1$, indicating that passive tracers must
-follow more tortuous paths when traveling transversely compared to longitudinally. The ratio $(T_2-1)/(T_1-1)$ provides
-a second measure of anisotropy to complement the permeability-dependent
-quantity. We have chosen to subtract one in parenthesis so that both
-numerator and denominator both vanish when no bodies are present, as
-analogous to resistivity.
+As a second way to quantify medium anisotropy, we measure the tortuosity, $T_1$ and $T_2$, in the longitudinal and transverse directions respectively.
+Figure~\ref{fig4}(a), shows how both vary over the course of the simulation.
+As the bodies erode, $T_2$ grows significantly larger than $T_1$, indicating that passive tracers must
+follow more tortuous paths when traveling transversely compared to longitudinally.
+The ratio $(T_2-1)/(T_1-1)$ provides a second measure of anisotropy to complement the permeability-dependent quantity.
+We have chosen to subtract one in parenthesis so that the numerator and denominator both vanish when no bodies are present, as analogous to resistivity.
 As seen in Figure~\ref{fig4}(b), the ratio $(T_2-1)/(T_1-1)$ grows significantly during erosion, up to a peak of nearly 8.
@@
 The previous section shows intriguing features to arise from the erosion of a single, random initialization of solid bodies.
-The observations natural raise the question: are the trends specific to the particular simulation shown or do these features emerge robustly across different initial conditions?
+The observations naturally raise the question: are the trends specific to the particular simulation shown or do these features emerge robustly across different initial conditions?
 To answer this question, we now analyze the same quantities---permeability, tortuosity, and anisotropy---over an ensemble of simulations having different numbers of bodies and different random initializations.

### 2022-12-01 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \newcommand{\nick}[1]{ {\color{red} #1} }
+\newcommand{\edit}[1]{ {\color{red} #1} }
+
 % For real and imaginary, could use \Re or \Im, or \mathcal{R}, or \text{Re}
@@
 \begin{abstract}
-Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion of a porous medium comprised of up to 100 solid bodies embedded in a Stokes flow.
+Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion of a porous medium comprised of up to 100 solid bodies embedded in a \edit{two-dimensional} Stokes flow.
 The grains of the medium are resolved individually and erode under the action of surface shear stress.
@@
 
-Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications~\cite{quaife2018boundary, chiu2020viscous}.
+Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in \edit{two-dimensional Stokes flows.
+We employ the Stokes equations because it is the regime relevant for groundwater applications~\cite{quaife2018boundary, chiu2020viscous}}.
 Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
 The more recent Cauchy reformulation of the BIE and the associated quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}.
-Though the governing fluid-flow equations (Stokes) are linear, the nonlinear feedback between evolving microstructure and flow gives rise to highly complex and anisotropic configurations.
+Though the governing Stokes equations are linear, the nonlinear feedback between evolving microstructure and flow gives rise to highly complex and anisotropic configurations.
 
@@
 \begin{align}
-\Vn = \CE \, \abs{\tau}, 
-	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em erosion model}, 
+\Vn &= \CE \, \abs{\tau}, 
+	\hspace{88pt} \xx \in \gamma, &&\mbox{\em erosion model}, 
 \label{Vn0} \\
-\tau = -\mu \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss,
-	&\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
+\tau &= -\mu \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss,
+	\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
 \label{tau0}
@@
 where $\nn$ is the unit normal vector pointing into each body, $\ss$ is the unit tangent vector pointing in the counterclockwise direction, and $\CE$ is a material-dependent erosion constant.
-
-% SNIPPETS 
-%The strength of $\UU$ is adjusted at each time step to achieve a constant pressure drop across the channel, motivated by the geological situation of a porous medium connecting two regions of  fixed hydraulic heads.
-
-%to transition to the more complex flow intervening between the bodies.
+\edit{For numerical stability, we will modify this law in Section \ref{sec:int_evo} to include a smoothing term that depends on the local curvature of each body.}
 
@@
 \subsection{Interface evolution}
+\label{sec:int_evo}
 %-----------------------------------------------------------------------------------------------%
@@
 
-The late emergence of substantial configurational anisotropy may seem
-like a spurious effect that is particular to the simulation shown in
-Figure~\ref{fig3}. However, statistical analysis of many simulations will show this feature to emerge robustly in simulations featuring a relatively large number of bodies $M \ge 60$.
+The late emergence of substantial configurational anisotropy may seem like a spurious effect that is particular to the simulation shown in Figure~\ref{fig3}. 
+\edit{The statistical analysis presented in Section \ref{sec:stat_sims}, however, reveals this feature to emerge robustly across many simulations as long as the number of bodies is relatively large, $M \ge 60$.}
 
@@
 \subsection{Statistics of ensembles of simulations}
+\label{sec:stat_sims}
 

### 2022-12-02 docs/PhysicsPaper/StokesErosion.tex
working on revisions

@@
 \usepackage{todonotes, comment, soul, float}
+\usepackage[title]{appendix}
+
 %---------------------------------------------------%
@@
 \newcommand{\nick}[1]{ {\color{red} #1} }
-\newcommand{\edit}[1]{ {\color{red} #1} }
+\newcommand{\edit}[1]{{\color{red} #1}}
 
@@
 
-The outline of the paper is as follows.
-In Section~\ref{sec:formulation} we discuss the governing equations for the fluid flow and interface evolution.
-In Section~\ref{sec:DLP} we discuss the numerical methods, including the Cauchy formulation of the BIE.
+The outline of the paper is as follows. In Section~\ref{sec:formulation}
+we discuss the governing equations for the fluid flow and interface
+evolution.
+In Section~\ref{sec:numerics} we discuss the numerical methods, including the Cauchy formulation of the BIE.
 In Section~\ref{sec:medium} we explain how to extract porous-medium properties, such permeability, anisotropy, and tortuosity.
@@
 %-----------------------------------------------------------------------------------------------%
-\section{Governing Equations}
+\section{Governing equations}
 \label{sec:formulation}
@@
 %-----------------------------------------------------------------------------------------------%
-\section{Boundary Integral Equation and Cauchy Integral Formulation}
-\label{sec:DLP}
+\section{\edit{Numerical methods}}
+%\section{Boundary Integral Equation and Cauchy Integral Formulation}
+\label{sec:numerics}
 %-----------------------------------------------------------------------------------------------%
+\edit{To investigate the large-scale features of microscopic erosion, we
+require numerical methods that are accurate in both space and time.
+Section~\ref{sec:bie} reformulates the governing equations using a
+boundary integral equation that is discretized with a spectrally
+accurate quadrature rule, and Section~\ref{sec:int_evo} describes our
+second-order numerical method for evolving the bodies. We note that the
+numerical methods described in both sections require that the geometry
+is two-dimensional. Extending our work to three dimensions requires
+entirely different time quadrature formulas and time stepping methods.}
+
+\subsection{\edit{Boundary integral equation formulation}}
+\label{sec:bie}
 To accurately and efficiently solve the Stokes equations~\eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE).
@@
 \end{align}
-respectively, where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and $\cc_\ell$ is a point inside body $\ell$.
-If the density function, Stokeslets, and rotlets satisfy the second-kind boundary integral equation
+respectively, where $\rr_\ell = \xx - \cc_\ell$, \edit{$\rr_\ell^\perp =
+(r_2,-r_1)$,} $\rho_\ell = \|\rr_\ell\|$, and $\cc_\ell$ is a point inside body $\ell$. If the density function, Stokeslets, and rotlets satisfy the second-kind boundary integral equation
 \begin{subequations}
@@
 \end{subequations}
-then the representation~\eqref{eqn:velocity} satisfies the Stokes equations with the required boundary conditions~\eqref{eqn:StokesEq}.
-We solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at equispaced collocation points, and then replacing the integrals with quadrature rules.
-This results in a linear system with a mesh-independent condition number, and it is solved iteratively with GMRES.
-
-Instead of evaluating the Stokes double-layer potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we convert the integral to a sum of contour integrals around Jordan curves in $\CC$.
-We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_2$ and use similar notation for $\yy$, $\nn$, and $\eeta$.
-We also interpret $\gamma$, the boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan curve in $\CC$.
-We introduce the functions
-\begin{align}
-  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
-  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)),
-\end{align}
-and then define the five Cauchy integrals
-\begin{align}
-  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\Re(\eta(y))}{x-y} \,dy, 
-  \quad
-  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\Im(\eta(y))}{x-y} \, dy, 
-  \quad
-  v_3(x) = \frac{1}{2\pi i} \int_{\gamma}
-  \frac{\Re(\overline{y}\eta(y))}{x-y} \, dy, \\
-  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
-  \quad
-  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
-\end{align}
-Then, the first and second components of the Stokes double-layer
-potential are
-\begin{subequations}
-  \begin{align}
-    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
-             \Re(v_3'(x)) + \Re(v_4(x)) \\
-    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
-             \Im(v_3'(x)) + \Re(v_5(x)),
-  \end{align}
-  \label{eqn:velocityCauchy}
-\end{subequations}
-respectively. The components of the deformation tensor are
-\begin{subequations}
-  \begin{align}
-    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
-                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
-    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
-                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
-    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
-                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
-    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
-                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
-  \end{align}
-  \label{eqn:deformationCauchy}
-\end{subequations}
-Having the deformation tensor at hand, the vorticity can be shown to
-satisfy
-\begin{align}
-  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
-     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
-  \label{eqn:vorticityCauchy}
-\end{align}
-We note that the deformation tensor requires second-order derivatives of
-Cauchy integrals, while the vorticity only requires first-order
-derivatives. On solid boundaries, the vorticity reduces to the shear stress given in \eqref{tau0} and needed in errosion law \eqref{Vn0} \cite{quaife2018boundary, chiu2020viscous}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quadrature for Cauchy integrals}
-The overall accuracy of our method is determined by the
-quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
-written the Stokes double-layer potential
-velocity~\eqref{eqn:velocityCauchy}, deformation
-tensor~\eqref{eqn:deformationCauchy}, and
-vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
-their derivatives, the overall accuracy hinges on the computation of a general Cauchy integral
-\begin{align}
-  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
-  \label{eqn:cauchy1}
-\end{align}
-Here we describe a quadrature formulae that was first used to
-approximate analytic functions~\cite{ioa-pap-per1991}, and then extended
-to Stokes layer potentials~\cite{bar-wu-vee2015}. The quadrature method
-requires the boundary data of the analytic function~\eqref{eqn:cauchy1}
-which satisfies the Sokhotski-Plemelj jump relation
-\begin{align}
-  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
-    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
-    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x_0-y} \, dy,
-    \quad x_0 \in \gamma,
-    \label{eqn:SP}
-\end{align}
-where the last integral is interpreted in the principal-value sense.
-Here we are assuming that $\Omega$ is the bounded region interior to
-$\gamma$. Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be
-determined by its boundary data alone using the Cauchy Integral Theorem
-\begin{subequations}
-  \label{eqn:cauchy}
-  \begin{alignat}{3}
-  \label{eqn:cauchyv}
-  v(x) &= \frac{1}{2\pi i}\int_{\gamma} 
-    \frac{v^{-}(y)}{y-x} \,dy, \\
-  v'(x) &= \frac{1}{2\pi i} \int_{\gamma}
-    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
-  v''(x) &= \frac{1}{\pi i} \int_{\gamma}
-    \frac{v^{-}(y)}{(y-x)^3} \, dy.
-  \end{alignat}
-\end{subequations}
-
-The trapezoid rule can be used to approximate this Cauchy integral and
-its derivatives. For example, the Cauchy integral~\eqref{eqn:cauchyv}
-can be approximated as
-\begin{align}
-  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
-    w_j \frac{v^{-}(y_j)}{y_j - x},
-  \label{eqn:trap}
-\end{align}
-where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
-the length of $\gamma$. Because the integrand is both periodic and
-smooth, given a fixed point $x$, the trapezoid rule achieves spectral
-accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
-error is not bounded uniformly with respect to $x$ because the
-derivative of the integrand grows without bound as $x$ approaches
-$\gamma$. This error is problematic for many of our simulations since we
-allow eroding bodies to be arbitrarily close to one another, and we
-often compute the velocity and vorticity at points in the fluid domain
-that are close to an eroding body. In contrast to the integrand in the
-Cauchy integral~\eqref{eqn:cauchyv}, the integrand in the identity
-\begin{align}
-  \frac{1}{2\pi i}\int_{\gamma} 
-    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
-  \label{eqn:trap2}
-\end{align}
-is bounded with respect to $x$, and therefore the error of the trapezoid
-rule is bounded with respect to $x$. Applying the trapezoid rule, we
-have
-\begin{align}
-  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
-    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
-\end{align}
-where the error is now uniformly bounded for all $x$. Rearranging, we
-have
-\begin{align}
-  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
-    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
-  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
-  \quad x \in \Omega.
-  \label{eqn:vBary}
-\end{align}
-Note that the numerator in~\eqref{eqn:vBary} is identical to
-equation~\eqref{eqn:trap}, while the denominator is an approximation of
-the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the errors
-in the numerator and denominator grow, however, since the integrand in
-equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
-the ratio is also bounded independent of $x$.
-
-The derivatives of the Cauchy integral in~\eqref{eqn:cauchy} can be
-approximated with spectral accuracy, uniformly in $x$, using similar quadrature
-rules. To summarize, for $x \in \Omega$, 
-\begin{align}
-  v'(x) &\approx \left(\frac{1}{2\pi i}\sum_{j=1}^{N}
-    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
-  \Bigg/
-  \left(\frac{1}{2\pi i}\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
-  \label{eqn:D1vBary} \\
-  v''(x) &\approx \left(\frac{2}{2\pi i}\sum_{j=1}^N 
-    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
-    \Bigg/
-    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
-  \label{eqn:D2vBary}
-\end{align}
-We note that equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
-and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
-is the bounded region interior to the Jordan curve $\gamma$. However, in
-our application, when $\gamma$ is one of the eroding bodies, $x$ is in
-the exterior region of the Jordan curve. In this case, slightly
-different identities are used, but they all guarantee that the trapezoid
-rule achieves spectral accuracy with an error that is independent of
-$x$. A complete description of the quadrature rules
-for~\eqref{eqn:vBary} and~\eqref{eqn:D1vBary} are described by Barnett,
-Wu, and Veerapaneni~\cite{bar-wu-vee2015}, and the quadrature rule
-for~\eqref{eqn:D2vBary} is described in our previous
-work~\cite{chiu2020viscous}.
+then the representation~\eqref{eqn:velocity} satisfies the Stokes
+equations with the required boundary conditions~\eqref{eqn:StokesEq}. We
+solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at
+equispaced collocation points, and then replacing the integrals with
+quadrature rules. This results in a linear system with a
+mesh-independent condition number, and it is solved iteratively with
+GMRES. Instead of evaluating the Stokes double-layer
+potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we
+convert the integral to a sum of contour integrals around Jordan curves
+in $\CC$. \edit{This conversion allows us to use quadrature formulas
+whose errors are uniformly bounded independent of the proximity of the
+bodies. Details of the conversion and the quadrature formulas are in
+Appendix~\ref{appendix:A}.}
 
@@
 \section*{Acknowledgements}
-N.J.M., J.C., and B.D.Q. recognize the support of NSF Grant DMS-2012560
+N.J.M., J.C., and B.D.Q.~recognize the support of NSF Grant DMS-2012560
 %-----------------------------------------------------------------------------------------------%
@@
 \bibliography{refs}
+
+\begin{appendices}
+\renewcommand{\theequation}{A.\arabic{equation}}
+\setcounter{equation}{0}
+
+\section{Cauchy integral representations and quadrature of the integral operators}
+\label{appendix:A}
+
+\edit{Here we convert the Stokes double-layer
+  potential~\eqref{eqn:velocityDLP} and its derivatives to contour
+  integrals around Jordan curves. We also provide quadrature formulas
+  for each of these integrals.}
+We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_2$ and use similar notation for $\yy$, $\nn$, and $\eeta$.
+We also interpret $\gamma$, the boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan curve in $\CC$.
+We introduce the functions
+\begin{align}
+  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
+  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)),
+\end{align}
+and define the five Cauchy integrals
+\begin{align}
+%  \label{eqn:cauchy_ints}
+%  \begin{aligned}
+  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\Re(\eta(y))}{x-y} \,dy, 
+  \quad
+  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\Im(\eta(y))}{x-y} \, dy, 
+  \quad
+  v_3(x) = \frac{1}{2\pi i} \int_{\gamma}
+  \frac{\Re(\overline{y}\eta(y))}{x-y} \, dy, \\
+  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
+  \quad
+  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
+%  \end{aligned}
+\end{align}
+Then, the first and second components of the Stokes double-layer
+  potential~\eqref{eqn:velocityDLP} are
+\begin{subequations}
+  \begin{align}
+    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
+             \Re(v_3'(x)) + \Re(v_4(x)), \\
+    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
+             \Im(v_3'(x)) + \Re(v_5(x)),
+  \end{align}
+  \label{eqn:velocityCauchy}
+\end{subequations}
+respectively. \edit{The deformation tensor is found by differentiating
+  equation~\eqref{eqn:velocityCauchy}, and}
+%  The components of the deformation tensor are
+%\begin{subequations}
+%  \begin{align}
+%    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
+%                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
+%    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
+%                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
+%    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
+%                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
+%    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
+%                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
+%  \end{align}
+%  \label{eqn:deformationCauchy}
+%\end{subequations}
+%Having the deformation tensor at hand, 
+the vorticity satisfies~\cite{chiu2020viscous}
+%\begin{align}
+%  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
+%     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
+%  \label{eqn:vorticityCauchy}
+%\end{align}
+\begin{align}
+  \omega(x) = \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
+  \label{eqn:vorticityCauchy}
+\end{align}
+We note that the deformation tensor requires second-order derivatives of
+Cauchy integrals, while the vorticity only requires first-order
+derivatives. On solid boundaries, the vorticity reduces to the shear
+stress given in~\eqref{tau0} and needed in erosion
+law~\eqref{Vn0}~\cite{quaife2018boundary, chiu2020viscous}.
+
+\edit{The overall accuracy of our method is determined by the accuracy
+of the quadrature methods used to compute $v_i(x)$, $i=1,\ldots,5$, and
+their first and second derivatives. Each $v_i(x)$ is a Cauchy integral
+with the generic form}
+\begin{align}
+  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
+  \label{eqn:cauchy1}
+\end{align}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%\subsection{Quadrature for Cauchy integrals}
+%The overall accuracy of our method is determined by the
+%quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
+%written the Stokes double-layer potential
+%velocity~\eqref{eqn:velocityCauchy}, deformation
+%tensor~\eqref{eqn:deformationCauchy}, and
+%vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
+%their derivatives, the overall accuracy hinges on the computation of a general Cauchy integral
+%\begin{align}
+%  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
+%  \label{eqn:cauchy1}
+%\end{align}
+Here we describe a quadrature formula that was first used to approximate
+analytic functions~\cite{ioa-pap-per1991}, and then extended to Stokes
+layer potentials~\cite{bar-wu-vee2015}. The quadrature method requires
+the boundary data of the analytic function~\eqref{eqn:cauchy1} which
+satisfies the Sokhotski-Plemelj jump relation
+\begin{align}
+  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} 
+    \edit{\frac{1}{2\pi i}} \int_{\gamma}
+    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
+    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x_0-y} \, dy,
+    \quad x_0 \in \gamma,
+    \label{eqn:SP}
+\end{align}
+where the last integral is interpreted in the principal-value sense.
+Here we are assuming that $\Omega$ is the bounded region interior to
+$\gamma$. Once $v^{-}$ is calculated, $v(x)$ and its derivatives 
+\edit{can be approximated by applying the trapezoid rule to the Cauchy
+Integral Theorem. For example,
+\begin{align}
+  v(x) &= \frac{1}{2\pi i}\int_{\gamma} \frac{v^{-}(y)}{y-x} \,dy \approx 
+    \frac{1}{2\pi i} \sum_{j=1}^{N} w_j \frac{v^{-}(y_j)}{y_j - x},
+  \label{eqn:cauchyv}
+\end{align}
+}
+%\begin{subequations}
+%  \label{eqn:cauchy}
+%  \begin{alignat}{3}
+%  \label{eqn:cauchyv}
+%  v(x) &= \frac{1}{2\pi i}\int_{\gamma} 
+%    \frac{v^{-}(y)}{y-x} \,dy, \\
+%  v'(x) &= \frac{1}{2\pi i} \int_{\gamma}
+%    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
+%  v''(x) &= \frac{1}{\pi i} \int_{\gamma}
+%    \frac{v^{-}(y)}{(y-x)^3} \, dy.
+%  \end{alignat}
+%\end{subequations}
+%The trapezoid rule can be used to approximate this Cauchy integral and
+%its derivatives. For example, the Cauchy integral~\eqref{eqn:cauchyv}
+%can be approximated as
+%\begin{align}
+%  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
+%    w_j \frac{v^{-}(y_j)}{y_j - x},
+%  \label{eqn:trap}
+%\end{align}
+where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
+the length of $\gamma$. Because the integrand is both periodic and
+smooth, given a fixed point $x$, the trapezoid rule achieves spectral
+accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
+error is not bounded uniformly with respect to $x$ because the
+derivative of the integrand grows without bound as $x$ approaches
+$\gamma$. This error is problematic for many of our simulations since we
+allow eroding bodies to be arbitrarily close to one another, and we
+often compute the velocity and vorticity at points in the fluid domain
+that are close to an eroding body. In contrast to the integrand in the
+Cauchy integral~\eqref{eqn:cauchyv}, the integrand in the identity
+\begin{align}
+  \frac{1}{2\pi i}\int_{\gamma} 
+    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
+  \label{eqn:trap2}
+\end{align}
+is bounded with respect to $x$, and therefore the error of the trapezoid
+rule is bounded with respect to $x$. Applying the trapezoid rule, we
+have
+\begin{align}
+  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
+    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
+\end{align}
+where the error is now uniformly bounded for all $x$. Rearranging, we
+have
+\begin{align}
+  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
+    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
+  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
+  \quad x \in \Omega.
+  \label{eqn:vBary}
+\end{align}
+Note that the numerator in~\eqref{eqn:vBary} is identical to \edit{the
+approximation in}
+equation~\eqref{eqn:cauchyv}, while the denominator is an approximation of
+the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the errors
+in the numerator and denominator grow, however, since the integrand in
+equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
+the ratio is also bounded independent of $x$.
+
+The derivatives of the Cauchy integral in~\eqref{eqn:cauchy1},
+\edit{which are need to compute the vorticty and deformation tensor,}
+can be approximated with spectral accuracy, uniformly in $x$, using
+similar quadrature rules. To summarize, for $x \in \Omega$, 
+\begin{align}
+  v'(x) &\approx \left(\frac{1}{2\pi i}\sum_{j=1}^{N}
+    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
+  \Bigg/
+  \left(\frac{1}{2\pi i}\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
+  \label{eqn:D1vBary} \\
+  v''(x) &\approx \left(\frac{2}{2\pi i}\sum_{j=1}^N 
+    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
+    \Bigg/
+    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
+  \label{eqn:D2vBary}
+\end{align}
+We note that equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
+and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
+is the bounded region interior to the Jordan curve $\gamma$. However, in
+our application, when $\gamma$ is one of the eroding bodies, $x$ is in
+the exterior region of the Jordan curve. In this case, slightly
+different identities are used, but they all guarantee that the trapezoid
+rule achieves spectral accuracy with an error that is independent of
+$x$. A complete description of the quadrature rules
+for~\eqref{eqn:vBary} and~\eqref{eqn:D1vBary} are described by Barnett,
+Wu, and Veerapaneni~\cite{bar-wu-vee2015}, and the quadrature rule
+for~\eqref{eqn:D2vBary} is described in our previous
+work~\cite{chiu2020viscous}.
+
+\end{appendices}
+
 \end{document}

### 2022-12-02 docs/proposals/NSF/PostDocs/Colgate_Transfer/budgetJustificationFSU2022.tex
working on revisions

--- 2020-08-26 docs/proposals/NSF/budgets/budgetJustificationFSU.tex
@@
 The requested senior personnel funding is to support one month of the
-PI's summer salary in years 1 and 2, and 0.5 months of the PI's summer
+PI's summer salary in years 1 and 2, and 0.25 months of the PI's summer
 salary in year 3. During this period, the PI will work together to
@@
     \hline
-    PI & $\$10,553$ & $\$10,869$ & $\$5,598$ & $\$27,020$ \\
+    PI & $\$10,553$ & $\$10,869$ & $\$2,799$ & $\$24,221$ \\
     \hline
@@
 The requested other personnel funding includes salary for one full-time
-Ph.D.~student in two semesters of each year starting at $\$21,000$. The
-Ph.D.~student will develop and perform numerical simulations. An annual
-increase of 3\% is included.
+Ph.D.~student in two semesters of years one, two, and three, starting at
+$\$21,000$. The Ph.D.~student will develop and perform numerical
+simulations. An annual increase of 3\% is included in years 2 and 3.
 %\hfill \\
@@
     \hline
-    PI & $\$1,956$ & $\$2,015$ & $\$1,037$ & $\$5,008$ \\
+    PI & $\$1,956$ & $\$2,015$ & $\$519$ & $\$4,490$ \\
     \hline
@@
     \hline
-    Total & $\$4,047$ & $\$4,110$ & $\$3,136$ & $\$11,293$ \\
+    Total & $\$4,047$ & $\$4,110$ & $\$2,618$ & $\$10,775$ \\
     \hline
@@
 The requested travel funds is to fund an annual domestic trip for the PI
-or the Ph.D.~student.  The expected costs per conference participant is
-$\$1,000$ with a breakdown of $\$300$ for airfare, $\$300$ for lodging,
-$\$56$ for local transportation, $\$144$ for meals (four days at $\$36$
-per day), and $\$200$ for conference registration. An additional $\$195$
-is budgeted for year 2. Potential meeting venues include several SIAM
-Meetings (Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings,
-or appropriately themed workshops. The PI and Ph.D.~student will give
-presentations and actively participate in the meeting or workshop.
-Travel funds for the first year are removed due to the COVID crisis.
+or the Ph.D.~student in years 2 and 3. The expected costs per conference
+participant is $\$1,097$ with a breakdown of $\$397$ for airfare,
+$\$300$ for lodging, $\$56$ for local transportation, $\$144$ for meals
+(four days at $\$36$ per day), and $\$200$ for conference registration.
+An additional $\$523$ is budgeted for year 3. Potential meeting venues
+include several SIAM Meetings (Annual Meetings, CSE, Dynamical Systems),
+APS Fluids Meetings, or appropriately themed workshops. The PI and
+Ph.D.~student will give presentations and actively participate in the
+meeting or workshop. Travel funds for the first year are removed due to
+the COVID crisis.
 %\hfill \\
@@
     \hline
-    Domestic Conferences &  & $\$2,195$ & $\$2,000$ & $\$4,195$ \\
+    Domestic Conferences &  & $\$2,195$ & $\$2,718$ & $\$4,813$ \\
     \hline
@@
 not otherwise available, for the PI and Ph.D.~student in year 1. The
-laptop will be used for developing the proposed algorithms and
+laptops will be used for developing the proposed algorithms and
 presenting the results at conferences. The laptop will give the group
@@
 \\
-\paragraph{\bf Subawards:} The requested subaward is for Dr.~Nick Moore
-at the US Naval Academy to provide two of the deliverables as described
-in the scope of work.
+\paragraph{\bf Subawards:} The requested subaward is for Dr.~Nick Moore,
+previously employed at the US Naval Academy (USNA), and currently
+employed at Colgate University, to provide two of the deliverables as
+described in the scope of work.
 \\
-\paragraph{\bf Other:} The requested other direct costs are to cover the
+\paragraph{\bf Tuition:} The requested other direct costs are to cover the
 Ph.D.~student's tuition for 18 credit hours, at a rate of $\$407.55$ per
@@
     \hline
-    Materials and Supplies & $\$1,359$ & & & $\$1,359$ \\
+    Materials and Supplies & $\$1,500$ & & & $\$1,500$ \\
     \hline
-    Subawards & $\$14,445$ & $\$15,811$ & $\$16,135$ & $\$46,391$ \\
+    Subawards & $\$14,445$ & $\$15,811$ & $\$19,921$ & $\$50,177$ \\
     \hline
-    Other & $\$7,336$ & $\$7,410$ & $\$7,484$ & $\$22,230$ \\
+    Subaward Location 
+    & USNA & USNA & Colgate & \\
     \hline
-    Total & $\$23,140$ & $\$23,221$ & $\$23,619$ & $\$69,980$ \\
+    Tuition & $\$7,336$ & $\$7,409$ & $\$7,484$ & $\$22,229$ \\
+    \hline
+    Total & $\$23,281$ & $\$23,220$ & $\$27,405$ & $\$73,906$ \\
     \hline
@@
     \hline
-    $\$58,740$ & $\$62,025$ & $\$56,632$ & $\$177,397$ \\
+    $\$58,881$ & $\$62,024$ & $\$57,819$ & $\$178,724$ \\
     \hline
@@
 tuition subaward costs after the first \$25,000. The base for overhead
-is $\$51,504$ in year 1, $\$49,359$ in year 2, and $\$33,013$ in year 3.
+is $\$51,545$ in year 1, $\$49,359$ in year 2, and $\$30,414$ in year 3.
 Florida State University defines a fiscal year to be July 1--June 30.
@@
     \hline
-    $\$27,758$ & $\$26,654$ & $\$17,827$ & $\$72,239$ \\
+    $\$27,834$ & $\$26,654$ & $\$16,424$ & $\$70,912$ \\
     \hline
@@
     \hline
-    $\$86,498$ & $\$88,679$ & $\$74,459$ & $\$249,636$ \\
+    $\$86,715$ & $\$88,678$ & $\$74,243$ & $\$249,636$ \\
     \hline

### 2022-12-13 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work.
-Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.
+Here, we use numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.
 
-Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in \edit{two-dimensional Stokes flows.
-We employ the Stokes equations because it is the regime relevant for groundwater applications~\cite{quaife2018boundary, chiu2020viscous}}.
+Our method merges \edit{spectrally}-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in \edit{two-dimensional Stokes flows.
+We employ the Stokes system because it is the regime relevant for groundwater applications~\cite{quaife2018boundary, chiu2020viscous}}.
 Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
@@
 \label{sec:bie}
-To accurately and efficiently solve the Stokes equations~\eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE).
+To \edit{numerically} solve the Stokes equations~\eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE).
 A BIE formulation has the advantage that all the unknowns are on the one-dimensional boundaries of the domain.

### 2022-12-14 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 
-Our method merges \edit{spectrally}-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in \edit{two-dimensional Stokes flows.
-We employ the Stokes system because it is the regime relevant for groundwater applications~\cite{quaife2018boundary, chiu2020viscous}}.
+Our method merges \edit{spectrally}-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies embedded in \edit{two-dimensional Stokes flows.}
 Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
@@
 
-%A plug flow is imposed on artificial walls to the left and right of each frame, and a no-slip boundary condition is imposed along the top and bottom of each frame.
+%We employ the Stokes system for two reasons:~(1) this flow regime is appropriate for many groundwater applications \cite{bear1988dynamics}; and (2) the linearity of the Stokes system provides
 
@@
 We then measure the two permeabilities, $k_{11}^{(c)}$ and $ k_{22}^{(c)}$, of this configuration of circular bodies.
-Since all of the individual shapes are identical and isotropic (i.e.~circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$.
+\edit{Importantly, since we have preserved the area of each body, the configurational permeability accounts for the distribution of overall body sizes.
+We can consider the total permeability, $k_{11}$, as the product of $k_{11}^{(c)}$ and another component, $k_{11}^{(s)}$, that depends on the detailed shape of each body.
+Since $k_{11}^{(s)}$ depends on shape, but {\em not} on the overall body sizes, this shape permeability is analogous to a dimensionless drag coefficient.
+A similar decomposition is made for $k_{22}$.
+Since we have replaced each body with a circle, which is an isotropic object, the anisotropy that results from this test is entirely due to the relative positions of the bodies, allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$.
+Further, since $k_{11} = k_{11}^{(c)} k_{11}^{(s)}$ and a similar formula holds for $k_{22}$, we have the total anisotropy as the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured.
+We can therefore deduce the shape anisotropy through $\anis_S = \anis/\anis_C$.
+}
+
+%
+%Since all of the individual shapes are identical and isotropic (i.e.~circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$.
 The total anisotropy, meanwhile, is the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured.

### 2022-12-14 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 second-order numerical method for evolving the bodies. We note that the
-numerical methods described in both sections require that the geometry
-is two-dimensional. Extending our work to three dimensions requires
-entirely different time quadrature formulas and time stepping methods.}
+numerical methods described in both sections require the geometry
+to be two-dimensional. Extending our work to three dimensions would require
+ different quadrature formulas and time-stepping methods.}
 

### 2022-12-14 docs/PhysicsPaper/Referee Reports/Ref 1 Response/Ref1.tex
NM

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{graphicx,amsmath,amsfonts,amssymb,stmaryrd}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}

%----------------------------- CUSTOM COMMANDS -----------------------------%

%----------------------------------------------------------------------------%
%% LATEX DEFINITIONS
%----------------------------------------------------------------------------%
% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}

% Derivatives
\newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
\newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
\newcommand{\pdi}[2] { {\partial_#2} #1 }
\newcommand{\td}[2] { \frac{d #1} { d #2 } }
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
% Vectors and operators
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\Real}{\text{Re}}
\newcommand{\Imag}{\text{Im}}
\newcommand{\dotp}{\boldsymbol{\cdot}}

% Edit
\newcommand{\edit}[1]{{\color{red} #1}}

% Math
\newcommand{\anis}{\mathcal{A}}

%----------------------------- DOCUMENT -----------------------------%
\begin{document}

\section*{Responses to Referee 1}

We would like to thank the referee for reviewing our work ....

Below we respond to each of the referee's comments in sequence. For your convenience, we are submitting a version of the revised manuscript with the changes highlighted. \\ \\ \\

\noindent \comment{Reviewer \#1: 
I enjoyed reading this paper. It will make a nice contribution to the special issue of Physica D. It begins by formulating a numerical boundary integral method based on Cauchy integrals for 2D Stokes flow past multiple solid bodies. The bodies erode with the normal velocity of their boundaries proportional to the local shear stress at the fluid-body interface. The method employs quadrature formulas enabling large numbers of bodies (up to 100) to be considered.
The numerical method is then applied to an interesting problem related to porous media flow: 2D Stokes flow past an ensemble of initially circular bodies. Erosion causes the bodies to become slender in the direction of the mean fluid flow and also results in the formation of channels within the porous media in the same direction. These two effects combine to create a media with anisotropic permeability.
The paper is well-written with the derivation of the method and examples and results clearly described. A particularly nice feature of the discussion is the linking of microscopic properties of the medium to large scale quantities such as permeability and tortuosity, including a clever way to compute both the longitudinal and transverse permeability; and the quantification of the channelization versus body-shape effects in contributing to the permeability. The paper will be of interest to readers with interests in fluid mechanics, applied complex analysis, free boundary problems and porous media flow. I am pleased to recommend publication. Below are some minor comments the authors should consider before publication.
\\ }

\noindent
We thank the referee for this positive evaluation of our work. \\ \\

\noindent \comment{Reviewer \#1: 
1. In several places the numerical method is claimed to be ‘highly accurate’ and ‘highly- efficient’. Some justification should be provided for these claims e.g. comparison to a simple test case and subsequent error analysis, comparisons to conserved quantities (if any) or citation of previous works that do such tests. Also, does the use of a narrow Gaussian filter (page 6) still preserve the high accuracy’? Please justify.
\\ }

\noindent
Thank you for bring up this point. To explain our intent, boundary-integral equations can be considered `highly accurate' because of their spectral accuracy (i.e. exponential rate of convergence), and they can be considered `highly efficient' due to the reduction of dimension, i.e. only a boundary needs to be resolved rather than the interior of the domain. This later point regarding the efficiency of a BIE is briefly explained in the first paragraph of Section 3.1.
We agree, though, that in the original manuscript such meanings were not adequately conveyed by the terms `highly accurate' and `highly efficient'. We have therefore either removed these terms or  replaced them with more precise descriptors in all instances. For example, in the second paragraph of the introduction, we have modified the first sentence to read: ``Our method merges spectrally-accurate boundary-integral equation (BIE) methods...''

The regularization terms, including the narrow Gaussian filter, are introduced for stability of the time stepping, and, for a fixed geometry, these terms do not affect the accuracy with which the velocity and stress fields are computed. However, the referee is correct that, over time, these terms cause the computed interfaces to deviate from the interfaces that would have been computed without regularization, i.e.~the unmodified Eq.~(2). We believe this discrepancy is best viewed as `modeling' error. Indeed, the modeling error scales linearly with the strength of the regularization, e.g.~the $\epsilon$ in Eq.~(8). This situation is similar to artificial viscosity or hyper-viscosity terms used for numerical stability in a range of applications.
\\ \\

\noindent \comment{Reviewer \#1: 
2. Some justification for using Stokes flow in studying porous media flow should given. For example, what is a typical Reynolds number?
\\ }

\noindent
This is a good question, and one that is much more complex than it appears. In short, the range of Reynolds numbers found in natural porous media is too vast to summarize by a typical value. For illustration, Fig.~5.3.1 in Bear's textbook (among the most widely used references for porous media) shows a Reynolds number range of $10^{-2}$ to $10^{3}$ for porous-media {\em laboratory experiments}. The range found in natural materials, which even Bear does not give, would be expected to be even greater. The reason being that the Reynolds number depends on not only the mean particle diameter (for which there are neat tables) but also the typical specific discharge, which can be arbitrarily slow or arbitrarily fast (for example, a flood moving through loose gravel) in natural settings.
Considerable attention has been given to the question of when the low-Reynolds approximation is valid for porous-media applications (see for example, section 5.3 of Bear).
It is fair to say that the Stokes regime reasonably applies to {\em many} groundwater situations, but it would be difficult to justify a stronger statement. Such a complex discussion would be appropriate for a groundwater-engineering article, but lies outside of the scope of our article. We have therefore removed any discussion about typical flow regimes of natural porous media, as we believe such a discussion would distract from the main points of our paper.
\\ \\

\noindent \comment{Reviewer \#1: 
3. Is there any effect of the choice of length of the ‘buffer regions’ (page 2) on the results?
\\ }

\noindent
We do not expect the size of the buffer region to strongly affect the results. Benchmark results from Quaife Moore {\it JCP} 2018 show that, for the simulated erosion of a single body, the opening angle at the front and rear converges to the theoretically-predicted angle of $102^\circ$. There is no buffer region in the theoretical prediction, and so the agreement between the simulation and theory suggests the buffer region is not playing a strong role. Incidentally, this same benchmark suggests the regularization terms do not strongly influence the results as well (other than to keep the numerics stable). This same paper also presents results on the rate at which the solid area vanishes, which again is consistent with theoretical predictions suggesting that the buffer region and regularization terms do not strongly alter the results. We acknowledge that we have not directly tested the effect of the buffer-region size, but please see Quaife Moore {\it JCP} 2018 for a range of other tests that we have performed.
\\ \\

\noindent \comment{Reviewer \#1: 
4. In (6) $r_{\ell}^{\perp}$ should be defined.
\\ }

\noindent
Thank you for pointing this out. We have now defined $r_{\ell}^{\perp}$ directly below Eq.~(6).
\\ \\

\noindent \comment{Reviewer \#1: 
5. Is there a missing $2\pi i$ in the first integral of (15)?
\\ }

\noindent
Yes, there was a missing $2 \pi i$ which we have now included in this equation. This equation now appears in Eq.~(A.7) of the Appendix. Thank you for pointing out our oversight.
\\ \\

\noindent \comment{Reviewer \#1: 
6. It’s not completely clear to me why the product of shape and configurational anisotropy is the total anisotropy. I think some further remarks on this would be useful.
\\ }

This is a good question and, admittedly, a point that was glossed over in the original manuscript. The reason that total anisotropy can be regarded as the produce of shape and configurational anisotropy essential boils down to a dimensional analysis argument.

For the sake of this discussion, suppose that quantities such as drag and permeability are dimensional (even though they are dimensionless in our paper). To begin, as an analogy, it is routine to represent hydrodynamic drag exerted on an object in a high-Reynolds number flow with the familiar formula
\begin{equation}
F_D = \frac{1}{2} C_D \rho V^2 A
\end{equation}
where $\rho$ is the fluid density, $V$ is a characteristic velocity (often taken to be the velocity of the object) and $A$ a characteristic area (often taken as the surface area of the object, or else the `wetted' frontal area, etc.). Importantly, the dimensionless drag coefficient $C_D$ encapsulates all of the details of the object's shape that affect drag. Notice that $C_D$ appears in product with the dimensional quantities.

Of course, in our manuscript, we consider the Stokes limit of the drag, for which there is a different formula, but the principle remains that it can be decomposed into a dimensional component (that depends on the length-scale of the object, fluid properties, the flow speed, etc.) and a dimensionless coefficient to represent the detailed shape of the object.
Likewise, the permeability associated with a single object can be represented in a similar way, where the dimensionless coefficient could be considered the `shape' permeability, $k_{11}^{(s)}$, analogous to the shape anisotropy defined in our manuscript. That is, the value $k_{11}^{(s)}$ associated with a single body depends on the detailed shape of that body, and not on its overall size, or the viscosity of the fluid, or the flow speed, etc. The dimensional component of the permeability we can call `configurational' permeability $k_{11}^{(c)}$, which, though it seems strange for a single body, will connect to the configurational anisotropy. The value $k_{11}^{(c)}$ represents the dimensional part of the permeability, and it takes into account the length-scale of the body, the strength of the flow, the viscosity of the fluid etc. Therefore, in this notation, we have
\begin{equation}
k_{11} = k_{11}^{(s)} k_{11}^{(c)}
\end{equation}
These quantities could of course be defined similarly for a collection of objects, as in our paper. It is important to note that, in the extraction of $k_{11}^{(c)}$ in our paper, we replace every body with a circle of the same location {\em and the same area}. The later point implies that $k_{11}^{(c)}$ represents the component of $k_{11}$ that depends on overall body length-scale, so that what is left, $k_{11}^{(s)}$ does {\em not} depend on length scale, and instead only depends on the detailed shapes of the bodies.

Introducing a similar decomposition of transverse permeability $k_{22}$ and putting everything together yields
\begin{equation}
\anis = \frac{k_{11}}{k_{22}} = \frac{ k_{11}^{(s)} k_{11}^{(c)} }{ k_{22}^{(s)} k_{22}^{(c)} }
= \anis^{(s)} \anis^{(c)}
\end{equation}
which is the result used in our paper. We have added a brief explanation in the updated manuscript at the end of Section 4.3.
\\ \\

\noindent \comment{Reviewer \#1: 
7. It would be helpful to know (page 10) how the randomized sizes and locations of the bodies are chosen so as they do not overlap.
\\ }

Great question. This is an aspect of the simulation that we regarded as too detailed to fully explain in this manuscript, but it is an interesting aspect that we are happy to explain here. In essence, we use a simulated annealing procedure to initialize the configuration of circular bodies. We first determine the distribution of circle radii by straightforward sampling (we use a Chi distribution, but this choice is arbitrary) and by using the porosity that is specified. Second, we randomly assign the circle centers; many of the circles will overlap (unless we are incredibly lucky). Next, we specify fictitious forces that act to repel overlapping bodies and also repel bodies from the domain walls. In addition, the force acting on each body has a stochastic component with magnitude, or `temperature', that decreases over the course of the initialization routine. Hence, early in the initialization routine, the temperature is high and the random component is large compared to the deterministic forces, but at later stages, the temperature is low and the random component tends to zero. This algorithm allows the bodies to jump around substantially to explore different configurations and eventually converge to a configuration in which none overlap. Naturally, there are limitations to such an initialization algorithm. For example, there exists thresholds for the solid area fraction (that depend on the radius distribution) above which no circle packing is possible.
\end{document}

### 2022-12-14 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second-order in time~\cite{quaife2018boundary}.
+
+	\edit{Random configurations of bodies are initialized by sampling a list of the radii from a Chi distribution while enforcing the desired initial porosity.
+These circular bodies are initially positioned randomly, which typically results in many overlapping bodies.
+To eliminate overlap, we employ a simulated-annealing algorithm, in which fictitious forces act on the bodies.
+The force on each body includes a deterministic repulsive component that acts to separate the bodies from one another and from the domain walls along with a stochastic component whose magnitude decreases with time.}
 

### 2022-12-14 docs/PhysicsPaper/Referee Reports/Ref 1 Response/Ref1.tex
NM

@@
 Great question.
-This is an aspect of the simulation that we regarded as too detailed to fully explain in this manuscript, but it is an interesting aspect that we are happy to explain here.
+This is an aspect of the simulation that we had regarded as too detailed to fully explain in this manuscript, but it is an interesting aspect that we are happy to explain here.
 In essence, we use a simulated annealing procedure to initialize the configuration of circular bodies.
@@
 For example, there exists thresholds for the solid area fraction (that depend on the radius distribution) above which no circle packing is possible.
+
+We have added a brief explanation of this initialization algorithm to the updated manuscript. stuff
+
 \end{document}

### 2022-12-15 docs/PhysicsPaper/StokesErosion.tex
NM

--- 2022-12-14 docs/PhysicsPaper/StokesErosion.tex
@@
 In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second-order in time~\cite{quaife2018boundary}.
+
+	\edit{Random configurations of circular bodies are initialized by a simulated-annealing algorithm.
+First, a list of radii are sampled from a Chi distribution.
+The radii are then rescaled to achieve the desired initial porosity.
+Next, the circular bodies are positioned randomly, which typically results in many overlapping bodies.
+To eliminate overlap, fictitious forces are introduced that act to repel bodies from one another and from domain boundaries.
+The force also has a stochastic component whose magnitude decreases with time.
+This algorithm allows the bodies to explore different configurations and eventually settle on one without any overlap between bodies.}
 

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

--- 2022-12-14 docs/PhysicsPaper/Referee Reports/Ref 1 Response/Ref1.tex
@@
 
-\section*{Responses to Referee 1}
+\section*{Responses to Referee 2}
 
@@
 \noindent \comment{Reviewer \#1: 
-I enjoyed reading this paper.
-It will make a nice contribution to the special issue of Physica D.
-It begins by formulating a numerical boundary integral method based on Cauchy integrals for 2D Stokes flow past multiple solid bodies.
-The bodies erode with the normal velocity of their boundaries proportional to the local shear stress at the fluid-body interface.
-The method employs quadrature formulas enabling large numbers of bodies (up to 100) to be considered.
-The numerical method is then applied to an interesting problem related to porous media flow: 2D Stokes flow past an ensemble of initially circular bodies.
-Erosion causes the bodies to become slender in the direction of the mean fluid flow and also results in the formation of channels within the porous media in the same direction.
-These two effects combine to create a media with anisotropic permeability.
-The paper is well-written with the derivation of the method and examples and results clearly described.
-A particularly nice feature of the discussion is the linking of microscopic properties of the medium to large scale quantities such as permeability and tortuosity, including a clever way to compute both the longitudinal and transverse permeability; and the quantification of the channelization versus body-shape effects in contributing to the permeability.
-The paper will be of interest to readers with interests in fluid mechanics, applied complex analysis, free boundary problems and porous media flow.
-I am pleased to recommend publication.
-Below are some minor comments the authors should consider before publication.
+The paper studies erosion within a porous medium comprising an array of (initially) close-packed circular cylinders, across which a Stokesian fluid flows.
+Erosion of the cylinders occurs, at a rate proportional to local shear stress at cylinder boundaries.
+The authors study how the erosion leads to the initially isotropic medium developing anisotropic features over time, and they present various measures to quantify the extent and nature of the anisotropy.
+\\
+
+I found the paper well written and easy to read.
+The work is certainly worthy of publication; however several questions and comments came to mind as I read it, and I'd like the authors to consider these in a revised version.
 \\ }
@@
 
-\noindent \comment{Reviewer \#1: 
-1.
-In several places the numerical method is claimed to be ‘highly accurate’ and ‘highly- efficient’.
-Some justification should be provided for these claims e.g.
-comparison to a simple test case and subsequent error analysis, comparisons to conserved quantities (if any) or citation of previous works that do such tests.
-Also, does the use of a narrow Gaussian filter (page 6) still preserve the high accuracy’?
-Please justify.
+\noindent \comment{Reviewer \#2: 
+Stylistic comments: \\
+- Section 3 (mainly section 3.1 and what comes before it) seems much longer than necessary and contains a lot of technical (sometimes trivial) detail.
+For example, do we really need to see the components of the deformation tensor (12a-d) in the main text?
+Do we really need to see the same function differentiated twice (16a-c)?
+Then a straightforward trapezoidal approximation (17)?
+Why not omit (16b,c) and combine (16a) and (17) in a single line?
+Then more approximations in (21-22).
+To my mind, much of the detail in this section belongs in an appendix.
+Or SI.
 \\ }
@@
 \noindent
-Thank you for bring up this point.
-To explain our intent, boundary-integral equations can be considered `highly accurate' because of their spectral accuracy (i.e.
-exponential rate of convergence), and they can be considered `highly efficient' due to the reduction of dimension, i.e.
-only a boundary needs to be resolved rather than the interior of the domain.
-This later point regarding the efficiency of a BIE is briefly explained in the first paragraph of Section 3.1.
-We agree, though, that in the original manuscript such meanings were not adequately conveyed by the terms `highly accurate' and `highly efficient'.
-We have therefore either removed these terms or  replaced them with more precise descriptors in all instances.
-For example, in the second paragraph of the introduction, we have modified the first sentence to read: ``Our method merges spectrally-accurate boundary-integral equation (BIE) methods...''
-
-The regularization terms, including the narrow Gaussian filter, are introduced for stability of the time stepping, and, for a fixed geometry, these terms do not affect the accuracy with which the velocity and stress fields are computed.
-However, the referee is correct that, over time, these terms cause the computed interfaces to deviate from the interfaces that would have been computed without regularization, i.e.~the unmodified Eq.~(2).
-We believe this discrepancy is best viewed as `modeling' error.
-Indeed, the modeling error scales linearly with the strength of the regularization, e.g.~the $\epsilon$ in Eq.~(8).
-This situation is similar to artificial viscosity or hyper-viscosity terms used for numerical stability in a range of applications.
+Thank you for bringing this stylistic point to our attention. We have taken the referee's advice and moved many of the more detailed equations into an appendix. 
 \\ \\
 
-\noindent \comment{Reviewer \#1: 
-2. Some justification for using Stokes flow in studying porous media flow should given. For example, what is a typical Reynolds number?
+\noindent \comment{Reviewer \#2: 
+- Equation (2) for the erosion - but this is not in fact the law that is implemented in the paper.
+So it seems a bit misleading to use it in the model formulation.
+I can see the authors might prefer a cleaner model presentation, but I think at least a comment saying that in the implementation the law is modified would be appropriate.
 \\ }
@@
 \noindent
-This is a good question, and one that is much more complex than it appears.
-In short, the range of Reynolds numbers found in natural porous media is too vast to summarize by a typical value.
-For illustration, Fig.~5.3.1 in Bear's textbook (among the most widely used references for porous media) shows a Reynolds number range of $10^{-2}$ to $10^{3}$ for porous-media {\em laboratory experiments}.
-The range found in natural materials, which even Bear does not give, would be expected to be even greater.
-The reason being that the Reynolds number depends on not only the mean particle diameter (for which there are neat tables) but also the typical specific discharge, which can be arbitrarily slow or arbitrarily fast (for example, a flood moving through loose gravel) in natural settings.
-Considerable attention has been given to the question of when the low-Reynolds approximation is valid for porous-media applications (see for example, section 5.3 of Bear).
-It is fair to say that the Stokes regime reasonably applies to {\em many} groundwater situations, but it would be difficult to justify a stronger statement.
-Such a complex discussion would be appropriate for a groundwater-engineering article, but lies outside of the scope of our article.
-We have therefore removed any discussion about typical flow regimes of natural porous media, as we believe such a discussion would distract from the main points of our paper.
+This is a good point. In the updated manuscript, we have included a comment after Eqs.~(2)--(3) that this law will be slightly modified in Section 3.2 for the sake of numerical stability.
 \\ \\
 
-\noindent \comment{Reviewer \#1: 
-3. Is there any effect of the choice of length of the ‘buffer regions’ (page 2) on the results?
+\noindent \comment{Reviewer \#2: 
+- Bottom of p11: "statistical analysis of many simulations will show" - this sounds speculative.
+ I interpreted this on first reading to be the authors' conjecture, rather than something they actually do in the present paper.
+Why not rephrase to indicate where this is shown (Sec.
+5.2)?
 \\ }
@@
 \noindent
-We do not expect the size of the buffer region to strongly affect the results.
-Benchmark results from Quaife Moore {\it JCP} 2018 show that, for the simulated erosion of a single body, the opening angle at the front and rear converges to the theoretically-predicted angle of $102^\circ$.
-There is no buffer region in the theoretical prediction, and so the agreement between the simulation and theory suggests the buffer region is not playing a strong role.
-Incidentally, this same benchmark suggests the regularization terms do not strongly influence the results as well (other than to keep the numerics stable).
-This same paper also presents results on the rate at which the solid area vanishes, which again is consistent with theoretical predictions suggesting that the buffer region and regularization terms do not strongly alter the results.
-We acknowledge that we have not directly tested the effect of the buffer-region size, but please see Quaife Moore {\it JCP} 2018 for a range of other tests that we have performed.
+Thank you for bringing this ambiguity to our attention. We have rephrased this passage to make it clear that our statistical analysis in Section 5.2 demonstrates the point in question.
 \\ \\
 
-\noindent \comment{Reviewer \#1: 
-4. In (6) $r_{\ell}^{\perp}$ should be defined.
+\noindent \comment{Reviewer \#2: 
+Scientific comments \\ \\
+- I didn't see any mention in the paper that the study is restricted to 2D flows.
+Of course, it's obvious from the presented study and the methods - but I think it's worth pointing this out explicitly, and it's also worth mentioning specifically in the paper where differences in the modeling and results would arise in a more general 3D study.
+(For instance, in the modeling, more care would be needed with the shear stress definition in (3) and the associated erosion law.) If the authors are considering real-world situations where the geometry is (quasi)-2D then this is worth mentioning also.
+But in 3D I would expect the anisotropy progression to be weaker than in the 2D case, due to the flow having an extra dimension to flow into.
+So I'd like to see some discussion of this point, if only at a speculative level.
 \\ }
 
-\noindent
-Thank you for pointing this out. We have now defined $r_{\ell}^{\perp}$ directly below Eq.~(6).
-\\ \\
-
-\noindent \comment{Reviewer \#1: 
-5. Is there a missing $2\pi i$ in the first integral of (15)?
-\\ }
-
-\noindent
-Yes, there was a missing $2 \pi i$ which we have now included in this equation. This equation now appears in Eq.~(A.7) of the Appendix. Thank you for pointing out our oversight.
-\\ \\
-
-\noindent \comment{Reviewer \#1: 
-6. It’s not completely clear to me why the product of shape and configurational anisotropy is the total anisotropy. I think some further remarks on this would be useful.
-\\ }
-
-This is a good question and, admittedly, a point that was glossed over in the original manuscript.
-The reason that total anisotropy can be regarded as the produce of shape and configurational anisotropy essential boils down to a dimensional analysis argument.
-
-For the sake of this discussion, suppose that quantities such as drag and permeability are dimensional (even though they are dimensionless in our paper).
-To begin, as an analogy, it is routine to represent hydrodynamic drag exerted on an object in a high-Reynolds number flow with the familiar formula
-\begin{equation}
-F_D = \frac{1}{2} C_D \rho V^2 A
-\end{equation}
-where $\rho$ is the fluid density, $V$ is a characteristic velocity (often taken to be the velocity of the object) and $A$ a characteristic area (often taken as the surface area of the object, or else the `wetted' frontal area, etc.).
-Importantly, the dimensionless drag coefficient $C_D$ encapsulates all of the details of the object's shape that affect drag.
-Notice that $C_D$ appears in product with the dimensional quantities.
-
-Of course, in our manuscript, we consider the Stokes limit of the drag, for which there is a different formula, but the principle remains that it can be decomposed into a dimensional component (that depends on the length-scale of the object, fluid properties, the flow speed, etc.) and a dimensionless coefficient to represent the detailed shape of the object.
-Likewise, the permeability associated with a single object can be represented in a similar way, where the dimensionless coefficient could be considered the `shape' permeability, $k_{11}^{(s)}$, analogous to the shape anisotropy defined in our manuscript.
-That is, the value $k_{11}^{(s)}$ associated with a single body depends on the detailed shape of that body, and not on its overall size, or the viscosity of the fluid, or the flow speed, etc.
-The dimensional component of the permeability we can call `configurational' permeability $k_{11}^{(c)}$, which, though it seems strange for a single body, will connect to the configurational anisotropy.
-The value $k_{11}^{(c)}$ represents the dimensional part of the permeability, and it takes into account the length-scale of the body, the strength of the flow, the viscosity of the fluid etc.
-Therefore, in this notation, we have
-\begin{equation}
-k_{11} = k_{11}^{(s)} k_{11}^{(c)}
-\end{equation}
-These quantities could of course be defined similarly for a collection of objects, as in our paper.
-It is important to note that, in the extraction of $k_{11}^{(c)}$ in our paper, we replace every body with a circle of the same location {\em and the same area}.
-The later point implies that $k_{11}^{(c)}$ represents the component of $k_{11}$ that depends on overall body length-scale, so that what is left, $k_{11}^{(s)}$ does {\em not} depend on length scale, and instead only depends on the detailed shapes of the bodies.
-
-Introducing a similar decomposition of transverse permeability $k_{22}$ and putting everything together yields
-\begin{equation}
-\anis = \frac{k_{11}}{k_{22}} = \frac{ k_{11}^{(s)} k_{11}^{(c)} }{ k_{22}^{(s)} k_{22}^{(c)} }
-= \anis^{(s)} \anis^{(c)}
-\end{equation}
-which is the result used in our paper. We have added a brief explanation in the updated manuscript at the end of Section 4.3.
-\\ \\
-
-\noindent \comment{Reviewer \#1: 
-7. It would be helpful to know (page 10) how the randomized sizes and locations of the bodies are chosen so as they do not overlap.
-\\ }
-
-Great question.
-This is an aspect of the simulation that we regarded as too detailed to fully explain in this manuscript, but it is an interesting aspect that we are happy to explain here.
-In essence, we use a simulated annealing procedure to initialize the configuration of circular bodies.
-We first determine the distribution of circle radii by straightforward sampling (we use a Chi distribution, but this choice is arbitrary) and by using the porosity that is specified.
-Second, we randomly assign the circle centers; many of the circles will overlap (unless we are incredibly lucky).
-Next, we specify fictitious forces that act to repel overlapping bodies and also repel bodies from the domain walls.
-In addition, the force acting on each body has a stochastic component with magnitude, or `temperature', that decreases over the course of the initialization routine.
-Hence, early in the initialization routine, the temperature is high and the random component is large compared to the deterministic forces, but at later stages, the temperature is low and the random component tends to zero.
-This algorithm allows the bodies to jump around substantially to explore different configurations and eventually converge to a configuration in which none overlap.
-Naturally, there are limitations to such an initialization algorithm.
-For example, there exists thresholds for the solid area fraction (that depend on the radius distribution) above which no circle packing is possible.
 \end{document}

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

@@
 
+\noindent
+Thank you for bringing up this point.
+We have no explicitly stated that the computations are two-dimensional in the abstract, the introduction, and in a few other places in the paper.
+We also included a brief discussion at the beginning of Section 3 on modifications that would be necessary for 3D.
+In short, many aspects of the numerical methods (not only the quadrature method) would need to change substantially.
+
 \end{document}

### 2022-12-15 docs/PhysicsPaper/StokesErosion.tex
NM

@@
   \begin{split}
-    \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap 
+    \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap 
       &&\mbox{\em conservation of momentum}, \\
@@
 \end{equation}
-Above, $\UU$ represents the fluid velocity imposed along the outer boundary $\Gamma$, in particular at the inlet and outlet, as well as along the top and bottom walls.
+\edit{The above equations are in dimensionless form, where space has been scaled on a domain length-scale, velocity has been scaled on a characteristic inlet value, and pressure has been scaled on the viscous force-per-unit-area that results from the choices of length and velocity scales.}
+Meanwhile, $\UU$ represents the (dimensionless) fluid velocity imposed along the outer boundary $\Gamma$, in particular at the inlet and outlet, as well as along the top and bottom walls.
 In this work, we impose a {\em uniform} flow profile along $\Gamma$, i.e.~$\UU = (U,0)$, although other choices are possible, for example a Poiseuille profile as employed in previous work~\cite{chiu2020viscous, quaife2018boundary}.
@@
 We will allow the imposed flow speed to change with time $U = U(t)$ to enforce, for example, a desired pressure drop across the flow cell.
-To nondimensionalize the above system, we set the fluid viscosity to unity, $\mu = 1$.
+%To nondimensionalize the above system, we set the fluid viscosity to unity, $\mu = 1$.
 
@@
 \label{Vn0} \\
-\tau &= -\mu \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss,
+\tau &= - \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss,
 	\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
@@
 \end{equation}
-Here, $p$ and $\mu$ represent the pressure field and fluid viscosity as before, with $\mu = 1$ by the non-dimensionalization.
+\edit{Here, $p$ represents the pressure field and $\mu$ represents the fluid viscosity, which is set to unity due to the non-dimensionalization, $\mu=1$.}
 Meanwhile, $\bq = (q_1, q_2)$ represents the {\em specific discharge}, which is the volume of water flowing through a unit cross sectional area of porous media per unit time; $\bq$ relates to the (interstitial) velocity $\uu$, by integrating $\uu$ over a sufficiently small control region and dividing by the total volume (including both fluid and solid) of the region.
@@
 The permeability of the medium is directly related to the drag exerted by the collection of bodies.
-The stress tensor associated with the Stokes equations~\eqref{eqn:StokesEq} is given by $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$, and the Stokes equations can alternatively be expressed as $\grad \cdot \stress = 0$.
+The stress tensor associated with the Stokes equations~\eqref{eqn:StokesEq} is given by $\stress = -p \bvec{I} + \left( \grad \uu + \grad \uu^T \right)$, and the Stokes equations can alternatively be expressed as $\grad \cdot \stress = 0$.
 Integrating over an arbitrary domain $D$ and applying the divergence theorem gives
@@
 \label{drag_press}
-\FD \cdot \ex = \int_{-1}^{1} \left( -p(x,y) + 2 \mu u_x(x,y) \right) \big|_{x=-x_0}^{x=x_0} dy + 
-\int_{-x_0}^{x_0} \mu u_y(x,y) \big|_{y=-1}^{y=1} dx.
+\FD \cdot \ex = \int_{-1}^{1} \left( -p(x,y) + 2 u_x(x,y) \right) \big|_{x=-x_0}^{x=x_0} dy + 
+\int_{-x_0}^{x_0} u_y(x,y) \big|_{y=-1}^{y=1} dx.
 \end{equation}

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

@@
 In short, many aspects of the numerical methods (not only the quadrature method) would need to change substantially.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+- In the introduction, first paragraph, it is stated: ``Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely…" - what does this even mean?
+What determines the longitudinal direction in such a typical material?
+The statement (and the short discussion that follows) seems almost circular to me - the material is more permeable in the direction in which it admits flow?
+That's almost the definition of permeability.
+\\ }
+
+\noindent
+It is the direction of the pressure gradient that primarily determines the direction of flow.
+The direction of the pressure gradient could change with time, and so, in principle, a porous material with fixed microstructure (and hence fixed permeability tensor) could admit flow in any direction.
+For example, a porous material might be isotropic, meaning that it admits flow in the vertical direction just as easily as it does in the horizontal direction, or any direction for that matter.
+The actual flow direction at any given time would thus be determined entirely by the pressure gradient that is imposed.
+As a second example, a porous medium might be composed of slender and primarily vertically-aligned particles.
+This material would preferably admit flow in the vertical direction over the horizontal direction, but if the pressure gradient is horizontal, the flow will be horizontal.
+Hence, the direction of the anisotropy in permeability does not determine the flow direction, although it is an influencing factor.
+
+We have slightly rephrased this statement, removing the terms longitudinal and transversely and replacing them with horizontal and vertical, to prevent confusion.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+- Section 2, page 2, below equations (1): "To nondimensionalize, we set the fluid viscosity to unity, $\mu=1$." This is a lazy way to nondimensionalize.
+The authors have already gone half-way to nondimensionalizing by this stage, without saying so, by choice of the computational domain.
+Why not just do it properly and say what the appropriate scalings for all physical quantities are?
+Then $\mu$ won't appear in any of the equations (which currently have an uncomfortable hybrid feel - are they meant to be dimensionless, or not?).
+\\ }
+
+\noindent
+We have taken the referee's advice by removing $\mu$ from the governing equations and stating the scales used in the non-dimensionalization.
+Please see the revised Section 2.
+We note that we have kept $\mu$ in Eq.~(9), and shortly thereafter set it to unity, because it may be useful for future work to see where the viscosity enters Darcy's law.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+- Section 3.2, first line: "…vorticity, which reduces to shear stress $\tau$ on solid boundaries" - is that right?
+\\ }
+
+\noindent
+Yes, the vorticity reduces to the shear stress, up to a sign, on a no-slip boundary.
+We note that the no-slip part is essential for this to be true.
+It can be seen in 2D by, without loss of generality, taking a horizontal surface and evaluating the vorticity $\omega =  v_x - u_y$ on the no-slip surface.
+By the no-slip assumption, $v_x = 0$, and so $\omega = -u_y$ which is the same, up to a sign, as the shear stress $\tau$.
+For any other alignment of the surface, the coordinate system can simply be rotated.
+Since we use $\abs{\tau}$ in the erosion law, the sign makes no difference.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+- Section 4.1, diagonal permeability tensor.
+I understand why the authors take the approach that they do, and most likely it's justified.
+However, the authors don't ever check the consistency of the diagonal assumption.
+How would they go about checking this?
+Could this be commented on?
+\\ }
+
+\noindent
+This is a great question and one that we have thought about.
+Unfortunately, it would be difficult to check the diagonal assumption in the current computational setup since rotating the configuration of bodies by any angle that is not a multiple of $90^\circ$ does not guarantee the bodies would remain in the square domain.
+Imagining a nice computational domain that is not subject to this limitation is tricky.
+In principle, we could confine the bodies to a circular sub-domain (as opposed to a square sub-domain) with the whole domain, including the buffer region, remaining a rectangle.
+This setup has its own pitfalls though.
+For one, the flow would impinge on the bodies in a non-uniform way.
+For example, the bodies near the left-most and right-most extreme of the circular subdomain would experience the `leading front' of the flow profile.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+- Paragraph below eq.(36) - "keep the outer geometry fixed and rotate the inner configuration of bodies" - in the model introduction, the authors described the "buffer zones" [-3,-1], [1,3] in the x-direction, used to allow the flow to adjust to the presence of the bodies (and presumably give more reliable indicators for the anisotropy measures calculated).
+But the computational domain in the y-direction is only given as [-1,1].
+Do the authors extend it for the y-permeability calculation, to get similarly reliable estimates?
+Or maybe I'm misunderstanding the procedure used.
+\\ }
 

### 2022-12-15 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 Porous media encountered in nature typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
-Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely by a factor of 5--20~\cite{bear1988dynamics, anderson2015applied}.
+Typical materials are more permeable to flow in the \edit{horizontal} direction than \edit{the vertical} by a factor of 5--20~\cite{bear1988dynamics, anderson2015applied}.
 Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plane of deposition~\cite{bear1988dynamics}.

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

@@
 \noindent \comment{Reviewer \#2: 
-- Paragraph below eq.(36) - "keep the outer geometry fixed and rotate the inner configuration of bodies" - in the model introduction, the authors described the "buffer zones" [-3,-1], [1,3] in the x-direction, used to allow the flow to adjust to the presence of the bodies (and presumably give more reliable indicators for the anisotropy measures calculated).
+- Paragraph below eq.(36) - ``keep the outer geometry fixed and rotate the inner configuration of bodies" - in the model introduction, the authors described the ``buffer zones" [-3,-1], [1,3] in the x-direction, used to allow the flow to adjust to the presence of the bodies (and presumably give more reliable indicators for the anisotropy measures calculated).
 But the computational domain in the y-direction is only given as [-1,1].
@@
 
+\noindent
+Please read on to the next sentence to answer your question: ``In practice, it is simpler to keep the outer geometry fixed and rotate the inner configuration of bodies, then simply apply the method from Section 4.1 to measure $k_22$.''
+
+You are correct, if we were to keep the outer geometry fixed and rotate the inner configuration of bodies, then we would need to adjust the buffer region accordingly.
+However, this harry process can be circumvented by instead simply rotating the inner configuration of bodies and keeping the outer geometry, bugger region included, as is.
+Then imposing a horizontal flow in this altered configuration is equivalent to imposting a vertical flow in the original configuration.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+- Page 9, last paragraph of section 4.3: "… for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass.
+Since the configurations resulted from the erosion of initially circular bodies, such a replacement does not lead to any overlap between bodies" - this certainly sounds reasonable, but is it obvious?
+I assume that, depending on the flow, the COM can change during erosion.
+Might there be some non-standard examples where the statement doesn't hold?
+[This is mainly curiosity on my side; for the purposes of publication, if the authors say that overlap never does occur in any simulations then that's fine!]
+\\ }
+
+\noindent
+You are correct that this is not a theorem that we can prove since the COM could in principle move somewhat.
+But it is fairly intuitive that overlaps should not result from this process (since the amount the boundary moves inward would likely dominate any motion of the COM), and, in practice, we observe that overlaps do not result.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+- Results, Section 5.1, Figure 2: Here the authors compare 1/k11 (from the Darcy law) with F1/(4U) (from the Stokes calculations).
+Why don't they make a similar comparison for k22, since they also compute the flow in the transverse configuration?
+\\ }
+
+\noindent
+Why would we do this? Just to be painstakingly thorough?
+
 \end{document}

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

@@
 \noindent
-Why would we do this? Just to be painstakingly thorough?
+The purpose of the drag-permeability comparison is to test the connection between the microscopic Stokes description and the coarse-grained Darcy description.
+We believe that purpose is adequately achieved with the data shown in the Figure.
+Computing $F_2$ would be redundant and likely confusing to some for the following reason.
+Even with the original horizontal flow, there is typically a non-zero component of vertical drag, due to random up-down asymmetries of the bodies.
+Hence it might be unclear if $F_2$ refers to the vertical component of force in the original flow configuration or the component measured with the rotated flow.
+Of course, this could all be explained but it would add a significant amount of text, and for what purpose?
+We have already established the micro-macro connection with $F_1$.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+- Results, Section 5.2: What's the rationale for considering trends as the number of bodies M is increased?
+I'd have preferred to see more simulations (= better statistics) for large values of M, where the Darcy model is more applicable.
+Is there a specific reason to look at small M-values?
+Variations with M seems an odd choice to study.
+\\ }
+
+\noindent
+It does not seem odd to us.
+Varying the number of bodies, $M$, is one way (perhaps the best way) to alter the permeability while keeping the porosity fixed.
+In the study of porous media, considerable attention is given to characterizing both a medium's porosity and it's permeability, as these two properties can change independent of one another due to microstructure.
+Studying few instances of small $M$ would not permit us to study more instances of large $M$ since the computational time required for the large-$M$ simulations is so much larger.
 

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

@@
 It does not seem odd to us.
-Varying the number of bodies, $M$, is one way (perhaps the best way) to alter the permeability while keeping the porosity fixed.
-In the study of porous media, considerable attention is given to characterizing both a medium's porosity and it's permeability, as these two properties can change independent of one another due to microstructure.
-Studying few instances of small $M$ would not permit us to study more instances of large $M$ since the computational time required for the large-$M$ simulations is so much larger.
+Varying the number of bodies, $M$, is one way (perhaps the best way) to alter the permeability of a medium while keeping it's porosity fixed.
+In the study of porous media, considerable attention is given to characterizing both a medium's porosity and it's permeability, as these two properties can be altered independently by altering the microstructure.
+Studying fewer instances of small $M$ would not permit us to study more instances of large $M$ since the computational time required for the large-$M$ simulations is so much larger.
+
+We remark that one key discovery we made was the late surge in configurational anisotropy for simulations featuring a large number of bodies, $M \ge 60$, and how this connects to channelization.
+Had we not varied $M$, we could not have discovered the threshold of 60 required for this phenomenon.
+\\ \\
+
+\noindent \comment{Reviewer \#2: 
+In addition, I found a few typos as I read:
+\\ }
 

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 1 Response/Ref1.tex
NM

@@
 
-We would like to thank the referee for reviewing our work ....
-
-Below we respond to each of the referee's comments in sequence. For your convenience, we are submitting a version of the revised manuscript with the changes highlighted. \\ \\ \\
+We would like to thank the referee for the careful and insightful review of our work.
+The referee's comments have gone a long way in helping us to improve the clarity and quality of the manuscript.
+Below we respond to each of the referee's comments in sequence.
+For your convenience, we are submitting a version of the revised manuscript with the changes highlighted.
+\\ \\
 
@@
 For example, there exists thresholds for the solid area fraction (that depend on the radius distribution) above which no circle packing is possible.
-
-We have added a brief explanation of this initialization algorithm to the updated manuscript. stuff
+We have added a brief explanation of this initialization algorithm to the updated manuscript at the end of Section 3.2.
 

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 1 Response/Ref1.tex
NM

@@
 \noindent
-Thank you for bring up this point.
+Thank you for bringing up this point.
 To explain our intent, boundary-integral equations can be considered `highly accurate' because of their spectral accuracy (i.e.
@@
 \noindent
-This is a good question, and one that is much more complex than it appears.
+This is a good question, and one that is more complex than it appears.
 In short, the range of Reynolds numbers found in natural porous media is too vast to summarize by a typical value.
@@
 This is a good question and, admittedly, a point that was glossed over in the original manuscript.
-The reason that total anisotropy can be regarded as the produce of shape and configurational anisotropy essential boils down to a dimensional analysis argument.
+The reason that total anisotropy can be regarded as the product of shape and configurational anisotropy essential boils down to a dimensional analysis argument.
 

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

@@
 
+\noindent
+We have corrected all of these typos. Many thanks for spotting them!
+
 \end{document}

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 1 Response/Ref1.tex
NM

@@
 Of course, in our manuscript, we consider the Stokes limit of the drag, for which there is a different formula, but the principle remains that it can be decomposed into a dimensional component (that depends on the length-scale of the object, fluid properties, the flow speed, etc.) and a dimensionless coefficient to represent the detailed shape of the object.
-Likewise, the permeability associated with a single object can be represented in a similar way, where the dimensionless coefficient could be considered the `shape' permeability, $k_{11}^{(s)}$, analogous to the shape anisotropy defined in our manuscript.
+Likewise, the permeability associated with a single object can be represented in a similar way, where the dimensionless coefficient, e.g.~the $C_D$, could be considered the `shape' permeability, $k_{11}^{(s)}$.
 That is, the value $k_{11}^{(s)}$ associated with a single body depends on the detailed shape of that body, and not on its overall size, or the viscosity of the fluid, or the flow speed, etc.
@@
 \end{equation}
-which is the result used in our paper. We have added a brief explanation in the updated manuscript at the end of Section 4.3.
+which is the result used in our paper. We have added a brief explanation of all this in the updated manuscript at the end of Section 4.3.
 \\ \\
@@
 Great question.
-This is an aspect of the simulation that we had regarded as too detailed to fully explain in this manuscript, but it is an interesting aspect that we are happy to explain here.
-In essence, we use a simulated annealing procedure to initialize the configuration of circular bodies.
-We first determine the distribution of circle radii by straightforward sampling (we use a Chi distribution, but this choice is arbitrary) and by using the porosity that is specified.
-Second, we randomly assign the circle centers; many of the circles will overlap (unless we are incredibly lucky).
+This is an aspect of the simulation that we had initially regarded as too detailed to fully explain in the manuscript, but it is an interesting aspect that we are happy to explain here, and we have added a brief explanation in the updated manuscript.
+In essence, we use a simulated annealing algorithm to initialize the configuration of circular bodies.
+We first determine the distribution of circle radii by straightforward sampling (we use a Chi distribution, but this choice is arbitrary).
+Second, we randomly assign the circle centers; many of the circles will overlap, unless we are incredibly lucky.
 Next, we specify fictitious forces that act to repel overlapping bodies and also repel bodies from the domain walls.
-In addition, the force acting on each body has a stochastic component with magnitude, or `temperature', that decreases over the course of the initialization routine.
+In addition, we imbue this force with a stochastic component with magnitude, or `temperature', that decreases over the course of the initialization routine.
 Hence, early in the initialization routine, the temperature is high and the random component is large compared to the deterministic forces, but at later stages, the temperature is low and the random component tends to zero.
@@
 Naturally, there are limitations to such an initialization algorithm.
-For example, there exists thresholds for the solid area fraction (that depend on the radius distribution) above which no circle packing is possible.
+For example, there exists thresholds for the solid area fraction (depending on the radius distribution) above which no circle packing is possible.
 We have added a brief explanation of this initialization algorithm to the updated manuscript at the end of Section 3.2.

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

@@
 \noindent
-Thank you for bringing this stylistic point to our attention. We have taken the referee's advice and moved many of the more detailed equations into an appendix. 
+Thank you for bringing these stylistic points to our attention. We have taken the referee's advice and moved many of the more detailed equations into an appendix. 
 \\ \\
@@
 \noindent
-This is a good point. In the updated manuscript, we have included a comment after Eqs.~(2)--(3) that this law will be slightly modified in Section 3.2 for the sake of numerical stability.
+This is a good point. In the updated manuscript, we have included a comment after Eqs.~(2)--(3) that the erosion law will be slightly modified in Section 3.2 for the sake of numerical stability.
 \\ \\
@@
 \noindent \comment{Reviewer \#2: 
-- Bottom of p11: "statistical analysis of many simulations will show" - this sounds speculative.
+- Bottom of p11: ``statistical analysis of many simulations will show" - this sounds speculative.
  I interpreted this on first reading to be the authors' conjecture, rather than something they actually do in the present paper.
@@
 Thank you for bringing up this point.
-We have no explicitly stated that the computations are two-dimensional in the abstract, the introduction, and in a few other places in the paper.
+We have now explicitly stated that the computations are two-dimensional in the abstract, the introduction, and in a few other places in the paper.
 We also included a brief discussion at the beginning of Section 3 on modifications that would be necessary for 3D.
@@
 \noindent
-It is the direction of the pressure gradient that primarily determines the direction of flow.
+It is the direction of the pressure gradient that determines the direction of flow.
 The direction of the pressure gradient could change with time, and so, in principle, a porous material with fixed microstructure (and hence fixed permeability tensor) could admit flow in any direction.
@@
 \noindent \comment{Reviewer \#2: 
-- Section 2, page 2, below equations (1): "To nondimensionalize, we set the fluid viscosity to unity, $\mu=1$." This is a lazy way to nondimensionalize.
+- Section 2, page 2, below equations (1): ``To nondimensionalize, we set the fluid viscosity to unity, $\mu=1$." This is a lazy way to nondimensionalize.
 The authors have already gone half-way to nondimensionalizing by this stage, without saying so, by choice of the computational domain.
@@
 \noindent
-We have taken the referee's advice by removing $\mu$ from the governing equations and stating the scales used in the non-dimensionalization.
+We have taken the referee's advice and removed $\mu$ from the governing equations and also stated the scales used in the non-dimensionalization.
 Please see the revised Section 2.
@@
 \noindent \comment{Reviewer \#2: 
-- Section 3.2, first line: "…vorticity, which reduces to shear stress $\tau$ on solid boundaries" - is that right?
+- Section 3.2, first line: ``…vorticity, which reduces to shear stress $\tau$ on solid boundaries" - is that right?
 \\ }
@@
 Yes, the vorticity reduces to the shear stress, up to a sign, on a no-slip boundary.
-We note that the no-slip part is essential for this to be true.
+We note that the no-slip part is essential for this statement to be true.
 It can be seen in 2D by, without loss of generality, taking a horizontal surface and evaluating the vorticity $\omega =  v_x - u_y$ on the no-slip surface.
@@
 \noindent
-This is a great question and one that we have thought about.
+This is a great question and one that we have given a fair amount of thought to.
 Unfortunately, it would be difficult to check the diagonal assumption in the current computational setup since rotating the configuration of bodies by any angle that is not a multiple of $90^\circ$ does not guarantee the bodies would remain in the square domain.
@@
 For example, the bodies near the left-most and right-most extreme of the circular subdomain would experience the `leading front' of the flow profile.
+In our mind, this would be worse than the left-most (or right-most) column of bodies experiencing the leading front, since in that situation, the effect is spread out over more bodies in a uniform way.
 \\ \\
@@
 \noindent
-Please read on to the next sentence to answer your question: ``In practice, it is simpler to keep the outer geometry fixed and rotate the inner configuration of bodies, then simply apply the method from Section 4.1 to measure $k_22$.''
+Please read on to the next sentence to answer your question: ``In practice, it is simpler to keep the outer geometry fixed and rotate the inner configuration of bodies, then simply apply the method from Section 4.1 to measure $k_{22}$.''
 
 You are correct, if we were to keep the outer geometry fixed and rotate the inner configuration of bodies, then we would need to adjust the buffer region accordingly.
-However, this harry process can be circumvented by instead simply rotating the inner configuration of bodies and keeping the outer geometry, bugger region included, as is.
-Then imposing a horizontal flow in this altered configuration is equivalent to imposting a vertical flow in the original configuration.
+However, this harry process can be circumvented by instead simply rotating the inner configuration of bodies and keeping the outer geometry, buffer region included, as is.
+Then imposing a horizontal flow in this altered configuration is equivalent to imposing a vertical flow in the original configuration.
 \\ \\

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

@@
 \noindent \comment{Reviewer \#2: 
-- Page 9, last paragraph of section 4.3: "… for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass.
+- Page 9, last paragraph of section 4.3: ``… for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass.
 Since the configurations resulted from the erosion of initially circular bodies, such a replacement does not lead to any overlap between bodies" - this certainly sounds reasonable, but is it obvious?
@@
 You are correct that this is not a theorem that we can prove since the COM could in principle move somewhat.
-But it is fairly intuitive that overlaps should not result from this process (since the amount the boundary moves inward would likely dominate any motion of the COM), and, in practice, we observe that overlaps do not result.
+But it is fairly intuitive that overlaps should not result from this process, since the amount the boundary moves inward would likely dominate any motion of the COM.
+In practice, we observe that overlaps do not result from this process.
 \\ \\
@@
 The purpose of the drag-permeability comparison is to test the connection between the microscopic Stokes description and the coarse-grained Darcy description.
-We believe that purpose is adequately achieved with the data shown in the Figure.
-Computing $F_2$ would be redundant and likely confusing to some for the following reason.
-Even with the original horizontal flow, there is typically a non-zero component of vertical drag, due to random up-down asymmetries of the bodies.
+We believe that purpose is adequately achieved with the $F_1$ data shown in the Figure.
+Computing $F_2$ would be redundant and possibly confusing to some readers for the following reason.
+Even in the original horizontal flow, there is typically a non-zero component of vertical drag, due to random up-down asymmetries of the bodies.
 Hence it might be unclear if $F_2$ refers to the vertical component of force in the original flow configuration or the component measured with the rotated flow.
@@
 Varying the number of bodies, $M$, is one way (perhaps the best way) to alter the permeability of a medium while keeping it's porosity fixed.
-In the study of porous media, considerable attention is given to characterizing both a medium's porosity and it's permeability, as these two properties can be altered independently by altering the microstructure.
+In the study of porous media, considerable attention is given to characterizing both a medium's porosity and it's permeability, as these two properties can be altered independently by changing the microstructure.
 Studying fewer instances of small $M$ would not permit us to study more instances of large $M$ since the computational time required for the large-$M$ simulations is so much larger.
 
-We remark that one key discovery we made was the late surge in configurational anisotropy for simulations featuring a large number of bodies, $M \ge 60$, and how this connects to channelization.
+We remark that one key discovery we made was the late surge in configurational anisotropy for simulations featuring a large number of bodies, $M \ge 60$, and how this configurational anisotropy connects to channelization.
 Had we not varied $M$, we could not have discovered the threshold of 60 required for this phenomenon.

### 2022-12-15 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies.
-The more recent Cauchy reformulation of the BIE and the associated quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}.
+The more recent Cauchy reformulation of the BIE and the associated quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulations of dense suspensions of erodable bodies~\cite{chiu2020viscous}.
 Though the governing Stokes equations are linear, the nonlinear feedback between evolving microstructure and flow gives rise to highly complex and anisotropic configurations.
@@
 \Vn &= \CE \, \abs{\tau}, 
-	\hspace{88pt} \xx \in \gamma, &&\mbox{\em erosion model}, 
+	\hspace{82pt} \xx \in \gamma, &&\mbox{\em erosion model}, 
 \label{Vn0} \\

### 2022-12-20 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \newcommand{\tocite}{ {\color{blue}(to cite)} }
-\newcommand{\nick}[1]{ {\color{red} #1} }
-\newcommand{\edit}[1]{{\color{red} #1}}
+
+\newcommand{\red}[1]{{\color{red} #1}}
+\newcommand{\black}[1]{#1}
+\newcommand{\edit}[1]{\red{#1}}
 
@@
 Porous media encountered in nature typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others.
-Typical materials are more permeable to flow in the \edit{horizontal} direction than \edit{the vertical} by a factor of 5--20~\cite{bear1988dynamics, anderson2015applied}.
-Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plane of deposition~\cite{bear1988dynamics}.
+\edit{Most commonly, this anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plane of deposition~\cite{bear1988dynamics}.
+This idea is supported by the observation that natural materials are typically more permeable in the horizontal direction than the vertical by a factor of 5--20~\cite{bear1988dynamics, anderson2015applied}.}
 Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work.

### 2023-01-08 docs/PhysicsPaper/StokesErosion.tex
NM

@@
 \newcommand{\black}[1]{#1}
-\newcommand{\edit}[1]{\red{#1}}
+\newcommand{\edit}[1]{\black{#1}}
 
@@
 
-% Maybe HOW fluid-mechanical erosion creates anisotropic porous media.
-%\title{Fluid-mechanical erosion generates anisotropy in porous media}
-%\title{Erosion leads to anisotropy in a porous medium}
-%\title{The development of anisotropy in an eroding porous medium}
-
 \author[Colgate]{Nicholas J.~Moore}
@@
 \maketitle
-
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
-% dematerialize, disintegrate
-% internal, permeating, intervening
 
@@
 For example, horizontally-oriented channels are clearly visible in the third and fourth frames, and these contribute to the overall anisotropy of the medium.
-
-%We employ the Stokes system for two reasons:~(1) this flow regime is appropriate for many groundwater applications \cite{bear1988dynamics}; and (2) the linearity of the Stokes system provides
 
@@
 The empty space to the left and right of $[-1,1] \times [-1,1]$ serve as buffer regions to allow the flow profile imposed at the inlet and outlet to gradually adjust to the presence of the bodies.
-The equations governing the velocity $\uu = (u,v)$ and pressure $p$ of the fluid consist of the incompressible, Stokes equations coupled to boundary conditions: \begin{equation}
+The equations governing the velocity $\uu = (u,v)$ and pressure $p$ of the fluid consist of the incompressible, Stokes equations coupled to boundary conditions:
+\begin{equation}
 \label{eqn:StokesEq}
@@
 We will allow the imposed flow speed to change with time $U = U(t)$ to enforce, for example, a desired pressure drop across the flow cell.
-%To nondimensionalize the above system, we set the fluid viscosity to unity, $\mu = 1$.
 
@@
 The parameter $\bvec{k}$ represents the {\em permeability} of the porous medium, which generally takes the form of a rank-2 tensor to permit different propensities to flow in different directions, i.e.~medium anisotropy.
-%The permeability may vary in space and will certainly vary in time as the bodies erode.
 
@@
 and measurements of the upstream and downstream pressures.
-
-%Since $\bq$ is a volume-average of the tracer velocity, $\qavg$ can be equivalently obtained by averaging the tracer velocity, which is how we will measure this quantity in the simulations.
 
@@
 
-%verifying the relationship \eqref{perm_drag}, as will be done in Fig.~\ref{fig2}, validates a number of approximations made in the coarse-grained approach, such as (1) the homogenization of the flow field implicit in Darcy's law \eqref{eqn:Darcy}; (2) the calculation of the permeability from measurements of the flow rate and upstream/downstream pressures through \eqref{eqn:k11}.
-
 %-------------------------------------------------------------------%
@@
 
-%
-%Since all of the individual shapes are identical and isotropic (i.e.~circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$.
-The total anisotropy, meanwhile, is the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured.
-We can therefore deduce the shape anisotropy through $\anis_S = \anis/\anis_C$.
-
 %-------------------------------------------------------------------%
 \subsection{Tortuosity}
-%
-%We need to write this section.
-%Could reference Souzy et al. JFM article on velocity distributions in porous media \cite{souzy2020velocity}
 
@@
 Identical to how we calculate the transverse permeability, we rotate the configuration of eroded bodies by 90 degrees to compute a transverse tortuosity $T_2$.
-
-% NOTE: I explain what ratio we compute in the results section, so we don't need to do it here.
-%Then, another measure of the anisotropy is
-%\begin{align}
- % \anistort = T_2/T_1.
-%\end{align}
-%\todo[inline]{Might eliminate this line so that we don't double-use anisotropy. In any case, I think $(T_2-1)/(T_1-1)$ might be more useful. Will give it thought.}
-%As in the permeability definition of anisotropy, the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one.
-As this configuration erodes, the streamlines in the longitudinal direction are expected to less tortuous than those in the transverse direction, yielding $\anis > 1$.
 
@@
 We analyze runs having $M$ = 20, 40, 60, 80, and 100 bodies, with at least three different instances of each.
-This data set represents roughly 2,100 hours of computational time.
+\edit{We remark that varying $M$ permits us to study different initial permeabilities while keeping the initial porosity fixed at $\varphi = 0.4$.}
+The entire data set represents roughly 2,100 hours of computational time.
 
